### 2021-08-31 main.tex
:pencil: Add remark on backscatter modulation

\documentclass[journal]{IEEEtran}

\usepackage{adjustbox}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{array}
\usepackage{circuitikz}
\usepackage{cite}
\usepackage{colortbl}
\usepackage{environ}
\usepackage{grffile}
\usepackage{hyperref}
\usepackage{import}
\usepackage{mathtools}
\usepackage{microtype}
\usepackage{multirow}
\usepackage{pgffor}
\usepackage{pgfplots}
\usepackage{siunitx}
\usepackage{stfloats}
\usepackage{tikz}
\usepackage{url}
\usepackage{xcolor}
\usepackage[T1]{fontenc}
\usepackage[caption=false,font=footnotesize,subrefformat=parens,labelformat=parens]{subfig}
\usepackage[short]{optidef}
% \usepackage[subtle]{savetrees}

\interdisplaylinepenalty=2500
\pgfplotsset{compat=newest}
\usepgfplotslibrary{patchplots}
\newtheorem{proposition}{Proposition}
\newtheorem{remark}{Remark}
\DeclareSIUnit{\belm}{Bm}
\DeclareSIUnit{\dBm}{\deci\belm}
\DeclareSIUnit{\beli}{Bi}
\DeclareSIUnit{\dBi}{\deci\beli}
\ctikzset{american}
\usetikzlibrary{arrows,matrix,positioning,patterns}

\algrenewcommand{\algorithmicwhile}{\textbf{While}}
\algrenewcommand{\algorithmicif}{\textbf{If}}
\algrenewcommand{\algorithmicthen}{\textbf{Then}}
\algrenewcommand{\algorithmicelse}{\textbf{Else}}
\algrenewcommand{\algorithmicend}{\textbf{End}}
\algrenewcommand{\algorithmicrepeat}{\textbf{Repeat}}
\algrenewcommand{\algorithmicuntil}{\textbf{Until}}

\begin{document}
	\title{Backscatter Modulation Design for Symbiotic Radio Networks}
	\maketitle

	\begin{section}{Backscatter Model}
		\begin{subsection}{Backscatter Principles}
			\begin{figure}[!t]
				\centering
				\subfloat[Backscatter antenna]{
					\resizebox{0.3\columnwidth}{!}{
						\begin{circuitikz}[transform shape]
							\draw (0,0) node[bareantenna](bareantenna){};
							\draw (bareantenna.west) ++(-1.5,0) node[waves](WI){};
							\draw (WI.north east) ++(0.25,0) node[]{$\vec{E}_{\mathrm{I}}$};
							\draw (WI.south east) ++(0.25,0) node[]{$\vec{H}_{\mathrm{I}}$};
							\draw (bareantenna.east) ++(0.875,0) node[waves](WR){};
							\draw (WR.north east) ++(0.25,0) node[]{$\vec{E}_i$};
							\draw (WR.south east) ++(0.25,0) node[]{$\vec{H}_i$};
							\draw (bareantenna)
								to [R=$Z_{\mathrm{A}}$] ++(0,-2)
								to [R=$Z_i$] ++(3,0) node[ground](GND){};
						\end{circuitikz}
					}
					\label{ci:backscatter_antenna}
				}
				\subfloat[Tag equivalent circuit]{
					\resizebox{0.65\columnwidth}{!}{
						\begin{circuitikz}[transform shape]
							\draw (0,0) coordinate(O)
								to [sV,l=$V_0$] ++(0,1.5)
								to [L,l=$X_{\mathrm{A}}$] ++(0,1.5)
								to [R=$R_{\mathrm{R}}$,-*] ++(3,0) coordinate(AM)
								to [sI,l_=$I_0$,-*] ++(0,-3)
								to [short] (O);
							\draw (AM)
								to [short] ++(0.5,0)
								to [L,l=$X_i^{\mathrm{M}}$,-*] ++(3,0) coordinate(M)
								to [R=$R_{i,2}^{\mathrm{M}}$] ++(3,0) coordinate(MH);
							\draw (M)
								to [R=$R_{i,1}^{\mathrm{M}}$,-*] ++(0,-3);
							\draw (MH)
								to [D,-*] ++(1.5,0) coordinate(H)
								to [C=$X_{\mathrm{H}}$,-*] ++(0,-3);
							\draw (H)
								to [short] ++(1.5,0)
								to [R=$R_{\mathrm{C}}$] ++(0,-3)
								to [short] (O);

							\draw [blue,dashed] (-1.25,-0.5) rectangle (3.5,3.75);
							\draw [yellow,dashed] (4,-0.5) rectangle (9,3.75);
							\draw [red,dashed] (9.5,-0.5) rectangle (13.5,3.75);

							\draw [blue] (1.125,4) node[]{Antenna};
							\draw [yellow] (6.5,4) node[]{Modulator};
							\draw [red] (11.5,4) node[]{Harvester + Chip};

							\draw (3.375,2.675) to [short] (3.375,3.175) to [short] (3.25,3.175) to [short,i_=$Z_{\mathrm{A}}$] (3.125,3.175);
							\draw (4.125,-0.125) to [short] (4.125,0.375) to [short] (4.25,0.375) to [short,i=$Z_i$] (4.375,0.375);
							\draw (9.625,-0.125) to [short] (9.625,0.375) to [short] (9.75,0.375) to [short,i=$Z_{\mathrm{H}}$] (9.875,0.375);
						\end{circuitikz}
					}
					\label{ci:tag_equivalent_circuit}
				}
				\caption{The backscatter antenna behaves as a constant power source. In the tag equivalent circuit, the blue, yellow and red block represent respectively the lossless minimum scattering antenna \cite{Huang2021}, the dual-load matching network as modulator \cite{Ebrahimi-Asl2018}, and the harvester feeding the chip \cite{Clerckx2016a}.}
				\label{fi:tag}
			\end{figure}
			Consider a bistatic backscatter system that consists of an excitation source, a backscatter reader, and a passive tag. The excitation source generates a carrier wave signal, the backscatter reader detects the tag message, and the tag employs the impinging electromagnetic wave for information modulation and energy harvesting. A typical passive tag consists of a backscatter antenna, a matching network, an energy harvester, and on-chip components (e.g., microcontroller, memory, sensor, and integrated receiver\footnote{For example, a compact-size integrated receiver was prototyped in \cite{Kim2021a} to perform pulse position demodulation by an envelope detector. It enables coordination, synchronization, and reflection pattern control.}). The backscatter antenna behaves as a constant power source, where the voltage is induced by the incident electric field $\vec{E}_{\mathrm{I}}$ and the current is induced by the incident magnetic field $\vec{H}_{\mathrm{I}}$ \cite{Paul2006}. As shown in Fig.~\subref*{ci:backscatter_antenna}, a portion of the incident power is absorbed by the tag while the remaining is backscattered to the space. The backscattered signal can be decomposed into the \emph{structural mode} component and the \emph{antenna mode} component \cite{Hansen1989}. The former is fixed and depends on the antenna geometry and material properties\footnote{We assume the structural mode reflection can be modeled as part of the environment multipath and covered by channel estimation \cite{Boyer2014}.}, while the latter is adjustable and depends on the mismatch of the antenna and load impedance. Hence, the equivalent reflection coefficient at tag state $i$ is defined as\footnote{We assume the linear backscatter where $\Gamma_i$ is irrelevant to the incident electromagnetic field at the tag \cite{Dobkin2012}.}
			\begin{equation}
				\Gamma_i = \frac{Z_i - Z_{\mathrm{A}}^*}{Z_i + Z_{\mathrm{A}}},
				\label{eq:reflection_coefficient}
			\end{equation}
			where $Z_i = R_i + \jmath X_i$ is the antenna load impedance at state $i$, $Z_{\mathrm{A}} = R_{\mathrm{R}} + R_{\mathrm{loss}} + \jmath X_{\mathrm{A}}$ is the antenna input impedance, $R_{\mathrm{R}}$ is the radiation resistance that measures the antenna energy efficiency, $R_{\mathrm{loss}}$ is the loss resistance that models the ohmic or dielectric loss, and $X_{\mathrm{A}}$ is the antenna reactance \cite{Huang2021}.
			\begin{remark}
				The reflection coefficient plays an important role in various network designs. For example, $\Gamma_i = 0$ (perfect matching) achieves maximum power transfer that is optimal for Wireless Power Transfer (WPT), $\lvert \Gamma_i \rvert = 1$ (perfect mismatching) achieves fully signal reflection that is optimal for Intelligent Reflecting Surface (IRS), and $\Gamma_i \ne \Gamma_j$ (adjustable matching) enables backscatter modulation.
			\end{remark}
		\end{subsection}

		\begin{subsection}{Backscatter Modulation}
			Tags perform backscatter modulation by switching the load impedance between different states. For $M$-ary Phase Shift Keying (PSK), the reflection coefficient $\Gamma_i$ maps to the desired signal constellation point $c_i$ as \cite{Thomas2012a}
			\begin{equation}
				\Gamma_i = \alpha c_i = \alpha e^{\jmath \left(\frac{2 \pi i}{M} + \phi\right)},
				\label{eq:backscatter_modulation}
			\end{equation}
			where $\alpha \in [0,1]$ is the reflection efficiency at a given direction, and $\phi$ is a fixed phase offset.
			\begin{remark}
				For passive tags, the reflection efficiency $\alpha$ controls the tradeoff between the backscatter strength and harvestable power. Interestingly, when $\alpha = 1$, the reflection coefficient set $\{\Gamma_i\}$ of the $M$-PSK backscatter coincides with that of an ideal discrete $M$-state uniform IRS. The optimal strategy for the IRS is to choose one reflection state with probability \num{1} to boost the equivalent channel, while the optimal strategy for the modulator is to utilize all constellation points with equal probability. It inspires one to adaptively design the p.m.f. of tag symbols to jointly benefit the backscatter modulation and passive beamforming.
			\end{remark}
		\end{subsection}
	\end{section}

	\bibliographystyle{IEEEtran}
	\bibliography{IEEEabrv,library.bib}
\end{document}

### 2021-09-01 main.tex
:pencil: Update manuscript

@@
 \ctikzset{american}
-\usetikzlibrary{arrows,matrix,positioning,patterns}
+\usetikzlibrary{arrows,calc,matrix,patterns,positioning}
+
+\makeatletter
+\tikzset{
+	block/.style={draw,rectangle,align=center},
+    from/.style args={#1 to #2}{
+        above right={0cm of #1},
+        /utils/exec=\pgfpointdiff
+            {\tikz@scan@one@point\pgfutil@firstofone(#1)\relax}
+            {\tikz@scan@one@point\pgfutil@firstofone(#2)\relax},
+        minimum width/.expanded=\the\pgf@x,
+        minimum height/.expanded=\the\pgf@y
+	}
+}
+\makeatother
 
@@
 				\centering
-				\subfloat[Backscatter antenna]{
-					\resizebox{0.3\columnwidth}{!}{
+				\subfloat[Block diagram]{
+					\resizebox{0.6\columnwidth}{!}{
+						\begin{circuitikz}[transform shape]
+							\coordinate (O) at (0,0);
+							\node[block,from={O to $(O) + (6.375,3.25)$}](T){};
+							\draw (0,1.75)
+								to[short] ++(-0.75,0)
+								to[short] ++(0,0.75) node[bareantenna](A){};
+							\draw (0,1.75)
+								to[short,-*] ++(0.25,0) coordinate(J);
+							\draw (J)
+								to[short] ++(0,1)
+								to[short] ++(0.5,0) coordinate(J1);
+							\node[block,from={$(J1) + (0,-0.25)$ to $(J1) + (2.5,0.25)$}](R){Rectifier};
+							\draw (J)
+								to[short] ++(0.5,0) coordinate(J2);
+							\node[block,from={$(J2) + (0,-0.25)$ to $(J2) + (2.5,0.25)$}](D){Demodulator};
+							\draw (J)
+								to[short] ++(0,-1)
+								to[short] ++(0.5,0) coordinate(J3)
+								to [vR,mirror,invert,/tikz/circuitikz/bipoles/length=1cm] ++(1.75,0) node[ground,rotate=90]{};
+							\node[block,from={$(J3) + (0,-0.25)$ to $(J3) + (2.5,0.25)$},draw=none](M){};
+							\draw ($(J3) + (0,-0.25)$) rectangle ($(J3) + (2.5,0.25)$);
+							\draw ($(J3) + (1.25,-0.5)$) node[]{Modulator};
+							\draw[-{Latex[length=2mm]}] (R.east) -- ++(0.75,0);
+							\draw[-{Latex[length=2mm]}] (D.east) -- ++(0.75,0);
+							\draw[{Latex[length=2mm]}-] (M.east) -- ++(0.75,0);
+							\node[block,from={$(R.east) + (0.75,-0.25)$ to $(R.east) + (2.875,0.25)$}](P){Power buffer};
+							\node[block,from={$(M.east) + (0.75,-0.25)$ to $(D.east) + (2.875,0.25)$}](S){Digital\\section};
+							\draw[dashed,-{Latex[length=2mm]}] (P.south) to (S.north);
+							\coordinate (F1) at ($(P.south)!0.5!(S.north)$);
+							\coordinate (F2) at ($(D.east)!0.5!(S.west)$);
+							\coordinate (F3) at ($(D.south)!0.5!(M.north)$);
+							\draw[dashed] (F1) to (F1-|D.north);
+							\draw[dashed,-{Latex[length=2mm]}] (F1-|D.north) to (D.north);
+							\draw[dashed] (F1-|F2) to (F2|-F3) to (M|-F3);
+							\draw[dashed,-{Latex[length=2mm]}] (M|-F3) to (M.north);
+						\end{circuitikz}
+					}
+					\label{fi:block_diagram}
+				}
+				\subfloat[One-port network model]{
+					\resizebox{0.35\columnwidth}{!}{
 						\begin{circuitikz}[transform shape]
@@
 								to [R=$Z_{\mathrm{A}}$] ++(0,-2)
-								to [R=$Z_i$] ++(3,0) node[ground](GND){};
+								to [R=$Z_i$] ++(2,0) node[ground]{};
 						\end{circuitikz}
 					}
-					\label{ci:backscatter_antenna}
+					\label{fi:one_port_network_model}
 				}
-				\subfloat[Tag equivalent circuit]{
-					\resizebox{0.65\columnwidth}{!}{
-						\begin{circuitikz}[transform shape]
-							\draw (0,0) coordinate(O)
-								to [sV,l=$V_0$] ++(0,1.5)
-								to [L,l=$X_{\mathrm{A}}$] ++(0,1.5)
-								to [R=$R_{\mathrm{R}}$,-*] ++(3,0) coordinate(AM)
-								to [sI,l_=$I_0$,-*] ++(0,-3)
-								to [short] (O);
-							\draw (AM)
-								to [short] ++(0.5,0)
-								to [L,l=$X_i^{\mathrm{M}}$,-*] ++(3,0) coordinate(M)
-								to [R=$R_{i,2}^{\mathrm{M}}$] ++(3,0) coordinate(MH);
-							\draw (M)
-								to [R=$R_{i,1}^{\mathrm{M}}$,-*] ++(0,-3);
-							\draw (MH)
-								to [D,-*] ++(1.5,0) coordinate(H)
-								to [C=$X_{\mathrm{H}}$,-*] ++(0,-3);
-							\draw (H)
-								to [short] ++(1.5,0)
-								to [R=$R_{\mathrm{C}}$] ++(0,-3)
-								to [short] (O);
-
-							\draw [blue,dashed] (-1.25,-0.5) rectangle (3.5,3.75);
-							\draw [yellow,dashed] (4,-0.5) rectangle (9,3.75);
-							\draw [red,dashed] (9.5,-0.5) rectangle (13.5,3.75);
-
-							\draw [blue] (1.125,4) node[]{Antenna};
-							\draw [yellow] (6.5,4) node[]{Modulator};
-							\draw [red] (11.5,4) node[]{Harvester + Chip};
-
-							\draw (3.375,2.675) to [short] (3.375,3.175) to [short] (3.25,3.175) to [short,i_=$Z_{\mathrm{A}}$] (3.125,3.175);
-							\draw (4.125,-0.125) to [short] (4.125,0.375) to [short] (4.25,0.375) to [short,i=$Z_i$] (4.375,0.375);
-							\draw (9.625,-0.125) to [short] (9.625,0.375) to [short] (9.75,0.375) to [short,i=$Z_{\mathrm{H}}$] (9.875,0.375);
-						\end{circuitikz}
-					}
-					\label{ci:tag_equivalent_circuit}
-				}
-				\caption{The backscatter antenna behaves as a constant power source.
-In the tag equivalent circuit, the blue, yellow and red block represent respectively the lossless minimum scattering antenna \cite{Huang2021}, the dual-load matching network as modulator \cite{Ebrahimi-Asl2018}, and the harvester feeding the chip \cite{Clerckx2016a}.}
+				\caption{For a passive tag, the rectifier and demodulator rely on the incident electromagnetic wave for energy harvesting and downlink information decoding, while the load-switcher manipulate the reradiated signal for backscatter modulation.}
 				\label{fi:tag}
 			\end{figure}
-			Consider a bistatic backscatter system that consists of an excitation source, a backscatter reader, and a passive tag.
-The excitation source generates a carrier wave signal, the backscatter reader detects the tag message, and the tag employs the impinging electromagnetic wave for information modulation and energy harvesting.
-A typical passive tag consists of a backscatter antenna, a matching network, an energy harvester, and on-chip components (e.g., microcontroller, memory, sensor, and integrated receiver\footnote{For example, a compact-size integrated receiver was prototyped in \cite{Kim2021a} to perform pulse position demodulation by an envelope detector.
-It enables coordination, synchronization, and reflection pattern control.}).
-The backscatter antenna behaves as a constant power source, where the voltage is induced by the incident electric field $\vec{E}_{\mathrm{I}}$ and the current is induced by the incident magnetic field $\vec{H}_{\mathrm{I}}$ \cite{Paul2006}.
-As shown in Fig.~\subref*{ci:backscatter_antenna}, a portion of the incident power is absorbed by the tag while the remaining is backscattered to the space.
-The backscattered signal can be decomposed into the \emph{structural mode} component and the \emph{antenna mode} component \cite{Hansen1989}.
+			Consider a bistatic backscatter system that consists of an excitation source, a dedicated reader, and a passive tag.
+The excitation source generates a carrier wave signal, the dedicated reader decodes the tag message, and the tag simultaneously harvests energy, backscatters its own message, and demodulates the downlink information if necessary.
+As shown in Fig.~\subref*{fi:block_diagram}, a typical passive tag consists of a scattering antenna, an energy harvester, a integrated receiver\footnote{For example, \cite{Kim2021a} prototyped a compact-size pulse position demodulator based on an envelope detector, which brings great potential to coordination, synchronization, and reflection pattern control.}, a load-switching modulator, and on-chip components (e.g., micro-controller, memory, and sensors).
+A portion of the impinging signal is absorbed by the tag while the remaining is backscattered to the space, as illustrated in Fig.~\subref*{fi:one_port_network_model}.
+According to Green's decomposition \cite{Hansen1989}, the backscattered signal can be decomposed into the \emph{structural mode} component and the \emph{antenna mode} component.
 The former is fixed and depends on the antenna geometry and material properties\footnote{We assume the structural mode reflection can be modeled as part of the environment multipath and covered by channel estimation \cite{Boyer2014}.}, while the latter is adjustable and depends on the mismatch of the antenna and load impedance.
@@
 			\end{equation}
-			where $Z_i = R_i + \jmath X_i$ is the antenna load impedance at state $i$, $Z_{\mathrm{A}} = R_{\mathrm{R}} + R_{\mathrm{loss}} + \jmath X_{\mathrm{A}}$ is the antenna input impedance, $R_{\mathrm{R}}$ is the radiation resistance that measures the antenna energy efficiency, $R_{\mathrm{loss}}$ is the loss resistance that models the ohmic or dielectric loss, and $X_{\mathrm{A}}$ is the antenna reactance \cite{Huang2021}.
+			where $Z_i$ is the designable antenna load impedance at state $i$ and $Z_{\mathrm{A}}$ is the antenna input impedance.
 			\begin{remark}
@@
 
+	\begin{section}{System Model}
+		\begin{figure}[!t]
+			\centering
+			\def\svgwidth{0.9\columnwidth}
+			\import{assets/}{symbiotic_radio.pdf_tex}
+			\caption{A single-user single-tag symbiotic radio system.}
+			\label{fi:symbiotic_radio}
+		\end{figure}
+		% As shown in Fig.~\ref{fi:system}, we propose a single-user (UE) single-tag (TG) symbiotic radio network where the RF signal generated by a $Q$-antenna Access Point (AP) is shared by two coexisting systems.
+In the primary AP-UE downlink system, the AP broadcasts to the single-antenna user.
+In the secondary AP-TG-UE backscatter system, the user serves as the reader of $L$ nearby single-antenna tags, while tag $l_k \in \mathcal{L}_k \triangleq \{1,\ldots,L_k\}$ harvests energy from and modulates information over the ambient RF signal by varying its reflection coefficient $\Gamma_{l_k}$\footnote{Due to the product-distance path loss model corresponding to finite-size tag reflection \cite{Ozdogan2020}, the backscatter dyadic channel deteriorates fast when the forward/backward distance increases or the number of hops increases \cite{Griffin2008}.
+Therefore, we assume each tag only contributes to its nearest user (i.e., creates no interference to other users), and omit all signals backscattered by two or more times.}.
+Denote the AP-UE $k$ direct channel as $\boldsymbol{h}_{\mathrm{D},k}^H \in \mathbb{C}^{1 \times Q}$, the AP-TG $l_k$ forward channel as $\boldsymbol{h}_{\mathrm{F},{l_k}}^H \in \mathbb{C}^{1 \times Q}$, and the TG $l_k$-UE $k$ backward channel as $h_{\mathrm{B},l_k} \in \mathbb{C}$.
+We consider the quasi-static block fading model and assume the CSI of all direct, forward and backward channels are known at the AP.\footnote{Due to the lack of RF chains at the passive tags, accurate and efficient estimation for the forward and backward channels can be challenging.
+Our assumption is based on the following reasoning.
+First, the direct AP-UE channel and the dyadic AP-TG-UE channel can be estimated with the AP sending pilots, the tags responding in a pre-defined frame-based manner, and the users performing least-square estimation within each frame\cite{Bharadia2015,Yang2015b,Guo2019e}.
+Second, the UE-TG-UE channel can be estimated similarly with the full-duplex users sending pilots\cite{Mishra2019}.
+Third, the users seek reciprocity to recover the TG-UE backward channel from the estimated UE-TG-UE channel\cite{Mishra2019b,Zawawi2019}, then extracts the AP-TG forward channel from the estimated AP-TG-UE channel provided by the AP.
+The whole process can be accelerated by the parallel estimation protocol proposed in \cite{Jin2021}.} Define $s_k$ as the primary symbol for user $k$ with $\boldsymbol{s} \triangleq [s_1,\ldots,s_K]^H \in \mathbb{C}^{K \times 1}$ satisfying $\mathbb{E}\{\boldsymbol{s}\boldsymbol{s}^H\}=\boldsymbol{I}$, and $c_{l_k}$ as the secondary symbol of tag $l_k$ with $\boldsymbol{c}_k \triangleq [c_1,\ldots,c_{L_k}]^H \in \mathbb{C}^{L_k \times 1}$ satisfying $\mathbb{E}\{\boldsymbol{c}_k\boldsymbol{c}_k^H\}=\boldsymbol{I}$.
+Let $s_k \sim \mathcal{CN} (0,1)$ and $c_{l_k}$ employs $M$-PSK by \eqref{eq:c}.
+As tags typically transmit at a much lower rate than the AP, we assume the secondary symbol period $T_c$ is $N \in \mathbb{Z}_{++}$ times the primary symbol period $T_s$ (i.e., $T_c=NT_s$) and focus on one particular secondary symbol period.
+For linear precoding with no dedicated tag beams, the transmit signal during the primary symbol period $n \in \mathcal{N} \triangleq \{1,\ldots,N\}$ is
+		% \begin{equation}
+		% 	\boldsymbol{x}(n) = \sum_{k=1}^K \boldsymbol{w}_k s_k(n),
+		% \end{equation}
+		% where $\boldsymbol{w}_k$ is the precoder for user $k$ satisfying the average transmit power constraint $\sum_{k=1}^K \lVert \boldsymbol{w}_k \rVert^2 \le P$.
+The received signal at tag $l_k$ is\footnote{For simplicity, the backscattered signals from all other tags are modeled within noise.}
+		% \begin{equation}
+		% 	y_{l_k}(n) = \sum_{j=1}^K \boldsymbol{h}_{\mathrm{F},l_k}^H \boldsymbol{w}_j s_j(n) + z_{l_k}(n),
+		% \end{equation}
+		% where $z_{l_k} \sim \mathcal{CN} (0,\sigma_{l_k}^2)$ is the additive white Gaussian noise\footnote{Since the tag employs no active RF components, the noise captured at backscatter antenna $z_{l_k}$ is assumed negligible \cite{Nikitin2005,Arnitz2013,Wu2021b}.}.
+Hence, the corresponding antenna input power is
+		% \begin{equation}
+		% 	P_{0,l_k} = \sum_{j=1}^K \lvert \boldsymbol{h}_{\mathrm{F},l_k}^H \boldsymbol{w}_j \rvert^2.
+		% 	\label{eq:P_0}
+		% \end{equation}
+		% In practice, the rectifier is a non-linear device and the RF-to-DC conversion efficiency depends on the input power \cite{Clerckx2016a,Clerckx2018,Clerckx2019}.
+On top of \eqref{eq:P_H} and \eqref{eq:P_0}, when all modulation states are equiprobable, the average harvester output power is
+		% \begin{align}
+		% 	P_{l_k}
+		% 	& = \frac{1}{M} \Biggl( \sum_{i_1} \zeta \biggl( \eta_{i_1} (1 - \alpha_{l_k}^2) \sum_{j=1}^K \lvert \boldsymbol{h}_{\mathrm{F},l_k}^H \boldsymbol{w}_j \rvert^2 \biggr) \\
+		% 	& \quad + \sum_{i_2} \zeta \biggl( \frac{(1 - \alpha_{l_k}^2) \sum_{j=1}^K \lvert \boldsymbol{h}_{\mathrm{F},l_k}^H \boldsymbol{w}_j \rvert^2}{\eta_{i_2}} \biggr) \Biggr),
+		% \end{align}
+		% where $i_1 \ge M {\arccos \alpha_{l_k}} / {2 \pi}$, $i_2<M {\arccos \alpha_{l_k}} / {2 \pi}$, and $\zeta(\cdot)$ is the harvester response function.
+On the other hand, we define the scattered channel by tag $l_k$ as
+		% \begin{equation}
+		% 	\boldsymbol{h}_{l_k}^H \triangleq \alpha_{l_k} h_{\mathrm{B},l_k} \boldsymbol{h}_{\mathrm{F},l_k}^H.
+		% \end{equation}
+		% Hence, the received signal at user $k$ is
+		% \begin{align}
+		% 	y_k(n)
+		% 	& = \sum_{j=1}^K \left( \boldsymbol{h}_{\mathrm{D},k}^H + \sum_{l_k=1}^{L_k} c_{l_k} \boldsymbol{h}_{l_k}^H \right) \boldsymbol{w}_j s_j(n) + z_k(n) \\
+		% 	& \triangleq \sum_{j=1}^K \boldsymbol{h}_k^H \boldsymbol{w}_j s_j(n) + z_k(n),
+		% \end{align}
+		% where
+		% \begin{equation}
+		% 	\boldsymbol{h}_k^H \triangleq \boldsymbol{h}_{\mathrm{D},k}^H + \sum_{l_k=1}^{L_k} c_{l_k} \boldsymbol{h}_{l_k}^H
+		% 	\label{eq:h}
+		% \end{equation}
+		% is the equivalent channel of user $k$ and $z_k \sim \mathcal{CN} (0,\sigma_k^2)$ is the additive white Gaussian noise.
+		% \begin{remark}
+		% 	From the perspective of broadcast, the components scattered by the tags essentially create uncertainty over the direct AP-UE channel.
+If the backscattered symbols are unknown when decoding the broadcasted symbols, the uncertainty should be either covered by non-coherent detection \cite{Long2020a} or modeled as CSI error that introduces interference.
+That is to say, the equivalent channel is perfectly known only when all tag massages are successfully decoded.
+		% \end{remark}
+
+		% \begin{figure}[!t]
+		% 	\centering
+		% 		\resizebox{0.95\columnwidth}{!}{
+		% 			\begin{tikzpicture}
+		% 				\foreach \x in {1,...,12}
+		% 					\draw [pattern=crosshatch dots,pattern color=blue](\x,0) rectangle ++(1,1);
+		% 				\foreach \x in {1,...,12}
+		% 					\foreach \y in {-3,...,-1}{
+		% 						\pgfmathsetmacro\floorval{int(floor((\x+\y)/4))}
+		% 						\pgfmathsetmacro\modval{int(mod((\x+\y),4))}
+		% 						\ifnum \floorval=0
+		% 							\ifnum \modval=0
+		% 								\draw [pattern=horizontal lines,pattern color=red](\x,\y) rectangle ++(1,1);
+		% 							\else
+		% 								\draw [pattern=horizontal lines,pattern color=yellow](\x,\y) rectangle ++(1,1);
+		% 							\fi
+		% 						\else
+		% 							\ifnum \floorval=1
+		% 								\ifnum \modval=0
+		% 									\draw [pattern=north west lines,pattern color=red](\x,\y) rectangle ++(1,1);
+		% 								\else
+		% 									\draw [pattern=north west lines,pattern color=yellow](\x,\y) rectangle ++(1,1);
+		% 								\fi
+		% 							\else
+		% 								\ifnum \floorval=2
+		% 									\ifnum \modval=0
+		% 										\draw [pattern=vertical lines,pattern color=red](\x,\y) rectangle ++(1,1);
+		% 									\else
+		% 										\draw [pattern=vertical lines,pattern color=yellow](\x,\y) rectangle ++(1,1);
+		% 									\fi
+		% 								\else
+		% 									\draw (\x,\y) rectangle ++(1,1);
+		% 									% \ifnum \modval=0
+		% 									% 	\draw (\x,\y) rectangle ++(1,1);
+		% 									% \else
+		% 									% 	\draw [pattern=north east lines,pattern color=yellow](\x,\y) rectangle ++(1,1);
+		% 									% \fi
+		% 								\fi
+		% 							\fi
+		% 						\fi
+		% 					}
+		% 				\node[font=\huge] at (-2,0.5) {Broadcast};
+		% 				\node[font=\huge] at (-2,-0.5) {Tag \num{1}};
+		% 				\node[font=\huge] at (-2,-1.5) {Tag \num{2}};
+		% 				\node[font=\huge] at (-2,-2.5) {Tag \num{3}};
+		% 				\node[font=\huge] at (14,-1) {$\cdots$};
+		% 				\node[font=\huge,right] at (16.75,0){$b=1$};
+		% 				\node[font=\huge,right] at (16.75,-1){$b=2$};
+		% 				\node[font=\huge,right] at (16.75,-2){$b=3$};
+		% 				\draw [pattern=horizontal lines](16,-0.25) rectangle ++(0.5,0.5);
+		% 				\draw [pattern=north west lines](16,-1.25) rectangle ++(0.5,0.5);
+		% 				\draw [pattern=vertical lines](16,-2.25) rectangle ++(0.5,0.5);
+		% 				\draw[<->] (1,1.5) -- (2,1.5) node[font=\huge,midway,above]{$T_s$};
+		% 				\draw[<->] (1,-3.5) -- (5,-3.5) node[font=\huge,midway,below=0.125]{$T_c=NT_s$};
+		% 				\draw[->] (10.5,1.625) -- (10.5,1.25) node[font=\huge,at start,above]{Block $r$};
+		% 			\end{tikzpicture}
+		% 		}
+		% 	\caption{Primary and secondary symbol blocks received by user $k$ for $N=4$ and $L_k=3$.
+The blocks are normalized to the primary symbol period $T_s$.
+In the broadcast link, each block contains the message of all users at a specific time.
+In the backscatter links, each tag symbol lasts $N$ blocks (illustrated by a specific pattern) and the tag streams are delayed by multiples of $T_s$.
+Apart from decoding the self message, each user also decodes at most one tag message per primary symbol period (denoted by red blocks) and regards it as part of known channel in the following $N-1$ blocks.}
+		% 	\label{fi:blocks}
+		% \end{figure}
+
+		% To mitigate the interference from the backscatter link, we utilize its low rate property and propose a joint user and tag multiple access scheme as illustrated in Fig.~\ref{fi:blocks}.
+Specifically, the broadcast system can employ any general multiple access scheme\footnote{Since tags are associated to the nearest user, non-orthogonal protocols (e.g., NOMA and MU-LP) involving less coordination among users and tags are preferred \cite{Ding2021}.} (denoted by blue blocks), while the backscatter system integrates TDMA and NOMA as follows.
+Assuming the number of tags associated to user $k$ satisfies $L_k \le N$, $\forall k \in \mathcal{K}$\footnote{The proposed scheme can be extended to case of $L_k > N$, where at most $\lceil L_k/N \rceil$ tags transmit synchronously and user $k$ decodes up to $\lceil L_k/N \rceil$ tags per primary symbol period.
+Here we assume $L_k \le N$ for simplicity.}, we intentionally delay the stream of tag $l_k$ by $l_k-1$ primary symbol periods such that all tags transmit asynchronously and non-orthogonally.
+In such case, each user only needs to decode at most one tag message per primary symbol period (denoted by red blocks) and models it as part of the estimated channel in the following $N-1$ primary symbol periods (denoted by yellow blocks).
+We denote $r \in \mathbb{Z}_{++}$ as the index of primary symbols, and define $b \triangleq \lceil r/N \rceil$ as the index of secondary symbols and $d \equiv r \pmod N$ as the remainder of $N$ divides $r$.
+Therefore, the backscattered symbol by tag $l_k$ at block $r$ can be related to its index $b$ as
+		% \begin{equation}
+		% 	c_{l_k}(r) =
+		% 	\begin{cases}
+		% 		c_{l_k}(b), & d = 0 \text{ or } d \ge l_k, \\
+		% 		c_{l_k}(b-1), & 0 < d < l_k.
+		% 	\end{cases}
+		% \end{equation}
+		% It is assumed that $c_{l_k}(0)$, $\forall l_k \in \mathcal{L}_k$ is known at user $k$ and can be designed as zeros or pilots or cyclic prefixes.
+
+		% At block $r$, user $k$ always decodes its $r$-th primary symbol $s_k(r)$ first.
+If $d=0$ or $d>L_k$ \footnote{Note that $d=0$ corresponds to $n=N$.}, all backscattered symbols would be the same as in the previous block and no uncertainty is introduced by the backscattered link (denoted by all-yellow columns).
+Therefore, the equivalent channel at block $r$ is perfectly known and the tags create no interference to the primary transmission.
+On the other hand, if $0 < d \le L_k$, tag $d$ would trigger a new symbol $c_d(b)$ that lasts $N$ blocks but should be decoded within the current block $r$.
+In this case, user $k$ first treats the channel uncertainty from $c_d(b)$ as interference during primary decoding, then cancels the interference from decoded primary symbols and detects $c_d(b)$.
+Once a backscattered symbol is successfully decoded, its contribution to the equivalent channel \eqref{eq:h} is known.
+Therefore, under perfect detection, the estimated channel of user $k$ at block $r$ is
+		% \begin{equation}
+		% 	\bar{\boldsymbol{h}}_k^H(r) =
+		% 		\begin{cases}
+		% 			\boldsymbol{h}_{\mathrm{D},k}^H + \boldsymbol{c}_k^H(r) \boldsymbol{H}_k, & d = 0 \text{ or } d > L_k, \\
+		% 			\boldsymbol{h}_{\mathrm{D},k}^H + \boldsymbol{c}_{k \setminus d}^H(r) \boldsymbol{H}_{k \setminus d}, & 0 < d \le L_k,
+		% 		\end{cases}
+		% 		\label{eq:h_bar}
+		% \end{equation}
+		% where we define $\boldsymbol{c}_{k \setminus d} \triangleq [c_1,\ldots,c_{d-1},c_{d+1},\ldots,c_{L_k}]^H \in \mathbb{C}^{(L_k-1) \times 1}$, $\boldsymbol{H}_k \triangleq [\boldsymbol{h}_1,\ldots,\boldsymbol{h}_{L_k}]^H \in \mathbb{C}^{L_k \times Q}$ and $\boldsymbol{H}_{k \setminus d} \triangleq [\boldsymbol{h}_1,\ldots,\boldsymbol{h}_{d-1},\boldsymbol{h}_{d+1},\ldots,\boldsymbol{h}_{L_k}]^H \in \mathbb{C}^{(L_k-1) \times Q}$.
+Besides, the corresponding channel uncertainty is
+		% \begin{equation}
+		% 	\tilde{\boldsymbol{h}}_k^H(r) = \boldsymbol{h}_k^H(r) - \bar{\boldsymbol{h}}_k^H(r) =
+		% 		\begin{cases}
+		% 			0, & d = 0 \text{ or } d > L_k, \\
+		% 			c_{d}(r) \boldsymbol{h}_{d}^H, & 0 < d \le L_k.
+		% 		\end{cases}
+		% 		\label{eq:h_tilde}
+		% \end{equation}
+		% \begin{remark}
+		% 	From the perspective of broadcast, the backscattered channel is similar to the auxiliary channel provided by IRS.
+Once a tag symbol is successfully decoded, the corresponding channel uncertainty can be mitigated in the following $N-1$ primary symbol periods.
+This decoding mechanism can be viewed as a backscatter channel training process where the cascaded channels remain unchanged and the tag reflection coefficients are learned.
+If $N \gg L_k$, the training overhead (corresponding to $0 < d \le L_k$) can be omitted where the tags backscatter at very low rates and behave similar to the IRS elements.
+That is to say, passive beamforming can be enabled by carefully choosing the backscatter symbols based on CSI.
+		% \end{remark}
+
+		% Next, we investigate the performance of the proposed protocol under typical primary multiple access schemes.
+
+		% \begin{subsection}{NOMA}
+		% 	We first consider NOMA for the primary link.
+Without loss of generality, we assume the SNR of the estimated channels at block $r$ satisfy $\lVert \bar{\boldsymbol{h}}_j(r) \rVert / \sigma_j \le \lVert \bar{\boldsymbol{h}}_k(r) \rVert / \sigma_k$ such that the downlink symbol $s_j(r)$ is decoded before $s_k(r)$, $\forall j < k, \, j,k \in \mathcal{K}$.
+The SINR for user $k$ to decode the message of user $j$ at block $r$ is
+		% 	\begin{equation}
+		% 		\gamma_{j \to k}^{\mathrm{(N)}}(r) = \frac{\lvert \bar{\boldsymbol{h}}_k^H(r) \boldsymbol{w}_j \rvert^2}{\sum_{i=j+1}^K \lvert \bar{\boldsymbol{h}}_k^H(r) \boldsymbol{w}_i \rvert^2 + \sum_{i=1}^K \lvert \tilde{\boldsymbol{h}}_k^H(r) \boldsymbol{w}_i \rvert^2 + \sigma_k^2},
+		% 		\label{eq:gamma_jk^N}
+		% 	\end{equation}
+		% 	where the interference from all users stronger than $j$ and channel uncertainty from all tags are treated as noise.
+Once $s_j(r)$ is successfully decoded, its contribution is cancelled from $y_k(r)$.
+The process is repeated until user $k$ reaches its own stream, and the self-decoding SINR is
+		% 	\begin{equation}
+		% 		\gamma_{k \to k}^{\mathrm{(N)}}(r) = \frac{\lvert \bar{\boldsymbol{h}}_k^H(r) \boldsymbol{w}_k \rvert^2}{\sum_{j=k+1}^K \lvert \bar{\boldsymbol{h}}_k^H(r) \boldsymbol{w}_j \rvert^2 + \sum_{j=1}^K \lvert \tilde{\boldsymbol{h}}_k^H(r) \boldsymbol{w}_j \rvert^2 + \sigma_k^2}.
+		% 		\label{eq:gamma_kk^N}
+		% 	\end{equation}
+		% 	After successfully decoded its own stream, user $k$ has two options.
+When $d=0$ or $d>L_k$, the estimated channel \eqref{eq:h_bar} equals the equivalent channel \eqref{eq:h} and it boils down to an backscatter-assisted NOMA broadcast block.
+In this case, the second term of the denominator of \eqref{eq:gamma_jk^N}, \eqref{eq:gamma_kk^N} are zero and user $k$ terminates the operation after decoding its own stream.
+On the other hand, when $0 < d \le L_k$, tag $d$ triggers a new symbol at block $r$ that contributes to channel uncertainty \eqref{eq:h_tilde}.
+In this case, user $k$ continues to cancel the interference from its own stream (i.e., perform an extra layer SIC on top of primary decoding), then decodes $c_d(b)$ at SINR
+		% 	\begin{equation}
+		% 		\gamma_{d \to k}^{\mathrm{(N)}}(r) = \frac{\sum_{j=1}^K \lvert \boldsymbol{h}_d^H \boldsymbol{w}_j \rvert^2}{\sum_{j=k+1}^K \lvert \bar{\boldsymbol{h}}_k^H(r) \boldsymbol{w}_j \rvert^2 + \sigma_k^2}.
+		% 		\label{eq:gamma_dk^N}
+		% 	\end{equation}
+		% 	Once $c_d(b)$ is successfully decoded, its contribution would be modeled within the known channel in the following $N-1$ blocks to help both primary and secondary decodings.
+		% \end{subsection}
+
+		% \begin{subsection}{MU-LP}
+		% 	MU-LP in the primary link treats the interference occurred in primary decoding as interference. The SINR for user $k$ to decode its own stream at block $r$ is
+		% 	\begin{equation}
+		% 		\gamma_{k \to k}^{\mathrm{(M)}}(r) = \frac{\lvert \bar{\boldsymbol{h}}_k^H(r) \boldsymbol{w}_k \rvert^2}{\sum_{j \in \mathcal{K} \setminus k} \lvert \bar{\boldsymbol{h}}_k^H(r) \boldsymbol{w}_j \rvert^2 + \sum_{j=1}^K \lvert \tilde{\boldsymbol{h}}_k^H(r) \boldsymbol{w}_j \rvert^2 + \sigma_k^2}.
+		% 		\label{eq:gamma_kk^M}
+		% 	\end{equation}
+		% 	Similarly, when $0 < d \le L_k$, user $k$ cancels the interference from its own stream and decodes $c_d(b)$ at SINR
+		% 	\begin{equation}
+		% 		\gamma_{d \to k}^{\mathrm{(N)}}(r) = \frac{\sum_{j=1}^K \lvert \boldsymbol{h}_d^H \boldsymbol{w}_j \rvert^2}{\sum_{j \in \mathcal{K} \setminus k} \lvert \bar{\boldsymbol{h}}_k^H(r) \boldsymbol{w}_j \rvert^2 + \sigma_k^2}.
+		% 		\label{eq:gamma_dk^M}
+		% 	\end{equation}
+		% 	The contribution of $c_d(b)$ is then modeled within the estimated channel in the following $N-1$ blocks.
+		% \end{subsection}
+
+		% \begin{remark}
+		% 	For a specific channel realization, we notice that $\gamma_{j \to k}$ and $\gamma_{k \to k}$ are generally functions of $\boldsymbol{c}_k$ such that the primary rate at each block should be evaluated over the expectation of the backscattered symbols \cite{Long2020a,Zhang2020c}.
+On the other hand, how tags contribute to the estimated channel depends on the specific block.
+Since each decoding cycle lasts $N$ blocks, another expectation over $N$ blocks is necessary.
+For a sufficiently large $N$, the average primary achievable rate of user $k$ is
+		% 	\begin{equation}
+		% 		\mathbb{E}_n \Bigl\{ \mathbb{E}_{\boldsymbol{c}_k}\bigl\{R_{k \to k}(n)\bigr\} \Bigr\} = \frac{1}{N} \sum_{n=1}^N \mathbb{E}_{\boldsymbol{c}_k}\Bigl\{\log_2 \bigl( 1 + \gamma_{k \to k}(n) \bigr)\Bigr\}.
+		% 		% \mathbb{E}_n \bigl\{ \mathbb{E}_{\boldsymbol{c}_k}\{\gamma_{k \to k}\} \bigl\} = \frac{1}{N} \sum_{n=1}^N \mathbb{E}_{\boldsymbol{c}_k}\{\gamma_{k \to k}(n)\}.
+		% 	\end{equation}
+		% 	In contrast, although $\gamma_{l_k \to k}$ depends on $\boldsymbol{c}_{k \setminus l_k}$, the decoding process for tag $l_k$ only lasts one block such that $\gamma_{l_k \to k}$ is irrelevant to $N$.
+Hence, the average secondary SINR of tag $l_k$ is $\mathbb{E}_{\boldsymbol{c}_{k \setminus l_k}}\{\gamma_{l_k \to k}\}$.
+[Need rate-SINR relationship for M-PSK.]
+		% \end{remark}
+		\label{se:system_model}
+	\end{section}
+
 	\bibliographystyle{IEEEtran}

### 2021-09-02 main.tex
:pencil: Add remarks on decoding order

@@
 							\draw (0,1.75)
-								to[short] ++(-0.75,0)
-								to[short] ++(0,0.75) node[bareantenna](A){};
+								to[short] ++(-1,0)
+								to[short] ++(0,0.75) node[bareantenna](A){Ant};
 							\draw (0,1.75)
@@
 							\draw (bareantenna.west) ++(-1.5,0) node[waves](WI){};
-							\draw (WI.north east) ++(0.25,0) node[]{$\vec{E}_{\mathrm{I}}$};
-							\draw (WI.south east) ++(0.25,0) node[]{$\vec{H}_{\mathrm{I}}$};
+							\draw (WI.north east) ++(0.25,0) node[font=\Large]{$\vec{E}_{\mathrm{I}}$};
+							\draw (WI.south east) ++(0.25,0) node[font=\Large]{$\vec{H}_{\mathrm{I}}$};
 							\draw (bareantenna.east) ++(0.875,0) node[waves](WR){};
-							\draw (WR.north east) ++(0.25,0) node[]{$\vec{E}_i$};
-							\draw (WR.south east) ++(0.25,0) node[]{$\vec{H}_i$};
+							\draw (WR.north east) ++(0.25,0) node[font=\Large]{$\vec{E}_i$};
+							\draw (WR.south east) ++(0.25,0) node[font=\Large]{$\vec{H}_i$};
 							\draw (bareantenna)
-								to [R=$Z_{\mathrm{A}}$] ++(0,-2)
-								to [R=$Z_i$] ++(2,0) node[ground]{};
+								to [R=$Z_{\mathrm{A}}$,font=\Large,/tikz/circuitikz/bipoles/length=1cm] ++(0,-2)
+								to [R=$Z_i$,font=\Large,/tikz/circuitikz/bipoles/length=1cm] ++(2,0) node[ground]{};
 						\end{circuitikz}
@@
 The former is fixed and depends on the antenna geometry and material properties\footnote{We assume the structural mode reflection can be modeled as part of the environment multipath and covered by channel estimation \cite{Boyer2014}.}, while the latter is adjustable and depends on the mismatch of the antenna and load impedance.
-Hence, the equivalent reflection coefficient at tag state $i$ is defined as\footnote{We assume the linear backscatter where $\Gamma_i$ is irrelevant to the incident electromagnetic field at the tag \cite{Dobkin2012}.}
+Hence, the equivalent reflection coefficient at tag state $i$ is defined as\footnote{We assume the linear backscatter model where $\Gamma_i$ is irrelevant to the incident electromagnetic field at the tag \cite{Dobkin2012}.}
 			\begin{equation}
@@
 		\end{figure}
-		% As shown in Fig.~\ref{fi:system}, we propose a single-user (UE) single-tag (TG) symbiotic radio network where the RF signal generated by a $Q$-antenna Access Point (AP) is shared by two coexisting systems.
-In the primary AP-UE downlink system, the AP broadcasts to the single-antenna user.
-In the secondary AP-TG-UE backscatter system, the user serves as the reader of $L$ nearby single-antenna tags, while tag $l_k \in \mathcal{L}_k \triangleq \{1,\ldots,L_k\}$ harvests energy from and modulates information over the ambient RF signal by varying its reflection coefficient $\Gamma_{l_k}$\footnote{Due to the product-distance path loss model corresponding to finite-size tag reflection \cite{Ozdogan2020}, the backscatter dyadic channel deteriorates fast when the forward/backward distance increases or the number of hops increases \cite{Griffin2008}.
-Therefore, we assume each tag only contributes to its nearest user (i.e., creates no interference to other users), and omit all signals backscattered by two or more times.}.
-Denote the AP-UE $k$ direct channel as $\boldsymbol{h}_{\mathrm{D},k}^H \in \mathbb{C}^{1 \times Q}$, the AP-TG $l_k$ forward channel as $\boldsymbol{h}_{\mathrm{F},{l_k}}^H \in \mathbb{C}^{1 \times Q}$, and the TG $l_k$-UE $k$ backward channel as $h_{\mathrm{B},l_k} \in \mathbb{C}$.
-We consider the quasi-static block fading model and assume the CSI of all direct, forward and backward channels are known at the AP.\footnote{Due to the lack of RF chains at the passive tags, accurate and efficient estimation for the forward and backward channels can be challenging.
-Our assumption is based on the following reasoning.
-First, the direct AP-UE channel and the dyadic AP-TG-UE channel can be estimated with the AP sending pilots, the tags responding in a pre-defined frame-based manner, and the users performing least-square estimation within each frame\cite{Bharadia2015,Yang2015b,Guo2019e}.
-Second, the UE-TG-UE channel can be estimated similarly with the full-duplex users sending pilots\cite{Mishra2019}.
-Third, the users seek reciprocity to recover the TG-UE backward channel from the estimated UE-TG-UE channel\cite{Mishra2019b,Zawawi2019}, then extracts the AP-TG forward channel from the estimated AP-TG-UE channel provided by the AP.
-The whole process can be accelerated by the parallel estimation protocol proposed in \cite{Jin2021}.} Define $s_k$ as the primary symbol for user $k$ with $\boldsymbol{s} \triangleq [s_1,\ldots,s_K]^H \in \mathbb{C}^{K \times 1}$ satisfying $\mathbb{E}\{\boldsymbol{s}\boldsymbol{s}^H\}=\boldsymbol{I}$, and $c_{l_k}$ as the secondary symbol of tag $l_k$ with $\boldsymbol{c}_k \triangleq [c_1,\ldots,c_{L_k}]^H \in \mathbb{C}^{L_k \times 1}$ satisfying $\mathbb{E}\{\boldsymbol{c}_k\boldsymbol{c}_k^H\}=\boldsymbol{I}$.
-Let $s_k \sim \mathcal{CN} (0,1)$ and $c_{l_k}$ employs $M$-PSK by \eqref{eq:c}.
+		As shown in Fig.~\ref{fi:symbiotic_radio}, we propose a single-user (UE) single-tag (TG) symbiotic radio network where the RF signal generated by the single-antenna Access Point (AP) is shared by two coexisting systems.
+In the primary AP-UE downlink system, the AP transmits to the single-antenna user.
+In the secondary AP-TG-UE backscatter system, the AP acts as the carrier emitter, the user serves as the backscatter reader, and the single-antenna tag modulates its information over the reradiated RF signal by varying the reflection coefficient.
+Denote the AP-UE direct channel as $h_{\mathrm{D}}$, the AP-TG forward channel as $h_{\mathrm{F}}$, and the TG-UE backward channel as $h_{\mathrm{B}}$.
+We consider the quasi-static block fading model and assume the CSI of the direct channel and the cascaded forward-backward channel $h_{\mathrm{C}} \triangleq h_{\mathrm{B}} h_{\mathrm{F}}$ are known at the AP.\footnote{Due to the lack of RF chains at the passive tag, accurate and efficient CSI acquisition at the AP can be challenging.
+One possible approach is that the AP sends known pilots, the tag responds in a pre-defined manner, and the user performs least-square estimation then feeds back to the AP \cite{Bharadia2015,Yang2015b,Guo2019e}.} It is assumed that the primary symbol $s$ follows standard CSCG distribution $\mathcal{CN}(0,1)$ and the secondary symbol $c$ employs $M$-PSK modulation by \eqref{eq:backscatter_modulation}.
+Let $P$ be the average transmit power of the AP.
+The user simultaneously captures the signal from both primary and secondary links as\footnote{We assume the time difference of arrival from the AP-UE path and the AP-TG-UE path are negligible compared to the symbol period \cite{Guo2019b,Liang2020,Long2020a}.}
+		\begin{equation}
+			y = \sqrt{P} h_{\mathrm{D}} s + \sqrt{\alpha P} h_{\mathrm{C}} s c + n,
+		\end{equation}
+		where $n \sim \mathcal{CN}(0,1)$ is the additive white Gaussian noise.
+
+		\begin{remark}
+			The symbiotic radio network can be regarded as as a special case of Multiple Access Channel (MAC) because the AP and the tag transmit to the user simultaneously.
+It is known that SC-SIC with different decoding orders can achieve different vertices of the MAC capacity region \cite{Goldsmith2005}.
+Therefore, most relevant papers proposed to decode the primary message first (by treating the tag interference as noise), cancel out the primary contribution from the received signal, then decode the secondary message.
+Since the direct channel is typically much stronger than the cascaded channel \cite{Ozdogan2020}, the primary decoding should enjoy a high Signal-to-Interference-and-Noise Ratio (SINR) and the secondary decoding should be interference-free in the ideal case.
+		\end{remark}
+
+		\begin{remark}
+			To investigate how backscatter modulation potentially benefits the primary transmission, we instead decode the secondary link before the primary link.
+Once the tag message is successfully decoded, the uncertainty of the AP-TG-UE path can be perfectly removed (by combining the backscattered symbol and the cascaded channel), and its contribution can be modeled within the equivalent AP-UE channel.
+This is reminiscent of IRS-aided point-to-point transmission with CSI uncertainty (by backscatter modulation instead of channel estimation), where the passive tag simultaneously embeds its own message (embodied in secondary decoding) and assists the legacy transmission (embodied in primary decoding).
+
+			[Channel over channel, randomness over randomness]
+		\end{remark}
+
+		% Define $s_k$ as the primary symbol for user $k$ with $\boldsymbol{s} \triangleq [s_1,\ldots,s_K]^H \in \mathbb{C}^{K \times 1}$ satisfying $\mathbb{E}\{\boldsymbol{s}\boldsymbol{s}^H\}=\boldsymbol{I}$, and $c_{l_k}$ as the secondary symbol of tag $l_k$ with $\boldsymbol{c}_k \triangleq [c_1,\ldots,c_{L_k}]^H \in \mathbb{C}^{L_k \times 1}$ satisfying $\mathbb{E}\{\boldsymbol{c}_k\boldsymbol{c}_k^H\}=\boldsymbol{I}$.
+Let $s_k \sim \mathcal{CN} (0,1)$ and $c_{l_k}$ employs $M$-PSK by \eqref{eq:reflection_coefficient}.
 As tags typically transmit at a much lower rate than the AP, we assume the secondary symbol period $T_c$ is $N \in \mathbb{Z}_{++}$ times the primary symbol period $T_s$ (i.e., $T_c=NT_s$) and focus on one particular secondary symbol period.

### 2021-09-03 main.tex
:pencil: Update remark on SR vs MAC

@@
 			\end{equation}
-			where $Z_i$ is the designable antenna load impedance at state $i$ and $Z_{\mathrm{A}}$ is the antenna input impedance.
+			where $Z_i$ is the load impedance at state $i$ and $Z_{\mathrm{A}}$ is the antenna input impedance.
 			\begin{remark}
@@
 One possible approach is that the AP sends known pilots, the tag responds in a pre-defined manner, and the user performs least-square estimation then feeds back to the AP \cite{Bharadia2015,Yang2015b,Guo2019e}.} It is assumed that the primary symbol $s$ follows standard CSCG distribution $\mathcal{CN}(0,1)$ and the secondary symbol $c$ employs $M$-PSK modulation by \eqref{eq:backscatter_modulation}.
-Let $P$ be the average transmit power of the AP.
-The user simultaneously captures the signal from both primary and secondary links as\footnote{We assume the time difference of arrival from the AP-UE path and the AP-TG-UE path are negligible compared to the symbol period \cite{Guo2019b,Liang2020,Long2020a}.}
+To provide a preliminary insight, we consider a parasitic symbiotic radio \cite{Long2020a} where the primary and secondary symbol periods are equal.
+\footnote{However, parasitic symbiotic radio requires fast tag-state switching and frequent synchronization, which can be challenging for passive tags.} The user simultaneously captures the signal from both primary and secondary links as\footnote{We assume the time difference of arrival from the AP-UE path and the AP-TG-UE path are negligible compared to the symbol period \cite{Guo2019b,Liang2020,Long2020a}.}
 		\begin{equation}
@@
 		\end{equation}
-		where $n \sim \mathcal{CN}(0,1)$ is the additive white Gaussian noise.
+		where $P$ is the average transmit power of the AP and $n \sim \mathcal{CN}(0,1)$ is the additive white Gaussian noise.
 
 		\begin{remark}
-			The symbiotic radio network can be regarded as as a special case of Multiple Access Channel (MAC) because the AP and the tag transmit to the user simultaneously.
-It is known that SC-SIC with different decoding orders can achieve different vertices of the MAC capacity region \cite{Goldsmith2005}.
-Therefore, most relevant papers proposed to decode the primary message first (by treating the tag interference as noise), cancel out the primary contribution from the received signal, then decode the secondary message.
-Since the direct channel is typically much stronger than the cascaded channel \cite{Ozdogan2020}, the primary decoding should enjoy a high Signal-to-Interference-and-Noise Ratio (SINR) and the secondary decoding should be interference-free in the ideal case.
+			The symbiotic radio network can be regarded as as a special case of Multiple Access Channel (MAC) because the AP and the tag simultaneously transmit to the user.
+It is known that Superposition Coding-Successive Interference Cancellation (SC-SIC) with different decoding orders can achieve different vertices of the MAC capacity region \cite{Goldsmith2005}.
+Therefore, most relevant papers proposed the user to decode the primary message first (by treating the tag interference as noise), cancel out its contribution from the received signal, then decode the secondary message.
+Since the direct channel is typically much stronger than the cascaded channel \cite{Ozdogan2020}, the primary decoding is expected to enjoy a high Signal-to-Interference-and-Noise Ratio (SINR) and the secondary decoding is ideally interference-free.
 		\end{remark}
 
+		To investigate how backscatter modulation potentially benefits the primary transmission, we instead start decoding from the secondary link.
+Once the tag message is successfully recovered, by combining the backscattered symbol with the cascaded channel, the uncertainty of the AP-TG-UE path can be eliminated, and its contribution to primary transmission can be modeled within the equivalent AP-UE channel.
+This is reminiscent of IRS-aided point-to-point transmission.
+Overall, the passive tag not only embeds its own message in the reflection pattern, but also influences the legacy transmission.
+
 		\begin{remark}
-			To investigate how backscatter modulation potentially benefits the primary transmission, we instead decode the secondary link before the primary link.
+			The main difference between symbiotic radio and conventional MAC is that the primary message also reaches the user from the backscatter link.
+This characteristic inspires one to decode the tag message first and model its contribution within the equivalent channel (i.e., unify backscatter decoding and channel training), instead of performing SIC.
+In such case, the primary transmission is able to achieve ergodic capacity with artificial channel variation created by the backscatter modulation.
+		\end{remark}
+
+		% channel training - backscatter decoding
+
+		% \begin{remark}
+		% 	To investigate how backscatter modulation potentially benefits the primary transmission, we instead decode the secondary link before the primary link.
 Once the tag message is successfully decoded, the uncertainty of the AP-TG-UE path can be perfectly removed (by combining the backscattered symbol and the cascaded channel), and its contribution can be modeled within the equivalent AP-UE channel.
@@
 
-			[Channel over channel, randomness over randomness]
-		\end{remark}
+		% 	[Channel over channel, randomness over randomness]
+		% \end{remark}
 

### 2021-09-03 main.tex
:pencil: Update signal model

@@
 		\begin{equation}
-			y = \sqrt{P} h_{\mathrm{D}} s + \sqrt{\alpha P} h_{\mathrm{C}} s c + n,
+			y = \sqrt{p} h_{\mathrm{D}} s + \sqrt{\alpha p} h_{\mathrm{C}} s c + n,
 		\end{equation}
-		where $P$ is the average transmit power of the AP and $n \sim \mathcal{CN}(0,1)$ is the additive white Gaussian noise.
+		where $p$ is the average transmit power at the AP and $n \sim \mathcal{CN}(0,1)$ is the additive white Gaussian noise.
 
@@
 It is known that Superposition Coding-Successive Interference Cancellation (SC-SIC) with different decoding orders can achieve different vertices of the MAC capacity region \cite{Goldsmith2005}.
-Therefore, most relevant papers proposed the user to decode the primary message first (by treating the tag interference as noise), cancel out its contribution from the received signal, then decode the secondary message.
+Therefore, most relevant papers proposed the user to first decode the primary message (by treating the tag interference as noise), cancel out its contribution from the received signal, then decode the secondary message.
 Since the direct channel is typically much stronger than the cascaded channel \cite{Ozdogan2020}, the primary decoding is expected to enjoy a high Signal-to-Interference-and-Noise Ratio (SINR) and the secondary decoding is ideally interference-free.
@@
 
-		To investigate how backscatter modulation potentially benefits the primary transmission, we instead start decoding from the secondary link.
-Once the tag message is successfully recovered, by combining the backscattered symbol with the cascaded channel, the uncertainty of the AP-TG-UE path can be eliminated, and its contribution to primary transmission can be modeled within the equivalent AP-UE channel.
-This is reminiscent of IRS-aided point-to-point transmission.
-Overall, the passive tag not only embeds its own message in the reflection pattern, but also influences the legacy transmission.
-
 		\begin{remark}
 			The main difference between symbiotic radio and conventional MAC is that the primary message also reaches the user from the backscatter link.
-This characteristic inspires one to decode the tag message first and model its contribution within the equivalent channel (i.e., unify backscatter decoding and channel training), instead of performing SIC.
-In such case, the primary transmission is able to achieve ergodic capacity with artificial channel variation created by the backscatter modulation.
+This characteristic inspires one to first decode the tag message, then model its contribution within the equivalent channel during primary decoding (i.e., unify secondary decoding and backscatter channel training), instead of performing SIC.
+In such case, for each fading block, the primary transmission is able to achieve ergodic capacity with artificial channel variation created by the backscatter modulation.
 		\end{remark}
+
+		To investigate how backscatter modulation potentially benefits the primary transmission, we start the decoding process from the secondary link.
+Since $\mathbb{E}[\lvert s \rvert^2] = \mathbb{E}[\lvert c \rvert^2] = 1$, by treating the primary interference as noise, the SINR for the user to decode tag message $c$ is
+		\begin{equation}
+			\gamma_c = \frac{\alpha p \lvert h_{\mathrm{C}} \rvert^2}{p \lvert h_{\mathrm{D}} \rvert^2 + 1}.
+		\end{equation}
+		Once the tag message is successfully recovered, we combine the backscattered symbol with the cascaded channel to eliminate the uncertainty of the AP-TG-UE path, and the received signal is essentially
+		\begin{equation}
+			y = \sqrt{p} (h_{\mathrm{D}} + \sqrt{\alpha} h_{\mathrm{C}} c) s + n \triangleq \sqrt{p} h(c) s + n,
+		\end{equation}
+		which is reminiscent of IRS-aided point-to-point transmission with the equivalent channel defined as
+		\begin{equation}
+			h(c) \triangleq h_{\mathrm{D}} + \sqrt{\alpha} h_{\mathrm{C}} c.
+		\end{equation}
+		That is to say, the passive tag not only embeds its own message in the reflection pattern, but also influences the legacy transmission.
+For primary transmission, backscatter modulation creates a fast fading channel within the coherence time, and the equivalent CSI is known at the receiver once the backscattered symbol is successfully decoded.
+Therefore, the ergodic capacity of primary transmission within each fading block is \cite{Tse2005}
+		\begin{equation}
+			R_s = \mathbb{E}_c \bigl[ \log_2 ( 1 + \lvert h(c) \rvert^2 ) \bigr].
+		\end{equation}
+		We aims to optimize the input distribution of $c$ (i.e., the p.m.f. of $M$-PSK) to achieve a flexible balance between the primary and secondary links.
 

### 2021-09-05 main.tex
:pencil: Consider CSR and AmBC

@@
 							\draw (bareantenna.east) ++(0.875,0) node[waves](WR){};
-							\draw (WR.north east) ++(0.25,0) node[font=\Large]{$\vec{E}_i$};
-							\draw (WR.south east) ++(0.25,0) node[font=\Large]{$\vec{H}_i$};
+							\draw (WR.north east) ++(0.25,0) node[font=\Large]{$\vec{E}_m$};
+							\draw (WR.south east) ++(0.25,0) node[font=\Large]{$\vec{H}_m$};
 							\draw (bareantenna)
 								to [R=$Z_{\mathrm{A}}$,font=\Large,/tikz/circuitikz/bipoles/length=1cm] ++(0,-2)
-								to [R=$Z_i$,font=\Large,/tikz/circuitikz/bipoles/length=1cm] ++(2,0) node[ground]{};
+								to [R=$Z_m$,font=\Large,/tikz/circuitikz/bipoles/length=1cm] ++(2,0) node[ground]{};
 						\end{circuitikz}
@@
 The former is fixed and depends on the antenna geometry and material properties\footnote{We assume the structural mode reflection can be modeled as part of the environment multipath and covered by channel estimation \cite{Boyer2014}.}, while the latter is adjustable and depends on the mismatch of the antenna and load impedance.
-Hence, the equivalent reflection coefficient at tag state $i$ is defined as\footnote{We assume the linear backscatter model where $\Gamma_i$ is irrelevant to the incident electromagnetic field at the tag \cite{Dobkin2012}.}
+Hence, the equivalent reflection coefficient at tag state $m$ is defined as\footnote{We assume the linear backscatter model where $\Gamma_m$ is irrelevant to the incident electromagnetic field at the tag \cite{Dobkin2012}.}
 			\begin{equation}
-				\Gamma_i = \frac{Z_i - Z_{\mathrm{A}}^*}{Z_i + Z_{\mathrm{A}}},
+				\Gamma_m = \frac{Z_m - Z_{\mathrm{A}}^*}{Z_m + Z_{\mathrm{A}}},
 				\label{eq:reflection_coefficient}
 			\end{equation}
-			where $Z_i$ is the load impedance at state $i$ and $Z_{\mathrm{A}}$ is the antenna input impedance.
+			where $Z_m$ is the load impedance at state $m$ and $Z_{\mathrm{A}}$ is the antenna input impedance.
 			\begin{remark}
 				The reflection coefficient plays an important role in various network designs.
-For example, $\Gamma_i = 0$ (perfect matching) achieves maximum power transfer that is optimal for Wireless Power Transfer (WPT), $\lvert \Gamma_i \rvert = 1$ (perfect mismatching) achieves fully signal reflection that is optimal for Intelligent Reflecting Surface (IRS), and $\Gamma_i \ne \Gamma_j$ (adjustable matching) enables backscatter modulation.
+For example, $\Gamma_m = 0$ (perfect matching) achieves maximum power transfer that is optimal for Wireless Power Transfer (WPT), $\lvert \Gamma_m \rvert = 1$ (perfect mismatching) achieves fully signal reflection that is optimal for Intelligent Reflecting Surface (IRS), and $\Gamma_m \ne \Gamma_{m'}$ (adjustable matching) enables backscatter modulation.
 			\end{remark}
@@
 			Tags perform backscatter modulation by switching the load impedance between different states.
-For $M$-ary Phase Shift Keying (PSK), the reflection coefficient $\Gamma_i$ maps to the desired signal constellation point $c_i$ as \cite{Thomas2012a}
+Consider an $M$-ary Phase Shift Keying (PSK).
+At tag state $m \in \mathcal{M} \triangleq \{1,\ldots,M\}$, the reflection coefficient $\Gamma_m$ maps to the desired signal constellation point $c_m$ as \cite{Thomas2012a}
 			\begin{equation}
-				\Gamma_i = \alpha c_i = \alpha e^{\jmath \left(\frac{2 \pi i}{M} + \phi\right)},
+				\Gamma_m = \alpha c_m = \alpha e^{\jmath \theta_m},
 				\label{eq:backscatter_modulation}
 			\end{equation}
-			where $\alpha \in [0,1]$ is the reflection efficiency at a given direction, and $\phi$ is a fixed phase offset.
+			where $\alpha \in [0,1]$ is the reflection efficiency at a given direction, and $\theta_m \triangleq 2 \pi m / M$ is the phase of the $m$-th constellation point of $M$-PSK.
 			\begin{remark}
 				For passive tags, the reflection efficiency $\alpha$ controls the tradeoff between the backscatter strength and harvestable power.
-Interestingly, when $\alpha = 1$, the reflection coefficient set $\{\Gamma_i\}$ of the $M$-PSK backscatter coincides with that of an ideal discrete $M$-state uniform IRS.
+Interestingly, when $\alpha = 1$, the reflection coefficient set $\{\Gamma_m\}$ of the $M$-PSK backscatter coincides with that of an ideal discrete $M$-state uniform IRS.
 The optimal strategy for the IRS is to choose one reflection state with probability \num{1} to boost the equivalent channel, while the optimal strategy for the modulator is to utilize all constellation points with equal probability.
-It inspires one to adaptively design the p.m.f.
-of tag symbols to jointly benefit the backscatter modulation and passive beamforming.
+It inspires one to adaptively design the probability mass function of tag symbols to jointly benefit the backscatter modulation and passive beamforming.
 			\end{remark}
@@
 One possible approach is that the AP sends known pilots, the tag responds in a pre-defined manner, and the user performs least-square estimation then feeds back to the AP \cite{Bharadia2015,Yang2015b,Guo2019e}.} It is assumed that the primary symbol $s$ follows standard CSCG distribution $\mathcal{CN}(0,1)$ and the secondary symbol $c$ employs $M$-PSK modulation by \eqref{eq:backscatter_modulation}.
-To provide a preliminary insight, we consider a parasitic symbiotic radio \cite{Long2020a} where the primary and secondary symbol periods are equal.
-\footnote{However, parasitic symbiotic radio requires fast tag-state switching and frequent synchronization, which can be challenging for passive tags.} The user simultaneously captures the signal from both primary and secondary links as\footnote{We assume the time difference of arrival from the AP-UE path and the AP-TG-UE path are negligible compared to the symbol period \cite{Guo2019b,Liang2020,Long2020a}.}
+Due to the practical constraints on switching speed and synchronization gap, the passive tag typically transmits at a much lower data rate than the AP.
+Hence, we assume the secondary symbol period is $N \gg 1 \in \mathbb{Z}_{++}$ times the primary symbol period and focus on the interval of one particular $c$.
+At symbol block $n \in \mathcal{N} \triangleq \{1,\ldots,N\}$, the user simultaneously captures the signal from both primary and secondary links as\footnote{We assume the time difference of arrival from the AP-UE path and the AP-TG-UE path are negligible compared to the symbol period \cite{Guo2019b,Liang2020,Long2020a}.}
 		\begin{equation}
-			y = \sqrt{p} h_{\mathrm{D}} s + \sqrt{\alpha p} h_{\mathrm{C}} s c + n,
+			y[n] = \sqrt{p} h_{\mathrm{D}} s[n] + \sqrt{\alpha p} h_{\mathrm{C}} c s[n] + w[n],
 		\end{equation}
-		where $p$ is the average transmit power at the AP and $n \sim \mathcal{CN}(0,1)$ is the additive white Gaussian noise.
+		where $p$ is the average transmit power at the AP and $w \sim \mathcal{CN}(0,\sigma^2)$ is the additive white Gaussian noise.
+We also define $\boldsymbol{y} \triangleq \bigl[y[1], \ldots, y[N]\bigr]^T$, $\boldsymbol{s} \triangleq \bigl[s[1], \ldots, s[N]\bigr]^T$, and $\boldsymbol{w} \triangleq \bigl[w[1], \ldots, w[N]\bigr]^T$.
 
@@
 
-		To investigate how backscatter modulation potentially benefits the primary transmission, we start the decoding process from the secondary link.
-Since $\mathbb{E}[\lvert s \rvert^2] = \mathbb{E}[\lvert c \rvert^2] = 1$, by treating the primary interference as noise, the SINR for the user to decode tag message $c$ is
+		To investigate how backscatter modulation potentially benefits the primary transmission, we first decode the tag symbol $c$ in presence of unknown AP symbol $\boldsymbol{s}$.
+Interestingly, the tag detection indeed aligns with the case of Ambient Backscatter Communications (AmBC) where the signal from the ambient source is unknown.
+The optimal Maximum-Likelihood (ML) detector is
 		\begin{equation}
-			\gamma_c = \frac{\alpha p \lvert h_{\mathrm{C}} \rvert^2}{p \lvert h_{\mathrm{D}} \rvert^2 + 1}.
+			\hat{m} = \arg \max_{m \in \mathcal{M}} p(\boldsymbol{y} \mid c_m),
 		\end{equation}
+		where $p(\boldsymbol{y} \mid c_m)$ denotes the probability density function of receiving $\boldsymbol{y}$ when the tag transmits $c_m$.
+
+		During the backscatter detection, the conditional probability density function of the channel output given the tag input for $M$-PSK is
+		\begin{equation}
+			f_{Y \mid C}(y \mid c_m) = ?
+		\end{equation}
+
+		% Since $\mathbb{E}[\lvert s \rvert^2] = \mathbb{E}[\lvert c \rvert^2] = 1$, by treating the primary interference as noise, the SINR for the user to decode tag message $c$ is
+		% \begin{equation}
+		% 	\gamma_c = \frac{\alpha p \lvert h_{\mathrm{C}} \rvert^2}{p \lvert h_{\mathrm{D}} \rvert^2 + 1}.
+		% \end{equation}
 		Once the tag message is successfully recovered, we combine the backscattered symbol with the cascaded channel to eliminate the uncertainty of the AP-TG-UE path, and the received signal is essentially
 		\begin{equation}
-			y = \sqrt{p} (h_{\mathrm{D}} + \sqrt{\alpha} h_{\mathrm{C}} c) s + n \triangleq \sqrt{p} h(c) s + n,
+			y[n] = \sqrt{p} (h_{\mathrm{D}} + \sqrt{\alpha} h_{\mathrm{C}} c) s[n] + w[n] \triangleq \sqrt{p} h(c) s + w[n],
 		\end{equation}
@@
 		\end{equation}
-		We aims to optimize the input distribution of $c$ (i.e., the p.m.f. of $M$-PSK) to achieve a flexible balance between the primary and secondary links.
+		We aims to optimize the input distribution of $c$ (i.e., the probability mass function of $M$-PSK) to achieve a flexible balance between the primary and secondary links.
 

### 2021-09-06 main.tex
:pencil: Transition probability matrix

@@
 \usepackage{pgfplots}
+\usepackage{physics}
 \usepackage{siunitx}
@@
 Hence, we assume the secondary symbol period is $N \gg 1 \in \mathbb{Z}_{++}$ times the primary symbol period and focus on the interval of one particular $c$.
-At symbol block $n \in \mathcal{N} \triangleq \{1,\ldots,N\}$, the user simultaneously captures the signal from both primary and secondary links as\footnote{We assume the time difference of arrival from the AP-UE path and the AP-TG-UE path are negligible compared to the symbol period \cite{Guo2019b,Liang2020,Long2020a}.}
+At (primary) symbol block $n \in \mathcal{N} \triangleq \{1,\ldots,N\}$, the user simultaneously captures the signal from both primary and secondary links as\footnote{We assume the time difference of arrival from the AP-UE path and the AP-TG-UE path are negligible compared to the symbol period \cite{Guo2019b,Liang2020,Long2020a}.}
 		\begin{equation}
@@
 		where $p$ is the average transmit power at the AP and $w \sim \mathcal{CN}(0,\sigma^2)$ is the additive white Gaussian noise.
-We also define $\boldsymbol{y} \triangleq \bigl[y[1], \ldots, y[N]\bigr]^T$, $\boldsymbol{s} \triangleq \bigl[s[1], \ldots, s[N]\bigr]^T$, and $\boldsymbol{w} \triangleq \bigl[w[1], \ldots, w[N]\bigr]^T$.
+We also define $\boldsymbol{y} \triangleq \bigl[y[1], \ldots, y[N]\bigr]^T$.
 
@@
 		To investigate how backscatter modulation potentially benefits the primary transmission, we first decode the tag symbol $c$ in presence of unknown AP symbol $\boldsymbol{s}$.
-Interestingly, the tag detection indeed aligns with the case of Ambient Backscatter Communications (AmBC) where the signal from the ambient source is unknown.
-The optimal Maximum-Likelihood (ML) detector is
+Interestingly, the tag detection indeed coincides with Ambient Backscatter Communications (AmBC) where the signal from the ambient source is unknown.
+Denote $\mathcal{H}_m$ as the hypothesis that the tag transmits $c_m$.
+In such case, the received signal per symbol block follows the CSCG distribution of $y_m[n] \sim \mathcal{CN}(0,\sigma_m^2)$, where
 		\begin{equation}
-			\hat{m} = \arg \max_{m \in \mathcal{M}} p(\boldsymbol{y} \mid c_m),
+			\sigma_m^2 \triangleq \lvert h_{\mathrm{D}} + \sqrt{\alpha} h_{\mathrm{C}} c_m \rvert^2 p + \sigma^2
 		\end{equation}
-		where $p(\boldsymbol{y} \mid c_m)$ denotes the probability density function of receiving $\boldsymbol{y}$ when the tag transmits $c_m$.
+		can be estimated at the user.
+For the ease of exposition, we sort $\{\sigma_m^2\}$ in a descending order by bijective mapping $f \colon m \mapsto i$,\footnote{Note that the mapping is not unique and the detection fails when two different constellation points yield the same energy level.} and formulate a sequence $\langle \sigma_i^2 \rangle$ where $\sigma_i^2 \ge \sigma_j^2$ for $i > j$, $i,j \in \mathcal{M}$.
+Following \cite{Qian2019}, the optimal Maximum-Likelihood (ML) detector boils down to the energy detector, and the likelihood ratio between hypotheses $\mathcal{H}_i$ and $\mathcal{H}_j$ is
+		\begin{equation}
+			\Lambda_{i, j}(\boldsymbol{y}) = \frac{f(\boldsymbol{y} \mid \mathcal{H}_i)}{f(\boldsymbol{y} \mid \mathcal{H}_j)} = \left( \frac{\sigma_j^2}{\sigma_i^2} \right)^N \exp \left( \frac{(\sigma_i^2 - \sigma_j^2) z}{\sigma_i^2 \sigma_j^2} \right),
+		\end{equation}
+		where $f(\boldsymbol{y} \mid \mathcal{H}_i)$, $f(\boldsymbol{y} \mid \mathcal{H}_j)$ denote respectively the conditional probability density function of receiving $\boldsymbol{y}$ under hypothesis $\mathcal{H}_i$ and $\mathcal{H}_j$, and $z \triangleq \lVert y \rVert^2$ is the received signal energy over $N$ symbol blocks.
+The corresponding decision rule is
+		\begin{equation}
+			\Lambda_{i, j}(\boldsymbol{y}) \underset{H_j}{\overset{H_i}{\gtrless}} 1 \iff z \underset{H_j}{\overset{H_i}{\gtrless}} T_{i, j},
+		\end{equation}
+		where the optimal detection threshold is
+		\begin{equation}
+			T_{i, j} \triangleq N \frac{\sigma_i^2 \sigma_j^2}{\sigma_i^2 - \sigma_j^2} \log \frac{\sigma_i^2}{\sigma_j^2}.
+		\end{equation}
+		On top of this, the decision region of hypothesis $\mathcal{H}_i$ can be expressed as
+		% \begin{equation}
+		% 	\mathcal{R}(\mathcal{H}_i) \triangleq
+		% 	\begin{cases}
+		% 		[0, T_{1, 2}), & i = 1, \\
+		% 		[T_{M-1, M}, \infty), & i = M, \\
+		% 		[T_{i-1, i}, T_{i, i+1}), & \text{otherwise}
+		% 	\end{cases}
+		% \end{equation}
+		\begin{equation}
+			\mathcal{R}_i \triangleq [T_{i-1, i}, T_{i, i+1}),
+		\end{equation}
+		where we define $T_{0, 1} \triangleq 0$ and $T_{M, M+1} \triangleq \infty$. On the other hand, the transition probability matrix is
+		\begin{equation}
+			\boldsymbol{P} =
+			\begin{bmatrix}
+				p_{1 \mid 1} & \ldots & p_{M \mid 1} \\
+				\vdots & \ddots & \vdots \\
+				p_{1 \mid M} & \ldots & p_{M \mid M}
+			\end{bmatrix},
+		\end{equation}
+		where $p_{j \mid i}$ denotes the transition probability from channel input state $i$ to output state $j$. It can be derived as
+		\begin{equation}
+			p_{j \mid i} = p(z \in \mathcal{R}_j \mid \mathcal{H}_i) = \int_{\mathcal{R}_j} f(z \mid \mathcal{H}_i) \dd z
+			\label{eq:transition_probability}
+		\end{equation}
+		where $f(z \mid \mathcal{H}_i)$ is the conditional probability density function of receiving $z$ under hypothesis $\mathcal{H}_i$.
+Since $z$ follows chi-squared distribution with $2N$ degrees of freedom, it holds that
+		\begin{equation}
+			f(z \mid \mathcal{H}_i) = \frac{z^{N-1} e^{-z/\sigma_i^2}}{\sigma_i^{2N} \Gamma(N)}
+			\label{eq:conditional_pdf}
+		\end{equation}
+		where $\Gamma(\cdot)$ is the gamma function and $\Gamma(N) = (N - 1) !$ for positive integer $N$.
+Therefore, the transition matrix $\boldsymbol{P}$ can be calculated by substituting \eqref{eq:conditional_pdf} into \eqref{eq:transition_probability}, and the optimal input distribution can be obtained by the Blahut-Arimoto algorithm \cite{Arimoto1972,Blahut1972}.
 
-		During the backscatter detection, the conditional probability density function of the channel output given the tag input for $M$-PSK is
-		\begin{equation}
-			f_{Y \mid C}(y \mid c_m) = ?
-		\end{equation}
+		% During the backscatter detection, the conditional probability density function of the channel output given the tag input for $M$-PSK is
+		% \begin{equation}
+		% 	f_{Y \mid C}(y \mid c_m) = ?
+		% \end{equation}
 

### 2021-09-07 main.tex
:pencil: Formulate WSR problem

@@
 		\begin{equation}
-			y[n] = \sqrt{p} h_{\mathrm{D}} s[n] + \sqrt{\alpha p} h_{\mathrm{C}} c s[n] + w[n],
+			y[n] = \sqrt{P} h_{\mathrm{D}} s[n] + \sqrt{\alpha P} h_{\mathrm{C}} c s[n] + w[n],
 		\end{equation}
-		where $p$ is the average transmit power at the AP and $w \sim \mathcal{CN}(0,\sigma^2)$ is the additive white Gaussian noise.
+		where $P$ is the average transmit power at the AP and $w \sim \mathcal{CN}(0,\sigma^2)$ is the additive white Gaussian noise.
 We also define $\boldsymbol{y} \triangleq \bigl[y[1], \ldots, y[N]\bigr]^T$.
@@
 			The main difference between symbiotic radio and conventional MAC is that the primary message also reaches the user from the backscatter link.
-This characteristic inspires one to first decode the tag message, then model its contribution within the equivalent channel during primary decoding (i.e., unify secondary decoding and backscatter channel training), instead of performing SIC.
-In such case, for each fading block, the primary transmission is able to achieve ergodic capacity with artificial channel variation created by the backscatter modulation.
+This characteristic inspires one to first decode the tag message, then model its contribution within the equivalent channel during primary decoding (i.e., unify backscatter decoding and channel training), instead of performing SIC.
+In such case, the reflection pattern not only embeds the tag message but also adjusts the legacy channel in a controllable manner.
+Therefore, for a fixed fading block, the primary transmission is able to achieve the ergodic capacity with artificial channel variation created by the backscatter modulation.
+[Channel over channel, randomness over randomness]
 		\end{remark}
 
-		To investigate how backscatter modulation potentially benefits the primary transmission, we first decode the tag symbol $c$ in presence of unknown AP symbol $\boldsymbol{s}$.
-Interestingly, the tag detection indeed coincides with Ambient Backscatter Communications (AmBC) where the signal from the ambient source is unknown.
-Denote $\mathcal{H}_m$ as the hypothesis that the tag transmits $c_m$.
-In such case, the received signal per symbol block follows the CSCG distribution of $y_m[n] \sim \mathcal{CN}(0,\sigma_m^2)$, where
+		\begin{subsection}{Backscatter Detection}
+			To investigate how backscatter modulation potentially benefits the primary transmission, we first decode the tag symbol $c$ in presence of the interference from the primary message $\boldsymbol{s}$.
+In such case, the detection indeed coincides with that of Ambient Backscatter Communications (AmBC) where the signaling from the ambient source is unknown, and the received signal per symbol block follows the CSCG distribution of $y_m[n] \sim \mathcal{CN}(0,\sigma_m^2)$, where
 			\begin{equation}
-			\sigma_m^2 \triangleq \lvert h_{\mathrm{D}} + \sqrt{\alpha} h_{\mathrm{C}} c_m \rvert^2 p + \sigma^2
+				\sigma_m^2 \triangleq \lvert h_{\mathrm{D}} + \sqrt{\alpha} h_{\mathrm{C}} c_m \rvert^2 P + \sigma^2
 			\end{equation}
@@
 For the ease of exposition, we sort $\{\sigma_m^2\}$ in a descending order by bijective mapping $f \colon m \mapsto i$,\footnote{Note that the mapping is not unique and the detection fails when two different constellation points yield the same energy level.} and formulate a sequence $\langle \sigma_i^2 \rangle$ where $\sigma_i^2 \ge \sigma_j^2$ for $i > j$, $i,j \in \mathcal{M}$.
+Denote $\mathcal{H}_i$ as the hypothesis that the tag transmits $c_i$.
 Following \cite{Qian2019}, the optimal Maximum-Likelihood (ML) detector boils down to the energy detector, and the likelihood ratio between hypotheses $\mathcal{H}_i$ and $\mathcal{H}_j$ is
@@
 			On top of this, the decision region of hypothesis $\mathcal{H}_i$ can be expressed as
-		% \begin{equation}
-		% 	\mathcal{R}(\mathcal{H}_i) \triangleq
-		% 	\begin{cases}
-		% 		[0, T_{1, 2}), & i = 1, \\
-		% 		[T_{M-1, M}, \infty), & i = M, \\
-		% 		[T_{i-1, i}, T_{i, i+1}), & \text{otherwise}
-		% 	\end{cases}
-		% \end{equation}
 			\begin{equation}
@@
 			\end{equation}
-		where $\Gamma(\cdot)$ is the gamma function and $\Gamma(N) = (N - 1) !$ for positive integer $N$.
+			where $\Gamma(\cdot)$ is the gamma function.
 Therefore, the transition matrix $\boldsymbol{P}$ can be calculated by substituting \eqref{eq:conditional_pdf} into \eqref{eq:transition_probability}, and the optimal input distribution can be obtained by the Blahut-Arimoto algorithm \cite{Arimoto1972,Blahut1972}.
+		\end{subsection}
 
-		% During the backscatter detection, the conditional probability density function of the channel output given the tag input for $M$-PSK is
-		% \begin{equation}
-		% 	f_{Y \mid C}(y \mid c_m) = ?
-		% \end{equation}
+		\begin{subsection}{Legacy Transmission}
+			Once the tag message is successfully recovered, the user combines the backscattered symbol with the cascaded channel to eliminate the uncertainty of the AP-TG-UE path and detects the legacy information.
+The received signal at symbol block $n$ is essentially
+			\begin{equation}
+				y[n] = \sqrt{P} (h_{\mathrm{D}} + \sqrt{\alpha} h_{\mathrm{C}} c) s[n] + w[n] \triangleq \sqrt{P} h_{\mathrm{E}}(c) s + w[n],
+			\end{equation}
+			which is reminiscent of IRS-aided point-to-point transmission with an equivalent channel of
+			\begin{equation}
+				h_{\mathrm{E}}(c) \triangleq h_{\mathrm{D}} + \sqrt{\alpha} h_{\mathrm{C}} c.
+			\end{equation}
+			For primary transmission, backscatter modulation creates an artificial fast fading within each fading block, and the equivalent CSI is known at the receiver once the backscattered symbol is successfully decoded.
+Therefore, the ergodic capacity of primary transmission within each symbol block is \cite{Tse2005}
+			\begin{equation}
+				R_s = \mathbb{E}_c \bigl[ \log_2 ( 1 + \lvert h_{\mathrm{E}}(c) \rvert^2 ) \bigr].
+			\end{equation}
+			It can be observed that the input distribution of $c$ determines the capacity of both primary and secondary links.
+		\end{subsection}
+		\label{se:system_model}
+	\end{section}
 
-		% Since $\mathbb{E}[\lvert s \rvert^2] = \mathbb{E}[\lvert c \rvert^2] = 1$, by treating the primary interference as noise, the SINR for the user to decode tag message $c$ is
-		% \begin{equation}
-		% 	\gamma_c = \frac{\alpha p \lvert h_{\mathrm{C}} \rvert^2}{p \lvert h_{\mathrm{D}} \rvert^2 + 1}.
-		% \end{equation}
-		Once the tag message is successfully recovered, we combine the backscattered symbol with the cascaded channel to eliminate the uncertainty of the AP-TG-UE path, and the received signal is essentially
-		\begin{equation}
-			y[n] = \sqrt{p} (h_{\mathrm{D}} + \sqrt{\alpha} h_{\mathrm{C}} c) s[n] + w[n] \triangleq \sqrt{p} h(c) s + w[n],
-		\end{equation}
-		which is reminiscent of IRS-aided point-to-point transmission with the equivalent channel defined as
-		\begin{equation}
-			h(c) \triangleq h_{\mathrm{D}} + \sqrt{\alpha} h_{\mathrm{C}} c.
-		\end{equation}
-		That is to say, the passive tag not only embeds its own message in the reflection pattern, but also influences the legacy transmission.
-For primary transmission, backscatter modulation creates a fast fading channel within the coherence time, and the equivalent CSI is known at the receiver once the backscattered symbol is successfully decoded.
-Therefore, the ergodic capacity of primary transmission within each fading block is \cite{Tse2005}
-		\begin{equation}
-			R_s = \mathbb{E}_c \bigl[ \log_2 ( 1 + \lvert h(c) \rvert^2 ) \bigr].
-		\end{equation}
-		We aims to optimize the input distribution of $c$ (i.e., the probability mass function of $M$-PSK) to achieve a flexible balance between the primary and secondary links.
-
-		% channel training - backscatter decoding
-
-		% \begin{remark}
-		% 	To investigate how backscatter modulation potentially benefits the primary transmission, we instead decode the secondary link before the primary link.
-Once the tag message is successfully decoded, the uncertainty of the AP-TG-UE path can be perfectly removed (by combining the backscattered symbol and the cascaded channel), and its contribution can be modeled within the equivalent AP-UE channel.
-This is reminiscent of IRS-aided point-to-point transmission with CSI uncertainty (by backscatter modulation instead of channel estimation), where the passive tag simultaneously embeds its own message (embodied in secondary decoding) and assists the legacy transmission (embodied in primary decoding).
-
-		% 	[Channel over channel, randomness over randomness]
-		% \end{remark}
-
-		% Define $s_k$ as the primary symbol for user $k$ with $\boldsymbol{s} \triangleq [s_1,\ldots,s_K]^H \in \mathbb{C}^{K \times 1}$ satisfying $\mathbb{E}\{\boldsymbol{s}\boldsymbol{s}^H\}=\boldsymbol{I}$, and $c_{l_k}$ as the secondary symbol of tag $l_k$ with $\boldsymbol{c}_k \triangleq [c_1,\ldots,c_{L_k}]^H \in \mathbb{C}^{L_k \times 1}$ satisfying $\mathbb{E}\{\boldsymbol{c}_k\boldsymbol{c}_k^H\}=\boldsymbol{I}$.
-Let $s_k \sim \mathcal{CN} (0,1)$ and $c_{l_k}$ employs $M$-PSK by \eqref{eq:reflection_coefficient}.
-As tags typically transmit at a much lower rate than the AP, we assume the secondary symbol period $T_c$ is $N \in \mathbb{Z}_{++}$ times the primary symbol period $T_s$ (i.e., $T_c=NT_s$) and focus on one particular secondary symbol period.
-For linear precoding with no dedicated tag beams, the transmit signal during the primary symbol period $n \in \mathcal{N} \triangleq \{1,\ldots,N\}$ is
-		% \begin{equation}
-		% 	\boldsymbol{x}(n) = \sum_{k=1}^K \boldsymbol{w}_k s_k(n),
-		% \end{equation}
-		% where $\boldsymbol{w}_k$ is the precoder for user $k$ satisfying the average transmit power constraint $\sum_{k=1}^K \lVert \boldsymbol{w}_k \rVert^2 \le P$.
-The received signal at tag $l_k$ is\footnote{For simplicity, the backscattered signals from all other tags are modeled within noise.}
-		% \begin{equation}
-		% 	y_{l_k}(n) = \sum_{j=1}^K \boldsymbol{h}_{\mathrm{F},l_k}^H \boldsymbol{w}_j s_j(n) + z_{l_k}(n),
-		% \end{equation}
-		% where $z_{l_k} \sim \mathcal{CN} (0,\sigma_{l_k}^2)$ is the additive white Gaussian noise\footnote{Since the tag employs no active RF components, the noise captured at backscatter antenna $z_{l_k}$ is assumed negligible \cite{Nikitin2005,Arnitz2013,Wu2021b}.}.
-Hence, the corresponding antenna input power is
-		% \begin{equation}
-		% 	P_{0,l_k} = \sum_{j=1}^K \lvert \boldsymbol{h}_{\mathrm{F},l_k}^H \boldsymbol{w}_j \rvert^2.
-		% 	\label{eq:P_0}
-		% \end{equation}
-		% In practice, the rectifier is a non-linear device and the RF-to-DC conversion efficiency depends on the input power \cite{Clerckx2016a,Clerckx2018,Clerckx2019}.
-On top of \eqref{eq:P_H} and \eqref{eq:P_0}, when all modulation states are equiprobable, the average harvester output power is
-		% \begin{align}
-		% 	P_{l_k}
-		% 	& = \frac{1}{M} \Biggl( \sum_{i_1} \zeta \biggl( \eta_{i_1} (1 - \alpha_{l_k}^2) \sum_{j=1}^K \lvert \boldsymbol{h}_{\mathrm{F},l_k}^H \boldsymbol{w}_j \rvert^2 \biggr) \\
-		% 	& \quad + \sum_{i_2} \zeta \biggl( \frac{(1 - \alpha_{l_k}^2) \sum_{j=1}^K \lvert \boldsymbol{h}_{\mathrm{F},l_k}^H \boldsymbol{w}_j \rvert^2}{\eta_{i_2}} \biggr) \Biggr),
-		% \end{align}
-		% where $i_1 \ge M {\arccos \alpha_{l_k}} / {2 \pi}$, $i_2<M {\arccos \alpha_{l_k}} / {2 \pi}$, and $\zeta(\cdot)$ is the harvester response function.
-On the other hand, we define the scattered channel by tag $l_k$ as
-		% \begin{equation}
-		% 	\boldsymbol{h}_{l_k}^H \triangleq \alpha_{l_k} h_{\mathrm{B},l_k} \boldsymbol{h}_{\mathrm{F},l_k}^H.
-		% \end{equation}
-		% Hence, the received signal at user $k$ is
-		% \begin{align}
-		% 	y_k(n)
-		% 	& = \sum_{j=1}^K \left( \boldsymbol{h}_{\mathrm{D},k}^H + \sum_{l_k=1}^{L_k} c_{l_k} \boldsymbol{h}_{l_k}^H \right) \boldsymbol{w}_j s_j(n) + z_k(n) \\
-		% 	& \triangleq \sum_{j=1}^K \boldsymbol{h}_k^H \boldsymbol{w}_j s_j(n) + z_k(n),
-		% \end{align}
-		% where
-		% \begin{equation}
-		% 	\boldsymbol{h}_k^H \triangleq \boldsymbol{h}_{\mathrm{D},k}^H + \sum_{l_k=1}^{L_k} c_{l_k} \boldsymbol{h}_{l_k}^H
-		% 	\label{eq:h}
-		% \end{equation}
-		% is the equivalent channel of user $k$ and $z_k \sim \mathcal{CN} (0,\sigma_k^2)$ is the additive white Gaussian noise.
-		% \begin{remark}
-		% 	From the perspective of broadcast, the components scattered by the tags essentially create uncertainty over the direct AP-UE channel.
-If the backscattered symbols are unknown when decoding the broadcasted symbols, the uncertainty should be either covered by non-coherent detection \cite{Long2020a} or modeled as CSI error that introduces interference.
-That is to say, the equivalent channel is perfectly known only when all tag massages are successfully decoded.
-		% \end{remark}
-
-		% \begin{figure}[!t]
-		% 	\centering
-		% 		\resizebox{0.95\columnwidth}{!}{
-		% 			\begin{tikzpicture}
-		% 				\foreach \x in {1,...,12}
-		% 					\draw [pattern=crosshatch dots,pattern color=blue](\x,0) rectangle ++(1,1);
-		% 				\foreach \x in {1,...,12}
-		% 					\foreach \y in {-3,...,-1}{
-		% 						\pgfmathsetmacro\floorval{int(floor((\x+\y)/4))}
-		% 						\pgfmathsetmacro\modval{int(mod((\x+\y),4))}
-		% 						\ifnum \floorval=0
-		% 							\ifnum \modval=0
-		% 								\draw [pattern=horizontal lines,pattern color=red](\x,\y) rectangle ++(1,1);
-		% 							\else
-		% 								\draw [pattern=horizontal lines,pattern color=yellow](\x,\y) rectangle ++(1,1);
-		% 							\fi
-		% 						\else
-		% 							\ifnum \floorval=1
-		% 								\ifnum \modval=0
-		% 									\draw [pattern=north west lines,pattern color=red](\x,\y) rectangle ++(1,1);
-		% 								\else
-		% 									\draw [pattern=north west lines,pattern color=yellow](\x,\y) rectangle ++(1,1);
-		% 								\fi
-		% 							\else
-		% 								\ifnum \floorval=2
-		% 									\ifnum \modval=0
-		% 										\draw [pattern=vertical lines,pattern color=red](\x,\y) rectangle ++(1,1);
-		% 									\else
-		% 										\draw [pattern=vertical lines,pattern color=yellow](\x,\y) rectangle ++(1,1);
-		% 									\fi
-		% 								\else
-		% 									\draw (\x,\y) rectangle ++(1,1);
-		% 									% \ifnum \modval=0
-		% 									% 	\draw (\x,\y) rectangle ++(1,1);
-		% 									% \else
-		% 									% 	\draw [pattern=north east lines,pattern color=yellow](\x,\y) rectangle ++(1,1);
-		% 									% \fi
-		% 								\fi
-		% 							\fi
-		% 						\fi
-		% 					}
-		% 				\node[font=\huge] at (-2,0.5) {Broadcast};
-		% 				\node[font=\huge] at (-2,-0.5) {Tag \num{1}};
-		% 				\node[font=\huge] at (-2,-1.5) {Tag \num{2}};
-		% 				\node[font=\huge] at (-2,-2.5) {Tag \num{3}};
-		% 				\node[font=\huge] at (14,-1) {$\cdots$};
-		% 				\node[font=\huge,right] at (16.75,0){$b=1$};
-		% 				\node[font=\huge,right] at (16.75,-1){$b=2$};
-		% 				\node[font=\huge,right] at (16.75,-2){$b=3$};
-		% 				\draw [pattern=horizontal lines](16,-0.25) rectangle ++(0.5,0.5);
-		% 				\draw [pattern=north west lines](16,-1.25) rectangle ++(0.5,0.5);
-		% 				\draw [pattern=vertical lines](16,-2.25) rectangle ++(0.5,0.5);
-		% 				\draw[<->] (1,1.5) -- (2,1.5) node[font=\huge,midway,above]{$T_s$};
-		% 				\draw[<->] (1,-3.5) -- (5,-3.5) node[font=\huge,midway,below=0.125]{$T_c=NT_s$};
-		% 				\draw[->] (10.5,1.625) -- (10.5,1.25) node[font=\huge,at start,above]{Block $r$};
-		% 			\end{tikzpicture}
-		% 		}
-		% 	\caption{Primary and secondary symbol blocks received by user $k$ for $N=4$ and $L_k=3$.
-The blocks are normalized to the primary symbol period $T_s$.
-In the broadcast link, each block contains the message of all users at a specific time.
-In the backscatter links, each tag symbol lasts $N$ blocks (illustrated by a specific pattern) and the tag streams are delayed by multiples of $T_s$.
-Apart from decoding the self message, each user also decodes at most one tag message per primary symbol period (denoted by red blocks) and regards it as part of known channel in the following $N-1$ blocks.}
-		% 	\label{fi:blocks}
-		% \end{figure}
-
-		% To mitigate the interference from the backscatter link, we utilize its low rate property and propose a joint user and tag multiple access scheme as illustrated in Fig.~\ref{fi:blocks}.
-Specifically, the broadcast system can employ any general multiple access scheme\footnote{Since tags are associated to the nearest user, non-orthogonal protocols (e.g., NOMA and MU-LP) involving less coordination among users and tags are preferred \cite{Ding2021}.} (denoted by blue blocks), while the backscatter system integrates TDMA and NOMA as follows.
-Assuming the number of tags associated to user $k$ satisfies $L_k \le N$, $\forall k \in \mathcal{K}$\footnote{The proposed scheme can be extended to case of $L_k > N$, where at most $\lceil L_k/N \rceil$ tags transmit synchronously and user $k$ decodes up to $\lceil L_k/N \rceil$ tags per primary symbol period.
-Here we assume $L_k \le N$ for simplicity.}, we intentionally delay the stream of tag $l_k$ by $l_k-1$ primary symbol periods such that all tags transmit asynchronously and non-orthogonally.
-In such case, each user only needs to decode at most one tag message per primary symbol period (denoted by red blocks) and models it as part of the estimated channel in the following $N-1$ primary symbol periods (denoted by yellow blocks).
-We denote $r \in \mathbb{Z}_{++}$ as the index of primary symbols, and define $b \triangleq \lceil r/N \rceil$ as the index of secondary symbols and $d \equiv r \pmod N$ as the remainder of $N$ divides $r$.
-Therefore, the backscattered symbol by tag $l_k$ at block $r$ can be related to its index $b$ as
-		% \begin{equation}
-		% 	c_{l_k}(r) =
-		% 	\begin{cases}
-		% 		c_{l_k}(b), & d = 0 \text{ or } d \ge l_k, \\
-		% 		c_{l_k}(b-1), & 0 < d < l_k.
-		% 	\end{cases}
-		% \end{equation}
-		% It is assumed that $c_{l_k}(0)$, $\forall l_k \in \mathcal{L}_k$ is known at user $k$ and can be designed as zeros or pilots or cyclic prefixes.
-
-		% At block $r$, user $k$ always decodes its $r$-th primary symbol $s_k(r)$ first.
-If $d=0$ or $d>L_k$ \footnote{Note that $d=0$ corresponds to $n=N$.}, all backscattered symbols would be the same as in the previous block and no uncertainty is introduced by the backscattered link (denoted by all-yellow columns).
-Therefore, the equivalent channel at block $r$ is perfectly known and the tags create no interference to the primary transmission.
-On the other hand, if $0 < d \le L_k$, tag $d$ would trigger a new symbol $c_d(b)$ that lasts $N$ blocks but should be decoded within the current block $r$.
-In this case, user $k$ first treats the channel uncertainty from $c_d(b)$ as interference during primary decoding, then cancels the interference from decoded primary symbols and detects $c_d(b)$.
-Once a backscattered symbol is successfully decoded, its contribution to the equivalent channel \eqref{eq:h} is known.
-Therefore, under perfect detection, the estimated channel of user $k$ at block $r$ is
-		% \begin{equation}
-		% 	\bar{\boldsymbol{h}}_k^H(r) =
-		% 		\begin{cases}
-		% 			\boldsymbol{h}_{\mathrm{D},k}^H + \boldsymbol{c}_k^H(r) \boldsymbol{H}_k, & d = 0 \text{ or } d > L_k, \\
-		% 			\boldsymbol{h}_{\mathrm{D},k}^H + \boldsymbol{c}_{k \setminus d}^H(r) \boldsymbol{H}_{k \setminus d}, & 0 < d \le L_k,
-		% 		\end{cases}
-		% 		\label{eq:h_bar}
-		% \end{equation}
-		% where we define $\boldsymbol{c}_{k \setminus d} \triangleq [c_1,\ldots,c_{d-1},c_{d+1},\ldots,c_{L_k}]^H \in \mathbb{C}^{(L_k-1) \times 1}$, $\boldsymbol{H}_k \triangleq [\boldsymbol{h}_1,\ldots,\boldsymbol{h}_{L_k}]^H \in \mathbb{C}^{L_k \times Q}$ and $\boldsymbol{H}_{k \setminus d} \triangleq [\boldsymbol{h}_1,\ldots,\boldsymbol{h}_{d-1},\boldsymbol{h}_{d+1},\ldots,\boldsymbol{h}_{L_k}]^H \in \mathbb{C}^{(L_k-1) \times Q}$.
-Besides, the corresponding channel uncertainty is
-		% \begin{equation}
-		% 	\tilde{\boldsymbol{h}}_k^H(r) = \boldsymbol{h}_k^H(r) - \bar{\boldsymbol{h}}_k^H(r) =
-		% 		\begin{cases}
-		% 			0, & d = 0 \text{ or } d > L_k, \\
-		% 			c_{d}(r) \boldsymbol{h}_{d}^H, & 0 < d \le L_k.
-		% 		\end{cases}
-		% 		\label{eq:h_tilde}
-		% \end{equation}
-		% \begin{remark}
-		% 	From the perspective of broadcast, the backscattered channel is similar to the auxiliary channel provided by IRS.
-Once a tag symbol is successfully decoded, the corresponding channel uncertainty can be mitigated in the following $N-1$ primary symbol periods.
-This decoding mechanism can be viewed as a backscatter channel training process where the cascaded channels remain unchanged and the tag reflection coefficients are learned.
-If $N \gg L_k$, the training overhead (corresponding to $0 < d \le L_k$) can be omitted where the tags backscatter at very low rates and behave similar to the IRS elements.
-That is to say, passive beamforming can be enabled by carefully choosing the backscatter symbols based on CSI.
-		% \end{remark}
-
-		% Next, we investigate the performance of the proposed protocol under typical primary multiple access schemes.
-
-		% \begin{subsection}{NOMA}
-		% 	We first consider NOMA for the primary link.
-Without loss of generality, we assume the SNR of the estimated channels at block $r$ satisfy $\lVert \bar{\boldsymbol{h}}_j(r) \rVert / \sigma_j \le \lVert \bar{\boldsymbol{h}}_k(r) \rVert / \sigma_k$ such that the downlink symbol $s_j(r)$ is decoded before $s_k(r)$, $\forall j < k, \, j,k \in \mathcal{K}$.
-The SINR for user $k$ to decode the message of user $j$ at block $r$ is
-		% 	\begin{equation}
-		% 		\gamma_{j \to k}^{\mathrm{(N)}}(r) = \frac{\lvert \bar{\boldsymbol{h}}_k^H(r) \boldsymbol{w}_j \rvert^2}{\sum_{i=j+1}^K \lvert \bar{\boldsymbol{h}}_k^H(r) \boldsymbol{w}_i \rvert^2 + \sum_{i=1}^K \lvert \tilde{\boldsymbol{h}}_k^H(r) \boldsymbol{w}_i \rvert^2 + \sigma_k^2},
-		% 		\label{eq:gamma_jk^N}
-		% 	\end{equation}
-		% 	where the interference from all users stronger than $j$ and channel uncertainty from all tags are treated as noise.
-Once $s_j(r)$ is successfully decoded, its contribution is cancelled from $y_k(r)$.
-The process is repeated until user $k$ reaches its own stream, and the self-decoding SINR is
-		% 	\begin{equation}
-		% 		\gamma_{k \to k}^{\mathrm{(N)}}(r) = \frac{\lvert \bar{\boldsymbol{h}}_k^H(r) \boldsymbol{w}_k \rvert^2}{\sum_{j=k+1}^K \lvert \bar{\boldsymbol{h}}_k^H(r) \boldsymbol{w}_j \rvert^2 + \sum_{j=1}^K \lvert \tilde{\boldsymbol{h}}_k^H(r) \boldsymbol{w}_j \rvert^2 + \sigma_k^2}.
-		% 		\label{eq:gamma_kk^N}
-		% 	\end{equation}
-		% 	After successfully decoded its own stream, user $k$ has two options.
-When $d=0$ or $d>L_k$, the estimated channel \eqref{eq:h_bar} equals the equivalent channel \eqref{eq:h} and it boils down to an backscatter-assisted NOMA broadcast block.
-In this case, the second term of the denominator of \eqref{eq:gamma_jk^N}, \eqref{eq:gamma_kk^N} are zero and user $k$ terminates the operation after decoding its own stream.
-On the other hand, when $0 < d \le L_k$, tag $d$ triggers a new symbol at block $r$ that contributes to channel uncertainty \eqref{eq:h_tilde}.
-In this case, user $k$ continues to cancel the interference from its own stream (i.e., perform an extra layer SIC on top of primary decoding), then decodes $c_d(b)$ at SINR
-		% 	\begin{equation}
-		% 		\gamma_{d \to k}^{\mathrm{(N)}}(r) = \frac{\sum_{j=1}^K \lvert \boldsymbol{h}_d^H \boldsymbol{w}_j \rvert^2}{\sum_{j=k+1}^K \lvert \bar{\boldsymbol{h}}_k^H(r) \boldsymbol{w}_j \rvert^2 + \sigma_k^2}.
-		% 		\label{eq:gamma_dk^N}
-		% 	\end{equation}
-		% 	Once $c_d(b)$ is successfully decoded, its contribution would be modeled within the known channel in the following $N-1$ blocks to help both primary and secondary decodings.
-		% \end{subsection}
-
-		% \begin{subsection}{MU-LP}
-		% 	MU-LP in the primary link treats the interference occurred in primary decoding as interference. The SINR for user $k$ to decode its own stream at block $r$ is
-		% 	\begin{equation}
-		% 		\gamma_{k \to k}^{\mathrm{(M)}}(r) = \frac{\lvert \bar{\boldsymbol{h}}_k^H(r) \boldsymbol{w}_k \rvert^2}{\sum_{j \in \mathcal{K} \setminus k} \lvert \bar{\boldsymbol{h}}_k^H(r) \boldsymbol{w}_j \rvert^2 + \sum_{j=1}^K \lvert \tilde{\boldsymbol{h}}_k^H(r) \boldsymbol{w}_j \rvert^2 + \sigma_k^2}.
-		% 		\label{eq:gamma_kk^M}
-		% 	\end{equation}
-		% 	Similarly, when $0 < d \le L_k$, user $k$ cancels the interference from its own stream and decodes $c_d(b)$ at SINR
-		% 	\begin{equation}
-		% 		\gamma_{d \to k}^{\mathrm{(N)}}(r) = \frac{\sum_{j=1}^K \lvert \boldsymbol{h}_d^H \boldsymbol{w}_j \rvert^2}{\sum_{j \in \mathcal{K} \setminus k} \lvert \bar{\boldsymbol{h}}_k^H(r) \boldsymbol{w}_j \rvert^2 + \sigma_k^2}.
-		% 		\label{eq:gamma_dk^M}
-		% 	\end{equation}
-		% 	The contribution of $c_d(b)$ is then modeled within the estimated channel in the following $N-1$ blocks.
-		% \end{subsection}
-
-		% \begin{remark}
-		% 	For a specific channel realization, we notice that $\gamma_{j \to k}$ and $\gamma_{k \to k}$ are generally functions of $\boldsymbol{c}_k$ such that the primary rate at each block should be evaluated over the expectation of the backscattered symbols \cite{Long2020a,Zhang2020c}.
-On the other hand, how tags contribute to the estimated channel depends on the specific block.
-Since each decoding cycle lasts $N$ blocks, another expectation over $N$ blocks is necessary.
-For a sufficiently large $N$, the average primary achievable rate of user $k$ is
-		% 	\begin{equation}
-		% 		\mathbb{E}_n \Bigl\{ \mathbb{E}_{\boldsymbol{c}_k}\bigl\{R_{k \to k}(n)\bigr\} \Bigr\} = \frac{1}{N} \sum_{n=1}^N \mathbb{E}_{\boldsymbol{c}_k}\Bigl\{\log_2 \bigl( 1 + \gamma_{k \to k}(n) \bigr)\Bigr\}.
-		% 		% \mathbb{E}_n \bigl\{ \mathbb{E}_{\boldsymbol{c}_k}\{\gamma_{k \to k}\} \bigl\} = \frac{1}{N} \sum_{n=1}^N \mathbb{E}_{\boldsymbol{c}_k}\{\gamma_{k \to k}(n)\}.
-		% 	\end{equation}
-		% 	In contrast, although $\gamma_{l_k \to k}$ depends on $\boldsymbol{c}_{k \setminus l_k}$, the decoding process for tag $l_k$ only lasts one block such that $\gamma_{l_k \to k}$ is irrelevant to $N$.
-Hence, the average secondary SINR of tag $l_k$ is $\mathbb{E}_{\boldsymbol{c}_{k \setminus l_k}}\{\gamma_{l_k \to k}\}$.
-[Need rate-SINR relationship for M-PSK.]
-		% \end{remark}
-		\label{se:system_model}
+	\begin{section}{Tag Input Distribution}
+		To achieve a flexible tradeoff between the backscatter and legacy links, we aims to optimize the probability mass function of the tag input distribution under $M$-PSK modulation.
+Denote the probability that the tag symbol $c$ takes $c_m$ as $p_m$ and the corresponding probability mass function as $\boldsymbol{p} = [p_1,\ldots,p_M]^T \in \mathbb{R}_+^{M \times 1}$.
+One possible problem formulation is to maximize the weighted sum of the primary and secondary rates subject to the sum-probability constraint
+		\begin{maxi!}
+			{\scriptstyle{\boldsymbol{p}}}{\rho R_s + (1 - \rho) R_c}{}{}
+			\addConstraint{\sum_{m \in \mathcal{M}} p_m}{=1,}{}
+		\end{maxi!}
+		where $\rho \in [0, 1]$ is the weight factor to control the backscatter-legacy tradeoff.
 	\end{section}

### 2021-09-08 main.tex
:pencil: Update channel transition probility matrix
:pencil: Derive backscatter achievable rate

@@
 The optimal strategy for the IRS is to choose one reflection state with probability \num{1} to boost the equivalent channel, while the optimal strategy for the modulator is to utilize all constellation points with equal probability.
-It inspires one to adaptively design the probability mass function of tag symbols to jointly benefit the backscatter modulation and passive beamforming.
+It inspires one to optimize the tag input distribution to jointly benefit the backscatter modulation and passive beamforming.
 			\end{remark}
@@
 
-		\begin{subsection}{Backscatter Detection}
+		\begin{subsection}{Backscatter Transmission}
 			To investigate how backscatter modulation potentially benefits the primary transmission, we first decode the tag symbol $c$ in presence of the interference from the primary message $\boldsymbol{s}$.
@@
 				\sigma_m^2 \triangleq \lvert h_{\mathrm{D}} + \sqrt{\alpha} h_{\mathrm{C}} c_m \rvert^2 P + \sigma^2
+				\label{eq:typical_energy}
 			\end{equation}
-			can be estimated at the user.
+			denotes the typical energy of the received signal when the tag is at state $m$, which can be estimated at the user.
 For the ease of exposition, we sort $\{\sigma_m^2\}$ in a descending order by bijective mapping $f \colon m \mapsto i$,\footnote{Note that the mapping is not unique and the detection fails when two different constellation points yield the same energy level.} and formulate a sequence $\langle \sigma_i^2 \rangle$ where $\sigma_i^2 \ge \sigma_j^2$ for $i > j$, $i,j \in \mathcal{M}$.
@@
 			\begin{equation}
-				T_{i, j} \triangleq N \frac{\sigma_i^2 \sigma_j^2}{\sigma_i^2 - \sigma_j^2} \log \frac{\sigma_i^2}{\sigma_j^2}.
+				T_{i, j} \triangleq N \frac{\sigma_i^2 \sigma_j^2}{\sigma_i^2 - \sigma_j^2} \log \frac{\sigma_i^2}{\sigma_j^2},
+				\label{eq:detection_threshold}
 			\end{equation}
-			On top of this, the decision region of hypothesis $\mathcal{H}_i$ can be expressed as
+			and the decision region of hypothesis $\mathcal{H}_i$ can be expressed as
 			\begin{equation}
 				\mathcal{R}_i \triangleq [T_{i-1, i}, T_{i, i+1}),
+				\label{eq:decision_region}
 			\end{equation}
-			where we define $T_{0, 1} \triangleq 0$ and $T_{M, M+1} \triangleq \infty$. On the other hand, the transition probability matrix is
+			where $T_{0, 1} \triangleq 0$ and $T_{M, M+1} \triangleq \infty$. On top of this, we define the forward transition probability matrix as
 			\begin{equation}
-				\boldsymbol{P} =
+				\boldsymbol{P} \triangleq
 				\begin{bmatrix}
-					p_{1 \mid 1} & \ldots & p_{M \mid 1} \\
+					p_{1, 1} & \ldots & p_{1, M} \\
 					\vdots & \ddots & \vdots \\
-					p_{1 \mid M} & \ldots & p_{M \mid M}
+					p_{M, 1} & \ldots & p_{M, M}
 				\end{bmatrix},
 			\end{equation}
-			where $p_{j \mid i}$ denotes the transition probability from channel input state $i$ to output state $j$. It can be derived as
+			where $p_{i, j}$ denotes the transition probability from channel input state $i$ to output state $j$. It can be derived as
 			\begin{equation}
-				p_{j \mid i} = p(z \in \mathcal{R}_j \mid \mathcal{H}_i) = \int_{\mathcal{R}_j} f(z \mid \mathcal{H}_i) \dd z
+				p_{i, j} = p(z \in \mathcal{R}_j \mid \mathcal{H}_i) = \int_{\mathcal{R}_j} f(z \mid \mathcal{H}_i) \dd z,
 				\label{eq:transition_probability}
@@
 			\begin{equation}
-				f(z \mid \mathcal{H}_i) = \frac{z^{N-1} e^{-z/\sigma_i^2}}{\sigma_i^{2N} \Gamma(N)}
+				f(z \mid \mathcal{H}_i) = \frac{z^{N-1} e^{-z/\sigma_i^2}}{\sigma_i^{2N} \Gamma(N)},
 				\label{eq:conditional_pdf}
@@
 			where $\Gamma(\cdot)$ is the gamma function.
-Therefore, the transition matrix $\boldsymbol{P}$ can be calculated by substituting \eqref{eq:conditional_pdf} into \eqref{eq:transition_probability}, and the optimal input distribution can be obtained by the Blahut-Arimoto algorithm \cite{Arimoto1972,Blahut1972}.
+To summarize, once the CSI of the direct and cascaded links are obtained, the typical energy of the received signal can be estimated by \eqref{eq:typical_energy}, the energy detection threshold can be computed by \eqref{eq:detection_threshold}, the decision region can be retrieved by \eqref{eq:decision_region}, and the forward transition matrix $\boldsymbol{P}$ can be calculated by substituting \eqref{eq:conditional_pdf} into \eqref{eq:transition_probability}.
+
+			We then investigate the achievable rate of the backscatter link.
+Denote the tag input probability mass function as $\boldsymbol{r} = [r_1,\ldots,r_M]^T \in \mathbb{R}_+^{M \times 1}$ where $r_m$ is the probability to transmit symbol $c_m$ [strictly positive?].
+For a given input distribution $\boldsymbol{r}$ and forward transition matrix $\boldsymbol{P}$, the achievable backscatter rate can be expressed as
+			\begin{equation}
+				R_c = \max_{\boldsymbol{Q}} \sum_{i \in \mathcal{M}} \sum_{j \in \mathcal{M}} r_i p_{i, j} \log \frac{q_{j, i}}{r_i},
+			\end{equation}
+			where $\boldsymbol{Q}$ is the backward transition probability matrix \cite{Blahut1972}
+			\begin{equation}
+				\boldsymbol{Q} \triangleq
+				\begin{bmatrix}
+					q_{1, 1} & \ldots & q_{1, M} \\
+					\vdots & \ddots & \vdots \\
+					q_{M, 1} & \ldots & q_{M, M}
+				\end{bmatrix},
+			\end{equation}
+			and $q_{j, i}$ denotes the transition probability from channel output state $j$ to input state $i$.
 		\end{subsection}
@@
 Therefore, the ergodic capacity of primary transmission within each symbol block is \cite{Tse2005}
-			\begin{equation}
-				R_s = \mathbb{E}_c \bigl[ \log_2 ( 1 + \lvert h_{\mathrm{E}}(c) \rvert^2 ) \bigr].
-			\end{equation}
-			It can be observed that the input distribution of $c$ determines the capacity of both primary and secondary links.
+			\begin{align}
+				R_s
+				& = \mathbb{E}_c \bigl[ \log_2 (1 + \gamma \lvert h_{\mathrm{E}}(c) \rvert^2) \bigr] \nonumber \\
+				& = \sum_{m \in \mathcal{M}} r_m \log_2 \bigl( 1 + \gamma \lvert h_{\mathrm{D}} + \sqrt{\alpha} h_{\mathrm{C}} c_m \rvert^2 \bigr),
+			\end{align}
+			where $\gamma \triangleq P / \sigma^2$ is the average transmit Signal-to-Noise Ratio (SNR).
+It can be observed that the input distribution of $c$ determines the achievable rate of both primary and secondary links.
 		\end{subsection}
@@
 	\begin{section}{Tag Input Distribution}
-		To achieve a flexible tradeoff between the backscatter and legacy links, we aims to optimize the probability mass function of the tag input distribution under $M$-PSK modulation.
-Denote the probability that the tag symbol $c$ takes $c_m$ as $p_m$ and the corresponding probability mass function as $\boldsymbol{p} = [p_1,\ldots,p_M]^T \in \mathbb{R}_+^{M \times 1}$.
-One possible problem formulation is to maximize the weighted sum of the primary and secondary rates subject to the sum-probability constraint
+		To achieve a flexible tradeoff between the backscatter and legacy links, we aims to optimize the tag input probability mass function, under $M$-PSK modulation, to maximize the weighted sum of the primary and secondary rates subject to the sum-probability constraint
 		\begin{maxi!}
-			{\scriptstyle{\boldsymbol{p}}}{\rho R_s + (1 - \rho) R_c}{}{}
-			\addConstraint{\sum_{m \in \mathcal{M}} p_m}{=1,}{}
+			{\scriptstyle{\boldsymbol{r}}}{\rho R_s + (1 - \rho) R_c}{}{}
+			\addConstraint{\sum_{m \in \mathcal{M}} r_m}{=1,}{}
 		\end{maxi!}
-		where $\rho \in [0, 1]$ is the weight factor to control the backscatter-legacy tradeoff.
+		where $\rho \in [0, 1]$ is the weight factor.
 	\end{section}

### 2021-09-09 main.tex
:pencil: Derive optimal backward transition probability and input distribution

@@
 
+\listfiles
 \interdisplaylinepenalty=2500
@@
 \newtheorem{remark}{Remark}
+\newtheorem{theorem}{Theorem}
 \DeclareSIUnit{\belm}{Bm}
@@
 \usetikzlibrary{arrows,calc,matrix,patterns,positioning}
+
+\DeclarePairedDelimiterX{\infdivx}[2]{(}{)}{%
+	#1\;\delimsize\|\;#2%
+}
+\newcommand{\infdiv}{D\infdivx}
 
@@
 			\end{equation}
-			denotes the typical energy of the received signal when the tag is at state $m$, which can be estimated at the user.
-For the ease of exposition, we sort $\{\sigma_m^2\}$ in a descending order by bijective mapping $f \colon m \mapsto i$,\footnote{Note that the mapping is not unique and the detection fails when two different constellation points yield the same energy level.} and formulate a sequence $\langle \sigma_i^2 \rangle$ where $\sigma_i^2 \ge \sigma_j^2$ for $i > j$, $i,j \in \mathcal{M}$.
+			denotes the typical received signal energy over $N$ symbol blocks when the tag is at state $m$, which can be estimated at the user.
+For the ease of exposition, we sort $\{\sigma_m^2\}$ in a descending order by bijective mapping $f \colon m \mapsto i$\footnote{Note that the mapping is not unique and the detection fails when two different constellation points yield the same energy level.} and let $\sigma_i^2 \ge \sigma_j^2$ for $i > j$, $i,j \in \mathcal{M}$.
 Denote $\mathcal{H}_i$ as the hypothesis that the tag transmits $c_i$.
@@
 			\end{equation}
-			where $T_{0, 1} \triangleq 0$ and $T_{M, M+1} \triangleq \infty$. On top of this, we define the forward transition probability matrix as
+			with $T_{0, 1} \triangleq 0$ and $T_{M, M+1} \triangleq \infty$. On top of this, we define the forward transition probability matrix $\boldsymbol{P} \in \mathbb{R}_{+}^{M \times M}$ as
 			\begin{equation}
@@
 			where $\Gamma(\cdot)$ is the gamma function.
-To summarize, once the CSI of the direct and cascaded links are obtained, the typical energy of the received signal can be estimated by \eqref{eq:typical_energy}, the energy detection threshold can be computed by \eqref{eq:detection_threshold}, the decision region can be retrieved by \eqref{eq:decision_region}, and the forward transition matrix $\boldsymbol{P}$ can be calculated by substituting \eqref{eq:conditional_pdf} into \eqref{eq:transition_probability}.
+To summarize, with the CSI of the direct and cascaded links, the typical energy of the received signal can be estimated by \eqref{eq:typical_energy}, the energy detection threshold can be computed by \eqref{eq:detection_threshold}, the decision region can be retrieved by \eqref{eq:decision_region}, and the forward transition matrix $\boldsymbol{P}$ can be calculated by substituting \eqref{eq:conditional_pdf} into \eqref{eq:transition_probability}.
 
@@
 Denote the tag input probability mass function as $\boldsymbol{r} = [r_1,\ldots,r_M]^T \in \mathbb{R}_+^{M \times 1}$ where $r_m$ is the probability to transmit symbol $c_m$ [strictly positive?].
-For a given input distribution $\boldsymbol{r}$ and forward transition matrix $\boldsymbol{P}$, the achievable backscatter rate can be expressed as
+For a given input distribution $\boldsymbol{r}$ and forward transition matrix $\boldsymbol{P}$, the achievable backscatter rate can be written as
 			\begin{equation}
-				R_c = \max_{\boldsymbol{Q}} \sum_{i \in \mathcal{M}} \sum_{j \in \mathcal{M}} r_i p_{i, j} \log \frac{q_{j, i}}{r_i},
+				R_c = \max_{\boldsymbol{Q} \ge 0} \sum_{i \in \mathcal{M}} \sum_{j \in \mathcal{M}} r_i p_{i, j} \log_2 \frac{q_{j, i}}{r_i} \ [\si{bpcu}],
+				\label{eq:secondary_rate}
 			\end{equation}
-			where $\boldsymbol{Q}$ is the backward transition probability matrix \cite{Blahut1972}
+			where $\boldsymbol{Q} \in \mathbb{R}_{+}^{M \times M}$ is the backward transition probability matrix \cite{Yeung2008}
 			\begin{equation}
@@
 		\begin{subsection}{Legacy Transmission}
-			Once the tag message is successfully recovered, the user combines the backscattered symbol with the cascaded channel to eliminate the uncertainty of the AP-TG-UE path and detects the legacy information.
-The received signal at symbol block $n$ is essentially
+			Once the backscattered symbol is successfully recovered, it is combined with the cascaded channel to eliminate the uncertainty of the AP-TG-UE path and assist the legacy transmission.
+Therefore, the received signal at symbol block $n$ is essentially
 			\begin{equation}
@@
 			\end{equation}
-			which is reminiscent of IRS-aided point-to-point transmission with an equivalent channel of
+			which is reminiscent of an IRS-aided point-to-point transmission with an equivalent channel of
 			\begin{equation}
@@
 			\end{equation}
-			For primary transmission, backscatter modulation creates an artificial fast fading within each fading block, and the equivalent CSI is known at the receiver once the backscattered symbol is successfully decoded.
+			For primary transmission, backscatter modulation creates an artificial fast fading within each fading block, and AP can obtain the equivalent CSI distribution for any given tag input probability mass function $\boldsymbol{r}$.
 Therefore, the ergodic capacity of primary transmission within each symbol block is \cite{Tse2005}
@@
 				& = \mathbb{E}_c \bigl[ \log_2 (1 + \gamma \lvert h_{\mathrm{E}}(c) \rvert^2) \bigr] \nonumber \\
-				& = \sum_{m \in \mathcal{M}} r_m \log_2 \bigl( 1 + \gamma \lvert h_{\mathrm{D}} + \sqrt{\alpha} h_{\mathrm{C}} c_m \rvert^2 \bigr),
+				& = \sum_{i \in \mathcal{M}} r_i \log_2 \bigl( 1 + \gamma \lvert h_{\mathrm{D}} + \sqrt{\alpha} h_{\mathrm{C}} c_i \rvert^2 \bigr) \ [\si{bps/Hz}],
+				\label{eq:primary_rate}
 			\end{align}
 			where $\gamma \triangleq P / \sigma^2$ is the average transmit Signal-to-Noise Ratio (SNR).
-It can be observed that the input distribution of $c$ determines the achievable rate of both primary and secondary links.
+It can be concluded that the achievable rate of both primary and secondary links depend on the tag input distribution.
 		\end{subsection}
@@
 		\begin{maxi!}
-			{\scriptstyle{\boldsymbol{r}}}{\rho R_s + (1 - \rho) R_c}{}{}
-			\addConstraint{\sum_{m \in \mathcal{M}} r_m}{=1,}{}
+			{\scriptstyle{\boldsymbol{r} \ge 0}}{\rho R_s + (1 - \rho) R_c}{\label{op:weighted_sum_rate}}{\label{ob:weighted_sum_rate}}
+			\addConstraint{\sum_{i \in \mathcal{M}} r_i}{=1,}{\label{co:sum_probability}}
 		\end{maxi!}
-		where $\rho \in [0, 1]$ is the weight factor.
+		where $\rho \in [0, 1]$ is the weight factor. By substituting \eqref{eq:secondary_rate} and \eqref{eq:primary_rate} into \eqref{ob:weighted_sum_rate}, the problem expands to
+		\begin{maxi!}
+			% {\scriptstyle{\boldsymbol{r} \ge 0, \boldsymbol{Q} \ge 0}}{R(\boldsymbol{r}, \boldsymbol{Q}) \triangleq \rho \sum_{i \in \mathcal{M}} r_i \log_2 \bigl( 1 + \gamma \lvert h_{\mathrm{D}} + \sqrt{\alpha} h_{\mathrm{C}} c_i \rvert^2 \bigr) \nonumber}{}{}
+			% \breakObjective{\qquad \qquad \ + (1 - \rho) \sum_{i \in \mathcal{M}} \sum_{j \in \mathcal{M}} r_i p_{i, j} \log_2 \frac{q_{j, i}}{r_i}}
+			{\scriptstyle{\boldsymbol{r} \ge 0, \boldsymbol{Q} \ge 0}}{\rho \sum_{i \in \mathcal{M}} r_i \log_2 \bigl( 1 + \gamma \lvert h_{\mathrm{D}} + \sqrt{\alpha} h_{\mathrm{C}} c_i \rvert^2 \bigr) \nonumber}{}{}
+			\breakObjective{+ (1 - \rho) \sum_{i \in \mathcal{M}} \sum_{j \in \mathcal{M}} r_i p_{i, j} \log_2 \frac{q_{j, i}}{r_i}}{\label{ob:weighted_sum_rate_expanded}}
+			\addConstraint{\sum_{i \in \mathcal{M}} r_i}{=1.}{}
+		\end{maxi!}
+		Similar to the Blahut-Arimoto algorithm \cite{Arimoto1972,Blahut1972}, we optimize $\boldsymbol{r}$ and $\boldsymbol{Q}$ alternatively to obtain the local optimal tag input distribution and the corresponding weighted sum-rate.
+		\begin{theorem}
+			For any valid tag input probability mass function $\boldsymbol{r}$ [$\boldsymbol{r} > \boldsymbol{0}$?], the optimal backward transition probability from channel output state $j$ to input state $i$ is given by
+			\begin{equation}
+				q_{j, i}^{\star} = \frac{r_i p_{i, j}}{\sum_{i'} r_{i'} p_{i', j}}.
+				\label{eq:backward_transition}
+			\end{equation}
+			\label{th:backward_transition}
+		\end{theorem}
+		\begin{proof}
+			Please refer to Appendix~\ref{ap:backward_transition}.
+		\end{proof}
+		\begin{theorem}
+			For any valid backward transition probability $\boldsymbol{Q}$ [$\boldsymbol{Q} \ge \boldsymbol{0}$?], the optimal tag input probability mass function is given by
+			\begin{equation}
+				r_i = \frac{\bigl( 1 + \gamma \lvert h_{\mathrm{D}} + \sqrt{\alpha} h_{\mathrm{C}} c_i \rvert^2 \bigr)^{\rho / (1 - \rho)} \prod_{j \in \mathcal{M}} q_{j, i}^{p_{i, j}}}{\sum_{i' \in \mathcal{M}} \bigl( 1 + \gamma \lvert h_{\mathrm{D}} + \sqrt{\alpha} h_{\mathrm{C}} c_{i'} \rvert^2 \bigr)^{\rho / (1 - \rho)} \prod_{j \in \mathcal{M}} q_{j, i'}^{p_{i', j}}}.
+				\label{eq:input_distribution}
+			\end{equation}
+			\label{th:input_distribution}
+		\end{theorem}
+		\begin{proof}
+			Please refer to Appendix~\ref{ap:input_distribution}.
+		\end{proof}
+
 	\end{section}
+
+	\begin{appendix}
+		\begin{subsection}{Proof of Theorem~\ref{th:backward_transition}}
+			Denote the objective function \eqref{ob:weighted_sum_rate_expanded} as $R(\boldsymbol{r}, \boldsymbol{Q})$.
+Let $w_j \triangleq \sum_{i'} r_{i'} p_{i', j}$ and rearrange \eqref{eq:backward_transition} as
+			\begin{equation}
+				w_j q_{j, i}^{\star} = r_i p_{i, j}.
+			\end{equation}
+			Therefore,
+			\begin{align}
+				R(\boldsymbol{r}, \boldsymbol{Q}^{\star}) - R(\boldsymbol{r}, \boldsymbol{Q})
+				& = (1 - \rho) \sum_{i \in \mathcal{M}} \sum_{j \in \mathcal{M}} r_i p_{i, j} \log_2 \frac{q_{j, i}^{\star}}{q_{j, i}} \nonumber \\
+				& = (1 - \rho) \sum_{i \in \mathcal{M}} \sum_{j \in \mathcal{M}} w_j q_{j, i}^{\star} \log_2 \frac{q_{j, i}^{\star}}{q_{j, i}} \nonumber \\
+				& = (1 - \rho) \sum_{j \in \mathcal{M}} w_j \sum_{i \in \mathcal{M}} q_{j, i}^{\star} \log_2 \frac{q_{j, i}^{\star}}{q_{j, i}} \nonumber \\
+				& = (1 - \rho) \sum_{j \in \mathcal{M}} w_j \infdiv{q_{j, i}^{\star}}{q_{j, i}} \nonumber \\
+				& \ge 0,
+			\end{align}
+			with equality iff $\boldsymbol{Q} = \boldsymbol{Q}^{\star}$.
+			\label{ap:backward_transition}
+		\end{subsection}
+		\begin{subsection}{Proof of Theorem~\ref{th:input_distribution}}
+			We employ the method of Lagrange multipliers, temporally ignore the constraint $\boldsymbol{r} \ge 0$, and assume all logarithms are of base $e$. Define the Lagrangian function as
+			\begin{align}
+				J
+				& = \rho \sum_{i \in \mathcal{M}} r_i \log \bigl( 1 + \gamma \lvert h_{\mathrm{D}} + \sqrt{\alpha} h_{\mathrm{C}} c_i \rvert^2 \bigr) \nonumber \\
+				& \quad + (1 - \rho) \sum_{i \in \mathcal{M}} \sum_{j \in \mathcal{M}} r_i p_{i, j} \log \frac{q_{j, i}}{r_i} + \lambda \left( 1 - \sum_{i \in \mathcal{M}} r_i \right),
+			\end{align}
+			where $\lambda$ is the Lagrange multiplier associated with the sum-probability constraint. Differentiating $J$ with respect to $r_i$ gives
+			\begin{align}
+				\pdv{J}{r_i}
+				& = \rho \log \bigl( 1 + \gamma \lvert h_{\mathrm{D}} + \sqrt{\alpha} h_{\mathrm{C}} c_i \rvert^2 \bigr) \\
+				& \quad + (1 - \rho) \left( \sum_{j \in \mathcal{M}} p_{i, j} \log q_{j, i} - \log r_i - 1 \right),
+			\end{align}
+			and setting $\pdv*{J}{r_i} = 0$ suggests
+			\begin{equation}
+				r_i = e^{ -(\frac{\lambda}{1 - \rho} + 1)} \bigl( 1 + \gamma \lvert h_{\mathrm{D}} + \sqrt{\alpha} h_{\mathrm{C}} c_i \rvert^2 \bigr)^{\rho / (1 - \rho)} \prod_{j \in \mathcal{M}} q_{j, i}^{p_{i, j}}.
+			\end{equation}
+			By considering $\sum_{i \in \mathcal{M}} r_i = 1$, we can eliminate $\lambda$ and obtain the optimal tag input distribution as \eqref{eq:input_distribution}.
+			\label{ap:input_distribution}
+		\end{subsection}
+	\end{appendix}
 

### 2021-09-10 main.tex
:pencil: Update manuscript

@@
 			denotes the typical received signal energy over $N$ symbol blocks when the tag is at state $m$, which can be estimated at the user.
-For the ease of exposition, we sort $\{\sigma_m^2\}$ in a descending order by bijective mapping $f \colon m \mapsto i$\footnote{Note that the mapping is not unique and the detection fails when two different constellation points yield the same energy level.} and let $\sigma_i^2 \ge \sigma_j^2$ for $i > j$, $i,j \in \mathcal{M}$.
+For the ease of exposition, we sort $\{\sigma_m^2\}$ in a ascending order by bijective mapping $f \colon m \mapsto i$\footnote{Note that the mapping is not unique and the detection fails when two different constellation points yield the same energy level.} and let $\sigma_i^2 \le \sigma_j^2$ for $i < j$, $i,j \in \mathcal{M}$.
 Denote $\mathcal{H}_i$ as the hypothesis that the tag transmits $c_i$.
@@
 			\begin{equation}
-				\Lambda_{i, j}(\boldsymbol{y}) \underset{H_j}{\overset{H_i}{\gtrless}} 1 \iff z \underset{H_j}{\overset{H_i}{\gtrless}} T_{i, j},
+				\Lambda_{i, j}(\boldsymbol{y}) \underset{H_j}{\overset{H_i}{\lessgtr}} 1 \iff z \underset{H_j}{\overset{H_i}{\lessgtr}} T_{i, j},
 			\end{equation}
@@
 			\end{equation}
-			where $\boldsymbol{Q} \in \mathbb{R}_{+}^{M \times M}$ is the backward transition probability matrix \cite{Yeung2008}
+			where $\boldsymbol{Q} \in \mathbb{R}_{+}^{M \times M}$ is the backward transition probability matrix
 			\begin{equation}
@@
 		\begin{theorem}
-			For any valid tag input probability mass function $\boldsymbol{r}$ [$\boldsymbol{r} > \boldsymbol{0}$?], the optimal backward transition probability from channel output state $j$ to input state $i$ is given by
+			For any valid tag input probability mass function $\boldsymbol{r}$ [$\boldsymbol{r} > \boldsymbol{0}$?], the optimal backward transition probability from channel output state $j$ to input state $i$ follows Bayes' Theorem as
 			\begin{equation}
@@
 		\begin{theorem}
-			For any valid backward transition probability $\boldsymbol{Q}$ [$\boldsymbol{Q} \ge \boldsymbol{0}$?], the optimal tag input probability mass function is given by
+			For any valid backward transition probability $\boldsymbol{Q}$ [$\boldsymbol{Q} \ge 0$?], the optimal tag input probability mass function is given by
 			\begin{equation}
@@
 		\end{proof}
-
+		\begin{proposition}
+			For any feasible initial point [constellation subset], the Algorithm is guaranteed to converge to the global optimal of problem \eqref{op:weighted_sum_rate} and achieve the maximum weighted-sum rate.
+		\end{proposition}
+		\begin{proof}
+			The proof is similar to that in \cite[Chapter~9.3]{Yeung2008} and omitted here.
+		\end{proof}
 	\end{section}

### 2021-10-17 main.tex
:dizzy: Propose the idea of OFDM-based multiple access

@@
 
+	\begin{section}{OFDM}
+		Due to the constraint of energy detection, with single-antenna tags and reader, at most one AmBC tag can be decoded at a time and accurate detection requires repetition coding over multiple time/frequency blocks to mitigate the impact of primary symbols.
+Here we consider frequency-independent tag reflection and schedule one tag per OFDM symbol.
+
+		At OFDM symbol $r$, tag $l$ modulates its own information over all $N$ subcarriers while the remaining tags may operate in the cooperative (quantized IRS) mode.
+Channel frequency response at subband $n$ and block $r$
+		Received signal at OFDM symbol $r$ and subband $n$ is
+		\begin{equation}
+			y_n[r] = \sqrt{P} h_{\mathrm{E}}[r] s_n[r] + \sqrt{\alpha P} h_{\mathrm{C},l} c_l s_n[r] + w_n[r],
+		\end{equation}
+		where $h_{\mathrm{E}}[r] \triangleq \sum_{l' \ne l} h_{\mathrm{C},l'} c_{l'}^\star$ and $c_l$ is the symbol of tag $l$.
+Apparently $y_n[r] \sim \mathcal{CN}(0,\sigma_n^2[r])$ with $\sigma_n^2[r] \triangleq \lvert h_{\mathrm{E}}[r] + \sqrt{\alpha} h_{\mathrm{C},l} c_l \rvert^2 P + \sigma^2$.
+Define $\boldsymbol{y}[r] \triangleq [y_1[r],\ldots,y_N[r]]^T$ and we can do energy detection over $N$ subcarriers.
+	\end{section}
+
 	\begin{appendix}

### 2021-10-30 main.tex
:dizzy: Propose multi-tag cases

@@
 
+	\begin{section}{Multi-Tag Case}
+		In the $K$-tag scenario, the received signal at symbol block $n$ is
+		\begin{equation}
+			y[n] = \sqrt{P} h_{\mathrm{D}} s[n] + \sum_k \sqrt{\alpha_k} h_{\mathrm{C},k} c_k \sqrt{P} s[n] + w[n].
+		\end{equation}
+
+		On the one hand, we can compute the \emph{sum-rate} of the tags and characterize the (ergodic) primary-secondary capacity region by adjusting weight $\rho$. The weighted sum-rate can be expressed as
+		\begin{align}
+			J_1
+			& = \rho \mathbb{E}_{\boldsymbol{c}} \left[ \log_2 \left( 1 + \gamma \lvert h_{\mathrm{D}} + \sum_k \sqrt{\alpha_k} h_{\mathrm{C},k} c_k \rvert \right) \right] + (1 - \rho) R_c\\
+			& = \rho \sum_{i_1,\dots,i_K \in \mathcal{M}} \prod_{k \in \mathcal{K}} r_{k,i_k} \log_2 \left( 1 + \gamma \lvert h_{\mathrm{D}} + \sum_{k' \in \mathcal{K}} \sqrt{\alpha_{k'}} h_{\mathrm{C},k'} c_{k',i_{k'}} \rvert^2 \right)\\
+			& \quad + (1 - \rho) \sum_{i \in \mathcal{M}} \sum_{j \in \mathcal{M}^K} \sum_{k \in \mathcal{K}} r_{k,i} p_{i,j} \log \frac{q_{j,i}}{r_{k,i}}.
+		\end{align}
+		In this case, although we can independently maximize the primary/secondary rate in closed form (resp.
+quantized IRS and multi-user Blahut-Arimoto), the joint form can be tricky due to the $K$-product term.
+We may consider a 2-loop iterative algorithm, where the inner loop optimizes input distribution over letters while the outer loop over users.
+I am still working on the convergence and optimality proofs and they are very deep into information theory.
+
+		On the other hand, we can compute the rate region of the user and $K$ tags.
+However, the capacity region of discrete MAC remains unknown.
+We can obtain its outer bound by formulating a non-convex problem with a rank-1 constraint, then solve the relaxed problem.
+The difficulty is that the optimization is performed over $K$-dimensional array $\mathbb{R}^{\underbrace{M \times \ldots \times M}_{K}}$.
+	\end{section}
+
 	\begin{appendix}

### 2021-11-22 main.tex
:pencil: Update system model

@@
 			Tags perform backscatter modulation by switching the load impedance between different states.
-Consider an $M$-ary Phase Shift Keying (PSK).
-At tag state $m \in \mathcal{M} \triangleq \{1,\ldots,M\}$, the reflection coefficient $\Gamma_m$ maps to the desired signal constellation point $c_m$ as \cite{Thomas2012a}
+For an $M$-ary Quadrature Amplitude Modulation (QAM) at state $m \in \mathcal{M} \triangleq \{1,\ldots,M\}$, the reflection coefficient $\Gamma_m$ maps to the desired signal constellation point $c_m$ as \cite{Thomas2012a}
 			\begin{equation}
-				\Gamma_m = \alpha c_m = \alpha e^{\jmath \theta_m},
+				\Gamma_m = \alpha \frac{c_m}{\max_{m'} \lvert c_{m'} \rvert},
 				\label{eq:backscatter_modulation}
 			\end{equation}
-			where $\alpha \in [0,1]$ is the reflection efficiency at a given direction, and $\theta_m \triangleq 2 \pi m / M$ is the phase of the $m$-th constellation point of $M$-PSK.
+			where $\alpha \in [0,1]$ is the reflection efficiency at a given direction.
+For simplicity, we consider an $M$-ary Phase Shift Keying (PSK) with zero-offset (TODO), where the $m$-th constellation point is
+			\begin{equation}
+				c_m = \exp \left(j \frac{2 \pi m}{M}\right).
+				\label{eq:mpsk}
+			\end{equation}
 			\begin{remark}
@@
 
-	\begin{section}{System Model}
+	\begin{section}{The Multi-Tag Case}
+		% We then extend the algorithm to the $K$-tag case and characterize the achievable legacy rate-backscatter sum-rate region.
+
+		\begin{subsection}{System Model}
 			\begin{figure}[!t]
@@
 				\def\svgwidth{0.9\columnwidth}
-			\import{assets/}{symbiotic_radio.pdf_tex}
-			\caption{A single-user single-tag symbiotic radio system.}
+				\import{assets/}{symbiotic_radio.eps_tex}
+				\caption{A single-user multi-tag symbiotic radio system.}
 				\label{fi:symbiotic_radio}
 			\end{figure}
-		As shown in Fig.~\ref{fi:symbiotic_radio}, we propose a single-user (UE) single-tag (TG) symbiotic radio network where the RF signal generated by the single-antenna Access Point (AP) is shared by two coexisting systems.
+			As shown in Fig.~\ref{fi:symbiotic_radio}, we propose a single-user (UE) multi-tag (TG) symbiotic radio network where the RF signal generated by the single-antenna Access Point (AP) is shared by two coexisting systems.
+In the primary downlink system, the AP transmits information to the single-antenna user.
+In the secondary backscatter system, the AP acts as the carrier emitter, the $K$ nearby single-antenna tags modulate their information over the reradiated RF signals, and the user serves as the multi-tag backscatter reader.
+Denote the AP-UE direct channel as $h^{\mathrm{D}}$, the AP-TG $k \in \mathcal{K} \triangleq \{1,\ldots,K\}$ forward channel as $h_k^{\mathrm{F}}$, the TG $k$-UE backward channel as $h_k^{\mathrm{B}}$, and the cascaded forward-backward channel of tag $k$ as $h_k^{\mathrm{C}} \triangleq h_k^{\mathrm{B}} h_k^{\mathrm{F}}$.
+			% Let $h_k^{\mathrm{C}} \triangleq h_k^{\mathrm{B}} h_k^{\mathrm{F}}$ be the cascaded forward-backward channel of tag $k$.
+			For simplicity, we consider a quasi-static block fading model where the channel coefficients remain constant within each coherence interval and vary independently over different coherence intervals, and let the coherence interval $T$ be much longer than the backscatter symbol period $T_c$ and primary symbol period $T_s$.
+We also assume the direct channel and all cascaded channels can be successfully estimated and fed back to the AP.\footnote{Due to the lack of RF chains at the passive tag, accurate and efficient Channel State Information at the Transmitter (CSIT) acquisition can be challenging.
+One possible approach is that the AP sends pre-defined pilots, the tags respond in well-designed manners, and the user performs least-square estimation with feedbacks \cite{Bharadia2015,Yang2015b,Guo2019e}.} Since the tags need to physically switch the loads for backscatter modulation, they communicate at a much longer symbol period (and thus lower rates) than the primary system.
+As such, we assume all tags are perfectly synchronized and the backscatter symbol period satisfies $T_c = N T_s$ where $N \gg 1$ is a positive integer.
+
+			Without loss of generality, we focus on the transmissions during the interval of one particular backscatter symbol.
+To provide a preliminary insight, we assume the primary symbol $s[n]$ at block $n \in \mathcal{N} \triangleq \{1,\ldots,N\}$ is in standard CSCG distribution, and the backscatter symbol $c_k$ of tag $k$ employs $M$-PSK modulation by \eqref{eq:mpsk}, $\forall k \in \mathcal{K}$.
+			% at primary symbol block $n \in \mathcal{N} \triangleq \{1,\ldots,N\}$, the primary symbol $s[n] \sim \mathcal{CN}(0,1)$ is assumed in standard CSCG distribution.
+On the other hand, let the backscatter symbol $c_k$ of tag $k$ employ $M$-PSK modulation by \eqref{eq:mpsk}, $\forall k \in \mathcal{K}$.
+			Thus, the signal received by the user at block $n$ can be expressed as\footnote{We omit the signal reflected by two or more times and assume the time difference of arrival from different paths are negligible\cite{Wu2019,Guo2019b}.}
+			\begin{equation}
+				y[n] = \sqrt{P} \left(h^{\mathrm{D}} + \sum_{k \in \mathcal{K}} \sqrt{\alpha_k} h_k^{\mathrm{C}} c_k\right) s[n] + w[n],
+			\end{equation}
+			where $P$ is the average transmit power at the AP, and $w[n] \sim \mathcal{CN}(0,\sigma^2)$ is the Additive White Gaussian Noise (AWGN) at block $n$.
+Also, we stack the backscatter symbol of $K$ tags as $\boldsymbol{c} \triangleq [c_1,\ldots,c_K]^T$, the received signal over $N$ blocks as $\boldsymbol{y} \triangleq [y[1],\ldots,y[N]]^T$, and define the equivalent channel for primary transmission as
+			\begin{equation}
+				h^{\mathrm{E}}(\boldsymbol{c}) \triangleq h^{\mathrm{D}} + \sum_{k \in \mathcal{K}} \sqrt{\alpha_k} h_k^{\mathrm{C}} c_k.
+			\end{equation}
+
+			\begin{remark}
+				The proposed symbiotic radio system is reminiscent of a Multiple Access Channel (MAC) where the AP and the tags transmit simultaneously to the user.
+It inspired all existing papers [TODO] to perform Successive Interference Cancellation (SIC) that first decode the primary message in the presence of backscatter uncertainty, then cancel its contribution and decode the backscatter messages.
+However, different from the conventional MAC with Superposition Coding (SC), the symbiotic radio system involves Multiplication Coding (MC) because the primary and secondary messages are indeed multiplied in the backscattered signals.
+Therefore, the benefits of SIC might not outstand for symbiotic radio systems.
+			\end{remark}
+		\end{subsection}
+
+		\begin{subsection}{Signal Detection}
+			The main difference between symbiotic radio and conventional MAC is that the primary message also reaches the user from the backscatter link.
+This characteristic inspires one to first decode the tag message, then model its contribution within the equivalent channel during primary decoding (i.e., unify backscatter decoding and channel training), instead of performing SIC.
+In such case, the reflection pattern not only embeds the tag message but also adjusts the legacy channel in a controllable manner.
+Therefore, for a fixed fading block, the primary transmission is able to achieve the ergodic capacity with artificial channel variation created by the backscatter modulation.
+[Channel over channel, randomness over randomness]
+
+			To investigate how backscatter modulation potentially benefits the primary transmission, we first decode the tag symbol $c$ in presence of the interference from the primary message $\boldsymbol{s}$.
+In such case, the detection indeed coincides with that of Ambient Backscatter Communications (AmBC) where the signaling from the ambient source is unknown, and the received signal per symbol block follows the CSCG distribution of $y_m[n] \sim \mathcal{CN}(0,\sigma_m^2)$, where
+			\begin{equation}
+				\sigma_m^2 \triangleq \lvert h_{\mathrm{D}} + \sqrt{\alpha} h_{\mathrm{C}} c_m \rvert^2 P + \sigma^2
+				\label{eq:typical_energy}
+			\end{equation}
+			denotes the typical received signal energy over $N$ symbol blocks when the tag is at state $m$, which can be estimated at the user.
+For the ease of exposition, we sort $\{\sigma_m^2\}$ in a ascending order by bijective mapping $f \colon m \mapsto i$\footnote{Note that the mapping is not unique and the detection fails when two different constellation points yield the same energy level.} and let $\sigma_i^2 \le \sigma_j^2$ for $i < j$, $i,j \in \mathcal{M}$.
+Denote $\mathcal{H}_i$ as the hypothesis that the tag transmits $c_i$.
+Following \cite{Qian2019}, the optimal Maximum-Likelihood (ML) detector boils down to the energy detector, and the likelihood ratio between hypotheses $\mathcal{H}_i$ and $\mathcal{H}_j$ is
+			\begin{equation}
+				\Lambda_{i, j}(\boldsymbol{y}) = \frac{f(\boldsymbol{y} \mid \mathcal{H}_i)}{f(\boldsymbol{y} \mid \mathcal{H}_j)} = \left( \frac{\sigma_j^2}{\sigma_i^2} \right)^N \exp \left( \frac{(\sigma_i^2 - \sigma_j^2) z}{\sigma_i^2 \sigma_j^2} \right),
+			\end{equation}
+			where $f(\boldsymbol{y} \mid \mathcal{H}_i)$, $f(\boldsymbol{y} \mid \mathcal{H}_j)$ denote respectively the conditional probability density function of receiving $\boldsymbol{y}$ under hypothesis $\mathcal{H}_i$ and $\mathcal{H}_j$, and $z \triangleq \lVert y \rVert^2$ is the received signal energy over $N$ symbol blocks.
+The corresponding decision rule is
+			\begin{equation}
+				\Lambda_{i, j}(\boldsymbol{y}) \underset{H_j}{\overset{H_i}{\lessgtr}} 1 \iff z \underset{H_j}{\overset{H_i}{\lessgtr}} T_{i, j},
+			\end{equation}
+			where the optimal detection threshold is
+			\begin{equation}
+				T_{i, j} \triangleq N \frac{\sigma_i^2 \sigma_j^2}{\sigma_i^2 - \sigma_j^2} \log \frac{\sigma_i^2}{\sigma_j^2},
+				\label{eq:detection_threshold}
+			\end{equation}
+			and the decision region of hypothesis $\mathcal{H}_i$ can be expressed as
+			\begin{equation}
+				\mathcal{R}_i \triangleq [T_{i-1, i}, T_{i, i+1}),
+				\label{eq:decision_region}
+			\end{equation}
+			with $T_{0, 1} \triangleq 0$ and $T_{M, M+1} \triangleq \infty$. On top of this, we define the forward transition probability matrix $\boldsymbol{P} \in \mathbb{R}_{+}^{M \times M}$ as
+			\begin{equation}
+				\boldsymbol{P} \triangleq
+				\begin{bmatrix}
+					p_{1, 1} & \ldots & p_{1, M} \\
+					\vdots & \ddots & \vdots \\
+					p_{M, 1} & \ldots & p_{M, M}
+				\end{bmatrix},
+			\end{equation}
+			where $p_{i, j}$ denotes the transition probability from channel input state $i$ to output state $j$. It can be derived as
+			\begin{equation}
+				p_{i, j} = p(z \in \mathcal{R}_j \mid \mathcal{H}_i) = \int_{\mathcal{R}_j} f(z \mid \mathcal{H}_i) \dd z,
+				\label{eq:transition_probability}
+			\end{equation}
+			where $f(z \mid \mathcal{H}_i)$ is the conditional probability density function of receiving $z$ under hypothesis $\mathcal{H}_i$.
+Since $z$ follows chi-squared distribution with $2N$ degrees of freedom, it holds that
+			\begin{equation}
+				f(z \mid \mathcal{H}_i) = \frac{z^{N-1} e^{-z/\sigma_i^2}}{\sigma_i^{2N} \Gamma(N)},
+				\label{eq:conditional_pdf}
+			\end{equation}
+			where $\Gamma(\cdot)$ is the gamma function.
+To summarize, with the CSI of the direct and cascaded links, the typical energy of the received signal can be estimated by \eqref{eq:typical_energy}, the energy detection threshold can be computed by \eqref{eq:detection_threshold}, the decision region can be retrieved by \eqref{eq:decision_region}, and the forward transition matrix $\boldsymbol{P}$ can be calculated by substituting \eqref{eq:conditional_pdf} into \eqref{eq:transition_probability}.
+
+			We then investigate the achievable rate of the backscatter link.
+Denote the tag input probability mass function as $\boldsymbol{r} = [r_1,\ldots,r_M]^T \in \mathbb{R}_+^{M \times 1}$ where $r_m$ is the probability to transmit symbol $c_m$ [strictly positive?].
+For a given input distribution $\boldsymbol{r}$ and forward transition matrix $\boldsymbol{P}$, the achievable backscatter rate can be written as
+			\begin{equation}
+				R_c = \max_{\boldsymbol{Q} \ge 0} \sum_{i \in \mathcal{M}} \sum_{j \in \mathcal{M}} r_i p_{i, j} \log_2 \frac{q_{j, i}}{r_i} \ [\si{bpcu}],
+				\label{eq:secondary_rate}
+			\end{equation}
+			where $\boldsymbol{Q} \in \mathbb{R}_{+}^{M \times M}$ is the backward transition probability matrix
+			\begin{equation}
+				\boldsymbol{Q} \triangleq
+				\begin{bmatrix}
+					q_{1, 1} & \ldots & q_{1, M} \\
+					\vdots & \ddots & \vdots \\
+					q_{M, 1} & \ldots & q_{M, M}
+				\end{bmatrix},
+			\end{equation}
+			and $q_{j, i}$ denotes the transition probability from channel output state $j$ to input state $i$.
+		\end{subsection}
+	\end{section}
+
+	\begin{section}{The Single-tag Case}
+		% \begin{figure}[!t]
+		% 	\centering
+		% 	\def\svgwidth{0.9\columnwidth}
+		% 	\import{assets/}{symbiotic_radio.pdf_tex}
+		% 	\caption{A single-user single-tag symbiotic radio system.}
+		% 	\label{fi:symbiotic_radio}
+		% \end{figure}
+		As shown in Fig.~NULL, we propose a single-user (UE) single-tag (TG) symbiotic radio network where the RF signal generated by the single-antenna Access Point (AP) is shared by two coexisting systems.
 In the primary AP-UE downlink system, the AP transmits to the single-antenna user.
@@
 		where $P$ is the average transmit power at the AP and $w \sim \mathcal{CN}(0,\sigma^2)$ is the additive white Gaussian noise.
-We also define $\boldsymbol{y} \triangleq \bigl[y[1], \ldots, y[N]\bigr]^T$.
+We also define $\boldsymbol{y} \triangleq \bigl[y[1],\ldots,y[N]\bigr]^T$.
 
 		\begin{remark}
-			The symbiotic radio network can be regarded as as a special case of Multiple Access Channel (MAC) because the AP and the tag simultaneously transmit to the user.
+			The symbiotic radio network can be regarded as a special case of Multiple Access Channel (MAC) because the AP and the tag simultaneously transmit to the user.
 It is known that Superposition Coding-Successive Interference Cancellation (SC-SIC) with different decoding orders can achieve different vertices of the MAC capacity region \cite{Goldsmith2005}.
@@
 		\label{se:system_model}
-	\end{section}
 
-	\begin{section}{Tag Input Distribution}
+		\begin{subsection}{Achievable rate region}
 			To achieve a flexible tradeoff between the backscatter and legacy links, we aims to optimize the tag input probability mass function, under $M$-PSK modulation, to maximize the weighted sum of the primary and secondary rates subject to the sum-probability constraint
@@
 			\begin{maxi!}
-			% {\scriptstyle{\boldsymbol{r} \ge 0, \boldsymbol{Q} \ge 0}}{R(\boldsymbol{r}, \boldsymbol{Q}) \triangleq \rho \sum_{i \in \mathcal{M}} r_i \log_2 \bigl( 1 + \gamma \lvert h_{\mathrm{D}} + \sqrt{\alpha} h_{\mathrm{C}} c_i \rvert^2 \bigr) \nonumber}{}{}
-			% \breakObjective{\qquad \qquad \ + (1 - \rho) \sum_{i \in \mathcal{M}} \sum_{j \in \mathcal{M}} r_i p_{i, j} \log_2 \frac{q_{j, i}}{r_i}}
 				{\scriptstyle{\boldsymbol{r} \ge 0, \boldsymbol{Q} \ge 0}}{\rho \sum_{i \in \mathcal{M}} r_i \log_2 \bigl( 1 + \gamma \lvert h_{\mathrm{D}} + \sqrt{\alpha} h_{\mathrm{C}} c_i \rvert^2 \bigr) \nonumber}{}{}
@@
 			\end{proof}
+		\end{subsection}
 	\end{section}

### 2021-11-22 main.tex
:pencil: Update model for multi-antenna AP

@@
 	\begin{section}{The Multi-Tag Case}
-		% We then extend the algorithm to the $K$-tag case and characterize the achievable legacy rate-backscatter sum-rate region.
-
 		\begin{subsection}{System Model}
@@
 			\end{figure}
-			As shown in Fig.~\ref{fi:symbiotic_radio}, we propose a single-user (UE) multi-tag (TG) symbiotic radio network where the RF signal generated by the single-antenna Access Point (AP) is shared by two coexisting systems.
+			As shown in Fig.~\ref{fi:symbiotic_radio}, we propose a single-user (UE) multi-tag (TG) symbiotic radio network where the RF signal generated by the $Q$-antenna Access Point (AP) is shared by two coexisting systems.
 In the primary downlink system, the AP transmits information to the single-antenna user.
 In the secondary backscatter system, the AP acts as the carrier emitter, the $K$ nearby single-antenna tags modulate their information over the reradiated RF signals, and the user serves as the multi-tag backscatter reader.
-Denote the AP-UE direct channel as $h^{\mathrm{D}}$, the AP-TG $k \in \mathcal{K} \triangleq \{1,\ldots,K\}$ forward channel as $h_k^{\mathrm{F}}$, the TG $k$-UE backward channel as $h_k^{\mathrm{B}}$, and the cascaded forward-backward channel of tag $k$ as $h_k^{\mathrm{C}} \triangleq h_k^{\mathrm{B}} h_k^{\mathrm{F}}$.
-			% Let $h_k^{\mathrm{C}} \triangleq h_k^{\mathrm{B}} h_k^{\mathrm{F}}$ be the cascaded forward-backward channel of tag $k$.
-			For simplicity, we consider a quasi-static block fading model where the channel coefficients remain constant within each coherence interval and vary independently over different coherence intervals, and let the coherence interval $T$ be much longer than the backscatter symbol period $T_c$ and primary symbol period $T_s$.
+Denote the AP-UE direct channel as $\boldsymbol{h}_{\mathrm{D}}^H \in \mathbb{C}^{1 \times Q}$, the AP-TG $k \in \mathcal{K} \triangleq \{1,\ldots,K\}$ forward channel as $\boldsymbol{h}_{\mathrm{F},k}^H \in \mathbb{C}^{1 \times Q}$, the TG $k$-UE backward channel as $h_{\mathrm{B},k}$, and the cascaded forward-backward channel of tag $k$ as $\boldsymbol{h}_{\mathrm{C},k}^H \triangleq h_{\mathrm{B},k} \boldsymbol{h}_{\mathrm{F},k}^H \in \mathbb{C}^{1 \times Q}$.
+For simplicity, we consider a quasi-static block fading model where the channel coefficients remain constant within each coherence interval and vary independently over different coherence intervals, and assume the coherence interval $T$ is much longer than the backscatter symbol period $T_c$ and primary symbol period $T_s$.
 We also assume the direct channel and all cascaded channels can be successfully estimated and fed back to the AP.\footnote{Due to the lack of RF chains at the passive tag, accurate and efficient Channel State Information at the Transmitter (CSIT) acquisition can be challenging.
 One possible approach is that the AP sends pre-defined pilots, the tags respond in well-designed manners, and the user performs least-square estimation with feedbacks \cite{Bharadia2015,Yang2015b,Guo2019e}.} Since the tags need to physically switch the loads for backscatter modulation, they communicate at a much longer symbol period (and thus lower rates) than the primary system.
-As such, we assume all tags are perfectly synchronized and the backscatter symbol period satisfies $T_c = N T_s$ where $N \gg 1$ is a positive integer.
+As such, we assume the transitions of all tags are perfectly synchronized, and the backscatter symbol period satisfies $T_c = N T_s$ where $N \gg 1$ is a positive integer.
 
-			Without loss of generality, we focus on the transmissions during the interval of one particular backscatter symbol.
+			Without loss of generality, we focus on the transmissions and detections during the interval of one particular backscatter symbol.
 To provide a preliminary insight, we assume the primary symbol $s[n]$ at block $n \in \mathcal{N} \triangleq \{1,\ldots,N\}$ is in standard CSCG distribution, and the backscatter symbol $c_k$ of tag $k$ employs $M$-PSK modulation by \eqref{eq:mpsk}, $\forall k \in \mathcal{K}$.
-			% at primary symbol block $n \in \mathcal{N} \triangleq \{1,\ldots,N\}$, the primary symbol $s[n] \sim \mathcal{CN}(0,1)$ is assumed in standard CSCG distribution.
-On the other hand, let the backscatter symbol $c_k$ of tag $k$ employ $M$-PSK modulation by \eqref{eq:mpsk}, $\forall k \in \mathcal{K}$.
 Thus, the signal received by the user at block $n$ can be expressed as\footnote{We omit the signal reflected by two or more times and assume the time difference of arrival from different paths are negligible\cite{Wu2019,Guo2019b}.}
 			\begin{equation}
-				y[n] = \sqrt{P} \left(h^{\mathrm{D}} + \sum_{k \in \mathcal{K}} \sqrt{\alpha_k} h_k^{\mathrm{C}} c_k\right) s[n] + w[n],
+				y[n] = \left(\boldsymbol{h}_{\mathrm{D}}^H + \sum_{k \in \mathcal{K}} \sqrt{\alpha_k} \boldsymbol{h}_{\mathrm{C},k}^H c_k\right) \boldsymbol{w} s[n] + w[n],
+				\label{eq:received_signal}
 			\end{equation}
-			where $P$ is the average transmit power at the AP, and $w[n] \sim \mathcal{CN}(0,\sigma^2)$ is the Additive White Gaussian Noise (AWGN) at block $n$.
-Also, we stack the backscatter symbol of $K$ tags as $\boldsymbol{c} \triangleq [c_1,\ldots,c_K]^T$, the received signal over $N$ blocks as $\boldsymbol{y} \triangleq [y[1],\ldots,y[N]]^T$, and define the equivalent channel for primary transmission as
+			where $\boldsymbol{w} \in \mathbb{C}^{Q \times 1}$ is the active precoder satisfying $\lVert \boldsymbol{w} \rVert^2 \le P$, $P$ is the average transmit power constraint at the AP, and $w[n] \sim \mathcal{CN}(0,\sigma^2)$ is the Additive White Gaussian Noise (AWGN) at block $n$.
+Besides, we stack the backscatter symbol of $K$ tags as $\boldsymbol{c} \triangleq [c_1,\ldots,c_K]^T \in \mathbb{C}^{K \times 1}$, the received signal over $N$ blocks as $\boldsymbol{y} \triangleq [y[1],\ldots,y[N]]^T \in \mathbb{C}^{N \times 1}$, and define the equivalent channel for primary transmission as
 			\begin{equation}
-				h^{\mathrm{E}}(\boldsymbol{c}) \triangleq h^{\mathrm{D}} + \sum_{k \in \mathcal{K}} \sqrt{\alpha_k} h_k^{\mathrm{C}} c_k.
+				h_{\mathrm{E}}^H(\boldsymbol{c}) \triangleq \boldsymbol{h}_{\mathrm{D}}^H + \sum_{k \in \mathcal{K}} \sqrt{\alpha_k} \boldsymbol{h}_{\mathrm{C},k}^H c_k.
+				\label{eq:equivalent_channel}
 			\end{equation}
@@
 				The proposed symbiotic radio system is reminiscent of a Multiple Access Channel (MAC) where the AP and the tags transmit simultaneously to the user.
-It inspired all existing papers [TODO] to perform Successive Interference Cancellation (SIC) that first decode the primary message in the presence of backscatter uncertainty, then cancel its contribution and decode the backscatter messages.
-However, different from the conventional MAC with Superposition Coding (SC), the symbiotic radio system involves Multiplication Coding (MC) because the primary and secondary messages are indeed multiplied in the backscattered signals.
-Therefore, the benefits of SIC might not outstand for symbiotic radio systems.
+It inspired all existing papers [TODO] to perform Successive Interference Cancellation (SIC) that first non-coherently detects the primary message under backscatter uncertainty (requires non-coherent codes), then cancels its contribution and decodes the backscatter messages.
+However, different from the conventional MAC with Superposition Coding (SC), the symbiotic radio system involves Multiplication Coding (MC) because the primary and secondary messages are indeed combined in the received signal by multiplication.
+Also, the computational complexity of SIC can be high since it requires $K$ re-encoding, precoding, and subtraction operations.
+Therefore, novel multi-stream detection techniques should be tailored for symbiotic radio systems.
 			\end{remark}

### 2021-11-23 main.tex
:pencil: Update backscatter model

@@
 				\centering
-				\subfloat[Block diagram]{
+				\subfloat[Block diagram of a passive tag]{
 					\resizebox{0.6\columnwidth}{!}{
@@
 					}
-					\label{fi:block_diagram}
+					\label{fi:block_diagram_of_a_passive_tag}
 				}
-				\subfloat[One-port network model]{
+				\subfloat[Backscatter modualtion]{
 					\resizebox{0.35\columnwidth}{!}{
@@
 					}
-					\label{fi:one_port_network_model}
+					\label{fi:backscatter_modualtion}
 				}
-				\caption{For a passive tag, the rectifier and demodulator rely on the incident electromagnetic wave for energy harvesting and downlink information decoding, while the load-switcher manipulate the reradiated signal for backscatter modulation.}
+				\caption{For a passive tag, the rectifier and demodulator rely on the incident electromagnetic wave for energy harvesting and source decoding, while the load-switcher adjusts the reradiated signal for backscatter modulation.}
 				\label{fi:tag}
 			\end{figure}
-			Consider a bistatic backscatter system that consists of an excitation source, a dedicated reader, and a passive tag.
-The excitation source generates a carrier wave signal, the dedicated reader decodes the tag message, and the tag simultaneously harvests energy, backscatters its own message, and demodulates the downlink information if necessary.
-As shown in Fig.~\subref*{fi:block_diagram}, a typical passive tag consists of a scattering antenna, an energy harvester, a integrated receiver\footnote{For example, \cite{Kim2021a} prototyped a compact-size pulse position demodulator based on an envelope detector, which brings great potential to coordination, synchronization, and reflection pattern control.}, a load-switching modulator, and on-chip components (e.g., micro-controller, memory, and sensors).
-A portion of the impinging signal is absorbed by the tag while the remaining is backscattered to the space, as illustrated in Fig.~\subref*{fi:one_port_network_model}.
+			A bistatic backscatter system consists of an excitation source, multiple (semi-)passive tags, and a backscatter reader.
+When illuminated, the tags simultaneously harvest energy, backscatter message, and demodulate the source signal if necessary.
+Fig.~\subref*{fi:block_diagram_of_a_passive_tag} shows a typical passive with a scattering antenna, an energy harvester, an integrated receiver\footnote{For example, \cite{Kim2021a} prototyped a compact-size pulse position demodulator based on an envelope detector, which brings great potential to coordination, synchronization, and reflection pattern control.}, a load-switching modulator, and on-chip components (e.g., micro-controller, memory, and sensors).
+A portion of the impinging signal is absorbed by the tag while the remaining is backscattered to the space.
 According to Green's decomposition \cite{Hansen1989}, the backscattered signal can be decomposed into the \emph{structural mode} component and the \emph{antenna mode} component.
-The former is fixed and depends on the antenna geometry and material properties\footnote{We assume the structural mode reflection can be modeled as part of the environment multipath and covered by channel estimation \cite{Boyer2014}.}, while the latter is adjustable and depends on the mismatch of the antenna and load impedance.
-Hence, the equivalent reflection coefficient at tag state $m$ is defined as\footnote{We assume the linear backscatter model where $\Gamma_m$ is irrelevant to the incident electromagnetic field at the tag \cite{Dobkin2012}.}
+The former is fixed and depends on the antenna geometry and material properties\footnote{The structural mode component can be regarded as part of the environment multipath and modeled by channel estimation \cite{Boyer2014}.}, while the latter is adjustable and depends on the mismatch of the antenna and load impedance.
+Fig.~\subref*{fi:backscatter_modualtion} illustrates a simplified circuit and backscatter model at tag state $m$.
+The corresponding reflection coefficient is defined as\footnote{We assume the linear backscatter model where the reflection coefficient is irrelevant to the incident electromagnetic field at the tag \cite{Dobkin2012}.}
 			\begin{equation}
@@
 			where $Z_m$ is the load impedance at state $m$ and $Z_{\mathrm{A}}$ is the antenna input impedance.
-			\begin{remark}
-				The reflection coefficient plays an important role in various network designs.
-For example, $\Gamma_m = 0$ (perfect matching) achieves maximum power transfer that is optimal for Wireless Power Transfer (WPT), $\lvert \Gamma_m \rvert = 1$ (perfect mismatching) achieves fully signal reflection that is optimal for Intelligent Reflecting Surface (IRS), and $\Gamma_m \ne \Gamma_{m'}$ (adjustable matching) enables backscatter modulation.
-			\end{remark}
 		\end{subsection}
@@
 		\begin{subsection}{Backscatter Modulation}
-			Tags perform backscatter modulation by switching the load impedance between different states.
-For an $M$-ary Quadrature Amplitude Modulation (QAM) at state $m \in \mathcal{M} \triangleq \{1,\ldots,M\}$, the reflection coefficient $\Gamma_m$ maps to the desired signal constellation point $c_m$ as \cite{Thomas2012a}
+			Backscatter modulation is achieved by switching the tag load impedance between different states.
+For an $M$-ary Quadrature Amplitude Modulation (QAM) at state $m \in \mathcal{M} \triangleq \{1,\ldots,M\}$, the reflection coefficient $\Gamma_m$ maps to the signal constellation point $c_m$ as \cite{Thomas2012a}
 			\begin{equation}
@@
 			\begin{remark}
-				For passive tags, the reflection efficiency $\alpha$ controls the tradeoff between the backscatter strength and harvestable power.
-Interestingly, when $\alpha = 1$, the reflection coefficient set $\{\Gamma_m\}$ of the $M$-PSK backscatter coincides with that of an ideal discrete $M$-state uniform IRS.
-The optimal strategy for the IRS is to choose one reflection state with probability \num{1} to boost the equivalent channel, while the optimal strategy for the modulator is to utilize all constellation points with equal probability.
-It inspires one to optimize the tag input distribution to jointly benefit the backscatter modulation and passive beamforming.
+				For passive tags, the reflection efficiency $\alpha$ controls the tradeoff between the harvestable power and backscatter strength: $\alpha = 0$ corresponds to maximum power transfer to the tag, while $\alpha = 1$ with $M$-PSK corresponds to ideal Intelligent Reflecting Surface (IRS) with $M$ discrete states.
 			\end{remark}
@@
 We also assume the direct channel and all cascaded channels can be successfully estimated and fed back to the AP.\footnote{Due to the lack of RF chains at the passive tag, accurate and efficient Channel State Information at the Transmitter (CSIT) acquisition can be challenging.
-One possible approach is that the AP sends pre-defined pilots, the tags respond in well-designed manners, and the user performs least-square estimation with feedbacks \cite{Bharadia2015,Yang2015b,Guo2019e}.} Since the tags need to physically switch the loads for backscatter modulation, they communicate at a much longer symbol period (and thus lower rates) than the primary system.
+One possible approach is that the AP sends pre-defined pilots, the tags respond in well-designed manners, and the user performs least-square estimation with feedbacks \cite{Bharadia2015,Yang2015b,Guo2019e}.} Since the tags need to physically switch the loads for backscatter modulation, they communicate at a much longer symbol period (and lower rates) than the primary system.
 As such, we assume the transitions of all tags are perfectly synchronized, and the backscatter symbol period satisfies $T_c = N T_s$ where $N \gg 1$ is a positive integer.
 
-			Without loss of generality, we focus on the transmissions and detections during the interval of one particular backscatter symbol.
+			Without loss of generality, we focus on the transmissions and detections during one particular backscatter symbol period.
 To provide a preliminary insight, we assume the primary symbol $s[n]$ at block $n \in \mathcal{N} \triangleq \{1,\ldots,N\}$ is in standard CSCG distribution, and the backscatter symbol $c_k$ of tag $k$ employs $M$-PSK modulation by \eqref{eq:mpsk}, $\forall k \in \mathcal{K}$.
-Thus, the signal received by the user at block $n$ can be expressed as\footnote{We omit the signal reflected by two or more times and assume the time difference of arrival from different paths are negligible\cite{Wu2019,Guo2019b}.}
+Thus, the signal received by the user at block $n$ can be expressed as\footnote{We omit the signal reflected by two or more times\cite{Wu2019} and assume the time difference of arrival from different paths are negligible\cite{Guo2019b}.}
 			\begin{equation}
@@
 			\end{equation}
-			where $\boldsymbol{w} \in \mathbb{C}^{Q \times 1}$ is the active precoder satisfying $\lVert \boldsymbol{w} \rVert^2 \le P$, $P$ is the average transmit power constraint at the AP, and $w[n] \sim \mathcal{CN}(0,\sigma^2)$ is the Additive White Gaussian Noise (AWGN) at block $n$.
+			where $\boldsymbol{w} \in \mathbb{C}^{Q \times 1}$ is the active precoder satisfying $\lVert \boldsymbol{w} \rVert^2 \le P$, $P$ is the average transmit power constraint at the AP, and $w[n] \sim \mathcal{CN}(0,\sigma^2)$ is the equivalent Additive White Gaussian Noise (AWGN) at block $n$.
 Besides, we stack the backscatter symbol of $K$ tags as $\boldsymbol{c} \triangleq [c_1,\ldots,c_K]^T \in \mathbb{C}^{K \times 1}$, the received signal over $N$ blocks as $\boldsymbol{y} \triangleq [y[1],\ldots,y[N]]^T \in \mathbb{C}^{N \times 1}$, and define the equivalent channel for primary transmission as
@@
 			\begin{remark}
-				The proposed symbiotic radio system is reminiscent of a Multiple Access Channel (MAC) where the AP and the tags transmit simultaneously to the user.
-It inspired all existing papers [TODO] to perform Successive Interference Cancellation (SIC) that first non-coherently detects the primary message under backscatter uncertainty (requires non-coherent codes), then cancels its contribution and decodes the backscatter messages.
-However, different from the conventional MAC with Superposition Coding (SC), the symbiotic radio system involves Multiplication Coding (MC) because the primary and secondary messages are indeed combined in the received signal by multiplication.
-Also, the computational complexity of SIC can be high since it requires $K$ re-encoding, precoding, and subtraction operations.
-Therefore, novel multi-stream detection techniques should be tailored for symbiotic radio systems.
+				The proposed symbiotic radio system includes a multiplicative Multiple Access Channel (MAC) where the AP and the tags simultaneously transmit to the user.
+It inspired [TODO] to perform Successive Interference Cancellation (SIC) that first non-coherently detects the primary message under backscatter uncertainty, then cancels its contribution and decodes the tag messages.
+This scheme requires non-coherent coding at the AP and $K$ re-encoding, precoding, and subtraction operations at the user.
+However, different from the conventional MAC with Superposition Coding (SC), the symbiotic radio system involves Multiplication Coding (MC) that combines the primary and secondary messages by multiplication.
+Hence, novel multi-stream detection techniques should be tailored to symbiotic radio systems to accommodate the massive connectivity of tags and the multiplicative combination of links.
 			\end{remark}
@@
 		\begin{subsection}{Signal Detection}
-			The main difference between symbiotic radio and conventional MAC is that the primary message also reaches the user from the backscatter link.
-This characteristic inspires one to first decode the tag message, then model its contribution within the equivalent channel during primary decoding (i.e., unify backscatter decoding and channel training), instead of performing SIC.
-In such case, the reflection pattern not only embeds the tag message but also adjusts the legacy channel in a controllable manner.
-Therefore, for a fixed fading block, the primary transmission is able to achieve the ergodic capacity with artificial channel variation created by the backscatter modulation.
-[Channel over channel, randomness over randomness]
+			Based on a legacy downlink receiver, we propose a low-complexity multi-tag energy detection scheme in the presence of primary interference.
+It is achieved by extending the AmBC detection to the case of multiple sources.
+			\begin{remark}
+				One key property of symbiotic radio is the primary message propagates to the user from a known channel and multiple multiplicative channels with uncertainty introduced by backscatter modulation.
+If the backscatter symbols can be successfully decoded first, they can be modeled within the equivalent channel \eqref{eq:equivalent_channel} as channel training, instead of being removed by SIC.
+As such, the reflection coefficient simultaneously encodes the tag message and influences the equivalent channel for legacy transmission.
+			\end{remark}
 

### 2021-11-23 main.tex
:pencil: Update detection background

@@
 		\begin{subsection}{Signal Detection}
-			Based on a legacy downlink receiver, we propose a low-complexity multi-tag energy detection scheme in the presence of primary interference.
-It is achieved by extending the AmBC detection to the case of multiple sources.
+			To reveal the impact of backscatter modulation on the primary transmission, we extend the non-coherent AmBC detection scheme \cite{Qian2019} to the multi-tag case and propose a low-complexity energy detection that decodes the backscatter symbols under primary source uncertainty.
+It requires no dedicated receivers or non-coherent codes at the AP, and can be readily implemented over legacy downlink systems.
+
 			\begin{remark}
@@
 If the backscatter symbols can be successfully decoded first, they can be modeled within the equivalent channel \eqref{eq:equivalent_channel} as channel training, instead of being removed by SIC.
-As such, the reflection coefficient simultaneously encodes the tag message and influences the equivalent channel for legacy transmission.
+In other words, the reflection coefficient simultaneously encodes the tag message and influences the equivalent channel of primary link.
 			\end{remark}
 
-			To investigate how backscatter modulation potentially benefits the primary transmission, we first decode the tag symbol $c$ in presence of the interference from the primary message $\boldsymbol{s}$.
+			how backscatter modulation potentially benefits the primary transmission, we first decode the tag symbol $c$ in presence of the interference from the primary message $\boldsymbol{s}$.
 In such case, the detection indeed coincides with that of Ambient Backscatter Communications (AmBC) where the signaling from the ambient source is unknown, and the received signal per symbol block follows the CSCG distribution of $y_m[n] \sim \mathcal{CN}(0,\sigma_m^2)$, where

### 2021-11-23 main.tex
:pencil: Add naive label for backscatter symbol vector

@@
 			Backscatter modulation is achieved by switching the tag load impedance between different states.
-For an $M$-ary Quadrature Amplitude Modulation (QAM) at state $m \in \mathcal{M} \triangleq \{1,\ldots,M\}$, the reflection coefficient $\Gamma_m$ maps to the signal constellation point $c_m$ as \cite{Thomas2012a}
+For an $M$-ary Quadrature Amplitude Modulation (QAM) at state $m \in \mathcal{M} \triangleq \{1,\ldots,M\}$, the reflection coefficient $\Gamma_m$ maps to the signal constellation point $\bar{c}_m$ as \cite{Thomas2012a}
 			\begin{equation}
-				\Gamma_m = \alpha \frac{c_m}{\max_{m'} \lvert c_{m'} \rvert},
+				\Gamma_m = \alpha \frac{\bar{c}_m}{\max_{m'} \lvert \bar{c}_{m'} \rvert},
 				\label{eq:backscatter_modulation}
@@
 			where $\alpha \in [0,1]$ is the reflection efficiency at a given direction.
-For simplicity, we consider an $M$-ary Phase Shift Keying (PSK) with zero-offset (TODO), where the $m$-th constellation point is
+For simplicity, we consider an $M$-ary Phase Shift Keying (PSK) with constellation set $\mathcal{C} \triangleq \{\bar{c}_1,\ldots,\bar{c}_M\}$, where the $m$-th constellation point is
 			\begin{equation}
-				c_m = \exp \left(j \frac{2 \pi m}{M}\right).
+				\bar{c}_m = \exp \left(j \frac{2 \pi m}{M}\right).
 				\label{eq:mpsk}
 			\end{equation}
+			% Also, define the $M$-PSK constellation set as $\mathcal{C} \triangleq \{\bar{c}_1,\ldots,\bar{c}_M\}$.
+
 			\begin{remark}
@@
 			Without loss of generality, we focus on the transmissions and detections during one particular backscatter symbol period.
-To provide a preliminary insight, we assume the primary symbol $s[n]$ at block $n \in \mathcal{N} \triangleq \{1,\ldots,N\}$ is in standard CSCG distribution, and the backscatter symbol $c_k$ of tag $k$ employs $M$-PSK modulation by \eqref{eq:mpsk}, $\forall k \in \mathcal{K}$.
+To provide a preliminary insight, we assume the primary symbol $s[n]$ at block $n \in \mathcal{N} \triangleq \{1,\ldots,N\}$ is in standard CSCG distribution, and the backscatter symbol $c_k$ of tag $k$ employs $M$-PSK modulation by \eqref{eq:mpsk}, i.e., $c_k \in \mathcal{C}$, $\forall k \in \mathcal{K}$.
 Thus, the signal received by the user at block $n$ can be expressed as\footnote{We omit the signal reflected by two or more times\cite{Wu2019} and assume the time difference of arrival from different paths are negligible\cite{Guo2019b}.}
@@
 			\end{equation}
-			where $\boldsymbol{w} \in \mathbb{C}^{Q \times 1}$ is the active precoder satisfying $\lVert \boldsymbol{w} \rVert^2 \le P$, $P$ is the average transmit power constraint at the AP, and $w[n] \sim \mathcal{CN}(0,\sigma^2)$ is the equivalent Additive White Gaussian Noise (AWGN) at block $n$.
-Besides, we stack the backscatter symbol of $K$ tags as $\boldsymbol{c} \triangleq [c_1,\ldots,c_K]^T \in \mathbb{C}^{K \times 1}$, the received signal over $N$ blocks as $\boldsymbol{y} \triangleq [y[1],\ldots,y[N]]^T \in \mathbb{C}^{N \times 1}$, and define the equivalent channel for primary transmission as
+			where $\boldsymbol{w} \in \mathbb{C}^{Q \times 1}$ is the active precoder satisfying $\lVert \boldsymbol{w} \rVert^2 \le P$, $P$ is the average transmit power constraint at the AP, and $w[n] \sim \mathcal{CN}(0,\sigma_w^2)$ is the equivalent Additive White Gaussian Noise (AWGN) at block $n$.
+Besides, we stack the backscatter symbol of $K$ tags as $\boldsymbol{c} \triangleq [c_1,\ldots,c_K]^T \in \mathcal{C}^{K \times 1}$, the received signal over $N$ blocks as $\boldsymbol{y} \triangleq [y[1],\ldots,y[N]]^T \in \mathbb{C}^{N \times 1}$, and define the equivalent channel for primary transmission as
 			\begin{equation}
@@
 		\begin{subsection}{Signal Detection}
-			To reveal the impact of backscatter modulation on the primary transmission, we extend the non-coherent AmBC detection scheme \cite{Qian2019} to the multi-tag case and propose a low-complexity energy detection that decodes the backscatter symbols under primary source uncertainty.
+			To reveal the impact of backscatter modulation on the primary transmission, we extend the non-coherent Ambient Backscatter Communications (AmBC) detection \cite{Qian2019} to the multi-tag case, and propose a low-complexity energy detection to decode the backscatter symbols under primary source uncertainty.
 It requires no dedicated receivers or non-coherent codes at the AP, and can be readily implemented over legacy downlink systems.
@@
 				One key property of symbiotic radio is the primary message propagates to the user from a known channel and multiple multiplicative channels with uncertainty introduced by backscatter modulation.
-If the backscatter symbols can be successfully decoded first, they can be modeled within the equivalent channel \eqref{eq:equivalent_channel} as channel training, instead of being removed by SIC.
-In other words, the reflection coefficient simultaneously encodes the tag message and influences the equivalent channel of primary link.
+As such, each reflection coefficient simultaneously encodes the tag message and influences the equivalent channel of the primary link.
+If the backscatter symbols can be successfully decoded first, they can be modeled within the equivalent channel \eqref{eq:equivalent_channel} as in channel training, instead of being removed by SIC.
 			\end{remark}
+
+			For the ease of notation, we label the backscatter symbol vector by a decimal number that uniquely maps to the modulation index set.
+As an example, when tag $k$ is at state $m_k$, the modulation index set is $\{m_1,\ldots,m_K\}$, and the backscatter symbol vector can be defined as $\boldsymbol{c}_l \triangleq [\bar{c}_{m_1},\ldots,\bar{c}_{m_K}]^T$, where $l \in \{1,\ldots,M^K\}$ in decimal equals $m_1 - 1 \ldots m_{K-1} - 1 \ m_K$ in base-$M$.
+
+			% $\forall k \in \mathcal{K}$, the backscatter symbol vector is $\boldsymbol{c}_l$, where $l$
+
+			% assign the backscatter symbol vector to the corresponding modulation index set, and further label it by the corresponding base-$M$ number.
+
+			% we label the modulation index set $\{m_1,\ldots,m_K\}$ by the corresponding base-$M$ number
+
+			% define the modulation index set as $\{m_1,\ldots,m_K\}$
+			% For any backscatter symbol vector $\boldsymbol{c}_l$, the received signal at block $n$ is only subject to the variation of the primary symbol $s[n]$ and AWGN $w[n]$, and thus follows CSCG distribution as
+
+			% Since the status of all tags remain unchanged over $N$ primary symbols, the received signal at block $n$ is only subject to the variation of the primary symbol $s[n]$ and AWGN $w[n]$, and thus follows CSCG distribution.
+When the backscatter symbol vector is $\boldsymbol{c}_l$,
+			Since the status of all tags remain unchanged over $N$ primary symbols, the received signal is only subject to the variation of the primary source and AWGN.
+When the backscatter symbol vector is $\boldsymbol{c}_l$, the received signal at block $n$ follows CSCG distribution as
+			\begin{equation}
+				y_l[n] \sim \mathcal{CN}\biggl(0,\sigma_l^2 \triangleq \Bigl\lvert \bigl(\boldsymbol{h}_{\mathrm{D}}^H + \sum_{k \in \mathcal{K}} \sqrt{\alpha_k} \boldsymbol{h}_{\mathrm{C},k}^H \bar{c}_{m_k}\bigr) \boldsymbol{w} \Bigr\rvert^2 + \sigma_w^2\biggr).
+			\end{equation}
+
+			% , and thus follows CSCG distribution. When the backscatter symbol vector is $\boldsymbol{c}_l$,
+
+			% any backscatter symbol vector
+
+			% , and thus follows CSCG distribution as
+
+			% the received
 

### 2021-11-24 main.tex
:pencil: Update energy detection rules

@@
 			where $\boldsymbol{w} \in \mathbb{C}^{Q \times 1}$ is the active precoder satisfying $\lVert \boldsymbol{w} \rVert^2 \le P$, $P$ is the average transmit power constraint at the AP, and $w[n] \sim \mathcal{CN}(0,\sigma_w^2)$ is the equivalent Additive White Gaussian Noise (AWGN) at block $n$.
-Besides, we stack the backscatter symbol of $K$ tags as $\boldsymbol{c} \triangleq [c_1,\ldots,c_K]^T \in \mathcal{C}^{K \times 1}$, the received signal over $N$ blocks as $\boldsymbol{y} \triangleq [y[1],\ldots,y[N]]^T \in \mathbb{C}^{N \times 1}$, and define the equivalent channel for primary transmission as
+Besides, we stack the backscatter symbol of $K$ tags as $\boldsymbol{c} \triangleq [c_1,\ldots,c_K]^T \in \mathcal{C}^{K \times 1}$, the received signal over $N$ blocks as $\boldsymbol{y} \triangleq \left[y[1],\ldots,y[N]\right]^T \in \mathbb{C}^{N \times 1}$, and define the equivalent channel for primary transmission as
 			\begin{equation}
@@
 
-			For the ease of notation, we label the backscatter symbol vector by a decimal number that uniquely maps to the modulation index set.
+			To explicitly specify the content of backscatter symbol vector, we label it by the corresponding modulation index set.
+For example, when tag $k$ is at state $m_k$, $\forall k \in \mathcal{K}$, the backscatter symbol vector is defined as $\boldsymbol{c}_{\{m_k\}} \triangleq [\bar{c}_{m_1},\ldots,\bar{c}_{m_K}]^T \in \mathcal{C}^{K \times 1}$.
+Since any $\boldsymbol{c}_{\{m_k\}}$ remains constant over $N$ primary symbols, the received signal at block $n$ is only subject to the variation of the primary source $s[n]$ and AWGN $w[n]$, and thus follows CSCG distribution $y_{\{m_k\}}[n] \sim \mathcal{CN}\left(0,\sigma_{\{m_k\}}^2\right)$ with variance
+			\begin{equation}
+				\sigma_{\{m_k\}}^2 \triangleq \Bigl\lvert \bigl(\boldsymbol{h}_{\mathrm{D}}^H + \sum_{k \in \mathcal{K}} \sqrt{\alpha_k} \boldsymbol{h}_{\mathrm{C},k}^H \bar{c}_{m_k}\bigr) \boldsymbol{w} \Bigr\rvert^2 + \sigma_w^2.
+				\label{eq:receive_variance}
+			\end{equation}
+			Note that $\sigma_{\{m_k\}}^2$ denotes the expectation of the received power per primary block when tag $k$ is at state $m_k$, $\forall k \in \mathcal{K}$, which can be numerically evaluated based on the precoder, tag, channel, and noise knowledge.
+For the ease of exposition, we sort all possible $\sigma_{\{m_k\}}^2$ in ascending order by a one-to-one mapping $\{m_k\} \mapsto i$, denote the hypothesis that the backscatter symbol vector in status $i$ as $\mathcal{H}_i$, and define $\sigma_i^2 \le \sigma_j^2$ for $i < j$, $i,j \in \mathcal{M^K} \triangleq \{1,\ldots,M^K\}$.\footnote{When more than one modulation index sets yield the same energy level, the mapping is not unique and the detection fails to separate them.
+This blind spot issue can be mitigated by multi-antenna techniques.} For the optimal Maximum-Likelihood (ML) detector, the likelihood ratio between hypotheses $\mathcal{H}_i$ and $\mathcal{H}_j$ is \cite{Qian2019}
+			\begin{equation}
+				\Lambda_{i,j}(\boldsymbol{y}) = \frac{f(\boldsymbol{y} \mid \mathcal{H}_i)}{f(\boldsymbol{y} \mid \mathcal{H}_j)} = \left( \frac{\sigma_j^2}{\sigma_i^2} \right)^N \exp \left( \frac{\sigma_i^2 - \sigma_j^2}{\sigma_i^2 \sigma_j^2} z \right),
+				\label{eq:likelihood_ratio}
+			\end{equation}
+			where $f(\boldsymbol{y} \mid \mathcal{H}_i)$ and $f(\boldsymbol{y} \mid \mathcal{H}_j)$ are respectively the conditional probability density function of receiving $\boldsymbol{y}$ under hypothesis $\mathcal{H}_i$ and $\mathcal{H}_j$, and $z \triangleq \lVert \boldsymbol{y} \rVert^2$ is the received signal energy over $N$ primary blocks.
+Obviously, the likelihood ratio only depends on $z$ and the energy detection is thus optimal.
+The corresponding decision rule is
+			\begin{equation}
+				\Lambda_{i,j}(z) \underset{\mathcal{H}_j}{\overset{\mathcal{H}_i}{\lessgtr}} 1 \iff z \underset{\mathcal{H}_j}{\overset{\mathcal{H}_i}{\lessgtr}} T_{i,j},
+				\label{eq:decision_rule}
+			\end{equation}
+			where the detection threshold between $\mathcal{H}_i$ and $\mathcal{H}_j$ is
+			\begin{equation}
+				T_{i,j} \triangleq N \frac{\sigma_i^2 \sigma_j^2}{\sigma_i^2 - \sigma_j^2} \log \frac{\sigma_i^2}{\sigma_j^2}.
+				\label{eq:detection_threshold}
+			\end{equation}
+			On top of this, the decision region of hypothesis $\mathcal{H}_i$ is
+			\begin{equation}
+				\mathcal{R}_i \triangleq [T_{i-1, i}, T_{i, i+1}),
+				\label{eq:decision_region}
+			\end{equation}
+			and we manually define $T_{0,1} \triangleq 0$ and $T_{M^K,M^K+1} \triangleq \infty$.
+Let $f(z \mid \mathcal{H}_i)$ be the conditional probability density function of receiving $z$ under hypothesis $\mathcal{H}_i$.
+Since $z$ follows chi-squared distribution with $2N$ degrees of freedom, it holds that
+			\begin{equation}
+				f(z \mid \mathcal{H}_i) = \frac{z^{N-1} e^{-z/\sigma_i^2}}{\sigma_i^{2N} \Gamma(N)},
+				\label{eq:energy_distribution}
+			\end{equation}
+			% where $\Gamma(\cdot)$ is the gamma function.
+As such, the equivalent discrete memoryless channel can be defined by a transition matrix from $\mathcal{M^K}$ to $\mathcal{M^K}$,\footnote{For simplicity, we assume all possible input combinations yield distinct energy levels.} where the probability of observing output state $j$ under input state $i$ is
+			where $\Gamma(\cdot)$ is the gamma function.
+As such, the equivalent discrete memoryless channel can be defined by a transition matrix where the probability of observing output state $j \in \mathcal{M^K}$ under input state $i \in \mathcal{M^K}$ is\footnote{For simplicity, we assume all possible input combinations yield distinct energy levels.}
+			\begin{equation}
+				p(z_j \mid \boldsymbol{c}_i) = p(z \in \mathcal{R}_j \mid \mathcal{H}_i) = \int_{\mathcal{R}_j} f(z \mid \mathcal{H}_i) \dd z.
+				\label{eq:transition_probability}
+			\end{equation}
+			In summary, for every candidate backscatter symbol vector, the expected power of the received signal per block can be evaluated by \eqref{eq:receive_variance}, the energy detection threshold to the nearby states can be computed by \eqref{eq:detection_threshold}, the decision region can be retrieved by \eqref{eq:decision_region}, and the channel transition matrix can be obtained by \eqref{eq:energy_distribution} and \eqref{eq:transition_probability}.
+
+			% the expected power of the received signal per block under all backscatter combinations can be estimated by \eqref{eq:receive_variance}, the energy detection threshold between any backscatter symbol vectors with adjacent
+
+			% can be computed by \eqref{eq:detection_threshold}, the decision region can be retrieved by \eqref{eq:decision_region}, and the forward transition matrix $\boldsymbol{P}$ can be calculated by substituting \eqref{eq:conditional_pdf} into \eqref{eq:transition_probability}.
+
+			% estimated at the user.
+
+			% To enable energy detection
+
+			% For the ease of notation, we label the backscatter symbol vector by a decimal number that uniquely maps to the modulation index set.
 As an example, when tag $k$ is at state $m_k$, the modulation index set is $\{m_1,\ldots,m_K\}$, and the backscatter symbol vector can be defined as $\boldsymbol{c}_l \triangleq [\bar{c}_{m_1},\ldots,\bar{c}_{m_K}]^T$, where $l \in \{1,\ldots,M^K\}$ in decimal equals $m_1 - 1 \ldots m_{K-1} - 1 \ m_K$ in base-$M$.
@@
 When the backscatter symbol vector is $\boldsymbol{c}_l$,
-			Since the status of all tags remain unchanged over $N$ primary symbols, the received signal is only subject to the variation of the primary source and AWGN.
+			% Since the status of all tags remain unchanged over $N$ primary symbols, the received signal is only subject to the variation of the primary source and AWGN.
 When the backscatter symbol vector is $\boldsymbol{c}_l$, the received signal at block $n$ follows CSCG distribution as
-			\begin{equation}
-				y_l[n] \sim \mathcal{CN}\biggl(0,\sigma_l^2 \triangleq \Bigl\lvert \bigl(\boldsymbol{h}_{\mathrm{D}}^H + \sum_{k \in \mathcal{K}} \sqrt{\alpha_k} \boldsymbol{h}_{\mathrm{C},k}^H \bar{c}_{m_k}\bigr) \boldsymbol{w} \Bigr\rvert^2 + \sigma_w^2\biggr).
-			\end{equation}
+			% \begin{equation}
+			% 	y_l[n] \sim \mathcal{CN}\biggl(0,\sigma_l^2 \triangleq \Bigl\lvert \bigl(\boldsymbol{h}_{\mathrm{D}}^H + \sum_{k \in \mathcal{K}} \sqrt{\alpha_k} \boldsymbol{h}_{\mathrm{C},k}^H \bar{c}_{m_k}\bigr) \boldsymbol{w} \Bigr\rvert^2 + \sigma_w^2\biggr).
+			% \end{equation}
 
@@
 			\begin{equation}
-				\Lambda_{i, j}(\boldsymbol{y}) = \frac{f(\boldsymbol{y} \mid \mathcal{H}_i)}{f(\boldsymbol{y} \mid \mathcal{H}_j)} = \left( \frac{\sigma_j^2}{\sigma_i^2} \right)^N \exp \left( \frac{(\sigma_i^2 - \sigma_j^2) z}{\sigma_i^2 \sigma_j^2} \right),
+				\Lambda_{i,j}(\boldsymbol{y}) = \frac{f(\boldsymbol{y} \mid \mathcal{H}_i)}{f(\boldsymbol{y} \mid \mathcal{H}_j)} = \left( \frac{\sigma_j^2}{\sigma_i^2} \right)^N \exp \left( \frac{(\sigma_i^2 - \sigma_j^2) z}{\sigma_i^2 \sigma_j^2} \right),
 			\end{equation}
@@
 			\begin{equation}
-				\Lambda_{i, j}(\boldsymbol{y}) \underset{H_j}{\overset{H_i}{\lessgtr}} 1 \iff z \underset{H_j}{\overset{H_i}{\lessgtr}} T_{i, j},
+				\Lambda_{i,j}(\boldsymbol{y}) \underset{H_j}{\overset{H_i}{\lessgtr}} 1 \iff z \underset{H_j}{\overset{H_i}{\lessgtr}} T_{i,j},
 			\end{equation}
@@
 			\begin{equation}
-				T_{i, j} \triangleq N \frac{\sigma_i^2 \sigma_j^2}{\sigma_i^2 - \sigma_j^2} \log \frac{\sigma_i^2}{\sigma_j^2},
+				T_{i,j} \triangleq N \frac{\sigma_i^2 \sigma_j^2}{\sigma_i^2 - \sigma_j^2} \log \frac{\sigma_i^2}{\sigma_j^2},
 				\label{eq:detection_threshold}
@@
 			\end{equation}
-			where $p_{i, j}$ denotes the transition probability from channel input state $i$ to output state $j$. It can be derived as
+			where $p_{i,j}$ denotes the transition probability from channel input state $i$ to output state $j$. It can be derived as
 			\begin{equation}
-				p_{i, j} = p(z \in \mathcal{R}_j \mid \mathcal{H}_i) = \int_{\mathcal{R}_j} f(z \mid \mathcal{H}_i) \dd z,
+				p_{i,j} = p(z \in \mathcal{R}_j \mid \mathcal{H}_i) = \int_{\mathcal{R}_j} f(z \mid \mathcal{H}_i) \dd z,
 				\label{eq:transition_probability}
@@
 			\begin{equation}
-				R_c = \max_{\boldsymbol{Q} \ge 0} \sum_{i \in \mathcal{M}} \sum_{j \in \mathcal{M}} r_i p_{i, j} \log_2 \frac{q_{j, i}}{r_i} \ [\si{bpcu}],
+				R_c = \max_{\boldsymbol{Q} \ge 0} \sum_{i \in \mathcal{M}} \sum_{j \in \mathcal{M}} r_i p_{i,j} \log_2 \frac{q_{j, i}}{r_i} \ [\si{bpcu}],
 				\label{eq:secondary_rate}
@@
 				{\scriptstyle{\boldsymbol{r} \ge 0, \boldsymbol{Q} \ge 0}}{\rho \sum_{i \in \mathcal{M}} r_i \log_2 \bigl( 1 + \gamma \lvert h_{\mathrm{D}} + \sqrt{\alpha} h_{\mathrm{C}} c_i \rvert^2 \bigr) \nonumber}{}{}
-				\breakObjective{+ (1 - \rho) \sum_{i \in \mathcal{M}} \sum_{j \in \mathcal{M}} r_i p_{i, j} \log_2 \frac{q_{j, i}}{r_i}}{\label{ob:weighted_sum_rate_expanded}}
+				\breakObjective{+ (1 - \rho) \sum_{i \in \mathcal{M}} \sum_{j \in \mathcal{M}} r_i p_{i,j} \log_2 \frac{q_{j, i}}{r_i}}{\label{ob:weighted_sum_rate_expanded}}
 				\addConstraint{\sum_{i \in \mathcal{M}} r_i}{=1.}{}
@@
 				\begin{equation}
-					q_{j, i}^{\star} = \frac{r_i p_{i, j}}{\sum_{i'} r_{i'} p_{i', j}}.
+					q_{j, i}^{\star} = \frac{r_i p_{i,j}}{\sum_{i'} r_{i'} p_{i', j}}.
 					\label{eq:backward_transition}
@@
 				\begin{equation}
-					r_i = \frac{\bigl( 1 + \gamma \lvert h_{\mathrm{D}} + \sqrt{\alpha} h_{\mathrm{C}} c_i \rvert^2 \bigr)^{\rho / (1 - \rho)} \prod_{j \in \mathcal{M}} q_{j, i}^{p_{i, j}}}{\sum_{i' \in \mathcal{M}} \bigl( 1 + \gamma \lvert h_{\mathrm{D}} + \sqrt{\alpha} h_{\mathrm{C}} c_{i'} \rvert^2 \bigr)^{\rho / (1 - \rho)} \prod_{j \in \mathcal{M}} q_{j, i'}^{p_{i', j}}}.
+					r_i = \frac{\bigl( 1 + \gamma \lvert h_{\mathrm{D}} + \sqrt{\alpha} h_{\mathrm{C}} c_i \rvert^2 \bigr)^{\rho / (1 - \rho)} \prod_{j \in \mathcal{M}} q_{j, i}^{p_{i,j}}}{\sum_{i' \in \mathcal{M}} \bigl( 1 + \gamma \lvert h_{\mathrm{D}} + \sqrt{\alpha} h_{\mathrm{C}} c_{i'} \rvert^2 \bigr)^{\rho / (1 - \rho)} \prod_{j \in \mathcal{M}} q_{j, i'}^{p_{i', j}}}.
 					\label{eq:input_distribution}
@@
 			\begin{equation}
-				w_j q_{j, i}^{\star} = r_i p_{i, j}.
+				w_j q_{j, i}^{\star} = r_i p_{i,j}.
 			\end{equation}
@@
 				R(\boldsymbol{r}, \boldsymbol{Q}^{\star}) - R(\boldsymbol{r}, \boldsymbol{Q})
-				& = (1 - \rho) \sum_{i \in \mathcal{M}} \sum_{j \in \mathcal{M}} r_i p_{i, j} \log_2 \frac{q_{j, i}^{\star}}{q_{j, i}} \nonumber \\
+				& = (1 - \rho) \sum_{i \in \mathcal{M}} \sum_{j \in \mathcal{M}} r_i p_{i,j} \log_2 \frac{q_{j, i}^{\star}}{q_{j, i}} \nonumber \\
 				& = (1 - \rho) \sum_{i \in \mathcal{M}} \sum_{j \in \mathcal{M}} w_j q_{j, i}^{\star} \log_2 \frac{q_{j, i}^{\star}}{q_{j, i}} \nonumber \\
@@
 				& = \rho \sum_{i \in \mathcal{M}} r_i \log \bigl( 1 + \gamma \lvert h_{\mathrm{D}} + \sqrt{\alpha} h_{\mathrm{C}} c_i \rvert^2 \bigr) \nonumber \\
-				& \quad + (1 - \rho) \sum_{i \in \mathcal{M}} \sum_{j \in \mathcal{M}} r_i p_{i, j} \log \frac{q_{j, i}}{r_i} + \lambda \left( 1 - \sum_{i \in \mathcal{M}} r_i \right),
+				& \quad + (1 - \rho) \sum_{i \in \mathcal{M}} \sum_{j \in \mathcal{M}} r_i p_{i,j} \log \frac{q_{j, i}}{r_i} + \lambda \left( 1 - \sum_{i \in \mathcal{M}} r_i \right),
 			\end{align}
@@
 				& = \rho \log \bigl( 1 + \gamma \lvert h_{\mathrm{D}} + \sqrt{\alpha} h_{\mathrm{C}} c_i \rvert^2 \bigr) \\
-				& \quad + (1 - \rho) \left( \sum_{j \in \mathcal{M}} p_{i, j} \log q_{j, i} - \log r_i - 1 \right),
+				& \quad + (1 - \rho) \left( \sum_{j \in \mathcal{M}} p_{i,j} \log q_{j, i} - \log r_i - 1 \right),
 			\end{align}
@@
 			\begin{equation}
-				r_i = e^{ -(\frac{\lambda}{1 - \rho} + 1)} \bigl( 1 + \gamma \lvert h_{\mathrm{D}} + \sqrt{\alpha} h_{\mathrm{C}} c_i \rvert^2 \bigr)^{\rho / (1 - \rho)} \prod_{j \in \mathcal{M}} q_{j, i}^{p_{i, j}}.
+				r_i = e^{ -(\frac{\lambda}{1 - \rho} + 1)} \bigl( 1 + \gamma \lvert h_{\mathrm{D}} + \sqrt{\alpha} h_{\mathrm{C}} c_i \rvert^2 \bigr)^{\rho / (1 - \rho)} \prod_{j \in \mathcal{M}} q_{j, i}^{p_{i,j}}.
 			\end{equation}

### 2021-11-24 main.tex
:pencil: Summarize energy detection

@@
 			\end{equation}
-			% Also, define the $M$-PSK constellation set as $\mathcal{C} \triangleq \{\bar{c}_1,\ldots,\bar{c}_M\}$.
 
@@
 
-		\begin{subsection}{Signal Detection}
+		\begin{subsection}{Backscatter Detection}
 			To reveal the impact of backscatter modulation on the primary transmission, we extend the non-coherent Ambient Backscatter Communications (AmBC) detection \cite{Qian2019} to the multi-tag case, and propose a low-complexity energy detection to decode the backscatter symbols under primary source uncertainty.
@@
 			\end{equation}
-			% where $\Gamma(\cdot)$ is the gamma function.
-As such, the equivalent discrete memoryless channel can be defined by a transition matrix from $\mathcal{M^K}$ to $\mathcal{M^K}$,\footnote{For simplicity, we assume all possible input combinations yield distinct energy levels.} where the probability of observing output state $j$ under input state $i$ is
 			where $\Gamma(\cdot)$ is the gamma function.
-As such, the equivalent discrete memoryless channel can be defined by a transition matrix where the probability of observing output state $j \in \mathcal{M^K}$ under input state $i \in \mathcal{M^K}$ is\footnote{For simplicity, we assume all possible input combinations yield distinct energy levels.}
+As such, the equivalent discrete memoryless channel can be defined by a transition matrix where the probability of observing output $j \in \mathcal{M^K}$ under input $i \in \mathcal{M^K}$ is\footnote{For simplicity, we assume all possible input combinations yield distinct energy levels.}
 			\begin{equation}
@@
 			\end{equation}
-			In summary, for every candidate backscatter symbol vector, the expected power of the received signal per block can be evaluated by \eqref{eq:receive_variance}, the energy detection threshold to the nearby states can be computed by \eqref{eq:detection_threshold}, the decision region can be retrieved by \eqref{eq:decision_region}, and the channel transition matrix can be obtained by \eqref{eq:energy_distribution} and \eqref{eq:transition_probability}.
-
-			% the expected power of the received signal per block under all backscatter combinations can be estimated by \eqref{eq:receive_variance}, the energy detection threshold between any backscatter symbol vectors with adjacent
-
-			% can be computed by \eqref{eq:detection_threshold}, the decision region can be retrieved by \eqref{eq:decision_region}, and the forward transition matrix $\boldsymbol{P}$ can be calculated by substituting \eqref{eq:conditional_pdf} into \eqref{eq:transition_probability}.
-
-			% estimated at the user.
-
-			% To enable energy detection
-
-			% For the ease of notation, we label the backscatter symbol vector by a decimal number that uniquely maps to the modulation index set.
-As an example, when tag $k$ is at state $m_k$, the modulation index set is $\{m_1,\ldots,m_K\}$, and the backscatter symbol vector can be defined as $\boldsymbol{c}_l \triangleq [\bar{c}_{m_1},\ldots,\bar{c}_{m_K}]^T$, where $l \in \{1,\ldots,M^K\}$ in decimal equals $m_1 - 1 \ldots m_{K-1} - 1 \ m_K$ in base-$M$.
-
-			% $\forall k \in \mathcal{K}$, the backscatter symbol vector is $\boldsymbol{c}_l$, where $l$
-
-			% assign the backscatter symbol vector to the corresponding modulation index set, and further label it by the corresponding base-$M$ number.
-
-			% we label the modulation index set $\{m_1,\ldots,m_K\}$ by the corresponding base-$M$ number
-
-			% define the modulation index set as $\{m_1,\ldots,m_K\}$
-			% For any backscatter symbol vector $\boldsymbol{c}_l$, the received signal at block $n$ is only subject to the variation of the primary symbol $s[n]$ and AWGN $w[n]$, and thus follows CSCG distribution as
-
-			% Since the status of all tags remain unchanged over $N$ primary symbols, the received signal at block $n$ is only subject to the variation of the primary symbol $s[n]$ and AWGN $w[n]$, and thus follows CSCG distribution.
-When the backscatter symbol vector is $\boldsymbol{c}_l$,
-			% Since the status of all tags remain unchanged over $N$ primary symbols, the received signal is only subject to the variation of the primary source and AWGN.
-When the backscatter symbol vector is $\boldsymbol{c}_l$, the received signal at block $n$ follows CSCG distribution as
-			% \begin{equation}
-			% 	y_l[n] \sim \mathcal{CN}\biggl(0,\sigma_l^2 \triangleq \Bigl\lvert \bigl(\boldsymbol{h}_{\mathrm{D}}^H + \sum_{k \in \mathcal{K}} \sqrt{\alpha_k} \boldsymbol{h}_{\mathrm{C},k}^H \bar{c}_{m_k}\bigr) \boldsymbol{w} \Bigr\rvert^2 + \sigma_w^2\biggr).
-			% \end{equation}
-
-			% , and thus follows CSCG distribution. When the backscatter symbol vector is $\boldsymbol{c}_l$,
-
-			% any backscatter symbol vector
-
-			% , and thus follows CSCG distribution as
-
-			% the received
-
-			how backscatter modulation potentially benefits the primary transmission, we first decode the tag symbol $c$ in presence of the interference from the primary message $\boldsymbol{s}$.
-In such case, the detection indeed coincides with that of Ambient Backscatter Communications (AmBC) where the signaling from the ambient source is unknown, and the received signal per symbol block follows the CSCG distribution of $y_m[n] \sim \mathcal{CN}(0,\sigma_m^2)$, where
-			\begin{equation}
-				\sigma_m^2 \triangleq \lvert h_{\mathrm{D}} + \sqrt{\alpha} h_{\mathrm{C}} c_m \rvert^2 P + \sigma^2
-				\label{eq:typical_energy}
-			\end{equation}
-			denotes the typical received signal energy over $N$ symbol blocks when the tag is at state $m$, which can be estimated at the user.
-For the ease of exposition, we sort $\{\sigma_m^2\}$ in a ascending order by bijective mapping $f \colon m \mapsto i$\footnote{Note that the mapping is not unique and the detection fails when two different constellation points yield the same energy level.} and let $\sigma_i^2 \le \sigma_j^2$ for $i < j$, $i,j \in \mathcal{M}$.
-Denote $\mathcal{H}_i$ as the hypothesis that the tag transmits $c_i$.
-Following \cite{Qian2019}, the optimal Maximum-Likelihood (ML) detector boils down to the energy detector, and the likelihood ratio between hypotheses $\mathcal{H}_i$ and $\mathcal{H}_j$ is
-			\begin{equation}
-				\Lambda_{i,j}(\boldsymbol{y}) = \frac{f(\boldsymbol{y} \mid \mathcal{H}_i)}{f(\boldsymbol{y} \mid \mathcal{H}_j)} = \left( \frac{\sigma_j^2}{\sigma_i^2} \right)^N \exp \left( \frac{(\sigma_i^2 - \sigma_j^2) z}{\sigma_i^2 \sigma_j^2} \right),
-			\end{equation}
-			where $f(\boldsymbol{y} \mid \mathcal{H}_i)$, $f(\boldsymbol{y} \mid \mathcal{H}_j)$ denote respectively the conditional probability density function of receiving $\boldsymbol{y}$ under hypothesis $\mathcal{H}_i$ and $\mathcal{H}_j$, and $z \triangleq \lVert y \rVert^2$ is the received signal energy over $N$ symbol blocks.
-The corresponding decision rule is
-			\begin{equation}
-				\Lambda_{i,j}(\boldsymbol{y}) \underset{H_j}{\overset{H_i}{\lessgtr}} 1 \iff z \underset{H_j}{\overset{H_i}{\lessgtr}} T_{i,j},
-			\end{equation}
-			where the optimal detection threshold is
-			\begin{equation}
-				T_{i,j} \triangleq N \frac{\sigma_i^2 \sigma_j^2}{\sigma_i^2 - \sigma_j^2} \log \frac{\sigma_i^2}{\sigma_j^2},
-				\label{eq:detection_threshold}
-			\end{equation}
-			and the decision region of hypothesis $\mathcal{H}_i$ can be expressed as
-			\begin{equation}
-				\mathcal{R}_i \triangleq [T_{i-1, i}, T_{i, i+1}),
-				\label{eq:decision_region}
-			\end{equation}
-			with $T_{0, 1} \triangleq 0$ and $T_{M, M+1} \triangleq \infty$. On top of this, we define the forward transition probability matrix $\boldsymbol{P} \in \mathbb{R}_{+}^{M \times M}$ as
-			\begin{equation}
-				\boldsymbol{P} \triangleq
-				\begin{bmatrix}
-					p_{1, 1} & \ldots & p_{1, M} \\
-					\vdots & \ddots & \vdots \\
-					p_{M, 1} & \ldots & p_{M, M}
-				\end{bmatrix},
-			\end{equation}
-			where $p_{i,j}$ denotes the transition probability from channel input state $i$ to output state $j$. It can be derived as
-			\begin{equation}
-				p_{i,j} = p(z \in \mathcal{R}_j \mid \mathcal{H}_i) = \int_{\mathcal{R}_j} f(z \mid \mathcal{H}_i) \dd z,
-				\label{eq:transition_probability}
-			\end{equation}
-			where $f(z \mid \mathcal{H}_i)$ is the conditional probability density function of receiving $z$ under hypothesis $\mathcal{H}_i$.
-Since $z$ follows chi-squared distribution with $2N$ degrees of freedom, it holds that
-			\begin{equation}
-				f(z \mid \mathcal{H}_i) = \frac{z^{N-1} e^{-z/\sigma_i^2}}{\sigma_i^{2N} \Gamma(N)},
-				\label{eq:conditional_pdf}
-			\end{equation}
-			where $\Gamma(\cdot)$ is the gamma function.
-To summarize, with the CSI of the direct and cascaded links, the typical energy of the received signal can be estimated by \eqref{eq:typical_energy}, the energy detection threshold can be computed by \eqref{eq:detection_threshold}, the decision region can be retrieved by \eqref{eq:decision_region}, and the forward transition matrix $\boldsymbol{P}$ can be calculated by substituting \eqref{eq:conditional_pdf} into \eqref{eq:transition_probability}.
+			In summary, for every candidate backscatter symbol vector, the expected power of the received signal per block can be evaluated by \eqref{eq:receive_variance}, the energy detection threshold to nearby states can be computed by \eqref{eq:detection_threshold}, the decision region can be retrieved by \eqref{eq:decision_region}, and the channel transition matrix can be obtained by \eqref{eq:energy_distribution} and \eqref{eq:transition_probability}.
 

### 2021-11-25 main.tex
:dizzy: MAC channel by marginal distributions

@@
 			\end{equation}
-			On top of this, the decision region of hypothesis $\mathcal{H}_i$ is
+			Accordingly, the decision region of hypothesis $\mathcal{H}_i$ is
 			\begin{equation}
@@
 			where $\Gamma(\cdot)$ is the gamma function.
-As such, the equivalent discrete memoryless channel can be defined by a transition matrix where the probability of observing output $j \in \mathcal{M^K}$ under input $i \in \mathcal{M^K}$ is\footnote{For simplicity, we assume all possible input combinations yield distinct energy levels.}
+Hence, the equivalent point-to-point discrete memoryless channel from tag input combination alphabet $\mathcal{M^K}$ to received energy level alphabet $\mathcal{M^K}$ can be defined by a transition matrix, where the probability of observing energy level $j$ under tag input combination $i$ is\footnote{For simplicity, we assume there exists at least one feasible precoder that produces distinct received energy levels for all tag input combinations.
+[TODO] Is this necessary?
+Maybe we can keep those same energy levels and avoid them by input distribution design.}
 			\begin{equation}
 				p(z_j \mid \boldsymbol{c}_i) = p(z \in \mathcal{R}_j \mid \mathcal{H}_i) = \int_{\mathcal{R}_j} f(z \mid \mathcal{H}_i) \dd z.
-				\label{eq:transition_probability}
+				\label{eq:equivalent_channel}
 			\end{equation}
+			Based on the equivalent point-to-point channel \eqref{eq:equivalent_channel}, we can compute the marginal on all tags and obtain $K$ transition matrices from $\mathcal{M}$ to $\mathcal{M^K}$ that compose a discrete memoryless MAC.
+[ADD EQUATION HERE]
+
+			Mathematically speaking,
+			\begin{equation}
+				p(z_j \mid c_{m_k}) = \sum_{i_1,\ldots,i_{k-1},i_{k+1},\ldots,i_K} p(z_j \mid \boldsymbol{c}_{i \setminus k}, c_{m_k}) / \sum_{i_1,\ldots,i_K} p(z_j \mid \boldsymbol{c}_i)
+			\end{equation}
+
 			In summary, for every candidate backscatter symbol vector, the expected power of the received signal per block can be evaluated by \eqref{eq:receive_variance}, the energy detection threshold to nearby states can be computed by \eqref{eq:detection_threshold}, the decision region can be retrieved by \eqref{eq:decision_region}, and the channel transition matrix can be obtained by \eqref{eq:energy_distribution} and \eqref{eq:transition_probability}.

### 2021-11-26 main.tex
:pencil: Extract discrete memoryless MAC from equivalent point-to-point channel

--- 2021-11-24 main.tex
@@
 			To explicitly specify the content of backscatter symbol vector, we label it by the corresponding modulation index set.
-For example, when tag $k$ is at state $m_k$, $\forall k \in \mathcal{K}$, the backscatter symbol vector is defined as $\boldsymbol{c}_{\{m_k\}} \triangleq [\bar{c}_{m_1},\ldots,\bar{c}_{m_K}]^T \in \mathcal{C}^{K \times 1}$.
-Since any $\boldsymbol{c}_{\{m_k\}}$ remains constant over $N$ primary symbols, the received signal at block $n$ is only subject to the variation of the primary source $s[n]$ and AWGN $w[n]$, and thus follows CSCG distribution $y_{\{m_k\}}[n] \sim \mathcal{CN}\left(0,\sigma_{\{m_k\}}^2\right)$ with variance
+For tag $k$ at state $m_k$, $\forall k \in \mathcal{K}$, we define the modulation index set as $m_{\mathcal{K}} \triangleq \{m_k \colon k \in \mathcal{K}\}$ and the backscatter symbol vector as $\bar{\boldsymbol{c}}_{m_{\mathcal{K}}} \triangleq [\bar{c}_{m_1},\ldots,\bar{c}_{m_K}]^T \in \mathcal{C}^{K \times 1}$.
+Since any $\bar{\boldsymbol{c}}_{m_{\mathcal{K}}}$ remains constant per $N$ primary symbols, the received signal at block $n$ is only subject to the variation of the primary source $s[n]$ and AWGN $w[n]$, and thus follows CSCG distribution $y_{m_{\mathcal{K}}}[n] \sim \mathcal{CN}\left(0,\sigma_{m_{\mathcal{K}}}^2\right)$ with variance
 			\begin{equation}
-				\sigma_{\{m_k\}}^2 \triangleq \Bigl\lvert \bigl(\boldsymbol{h}_{\mathrm{D}}^H + \sum_{k \in \mathcal{K}} \sqrt{\alpha_k} \boldsymbol{h}_{\mathrm{C},k}^H \bar{c}_{m_k}\bigr) \boldsymbol{w} \Bigr\rvert^2 + \sigma_w^2.
+				\sigma_{m_{\mathcal{K}}}^2 \triangleq \Bigl\lvert \bigl(\boldsymbol{h}_{\mathrm{D}}^H + \sum_{k \in \mathcal{K}} \sqrt{\alpha_k} \boldsymbol{h}_{\mathrm{C},k}^H \bar{c}_{m_k}\bigr) \boldsymbol{w} \Bigr\rvert^2 + \sigma_w^2,
 				\label{eq:receive_variance}
 			\end{equation}
-			Note that $\sigma_{\{m_k\}}^2$ denotes the expectation of the received power per primary block when tag $k$ is at state $m_k$, $\forall k \in \mathcal{K}$, which can be numerically evaluated based on the precoder, tag, channel, and noise knowledge.
-For the ease of exposition, we sort all possible $\sigma_{\{m_k\}}^2$ in ascending order by a one-to-one mapping $\{m_k\} \mapsto i$, denote the hypothesis that the backscatter symbol vector in status $i$ as $\mathcal{H}_i$, and define $\sigma_i^2 \le \sigma_j^2$ for $i < j$, $i,j \in \mathcal{M^K} \triangleq \{1,\ldots,M^K\}$.\footnote{When more than one modulation index sets yield the same energy level, the mapping is not unique and the detection fails to separate them.
+			which denotes the expectation of the received power per primary block under tag modulation index set $\boldsymbol{m}$, and can be numerically evaluated based on the precoder, tag, channel, and noise knowledge.
+For the ease of exposition, we sort all possible $\sigma_{m_{\mathcal{K}}}^2$ in ascending order by a one-to-one mapping $\boldsymbol{m} \mapsto i$, denote the hypothesis that the backscatter symbol vector in status $i$ as $\mathcal{H}_i$, and define $\sigma_i^2 \le \sigma_j^2$ for $i < j$, $i,j \in \mathcal{M^K} \triangleq \{1,\ldots,M^K\}$.\footnote{When more than one modulation index sets yield the same energy level, the mapping is not unique and the detection fails to separate them.
 This blind spot issue can be mitigated by multi-antenna techniques.} For the optimal Maximum-Likelihood (ML) detector, the likelihood ratio between hypotheses $\mathcal{H}_i$ and $\mathcal{H}_j$ is \cite{Qian2019}
@@
 			\end{equation}
-			On top of this, the decision region of hypothesis $\mathcal{H}_i$ is
+
+			Accordingly, the decision region of hypothesis $\mathcal{H}_i$ is
 			\begin{equation}
@@
 			where $\Gamma(\cdot)$ is the gamma function.
-As such, the equivalent discrete memoryless channel can be defined by a transition matrix where the probability of observing output $j \in \mathcal{M^K}$ under input $i \in \mathcal{M^K}$ is\footnote{For simplicity, we assume all possible input combinations yield distinct energy levels.}
+As such, we can formulate an equivalent point-to-point discrete memoryless channel from tag input combination alphabet $\mathcal{M^K}$ to received energy level alphabet $\mathcal{M^K}$ as a transition matrix, where the probability of observing energy level $j$ under tag input combination $i$ is\footnote{For simplicity, we assume there exists at least one feasible precoder that produces distinct received energy levels for all tag input combinations.
+[TODO] Is this necessary?
+Maybe we can keep those same energy levels and avoid them by input distribution design.}
 			\begin{equation}
-				p(z_j \mid \boldsymbol{c}_i) = p(z \in \mathcal{R}_j \mid \mathcal{H}_i) = \int_{\mathcal{R}_j} f(z \mid \mathcal{H}_i) \dd z.
-				\label{eq:transition_probability}
+				p(z_j \mid \bar{\boldsymbol{c}}_i) = p(z \in \mathcal{R}_j \mid \mathcal{H}_i) = \int_{\mathcal{R}_j} f(z \mid \mathcal{H}_i) \dd z.
+				\label{eq:equivalent_channel}
 			\end{equation}
-			In summary, for every candidate backscatter symbol vector, the expected power of the received signal per block can be evaluated by \eqref{eq:receive_variance}, the energy detection threshold to nearby states can be computed by \eqref{eq:detection_threshold}, the decision region can be retrieved by \eqref{eq:decision_region}, and the channel transition matrix can be obtained by \eqref{eq:energy_distribution} and \eqref{eq:transition_probability}.
 
-			We then investigate the achievable rate of the backscatter link.
-Denote the tag input probability mass function as $\boldsymbol{r} = [r_1,\ldots,r_M]^T \in \mathbb{R}_+^{M \times 1}$ where $r_m$ is the probability to transmit symbol $c_m$ [strictly positive?].
-For a given input distribution $\boldsymbol{r}$ and forward transition matrix $\boldsymbol{P}$, the achievable backscatter rate can be written as
+			Based on the equivalent point-to-point channel \eqref{eq:equivalent_channel}, we can compute the marginal probability on all tags and obtain $K$ transition matrices from $\mathcal{M}$ to $\mathcal{M^K}$ that compose a discrete memoryless MAC.
+Mathematically speaking, the probability of observing energy level $j$ when tag $k$ at status $m_k$ is
 			\begin{equation}
-				R_c = \max_{\boldsymbol{Q} \ge 0} \sum_{i \in \mathcal{M}} \sum_{j \in \mathcal{M}} r_i p_{i,j} \log_2 \frac{q_{j, i}}{r_i} \ [\si{bpcu}],
-				\label{eq:secondary_rate}
+				p(z_j \mid c_k = \bar{c}_{m_k}) = \frac{\sum_{m_{\mathcal{K} \setminus k}} p(z_j \mid \bar{\boldsymbol{c}}_{m_{\mathcal{K}}})}{\sum_{m_{\mathcal{K}}} p(z_j \mid \bar{\boldsymbol{c}}_{m_{\mathcal{K}}})}.
+				\label{eq:mac}
 			\end{equation}
-			where $\boldsymbol{Q} \in \mathbb{R}_{+}^{M \times M}$ is the backward transition probability matrix
-			\begin{equation}
-				\boldsymbol{Q} \triangleq
-				\begin{bmatrix}
-					q_{1, 1} & \ldots & q_{1, M} \\
-					\vdots & \ddots & \vdots \\
-					q_{M, 1} & \ldots & q_{M, M}
-				\end{bmatrix},
-			\end{equation}
-			and $q_{j, i}$ denotes the transition probability from channel output state $j$ to input state $i$.
+
+			In summary, for every possible tag input combination, the expected power of the received signal per block can be evaluated by \eqref{eq:receive_variance}, the energy detection threshold to nearby states can be computed by \eqref{eq:detection_threshold}, the decision region can be retrieved by \eqref{eq:decision_region}, the equivalent point-to-point channel can be obtained by \eqref{eq:energy_distribution} and \eqref{eq:equivalent_channel}, and the discrete memoryless MAC can be extracted by \eqref{eq:mac}.
 		\end{subsection}
+	\end{section}
+
+	\begin{section}{Precoder and Tag Input Design}
+		TODO
 	\end{section}

### 2021-11-26 main.tex
:dizzy: Information functions

@@
 We also assume the direct channel and all cascaded channels can be successfully estimated and fed back to the AP.\footnote{Due to the lack of RF chains at the passive tag, accurate and efficient Channel State Information at the Transmitter (CSIT) acquisition can be challenging.
-One possible approach is that the AP sends pre-defined pilots, the tags respond in well-designed manners, and the user performs least-square estimation with feedbacks \cite{Bharadia2015,Yang2015b,Guo2019e}.} Since the tags need to physically switch the loads for backscatter modulation, they communicate at a much longer symbol period (and lower rates) than the primary system.
+One possible approach is that the AP sends pre-defined pilots, the tags respond in well-designed manners, and the user performs least-square estimation with feedbacks \cite{Bharadia2015,Yang2015b,Guo2019g}.} Since the tags need to physically switch the loads for backscatter modulation, they communicate at a much longer symbol period (and lower rates) than the primary system.
 As such, we assume the transitions of all tags are perfectly synchronized, and the backscatter symbol period satisfies $T_c = N T_s$ where $N \gg 1$ is a positive integer.
@@
 
-			To explicitly specify the content of backscatter symbol vector, we label it by the corresponding modulation index set.
-For tag $k$ at state $m_k$, $\forall k \in \mathcal{K}$, we define the modulation index set as $m_{\mathcal{K}} \triangleq \{m_k \colon k \in \mathcal{K}\}$ and the backscatter symbol vector as $\bar{\boldsymbol{c}}_{m_{\mathcal{K}}} \triangleq [\bar{c}_{m_1},\ldots,\bar{c}_{m_K}]^T \in \mathcal{C}^{K \times 1}$.
-Since any $\bar{\boldsymbol{c}}_{m_{\mathcal{K}}}$ remains constant per $N$ primary symbols, the received signal at block $n$ is only subject to the variation of the primary source $s[n]$ and AWGN $w[n]$, and thus follows CSCG distribution $y_{m_{\mathcal{K}}}[n] \sim \mathcal{CN}\left(0,\sigma_{m_{\mathcal{K}}}^2\right)$ with variance
+			To explicitly specify each backscatter symbol combination, we label it by the corresponding modulation index set.
+For tag $k$ at state $m_k$, $\forall k \in \mathcal{K}$, we define the modulation index set as $m_{\mathcal{K}} \triangleq \{m_k : k \in \mathcal{K}\}$ and the tag input combination as $\bar{c}_{m_{\mathcal{K}}} \triangleq \{\bar{c}_{m_k} : k \in \mathcal{K}\}$.
+Since any $\bar{c}_{m_{\mathcal{K}}}$ remains constant per $N$ primary symbols, the received signal at block $n$ is only subject to the variation of the primary source $s[n]$ and AWGN $w[n]$, and thus follows CSCG distribution $y_{m_{\mathcal{K}}}[n] \sim \mathcal{CN}\left(0,\sigma_{m_{\mathcal{K}}}^2\right)$ with variance
 			\begin{equation}
@@
 			which denotes the expectation of the received power per primary block under tag modulation index set $\boldsymbol{m}$, and can be numerically evaluated based on the precoder, tag, channel, and noise knowledge.
-For the ease of exposition, we sort all possible $\sigma_{m_{\mathcal{K}}}^2$ in ascending order by a one-to-one mapping $\boldsymbol{m} \mapsto i$, denote the hypothesis that the backscatter symbol vector in status $i$ as $\mathcal{H}_i$, and define $\sigma_i^2 \le \sigma_j^2$ for $i < j$, $i,j \in \mathcal{M^K} \triangleq \{1,\ldots,M^K\}$.\footnote{When more than one modulation index sets yield the same energy level, the mapping is not unique and the detection fails to separate them.
+For the ease of exposition, we sort all possible $\sigma_{m_{\mathcal{K}}}^2$ in ascending order by a one-to-one mapping $\boldsymbol{m} \mapsto i$, denote the hypothesis that the tag input combination at status $i$ as $\mathcal{H}_i$, and define $\sigma_i^2 \le \sigma_j^2$ for $i < j$, $i,j \in \mathcal{M^K} \triangleq \{1,\ldots,M^K\}$.\footnote{When more than one modulation index sets yield the same energy level, the mapping is not unique and the detection fails to separate them.
 This blind spot issue can be mitigated by multi-antenna techniques.} For the optimal Maximum-Likelihood (ML) detector, the likelihood ratio between hypotheses $\mathcal{H}_i$ and $\mathcal{H}_j$ is \cite{Qian2019}
@@
 			\begin{equation}
-				p(z_j \mid \bar{\boldsymbol{c}}_i) = p(z \in \mathcal{R}_j \mid \mathcal{H}_i) = \int_{\mathcal{R}_j} f(z \mid \mathcal{H}_i) \dd z.
+				P(z_j \mid \bar{c}_i) = P(z \in \mathcal{R}_j \mid \mathcal{H}_i) = \int_{\mathcal{R}_j} f(z \mid \mathcal{H}_i) \dd z.
 				\label{eq:equivalent_channel}
@@
 			\begin{equation}
-				p(z_j \mid c_k = \bar{c}_{m_k}) = \frac{\sum_{m_{\mathcal{K} \setminus k}} p(z_j \mid \bar{\boldsymbol{c}}_{m_{\mathcal{K}}})}{\sum_{m_{\mathcal{K}}} p(z_j \mid \bar{\boldsymbol{c}}_{m_{\mathcal{K}}})}.
+				P(z_j \mid c_k = \bar{c}_{m_k}) = \frac{\sum_{m_{\mathcal{K} \setminus k}} P(z_j \mid \bar{c}_{m_{\mathcal{K}}})}{\sum_{m_{\mathcal{K}}} P(z_j \mid \bar{c}_{m_{\mathcal{K}}})}.
 				\label{eq:mac}
@@
 		\end{subsection}
+
+		\begin{subsection}{Backscatter sum-capacity}
+			Before investigating the sum-capacity of the tags, we introduce some definitions in information theory.
+Following \cite{Rezaeian2004}, the information function associated with individual tag input combination $\bar{c}_{m_{\mathcal{K}}}$ is defined as
+			\begin{equation}
+				% I(\bar{c}_{m_{\mathcal{K}}} ; z) = \infdiv*{P(z \mid \bar{c}_{m_{\mathcal{K}}})}{P(z)}
+				I(\bar{c}_{m_{\mathcal{K}}} ; z) \triangleq \sum_j P(z_j \mid \bar{c}_{m_{\mathcal{K}}}) \log \frac{P(z_j \mid \bar{c}_{m_{\mathcal{K}}})}{P(z_j)},
+				\label{eq:information_function}
+			\end{equation}
+			and the marginal information function on $\mathcal{S} \subset \mathcal{K}$ is thus
+			\begin{equation}
+				I_{\mathcal{S}}(\bar{c}_{m_{\mathcal{S}}} ; z) = \sum_{m_{\mathcal{K} \setminus \mathcal{S}}} P_{m_{\mathcal{K} \setminus \mathcal{S}}}(\bar{c}_{m_{\mathcal{K} \setminus \mathcal{S}}}) I(\bar{c}_{m_{\mathcal{K}}} ; z).
+			\end{equation}
+			On top of this, the mutual information and marginal mutual information can be expressed respectively as
+			\begin{align}
+				I(c_{\mathcal{K}} ; z)
+				& = \mathbb{E}_{c_{\mathcal{S}}} \left[I_{\mathcal{S}}(\bar{c}_{m_{\mathcal{S}}} ; z)\right],\\
+				I(c_{\mathcal{S}} ; z)
+				& = \mathbb{E}_{c_{\mathcal{S}}} \left[I(\bar{c}_{m_{\mathcal{S}}} ; z)\right].
+			\end{align}
+
+			% \begin{equation}
+			% 	I_{\mathcal{S}}(\bar{c}_{m_{\mathcal{S}}} ; z) = \sum_{\mathcal{S}^c} P_{\mathcal{S}^c}(\bar{c}_{m_{\mathcal{S}^c}}) I(\bar{c}_{m_{\mathcal{K}}} ; z),
+			% \end{equation}
+			% where $\mathcal{S}^c \triangleq \mathcal{K} \setminus \mathcal{S}$.
+
+			% and the mutual information can be expressed as
+			% \begin{equation}
+			% 	I(\boldsymbol{c} ; z) = \mathbb{E}_{\boldsymbol{c}}
+			% \end{equation}
+
+			% function that evaluates the information associated with individual
+
+			Denote the input probability distribution of tag $k$ at status $m_k$ as $r_k(\bar{c}_{m_k})$.
+
+			% For $\mathcal{S} \subset \mathcal{K}$, denote the input probability distribution that user $r_{\mathcal{S}}(\bar{c}_{m_{\mathcal{S}}})$
+		\end{subsection}
 	\end{section}
 
-	\begin{section}{Precoder and Tag Input Design}
-		TODO
+	\begin{section}{Tag Input and Precoder Design}
+		In this section, we exploit tag input and precoder design to characterize the achievable region of the primary rate and the backscatter sum-rate.
+		\begin{subsection}{Backscatter sum-rate}
+
+		\end{subsection}
 	\end{section}
@@
 We consider the quasi-static block fading model and assume the CSI of the direct channel and the cascaded forward-backward channel $h_{\mathrm{C}} \triangleq h_{\mathrm{B}} h_{\mathrm{F}}$ are known at the AP.\footnote{Due to the lack of RF chains at the passive tag, accurate and efficient CSI acquisition at the AP can be challenging.
-One possible approach is that the AP sends known pilots, the tag responds in a pre-defined manner, and the user performs least-square estimation then feeds back to the AP \cite{Bharadia2015,Yang2015b,Guo2019e}.} It is assumed that the primary symbol $s$ follows standard CSCG distribution $\mathcal{CN}(0,1)$ and the secondary symbol $c$ employs $M$-PSK modulation by \eqref{eq:backscatter_modulation}.
+One possible approach is that the AP sends known pilots, the tag responds in a pre-defined manner, and the user performs least-square estimation then feeds back to the AP \cite{Bharadia2015,Yang2015b,Guo2019g}.} It is assumed that the primary symbol $s$ follows standard CSCG distribution $\mathcal{CN}(0,1)$ and the secondary symbol $c$ employs $M$-PSK modulation by \eqref{eq:backscatter_modulation}.
 Due to the practical constraints on switching speed and synchronization gap, the passive tag typically transmits at a much lower data rate than the AP.
 Hence, we assume the secondary symbol period is $N \gg 1 \in \mathbb{Z}_{++}$ times the primary symbol period and focus on the interval of one particular $c$.
-At (primary) symbol block $n \in \mathcal{N} \triangleq \{1,\ldots,N\}$, the user simultaneously captures the signal from both primary and secondary links as\footnote{We assume the time difference of arrival from the AP-UE path and the AP-TG-UE path are negligible compared to the symbol period \cite{Guo2019b,Liang2020,Long2020a}.}
+At (primary) symbol block $n \in \mathcal{N} \triangleq \{1,\ldots,N\}$, the user simultaneously captures the signal from both primary and secondary links as\footnote{We assume the time difference of arrival from the AP-UE path and the AP-TG-UE path are negligible compared to the symbol period \cite{Guo2019b,Liang2020,Long2020b}.}
 		\begin{equation}

### 2021-11-27 main.tex
:pencil: Add backscatter sum-capacity and primary ergodic capacity

@@
 			where $\boldsymbol{w} \in \mathbb{C}^{Q \times 1}$ is the active precoder satisfying $\lVert \boldsymbol{w} \rVert^2 \le P$, $P$ is the average transmit power constraint at the AP, and $w[n] \sim \mathcal{CN}(0,\sigma_w^2)$ is the equivalent Additive White Gaussian Noise (AWGN) at block $n$.
-Besides, we stack the backscatter symbol of $K$ tags as $\boldsymbol{c} \triangleq [c_1,\ldots,c_K]^T \in \mathcal{C}^{K \times 1}$, the received signal over $N$ blocks as $\boldsymbol{y} \triangleq \left[y[1],\ldots,y[N]\right]^T \in \mathbb{C}^{N \times 1}$, and define the equivalent channel for primary transmission as
+Besides, we collect the backscatter symbols of $K$ tags into $c_{\mathcal{K}} \triangleq \{c_k : k \in \mathcal{K}\}$, stack the received signal over $N$ blocks as $\boldsymbol{y} \triangleq \left[y[1],\ldots,y[N]\right]^T \in \mathbb{C}^{N \times 1}$, and define the equivalent channel for primary transmission as
 			\begin{equation}
-				h_{\mathrm{E}}^H(\boldsymbol{c}) \triangleq \boldsymbol{h}_{\mathrm{D}}^H + \sum_{k \in \mathcal{K}} \sqrt{\alpha_k} \boldsymbol{h}_{\mathrm{C},k}^H c_k.
-				\label{eq:equivalent_channel}
+				\boldsymbol{h}_{\mathrm{E}}^H(c_{\mathcal{K}}) \triangleq \boldsymbol{h}_{\mathrm{D}}^H + \sum_{k \in \mathcal{K}} \sqrt{\alpha_k} \boldsymbol{h}_{\mathrm{C},k}^H c_k.
+				\label{eq:equivalent_primary_channel}
 			\end{equation}
@@
 As such, each reflection coefficient simultaneously encodes the tag message and influences the equivalent channel of the primary link.
-If the backscatter symbols can be successfully decoded first, they can be modeled within the equivalent channel \eqref{eq:equivalent_channel} as in channel training, instead of being removed by SIC.
+If the backscatter symbols can be successfully decoded first, they can be modeled within the equivalent channel \eqref{eq:equivalent_primary_channel} as in channel training, instead of being removed by SIC.
 			\end{remark}
@@
 			\begin{equation}
-				\sigma_{m_{\mathcal{K}}}^2 \triangleq \Bigl\lvert \bigl(\boldsymbol{h}_{\mathrm{D}}^H + \sum_{k \in \mathcal{K}} \sqrt{\alpha_k} \boldsymbol{h}_{\mathrm{C},k}^H \bar{c}_{m_k}\bigr) \boldsymbol{w} \Bigr\rvert^2 + \sigma_w^2,
+				\sigma_{m_{\mathcal{K}}}^2 = \Bigl\lvert \underbrace{\bigl(\boldsymbol{h}_{\mathrm{D}}^H + \sum_{k \in \mathcal{K}} \sqrt{\alpha_k} \boldsymbol{h}_{\mathrm{C},k}^H \bar{c}_{m_k}\bigr)}_{\boldsymbol{h}_{\mathrm{E}}^H(\bar{c}_{m_{\mathcal{K}}})} \boldsymbol{w} \Bigr\rvert^2 + \sigma_w^2,
 				\label{eq:receive_variance}
 			\end{equation}
-			which denotes the expectation of the received power per primary block under tag modulation index set $\boldsymbol{m}$, and can be numerically evaluated based on the precoder, tag, channel, and noise knowledge.
-For the ease of exposition, we sort all possible $\sigma_{m_{\mathcal{K}}}^2$ in ascending order by a one-to-one mapping $\boldsymbol{m} \mapsto i$, denote the hypothesis that the tag input combination at status $i$ as $\mathcal{H}_i$, and define $\sigma_i^2 \le \sigma_j^2$ for $i < j$, $i,j \in \mathcal{M^K} \triangleq \{1,\ldots,M^K\}$.\footnote{When more than one modulation index sets yield the same energy level, the mapping is not unique and the detection fails to separate them.
+			which denotes the expectation of the received power per primary block under tag modulation index set $m_{\mathcal{K}}$, and can be numerically evaluated based on the precoder, tag, channel, and noise knowledge.
+For the ease of exposition, we sort all possible $\sigma_{m_{\mathcal{K}}}^2$ in ascending order by a one-to-one mapping $m_{\mathcal{K}} \mapsto i$, denote the hypothesis that the tag input combination at status $i$ as $\mathcal{H}_i$, and define $\sigma_i^2 \le \sigma_j^2$ for $i < j$, $i,j \in \mathcal{M^K} \triangleq \{1,\ldots,M^K\}$.\footnote{When more than one modulation index sets yield the same energy level, the mapping is not unique and the detection fails to separate them.
 This blind spot issue can be mitigated by multi-antenna techniques.} For the optimal Maximum-Likelihood (ML) detector, the likelihood ratio between hypotheses $\mathcal{H}_i$ and $\mathcal{H}_j$ is \cite{Qian2019}
@@
 			\begin{equation}
-				P(z_j \mid \bar{c}_i) = P(z \in \mathcal{R}_j \mid \mathcal{H}_i) = \int_{\mathcal{R}_j} f(z \mid \mathcal{H}_i) \dd z.
-				\label{eq:equivalent_channel}
+				P(\bar{z}_j \mid \bar{c}_i) = P(z \in \mathcal{R}_j \mid \mathcal{H}_i) = \int_{\mathcal{R}_j} f(z \mid \mathcal{H}_i) \dd z.
+				\label{eq:point_to_point_channel}
 			\end{equation}
 
-			Based on the equivalent point-to-point channel \eqref{eq:equivalent_channel}, we can compute the marginal probability on all tags and obtain $K$ transition matrices from $\mathcal{M}$ to $\mathcal{M^K}$ that compose a discrete memoryless MAC.
+			Based on the equivalent point-to-point channel \eqref{eq:point_to_point_channel}, we can compute the marginal probability on all tags and obtain $K$ transition matrices from $\mathcal{M}$ to $\mathcal{M^K}$ that compose a discrete memoryless MAC.
 Mathematically speaking, the probability of observing energy level $j$ when tag $k$ at status $m_k$ is
 			\begin{equation}
-				P(z_j \mid c_k = \bar{c}_{m_k}) = \frac{\sum_{m_{\mathcal{K} \setminus k}} P(z_j \mid \bar{c}_{m_{\mathcal{K}}})}{\sum_{m_{\mathcal{K}}} P(z_j \mid \bar{c}_{m_{\mathcal{K}}})}.
+				P(\bar{z}_j \mid \bar{c}_{m_k}) = \frac{\sum_{m_{\mathcal{K} \setminus k}} P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K}}})}{\sum_{m_{\mathcal{K}}} P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K}}})}.
 				\label{eq:mac}
@@
 
-			In summary, for every possible tag input combination, the expected power of the received signal per block can be evaluated by \eqref{eq:receive_variance}, the energy detection threshold to nearby states can be computed by \eqref{eq:detection_threshold}, the decision region can be retrieved by \eqref{eq:decision_region}, the equivalent point-to-point channel can be obtained by \eqref{eq:energy_distribution} and \eqref{eq:equivalent_channel}, and the discrete memoryless MAC can be extracted by \eqref{eq:mac}.
+			In summary, for every possible tag input combination, the expected power of the received signal per block can be evaluated by \eqref{eq:receive_variance}, the energy detection threshold to nearby states can be computed by \eqref{eq:detection_threshold}, the decision region can be retrieved by \eqref{eq:decision_region}, the equivalent point-to-point channel can be obtained by \eqref{eq:energy_distribution} and \eqref{eq:point_to_point_channel}, and the discrete memoryless MAC can be extracted by \eqref{eq:mac}.
 		\end{subsection}
@@
 		\begin{subsection}{Backscatter sum-capacity}
-			Before investigating the sum-capacity of the tags, we introduce some definitions in information theory.
-Following \cite{Rezaeian2004}, the information function associated with individual tag input combination $\bar{c}_{m_{\mathcal{K}}}$ is defined as
+			Before investigating the sum-capacity of the tags, we introduce some prerequisites in information theory.
+Define the input probability distribution of tag $k$ at status $m_k$ as $P_k(\bar{c}_{m_k})$, and assume the input distribution of all tags are mutually independent, such that $P_{\mathcal{K}}(\bar{c}_{m_{\mathcal{K}}}) = \prod_{k \in \mathcal{K}} P_k(\bar{c}_{m_k})$.
+Following \cite{Rezaeian2004}, the information function associated with specific tag input combination $\bar{c}_{m_{\mathcal{K}}}$ is defined as
 			\begin{equation}
-				% I(\bar{c}_{m_{\mathcal{K}}} ; z) = \infdiv*{P(z \mid \bar{c}_{m_{\mathcal{K}}})}{P(z)}
-				I(\bar{c}_{m_{\mathcal{K}}} ; z) \triangleq \sum_j P(z_j \mid \bar{c}_{m_{\mathcal{K}}}) \log \frac{P(z_j \mid \bar{c}_{m_{\mathcal{K}}})}{P(z_j)},
+				I(\bar{c}_{m_{\mathcal{K}}} ; z) \triangleq \sum_j P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K}}}) \log \frac{P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K}}})}{P(\bar{z}_j)},
 				\label{eq:information_function}
 			\end{equation}
-			and the marginal information function on $\mathcal{S} \subset \mathcal{K}$ is thus
+			the marginal information function on $\mathcal{S} \subset \mathcal{K}$ can be written as
 			\begin{equation}
-				I_{\mathcal{S}}(\bar{c}_{m_{\mathcal{S}}} ; z) = \sum_{m_{\mathcal{K} \setminus \mathcal{S}}} P_{m_{\mathcal{K} \setminus \mathcal{S}}}(\bar{c}_{m_{\mathcal{K} \setminus \mathcal{S}}}) I(\bar{c}_{m_{\mathcal{K}}} ; z).
+				I_{\mathcal{S}}(\bar{c}_{m_{\mathcal{S}}} ; z) = \sum_{m_{\mathcal{K} \setminus \mathcal{S}}} P_{\mathcal{K} \setminus \mathcal{S}}(\bar{c}_{m_{\mathcal{K} \setminus \mathcal{S}}}) I(\bar{c}_{m_{\mathcal{K}}} ; z),
+				\label{eq:marginal_information_function}
 			\end{equation}
-			On top of this, the mutual information and marginal mutual information can be expressed respectively as
-			\begin{align}
-				I(c_{\mathcal{K}} ; z)
-				& = \mathbb{E}_{c_{\mathcal{S}}} \left[I_{\mathcal{S}}(\bar{c}_{m_{\mathcal{S}}} ; z)\right],\\
-				I(c_{\mathcal{S}} ; z)
-				& = \mathbb{E}_{c_{\mathcal{S}}} \left[I(\bar{c}_{m_{\mathcal{S}}} ; z)\right].
-			\end{align}
+			and the mutual information of the tags and the received signal can be expressed as\footnote{Please be aware that $c_{\mathcal{K}}$, $c_{\mathcal{S}}$, $z$ are random variables, while $\bar{c}_{m_{\mathcal{K}}}$ (and $\bar{c}_i$), $\bar{c}_{m_{\mathcal{S}}}$, $\bar{z}_j$ represent the corresponding instances.}
+			\begin{equation}
+				I(c_{\mathcal{K}} ; z) = \mathbb{E}_{c_{\mathcal{K}}} \left[I(\bar{c}_{m_{\mathcal{K}}} ; z)\right] = \mathbb{E}_{c_{\mathcal{S}}} \left[I_{\mathcal{S}}(\bar{c}_{m_{\mathcal{S}}} ; z)\right].
+			\end{equation}
+
+			Evidently, for a given discrete memoryless MAC with transition probability $P(z \mid c_{\mathcal{K}})$, the information function $I(\bar{c}_{m_{\mathcal{K}}} ; z)$ and mutual information $I(c_{\mathcal{K}} ; z)$ only depend on the tag input distribution $P_k(\bar{c}_{m_k})$, $\forall m_k \in \mathcal{M}, k \in \mathcal{K}$.
+Therefore, we can obtain the backscatter sum-capacity by maximizing the mutual information over the tag input distributions as
+			\begin{equation}
+				R_c = \max_{P(c_{\mathcal{K}})} I(c_{\mathcal{K}} ; z) \ [\si{bpcu}].
+			\end{equation}
+
+			% On top of them, the mutual information and marginal mutual information can be written respectively as\footnote{Please be aware that $c_{\mathcal{K}}$, $c_{\mathcal{S}}$, $z$ are random variables, while $\bar{c}_{m_{\mathcal{K}}}$ (and $\bar{c}_i$), $\bar{c}_{m_{\mathcal{S}}}$, $\bar{z}_j$ represent the corresponding instances.}
+			% \begin{align}
+			% 	I(c_{\mathcal{K}} ; z)
+			% 	& = \mathbb{E}_{c_{\mathcal{S}}} \left[I_{\mathcal{S}}(\bar{c}_{m_{\mathcal{S}}} ; z)\right],\\
+			% 	I(c_{\mathcal{S}} ; z)
+			% 	& = \mathbb{E}_{c_{\mathcal{S}}} \left[I(\bar{c}_{m_{\mathcal{S}}} ; z)\right].
+			% \end{align}
+
+			% On top of \eqref{eq:information_function} and \eqref{eq:marginal_information_function}, the mutual information can be expressed as\footnote{Please be aware that $c_{\mathcal{K}}$, $c_{\mathcal{S}}$, $z$ are random variables, while $\bar{c}_{m_{\mathcal{K}}}$ (and $\bar{c}_i$), $\bar{c}_{m_{\mathcal{S}}}$, $\bar{z}_j$ represent the corresponding instances.}
+			% \begin{equation}
+			% 	I(c_{\mathcal{K}} ; z) = \mathbb{E}_{c_{\mathcal{K}}} \left[I(\bar{c}_{m_{\mathcal{K}}} ; z)\right] = \mathbb{E}_{c_{\mathcal{S}}} \left[I_{\mathcal{S}}(\bar{c}_{m_{\mathcal{S}}} ; z)\right].
+			% \end{equation}
 
@@
 
-			Denote the input probability distribution of tag $k$ at status $m_k$ as $r_k(\bar{c}_{m_k})$.
-
 			% For $\mathcal{S} \subset \mathcal{K}$, denote the input probability distribution that user $r_{\mathcal{S}}(\bar{c}_{m_{\mathcal{S}}})$
 		\end{subsection}
+
+		\begin{subsection}{Primary ergodic capacity}
+			Once the tag symbol set $\bar{c}_{m_{\mathcal{K}}}$ is successfully detected, the user can eliminate the backscatter uncertainty and obtain the equivalent primary channel by \eqref{eq:equivalent_primary_channel}.
+From the perspective of primary transmission, the tags adjust the propagation environment in a potentially beneficial manner, and create artificial channel variation within each fading block.
+As such, the ergodic primary capacity can be expressed as
+			\begin{align}
+				R_s
+				& = \mathbb{E}_{c_{\mathcal{K}}} \left[\log_2 \left(1 + \frac{\lvert \boldsymbol{h}_{\mathrm{E}}^H(c_{\mathcal{K}}) \boldsymbol{w} \rvert^2}{\sigma_w^2}\right)\right]\nonumber\\
+				& = \sum_{m_{\mathcal{K}}} \prod_{k \in \mathcal{K}} P_k(\bar{c}_{m_k}) \log_2 \left(1 + \frac{\lvert \boldsymbol{h}_{\mathrm{E}}^H(\bar{c}_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_w^2}\right) \ [\si{bps/Hz}].
+				\label{eq:primary_rate}
+			\end{align}
+			which is also a function of the tag input distribution $P_k(\bar{c}_{m_k})$, $\forall m_k \in \mathcal{M}, k \in \mathcal{K}$.
+		\end{subsection}
+		\label{se:system_model}
 	\end{section}

### 2021-11-29 main.tex
:pencil: Update energy distribution and formulate problem

@@
 			To explicitly specify each backscatter symbol combination, we label it by the corresponding modulation index set.
-For tag $k$ at state $m_k$, $\forall k \in \mathcal{K}$, we define the modulation index set as $m_{\mathcal{K}} \triangleq \{m_k : k \in \mathcal{K}\}$ and the tag input combination as $\bar{c}_{m_{\mathcal{K}}} \triangleq \{\bar{c}_{m_k} : k \in \mathcal{K}\}$.
+For tag $k$ at state $m_k \in \mathcal{M}$, $\forall k \in \mathcal{K}$, we define the modulation index set as $m_{\mathcal{K}} \triangleq \{m_k : k \in \mathcal{K}\}$ and the tag input combination as $\bar{c}_{m_{\mathcal{K}}} \triangleq \{\bar{c}_{m_k} : k \in \mathcal{K}\}$.
 Since any $\bar{c}_{m_{\mathcal{K}}}$ remains constant per $N$ primary symbols, the received signal at block $n$ is only subject to the variation of the primary source $s[n]$ and AWGN $w[n]$, and thus follows CSCG distribution $y_{m_{\mathcal{K}}}[n] \sim \mathcal{CN}\left(0,\sigma_{m_{\mathcal{K}}}^2\right)$ with variance
@@
 			\begin{equation}
-				\mathcal{R}_i \triangleq [T_{i-1, i}, T_{i, i+1}),
+				\mathcal{R}_i \triangleq [T_{i-1,i}, T_{i,i+1}),
 				\label{eq:decision_region}
@@
 Let $f(z \mid \mathcal{H}_i)$ be the conditional probability density function of receiving $z$ under hypothesis $\mathcal{H}_i$.
-Since $z$ follows chi-squared distribution with $2N$ degrees of freedom, it holds that
+Correspondingly, $z$ is the sum of $N$ i.i.d.
+exponential variables each with mean $\sigma_i^2$, and thus follows Erlang distribution with shape $N$ and scale $\sigma_i^2$
 			\begin{equation}
-				f(z \mid \mathcal{H}_i) = \frac{z^{N-1} e^{-z/\sigma_i^2}}{\sigma_i^{2N} \Gamma(N)},
+				f(z \mid \mathcal{H}_i) = \frac{z^{N-1} e^{-z/\sigma_i^2}}{\sigma_i^{2N} (N-1)!}.
 				\label{eq:energy_distribution}
 			\end{equation}
-			where $\Gamma(\cdot)$ is the gamma function.
-As such, we can formulate an equivalent point-to-point discrete memoryless channel from tag input combination alphabet $\mathcal{M^K}$ to received energy level alphabet $\mathcal{M^K}$ as a transition matrix, where the probability of observing energy level $j$ under tag input combination $i$ is\footnote{For simplicity, we assume there exists at least one feasible precoder that produces distinct received energy levels for all tag input combinations.
+
+			On top of \eqref{eq:decision_region} and \eqref{eq:energy_distribution}, we can formulate an equivalent point-to-point discrete memoryless channel from tag input combination alphabet $\mathcal{M^K}$ to received energy level alphabet $\mathcal{M^K}$ as a transition matrix, where the probability of observing energy level $j$ under tag input combination $i$ is\footnote{For simplicity, we assume there exists at least one feasible precoder that produces distinct received energy levels for all tag input combinations.
 [TODO] Is this necessary?
@@
 
-			Evidently, for a given discrete memoryless MAC with transition probability $P(z \mid c_{\mathcal{K}})$, the information function $I(\bar{c}_{m_{\mathcal{K}}} ; z)$ and mutual information $I(c_{\mathcal{K}} ; z)$ only depend on the tag input distribution $P_k(\bar{c}_{m_k})$, $\forall m_k \in \mathcal{M}, k \in \mathcal{K}$.
+			Evidently, for a given discrete memoryless MAC with transition probability $P(z \mid c_{\mathcal{K}})$, the information function $I(\bar{c}_{m_{\mathcal{K}}} ; z)$ and mutual information $I(c_{\mathcal{K}} ; z)$ only depend on the tag input distribution $P_k(\bar{c}_{m_k})$, $\forall m_k \in \mathcal{M}$, $\forall k \in \mathcal{K}$.
 Therefore, we can obtain the backscatter sum-capacity by maximizing the mutual information over the tag input distributions as
@@
 			\end{equation}
-
-			% On top of them, the mutual information and marginal mutual information can be written respectively as\footnote{Please be aware that $c_{\mathcal{K}}$, $c_{\mathcal{S}}$, $z$ are random variables, while $\bar{c}_{m_{\mathcal{K}}}$ (and $\bar{c}_i$), $\bar{c}_{m_{\mathcal{S}}}$, $\bar{z}_j$ represent the corresponding instances.}
-			% \begin{align}
-			% 	I(c_{\mathcal{K}} ; z)
-			% 	& = \mathbb{E}_{c_{\mathcal{S}}} \left[I_{\mathcal{S}}(\bar{c}_{m_{\mathcal{S}}} ; z)\right],\\
-			% 	I(c_{\mathcal{S}} ; z)
-			% 	& = \mathbb{E}_{c_{\mathcal{S}}} \left[I(\bar{c}_{m_{\mathcal{S}}} ; z)\right].
-			% \end{align}
-
-			% On top of \eqref{eq:information_function} and \eqref{eq:marginal_information_function}, the mutual information can be expressed as\footnote{Please be aware that $c_{\mathcal{K}}$, $c_{\mathcal{S}}$, $z$ are random variables, while $\bar{c}_{m_{\mathcal{K}}}$ (and $\bar{c}_i$), $\bar{c}_{m_{\mathcal{S}}}$, $\bar{z}_j$ represent the corresponding instances.}
-			% \begin{equation}
-			% 	I(c_{\mathcal{K}} ; z) = \mathbb{E}_{c_{\mathcal{K}}} \left[I(\bar{c}_{m_{\mathcal{K}}} ; z)\right] = \mathbb{E}_{c_{\mathcal{S}}} \left[I_{\mathcal{S}}(\bar{c}_{m_{\mathcal{S}}} ; z)\right].
-			% \end{equation}
-
-			% \begin{equation}
-			% 	I_{\mathcal{S}}(\bar{c}_{m_{\mathcal{S}}} ; z) = \sum_{\mathcal{S}^c} P_{\mathcal{S}^c}(\bar{c}_{m_{\mathcal{S}^c}}) I(\bar{c}_{m_{\mathcal{K}}} ; z),
-			% \end{equation}
-			% where $\mathcal{S}^c \triangleq \mathcal{K} \setminus \mathcal{S}$.
-
-			% and the mutual information can be expressed as
-			% \begin{equation}
-			% 	I(\boldsymbol{c} ; z) = \mathbb{E}_{\boldsymbol{c}}
-			% \end{equation}
-
-			% function that evaluates the information associated with individual
-
-			% For $\mathcal{S} \subset \mathcal{K}$, denote the input probability distribution that user $r_{\mathcal{S}}(\bar{c}_{m_{\mathcal{S}}})$
 		\end{subsection}
@@
 		\begin{subsection}{Primary ergodic capacity}
-			Once the tag symbol set $\bar{c}_{m_{\mathcal{K}}}$ is successfully detected, the user can eliminate the backscatter uncertainty and obtain the equivalent primary channel by \eqref{eq:equivalent_primary_channel}.
+			Once the tag symbol set $\bar{c}_{m_{\mathcal{K}}}$ is successfully decoded, the user can eliminate the backscatter uncertainty and model it within the equivalent primary channel by \eqref{eq:equivalent_primary_channel}.
 From the perspective of primary transmission, the tags adjust the propagation environment in a potentially beneficial manner, and create artificial channel variation within each fading block.
@@
 			\end{align}
-			which is also a function of the tag input distribution $P_k(\bar{c}_{m_k})$, $\forall m_k \in \mathcal{M}, k \in \mathcal{K}$.
+			which is also a function of the tag input distribution $P(c_{\mathcal{K}})$.
 		\end{subsection}
-		\label{se:system_model}
 	\end{section}
@@
 	\begin{section}{Tag Input and Precoder Design}
-		In this section, we exploit tag input and precoder design to characterize the achievable region of the primary rate and the backscatter sum-rate.
-		\begin{subsection}{Backscatter sum-rate}
+		\begin{subsection}{Primary ergodic-secondary sum rate region}
+			To achieve a flexible tradeoff between the primary and backscatter links, we aim to optimize the precoder and tag input distribution to maximize the weighted sum of the ergodic primary rate and the total backscatter rate, under the average transmit power and probability constraints
+			\begin{maxi!}
+				{\scriptstyle{{P(c_{\mathcal{K}})},{\boldsymbol{w}}}}{\rho R_s + (1 - \rho) R_c}{\label{op:rate_region}}{\label{ob:weighted_sum_rate}}
+				\addConstraint{\lVert \boldsymbol{w} \rVert^2}{\le P\label{co:average_transmit_power}}
+				\addConstraint{\sum_{m_k} P_k(\bar{c}_{m_k})}{=1,\quad\label{co:sum_probability}}{\forall k \in \mathcal{K}}
+				\addConstraint{P_k(\bar{c}_{m_k})}{\ge 0,\quad\label{co:nonnegative_probability}}{\forall m_k \in \mathcal{M}, \ \forall k \in \mathcal{K}}
+			\end{maxi!}
+			where $\rho \in [0,1]$ denotes the priority of the primary link.
+As problem \eqref{op:rate_region} is not jointly convex over $\boldsymbol{w}$ and $P(c_{\mathcal{K}})$, we propose an alternating optimization (AO)-based algorithm that iteratively retrieve the global optimal precoder and capacity-achieving input distribution in closed forms.
+		\end{subsection}
 
+		\begin{subsection}{Precoder}
+			TODO
 		\end{subsection}

### 2021-12-02 main.tex
:seedling: Log ideas on decision regions and precoder design

@@
 
-		\begin{subsection}{Backscatter sum-capacity}
-			Before investigating the sum-capacity of the tags, we introduce some prerequisites in information theory.
+		\begin{subsection}{Backscatter sum-rate}
+			Before investigating the sum-rate of the tags, we introduce some prerequisites in information theory.
 Define the input probability distribution of tag $k$ at status $m_k$ as $P_k(\bar{c}_{m_k})$, and assume the input distribution of all tags are mutually independent, such that $P_{\mathcal{K}}(\bar{c}_{m_{\mathcal{K}}}) = \prod_{k \in \mathcal{K}} P_k(\bar{c}_{m_k})$.
@@
 				I(c_{\mathcal{K}} ; z) = \mathbb{E}_{c_{\mathcal{K}}} \left[I(\bar{c}_{m_{\mathcal{K}}} ; z)\right] = \mathbb{E}_{c_{\mathcal{S}}} \left[I_{\mathcal{S}}(\bar{c}_{m_{\mathcal{S}}} ; z)\right].
+				\label{eq:mutual_information}
 			\end{equation}
@@
 			Evidently, for a given discrete memoryless MAC with transition probability $P(z \mid c_{\mathcal{K}})$, the information function $I(\bar{c}_{m_{\mathcal{K}}} ; z)$ and mutual information $I(c_{\mathcal{K}} ; z)$ only depend on the tag input distribution $P_k(\bar{c}_{m_k})$, $\forall m_k \in \mathcal{M}$, $\forall k \in \mathcal{K}$.
-Therefore, we can obtain the backscatter sum-capacity by maximizing the mutual information over the tag input distributions as
+Therefore, we can obtain the backscatter sum-rate by maximizing the mutual information over the tag input distributions as
 			\begin{equation}
 				R_c = \max_{P(c_{\mathcal{K}})} I(c_{\mathcal{K}} ; z) \ [\si{bpcu}].
+				\label{eq:backscatter_sum_rate}
 			\end{equation}
@@
 
-		\begin{subsection}{Primary ergodic capacity}
+		\begin{subsection}{Primary ergodic rate}
 			Once the tag symbol set $\bar{c}_{m_{\mathcal{K}}}$ is successfully decoded, the user can eliminate the backscatter uncertainty and model it within the equivalent primary channel by \eqref{eq:equivalent_primary_channel}.
 From the perspective of primary transmission, the tags adjust the propagation environment in a potentially beneficial manner, and create artificial channel variation within each fading block.
-As such, the ergodic primary capacity can be expressed as
+As such, the ergodic primary rate can be expressed as
 			\begin{align}
@@
 				& = \sum_{m_{\mathcal{K}}} \prod_{k \in \mathcal{K}} P_k(\bar{c}_{m_k}) \log_2 \left(1 + \frac{\lvert \boldsymbol{h}_{\mathrm{E}}^H(\bar{c}_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_w^2}\right) \ [\si{bps/Hz}].
-				\label{eq:primary_rate}
+				\label{eq:primary_ergodic_rate}
 			\end{align}
@@
 		\begin{subsection}{Primary ergodic-secondary sum rate region}
-			To achieve a flexible tradeoff between the primary and backscatter links, we aim to optimize the precoder and tag input distribution to maximize the weighted sum of the ergodic primary rate and the total backscatter rate, under the average transmit power and probability constraints
+			To achieve a flexible tradeoff between the primary and backscatter links, we aim to optimize the tag input distribution, decision regions, and precoder to maximize the weighted sum of the ergodic primary rate and the total backscatter rate, under the average transmit power and probability constraints
 			\begin{maxi!}
-				{\scriptstyle{{P(c_{\mathcal{K}})},{\boldsymbol{w}}}}{\rho R_s + (1 - \rho) R_c}{\label{op:rate_region}}{\label{ob:weighted_sum_rate}}
+				{\scriptstyle{P(c_{\mathcal{K}}),\mathcal{T},\boldsymbol{w}}}{\rho R_s + (1 - \rho) R_c}{\label{op:rate_region}}{\label{ob:weighted_sum_rate}}
 				\addConstraint{\lVert \boldsymbol{w} \rVert^2}{\le P\label{co:average_transmit_power}}
@@
 			where $\rho \in [0,1]$ denotes the priority of the primary link.
-As problem \eqref{op:rate_region} is not jointly convex over $\boldsymbol{w}$ and $P(c_{\mathcal{K}})$, we propose an alternating optimization (AO)-based algorithm that iteratively retrieve the global optimal precoder and capacity-achieving input distribution in closed forms.
+As problem \eqref{op:rate_region} is not jointly convex over $\boldsymbol{w}$ and $P(c_{\mathcal{K}})$, we propose an Block Coordinate Descent (BCD)-based algorithm that iteratively updates the input distribution, decision region, and precoder, until convergence.
+		\end{subsection}
+
+		\begin{subsection}{Input distribution}
+			Once the decision region boundaries $\mathcal{T}$ and the precoder $\boldsymbol{w}$ are determined, we can obtain the equivalent discrete memoryless MAC by \eqref{eq:mac}.
+[The optimal solution is obtained in closed form; to add here]
+		\end{subsection}
+
+		\begin{subsection}{Decision region}
+			As indicated by \cite{Qian2019b}, the optimal ML decision regions are very close to the optimal decision regions to problem \eqref{op:weighted_sum_rate}.
+We can either use \eqref{eq:decision_region} as suboptimal, or take derivative of \eqref{eq:mutual_information} w.r.t.
+$T_{i-1,i}$ and $T_{i,i+1}$ (however, closed-form solutions are unavailable and two-dimensional search is needed).
 		\end{subsection}
@@
 		\begin{subsection}{Precoder}
-			TODO
+			Interestingly, we can design precoder to adjust the expectation of the received power \eqref{eq:receive_variance} at each tag input combination, which can avoid the detection blind spots in \cite{Qian2019} and further boost the weighted sum-rate.
+However, the problem is highly non-convex -- the information function associated with input combination status $i$ is
+			\begin{align}
+				I(\bar{c}_i ; z)
+				& = \sum_{j \in \mathcal{M^K}} \int_{T_{j-1,j}}^{T_{j,j+1}} \frac{z^{N-1} \exp \left(-\frac{z}{\mathrm{tr}(H_{\mathrm{E},i} W) + \sigma_w^2}\right)}{\left(\mathrm{tr}(H_{\mathrm{E},i} W) + \sigma_w^2\right)^N (N-1)!} \dd z\nonumber\\
+				& \quad \times \log \frac{\int_{T_{j-1,j}}^{T_{j,j+1}} \frac{z^{N-1} \exp \left(-\frac{z}{\mathrm{tr}(H_{\mathrm{E},i} W) + \sigma_w^2}\right)}{\left(\mathrm{tr}(H_{\mathrm{E},i} W) + \sigma_w^2\right)^N (N-1)!} \dd z}{\sum_{i' \in \mathcal{M^K}} \int_{T_{j-1,j}}^{T_{j,j+1}} \frac{z^{N-1} \exp \left(-\frac{z}{\mathrm{tr}(H_{\mathrm{E},i'} W) + \sigma_w^2}\right)}{\left(\mathrm{tr}(H_{\mathrm{E},i'} W) + \sigma_w^2\right)^N (N-1)!} \dd z},
+				\label{eq:information_function_precoder}
+			\end{align}
+			and the mutual information can be expressed as a function of $W$ by combining \eqref{eq:mutual_information} and \eqref{eq:information_function_precoder}.
+
+			So far I have no idea how to solve this issue, and found no reference regarding precoder design for AmBC/SR with discrete channels (although some naive combiner designs are available for BIBO).
+Personally, I believe the precoder design is the key to (i) boost the rate region and avoid blind spots in conventional AmBC; (ii) build our proposal over existing infrastructures.
+Ideally, assuming the number of transmit antennas $Q$ is larger than the number of tags $K$, the optimal energy levels should be almost uniformly spaced (as $z$ follows Erlang distribution) to concentrate the channel transitional probability on diagonal as possible.
 		\end{subsection}

### 2021-12-02 main.tex
:pencil: ML vs capacity-achieving decision threshold

@@
 		\begin{subsection}{Backscatter Detection}
-			To reveal the impact of backscatter modulation on the primary transmission, we extend the non-coherent Ambient Backscatter Communications (AmBC) detection \cite{Qian2019} to the multi-tag case, and propose a low-complexity energy detection to decode the backscatter symbols under primary source uncertainty.
+			To reveal the impact of backscatter modulation on the primary transmission and avoid the exponential complexity of joint detection, we extend the non-coherent Ambient Backscatter Communications (AmBC) detection \cite{Qian2019} to the multi-tag case, and propose a low-complexity energy detection to decode the backscatter symbols under primary source uncertainty.
 It requires no dedicated receivers or non-coherent codes at the AP, and can be readily implemented over legacy downlink systems.
@@
 For the ease of exposition, we sort all possible $\sigma_{m_{\mathcal{K}}}^2$ in ascending order by a one-to-one mapping $m_{\mathcal{K}} \mapsto i$, denote the hypothesis that the tag input combination at status $i$ as $\mathcal{H}_i$, and define $\sigma_i^2 \le \sigma_j^2$ for $i < j$, $i,j \in \mathcal{M^K} \triangleq \{1,\ldots,M^K\}$.\footnote{When more than one modulation index sets yield the same energy level, the mapping is not unique and the detection fails to separate them.
-This blind spot issue can be mitigated by multi-antenna techniques.} For the optimal Maximum-Likelihood (ML) detector, the likelihood ratio between hypotheses $\mathcal{H}_i$ and $\mathcal{H}_j$ is \cite{Qian2019}
-			\begin{equation}
-				\Lambda_{i,j}(\boldsymbol{y}) = \frac{f(\boldsymbol{y} \mid \mathcal{H}_i)}{f(\boldsymbol{y} \mid \mathcal{H}_j)} = \left( \frac{\sigma_j^2}{\sigma_i^2} \right)^N \exp \left( \frac{\sigma_i^2 - \sigma_j^2}{\sigma_i^2 \sigma_j^2} z \right),
-				\label{eq:likelihood_ratio}
-			\end{equation}
-			where $f(\boldsymbol{y} \mid \mathcal{H}_i)$ and $f(\boldsymbol{y} \mid \mathcal{H}_j)$ are respectively the conditional probability density function of receiving $\boldsymbol{y}$ under hypothesis $\mathcal{H}_i$ and $\mathcal{H}_j$, and $z \triangleq \lVert \boldsymbol{y} \rVert^2$ is the received signal energy over $N$ primary blocks.
-Obviously, the likelihood ratio only depends on $z$ and the energy detection is thus optimal.
-The corresponding decision rule is
-			\begin{equation}
-				\Lambda_{i,j}(z) \underset{\mathcal{H}_j}{\overset{\mathcal{H}_i}{\lessgtr}} 1 \iff z \underset{\mathcal{H}_j}{\overset{\mathcal{H}_i}{\lessgtr}} T_{i,j},
-				\label{eq:decision_rule}
-			\end{equation}
-			where the detection threshold between $\mathcal{H}_i$ and $\mathcal{H}_j$ is
-			\begin{equation}
-				T_{i,j} \triangleq N \frac{\sigma_i^2 \sigma_j^2}{\sigma_i^2 - \sigma_j^2} \log \frac{\sigma_i^2}{\sigma_j^2}.
-				\label{eq:detection_threshold}
-			\end{equation}
-
-			Accordingly, the decision region of hypothesis $\mathcal{H}_i$ is
-			\begin{equation}
-				\mathcal{R}_i \triangleq [T_{i-1,i}, T_{i,i+1}),
-				\label{eq:decision_region}
-			\end{equation}
-			and we manually define $T_{0,1} \triangleq 0$ and $T_{M^K,M^K+1} \triangleq \infty$.
-Let $f(z \mid \mathcal{H}_i)$ be the conditional probability density function of receiving $z$ under hypothesis $\mathcal{H}_i$.
+This blind spot issue can be mitigated by multi-antenna techniques.} We also define $z \triangleq \lVert \boldsymbol{y} \rVert^2$ as the received signal energy over $N$ primary blocks, and $f(z \mid \mathcal{H}_i)$ as the conditional probability density function of receiving $z$ under hypothesis $\mathcal{H}_i$.
 Correspondingly, $z$ is the sum of $N$ i.i.d.
@@
 
-			On top of \eqref{eq:decision_region} and \eqref{eq:energy_distribution}, we can formulate an equivalent point-to-point discrete memoryless channel from tag input combination alphabet $\mathcal{M^K}$ to received energy level alphabet $\mathcal{M^K}$ as a transition matrix, where the probability of observing energy level $j$ under tag input combination $i$ is\footnote{For simplicity, we assume there exists at least one feasible precoder that produces distinct received energy levels for all tag input combinations.
+			\begin{remark}
+				The backscatter links essentially create a discrete-input continuous-output memoryless channel.
+To further reduce decoding complexity, we apply hard-decision detection and formulate a Discrete Memoryless Thresholding Channel (DMTC), whose capacity is a function of both input distribution and decision thresholds.
+			\end{remark}
+
+			For example, consider the Maximum-Likelihood (ML) detector where the likelihood ratio between hypotheses $\mathcal{H}_i$ and $\mathcal{H}_j$ is \cite{Qian2019}
+			\begin{equation}
+				\Lambda_{i,j}^{\mathrm{ML}}(z) = \frac{f(z \mid \mathcal{H}_i)}{f(z \mid \mathcal{H}_j)} = \left( \frac{\sigma_j^2}{\sigma_i^2} \right)^N \exp \left( \frac{\sigma_i^2 - \sigma_j^2}{\sigma_i^2 \sigma_j^2} z \right),
+				\label{eq:likelihood_ratio}
+			\end{equation}
+			and the corresponding decision rule is
+			\begin{equation}
+				\Lambda_{i,j}^{\mathrm{ML}}(z) \underset{\mathcal{H}_j}{\overset{\mathcal{H}_i}{\lessgtr}} 1 \iff z \underset{\mathcal{H}_j}{\overset{\mathcal{H}_i}{\lessgtr}} T_{i,j}^{\mathrm{ML}},
+				\label{eq:decision_rule}
+			\end{equation}
+			where the detection threshold between $\mathcal{H}_i$ and $\mathcal{H}_j$ is
+			\begin{equation}
+				T_{i,j}^{\mathrm{ML}} \triangleq N \frac{\sigma_i^2 \sigma_j^2}{\sigma_i^2 - \sigma_j^2} \log \frac{\sigma_i^2}{\sigma_j^2},
+				\label{eq:detection_threshold}
+			\end{equation}
+			and we manually define $T_{0,1}^{\mathrm{ML}} \triangleq 0$ and $T_{M^K,M^K+1}^{\mathrm{ML}} \triangleq \infty$.
+Let $\mathcal{T}^{\mathrm{ML}} \triangleq \{T_{0,1}^{\mathrm{ML}},\ldots,T_{M^K,M^K+1}^{\mathrm{ML}}\}$.
+
+			\begin{remark}
+				Although the ML decision threshold set $\mathcal{T}^{\mathrm{ML}}$ is optimal in terms of the likelihood function, it is not necessarily the same with the capacity-achieving threshold set $\mathcal{T}^{\star}$.
+Interestingly, it was shown in \cite{Qian2019b} that $\mathcal{T}^{\mathrm{ML}}$ and $\mathcal{T}^{\star}$ are very close in the single-tag BIBO case.
+			\end{remark}
+
+			For any given threshold set $\mathcal{T} \triangleq \{T_{0,1},\ldots,T_{M^K,M^K+1}\}$, the decision region of hypothesis $\mathcal{H}_i$ is
+			\begin{equation}
+				\mathcal{R}_i \triangleq [T_{i-1,i}, T_{i,i+1}),
+				\label{eq:decision_region}
+			\end{equation}
+			which can be combined with \eqref{eq:energy_distribution} to formulate an equivalent point-to-point discrete memoryless channel from tag input combination alphabet $\mathcal{M^K}$ to received energy level alphabet $\mathcal{M^K}$ as a transition matrix.
+The probability of observing energy level $j$ under tag input combination $i$ is\footnote{For simplicity, we assume there exists at least one feasible precoder that produces distinct received energy levels for all tag input combinations.
 [TODO] Is this necessary?
@@
 			Based on the equivalent point-to-point channel \eqref{eq:point_to_point_channel}, we can compute the marginal probability on all tags and obtain $K$ transition matrices from $\mathcal{M}$ to $\mathcal{M^K}$ that compose a discrete memoryless MAC.
-Mathematically speaking, the probability of observing energy level $j$ when tag $k$ at status $m_k$ is
+Hence, the probability of observing energy level $j$ when tag $k$ at status $m_k$ is
 			\begin{equation}
@@
 
-			In summary, for every possible tag input combination, the expected power of the received signal per block can be evaluated by \eqref{eq:receive_variance}, the energy detection threshold to nearby states can be computed by \eqref{eq:detection_threshold}, the decision region can be retrieved by \eqref{eq:decision_region}, the equivalent point-to-point channel can be obtained by \eqref{eq:energy_distribution} and \eqref{eq:point_to_point_channel}, and the discrete memoryless MAC can be extracted by \eqref{eq:mac}.
+			In summary, for every tag input combination with fixed threshold set, we can obtain the expected power of the received signal per block by \eqref{eq:receive_variance}, the conditional probability density function by \eqref{eq:energy_distribution}, the decision region by \eqref{eq:decision_region}, the equivalent point-to-point channel by \eqref{eq:point_to_point_channel}, and the discrete memoryless MAC by \eqref{eq:mac}.
 		\end{subsection}
@@
 			\end{equation}
-			the marginal information function on $\mathcal{S} \subset \mathcal{K}$ can be written as
+			the marginal information function on $\mathcal{S} \subset \mathcal{K}$ is written as
 			\begin{equation}
@@
 			Once the tag symbol set $\bar{c}_{m_{\mathcal{K}}}$ is successfully decoded, the user can eliminate the backscatter uncertainty and model it within the equivalent primary channel by \eqref{eq:equivalent_primary_channel}.
-From the perspective of primary transmission, the tags adjust the propagation environment in a potentially beneficial manner, and create artificial channel variation within each fading block.
+For primary transmission, the tags adjust the propagation environment in a potentially beneficial manner, and create artificial channel variation within each fading block.
 As such, the ergodic primary rate can be expressed as
@@
 
-	\begin{section}{Tag Input and Precoder Design}
+	\begin{section}{Input Distribution, Decision Region, and Precoder Design}
 		\begin{subsection}{Primary ergodic-secondary sum rate region}
-			To achieve a flexible tradeoff between the primary and backscatter links, we aim to optimize the tag input distribution, decision regions, and precoder to maximize the weighted sum of the ergodic primary rate and the total backscatter rate, under the average transmit power and probability constraints
+			To achieve a flexible tradeoff between the primary and backscatter links, we aim to optimize the tag input distribution, decision region, and precoder to maximize the weighted sum of the ergodic primary rate and the total backscatter rate, under the average transmit power and probability constraints
 			\begin{maxi!}
@@
 			where $\rho \in [0,1]$ denotes the priority of the primary link.
-As problem \eqref{op:rate_region} is not jointly convex over $\boldsymbol{w}$ and $P(c_{\mathcal{K}})$, we propose an Block Coordinate Descent (BCD)-based algorithm that iteratively updates the input distribution, decision region, and precoder, until convergence.
+As problem \eqref{op:rate_region} is not jointly convex over $P(c_{\mathcal{K}})$, $\mathcal{T}$ and $\boldsymbol{w}$, we propose an Block Coordinate Descent (BCD)-based algorithm that iteratively updates the input distribution, decision region, and precoder, until convergence.
 		\end{subsection}
@@
 		\begin{subsection}{Decision region}
-			As indicated by \cite{Qian2019b}, the optimal ML decision regions are very close to the optimal decision regions to problem \eqref{op:weighted_sum_rate}.
+			As indicated by \cite{Qian2019b}, the optimal ML decision regions are very close to the optimal decision regions to problem \eqref{op:rate_region}.
 We can either use \eqref{eq:decision_region} as suboptimal, or take derivative of \eqref{eq:mutual_information} w.r.t.
@@
 
-	\begin{section}{The Single-tag Case}
-		% \begin{figure}[!t]
-		% 	\centering
-		% 	\def\svgwidth{0.9\columnwidth}
-		% 	\import{assets/}{symbiotic_radio.pdf_tex}
-		% 	\caption{A single-user single-tag symbiotic radio system.}
-		% 	\label{fi:symbiotic_radio}
-		% \end{figure}
-		As shown in Fig.~NULL, we propose a single-user (UE) single-tag (TG) symbiotic radio network where the RF signal generated by the single-antenna Access Point (AP) is shared by two coexisting systems.
+	% \begin{section}{The Single-tag Case}
+	% 	% \begin{figure}[!t]
+	% 	% 	\centering
+	% 	% 	\def\svgwidth{0.9\columnwidth}
+	% 	% 	\import{assets/}{symbiotic_radio.pdf_tex}
+	% 	% 	\caption{A single-user single-tag symbiotic radio system.}
+	% 	% 	\label{fi:symbiotic_radio}
+	% 	% \end{figure}
+	% 	As shown in Fig.~NULL, we propose a single-user (UE) single-tag (TG) symbiotic radio network where the RF signal generated by the single-antenna Access Point (AP) is shared by two coexisting systems.
 In the primary AP-UE downlink system, the AP transmits to the single-antenna user.
@@
 At (primary) symbol block $n \in \mathcal{N} \triangleq \{1,\ldots,N\}$, the user simultaneously captures the signal from both primary and secondary links as\footnote{We assume the time difference of arrival from the AP-UE path and the AP-TG-UE path are negligible compared to the symbol period \cite{Guo2019b,Liang2020,Long2020b}.}
-		\begin{equation}
-			y[n] = \sqrt{P} h_{\mathrm{D}} s[n] + \sqrt{\alpha P} h_{\mathrm{C}} c s[n] + w[n],
-		\end{equation}
-		where $P$ is the average transmit power at the AP and $w \sim \mathcal{CN}(0,\sigma^2)$ is the additive white Gaussian noise.
+	% 	\begin{equation}
+	% 		y[n] = \sqrt{P} h_{\mathrm{D}} s[n] + \sqrt{\alpha P} h_{\mathrm{C}} c s[n] + w[n],
+	% 	\end{equation}
+	% 	where $P$ is the average transmit power at the AP and $w \sim \mathcal{CN}(0,\sigma^2)$ is the additive white Gaussian noise.
 We also define $\boldsymbol{y} \triangleq \bigl[y[1],\ldots,y[N]\bigr]^T$.
 
-		\begin{remark}
-			The symbiotic radio network can be regarded as a special case of Multiple Access Channel (MAC) because the AP and the tag simultaneously transmit to the user.
+	% 	\begin{remark}
+	% 		The symbiotic radio network can be regarded as a special case of Multiple Access Channel (MAC) because the AP and the tag simultaneously transmit to the user.
 It is known that Superposition Coding-Successive Interference Cancellation (SC-SIC) with different decoding orders can achieve different vertices of the MAC capacity region \cite{Goldsmith2005}.
@@
 Since the direct channel is typically much stronger than the cascaded channel \cite{Ozdogan2020}, the primary decoding is expected to enjoy a high Signal-to-Interference-and-Noise Ratio (SINR) and the secondary decoding is ideally interference-free.
-		\end{remark}
+	% 	\end{remark}
 
-		\begin{remark}
-			The main difference between symbiotic radio and conventional MAC is that the primary message also reaches the user from the backscatter link.
+	% 	\begin{remark}
+	% 		The main difference between symbiotic radio and conventional MAC is that the primary message also reaches the user from the backscatter link.
 This characteristic inspires one to first decode the tag message, then model its contribution within the equivalent channel during primary decoding (i.e., unify backscatter decoding and channel training), instead of performing SIC.
@@
 [Channel over channel, randomness over randomness]
-		\end{remark}
+	% 	\end{remark}
 
-		\begin{subsection}{Backscatter Transmission}
-			To investigate how backscatter modulation potentially benefits the primary transmission, we first decode the tag symbol $c$ in presence of the interference from the primary message $\boldsymbol{s}$.
+	% 	\begin{subsection}{Backscatter Transmission}
+	% 		To investigate how backscatter modulation potentially benefits the primary transmission, we first decode the tag symbol $c$ in presence of the interference from the primary message $\boldsymbol{s}$.
 In such case, the detection indeed coincides with that of Ambient Backscatter Communications (AmBC) where the signaling from the ambient source is unknown, and the received signal per symbol block follows the CSCG distribution of $y_m[n] \sim \mathcal{CN}(0,\sigma_m^2)$, where
-			\begin{equation}
-				\sigma_m^2 \triangleq \lvert h_{\mathrm{D}} + \sqrt{\alpha} h_{\mathrm{C}} c_m \rvert^2 P + \sigma^2
-				\label{eq:typical_energy}
-			\end{equation}
-			denotes the typical received signal energy over $N$ symbol blocks when the tag is at state $m$, which can be estimated at the user.
+	% 		\begin{equation}
+	% 			\sigma_m^2 \triangleq \lvert h_{\mathrm{D}} + \sqrt{\alpha} h_{\mathrm{C}} c_m \rvert^2 P + \sigma^2
+	% 			\label{eq:typical_energy}
+	% 		\end{equation}
+	% 		denotes the typical received signal energy over $N$ symbol blocks when the tag is at state $m$, which can be estimated at the user.
 For the ease of exposition, we sort $\{\sigma_m^2\}$ in a ascending order by bijective mapping $f \colon m \mapsto i$\footnote{Note that the mapping is not unique and the detection fails when two different constellation points yield the same energy level.} and let $\sigma_i^2 \le \sigma_j^2$ for $i < j$, $i,j \in \mathcal{M}$.
@@
 Following \cite{Qian2019}, the optimal Maximum-Likelihood (ML) detector boils down to the energy detector, and the likelihood ratio between hypotheses $\mathcal{H}_i$ and $\mathcal{H}_j$ is
-			\begin{equation}
-				\Lambda_{i,j}(\boldsymbol{y}) = \frac{f(\boldsymbol{y} \mid \mathcal{H}_i)}{f(\boldsymbol{y} \mid \mathcal{H}_j)} = \left( \frac{\sigma_j^2}{\sigma_i^2} \right)^N \exp \left( \frac{(\sigma_i^2 - \sigma_j^2) z}{\sigma_i^2 \sigma_j^2} \right),
-			\end{equation}
-			where $f(\boldsymbol{y} \mid \mathcal{H}_i)$, $f(\boldsymbol{y} \mid \mathcal{H}_j)$ denote respectively the conditional probability density function of receiving $\boldsymbol{y}$ under hypothesis $\mathcal{H}_i$ and $\mathcal{H}_j$, and $z \triangleq \lVert y \rVert^2$ is the received signal energy over $N$ symbol blocks.
+	% 		\begin{equation}
+	% 			\Lambda_{i,j}(\boldsymbol{y}) = \frac{f(\boldsymbol{y} \mid \mathcal{H}_i)}{f(\boldsymbol{y} \mid \mathcal{H}_j)} = \left( \frac{\sigma_j^2}{\sigma_i^2} \right)^N \exp \left( \frac{(\sigma_i^2 - \sigma_j^2) z}{\sigma_i^2 \sigma_j^2} \right),
+	% 		\end{equation}
+	% 		where $f(\boldsymbol{y} \mid \mathcal{H}_i)$, $f(\boldsymbol{y} \mid \mathcal{H}_j)$ denote respectively the conditional probability density function of receiving $\boldsymbol{y}$ under hypothesis $\mathcal{H}_i$ and $\mathcal{H}_j$, and $z \triangleq \lVert y \rVert^2$ is the received signal energy over $N$ symbol blocks.
 The corresponding decision rule is
-			\begin{equation}
-				\Lambda_{i,j}(\boldsymbol{y}) \underset{H_j}{\overset{H_i}{\lessgtr}} 1 \iff z \underset{H_j}{\overset{H_i}{\lessgtr}} T_{i,j},
-			\end{equation}
-			where the optimal detection threshold is
-			\begin{equation}
-				T_{i,j} \triangleq N \frac{\sigma_i^2 \sigma_j^2}{\sigma_i^2 - \sigma_j^2} \log \frac{\sigma_i^2}{\sigma_j^2},
-				\label{eq:detection_threshold}
-			\end{equation}
-			and the decision region of hypothesis $\mathcal{H}_i$ can be expressed as
-			\begin{equation}
-				\mathcal{R}_i \triangleq [T_{i-1, i}, T_{i, i+1}),
-				\label{eq:decision_region}
-			\end{equation}
-			with $T_{0, 1} \triangleq 0$ and $T_{M, M+1} \triangleq \infty$. On top of this, we define the forward transition probability matrix $\boldsymbol{P} \in \mathbb{R}_{+}^{M \times M}$ as
-			\begin{equation}
-				\boldsymbol{P} \triangleq
-				\begin{bmatrix}
-					p_{1, 1} & \ldots & p_{1, M} \\
-					\vdots & \ddots & \vdots \\
-					p_{M, 1} & \ldots & p_{M, M}
-				\end{bmatrix},
-			\end{equation}
-			where $p_{i,j}$ denotes the transition probability from channel input state $i$ to output state $j$. It can be derived as
-			\begin{equation}
-				p_{i,j} = p(z \in \mathcal{R}_j \mid \mathcal{H}_i) = \int_{\mathcal{R}_j} f(z \mid \mathcal{H}_i) \dd z,
-				\label{eq:transition_probability}
-			\end{equation}
-			where $f(z \mid \mathcal{H}_i)$ is the conditional probability density function of receiving $z$ under hypothesis $\mathcal{H}_i$.
+	% 		\begin{equation}
+	% 			\Lambda_{i,j}(\boldsymbol{y}) \underset{H_j}{\overset{H_i}{\lessgtr}} 1 \iff z \underset{H_j}{\overset{H_i}{\lessgtr}} T_{i,j},
+	% 		\end{equation}
+	% 		where the optimal detection threshold is
+	% 		\begin{equation}
+	% 			T_{i,j} \triangleq N \frac{\sigma_i^2 \sigma_j^2}{\sigma_i^2 - \sigma_j^2} \log \frac{\sigma_i^2}{\sigma_j^2},
+	% 			\label{eq:detection_threshold}
+	% 		\end{equation}
+	% 		and the decision region of hypothesis $\mathcal{H}_i$ can be expressed as
+	% 		\begin{equation}
+	% 			\mathcal{R}_i \triangleq [T_{i-1, i}, T_{i, i+1}),
+	% 			\label{eq:decision_region_}
+	% 		\end{equation}
+	% 		with $T_{0, 1} \triangleq 0$ and $T_{M, M+1} \triangleq \infty$. On top of this, we define the forward transition probability matrix $\boldsymbol{P} \in \mathbb{R}_{+}^{M \times M}$ as
+	% 		\begin{equation}
+	% 			\boldsymbol{P} \triangleq
+	% 			\begin{bmatrix}
+	% 				p_{1, 1} & \ldots & p_{1, M} \\
+	% 				\vdots & \ddots & \vdots \\
+	% 				p_{M, 1} & \ldots & p_{M, M}
+	% 			\end{bmatrix},
+	% 		\end{equation}
+	% 		where $p_{i,j}$ denotes the transition probability from channel input state $i$ to output state $j$. It can be derived as
+	% 		\begin{equation}
+	% 			p_{i,j} = p(z \in \mathcal{R}_j \mid \mathcal{H}_i) = \int_{\mathcal{R}_j} f(z \mid \mathcal{H}_i) \dd z,
+	% 			\label{eq:transition_probability}
+	% 		\end{equation}
+	% 		where $f(z \mid \mathcal{H}_i)$ is the conditional probability density function of receiving $z$ under hypothesis $\mathcal{H}_i$.
 Since $z$ follows chi-squared distribution with $2N$ degrees of freedom, it holds that
-			\begin{equation}
-				f(z \mid \mathcal{H}_i) = \frac{z^{N-1} e^{-z/\sigma_i^2}}{\sigma_i^{2N} \Gamma(N)},
-				\label{eq:conditional_pdf}
-			\end{equation}
-			where $\Gamma(\cdot)$ is the gamma function.
+	% 		\begin{equation}
+	% 			f(z \mid \mathcal{H}_i) = \frac{z^{N-1} e^{-z/\sigma_i^2}}{\sigma_i^{2N} \Gamma(N)},
+	% 			\label{eq:conditional_pdf}
+	% 		\end{equation}
+	% 		where $\Gamma(\cdot)$ is the gamma function.
 To summarize, with the CSI of the direct and cascaded links, the typical energy of the received signal can be estimated by \eqref{eq:typical_energy}, the energy detection threshold can be computed by \eqref{eq:detection_threshold}, the decision region can be retrieved by \eqref{eq:decision_region}, and the forward transition matrix $\boldsymbol{P}$ can be calculated by substituting \eqref{eq:conditional_pdf} into \eqref{eq:transition_probability}.
 
-			We then investigate the achievable rate of the backscatter link.
+	% 		We then investigate the achievable rate of the backscatter link.
 Denote the tag input probability mass function as $\boldsymbol{r} = [r_1,\ldots,r_M]^T \in \mathbb{R}_+^{M \times 1}$ where $r_m$ is the probability to transmit symbol $c_m$ [strictly positive?].
 For a given input distribution $\boldsymbol{r}$ and forward transition matrix $\boldsymbol{P}$, the achievable backscatter rate can be written as
-			\begin{equation}
-				R_c = \max_{\boldsymbol{Q} \ge 0} \sum_{i \in \mathcal{M}} \sum_{j \in \mathcal{M}} r_i p_{i,j} \log_2 \frac{q_{j, i}}{r_i} \ [\si{bpcu}],
-				\label{eq:secondary_rate}
-			\end{equation}
-			where $\boldsymbol{Q} \in \mathbb{R}_{+}^{M \times M}$ is the backward transition probability matrix
-			\begin{equation}
-				\boldsymbol{Q} \triangleq
-				\begin{bmatrix}
-					q_{1, 1} & \ldots & q_{1, M} \\
-					\vdots & \ddots & \vdots \\
-					q_{M, 1} & \ldots & q_{M, M}
-				\end{bmatrix},
-			\end{equation}
-			and $q_{j, i}$ denotes the transition probability from channel output state $j$ to input state $i$.
-		\end{subsection}
+	% 		\begin{equation}
+	% 			R_c = \max_{\boldsymbol{Q} \ge 0} \sum_{i \in \mathcal{M}} \sum_{j \in \mathcal{M}} r_i p_{i,j} \log_2 \frac{q_{j, i}}{r_i} \ [\si{bpcu}],
+	% 			\label{eq:secondary_rate}
+	% 		\end{equation}
+	% 		where $\boldsymbol{Q} \in \mathbb{R}_{+}^{M \times M}$ is the backward transition probability matrix
+	% 		\begin{equation}
+	% 			\boldsymbol{Q} \triangleq
+	% 			\begin{bmatrix}
+	% 				q_{1, 1} & \ldots & q_{1, M} \\
+	% 				\vdots & \ddots & \vdots \\
+	% 				q_{M, 1} & \ldots & q_{M, M}
+	% 			\end{bmatrix},
+	% 		\end{equation}
+	% 		and $q_{j, i}$ denotes the transition probability from channel output state $j$ to input state $i$.
+	% 	\end{subsection}
 
-		\begin{subsection}{Legacy Transmission}
-			Once the backscattered symbol is successfully recovered, it is combined with the cascaded channel to eliminate the uncertainty of the AP-TG-UE path and assist the legacy transmission.
+	% 	\begin{subsection}{Legacy Transmission}
+	% 		Once the backscattered symbol is successfully recovered, it is combined with the cascaded channel to eliminate the uncertainty of the AP-TG-UE path and assist the legacy transmission.
 Therefore, the received signal at symbol block $n$ is essentially
-			\begin{equation}
-				y[n] = \sqrt{P} (h_{\mathrm{D}} + \sqrt{\alpha} h_{\mathrm{C}} c) s[n] + w[n] \triangleq \sqrt{P} h_{\mathrm{E}}(c) s + w[n],
-			\end{equation}
-			which is reminiscent of an IRS-aided point-to-point transmission with an equivalent channel of
-			\begin{equation}
-				h_{\mathrm{E}}(c) \triangleq h_{\mathrm{D}} + \sqrt{\alpha} h_{\mathrm{C}} c.
-			\end{equation}
-			For primary transmission, backscatter modulation creates an artificial fast fading within each fading block, and AP can obtain the equivalent CSI distribution for any given tag input probability mass function $\boldsymbol{r}$.
+	% 		\begin{equation}
+	% 			y[n] = \sqrt{P} (h_{\mathrm{D}} + \sqrt{\alpha} h_{\mathrm{C}} c) s[n] + w[n] \triangleq \sqrt{P} h_{\mathrm{E}}(c) s + w[n],
+	% 		\end{equation}
+	% 		which is reminiscent of an IRS-aided point-to-point transmission with an equivalent channel of
+	% 		\begin{equation}
+	% 			h_{\mathrm{E}}(c) \triangleq h_{\mathrm{D}} + \sqrt{\alpha} h_{\mathrm{C}} c.
+	% 		\end{equation}
+	% 		For primary transmission, backscatter modulation creates an artificial fast fading within each fading block, and AP can obtain the equivalent CSI distribution for any given tag input probability mass function $\boldsymbol{r}$.
 Therefore, the ergodic capacity of primary transmission within each symbol block is \cite{Tse2005}
-			\begin{align}
-				R_s
-				& = \mathbb{E}_c \bigl[ \log_2 (1 + \gamma \lvert h_{\mathrm{E}}(c) \rvert^2) \bigr] \nonumber \\
-				& = \sum_{i \in \mathcal{M}} r_i \log_2 \bigl( 1 + \gamma \lvert h_{\mathrm{D}} + \sqrt{\alpha} h_{\mathrm{C}} c_i \rvert^2 \bigr) \ [\si{bps/Hz}],
-				\label{eq:primary_rate}
-			\end{align}
-			where $\gamma \triangleq P / \sigma^2$ is the average transmit Signal-to-Noise Ratio (SNR).
+	% 		\begin{align}
+	% 			R_s
+	% 			& = \mathbb{E}_c \bigl[ \log_2 (1 + \gamma \lvert h_{\mathrm{E}}(c) \rvert^2) \bigr] \nonumber \\
+	% 			& = \sum_{i \in \mathcal{M}} r_i \log_2 \bigl( 1 + \gamma \lvert h_{\mathrm{D}} + \sqrt{\alpha} h_{\mathrm{C}} c_i \rvert^2 \bigr) \ [\si{bps/Hz}],
+	% 			\label{eq:primary_rate}
+	% 		\end{align}
+	% 		where $\gamma \triangleq P / \sigma^2$ is the average transmit Signal-to-Noise Ratio (SNR).
 It can be concluded that the achievable rate of both primary and secondary links depend on the tag input distribution.
-		\end{subsection}
-		\label{se:system_model}
+	% 	\end{subsection}
+	% 	\label{se:system_model}
 
-		\begin{subsection}{Achievable rate region}
-			To achieve a flexible tradeoff between the backscatter and legacy links, we aims to optimize the tag input probability mass function, under $M$-PSK modulation, to maximize the weighted sum of the primary and secondary rates subject to the sum-probability constraint
-			\begin{maxi!}
-				{\scriptstyle{\boldsymbol{r} \ge 0}}{\rho R_s + (1 - \rho) R_c}{\label{op:weighted_sum_rate}}{\label{ob:weighted_sum_rate}}
-				\addConstraint{\sum_{i \in \mathcal{M}} r_i}{=1,}{\label{co:sum_probability}}
-			\end{maxi!}
-			where $\rho \in [0, 1]$ is the weight factor. By substituting \eqref{eq:secondary_rate} and \eqref{eq:primary_rate} into \eqref{ob:weighted_sum_rate}, the problem expands to
-			\begin{maxi!}
-				{\scriptstyle{\boldsymbol{r} \ge 0, \boldsymbol{Q} \ge 0}}{\rho \sum_{i \in \mathcal{M}} r_i \log_2 \bigl( 1 + \gamma \lvert h_{\mathrm{D}} + \sqrt{\alpha} h_{\mathrm{C}} c_i \rvert^2 \bigr) \nonumber}{}{}
-				\breakObjective{+ (1 - \rho) \sum_{i \in \mathcal{M}} \sum_{j \in \mathcal{M}} r_i p_{i,j} \log_2 \frac{q_{j, i}}{r_i}}{\label{ob:weighted_sum_rate_expanded}}
-				\addConstraint{\sum_{i \in \mathcal{M}} r_i}{=1.}{}
-			\end{maxi!}
-			Similar to the Blahut-Arimoto algorithm \cite{Arimoto1972,Blahut1972}, we optimize $\boldsymbol{r}$ and $\boldsymbol{Q}$ alternatively to obtain the local optimal tag input distribution and the corresponding weighted sum-rate.
-			\begin{theorem}
-				For any valid tag input probability mass function $\boldsymbol{r}$ [$\boldsymbol{r} > \boldsymbol{0}$?], the optimal backward transition probability from channel output state $j$ to input state $i$ follows Bayes' Theorem as
-				\begin{equation}
-					q_{j, i}^{\star} = \frac{r_i p_{i,j}}{\sum_{i'} r_{i'} p_{i', j}}.
-					\label{eq:backward_transition}
-				\end{equation}
-				\label{th:backward_transition}
-			\end{theorem}
-			\begin{proof}
-				Please refer to Appendix~\ref{ap:backward_transition}.
-			\end{proof}
-			\begin{theorem}
-				For any valid backward transition probability $\boldsymbol{Q}$ [$\boldsymbol{Q} \ge 0$?], the optimal tag input probability mass function is given by
-				\begin{equation}
-					r_i = \frac{\bigl( 1 + \gamma \lvert h_{\mathrm{D}} + \sqrt{\alpha} h_{\mathrm{C}} c_i \rvert^2 \bigr)^{\rho / (1 - \rho)} \prod_{j \in \mathcal{M}} q_{j, i}^{p_{i,j}}}{\sum_{i' \in \mathcal{M}} \bigl( 1 + \gamma \lvert h_{\mathrm{D}} + \sqrt{\alpha} h_{\mathrm{C}} c_{i'} \rvert^2 \bigr)^{\rho / (1 - \rho)} \prod_{j \in \mathcal{M}} q_{j, i'}^{p_{i', j}}}.
-					\label{eq:input_distribution}
-				\end{equation}
-				\label{th:input_distribution}
-			\end{theorem}
-			\begin{proof}
-				Please refer to Appendix~\ref{ap:input_distribution}.
-			\end{proof}
-			\begin{proposition}
-				For any feasible initial point [constellation subset], the Algorithm is guaranteed to converge to the global optimal of problem \eqref{op:weighted_sum_rate} and achieve the maximum weighted-sum rate.
-			\end{proposition}
-			\begin{proof}
-				The proof is similar to that in \cite[Chapter~9.3]{Yeung2008} and omitted here.
-			\end{proof}
-		\end{subsection}
-	\end{section}
+	% 	\begin{subsection}{Achievable rate region}
+	% 		To achieve a flexible tradeoff between the backscatter and legacy links, we aims to optimize the tag input probability mass function, under $M$-PSK modulation, to maximize the weighted sum of the primary and secondary rates subject to the sum-probability constraint
+	% 		\begin{maxi!}
+	% 			{\scriptstyle{\boldsymbol{r} \ge 0}}{\rho R_s + (1 - \rho) R_c}{\label{op:weighted_sum_rate}}{\label{ob:weighted_sum_rate}}
+	% 			\addConstraint{\sum_{i \in \mathcal{M}} r_i}{=1,}{\label{co:sum_probability}}
+	% 		\end{maxi!}
+	% 		where $\rho \in [0, 1]$ is the weight factor. By substituting \eqref{eq:secondary_rate} and \eqref{eq:primary_rate} into \eqref{ob:weighted_sum_rate}, the problem expands to
+	% 		\begin{maxi!}
+	% 			{\scriptstyle{\boldsymbol{r} \ge 0, \boldsymbol{Q} \ge 0}}{\rho \sum_{i \in \mathcal{M}} r_i \log_2 \bigl( 1 + \gamma \lvert h_{\mathrm{D}} + \sqrt{\alpha} h_{\mathrm{C}} c_i \rvert^2 \bigr) \nonumber}{}{}
+	% 			\breakObjective{+ (1 - \rho) \sum_{i \in \mathcal{M}} \sum_{j \in \mathcal{M}} r_i p_{i,j} \log_2 \frac{q_{j, i}}{r_i}}{\label{ob:weighted_sum_rate_expanded}}
+	% 			\addConstraint{\sum_{i \in \mathcal{M}} r_i}{=1.}{}
+	% 		\end{maxi!}
+	% 		Similar to the Blahut-Arimoto algorithm \cite{Arimoto1972,Blahut1972}, we optimize $\boldsymbol{r}$ and $\boldsymbol{Q}$ alternatively to obtain the local optimal tag input distribution and the corresponding weighted sum-rate.
+	% 		\begin{theorem}
+	% 			For any valid tag input probability mass function $\boldsymbol{r}$ [$\boldsymbol{r} > \boldsymbol{0}$?], the optimal backward transition probability from channel output state $j$ to input state $i$ follows Bayes' Theorem as
+	% 			\begin{equation}
+	% 				q_{j, i}^{\star} = \frac{r_i p_{i,j}}{\sum_{i'} r_{i'} p_{i', j}}.
+	% 				\label{eq:backward_transition}
+	% 			\end{equation}
+	% 			\label{th:backward_transition}
+	% 		\end{theorem}
+	% 		\begin{proof}
+	% 			Please refer to Appendix~\ref{ap:backward_transition}.
+	% 		\end{proof}
+	% 		\begin{theorem}
+	% 			For any valid backward transition probability $\boldsymbol{Q}$ [$\boldsymbol{Q} \ge 0$?], the optimal tag input probability mass function is given by
+	% 			\begin{equation}
+	% 				r_i = \frac{\bigl( 1 + \gamma \lvert h_{\mathrm{D}} + \sqrt{\alpha} h_{\mathrm{C}} c_i \rvert^2 \bigr)^{\rho / (1 - \rho)} \prod_{j \in \mathcal{M}} q_{j, i}^{p_{i,j}}}{\sum_{i' \in \mathcal{M}} \bigl( 1 + \gamma \lvert h_{\mathrm{D}} + \sqrt{\alpha} h_{\mathrm{C}} c_{i'} \rvert^2 \bigr)^{\rho / (1 - \rho)} \prod_{j \in \mathcal{M}} q_{j, i'}^{p_{i', j}}}.
+	% 				\label{eq:input_distribution}
+	% 			\end{equation}
+	% 			\label{th:input_distribution}
+	% 		\end{theorem}
+	% 		\begin{proof}
+	% 			Please refer to Appendix~\ref{ap:input_distribution}.
+	% 		\end{proof}
+	% 		\begin{proposition}
+	% 			For any feasible initial point [constellation subset], the Algorithm is guaranteed to converge to the global optimal of problem \eqref{op:weighted_sum_rate} and achieve the maximum weighted-sum rate.
+	% 		\end{proposition}
+	% 		\begin{proof}
+	% 			The proof is similar to that in \cite[Chapter~9.3]{Yeung2008} and omitted here.
+	% 		\end{proof}
+	% 	\end{subsection}
+	% \end{section}
 
-	\begin{section}{OFDM}
-		Due to the constraint of energy detection, with single-antenna tags and reader, at most one AmBC tag can be decoded at a time and accurate detection requires repetition coding over multiple time/frequency blocks to mitigate the impact of primary symbols.
+	% \begin{section}{OFDM}
+	% 	Due to the constraint of energy detection, with single-antenna tags and reader, at most one AmBC tag can be decoded at a time and accurate detection requires repetition coding over multiple time/frequency blocks to mitigate the impact of primary symbols.
 Here we consider frequency-independent tag reflection and schedule one tag per OFDM symbol.
 
-		At OFDM symbol $r$, tag $l$ modulates its own information over all $N$ subcarriers while the remaining tags may operate in the cooperative (quantized IRS) mode.
+	% 	At OFDM symbol $r$, tag $l$ modulates its own information over all $N$ subcarriers while the remaining tags may operate in the cooperative (quantized IRS) mode.
 Channel frequency response at subband $n$ and block $r$
-		Received signal at OFDM symbol $r$ and subband $n$ is
-		\begin{equation}
-			y_n[r] = \sqrt{P} h_{\mathrm{E}}[r] s_n[r] + \sqrt{\alpha P} h_{\mathrm{C},l} c_l s_n[r] + w_n[r],
-		\end{equation}
-		where $h_{\mathrm{E}}[r] \triangleq \sum_{l' \ne l} h_{\mathrm{C},l'} c_{l'}^\star$ and $c_l$ is the symbol of tag $l$.
+	% 	Received signal at OFDM symbol $r$ and subband $n$ is
+	% 	\begin{equation}
+	% 		y_n[r] = \sqrt{P} h_{\mathrm{E}}[r] s_n[r] + \sqrt{\alpha P} h_{\mathrm{C},l} c_l s_n[r] + w_n[r],
+	% 	\end{equation}
+	% 	where $h_{\mathrm{E}}[r] \triangleq \sum_{l' \ne l} h_{\mathrm{C},l'} c_{l'}^\star$ and $c_l$ is the symbol of tag $l$.
 Apparently $y_n[r] \sim \mathcal{CN}(0,\sigma_n^2[r])$ with $\sigma_n^2[r] \triangleq \lvert h_{\mathrm{E}}[r] + \sqrt{\alpha} h_{\mathrm{C},l} c_l \rvert^2 P + \sigma^2$.
 Define $\boldsymbol{y}[r] \triangleq [y_1[r],\ldots,y_N[r]]^T$ and we can do energy detection over $N$ subcarriers.
-	\end{section}
+	% \end{section}
 
-	\begin{section}{Multi-Tag Case}
-		In the $K$-tag scenario, the received signal at symbol block $n$ is
-		\begin{equation}
-			y[n] = \sqrt{P} h_{\mathrm{D}} s[n] + \sum_k \sqrt{\alpha_k} h_{\mathrm{C},k} c_k \sqrt{P} s[n] + w[n].
-		\end{equation}
+	% \begin{section}{Multi-Tag Case}
+	% 	In the $K$-tag scenario, the received signal at symbol block $n$ is
+	% 	\begin{equation}
+	% 		y[n] = \sqrt{P} h_{\mathrm{D}} s[n] + \sum_k \sqrt{\alpha_k} h_{\mathrm{C},k} c_k \sqrt{P} s[n] + w[n].
+	% 	\end{equation}
 
-		On the one hand, we can compute the \emph{sum-rate} of the tags and characterize the (ergodic) primary-secondary capacity region by adjusting weight $\rho$. The weighted sum-rate can be expressed as
-		\begin{align}
-			J_1
-			& = \rho \mathbb{E}_{\boldsymbol{c}} \left[ \log_2 \left( 1 + \gamma \lvert h_{\mathrm{D}} + \sum_k \sqrt{\alpha_k} h_{\mathrm{C},k} c_k \rvert \right) \right] + (1 - \rho) R_c\\
-			& = \rho \sum_{i_1,\dots,i_K \in \mathcal{M}} \prod_{k \in \mathcal{K}} r_{k,i_k} \log_2 \left( 1 + \gamma \lvert h_{\mathrm{D}} + \sum_{k' \in \mathcal{K}} \sqrt{\alpha_{k'}} h_{\mathrm{C},k'} c_{k',i_{k'}} \rvert^2 \right)\\
-			& \quad + (1 - \rho) \sum_{i \in \mathcal{M}} \sum_{j \in \mathcal{M}^K} \sum_{k \in \mathcal{K}} r_{k,i} p_{i,j} \log \frac{q_{j,i}}{r_{k,i}}.
-		\end{align}
-		In this case, although we can independently maximize the primary/secondary rate in closed form (resp.
+	% 	On the one hand, we can compute the \emph{sum-rate} of the tags and characterize the (ergodic) primary-secondary capacity region by adjusting weight $\rho$.
+The weighted sum-rate can be expressed as
+	% 	\begin{align}
+	% 		J_1
+	% 		& = \rho \mathbb{E}_{\boldsymbol{c}} \left[ \log_2 \left( 1 + \gamma \lvert h_{\mathrm{D}} + \sum_k \sqrt{\alpha_k} h_{\mathrm{C},k} c_k \rvert \right) \right] + (1 - \rho) R_c\\
+	% 		& = \rho \sum_{i_1,\dots,i_K \in \mathcal{M}} \prod_{k \in \mathcal{K}} r_{k,i_k} \log_2 \left( 1 + \gamma \lvert h_{\mathrm{D}} + \sum_{k' \in \mathcal{K}} \sqrt{\alpha_{k'}} h_{\mathrm{C},k'} c_{k',i_{k'}} \rvert^2 \right)\\
+	% 		& \quad + (1 - \rho) \sum_{i \in \mathcal{M}} \sum_{j \in \mathcal{M}^K} \sum_{k \in \mathcal{K}} r_{k,i} p_{i,j} \log \frac{q_{j,i}}{r_{k,i}}.
+	% 	\end{align}
+	% 	In this case, although we can independently maximize the primary/secondary rate in closed form (resp.
 quantized IRS and multi-user Blahut-Arimoto), the joint form can be tricky due to the $K$-product term.
@@
 
-		On the other hand, we can compute the rate region of the user and $K$ tags.
+	% 	On the other hand, we can compute the rate region of the user and $K$ tags.
 However, the capacity region of discrete MAC remains unknown.
@@
 The difficulty is that the optimization is performed over $K$-dimensional array $\mathbb{R}^{\underbrace{M \times \ldots \times M}_{K}}$.
-	\end{section}
+	% \end{section}
 
-	\begin{appendix}
-		\begin{subsection}{Proof of Theorem~\ref{th:backward_transition}}
-			Denote the objective function \eqref{ob:weighted_sum_rate_expanded} as $R(\boldsymbol{r}, \boldsymbol{Q})$.
+	% \begin{appendix}
+	% 	\begin{subsection}{Proof of Theorem~\ref{th:backward_transition}}
+	% 		Denote the objective function \eqref{ob:weighted_sum_rate_expanded} as $R(\boldsymbol{r}, \boldsymbol{Q})$.
 Let $w_j \triangleq \sum_{i'} r_{i'} p_{i', j}$ and rearrange \eqref{eq:backward_transition} as
-			\begin{equation}
-				w_j q_{j, i}^{\star} = r_i p_{i,j}.
-			\end{equation}
-			Therefore,
-			\begin{align}
-				R(\boldsymbol{r}, \boldsymbol{Q}^{\star}) - R(\boldsymbol{r}, \boldsymbol{Q})
-				& = (1 - \rho) \sum_{i \in \mathcal{M}} \sum_{j \in \mathcal{M}} r_i p_{i,j} \log_2 \frac{q_{j, i}^{\star}}{q_{j, i}} \nonumber \\
-				& = (1 - \rho) \sum_{i \in \mathcal{M}} \sum_{j \in \mathcal{M}} w_j q_{j, i}^{\star} \log_2 \frac{q_{j, i}^{\star}}{q_{j, i}} \nonumber \\
-				& = (1 - \rho) \sum_{j \in \mathcal{M}} w_j \sum_{i \in \mathcal{M}} q_{j, i}^{\star} \log_2 \frac{q_{j, i}^{\star}}{q_{j, i}} \nonumber \\
-				& = (1 - \rho) \sum_{j \in \mathcal{M}} w_j \infdiv{q_{j, i}^{\star}}{q_{j, i}} \nonumber \\
-				& \ge 0,
-			\end{align}
-			with equality iff $\boldsymbol{Q} = \boldsymbol{Q}^{\star}$.
-			\label{ap:backward_transition}
-		\end{subsection}
-		\begin{subsection}{Proof of Theorem~\ref{th:input_distribution}}
-			We employ the method of Lagrange multipliers, temporally ignore the constraint $\boldsymbol{r} \ge 0$, and assume all logarithms are of base $e$. Define the Lagrangian function as
-			\begin{align}
-				J
-				& = \rho \sum_{i \in \mathcal{M}} r_i \log \bigl( 1 + \gamma \lvert h_{\mathrm{D}} + \sqrt{\alpha} h_{\mathrm{C}} c_i \rvert^2 \bigr) \nonumber \\
-				& \quad + (1 - \rho) \sum_{i \in \mathcal{M}} \sum_{j \in \mathcal{M}} r_i p_{i,j} \log \frac{q_{j, i}}{r_i} + \lambda \left( 1 - \sum_{i \in \mathcal{M}} r_i \right),
-			\end{align}
-			where $\lambda$ is the Lagrange multiplier associated with the sum-probability constraint. Differentiating $J$ with respect to $r_i$ gives
-			\begin{align}
-				\pdv{J}{r_i}
-				& = \rho \log \bigl( 1 + \gamma \lvert h_{\mathrm{D}} + \sqrt{\alpha} h_{\mathrm{C}} c_i \rvert^2 \bigr) \\
-				& \quad + (1 - \rho) \left( \sum_{j \in \mathcal{M}} p_{i,j} \log q_{j, i} - \log r_i - 1 \right),
-			\end{align}
-			and setting $\pdv*{J}{r_i} = 0$ suggests
-			\begin{equation}
-				r_i = e^{ -(\frac{\lambda}{1 - \rho} + 1)} \bigl( 1 + \gamma \lvert h_{\mathrm{D}} + \sqrt{\alpha} h_{\mathrm{C}} c_i \rvert^2 \bigr)^{\rho / (1 - \rho)} \prod_{j \in \mathcal{M}} q_{j, i}^{p_{i,j}}.
-			\end{equation}
-			By considering $\sum_{i \in \mathcal{M}} r_i = 1$, we can eliminate $\lambda$ and obtain the optimal tag input distribution as \eqref{eq:input_distribution}.
-			\label{ap:input_distribution}
-		\end{subsection}
-	\end{appendix}
+	% 		\begin{equation}
+	% 			w_j q_{j, i}^{\star} = r_i p_{i,j}.
+	% 		\end{equation}
+	% 		Therefore,
+	% 		\begin{align}
+	% 			R(\boldsymbol{r}, \boldsymbol{Q}^{\star}) - R(\boldsymbol{r}, \boldsymbol{Q})
+	% 			& = (1 - \rho) \sum_{i \in \mathcal{M}} \sum_{j \in \mathcal{M}} r_i p_{i,j} \log_2 \frac{q_{j, i}^{\star}}{q_{j, i}} \nonumber \\
+	% 			& = (1 - \rho) \sum_{i \in \mathcal{M}} \sum_{j \in \mathcal{M}} w_j q_{j, i}^{\star} \log_2 \frac{q_{j, i}^{\star}}{q_{j, i}} \nonumber \\
+	% 			& = (1 - \rho) \sum_{j \in \mathcal{M}} w_j \sum_{i \in \mathcal{M}} q_{j, i}^{\star} \log_2 \frac{q_{j, i}^{\star}}{q_{j, i}} \nonumber \\
+	% 			& = (1 - \rho) \sum_{j \in \mathcal{M}} w_j \infdiv{q_{j, i}^{\star}}{q_{j, i}} \nonumber \\
+	% 			& \ge 0,
+	% 		\end{align}
+	% 		with equality iff $\boldsymbol{Q} = \boldsymbol{Q}^{\star}$.
+	% 		\label{ap:backward_transition}
+	% 	\end{subsection}
+	% 	\begin{subsection}{Proof of Theorem~\ref{th:input_distribution}}
+	% 		We employ the method of Lagrange multipliers, temporally ignore the constraint $\boldsymbol{r} \ge 0$, and assume all logarithms are of base $e$. Define the Lagrangian function as
+	% 		\begin{align}
+	% 			J
+	% 			& = \rho \sum_{i \in \mathcal{M}} r_i \log \bigl( 1 + \gamma \lvert h_{\mathrm{D}} + \sqrt{\alpha} h_{\mathrm{C}} c_i \rvert^2 \bigr) \nonumber \\
+	% 			& \quad + (1 - \rho) \sum_{i \in \mathcal{M}} \sum_{j \in \mathcal{M}} r_i p_{i,j} \log \frac{q_{j, i}}{r_i} + \lambda \left( 1 - \sum_{i \in \mathcal{M}} r_i \right),
+	% 		\end{align}
+	% 		where $\lambda$ is the Lagrange multiplier associated with the sum-probability constraint. Differentiating $J$ with respect to $r_i$ gives
+	% 		\begin{align}
+	% 			\pdv{J}{r_i}
+	% 			& = \rho \log \bigl( 1 + \gamma \lvert h_{\mathrm{D}} + \sqrt{\alpha} h_{\mathrm{C}} c_i \rvert^2 \bigr) \\
+	% 			& \quad + (1 - \rho) \left( \sum_{j \in \mathcal{M}} p_{i,j} \log q_{j, i} - \log r_i - 1 \right),
+	% 		\end{align}
+	% 		and setting $\pdv*{J}{r_i} = 0$ suggests
+	% 		\begin{equation}
+	% 			r_i = e^{ -(\frac{\lambda}{1 - \rho} + 1)} \bigl( 1 + \gamma \lvert h_{\mathrm{D}} + \sqrt{\alpha} h_{\mathrm{C}} c_i \rvert^2 \bigr)^{\rho / (1 - \rho)} \prod_{j \in \mathcal{M}} q_{j, i}^{p_{i,j}}.
+	% 		\end{equation}
+	% 		By considering $\sum_{i \in \mathcal{M}} r_i = 1$, we can eliminate $\lambda$ and obtain the optimal tag input distribution as \eqref{eq:input_distribution}.
+	% 		\label{ap:input_distribution}
+	% 	\end{subsection}
+	% \end{appendix}
 

### 2021-12-13 main.tex
:pencil: Update energy detection

@@
 \usepackage{xcolor}
+\usepackage[acronym]{glossaries-extra}
 \usepackage[T1]{fontenc}
@@
 \algrenewcommand{\algorithmicuntil}{\textbf{Until}}
+
+\setabbreviationstyle[acronym]{long-short}
+
+\newacronym{kkt}{KKT}{Karush–Kuhn–Tucker}
 
@@
 			\end{equation}
-			which denotes the expectation of the received power per primary block under tag modulation index set $m_{\mathcal{K}}$, and can be numerically evaluated based on the precoder, tag, channel, and noise knowledge.
-For the ease of exposition, we sort all possible $\sigma_{m_{\mathcal{K}}}^2$ in ascending order by a one-to-one mapping $m_{\mathcal{K}} \mapsto i$, denote the hypothesis that the tag input combination at status $i$ as $\mathcal{H}_i$, and define $\sigma_i^2 \le \sigma_j^2$ for $i < j$, $i,j \in \mathcal{M^K} \triangleq \{1,\ldots,M^K\}$.\footnote{When more than one modulation index sets yield the same energy level, the mapping is not unique and the detection fails to separate them.
-This blind spot issue can be mitigated by multi-antenna techniques.} We also define $z \triangleq \lVert \boldsymbol{y} \rVert^2$ as the received signal energy over $N$ primary blocks, and $f(z \mid \mathcal{H}_i)$ as the conditional probability density function of receiving $z$ under hypothesis $\mathcal{H}_i$.
+			which denotes the expectation of the received power per primary block under tag modulation index set $m_{\mathcal{K}}$.
+			% It can be numerically evaluated based on the precoder, tag, channel, and noise knowledge.
+			For the ease of exposition, we denote the hypothesis that the tag input combination at status $i \in \mathcal{M^K} \triangleq \{1,\ldots,M^K\}$ as $\mathcal{H}_i$, sort $\{\sigma_{m_{\mathcal{K}}}^2\}$ in ascending order by a one-to-one mapping $m_{\mathcal{K}} \mapsto i$,\footnote{When more than one modulation index sets yield the same energy level, the mapping is not unique and the detection fails to separate them.
+This blind spot issue can be mitigated by multi-antenna techniques.} define the received signal energy over $N$ primary blocks as $z \triangleq \lVert \boldsymbol{y} \rVert^2$, and let $f(z \mid \mathcal{H}_i)$ be the conditional probability density function of receiving $z$ under hypothesis $\mathcal{H}_i$.
 Correspondingly, $z$ is the sum of $N$ i.i.d.
-exponential variables each with mean $\sigma_i^2$, and thus follows Erlang distribution with shape $N$ and scale $\sigma_i^2$
+exponential variables each with mean $\sigma_i^2$, and the conditional probability density function follows Erlang distribution with shape $N$ and scale $\sigma_i^2$ as
 			\begin{equation}
@@
 			\begin{remark}
-				The backscatter links essentially create a discrete-input continuous-output memoryless channel.
-To further reduce decoding complexity, we apply hard-decision detection and formulate a Discrete Memoryless Thresholding Channel (DMTC), whose capacity is a function of both input distribution and decision thresholds.
+				The backscatter links essentially form a discrete-input continuous-output memoryless channel.
+To further reduce decoding complexity, we apply hard-decision detection and construct a Discrete Memoryless Thresholding Channel (DMTC), whose capacity is a function of both input distribution and decision thresholds \cite{Nguyen2018}.
 			\end{remark}
 
-			For example, consider the Maximum-Likelihood (ML) detector where the likelihood ratio between hypotheses $\mathcal{H}_i$ and $\mathcal{H}_j$ is \cite{Qian2019}
+			Denote the decision region of hypothesis $\mathcal{H}_i$ as
 			\begin{equation}
-				\Lambda_{i,j}^{\mathrm{ML}}(z) = \frac{f(z \mid \mathcal{H}_i)}{f(z \mid \mathcal{H}_j)} = \left( \frac{\sigma_j^2}{\sigma_i^2} \right)^N \exp \left( \frac{\sigma_i^2 - \sigma_j^2}{\sigma_i^2 \sigma_j^2} z \right),
+				\mathcal{R}_i \triangleq [T_{i-1,i}, T_{i,i+1}),
+				\label{eq:decision_region}
+			\end{equation}
+			where $T_{i-1,i}$ is the decision threshold between $\mathcal{H}_{i-1}$ and $\mathcal{H}_i$, and $T_{i,i+1}$ is the decision threshold between $\mathcal{H}_i$ and $\mathcal{H}_{i+1}$.
+We also define $T_{0,1} \triangleq 0$, $T_{M^K,M^K+1} \triangleq \infty$, and $\mathcal{T} \triangleq \{T_{0,1},\ldots,T_{M^K,M^K+1}\}$.
+
+			Consider the Maximum-Likelihood (ML) detector for example. The likelihood ratio between hypotheses $\mathcal{H}_i$ and $\mathcal{H}_{i'}$ is \cite{Qian2019}
+			\begin{equation}
+				\Lambda_{i,{i'}}^{\mathrm{ML}}(z) = \frac{f(z \mid \mathcal{H}_i)}{f(z \mid \mathcal{H}_{i'})} = \left( \frac{\sigma_{i'}^2}{\sigma_i^2} \right)^N \exp \left( \frac{\sigma_i^2 - \sigma_{i'}^2}{\sigma_i^2 \sigma_{i'}^2} z \right),
 				\label{eq:likelihood_ratio}
@@
 			\begin{equation}
-				\Lambda_{i,j}^{\mathrm{ML}}(z) \underset{\mathcal{H}_j}{\overset{\mathcal{H}_i}{\lessgtr}} 1 \iff z \underset{\mathcal{H}_j}{\overset{\mathcal{H}_i}{\lessgtr}} T_{i,j}^{\mathrm{ML}},
+				\Lambda_{i,{i'}}^{\mathrm{ML}}(z) \underset{\mathcal{H}_{i'}}{\overset{\mathcal{H}_i}{\lessgtr}} 1 \iff z \underset{\mathcal{H}_{i'}}{\overset{\mathcal{H}_i}{\lessgtr}} T_{i,{i'}}^{\mathrm{ML}},
 				\label{eq:decision_rule}
 			\end{equation}
-			where the detection threshold between $\mathcal{H}_i$ and $\mathcal{H}_j$ is
+			where the detection threshold between $\mathcal{H}_i$ and $\mathcal{H}_{i'}$ is
 			\begin{equation}
-				T_{i,j}^{\mathrm{ML}} \triangleq N \frac{\sigma_i^2 \sigma_j^2}{\sigma_i^2 - \sigma_j^2} \log \frac{\sigma_i^2}{\sigma_j^2},
+				T_{i,{i'}}^{\mathrm{ML}} \triangleq N \frac{\sigma_i^2 \sigma_{i'}^2}{\sigma_i^2 - \sigma_{i'}^2} \log \frac{\sigma_i^2}{\sigma_{i'}^2}.
 				\label{eq:detection_threshold}
 			\end{equation}
-			and we manually define $T_{0,1}^{\mathrm{ML}} \triangleq 0$ and $T_{M^K,M^K+1}^{\mathrm{ML}} \triangleq \infty$.
-Let $\mathcal{T}^{\mathrm{ML}} \triangleq \{T_{0,1}^{\mathrm{ML}},\ldots,T_{M^K,M^K+1}^{\mathrm{ML}}\}$.
 
 			\begin{remark}
-				Although the ML decision threshold set $\mathcal{T}^{\mathrm{ML}}$ is optimal in terms of the likelihood function, it is not necessarily the same with the capacity-achieving threshold set $\mathcal{T}^{\star}$.
-Interestingly, it was shown in \cite{Qian2019b} that $\mathcal{T}^{\mathrm{ML}}$ and $\mathcal{T}^{\star}$ are very close in the single-tag BIBO case.
+				Although the ML decision threshold is optimal in terms of the likelihood function, it is not necessarily capacity-achieving, although the performance gap can be negligible in the single-tag BIBO case.
 			\end{remark}
 
-			For any given threshold set $\mathcal{T} \triangleq \{T_{0,1},\ldots,T_{M^K,M^K+1}\}$, the decision region of hypothesis $\mathcal{H}_i$ is
-			\begin{equation}
-				\mathcal{R}_i \triangleq [T_{i-1,i}, T_{i,i+1}),
-				\label{eq:decision_region}
-			\end{equation}
-			which can be combined with \eqref{eq:energy_distribution} to formulate an equivalent point-to-point discrete memoryless channel from tag input combination alphabet $\mathcal{M^K}$ to received energy level alphabet $\mathcal{M^K}$ as a transition matrix.
-The probability of observing energy level $j$ under tag input combination $i$ is\footnote{For simplicity, we assume there exists at least one feasible precoder that produces distinct received energy levels for all tag input combinations.
-[TODO] Is this necessary?
-Maybe we can keep those same energy levels and avoid them by input distribution design.}
+			Once the decision region is determined, we can formulate an equivalent point-to-point DMC from tag input combination alphabet $\mathcal{M^K}$ to output energy level alphabet $\mathcal{M^K}$.
+The probability of receiving energy level $j$ under tag input combination $i$ is\footnote{For simplicity, we assume there exists at least one feasible precoder that produces distinct received energy levels for all tag input combinations.
+[TODO] Merge with precoder design.}
 			\begin{equation}
@@
 
-			Based on the equivalent point-to-point channel \eqref{eq:point_to_point_channel}, we can compute the marginal probability on all tags and obtain $K$ transition matrices from $\mathcal{M}$ to $\mathcal{M^K}$ that compose a discrete memoryless MAC.
-Hence, the probability of observing energy level $j$ when tag $k$ at status $m_k$ is
+			On top of this, we can compute the marginal probability on all tags and obtain $K$ transition matrices from $\mathcal{M}$ to $\mathcal{M^K}$ that compose a discrete memoryless MAC.
+The probability of observing energy level $j$ when tag $k$ at status $m_k$ is
 			\begin{equation}
@@
 
-			In summary, for every tag input combination with fixed threshold set, we can obtain the expected power of the received signal per block by \eqref{eq:receive_variance}, the conditional probability density function by \eqref{eq:energy_distribution}, the decision region by \eqref{eq:decision_region}, the equivalent point-to-point channel by \eqref{eq:point_to_point_channel}, and the discrete memoryless MAC by \eqref{eq:mac}.
+			In summary, with CSI knowledge and for any given precoder and detection threshold set, we can obtain the expected power of the received signal per block by \eqref{eq:receive_variance}, the conditional probability density function of the accumulated energy by \eqref{eq:energy_distribution}, the decision region by \eqref{eq:decision_region}, the equivalent point-to-point channel by \eqref{eq:point_to_point_channel}, and the discrete memoryless MAC by \eqref{eq:mac}.
 		\end{subsection}
@@
 		\begin{subsection}{Backscatter sum-rate}
-			Before investigating the sum-rate of the tags, we introduce some prerequisites in information theory.
-Define the input probability distribution of tag $k$ at status $m_k$ as $P_k(\bar{c}_{m_k})$, and assume the input distribution of all tags are mutually independent, such that $P_{\mathcal{K}}(\bar{c}_{m_{\mathcal{K}}}) = \prod_{k \in \mathcal{K}} P_k(\bar{c}_{m_k})$.
-Following \cite{Rezaeian2004}, the information function associated with specific tag input combination $\bar{c}_{m_{\mathcal{K}}}$ is defined as
+			Before investigating the sum-rate of the tags, we introduce some prerequisites of information theory.
+Define the input probability distribution of tag $k$ at status $m_k$ as $P_k(\bar{c}_{m_k})$, and assume the input distribution of all tags are mutually independent, i.e., $P_{\mathcal{K}}(\bar{c}_{m_{\mathcal{K}}}) = \prod_{k \in \mathcal{K}} P_k(\bar{c}_{m_k})$.
+Following \cite{Rezaeian2004}, the backscatter information function associated with tag input combination $\bar{c}_{m_{\mathcal{K}}}$ is defined as
 			\begin{equation}
-				I(\bar{c}_{m_{\mathcal{K}}} ; z) \triangleq \sum_j P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K}}}) \log \frac{P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K}}})}{P(\bar{z}_j)},
+				I_{\mathrm{B}}(\bar{c}_{m_{\mathcal{K}}} ; z) \triangleq \sum_j P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K}}}) \log \frac{P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K}}})}{P(\bar{z}_j)},
 				\label{eq:information_function}
@@
 			\begin{equation}
-				I_{\mathcal{S}}(\bar{c}_{m_{\mathcal{S}}} ; z) = \sum_{m_{\mathcal{K} \setminus \mathcal{S}}} P_{\mathcal{K} \setminus \mathcal{S}}(\bar{c}_{m_{\mathcal{K} \setminus \mathcal{S}}}) I(\bar{c}_{m_{\mathcal{K}}} ; z),
+				I_{\mathrm{B},\mathcal{S}}(\bar{c}_{m_{\mathcal{S}}} ; z) = \sum_{m_{\mathcal{K} \setminus \mathcal{S}}} P_{\mathcal{K} \setminus \mathcal{S}}(\bar{c}_{m_{\mathcal{K} \setminus \mathcal{S}}}) I(\bar{c}_{m_{\mathcal{K}}} ; z),
 				\label{eq:marginal_information_function}
@@
 			\begin{equation}
-				I(c_{\mathcal{K}} ; z) = \mathbb{E}_{c_{\mathcal{K}}} \left[I(\bar{c}_{m_{\mathcal{K}}} ; z)\right] = \mathbb{E}_{c_{\mathcal{S}}} \left[I_{\mathcal{S}}(\bar{c}_{m_{\mathcal{S}}} ; z)\right].
+				I_{\mathrm{B}}(c_{\mathcal{K}} ; z) = \mathbb{E}_{c_{\mathcal{K}}} \left[I_{\mathrm{B}}(\bar{c}_{m_{\mathcal{K}}} ; z)\right] = \mathbb{E}_{c_{\mathcal{S}}} \left[I_{\mathrm{B},\mathcal{S}}(\bar{c}_{m_{\mathcal{S}}} ; z)\right].
 				\label{eq:mutual_information}
@@
 			Evidently, for a given discrete memoryless MAC with transition probability $P(z \mid c_{\mathcal{K}})$, the information function $I(\bar{c}_{m_{\mathcal{K}}} ; z)$ and mutual information $I(c_{\mathcal{K}} ; z)$ only depend on the tag input distribution $P_k(\bar{c}_{m_k})$, $\forall m_k \in \mathcal{M}$, $\forall k \in \mathcal{K}$.
-Therefore, we can obtain the backscatter sum-rate by maximizing the mutual information over the tag input distributions as
+Therefore, the mutual information of the tags can be explicitly written as
 			\begin{equation}
-				R_c = \max_{P(c_{\mathcal{K}})} I(c_{\mathcal{K}} ; z) \ [\si{bpcu}].
+				I_{\mathrm{B}}(c_{\mathcal{K}} ; z) = \sum_{m_{\mathcal{K}}} \prod_{k \in \mathcal{K}} P_k(\bar{c}_{m_k}) \sum_j P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K}}}) \log \frac{P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K}}})}{P(\bar{z}_j)}.
 				\label{eq:backscatter_sum_rate}
 			\end{equation}
+
+			% we can explicitly write the mutual information as
+
+			% obtain the backscatter sum-rate by maximizing the mutual information over the tag input distributions as
+			% \begin{equation}
+			% 	R_c = \max_{P(c_{\mathcal{K}})} I(c_{\mathcal{K}} ; z) \ [\si{bpcu}].
+			% 	\label{eq:backscatter_sum_rate}
+			% \end{equation}
 		\end{subsection}
@@
 For primary transmission, the tags adjust the propagation environment in a potentially beneficial manner, and create artificial channel variation within each fading block.
-As such, the ergodic primary rate can be expressed as
+As such, the ergodic primary mutual information can be expressed as
 			\begin{align}
-				R_s
+				I_{\mathrm{P}}
 				& = \mathbb{E}_{c_{\mathcal{K}}} \left[\log_2 \left(1 + \frac{\lvert \boldsymbol{h}_{\mathrm{E}}^H(c_{\mathcal{K}}) \boldsymbol{w} \rvert^2}{\sigma_w^2}\right)\right]\nonumber\\
@@
 			\begin{maxi!}
-				{\scriptstyle{P(c_{\mathcal{K}}),\mathcal{T},\boldsymbol{w}}}{\rho R_s + (1 - \rho) R_c}{\label{op:rate_region}}{\label{ob:weighted_sum_rate}}
+				{\scriptstyle{P(c_{\mathcal{K}}),\mathcal{T},\boldsymbol{w}}}{I \triangleq \rho I^{\mathrm{P}} + (1 - \rho) I^{\mathrm{B}}}{\label{op:rate_region}}{\label{ob:weighted_sum_rate}}
 				\addConstraint{\lVert \boldsymbol{w} \rVert^2}{\le P\label{co:average_transmit_power}}
@@
 		\begin{subsection}{Input distribution}
-			Once the decision region boundaries $\mathcal{T}$ and the precoder $\boldsymbol{w}$ are determined, we can obtain the equivalent discrete memoryless MAC by \eqref{eq:mac}.
-[The optimal solution is obtained in closed form; to add here]
+			Once the decision boundaries $\mathcal{T}$ and the precoder $\boldsymbol{w}$ are determined, obtain the equivalent discrete memoryless MAC by \eqref{eq:mac}.
+The input distribution optimization subproblem is
+			\begin{maxi!}
+				{\scriptstyle{P(c_{\mathcal{K}})}}{I}{\label{op:input_distribution}}{\label{ob:weighted_sum_rate_input_distribution}}
+				\addConstraint{\sum_{m_k} P_k(\bar{c}_{m_k})}{=1,\quad\label{co:sum_probability_input_distribution}}{\forall k \in \mathcal{K}}
+				\addConstraint{P_k(\bar{c}_{m_k})}{\ge 0,\quad\label{co:nonnegative_probability_input_distribution}}{\forall m_k \in \mathcal{M}, \ \forall k \in \mathcal{K}}
+			\end{maxi!}
+
+			Although the domain is non-convex for $K>1$, the \gls{kkt} conditions are sufficient and necessary for an input distribution to achieve the weighted sum-capacity.
+The proof follows straightforwardly from \cite{Watanabe2009} and details are omitted here.\footnote{For any elementary MAC (the sizes of input alphabets are no greater than that of the output alphabet), the sufficiency can be proved by local maximum and connectedness of \gls{kkt} solutions.
+Also, the capacity of an arbitrary MAC is achieved by an elementary MAC included within.}
+			% We restrict the discussion of this paper to elementary MACs.
+
 		\end{subsection}

### 2021-12-13 main.tex
:pencil: Update primary and backscatter rates

@@
 \newacronym{kkt}{KKT}{Karush–Kuhn–Tucker}
+\newacronym{bpcu}{\si{bpcu}}{bit per channel use}
+\newacronym{bpsphz}{\si{bps/Hz}}{bit per second per Hertz}
 
@@
 
-	\begin{section}{The Multi-Tag Case}
+	\begin{section}{Backscatter Detection and Achievable Rates}
 		\begin{subsection}{System Model}
@@
 
-			To explicitly specify each backscatter symbol combination, we label it by the corresponding modulation index set.
-For tag $k$ at state $m_k \in \mathcal{M}$, $\forall k \in \mathcal{K}$, we define the modulation index set as $m_{\mathcal{K}} \triangleq \{m_k : k \in \mathcal{K}\}$ and the tag input combination as $\bar{c}_{m_{\mathcal{K}}} \triangleq \{\bar{c}_{m_k} : k \in \mathcal{K}\}$.
-Since any $\bar{c}_{m_{\mathcal{K}}}$ remains constant per $N$ primary symbols, the received signal at block $n$ is only subject to the variation of the primary source $s[n]$ and AWGN $w[n]$, and thus follows CSCG distribution $y_{m_{\mathcal{K}}}[n] \sim \mathcal{CN}\left(0,\sigma_{m_{\mathcal{K}}}^2\right)$ with variance
+			To explicitly specify the instances of the backscatter symbols, we define the modulation index set as $m_{\mathcal{K}} \triangleq \{m_k \in \mathcal{M} : k \in \mathcal{K}\}$ and label the corresponding tag input combination as $\bar{c}_{m_{\mathcal{K}}} \triangleq \{\bar{c}_{m_k} \in \mathcal{C} : m_k \in \mathcal{M}, k \in \mathcal{K}\}$.
+Since any $\bar{c}_{m_{\mathcal{K}}}$ remains constant per $N$ primary symbols, the received signal at block $n$ is only subject to the variation of the primary source $s[n]$ and AWGN $w[n]$, and thus follows CSCG distribution $y_{m_{\mathcal{K}}}[n] \sim \mathcal{CN}\left(0,\sigma_{m_{\mathcal{K}}}^2\right)$, where the variance
 			\begin{equation}
@@
 			\end{equation}
-			which denotes the expectation of the received power per primary block under tag modulation index set $m_{\mathcal{K}}$.
-			% It can be numerically evaluated based on the precoder, tag, channel, and noise knowledge.
+			denotes the expectation of the received power per primary block under tag modulation index set $m_{\mathcal{K}}$.
 For the ease of exposition, we denote the hypothesis that the tag input combination at status $i \in \mathcal{M^K} \triangleq \{1,\ldots,M^K\}$ as $\mathcal{H}_i$, sort $\{\sigma_{m_{\mathcal{K}}}^2\}$ in ascending order by a one-to-one mapping $m_{\mathcal{K}} \mapsto i$,\footnote{When more than one modulation index sets yield the same energy level, the mapping is not unique and the detection fails to separate them.
@@
 			\end{equation}
-			and the corresponding decision rule is
+			the corresponding decision rule is
 			\begin{equation}
@@
 			\end{equation}
-			where the detection threshold between $\mathcal{H}_i$ and $\mathcal{H}_{i'}$ is
+			and the detection threshold is
 			\begin{equation}
@@
 			\begin{equation}
-				P(\bar{z}_j \mid \bar{c}_{m_k}) = \frac{\sum_{m_{\mathcal{K} \setminus k}} P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K}}})}{\sum_{m_{\mathcal{K}}} P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K}}})}.
+				P(\bar{z}_j \mid \bar{c}_{m_k}) = \frac{\sum_{m_{\mathcal{K} \setminus \{k\}}} P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K}}})}{\sum_{m_{\mathcal{K}}} P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K}}})}.
 				\label{eq:mac}
@@
 
-			In summary, with CSI knowledge and for any given precoder and detection threshold set, we can obtain the expected power of the received signal per block by \eqref{eq:receive_variance}, the conditional probability density function of the accumulated energy by \eqref{eq:energy_distribution}, the decision region by \eqref{eq:decision_region}, the equivalent point-to-point channel by \eqref{eq:point_to_point_channel}, and the discrete memoryless MAC by \eqref{eq:mac}.
+			In summary, with the CSI knowledge and for any given precoder and detection threshold set, we can obtain the expected power of the received signal per block by \eqref{eq:receive_variance}, the conditional probability density function of the accumulated energy by \eqref{eq:energy_distribution}, the decision region by \eqref{eq:decision_region}, the equivalent point-to-point channel by \eqref{eq:point_to_point_channel}, and the discrete memoryless MAC by \eqref{eq:mac}.
 		\end{subsection}
 
-		\begin{subsection}{Backscatter sum-rate}
-			Before investigating the sum-rate of the tags, we introduce some prerequisites of information theory.
-Define the input probability distribution of tag $k$ at status $m_k$ as $P_k(\bar{c}_{m_k})$, and assume the input distribution of all tags are mutually independent, i.e., $P_{\mathcal{K}}(\bar{c}_{m_{\mathcal{K}}}) = \prod_{k \in \mathcal{K}} P_k(\bar{c}_{m_k})$.
+		\begin{subsection}{Sum backscatter rate}
+			We first introduce some prerequisites of information theory.
+Define the input probability distribution of tag $k$ at status $m_k$ as $P_k(\bar{c}_{m_k})$, collect the input probability distribution of all tags at all states into $\mathcal{P} \triangleq \{P_k(\bar{c}_{m_k}) : m_k \in \mathcal{M}, k \in \mathcal{K}\}$, and assume the input distribution of all tags are mutually independent, such that $P_{\mathcal{K}}(\bar{c}_{m_{\mathcal{K}}}) = \prod_{k \in \mathcal{K}} P_k(\bar{c}_{m_k})$.
 Following \cite{Rezaeian2004}, the backscatter information function associated with tag input combination $\bar{c}_{m_{\mathcal{K}}}$ is defined as
@@
 			\end{equation}
-			the marginal information function on $\mathcal{S} \subset \mathcal{K}$ is written as
+			the marginal information function on $\mathcal{S} \subset \mathcal{K}$ is defined as
 			\begin{equation}
-				I_{\mathrm{B},\mathcal{S}}(\bar{c}_{m_{\mathcal{S}}} ; z) = \sum_{m_{\mathcal{K} \setminus \mathcal{S}}} P_{\mathcal{K} \setminus \mathcal{S}}(\bar{c}_{m_{\mathcal{K} \setminus \mathcal{S}}}) I(\bar{c}_{m_{\mathcal{K}}} ; z),
+				I_{\mathrm{B},\mathcal{S}}(\bar{c}_{m_{\mathcal{S}}} ; z) = \sum_{m_{\mathcal{K} \setminus \mathcal{S}}} P_{\mathcal{K} \setminus \mathcal{S}}(\bar{c}_{m_{\mathcal{K} \setminus \mathcal{S}}}) I_{\mathrm{B}}(\bar{c}_{m_{\mathcal{K}}} ; z),
 				\label{eq:marginal_information_function}
 			\end{equation}
-			and the mutual information of the tags and the received signal can be expressed as\footnote{Please be aware that $c_{\mathcal{K}}$, $c_{\mathcal{S}}$, $z$ are random variables, while $\bar{c}_{m_{\mathcal{K}}}$ (and $\bar{c}_i$), $\bar{c}_{m_{\mathcal{S}}}$, $\bar{z}_j$ represent the corresponding instances.}
-			\begin{equation}
-				I_{\mathrm{B}}(c_{\mathcal{K}} ; z) = \mathbb{E}_{c_{\mathcal{K}}} \left[I_{\mathrm{B}}(\bar{c}_{m_{\mathcal{K}}} ; z)\right] = \mathbb{E}_{c_{\mathcal{S}}} \left[I_{\mathrm{B},\mathcal{S}}(\bar{c}_{m_{\mathcal{S}}} ; z)\right].
-				\label{eq:mutual_information}
-			\end{equation}
+			and the mutual information can be expressed as\footnote{Please be aware that $c_{\mathcal{K}}$, $c_{\mathcal{S}}$, $z$ are random variables, while $\bar{c}_{m_{\mathcal{K}}}$ and $\bar{c}_i$, $\bar{c}_{m_{\mathcal{S}}}$, $\bar{z}_j$ represent the corresponding instances.}
+			\begin{align}
+				I_{\mathrm{B}}(c_{\mathcal{K}} ; z)
+				& = \mathbb{E}_{c_{\mathcal{K}}} \left[I_{\mathrm{B}}(\bar{c}_{m_{\mathcal{K}}} ; z)\right] = \mathbb{E}_{c_{\mathcal{S}}} \left[I_{\mathrm{B},\mathcal{S}}(\bar{c}_{m_{\mathcal{S}}} ; z)\right]\label{eq:mutual_information}\\
+				& = \sum_{m_{\mathcal{K}}} \prod_{k \in \mathcal{K}} P_k(\bar{c}_{m_k}) \sum_j P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K}}}) \log \frac{P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K}}})}{P(\bar{z}_j)}.\label{eq:backscatter_sum_rate}
+			\end{align}
 
-			Evidently, for a given discrete memoryless MAC with transition probability $P(z \mid c_{\mathcal{K}})$, the information function $I(\bar{c}_{m_{\mathcal{K}}} ; z)$ and mutual information $I(c_{\mathcal{K}} ; z)$ only depend on the tag input distribution $P_k(\bar{c}_{m_k})$, $\forall m_k \in \mathcal{M}$, $\forall k \in \mathcal{K}$.
-Therefore, the mutual information of the tags can be explicitly written as
-			\begin{equation}
-				I_{\mathrm{B}}(c_{\mathcal{K}} ; z) = \sum_{m_{\mathcal{K}}} \prod_{k \in \mathcal{K}} P_k(\bar{c}_{m_k}) \sum_j P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K}}}) \log \frac{P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K}}})}{P(\bar{z}_j)}.
-				\label{eq:backscatter_sum_rate}
-			\end{equation}
-
-			% we can explicitly write the mutual information as
-
-			% obtain the backscatter sum-rate by maximizing the mutual information over the tag input distributions as
-			% \begin{equation}
-			% 	R_c = \max_{P(c_{\mathcal{K}})} I(c_{\mathcal{K}} ; z) \ [\si{bpcu}].
-			% 	\label{eq:backscatter_sum_rate}
-			% \end{equation}
+			Evidently, for a given discrete memoryless MAC with transition probability $P(z \mid c_{\mathcal{K}})$, the information function $I_{\mathrm{B}}(\bar{c}_{m_{\mathcal{K}}} ; z)$ and mutual information $I_{\mathrm{B}}(c_{\mathcal{K}} ; z)$ only depend on the tag input distribution $\mathcal{P}$.\footnote{Note that the contribution of the precoder and detection threshold are modelled within the discrete memoryless MAC.}
 		\end{subsection}
 
-		\begin{subsection}{Primary ergodic rate}
-			Once the tag symbol set $\bar{c}_{m_{\mathcal{K}}}$ is successfully decoded, the user can eliminate the backscatter uncertainty and model it within the equivalent primary channel by \eqref{eq:equivalent_primary_channel}.
-For primary transmission, the tags adjust the propagation environment in a potentially beneficial manner, and create artificial channel variation within each fading block.
-As such, the ergodic primary mutual information can be expressed as
+		\begin{subsection}{Ergodic primary rate}
+			Once the tag input combination is successfully decoded, the user can eliminate backscatter uncertainty and model its contribution within the equivalent primary channel \eqref{eq:equivalent_primary_channel}.
+As such, the tags can adjust the propagation environment in a potentially beneficial manner, and create artificial channel variation within each fading block.
+Hence, the ergodic primary rate can be expressed as \footnote{The unit of \eqref{eq:backscatter_sum_rate} is \gls{bpcu} while the unit of \eqref{eq:primary_ergodic_rate} is \gls{bpsphz}.}
 			\begin{align}
@@
 				& = \mathbb{E}_{c_{\mathcal{K}}} \left[\log_2 \left(1 + \frac{\lvert \boldsymbol{h}_{\mathrm{E}}^H(c_{\mathcal{K}}) \boldsymbol{w} \rvert^2}{\sigma_w^2}\right)\right]\nonumber\\
-				& = \sum_{m_{\mathcal{K}}} \prod_{k \in \mathcal{K}} P_k(\bar{c}_{m_k}) \log_2 \left(1 + \frac{\lvert \boldsymbol{h}_{\mathrm{E}}^H(\bar{c}_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_w^2}\right) \ [\si{bps/Hz}].
+				& = \sum_{m_{\mathcal{K}}} \prod_{k \in \mathcal{K}} P_k(\bar{c}_{m_k}) \log_2 \left(1 + \frac{\lvert \boldsymbol{h}_{\mathrm{E}}^H(\bar{c}_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_w^2}\right).
 				\label{eq:primary_ergodic_rate}
 			\end{align}
-			which is also a function of the tag input distribution $P(c_{\mathcal{K}})$.
+			which is also a function of the tag input distribution $\mathcal{P}$.
+			% $P(c_{\mathcal{K}})$.
 		\end{subsection}
@@
 	\begin{section}{Input Distribution, Decision Region, and Precoder Design}
-		\begin{subsection}{Primary ergodic-secondary sum rate region}
-			To achieve a flexible tradeoff between the primary and backscatter links, we aim to optimize the tag input distribution, decision region, and precoder to maximize the weighted sum of the ergodic primary rate and the total backscatter rate, under the average transmit power and probability constraints
+		\begin{subsection}{Primary-backscatter rate region}
+			Define the weighted sum primary-backscatter rate as
+			\begin{equation}
+				I \triangleq \rho I_{\mathrm{B}}(c_{\mathcal{K}} ; z) + (1 - \rho) I_{\mathrm{P}},
+			\end{equation}
+			where $\rho \in [0,1]$ denotes the priority of the primary link.
+To investigate how the primary and backscatter links influence each other, we optimize the input probability distribution, decision region, and transmit precoder to maximize the weighted sum rate subject to the average transmit power and input probability constraints
+
 			\begin{maxi!}
-				{\scriptstyle{P(c_{\mathcal{K}}),\mathcal{T},\boldsymbol{w}}}{I \triangleq \rho I^{\mathrm{P}} + (1 - \rho) I^{\mathrm{B}}}{\label{op:rate_region}}{\label{ob:weighted_sum_rate}}
-				\addConstraint{\lVert \boldsymbol{w} \rVert^2}{\le P\label{co:average_transmit_power}}
-				\addConstraint{\sum_{m_k} P_k(\bar{c}_{m_k})}{=1,\quad\label{co:sum_probability}}{\forall k \in \mathcal{K}}
+				{\scriptstyle{\mathcal{P},\mathcal{T},\boldsymbol{w}}}{I}{\label{op:rate_region}}{\label{ob:weighted_sum_rate}}
+				\addConstraint{\sum \nolimits_{m_k} P_k(\bar{c}_{m_k})}{=1,\quad\label{co:sum_probability}}{\forall k \in \mathcal{K}}
 				\addConstraint{P_k(\bar{c}_{m_k})}{\ge 0,\quad\label{co:nonnegative_probability}}{\forall m_k \in \mathcal{M}, \ \forall k \in \mathcal{K}}
+				\addConstraint{\lVert \boldsymbol{w} \rVert^2}{\le P.\label{co:average_transmit_power}}
 			\end{maxi!}
-			where $\rho \in [0,1]$ denotes the priority of the primary link.
-As problem \eqref{op:rate_region} is not jointly convex over $P(c_{\mathcal{K}})$, $\mathcal{T}$ and $\boldsymbol{w}$, we propose an Block Coordinate Descent (BCD)-based algorithm that iteratively updates the input distribution, decision region, and precoder, until convergence.
+
+			As problem \eqref{op:rate_region} is not jointly convex over $\mathcal{P}$, $\mathcal{T}$ and $\boldsymbol{w}$, we propose a Block Coordinate Descent (BCD) method that iteratively updates the input distribution, decision region, and transmit precoder, until convergence is achieved.
 		\end{subsection}
 
-		\begin{subsection}{Input distribution}
-			Once the decision boundaries $\mathcal{T}$ and the precoder $\boldsymbol{w}$ are determined, obtain the equivalent discrete memoryless MAC by \eqref{eq:mac}.
-The input distribution optimization subproblem is
+		\begin{subsection}{Input probability distribution}
+			For any fixed decision boundary $\mathcal{T}$ and transmit precoder $\boldsymbol{w}$, the equivalent discrete memoryless MAC can be determined by \eqref{eq:mac}, and problem~\eqref{op:rate_region} boils down to
 			\begin{maxi!}
-				{\scriptstyle{P(c_{\mathcal{K}})}}{I}{\label{op:input_distribution}}{\label{ob:weighted_sum_rate_input_distribution}}
-				\addConstraint{\sum_{m_k} P_k(\bar{c}_{m_k})}{=1,\quad\label{co:sum_probability_input_distribution}}{\forall k \in \mathcal{K}}
-				\addConstraint{P_k(\bar{c}_{m_k})}{\ge 0,\quad\label{co:nonnegative_probability_input_distribution}}{\forall m_k \in \mathcal{M}, \ \forall k \in \mathcal{K}}
+				{\scriptstyle{\mathcal{P}}}{I}{\label{op:input_probability_distribution}}{}
+				\addConstraint{\eqref{co:sum_probability},\eqref{co:nonnegative_probability},}
 			\end{maxi!}
+			which is non-convex for $K > 1$ due to the product term $\prod_{k \in \mathcal{K}} P_k(\bar{c}_{m_k})$.
+Fortunately, the \gls{kkt} conditions are sufficient and necessary for this type of problem, and the proof follows straightforwardly from \cite{Watanabe2009}.\footnote{For any elementary discrete memoryless MAC (sizes of input alphabets are no greater than that of output alphabet), the sufficiency can be proved by combining the local maximum and connectedness of \gls{kkt} solutions.
+For any general discrete memoryless MAC, the capacity can be achieved by an elementary discrete memoryless MAC included within.
+Thus, we restrict the discussion of this paper to elementary discrete memoryless MACs.}
 
-			Although the domain is non-convex for $K>1$, the \gls{kkt} conditions are sufficient and necessary for an input distribution to achieve the weighted sum-capacity.
+			% Although the domain is non-convex for $K>1$, the \gls{kkt} conditions are sufficient and necessary for an input distribution to achieve the weighted sum-capacity.
 The proof follows straightforwardly from \cite{Watanabe2009} and details are omitted here.\footnote{For any elementary MAC (the sizes of input alphabets are no greater than that of the output alphabet), the sufficiency can be proved by local maximum and connectedness of \gls{kkt} solutions.

### 2021-12-13 main.tex
:pencil: Link abbreviations

@@
 
-\newacronym{kkt}{KKT}{Karush–Kuhn–Tucker}
+\newacronym{ambc}{AmBC}{Ambient Backscatter Communications}
+\newacronym{ap}{AP}{Access Point}
+\newacronym{awgn}{AWGN}{Additive White Gaussian Noise}
+\newacronym{bcd}{BCD}{Block Coordinate Descent}
+\newacronym{bibo}{BIBO}{Binary-Input Binary-Output}
 \newacronym{bpcu}{\si{bpcu}}{bit per channel use}
 \newacronym{bpsphz}{\si{bps/Hz}}{bit per second per Hertz}
+\newacronym{cscg}{CSCG}{Circularly Symmetric Complex Gaussian}
+\newacronym{csi}{CSI}{Channel State Information}
+\newacronym{dmc}{DMC}{Discrete Memoryless Channel}
+\newacronym{dmtc}{DMTC}{Discrete Memoryless Thresholding Channel}
+\newacronym{irs}{IRS}{Intelligent Reflecting Surface}
+\newacronym{kkt}{KKT}{Karush–Kuhn–Tucker}
+\newacronym{mac}{MAC}{Multiple Access Channel}
+\newacronym{mc}{MC}{Multiplication Coding}
+\newacronym{ml}{ML}{Maximum-Likelihood}
+\newacronym{psk}{PSK}{Phase Shift Keying}
+\newacronym{qam}{QAM}{Quadrature Amplitude Modulation}
+\newacronym{rf}{RF}{Radio Frequency}
+\newacronym{sc}{SC}{Superposition Coding}
+\newacronym{sic}{SIC}{Successive Interference Cancellation}
+\newacronym{sr}{SR}{Symbiotic Radio}
+\newacronym{tg}{TG}{tag}
+\newacronym{ue}{UE}{user}
 
@@
 			Backscatter modulation is achieved by switching the tag load impedance between different states.
-For an $M$-ary Quadrature Amplitude Modulation (QAM) at state $m \in \mathcal{M} \triangleq \{1,\ldots,M\}$, the reflection coefficient $\Gamma_m$ maps to the signal constellation point $\bar{c}_m$ as \cite{Thomas2012a}
+For an $M$-ary \gls{qam} at state $m \in \mathcal{M} \triangleq \{1,\ldots,M\}$, the reflection coefficient $\Gamma_m$ maps to the signal constellation point $\bar{c}_m$ as \cite{Thomas2012a}
 			\begin{equation}
@@
 			where $\alpha \in [0,1]$ is the reflection efficiency at a given direction.
-For simplicity, we consider an $M$-ary Phase Shift Keying (PSK) with constellation set $\mathcal{C} \triangleq \{\bar{c}_1,\ldots,\bar{c}_M\}$, where the $m$-th constellation point is
+For simplicity, we consider an $M$-ary \gls{psk} with constellation set $\mathcal{C} \triangleq \{\bar{c}_1,\ldots,\bar{c}_M\}$, where the $m$-th constellation point is
 			\begin{equation}
@@
 			\begin{remark}
-				For passive tags, the reflection efficiency $\alpha$ controls the tradeoff between the harvestable power and backscatter strength: $\alpha = 0$ corresponds to maximum power transfer to the tag, while $\alpha = 1$ with $M$-PSK corresponds to ideal Intelligent Reflecting Surface (IRS) with $M$ discrete states.
+				For passive tags, the reflection efficiency $\alpha$ controls the tradeoff between the harvestable power and backscatter strength: $\alpha = 0$ corresponds to maximum power transfer to the tag, while $\alpha = 1$ with $M$-\gls{psk} corresponds to ideal \gls{irs} with $M$ discrete states.
 			\end{remark}
@@
 			\end{figure}
-			As shown in Fig.~\ref{fi:symbiotic_radio}, we propose a single-user (UE) multi-tag (TG) symbiotic radio network where the RF signal generated by the $Q$-antenna Access Point (AP) is shared by two coexisting systems.
-In the primary downlink system, the AP transmits information to the single-antenna user.
-In the secondary backscatter system, the AP acts as the carrier emitter, the $K$ nearby single-antenna tags modulate their information over the reradiated RF signals, and the user serves as the multi-tag backscatter reader.
-Denote the AP-UE direct channel as $\boldsymbol{h}_{\mathrm{D}}^H \in \mathbb{C}^{1 \times Q}$, the AP-TG $k \in \mathcal{K} \triangleq \{1,\ldots,K\}$ forward channel as $\boldsymbol{h}_{\mathrm{F},k}^H \in \mathbb{C}^{1 \times Q}$, the TG $k$-UE backward channel as $h_{\mathrm{B},k}$, and the cascaded forward-backward channel of tag $k$ as $\boldsymbol{h}_{\mathrm{C},k}^H \triangleq h_{\mathrm{B},k} \boldsymbol{h}_{\mathrm{F},k}^H \in \mathbb{C}^{1 \times Q}$.
+			As shown in Fig.~\ref{fi:symbiotic_radio}, we propose a single-\gls{ue} multi-\gls{tg} symbiotic radio network where the \gls{rf} signal generated by the $Q$-antenna \gls{ap} is shared by two coexisting systems.
+In the primary downlink system, the \gls{ap} transmits information to the single-antenna user.
+In the secondary backscatter system, the \gls{ap} acts as the carrier emitter, the $K$ nearby single-antenna tags modulate their information over the reradiated \gls{rf} signals, and the user serves as the multi-tag backscatter reader.
+Denote the \gls{ap}-\gls{ue} direct channel as $\boldsymbol{h}_{\mathrm{D}}^H \in \mathbb{C}^{1 \times Q}$, the \gls{ap}-\gls{tg} $k \in \mathcal{K} \triangleq \{1,\ldots,K\}$ forward channel as $\boldsymbol{h}_{\mathrm{F},k}^H \in \mathbb{C}^{1 \times Q}$, the \gls{tg} $k$-\gls{ue} backward channel as $h_{\mathrm{B},k}$, and the cascaded forward-backward channel of tag $k$ as $\boldsymbol{h}_{\mathrm{C},k}^H \triangleq h_{\mathrm{B},k} \boldsymbol{h}_{\mathrm{F},k}^H \in \mathbb{C}^{1 \times Q}$.
 For simplicity, we consider a quasi-static block fading model where the channel coefficients remain constant within each coherence interval and vary independently over different coherence intervals, and assume the coherence interval $T$ is much longer than the backscatter symbol period $T_c$ and primary symbol period $T_s$.
-We also assume the direct channel and all cascaded channels can be successfully estimated and fed back to the AP.\footnote{Due to the lack of RF chains at the passive tag, accurate and efficient Channel State Information at the Transmitter (CSIT) acquisition can be challenging.
-One possible approach is that the AP sends pre-defined pilots, the tags respond in well-designed manners, and the user performs least-square estimation with feedbacks \cite{Bharadia2015,Yang2015b,Guo2019g}.} Since the tags need to physically switch the loads for backscatter modulation, they communicate at a much longer symbol period (and lower rates) than the primary system.
+We also assume the direct channel and all cascaded channels can be successfully estimated and fed back to the \gls{ap}.\footnote{Due to the lack of \gls{rf} chains at the passive tag, accurate and efficient \gls{csi} acquisition at the \gls{ap} can be challenging.
+One possible approach is that the \gls{ap} sends pre-defined pilots, the tags respond in well-designed manners, and the user performs least-square estimation with feedbacks \cite{Bharadia2015,Yang2015b,Guo2019g}.} Since the tags need to physically switch the loads for backscatter modulation, they communicate at a much longer symbol period (and lower rates) than the primary system.
 As such, we assume the transitions of all tags are perfectly synchronized, and the backscatter symbol period satisfies $T_c = N T_s$ where $N \gg 1$ is a positive integer.
@@
 			Without loss of generality, we focus on the transmissions and detections during one particular backscatter symbol period.
-To provide a preliminary insight, we assume the primary symbol $s[n]$ at block $n \in \mathcal{N} \triangleq \{1,\ldots,N\}$ is in standard CSCG distribution, and the backscatter symbol $c_k$ of tag $k$ employs $M$-PSK modulation by \eqref{eq:mpsk}, i.e., $c_k \in \mathcal{C}$, $\forall k \in \mathcal{K}$.
+To provide a preliminary insight, we assume the primary symbol $s[n]$ at block $n \in \mathcal{N} \triangleq \{1,\ldots,N\}$ is in standard \gls{cscg} distribution, and the backscatter symbol $c_k$ of tag $k$ employs $M$-\gls{psk} modulation by \eqref{eq:mpsk}, i.e., $c_k \in \mathcal{C}$, $\forall k \in \mathcal{K}$.
 Thus, the signal received by the user at block $n$ can be expressed as\footnote{We omit the signal reflected by two or more times\cite{Wu2019} and assume the time difference of arrival from different paths are negligible\cite{Guo2019b}.}
@@
 			\end{equation}
-			where $\boldsymbol{w} \in \mathbb{C}^{Q \times 1}$ is the active precoder satisfying $\lVert \boldsymbol{w} \rVert^2 \le P$, $P$ is the average transmit power constraint at the AP, and $w[n] \sim \mathcal{CN}(0,\sigma_w^2)$ is the equivalent Additive White Gaussian Noise (AWGN) at block $n$.
+			where $\boldsymbol{w} \in \mathbb{C}^{Q \times 1}$ is the active precoder satisfying $\lVert \boldsymbol{w} \rVert^2 \le P$, $P$ is the average transmit power constraint at the \gls{ap}, and $w[n] \sim \mathcal{CN}(0,\sigma_w^2)$ is the equivalent \gls{awgn} at block $n$.
 Besides, we collect the backscatter symbols of $K$ tags into $c_{\mathcal{K}} \triangleq \{c_k : k \in \mathcal{K}\}$, stack the received signal over $N$ blocks as $\boldsymbol{y} \triangleq \left[y[1],\ldots,y[N]\right]^T \in \mathbb{C}^{N \times 1}$, and define the equivalent channel for primary transmission as
@@
 			\begin{remark}
-				The proposed symbiotic radio system includes a multiplicative Multiple Access Channel (MAC) where the AP and the tags simultaneously transmit to the user.
-It inspired [TODO] to perform Successive Interference Cancellation (SIC) that first non-coherently detects the primary message under backscatter uncertainty, then cancels its contribution and decodes the tag messages.
-This scheme requires non-coherent coding at the AP and $K$ re-encoding, precoding, and subtraction operations at the user.
-However, different from the conventional MAC with Superposition Coding (SC), the symbiotic radio system involves Multiplication Coding (MC) that combines the primary and secondary messages by multiplication.
+				The proposed symbiotic radio system includes a multiplicative \gls{mac} where the \gls{ap} and the tags simultaneously transmit to the user.
+It inspired [TODO] to perform \gls{sic} that first non-coherently detects the primary message under backscatter uncertainty, then cancels its contribution and decodes the tag messages.
+This scheme requires non-coherent coding at the \gls{ap} and $K$ re-encoding, precoding, and subtraction operations at the user.
+However, different from the conventional \gls{mac} with \gls{sc}, the symbiotic radio system involves \gls{mc} that combines the primary and secondary messages by multiplication.
 Hence, novel multi-stream detection techniques should be tailored to symbiotic radio systems to accommodate the massive connectivity of tags and the multiplicative combination of links.
@@
 		\begin{subsection}{Backscatter Detection}
-			To reveal the impact of backscatter modulation on the primary transmission and avoid the exponential complexity of joint detection, we extend the non-coherent Ambient Backscatter Communications (AmBC) detection \cite{Qian2019} to the multi-tag case, and propose a low-complexity energy detection to decode the backscatter symbols under primary source uncertainty.
-It requires no dedicated receivers or non-coherent codes at the AP, and can be readily implemented over legacy downlink systems.
+			To reveal the impact of backscatter modulation on the primary transmission and avoid the exponential complexity of joint detection, we extend the non-coherent \gls{ambc} detection \cite{Qian2019} to the multi-tag case, and propose a low-complexity energy detection to decode the backscatter symbols under primary source uncertainty.
+It requires no dedicated receivers or non-coherent codes at the \gls{ap}, and can be readily implemented over legacy downlink systems.
 
@@
 As such, each reflection coefficient simultaneously encodes the tag message and influences the equivalent channel of the primary link.
-If the backscatter symbols can be successfully decoded first, they can be modeled within the equivalent channel \eqref{eq:equivalent_primary_channel} as in channel training, instead of being removed by SIC.
+If the backscatter symbols can be successfully decoded first, they can be modeled within the equivalent channel \eqref{eq:equivalent_primary_channel} as in channel training, instead of being removed by \gls{sic}.
 			\end{remark}
@@
 			To explicitly specify the instances of the backscatter symbols, we define the modulation index set as $m_{\mathcal{K}} \triangleq \{m_k \in \mathcal{M} : k \in \mathcal{K}\}$ and label the corresponding tag input combination as $\bar{c}_{m_{\mathcal{K}}} \triangleq \{\bar{c}_{m_k} \in \mathcal{C} : m_k \in \mathcal{M}, k \in \mathcal{K}\}$.
-Since any $\bar{c}_{m_{\mathcal{K}}}$ remains constant per $N$ primary symbols, the received signal at block $n$ is only subject to the variation of the primary source $s[n]$ and AWGN $w[n]$, and thus follows CSCG distribution $y_{m_{\mathcal{K}}}[n] \sim \mathcal{CN}\left(0,\sigma_{m_{\mathcal{K}}}^2\right)$, where the variance
+Since any $\bar{c}_{m_{\mathcal{K}}}$ remains constant per $N$ primary symbols, the received signal at block $n$ is only subject to the variation of the primary source $s[n]$ and \gls{awgn} $w[n]$, and thus follows \gls{cscg} distribution $y_{m_{\mathcal{K}}}[n] \sim \mathcal{CN}\left(0,\sigma_{m_{\mathcal{K}}}^2\right)$, where the variance
 			\begin{equation}
@@
 				The backscatter links essentially form a discrete-input continuous-output memoryless channel.
-To further reduce decoding complexity, we apply hard-decision detection and construct a Discrete Memoryless Thresholding Channel (DMTC), whose capacity is a function of both input distribution and decision thresholds \cite{Nguyen2018}.
+To further reduce decoding complexity, we apply hard-decision detection and construct a \gls{dmtc}, whose capacity is a function of both input distribution and decision thresholds \cite{Nguyen2018}.
 			\end{remark}
@@
 
-			Consider the Maximum-Likelihood (ML) detector for example. The likelihood ratio between hypotheses $\mathcal{H}_i$ and $\mathcal{H}_{i'}$ is \cite{Qian2019}
+			Consider the (\gls{ml}) detector for example. The likelihood ratio between hypotheses $\mathcal{H}_i$ and $\mathcal{H}_{i'}$ is \cite{Qian2019}
 			\begin{equation}
-				\Lambda_{i,{i'}}^{\mathrm{ML}}(z) = \frac{f(z \mid \mathcal{H}_i)}{f(z \mid \mathcal{H}_{i'})} = \left( \frac{\sigma_{i'}^2}{\sigma_i^2} \right)^N \exp \left( \frac{\sigma_i^2 - \sigma_{i'}^2}{\sigma_i^2 \sigma_{i'}^2} z \right),
+				\Lambda_{i,{i'}}^{\mathrm{\gls{ml}}}(z) = \frac{f(z \mid \mathcal{H}_i)}{f(z \mid \mathcal{H}_{i'})} = \left( \frac{\sigma_{i'}^2}{\sigma_i^2} \right)^N \exp \left( \frac{\sigma_i^2 - \sigma_{i'}^2}{\sigma_i^2 \sigma_{i'}^2} z \right),
 				\label{eq:likelihood_ratio}
@@
 			\begin{equation}
-				\Lambda_{i,{i'}}^{\mathrm{ML}}(z) \underset{\mathcal{H}_{i'}}{\overset{\mathcal{H}_i}{\lessgtr}} 1 \iff z \underset{\mathcal{H}_{i'}}{\overset{\mathcal{H}_i}{\lessgtr}} T_{i,{i'}}^{\mathrm{ML}},
+				\Lambda_{i,{i'}}^{\mathrm{\gls{ml}}}(z) \underset{\mathcal{H}_{i'}}{\overset{\mathcal{H}_i}{\lessgtr}} 1 \iff z \underset{\mathcal{H}_{i'}}{\overset{\mathcal{H}_i}{\lessgtr}} T_{i,{i'}}^{\mathrm{\gls{ml}}},
 				\label{eq:decision_rule}
@@
 			\begin{equation}
-				T_{i,{i'}}^{\mathrm{ML}} \triangleq N \frac{\sigma_i^2 \sigma_{i'}^2}{\sigma_i^2 - \sigma_{i'}^2} \log \frac{\sigma_i^2}{\sigma_{i'}^2}.
+				T_{i,{i'}}^{\mathrm{\gls{ml}}} \triangleq N \frac{\sigma_i^2 \sigma_{i'}^2}{\sigma_i^2 - \sigma_{i'}^2} \log \frac{\sigma_i^2}{\sigma_{i'}^2}.
 				\label{eq:detection_threshold}
@@
 			\begin{remark}
-				Although the ML decision threshold is optimal in terms of the likelihood function, it is not necessarily capacity-achieving, although the performance gap can be negligible in the single-tag BIBO case.
+				Although the \gls{ml} decision threshold is optimal in terms of the likelihood function, it is not necessarily capacity-achieving, although the performance gap can be negligible in the single-tag \gls{bibo} case.
 			\end{remark}
 
-			Once the decision region is determined, we can formulate an equivalent point-to-point DMC from tag input combination alphabet $\mathcal{M^K}$ to output energy level alphabet $\mathcal{M^K}$.
+			Once the decision region is determined, we can formulate an equivalent point-to-point \gls{dmc} from tag input combination alphabet $\mathcal{M^K}$ to output energy level alphabet $\mathcal{M^K}$.
 The probability of receiving energy level $j$ under tag input combination $i$ is\footnote{For simplicity, we assume there exists at least one feasible precoder that produces distinct received energy levels for all tag input combinations.
@@
 
-			On top of this, we can compute the marginal probability on all tags and obtain $K$ transition matrices from $\mathcal{M}$ to $\mathcal{M^K}$ that compose a discrete memoryless MAC.
+			On top of this, we can compute the marginal probability on all tags and obtain $K$ transition matrices from $\mathcal{M}$ to $\mathcal{M^K}$ that compose a discrete memoryless \gls{mac}.
 The probability of observing energy level $j$ when tag $k$ at status $m_k$ is
@@
 
-			In summary, with the CSI knowledge and for any given precoder and detection threshold set, we can obtain the expected power of the received signal per block by \eqref{eq:receive_variance}, the conditional probability density function of the accumulated energy by \eqref{eq:energy_distribution}, the decision region by \eqref{eq:decision_region}, the equivalent point-to-point channel by \eqref{eq:point_to_point_channel}, and the discrete memoryless MAC by \eqref{eq:mac}.
+			In summary, with the \gls{csi} knowledge and for any given precoder and detection threshold set, we can obtain the expected power of the received signal per block by \eqref{eq:receive_variance}, the conditional probability density function of the accumulated energy by \eqref{eq:energy_distribution}, the decision region by \eqref{eq:decision_region}, the equivalent point-to-point channel by \eqref{eq:point_to_point_channel}, and the discrete memoryless \gls{mac} by \eqref{eq:mac}.
 		\end{subsection}
@@
 
-			Evidently, for a given discrete memoryless MAC with transition probability $P(z \mid c_{\mathcal{K}})$, the information function $I_{\mathrm{B}}(\bar{c}_{m_{\mathcal{K}}} ; z)$ and mutual information $I_{\mathrm{B}}(c_{\mathcal{K}} ; z)$ only depend on the tag input distribution $\mathcal{P}$.\footnote{Note that the contribution of the precoder and detection threshold are modelled within the discrete memoryless MAC.}
+			Evidently, for a given discrete memoryless \gls{mac} with transition probability $P(z \mid c_{\mathcal{K}})$, the information function $I_{\mathrm{B}}(\bar{c}_{m_{\mathcal{K}}} ; z)$ and mutual information $I_{\mathrm{B}}(c_{\mathcal{K}} ; z)$ only depend on the tag input distribution $\mathcal{P}$.\footnote{Note that the contribution of the precoder and detection threshold are modelled within the discrete memoryless \gls{mac}.}
 		\end{subsection}
@@
 
-			As problem \eqref{op:rate_region} is not jointly convex over $\mathcal{P}$, $\mathcal{T}$ and $\boldsymbol{w}$, we propose a Block Coordinate Descent (BCD) method that iteratively updates the input distribution, decision region, and transmit precoder, until convergence is achieved.
+			As problem \eqref{op:rate_region} is not jointly convex over $\mathcal{P}$, $\mathcal{T}$ and $\boldsymbol{w}$, we propose a \gls{bcd} method that iteratively updates the input distribution, decision region, and transmit precoder, until convergence is achieved.
 		\end{subsection}
@@
 		\begin{subsection}{Input probability distribution}
-			For any fixed decision boundary $\mathcal{T}$ and transmit precoder $\boldsymbol{w}$, the equivalent discrete memoryless MAC can be determined by \eqref{eq:mac}, and problem~\eqref{op:rate_region} boils down to
+			For any fixed decision boundary $\mathcal{T}$ and transmit precoder $\boldsymbol{w}$, the equivalent discrete memoryless \gls{mac} can be determined by \eqref{eq:mac}, and problem~\eqref{op:rate_region} boils down to
 			\begin{maxi!}
@@
 			which is non-convex for $K > 1$ due to the product term $\prod_{k \in \mathcal{K}} P_k(\bar{c}_{m_k})$.
-Fortunately, the \gls{kkt} conditions are sufficient and necessary for this type of problem, and the proof follows straightforwardly from \cite{Watanabe2009}.\footnote{For any elementary discrete memoryless MAC (sizes of input alphabets are no greater than that of output alphabet), the sufficiency can be proved by combining the local maximum and connectedness of \gls{kkt} solutions.
-For any general discrete memoryless MAC, the capacity can be achieved by an elementary discrete memoryless MAC included within.
-Thus, we restrict the discussion of this paper to elementary discrete memoryless MACs.}
+Fortunately, the \gls{kkt} conditions are sufficient and necessary for this type of problem, and the proof follows straightforwardly from \cite{Watanabe2009}.\footnote{For any elementary discrete memoryless \gls{mac} (sizes of input alphabets are no greater than that of output alphabet), the sufficiency can be proved by combining the local maximum and connectedness of \gls{kkt} solutions.
+For any general discrete memoryless \gls{mac}, the capacity can be achieved by an elementary discrete memoryless \gls{mac} included within.
+Thus, we restrict the discussion of this paper to elementary discrete memoryless \gls{mac}s.}
 
 			% Although the domain is non-convex for $K>1$, the \gls{kkt} conditions are sufficient and necessary for an input distribution to achieve the weighted sum-capacity.
-The proof follows straightforwardly from \cite{Watanabe2009} and details are omitted here.\footnote{For any elementary MAC (the sizes of input alphabets are no greater than that of the output alphabet), the sufficiency can be proved by local maximum and connectedness of \gls{kkt} solutions.
-Also, the capacity of an arbitrary MAC is achieved by an elementary MAC included within.}
-			% We restrict the discussion of this paper to elementary MACs.
+The proof follows straightforwardly from \cite{Watanabe2009} and details are omitted here.\footnote{For any elementary \gls{mac} (the sizes of input alphabets are no greater than that of the output alphabet), the sufficiency can be proved by local maximum and connectedness of \gls{kkt} solutions.
+Also, the capacity of an arbitrary \gls{mac} is achieved by an elementary \gls{mac} included within.}
+			% We restrict the discussion of this paper to elementary \gls{mac}s.
 
@@
 		\begin{subsection}{Decision region}
-			As indicated by \cite{Qian2019b}, the optimal ML decision regions are very close to the optimal decision regions to problem \eqref{op:rate_region}.
+			As indicated by \cite{Qian2019b}, the optimal \gls{ml} decision regions are very close to the optimal decision regions to problem \eqref{op:rate_region}.
 We can either use \eqref{eq:decision_region} as suboptimal, or take derivative of \eqref{eq:mutual_information} w.r.t.
@@
 
-			So far I have no idea how to solve this issue, and found no reference regarding precoder design for AmBC/SR with discrete channels (although some naive combiner designs are available for BIBO).
-Personally, I believe the precoder design is the key to (i) boost the rate region and avoid blind spots in conventional AmBC; (ii) build our proposal over existing infrastructures.
+			So far I have no idea how to solve this issue, and found no reference regarding precoder design for \gls{ambc}/\gls{sr} with discrete channels (although some naive combiner designs are available for \gls{bibo}).
+Personally, I believe the precoder design is the key to (i) boost the rate region and avoid blind spots in conventional \gls{ambc}; (ii) build our proposal over existing infrastructures.
 Ideally, assuming the number of transmit antennas $Q$ is larger than the number of tags $K$, the optimal energy levels should be almost uniformly spaced (as $z$ follows Erlang distribution) to concentrate the channel transitional probability on diagonal as possible.
@@
 	% 	% \end{figure}
-	% 	As shown in Fig.~NULL, we propose a single-user (UE) single-tag (TG) symbiotic radio network where the RF signal generated by the single-antenna Access Point (AP) is shared by two coexisting systems.
-In the primary AP-UE downlink system, the AP transmits to the single-antenna user.
-In the secondary AP-TG-UE backscatter system, the AP acts as the carrier emitter, the user serves as the backscatter reader, and the single-antenna tag modulates its information over the reradiated RF signal by varying the reflection coefficient.
-Denote the AP-UE direct channel as $h_{\mathrm{D}}$, the AP-TG forward channel as $h_{\mathrm{F}}$, and the TG-UE backward channel as $h_{\mathrm{B}}$.
-We consider the quasi-static block fading model and assume the CSI of the direct channel and the cascaded forward-backward channel $h_{\mathrm{C}} \triangleq h_{\mathrm{B}} h_{\mathrm{F}}$ are known at the AP.\footnote{Due to the lack of RF chains at the passive tag, accurate and efficient CSI acquisition at the AP can be challenging.
-One possible approach is that the AP sends known pilots, the tag responds in a pre-defined manner, and the user performs least-square estimation then feeds back to the AP \cite{Bharadia2015,Yang2015b,Guo2019g}.} It is assumed that the primary symbol $s$ follows standard CSCG distribution $\mathcal{CN}(0,1)$ and the secondary symbol $c$ employs $M$-PSK modulation by \eqref{eq:backscatter_modulation}.
-Due to the practical constraints on switching speed and synchronization gap, the passive tag typically transmits at a much lower data rate than the AP.
+	% 	As shown in Fig.~NULL, we propose a single-user (\gls{ue}) single-tag (\gls{tg}) symbiotic radio network where the \gls{rf} signal generated by the single-antenna Access Point (\gls{ap}) is shared by two coexisting systems.
+In the primary \gls{ap}-\gls{ue} downlink system, the \gls{ap} transmits to the single-antenna user.
+In the secondary \gls{ap}-\gls{tg}-\gls{ue} backscatter system, the \gls{ap} acts as the carrier emitter, the user serves as the backscatter reader, and the single-antenna tag modulates its information over the reradiated \gls{rf} signal by varying the reflection coefficient.
+Denote the \gls{ap}-\gls{ue} direct channel as $h_{\mathrm{D}}$, the \gls{ap}-\gls{tg} forward channel as $h_{\mathrm{F}}$, and the \gls{tg}-\gls{ue} backward channel as $h_{\mathrm{B}}$.
+We consider the quasi-static block fading model and assume the CSI of the direct channel and the cascaded forward-backward channel $h_{\mathrm{C}} \triangleq h_{\mathrm{B}} h_{\mathrm{F}}$ are known at the \gls{ap}.\footnote{Due to the lack of \gls{rf} chains at the passive tag, accurate and efficient CSI acquisition at the \gls{ap} can be challenging.
+One possible approach is that the \gls{ap} sends known pilots, the tag responds in a pre-defined manner, and the user performs least-square estimation then feeds back to the \gls{ap} \cite{Bharadia2015,Yang2015b,Guo2019g}.} It is assumed that the primary symbol $s$ follows standard \gls{cscg} distribution $\mathcal{CN}(0,1)$ and the secondary symbol $c$ employs $M$-\gls{psk} modulation by \eqref{eq:backscatter_modulation}.
+Due to the practical constraints on switching speed and synchronization gap, the passive tag typically transmits at a much lower data rate than the \gls{ap}.
 Hence, we assume the secondary symbol period is $N \gg 1 \in \mathbb{Z}_{++}$ times the primary symbol period and focus on the interval of one particular $c$.
-At (primary) symbol block $n \in \mathcal{N} \triangleq \{1,\ldots,N\}$, the user simultaneously captures the signal from both primary and secondary links as\footnote{We assume the time difference of arrival from the AP-UE path and the AP-TG-UE path are negligible compared to the symbol period \cite{Guo2019b,Liang2020,Long2020b}.}
+At (primary) symbol block $n \in \mathcal{N} \triangleq \{1,\ldots,N\}$, the user simultaneously captures the signal from both primary and secondary links as\footnote{We assume the time difference of arrival from the \gls{ap}-\gls{ue} path and the \gls{ap}-\gls{tg}-\gls{ue} path are negligible compared to the symbol period \cite{Guo2019b,Liang2020,Long2020b}.}
 	% 	\begin{equation}
@@
 	% 	\end{equation}
-	% 	where $P$ is the average transmit power at the AP and $w \sim \mathcal{CN}(0,\sigma^2)$ is the additive white Gaussian noise.
+	% 	where $P$ is the average transmit power at the \gls{ap} and $w \sim \mathcal{CN}(0,\sigma^2)$ is the additive white Gaussian noise.
 We also define $\boldsymbol{y} \triangleq \bigl[y[1],\ldots,y[N]\bigr]^T$.
@@
 	% 	\begin{remark}
-	% 		The symbiotic radio network can be regarded as a special case of Multiple Access Channel (MAC) because the AP and the tag simultaneously transmit to the user.
-It is known that Superposition Coding-Successive Interference Cancellation (SC-SIC) with different decoding orders can achieve different vertices of the MAC capacity region \cite{Goldsmith2005}.
+	% 		The symbiotic radio network can be regarded as a special case of Multiple Access Channel (\gls{mac}) because the \gls{ap} and the tag simultaneously transmit to the user.
+It is known that Superposition Coding-Successive Interference Cancellation (\gls{sc}-\gls{sic}) with different decoding orders can achieve different vertices of the \gls{mac} capacity region \cite{Goldsmith2005}.
 Therefore, most relevant papers proposed the user to first decode the primary message (by treating the tag interference as noise), cancel out its contribution from the received signal, then decode the secondary message.
@@
 	% 	\begin{remark}
-	% 		The main difference between symbiotic radio and conventional MAC is that the primary message also reaches the user from the backscatter link.
-This characteristic inspires one to first decode the tag message, then model its contribution within the equivalent channel during primary decoding (i.e., unify backscatter decoding and channel training), instead of performing SIC.
+	% 		The main difference between symbiotic radio and conventional \gls{mac} is that the primary message also reaches the user from the backscatter link.
+This characteristic inspires one to first decode the tag message, then model its contribution within the equivalent channel during primary decoding (i.e., unify backscatter decoding and channel training), instead of performing \gls{sic}.
 In such case, the reflection pattern not only embeds the tag message but also adjusts the legacy channel in a controllable manner.
@@
 	% 		To investigate how backscatter modulation potentially benefits the primary transmission, we first decode the tag symbol $c$ in presence of the interference from the primary message $\boldsymbol{s}$.
-In such case, the detection indeed coincides with that of Ambient Backscatter Communications (AmBC) where the signaling from the ambient source is unknown, and the received signal per symbol block follows the CSCG distribution of $y_m[n] \sim \mathcal{CN}(0,\sigma_m^2)$, where
+In such case, the detection indeed coincides with that of Ambient Backscatter Communications (\gls{ambc}) where the signaling from the ambient source is unknown, and the received signal per symbol block follows the \gls{cscg} distribution of $y_m[n] \sim \mathcal{CN}(0,\sigma_m^2)$, where
 	% 		\begin{equation}
@@
 Denote $\mathcal{H}_i$ as the hypothesis that the tag transmits $c_i$.
-Following \cite{Qian2019}, the optimal Maximum-Likelihood (ML) detector boils down to the energy detector, and the likelihood ratio between hypotheses $\mathcal{H}_i$ and $\mathcal{H}_j$ is
+Following \cite{Qian2019}, the optimal Maximum-Likelihood (\gls{ml}) detector boils down to the energy detector, and the likelihood ratio between hypotheses $\mathcal{H}_i$ and $\mathcal{H}_j$ is
 	% 		\begin{equation}
@@
 	% 	\begin{subsection}{Legacy Transmission}
-	% 		Once the backscattered symbol is successfully recovered, it is combined with the cascaded channel to eliminate the uncertainty of the AP-TG-UE path and assist the legacy transmission.
+	% 		Once the backscattered symbol is successfully recovered, it is combined with the cascaded channel to eliminate the uncertainty of the \gls{ap}-\gls{tg}-\gls{ue} path and assist the legacy transmission.
 Therefore, the received signal at symbol block $n$ is essentially
@@
 	% 		\end{equation}
-	% 		which is reminiscent of an IRS-aided point-to-point transmission with an equivalent channel of
+	% 		which is reminiscent of an \gls{irs}-aided point-to-point transmission with an equivalent channel of
 	% 		\begin{equation}
@@
 	% 		\end{equation}
-	% 		For primary transmission, backscatter modulation creates an artificial fast fading within each fading block, and AP can obtain the equivalent CSI distribution for any given tag input probability mass function $\boldsymbol{r}$.
+	% 		For primary transmission, backscatter modulation creates an artificial fast fading within each fading block, and \gls{ap} can obtain the equivalent CSI distribution for any given tag input probability mass function $\boldsymbol{r}$.
 Therefore, the ergodic capacity of primary transmission within each symbol block is \cite{Tse2005}
@@
 	% 	\begin{subsection}{Achievable rate region}
-	% 		To achieve a flexible tradeoff between the backscatter and legacy links, we aims to optimize the tag input probability mass function, under $M$-PSK modulation, to maximize the weighted sum of the primary and secondary rates subject to the sum-probability constraint
+	% 		To achieve a flexible tradeoff between the backscatter and legacy links, we aims to optimize the tag input probability mass function, under $M$-\gls{psk} modulation, to maximize the weighted sum of the primary and secondary rates subject to the sum-probability constraint
 	% 		\begin{maxi!}
@@
 	% \begin{section}{OFDM}
-	% 	Due to the constraint of energy detection, with single-antenna tags and reader, at most one AmBC tag can be decoded at a time and accurate detection requires repetition coding over multiple time/frequency blocks to mitigate the impact of primary symbols.
+	% 	Due to the constraint of energy detection, with single-antenna tags and reader, at most one \gls{ambc} tag can be decoded at a time and accurate detection requires repetition coding over multiple time/frequency blocks to mitigate the impact of primary symbols.
 Here we consider frequency-independent tag reflection and schedule one tag per OFDM symbol.
 
-	% 	At OFDM symbol $r$, tag $l$ modulates its own information over all $N$ subcarriers while the remaining tags may operate in the cooperative (quantized IRS) mode.
+	% 	At OFDM symbol $r$, tag $l$ modulates its own information over all $N$ subcarriers while the remaining tags may operate in the cooperative (quantized \gls{irs}) mode.
 Channel frequency response at subband $n$ and block $r$
@@
 	% 	In this case, although we can independently maximize the primary/secondary rate in closed form (resp.
-quantized IRS and multi-user Blahut-Arimoto), the joint form can be tricky due to the $K$-product term.
+quantized \gls{irs} and multi-user Blahut-Arimoto), the joint form can be tricky due to the $K$-product term.
 We may consider a 2-loop iterative algorithm, where the inner loop optimizes input distribution over letters while the outer loop over users.
@@
 	% 	On the other hand, we can compute the rate region of the user and $K$ tags.
-However, the capacity region of discrete MAC remains unknown.
+However, the capacity region of discrete \gls{mac} remains unknown.
 We can obtain its outer bound by formulating a non-convex problem with a rank-1 constraint, then solve the relaxed problem.

### 2021-12-14 main.tex
:pencil: Update information-related functions

@@
 			where $T_{i-1,i}$ is the decision threshold between $\mathcal{H}_{i-1}$ and $\mathcal{H}_i$, and $T_{i,i+1}$ is the decision threshold between $\mathcal{H}_i$ and $\mathcal{H}_{i+1}$.
-We also define $T_{0,1} \triangleq 0$, $T_{M^K,M^K+1} \triangleq \infty$, and $\mathcal{T} \triangleq \{T_{0,1},\ldots,T_{M^K,M^K+1}\}$.
+We also define $T_{0,1} \triangleq 0$, $T_{M^K,M^K+1} \triangleq \infty$, and $\boldsymbol{t} \triangleq [T_{0,1},\ldots,T_{M^K,M^K+1}]^T \in \mathbb{R}^{(M^K + 1) \times 1}$.
 
@@
 
-			On top of this, we can compute the marginal probability on all tags and obtain $K$ transition matrices from $\mathcal{M}$ to $\mathcal{M^K}$ that compose a discrete memoryless \gls{mac}.
+			On top of this, we can compute the marginal probability of each tag and obtain $K$ transition matrices from $\mathcal{M}$ to $\mathcal{M^K}$ that compose a discrete memoryless \gls{mac}.
 The probability of observing energy level $j$ when tag $k$ at status $m_k$ is
@@
 			We first introduce some prerequisites of information theory.
-Define the input probability distribution of tag $k$ at status $m_k$ as $P_k(\bar{c}_{m_k})$, collect the input probability distribution of all tags at all states into $\mathcal{P} \triangleq \{P_k(\bar{c}_{m_k}) : m_k \in \mathcal{M}, k \in \mathcal{K}\}$, and assume the input distribution of all tags are mutually independent, such that $P_{\mathcal{K}}(\bar{c}_{m_{\mathcal{K}}}) = \prod_{k \in \mathcal{K}} P_k(\bar{c}_{m_k})$.
+Define the input probability distribution of tag $k$ at status $m_k$ as $P_k(\bar{c}_{m_k})$, and let $\boldsymbol{p}_k \triangleq [P_k(\bar{c}_1),\ldots,P_k(\bar{c}_M)]^T \in \mathbb{R}^{M \times 1}$, $\boldsymbol{P} \triangleq [\boldsymbol{p}_1^T,\ldots,\boldsymbol{p}_K^T]^T \in \mathbb{R}^{M \times K}$.
+Assume the input distribution of all tags are mutually independent such that $P_{\mathcal{K}}(\bar{c}_{m_{\mathcal{K}}}) = \prod_{k \in \mathcal{K}} P_k(\bar{c}_{m_k})$.
 Following \cite{Rezaeian2004}, the backscatter information function associated with tag input combination $\bar{c}_{m_{\mathcal{K}}}$ is defined as
@@
 				I_{\mathrm{B}}(\bar{c}_{m_{\mathcal{K}}} ; z) \triangleq \sum_j P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K}}}) \log \frac{P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K}}})}{P(\bar{z}_j)},
-				\label{eq:information_function}
+				\label{eq:backscatter_information_function}
 			\end{equation}
-			the marginal information function on $\mathcal{S} \subset \mathcal{K}$ is defined as
+			% \begin{align}
+			% 	I_{\mathrm{B}}(\bar{c}_{m_{\mathcal{K}}} ; z)
+			% 	& \triangleq \sum_j P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K}}}) \log \frac{P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K}}})}{P(\bar{z}_j)}\\
+			% 	& = \sum_j P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K}}}) \log \frac{P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K}}})}{\sum_{m_{\mathcal{K}}} \prod_{k \in \mathcal{K}} P(\bar{c}_{m_{\mathcal{K}}}) P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K}}})}
+			% 	\label{eq:backscatter_information_function}
+			% \end{align}
+			the backscatter marginal information function of tag $k$ associated with $\bar{c}_{m_{k}}$ is defined as
 			\begin{equation}
-				I_{\mathrm{B},\mathcal{S}}(\bar{c}_{m_{\mathcal{S}}} ; z) = \sum_{m_{\mathcal{K} \setminus \mathcal{S}}} P_{\mathcal{K} \setminus \mathcal{S}}(\bar{c}_{m_{\mathcal{K} \setminus \mathcal{S}}}) I_{\mathrm{B}}(\bar{c}_{m_{\mathcal{K}}} ; z),
-				\label{eq:marginal_information_function}
+				I_{\mathrm{B},k}(\bar{c}_{m_{k}} ; z) \triangleq \sum_{m_{\mathcal{K} \setminus \{k\}}} \prod_{k' \in \mathcal{K} \setminus \{k\}} P_{k'}(\bar{c}_{m_{k'}}) I_{\mathrm{B}}(\bar{c}_{m_{\mathcal{K}}} ; z),
+				\label{eq:backscatter_marginal_information_function}
 			\end{equation}
-			and the mutual information can be expressed as\footnote{Please be aware that $c_{\mathcal{K}}$, $c_{\mathcal{S}}$, $z$ are random variables, while $\bar{c}_{m_{\mathcal{K}}}$ and $\bar{c}_i$, $\bar{c}_{m_{\mathcal{S}}}$, $\bar{z}_j$ represent the corresponding instances.}
+			% \begin{align}
+			% 	I_{\mathrm{B},k}(\bar{c}_{m_{k}} ; z)
+			% 	& \triangleq \sum_{m_{\mathcal{K} \setminus \{k\}}} P_{\mathcal{K} \setminus \{k\}}(\bar{c}_{m_{\mathcal{K} \setminus \{k\}}}) I_{\mathrm{B}}(\bar{c}_{m_{\mathcal{K}}} ; z)\\
+			% 	& = \sum_{m_{\mathcal{K} \setminus \{k\}}} \prod_{k' \in \mathcal{K} \setminus \{k\}} P_{k'}(\bar{c}_{m_{k'}}) I_{\mathrm{B}}(\bar{c}_{m_{\mathcal{K}}} ; z),
+			% 	\label{eq:backscatter_marginal_information_function}
+			% \end{align}
+			% the backscatter marginal information function of $\mathcal{S} \subset \mathcal{K}$ is defined as
+			% \begin{equation}
+			% 	I_{\mathrm{B},\mathcal{S}}(\bar{c}_{m_{\mathcal{S}}} ; z) \triangleq \sum_{m_{\mathcal{K} \setminus \mathcal{S}}} P_{\mathcal{K} \setminus \mathcal{S}}(\bar{c}_{m_{\mathcal{K} \setminus \mathcal{S}}}) I_{\mathrm{B}}(\bar{c}_{m_{\mathcal{K}}} ; z),
+			% 	\label{eq:backscatter_marginal_information_function}
+			% \end{equation}
+			and the backscatter mutual information can be expressed as\footnote{Please be aware that $c_{\mathcal{K}}$, $c_{\mathcal{S}}$, $z$ are random variables, while $\bar{c}_{m_{\mathcal{K}}}$ and $\bar{c}_i$, $\bar{c}_{m_{\mathcal{S}}}$, $\bar{z}_j$ represent the corresponding instances.}
 			\begin{align}
 				I_{\mathrm{B}}(c_{\mathcal{K}} ; z)
-				& = \mathbb{E}_{c_{\mathcal{K}}} \left[I_{\mathrm{B}}(\bar{c}_{m_{\mathcal{K}}} ; z)\right] = \mathbb{E}_{c_{\mathcal{S}}} \left[I_{\mathrm{B},\mathcal{S}}(\bar{c}_{m_{\mathcal{S}}} ; z)\right]\label{eq:mutual_information}\\
+				& = \mathbb{E}_{c_{\mathcal{K}}} \left[I_{\mathrm{B}}(\bar{c}_{m_{\mathcal{K}}} ; z)\right] = \mathbb{E}_{c_{k}} \left[I_{\mathrm{B},k}(\bar{c}_{m_{k}} ; z)\right]\\
 				& = \sum_{m_{\mathcal{K}}} \prod_{k \in \mathcal{K}} P_k(\bar{c}_{m_k}) \sum_j P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K}}}) \log \frac{P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K}}})}{P(\bar{z}_j)}.\label{eq:backscatter_sum_rate}
 			\end{align}
+			% \begin{align}
+			% 	I_{\mathrm{B}}(c_{\mathcal{K}} ; z)
+			% 	& = \mathbb{E}_{c_{\mathcal{K}}} \left[I_{\mathrm{B}}(\bar{c}_{m_{\mathcal{K}}} ; z)\right] = \mathbb{E}_{c_{\mathcal{S}}} \left[I_{\mathrm{B},\mathcal{S}}(\bar{c}_{m_{\mathcal{S}}} ; z)\right]\\
+			% 	& = \sum_{m_{\mathcal{K}}} \prod_{k \in \mathcal{K}} P_k(\bar{c}_{m_k}) \sum_j P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K}}}) \log \frac{P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K}}})}{P(\bar{z}_j)}.\label{eq:backscatter_sum_rate}
+			% \end{align}
 
-			Evidently, for a given discrete memoryless \gls{mac} with transition probability $P(z \mid c_{\mathcal{K}})$, the information function $I_{\mathrm{B}}(\bar{c}_{m_{\mathcal{K}}} ; z)$ and mutual information $I_{\mathrm{B}}(c_{\mathcal{K}} ; z)$ only depend on the tag input distribution $\mathcal{P}$.\footnote{Note that the contribution of the precoder and detection threshold are modelled within the discrete memoryless \gls{mac}.}
+			Evidently, \eqref{eq:backscatter_information_function}--\eqref{eq:backscatter_sum_rate} are functions of the tag input distribution $\boldsymbol{P}$ as well as the discrete memoryless \gls{mac} $P(z \mid c_{\mathcal{K}})$, and thus depend on the transmit precoder $\boldsymbol{w}$ and the detection threshold $\boldsymbol{t}$.
 		\end{subsection}
@@
 As such, the tags can adjust the propagation environment in a potentially beneficial manner, and create artificial channel variation within each fading block.
-Hence, the ergodic primary rate can be expressed as \footnote{The unit of \eqref{eq:backscatter_sum_rate} is \gls{bpcu} while the unit of \eqref{eq:primary_ergodic_rate} is \gls{bpsphz}.}
+Similarly, we define the primary information function associated with tag input combination $\bar{c}_{m_{\mathcal{K}}}$ and the primary marginal information function of tag $k$ associated with symbol $\bar{c}_{m_{k}}$ respectively as
+			\begin{equation}
+				I_{\mathrm{P}}(\bar{c}_{m_{\mathcal{K}}} ; \boldsymbol{y}) \triangleq N \log_2 \left(1 + \frac{\lvert \boldsymbol{h}_{\mathrm{E}}^H(\bar{c}_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_w^2}\right),
+				\label{eq:primary_information_function}
+			\end{equation}
+			\begin{equation}
+				I_{\mathrm{P},k}(\bar{c}_{m_{k}} ; \boldsymbol{y}) \triangleq \sum_{m_{\mathcal{K} \setminus \{k\}}} \prod_{k' \in \mathcal{K} \setminus \{k\}} P_{k'}(\bar{c}_{m_{k'}}) I_{\mathrm{P}}(\bar{c}_{m_{\mathcal{K}}} ; \boldsymbol{y}),
+				\label{eq:primary_marginal_information_function}
+			\end{equation}
+			% \begin{equation}
+			% 	I_{\mathrm{P},k}(\bar{c}_{m_{k}}) \triangleq \sum_{m_{\mathcal{K} \setminus \{k\}}} P_{\mathcal{K} \setminus \{k\}}(\bar{c}_{m_{\mathcal{K} \setminus \{k\}}}) I_{\mathrm{P}}(\bar{c}_{m_{\mathcal{K}}}),
+			% 	\label{eq:primary_marginal_information_function}
+			% \end{equation}
+			% \begin{equation}
+			% 	I_{\mathrm{P},\mathcal{S}}(\bar{c}_{m_{\mathcal{S}}}) \triangleq \sum_{m_{\mathcal{K} \setminus \mathcal{S}}} P_{\mathcal{K} \setminus \mathcal{S}}(\bar{c}_{m_{\mathcal{K} \setminus \mathcal{S}}}) I_{\mathrm{P}}(\bar{c}_{m_{\mathcal{K}}}),
+			% 	\label{eq:primary_marginal_information_function}
+			% \end{equation}
+			and the ergodic primary rate can be expressed as \footnote{The unit of \eqref{eq:backscatter_information_function}, \eqref{eq:backscatter_marginal_information_function} and \eqref{eq:backscatter_sum_rate} are \gls{bpcu}, while the unit of \eqref{eq:primary_information_function}, \eqref{eq:primary_marginal_information_function} and \eqref{eq:primary_ergodic_rate} are \gls{bpsphz}.}
 			\begin{align}
-				I_{\mathrm{P}}
-				& = \mathbb{E}_{c_{\mathcal{K}}} \left[\log_2 \left(1 + \frac{\lvert \boldsymbol{h}_{\mathrm{E}}^H(c_{\mathcal{K}}) \boldsymbol{w} \rvert^2}{\sigma_w^2}\right)\right]\nonumber\\
-				& = \sum_{m_{\mathcal{K}}} \prod_{k \in \mathcal{K}} P_k(\bar{c}_{m_k}) \log_2 \left(1 + \frac{\lvert \boldsymbol{h}_{\mathrm{E}}^H(\bar{c}_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_w^2}\right).
+				I_{\mathrm{P}}(c_{\mathcal{K}} ; \boldsymbol{y})
+				& = \mathbb{E}_{c_{\mathcal{K}}} \left[I_{\mathrm{P}}(\bar{c}_{m_{\mathcal{K}}} ; \boldsymbol{y})\right] = \mathbb{E}_{c_{k}} \left[I_{\mathrm{P},k}(\bar{c}_{m_{k}} ; \boldsymbol{y})\right]\\
+				& = \sum_{m_{\mathcal{K}}} \prod_{k \in \mathcal{K}} P_k(\bar{c}_{m_k}) N \log_2 \left(1 + \frac{\lvert \boldsymbol{h}_{\mathrm{E}}^H(\bar{c}_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_w^2}\right).
 				\label{eq:primary_ergodic_rate}
 			\end{align}
-			which is also a function of the tag input distribution $\mathcal{P}$.
-			% $P(c_{\mathcal{K}})$.
+			% \begin{align}
+			% 	I_{\mathrm{P}}(c_{\mathcal{K}})
+			% 	& = \mathbb{E}_{c_{\mathcal{K}}} \left[I_{\mathrm{P}}(\bar{c}_{m_{\mathcal{K}}})\right] = \mathbb{E}_{c_{\mathcal{S}}} \left[I_{\mathrm{P},\mathcal{S}}(\bar{c}_{m_{\mathcal{S}}})\right]\\
+			% 	& = \sum_{m_{\mathcal{K}}} \prod_{k \in \mathcal{K}} P_k(\bar{c}_{m_k}) \log_2 \left(1 + \frac{\lvert \boldsymbol{h}_{\mathrm{E}}^H(\bar{c}_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_w^2}\right).
+			% 	\label{eq:primary_ergodic_rate}
+			% \end{align}
+
+			In contrast to the backscatter case, \eqref{eq:primary_information_function}--\eqref{eq:primary_ergodic_rate} are irrelevant to the detection threshold $\boldsymbol{t}$, but depend on the tag input probability distribution $\boldsymbol{P}$ and the transmit precoder $\boldsymbol{w}$.
 		\end{subsection}
@@
 		\begin{subsection}{Primary-backscatter rate region}
-			Define the weighted sum primary-backscatter rate as
-			\begin{equation}
-				I \triangleq \rho I_{\mathrm{B}}(c_{\mathcal{K}} ; z) + (1 - \rho) I_{\mathrm{P}},
-			\end{equation}
+			First, we define the weighted sum marginal information of tag $k$ associated with symbol $\bar{c}_{m_{k}}$ and the weighted sum primary-backscatter rate respectively as
+			\begin{align}
+				I_{q}(\bar{c}_{m_{k}} ; \boldsymbol{y},z)
+				& \triangleq \rho I_{\mathrm{P},q}(\bar{c}_{m_{k}} ; \boldsymbol{y}) + (1 - \rho) I_{\mathrm{B},q}(\bar{c}_{m_{k}} ; z),\\
+				I(c_{\mathcal{K}} ; \boldsymbol{y}, z)
+				& \triangleq \rho I_{\mathrm{P}}(c_{\mathcal{K}} ; \boldsymbol{y}) + (1 - \rho) I_{\mathrm{B}}(c_{\mathcal{K}} ; z)
+			\end{align}
 			where $\rho \in [0,1]$ denotes the priority of the primary link.
@@
 			\begin{maxi!}
-				{\scriptstyle{\mathcal{P},\mathcal{T},\boldsymbol{w}}}{I}{\label{op:rate_region}}{\label{ob:weighted_sum_rate}}
+				{\scriptstyle{\boldsymbol{P},\boldsymbol{t},\boldsymbol{w}}}{I}{\label{op:rate_region}}{\label{ob:weighted_sum_rate}}
 				\addConstraint{\sum \nolimits_{m_k} P_k(\bar{c}_{m_k})}{=1,\quad\label{co:sum_probability}}{\forall k \in \mathcal{K}}
@@
 
-			As problem \eqref{op:rate_region} is not jointly convex over $\mathcal{P}$, $\mathcal{T}$ and $\boldsymbol{w}$, we propose a \gls{bcd} method that iteratively updates the input distribution, decision region, and transmit precoder, until convergence is achieved.
+			As problem \eqref{op:rate_region} is not jointly convex over $\boldsymbol{P}$, $\boldsymbol{t}$ and $\boldsymbol{w}$, we propose a \gls{bcd} method that iteratively updates the input distribution, decision region, and transmit precoder, until convergence is achieved.
 		\end{subsection}
@@
 		\begin{subsection}{Input probability distribution}
-			For any fixed decision boundary $\mathcal{T}$ and transmit precoder $\boldsymbol{w}$, the equivalent discrete memoryless \gls{mac} can be determined by \eqref{eq:mac}, and problem~\eqref{op:rate_region} boils down to
+			For any fixed decision boundary $\boldsymbol{t}$ and transmit precoder $\boldsymbol{w}$, the equivalent discrete memoryless \gls{mac} can be determined by \eqref{eq:mac} and problem~\eqref{op:rate_region} boils down to
 			\begin{maxi!}
-				{\scriptstyle{\mathcal{P}}}{I}{\label{op:input_probability_distribution}}{}
+				{\scriptstyle{\boldsymbol{P}}}{I}{\label{op:input_probability_distribution}}{}
 				\addConstraint{\eqref{co:sum_probability},\eqref{co:nonnegative_probability},}
@@
 For any general discrete memoryless \gls{mac}, the capacity can be achieved by an elementary discrete memoryless \gls{mac} included within.
-Thus, we restrict the discussion of this paper to elementary discrete memoryless \gls{mac}s.}
+Thus, we restrict the discussion of this paper to elementary discrete memoryless \gls{mac}s.} Denote the Lagrange multiplier associated with \eqref{co:sum_probability} and \eqref{co:nonnegative_probability} as $\boldsymbol{\mu} \triangleq [\mu_1,\ldots,\mu_K]^T \in \mathbb{R}^{K \times 1}$ and $\boldsymbol{\Lambda} \triangleq [\boldsymbol{\lambda}_1^T,\ldots,\boldsymbol{\lambda}_K^T]^T \in \mathbb{R}^{M \times K}$ with $\boldsymbol{\lambda}_k \triangleq [\lambda_{k,1},\ldots,\lambda_{k,M}]^T \in \mathbb{R}^{M \times 1}$, respectively.
+The Lagrangian function of problem~\eqref{op:input_probability_distribution} is
+			\begin{align}
+				J
+				& = - I + \sum_{k \in \mathcal{K}} \mu_k \left( \sum_{m_k \in \mathcal{M}} P_k(\bar{c}_{m_k}) - 1 \right)\nonumber\\
+				& \quad - \sum_{k \in \mathcal{K}} \sum_{m_k \in \mathcal{M}} \lambda_{k,m_k} P_k(\bar{c}_{m_k}),
+			\end{align}
+			and the corresponding \gls{kkt} conditions on the primal and dual solutions are, $\forall i_q \in \mathcal{M}$ and $\forall q \in \mathcal{K}$,
+			\begin{subequations}
+				\begin{equation}
+					- \pdv{I}{P_q^{\star}(\bar{c}_{i_q})} + \mu_q^{\star} - \lambda_{q,i_q}^{\star} = 0,
+				\end{equation}
+				\begin{equation}
+					\lambda_{q,i_q}^{\star} = 0, \quad P_q^{\star}(\bar{c}_{i_q}) > 0,
+				\end{equation}
+				\begin{equation}
+					\lambda_{q,i_q}^{\star} \ge 0, \quad P_q^{\star}(\bar{c}_{i_q}) = 0,
+				\end{equation}
+			\end{subequations}
+			and the partial derivative can be explicitly expressed as
+			% \begin{equation}
+			% 	\pdv{I}{P_q^{\star}(\bar{c}_{i_q})} = \rho I_{\mathrm{P},q}(\bar{c}_{i_q} ; \boldsymbol{y}) + (1 - \rho) \left( I_{\mathrm{B},q}(\bar{c}_{i_q} ; z) - 1 \right).
+			% \end{equation}
+			\begin{align}
+				\pdv{I}{P_q^{\star}(\bar{c}_{i_q})}
+				& = \rho I_{\mathrm{P},q}(\bar{c}_{i_q} ; \boldsymbol{y}) + (1 - \rho) \left( I_{\mathrm{B},q}(\bar{c}_{i_q} ; z) - 1 \right)\\
+				& = I_{q}(\bar{c}_{i_q} ; \boldsymbol{y},z) - (1 - \rho).
+			\end{align}
+			which suggests $\mu_q^{\star}$ must satisfy
+			\begin{subequations}
+				\begin{equation}
+					\mu_q^{\star} = I_{q}(\bar{c}_{i_q} ; \boldsymbol{y},z) - (1 - \rho), \quad P_q^{\star}(\bar{c}_{i_q}) > 0,
+				\end{equation}
+				\begin{equation}
+					\mu_q^{\star} \ge I_{q}(\bar{c}_{i_q} ; \boldsymbol{y},z) - (1 - \rho), \quad P_q^{\star}(\bar{c}_{i_q}) = 0.
+				\end{equation}
+			\end{subequations}
 
-			% Although the domain is non-convex for $K>1$, the \gls{kkt} conditions are sufficient and necessary for an input distribution to achieve the weighted sum-capacity.
-The proof follows straightforwardly from \cite{Watanabe2009} and details are omitted here.\footnote{For any elementary \gls{mac} (the sizes of input alphabets are no greater than that of the output alphabet), the sufficiency can be proved by local maximum and connectedness of \gls{kkt} solutions.
-Also, the capacity of an arbitrary \gls{mac} is achieved by an elementary \gls{mac} included within.}
-			% We restrict the discussion of this paper to elementary \gls{mac}s.
-
+			Due to the sufficiency and necessity of the \gls{kkt} conditions, we can conclude that any input probability distribution $\boldsymbol{P}^{\star}$ maximizes the weighted sum primary-backscatter rate if and only if, $\forall i_q \in \mathcal{M}$ and $\forall q \in \mathcal{K}$,
+			\begin{subequations}
+				\begin{equation}
+					I_{q}(\bar{c}_{i_q} ; \boldsymbol{y},z) = C_q, \quad P_q^{\star}(\bar{c}_{i_q}) > 0,
+				\end{equation}
+				\begin{equation}
+					I_{q}(\bar{c}_{i_q} ; \boldsymbol{y},z) \le C_q, \quad P_q^{\star}(\bar{c}_{i_q}) = 0,
+				\end{equation}
+			\end{subequations}
 		\end{subsection}
@@
 			As indicated by \cite{Qian2019b}, the optimal \gls{ml} decision regions are very close to the optimal decision regions to problem \eqref{op:rate_region}.
-We can either use \eqref{eq:decision_region} as suboptimal, or take derivative of \eqref{eq:mutual_information} w.r.t.
+We can either use \eqref{eq:decision_region} as suboptimal, or take derivative of \eqref{eq:backscatter_sum_rate} w.r.t.
 $T_{i-1,i}$ and $T_{i,i+1}$ (however, closed-form solutions are unavailable and two-dimensional search is needed).
@@
 				& \quad \times \log \frac{\int_{T_{j-1,j}}^{T_{j,j+1}} \frac{z^{N-1} \exp \left(-\frac{z}{\mathrm{tr}(H_{\mathrm{E},i} W) + \sigma_w^2}\right)}{\left(\mathrm{tr}(H_{\mathrm{E},i} W) + \sigma_w^2\right)^N (N-1)!} \dd z}{\sum_{i' \in \mathcal{M^K}} \int_{T_{j-1,j}}^{T_{j,j+1}} \frac{z^{N-1} \exp \left(-\frac{z}{\mathrm{tr}(H_{\mathrm{E},i'} W) + \sigma_w^2}\right)}{\left(\mathrm{tr}(H_{\mathrm{E},i'} W) + \sigma_w^2\right)^N (N-1)!} \dd z},
-				\label{eq:information_function_precoder}
+				\label{eq:foo}
 			\end{align}
-			and the mutual information can be expressed as a function of $W$ by combining \eqref{eq:mutual_information} and \eqref{eq:information_function_precoder}.
+			and the mutual information can be expressed as a function of $W$ by combining \eqref{eq:backscatter_sum_rate} and \eqref{eq:foo}.
 

### 2021-12-15 main.tex
:pencil: Add optimality conditions of input distribution

@@
 			\begin{equation}
-				I_{\mathrm{B}}(\bar{c}_{m_{\mathcal{K}}} ; z) \triangleq \sum_j P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K}}}) \log \frac{P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K}}})}{P(\bar{z}_j)},
+				I_{\mathrm{B}}(\bar{c}_{m_{\mathcal{K}}};z) \triangleq \sum_j P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K}}}) \log \frac{P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K}}})}{P(\bar{z}_j)},
 				\label{eq:backscatter_information_function}
@@
 			% \begin{align}
-			% 	I_{\mathrm{B}}(\bar{c}_{m_{\mathcal{K}}} ; z)
+			% 	I_{\mathrm{B}}(\bar{c}_{m_{\mathcal{K}}};z)
 			% 	& \triangleq \sum_j P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K}}}) \log \frac{P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K}}})}{P(\bar{z}_j)}\\
@@
 			% \end{align}
-			the backscatter marginal information function of tag $k$ associated with $\bar{c}_{m_{k}}$ is defined as
+			the backscatter marginal information function of tag $q \in \mathcal{K}$ associated with $\bar{c}_{i_q}$, $i_q \in \mathcal{M}$ is defined as
 			\begin{equation}
-				I_{\mathrm{B},k}(\bar{c}_{m_{k}} ; z) \triangleq \sum_{m_{\mathcal{K} \setminus \{k\}}} \prod_{k' \in \mathcal{K} \setminus \{k\}} P_{k'}(\bar{c}_{m_{k'}}) I_{\mathrm{B}}(\bar{c}_{m_{\mathcal{K}}} ; z),
+				I_{\mathrm{B},q}(\bar{c}_{i_q};z) \triangleq \sum_{m_{\mathcal{K} \setminus \{q\}}} \prod_{k \in \mathcal{K} \setminus \{q\}} P_k(\bar{c}_{m_k}) I_{\mathrm{B}}(\bar{c}_{m_{\mathcal{K} \setminus \{q\}}},\bar{c}_{i_q};z),
 				\label{eq:backscatter_marginal_information_function}
 			\end{equation}
+			% the backscatter marginal information function of tag $k$ associated with $\bar{c}_{m_k}$ is defined as
+			% \begin{equation}
+			% 	I_{\mathrm{B},k}(\bar{c}_{m_k};z) \triangleq \sum_{m_{\mathcal{K} \setminus \{k\}}} \prod_{k' \in \mathcal{K} \setminus \{k\}} P_{k'}(\bar{c}_{m_{k'}}) I_{\mathrm{B}}(\bar{c}_{m_{\mathcal{K} \setminus \{k\}}}, \bar{c}_{m_k};z),
+			% 	% \label{eq:backscatter_marginal_information_function}
+			% \end{equation}
+			% \begin{equation}
+			% 	I_{\mathrm{B},k}(\bar{c}_{m_k};z) \triangleq \sum_{m_{\mathcal{K} \setminus \{k\}}} \prod_{k' \in \mathcal{K} \setminus \{k\}} P_{k'}(\bar{c}_{m_{k'}}) I_{\mathrm{B}}(\bar{c}_{m_{\mathcal{K}}};z),
+			% 	\label{eq:backscatter_marginal_information_function}
+			% \end{equation}
 			% \begin{align}
-			% 	I_{\mathrm{B},k}(\bar{c}_{m_{k}} ; z)
-			% 	& \triangleq \sum_{m_{\mathcal{K} \setminus \{k\}}} P_{\mathcal{K} \setminus \{k\}}(\bar{c}_{m_{\mathcal{K} \setminus \{k\}}}) I_{\mathrm{B}}(\bar{c}_{m_{\mathcal{K}}} ; z)\\
-			% 	& = \sum_{m_{\mathcal{K} \setminus \{k\}}} \prod_{k' \in \mathcal{K} \setminus \{k\}} P_{k'}(\bar{c}_{m_{k'}}) I_{\mathrm{B}}(\bar{c}_{m_{\mathcal{K}}} ; z),
-			% 	\label{eq:backscatter_marginal_information_function}
+			% 	I_{\mathrm{B},k}(\bar{c}_{m_k};z)
+			% 	& \triangleq \sum_{m_{\mathcal{K} \setminus \{k\}}} P_{\mathcal{K} \setminus \{k\}}(\bar{c}_{m_{\mathcal{K} \setminus \{k\}}}) I_{\mathrm{B}}(\bar{c}_{m_{\mathcal{K}}};z)\\
+			% 	& = \sum_{m_{\mathcal{K} \setminus \{k\}}} \prod_{k' \in \mathcal{K} \setminus \{k\}} P_{k'}(\bar{c}_{m_{k'}}) I_{\mathrm{B}}(\bar{c}_{m_{\mathcal{K}}};z),
+			% 	% \label{eq:backscatter_marginal_information_function}
 			% \end{align}
@@
 			% \begin{equation}
-			% 	I_{\mathrm{B},\mathcal{S}}(\bar{c}_{m_{\mathcal{S}}} ; z) \triangleq \sum_{m_{\mathcal{K} \setminus \mathcal{S}}} P_{\mathcal{K} \setminus \mathcal{S}}(\bar{c}_{m_{\mathcal{K} \setminus \mathcal{S}}}) I_{\mathrm{B}}(\bar{c}_{m_{\mathcal{K}}} ; z),
+			% 	I_{\mathrm{B},\mathcal{S}}(\bar{c}_{m_{\mathcal{S}}};z) \triangleq \sum_{m_{\mathcal{K} \setminus \mathcal{S}}} P_{\mathcal{K} \setminus \mathcal{S}}(\bar{c}_{m_{\mathcal{K} \setminus \mathcal{S}}}) I_{\mathrm{B}}(\bar{c}_{m_{\mathcal{K}}};z),
 			% 	\label{eq:backscatter_marginal_information_function}
 			% \end{equation}
-			and the backscatter mutual information can be expressed as\footnote{Please be aware that $c_{\mathcal{K}}$, $c_{\mathcal{S}}$, $z$ are random variables, while $\bar{c}_{m_{\mathcal{K}}}$ and $\bar{c}_i$, $\bar{c}_{m_{\mathcal{S}}}$, $\bar{z}_j$ represent the corresponding instances.}
+			and the backscatter mutual information can be expressed as\footnote{Please be aware that $c_{\mathcal{K}}$, $c_k$, $z$ are random variables, while $\bar{c}_{m_{\mathcal{K}}}$ and $\bar{c}_i$, $\bar{c}_{m_k}$, $\bar{z}_j$ represent the corresponding instances.}
+			\begin{subequations}
 				\begin{align}
-				I_{\mathrm{B}}(c_{\mathcal{K}} ; z)
-				& = \mathbb{E}_{c_{\mathcal{K}}} \left[I_{\mathrm{B}}(\bar{c}_{m_{\mathcal{K}}} ; z)\right] = \mathbb{E}_{c_{k}} \left[I_{\mathrm{B},k}(\bar{c}_{m_{k}} ; z)\right]\\
-				& = \sum_{m_{\mathcal{K}}} \prod_{k \in \mathcal{K}} P_k(\bar{c}_{m_k}) \sum_j P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K}}}) \log \frac{P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K}}})}{P(\bar{z}_j)}.\label{eq:backscatter_sum_rate}
+					I_{\mathrm{B}}(c_{\mathcal{K}};z)
+					& = \mathbb{E}_{c_{\mathcal{K}}} \left[I_{\mathrm{B}}(\bar{c}_{m_{\mathcal{K}}};z)\right] = \mathbb{E}_{c_k} \left[I_{\mathrm{B},k}(\bar{c}_{m_k};z)\right]\label{eq:backscatter_sum_rate_expectation}\\
+					& = \sum_{m_{\mathcal{K}}} \prod_{k \in \mathcal{K}} P_k(\bar{c}_{m_k}) \sum_j P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K}}}) \log \frac{P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K}}})}{P(\bar{z}_j)}.\label{eq:backscatter_sum_rate_expansion}
 				\end{align}
+				\label{eq:backscatter_sum_rate}
+			\end{subequations}
 			% \begin{align}
-			% 	I_{\mathrm{B}}(c_{\mathcal{K}} ; z)
-			% 	& = \mathbb{E}_{c_{\mathcal{K}}} \left[I_{\mathrm{B}}(\bar{c}_{m_{\mathcal{K}}} ; z)\right] = \mathbb{E}_{c_{\mathcal{S}}} \left[I_{\mathrm{B},\mathcal{S}}(\bar{c}_{m_{\mathcal{S}}} ; z)\right]\\
+			% 	I_{\mathrm{B}}(c_{\mathcal{K}};z)
+			% 	& = \mathbb{E}_{c_{\mathcal{K}}} \left[I_{\mathrm{B}}(\bar{c}_{m_{\mathcal{K}}};z)\right] = \mathbb{E}_{c_{\mathcal{S}}} \left[I_{\mathrm{B},\mathcal{S}}(\bar{c}_{m_{\mathcal{S}}};z)\right]\\
 			% 	& = \sum_{m_{\mathcal{K}}} \prod_{k \in \mathcal{K}} P_k(\bar{c}_{m_k}) \sum_j P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K}}}) \log \frac{P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K}}})}{P(\bar{z}_j)}.\label{eq:backscatter_sum_rate}
@@
 As such, the tags can adjust the propagation environment in a potentially beneficial manner, and create artificial channel variation within each fading block.
-Similarly, we define the primary information function associated with tag input combination $\bar{c}_{m_{\mathcal{K}}}$ and the primary marginal information function of tag $k$ associated with symbol $\bar{c}_{m_{k}}$ respectively as
-			\begin{equation}
-				I_{\mathrm{P}}(\bar{c}_{m_{\mathcal{K}}} ; \boldsymbol{y}) \triangleq N \log_2 \left(1 + \frac{\lvert \boldsymbol{h}_{\mathrm{E}}^H(\bar{c}_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_w^2}\right),
-				\label{eq:primary_information_function}
-			\end{equation}
-			\begin{equation}
-				I_{\mathrm{P},k}(\bar{c}_{m_{k}} ; \boldsymbol{y}) \triangleq \sum_{m_{\mathcal{K} \setminus \{k\}}} \prod_{k' \in \mathcal{K} \setminus \{k\}} P_{k'}(\bar{c}_{m_{k'}}) I_{\mathrm{P}}(\bar{c}_{m_{\mathcal{K}}} ; \boldsymbol{y}),
-				\label{eq:primary_marginal_information_function}
-			\end{equation}
+Similarly, we define the primary information function associated with tag input combination $\bar{c}_{m_{\mathcal{K}}}$ and the primary marginal information function of tag $q$ associated with symbol $\bar{c}_{i_q}$ respectively as
+			\begin{align}
+				I_{\mathrm{P}}(\bar{c}_{m_{\mathcal{K}}};\boldsymbol{y})
+				& \triangleq N \log_2 \left(1 + \frac{\lvert \boldsymbol{h}_{\mathrm{E}}^H(\bar{c}_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_w^2}\right),\label{eq:primary_information_function}\\
+				I_{\mathrm{P},q}(\bar{c}_{i_q};\boldsymbol{y})
+				& \triangleq \sum_{m_{\mathcal{K} \setminus \{q\}}} \prod_{k \in \mathcal{K} \setminus \{q\}} P_{k}(\bar{c}_{m_{k}}) I_{\mathrm{P}}(\bar{c}_{m_{\mathcal{K} \setminus \{q\}}},\bar{c}_{i_q};\boldsymbol{y}),\label{eq:primary_marginal_information_function}
+			\end{align}
 			% \begin{equation}
-			% 	I_{\mathrm{P},k}(\bar{c}_{m_{k}}) \triangleq \sum_{m_{\mathcal{K} \setminus \{k\}}} P_{\mathcal{K} \setminus \{k\}}(\bar{c}_{m_{\mathcal{K} \setminus \{k\}}}) I_{\mathrm{P}}(\bar{c}_{m_{\mathcal{K}}}),
+			% 	I_{\mathrm{P},k}(\bar{c}_{m_k};\boldsymbol{y}) \triangleq \sum_{m_{\mathcal{K} \setminus \{k\}}} \prod_{k' \in \mathcal{K} \setminus \{k\}} P_{k'}(\bar{c}_{m_{k'}}) I_{\mathrm{P}}(\bar{c}_{m_{\mathcal{K}}};\boldsymbol{y}),
+			% 	\label{eq:primary_marginal_information_function}
+			% \end{equation}
+			% \begin{equation}
+			% 	I_{\mathrm{P},k}(\bar{c}_{m_k}) \triangleq \sum_{m_{\mathcal{K} \setminus \{k\}}} P_{\mathcal{K} \setminus \{k\}}(\bar{c}_{m_{\mathcal{K} \setminus \{k\}}}) I_{\mathrm{P}}(\bar{c}_{m_{\mathcal{K}}}),
 			% 	\label{eq:primary_marginal_information_function}
@@
 			% \end{equation}
-			and the ergodic primary rate can be expressed as \footnote{The unit of \eqref{eq:backscatter_information_function}, \eqref{eq:backscatter_marginal_information_function} and \eqref{eq:backscatter_sum_rate} are \gls{bpcu}, while the unit of \eqref{eq:primary_information_function}, \eqref{eq:primary_marginal_information_function} and \eqref{eq:primary_ergodic_rate} are \gls{bpsphz}.}
+			and the ergodic primary rate can be expressed as\footnote{The unit of \eqref{eq:backscatter_information_function}--\eqref{eq:backscatter_sum_rate} are \gls{bpcu}, while the unit of \eqref{eq:primary_information_function}--\eqref{eq:primary_ergodic_rate} are \gls{bpsphz}.}
+			\begin{subequations}
 				\begin{align}
-				I_{\mathrm{P}}(c_{\mathcal{K}} ; \boldsymbol{y})
-				& = \mathbb{E}_{c_{\mathcal{K}}} \left[I_{\mathrm{P}}(\bar{c}_{m_{\mathcal{K}}} ; \boldsymbol{y})\right] = \mathbb{E}_{c_{k}} \left[I_{\mathrm{P},k}(\bar{c}_{m_{k}} ; \boldsymbol{y})\right]\\
+					I_{\mathrm{P}}(c_{\mathcal{K}};\boldsymbol{y})
+					& = \mathbb{E}_{c_{\mathcal{K}}} \left[I_{\mathrm{P}}(\bar{c}_{m_{\mathcal{K}}};\boldsymbol{y})\right] = \mathbb{E}_{c_k} \left[I_{\mathrm{P},k}(\bar{c}_{m_k};\boldsymbol{y})\right]\label{eq:primary_ergodic_rate_expectation}\\
 					& = \sum_{m_{\mathcal{K}}} \prod_{k \in \mathcal{K}} P_k(\bar{c}_{m_k}) N \log_2 \left(1 + \frac{\lvert \boldsymbol{h}_{\mathrm{E}}^H(\bar{c}_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_w^2}\right).
+					\label{eq:primary_ergodic_rate_expansion}
+				\end{align}
 				\label{eq:primary_ergodic_rate}
-			\end{align}
+			\end{subequations}
 			% \begin{align}
@@
 		\begin{subsection}{Primary-backscatter rate region}
-			First, we define the weighted sum marginal information of tag $k$ associated with symbol $\bar{c}_{m_{k}}$ and the weighted sum primary-backscatter rate respectively as
+			The weighted sum marginal information of tag $q$ associated with symbol $\bar{c}_{i_q}$ and the weighted sum primary-backscatter rate are defined respectively as
 			\begin{align}
-				I_{q}(\bar{c}_{m_{k}} ; \boldsymbol{y},z)
-				& \triangleq \rho I_{\mathrm{P},q}(\bar{c}_{m_{k}} ; \boldsymbol{y}) + (1 - \rho) I_{\mathrm{B},q}(\bar{c}_{m_{k}} ; z),\\
-				I(c_{\mathcal{K}} ; \boldsymbol{y}, z)
-				& \triangleq \rho I_{\mathrm{P}}(c_{\mathcal{K}} ; \boldsymbol{y}) + (1 - \rho) I_{\mathrm{B}}(c_{\mathcal{K}} ; z)
+				I_q(\bar{c}_{i_q};\boldsymbol{y},z)
+				& \triangleq \rho I_{\mathrm{P},q}(\bar{c}_{i_q};\boldsymbol{y}) + (1 - \rho) I_{\mathrm{B},q}(\bar{c}_{i_q};z),\label{eq:weighted_sum_marginal_information}\\
+				I(c_{\mathcal{K}};\boldsymbol{y},z)
+				& \triangleq \rho I_{\mathrm{P}}(c_{\mathcal{K}};\boldsymbol{y}) + (1 - \rho) I_{\mathrm{B}}(c_{\mathcal{K}};z),\label{eq:weighted_sum_rate}
 			\end{align}
 			where $\rho \in [0,1]$ denotes the priority of the primary link.
-To investigate how the primary and backscatter links influence each other, we optimize the input probability distribution, decision region, and transmit precoder to maximize the weighted sum rate subject to the average transmit power and input probability constraints
-
+To investigate how backscatter modulation and detection may influence the primary transmission, we optimize the input probability distribution, decision region, and transmit precoder to maximize the weighted primary-backscatter sum rate
 			\begin{maxi!}
@@
 			\end{maxi!}
-
+			where \eqref{co:sum_probability} and \eqref{co:nonnegative_probability} are input probability constraints and \eqref{co:average_transmit_power} is the average transmit power budget.
 As problem \eqref{op:rate_region} is not jointly convex over $\boldsymbol{P}$, $\boldsymbol{t}$ and $\boldsymbol{w}$, we propose a \gls{bcd} method that iteratively updates the input distribution, decision region, and transmit precoder, until convergence is achieved.
@@
 				\begin{equation}
-					\lambda_{q,i_q}^{\star} \ge 0, \quad P_q^{\star}(\bar{c}_{i_q}) = 0,
+					\lambda_{q,i_q}^{\star} \ge 0, \quad P_q^{\star}(\bar{c}_{i_q}) = 0.
 				\end{equation}
 			\end{subequations}
-			and the partial derivative can be explicitly expressed as
-			% \begin{equation}
-			% 	\pdv{I}{P_q^{\star}(\bar{c}_{i_q})} = \rho I_{\mathrm{P},q}(\bar{c}_{i_q} ; \boldsymbol{y}) + (1 - \rho) \left( I_{\mathrm{B},q}(\bar{c}_{i_q} ; z) - 1 \right).
-			% \end{equation}
+
+			The partial derivative can be explicitly expressed as
+			\begin{subequations}
 				\begin{align}
 					\pdv{I}{P_q^{\star}(\bar{c}_{i_q})}
-				& = \rho I_{\mathrm{P},q}(\bar{c}_{i_q} ; \boldsymbol{y}) + (1 - \rho) \left( I_{\mathrm{B},q}(\bar{c}_{i_q} ; z) - 1 \right)\\
-				& = I_{q}(\bar{c}_{i_q} ; \boldsymbol{y},z) - (1 - \rho).
+					& = \rho I_{\mathrm{P},q}(\bar{c}_{i_q};\boldsymbol{y}) + (1 - \rho) \left( I_{\mathrm{B},q}(\bar{c}_{i_q};z) - 1 \right)\\
+					& = I_q(\bar{c}_{i_q};\boldsymbol{y},z) - (1 - \rho),
 				\end{align}
+			\end{subequations}
 			which suggests $\mu_q^{\star}$ must satisfy
 			\begin{subequations}
-				\begin{equation}
-					\mu_q^{\star} = I_{q}(\bar{c}_{i_q} ; \boldsymbol{y},z) - (1 - \rho), \quad P_q^{\star}(\bar{c}_{i_q}) > 0,
-				\end{equation}
-				\begin{equation}
-					\mu_q^{\star} \ge I_{q}(\bar{c}_{i_q} ; \boldsymbol{y},z) - (1 - \rho), \quad P_q^{\star}(\bar{c}_{i_q}) = 0.
-				\end{equation}
+				\begin{alignat}{2}
+					\mu_q^{\star} & = I_q(\bar{c}_{i_q};\boldsymbol{y},z) - (1 - \rho), \quad && P_q^{\star}(\bar{c}_{i_q}) > 0,\\
+					\mu_q^{\star} & \ge I_q(\bar{c}_{i_q};\boldsymbol{y},z) - (1 - \rho), \quad && P_q^{\star}(\bar{c}_{i_q}) = 0.
+				\end{alignat}
 			\end{subequations}
@@
 			\begin{subequations}
+				\begin{alignat}{2}
+					I_q(\bar{c}_{i_q};\boldsymbol{y},z) & = C_q, \quad && P_q^{\star}(\bar{c}_{i_q}) > 0,\\
+					I_q(\bar{c}_{i_q};\boldsymbol{y},z) & \le C_q, \quad && P_q^{\star}(\bar{c}_{i_q}) = 0,
+				\end{alignat}
+			\end{subequations}
+			where $C_q \triangleq \mu_q^{\star} + (1 - \rho)$. Apparently, it holds that
 			\begin{equation}
-					I_{q}(\bar{c}_{i_q} ; \boldsymbol{y},z) = C_q, \quad P_q^{\star}(\bar{c}_{i_q}) > 0,
+				\sum_{i_q} P_q^{\star}(\bar{c}_{i_q}) I_q(\bar{c}_{i_q};\boldsymbol{y},z) = C_q.
 			\end{equation}
+
+			On the other hand, by the definition of marginations \eqref{eq:backscatter_sum_rate_expectation}, \eqref{eq:primary_ergodic_rate_expectation} and weighted summations \eqref{eq:weighted_sum_marginal_information}, \eqref{eq:weighted_sum_rate}, we have
 			\begin{equation}
-					I_{q}(\bar{c}_{i_q} ; \boldsymbol{y},z) \le C_q, \quad P_q^{\star}(\bar{c}_{i_q}) = 0,
+				\sum_{i_q} P_q^{\star}(\bar{c}_{i_q}) I_q(\bar{c}_{i_q};\boldsymbol{y},z) = I(c_{\mathcal{K}};\boldsymbol{y},z),
 			\end{equation}
+			which is irrelevant to $q$. Hence, $C_q = I(c_{\mathcal{K}};\boldsymbol{y},z)$, $\forall q \in \mathcal{K}$ and
+			\begin{subequations}
+				\begin{alignat}{2}
+					I_q(\bar{c}_{i_q};\boldsymbol{y},z) & = I(c_{\mathcal{K}};\boldsymbol{y},z), \quad && P_q^{\star}(\bar{c}_{i_q}) > 0,\\
+					I_q(\bar{c}_{i_q};\boldsymbol{y},z) & \le I(c_{\mathcal{K}};\boldsymbol{y},z), \quad && P_q^{\star}(\bar{c}_{i_q}) = 0.
+				\end{alignat}
 			\end{subequations}
+
+			It suggests that an input probability distribution maximizes the weighted primary-backscatter sum rate if and only if each probable state of each tag produces the same mutual information.
 		\end{subsection}
@@
 			\begin{align}
-				I(\bar{c}_i ; z)
+				I(\bar{c}_i;z)
 				& = \sum_{j \in \mathcal{M^K}} \int_{T_{j-1,j}}^{T_{j,j+1}} \frac{z^{N-1} \exp \left(-\frac{z}{\mathrm{tr}(H_{\mathrm{E},i} W) + \sigma_w^2}\right)}{\left(\mathrm{tr}(H_{\mathrm{E},i} W) + \sigma_w^2\right)^N (N-1)!} \dd z\nonumber\\

### 2021-12-15 main.tex
:pencil: Add optimal input distribution

@@
 			where $\rho \in [0,1]$ denotes the priority of the primary link.
-To investigate how backscatter modulation and detection may influence the primary transmission, we optimize the input probability distribution, decision region, and transmit precoder to maximize the weighted primary-backscatter sum rate
+To investigate how backscatter modulation and detection may influence the primary transmission, we optimize the input probability distribution, decision region, and transmit precoder to maximize the weighted sum primary-backscatter rate
 			\begin{maxi!}
@@
 
-			It suggests that an input probability distribution maximizes the weighted primary-backscatter sum rate if and only if each probable state of each tag produces the same mutual information.
+			It suggests that an input probability distribution maximizes the weighted sum primary-backscatter rate if and only if each probable state of each tag produces the same mutual information.
+On top of this, we extend the Blahut-Arimoto algorithm and obtain the optimal input probability distribution in closed form as follows.
+
+			\begin{theorem}
+				The input probability distribution that achieves the weighted sum primary-backscatter capacity is given by the limit of the following sequence, $\forall i_q \in \mathcal{M}$ and $\forall q \in \mathcal{K}$,
+				\begin{equation}
+					P_q^{(r+1)}(\bar{c}_{i_q}) = P_q^{(r)}(\bar{c}_{i_q}) \frac{\exp \left( I_q(\bar{c}_{i_q};\boldsymbol{y},z) \right)}{\sum_{m_q} P_q^{(r)}(\bar{c}_{m_q}) \exp \left( I_q(\bar{c}_{m_q};\boldsymbol{y},z) \right)},
+				\end{equation}
+				where $r \in \mathbb{Z}_+$ is the iteration index and $P_q^{(0)}(\bar{c}_{i_q}) > 0$.
+[TODO] The probability distribution of tag $q$ is based on the updated probability distribution of tags $1,\ldots,q-1$.
+			\end{theorem}
 		\end{subsection}

### 2021-12-15 main.tex
:pencil: Encapsulate proposition on optimality conditions

@@
 			which is non-convex for $K > 1$ due to the product term $\prod_{k \in \mathcal{K}} P_k(\bar{c}_{m_k})$.
-Fortunately, the \gls{kkt} conditions are sufficient and necessary for this type of problem, and the proof follows straightforwardly from \cite{Watanabe2009}.\footnote{For any elementary discrete memoryless \gls{mac} (sizes of input alphabets are no greater than that of output alphabet), the sufficiency can be proved by combining the local maximum and connectedness of \gls{kkt} solutions.
+Fortunately, the \gls{kkt} conditions are necessary and sufficient for this type of problem, and the proof follows straightforwardly from \cite{Watanabe2009}.\footnote{For any elementary discrete memoryless \gls{mac} (sizes of input alphabets are no greater than that of output alphabet), the sufficiency can be proved by combining the local maximum and connectedness of \gls{kkt} solutions.
 For any general discrete memoryless \gls{mac}, the capacity can be achieved by an elementary discrete memoryless \gls{mac} included within.
-Thus, we restrict the discussion of this paper to elementary discrete memoryless \gls{mac}s.} Denote the Lagrange multiplier associated with \eqref{co:sum_probability} and \eqref{co:nonnegative_probability} as $\boldsymbol{\mu} \triangleq [\mu_1,\ldots,\mu_K]^T \in \mathbb{R}^{K \times 1}$ and $\boldsymbol{\Lambda} \triangleq [\boldsymbol{\lambda}_1^T,\ldots,\boldsymbol{\lambda}_K^T]^T \in \mathbb{R}^{M \times K}$ with $\boldsymbol{\lambda}_k \triangleq [\lambda_{k,1},\ldots,\lambda_{k,M}]^T \in \mathbb{R}^{M \times 1}$, respectively.
+Thus, we restrict the discussion of this paper to elementary discrete memoryless \gls{mac}s.}
+			\begin{proposition}
+				The necessary and sufficient conditions for an input probability distribution $\boldsymbol{P}^{\star}$ to maximize the weighted sum primary-backscatter rate are that, $\forall i_q \in \mathcal{M}$ and $\forall q \in \mathcal{K}$,
+				\begin{subequations}
+					\begin{alignat}{2}
+						I_q(\bar{c}_{i_q};\boldsymbol{y},z) & = I(c_{\mathcal{K}};\boldsymbol{y},z), \quad && P_q^{\star}(\bar{c}_{i_q}) > 0,\label{co:probable_states}\\
+						I_q(\bar{c}_{i_q};\boldsymbol{y},z) & \le I(c_{\mathcal{K}};\boldsymbol{y},z), \quad && P_q^{\star}(\bar{c}_{i_q}) = 0.\label{co:dropped_states}
+					\end{alignat}
+				\end{subequations}
+
+				% \eqref{co:probable_states} means each probable state of each tag should produce the same marginal information (averaged over all states of other tags), while \eqref{co:dropped_states} implies any state of any tag with potentially less marginal information than above should not be used.
+				An interpretation is that each probable state of each tag should produce the same marginal information (averaged over all states of other tags), while any state of any tag with potentially less marginal information than above should not be used.
+				% \begin{itemize}
+				% 	\item each probable state of each tag produces the same marginal information (averaged over all states of other tags)
+				% 	\item all states of all tags with potentially less marginal information should be dropped
+				% \end{itemize}
+				% An input probability distribution maximizes the weighted sum primary-backscatter rate if and only if each probable state of each tag produces the same mutual information.
+Specifically, the optimal $\boldsymbol{P}^{\star}$ to problem~\eqref{op:input_probability_distribution}
+
+				% the input probability distribution that achieves the weighted sum primary-backscatter capacity, at state $i_q \in \mathcal{M}$ of tag $q \in \mathcal{K}$,
+				% \begin{subequations}
+				% 	\begin{alignat}{2}
+				% 		I_q(\bar{c}_{i_q};\boldsymbol{y},z) & = I(c_{\mathcal{K}};\boldsymbol{y},z), \quad && P_q^{\star}(\bar{c}_{i_q}) > 0,\\
+				% 		I_q(\bar{c}_{i_q};\boldsymbol{y},z) & \le I(c_{\mathcal{K}};\boldsymbol{y},z), \quad && P_q^{\star}(\bar{c}_{i_q}) = 0.
+				% 	\end{alignat}
+				% \end{subequations}
+				\label{pr:optimal_conditions}
+			\end{proposition}
+			\begin{proof}
+				Denote the Lagrange multiplier associated with \eqref{co:sum_probability} and \eqref{co:nonnegative_probability} as $\boldsymbol{\mu} \triangleq [\mu_1,\ldots,\mu_K]^T \in \mathbb{R}^{K \times 1}$ and $\boldsymbol{\Lambda} \triangleq [\boldsymbol{\lambda}_1^T,\ldots,\boldsymbol{\lambda}_K^T]^T \in \mathbb{R}^{M \times K}$ with $\boldsymbol{\lambda}_k \triangleq [\lambda_{k,1},\ldots,\lambda_{k,M}]^T \in \mathbb{R}^{M \times 1}$, respectively.
 The Lagrangian function of problem~\eqref{op:input_probability_distribution} is
@@
 					\begin{equation}
-					\lambda_{q,i_q}^{\star} \ge 0, \quad P_q^{\star}(\bar{c}_{i_q}) = 0.
+						\lambda_{q,i_q}^{\star} \ge 0, \quad P_q^{\star}(\bar{c}_{i_q}) = 0,
 					\end{equation}
 				\end{subequations}
-
-			The partial derivative can be explicitly expressed as
+				where the partial derivative can be explicitly expressed as
 				\begin{subequations}
@@
 				\end{subequations}
-			which suggests $\mu_q^{\star}$ must satisfy
+				such that $\mu_q^{\star}$ must satisfy
 				\begin{subequations}
@@
 
-			Due to the sufficiency and necessity of the \gls{kkt} conditions, we can conclude that any input probability distribution $\boldsymbol{P}^{\star}$ maximizes the weighted sum primary-backscatter rate if and only if, $\forall i_q \in \mathcal{M}$ and $\forall q \in \mathcal{K}$,
+				Due to the necessity and sufficiency of the \gls{kkt} conditions, we can conclude that any input probability distribution $\boldsymbol{P}^{\star}$ maximizes the weighted sum primary-backscatter rate if and only if, $\forall i_q \in \mathcal{M}$ and $\forall q \in \mathcal{K}$,
 				\begin{subequations}
@@
 				\end{equation}
-			which is irrelevant to $q$. Hence, $C_q = I(c_{\mathcal{K}};\boldsymbol{y},z)$, $\forall q \in \mathcal{K}$ and
-			\begin{subequations}
-				\begin{alignat}{2}
-					I_q(\bar{c}_{i_q};\boldsymbol{y},z) & = I(c_{\mathcal{K}};\boldsymbol{y},z), \quad && P_q^{\star}(\bar{c}_{i_q}) > 0,\\
-					I_q(\bar{c}_{i_q};\boldsymbol{y},z) & \le I(c_{\mathcal{K}};\boldsymbol{y},z), \quad && P_q^{\star}(\bar{c}_{i_q}) = 0.
-				\end{alignat}
-			\end{subequations}
+				which is irrelevant to $q$. It implies that $\forall q \in \mathcal{K}$, $C_q = I(c_{\mathcal{K}};\boldsymbol{y},z)$, and thus Proposition~\eqref{pr:optimal_conditions} holds.
+			\end{proof}
 
-			It suggests that an input probability distribution maximizes the weighted sum primary-backscatter rate if and only if each probable state of each tag produces the same mutual information.
-On top of this, we extend the Blahut-Arimoto algorithm and obtain the optimal input probability distribution in closed form as follows.
+			Next, we extend the Blahut-Arimoto algorithm to the proposed case and obtain the optimal input probability distribution as follows.
 
 			\begin{theorem}
-				The input probability distribution that achieves the weighted sum primary-backscatter capacity is given by the limit of the following sequence, $\forall i_q \in \mathcal{M}$ and $\forall q \in \mathcal{K}$,
+				The input probability distribution that achieves the weighted sum primary-backscatter capacity, at state $i_q \in \mathcal{M}$ of tag $q \in \mathcal{K}$, is given by the limit of the following sequence\footnote{Note that the probability distribution of tag $q$ is based on the updated probability distribution of tags $1,\ldots,q-1$.}
 				\begin{equation}
@@
 				\end{equation}
-				where $r \in \mathbb{Z}_+$ is the iteration index and $P_q^{(0)}(\bar{c}_{i_q}) > 0$.
-[TODO] The probability distribution of tag $q$ is based on the updated probability distribution of tags $1,\ldots,q-1$.
+				where $r \in \mathbb{Z}_+$ is the iteration index and $P_q^{(0)}(\bar{c}_{i_q}) > 0$, $\forall i_q \in \mathcal{M}$ and $\forall q \in \mathcal{K}$.
 			\end{theorem}
+
+			% Denote the Lagrange multiplier associated with \eqref{co:sum_probability} and \eqref{co:nonnegative_probability} as $\boldsymbol{\mu} \triangleq [\mu_1,\ldots,\mu_K]^T \in \mathbb{R}^{K \times 1}$ and $\boldsymbol{\Lambda} \triangleq [\boldsymbol{\lambda}_1^T,\ldots,\boldsymbol{\lambda}_K^T]^T \in \mathbb{R}^{M \times K}$ with $\boldsymbol{\lambda}_k \triangleq [\lambda_{k,1},\ldots,\lambda_{k,M}]^T \in \mathbb{R}^{M \times 1}$, respectively.
+The Lagrangian function of problem~\eqref{op:input_probability_distribution} is
+			% \begin{align}
+			% 	J
+			% 	& = - I + \sum_{k \in \mathcal{K}} \mu_k \left( \sum_{m_k \in \mathcal{M}} P_k(\bar{c}_{m_k}) - 1 \right)\nonumber\\
+			% 	& \quad - \sum_{k \in \mathcal{K}} \sum_{m_k \in \mathcal{M}} \lambda_{k,m_k} P_k(\bar{c}_{m_k}),
+			% \end{align}
+			% and the corresponding \gls{kkt} conditions on the primal and dual solutions are, $\forall i_q \in \mathcal{M}$ and $\forall q \in \mathcal{K}$,
+			% \begin{subequations}
+			% 	\begin{equation}
+			% 		- \pdv{I}{P_q^{\star}(\bar{c}_{i_q})} + \mu_q^{\star} - \lambda_{q,i_q}^{\star} = 0,
+			% 	\end{equation}
+			% 	\begin{equation}
+			% 		\lambda_{q,i_q}^{\star} = 0, \quad P_q^{\star}(\bar{c}_{i_q}) > 0,
+			% 	\end{equation}
+			% 	\begin{equation}
+			% 		\lambda_{q,i_q}^{\star} \ge 0, \quad P_q^{\star}(\bar{c}_{i_q}) = 0.
+			% 	\end{equation}
+			% \end{subequations}
+
+			% The partial derivative can be explicitly expressed as
+			% \begin{subequations}
+			% 	\begin{align}
+			% 		\pdv{I}{P_q^{\star}(\bar{c}_{i_q})}
+			% 		& = \rho I_{\mathrm{P},q}(\bar{c}_{i_q};\boldsymbol{y}) + (1 - \rho) \left( I_{\mathrm{B},q}(\bar{c}_{i_q};z) - 1 \right)\\
+			% 		& = I_q(\bar{c}_{i_q};\boldsymbol{y},z) - (1 - \rho),
+			% 	\end{align}
+			% \end{subequations}
+			% which suggests $\mu_q^{\star}$ must satisfy
+			% \begin{subequations}
+			% 	\begin{alignat}{2}
+			% 		\mu_q^{\star} & = I_q(\bar{c}_{i_q};\boldsymbol{y},z) - (1 - \rho), \quad && P_q^{\star}(\bar{c}_{i_q}) > 0,\\
+			% 		\mu_q^{\star} & \ge I_q(\bar{c}_{i_q};\boldsymbol{y},z) - (1 - \rho), \quad && P_q^{\star}(\bar{c}_{i_q}) = 0.
+			% 	\end{alignat}
+			% \end{subequations}
+
+			% Due to the necessity and sufficiency of the \gls{kkt} conditions, we can conclude that any input probability distribution $\boldsymbol{P}^{\star}$ maximizes the weighted sum primary-backscatter rate if and only if, $\forall i_q \in \mathcal{M}$ and $\forall q \in \mathcal{K}$,
+			% \begin{subequations}
+			% 	\begin{alignat}{2}
+			% 		I_q(\bar{c}_{i_q};\boldsymbol{y},z) & = C_q, \quad && P_q^{\star}(\bar{c}_{i_q}) > 0,\\
+			% 		I_q(\bar{c}_{i_q};\boldsymbol{y},z) & \le C_q, \quad && P_q^{\star}(\bar{c}_{i_q}) = 0,
+			% 	\end{alignat}
+			% \end{subequations}
+			% where $C_q \triangleq \mu_q^{\star} + (1 - \rho)$. Apparently, it holds that
+			% \begin{equation}
+			% 	\sum_{i_q} P_q^{\star}(\bar{c}_{i_q}) I_q(\bar{c}_{i_q};\boldsymbol{y},z) = C_q.
+			% \end{equation}
+
+			% On the other hand, by the definition of marginations \eqref{eq:backscatter_sum_rate_expectation}, \eqref{eq:primary_ergodic_rate_expectation} and weighted summations \eqref{eq:weighted_sum_marginal_information}, \eqref{eq:weighted_sum_rate}, we have
+			% \begin{equation}
+			% 	\sum_{i_q} P_q^{\star}(\bar{c}_{i_q}) I_q(\bar{c}_{i_q};\boldsymbol{y},z) = I(c_{\mathcal{K}};\boldsymbol{y},z),
+			% \end{equation}
+			% which is irrelevant to $q$. Hence, $C_q = I(c_{\mathcal{K}};\boldsymbol{y},z)$, $\forall q \in \mathcal{K}$ and
+			% \begin{subequations}
+			% 	\begin{alignat}{2}
+			% 		I_q(\bar{c}_{i_q};\boldsymbol{y},z) & = I(c_{\mathcal{K}};\boldsymbol{y},z), \quad && P_q^{\star}(\bar{c}_{i_q}) > 0,\\
+			% 		I_q(\bar{c}_{i_q};\boldsymbol{y},z) & \le I(c_{\mathcal{K}};\boldsymbol{y},z), \quad && P_q^{\star}(\bar{c}_{i_q}) = 0.
+			% 	\end{alignat}
+			% \end{subequations}
+
+			% It suggests that an input probability distribution maximizes the weighted sum primary-backscatter rate if and only if each probable state of each tag produces the same mutual information.
+On top of this, we extend the Blahut-Arimoto algorithm to our case and obtain the optimal input probability distribution as follows.
+
+			% \begin{theorem}
+			% 	The input probability distribution that achieves the weighted sum primary-backscatter capacity, at state $i_q \in \mathcal{M}$ of tag $q \in \mathcal{K}$, is given by the limit of the following sequence\footnote{Note that the probability distribution of tag $q$ is based on the updated probability distribution of tags $1,\ldots,q-1$.}
+			% 	\begin{equation}
+			% 		P_q^{(r+1)}(\bar{c}_{i_q}) = P_q^{(r)}(\bar{c}_{i_q}) \frac{\exp \left( I_q(\bar{c}_{i_q};\boldsymbol{y},z) \right)}{\sum_{m_q} P_q^{(r)}(\bar{c}_{m_q}) \exp \left( I_q(\bar{c}_{m_q};\boldsymbol{y},z) \right)},
+			% 	\end{equation}
+			% 	where $r \in \mathbb{Z}_+$ is the iteration index and $P_q^{(0)}(\bar{c}_{i_q}) > 0$, $\forall i_q \in \mathcal{M}$ and $\forall q \in \mathcal{K}$.
+			% \end{theorem}
 		\end{subsection}

### 2021-12-16 main.tex
:pencil: Add intermediate information function

@@
 			\end{equation}
+			where $P(\bar{z}_j) = \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(\bar{c}_{m_{\mathcal{K}}}) P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K}}})$.
 			% \begin{align}
@@
 			% \end{align}
-			the backscatter marginal information function of tag $q \in \mathcal{K}$ associated with $\bar{c}_{i_q}$, $i_q \in \mathcal{M}$ is defined as
+			The backscatter marginal information function of tag $q \in \mathcal{K}$ associated with $\bar{c}_{i_q}$, $i_q \in \mathcal{M}$ is defined as
 			\begin{equation}
@@
 
-				% \eqref{co:probable_states} means each probable state of each tag should produce the same marginal information (averaged over all states of other tags), while \eqref{co:dropped_states} implies any state of any tag with potentially less marginal information than above should not be used.
-				An interpretation is that each probable state of each tag should produce the same marginal information (averaged over all states of other tags), while any state of any tag with potentially less marginal information than above should not be used.
+				\eqref{co:probable_states} means each probable state of each tag should produce the same marginal information (averaged over all states of other tags), while \eqref{co:dropped_states} implies any state of any tag with potentially less marginal information than above should not be used.
+				% An interpretation is that each probable state of each tag should produce the same marginal information (averaged over all states of other tags), while any state of any tag with potentially less marginal information than above should not be used.
 				% \begin{itemize}
@@
 				\begin{align}
-					J
+					L
 					& = - I + \sum_{k \in \mathcal{K}} \mu_k \left( \sum_{m_k \in \mathcal{M}} P_k(\bar{c}_{m_k}) - 1 \right)\nonumber\\
@@
 				\begin{equation}
-					P_q^{(r+1)}(\bar{c}_{i_q}) = P_q^{(r)}(\bar{c}_{i_q}) \frac{\exp \left( I_q(\bar{c}_{i_q};\boldsymbol{y},z) \right)}{\sum_{m_q} P_q^{(r)}(\bar{c}_{m_q}) \exp \left( I_q(\bar{c}_{m_q};\boldsymbol{y},z) \right)},
+					P_q^{(r+1)}(\bar{c}_{i_q}) = P_q^{(r)}(\bar{c}_{i_q}) \frac{\exp \left( \frac{\rho}{1 - \rho} I_q(\bar{c}_{i_q};\boldsymbol{y},z) \right)}{\sum_{m_q} P_q^{(r)}(\bar{c}_{m_q}) \exp \left( \frac{\rho}{1 - \rho} I_q(\bar{c}_{m_q};\boldsymbol{y},z) \right)},
+					\label{eq:optimal_distribution}
 				\end{equation}
 				where $r \in \mathbb{Z}_+$ is the iteration index and $P_q^{(0)}(\bar{c}_{i_q}) > 0$, $\forall i_q \in \mathcal{M}$ and $\forall q \in \mathcal{K}$.
+				\label{th:optimal_distribution}
 			\end{theorem}
+			\begin{proof}
+				We first prove that for tag $q \in \mathcal{K}$, updating the probability of state $i_q \in \mathcal{M}$ by sequence~\eqref{eq:optimal_distribution} does not decrease the mutual information.
+				For a certain input combination $\bar{c}_{m_{\mathcal{K}}}$, let $P_{\mathcal{K}}(\bar{c}_{m_{\mathcal{K}}}) = \prod_{k \in \mathcal{K}} P_k(\bar{c}_{m_k})$ and $P_{\mathcal{K}}'(\bar{c}_{m_{\mathcal{K}}}) = P_q'(\bar{c}_{m_q}) \prod_{k \in \mathcal{K} \setminus \{q\}} P_k(\bar{c}_{m_k})$ be two probability distributions with potentially different marginal for tag $q$.
+Correspondingly, $P'(\bar{z}_j) = \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}'(\bar{c}_{m_{\mathcal{K}}}) P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K}}})$.
+We also define $J$ in \eqref{eq:intermediate_information_function} as an intermediate information function between two probability distributions.
+It can be verified that for a fixed $P_{\mathcal{K}}'(\bar{c}_{m_{\mathcal{K}}})$, $J \left( P_{\mathcal{K}}(\bar{c}_{m_{\mathcal{K}}}),P_{\mathcal{K}}'(\bar{c}_{m_{\mathcal{K}}}) \right)$ is a concave function of $P_{\mathcal{K}}(\bar{c}_{m_{\mathcal{K}}})$.
+As such, $J \left( P_{\mathcal{K}}(\bar{c}_{m_{\mathcal{K}}}),P_{\mathcal{K}}'(\bar{c}_{m_{\mathcal{K}}}) \right)$ is maximized by the solution to $\pdv*{J \left( P_{\mathcal{K}}(\bar{c}_{m_{\mathcal{K}}}),P_{\mathcal{K}}'(\bar{c}_{m_{\mathcal{K}}}) \right)}{P_k(\bar{c}_{m_k})} = 0$.
+				\begin{figure*}
+					\begin{align}
+						J \left( P_{\mathcal{K}}(\bar{c}_{m_{\mathcal{K}}}),P_{\mathcal{K}}'(\bar{c}_{m_{\mathcal{K}}}) \right)
+						& \triangleq \rho \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(\bar{c}_{m_{\mathcal{K}}}) N \log_2 \left(1 + \frac{\lvert \boldsymbol{h}_{\mathrm{E}}^H(\bar{c}_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_w^2}\right)\nonumber\\
+						& \quad + (1 - \rho) \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(\bar{c}_{m_{\mathcal{K}}}) \sum_j P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K}}}) \log \frac{P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K}}}) P_{\mathcal{K}}'(\bar{c}_{m_{\mathcal{K}}})}{P'(\bar{z}_j) P_{\mathcal{K}}(\bar{c}_{m_{\mathcal{K}}})}
+						\label{eq:intermediate_information_function}
+					\end{align}
+				\end{figure*}
+
+				% Let $P_{\mathcal{K}}(\bar{c}_{m_{\mathcal{K}}}) = \prod_{k \in \mathcal{K}} P_k(\bar{c}_{m_k})$ and $P_{\mathcal{K}}'(\bar{c}_{m_{\mathcal{K}}}) = P_q'(\bar{c}_{m_q}) \prod_{k \in \mathcal{K} \setminus \{q\}} P_k(\bar{c}_{m_k})$ be two probability distributions associated with input combination $\bar{c}_{m_{\mathcal{K}}}$
+			\end{proof}
 

### 2021-12-16 main.tex
:pencil: Add quick one-side proof

--- 2021-12-15 main.tex
@@
 			denotes the expectation of the received power per primary block under tag modulation index set $m_{\mathcal{K}}$.
-For the ease of exposition, we denote the hypothesis that the tag input combination at status $i \in \mathcal{M^K} \triangleq \{1,\ldots,M^K\}$ as $\mathcal{H}_i$, sort $\{\sigma_{m_{\mathcal{K}}}^2\}$ in ascending order by a one-to-one mapping $m_{\mathcal{K}} \mapsto i$,\footnote{When more than one modulation index sets yield the same energy level, the mapping is not unique and the detection fails to separate them.
+For the ease of exposition, we denote the hypothesis that the tag input combination at state $i \in \mathcal{M^K} \triangleq \{1,\ldots,M^K\}$ as $\mathcal{H}_i$, sort $\{\sigma_{m_{\mathcal{K}}}^2\}$ in ascending order by a one-to-one mapping $m_{\mathcal{K}} \mapsto i$,\footnote{When more than one modulation index sets yield the same energy level, the mapping is not unique and the detection fails to separate them.
 This blind spot issue can be mitigated by multi-antenna techniques.} define the received signal energy over $N$ primary blocks as $z \triangleq \lVert \boldsymbol{y} \rVert^2$, and let $f(z \mid \mathcal{H}_i)$ be the conditional probability density function of receiving $z$ under hypothesis $\mathcal{H}_i$.
@@
 			On top of this, we can compute the marginal probability of each tag and obtain $K$ transition matrices from $\mathcal{M}$ to $\mathcal{M^K}$ that compose a discrete memoryless \gls{mac}.
-The probability of observing energy level $j$ when tag $k$ at status $m_k$ is
+The probability of observing energy level $j$ when tag $k$ at state $m_k$ is
 			\begin{equation}
@@
 			We first introduce some prerequisites of information theory.
-Define the input probability distribution of tag $k$ at status $m_k$ as $P_k(\bar{c}_{m_k})$, and let $\boldsymbol{p}_k \triangleq [P_k(\bar{c}_1),\ldots,P_k(\bar{c}_M)]^T \in \mathbb{R}^{M \times 1}$, $\boldsymbol{P} \triangleq [\boldsymbol{p}_1^T,\ldots,\boldsymbol{p}_K^T]^T \in \mathbb{R}^{M \times K}$.
-Assume the input distribution of all tags are mutually independent such that $P_{\mathcal{K}}(\bar{c}_{m_{\mathcal{K}}}) = \prod_{k \in \mathcal{K}} P_k(\bar{c}_{m_k})$.
-Following \cite{Rezaeian2004}, the backscatter information function associated with tag input combination $\bar{c}_{m_{\mathcal{K}}}$ is defined as
+Define the input probability distribution of tag $k$ at state $m_k$ as $P_k(\bar{c}_{m_k})$, and let $\boldsymbol{p}_k \triangleq [P_k(\bar{c}_1),\ldots,P_k(\bar{c}_M)]^T \in \mathbb{R}^{M \times 1}$, $\boldsymbol{P} \triangleq [\boldsymbol{p}_1^T,\ldots,\boldsymbol{p}_K^T]^T \in \mathbb{R}^{M \times K}$.
+Assume the input distribution of all tags are mutually independent such that the probability associated with input combination $\bar{c}_{m_{\mathcal{K}}}$ satisfies $P_{\mathcal{K}}(\bar{c}_{m_{\mathcal{K}}}) = \prod_{k \in \mathcal{K}} P_k(\bar{c}_{m_k})$.
+Following \cite{Rezaeian2004}, the corresponding backscatter information function is defined as
 			\begin{equation}
@@
 			% \end{align}
-			the backscatter marginal information function of tag $q \in \mathcal{K}$ associated with $\bar{c}_{i_q}$, $i_q \in \mathcal{M}$ is defined as
+			The backscatter marginal information function of tag $q \in \mathcal{K}$ associated with $\bar{c}_{i_q}$, $i_q \in \mathcal{M}$ is defined as
 			\begin{equation}
-				I_{\mathrm{B},q}(\bar{c}_{i_q};z) \triangleq \sum_{m_{\mathcal{K} \setminus \{q\}}} \prod_{k \in \mathcal{K} \setminus \{q\}} P_k(\bar{c}_{m_k}) I_{\mathrm{B}}(\bar{c}_{m_{\mathcal{K} \setminus \{q\}}},\bar{c}_{i_q};z),
+				I_{\mathrm{B},q}(\bar{c}_{i_q};z) \triangleq \sum_{m_{\mathcal{K} \setminus \{q\}}} P_{\mathcal{K} \setminus \{q\}}(\bar{c}_{m_{\mathcal{K} \setminus \{q\}}}) I_{\mathrm{B}}(\bar{c}_{m_{\mathcal{K} \setminus \{q\}}},\bar{c}_{i_q};z),
 				\label{eq:backscatter_marginal_information_function}
 			\end{equation}
+			% \begin{equation}
+			% 	I_{\mathrm{B},q}(\bar{c}_{i_q};z) \triangleq \sum_{m_{\mathcal{K} \setminus \{q\}}} \prod_{k \in \mathcal{K} \setminus \{q\}} P_k(\bar{c}_{m_k}) I_{\mathrm{B}}(\bar{c}_{m_{\mathcal{K} \setminus \{q\}}},\bar{c}_{i_q};z),
+			% 	\label{eq:backscatter_marginal_information_function}
+			% \end{equation}
 			% the backscatter marginal information function of tag $k$ associated with $\bar{c}_{m_k}$ is defined as
@@
 			% \end{equation}
-			and the backscatter mutual information can be expressed as\footnote{Please be aware that $c_{\mathcal{K}}$, $c_k$, $z$ are random variables, while $\bar{c}_{m_{\mathcal{K}}}$ and $\bar{c}_i$, $\bar{c}_{m_k}$, $\bar{z}_j$ represent the corresponding instances.}
+			where $P_{\mathcal{K} \setminus \{q\}}(\bar{c}_{m_{\mathcal{K} \setminus \{q\}}}) = \prod_{k \in \mathcal{K} \setminus \{q\}} P_k(\bar{c}_{m_k})$.
+The backscatter mutual information can be expressed as\footnote{Please be aware that $c_{\mathcal{K}}$, $c_k$, $z$ are random variables, while $\bar{c}_{m_{\mathcal{K}}}$ and $\bar{c}_i$, $\bar{c}_{m_k}$, $\bar{z}_j$ represent the corresponding instances.}
 			\begin{subequations}
@@
 					& = \mathbb{E}_{c_{\mathcal{K}}} \left[I_{\mathrm{B}}(\bar{c}_{m_{\mathcal{K}}};z)\right] = \mathbb{E}_{c_k} \left[I_{\mathrm{B},k}(\bar{c}_{m_k};z)\right]\label{eq:backscatter_sum_rate_expectation}\\
-					& = \sum_{m_{\mathcal{K}}} \prod_{k \in \mathcal{K}} P_k(\bar{c}_{m_k}) \sum_j P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K}}}) \log \frac{P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K}}})}{P(\bar{z}_j)}.\label{eq:backscatter_sum_rate_expansion}
+					& = \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(\bar{c}_{m_{\mathcal{K}}}) \sum_j P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K}}}) \log \frac{P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K}}})}{P(\bar{z}_j)}.\label{eq:backscatter_sum_rate_expansion}
 				\end{align}
@@
 				I_{\mathrm{P},q}(\bar{c}_{i_q};\boldsymbol{y})
-				& \triangleq \sum_{m_{\mathcal{K} \setminus \{q\}}} \prod_{k \in \mathcal{K} \setminus \{q\}} P_{k}(\bar{c}_{m_{k}}) I_{\mathrm{P}}(\bar{c}_{m_{\mathcal{K} \setminus \{q\}}},\bar{c}_{i_q};\boldsymbol{y}),\label{eq:primary_marginal_information_function}
+				& \triangleq \sum_{m_{\mathcal{K} \setminus \{q\}}} P_{\mathcal{K} \setminus \{q\}}(\bar{c}_{m_{\mathcal{K} \setminus \{q\}}}) I_{\mathrm{P}}(\bar{c}_{m_{\mathcal{K} \setminus \{q\}}},\bar{c}_{i_q};\boldsymbol{y}),\label{eq:primary_marginal_information_function}
 			\end{align}
@@
 					& = \mathbb{E}_{c_{\mathcal{K}}} \left[I_{\mathrm{P}}(\bar{c}_{m_{\mathcal{K}}};\boldsymbol{y})\right] = \mathbb{E}_{c_k} \left[I_{\mathrm{P},k}(\bar{c}_{m_k};\boldsymbol{y})\right]\label{eq:primary_ergodic_rate_expectation}\\
-					& = \sum_{m_{\mathcal{K}}} \prod_{k \in \mathcal{K}} P_k(\bar{c}_{m_k}) N \log_2 \left(1 + \frac{\lvert \boldsymbol{h}_{\mathrm{E}}^H(\bar{c}_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_w^2}\right).
+					& = \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(\bar{c}_{m_{\mathcal{K}}}) N \log_2 \left(1 + \frac{\lvert \boldsymbol{h}_{\mathrm{E}}^H(\bar{c}_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_w^2}\right).
 					\label{eq:primary_ergodic_rate_expansion}
@@
 			\begin{maxi!}
-				{\scriptstyle{\boldsymbol{P},\boldsymbol{t},\boldsymbol{w}}}{I}{\label{op:rate_region}}{\label{ob:weighted_sum_rate}}
+				{\scriptstyle{\boldsymbol{P},\boldsymbol{t},\boldsymbol{w}}}{I(c_{\mathcal{K}};\boldsymbol{y},z)}{\label{op:rate_region}}{\label{ob:weighted_sum_rate}}
 				\addConstraint{\sum \nolimits_{m_k} P_k(\bar{c}_{m_k})}{=1,\quad\label{co:sum_probability}}{\forall k \in \mathcal{K}}
@@
 			\begin{maxi!}
-				{\scriptstyle{\boldsymbol{P}}}{I}{\label{op:input_probability_distribution}}{}
+				{\scriptstyle{\boldsymbol{P}}}{I(c_{\mathcal{K}};\boldsymbol{y},z)}{\label{op:input_probability_distribution}}{}
 				\addConstraint{\eqref{co:sum_probability},\eqref{co:nonnegative_probability},}
@@
 				\begin{align}
-					J
-					& = - I + \sum_{k \in \mathcal{K}} \mu_k \left( \sum_{m_k \in \mathcal{M}} P_k(\bar{c}_{m_k}) - 1 \right)\nonumber\\
+					L(\boldsymbol{P},\boldsymbol{\mu},\boldsymbol{\Lambda})
+					& = - I(c_{\mathcal{K}};\boldsymbol{y},z) + \sum_{k \in \mathcal{K}} \mu_k \left( \sum_{m_k \in \mathcal{M}} P_k(\bar{c}_{m_k}) - 1 \right)\nonumber\\
 					& \quad - \sum_{k \in \mathcal{K}} \sum_{m_k \in \mathcal{M}} \lambda_{k,m_k} P_k(\bar{c}_{m_k}),
@@
 					\begin{equation}
-						- \pdv{I}{P_q^{\star}(\bar{c}_{i_q})} + \mu_q^{\star} - \lambda_{q,i_q}^{\star} = 0,
+						- \nabla_{P_q^{\star}(\bar{c}_{i_q})} I(c_{\mathcal{K}};\boldsymbol{y},z) + \mu_q^{\star} - \lambda_{q,i_q}^{\star} = 0,
 					\end{equation}
@@
 				\end{subequations}
-				where the partial derivative can be explicitly expressed as
+				where the directional derivative can be explicitly expressed as
 				\begin{subequations}
 					\begin{align}
-						\pdv{I}{P_q^{\star}(\bar{c}_{i_q})}
+						\nabla_{P_q^{\star}(\bar{c}_{i_q})} I(c_{\mathcal{K}};\boldsymbol{y},z)
 						& = \rho I_{\mathrm{P},q}(\bar{c}_{i_q};\boldsymbol{y}) + (1 - \rho) \left( I_{\mathrm{B},q}(\bar{c}_{i_q};z) - 1 \right)\\
@@
 			\begin{theorem}
-				The input probability distribution that achieves the weighted sum primary-backscatter capacity, at state $i_q \in \mathcal{M}$ of tag $q \in \mathcal{K}$, is given by the limit of the following sequence\footnote{Note that the probability distribution of tag $q$ is based on the updated probability distribution of tags $1,\ldots,q-1$.}
+				The input probability distribution that achieves the weighted sum primary-backscatter capacity at state $i_q \in \mathcal{M}$ of tag $q \in \mathcal{K}$ is given by the limit of the following sequence\footnote{Note that the probability distribution of tag $q$ is based on the updated probability distribution of tags $1,\ldots,q-1$.}
 				\begin{equation}
-					P_q^{(r+1)}(\bar{c}_{i_q}) = P_q^{(r)}(\bar{c}_{i_q}) \frac{\exp \left( I_q(\bar{c}_{i_q};\boldsymbol{y},z) \right)}{\sum_{m_q} P_q^{(r)}(\bar{c}_{m_q}) \exp \left( I_q(\bar{c}_{m_q};\boldsymbol{y},z) \right)},
+					P_q^{(r+1)}(\bar{c}_{i_q}) = \frac{P_q^{(r)}(\bar{c}_{i_q}) \exp \left( \frac{\rho}{1 - \rho} I_q(\bar{c}_{i_q};\boldsymbol{y},z) \right)}{\sum_{m_q} P_q^{(r)}(\bar{c}_{m_q}) \exp \left( \frac{\rho}{1 - \rho} I_q(\bar{c}_{m_q};\boldsymbol{y},z) \right)},
+					\label{eq:optimal_distribution}
 				\end{equation}
 				where $r \in \mathbb{Z}_+$ is the iteration index and $P_q^{(0)}(\bar{c}_{i_q}) > 0$, $\forall i_q \in \mathcal{M}$ and $\forall q \in \mathcal{K}$.
+				\label{th:optimal_distribution}
 			\end{theorem}
+			\begin{proof}
+				We first prove that for tag $q \in \mathcal{K}$, updating the probability of state $i_q \in \mathcal{M}$ by sequence~\eqref{eq:optimal_distribution} does not decrease the mutual information.
+				For a certain input combination $\bar{c}_{m_{\mathcal{K}}}$, let $P_{\mathcal{K}}(\bar{c}_{m_{\mathcal{K}}}) = \prod_{k \in \mathcal{K}} P_k(\bar{c}_{m_k})$ and $P_{\mathcal{K}}'(\bar{c}_{m_{\mathcal{K}}}) = P_q'(\bar{c}_{m_q}) \prod_{k \in \mathcal{K} \setminus \{q\}} P_k(\bar{c}_{m_k})$ be two probability distributions with potentially different marginal for tag $q$, and define $J \left( P_{\mathcal{K}}(\bar{c}_{m_{\mathcal{K}}}),P_{\mathcal{K}}'(\bar{c}_{m_{\mathcal{K}}}) \right)$ as the intermediate information function by \eqref{eq:intermediate_information_function}.
+				\begin{figure*}[!b]
+					\hrule
+					\begin{align}
+						J \left( P_{\mathcal{K}}(\bar{c}_{m_{\mathcal{K}}}),P_{\mathcal{K}}'(\bar{c}_{m_{\mathcal{K}}}) \right)
+						& \triangleq \rho \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(\bar{c}_{m_{\mathcal{K}}}) N \log_2 \left(1 + \frac{\lvert \boldsymbol{h}_{\mathrm{E}}^H(\bar{c}_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_w^2}\right)\nonumber\\
+						& \quad + (1 - \rho) \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(\bar{c}_{m_{\mathcal{K}}}) \sum_j P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K}}}) \log \frac{P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K}}}) P_{\mathcal{K}}'(\bar{c}_{m_{\mathcal{K}}})}{P'(\bar{z}_j) P_{\mathcal{K}}(\bar{c}_{m_{\mathcal{K}}})}.
+						\label{eq:intermediate_information_function}
+					\end{align}
+				\end{figure*}
+				It can be verified that for a fixed $P_{\mathcal{K}}'(\bar{c}_{m_{\mathcal{K}}})$, $J \left( P_{\mathcal{K}}(\bar{c}_{m_{\mathcal{K}}}),P_{\mathcal{K}}'(\bar{c}_{m_{\mathcal{K}}}) \right)$ is a concave function of $P_q(\bar{c}_{m_q})$ and is maximized by $\nabla_{P_q^{\star}(\bar{c}_{m_q})} J \left( P_{\mathcal{K}}(\bar{c}_{m_{\mathcal{K}}}),P_{\mathcal{K}}'(\bar{c}_{m_{\mathcal{K}}}) \right) = 0$, which can be explicitly written as
+				\begin{equation}
+					S_q'(\bar{c}_{m_q}) - S_q'(\bar{c}_{i_q}) + (1 - \rho) \log \frac{P_q(\bar{c}_{i_q})}{P_q^{\star}(\bar{c}_{m_q})} = 0,
+					\label{eq:optimal_intermediate_information_condition}
+				\end{equation}
+				where $i_q \ne m_q$ is the reference state and
+				% , and we define $\forall i_q \in \mathcal{M}$ and $\forall q \in \mathcal{K}$
+				\begin{align}
+					S_k'(\bar{c}_{m_q})
+					& \triangleq I_k(\bar{c}_{m_q};\boldsymbol{y},z) + (1 - \rho) \sum_{m_{\mathcal{K} \setminus \{q\}}} P_{\mathcal{K} \setminus \{q\}}(\bar{c}_{m_{\mathcal{K} \setminus \{q\}}})\nonumber\\
+					& \quad \times \sum_j P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K} \setminus \{q\}}},\bar{c}_{m_q}) \log P_{\mathcal{K}}'(\bar{c}_{m_{\mathcal{K}}}).
+				\end{align}
+
+				Evidently, $\forall m_q \ne i_q$, \eqref{eq:optimal_intermediate_information_condition} can be recast as
+				\begin{subequations}
+					\begin{align}
+						P_q^{\star}(\bar{c}_{m_q})
+						& = \frac{\exp \left( \frac{1}{1 - \rho} S_k'(\bar{c}_{m_q}) \right)}{\sum_{m_q} \exp \left( \frac{1}{1 - \rho} S_k'(\bar{c}_{m_q}) \right)}\\
+						& = \frac{P_q^{(r)}(\bar{c}_{m_q}) \exp \left( \frac{\rho}{1 - \rho} I_q(\bar{c}_{m_q};\boldsymbol{y},z) \right)}{\sum_{m_q} P_q^{(r)}(\bar{c}_{m_q}) \exp \left( \frac{\rho}{1 - \rho} I_q(\bar{c}_{m_q};\boldsymbol{y},z) \right)}.
+						\label{eq:optimal_relative_distribution}
+					\end{align}
+				\end{subequations}
+
+				Also, we notice that $P_q(\bar{c}_{i_q}) = 1 - \sum_{m_q \ne i_q} P_q^{\star}(\bar{c}_{m_q})$ has exactly the same form.
+It suggests that the solution of choosing $i_q$ as reference would coincide with that of choosing any $m_q \ne i_q$ as reference, such that \eqref{eq:optimal_relative_distribution} is also optimal for $i_q$.
+Therefore, for a fixed $P_{\mathcal{K}}'(\bar{c}_{m_{\mathcal{K}}})$, choosing $P_q(\bar{c}_{m_q})$ by \eqref{eq:optimal_relative_distribution} guarantees
+				\begin{equation}
+					J \left( P_{\mathcal{K}}(\bar{c}_{m_{\mathcal{K}}}),P_{\mathcal{K}}'(\bar{c}_{m_{\mathcal{K}}}) \right) \ge J \left( P_{\mathcal{K}}'(\bar{c}_{m_{\mathcal{K}}}),P_{\mathcal{K}}'(\bar{c}_{m_{\mathcal{K}}}) \right) = I \left(P_{\mathcal{K}}'(\bar{c}_{m_{\mathcal{K}}}) \right).
+				\end{equation}
+
+				TODO
+				% \begin{equation}
+				% 	P_q^{\star}(\bar{c}_{i_q}) = \frac{P_q^{(r)}(\bar{c}_{i_q}) \exp \left( \frac{\rho}{1 - \rho} I_q(\bar{c}_{i_q};\boldsymbol{y},z) \right)}{\sum_{i_q} P_q^{(r)}(\bar{c}_{i_q}) \exp \left( \frac{\rho}{1 - \rho} I_q(\bar{c}_{i_q};\boldsymbol{y},z) \right)}.
+				% 	\label{eq:optimal_reference_distribution}
+				% \end{equation}
+
+				% of choosing any $i_q$ coincide
+				% Regularization on \eqref{eq:optimal_intermediate_information_condition}
+			\end{proof}
 
@@
 			Interestingly, we can design precoder to adjust the expectation of the received power \eqref{eq:receive_variance} at each tag input combination, which can avoid the detection blind spots in \cite{Qian2019} and further boost the weighted sum-rate.
-However, the problem is highly non-convex -- the information function associated with input combination status $i$ is
+However, the problem is highly non-convex -- the information function associated with input combination state $i$ is
 			\begin{align}

### 2021-12-17 main.tex
:pencil: Add non-decreasing proof

@@
 			where $P(\bar{z}_j) = \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(\bar{c}_{m_{\mathcal{K}}}) P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K}}})$.
-			% \begin{align}
-			% 	I_{\mathrm{B}}(\bar{c}_{m_{\mathcal{K}}};z)
-			% 	& \triangleq \sum_j P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K}}}) \log \frac{P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K}}})}{P(\bar{z}_j)}\\
-			% 	& = \sum_j P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K}}}) \log \frac{P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K}}})}{\sum_{m_{\mathcal{K}}} \prod_{k \in \mathcal{K}} P(\bar{c}_{m_{\mathcal{K}}}) P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K}}})}
-			% 	\label{eq:backscatter_information_function}
-			% \end{align}
-			The backscatter marginal information function of tag $q \in \mathcal{K}$ associated with $\bar{c}_{i_q}$, $i_q \in \mathcal{M}$ is defined as
+			The backscatter marginal information function of tag $k \in \mathcal{K}$ associated with $\bar{c}_{m_k}$, $m_k \in \mathcal{M}$ is defined as
 			\begin{equation}
-				I_{\mathrm{B},q}(\bar{c}_{i_q};z) \triangleq \sum_{m_{\mathcal{K} \setminus \{q\}}} P_{\mathcal{K} \setminus \{q\}}(\bar{c}_{m_{\mathcal{K} \setminus \{q\}}}) I_{\mathrm{B}}(\bar{c}_{m_{\mathcal{K} \setminus \{q\}}},\bar{c}_{i_q};z),
+				I_{\mathrm{B},k}(\bar{c}_{m_k};z) \triangleq \sum_{m_{\mathcal{K} \setminus \{k\}}} P_{\mathcal{K} \setminus \{k\}}(\bar{c}_{m_{\mathcal{K} \setminus \{k\}}}) I_{\mathrm{B}}(\bar{c}_{m_{\mathcal{K} \setminus \{k\}}},\bar{c}_{m_k};z),
 				\label{eq:backscatter_marginal_information_function}
 			\end{equation}
-			% \begin{equation}
-			% 	I_{\mathrm{B},q}(\bar{c}_{i_q};z) \triangleq \sum_{m_{\mathcal{K} \setminus \{q\}}} \prod_{k \in \mathcal{K} \setminus \{q\}} P_k(\bar{c}_{m_k}) I_{\mathrm{B}}(\bar{c}_{m_{\mathcal{K} \setminus \{q\}}},\bar{c}_{i_q};z),
-			% 	\label{eq:backscatter_marginal_information_function}
-			% \end{equation}
-			% the backscatter marginal information function of tag $k$ associated with $\bar{c}_{m_k}$ is defined as
-			% \begin{equation}
-			% 	I_{\mathrm{B},k}(\bar{c}_{m_k};z) \triangleq \sum_{m_{\mathcal{K} \setminus \{k\}}} \prod_{k' \in \mathcal{K} \setminus \{k\}} P_{k'}(\bar{c}_{m_{k'}}) I_{\mathrm{B}}(\bar{c}_{m_{\mathcal{K} \setminus \{k\}}}, \bar{c}_{m_k};z),
-			% 	% \label{eq:backscatter_marginal_information_function}
-			% \end{equation}
-			% \begin{equation}
-			% 	I_{\mathrm{B},k}(\bar{c}_{m_k};z) \triangleq \sum_{m_{\mathcal{K} \setminus \{k\}}} \prod_{k' \in \mathcal{K} \setminus \{k\}} P_{k'}(\bar{c}_{m_{k'}}) I_{\mathrm{B}}(\bar{c}_{m_{\mathcal{K}}};z),
-			% 	\label{eq:backscatter_marginal_information_function}
-			% \end{equation}
-			% \begin{align}
-			% 	I_{\mathrm{B},k}(\bar{c}_{m_k};z)
-			% 	& \triangleq \sum_{m_{\mathcal{K} \setminus \{k\}}} P_{\mathcal{K} \setminus \{k\}}(\bar{c}_{m_{\mathcal{K} \setminus \{k\}}}) I_{\mathrm{B}}(\bar{c}_{m_{\mathcal{K}}};z)\\
-			% 	& = \sum_{m_{\mathcal{K} \setminus \{k\}}} \prod_{k' \in \mathcal{K} \setminus \{k\}} P_{k'}(\bar{c}_{m_{k'}}) I_{\mathrm{B}}(\bar{c}_{m_{\mathcal{K}}};z),
-			% 	% \label{eq:backscatter_marginal_information_function}
-			% \end{align}
-			% the backscatter marginal information function of $\mathcal{S} \subset \mathcal{K}$ is defined as
-			% \begin{equation}
-			% 	I_{\mathrm{B},\mathcal{S}}(\bar{c}_{m_{\mathcal{S}}};z) \triangleq \sum_{m_{\mathcal{K} \setminus \mathcal{S}}} P_{\mathcal{K} \setminus \mathcal{S}}(\bar{c}_{m_{\mathcal{K} \setminus \mathcal{S}}}) I_{\mathrm{B}}(\bar{c}_{m_{\mathcal{K}}};z),
-			% 	\label{eq:backscatter_marginal_information_function}
-			% \end{equation}
-			where $P_{\mathcal{K} \setminus \{q\}}(\bar{c}_{m_{\mathcal{K} \setminus \{q\}}}) = \prod_{k \in \mathcal{K} \setminus \{q\}} P_k(\bar{c}_{m_k})$.
+			where $P_{\mathcal{K} \setminus \{k\}}(\bar{c}_{m_{\mathcal{K} \setminus \{k\}}}) = \prod_{k' \in \mathcal{K} \setminus \{k\}} P_{k'}(\bar{c}_{m_{k'}})$.
 The backscatter mutual information can be expressed as\footnote{Please be aware that $c_{\mathcal{K}}$, $c_k$, $z$ are random variables, while $\bar{c}_{m_{\mathcal{K}}}$ and $\bar{c}_i$, $\bar{c}_{m_k}$, $\bar{z}_j$ represent the corresponding instances.}
@@
 			\end{subequations}
-			% \begin{align}
-			% 	I_{\mathrm{B}}(c_{\mathcal{K}};z)
-			% 	& = \mathbb{E}_{c_{\mathcal{K}}} \left[I_{\mathrm{B}}(\bar{c}_{m_{\mathcal{K}}};z)\right] = \mathbb{E}_{c_{\mathcal{S}}} \left[I_{\mathrm{B},\mathcal{S}}(\bar{c}_{m_{\mathcal{S}}};z)\right]\\
-			% 	& = \sum_{m_{\mathcal{K}}} \prod_{k \in \mathcal{K}} P_k(\bar{c}_{m_k}) \sum_j P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K}}}) \log \frac{P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K}}})}{P(\bar{z}_j)}.\label{eq:backscatter_sum_rate}
-			% \end{align}
 
@@
 As such, the tags can adjust the propagation environment in a potentially beneficial manner, and create artificial channel variation within each fading block.
-Similarly, we define the primary information function associated with tag input combination $\bar{c}_{m_{\mathcal{K}}}$ and the primary marginal information function of tag $q$ associated with symbol $\bar{c}_{i_q}$ respectively as
+Similarly, we define the primary information function associated with tag input combination $\bar{c}_{m_{\mathcal{K}}}$ and the primary marginal information function of tag $k$ associated with symbol $\bar{c}_{m_k}$ respectively as
+
 			\begin{align}
@@
 				& \triangleq N \log_2 \left(1 + \frac{\lvert \boldsymbol{h}_{\mathrm{E}}^H(\bar{c}_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_w^2}\right),\label{eq:primary_information_function}\\
-				I_{\mathrm{P},q}(\bar{c}_{i_q};\boldsymbol{y})
-				& \triangleq \sum_{m_{\mathcal{K} \setminus \{q\}}} P_{\mathcal{K} \setminus \{q\}}(\bar{c}_{m_{\mathcal{K} \setminus \{q\}}}) I_{\mathrm{P}}(\bar{c}_{m_{\mathcal{K} \setminus \{q\}}},\bar{c}_{i_q};\boldsymbol{y}),\label{eq:primary_marginal_information_function}
+				I_{\mathrm{P},k}(\bar{c}_{m_k};\boldsymbol{y})
+				& \triangleq \sum_{m_{\mathcal{K} \setminus \{k\}}} P_{\mathcal{K} \setminus \{k\}}(\bar{c}_{m_{\mathcal{K} \setminus \{k\}}}) I_{\mathrm{P}}(\bar{c}_{m_{\mathcal{K} \setminus \{k\}}},\bar{c}_{m_k};\boldsymbol{y}),\label{eq:primary_marginal_information_function}
 			\end{align}
-			% \begin{equation}
-			% 	I_{\mathrm{P},k}(\bar{c}_{m_k};\boldsymbol{y}) \triangleq \sum_{m_{\mathcal{K} \setminus \{k\}}} \prod_{k' \in \mathcal{K} \setminus \{k\}} P_{k'}(\bar{c}_{m_{k'}}) I_{\mathrm{P}}(\bar{c}_{m_{\mathcal{K}}};\boldsymbol{y}),
-			% 	\label{eq:primary_marginal_information_function}
-			% \end{equation}
-			% \begin{equation}
-			% 	I_{\mathrm{P},k}(\bar{c}_{m_k}) \triangleq \sum_{m_{\mathcal{K} \setminus \{k\}}} P_{\mathcal{K} \setminus \{k\}}(\bar{c}_{m_{\mathcal{K} \setminus \{k\}}}) I_{\mathrm{P}}(\bar{c}_{m_{\mathcal{K}}}),
-			% 	\label{eq:primary_marginal_information_function}
-			% \end{equation}
-			% \begin{equation}
-			% 	I_{\mathrm{P},\mathcal{S}}(\bar{c}_{m_{\mathcal{S}}}) \triangleq \sum_{m_{\mathcal{K} \setminus \mathcal{S}}} P_{\mathcal{K} \setminus \mathcal{S}}(\bar{c}_{m_{\mathcal{K} \setminus \mathcal{S}}}) I_{\mathrm{P}}(\bar{c}_{m_{\mathcal{K}}}),
-			% 	\label{eq:primary_marginal_information_function}
-			% \end{equation}
 			and the ergodic primary rate can be expressed as\footnote{The unit of \eqref{eq:backscatter_information_function}--\eqref{eq:backscatter_sum_rate} are \gls{bpcu}, while the unit of \eqref{eq:primary_information_function}--\eqref{eq:primary_ergodic_rate} are \gls{bpsphz}.}
@@
 			\end{subequations}
-			% \begin{align}
-			% 	I_{\mathrm{P}}(c_{\mathcal{K}})
-			% 	& = \mathbb{E}_{c_{\mathcal{K}}} \left[I_{\mathrm{P}}(\bar{c}_{m_{\mathcal{K}}})\right] = \mathbb{E}_{c_{\mathcal{S}}} \left[I_{\mathrm{P},\mathcal{S}}(\bar{c}_{m_{\mathcal{S}}})\right]\\
-			% 	& = \sum_{m_{\mathcal{K}}} \prod_{k \in \mathcal{K}} P_k(\bar{c}_{m_k}) \log_2 \left(1 + \frac{\lvert \boldsymbol{h}_{\mathrm{E}}^H(\bar{c}_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_w^2}\right).
-			% 	\label{eq:primary_ergodic_rate}
-			% \end{align}
 
@@
 		\begin{subsection}{Primary-backscatter rate region}
-			The weighted sum marginal information of tag $q$ associated with symbol $\bar{c}_{i_q}$ and the weighted sum primary-backscatter rate are defined respectively as
-			\begin{align}
-				I_q(\bar{c}_{i_q};\boldsymbol{y},z)
-				& \triangleq \rho I_{\mathrm{P},q}(\bar{c}_{i_q};\boldsymbol{y}) + (1 - \rho) I_{\mathrm{B},q}(\bar{c}_{i_q};z),\label{eq:weighted_sum_marginal_information}\\
-				I(c_{\mathcal{K}};\boldsymbol{y},z)
-				& \triangleq \rho I_{\mathrm{P}}(c_{\mathcal{K}};\boldsymbol{y}) + (1 - \rho) I_{\mathrm{B}}(c_{\mathcal{K}};z),\label{eq:weighted_sum_rate}
-			\end{align}
+			Define the weighted sum information function associated with tag input combination $\bar{c}_{m_{\mathcal{K}}}$ as
+			\begin{equation}
+				I(\bar{c}_{m_{\mathcal{K}}};\boldsymbol{y},z) \triangleq \rho I_{\mathrm{P}}(\bar{c}_{m_{\mathcal{K}}};\boldsymbol{y}) + (1 - \rho) I_{\mathrm{B}}(\bar{c}_{m_{\mathcal{K}}};z),
+				\label{eq:weighted_sum_information_function}
+			\end{equation}
+			the weighted sum marginal information of tag $k$ associated with symbol $\bar{c}_{m_k}$ as
+			\begin{equation}
+				I_k(\bar{c}_{m_k};\boldsymbol{y},z) \triangleq \rho I_{\mathrm{P},k}(\bar{c}_{m_k};\boldsymbol{y}) + (1 - \rho) I_{\mathrm{B},k}(\bar{c}_{m_k};z),
+				\label{eq:weighted_sum_marginal_information}
+			\end{equation}
+			and the weighted sum primary-backscatter rate as
+			\begin{equation}
+				I(c_{\mathcal{K}};\boldsymbol{y},z) \triangleq \rho I_{\mathrm{P}}(c_{\mathcal{K}};\boldsymbol{y}) + (1 - \rho) I_{\mathrm{B}}(c_{\mathcal{K}};z),
+				\label{eq:weighted_sum_rate}
+			\end{equation}
 			where $\rho \in [0,1]$ denotes the priority of the primary link.
@@
 			\begin{proposition}
-				The necessary and sufficient conditions for an input probability distribution $\boldsymbol{P}^{\star}$ to maximize the weighted sum primary-backscatter rate are that, $\forall i_q \in \mathcal{M}$ and $\forall q \in \mathcal{K}$,
+				The necessary and sufficient conditions for an input probability distribution $\boldsymbol{P}^{\star}$ to maximize the weighted sum primary-backscatter rate are that, $\forall m_k \in \mathcal{M}$ and $\forall k \in \mathcal{K}$,
 				\begin{subequations}
 					\begin{alignat}{2}
-						I_q(\bar{c}_{i_q};\boldsymbol{y},z) & = I(c_{\mathcal{K}};\boldsymbol{y},z), \quad && P_q^{\star}(\bar{c}_{i_q}) > 0,\label{co:probable_states}\\
-						I_q(\bar{c}_{i_q};\boldsymbol{y},z) & \le I(c_{\mathcal{K}};\boldsymbol{y},z), \quad && P_q^{\star}(\bar{c}_{i_q}) = 0.\label{co:dropped_states}
+						I_k(\bar{c}_{m_k};\boldsymbol{y},z) & = I(c_{\mathcal{K}};\boldsymbol{y},z), \quad && P_k^{\star}(\bar{c}_{m_k}) > 0,\label{co:probable_states}\\
+						I_k(\bar{c}_{m_k};\boldsymbol{y},z) & \le I(c_{\mathcal{K}};\boldsymbol{y},z), \quad && P_k^{\star}(\bar{c}_{m_k}) = 0.\label{co:dropped_states}
 					\end{alignat}
@@
 				\eqref{co:probable_states} means each probable state of each tag should produce the same marginal information (averaged over all states of other tags), while \eqref{co:dropped_states} implies any state of any tag with potentially less marginal information than above should not be used.
-				% An interpretation is that each probable state of each tag should produce the same marginal information (averaged over all states of other tags), while any state of any tag with potentially less marginal information than above should not be used.
-				% \begin{itemize}
-				% 	\item each probable state of each tag produces the same marginal information (averaged over all states of other tags)
-				% 	\item all states of all tags with potentially less marginal information should be dropped
-				% \end{itemize}
-				% An input probability distribution maximizes the weighted sum primary-backscatter rate if and only if each probable state of each tag produces the same mutual information.
-Specifically, the optimal $\boldsymbol{P}^{\star}$ to problem~\eqref{op:input_probability_distribution}
-
-				% the input probability distribution that achieves the weighted sum primary-backscatter capacity, at state $i_q \in \mathcal{M}$ of tag $q \in \mathcal{K}$,
-				% \begin{subequations}
-				% 	\begin{alignat}{2}
-				% 		I_q(\bar{c}_{i_q};\boldsymbol{y},z) & = I(c_{\mathcal{K}};\boldsymbol{y},z), \quad && P_q^{\star}(\bar{c}_{i_q}) > 0,\\
-				% 		I_q(\bar{c}_{i_q};\boldsymbol{y},z) & \le I(c_{\mathcal{K}};\boldsymbol{y},z), \quad && P_q^{\star}(\bar{c}_{i_q}) = 0.
-				% 	\end{alignat}
-				% \end{subequations}
 				\label{pr:optimal_conditions}
@@
 				\end{align}
-				and the corresponding \gls{kkt} conditions on the primal and dual solutions are, $\forall i_q \in \mathcal{M}$ and $\forall q \in \mathcal{K}$,
+				and the corresponding \gls{kkt} conditions on the primal and dual solutions are, $\forall m_k \in \mathcal{M}$ and $\forall k \in \mathcal{K}$,
 				\begin{subequations}
 					\begin{equation}
-						- \nabla_{P_q^{\star}(\bar{c}_{i_q})} I(c_{\mathcal{K}};\boldsymbol{y},z) + \mu_q^{\star} - \lambda_{q,i_q}^{\star} = 0,
+						- \nabla_{P_k^{\star}(\bar{c}_{m_k})} I(c_{\mathcal{K}};\boldsymbol{y},z) + \mu_k^{\star} - \lambda_{k,m_k}^{\star} = 0,
 					\end{equation}
 					\begin{equation}
-						\lambda_{q,i_q}^{\star} = 0, \quad P_q^{\star}(\bar{c}_{i_q}) > 0,
+						\lambda_{k,m_k}^{\star} = 0, \quad P_k^{\star}(\bar{c}_{m_k}) > 0,
 					\end{equation}
 					\begin{equation}
-						\lambda_{q,i_q}^{\star} \ge 0, \quad P_q^{\star}(\bar{c}_{i_q}) = 0,
+						\lambda_{k,m_k}^{\star} \ge 0, \quad P_k^{\star}(\bar{c}_{m_k}) = 0,
 					\end{equation}
@@
 				where the directional derivative can be explicitly expressed as
-				\begin{subequations}
-					\begin{align}
-						\nabla_{P_q^{\star}(\bar{c}_{i_q})} I(c_{\mathcal{K}};\boldsymbol{y},z)
-						& = \rho I_{\mathrm{P},q}(\bar{c}_{i_q};\boldsymbol{y}) + (1 - \rho) \left( I_{\mathrm{B},q}(\bar{c}_{i_q};z) - 1 \right)\\
-						& = I_q(\bar{c}_{i_q};\boldsymbol{y},z) - (1 - \rho),
-					\end{align}
-				\end{subequations}
-				such that $\mu_q^{\star}$ must satisfy
+				\begin{equation}
+					\nabla_{P_k^{\star}(\bar{c}_{m_k})} I(c_{\mathcal{K}};\boldsymbol{y},z) = I_k(\bar{c}_{m_k};\boldsymbol{y},z) - (1 - \rho).
+				\end{equation}
+
+				Due to the necessity and sufficiency of the \gls{kkt} conditions, we conclude that any input probability distribution $\boldsymbol{P}^{\star}$ maximizes the weighted sum primary-backscatter rate if and only if, $\forall m_k \in \mathcal{M}$ and $\forall k \in \mathcal{K}$,
 				\begin{subequations}
 					\begin{alignat}{2}
-						\mu_q^{\star} & = I_q(\bar{c}_{i_q};\boldsymbol{y},z) - (1 - \rho), \quad && P_q^{\star}(\bar{c}_{i_q}) > 0,\\
-						\mu_q^{\star} & \ge I_q(\bar{c}_{i_q};\boldsymbol{y},z) - (1 - \rho), \quad && P_q^{\star}(\bar{c}_{i_q}) = 0.
+						I_k(\bar{c}_{m_k};\boldsymbol{y},z) & = \mu_k^{\star} + (1 - \rho), \quad && P_k^{\star}(\bar{c}_{m_k}) > 0,\\
+						I_k(\bar{c}_{m_k};\boldsymbol{y},z) & \le \mu_k^{\star} + (1 - \rho), \quad && P_k^{\star}(\bar{c}_{m_k}) = 0,
 					\end{alignat}
 				\end{subequations}
-
-				Due to the necessity and sufficiency of the \gls{kkt} conditions, we can conclude that any input probability distribution $\boldsymbol{P}^{\star}$ maximizes the weighted sum primary-backscatter rate if and only if, $\forall i_q \in \mathcal{M}$ and $\forall q \in \mathcal{K}$,
-				\begin{subequations}
-					\begin{alignat}{2}
-						I_q(\bar{c}_{i_q};\boldsymbol{y},z) & = C_q, \quad && P_q^{\star}(\bar{c}_{i_q}) > 0,\\
-						I_q(\bar{c}_{i_q};\boldsymbol{y},z) & \le C_q, \quad && P_q^{\star}(\bar{c}_{i_q}) = 0,
-					\end{alignat}
-				\end{subequations}
-				where $C_q \triangleq \mu_q^{\star} + (1 - \rho)$. Apparently, it holds that
+				which implies
 				\begin{equation}
-					\sum_{i_q} P_q^{\star}(\bar{c}_{i_q}) I_q(\bar{c}_{i_q};\boldsymbol{y},z) = C_q.
+					\sum_{m_k} P_k^{\star}(\bar{c}_{m_k}) I_k(\bar{c}_{m_k};\boldsymbol{y},z) = \mu_k^{\star} + (1 - \rho).
 				\end{equation}
 
-				On the other hand, by the definition of marginations \eqref{eq:backscatter_sum_rate_expectation}, \eqref{eq:primary_ergodic_rate_expectation} and weighted summations \eqref{eq:weighted_sum_marginal_information}, \eqref{eq:weighted_sum_rate}, we have
+				On the other hand, by definition of marginations \eqref{eq:backscatter_sum_rate_expectation}, \eqref{eq:primary_ergodic_rate_expectation} and weighted summations \eqref{eq:weighted_sum_marginal_information}, \eqref{eq:weighted_sum_rate}, we have
 				\begin{equation}
-					\sum_{i_q} P_q^{\star}(\bar{c}_{i_q}) I_q(\bar{c}_{i_q};\boldsymbol{y},z) = I(c_{\mathcal{K}};\boldsymbol{y},z),
+					\sum_{m_k} P_k^{\star}(\bar{c}_{m_k}) I_k(\bar{c}_{m_k};\boldsymbol{y},z) = I(c_{\mathcal{K}};\boldsymbol{y},z),
 				\end{equation}
-				which is irrelevant to $q$. It implies that $\forall q \in \mathcal{K}$, $C_q = I(c_{\mathcal{K}};\boldsymbol{y},z)$, and thus Proposition~\eqref{pr:optimal_conditions} holds.
+				which is irrelevant to $k$. It suggests $I(c_{\mathcal{K}};\boldsymbol{y},z) = \mu_k^{\star} + (1 - \rho)$, $\forall k \in \mathcal{K}$, and completes the proof.
 			\end{proof}
@@
 			\begin{theorem}
-				The input probability distribution that achieves the weighted sum primary-backscatter capacity at state $i_q \in \mathcal{M}$ of tag $q \in \mathcal{K}$ is given by the limit of the following sequence\footnote{Note that the probability distribution of tag $q$ is based on the updated probability distribution of tags $1,\ldots,q-1$.}
+				The input probability distribution that achieves the weighted sum primary-backscatter capacity at state $i_k \in \mathcal{M}$ of tag $q \in \mathcal{K}$ is given by the limit of the following sequence\footnote{Note that the probability distribution of tag $q$ is based on the updated probability distribution of tags $1,\ldots,k-1$.}
 				\begin{equation}
@@
 			\begin{proof}
-				We first prove that for tag $q \in \mathcal{K}$, updating the probability of state $i_q \in \mathcal{M}$ by sequence~\eqref{eq:optimal_distribution} does not decrease the mutual information.
-				For a certain input combination $\bar{c}_{m_{\mathcal{K}}}$, let $P_{\mathcal{K}}(\bar{c}_{m_{\mathcal{K}}}) = \prod_{k \in \mathcal{K}} P_k(\bar{c}_{m_k})$ and $P_{\mathcal{K}}'(\bar{c}_{m_{\mathcal{K}}}) = P_q'(\bar{c}_{m_q}) \prod_{k \in \mathcal{K} \setminus \{q\}} P_k(\bar{c}_{m_k})$ be two probability distributions with potentially different marginal for tag $q$, and define $J \left( P_{\mathcal{K}}(\bar{c}_{m_{\mathcal{K}}}),P_{\mathcal{K}}'(\bar{c}_{m_{\mathcal{K}}}) \right)$ as the intermediate information function by \eqref{eq:intermediate_information_function}.
+				We first prove that for tag $q \in \mathcal{K}$, updating the probability of state $i_q \in \mathcal{M}$ by sequence~\eqref{eq:optimal_distribution} does not decrease mutual information.
+For any input combination $\bar{c}_{m_{\mathcal{K}}}$, let $P_{\mathcal{K}}(\bar{c}_{m_{\mathcal{K}}}) = \prod_{k \in \mathcal{K}} P_k(\bar{c}_{m_k})$ and $P_{\mathcal{K}}'(\bar{c}_{m_{\mathcal{K}}}) = P_q'(\bar{c}_{m_q}) \prod_{k \in \mathcal{K} \setminus \{q\}} P_k(\bar{c}_{m_k})$ be two probability distributions with potentially different marginal for tag $q$, and denote the corresponding mutual information and received energy distribution as $I(\bar{c}_{\mathcal{K}};\boldsymbol{y},z)$, $I'(\bar{c}_{\mathcal{K}};\boldsymbol{y},z)$ and $P(\bar{z}_j)$, $P'(\bar{z}_j)$, respectively.
+Also, define an intermediate function $J \left( P_{\mathcal{K}}(\bar{c}_{m_{\mathcal{K}}}),P_{\mathcal{K}}'(\bar{c}_{m_{\mathcal{K}}}) \right)$ by \eqref{eq:intermediate_information_function}, and apparently $I(\bar{c}_{\mathcal{K}};\boldsymbol{y},z) = J \left( P_{\mathcal{K}}(\bar{c}_{m_{\mathcal{K}}}),P_{\mathcal{K}}(\bar{c}_{m_{\mathcal{K}}}) \right)$.
 				\begin{figure*}[!b]
@@
 				\end{figure*}
-				It can be verified that for a fixed $P_{\mathcal{K}}'(\bar{c}_{m_{\mathcal{K}}})$, $J \left( P_{\mathcal{K}}(\bar{c}_{m_{\mathcal{K}}}),P_{\mathcal{K}}'(\bar{c}_{m_{\mathcal{K}}}) \right)$ is a concave function of $P_q(\bar{c}_{m_q})$ and is maximized by $\nabla_{P_q^{\star}(\bar{c}_{m_q})} J \left( P_{\mathcal{K}}(\bar{c}_{m_{\mathcal{K}}}),P_{\mathcal{K}}'(\bar{c}_{m_{\mathcal{K}}}) \right) = 0$, which can be explicitly written as
+				For a fixed $P_{\mathcal{K}}'(\bar{c}_{m_{\mathcal{K}}})$, $J \left( P_{\mathcal{K}}(\bar{c}_{m_{\mathcal{K}}}),P_{\mathcal{K}}'(\bar{c}_{m_{\mathcal{K}}}) \right)$ is a concave function of $P_q(\bar{c}_{m_q})$ and can be maximized at $\nabla_{P_q^{\star}(\bar{c}_{m_q})} J \left( P_{\mathcal{K}}(\bar{c}_{m_{\mathcal{K}}}),P_{\mathcal{K}}'(\bar{c}_{m_{\mathcal{K}}}) \right) = 0$, which reduces to
 				\begin{equation}
@@
 				where $i_q \ne m_q$ is the reference state and
-				% , and we define $\forall i_q \in \mathcal{M}$ and $\forall q \in \mathcal{K}$
 				\begin{align}
@@
 						& = \frac{\exp \left( \frac{1}{1 - \rho} S_k'(\bar{c}_{m_q}) \right)}{\sum_{m_q} \exp \left( \frac{1}{1 - \rho} S_k'(\bar{c}_{m_q}) \right)}\\
-						& = \frac{P_q^{(r)}(\bar{c}_{m_q}) \exp \left( \frac{\rho}{1 - \rho} I_q(\bar{c}_{m_q};\boldsymbol{y},z) \right)}{\sum_{m_q} P_q^{(r)}(\bar{c}_{m_q}) \exp \left( \frac{\rho}{1 - \rho} I_q(\bar{c}_{m_q};\boldsymbol{y},z) \right)}.
+						& = \frac{P_q'(\bar{c}_{m_q}) \exp \left( \frac{\rho}{1 - \rho} I_q(\bar{c}_{m_q};\boldsymbol{y},z) \right)}{\sum_{m_q} P_q'(\bar{c}_{m_q}) \exp \left( \frac{\rho}{1 - \rho} I_q(\bar{c}_{m_q};\boldsymbol{y},z) \right)}.
 						\label{eq:optimal_relative_distribution}
@@
 
-				Also, we notice that $P_q(\bar{c}_{i_q}) = 1 - \sum_{m_q \ne i_q} P_q^{\star}(\bar{c}_{m_q})$ has exactly the same form.
-It suggests that the solution of choosing $i_q$ as reference would coincide with that of choosing any $m_q \ne i_q$ as reference, such that \eqref{eq:optimal_relative_distribution} is also optimal for $i_q$.
-Therefore, for a fixed $P_{\mathcal{K}}'(\bar{c}_{m_{\mathcal{K}}})$, choosing $P_q(\bar{c}_{m_q})$ by \eqref{eq:optimal_relative_distribution} guarantees
+				Although optimality is not guaranteed for state $i_q$, we notice that $P_q(\bar{c}_{i_q}) = 1 - \sum_{m_q \ne i_q} P_q^{\star}(\bar{c}_{m_q})$ has exactly the same form as \eqref{eq:optimal_relative_distribution}.
+It suggests that the solution of choosing $i_q$ as reference would coincide with that of choosing any $m_q \ne i_q$ as reference, while optimality is guaranteed for $i_q$ in the latter case.
+Therefore, for a fixed $P_{\mathcal{K}}'(\bar{c}_{m_{\mathcal{K}}})$, $\forall i_q \in \mathcal{M}$ and $\forall q \in \mathcal{K}$, \eqref{eq:optimal_relative_distribution} ensures
 				\begin{equation}
-					J \left( P_{\mathcal{K}}(\bar{c}_{m_{\mathcal{K}}}),P_{\mathcal{K}}'(\bar{c}_{m_{\mathcal{K}}}) \right) \ge J \left( P_{\mathcal{K}}'(\bar{c}_{m_{\mathcal{K}}}),P_{\mathcal{K}}'(\bar{c}_{m_{\mathcal{K}}}) \right) = I \left(P_{\mathcal{K}}'(\bar{c}_{m_{\mathcal{K}}}) \right).
+					J \left( P_{\mathcal{K}}(\bar{c}_{m_{\mathcal{K}}}),P_{\mathcal{K}}'(\bar{c}_{m_{\mathcal{K}}}) \right) \ge I'(\bar{c}_{\mathcal{K}};\boldsymbol{y},z).
+					\label{eq:information_difference_lower}
 				\end{equation}
 
+				On the other hand, choosing $P_q(\bar{c}_{m_q})$ by \eqref{eq:optimal_relative_distribution} also satisfies
+				\begin{subequations}
+					\label{eq:information_difference_upper}
+					\begin{align}
+						\Delta
+						& \triangleq I(\bar{c}_{\mathcal{K}};\boldsymbol{y},z) - J \left( P_{\mathcal{K}}(\bar{c}_{m_{\mathcal{K}}}),P_{\mathcal{K}}'(\bar{c}_{m_{\mathcal{K}}}) \right)\\
+						& = (1 - \rho)
+						\sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(\bar{c}_{m_{\mathcal{K}}}) \sum_j P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K}}}) \log \frac{P'(\bar{z}_j) P_q(\bar{c}_{m_q})}{P(\bar{z}_j) P_q'(\bar{c}_{m_q})}\\
+						& = (1 - \rho) \sum_{m_q} \frac{P_q'(\bar{c}_{m_q}) u_q(\bar{c}_{m_q})}{\sum_{i_q} P_q'(\bar{c}_{i_q}) u_q(\bar{c}_{i_q})} \sum_j P(\bar{z}_j \mid \bar{c}_{m_q})\nonumber\\
+						& \quad \times \log \frac{\sum_{m_q'} P_q'(\bar{c}_{m_q'}) P(\bar{z}_j \mid \bar{c}_{m_q'}) u_q(\bar{c}_{m_q})}{\sum_{i_q'} P_q'(\bar{c}_{i_q'}) P(\bar{z}_j \mid \bar{c}_{i_q'}) u_q(\bar{c}_{i_q'})}\\
+						& \ge (1 - \rho) \sum_{m_q} \frac{P_q'(\bar{c}_{m_q}) u_q(\bar{c}_{m_q})}{\sum_{i_q} P_q'(\bar{c}_{i_q}) u_q(\bar{c}_{i_q})} \sum_j P(\bar{z}_j \mid \bar{c}_{m_q})\nonumber\\
+						& \quad \times \left( 1 - \frac{\sum_{i_q'} P_q'(\bar{c}_{i_q'}) P(\bar{z}_j \mid \bar{c}_{i_q'}) u_q(\bar{c}_{i_q'})}{\sum_{m_q'} P_q'(\bar{c}_{m_q'}) P(\bar{z}_j \mid \bar{c}_{m_q'}) u_q(\bar{c}_{m_q})} \right)\\
+						& = 0,
+					\end{align}
+				\end{subequations}
+				where $u_q(\bar{c}_{m_q}) \triangleq \exp \left( \frac{\rho}{1 - \rho} I_q(\bar{c}_{m_q};\boldsymbol{y},z) \right)$ and the equality holds if and only if \eqref{eq:optimal_relative_distribution} converges.
+Combining \eqref{eq:information_difference_lower} and \eqref{eq:information_difference_upper}, we conclude that update the input probability distribution of tag $q \in \mathcal{K}$ by \eqref{eq:optimal_distribution} does not decrease mutual information.
+
 				TODO
-				% \begin{equation}
-				% 	P_q^{\star}(\bar{c}_{i_q}) = \frac{P_q^{(r)}(\bar{c}_{i_q}) \exp \left( \frac{\rho}{1 - \rho} I_q(\bar{c}_{i_q};\boldsymbol{y},z) \right)}{\sum_{i_q} P_q^{(r)}(\bar{c}_{i_q}) \exp \left( \frac{\rho}{1 - \rho} I_q(\bar{c}_{i_q};\boldsymbol{y},z) \right)}.
-				% 	\label{eq:optimal_reference_distribution}
-				% \end{equation}
-
-				% of choosing any $i_q$ coincide
-				% Regularization on \eqref{eq:optimal_intermediate_information_condition}
 			\end{proof}
-
-			% Denote the Lagrange multiplier associated with \eqref{co:sum_probability} and \eqref{co:nonnegative_probability} as $\boldsymbol{\mu} \triangleq [\mu_1,\ldots,\mu_K]^T \in \mathbb{R}^{K \times 1}$ and $\boldsymbol{\Lambda} \triangleq [\boldsymbol{\lambda}_1^T,\ldots,\boldsymbol{\lambda}_K^T]^T \in \mathbb{R}^{M \times K}$ with $\boldsymbol{\lambda}_k \triangleq [\lambda_{k,1},\ldots,\lambda_{k,M}]^T \in \mathbb{R}^{M \times 1}$, respectively.
-The Lagrangian function of problem~\eqref{op:input_probability_distribution} is
-			% \begin{align}
-			% 	J
-			% 	& = - I + \sum_{k \in \mathcal{K}} \mu_k \left( \sum_{m_k \in \mathcal{M}} P_k(\bar{c}_{m_k}) - 1 \right)\nonumber\\
-			% 	& \quad - \sum_{k \in \mathcal{K}} \sum_{m_k \in \mathcal{M}} \lambda_{k,m_k} P_k(\bar{c}_{m_k}),
-			% \end{align}
-			% and the corresponding \gls{kkt} conditions on the primal and dual solutions are, $\forall i_q \in \mathcal{M}$ and $\forall q \in \mathcal{K}$,
-			% \begin{subequations}
-			% 	\begin{equation}
-			% 		- \pdv{I}{P_q^{\star}(\bar{c}_{i_q})} + \mu_q^{\star} - \lambda_{q,i_q}^{\star} = 0,
-			% 	\end{equation}
-			% 	\begin{equation}
-			% 		\lambda_{q,i_q}^{\star} = 0, \quad P_q^{\star}(\bar{c}_{i_q}) > 0,
-			% 	\end{equation}
-			% 	\begin{equation}
-			% 		\lambda_{q,i_q}^{\star} \ge 0, \quad P_q^{\star}(\bar{c}_{i_q}) = 0.
-			% 	\end{equation}
-			% \end{subequations}
-
-			% The partial derivative can be explicitly expressed as
-			% \begin{subequations}
-			% 	\begin{align}
-			% 		\pdv{I}{P_q^{\star}(\bar{c}_{i_q})}
-			% 		& = \rho I_{\mathrm{P},q}(\bar{c}_{i_q};\boldsymbol{y}) + (1 - \rho) \left( I_{\mathrm{B},q}(\bar{c}_{i_q};z) - 1 \right)\\
-			% 		& = I_q(\bar{c}_{i_q};\boldsymbol{y},z) - (1 - \rho),
-			% 	\end{align}
-			% \end{subequations}
-			% which suggests $\mu_q^{\star}$ must satisfy
-			% \begin{subequations}
-			% 	\begin{alignat}{2}
-			% 		\mu_q^{\star} & = I_q(\bar{c}_{i_q};\boldsymbol{y},z) - (1 - \rho), \quad && P_q^{\star}(\bar{c}_{i_q}) > 0,\\
-			% 		\mu_q^{\star} & \ge I_q(\bar{c}_{i_q};\boldsymbol{y},z) - (1 - \rho), \quad && P_q^{\star}(\bar{c}_{i_q}) = 0.
-			% 	\end{alignat}
-			% \end{subequations}
-
-			% Due to the necessity and sufficiency of the \gls{kkt} conditions, we can conclude that any input probability distribution $\boldsymbol{P}^{\star}$ maximizes the weighted sum primary-backscatter rate if and only if, $\forall i_q \in \mathcal{M}$ and $\forall q \in \mathcal{K}$,
-			% \begin{subequations}
-			% 	\begin{alignat}{2}
-			% 		I_q(\bar{c}_{i_q};\boldsymbol{y},z) & = C_q, \quad && P_q^{\star}(\bar{c}_{i_q}) > 0,\\
-			% 		I_q(\bar{c}_{i_q};\boldsymbol{y},z) & \le C_q, \quad && P_q^{\star}(\bar{c}_{i_q}) = 0,
-			% 	\end{alignat}
-			% \end{subequations}
-			% where $C_q \triangleq \mu_q^{\star} + (1 - \rho)$. Apparently, it holds that
-			% \begin{equation}
-			% 	\sum_{i_q} P_q^{\star}(\bar{c}_{i_q}) I_q(\bar{c}_{i_q};\boldsymbol{y},z) = C_q.
-			% \end{equation}
-
-			% On the other hand, by the definition of marginations \eqref{eq:backscatter_sum_rate_expectation}, \eqref{eq:primary_ergodic_rate_expectation} and weighted summations \eqref{eq:weighted_sum_marginal_information}, \eqref{eq:weighted_sum_rate}, we have
-			% \begin{equation}
-			% 	\sum_{i_q} P_q^{\star}(\bar{c}_{i_q}) I_q(\bar{c}_{i_q};\boldsymbol{y},z) = I(c_{\mathcal{K}};\boldsymbol{y},z),
-			% \end{equation}
-			% which is irrelevant to $q$. Hence, $C_q = I(c_{\mathcal{K}};\boldsymbol{y},z)$, $\forall q \in \mathcal{K}$ and
-			% \begin{subequations}
-			% 	\begin{alignat}{2}
-			% 		I_q(\bar{c}_{i_q};\boldsymbol{y},z) & = I(c_{\mathcal{K}};\boldsymbol{y},z), \quad && P_q^{\star}(\bar{c}_{i_q}) > 0,\\
-			% 		I_q(\bar{c}_{i_q};\boldsymbol{y},z) & \le I(c_{\mathcal{K}};\boldsymbol{y},z), \quad && P_q^{\star}(\bar{c}_{i_q}) = 0.
-			% 	\end{alignat}
-			% \end{subequations}
-
-			% It suggests that an input probability distribution maximizes the weighted sum primary-backscatter rate if and only if each probable state of each tag produces the same mutual information.
-On top of this, we extend the Blahut-Arimoto algorithm to our case and obtain the optimal input probability distribution as follows.
-
-			% \begin{theorem}
-			% 	The input probability distribution that achieves the weighted sum primary-backscatter capacity, at state $i_q \in \mathcal{M}$ of tag $q \in \mathcal{K}$, is given by the limit of the following sequence\footnote{Note that the probability distribution of tag $q$ is based on the updated probability distribution of tags $1,\ldots,q-1$.}
-			% 	\begin{equation}
-			% 		P_q^{(r+1)}(\bar{c}_{i_q}) = P_q^{(r)}(\bar{c}_{i_q}) \frac{\exp \left( I_q(\bar{c}_{i_q};\boldsymbol{y},z) \right)}{\sum_{m_q} P_q^{(r)}(\bar{c}_{m_q}) \exp \left( I_q(\bar{c}_{m_q};\boldsymbol{y},z) \right)},
-			% 	\end{equation}
-			% 	where $r \in \mathbb{Z}_+$ is the iteration index and $P_q^{(0)}(\bar{c}_{i_q}) > 0$, $\forall i_q \in \mathcal{M}$ and $\forall q \in \mathcal{K}$.
-			% \end{theorem}
 		\end{subsection}
 
-		\begin{subsection}{Decision region}
-			As indicated by \cite{Qian2019b}, the optimal \gls{ml} decision regions are very close to the optimal decision regions to problem \eqref{op:rate_region}.
+		% \begin{subsection}{Decision region}
+		% 	As indicated by \cite{Qian2019b}, the optimal \gls{ml} decision regions are very close to the optimal decision regions to problem \eqref{op:rate_region}.
 We can either use \eqref{eq:decision_region} as suboptimal, or take derivative of \eqref{eq:backscatter_sum_rate} w.r.t.
 $T_{i-1,i}$ and $T_{i,i+1}$ (however, closed-form solutions are unavailable and two-dimensional search is needed).
-		\end{subsection}
+		% \end{subsection}
 
-		\begin{subsection}{Precoder}
-			Interestingly, we can design precoder to adjust the expectation of the received power \eqref{eq:receive_variance} at each tag input combination, which can avoid the detection blind spots in \cite{Qian2019} and further boost the weighted sum-rate.
+		% \begin{subsection}{Precoder}
+		% 	Interestingly, we can design precoder to adjust the expectation of the received power \eqref{eq:receive_variance} at each tag input combination, which can avoid the detection blind spots in \cite{Qian2019} and further boost the weighted sum-rate.
 However, the problem is highly non-convex -- the information function associated with input combination state $i$ is
-			\begin{align}
-				I(\bar{c}_i;z)
-				& = \sum_{j \in \mathcal{M^K}} \int_{T_{j-1,j}}^{T_{j,j+1}} \frac{z^{N-1} \exp \left(-\frac{z}{\mathrm{tr}(H_{\mathrm{E},i} W) + \sigma_w^2}\right)}{\left(\mathrm{tr}(H_{\mathrm{E},i} W) + \sigma_w^2\right)^N (N-1)!} \dd z\nonumber\\
-				& \quad \times \log \frac{\int_{T_{j-1,j}}^{T_{j,j+1}} \frac{z^{N-1} \exp \left(-\frac{z}{\mathrm{tr}(H_{\mathrm{E},i} W) + \sigma_w^2}\right)}{\left(\mathrm{tr}(H_{\mathrm{E},i} W) + \sigma_w^2\right)^N (N-1)!} \dd z}{\sum_{i' \in \mathcal{M^K}} \int_{T_{j-1,j}}^{T_{j,j+1}} \frac{z^{N-1} \exp \left(-\frac{z}{\mathrm{tr}(H_{\mathrm{E},i'} W) + \sigma_w^2}\right)}{\left(\mathrm{tr}(H_{\mathrm{E},i'} W) + \sigma_w^2\right)^N (N-1)!} \dd z},
-				\label{eq:foo}
-			\end{align}
-			and the mutual information can be expressed as a function of $W$ by combining \eqref{eq:backscatter_sum_rate} and \eqref{eq:foo}.
+		% 	\begin{align}
+		% 		I(\bar{c}_i;z)
+		% 		& = \sum_{j \in \mathcal{M^K}} \int_{T_{j-1,j}}^{T_{j,j+1}} \frac{z^{N-1} \exp \left(-\frac{z}{\mathrm{tr}(H_{\mathrm{E},i} W) + \sigma_w^2}\right)}{\left(\mathrm{tr}(H_{\mathrm{E},i} W) + \sigma_w^2\right)^N (N-1)!} \dd z\nonumber\\
+		% 		& \quad \times \log \frac{\int_{T_{j-1,j}}^{T_{j,j+1}} \frac{z^{N-1} \exp \left(-\frac{z}{\mathrm{tr}(H_{\mathrm{E},i} W) + \sigma_w^2}\right)}{\left(\mathrm{tr}(H_{\mathrm{E},i} W) + \sigma_w^2\right)^N (N-1)!} \dd z}{\sum_{i' \in \mathcal{M^K}} \int_{T_{j-1,j}}^{T_{j,j+1}} \frac{z^{N-1} \exp \left(-\frac{z}{\mathrm{tr}(H_{\mathrm{E},i'} W) + \sigma_w^2}\right)}{\left(\mathrm{tr}(H_{\mathrm{E},i'} W) + \sigma_w^2\right)^N (N-1)!} \dd z},
+		% 		\label{eq:foo}
+		% 	\end{align}
+		% 	and the mutual information can be expressed as a function of $W$ by combining \eqref{eq:backscatter_sum_rate} and \eqref{eq:foo}.
 
-			So far I have no idea how to solve this issue, and found no reference regarding precoder design for \gls{ambc}/\gls{sr} with discrete channels (although some naive combiner designs are available for \gls{bibo}).
+		% 	So far I have no idea how to solve this issue, and found no reference regarding precoder design for \gls{ambc}/\gls{sr} with discrete channels (although some naive combiner designs are available for \gls{bibo}).
 Personally, I believe the precoder design is the key to (i) boost the rate region and avoid blind spots in conventional \gls{ambc}; (ii) build our proposal over existing infrastructures.
 Ideally, assuming the number of transmit antennas $Q$ is larger than the number of tags $K$, the optimal energy levels should be almost uniformly spaced (as $z$ follows Erlang distribution) to concentrate the channel transitional probability on diagonal as possible.
-		\end{subsection}
+		% \end{subsection}
 	\end{section}
-
-	% \begin{section}{The Single-tag Case}
-	% 	% \begin{figure}[!t]
-	% 	% 	\centering
-	% 	% 	\def\svgwidth{0.9\columnwidth}
-	% 	% 	\import{assets/}{symbiotic_radio.pdf_tex}
-	% 	% 	\caption{A single-user single-tag symbiotic radio system.}
-	% 	% 	\label{fi:symbiotic_radio}
-	% 	% \end{figure}
-	% 	As shown in Fig.~NULL, we propose a single-user (\gls{ue}) single-tag (\gls{tg}) symbiotic radio network where the \gls{rf} signal generated by the single-antenna Access Point (\gls{ap}) is shared by two coexisting systems.
-In the primary \gls{ap}-\gls{ue} downlink system, the \gls{ap} transmits to the single-antenna user.
-In the secondary \gls{ap}-\gls{tg}-\gls{ue} backscatter system, the \gls{ap} acts as the carrier emitter, the user serves as the backscatter reader, and the single-antenna tag modulates its information over the reradiated \gls{rf} signal by varying the reflection coefficient.
-Denote the \gls{ap}-\gls{ue} direct channel as $h_{\mathrm{D}}$, the \gls{ap}-\gls{tg} forward channel as $h_{\mathrm{F}}$, and the \gls{tg}-\gls{ue} backward channel as $h_{\mathrm{B}}$.
-We consider the quasi-static block fading model and assume the CSI of the direct channel and the cascaded forward-backward channel $h_{\mathrm{C}} \triangleq h_{\mathrm{B}} h_{\mathrm{F}}$ are known at the \gls{ap}.\footnote{Due to the lack of \gls{rf} chains at the passive tag, accurate and efficient CSI acquisition at the \gls{ap} can be challenging.
-One possible approach is that the \gls{ap} sends known pilots, the tag responds in a pre-defined manner, and the user performs least-square estimation then feeds back to the \gls{ap} \cite{Bharadia2015,Yang2015b,Guo2019g}.} It is assumed that the primary symbol $s$ follows standard \gls{cscg} distribution $\mathcal{CN}(0,1)$ and the secondary symbol $c$ employs $M$-\gls{psk} modulation by \eqref{eq:backscatter_modulation}.
-Due to the practical constraints on switching speed and synchronization gap, the passive tag typically transmits at a much lower data rate than the \gls{ap}.
-Hence, we assume the secondary symbol period is $N \gg 1 \in \mathbb{Z}_{++}$ times the primary symbol period and focus on the interval of one particular $c$.
-At (primary) symbol block $n \in \mathcal{N} \triangleq \{1,\ldots,N\}$, the user simultaneously captures the signal from both primary and secondary links as\footnote{We assume the time difference of arrival from the \gls{ap}-\gls{ue} path and the \gls{ap}-\gls{tg}-\gls{ue} path are negligible compared to the symbol period \cite{Guo2019b,Liang2020,Long2020b}.}
-	% 	\begin{equation}
-	% 		y[n] = \sqrt{P} h_{\mathrm{D}} s[n] + \sqrt{\alpha P} h_{\mathrm{C}} c s[n] + w[n],
-	% 	\end{equation}
-	% 	where $P$ is the average transmit power at the \gls{ap} and $w \sim \mathcal{CN}(0,\sigma^2)$ is the additive white Gaussian noise.
-We also define $\boldsymbol{y} \triangleq \bigl[y[1],\ldots,y[N]\bigr]^T$.
-
-	% 	\begin{remark}
-	% 		The symbiotic radio network can be regarded as a special case of Multiple Access Channel (\gls{mac}) because the \gls{ap} and the tag simultaneously transmit to the user.
-It is known that Superposition Coding-Successive Interference Cancellation (\gls{sc}-\gls{sic}) with different decoding orders can achieve different vertices of the \gls{mac} capacity region \cite{Goldsmith2005}.
-Therefore, most relevant papers proposed the user to first decode the primary message (by treating the tag interference as noise), cancel out its contribution from the received signal, then decode the secondary message.
-Since the direct channel is typically much stronger than the cascaded channel \cite{Ozdogan2020}, the primary decoding is expected to enjoy a high Signal-to-Interference-and-Noise Ratio (SINR) and the secondary decoding is ideally interference-free.
-	% 	\end{remark}
-
-	% 	\begin{remark}
-	% 		The main difference between symbiotic radio and conventional \gls{mac} is that the primary message also reaches the user from the backscatter link.
-This characteristic inspires one to first decode the tag message, then model its contribution within the equivalent channel during primary decoding (i.e., unify backscatter decoding and channel training), instead of performing \gls{sic}.
-In such case, the reflection pattern not only embeds the tag message but also adjusts the legacy channel in a controllable manner.
-Therefore, for a fixed fading block, the primary transmission is able to achieve the ergodic capacity with artificial channel variation created by the backscatter modulation.
-[Channel over channel, randomness over randomness]
-	% 	\end{remark}
-
-	% 	\begin{subsection}{Backscatter Transmission}
-	% 		To investigate how backscatter modulation potentially benefits the primary transmission, we first decode the tag symbol $c$ in presence of the interference from the primary message $\boldsymbol{s}$.
-In such case, the detection indeed coincides with that of Ambient Backscatter Communications (\gls{ambc}) where the signaling from the ambient source is unknown, and the received signal per symbol block follows the \gls{cscg} distribution of $y_m[n] \sim \mathcal{CN}(0,\sigma_m^2)$, where
-	% 		\begin{equation}
-	% 			\sigma_m^2 \triangleq \lvert h_{\mathrm{D}} + \sqrt{\alpha} h_{\mathrm{C}} c_m \rvert^2 P + \sigma^2
-	% 			\label{eq:typical_energy}
-	% 		\end{equation}
-	% 		denotes the typical received signal energy over $N$ symbol blocks when the tag is at state $m$, which can be estimated at the user.
-For the ease of exposition, we sort $\{\sigma_m^2\}$ in a ascending order by bijective mapping $f \colon m \mapsto i$\footnote{Note that the mapping is not unique and the detection fails when two different constellation points yield the same energy level.} and let $\sigma_i^2 \le \sigma_j^2$ for $i < j$, $i,j \in \mathcal{M}$.
-Denote $\mathcal{H}_i$ as the hypothesis that the tag transmits $c_i$.
-Following \cite{Qian2019}, the optimal Maximum-Likelihood (\gls{ml}) detector boils down to the energy detector, and the likelihood ratio between hypotheses $\mathcal{H}_i$ and $\mathcal{H}_j$ is
-	% 		\begin{equation}
-	% 			\Lambda_{i,j}(\boldsymbol{y}) = \frac{f(\boldsymbol{y} \mid \mathcal{H}_i)}{f(\boldsymbol{y} \mid \mathcal{H}_j)} = \left( \frac{\sigma_j^2}{\sigma_i^2} \right)^N \exp \left( \frac{(\sigma_i^2 - \sigma_j^2) z}{\sigma_i^2 \sigma_j^2} \right),
-	% 		\end{equation}
-	% 		where $f(\boldsymbol{y} \mid \mathcal{H}_i)$, $f(\boldsymbol{y} \mid \mathcal{H}_j)$ denote respectively the conditional probability density function of receiving $\boldsymbol{y}$ under hypothesis $\mathcal{H}_i$ and $\mathcal{H}_j$, and $z \triangleq \lVert y \rVert^2$ is the received signal energy over $N$ symbol blocks.
-The corresponding decision rule is
-	% 		\begin{equation}
-	% 			\Lambda_{i,j}(\boldsymbol{y}) \underset{H_j}{\overset{H_i}{\lessgtr}} 1 \iff z \underset{H_j}{\overset{H_i}{\lessgtr}} T_{i,j},
-	% 		\end{equation}
-	% 		where the optimal detection threshold is
-	% 		\begin{equation}
-	% 			T_{i,j} \triangleq N \frac{\sigma_i^2 \sigma_j^2}{\sigma_i^2 - \sigma_j^2} \log \frac{\sigma_i^2}{\sigma_j^2},
-	% 			\label{eq:detection_threshold}
-	% 		\end{equation}
-	% 		and the decision region of hypothesis $\mathcal{H}_i$ can be expressed as
-	% 		\begin{equation}
-	% 			\mathcal{R}_i \triangleq [T_{i-1, i}, T_{i, i+1}),
-	% 			\label{eq:decision_region_}
-	% 		\end{equation}
-	% 		with $T_{0, 1} \triangleq 0$ and $T_{M, M+1} \triangleq \infty$. On top of this, we define the forward transition probability matrix $\boldsymbol{P} \in \mathbb{R}_{+}^{M \times M}$ as
-	% 		\begin{equation}
-	% 			\boldsymbol{P} \triangleq
-	% 			\begin{bmatrix}
-	% 				p_{1, 1} & \ldots & p_{1, M} \\
-	% 				\vdots & \ddots & \vdots \\
-	% 				p_{M, 1} & \ldots & p_{M, M}
-	% 			\end{bmatrix},
-	% 		\end{equation}
-	% 		where $p_{i,j}$ denotes the transition probability from channel input state $i$ to output state $j$. It can be derived as
-	% 		\begin{equation}
-	% 			p_{i,j} = p(z \in \mathcal{R}_j \mid \mathcal{H}_i) = \int_{\mathcal{R}_j} f(z \mid \mathcal{H}_i) \dd z,
-	% 			\label{eq:transition_probability}
-	% 		\end{equation}
-	% 		where $f(z \mid \mathcal{H}_i)$ is the conditional probability density function of receiving $z$ under hypothesis $\mathcal{H}_i$.
-Since $z$ follows chi-squared distribution with $2N$ degrees of freedom, it holds that
-	% 		\begin{equation}
-	% 			f(z \mid \mathcal{H}_i) = \frac{z^{N-1} e^{-z/\sigma_i^2}}{\sigma_i^{2N} \Gamma(N)},
-	% 			\label{eq:conditional_pdf}
-	% 		\end{equation}
-	% 		where $\Gamma(\cdot)$ is the gamma function.
-To summarize, with the CSI of the direct and cascaded links, the typical energy of the received signal can be estimated by \eqref{eq:typical_energy}, the energy detection threshold can be computed by \eqref{eq:detection_threshold}, the decision region can be retrieved by \eqref{eq:decision_region}, and the forward transition matrix $\boldsymbol{P}$ can be calculated by substituting \eqref{eq:conditional_pdf} into \eqref{eq:transition_probability}.
-
-	% 		We then investigate the achievable rate of the backscatter link.
-Denote the tag input probability mass function as $\boldsymbol{r} = [r_1,\ldots,r_M]^T \in \mathbb{R}_+^{M \times 1}$ where $r_m$ is the probability to transmit symbol $c_m$ [strictly positive?].
-For a given input distribution $\boldsymbol{r}$ and forward transition matrix $\boldsymbol{P}$, the achievable backscatter rate can be written as
-	% 		\begin{equation}
-	% 			R_c = \max_{\boldsymbol{Q} \ge 0} \sum_{i \in \mathcal{M}} \sum_{j \in \mathcal{M}} r_i p_{i,j} \log_2 \frac{q_{j, i}}{r_i} \ [\si{bpcu}],
-	% 			\label{eq:secondary_rate}
-	% 		\end{equation}
-	% 		where $\boldsymbol{Q} \in \mathbb{R}_{+}^{M \times M}$ is the backward transition probability matrix
-	% 		\begin{equation}
-	% 			\boldsymbol{Q} \triangleq
-	% 			\begin{bmatrix}
-	% 				q_{1, 1} & \ldots & q_{1, M} \\
-	% 				\vdots & \ddots & \vdots \\
-	% 				q_{M, 1} & \ldots & q_{M, M}
-	% 			\end{bmatrix},
-	% 		\end{equation}
-	% 		and $q_{j, i}$ denotes the transition probability from channel output state $j$ to input state $i$.
-	% 	\end{subsection}
-
-	% 	\begin{subsection}{Legacy Transmission}
-	% 		Once the backscattered symbol is successfully recovered, it is combined with the cascaded channel to eliminate the uncertainty of the \gls{ap}-\gls{tg}-\gls{ue} path and assist the legacy transmission.
-Therefore, the received signal at symbol block $n$ is essentially
-	% 		\begin{equation}
-	% 			y[n] = \sqrt{P} (h_{\mathrm{D}} + \sqrt{\alpha} h_{\mathrm{C}} c) s[n] + w[n] \triangleq \sqrt{P} h_{\mathrm{E}}(c) s + w[n],
-	% 		\end{equation}
-	% 		which is reminiscent of an \gls{irs}-aided point-to-point transmission with an equivalent channel of
-	% 		\begin{equation}
-	% 			h_{\mathrm{E}}(c) \triangleq h_{\mathrm{D}} + \sqrt{\alpha} h_{\mathrm{C}} c.
-	% 		\end{equation}
-	% 		For primary transmission, backscatter modulation creates an artificial fast fading within each fading block, and \gls{ap} can obtain the equivalent CSI distribution for any given tag input probability mass function $\boldsymbol{r}$.
-Therefore, the ergodic capacity of primary transmission within each symbol block is \cite{Tse2005}
-	% 		\begin{align}
-	% 			R_s
-	% 			& = \mathbb{E}_c \bigl[ \log_2 (1 + \gamma \lvert h_{\mathrm{E}}(c) \rvert^2) \bigr] \nonumber \\
-	% 			& = \sum_{i \in \mathcal{M}} r_i \log_2 \bigl( 1 + \gamma \lvert h_{\mathrm{D}} + \sqrt{\alpha} h_{\mathrm{C}} c_i \rvert^2 \bigr) \ [\si{bps/Hz}],
-	% 			\label{eq:primary_rate}
-	% 		\end{align}
-	% 		where $\gamma \triangleq P / \sigma^2$ is the average transmit Signal-to-Noise Ratio (SNR).
-It can be concluded that the achievable rate of both primary and secondary links depend on the tag input distribution.
-	% 	\end{subsection}
-	% 	\label{se:system_model}
-
-	% 	\begin{subsection}{Achievable rate region}
-	% 		To achieve a flexible tradeoff between the backscatter and legacy links, we aims to optimize the tag input probability mass function, under $M$-\gls{psk} modulation, to maximize the weighted sum of the primary and secondary rates subject to the sum-probability constraint
-	% 		\begin{maxi!}
-	% 			{\scriptstyle{\boldsymbol{r} \ge 0}}{\rho R_s + (1 - \rho) R_c}{\label{op:weighted_sum_rate}}{\label{ob:weighted_sum_rate}}
-	% 			\addConstraint{\sum_{i \in \mathcal{M}} r_i}{=1,}{\label{co:sum_probability}}
-	% 		\end{maxi!}
-	% 		where $\rho \in [0, 1]$ is the weight factor. By substituting \eqref{eq:secondary_rate} and \eqref{eq:primary_rate} into \eqref{ob:weighted_sum_rate}, the problem expands to
-	% 		\begin{maxi!}
-	% 			{\scriptstyle{\boldsymbol{r} \ge 0, \boldsymbol{Q} \ge 0}}{\rho \sum_{i \in \mathcal{M}} r_i \log_2 \bigl( 1 + \gamma \lvert h_{\mathrm{D}} + \sqrt{\alpha} h_{\mathrm{C}} c_i \rvert^2 \bigr) \nonumber}{}{}
-	% 			\breakObjective{+ (1 - \rho) \sum_{i \in \mathcal{M}} \sum_{j \in \mathcal{M}} r_i p_{i,j} \log_2 \frac{q_{j, i}}{r_i}}{\label{ob:weighted_sum_rate_expanded}}
-	% 			\addConstraint{\sum_{i \in \mathcal{M}} r_i}{=1.}{}
-	% 		\end{maxi!}
-	% 		Similar to the Blahut-Arimoto algorithm \cite{Arimoto1972,Blahut1972}, we optimize $\boldsymbol{r}$ and $\boldsymbol{Q}$ alternatively to obtain the local optimal tag input distribution and the corresponding weighted sum-rate.
-	% 		\begin{theorem}
-	% 			For any valid tag input probability mass function $\boldsymbol{r}$ [$\boldsymbol{r} > \boldsymbol{0}$?], the optimal backward transition probability from channel output state $j$ to input state $i$ follows Bayes' Theorem as
-	% 			\begin{equation}
-	% 				q_{j, i}^{\star} = \frac{r_i p_{i,j}}{\sum_{i'} r_{i'} p_{i', j}}.
-	% 				\label{eq:backward_transition}
-	% 			\end{equation}
-	% 			\label{th:backward_transition}
-	% 		\end{theorem}
-	% 		\begin{proof}
-	% 			Please refer to Appendix~\ref{ap:backward_transition}.
-	% 		\end{proof}
-	% 		\begin{theorem}
-	% 			For any valid backward transition probability $\boldsymbol{Q}$ [$\boldsymbol{Q} \ge 0$?], the optimal tag input probability mass function is given by
-	% 			\begin{equation}
-	% 				r_i = \frac{\bigl( 1 + \gamma \lvert h_{\mathrm{D}} + \sqrt{\alpha} h_{\mathrm{C}} c_i \rvert^2 \bigr)^{\rho / (1 - \rho)} \prod_{j \in \mathcal{M}} q_{j, i}^{p_{i,j}}}{\sum_{i' \in \mathcal{M}} \bigl( 1 + \gamma \lvert h_{\mathrm{D}} + \sqrt{\alpha} h_{\mathrm{C}} c_{i'} \rvert^2 \bigr)^{\rho / (1 - \rho)} \prod_{j \in \mathcal{M}} q_{j, i'}^{p_{i', j}}}.
-	% 				\label{eq:input_distribution}
-	% 			\end{equation}
-	% 			\label{th:input_distribution}
-	% 		\end{theorem}
-	% 		\begin{proof}
-	% 			Please refer to Appendix~\ref{ap:input_distribution}.
-	% 		\end{proof}
-	% 		\begin{proposition}
-	% 			For any feasible initial point [constellation subset], the Algorithm is guaranteed to converge to the global optimal of problem \eqref{op:weighted_sum_rate} and achieve the maximum weighted-sum rate.
-	% 		\end{proposition}
-	% 		\begin{proof}
-	% 			The proof is similar to that in \cite[Chapter~9.3]{Yeung2008} and omitted here.
-	% 		\end{proof}
-	% 	\end{subsection}
-	% \end{section}
-
-	% \begin{section}{OFDM}
-	% 	Due to the constraint of energy detection, with single-antenna tags and reader, at most one \gls{ambc} tag can be decoded at a time and accurate detection requires repetition coding over multiple time/frequency blocks to mitigate the impact of primary symbols.
-Here we consider frequency-independent tag reflection and schedule one tag per OFDM symbol.
-
-	% 	At OFDM symbol $r$, tag $l$ modulates its own information over all $N$ subcarriers while the remaining tags may operate in the cooperative (quantized \gls{irs}) mode.
-Channel frequency response at subband $n$ and block $r$
-	% 	Received signal at OFDM symbol $r$ and subband $n$ is
-	% 	\begin{equation}
-	% 		y_n[r] = \sqrt{P} h_{\mathrm{E}}[r] s_n[r] + \sqrt{\alpha P} h_{\mathrm{C},l} c_l s_n[r] + w_n[r],
-	% 	\end{equation}
-	% 	where $h_{\mathrm{E}}[r] \triangleq \sum_{l' \ne l} h_{\mathrm{C},l'} c_{l'}^\star$ and $c_l$ is the symbol of tag $l$.
-Apparently $y_n[r] \sim \mathcal{CN}(0,\sigma_n^2[r])$ with $\sigma_n^2[r] \triangleq \lvert h_{\mathrm{E}}[r] + \sqrt{\alpha} h_{\mathrm{C},l} c_l \rvert^2 P + \sigma^2$.
-Define $\boldsymbol{y}[r] \triangleq [y_1[r],\ldots,y_N[r]]^T$ and we can do energy detection over $N$ subcarriers.
-	% \end{section}
-
-	% \begin{section}{Multi-Tag Case}
-	% 	In the $K$-tag scenario, the received signal at symbol block $n$ is
-	% 	\begin{equation}
-	% 		y[n] = \sqrt{P} h_{\mathrm{D}} s[n] + \sum_k \sqrt{\alpha_k} h_{\mathrm{C},k} c_k \sqrt{P} s[n] + w[n].
-	% 	\end{equation}
-
-	% 	On the one hand, we can compute the \emph{sum-rate} of the tags and characterize the (ergodic) primary-secondary capacity region by adjusting weight $\rho$.
-The weighted sum-rate can be expressed as
-	% 	\begin{align}
-	% 		J_1
-	% 		& = \rho \mathbb{E}_{\boldsymbol{c}} \left[ \log_2 \left( 1 + \gamma \lvert h_{\mathrm{D}} + \sum_k \sqrt{\alpha_k} h_{\mathrm{C},k} c_k \rvert \right) \right] + (1 - \rho) R_c\\
-	% 		& = \rho \sum_{i_1,\dots,i_K \in \mathcal{M}} \prod_{k \in \mathcal{K}} r_{k,i_k} \log_2 \left( 1 + \gamma \lvert h_{\mathrm{D}} + \sum_{k' \in \mathcal{K}} \sqrt{\alpha_{k'}} h_{\mathrm{C},k'} c_{k',i_{k'}} \rvert^2 \right)\\
-	% 		& \quad + (1 - \rho) \sum_{i \in \mathcal{M}} \sum_{j \in \mathcal{M}^K} \sum_{k \in \mathcal{K}} r_{k,i} p_{i,j} \log \frac{q_{j,i}}{r_{k,i}}.
-	% 	\end{align}
-	% 	In this case, although we can independently maximize the primary/secondary rate in closed form (resp.
-quantized \gls{irs} and multi-user Blahut-Arimoto), the joint form can be tricky due to the $K$-product term.
-We may consider a 2-loop iterative algorithm, where the inner loop optimizes input distribution over letters while the outer loop over users.
-I am still working on the convergence and optimality proofs and they are very deep into information theory.
-
-	% 	On the other hand, we can compute the rate region of the user and $K$ tags.
-However, the capacity region of discrete \gls{mac} remains unknown.
-We can obtain its outer bound by formulating a non-convex problem with a rank-1 constraint, then solve the relaxed problem.
-The difficulty is that the optimization is performed over $K$-dimensional array $\mathbb{R}^{\underbrace{M \times \ldots \times M}_{K}}$.
-	% \end{section}
-
-	% \begin{appendix}
-	% 	\begin{subsection}{Proof of Theorem~\ref{th:backward_transition}}
-	% 		Denote the objective function \eqref{ob:weighted_sum_rate_expanded} as $R(\boldsymbol{r}, \boldsymbol{Q})$.
-Let $w_j \triangleq \sum_{i'} r_{i'} p_{i', j}$ and rearrange \eqref{eq:backward_transition} as
-	% 		\begin{equation}
-	% 			w_j q_{j, i}^{\star} = r_i p_{i,j}.
-	% 		\end{equation}
-	% 		Therefore,
-	% 		\begin{align}
-	% 			R(\boldsymbol{r}, \boldsymbol{Q}^{\star}) - R(\boldsymbol{r}, \boldsymbol{Q})
-	% 			& = (1 - \rho) \sum_{i \in \mathcal{M}} \sum_{j \in \mathcal{M}} r_i p_{i,j} \log_2 \frac{q_{j, i}^{\star}}{q_{j, i}} \nonumber \\
-	% 			& = (1 - \rho) \sum_{i \in \mathcal{M}} \sum_{j \in \mathcal{M}} w_j q_{j, i}^{\star} \log_2 \frac{q_{j, i}^{\star}}{q_{j, i}} \nonumber \\
-	% 			& = (1 - \rho) \sum_{j \in \mathcal{M}} w_j \sum_{i \in \mathcal{M}} q_{j, i}^{\star} \log_2 \frac{q_{j, i}^{\star}}{q_{j, i}} \nonumber \\
-	% 			& = (1 - \rho) \sum_{j \in \mathcal{M}} w_j \infdiv{q_{j, i}^{\star}}{q_{j, i}} \nonumber \\
-	% 			& \ge 0,
-	% 		\end{align}
-	% 		with equality iff $\boldsymbol{Q} = \boldsymbol{Q}^{\star}$.
-	% 		\label{ap:backward_transition}
-	% 	\end{subsection}
-	% 	\begin{subsection}{Proof of Theorem~\ref{th:input_distribution}}
-	% 		We employ the method of Lagrange multipliers, temporally ignore the constraint $\boldsymbol{r} \ge 0$, and assume all logarithms are of base $e$. Define the Lagrangian function as
-	% 		\begin{align}
-	% 			J
-	% 			& = \rho \sum_{i \in \mathcal{M}} r_i \log \bigl( 1 + \gamma \lvert h_{\mathrm{D}} + \sqrt{\alpha} h_{\mathrm{C}} c_i \rvert^2 \bigr) \nonumber \\
-	% 			& \quad + (1 - \rho) \sum_{i \in \mathcal{M}} \sum_{j \in \mathcal{M}} r_i p_{i,j} \log \frac{q_{j, i}}{r_i} + \lambda \left( 1 - \sum_{i \in \mathcal{M}} r_i \right),
-	% 		\end{align}
-	% 		where $\lambda$ is the Lagrange multiplier associated with the sum-probability constraint. Differentiating $J$ with respect to $r_i$ gives
-	% 		\begin{align}
-	% 			\pdv{J}{r_i}
-	% 			& = \rho \log \bigl( 1 + \gamma \lvert h_{\mathrm{D}} + \sqrt{\alpha} h_{\mathrm{C}} c_i \rvert^2 \bigr) \\
-	% 			& \quad + (1 - \rho) \left( \sum_{j \in \mathcal{M}} p_{i,j} \log q_{j, i} - \log r_i - 1 \right),
-	% 		\end{align}
-	% 		and setting $\pdv*{J}{r_i} = 0$ suggests
-	% 		\begin{equation}
-	% 			r_i = e^{ -(\frac{\lambda}{1 - \rho} + 1)} \bigl( 1 + \gamma \lvert h_{\mathrm{D}} + \sqrt{\alpha} h_{\mathrm{C}} c_i \rvert^2 \bigr)^{\rho / (1 - \rho)} \prod_{j \in \mathcal{M}} q_{j, i}^{p_{i,j}}.
-	% 		\end{equation}
-	% 		By considering $\sum_{i \in \mathcal{M}} r_i = 1$, we can eliminate $\lambda$ and obtain the optimal tag input distribution as \eqref{eq:input_distribution}.
-	% 		\label{ap:input_distribution}
-	% 	\end{subsection}
-	% \end{appendix}
-
 	\bibliographystyle{IEEEtran}

### 2021-12-18 main.tex
:pencil: Add convergence proof (monotonic + bounded)

@@
 			\end{equation}
-			where $P_{\mathcal{K} \setminus \{k\}}(\bar{c}_{m_{\mathcal{K} \setminus \{k\}}}) = \prod_{k' \in \mathcal{K} \setminus \{k\}} P_{k'}(\bar{c}_{m_{k'}})$.
+			where $P_{\mathcal{K} \setminus \{k\}}(\bar{c}_{m_{\mathcal{K} \setminus \{k\}}}) = \prod_{q \in \mathcal{K} \setminus \{k\}} P_{q}(\bar{c}_{m_{q}})$.
 The backscatter mutual information can be expressed as\footnote{Please be aware that $c_{\mathcal{K}}$, $c_k$, $z$ are random variables, while $\bar{c}_{m_{\mathcal{K}}}$ and $\bar{c}_i$, $\bar{c}_{m_k}$, $\bar{z}_j$ represent the corresponding instances.}
@@
 			\begin{theorem}
-				The input probability distribution that achieves the weighted sum primary-backscatter capacity at state $i_k \in \mathcal{M}$ of tag $q \in \mathcal{K}$ is given by the limit of the following sequence\footnote{Note that the probability distribution of tag $q$ is based on the updated probability distribution of tags $1,\ldots,k-1$.}
+				The input probability distribution that achieves the weighted sum primary-backscatter capacity, at state $m_k \in \mathcal{M}$ of tag $k \in \mathcal{K}$, is given by the converging point of sequence\footnote{Note that the probability distribution of tag $k$ is based on the updated probability distribution of tags $1,\ldots,k-1$.}
 				\begin{equation}
-					P_q^{(r+1)}(\bar{c}_{i_q}) = \frac{P_q^{(r)}(\bar{c}_{i_q}) \exp \left( \frac{\rho}{1 - \rho} I_q(\bar{c}_{i_q};\boldsymbol{y},z) \right)}{\sum_{m_q} P_q^{(r)}(\bar{c}_{m_q}) \exp \left( \frac{\rho}{1 - \rho} I_q(\bar{c}_{m_q};\boldsymbol{y},z) \right)},
+					P_k^{(r+1)}(\bar{c}_{m_k}) = \frac{P_k^{(r)}(\bar{c}_{m_k}) \exp \left( \frac{\rho}{1 - \rho} I_k(\bar{c}_{m_k};\boldsymbol{y},z) \right)}{\sum_{m_k'} P_k^{(r)}(\bar{c}_{m_k'}) \exp \left( \frac{\rho}{1 - \rho} I_k(\bar{c}_{m_k'};\boldsymbol{y},z) \right)},
 					\label{eq:optimal_distribution}
 				\end{equation}
-				where $r \in \mathbb{Z}_+$ is the iteration index and $P_q^{(0)}(\bar{c}_{i_q}) > 0$, $\forall i_q \in \mathcal{M}$ and $\forall q \in \mathcal{K}$.
+				where $r \in \mathbb{Z}_+$ is the iteration index and $P_k^{(0)}(\bar{c}_{m_k}) > 0$, $\forall m_k \in \mathcal{M}$ and $\forall k \in \mathcal{K}$.
 				\label{th:optimal_distribution}
@@
 			\begin{proof}
-				We first prove that for tag $q \in \mathcal{K}$, updating the probability of state $i_q \in \mathcal{M}$ by sequence~\eqref{eq:optimal_distribution} does not decrease mutual information.
-For any input combination $\bar{c}_{m_{\mathcal{K}}}$, let $P_{\mathcal{K}}(\bar{c}_{m_{\mathcal{K}}}) = \prod_{k \in \mathcal{K}} P_k(\bar{c}_{m_k})$ and $P_{\mathcal{K}}'(\bar{c}_{m_{\mathcal{K}}}) = P_q'(\bar{c}_{m_q}) \prod_{k \in \mathcal{K} \setminus \{q\}} P_k(\bar{c}_{m_k})$ be two probability distributions with potentially different marginal for tag $q$, and denote the corresponding mutual information and received energy distribution as $I(\bar{c}_{\mathcal{K}};\boldsymbol{y},z)$, $I'(\bar{c}_{\mathcal{K}};\boldsymbol{y},z)$ and $P(\bar{z}_j)$, $P'(\bar{z}_j)$, respectively.
-Also, define an intermediate function $J \left( P_{\mathcal{K}}(\bar{c}_{m_{\mathcal{K}}}),P_{\mathcal{K}}'(\bar{c}_{m_{\mathcal{K}}}) \right)$ by \eqref{eq:intermediate_information_function}, and apparently $I(\bar{c}_{\mathcal{K}};\boldsymbol{y},z) = J \left( P_{\mathcal{K}}(\bar{c}_{m_{\mathcal{K}}}),P_{\mathcal{K}}(\bar{c}_{m_{\mathcal{K}}}) \right)$.
+				We first prove sequence~\eqref{eq:optimal_distribution} is non-decreasing in mutual information.
+For state $m_k \in \mathcal{M}$ of tag $k \in \mathcal{K}$, let $P_{\mathcal{K}}(\bar{c}_{m_{\mathcal{K}}}) = \prod_{q \in \mathcal{K}} P_q(\bar{c}_{m_q})$ and $P_{\mathcal{K}}'(\bar{c}_{m_{\mathcal{K}}}) = P_k'(\bar{c}_{m_k}) \prod_{q \in \mathcal{K} \setminus \{k\}} P_q(\bar{c}_{m_q})$ be two probability distributions with potentially different marginal for tag $k$, and denote the corresponding mutual information and received energy distribution as $I(\bar{c}_{\mathcal{K}};\boldsymbol{y},z)$, $I'(\bar{c}_{\mathcal{K}};\boldsymbol{y},z)$ and $P(\bar{z}_j)$, $P'(\bar{z}_j)$, respectively.
+Also, define an intermediate function $J \left( P_{\mathcal{K}}(\bar{c}_{m_{\mathcal{K}}}),P_{\mathcal{K}}'(\bar{c}_{m_{\mathcal{K}}}) \right)$ by \eqref{eq:intermediate_information_function}.
+Apparently, $I(\bar{c}_{\mathcal{K}};\boldsymbol{y},z) = J \left( P_{\mathcal{K}}(\bar{c}_{m_{\mathcal{K}}}),P_{\mathcal{K}}(\bar{c}_{m_{\mathcal{K}}}) \right)$.
 				\begin{figure*}[!b]
@@
 				\end{figure*}
-				For a fixed $P_{\mathcal{K}}'(\bar{c}_{m_{\mathcal{K}}})$, $J \left( P_{\mathcal{K}}(\bar{c}_{m_{\mathcal{K}}}),P_{\mathcal{K}}'(\bar{c}_{m_{\mathcal{K}}}) \right)$ is a concave function of $P_q(\bar{c}_{m_q})$ and can be maximized at $\nabla_{P_q^{\star}(\bar{c}_{m_q})} J \left( P_{\mathcal{K}}(\bar{c}_{m_{\mathcal{K}}}),P_{\mathcal{K}}'(\bar{c}_{m_{\mathcal{K}}}) \right) = 0$, which reduces to
+				For a fixed $P_{\mathcal{K}}'(\bar{c}_{m_{\mathcal{K}}})$, $J \left( P_{\mathcal{K}}(\bar{c}_{m_{\mathcal{K}}}),P_{\mathcal{K}}'(\bar{c}_{m_{\mathcal{K}}}) \right)$ is a concave function of $P_k(\bar{c}_{m_k})$ and is maximized at $\nabla_{P_k^{\star}(\bar{c}_{m_k})} J \left( P_{\mathcal{K}}(\bar{c}_{m_{\mathcal{K}}}),P_{\mathcal{K}}'(\bar{c}_{m_{\mathcal{K}}}) \right) = 0$, namely
 				\begin{equation}
-					S_q'(\bar{c}_{m_q}) - S_q'(\bar{c}_{i_q}) + (1 - \rho) \log \frac{P_q(\bar{c}_{i_q})}{P_q^{\star}(\bar{c}_{m_q})} = 0,
+					S_k'(\bar{c}_{m_k}) - S_k'(\bar{c}_{i_k}) + (1 - \rho) \log \frac{P_k(\bar{c}_{i_k})}{P_k^{\star}(\bar{c}_{m_k})} = 0,
 					\label{eq:optimal_intermediate_information_condition}
 				\end{equation}
-				where $i_q \ne m_q$ is the reference state and
+				where $i_k \ne m_k$ is the reference state and
 				\begin{align}
-					S_k'(\bar{c}_{m_q})
-					& \triangleq I_k(\bar{c}_{m_q};\boldsymbol{y},z) + (1 - \rho) \sum_{m_{\mathcal{K} \setminus \{q\}}} P_{\mathcal{K} \setminus \{q\}}(\bar{c}_{m_{\mathcal{K} \setminus \{q\}}})\nonumber\\
-					& \quad \times \sum_j P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K} \setminus \{q\}}},\bar{c}_{m_q}) \log P_{\mathcal{K}}'(\bar{c}_{m_{\mathcal{K}}}).
+					S_k'(\bar{c}_{m_k})
+					& \triangleq I_k(\bar{c}_{m_k};\boldsymbol{y},z) + (1 - \rho) \sum_{m_{\mathcal{K} \setminus \{k\}}} P_{\mathcal{K} \setminus \{k\}}(\bar{c}_{m_{\mathcal{K} \setminus \{k\}}})\nonumber\\
+					& \quad \times \sum_j P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K} \setminus \{k\}}},\bar{c}_{m_k}) \log P_{\mathcal{K}}'(\bar{c}_{m_{\mathcal{K} \setminus \{k\}}},\bar{c}_{m_k}).
 				\end{align}
 
-				Evidently, $\forall m_q \ne i_q$, \eqref{eq:optimal_intermediate_information_condition} can be recast as
+				Evidently, $\forall m_k \ne i_k$, \eqref{eq:optimal_intermediate_information_condition} boils down to
 				\begin{subequations}
 					\begin{align}
-						P_q^{\star}(\bar{c}_{m_q})
-						& = \frac{\exp \left( \frac{1}{1 - \rho} S_k'(\bar{c}_{m_q}) \right)}{\sum_{m_q} \exp \left( \frac{1}{1 - \rho} S_k'(\bar{c}_{m_q}) \right)}\\
-						& = \frac{P_q'(\bar{c}_{m_q}) \exp \left( \frac{\rho}{1 - \rho} I_q(\bar{c}_{m_q};\boldsymbol{y},z) \right)}{\sum_{m_q} P_q'(\bar{c}_{m_q}) \exp \left( \frac{\rho}{1 - \rho} I_q(\bar{c}_{m_q};\boldsymbol{y},z) \right)}.
+						P_k^{\star}(\bar{c}_{m_k})
+						& = \frac{\exp \left( \frac{1}{1 - \rho} S_k'(\bar{c}_{m_k}) \right)}{\sum_{m_k'} \exp \left( \frac{1}{1 - \rho} S_k'(\bar{c}_{m_k'}) \right)}\\
+						& = \frac{P_k'(\bar{c}_{m_k}) \exp \left( \frac{\rho}{1 - \rho} I_k(\bar{c}_{m_k};\boldsymbol{y},z) \right)}{\sum_{m_k'} P_k'(\bar{c}_{m_k'}) \exp \left( \frac{\rho}{1 - \rho} I_k(\bar{c}_{m_k'};\boldsymbol{y},z) \right)}.
 						\label{eq:optimal_relative_distribution}
@@
 
-				Although optimality is not guaranteed for state $i_q$, we notice that $P_q(\bar{c}_{i_q}) = 1 - \sum_{m_q \ne i_q} P_q^{\star}(\bar{c}_{m_q})$ has exactly the same form as \eqref{eq:optimal_relative_distribution}.
-It suggests that the solution of choosing $i_q$ as reference would coincide with that of choosing any $m_q \ne i_q$ as reference, while optimality is guaranteed for $i_q$ in the latter case.
-Therefore, for a fixed $P_{\mathcal{K}}'(\bar{c}_{m_{\mathcal{K}}})$, $\forall i_q \in \mathcal{M}$ and $\forall q \in \mathcal{K}$, \eqref{eq:optimal_relative_distribution} ensures
+				Although $P_k(\bar{c}_{i_k}) = 1 - \sum_{m_k \ne i_k} P_k^{\star}(\bar{c}_{m_k})$ is not guaranteed to be optimal, it has exactly the same form as \eqref{eq:optimal_relative_distribution}.
+In such case, the solution of choosing $i_k$ as reference would coincide with that of choosing any $m_k \ne i_k$ as reference, while optimality for $i_k$ is guaranteed in the latter case.
+Therefore, for a fixed $P_{\mathcal{K}}'(\bar{c}_{m_{\mathcal{K}}})$, $\forall i_k \in \mathcal{M}$ and $\forall k \in \mathcal{K}$, \eqref{eq:optimal_relative_distribution} ensures
 				\begin{equation}
@@
 
-				On the other hand, choosing $P_q(\bar{c}_{m_q})$ by \eqref{eq:optimal_relative_distribution} also satisfies
+				On the other hand, choosing $P_k(\bar{c}_{m_k})$ by \eqref{eq:optimal_relative_distribution} also satisfies
 				\begin{subequations}
@@
 						& \triangleq I(\bar{c}_{\mathcal{K}};\boldsymbol{y},z) - J \left( P_{\mathcal{K}}(\bar{c}_{m_{\mathcal{K}}}),P_{\mathcal{K}}'(\bar{c}_{m_{\mathcal{K}}}) \right)\\
-						& = (1 - \rho)
-						\sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(\bar{c}_{m_{\mathcal{K}}}) \sum_j P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K}}}) \log \frac{P'(\bar{z}_j) P_q(\bar{c}_{m_q})}{P(\bar{z}_j) P_q'(\bar{c}_{m_q})}\\
-						& = (1 - \rho) \sum_{m_q} \frac{P_q'(\bar{c}_{m_q}) u_q(\bar{c}_{m_q})}{\sum_{i_q} P_q'(\bar{c}_{i_q}) u_q(\bar{c}_{i_q})} \sum_j P(\bar{z}_j \mid \bar{c}_{m_q})\nonumber\\
-						& \quad \times \log \frac{\sum_{m_q'} P_q'(\bar{c}_{m_q'}) P(\bar{z}_j \mid \bar{c}_{m_q'}) u_q(\bar{c}_{m_q})}{\sum_{i_q'} P_q'(\bar{c}_{i_q'}) P(\bar{z}_j \mid \bar{c}_{i_q'}) u_q(\bar{c}_{i_q'})}\\
-						& \ge (1 - \rho) \sum_{m_q} \frac{P_q'(\bar{c}_{m_q}) u_q(\bar{c}_{m_q})}{\sum_{i_q} P_q'(\bar{c}_{i_q}) u_q(\bar{c}_{i_q})} \sum_j P(\bar{z}_j \mid \bar{c}_{m_q})\nonumber\\
-						& \quad \times \left( 1 - \frac{\sum_{i_q'} P_q'(\bar{c}_{i_q'}) P(\bar{z}_j \mid \bar{c}_{i_q'}) u_q(\bar{c}_{i_q'})}{\sum_{m_q'} P_q'(\bar{c}_{m_q'}) P(\bar{z}_j \mid \bar{c}_{m_q'}) u_q(\bar{c}_{m_q})} \right)\\
+						& = (1 - \rho) \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(\bar{c}_{m_{\mathcal{K}}}) \sum_j P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K}}}) \log \frac{P'(\bar{z}_j) P_k(\bar{c}_{m_k})}{P(\bar{z}_j) P_k'(\bar{c}_{m_k})}\\
+						& = (1 - \rho) \sum_{m_k} \frac{P_k'(\bar{c}_{m_k}) u_k(\bar{c}_{m_k})}{\sum_{m_k'} P_k'(\bar{c}_{m_k'}) u_k(\bar{c}_{m_k'})} \sum_j P(\bar{z}_j \mid \bar{c}_{m_k})\nonumber\\
+						& \quad \times \log \frac{\sum_{m_k'} P_k'(\bar{c}_{m_k'}) P(\bar{z}_j \mid \bar{c}_{m_k'}) u_k(\bar{c}_{m_k})}{\sum_{m_k'} P_k'(\bar{c}_{m_k'}) P(\bar{z}_j \mid \bar{c}_{m_k'}) u_k(\bar{c}_{m_k'})}\\
+						& \ge (1 - \rho) \sum_{m_k} \frac{P_k'(\bar{c}_{m_k}) u_k(\bar{c}_{m_k})}{\sum_{m_k'} P_k'(\bar{c}_{m_k'}) u_k(\bar{c}_{m_k'})} \sum_j P(\bar{z}_j \mid \bar{c}_{m_k})\nonumber\\
+						& \quad \times \left( 1 - \frac{\sum_{m_k'} P_k'(\bar{c}_{m_k'}) P(\bar{z}_j \mid \bar{c}_{m_k'}) u_k(\bar{c}_{m_k'})}{\sum_{m_k'} P_k'(\bar{c}_{m_k'}) P(\bar{z}_j \mid \bar{c}_{m_k'}) u_k(\bar{c}_{m_k})} \right)\\
 						& = 0,
@@
 				\end{subequations}
-				where $u_q(\bar{c}_{m_q}) \triangleq \exp \left( \frac{\rho}{1 - \rho} I_q(\bar{c}_{m_q};\boldsymbol{y},z) \right)$ and the equality holds if and only if \eqref{eq:optimal_relative_distribution} converges.
-Combining \eqref{eq:information_difference_lower} and \eqref{eq:information_difference_upper}, we conclude that update the input probability distribution of tag $q \in \mathcal{K}$ by \eqref{eq:optimal_distribution} does not decrease mutual information.
-
-				TODO
+				where $u_k(\bar{c}_{m_k}) \triangleq \exp \left( \frac{\rho}{1 - \rho} I_k(\bar{c}_{m_k};\boldsymbol{y},z) \right)$ and the equality holds if and only if \eqref{eq:optimal_relative_distribution} converges.
+Combining \eqref{eq:information_difference_lower} and \eqref{eq:information_difference_upper} suggests $I(\bar{c}_{\mathcal{K}};\boldsymbol{y},z) \ge I'(\bar{c}_{\mathcal{K}};\boldsymbol{y},z)$.
+Since mutual information is bounded above, we conclude sequence \eqref{eq:optimal_distribution} is convergent and non-decreasing in mutual information.
 			\end{proof}

### 2021-12-18 main.tex
:pencil: Add optimality proof

@@
 				\begin{subequations}
+					\label{eq:optimal_conditions}
 					\begin{alignat}{2}
-						I_k(\bar{c}_{m_k};\boldsymbol{y},z) & = I(c_{\mathcal{K}};\boldsymbol{y},z), \quad && P_k^{\star}(\bar{c}_{m_k}) > 0,\label{co:probable_states}\\
-						I_k(\bar{c}_{m_k};\boldsymbol{y},z) & \le I(c_{\mathcal{K}};\boldsymbol{y},z), \quad && P_k^{\star}(\bar{c}_{m_k}) = 0.\label{co:dropped_states}
+						I_k(\bar{c}_{m_k};\boldsymbol{y},z) & = I(c_{\mathcal{K}};\boldsymbol{y},z), \quad && P_k^{\star}(\bar{c}_{m_k}) > 0,\label{eq:probable_states}\\
+						I_k(\bar{c}_{m_k};\boldsymbol{y},z) & \le I(c_{\mathcal{K}};\boldsymbol{y},z), \quad && P_k^{\star}(\bar{c}_{m_k}) = 0.\label{eq:dropped_states}
 					\end{alignat}
 				\end{subequations}
-
-				\eqref{co:probable_states} means each probable state of each tag should produce the same marginal information (averaged over all states of other tags), while \eqref{co:dropped_states} implies any state of any tag with potentially less marginal information than above should not be used.
+				\eqref{eq:probable_states} means each probable state of each tag should produce the same marginal information (averaged over all states of other tags), while \eqref{eq:dropped_states} implies any state of any tag with potentially less marginal information than above should not be used.
 				\label{pr:optimal_conditions}
@@
 					\begin{alignat}{2}
-						I_k(\bar{c}_{m_k};\boldsymbol{y},z) & = \mu_k^{\star} + (1 - \rho), \quad && P_k^{\star}(\bar{c}_{m_k}) > 0,\\
-						I_k(\bar{c}_{m_k};\boldsymbol{y},z) & \le \mu_k^{\star} + (1 - \rho), \quad && P_k^{\star}(\bar{c}_{m_k}) = 0,
+						I_k(\bar{c}_{m_k};\boldsymbol{y},z) & = \mu_k^{\star} + (1 - \rho), \quad && P_k^{\star}(\bar{c}_{m_k}) > 0,\label{eq:probable_states_marginal}\\
+						I_k(\bar{c}_{m_k};\boldsymbol{y},z) & \le \mu_k^{\star} + (1 - \rho), \quad && P_k^{\star}(\bar{c}_{m_k}) = 0,\label{eq:dropped_states_marginal}
 					\end{alignat}
@@
 				\end{equation}
-				where $r \in \mathbb{Z}_+$ is the iteration index and $P_k^{(0)}(\bar{c}_{m_k}) > 0$, $\forall m_k \in \mathcal{M}$ and $\forall k \in \mathcal{K}$.
+				where $r \in \mathbb{Z}_+$ is the iteration index and $P_k^{(0)}(\bar{c}_{m_k}) > 0$.
+				% , $\forall m_k \in \mathcal{M}$ and $\forall k \in \mathcal{K}$.
 				\label{th:optimal_distribution}
@@
 Combining \eqref{eq:information_difference_lower} and \eqref{eq:information_difference_upper} suggests $I(\bar{c}_{\mathcal{K}};\boldsymbol{y},z) \ge I'(\bar{c}_{\mathcal{K}};\boldsymbol{y},z)$.
-Since mutual information is bounded above, we conclude sequence \eqref{eq:optimal_distribution} is convergent and non-decreasing in mutual information.
+Since mutual information is bounded above, we conclude sequence \eqref{eq:optimal_distribution} is non-decreasing and convergent in mutual information.
+
+				We then prove any converging point of sequence \eqref{eq:optimal_distribution}, denoted as $P_k^{\star}(\bar{c}_{m_k})$, fulfills the optimal conditions \eqref{eq:optimal_conditions} and achieves the weighted primary-backscatter sum capacity.
+To see this, define
+				\begin{equation}
+					D_k^{(r)}(\bar{c}_{m_k}) \triangleq \frac{P_k^{(r+1)}(\bar{c}_{m_k})}{P_k^{(r)}(\bar{c}_{m_k})} = \frac{u_k(\bar{c}_{m_k})}{\sum_{m_k'} P_k^{(r)}(\bar{c}_{m_k'}) u_k(\bar{c}_{m_k'})},
+				\end{equation}
+				where $P_k^{(0)}(\bar{c}_{m_k}) > 0$.
+As sequence \eqref{eq:optimal_distribution} is convergent, any state with $P_k^{\star}(\bar{c}_{m_k}) > 0$ need to satisfy $D_k^{\star}(\bar{c}_{m_k}) \triangleq \lim_{r \to \infty} D_k^{(r)}(\bar{c}_{m_k}) = 1$, namely
+				\begin{equation}
+					I_k(\bar{c}_{m_k};\boldsymbol{y},z) = \frac{1 - \rho}{\rho} \log \sum_{m_k'} P_k^{(r)}(\bar{c}_{m_k'}) u_k(\bar{c}_{m_k'}),
+				\end{equation}
+				which coincides with \eqref{eq:probable_states_marginal} and implies \eqref{eq:probable_states}.
+That is, given $P_k^{(0)}(\bar{c}_{m_k}) > 0$, any converging point with $P_k^{\star}(\bar{c}_{m_k}) > 0$ must satisfy \eqref{eq:probable_states}.
+				On the other hand, we assume $P_k^{\star}(\bar{c}_{m_k})$ does not satisfy \eqref{eq:dropped_states}, such that for any state with $P_k^{\star}(\bar{c}_{m_k}) = 0$,
+				% On the other hand, we show if $P_k^{\star}(\bar{c}_{m_k})$ does not satisfy \eqref{eq:dropped_states}, then it is not a converging point of sequence \eqref{eq:optimal_distribution}.
+By this assumption, for any state with $P_k^{\star}(\bar{c}_{m_k}) = 0$,
+				\begin{equation}
+					I_k(\bar{c}_{m_k};\boldsymbol{y},z) > I(c_{\mathcal{K}};\boldsymbol{y},z) = \sum_{m_k'} P_k^{\star}(\bar{c}_{m_k'}) I_k(\bar{c}_{m_k'};\boldsymbol{y},z),
+				\end{equation}
+				where the equality origins from \eqref{eq:backscatter_sum_rate_expectation} and \eqref{eq:primary_ergodic_rate_expectation}.
+Since the exponential function is monotonically increasing, we have $u_k(\bar{c}_{m_k}) > \sum_{m_k'} P_k^{\star}(\bar{c}_{m_k'}) u_k(\bar{c}_{m_k'})$ and $D_k^{\star}(\bar{c}_{m_k}) > 1$.
+Considering $P_k^{(0)}(\bar{c}_{m_k}) > 0$ and $P_k^{\star}(\bar{c}_{m_k}) = 0$, it contradicts with
+				\begin{equation}
+					P_k^{(r)}(\bar{c}_{m_k}) = P_k^{(0)}(\bar{c}_{m_k}) \prod_{n=1}^r D_k^{(n)}(\bar{c}_{m_k}).
+				\end{equation}
+				Therefore, given $P_k^{(0)}(\bar{c}_{m_k}) > 0$, any converging point with $P_k^{\star}(\bar{c}_{m_k}) = 0$ must satisfy \eqref{eq:dropped_states}.
+
+				In conclusion, sequence \eqref{eq:optimal_distribution} always converges to a weighted sum capacity-achieving distribution for state $m_k$ of tag $k$.
 			\end{proof}

### 2021-12-18 main.tex
:pencil: Update notation and index

@@
 			\end{subequations}
-
 			Evidently, \eqref{eq:backscatter_information_function}--\eqref{eq:backscatter_sum_rate} are functions of the tag input distribution $\boldsymbol{P}$ as well as the discrete memoryless \gls{mac} $P(z \mid c_{\mathcal{K}})$, and thus depend on the transmit precoder $\boldsymbol{w}$ and the detection threshold $\boldsymbol{t}$.
@@
 					\begin{alignat}{2}
-						I_k(\bar{c}_{m_k};\boldsymbol{y},z) & = I(c_{\mathcal{K}};\boldsymbol{y},z), \quad && P_k^{\star}(\bar{c}_{m_k}) > 0,\label{eq:probable_states}\\
-						I_k(\bar{c}_{m_k};\boldsymbol{y},z) & \le I(c_{\mathcal{K}};\boldsymbol{y},z), \quad && P_k^{\star}(\bar{c}_{m_k}) = 0.\label{eq:dropped_states}
+						I_k^{\star}(\bar{c}_{m_k};\boldsymbol{y},z) & = I^{\star}(c_{\mathcal{K}};\boldsymbol{y},z), \quad && P_k^{\star}(\bar{c}_{m_k}) > 0,\label{eq:probable_states}\\
+						I_k^{\star}(\bar{c}_{m_k};\boldsymbol{y},z) & \le I^{\star}(c_{\mathcal{K}};\boldsymbol{y},z), \quad && P_k^{\star}(\bar{c}_{m_k}) = 0.\label{eq:dropped_states}
 					\end{alignat}
@@
 					\begin{equation}
-						- \nabla_{P_k^{\star}(\bar{c}_{m_k})} I(c_{\mathcal{K}};\boldsymbol{y},z) + \mu_k^{\star} - \lambda_{k,m_k}^{\star} = 0,
+						- \nabla_{P_k^{\star}(\bar{c}_{m_k})} I^{\star}(c_{\mathcal{K}};\boldsymbol{y},z) + \mu_k^{\star} - \lambda_{k,m_k}^{\star} = 0,
 					\end{equation}
@@
 				\begin{equation}
-					\nabla_{P_k^{\star}(\bar{c}_{m_k})} I(c_{\mathcal{K}};\boldsymbol{y},z) = I_k(\bar{c}_{m_k};\boldsymbol{y},z) - (1 - \rho).
+					\nabla_{P_k^{\star}(\bar{c}_{m_k})} I^{\star}(c_{\mathcal{K}};\boldsymbol{y},z) = I_k^{\star}(\bar{c}_{m_k};\boldsymbol{y},z) - (1 - \rho).
 				\end{equation}
@@
 					\begin{alignat}{2}
-						I_k(\bar{c}_{m_k};\boldsymbol{y},z) & = \mu_k^{\star} + (1 - \rho), \quad && P_k^{\star}(\bar{c}_{m_k}) > 0,\label{eq:probable_states_marginal}\\
-						I_k(\bar{c}_{m_k};\boldsymbol{y},z) & \le \mu_k^{\star} + (1 - \rho), \quad && P_k^{\star}(\bar{c}_{m_k}) = 0,\label{eq:dropped_states_marginal}
+						I_k^{\star}(\bar{c}_{m_k};\boldsymbol{y},z) & = \mu_k^{\star} + (1 - \rho), \quad && P_k^{\star}(\bar{c}_{m_k}) > 0,\label{eq:probable_states_marginal}\\
+						I_k^{\star}(\bar{c}_{m_k};\boldsymbol{y},z) & \le \mu_k^{\star} + (1 - \rho), \quad && P_k^{\star}(\bar{c}_{m_k}) = 0,\label{eq:dropped_states_marginal}
 					\end{alignat}
@@
 				\begin{equation}
-					\sum_{m_k} P_k^{\star}(\bar{c}_{m_k}) I_k(\bar{c}_{m_k};\boldsymbol{y},z) = \mu_k^{\star} + (1 - \rho).
+					\sum_{m_k} P_k^{\star}(\bar{c}_{m_k}) I_k^{\star}(\bar{c}_{m_k};\boldsymbol{y},z) = \mu_k^{\star} + (1 - \rho).
 				\end{equation}
@@
 				\begin{equation}
-					\sum_{m_k} P_k^{\star}(\bar{c}_{m_k}) I_k(\bar{c}_{m_k};\boldsymbol{y},z) = I(c_{\mathcal{K}};\boldsymbol{y},z),
+					\sum_{m_k} P_k^{\star}(\bar{c}_{m_k}) I_k^{\star}(\bar{c}_{m_k};\boldsymbol{y},z) = I^{\star}(c_{\mathcal{K}};\boldsymbol{y},z),
 				\end{equation}
-				which is irrelevant to $k$. It suggests $I(c_{\mathcal{K}};\boldsymbol{y},z) = \mu_k^{\star} + (1 - \rho)$, $\forall k \in \mathcal{K}$, and completes the proof.
+				which is irrelevant to $k$. It suggests $I^{\star}(c_{\mathcal{K}};\boldsymbol{y},z) = \mu_k^{\star} + (1 - \rho)$, $\forall k \in \mathcal{K}$, and completes the proof.
 			\end{proof}
@@
 				\begin{equation}
-					P_k^{(r+1)}(\bar{c}_{m_k}) = \frac{P_k^{(r)}(\bar{c}_{m_k}) \exp \left( \frac{\rho}{1 - \rho} I_k(\bar{c}_{m_k};\boldsymbol{y},z) \right)}{\sum_{m_k'} P_k^{(r)}(\bar{c}_{m_k'}) \exp \left( \frac{\rho}{1 - \rho} I_k(\bar{c}_{m_k'};\boldsymbol{y},z) \right)},
+					P_k^{(r+1)}(\bar{c}_{m_k}) = \frac{P_k^{(r)}(\bar{c}_{m_k}) \exp \left( \frac{\rho}{1 - \rho} I_k^{(r)}(\bar{c}_{m_k};\boldsymbol{y},z) \right)}{\sum_{m_k'} P_k^{(r)}(\bar{c}_{m_k'}) \exp \left( \frac{\rho}{1 - \rho} I_k^{(r)}(\bar{c}_{m_k'};\boldsymbol{y},z) \right)},
 					\label{eq:optimal_distribution}
@@
 				We first prove sequence~\eqref{eq:optimal_distribution} is non-decreasing in mutual information.
-For state $m_k \in \mathcal{M}$ of tag $k \in \mathcal{K}$, let $P_{\mathcal{K}}(\bar{c}_{m_{\mathcal{K}}}) = \prod_{q \in \mathcal{K}} P_q(\bar{c}_{m_q})$ and $P_{\mathcal{K}}'(\bar{c}_{m_{\mathcal{K}}}) = P_k'(\bar{c}_{m_k}) \prod_{q \in \mathcal{K} \setminus \{k\}} P_q(\bar{c}_{m_q})$ be two probability distributions with potentially different marginal for tag $k$, and denote the corresponding mutual information and received energy distribution as $I(\bar{c}_{\mathcal{K}};\boldsymbol{y},z)$, $I'(\bar{c}_{\mathcal{K}};\boldsymbol{y},z)$ and $P(\bar{z}_j)$, $P'(\bar{z}_j)$, respectively.
-Also, define an intermediate function $J \left( P_{\mathcal{K}}(\bar{c}_{m_{\mathcal{K}}}),P_{\mathcal{K}}'(\bar{c}_{m_{\mathcal{K}}}) \right)$ by \eqref{eq:intermediate_information_function}.
+For state $m_k \in \mathcal{M}$ of tag $k \in \mathcal{K}$, let $P_{\mathcal{K}}(\bar{c}_{m_{\mathcal{K}}}) = \prod_{q \in \mathcal{K}} P_q(\bar{c}_{m_q})$ and $P_{\mathcal{K}}'(\bar{c}_{m_{\mathcal{K}}}) = P_k'(\bar{c}_{m_k}) \prod_{q \in \mathcal{K} \setminus \{k\}} P_q(\bar{c}_{m_q})$ be two probability distributions with potentially different marginal for tag $k$, and define an intermediate function $J \left( P_{\mathcal{K}}(\bar{c}_{m_{\mathcal{K}}}),P_{\mathcal{K}}'(\bar{c}_{m_{\mathcal{K}}}) \right)$ by \eqref{eq:intermediate_information_function}.
 Apparently, $I(\bar{c}_{\mathcal{K}};\boldsymbol{y},z) = J \left( P_{\mathcal{K}}(\bar{c}_{m_{\mathcal{K}}}),P_{\mathcal{K}}(\bar{c}_{m_{\mathcal{K}}}) \right)$.
@@
 					S_k'(\bar{c}_{m_k})
-					& \triangleq I_k(\bar{c}_{m_k};\boldsymbol{y},z) + (1 - \rho) \sum_{m_{\mathcal{K} \setminus \{k\}}} P_{\mathcal{K} \setminus \{k\}}(\bar{c}_{m_{\mathcal{K} \setminus \{k\}}})\nonumber\\
+					& \triangleq I_k'(\bar{c}_{m_k};\boldsymbol{y},z) + (1 - \rho) \sum_{m_{\mathcal{K} \setminus \{k\}}} P_{\mathcal{K} \setminus \{k\}}(\bar{c}_{m_{\mathcal{K} \setminus \{k\}}})\nonumber\\
 					& \quad \times \sum_j P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K} \setminus \{k\}}},\bar{c}_{m_k}) \log P_{\mathcal{K}}'(\bar{c}_{m_{\mathcal{K} \setminus \{k\}}},\bar{c}_{m_k}).
 				\end{align}
-
 				Evidently, $\forall m_k \ne i_k$, \eqref{eq:optimal_intermediate_information_condition} boils down to
+				% \begin{subequations}
+				% 	\begin{align}
+				% 		P_k^{\star}(\bar{c}_{m_k})
+				% 		& = \frac{\exp \left( \frac{1}{1 - \rho} S_k'(\bar{c}_{m_k}) \right)}{\sum_{m_k'} \exp \left( \frac{1}{1 - \rho} S_k'(\bar{c}_{m_k'}) \right)}\\
+				% 		& = \frac{P_k'(\bar{c}_{m_k}) \exp \left( \frac{\rho}{1 - \rho} I_k'(\bar{c}_{m_k};\boldsymbol{y},z) \right)}{\sum_{m_k'} P_k'(\bar{c}_{m_k'}) \exp \left( \frac{\rho}{1 - \rho} I_k'(\bar{c}_{m_k'};\boldsymbol{y},z) \right)}.
+				% 		\label{eq:optimal_relative_distribution}
+				% 	\end{align}
+				% \end{subequations}
 				\begin{subequations}
@@
 						& = \frac{\exp \left( \frac{1}{1 - \rho} S_k'(\bar{c}_{m_k}) \right)}{\sum_{m_k'} \exp \left( \frac{1}{1 - \rho} S_k'(\bar{c}_{m_k'}) \right)}\\
-						& = \frac{P_k'(\bar{c}_{m_k}) \exp \left( \frac{\rho}{1 - \rho} I_k(\bar{c}_{m_k};\boldsymbol{y},z) \right)}{\sum_{m_k'} P_k'(\bar{c}_{m_k'}) \exp \left( \frac{\rho}{1 - \rho} I_k(\bar{c}_{m_k'};\boldsymbol{y},z) \right)}.
+						& = \frac{P_k'(\bar{c}_{m_k}) u_k'(\bar{c}_{m_k})}{\sum_{m_k'} P_k'(\bar{c}_{m_k'}) u_k'(\bar{c}_{m_k'})},
 						\label{eq:optimal_relative_distribution}
@@
 				\end{subequations}
-
+				where we define $u_k'(\bar{c}_{m_k}) \triangleq \exp \left( \frac{\rho}{1 - \rho} I_k'(\bar{c}_{m_k};\boldsymbol{y},z) \right)$.
 Although $P_k(\bar{c}_{i_k}) = 1 - \sum_{m_k \ne i_k} P_k^{\star}(\bar{c}_{m_k})$ is not guaranteed to be optimal, it has exactly the same form as \eqref{eq:optimal_relative_distribution}.
@@
 						& = (1 - \rho) \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(\bar{c}_{m_{\mathcal{K}}}) \sum_j P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K}}}) \log \frac{P'(\bar{z}_j) P_k(\bar{c}_{m_k})}{P(\bar{z}_j) P_k'(\bar{c}_{m_k})}\\
-						& = (1 - \rho) \sum_{m_k} \frac{P_k'(\bar{c}_{m_k}) u_k(\bar{c}_{m_k})}{\sum_{m_k'} P_k'(\bar{c}_{m_k'}) u_k(\bar{c}_{m_k'})} \sum_j P(\bar{z}_j \mid \bar{c}_{m_k})\nonumber\\
-						& \quad \times \log \frac{\sum_{m_k'} P_k'(\bar{c}_{m_k'}) P(\bar{z}_j \mid \bar{c}_{m_k'}) u_k(\bar{c}_{m_k})}{\sum_{m_k'} P_k'(\bar{c}_{m_k'}) P(\bar{z}_j \mid \bar{c}_{m_k'}) u_k(\bar{c}_{m_k'})}\\
-						& \ge (1 - \rho) \sum_{m_k} \frac{P_k'(\bar{c}_{m_k}) u_k(\bar{c}_{m_k})}{\sum_{m_k'} P_k'(\bar{c}_{m_k'}) u_k(\bar{c}_{m_k'})} \sum_j P(\bar{z}_j \mid \bar{c}_{m_k})\nonumber\\
-						& \quad \times \left( 1 - \frac{\sum_{m_k'} P_k'(\bar{c}_{m_k'}) P(\bar{z}_j \mid \bar{c}_{m_k'}) u_k(\bar{c}_{m_k'})}{\sum_{m_k'} P_k'(\bar{c}_{m_k'}) P(\bar{z}_j \mid \bar{c}_{m_k'}) u_k(\bar{c}_{m_k})} \right)\\
+						& = (1 - \rho) \sum_{m_k} \frac{P_k'(\bar{c}_{m_k}) u_k'(\bar{c}_{m_k})}{\sum_{m_k'} P_k'(\bar{c}_{m_k'}) u_k'(\bar{c}_{m_k'})} \sum_j P(\bar{z}_j \mid \bar{c}_{m_k})\nonumber\\
+						& \quad \times \log \frac{\sum_{m_k'} P_k'(\bar{c}_{m_k'}) P(\bar{z}_j \mid \bar{c}_{m_k'}) u_k'(\bar{c}_{m_k})}{\sum_{m_k'} P_k'(\bar{c}_{m_k'}) P(\bar{z}_j \mid \bar{c}_{m_k'}) u_k'(\bar{c}_{m_k'})}\\
+						& \ge (1 - \rho) \sum_{m_k} \frac{P_k'(\bar{c}_{m_k}) u_k'(\bar{c}_{m_k})}{\sum_{m_k'} P_k'(\bar{c}_{m_k'}) u_k'(\bar{c}_{m_k'})} \sum_j P(\bar{z}_j \mid \bar{c}_{m_k})\nonumber\\
+						& \quad \times \left( 1 - \frac{\sum_{m_k'} P_k'(\bar{c}_{m_k'}) P(\bar{z}_j \mid \bar{c}_{m_k'}) u_k'(\bar{c}_{m_k'})}{\sum_{m_k'} P_k'(\bar{c}_{m_k'}) P(\bar{z}_j \mid \bar{c}_{m_k'}) u_k'(\bar{c}_{m_k})} \right)\\
 						& = 0,
@@
 				\end{subequations}
-				where $u_k(\bar{c}_{m_k}) \triangleq \exp \left( \frac{\rho}{1 - \rho} I_k(\bar{c}_{m_k};\boldsymbol{y},z) \right)$ and the equality holds if and only if \eqref{eq:optimal_relative_distribution} converges.
+				where the equality holds if and only if \eqref{eq:optimal_relative_distribution} converges.
 Combining \eqref{eq:information_difference_lower} and \eqref{eq:information_difference_upper} suggests $I(\bar{c}_{\mathcal{K}};\boldsymbol{y},z) \ge I'(\bar{c}_{\mathcal{K}};\boldsymbol{y},z)$.
@@
 				\begin{equation}
-					D_k^{(r)}(\bar{c}_{m_k}) \triangleq \frac{P_k^{(r+1)}(\bar{c}_{m_k})}{P_k^{(r)}(\bar{c}_{m_k})} = \frac{u_k(\bar{c}_{m_k})}{\sum_{m_k'} P_k^{(r)}(\bar{c}_{m_k'}) u_k(\bar{c}_{m_k'})},
+					D_k^{(r)}(\bar{c}_{m_k}) \triangleq \frac{P_k^{(r+1)}(\bar{c}_{m_k})}{P_k^{(r)}(\bar{c}_{m_k})} = \frac{u_k^{(r)}(\bar{c}_{m_k})}{\sum_{m_k'} P_k^{(r)}(\bar{c}_{m_k'}) u_k^{(r)}(\bar{c}_{m_k'})},
 				\end{equation}
@@
 				\begin{equation}
-					I_k(\bar{c}_{m_k};\boldsymbol{y},z) = \frac{1 - \rho}{\rho} \log \sum_{m_k'} P_k^{(r)}(\bar{c}_{m_k'}) u_k(\bar{c}_{m_k'}),
+					I_k^{\star}(\bar{c}_{m_k};\boldsymbol{y},z) = \frac{1 - \rho}{\rho} \log \sum_{m_k'} P_k^{\star}(\bar{c}_{m_k'}) u_k^{\star}(\bar{c}_{m_k'}),
 				\end{equation}
@@
 				\begin{equation}
-					I_k(\bar{c}_{m_k};\boldsymbol{y},z) > I(c_{\mathcal{K}};\boldsymbol{y},z) = \sum_{m_k'} P_k^{\star}(\bar{c}_{m_k'}) I_k(\bar{c}_{m_k'};\boldsymbol{y},z),
+					I_k^{\star}(\bar{c}_{m_k};\boldsymbol{y},z) > I^{\star}(c_{\mathcal{K}};\boldsymbol{y},z) = \sum_{m_k'} P_k^{\star}(\bar{c}_{m_k'}) I_k^{\star}(\bar{c}_{m_k'};\boldsymbol{y},z),
 				\end{equation}
 				where the equality origins from \eqref{eq:backscatter_sum_rate_expectation} and \eqref{eq:primary_ergodic_rate_expectation}.
-Since the exponential function is monotonically increasing, we have $u_k(\bar{c}_{m_k}) > \sum_{m_k'} P_k^{\star}(\bar{c}_{m_k'}) u_k(\bar{c}_{m_k'})$ and $D_k^{\star}(\bar{c}_{m_k}) > 1$.
+Since the exponential function is monotonically increasing, we have $u_k^{\star}(\bar{c}_{m_k}) > \sum_{m_k'} P_k^{\star}(\bar{c}_{m_k'}) u_k^{\star}(\bar{c}_{m_k'})$ and $D_k^{\star}(\bar{c}_{m_k}) > 1$.
 Considering $P_k^{(0)}(\bar{c}_{m_k}) > 0$ and $P_k^{\star}(\bar{c}_{m_k}) = 0$, it contradicts with

### 2021-12-22 main.tex
:pencil: Remove marginal MAC

@@
 % \usepackage[subtle]{savetrees}
+\usepackage{stmaryrd}
 
@@
 
-			Once the decision region is determined, we can formulate an equivalent point-to-point \gls{dmc} from tag input combination alphabet $\mathcal{M^K}$ to output energy level alphabet $\mathcal{M^K}$.
-The probability of receiving energy level $j$ under tag input combination $i$ is\footnote{For simplicity, we assume there exists at least one feasible precoder that produces distinct received energy levels for all tag input combinations.
+			Once the decision region is determined, the discrete memoryless \gls{mac} can be recast as an equivalent point-to-point \gls{dmc} from tag input combination alphabet $\mathcal{M^K}$ to output energy level alphabet $\mathcal{M^K}$.
+The the probability of receiving energy level $j$ under tag input combination $i$ is\footnote{For simplicity, we assume there exists at least one feasible precoder that produces distinct received energy levels for all tag input combinations.
 [TODO] Merge with precoder design.}
 			\begin{equation}
-				P(\bar{z}_j \mid \bar{c}_i) = P(z \in \mathcal{R}_j \mid \mathcal{H}_i) = \int_{\mathcal{R}_j} f(z \mid \mathcal{H}_i) \dd z.
+				P(\bar{z}_j \mid \bar{c}_i) = P(z \in \mathcal{R}_j \mid \mathcal{H}_i) = \int_{\mathcal{R}_j} f(z \mid \mathcal{H}_i) \dd z,
 				\label{eq:point_to_point_channel}
 			\end{equation}
-
-			On top of this, we can compute the marginal probability of each tag and obtain $K$ transition matrices from $\mathcal{M}$ to $\mathcal{M^K}$ that compose a discrete memoryless \gls{mac}.
-The probability of observing energy level $j$ when tag $k$ at state $m_k$ is
-			\begin{equation}
-				P(\bar{z}_j \mid \bar{c}_{m_k}) = \frac{\sum_{m_{\mathcal{K} \setminus \{k\}}} P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K}}})}{\sum_{m_{\mathcal{K}}} P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K}}})}.
-				\label{eq:mac}
-			\end{equation}
-
-			In summary, with the \gls{csi} knowledge and for any given precoder and detection threshold set, we can obtain the expected power of the received signal per block by \eqref{eq:receive_variance}, the conditional probability density function of the accumulated energy by \eqref{eq:energy_distribution}, the decision region by \eqref{eq:decision_region}, the equivalent point-to-point channel by \eqref{eq:point_to_point_channel}, and the discrete memoryless \gls{mac} by \eqref{eq:mac}.
+			which corresponds to $P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K}}})$ by reverse mapping $m_k \mapsfrom i$.
+In summary, with the \gls{csi} knowledge and for any given precoder and detection threshold set, we can obtain the expected power of the received signal per block by \eqref{eq:receive_variance}, the conditional probability density function of the accumulated energy by \eqref{eq:energy_distribution}, the corresponding decision region by \eqref{eq:decision_region}, and the equivalent point-to-point channel by \eqref{eq:point_to_point_channel}.
 		\end{subsection}
@@
 		\begin{subsection}{Input probability distribution}
-			For any fixed decision boundary $\boldsymbol{t}$ and transmit precoder $\boldsymbol{w}$, the equivalent discrete memoryless \gls{mac} can be determined by \eqref{eq:mac} and problem~\eqref{op:rate_region} boils down to
+			For any fixed decision boundary $\boldsymbol{t}$ and transmit precoder $\boldsymbol{w}$, the equivalent discrete memoryless \gls{mac} can be determined by \eqref{eq:point_to_point_channel} and problem~\eqref{op:rate_region} boils down to
 			\begin{maxi!}
@@
 
-		% \begin{subsection}{Decision region}
-		% 	As indicated by \cite{Qian2019b}, the optimal \gls{ml} decision regions are very close to the optimal decision regions to problem \eqref{op:rate_region}.
+		\begin{subsection}{Decision region}
+			As indicated by \cite{Qian2019b}, the optimal \gls{ml} decision regions are very close to the optimal decision regions to problem \eqref{op:rate_region}.
 We can either use \eqref{eq:decision_region} as suboptimal, or take derivative of \eqref{eq:backscatter_sum_rate} w.r.t.
 $T_{i-1,i}$ and $T_{i,i+1}$ (however, closed-form solutions are unavailable and two-dimensional search is needed).
-		% \end{subsection}
+		\end{subsection}
 
-		% \begin{subsection}{Precoder}
-		% 	Interestingly, we can design precoder to adjust the expectation of the received power \eqref{eq:receive_variance} at each tag input combination, which can avoid the detection blind spots in \cite{Qian2019} and further boost the weighted sum-rate.
+		\begin{subsection}{Precoder}
+			Interestingly, we can design precoder to adjust the expectation of the received power \eqref{eq:receive_variance} at each tag input combination, which can avoid the detection blind spots in \cite{Qian2019} and further boost the weighted sum-rate.
 However, the problem is highly non-convex -- the information function associated with input combination state $i$ is
-		% 	\begin{align}
-		% 		I(\bar{c}_i;z)
-		% 		& = \sum_{j \in \mathcal{M^K}} \int_{T_{j-1,j}}^{T_{j,j+1}} \frac{z^{N-1} \exp \left(-\frac{z}{\mathrm{tr}(H_{\mathrm{E},i} W) + \sigma_w^2}\right)}{\left(\mathrm{tr}(H_{\mathrm{E},i} W) + \sigma_w^2\right)^N (N-1)!} \dd z\nonumber\\
-		% 		& \quad \times \log \frac{\int_{T_{j-1,j}}^{T_{j,j+1}} \frac{z^{N-1} \exp \left(-\frac{z}{\mathrm{tr}(H_{\mathrm{E},i} W) + \sigma_w^2}\right)}{\left(\mathrm{tr}(H_{\mathrm{E},i} W) + \sigma_w^2\right)^N (N-1)!} \dd z}{\sum_{i' \in \mathcal{M^K}} \int_{T_{j-1,j}}^{T_{j,j+1}} \frac{z^{N-1} \exp \left(-\frac{z}{\mathrm{tr}(H_{\mathrm{E},i'} W) + \sigma_w^2}\right)}{\left(\mathrm{tr}(H_{\mathrm{E},i'} W) + \sigma_w^2\right)^N (N-1)!} \dd z},
-		% 		\label{eq:foo}
-		% 	\end{align}
-		% 	and the mutual information can be expressed as a function of $W$ by combining \eqref{eq:backscatter_sum_rate} and \eqref{eq:foo}.
+			\begin{align}
+				I(\bar{c}_i;z)
+				& = \sum_{j \in \mathcal{M^K}} \int_{T_{j-1,j}}^{T_{j,j+1}} \frac{z^{N-1} \exp \left(-\frac{z}{\mathrm{tr}(H_{\mathrm{E},i} W) + \sigma_w^2}\right)}{\left(\mathrm{tr}(H_{\mathrm{E},i} W) + \sigma_w^2\right)^N (N-1)!} \dd z\nonumber\\
+				& \quad \times \log \frac{\int_{T_{j-1,j}}^{T_{j,j+1}} \frac{z^{N-1} \exp \left(-\frac{z}{\mathrm{tr}(H_{\mathrm{E},i} W) + \sigma_w^2}\right)}{\left(\mathrm{tr}(H_{\mathrm{E},i} W) + \sigma_w^2\right)^N (N-1)!} \dd z}{\sum_{i' \in \mathcal{M^K}} \int_{T_{j-1,j}}^{T_{j,j+1}} \frac{z^{N-1} \exp \left(-\frac{z}{\mathrm{tr}(H_{\mathrm{E},i'} W) + \sigma_w^2}\right)}{\left(\mathrm{tr}(H_{\mathrm{E},i'} W) + \sigma_w^2\right)^N (N-1)!} \dd z},
+				\label{eq:foo}
+			\end{align}
+			and the mutual information can be expressed as a function of $W$ by combining \eqref{eq:backscatter_sum_rate} and \eqref{eq:foo}.
 
-		% 	So far I have no idea how to solve this issue, and found no reference regarding precoder design for \gls{ambc}/\gls{sr} with discrete channels (although some naive combiner designs are available for \gls{bibo}).
+			So far I have no idea how to solve this issue, and found no reference regarding precoder design for \gls{ambc}/\gls{sr} with discrete channels (although some naive combiner designs are available for \gls{bibo}).
 Personally, I believe the precoder design is the key to (i) boost the rate region and avoid blind spots in conventional \gls{ambc}; (ii) build our proposal over existing infrastructures.
 Ideally, assuming the number of transmit antennas $Q$ is larger than the number of tags $K$, the optimal energy levels should be almost uniformly spaced (as $z$ follows Erlang distribution) to concentrate the channel transitional probability on diagonal as possible.
-		% \end{subsection}
+		\end{subsection}
 	\end{section}

### 2021-12-25 main.tex
:pencil: Update notation

@@
 % \usepackage[subtle]{savetrees}
-\usepackage{stmaryrd}
+% \usepackage{stmaryrd}
 
@@
 			denotes the expectation of the received power per primary block under tag modulation index set $m_{\mathcal{K}}$.
-For the ease of exposition, we denote the hypothesis that the tag input combination at state $i \in \mathcal{M^K} \triangleq \{1,\ldots,M^K\}$ as $\mathcal{H}_i$, sort $\{\sigma_{m_{\mathcal{K}}}^2\}$ in ascending order by a one-to-one mapping $m_{\mathcal{K}} \mapsto i$,\footnote{When more than one modulation index sets yield the same energy level, the mapping is not unique and the detection fails to separate them.
+For the ease of exposition, we denote the hypothesis that the tag input combination at state $i \in \mathcal{I} \triangleq \{1,\ldots,M^K\}$ as $\mathcal{H}_i$, sort $\{\sigma_{m_{\mathcal{K}}}^2\}$ in ascending order by a one-to-one mapping $m_{\mathcal{K}} \mapsto i$,\footnote{When more than one modulation index sets yield the same energy level, the mapping is not unique and the detection fails to separate them.
 This blind spot issue can be mitigated by multi-antenna techniques.} define the received signal energy over $N$ primary blocks as $z \triangleq \lVert \boldsymbol{y} \rVert^2$, and let $f(z \mid \mathcal{H}_i)$ be the conditional probability density function of receiving $z$ under hypothesis $\mathcal{H}_i$.
@@
 
-			Once the decision region is determined, the discrete memoryless \gls{mac} can be recast as an equivalent point-to-point \gls{dmc} from tag input combination alphabet $\mathcal{M^K}$ to output energy level alphabet $\mathcal{M^K}$.
+			Once the decision region is determined, the discrete memoryless \gls{mac} can be recast as an equivalent point-to-point \gls{dmc} from tag input combination alphabet $\mathcal{I}$ to output energy level alphabet $\mathcal{I}$.
 The the probability of receiving energy level $j$ under tag input combination $i$ is\footnote{For simplicity, we assume there exists at least one feasible precoder that produces distinct received energy levels for all tag input combinations.
@@
 			\end{equation}
-			which corresponds to $P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K}}})$ by reverse mapping $m_k \mapsfrom i$.
+			which corresponds to $P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K}}})$ by reverse mapping $m_k \mapsto i$.
 In summary, with the \gls{csi} knowledge and for any given precoder and detection threshold set, we can obtain the expected power of the received signal per block by \eqref{eq:receive_variance}, the conditional probability density function of the accumulated energy by \eqref{eq:energy_distribution}, the corresponding decision region by \eqref{eq:decision_region}, and the equivalent point-to-point channel by \eqref{eq:point_to_point_channel}.
@@
 				I(\bar{c}_i;z)
-				& = \sum_{j \in \mathcal{M^K}} \int_{T_{j-1,j}}^{T_{j,j+1}} \frac{z^{N-1} \exp \left(-\frac{z}{\mathrm{tr}(H_{\mathrm{E},i} W) + \sigma_w^2}\right)}{\left(\mathrm{tr}(H_{\mathrm{E},i} W) + \sigma_w^2\right)^N (N-1)!} \dd z\nonumber\\
-				& \quad \times \log \frac{\int_{T_{j-1,j}}^{T_{j,j+1}} \frac{z^{N-1} \exp \left(-\frac{z}{\mathrm{tr}(H_{\mathrm{E},i} W) + \sigma_w^2}\right)}{\left(\mathrm{tr}(H_{\mathrm{E},i} W) + \sigma_w^2\right)^N (N-1)!} \dd z}{\sum_{i' \in \mathcal{M^K}} \int_{T_{j-1,j}}^{T_{j,j+1}} \frac{z^{N-1} \exp \left(-\frac{z}{\mathrm{tr}(H_{\mathrm{E},i'} W) + \sigma_w^2}\right)}{\left(\mathrm{tr}(H_{\mathrm{E},i'} W) + \sigma_w^2\right)^N (N-1)!} \dd z},
+				& = \sum_{j \in \mathcal{I}} \int_{T_{j-1,j}}^{T_{j,j+1}} \frac{z^{N-1} \exp \left(-\frac{z}{\mathrm{tr}(H_{\mathrm{E},i} W) + \sigma_w^2}\right)}{\left(\mathrm{tr}(H_{\mathrm{E},i} W) + \sigma_w^2\right)^N (N-1)!} \dd z\nonumber\\
+				& \quad \times \log \frac{\int_{T_{j-1,j}}^{T_{j,j+1}} \frac{z^{N-1} \exp \left(-\frac{z}{\mathrm{tr}(H_{\mathrm{E},i} W) + \sigma_w^2}\right)}{\left(\mathrm{tr}(H_{\mathrm{E},i} W) + \sigma_w^2\right)^N (N-1)!} \dd z}{\sum_{i' \in \mathcal{I}} \int_{T_{j-1,j}}^{T_{j,j+1}} \frac{z^{N-1} \exp \left(-\frac{z}{\mathrm{tr}(H_{\mathrm{E},i'} W) + \sigma_w^2}\right)}{\left(\mathrm{tr}(H_{\mathrm{E},i'} W) + \sigma_w^2\right)^N (N-1)!} \dd z},
 				\label{eq:foo}

### 2022-01-23 main.tex
:pencil: Add thresholding design problem

@@
 For the ease of exposition, we denote the hypothesis that the tag input combination at state $i \in \mathcal{I} \triangleq \{1,\ldots,M^K\}$ as $\mathcal{H}_i$, sort $\{\sigma_{m_{\mathcal{K}}}^2\}$ in ascending order by a one-to-one mapping $m_{\mathcal{K}} \mapsto i$,\footnote{When more than one modulation index sets yield the same energy level, the mapping is not unique and the detection fails to separate them.
-This blind spot issue can be mitigated by multi-antenna techniques.} define the received signal energy over $N$ primary blocks as $z \triangleq \lVert \boldsymbol{y} \rVert^2$, and let $f(z \mid \mathcal{H}_i)$ be the conditional probability density function of receiving $z$ under hypothesis $\mathcal{H}_i$.
+This blind spot issue can be potentially mitigated by multi-antenna techniques and is beyond the scope of this paper.} define the received signal energy over $N$ primary blocks as $z \triangleq \lVert \boldsymbol{y} \rVert^2$, and let $f(z \mid \mathcal{H}_i)$ be the conditional probability density function of receiving $z$ under hypothesis $\mathcal{H}_i$.
 Correspondingly, $z$ is the sum of $N$ i.i.d.
-exponential variables each with mean $\sigma_i^2$, and the conditional probability density function follows Erlang distribution with shape $N$ and scale $\sigma_i^2$ as
+exponential variables each with mean $\sigma_i^2$, and the conditional probability density function follows Erlang distribution with shape $N$ and scale $\sigma_i^2$ as\footnote{In some papers, it may also be referred to as Gamma distribution.}
 			\begin{equation}
@@
 
-			Denote the decision region of hypothesis $\mathcal{H}_i$ as
+			To maximize the mutual information for a general non-binary-input continuous-output channel, not only the decision region design remains an open problem, but also the optimal number of decision thresholds is still unknown.
+The reason is that the optimal decision region $\mathcal{R}_j$ of hypothesis $\mathcal{H}_j$ may be non-convex (i.e., consist of more than one disjoint partitions).
+The authors of \cite{Nguyen2021} showed that any optimal quantizer with arbitrary cost function must separate the backward channel  (i.e., posterior distribution) into convex decision regions, and provided an upper bound on the number of thresholds.
+
+			\begin{theorem}
+				If any $L$-input ($L \in \mathbb{Z}_{++}$) continuous-output channel follows Erlang distribution~\eqref{eq:energy_distribution}, then the optimal number of thresholds is $L+1$ and the capacity-achieving decision region $j$ has convex structure $\mathcal{R}_j^{\star} = [t_{j-1}^{\star}, t_j^{\star})$.
+			\end{theorem}
+
+			\begin{proof}
+				For any finite number of thresholds $S \in \mathbb{Z}_{++}$, let $\boldsymbol{t} \triangleq [t_0,\ldots,t_S]^T \in \mathbb{R}_{+}^{S \times 1}$ be the thresholding vector where $t_{s-1} < t_s$, $\forall s \in \mathcal{S} \triangleq \{1,\ldots,S\}$.\footnote{We consider strict inequality in definition, since otherwise $S$ and $\boldsymbol{t}$ could be non-unique for a given thresholding scheme.} Denote the decision partition $s$ as $R_s \triangleq [t_{s-1},t_s)$.
+Without loss of generality, we assume
+				% $L \mid S$ and
+				$\mathcal{R}_j = \bigcup_{s \equiv j \pmod L} R_s$.\footnote{Note that the proof holds for general mapping and we focus on this case for the ease of notation.} The thresholding design problem can be expressed as
+				\begin{maxi!}
+					{\scriptstyle{\boldsymbol{t}}}{I_{\mathrm{B}}(c_{\mathcal{K}};z)}{\label{op:thresholding}}{\label{ob:backscatter_mutual_information}}
+					\addConstraint{t_{s-1}}{< t_s,}{\quad \forall s \in \mathcal{S}.}{\label{co:strict_inequality}}
+				\end{maxi!}
+
+				Problem~\eqref{op:thresholding} is intricate due to the strict inequality constraint~\eqref{co:strict_inequality}.
+Following \cite{Nguyen2020}, we first relax it to the convex counterpart, then discard the solutions that violate the original constraints.
+The Lagrangian function for the relaxed problem is
 				\begin{equation}
-				\mathcal{R}_i \triangleq [T_{i-1,i}, T_{i,i+1}),
-				\label{eq:decision_region}
+					L(\boldsymbol{t},\boldsymbol{\mu}) = - I_{\mathrm{B}}(c_{\mathcal{K}};z) + \sum_{s \in \mathcal{S}} \mu_s (t_{s-1} - t_s),
+					% = \sum_{j \in \mathcal{L}} P(\bar{z}_j) \log P(\bar{z}_j) - \sum_{i \in \mathcal{L}} \sum_{j \in \mathcal{L}}
 				\end{equation}
-			where $T_{i-1,i}$ is the decision threshold between $\mathcal{H}_{i-1}$ and $\mathcal{H}_i$, and $T_{i,i+1}$ is the decision threshold between $\mathcal{H}_i$ and $\mathcal{H}_{i+1}$.
-We also define $T_{0,1} \triangleq 0$, $T_{M^K,M^K+1} \triangleq \infty$, and $\boldsymbol{t} \triangleq [T_{0,1},\ldots,T_{M^K,M^K+1}]^T \in \mathbb{R}^{(M^K + 1) \times 1}$.
+				where $\mu_s$ is the Lagrange multiplier associated with the non-strict counterpart of \eqref{co:strict_inequality} and $\boldsymbol{\mu} \triangleq [\mu_1,\ldots,\mu_S]^T \in \mathbb{R}^{S \times 1}$.
+The corresponding \gls{kkt} conditions on the optimal primal and dual solutions are, $\forall s \in \mathcal{S}$,
+				\begin{subequations}
+					\begin{equation}
+						- \nabla_{t_s^{\star}} I^{\star}_{\mathrm{B}}(c_{\mathcal{K}};z) + \mu_{s-1}^{\star} - \mu_s^{\star} = 0,
+						\label{eq:stationarity}
+					\end{equation}
+					\begin{equation}
+						\mu_s^{\star} \ge 0,
+						\label{eq:dual_feasibility}
+					\end{equation}
+					\begin{equation}
+						\mu_s^{\star} (t_{s-1}^{\star} - t_s^{\star}) = 0.
+						\label{eq:complementary_slackness}
+					\end{equation}
+				\end{subequations}
+				Since we require $t_{s-1} < t_s$ by definition, \eqref{eq:dual_feasibility} and \eqref{eq:complementary_slackness} imply $\mu_s^{\star} = 0$, $\forall s \in \mathcal{S}$.
+Therefore, \eqref{eq:stationarity} reduces to
+				\begin{equation}
+					\nabla_{t_s^{\star}} I^{\star}_{\mathrm{B}}(c_{\mathcal{K}};z) = 0.
+				\end{equation}
+			\end{proof}
 
-			Consider the (\gls{ml}) detector for example. The likelihood ratio between hypotheses $\mathcal{H}_i$ and $\mathcal{H}_{i'}$ is \cite{Qian2019}
-			\begin{equation}
-				\Lambda_{i,{i'}}^{\mathrm{\gls{ml}}}(z) = \frac{f(z \mid \mathcal{H}_i)}{f(z \mid \mathcal{H}_{i'})} = \left( \frac{\sigma_{i'}^2}{\sigma_i^2} \right)^N \exp \left( \frac{\sigma_i^2 - \sigma_{i'}^2}{\sigma_i^2 \sigma_{i'}^2} z \right),
-				\label{eq:likelihood_ratio}
-			\end{equation}
-			the corresponding decision rule is
-			\begin{equation}
-				\Lambda_{i,{i'}}^{\mathrm{\gls{ml}}}(z) \underset{\mathcal{H}_{i'}}{\overset{\mathcal{H}_i}{\lessgtr}} 1 \iff z \underset{\mathcal{H}_{i'}}{\overset{\mathcal{H}_i}{\lessgtr}} T_{i,{i'}}^{\mathrm{\gls{ml}}},
-				\label{eq:decision_rule}
-			\end{equation}
-			and the detection threshold is
-			\begin{equation}
-				T_{i,{i'}}^{\mathrm{\gls{ml}}} \triangleq N \frac{\sigma_i^2 \sigma_{i'}^2}{\sigma_i^2 - \sigma_{i'}^2} \log \frac{\sigma_i^2}{\sigma_{i'}^2}.
-				\label{eq:detection_threshold}
-			\end{equation}
+			% It was proved in \cite{Nguyen2021} that the optimal quantizer producing maximizing mutual information with arbitrary cost function separates the backward channel (i.e., posterior distribution) in a convex manner
 
-			\begin{remark}
-				Although the \gls{ml} decision threshold is optimal in terms of the likelihood function, it is not necessarily capacity-achieving, although the performance gap can be negligible in the single-tag \gls{bibo} case.
-			\end{remark}
+			% not only the capacity-achieving thresholding design remains an open problem, but also the optimal number of thresholds for general non-binary-input channels remains unknown.
+I am now trying to prove that, for our channel in Gamma distribution, the optimal decision region for each codeword cannot be disjoint
+
+			% Denote the decision region of hypothesis $\mathcal{H}_i$ as
+			% \begin{equation}
+			% 	\mathcal{R}_i \triangleq [t_{i-1,i}, t_{i,i+1}),
+			% 	\label{eq:decision_region}
+			% \end{equation}
+			% where $t_{i-1,i}$ is the decision threshold between $\mathcal{H}_{i-1}$ and $\mathcal{H}_i$, and $t_{i,i+1}$ is the decision threshold between $\mathcal{H}_i$ and $\mathcal{H}_{i+1}$.
+We also define $t_{0,1} \triangleq 0$, $t_{M^K,M^K+1} \triangleq \infty$, and $\boldsymbol{t} \triangleq [t_{0,1},\ldots,t_{M^K,M^K+1}]^T \in \mathbb{R}^{(M^K + 1) \times 1}$.
+
+			% Consider the (\gls{ml}) detector for example. The likelihood ratio between hypotheses $\mathcal{H}_i$ and $\mathcal{H}_{i'}$ is \cite{Qian2019}
+			% \begin{equation}
+			% 	\Lambda_{i,{i'}}^{\mathrm{\gls{ml}}}(z) = \frac{f(z \mid \mathcal{H}_i)}{f(z \mid \mathcal{H}_{i'})} = \left( \frac{\sigma_{i'}^2}{\sigma_i^2} \right)^N \exp \left( \frac{\sigma_i^2 - \sigma_{i'}^2}{\sigma_i^2 \sigma_{i'}^2} z \right),
+			% 	\label{eq:likelihood_ratio}
+			% \end{equation}
+			% the corresponding decision rule is
+			% \begin{equation}
+			% 	\Lambda_{i,{i'}}^{\mathrm{\gls{ml}}}(z) \underset{\mathcal{H}_{i'}}{\overset{\mathcal{H}_i}{\lessgtr}} 1 \iff z \underset{\mathcal{H}_{i'}}{\overset{\mathcal{H}_i}{\lessgtr}} t_{i,{i'}}^{\mathrm{\gls{ml}}},
+			% 	\label{eq:decision_rule}
+			% \end{equation}
+			% and the detection threshold is
+			% \begin{equation}
+			% 	t_{i,{i'}}^{\mathrm{\gls{ml}}} \triangleq N \frac{\sigma_i^2 \sigma_{i'}^2}{\sigma_i^2 - \sigma_{i'}^2} \log \frac{\sigma_i^2}{\sigma_{i'}^2}.
+			% 	\label{eq:detection_threshold}
+			% \end{equation}
+
+			% \begin{remark}
+			% 	Although the \gls{ml} decision threshold is optimal in terms of the likelihood function, it is not necessarily capacity-achieving, although the performance gap can be negligible in the single-tag \gls{bibo} case.
+			% \end{remark}
 
@@
 				{\scriptstyle{\boldsymbol{P},\boldsymbol{t},\boldsymbol{w}}}{I(c_{\mathcal{K}};\boldsymbol{y},z)}{\label{op:rate_region}}{\label{ob:weighted_sum_rate}}
-				\addConstraint{\sum \nolimits_{m_k} P_k(\bar{c}_{m_k})}{=1,\quad\label{co:sum_probability}}{\forall k \in \mathcal{K}}
-				\addConstraint{P_k(\bar{c}_{m_k})}{\ge 0,\quad\label{co:nonnegative_probability}}{\forall m_k \in \mathcal{M}, \ \forall k \in \mathcal{K}}
-				\addConstraint{\lVert \boldsymbol{w} \rVert^2}{\le P.\label{co:average_transmit_power}}
+				\addConstraint{\sum \nolimits_{m_k} P_k(\bar{c}_{m_k})}{=1,}{\quad \forall k \in \mathcal{K}}{\label{co:sum_probability}}
+				\addConstraint{P_k(\bar{c}_{m_k})}{\ge 0,}{\quad \forall m_k \in \mathcal{M}, \ \forall k \in \mathcal{K}}{\label{co:nonnegative_probability}}
+				\addConstraint{\lVert \boldsymbol{w} \rVert^2}{\le P.}{\label{co:average_transmit_power}}
 			\end{maxi!}
@@
 			\begin{proof}
-				Denote the Lagrange multiplier associated with \eqref{co:sum_probability} and \eqref{co:nonnegative_probability} as $\boldsymbol{\mu} \triangleq [\mu_1,\ldots,\mu_K]^T \in \mathbb{R}^{K \times 1}$ and $\boldsymbol{\Lambda} \triangleq [\boldsymbol{\lambda}_1^T,\ldots,\boldsymbol{\lambda}_K^T]^T \in \mathbb{R}^{M \times K}$ with $\boldsymbol{\lambda}_k \triangleq [\lambda_{k,1},\ldots,\lambda_{k,M}]^T \in \mathbb{R}^{M \times 1}$, respectively.
+				Denote the Lagrange multiplier associated with \eqref{co:sum_probability} and \eqref{co:nonnegative_probability} as $\boldsymbol{\nu} \triangleq [\nu_1,\ldots,\nu_K]^T \in \mathbb{R}^{K \times 1}$ and $\boldsymbol{\Lambda} \triangleq [\boldsymbol{\lambda}_1^T,\ldots,\boldsymbol{\lambda}_K^T]^T \in \mathbb{R}^{M \times K}$ with $\boldsymbol{\lambda}_k \triangleq [\lambda_{k,1},\ldots,\lambda_{k,M}]^T \in \mathbb{R}^{M \times 1}$, respectively.
 The Lagrangian function of problem~\eqref{op:input_probability_distribution} is
 				\begin{align}
-					L(\boldsymbol{P},\boldsymbol{\mu},\boldsymbol{\Lambda})
-					& = - I(c_{\mathcal{K}};\boldsymbol{y},z) + \sum_{k \in \mathcal{K}} \mu_k \left( \sum_{m_k \in \mathcal{M}} P_k(\bar{c}_{m_k}) - 1 \right)\nonumber\\
+					L(\boldsymbol{P},\boldsymbol{\nu},\boldsymbol{\Lambda})
+					& = - I(c_{\mathcal{K}};\boldsymbol{y},z) + \sum_{k \in \mathcal{K}} \nu_k \left( \sum_{m_k \in \mathcal{M}} P_k(\bar{c}_{m_k}) - 1 \right)\nonumber\\
 					& \quad - \sum_{k \in \mathcal{K}} \sum_{m_k \in \mathcal{M}} \lambda_{k,m_k} P_k(\bar{c}_{m_k}),
 				\end{align}
-				and the corresponding \gls{kkt} conditions on the primal and dual solutions are, $\forall m_k \in \mathcal{M}$ and $\forall k \in \mathcal{K}$,
+				and the corresponding \gls{kkt} conditions are, $\forall m_k \in \mathcal{M}$ and $\forall k \in \mathcal{K}$,
 				\begin{subequations}
 					\begin{equation}
-						- \nabla_{P_k^{\star}(\bar{c}_{m_k})} I^{\star}(c_{\mathcal{K}};\boldsymbol{y},z) + \mu_k^{\star} - \lambda_{k,m_k}^{\star} = 0,
+						- \nabla_{P_k^{\star}(\bar{c}_{m_k})} I^{\star}(c_{\mathcal{K}};\boldsymbol{y},z) + \nu_k^{\star} - \lambda_{k,m_k}^{\star} = 0,
 					\end{equation}
@@
 					\begin{alignat}{2}
-						I_k^{\star}(\bar{c}_{m_k};\boldsymbol{y},z) & = \mu_k^{\star} + (1 - \rho), \quad && P_k^{\star}(\bar{c}_{m_k}) > 0,\label{eq:probable_states_marginal}\\
-						I_k^{\star}(\bar{c}_{m_k};\boldsymbol{y},z) & \le \mu_k^{\star} + (1 - \rho), \quad && P_k^{\star}(\bar{c}_{m_k}) = 0,\label{eq:dropped_states_marginal}
+						I_k^{\star}(\bar{c}_{m_k};\boldsymbol{y},z) & = \nu_k^{\star} + (1 - \rho), \quad && P_k^{\star}(\bar{c}_{m_k}) > 0,\label{eq:probable_states_marginal}\\
+						I_k^{\star}(\bar{c}_{m_k};\boldsymbol{y},z) & \le \nu_k^{\star} + (1 - \rho), \quad && P_k^{\star}(\bar{c}_{m_k}) = 0,\label{eq:dropped_states_marginal}
 					\end{alignat}
@@
 				\begin{equation}
-					\sum_{m_k} P_k^{\star}(\bar{c}_{m_k}) I_k^{\star}(\bar{c}_{m_k};\boldsymbol{y},z) = \mu_k^{\star} + (1 - \rho).
+					\sum_{m_k} P_k^{\star}(\bar{c}_{m_k}) I_k^{\star}(\bar{c}_{m_k};\boldsymbol{y},z) = \nu_k^{\star} + (1 - \rho).
 				\end{equation}
@@
 				\end{equation}
-				which is irrelevant to $k$. It suggests $I^{\star}(c_{\mathcal{K}};\boldsymbol{y},z) = \mu_k^{\star} + (1 - \rho)$, $\forall k \in \mathcal{K}$, and completes the proof.
+				which is irrelevant to $k$. It suggests $I^{\star}(c_{\mathcal{K}};\boldsymbol{y},z) = \nu_k^{\star} + (1 - \rho)$, $\forall k \in \mathcal{K}$, and completes the proof.
 			\end{proof}
@@
 We can either use \eqref{eq:decision_region} as suboptimal, or take derivative of \eqref{eq:backscatter_sum_rate} w.r.t.
-$T_{i-1,i}$ and $T_{i,i+1}$ (however, closed-form solutions are unavailable and two-dimensional search is needed).
+$t_{i-1,i}$ and $t_{i,i+1}$ (however, closed-form solutions are unavailable and two-dimensional search is needed).
 		\end{subsection}
@@
 				I(\bar{c}_i;z)
-				& = \sum_{j \in \mathcal{I}} \int_{T_{j-1,j}}^{T_{j,j+1}} \frac{z^{N-1} \exp \left(-\frac{z}{\mathrm{tr}(H_{\mathrm{E},i} W) + \sigma_w^2}\right)}{\left(\mathrm{tr}(H_{\mathrm{E},i} W) + \sigma_w^2\right)^N (N-1)!} \dd z\nonumber\\
-				& \quad \times \log \frac{\int_{T_{j-1,j}}^{T_{j,j+1}} \frac{z^{N-1} \exp \left(-\frac{z}{\mathrm{tr}(H_{\mathrm{E},i} W) + \sigma_w^2}\right)}{\left(\mathrm{tr}(H_{\mathrm{E},i} W) + \sigma_w^2\right)^N (N-1)!} \dd z}{\sum_{i' \in \mathcal{I}} \int_{T_{j-1,j}}^{T_{j,j+1}} \frac{z^{N-1} \exp \left(-\frac{z}{\mathrm{tr}(H_{\mathrm{E},i'} W) + \sigma_w^2}\right)}{\left(\mathrm{tr}(H_{\mathrm{E},i'} W) + \sigma_w^2\right)^N (N-1)!} \dd z},
+				& = \sum_{j \in \mathcal{I}} \int_{t_{j-1,j}}^{t_{j,j+1}} \frac{z^{N-1} \exp \left(-\frac{z}{\mathrm{tr}(H_{\mathrm{E},i} W) + \sigma_w^2}\right)}{\left(\mathrm{tr}(H_{\mathrm{E},i} W) + \sigma_w^2\right)^N (N-1)!} \dd z\nonumber\\
+				& \quad \times \log \frac{\int_{t_{j-1,j}}^{t_{j,j+1}} \frac{z^{N-1} \exp \left(-\frac{z}{\mathrm{tr}(H_{\mathrm{E},i} W) + \sigma_w^2}\right)}{\left(\mathrm{tr}(H_{\mathrm{E},i} W) + \sigma_w^2\right)^N (N-1)!} \dd z}{\sum_{i' \in \mathcal{I}} \int_{t_{j-1,j}}^{t_{j,j+1}} \frac{z^{N-1} \exp \left(-\frac{z}{\mathrm{tr}(H_{\mathrm{E},i'} W) + \sigma_w^2}\right)}{\left(\mathrm{tr}(H_{\mathrm{E},i'} W) + \sigma_w^2\right)^N (N-1)!} \dd z},
 				\label{eq:foo}

### 2022-01-24 main.tex
:pencil: Add initial thresholding proof

@@
 			\begin{proof}
-				For any finite number of thresholds $S \in \mathbb{Z}_{++}$, let $\boldsymbol{t} \triangleq [t_0,\ldots,t_S]^T \in \mathbb{R}_{+}^{S \times 1}$ be the thresholding vector where $t_{s-1} < t_s$, $\forall s \in \mathcal{S} \triangleq \{1,\ldots,S\}$.\footnote{We consider strict inequality in definition, since otherwise $S$ and $\boldsymbol{t}$ could be non-unique for a given thresholding scheme.} Denote the decision partition $s$ as $R_s \triangleq [t_{s-1},t_s)$.
+				For any finite number of thresholds $S \in \mathbb{Z}_{++}$, let $\boldsymbol{t} \triangleq [t_0,\ldots,t_S]^T \in \mathbb{R}_{+}^{S \times 1}$ be the thresholding vector where $t_{s-1} < t_s$, $\forall s \in \mathcal{S} \triangleq \{1,\ldots,S\}$.\footnote{We consider strict inequality in the definition, as otherwise $S$ and $\boldsymbol{t}$ could be non-unique for a given thresholding scheme.} Denote the decision partition $s$ as $R_s \triangleq [t_{s-1},t_s)$.
 Without loss of generality, we assume
 				% $L \mid S$ and
-				$\mathcal{R}_j = \bigcup_{s \equiv j \pmod L} R_s$.\footnote{Note that the proof holds for general mapping and we focus on this case for the ease of notation.} The thresholding design problem can be expressed as
+				$\mathcal{R}_j = \bigcup_{s \equiv j \pmod L} R_s$.\footnote{The proof holds for general mapping $R_s \mapsto \mathcal{R}_j$, and we focus on this specific case for the ease of notation.} The thresholding design problem can be expressed as
 				\begin{maxi!}
@@
 				\end{equation}
-				where $\mu_s$ is the Lagrange multiplier associated with the non-strict counterpart of \eqref{co:strict_inequality} and $\boldsymbol{\mu} \triangleq [\mu_1,\ldots,\mu_S]^T \in \mathbb{R}^{S \times 1}$.
+				where $\mu_s$ is the Lagrange multiplier associated with the non-strict version of \eqref{co:strict_inequality} and $\boldsymbol{\mu} \triangleq [\mu_1,\ldots,\mu_S]^T \in \mathbb{R}^{S \times 1}$.
 The corresponding \gls{kkt} conditions on the optimal primal and dual solutions are, $\forall s \in \mathcal{S}$,
@@
 					\end{equation}
+					\label{eq:kkt_thresholding}
 				\end{subequations}
-				Since we require $t_{s-1} < t_s$ by definition, \eqref{eq:dual_feasibility} and \eqref{eq:complementary_slackness} imply $\mu_s^{\star} = 0$, $\forall s \in \mathcal{S}$.
-Therefore, \eqref{eq:stationarity} reduces to
+				For \gls{dmtc} based on energy detection~\eqref{eq:energy_distribution}, it is trivial to conclude $t_0^{\star} = 0$ and $t_S^{\star} = \infty$.
+Besides, since $t_{s-1} < t_s$ by definition, \eqref{eq:dual_feasibility} and \eqref{eq:complementary_slackness} imply $\mu_s^{\star} = 0$, $\forall s \in \mathcal{S}$.
+As such, $\forall s' \in \mathcal{S} \setminus \{S\}$, \eqref{eq:kkt_thresholding} reduces to
 				\begin{equation}
-					\nabla_{t_s^{\star}} I^{\star}_{\mathrm{B}}(c_{\mathcal{K}};z) = 0.
+					\nabla_{t_{s'}^{\star}} I^{\star}_{\mathrm{B}}(c_{\mathcal{K}};z) = 0,
 				\end{equation}
+				which can be explicitly written as
+				\begin{equation}
+					\sum_l P(x_l) \log \frac{P(z_j)}{P(z_{j+1})} \frac{P(z_{j+1} \mid x_l)}{P(z_j \mid x_l)} f(h_s \mid x_l) = 0,
+					\label{eq:kkt_thresholding_explicit}
+				\end{equation}
+				where $j \equiv s \pmod L$.
+We notice that for a given $j$, $a_l \triangleq P(x_l) \log \frac{P(z_j)}{P(z_{j+1})} \frac{P(z_{j+1} \mid x_l)}{P(z_j \mid x_l)}$ is a constant for all $s \equiv j \pmod L$.
+Plugging~\eqref{eq:energy_distribution} into \eqref{eq:kkt_thresholding_explicit}, we have
+				\begin{equation}
+					\sum_l a_l e^{-{h_s}/{\sigma_l^2}} = 0,
+					\label{eq:optimal_thresholding_condition}
+				\end{equation}
+				which by Rolle's theorem has at most $L-1$ distinct real roots if $\sigma_i^2 \ne \sigma_j^2$, $i,j \in \mathcal{L}$.
+				% where the directional derivative can be explicitly written as
+				% \begin{subequations}
+				% 	\begin{align}
+				% 		\nabla_{t_{s'}^{\star}} I^{\star}_{\mathrm{B}}(c_{\mathcal{K}};z)
+				% 		& = \sum_l P(x_l) \log \frac{P(z_j)}{P(z_{j+1})} \frac{P(z_{j+1} \mid x_l)}{P(z_j \mid x_l)} f(h_s \mid x_l)\\
+				% 		& = 1
+				% 	\end{align}
+				% \end{subequations}
 			\end{proof}

### 2022-01-26 main.tex
:pencil: Update thresholding proof

--- 2022-01-23 main.tex
@@
 			\begin{theorem}
-				If any $L$-input ($L \in \mathbb{Z}_{++}$) continuous-output channel follows Erlang distribution~\eqref{eq:energy_distribution}, then the optimal number of thresholds is $L+1$ and the capacity-achieving decision region $j$ has convex structure $\mathcal{R}_j^{\star} = [t_{j-1}^{\star}, t_j^{\star})$.
+				If any $L$-input continuous-output channel follows Erlang distribution~\eqref{eq:energy_distribution}, then the optimal number of thresholds is $L+1$ and the capacity-achieving decision region $j$ has convex structure $\mathcal{R}_j^\star = [t_{j-1}^\star, t_j^\star)$.
 			\end{theorem}
@@
 			\begin{proof}
-				For any finite number of thresholds $S \in \mathbb{Z}_{++}$, let $\boldsymbol{t} \triangleq [t_0,\ldots,t_S]^T \in \mathbb{R}_{+}^{S \times 1}$ be the thresholding vector where $t_{s-1} < t_s$, $\forall s \in \mathcal{S} \triangleq \{1,\ldots,S\}$.\footnote{We consider strict inequality in definition, since otherwise $S$ and $\boldsymbol{t}$ could be non-unique for a given thresholding scheme.} Denote the decision partition $s$ as $R_s \triangleq [t_{s-1},t_s)$.
+				For any finite number of thresholds $S \ge L+1$, let $\boldsymbol{t} \triangleq [t_0,\ldots,t_S]^T \in \mathbb{R}_{+}^{S \times 1}$ be the thresholding vector where $t_{s-1} < t_s$, $\forall s \in \mathcal{S} \triangleq \{1,\ldots,S\}$.\footnote{We consider strict inequality in the definition, as otherwise $S$ and $\boldsymbol{t}$ could be non-unique for a given thresholding scheme.} Denote the decision partition $s$ as $R_s \triangleq [t_{s-1},t_s)$.
 Without loss of generality, we assume
 				% $L \mid S$ and
-				$\mathcal{R}_j = \bigcup_{s \equiv j \pmod L} R_s$.\footnote{Note that the proof holds for general mapping and we focus on this case for the ease of notation.} The thresholding design problem can be expressed as
+				$\mathcal{R}_j = \bigcup_{s \equiv j \pmod L} R_s$.\footnote{The proof holds for general mapping $R_s \mapsto \mathcal{R}_j$, and we focus on this specific case for the ease of notation.} The thresholding design problem can be expressed as
 				\begin{maxi!}
@@
 				\end{equation}
-				where $\mu_s$ is the Lagrange multiplier associated with the non-strict counterpart of \eqref{co:strict_inequality} and $\boldsymbol{\mu} \triangleq [\mu_1,\ldots,\mu_S]^T \in \mathbb{R}^{S \times 1}$.
+				where $\mu_s$ is the Lagrange multiplier associated with the non-strict version of \eqref{co:strict_inequality} and $\boldsymbol{\mu} \triangleq [\mu_1,\ldots,\mu_S]^T \in \mathbb{R}^{S \times 1}$.
 The corresponding \gls{kkt} conditions on the optimal primal and dual solutions are, $\forall s \in \mathcal{S}$,
 				\begin{subequations}
+					\label{eq:kkt_thresholding}
 					\begin{equation}
-						- \nabla_{t_s^{\star}} I^{\star}_{\mathrm{B}}(c_{\mathcal{K}};z) + \mu_{s-1}^{\star} - \mu_s^{\star} = 0,
+						- \nabla_{t_s^\star} I^\star_{\mathrm{B}}(c_{\mathcal{K}};z) + \mu_{s-1}^\star - \mu_s^\star = 0,
 						\label{eq:stationarity}
@@
 					\begin{equation}
-						\mu_s^{\star} \ge 0,
+						\mu_s^\star \ge 0,
 						\label{eq:dual_feasibility}
@@
 					\begin{equation}
-						\mu_s^{\star} (t_{s-1}^{\star} - t_s^{\star}) = 0.
+						\mu_s^\star (t_{s-1}^\star - t_s^\star) = 0.
 						\label{eq:complementary_slackness}
 					\end{equation}
+
 				\end{subequations}
-				Since we require $t_{s-1} < t_s$ by definition, \eqref{eq:dual_feasibility} and \eqref{eq:complementary_slackness} imply $\mu_s^{\star} = 0$, $\forall s \in \mathcal{S}$.
-Therefore, \eqref{eq:stationarity} reduces to
+				Due to the strict inequality constraint~\eqref{co:strict_inequality}, conditions \eqref{eq:dual_feasibility} and \eqref{eq:complementary_slackness} together imply $\mu_s^\star = 0$, $\forall s \in \mathcal{S}$.
+For \gls{dmtc} based on energy detection~\eqref{eq:energy_distribution}, it is trivial to conclude $t_0^\star = 0$ and $t_S^\star = \infty$.
+Hence, we focus on $s' \in \mathcal{S} \setminus \{S\}$ and \eqref{eq:kkt_thresholding} reduces to
 				\begin{equation}
-					\nabla_{t_s^{\star}} I^{\star}_{\mathrm{B}}(c_{\mathcal{K}};z) = 0.
+					\nabla_{t_{s'}^\star} I^\star_{\mathrm{B}}(c_{\mathcal{K}};z) = 0,
 				\end{equation}
+				that is, for $j \in \mathcal{L}$ and $j \equiv s' \pmod L$,
+				\begin{equation}
+					\sum_l a_{l,j} f(t_{s'}^\star \mid x_l) = 0,
+					\label{eq:kkt_thresholding_explicit}
+				\end{equation}
+				where
+				\begin{equation}
+					a_{l,j} =
+					\begin{cases}
+						P(x_l) \log \frac{P(x_l \mid z_{j+1}^\star)}{P(x_l \mid z_j^\star)}, & j \in \mathcal{L} \setminus \{L\},\\
+						P(x_l) \log \frac{P(x_l \mid z_{1}^\star)}{P(x_l \mid z_j^\star)}, & j = L.
+					\end{cases}
+				\end{equation}
+
+				Since the optimal backward channel quantizer is convex and separates each pair of posterior distribution by a hyperplane~\cite{Nguyen2020a}, the sequence $(a_{l,j})_{l=1}^{L}$ only change sign once for a given $j$.
+Besides, we notice the LHS of~\eqref{eq:kkt_thresholding_explicit} is a generalized Dirichlet polynomial, as $f(t_{s'}^\star \mid x_l)$ follows Erlang distribution~\eqref{eq:energy_distribution}.
+By Descartes' rule of signs~\cite{Jameson2006}, for each $j \in \mathcal{L}$, $t_s^\star$ has at most 1 real solution if $\sigma_l^2 \ne \sigma_{l'}^2$, $l,l' \in \mathcal{L}$.
+
+				% if $\sigma_l^2 \ne \sigma_{l'}^2$, $l,l' \in \mathcal{L}$, then $t_s^\star$ has at most 1 real solution.
+
+				% for a given $j$, $t_s^\star$ has at most 1 real solution if $\sigma_l^2 \ne \sigma_{l'}^2$, $l,l' \in \mathcal{L}$.
+
+				% Therefore,
+
+				% it can be concluded that for a given $j$, the sequence $(a_{l,j})_{l=1}^{L}$ only change sign once. Plugging~\eqref{eq:energy_distribution} into~\eqref{eq:kkt_thresholding_explicit}, we have
+				% \begin{equation}
+				% 	\sum_l a_{l,j} e^{-{t_s^\star}/{\sigma_l^2}} = 0,
+				% 	\label{eq:optimal_thresholding_condition}
+				% \end{equation}
+				% where the LHS is a generalized Dirichlet polynomial.
+By Descartes' rule of signs~\cite{Jameson2006}, for a given $j$, $t_s^\star$ has at most 1 real solution if $\sigma_l^2 \ne \sigma_{l'}^2$, $l,l' \in \mathcal{L}$.
+
+				% he number of positive roots is at most the number of sign changes in the sequence of polynomial's coefficients
+				% and by Descartes' rule of signs has at most $L-1$ distinct real roots if $\sigma_i^2 \ne \sigma_j^2$, $i,j \in \mathcal{L}$.
+
+				% % As proved by~\cite{Nguyen2020a}, the optimal backward channel quantizer
+				% % \begin{equation}
+				% % 	\sum_l P(x_l) \log \frac{P(z_j)}{P(z_{j+1})} \frac{P(z_{j+1} \mid x_l)}{P(z_j \mid x_l)} f(t_s^\star \mid x_l) = 0,
+				% % \end{equation}
+				% where $j \equiv s \pmod L$. Since the
+				% % We notice that for a given $j$, $a_l \triangleq P(x_l) \log \frac{P(z_j)}{P(z_{j+1})} \frac{P(z_{j+1} \mid x_l)}{P(z_j \mid x_l)}$ is a constant for all $s \equiv j \pmod L$.
+Plugging~\eqref{eq:energy_distribution} into \eqref{eq:kkt_thresholding_explicit}, we have
+				% \begin{equation}
+				% 	\sum_l a_{l,j} e^{-{h_s}/{\sigma_l^2}} = 0,
+				% 	\label{eq:optimal_thresholding_condition}
+				% \end{equation}
+				% where the LHS is a Dirichlet polynomial and by Descartes' rule of signs has at most $L-1$ distinct real roots if $\sigma_i^2 \ne \sigma_j^2$, $i,j \in \mathcal{L}$.
+				% % where the directional derivative can be explicitly written as
+				% % \begin{subequations}
+				% % 	\begin{align}
+				% % 		\nabla_{t_{s'}^\star} I^\star_{\mathrm{B}}(c_{\mathcal{K}};z)
+				% % 		& = \sum_l P(x_l) \log \frac{P(z_j)}{P(z_{j+1})} \frac{P(z_{j+1} \mid x_l)}{P(z_j \mid x_l)} f(h_s \mid x_l)\\
+				% % 		& = 1
+				% % 	\end{align}
+				% % \end{subequations}
 			\end{proof}
@@
 			\begin{proposition}
-				The necessary and sufficient conditions for an input probability distribution $\boldsymbol{P}^{\star}$ to maximize the weighted sum primary-backscatter rate are that, $\forall m_k \in \mathcal{M}$ and $\forall k \in \mathcal{K}$,
+				The necessary and sufficient conditions for an input probability distribution $\boldsymbol{P}^\star$ to maximize the weighted sum primary-backscatter rate are that, $\forall m_k \in \mathcal{M}$ and $\forall k \in \mathcal{K}$,
 				\begin{subequations}
@@
 					\begin{alignat}{2}
-						I_k^{\star}(\bar{c}_{m_k};\boldsymbol{y},z) & = I^{\star}(c_{\mathcal{K}};\boldsymbol{y},z), \quad && P_k^{\star}(\bar{c}_{m_k}) > 0,\label{eq:probable_states}\\
-						I_k^{\star}(\bar{c}_{m_k};\boldsymbol{y},z) & \le I^{\star}(c_{\mathcal{K}};\boldsymbol{y},z), \quad && P_k^{\star}(\bar{c}_{m_k}) = 0.\label{eq:dropped_states}
+						I_k^\star(\bar{c}_{m_k};\boldsymbol{y},z) & = I^\star(c_{\mathcal{K}};\boldsymbol{y},z), \quad && P_k^\star(\bar{c}_{m_k}) > 0,\label{eq:probable_states}\\
+						I_k^\star(\bar{c}_{m_k};\boldsymbol{y},z) & \le I^\star(c_{\mathcal{K}};\boldsymbol{y},z), \quad && P_k^\star(\bar{c}_{m_k}) = 0.\label{eq:dropped_states}
 					\end{alignat}
@@
 					\begin{equation}
-						- \nabla_{P_k^{\star}(\bar{c}_{m_k})} I^{\star}(c_{\mathcal{K}};\boldsymbol{y},z) + \nu_k^{\star} - \lambda_{k,m_k}^{\star} = 0,
+						- \nabla_{P_k^\star(\bar{c}_{m_k})} I^\star(c_{\mathcal{K}};\boldsymbol{y},z) + \nu_k^\star - \lambda_{k,m_k}^\star = 0,
 					\end{equation}
 					\begin{equation}
-						\lambda_{k,m_k}^{\star} = 0, \quad P_k^{\star}(\bar{c}_{m_k}) > 0,
+						\lambda_{k,m_k}^\star = 0, \quad P_k^\star(\bar{c}_{m_k}) > 0,
 					\end{equation}
 					\begin{equation}
-						\lambda_{k,m_k}^{\star} \ge 0, \quad P_k^{\star}(\bar{c}_{m_k}) = 0,
+						\lambda_{k,m_k}^\star \ge 0, \quad P_k^\star(\bar{c}_{m_k}) = 0,
 					\end{equation}
@@
 				\begin{equation}
-					\nabla_{P_k^{\star}(\bar{c}_{m_k})} I^{\star}(c_{\mathcal{K}};\boldsymbol{y},z) = I_k^{\star}(\bar{c}_{m_k};\boldsymbol{y},z) - (1 - \rho).
+					\nabla_{P_k^\star(\bar{c}_{m_k})} I^\star(c_{\mathcal{K}};\boldsymbol{y},z) = I_k^\star(\bar{c}_{m_k};\boldsymbol{y},z) - (1 - \rho).
 				\end{equation}
 
-				Due to the necessity and sufficiency of the \gls{kkt} conditions, we conclude that any input probability distribution $\boldsymbol{P}^{\star}$ maximizes the weighted sum primary-backscatter rate if and only if, $\forall m_k \in \mathcal{M}$ and $\forall k \in \mathcal{K}$,
+				Due to the necessity and sufficiency of the \gls{kkt} conditions, we conclude that any input probability distribution $\boldsymbol{P}^\star$ maximizes the weighted sum primary-backscatter rate if and only if, $\forall m_k \in \mathcal{M}$ and $\forall k \in \mathcal{K}$,
 				\begin{subequations}
 					\begin{alignat}{2}
-						I_k^{\star}(\bar{c}_{m_k};\boldsymbol{y},z) & = \nu_k^{\star} + (1 - \rho), \quad && P_k^{\star}(\bar{c}_{m_k}) > 0,\label{eq:probable_states_marginal}\\
-						I_k^{\star}(\bar{c}_{m_k};\boldsymbol{y},z) & \le \nu_k^{\star} + (1 - \rho), \quad && P_k^{\star}(\bar{c}_{m_k}) = 0,\label{eq:dropped_states_marginal}
+						I_k^\star(\bar{c}_{m_k};\boldsymbol{y},z) & = \nu_k^\star + (1 - \rho), \quad && P_k^\star(\bar{c}_{m_k}) > 0,\label{eq:probable_states_marginal}\\
+						I_k^\star(\bar{c}_{m_k};\boldsymbol{y},z) & \le \nu_k^\star + (1 - \rho), \quad && P_k^\star(\bar{c}_{m_k}) = 0,\label{eq:dropped_states_marginal}
 					\end{alignat}
@@
 				\begin{equation}
-					\sum_{m_k} P_k^{\star}(\bar{c}_{m_k}) I_k^{\star}(\bar{c}_{m_k};\boldsymbol{y},z) = \nu_k^{\star} + (1 - \rho).
+					\sum_{m_k} P_k^\star(\bar{c}_{m_k}) I_k^\star(\bar{c}_{m_k};\boldsymbol{y},z) = \nu_k^\star + (1 - \rho).
 				\end{equation}
@@
 				\begin{equation}
-					\sum_{m_k} P_k^{\star}(\bar{c}_{m_k}) I_k^{\star}(\bar{c}_{m_k};\boldsymbol{y},z) = I^{\star}(c_{\mathcal{K}};\boldsymbol{y},z),
+					\sum_{m_k} P_k^\star(\bar{c}_{m_k}) I_k^\star(\bar{c}_{m_k};\boldsymbol{y},z) = I^\star(c_{\mathcal{K}};\boldsymbol{y},z),
 				\end{equation}
-				which is irrelevant to $k$. It suggests $I^{\star}(c_{\mathcal{K}};\boldsymbol{y},z) = \nu_k^{\star} + (1 - \rho)$, $\forall k \in \mathcal{K}$, and completes the proof.
+				which is irrelevant to $k$. It suggests $I^\star(c_{\mathcal{K}};\boldsymbol{y},z) = \nu_k^\star + (1 - \rho)$, $\forall k \in \mathcal{K}$, and completes the proof.
 			\end{proof}
@@
 				\end{figure*}
-				For a fixed $P_{\mathcal{K}}'(\bar{c}_{m_{\mathcal{K}}})$, $J \left( P_{\mathcal{K}}(\bar{c}_{m_{\mathcal{K}}}),P_{\mathcal{K}}'(\bar{c}_{m_{\mathcal{K}}}) \right)$ is a concave function of $P_k(\bar{c}_{m_k})$ and is maximized at $\nabla_{P_k^{\star}(\bar{c}_{m_k})} J \left( P_{\mathcal{K}}(\bar{c}_{m_{\mathcal{K}}}),P_{\mathcal{K}}'(\bar{c}_{m_{\mathcal{K}}}) \right) = 0$, namely
+				For a fixed $P_{\mathcal{K}}'(\bar{c}_{m_{\mathcal{K}}})$, $J \left( P_{\mathcal{K}}(\bar{c}_{m_{\mathcal{K}}}),P_{\mathcal{K}}'(\bar{c}_{m_{\mathcal{K}}}) \right)$ is a concave function of $P_k(\bar{c}_{m_k})$ and is maximized at $\nabla_{P_k^\star(\bar{c}_{m_k})} J \left( P_{\mathcal{K}}(\bar{c}_{m_{\mathcal{K}}}),P_{\mathcal{K}}'(\bar{c}_{m_{\mathcal{K}}}) \right) = 0$, namely
 				\begin{equation}
-					S_k'(\bar{c}_{m_k}) - S_k'(\bar{c}_{i_k}) + (1 - \rho) \log \frac{P_k(\bar{c}_{i_k})}{P_k^{\star}(\bar{c}_{m_k})} = 0,
+					S_k'(\bar{c}_{m_k}) - S_k'(\bar{c}_{i_k}) + (1 - \rho) \log \frac{P_k(\bar{c}_{i_k})}{P_k^\star(\bar{c}_{m_k})} = 0,
 					\label{eq:optimal_intermediate_information_condition}
@@
 				% 	\begin{align}
-				% 		P_k^{\star}(\bar{c}_{m_k})
+				% 		P_k^\star(\bar{c}_{m_k})
 				% 		& = \frac{\exp \left( \frac{1}{1 - \rho} S_k'(\bar{c}_{m_k}) \right)}{\sum_{m_k'} \exp \left( \frac{1}{1 - \rho} S_k'(\bar{c}_{m_k'}) \right)}\\
@@
 					\begin{align}
-						P_k^{\star}(\bar{c}_{m_k})
+						P_k^\star(\bar{c}_{m_k})
 						& = \frac{\exp \left( \frac{1}{1 - \rho} S_k'(\bar{c}_{m_k}) \right)}{\sum_{m_k'} \exp \left( \frac{1}{1 - \rho} S_k'(\bar{c}_{m_k'}) \right)}\\
@@
 				where we define $u_k'(\bar{c}_{m_k}) \triangleq \exp \left( \frac{\rho}{1 - \rho} I_k'(\bar{c}_{m_k};\boldsymbol{y},z) \right)$.
-Although $P_k(\bar{c}_{i_k}) = 1 - \sum_{m_k \ne i_k} P_k^{\star}(\bar{c}_{m_k})$ is not guaranteed to be optimal, it has exactly the same form as \eqref{eq:optimal_relative_distribution}.
+Although $P_k(\bar{c}_{i_k}) = 1 - \sum_{m_k \ne i_k} P_k^\star(\bar{c}_{m_k})$ is not guaranteed to be optimal, it has exactly the same form as \eqref{eq:optimal_relative_distribution}.
 In such case, the solution of choosing $i_k$ as reference would coincide with that of choosing any $m_k \ne i_k$ as reference, while optimality for $i_k$ is guaranteed in the latter case.
@@
 
-				We then prove any converging point of sequence \eqref{eq:optimal_distribution}, denoted as $P_k^{\star}(\bar{c}_{m_k})$, fulfills the optimal conditions \eqref{eq:optimal_conditions} and achieves the weighted primary-backscatter sum capacity.
+				We then prove any converging point of sequence \eqref{eq:optimal_distribution}, denoted as $P_k^\star(\bar{c}_{m_k})$, fulfills the optimal conditions \eqref{eq:optimal_conditions} and achieves the weighted primary-backscatter sum capacity.
 To see this, define
@@
 				where $P_k^{(0)}(\bar{c}_{m_k}) > 0$.
-As sequence \eqref{eq:optimal_distribution} is convergent, any state with $P_k^{\star}(\bar{c}_{m_k}) > 0$ need to satisfy $D_k^{\star}(\bar{c}_{m_k}) \triangleq \lim_{r \to \infty} D_k^{(r)}(\bar{c}_{m_k}) = 1$, namely
+As sequence \eqref{eq:optimal_distribution} is convergent, any state with $P_k^\star(\bar{c}_{m_k}) > 0$ need to satisfy $D_k^\star(\bar{c}_{m_k}) \triangleq \lim_{r \to \infty} D_k^{(r)}(\bar{c}_{m_k}) = 1$, namely
 				\begin{equation}
-					I_k^{\star}(\bar{c}_{m_k};\boldsymbol{y},z) = \frac{1 - \rho}{\rho} \log \sum_{m_k'} P_k^{\star}(\bar{c}_{m_k'}) u_k^{\star}(\bar{c}_{m_k'}),
+					I_k^\star(\bar{c}_{m_k};\boldsymbol{y},z) = \frac{1 - \rho}{\rho} \log \sum_{m_k'} P_k^\star(\bar{c}_{m_k'}) u_k^\star(\bar{c}_{m_k'}),
 				\end{equation}
 				which coincides with \eqref{eq:probable_states_marginal} and implies \eqref{eq:probable_states}.
-That is, given $P_k^{(0)}(\bar{c}_{m_k}) > 0$, any converging point with $P_k^{\star}(\bar{c}_{m_k}) > 0$ must satisfy \eqref{eq:probable_states}.
-				On the other hand, we assume $P_k^{\star}(\bar{c}_{m_k})$ does not satisfy \eqref{eq:dropped_states}, such that for any state with $P_k^{\star}(\bar{c}_{m_k}) = 0$,
-				% On the other hand, we show if $P_k^{\star}(\bar{c}_{m_k})$ does not satisfy \eqref{eq:dropped_states}, then it is not a converging point of sequence \eqref{eq:optimal_distribution}.
-By this assumption, for any state with $P_k^{\star}(\bar{c}_{m_k}) = 0$,
+That is, given $P_k^{(0)}(\bar{c}_{m_k}) > 0$, any converging point with $P_k^\star(\bar{c}_{m_k}) > 0$ must satisfy \eqref{eq:probable_states}.
+				On the other hand, we assume $P_k^\star(\bar{c}_{m_k})$ does not satisfy \eqref{eq:dropped_states}, such that for any state with $P_k^\star(\bar{c}_{m_k}) = 0$,
+				% On the other hand, we show if $P_k^\star(\bar{c}_{m_k})$ does not satisfy \eqref{eq:dropped_states}, then it is not a converging point of sequence \eqref{eq:optimal_distribution}.
+By this assumption, for any state with $P_k^\star(\bar{c}_{m_k}) = 0$,
 				\begin{equation}
-					I_k^{\star}(\bar{c}_{m_k};\boldsymbol{y},z) > I^{\star}(c_{\mathcal{K}};\boldsymbol{y},z) = \sum_{m_k'} P_k^{\star}(\bar{c}_{m_k'}) I_k^{\star}(\bar{c}_{m_k'};\boldsymbol{y},z),
+					I_k^\star(\bar{c}_{m_k};\boldsymbol{y},z) > I^\star(c_{\mathcal{K}};\boldsymbol{y},z) = \sum_{m_k'} P_k^\star(\bar{c}_{m_k'}) I_k^\star(\bar{c}_{m_k'};\boldsymbol{y},z),
 				\end{equation}
 				where the equality origins from \eqref{eq:backscatter_sum_rate_expectation} and \eqref{eq:primary_ergodic_rate_expectation}.
-Since the exponential function is monotonically increasing, we have $u_k^{\star}(\bar{c}_{m_k}) > \sum_{m_k'} P_k^{\star}(\bar{c}_{m_k'}) u_k^{\star}(\bar{c}_{m_k'})$ and $D_k^{\star}(\bar{c}_{m_k}) > 1$.
-Considering $P_k^{(0)}(\bar{c}_{m_k}) > 0$ and $P_k^{\star}(\bar{c}_{m_k}) = 0$, it contradicts with
+Since the exponential function is monotonically increasing, we have $u_k^\star(\bar{c}_{m_k}) > \sum_{m_k'} P_k^\star(\bar{c}_{m_k'}) u_k^\star(\bar{c}_{m_k'})$ and $D_k^\star(\bar{c}_{m_k}) > 1$.
+Considering $P_k^{(0)}(\bar{c}_{m_k}) > 0$ and $P_k^\star(\bar{c}_{m_k}) = 0$, it contradicts with
 				\begin{equation}
@@
 				\end{equation}
-				Therefore, given $P_k^{(0)}(\bar{c}_{m_k}) > 0$, any converging point with $P_k^{\star}(\bar{c}_{m_k}) = 0$ must satisfy \eqref{eq:dropped_states}.
+				Therefore, given $P_k^{(0)}(\bar{c}_{m_k}) > 0$, any converging point with $P_k^\star(\bar{c}_{m_k}) = 0$ must satisfy \eqref{eq:dropped_states}.
 

### 2022-01-26 main.tex
:pencil: Update thresholding proof

@@
 			\begin{theorem}
-				If any $L$-input continuous-output channel follows Erlang distribution~\eqref{eq:energy_distribution}, then the optimal number of thresholds is $L+1$ and the capacity-achieving decision region $j$ has convex structure $\mathcal{R}_j^\star = [t_{j-1}^\star, t_j^\star)$.
+				For any $L$-input continuous-output channel with Erlang distribution~\eqref{eq:energy_distribution}, the number of thresholds required to achieve the \gls{dmtc} capacity is $L+1$ and the optimal decision region $j \in \mathcal{L} \triangleq \{1,\ldots,L\}$ has a convex structure $\mathcal{R}_j^\star = [t_{j-1}^\star, t_j^\star)$.
 			\end{theorem}
@@
 			\begin{proof}
-				For any finite number of thresholds $S \ge L+1$, let $\boldsymbol{t} \triangleq [t_0,\ldots,t_S]^T \in \mathbb{R}_{+}^{S \times 1}$ be the thresholding vector where $t_{s-1} < t_s$, $\forall s \in \mathcal{S} \triangleq \{1,\ldots,S\}$.\footnote{We consider strict inequality in the definition, as otherwise $S$ and $\boldsymbol{t}$ could be non-unique for a given thresholding scheme.} Denote the decision partition $s$ as $R_s \triangleq [t_{s-1},t_s)$.
-Without loss of generality, we assume
-				% $L \mid S$ and
-				$\mathcal{R}_j = \bigcup_{s \equiv j \pmod L} R_s$.\footnote{The proof holds for general mapping $R_s \mapsto \mathcal{R}_j$, and we focus on this specific case for the ease of notation.} The thresholding design problem can be expressed as
+				Assume the optimal number of thresholds is $S+1$.
+Since $x \to z \to \bar{z}$ formulates a Markov chain, we need at least $L+1$ thresholds to construct $L$ valid detection regions and minimize the distortion between $x$ and $\bar{z}$.
+It suggests $S \ge L$.
+Let $\boldsymbol{t} \triangleq [t_0,\ldots,t_S]^T \in \mathbb{R}_{+}^{(S+1) \times 1}$ be the optimal thresholding vector where $t_{s-1} < t_s$, $\forall s \in \mathcal{S} \triangleq \{1,\ldots,S\}$.\footnote{We consider strict inequality in the definition, as otherwise $S$ and $\boldsymbol{t}$ could be non-unique for a given thresholding scheme.} Denote the decision partition $s$ as $R_s \triangleq [t_{s-1},t_s)$.
+Without loss of generality, we assume $\mathcal{R}_j = \bigcup_{s \equiv j \pmod L} R_s$.\footnote{The proof holds for general mapping $R_s \mapsto \mathcal{R}_j$, and we focus on this specific case for the ease of notation.} The thresholding design problem can be expressed as
 				\begin{maxi!}
@@
 					L(\boldsymbol{t},\boldsymbol{\mu}) = - I_{\mathrm{B}}(c_{\mathcal{K}};z) + \sum_{s \in \mathcal{S}} \mu_s (t_{s-1} - t_s),
-					% = \sum_{j \in \mathcal{L}} P(\bar{z}_j) \log P(\bar{z}_j) - \sum_{i \in \mathcal{L}} \sum_{j \in \mathcal{L}}
 				\end{equation}
 				where $\mu_s$ is the Lagrange multiplier associated with the non-strict version of \eqref{co:strict_inequality} and $\boldsymbol{\mu} \triangleq [\mu_1,\ldots,\mu_S]^T \in \mathbb{R}^{S \times 1}$.
-The corresponding \gls{kkt} conditions on the optimal primal and dual solutions are, $\forall s \in \mathcal{S}$,
+The \gls{kkt} conditions on the optimal primal and dual solutions are, $\forall s \in \mathcal{S}$,
 				\begin{subequations}
@@
 				\end{subequations}
+				% For \gls{dmtc} based on energy detection~\eqref{eq:energy_distribution}, it is trivial to conclude $t_0^\star = 0$ and $t_S^\star = \infty$.
 				Due to the strict inequality constraint~\eqref{co:strict_inequality}, conditions \eqref{eq:dual_feasibility} and \eqref{eq:complementary_slackness} together imply $\mu_s^\star = 0$, $\forall s \in \mathcal{S}$.
-For \gls{dmtc} based on energy detection~\eqref{eq:energy_distribution}, it is trivial to conclude $t_0^\star = 0$ and $t_S^\star = \infty$.
-Hence, we focus on $s' \in \mathcal{S} \setminus \{S\}$ and \eqref{eq:kkt_thresholding} reduces to
+Besides, it is trivial to conclude $t_0^\star = 0$ for our \gls{dmtc} based on energy detection.
+As such, the necessary optimality condition for $t_s^\star$, $s \in \mathcal{S}$ is
 				\begin{equation}
-					\nabla_{t_{s'}^\star} I^\star_{\mathrm{B}}(c_{\mathcal{K}};z) = 0,
+					\nabla_{t_{s}^\star} I^\star_{\mathrm{B}}(c_{\mathcal{K}};z) = 0,
 				\end{equation}
-				that is, for $j \in \mathcal{L}$ and $j \equiv s' \pmod L$,
+				namely
 				\begin{equation}
-					\sum_l a_{l,j} f(t_{s'}^\star \mid x_l) = 0,
+					\sum_l a_{l,j} f(t_{s}^\star \mid x_l) = 0,
 					\label{eq:kkt_thresholding_explicit}
 				\end{equation}
-				where
+				where $j \equiv s \pmod L$, $j \in \mathcal{L}$ and
 				\begin{equation}
-					a_{l,j} =
+					a_{l,j} \triangleq
 					\begin{cases}
@@
 
-				Since the optimal backward channel quantizer is convex and separates each pair of posterior distribution by a hyperplane~\cite{Nguyen2020a}, the sequence $(a_{l,j})_{l=1}^{L}$ only change sign once for a given $j$.
-Besides, we notice the LHS of~\eqref{eq:kkt_thresholding_explicit} is a generalized Dirichlet polynomial, as $f(t_{s'}^\star \mid x_l)$ follows Erlang distribution~\eqref{eq:energy_distribution}.
-By Descartes' rule of signs~\cite{Jameson2006}, for each $j \in \mathcal{L}$, $t_s^\star$ has at most 1 real solution if $\sigma_l^2 \ne \sigma_{l'}^2$, $l,l' \in \mathcal{L}$.
+				Since the optimal backward channel quantizer is convex and separates each pair of posterior distribution by a hyperplane~\cite{Nguyen2020a}, for a given $j$, the sequence $(a_{l,j})_{l=1}^{L}$ only change sign once.
+As $f(t_{s}^\star \mid x_l)$ follows Erlang distribution~\eqref{eq:energy_distribution}, the LHS of~\eqref{eq:kkt_thresholding_explicit} is a generalized Dirichlet polynomial and has at most one real solution by Descartes' rule of signs~\cite{Jameson2006}.
+In other words, each decision region $j \in \mathcal{L}$ requires at most one additional threshold, and therefore $S \le L$.
+This suggests $S = L$ completes the proof.
+
+				% . By Descartes' rule of signs~\cite{Jameson2006}, for each $j \in \mathcal{L}$, $t_s^\star$ has at most 1 real solution if $\sigma_l^2 \ne \sigma_{l'}^2$, $\forall l,l' \in \mathcal{L}$.
+
+				% In other words, based on $t_0^\star = 0$, each decision region $j \in \mathcal{L}$ requires at most one additional threshold, such that $S \le L+1$.
+				% $s \equiv j \pmod L$
 

### 2022-04-04 main.tex
:pencil: Update manuscript

--- 2022-01-24 main.tex
@@
 \usepackage{environ}
+\usepackage{fixmath}
 \usepackage{grffile}
@@
 \usepackage{pgffor}
+\usepackage{pgfgantt}
 \usepackage{pgfplots}
@@
 \usepackage{stfloats}
+\usepackage{tcolorbox}
 \usepackage{tikz}
@@
 \usepackage{xcolor}
+\usepackage[T1]{fontenc}
 \usepackage[acronym]{glossaries-extra}
-\usepackage[T1]{fontenc}
 \usepackage[caption=false,font=footnotesize,subrefformat=parens,labelformat=parens]{subfig}
 \usepackage[short]{optidef}
-% \usepackage[subtle]{savetrees}
-% \usepackage{stmaryrd}
+\usepackage[subtle]{savetrees}
 
@@
 \newcommand{\infdiv}{D\infdivx}
+\renewcommand{\qedsymbol}{\hfill\ensuremath{\Box}}
 
@@
 
+\newacronym{af}{AF}{Amplify-and-Forward}
 \newacronym{ambc}{AmBC}{Ambient Backscatter Communications}
@@
 \newacronym{csi}{CSI}{Channel State Information}
+\newacronym{df}{DF}{Decode-and-Forward}
 \newacronym{dmc}{DMC}{Discrete Memoryless Channel}
 \newacronym{dmtc}{DMTC}{Discrete Memoryless Thresholding Channel}
+\newacronym{dmtmac}{DMTMAC}{Discrete Memoryless Thresholding Multiple Access Channel}
+\newacronym{dp}{DP}{Dynamic Programming}
+\newacronym{iid}{i.i.d.}{independent and identically distributed}
 \newacronym{irs}{IRS}{Intelligent Reflecting Surface}
@@
 \newacronym{mc}{MC}{Multiplication Coding}
+\newacronym{miso}{MISO}{Multiple-Input Single-Output}
+\newacronym{mimo}{MIMO}{Multiple-Input Multiple-Output}
 \newacronym{ml}{ML}{Maximum-Likelihood}
+\newacronym{noma}{NOMA}{Non-Orthogonal Multiple Access}
+\newacronym{ofdm}{OFDM}{Orthogonal Frequency-Division Multiplexing}
+\newacronym{pdf}{PDF}{Probability Density Function}
 \newacronym{psk}{PSK}{Phase Shift Keying}
+\newacronym{pin}{PIN}{Positive Intrinsic-Negative}
 \newacronym{qam}{QAM}{Quadrature Amplitude Modulation}
@@
 \newacronym{sic}{SIC}{Successive Interference Cancellation}
+\newacronym{simo}{SIMO}{Single-Input Multiple-Output}
+\newacronym{sinr}{SINR}{Signal-to-Interference-plus-Noise Ratio}
+\newacronym{smawk}{SMAWK}{Shor-Moran-Aggarwal-Wilber-Klawe}
 \newacronym{sr}{SR}{Symbiotic Radio}
+\newacronym{tdma}{TDMA}{Time-Division Multiple Access}
 \newacronym{tg}{TG}{tag}
@@
 \begin{document}
-	\title{Backscatter Modulation Design for Symbiotic Radio Networks}
+\title{Metascatter: Unifying Symbiotic Radio and Intelligent Reflecting Surface}
+\author{
+	\IEEEauthorblockN{
+		Yang~Zhao,~\IEEEmembership{Member,~IEEE,}
+		and~Bruno~Clerckx,~\IEEEmembership{Senior~Member,~IEEE}
+	}
+	\thanks{
+		The authors are with the Department of Electrical and Electronic Engineering, Imperial College London, London SW7 2AZ, U.K. (e-mail: \{yang.zhao18, b.clerckx\}@imperial.ac.uk).
+	}
+}
 \maketitle
 
-	\begin{section}{Backscatter Model}
-		\begin{subsection}{Backscatter Principles}
+\begin{section}{Introduction}
+	\IEEEPARstart{B}{ackscatter} is recently re-innovated as a promising approach to support low-power communications and control wireless propagation environments.
+	The concept of \gls{ambc} was first proposed in \cite{Liu2013b}, where each tag harvests energy from and modulates information over ambient \gls{rf} signals by periodically switching between different reflection patterns.
+	It enables battery-free communication between fully passive nodes, but the backscatter signal strength can be relatively weak and the decoding is subject to strong direct-link interference.
+	To solve this, \cite{Yang2018d} exploited the repeating structure of \gls{ofdm} symbol for interference cancellation based on backscatter channel strength.
+	Cooperative primary-backscatter decoding using co-located receiver, known as cooperative \gls{ambc}, was proposed in \cite{Yang2018}.
+	The authors evaluated the error performance of \gls{ml}, linear, and \gls{sic} detectors for flat fading channels, and proposed a low-complexity \gls{ml} detector for frequency-selective fading channels with ambient \gls{ofdm} carrier.
+	When transmit cooperation is also available, cooperative \gls{ambc} is more commonly known as \gls{sr} \cite{Liang2020}.
+	The authors of \cite{Guo2019b} classified \gls{sr} into commensal, parasitic, and competitive modes based on the relative link priority, then derived their instantaneous achievable rate and optimal power allocation.
+	The outage probability for those modes was later studied in \cite{Ding2020}.
+	On the other hand, it was concluded in \cite{Long2020a} that if the backscatter symbol period is much longer than the primary symbol period, then the non-coherent achievable rate of primary decoding would approach that of the coherent case.
+	The authors also considered the transmit precoder design for weighted sum-rate maximization and transmit power minimization problems.
+	\cite{Zhou2019a} explored how the number of transmit antennas, receive antennas, and symbol period ratio asymptotically influence the ergodic rate of primary and backscatter links.
+	With multi-antenna at all ends, \cite{Wu2021a} optimized the transmit precoder to maximize the backscatter achievable rate under primary rate constraint.
+	However, those paper only considered single tag scenario and the optimal tag multiple access scheme remains unknown.
+	\cite{Xu2021a} proposed a \gls{noma}-based \gls{sr} and studied the receive combiner design when the receiver decodes in the order of equivalent channel strength.
+	A \gls{tdma}-based \gls{sr} with energy harvesting constraints was also presented in \cite{Yang2021a}, and energy efficiency maximization was considered with respect to transmit power, reflection efficiency, and time allocation design.
+	In \cite{Han2021}, random code-assisted backscatter multiple access was combined with \gls{sr}, and the authors evaluated the asymptotic \gls{sinr} performance using random matrix theory.
+
+	On the other hand, \gls{irs} has recently emerged as a promising technique to enhance the energy efficiency.
+	In practice, an \gls{irs} consists of multiple individual sub-wavelength reflecting elements to adjust the amplitude and phase of the incoming signal (i.e., passive beamforming).
+	Different from relay, backscatter and frequency-selective surface \cite{Anwar2018}, \gls{irs} assists the primary transmission using passive components with much lower energy consumption and thermal noise, but is limited to frequency-dependent reflection.
+	\cite{Wu2018} proposed an \gls{irs}-assisted \gls{miso} system and jointly optimized the precoder and the phase shifts to minimize the transmit power.
+	The active and passive beamforming problem was then extended to the discrete phase shift case \cite{Wu2019a} and the multi-user case \cite{Wu2019}.
+	In \cite{Abeywickrama2020}, the authors investigated the impact of non-zero resistance on the reflection pattern and emphasized the coupling between reflection amplitude and phase shift in practice.
+	To estimate the cascaded link without \gls{rf}-chains at the \gls{irs}, practical protocols were developed based on element-wise on/off switching \cite{Nadeem2019}, training sequence and reflection pattern design \cite{You2019,Kang2020}, and compressed sensing \cite{Wang2020}.
+	\gls{irs} was also added to single-tag and multi-tag \gls{sr} systems to improve backscatter efficiency \cite{Chen2021,Zhang2021d}.
+	Recently, the idea of \gls{irs}-empowered \gls{sr} was proposed in \cite{Xu2020b,Hua2022}, where the reflection pattern can be decoupled as the multiplication of whole phase shift matrix and one backscatter symbol.
+	The idea was combined with spatial modulation to divide the \gls{irs} into reflection and information and elements, and the error performance of non-coherent backscatter detection was studied accordingly \cite{Hu2021a}.
+
+	To the best of our knowledge, most existing \gls{sr} systems \cite{Yang2018,Guo2019b,Ding2020,Long2020a,Zhou2019a,Wu2021a,Xu2021a} assumed Gaussian codebook at the tags and employed \gls{sic} from primary to backscatter link.
+	It thus requires non-coherent primary encoding at the transmitter and involves re-encoding, precoding, and subtraction operations that may not be available to legacy receivers.
+	Besides, the primary and backscatter symbols in \gls{sr} are mixed by multiplication coding instead of superposition coding, and the backscatter symbol period can be much longer than the primary symbol period due to physical constraints.
+	Inspired by above, we propose a novel Metascatter network where multiple battery-free tags ride over a conventional point-to-point system and adapt their input probability distribution to simultaneously act as backscatter tags of \gls{sr} and reflecting elements of \gls{irs}.
+	To fully utilize the reflection pattern and signal structure, we also present a novel decoding strategy with minor modifications on existing receivers.
+	The contributions of this paper is summarized as follows.
+
+	\emph{First,} Metascatter adapts the input probability distribution of a finite-state backscatter device based on the primary and backscatter \gls{csi}.
+	It generalizes the backscatter tags of \gls{sr} and reflecting elements of \gls{irs} to improve the primary-backscatter tradeoff in a flexible manner.
+	When the primary link is absolutely prioritized, the tag input probability boils down to \num{1} at the state that maximizes the equivalent channel strength and \num{0} at other states, which is essentially the phase shift selection of an \gls{irs} element.
+	When we only care about the backscatter performance, the network boils down to a multi-tag \gls{ambc} and the input design can be simplified accordingly.
+
+	\emph{Second,} we propose a novel receiving strategy where the backscatter symbol of all tags are first recovered by energy-based decoding, then modeled within equivalent \gls{csi} for primary decoding.
+	When the ratio of backscatter symbol period over primary symbol period is large enough, the randomness of primary source can be averaged out and the performance of non-coherent backscatter decoding can be greatly improved.
+	Since the primary and backscatter symbols are mixed by multiplication coding, the backscatter decoding can be viewed as part of primary channel training, which avoids non-coherent encoding at the transmitter and \gls{sic} at the receiver.
+
+	\emph{Third,} we characterize the achievable primary-(sum-)backscatter rate region by iteratively optimizing the tag input distribution, the backscatter decision threshold, and the transmit precoder.
+	For the input design, we propose a numerical method to evaluate the \gls{kkt} solutions by limits of sequences.
+	For the threshold design, we derive the minimum number of decision thresholds to maximize the total backscatter rate, and obtain the optimal thresholds by \gls{dp} accelerated by \gls{smawk} algorithm.
+	However, the optimal precoder design can be non-trivial and we may end up with a low-complexity suboptimal solution.
+
+\end{section}
+
+\begin{section}{Backscatter Principles}
 	\begin{figure}[!t]
 		\centering
-				\subfloat[Block diagram of a passive tag]{
+		\subfloat[Passive tag structure]{
 			\resizebox{0.6\columnwidth}{!}{
@@
 					\draw (0,1.75)
-								to[short] ++(-1,0)
-								to[short] ++(0,0.75) node[bareantenna](A){Ant};
+					to[short] ++(-0.875,0)
+					to[short] ++(0,0.5) node[bareantenna](A){Bx};
 					\draw (0,1.75)
@@
 			}
-					\label{fi:block_diagram_of_a_passive_tag}
+			\label{fi:passive_tag_structure}
 		}
-				\subfloat[Backscatter modualtion]{
+		\subfloat[Equivalent model]{
 			\resizebox{0.35\columnwidth}{!}{
@@
 					\draw (bareantenna.east) ++(0.875,0) node[waves](WR){};
-							\draw (WR.north east) ++(0.25,0) node[font=\Large]{$\vec{E}_m$};
-							\draw (WR.south east) ++(0.25,0) node[font=\Large]{$\vec{H}_m$};
+					\draw (WR.north east) ++(0.35,0) node[font=\Large]{$\vec{E}_m$};
+					\draw (WR.south east) ++(0.35,0) node[font=\Large]{$\vec{H}_m$};
 					\draw (bareantenna)
-								to [R=$Z_{\mathrm{A}}$,font=\Large,/tikz/circuitikz/bipoles/length=1cm] ++(0,-2)
+					to [R=$Z_{\mathrm{A}}$,font=\Large,/tikz/circuitikz/bipoles/length=1cm] ++(0,-1.5) node[rotary switch=4 in 90 wiper 30,anchor=ext center,rotate=270](SW){};
+					\draw (SW.cout 2) node[below=0.1cm,font=\Large]{$m$}
 					to [R=$Z_m$,font=\Large,/tikz/circuitikz/bipoles/length=1cm] ++(2,0) node[ground]{};
@@
 			}
-					\label{fi:backscatter_modualtion}
+			\label{fi:equivalent_model}
 		}
@@
 	\end{figure}
-			A bistatic backscatter system consists of an excitation source, multiple (semi-)passive tags, and a backscatter reader.
-When illuminated, the tags simultaneously harvest energy, backscatter message, and demodulate the source signal if necessary.
-Fig.~\subref*{fi:block_diagram_of_a_passive_tag} shows a typical passive with a scattering antenna, an energy harvester, an integrated receiver\footnote{For example, \cite{Kim2021a} prototyped a compact-size pulse position demodulator based on an envelope detector, which brings great potential to coordination, synchronization, and reflection pattern control.}, a load-switching modulator, and on-chip components (e.g., micro-controller, memory, and sensors).
-A portion of the impinging signal is absorbed by the tag while the remaining is backscattered to the space.
-According to Green's decomposition \cite{Hansen1989}, the backscattered signal can be decomposed into the \emph{structural mode} component and the \emph{antenna mode} component.
-The former is fixed and depends on the antenna geometry and material properties\footnote{The structural mode component can be regarded as part of the environment multipath and modeled by channel estimation \cite{Boyer2014}.}, while the latter is adjustable and depends on the mismatch of the antenna and load impedance.
-Fig.~\subref*{fi:backscatter_modualtion} illustrates a simplified circuit and backscatter model at tag state $m$.
-The corresponding reflection coefficient is defined as\footnote{We assume the linear backscatter model where the reflection coefficient is irrelevant to the incident electromagnetic field at the tag \cite{Dobkin2012}.}
+	Consider a bistatic backscatter system with an excitation source, multiple (semi-)passive tags, and a backscatter reader.
+	The structure of a passive tag is shown in Fig. \subref*{fi:passive_tag_structure}.
+	It typically consists of a scattering antenna, an energy harvester, an integrated receiver, a load-switching modulator, and on-chip components (e.g., micro-controller and sensors) \cite{Dobkin2012}.
+	When a tag is illuminated, a portion of the impinging signal is absorbed while the remaining is scattered back, and the tag can harvest energy, transmit message, and decode the source if necessary.
+	According to \cite{Hansen1989}, the backscatter signal can be decomposed into a \emph{structural component} that depends on the antenna geometry and material properties, and an \emph{antenna component} that depends on the antenna-load impedance mismatch.
+	The former contributes to environment multipath and can be modeled by channel estimation \cite{Boyer2014}, while the latter can be utilized for backscatter modulation.
+	As illustrated by Fig. \subref*{fi:equivalent_model}, if $M$ symbol states are available at the tag, the reflection coefficient at state $m \in \mathcal{M} \triangleq \{1,\ldots,M\}$ is
+	\footnote{
+		It corresponds to a linear backscatter model where the reflection coefficient is irrelevant to incident electromagnetic field strength.
+	}
 	\begin{equation}
@@
 	where $Z_m$ is the load impedance at state $m$ and $Z_{\mathrm{A}}$ is the antenna input impedance.
-		\end{subsection}
 
-		\begin{subsection}{Backscatter Modulation}
-			Backscatter modulation is achieved by switching the tag load impedance between different states.
-For an $M$-ary \gls{qam} at state $m \in \mathcal{M} \triangleq \{1,\ldots,M\}$, the reflection coefficient $\Gamma_m$ maps to the signal constellation point $\bar{c}_m$ as \cite{Thomas2012a}
+	Tags periodically switch between different states to perform backscatter modulation.
+	For $M$-ary \gls{qam}, the complex constellation point $c_m \in \mathcal{C}$ maps to the reflection coefficient by \cite{Thomas2012a}
 	\begin{equation}
-				\Gamma_m = \alpha \frac{\bar{c}_m}{\max_{m'} \lvert \bar{c}_{m'} \rvert},
+		\Gamma_m = \alpha \frac{c_m}{\max_{m'} \lvert c_{m'} \rvert},
 		\label{eq:backscatter_modulation}
 	\end{equation}
-			where $\alpha \in [0,1]$ is the reflection efficiency at a given direction.
-For simplicity, we consider an $M$-ary \gls{psk} with constellation set $\mathcal{C} \triangleq \{\bar{c}_1,\ldots,\bar{c}_M\}$, where the $m$-th constellation point is
-			\begin{equation}
-				\bar{c}_m = \exp \left(j \frac{2 \pi m}{M}\right).
-				\label{eq:mpsk}
-			\end{equation}
+	where $\alpha \in [0,1]$ models the (amplitude) harvest-backscatter efficiency at the direction of interest.
+	For passive tags, $\alpha \ll 1$ is commonly assumed as the majority of the incident wave can be harvested to support tag modules \cite{Thomas2012a}.
 
 	\begin{remark}
-				For passive tags, the reflection efficiency $\alpha$ controls the tradeoff between the harvestable power and backscatter strength: $\alpha = 0$ corresponds to maximum power transfer to the tag, while $\alpha = 1$ with $M$-\gls{psk} corresponds to ideal \gls{irs} with $M$ discrete states.
+		By choosing proper load impedance, it is possible to implement any signal constellation or think beyond modulation.
+		For example, perfect matching enables maximum power transfer to the tag, while perfect mismatch leads to complete reflection as desired by ideal \gls{irs}.
+		It inspires Metascatter to design a smart reflection and unify wireless power transfer, backscatter modulation, and passive beamforming.
 	\end{remark}
-		\end{subsection}
 \end{section}
 
-	\begin{section}{Backscatter Detection and Achievable Rates}
+\begin{section}{Metascatter}
 	\begin{subsection}{System Model}
@@
 			\def\svgwidth{0.9\columnwidth}
-				\import{assets/}{symbiotic_radio.eps_tex}
-				\caption{A single-user multi-tag symbiotic radio system.}
-				\label{fi:symbiotic_radio}
+			\import{assets/}{metascatter_system.eps_tex}
+			\caption{The proposed Metascatter system.}
+			\label{fi:metascatter_system}
 		\end{figure}
-			As shown in Fig.~\ref{fi:symbiotic_radio}, we propose a single-\gls{ue} multi-\gls{tg} symbiotic radio network where the \gls{rf} signal generated by the $Q$-antenna \gls{ap} is shared by two coexisting systems.
-In the primary downlink system, the \gls{ap} transmits information to the single-antenna user.
-In the secondary backscatter system, the \gls{ap} acts as the carrier emitter, the $K$ nearby single-antenna tags modulate their information over the reradiated \gls{rf} signals, and the user serves as the multi-tag backscatter reader.
-Denote the \gls{ap}-\gls{ue} direct channel as $\boldsymbol{h}_{\mathrm{D}}^H \in \mathbb{C}^{1 \times Q}$, the \gls{ap}-\gls{tg} $k \in \mathcal{K} \triangleq \{1,\ldots,K\}$ forward channel as $\boldsymbol{h}_{\mathrm{F},k}^H \in \mathbb{C}^{1 \times Q}$, the \gls{tg} $k$-\gls{ue} backward channel as $h_{\mathrm{B},k}$, and the cascaded forward-backward channel of tag $k$ as $\boldsymbol{h}_{\mathrm{C},k}^H \triangleq h_{\mathrm{B},k} \boldsymbol{h}_{\mathrm{F},k}^H \in \mathbb{C}^{1 \times Q}$.
-For simplicity, we consider a quasi-static block fading model where the channel coefficients remain constant within each coherence interval and vary independently over different coherence intervals, and assume the coherence interval $T$ is much longer than the backscatter symbol period $T_c$ and primary symbol period $T_s$.
-We also assume the direct channel and all cascaded channels can be successfully estimated and fed back to the \gls{ap}.\footnote{Due to the lack of \gls{rf} chains at the passive tag, accurate and efficient \gls{csi} acquisition at the \gls{ap} can be challenging.
-One possible approach is that the \gls{ap} sends pre-defined pilots, the tags respond in well-designed manners, and the user performs least-square estimation with feedbacks \cite{Bharadia2015,Yang2015b,Guo2019g}.} Since the tags need to physically switch the loads for backscatter modulation, they communicate at a much longer symbol period (and lower rates) than the primary system.
-As such, we assume the transitions of all tags are perfectly synchronized, and the backscatter symbol period satisfies $T_c = N T_s$ where $N \gg 1$ is a positive integer.
+		As shown in Fig.
+\ref{fi:metascatter_system}, we propose a single-\gls{ue} multi-\gls{tg} symbiotic radio network where the \gls{rf} signal generated by the $Q$-antenna \gls{ap} is shared by two coexisting systems.
+		In the primary point-to-point system, the \gls{ap} transmits information to the single-antenna user.
+		In the secondary backscatter system, the \gls{ap} acts as the carrier emitter, the $K$ nearby single-antenna tags modulate their information over the reradiated \gls{rf} signals, and the user receives and decodes the backscatter messages.
+		Denote the \gls{ap}-\gls{ue} direct channel as $\boldsymbol{h}_{\mathrm{D}}^H \in \mathbb{C}^{1 \times Q}$, the \gls{ap}-\gls{tg} $k \in \mathcal{K} \triangleq \{1,\ldots,K\}$ forward channel as $\boldsymbol{h}_{\mathrm{F},k}^H \in \mathbb{C}^{1 \times Q}$, the \gls{tg} $k$-\gls{ue} backward channel as $h_{\mathrm{B},k}$, and define the cascaded channel of tag $k$ as $\boldsymbol{h}_{\mathrm{C},k}^H \triangleq h_{\mathrm{B},k} \boldsymbol{h}_{\mathrm{F},k}^H \in \mathbb{C}^{1 \times Q}$.
+		For simplicity, we consider a quasi-static block fading model where the channel response remain constant within each coherence interval and vary independently between consecutive blocks.
+		Since backscatter modulation involves load switching, tags typically transmit at much lower rate, and we assume the backscatter symbol period is $N \in \mathbb{Z}_{++}$ times the primary symbol period.
+		We also assume the direct channel and all cascaded channels can be estimated and fed back to the \gls{ap}.
+		\footnote{
+			Due to the lack of \gls{rf} chains at the passive tag, accurate and efficient \gls{csi} acquisition at the \gls{ap} can be challenging.
+			One possible approach is that the \gls{ap} sends pre-defined pilots, the tags respond in well-designed manners, and the user performs least-square estimation with feedbacks \cite{Bharadia2015,Yang2015b,Guo2019g}.
+		}
 
-			Without loss of generality, we focus on the transmissions and detections during one particular backscatter symbol period.
-To provide a preliminary insight, we assume the primary symbol $s[n]$ at block $n \in \mathcal{N} \triangleq \{1,\ldots,N\}$ is in standard \gls{cscg} distribution, and the backscatter symbol $c_k$ of tag $k$ employs $M$-\gls{psk} modulation by \eqref{eq:mpsk}, i.e., $c_k \in \mathcal{C}$, $\forall k \in \mathcal{K}$.
-Thus, the signal received by the user at block $n$ can be expressed as\footnote{We omit the signal reflected by two or more times\cite{Wu2019} and assume the time difference of arrival from different paths are negligible\cite{Guo2019b}.}
+		Consider the signal model during one backscatter symbol period.
+		We assume the primary symbol follows standard \gls{cscg} distribution and the backscatter symbol of all tags employs $M$-\gls{qam}.
+		Under perfect synchronization, the signal received by the user at primary symbol block $n \in \mathcal{N} \triangleq \{1,\ldots,N\}$ is
+		\footnote{
+			We omit the signal reflected by two or more times\cite{Wu2019} and assume the time difference of arrival from different paths are negligible\cite{Guo2019b}.
+		}
 		\begin{equation}
-				y[n] = \left(\boldsymbol{h}_{\mathrm{D}}^H + \sum_{k \in \mathcal{K}} \sqrt{\alpha_k} \boldsymbol{h}_{\mathrm{C},k}^H c_k\right) \boldsymbol{w} s[n] + w[n],
+			y[n] = \left(\boldsymbol{h}_{\mathrm{D}}^H + \sum_{k \in \mathcal{K}} \sqrt{\alpha_k} \boldsymbol{h}_{\mathrm{C},k}^H x_k\right) \boldsymbol{w} s[n] + w[n],
 			\label{eq:received_signal}
 		\end{equation}
-			where $\boldsymbol{w} \in \mathbb{C}^{Q \times 1}$ is the active precoder satisfying $\lVert \boldsymbol{w} \rVert^2 \le P$, $P$ is the average transmit power constraint at the \gls{ap}, and $w[n] \sim \mathcal{CN}(0,\sigma_w^2)$ is the equivalent \gls{awgn} at block $n$.
-Besides, we collect the backscatter symbols of $K$ tags into $c_{\mathcal{K}} \triangleq \{c_k : k \in \mathcal{K}\}$, stack the received signal over $N$ blocks as $\boldsymbol{y} \triangleq \left[y[1],\ldots,y[N]\right]^T \in \mathbb{C}^{N \times 1}$, and define the equivalent channel for primary transmission as
+		where $\alpha_k$ and $x_k$ denote respectively the harvest-backscatter efficiency and backscatter symbol of tag $k$, $s[n]$ and $w[n] \sim \mathcal{CN}(0,\sigma_w^2)$ denote respectively the primary symbol and \gls{awgn} at block $n$, and $\boldsymbol{w} \in \mathbb{C}^{Q \times 1}$ is the transmit precoder satisfying power constraint $\lVert \boldsymbol{w} \rVert^2 \le P$.
+		For the ease of notation, we define $x_{\mathcal{K}} \triangleq \{x_k : k \in \mathcal{K}\}$ as the tag input combination, and $\boldsymbol{y} \triangleq \left[y[1],\ldots,y[N]\right]^T \in \mathbb{C}^{N \times 1}$ as the received signal per backscatter symbol period.
+		For primary transmission, the equivalent channel is subject to backscatter modulation uncertainty as
 		\begin{equation}
-				\boldsymbol{h}_{\mathrm{E}}^H(c_{\mathcal{K}}) \triangleq \boldsymbol{h}_{\mathrm{D}}^H + \sum_{k \in \mathcal{K}} \sqrt{\alpha_k} \boldsymbol{h}_{\mathrm{C},k}^H c_k.
-				\label{eq:equivalent_primary_channel}
+			\boldsymbol{h}_{\mathrm{E}}^H(x_{\mathcal{K}}) \triangleq \boldsymbol{h}_{\mathrm{D}}^H + \sum_{k \in \mathcal{K}} \sqrt{\alpha_k} \boldsymbol{h}_{\mathrm{C},k}^H x_k.
+			\label{eq:equivalent_channel}
 		\end{equation}
@@
 		\begin{remark}
-				The proposed symbiotic radio system includes a multiplicative \gls{mac} where the \gls{ap} and the tags simultaneously transmit to the user.
-It inspired [TODO] to perform \gls{sic} that first non-coherently detects the primary message under backscatter uncertainty, then cancels its contribution and decodes the tag messages.
-This scheme requires non-coherent coding at the \gls{ap} and $K$ re-encoding, precoding, and subtraction operations at the user.
-However, different from the conventional \gls{mac} with \gls{sc}, the symbiotic radio system involves \gls{mc} that combines the primary and secondary messages by multiplication.
-Hence, novel multi-stream detection techniques should be tailored to symbiotic radio systems to accommodate the massive connectivity of tags and the multiplicative combination of links.
+			Metascatter involves an unconventional \gls{mac} where the primary and backscatter symbols of different duration are mixed by \gls{mc} instead of \gls{sc}.
+			For each tag, the reflection coefficient not only encodes the backscatter message but also influences the equivalent primary channel \eqref{eq:equivalent_channel}.
+			As such, novel receiving strategy other than \gls{sic} should be tailored to signal characteristics to unveil how reflection pattern potentially influences the primary-backscatter tradeoff.
 		\end{remark}
@@
 
-		\begin{subsection}{Backscatter Detection}
-			To reveal the impact of backscatter modulation on the primary transmission and avoid the exponential complexity of joint detection, we extend the non-coherent \gls{ambc} detection \cite{Qian2019} to the multi-tag case, and propose a low-complexity energy detection to decode the backscatter symbols under primary source uncertainty.
-It requires no dedicated receivers or non-coherent codes at the \gls{ap}, and can be readily implemented over legacy downlink systems.
+	\begin{subsection}{Receiving Strategy}
+		We propose a novel receiving strategy where the backscatter symbol of all tags are first jointly identified by non-coherent energy detection, then modeled within equivalent channel \eqref{eq:equivalent_channel} as if passive beamforming.
+		Compared with conventional schemes as joint decoding and \gls{sic}, the Metascatter receiver may not achieve as high data rate for one tag, but it avoids non-coherent primary encoding and enables tag multiple access in a practical and low-complexity manner.
+		Therefore, we believe it can be compatible to and readily implemented over legacy point-to-point systems.
 
-			\begin{remark}
-				One key property of symbiotic radio is the primary message propagates to the user from a known channel and multiple multiplicative channels with uncertainty introduced by backscatter modulation.
-As such, each reflection coefficient simultaneously encodes the tag message and influences the equivalent channel of the primary link.
-If the backscatter symbols can be successfully decoded first, they can be modeled within the equivalent channel \eqref{eq:equivalent_primary_channel} as in channel training, instead of being removed by \gls{sic}.
-			\end{remark}
-
-			To explicitly specify the instances of the backscatter symbols, we define the modulation index set as $m_{\mathcal{K}} \triangleq \{m_k \in \mathcal{M} : k \in \mathcal{K}\}$ and label the corresponding tag input combination as $\bar{c}_{m_{\mathcal{K}}} \triangleq \{\bar{c}_{m_k} \in \mathcal{C} : m_k \in \mathcal{M}, k \in \mathcal{K}\}$.
-Since any $\bar{c}_{m_{\mathcal{K}}}$ remains constant per $N$ primary symbols, the received signal at block $n$ is only subject to the variation of the primary source $s[n]$ and \gls{awgn} $w[n]$, and thus follows \gls{cscg} distribution $y_{m_{\mathcal{K}}}[n] \sim \mathcal{CN}\left(0,\sigma_{m_{\mathcal{K}}}^2\right)$, where the variance
+		Define $m_k \in \mathcal{M}$ as the modulation index of tag $k$, and $m_{\mathcal{K}} \triangleq \{m_k: k \in \mathcal{K}\}$ as the modulation index combination of all tags.
+		Recall that $x_k$ and $x_{\mathcal{K}}$ are random variables representing the backscatter symbol of tag $k$ and the symbol combination of all tags, respectively.
+		Their instances are denoted by modulation index (combination) as $x_{m_k}$ and $x_{m_\mathcal{K}}$.
+		Since any backscatter combination $x_{m_\mathcal{K}}$ remains unchanged over $N$ primary symbol duration, the received signal at symbol block $n$ is only subject to the variation of $s[n]$ and $w[n]$, and follows zero-mean \gls{cscg} distribution with variance
 		\begin{equation}
-				\sigma_{m_{\mathcal{K}}}^2 = \Bigl\lvert \underbrace{\bigl(\boldsymbol{h}_{\mathrm{D}}^H + \sum_{k \in \mathcal{K}} \sqrt{\alpha_k} \boldsymbol{h}_{\mathrm{C},k}^H \bar{c}_{m_k}\bigr)}_{\boldsymbol{h}_{\mathrm{E}}^H(\bar{c}_{m_{\mathcal{K}}})} \boldsymbol{w} \Bigr\rvert^2 + \sigma_w^2,
+			\sigma_{m_{\mathcal{K}}}^2 = \Bigl\lvert \underbrace{\bigl(\boldsymbol{h}_{\mathrm{D}}^H + \sum_{k \in \mathcal{K}} \sqrt{\alpha_k} \boldsymbol{h}_{\mathrm{C},k}^H x_{m_k}\bigr)}_{\boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}})} \boldsymbol{w} \Bigr\rvert^2 + \sigma_w^2.
 			\label{eq:receive_variance}
 		\end{equation}
-			denotes the expectation of the received power per primary block under tag modulation index set $m_{\mathcal{K}}$.
-For the ease of exposition, we denote the hypothesis that the tag input combination at state $i \in \mathcal{I} \triangleq \{1,\ldots,M^K\}$ as $\mathcal{H}_i$, sort $\{\sigma_{m_{\mathcal{K}}}^2\}$ in ascending order by a one-to-one mapping $m_{\mathcal{K}} \mapsto i$,\footnote{When more than one modulation index sets yield the same energy level, the mapping is not unique and the detection fails to separate them.
-This blind spot issue can be potentially mitigated by multi-antenna techniques and is beyond the scope of this paper.} define the received signal energy over $N$ primary blocks as $z \triangleq \lVert \boldsymbol{y} \rVert^2$, and let $f(z \mid \mathcal{H}_i)$ be the conditional probability density function of receiving $z$ under hypothesis $\mathcal{H}_i$.
-Correspondingly, $z$ is the sum of $N$ i.i.d.
-exponential variables each with mean $\sigma_i^2$, and the conditional probability density function follows Erlang distribution with shape $N$ and scale $\sigma_i^2$ as\footnote{In some papers, it may also be referred to as Gamma distribution.}
+
+		Besides, we denote the total received energy as $z \triangleq \lVert \boldsymbol{y} \rVert^2$ and the hypothesis of modulation index combination $m_{\mathcal{K}}$ as $\mathcal{H}_{m_{\mathcal{K}}}$.
+		Since $z$ is the sum of $N$ \gls{iid} exponential variables, its conditional \gls{pdf} under $\mathcal{H}_{m_{\mathcal{K}}}$ follows Erlang distribution with shape $N$ and scale $\sigma_{m_{\mathcal{K}}}^2$ as
 		\begin{equation}
-				f(z \mid \mathcal{H}_i) = \frac{z^{N-1} e^{-z/\sigma_i^2}}{\sigma_i^{2N} (N-1)!}.
+			f(z \mid \mathcal{H}_{m_{\mathcal{K}}}) = \frac{z^{N-1} e^{-z/\sigma_{m_{\mathcal{K}}}^2}}{\sigma_{m_{\mathcal{K}}}^{2N} (N-1)!}.
 			\label{eq:energy_distribution}
@@
 
+		Energy-based backscatter detection essentially formulates a discrete-input continuous-output memoryless \gls{mac}.
+		To further reduce decoding complexity, we divide the continuous output $z$ into disjoint decision regions to construct a \gls{dmtmac}, where the transition probability from tag input combination $x_{m_{\mathcal{K}}}$ to detector output combination $\hat{x}_{m_{\mathcal{K}}'}$ is
+		\begin{equation}
+			P(\hat{x}_{m_{\mathcal{K}}'} \mid x_{m_{\mathcal{K}}}) = \int_{\mathcal{R}_{m_{\mathcal{K}}'}} f(z \mid \mathcal{H}_{m_{\mathcal{K}}}) \dd z,
+			\label{eq:dmtmac}
+		\end{equation}
+		where $\mathcal{R}_{m_{\mathcal{K}}'}$ is the decision region over $z$ for hypothesis $\mathcal{H}_{m_{\mathcal{K}}'}$.
+	\end{subsection}
+
+	\begin{subsection}{Achievable Rates}
+		Denote the input probability distribution vector of tag $k$ as $\boldsymbol{p}_k \triangleq [P_k(x_1),\ldots,P_k(x_M)]^T \in \mathbb{R}^{M \times 1}$, where $P_k(x_{m_k})$ is the probability at state $m_k$.
+		Consider independent encoding at all tags such that the probability of input combination $x_{m_{\mathcal{K}}}$ is $P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) = \prod_{k \in \mathcal{K}} P_k(x_{m_k})$.
+		The backscatter information function of input combination $x_{m_{\mathcal{K}}}$ is defined as
+		\begin{equation}
+			I_{\mathrm{B}}(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}}) \triangleq \sum_{m_{\mathcal{K}}'} P(\hat{x}_{m_{\mathcal{K}}'} \mid x_{m_{\mathcal{K}}}) \log \frac{P(\hat{x}_{m_{\mathcal{K}}'} \mid x_{m_{\mathcal{K}}})}{P(\hat{x}_{m_{\mathcal{K}}'})},
+			\label{eq:backscatter_information_function}
+		\end{equation}
+		where $P(\hat{x}_{m_{\mathcal{K}}'}) = \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) P(\hat{x}_{m_{\mathcal{K}}'} \mid x_{m_{\mathcal{K}}})$.
+		Besides, the backscatter marginal information function associated with letter $x_{m_k}$ of tag $k$ is
+		\begin{equation}
+			I_{\mathrm{B},k}(x_{m_k};\hat{x}_{\mathcal{K}}) \triangleq \sum_{m_{\mathcal{K} \setminus \{k\}}} P_{\mathcal{K} \setminus \{k\}}(x_{m_{\mathcal{K} \setminus \{k\}}}) I_{\mathrm{B}}(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}}),
+			\label{eq:backscatter_marginal_information_function}
+		\end{equation}
+		where $P_{\mathcal{K} \setminus \{k\}}(x_{m_{\mathcal{K} \setminus \{k\}}}) = \prod_{q \in \mathcal{K} \setminus \{k\}} P_{q}(x_{m_{q}})$.
+		Therefore, the backscatter mutual information is
+		\begin{equation}
+			I_{\mathrm{B}}(x_{\mathcal{K}};\hat{x}_{\mathcal{K}}) = \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) \sum_{m_{\mathcal{K}}'} P(\hat{x}_{m_{\mathcal{K}}'} \mid x_{m_{\mathcal{K}}}) \log \frac{P(\hat{x}_{m_{\mathcal{K}}'} \mid x_{m_{\mathcal{K}}})}{P(\hat{x}_{m_{\mathcal{K}}'})}.
+			\label{eq:backscatter_mutual_information}
+		\end{equation}
+
+		Once the tag input combination is successfully decoded, the backscatter uncertainty can be eliminated and the equivalent channel for primary transmission can be updated by \eqref{eq:equivalent_channel}.
+		Similar to above, the primary information function of input combination $x_{m_{\mathcal{K}}}$ is
+		\begin{equation}
+			I_{\mathrm{P}}(x_{m_{\mathcal{K}}};\boldsymbol{y}) \triangleq N \log_2 \left(1 + \frac{\lvert \boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_w^2}\right),
+			\label{eq:primary_information_function}
+		\end{equation}
+		the primary marginal information function associated with letter $x_{m_k}$ of tag $k$ is
+		\begin{equation}
+			I_{\mathrm{P},k}(x_{m_k};\boldsymbol{y}) \triangleq \sum_{m_{\mathcal{K} \setminus \{k\}}} P_{\mathcal{K} \setminus \{k\}}(x_{m_{\mathcal{K} \setminus \{k\}}}) I_{\mathrm{P}}(x_{m_{\mathcal{K}}};\boldsymbol{y}),
+			\label{eq:primary_marginal_information_function}
+		\end{equation}
+		and the primary (ergodic) mutual information is
+		\begin{equation}
+			I_{\mathrm{P}}(x_{\mathcal{K}};\boldsymbol{y}) = \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) N \log_2 \left(1 + \frac{\lvert \boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_w^2}\right).
+			\label{eq:primary_mutual_information}
+		\end{equation}
+
+		Therefore, the weighted sum information function, marginal information function, and mutual information of primary and backscatter links are respectively given by
+		\begin{align}
+			I(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}},\boldsymbol{y})
+			 & \triangleq \rho I_{\mathrm{P}}(x_{m_{\mathcal{K}}};\boldsymbol{y}) + (1 - \rho) I_{\mathrm{B}}(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}}),\label{eq:weighted_sum_information_function} \\
+			I_k(x_{m_k};\hat{x}_{\mathcal{K}},\boldsymbol{y})
+			 & \triangleq \rho I_{\mathrm{P},k}(x_{m_k};\boldsymbol{y}) + (1 - \rho) I_{\mathrm{B},k}(x_{m_k};\hat{x}_{\mathcal{K}}),\label{eq:weighted_sum_marginal_information}                     \\
+			I(x_{\mathcal{K}};\hat{x}_{\mathcal{K}},\boldsymbol{y})
+			 & \triangleq \rho I_{\mathrm{P}}(x_{\mathcal{K}};\boldsymbol{y}) + (1 - \rho) I_{\mathrm{B}}(x_{\mathcal{K}};\hat{x}_{\mathcal{K}}),\label{eq:weighted_sum_mutual_information}
+		\end{align}
+		where $\rho \in [0,1]$ represents the priority of the primary link.
+	\end{subsection}
+
+\end{section}
+
+\begin{section}{Input, Threshold, and Precoder Design}
+To characterize the achievable primary-(sum-)backscatter rate region of Metascatter, we aim to maximize the weighted sum mutual information with respect to tag input probability distribution $\{\boldsymbol{p}_k\}$, decision threshold vector $\boldsymbol{t}$, and transmit precoder $\boldsymbol{w}$
+\begin{maxi!}
+{\scriptstyle{\{\boldsymbol{p}_k\},\boldsymbol{t},\boldsymbol{w}}}{I(x_{\mathcal{K}};\hat{x}_{\mathcal{K}},\boldsymbol{y})}{\label{op:weighted_sum_rate}}{\label{ob:weighted_sum_rate}}
+\addConstraint{\sum \nolimits_{m_k} P_k(x_{m_k})}{=1,}{\quad \forall k \in \mathcal{K}}{\label{co:sum_probability}}
+\addConstraint{P_k(x_{m_k})}{\ge 0,}{\quad \forall k \in \mathcal{K}, \ \forall m_k \in \mathcal{M}}{\label{co:nonnegative_probability}}
+\addConstraint{\lVert \boldsymbol{w} \rVert^2}{\le P.}{\label{co:transmit_power}}
+\end{maxi!}
+Since problem \eqref{op:weighted_sum_rate} is not jointly convex, we propose a \gls{bcd} algorithm that iteratively updates $\{\boldsymbol{p}_k\}$, $\boldsymbol{t}$ and $\boldsymbol{w}$ until convergence.
+
+\begin{subsection}{Input Probability Distribution}
+For any fixed decision boundary $\boldsymbol{t}$ and transmit precoder $\boldsymbol{w}$, the equivalent \gls{dmtmac} can be formulated by \eqref{eq:dmtmac} and problem \eqref{op:weighted_sum_rate} boils down to
+\begin{maxi!}
+{\scriptstyle{\{\boldsymbol{p}_k\}}}{I(x_{\mathcal{K}};\hat{x}_{\mathcal{K}},\boldsymbol{y})}{\label{op:input_probability_distribution}}{}
+\addConstraint{\eqref{co:sum_probability},\eqref{co:nonnegative_probability},}
+\end{maxi!}
+which involves the product term $\prod_{k \in \mathcal{K}} P_k(x_{m_k})$ and is non-convex when $K > 1$.
+Interestingly, the sum-rate optimal input design for general discrete memoryless \gls{mac} remains an open problem, and we instead propose a \gls{kkt} solution to problem \eqref{op:input_probability_distribution}.
+\footnote{
+	As pointed out in \cite{Buhler2011}, \gls{kkt} conditions are only necessary for sum-rate optimality and these solutions may end up being saddle points.
+}
+\begin{proposition}
+	The \gls{kkt} optimality conditions for problem \eqref{op:input_probability_distribution} are equivalent to, $\forall k \in \mathcal{K}$ and $\forall m_k \in \mathcal{M}$,
+	\begin{subequations}
+		\label{eq:input_kkt_condition}
+		\begin{alignat}{2}
+			I_k^\star(x_{m_k};\hat{x}_{\mathcal{K}},\boldsymbol{y}) & = I^\star(x_{\mathcal{K}};\hat{x}_{\mathcal{K}},\boldsymbol{y}), \quad   &  & P_k^\star(x_{m_k}) > 0,\label{eq:probable_states} \\
+			I_k^\star(x_{m_k};\hat{x}_{\mathcal{K}},\boldsymbol{y}) & \le I^\star(x_{\mathcal{K}};\hat{x}_{\mathcal{K}},\boldsymbol{y}), \quad &  & P_k^\star(x_{m_k}) = 0.\label{eq:dropped_states}
+		\end{alignat}
+	\end{subequations}
+	\label{pr:input_kkt_condition}
+\end{proposition}
+
+\begin{proof}
+	Please refer to Appendix \ref{ap:input_kkt_condition}.
+	\label{pf:input_kkt_condition}
+\end{proof}
+
+We notice \eqref{eq:probable_states} means each probable state of each tag should produce the same marginal information (averaged over all states of other tags), while \eqref{eq:dropped_states} implies any state of any tag with potentially less marginal information than above should not be used.
+Next, we generalize the Blahut-Arimoto algorithm \cite{Arimoto1972,Blahut1972a} and propose a numerical evaluation of \gls{kkt} points by limits of sequences.
+
+\begin{proposition}
+	The \gls{kkt} solution of input probability of tag $k$ at state $m_k$ is given by the converging point of the sequence
+	\begin{equation}
+		P_k^{(r+1)}(x_{m_k}) = \frac{P_k^{(r)}(x_{m_k}) \exp \left( \frac{\rho}{1 - \rho} I_k^{(r)}(x_{m_k};\hat{x}_{\mathcal{K}},\boldsymbol{y}) \right)}{\sum_{m_k'} P_k^{(r)}(x_{m_k'}) \exp \left( \frac{\rho}{1 - \rho} I_k^{(r)}(x_{m_k'};\hat{x}_{\mathcal{K}},\boldsymbol{y}) \right)},
+		\label{eq:input_kkt_solution}
+	\end{equation}
+	where $r$ is the iteration index and $\boldsymbol{p}_k^{(0)} > \boldsymbol{0}$, $\forall k \in \mathcal{K}$.
+	At each iteration, the input distribution of tag $k$ is evaluated based on the updated input distribution of tags $1$ to $k-1$.
+	\label{pr:input_kkt_solution}
+\end{proposition}
+\begin{proof}
+	Please refer to Appendix \ref{ap:input_kkt_solution}.
+	\label{pf:input_kkt_solution}
+\end{proof}
+\end{subsection}
+
+\begin{subsection}{Decision Threshold}
+	For a given tag input distribution $\{\boldsymbol{p}_k\}$, we can formulate an equivalent information source with augmented alphabet of tag input combination.
+	This equivalent source transmits at the total backscatter rate, and the input distribution is given by $P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) = \prod_{k \in \mathcal{K}} P_k(x_{m_k})$, $\forall k \in \mathcal{K}$ and $\forall m_k \in \mathcal{M}$.
+
 	\begin{remark}
-				The backscatter links essentially form a discrete-input continuous-output memoryless channel.
-To further reduce decoding complexity, we apply hard-decision detection and construct a \gls{dmtc}, whose capacity is a function of both input distribution and decision thresholds \cite{Nguyen2018}.
+		Since the equivalent source transmits at the total backscatter rate, the \gls{dmtmac} \eqref{eq:dmtmac} is essentially a point-to-point \gls{dmtc} and we can simplify the decision threshold design accordingly.
+		\label{re:input_combination}
 	\end{remark}
 
-			To maximize the mutual information for a general non-binary-input continuous-output channel, not only the decision region design remains an open problem, but also the optimal number of decision thresholds is still unknown.
-The reason is that the optimal decision region $\mathcal{R}_j$ of hypothesis $\mathcal{H}_j$ may be non-convex (i.e., consist of more than one disjoint partitions).
-The authors of \cite{Nguyen2021} showed that any optimal quantizer with arbitrary cost function must separate the backward channel  (i.e., posterior distribution) into convex decision regions, and provided an upper bound on the number of thresholds.
+	Interestingly, the optimal threshold design to maximize the mutual information for a general \gls{dmtc} with a fixed number of output letters remains an open issue.
+	The reason is that each decision region may contain more than one disjoint partitions (i.e., non-convex) and the number of thresholds are unknown.
+	Fortunately, for the proposed energy detection, we proved that the \gls{dmtc} capacity can be achieved using only convex decision regions.
+	This conclusion is summarized below.
 
-			\begin{theorem}
-				If any $L$-input ($L \in \mathbb{Z}_{++}$) continuous-output channel follows Erlang distribution~\eqref{eq:energy_distribution}, then the optimal number of thresholds is $L+1$ and the capacity-achieving decision region $j$ has convex structure $\mathcal{R}_j^{\star} = [t_{j-1}^{\star}, t_j^{\star})$.
-			\end{theorem}
+	\begin{proposition}
+		For a discrete-input continuous-output channel in Erlang distribution \eqref{eq:energy_distribution}, if the \gls{dmtc} is constructed for detection (i.e., same input/output alphabet) and $L$ input letters are with non-zero probability, then it is possible to achieve the \gls{dmtc} capacity by $L$ non-empty convex decision regions defined by $L+1$ distinct decision thresholds.
+		\label{pr:threshold}
+	\end{proposition}
 
 	\begin{proof}
-				For any finite number of thresholds $S \in \mathbb{Z}_{++}$, let $\boldsymbol{t} \triangleq [t_0,\ldots,t_S]^T \in \mathbb{R}_{+}^{S \times 1}$ be the thresholding vector where $t_{s-1} < t_s$, $\forall s \in \mathcal{S} \triangleq \{1,\ldots,S\}$.\footnote{We consider strict inequality in the definition, as otherwise $S$ and $\boldsymbol{t}$ could be non-unique for a given thresholding scheme.} Denote the decision partition $s$ as $R_s \triangleq [t_{s-1},t_s)$.
-Without loss of generality, we assume
-				% $L \mid S$ and
-				$\mathcal{R}_j = \bigcup_{s \equiv j \pmod L} R_s$.\footnote{The proof holds for general mapping $R_s \mapsto \mathcal{R}_j$, and we focus on this specific case for the ease of notation.} The thresholding design problem can be expressed as
-				\begin{maxi!}
-					{\scriptstyle{\boldsymbol{t}}}{I_{\mathrm{B}}(c_{\mathcal{K}};z)}{\label{op:thresholding}}{\label{ob:backscatter_mutual_information}}
-					\addConstraint{t_{s-1}}{< t_s,}{\quad \forall s \in \mathcal{S}.}{\label{co:strict_inequality}}
-				\end{maxi!}
-
-				Problem~\eqref{op:thresholding} is intricate due to the strict inequality constraint~\eqref{co:strict_inequality}.
-Following \cite{Nguyen2020}, we first relax it to the convex counterpart, then discard the solutions that violate the original constraints.
-The Lagrangian function for the relaxed problem is
-				\begin{equation}
-					L(\boldsymbol{t},\boldsymbol{\mu}) = - I_{\mathrm{B}}(c_{\mathcal{K}};z) + \sum_{s \in \mathcal{S}} \mu_s (t_{s-1} - t_s),
-					% = \sum_{j \in \mathcal{L}} P(\bar{z}_j) \log P(\bar{z}_j) - \sum_{i \in \mathcal{L}} \sum_{j \in \mathcal{L}}
-				\end{equation}
-				where $\mu_s$ is the Lagrange multiplier associated with the non-strict version of \eqref{co:strict_inequality} and $\boldsymbol{\mu} \triangleq [\mu_1,\ldots,\mu_S]^T \in \mathbb{R}^{S \times 1}$.
-The corresponding \gls{kkt} conditions on the optimal primal and dual solutions are, $\forall s \in \mathcal{S}$,
-				\begin{subequations}
-					\begin{equation}
-						- \nabla_{t_s^{\star}} I^{\star}_{\mathrm{B}}(c_{\mathcal{K}};z) + \mu_{s-1}^{\star} - \mu_s^{\star} = 0,
-						\label{eq:stationarity}
-					\end{equation}
-					\begin{equation}
-						\mu_s^{\star} \ge 0,
-						\label{eq:dual_feasibility}
-					\end{equation}
-					\begin{equation}
-						\mu_s^{\star} (t_{s-1}^{\star} - t_s^{\star}) = 0.
-						\label{eq:complementary_slackness}
-					\end{equation}
-					\label{eq:kkt_thresholding}
-				\end{subequations}
-				For \gls{dmtc} based on energy detection~\eqref{eq:energy_distribution}, it is trivial to conclude $t_0^{\star} = 0$ and $t_S^{\star} = \infty$.
-Besides, since $t_{s-1} < t_s$ by definition, \eqref{eq:dual_feasibility} and \eqref{eq:complementary_slackness} imply $\mu_s^{\star} = 0$, $\forall s \in \mathcal{S}$.
-As such, $\forall s' \in \mathcal{S} \setminus \{S\}$, \eqref{eq:kkt_thresholding} reduces to
-				\begin{equation}
-					\nabla_{t_{s'}^{\star}} I^{\star}_{\mathrm{B}}(c_{\mathcal{K}};z) = 0,
-				\end{equation}
-				which can be explicitly written as
-				\begin{equation}
-					\sum_l P(x_l) \log \frac{P(z_j)}{P(z_{j+1})} \frac{P(z_{j+1} \mid x_l)}{P(z_j \mid x_l)} f(h_s \mid x_l) = 0,
-					\label{eq:kkt_thresholding_explicit}
-				\end{equation}
-				where $j \equiv s \pmod L$.
-We notice that for a given $j$, $a_l \triangleq P(x_l) \log \frac{P(z_j)}{P(z_{j+1})} \frac{P(z_{j+1} \mid x_l)}{P(z_j \mid x_l)}$ is a constant for all $s \equiv j \pmod L$.
-Plugging~\eqref{eq:energy_distribution} into \eqref{eq:kkt_thresholding_explicit}, we have
-				\begin{equation}
-					\sum_l a_l e^{-{h_s}/{\sigma_l^2}} = 0,
-					\label{eq:optimal_thresholding_condition}
-				\end{equation}
-				which by Rolle's theorem has at most $L-1$ distinct real roots if $\sigma_i^2 \ne \sigma_j^2$, $i,j \in \mathcal{L}$.
-				% where the directional derivative can be explicitly written as
-				% \begin{subequations}
-				% 	\begin{align}
-				% 		\nabla_{t_{s'}^{\star}} I^{\star}_{\mathrm{B}}(c_{\mathcal{K}};z)
-				% 		& = \sum_l P(x_l) \log \frac{P(z_j)}{P(z_{j+1})} \frac{P(z_{j+1} \mid x_l)}{P(z_j \mid x_l)} f(h_s \mid x_l)\\
-				% 		& = 1
-				% 	\end{align}
-				% \end{subequations}
+		Please refer to Appendix \ref{ap:threshold}.
+		\label{pf:threshold}
 	\end{proof}
 
-			% It was proved in \cite{Nguyen2021} that the optimal quantizer producing maximizing mutual information with arbitrary cost function separates the backward channel (i.e., posterior distribution) in a convex manner
+	Once the optimal number of decision threshold is determined, we can first discretize the output energy level into numerous bins, then obtain the optimal decision regions that maximizes the total backscatter rate by \gls{dp} accelerated by \gls{smawk} algorithm \cite{He2021}.
 
-			% not only the capacity-achieving thresholding design remains an open problem, but also the optimal number of thresholds for general non-binary-input channels remains unknown.
-I am now trying to prove that, for our channel in Gamma distribution, the optimal decision region for each codeword cannot be disjoint
-
-			% Denote the decision region of hypothesis $\mathcal{H}_i$ as
-			% \begin{equation}
-			% 	\mathcal{R}_i \triangleq [t_{i-1,i}, t_{i,i+1}),
-			% 	\label{eq:decision_region}
-			% \end{equation}
-			% where $t_{i-1,i}$ is the decision threshold between $\mathcal{H}_{i-1}$ and $\mathcal{H}_i$, and $t_{i,i+1}$ is the decision threshold between $\mathcal{H}_i$ and $\mathcal{H}_{i+1}$.
-We also define $t_{0,1} \triangleq 0$, $t_{M^K,M^K+1} \triangleq \infty$, and $\boldsymbol{t} \triangleq [t_{0,1},\ldots,t_{M^K,M^K+1}]^T \in \mathbb{R}^{(M^K + 1) \times 1}$.
-
-			% Consider the (\gls{ml}) detector for example. The likelihood ratio between hypotheses $\mathcal{H}_i$ and $\mathcal{H}_{i'}$ is \cite{Qian2019}
-			% \begin{equation}
-			% 	\Lambda_{i,{i'}}^{\mathrm{\gls{ml}}}(z) = \frac{f(z \mid \mathcal{H}_i)}{f(z \mid \mathcal{H}_{i'})} = \left( \frac{\sigma_{i'}^2}{\sigma_i^2} \right)^N \exp \left( \frac{\sigma_i^2 - \sigma_{i'}^2}{\sigma_i^2 \sigma_{i'}^2} z \right),
-			% 	\label{eq:likelihood_ratio}
-			% \end{equation}
-			% the corresponding decision rule is
-			% \begin{equation}
-			% 	\Lambda_{i,{i'}}^{\mathrm{\gls{ml}}}(z) \underset{\mathcal{H}_{i'}}{\overset{\mathcal{H}_i}{\lessgtr}} 1 \iff z \underset{\mathcal{H}_{i'}}{\overset{\mathcal{H}_i}{\lessgtr}} t_{i,{i'}}^{\mathrm{\gls{ml}}},
-			% 	\label{eq:decision_rule}
-			% \end{equation}
-			% and the detection threshold is
-			% \begin{equation}
-			% 	t_{i,{i'}}^{\mathrm{\gls{ml}}} \triangleq N \frac{\sigma_i^2 \sigma_{i'}^2}{\sigma_i^2 - \sigma_{i'}^2} \log \frac{\sigma_i^2}{\sigma_{i'}^2}.
-			% 	\label{eq:detection_threshold}
-			% \end{equation}
-
-			% \begin{remark}
-			% 	Although the \gls{ml} decision threshold is optimal in terms of the likelihood function, it is not necessarily capacity-achieving, although the performance gap can be negligible in the single-tag \gls{bibo} case.
-			% \end{remark}
-
-			Once the decision region is determined, the discrete memoryless \gls{mac} can be recast as an equivalent point-to-point \gls{dmc} from tag input combination alphabet $\mathcal{I}$ to output energy level alphabet $\mathcal{I}$.
-The the probability of receiving energy level $j$ under tag input combination $i$ is\footnote{For simplicity, we assume there exists at least one feasible precoder that produces distinct received energy levels for all tag input combinations.
-[TODO] Merge with precoder design.}
-			\begin{equation}
-				P(\bar{z}_j \mid \bar{c}_i) = P(z \in \mathcal{R}_j \mid \mathcal{H}_i) = \int_{\mathcal{R}_j} f(z \mid \mathcal{H}_i) \dd z,
-				\label{eq:point_to_point_channel}
-			\end{equation}
-			which corresponds to $P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K}}})$ by reverse mapping $m_k \mapsto i$.
-In summary, with the \gls{csi} knowledge and for any given precoder and detection threshold set, we can obtain the expected power of the received signal per block by \eqref{eq:receive_variance}, the conditional probability density function of the accumulated energy by \eqref{eq:energy_distribution}, the corresponding decision region by \eqref{eq:decision_region}, and the equivalent point-to-point channel by \eqref{eq:point_to_point_channel}.
+	\begin{tcolorbox}
+		We may need to tailor threshold design for Metascatter as threshold design has potential impact on primary achievable rate, as implied by some simulation results.
+	\end{tcolorbox}
 \end{subsection}
 
-		\begin{subsection}{Sum backscatter rate}
-			We first introduce some prerequisites of information theory.
-Define the input probability distribution of tag $k$ at state $m_k$ as $P_k(\bar{c}_{m_k})$, and let $\boldsymbol{p}_k \triangleq [P_k(\bar{c}_1),\ldots,P_k(\bar{c}_M)]^T \in \mathbb{R}^{M \times 1}$, $\boldsymbol{P} \triangleq [\boldsymbol{p}_1^T,\ldots,\boldsymbol{p}_K^T]^T \in \mathbb{R}^{M \times K}$.
-Assume the input distribution of all tags are mutually independent such that the probability associated with input combination $\bar{c}_{m_{\mathcal{K}}}$ satisfies $P_{\mathcal{K}}(\bar{c}_{m_{\mathcal{K}}}) = \prod_{k \in \mathcal{K}} P_k(\bar{c}_{m_k})$.
-Following \cite{Rezaeian2004}, the corresponding backscatter information function is defined as
-			\begin{equation}
-				I_{\mathrm{B}}(\bar{c}_{m_{\mathcal{K}}};z) \triangleq \sum_j P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K}}}) \log \frac{P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K}}})}{P(\bar{z}_j)},
-				\label{eq:backscatter_information_function}
-			\end{equation}
-			where $P(\bar{z}_j) = \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(\bar{c}_{m_{\mathcal{K}}}) P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K}}})$.
-			The backscatter marginal information function of tag $k \in \mathcal{K}$ associated with $\bar{c}_{m_k}$, $m_k \in \mathcal{M}$ is defined as
-			\begin{equation}
-				I_{\mathrm{B},k}(\bar{c}_{m_k};z) \triangleq \sum_{m_{\mathcal{K} \setminus \{k\}}} P_{\mathcal{K} \setminus \{k\}}(\bar{c}_{m_{\mathcal{K} \setminus \{k\}}}) I_{\mathrm{B}}(\bar{c}_{m_{\mathcal{K} \setminus \{k\}}},\bar{c}_{m_k};z),
-				\label{eq:backscatter_marginal_information_function}
-			\end{equation}
-			where $P_{\mathcal{K} \setminus \{k\}}(\bar{c}_{m_{\mathcal{K} \setminus \{k\}}}) = \prod_{q \in \mathcal{K} \setminus \{k\}} P_{q}(\bar{c}_{m_{q}})$.
-The backscatter mutual information can be expressed as\footnote{Please be aware that $c_{\mathcal{K}}$, $c_k$, $z$ are random variables, while $\bar{c}_{m_{\mathcal{K}}}$ and $\bar{c}_i$, $\bar{c}_{m_k}$, $\bar{z}_j$ represent the corresponding instances.}
-			\begin{subequations}
+\begin{subsection}{Precoder}
+	\begin{tcolorbox}
+		The optimal precoder design is highly non-convex that involves integration, entropy term, and variable on exponential.
+		We may propose a suboptimal precoder based on linear combination of equivalent and cascaded channels, or consider single transmit antenna instead.
+	\end{tcolorbox}
 	\begin{align}
-					I_{\mathrm{B}}(c_{\mathcal{K}};z)
-					& = \mathbb{E}_{c_{\mathcal{K}}} \left[I_{\mathrm{B}}(\bar{c}_{m_{\mathcal{K}}};z)\right] = \mathbb{E}_{c_k} \left[I_{\mathrm{B},k}(\bar{c}_{m_k};z)\right]\label{eq:backscatter_sum_rate_expectation}\\
-					& = \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(\bar{c}_{m_{\mathcal{K}}}) \sum_j P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K}}}) \log \frac{P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K}}})}{P(\bar{z}_j)}.\label{eq:backscatter_sum_rate_expansion}
+		I(x_i;\hat{x}_j)
+		 & = \sum_{j \in \mathcal{I}} \int_{t_{j-1,j}}^{t_{j,j+1}} \frac{z^{N-1} \exp \left(-\frac{z}{\mathrm{tr}(H_{\mathrm{E},i} W) + \sigma_w^2}\right)}{\left(\mathrm{tr}(H_{\mathrm{E},i} W) + \sigma_w^2\right)^N (N-1)!} \dd z\nonumber                                                                                                                                                                                                                    \\
+		 & \quad \times \log \frac{\int_{t_{j-1,j}}^{t_{j,j+1}} \frac{z^{N-1} \exp \left(-\frac{z}{\mathrm{tr}(H_{\mathrm{E},i} W) + \sigma_w^2}\right)}{\left(\mathrm{tr}(H_{\mathrm{E},i} W) + \sigma_w^2\right)^N (N-1)!} \dd z}{\sum_{i' \in \mathcal{I}} \int_{t_{j-1,j}}^{t_{j,j+1}} \frac{z^{N-1} \exp \left(-\frac{z}{\mathrm{tr}(H_{\mathrm{E},i'} W) + \sigma_w^2}\right)}{\left(\mathrm{tr}(H_{\mathrm{E},i'} W) + \sigma_w^2\right)^N (N-1)!} \dd z},
 	\end{align}
-				\label{eq:backscatter_sum_rate}
-			\end{subequations}
-			Evidently, \eqref{eq:backscatter_information_function}--\eqref{eq:backscatter_sum_rate} are functions of the tag input distribution $\boldsymbol{P}$ as well as the discrete memoryless \gls{mac} $P(z \mid c_{\mathcal{K}})$, and thus depend on the transmit precoder $\boldsymbol{w}$ and the detection threshold $\boldsymbol{t}$.
-		\end{subsection}
-
-		\begin{subsection}{Ergodic primary rate}
-			Once the tag input combination is successfully decoded, the user can eliminate backscatter uncertainty and model its contribution within the equivalent primary channel \eqref{eq:equivalent_primary_channel}.
-As such, the tags can adjust the propagation environment in a potentially beneficial manner, and create artificial channel variation within each fading block.
-Similarly, we define the primary information function associated with tag input combination $\bar{c}_{m_{\mathcal{K}}}$ and the primary marginal information function of tag $k$ associated with symbol $\bar{c}_{m_k}$ respectively as
-
-			\begin{align}
-				I_{\mathrm{P}}(\bar{c}_{m_{\mathcal{K}}};\boldsymbol{y})
-				& \triangleq N \log_2 \left(1 + \frac{\lvert \boldsymbol{h}_{\mathrm{E}}^H(\bar{c}_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_w^2}\right),\label{eq:primary_information_function}\\
-				I_{\mathrm{P},k}(\bar{c}_{m_k};\boldsymbol{y})
-				& \triangleq \sum_{m_{\mathcal{K} \setminus \{k\}}} P_{\mathcal{K} \setminus \{k\}}(\bar{c}_{m_{\mathcal{K} \setminus \{k\}}}) I_{\mathrm{P}}(\bar{c}_{m_{\mathcal{K} \setminus \{k\}}},\bar{c}_{m_k};\boldsymbol{y}),\label{eq:primary_marginal_information_function}
-			\end{align}
-			and the ergodic primary rate can be expressed as\footnote{The unit of \eqref{eq:backscatter_information_function}--\eqref{eq:backscatter_sum_rate} are \gls{bpcu}, while the unit of \eqref{eq:primary_information_function}--\eqref{eq:primary_ergodic_rate} are \gls{bpsphz}.}
-			\begin{subequations}
-				\begin{align}
-					I_{\mathrm{P}}(c_{\mathcal{K}};\boldsymbol{y})
-					& = \mathbb{E}_{c_{\mathcal{K}}} \left[I_{\mathrm{P}}(\bar{c}_{m_{\mathcal{K}}};\boldsymbol{y})\right] = \mathbb{E}_{c_k} \left[I_{\mathrm{P},k}(\bar{c}_{m_k};\boldsymbol{y})\right]\label{eq:primary_ergodic_rate_expectation}\\
-					& = \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(\bar{c}_{m_{\mathcal{K}}}) N \log_2 \left(1 + \frac{\lvert \boldsymbol{h}_{\mathrm{E}}^H(\bar{c}_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_w^2}\right).
-					\label{eq:primary_ergodic_rate_expansion}
-				\end{align}
-				\label{eq:primary_ergodic_rate}
-			\end{subequations}
-
-			In contrast to the backscatter case, \eqref{eq:primary_information_function}--\eqref{eq:primary_ergodic_rate} are irrelevant to the detection threshold $\boldsymbol{t}$, but depend on the tag input probability distribution $\boldsymbol{P}$ and the transmit precoder $\boldsymbol{w}$.
 \end{subsection}
@@
 
-	\begin{section}{Input Distribution, Decision Region, and Precoder Design}
-		\begin{subsection}{Primary-backscatter rate region}
-			Define the weighted sum information function associated with tag input combination $\bar{c}_{m_{\mathcal{K}}}$ as
+\begin{section}{Preliminary Results}
+	\begin{table}[t!]
+		\centering
+		\caption{Parameters in simulation}
+		\begin{tabular}{ll}
+			Transmit antenna $Q$     & 1   \\
+			Tags $K$                 & 2   \\
+			States $M$               & 2   \\
+			Reflect ratio $\alpha$   & 0.5 \\
+			Duration ratio $N$       & 10  \\
+			Noise power $\sigma_w^2$ & 1   \\
+			Discretization bins      & 256
+		\end{tabular}
+		\label{ta:parameters}
+	\end{table}
+	Table \ref{ta:parameters} shows the parameters used in simulation.
+	We assume all links are in standard \gls{cscg} distribution and evaluated the rate regions on two instances.
+	For the input design, ``Cooperation'' assumes full transmit cooperation at all tags (i.e., joint encoding), ``Exhaustion'' runs exhaustive search on all possible input distributions, ``\gls{kkt}'' is proposed \gls{kkt} input design \eqref{eq:input_kkt_solution}, and ``Marginalization'' marginalizes the joint input array by ``Cooperation'' to obtain independent tag input distribution.
+	For the threshold design, ``\gls{smawk}'' refers to the \gls{dp}-based quantization proposed in \cite{He2021}, ``Bisection'' sequentially optimizes each threshold by bisection \cite{Nguyen2020a}, and ``\gls{ml}'' is the \gls{ml} detector that requires no knowledge of input distribution.
+
+	Figs. \ref{fi:rate_region_1} and \ref{fi:rate_region_2} show two typical scenarios where joint encoding can be helpful and unnecessary, respectively.
+	Although the proposed \gls{kkt} input design converges to the optimal solutions in both examples, it may be trapped at saddle points under poor initialization, especially when the number of tags increases.
+
+	We believed threshold design has no impact on the primary achievable rate, because primary decoding acts on $\boldsymbol{y}$ while thresholding acts on $z$.
+	As such, the threshold that maximizes the total backscatter rate should also maximize the weighted sum rate.
+	Interestingly, this may not be the case because the \gls{smawk} and Bisection threshold designs, both maximizing the total backscatter rate, can be outperformed by the \gls{ml} when it comes to weighted sum primary-(sum-)backscatter rate.
+	It may result from a precision issue, but inspires further research on threshold design for Metascatter.
+
+	\begin{figure}[!t]
+		\centering
+		\resizebox{\columnwidth}{!}{
+			\includegraphics{assets/rate_region_1.eps}
+		}
+		\caption{Achievable rate regions by input-threshold design: Case I.}
+		\label{fi:rate_region_1}
+	\end{figure}
+
+	\begin{figure}[!t]
+		\centering
+		\resizebox{\columnwidth}{!}{
+			\includegraphics{assets/rate_region_2.eps}
+		}
+		\caption{Achievable rate regions by input-threshold design: Case II.}
+		\label{fi:rate_region_2}
+	\end{figure}
+\end{section}
+
+\begin{appendix}
+\begin{subsection}{Proof of Proposition \ref{pr:input_kkt_condition}}
+	Denote the Lagrange multipliers associated with \eqref{co:sum_probability} and \eqref{co:nonnegative_probability} as $\{\nu_k\}_{k \in \mathcal{K}}$ and $\{\lambda_{k,m_k}\}_{k \in \mathcal{K},m_k \in \mathcal{M}}$, respectively.
+	The Lagrangian function of problem \eqref{op:input_probability_distribution} is
+	\begin{align}
+		% L(\{\boldsymbol{p}_k\},\{\nu_k\},\{\lambda_{k,m_k}\})
+		L
+		 & = - I(x_{\mathcal{K}};\hat{x}_{\mathcal{K}},\boldsymbol{y}) + \sum_{k \in \mathcal{K}} \nu_k \left( \sum_{m_k \in \mathcal{M}} P_k(x_{m_k}) - 1 \right)\nonumber \\
+		 & \quad - \sum_{k \in \mathcal{K}} \sum_{m_k \in \mathcal{M}} \lambda_{k,m_k} P_k(x_{m_k}),
+	\end{align}
+	and the \gls{kkt} conditions on the optimal primal and dual variables are, $\forall m_k \in \mathcal{M}$ and $\forall k \in \mathcal{K}$,
+	\begin{subequations}
+		\label{eq:input_kkt_condition_original}
 		\begin{equation}
-				I(\bar{c}_{m_{\mathcal{K}}};\boldsymbol{y},z) \triangleq \rho I_{\mathrm{P}}(\bar{c}_{m_{\mathcal{K}}};\boldsymbol{y}) + (1 - \rho) I_{\mathrm{B}}(\bar{c}_{m_{\mathcal{K}}};z),
-				\label{eq:weighted_sum_information_function}
-			\end{equation}
-			the weighted sum marginal information of tag $k$ associated with symbol $\bar{c}_{m_k}$ as
-			\begin{equation}
-				I_k(\bar{c}_{m_k};\boldsymbol{y},z) \triangleq \rho I_{\mathrm{P},k}(\bar{c}_{m_k};\boldsymbol{y}) + (1 - \rho) I_{\mathrm{B},k}(\bar{c}_{m_k};z),
-				\label{eq:weighted_sum_marginal_information}
-			\end{equation}
-			and the weighted sum primary-backscatter rate as
-			\begin{equation}
-				I(c_{\mathcal{K}};\boldsymbol{y},z) \triangleq \rho I_{\mathrm{P}}(c_{\mathcal{K}};\boldsymbol{y}) + (1 - \rho) I_{\mathrm{B}}(c_{\mathcal{K}};z),
-				\label{eq:weighted_sum_rate}
-			\end{equation}
-			where $\rho \in [0,1]$ denotes the priority of the primary link.
-To investigate how backscatter modulation and detection may influence the primary transmission, we optimize the input probability distribution, decision region, and transmit precoder to maximize the weighted sum primary-backscatter rate
-			\begin{maxi!}
-				{\scriptstyle{\boldsymbol{P},\boldsymbol{t},\boldsymbol{w}}}{I(c_{\mathcal{K}};\boldsymbol{y},z)}{\label{op:rate_region}}{\label{ob:weighted_sum_rate}}
-				\addConstraint{\sum \nolimits_{m_k} P_k(\bar{c}_{m_k})}{=1,}{\quad \forall k \in \mathcal{K}}{\label{co:sum_probability}}
-				\addConstraint{P_k(\bar{c}_{m_k})}{\ge 0,}{\quad \forall m_k \in \mathcal{M}, \ \forall k \in \mathcal{K}}{\label{co:nonnegative_probability}}
-				\addConstraint{\lVert \boldsymbol{w} \rVert^2}{\le P.}{\label{co:average_transmit_power}}
-			\end{maxi!}
-			where \eqref{co:sum_probability} and \eqref{co:nonnegative_probability} are input probability constraints and \eqref{co:average_transmit_power} is the average transmit power budget.
-As problem \eqref{op:rate_region} is not jointly convex over $\boldsymbol{P}$, $\boldsymbol{t}$ and $\boldsymbol{w}$, we propose a \gls{bcd} method that iteratively updates the input distribution, decision region, and transmit precoder, until convergence is achieved.
-		\end{subsection}
-
-		\begin{subsection}{Input probability distribution}
-			For any fixed decision boundary $\boldsymbol{t}$ and transmit precoder $\boldsymbol{w}$, the equivalent discrete memoryless \gls{mac} can be determined by \eqref{eq:point_to_point_channel} and problem~\eqref{op:rate_region} boils down to
-			\begin{maxi!}
-				{\scriptstyle{\boldsymbol{P}}}{I(c_{\mathcal{K}};\boldsymbol{y},z)}{\label{op:input_probability_distribution}}{}
-				\addConstraint{\eqref{co:sum_probability},\eqref{co:nonnegative_probability},}
-			\end{maxi!}
-			which is non-convex for $K > 1$ due to the product term $\prod_{k \in \mathcal{K}} P_k(\bar{c}_{m_k})$.
-Fortunately, the \gls{kkt} conditions are necessary and sufficient for this type of problem, and the proof follows straightforwardly from \cite{Watanabe2009}.\footnote{For any elementary discrete memoryless \gls{mac} (sizes of input alphabets are no greater than that of output alphabet), the sufficiency can be proved by combining the local maximum and connectedness of \gls{kkt} solutions.
-For any general discrete memoryless \gls{mac}, the capacity can be achieved by an elementary discrete memoryless \gls{mac} included within.
-Thus, we restrict the discussion of this paper to elementary discrete memoryless \gls{mac}s.}
-			\begin{proposition}
-				The necessary and sufficient conditions for an input probability distribution $\boldsymbol{P}^{\star}$ to maximize the weighted sum primary-backscatter rate are that, $\forall m_k \in \mathcal{M}$ and $\forall k \in \mathcal{K}$,
-				\begin{subequations}
-					\label{eq:optimal_conditions}
-					\begin{alignat}{2}
-						I_k^{\star}(\bar{c}_{m_k};\boldsymbol{y},z) & = I^{\star}(c_{\mathcal{K}};\boldsymbol{y},z), \quad && P_k^{\star}(\bar{c}_{m_k}) > 0,\label{eq:probable_states}\\
-						I_k^{\star}(\bar{c}_{m_k};\boldsymbol{y},z) & \le I^{\star}(c_{\mathcal{K}};\boldsymbol{y},z), \quad && P_k^{\star}(\bar{c}_{m_k}) = 0.\label{eq:dropped_states}
-					\end{alignat}
-				\end{subequations}
-				\eqref{eq:probable_states} means each probable state of each tag should produce the same marginal information (averaged over all states of other tags), while \eqref{eq:dropped_states} implies any state of any tag with potentially less marginal information than above should not be used.
-				\label{pr:optimal_conditions}
-			\end{proposition}
-			\begin{proof}
-				Denote the Lagrange multiplier associated with \eqref{co:sum_probability} and \eqref{co:nonnegative_probability} as $\boldsymbol{\nu} \triangleq [\nu_1,\ldots,\nu_K]^T \in \mathbb{R}^{K \times 1}$ and $\boldsymbol{\Lambda} \triangleq [\boldsymbol{\lambda}_1^T,\ldots,\boldsymbol{\lambda}_K^T]^T \in \mathbb{R}^{M \times K}$ with $\boldsymbol{\lambda}_k \triangleq [\lambda_{k,1},\ldots,\lambda_{k,M}]^T \in \mathbb{R}^{M \times 1}$, respectively.
-The Lagrangian function of problem~\eqref{op:input_probability_distribution} is
-				\begin{align}
-					L(\boldsymbol{P},\boldsymbol{\nu},\boldsymbol{\Lambda})
-					& = - I(c_{\mathcal{K}};\boldsymbol{y},z) + \sum_{k \in \mathcal{K}} \nu_k \left( \sum_{m_k \in \mathcal{M}} P_k(\bar{c}_{m_k}) - 1 \right)\nonumber\\
-					& \quad - \sum_{k \in \mathcal{K}} \sum_{m_k \in \mathcal{M}} \lambda_{k,m_k} P_k(\bar{c}_{m_k}),
-				\end{align}
-				and the corresponding \gls{kkt} conditions are, $\forall m_k \in \mathcal{M}$ and $\forall k \in \mathcal{K}$,
-				\begin{subequations}
-					\begin{equation}
-						- \nabla_{P_k^{\star}(\bar{c}_{m_k})} I^{\star}(c_{\mathcal{K}};\boldsymbol{y},z) + \nu_k^{\star} - \lambda_{k,m_k}^{\star} = 0,
+			- \nabla_{P_k^\star(x_{m_k})} I^\star(x_{\mathcal{K}};\hat{x}_{\mathcal{K}},\boldsymbol{y}) + \nu_k^\star - \lambda_{k,m_k}^\star = 0,
 		\end{equation}
 		\begin{equation}
-						\lambda_{k,m_k}^{\star} = 0, \quad P_k^{\star}(\bar{c}_{m_k}) > 0,
+			\lambda_{k,m_k}^\star = 0, \quad P_k^\star(x_{m_k}) > 0,
 		\end{equation}
 		\begin{equation}
-						\lambda_{k,m_k}^{\star} \ge 0, \quad P_k^{\star}(\bar{c}_{m_k}) = 0,
+			\lambda_{k,m_k}^\star \ge 0, \quad P_k^\star(x_{m_k}) = 0,
 		\end{equation}
@@
 	\begin{equation}
-					\nabla_{P_k^{\star}(\bar{c}_{m_k})} I^{\star}(c_{\mathcal{K}};\boldsymbol{y},z) = I_k^{\star}(\bar{c}_{m_k};\boldsymbol{y},z) - (1 - \rho).
+		\nabla_{P_k^\star(x_{m_k})} I^\star(x_{\mathcal{K}};\hat{x}_{\mathcal{K}},\boldsymbol{y}) = I_k^\star(x_{m_k};\hat{x}_{\mathcal{K}},\boldsymbol{y}) - (1 - \rho).
+		\label{eq:input_directional_derivative}
 	\end{equation}
 
-				Due to the necessity and sufficiency of the \gls{kkt} conditions, we conclude that any input probability distribution $\boldsymbol{P}^{\star}$ maximizes the weighted sum primary-backscatter rate if and only if, $\forall m_k \in \mathcal{M}$ and $\forall k \in \mathcal{K}$,
+	Combining \eqref{eq:input_kkt_condition_original} and \eqref{eq:input_directional_derivative}, we have
 	\begin{subequations}
+		\label{eq:input_kkt_condition_transformed}
 		\begin{alignat}{2}
-						I_k^{\star}(\bar{c}_{m_k};\boldsymbol{y},z) & = \nu_k^{\star} + (1 - \rho), \quad && P_k^{\star}(\bar{c}_{m_k}) > 0,\label{eq:probable_states_marginal}\\
-						I_k^{\star}(\bar{c}_{m_k};\boldsymbol{y},z) & \le \nu_k^{\star} + (1 - \rho), \quad && P_k^{\star}(\bar{c}_{m_k}) = 0,\label{eq:dropped_states_marginal}
+			I_k^\star(x_{m_k};\hat{x}_{\mathcal{K}},\boldsymbol{y}) & = \nu_k^\star + (1 - \rho), \quad   &  & P_k^\star(x_{m_k}) > 0,\label{eq:probable_states_marginal} \\
+			I_k^\star(x_{m_k};\hat{x}_{\mathcal{K}},\boldsymbol{y}) & \le \nu_k^\star + (1 - \rho), \quad &  & P_k^\star(x_{m_k}) = 0,\label{eq:dropped_states_marginal}
 		\end{alignat}
 	\end{subequations}
-				which implies
+	which suggests
 	\begin{equation}
-					\sum_{m_k} P_k^{\star}(\bar{c}_{m_k}) I_k^{\star}(\bar{c}_{m_k};\boldsymbol{y},z) = \nu_k^{\star} + (1 - \rho).
+		\sum_{m_k} P_k^\star(x_{m_k}) I_k^\star(x_{m_k};\hat{x}_{\mathcal{K}},\boldsymbol{y}) = \nu_k^\star + (1 - \rho).
+		\label{eq:input_kkt_condition_implied}
 	\end{equation}
 
-				On the other hand, by definition of marginations \eqref{eq:backscatter_sum_rate_expectation}, \eqref{eq:primary_ergodic_rate_expectation} and weighted summations \eqref{eq:weighted_sum_marginal_information}, \eqref{eq:weighted_sum_rate}, we have
+	On the other hand, by definition of weighted sum marginal information \eqref{eq:weighted_sum_marginal_information},
 	\begin{equation}
-					\sum_{m_k} P_k^{\star}(\bar{c}_{m_k}) I_k^{\star}(\bar{c}_{m_k};\boldsymbol{y},z) = I^{\star}(c_{\mathcal{K}};\boldsymbol{y},z),
+		\sum_{m_k} P_k^\star(x_{m_k}) I_k^\star(x_{m_k};\hat{x}_{\mathcal{K}},\boldsymbol{y}) = I^\star(x_{\mathcal{K}};\hat{x}_{\mathcal{K}},\boldsymbol{y}),
+		\label{eq:weighted_sum_marginal_information_implied}
 	\end{equation}
-				which is irrelevant to $k$. It suggests $I^{\star}(c_{\mathcal{K}};\boldsymbol{y},z) = \nu_k^{\star} + (1 - \rho)$, $\forall k \in \mathcal{K}$, and completes the proof.
-			\end{proof}
+	where the right-hand side is irrelevant to $k$.
+	\eqref{eq:input_kkt_condition_transformed}, \eqref{eq:input_kkt_condition_implied}, and \eqref{eq:weighted_sum_marginal_information_implied} together complete the proof.
+	\qedsymbol
+	\label{ap:input_kkt_condition}
+\end{subsection}
 
-			Next, we extend the Blahut-Arimoto algorithm to the proposed case and obtain the optimal input probability distribution as follows.
-
-			\begin{theorem}
-				The input probability distribution that achieves the weighted sum primary-backscatter capacity, at state $m_k \in \mathcal{M}$ of tag $k \in \mathcal{K}$, is given by the converging point of sequence\footnote{Note that the probability distribution of tag $k$ is based on the updated probability distribution of tags $1,\ldots,k-1$.}
-				\begin{equation}
-					P_k^{(r+1)}(\bar{c}_{m_k}) = \frac{P_k^{(r)}(\bar{c}_{m_k}) \exp \left( \frac{\rho}{1 - \rho} I_k^{(r)}(\bar{c}_{m_k};\boldsymbol{y},z) \right)}{\sum_{m_k'} P_k^{(r)}(\bar{c}_{m_k'}) \exp \left( \frac{\rho}{1 - \rho} I_k^{(r)}(\bar{c}_{m_k'};\boldsymbol{y},z) \right)},
-					\label{eq:optimal_distribution}
-				\end{equation}
-				where $r \in \mathbb{Z}_+$ is the iteration index and $P_k^{(0)}(\bar{c}_{m_k}) > 0$.
-				% , $\forall m_k \in \mathcal{M}$ and $\forall k \in \mathcal{K}$.
-				\label{th:optimal_distribution}
-			\end{theorem}
-			\begin{proof}
-				We first prove sequence~\eqref{eq:optimal_distribution} is non-decreasing in mutual information.
-For state $m_k \in \mathcal{M}$ of tag $k \in \mathcal{K}$, let $P_{\mathcal{K}}(\bar{c}_{m_{\mathcal{K}}}) = \prod_{q \in \mathcal{K}} P_q(\bar{c}_{m_q})$ and $P_{\mathcal{K}}'(\bar{c}_{m_{\mathcal{K}}}) = P_k'(\bar{c}_{m_k}) \prod_{q \in \mathcal{K} \setminus \{k\}} P_q(\bar{c}_{m_q})$ be two probability distributions with potentially different marginal for tag $k$, and define an intermediate function $J \left( P_{\mathcal{K}}(\bar{c}_{m_{\mathcal{K}}}),P_{\mathcal{K}}'(\bar{c}_{m_{\mathcal{K}}}) \right)$ by \eqref{eq:intermediate_information_function}.
-Apparently, $I(\bar{c}_{\mathcal{K}};\boldsymbol{y},z) = J \left( P_{\mathcal{K}}(\bar{c}_{m_{\mathcal{K}}}),P_{\mathcal{K}}(\bar{c}_{m_{\mathcal{K}}}) \right)$.
+\begin{subsection}{Proof of Proposition \ref{pr:input_kkt_solution}}
+	We first prove sequence \eqref{eq:input_kkt_solution} is non-decreasing in mutual information.
+	Let $P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) = \prod_{q \in \mathcal{K}} P_q(x_{m_q})$ and $P_{\mathcal{K}}'(x_{m_{\mathcal{K}}}) = P_k'(x_{m_k}) \prod_{q \in \mathcal{K} \setminus \{k\}} P_q(x_{m_q})$ be two probability distributions with potentially different marginal for tag $k \in \mathcal{K}$ at state $m_k \in \mathcal{M}$, and define an intermediate function $J \left( P_{\mathcal{K}}(x_{m_{\mathcal{K}}}),P_{\mathcal{K}}'(x_{m_{\mathcal{K}}}) \right)$ as \eqref{eq:intermediate_information_function}.
 	\begin{figure*}[!b]
@@
 		\begin{align}
-						J \left( P_{\mathcal{K}}(\bar{c}_{m_{\mathcal{K}}}),P_{\mathcal{K}}'(\bar{c}_{m_{\mathcal{K}}}) \right)
-						& \triangleq \rho \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(\bar{c}_{m_{\mathcal{K}}}) N \log_2 \left(1 + \frac{\lvert \boldsymbol{h}_{\mathrm{E}}^H(\bar{c}_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_w^2}\right)\nonumber\\
-						& \quad + (1 - \rho) \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(\bar{c}_{m_{\mathcal{K}}}) \sum_j P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K}}}) \log \frac{P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K}}}) P_{\mathcal{K}}'(\bar{c}_{m_{\mathcal{K}}})}{P'(\bar{z}_j) P_{\mathcal{K}}(\bar{c}_{m_{\mathcal{K}}})}.
+			J \left( P_{\mathcal{K}}(x_{m_{\mathcal{K}}}),P_{\mathcal{K}}'(x_{m_{\mathcal{K}}}) \right)
+			 & \triangleq \rho \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) N \log_2 \left(1 + \frac{\lvert \boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_w^2}\right)\nonumber                                                                                                                          \\
+			 & \quad + (1 - \rho) \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) \sum_{m_{\mathcal{K}}'} P(\hat{x}_{m_{\mathcal{K}}'} \mid x_{m_{\mathcal{K}}}) \log \frac{P(\hat{x}_{m_{\mathcal{K}}'} \mid x_{m_{\mathcal{K}}}) P_{\mathcal{K}}'(x_{m_{\mathcal{K}}})}{P'(\hat{x}_{m_{\mathcal{K}}'}) P_{\mathcal{K}}(x_{m_{\mathcal{K}}})}.
 			\label{eq:intermediate_information_function}
@@
 	\end{figure*}
-				For a fixed $P_{\mathcal{K}}'(\bar{c}_{m_{\mathcal{K}}})$, $J \left( P_{\mathcal{K}}(\bar{c}_{m_{\mathcal{K}}}),P_{\mathcal{K}}'(\bar{c}_{m_{\mathcal{K}}}) \right)$ is a concave function of $P_k(\bar{c}_{m_k})$ and is maximized at $\nabla_{P_k^{\star}(\bar{c}_{m_k})} J \left( P_{\mathcal{K}}(\bar{c}_{m_{\mathcal{K}}}),P_{\mathcal{K}}'(\bar{c}_{m_{\mathcal{K}}}) \right) = 0$, namely
+	It is straightforward to verify $J \left( P_{\mathcal{K}}(x_{m_{\mathcal{K}}}),P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) \right) = I(x_{\mathcal{K}};\hat{x}_{\mathcal{K}},\boldsymbol{y})$ and $J \left( P_{\mathcal{K}}(x_{m_{\mathcal{K}}}),P_{\mathcal{K}}'(x_{m_{\mathcal{K}}}) \right)$ is a concave function for a fixed $P_{\mathcal{K}}'(x_{m_{\mathcal{K}}})$.
+	By choosing $\nabla_{P_k^\star(x_{m_k})} J \left( P_{\mathcal{K}}(x_{m_{\mathcal{K}}}),P_{\mathcal{K}}'(x_{m_{\mathcal{K}}}) \right) = 0$, we have
 	\begin{equation}
-					S_k'(\bar{c}_{m_k}) - S_k'(\bar{c}_{i_k}) + (1 - \rho) \log \frac{P_k(\bar{c}_{i_k})}{P_k^{\star}(\bar{c}_{m_k})} = 0,
+		S_k'(x_{m_k}) - S_k'(x_{i_k}) + (1 - \rho) \log \frac{P_k(x_{i_k})}{P_k^\star(x_{m_k})} = 0,
 		\label{eq:optimal_intermediate_information_condition}
@@
 	\begin{align}
-					S_k'(\bar{c}_{m_k})
-					& \triangleq I_k'(\bar{c}_{m_k};\boldsymbol{y},z) + (1 - \rho) \sum_{m_{\mathcal{K} \setminus \{k\}}} P_{\mathcal{K} \setminus \{k\}}(\bar{c}_{m_{\mathcal{K} \setminus \{k\}}})\nonumber\\
-					& \quad \times \sum_j P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K} \setminus \{k\}}},\bar{c}_{m_k}) \log P_{\mathcal{K}}'(\bar{c}_{m_{\mathcal{K} \setminus \{k\}}},\bar{c}_{m_k}).
+		S_k'(x_{m_k})
+		 & \triangleq I_k'(x_{m_k};\hat{x}_{\mathcal{K}},\boldsymbol{y}) + (1 - \rho) \sum_{m_{\mathcal{K} \setminus \{k\}}} P_{\mathcal{K} \setminus \{k\}}(x_{m_{\mathcal{K} \setminus \{k\}}})\nonumber \\
+		 & \quad \times \sum_{m_{\mathcal{K}}'} P(\hat{x}_{m_{\mathcal{K}}'} \mid x_{m_{\mathcal{K}}}) \log P_{\mathcal{K}}'(x_{m_{\mathcal{K}}}).
 	\end{align}
+
 	Evidently, $\forall m_k \ne i_k$, \eqref{eq:optimal_intermediate_information_condition} boils down to
-				% \begin{subequations}
-				% 	\begin{align}
-				% 		P_k^{\star}(\bar{c}_{m_k})
-				% 		& = \frac{\exp \left( \frac{1}{1 - \rho} S_k'(\bar{c}_{m_k}) \right)}{\sum_{m_k'} \exp \left( \frac{1}{1 - \rho} S_k'(\bar{c}_{m_k'}) \right)}\\
-				% 		& = \frac{P_k'(\bar{c}_{m_k}) \exp \left( \frac{\rho}{1 - \rho} I_k'(\bar{c}_{m_k};\boldsymbol{y},z) \right)}{\sum_{m_k'} P_k'(\bar{c}_{m_k'}) \exp \left( \frac{\rho}{1 - \rho} I_k'(\bar{c}_{m_k'};\boldsymbol{y},z) \right)}.
-				% 		\label{eq:optimal_relative_distribution}
-				% 	\end{align}
-				% \end{subequations}
-				\begin{subequations}
-					\begin{align}
-						P_k^{\star}(\bar{c}_{m_k})
-						& = \frac{\exp \left( \frac{1}{1 - \rho} S_k'(\bar{c}_{m_k}) \right)}{\sum_{m_k'} \exp \left( \frac{1}{1 - \rho} S_k'(\bar{c}_{m_k'}) \right)}\\
-						& = \frac{P_k'(\bar{c}_{m_k}) u_k'(\bar{c}_{m_k})}{\sum_{m_k'} P_k'(\bar{c}_{m_k'}) u_k'(\bar{c}_{m_k'})},
+	\begin{equation}
+		P_k^\star(x_{m_k}) = \frac{P_k'(x_{m_k}) \exp \left( \frac{\rho}{1 - \rho} I_k'(x_{m_k};\hat{x}_{\mathcal{K}},\boldsymbol{y}) \right)}{\sum_{m_k'} P_k'(x_{m_k'}) \exp \left( \frac{\rho}{1 - \rho} I_k'(x_{m_k'};\hat{x}_{\mathcal{K}},\boldsymbol{y}) \right)}.
 		\label{eq:optimal_relative_distribution}
-					\end{align}
-				\end{subequations}
-				where we define $u_k'(\bar{c}_{m_k}) \triangleq \exp \left( \frac{\rho}{1 - \rho} I_k'(\bar{c}_{m_k};\boldsymbol{y},z) \right)$.
-Although $P_k(\bar{c}_{i_k}) = 1 - \sum_{m_k \ne i_k} P_k^{\star}(\bar{c}_{m_k})$ is not guaranteed to be optimal, it has exactly the same form as \eqref{eq:optimal_relative_distribution}.
-In such case, the solution of choosing $i_k$ as reference would coincide with that of choosing any $m_k \ne i_k$ as reference, while optimality for $i_k$ is guaranteed in the latter case.
-Therefore, for a fixed $P_{\mathcal{K}}'(\bar{c}_{m_{\mathcal{K}}})$, $\forall i_k \in \mathcal{M}$ and $\forall k \in \mathcal{K}$, \eqref{eq:optimal_relative_distribution} ensures
+	\end{equation}
+
+	Although it seems $P_k(x_{i_k}) = 1 - \sum_{m_k \ne i_k} P_k^\star(x_{m_k})$ has no optimality guarantee, we can verify that $P_k(x_{i_k})$ has exactly the same form as \eqref{eq:optimal_relative_distribution}.
+	It implies the selection of reference state does not matter and \eqref{eq:optimal_relative_distribution} is indeed optimal $\forall m_k \in \mathcal{M}$.
+	Therefore, for a fixed $P_{\mathcal{K}}'(x_{m_{\mathcal{K}}})$, choosing $P_k(x_{m_k})$ by \eqref{eq:optimal_relative_distribution} ensures
 	\begin{equation}
-					J \left( P_{\mathcal{K}}(\bar{c}_{m_{\mathcal{K}}}),P_{\mathcal{K}}'(\bar{c}_{m_{\mathcal{K}}}) \right) \ge I'(\bar{c}_{\mathcal{K}};\boldsymbol{y},z).
+		J \left( P_{\mathcal{K}}(x_{m_{\mathcal{K}}}),P_{\mathcal{K}}'(x_{m_{\mathcal{K}}}) \right) \ge I'(x_{\mathcal{K}};\hat{x}_{\mathcal{K}},\boldsymbol{y}).
 		\label{eq:information_difference_lower}
@@
 
-				On the other hand, choosing $P_k(\bar{c}_{m_k})$ by \eqref{eq:optimal_relative_distribution} also satisfies
+	On the other hand, \eqref{eq:optimal_relative_distribution} also guarantees
 	\begin{subequations}
@@
 			\Delta
-						& \triangleq I(\bar{c}_{\mathcal{K}};\boldsymbol{y},z) - J \left( P_{\mathcal{K}}(\bar{c}_{m_{\mathcal{K}}}),P_{\mathcal{K}}'(\bar{c}_{m_{\mathcal{K}}}) \right)\\
-						& = (1 - \rho) \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(\bar{c}_{m_{\mathcal{K}}}) \sum_j P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K}}}) \log \frac{P'(\bar{z}_j) P_k(\bar{c}_{m_k})}{P(\bar{z}_j) P_k'(\bar{c}_{m_k})}\\
-						& = (1 - \rho) \sum_{m_k} \frac{P_k'(\bar{c}_{m_k}) u_k'(\bar{c}_{m_k})}{\sum_{m_k'} P_k'(\bar{c}_{m_k'}) u_k'(\bar{c}_{m_k'})} \sum_j P(\bar{z}_j \mid \bar{c}_{m_k})\nonumber\\
-						& \quad \times \log \frac{\sum_{m_k'} P_k'(\bar{c}_{m_k'}) P(\bar{z}_j \mid \bar{c}_{m_k'}) u_k'(\bar{c}_{m_k})}{\sum_{m_k'} P_k'(\bar{c}_{m_k'}) P(\bar{z}_j \mid \bar{c}_{m_k'}) u_k'(\bar{c}_{m_k'})}\\
-						& \ge (1 - \rho) \sum_{m_k} \frac{P_k'(\bar{c}_{m_k}) u_k'(\bar{c}_{m_k})}{\sum_{m_k'} P_k'(\bar{c}_{m_k'}) u_k'(\bar{c}_{m_k'})} \sum_j P(\bar{z}_j \mid \bar{c}_{m_k})\nonumber\\
-						& \quad \times \left( 1 - \frac{\sum_{m_k'} P_k'(\bar{c}_{m_k'}) P(\bar{z}_j \mid \bar{c}_{m_k'}) u_k'(\bar{c}_{m_k'})}{\sum_{m_k'} P_k'(\bar{c}_{m_k'}) P(\bar{z}_j \mid \bar{c}_{m_k'}) u_k'(\bar{c}_{m_k})} \right)\\
+			 & \triangleq I(x_{\mathcal{K}};\hat{x}_{\mathcal{K}},\boldsymbol{y}) - J \left( P_{\mathcal{K}}(x_{m_{\mathcal{K}}}),P_{\mathcal{K}}'(x_{m_{\mathcal{K}}}) \right)                                                                                                                               \\
+			 & = (1 - \rho) \sum_{m_k} \frac{P_k'(x_{m_k}) f_k'(x_{m_k};\hat{x}_{\mathcal{K}},\boldsymbol{y})}{\sum_{m_k'} P_k'(x_{m_k'}) f_k'(x_{m_k'};\hat{x}_{\mathcal{K}},\boldsymbol{y})} \sum_{m_{\mathcal{K}}''} P(\hat{x}_{m_{\mathcal{K}}''} \mid x_{m_k})\nonumber                                  \\
+			 & \quad \times \log \frac{\sum_{m_k'} P_k'(x_{m_k'}) P(\hat{x}_{m_{\mathcal{K}}''} \mid x_{m_k'}) f_k'(x_{m_k};\hat{x}_{\mathcal{K}},\boldsymbol{y})}{\sum_{m_k'} P_k'(x_{m_k'}) P(\hat{x}_{m_{\mathcal{K}}''} \mid x_{m_k'}) f_k'(x_{m_k'};\hat{x}_{\mathcal{K}},\boldsymbol{y})}               \\
+			 & \ge (1 - \rho) \sum_{m_k} \frac{P_k'(x_{m_k}) f_k'(x_{m_k};\hat{x}_{\mathcal{K}},\boldsymbol{y})}{\sum_{m_k'} P_k'(x_{m_k'}) f_k'(x_{m_k'};\hat{x}_{\mathcal{K}},\boldsymbol{y})} \sum_{m_{\mathcal{K}}''} P(\hat{x}_{m_{\mathcal{K}}''} \mid x_{m_k})\nonumber                                \\
+			 & \quad \times \left( 1 - \frac{\sum_{m_k'} P_k'(x_{m_k'}) P(\hat{x}_{m_{\mathcal{K}}''} \mid x_{m_k'}) f_k'(x_{m_k'};\hat{x}_{\mathcal{K}},\boldsymbol{y})}{\sum_{m_k'} P_k'(x_{m_k'}) P(\hat{x}_{m_{\mathcal{K}}''} \mid x_{m_k'}) f_k'(x_{m_k};\hat{x}_{\mathcal{K}},\boldsymbol{y})} \right) \\
 			 & = 0,
@@
 	\end{subequations}
-				where the equality holds if and only if \eqref{eq:optimal_relative_distribution} converges.
-Combining \eqref{eq:information_difference_lower} and \eqref{eq:information_difference_upper} suggests $I(\bar{c}_{\mathcal{K}};\boldsymbol{y},z) \ge I'(\bar{c}_{\mathcal{K}};\boldsymbol{y},z)$.
-Since mutual information is bounded above, we conclude sequence \eqref{eq:optimal_distribution} is non-decreasing and convergent in mutual information.
+	where $f_k'(x_{m_k};\hat{x}_{\mathcal{K}},\boldsymbol{y}) \triangleq \exp \left( \frac{\rho}{1 - \rho} I_k'(x_{m_k};\hat{x}_{\mathcal{K}},\boldsymbol{y}) \right)$ and the equality holds if and only if \eqref{eq:optimal_relative_distribution} converges.
+	\eqref{eq:information_difference_lower} and \eqref{eq:information_difference_upper} together imply $I(x_{\mathcal{K}};\hat{x}_{\mathcal{K}},\boldsymbol{y}) \ge I'(x_{\mathcal{K}};\hat{x}_{\mathcal{K}},\boldsymbol{y})$.
+	Since mutual information is bounded above, we conclude the sequence \eqref{eq:input_kkt_solution} is non-decreasing and convergent in mutual information.
 
-				We then prove any converging point of sequence \eqref{eq:optimal_distribution}, denoted as $P_k^{\star}(\bar{c}_{m_k})$, fulfills the optimal conditions \eqref{eq:optimal_conditions} and achieves the weighted primary-backscatter sum capacity.
-To see this, define
+	Next, we prove that any converging point of sequence \eqref{eq:input_kkt_solution}, denoted as $P_k^\star(x_{m_k})$, fulfills \gls{kkt} conditions \eqref{eq:input_kkt_condition}.
+	To see this, consider $P_k^{(0)}(x_{m_k}) > 0$ and define
 	\begin{equation}
-					D_k^{(r)}(\bar{c}_{m_k}) \triangleq \frac{P_k^{(r+1)}(\bar{c}_{m_k})}{P_k^{(r)}(\bar{c}_{m_k})} = \frac{u_k^{(r)}(\bar{c}_{m_k})}{\sum_{m_k'} P_k^{(r)}(\bar{c}_{m_k'}) u_k^{(r)}(\bar{c}_{m_k'})},
+		D_k^{(r)}(x_{m_k}) \triangleq \frac{P_k^{(r+1)}(x_{m_k})}{P_k^{(r)}(x_{m_k})} = \frac{f_k^{(r)}(x_{m_k};\hat{x}_{\mathcal{K}},\boldsymbol{y})}{\sum_{m_k'} P_k^{(r)}(x_{m_k'}) f_k^{(r)}(x_{m_k'};\hat{x}_{\mathcal{K}},\boldsymbol{y})}.
 	\end{equation}
-				where $P_k^{(0)}(\bar{c}_{m_k}) > 0$.
-As sequence \eqref{eq:optimal_distribution} is convergent, any state with $P_k^{\star}(\bar{c}_{m_k}) > 0$ need to satisfy $D_k^{\star}(\bar{c}_{m_k}) \triangleq \lim_{r \to \infty} D_k^{(r)}(\bar{c}_{m_k}) = 1$, namely
+
+	As sequence \eqref{eq:input_kkt_solution} is convergent, any state with $P_k^\star(x_{m_k}) > 0$ need to satisfy $D_k^\star(x_{m_k}) \triangleq \lim_{r \to \infty} D_k^{(r)}(x_{m_k}) = 1$, namely
 	\begin{equation}
-					I_k^{\star}(\bar{c}_{m_k};\boldsymbol{y},z) = \frac{1 - \rho}{\rho} \log \sum_{m_k'} P_k^{\star}(\bar{c}_{m_k'}) u_k^{\star}(\bar{c}_{m_k'}),
+		I_k^\star(x_{m_k};\hat{x}_{\mathcal{K}},\boldsymbol{y}) = \frac{1 - \rho}{\rho} \log \sum_{m_k'} P_k^\star(x_{m_k'}) f_k^\star(x_{m_k'};\hat{x}_{\mathcal{K}},\boldsymbol{y}),
 	\end{equation}
-				which coincides with \eqref{eq:probable_states_marginal} and implies \eqref{eq:probable_states}.
-That is, given $P_k^{(0)}(\bar{c}_{m_k}) > 0$, any converging point with $P_k^{\star}(\bar{c}_{m_k}) > 0$ must satisfy \eqref{eq:probable_states}.
-				On the other hand, we assume $P_k^{\star}(\bar{c}_{m_k})$ does not satisfy \eqref{eq:dropped_states}, such that for any state with $P_k^{\star}(\bar{c}_{m_k}) = 0$,
-				% On the other hand, we show if $P_k^{\star}(\bar{c}_{m_k})$ does not satisfy \eqref{eq:dropped_states}, then it is not a converging point of sequence \eqref{eq:optimal_distribution}.
-By this assumption, for any state with $P_k^{\star}(\bar{c}_{m_k}) = 0$,
+	which is reminiscent of \eqref{eq:probable_states_marginal} (and hence \eqref{eq:probable_states}).
+	That is to say, given $P_k^{(0)}(x_{m_k}) > 0$, any converging point with $P_k^\star(x_{m_k}) > 0$ must satisfy \eqref{eq:probable_states}.
+	On the other hand, we assume $P_k^\star(x_{m_k})$ does not satisfy \eqref{eq:dropped_states}, such that for any state with $P_k^\star(x_{m_k}) = 0$,
+	% On the other hand, we show if $P_k^\star(x_{m_k})$ does not satisfy \eqref{eq:dropped_states}, then it is not a converging point of sequence \eqref{eq:input_kkt_solution}.
+By this assumption, for any state with $P_k^\star(x_{m_k}) = 0$,
 	\begin{equation}
-					I_k^{\star}(\bar{c}_{m_k};\boldsymbol{y},z) > I^{\star}(c_{\mathcal{K}};\boldsymbol{y},z) = \sum_{m_k'} P_k^{\star}(\bar{c}_{m_k'}) I_k^{\star}(\bar{c}_{m_k'};\boldsymbol{y},z),
+		I_k^\star(x_{m_k};\hat{x}_{\mathcal{K}},\boldsymbol{y}) > I^\star(x_{\mathcal{K}};\hat{x}_{\mathcal{K}},\boldsymbol{y}) = \sum_{m_k'} P_k^\star(x_{m_k'}) I_k^\star(x_{m_k'};\hat{x}_{\mathcal{K}},\boldsymbol{y}),
 	\end{equation}
-				where the equality origins from \eqref{eq:backscatter_sum_rate_expectation} and \eqref{eq:primary_ergodic_rate_expectation}.
-Since the exponential function is monotonically increasing, we have $u_k^{\star}(\bar{c}_{m_k}) > \sum_{m_k'} P_k^{\star}(\bar{c}_{m_k'}) u_k^{\star}(\bar{c}_{m_k'})$ and $D_k^{\star}(\bar{c}_{m_k}) > 1$.
-Considering $P_k^{(0)}(\bar{c}_{m_k}) > 0$ and $P_k^{\star}(\bar{c}_{m_k}) = 0$, it contradicts with
+	where the equality inherits from \eqref{eq:weighted_sum_mutual_information}.
+	Since the exponential function is monotonically increasing, we have $f_k^\star(x_{m_k};\hat{x}_{\mathcal{K}},\boldsymbol{y}) > \sum_{m_k'} P_k^\star(x_{m_k'}) f_k^\star(x_{m_k'};\hat{x}_{\mathcal{K}},\boldsymbol{y})$ and $D_k^\star(x_{m_k}) > 1$.
+	Considering $P_k^{(0)}(x_{m_k}) > 0$ and $P_k^\star(x_{m_k}) = 0$, it contradicts with
 	\begin{equation}
-					P_k^{(r)}(\bar{c}_{m_k}) = P_k^{(0)}(\bar{c}_{m_k}) \prod_{n=1}^r D_k^{(n)}(\bar{c}_{m_k}).
+		P_k^{(r)}(x_{m_k}) = P_k^{(0)}(x_{m_k}) \prod_{n=1}^r D_k^{(n)}(x_{m_k}).
 	\end{equation}
-				Therefore, given $P_k^{(0)}(\bar{c}_{m_k}) > 0$, any converging point with $P_k^{\star}(\bar{c}_{m_k}) = 0$ must satisfy \eqref{eq:dropped_states}.
-
-				In conclusion, sequence \eqref{eq:optimal_distribution} always converges to a weighted sum capacity-achieving distribution for state $m_k$ of tag $k$.
-			\end{proof}
+	Therefore, given $P_k^{(0)}(x_{m_k}) > 0$, any converging point with $P_k^\star(x_{m_k}) = 0$ must satisfy \eqref{eq:dropped_states}.
+	This completes the proof.
+	\qedsymbol
+	\label{ap:input_kkt_solution}
 \end{subsection}
 
-		\begin{subsection}{Decision region}
-			As indicated by \cite{Qian2019b}, the optimal \gls{ml} decision regions are very close to the optimal decision regions to problem \eqref{op:rate_region}.
-We can either use \eqref{eq:decision_region} as suboptimal, or take derivative of \eqref{eq:backscatter_sum_rate} w.r.t.
-$t_{i-1,i}$ and $t_{i,i+1}$ (however, closed-form solutions are unavailable and two-dimensional search is needed).
+\begin{subsection}{Proof of Proposition \ref{pr:threshold}}
+Since $L$ input letters are with non-zero probability and $x \to z \to \hat{x}$ formulates a Markov chain, we need $L$ non-empty decision regions and at least $L+1$ distinct thresholds (including \num{0} and $\infty$) to minimize the distortion between source and decision.
+On the other hand, the optimal decision regions are apparently empty for those unused letters.
+
+Suppose the optimal number of thresholds is $S+1$ where $S \ge L$.
+Let $\boldsymbol{t} \triangleq [t_0,\ldots,t_S]^T \in \mathbb{R}_{+}^{(S+1) \times 1}$ be the optimal threshold vector where $t_{s-1} < t_s$, $\forall s \in \mathcal{S} \triangleq \{1,\ldots,S\}$.
+Since the optimal decision region for any letter may consist of multiple partitions, without loss of generality, we assume the mapping from threshold vector to decision region $l' \in \mathcal{L} \triangleq \{1,\ldots,L\}$ is given by $\mathcal{R}_{l'} = \bigcup_{s \equiv l' \pmod L} [t_{s-1},t_s)$.
+\footnote{
+	The proof holds for any valid mapping from threshold vector to decision regions, and we consider this specific case for the ease of presentation.
+}
+The threshold optimization problem is
+\begin{maxi!}
+{\scriptstyle{\boldsymbol{t}}}{I_{\mathrm{B}}(x;\hat{x})}{\label{op:decision_threshold}}{\label{ob:backscatter_mutual_information}}
+\addConstraint{t_{s-1}}{< t_s,}{\quad \forall s \in \mathcal{S}.}{\label{co:strict_inequality}}
+\end{maxi!}
+
+Problem \eqref{op:decision_threshold} is intricate due to the strict inequality constraint \eqref{co:strict_inequality}.
+Following \cite{Nguyen2020}, we first relax it to the convex counterpart, then discard the solutions that violate any original constraint.
+The Lagrangian function for the relaxed problem is
+\begin{equation}
+	L = - I_{\mathrm{B}}(x;\hat{x}) + \sum_{s \in \mathcal{S}} \mu_s (t_{s-1} - t_s),
+\end{equation}
+where $\mu_s$ is the Lagrange multiplier associated with the non-strict version of \eqref{co:strict_inequality}.
+The \gls{kkt} conditions on the optimal primal and dual solutions are, $\forall s \in \mathcal{S}$,
+\begin{subequations}
+	\label{eq:kkt_thresholding}
+	\begin{equation}
+		- \nabla_{t_s^\star} I^\star_{\mathrm{B}}(x;\hat{x}) + \mu_{s-1}^\star - \mu_s^\star = 0,
+		\label{eq:stationarity}
+	\end{equation}
+	\begin{equation}
+		\mu_s^\star \ge 0,
+		\label{eq:dual_feasibility}
+	\end{equation}
+	\begin{equation}
+		\mu_s^\star (t_{s-1}^\star - t_s^\star) = 0.
+		\label{eq:complementary_slackness}
+	\end{equation}
+
+\end{subequations}
+Due to the strict inequality constraint \eqref{co:strict_inequality}, conditions \eqref{eq:dual_feasibility} and \eqref{eq:complementary_slackness} together imply $\mu_s^\star = 0$, $\forall s \in \mathcal{S}$.
+Besides, it is trivial to conclude $t_0^\star = 0$ for energy-based detection.
+As such, the necessary optimality conditions for problem \eqref{op:decision_threshold}, $s \in \mathcal{S}$,
+\begin{equation}
+	\nabla_{t_{s}^\star} I^\star_{\mathrm{B}}(x;\hat{x}) = 0,
+\end{equation}
+which can be explicitly written as
+\begin{equation}
+	\sum_l P(x_l) \frac{(t_s^\star)^{N-1} e^{-t_s^\star/\sigma_l^2}}{\sigma_l^{2N} (N-1)!} \log \frac{P(x_l \mid \hat{x}_{l'+1})}{P(x_l \mid \hat{x}_{l'})} = 0,
+	\label{eq:kkt_threshold_explicit}
+\end{equation}
+where $l' \equiv s \pmod L$.
+According to \cite{Nguyen2020a}, the optimal backward channel quantizer is convex and separates each pair of posterior distribution by a hyperplane.
+It implies the sequence $\{\log {P(x_l \mid \hat{x}_{l'+1})}/{P(x_l \mid \hat{x}_{l'})}\}_{l \in \mathcal{L}}$ changes sign exactly once.
+We notice the left-hand side of \eqref{eq:kkt_threshold_explicit} is a generalized Dirichlet polynomial, which has at most one real solution by Descartes' rule of signs \cite{Jameson2006}.
+In other words, starting from $t_0^\star$, each optimal decision region requires at most one additional distinct threshold, and we have $S \le L$.
+Therefore, we conclude $S = L$ and the proof is completed.
+\qedsymbol
+\label{ap:threshold}
 \end{subsection}
+\end{appendix}
 
-		\begin{subsection}{Precoder}
-			Interestingly, we can design precoder to adjust the expectation of the received power \eqref{eq:receive_variance} at each tag input combination, which can avoid the detection blind spots in \cite{Qian2019} and further boost the weighted sum-rate.
-However, the problem is highly non-convex -- the information function associated with input combination state $i$ is
-			\begin{align}
-				I(\bar{c}_i;z)
-				& = \sum_{j \in \mathcal{I}} \int_{t_{j-1,j}}^{t_{j,j+1}} \frac{z^{N-1} \exp \left(-\frac{z}{\mathrm{tr}(H_{\mathrm{E},i} W) + \sigma_w^2}\right)}{\left(\mathrm{tr}(H_{\mathrm{E},i} W) + \sigma_w^2\right)^N (N-1)!} \dd z\nonumber\\
-				& \quad \times \log \frac{\int_{t_{j-1,j}}^{t_{j,j+1}} \frac{z^{N-1} \exp \left(-\frac{z}{\mathrm{tr}(H_{\mathrm{E},i} W) + \sigma_w^2}\right)}{\left(\mathrm{tr}(H_{\mathrm{E},i} W) + \sigma_w^2\right)^N (N-1)!} \dd z}{\sum_{i' \in \mathcal{I}} \int_{t_{j-1,j}}^{t_{j,j+1}} \frac{z^{N-1} \exp \left(-\frac{z}{\mathrm{tr}(H_{\mathrm{E},i'} W) + \sigma_w^2}\right)}{\left(\mathrm{tr}(H_{\mathrm{E},i'} W) + \sigma_w^2\right)^N (N-1)!} \dd z},
-				\label{eq:foo}
-			\end{align}
-			and the mutual information can be expressed as a function of $W$ by combining \eqref{eq:backscatter_sum_rate} and \eqref{eq:foo}.
-
-			So far I have no idea how to solve this issue, and found no reference regarding precoder design for \gls{ambc}/\gls{sr} with discrete channels (although some naive combiner designs are available for \gls{bibo}).
-Personally, I believe the precoder design is the key to (i) boost the rate region and avoid blind spots in conventional \gls{ambc}; (ii) build our proposal over existing infrastructures.
-Ideally, assuming the number of transmit antennas $Q$ is larger than the number of tags $K$, the optimal energy levels should be almost uniformly spaced (as $z$ follows Erlang distribution) to concentrate the channel transitional probability on diagonal as possible.
-		\end{subsection}
-	\end{section}
 \bibliographystyle{IEEEtran}
-	\bibliography{IEEEabrv,library.bib}
+\bibliography{library.bib}
 \end{document}

### 2022-04-18 main.tex
:pencil: Update manuscript

@@
 	\end{equation}
-	where $\alpha \in [0,1]$ models the (amplitude) harvest-backscatter efficiency at the direction of interest.
+	where $\alpha \in [0,1]$ models the harvest-backscatter ratio at the direction of interest.
 	For passive tags, $\alpha \ll 1$ is commonly assumed as the majority of the incident wave can be harvested to support tag modules \cite{Thomas2012a}.
@@
 	\end{subsection}
-
 \end{section}
@@
 		Besides, it is trivial to conclude $t_0^\star = 0$ for energy-based detection.
-As such, the necessary optimality conditions for problem \eqref{op:decision_threshold}, $s \in \mathcal{S}$,
+		As such, the necessary optimality conditions for problem \eqref{op:decision_threshold}, $\forall s \in \mathcal{S}$,
 		\begin{equation}
@@
 		\end{equation}
-which can be explicitly written as
+		which can be explicitly written as, $\forall s \equiv l' \pmod L$,
 		\begin{equation}
@@
 		\end{equation}
-where $l' \equiv s \pmod L$.
-According to \cite{Nguyen2020a}, the optimal backward channel quantizer is convex and separates each pair of posterior distribution by a hyperplane.
-It implies the sequence $\{\log {P(x_l \mid \hat{x}_{l'+1})}/{P(x_l \mid \hat{x}_{l'})}\}_{l \in \mathcal{L}}$ changes sign exactly once.
-We notice the left-hand side of \eqref{eq:kkt_threshold_explicit} is a generalized Dirichlet polynomial, which has at most one real solution by Descartes' rule of signs \cite{Jameson2006}.
+
+		According to \cite{He2021}, the optimal backward channel quantizer is convex and separates each pair of posterior distribution by a hyperplane.
+		It implies, for a given output letter $l'$, the sequence $\{\log {P(x_l \mid \hat{x}_{l'+1})}/{P(x_l \mid \hat{x}_{l'})}\}_{l \in \mathcal{L}}$ changes sign exactly once.
+		We notice the left-hand side of \eqref{eq:kkt_threshold_explicit} is a generalized Dirichlet polynomial, and by Descartes' rule of signs \cite{Jameson2006}, has at most one positive solution.
+		% TODO
 		In other words, starting from $t_0^\star$, each optimal decision region requires at most one additional distinct threshold, and we have $S \le L$.

### 2022-04-25 main.tex
:pencil: Add tag equivalent circuit

@@
 \begin{section}{Backscatter Principles}
+	% \begin{figure}[!t]
+	% 	\centering
+	% 	\resizebox{0.6\columnwidth}{!}{
+	% 		\begin{circuitikz}[transform shape]
+	% 			\coordinate (O) at (0,0);
+	% 			\node[block,from={O to $(O) + (6.375,3.25)$}](T){};
+	% 			\draw (0,1.75)
+	% 			to[short] ++(-0.875,0)
+	% 			to[short] ++(0,0.5) node[bareantenna](A){Bx};
+	% 			\draw (0,1.75)
+	% 			to[short,-*] ++(0.25,0) coordinate(J);
+	% 			\draw (J)
+	% 			to[short] ++(0,1)
+	% 			to[short] ++(0.5,0) coordinate(J1);
+	% 			\node[block,from={$(J1) + (0,-0.25)$ to $(J1) + (2.5,0.25)$}](R){Rectifier};
+	% 			\draw (J)
+	% 			to[short] ++(0.5,0) coordinate(J2);
+	% 			\node[block,from={$(J2) + (0,-0.25)$ to $(J2) + (2.5,0.25)$}](D){Demodulator};
+	% 			\draw (J)
+	% 			to[short] ++(0,-1)
+	% 			to[short] ++(0.5,0) coordinate(J3)
+	% 			to [vR,mirror,invert,/tikz/circuitikz/bipoles/length=1cm] ++(1.75,0) node[ground,rotate=90]{};
+	% 			\node[block,from={$(J3) + (0,-0.25)$ to $(J3) + (2.5,0.25)$},draw=none](M){};
+	% 			\draw ($(J3) + (0,-0.25)$) rectangle ($(J3) + (2.5,0.25)$);
+	% 			\draw ($(J3) + (1.25,-0.5)$) node[]{Modulator};
+	% 			\draw[dashed,-{Latex[length=2mm]}] (R.east) -- ++(0.75,0);
+	% 			\draw[-{Latex[length=2mm]}] (D.east) -- ++(0.75,0);
+	% 			\draw[{Latex[length=2mm]}-] (M.east) -- ++(0.75,0);
+	% 			\node[block,from={$(R.east) + (0.75,-0.25)$ to $(R.east) + (2.875,0.25)$}](P){Power buffer};
+	% 			\node[block,from={$(M.east) + (0.75,-0.25)$ to $(D.east) + (2.875,0.25)$}](S){Digital\\section};
+	% 			\draw[dashed,-{Latex[length=2mm]}] (P.south) to (S.north);
+	% 			\coordinate (F1) at ($(P.south)!0.5!(S.north)$);
+	% 			\coordinate (F2) at ($(D.east)!0.5!(S.west)$);
+	% 			\coordinate (F3) at ($(D.south)!0.5!(M.north)$);
+	% 			\draw[dashed] (F1) to (F1-|D.north);
+	% 			\draw[dashed,-{Latex[length=2mm]}] (F1-|D.north) to (D.north);
+	% 			\draw[dashed] (F1-|F2) to (F2|-F3) to (M|-F3);
+	% 			\draw[dashed,-{Latex[length=2mm]}] (M|-F3) to (M.north);
+	% 		\end{circuitikz}
+	% 	}
+	% 	\caption{The block diagram and equivalent circuit of a passive tag. The solid and dashed vectors represent signal and energy flows.}
+	% 	\label{fi:tag_block_diagram}
+	% \end{figure}
+
 	\begin{figure}[!t]
 		\centering
-		\subfloat[Passive tag structure]{
+		\subfloat[Block diagram]{
 			\resizebox{0.6\columnwidth}{!}{
@@
 					\draw ($(J3) + (1.25,-0.5)$) node[]{Modulator};
-					\draw[-{Latex[length=2mm]}] (R.east) -- ++(0.75,0);
+					\draw[dashed,-{Latex[length=2mm]}] (R.east) -- ++(0.75,0);
 					\draw[-{Latex[length=2mm]}] (D.east) -- ++(0.75,0);
@@
 			}
-			\label{fi:passive_tag_structure}
+			\label{fi:block_diagram}
 		}
-		\subfloat[Equivalent model]{
+		\setcounter{subfigure}{2}%
+		\subfloat[Scatter model]{
 			\resizebox{0.35\columnwidth}{!}{
 				\begin{circuitikz}[transform shape]
+					\tikzstyle{every node}=[font=\Large]
 					\draw (0,0) node[bareantenna](bareantenna){};
@@
 					\draw (bareantenna)
-					to [R=$Z_{\mathrm{A}}$,font=\Large,/tikz/circuitikz/bipoles/length=1cm] ++(0,-1.5) node[rotary switch=4 in 90 wiper 30,anchor=ext center,rotate=270](SW){};
+					to [R=$Z_{\mathrm{A}}$] ++(0,-1.5) node[rotary switch=4 in 90 wiper 30,anchor=ext center,rotate=270](SW){};
 					\draw (SW.cout 2) node[below=0.1cm,font=\Large]{$m$}
-					to [R=$Z_m$,font=\Large,/tikz/circuitikz/bipoles/length=1cm] ++(2,0) node[ground]{};
+					to [R=$Z_m$] ++(2,0) node[ground]{};
 				\end{circuitikz}
 			}
-			\label{fi:equivalent_model}
+			\label{fi:scatter_model}
 		}
-		\caption{For a passive tag, the rectifier and demodulator rely on the incident electromagnetic wave for energy harvesting and source decoding, while the load-switcher adjusts the reradiated signal for backscatter modulation.}
-		\label{fi:tag}
+		\setcounter{subfigure}{1}
+		\subfloat[Equivalent circuit]{
+			\resizebox{0.9\columnwidth}{!}{
+				\begin{circuitikz}[transform shape]
+					\tikzstyle{every node}=[font=\Large]
+					\draw (0,0) coordinate(O)
+					to [sV,l=$V_0$] ++(0,1.5)
+					to [L,l=$X_{\mathrm{A}}$] ++(0,1.5)
+					to [R=$R_{\mathrm{A}}$,-*] ++(3,0) coordinate(AM)
+					to [sI,l_=$I_0$,-*] ++(0,-3)
+					to [short] (O);
+					\draw (AM)
+					to [short] ++(0.5,0)
+					to [L,l=$X_m$,-*] ++(3,0) coordinate(M)
+					to [R=$R_m^{\mathrm{S}}$] ++(3,0) coordinate(MH);
+					\draw (M)
+					to [R=$R_m^{\mathrm{P}}$,-*] ++(0,-3);
+					\draw (MH)
+					to [D,-*] ++(1.5,0) coordinate(H)
+					to [C=$X_{\mathrm{H}}$,-*] ++(0,-3);
+					\draw (H)
+					to [short] ++(1.5,0)
+					to [R=$R_{\mathrm{H}}$] ++(0,-3)
+					to [short] (O);
+
+					\draw [blue,dashed] (-1.125,-0.5) rectangle (3.5,4);
+					\draw [yellow,dashed] (4,-0.5) rectangle (9,4);
+					\draw [red,dashed] (9.5,-0.5) rectangle (13.5,4);
+
+					\draw [blue] (1.125,4.25) node[]{Antenna};
+					\draw [yellow] (6.5,4.25) node[]{Modulator};
+					\draw [red] (11.5,4.25) node[]{Harvester + Chip};
+
+					\draw (3.375,2.675) to [short] (3.375,3.175) to [short] (3.25,3.175) to [short,i_=$Z_{\mathrm{A}}$] (3.125,3.175);
+					\draw (4.125,-0.125) to [short] (4.125,0.375) to [short] (4.25,0.375) to [short,i=$Z_m$] (4.375,0.375);
+					\draw (9.625,-0.125) to [short] (9.625,0.375) to [short] (9.75,0.375) to [short,i=$Z_{\mathrm{H}}$] (9.875,0.375);
+				\end{circuitikz}
+			}
+			\label{fi:equivalent_circuit}
+		}
+		\caption{Block diagram, equivalent circuit, and scatter model of a typical passive tag.
+The solid and dashed vectors represent signal and energy flows.
+The backscatter antenna behaves as a constant power source, where the voltage $V_0$ and current $I_0$ are introduced by incident electric field $\vec{E}_{\mathrm{I}}$ and magnetic field $\vec{H}_{\mathrm{I}}$ \cite{Huang2021}.}
 	\end{figure}
-	Consider a bistatic backscatter system with an excitation source, multiple (semi-)passive tags, and a backscatter reader.
-	The structure of a passive tag is shown in Fig. \subref*{fi:passive_tag_structure}.
-	It typically consists of a scattering antenna, an energy harvester, an integrated receiver, a load-switching modulator, and on-chip components (e.g., micro-controller and sensors) \cite{Dobkin2012}.
-	When a tag is illuminated, a portion of the impinging signal is absorbed while the remaining is scattered back, and the tag can harvest energy, transmit message, and decode the source if necessary.
-	According to \cite{Hansen1989}, the backscatter signal can be decomposed into a \emph{structural component} that depends on the antenna geometry and material properties, and an \emph{antenna component} that depends on the antenna-load impedance mismatch.
-	The former contributes to environment multipath and can be modeled by channel estimation \cite{Boyer2014}, while the latter can be utilized for backscatter modulation.
-	As illustrated by Fig. \subref*{fi:equivalent_model}, if $M$ symbol states are available at the tag, the reflection coefficient at state $m \in \mathcal{M} \triangleq \{1,\ldots,M\}$ is
-	\footnote{
+	% In a bistatic backscatter system,
+	% Consider a bistatic backscatter system with an excitation source, multiple passive tags, and a backscatter reader.
+	Passive backscatter devices (a.k.a., tags) harvest energy from and modulate information over surrounding \gls{rf} signal.
+	As shown in Fig.
+\subref*{fi:block_diagram}, a typical passive tag consists of a scattering antenna, an energy harvester, an integrated receiver, a load-switching modulator, and on-chip components (e.g., micro-controller and sensors) \cite{Dobkin2012}.
+Its equivalent circuit is also given by Fig.
+\subref*{fi:equivalent_circuit}.
+	When illuminated, the tag absorbs a portion of the impinging wave and scatters the rest back to the space.
+	The absorbed signal can be used for source decoding and energy harvesting \cite{Kim2021a}, while the scattered signal can be decomposed into the \emph{structural} and \emph{antenna} mode components \cite{Hansen1989}.
+	The structural mode scattering applies to general objects and is related to the antenna structure, shape and material, which contributes to environment multipath and can be covered by channel estimation \cite{Boyer2014}.
+	On the other hand, the antenna mode scattering models the antenna radiation and depends on the antenna-load impedance mismatch, which can be used for backscatter modulation \cite{Boyer2012} or channel reconfiguration \cite{Wu2021b}.
+	Fig. \subref*{fi:scatter_model} illustrates the scatter model.
+	For a tag with $M$ candidate states, the reflection coefficient of state $m \in \mathcal{M} \triangleq \{1,\ldots,M\}$ is defined as
+	\begin{footnote}
 		It corresponds to a linear backscatter model where the reflection coefficient is irrelevant to incident electromagnetic field strength.
-	}
+	\end{footnote}
 	\begin{equation}
@@
 
-	Tags periodically switch between different states to perform backscatter modulation.
-	For $M$-ary \gls{qam}, the complex constellation point $c_m \in \mathcal{C}$ maps to the reflection coefficient by \cite{Thomas2012a}
+	\begin{subsection}{Backscatter Modulation}
+		In backscatter modulation, the tag \emph{periodically varies} the reflection coefficient to embed its own information.
+		As such, there exists a mapping from the alphabet to the set.
+		When the \gls{csi} and reflection alphabet $\{\Gamma_1,\ldots,\Gamma_M\}$ are available at the reader, it can decode the tag message from the observed scattered signal.
+
+		For $M$-ary \gls{qam}, the complex constellation point $c_m$ maps to the corresponding reflection coefficient by \cite{Thomas2012a}
 		\begin{equation}
@@
 		where $\alpha \in [0,1]$ models the harvest-backscatter ratio at the direction of interest.
+
+		% When the \gls{csi} and reflection alphabet $\{\Gamma_1,\ldots,\Gamma_M\}$ are available at the reader, the tag can be successfully decoded based on the received signal.
+
+	\end{subsection}
+
+	\begin{subsection}{Channel Reconfiguration}
+		2
+	\end{subsection}
+	% Tags periodically switch between different states to perform backscatter modulation.
+	% For $M$-ary \gls{qam}, the complex constellation point $c_m \in \mathcal{C}$ maps to the reflection coefficient by \cite{Thomas2012a}
+	% \begin{equation}
+	% 	\Gamma_m = \alpha \frac{c_m}{\max_{m'} \lvert c_{m'} \rvert},
+	% 	\label{eq:backscatter_modulation}
+	% \end{equation}
+	% where $\alpha \in [0,1]$ models the harvest-backscatter ratio at the direction of interest.
 	For passive tags, $\alpha \ll 1$ is commonly assumed as the majority of the incident wave can be harvested to support tag modules \cite{Thomas2012a}.
@@
 		We also assume the direct channel and all cascaded channels can be estimated and fed back to the \gls{ap}.
-		\footnote{
+		\begin{footnote}
 			Due to the lack of \gls{rf} chains at the passive tag, accurate and efficient \gls{csi} acquisition at the \gls{ap} can be challenging.
 			One possible approach is that the \gls{ap} sends pre-defined pilots, the tags respond in well-designed manners, and the user performs least-square estimation with feedbacks \cite{Bharadia2015,Yang2015b,Guo2019g}.
-		}
+		\end{footnote}
 
@@
 		Under perfect synchronization, the signal received by the user at primary symbol block $n \in \mathcal{N} \triangleq \{1,\ldots,N\}$ is
-		\footnote{
+		\begin{footnote}
 			We omit the signal reflected by two or more times\cite{Wu2019} and assume the time difference of arrival from different paths are negligible\cite{Guo2019b}.
-		}
+		\end{footnote}
 		\begin{equation}
@@
 		Interestingly, the sum-rate optimal input design for general discrete memoryless \gls{mac} remains an open problem, and we instead propose a \gls{kkt} solution to problem \eqref{op:input_probability_distribution}.
-		\footnote{
+		\begin{footnote}
 			As pointed out in \cite{Buhler2011}, \gls{kkt} conditions are only necessary for sum-rate optimality and these solutions may end up being saddle points.
-		}
+		\end{footnote}
 		\begin{proposition}
@@
 		Since the optimal decision region for any letter may consist of multiple partitions, without loss of generality, we assume the mapping from threshold vector to decision region $l' \in \mathcal{L} \triangleq \{1,\ldots,L\}$ is given by $\mathcal{R}_{l'} = \bigcup_{s \equiv l' \pmod L} [t_{s-1},t_s)$.
-		\footnote{
+		\begin{footnote}
 			The proof holds for any valid mapping from threshold vector to decision regions, and we consider this specific case for the ease of presentation.
-		}
+		\end{footnote}
 		The threshold optimization problem is

### 2022-04-28 main.tex
:pencil: Add abstract

@@
 \maketitle
+
+\begin{abstract}
+	Backscatter allows wireless nodes to harvest energy from, modulate information over, and reconfigure propagation of surrounding radio waves.
+	We introduce the concept of Metascatter, which adapts the input probability distribution of a finite-state backscatter device based on Channel State Information (CSI), to simultaneously act as parasitic source of Symbiotic Radio (SR) that conveys sensor data and reflecting element of Intelligent Reflecting Surface (IRS) that assists legacy transmission.
+	Using shared spectrum, energy, and infrastructures, fully cognitive networks can be built over Metascatter, and we consider a basic scenario where a multi-antenna Access Point (AP) and multiple Metascatter simultaneously transmit to a single-antenna user.
+	Since tags involve load switching and the primary and backscatter messages are multiplied (instead of superposed) in the received signal, it is assumed the user employ joint energy detection on all tags, then model their reflection pattern within the equivalent CSI for primary decoding.
+	We characterize the achievable primary-(sum-)backscatter rate region through a joint optimization of transmit beamforming vector at the AP, input probability distribution at the tags, and energy detection regions at the user.
+	A suboptimal solution is provided by the Block Coordinate Descent (BCD) method, where the beamforming, input distribution, and decision thresholds are obtained by Successive Convex Approximation (SCA), Karush–Kuhn–Tucker (KKT), and Dynamic Programming (DP), respectively.
+	Simulation results demonstrate Metascatter can exploit the additional backscatter path to transmit and assist.
+\end{abstract}
 

### 2022-05-22 main.tex
:art: Refactor code

@@
 		\end{equation}
-		where $\alpha \in [0,1]$ models the harvest-backscatter ratio at the direction of interest.
+		where $\alpha \in [0,1]$ models the amplitude scatter ratio at the direction of interest.
 
@@
 		For simplicity, we consider a quasi-static block fading model where the channel response remain constant within each coherence interval and vary independently between consecutive blocks.
-		Since backscatter modulation involves load switching, tags typically transmit at much lower rate, and we assume the backscatter symbol period is $N \in \mathbb{Z}_{++}$ times the primary symbol period.
+		% Since backscatter modulation involves load switching, tags typically transmit at much lower rate, and we assume the backscatter symbol period is $N \in \mathbb{Z}_{++}$ times the primary symbol period.
+		Since backscatter modulation involves load switching, tags typically transmit at much lower rate, and we assume the backscatter symbol length is $N \in \mathbb{Z}_{++}$ times the primary symbol length.
 		We also assume the direct channel and all cascaded channels can be estimated and fed back to the \gls{ap}.
@@
 		Similar to above, the primary information function of input combination $x_{m_{\mathcal{K}}}$ is
+		% TODO notation
 		\begin{equation}

### 2022-05-22 src/config/config.m

@@ -1,29 +1,51 @@
 %% * System
+% carrier frequency
+frequency = 9e8;
 % number of transmit antennas
 nTxs = 3;
 % number of tags
 nTags = 2;
-% modulation order
+% number of available states at tags (i.e., modulation order)
 nStates = 2;
-% input and output alphabet size
+% number of possible input and output tuples (i.e., alphabet size)
 [nInputs, nOutputs] = deal(nStates ^ nTags);
-% harvest-backscatter ratio
-reflectRatio = 0.5;
-% symbol period ratio
+% amplitude scatter ratio at tags
+scatterRatio = 0.5;
+% backscatter/primary symbol duration ratio
 symbolRatio = 10;
+% constellation diagram at tags
+constellation = normalize(qammod(transpose(0 : nStates - 1), nStates), 'norm', Inf);
+% constellation = transpose(exp(1i * 2 * pi * (0 : nStates - 1) / nStates));
 % average transmit power
-txPower = 10;
+% transmitPower = db2pow(6);
+transmitPower = 1e3;
 % average noise power
-noisePower = db2pow(-70);
-% backscatter symbol candidates
-constellation = qammod(0 : nStates - 1, nStates) ./ max(abs(qammod(0 : nStates - 1, nStates)));
+noisePower = db2pow(-160);
+% path loss exponents
+directExponent = 2.6;
+forwardExponent = 2.4;
+backwardExponent = 2;
+% angle of arrivals
+directAoa = 2 * pi * rand;
+forwardAoa = 2 * pi * rand(nTags, 1);
+backwardAoa = 2 * pi * rand(nTags, 1);
+% Ricean factors
+directFactor = 5;
+forwardFactor = 5;
+backwardFactor = 5;
+
+%% * Layout
+% coordinates
+ap = [5; 0];
+user = [0; 0];
+[tag(1, :), tag(2, :)] = pol2cart(2 * pi * rand(1, nTags), sqrt(1 * rand(1, nTags)));
+% distances
+directDistance = norm(ap - user);
+forwardDistance = vecnorm(ap - tag);
+backwardDistance = vecnorm(tag - user);
 
 %% * Algorithm
-% number of weights
-nWeights = 20;
-% primary-backscatter weight pairs
-weightSet = [linspace(0.5, 0.1, nWeights - 1), 1]; % For large rho, MRT to equivalent channel is nearly optimal; this does not hold for small rho
-% number of output discretization bins
-nBins = 2 ^ 8;
[…]

### 2022-05-22 src/lib/beamformer_bpgd.m

@@ -1,12 +1,12 @@
-function [beamformer, weightedSumRate] = beamformer_bpgd(weight, symbolRatio, equivalentChannel, txPower, noisePower, equivalentDistribution, threshold, tolerance, btls)
-
+function [beamformer, weightedSumRate] = beamformer_bpgd(weight, symbolRatio, equivalentChannel, transmitPower, noisePower, equivalentDistribution, threshold, tolerance, btls)
+% For large rho, MRT to equivalent channel is nearly optimal; this does not hold for small rho
 
 	% * Declare default tolerance
 	arguments
 		weight;
 		symbolRatio;
 		equivalentChannel;
-		txPower;
+		transmitPower;
 		noisePower;
 		equivalentDistribution;
 		threshold;
@@ -24,9 +24,9 @@ function [beamformer, weightedSumRate] = beamformer_bpgd(weight, symbolRatio, eq
 	nTxs = size(equivalentChannel, 2);
 
 	% * Initialize beamformer
-	beamformer = sqrt(txPower) * ctranspose(equivalentDistribution * equivalentChannel) / norm(equivalentDistribution * equivalentChannel);
+	beamformer = sqrt(transmitPower) * ctranspose(equivalentDistribution * equivalentChannel) / norm(equivalentDistribution * equivalentChannel);
 	a = rand(1, nTxs) + 1i * rand(1, nTxs);
-	beamformer = sqrt(txPower) * ctranspose(a) / norm(a);
+	beamformer = sqrt(transmitPower) * ctranspose(a) / norm(a);
 	weightedSumRate = weighted_sum_rate_local(weight, symbolRatio, equivalentChannel, noisePower, equivalentDistribution, beamformer, threshold);
 
 	% * Projected gradient descent
@@ -43,13 +43,13 @@ function [beamformer, weightedSumRate] = beamformer_bpgd(weight, symbolRatio, eq
 		y1 = weighted_sum_rate_local(weight, symbolRatio, equivalentChannel, noisePower, equivalentDistribution, beamformer, threshold);
 		t = 1;
 		beamformerCandidate = beamformer + t * gradient;
-		beamformerCandidate = sqrt(txPower) * beamformerCandidate / max(sqrt(txPower), norm(beamformerCandidate));
+		beamformerCandidate = sqrt(transmitPower) * beamformerCandidate / max(sqrt(transmitPower), norm(beamformerCandidate));
[…]

### 2022-05-22 src/lib/beamformer_newton.m

@@ -1,4 +1,4 @@
-function [beamformer, dmtc, weightedSumRate] = beamformer_newton(weight, symbolRatio, equivalentChannel, txPower, noisePower, equivalentDistribution, threshold, tolerance)
+function [beamformer, dmtc, weightedSumRate] = beamformer_newton(weight, symbolRatio, equivalentChannel, transmitPower, noisePower, equivalentDistribution, threshold, tolerance)
 
 
 	% * Declare default tolerance
@@ -6,7 +6,7 @@ function [beamformer, dmtc, weightedSumRate] = beamformer_newton(weight, symbolR
 		weight;
 		symbolRatio;
 		equivalentChannel;
-		txPower;
+		transmitPower;
 		noisePower;
 		equivalentDistribution;
 		threshold;
@@ -21,7 +21,7 @@ function [beamformer, dmtc, weightedSumRate] = beamformer_newton(weight, symbolR
 	nTxs = size(equivalentChannel, 2);
 
 	% * Initialize beamformer
-	beamformer = sqrt(txPower) * ctranspose(equivalentDistribution * equivalentChannel) / norm(equivalentDistribution * equivalentChannel);
+	beamformer = sqrt(transmitPower) * ctranspose(equivalentDistribution * equivalentChannel) / norm(equivalentDistribution * equivalentChannel);
 % 	beamformer = conj(beamformer);
 	beamformer = rand(size(beamformer)) + 1i * rand(size(beamformer));
 	beamformerComponent_ = zeros(nTxs, 2);

### 2022-05-22 src/lib/beamformer_pgd.m

@@ -1,4 +1,4 @@
-function [beamformer, weightedSumRate] = beamformer_pgd(weight, symbolRatio, equivalentChannel, txPower, noisePower, equivalentDistribution, threshold, step, tolerance)
+function [beamformer, weightedSumRate] = beamformer_pgd(weight, symbolRatio, equivalentChannel, transmitPower, noisePower, equivalentDistribution, threshold, step, tolerance)
 
 
 	% * Declare default tolerance
@@ -6,7 +6,7 @@ function [beamformer, weightedSumRate] = beamformer_pgd(weight, symbolRatio, equ
 		weight;
 		symbolRatio;
 		equivalentChannel;
-		txPower;
+		transmitPower;
 		noisePower;
 		equivalentDistribution;
 		threshold;
@@ -22,9 +22,9 @@ function [beamformer, weightedSumRate] = beamformer_pgd(weight, symbolRatio, equ
 	nTxs = size(equivalentChannel, 2);
 
 	% * Initialize beamformer
-	beamformer = sqrt(txPower) * ctranspose(equivalentDistribution * equivalentChannel) / norm(equivalentDistribution * equivalentChannel);
+	beamformer = sqrt(transmitPower) * ctranspose(equivalentDistribution * equivalentChannel) / norm(equivalentDistribution * equivalentChannel);
 	a = rand(1, nTxs) + 1i * rand(1, nTxs);
-	beamformer = sqrt(txPower) * ctranspose(a) / norm(a);
+	beamformer = sqrt(transmitPower) * ctranspose(a) / norm(a);
 	weightedSumRate = weighted_sum_rate_local(weight, symbolRatio, equivalentChannel, noisePower, equivalentDistribution, beamformer, threshold);
 
 	% * Projected gradient descent
@@ -52,8 +52,8 @@ function [beamformer, weightedSumRate] = beamformer_pgd(weight, symbolRatio, equ
 		beamformer = beamformer + step * gradient;
 
 		% * Project onto subspace (l2-norm ball)
-% 		beamformer = sqrt(txPower) * beamformer / max(1, norm(beamformer));
-		beamformer = sqrt(txPower) * beamformer / max(sqrt(txPower), norm(beamformer));
+% 		beamformer = sqrt(transmitPower) * beamformer / max(1, norm(beamformer));
+		beamformer = sqrt(transmitPower) * beamformer / max(sqrt(transmitPower), norm(beamformer));
 
 		% * Update weighted sum rate
[…]

### 2022-05-22 src/lib/beamformer_sca.m

@@ -1,12 +1,12 @@
-function [beamformer, dmtc, weightedSumRate] = beamformer_sca(weight, symbolRatio, equivalentChannel, txPower, noisePower, equivalentDistribution, threshold, tolerance)
+function [beamformer, dmtc, weightedSumRate] = beamformer_sca(weight, symbolRatio, equivalentChannel, transmitPower, noisePower, equivalentDistribution, threshold, tolerance)
 	% Function:
 	%	- optimize the transmit beamformer to maximize the weighted sum primary-backscatter rate by successive convex approximation
     %
     % Input:
 	%	- weight: the relative priority of the primary link
 	%	- symbolRatio: the ratio of the backscatter symbol period over the primary symbol period
-	%	- equivalentChannel [(nStates ^ nTags) * nTxs]: equivalent AP-user channels under all backscatter input combinations
-	%	- txPower: average transmit power at the AP
+	%	- equivalentChannel [(nStates ^ nTags) * nTxs]: equivalent primary channel under each tag input combination
+	%	- transmitPower: average transmit power at the AP
 	%	- noisePower: average noise power at the user
 	%	- equivalentDistribution [1 * (nStates ^ nTags)]: equivalent input combination probability distribution
 	%	- threshold [1 * (nOutputs + 1)]: boundaries of decision regions
@@ -30,7 +30,7 @@ function [beamformer, dmtc, weightedSumRate] = beamformer_sca(weight, symbolRati
 		weight;
 		symbolRatio;
 		equivalentChannel;
-		txPower;
+		transmitPower;
 		noisePower;
 		equivalentDistribution;
 		threshold;
@@ -45,7 +45,7 @@ function [beamformer, dmtc, weightedSumRate] = beamformer_sca(weight, symbolRati
 	nTxs = size(equivalentChannel, 2);
 
 	% * Initialize beamformer matrix and DMTC
-	beamformer = sqrt(txPower) * ctranspose(equivalentDistribution * equivalentChannel) / norm(equivalentDistribution * equivalentChannel);
+	beamformer = sqrt(transmitPower) * ctranspose(equivalentDistribution * equivalentChannel) / norm(equivalentDistribution * equivalentChannel);
 	beamformerMatrix = beamformer * beamformer';
[…]

### 2022-05-22 src/lib/beamformer_sca_.m

@@ -1,12 +1,12 @@
-function [beamformer, dmtc, weightedSumRate] = beamformer_sca_(weight, symbolRatio, equivalentChannel, txPower, noisePower, equivalentDistribution, threshold, tolerance)
+function [beamformer, dmtc, weightedSumRate] = beamformer_sca_(weight, symbolRatio, equivalentChannel, transmitPower, noisePower, equivalentDistribution, threshold, tolerance)
 	% Function:
 	%	- optimize the transmit beamformer to maximize the weighted sum primary-backscatter rate by successive convex approximation
     %
     % Input:
 	%	- weight: the relative priority of the primary link
 	%	- symbolRatio: the ratio of the backscatter symbol period over the primary symbol period
-	%	- equivalentChannel [(nStates ^ nTags) * nTxs]: equivalent AP-user channels under all backscatter input combinations
-	%	- txPower: average transmit power at the AP
+	%	- equivalentChannel [(nStates ^ nTags) * nTxs]: equivalent primary channel under each tag input combination
+	%	- transmitPower: average transmit power at the AP
 	%	- noisePower: average noise power at the user
 	%	- equivalentDistribution [1 * (nStates ^ nTags)]: equivalent input combination probability distribution
 	%	- threshold [1 * (nOutputs + 1)]: boundaries of decision regions
@@ -30,7 +30,7 @@ function [beamformer, dmtc, weightedSumRate] = beamformer_sca_(weight, symbolRat
 		weight;
 		symbolRatio;
 		equivalentChannel;
-		txPower;
+		transmitPower;
 		noisePower;
 		equivalentDistribution;
 		threshold;
@@ -45,9 +45,9 @@ function [beamformer, dmtc, weightedSumRate] = beamformer_sca_(weight, symbolRat
 	nTxs = size(equivalentChannel, 2);
 
 	% * Initialize beamformer matrix
-	beamformer = sqrt(txPower) * ctranspose(equivalentDistribution * equivalentChannel) / norm(equivalentDistribution * equivalentChannel);
+	beamformer = sqrt(transmitPower) * ctranspose(equivalentDistribution * equivalentChannel) / norm(equivalentDistribution * equivalentChannel);
 % 	a = rand(1, nTxs) + 1i * rand(1, nTxs);
-% 	beamformer = sqrt(txPower) * ctranspose(a) / norm(a);
[…]

### 2022-05-22 src/lib/beamformer_sca_1.m

@@ -1,12 +1,12 @@
-function [beamformer, dmtc, weightedSumRate] = beamformer_sca_(weight, symbolRatio, equivalentChannel, txPower, noisePower, equivalentDistribution, threshold, tolerance)
+function [beamformer, dmtc, weightedSumRate] = beamformer_sca_(weight, symbolRatio, equivalentChannel, transmitPower, noisePower, equivalentDistribution, threshold, tolerance)
 	% Function:
 	%	- optimize the transmit beamformer to maximize the weighted sum primary-backscatter rate by successive convex approximation
     %
     % Input:
 	%	- weight: the relative priority of the primary link
 	%	- symbolRatio: the ratio of the backscatter symbol period over the primary symbol period
-	%	- equivalentChannel [(nStates ^ nTags) * nTxs]: equivalent AP-user channels under all backscatter input combinations
-	%	- txPower: average transmit power at the AP
+	%	- equivalentChannel [(nStates ^ nTags) * nTxs]: equivalent primary channel under each tag input combination
+	%	- transmitPower: average transmit power at the AP
 	%	- noisePower: average noise power at the user
 	%	- equivalentDistribution [1 * (nStates ^ nTags)]: equivalent input combination probability distribution
 	%	- threshold [1 * (nOutputs + 1)]: boundaries of decision regions
@@ -30,7 +30,7 @@ function [beamformer, dmtc, weightedSumRate] = beamformer_sca_(weight, symbolRat
 		weight;
 		symbolRatio;
 		equivalentChannel;
-		txPower;
+		transmitPower;
 		noisePower;
 		equivalentDistribution;
 		threshold;
@@ -45,7 +45,7 @@ function [beamformer, dmtc, weightedSumRate] = beamformer_sca_(weight, symbolRat
 	nTxs = size(equivalentChannel, 2);
 
 	% * Initialize beamformer matrix
-	beamformer = sqrt(txPower) * ctranspose(equivalentDistribution * equivalentChannel) / norm(equivalentDistribution * equivalentChannel);
+	beamformer = sqrt(transmitPower) * ctranspose(equivalentDistribution * equivalentChannel) / norm(equivalentDistribution * equivalentChannel);
 	beamformerMatrix = beamformer * beamformer';
 
 	% * Compute expected received power under all backscatter input combinations and update DMTC
[…]

### 2022-05-22 src/lib/beamformer_sca_backup.m

@@ -1,12 +1,12 @@
-function [beamformer, dmtc, weightedSumRate] = beamformer_sca_backup(weight, symbolRatio, equivalentChannel, txPower, noisePower, equivalentDistribution, threshold, tolerance)
+function [beamformer, dmtc, weightedSumRate] = beamformer_sca_backup(weight, symbolRatio, equivalentChannel, transmitPower, noisePower, equivalentDistribution, threshold, tolerance)
 	% Function:
 	%	- optimize the transmit beamformer to maximize the weighted sum primary-backscatter rate by successive convex approximation
     %
     % Input:
 	%	- weight: the relative priority of the primary link
 	%	- symbolRatio: the ratio of the backscatter symbol period over the primary symbol period
-	%	- equivalentChannel [(nStates ^ nTags) * nTxs]: equivalent AP-user channels under all backscatter input combinations
-	%	- txPower: average transmit power at the AP
+	%	- equivalentChannel [(nStates ^ nTags) * nTxs]: equivalent primary channel under each tag input combination
+	%	- transmitPower: average transmit power at the AP
 	%	- noisePower: average noise power at the user
 	%	- equivalentDistribution [1 * (nStates ^ nTags)]: equivalent input combination probability distribution
 	%	- threshold [1 * (nOutputs + 1)]: boundaries of decision regions
@@ -30,7 +30,7 @@ function [beamformer, dmtc, weightedSumRate] = beamformer_sca_backup(weight, sym
 		weight;
 		symbolRatio;
 		equivalentChannel;
-		txPower;
+		transmitPower;
 		noisePower;
 		equivalentDistribution;
 		threshold;
@@ -45,9 +45,9 @@ function [beamformer, dmtc, weightedSumRate] = beamformer_sca_backup(weight, sym
 	nTxs = size(equivalentChannel, 2);
 
 	% * Initialize beamformer matrix
-	% beamformer = sqrt(txPower) * ctranspose(equivalentDistribution * equivalentChannel) / norm(equivalentDistribution * equivalentChannel);
+	% beamformer = sqrt(transmitPower) * ctranspose(equivalentDistribution * equivalentChannel) / norm(equivalentDistribution * equivalentChannel);
 	a = rand(1, nTxs) + 1i * rand(1, nTxs);
-	beamformer = sqrt(txPower) * ctranspose(a) / norm(a);
[…]

### 2022-05-22 src/lib/beamforming_pgd.m

@@ -1,0 +1,126 @@
+function [beamforming] = beamforming_pgd(symbolRatio, weight, transmitPower, noisePower, equivalentChannel, equivalentDistribution, threshold, tolerance, alpha, beta)
+	% Function:
+	%	- optimize beamforming vector by projected gradient descent with step size determined by backtracking line search
+    %
+    % Input:
+	%	- symbolRatio: backscatter/primary symbol duration ratio
+	%	- weight: relative priority of primary link
+	%	- transmitPower: average transmit power
+	%	- noisePower: average noise power
+	%	- equivalentChannel [nTxs x nInputs]: equivalent primary channel for each tag state tuple
+	%	- equivalentDistribution [nInputs x 1]: equivalent single-source distribution for each tag input distribution tuple
+	%	- threshold [1 x (nOutputs + 1)]: boundaries of quantization bins or decision regions (including 0 and Inf)
+    %	- tolerance: minimum rate gain per iteration
+	%	- alpha: fraction of acceptable decrease predicted by linear extrapolation
+	%	- beta: ratio of step size reduction in backtracking line search
+    %
+    % Output:
+	%	- beamforming [nTxs x 1]: transmit beamforming vector
+    %
+	% Comment:
+	%	- complex gradient w.r.t. beamforming vector is obtained in closed form
+	%	- use backtracking line search to accelerate convergence
+	%	- when primary link is prioritized, MRT to (ergodic) equivalent channel is nearly optimal; this may not hold when backscatter links are prioritized
+	%
+    % Author & Date: Yang (i@snowztail.com), 22 May 16
+
+	% * Set default tolerance and parameters of backtracking line search
+	arguments
+		symbolRatio;
+		weight;
+		transmitPower;
+		noisePower;
+		equivalentChannel;
+		equivalentDistribution;
+		threshold;
+		tolerance = 1e-6;
+		alpha = 0.01;
+		beta = 0.5;
+	end
+
+	% ! Use finite threshold to avoid precision issue of incomplete gamma function
+	threshold(end) = 10 * threshold(end - 1);
+
+	% * Initialize beamforming vector as MRT to ergodic equivalent channel
[…]

### 2022-05-22 src/lib/block_coordinate_descent.m

@@ -1,106 +1,123 @@
-function [rate, inputDistribution, threshold, beamformer] = block_coordinate_descent(weight, nTags, symbolRatio, equivalentChannel, txPower, noisePower, nBins, tolerance, options)
+function [rate, distribution, threshold, beamforming] = block_coordinate_descent(nTags, symbolRatio, transmitPower, noisePower, weight, equivalentChannel, tolerance, options)
 	% Function:
-    %	- maximize the weighted sum of primary and total backscatter rate by alternatively optimizing input distribution and energy detection threshold
+	%	- iteratively update the input distribution, detection threshold, and beamforming vector to maximize weighted sum rate
     %
     % Input:
-	%	- weight: the relative priority of the primary link
 	%	- nTags: number of tags
-	%	- symbolRatio: the ratio of the backscatter symbol period over the primary symbol period
-	%	- equivalentChannel [(nStates ^ nTags) * nTxs]: equivalent AP-user channels under all backscatter input combinations
-	%	- txPower: average transmit power at the AP
-	%	- noisePower: average noise power at the user
-	%	- nBins: number of discretization bins over received signal
+	%	- symbolRatio: backscatter/primary symbol duration ratio
+	%	- transmitPower: average transmit power
+	%	- noisePower: average noise power
+	%	- weight: relative priority of primary link
+	%	- equivalentChannel [nTxs x nInputs]: equivalent primary channel for each tag state tuple
     %   - tolerance: minimum rate gain per iteration
-	%	- options:
-	%		- Input: choose from 'cooperation', 'exhaustion', 'kkt', 'sca'
-	%		- Threshold: choose from 'smawk', 'dp', 'bisection', 'ml'
-	%		- Recovery: choose from 'marginalization', 'decomposition', 'randomization'
+	%	- options: methods and algorithms
     %
     % Output:
-	%	- rate [2 * 1]:
-	%		- primaryRate: the achievable rate for the primary link (nats per second per Hertz)
-	%		- backscatterRate: the achievable sum rate for the backscatter link (nats per channel use)
-	%	- inputDistribution [nTags * nStates]: input probability distribution
-	%	- threshold [1 * (nOutputs + 1)]: boundaries of decision regions
[…]

### 2022-05-22 src/lib/channel_discretization.m

@@ -5,7 +5,7 @@ function [discreteChannel, receivedPower] = channel_discretization(symbolRatio, 
     %
     % Input:
 	%	- symbolRatio: the ratio of the secondary symbol period over the primary symbol period
-	%	- equivalentChannel [(nStates ^ nTags) * nTxs]: equivalent AP-user channels under all backscatter input combinations
+	%	- equivalentChannel [(nStates ^ nTags) * nTxs]: equivalent primary channel under each tag input combination
 	%	- noisePower: average noise power at the user
 	%	- beamformer [nTxs * 1]: transmit beamforming vector at the AP
 	%	- threshold [1 * nOutputs + 1]: bin boundaries or decision thresholds

### 2022-05-22 src/lib/cost_quantization.m

@@ -1,0 +1,19 @@
+function [quantizationCost] = cost_quantization(binIndex, jointDistribution, outputDistribution)
+	% Function:
+	%	- compute quantization cost of grouping indexed energy bins into a decision region
+    %
+    % Input:
+	%	- jointDistribution [nInputs x nBins]: joint probability distribution of input tag distribution tuples and output energy bins
+	%	- outputDistribution [1 x nBins]: probability distribution of output energy bins
+    %
+    % Output:
+	%	- quantizationCost: cost of grouping indexed energy bins into a decision region
+    %
+    % Comment:
+	%	- quantization cost evaluates loss of mutual information
+	%
+    % Author & Date: Yang (i@snowztail.com), 22 May 21
+
+	backwardDistribution = sum(jointDistribution(:, binIndex), 2) / sum(outputDistribution(binIndex), 2);
+	quantizationCost = sum(entr(backwardDistribution)) * sum(outputDistribution(binIndex));
+end

### 2022-05-22 src/lib/dimension_number.m

@@ -1,13 +1,12 @@
-function [nDimensions] = ndims_modified(array)
+function [nDimensions] = dimension_number(array)
 	% Function:
-    %	- get the actual dimensions of an array
-	%	- obtain the optimal tag input distribution for a given discrete memoryless MAC
+    %	- return number of dimensions of an array
     %
     % Input:
-	%	- array: the input array
+	%	- array: input array
     %
     % Output:
-	%	- nDimensions: the actual dimensions of the array
+	%	- nDimensions: number of dimensions of an array
     %
     % Comment:
 	%	- return 1 for row/column vectors and 0 for []

### 2022-05-22 src/lib/distribution_cooperation.m

@@ -1,0 +1,53 @@
+function [jointDistribution, equivalentDistribution] = distribution_cooperation(nTags, symbolRatio, weight, snr, dmac, tolerance)
+	% Function:
+	%	- obtain the optimal joint tag input distribution with full transmit cooperation for maximizing weighted sum of primary and total backscatter rate
+    %
+    % Input:
+	%	- nTags: number of tags
+	%	- symbolRatio: backscatter/primary symbol duration ratio
+	%	- weight: relative priority of primary link
+	%	- snr [nInputs x 1]: average receive signal-to-noise ratio per primary symbol for each tag state tuple
+	%	- dmac [nInputs x nOutputs]: discrete memoryless thresholding multiple access channel whose input and output are tag state tuple
+    %	- tolerance: minimum rate gain per iteration
+    %
+    % Output:
+	%	- jointDistribution [nStates x ... (nTags-dimensional) ... x nStates]: joint tag input distribution with full transmit cooperation
+	%	- equivalentDistribution [nInputs x 1]: equivalent single-source distribution for each tag input distribution tuple
+    %
+    % Comment:
+	%	- with full transmit cooperation, the tags are equivalent to a single information source with input distribution in nInputs-dimensional probability simplex
+    %   - in general, tags encode independently and it is hard to approximate the joint distribution array without cooperation
+    %
+    % Author & Date: Yang (i@snowztail.com), 22 Mar 17
+
+	% * Set default tolerance
+	arguments
+		nTags;
+		symbolRatio;
+		weight;
+		snr;
+		dmac;
+		tolerance = 1e-6;
+	end
+
+	% * Get data
+	nInputs = size(dmac, 1);
+	nStates = nthroot(nInputs, nTags);
+
+	% * Initialize input distribution as uniform distribution
+	distribution = normalize(ones(nStates, nTags), 'norm', 1);
+	equivalentDistribution = prod(tuple_tag(distribution), 2);
+	informationFunction = weight * information_primary(symbolRatio, snr) + (1 - weight) * information_backscatter(equivalentDistribution, dmac);
+	wsr = equivalentDistribution' * informationFunction;
+
+	% * Iteratively update equivalent distribution, information function associated with each (joint) codeword, and weighted sum achievable rate
+	isConverged = false;
+	while ~isConverged
+		wsr_ = wsr;
[…]

### 2022-05-22 src/lib/distribution_exhaustion.m

@@ -1,0 +1,62 @@
+function [distribution, equivalentDistribution] = distribution_exhaustion(nTags, symbolRatio, weight, snr, dmac, resolution)
+	% Function:
+	%	- exhaustively search tag input probability distribution for maximizing weighted sum of primary and total backscatter rate
+    %
+    % Input:
+	%	- nTags: number of tags
+	%	- symbolRatio: backscatter/primary symbol duration ratio
+	%	- weight: relative priority of primary link
+	%	- snr [nInputs x 1]: average receive signal-to-noise ratio per primary symbol for each tag state tuple
+	%	- dmac [nInputs x nOutputs]: discrete memoryless thresholding multiple access channel whose input and output are tag state tuple
+	%	- resolution: gap between neighbor search levels
+    %	- tolerance: minimum rate gain per iteration
+    %
+    % Output:
+	%	- distribution [nStates x nTags]: tag input (i.e., state) probability distribution
+	%	- equivalentDistribution [nInputs x 1]: equivalent single-source distribution for each tag input distribution tuple
+    %
+    % Author & Date: Yang (i@snowztail.com), 22 Mar 17
+
+	% * Set default resolution
+	arguments
+		nTags;
+		symbolRatio;
+		weight;
+		snr;
+		dmac;
+		resolution = 5e-3;
+	end
+
+	% * Get data
+	nInputs = size(dmac, 1);
+	nStates = nthroot(nInputs, nTags);
+
+	% * Obtain probability simplex and tag-state tuples to evaluate
+	[probabilitySimplex, nVertices] = simplex_probability(nStates, resolution);
+	candidateTuple = tuple_tag(repmat(transpose(1 : nVertices), [1, nTags]));
+	nTuples = size(candidateTuple, 1);
+
+	% * Exhaustive search
+	wsr = 0;
+	for iTuple = 1 : nTuples
+		distributionInstance = probabilitySimplex(:, candidateTuple(iTuple, :));
+		equivalentDistributionInstance = prod(tuple_tag(distributionInstance), 2);
+		wsrInstance = equivalentDistributionInstance' * (weight * information_primary(symbolRatio, snr) + (1 - weight) * information_backscatter(equivalentDistributionInstance, dmac));
+		if wsrInstance > wsr
+			distribution = distributionInstance;
+			equivalentDistribution = equivalentDistributionInstance;
+			wsr = wsrInstance;
[…]

### 2022-05-22 src/lib/distribution_kkt.m

@@ -1,0 +1,81 @@
+function [distribution, equivalentDistribution] = distribution_kkt(nTags, symbolRatio, weight, snr, dmac, tolerance)
+	% Function:
+	%	- obtain KKT tag input probability distribution for maximizing weighted sum of primary and total backscatter rate
+    %
+    % Input:
+	%	- nTags: number of tags
+	%	- symbolRatio: backscatter/primary symbol duration ratio
+	%	- weight: relative priority of primary link
+	%	- snr [nInputs x 1]: average receive signal-to-noise ratio per primary symbol for each tag state tuple
+	%	- dmac [nInputs x nOutputs]: discrete memoryless thresholding multiple access channel whose input and output are tag state tuple
+    %	- tolerance: minimum rate gain per iteration
+    %
+    % Output:
+	%	- distribution [nStates x nTags]: tag input (i.e., state) probability distribution
+	%	- equivalentDistribution [nInputs x 1]: equivalent single-source distribution for each tag input distribution tuple
+    %
+    % Comment:
+    %	- iteratively update input distribution of each tag by coordinate descent
+	%	- converge to KKT solution (stationary point)
+	%	- DMAC is in joint form P(y | x_1, ..., x_K) instead of marginal form p(y | x_k)
+    %
+    % Author & Date: Yang (i@snowztail.com), 22 Jan 09
+
+	% * Set default tolerance
+	arguments
+		nTags;
+		symbolRatio;
+		weight;
+		snr;
+		dmac;
+		tolerance = 1e-6;
+	end
+
+	% * Get data
+	nInputs = size(dmac, 1);
+	nStates = nthroot(nInputs, nTags);
+
+	% * Initialize input distribution as uniform
+	distribution = normalize(ones(nStates, nTags), 'norm', 1);
+	distributionTuple = tuple_tag(distribution);
+	equivalentDistribution = prod(distributionTuple, 2);
+	informationFunction = weight * information_primary(symbolRatio, snr) + (1 - weight) * information_backscatter(equivalentDistribution, dmac);
+	marginalInformation = marginal_information(distributionTuple, informationFunction);
+	wsr = equivalentDistribution' * informationFunction;
+
+	% * Iteratively update input distribution for all tags
+	isConverged = false;
+	while ~isConverged
+		wsr_ = wsr;
[…]

### 2022-05-22 src/lib/distribution_sca.m

@@ -1,0 +1,74 @@
+function [distribution, equivalentDistribution] = distribution_sca(nTags, symbolRatio, weight, snr, dmac, tolerance)
+	% Function:
+	%	- optimize tag input probability distribution by successive convex approximation for maximizing weighted sum of primary and total backscatter rate
+    %
+    % Input:
+	%	- nTags: number of tags
+	%	- symbolRatio: backscatter/primary symbol duration ratio
+	%	- weight: relative priority of primary link
+	%	- snr [nInputs x 1]: average receive signal-to-noise ratio per primary symbol for each tag state tuple
+	%	- dmac [nInputs x nOutputs]: discrete memoryless thresholding multiple access channel whose input and output are tag state tuple
+    %	- tolerance: minimum rate gain per iteration
+    %
+    % Output:
+	%	- distribution [nStates x nTags]: tag input (i.e., state) probability distribution
+	%	- equivalentDistribution [nInputs x 1]: equivalent single-source distribution for each tag input distribution tuple
+    %
+    % Comment:
+	%	- sequentially approximate the equivalent (i.e. product of individual) distribution by its first-order Taylor expansion at previous point
+	%	- expected to converge to KKT points but convergence is unstable
+    %
+    % Author & Date: Yang (i@snowztail.com), 23 Mar 15
+
+	% * Set default tolerance
+	arguments
+		nTags;
+		symbolRatio;
+		weight;
+		snr;
+		dmac;
+		tolerance = 1e-6;
+	end
+
+	% * Get data
+	nInputs = size(dmac, 1);
+	nStates = nthroot(nInputs, nTags);
+
+	% * Construct tag state tuple
+	stateTuple = tuple_tag(repmat(transpose(1 : nStates), [1, nTags]));
+
+	% * Initialize input distribution as uniform
+	distribution = normalize(ones(nStates, nTags), 'norm', 1);
+	equivalentDistribution = prod(tuple_tag(distribution), 2);
+	wsr = rate_weighted(symbolRatio, weight, snr, equivalentDistribution, dmac);
+
+	% * Iteratively update input distribution by SCA
+	isConverged = false;
+	while ~isConverged
+		distribution_ = distribution;
+		wsr_ = wsr;
+		cvx_begin
+			variable distribution(nStates, nTags);
+			expression equivalentDistributionSca(nInputs, 1);
[…]

### 2022-05-22 src/lib/distribution_tuple.m

@@ -1,0 +1,20 @@
+function [distributionTuple] = distribution_tuple(distribution)
+	% Function:
+    %	- obtain all combinations of tag input probability
+    %
+    % Input:
+	%	- distribution [nTags * nStates]: input probability distribution
+    %
+    % Output:
+	%	- combinationDistribution [nTags * (nStates ^ nTags)]: each column represents a possible tag input probability combination
+    %
+    % Author & Date: Yang (i@snowztail.com), 22 Jan 09
+
+	[nTags, nStates] = size(distribution);
+	if nTags > 1
+% 		distributionTuple = flipud(combvec(distribution(1, :), distribution_tuple(distribution(2 : end, :))));
+		distributionTuple = combvec(distribution_tuple(distribution(1 : end - 1, :)), distribution(end, :));
+	elseif nTags == 1
+		distributionTuple = distribution;
+	end
+end

### 2022-05-22 src/lib/dmc_integration.m

@@ -1,0 +1,35 @@
+function [dmc] = dmc_integration(symbolRatio, receivePower, threshold)
+	% Function:
+	%	- construct discrete memoryless channel for energy detection based on conditional energy p.d.f. and decision thresholds
+    %
+    % Input:
+	%	- symbolRatio: backscatter/primary symbol duration ratio
+	%	- receivePower [nInputs x 1]: average receive power per primary symbol for each tag state tuple
+	%	- threshold [1 x (nOutputs + 1)]: boundaries of quantization bins or decision regions (including 0 and Inf)
+    %
+    % Output:
+	%	- dmc [nInputs x nOutputs]: discrete memoryless channel whose input is tag state tuple and output is (high-resolution) quantized energy bins or tag state tuple
+    %
+    % Comment:
+    %	- for each tag state tuple, received power per primary symbol follows Erlang distribution
+	%	- DMC depends on bin boundaries or decision thresholds
+    %
+    % Author & Date: Yang (i@snowztail.com), 22 Feb 09
+
+	% * Get data
+	nInputs = size(receivePower, 1);
+	nOutputs = size(threshold, 2) - 1;
+	% [sortPower, sortIndex] = sort(receivePower);
+
+	% * Construct DMC based on conditional energy p.d.f. and decision thresholds
+	dmc = zeros(nInputs, nOutputs);
+	for iInput = 1 : nInputs
+		channelDistribution = @(z) (z .^ (symbolRatio - 1) .* exp(-z ./ receivePower(iInput))) ./ (receivePower(iInput) .^ symbolRatio .* gamma(symbolRatio));
+		for iOutput = 1 : nOutputs
+			dmc(iInput, iOutput) = integral(channelDistribution, threshold(iOutput), threshold(iOutput + 1));
+		end
+	end
+
+	% % * Desort to recover i/o mapping
+	% dmc(:, sortIndex) = dmc;
+end

### 2022-05-22 src/lib/fading_rayleigh.m

@@ -1,0 +1,16 @@
+function [fading] = fading_rayleigh(nTxs, nRxs)
+	% Function:
+	%	- simulate small-scale fading in i.i.d. Rayleigh (CSCG) distribution with unit variance
+    %
+    % Input:
+	%	- nTxs: number of transmit antennas
+	%	- nRxs: number of receive antennas
+    %
+    % Output:
+	%	- fading [nTxs x nRxs]: small-scale signal attenuation
+    %
+    % Author & Date: Yang (i@snowztail.com), 22 May 10
+
+	% * Simulate Rayleigh fading
+	fading = sqrt(0.5) * (randn(nTxs, nRxs) + 1i * randn(nTxs, nRxs));
+end

### 2022-05-22 src/lib/fading_ricean.m

@@ -1,0 +1,26 @@
+function [fading] = fading_ricean(nTxs, nRxs, factor, aoa)
+	% Function:
+	%	- simulate small-scale fading in i.i.d. Ricean distribution
+    %
+    % Input:
+	%	- nTxs: number of transmit antennas
+	%	- nRxs: number of receive antennas
+	%	- factor: Ricean factor
+	%	- aoa: angle of arrival
+    %
+    % Output:
+	%	- fading [nTxs x nRxs]: small-scale signal attenuation
+    %
+    % Author & Date: Yang (i@snowztail.com), 22 May 10
+
+	% * Set default angle of arrival
+	arguments
+		nTxs;
+		nRxs;
+		factor;
+		aoa = rand * 2 * pi;
+	end
+
+	% * Simulate Ricean fading
+	fading = sqrt(0.5 * factor / (factor + 1)) * exp(1i * aoa) + sqrt(0.5 / (factor + 1)) * (randn(nTxs, nRxs) + 1i * randn(nTxs, nRxs));
+end

### 2022-05-22 src/lib/information_backscatter.m

@@ -1,0 +1,25 @@
+function [backscatterInformation] = information_backscatter(equivalentDistribution, dmac)
+	% Function:
+	%	- compute total backscatter information function for each tag state tuple
+    %
+    % Input:
+	%	- equivalentDistribution [nInputs x 1]: equivalent single-source distribution for each tag input distribution tuple
+	%	- dmac [nInputs x nOutputs]: discrete memoryless thresholding multiple access channel whose input and output are tag state tuple
+    %
+    % Output:
+	%	- backscatterInformation [nInputs x 1]: total backscatter information function for each tag state tuple
+    %
+    % Author & Date: Yang (i@snowztail.com), 22 Feb 19
+
+	% * Get data
+	[nInputs, nOutputs] = size(dmac);
+
+	% * Compute total backscatter information function
+	backscatterInformation = zeros(nInputs, nOutputs);
+	for iInput = 1 : nInputs
+		for iOutput = 1 : nOutputs
+			backscatterInformation(iInput, iOutput) = dmac(iInput, iOutput) * log(dmac(iInput, iOutput) / (equivalentDistribution' * dmac(:, iOutput)));
+		end
+	end
+	backscatterInformation = sum(backscatterInformation, 2);
+end

### 2022-05-22 src/lib/information_function.m

@@ -5,7 +5,7 @@ function [informationFunction] = information_function(weight, symbolRatio, equiv
     % Input:
 	%	- weight: the relative priority of the primary link
 	%	- symbolRatio: the ratio of the backscatter symbol period over the primary symbol period
-	%	- equivalentChannel [(nStates ^ nTags) * nTxs]: equivalent AP-user channels under all backscatter input combinations
+	%	- equivalentChannel [(nStates ^ nTags) * nTxs]: equivalent primary channel under each tag input combination
 	%	- noisePower: average noise power at the user
 	%	- equivalentDistribution [1 * (nStates ^ nTags)]: equivalent input combination probability distribution
 	%	- beamformer [nTxs * 1]: transmit beamforming vector at the AP

### 2022-05-22 src/lib/information_primary.m

@@ -1,0 +1,15 @@
+function [primaryInformation] = information_primary(symbolRatio, snr)
+	% Function:
+	%	- compute primary information function for each tag state tuple
+    %
+    % Input:
+	%	- symbolRatio: backscatter/primary symbol duration ratio
+	%	- snr [nInputs x 1]: average receive signal-to-noise ratio per primary symbol for each tag state tuple
+    %
+    % Output:
+	%	- primaryInformation [nInputs x 1]: primary information function for each tag state tuple
+    %
+    % Author & Date: Yang (i@snowztail.com), 22 Feb 19
+
+	primaryInformation = symbolRatio * log(1 + snr);
+end

### 2022-05-22 src/lib/input_distribution_cooperation.m

@@ -6,7 +6,7 @@ function [jointDistribution, equivalentDistribution, weightedSumRate] = input_di
 	%	- weight: the relative priority of the primary link
 	%	- nTags: number of tags
 	%	- symbolRatio: the ratio of the backscatter symbol period over the primary symbol period
-	%	- equivalentChannel [(nStates ^ nTags) * nTxs]: equivalent AP-user channels under all backscatter input combinations
+	%	- equivalentChannel [(nStates ^ nTags) * nTxs]: equivalent primary channel under each tag input combination
 	%	- noisePower: average noise power at the user
 	%	- beamformer [nTxs * 1]: transmit beamforming vector at the AP
     %	- dmtc [(nStates ^ nTags) * nOutputs]: the transition probability matrix of the backscatter discrete memoryless thresholding MAC
@@ -54,7 +54,7 @@ function [jointDistribution, equivalentDistribution, weightedSumRate] = input_di
 	while ~isConverged
 		weightedSumRate_ = weightedSumRate;
 		equivalentDistribution = equivalent_distribution(equivalentDistribution, informationFunction);
-		jointDistribution = permute(reshape(equivalentDistribution, nStates * ones(1, nTags)), nTags : - 1 : 1);
+		jointDistribution = permute(reshape(equivalentDistribution, nStates * ones(1, nTags)), nTags : -1 : 1);
 		informationFunction = information_function(weight, symbolRatio, equivalentChannel, noisePower, equivalentDistribution, beamformer, dmtc);
 		weightedSumRate = equivalentDistribution * informationFunction;
 		isConverged = abs(weightedSumRate - weightedSumRate_) <= tolerance;

### 2022-05-22 src/lib/input_distribution_sca.m

@@ -6,7 +6,7 @@ function [inputDistribution, equivalentDistribution, weightedSumRate] = input_di
 	%	- weight: the relative priority of the primary link
 	%	- nTags: number of tags
 	%	- symbolRatio: the ratio of the backscatter symbol period over the primary symbol period
-	%	- equivalentChannel [(nStates ^ nTags) * nTxs]: equivalent AP-user channels under all backscatter input combinations
+	%	- equivalentChannel [(nStates ^ nTags) * nTxs]: equivalent primary channel under each tag input combination
 	%	- noisePower: average noise power at the user
 	%	- beamformer [nTxs * 1]: transmit beamforming vector at the AP
     %	- dmtc [(nStates ^ nTags) * nOutputs]: the transition probability matrix of the backscatter discrete memoryless thresholding MAC

### 2022-05-22 src/lib/path_loss.m

@@ -1,0 +1,29 @@
+function [pathLoss] = path_loss(frequency, distance, exponent, txGain, rxGain)
+	% Function:
+	%	- compute the path loss between transmitter and receiver
+    %
+    % Input:
+	%	- frequency: carrier frequency
+    %	- distance: distance between transmitter and receiver
+	%	- exponent: path loss exponent
+	%	- txGain: transmit antenna gain
+	%	- rxGain: receive antenna gain
+    %
+    % Output:
+	%	- pathLoss: large-scale signal attenuation
+    %
+    % Author & Date: Yang (i@snowztail.com), 22 May 10
+
+	% * Set default antenna gains
+	arguments
+		frequency;
+		distance;
+		exponent;
+		txGain = 1;
+		rxGain = 1;
+	end
+
+	% * Compute path loss
+	wavelength = physconst('LightSpeed') / frequency;
+	pathLoss = txGain * rxGain * wavelength ^ 2 / (16 * pi ^ 2 * distance ^ exponent);
+end

### 2022-05-22 src/lib/product_cartesian.m

@@ -1,0 +1,27 @@
+function [tuple] = product_cartesian(varargin)
+	% Function:
+	%	- compute (N-fold) Cartesian product of N input sets
+    %
+    % Input:
+	%	- varargin: each input set is a column vector
+    %
+    % Output:
+	%	- tuple: each row is a N-tuple whose n-th entry come from set C_n
+    %
+	% Comment:
+	%	- Cartesian product of sets C_1, ..., C_N is defined as the set of all ordered N-tuples (x_1, ..., x_N) such that x_n belongs to C_n
+	%	- modified from built-in function `combvec`
+	%
+    % Author & Date: Yang (i@snowztail.com), 22 May 14
+
+	if isempty(varargin)
+		tuple = [];
+	else
+		tuple = varargin{1};
+		for i = 2 : length(varargin)
+			tail = varargin{i};
+			% tuple = [repelem(tuple, size(tail, 1), size(tail, 2)), copy_interleaved(tail, size(tuple, 1))];
+			tuple = [repelem(tuple, size(tail, 1), 1), repmat(tail, size(tuple, 1), 1)];
+		end
+	end
+end

### 2022-05-22 src/lib/quantization_set.m

@@ -1,0 +1,40 @@
+function [quantizationSet] = quantization_set(symbolRatio, receivePower, nBins, confidence)
+	% Function:
+    %	- determine (high-resolution) quantization threshold set to quantize receive energy into numerous bins
+    %
+    % Input:
+	%	- symbolRatio: the ratio of the backscatter symbol period over the primary symbol period
+	%	- receivePower [nInputs x 1]: average receive power per primary symbol for each tag state tuple
+	%	- nBins: number of receive energy quantization bins
+    %	- confidence: number of standard deviations from mean (i.e., parameter k in Chebyshev's inequality)
+    %
+    % Output:
+	%	- quantizationSet [1 x (nBins + 1)]: boundaries of quantized energy bins
+    %
+    % Comment:
+	%	- quantized receive energy bins should be grouped to formulate decision regions
+	%	- hence, decision thresholds are selected from quantization threshold set
+	%	- quantization threshold set is constructed within empirical interval by Chebyshev's inequality
+	%	- high-resolution quantization threshold set improves detection performance at the cost of (linear) computation complexity
+    %
+    % Author & Date: Yang (i@snowztail.com), 22 Apr 18
+
+	% * Set default bin number and confidence score
+	arguments
+		symbolRatio;
+		receivePower;
+		nBins = 2 ^ 8;
+		confidence = 3;
+	end
+
+	% * Obtain empirical lower and upper energy bounds by Chebyshev's inequality
+	lowerBound = symbolRatio * min(receivePower) - confidence * sqrt(symbolRatio * min(receivePower));
+	upperBound = symbolRatio * max(receivePower) + confidence * sqrt(symbolRatio * max(receivePower));
+
+	% * Ensure non-negative thresholds
+	if lowerBound <= 0
+		quantizationSet = [linspace(0, upperBound, nBins), Inf];
+	else
+		quantizationSet = [0, linspace(lowerBound, upperBound, nBins - 1), Inf];
+	end
+end

### 2022-05-22 src/lib/rate_primary.m

@@ -5,7 +5,7 @@ function [primaryRate] = rate_primary(symbolRatio, equivalentChannel, noisePower
     %
     % Input:
 	%	- symbolRatio: the ratio of the backscatter symbol period over the primary symbol period
-	%	- equivalentChannel [(nStates ^ nTags) * nTxs]: equivalent AP-user channels under all backscatter input combinations
+	%	- equivalentChannel [(nStates ^ nTags) * nTxs]: equivalent primary channel under each tag input combination
 	%	- noisePower: average noise power at the user
 	%	- equivalentDistribution [1 * (nStates ^ nTags)]: equivalent input combination probability distribution
 	%	- beamformer [nTxs * 1]: transmit beamforming vector at the AP

### 2022-05-22 src/lib/rate_weighted.m

@@ -1,0 +1,22 @@
+function [wsr, rate] = rate_weighted(symbolRatio, weight, snr, equivalentDistribution, dmac)
+	% Function:
+    %	- compute weighted sum rate, primary rate, and total backscatter rate
+    %
+    % Input:
+	%	- symbolRatio: backscatter/primary symbol duration ratio
+	%	- weight: relative priority of primary link
+	%	- snr [nInputs x 1]: average receive signal-to-noise ratio per primary symbol for each tag state tuple
+	%	- equivalentDistribution [nInputs x 1]: equivalent single-source distribution for each tag input distribution tuple
+	%	- dmac [nInputs x nOutputs]: discrete memoryless thresholding multiple access channel whose input and output are tag state tuple
+    %
+    % Output:
+	%	- wsr: weighted sum of primary rate and total backscatter rate
+	%	- rate [2 x 1]: primary rate (nats/s/Hz) and total backscatter rate (nats/cu)
+    %
+    % Author & Date: Yang (i@snowztail.com), 22 Feb 22
+
+	primaryRate = equivalentDistribution' * symbolRatio * log(1 + snr);
+	backscatterRate = sum(entr(equivalentDistribution' * dmac) - equivalentDistribution' * entr(dmac));
+	rate = [primaryRate; backscatterRate];
+	wsr = weight * primaryRate + (1 - weight) * backscatterRate;
+end

### 2022-05-22 src/lib/rate_weighted_sum.m

@@ -5,7 +5,7 @@ function [weightedSumRate, rate] = rate_weighted_sum(weight, symbolRatio, equiva
     % Input:
 	%	- weight: the relative priority of the primary link
 	%	- symbolRatio: the ratio of the backscatter symbol period over the primary symbol period
-	%	- equivalentChannel [(nStates ^ nTags) * nTxs]: equivalent AP-user channels under all backscatter input combinations
+	%	- equivalentChannel [(nStates ^ nTags) * nTxs]: equivalent primary channel under each tag input combination
 	%	- noisePower: average noise power at the user
 	%	- equivalentDistribution [1 * (nStates ^ nTags)]: equivalent input combination probability distribution
 	%	- beamformer [nTxs * 1]: transmit beamforming vector at the AP
@@ -13,7 +13,7 @@ function [weightedSumRate, rate] = rate_weighted_sum(weight, symbolRatio, equiva
     %
     % Output:
 	%	- weightedSumRate: weighted sum of primary rate and total backscatter rate
-	%	- rate [2 * 1]:
+	%	- rate [2 x 1]:
 	%		- primaryRate: the achievable rate for the primary link (nats per second per Hertz)
 	%		- backscatterRate: the achievable sum rate for the backscatter link (nats per channel use)
     %

### 2022-05-22 src/lib/recovery_decomposition.m

@@ -1,22 +1,13 @@
-function [inputDistribution, equivalentDistribution, weightedSumRate] = recovery_decomposition(weight, symbolRatio, equivalentChannel, noisePower, jointDistribution, beamformer, dmtc)
+function [distribution, equivalentDistribution] = recovery_decomposition(jointDistribution)
 	% Function:
-	%	- extract a good tag input distribution (corresponding to no transmit cooperation) by normalizing the best rank-1 CP approximation
+	%	- extract individual tag input distribution from joint input distribution by normalizing the best rank-1 CP approximation
     %
     % Input:
-	%	- weight: the relative priority of the primary link
-	%	- symbolRatio: the ratio of the backscatter symbol period over the primary symbol period
-	%	- equivalentChannel [(nStates ^ nTags) * nTxs]: equivalent AP-user channels under all backscatter input combinations
-	%	- noisePower: average noise power at the user
-	%	- jointDistribution [nStates * ... (nTags) ... * nStates]: the joint input distribution of all tags corresponding to the relaxed input optimization problem
-	%	- beamformer [nTxs * 1]: transmit beamforming vector at the AP
-    %	- dmtc [(nStates ^ nTags) * nOutputs]: the transition probability matrix of the backscatter discrete memoryless thresholding MAC
+	%	- jointDistribution [nStates x ... (nTags-dimensional) ... x nStates]: joint tag input distribution with full transmit cooperation
     %
     % Output:
-	%	- inputDistribution [nTags * nStates]: input probability distribution
-	%	- equivalentDistribution [1 * (nStates ^ nTags)]: equivalent input combination probability distribution
-	%	- weightedSumRate: weighted sum of primary rate and total backscatter rate
-	%		- primaryRate: the achievable rate for the primary link (nats per second per Hertz)
-	%		- backscatterRate: the achievable sum rate for the backscatter link (nats per channel use)
+	%	- distribution [nStates x nTags]: tag input (i.e., state) probability distribution
+	%	- equivalentDistribution [nInputs x 1]: equivalent single-source distribution for each tag input distribution tuple
     %
     % Comment:
     %	- approximate the joint input distribution tensor by the best rank-1 CP tensor
@@ -27,8 +18,6 @@ function [inputDistribution, equivalentDistribution, weightedSumRate] = recovery
[…]

### 2022-05-22 src/lib/recovery_marginalization.m

@@ -1,37 +1,24 @@
-function [inputDistribution, equivalentDistribution, weightedSumRate] = recovery_marginalization(weight, symbolRatio, equivalentChannel, noisePower, jointDistribution, beamformer, dmtc)
+function [distribution, equivalentDistribution] = recovery_marginalization(jointDistribution)
 	% Function:
-	%	- extract a good tag input distribution (corresponding to no transmit cooperation) by marginalization
+	%	- extract individual tag input distribution from joint input distribution by marginalization
     %
     % Input:
-	%	- weight: the relative priority of the primary link
-	%	- symbolRatio: the ratio of the backscatter symbol period over the primary symbol period
-	%	- equivalentChannel [(nStates ^ nTags) * nTxs]: equivalent AP-user channels under all backscatter input combinations
-	%	- noisePower: average noise power at the user
-	%	- jointDistribution [nStates * ... (nTags) ... * nStates]: the joint input distribution of all tags corresponding to the relaxed input optimization problem
-	%	- beamformer [nTxs * 1]: transmit beamforming vector at the AP
-    %	- dmtc [(nStates ^ nTags) * nOutputs]: the transition probability matrix of the backscatter discrete memoryless thresholding MAC
+	%	- jointDistribution [nStates x ... (nTags-dimensional) ... x nStates]: joint tag input distribution with full transmit cooperation
     %
     % Output:
-	%	- inputDistribution [nTags * nStates]: input probability distribution
-	%	- equivalentDistribution [1 * (nStates ^ nTags)]: equivalent input combination probability distribution
-	%	- weightedSumRate: weighted sum of primary rate and total backscatter rate
-	%		- primaryRate: the achievable rate for the primary link (nats per second per Hertz)
-	%		- backscatterRate: the achievable sum rate for the backscatter link (nats per channel use)
-    %
-    % Comment:
-    %	- obtain the marginal distribution from the joint distribution array
+	%	- distribution [nStates x nTags]: tag input (i.e., state) probability distribution
+	%	- equivalentDistribution [nInputs x 1]: equivalent single-source distribution for each tag input distribution tuple
     %
     % Author & Date: Yang (i@snowztail.com), 22 Mar 09
 
 	% * Get data
-	nTags = ndims_modified(jointDistribution);
-	nStates = nthroot(size(dmtc, 1), nTags);
[…]

### 2022-05-22 src/lib/recovery_randomization.m

@@ -1,119 +1,119 @@
-function [inputDistribution, equivalentDistribution, weightedSumRate] = recovery_randomization(weight, symbolRatio, equivalentChannel, noisePower, jointDistribution, beamformer, dmtc, nKernels, nSamples, tolerance)
+function [distribution, equivalentDistribution] = recovery_randomization(symbolRatio, weight, snr, jointDistribution, dmac, nKernels, nInstances, tolerance)
 	% Function:
-	%	- extract a good tag input distribution (corresponding to no transmit cooperation) by randomization
+	%	- extract individual tag input distribution from joint input distribution by randomization
     %
     % Input:
-	%	- weight: the relative priority of the primary link
-	%	- symbolRatio: the ratio of the backscatter symbol period over the primary symbol period
-	%	- equivalentChannel [(nStates ^ nTags) * nTxs]: equivalent AP-user channels under all backscatter input combinations
-	%	- noisePower: average noise power at the user
-	%	- jointDistribution [nStates * ... (nTags) ... * nStates]: the joint input distribution of all tags corresponding to the relaxed input optimization problem
-	%	- beamformer [nTxs * 1]: transmit beamforming vector at the AP
-    %	- dmtc [(nStates ^ nTags) * nOutputs]: the transition probability matrix of the backscatter discrete memoryless thresholding MAC
-	%	- nKernels: number of kernels used in the approximation (equals to the rank)
-	%	- nSamples: number of random samples to be generated in randomization
-	%	- tolerance: the maximum tolerable relative entropy between the original and approximated arrays
+	%	- symbolRatio: backscatter/primary symbol duration ratio
+	%	- weight: relative priority of primary link
+	%	- snr [nInputs x 1]: average receive signal-to-noise ratio per primary symbol for each tag state tuple
+	%	- jointDistribution [nStates x ... (nTags-dimensional) ... x nStates]: joint tag input distribution with full transmit cooperation
+	%	- dmac [nInputs x nOutputs]: discrete memoryless thresholding multiple access channel whose input and output are tag state tuple
+	%	- nKernels: number of kernels used in appriximate array (i.e. rank of approximate array)
+	%	- nInstances: number of random instances to generate for each tag
[…]

### 2022-05-22 src/lib/smawk.m

@@ -11,7 +11,7 @@ function [p] = smawk(matrix, r, c)
 			if i < length(r)
 				u = p(i + 1);
 			else
-				u = inf;
+				u = Inf;
 			end
 			while j <= length(r) && c(j) <= u
 				if matrix(r(i), c(j)) < matrix(r(i), p(i))

### 2022-05-22 src/lib/state_tuple.m

@@ -1,0 +1,22 @@
+function [stateTuple] = state_tuple(nTags, nStates)
+	% Function:
+	%	- enumerate tag state tuples with entries as state indexes
+    %
+    % Input:
+	%	- nTags: number of tags
+    %	- nStates: number of available states at tags (i.e., modulation order)
+    %
+    % Output:
+	%	- stateTuple [nTags x nInputs]: each column is a nTags-tuple whose entries come from state indexes
+    %
+    % Author & Date: Yang (i@snowztail.com), 21 Dec 25
+
+	% * Enumerate tuples by recursion
+	if nTags > 1
+		stateTuple = sortrows(combvec(1 : nStates, state_tuple(nTags - 1, nStates)));
+	elseif nTags == 1
+		stateTuple = 1 : nStates;
+	% elseif nTags == 0
+	% 	stateTuple = double.empty(0, 1);
+	end
+end

### 2022-05-22 src/lib/t_bisection.m

@@ -1,0 +1,135 @@
+function [threshold, dmtc, backscatterRate] = t_bisection(symbolRatio, equivalentChannel, noisePower, nBins, equivalentDistribution, beamformer)
+	% Function:
+	%	- group the received energy bins into convex adjoint decision regions by bisection
+    %
+    % Input:
+	%	- symbolRatio: the ratio of the backscatter symbol period over the primary symbol period
+	%	- equivalentChannel [(nStates ^ nTags) * nTxs]: equivalent primary channel under each tag input combination
+	%	- noisePower: average noise power at the user
+	%	- nBins: number of discretization bins over received signal
+	%	- equivalentDistribution [1 * (nStates ^ nTags)]: equivalent input combination probability distribution
+	%	- beamformer [nTxs * 1]: transmit beamforming vector at the AP
+    %
+    % Output:
+	%	- threshold [1 * (nOutputs + 1)]: boundaries of decision regions
+	%	- dmtc [(nStates ^ nTags) * nOutputs]: the transition probability matrix of the backscatter discrete memoryless thresholding MAC
+	%	- backscatterRate: the achievable sum rate for the backscatter link (nats per channel use)
+    %
+    % Comment:
+    %	- For a given t_0 and t_1, the optimal t_j for j = 2, ..., K - 1 can be uniquely determined by bisection
+	%	- Traverse all possible t_1 and choose the corresponding thresholding set that maximizes mutual information
+    %
+    % Author & Date: Yang (i@snowztail.com), 22 Feb 18
+	% ! sort received power to match decision regions?
+
+	tolerance = 1e-6;
+	
+	% * Get data
+	nOutputs = size(equivalentDistribution, 2);
+	nLevels = nBins + 1;
+
+	% * Obtain threshold candidates that delimit output into discrete bins
+	thresholdCandidate = threshold_candidate(symbolRatio, equivalentChannel, noisePower, nBins, beamformer);
+
+	% * Evaluate DMC over all bins
+	dmc = channel_discretization(symbolRatio, equivalentChannel, noisePower, beamformer, thresholdCandidate);
+
+	% * Optimal t_0 = 0 and t_K+1 = ∞, traverse all possible t_1
+	backscatterRateSet = zeros(nLevels, 1);
+	thresholdSet = cell(nLevels, 1);
+	for iLevel = 2 : nLevels - 1
[…]

### 2022-05-22 src/lib/t_dp.m

@@ -1,0 +1,65 @@
+function [threshold, dmtc, backscatterRate] = threshold_dp(symbolRatio, equivalentChannel, noisePower, nBins, equivalentDistribution, beamformer)
+	% Function:
+	%	- group the received energy bins into convex decision regions by dynamic programming
+    %
+    % Input:
+	%	- symbolRatio: the ratio of the backscatter symbol period over the primary symbol period
+	%	- equivalentChannel [(nStates ^ nTags) * nTxs]: equivalent primary channel under each tag input combination
+	%	- noisePower: average noise power at the user
+	%	- nBins: number of discretization bins over received signal
+	%	- equivalentDistribution [1 * (nStates ^ nTags)]: equivalent input combination probability distribution
+	%	- beamformer [nTxs * 1]: transmit beamforming vector at the AP
+    %
+    % Output:
+	%	- threshold [1 * (nOutputs + 1)]: boundaries of decision regions
+	%	- dmtc [(nStates ^ nTags) * nOutputs]: the transition probability matrix of the backscatter discrete memoryless thresholding MAC
+	%	- backscatterRate: the achievable sum rate for the backscatter link (nats per channel use)
+    %
+    % Author & Date: Yang (i@snowztail.com), 22 Feb 09
+
+	% * Get data
+	nOutputs = size(equivalentDistribution, 2);
+
+	% * Obtain threshold candidates that delimit output into discrete bins
+	thresholdCandidate = threshold_candidate(symbolRatio, equivalentChannel, noisePower, nBins, beamformer);
+
+	% * Evaluate DMC over all bins
+	dmc = channel_discretization(symbolRatio, equivalentChannel, noisePower, beamformer, thresholdCandidate);
+
+	% * Initialize cost functions
+	dp = zeros(nBins, nOutputs);
+	sol = zeros(nBins, nOutputs);
+	for iBin = 1 : nBins
+		dp(iBin, 1) = quantization_cost(1 : iBin, equivalentDistribution, dmc);
+	end
+
+	% * Compute dp
+	for iOutput = 2 : nOutputs
+		for iBin = nBins - nOutputs + iOutput : -1 : iOutput
+			dpCandidate = inf(nBins - 2, 1);
+			for iThreshold = iOutput - 1 : iBin - 1
[…]

### 2022-05-22 src/lib/t_smawk.m

@@ -1,0 +1,80 @@
+function [threshold, dmtc, backscatterRate] = t_smawk(symbolRatio, equivalentChannel, noisePower, nBins, equivalentDistribution, beamformer)
+	% Function:
+	%	- group the received energy bins into convex decision regions by dynamic programming accelerated by SMAWK algorithm
+    %
+    % Input:
+	%	- symbolRatio: backscatter/primary symbol duration ratio
+	%	- receivePower [nInputs x 1]: average receive power per primary symbol for each tag state tuple
+	%	- equivalentDistribution [nInputs x 1]: equivalent single-source distribution for each tag input distribution tuple
+	%	- dmc [nInputs x nBins]: discrete memoryless channel whose input is tag state tuple and output is (high-resolution) quantized energy bins
+	%	- thresholdSet [1 x (nBins + 1)]: boundaries of quantized energy bins
+    %
+    % Output:
+	%	- threshold [1 x (nOutputs + 1)]: boundaries of decision regions (including 0 and Inf)
+    %
+    % Comment:
+    %	- SWAWK algorithm requires quantization cost to satisfy the Quadrangle Inequality (QI)
+    %
+    % Author & Date: Yang (i@snowztail.com), 22 Feb 09
+
+
+	% * Get data
+	nOutputs = size(equivalentDistribution, 1);
+
+	% * Obtain threshold candidates that delimit output into discrete bins
+	thresholdCandidate = threshold_candidate(symbolRatio, equivalentChannel, noisePower, nBins, beamformer);
+
+	% * Evaluate DMC over all bins
+	dmc = channel_discretization(symbolRatio, equivalentChannel, noisePower, beamformer, thresholdCandidate);
+
+	% * Initialize cost functions
+	dp = zeros(nBins, nOutputs);
+	sol = zeros(nBins, nOutputs);
+	for iBin = 1 : nBins
+		dp(iBin, 1) = quantization_cost(1 : iBin, equivalentDistribution, dmc);
+	end
+
+	% * Generate monotone matrix
+	for iOutput = 2 : nOutputs
+		D = zeros(nBins - nOutputs + 1);
+		for iRow = 1 : nBins - nOutputs + 1
+			for iColumn = 1 : nBins - nOutputs + 1
+				if iRow >= iColumn
[…]

### 2022-05-22 src/lib/threshold_bisection.m

@@ -1,133 +1,105 @@
-function [threshold, dmtc, backscatterRate] = threshold_bisection(symbolRatio, equivalentChannel, noisePower, nBins, equivalentDistribution, beamformer)
+function [threshold] = threshold_bisection(symbolRatio, receivePower, equivalentDistribution, quantizationSet, binDmc, tolerance)
 	% Function:
-	%	- group the received energy bins into convex decision regions by bisection
+	%	- group received energy bins into convex adjoint decision regions by bisection
     %
     % Input:
-	%	- symbolRatio: the ratio of the backscatter symbol period over the primary symbol period
-	%	- equivalentChannel [(nStates ^ nTags) * nTxs]: equivalent AP-user channels under all backscatter input combinations
-	%	- noisePower: average noise power at the user
-	%	- nBins: number of discretization bins over received signal
-	%	- equivalentDistribution [1 * (nStates ^ nTags)]: equivalent input combination probability distribution
-	%	- beamformer [nTxs * 1]: transmit beamforming vector at the AP
+	%	- symbolRatio: backscatter/primary symbol duration ratio
+	%	- receivePower [nInputs x 1]: average receive power per primary symbol for each tag state tuple
+	%	- equivalentDistribution [nInputs x 1]: equivalent single-source distribution for each tag input distribution tuple
+	%	- quantizationSet [1 x (nBins + 1)]: boundaries of quantized energy bins
+	%	- binDmc [nInputs x nBins]: discrete memoryless channel whose input is tag state tuple and output is (high-resolution) quantized energy bins
+    %	- tolerance: minimum rate gain per iteration
     %
     % Output:
-	%	- threshold [1 * (nOutputs + 1)]: boundaries of decision regions
-	%	- dmtc [(nStates ^ nTags) * nOutputs]: the transition probability matrix of the backscatter discrete memoryless thresholding MAC
-	%	- backscatterRate: the achievable sum rate for the backscatter link (nats per channel use)
+	%	- threshold [1 x (nOutputs + 1)]: boundaries of decision regions (including 0 and Inf)
     %
     % Comment:
[…]

### 2022-05-22 src/lib/threshold_dp.m

@@ -1,44 +1,41 @@
-function [threshold, dmtc, backscatterRate] = threshold_dp(symbolRatio, equivalentChannel, noisePower, nBins, equivalentDistribution, beamformer)
+function [threshold] = threshold_dp(equivalentDistribution, quantizationSet, binDmc)
 	% Function:
-	%	- group the received energy bins into convex decision regions by dynamic programming
+	%	- group received energy bins into convex adjoint decision regions by dynamic programming
     %
     % Input:
-	%	- symbolRatio: the ratio of the backscatter symbol period over the primary symbol period
-	%	- equivalentChannel [(nStates ^ nTags) * nTxs]: equivalent AP-user channels under all backscatter input combinations
-	%	- noisePower: average noise power at the user
-	%	- nBins: number of discretization bins over received signal
-	%	- equivalentDistribution [1 * (nStates ^ nTags)]: equivalent input combination probability distribution
-	%	- beamformer [nTxs * 1]: transmit beamforming vector at the AP
+	%	- equivalentDistribution [nInputs x 1]: equivalent single-source distribution for each tag input distribution tuple
+	%	- quantizationSet [1 x (nBins + 1)]: boundaries of quantized energy bins
+	%	- binDmc [nInputs x nBins]: discrete memoryless channel whose input is tag state tuple and output is (high-resolution) quantized energy bins
     %
     % Output:
-	%	- threshold [1 * (nOutputs + 1)]: boundaries of decision regions
-	%	- dmtc [(nStates ^ nTags) * nOutputs]: the transition probability matrix of the backscatter discrete memoryless thresholding MAC
-	%	- backscatterRate: the achievable sum rate for the backscatter link (nats per channel use)
+	%	- threshold [1 x (nOutputs + 1)]: boundaries of decision regions (including 0 and Inf)
     %
+	% Reference:
+	%	- X. He, K. Cai, W. Song, and Z. Mei, “Dynamic programming for sequential deterministic quantization of discrete memoryless channels,” IEEE Transactions on Communications, vol. 69, no. 6, pp. 3638–3651, 2021.
+	%
     % Author & Date: Yang (i@snowztail.com), 22 Feb 09
 
 	% * Get data
[…]

### 2022-05-22 src/lib/threshold_ml.m

@@ -1,35 +1,26 @@
-function [threshold, dmtc] = threshold_ml(symbolRatio, equivalentChannel, noisePower, beamformer)
+function [threshold] = threshold_ml(symbolRatio, receivePower)
 	% Function:
-	%	- obtain the decision thresholds of maximum likelihood detector
+	%	- obtain the decision thresholds for maximum likelihood detector
     %
     % Input:
-	%	- symbolRatio: the ratio of the secondary symbol period over the primary symbol period
-	%	- equivalentChannel [(nStates ^ nTags) * nTxs]: equivalent AP-user channels under all backscatter input combinations
-	%	- noisePower: average noise power at the user
-	%	- beamformer [nTxs * 1]: transmit beamforming vector at the AP
+	%	- symbolRatio: backscatter/primary symbol duration ratio
+	%	- receivePower [nInputs x 1]: average receive power per primary symbol for each tag state tuple
     %
     % Output:
-	%	- threshold [1 * (nOutputs + 1)] : the ML thresholding values
-	%	- dmtc [(nStates ^ nTags) * nOutputs]: the transition probability matrix of the backscatter discrete memoryless thresholding MAC
+	%	- threshold [1 x (nOutputs + 1)]: boundaries of ML decision regions (including 0 and Inf)
     %
     % Comment:
-    %	- ML detection does not require input distribution
+    %	- ML detector does not depend on input distribution
     %
     % Author & Date: Yang (i@snowztail.com), 23 Mar 17
 
 	% * Get data
-	nOutputs = size(equivalentChannel, 1);
+	nOutputs = size(receivePower, 1);
 
-	% * Compute the expected received power under all backscatter input combinations
-	[sortedPower, sortIndex] = sort(abs(equivalentChannel * beamformer) .^ 2 + noisePower);
-
-	% * Each ML threshold depends on the average received power of adjacent detection regions
-	threshold(nOutputs + 1) = inf;
+	% * Each ML threshold depends on average receive power of adjacent letters
+	sortPower = sort(receivePower);
+	threshold(nOutputs + 1) = Inf;
 	for iOutput = 2 : nOutputs
[…]

### 2022-05-22 src/lib/threshold_smawk.m

@@ -1,40 +1,38 @@
-function [threshold, dmtc, backscatterRate] = threshold_smawk(symbolRatio, equivalentChannel, noisePower, nBins, equivalentDistribution, beamformer)
+function [threshold] = threshold_smawk(equivalentDistribution, quantizationSet, binDmc)
 	% Function:
-	%	- group the received energy bins into convex decision regions by dynamic programming accelerated by SMAWK algorithm
+	%	- group received energy bins into convex adjoint decision regions by dynamic programming accelerated by SMAWK algorithm
     %
     % Input:
-	%	- symbolRatio: the ratio of the backscatter symbol period over the primary symbol period
-	%	- equivalentChannel [(nStates ^ nTags) * nTxs]: equivalent AP-user channels under all backscatter input combinations
-	%	- noisePower: average noise power at the user
-	%	- nBins: number of discretization bins over received signal
-	%	- equivalentDistribution [1 * (nStates ^ nTags)]: equivalent input combination probability distribution
-	%	- beamformer [nTxs * 1]: transmit beamforming vector at the AP
+	%	- equivalentDistribution [nInputs x 1]: equivalent single-source distribution for each tag input distribution tuple
+	%	- quantizationSet [1 x (nBins + 1)]: boundaries of quantized energy bins
+	%	- binDmc [nInputs x nBins]: discrete memoryless channel whose input is tag state tuple and output is (high-resolution) quantized energy bins
     %
     % Output:
-	%	- threshold [1 * (nOutputs + 1)]: boundaries of decision regions
-	%	- dmtc [(nStates ^ nTags) * nOutputs]: the transition probability matrix of the backscatter discrete memoryless thresholding MAC
-	%	- backscatterRate: the achievable sum rate for the backscatter link (nats per channel use)
+	%	- threshold [1 x (nOutputs + 1)]: boundaries of decision regions (including 0 and Inf)
     %
     % Comment:
-    %	- SWAWK algorithm requires the quantization cost function to satisfy the Quadrangle Inequality (QI)
[…]

### 2022-05-22 src/lib/tuple_tag.m

@@ -1,0 +1,22 @@
+function [tuple] = tuple_tag(domain)
+	% Function:
+	%	- enumerate tag state index/input probability tuples
+    %
+    % Input:
+	%	- domain [nStates x nTags]: k-th column denotes state index set or input probability set of tag k
+    %
+    % Output:
+	%	- tuple [nInputs x nTags]: i-th row is a K-tuple whose entries come from state index/input distribution of all tags
+    %
+    % Author & Date: Yang (i@snowztail.com), 22 May 10
+
+	% * Get data
+	nTags = size(domain, 2);
+
+	% * Enumerate tuples by recursion
+	if nTags > 1
+		tuple = product_cartesian(domain(:, 1), tuple_tag(domain(:, 2 : end)));
+	elseif nTags == 1
+		tuple = domain;
+	end
+end

### 2022-05-22 src/main.m

@@ -1,23 +1,15 @@
-setup; clear; cvx_clear; clc; close all; config;
+setup; clear; cvx_clear; cvx_begin; cvx_end; clc; close all; config;
 
 % * Generate channels
-directChannel = sqrt(0.5) * (randn(1, nTxs) + 1i * randn(1, nTxs));
-cascadedChannel = zeros(nTags, nTxs);
+directChannel = path_loss(frequency, directDistance, directExponent) * fading_ricean(nTxs, 1, directFactor, directAoa);
+cascadedChannel = zeros(nTxs, nTags);
 for iTag = 1 : nTags
-	cascadedChannel(iTag, :) = (sqrt(0.5) * (randn(1, nTxs) + 1i * randn(1, nTxs))) * (sqrt(0.5) * (randn + 1i * randn));
+	cascadedChannel(:, iTag) = path_loss(frequency, forwardDistance(iTag), forwardExponent) * fading_ricean(nTxs, 1, forwardFactor, forwardAoa(iTag)) * path_loss(frequency, backwardDistance(iTag), backwardExponent) * fading_ricean(1, 1, backwardFactor, backwardAoa(iTag));
 end
+equivalentChannel = directChannel + sqrt(scatterRatio) * cascadedChannel * transpose(constellation(tuple_tag(repmat(transpose(1 : nStates), [1, nTags]))));
 
-% * Obtain equivalent AP-user channels under all backscatter input combinations
-indexCombination = index_combination(nTags, nStates);
-inputCombination = transpose(constellation(indexCombination));
-equivalentChannel = zeros(nInputs, nTxs);
-for iInput = 1 : nInputs
-	equivalentChannel(iInput, :) = directChannel + sqrt(reflectRatio) * inputCombination(iInput, :) * cascadedChannel;
-end
-
-% * Evaluate rate regions
+% * Evaluate rate region
 rate = zeros(2, nWeights);
 for iWeight = 1 : nWeights
-	weight = weightSet(iWeight);
-	[rate, inputDistribution, threshold, beamformer] = block_coordinate_descent(weight, nTags, symbolRatio, equivalentChannel, txPower, noisePower, nBins, tolerance, 'Input', 'kkt', 'Threshold', 'smawk');
+	[rate, inputDistribution, threshold, beamformer] = block_coordinate_descent(nTags, symbolRatio, transmitPower, noisePower, weightSet(iWeight), equivalentChannel, 'Distribution', 'kkt', 'Beamforming', 'pgd', 'Threshold', 'smawk');
 end

### 2022-05-22 src/main_h.m

@@ -1,0 +1,25 @@
+setup; clear; cvx_clear; clc; close all; config;
+
+% * Generate channels
+directChannel = sqrt(0.5) * (randn(1, nTxs) + 1i * randn(1, nTxs));
+cascadedChannel = zeros(nTags, nTxs);
+for iTag = 1 : nTags
+	cascadedChannel(iTag, :) = (sqrt(0.5) * (randn(1, nTxs) + 1i * randn(1, nTxs))) * (sqrt(0.5) * (randn + 1i * randn));
+end
+
+% * Obtain equivalent primary channel for each tag state tuple
+% [indexTuple, inputTuple] = state_tuple(nTags, nStates);
+% indexCombination = index_combination(nTags, nStates);
+stateTuple = state_tuple(nTags, nStates);
+inputCombination = constellation(stateTuple);
+equivalentChannel = zeros(nInputs, nTxs);
+for iInput = 1 : nInputs
+	equivalentChannel(iInput, :) = directChannel + sqrt(scatterRatio) * inputCombination(iInput, :) * cascadedChannel;
+end
+
+% * Evaluate rate regions
+rate = zeros(2, nWeights);
+for iWeight = 1 : nWeights
+	weight = weightSet(iWeight);
+	[rate, inputDistribution, threshold, beamformer] = block_coordinate_descent(weight, nTags, symbolRatio, equivalentChannel, transmitPower, noisePower, nBins, tolerance, 'Input', 'kkt', 'Threshold', 'smawk');
+end

### 2022-05-22 src/outer_product.m

@@ -1,0 +1,8 @@
+function [outerProduct] = outer_product(matrix)
+	nVectors = size(matrix, 2);
+    outerProduct = matrix(:, 1);
+	for iVector = 2 : nVectors
+		vector = permute(matrix(:, iVector), circshift(1 : (dimension_number(outerProduct) + 1), dimension_number(outerProduct)));
+		outerProduct = repmat(outerProduct, size(vector)) .* repmat(vector, size(outerProduct));
+	end
+end

### 2022-05-22 src/setup.m

@@ -1,5 +1,5 @@
 addpath(genpath(pwd));
-rmpath('toolbox/CVX/');
+% rmpath('toolbox/CVX/');
 set(groot, 'defaulttextinterpreter', 'latex');
 set(groot, 'defaultaxesticklabelinterpreter', 'latex');
 set(groot, 'defaultaxesfontname', 'latex');

### 2022-05-23 assets/tag_distribution.tex
:paintbrush: Illustrate probability distribution

\begin{tikzpicture}
    \begin{groupplot}
        [group style = {%
        rows = 3,
        group name = plots,
%         xlabels at = edge bottom,
        x descriptions at = edge bottom,
        y descriptions at = edge left,
        vertical sep = 15
        },
        ybar,
        xmin = 0,
        xmax = 4,
        xtick = data,
        ymin = 0,
        ymax = 1,
        xlabel={Reflection State},
        ylabel={Probability},
        enlarge x limits = {value = 0.25, upper},
        enlarge y limits = {value = 0.1, upper},
        width = 10cm,
        height = 4cm
        ]
        \nextgroupplot
        \addplot[blue,fill=blue!30!white] coordinates {(1,0.25) (2,0.25) (3,0.25) (4,0.25)};
        \legend{SR}
        \nextgroupplot
        \addplot[red,fill=red!30!white] coordinates {(1,0) (2,1) (3,0) (4,0)};
        \legend{IRS}
        \nextgroupplot
        \addplot[brown!60!black!,fill=brown!30!white] coordinates {(1,0.2) (2,0.4) (3,0.3) (4,0.1)};
        \legend{Metascatter}
    \end{groupplot}
\end{tikzpicture}

### 2022-05-24 assets/tag_distribution.tex
:paintbrush: Illustrate probability distribution

@@
 	\begin{groupplot}
-        [group style = {%
-        rows = 3,
-        group name = plots,
-%         xlabels at = edge bottom,
-        x descriptions at = edge bottom,
-        y descriptions at = edge left,
-        vertical sep = 15
+		[group style={%
+					rows=3,
+					group name=plots,
+					x descriptions at=edge bottom,
+					y descriptions at=edge left,
+					vertical sep=15
 				},
 			ybar,
-        xmin = 0,
-        xmax = 4,
-        xtick = data,
-        ymin = 0,
-        ymax = 1,
+			xmin=0,
+			xmax=4,
+			xtick={1,2,3,4},
+			ymin=0,
+			ymax=1,
 			xlabel={Reflection State},
 			ylabel={Probability},
-        enlarge x limits = {value = 0.25, upper},
-        enlarge y limits = {value = 0.1, upper},
-        width = 10cm,
-        height = 4cm
+			enlarge x limits={value=0.25,upper},
+			enlarge y limits={value=0.1,upper},
+			width=10cm,
+			height=4cm,
+			every axis plot/.append style={bar shift=0},
+			legend style={pattern=none}
 		]
 		\nextgroupplot
-        \addplot[blue,fill=blue!30!white] coordinates {(1,0.25) (2,0.25) (3,0.25) (4,0.25)};
+		\addplot[blue,fill=blue!30!white] coordinates {(-1,-1)};
+		\addplot[blue,fill=blue!30!white,postaction={pattern=horizontal lines},pattern color=.] coordinates {(1,0.25)};
+		\addplot[blue,fill=blue!30!white,postaction={pattern=north west lines},pattern color=.] coordinates {(2,0.25)};
+		\addplot[blue,fill=blue!30!white,postaction={pattern=vertical lines},pattern color=.] coordinates {(3,0.25)};
+		\addplot[blue,fill=blue!30!white,postaction={pattern=north east lines},pattern color=.] coordinates {(4,0.25)};
 		\legend{SR}
 		\nextgroupplot
-        \addplot[red,fill=red!30!white] coordinates {(1,0) (2,1) (3,0) (4,0)};
+		\addplot[red,fill=red!30!white] coordinates {(-1,-1)};
+		\addplot[red,fill=red!30!white,postaction={pattern=horizontal lines},pattern color=.] coordinates {(1,0)};
+		\addplot[red,fill=red!30!white,postaction={pattern=north west lines},pattern color=.] coordinates {(2,1)};
+		\addplot[red,fill=red!30!white,postaction={pattern=vertical lines},pattern color=.] coordinates {(3,0)};
+		\addplot[red,fill=red!30!white,postaction={pattern=north east lines},pattern color=.] coordinates {(4,0)};
 		\legend{IRS}
 		\nextgroupplot
-        \addplot[brown!60!black!,fill=brown!30!white] coordinates {(1,0.2) (2,0.4) (3,0.3) (4,0.1)};
+		\addplot[brown,fill=brown!30!white] coordinates {(-1,-1)};
+		\addplot[brown,fill=brown!30!white,postaction={pattern=horizontal lines},pattern color=.] coordinates {(1,0.2)};
+		\addplot[brown,fill=brown!30!white,postaction={pattern=north west lines},pattern color=.] coordinates {(2,0.4)};
+		\addplot[brown,fill=brown!30!white,postaction={pattern=vertical lines},pattern color=.] coordinates {(3,0.3)};
+		\addplot[brown,fill=brown!30!white,postaction={pattern=north east lines},pattern color=.] coordinates {(4,0.1)};
 		\legend{Metascatter}

### 2022-05-24 main.tex
:paintbrush: Illustrate probability distribution

@@
 \pgfplotsset{compat=newest}
-\usepgfplotslibrary{patchplots}
+\usepgfplotslibrary{patchplots,groupplots}
 \newtheorem{proposition}{Proposition}
@@
 \ctikzset{american}
-\usetikzlibrary{arrows,calc,matrix,patterns,positioning}
+\usetikzlibrary{arrows,calc,matrix,patterns,pgfplots.groupplots,plotmarks,positioning}
 
@@
 		% When the \gls{csi} and reflection alphabet $\{\Gamma_1,\ldots,\Gamma_M\}$ are available at the reader, the tag can be successfully decoded based on the received signal.
+
+		\begin{figure}[!t]
+			\centering
+			\resizebox{0.95\columnwidth}{!}{
+				\begin{tikzpicture}
+					\begin{groupplot}
+						[group style={%
+									rows=3,
+									group name=plots,
+									x descriptions at=edge bottom,
+									y descriptions at=edge left,
+									vertical sep=15
+								},
+							ybar,
+							xmin=0,
+							xmax=4,
+							xtick={1,2,3,4},
+							ymin=0,
+							ymax=1,
+							xlabel={Reflection State},
+							ylabel={Probability},
+							enlarge x limits={value=0.25,upper},
+							enlarge y limits={value=0.1,upper},
+							width=10cm,
+							height=4cm,
+							every axis plot/.append style={bar shift=0},
+							legend style={pattern=none}
+						]
+						\nextgroupplot
+						\addplot[blue,fill=blue!30!white] coordinates {(-1,-1)};
+						\addplot[blue,fill=blue!30!white,postaction={pattern=horizontal lines},pattern color=.] coordinates {(1,0.25)};
+						\addplot[blue,fill=blue!30!white,postaction={pattern=north west lines},pattern color=.] coordinates {(2,0.25)};
+						\addplot[blue,fill=blue!30!white,postaction={pattern=vertical lines},pattern color=.] coordinates {(3,0.25)};
+						\addplot[blue,fill=blue!30!white,postaction={pattern=north east lines},pattern color=.] coordinates {(4,0.25)};
+						\legend{SR}
+						\nextgroupplot
+						\addplot[red,fill=red!30!white] coordinates {(-1,-1)};
+						\addplot[red,fill=red!30!white,postaction={pattern=horizontal lines},pattern color=.] coordinates {(1,0)};
+						\addplot[red,fill=red!30!white,postaction={pattern=north west lines},pattern color=.] coordinates {(2,1)};
+						\addplot[red,fill=red!30!white,postaction={pattern=vertical lines},pattern color=.] coordinates {(3,0)};
+						\addplot[red,fill=red!30!white,postaction={pattern=north east lines},pattern color=.] coordinates {(4,0)};
+						\legend{IRS}
+						\nextgroupplot
+						\addplot[brown,fill=brown!30!white] coordinates {(-1,-1)};
+						\addplot[brown,fill=brown!30!white,postaction={pattern=horizontal lines},pattern color=.] coordinates {(1,0.2)};
+						\addplot[brown,fill=brown!30!white,postaction={pattern=north west lines},pattern color=.] coordinates {(2,0.4)};
+						\addplot[brown,fill=brown!30!white,postaction={pattern=vertical lines},pattern color=.] coordinates {(3,0.3)};
+						\addplot[brown,fill=brown!30!white,postaction={pattern=north east lines},pattern color=.] coordinates {(4,0.1)};
+						\legend{Metascatter}
+					\end{groupplot}
+				\end{tikzpicture}
+			}
+		\end{figure}
 

### 2022-05-25 assets/tag_distribution.tex
:paintbrush: Add probability and block illustrations

@@
 		\addplot[brown,fill=brown!30!white] coordinates {(-1,-1)};
-		\addplot[brown,fill=brown!30!white,postaction={pattern=horizontal lines},pattern color=.] coordinates {(1,0.2)};
-		\addplot[brown,fill=brown!30!white,postaction={pattern=north west lines},pattern color=.] coordinates {(2,0.4)};
-		\addplot[brown,fill=brown!30!white,postaction={pattern=vertical lines},pattern color=.] coordinates {(3,0.3)};
-		\addplot[brown,fill=brown!30!white,postaction={pattern=north east lines},pattern color=.] coordinates {(4,0.1)};
+		\addplot[brown,fill=brown!30!white,postaction={pattern=horizontal lines},pattern color=.] coordinates {(1,0.125)};
+		\addplot[brown,fill=brown!30!white,postaction={pattern=north west lines},pattern color=.] coordinates {(2,0.625)};
+		\addplot[brown,fill=brown!30!white,postaction={pattern=vertical lines},pattern color=.] coordinates {(3,0.25)};
+		\addplot[brown,fill=brown!30!white,postaction={pattern=north east lines},pattern color=.] coordinates {(4,0)};
 		\legend{Metascatter}

### 2022-05-25 assets/time_block.tex
:paintbrush: Add probability and block illustrations

\begin{tikzpicture}
	% SR
	\draw [blue,fill=blue!30!white,postaction={pattern=north west lines},pattern color=.](0,0) rectangle ++(1,1);
	\draw [blue,fill=blue!30!white,postaction={pattern=vertical lines},pattern color=.](1,0) rectangle ++(1,1);
	\draw [blue,fill=blue!30!white,postaction={pattern=horizontal lines},pattern color=.](2,0) rectangle ++(1,1);
	\draw [blue,fill=blue!30!white,postaction={pattern=north east lines},pattern color=.](3,0) rectangle ++(1,1);
	\draw [blue,fill=blue!30!white,postaction={pattern=north east lines},pattern color=.](4,0) rectangle ++(1,1);
	\draw [blue,fill=blue!30!white,postaction={pattern=vertical lines},pattern color=.](5,0) rectangle ++(1,1);
	\draw [blue,fill=blue!30!white,postaction={pattern=horizontal lines},pattern color=.](6,0) rectangle ++(1,1);
	\draw [blue,fill=blue!30!white,postaction={pattern=north west lines},pattern color=.](7,0) rectangle ++(1,1);
	\node[font=\LARGE] at (-0.75,0.5) {$\cdots$};
	\node[font=\LARGE] at (8.75,0.5) {$\cdots$};
	\node[font=\LARGE] at (-3.75,0.5) {SR};

	% IRS
	\foreach \x in {0,...,7}{
			\draw [red,fill=red!30!white,postaction={pattern=north west lines},pattern color=.](\x,-1.5) rectangle ++(1,1);
		}
	\node[font=\LARGE] at (-0.75,-1) {$\cdots$};
	\node[font=\LARGE] at (8.75,-1) {$\cdots$};
	\node[font=\LARGE] at (-3.75,-1) {IRS};

	% SR
	\draw [brown,fill=brown!30!white,postaction={pattern=north west lines},pattern color=.](0,-3) rectangle ++(1,1);
	\draw [brown,fill=brown!30!white,postaction={pattern=vertical lines},pattern color=.](1,-3) rectangle ++(1,1);
	\draw [brown,fill=brown!30!white,postaction={pattern=north west lines},pattern color=.](2,-3) rectangle ++(1,1);
	\draw [brown,fill=brown!30!white,postaction={pattern=north west lines},pattern color=.](3,-3) rectangle ++(1,1);
	\draw [brown,fill=brown!30!white,postaction={pattern=north west lines},pattern color=.](4,-3) rectangle ++(1,1);
	\draw [brown,fill=brown!30!white,postaction={pattern=vertical lines},pattern color=.](5,-3) rectangle ++(1,1);
	\draw [brown,fill=brown!30!white,postaction={pattern=horizontal lines},pattern color=.](6,-3) rectangle ++(1,1);
	\draw [brown,fill=brown!30!white,postaction={pattern=north west lines},pattern color=.](7,-3) rectangle ++(1,1);
	\node[font=\LARGE] at (-0.75,-2.5) {$\cdots$};
	\node[font=\LARGE] at (8.75,-2.5) {$\cdots$};
	\node[font=\LARGE] at (-3.75,-2.5) {Metascatter};

	\draw [pattern=horizontal lines](11,0.5) rectangle ++(0.5,0.5);
	\draw [pattern=north west lines](11,-2/3) rectangle ++(0.5,0.5);
	\draw [pattern=vertical lines](11,-11/6) rectangle ++(0.5,0.5);
	\draw [pattern=north east lines](11,-3) rectangle ++(0.5,0.5);
	\node[font=\Large,right] at (11.75,0.75){State 1};
	\node[font=\Large,right] at (11.75,-5/12){State 2};
	\node[font=\Large,right] at (11.75,-19/12){State 3};
	\node[font=\Large,right] at (11.75,-2.75){State 4};

% 	\draw [pattern=horizontal lines](11,0.5) rectangle ++(0.5,0.5);
% 	\draw [pattern=north west lines](11,-0.625) rectangle ++(0.5,0.5);
% 	\draw [pattern=vertical lines](11,-1.75) rectangle ++(0.5,0.5);
% 	\draw [pattern=north east lines](11,-2.875) rectangle ++(0.5,0.5);
% 	\node[font=\Large,right] at (11.75,0.75){State 1};
% 	\node[font=\Large,right] at (11.75,-0.375){State 2};
% 	\node[font=\Large,right] at (11.75,-1.5){State 3};
% 	\node[font=\Large,right] at (11.75,-2.625){State 4};

	% Time block
	\foreach \x in {0,...,7}{
			\draw (\x,1.75) rectangle ++(1,0.5);
		}
	\node[font=\LARGE] at (-0.75,2) {$\cdots$};
	\node[font=\LARGE] at (8.75,2) {$\cdots$};
	\node[font=\LARGE] at (-3.75,2) {Backscatter Block};
% 	\path (3,1.75) rectangle ++(1,0.5) node[midway,font=\Large] {$T_c$};

	\draw (11,1.875) rectangle ++(0.5,0.25);
	\node[font=\Large,right] at (11.75,2){$T_c$};

	\draw (11.125,3) rectangle ++(0.25,0.25);
	\node[font=\Large,right] at (11.75,3.125){$T_s$};

	\foreach \x in {0,...,31}{
			\draw (0.25*\x,3) rectangle ++(0.25,0.25);
		}
	\node[font=\LARGE] at (-0.75,3.125) {$\cdots$};
	\node[font=\LARGE] at (8.75,3.125) {$\cdots$};
	\node[font=\LARGE] at (-3.75,3.125) {Primary Block};

% 	\draw[dashed] (3.5,3.25) -- (3.25,3.5);
% 	\draw[dashed] (3.75,3.25) -- (4,3.5);
% 	\node[font=\Large,above] at (3.625,3.375){$T_s$};
\end{tikzpicture}

### 2022-05-25 main.tex
:paintbrush: Add probability and block illustrations

@@
 						\addplot[brown,fill=brown!30!white] coordinates {(-1,-1)};
-						\addplot[brown,fill=brown!30!white,postaction={pattern=horizontal lines},pattern color=.] coordinates {(1,0.2)};
-						\addplot[brown,fill=brown!30!white,postaction={pattern=north west lines},pattern color=.] coordinates {(2,0.4)};
-						\addplot[brown,fill=brown!30!white,postaction={pattern=vertical lines},pattern color=.] coordinates {(3,0.3)};
-						\addplot[brown,fill=brown!30!white,postaction={pattern=north east lines},pattern color=.] coordinates {(4,0.1)};
+						\addplot[brown,fill=brown!30!white,postaction={pattern=horizontal lines},pattern color=.] coordinates {(1,0.125)};
+						\addplot[brown,fill=brown!30!white,postaction={pattern=north west lines},pattern color=.] coordinates {(2,0.625)};
+						\addplot[brown,fill=brown!30!white,postaction={pattern=vertical lines},pattern color=.] coordinates {(3,0.25)};
+						\addplot[brown,fill=brown!30!white,postaction={pattern=north east lines},pattern color=.] coordinates {(4,0)};
 						\legend{Metascatter}

### 2022-05-26 assets/equivalent_circuit.tex
:paintbrush: Update probability and block illustrations

--- 2022-05-22 main.tex
@@
-\documentclass[journal]{IEEEtran}
-
-\usepackage{adjustbox}
-\usepackage{algorithm}
-\usepackage{algpseudocode}
-\usepackage{amsfonts}
-\usepackage{amsmath}
-\usepackage{amssymb}
-\usepackage{amsthm}
-\usepackage{array}
-\usepackage{circuitikz}
-\usepackage{cite}
-\usepackage{colortbl}
-\usepackage{environ}
-\usepackage{fixmath}
-\usepackage{grffile}
-\usepackage{hyperref}
-\usepackage{import}
-\usepackage{mathtools}
-\usepackage{microtype}
-\usepackage{multirow}
-\usepackage{pgffor}
-\usepackage{pgfgantt}
-\usepackage{pgfplots}
-\usepackage{physics}
-\usepackage{siunitx}
-\usepackage{stfloats}
-\usepackage{tcolorbox}
-\usepackage{tikz}
-\usepackage{url}
-\usepackage{xcolor}
-\usepackage[T1]{fontenc}
-\usepackage[acronym]{glossaries-extra}
-\usepackage[caption=false,font=footnotesize,subrefformat=parens,labelformat=parens]{subfig}
-\usepackage[short]{optidef}
-\usepackage[subtle]{savetrees}
-
-\listfiles
-\interdisplaylinepenalty=2500
-\pgfplotsset{compat=newest}
-\usepgfplotslibrary{patchplots}
-\newtheorem{proposition}{Proposition}
-\newtheorem{remark}{Remark}
-\newtheorem{theorem}{Theorem}
-\DeclareSIUnit{\belm}{Bm}
-\DeclareSIUnit{\dBm}{\deci\belm}
-\DeclareSIUnit{\beli}{Bi}
-\DeclareSIUnit{\dBi}{\deci\beli}
-\ctikzset{american}
-\usetikzlibrary{arrows,calc,matrix,patterns,positioning}
-
-\DeclarePairedDelimiterX{\infdivx}[2]{(}{)}{%
-	#1\;\delimsize\|\;#2%
-}
-\newcommand{\infdiv}{D\infdivx}
-\renewcommand{\qedsymbol}{\hfill\ensuremath{\Box}}
-
-\makeatletter
-\tikzset{
-	block/.style={draw,rectangle,align=center},
-    from/.style args={#1 to #2}{
-        above right={0cm of #1},
-        /utils/exec=\pgfpointdiff
-            {\tikz@scan@one@point\pgfutil@firstofone(#1)\relax}
-            {\tikz@scan@one@point\pgfutil@firstofone(#2)\relax},
-        minimum width/.expanded=\the\pgf@x,
-        minimum height/.expanded=\the\pgf@y
-	}
-}
-\makeatother
-
-\algrenewcommand{\algorithmicwhile}{\textbf{While}}
-\algrenewcommand{\algorithmicif}{\textbf{If}}
-\algrenewcommand{\algorithmicthen}{\textbf{Then}}
-\algrenewcommand{\algorithmicelse}{\textbf{Else}}
-\algrenewcommand{\algorithmicend}{\textbf{End}}
-\algrenewcommand{\algorithmicrepeat}{\textbf{Repeat}}
-\algrenewcommand{\algorithmicuntil}{\textbf{Until}}
-
-\setabbreviationstyle[acronym]{long-short}
-
-\newacronym{af}{AF}{Amplify-and-Forward}
-\newacronym{ambc}{AmBC}{Ambient Backscatter Communications}
-\newacronym{ap}{AP}{Access Point}
-\newacronym{awgn}{AWGN}{Additive White Gaussian Noise}
-\newacronym{bcd}{BCD}{Block Coordinate Descent}
-\newacronym{bibo}{BIBO}{Binary-Input Binary-Output}
-\newacronym{bpcu}{\si{bpcu}}{bit per channel use}
-\newacronym{bpsphz}{\si{bps/Hz}}{bit per second per Hertz}
-\newacronym{cscg}{CSCG}{Circularly Symmetric Complex Gaussian}
-\newacronym{csi}{CSI}{Channel State Information}
-\newacronym{df}{DF}{Decode-and-Forward}
-\newacronym{dmc}{DMC}{Discrete Memoryless Channel}
-\newacronym{dmtc}{DMTC}{Discrete Memoryless Thresholding Channel}
-\newacronym{dmtmac}{DMTMAC}{Discrete Memoryless Thresholding Multiple Access Channel}
-\newacronym{dp}{DP}{Dynamic Programming}
-\newacronym{iid}{i.i.d.}{independent and identically distributed}
-\newacronym{irs}{IRS}{Intelligent Reflecting Surface}
-\newacronym{kkt}{KKT}{Karush–Kuhn–Tucker}
-\newacronym{mac}{MAC}{Multiple Access Channel}
-\newacronym{mc}{MC}{Multiplication Coding}
-\newacronym{miso}{MISO}{Multiple-Input Single-Output}
-\newacronym{mimo}{MIMO}{Multiple-Input Multiple-Output}
-\newacronym{ml}{ML}{Maximum-Likelihood}
-\newacronym{noma}{NOMA}{Non-Orthogonal Multiple Access}
-\newacronym{ofdm}{OFDM}{Orthogonal Frequency-Division Multiplexing}
-\newacronym{pdf}{PDF}{Probability Density Function}
-\newacronym{psk}{PSK}{Phase Shift Keying}
-\newacronym{pin}{PIN}{Positive Intrinsic-Negative}
-\newacronym{qam}{QAM}{Quadrature Amplitude Modulation}
-\newacronym{rf}{RF}{Radio Frequency}
-\newacronym{sc}{SC}{Superposition Coding}
-\newacronym{sic}{SIC}{Successive Interference Cancellation}
-\newacronym{simo}{SIMO}{Single-Input Multiple-Output}
-\newacronym{sinr}{SINR}{Signal-to-Interference-plus-Noise Ratio}
-\newacronym{smawk}{SMAWK}{Shor-Moran-Aggarwal-Wilber-Klawe}
-\newacronym{sr}{SR}{Symbiotic Radio}
-\newacronym{tdma}{TDMA}{Time-Division Multiple Access}
-\newacronym{tg}{TG}{tag}
-\newacronym{ue}{UE}{user}
-
-\begin{document}
-\title{Metascatter: Unifying Symbiotic Radio and Intelligent Reflecting Surface}
-\author{
-	\IEEEauthorblockN{
-		Yang~Zhao,~\IEEEmembership{Member,~IEEE,}
-		and~Bruno~Clerckx,~\IEEEmembership{Senior~Member,~IEEE}
-	}
-	\thanks{
-		The authors are with the Department of Electrical and Electronic Engineering, Imperial College London, London SW7 2AZ, U.K. (e-mail: \{yang.zhao18, b.clerckx\}@imperial.ac.uk).
-	}
-}
-\maketitle
-
-\begin{abstract}
-	Backscatter allows wireless nodes to harvest energy from, modulate information over, and reconfigure propagation of surrounding radio waves.
-	We introduce the concept of Metascatter, which adapts the input probability distribution of a finite-state backscatter device based on Channel State Information (CSI), to simultaneously act as parasitic source of Symbiotic Radio (SR) that conveys sensor data and reflecting element of Intelligent Reflecting Surface (IRS) that assists legacy transmission.
-	Using shared spectrum, energy, and infrastructures, fully cognitive networks can be built over Metascatter, and we consider a basic scenario where a multi-antenna Access Point (AP) and multiple Metascatter simultaneously transmit to a single-antenna user.
-	Since tags involve load switching and the primary and backscatter messages are multiplied (instead of superposed) in the received signal, it is assumed the user employ joint energy detection on all tags, then model their reflection pattern within the equivalent CSI for primary decoding.
-	We characterize the achievable primary-(sum-)backscatter rate region through a joint optimization of transmit beamforming vector at the AP, input probability distribution at the tags, and energy detection regions at the user.
-	A suboptimal solution is provided by the Block Coordinate Descent (BCD) method, where the beamforming, input distribution, and decision thresholds are obtained by Successive Convex Approximation (SCA), Karush–Kuhn–Tucker (KKT), and Dynamic Programming (DP), respectively.
-	Simulation results demonstrate Metascatter can exploit the additional backscatter path to transmit and assist.
-\end{abstract}
-
-\begin{section}{Introduction}
-	\IEEEPARstart{B}{ackscatter} is recently re-innovated as a promising approach to support low-power communications and control wireless propagation environments.
-	The concept of \gls{ambc} was first proposed in \cite{Liu2013b}, where each tag harvests energy from and modulates information over ambient \gls{rf} signals by periodically switching between different reflection patterns.
-	It enables battery-free communication between fully passive nodes, but the backscatter signal strength can be relatively weak and the decoding is subject to strong direct-link interference.
-	To solve this, \cite{Yang2018d} exploited the repeating structure of \gls{ofdm} symbol for interference cancellation based on backscatter channel strength.
-	Cooperative primary-backscatter decoding using co-located receiver, known as cooperative \gls{ambc}, was proposed in \cite{Yang2018}.
-	The authors evaluated the error performance of \gls{ml}, linear, and \gls{sic} detectors for flat fading channels, and proposed a low-complexity \gls{ml} detector for frequency-selective fading channels with ambient \gls{ofdm} carrier.
-	When transmit cooperation is also available, cooperative \gls{ambc} is more commonly known as \gls{sr} \cite{Liang2020}.
-	The authors of \cite{Guo2019b} classified \gls{sr} into commensal, parasitic, and competitive modes based on the relative link priority, then derived their instantaneous achievable rate and optimal power allocation.
-	The outage probability for those modes was later studied in \cite{Ding2020}.
-	On the other hand, it was concluded in \cite{Long2020a} that if the backscatter symbol period is much longer than the primary symbol period, then the non-coherent achievable rate of primary decoding would approach that of the coherent case.
-	The authors also considered the transmit precoder design for weighted sum-rate maximization and transmit power minimization problems.
-	\cite{Zhou2019a} explored how the number of transmit antennas, receive antennas, and symbol period ratio asymptotically influence the ergodic rate of primary and backscatter links.
-	With multi-antenna at all ends, \cite{Wu2021a} optimized the transmit precoder to maximize the backscatter achievable rate under primary rate constraint.
-	However, those paper only considered single tag scenario and the optimal tag multiple access scheme remains unknown.
-	\cite{Xu2021a} proposed a \gls{noma}-based \gls{sr} and studied the receive combiner design when the receiver decodes in the order of equivalent channel strength.
-	A \gls{tdma}-based \gls{sr} with energy harvesting constraints was also presented in \cite{Yang2021a}, and energy efficiency maximization was considered with respect to transmit power, reflection efficiency, and time allocation design.
-	In \cite{Han2021}, random code-assisted backscatter multiple access was combined with \gls{sr}, and the authors evaluated the asymptotic \gls{sinr} performance using random matrix theory.
-
-	On the other hand, \gls{irs} has recently emerged as a promising technique to enhance the energy efficiency.
-	In practice, an \gls{irs} consists of multiple individual sub-wavelength reflecting elements to adjust the amplitude and phase of the incoming signal (i.e., passive beamforming).
-	Different from relay, backscatter and frequency-selective surface \cite{Anwar2018}, \gls{irs} assists the primary transmission using passive components with much lower energy consumption and thermal noise, but is limited to frequency-dependent reflection.
-	\cite{Wu2018} proposed an \gls{irs}-assisted \gls{miso} system and jointly optimized the precoder and the phase shifts to minimize the transmit power.
-	The active and passive beamforming problem was then extended to the discrete phase shift case \cite{Wu2019a} and the multi-user case \cite{Wu2019}.
-	In \cite{Abeywickrama2020}, the authors investigated the impact of non-zero resistance on the reflection pattern and emphasized the coupling between reflection amplitude and phase shift in practice.
-	To estimate the cascaded link without \gls{rf}-chains at the \gls{irs}, practical protocols were developed based on element-wise on/off switching \cite{Nadeem2019}, training sequence and reflection pattern design \cite{You2019,Kang2020}, and compressed sensing \cite{Wang2020}.
-	\gls{irs} was also added to single-tag and multi-tag \gls{sr} systems to improve backscatter efficiency \cite{Chen2021,Zhang2021d}.
-	Recently, the idea of \gls{irs}-empowered \gls{sr} was proposed in \cite{Xu2020b,Hua2022}, where the reflection pattern can be decoupled as the multiplication of whole phase shift matrix and one backscatter symbol.
-	The idea was combined with spatial modulation to divide the \gls{irs} into reflection and information and elements, and the error performance of non-coherent backscatter detection was studied accordingly \cite{Hu2021a}.
-
-	To the best of our knowledge, most existing \gls{sr} systems \cite{Yang2018,Guo2019b,Ding2020,Long2020a,Zhou2019a,Wu2021a,Xu2021a} assumed Gaussian codebook at the tags and employed \gls{sic} from primary to backscatter link.
-	It thus requires non-coherent primary encoding at the transmitter and involves re-encoding, precoding, and subtraction operations that may not be available to legacy receivers.
-	Besides, the primary and backscatter symbols in \gls{sr} are mixed by multiplication coding instead of superposition coding, and the backscatter symbol period can be much longer than the primary symbol period due to physical constraints.
-	Inspired by above, we propose a novel Metascatter network where multiple battery-free tags ride over a conventional point-to-point system and adapt their input probability distribution to simultaneously act as backscatter tags of \gls{sr} and reflecting elements of \gls{irs}.
-	To fully utilize the reflection pattern and signal structure, we also present a novel decoding strategy with minor modifications on existing receivers.
-	The contributions of this paper is summarized as follows.
-
-	\emph{First,} Metascatter adapts the input probability distribution of a finite-state backscatter device based on the primary and backscatter \gls{csi}.
-	It generalizes the backscatter tags of \gls{sr} and reflecting elements of \gls{irs} to improve the primary-backscatter tradeoff in a flexible manner.
-	When the primary link is absolutely prioritized, the tag input probability boils down to \num{1} at the state that maximizes the equivalent channel strength and \num{0} at other states, which is essentially the phase shift selection of an \gls{irs} element.
-	When we only care about the backscatter performance, the network boils down to a multi-tag \gls{ambc} and the input design can be simplified accordingly.
-
-	\emph{Second,} we propose a novel receiving strategy where the backscatter symbol of all tags are first recovered by energy-based decoding, then modeled within equivalent \gls{csi} for primary decoding.
-	When the ratio of backscatter symbol period over primary symbol period is large enough, the randomness of primary source can be averaged out and the performance of non-coherent backscatter decoding can be greatly improved.
-	Since the primary and backscatter symbols are mixed by multiplication coding, the backscatter decoding can be viewed as part of primary channel training, which avoids non-coherent encoding at the transmitter and \gls{sic} at the receiver.
-
-	\emph{Third,} we characterize the achievable primary-(sum-)backscatter rate region by iteratively optimizing the tag input distribution, the backscatter decision threshold, and the transmit precoder.
-	For the input design, we propose a numerical method to evaluate the \gls{kkt} solutions by limits of sequences.
-	For the threshold design, we derive the minimum number of decision thresholds to maximize the total backscatter rate, and obtain the optimal thresholds by \gls{dp} accelerated by \gls{smawk} algorithm.
-	However, the optimal precoder design can be non-trivial and we may end up with a low-complexity suboptimal solution.
-
-\end{section}
-
-\begin{section}{Backscatter Principles}
-	% \begin{figure}[!t]
-	% 	\centering
-	% 	\resizebox{0.6\columnwidth}{!}{
-	% 		\begin{circuitikz}[transform shape]
-	% 			\coordinate (O) at (0,0);
-	% 			\node[block,from={O to $(O) + (6.375,3.25)$}](T){};
-	% 			\draw (0,1.75)
-	% 			to[short] ++(-0.875,0)
-	% 			to[short] ++(0,0.5) node[bareantenna](A){Bx};
-	% 			\draw (0,1.75)
-	% 			to[short,-*] ++(0.25,0) coordinate(J);
-	% 			\draw (J)
-	% 			to[short] ++(0,1)
-	% 			to[short] ++(0.5,0) coordinate(J1);
-	% 			\node[block,from={$(J1) + (0,-0.25)$ to $(J1) + (2.5,0.25)$}](R){Rectifier};
-	% 			\draw (J)
-	% 			to[short] ++(0.5,0) coordinate(J2);
-	% 			\node[block,from={$(J2) + (0,-0.25)$ to $(J2) + (2.5,0.25)$}](D){Demodulator};
-	% 			\draw (J)
-	% 			to[short] ++(0,-1)
-	% 			to[short] ++(0.5,0) coordinate(J3)
-	% 			to [vR,mirror,invert,/tikz/circuitikz/bipoles/length=1cm] ++(1.75,0) node[ground,rotate=90]{};
-	% 			\node[block,from={$(J3) + (0,-0.25)$ to $(J3) + (2.5,0.25)$},draw=none](M){};
-	% 			\draw ($(J3) + (0,-0.25)$) rectangle ($(J3) + (2.5,0.25)$);
-	% 			\draw ($(J3) + (1.25,-0.5)$) node[]{Modulator};
-	% 			\draw[dashed,-{Latex[length=2mm]}] (R.east) -- ++(0.75,0);
-	% 			\draw[-{Latex[length=2mm]}] (D.east) -- ++(0.75,0);
-	% 			\draw[{Latex[length=2mm]}-] (M.east) -- ++(0.75,0);
-	% 			\node[block,from={$(R.east) + (0.75,-0.25)$ to $(R.east) + (2.875,0.25)$}](P){Power buffer};
-	% 			\node[block,from={$(M.east) + (0.75,-0.25)$ to $(D.east) + (2.875,0.25)$}](S){Digital\\section};
-	% 			\draw[dashed,-{Latex[length=2mm]}] (P.south) to (S.north);
-	% 			\coordinate (F1) at ($(P.south)!0.5!(S.north)$);
-	% 			\coordinate (F2) at ($(D.east)!0.5!(S.west)$);
-	% 			\coordinate (F3) at ($(D.south)!0.5!(M.north)$);
-	% 			\draw[dashed] (F1) to (F1-|D.north);
-	% 			\draw[dashed,-{Latex[length=2mm]}] (F1-|D.north) to (D.north);
-	% 			\draw[dashed] (F1-|F2) to (F2|-F3) to (M|-F3);
-	% 			\draw[dashed,-{Latex[length=2mm]}] (M|-F3) to (M.north);
-	% 		\end{circuitikz}
-	% 	}
-	% 	\caption{The block diagram and equivalent circuit of a passive tag. The solid and dashed vectors represent signal and energy flows.}
-	% 	\label{fi:tag_block_diagram}
-	% \end{figure}
-
-	\begin{figure}[!t]
-		\centering
-		\subfloat[Block diagram]{
-			\resizebox{0.6\columnwidth}{!}{
-				\begin{circuitikz}[transform shape]
-					\coordinate (O) at (0,0);
-					\node[block,from={O to $(O) + (6.375,3.25)$}](T){};
-					\draw (0,1.75)
-					to[short] ++(-0.875,0)
-					to[short] ++(0,0.5) node[bareantenna](A){Bx};
-					\draw (0,1.75)
-					to[short,-*] ++(0.25,0) coordinate(J);
-					\draw (J)
-					to[short] ++(0,1)
-					to[short] ++(0.5,0) coordinate(J1);
-					\node[block,from={$(J1) + (0,-0.25)$ to $(J1) + (2.5,0.25)$}](R){Rectifier};
-					\draw (J)
-					to[short] ++(0.5,0) coordinate(J2);
-					\node[block,from={$(J2) + (0,-0.25)$ to $(J2) + (2.5,0.25)$}](D){Demodulator};
-					\draw (J)
-					to[short] ++(0,-1)
-					to[short] ++(0.5,0) coordinate(J3)
-					to [vR,mirror,invert,/tikz/circuitikz/bipoles/length=1cm] ++(1.75,0) node[ground,rotate=90]{};
-					\node[block,from={$(J3) + (0,-0.25)$ to $(J3) + (2.5,0.25)$},draw=none](M){};
-					\draw ($(J3) + (0,-0.25)$) rectangle ($(J3) + (2.5,0.25)$);
-					\draw ($(J3) + (1.25,-0.5)$) node[]{Modulator};
-					\draw[dashed,-{Latex[length=2mm]}] (R.east) -- ++(0.75,0);
-					\draw[-{Latex[length=2mm]}] (D.east) -- ++(0.75,0);
-					\draw[{Latex[length=2mm]}-] (M.east) -- ++(0.75,0);
-					\node[block,from={$(R.east) + (0.75,-0.25)$ to $(R.east) + (2.875,0.25)$}](P){Power buffer};
-					\node[block,from={$(M.east) + (0.75,-0.25)$ to $(D.east) + (2.875,0.25)$}](S){Digital\\section};
-					\draw[dashed,-{Latex[length=2mm]}] (P.south) to (S.north);
-					\coordinate (F1) at ($(P.south)!0.5!(S.north)$);
-					\coordinate (F2) at ($(D.east)!0.5!(S.west)$);
-					\coordinate (F3) at ($(D.south)!0.5!(M.north)$);
-					\draw[dashed] (F1) to (F1-|D.north);
-					\draw[dashed,-{Latex[length=2mm]}] (F1-|D.north) to (D.north);
-					\draw[dashed] (F1-|F2) to (F2|-F3) to (M|-F3);
-					\draw[dashed,-{Latex[length=2mm]}] (M|-F3) to (M.north);
-				\end{circuitikz}
-			}
-			\label{fi:block_diagram}
-		}
-		\setcounter{subfigure}{2}%
-		\subfloat[Scatter model]{
-			\resizebox{0.35\columnwidth}{!}{
-				\begin{circuitikz}[transform shape]
-					\tikzstyle{every node}=[font=\Large]
-					\draw (0,0) node[bareantenna](bareantenna){};
-					\draw (bareantenna.west) ++(-1.5,0) node[waves](WI){};
-					\draw (WI.north east) ++(0.25,0) node[font=\Large]{$\vec{E}_{\mathrm{I}}$};
-					\draw (WI.south east) ++(0.25,0) node[font=\Large]{$\vec{H}_{\mathrm{I}}$};
-					\draw (bareantenna.east) ++(0.875,0) node[waves](WR){};
-					\draw (WR.north east) ++(0.35,0) node[font=\Large]{$\vec{E}_m$};
-					\draw (WR.south east) ++(0.35,0) node[font=\Large]{$\vec{H}_m$};
-					\draw (bareantenna)
-					to [R=$Z_{\mathrm{A}}$] ++(0,-1.5) node[rotary switch=4 in 90 wiper 30,anchor=ext center,rotate=270](SW){};
-					\draw (SW.cout 2) node[below=0.1cm,font=\Large]{$m$}
-					to [R=$Z_m$] ++(2,0) node[ground]{};
-				\end{circuitikz}
-			}
-			\label{fi:scatter_model}
-		}
-		\setcounter{subfigure}{1}
-		\subfloat[Equivalent circuit]{
-			\resizebox{0.9\columnwidth}{!}{
 \begin{circuitikz}[transform shape]
@@
 	\draw [yellow] (6.5,4.25) node[]{Modulator};
-					\draw [red] (11.5,4.25) node[]{Harvester + Chip};
+	\draw [red] (11.5,4.25) node[]{Harvester \& Chip};
 
@@
 \end{circuitikz}
-			}
-			\label{fi:equivalent_circuit}
-		}
-		\caption{Block diagram, equivalent circuit, and scatter model of a typical passive tag.
-The solid and dashed vectors represent signal and energy flows.
-The backscatter antenna behaves as a constant power source, where the voltage $V_0$ and current $I_0$ are introduced by incident electric field $\vec{E}_{\mathrm{I}}$ and magnetic field $\vec{H}_{\mathrm{I}}$ \cite{Huang2021}.}
-	\end{figure}
-	% In a bistatic backscatter system,
-	% Consider a bistatic backscatter system with an excitation source, multiple passive tags, and a backscatter reader.
-	Passive backscatter devices (a.k.a., tags) harvest energy from and modulate information over surrounding \gls{rf} signal.
-	As shown in Fig.
-\subref*{fi:block_diagram}, a typical passive tag consists of a scattering antenna, an energy harvester, an integrated receiver, a load-switching modulator, and on-chip components (e.g., micro-controller and sensors) \cite{Dobkin2012}.
-Its equivalent circuit is also given by Fig.
-\subref*{fi:equivalent_circuit}.
-	When illuminated, the tag absorbs a portion of the impinging wave and scatters the rest back to the space.
-	The absorbed signal can be used for source decoding and energy harvesting \cite{Kim2021a}, while the scattered signal can be decomposed into the \emph{structural} and \emph{antenna} mode components \cite{Hansen1989}.
-	The structural mode scattering applies to general objects and is related to the antenna structure, shape and material, which contributes to environment multipath and can be covered by channel estimation \cite{Boyer2014}.
-	On the other hand, the antenna mode scattering models the antenna radiation and depends on the antenna-load impedance mismatch, which can be used for backscatter modulation \cite{Boyer2012} or channel reconfiguration \cite{Wu2021b}.
-	Fig. \subref*{fi:scatter_model} illustrates the scatter model.
-	For a tag with $M$ candidate states, the reflection coefficient of state $m \in \mathcal{M} \triangleq \{1,\ldots,M\}$ is defined as
-	\begin{footnote}
-		It corresponds to a linear backscatter model where the reflection coefficient is irrelevant to incident electromagnetic field strength.
-	\end{footnote}
-	\begin{equation}
-		\Gamma_m = \frac{Z_m - Z_{\mathrm{A}}^*}{Z_m + Z_{\mathrm{A}}},
-		\label{eq:reflection_coefficient}
-	\end{equation}
-	where $Z_m$ is the load impedance at state $m$ and $Z_{\mathrm{A}}$ is the antenna input impedance.
-
-	\begin{subsection}{Backscatter Modulation}
-		In backscatter modulation, the tag \emph{periodically varies} the reflection coefficient to embed its own information.
-		As such, there exists a mapping from the alphabet to the set.
-		When the \gls{csi} and reflection alphabet $\{\Gamma_1,\ldots,\Gamma_M\}$ are available at the reader, it can decode the tag message from the observed scattered signal.
-
-		For $M$-ary \gls{qam}, the complex constellation point $c_m$ maps to the corresponding reflection coefficient by \cite{Thomas2012a}
-		\begin{equation}
-			\Gamma_m = \alpha \frac{c_m}{\max_{m'} \lvert c_{m'} \rvert},
-			\label{eq:backscatter_modulation}
-		\end{equation}
-		where $\alpha \in [0,1]$ models the amplitude scatter ratio at the direction of interest.
-
-		% When the \gls{csi} and reflection alphabet $\{\Gamma_1,\ldots,\Gamma_M\}$ are available at the reader, the tag can be successfully decoded based on the received signal.
-
-	\end{subsection}
-
-	\begin{subsection}{Channel Reconfiguration}
-		2
-	\end{subsection}
-	% Tags periodically switch between different states to perform backscatter modulation.
-	% For $M$-ary \gls{qam}, the complex constellation point $c_m \in \mathcal{C}$ maps to the reflection coefficient by \cite{Thomas2012a}
-	% \begin{equation}
-	% 	\Gamma_m = \alpha \frac{c_m}{\max_{m'} \lvert c_{m'} \rvert},
-	% 	\label{eq:backscatter_modulation}
-	% \end{equation}
-	% where $\alpha \in [0,1]$ models the harvest-backscatter ratio at the direction of interest.
-	For passive tags, $\alpha \ll 1$ is commonly assumed as the majority of the incident wave can be harvested to support tag modules \cite{Thomas2012a}.
-
-	\begin{remark}
-		By choosing proper load impedance, it is possible to implement any signal constellation or think beyond modulation.
-		For example, perfect matching enables maximum power transfer to the tag, while perfect mismatch leads to complete reflection as desired by ideal \gls{irs}.
-		It inspires Metascatter to design a smart reflection and unify wireless power transfer, backscatter modulation, and passive beamforming.
-	\end{remark}
-\end{section}
-
-\begin{section}{Metascatter}
-	\begin{subsection}{System Model}
-		\begin{figure}[!t]
-			\centering
-			\def\svgwidth{0.9\columnwidth}
-			\import{assets/}{metascatter_system.eps_tex}
-			\caption{The proposed Metascatter system.}
-			\label{fi:metascatter_system}
-		\end{figure}
-		As shown in Fig.
-\ref{fi:metascatter_system}, we propose a single-\gls{ue} multi-\gls{tg} symbiotic radio network where the \gls{rf} signal generated by the $Q$-antenna \gls{ap} is shared by two coexisting systems.
-		In the primary point-to-point system, the \gls{ap} transmits information to the single-antenna user.
-		In the secondary backscatter system, the \gls{ap} acts as the carrier emitter, the $K$ nearby single-antenna tags modulate their information over the reradiated \gls{rf} signals, and the user receives and decodes the backscatter messages.
-		Denote the \gls{ap}-\gls{ue} direct channel as $\boldsymbol{h}_{\mathrm{D}}^H \in \mathbb{C}^{1 \times Q}$, the \gls{ap}-\gls{tg} $k \in \mathcal{K} \triangleq \{1,\ldots,K\}$ forward channel as $\boldsymbol{h}_{\mathrm{F},k}^H \in \mathbb{C}^{1 \times Q}$, the \gls{tg} $k$-\gls{ue} backward channel as $h_{\mathrm{B},k}$, and define the cascaded channel of tag $k$ as $\boldsymbol{h}_{\mathrm{C},k}^H \triangleq h_{\mathrm{B},k} \boldsymbol{h}_{\mathrm{F},k}^H \in \mathbb{C}^{1 \times Q}$.
-		For simplicity, we consider a quasi-static block fading model where the channel response remain constant within each coherence interval and vary independently between consecutive blocks.
-		% Since backscatter modulation involves load switching, tags typically transmit at much lower rate, and we assume the backscatter symbol period is $N \in \mathbb{Z}_{++}$ times the primary symbol period.
-		Since backscatter modulation involves load switching, tags typically transmit at much lower rate, and we assume the backscatter symbol length is $N \in \mathbb{Z}_{++}$ times the primary symbol length.
-		We also assume the direct channel and all cascaded channels can be estimated and fed back to the \gls{ap}.
-		\begin{footnote}
-			Due to the lack of \gls{rf} chains at the passive tag, accurate and efficient \gls{csi} acquisition at the \gls{ap} can be challenging.
-			One possible approach is that the \gls{ap} sends pre-defined pilots, the tags respond in well-designed manners, and the user performs least-square estimation with feedbacks \cite{Bharadia2015,Yang2015b,Guo2019g}.
-		\end{footnote}
-
-		Consider the signal model during one backscatter symbol period.
-		We assume the primary symbol follows standard \gls{cscg} distribution and the backscatter symbol of all tags employs $M$-\gls{qam}.
-		Under perfect synchronization, the signal received by the user at primary symbol block $n \in \mathcal{N} \triangleq \{1,\ldots,N\}$ is
-		\begin{footnote}
-			We omit the signal reflected by two or more times\cite{Wu2019} and assume the time difference of arrival from different paths are negligible\cite{Guo2019b}.
-		\end{footnote}
-		\begin{equation}
-			y[n] = \left(\boldsymbol{h}_{\mathrm{D}}^H + \sum_{k \in \mathcal{K}} \sqrt{\alpha_k} \boldsymbol{h}_{\mathrm{C},k}^H x_k\right) \boldsymbol{w} s[n] + w[n],
-			\label{eq:received_signal}
-		\end{equation}
-		where $\alpha_k$ and $x_k$ denote respectively the harvest-backscatter efficiency and backscatter symbol of tag $k$, $s[n]$ and $w[n] \sim \mathcal{CN}(0,\sigma_w^2)$ denote respectively the primary symbol and \gls{awgn} at block $n$, and $\boldsymbol{w} \in \mathbb{C}^{Q \times 1}$ is the transmit precoder satisfying power constraint $\lVert \boldsymbol{w} \rVert^2 \le P$.
-		For the ease of notation, we define $x_{\mathcal{K}} \triangleq \{x_k : k \in \mathcal{K}\}$ as the tag input combination, and $\boldsymbol{y} \triangleq \left[y[1],\ldots,y[N]\right]^T \in \mathbb{C}^{N \times 1}$ as the received signal per backscatter symbol period.
-		For primary transmission, the equivalent channel is subject to backscatter modulation uncertainty as
-		\begin{equation}
-			\boldsymbol{h}_{\mathrm{E}}^H(x_{\mathcal{K}}) \triangleq \boldsymbol{h}_{\mathrm{D}}^H + \sum_{k \in \mathcal{K}} \sqrt{\alpha_k} \boldsymbol{h}_{\mathrm{C},k}^H x_k.
-			\label{eq:equivalent_channel}
-		\end{equation}
-
-		\begin{remark}
-			Metascatter involves an unconventional \gls{mac} where the primary and backscatter symbols of different duration are mixed by \gls{mc} instead of \gls{sc}.
-			For each tag, the reflection coefficient not only encodes the backscatter message but also influences the equivalent primary channel \eqref{eq:equivalent_channel}.
-			As such, novel receiving strategy other than \gls{sic} should be tailored to signal characteristics to unveil how reflection pattern potentially influences the primary-backscatter tradeoff.
-		\end{remark}
-	\end{subsection}
-
-	\begin{subsection}{Receiving Strategy}
-		We propose a novel receiving strategy where the backscatter symbol of all tags are first jointly identified by non-coherent energy detection, then modeled within equivalent channel \eqref{eq:equivalent_channel} as if passive beamforming.
-		Compared with conventional schemes as joint decoding and \gls{sic}, the Metascatter receiver may not achieve as high data rate for one tag, but it avoids non-coherent primary encoding and enables tag multiple access in a practical and low-complexity manner.
-		Therefore, we believe it can be compatible to and readily implemented over legacy point-to-point systems.
-
-		Define $m_k \in \mathcal{M}$ as the modulation index of tag $k$, and $m_{\mathcal{K}} \triangleq \{m_k: k \in \mathcal{K}\}$ as the modulation index combination of all tags.
-		Recall that $x_k$ and $x_{\mathcal{K}}$ are random variables representing the backscatter symbol of tag $k$ and the symbol combination of all tags, respectively.
-		Their instances are denoted by modulation index (combination) as $x_{m_k}$ and $x_{m_\mathcal{K}}$.
-		Since any backscatter combination $x_{m_\mathcal{K}}$ remains unchanged over $N$ primary symbol duration, the received signal at symbol block $n$ is only subject to the variation of $s[n]$ and $w[n]$, and follows zero-mean \gls{cscg} distribution with variance
-		\begin{equation}
-			\sigma_{m_{\mathcal{K}}}^2 = \Bigl\lvert \underbrace{\bigl(\boldsymbol{h}_{\mathrm{D}}^H + \sum_{k \in \mathcal{K}} \sqrt{\alpha_k} \boldsymbol{h}_{\mathrm{C},k}^H x_{m_k}\bigr)}_{\boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}})} \boldsymbol{w} \Bigr\rvert^2 + \sigma_w^2.
-			\label{eq:receive_variance}
-		\end{equation}
-
-		Besides, we denote the total received energy as $z \triangleq \lVert \boldsymbol{y} \rVert^2$ and the hypothesis of modulation index combination $m_{\mathcal{K}}$ as $\mathcal{H}_{m_{\mathcal{K}}}$.
-		Since $z$ is the sum of $N$ \gls{iid} exponential variables, its conditional \gls{pdf} under $\mathcal{H}_{m_{\mathcal{K}}}$ follows Erlang distribution with shape $N$ and scale $\sigma_{m_{\mathcal{K}}}^2$ as
-		\begin{equation}
-			f(z \mid \mathcal{H}_{m_{\mathcal{K}}}) = \frac{z^{N-1} e^{-z/\sigma_{m_{\mathcal{K}}}^2}}{\sigma_{m_{\mathcal{K}}}^{2N} (N-1)!}.
-			\label{eq:energy_distribution}
-		\end{equation}
-
-		Energy-based backscatter detection essentially formulates a discrete-input continuous-output memoryless \gls{mac}.
-		To further reduce decoding complexity, we divide the continuous output $z$ into disjoint decision regions to construct a \gls{dmtmac}, where the transition probability from tag input combination $x_{m_{\mathcal{K}}}$ to detector output combination $\hat{x}_{m_{\mathcal{K}}'}$ is
-		\begin{equation}
-			P(\hat{x}_{m_{\mathcal{K}}'} \mid x_{m_{\mathcal{K}}}) = \int_{\mathcal{R}_{m_{\mathcal{K}}'}} f(z \mid \mathcal{H}_{m_{\mathcal{K}}}) \dd z,
-			\label{eq:dmtmac}
-		\end{equation}
-		where $\mathcal{R}_{m_{\mathcal{K}}'}$ is the decision region over $z$ for hypothesis $\mathcal{H}_{m_{\mathcal{K}}'}$.
-	\end{subsection}
-
-	\begin{subsection}{Achievable Rates}
-		Denote the input probability distribution vector of tag $k$ as $\boldsymbol{p}_k \triangleq [P_k(x_1),\ldots,P_k(x_M)]^T \in \mathbb{R}^{M \times 1}$, where $P_k(x_{m_k})$ is the probability at state $m_k$.
-		Consider independent encoding at all tags such that the probability of input combination $x_{m_{\mathcal{K}}}$ is $P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) = \prod_{k \in \mathcal{K}} P_k(x_{m_k})$.
-		The backscatter information function of input combination $x_{m_{\mathcal{K}}}$ is defined as
-		\begin{equation}
-			I_{\mathrm{B}}(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}}) \triangleq \sum_{m_{\mathcal{K}}'} P(\hat{x}_{m_{\mathcal{K}}'} \mid x_{m_{\mathcal{K}}}) \log \frac{P(\hat{x}_{m_{\mathcal{K}}'} \mid x_{m_{\mathcal{K}}})}{P(\hat{x}_{m_{\mathcal{K}}'})},
-			\label{eq:backscatter_information_function}
-		\end{equation}
-		where $P(\hat{x}_{m_{\mathcal{K}}'}) = \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) P(\hat{x}_{m_{\mathcal{K}}'} \mid x_{m_{\mathcal{K}}})$.
-		Besides, the backscatter marginal information function associated with letter $x_{m_k}$ of tag $k$ is
-		\begin{equation}
-			I_{\mathrm{B},k}(x_{m_k};\hat{x}_{\mathcal{K}}) \triangleq \sum_{m_{\mathcal{K} \setminus \{k\}}} P_{\mathcal{K} \setminus \{k\}}(x_{m_{\mathcal{K} \setminus \{k\}}}) I_{\mathrm{B}}(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}}),
-			\label{eq:backscatter_marginal_information_function}
-		\end{equation}
-		where $P_{\mathcal{K} \setminus \{k\}}(x_{m_{\mathcal{K} \setminus \{k\}}}) = \prod_{q \in \mathcal{K} \setminus \{k\}} P_{q}(x_{m_{q}})$.
-		Therefore, the backscatter mutual information is
-		\begin{equation}
-			I_{\mathrm{B}}(x_{\mathcal{K}};\hat{x}_{\mathcal{K}}) = \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) \sum_{m_{\mathcal{K}}'} P(\hat{x}_{m_{\mathcal{K}}'} \mid x_{m_{\mathcal{K}}}) \log \frac{P(\hat{x}_{m_{\mathcal{K}}'} \mid x_{m_{\mathcal{K}}})}{P(\hat{x}_{m_{\mathcal{K}}'})}.
-			\label{eq:backscatter_mutual_information}
-		\end{equation}
-
-		Once the tag input combination is successfully decoded, the backscatter uncertainty can be eliminated and the equivalent channel for primary transmission can be updated by \eqref{eq:equivalent_channel}.
-		Similar to above, the primary information function of input combination $x_{m_{\mathcal{K}}}$ is
-		% TODO notation
-		\begin{equation}
-			I_{\mathrm{P}}(x_{m_{\mathcal{K}}};\boldsymbol{y}) \triangleq N \log_2 \left(1 + \frac{\lvert \boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_w^2}\right),
-			\label{eq:primary_information_function}
-		\end{equation}
-		the primary marginal information function associated with letter $x_{m_k}$ of tag $k$ is
-		\begin{equation}
-			I_{\mathrm{P},k}(x_{m_k};\boldsymbol{y}) \triangleq \sum_{m_{\mathcal{K} \setminus \{k\}}} P_{\mathcal{K} \setminus \{k\}}(x_{m_{\mathcal{K} \setminus \{k\}}}) I_{\mathrm{P}}(x_{m_{\mathcal{K}}};\boldsymbol{y}),
-			\label{eq:primary_marginal_information_function}
-		\end{equation}
-		and the primary (ergodic) mutual information is
-		\begin{equation}
-			I_{\mathrm{P}}(x_{\mathcal{K}};\boldsymbol{y}) = \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) N \log_2 \left(1 + \frac{\lvert \boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_w^2}\right).
-			\label{eq:primary_mutual_information}
-		\end{equation}
-
-		Therefore, the weighted sum information function, marginal information function, and mutual information of primary and backscatter links are respectively given by
-		\begin{align}
-			I(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}},\boldsymbol{y})
-			 & \triangleq \rho I_{\mathrm{P}}(x_{m_{\mathcal{K}}};\boldsymbol{y}) + (1 - \rho) I_{\mathrm{B}}(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}}),\label{eq:weighted_sum_information_function} \\
-			I_k(x_{m_k};\hat{x}_{\mathcal{K}},\boldsymbol{y})
-			 & \triangleq \rho I_{\mathrm{P},k}(x_{m_k};\boldsymbol{y}) + (1 - \rho) I_{\mathrm{B},k}(x_{m_k};\hat{x}_{\mathcal{K}}),\label{eq:weighted_sum_marginal_information}                     \\
-			I(x_{\mathcal{K}};\hat{x}_{\mathcal{K}},\boldsymbol{y})
-			 & \triangleq \rho I_{\mathrm{P}}(x_{\mathcal{K}};\boldsymbol{y}) + (1 - \rho) I_{\mathrm{B}}(x_{\mathcal{K}};\hat{x}_{\mathcal{K}}),\label{eq:weighted_sum_mutual_information}
-		\end{align}
-		where $\rho \in [0,1]$ represents the priority of the primary link.
-	\end{subsection}
-\end{section}
-
-\begin{section}{Input, Threshold, and Precoder Design}
-	To characterize the achievable primary-(sum-)backscatter rate region of Metascatter, we aim to maximize the weighted sum mutual information with respect to tag input probability distribution $\{\boldsymbol{p}_k\}$, decision threshold vector $\boldsymbol{t}$, and transmit precoder $\boldsymbol{w}$
-	\begin{maxi!}
-		{\scriptstyle{\{\boldsymbol{p}_k\},\boldsymbol{t},\boldsymbol{w}}}{I(x_{\mathcal{K}};\hat{x}_{\mathcal{K}},\boldsymbol{y})}{\label{op:weighted_sum_rate}}{\label{ob:weighted_sum_rate}}
-		\addConstraint{\sum \nolimits_{m_k} P_k(x_{m_k})}{=1,}{\quad \forall k \in \mathcal{K}}{\label{co:sum_probability}}
-		\addConstraint{P_k(x_{m_k})}{\ge 0,}{\quad \forall k \in \mathcal{K}, \ \forall m_k \in \mathcal{M}}{\label{co:nonnegative_probability}}
-		\addConstraint{\lVert \boldsymbol{w} \rVert^2}{\le P.}{\label{co:transmit_power}}
-	\end{maxi!}
-	Since problem \eqref{op:weighted_sum_rate} is not jointly convex, we propose a \gls{bcd} algorithm that iteratively updates $\{\boldsymbol{p}_k\}$, $\boldsymbol{t}$ and $\boldsymbol{w}$ until convergence.
-
-	\begin{subsection}{Input Probability Distribution}
-		For any fixed decision boundary $\boldsymbol{t}$ and transmit precoder $\boldsymbol{w}$, the equivalent \gls{dmtmac} can be formulated by \eqref{eq:dmtmac} and problem \eqref{op:weighted_sum_rate} boils down to
-		\begin{maxi!}
-			{\scriptstyle{\{\boldsymbol{p}_k\}}}{I(x_{\mathcal{K}};\hat{x}_{\mathcal{K}},\boldsymbol{y})}{\label{op:input_probability_distribution}}{}
-			\addConstraint{\eqref{co:sum_probability},\eqref{co:nonnegative_probability},}
-		\end{maxi!}
-		which involves the product term $\prod_{k \in \mathcal{K}} P_k(x_{m_k})$ and is non-convex when $K > 1$.
-		Interestingly, the sum-rate optimal input design for general discrete memoryless \gls{mac} remains an open problem, and we instead propose a \gls{kkt} solution to problem \eqref{op:input_probability_distribution}.
-		\begin{footnote}
-			As pointed out in \cite{Buhler2011}, \gls{kkt} conditions are only necessary for sum-rate optimality and these solutions may end up being saddle points.
-		\end{footnote}
-		\begin{proposition}
-			The \gls{kkt} optimality conditions for problem \eqref{op:input_probability_distribution} are equivalent to, $\forall k \in \mathcal{K}$ and $\forall m_k \in \mathcal{M}$,
-			\begin{subequations}
-				\label{eq:input_kkt_condition}
-				\begin{alignat}{2}
-					I_k^\star(x_{m_k};\hat{x}_{\mathcal{K}},\boldsymbol{y}) & = I^\star(x_{\mathcal{K}};\hat{x}_{\mathcal{K}},\boldsymbol{y}), \quad   &  & P_k^\star(x_{m_k}) > 0,\label{eq:probable_states} \\
-					I_k^\star(x_{m_k};\hat{x}_{\mathcal{K}},\boldsymbol{y}) & \le I^\star(x_{\mathcal{K}};\hat{x}_{\mathcal{K}},\boldsymbol{y}), \quad &  & P_k^\star(x_{m_k}) = 0.\label{eq:dropped_states}
-				\end{alignat}
-			\end{subequations}
-			\label{pr:input_kkt_condition}
-		\end{proposition}
-
-		\begin{proof}
-			Please refer to Appendix \ref{ap:input_kkt_condition}.
-			\label{pf:input_kkt_condition}
-		\end{proof}
-
-		We notice \eqref{eq:probable_states} means each probable state of each tag should produce the same marginal information (averaged over all states of other tags), while \eqref{eq:dropped_states} implies any state of any tag with potentially less marginal information than above should not be used.
-		Next, we generalize the Blahut-Arimoto algorithm \cite{Arimoto1972,Blahut1972a} and propose a numerical evaluation of \gls{kkt} points by limits of sequences.
-
-		\begin{proposition}
-			The \gls{kkt} solution of input probability of tag $k$ at state $m_k$ is given by the converging point of the sequence
-			\begin{equation}
-				P_k^{(r+1)}(x_{m_k}) = \frac{P_k^{(r)}(x_{m_k}) \exp \left( \frac{\rho}{1 - \rho} I_k^{(r)}(x_{m_k};\hat{x}_{\mathcal{K}},\boldsymbol{y}) \right)}{\sum_{m_k'} P_k^{(r)}(x_{m_k'}) \exp \left( \frac{\rho}{1 - \rho} I_k^{(r)}(x_{m_k'};\hat{x}_{\mathcal{K}},\boldsymbol{y}) \right)},
-				\label{eq:input_kkt_solution}
-			\end{equation}
-			where $r$ is the iteration index and $\boldsymbol{p}_k^{(0)} > \boldsymbol{0}$, $\forall k \in \mathcal{K}$.
-			At each iteration, the input distribution of tag $k$ is evaluated based on the updated input distribution of tags $1$ to $k-1$.
-			\label{pr:input_kkt_solution}
-		\end{proposition}
-		\begin{proof}
-			Please refer to Appendix \ref{ap:input_kkt_solution}.
-			\label{pf:input_kkt_solution}
-		\end{proof}
-	\end{subsection}
-
-	\begin{subsection}{Decision Threshold}
-		For a given tag input distribution $\{\boldsymbol{p}_k\}$, we can formulate an equivalent information source with augmented alphabet of tag input combination.
-		This equivalent source transmits at the total backscatter rate, and the input distribution is given by $P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) = \prod_{k \in \mathcal{K}} P_k(x_{m_k})$, $\forall k \in \mathcal{K}$ and $\forall m_k \in \mathcal{M}$.
-
-		\begin{remark}
-			Since the equivalent source transmits at the total backscatter rate, the \gls{dmtmac} \eqref{eq:dmtmac} is essentially a point-to-point \gls{dmtc} and we can simplify the decision threshold design accordingly.
-			\label{re:input_combination}
-		\end{remark}
-
-		Interestingly, the optimal threshold design to maximize the mutual information for a general \gls{dmtc} with a fixed number of output letters remains an open issue.
-		The reason is that each decision region may contain more than one disjoint partitions (i.e., non-convex) and the number of thresholds are unknown.
-		Fortunately, for the proposed energy detection, we proved that the \gls{dmtc} capacity can be achieved using only convex decision regions.
-		This conclusion is summarized below.
-
-		\begin{proposition}
-			For a discrete-input continuous-output channel in Erlang distribution \eqref{eq:energy_distribution}, if the \gls{dmtc} is constructed for detection (i.e., same input/output alphabet) and $L$ input letters are with non-zero probability, then it is possible to achieve the \gls{dmtc} capacity by $L$ non-empty convex decision regions defined by $L+1$ distinct decision thresholds.
-			\label{pr:threshold}
-		\end{proposition}
-
-		\begin{proof}
-			Please refer to Appendix \ref{ap:threshold}.
-			\label{pf:threshold}
-		\end{proof}
-
-		Once the optimal number of decision threshold is determined, we can first discretize the output energy level into numerous bins, then obtain the optimal decision regions that maximizes the total backscatter rate by \gls{dp} accelerated by \gls{smawk} algorithm \cite{He2021}.
-
-		\begin{tcolorbox}
-			We may need to tailor threshold design for Metascatter as threshold design has potential impact on primary achievable rate, as implied by some simulation results.
-		\end{tcolorbox}
-	\end{subsection}
-
-	\begin{subsection}{Precoder}
-		\begin{tcolorbox}
-			The optimal precoder design is highly non-convex that involves integration, entropy term, and variable on exponential.
-			We may propose a suboptimal precoder based on linear combination of equivalent and cascaded channels, or consider single transmit antenna instead.
-		\end{tcolorbox}
-		\begin{align}
-			I(x_i;\hat{x}_j)
-			 & = \sum_{j \in \mathcal{I}} \int_{t_{j-1,j}}^{t_{j,j+1}} \frac{z^{N-1} \exp \left(-\frac{z}{\mathrm{tr}(H_{\mathrm{E},i} W) + \sigma_w^2}\right)}{\left(\mathrm{tr}(H_{\mathrm{E},i} W) + \sigma_w^2\right)^N (N-1)!} \dd z\nonumber                                                                                                                                                                                                                    \\
-			 & \quad \times \log \frac{\int_{t_{j-1,j}}^{t_{j,j+1}} \frac{z^{N-1} \exp \left(-\frac{z}{\mathrm{tr}(H_{\mathrm{E},i} W) + \sigma_w^2}\right)}{\left(\mathrm{tr}(H_{\mathrm{E},i} W) + \sigma_w^2\right)^N (N-1)!} \dd z}{\sum_{i' \in \mathcal{I}} \int_{t_{j-1,j}}^{t_{j,j+1}} \frac{z^{N-1} \exp \left(-\frac{z}{\mathrm{tr}(H_{\mathrm{E},i'} W) + \sigma_w^2}\right)}{\left(\mathrm{tr}(H_{\mathrm{E},i'} W) + \sigma_w^2\right)^N (N-1)!} \dd z},
-		\end{align}
-	\end{subsection}
-\end{section}
-
-\begin{section}{Preliminary Results}
-	\begin{table}[t!]
-		\centering
-		\caption{Parameters in simulation}
-		\begin{tabular}{ll}
-			Transmit antenna $Q$     & 1   \\
-			Tags $K$                 & 2   \\
-			States $M$               & 2   \\
-			Reflect ratio $\alpha$   & 0.5 \\
-			Duration ratio $N$       & 10  \\
-			Noise power $\sigma_w^2$ & 1   \\
-			Discretization bins      & 256
-		\end{tabular}
-		\label{ta:parameters}
-	\end{table}
-	Table \ref{ta:parameters} shows the parameters used in simulation.
-	We assume all links are in standard \gls{cscg} distribution and evaluated the rate regions on two instances.
-	For the input design, ``Cooperation'' assumes full transmit cooperation at all tags (i.e., joint encoding), ``Exhaustion'' runs exhaustive search on all possible input distributions, ``\gls{kkt}'' is proposed \gls{kkt} input design \eqref{eq:input_kkt_solution}, and ``Marginalization'' marginalizes the joint input array by ``Cooperation'' to obtain independent tag input distribution.
-	For the threshold design, ``\gls{smawk}'' refers to the \gls{dp}-based quantization proposed in \cite{He2021}, ``Bisection'' sequentially optimizes each threshold by bisection \cite{Nguyen2020a}, and ``\gls{ml}'' is the \gls{ml} detector that requires no knowledge of input distribution.
-
-	Figs. \ref{fi:rate_region_1} and \ref{fi:rate_region_2} show two typical scenarios where joint encoding can be helpful and unnecessary, respectively.
-	Although the proposed \gls{kkt} input design converges to the optimal solutions in both examples, it may be trapped at saddle points under poor initialization, especially when the number of tags increases.
-
-	We believed threshold design has no impact on the primary achievable rate, because primary decoding acts on $\boldsymbol{y}$ while thresholding acts on $z$.
-	As such, the threshold that maximizes the total backscatter rate should also maximize the weighted sum rate.
-	Interestingly, this may not be the case because the \gls{smawk} and Bisection threshold designs, both maximizing the total backscatter rate, can be outperformed by the \gls{ml} when it comes to weighted sum primary-(sum-)backscatter rate.
-	It may result from a precision issue, but inspires further research on threshold design for Metascatter.
-
-	\begin{figure}[!t]
-		\centering
-		\resizebox{\columnwidth}{!}{
-			\includegraphics{assets/rate_region_1.eps}
-		}
-		\caption{Achievable rate regions by input-threshold design: Case I.}
-		\label{fi:rate_region_1}
-	\end{figure}
-
-	\begin{figure}[!t]
-		\centering
-		\resizebox{\columnwidth}{!}{
-			\includegraphics{assets/rate_region_2.eps}
-		}
-		\caption{Achievable rate regions by input-threshold design: Case II.}
-		\label{fi:rate_region_2}
-	\end{figure}
-\end{section}
-
-\begin{appendix}
-	\begin{subsection}{Proof of Proposition \ref{pr:input_kkt_condition}}
-		Denote the Lagrange multipliers associated with \eqref{co:sum_probability} and \eqref{co:nonnegative_probability} as $\{\nu_k\}_{k \in \mathcal{K}}$ and $\{\lambda_{k,m_k}\}_{k \in \mathcal{K},m_k \in \mathcal{M}}$, respectively.
-		The Lagrangian function of problem \eqref{op:input_probability_distribution} is
-		\begin{align}
-			% L(\{\boldsymbol{p}_k\},\{\nu_k\},\{\lambda_{k,m_k}\})
-			L
-			 & = - I(x_{\mathcal{K}};\hat{x}_{\mathcal{K}},\boldsymbol{y}) + \sum_{k \in \mathcal{K}} \nu_k \left( \sum_{m_k \in \mathcal{M}} P_k(x_{m_k}) - 1 \right)\nonumber \\
-			 & \quad - \sum_{k \in \mathcal{K}} \sum_{m_k \in \mathcal{M}} \lambda_{k,m_k} P_k(x_{m_k}),
-		\end{align}
-		and the \gls{kkt} conditions on the optimal primal and dual variables are, $\forall m_k \in \mathcal{M}$ and $\forall k \in \mathcal{K}$,
-		\begin{subequations}
-			\label{eq:input_kkt_condition_original}
-			\begin{equation}
-				- \nabla_{P_k^\star(x_{m_k})} I^\star(x_{\mathcal{K}};\hat{x}_{\mathcal{K}},\boldsymbol{y}) + \nu_k^\star - \lambda_{k,m_k}^\star = 0,
-			\end{equation}
-			\begin{equation}
-				\lambda_{k,m_k}^\star = 0, \quad P_k^\star(x_{m_k}) > 0,
-			\end{equation}
-			\begin{equation}
-				\lambda_{k,m_k}^\star \ge 0, \quad P_k^\star(x_{m_k}) = 0,
-			\end{equation}
-		\end{subequations}
-		where the directional derivative can be explicitly expressed as
-		\begin{equation}
-			\nabla_{P_k^\star(x_{m_k})} I^\star(x_{\mathcal{K}};\hat{x}_{\mathcal{K}},\boldsymbol{y}) = I_k^\star(x_{m_k};\hat{x}_{\mathcal{K}},\boldsymbol{y}) - (1 - \rho).
-			\label{eq:input_directional_derivative}
-		\end{equation}
-
-		Combining \eqref{eq:input_kkt_condition_original} and \eqref{eq:input_directional_derivative}, we have
-		\begin{subequations}
-			\label{eq:input_kkt_condition_transformed}
-			\begin{alignat}{2}
-				I_k^\star(x_{m_k};\hat{x}_{\mathcal{K}},\boldsymbol{y}) & = \nu_k^\star + (1 - \rho), \quad   &  & P_k^\star(x_{m_k}) > 0,\label{eq:probable_states_marginal} \\
-				I_k^\star(x_{m_k};\hat{x}_{\mathcal{K}},\boldsymbol{y}) & \le \nu_k^\star + (1 - \rho), \quad &  & P_k^\star(x_{m_k}) = 0,\label{eq:dropped_states_marginal}
-			\end{alignat}
-		\end{subequations}
-		which suggests
-		\begin{equation}
-			\sum_{m_k} P_k^\star(x_{m_k}) I_k^\star(x_{m_k};\hat{x}_{\mathcal{K}},\boldsymbol{y}) = \nu_k^\star + (1 - \rho).
-			\label{eq:input_kkt_condition_implied}
-		\end{equation}
-
-		On the other hand, by definition of weighted sum marginal information \eqref{eq:weighted_sum_marginal_information},
-		\begin{equation}
-			\sum_{m_k} P_k^\star(x_{m_k}) I_k^\star(x_{m_k};\hat{x}_{\mathcal{K}},\boldsymbol{y}) = I^\star(x_{\mathcal{K}};\hat{x}_{\mathcal{K}},\boldsymbol{y}),
-			\label{eq:weighted_sum_marginal_information_implied}
-		\end{equation}
-		where the right-hand side is irrelevant to $k$.
-		\eqref{eq:input_kkt_condition_transformed}, \eqref{eq:input_kkt_condition_implied}, and \eqref{eq:weighted_sum_marginal_information_implied} together complete the proof.
-		\qedsymbol
-		\label{ap:input_kkt_condition}
-	\end{subsection}
-
-	\begin{subsection}{Proof of Proposition \ref{pr:input_kkt_solution}}
-		We first prove sequence \eqref{eq:input_kkt_solution} is non-decreasing in mutual information.
-		Let $P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) = \prod_{q \in \mathcal{K}} P_q(x_{m_q})$ and $P_{\mathcal{K}}'(x_{m_{\mathcal{K}}}) = P_k'(x_{m_k}) \prod_{q \in \mathcal{K} \setminus \{k\}} P_q(x_{m_q})$ be two probability distributions with potentially different marginal for tag $k \in \mathcal{K}$ at state $m_k \in \mathcal{M}$, and define an intermediate function $J \left( P_{\mathcal{K}}(x_{m_{\mathcal{K}}}),P_{\mathcal{K}}'(x_{m_{\mathcal{K}}}) \right)$ as \eqref{eq:intermediate_information_function}.
-		\begin{figure*}[!b]
-			\hrule
-			\begin{align}
-				J \left( P_{\mathcal{K}}(x_{m_{\mathcal{K}}}),P_{\mathcal{K}}'(x_{m_{\mathcal{K}}}) \right)
-				 & \triangleq \rho \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) N \log_2 \left(1 + \frac{\lvert \boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_w^2}\right)\nonumber                                                                                                                          \\
-				 & \quad + (1 - \rho) \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) \sum_{m_{\mathcal{K}}'} P(\hat{x}_{m_{\mathcal{K}}'} \mid x_{m_{\mathcal{K}}}) \log \frac{P(\hat{x}_{m_{\mathcal{K}}'} \mid x_{m_{\mathcal{K}}}) P_{\mathcal{K}}'(x_{m_{\mathcal{K}}})}{P'(\hat{x}_{m_{\mathcal{K}}'}) P_{\mathcal{K}}(x_{m_{\mathcal{K}}})}.
-				\label{eq:intermediate_information_function}
-			\end{align}
-		\end{figure*}
-		It is straightforward to verify $J \left( P_{\mathcal{K}}(x_{m_{\mathcal{K}}}),P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) \right) = I(x_{\mathcal{K}};\hat{x}_{\mathcal{K}},\boldsymbol{y})$ and $J \left( P_{\mathcal{K}}(x_{m_{\mathcal{K}}}),P_{\mathcal{K}}'(x_{m_{\mathcal{K}}}) \right)$ is a concave function for a fixed $P_{\mathcal{K}}'(x_{m_{\mathcal{K}}})$.
-		By choosing $\nabla_{P_k^\star(x_{m_k})} J \left( P_{\mathcal{K}}(x_{m_{\mathcal{K}}}),P_{\mathcal{K}}'(x_{m_{\mathcal{K}}}) \right) = 0$, we have
-		\begin{equation}
-			S_k'(x_{m_k}) - S_k'(x_{i_k}) + (1 - \rho) \log \frac{P_k(x_{i_k})}{P_k^\star(x_{m_k})} = 0,
-			\label{eq:optimal_intermediate_information_condition}
-		\end{equation}
-		where $i_k \ne m_k$ is the reference state and
-		\begin{align}
-			S_k'(x_{m_k})
-			 & \triangleq I_k'(x_{m_k};\hat{x}_{\mathcal{K}},\boldsymbol{y}) + (1 - \rho) \sum_{m_{\mathcal{K} \setminus \{k\}}} P_{\mathcal{K} \setminus \{k\}}(x_{m_{\mathcal{K} \setminus \{k\}}})\nonumber \\
-			 & \quad \times \sum_{m_{\mathcal{K}}'} P(\hat{x}_{m_{\mathcal{K}}'} \mid x_{m_{\mathcal{K}}}) \log P_{\mathcal{K}}'(x_{m_{\mathcal{K}}}).
-		\end{align}
-
-		Evidently, $\forall m_k \ne i_k$, \eqref{eq:optimal_intermediate_information_condition} boils down to
-		\begin{equation}
-			P_k^\star(x_{m_k}) = \frac{P_k'(x_{m_k}) \exp \left( \frac{\rho}{1 - \rho} I_k'(x_{m_k};\hat{x}_{\mathcal{K}},\boldsymbol{y}) \right)}{\sum_{m_k'} P_k'(x_{m_k'}) \exp \left( \frac{\rho}{1 - \rho} I_k'(x_{m_k'};\hat{x}_{\mathcal{K}},\boldsymbol{y}) \right)}.
-			\label{eq:optimal_relative_distribution}
-		\end{equation}
-
-		Although it seems $P_k(x_{i_k}) = 1 - \sum_{m_k \ne i_k} P_k^\star(x_{m_k})$ has no optimality guarantee, we can verify that $P_k(x_{i_k})$ has exactly the same form as \eqref{eq:optimal_relative_distribution}.
-		It implies the selection of reference state does not matter and \eqref{eq:optimal_relative_distribution} is indeed optimal $\forall m_k \in \mathcal{M}$.
-		Therefore, for a fixed $P_{\mathcal{K}}'(x_{m_{\mathcal{K}}})$, choosing $P_k(x_{m_k})$ by \eqref{eq:optimal_relative_distribution} ensures
-		\begin{equation}
-			J \left( P_{\mathcal{K}}(x_{m_{\mathcal{K}}}),P_{\mathcal{K}}'(x_{m_{\mathcal{K}}}) \right) \ge I'(x_{\mathcal{K}};\hat{x}_{\mathcal{K}},\boldsymbol{y}).
-			\label{eq:information_difference_lower}
-		\end{equation}
-
-		On the other hand, \eqref{eq:optimal_relative_distribution} also guarantees
-		\begin{subequations}
-			\label{eq:information_difference_upper}
-			\begin{align}
-				\Delta
-				 & \triangleq I(x_{\mathcal{K}};\hat{x}_{\mathcal{K}},\boldsymbol{y}) - J \left( P_{\mathcal{K}}(x_{m_{\mathcal{K}}}),P_{\mathcal{K}}'(x_{m_{\mathcal{K}}}) \right)                                                                                                                               \\
-				 & = (1 - \rho) \sum_{m_k} \frac{P_k'(x_{m_k}) f_k'(x_{m_k};\hat{x}_{\mathcal{K}},\boldsymbol{y})}{\sum_{m_k'} P_k'(x_{m_k'}) f_k'(x_{m_k'};\hat{x}_{\mathcal{K}},\boldsymbol{y})} \sum_{m_{\mathcal{K}}''} P(\hat{x}_{m_{\mathcal{K}}''} \mid x_{m_k})\nonumber                                  \\
-				 & \quad \times \log \frac{\sum_{m_k'} P_k'(x_{m_k'}) P(\hat{x}_{m_{\mathcal{K}}''} \mid x_{m_k'}) f_k'(x_{m_k};\hat{x}_{\mathcal{K}},\boldsymbol{y})}{\sum_{m_k'} P_k'(x_{m_k'}) P(\hat{x}_{m_{\mathcal{K}}''} \mid x_{m_k'}) f_k'(x_{m_k'};\hat{x}_{\mathcal{K}},\boldsymbol{y})}               \\
-				 & \ge (1 - \rho) \sum_{m_k} \frac{P_k'(x_{m_k}) f_k'(x_{m_k};\hat{x}_{\mathcal{K}},\boldsymbol{y})}{\sum_{m_k'} P_k'(x_{m_k'}) f_k'(x_{m_k'};\hat{x}_{\mathcal{K}},\boldsymbol{y})} \sum_{m_{\mathcal{K}}''} P(\hat{x}_{m_{\mathcal{K}}''} \mid x_{m_k})\nonumber                                \\
-				 & \quad \times \left( 1 - \frac{\sum_{m_k'} P_k'(x_{m_k'}) P(\hat{x}_{m_{\mathcal{K}}''} \mid x_{m_k'}) f_k'(x_{m_k'};\hat{x}_{\mathcal{K}},\boldsymbol{y})}{\sum_{m_k'} P_k'(x_{m_k'}) P(\hat{x}_{m_{\mathcal{K}}''} \mid x_{m_k'}) f_k'(x_{m_k};\hat{x}_{\mathcal{K}},\boldsymbol{y})} \right) \\
-				 & = 0,
-			\end{align}
-		\end{subequations}
-		where $f_k'(x_{m_k};\hat{x}_{\mathcal{K}},\boldsymbol{y}) \triangleq \exp \left( \frac{\rho}{1 - \rho} I_k'(x_{m_k};\hat{x}_{\mathcal{K}},\boldsymbol{y}) \right)$ and the equality holds if and only if \eqref{eq:optimal_relative_distribution} converges.
-		\eqref{eq:information_difference_lower} and \eqref{eq:information_difference_upper} together imply $I(x_{\mathcal{K}};\hat{x}_{\mathcal{K}},\boldsymbol{y}) \ge I'(x_{\mathcal{K}};\hat{x}_{\mathcal{K}},\boldsymbol{y})$.
-		Since mutual information is bounded above, we conclude the sequence \eqref{eq:input_kkt_solution} is non-decreasing and convergent in mutual information.
-
-		Next, we prove that any converging point of sequence \eqref{eq:input_kkt_solution}, denoted as $P_k^\star(x_{m_k})$, fulfills \gls{kkt} conditions \eqref{eq:input_kkt_condition}.
-		To see this, consider $P_k^{(0)}(x_{m_k}) > 0$ and define
-		\begin{equation}
-			D_k^{(r)}(x_{m_k}) \triangleq \frac{P_k^{(r+1)}(x_{m_k})}{P_k^{(r)}(x_{m_k})} = \frac{f_k^{(r)}(x_{m_k};\hat{x}_{\mathcal{K}},\boldsymbol{y})}{\sum_{m_k'} P_k^{(r)}(x_{m_k'}) f_k^{(r)}(x_{m_k'};\hat{x}_{\mathcal{K}},\boldsymbol{y})}.
-		\end{equation}
-
-		As sequence \eqref{eq:input_kkt_solution} is convergent, any state with $P_k^\star(x_{m_k}) > 0$ need to satisfy $D_k^\star(x_{m_k}) \triangleq \lim_{r \to \infty} D_k^{(r)}(x_{m_k}) = 1$, namely
-		\begin{equation}
-			I_k^\star(x_{m_k};\hat{x}_{\mathcal{K}},\boldsymbol{y}) = \frac{1 - \rho}{\rho} \log \sum_{m_k'} P_k^\star(x_{m_k'}) f_k^\star(x_{m_k'};\hat{x}_{\mathcal{K}},\boldsymbol{y}),
-		\end{equation}
-		which is reminiscent of \eqref{eq:probable_states_marginal} (and hence \eqref{eq:probable_states}).
-		That is to say, given $P_k^{(0)}(x_{m_k}) > 0$, any converging point with $P_k^\star(x_{m_k}) > 0$ must satisfy \eqref{eq:probable_states}.
-		On the other hand, we assume $P_k^\star(x_{m_k})$ does not satisfy \eqref{eq:dropped_states}, such that for any state with $P_k^\star(x_{m_k}) = 0$,
-		% On the other hand, we show if $P_k^\star(x_{m_k})$ does not satisfy \eqref{eq:dropped_states}, then it is not a converging point of sequence \eqref{eq:input_kkt_solution}.
-By this assumption, for any state with $P_k^\star(x_{m_k}) = 0$,
-		\begin{equation}
-			I_k^\star(x_{m_k};\hat{x}_{\mathcal{K}},\boldsymbol{y}) > I^\star(x_{\mathcal{K}};\hat{x}_{\mathcal{K}},\boldsymbol{y}) = \sum_{m_k'} P_k^\star(x_{m_k'}) I_k^\star(x_{m_k'};\hat{x}_{\mathcal{K}},\boldsymbol{y}),
-		\end{equation}
-		where the equality inherits from \eqref{eq:weighted_sum_mutual_information}.
-		Since the exponential function is monotonically increasing, we have $f_k^\star(x_{m_k};\hat{x}_{\mathcal{K}},\boldsymbol{y}) > \sum_{m_k'} P_k^\star(x_{m_k'}) f_k^\star(x_{m_k'};\hat{x}_{\mathcal{K}},\boldsymbol{y})$ and $D_k^\star(x_{m_k}) > 1$.
-		Considering $P_k^{(0)}(x_{m_k}) > 0$ and $P_k^\star(x_{m_k}) = 0$, it contradicts with
-		\begin{equation}
-			P_k^{(r)}(x_{m_k}) = P_k^{(0)}(x_{m_k}) \prod_{n=1}^r D_k^{(n)}(x_{m_k}).
-		\end{equation}
-		Therefore, given $P_k^{(0)}(x_{m_k}) > 0$, any converging point with $P_k^\star(x_{m_k}) = 0$ must satisfy \eqref{eq:dropped_states}.
-		This completes the proof.
-		\qedsymbol
-		\label{ap:input_kkt_solution}
-	\end{subsection}
-
-	\begin{subsection}{Proof of Proposition \ref{pr:threshold}}
-		Since $L$ input letters are with non-zero probability and $x \to z \to \hat{x}$ formulates a Markov chain, we need $L$ non-empty decision regions and at least $L+1$ distinct thresholds (including \num{0} and $\infty$) to minimize the distortion between source and decision.
-		On the other hand, the optimal decision regions are apparently empty for those unused letters.
-
-		Suppose the optimal number of thresholds is $S+1$ where $S \ge L$.
-		Let $\boldsymbol{t} \triangleq [t_0,\ldots,t_S]^T \in \mathbb{R}_{+}^{(S+1) \times 1}$ be the optimal threshold vector where $t_{s-1} < t_s$, $\forall s \in \mathcal{S} \triangleq \{1,\ldots,S\}$.
-		Since the optimal decision region for any letter may consist of multiple partitions, without loss of generality, we assume the mapping from threshold vector to decision region $l' \in \mathcal{L} \triangleq \{1,\ldots,L\}$ is given by $\mathcal{R}_{l'} = \bigcup_{s \equiv l' \pmod L} [t_{s-1},t_s)$.
-		\begin{footnote}
-			The proof holds for any valid mapping from threshold vector to decision regions, and we consider this specific case for the ease of presentation.
-		\end{footnote}
-		The threshold optimization problem is
-		\begin{maxi!}
-			{\scriptstyle{\boldsymbol{t}}}{I_{\mathrm{B}}(x;\hat{x})}{\label{op:decision_threshold}}{\label{ob:backscatter_mutual_information}}
-			\addConstraint{t_{s-1}}{< t_s,}{\quad \forall s \in \mathcal{S}.}{\label{co:strict_inequality}}
-		\end{maxi!}
-
-		Problem \eqref{op:decision_threshold} is intricate due to the strict inequality constraint \eqref{co:strict_inequality}.
-		Following \cite{Nguyen2020}, we first relax it to the convex counterpart, then discard the solutions that violate any original constraint.
-		The Lagrangian function for the relaxed problem is
-		\begin{equation}
-			L = - I_{\mathrm{B}}(x;\hat{x}) + \sum_{s \in \mathcal{S}} \mu_s (t_{s-1} - t_s),
-		\end{equation}
-		where $\mu_s$ is the Lagrange multiplier associated with the non-strict version of \eqref{co:strict_inequality}.
-		The \gls{kkt} conditions on the optimal primal and dual solutions are, $\forall s \in \mathcal{S}$,
-		\begin{subequations}
-			\label{eq:kkt_thresholding}
-			\begin{equation}
-				- \nabla_{t_s^\star} I^\star_{\mathrm{B}}(x;\hat{x}) + \mu_{s-1}^\star - \mu_s^\star = 0,
-				\label{eq:stationarity}
-			\end{equation}
-			\begin{equation}
-				\mu_s^\star \ge 0,
-				\label{eq:dual_feasibility}
-			\end{equation}
-			\begin{equation}
-				\mu_s^\star (t_{s-1}^\star - t_s^\star) = 0.
-				\label{eq:complementary_slackness}
-			\end{equation}
-
-		\end{subequations}
-		Due to the strict inequality constraint \eqref{co:strict_inequality}, conditions \eqref{eq:dual_feasibility} and \eqref{eq:complementary_slackness} together imply $\mu_s^\star = 0$, $\forall s \in \mathcal{S}$.
-		Besides, it is trivial to conclude $t_0^\star = 0$ for energy-based detection.
-		As such, the necessary optimality conditions for problem \eqref{op:decision_threshold}, $\forall s \in \mathcal{S}$,
-		\begin{equation}
-			\nabla_{t_{s}^\star} I^\star_{\mathrm{B}}(x;\hat{x}) = 0,
-		\end{equation}
-		which can be explicitly written as, $\forall s \equiv l' \pmod L$,
-		\begin{equation}
-			\sum_l P(x_l) \frac{(t_s^\star)^{N-1} e^{-t_s^\star/\sigma_l^2}}{\sigma_l^{2N} (N-1)!} \log \frac{P(x_l \mid \hat{x}_{l'+1})}{P(x_l \mid \hat{x}_{l'})} = 0,
-			\label{eq:kkt_threshold_explicit}
-		\end{equation}
-
-		According to \cite{He2021}, the optimal backward channel quantizer is convex and separates each pair of posterior distribution by a hyperplane.
-		It implies, for a given output letter $l'$, the sequence $\{\log {P(x_l \mid \hat{x}_{l'+1})}/{P(x_l \mid \hat{x}_{l'})}\}_{l \in \mathcal{L}}$ changes sign exactly once.
-		We notice the left-hand side of \eqref{eq:kkt_threshold_explicit} is a generalized Dirichlet polynomial, and by Descartes' rule of signs \cite{Jameson2006}, has at most one positive solution.
-		% TODO
-		In other words, starting from $t_0^\star$, each optimal decision region requires at most one additional distinct threshold, and we have $S \le L$.
-		Therefore, we conclude $S = L$ and the proof is completed.
-		\qedsymbol
-		\label{ap:threshold}
-	\end{subsection}
-\end{appendix}
-
-\bibliographystyle{IEEEtran}
-\bibliography{library.bib}
-\end{document}

### 2022-05-26 assets/reflection_state_distribution.tex
:paintbrush: Update probability and block illustrations

--- 2022-05-25 assets/tag_distribution.tex
@@
 					y descriptions at=edge left,
-					vertical sep=15
+					vertical sep=10
 				},
@@
 			xlabel={Reflection State},
-			ylabel={Probability},
 			enlarge x limits={value=0.25,upper},
@@
 			width=10cm,
-			height=4cm,
-			every axis plot/.append style={bar shift=0},
-			legend style={pattern=none}
+			height=3cm,
+			every axis plot/.append style={bar shift=0}
 		]
@@
 		\legend{SR}
-		\nextgroupplot
+		\nextgroupplot[ylabel={Probability Distribution}]
 		\addplot[red,fill=red!30!white] coordinates {(-1,-1)};

### 2022-05-26 assets/scatter_model.tex
:paintbrush: Update probability and block illustrations

--- 2022-05-22 main.tex
@@
-\documentclass[journal]{IEEEtran}
-
-\usepackage{adjustbox}
-\usepackage{algorithm}
-\usepackage{algpseudocode}
-\usepackage{amsfonts}
-\usepackage{amsmath}
-\usepackage{amssymb}
-\usepackage{amsthm}
-\usepackage{array}
-\usepackage{circuitikz}
-\usepackage{cite}
-\usepackage{colortbl}
-\usepackage{environ}
-\usepackage{fixmath}
-\usepackage{grffile}
-\usepackage{hyperref}
-\usepackage{import}
-\usepackage{mathtools}
-\usepackage{microtype}
-\usepackage{multirow}
-\usepackage{pgffor}
-\usepackage{pgfgantt}
-\usepackage{pgfplots}
-\usepackage{physics}
-\usepackage{siunitx}
-\usepackage{stfloats}
-\usepackage{tcolorbox}
-\usepackage{tikz}
-\usepackage{url}
-\usepackage{xcolor}
-\usepackage[T1]{fontenc}
-\usepackage[acronym]{glossaries-extra}
-\usepackage[caption=false,font=footnotesize,subrefformat=parens,labelformat=parens]{subfig}
-\usepackage[short]{optidef}
-\usepackage[subtle]{savetrees}
-
-\listfiles
-\interdisplaylinepenalty=2500
-\pgfplotsset{compat=newest}
-\usepgfplotslibrary{patchplots}
-\newtheorem{proposition}{Proposition}
-\newtheorem{remark}{Remark}
-\newtheorem{theorem}{Theorem}
-\DeclareSIUnit{\belm}{Bm}
-\DeclareSIUnit{\dBm}{\deci\belm}
-\DeclareSIUnit{\beli}{Bi}
-\DeclareSIUnit{\dBi}{\deci\beli}
-\ctikzset{american}
-\usetikzlibrary{arrows,calc,matrix,patterns,positioning}
-
-\DeclarePairedDelimiterX{\infdivx}[2]{(}{)}{%
-	#1\;\delimsize\|\;#2%
-}
-\newcommand{\infdiv}{D\infdivx}
-\renewcommand{\qedsymbol}{\hfill\ensuremath{\Box}}
-
-\makeatletter
-\tikzset{
-	block/.style={draw,rectangle,align=center},
-    from/.style args={#1 to #2}{
-        above right={0cm of #1},
-        /utils/exec=\pgfpointdiff
-            {\tikz@scan@one@point\pgfutil@firstofone(#1)\relax}
-            {\tikz@scan@one@point\pgfutil@firstofone(#2)\relax},
-        minimum width/.expanded=\the\pgf@x,
-        minimum height/.expanded=\the\pgf@y
-	}
-}
-\makeatother
-
-\algrenewcommand{\algorithmicwhile}{\textbf{While}}
-\algrenewcommand{\algorithmicif}{\textbf{If}}
-\algrenewcommand{\algorithmicthen}{\textbf{Then}}
-\algrenewcommand{\algorithmicelse}{\textbf{Else}}
-\algrenewcommand{\algorithmicend}{\textbf{End}}
-\algrenewcommand{\algorithmicrepeat}{\textbf{Repeat}}
-\algrenewcommand{\algorithmicuntil}{\textbf{Until}}
-
-\setabbreviationstyle[acronym]{long-short}
-
-\newacronym{af}{AF}{Amplify-and-Forward}
-\newacronym{ambc}{AmBC}{Ambient Backscatter Communications}
-\newacronym{ap}{AP}{Access Point}
-\newacronym{awgn}{AWGN}{Additive White Gaussian Noise}
-\newacronym{bcd}{BCD}{Block Coordinate Descent}
-\newacronym{bibo}{BIBO}{Binary-Input Binary-Output}
-\newacronym{bpcu}{\si{bpcu}}{bit per channel use}
-\newacronym{bpsphz}{\si{bps/Hz}}{bit per second per Hertz}
-\newacronym{cscg}{CSCG}{Circularly Symmetric Complex Gaussian}
-\newacronym{csi}{CSI}{Channel State Information}
-\newacronym{df}{DF}{Decode-and-Forward}
-\newacronym{dmc}{DMC}{Discrete Memoryless Channel}
-\newacronym{dmtc}{DMTC}{Discrete Memoryless Thresholding Channel}
-\newacronym{dmtmac}{DMTMAC}{Discrete Memoryless Thresholding Multiple Access Channel}
-\newacronym{dp}{DP}{Dynamic Programming}
-\newacronym{iid}{i.i.d.}{independent and identically distributed}
-\newacronym{irs}{IRS}{Intelligent Reflecting Surface}
-\newacronym{kkt}{KKT}{Karush–Kuhn–Tucker}
-\newacronym{mac}{MAC}{Multiple Access Channel}
-\newacronym{mc}{MC}{Multiplication Coding}
-\newacronym{miso}{MISO}{Multiple-Input Single-Output}
-\newacronym{mimo}{MIMO}{Multiple-Input Multiple-Output}
-\newacronym{ml}{ML}{Maximum-Likelihood}
-\newacronym{noma}{NOMA}{Non-Orthogonal Multiple Access}
-\newacronym{ofdm}{OFDM}{Orthogonal Frequency-Division Multiplexing}
-\newacronym{pdf}{PDF}{Probability Density Function}
-\newacronym{psk}{PSK}{Phase Shift Keying}
-\newacronym{pin}{PIN}{Positive Intrinsic-Negative}
-\newacronym{qam}{QAM}{Quadrature Amplitude Modulation}
-\newacronym{rf}{RF}{Radio Frequency}
-\newacronym{sc}{SC}{Superposition Coding}
-\newacronym{sic}{SIC}{Successive Interference Cancellation}
-\newacronym{simo}{SIMO}{Single-Input Multiple-Output}
-\newacronym{sinr}{SINR}{Signal-to-Interference-plus-Noise Ratio}
-\newacronym{smawk}{SMAWK}{Shor-Moran-Aggarwal-Wilber-Klawe}
-\newacronym{sr}{SR}{Symbiotic Radio}
-\newacronym{tdma}{TDMA}{Time-Division Multiple Access}
-\newacronym{tg}{TG}{tag}
-\newacronym{ue}{UE}{user}
-
-\begin{document}
-\title{Metascatter: Unifying Symbiotic Radio and Intelligent Reflecting Surface}
-\author{
-	\IEEEauthorblockN{
-		Yang~Zhao,~\IEEEmembership{Member,~IEEE,}
-		and~Bruno~Clerckx,~\IEEEmembership{Senior~Member,~IEEE}
-	}
-	\thanks{
-		The authors are with the Department of Electrical and Electronic Engineering, Imperial College London, London SW7 2AZ, U.K. (e-mail: \{yang.zhao18, b.clerckx\}@imperial.ac.uk).
-	}
-}
-\maketitle
-
-\begin{abstract}
-	Backscatter allows wireless nodes to harvest energy from, modulate information over, and reconfigure propagation of surrounding radio waves.
-	We introduce the concept of Metascatter, which adapts the input probability distribution of a finite-state backscatter device based on Channel State Information (CSI), to simultaneously act as parasitic source of Symbiotic Radio (SR) that conveys sensor data and reflecting element of Intelligent Reflecting Surface (IRS) that assists legacy transmission.
-	Using shared spectrum, energy, and infrastructures, fully cognitive networks can be built over Metascatter, and we consider a basic scenario where a multi-antenna Access Point (AP) and multiple Metascatter simultaneously transmit to a single-antenna user.
-	Since tags involve load switching and the primary and backscatter messages are multiplied (instead of superposed) in the received signal, it is assumed the user employ joint energy detection on all tags, then model their reflection pattern within the equivalent CSI for primary decoding.
-	We characterize the achievable primary-(sum-)backscatter rate region through a joint optimization of transmit beamforming vector at the AP, input probability distribution at the tags, and energy detection regions at the user.
-	A suboptimal solution is provided by the Block Coordinate Descent (BCD) method, where the beamforming, input distribution, and decision thresholds are obtained by Successive Convex Approximation (SCA), Karush–Kuhn–Tucker (KKT), and Dynamic Programming (DP), respectively.
-	Simulation results demonstrate Metascatter can exploit the additional backscatter path to transmit and assist.
-\end{abstract}
-
-\begin{section}{Introduction}
-	\IEEEPARstart{B}{ackscatter} is recently re-innovated as a promising approach to support low-power communications and control wireless propagation environments.
-	The concept of \gls{ambc} was first proposed in \cite{Liu2013b}, where each tag harvests energy from and modulates information over ambient \gls{rf} signals by periodically switching between different reflection patterns.
-	It enables battery-free communication between fully passive nodes, but the backscatter signal strength can be relatively weak and the decoding is subject to strong direct-link interference.
-	To solve this, \cite{Yang2018d} exploited the repeating structure of \gls{ofdm} symbol for interference cancellation based on backscatter channel strength.
-	Cooperative primary-backscatter decoding using co-located receiver, known as cooperative \gls{ambc}, was proposed in \cite{Yang2018}.
-	The authors evaluated the error performance of \gls{ml}, linear, and \gls{sic} detectors for flat fading channels, and proposed a low-complexity \gls{ml} detector for frequency-selective fading channels with ambient \gls{ofdm} carrier.
-	When transmit cooperation is also available, cooperative \gls{ambc} is more commonly known as \gls{sr} \cite{Liang2020}.
-	The authors of \cite{Guo2019b} classified \gls{sr} into commensal, parasitic, and competitive modes based on the relative link priority, then derived their instantaneous achievable rate and optimal power allocation.
-	The outage probability for those modes was later studied in \cite{Ding2020}.
-	On the other hand, it was concluded in \cite{Long2020a} that if the backscatter symbol period is much longer than the primary symbol period, then the non-coherent achievable rate of primary decoding would approach that of the coherent case.
-	The authors also considered the transmit precoder design for weighted sum-rate maximization and transmit power minimization problems.
-	\cite{Zhou2019a} explored how the number of transmit antennas, receive antennas, and symbol period ratio asymptotically influence the ergodic rate of primary and backscatter links.
-	With multi-antenna at all ends, \cite{Wu2021a} optimized the transmit precoder to maximize the backscatter achievable rate under primary rate constraint.
-	However, those paper only considered single tag scenario and the optimal tag multiple access scheme remains unknown.
-	\cite{Xu2021a} proposed a \gls{noma}-based \gls{sr} and studied the receive combiner design when the receiver decodes in the order of equivalent channel strength.
-	A \gls{tdma}-based \gls{sr} with energy harvesting constraints was also presented in \cite{Yang2021a}, and energy efficiency maximization was considered with respect to transmit power, reflection efficiency, and time allocation design.
-	In \cite{Han2021}, random code-assisted backscatter multiple access was combined with \gls{sr}, and the authors evaluated the asymptotic \gls{sinr} performance using random matrix theory.
-
-	On the other hand, \gls{irs} has recently emerged as a promising technique to enhance the energy efficiency.
-	In practice, an \gls{irs} consists of multiple individual sub-wavelength reflecting elements to adjust the amplitude and phase of the incoming signal (i.e., passive beamforming).
-	Different from relay, backscatter and frequency-selective surface \cite{Anwar2018}, \gls{irs} assists the primary transmission using passive components with much lower energy consumption and thermal noise, but is limited to frequency-dependent reflection.
-	\cite{Wu2018} proposed an \gls{irs}-assisted \gls{miso} system and jointly optimized the precoder and the phase shifts to minimize the transmit power.
-	The active and passive beamforming problem was then extended to the discrete phase shift case \cite{Wu2019a} and the multi-user case \cite{Wu2019}.
-	In \cite{Abeywickrama2020}, the authors investigated the impact of non-zero resistance on the reflection pattern and emphasized the coupling between reflection amplitude and phase shift in practice.
-	To estimate the cascaded link without \gls{rf}-chains at the \gls{irs}, practical protocols were developed based on element-wise on/off switching \cite{Nadeem2019}, training sequence and reflection pattern design \cite{You2019,Kang2020}, and compressed sensing \cite{Wang2020}.
-	\gls{irs} was also added to single-tag and multi-tag \gls{sr} systems to improve backscatter efficiency \cite{Chen2021,Zhang2021d}.
-	Recently, the idea of \gls{irs}-empowered \gls{sr} was proposed in \cite{Xu2020b,Hua2022}, where the reflection pattern can be decoupled as the multiplication of whole phase shift matrix and one backscatter symbol.
-	The idea was combined with spatial modulation to divide the \gls{irs} into reflection and information and elements, and the error performance of non-coherent backscatter detection was studied accordingly \cite{Hu2021a}.
-
-	To the best of our knowledge, most existing \gls{sr} systems \cite{Yang2018,Guo2019b,Ding2020,Long2020a,Zhou2019a,Wu2021a,Xu2021a} assumed Gaussian codebook at the tags and employed \gls{sic} from primary to backscatter link.
-	It thus requires non-coherent primary encoding at the transmitter and involves re-encoding, precoding, and subtraction operations that may not be available to legacy receivers.
-	Besides, the primary and backscatter symbols in \gls{sr} are mixed by multiplication coding instead of superposition coding, and the backscatter symbol period can be much longer than the primary symbol period due to physical constraints.
-	Inspired by above, we propose a novel Metascatter network where multiple battery-free tags ride over a conventional point-to-point system and adapt their input probability distribution to simultaneously act as backscatter tags of \gls{sr} and reflecting elements of \gls{irs}.
-	To fully utilize the reflection pattern and signal structure, we also present a novel decoding strategy with minor modifications on existing receivers.
-	The contributions of this paper is summarized as follows.
-
-	\emph{First,} Metascatter adapts the input probability distribution of a finite-state backscatter device based on the primary and backscatter \gls{csi}.
-	It generalizes the backscatter tags of \gls{sr} and reflecting elements of \gls{irs} to improve the primary-backscatter tradeoff in a flexible manner.
-	When the primary link is absolutely prioritized, the tag input probability boils down to \num{1} at the state that maximizes the equivalent channel strength and \num{0} at other states, which is essentially the phase shift selection of an \gls{irs} element.
-	When we only care about the backscatter performance, the network boils down to a multi-tag \gls{ambc} and the input design can be simplified accordingly.
-
-	\emph{Second,} we propose a novel receiving strategy where the backscatter symbol of all tags are first recovered by energy-based decoding, then modeled within equivalent \gls{csi} for primary decoding.
-	When the ratio of backscatter symbol period over primary symbol period is large enough, the randomness of primary source can be averaged out and the performance of non-coherent backscatter decoding can be greatly improved.
-	Since the primary and backscatter symbols are mixed by multiplication coding, the backscatter decoding can be viewed as part of primary channel training, which avoids non-coherent encoding at the transmitter and \gls{sic} at the receiver.
-
-	\emph{Third,} we characterize the achievable primary-(sum-)backscatter rate region by iteratively optimizing the tag input distribution, the backscatter decision threshold, and the transmit precoder.
-	For the input design, we propose a numerical method to evaluate the \gls{kkt} solutions by limits of sequences.
-	For the threshold design, we derive the minimum number of decision thresholds to maximize the total backscatter rate, and obtain the optimal thresholds by \gls{dp} accelerated by \gls{smawk} algorithm.
-	However, the optimal precoder design can be non-trivial and we may end up with a low-complexity suboptimal solution.
-
-\end{section}
-
-\begin{section}{Backscatter Principles}
-	% \begin{figure}[!t]
-	% 	\centering
-	% 	\resizebox{0.6\columnwidth}{!}{
-	% 		\begin{circuitikz}[transform shape]
-	% 			\coordinate (O) at (0,0);
-	% 			\node[block,from={O to $(O) + (6.375,3.25)$}](T){};
-	% 			\draw (0,1.75)
-	% 			to[short] ++(-0.875,0)
-	% 			to[short] ++(0,0.5) node[bareantenna](A){Bx};
-	% 			\draw (0,1.75)
-	% 			to[short,-*] ++(0.25,0) coordinate(J);
-	% 			\draw (J)
-	% 			to[short] ++(0,1)
-	% 			to[short] ++(0.5,0) coordinate(J1);
-	% 			\node[block,from={$(J1) + (0,-0.25)$ to $(J1) + (2.5,0.25)$}](R){Rectifier};
-	% 			\draw (J)
-	% 			to[short] ++(0.5,0) coordinate(J2);
-	% 			\node[block,from={$(J2) + (0,-0.25)$ to $(J2) + (2.5,0.25)$}](D){Demodulator};
-	% 			\draw (J)
-	% 			to[short] ++(0,-1)
-	% 			to[short] ++(0.5,0) coordinate(J3)
-	% 			to [vR,mirror,invert,/tikz/circuitikz/bipoles/length=1cm] ++(1.75,0) node[ground,rotate=90]{};
-	% 			\node[block,from={$(J3) + (0,-0.25)$ to $(J3) + (2.5,0.25)$},draw=none](M){};
-	% 			\draw ($(J3) + (0,-0.25)$) rectangle ($(J3) + (2.5,0.25)$);
-	% 			\draw ($(J3) + (1.25,-0.5)$) node[]{Modulator};
-	% 			\draw[dashed,-{Latex[length=2mm]}] (R.east) -- ++(0.75,0);
-	% 			\draw[-{Latex[length=2mm]}] (D.east) -- ++(0.75,0);
-	% 			\draw[{Latex[length=2mm]}-] (M.east) -- ++(0.75,0);
-	% 			\node[block,from={$(R.east) + (0.75,-0.25)$ to $(R.east) + (2.875,0.25)$}](P){Power buffer};
-	% 			\node[block,from={$(M.east) + (0.75,-0.25)$ to $(D.east) + (2.875,0.25)$}](S){Digital\\section};
-	% 			\draw[dashed,-{Latex[length=2mm]}] (P.south) to (S.north);
-	% 			\coordinate (F1) at ($(P.south)!0.5!(S.north)$);
-	% 			\coordinate (F2) at ($(D.east)!0.5!(S.west)$);
-	% 			\coordinate (F3) at ($(D.south)!0.5!(M.north)$);
-	% 			\draw[dashed] (F1) to (F1-|D.north);
-	% 			\draw[dashed,-{Latex[length=2mm]}] (F1-|D.north) to (D.north);
-	% 			\draw[dashed] (F1-|F2) to (F2|-F3) to (M|-F3);
-	% 			\draw[dashed,-{Latex[length=2mm]}] (M|-F3) to (M.north);
-	% 		\end{circuitikz}
-	% 	}
-	% 	\caption{The block diagram and equivalent circuit of a passive tag. The solid and dashed vectors represent signal and energy flows.}
-	% 	\label{fi:tag_block_diagram}
-	% \end{figure}
-
-	\begin{figure}[!t]
-		\centering
-		\subfloat[Block diagram]{
-			\resizebox{0.6\columnwidth}{!}{
-				\begin{circuitikz}[transform shape]
-					\coordinate (O) at (0,0);
-					\node[block,from={O to $(O) + (6.375,3.25)$}](T){};
-					\draw (0,1.75)
-					to[short] ++(-0.875,0)
-					to[short] ++(0,0.5) node[bareantenna](A){Bx};
-					\draw (0,1.75)
-					to[short,-*] ++(0.25,0) coordinate(J);
-					\draw (J)
-					to[short] ++(0,1)
-					to[short] ++(0.5,0) coordinate(J1);
-					\node[block,from={$(J1) + (0,-0.25)$ to $(J1) + (2.5,0.25)$}](R){Rectifier};
-					\draw (J)
-					to[short] ++(0.5,0) coordinate(J2);
-					\node[block,from={$(J2) + (0,-0.25)$ to $(J2) + (2.5,0.25)$}](D){Demodulator};
-					\draw (J)
-					to[short] ++(0,-1)
-					to[short] ++(0.5,0) coordinate(J3)
-					to [vR,mirror,invert,/tikz/circuitikz/bipoles/length=1cm] ++(1.75,0) node[ground,rotate=90]{};
-					\node[block,from={$(J3) + (0,-0.25)$ to $(J3) + (2.5,0.25)$},draw=none](M){};
-					\draw ($(J3) + (0,-0.25)$) rectangle ($(J3) + (2.5,0.25)$);
-					\draw ($(J3) + (1.25,-0.5)$) node[]{Modulator};
-					\draw[dashed,-{Latex[length=2mm]}] (R.east) -- ++(0.75,0);
-					\draw[-{Latex[length=2mm]}] (D.east) -- ++(0.75,0);
-					\draw[{Latex[length=2mm]}-] (M.east) -- ++(0.75,0);
-					\node[block,from={$(R.east) + (0.75,-0.25)$ to $(R.east) + (2.875,0.25)$}](P){Power buffer};
-					\node[block,from={$(M.east) + (0.75,-0.25)$ to $(D.east) + (2.875,0.25)$}](S){Digital\\section};
-					\draw[dashed,-{Latex[length=2mm]}] (P.south) to (S.north);
-					\coordinate (F1) at ($(P.south)!0.5!(S.north)$);
-					\coordinate (F2) at ($(D.east)!0.5!(S.west)$);
-					\coordinate (F3) at ($(D.south)!0.5!(M.north)$);
-					\draw[dashed] (F1) to (F1-|D.north);
-					\draw[dashed,-{Latex[length=2mm]}] (F1-|D.north) to (D.north);
-					\draw[dashed] (F1-|F2) to (F2|-F3) to (M|-F3);
-					\draw[dashed,-{Latex[length=2mm]}] (M|-F3) to (M.north);
-				\end{circuitikz}
-			}
-			\label{fi:block_diagram}
-		}
-		\setcounter{subfigure}{2}%
-		\subfloat[Scatter model]{
-			\resizebox{0.35\columnwidth}{!}{
 \begin{circuitikz}[transform shape]
@@
 \end{circuitikz}
-			}
-			\label{fi:scatter_model}
-		}
-		\setcounter{subfigure}{1}
-		\subfloat[Equivalent circuit]{
-			\resizebox{0.9\columnwidth}{!}{
-				\begin{circuitikz}[transform shape]
-					\tikzstyle{every node}=[font=\Large]
-					\draw (0,0) coordinate(O)
-					to [sV,l=$V_0$] ++(0,1.5)
-					to [L,l=$X_{\mathrm{A}}$] ++(0,1.5)
-					to [R=$R_{\mathrm{A}}$,-*] ++(3,0) coordinate(AM)
-					to [sI,l_=$I_0$,-*] ++(0,-3)
-					to [short] (O);
-					\draw (AM)
-					to [short] ++(0.5,0)
-					to [L,l=$X_m$,-*] ++(3,0) coordinate(M)
-					to [R=$R_m^{\mathrm{S}}$] ++(3,0) coordinate(MH);
-					\draw (M)
-					to [R=$R_m^{\mathrm{P}}$,-*] ++(0,-3);
-					\draw (MH)
-					to [D,-*] ++(1.5,0) coordinate(H)
-					to [C=$X_{\mathrm{H}}$,-*] ++(0,-3);
-					\draw (H)
-					to [short] ++(1.5,0)
-					to [R=$R_{\mathrm{H}}$] ++(0,-3)
-					to [short] (O);
-
-					\draw [blue,dashed] (-1.125,-0.5) rectangle (3.5,4);
-					\draw [yellow,dashed] (4,-0.5) rectangle (9,4);
-					\draw [red,dashed] (9.5,-0.5) rectangle (13.5,4);
-
-					\draw [blue] (1.125,4.25) node[]{Antenna};
-					\draw [yellow] (6.5,4.25) node[]{Modulator};
-					\draw [red] (11.5,4.25) node[]{Harvester + Chip};
-
-					\draw (3.375,2.675) to [short] (3.375,3.175) to [short] (3.25,3.175) to [short,i_=$Z_{\mathrm{A}}$] (3.125,3.175);
-					\draw (4.125,-0.125) to [short] (4.125,0.375) to [short] (4.25,0.375) to [short,i=$Z_m$] (4.375,0.375);
-					\draw (9.625,-0.125) to [short] (9.625,0.375) to [short] (9.75,0.375) to [short,i=$Z_{\mathrm{H}}$] (9.875,0.375);
-				\end{circuitikz}
-			}
-			\label{fi:equivalent_circuit}
-		}
-		\caption{Block diagram, equivalent circuit, and scatter model of a typical passive tag.
-The solid and dashed vectors represent signal and energy flows.
-The backscatter antenna behaves as a constant power source, where the voltage $V_0$ and current $I_0$ are introduced by incident electric field $\vec{E}_{\mathrm{I}}$ and magnetic field $\vec{H}_{\mathrm{I}}$ \cite{Huang2021}.}
-	\end{figure}
-	% In a bistatic backscatter system,
-	% Consider a bistatic backscatter system with an excitation source, multiple passive tags, and a backscatter reader.
-	Passive backscatter devices (a.k.a., tags) harvest energy from and modulate information over surrounding \gls{rf} signal.
-	As shown in Fig.
-\subref*{fi:block_diagram}, a typical passive tag consists of a scattering antenna, an energy harvester, an integrated receiver, a load-switching modulator, and on-chip components (e.g., micro-controller and sensors) \cite{Dobkin2012}.
-Its equivalent circuit is also given by Fig.
-\subref*{fi:equivalent_circuit}.
-	When illuminated, the tag absorbs a portion of the impinging wave and scatters the rest back to the space.
-	The absorbed signal can be used for source decoding and energy harvesting \cite{Kim2021a}, while the scattered signal can be decomposed into the \emph{structural} and \emph{antenna} mode components \cite{Hansen1989}.
-	The structural mode scattering applies to general objects and is related to the antenna structure, shape and material, which contributes to environment multipath and can be covered by channel estimation \cite{Boyer2014}.
-	On the other hand, the antenna mode scattering models the antenna radiation and depends on the antenna-load impedance mismatch, which can be used for backscatter modulation \cite{Boyer2012} or channel reconfiguration \cite{Wu2021b}.
-	Fig. \subref*{fi:scatter_model} illustrates the scatter model.
-	For a tag with $M$ candidate states, the reflection coefficient of state $m \in \mathcal{M} \triangleq \{1,\ldots,M\}$ is defined as
-	\begin{footnote}
-		It corresponds to a linear backscatter model where the reflection coefficient is irrelevant to incident electromagnetic field strength.
-	\end{footnote}
-	\begin{equation}
-		\Gamma_m = \frac{Z_m - Z_{\mathrm{A}}^*}{Z_m + Z_{\mathrm{A}}},
-		\label{eq:reflection_coefficient}
-	\end{equation}
-	where $Z_m$ is the load impedance at state $m$ and $Z_{\mathrm{A}}$ is the antenna input impedance.
-
-	\begin{subsection}{Backscatter Modulation}
-		In backscatter modulation, the tag \emph{periodically varies} the reflection coefficient to embed its own information.
-		As such, there exists a mapping from the alphabet to the set.
-		When the \gls{csi} and reflection alphabet $\{\Gamma_1,\ldots,\Gamma_M\}$ are available at the reader, it can decode the tag message from the observed scattered signal.
-
-		For $M$-ary \gls{qam}, the complex constellation point $c_m$ maps to the corresponding reflection coefficient by \cite{Thomas2012a}
-		\begin{equation}
-			\Gamma_m = \alpha \frac{c_m}{\max_{m'} \lvert c_{m'} \rvert},
-			\label{eq:backscatter_modulation}
-		\end{equation}
-		where $\alpha \in [0,1]$ models the amplitude scatter ratio at the direction of interest.
-
-		% When the \gls{csi} and reflection alphabet $\{\Gamma_1,\ldots,\Gamma_M\}$ are available at the reader, the tag can be successfully decoded based on the received signal.
-
-	\end{subsection}
-
-	\begin{subsection}{Channel Reconfiguration}
-		2
-	\end{subsection}
-	% Tags periodically switch between different states to perform backscatter modulation.
-	% For $M$-ary \gls{qam}, the complex constellation point $c_m \in \mathcal{C}$ maps to the reflection coefficient by \cite{Thomas2012a}
-	% \begin{equation}
-	% 	\Gamma_m = \alpha \frac{c_m}{\max_{m'} \lvert c_{m'} \rvert},
-	% 	\label{eq:backscatter_modulation}
-	% \end{equation}
-	% where $\alpha \in [0,1]$ models the harvest-backscatter ratio at the direction of interest.
-	For passive tags, $\alpha \ll 1$ is commonly assumed as the majority of the incident wave can be harvested to support tag modules \cite{Thomas2012a}.
-
-	\begin{remark}
-		By choosing proper load impedance, it is possible to implement any signal constellation or think beyond modulation.
-		For example, perfect matching enables maximum power transfer to the tag, while perfect mismatch leads to complete reflection as desired by ideal \gls{irs}.
-		It inspires Metascatter to design a smart reflection and unify wireless power transfer, backscatter modulation, and passive beamforming.
-	\end{remark}
-\end{section}
-
-\begin{section}{Metascatter}
-	\begin{subsection}{System Model}
-		\begin{figure}[!t]
-			\centering
-			\def\svgwidth{0.9\columnwidth}
-			\import{assets/}{metascatter_system.eps_tex}
-			\caption{The proposed Metascatter system.}
-			\label{fi:metascatter_system}
-		\end{figure}
-		As shown in Fig.
-\ref{fi:metascatter_system}, we propose a single-\gls{ue} multi-\gls{tg} symbiotic radio network where the \gls{rf} signal generated by the $Q$-antenna \gls{ap} is shared by two coexisting systems.
-		In the primary point-to-point system, the \gls{ap} transmits information to the single-antenna user.
-		In the secondary backscatter system, the \gls{ap} acts as the carrier emitter, the $K$ nearby single-antenna tags modulate their information over the reradiated \gls{rf} signals, and the user receives and decodes the backscatter messages.
-		Denote the \gls{ap}-\gls{ue} direct channel as $\boldsymbol{h}_{\mathrm{D}}^H \in \mathbb{C}^{1 \times Q}$, the \gls{ap}-\gls{tg} $k \in \mathcal{K} \triangleq \{1,\ldots,K\}$ forward channel as $\boldsymbol{h}_{\mathrm{F},k}^H \in \mathbb{C}^{1 \times Q}$, the \gls{tg} $k$-\gls{ue} backward channel as $h_{\mathrm{B},k}$, and define the cascaded channel of tag $k$ as $\boldsymbol{h}_{\mathrm{C},k}^H \triangleq h_{\mathrm{B},k} \boldsymbol{h}_{\mathrm{F},k}^H \in \mathbb{C}^{1 \times Q}$.
-		For simplicity, we consider a quasi-static block fading model where the channel response remain constant within each coherence interval and vary independently between consecutive blocks.
-		% Since backscatter modulation involves load switching, tags typically transmit at much lower rate, and we assume the backscatter symbol period is $N \in \mathbb{Z}_{++}$ times the primary symbol period.
-		Since backscatter modulation involves load switching, tags typically transmit at much lower rate, and we assume the backscatter symbol length is $N \in \mathbb{Z}_{++}$ times the primary symbol length.
-		We also assume the direct channel and all cascaded channels can be estimated and fed back to the \gls{ap}.
-		\begin{footnote}
-			Due to the lack of \gls{rf} chains at the passive tag, accurate and efficient \gls{csi} acquisition at the \gls{ap} can be challenging.
-			One possible approach is that the \gls{ap} sends pre-defined pilots, the tags respond in well-designed manners, and the user performs least-square estimation with feedbacks \cite{Bharadia2015,Yang2015b,Guo2019g}.
-		\end{footnote}
-
-		Consider the signal model during one backscatter symbol period.
-		We assume the primary symbol follows standard \gls{cscg} distribution and the backscatter symbol of all tags employs $M$-\gls{qam}.
-		Under perfect synchronization, the signal received by the user at primary symbol block $n \in \mathcal{N} \triangleq \{1,\ldots,N\}$ is
-		\begin{footnote}
-			We omit the signal reflected by two or more times\cite{Wu2019} and assume the time difference of arrival from different paths are negligible\cite{Guo2019b}.
-		\end{footnote}
-		\begin{equation}
-			y[n] = \left(\boldsymbol{h}_{\mathrm{D}}^H + \sum_{k \in \mathcal{K}} \sqrt{\alpha_k} \boldsymbol{h}_{\mathrm{C},k}^H x_k\right) \boldsymbol{w} s[n] + w[n],
-			\label{eq:received_signal}
-		\end{equation}
-		where $\alpha_k$ and $x_k$ denote respectively the harvest-backscatter efficiency and backscatter symbol of tag $k$, $s[n]$ and $w[n] \sim \mathcal{CN}(0,\sigma_w^2)$ denote respectively the primary symbol and \gls{awgn} at block $n$, and $\boldsymbol{w} \in \mathbb{C}^{Q \times 1}$ is the transmit precoder satisfying power constraint $\lVert \boldsymbol{w} \rVert^2 \le P$.
-		For the ease of notation, we define $x_{\mathcal{K}} \triangleq \{x_k : k \in \mathcal{K}\}$ as the tag input combination, and $\boldsymbol{y} \triangleq \left[y[1],\ldots,y[N]\right]^T \in \mathbb{C}^{N \times 1}$ as the received signal per backscatter symbol period.
-		For primary transmission, the equivalent channel is subject to backscatter modulation uncertainty as
-		\begin{equation}
-			\boldsymbol{h}_{\mathrm{E}}^H(x_{\mathcal{K}}) \triangleq \boldsymbol{h}_{\mathrm{D}}^H + \sum_{k \in \mathcal{K}} \sqrt{\alpha_k} \boldsymbol{h}_{\mathrm{C},k}^H x_k.
-			\label{eq:equivalent_channel}
-		\end{equation}
-
-		\begin{remark}
-			Metascatter involves an unconventional \gls{mac} where the primary and backscatter symbols of different duration are mixed by \gls{mc} instead of \gls{sc}.
-			For each tag, the reflection coefficient not only encodes the backscatter message but also influences the equivalent primary channel \eqref{eq:equivalent_channel}.
-			As such, novel receiving strategy other than \gls{sic} should be tailored to signal characteristics to unveil how reflection pattern potentially influences the primary-backscatter tradeoff.
-		\end{remark}
-	\end{subsection}
-
-	\begin{subsection}{Receiving Strategy}
-		We propose a novel receiving strategy where the backscatter symbol of all tags are first jointly identified by non-coherent energy detection, then modeled within equivalent channel \eqref{eq:equivalent_channel} as if passive beamforming.
-		Compared with conventional schemes as joint decoding and \gls{sic}, the Metascatter receiver may not achieve as high data rate for one tag, but it avoids non-coherent primary encoding and enables tag multiple access in a practical and low-complexity manner.
-		Therefore, we believe it can be compatible to and readily implemented over legacy point-to-point systems.
-
-		Define $m_k \in \mathcal{M}$ as the modulation index of tag $k$, and $m_{\mathcal{K}} \triangleq \{m_k: k \in \mathcal{K}\}$ as the modulation index combination of all tags.
-		Recall that $x_k$ and $x_{\mathcal{K}}$ are random variables representing the backscatter symbol of tag $k$ and the symbol combination of all tags, respectively.
-		Their instances are denoted by modulation index (combination) as $x_{m_k}$ and $x_{m_\mathcal{K}}$.
-		Since any backscatter combination $x_{m_\mathcal{K}}$ remains unchanged over $N$ primary symbol duration, the received signal at symbol block $n$ is only subject to the variation of $s[n]$ and $w[n]$, and follows zero-mean \gls{cscg} distribution with variance
-		\begin{equation}
-			\sigma_{m_{\mathcal{K}}}^2 = \Bigl\lvert \underbrace{\bigl(\boldsymbol{h}_{\mathrm{D}}^H + \sum_{k \in \mathcal{K}} \sqrt{\alpha_k} \boldsymbol{h}_{\mathrm{C},k}^H x_{m_k}\bigr)}_{\boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}})} \boldsymbol{w} \Bigr\rvert^2 + \sigma_w^2.
-			\label{eq:receive_variance}
-		\end{equation}
-
-		Besides, we denote the total received energy as $z \triangleq \lVert \boldsymbol{y} \rVert^2$ and the hypothesis of modulation index combination $m_{\mathcal{K}}$ as $\mathcal{H}_{m_{\mathcal{K}}}$.
-		Since $z$ is the sum of $N$ \gls{iid} exponential variables, its conditional \gls{pdf} under $\mathcal{H}_{m_{\mathcal{K}}}$ follows Erlang distribution with shape $N$ and scale $\sigma_{m_{\mathcal{K}}}^2$ as
-		\begin{equation}
-			f(z \mid \mathcal{H}_{m_{\mathcal{K}}}) = \frac{z^{N-1} e^{-z/\sigma_{m_{\mathcal{K}}}^2}}{\sigma_{m_{\mathcal{K}}}^{2N} (N-1)!}.
-			\label{eq:energy_distribution}
-		\end{equation}
-
-		Energy-based backscatter detection essentially formulates a discrete-input continuous-output memoryless \gls{mac}.
-		To further reduce decoding complexity, we divide the continuous output $z$ into disjoint decision regions to construct a \gls{dmtmac}, where the transition probability from tag input combination $x_{m_{\mathcal{K}}}$ to detector output combination $\hat{x}_{m_{\mathcal{K}}'}$ is
-		\begin{equation}
-			P(\hat{x}_{m_{\mathcal{K}}'} \mid x_{m_{\mathcal{K}}}) = \int_{\mathcal{R}_{m_{\mathcal{K}}'}} f(z \mid \mathcal{H}_{m_{\mathcal{K}}}) \dd z,
-			\label{eq:dmtmac}
-		\end{equation}
-		where $\mathcal{R}_{m_{\mathcal{K}}'}$ is the decision region over $z$ for hypothesis $\mathcal{H}_{m_{\mathcal{K}}'}$.
-	\end{subsection}
-
-	\begin{subsection}{Achievable Rates}
-		Denote the input probability distribution vector of tag $k$ as $\boldsymbol{p}_k \triangleq [P_k(x_1),\ldots,P_k(x_M)]^T \in \mathbb{R}^{M \times 1}$, where $P_k(x_{m_k})$ is the probability at state $m_k$.
-		Consider independent encoding at all tags such that the probability of input combination $x_{m_{\mathcal{K}}}$ is $P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) = \prod_{k \in \mathcal{K}} P_k(x_{m_k})$.
-		The backscatter information function of input combination $x_{m_{\mathcal{K}}}$ is defined as
-		\begin{equation}
-			I_{\mathrm{B}}(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}}) \triangleq \sum_{m_{\mathcal{K}}'} P(\hat{x}_{m_{\mathcal{K}}'} \mid x_{m_{\mathcal{K}}}) \log \frac{P(\hat{x}_{m_{\mathcal{K}}'} \mid x_{m_{\mathcal{K}}})}{P(\hat{x}_{m_{\mathcal{K}}'})},
-			\label{eq:backscatter_information_function}
-		\end{equation}
-		where $P(\hat{x}_{m_{\mathcal{K}}'}) = \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) P(\hat{x}_{m_{\mathcal{K}}'} \mid x_{m_{\mathcal{K}}})$.
-		Besides, the backscatter marginal information function associated with letter $x_{m_k}$ of tag $k$ is
-		\begin{equation}
-			I_{\mathrm{B},k}(x_{m_k};\hat{x}_{\mathcal{K}}) \triangleq \sum_{m_{\mathcal{K} \setminus \{k\}}} P_{\mathcal{K} \setminus \{k\}}(x_{m_{\mathcal{K} \setminus \{k\}}}) I_{\mathrm{B}}(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}}),
-			\label{eq:backscatter_marginal_information_function}
-		\end{equation}
-		where $P_{\mathcal{K} \setminus \{k\}}(x_{m_{\mathcal{K} \setminus \{k\}}}) = \prod_{q \in \mathcal{K} \setminus \{k\}} P_{q}(x_{m_{q}})$.
-		Therefore, the backscatter mutual information is
-		\begin{equation}
-			I_{\mathrm{B}}(x_{\mathcal{K}};\hat{x}_{\mathcal{K}}) = \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) \sum_{m_{\mathcal{K}}'} P(\hat{x}_{m_{\mathcal{K}}'} \mid x_{m_{\mathcal{K}}}) \log \frac{P(\hat{x}_{m_{\mathcal{K}}'} \mid x_{m_{\mathcal{K}}})}{P(\hat{x}_{m_{\mathcal{K}}'})}.
-			\label{eq:backscatter_mutual_information}
-		\end{equation}
-
-		Once the tag input combination is successfully decoded, the backscatter uncertainty can be eliminated and the equivalent channel for primary transmission can be updated by \eqref{eq:equivalent_channel}.
-		Similar to above, the primary information function of input combination $x_{m_{\mathcal{K}}}$ is
-		% TODO notation
-		\begin{equation}
-			I_{\mathrm{P}}(x_{m_{\mathcal{K}}};\boldsymbol{y}) \triangleq N \log_2 \left(1 + \frac{\lvert \boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_w^2}\right),
-			\label{eq:primary_information_function}
-		\end{equation}
-		the primary marginal information function associated with letter $x_{m_k}$ of tag $k$ is
-		\begin{equation}
-			I_{\mathrm{P},k}(x_{m_k};\boldsymbol{y}) \triangleq \sum_{m_{\mathcal{K} \setminus \{k\}}} P_{\mathcal{K} \setminus \{k\}}(x_{m_{\mathcal{K} \setminus \{k\}}}) I_{\mathrm{P}}(x_{m_{\mathcal{K}}};\boldsymbol{y}),
-			\label{eq:primary_marginal_information_function}
-		\end{equation}
-		and the primary (ergodic) mutual information is
-		\begin{equation}
-			I_{\mathrm{P}}(x_{\mathcal{K}};\boldsymbol{y}) = \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) N \log_2 \left(1 + \frac{\lvert \boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_w^2}\right).
-			\label{eq:primary_mutual_information}
-		\end{equation}
-
-		Therefore, the weighted sum information function, marginal information function, and mutual information of primary and backscatter links are respectively given by
-		\begin{align}
-			I(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}},\boldsymbol{y})
-			 & \triangleq \rho I_{\mathrm{P}}(x_{m_{\mathcal{K}}};\boldsymbol{y}) + (1 - \rho) I_{\mathrm{B}}(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}}),\label{eq:weighted_sum_information_function} \\
-			I_k(x_{m_k};\hat{x}_{\mathcal{K}},\boldsymbol{y})
-			 & \triangleq \rho I_{\mathrm{P},k}(x_{m_k};\boldsymbol{y}) + (1 - \rho) I_{\mathrm{B},k}(x_{m_k};\hat{x}_{\mathcal{K}}),\label{eq:weighted_sum_marginal_information}                     \\
-			I(x_{\mathcal{K}};\hat{x}_{\mathcal{K}},\boldsymbol{y})
-			 & \triangleq \rho I_{\mathrm{P}}(x_{\mathcal{K}};\boldsymbol{y}) + (1 - \rho) I_{\mathrm{B}}(x_{\mathcal{K}};\hat{x}_{\mathcal{K}}),\label{eq:weighted_sum_mutual_information}
-		\end{align}
-		where $\rho \in [0,1]$ represents the priority of the primary link.
-	\end{subsection}
-\end{section}
-
-\begin{section}{Input, Threshold, and Precoder Design}
-	To characterize the achievable primary-(sum-)backscatter rate region of Metascatter, we aim to maximize the weighted sum mutual information with respect to tag input probability distribution $\{\boldsymbol{p}_k\}$, decision threshold vector $\boldsymbol{t}$, and transmit precoder $\boldsymbol{w}$
-	\begin{maxi!}
-		{\scriptstyle{\{\boldsymbol{p}_k\},\boldsymbol{t},\boldsymbol{w}}}{I(x_{\mathcal{K}};\hat{x}_{\mathcal{K}},\boldsymbol{y})}{\label{op:weighted_sum_rate}}{\label{ob:weighted_sum_rate}}
-		\addConstraint{\sum \nolimits_{m_k} P_k(x_{m_k})}{=1,}{\quad \forall k \in \mathcal{K}}{\label{co:sum_probability}}
-		\addConstraint{P_k(x_{m_k})}{\ge 0,}{\quad \forall k \in \mathcal{K}, \ \forall m_k \in \mathcal{M}}{\label{co:nonnegative_probability}}
-		\addConstraint{\lVert \boldsymbol{w} \rVert^2}{\le P.}{\label{co:transmit_power}}
-	\end{maxi!}
-	Since problem \eqref{op:weighted_sum_rate} is not jointly convex, we propose a \gls{bcd} algorithm that iteratively updates $\{\boldsymbol{p}_k\}$, $\boldsymbol{t}$ and $\boldsymbol{w}$ until convergence.
-
-	\begin{subsection}{Input Probability Distribution}
-		For any fixed decision boundary $\boldsymbol{t}$ and transmit precoder $\boldsymbol{w}$, the equivalent \gls{dmtmac} can be formulated by \eqref{eq:dmtmac} and problem \eqref{op:weighted_sum_rate} boils down to
-		\begin{maxi!}
-			{\scriptstyle{\{\boldsymbol{p}_k\}}}{I(x_{\mathcal{K}};\hat{x}_{\mathcal{K}},\boldsymbol{y})}{\label{op:input_probability_distribution}}{}
-			\addConstraint{\eqref{co:sum_probability},\eqref{co:nonnegative_probability},}
-		\end{maxi!}
-		which involves the product term $\prod_{k \in \mathcal{K}} P_k(x_{m_k})$ and is non-convex when $K > 1$.
-		Interestingly, the sum-rate optimal input design for general discrete memoryless \gls{mac} remains an open problem, and we instead propose a \gls{kkt} solution to problem \eqref{op:input_probability_distribution}.
-		\begin{footnote}
-			As pointed out in \cite{Buhler2011}, \gls{kkt} conditions are only necessary for sum-rate optimality and these solutions may end up being saddle points.
-		\end{footnote}
-		\begin{proposition}
-			The \gls{kkt} optimality conditions for problem \eqref{op:input_probability_distribution} are equivalent to, $\forall k \in \mathcal{K}$ and $\forall m_k \in \mathcal{M}$,
-			\begin{subequations}
-				\label{eq:input_kkt_condition}
-				\begin{alignat}{2}
-					I_k^\star(x_{m_k};\hat{x}_{\mathcal{K}},\boldsymbol{y}) & = I^\star(x_{\mathcal{K}};\hat{x}_{\mathcal{K}},\boldsymbol{y}), \quad   &  & P_k^\star(x_{m_k}) > 0,\label{eq:probable_states} \\
-					I_k^\star(x_{m_k};\hat{x}_{\mathcal{K}},\boldsymbol{y}) & \le I^\star(x_{\mathcal{K}};\hat{x}_{\mathcal{K}},\boldsymbol{y}), \quad &  & P_k^\star(x_{m_k}) = 0.\label{eq:dropped_states}
-				\end{alignat}
-			\end{subequations}
-			\label{pr:input_kkt_condition}
-		\end{proposition}
-
-		\begin{proof}
-			Please refer to Appendix \ref{ap:input_kkt_condition}.
-			\label{pf:input_kkt_condition}
-		\end{proof}
-
-		We notice \eqref{eq:probable_states} means each probable state of each tag should produce the same marginal information (averaged over all states of other tags), while \eqref{eq:dropped_states} implies any state of any tag with potentially less marginal information than above should not be used.
-		Next, we generalize the Blahut-Arimoto algorithm \cite{Arimoto1972,Blahut1972a} and propose a numerical evaluation of \gls{kkt} points by limits of sequences.
-
-		\begin{proposition}
-			The \gls{kkt} solution of input probability of tag $k$ at state $m_k$ is given by the converging point of the sequence
-			\begin{equation}
-				P_k^{(r+1)}(x_{m_k}) = \frac{P_k^{(r)}(x_{m_k}) \exp \left( \frac{\rho}{1 - \rho} I_k^{(r)}(x_{m_k};\hat{x}_{\mathcal{K}},\boldsymbol{y}) \right)}{\sum_{m_k'} P_k^{(r)}(x_{m_k'}) \exp \left( \frac{\rho}{1 - \rho} I_k^{(r)}(x_{m_k'};\hat{x}_{\mathcal{K}},\boldsymbol{y}) \right)},
-				\label{eq:input_kkt_solution}
-			\end{equation}
-			where $r$ is the iteration index and $\boldsymbol{p}_k^{(0)} > \boldsymbol{0}$, $\forall k \in \mathcal{K}$.
-			At each iteration, the input distribution of tag $k$ is evaluated based on the updated input distribution of tags $1$ to $k-1$.
-			\label{pr:input_kkt_solution}
-		\end{proposition}
-		\begin{proof}
-			Please refer to Appendix \ref{ap:input_kkt_solution}.
-			\label{pf:input_kkt_solution}
-		\end{proof}
-	\end{subsection}
-
-	\begin{subsection}{Decision Threshold}
-		For a given tag input distribution $\{\boldsymbol{p}_k\}$, we can formulate an equivalent information source with augmented alphabet of tag input combination.
-		This equivalent source transmits at the total backscatter rate, and the input distribution is given by $P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) = \prod_{k \in \mathcal{K}} P_k(x_{m_k})$, $\forall k \in \mathcal{K}$ and $\forall m_k \in \mathcal{M}$.
-
-		\begin{remark}
-			Since the equivalent source transmits at the total backscatter rate, the \gls{dmtmac} \eqref{eq:dmtmac} is essentially a point-to-point \gls{dmtc} and we can simplify the decision threshold design accordingly.
-			\label{re:input_combination}
-		\end{remark}
-
-		Interestingly, the optimal threshold design to maximize the mutual information for a general \gls{dmtc} with a fixed number of output letters remains an open issue.
-		The reason is that each decision region may contain more than one disjoint partitions (i.e., non-convex) and the number of thresholds are unknown.
-		Fortunately, for the proposed energy detection, we proved that the \gls{dmtc} capacity can be achieved using only convex decision regions.
-		This conclusion is summarized below.
-
-		\begin{proposition}
-			For a discrete-input continuous-output channel in Erlang distribution \eqref{eq:energy_distribution}, if the \gls{dmtc} is constructed for detection (i.e., same input/output alphabet) and $L$ input letters are with non-zero probability, then it is possible to achieve the \gls{dmtc} capacity by $L$ non-empty convex decision regions defined by $L+1$ distinct decision thresholds.
-			\label{pr:threshold}
-		\end{proposition}
-
-		\begin{proof}
-			Please refer to Appendix \ref{ap:threshold}.
-			\label{pf:threshold}
-		\end{proof}
-
-		Once the optimal number of decision threshold is determined, we can first discretize the output energy level into numerous bins, then obtain the optimal decision regions that maximizes the total backscatter rate by \gls{dp} accelerated by \gls{smawk} algorithm \cite{He2021}.
-
-		\begin{tcolorbox}
-			We may need to tailor threshold design for Metascatter as threshold design has potential impact on primary achievable rate, as implied by some simulation results.
-		\end{tcolorbox}
-	\end{subsection}
-
-	\begin{subsection}{Precoder}
-		\begin{tcolorbox}
-			The optimal precoder design is highly non-convex that involves integration, entropy term, and variable on exponential.
-			We may propose a suboptimal precoder based on linear combination of equivalent and cascaded channels, or consider single transmit antenna instead.
-		\end{tcolorbox}
-		\begin{align}
-			I(x_i;\hat{x}_j)
-			 & = \sum_{j \in \mathcal{I}} \int_{t_{j-1,j}}^{t_{j,j+1}} \frac{z^{N-1} \exp \left(-\frac{z}{\mathrm{tr}(H_{\mathrm{E},i} W) + \sigma_w^2}\right)}{\left(\mathrm{tr}(H_{\mathrm{E},i} W) + \sigma_w^2\right)^N (N-1)!} \dd z\nonumber                                                                                                                                                                                                                    \\
-			 & \quad \times \log \frac{\int_{t_{j-1,j}}^{t_{j,j+1}} \frac{z^{N-1} \exp \left(-\frac{z}{\mathrm{tr}(H_{\mathrm{E},i} W) + \sigma_w^2}\right)}{\left(\mathrm{tr}(H_{\mathrm{E},i} W) + \sigma_w^2\right)^N (N-1)!} \dd z}{\sum_{i' \in \mathcal{I}} \int_{t_{j-1,j}}^{t_{j,j+1}} \frac{z^{N-1} \exp \left(-\frac{z}{\mathrm{tr}(H_{\mathrm{E},i'} W) + \sigma_w^2}\right)}{\left(\mathrm{tr}(H_{\mathrm{E},i'} W) + \sigma_w^2\right)^N (N-1)!} \dd z},
-		\end{align}
-	\end{subsection}
-\end{section}
-
-\begin{section}{Preliminary Results}
-	\begin{table}[t!]
-		\centering
-		\caption{Parameters in simulation}
-		\begin{tabular}{ll}
-			Transmit antenna $Q$     & 1   \\
-			Tags $K$                 & 2   \\
-			States $M$               & 2   \\
-			Reflect ratio $\alpha$   & 0.5 \\
-			Duration ratio $N$       & 10  \\
-			Noise power $\sigma_w^2$ & 1   \\
-			Discretization bins      & 256
-		\end{tabular}
-		\label{ta:parameters}
-	\end{table}
-	Table \ref{ta:parameters} shows the parameters used in simulation.
-	We assume all links are in standard \gls{cscg} distribution and evaluated the rate regions on two instances.
-	For the input design, ``Cooperation'' assumes full transmit cooperation at all tags (i.e., joint encoding), ``Exhaustion'' runs exhaustive search on all possible input distributions, ``\gls{kkt}'' is proposed \gls{kkt} input design \eqref{eq:input_kkt_solution}, and ``Marginalization'' marginalizes the joint input array by ``Cooperation'' to obtain independent tag input distribution.
-	For the threshold design, ``\gls{smawk}'' refers to the \gls{dp}-based quantization proposed in \cite{He2021}, ``Bisection'' sequentially optimizes each threshold by bisection \cite{Nguyen2020a}, and ``\gls{ml}'' is the \gls{ml} detector that requires no knowledge of input distribution.
-
-	Figs. \ref{fi:rate_region_1} and \ref{fi:rate_region_2} show two typical scenarios where joint encoding can be helpful and unnecessary, respectively.
-	Although the proposed \gls{kkt} input design converges to the optimal solutions in both examples, it may be trapped at saddle points under poor initialization, especially when the number of tags increases.
-
-	We believed threshold design has no impact on the primary achievable rate, because primary decoding acts on $\boldsymbol{y}$ while thresholding acts on $z$.
-	As such, the threshold that maximizes the total backscatter rate should also maximize the weighted sum rate.
-	Interestingly, this may not be the case because the \gls{smawk} and Bisection threshold designs, both maximizing the total backscatter rate, can be outperformed by the \gls{ml} when it comes to weighted sum primary-(sum-)backscatter rate.
-	It may result from a precision issue, but inspires further research on threshold design for Metascatter.
-
-	\begin{figure}[!t]
-		\centering
-		\resizebox{\columnwidth}{!}{
-			\includegraphics{assets/rate_region_1.eps}
-		}
-		\caption{Achievable rate regions by input-threshold design: Case I.}
-		\label{fi:rate_region_1}
-	\end{figure}
-
-	\begin{figure}[!t]
-		\centering
-		\resizebox{\columnwidth}{!}{
-			\includegraphics{assets/rate_region_2.eps}
-		}
-		\caption{Achievable rate regions by input-threshold design: Case II.}
-		\label{fi:rate_region_2}
-	\end{figure}
-\end{section}
-
-\begin{appendix}
-	\begin{subsection}{Proof of Proposition \ref{pr:input_kkt_condition}}
-		Denote the Lagrange multipliers associated with \eqref{co:sum_probability} and \eqref{co:nonnegative_probability} as $\{\nu_k\}_{k \in \mathcal{K}}$ and $\{\lambda_{k,m_k}\}_{k \in \mathcal{K},m_k \in \mathcal{M}}$, respectively.
-		The Lagrangian function of problem \eqref{op:input_probability_distribution} is
-		\begin{align}
-			% L(\{\boldsymbol{p}_k\},\{\nu_k\},\{\lambda_{k,m_k}\})
-			L
-			 & = - I(x_{\mathcal{K}};\hat{x}_{\mathcal{K}},\boldsymbol{y}) + \sum_{k \in \mathcal{K}} \nu_k \left( \sum_{m_k \in \mathcal{M}} P_k(x_{m_k}) - 1 \right)\nonumber \\
-			 & \quad - \sum_{k \in \mathcal{K}} \sum_{m_k \in \mathcal{M}} \lambda_{k,m_k} P_k(x_{m_k}),
-		\end{align}
-		and the \gls{kkt} conditions on the optimal primal and dual variables are, $\forall m_k \in \mathcal{M}$ and $\forall k \in \mathcal{K}$,
-		\begin{subequations}
-			\label{eq:input_kkt_condition_original}
-			\begin{equation}
-				- \nabla_{P_k^\star(x_{m_k})} I^\star(x_{\mathcal{K}};\hat{x}_{\mathcal{K}},\boldsymbol{y}) + \nu_k^\star - \lambda_{k,m_k}^\star = 0,
-			\end{equation}
-			\begin{equation}
-				\lambda_{k,m_k}^\star = 0, \quad P_k^\star(x_{m_k}) > 0,
-			\end{equation}
-			\begin{equation}
-				\lambda_{k,m_k}^\star \ge 0, \quad P_k^\star(x_{m_k}) = 0,
-			\end{equation}
-		\end{subequations}
-		where the directional derivative can be explicitly expressed as
-		\begin{equation}
-			\nabla_{P_k^\star(x_{m_k})} I^\star(x_{\mathcal{K}};\hat{x}_{\mathcal{K}},\boldsymbol{y}) = I_k^\star(x_{m_k};\hat{x}_{\mathcal{K}},\boldsymbol{y}) - (1 - \rho).
-			\label{eq:input_directional_derivative}
-		\end{equation}
-
-		Combining \eqref{eq:input_kkt_condition_original} and \eqref{eq:input_directional_derivative}, we have
-		\begin{subequations}
-			\label{eq:input_kkt_condition_transformed}
-			\begin{alignat}{2}
-				I_k^\star(x_{m_k};\hat{x}_{\mathcal{K}},\boldsymbol{y}) & = \nu_k^\star + (1 - \rho), \quad   &  & P_k^\star(x_{m_k}) > 0,\label{eq:probable_states_marginal} \\
-				I_k^\star(x_{m_k};\hat{x}_{\mathcal{K}},\boldsymbol{y}) & \le \nu_k^\star + (1 - \rho), \quad &  & P_k^\star(x_{m_k}) = 0,\label{eq:dropped_states_marginal}
-			\end{alignat}
-		\end{subequations}
-		which suggests
-		\begin{equation}
-			\sum_{m_k} P_k^\star(x_{m_k}) I_k^\star(x_{m_k};\hat{x}_{\mathcal{K}},\boldsymbol{y}) = \nu_k^\star + (1 - \rho).
-			\label{eq:input_kkt_condition_implied}
-		\end{equation}
-
-		On the other hand, by definition of weighted sum marginal information \eqref{eq:weighted_sum_marginal_information},
-		\begin{equation}
-			\sum_{m_k} P_k^\star(x_{m_k}) I_k^\star(x_{m_k};\hat{x}_{\mathcal{K}},\boldsymbol{y}) = I^\star(x_{\mathcal{K}};\hat{x}_{\mathcal{K}},\boldsymbol{y}),
-			\label{eq:weighted_sum_marginal_information_implied}
-		\end{equation}
-		where the right-hand side is irrelevant to $k$.
-		\eqref{eq:input_kkt_condition_transformed}, \eqref{eq:input_kkt_condition_implied}, and \eqref{eq:weighted_sum_marginal_information_implied} together complete the proof.
-		\qedsymbol
-		\label{ap:input_kkt_condition}
-	\end{subsection}
-
-	\begin{subsection}{Proof of Proposition \ref{pr:input_kkt_solution}}
-		We first prove sequence \eqref{eq:input_kkt_solution} is non-decreasing in mutual information.
-		Let $P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) = \prod_{q \in \mathcal{K}} P_q(x_{m_q})$ and $P_{\mathcal{K}}'(x_{m_{\mathcal{K}}}) = P_k'(x_{m_k}) \prod_{q \in \mathcal{K} \setminus \{k\}} P_q(x_{m_q})$ be two probability distributions with potentially different marginal for tag $k \in \mathcal{K}$ at state $m_k \in \mathcal{M}$, and define an intermediate function $J \left( P_{\mathcal{K}}(x_{m_{\mathcal{K}}}),P_{\mathcal{K}}'(x_{m_{\mathcal{K}}}) \right)$ as \eqref{eq:intermediate_information_function}.
-		\begin{figure*}[!b]
-			\hrule
-			\begin{align}
-				J \left( P_{\mathcal{K}}(x_{m_{\mathcal{K}}}),P_{\mathcal{K}}'(x_{m_{\mathcal{K}}}) \right)
-				 & \triangleq \rho \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) N \log_2 \left(1 + \frac{\lvert \boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_w^2}\right)\nonumber                                                                                                                          \\
-				 & \quad + (1 - \rho) \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) \sum_{m_{\mathcal{K}}'} P(\hat{x}_{m_{\mathcal{K}}'} \mid x_{m_{\mathcal{K}}}) \log \frac{P(\hat{x}_{m_{\mathcal{K}}'} \mid x_{m_{\mathcal{K}}}) P_{\mathcal{K}}'(x_{m_{\mathcal{K}}})}{P'(\hat{x}_{m_{\mathcal{K}}'}) P_{\mathcal{K}}(x_{m_{\mathcal{K}}})}.
-				\label{eq:intermediate_information_function}
-			\end{align}
-		\end{figure*}
-		It is straightforward to verify $J \left( P_{\mathcal{K}}(x_{m_{\mathcal{K}}}),P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) \right) = I(x_{\mathcal{K}};\hat{x}_{\mathcal{K}},\boldsymbol{y})$ and $J \left( P_{\mathcal{K}}(x_{m_{\mathcal{K}}}),P_{\mathcal{K}}'(x_{m_{\mathcal{K}}}) \right)$ is a concave function for a fixed $P_{\mathcal{K}}'(x_{m_{\mathcal{K}}})$.
-		By choosing $\nabla_{P_k^\star(x_{m_k})} J \left( P_{\mathcal{K}}(x_{m_{\mathcal{K}}}),P_{\mathcal{K}}'(x_{m_{\mathcal{K}}}) \right) = 0$, we have
-		\begin{equation}
-			S_k'(x_{m_k}) - S_k'(x_{i_k}) + (1 - \rho) \log \frac{P_k(x_{i_k})}{P_k^\star(x_{m_k})} = 0,
-			\label{eq:optimal_intermediate_information_condition}
-		\end{equation}
-		where $i_k \ne m_k$ is the reference state and
-		\begin{align}
-			S_k'(x_{m_k})
-			 & \triangleq I_k'(x_{m_k};\hat{x}_{\mathcal{K}},\boldsymbol{y}) + (1 - \rho) \sum_{m_{\mathcal{K} \setminus \{k\}}} P_{\mathcal{K} \setminus \{k\}}(x_{m_{\mathcal{K} \setminus \{k\}}})\nonumber \\
-			 & \quad \times \sum_{m_{\mathcal{K}}'} P(\hat{x}_{m_{\mathcal{K}}'} \mid x_{m_{\mathcal{K}}}) \log P_{\mathcal{K}}'(x_{m_{\mathcal{K}}}).
-		\end{align}
-
-		Evidently, $\forall m_k \ne i_k$, \eqref{eq:optimal_intermediate_information_condition} boils down to
-		\begin{equation}
-			P_k^\star(x_{m_k}) = \frac{P_k'(x_{m_k}) \exp \left( \frac{\rho}{1 - \rho} I_k'(x_{m_k};\hat{x}_{\mathcal{K}},\boldsymbol{y}) \right)}{\sum_{m_k'} P_k'(x_{m_k'}) \exp \left( \frac{\rho}{1 - \rho} I_k'(x_{m_k'};\hat{x}_{\mathcal{K}},\boldsymbol{y}) \right)}.
-			\label{eq:optimal_relative_distribution}
-		\end{equation}
-
-		Although it seems $P_k(x_{i_k}) = 1 - \sum_{m_k \ne i_k} P_k^\star(x_{m_k})$ has no optimality guarantee, we can verify that $P_k(x_{i_k})$ has exactly the same form as \eqref{eq:optimal_relative_distribution}.
-		It implies the selection of reference state does not matter and \eqref{eq:optimal_relative_distribution} is indeed optimal $\forall m_k \in \mathcal{M}$.
-		Therefore, for a fixed $P_{\mathcal{K}}'(x_{m_{\mathcal{K}}})$, choosing $P_k(x_{m_k})$ by \eqref{eq:optimal_relative_distribution} ensures
-		\begin{equation}
-			J \left( P_{\mathcal{K}}(x_{m_{\mathcal{K}}}),P_{\mathcal{K}}'(x_{m_{\mathcal{K}}}) \right) \ge I'(x_{\mathcal{K}};\hat{x}_{\mathcal{K}},\boldsymbol{y}).
-			\label{eq:information_difference_lower}
-		\end{equation}
-
-		On the other hand, \eqref{eq:optimal_relative_distribution} also guarantees
-		\begin{subequations}
-			\label{eq:information_difference_upper}
-			\begin{align}
-				\Delta
-				 & \triangleq I(x_{\mathcal{K}};\hat{x}_{\mathcal{K}},\boldsymbol{y}) - J \left( P_{\mathcal{K}}(x_{m_{\mathcal{K}}}),P_{\mathcal{K}}'(x_{m_{\mathcal{K}}}) \right)                                                                                                                               \\
-				 & = (1 - \rho) \sum_{m_k} \frac{P_k'(x_{m_k}) f_k'(x_{m_k};\hat{x}_{\mathcal{K}},\boldsymbol{y})}{\sum_{m_k'} P_k'(x_{m_k'}) f_k'(x_{m_k'};\hat{x}_{\mathcal{K}},\boldsymbol{y})} \sum_{m_{\mathcal{K}}''} P(\hat{x}_{m_{\mathcal{K}}''} \mid x_{m_k})\nonumber                                  \\
-				 & \quad \times \log \frac{\sum_{m_k'} P_k'(x_{m_k'}) P(\hat{x}_{m_{\mathcal{K}}''} \mid x_{m_k'}) f_k'(x_{m_k};\hat{x}_{\mathcal{K}},\boldsymbol{y})}{\sum_{m_k'} P_k'(x_{m_k'}) P(\hat{x}_{m_{\mathcal{K}}''} \mid x_{m_k'}) f_k'(x_{m_k'};\hat{x}_{\mathcal{K}},\boldsymbol{y})}               \\
-				 & \ge (1 - \rho) \sum_{m_k} \frac{P_k'(x_{m_k}) f_k'(x_{m_k};\hat{x}_{\mathcal{K}},\boldsymbol{y})}{\sum_{m_k'} P_k'(x_{m_k'}) f_k'(x_{m_k'};\hat{x}_{\mathcal{K}},\boldsymbol{y})} \sum_{m_{\mathcal{K}}''} P(\hat{x}_{m_{\mathcal{K}}''} \mid x_{m_k})\nonumber                                \\
-				 & \quad \times \left( 1 - \frac{\sum_{m_k'} P_k'(x_{m_k'}) P(\hat{x}_{m_{\mathcal{K}}''} \mid x_{m_k'}) f_k'(x_{m_k'};\hat{x}_{\mathcal{K}},\boldsymbol{y})}{\sum_{m_k'} P_k'(x_{m_k'}) P(\hat{x}_{m_{\mathcal{K}}''} \mid x_{m_k'}) f_k'(x_{m_k};\hat{x}_{\mathcal{K}},\boldsymbol{y})} \right) \\
-				 & = 0,
-			\end{align}
-		\end{subequations}
-		where $f_k'(x_{m_k};\hat{x}_{\mathcal{K}},\boldsymbol{y}) \triangleq \exp \left( \frac{\rho}{1 - \rho} I_k'(x_{m_k};\hat{x}_{\mathcal{K}},\boldsymbol{y}) \right)$ and the equality holds if and only if \eqref{eq:optimal_relative_distribution} converges.
-		\eqref{eq:information_difference_lower} and \eqref{eq:information_difference_upper} together imply $I(x_{\mathcal{K}};\hat{x}_{\mathcal{K}},\boldsymbol{y}) \ge I'(x_{\mathcal{K}};\hat{x}_{\mathcal{K}},\boldsymbol{y})$.
-		Since mutual information is bounded above, we conclude the sequence \eqref{eq:input_kkt_solution} is non-decreasing and convergent in mutual information.
-
-		Next, we prove that any converging point of sequence \eqref{eq:input_kkt_solution}, denoted as $P_k^\star(x_{m_k})$, fulfills \gls{kkt} conditions \eqref{eq:input_kkt_condition}.
-		To see this, consider $P_k^{(0)}(x_{m_k}) > 0$ and define
-		\begin{equation}
-			D_k^{(r)}(x_{m_k}) \triangleq \frac{P_k^{(r+1)}(x_{m_k})}{P_k^{(r)}(x_{m_k})} = \frac{f_k^{(r)}(x_{m_k};\hat{x}_{\mathcal{K}},\boldsymbol{y})}{\sum_{m_k'} P_k^{(r)}(x_{m_k'}) f_k^{(r)}(x_{m_k'};\hat{x}_{\mathcal{K}},\boldsymbol{y})}.
-		\end{equation}
-
-		As sequence \eqref{eq:input_kkt_solution} is convergent, any state with $P_k^\star(x_{m_k}) > 0$ need to satisfy $D_k^\star(x_{m_k}) \triangleq \lim_{r \to \infty} D_k^{(r)}(x_{m_k}) = 1$, namely
-		\begin{equation}
-			I_k^\star(x_{m_k};\hat{x}_{\mathcal{K}},\boldsymbol{y}) = \frac{1 - \rho}{\rho} \log \sum_{m_k'} P_k^\star(x_{m_k'}) f_k^\star(x_{m_k'};\hat{x}_{\mathcal{K}},\boldsymbol{y}),
-		\end{equation}
-		which is reminiscent of \eqref{eq:probable_states_marginal} (and hence \eqref{eq:probable_states}).
-		That is to say, given $P_k^{(0)}(x_{m_k}) > 0$, any converging point with $P_k^\star(x_{m_k}) > 0$ must satisfy \eqref{eq:probable_states}.
-		On the other hand, we assume $P_k^\star(x_{m_k})$ does not satisfy \eqref{eq:dropped_states}, such that for any state with $P_k^\star(x_{m_k}) = 0$,
-		% On the other hand, we show if $P_k^\star(x_{m_k})$ does not satisfy \eqref{eq:dropped_states}, then it is not a converging point of sequence \eqref{eq:input_kkt_solution}.
-By this assumption, for any state with $P_k^\star(x_{m_k}) = 0$,
-		\begin{equation}
-			I_k^\star(x_{m_k};\hat{x}_{\mathcal{K}},\boldsymbol{y}) > I^\star(x_{\mathcal{K}};\hat{x}_{\mathcal{K}},\boldsymbol{y}) = \sum_{m_k'} P_k^\star(x_{m_k'}) I_k^\star(x_{m_k'};\hat{x}_{\mathcal{K}},\boldsymbol{y}),
-		\end{equation}
-		where the equality inherits from \eqref{eq:weighted_sum_mutual_information}.
-		Since the exponential function is monotonically increasing, we have $f_k^\star(x_{m_k};\hat{x}_{\mathcal{K}},\boldsymbol{y}) > \sum_{m_k'} P_k^\star(x_{m_k'}) f_k^\star(x_{m_k'};\hat{x}_{\mathcal{K}},\boldsymbol{y})$ and $D_k^\star(x_{m_k}) > 1$.
-		Considering $P_k^{(0)}(x_{m_k}) > 0$ and $P_k^\star(x_{m_k}) = 0$, it contradicts with
-		\begin{equation}
-			P_k^{(r)}(x_{m_k}) = P_k^{(0)}(x_{m_k}) \prod_{n=1}^r D_k^{(n)}(x_{m_k}).
-		\end{equation}
-		Therefore, given $P_k^{(0)}(x_{m_k}) > 0$, any converging point with $P_k^\star(x_{m_k}) = 0$ must satisfy \eqref{eq:dropped_states}.
-		This completes the proof.
-		\qedsymbol
-		\label{ap:input_kkt_solution}
-	\end{subsection}
-
-	\begin{subsection}{Proof of Proposition \ref{pr:threshold}}
-		Since $L$ input letters are with non-zero probability and $x \to z \to \hat{x}$ formulates a Markov chain, we need $L$ non-empty decision regions and at least $L+1$ distinct thresholds (including \num{0} and $\infty$) to minimize the distortion between source and decision.
-		On the other hand, the optimal decision regions are apparently empty for those unused letters.
-
-		Suppose the optimal number of thresholds is $S+1$ where $S \ge L$.
-		Let $\boldsymbol{t} \triangleq [t_0,\ldots,t_S]^T \in \mathbb{R}_{+}^{(S+1) \times 1}$ be the optimal threshold vector where $t_{s-1} < t_s$, $\forall s \in \mathcal{S} \triangleq \{1,\ldots,S\}$.
-		Since the optimal decision region for any letter may consist of multiple partitions, without loss of generality, we assume the mapping from threshold vector to decision region $l' \in \mathcal{L} \triangleq \{1,\ldots,L\}$ is given by $\mathcal{R}_{l'} = \bigcup_{s \equiv l' \pmod L} [t_{s-1},t_s)$.
-		\begin{footnote}
-			The proof holds for any valid mapping from threshold vector to decision regions, and we consider this specific case for the ease of presentation.
-		\end{footnote}
-		The threshold optimization problem is
-		\begin{maxi!}
-			{\scriptstyle{\boldsymbol{t}}}{I_{\mathrm{B}}(x;\hat{x})}{\label{op:decision_threshold}}{\label{ob:backscatter_mutual_information}}
-			\addConstraint{t_{s-1}}{< t_s,}{\quad \forall s \in \mathcal{S}.}{\label{co:strict_inequality}}
-		\end{maxi!}
-
-		Problem \eqref{op:decision_threshold} is intricate due to the strict inequality constraint \eqref{co:strict_inequality}.
-		Following \cite{Nguyen2020}, we first relax it to the convex counterpart, then discard the solutions that violate any original constraint.
-		The Lagrangian function for the relaxed problem is
-		\begin{equation}
-			L = - I_{\mathrm{B}}(x;\hat{x}) + \sum_{s \in \mathcal{S}} \mu_s (t_{s-1} - t_s),
-		\end{equation}
-		where $\mu_s$ is the Lagrange multiplier associated with the non-strict version of \eqref{co:strict_inequality}.
-		The \gls{kkt} conditions on the optimal primal and dual solutions are, $\forall s \in \mathcal{S}$,
-		\begin{subequations}
-			\label{eq:kkt_thresholding}
-			\begin{equation}
-				- \nabla_{t_s^\star} I^\star_{\mathrm{B}}(x;\hat{x}) + \mu_{s-1}^\star - \mu_s^\star = 0,
-				\label{eq:stationarity}
-			\end{equation}
-			\begin{equation}
-				\mu_s^\star \ge 0,
-				\label{eq:dual_feasibility}
-			\end{equation}
-			\begin{equation}
-				\mu_s^\star (t_{s-1}^\star - t_s^\star) = 0.
-				\label{eq:complementary_slackness}
-			\end{equation}
-
-		\end{subequations}
-		Due to the strict inequality constraint \eqref{co:strict_inequality}, conditions \eqref{eq:dual_feasibility} and \eqref{eq:complementary_slackness} together imply $\mu_s^\star = 0$, $\forall s \in \mathcal{S}$.
-		Besides, it is trivial to conclude $t_0^\star = 0$ for energy-based detection.
-		As such, the necessary optimality conditions for problem \eqref{op:decision_threshold}, $\forall s \in \mathcal{S}$,
-		\begin{equation}
-			\nabla_{t_{s}^\star} I^\star_{\mathrm{B}}(x;\hat{x}) = 0,
-		\end{equation}
-		which can be explicitly written as, $\forall s \equiv l' \pmod L$,
-		\begin{equation}
-			\sum_l P(x_l) \frac{(t_s^\star)^{N-1} e^{-t_s^\star/\sigma_l^2}}{\sigma_l^{2N} (N-1)!} \log \frac{P(x_l \mid \hat{x}_{l'+1})}{P(x_l \mid \hat{x}_{l'})} = 0,
-			\label{eq:kkt_threshold_explicit}
-		\end{equation}
-
-		According to \cite{He2021}, the optimal backward channel quantizer is convex and separates each pair of posterior distribution by a hyperplane.
-		It implies, for a given output letter $l'$, the sequence $\{\log {P(x_l \mid \hat{x}_{l'+1})}/{P(x_l \mid \hat{x}_{l'})}\}_{l \in \mathcal{L}}$ changes sign exactly once.
-		We notice the left-hand side of \eqref{eq:kkt_threshold_explicit} is a generalized Dirichlet polynomial, and by Descartes' rule of signs \cite{Jameson2006}, has at most one positive solution.
-		% TODO
-		In other words, starting from $t_0^\star$, each optimal decision region requires at most one additional distinct threshold, and we have $S \le L$.
-		Therefore, we conclude $S = L$ and the proof is completed.
-		\qedsymbol
-		\label{ap:threshold}
-	\end{subsection}
-\end{appendix}
-
-\bibliographystyle{IEEEtran}
-\bibliography{library.bib}
-\end{document}

### 2022-05-26 main.tex
:paintbrush: Update probability and block illustrations

--- 2022-05-22 main.tex
@@
 	Backscatter allows wireless nodes to harvest energy from, modulate information over, and reconfigure propagation of surrounding radio waves.
-	We introduce the concept of Metascatter, which adapts the input probability distribution of a finite-state backscatter device based on Channel State Information (CSI), to simultaneously act as parasitic source of Symbiotic Radio (SR) that conveys sensor data and reflecting element of Intelligent Reflecting Surface (IRS) that assists legacy transmission.
-	Using shared spectrum, energy, and infrastructures, fully cognitive networks can be built over Metascatter, and we consider a basic scenario where a multi-antenna Access Point (AP) and multiple Metascatter simultaneously transmit to a single-antenna user.
+	We uniquely introduce the concept of Metascatter, which adapts the input probability distribution of a finite-state backscatter device based on Channel State Information (CSI), to simultaneously act as parasitic source of Symbiotic Radio (SR) that conveys sensor data, and reflecting element of Intelligent Reflecting Surface (IRS) that assists legacy transmission.
+	Using shared spectrum, energy, and infrastructures, fully cognitive networks can be built over Metascatter, and we consider a fundamental scenario where a multi-antenna Access Point (AP) and multiple Metascatter simultaneously transmit to a single-antenna user.
 	Since tags involve load switching and the primary and backscatter messages are multiplied (instead of superposed) in the received signal, it is assumed the user employ joint energy detection on all tags, then model their reflection pattern within the equivalent CSI for primary decoding.
@@
 \begin{section}{Backscatter Principles}
-	% \begin{figure}[!t]
-	% 	\centering
-	% 	\resizebox{0.6\columnwidth}{!}{
-	% 		\begin{circuitikz}[transform shape]
-	% 			\coordinate (O) at (0,0);
-	% 			\node[block,from={O to $(O) + (6.375,3.25)$}](T){};
-	% 			\draw (0,1.75)
-	% 			to[short] ++(-0.875,0)
-	% 			to[short] ++(0,0.5) node[bareantenna](A){Bx};
-	% 			\draw (0,1.75)
-	% 			to[short,-*] ++(0.25,0) coordinate(J);
-	% 			\draw (J)
-	% 			to[short] ++(0,1)
-	% 			to[short] ++(0.5,0) coordinate(J1);
-	% 			\node[block,from={$(J1) + (0,-0.25)$ to $(J1) + (2.5,0.25)$}](R){Rectifier};
-	% 			\draw (J)
-	% 			to[short] ++(0.5,0) coordinate(J2);
-	% 			\node[block,from={$(J2) + (0,-0.25)$ to $(J2) + (2.5,0.25)$}](D){Demodulator};
-	% 			\draw (J)
-	% 			to[short] ++(0,-1)
-	% 			to[short] ++(0.5,0) coordinate(J3)
-	% 			to [vR,mirror,invert,/tikz/circuitikz/bipoles/length=1cm] ++(1.75,0) node[ground,rotate=90]{};
-	% 			\node[block,from={$(J3) + (0,-0.25)$ to $(J3) + (2.5,0.25)$},draw=none](M){};
-	% 			\draw ($(J3) + (0,-0.25)$) rectangle ($(J3) + (2.5,0.25)$);
-	% 			\draw ($(J3) + (1.25,-0.5)$) node[]{Modulator};
-	% 			\draw[dashed,-{Latex[length=2mm]}] (R.east) -- ++(0.75,0);
-	% 			\draw[-{Latex[length=2mm]}] (D.east) -- ++(0.75,0);
-	% 			\draw[{Latex[length=2mm]}-] (M.east) -- ++(0.75,0);
-	% 			\node[block,from={$(R.east) + (0.75,-0.25)$ to $(R.east) + (2.875,0.25)$}](P){Power buffer};
-	% 			\node[block,from={$(M.east) + (0.75,-0.25)$ to $(D.east) + (2.875,0.25)$}](S){Digital\\section};
-	% 			\draw[dashed,-{Latex[length=2mm]}] (P.south) to (S.north);
-	% 			\coordinate (F1) at ($(P.south)!0.5!(S.north)$);
-	% 			\coordinate (F2) at ($(D.east)!0.5!(S.west)$);
-	% 			\coordinate (F3) at ($(D.south)!0.5!(M.north)$);
-	% 			\draw[dashed] (F1) to (F1-|D.north);
-	% 			\draw[dashed,-{Latex[length=2mm]}] (F1-|D.north) to (D.north);
-	% 			\draw[dashed] (F1-|F2) to (F2|-F3) to (M|-F3);
-	% 			\draw[dashed,-{Latex[length=2mm]}] (M|-F3) to (M.north);
-	% 		\end{circuitikz}
-	% 	}
-	% 	\caption{The block diagram and equivalent circuit of a passive tag. The solid and dashed vectors represent signal and energy flows.}
-	% 	\label{fi:tag_block_diagram}
-	% \end{figure}
-
 	\begin{figure}[!t]
 		\centering
-		\subfloat[Block diagram]{
+		\subfloat[Block Diagram]{
 			\resizebox{0.6\columnwidth}{!}{
-				\begin{circuitikz}[transform shape]
-					\coordinate (O) at (0,0);
-					\node[block,from={O to $(O) + (6.375,3.25)$}](T){};
-					\draw (0,1.75)
-					to[short] ++(-0.875,0)
-					to[short] ++(0,0.5) node[bareantenna](A){Bx};
-					\draw (0,1.75)
-					to[short,-*] ++(0.25,0) coordinate(J);
-					\draw (J)
-					to[short] ++(0,1)
-					to[short] ++(0.5,0) coordinate(J1);
-					\node[block,from={$(J1) + (0,-0.25)$ to $(J1) + (2.5,0.25)$}](R){Rectifier};
-					\draw (J)
-					to[short] ++(0.5,0) coordinate(J2);
-					\node[block,from={$(J2) + (0,-0.25)$ to $(J2) + (2.5,0.25)$}](D){Demodulator};
-					\draw (J)
-					to[short] ++(0,-1)
-					to[short] ++(0.5,0) coordinate(J3)
-					to [vR,mirror,invert,/tikz/circuitikz/bipoles/length=1cm] ++(1.75,0) node[ground,rotate=90]{};
-					\node[block,from={$(J3) + (0,-0.25)$ to $(J3) + (2.5,0.25)$},draw=none](M){};
-					\draw ($(J3) + (0,-0.25)$) rectangle ($(J3) + (2.5,0.25)$);
-					\draw ($(J3) + (1.25,-0.5)$) node[]{Modulator};
-					\draw[dashed,-{Latex[length=2mm]}] (R.east) -- ++(0.75,0);
-					\draw[-{Latex[length=2mm]}] (D.east) -- ++(0.75,0);
-					\draw[{Latex[length=2mm]}-] (M.east) -- ++(0.75,0);
-					\node[block,from={$(R.east) + (0.75,-0.25)$ to $(R.east) + (2.875,0.25)$}](P){Power buffer};
-					\node[block,from={$(M.east) + (0.75,-0.25)$ to $(D.east) + (2.875,0.25)$}](S){Digital\\section};
-					\draw[dashed,-{Latex[length=2mm]}] (P.south) to (S.north);
-					\coordinate (F1) at ($(P.south)!0.5!(S.north)$);
-					\coordinate (F2) at ($(D.east)!0.5!(S.west)$);
-					\coordinate (F3) at ($(D.south)!0.5!(M.north)$);
-					\draw[dashed] (F1) to (F1-|D.north);
-					\draw[dashed,-{Latex[length=2mm]}] (F1-|D.north) to (D.north);
-					\draw[dashed] (F1-|F2) to (F2|-F3) to (M|-F3);
-					\draw[dashed,-{Latex[length=2mm]}] (M|-F3) to (M.north);
-				\end{circuitikz}
+				\input{assets/block_diagram.tex}
 			}
@@
 		\setcounter{subfigure}{2}%
-		\subfloat[Scatter model]{
+		\subfloat[Scatter Model]{
 			\resizebox{0.35\columnwidth}{!}{
-				\begin{circuitikz}[transform shape]
-					\tikzstyle{every node}=[font=\Large]
-					\draw (0,0) node[bareantenna](bareantenna){};
-					\draw (bareantenna.west) ++(-1.5,0) node[waves](WI){};
-					\draw (WI.north east) ++(0.25,0) node[font=\Large]{$\vec{E}_{\mathrm{I}}$};
-					\draw (WI.south east) ++(0.25,0) node[font=\Large]{$\vec{H}_{\mathrm{I}}$};
-					\draw (bareantenna.east) ++(0.875,0) node[waves](WR){};
-					\draw (WR.north east) ++(0.35,0) node[font=\Large]{$\vec{E}_m$};
-					\draw (WR.south east) ++(0.35,0) node[font=\Large]{$\vec{H}_m$};
-					\draw (bareantenna)
-					to [R=$Z_{\mathrm{A}}$] ++(0,-1.5) node[rotary switch=4 in 90 wiper 30,anchor=ext center,rotate=270](SW){};
-					\draw (SW.cout 2) node[below=0.1cm,font=\Large]{$m$}
-					to [R=$Z_m$] ++(2,0) node[ground]{};
-				\end{circuitikz}
+				\input{assets/scatter_model.tex}
 			}
@@
 		\setcounter{subfigure}{1}
-		\subfloat[Equivalent circuit]{
-			\resizebox{0.9\columnwidth}{!}{
-				\begin{circuitikz}[transform shape]
-					\tikzstyle{every node}=[font=\Large]
-					\draw (0,0) coordinate(O)
-					to [sV,l=$V_0$] ++(0,1.5)
-					to [L,l=$X_{\mathrm{A}}$] ++(0,1.5)
-					to [R=$R_{\mathrm{A}}$,-*] ++(3,0) coordinate(AM)
-					to [sI,l_=$I_0$,-*] ++(0,-3)
-					to [short] (O);
-					\draw (AM)
-					to [short] ++(0.5,0)
-					to [L,l=$X_m$,-*] ++(3,0) coordinate(M)
-					to [R=$R_m^{\mathrm{S}}$] ++(3,0) coordinate(MH);
-					\draw (M)
-					to [R=$R_m^{\mathrm{P}}$,-*] ++(0,-3);
-					\draw (MH)
-					to [D,-*] ++(1.5,0) coordinate(H)
-					to [C=$X_{\mathrm{H}}$,-*] ++(0,-3);
-					\draw (H)
-					to [short] ++(1.5,0)
-					to [R=$R_{\mathrm{H}}$] ++(0,-3)
-					to [short] (O);
-
-					\draw [blue,dashed] (-1.125,-0.5) rectangle (3.5,4);
-					\draw [yellow,dashed] (4,-0.5) rectangle (9,4);
-					\draw [red,dashed] (9.5,-0.5) rectangle (13.5,4);
-
-					\draw [blue] (1.125,4.25) node[]{Antenna};
-					\draw [yellow] (6.5,4.25) node[]{Modulator};
-					\draw [red] (11.5,4.25) node[]{Harvester + Chip};
-
-					\draw (3.375,2.675) to [short] (3.375,3.175) to [short] (3.25,3.175) to [short,i_=$Z_{\mathrm{A}}$] (3.125,3.175);
-					\draw (4.125,-0.125) to [short] (4.125,0.375) to [short] (4.25,0.375) to [short,i=$Z_m$] (4.375,0.375);
-					\draw (9.625,-0.125) to [short] (9.625,0.375) to [short] (9.75,0.375) to [short,i=$Z_{\mathrm{H}}$] (9.875,0.375);
-				\end{circuitikz}
+		\subfloat[Equivalent Circuit]{
+			\resizebox{0.95\columnwidth}{!}{
+				\input{assets/equivalent_circuit.tex}
 			}
@@
 		% When the \gls{csi} and reflection alphabet $\{\Gamma_1,\ldots,\Gamma_M\}$ are available at the reader, the tag can be successfully decoded based on the received signal.
+
+		\begin{figure}[!t]
+			\centering
+			\subfloat[Reflection State Distribution]{
+				\resizebox{0.95\columnwidth}{!}{
+					\input{assets/reflection_state_distribution.tex}
+				}
+			}
+			\\
+			\subfloat[Time Block Structure]{
+				\resizebox{0.95\columnwidth}{!}{
+					\input{assets/time_block_structure.tex}
+				}
+			}
+			\caption{Reflection state distribution and time block structure of \gls{sr}, \gls{irs}, and Metascatter.
+$T_s$ and $T_c$ denote the primary and backscatter symbol length, respectively.
+Based on \gls{csi}, Metascatter adapts the reflection state distribution to unify data transmission and channel reconfiguration.}
+		\end{figure}
 

### 2022-06-03 src/config/config_txs.m
:sparkles: Add rate region script

@@ -1,0 +1,43 @@
+%% * System
+% % number of transmit antennas
+% nTxs = 4;
+% number of tags
+nTags = 2;
+% number of available states at tags (i.e., modulation order)
+nStates = 2;
+% constellation diagram at tags
+constellation = normalize(qammod(transpose(0 : nStates - 1), nStates), 'norm', Inf);
+% carrier frequency
+frequency = 9e8;
+% amplitude scatter ratio at tags
+scatterRatio = 0.5;
+% backscatter/primary symbol duration ratio
+symbolRatio = 10;
+% average transmit power
+transmitPower = db2pow(6);
+% average noise power
+noisePower = db2pow(-100);
+% antenna gain
+rxGain = db2pow(3);
+% layout and distance
+[directDistance, forwardDistance, backwardDistance] = layout(nTags);
+% path loss exponents
+directExponent = 2.6;
+forwardExponent = 2.4;
+backwardExponent = 2;
+% Ricean factors
+directFactor = 5;
+forwardFactor = 5;
+backwardFactor = 10;
+
+
+%% * Algorithm
+% relative priority of primary link
+weightSet = [0 : 1e-3 : 2e-2, 1];
+% number of weights on rate region boundary
+nWeights = length(weightSet);
+
+
+%% * Variable
+Variable.nTxs = 2 .^ (0 : 3);
+nVariables = length(Variable.nStates);

### 2022-06-03 src/region_txs.m

@@ -1,0 +1,29 @@
+setup; clear; cvx_begin; cvx_end; clc; close all; config_txs;
+
+Result = cell(nVariables, 1);
+% * Evaluate rate region for different number of transmit antennas
+for iVariable = 1 : nVariables
+	% * Select layout
+	nTxs = Variable.nTxs(iVariable);
+
+	% * Generate channels
+	directChannel = rxGain * path_loss(frequency, directDistance, directExponent) * fading_ricean(nTxs, 1, directFactor);
+	cascadedChannel = zeros(nTxs, nTags);
+	for iTag = 1 : nTags
+		cascadedChannel(:, iTag) = rxGain * path_loss(frequency, forwardDistance(iTag), forwardExponent) * fading_ricean(nTxs, 1, forwardFactor) * path_loss(frequency, backwardDistance(iTag), backwardExponent) * fading_ricean(1, 1, backwardFactor);
+	end
+	equivalentChannel = directChannel + sqrt(scatterRatio) * cascadedChannel * transpose(constellation(tuple_tag(repmat(transpose(1 : nStates), [1, nTags]))));
+
+	% * Evaluate rate region
+	rate = zeros(2, nWeights);
+	distribution = zeros(nStates, nTags, nWeights);
+	threshold = zeros(nWeights, nStates ^ nTags + 1);
+	beamforming = zeros(nTxs, nWeights);
+	for iWeight = 1 : nWeights
+		[rate(:, iWeight), distribution(:, :, iWeight), threshold(iWeight, :), beamforming(:, iWeight)] = block_coordinate_descent(nTags, symbolRatio, transmitPower, noisePower, weightSet(iWeight), equivalentChannel, 'Distribution', 'kkt', 'Beamforming', 'pgd', 'Threshold', 'smawk');
+	end
+	Result{iVariable} = struct('rate', rate, 'distribution', distribution, 'threshold', threshold, 'beamforming', beamforming);
+end
+
+directory = strcat('data/', mfilename, '/');
+savedata;

### 2022-06-03 src/pbs/region_states.sh
:balloon: Update pbs scripts

@@ -1,8 +1,6 @@
-#PBS -l walltime=72:00:00,select=1:ncpus=1:ompthreads=1:mem=4gb
+#PBS -l walltime=24:00:00,select=1:ncpus=1:ompthreads=1:mem=4gb
 #PBS -N region_states
 #PBS -J 1-300
-#PBS -e ${PBS_O_WORKDIR}/log/err_${PBS_JOBID}.txt
-#PBS -o ${PBS_O_WORKDIR}/log/out_${PBS_JOBID}.txt
 
 module load matlab/R2021a
 

### 2022-06-03 src/pbs/region_txs.sh

@@ -1,10 +1,10 @@
 #PBS -l walltime=24:00:00,select=1:ncpus=1:ompthreads=1:mem=4gb
-#PBS -N region_tags
+#PBS -N region_txs
 #PBS -J 1-300
 
 module load matlab/R2021a
 
 cd $PBS_O_WORKDIR/..
-matlab -nodesktop -nodisplay -nosplash -singleCompThread < region_tags.m
+matlab -nodesktop -nodisplay -nosplash -singleCompThread < region_txs.m
 
 exit

### 2022-06-06 main.tex
:balloon: Update pbs scripts
:pencil: Update manuscript [in progress]

@@
 	Backscatter allows wireless nodes to harvest energy from, modulate information over, and reconfigure propagation of surrounding radio waves.
-	We uniquely introduce the concept of Metascatter, which adapts the input probability distribution of a finite-state backscatter device based on Channel State Information (CSI), to simultaneously act as parasitic source of Symbiotic Radio (SR) that conveys sensor data, and reflecting element of Intelligent Reflecting Surface (IRS) that assists legacy transmission.
+	% We uniquely introduce the concept of Metascatter, which adapts the input probability distribution of a finite-state backscatter device based on Channel State Information (CSI), to simultaneously act as parasitic source of Symbiotic Radio (SR) that conveys sensor data, and reflecting element of Intelligent Reflecting Surface (IRS) that assists legacy transmission.
+	% We uniquely introduce the concept of Metascatter, which adjusts the input probability distribution of a finite-state backscatter device based on Channel State Information (CSI), to simultaneously act as parasitic source of Symbiotic Radio (SR) that conveys sensor data, and reflecting element of Intelligent Reflecting Surface (IRS) that assists legacy transmission.
+	% We uniquely introduce the concept of Metascatter, which adjusts the input distribution of a finite-state backscatter device based on \gls{csi}, to \emph{simultaneously} encode its own data and assist ambient transmission.
+	% We uniquely introduce the concept of Metascatter, which \emph{simultaneously} encodes own message and assists ambient transmission, using adaptive input probability distribution based on \gls{csi}.
+	We uniquely introduce the concept of Metascatter, which adapts the input distribution of a finite-state backscatter device based on \gls{csi}, to \emph{simultaneously} encode self message and assist ambient transmission.
+	% Compared to existing strategies as modulation on IRS pattern
+	Compared to conventional \gls{irs}-empowered \gls{sr} that considers encoding and beamforming independently (overlay or parallel), Metascatter revisits backscatter principles and bridges parasitic source of \gls{sr} and reflecting element of \gls{irs} as extreme cases.
+
+	% It enables smoother primary-backscatter tradeoff
+
+	integrates \gls{irs} and \gls{sr} from backscatter principles
+
+	% treat backscatter modulation and passive beamforming independently (overlay or distinction), Metascatter
+
+	\gls{irs}-empowered \gls{sr} strategies that embed
+
+	by adaptive input distribution design based on \gls{csi}.
+
+	adjusts the input distribution of a finite-state backscatter device based on \gls{csi}, to \emph{simultaneously} encode its own data and assist ambient transmission.
+
+	% It not only generalizes SR and IRS
+
+	Compared to existing \gls{irs}-empowered \gls{sr},
+
+	A flexible input distribution design
+
+	Based on Channel State Information (CSI), the input distribution can be
+
+	KKT tag input probability distribution for maximizing weighted sum of primary and total backscatter rate
+
 	Using shared spectrum, energy, and infrastructures, fully cognitive networks can be built over Metascatter, and we consider a fundamental scenario where a multi-antenna Access Point (AP) and multiple Metascatter simultaneously transmit to a single-antenna user.
@@
 	For passive tags, $\alpha \ll 1$ is commonly assumed as the majority of the incident wave can be harvested to support tag modules \cite{Thomas2012a}.
+	% ! Use larger alpha in simulation: for high-order QAM, some constellation point may harvests more power than others
 

### 2022-06-06 assets/scatter_model.tex
:paintbrush: Update scatter model plot

@@
+% \begin{circuitikz}[transform shape]
+% 	\tikzstyle{every node}=[font=\Large]
+% 	\draw (0,0) node[bareantenna](bareantenna){};
+% 	\draw (bareantenna.west) ++(-1.5,0) node[waves](WI){};
+% 	\draw (WI.north east) ++(0.25,0) node[font=\Large]{$\vec{E}_{\mathrm{I}}$};
+% 	\draw (WI.south east) ++(0.25,0) node[font=\Large]{$\vec{H}_{\mathrm{I}}$};
+% 	\draw (bareantenna.east) ++(0.875,0) node[waves](WR){};
+% 	\draw (WR.north east) ++(0.35,0) node[font=\Large]{$\vec{E}_m$};
+% 	\draw (WR.south east) ++(0.35,0) node[font=\Large]{$\vec{H}_m$};
+% 	\draw (bareantenna)
+% 	to [R=$Z_{\mathrm{A}}$] ++(0,-1.5) node[rotary switch=4 in 90 wiper 30,anchor=ext center,rotate=270](SW){};
+% 	\draw (SW.cout 2) node[below=0.1cm,font=\Large]{$m$}
+% 	to [R=$Z_m$] ++(2,0) node[ground]{};
+% \end{circuitikz}
+
 \begin{circuitikz}[transform shape]
-	\tikzstyle{every node}=[font=\Large]
+	\tikzstyle{every node}=[font=\large]
 	\draw (0,0) node[bareantenna](bareantenna){};
 	\draw (bareantenna.west) ++(-1.5,0) node[waves](WI){};
-	\draw (WI.north east) ++(0.25,0) node[font=\Large]{$\vec{E}_{\mathrm{I}}$};
-	\draw (WI.south east) ++(0.25,0) node[font=\Large]{$\vec{H}_{\mathrm{I}}$};
+	\draw (WI.north east) ++(0.25,0) node{$\vec{E}_{\mathrm{I}}$};
+	\draw (WI.south east) ++(0.25,0) node{$\vec{H}_{\mathrm{I}}$};
 	\draw (bareantenna.east) ++(0.875,0) node[waves](WR){};
-	\draw (WR.north east) ++(0.35,0) node[font=\Large]{$\vec{E}_m$};
-	\draw (WR.south east) ++(0.35,0) node[font=\Large]{$\vec{H}_m$};
-	\draw (bareantenna)
-	to [R=$Z_{\mathrm{A}}$] ++(0,-1.5) node[rotary switch=4 in 90 wiper 30,anchor=ext center,rotate=270](SW){};
-	\draw (SW.cout 2) node[below=0.1cm,font=\Large]{$m$}
-	to [R=$Z_m$] ++(2,0) node[ground]{};
+	\draw (WR.north east) ++(0.35,0) node{$\vec{E}_m$};
+	\draw (WR.south east) ++(0.35,0) node{$\vec{H}_m$};
+	\draw (bareantenna) to ++(0,-1.5) to [generic,l=$Z_{\mathrm{A}}$,/tikz/circuitikz/bipoles/length=0.75cm] ++(3.5,0) node[rotary switch=4 in 90 wiper 30,anchor=ext center,rotate=0](SW){};
+	\draw (SW.cout 1) to ++(0.625,+0.5) to [generic,/tikz/circuitikz/bipoles/length=0.75cm] ++(3,0) coordinate(E1);
+	\draw (SW.cout 2) node[above right]{$m$} to [generic,l=$Z_m$,/tikz/circuitikz/bipoles/length=0.75cm] ++(3,0) coordinate(E2);
+	\draw (SW.cout 3) to [generic,/tikz/circuitikz/bipoles/length=0.75cm] ++(3,0) coordinate(E3);
+	\draw (SW.cout 4) to ++(0.625,-0.5) to [generic,/tikz/circuitikz/bipoles/length=0.75cm] ++(3,0) coordinate(E4);
+	% \coordinate (E) at ($(E2)! 0.5!(E3)$);
+	\draw (E1) to[short,-*] (E2);
+	\draw (E2) to[short,-*] (E3);
+	% \draw (E2) to[short,-*] (E);
+	% \draw (E) to[short,-*] (E3);
+	\draw (E3) to[short] (E4);
+	\draw (E2) to[short] ++(1,0) node[ground]{};
 \end{circuitikz}

### 2022-06-06 main.tex
:pencil: Update abstract

--- 2022-05-26 main.tex
@@
 \newacronym{pdf}{PDF}{Probability Density Function}
+\newacronym{pgd}{PGD}{Projected Gradient Descent}
 \newacronym{psk}{PSK}{Phase Shift Keying}
@@
 \newacronym{qam}{QAM}{Quadrature Amplitude Modulation}
-\newacronym{rf}{RF}{Radio Frequency}
+\newacronym{rf}{RF}{Radio-Frequency}
 \newacronym{sc}{SC}{Superposition Coding}
@@
 \begin{abstract}
-	Backscatter allows wireless nodes to harvest energy from, modulate information over, and reconfigure propagation of surrounding radio waves.
-	We uniquely introduce the concept of Metascatter, which adapts the input probability distribution of a finite-state backscatter device based on Channel State Information (CSI), to simultaneously act as parasitic source of Symbiotic Radio (SR) that conveys sensor data, and reflecting element of Intelligent Reflecting Surface (IRS) that assists legacy transmission.
-	Using shared spectrum, energy, and infrastructures, fully cognitive networks can be built over Metascatter, and we consider a fundamental scenario where a multi-antenna Access Point (AP) and multiple Metascatter simultaneously transmit to a single-antenna user.
-	Since tags involve load switching and the primary and backscatter messages are multiplied (instead of superposed) in the received signal, it is assumed the user employ joint energy detection on all tags, then model their reflection pattern within the equivalent CSI for primary decoding.
-	We characterize the achievable primary-(sum-)backscatter rate region through a joint optimization of transmit beamforming vector at the AP, input probability distribution at the tags, and energy detection regions at the user.
-	A suboptimal solution is provided by the Block Coordinate Descent (BCD) method, where the beamforming, input distribution, and decision thresholds are obtained by Successive Convex Approximation (SCA), Karush–Kuhn–Tucker (KKT), and Dynamic Programming (DP), respectively.
-	Simulation results demonstrate Metascatter can exploit the additional backscatter path to transmit and assist.
+	% Backscatter allows wireless nodes to harvest energy from, modulate information over, and reconfigure propagation of surrounding radio waves.
+	Passive backscatter nodes can harvest energy from, modulate information over, and reconfigure propagation of surrounding radio waves.
+	We uniquely introduce the concept of Metascatter, which adapts the input distribution of a finite-state backscatter tag based on \gls{csi}, to \emph{simultaneously} encode self message and assist legacy transmission while powered by ambient signal.
+	Compared to conventional \gls{irs}-empowered \gls{sr} that performs encoding and beamforming independently (overlay or parallel), Metascatter refines backscatter principles to bridge parasitic source of \gls{sr} and reflecting element of \gls{irs} as extreme cases.
+	Such an integrated distribution design not only yields universal modularity with reduced optimization cost, but also enables a flexible tradeoff between primary and backscatter links using shared spectrum, energy, and infrastructures.
+	To validate its benefits, we consider an application scenario where a multi-antenna \gls{ap} transmits to a single-antenna user surrounded by multiple Metascatters.
+	For simplicity, the user is assumed first decodes all Metascatters jointly by energy detection, then models their contribution within equivalent channel and decodes primary link.
+	We characterize the achievable primary-(sum-)backscatter rate region through a joint optimization of input distribution at the Metascatters, transmit beamforming at the AP, and decision thresholds at the user.
+	The problem is highly non-convex and we propose a suboptimal \gls{bcd} solution, where the input distribution satisfying the \gls{kkt} conditions is evaluated in closed form, the transmit beamforming is updated by \gls{pgd}, and the decision thresholds are optimized by \gls{dp}.
+	Simulation results demonstrate Metascatters can exploit additional backscatter paths to transmit and assist.
+	% the \gls{kkt} input distribution is
+
+	% KKT tag input probability distribution for maximizing weighted sum of primary and total backscatter rate
+
+	% A suboptimal solution is provided by the Block Coordinate Descent (BCD) method, where the beamforming, input distribution, and decision thresholds are obtained by Successive Convex Approximation (SCA), Karush–Kuhn–Tucker (KKT), and Dynamic Programming (DP), respectively.
+	% Simulation results demonstrate Metascatter can exploit the additional backscatter path to transmit and assist.
+	% the user employ joint energy detection on all tags, then model their reflection pattern within the equivalent CSI for primary decoding.
+	% Using shared spectrum, energy, and infrastructures, fully cognitive networks can be built over Metascatter, and we consider a fundamental scenario where a multi-antenna Access Point (AP) and multiple Metascatter simultaneously transmit to a single-antenna user.
+	% Since tags involve load switching and the primary and backscatter messages are multiplied (instead of superposed) in the received signal, it is assumed the user employ joint energy detection on all tags, then model their reflection pattern within the equivalent CSI for primary decoding.
+	% We characterize the achievable primary-(sum-)backscatter rate region through a joint optimization of transmit beamforming vector at the AP, input probability distribution at the tags, and energy detection regions at the user.
+	% A suboptimal solution is provided by the Block Coordinate Descent (BCD) method, where the beamforming, input distribution, and decision thresholds are obtained by Successive Convex Approximation (SCA), Karush–Kuhn–Tucker (KKT), and Dynamic Programming (DP), respectively.
+	% Simulation results demonstrate Metascatter can exploit the additional backscatter path to transmit and assist.
 \end{abstract}
@@
 \begin{section}{Backscatter Principles}
+	% \begin{figure}[!t]
+	% 	\centering
+	% 	\subfloat[Block Diagram]{
+	% 		\resizebox{0.6\columnwidth}{!}{
+	% 			\input{assets/block_diagram.tex}
+	% 		}
+	% 		\label{fi:block_diagram}
+	% 	}
+	% 	\setcounter{subfigure}{2}%
+	% 	\subfloat[Scatter Model]{
+	% 		\resizebox{0.35\columnwidth}{!}{
+	% 			\input{assets/scatter_model.tex}
+	% 		}
+	% 		\label{fi:scatter_model}
+	% 	}
+	% 	\setcounter{subfigure}{1}
+	% 	\subfloat[Equivalent Circuit]{
+	% 		\resizebox{0.95\columnwidth}{!}{
+	% 			\input{assets/equivalent_circuit.tex}
+	% 		}
+	% 		\label{fi:equivalent_circuit}
+	% 	}
+	% 	\caption{Block diagram, equivalent circuit, and scatter model of a typical passive tag.
+The solid and dashed vectors represent signal and energy flows.
+The backscatter antenna behaves as a constant power source, where the voltage $V_0$ and current $I_0$ are introduced by incident electric field $\vec{E}_{\mathrm{I}}$ and magnetic field $\vec{H}_{\mathrm{I}}$ \cite{Huang2021}.}
+	% \end{figure}
+
 	\begin{figure}[!t]
@@
 		\subfloat[Block Diagram]{
-			\resizebox{0.6\columnwidth}{!}{
+			\resizebox{0.8\columnwidth}{!}{
 				\input{assets/block_diagram.tex}
@@
 		}
-		\setcounter{subfigure}{2}%
-		\subfloat[Scatter Model]{
-			\resizebox{0.35\columnwidth}{!}{
-				\input{assets/scatter_model.tex}
-			}
-			\label{fi:scatter_model}
-		}
-		\setcounter{subfigure}{1}
+		\\
 		\subfloat[Equivalent Circuit]{
@@
 			\label{fi:equivalent_circuit}
+		}
+		\\
+		\subfloat[Scatter Model]{
+			\resizebox{0.8\columnwidth}{!}{
+				\input{assets/scatter_model.tex}
+			}
+			\label{fi:scatter_model}
 		}

### 2022-06-07 assets/scatter_model.tex
:paintbrush: Update plots

@@
 	\draw (WR.south east) ++(0.35,0) node{$\vec{H}_m$};
-	\draw (bareantenna) to ++(0,-1.5) to [generic,l=$Z_{\mathrm{A}}$,/tikz/circuitikz/bipoles/length=0.75cm] ++(3.5,0) node[rotary switch=4 in 90 wiper 30,anchor=ext center,rotate=0](SW){};
-	\draw (SW.cout 1) to ++(0.625,+0.5) to [generic,/tikz/circuitikz/bipoles/length=0.75cm] ++(3,0) coordinate(E1);
-	\draw (SW.cout 2) node[above right]{$m$} to [generic,l=$Z_m$,/tikz/circuitikz/bipoles/length=0.75cm] ++(3,0) coordinate(E2);
-	\draw (SW.cout 3) to [generic,/tikz/circuitikz/bipoles/length=0.75cm] ++(3,0) coordinate(E3);
-	\draw (SW.cout 4) to ++(0.625,-0.5) to [generic,/tikz/circuitikz/bipoles/length=0.75cm] ++(3,0) coordinate(E4);
+	\draw (bareantenna) to ++(0,-1.5) to [generic,l=$Z_{\mathrm{A}}$,/tikz/circuitikz/bipoles/length=0.75cm] ++(3,0) node[rotary switch=4 in 90 wiper 30,anchor=ext center,rotate=0](SW){};
+	\draw (SW.cout 1) to ++(0.625,+0.5) to [generic,/tikz/circuitikz/bipoles/length=0.75cm] ++(2.5,0) coordinate(E1);
+	\draw (SW.cout 2) node[above right]{$m$} to [generic,l=$Z_m$,/tikz/circuitikz/bipoles/length=0.75cm] ++(2.5,0) coordinate(E2);
+	\draw (SW.cout 3) to [generic,/tikz/circuitikz/bipoles/length=0.75cm] ++(2.5,0) coordinate(E3);
+	\draw (SW.cout 4) to ++(0.625,-0.5) to [generic,/tikz/circuitikz/bipoles/length=0.75cm] ++(2.5,0) coordinate(E4);
 	% \coordinate (E) at ($(E2)! 0.5!(E3)$);
@@
 	\draw (E3) to[short] (E4);
-	\draw (E2) to[short] ++(1,0) node[ground]{};
+	\draw (E2) to[short] ++(0.5,0) node[ground,rotate=90]{};
 \end{circuitikz}

### 2022-06-07 main.tex
:paintbrush: Update plots

@@
 	To validate its benefits, we consider an application scenario where a multi-antenna \gls{ap} transmits to a single-antenna user surrounded by multiple Metascatters.
-	For simplicity, the user is assumed first decodes all Metascatters jointly by energy detection, then models their contribution within equivalent channel and decodes primary link.
+	For simplicity, the user is assumed first decodes all Metascatters jointly by energy detection, then models their contribution within equivalent channel and decodes the primary link.
 	We characterize the achievable primary-(sum-)backscatter rate region through a joint optimization of input distribution at the Metascatters, transmit beamforming at the AP, and decision thresholds at the user.
 	The problem is highly non-convex and we propose a suboptimal \gls{bcd} solution, where the input distribution satisfying the \gls{kkt} conditions is evaluated in closed form, the transmit beamforming is updated by \gls{pgd}, and the decision thresholds are optimized by \gls{dp}.
-	Simulation results demonstrate Metascatters can exploit additional backscatter paths to transmit and assist.
-	% the \gls{kkt} input distribution is
-
-	% KKT tag input probability distribution for maximizing weighted sum of primary and total backscatter rate
-
-	% A suboptimal solution is provided by the Block Coordinate Descent (BCD) method, where the beamforming, input distribution, and decision thresholds are obtained by Successive Convex Approximation (SCA), Karush–Kuhn–Tucker (KKT), and Dynamic Programming (DP), respectively.
-	% Simulation results demonstrate Metascatter can exploit the additional backscatter path to transmit and assist.
-	% the user employ joint energy detection on all tags, then model their reflection pattern within the equivalent CSI for primary decoding.
-	% Using shared spectrum, energy, and infrastructures, fully cognitive networks can be built over Metascatter, and we consider a fundamental scenario where a multi-antenna Access Point (AP) and multiple Metascatter simultaneously transmit to a single-antenna user.
-	% Since tags involve load switching and the primary and backscatter messages are multiplied (instead of superposed) in the received signal, it is assumed the user employ joint energy detection on all tags, then model their reflection pattern within the equivalent CSI for primary decoding.
-	% We characterize the achievable primary-(sum-)backscatter rate region through a joint optimization of transmit beamforming vector at the AP, input probability distribution at the tags, and energy detection regions at the user.
-	% A suboptimal solution is provided by the Block Coordinate Descent (BCD) method, where the beamforming, input distribution, and decision thresholds are obtained by Successive Convex Approximation (SCA), Karush–Kuhn–Tucker (KKT), and Dynamic Programming (DP), respectively.
-	% Simulation results demonstrate Metascatter can exploit the additional backscatter path to transmit and assist.
+	Simulation results demonstrate Metascatters can exploit additional backscatter paths to coordinate transmit and assist via smart input design.
 \end{abstract}

### 2022-06-08 assets/trend_distribution.tex
:bento: Update assets

% This file was created by matlab2tikz.
%
%The latest updates can be retrieved from
%  http://www.mathworks.com/matlabcentral/fileexchange/22022-matlab2tikz-matlab2tikz
%where you can also make suggestions and rate matlab2tikz.
%
\definecolor{mycolor1}{rgb}{0.00000,0.44706,0.74118}%
\definecolor{mycolor2}{rgb}{0.85098,0.32549,0.09804}%
\definecolor{mycolor3}{rgb}{0.92941,0.69412,0.12549}%
\definecolor{mycolor4}{rgb}{0.49412,0.18431,0.55686}%
\definecolor{mycolor5}{rgb}{0.46667,0.67451,0.18824}%
%
\begin{tikzpicture}

\begin{axis}[%
width=4.036in,
height=3.396in,
at={(0.677in,0.458in)},
scale only axis,
xmin=1,
xmax=4,
xtick={1, 2, 3, 4},
xlabel style={font=\color{white!15!black}},
xlabel={Reflection State},
ymin=0,
ymax=1,
ylabel style={font=\color{white!15!black}},
ylabel={Probability Distribution},
axis background/.style={fill=white},
xminorgrids,
yminorgrids,
legend style={legend cell align=left, align=left, draw=white!15!black},
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
]
\addplot [color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}]
  table[row sep=crcr]{%
1	0.249999735242584\\
2	0.250000264588401\\
3	0.250000265053761\\
4	0.249999735115254\\
};
\addlegendentry{$\rho =0$}

\addplot [color=mycolor2, dashed, line width=2.0pt, mark=+, mark options={solid, mycolor2}]
  table[row sep=crcr]{%
1	0.295743068427155\\
2	0.375240201334651\\
3	0.156312315031268\\
4	0.172704415206926\\
};
\addlegendentry{$\rho =0.002$}

\addplot [color=mycolor3, dotted, line width=2.0pt, mark=square, mark options={solid, mycolor3}]
  table[row sep=crcr]{%
1	0.261901350518658\\
2	0.712510408293707\\
3	0.00842749500731859\\
4	0.0171607461803161\\
};
\addlegendentry{$\rho =0.005$}

\addplot [color=mycolor4, dashdotted, line width=2.0pt, mark=x, mark options={solid, mycolor4}]
  table[row sep=crcr]{%
1	0.139913707035647\\
2	0.859278410930712\\
3	0.000142053828609263\\
4	0.000665828205031897\\
};
\addlegendentry{$\rho =0.01$}

\addplot [color=mycolor5, line width=2.0pt, mark=triangle, mark options={solid, mycolor5}]
  table[row sep=crcr]{%
1	1.29237706072384e-05\\
2	0.999987076229393\\
3	4.46101240540389e-26\\
4	3.49723978579285e-21\\
};
\addlegendentry{$\rho =1$}

\end{axis}
\end{tikzpicture}%

### 2022-06-18 assets/distribution_weight.tex
:bento: Update assets

--- 2022-06-08 assets/trend_distribution.tex
@@
   table[row sep=crcr]{%
-1	0.249999735242584\\
-2	0.250000264588401\\
-3	0.250000265053761\\
-4	0.249999735115254\\
+1	0.249999734945382\\
+2	0.250000264528953\\
+3	0.25000026543652\\
+4	0.249999735089145\\
 };
@@
   table[row sep=crcr]{%
-1	0.295743068427155\\
-2	0.375240201334651\\
-3	0.156312315031268\\
-4	0.172704415206926\\
+1	0.29621586579285\\
+2	0.376168737406121\\
+3	0.155469818621155\\
+4	0.172145578179874\\
 };
-\addlegendentry{$\rho =0.002$}
+\addlegendentry{$\rho =0.02$}
 
@@
   table[row sep=crcr]{%
-1	0.261901350518658\\
-2	0.712510408293707\\
-3	0.00842749500731859\\
-4	0.0171607461803161\\
+1	0.262448276431783\\
+2	0.712350409003269\\
+3	0.00824022832841558\\
+4	0.0169610862365327\\
 };
-\addlegendentry{$\rho =0.005$}
+\addlegendentry{$\rho =0.05$}
 
@@
   table[row sep=crcr]{%
-1	0.139913707035647\\
-2	0.859278410930712\\
-3	0.000142053828609263\\
-4	0.000665828205031897\\
+1	0.140066723576523\\
+2	0.859156695957714\\
+3	0.000133936954753823\\
+4	0.000642643511009231\\
 };
-\addlegendentry{$\rho =0.01$}
+\addlegendentry{$\rho =0.1$}
 
@@
   table[row sep=crcr]{%
-1	1.29237706072384e-05\\
-2	0.999987076229393\\
-3	4.46101240540389e-26\\
-4	3.49723978579285e-21\\
+1	0.00129716398391274\\
+2	0.998702836015253\\
+3	1.07370451326091e-15\\
+4	8.33074594560992e-13\\
 };

### 2022-06-21 src/plot/plot_bins.m
:paintbrush: Update plot functions

@@ -17,17 +17,17 @@ end
 save(strcat('../data/region_', erase(mfilename, 'plot_')));
 
 %% * Draw primary-(sum-)backscatter rate regions
-figure('Name', 'Average Primary-(Sum-)Backscatter Rate Region vs Number of Metascatters', 'Position', [0, 0, 500, 400]);
+figure('Name', 'Average Primary-(Sum-)Backscatter Rate Region vs Number of Output Quantization Bits', 'Position', [0, 0, 500, 400]);
 object = gobjects(nVariables, 1);
 hold all;
 for iVariable = 1 : nVariables
-	nTags = Variable(iVariable).nTags;
-	object(iVariable) = plot(region{iVariable}(1, :), 1e3 * region{iVariable}(2, :), 'DisplayName', strcat('$K = ', num2str(nTags), '$'));
+	nBins = Variable(iVariable).nBins;
+	object(iVariable) = plot(region{iVariable}(1, :), 1e3 * region{iVariable}(2, :), 'DisplayName', strcat('$B = ', num2str(log2(nBins)), '$'));
 end
-hold off; legend('Location', 'nw'); grid on; box on; axis tight;
+hold off; legend('Location', 'sw'); grid on; box on; axis tight;
 xlabel('Primary Rate [nats/s/Hz]');
 ylabel('(Sum-)Backscatte Rate [$\mu$ nats/backscatter symbol duration]');
-xlim([6.5, Inf])
+xlim([6.5, inf]);
 style_plot(object);
 savefig(strcat('figures/region_', erase(mfilename, 'plot_')));
 matlab2tikz(strcat('../../assets/region_', erase(mfilename, 'plot_'), '.tex'), 'extraaxisoptions', ['title style={font=\huge}, ' 'label style={font=\huge}, ' 'ticklabel style={font=\LARGE}, ' 'legend style={font=\LARGE}']);

### 2022-06-21 src/plot/plot_coverage.m

@@ -17,17 +17,17 @@ end
 save(strcat('../data/region_', erase(mfilename, 'plot_')));
 
 %% * Draw primary-(sum-)backscatter rate regions
-figure('Name', 'Average Primary-(Sum-)Backscatter Rate Region vs Number of Metascatters', 'Position', [0, 0, 500, 400]);
+figure('Name', 'Average Primary-(Sum-)Backscatter Rate Region vs Maximum Tag-User Distance', 'Position', [0, 0, 500, 400]);
 object = gobjects(nVariables, 1);
 hold all;
 for iVariable = 1 : nVariables
-	nTags = Variable(iVariable).nTags;
-	object(iVariable) = plot(region{iVariable}(1, :), 1e3 * region{iVariable}(2, :), 'DisplayName', strcat('$K = ', num2str(nTags), '$'));
+	coverage = Variable(iVariable).coverage;
+	object(iVariable) = plot(region{iVariable}(1, :), 1e3 * region{iVariable}(2, :), 'DisplayName', strcat('$r = ', num2str(coverage), '$'));
 end
 hold off; legend('Location', 'nw'); grid on; box on; axis tight;
 xlabel('Primary Rate [nats/s/Hz]');
 ylabel('(Sum-)Backscatte Rate [$\mu$ nats/backscatter symbol duration]');
-xlim([6.5, Inf])
+xlim([6, Inf])
 style_plot(object);
 savefig(strcat('figures/region_', erase(mfilename, 'plot_')));
 matlab2tikz(strcat('../../assets/region_', erase(mfilename, 'plot_'), '.tex'), 'extraaxisoptions', ['title style={font=\huge}, ' 'label style={font=\huge}, ' 'ticklabel style={font=\LARGE}, ' 'legend style={font=\LARGE}']);

### 2022-06-21 src/plot/plot_distribution.m

@@ -26,7 +26,7 @@ end
 hold off; legend({'Exhaustion', 'KKT', 'Cooperation', 'Marginalization', 'Decomposition', 'Randomization'}, 'Location', 'sw'); grid on; box on; axis tight;
 xlabel('Primary Rate [nats/s/Hz]');
 ylabel('(Sum-)Backscatte Rate [$\mu$ nats/backscatter symbol duration]');
-xlim([1.3, inf]);
+xlim([6.5, inf]);
 style_plot(object);
 savefig(strcat('figures/region_', erase(mfilename, 'plot_')));
 matlab2tikz(strcat('../../assets/region_', erase(mfilename, 'plot_'), '.tex'), 'extraaxisoptions', ['title style={font=\huge}, ' 'label style={font=\huge}, ' 'ticklabel style={font=\LARGE}, ' 'legend style={font=\LARGE}']);

### 2022-06-21 src/plot/plot_duration.m

@@ -27,7 +27,7 @@ end
 hold off; legend('Location', 'sw'); grid on; box on; axis tight;
 xlabel('Primary Rate [nats/s/Hz]');
 ylabel('(Sum-)Backscatte Rate [$\mu$ nats/primary symbol duration]');
-xlim([1.3, inf]);
+xlim([6.5, inf]);
 style_plot(object);
 savefig(strcat('figures/region_', erase(mfilename, 'plot_')));
 matlab2tikz(strcat('../../assets/region_', erase(mfilename, 'plot_'), '.tex'), 'extraaxisoptions', ['title style={font=\huge}, ' 'label style={font=\huge}, ' 'ticklabel style={font=\LARGE}, ' 'legend style={font=\LARGE}']);

### 2022-06-21 src/plot/plot_frequency.m

@@ -17,17 +17,18 @@ end
 save(strcat('../data/region_', erase(mfilename, 'plot_')));
 
 %% * Draw primary-(sum-)backscatter rate regions
-figure('Name', 'Average Primary-(Sum-)Backscatter Rate Region vs Number of Metascatters', 'Position', [0, 0, 500, 400]);
+figure('Name', 'Average Primary-(Sum-)Backscatter Rate Region vs Carrier Frequency', 'Position', [0, 0, 500, 400]);
 object = gobjects(nVariables, 1);
 hold all;
 for iVariable = 1 : nVariables
-	nTags = Variable(iVariable).nTags;
-	object(iVariable) = plot(region{iVariable}(1, :), 1e3 * region{iVariable}(2, :), 'DisplayName', strcat('$K = ', num2str(nTags), '$'));
+	frequency = Variable(iVariable).frequency;
+	object(iVariable) = plot(region{iVariable}(1, :), region{iVariable}(2, :), 'DisplayName', strcat('$f = ', num2str(frequency / 1e6), '$ MHz'));
 end
-hold off; legend('Location', 'nw'); grid on; box on; axis tight;
+hold off; legend; grid on; box on; axis tight;
+set(gca, 'YScale', 'log');
 xlabel('Primary Rate [nats/s/Hz]');
 ylabel('(Sum-)Backscatte Rate [$\mu$ nats/backscatter symbol duration]');
-xlim([6.5, Inf])
+% xlim([0.9, Inf]);
 style_plot(object);
 savefig(strcat('figures/region_', erase(mfilename, 'plot_')));
 matlab2tikz(strcat('../../assets/region_', erase(mfilename, 'plot_'), '.tex'), 'extraaxisoptions', ['title style={font=\huge}, ' 'label style={font=\huge}, ' 'ticklabel style={font=\LARGE}, ' 'legend style={font=\LARGE}']);

### 2022-06-21 src/plot/plot_noise.m

@@ -17,17 +17,17 @@ end
 save(strcat('../data/region_', erase(mfilename, 'plot_')));
 
 %% * Draw primary-(sum-)backscatter rate regions
-figure('Name', 'Average Primary-(Sum-)Backscatter Rate Region vs Number of Metascatters', 'Position', [0, 0, 500, 400]);
+figure('Name', 'Average Primary-(Sum-)Backscatter Rate Region vs Average Noise Power', 'Position', [0, 0, 500, 400]);
 object = gobjects(nVariables, 1);
 hold all;
 for iVariable = 1 : nVariables
-	nTags = Variable(iVariable).nTags;
-	object(iVariable) = plot(region{iVariable}(1, :), 1e3 * region{iVariable}(2, :), 'DisplayName', strcat('$K = ', num2str(nTags), '$'));
+	noisePower = Variable(iVariable).noisePower;
+	object(iVariable) = plot(region{iVariable}(1, :), 1e3 * region{iVariable}(2, :), 'DisplayName', strcat('$\sigma_n^2 = ', num2str(pow2db(noisePower) + 30), '$ dBm'));
 end
-hold off; legend('Location', 'nw'); grid on; box on; axis tight;
+hold off; legend('Location', 'se'); grid on; box on; axis tight;
 xlabel('Primary Rate [nats/s/Hz]');
 ylabel('(Sum-)Backscatte Rate [$\mu$ nats/backscatter symbol duration]');
-xlim([6.5, Inf])
+% xlim([.3, inf]);
 style_plot(object);
 savefig(strcat('figures/region_', erase(mfilename, 'plot_')));
 matlab2tikz(strcat('../../assets/region_', erase(mfilename, 'plot_'), '.tex'), 'extraaxisoptions', ['title style={font=\huge}, ' 'label style={font=\huge}, ' 'ticklabel style={font=\LARGE}, ' 'legend style={font=\LARGE}']);

### 2022-06-21 src/plot/plot_scatter.m

@@ -17,17 +17,17 @@ end
 save(strcat('../data/region_', erase(mfilename, 'plot_')));
 
 %% * Draw primary-(sum-)backscatter rate regions
-figure('Name', 'Average Primary-(Sum-)Backscatter Rate Region vs Number of Metascatters', 'Position', [0, 0, 500, 400]);
+figure('Name', 'Average Primary-(Sum-)Backscatter Rate Region vs Tag Scatter Ratio', 'Position', [0, 0, 500, 400]);
 object = gobjects(nVariables, 1);
 hold all;
 for iVariable = 1 : nVariables
-	nTags = Variable(iVariable).nTags;
-	object(iVariable) = plot(region{iVariable}(1, :), 1e3 * region{iVariable}(2, :), 'DisplayName', strcat('$K = ', num2str(nTags), '$'));
+	scatterRatio = Variable(iVariable).scatterRatio;
+	object(iVariable) = plot(region{iVariable}(1, :), 1e3 * region{iVariable}(2, :), 'DisplayName', strcat('$\alpha = ', num2str(scatterRatio), '$'));
 end
-hold off; legend('Location', 'nw'); grid on; box on; axis tight;
+hold off; legend; grid on; box on; axis tight;
 xlabel('Primary Rate [nats/s/Hz]');
 ylabel('(Sum-)Backscatte Rate [$\mu$ nats/backscatter symbol duration]');
-xlim([6.5, Inf])
+xlim([6.5, inf]);
 style_plot(object);
 savefig(strcat('figures/region_', erase(mfilename, 'plot_')));
 matlab2tikz(strcat('../../assets/region_', erase(mfilename, 'plot_'), '.tex'), 'extraaxisoptions', ['title style={font=\huge}, ' 'label style={font=\huge}, ' 'ticklabel style={font=\LARGE}, ' 'legend style={font=\LARGE}']);

### 2022-06-21 src/plot/plot_states.m

@@ -21,12 +21,13 @@ figure('Name', 'Average Primary-(Sum-)Backscatter Rate Region vs Number of Refle
 object = gobjects(nVariables, 1);
 hold all;
 for iVariable = 1 : nVariables
-	object(iVariable) = plot(region{iVariable}(1, :), 1e3 * region{iVariable}(2, :), 'DisplayName', strcat('$M = ', num2str(Variable(iVariable).nStates), '$'));
+	nStates = Variable(iVariable).nStates;
+	object(iVariable) = plot(region{iVariable}(1, :), 1e3 * region{iVariable}(2, :), 'DisplayName', strcat('$M = ', num2str(nStates), '$'));
 end
-hold off; legend('Location', 'sw'); grid on; box on; axis tight;
+hold off; legend('Location', 'ne'); grid on; box on; axis tight;
 xlabel('Primary Rate [nats/s/Hz]');
 ylabel('(Sum-)Backscatte Rate [$\mu$ nats/backscatter symbol duration]');
-xlim([1.3, Inf]);
+xlim([6.5, Inf]);
 style_plot(object);
 savefig(strcat('figures/region_', erase(mfilename, 'plot_')));
 matlab2tikz(strcat('../../assets/region_', erase(mfilename, 'plot_'), '.tex'), 'extraaxisoptions', ['title style={font=\huge}, ' 'label style={font=\huge}, ' 'ticklabel style={font=\LARGE}, ' 'legend style={font=\LARGE}']);

### 2022-06-21 src/plot/plot_threshold.m

@@ -26,7 +26,7 @@ end
 hold off; legend({'SMAWK', 'DP', 'Bisection', 'ML'}, 'Location', 'sw'); grid on; box on; axis tight;
 xlabel('Primary Rate [nats/s/Hz]');
 ylabel('(Sum-)Backscatte Rate [$\mu$ nats/backscatter symbol duration]');
-xlim([1.3, inf]);
+xlim([6.5, inf]);
 style_plot(object);
 savefig(strcat('figures/region_', erase(mfilename, 'plot_')));
 matlab2tikz(strcat('../../assets/region_', erase(mfilename, 'plot_'), '.tex'), 'extraaxisoptions', ['title style={font=\huge}, ' 'label style={font=\huge}, ' 'ticklabel style={font=\LARGE}, ' 'legend style={font=\LARGE}']);

### 2022-06-21 src/plot/plot_txs.m

@@ -21,12 +21,13 @@ figure('Name', 'Average Primary-(Sum-)Backscatter Rate Region vs Number of Trans
 object = gobjects(nVariables, 1);
 hold all;
 for iVariable = 1 : nVariables
-	object(iVariable) = plot(region{iVariable}(1, :), 1e3 * region{iVariable}(2, :), 'DisplayName', strcat('$Q = ', num2str(Variable(iVariable).nTxs), '$'));
+	nTxs = Variable(iVariable).nTxs;
+	object(iVariable) = plot(region{iVariable}(1, :), 1e3 * region{iVariable}(2, :), 'DisplayName', strcat('$Q = ', num2str(nTxs), '$'));
 end
-hold off; legend; grid on; box on; axis tight;
+hold off; legend('Location', 'nw'); grid on; box on; axis tight;
 xlabel('Primary Rate [nats/s/Hz]');
 ylabel('(Sum-)Backscatte Rate [$\mu$ nats/backscatter symbol duration]');
-xlim([0.9, Inf]);
+xlim([5.5, Inf]);
 style_plot(object);
 savefig(strcat('figures/region_', erase(mfilename, 'plot_')));
 matlab2tikz(strcat('../../assets/region_', erase(mfilename, 'plot_'), '.tex'), 'extraaxisoptions', ['title style={font=\huge}, ' 'label style={font=\huge}, ' 'ticklabel style={font=\LARGE}, ' 'legend style={font=\LARGE}']);

### 2022-06-21 src/plot/plot_weights.m

@@ -4,11 +4,12 @@ clear; run('../setup'); run(strcat('config_', erase(mfilename, 'plot_'))); clc; 
 distribution = horzcat(load(strcat('../data/distribution_', erase(mfilename, 'plot_')), 'Result').Result.distribution);
 
 %% * Draw reflection state distributions
-figure('Name', 'Reflection State Distribution vs Weight', 'Position', [0, 0, 500, 400]);
+figure('Name', 'Tag Input Distribution vs Weight', 'Position', [0, 0, 500, 400]);
 object = gobjects(nWeights, 1);
 hold all;
 for iWeight = 1 : nWeights
-	object(iWeight) = plot(distribution(:, iWeight), 'DisplayName', strcat('$\rho = ', num2str(weightSet(iWeight)), '$'));
+	weight = weightSet(iWeight);
+	object(iWeight) = plot(distribution(:, iWeight), 'DisplayName', strcat('$\rho = ', num2str(weight), '$'));
 end
 hold off; legend; grid minor; box on;
 xlabel('Reflection State');

### 2022-06-21 assets/distribution_weights.tex
:bento: Update assets

--- 2022-06-18 assets/distribution_weight.tex
@@
   table[row sep=crcr]{%
-1	0.249999734945382\\
-2	0.250000264528953\\
-3	0.25000026543652\\
-4	0.249999735089145\\
+1	2.62331519807269e-06\\
+2	0.999997376684802\\
+3	4.89949641833056e-30\\
+4	2.6174774451771e-24\\
+};
+\addlegendentry{$\rho =1$}
+
+\addplot [color=mycolor2, dashed, line width=2.0pt, mark=+, mark options={solid, mycolor2}]
+  table[row sep=crcr]{%
+1	9.21083675347438e-06\\
+2	0.812542727242104\\
+3	0.187445044005617\\
+4	3.01791552545155e-06\\
+};
+\addlegendentry{$\rho =0.15$}
+
+\addplot [color=mycolor3, dotted, line width=2.0pt, mark=square, mark options={solid, mycolor3}]
+  table[row sep=crcr]{%
+1	1.56711271328569e-05\\
+2	0.695664383940126\\
+3	0.304312342609931\\
+4	7.60232280996882e-06\\
+};
+\addlegendentry{$\rho =0.1$}
+
+\addplot [color=mycolor4, dashdotted, line width=2.0pt, mark=x, mark options={solid, mycolor4}]
+  table[row sep=crcr]{%
+1	1.79207354228568e-05\\
+2	0.591606048367841\\
+3	0.408364572353122\\
+4	1.14585436146039e-05\\
+};
+\addlegendentry{$\rho =0.05$}
+
+\addplot [color=mycolor5, line width=2.0pt, mark=triangle, mark options={solid, mycolor5}]
+  table[row sep=crcr]{%
+1	2.61368383798461e-05\\
+2	0.497964372118738\\
+3	0.501988384568931\\
+4	2.11064739508265e-05\\
 };
@@
 
-\addplot [color=mycolor2, dashed, line width=2.0pt, mark=+, mark options={solid, mycolor2}]
-  table[row sep=crcr]{%
-1	0.29621586579285\\
-2	0.376168737406121\\
-3	0.155469818621155\\
-4	0.172145578179874\\
-};
-\addlegendentry{$\rho =0.02$}
-
-\addplot [color=mycolor3, dotted, line width=2.0pt, mark=square, mark options={solid, mycolor3}]
-  table[row sep=crcr]{%
-1	0.262448276431783\\
-2	0.712350409003269\\
-3	0.00824022832841558\\
-4	0.0169610862365327\\
-};
-\addlegendentry{$\rho =0.05$}
-
-\addplot [color=mycolor4, dashdotted, line width=2.0pt, mark=x, mark options={solid, mycolor4}]
-  table[row sep=crcr]{%
-1	0.140066723576523\\
-2	0.859156695957714\\
-3	0.000133936954753823\\
-4	0.000642643511009231\\
-};
-\addlegendentry{$\rho =0.1$}
-
-\addplot [color=mycolor5, line width=2.0pt, mark=triangle, mark options={solid, mycolor5}]
-  table[row sep=crcr]{%
-1	0.00129716398391274\\
-2	0.998702836015253\\
-3	1.07370451326091e-15\\
-4	8.33074594560992e-13\\
-};
-\addlegendentry{$\rho =1$}
-
 \end{axis}

### 2022-06-22 src/plot/plot_bins.m
:paintbrush: Update plot functions

@@ -9,7 +9,7 @@ region = cell(nVariables, 1);
 for iVariable = 1 : nVariables
 	rate = zeros(2, nWeights + 3);
 	for iWeight = 1 : nWeights
-		rate(:, iWeight) = mean(cat(2, Result(iVariable, iWeight, :).rate), 2);
+		rate(:, iWeight) = mean(cat(2, Result(iVariable, iWeight, :).rate), 2, 'omitnan');
 	end
 	[rate(1, nWeights + 1), rate(2, nWeights + 2)] = deal(max(rate(1, :)), max(rate(2, :)));
 	region{iVariable} = rate(:, convhull(transpose(rate)));
@@ -22,12 +22,12 @@ object = gobjects(nVariables, 1);
 hold all;
 for iVariable = 1 : nVariables
 	nBins = Variable(iVariable).nBins;
-	object(iVariable) = plot(region{iVariable}(1, :), 1e3 * region{iVariable}(2, :), 'DisplayName', strcat('$B = ', num2str(log2(nBins)), '$'));
+	object(iVariable) = plot(region{iVariable}(1, :) / log(2), 1e3 * region{iVariable}(2, :) / log(2), 'DisplayName', strcat('$b = ', num2str(log2(nBins)), '$'));
 end
 hold off; legend('Location', 'sw'); grid on; box on; axis tight;
-xlabel('Primary Rate [nats/s/Hz]');
-ylabel('(Sum-)Backscatte Rate [$\mu$ nats/backscatter symbol duration]');
-xlim([6.5, inf]);
+xlabel('Primary Rate [bits/s/Hz]');
+ylabel('Total Backscatte Rate [$\mu$ bits/backscatter symbol]');
+xlim([9, inf]);
 style_plot(object);
 savefig(strcat('figures/region_', erase(mfilename, 'plot_')));
 matlab2tikz(strcat('../../assets/region_', erase(mfilename, 'plot_'), '.tex'), 'extraaxisoptions', ['title style={font=\huge}, ' 'label style={font=\huge}, ' 'ticklabel style={font=\LARGE}, ' 'legend style={font=\LARGE}']);

### 2022-06-22 src/plot/plot_coverage.m

@@ -9,7 +9,7 @@ region = cell(nVariables, 1);
 for iVariable = 1 : nVariables
 	rate = zeros(2, nWeights + 3);
 	for iWeight = 1 : nWeights
-		rate(:, iWeight) = mean(cat(2, Result(iVariable, iWeight, :).rate), 2);
+		rate(:, iWeight) = mean(cat(2, Result(iVariable, iWeight, :).rate), 2, 'omitnan');
 	end
 	[rate(1, nWeights + 1), rate(2, nWeights + 2)] = deal(max(rate(1, :)), max(rate(2, :)));
 	region{iVariable} = rate(:, convhull(transpose(rate)));
@@ -22,12 +22,12 @@ object = gobjects(nVariables, 1);
 hold all;
 for iVariable = 1 : nVariables
 	coverage = Variable(iVariable).coverage;
-	object(iVariable) = plot(region{iVariable}(1, :), 1e3 * region{iVariable}(2, :), 'DisplayName', strcat('$r = ', num2str(coverage), '$'));
+	object(iVariable) = plot(region{iVariable}(1, :) / log(2), 1e3 * region{iVariable}(2, :) / log(2), 'DisplayName', strcat('$r = ', num2str(coverage), '$'));
 end
-hold off; legend('Location', 'nw'); grid on; box on; axis tight;
-xlabel('Primary Rate [nats/s/Hz]');
-ylabel('(Sum-)Backscatte Rate [$\mu$ nats/backscatter symbol duration]');
-xlim([6, Inf])
+hold off; legend('Location', 'sw'); grid on; box on; axis tight;
+xlabel('Primary Rate [bits/s/Hz]');
+ylabel('Total Backscatte Rate [$\mu$ bits/backscatter symbol]');
+xlim([9, Inf])
 style_plot(object);
 savefig(strcat('figures/region_', erase(mfilename, 'plot_')));
 matlab2tikz(strcat('../../assets/region_', erase(mfilename, 'plot_'), '.tex'), 'extraaxisoptions', ['title style={font=\huge}, ' 'label style={font=\huge}, ' 'ticklabel style={font=\LARGE}, ' 'legend style={font=\LARGE}']);

### 2022-06-22 src/plot/plot_distribution.m

@@ -9,7 +9,7 @@ region = cell(nVariables, 1);
 for iVariable = 1 : nVariables
 	rate = zeros(2, nWeights + 3);
 	for iWeight = 1 : nWeights
-		rate(:, iWeight) = mean(cat(2, Result(iVariable, iWeight, :).rate), 2);
+		rate(:, iWeight) = mean(cat(2, Result(iVariable, iWeight, :).rate), 2, 'omitnan');
 	end
 	[rate(1, nWeights + 1), rate(2, nWeights + 2)] = deal(max(rate(1, :)), max(rate(2, :)));
 	region{iVariable} = rate(:, convhull(transpose(rate)));
@@ -21,12 +21,12 @@ figure('Name', 'Average Primary-(Sum-)Backscatter Rate Region by Different Input
 object = gobjects(nVariables, 1);
 hold all;
 for iVariable = 1 : nVariables
-	object(iVariable) = plot(region{iVariable}(1, :), 1e3 * region{iVariable}(2, :));
+	object(iVariable) = plot(region{iVariable}(1, :) / log(2), 1e3 * region{iVariable}(2, :) / log(2));
 end
 hold off; legend({'Exhaustion', 'KKT', 'Cooperation', 'Marginalization', 'Decomposition', 'Randomization'}, 'Location', 'sw'); grid on; box on; axis tight;
-xlabel('Primary Rate [nats/s/Hz]');
-ylabel('(Sum-)Backscatte Rate [$\mu$ nats/backscatter symbol duration]');
-xlim([6.5, inf]);
+xlabel('Primary Rate [bits/s/Hz]');
+ylabel('Total Backscatte Rate [$\mu$ bits/backscatter symbol]');
+xlim([9, inf]);
 style_plot(object);
 savefig(strcat('figures/region_', erase(mfilename, 'plot_')));
 matlab2tikz(strcat('../../assets/region_', erase(mfilename, 'plot_'), '.tex'), 'extraaxisoptions', ['title style={font=\huge}, ' 'label style={font=\huge}, ' 'ticklabel style={font=\LARGE}, ' 'legend style={font=\LARGE}']);

### 2022-06-22 src/plot/plot_duration.m

@@ -9,7 +9,7 @@ region = cell(nVariables, 1);
 for iVariable = 1 : nVariables
 	rate = zeros(2, nWeights + 3);
 	for iWeight = 1 : nWeights
-		rate(:, iWeight) = mean(cat(2, Result(iVariable, iWeight, :).rate), 2);
+		rate(:, iWeight) = mean(cat(2, Result(iVariable, iWeight, :).rate), 2, 'omitnan');
 	end
 	[rate(1, nWeights + 1), rate(2, nWeights + 2)] = deal(max(rate(1, :)), max(rate(2, :)));
 	region{iVariable} = rate(:, convhull(transpose(rate)));
@@ -22,12 +22,12 @@ object = gobjects(nVariables, 1);
 hold all;
 for iVariable = 1 : nVariables
 	symbolRatio = Variable(iVariable).symbolRatio;
-	object(iVariable) = plot(region{iVariable}(1, :), 1e3 * region{iVariable}(2, :) / symbolRatio, 'DisplayName', strcat('$N = ', num2str(symbolRatio), '$'));
+	object(iVariable) = plot(region{iVariable}(1, :) / log(2), 1e3 * region{iVariable}(2, :) / log(2) / symbolRatio, 'DisplayName', strcat('$N = ', num2str(symbolRatio), '$'));
 end
 hold off; legend('Location', 'sw'); grid on; box on; axis tight;
-xlabel('Primary Rate [nats/s/Hz]');
-ylabel('(Sum-)Backscatte Rate [$\mu$ nats/primary symbol duration]');
-xlim([6.5, inf]);
+xlabel('Primary Rate [bits/s/Hz]');
+ylabel('Total Backscatte Rate [$\mu$ bits/primary symbol]');
+xlim([9, inf]);
 style_plot(object);
 savefig(strcat('figures/region_', erase(mfilename, 'plot_')));
 matlab2tikz(strcat('../../assets/region_', erase(mfilename, 'plot_'), '.tex'), 'extraaxisoptions', ['title style={font=\huge}, ' 'label style={font=\huge}, ' 'ticklabel style={font=\LARGE}, ' 'legend style={font=\LARGE}']);

### 2022-06-22 src/plot/plot_frequency.m

@@ -9,7 +9,7 @@ region = cell(nVariables, 1);
 for iVariable = 1 : nVariables
 	rate = zeros(2, nWeights + 3);
 	for iWeight = 1 : nWeights
-		rate(:, iWeight) = mean(cat(2, Result(iVariable, iWeight, :).rate), 2);
+		rate(:, iWeight) = mean(cat(2, Result(iVariable, iWeight, :).rate), 2, 'omitnan');
 	end
 	[rate(1, nWeights + 1), rate(2, nWeights + 2)] = deal(max(rate(1, :)), max(rate(2, :)));
 	region{iVariable} = rate(:, convhull(transpose(rate)));
@@ -24,11 +24,11 @@ for iVariable = 1 : nVariables
 	frequency = Variable(iVariable).frequency;
 	object(iVariable) = plot(region{iVariable}(1, :), region{iVariable}(2, :), 'DisplayName', strcat('$f = ', num2str(frequency / 1e6), '$ MHz'));
 end
-hold off; legend; grid on; box on; axis tight;
+hold off; legend('Location', 'se'); grid on; box on; axis tight;
 set(gca, 'YScale', 'log');
-xlabel('Primary Rate [nats/s/Hz]');
-ylabel('(Sum-)Backscatte Rate [$\mu$ nats/backscatter symbol duration]');
-% xlim([0.9, Inf]);
+xlabel('Primary Rate [bits/s/Hz]');
+ylabel('Total Backscatte Rate [$\mu$ bits/backscatter symbol]');
+ylim([1e-7, 1e-1]);
 style_plot(object);
 savefig(strcat('figures/region_', erase(mfilename, 'plot_')));
 matlab2tikz(strcat('../../assets/region_', erase(mfilename, 'plot_'), '.tex'), 'extraaxisoptions', ['title style={font=\huge}, ' 'label style={font=\huge}, ' 'ticklabel style={font=\LARGE}, ' 'legend style={font=\LARGE}']);

### 2022-06-22 src/plot/plot_noise.m

@@ -9,7 +9,7 @@ region = cell(nVariables, 1);
 for iVariable = 1 : nVariables
 	rate = zeros(2, nWeights + 3);
 	for iWeight = 1 : nWeights
-		rate(:, iWeight) = mean(cat(2, Result(iVariable, iWeight, :).rate), 2);
+		rate(:, iWeight) = mean(cat(2, Result(iVariable, iWeight, :).rate), 2, 'omitnan');
 	end
 	[rate(1, nWeights + 1), rate(2, nWeights + 2)] = deal(max(rate(1, :)), max(rate(2, :)));
 	region{iVariable} = rate(:, convhull(transpose(rate)));
@@ -22,12 +22,11 @@ object = gobjects(nVariables, 1);
 hold all;
 for iVariable = 1 : nVariables
 	noisePower = Variable(iVariable).noisePower;
-	object(iVariable) = plot(region{iVariable}(1, :), 1e3 * region{iVariable}(2, :), 'DisplayName', strcat('$\sigma_n^2 = ', num2str(pow2db(noisePower) + 30), '$ dBm'));
+	object(iVariable) = plot(region{iVariable}(1, :) / log(2), 1e3 * region{iVariable}(2, :) / log(2), 'DisplayName', strcat('$\sigma_n^2 = ', num2str(pow2db(noisePower) + 30), '$ dBm'));
 end
 hold off; legend('Location', 'se'); grid on; box on; axis tight;
-xlabel('Primary Rate [nats/s/Hz]');
-ylabel('(Sum-)Backscatte Rate [$\mu$ nats/backscatter symbol duration]');
-% xlim([.3, inf]);
+xlabel('Primary Rate [bits/s/Hz]');
+ylabel('Total Backscatte Rate [$\mu$ bits/backscatter symbol]');
 style_plot(object);
 savefig(strcat('figures/region_', erase(mfilename, 'plot_')));
 matlab2tikz(strcat('../../assets/region_', erase(mfilename, 'plot_'), '.tex'), 'extraaxisoptions', ['title style={font=\huge}, ' 'label style={font=\huge}, ' 'ticklabel style={font=\LARGE}, ' 'legend style={font=\LARGE}']);

### 2022-06-22 src/plot/plot_scatter.m

@@ -9,7 +9,7 @@ region = cell(nVariables, 1);
 for iVariable = 1 : nVariables
 	rate = zeros(2, nWeights + 3);
 	for iWeight = 1 : nWeights
-		rate(:, iWeight) = mean(cat(2, Result(iVariable, iWeight, :).rate), 2);
+		rate(:, iWeight) = mean(cat(2, Result(iVariable, iWeight, :).rate), 2, 'omitnan');
 	end
 	[rate(1, nWeights + 1), rate(2, nWeights + 2)] = deal(max(rate(1, :)), max(rate(2, :)));
 	region{iVariable} = rate(:, convhull(transpose(rate)));
@@ -22,12 +22,12 @@ object = gobjects(nVariables, 1);
 hold all;
 for iVariable = 1 : nVariables
 	scatterRatio = Variable(iVariable).scatterRatio;
-	object(iVariable) = plot(region{iVariable}(1, :), 1e3 * region{iVariable}(2, :), 'DisplayName', strcat('$\alpha = ', num2str(scatterRatio), '$'));
+	object(iVariable) = plot(region{iVariable}(1, :) / log(2), 1e3 * region{iVariable}(2, :) / log(2), 'DisplayName', strcat('$\alpha = ', num2str(scatterRatio), '$'));
 end
-hold off; legend; grid on; box on; axis tight;
-xlabel('Primary Rate [nats/s/Hz]');
-ylabel('(Sum-)Backscatte Rate [$\mu$ nats/backscatter symbol duration]');
-xlim([6.5, inf]);
+hold off; legend('Location', 'sw'); grid on; box on; axis tight;
+xlabel('Primary Rate [bits/s/Hz]');
+ylabel('Total Backscatte Rate [$\mu$ bits/backscatter symbol]');
+xlim([9, inf]);
 style_plot(object);
 savefig(strcat('figures/region_', erase(mfilename, 'plot_')));
 matlab2tikz(strcat('../../assets/region_', erase(mfilename, 'plot_'), '.tex'), 'extraaxisoptions', ['title style={font=\huge}, ' 'label style={font=\huge}, ' 'ticklabel style={font=\LARGE}, ' 'legend style={font=\LARGE}']);

### 2022-06-22 src/plot/plot_states.m

@@ -9,7 +9,7 @@ region = cell(nVariables, 1);
 for iVariable = 1 : nVariables
 	rate = zeros(2, nWeights + 3);
 	for iWeight = 1 : nWeights
-		rate(:, iWeight) = mean(cat(2, Result(iVariable, iWeight, :).rate), 2);
+		rate(:, iWeight) = mean(cat(2, Result(iVariable, iWeight, :).rate), 2, 'omitnan');
 	end
 	[rate(1, nWeights + 1), rate(2, nWeights + 2)] = deal(max(rate(1, :)), max(rate(2, :)));
 	region{iVariable} = rate(:, convhull(transpose(rate)));
@@ -22,12 +22,12 @@ object = gobjects(nVariables, 1);
 hold all;
 for iVariable = 1 : nVariables
 	nStates = Variable(iVariable).nStates;
-	object(iVariable) = plot(region{iVariable}(1, :), 1e3 * region{iVariable}(2, :), 'DisplayName', strcat('$M = ', num2str(nStates), '$'));
+	object(iVariable) = plot(region{iVariable}(1, :) / log(2), 1e3 * region{iVariable}(2, :) / log(2), 'DisplayName', strcat('$M = ', num2str(nStates), '$'));
 end
-hold off; legend('Location', 'ne'); grid on; box on; axis tight;
-xlabel('Primary Rate [nats/s/Hz]');
-ylabel('(Sum-)Backscatte Rate [$\mu$ nats/backscatter symbol duration]');
-xlim([6.5, Inf]);
+hold off; legend('Location', 'sw'); grid on; box on; axis tight;
+xlabel('Primary Rate [bits/s/Hz]');
+ylabel('Total Backscatte Rate [$\mu$ bits/backscatter symbol]');
+xlim([9, Inf]);
 style_plot(object);
 savefig(strcat('figures/region_', erase(mfilename, 'plot_')));
 matlab2tikz(strcat('../../assets/region_', erase(mfilename, 'plot_'), '.tex'), 'extraaxisoptions', ['title style={font=\huge}, ' 'label style={font=\huge}, ' 'ticklabel style={font=\LARGE}, ' 'legend style={font=\LARGE}']);

### 2022-06-22 src/plot/plot_tags.m

@@ -9,7 +9,7 @@ region = cell(nVariables, 1);
 for iVariable = 1 : nVariables
 	rate = zeros(2, nWeights + 3);
 	for iWeight = 1 : nWeights
-		rate(:, iWeight) = mean(cat(2, Result(iVariable, iWeight, :).rate), 2);
+		rate(:, iWeight) = mean(cat(2, Result(iVariable, iWeight, :).rate), 2, 'omitnan');
 	end
 	[rate(1, nWeights + 1), rate(2, nWeights + 2)] = deal(max(rate(1, :)), max(rate(2, :)));
 	region{iVariable} = rate(:, convhull(transpose(rate)));
@@ -22,12 +22,12 @@ object = gobjects(nVariables, 1);
 hold all;
 for iVariable = 1 : nVariables
 	nTags = Variable(iVariable).nTags;
-	object(iVariable) = plot(region{iVariable}(1, :), 1e3 * region{iVariable}(2, :), 'DisplayName', strcat('$K = ', num2str(nTags), '$'));
+	object(iVariable) = plot(region{iVariable}(1, :) / log(2), 1e3 * region{iVariable}(2, :) / log(2), 'DisplayName', strcat('$K = ', num2str(nTags), '$'));
 end
-hold off; legend('Location', 'nw'); grid on; box on; axis tight;
-xlabel('Primary Rate [nats/s/Hz]');
-ylabel('(Sum-)Backscatte Rate [$\mu$ nats/backscatter symbol duration]');
-xlim([6.5, Inf])
+hold off; legend('Location', 'se'); grid on; box on; axis tight;
+xlabel('Primary Rate [bits/s/Hz]');
+ylabel('Total Backscatte Rate [$\mu$ bits/backscatter symbol]');
+xlim([9, Inf])
 style_plot(object);
 savefig(strcat('figures/region_', erase(mfilename, 'plot_')));
 matlab2tikz(strcat('../../assets/region_', erase(mfilename, 'plot_'), '.tex'), 'extraaxisoptions', ['title style={font=\huge}, ' 'label style={font=\huge}, ' 'ticklabel style={font=\LARGE}, ' 'legend style={font=\LARGE}']);

### 2022-06-22 src/plot/plot_threshold.m

@@ -9,7 +9,7 @@ region = cell(nVariables, 1);
 for iVariable = 1 : nVariables
 	rate = zeros(2, nWeights + 3);
 	for iWeight = 1 : nWeights
-		rate(:, iWeight) = mean(cat(2, Result(iVariable, iWeight, :).rate), 2);
+		rate(:, iWeight) = mean(cat(2, Result(iVariable, iWeight, :).rate), 2, 'omitnan');
 	end
 	[rate(1, nWeights + 1), rate(2, nWeights + 2)] = deal(max(rate(1, :)), max(rate(2, :)));
 	region{iVariable} = rate(:, convhull(transpose(rate)));
@@ -21,12 +21,12 @@ figure('Name', 'Average Primary-(Sum-)Backscatter Rate Region by Different Decis
 object = gobjects(nVariables, 1);
 hold all;
 for iVariable = 1 : nVariables
-	object(iVariable) = plot(region{iVariable}(1, :), 1e3 * region{iVariable}(2, :));
+	object(iVariable) = plot(region{iVariable}(1, :) / log(2), 1e3 * region{iVariable}(2, :) / log(2));
 end
 hold off; legend({'SMAWK', 'DP', 'Bisection', 'ML'}, 'Location', 'sw'); grid on; box on; axis tight;
-xlabel('Primary Rate [nats/s/Hz]');
-ylabel('(Sum-)Backscatte Rate [$\mu$ nats/backscatter symbol duration]');
-xlim([6.5, inf]);
+xlabel('Primary Rate [bits/s/Hz]');
+ylabel('Total Backscatte Rate [$\mu$ bits/backscatter symbol]');
+xlim([9, inf]);
 style_plot(object);
 savefig(strcat('figures/region_', erase(mfilename, 'plot_')));
 matlab2tikz(strcat('../../assets/region_', erase(mfilename, 'plot_'), '.tex'), 'extraaxisoptions', ['title style={font=\huge}, ' 'label style={font=\huge}, ' 'ticklabel style={font=\LARGE}, ' 'legend style={font=\LARGE}']);

### 2022-06-22 src/plot/plot_txs.m

@@ -9,7 +9,7 @@ region = cell(nVariables, 1);
 for iVariable = 1 : nVariables
 	rate = zeros(2, nWeights + 3);
 	for iWeight = 1 : nWeights
-		rate(:, iWeight) = mean(cat(2, Result(iVariable, iWeight, :).rate), 2);
+		rate(:, iWeight) = mean(cat(2, Result(iVariable, iWeight, :).rate), 2, 'omitnan');
 	end
 	[rate(1, nWeights + 1), rate(2, nWeights + 2)] = deal(max(rate(1, :)), max(rate(2, :)));
 	region{iVariable} = rate(:, convhull(transpose(rate)));
@@ -22,12 +22,12 @@ object = gobjects(nVariables, 1);
 hold all;
 for iVariable = 1 : nVariables
 	nTxs = Variable(iVariable).nTxs;
-	object(iVariable) = plot(region{iVariable}(1, :), 1e3 * region{iVariable}(2, :), 'DisplayName', strcat('$Q = ', num2str(nTxs), '$'));
+	object(iVariable) = plot(region{iVariable}(1, :) / log(2), 1e3 * region{iVariable}(2, :) / log(2), 'DisplayName', strcat('$Q = ', num2str(nTxs), '$'));
 end
-hold off; legend('Location', 'nw'); grid on; box on; axis tight;
-xlabel('Primary Rate [nats/s/Hz]');
-ylabel('(Sum-)Backscatte Rate [$\mu$ nats/backscatter symbol duration]');
-xlim([5.5, Inf]);
+hold off; legend('Location', 'se'); grid on; box on; axis tight;
+xlabel('Primary Rate [bits/s/Hz]');
+ylabel('Total Backscatte Rate [$\mu$ bits/backscatter symbol]');
+xlim([7, Inf]);
 style_plot(object);
 savefig(strcat('figures/region_', erase(mfilename, 'plot_')));
 matlab2tikz(strcat('../../assets/region_', erase(mfilename, 'plot_'), '.tex'), 'extraaxisoptions', ['title style={font=\huge}, ' 'label style={font=\huge}, ' 'ticklabel style={font=\LARGE}, ' 'legend style={font=\LARGE}']);

### 2022-06-24 src/plot/plot_tags.m
:paintbrush: Update plot functions

@@ -24,7 +24,7 @@ for iVariable = 1 : nVariables
 	nTags = Variable(iVariable).nTags;
 	object(iVariable) = plot(region{iVariable}(1, :) / log(2), 1e3 * region{iVariable}(2, :) / log(2), 'DisplayName', strcat('$K = ', num2str(nTags), '$'));
 end
-hold off; legend('Location', 'se'); grid on; box on; axis tight;
+hold off; legend('Location', 'sw'); grid on; box on; axis tight;
 xlabel('Primary Rate [bits/s/Hz]');
 ylabel('Total Backscatte Rate [$\mu$ bits/backscatter symbol]');
 xlim([9, Inf])

### 2022-07-12 main.tex
:pencil: Fix primary rate expression
:pencil: Update manuscript

@@
 \newacronym{bibo}{BIBO}{Binary-Input Binary-Output}
-\newacronym{bpcu}{\si{bpcu}}{bit per channel use}
-\newacronym{bpsphz}{\si{bps/Hz}}{bit per second per Hertz}
+\newacronym{bpcu}{\si{bpcu}}{bits per channel use}
+\newacronym{bpsphz}{\si{bps/Hz}}{bits per second per Hertz}
 \newacronym{cscg}{CSCG}{Circularly Symmetric Complex Gaussian}
@@
 		Yang~Zhao,~\IEEEmembership{Member,~IEEE,}
-		and~Bruno~Clerckx,~\IEEEmembership{Senior~Member,~IEEE}
+		and~Bruno~Clerckx,~\IEEEmembership{Fellow,~IEEE}
 	}
@@
 	% Backscatter allows wireless nodes to harvest energy from, modulate information over, and reconfigure propagation of surrounding radio waves.
-	Passive backscatter nodes can harvest energy from, modulate information over, and reconfigure propagation of surrounding radio waves.
-	We uniquely introduce the concept of Metascatter, which adapts the input distribution of a finite-state backscatter tag based on \gls{csi}, to \emph{simultaneously} encode self message and assist legacy transmission while powered by ambient signal.
-	Compared to conventional \gls{irs}-empowered \gls{sr} that performs encoding and beamforming independently (overlay or parallel), Metascatter refines backscatter principles to bridge parasitic source of \gls{sr} and reflecting element of \gls{irs} as extreme cases.
-	Such an integrated distribution design not only yields universal modularity with reduced optimization cost, but also enables a flexible tradeoff between primary and backscatter links using shared spectrum, energy, and infrastructures.
-	To validate its benefits, we consider an application scenario where a multi-antenna \gls{ap} transmits to a single-antenna user surrounded by multiple Metascatters.
-	For simplicity, the user is assumed first decodes all Metascatters jointly by energy detection, then models their contribution within equivalent channel and decodes the primary link.
-	We characterize the achievable primary-(sum-)backscatter rate region through a joint optimization of input distribution at the Metascatters, transmit beamforming at the AP, and decision thresholds at the user.
-	The problem is highly non-convex and we propose a suboptimal \gls{bcd} solution, where the input distribution satisfying the \gls{kkt} conditions is evaluated in closed form, the transmit beamforming is updated by \gls{pgd}, and the decision thresholds are optimized by \gls{dp}.
-	Simulation results demonstrate Metascatters can exploit additional backscatter paths to coordinate transmit and assist via smart input design.
+	Backscatter nodes can harvest energy from, modulate information over, and reconfigure propagation of ambient signals.
+	% Backscatter nodes can harvest energy from, modulate information over, and reconfigure propagation of surrounding radio waves.
+	We uniquely introduce \emph{Metascatter} that adapts the input distribution of a finite-state passive backscatter node based on \gls{csi}, to \emph{simultaneously} encode self message and assist legacy transmission while powered by surrounding radio-frequency waves.
+	% Compared to conventional \gls{irs}-empowered \gls{sr} that encodes and precodes independently (e.g., overlay or parallel), Metascatter refines backscatter principles to bridge parasitic source of \gls{sr} and reflecting element of \gls{irs} as extreme cases.
+	Compared to existing \gls{irs}-empowered \gls{sr} that encodes and precodes independently using advanced architecture (e.g., overlay or parallel), Metascatter softly bridges and generalizes parasitic source of \gls{sr} and reflecting element of \gls{irs} via smart input design.
+	% Compared to \gls{irs}-empowered \gls{sr} that encodes and precodes independently (e.g., overlay or parallel), Metascatter refines backscatter principles to bridge parasitic source of \gls{sr} and reflecting element of \gls{irs} as extreme cases.
+	% Such an integrated distribution design not only yields universal modularity with reduced optimization cost, but also enables a flexible tradeoff between primary and backscatter links using shared spectrum, energy, and infrastructures.
+	It not only reduces hardware complexity and optimization cost, but also enables a flexible tradeoff between primary and backscatter links using shared spectrum, energy, and infrastructures.
+	Moreover, we consider an application scenario where a multi-antenna \gls{ap} serves a single-antenna user surrounded by multiple Metascatters.
+	For simplicity, it is assumed the user first jointly decodes all backscatter messages based on average received power, then models reflection patterns and backscatter paths within equivalent channel for primary decoding.
+	% Once modulation uncertainty of Metascatters are eliminated, models contributions from additional paths within equivalent channel
+	% decodes all Metascatters jointly by energy detection, then models their contribution within equivalent channel and decodes the primary link.
+	% For simplicity, the user is assumed first decodes all Metascatters jointly by energy detection, then models their contribution within equivalent channel and decodes the primary link.
+	We characterize achievable primary-(total-)backscatter rate regions by jointly design input distribution at Metascatters, active beamforming at AP, and decision regions at user.
+	% A suboptimal \gls{bcd} algorithm was proposed, where the input distribution satisfying the \gls{kkt} conditions is evaluated in closed form, the transmit beamforming is optimized by \gls{pgd}, and the decision thresholds are optimized by \gls{dp}.
+	A suboptimal \gls{bcd} algorithm was proposed, where the \gls{kkt} input distribution is evaluated in closed form, the active beamforming is optimized by \gls{pgd} with backtracking line search, and convex decision regions are refined by \gls{dp}.
+	% the decision regions are restricted as convex then optimized by \gls{dp}.
+	% A suboptimal \gls{bcd} algorithm was proposed, where the \gls{kkt} input distribution is evaluated in closed form, the active beamforming is optimized by \gls{pgd} with backtracking line search, and the decision thresholds are optimized by \gls{dp}.
+	Simulation results demonstrate Metascatters can exploit additional propagation paths to transmit and assist via input design.
 \end{abstract}
@@
 	\IEEEPARstart{B}{ackscatter} is recently re-innovated as a promising approach to support low-power communications and control wireless propagation environments.
-	The concept of \gls{ambc} was first proposed in \cite{Liu2013b}, where each tag harvests energy from and modulates information over ambient \gls{rf} signals by periodically switching between different reflection patterns.
+	% The concept of \gls{ambc} was first proposed in \cite{Liu2013b}, where battery-free communication between passive nodes was established by
+	\gls{ambc} that enables battery-free communication between passive nodes was first proposed in \cite{Liu2013b}, where battery-free communication between passive nodes was established by
+
+	Battery-free communication between passive nodes was first by
+
+	each tag harvests energy from and modulates information over ambient \gls{rf} signals by periodically switching between different reflection patterns.
 	It enables battery-free communication between fully passive nodes, but the backscatter signal strength can be relatively weak and the decoding is subject to strong direct-link interference.
@@
 	On the other hand, it was concluded in \cite{Long2020a} that if the backscatter symbol period is much longer than the primary symbol period, then the non-coherent achievable rate of primary decoding would approach that of the coherent case.
-	The authors also considered the transmit precoder design for weighted sum-rate maximization and transmit power minimization problems.
+	The authors also considered the transmit precoder design for weighted total-rate maximization and transmit power minimization problems.
 	\cite{Zhou2019a} explored how the number of transmit antennas, receive antennas, and symbol period ratio asymptotically influence the ergodic rate of primary and backscatter links.
@@
 
-	\emph{Third,} we characterize the achievable primary-(sum-)backscatter rate region by iteratively optimizing the tag input distribution, the backscatter decision threshold, and the transmit precoder.
+	\emph{Third,} we characterize the achievable primary-(total-)backscatter rate region by iteratively optimizing the tag input distribution, the backscatter decision threshold, and the transmit precoder.
 	For the input design, we propose a numerical method to evaluate the \gls{kkt} solutions by limits of sequences.
@@
 \begin{section}{Backscatter Principles}
-	% \begin{figure}[!t]
-	% 	\centering
-	% 	\subfloat[Block Diagram]{
-	% 		\resizebox{0.6\columnwidth}{!}{
-	% 			\input{assets/block_diagram.tex}
-	% 		}
-	% 		\label{fi:block_diagram}
-	% 	}
-	% 	\setcounter{subfigure}{2}%
-	% 	\subfloat[Scatter Model]{
-	% 		\resizebox{0.35\columnwidth}{!}{
-	% 			\input{assets/scatter_model.tex}
-	% 		}
-	% 		\label{fi:scatter_model}
-	% 	}
-	% 	\setcounter{subfigure}{1}
-	% 	\subfloat[Equivalent Circuit]{
-	% 		\resizebox{0.95\columnwidth}{!}{
-	% 			\input{assets/equivalent_circuit.tex}
-	% 		}
-	% 		\label{fi:equivalent_circuit}
-	% 	}
-	% 	\caption{Block diagram, equivalent circuit, and scatter model of a typical passive tag.
-The solid and dashed vectors represent signal and energy flows.
-The backscatter antenna behaves as a constant power source, where the voltage $V_0$ and current $I_0$ are introduced by incident electric field $\vec{E}_{\mathrm{I}}$ and magnetic field $\vec{H}_{\mathrm{I}}$ \cite{Huang2021}.}
-	% \end{figure}
-
 	\begin{figure}[!t]
@@
 	\end{figure}
-	% In a bistatic backscatter system,
-	% Consider a bistatic backscatter system with an excitation source, multiple passive tags, and a backscatter reader.
 	Passive backscatter devices (a.k.a., tags) harvest energy from and modulate information over surrounding \gls{rf} signal.
@@
 		\begin{equation}
-			I_{\mathrm{P}}(x_{m_{\mathcal{K}}};\boldsymbol{y}) \triangleq N \log_2 \left(1 + \frac{\lvert \boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_w^2}\right),
+			I_{\mathrm{P}}(x_{m_{\mathcal{K}}};\boldsymbol{y}) \triangleq \log_2 \left(1 + \frac{\lvert \boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_w^2}\right),
 			\label{eq:primary_information_function}
@@
 		\begin{equation}
-			I_{\mathrm{P}}(x_{\mathcal{K}};\boldsymbol{y}) = \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) N \log_2 \left(1 + \frac{\lvert \boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_w^2}\right).
+			I_{\mathrm{P}}(x_{\mathcal{K}};\boldsymbol{y}) = \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) \log_2 \left(1 + \frac{\lvert \boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_w^2}\right).
 			\label{eq:primary_mutual_information}
@@
 \begin{section}{Input, Threshold, and Precoder Design}
-	To characterize the achievable primary-(sum-)backscatter rate region of Metascatter, we aim to maximize the weighted sum mutual information with respect to tag input probability distribution $\{\boldsymbol{p}_k\}$, decision threshold vector $\boldsymbol{t}$, and transmit precoder $\boldsymbol{w}$
+	To characterize the achievable primary-(total-)backscatter rate region of Metascatter, we aim to maximize the weighted sum mutual information with respect to tag input probability distribution $\{\boldsymbol{p}_k\}$, decision threshold vector $\boldsymbol{t}$, and transmit precoder $\boldsymbol{w}$
 	\begin{maxi!}
@@
 		which involves the product term $\prod_{k \in \mathcal{K}} P_k(x_{m_k})$ and is non-convex when $K > 1$.
-		Interestingly, the sum-rate optimal input design for general discrete memoryless \gls{mac} remains an open problem, and we instead propose a \gls{kkt} solution to problem \eqref{op:input_probability_distribution}.
+		Interestingly, the total-rate optimal input design for general discrete memoryless \gls{mac} remains an open problem, and we instead propose a \gls{kkt} solution to problem \eqref{op:input_probability_distribution}.
 		\begin{footnote}
-			As pointed out in \cite{Buhler2011}, \gls{kkt} conditions are only necessary for sum-rate optimality and these solutions may end up being saddle points.
+			As pointed out in \cite{Buhler2011}, \gls{kkt} conditions are only necessary for total-rate optimality and these solutions may end up being saddle points.
 		\end{footnote}
@@
 	As such, the threshold that maximizes the total backscatter rate should also maximize the weighted sum rate.
-	Interestingly, this may not be the case because the \gls{smawk} and Bisection threshold designs, both maximizing the total backscatter rate, can be outperformed by the \gls{ml} when it comes to weighted sum primary-(sum-)backscatter rate.
+	Interestingly, this may not be the case because the \gls{smawk} and Bisection threshold designs, both maximizing the total backscatter rate, can be outperformed by the \gls{ml} when it comes to weighted sum primary-(total-)backscatter rate.
 	It may result from a precision issue, but inspires further research on threshold design for Metascatter.
@@
 				J \left( P_{\mathcal{K}}(x_{m_{\mathcal{K}}}),P_{\mathcal{K}}'(x_{m_{\mathcal{K}}}) \right)
-				 & \triangleq \rho \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) N \log_2 \left(1 + \frac{\lvert \boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_w^2}\right)\nonumber                                                                                                                          \\
+				 & \triangleq \rho \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) \log_2 \left(1 + \frac{\lvert \boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_w^2}\right)\nonumber                                                                                                                            \\
 				 & \quad + (1 - \rho) \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) \sum_{m_{\mathcal{K}}'} P(\hat{x}_{m_{\mathcal{K}}'} \mid x_{m_{\mathcal{K}}}) \log \frac{P(\hat{x}_{m_{\mathcal{K}}'} \mid x_{m_{\mathcal{K}}}) P_{\mathcal{K}}'(x_{m_{\mathcal{K}}})}{P'(\hat{x}_{m_{\mathcal{K}}'}) P_{\mathcal{K}}(x_{m_{\mathcal{K}}})}.

### 2022-07-13 main.tex
:pencil: Update manuscript

@@
 \newacronym{bpsphz}{\si{bps/Hz}}{bits per second per Hertz}
+\newacronym{cr}{CR}{Cognitive Radio}
 \newacronym{cscg}{CSCG}{Circularly Symmetric Complex Gaussian}
@@
 \newacronym{ue}{UE}{user}
+\newacronym{wpcn}{WPCN}{Wireless Powered Communication Network}
 
@@
 	% Backscatter nodes can harvest energy from, modulate information over, and reconfigure propagation of surrounding radio waves.
-	We uniquely introduce \emph{Metascatter} that adapts the input distribution of a finite-state passive backscatter node based on \gls{csi}, to \emph{simultaneously} encode self message and assist legacy transmission while powered by surrounding radio-frequency waves.
+	We uniquely introduce \emph{Metascatter} that adapts the input distribution of a finite-state passive backscatter node based on \gls{csi}, to \emph{simultaneously} encode self message and assist legacy transmission while powered by surrounding waves.
 	% Compared to conventional \gls{irs}-empowered \gls{sr} that encodes and precodes independently (e.g., overlay or parallel), Metascatter refines backscatter principles to bridge parasitic source of \gls{sr} and reflecting element of \gls{irs} as extreme cases.
@@
 	% Such an integrated distribution design not only yields universal modularity with reduced optimization cost, but also enables a flexible tradeoff between primary and backscatter links using shared spectrum, energy, and infrastructures.
-	It not only reduces hardware complexity and optimization cost, but also enables a flexible tradeoff between primary and backscatter links using shared spectrum, energy, and infrastructures.
-	Moreover, we consider an application scenario where a multi-antenna \gls{ap} serves a single-antenna user surrounded by multiple Metascatters.
+	This not only reduces hardware complexity and optimization cost, but also enables a flexible tradeoff between primary (legacy) and backscatter links using shared spectrum, energy, and infrastructures.
+	Moreover, we consider a specific scenario where a multi-antenna \gls{ap} serves a single-antenna user surrounded by multiple Metascatters.
 	For simplicity, it is assumed the user first jointly decodes all backscatter messages based on average received power, then models reflection patterns and backscatter paths within equivalent channel for primary decoding.
@@
 	% For simplicity, the user is assumed first decodes all Metascatters jointly by energy detection, then models their contribution within equivalent channel and decodes the primary link.
-	We characterize achievable primary-(total-)backscatter rate regions by jointly design input distribution at Metascatters, active beamforming at AP, and decision regions at user.
+	We characterize the achievable primary-(total-)backscatter rate region by optimizing the input distribution at Metascatters, the active beamforming at the AP, and the decision regions at the user.
 	% A suboptimal \gls{bcd} algorithm was proposed, where the input distribution satisfying the \gls{kkt} conditions is evaluated in closed form, the transmit beamforming is optimized by \gls{pgd}, and the decision thresholds are optimized by \gls{dp}.
-	A suboptimal \gls{bcd} algorithm was proposed, where the \gls{kkt} input distribution is evaluated in closed form, the active beamforming is optimized by \gls{pgd} with backtracking line search, and convex decision regions are refined by \gls{dp}.
+	A suboptimal \gls{bcd} algorithm is proposed, where the \gls{kkt} input distribution is evaluated in closed form, the active beamforming is updated by \gls{pgd}, and the suboptimal convex decision regions are refined by \gls{dp}.
+	% A suboptimal \gls{bcd} algorithm was proposed with the \gls{kkt} input distribution evaluated in closed form, the active beamforming updated by \gls{pgd}, and the decision regions restricted to convex then refined by \gls{dp}.
 	% the decision regions are restricted as convex then optimized by \gls{dp}.
@@
 	\IEEEPARstart{B}{ackscatter} is recently re-innovated as a promising approach to support low-power communications and control wireless propagation environments.
+	% \IEEEPARstart{B}{ackscatter} is re-innovated to support low-power communications and control wireless propagation environments.
+	% \IEEEPARstart{B}{ackscatter} allows wireless nodes to recycle existing .
+	% \IEEEPARstart{B}{ackscatter} allows wireless nodes to communicate without generating carrier.
 	% The concept of \gls{ambc} was first proposed in \cite{Liu2013b}, where battery-free communication between passive nodes was established by
-	\gls{ambc} that enables battery-free communication between passive nodes was first proposed in \cite{Liu2013b}, where battery-free communication between passive nodes was established by
+	\gls{ambc} that enables battery-free communication between interactive nodes was first introduced and prototyped in \cite{Liu2013b}, where devices harvest energy from and modulate information over ambient \gls{rf} signals by switching between reflecting and absorbing states.
+	To combat the strong direct-link interference of \gls{ambc}, \cite{Yang2018d} exploited the repeating structure of \gls{ofdm} symbol and proposed a multi-antenna detector that only requires the backscatter channel strength.
+	% with periodical change of states.
+	% each tag harvests energy from and modulates information over ambient \gls{rf} signals by periodically switching between different reflection patterns.
+	% It enables battery-free communication between fully passive nodes, but the backscatter signal strength can be relatively weak and the decoding is subject to strong direct-link interference.
+	% To solve this, \cite{Yang2018d} exploited the repeating structure of \gls{ofdm} symbol for interference cancellation based on backscatter channel strength.
+	% Using co-located receiver to decode
+	Cooperative \gls{ambc} that decodes primary and backscatter links using co-located receiver was proposed in \cite{Yang2018}, where the authors evaluated the error performance of \gls{ml}, linear, and \gls{sic} detectors for flat fading channels and proposed a low-complexity \gls{ml} detector for frequency-selective fading channels.
+	The concept was then generalized to \gls{sr} in \cite{Liang2020} to ``exploit the benefits and address the drawbacks'' of \gls{cr} and \gls{ambc}.
+	% The concept of \gls{sr} was then proposed in \cite{Liang2020} to exploit
+	% symbiotic radio (SR), is proposed to ex- ploit the benefits and address the drawbacks of cognitive radio (CR) and ambient backscattering communications (AmBC)
+	% When transmit cooperation is also available, cooperative \gls{ambc} is also termed as \gls{sr} \cite{Liang2020}.
+	The authors of \cite{Guo2019b} classified \gls{sr} into commensal, parasitic, and competitive types based on link priority, and derived their instantaneous rates and optimal power allocations.
+	The corresponding outage probabilities were also studied in \cite{Ding2020}.
+	Besides, \cite{Long2020a} concluded that if the backscatter symbol period is sufficiently long, then the non-coherent primary rate would approach its coherent counterpart.
+	The authors thus proposed to decode the primary link under backscatter uncertainty, then perform \gls{sic} and decode the backscatter link.
+	% The authors also considered the transmit precoder design for weighted total-rate maximization and transmit power minimization problems.
+	% \cite{Zhou2019a} explored how the number of transmit antennas, receive antennas, and symbol period ratio asymptotically influence the ergodic rate of primary and backscatter links.
+	\cite{Zhou2019a} explored the impact of transmit antennas, receive antennas, and backscatter symbol period on the ergodic rate of primary and backscatter links.
+	For multi-antenna at all ends, \cite{Wu2021a} optimized transmit beamforming to maximize the backscatter achievable rate under primary rate constraint.
+	However, those paper only considered single backscatter node and backscatter multiple access remains an open issue.
+	In \cite{Xu2021a}, a \gls{noma}-based \gls{sr} was proposed and receive combining was investigated for \gls{sic} order in equivalent channel strength.
+	% \cite{Xu2021a} proposed a \gls{noma}-based \gls{sr} and investigated receive beamforming when \gls{sic} order is determined by equivalent channel strength.
+	% \cite{Xu2021a} proposed a \gls{noma}-based \gls{sr} and studied the receive combiner design when the receiver decodes in the order of equivalent channel strength.
+	% A \gls{tdma}-based \gls{sr} with energy harvesting constraints was also presented in \cite{Yang2021a}, and energy efficiency maximization was considered with respect to transmit power, reflection efficiency, and time allocation design.
+	A \gls{tdma}-based \gls{sr} with energy harvesting constraints was also presented in \cite{Yang2021a}, where transmit power, reflection efficiency, and time allocation was optimized to maximize energy efficiency.
+	% In \cite{Han2021}, random code-assisted backscatter multiple access was combined with \gls{sr}, and the authors evaluated the asymptotic \gls{sinr} performance using random matrix theory.
+	To reduce coordination between passive nodes, \cite{Han2021} proposed a random code-assisted multiple access for \gls{sr} and evaluated the asymptotic \gls{sinr} using random matrix theory.
 
-	Battery-free communication between passive nodes was first by
+	% On the other hand, \gls{irs} has recently emerged as a promising technique to enhance the energy efficiency.
+	% In practice, an \gls{irs} consists of multiple individual sub-wavelength reflecting elements to adjust the amplitude and phase of the incoming signal (i.e., passive beamforming).
+	% Different from relay, backscatter and frequency-selective surface \cite{Anwar2018}, \gls{irs} assists the primary transmission using passive components with much lower energy consumption and thermal noise, but is limited to frequency-dependent reflection.
+	% On the other hand, \gls{irs} consists of numerous sub-wavelength passive elements that alter propagation environment using adaptive backscatter pattern to assist existing networks.
+Extensive research has been devoted to optimizing the reflection coefficient
+	On the other hand, \gls{irs} consists of numerous sub-wavelength passive elements with adaptive amplitudes and/or phases that alter propagation environment to assist existing networks.
+	Extensive research has been devoted to optimizing the phases of \gls{irs} during whole channel block for different metrices, as TODO \cite{Wu2018,Wu2019a,Wu2019}.
+	% In contrast, dynamic passive beamforming that adjusts \gls{irs} within channel block was proposed in \cite{Yang2020} to create diversity for \gls{ofdm} systems.
+	% In contrast, dynamic passive beamforming that adjusts \gls{irs} over finer time slots was proposed in \cite{Yang2020} to create diversity for \gls{ofdm} systems.
+	Besides, dynamic passive beamforming that adjusts \gls{irs} over fine-grained slots within channel coherence time was proposed for \gls{ofdm} systems in \cite{Yang2020}.
 
-	each tag harvests energy from and modulates information over ambient \gls{rf} signals by periodically switching between different reflection patterns.
-	It enables battery-free communication between fully passive nodes, but the backscatter signal strength can be relatively weak and the decoding is subject to strong direct-link interference.
-	To solve this, \cite{Yang2018d} exploited the repeating structure of \gls{ofdm} symbol for interference cancellation based on backscatter channel strength.
-	Cooperative primary-backscatter decoding using co-located receiver, known as cooperative \gls{ambc}, was proposed in \cite{Yang2018}.
-	The authors evaluated the error performance of \gls{ml}, linear, and \gls{sic} detectors for flat fading channels, and proposed a low-complexity \gls{ml} detector for frequency-selective fading channels with ambient \gls{ofdm} carrier.
-	When transmit cooperation is also available, cooperative \gls{ambc} is more commonly known as \gls{sr} \cite{Liang2020}.
-	The authors of \cite{Guo2019b} classified \gls{sr} into commensal, parasitic, and competitive modes based on the relative link priority, then derived their instantaneous achievable rate and optimal power allocation.
-	The outage probability for those modes was later studied in \cite{Ding2020}.
-	On the other hand, it was concluded in \cite{Long2020a} that if the backscatter symbol period is much longer than the primary symbol period, then the non-coherent achievable rate of primary decoding would approach that of the coherent case.
-	The authors also considered the transmit precoder design for weighted total-rate maximization and transmit power minimization problems.
-	\cite{Zhou2019a} explored how the number of transmit antennas, receive antennas, and symbol period ratio asymptotically influence the ergodic rate of primary and backscatter links.
-	With multi-antenna at all ends, \cite{Wu2021a} optimized the transmit precoder to maximize the backscatter achievable rate under primary rate constraint.
-	However, those paper only considered single tag scenario and the optimal tag multiple access scheme remains unknown.
-	\cite{Xu2021a} proposed a \gls{noma}-based \gls{sr} and studied the receive combiner design when the receiver decodes in the order of equivalent channel strength.
-	A \gls{tdma}-based \gls{sr} with energy harvesting constraints was also presented in \cite{Yang2021a}, and energy efficiency maximization was considered with respect to transmit power, reflection efficiency, and time allocation design.
-	In \cite{Han2021}, random code-assisted backscatter multiple access was combined with \gls{sr}, and the authors evaluated the asymptotic \gls{sinr} performance using random matrix theory.
+	The idea was further applied to \gls{wpcn} to strike the
 
-	On the other hand, \gls{irs} has recently emerged as a promising technique to enhance the energy efficiency.
-	In practice, an \gls{irs} consists of multiple individual sub-wavelength reflecting elements to adjust the amplitude and phase of the incoming signal (i.e., passive beamforming).
-	Different from relay, backscatter and frequency-selective surface \cite{Anwar2018}, \gls{irs} assists the primary transmission using passive components with much lower energy consumption and thermal noise, but is limited to frequency-dependent reflection.
+	proactively generate favourable time-varying channels by properly designing the IRS phase-shift vectors over different time slots,
+	which thus enhances the multiuser diversity over time and also allows more flexible resource allocation.
+
+	mic IRS beamforming is actually beneficial for maximizing the throughput
+	of WPCNs
+	% The authors
+	% of [29] considered a novel dynamic passive beamforming for
+	% Orthogonal Frequency-Division Multiplexing (OFDM) systems,
+	% where the reflection coefficient is varied over consequent
+	% time slots to enable flexible resource allocation over timefrequency Resource Blocks (RBs).
+
+	further adjusted the IRS reflection pattern within channel coherence time to mimic multi-beam reflection in a time-division manner
+
 	\cite{Wu2018} proposed an \gls{irs}-assisted \gls{miso} system and jointly optimized the precoder and the phase shifts to minimize the transmit power.

### 2022-07-15 main.tex
:pencil: Update literature review

@@
 \newacronym{ue}{UE}{user}
+\newacronym{wit}{WIT}{Wireless Information Transfer}
 \newacronym{wpcn}{WPCN}{Wireless Powered Communication Network}
+\newacronym{wpt}{WPT}{Wireless Power Transfer}
 
@@
 	% \cite{Zhou2019a} explored how the number of transmit antennas, receive antennas, and symbol period ratio asymptotically influence the ergodic rate of primary and backscatter links.
-	\cite{Zhou2019a} explored the impact of transmit antennas, receive antennas, and backscatter symbol period on the ergodic rate of primary and backscatter links.
-	For multi-antenna at all ends, \cite{Wu2021a} optimized transmit beamforming to maximize the backscatter achievable rate under primary rate constraint.
-	However, those paper only considered single backscatter node and backscatter multiple access remains an open issue.
-	In \cite{Xu2021a}, a \gls{noma}-based \gls{sr} was proposed and receive combining was investigated for \gls{sic} order in equivalent channel strength.
+	% For \gls{sr} with a single-antenna backscatter node,
+	\cite{Zhou2019a} also explored the asymptotic impact of transmit/receive antenna and backscatter symbol period on the ergodic rate of primary and backscatter links.
+	% When multi-antenna is available at the node, \cite{Wu2021a} proposed
+	For a \gls{mimo} \gls{sr} system with a multi-antenna backscatter node, \cite{Wu2021a} proposed a beamforming design to maximize the backscatter rate while guaranteeing the primary performance.
+	% For multi-antenna at all ends, \cite{Wu2021a} optimized transmit beamforming to maximize the backscatter achievable rate under primary rate constraint.
+	% For multi-antenna at all ends, \cite{Wu2021a} optimized transmit beamforming to maximize the backscatter achievable rate under primary rate constraint.
+	% For multi-antenna at all ends, \cite{Wu2021a} optimized transmit beamforming to enlarge the achievable rate region.
+	However, those paper only considered one backscatter node and backscatter multiple access remains an open issue.
+	In \cite{Xu2021a}, a \gls{noma}-based \gls{sr} was proposed and receive combining was investigated when \gls{sic} order follows equivalent channel strength.
 	% \cite{Xu2021a} proposed a \gls{noma}-based \gls{sr} and investigated receive beamforming when \gls{sic} order is determined by equivalent channel strength.
@@
 	% A \gls{tdma}-based \gls{sr} with energy harvesting constraints was also presented in \cite{Yang2021a}, and energy efficiency maximization was considered with respect to transmit power, reflection efficiency, and time allocation design.
-	A \gls{tdma}-based \gls{sr} with energy harvesting constraints was also presented in \cite{Yang2021a}, where transmit power, reflection efficiency, and time allocation was optimized to maximize energy efficiency.
+	A \gls{tdma}-based \gls{sr} with energy harvesting constraints was also presented in \cite{Yang2021a}, where transmit power, reflection efficiency, and time allocation were jointly optimized to maximize energy efficiency.
 	% In \cite{Han2021}, random code-assisted backscatter multiple access was combined with \gls{sr}, and the authors evaluated the asymptotic \gls{sinr} performance using random matrix theory.
@@
 Extensive research has been devoted to optimizing the reflection coefficient
-	On the other hand, \gls{irs} consists of numerous sub-wavelength passive elements with adaptive amplitudes and/or phases that alter propagation environment to assist existing networks.
-	Extensive research has been devoted to optimizing the phases of \gls{irs} during whole channel block for different metrices, as TODO \cite{Wu2018,Wu2019a,Wu2019}.
+	% On the other hand, \gls{irs} consists of numerous sub-wavelength passive elements with adaptive amplitudes and/or phases that alter propagation environment to assist existing networks.
+	On the other hand, \gls{irs} alters propagation environment for legacy networks using numerous sub-wavelength passive elements with adaptive amplitudes and/or phases.
+	Extensive research has been devoted to optimizing the phase shifts for the whole channel block to improve communication, sensing, and power performances \cite{Wu2018,Zhang2019a,Lin2022,Liu2022,Feng2022,Zhao2022}.
 	% In contrast, dynamic passive beamforming that adjusts \gls{irs} within channel block was proposed in \cite{Yang2020} to create diversity for \gls{ofdm} systems.
 	% In contrast, dynamic passive beamforming that adjusts \gls{irs} over finer time slots was proposed in \cite{Yang2020} to create diversity for \gls{ofdm} systems.
-	Besides, dynamic passive beamforming that adjusts \gls{irs} over fine-grained slots within channel coherence time was proposed for \gls{ofdm} systems in \cite{Yang2020}.
+	Besides, \cite{Yang2020} proposed a dynamic passive beamforming that further adjusts \gls{irs} over fine-grained time slots for \gls{ofdm} systems to balance beamforming gain and multiuser diversity.
+	The idea was further applied to \gls{wpcn} to accommodate the downlink \gls{wpt} phase and uplink \gls{wit} phase of the ``harvest-then-transmit'' protocol \cite{Wu2021d,Hua2022a}.
+	% For multiuser \gls{wpt}, \cite{Qiu2022} also reported that despite \gls{irs} is restricted to single-beam reflection, dynamic beamforming can mimic multi-beam reflection in a time-division manner and reduce the phase extraction loss.
+	For multiuser \gls{wpt}, \cite{Qiu2022} also reported that dynamic beamforming can mimic multi-beam reflection in a time-division manner and reduce the phase extraction loss.
+	% However, dynamic passive beamforming demands additional computational complexity and control overhead, and the performance-cost tradeoff needs reconsideration especially when the number of \gls{irs} elements is large.
+	% Although dynamic passive beamforming can artificially create time-varying channels for flexible channel reconfiguration and resource allocation, it demands additional computational complexity and control overhead, and the performance-cost tradeoff deserves further attention.
+	% Although dynamic passive beamforming can artificially introduce temporal diversity for flexible channel reconfiguration and resource allocation, it demands additional computational complexity and control overhead, and the performance-cost tradeoff deserves further attention.
+	Although dynamic passive beamforming artificially creates temporal diversity for flexible channel reconfiguration and resource allocation, it demands additional computational cost and control overhead, and the tradeoff deserves further attention especially for large \gls{irs}.
+	In \cite{Chen2021,Zhang2021d}, \gls{irs} was also introduced to single- and multi-node \gls{sr} systems to reduce the total transmit power.
+	When joint transmitter-\gls{irs} encoding is possible, \cite{Karasik2019} proved using \gls{irs} only for passive beamforming is generally suboptimal in terms of achievable rate for finite input constellations.
+	% The capacity-achieving \gls{irs} strategy was found to
+	Recently, \gls{irs}-empowered \gls{sr} was introduced in \cite{Xu2020b,Hua2022,Hu2021a} where independent passive beamforming and backscatter encoding were combined using advanced architectures.
+	The authors of \cite{Xu2020b,Hua2022} proposed the \gls{irs} to modulate binary message over the whole phase shift matrix and the receiver to decodes from (non-coherent) primary to (coherent) backscatter link.
+	In contrast, \cite{Hu2021a} divided the \gls{irs} into reflection and information elements, and evaluated the error performance of non-coherent backscatter detection.
+	% Compared to existing \gls{irs}-empowered \gls{sr} that encodes and precodes independently using advanced architecture (e.g., overlay or parallel), Metascatter softly bridges and generalizes parasitic source of \gls{sr} and reflecting element of \gls{irs} via smart input design.
 
-	The idea was further applied to \gls{wpcn} to strike the
-
-	proactively generate favourable time-varying channels by properly designing the IRS phase-shift vectors over different time slots,
-	which thus enhances the multiuser diversity over time and also allows more flexible resource allocation.
-
-	mic IRS beamforming is actually beneficial for maximizing the throughput
-	of WPCNs
-	% The authors
-	% of [29] considered a novel dynamic passive beamforming for
-	% Orthogonal Frequency-Division Multiplexing (OFDM) systems,
-	% where the reflection coefficient is varied over consequent
-	% time slots to enable flexible resource allocation over timefrequency Resource Blocks (RBs).
-
-	further adjusted the IRS reflection pattern within channel coherence time to mimic multi-beam reflection in a time-division manner
-
-	\cite{Wu2018} proposed an \gls{irs}-assisted \gls{miso} system and jointly optimized the precoder and the phase shifts to minimize the transmit power.
-	The active and passive beamforming problem was then extended to the discrete phase shift case \cite{Wu2019a} and the multi-user case \cite{Wu2019}.
-	In \cite{Abeywickrama2020}, the authors investigated the impact of non-zero resistance on the reflection pattern and emphasized the coupling between reflection amplitude and phase shift in practice.
-	To estimate the cascaded link without \gls{rf}-chains at the \gls{irs}, practical protocols were developed based on element-wise on/off switching \cite{Nadeem2019}, training sequence and reflection pattern design \cite{You2019,Kang2020}, and compressed sensing \cite{Wang2020}.
-	\gls{irs} was also added to single-tag and multi-tag \gls{sr} systems to improve backscatter efficiency \cite{Chen2021,Zhang2021d}.
-	Recently, the idea of \gls{irs}-empowered \gls{sr} was proposed in \cite{Xu2020b,Hua2022}, where the reflection pattern can be decoupled as the multiplication of whole phase shift matrix and one backscatter symbol.
-	The idea was combined with spatial modulation to divide the \gls{irs} into reflection and information and elements, and the error performance of non-coherent backscatter detection was studied accordingly \cite{Hu2021a}.
-
-	To the best of our knowledge, most existing \gls{sr} systems \cite{Yang2018,Guo2019b,Ding2020,Long2020a,Zhou2019a,Wu2021a,Xu2021a} assumed Gaussian codebook at the tags and employed \gls{sic} from primary to backscatter link.
-	It thus requires non-coherent primary encoding at the transmitter and involves re-encoding, precoding, and subtraction operations that may not be available to legacy receivers.
-	Besides, the primary and backscatter symbols in \gls{sr} are mixed by multiplication coding instead of superposition coding, and the backscatter symbol period can be much longer than the primary symbol period due to physical constraints.
-	Inspired by above, we propose a novel Metascatter network where multiple battery-free tags ride over a conventional point-to-point system and adapt their input probability distribution to simultaneously act as backscatter tags of \gls{sr} and reflecting elements of \gls{irs}.
-	To fully utilize the reflection pattern and signal structure, we also present a novel decoding strategy with minor modifications on existing receivers.
+	To the best of our knowledge, most existing \gls{sr} systems \cite{Yang2018,Guo2019b,Ding2020,Long2020a,Zhou2019a,Wu2021a,Xu2021a} assumed Gaussian codebook at backscatter nodes, and considered \gls{sic} from primary to backscatter link.
+	% It thus requires non-coherent primary encoding at transmitters, and re-encoding, precoding, and subtraction operations that may not be available to legacy receivers.
+	It thus requires non-coherent encoding at the transmitter and re-encoding, precoding, and subtraction processes at the receiver.
+	Besides, the advantage of \gls{sic} is questionable because 1) the primary and backscatter symbols are mixed by multiplication instead of superposition, and 2) the backscatter symbol period is typically much longer under physical constraints.
+	% Motivated by above, we propose a novel Metascatter network where multiple battery-free tags ride over a conventional point-to-point system and adapt their input probability distribution to simultaneously act as backscatter tags of \gls{sr} and reflecting elements of \gls{irs}.
+	Motivated by those, we introduce Metascatter that adapts the input distribution of a finite-state passive backscatter node based on \gls{csi} to unify backscatter sources of \gls{sr} and reflecting elements of \gls{irs}.
+	% An application scenario was considered where multiple Metascatters are introduced to conventional point-to-point system and adapt their input probability distribution to simultaneously act as backscatter tags of \gls{sr} and reflecting elements of \gls{irs}.
+	% An application scenario was considered where multiple Metascatters ride over a point-to-point transmission and simultaneously perform backscatter encoding and passive beamforming.
+	An application scenario was considered where multiple Metascatters ride over a point-to-point transmission to simultaneously encode self message and perform passive beamforming.
+	To fully accommodate backscatter characteristics, we also propose a novel receiving strategy that first jointly decodes all Metascatter based on average received power, then models their reflection patterns and backscatter paths within equivalent channel for primary decoding.
+	% minor modifications on existing receivers, easy to perform, fits backscatter characteristics.
 	The contributions of this paper is summarized as follows.

### 2022-07-16 assets/energy_distribution.tex
:paintbrush: Update illustrations

\begin{tikzpicture}
	\begin{axis}[%
			height=5cm,
			width=9cm,
			xlabel = $z$,
			ylabel = {Probability Density},
			font=\scriptsize,
			no markers,
			xmin=0,
			ymin=0,
			xmax=70,
			%     ticks=none,
			xtick={0,12.78,20.28,29.62,70},
			xticklabels={$t_0$,$t_1$,$t_2$,$t_3$,$t_4$},
			yticklabels={},
			samples = 200]

		\addplot+[thick] gnuplot[raw gnuplot] {%
				isint(x) = (int(x)==x);
				gmm(x,rho,lambda)=rho<=0||lambda<=0?1/0:  x<0?0.0:x==0?(rho>1?0.0:rho==1?real(lambda):1/0):  exp(rho*log(lambda)+(rho-1.0)*log(x)-lgamma(rho)-lambda*x);
				set xrange [0:80];
				set yrange [0:1];
				samples=200;
				plot gmm(x,10,1)};
		\addlegendentryexpanded{$f(z \mid \mathcal{H}_1)$}

		\addplot+[thick] gnuplot[raw gnuplot] {%
				isint(x) = (int(x)==x);
				gmm(x,rho,lambda)=rho<=0||lambda<=0?1/0:  x<0?0.0:x==0?(rho>1?0.0:rho==1?real(lambda):1/0):  exp(rho*log(lambda)+(rho-1.0)*log(x)-lgamma(rho)-lambda*x);
				set xrange [0:80];
				set yrange [0:1];
				samples=200;
				plot gmm(x,10,0.6)};
		\addlegendentryexpanded{$f(z \mid \mathcal{H}_2)$}

		\addplot+[thick,color=brown] gnuplot[raw gnuplot] {%
				isint(x) = (int(x)==x);
				gmm(x,rho,lambda)=rho<=0||lambda<=0?1/0:  x<0?0.0:x==0?(rho>1?0.0:rho==1?real(lambda):1/0):  exp(rho*log(lambda)+(rho-1.0)*log(x)-lgamma(rho)-lambda*x);
				set xrange [0:80];
				set yrange [0:1];
				samples=200;
				plot gmm(x,10,0.4)};
		\addlegendentryexpanded{$f(z \mid \mathcal{H}_3)$}

		\addplot+[thick,color=green!40!gray] gnuplot[raw gnuplot] {%
				isint(x) = (int(x)==x);
				gmm(x,rho,lambda)=rho<=0||lambda<=0?1/0:  x<0?0.0:x==0?(rho>1?0.0:rho==1?real(lambda):1/0):  exp(rho*log(lambda)+(rho-1.0)*log(x)-lgamma(rho)-lambda*x);
				set xrange [0:80];
				set yrange [0:1];
				samples=200;
				plot gmm(x,10,0.28)};
		\addlegendentryexpanded{$f(z \mid \mathcal{H}_4)$}
		\draw[color=gray,thick,dashed] (12.78,0) -- (12.78,0.1);
		\draw[color=gray,thick,dashed] (20.28,0) -- (20.28,0.1);
		\draw[color=gray,thick,dashed] (29.62,0) -- (29.62,0.1);
		\draw[latex-latex] (0,0.05) -- (12.78,0.05) node[below,midway]{$\mathcal{R}(\mathcal{H}_1)$};
		\draw[latex-latex] (12.78,0.05) -- (20.28,0.05) node[below,midway]{$\mathcal{R}(\mathcal{H}_2)$};
		\draw[latex-latex] (20.28,0.05) -- (29.62,0.05) node[below,midway]{$\mathcal{R}(\mathcal{H}_3)$};
		\draw[latex-latex] (29.62,0.05) -- (70,0.05) node[below,midway]{$\mathcal{R}(\mathcal{H}_4)$};
	\end{axis}
\end{tikzpicture}

### 2022-07-16 main.tex
:construction: Update literature review

@@
 \usepackage{array}
+\usepackage{bookmark}
 \usepackage{circuitikz}
@@
 
-	To the best of our knowledge, most existing \gls{sr} systems \cite{Yang2018,Guo2019b,Ding2020,Long2020a,Zhou2019a,Wu2021a,Xu2021a} assumed Gaussian codebook at backscatter nodes, and considered \gls{sic} from primary to backscatter link.
+	To the best of our knowledge, most existing \gls{sr} systems \cite{Yang2018,Guo2019b,Ding2020,Long2020a,Zhou2019a,Wu2021a,Xu2021a} assumed Gaussian codebook at backscatter nodes and considered \gls{sic} from primary to backscatter link.
 	% It thus requires non-coherent primary encoding at transmitters, and re-encoding, precoding, and subtraction operations that may not be available to legacy receivers.
-	It thus requires non-coherent encoding at the transmitter and re-encoding, precoding, and subtraction processes at the receiver.
+	It thus requires non-coherent encoding at the transmitter and re-encoding, precoding, and subtraction at the receiver.
 	Besides, the advantage of \gls{sic} is questionable because 1) the primary and backscatter symbols are mixed by multiplication instead of superposition, and 2) the backscatter symbol period is typically much longer under physical constraints.
 	% Motivated by above, we propose a novel Metascatter network where multiple battery-free tags ride over a conventional point-to-point system and adapt their input probability distribution to simultaneously act as backscatter tags of \gls{sr} and reflecting elements of \gls{irs}.
-	Motivated by those, we introduce Metascatter that adapts the input distribution of a finite-state passive backscatter node based on \gls{csi} to unify backscatter sources of \gls{sr} and reflecting elements of \gls{irs}.
+	Motivated by those, we introduce Metascatter that adapts the input distribution of a passive backscatter node to generalize backscatter sources of \gls{sr} and reflecting elements of \gls{irs}.
 	% An application scenario was considered where multiple Metascatters are introduced to conventional point-to-point system and adapt their input probability distribution to simultaneously act as backscatter tags of \gls{sr} and reflecting elements of \gls{irs}.
@@
 
-	\emph{First,} Metascatter adapts the input probability distribution of a finite-state backscatter device based on the primary and backscatter \gls{csi}.
-	It generalizes the backscatter tags of \gls{sr} and reflecting elements of \gls{irs} to improve the primary-backscatter tradeoff in a flexible manner.
+	\emph{First,} Metascatter adapts the input probability distribution of a finite-state passive backscatter device based on primary and (cascaded) backscatter \gls{csi} to unify and generalize parasitic source of \gls{sr} and reflecting elements of \gls{irs}.
+	The reflection pattern over time is no longer fully random or deterministic, but smartly distributed to simultaneously encode backscatter message and assist primary transmission.
+	% Instead of treating reflection as fully informative/random or fully auxiliary/deterministic,
+	One can adjust node input distribution for flexible primary-backscatter tradeoff.
 	When the primary link is absolutely prioritized, the tag input probability boils down to \num{1} at the state that maximizes the equivalent channel strength and \num{0} at other states, which is essentially the phase shift selection of an \gls{irs} element.

### 2022-07-16 assets/scatter_model.tex
:paintbrush: Update illustrations

--- 2022-06-06 assets/scatter_model.tex
@@
 	\draw (0,0) node[bareantenna](bareantenna){};
-	\draw (bareantenna.west) ++(-1.5,0) node[waves](WI){};
+	\draw (bareantenna.west) ++(-1,0) node[waves](WI){};
 	\draw (WI.north east) ++(0.25,0) node{$\vec{E}_{\mathrm{I}}$};
 	\draw (WI.south east) ++(0.25,0) node{$\vec{H}_{\mathrm{I}}$};
-	\draw (bareantenna.east) ++(0.875,0) node[waves](WR){};
+	\draw (bareantenna.east) ++(0.5,0) node[waves](WR){};
 	\draw (WR.north east) ++(0.35,0) node{$\vec{E}_m$};
 	\draw (WR.south east) ++(0.35,0) node{$\vec{H}_m$};
-	\draw (bareantenna) to ++(0,-1.5) to [generic,l=$Z_{\mathrm{A}}$,/tikz/circuitikz/bipoles/length=0.75cm] ++(3.5,0) node[rotary switch=4 in 90 wiper 30,anchor=ext center,rotate=0](SW){};
-	\draw (SW.cout 1) to ++(0.625,+0.5) to [generic,/tikz/circuitikz/bipoles/length=0.75cm] ++(3,0) coordinate(E1);
-	\draw (SW.cout 2) node[above right]{$m$} to [generic,l=$Z_m$,/tikz/circuitikz/bipoles/length=0.75cm] ++(3,0) coordinate(E2);
-	\draw (SW.cout 3) to [generic,/tikz/circuitikz/bipoles/length=0.75cm] ++(3,0) coordinate(E3);
-	\draw (SW.cout 4) to ++(0.625,-0.5) to [generic,/tikz/circuitikz/bipoles/length=0.75cm] ++(3,0) coordinate(E4);
+	\draw (bareantenna) to ++(0,-1.1) to [generic,l=$Z_{\mathrm{A}}$,/tikz/circuitikz/bipoles/length=0.75cm] ++(2.3,0) node[rotary switch=4 in 90 wiper 30,anchor=ext center,rotate=0](SW){};
+	\draw (SW.cout 1) to ++(0.625,+0.5) to [generic,/tikz/circuitikz/bipoles/length=0.75cm] ++(2.2,0) coordinate(E1);
+	\draw (SW.cout 2) node[above right]{$m$} to [generic,l=$Z_m$,/tikz/circuitikz/bipoles/length=0.75cm] ++(2.2,0) coordinate(E2);
+	\draw (SW.cout 3) to [generic,/tikz/circuitikz/bipoles/length=0.75cm] ++(2.2,0) coordinate(E3);
+	\draw (SW.cout 4) to ++(0.625,-0.5) to [generic,/tikz/circuitikz/bipoles/length=0.75cm] ++(2.2,0) coordinate(E4);
 	% \coordinate (E) at ($(E2)! 0.5!(E3)$);
@@
 	\draw (E3) to[short] (E4);
-	\draw (E2) to[short] ++(1,0) node[ground]{};
+	\draw (E2) to[short] ++(0.2,0) node[ground,rotate=90]{};
 \end{circuitikz}

### 2022-07-16 main.tex
:pencil: Update contributions

@@
 \usepgfplotslibrary{patchplots,groupplots}
+\usetikzlibrary{decorations.pathreplacing,calligraphy}
+\usetikzlibrary{arrows,calc,matrix,plotmarks,patterns,positioning}
 \newtheorem{proposition}{Proposition}
@@
 	% Motivated by above, we propose a novel Metascatter network where multiple battery-free tags ride over a conventional point-to-point system and adapt their input probability distribution to simultaneously act as backscatter tags of \gls{sr} and reflecting elements of \gls{irs}.
-	Motivated by those, we introduce Metascatter that adapts the input distribution of a passive backscatter node to generalize backscatter sources of \gls{sr} and reflecting elements of \gls{irs}.
+	Motivated by those, we propose the concept of Metascatter that adapts the input distribution of a passive backscatter node to generalize backscatter sources of \gls{sr} and reflecting elements of \gls{irs}.
 	% An application scenario was considered where multiple Metascatters are introduced to conventional point-to-point system and adapt their input probability distribution to simultaneously act as backscatter tags of \gls{sr} and reflecting elements of \gls{irs}.
 	% An application scenario was considered where multiple Metascatters ride over a point-to-point transmission and simultaneously perform backscatter encoding and passive beamforming.
-	An application scenario was considered where multiple Metascatters ride over a point-to-point transmission to simultaneously encode self message and perform passive beamforming.
-	To fully accommodate backscatter characteristics, we also propose a novel receiving strategy that first jointly decodes all Metascatter based on average received power, then models their reflection patterns and backscatter paths within equivalent channel for primary decoding.
+	% ! An application scenario was considered where multiple Metascatters ride over a point-to-point transmission to simultaneously encode self message and perform passive beamforming.
+	% To fully accommodate backscatter characteristics, we also propose a novel receiving strategy that first jointly decodes all Metascatter based on average received power, then models their reflection patterns and backscatter paths within equivalent channel for primary decoding.
 	% minor modifications on existing receivers, easy to perform, fits backscatter characteristics.
@@
 	\emph{First,} Metascatter adapts the input probability distribution of a finite-state passive backscatter device based on primary and (cascaded) backscatter \gls{csi} to unify and generalize parasitic source of \gls{sr} and reflecting elements of \gls{irs}.
-	The reflection pattern over time is no longer fully random or deterministic, but smartly distributed to simultaneously encode backscatter message and assist primary transmission.
-	% Instead of treating reflection as fully informative/random or fully auxiliary/deterministic,
-	One can adjust node input distribution for flexible primary-backscatter tradeoff.
-	When the primary link is absolutely prioritized, the tag input probability boils down to \num{1} at the state that maximizes the equivalent channel strength and \num{0} at other states, which is essentially the phase shift selection of an \gls{irs} element.
-	When we only care about the backscatter performance, the network boils down to a multi-tag \gls{ambc} and the input design can be simplified accordingly.
+	The reflection pattern over time is no longer fully random or deterministic, but can be flexibly distributed to balance backscatter encoding and passive beamforming.
+	For single-user scenario, when primary link is absolutely prioritized, the distribution falls on one state and Metascatter boils down to conventional \gls{irs}.
+	When only considering backscatter performance, the distribution involves the highest entropy and Metacatter is essentially an \gls{ambc} node.
 
-	\emph{Second,} we propose a novel receiving strategy where the backscatter symbol of all tags are first recovered by energy-based decoding, then modeled within equivalent \gls{csi} for primary decoding.
-	When the ratio of backscatter symbol period over primary symbol period is large enough, the randomness of primary source can be averaged out and the performance of non-coherent backscatter decoding can be greatly improved.
-	Since the primary and backscatter symbols are mixed by multiplication coding, the backscatter decoding can be viewed as part of primary channel training, which avoids non-coherent encoding at the transmitter and \gls{sic} at the receiver.
+	\emph{Second,} we consider an application scenario where multiple Metascatters ride over a point-to-point transmission, exploiting additional propagation paths to simultaneously transmit and assist.
+	To fully accommodate backscatter characteristics, we also propose a novel receiving strategy that first jointly decodes all Metascatter based on average received power, then models their reflection patterns and backscatter paths within equivalent channel for primary decoding.
+	Since backscatter message is modulated over primary signal, backscatter decoding is indeed part of primary channel training, and there is no need for operation-intensive \gls{sic} at the receiver.
 
-	\emph{Third,} we characterize the achievable primary-(total-)backscatter rate region by iteratively optimizing the tag input distribution, the backscatter decision threshold, and the transmit precoder.
-	For the input design, we propose a numerical method to evaluate the \gls{kkt} solutions by limits of sequences.
-	For the threshold design, we derive the minimum number of decision thresholds to maximize the total backscatter rate, and obtain the optimal thresholds by \gls{dp} accelerated by \gls{smawk} algorithm.
-	However, the optimal precoder design can be non-trivial and we may end up with a low-complexity suboptimal solution.
+	% \emph{Second,} we propose a novel receiving strategy where the backscatter symbol of all tags are first recovered by energy-based decoding, then modeled within equivalent \gls{csi} for primary decoding.
+	% When the ratio of backscatter symbol period over primary symbol period is large enough, the randomness of primary source can be averaged out and the performance of non-coherent backscatter decoding can be greatly improved.
+	% Since the primary and backscatter symbols are mixed by multiplication coding, the backscatter decoding can be viewed as part of primary channel training, which avoids non-coherent encoding at the transmitter and \gls{sic} at the receiver.
+
+	\emph{Third,} we evaluate the achievable primary-(total-)backscatter rate region by optimizing the input distribution at Metascatters, the active beamforming at the \gls{ap}, and the decision regions at the user.
+Since the original problem is highly non-convex, we consider a suboptimal \gls{bcd} algorithm where the \gls{kkt} input distribution is numerically evaluated by limit of sequences, the active beamforming is sequentially updated by \gls{pgd} accelerated by backtracking line search, and the decision regions are first restricted to convex, then refined by \gls{dp} and \gls{smawk} algorithm.
+
+	% \emph{Third,} we characterize the achievable primary-(total-)backscatter rate region by iteratively optimizing the tag input distribution, the backscatter decision threshold, and the transmit precoder.
+	% For the input design, we propose a numerical method to evaluate the \gls{kkt} solutions by limits of sequences.
+	% For the threshold design, we derive the minimum number of decision thresholds to maximize the total backscatter rate, and obtain the optimal thresholds by \gls{dp} accelerated by \gls{smawk} algorithm.
+	% However, the optimal precoder design can be non-trivial and we may end up with a low-complexity suboptimal solution.
 
@@
 	\end{figure}
+
+	% \begin{figure*}[!t]
+	% 	\centering
+	% 	\subfloat[Block Diagram]{
+	% 		\resizebox{0.3\linewidth}{!}{
+	% 			\input{assets/block_diagram.tex}
+	% 		}
+	% 		\label{fi:block_diagram}
+	% 	}
+	% 	\subfloat[Equivalent Circuit]{
+	% 		\resizebox{0.35\linewidth}{!}{
+	% 			\input{assets/equivalent_circuit.tex}
+	% 		}
+	% 		\label{fi:equivalent_circuit}
+	% 	}
+	% 	\subfloat[Scatter Model]{
+	% 		\resizebox{0.27\linewidth}{!}{
+	% 			\input{assets/scatter_model.tex}
+	% 		}
+	% 		\label{fi:scatter_model}
+	% 	}
+	% 	\caption{Block diagram, equivalent circuit, and scatter model of a typical passive tag.
+The solid and dashed vectors represent signal and energy flows.
+The backscatter antenna behaves as a constant power source, where the voltage $V_0$ and current $I_0$ are introduced by incident electric field $\vec{E}_{\mathrm{I}}$ and magnetic field $\vec{H}_{\mathrm{I}}$ \cite{Huang2021}.}
+	% \end{figure*}
+
 	Passive backscatter devices (a.k.a., tags) harvest energy from and modulate information over surrounding \gls{rf} signal.
@@
 	\begin{subsection}{Decision Threshold}
+		\begin{figure}[!t]
+			\centering
+			\resizebox{0.95\columnwidth}{!}{
+				\input{assets/energy_distribution.tex}
+			}
+			\caption{\gls{pdf} of Average Received Power Conditioned on Different Input Hypothesis. Example \gls{ml}.}
+		\end{figure}
+
 		For a given tag input distribution $\{\boldsymbol{p}_k\}$, we can formulate an equivalent information source with augmented alphabet of tag input combination.

### 2022-07-17 main.tex
:pencil: Update literature review

@@
 
-	To the best of our knowledge, most existing \gls{sr} systems \cite{Yang2018,Guo2019b,Ding2020,Long2020a,Zhou2019a,Wu2021a,Xu2021a} assumed Gaussian codebook at backscatter nodes and considered \gls{sic} from primary to backscatter link.
-	% It thus requires non-coherent primary encoding at transmitters, and re-encoding, precoding, and subtraction operations that may not be available to legacy receivers.
-	It thus requires non-coherent encoding at the transmitter and re-encoding, precoding, and subtraction at the receiver.
-	Besides, the advantage of \gls{sic} is questionable because 1) the primary and backscatter symbols are mixed by multiplication instead of superposition, and 2) the backscatter symbol period is typically much longer under physical constraints.
+	To the best of our knowledge, all existing \gls{sr} literatures assumed backscatter modulation employs either Gaussian codebook \cite{Guo2019b,Ding2020,Long2020a,Zhou2019a,Wu2021a,Xu2021a,Yang2021a} or finite equiprobable inputs \cite{Yang2018,Han2021,Zhang2022,Xu2020b,Hua2022,Hu2021a}.
+	The former is impratical for passive nodes with constrained number of states, while the latter does not fully exploit \gls{csi} to boost achievable backscatter rate.
+	Besides, most relevant designs \cite{Guo2019b,Ding2020,Long2020a,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Yang2018,Han2021,Zhang2022,Xu2020b,Hua2022} were built over ideal \gls{ml} or \gls{sic} receiver.
+	However, the advantage of \gls{sic} is questionable because 1) it requires non-coherent primary encoding at the transmitter and re-encoding, precoding, and subtraction at the receiver, 2) the primary and backscatter symbols are mixed by multiplication instead of superposition, and 3) the backscatter symbol period is typically much longer due to physical constraints.
 	% Motivated by above, we propose a novel Metascatter network where multiple battery-free tags ride over a conventional point-to-point system and adapt their input probability distribution to simultaneously act as backscatter tags of \gls{sr} and reflecting elements of \gls{irs}.
-	Motivated by those, we propose the concept of Metascatter that adapts the input distribution of a passive backscatter node to generalize backscatter sources of \gls{sr} and reflecting elements of \gls{irs}.
+	Motivated by those, we propose the concept of Metascatter, which adapts the input distribution of a passive backscatter node to generalize backscatter sources of \gls{sr} and reflecting elements of \gls{irs}.
 	% An application scenario was considered where multiple Metascatters are introduced to conventional point-to-point system and adapt their input probability distribution to simultaneously act as backscatter tags of \gls{sr} and reflecting elements of \gls{irs}.
@@
 
+	\emph{Notations:} Scalars, vectors and matrices are denoted respectively by italic, bold lower-case, and bold upper-case letters.
+	$j$ represents the imaginary unit.
+	% $\boldsymbol{0}$ and $\boldsymbol{1}$ denote respectively zero and one vector or matrix.
+	% $\boldsymbol{I}$ represents the identity matrix.
+	% $\mathbb{R}_+^{x \times y}$ and $\mathbb{C}^{x \times y}$ denote respectively the space of real nonnegative and complex $x \times y$ matrices.
+	$\mathbb{R}_+^{x \times y}$ and $\mathbb{C}^{x \times y}$ respectively denote the space of real nonnegative and complex $x \times y$ matrices.
+	$\Delta^n = \left\{ (p_0,\dots,p_n) \in \mathbb{R}_+^{n+1} \mid \sum_{i=0}^n t_i = 1 \right\}$ denotes the standard $n$-simplex.
+	% $\Re\{\cdot\}$ retrieves the real part of a complex entity. $[\cdot]_{(n)}$ denotes the $n$-th entry of a vector and $[\cdot]_{(1:n)}$ denotes the first $n$ entries of a vector.
+	$(\cdot)^*$, $(\cdot)^T$, $(\cdot)^H$, $(\cdot)^+$, $\lvert{\cdot}\rvert$, $\lVert{\cdot}\rVert$ respectively represent the conjugate, transpose, conjugate transpose, ramp function, absolute value, and Euclidean norm.
+	% $\arg(\cdot)$, $\mathrm{rank}(\cdot)$, $\mathrm{tr}(\cdot)$, $\mathrm{diag}(\cdot)$ and $\mathrm{diag}^{-1}(\cdot)$ respectively denote the argument, rank, trace, a square matrix with input vector on the main diagonal, and a vector retrieving the main diagonal of the input matrix.
+	% $\odot$ denotes the Hadamard product.
+	% $\boldsymbol{S} \succeq \boldsymbol{0}$ means $\boldsymbol{S}$ is positive semi-definite.
+	% $\mathbb{A}\{\cdot\}$ extracts the DC component of a signal.
+	% $\mathbb{E}_X\{\cdot\}$ takes expectation w.r.t. random variable $X$ ($X$ is omitted for simplicity).
+	The distribution of a CSCG random vector with mean $\boldsymbol{0}$ and covariance $\boldsymbol{\Sigma}$ is denoted by $\mathcal{CN}(\boldsymbol{0},\boldsymbol{\Sigma})$.
+	$\sim$ means ``distributed as''.
+	$(\cdot)^{(i)}$ represents the $i$-th iterated value and $(\cdot)^{\star}$ represents the end solution.
 \end{section}
@@
 \begin{section}{Backscatter Principles}
-	\begin{figure}[!t]
-		\centering
-		\subfloat[Block Diagram]{
-			\resizebox{0.8\columnwidth}{!}{
-				\input{assets/block_diagram.tex}
-			}
-			\label{fi:block_diagram}
-		}
-		\\
-		\subfloat[Equivalent Circuit]{
-			\resizebox{0.95\columnwidth}{!}{
-				\input{assets/equivalent_circuit.tex}
-			}
-			\label{fi:equivalent_circuit}
-		}
-		\\
-		\subfloat[Scatter Model]{
-			\resizebox{0.8\columnwidth}{!}{
-				\input{assets/scatter_model.tex}
-			}
-			\label{fi:scatter_model}
-		}
-		\caption{Block diagram, equivalent circuit, and scatter model of a typical passive tag.
-The solid and dashed vectors represent signal and energy flows.
-The backscatter antenna behaves as a constant power source, where the voltage $V_0$ and current $I_0$ are introduced by incident electric field $\vec{E}_{\mathrm{I}}$ and magnetic field $\vec{H}_{\mathrm{I}}$ \cite{Huang2021}.}
-	\end{figure}
-
-	% \begin{figure*}[!t]
+	% \begin{figure}[!t]
 	% 	\centering
 	% 	\subfloat[Block Diagram]{
-	% 		\resizebox{0.3\linewidth}{!}{
+	% 		\resizebox{0.8\columnwidth}{!}{
 	% 			\input{assets/block_diagram.tex}
@@
 	% 	}
+	% 	\\
 	% 	\subfloat[Equivalent Circuit]{
-	% 		\resizebox{0.35\linewidth}{!}{
+	% 		\resizebox{0.95\columnwidth}{!}{
 	% 			\input{assets/equivalent_circuit.tex}
@@
 	% 	}
+	% 	\\
 	% 	\subfloat[Scatter Model]{
-	% 		\resizebox{0.27\linewidth}{!}{
+	% 		\resizebox{0.8\columnwidth}{!}{
 	% 			\input{assets/scatter_model.tex}
@@
 The backscatter antenna behaves as a constant power source, where the voltage $V_0$ and current $I_0$ are introduced by incident electric field $\vec{E}_{\mathrm{I}}$ and magnetic field $\vec{H}_{\mathrm{I}}$ \cite{Huang2021}.}
-	% \end{figure*}
+	% \end{figure}
 
-	Passive backscatter devices (a.k.a., tags) harvest energy from and modulate information over surrounding \gls{rf} signal.
+	\begin{figure*}[!t]
+		\centering
+		\subfloat[Block Diagram]{
+			\resizebox{0.32\linewidth}{!}{
+				\input{assets/block_diagram.tex}
+			}
+			\label{fi:block_diagram}
+		}
+		\subfloat[Equivalent Circuit]{
+			\resizebox{0.37\linewidth}{!}{
+				\input{assets/equivalent_circuit.tex}
+			}
+			\label{fi:equivalent_circuit}
+		}
+		\subfloat[Scatter Model]{
+			\resizebox{0.28\linewidth}{!}{
+				\input{assets/scatter_model.tex}
+			}
+			\label{fi:scatter_model}
+		}
+		\caption{Block diagram, equivalent circuit, and scatter model of a passive backscatter node.
+The solid and dashed vectors represent signal and energy flows.
+The backscatter antenna behaves as a constant power source, where the voltage $V_0$ and current $I_0$ are introduced by incident electric field $\vec{E}_{\mathrm{I}}$ and magnetic field $\vec{H}_{\mathrm{I}}$ \cite{Huang2021}.}
+	\end{figure*}
+
+	Passive backscatter nodes harvest energy from and modulate information over surrounding \gls{rf} signal.
 	As shown in Fig.
-\subref*{fi:block_diagram}, a typical passive tag consists of a scattering antenna, an energy harvester, an integrated receiver, a load-switching modulator, and on-chip components (e.g., micro-controller and sensors) \cite{Dobkin2012}.
-Its equivalent circuit is also given by Fig.
-\subref*{fi:equivalent_circuit}.
-	When illuminated, the tag absorbs a portion of the impinging wave and scatters the rest back to the space.
-	The absorbed signal can be used for source decoding and energy harvesting \cite{Kim2021a}, while the scattered signal can be decomposed into the \emph{structural} and \emph{antenna} mode components \cite{Hansen1989}.
-	The structural mode scattering applies to general objects and is related to the antenna structure, shape and material, which contributes to environment multipath and can be covered by channel estimation \cite{Boyer2014}.
-	On the other hand, the antenna mode scattering models the antenna radiation and depends on the antenna-load impedance mismatch, which can be used for backscatter modulation \cite{Boyer2012} or channel reconfiguration \cite{Wu2021b}.
-	Fig. \subref*{fi:scatter_model} illustrates the scatter model.
-	For a tag with $M$ candidate states, the reflection coefficient of state $m \in \mathcal{M} \triangleq \{1,\ldots,M\}$ is defined as
-	\begin{footnote}
-		It corresponds to a linear backscatter model where the reflection coefficient is irrelevant to incident electromagnetic field strength.
-	\end{footnote}
+\subref*{fi:block_diagram}, a typical passive node consists of a scattering antenna, an energy harvester, an integrated receiver, a load-switching modulator, and on-chip components (e.g., micro-controller and sensors) \cite{Dobkin2012}.
+	Its equivalent circuit is presented in Fig. \subref*{fi:equivalent_circuit}.
+	When illuminated, the node absorbs a portion of the impinging wave and scatters the remaining to the space.
+	The absorbed signal can be used for information decoding and energy harvesting \cite{Kim2021a}, while the scattered signal is further decomposed into the \emph{structural} and \emph{antenna} mode components \cite{Hansen1989}.
+	Related to structure, shape and material of general objects, structural scattering consistently contributes to environment multipath and can be covered by channel estimation \cite{Boyer2014}.
+	In contrast, antenna scattering models radiation pattern from antenna-load impedance mismatch, and can be used for backscatter modulation \cite{Boyer2012} and/or channel reconfiguration \cite{Wu2021b}.
+	% The scatter model is illustrated in Fig. \subref*{fi:scatter_model}.
+	Fig. \subref*{fi:scatter_model} illustrates the scatter model of a node with $M$ candidate states, and the reflection coefficient of state $m \in \mathcal{M} \triangleq \{1,\ldots,M\}$ is defined as%
+	\footnote{It corresponds to a linear backscatter model where the reflection coefficient is irrelevant to incident electromagnetic field strength.}
 	\begin{equation}
@@
 	\begin{subsection}{Backscatter Modulation}
-		In backscatter modulation, the tag \emph{periodically varies} the reflection coefficient to embed its own information.
-		As such, there exists a mapping from the alphabet to the set.
-		When the \gls{csi} and reflection alphabet $\{\Gamma_1,\ldots,\Gamma_M\}$ are available at the reader, it can decode the tag message from the observed scattered signal.
+		% In backscatter modulation, the tag \emph{periodically varies} the reflection coefficient to embed its own information.
+		% To perform backscatter modulation, nodes encode message within distribution of reflection states.%
+		% To perform backscatter modulation, nodes encode message within distribution of reflection states.%
+		Backscatter nodes encode message by frequently change its reflection state.
 
+		% Although most backscatter and \gls{sr} literatures assumed equiprobable state distribution at nodes, the
+
+		within distribution of reflection states and
+
+		% In backscatter modulation, the tag \emph{periodically varies} the reflection coefficient to embed its own information.
+		% As such, there exists a mapping from the alphabet to the set.
 		For $M$-ary \gls{qam}, the complex constellation point $c_m$ maps to the corresponding reflection coefficient by \cite{Thomas2012a}
@@
 		\end{figure}
+
+		When the \gls{csi} and reflection alphabet $\{\Gamma_1,\ldots,\Gamma_M\}$ are available at the reader, it can decode the tag message from the observed scattered signal.
 

### 2022-07-18 main.tex
:construction: Update manuscript
:pencil: Update manuscript

@@
 	To the best of our knowledge, all existing \gls{sr} literatures assumed backscatter modulation employs either Gaussian codebook \cite{Guo2019b,Ding2020,Long2020a,Zhou2019a,Wu2021a,Xu2021a,Yang2021a} or finite equiprobable inputs \cite{Yang2018,Han2021,Zhang2022,Xu2020b,Hua2022,Hu2021a}.
-	The former is impratical for passive nodes with constrained number of states, while the latter does not fully exploit \gls{csi} to boost achievable backscatter rate.
+	The former is impractical for passive nodes with constrained number of states, while the latter does not fully exploit \gls{csi} to boost achievable backscatter rate.
 	Besides, most relevant designs \cite{Guo2019b,Ding2020,Long2020a,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Yang2018,Han2021,Zhang2022,Xu2020b,Hua2022} were built over ideal \gls{ml} or \gls{sic} receiver.
@@
 	For single-user scenario, when primary link is absolutely prioritized, the distribution falls on one state and Metascatter boils down to conventional \gls{irs}.
-	When only considering backscatter performance, the distribution involves the highest entropy and Metacatter is essentially an \gls{ambc} node.
+	When only considering backscatter performance, the distribution involves the highest entropy and Metascatter is essentially an \gls{ambc} node.
 
@@
 	As shown in Fig.
-\subref*{fi:block_diagram}, a typical passive node consists of a scattering antenna, an energy harvester, an integrated receiver, a load-switching modulator, and on-chip components (e.g., micro-controller and sensors) \cite{Dobkin2012}.
+\subref*{fi:block_diagram}, a typical passive node consists of a scattering antenna, an energy harvester, an integrated receiver, a load-switching modulator, and on-chip components (e.g., microcontroller and sensors) \cite{Dobkin2012}.
 	Its equivalent circuit is presented in Fig. \subref*{fi:equivalent_circuit}.
-	When illuminated, the node absorbs a portion of the impinging wave and scatters the remaining to the space.
-	The absorbed signal can be used for information decoding and energy harvesting \cite{Kim2021a}, while the scattered signal is further decomposed into the \emph{structural} and \emph{antenna} mode components \cite{Hansen1989}.
-	Related to structure, shape and material of general objects, structural scattering consistently contributes to environment multipath and can be covered by channel estimation \cite{Boyer2014}.
-	In contrast, antenna scattering models radiation pattern from antenna-load impedance mismatch, and can be used for backscatter modulation \cite{Boyer2012} and/or channel reconfiguration \cite{Wu2021b}.
-	% The scatter model is illustrated in Fig. \subref*{fi:scatter_model}.
-	Fig. \subref*{fi:scatter_model} illustrates the scatter model of a node with $M$ candidate states, and the reflection coefficient of state $m \in \mathcal{M} \triangleq \{1,\ldots,M\}$ is defined as%
+	When illuminated, the node absorbs a portion of the impinging wave for information decoding and energy harvesting \cite{Kim2021a}, and scatters the remaining to the space.
+The scattered signal is further decomposed into the \emph{structural} and \emph{antenna} mode components \cite{Hansen1989}.
+	Depending on structure, shape and material of general objects, structural scattering consistently contributes to environment multipath and is covered by channel estimation \cite{Boyer2014}.
+	In contrast, antenna scattering models radiation pattern from antenna-load impedance mismatch and can be used for backscatter modulation \cite{Boyer2012} and/or channel reconfiguration \cite{Wu2021b}.
+	Fig.
+\subref*{fi:scatter_model} illustrates the scatter model of a node with $M$ reflection states, where the reflection coefficient of state $m \in \mathcal{M} \triangleq \{1,\ldots,M\}$ is defined as%
 	\footnote{It corresponds to a linear backscatter model where the reflection coefficient is irrelevant to incident electromagnetic field strength.}
@@
 	\end{figure}
+	The parameters remain fixed unless specified.
 \end{section}

### 2022-07-18 main.tex
:pencil: Update backscatter principles

@@
 
-	\emph{Notations:} Scalars, vectors and matrices are denoted respectively by italic, bold lower-case, and bold upper-case letters.
+	\emph{Notations:} Scalars, vectors and matrices are respectively denoted by italic, bold lower-case, and bold upper-case letters.
 	$j$ represents the imaginary unit.
@@
 
-	Passive backscatter nodes harvest energy from and modulate information over surrounding \gls{rf} signal.
+	Passive backscatter nodes harvest energy from and modulate information over surrounding \gls{rf} signals.
 	As shown in Fig.
-\subref*{fi:block_diagram}, a typical passive node consists of a scattering antenna, an energy harvester, an integrated receiver, a load-switching modulator, and on-chip components (e.g., microcontroller and sensors) \cite{Dobkin2012}.
+\subref*{fi:block_diagram}, a typical passive node consists of a scattering antenna, an energy harvester, an integrated receiver, a load-switching modulator, and on-chip components (e.g., micro-controller and sensors) \cite{Dobkin2012}.
 	Its equivalent circuit is presented in Fig. \subref*{fi:equivalent_circuit}.
-	When illuminated, the node absorbs a portion of the impinging wave for information decoding and energy harvesting \cite{Kim2021a}, and scatters the remaining to the space.
-The scattered signal is further decomposed into the \emph{structural} and \emph{antenna} mode components \cite{Hansen1989}.
-	Depending on structure, shape and material of general objects, structural scattering consistently contributes to environment multipath and is covered by channel estimation \cite{Boyer2014}.
-	In contrast, antenna scattering models radiation pattern from antenna-load impedance mismatch and can be used for backscatter modulation \cite{Boyer2012} and/or channel reconfiguration \cite{Wu2021b}.
-	Fig.
-\subref*{fi:scatter_model} illustrates the scatter model of a node with $M$ reflection states, where the reflection coefficient of state $m \in \mathcal{M} \triangleq \{1,\ldots,M\}$ is defined as%
+	% When illuminated, the node absorbs a portion of the impinging wave for information decoding and energy harvesting \cite{Kim2021a}, while scatters the remaining back to the space.
+The scattered signal is further decomposed into the \emph{structural} component that consistently contributes to environment multipath and covered by channel estimation \cite{Boyer2014}, and the
+	When illuminated, the node absorbs a portion of the impinging wave for information decoding and/or energy harvesting \cite{Kim2021a}, and backscatters the remaining as \emph{structural} and \emph{antenna} components.
+	% The scattered signal is further decomposed into the \emph{structural} component that consistently contributes to environment multipath and covered by channel estimation \cite{Boyer2014}, and the \emph{antenna} mode component that
+	% and \emph{antenna} mode components \cite{Hansen1989}.
+	The former consistently contributes to environment multipath and can be modelled by channel estimation \cite{Boyer2014}, while the latter depends on antenna-load impedance mismatch and can be used for backscatter modulation \cite{Boyer2012} and/or channel reconfiguration \cite{Wu2021b}.
+	% Depending on structure, shape and material of general objects, structural scattering consistently contributes to environment multipath and is covered by channel estimation \cite{Boyer2014}.
+	% In contrast, antenna scattering models radiation pattern from antenna-load impedance mismatch and can be used for backscatter modulation \cite{Boyer2012} and/or channel reconfiguration \cite{Wu2021b}.
+	Fig. \subref*{fi:scatter_model} illustrates the scatter model of a node with $M$ states, where the reflection coefficient of state $m \in \mathcal{M} \triangleq \{1,\ldots,M\}$ is defined as%
 	\footnote{It corresponds to a linear backscatter model where the reflection coefficient is irrelevant to incident electromagnetic field strength.}
@@
 
-	\begin{subsection}{Backscatter Modulation}
-		% In backscatter modulation, the tag \emph{periodically varies} the reflection coefficient to embed its own information.
-		% To perform backscatter modulation, nodes encode message within distribution of reflection states.%
-		% To perform backscatter modulation, nodes encode message within distribution of reflection states.%
-		Backscatter nodes encode message by frequently change its reflection state.
-
-		% Although most backscatter and \gls{sr} literatures assumed equiprobable state distribution at nodes, the
-
-		within distribution of reflection states and
-
-		% In backscatter modulation, the tag \emph{periodically varies} the reflection coefficient to embed its own information.
-		% As such, there exists a mapping from the alphabet to the set.
-		For $M$-ary \gls{qam}, the complex constellation point $c_m$ maps to the corresponding reflection coefficient by \cite{Thomas2012a}
+	\begin{subsection}{SR: Backscatter Modulation}
+		% Backscatter sources encode self message by \emph{randomly changing reflection states.} For $M$-ary \gls{qam}, reflection coefficient $\Gamma_m$ maps to the corresponding complex constellation point $c_m$ by \cite{Thomas2012a}
+		Backscatter sources encode self message by \emph{random reflection states variation.} For $M$-ary \gls{qam}, reflection coefficient $\Gamma_m$ maps to the corresponding \emph{complex constellation point $c_m$} by \cite{Thomas2012a}
 		\begin{equation}
@@
 		\end{equation}
-		where $\alpha \in [0,1]$ models the amplitude scatter ratio at the direction of interest.
-
-		% When the \gls{csi} and reflection alphabet $\{\Gamma_1,\ldots,\Gamma_M\}$ are available at the reader, the tag can be successfully decoded based on the received signal.
-
-		\begin{figure}[!t]
-			\centering
-			\subfloat[Reflection State Distribution]{
-				\resizebox{0.95\columnwidth}{!}{
-					\input{assets/reflection_state_distribution.tex}
-				}
-			}
-			\\
-			\subfloat[Time Block Structure]{
-				\resizebox{0.95\columnwidth}{!}{
-					\input{assets/time_block_structure.tex}
-				}
-			}
-			\caption{Reflection state distribution and time block structure of \gls{sr}, \gls{irs}, and Metascatter.
-$T_s$ and $T_c$ denote the primary and backscatter symbol length, respectively.
-Based on \gls{csi}, Metascatter adapts the reflection state distribution to unify data transmission and channel reconfiguration.}
-		\end{figure}
-
-		When the \gls{csi} and reflection alphabet $\{\Gamma_1,\ldots,\Gamma_M\}$ are available at the reader, it can decode the tag message from the observed scattered signal.
+		where $\alpha \in [0,1]$ is the amplitude reflect ratio that controls the harvest-scatter tradeoff at the direction of interest.
+		% When the \gls{csi} and reflection alphabet $\{\Gamma_1,\ldots,\Gamma_M\}$ are available at the reader, it can decode the tag message from the observed scattered signal.
+		% ! Use larger alpha in simulation: for high-order QAM, some constellation point may harvests more power than others
 
@@
 
-	\begin{subsection}{Channel Reconfiguration}
-		2
+	\begin{subsection}{IRS: Channel Reconfiguration}
+		% \gls{irs} elements assist legacy transmission by \emph{deterministically choosing phase shifts} based on relevant \gls{csi}.
+For a reflecting element with $M$ candidate states, reflection coefficient $\Gamma_m$ maps to the corresponding phase shift $\theta_m$ by \cite{Wu2018}
+		\gls{irs} elements assist legacy transmission by \emph{deterministic phase shifts selection} based on relevant \gls{csi}.
+		For a reflecting element with $M$ candidate states, reflection coefficient $\Gamma_m$ relates to the corresponding \emph{phase shift $\theta_m$} by \cite{Wu2018}
+		\begin{equation}
+			\Gamma_m = \beta_m \exp(j \theta_m),
+		\end{equation}
+		where $\beta_m \in [0,1]$ is overall amplitude reflect ratio of state $m$.
+		% Based on relevant \gls{csi}
 	\end{subsection}
@@
 	% where $\alpha \in [0,1]$ models the harvest-backscatter ratio at the direction of interest.
-	For passive tags, $\alpha \ll 1$ is commonly assumed as the majority of the incident wave can be harvested to support tag modules \cite{Thomas2012a}.
-	% ! Use larger alpha in simulation: for high-order QAM, some constellation point may harvests more power than others
+	% For passive tags, $\alpha \ll 1$ is commonly assumed as the majority of the incident wave can be harvested to support tag modules \cite{Thomas2012a}.
 
+	\begin{subsection}{Metascatter: Bridge and Generalization}
+		\begin{figure}[!t]
+			\centering
+			\subfloat[Reflection State Distribution]{
+				\resizebox{0.8\columnwidth}{!}{
+					\input{assets/reflection_state_distribution.tex}
+				}
+			}
+			\\
+			\subfloat[Time Slot Structure]{
+				\resizebox{0.8\columnwidth}{!}{
+					\input{assets/time_block_structure.tex}
+				}
+			}
+			\caption{
+				Reflection state distribution and time block structure of \gls{sr}, \gls{irs}, and Metascatter.
+				$T_s$ and $T_c$ respectively denote the primary and backscatter symbol period.
+				Within channel coherence time, Metascatter semi-randomly selects reflection state for each backscatter block, with guidance from input probability distribution.
+			}
+			\label{fi:metascatter}
+		\end{figure}
+		% For a passive node with finite states, is it possible to unify backscatter modulation and channel reconfiguration by proper selection of reflection coefficient?
+		Metascatters simultaneously transmit and assist by \emph{adaptive input distribution design} based on primary and (cascaded) backscatter \gls{csi}.
+		% The reflection pattern is neither fully random nor fully deterministic, but flexibly distributed to balance backscatter encoding and passive beamforming.
+		% Instead of using fully random or deterministic reflection pattern over time, as shown in Fig.
+\ref{fi:metascatter}, Metascatter flexibly controls input distribution of candidate reflection states to balance backscatter encoding and passive beamforming.
+		% Instead of using fully random or deterministic reflection pattern over time, as shown in Fig.
+\ref{fi:metascatter}, Metascatter semi-randomly selects reflection state for each backscatter block with guidance from \emph{input probability distribution $P(\Gamma_m)$.}
+		% Instead of using fully random or deterministic reflection pattern over time, as shown in Fig.
+\ref{fi:metascatter}, Metascatter semi-randomly selects reflection state for each backscatter block, with guidance from \emph{input probability distribution $P(\Gamma_m)$.} In other words, it flexibly controls input distribution of candidate reflection states to balance backscatter encoding and passive beamforming.
+\gls{sr} and \gls{irs} can be regarded as extreme cases of Metascatter, where node input distribution boils down to uniform and deterministically biased, respectively.
+		Instead of using fully random or deterministic reflection pattern over time, as shown in Fig.
+\ref{fi:metascatter}, Metascatter semi-randomly selects reflection state for each backscatter block, with \emph{guidance of input probability $P(\Gamma_m)$} for state $m$.
+In other words, it flexibly controls input distribution of candidate reflection states to balance backscatter encoding and passive beamforming.
+\gls{sr} and \gls{irs} can be regarded as extreme cases of Metascatter, where node input distribution boils down to uniform and deterministic, respectively.
+		% flexibly controls input distribution of candidate reflection states to balance backscatter encoding and passive beamforming.
+		% Metascatter semi-randomly selects reflection state for each backscatter block, with guidance from \emph{input probability distribution $P(\Gamma_m)$.}
+		% % Based on \gls{csi}, Metascatter adapts the reflection state distribution to unify data transmission and channel reconfiguration.
+		% \gls{sr} and \gls{irs} can be regarded as its extreme cases, where node input distribution boils down to uniform and deterministically biased, respectively.
+		% Within channel coherence time, Metascatter semi-randomly selects reflection state for each backscatter block, with guidance from \emph{input probability distribution $P(\Gamma_m)$.}
 		\begin{remark}
-		By choosing proper load impedance, it is possible to implement any signal constellation or think beyond modulation.
-		For example, perfect matching enables maximum power transfer to the tag, while perfect mismatch leads to complete reflection as desired by ideal \gls{irs}.
-		It inspires Metascatter to design a smart reflection and unify wireless power transfer, backscatter modulation, and passive beamforming.
+			Compared to conventional \gls{irs} literatures that optimize phase shifts under unit-module constraint, Metascatter starts from predefined reflection coefficients and designs their input distribution under sum-probability constraint to achieve flexible primary-backscatter tradeoff.
 		\end{remark}
+		% Next, we will discuss the input design in a Metascatter-enabled network.
+		% consider a Metascatter-aided system to evaluate
+	\end{subsection}
 \end{section}
 
-\begin{section}{Metascatter}
+\begin{section}{Metascatter-Enabled Network}
 	\begin{subsection}{System Model}
@@
 			\centering
-			\def\svgwidth{0.9\columnwidth}
-			\import{assets/}{metascatter_system.eps_tex}
-			\caption{The proposed Metascatter system.}
-			\label{fi:metascatter_system}
+			\def\svgwidth{0.8\columnwidth}
+			\footnotesize{
+				\import{assets/}{metascatter_network.eps_tex}
+			}
+			\caption{A Metascatter-enabled single-user multi-node network.}
+			\label{fi:metascatter_network}
 		\end{figure}
-		As shown in Fig.
-\ref{fi:metascatter_system}, we propose a single-\gls{ue} multi-\gls{tg} symbiotic radio network where the \gls{rf} signal generated by the $Q$-antenna \gls{ap} is shared by two coexisting systems.
-		In the primary point-to-point system, the \gls{ap} transmits information to the single-antenna user.
-		In the secondary backscatter system, the \gls{ap} acts as the carrier emitter, the $K$ nearby single-antenna tags modulate their information over the reradiated \gls{rf} signals, and the user receives and decodes the backscatter messages.
-		Denote the \gls{ap}-\gls{ue} direct channel as $\boldsymbol{h}_{\mathrm{D}}^H \in \mathbb{C}^{1 \times Q}$, the \gls{ap}-\gls{tg} $k \in \mathcal{K} \triangleq \{1,\ldots,K\}$ forward channel as $\boldsymbol{h}_{\mathrm{F},k}^H \in \mathbb{C}^{1 \times Q}$, the \gls{tg} $k$-\gls{ue} backward channel as $h_{\mathrm{B},k}$, and define the cascaded channel of tag $k$ as $\boldsymbol{h}_{\mathrm{C},k}^H \triangleq h_{\mathrm{B},k} \boldsymbol{h}_{\mathrm{F},k}^H \in \mathbb{C}^{1 \times Q}$.
-		For simplicity, we consider a quasi-static block fading model where the channel response remain constant within each coherence interval and vary independently between consecutive blocks.
+		% As shown in Fig. \ref{fi:metascatter_network}, we propose a Metascatter-enabled single-user multi-node network where the spectrum, energy and infrastructures are shared by two coexisting systems.
+		As shown in Fig. \ref{fi:metascatter_network}, we propose a Metascatter-enabled single-user multi-node network where two coexisting systems share spectrum, energy and infrastructures.
+		% In the primary point-to-point system, the \gls{ap} transmits information to the single-antenna user.
+		% In the primary point-to-point system, a $Q$-antenna \gls{ap} transmit to a single-antenna user while assisted by $K$ nearby single-antenna Metascatters.
+		The primary point-to-point transmission from a $Q$-antenna \gls{ap} to a single-antenna user is assisted by $K$ nearby single-antenna Metascatters.
+		In the secondary backscatter \gls{mac} system, the \gls{ap} serves as the carrier emitter, $K$ nearby single-antenna Metascatters modulate information over reradiated \gls{rf} signals, and the user decodes their messages.
+		For simplicity, we consider a quasi-static block fading model where channels remain constant within coherence interval while vary independently between consecutive blocks.
 		% Since backscatter modulation involves load switching, tags typically transmit at much lower rate, and we assume the backscatter symbol period is $N \in \mathbb{Z}_{++}$ times the primary symbol period.
-		Since backscatter modulation involves load switching, tags typically transmit at much lower rate, and we assume the backscatter symbol length is $N \in \mathbb{Z}_{++}$ times the primary symbol length.
-		We also assume the direct channel and all cascaded channels can be estimated and fed back to the \gls{ap}.
-		\begin{footnote}
+		Due to physical constraints on load switching, we assume the backscatter symbol period is $N \gg 1$ times longer than primary and consider integer $N$ without loss of generality.
+		We also assume the direct channel and all cascaded channels can be estimated and fed back to the \gls{ap}.%
+		\footnote{
 			Due to the lack of \gls{rf} chains at the passive tag, accurate and efficient \gls{csi} acquisition at the \gls{ap} can be challenging.
-			One possible approach is that the \gls{ap} sends pre-defined pilots, the tags respond in well-designed manners, and the user performs least-square estimation with feedbacks \cite{Bharadia2015,Yang2015b,Guo2019g}.
-		\end{footnote}
+			One possibility is the \gls{ap} sends training pilots, the tags respond in predefined manners, and the user performs least-square estimation with feedbacks \cite{Bharadia2015,Yang2015b,Guo2019g}.
+		}
+		Besides, we omit the signal reflected by two or more times\cite{Wu2019} and ignore the time difference of arrival from different paths\cite{Guo2019b}.
 
-		Consider the signal model during one backscatter symbol period.
-		We assume the primary symbol follows standard \gls{cscg} distribution and the backscatter symbol of all tags employs $M$-\gls{qam}.
-		Under perfect synchronization, the signal received by the user at primary symbol block $n \in \mathcal{N} \triangleq \{1,\ldots,N\}$ is
-		\begin{footnote}
-			We omit the signal reflected by two or more times\cite{Wu2019} and assume the time difference of arrival from different paths are negligible\cite{Guo2019b}.
-		\end{footnote}
+		Denote the \gls{ap}-user direct channel as $\boldsymbol{h}_{\mathrm{D}}^H \in \mathbb{C}^{1 \times Q}$, the \gls{ap}-node $k \in \mathcal{K} \triangleq \{1,\ldots,K\}$ forward channel as $\boldsymbol{h}_{\mathrm{F},k}^H \in \mathbb{C}^{1 \times Q}$, and the node $k$-user backward channel as $h_{\mathrm{B},k}$.
+Also, define the cascaded channel of tag $k$ as $\boldsymbol{h}_{\mathrm{C},k}^H \triangleq h_{\mathrm{B},k} \boldsymbol{h}_{\mathrm{F},k}^H \in \mathbb{C}^{1 \times Q}$.
+		Consider the signal model during one backscatter block (i.e., $N$ primary blocks).
+		% We assume the primary symbol follows standard \gls{cscg} distribution and the backscatter symbol of all tags employs $M$-\gls{qam}.
+		Under perfect synchronization, the signal received by the user at primary block $n \in \mathcal{N} \triangleq \{1,\ldots,N\}$ is
 		\begin{equation}
-			y[n] = \left(\boldsymbol{h}_{\mathrm{D}}^H + \sum_{k \in \mathcal{K}} \sqrt{\alpha_k} \boldsymbol{h}_{\mathrm{C},k}^H x_k\right) \boldsymbol{w} s[n] + w[n],
+			y[n] = \left(\boldsymbol{h}_{\mathrm{D}}^H + \sum_{k \in \mathcal{K}} \sqrt{\alpha_k} \boldsymbol{h}_{\mathrm{C},k}^H x_k\right) \boldsymbol{w} s[n] + v[n],
 			\label{eq:received_signal}
 		\end{equation}
-		where $\alpha_k$ and $x_k$ denote respectively the harvest-backscatter efficiency and backscatter symbol of tag $k$, $s[n]$ and $w[n] \sim \mathcal{CN}(0,\sigma_w^2)$ denote respectively the primary symbol and \gls{awgn} at block $n$, and $\boldsymbol{w} \in \mathbb{C}^{Q \times 1}$ is the transmit precoder satisfying power constraint $\lVert \boldsymbol{w} \rVert^2 \le P$.
-		For the ease of notation, we define $x_{\mathcal{K}} \triangleq \{x_k : k \in \mathcal{K}\}$ as the tag input combination, and $\boldsymbol{y} \triangleq \left[y[1],\ldots,y[N]\right]^T \in \mathbb{C}^{N \times 1}$ as the received signal per backscatter symbol period.
-		For primary transmission, the equivalent channel is subject to backscatter modulation uncertainty as
+		where $\alpha_k$ is the amplitude reflect ratio of Metascatter $k$, $x_k \in \mathcal{X} \triangleq \{\Gamma_1,\ldots,\Gamma_M\}$ is the backscatter symbol of Metascatter $k$, $s \sim \mathcal{CN}(0,1)$ is the primary symbol, $v \sim \mathcal{CN}(0,\sigma_v^2)$ is the \gls{awgn}, $\boldsymbol{w} \in \mathbb{C}^{Q \times 1}$ is the active beamforming vector satisfying the average power constraint $\lVert \boldsymbol{w} \rVert^2 \le P$.
+		The equivalent channel for primary link is subject to backscatter uncertainty
 		\begin{equation}
-			\boldsymbol{h}_{\mathrm{E}}^H(x_{\mathcal{K}}) \triangleq \boldsymbol{h}_{\mathrm{D}}^H + \sum_{k \in \mathcal{K}} \sqrt{\alpha_k} \boldsymbol{h}_{\mathrm{C},k}^H x_k.
+			\boldsymbol{h}_{\mathrm{E}}^H(x_{\mathcal{K}}) \triangleq \boldsymbol{h}_{\mathrm{D}}^H + \sum_{k \in \mathcal{K}} \sqrt{\alpha_k} \boldsymbol{h}_{\mathrm{C},k}^H x_k,
 			\label{eq:equivalent_channel}
 		\end{equation}
+		where $x_{\mathcal{K}} \triangleq \{x_k : k \in \mathcal{K}\}$.
+
+		% where $\alpha_k$ and $x_k$ denote respectively the harvest-backscatter efficiency and backscatter symbol of tag $k$, $s[n]$ and $w[n] \sim \mathcal{CN}(0,\sigma_w^2)$ denote respectively the primary symbol and \gls{awgn} at block $n$, and $\boldsymbol{w} \in \mathbb{C}^{Q \times 1}$ is the transmit precoder satisfying power constraint $\lVert \boldsymbol{w} \rVert^2 \le P$.
+		% For the ease of notation, we define $x_{\mathcal{K}} \triangleq \{x_k : k \in \mathcal{K}\}$ as the tag input combination, and $\boldsymbol{y} \triangleq \left[y[1],\ldots,y[N]\right]^T \in \mathbb{C}^{N \times 1}$ as the received signal per backscatter symbol period.
+		% For primary transmission, the equivalent channel is subject to backscatter modulation uncertainty as
+		% \begin{equation}
+		% 	\boldsymbol{h}_{\mathrm{E}}^H(x_{\mathcal{K}}) \triangleq \boldsymbol{h}_{\mathrm{D}}^H + \sum_{k \in \mathcal{K}} \sqrt{\alpha_k} \boldsymbol{h}_{\mathrm{C},k}^H x_k.
+		% 	\label{eq:equivalent_channel}
+		% \end{equation}
 

### 2022-07-19 main.tex
:pencil: Update receiving strategy

@@
 \usepackage[subtle]{savetrees}
+
+\usepackage{xcolor} \pagecolor[rgb]{0,0,0} \color[rgb]{1,1,1}
 
@@
 \newacronym{dmtmac}{DMTMAC}{Discrete Memoryless Thresholding Multiple Access Channel}
+\newacronym{dtmac}{DTMAC}{Discrete Thresholding Multiple Access Channel}
 \newacronym{dp}{DP}{Dynamic Programming}
@@
 	Moreover, we consider a specific scenario where a multi-antenna \gls{ap} serves a single-antenna user surrounded by multiple Metascatters.
-	For simplicity, it is assumed the user first jointly decodes all backscatter messages based on average received power, then models reflection patterns and backscatter paths within equivalent channel for primary decoding.
+	For simplicity, it is assumed the user first jointly decodes all backscatter messages from accumulated energy, then models reflection patterns and backscatter paths within equivalent channel for primary decoding.
 	% Once modulation uncertainty of Metascatters are eliminated, models contributions from additional paths within equivalent channel
@@
 	% ! An application scenario was considered where multiple Metascatters ride over a point-to-point transmission to simultaneously encode self message and perform passive beamforming.
-	% To fully accommodate backscatter characteristics, we also propose a novel receiving strategy that first jointly decodes all Metascatter based on average received power, then models their reflection patterns and backscatter paths within equivalent channel for primary decoding.
+	% To fully accommodate backscatter characteristics, we also propose a novel receiving strategy that first jointly decodes all Metascatter from accumulated energy, then models their reflection patterns and backscatter paths within equivalent channel for primary decoding.
 	% minor modifications on existing receivers, easy to perform, fits backscatter characteristics.
@@
 	\emph{Second,} we consider an application scenario where multiple Metascatters ride over a point-to-point transmission, exploiting additional propagation paths to simultaneously transmit and assist.
-	To fully accommodate backscatter characteristics, we also propose a novel receiving strategy that first jointly decodes all Metascatter based on average received power, then models their reflection patterns and backscatter paths within equivalent channel for primary decoding.
+	To fully accommodate backscatter characteristics, we also propose a novel receiving strategy that first jointly decodes all Metascatter from accumulated energy, then models their reflection patterns and backscatter paths within equivalent channel for primary decoding.
 	Since backscatter message is modulated over primary signal, backscatter decoding is indeed part of primary channel training, and there is no need for operation-intensive \gls{sic} at the receiver.
@@
 		Denote the \gls{ap}-user direct channel as $\boldsymbol{h}_{\mathrm{D}}^H \in \mathbb{C}^{1 \times Q}$, the \gls{ap}-node $k \in \mathcal{K} \triangleq \{1,\ldots,K\}$ forward channel as $\boldsymbol{h}_{\mathrm{F},k}^H \in \mathbb{C}^{1 \times Q}$, and the node $k$-user backward channel as $h_{\mathrm{B},k}$.
-Also, define the cascaded channel of tag $k$ as $\boldsymbol{h}_{\mathrm{C},k}^H \triangleq h_{\mathrm{B},k} \boldsymbol{h}_{\mathrm{F},k}^H \in \mathbb{C}^{1 \times Q}$.
+Also, define the cascaded channel of tag $k$ as $\boldsymbol{h}_{\mathrm{C},k}^H \triangleq h_{\mathrm{B},k} \boldsymbol{h}_{\mathrm{F},k}^H \in \mathbb{C}^{1 \times Q}$, and $\boldsymbol{H}_{\mathrm{C}} \triangleq [\boldsymbol{h}_{\mathrm{C},1},\ldots,\boldsymbol{h}_{\mathrm{C},K}]^H \in \mathbb{C}^{K \times Q}$.
+		Let $x_{\mathcal{K}} \triangleq \{x_k : k \in \mathcal{K}\}$ be the backscatter symbols of all Metascatters.
 		Consider the signal model during one backscatter block (i.e., $N$ primary blocks).
 		% We assume the primary symbol follows standard \gls{cscg} distribution and the backscatter symbol of all tags employs $M$-\gls{qam}.
-		Under perfect synchronization, the signal received by the user at primary block $n \in \mathcal{N} \triangleq \{1,\ldots,N\}$ is
+		Under perfect synchronization, the equivalent primary channel is a function of backscatter symbols
+		\begin{subequations}
+			\begin{align}
+				\boldsymbol{h}_{\mathrm{E}}^H(x_{\mathcal{K}})
+				 & \triangleq \boldsymbol{h}_{\mathrm{D}}^H + \sum_{k \in \mathcal{K}} \sqrt{\alpha_k} \boldsymbol{h}_{\mathrm{C},k}^H x_k \\
+				 & = \boldsymbol{h}_{\mathrm{D}}^H + \boldsymbol{x}^H \mathrm{diag}(\boldsymbol{\alpha}) \boldsymbol{H}_{\mathrm{C}},
+			\end{align}
+			\label{eq:equivalent_channel}
+		\end{subequations}
+		where $\alpha_k$ is the amplitude reflect ratio of Metascatter $k$, $\boldsymbol{\alpha} \triangleq [\alpha_1,\ldots,\alpha_K]^T \in \mathbb{R}_+^{K \times 1}$, $x_k \in \mathcal{X} \triangleq \{\Gamma_1,\ldots,\Gamma_M\}$ is the backscatter symbol of Metascatter $k$, and $\boldsymbol{x} \triangleq [x_1,\ldots,x_K]^H \in \mathbb{C}^{K \times 1}$.
+The signal received by the user at primary block $n \in \mathcal{N} \triangleq \{1,\ldots,N\}$ is
 		\begin{equation}
-			y[n] = \left(\boldsymbol{h}_{\mathrm{D}}^H + \sum_{k \in \mathcal{K}} \sqrt{\alpha_k} \boldsymbol{h}_{\mathrm{C},k}^H x_k\right) \boldsymbol{w} s[n] + v[n],
-			\label{eq:received_signal}
+			y[n] = \boldsymbol{h}_{\mathrm{E}}^H(x_{\mathcal{K}}) \boldsymbol{w} s[n] + v[n],
 		\end{equation}
-		where $\alpha_k$ is the amplitude reflect ratio of Metascatter $k$, $x_k \in \mathcal{X} \triangleq \{\Gamma_1,\ldots,\Gamma_M\}$ is the backscatter symbol of Metascatter $k$, $s \sim \mathcal{CN}(0,1)$ is the primary symbol, $v \sim \mathcal{CN}(0,\sigma_v^2)$ is the \gls{awgn}, $\boldsymbol{w} \in \mathbb{C}^{Q \times 1}$ is the active beamforming vector satisfying the average power constraint $\lVert \boldsymbol{w} \rVert^2 \le P$.
-		The equivalent channel for primary link is subject to backscatter uncertainty
-		\begin{equation}
-			\boldsymbol{h}_{\mathrm{E}}^H(x_{\mathcal{K}}) \triangleq \boldsymbol{h}_{\mathrm{D}}^H + \sum_{k \in \mathcal{K}} \sqrt{\alpha_k} \boldsymbol{h}_{\mathrm{C},k}^H x_k,
-			\label{eq:equivalent_channel}
-		\end{equation}
-		where $x_{\mathcal{K}} \triangleq \{x_k : k \in \mathcal{K}\}$.
+		where $s \sim \mathcal{CN}(0,1)$ is the primary symbol, $v \sim \mathcal{CN}(0,\sigma_v^2)$ is the \gls{awgn}, and $\boldsymbol{w} \in \mathbb{C}^{Q \times 1}$ is the active beamforming vector with average power constraint $\lVert \boldsymbol{w} \rVert^2 \le P$.
+		% The equivalent channel for primary link is subject to backscatter uncertainty
+		% The equivalent primary channel is a function of backscatter symbols  as
+		% \begin{equation}
+		% 	% \boldsymbol{h}_{\mathrm{E}}^H(x_{\mathcal{K}}) \triangleq \boldsymbol{h}_{\mathrm{D}}^H + \sum_{k \in \mathcal{K}} \sqrt{\alpha_k} \boldsymbol{h}_{\mathrm{C},k}^H x_k.
+		% 	\boldsymbol{h}_{\mathrm{E}}^H(\boldsymbol{x}) \triangleq \boldsymbol{h}_{\mathrm{D}}^H + \boldsymbol{x}^H \mathrm{diag}(\boldsymbol{\alpha}) \boldsymbol{H}_{\mathrm{C}}.
+		% 	\label{eq:equivalent_channel}
+		% \end{equation}
 
@@
 		\begin{remark}
-			Metascatter involves an unconventional \gls{mac} where the primary and backscatter symbols of different duration are mixed by \gls{mc} instead of \gls{sc}.
-			For each tag, the reflection coefficient not only encodes the backscatter message but also influences the equivalent primary channel \eqref{eq:equivalent_channel}.
-			As such, novel receiving strategy other than \gls{sic} should be tailored to signal characteristics to unveil how reflection pattern potentially influences the primary-backscatter tradeoff.
+			Metascatter involves a symbiotic \gls{mac} where the primary and backscatter symbols of different duration are mixed by \gls{mc} instead of \gls{sc}.
+			For each node, the reflection coefficient not only encodes the backscatter message, but also influences the equivalent primary channel \eqref{eq:equivalent_channel}.
+			% As such, novel receiving strategy other than \gls{sic} should be tailored to signal characteristics to unveil how reflection pattern potentially influences the primary-backscatter tradeoff.
+			To accommodate such signal characteristics, novel receiving strategy apart from \gls{sic} is desired to better utilize the reflection pattern and boost the primary-backscatter tradeoff.
 		\end{remark}
@@
 	\begin{subsection}{Receiving Strategy}
-		We propose a novel receiving strategy where the backscatter symbol of all tags are first jointly identified by non-coherent energy detection, then modeled within equivalent channel \eqref{eq:equivalent_channel} as if passive beamforming.
-		Compared with conventional schemes as joint decoding and \gls{sic}, the Metascatter receiver may not achieve as high data rate for one tag, but it avoids non-coherent primary encoding and enables tag multiple access in a practical and low-complexity manner.
-		Therefore, we believe it can be compatible to and readily implemented over legacy point-to-point systems.
+		We propose a Metascatter receiver where the backscatter symbols of all Metascatters are first jointly and semi-coherently detected using total received energy per backscatter block, then modeled within equivalent channel \eqref{eq:equivalent_channel} as dynamic passive beamforming.
+		% identified by non-coherent energy detection, then
+		% Compared with conventional schemes as joint decoding and \gls{sic}, the Metascatter receiver may not achieve as high data rate for one tag, but it avoids non-coherent primary encoding and enables tag multiple access in a practical and low-complexity manner.
+		% Therefore, we believe it can be compatible to and readily implemented over legacy point-to-point systems.
+		Compared with \gls{ml} and \gls{sic}, Metascatter receiver allows practical and low-complexity node multiple access with minor adjustment over legacy equipments.
 
-		Define $m_k \in \mathcal{M}$ as the modulation index of tag $k$, and $m_{\mathcal{K}} \triangleq \{m_k: k \in \mathcal{K}\}$ as the modulation index combination of all tags.
-		Recall that $x_k$ and $x_{\mathcal{K}}$ are random variables representing the backscatter symbol of tag $k$ and the symbol combination of all tags, respectively.
-		Their instances are denoted by modulation index (combination) as $x_{m_k}$ and $x_{m_\mathcal{K}}$.
-		Since any backscatter combination $x_{m_\mathcal{K}}$ remains unchanged over $N$ primary symbol duration, the received signal at symbol block $n$ is only subject to the variation of $s[n]$ and $w[n]$, and follows zero-mean \gls{cscg} distribution with variance
+		At a specific backscatter block, denote $m_k \in \mathcal{M}$ as the state index of Metascatter $k$, and let $m_{\mathcal{K}} \triangleq \{m_k: k \in \mathcal{K}\}$ collect the state indexes of all Metascatters.
+		% The received signal at primary block $n$ is subject to the variation of $s[n]$ and $v[n]$, and thus distributed as $y[n] \sim \mathcal{CN}(0,\sigma_v^2)$
+		Conditioned on $m_{\mathcal{K}}$, the received signal at primary block $n$ is subject to the variation of $s[n]$ and $v[n]$, distributed as $y[n] \sim \mathcal{CN}(0,\sigma_{m_{\mathcal{K}}}^2)$ with
 		\begin{equation}
-			\sigma_{m_{\mathcal{K}}}^2 = \Bigl\lvert \underbrace{\bigl(\boldsymbol{h}_{\mathrm{D}}^H + \sum_{k \in \mathcal{K}} \sqrt{\alpha_k} \boldsymbol{h}_{\mathrm{C},k}^H x_{m_k}\bigr)}_{\boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}})} \boldsymbol{w} \Bigr\rvert^2 + \sigma_w^2.
+			% \sigma_{m_{\mathcal{K}}}^2 = \Bigl\lvert \underbrace{\bigl(\boldsymbol{h}_{\mathrm{D}}^H + \sum_{k \in \mathcal{K}} \sqrt{\alpha_k} \boldsymbol{h}_{\mathrm{C},k}^H x_{m_k}\bigr)}_{\boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}})} \boldsymbol{w} \Bigr\rvert^2 + \sigma_v^2,
+			\sigma_{m_{\mathcal{K}}}^2 = \lvert \boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2 + \sigma_v^2,
 			\label{eq:receive_variance}
 		\end{equation}
-
-		Besides, we denote the total received energy as $z \triangleq \lVert \boldsymbol{y} \rVert^2$ and the hypothesis of modulation index combination $m_{\mathcal{K}}$ as $\mathcal{H}_{m_{\mathcal{K}}}$.
-		Since $z$ is the sum of $N$ \gls{iid} exponential variables, its conditional \gls{pdf} under $\mathcal{H}_{m_{\mathcal{K}}}$ follows Erlang distribution with shape $N$ and scale $\sigma_{m_{\mathcal{K}}}^2$ as
+		where $x_{m_k}$ and $x_{m_\mathcal{K}}$ are the symbol and symbol set associated with state $m_k$ and state set $m_{\mathcal{K}}$, respectively.%
+		\footnote{
+			$x_k$ and $x_{\mathcal{K}}$ are random variables, while $x_{m_k}$ and $x_{m_{\mathcal{K}}}$ are their instances indexed by $m_k$ and $m_{\mathcal{K}}$.
+		}
+		Also, denote the total received energy within backscatter block as $z=\sum_{n=1}^N \lvert y[n] \rvert^2$.
+		% As the sum of $N$ \gls{iid} exponential variables, conditioned on $m_{\mathcal{K}}$, its \gls{pdf} follows Erlang distribution
+		As the sum of $N$ \gls{iid} exponential variables, the \gls{pdf} of $z$ conditioned on $m_{\mathcal{K}}$ follows Erlang distribution
 		\begin{equation}
-			f(z \mid \mathcal{H}_{m_{\mathcal{K}}}) = \frac{z^{N-1} e^{-z/\sigma_{m_{\mathcal{K}}}^2}}{\sigma_{m_{\mathcal{K}}}^{2N} (N-1)!}.
+			f(z \mid \mathcal{H}_{m_{\mathcal{K}}}) = \frac{z^{N-1} e^{-z/\sigma_{m_{\mathcal{K}}}^2}}{\sigma_{m_{\mathcal{K}}}^{2N} (N-1)!},
 			\label{eq:energy_distribution}
 		\end{equation}
-
-		Energy-based backscatter detection essentially formulates a discrete-input continuous-output memoryless \gls{mac}.
-		To further reduce decoding complexity, we divide the continuous output $z$ into disjoint decision regions to construct a \gls{dmtmac}, where the transition probability from tag input combination $x_{m_{\mathcal{K}}}$ to detector output combination $\hat{x}_{m_{\mathcal{K}}'}$ is
+		where $\mathcal{H}_{m_{\mathcal{K}}}$ denotes hypothesis $m_{\mathcal{K}}$.
+		% To accommodate backscatter characteristics and reduce decoding complexity, we consider a joint semi-coherent energy detection for all Metascatters based on disjoint decision regions over accumulated energy $z$.
+		To accommodate backscatter characteristics and reduce decoding complexity, we consider a joint semi-coherent detection for all Metascatters over accumulated energy $z$.
+		% To reduce decoding complexity, we consider a joint semi-coherent energy detection for all Metascatters based on disjoint decision regions over accumulated energy $z$.
+		\begin{figure}[!t]
+			\centering
+			\resizebox{0.95\columnwidth}{!}{
+				\input{assets/energy_distribution.tex}
+			}
+			% \caption{\gls{pdf} of Average Received Power Conditioned on Different Input Hypothesis. Example \gls{ml}.}
+			\caption{
+				\gls{pdf} of total received energy per backscatter block, conditioned on different input hypothesis.
+				% This \gls{ml} decision consists of convex regions and is generally rate-suboptimal except for equiprobable inputs.}
+				Here, the convex \gls{ml} decision regions are generally rate-suboptimal except for equiprobable inputs.
+			}
+			\label{fi:energy_distribution}
+		\end{figure}
+		% The idea is presented in Fig. \ref{fi:energy_distribution}.
+		% As illustrated in Fig. \ref{fi:energy_distribution}, o
+		Once disjoint energy decision regions are determined, we can construct a \gls{dtmac} and formulate the transition probability from input $x_{m_{\mathcal{K}}}$ to output $\hat{x}_{m_{\mathcal{K}}'}$ as
+		% it essentially formulates a \gls{dtmac}, and the transition probability from input $x_{m_{\mathcal{K}}}$ to output $\hat{x}_{m_{\mathcal{K}}'}$ is
 		\begin{equation}
 			P(\hat{x}_{m_{\mathcal{K}}'} \mid x_{m_{\mathcal{K}}}) = \int_{\mathcal{R}_{m_{\mathcal{K}}'}} f(z \mid \mathcal{H}_{m_{\mathcal{K}}}) \dd z,
-			\label{eq:dmtmac}
+			\label{eq:dtmac}
 		\end{equation}
-		where $\mathcal{R}_{m_{\mathcal{K}}'}$ is the decision region over $z$ for hypothesis $\mathcal{H}_{m_{\mathcal{K}}'}$.
+		where $\mathcal{R}_{m_{\mathcal{K}}'}$ is the decision region of hypothesis $\mathcal{H}_{m_{\mathcal{K}}'}$.
+An example of \gls{ml} energy decision is illustrated in Fig.
+\ref{fi:energy_distribution}.
+
+		\begin{remark}
+			% For a general input distribution, not only the optimal decision thresholds
+			The rate-optimal thresholding channel design remains under-investigated, and some attempts were made for single source with binary inputs in \cite{Qian2019b,Nguyen2021b}.
+			% The question was only answered for single source with binary inputs in \cite{Qian2019b,Nguyen2021b}.
+			% Some attempts for single source with binary inputs were presented in \cite{Qian2019b,Nguyen2021b}.
+			For non-binary inputs with general distribution, the optimal decision region for each letter can be non-convex (i.e., with non-adjacent partitions) and the optimal number of thresholds is still unknown.
+			% Next, we will restrict the design over convex decision regions.
+			Next, we will constrain the decision regions to convex and consider suboptimal threshold design accordingly.
+			% Hence,
+			% threshold design papers are constrained to convex quantizer, we may end up using a similar assumption.
+			% decision region design to convex
+
+			% design over convex decision regions.
+
+			% decision regions are first restricted to convex
+
+			% The question was answered in \cite{Qian2019b,Nguyen2021b} only for single source with binary inputs.
+
+			% Even for a single source with non-binary inputs,
+
+			% For a general input distribution, not only the rate-optimal decision thresholds
+			% % Interestingly, the optimal threshold design to maximize the mutual information for a general \gls{dmtc} with a fixed number of output letters remains an open issue.
+			% % The reason is that each decision region may contain more than one disjoint partitions (i.e., non-convex) and the number of thresholds are unknown.
+			% % Fortunately, for the proposed energy detection, we proved that the \gls{dmtc} capacity can be achieved using only convex decision regions.
+			% not only the capacity-achieving thresholding design remains an open problem, but also the optimal number of thresholds for general non-binary-input channels remains unknown.
+		\end{remark}
+
+		% divide the accumulated energy $z$ into disjoint decision regions.
+		% where $x_{m_k}$ is the backscatter symbol associated with state $m_k$ and $x_{m_\mathcal{K}}$ is
+		% and $x_{m_\mathcal{K}}$ are the backscatter symbols associated with state $m_k$ and $m_{\mathcal{K}}$, respectively.
+
+		% At primary block $n$, the received signal
+
+		% Define $m_k \in \mathcal{M}$ as the modulation index of tag $k$, and $m_{\mathcal{K}} \triangleq \{m_k: k \in \mathcal{K}\}$ as the modulation index combination of all tags.
+		% Recall that $x_k$ and $x_{\mathcal{K}}$ are random variables representing the backscatter symbol of tag $k$ and the symbol combination of all tags, respectively.
+		% Their instances are denoted by modulation index (combination) as $x_{m_k}$ and $x_{m_\mathcal{K}}$.
+		% Since any backscatter combination $x_{m_\mathcal{K}}$ remains unchanged over $N$ primary symbol duration, the received signal at symbol block $n$ is only subject to the variation of $s[n]$ and $w[n]$, and follows zero-mean \gls{cscg} distribution with variance
+		% \begin{equation}
+		% 	\sigma_{m_{\mathcal{K}}}^2 = \Bigl\lvert \underbrace{\bigl(\boldsymbol{h}_{\mathrm{D}}^H + \sum_{k \in \mathcal{K}} \sqrt{\alpha_k} \boldsymbol{h}_{\mathrm{C},k}^H x_{m_k}\bigr)}_{\boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}})} \boldsymbol{w} \Bigr\rvert^2 + \sigma_w^2.
+		% 	\label{eq:receive_variance}
+		% \end{equation}
+
+		% Besides, we denote the total received energy as $z \triangleq \lVert \boldsymbol{y} \rVert^2$ and the hypothesis of modulation index combination $m_{\mathcal{K}}$ as $\mathcal{H}_{m_{\mathcal{K}}}$.
+		% Since $z$ is the sum of $N$ \gls{iid} exponential variables, its conditional \gls{pdf} under $\mathcal{H}_{m_{\mathcal{K}}}$ follows Erlang distribution with shape $N$ and scale $\sigma_{m_{\mathcal{K}}}^2$ as
+		% \begin{equation}
+		% 	f(z \mid \mathcal{H}_{m_{\mathcal{K}}}) = \frac{z^{N-1} e^{-z/\sigma_{m_{\mathcal{K}}}^2}}{\sigma_{m_{\mathcal{K}}}^{2N} (N-1)!}.
+		% 	\label{eq:energy_distribution}
+		% \end{equation}
+
+		% Energy-based backscatter detection essentially formulates a discrete-input continuous-output memoryless \gls{mac}.
+		% To further reduce decoding complexity, we divide the continuous output $z$ into disjoint decision regions to construct a \gls{dtmac}, where the transition probability from tag input combination $x_{m_{\mathcal{K}}}$ to detector output combination $\hat{x}_{m_{\mathcal{K}}'}$ is
+		% \begin{equation}
+		% 	P(\hat{x}_{m_{\mathcal{K}}'} \mid x_{m_{\mathcal{K}}}) = \int_{\mathcal{R}_{m_{\mathcal{K}}'}} f(z \mid \mathcal{H}_{m_{\mathcal{K}}}) \dd z,
+		% 	\label{eq:dtmac}
+		% \end{equation}
+		% where $\mathcal{R}_{m_{\mathcal{K}}'}$ is the decision region over $z$ for hypothesis $\mathcal{H}_{m_{\mathcal{K}}'}$.
 	\end{subsection}
@@
 	\begin{subsection}{Input Probability Distribution}
-		For any fixed decision boundary $\boldsymbol{t}$ and transmit precoder $\boldsymbol{w}$, the equivalent \gls{dmtmac} can be formulated by \eqref{eq:dmtmac} and problem \eqref{op:weighted_sum_rate} boils down to
+		For any fixed decision boundary $\boldsymbol{t}$ and transmit precoder $\boldsymbol{w}$, the equivalent \gls{dtmac} can be formulated by \eqref{eq:dtmac} and problem \eqref{op:weighted_sum_rate} boils down to
 		\begin{maxi!}
@@
 	\begin{subsection}{Decision Threshold}
-		\begin{figure}[!t]
-			\centering
-			\resizebox{0.95\columnwidth}{!}{
-				\input{assets/energy_distribution.tex}
-			}
-			\caption{\gls{pdf} of Average Received Power Conditioned on Different Input Hypothesis. Example \gls{ml}.}
-		\end{figure}
 
@@
 		\begin{remark}
-			Since the equivalent source transmits at the total backscatter rate, the \gls{dmtmac} \eqref{eq:dmtmac} is essentially a point-to-point \gls{dmtc} and we can simplify the decision threshold design accordingly.
+			Since the equivalent source transmits at the total backscatter rate, the \gls{dtmac} \eqref{eq:dtmac} is essentially a point-to-point \gls{dmtc} and we can simplify the decision threshold design accordingly.
 			\label{re:input_combination}

### 2022-07-19 main.tex
:pencil: Update achievable rates

@@
 	$\mathbb{R}_+^{x \times y}$ and $\mathbb{C}^{x \times y}$ respectively denote the space of real nonnegative and complex $x \times y$ matrices.
-	$\Delta^n = \left\{ (p_0,\dots,p_n) \in \mathbb{R}_+^{n+1} \mid \sum_{i=0}^n t_i = 1 \right\}$ denotes the standard $n$-simplex.
+	$\Delta^n = \left\{ (p_0,\dots,p_n) \in \mathbb{R}_+^{n+1}|\sum_{i=0}^n t_i = 1 \right\}$ denotes the standard $n$-simplex.
 	% $\Re\{\cdot\}$ retrieves the real part of a complex entity. $[\cdot]_{(n)}$ denotes the $n$-th entry of a vector and $[\cdot]_{(1:n)}$ denotes the first $n$ entries of a vector.
@@
 Also, define the cascaded channel of tag $k$ as $\boldsymbol{h}_{\mathrm{C},k}^H \triangleq h_{\mathrm{B},k} \boldsymbol{h}_{\mathrm{F},k}^H \in \mathbb{C}^{1 \times Q}$, and $\boldsymbol{H}_{\mathrm{C}} \triangleq [\boldsymbol{h}_{\mathrm{C},1},\ldots,\boldsymbol{h}_{\mathrm{C},K}]^H \in \mathbb{C}^{K \times Q}$.
-		Let $x_{\mathcal{K}} \triangleq \{x_k : k \in \mathcal{K}\}$ be the backscatter symbols of all Metascatters.
+		% Let $x_{\mathcal{K}} \triangleq \{x_k : k \in \mathcal{K}\}$ be the backscatter symbols of all Metascatters.
+		Let $x_{\mathcal{K}} \triangleq (x_1,\ldots,x_K)$ be the backscatter symbol tuple of all Metascatters.
 		Consider the signal model during one backscatter block (i.e., $N$ primary blocks).
@@
 		\begin{subequations}
+			\label{eq:equivalent_channel}
 			\begin{align}
@@
 			\end{align}
-			\label{eq:equivalent_channel}
 		\end{subequations}
@@
 
-		At a specific backscatter block, denote $m_k \in \mathcal{M}$ as the state index of Metascatter $k$, and let $m_{\mathcal{K}} \triangleq \{m_k: k \in \mathcal{K}\}$ collect the state indexes of all Metascatters.
+		% At a specific backscatter block, denote $m_k \in \mathcal{M}$ as the state index of Metascatter $k$, and let $m_{\mathcal{K}} \triangleq \{m_k: k \in \mathcal{K}\}$ collect the state indexes of all Metascatters.
+		At a specific backscatter block, denote $m_k \in \mathcal{M}$ as the state index of Metascatter $k$, and let $m_{\mathcal{K}} \triangleq (m_1,\ldots,m_K)$ be the state index tuple of all Metascatters.
 		% The received signal at primary block $n$ is subject to the variation of $s[n]$ and $v[n]$, and thus distributed as $y[n] \sim \mathcal{CN}(0,\sigma_v^2)$
@@
 		\end{equation}
-		where $x_{m_k}$ and $x_{m_\mathcal{K}}$ are the symbol and symbol set associated with state $m_k$ and state set $m_{\mathcal{K}}$, respectively.%
+		where $x_{m_k}$ and $x_{m_\mathcal{K}}$ are the symbol and symbol tuple associated with state $m_k$ and state tuple $m_{\mathcal{K}}$, respectively.%
 		\footnote{
@@
 		\begin{equation}
-			f(z \mid \mathcal{H}_{m_{\mathcal{K}}}) = \frac{z^{N-1} e^{-z/\sigma_{m_{\mathcal{K}}}^2}}{\sigma_{m_{\mathcal{K}}}^{2N} (N-1)!},
+			f(z|\mathcal{H}_{m_{\mathcal{K}}}) = \frac{z^{N-1} e^{-z/\sigma_{m_{\mathcal{K}}}^2}}{\sigma_{m_{\mathcal{K}}}^{2N} (N-1)!},
 			\label{eq:energy_distribution}
@@
 			\centering
-			\resizebox{0.95\columnwidth}{!}{
+			\resizebox{0.9\columnwidth}{!}{
 				\input{assets/energy_distribution.tex}
@@
 		\begin{equation}
-			P(\hat{x}_{m_{\mathcal{K}}'} \mid x_{m_{\mathcal{K}}}) = \int_{\mathcal{R}_{m_{\mathcal{K}}'}} f(z \mid \mathcal{H}_{m_{\mathcal{K}}}) \dd z,
+			P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}}) = \int_{\mathcal{R}_{m_{\mathcal{K}}'}} f(z|\mathcal{H}_{m_{\mathcal{K}}}) \dd z,
 			\label{eq:dtmac}
@@
 			% Next, we will restrict the design over convex decision regions.
-			Next, we will constrain the decision regions to convex and consider suboptimal threshold design accordingly.
-			% Hence,
-			% threshold design papers are constrained to convex quantizer, we may end up using a similar assumption.
-			% decision region design to convex
-
-			% design over convex decision regions.
-
-			% decision regions are first restricted to convex
-
-			% The question was answered in \cite{Qian2019b,Nguyen2021b} only for single source with binary inputs.
-
-			% Even for a single source with non-binary inputs,
-
+			Next, we will constrain all decision regions to convex and consider suboptimal threshold design accordingly.
 			% For a general input distribution, not only the rate-optimal decision thresholds
@@
 		\end{remark}
-
-		% divide the accumulated energy $z$ into disjoint decision regions.
-		% where $x_{m_k}$ is the backscatter symbol associated with state $m_k$ and $x_{m_\mathcal{K}}$ is
-		% and $x_{m_\mathcal{K}}$ are the backscatter symbols associated with state $m_k$ and $m_{\mathcal{K}}$, respectively.
-
-		% At primary block $n$, the received signal
-
-		% Define $m_k \in \mathcal{M}$ as the modulation index of tag $k$, and $m_{\mathcal{K}} \triangleq \{m_k: k \in \mathcal{K}\}$ as the modulation index combination of all tags.
-		% Recall that $x_k$ and $x_{\mathcal{K}}$ are random variables representing the backscatter symbol of tag $k$ and the symbol combination of all tags, respectively.
-		% Their instances are denoted by modulation index (combination) as $x_{m_k}$ and $x_{m_\mathcal{K}}$.
-		% Since any backscatter combination $x_{m_\mathcal{K}}$ remains unchanged over $N$ primary symbol duration, the received signal at symbol block $n$ is only subject to the variation of $s[n]$ and $w[n]$, and follows zero-mean \gls{cscg} distribution with variance
+	\end{subsection}
+
+	\begin{subsection}{Achievable Rates}
+		Denote the input probability of state $m_k$ of Metascatter node $k$ as $P_k(x_{m_k})$, and define the input probability distribution vector of node $k$ as $\boldsymbol{p}_k \triangleq [P_k(\Gamma_1),\ldots,P_k(\Gamma_M)]^T \in \mathbb{R}^{M \times 1}$.
+With independent encoding at all nodes, the probability of backscatter symbol tuple $x_{m_{\mathcal{K}}}$ is $P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) = \prod_{k \in \mathcal{K}} P_k(x_{m_k})$.
+		% Denote the input probability distribution vector of tag $k$ as $\boldsymbol{p}_k \triangleq [P_k(x_1),\ldots,P_k(x_M)]^T \in \mathbb{R}^{M \times 1}$, where $P_k(x_{m_k})$ is the probability at state $m_k$.
+		% Consider independent encoding at all tags such that the probability of input combination $x_{m_{\mathcal{K}}}$ is $P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) = \prod_{k \in \mathcal{K}} P_k(x_{m_k})$.
+		% The backscatter information function of input combination $x_{m_{\mathcal{K}}}$ is defined as
+		Similar to \cite{Rezaeian2004}, we define the backscatter information function between input symbol tuple instance $x_{m_{\mathcal{K}}}$ and output symbol tuple $\hat{x}_{\mathcal{K}}$ as
+		\begin{equation}
+			I^{\mathrm{B}}(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}}) \triangleq \sum_{m_{\mathcal{K}}'} P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}}) \log \frac{P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}})}{P(\hat{x}_{m_{\mathcal{K}}'})},
+			\label{eq:backscatter_information_function}
+		\end{equation}
+		where $P(\hat{x}_{m_{\mathcal{K}}'}) = \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}})$.
+		We also define the backscatter marginal information of letter $x_{m_k}$ of node $k$ as
+		% Besides, the backscatter marginal information function associated with letter $x_{m_k}$ of tag $k$ is
+		\begin{equation}
+			% I_{\mathrm{B},k}(x_{m_k};\hat{x}_{\mathcal{K}}) \triangleq \sum_{m_{\mathcal{K} \setminus \{k\}}} P_{\mathcal{K} \setminus \{k\}}(x_{m_{\mathcal{K} \setminus \{k\}}}) I_{\mathrm{B}}(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}}),
+			I^{\mathrm{B}}_{k}(x_{m_k};\hat{x}_{\mathcal{K}}) \triangleq \sum_{m_{\mathcal{K} \setminus \{k\}}} P_{\mathcal{K} \setminus \{k\}}(x_{m_{\mathcal{K} \setminus \{k\}}}) I^{\mathrm{B}}(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}}),
+			\label{eq:backscatter_marginal_information_function}
+		\end{equation}
+		where $P_{\mathcal{K} \setminus \{k\}}(x_{m_{\mathcal{K} \setminus \{k\}}}) = \prod_{q \in \mathcal{K} \setminus \{k\}} P_{q}(x_{m_{q}})$.
+		Moreover, we can write the backscatter mutual information as
+		\begin{equation}
+			% I^{\mathrm{B}}(x_{\mathcal{K}};\hat{x}_{\mathcal{K}}) = \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) \sum_{m_{\mathcal{K}}'} P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}}) \log \frac{P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}})}{P(\hat{x}_{m_{\mathcal{K}}'})}.
+			I^{\mathrm{B}}(x_{\mathcal{K}};\hat{x}_{\mathcal{K}}) = \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) I^{\mathrm{B}}(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}}).
+			\label{eq:backscatter_mutual_information}
+		\end{equation}
+
+		% Once the tag input combination is successfully decoded, the backscatter uncertainty can be eliminated and the equivalent channel for primary transmission can be updated by \eqref{eq:equivalent_channel}.
+		Once backscatter symbols are successfully decoded, we can eliminate modulation uncertainty and retrieve equivalent primary channel by \eqref{eq:equivalent_channel}.
+We define the primary information function conditioned on backscatter symbol tuple $x_{m_{\mathcal{K}}}$ as
 		% \begin{equation}
-		% 	\sigma_{m_{\mathcal{K}}}^2 = \Bigl\lvert \underbrace{\bigl(\boldsymbol{h}_{\mathrm{D}}^H + \sum_{k \in \mathcal{K}} \sqrt{\alpha_k} \boldsymbol{h}_{\mathrm{C},k}^H x_{m_k}\bigr)}_{\boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}})} \boldsymbol{w} \Bigr\rvert^2 + \sigma_w^2.
-		% 	\label{eq:receive_variance}
+		% 	I_{\mathrm{P}}(x_{m_{\mathcal{K}}};\boldsymbol{y}) \triangleq \log \left(1 + \frac{\lvert \boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_w^2}\right),
+		% 	\label{eq:primary_information_function}
 		% \end{equation}
-
-		% Besides, we denote the total received energy as $z \triangleq \lVert \boldsymbol{y} \rVert^2$ and the hypothesis of modulation index combination $m_{\mathcal{K}}$ as $\mathcal{H}_{m_{\mathcal{K}}}$.
-		% Since $z$ is the sum of $N$ \gls{iid} exponential variables, its conditional \gls{pdf} under $\mathcal{H}_{m_{\mathcal{K}}}$ follows Erlang distribution with shape $N$ and scale $\sigma_{m_{\mathcal{K}}}^2$ as
-		% \begin{equation}
-		% 	f(z \mid \mathcal{H}_{m_{\mathcal{K}}}) = \frac{z^{N-1} e^{-z/\sigma_{m_{\mathcal{K}}}^2}}{\sigma_{m_{\mathcal{K}}}^{2N} (N-1)!}.
-		% 	\label{eq:energy_distribution}
-		% \end{equation}
-
-		% Energy-based backscatter detection essentially formulates a discrete-input continuous-output memoryless \gls{mac}.
-		% To further reduce decoding complexity, we divide the continuous output $z$ into disjoint decision regions to construct a \gls{dtmac}, where the transition probability from tag input combination $x_{m_{\mathcal{K}}}$ to detector output combination $\hat{x}_{m_{\mathcal{K}}'}$ is
-		% \begin{equation}
-		% 	P(\hat{x}_{m_{\mathcal{K}}'} \mid x_{m_{\mathcal{K}}}) = \int_{\mathcal{R}_{m_{\mathcal{K}}'}} f(z \mid \mathcal{H}_{m_{\mathcal{K}}}) \dd z,
-		% 	\label{eq:dtmac}
-		% \end{equation}
-		% where $\mathcal{R}_{m_{\mathcal{K}}'}$ is the decision region over $z$ for hypothesis $\mathcal{H}_{m_{\mathcal{K}}'}$.
-	\end{subsection}
-
-	\begin{subsection}{Achievable Rates}
-		Denote the input probability distribution vector of tag $k$ as $\boldsymbol{p}_k \triangleq [P_k(x_1),\ldots,P_k(x_M)]^T \in \mathbb{R}^{M \times 1}$, where $P_k(x_{m_k})$ is the probability at state $m_k$.
-		Consider independent encoding at all tags such that the probability of input combination $x_{m_{\mathcal{K}}}$ is $P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) = \prod_{k \in \mathcal{K}} P_k(x_{m_k})$.
-		The backscatter information function of input combination $x_{m_{\mathcal{K}}}$ is defined as
-		\begin{equation}
-			I_{\mathrm{B}}(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}}) \triangleq \sum_{m_{\mathcal{K}}'} P(\hat{x}_{m_{\mathcal{K}}'} \mid x_{m_{\mathcal{K}}}) \log \frac{P(\hat{x}_{m_{\mathcal{K}}'} \mid x_{m_{\mathcal{K}}})}{P(\hat{x}_{m_{\mathcal{K}}'})},
-			\label{eq:backscatter_information_function}
-		\end{equation}
-		where $P(\hat{x}_{m_{\mathcal{K}}'}) = \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) P(\hat{x}_{m_{\mathcal{K}}'} \mid x_{m_{\mathcal{K}}})$.
-		Besides, the backscatter marginal information function associated with letter $x_{m_k}$ of tag $k$ is
-		\begin{equation}
-			I_{\mathrm{B},k}(x_{m_k};\hat{x}_{\mathcal{K}}) \triangleq \sum_{m_{\mathcal{K} \setminus \{k\}}} P_{\mathcal{K} \setminus \{k\}}(x_{m_{\mathcal{K} \setminus \{k\}}}) I_{\mathrm{B}}(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}}),
-			\label{eq:backscatter_marginal_information_function}
-		\end{equation}
-		where $P_{\mathcal{K} \setminus \{k\}}(x_{m_{\mathcal{K} \setminus \{k\}}}) = \prod_{q \in \mathcal{K} \setminus \{k\}} P_{q}(x_{m_{q}})$.
-		Therefore, the backscatter mutual information is
-		\begin{equation}
-			I_{\mathrm{B}}(x_{\mathcal{K}};\hat{x}_{\mathcal{K}}) = \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) \sum_{m_{\mathcal{K}}'} P(\hat{x}_{m_{\mathcal{K}}'} \mid x_{m_{\mathcal{K}}}) \log \frac{P(\hat{x}_{m_{\mathcal{K}}'} \mid x_{m_{\mathcal{K}}})}{P(\hat{x}_{m_{\mathcal{K}}'})}.
-			\label{eq:backscatter_mutual_information}
-		\end{equation}
-
-		Once the tag input combination is successfully decoded, the backscatter uncertainty can be eliminated and the equivalent channel for primary transmission can be updated by \eqref{eq:equivalent_channel}.
-		Similar to above, the primary information function of input combination $x_{m_{\mathcal{K}}}$ is
-		% TODO notation
-		\begin{equation}
-			I_{\mathrm{P}}(x_{m_{\mathcal{K}}};\boldsymbol{y}) \triangleq \log_2 \left(1 + \frac{\lvert \boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_w^2}\right),
+		\begin{equation}
+			I^{\mathrm{P}}(s;y|x_{m_{\mathcal{K}}}) \triangleq \log \left(1 + \frac{\lvert \boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_w^2}\right),
 			\label{eq:primary_information_function}
 		\end{equation}
-		the primary marginal information function associated with letter $x_{m_k}$ of tag $k$ is
-		\begin{equation}
-			I_{\mathrm{P},k}(x_{m_k};\boldsymbol{y}) \triangleq \sum_{m_{\mathcal{K} \setminus \{k\}}} P_{\mathcal{K} \setminus \{k\}}(x_{m_{\mathcal{K} \setminus \{k\}}}) I_{\mathrm{P}}(x_{m_{\mathcal{K}}};\boldsymbol{y}),
+		the primary marginal information conditioned on letter $x_{m_k}$ of node $k$ as
+		% the primary marginal information function associated with letter $x_{m_k}$ of tag $k$ is
+		\begin{equation}
+			I^{\mathrm{P}}_{k}(s;y|x_{m_k}) \triangleq \sum_{m_{\mathcal{K} \setminus \{k\}}} P_{\mathcal{K} \setminus \{k\}}(x_{m_{\mathcal{K} \setminus \{k\}}}) I^{\mathrm{P}}(s;y|x_{m_{\mathcal{K}}}),
 			\label{eq:primary_marginal_information_function}
 		\end{equation}
-		and the primary (ergodic) mutual information is
-		\begin{equation}
-			I_{\mathrm{P}}(x_{\mathcal{K}};\boldsymbol{y}) = \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) \log_2 \left(1 + \frac{\lvert \boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_w^2}\right).
+		and the primary ergodic mutual information as
+		% and the primary (ergodic) mutual information is
+		\begin{equation}
+			% I^{\mathrm{P}}(s;y|x_{\mathcal{K}}) = \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) \log \left(1 + \frac{\lvert \boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_w^2}\right).
+			I^{\mathrm{P}}(s;y|x_{\mathcal{K}}) = \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) I^{\mathrm{P}}(s;y|x_{m_{\mathcal{K}}}).
 			\label{eq:primary_mutual_information}
@@
 
-		Therefore, the weighted sum information function, marginal information function, and mutual information of primary and backscatter links are respectively given by
+		% Moreover, with $\rho \in [0,1]$ being the relative priority of the primary link, we define corresponding weighted sum information function, marginal information, and mutual information respectively as
+		Finally, with a slight abuse of notation, we define the corresponding weighted sum information function, marginal information, and mutual information respectively as
 		\begin{align}
-			I(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}},\boldsymbol{y})
-			 & \triangleq \rho I_{\mathrm{P}}(x_{m_{\mathcal{K}}};\boldsymbol{y}) + (1 - \rho) I_{\mathrm{B}}(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}}),\label{eq:weighted_sum_information_function} \\
-			I_k(x_{m_k};\hat{x}_{\mathcal{K}},\boldsymbol{y})
-			 & \triangleq \rho I_{\mathrm{P},k}(x_{m_k};\boldsymbol{y}) + (1 - \rho) I_{\mathrm{B},k}(x_{m_k};\hat{x}_{\mathcal{K}}),\label{eq:weighted_sum_marginal_information}                     \\
-			I(x_{\mathcal{K}};\hat{x}_{\mathcal{K}},\boldsymbol{y})
-			 & \triangleq \rho I_{\mathrm{P}}(x_{\mathcal{K}};\boldsymbol{y}) + (1 - \rho) I_{\mathrm{B}}(x_{\mathcal{K}};\hat{x}_{\mathcal{K}}),\label{eq:weighted_sum_mutual_information}
+			I(x_{m_{\mathcal{K}}})
+			 & \triangleq \rho I^{\mathrm{P}}(s;y|x_{m_{\mathcal{K}}}) + (1 - \rho) I^{\mathrm{B}}(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}}),\label{eq:weighted_sum_information_function} \\
+			I_k(x_{m_k})
+			 & \triangleq \rho I^{\mathrm{P}}_{k}(s;y|x_{m_k}) + (1 - \rho) I^{\mathrm{B}}_{k}(x_{m_k};\hat{x}_{\mathcal{K}}),\label{eq:weighted_sum_marginal_information}                 \\
+			I(x_{\mathcal{K}})
+			 & \triangleq \rho I^{\mathrm{P}}(s;y|x_{\mathcal{K}}) + (1 - \rho) I^{\mathrm{B}}(x_{\mathcal{K}};\hat{x}_{\mathcal{K}}),\label{eq:weighted_sum_mutual_information}
 		\end{align}
-		where $\rho \in [0,1]$ represents the priority of the primary link.
+		where $\rho \in [0,1]$ is the relative priority of the primary link.
+
+		% Therefore, the weighted sum information function, marginal information function, and mutual information of primary and backscatter links are respectively given by
+		% \begin{align}
+		% 	I(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}},\boldsymbol{y})
+		% 	 & \triangleq \rho I_{\mathrm{P}}(x_{m_{\mathcal{K}}};\boldsymbol{y}) + (1 - \rho) I_{\mathrm{B}}(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}}),\label{eq:weighted_sum_information_function} \\
+		% 	I_k(x_{m_k};\hat{x}_{\mathcal{K}},\boldsymbol{y})
+		% 	 & \triangleq \rho I_{\mathrm{P},k}(x_{m_k};\boldsymbol{y}) + (1 - \rho) I_{\mathrm{B},k}(x_{m_k};\hat{x}_{\mathcal{K}}),\label{eq:weighted_sum_marginal_information}                     \\
+		% 	I(x_{\mathcal{K}};\hat{x}_{\mathcal{K}},\boldsymbol{y})
+		% 	 & \triangleq \rho I_{\mathrm{P}}(x_{\mathcal{K}};\boldsymbol{y}) + (1 - \rho) I_{\mathrm{B}}(x_{\mathcal{K}};\hat{x}_{\mathcal{K}}),\label{eq:weighted_sum_mutual_information}
+		% \end{align}
+		% where $\rho \in [0,1]$ represents the priority of the primary link.
 	\end{subsection}
@@
 
-\begin{section}{Input, Threshold, and Precoder Design}
+\begin{section}{Input Distribution, Decision Threshold, and Active Beamformer Design}
 	To characterize the achievable primary-(total-)backscatter rate region of Metascatter, we aim to maximize the weighted sum mutual information with respect to tag input probability distribution $\{\boldsymbol{p}_k\}$, decision threshold vector $\boldsymbol{t}$, and transmit precoder $\boldsymbol{w}$
 	\begin{maxi!}
-		{\scriptstyle{\{\boldsymbol{p}_k\},\boldsymbol{t},\boldsymbol{w}}}{I(x_{\mathcal{K}};\hat{x}_{\mathcal{K}},\boldsymbol{y})}{\label{op:weighted_sum_rate}}{\label{ob:weighted_sum_rate}}
+		{\scriptstyle{\{\boldsymbol{p}_k\},\boldsymbol{t},\boldsymbol{w}}}{I(x_{\mathcal{K}})}{\label{op:weighted_sum_rate}}{\label{ob:weighted_sum_rate}}
 		\addConstraint{\sum \nolimits_{m_k} P_k(x_{m_k})}{=1,}{\quad \forall k \in \mathcal{K}}{\label{co:sum_probability}}
@@
 		\begin{maxi!}
-			{\scriptstyle{\{\boldsymbol{p}_k\}}}{I(x_{\mathcal{K}};\hat{x}_{\mathcal{K}},\boldsymbol{y})}{\label{op:input_probability_distribution}}{}
+			{\scriptstyle{\{\boldsymbol{p}_k\}}}{I(x_{\mathcal{K}})}{\label{op:input_probability_distribution}}{}
 			\addConstraint{\eqref{co:sum_probability},\eqref{co:nonnegative_probability},}
@@
 				\begin{alignat}{2}
-					I_k^\star(x_{m_k};\hat{x}_{\mathcal{K}},\boldsymbol{y}) & = I^\star(x_{\mathcal{K}};\hat{x}_{\mathcal{K}},\boldsymbol{y}), \quad   &  & P_k^\star(x_{m_k}) > 0,\label{eq:probable_states} \\
-					I_k^\star(x_{m_k};\hat{x}_{\mathcal{K}},\boldsymbol{y}) & \le I^\star(x_{\mathcal{K}};\hat{x}_{\mathcal{K}},\boldsymbol{y}), \quad &  & P_k^\star(x_{m_k}) = 0.\label{eq:dropped_states}
+					I_k^\star(x_{m_k}) & = I^\star(x_{\mathcal{K}}), \quad   &  & P_k^\star(x_{m_k}) > 0,\label{eq:probable_states} \\
+					I_k^\star(x_{m_k}) & \le I^\star(x_{\mathcal{K}}), \quad &  & P_k^\star(x_{m_k}) = 0.\label{eq:dropped_states}
 				\end{alignat}
@@
 			\begin{equation}
-				P_k^{(r+1)}(x_{m_k}) = \frac{P_k^{(r)}(x_{m_k}) \exp \left( \frac{\rho}{1 - \rho} I_k^{(r)}(x_{m_k};\hat{x}_{\mathcal{K}},\boldsymbol{y}) \right)}{\sum_{m_k'} P_k^{(r)}(x_{m_k'}) \exp \left( \frac{\rho}{1 - \rho} I_k^{(r)}(x_{m_k'};\hat{x}_{\mathcal{K}},\boldsymbol{y}) \right)},
+				P_k^{(r+1)}(x_{m_k}) = \frac{P_k^{(r)}(x_{m_k}) \exp \left( \frac{\rho}{1 - \rho} I_k^{(r)}(x_{m_k}) \right)}{\sum_{m_k'} P_k^{(r)}(x_{m_k'}) \exp \left( \frac{\rho}{1 - \rho} I_k^{(r)}(x_{m_k'}) \right)},
 				\label{eq:input_kkt_solution}
@@
 			L
-			 & = - I(x_{\mathcal{K}};\hat{x}_{\mathcal{K}},\boldsymbol{y}) + \sum_{k \in \mathcal{K}} \nu_k \left( \sum_{m_k \in \mathcal{M}} P_k(x_{m_k}) - 1 \right)\nonumber \\
+			 & = - I(x_{\mathcal{K}}) + \sum_{k \in \mathcal{K}} \nu_k \left( \sum_{m_k \in \mathcal{M}} P_k(x_{m_k}) - 1 \right)\nonumber \\
 			 & \quad - \sum_{k \in \mathcal{K}} \sum_{m_k \in \mathcal{M}} \lambda_{k,m_k} P_k(x_{m_k}),
@@
 			\begin{equation}
-				- \nabla_{P_k^\star(x_{m_k})} I^\star(x_{\mathcal{K}};\hat{x}_{\mathcal{K}},\boldsymbol{y}) + \nu_k^\star - \lambda_{k,m_k}^\star = 0,
+				- \nabla_{P_k^\star(x_{m_k})} I^\star(x_{\mathcal{K}}) + \nu_k^\star - \lambda_{k,m_k}^\star = 0,
 			\end{equation}
@@
 		\begin{equation}
-			\nabla_{P_k^\star(x_{m_k})} I^\star(x_{\mathcal{K}};\hat{x}_{\mathcal{K}},\boldsymbol{y}) = I_k^\star(x_{m_k};\hat{x}_{\mathcal{K}},\boldsymbol{y}) - (1 - \rho).
+			\nabla_{P_k^\star(x_{m_k})} I^\star(x_{\mathcal{K}}) = I_k^\star(x_{m_k}) - (1 - \rho).
 			\label{eq:input_directional_derivative}
@@
 			\begin{alignat}{2}
-				I_k^\star(x_{m_k};\hat{x}_{\mathcal{K}},\boldsymbol{y}) & = \nu_k^\star + (1 - \rho), \quad   &  & P_k^\star(x_{m_k}) > 0,\label{eq:probable_states_marginal} \\
-				I_k^\star(x_{m_k};\hat{x}_{\mathcal{K}},\boldsymbol{y}) & \le \nu_k^\star + (1 - \rho), \quad &  & P_k^\star(x_{m_k}) = 0,\label{eq:dropped_states_marginal}
+				I_k^\star(x_{m_k}) & = \nu_k^\star + (1 - \rho), \quad   &  & P_k^\star(x_{m_k}) > 0,\label{eq:probable_states_marginal} \\
+				I_k^\star(x_{m_k}) & \le \nu_k^\star + (1 - \rho), \quad &  & P_k^\star(x_{m_k}) = 0,\label{eq:dropped_states_marginal}
 			\end{alignat}
@@
 		\begin{equation}
-			\sum_{m_k} P_k^\star(x_{m_k}) I_k^\star(x_{m_k};\hat{x}_{\mathcal{K}},\boldsymbol{y}) = \nu_k^\star + (1 - \rho).
+			\sum_{m_k} P_k^\star(x_{m_k}) I_k^\star(x_{m_k}) = \nu_k^\star + (1 - \rho).
 			\label{eq:input_kkt_condition_implied}
@@
 		\begin{equation}
-			\sum_{m_k} P_k^\star(x_{m_k}) I_k^\star(x_{m_k};\hat{x}_{\mathcal{K}},\boldsymbol{y}) = I^\star(x_{\mathcal{K}};\hat{x}_{\mathcal{K}},\boldsymbol{y}),
+			\sum_{m_k} P_k^\star(x_{m_k}) I_k^\star(x_{m_k}) = I^\star(x_{\mathcal{K}}),
 			\label{eq:weighted_sum_marginal_information_implied}
@@
 				J \left( P_{\mathcal{K}}(x_{m_{\mathcal{K}}}),P_{\mathcal{K}}'(x_{m_{\mathcal{K}}}) \right)
-				 & \triangleq \rho \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) \log_2 \left(1 + \frac{\lvert \boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_w^2}\right)\nonumber                                                                                                                            \\
-				 & \quad + (1 - \rho) \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) \sum_{m_{\mathcal{K}}'} P(\hat{x}_{m_{\mathcal{K}}'} \mid x_{m_{\mathcal{K}}}) \log \frac{P(\hat{x}_{m_{\mathcal{K}}'} \mid x_{m_{\mathcal{K}}}) P_{\mathcal{K}}'(x_{m_{\mathcal{K}}})}{P'(\hat{x}_{m_{\mathcal{K}}'}) P_{\mathcal{K}}(x_{m_{\mathcal{K}}})}.
+				 & \triangleq \rho \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) \log \left(1 + \frac{\lvert \boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_w^2}\right)\nonumber                                                                                                                    \\
+				 & \quad + (1 - \rho) \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) \sum_{m_{\mathcal{K}}'} P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}}) \log \frac{P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}}) P_{\mathcal{K}}'(x_{m_{\mathcal{K}}})}{P'(\hat{x}_{m_{\mathcal{K}}'}) P_{\mathcal{K}}(x_{m_{\mathcal{K}}})}.
 				\label{eq:intermediate_information_function}
@@
 		\end{figure*}
-		It is straightforward to verify $J \left( P_{\mathcal{K}}(x_{m_{\mathcal{K}}}),P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) \right) = I(x_{\mathcal{K}};\hat{x}_{\mathcal{K}},\boldsymbol{y})$ and $J \left( P_{\mathcal{K}}(x_{m_{\mathcal{K}}}),P_{\mathcal{K}}'(x_{m_{\mathcal{K}}}) \right)$ is a concave function for a fixed $P_{\mathcal{K}}'(x_{m_{\mathcal{K}}})$.
+		It is straightforward to verify $J \left( P_{\mathcal{K}}(x_{m_{\mathcal{K}}}),P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) \right) = I(x_{\mathcal{K}})$ and $J \left( P_{\mathcal{K}}(x_{m_{\mathcal{K}}}),P_{\mathcal{K}}'(x_{m_{\mathcal{K}}}) \right)$ is a concave function for a fixed $P_{\mathcal{K}}'(x_{m_{\mathcal{K}}})$.
 		By choosing $\nabla_{P_k^\star(x_{m_k})} J \left( P_{\mathcal{K}}(x_{m_{\mathcal{K}}}),P_{\mathcal{K}}'(x_{m_{\mathcal{K}}}) \right) = 0$, we have
@@
 			S_k'(x_{m_k})
-			 & \triangleq I_k'(x_{m_k};\hat{x}_{\mathcal{K}},\boldsymbol{y}) + (1 - \rho) \sum_{m_{\mathcal{K} \setminus \{k\}}} P_{\mathcal{K} \setminus \{k\}}(x_{m_{\mathcal{K} \setminus \{k\}}})\nonumber \\
-			 & \quad \times \sum_{m_{\mathcal{K}}'} P(\hat{x}_{m_{\mathcal{K}}'} \mid x_{m_{\mathcal{K}}}) \log P_{\mathcal{K}}'(x_{m_{\mathcal{K}}}).
+			 & \triangleq I_k'(x_{m_k}) + (1 - \rho) \sum_{m_{\mathcal{K} \setminus \{k\}}} P_{\mathcal{K} \setminus \{k\}}(x_{m_{\mathcal{K} \setminus \{k\}}})\nonumber \\
+			 & \quad \times \sum_{m_{\mathcal{K}}'} P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}}) \log P_{\mathcal{K}}'(x_{m_{\mathcal{K}}}).
 		\end{align}
@@
 		\begin{equation}
-			P_k^\star(x_{m_k}) = \frac{P_k'(x_{m_k}) \exp \left( \frac{\rho}{1 - \rho} I_k'(x_{m_k};\hat{x}_{\mathcal{K}},\boldsymbol{y}) \right)}{\sum_{m_k'} P_k'(x_{m_k'}) \exp \left( \frac{\rho}{1 - \rho} I_k'(x_{m_k'};\hat{x}_{\mathcal{K}},\boldsymbol{y}) \right)}.
+			P_k^\star(x_{m_k}) = \frac{P_k'(x_{m_k}) \exp \left( \frac{\rho}{1 - \rho} I_k'(x_{m_k}) \right)}{\sum_{m_k'} P_k'(x_{m_k'}) \exp \left( \frac{\rho}{1 - \rho} I_k'(x_{m_k'}) \right)}.
 			\label{eq:optimal_relative_distribution}
@@
 		\begin{equation}
-			J \left( P_{\mathcal{K}}(x_{m_{\mathcal{K}}}),P_{\mathcal{K}}'(x_{m_{\mathcal{K}}}) \right) \ge I'(x_{\mathcal{K}};\hat{x}_{\mathcal{K}},\boldsymbol{y}).
+			J \left( P_{\mathcal{K}}(x_{m_{\mathcal{K}}}),P_{\mathcal{K}}'(x_{m_{\mathcal{K}}}) \right) \ge I'(x_{\mathcal{K}}).
 			\label{eq:information_difference_lower}
@@
 				\Delta
-				 & \triangleq I(x_{\mathcal{K}};\hat{x}_{\mathcal{K}},\boldsymbol{y}) - J \left( P_{\mathcal{K}}(x_{m_{\mathcal{K}}}),P_{\mathcal{K}}'(x_{m_{\mathcal{K}}}) \right)                                                                                                                               \\
-				 & = (1 - \rho) \sum_{m_k} \frac{P_k'(x_{m_k}) f_k'(x_{m_k};\hat{x}_{\mathcal{K}},\boldsymbol{y})}{\sum_{m_k'} P_k'(x_{m_k'}) f_k'(x_{m_k'};\hat{x}_{\mathcal{K}},\boldsymbol{y})} \sum_{m_{\mathcal{K}}''} P(\hat{x}_{m_{\mathcal{K}}''} \mid x_{m_k})\nonumber                                  \\
-				 & \quad \times \log \frac{\sum_{m_k'} P_k'(x_{m_k'}) P(\hat{x}_{m_{\mathcal{K}}''} \mid x_{m_k'}) f_k'(x_{m_k};\hat{x}_{\mathcal{K}},\boldsymbol{y})}{\sum_{m_k'} P_k'(x_{m_k'}) P(\hat{x}_{m_{\mathcal{K}}''} \mid x_{m_k'}) f_k'(x_{m_k'};\hat{x}_{\mathcal{K}},\boldsymbol{y})}               \\
-				 & \ge (1 - \rho) \sum_{m_k} \frac{P_k'(x_{m_k}) f_k'(x_{m_k};\hat{x}_{\mathcal{K}},\boldsymbol{y})}{\sum_{m_k'} P_k'(x_{m_k'}) f_k'(x_{m_k'};\hat{x}_{\mathcal{K}},\boldsymbol{y})} \sum_{m_{\mathcal{K}}''} P(\hat{x}_{m_{\mathcal{K}}''} \mid x_{m_k})\nonumber                                \\
-				 & \quad \times \left( 1 - \frac{\sum_{m_k'} P_k'(x_{m_k'}) P(\hat{x}_{m_{\mathcal{K}}''} \mid x_{m_k'}) f_k'(x_{m_k'};\hat{x}_{\mathcal{K}},\boldsymbol{y})}{\sum_{m_k'} P_k'(x_{m_k'}) P(\hat{x}_{m_{\mathcal{K}}''} \mid x_{m_k'}) f_k'(x_{m_k};\hat{x}_{\mathcal{K}},\boldsymbol{y})} \right) \\
+				 & \triangleq I(x_{\mathcal{K}}) - J \left( P_{\mathcal{K}}(x_{m_{\mathcal{K}}}),P_{\mathcal{K}}'(x_{m_{\mathcal{K}}}) \right)                                                                                                                     \\
+				 & = (1 - \rho) \sum_{m_k} \frac{P_k'(x_{m_k}) f_k'(x_{m_k})}{\sum_{m_k'} P_k'(x_{m_k'}) f_k'(x_{m_k'})} \sum_{m_{\mathcal{K}}''} P(\hat{x}_{m_{\mathcal{K}}''}|x_{m_k})\nonumber                             \\
+				 & \quad \times \log \frac{\sum_{m_k'} P_k'(x_{m_k'}) P(\hat{x}_{m_{\mathcal{K}}''}|x_{m_k'}) f_k'(x_{m_k})}{\sum_{m_k'} P_k'(x_{m_k'}) P(\hat{x}_{m_{\mathcal{K}}''}|x_{m_k'}) f_k'(x_{m_k'})}               \\
+				 & \ge (1 - \rho) \sum_{m_k} \frac{P_k'(x_{m_k}) f_k'(x_{m_k})}{\sum_{m_k'} P_k'(x_{m_k'}) f_k'(x_{m_k'})} \sum_{m_{\mathcal{K}}''} P(\hat{x}_{m_{\mathcal{K}}''}|x_{m_k})\nonumber                           \\
+				 & \quad \times \left( 1 - \frac{\sum_{m_k'} P_k'(x_{m_k'}) P(\hat{x}_{m_{\mathcal{K}}''}|x_{m_k'}) f_k'(x_{m_k'})}{\sum_{m_k'} P_k'(x_{m_k'}) P(\hat{x}_{m_{\mathcal{K}}''}|x_{m_k'}) f_k'(x_{m_k})} \right) \\
 				 & = 0,
@@
 		\end{subequations}
-		where $f_k'(x_{m_k};\hat{x}_{\mathcal{K}},\boldsymbol{y}) \triangleq \exp \left( \frac{\rho}{1 - \rho} I_k'(x_{m_k};\hat{x}_{\mathcal{K}},\boldsymbol{y}) \right)$ and the equality holds if and only if \eqref{eq:optimal_relative_distribution} converges.
-		\eqref{eq:information_difference_lower} and \eqref{eq:information_difference_upper} together imply $I(x_{\mathcal{K}};\hat{x}_{\mathcal{K}},\boldsymbol{y}) \ge I'(x_{\mathcal{K}};\hat{x}_{\mathcal{K}},\boldsymbol{y})$.
+		where $f_k'(x_{m_k}) \triangleq \exp \left( \frac{\rho}{1 - \rho} I_k'(x_{m_k}) \right)$ and the equality holds if and only if \eqref{eq:optimal_relative_distribution} converges.
+		\eqref{eq:information_difference_lower} and \eqref{eq:information_difference_upper} together imply $I(x_{\mathcal{K}}) \ge I'(x_{\mathcal{K}})$.
 		Since mutual information is bounded above, we conclude the sequence \eqref{eq:input_kkt_solution} is non-decreasing and convergent in mutual information.
@@
 		\begin{equation}
-			D_k^{(r)}(x_{m_k}) \triangleq \frac{P_k^{(r+1)}(x_{m_k})}{P_k^{(r)}(x_{m_k})} = \frac{f_k^{(r)}(x_{m_k};\hat{x}_{\mathcal{K}},\boldsymbol{y})}{\sum_{m_k'} P_k^{(r)}(x_{m_k'}) f_k^{(r)}(x_{m_k'};\hat{x}_{\mathcal{K}},\boldsymbol{y})}.
+			D_k^{(r)}(x_{m_k}) \triangleq \frac{P_k^{(r+1)}(x_{m_k})}{P_k^{(r)}(x_{m_k})} = \frac{f_k^{(r)}(x_{m_k})}{\sum_{m_k'} P_k^{(r)}(x_{m_k'}) f_k^{(r)}(x_{m_k'})}.
 		\end{equation}
@@
 		\begin{equation}
-			I_k^\star(x_{m_k};\hat{x}_{\mathcal{K}},\boldsymbol{y}) = \frac{1 - \rho}{\rho} \log \sum_{m_k'} P_k^\star(x_{m_k'}) f_k^\star(x_{m_k'};\hat{x}_{\mathcal{K}},\boldsymbol{y}),
+			I_k^\star(x_{m_k}) = \frac{1 - \rho}{\rho} \log \sum_{m_k'} P_k^\star(x_{m_k'}) f_k^\star(x_{m_k'}),
 		\end{equation}
@@
 		\begin{equation}
-			I_k^\star(x_{m_k};\hat{x}_{\mathcal{K}},\boldsymbol{y}) > I^\star(x_{\mathcal{K}};\hat{x}_{\mathcal{K}},\boldsymbol{y}) = \sum_{m_k'} P_k^\star(x_{m_k'}) I_k^\star(x_{m_k'};\hat{x}_{\mathcal{K}},\boldsymbol{y}),
+			I_k^\star(x_{m_k}) > I^\star(x_{\mathcal{K}}) = \sum_{m_k'} P_k^\star(x_{m_k'}) I_k^\star(x_{m_k'}),
 		\end{equation}
 		where the equality inherits from \eqref{eq:weighted_sum_mutual_information}.
-		Since the exponential function is monotonically increasing, we have $f_k^\star(x_{m_k};\hat{x}_{\mathcal{K}},\boldsymbol{y}) > \sum_{m_k'} P_k^\star(x_{m_k'}) f_k^\star(x_{m_k'};\hat{x}_{\mathcal{K}},\boldsymbol{y})$ and $D_k^\star(x_{m_k}) > 1$.
+		Since the exponential function is monotonically increasing, we have $f_k^\star(x_{m_k}) > \sum_{m_k'} P_k^\star(x_{m_k'}) f_k^\star(x_{m_k'})$ and $D_k^\star(x_{m_k}) > 1$.
 		Considering $P_k^{(0)}(x_{m_k}) > 0$ and $P_k^\star(x_{m_k}) = 0$, it contradicts with
@@
 		\begin{equation}
-			\sum_l P(x_l) \frac{(t_s^\star)^{N-1} e^{-t_s^\star/\sigma_l^2}}{\sigma_l^{2N} (N-1)!} \log \frac{P(x_l \mid \hat{x}_{l'+1})}{P(x_l \mid \hat{x}_{l'})} = 0,
+			\sum_l P(x_l) \frac{(t_s^\star)^{N-1} e^{-t_s^\star/\sigma_l^2}}{\sigma_l^{2N} (N-1)!} \log \frac{P(x_l|\hat{x}_{l'+1})}{P(x_l|\hat{x}_{l'})} = 0,
 			\label{eq:kkt_threshold_explicit}
@@
 		According to \cite{He2021}, the optimal backward channel quantizer is convex and separates each pair of posterior distribution by a hyperplane.
-		It implies, for a given output letter $l'$, the sequence $\{\log {P(x_l \mid \hat{x}_{l'+1})}/{P(x_l \mid \hat{x}_{l'})}\}_{l \in \mathcal{L}}$ changes sign exactly once.
+		It implies, for a given output letter $l'$, the sequence $\{\log {P(x_l|\hat{x}_{l'+1})}/{P(x_l|\hat{x}_{l'})}\}_{l \in \mathcal{L}}$ changes sign exactly once.
 		We notice the left-hand side of \eqref{eq:kkt_threshold_explicit} is a generalized Dirichlet polynomial, and by Descartes' rule of signs \cite{Jameson2006}, has at most one positive solution.

### 2022-07-20 main.tex
:pencil: Summarize input distribution design

@@
 \usepackage{algpseudocode}
+\usepackage{algorithmicx}
 \usepackage{amsfonts}
@@
 \makeatletter
+\renewcommand{\fnum@algorithm}{\fname@algorithm{} \thealgorithm:}
 \tikzset{
@@
 \algrenewcommand{\algorithmicuntil}{\textbf{Until}}
+
+% \floatname{algorithm}{Procedure}
+\algrenewcommand{\algorithmicrequire}{\textbf{Input:}}
+\algrenewcommand{\algorithmicensure}{\textbf{Output:}}
 
@@
 		\end{equation}
-		where $\alpha \in [0,1]$ is the amplitude reflect ratio that controls the harvest-scatter tradeoff at the direction of interest.
+		where $0 \le \alpha \le 1$ is the amplitude reflect ratio that controls the harvest-scatter tradeoff at the direction of interest.
 		% When the \gls{csi} and reflection alphabet $\{\Gamma_1,\ldots,\Gamma_M\}$ are available at the reader, it can decode the tag message from the observed scattered signal.
@@
 		\end{equation}
-		where $\beta_m \in [0,1]$ is overall amplitude reflect ratio of state $m$.
+		where $0 \le \beta_m \le 1$ is overall amplitude reflect ratio of state $m$.
 		% Based on relevant \gls{csi}
@@
 				\boldsymbol{h}_{\mathrm{E}}^H(x_{\mathcal{K}})
-				 & \triangleq \boldsymbol{h}_{\mathrm{D}}^H + \sum_{k \in \mathcal{K}} \sqrt{\alpha_k} \boldsymbol{h}_{\mathrm{C},k}^H x_k \\
+				 & \triangleq \boldsymbol{h}_{\mathrm{D}}^H + \sum_{k \in \mathcal{K}} \alpha_k \boldsymbol{h}_{\mathrm{C},k}^H x_k   \\
 				 & = \boldsymbol{h}_{\mathrm{D}}^H + \boldsymbol{x}^H \mathrm{diag}(\boldsymbol{\alpha}) \boldsymbol{H}_{\mathrm{C}},
@@
 		\end{subequations}
-		where $\alpha_k$ is the amplitude reflect ratio of Metascatter $k$, $\boldsymbol{\alpha} \triangleq [\alpha_1,\ldots,\alpha_K]^T \in \mathbb{R}_+^{K \times 1}$, $x_k \in \mathcal{X} \triangleq \{\Gamma_1,\ldots,\Gamma_M\}$ is the backscatter symbol of Metascatter $k$, and $\boldsymbol{x} \triangleq [x_1,\ldots,x_K]^H \in \mathbb{C}^{K \times 1}$.
+		where $\alpha_k$ is the amplitude reflect ratio of Metascatter $k$, $\boldsymbol{\alpha} \triangleq [\alpha_1,\ldots,\alpha_K]^T \in \mathbb{R}_+^{K \times 1}$, $x_k \in \mathcal{X} \triangleq \{c_1,\ldots,c_M\}$ is the backscatter symbol of Metascatter $k$, and $\boldsymbol{x} \triangleq [x_1,\ldots,x_K]^H \in \mathbb{C}^{K \times 1}$.
 The signal received by the user at primary block $n \in \mathcal{N} \triangleq \{1,\ldots,N\}$ is
@@
 
-		% where $\alpha_k$ and $x_k$ denote respectively the harvest-backscatter efficiency and backscatter symbol of tag $k$, $s[n]$ and $w[n] \sim \mathcal{CN}(0,\sigma_w^2)$ denote respectively the primary symbol and \gls{awgn} at block $n$, and $\boldsymbol{w} \in \mathbb{C}^{Q \times 1}$ is the transmit precoder satisfying power constraint $\lVert \boldsymbol{w} \rVert^2 \le P$.
+		% where $\alpha_k$ and $x_k$ denote respectively the harvest-backscatter efficiency and backscatter symbol of tag $k$, $s[n]$ and $w[n] \sim \mathcal{CN}(0,\sigma_v^2)$ denote respectively the primary symbol and \gls{awgn} at block $n$, and $\boldsymbol{w} \in \mathbb{C}^{Q \times 1}$ is the transmit precoder satisfying power constraint $\lVert \boldsymbol{w} \rVert^2 \le P$.
 		% For the ease of notation, we define $x_{\mathcal{K}} \triangleq \{x_k : k \in \mathcal{K}\}$ as the tag input combination, and $\boldsymbol{y} \triangleq \left[y[1],\ldots,y[N]\right]^T \in \mathbb{C}^{N \times 1}$ as the received signal per backscatter symbol period.
@@
 		\begin{equation}
-			f(z|\mathcal{H}_{m_{\mathcal{K}}}) = \frac{z^{N-1} e^{-z/\sigma_{m_{\mathcal{K}}}^2}}{\sigma_{m_{\mathcal{K}}}^{2N} (N-1)!},
+			f(z|\mathcal{H}_{m_{\mathcal{K}}}) = \frac{z^{N-1} \exp(-z/\sigma_{m_{\mathcal{K}}}^2)}{\sigma_{m_{\mathcal{K}}}^{2N} (N-1)!},
+			% f(z|\mathcal{H}_{m_{\mathcal{K}}}) = \frac{z^{N-1} \exp(\frac{-z}{\sigma_{m_{\mathcal{K}}}^2})}{\sigma_{m_{\mathcal{K}}}^{2N} (N-1)!},
 			\label{eq:energy_distribution}
@@
 			% Next, we will restrict the design over convex decision regions.
-			Next, we will constrain all decision regions to convex and consider suboptimal threshold design accordingly.
 			% For a general input distribution, not only the rate-optimal decision thresholds
@@
 		\end{remark}
+		In the following context, we restrict all decision regions to convex and optimize decision thresholds accordingly.
+That is, for any bijective mapping $f : m_{\mathcal{K}} \to \mathcal{L} \triangleq \{1,\ldots,M^K\}$, the decision region of letter $l \in \mathcal{L}$ is defined as $\mathcal{R}_l \triangleq [t_{l-1},t_l)$, where $t_{l-1}<t_l$.
+We also define the decision threshold vector as $\boldsymbol{t} \triangleq [t_0,\ldots,t_L]^T \in \mathbb{R}_+^{(L+1) \times 1}$.
 	\end{subsection}
@@
 	\begin{subsection}{Achievable Rates}
-		Denote the input probability of state $m_k$ of Metascatter node $k$ as $P_k(x_{m_k})$, and define the input probability distribution vector of node $k$ as $\boldsymbol{p}_k \triangleq [P_k(\Gamma_1),\ldots,P_k(\Gamma_M)]^T \in \mathbb{R}^{M \times 1}$.
+		Denote the input probability of state $m_k$ of Metascatter node $k$ as $P_k(x_{m_k})$, and define the input probability distribution vector of node $k$ as $\boldsymbol{p}_k \triangleq [P_k(c_1),\ldots,P_k(c_M)]^T \in \mathbb{R}^{M \times 1}$.
 With independent encoding at all nodes, the probability of backscatter symbol tuple $x_{m_{\mathcal{K}}}$ is $P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) = \prod_{k \in \mathcal{K}} P_k(x_{m_k})$.
@@
 			I^{\mathrm{B}}_{k}(x_{m_k};\hat{x}_{\mathcal{K}}) \triangleq \sum_{m_{\mathcal{K} \setminus \{k\}}} P_{\mathcal{K} \setminus \{k\}}(x_{m_{\mathcal{K} \setminus \{k\}}}) I^{\mathrm{B}}(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}}),
-			\label{eq:backscatter_marginal_information_function}
+			\label{eq:backscatter_marginal_information}
 		\end{equation}
@@
 		% \begin{equation}
-		% 	I_{\mathrm{P}}(x_{m_{\mathcal{K}}};\boldsymbol{y}) \triangleq \log \left(1 + \frac{\lvert \boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_w^2}\right),
+		% 	I_{\mathrm{P}}(x_{m_{\mathcal{K}}};\boldsymbol{y}) \triangleq \log \left(1 + \frac{\lvert \boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_v^2}\right),
 		% 	\label{eq:primary_information_function}
@@
 		\begin{equation}
-			I^{\mathrm{P}}(s;y|x_{m_{\mathcal{K}}}) \triangleq \log \left(1 + \frac{\lvert \boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_w^2}\right),
+			I^{\mathrm{P}}(s;y|x_{m_{\mathcal{K}}}) \triangleq \log \Bigl(1 + \frac{\lvert \boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_v^2}\Bigr),
 			\label{eq:primary_information_function}
@@
 			I^{\mathrm{P}}_{k}(s;y|x_{m_k}) \triangleq \sum_{m_{\mathcal{K} \setminus \{k\}}} P_{\mathcal{K} \setminus \{k\}}(x_{m_{\mathcal{K} \setminus \{k\}}}) I^{\mathrm{P}}(s;y|x_{m_{\mathcal{K}}}),
-			\label{eq:primary_marginal_information_function}
+			\label{eq:primary_marginal_information}
 		\end{equation}
@@
 		\begin{equation}
-			% I^{\mathrm{P}}(s;y|x_{\mathcal{K}}) = \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) \log \left(1 + \frac{\lvert \boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_w^2}\right).
+			% I^{\mathrm{P}}(s;y|x_{\mathcal{K}}) = \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) \log \left(1 + \frac{\lvert \boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_v^2}\right).
 			I^{\mathrm{P}}(s;y|x_{\mathcal{K}}) = \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) I^{\mathrm{P}}(s;y|x_{m_{\mathcal{K}}}).
@@
 		\end{align}
-		where $\rho \in [0,1]$ is the relative priority of the primary link.
+		where $0 \le \rho \le 1$ is the relative priority of the primary link.
 
@@
 
-\begin{section}{Input Distribution, Decision Threshold, and Active Beamformer Design}
-	To characterize the achievable primary-(total-)backscatter rate region of Metascatter, we aim to maximize the weighted sum mutual information with respect to tag input probability distribution $\{\boldsymbol{p}_k\}$, decision threshold vector $\boldsymbol{t}$, and transmit precoder $\boldsymbol{w}$
+\begin{section}{Input Distribution, Active Beamforming, and Decision Threshold, Design}
+	To characterize the achievable primary-(total-)backscatter rate region of the proposed Metascatter-enabled network, we aim to maximize the weighted sum mutual information with respect to node input distributions $\{\boldsymbol{p}_k\}_{k \in \mathcal{K}}$, active beamforming vector $\boldsymbol{w}$, and decision threshold vector $\boldsymbol{t}$ as
 	\begin{maxi!}
-		{\scriptstyle{\{\boldsymbol{p}_k\},\boldsymbol{t},\boldsymbol{w}}}{I(x_{\mathcal{K}})}{\label{op:weighted_sum_rate}}{\label{ob:weighted_sum_rate}}
-		\addConstraint{\sum \nolimits_{m_k} P_k(x_{m_k})}{=1,}{\quad \forall k \in \mathcal{K}}{\label{co:sum_probability}}
-		\addConstraint{P_k(x_{m_k})}{\ge 0,}{\quad \forall k \in \mathcal{K}, \ \forall m_k \in \mathcal{M}}{\label{co:nonnegative_probability}}
+		{\scriptstyle{\{\boldsymbol{p}_k\}_{k \in \mathcal{K}},\boldsymbol{w},\boldsymbol{t}}}{I(x_{\mathcal{K}})}{\label{op:weighted_sum_rate}}{\label{ob:weighted_sum_rate}}
+		% \addConstraint{\sum \nolimits_{m_k} P_k(x_{m_k})}{=1,}{\quad \forall k \in \mathcal{K}}{\label{co:sum_probability}}
+		\addConstraint{\sum \nolimits_{m_k} P_k(x_{m_k})}{=1,}{\quad \forall k}{\label{co:sum_probability}}
+		% \addConstraint{P_k(x_{m_k})}{\ge 0,}{\quad \forall k \in \mathcal{K}, \ \forall m_k \in \mathcal{M}}{\label{co:nonnegative_probability}}
+		\addConstraint{P_k(x_{m_k})}{\ge 0,}{\quad \forall k,m_k}{\label{co:nonnegative_probability}}
 		\addConstraint{\lVert \boldsymbol{w} \rVert^2}{\le P.}{\label{co:transmit_power}}
 	\end{maxi!}
-	Since problem \eqref{op:weighted_sum_rate} is not jointly convex, we propose a \gls{bcd} algorithm that iteratively updates $\{\boldsymbol{p}_k\}$, $\boldsymbol{t}$ and $\boldsymbol{w}$ until convergence.
-
-	\begin{subsection}{Input Probability Distribution}
-		For any fixed decision boundary $\boldsymbol{t}$ and transmit precoder $\boldsymbol{w}$, the equivalent \gls{dtmac} can be formulated by \eqref{eq:dtmac} and problem \eqref{op:weighted_sum_rate} boils down to
+	% \begin{maxi!}
+	% 	{\scriptstyle{\{\boldsymbol{p}_k\}_{k \in \mathcal{K}},\boldsymbol{t},\boldsymbol{w}}}{I(x_{\mathcal{K}})}{\label{op:weighted_sum_rate}}{\label{ob:weighted_sum_rate}}
+	% 	\addConstraint{\boldsymbol{p}_k}{\in \Delta^{M-1},}{\quad \forall k \in \mathcal{K}}{\label{co:sum_probability}}
+	% 	% \addConstraint{P_k(x_{m_k})}{\ge 0,}{\quad \forall k \in \mathcal{K}, \ \forall m_k \in \mathcal{M}}{\label{co:nonnegative_probability}}
+	% 	\addConstraint{\lVert \boldsymbol{w} \rVert^2}{\le P.}{\label{co:transmit_power}}
+	% \end{maxi!}
+	% \begin{maxi!}
+	% 	{\scriptstyle{\boldsymbol{p}_k \in \Delta^{M-1},\boldsymbol{t},\boldsymbol{w}}}{I(x_{\mathcal{K}})}{\label{op:weighted_sum_rate}}{\label{ob:weighted_sum_rate}}
+	% 	% \addConstraint{\boldsymbol{p}_k}{\in \Delta^{M-1},}{\quad \forall k \in \mathcal{K}}{\label{co:sum_probability}}
+	% 	% \addConstraint{P_k(x_{m_k})}{\ge 0,}{\quad \forall k \in \mathcal{K}, \ \forall m_k \in \mathcal{M}}{\label{co:nonnegative_probability}}
+	% 	\addConstraint{\lVert \boldsymbol{w} \rVert^2}{\le P.}{\label{co:transmit_power}}
+	% \end{maxi!}
+	Problem \eqref{op:weighted_sum_rate} is highly non-convex, and we propose a \gls{bcd} algorithm that iteratively updates $\{\boldsymbol{p}_k\}_{k \in \mathcal{K}}$, $\boldsymbol{w}$ and $\boldsymbol{t}$ until convergence.
+
+	\begin{subsection}{Input Distribution}
+		% For any fixed decision boundary $\boldsymbol{t}$ and transmit precoder $\boldsymbol{w}$, the equivalent \gls{dtmac} can be formulated by \eqref{eq:dtmac} and problem \eqref{op:weighted_sum_rate} boils down to
+		For any given $\boldsymbol{w}$ and $\boldsymbol{t}$, we can construct the equivalent \gls{dtmac} by \eqref{eq:dtmac} and simplify \eqref{op:weighted_sum_rate} to
 		\begin{maxi!}
-			{\scriptstyle{\{\boldsymbol{p}_k\}}}{I(x_{\mathcal{K}})}{\label{op:input_probability_distribution}}{}
+			{\scriptstyle{\{\boldsymbol{p}_k\}_{k \in \mathcal{K}}}}{I(x_{\mathcal{K}})}{\label{op:input_probability_distribution}}{}
 			\addConstraint{\eqref{co:sum_probability},\eqref{co:nonnegative_probability},}
 		\end{maxi!}
-		which involves the product term $\prod_{k \in \mathcal{K}} P_k(x_{m_k})$ and is non-convex when $K > 1$.
-		Interestingly, the total-rate optimal input design for general discrete memoryless \gls{mac} remains an open problem, and we instead propose a \gls{kkt} solution to problem \eqref{op:input_probability_distribution}.
-		\begin{footnote}
-			As pointed out in \cite{Buhler2011}, \gls{kkt} conditions are only necessary for total-rate optimality and these solutions may end up being saddle points.
-		\end{footnote}
+		which involves coupled term $\prod_{k \in \mathcal{K}} P_k(x_{m_k})$ and is non-convex when $K > 1$.
+Next, we propose a numerical method that evaluate the \gls{kkt} input distribution by limit of sequences.
+		\begin{remark}
+			% As pointed out in \cite{Buhler2011}, \gls{kkt} conditions are only necessary for such kind of problems and these solutions may end up being saddle points.
+			As pointed out in \cite{Buhler2011}, \gls{kkt} conditions are generally necessary but insufficient for total rate maximization in discrete memoryless \gls{mac}.
+Therefore, \gls{kkt} solutions may end up being saddle points of problem \eqref{op:input_probability_distribution}.
+		\end{remark}
+		Following \cite{Rezaeian2004}, we first recast \gls{kkt} conditions to their equivalent form for problem \eqref{op:input_probability_distribution}, then propose an iterative method that guarantees input distribution satisfying above conditions on convergence.
+		% Interestingly, the total-rate optimal input design for general discrete memoryless \gls{mac} remains an open problem, and we instead propose a \gls{kkt} solution to problem \eqref{op:input_probability_distribution}.
 		\begin{proposition}
-			The \gls{kkt} optimality conditions for problem \eqref{op:input_probability_distribution} are equivalent to, $\forall k \in \mathcal{K}$ and $\forall m_k \in \mathcal{M}$,
+			% The \gls{kkt} optimality conditions for problem \eqref{op:input_probability_distribution} are equivalent to, $\forall k \in \mathcal{K}$ and $\forall m_k \in \mathcal{M}$,
+			The \gls{kkt} optimality conditions for problem \eqref{op:input_probability_distribution} are equivalent to, $\forall k,m_k$,
 			\begin{subequations}
@@
 
-		We notice \eqref{eq:probable_states} means each probable state of each tag should produce the same marginal information (averaged over all states of other tags), while \eqref{eq:dropped_states} implies any state of any tag with potentially less marginal information than above should not be used.
-		Next, we generalize the Blahut-Arimoto algorithm \cite{Arimoto1972,Blahut1972a} and propose a numerical evaluation of \gls{kkt} points by limits of sequences.
-
+		For each node, \eqref{eq:probable_states} suggests each probable state should produce the same marginal information (averaged over all states of other nodes), while \eqref{eq:dropped_states} implies any state with potentially less marginal information should not be used.
+		% We notice \eqref{eq:probable_states} means each probable state of each tag should produce the same marginal information (averaged over all states of other tags), while \eqref{eq:dropped_states} implies any state of any tag with potentially less marginal information than above should not be used.
+		% Next, we generalize the Blahut-Arimoto algorithm \cite{Arimoto1972,Blahut1972a} and propose a numerical evaluation of \gls{kkt} points by limits of sequences.
 		\begin{proposition}
-			The \gls{kkt} solution of input probability of tag $k$ at state $m_k$ is given by the converging point of the sequence
-			\begin{equation}
-				P_k^{(r+1)}(x_{m_k}) = \frac{P_k^{(r)}(x_{m_k}) \exp \left( \frac{\rho}{1 - \rho} I_k^{(r)}(x_{m_k}) \right)}{\sum_{m_k'} P_k^{(r)}(x_{m_k'}) \exp \left( \frac{\rho}{1 - \rho} I_k^{(r)}(x_{m_k'}) \right)},
+			% The \gls{kkt} solution of input probability of tag $k$ at state $m_k$ is given by the converging point of the sequence
+			The \gls{kkt} input probability of node $k$ of state $m_k$ is given by the converging point of the sequence
+			% The \gls{kkt} solution of input probability of tag $k$ at state $m_k$ is given by the converging point of the sequence
+			\begin{equation}
+				P_k^{(r+1)}(x_{m_k}) = \frac{P_k^{(r)}(x_{m_k}) \exp \Bigl( \frac{\rho}{1 - \rho} I_k^{(r)}(x_{m_k}) \Bigr)}{\sum_{m_k'} P_k^{(r)}(x_{m_k'}) \exp \Bigl( \frac{\rho}{1 - \rho} I_k^{(r)}(x_{m_k'}) \Bigr)},
 				\label{eq:input_kkt_solution}
 			\end{equation}
-			where $r$ is the iteration index and $\boldsymbol{p}_k^{(0)} > \boldsymbol{0}$, $\forall k \in \mathcal{K}$.
-			At each iteration, the input distribution of tag $k$ is evaluated based on the updated input distribution of tags $1$ to $k-1$.
+			% where $r$ is the iteration index and $\boldsymbol{p}_k^{(0)} > \boldsymbol{0}$, $\forall k \in \mathcal{K}$.
+			where $r$ is the iteration index and $\boldsymbol{p}_k^{(0)} > \boldsymbol{0}$, $\forall k$.
 			\label{pr:input_kkt_solution}
@@
 		\end{proof}
+
+		At each iteration, the input distribution of node $k$ is evaluated over updated input distribution of node $1$ to $k-1$, together with previous input distribution of node $k+1$ to $K$.
+The \gls{kkt} input distribution design is summarized in Algorithm TODO.
+
+		\begin{algorithm}[!t]
+			% \caption{Evaluate \gls{kkt} Input Distribution by Limits}
+			\caption{Numerical Evaluation of \gls{kkt} Input Distribution}
+			\label{al:input_distribution}
+			\begin{algorithmic}[1]
+				% % \State \textbf{Input:} $K$, $N$, $\boldsymbol{h}_{\mathrm{D}}^H$, $\boldsymbol{H}_{\mathrm{C}}$, $\boldsymbol{\alpha}$, $\mathcal{X}$, $\sigma_v^2$, $\rho$, $\boldsymbol{w}$, $\boldsymbol{t}$, $\epsilon$
+				\Require $K$, $N$, $\boldsymbol{h}_{\mathrm{D}}^H$, $\boldsymbol{H}_{\mathrm{C}}$, $\boldsymbol{\alpha}$, $\mathcal{X}$, $\sigma_v^2$, $\rho$, $\boldsymbol{w}$, $\boldsymbol{t}$, $\epsilon$
+				\Ensure $\{\boldsymbol{p}_k^\star\}_{k \in \mathcal{K}}$
+				\State Set $\boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}$ by \eqref{eq:equivalent_channel}
+				\State \phantom{Set} $\sigma^2_{m_{\mathcal{K}}}$, $\forall m_{\mathcal{K}}$ by \eqref{eq:receive_variance}
+				\State \phantom{Set} $f(z|\mathcal{H}_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}$ by \eqref{eq:energy_distribution}
+				\State \phantom{Set} $P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}, m_{\mathcal{K}}'$ by \eqref{eq:dtmac}
+				% \State \textbf{Initialize} $r \gets 0$, $\boldsymbol{p}_k > \boldsymbol{0}$, $\forall k$
+				\State Initialize $r \gets 0$
+				\State \phantom{Initialize} $\boldsymbol{p}_k^{(0)} > \boldsymbol{0}$, $\forall k$
+				\State \phantom{Initialize} $I^{(0)}(x_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}$ by \eqref{eq:backscatter_information_function}, \eqref{eq:primary_information_function}, \eqref{eq:weighted_sum_information_function}
+				\State \phantom{Initialize} $I^{(0)}_k(x_{m_k})$, $\forall k,m_k$ by \eqref{eq:backscatter_marginal_information}, \eqref{eq:primary_marginal_information}, \eqref{eq:weighted_sum_marginal_information}
+				\State \phantom{Initialize} $I^{(0)}(x_{\mathcal{K}})$ by \eqref{eq:backscatter_mutual_information}, \eqref{eq:primary_mutual_information}, \eqref{eq:weighted_sum_mutual_information}
+				\Repeat
+					\State Update $r \gets r+1$
+					\State \phantom{Update} $\boldsymbol{p}_k^{(r)}$, $\forall k$ by \eqref{eq:input_kkt_solution}
+					\State \phantom{Update} $I^{(r)}(x_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}$ by \eqref{eq:backscatter_information_function}, \eqref{eq:primary_information_function}, \eqref{eq:weighted_sum_information_function}
+					\State \phantom{Update} $I^{(r)}_k(x_{m_k})$, $\forall k,m_k$ by \eqref{eq:backscatter_marginal_information}, \eqref{eq:primary_marginal_information}, \eqref{eq:weighted_sum_marginal_information}
+					\State \phantom{Update} $I^{(r)}(x_{\mathcal{K}})$ by \eqref{eq:backscatter_mutual_information}, \eqref{eq:primary_mutual_information}, \eqref{eq:weighted_sum_mutual_information}
+				\Until $I^{(r)}(x_{\mathcal{K}}) - I^{(r-1)}(x_{\mathcal{K}}) \le \epsilon$
+				% \State \textbf{Initialize} $i \gets 0$, $\boldsymbol{\Phi}^{(0)}$
+				% \State Set $t_{\mathrm{I/P},k}^{(0)}$, $\forall k$ by \eqref{eq:t_k}
+				% \State Compute $z^{(0)}$ by \eqref{eq:z_irs}
+				% \Repeat
+				% 	\State $i \gets i + 1$
+				% 	\State Get $\boldsymbol{\Phi}^{(i)}$ by solving \eqref{ob:irs}--\eqref{co:irs_sd}
+				% 	\State Update $t_{\mathrm{I/P},k}^{(i)}$, $\forall k$ by \eqref{eq:t_k}
+				% 	\State Compute $z^{(i)}$ by \eqref{eq:z_irs}
+				% \Until $\lvert z^{(i)}-z^{(i-1)} \rvert \le \epsilon$
+				% \State Set $\boldsymbol{\Phi}^{\star} \gets \boldsymbol{\Phi}^{(i)}$
+				% \State Get $\hat{\boldsymbol{\phi}}^\star$ by eigen decomposition, $\boldsymbol{\Phi}^{\star}=\hat{\boldsymbol{\phi}}^\star(\hat{\boldsymbol{\phi}}^\star)^H$
+				% \State Set $\boldsymbol{\phi}^{\star} \gets e^{j \arg\left([\hat{\boldsymbol{\phi}}^\star]_{(1:L)} \middle/ [\hat{\boldsymbol{\phi}}^\star]_{(L+1)}\right)}$
+				% \State \textbf{Output} $\boldsymbol{\phi}^{\star}$
+			\end{algorithmic}
+		\end{algorithm}
 	\end{subsection}
 
+	\begin{subsection}{Active Beamforming}
+		For any given $\{\boldsymbol{p}_k\}_{k \in \mathcal{K}}$ and $\boldsymbol{t}$, problem \eqref{op:weighted_sum_rate} reduces to
+		\begin{maxi!}
+			{\scriptstyle{\boldsymbol{w}}}{I(x_{\mathcal{K}})}{\label{op:active_beamforming}}{\label{ob:active_beamforming}}
+			\addConstraint{\eqref{co:transmit_power},}
+		\end{maxi!}
+		which is still non-convex due to integration and entropy terms.
+		\begin{figure*}[!b]
+			\hrule
+			\begin{equation}
+				I(x_{\mathcal{K}})=\sum_{m_{\mathcal{K}}}P_{\mathcal{K}}(x_{m_{\mathcal{K}}})\Biggl(\rho\log\Bigl(1+\frac{\lvert\boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}})\boldsymbol{w}\rvert^2}{\sigma_v^2}\Bigr)+(1-\rho)\sum_l Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr) \log \frac{Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr)}{\sum_{m_{\mathcal{K}}'} P_{\mathcal{K}}(x_{m_{\mathcal{K}}'}) Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}'}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}'}^2}\Bigr)}\Biggr)
+				\label{eq:weighted_sum_mutual_information_explicit}
+			\end{equation}
+		\end{figure*}
+		To see this, we explicitly write \eqref{ob:active_beamforming} as \eqref{eq:weighted_sum_mutual_information_explicit} at the bottom of page \pageref{eq:regularized_incomplete_gamma}, where
+		\begin{equation}
+			Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr) = \frac{\int_{{t_{l-1}}/{\sigma_{m_{\mathcal{K}}}^2}}^{{t_l}/{\sigma_{m_{\mathcal{K}}}^2}} z^{N-1} \exp(-z) \dd z}{(N-1)!}
+			\label{eq:regularized_incomplete_gamma}
+		\end{equation}
+		is the regularized incomplete Gamma function that explicitly substitutes the \gls{dtmac} transition probability \eqref{eq:dtmac}.
+		Its series representation is given by \cite[Theorem~3]{Jameson2016}
+		\begin{align}
+			Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr)
+			 & = \exp \Bigl(-\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2}\Bigr) \sum_{n=0}^{N-1} \frac{\Bigl(\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2}\Bigr)^n}{n!} \nonumber \\
+			 & \quad - \exp \Bigl(-\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr) \sum_{n=0}^{N-1} \frac{\Bigl(\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr)^n}{n!}.
+			\label{eq:regularized_incomplete_gamma_series}
+		\end{align}
+		We further write the gradient of \eqref{eq:regularized_incomplete_gamma_series} and \eqref{eq:weighted_sum_mutual_information_explicit} w.r.t.
+$\boldsymbol{w}^*$ as \eqref{eq:regularized_incomplete_gamma_gradient} and TODO at the end of page \pageref{eq:regularized_incomplete_gamma_gradient} and TODO, respectively.
+		\begin{figure*}[!b]
+			\begin{align}
+				\nabla_{\boldsymbol{w}^*} Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr)
+				 & = \frac{\boldsymbol{h}_{\mathrm{E}}(x_{m_{\mathcal{K}}})\boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}})\boldsymbol{w}}{\bigl(\lvert\boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}})\boldsymbol{w}\rvert^2+\sigma_v^2\bigr)^2}\nonumber                                                                                                                                                                                                        \\
+				 & \quad \times \Biggl(t_l\exp\Bigl(-\frac{t_l}{\lvert\boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}})\boldsymbol{w}\rvert^2+\sigma_v^2}\Bigr)\biggl(-1+\sum_{n=1}^{N-1} \frac{n\Bigl(\frac{t_l}{\lvert\boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}})\boldsymbol{w}\rvert^2+\sigma_v^2}\Bigr)^{n-1}-\Bigl(\frac{t_l}{\lvert\boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}})\boldsymbol{w}\rvert^2+\sigma_v^2}\Bigr)^n}{n!}\biggr)\nonumber    \\
+				 & \qquad - t_{l-1}\exp\Bigl(-\frac{t_{l-1}}{\lvert\boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}})\boldsymbol{w}\rvert^2+\sigma_v^2}\Bigr)\biggl(-1+\sum_{n=1}^{N-1} \frac{n\Bigl(\frac{t_{l-1}}{\lvert\boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}})\boldsymbol{w}\rvert^2+\sigma_v^2}\Bigr)^{n-1}-\Bigl(\frac{t_{l-1}}{\lvert\boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}})\boldsymbol{w}\rvert^2+\sigma_v^2}\Bigr)^n}{n!}\biggr)\Biggr)
+				\label{eq:regularized_incomplete_gamma_gradient}
+			\end{align}
+		\end{figure*}
+		\begin{figure*}[!b]
+			\begin{align}
+				\nabla_{\boldsymbol{w}^*} I(x_{\mathcal{K}})
+				 & = \sum_{m_{\mathcal{K}}}P_{\mathcal{K}}(x_{m_{\mathcal{K}}})\Biggl(\rho\frac{\boldsymbol{h}_{\mathrm{E}}(x_{m_{\mathcal{K}}})\boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}})\boldsymbol{w}}{\lvert\boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}})\boldsymbol{w}\rvert^2+\sigma_v^2}+(1-\rho)\sum_l\biggl(\log\frac{Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr)}{\sum_{m_{\mathcal{K}}'}P_{\mathcal{K}}(x_{m_{\mathcal{K}}'})Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}'}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}'}^2}\Bigr)}+1\biggr)\nonumber \\
+				 & \qquad \times \nabla_{\boldsymbol{w}^*} Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr)-\frac{Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr)\sum_{m_{\mathcal{K}}'}P_{\mathcal{K}}(x_{m_{\mathcal{K}}'})\nabla_{\boldsymbol{w}^*}Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}'}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}'}^2}\Bigr)}{\sum_{m_{\mathcal{K}}'}P_{\mathcal{K}}(x_{m_{\mathcal{K}}'})Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}'}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}'}^2}\Bigr)}\Biggr)
+			\end{align}
+		\end{figure*}
+		% The optimal precoder design is highly non-convex that involves integration, entropy term, and variable on exponential.
+		% We may propose a suboptimal precoder based on linear combination of equivalent and cascaded channels, or consider single transmit antenna instead.
+	\end{subsection}
+
 	\begin{subsection}{Decision Threshold}
 
-		For a given tag input distribution $\{\boldsymbol{p}_k\}$, we can formulate an equivalent information source with augmented alphabet of tag input combination.
+		For a given tag input distribution $\{\boldsymbol{p}_k\}_{k \in \mathcal{K}}$, we can formulate an equivalent information source with augmented alphabet of tag input combination.
 		This equivalent source transmits at the total backscatter rate, and the input distribution is given by $P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) = \prod_{k \in \mathcal{K}} P_k(x_{m_k})$, $\forall k \in \mathcal{K}$ and $\forall m_k \in \mathcal{M}$.
@@
 
-	\begin{subsection}{Precoder}
-		\begin{tcolorbox}
-			The optimal precoder design is highly non-convex that involves integration, entropy term, and variable on exponential.
-			We may propose a suboptimal precoder based on linear combination of equivalent and cascaded channels, or consider single transmit antenna instead.
-		\end{tcolorbox}
-		\begin{align}
-			I(x_i;\hat{x}_j)
-			 & = \sum_{j \in \mathcal{I}} \int_{t_{j-1,j}}^{t_{j,j+1}} \frac{z^{N-1} \exp \left(-\frac{z}{\mathrm{tr}(H_{\mathrm{E},i} W) + \sigma_w^2}\right)}{\left(\mathrm{tr}(H_{\mathrm{E},i} W) + \sigma_w^2\right)^N (N-1)!} \dd z\nonumber                                                                                                                                                                                                                    \\
-			 & \quad \times \log \frac{\int_{t_{j-1,j}}^{t_{j,j+1}} \frac{z^{N-1} \exp \left(-\frac{z}{\mathrm{tr}(H_{\mathrm{E},i} W) + \sigma_w^2}\right)}{\left(\mathrm{tr}(H_{\mathrm{E},i} W) + \sigma_w^2\right)^N (N-1)!} \dd z}{\sum_{i' \in \mathcal{I}} \int_{t_{j-1,j}}^{t_{j,j+1}} \frac{z^{N-1} \exp \left(-\frac{z}{\mathrm{tr}(H_{\mathrm{E},i'} W) + \sigma_w^2}\right)}{\left(\mathrm{tr}(H_{\mathrm{E},i'} W) + \sigma_w^2\right)^N (N-1)!} \dd z},
-		\end{align}
-	\end{subsection}
 \end{section}
@@
 			Duration ratio $N$       & 10  \\
-			Noise power $\sigma_w^2$ & 1   \\
+			Noise power $\sigma_v^2$ & 1   \\
 			Discretization bins      & 256
@@
 		\begin{align}
-			% L(\{\boldsymbol{p}_k\},\{\nu_k\},\{\lambda_{k,m_k}\})
+			% L(\{\boldsymbol{p}_k\}_{k \in \mathcal{K}},\{\nu_k\},\{\lambda_{k,m_k}\})
 			L
-			 & = - I(x_{\mathcal{K}}) + \sum_{k \in \mathcal{K}} \nu_k \left( \sum_{m_k \in \mathcal{M}} P_k(x_{m_k}) - 1 \right)\nonumber \\
-			 & \quad - \sum_{k \in \mathcal{K}} \sum_{m_k \in \mathcal{M}} \lambda_{k,m_k} P_k(x_{m_k}),
+			%  & = - I(x_{\mathcal{K}}) + \sum_{k \in \mathcal{K}} \nu_k \left( \sum_{m_k \in \mathcal{M}} P_k(x_{m_k}) - 1 \right)\nonumber \\
+			 & = - I(x_{\mathcal{K}}) + \sum_k \nu_k \left( \sum_{m_k \in \mathcal{M}} P_k(x_{m_k}) - 1 \right)\nonumber \\
+			%  & \quad - \sum_{k \in \mathcal{K}} \sum_{m_k \in \mathcal{M}} \lambda_{k,m_k} P_k(x_{m_k}),
+			 & \quad - \sum_k \sum_{m_k} \lambda_{k,m_k} P_k(x_{m_k}),
 		\end{align}
-		and the \gls{kkt} conditions on the optimal primal and dual variables are, $\forall m_k \in \mathcal{M}$ and $\forall k \in \mathcal{K}$,
+		% and the \gls{kkt} conditions on the optimal primal and dual variables are, $\forall m_k \in \mathcal{M}$ and $\forall k \in \mathcal{K}$,
+		% and the \gls{kkt} conditions are, $\forall m_k \in \mathcal{M}$ and $\forall k \in \mathcal{K}$,
+		and the \gls{kkt} conditions are, $\forall k,m_k$,
 		\begin{subequations}
@@
 			\begin{equation}
-				\lambda_{k,m_k}^\star \ge 0, \quad P_k^\star(x_{m_k}) = 0,
+				\lambda_{k,m_k}^\star \ge 0, \quad P_k^\star(x_{m_k}) = 0.
 			\end{equation}
 		\end{subequations}
-		where the directional derivative can be explicitly expressed as
+		The directional derivative can be explicitly expressed as
 		\begin{equation}
@@
 		\end{equation}
-
 		Combining \eqref{eq:input_kkt_condition_original} and \eqref{eq:input_directional_derivative}, we have
@@
 		\end{equation}
-
 		On the other hand, by definition of weighted sum marginal information \eqref{eq:weighted_sum_marginal_information},
@@
 	\begin{subsection}{Proof of Proposition \ref{pr:input_kkt_solution}}
-		We first prove sequence \eqref{eq:input_kkt_solution} is non-decreasing in mutual information.
-		Let $P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) = \prod_{q \in \mathcal{K}} P_q(x_{m_q})$ and $P_{\mathcal{K}}'(x_{m_{\mathcal{K}}}) = P_k'(x_{m_k}) \prod_{q \in \mathcal{K} \setminus \{k\}} P_q(x_{m_q})$ be two probability distributions with potentially different marginal for tag $k \in \mathcal{K}$ at state $m_k \in \mathcal{M}$, and define an intermediate function $J \left( P_{\mathcal{K}}(x_{m_{\mathcal{K}}}),P_{\mathcal{K}}'(x_{m_{\mathcal{K}}}) \right)$ as \eqref{eq:intermediate_information_function}.
+		We first prove sequence \eqref{eq:input_kkt_solution} is non-decreasing in weighted sum mutual information.
+		Let $P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) = \prod_{q \in \mathcal{K}} P_q(x_{m_q})$ and $P_{\mathcal{K}}'(x_{m_{\mathcal{K}}}) = P_k'(x_{m_k}) \prod_{q \in \mathcal{K} \setminus \{k\}} P_q(x_{m_q})$ be two probability distributions with potentially different marginal for tag $k \in \mathcal{K}$ at state $m_k \in \mathcal{M}$, and define an intermediate function $J \left( P_{\mathcal{K}}(x_{m_{\mathcal{K}}}),P_{\mathcal{K}}'(x_{m_{\mathcal{K}}}) \right)$ as \eqref{eq:intermediate_information_function} at the end of page \pageref{eq:intermediate_information_function}.
 		\begin{figure*}[!b]
 			\hrule
+			% \begin{equation}
+			% 	J \left( P_{\mathcal{K}}(x_{m_{\mathcal{K}}}),P_{\mathcal{K}}'(x_{m_{\mathcal{K}}}) \right) \triangleq \rho \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) \log \left(1 + \frac{\lvert \boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_v^2}\right) + (1 - \rho) \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) \sum_{m_{\mathcal{K}}'} P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}}) \log \frac{P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}}) P_{\mathcal{K}}'(x_{m_{\mathcal{K}}})}{P'(\hat{x}_{m_{\mathcal{K}}'}) P_{\mathcal{K}}(x_{m_{\mathcal{K}}})}.
+			% 	\label{eq:intermediate_information_function}
+			% \end{equation}
 			\begin{align}
 				J \left( P_{\mathcal{K}}(x_{m_{\mathcal{K}}}),P_{\mathcal{K}}'(x_{m_{\mathcal{K}}}) \right)
-				 & \triangleq \rho \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) \log \left(1 + \frac{\lvert \boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_w^2}\right)\nonumber                                                                                                                    \\
+				 & \triangleq \rho \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) \log \left(1 + \frac{\lvert \boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_v^2}\right)\nonumber                                                                                                                    \\
 				 & \quad + (1 - \rho) \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) \sum_{m_{\mathcal{K}}'} P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}}) \log \frac{P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}}) P_{\mathcal{K}}'(x_{m_{\mathcal{K}}})}{P'(\hat{x}_{m_{\mathcal{K}}'}) P_{\mathcal{K}}(x_{m_{\mathcal{K}}})}.
@@
 		\end{align}
-
 		Evidently, $\forall m_k \ne i_k$, \eqref{eq:optimal_intermediate_information_condition} boils down to
@@
 		\end{equation}
-
-		Although it seems $P_k(x_{i_k}) = 1 - \sum_{m_k \ne i_k} P_k^\star(x_{m_k})$ has no optimality guarantee, we can verify that $P_k(x_{i_k})$ has exactly the same form as \eqref{eq:optimal_relative_distribution}.
-		It implies the selection of reference state does not matter and \eqref{eq:optimal_relative_distribution} is indeed optimal $\forall m_k \in \mathcal{M}$.
-		Therefore, for a fixed $P_{\mathcal{K}}'(x_{m_{\mathcal{K}}})$, choosing $P_k(x_{m_k})$ by \eqref{eq:optimal_relative_distribution} ensures
+		We also notice $P_k(x_{i_k}) = 1 - \sum_{m_k \ne i_k} P_k^\star(x_{m_k})$ has exactly the same expression as \eqref{eq:optimal_relative_distribution}.
+		% We also notice $P_k(x_{i_k}) = 1 - \sum_{m_k \ne i_k} P_k^\star(x_{m_k})$ is in the same expression as \eqref{eq:optimal_relative_distribution}.
+		Therefore, the result is irrelevant to the choice of reference state, and \eqref{eq:optimal_relative_distribution} is indeed optimal $\forall m_k \in \mathcal{M}$.
+		% It implies the selection of reference state does not matter and \eqref{eq:optimal_relative_distribution} is indeed optimal $\forall m_k \in \mathcal{M}$.
+		That is, for a fixed $P_{\mathcal{K}}'(x_{m_{\mathcal{K}}})$, choosing $P_k(x_{m_k})$ by \eqref{eq:optimal_relative_distribution} ensures
 		\begin{equation}
@@
 		\end{equation}
-
-		On the other hand, \eqref{eq:optimal_relative_distribution} also guarantees
+		On the other hand, it also guarantees
 		\begin{subequations}
@@
 
-		Next, we prove that any converging point of sequence \eqref{eq:input_kkt_solution}, denoted as $P_k^\star(x_{m_k})$, fulfills \gls{kkt} conditions \eqref{eq:input_kkt_condition}.
-		To see this, consider $P_k^{(0)}(x_{m_k}) > 0$ and define
+		Next, we prove any converging point of sequence \eqref{eq:input_kkt_solution}, denoted as $P_k^\star(x_{m_k})$, fulfills \gls{kkt} conditions \eqref{eq:input_kkt_condition}.
+		% Next, we prove that sequence \eqref{eq:input_kkt_solution} fulfills \gls{kkt} conditions \eqref{eq:input_kkt_condition} on convergence.
+		% To see this, recall $P_k^{(0)}(x_{m_k}) > 0$ and define
+		To see this, define
+		% To see this, we define
 		\begin{equation}
@@
 		\end{equation}
-
 		As sequence \eqref{eq:input_kkt_solution} is convergent, any state with $P_k^\star(x_{m_k}) > 0$ need to satisfy $D_k^\star(x_{m_k}) \triangleq \lim_{r \to \infty} D_k^{(r)}(x_{m_k}) = 1$, namely
@@
 		\end{equation}
-		which is reminiscent of \eqref{eq:probable_states_marginal} (and hence \eqref{eq:probable_states}).
+		which is reminiscent of \eqref{eq:probable_states_marginal} and \eqref{eq:probable_states}.
 		That is to say, given $P_k^{(0)}(x_{m_k}) > 0$, any converging point with $P_k^\star(x_{m_k}) > 0$ must satisfy \eqref{eq:probable_states}.
@@
 		where the equality inherits from \eqref{eq:weighted_sum_mutual_information}.
-		Since the exponential function is monotonically increasing, we have $f_k^\star(x_{m_k}) > \sum_{m_k'} P_k^\star(x_{m_k'}) f_k^\star(x_{m_k'})$ and $D_k^\star(x_{m_k}) > 1$.
+		Since exponential function is monotonically increasing, we have $f_k^\star(x_{m_k}) > \sum_{m_k'} P_k^\star(x_{m_k'}) f_k^\star(x_{m_k'})$ and $D_k^\star(x_{m_k}) > 1$.
 		Considering $P_k^{(0)}(x_{m_k}) > 0$ and $P_k^\star(x_{m_k}) = 0$, it contradicts with
@@
 		\begin{equation}
-			\sum_l P(x_l) \frac{(t_s^\star)^{N-1} e^{-t_s^\star/\sigma_l^2}}{\sigma_l^{2N} (N-1)!} \log \frac{P(x_l|\hat{x}_{l'+1})}{P(x_l|\hat{x}_{l'})} = 0,
+			\sum_l P(x_l) \frac{(t_s^\star)^{N-1} \exp{-t_s^\star/\sigma_l^2}}{\sigma_l^{2N} (N-1)!} \log \frac{P(x_l|\hat{x}_{l'+1})}{P(x_l|\hat{x}_{l'})} = 0,
 			\label{eq:kkt_threshold_explicit}

### 2022-07-21 main.tex
:pencil: Add active beamforming design

@@
 \algrenewcommand{\algorithmicuntil}{\textbf{Until}}
-
-% \floatname{algorithm}{Procedure}
+\algrenewcommand{\algorithmicdo}{}
+
+% \algrenewcommand\algorithmicdo{}
+% \renewcommand\algorithmicdo{}
+
 \algrenewcommand{\algorithmicrequire}{\textbf{Input:}}
@@
 		% We assume the primary symbol follows standard \gls{cscg} distribution and the backscatter symbol of all tags employs $M$-\gls{qam}.
-		Under perfect synchronization, the equivalent primary channel is a function of backscatter symbols
+		Under perfect synchronization, the equivalent primary channel is a function of \emph{coded} backscatter symbols
 		\begin{subequations}
@@
 		\end{subequations}
-		where $\alpha_k$ is the amplitude reflect ratio of Metascatter $k$, $\boldsymbol{\alpha} \triangleq [\alpha_1,\ldots,\alpha_K]^T \in \mathbb{R}_+^{K \times 1}$, $x_k \in \mathcal{X} \triangleq \{c_1,\ldots,c_M\}$ is the backscatter symbol of Metascatter $k$, and $\boldsymbol{x} \triangleq [x_1,\ldots,x_K]^H \in \mathbb{C}^{K \times 1}$.
+		where $\alpha_k$ is the amplitude reflect ratio of Metascatter $k$, $\boldsymbol{\alpha} \triangleq [\alpha_1,\ldots,\alpha_K]^T \in \mathbb{R}_+^{K \times 1}$, $x_k \in \mathcal{X} \triangleq \{c_1,\ldots,c_M\}$ is the coded backscatter symbol of Metascatter $k$, and $\boldsymbol{x} \triangleq [x_1,\ldots,x_K]^H \in \mathbb{C}^{K \times 1}$.
 The signal received by the user at primary block $n \in \mathcal{N} \triangleq \{1,\ldots,N\}$ is
@@
 	\begin{subsection}{Receiving Strategy}
-		We propose a Metascatter receiver where the backscatter symbols of all Metascatters are first jointly and semi-coherently detected using total received energy per backscatter block, then modeled within equivalent channel \eqref{eq:equivalent_channel} as dynamic passive beamforming.
+		We propose a Metascatter receiver where the backscatter messages of all Metascatters are first jointly and semi-coherently detected using total received energy per backscatter block, then modeled within equivalent channel \eqref{eq:equivalent_channel} as dynamic passive beamforming.
 		% identified by non-coherent energy detection, then
@@
 		In the following context, we restrict all decision regions to convex and optimize decision thresholds accordingly.
-That is, for any bijective mapping $f : m_{\mathcal{K}} \to \mathcal{L} \triangleq \{1,\ldots,M^K\}$, the decision region of letter $l \in \mathcal{L}$ is defined as $\mathcal{R}_l \triangleq [t_{l-1},t_l)$, where $t_{l-1}<t_l$.
+That is, for any bijective mapping $f : m_{\mathcal{K}} \to \mathcal{L} \triangleq \{1,\ldots,M^K\}$, the decision region of letter $l \in \mathcal{L}$ is defined as $\mathcal{R}_l \triangleq [t_{l-1},t_l)$, where $t_{l-1} \le t_l$.
 We also define the decision threshold vector as $\boldsymbol{t} \triangleq [t_0,\ldots,t_L]^T \in \mathbb{R}_+^{(L+1) \times 1}$.
@@
 		Denote the input probability of state $m_k$ of Metascatter node $k$ as $P_k(x_{m_k})$, and define the input probability distribution vector of node $k$ as $\boldsymbol{p}_k \triangleq [P_k(c_1),\ldots,P_k(c_M)]^T \in \mathbb{R}^{M \times 1}$.
-With independent encoding at all nodes, the probability of backscatter symbol tuple $x_{m_{\mathcal{K}}}$ is $P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) = \prod_{k \in \mathcal{K}} P_k(x_{m_k})$.
+With independent encoding at all nodes, the probability of backscatter symbol tuple $x_{m_{\mathcal{K}}}$ is
+		\begin{equation}
+			P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) = \prod_{k \in \mathcal{K}} P_k(x_{m_k}).
+			\label{eq:equivalent_distribution}
+		\end{equation}
 		% Denote the input probability distribution vector of tag $k$ as $\boldsymbol{p}_k \triangleq [P_k(x_1),\ldots,P_k(x_M)]^T \in \mathbb{R}^{M \times 1}$, where $P_k(x_{m_k})$ is the probability at state $m_k$.
@@
 		% Once the tag input combination is successfully decoded, the backscatter uncertainty can be eliminated and the equivalent channel for primary transmission can be updated by \eqref{eq:equivalent_channel}.
-		Once backscatter symbols are successfully decoded, we can eliminate modulation uncertainty and retrieve equivalent primary channel by \eqref{eq:equivalent_channel}.
+
+		% eliminate modulation uncertainty
+		Once backscatter messages are successfully decoded, we can re-encode to determine $x_{\mathcal{K}}$ and retrieve equivalent primary channel by \eqref{eq:equivalent_channel}.
+We define the primary information function conditioned on backscatter symbol tuple $x_{m_{\mathcal{K}}}$ as
+		% Once backscatter symbols are successfully decoded, we can eliminate modulation uncertainty and retrieve equivalent primary channel by \eqref{eq:equivalent_channel}.
 We define the primary information function conditioned on backscatter symbol tuple $x_{m_{\mathcal{K}}}$ as
@@
 	\begin{maxi!}
-		{\scriptstyle{\{\boldsymbol{p}_k\}_{k \in \mathcal{K}},\boldsymbol{w},\boldsymbol{t}}}{I(x_{\mathcal{K}})}{\label{op:weighted_sum_rate}}{\label{ob:weighted_sum_rate}}
+		{\scriptstyle{\{\boldsymbol{p}_k\}_{k \in \mathcal{K}},\boldsymbol{w},\boldsymbol{t}\in\mathbb{R}_+^{L+1}}}{I(x_{\mathcal{K}})}{\label{op:weighted_sum_rate}}{\label{ob:weighted_sum_rate}}
 		% \addConstraint{\sum \nolimits_{m_k} P_k(x_{m_k})}{=1,}{\quad \forall k \in \mathcal{K}}{\label{co:sum_probability}}
@@
 		\addConstraint{P_k(x_{m_k})}{\ge 0,}{\quad \forall k,m_k}{\label{co:nonnegative_probability}}
-		\addConstraint{\lVert \boldsymbol{w} \rVert^2}{\le P.}{\label{co:transmit_power}}
+		\addConstraint{\lVert \boldsymbol{w} \rVert^2}{\le P}{\label{co:transmit_power}}
+		\addConstraint{t_{l-1}}{\le t_l,}{\quad \forall l.}{\label{co:decision_threshold}}
 	\end{maxi!}
@@
 		At each iteration, the input distribution of node $k$ is evaluated over updated input distribution of node $1$ to $k-1$, together with previous input distribution of node $k+1$ to $K$.
-The \gls{kkt} input distribution design is summarized in Algorithm TODO.
+The \gls{kkt} input distribution design is summarized in Algorithm \ref{al:input_distribution}.
 
 		\begin{algorithm}[!t]
-			% \caption{Evaluate \gls{kkt} Input Distribution by Limits}
 			\caption{Numerical Evaluation of \gls{kkt} Input Distribution}
@@
 			\begin{algorithmic}[1]
-				% % \State \textbf{Input:} $K$, $N$, $\boldsymbol{h}_{\mathrm{D}}^H$, $\boldsymbol{H}_{\mathrm{C}}$, $\boldsymbol{\alpha}$, $\mathcal{X}$, $\sigma_v^2$, $\rho$, $\boldsymbol{w}$, $\boldsymbol{t}$, $\epsilon$
 				\Require $K$, $N$, $\boldsymbol{h}_{\mathrm{D}}^H$, $\boldsymbol{H}_{\mathrm{C}}$, $\boldsymbol{\alpha}$, $\mathcal{X}$, $\sigma_v^2$, $\rho$, $\boldsymbol{w}$, $\boldsymbol{t}$, $\epsilon$
@@
 				\State \phantom{Set} $P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}, m_{\mathcal{K}}'$ by \eqref{eq:dtmac}
-				% \State \textbf{Initialize} $r \gets 0$, $\boldsymbol{p}_k > \boldsymbol{0}$, $\forall k$
 				\State Initialize $r \gets 0$
 				\State \phantom{Initialize} $\boldsymbol{p}_k^{(0)} > \boldsymbol{0}$, $\forall k$
-				\State \phantom{Initialize} $I^{(0)}(x_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}$ by \eqref{eq:backscatter_information_function}, \eqref{eq:primary_information_function}, \eqref{eq:weighted_sum_information_function}
-				\State \phantom{Initialize} $I^{(0)}_k(x_{m_k})$, $\forall k,m_k$ by \eqref{eq:backscatter_marginal_information}, \eqref{eq:primary_marginal_information}, \eqref{eq:weighted_sum_marginal_information}
-				\State \phantom{Initialize} $I^{(0)}(x_{\mathcal{K}})$ by \eqref{eq:backscatter_mutual_information}, \eqref{eq:primary_mutual_information}, \eqref{eq:weighted_sum_mutual_information}
+				\State Get $P_{\mathcal{K}}^{(0)}(x_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}$ by \eqref{eq:equivalent_distribution}
+				\State \phantom{Get} $I^{(0)}(x_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}$ by \eqref{eq:backscatter_information_function}, \eqref{eq:primary_information_function}, \eqref{eq:weighted_sum_information_function}
+				\State \phantom{Get} $I^{(0)}_k(x_{m_k})$, $\forall k,m_k$ by \eqref{eq:backscatter_marginal_information}, \eqref{eq:primary_marginal_information}, \eqref{eq:weighted_sum_marginal_information}
+				\State \phantom{Get} $I^{(0)}(x_{\mathcal{K}})$ by \eqref{eq:backscatter_mutual_information}, \eqref{eq:primary_mutual_information}, \eqref{eq:weighted_sum_mutual_information}
 				\Repeat
@@
 					\State \phantom{Update} $\boldsymbol{p}_k^{(r)}$, $\forall k$ by \eqref{eq:input_kkt_solution}
-					\State \phantom{Update} $I^{(r)}(x_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}$ by \eqref{eq:backscatter_information_function}, \eqref{eq:primary_information_function}, \eqref{eq:weighted_sum_information_function}
-					\State \phantom{Update} $I^{(r)}_k(x_{m_k})$, $\forall k,m_k$ by \eqref{eq:backscatter_marginal_information}, \eqref{eq:primary_marginal_information}, \eqref{eq:weighted_sum_marginal_information}
-					\State \phantom{Update} $I^{(r)}(x_{\mathcal{K}})$ by \eqref{eq:backscatter_mutual_information}, \eqref{eq:primary_mutual_information}, \eqref{eq:weighted_sum_mutual_information}
+					\State Get $P_{\mathcal{K}}^{(r)}(x_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}$ by \eqref{eq:equivalent_distribution}
+					\State \phantom{Get} $I^{(r)}(x_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}$ by \eqref{eq:backscatter_information_function}, \eqref{eq:primary_information_function}, \eqref{eq:weighted_sum_information_function}
+					\State \phantom{Get} $I^{(r)}_k(x_{m_k})$, $\forall k,m_k$ by \eqref{eq:backscatter_marginal_information}, \eqref{eq:primary_marginal_information}, \eqref{eq:weighted_sum_marginal_information}
+					\State \phantom{Get} $I^{(r)}(x_{\mathcal{K}})$ by \eqref{eq:backscatter_mutual_information}, \eqref{eq:primary_mutual_information}, \eqref{eq:weighted_sum_mutual_information}
 				\Until $I^{(r)}(x_{\mathcal{K}}) - I^{(r-1)}(x_{\mathcal{K}}) \le \epsilon$
-				% \State \textbf{Initialize} $i \gets 0$, $\boldsymbol{\Phi}^{(0)}$
-				% \State Set $t_{\mathrm{I/P},k}^{(0)}$, $\forall k$ by \eqref{eq:t_k}
-				% \State Compute $z^{(0)}$ by \eqref{eq:z_irs}
-				% \Repeat
-				% 	\State $i \gets i + 1$
-				% 	\State Get $\boldsymbol{\Phi}^{(i)}$ by solving \eqref{ob:irs}--\eqref{co:irs_sd}
-				% 	\State Update $t_{\mathrm{I/P},k}^{(i)}$, $\forall k$ by \eqref{eq:t_k}
-				% 	\State Compute $z^{(i)}$ by \eqref{eq:z_irs}
-				% \Until $\lvert z^{(i)}-z^{(i-1)} \rvert \le \epsilon$
-				% \State Set $\boldsymbol{\Phi}^{\star} \gets \boldsymbol{\Phi}^{(i)}$
-				% \State Get $\hat{\boldsymbol{\phi}}^\star$ by eigen decomposition, $\boldsymbol{\Phi}^{\star}=\hat{\boldsymbol{\phi}}^\star(\hat{\boldsymbol{\phi}}^\star)^H$
-				% \State Set $\boldsymbol{\phi}^{\star} \gets e^{j \arg\left([\hat{\boldsymbol{\phi}}^\star]_{(1:L)} \middle/ [\hat{\boldsymbol{\phi}}^\star]_{(L+1)}\right)}$
-				% \State \textbf{Output} $\boldsymbol{\phi}^{\star}$
 			\end{algorithmic}
@@
 		\end{equation}
-		is the regularized incomplete Gamma function that explicitly substitutes the \gls{dtmac} transition probability \eqref{eq:dtmac}.
+		is the regularized incomplete Gamma function that substitutes the \gls{dtmac} transition probability \eqref{eq:dtmac}.
 		Its series representation is given by \cite[Theorem~3]{Jameson2016}
@@
 		\end{align}
-		We further write the gradient of \eqref{eq:regularized_incomplete_gamma_series} and \eqref{eq:weighted_sum_mutual_information_explicit} w.r.t.
-$\boldsymbol{w}^*$ as \eqref{eq:regularized_incomplete_gamma_gradient} and TODO at the end of page \pageref{eq:regularized_incomplete_gamma_gradient} and TODO, respectively.
+		Next, we derive the gradients of \eqref{eq:regularized_incomplete_gamma_series} and \eqref{eq:weighted_sum_mutual_information_explicit} w.r.t.
+$\boldsymbol{w}^*$ as \eqref{eq:regularized_incomplete_gamma_gradient} and \eqref{eq:weighted_sum_mutual_information_gradient} at the end of page \pageref{eq:regularized_incomplete_gamma_gradient} and \pageref{eq:weighted_sum_mutual_information_gradient}, respectively.
 		\begin{figure*}[!b]
@@
 		\begin{figure*}[!b]
+			\hrule
 			\begin{align}
@@
 				 & \qquad \times \nabla_{\boldsymbol{w}^*} Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr)-\frac{Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr)\sum_{m_{\mathcal{K}}'}P_{\mathcal{K}}(x_{m_{\mathcal{K}}'})\nabla_{\boldsymbol{w}^*}Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}'}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}'}^2}\Bigr)}{\sum_{m_{\mathcal{K}}'}P_{\mathcal{K}}(x_{m_{\mathcal{K}}'})Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}'}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}'}^2}\Bigr)}\Biggr)
+				\label{eq:weighted_sum_mutual_information_gradient}
 			\end{align}
 		\end{figure*}
-		% The optimal precoder design is highly non-convex that involves integration, entropy term, and variable on exponential.
-		% We may propose a suboptimal precoder based on linear combination of equivalent and cascaded channels, or consider single transmit antenna instead.
+		% Next, we express the gradient of \eqref{eq:regularized_incomplete_gamma_series} and \eqref{eq:weighted_sum_mutual_information_explicit} w.r.t.
+$\boldsymbol{w}^*$ as \eqref{eq:regularized_incomplete_gamma_gradient} and \eqref{eq:weighted_sum_mutual_information_gradient} at the end of page \pageref{eq:regularized_incomplete_gamma_gradient},
+		It allows problem \eqref{op:active_beamforming} to be solved by the \gls{pgd} method, where any unregulated beamforming vector $\bar{\boldsymbol{w}}$ can be projected onto the feasible domain of average transmit power constraint \eqref{co:transmit_power} by
+		% the projection function associated with average transmit power constraint \eqref{co:transmit_power} is
+		\begin{equation}
+			\boldsymbol{w} = \sqrt{P} \frac{\bar{\boldsymbol{w}}}{\max\bigl(\sqrt{P},\lVert\bar{\boldsymbol{w}}\rVert\bigr)}.
+			\label{eq:beamforming_projection}
+		\end{equation}
+		We present the iterative active beamforming design accelerated by backtracking line search in Algorithm \ref{al:active_beamforming}.
+		\begin{algorithm}[!t]
+			\caption{Iterative Active Beamforming Design by \gls{pgd} with Backtracking Line Search}
+			\label{al:active_beamforming}
+			\begin{algorithmic}[1]
+				\Require $Q$, $N$, $\boldsymbol{h}_{\mathrm{D}}^H$, $\boldsymbol{H}_{\mathrm{C}}$, $\boldsymbol{\alpha}$, $\mathcal{X}$, $P$, $\sigma_v^2$, $\rho$, $\{\boldsymbol{p}_k\}_{k \in \mathcal{K}}$, $\boldsymbol{t}$, $\alpha$, $\beta$, $\gamma$, $\epsilon$
+				\Ensure $\boldsymbol{w}^\star$
+				\State Set $\boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}$ by \eqref{eq:equivalent_channel}
+				\State \phantom{Set} $P_{\mathcal{K}}(x_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}$ by \eqref{eq:equivalent_distribution}
+				\State Initialize $r \gets 0$
+				\State \phantom{Initialize} $\boldsymbol{w}^{(0)}$, $\lVert\boldsymbol{w}^{(0)}\rVert^2 \le P$
+				\State Get $(\sigma_{m_{\mathcal{K}}}^{(0)})^2$, $\forall m_{\mathcal{K}}$ by \eqref{eq:receive_variance}
+				\State \phantom{Get} $Q^{(0)}\bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\bigr)$, $\forall m_{\mathcal{K}},l$ by \eqref{eq:regularized_incomplete_gamma} or \eqref{eq:regularized_incomplete_gamma_series}
+				\State \phantom{Get} $I^{(0)}(x_{\mathcal{K}})$ by \eqref{eq:weighted_sum_mutual_information_explicit}
+				\State \phantom{Get} $\nabla_{\boldsymbol{w}^*} Q^{(0)}\bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\bigr)$, $\forall m_{\mathcal{K}},l$ by \eqref{eq:regularized_incomplete_gamma_gradient}
+				\State \phantom{Get} $\nabla_{\boldsymbol{w}^*} I^{(0)}(x_{\mathcal{K}})$ by \eqref{eq:weighted_sum_mutual_information_gradient}
+				\Repeat
+					\State Update $r \gets r+1$
+					\State \phantom{Update} $\bar{\boldsymbol{w}}^{(r)} \gets \boldsymbol{w}^{(r-1)}+\gamma\nabla_{\boldsymbol{w}^*} I^{(r-1)}(x_{\mathcal{K}})$ \label{st:gradient_descent_begin}
+					\State \phantom{Update} $\boldsymbol{w}^{(r)}$ by \eqref{eq:beamforming_projection}
+					\State \phantom{Update} $(\sigma_{m_{\mathcal{K}}}^{(r)})^2$, $\forall m_{\mathcal{K}}$ by \eqref{eq:receive_variance}
+					\State \phantom{Update} $Q^{(r)}\bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\bigr)$, $\forall m_{\mathcal{K}},l$ by \eqref{eq:regularized_incomplete_gamma} or \eqref{eq:regularized_incomplete_gamma_series}
+					\State \phantom{Update} $I^{(r)}(x_{\mathcal{K}})$ by \eqref{eq:weighted_sum_mutual_information_explicit} \label{st:gradient_descent_end}
+					% \While{$I^{(r-1)}(x_{\mathcal{K}})>I^{(r)}(x_{\mathcal{K}})+\alpha\gamma\lVert\nabla_{\boldsymbol{w}^*}I^{(r-1)}(x_{\mathcal{K}})\rVert$}
+					\While{$I^{(r)}(x_{\mathcal{K}})<I^{(r-1)}(x_{\mathcal{K}})-\alpha\gamma\lVert\nabla_{\boldsymbol{w}^*}I^{(r-1)}(x_{\mathcal{K}})\rVert^2$}
+						\State Set $\gamma\gets\beta\gamma$
+						\State Redo Step \ref{st:gradient_descent_begin}--\ref{st:gradient_descent_end}
+					\EndWhile
+				\Until $\lVert\boldsymbol{w}^{(r)}-\boldsymbol{w}^{(r-1)}\rVert \le \epsilon$
+			\end{algorithmic}
+		\end{algorithm}
 	\end{subsection}
@@
 	\begin{subsection}{Decision Threshold}
-
-		For a given tag input distribution $\{\boldsymbol{p}_k\}_{k \in \mathcal{K}}$, we can formulate an equivalent information source with augmented alphabet of tag input combination.
-		This equivalent source transmits at the total backscatter rate, and the input distribution is given by $P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) = \prod_{k \in \mathcal{K}} P_k(x_{m_k})$, $\forall k \in \mathcal{K}$ and $\forall m_k \in \mathcal{M}$.
+		% Once node input distribution $\{\boldsymbol{p}_k\}_{k \in \mathcal{K}}$ and active beamforming vector $\boldsymbol{w}$ are obtained, problem \eqref{op:weighted_sum_rate}
+		For any given $\{\boldsymbol{p}_k\}_{k \in \mathcal{K}}$ and $\boldsymbol{w}$, problem \eqref{op:weighted_sum_rate} reduces to
+		\begin{maxi!}
+			{\scriptstyle{\{\boldsymbol{p}_k\}_{k \in \mathcal{K}},\boldsymbol{w},\boldsymbol{t}\in\mathbb{R}_+^{L+1}}}{I(x_{\mathcal{K}})}{\label{op:decision_threshold}}{\label{ob:decision_threshold}}
+			\addConstraint{\eqref{co:decision_threshold}.}
+		\end{maxi!}
 
 		\begin{remark}
-			Since the equivalent source transmits at the total backscatter rate, the \gls{dtmac} \eqref{eq:dtmac} is essentially a point-to-point \gls{dmtc} and we can simplify the decision threshold design accordingly.
-			\label{re:input_combination}
+			Ideally, backscatter detection (and decision design) has no impact on primary achievable rate.
+			When nodes transmit at non-zero total rate, the user can re-encode backscatter messages to recover coded backscatter symbol $x_{\mathcal{K}}$ at each block.
+Otherwise, $x_{\mathcal{K}}$ can be deterministic and known to the user.
+			% Decision threshold only influences backscatter rate instead of primary rate.
+		\end{remark}
+
+		\begin{remark}
+			% With input distribution of all nodes, we can formulate an equivalent information source with augmented alphabet of tag input combination.
+			% In terms of total backscatter rate, we can formulate an equivalent information source with augmented alphabet of tag input combination.
+			% When input distribution of all nodes are available, we can formulate an equivalent information source in terms of total backscatter rate.
+			% When input distribution of all nodes are available, we can think an equivalent information source with augmented alphabet of state tuple, in terms of total backscatter rate.
+			In terms of total backscatter rate, we can regard all nodes as an equivalent information source with augmented alphabet of node state tuple $x_{m_{\mathcal{K}}}$.
+			As such, the \gls{dtmac} \eqref{eq:dtmac} is essentially a \gls{dmtc}, and decision threshold design can be simplified accordingly.
 		\end{remark}
@@
 	\end{subsection}
-
 \end{section}
 
-\begin{section}{Preliminary Results}
+\begin{section}{Simulation Results}
+	In this section, we provide numerical results to evaluate the proposed input distribution, active beamforming and decision threshold designs over the Metascatter-enabled network in Fig.
+\ref{fi:metascatter_network}.
+
 	\begin{table}[t!]

### 2022-07-21 main.tex
:pencil: Update algorithms

@@
 				\State \phantom{Initialize} $\boldsymbol{p}_k^{(0)} > \boldsymbol{0}$, $\forall k$
-				\State Get $P_{\mathcal{K}}^{(0)}(x_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}$ by \eqref{eq:equivalent_distribution}
-				\State \phantom{Get} $I^{(0)}(x_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}$ by \eqref{eq:backscatter_information_function}, \eqref{eq:primary_information_function}, \eqref{eq:weighted_sum_information_function}
-				\State \phantom{Get} $I^{(0)}_k(x_{m_k})$, $\forall k,m_k$ by \eqref{eq:backscatter_marginal_information}, \eqref{eq:primary_marginal_information}, \eqref{eq:weighted_sum_marginal_information}
-				\State \phantom{Get} $I^{(0)}(x_{\mathcal{K}})$ by \eqref{eq:backscatter_mutual_information}, \eqref{eq:primary_mutual_information}, \eqref{eq:weighted_sum_mutual_information}
+				\State Get $P_{\mathcal{K}}^{(r)}(x_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}$ by \eqref{eq:equivalent_distribution} \label{st:input_distribution_begin}
+				\State \phantom{Get} $I^{(r)}(x_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}$ by \eqref{eq:backscatter_information_function}, \eqref{eq:primary_information_function}, \eqref{eq:weighted_sum_information_function}
+				\State \phantom{Get} $I^{(r)}_k(x_{m_k})$, $\forall k,m_k$ by \eqref{eq:backscatter_marginal_information}, \eqref{eq:primary_marginal_information}, \eqref{eq:weighted_sum_marginal_information}
+				\State \phantom{Get} $I^{(r)}(x_{\mathcal{K}})$ by \eqref{eq:backscatter_mutual_information}, \eqref{eq:primary_mutual_information}, \eqref{eq:weighted_sum_mutual_information} \label{st:input_distribution_end}
 				\Repeat
@@
 					\State \phantom{Update} $\boldsymbol{p}_k^{(r)}$, $\forall k$ by \eqref{eq:input_kkt_solution}
-					\State Get $P_{\mathcal{K}}^{(r)}(x_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}$ by \eqref{eq:equivalent_distribution}
-					\State \phantom{Get} $I^{(r)}(x_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}$ by \eqref{eq:backscatter_information_function}, \eqref{eq:primary_information_function}, \eqref{eq:weighted_sum_information_function}
-					\State \phantom{Get} $I^{(r)}_k(x_{m_k})$, $\forall k,m_k$ by \eqref{eq:backscatter_marginal_information}, \eqref{eq:primary_marginal_information}, \eqref{eq:weighted_sum_marginal_information}
-					\State \phantom{Get} $I^{(r)}(x_{\mathcal{K}})$ by \eqref{eq:backscatter_mutual_information}, \eqref{eq:primary_mutual_information}, \eqref{eq:weighted_sum_mutual_information}
+					\State Redo step \ref{st:input_distribution_begin}--\ref{st:input_distribution_end}
+					% \State Get $P_{\mathcal{K}}^{(r)}(x_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}$ by \eqref{eq:equivalent_distribution}
+					% \State \phantom{Get} $I^{(r)}(x_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}$ by \eqref{eq:backscatter_information_function}, \eqref{eq:primary_information_function}, \eqref{eq:weighted_sum_information_function}
+					% \State \phantom{Get} $I^{(r)}_k(x_{m_k})$, $\forall k,m_k$ by \eqref{eq:backscatter_marginal_information}, \eqref{eq:primary_marginal_information}, \eqref{eq:weighted_sum_marginal_information}
+					% \State \phantom{Get} $I^{(r)}(x_{\mathcal{K}})$ by \eqref{eq:backscatter_mutual_information}, \eqref{eq:primary_mutual_information}, \eqref{eq:weighted_sum_mutual_information}
 				\Until $I^{(r)}(x_{\mathcal{K}}) - I^{(r-1)}(x_{\mathcal{K}}) \le \epsilon$
@@
 				\State \phantom{Initialize} $\boldsymbol{w}^{(0)}$, $\lVert\boldsymbol{w}^{(0)}\rVert^2 \le P$
-				\State Get $(\sigma_{m_{\mathcal{K}}}^{(0)})^2$, $\forall m_{\mathcal{K}}$ by \eqref{eq:receive_variance}
-				\State \phantom{Get} $Q^{(0)}\bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\bigr)$, $\forall m_{\mathcal{K}},l$ by \eqref{eq:regularized_incomplete_gamma} or \eqref{eq:regularized_incomplete_gamma_series}
-				\State \phantom{Get} $I^{(0)}(x_{\mathcal{K}})$ by \eqref{eq:weighted_sum_mutual_information_explicit}
-				\State \phantom{Get} $\nabla_{\boldsymbol{w}^*} Q^{(0)}\bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\bigr)$, $\forall m_{\mathcal{K}},l$ by \eqref{eq:regularized_incomplete_gamma_gradient}
-				\State \phantom{Get} $\nabla_{\boldsymbol{w}^*} I^{(0)}(x_{\mathcal{K}})$ by \eqref{eq:weighted_sum_mutual_information_gradient}
+				\State Get $(\sigma_{m_{\mathcal{K}}}^{(r)})^2$, $\forall m_{\mathcal{K}}$ by \eqref{eq:receive_variance} \label{st:gradient_descent_begin}
+				\State \phantom{Get} $Q^{(r)}\bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\bigr)$, $\forall m_{\mathcal{K}},l$ by \eqref{eq:regularized_incomplete_gamma} or \eqref{eq:regularized_incomplete_gamma_series}
+				\State \phantom{Get} $I^{(r)}(x_{\mathcal{K}})$ by \eqref{eq:weighted_sum_mutual_information_explicit} \label{st:gradient_descent_end}
+				\State \phantom{Get} $\nabla_{\boldsymbol{w}^*} Q^{(r)}\bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\bigr)$, $\forall m_{\mathcal{K}},l$ by \eqref{eq:regularized_incomplete_gamma_gradient} \label{st:gradient_update_start}
+				\State \phantom{Get} $\nabla_{\boldsymbol{w}^*} I^{(r)}(x_{\mathcal{K}})$ by \eqref{eq:weighted_sum_mutual_information_gradient} \label{st:gradient_update_end}
 				\Repeat
 					\State Update $r \gets r+1$
-					\State \phantom{Update} $\bar{\boldsymbol{w}}^{(r)} \gets \boldsymbol{w}^{(r-1)}+\gamma\nabla_{\boldsymbol{w}^*} I^{(r-1)}(x_{\mathcal{K}})$ \label{st:gradient_descent_begin}
+					\State \phantom{Update} $\bar{\boldsymbol{w}}^{(r)} \gets \boldsymbol{w}^{(r-1)}+\gamma\nabla_{\boldsymbol{w}^*} I^{(r-1)}(x_{\mathcal{K}})$ \label{st:backtracking_line_search_begin}
 					\State \phantom{Update} $\boldsymbol{w}^{(r)}$ by \eqref{eq:beamforming_projection}
-					\State \phantom{Update} $(\sigma_{m_{\mathcal{K}}}^{(r)})^2$, $\forall m_{\mathcal{K}}$ by \eqref{eq:receive_variance}
-					\State \phantom{Update} $Q^{(r)}\bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\bigr)$, $\forall m_{\mathcal{K}},l$ by \eqref{eq:regularized_incomplete_gamma} or \eqref{eq:regularized_incomplete_gamma_series}
-					\State \phantom{Update} $I^{(r)}(x_{\mathcal{K}})$ by \eqref{eq:weighted_sum_mutual_information_explicit} \label{st:gradient_descent_end}
+					\State Redo step \ref{st:gradient_descent_begin}--\ref{st:gradient_descent_end} \label{st:backtracking_line_search_end}
+					% \State \phantom{Update} $(\sigma_{m_{\mathcal{K}}}^{(r)})^2$, $\forall m_{\mathcal{K}}$ by \eqref{eq:receive_variance}
+					% \State \phantom{Update} $Q^{(r)}\bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\bigr)$, $\forall m_{\mathcal{K}},l$ by \eqref{eq:regularized_incomplete_gamma} or \eqref{eq:regularized_incomplete_gamma_series}
+					% \State \phantom{Update} $I^{(r)}(x_{\mathcal{K}})$ by \eqref{eq:weighted_sum_mutual_information_explicit} \label{st:backtracking_line_search_end}
 					% \While{$I^{(r-1)}(x_{\mathcal{K}})>I^{(r)}(x_{\mathcal{K}})+\alpha\gamma\lVert\nabla_{\boldsymbol{w}^*}I^{(r-1)}(x_{\mathcal{K}})\rVert$}
@@
 						\State Set $\gamma\gets\beta\gamma$
-						\State Redo Step \ref{st:gradient_descent_begin}--\ref{st:gradient_descent_end}
+						\State Redo step \ref{st:backtracking_line_search_begin}--\ref{st:backtracking_line_search_end}
 					\EndWhile
+					\State Redo step \ref{st:gradient_update_start}, \ref{st:gradient_update_end}
 				\Until $\lVert\boldsymbol{w}^{(r)}-\boldsymbol{w}^{(r-1)}\rVert \le \epsilon$

### 2022-07-22 assets/illustration/energy_distribution.tex
:truck: Move assets

--- 2022-07-16 assets/energy_distribution.tex
@@
 \begin{tikzpicture}
-	\begin{axis}[%
+	\begin{axis}[
 			height=5cm,
@@
 			xmax=70,
-			%     ticks=none,
 			xtick={0,12.78,20.28,29.62,70},
@@
 			yticklabels={},
-			samples = 200]
+			samples = 200
+		]
 
@@
 		\draw[color=gray,thick,dashed] (29.62,0) -- (29.62,0.1);
-		\draw[latex-latex] (0,0.05) -- (12.78,0.05) node[below,midway]{$\mathcal{R}(\mathcal{H}_1)$};
-		\draw[latex-latex] (12.78,0.05) -- (20.28,0.05) node[below,midway]{$\mathcal{R}(\mathcal{H}_2)$};
-		\draw[latex-latex] (20.28,0.05) -- (29.62,0.05) node[below,midway]{$\mathcal{R}(\mathcal{H}_3)$};
-		\draw[latex-latex] (29.62,0.05) -- (70,0.05) node[below,midway]{$\mathcal{R}(\mathcal{H}_4)$};
+		\draw[latex-latex] (0,0.05) -- (12.78,0.05) node[below,midway]{$\mathcal{R}_1$};
+		\draw[latex-latex] (12.78,0.05) -- (20.28,0.05) node[below,midway]{$\mathcal{R}_2$};
+		\draw[latex-latex] (20.28,0.05) -- (29.62,0.05) node[below,midway]{$\mathcal{R}_3$};
+		\draw[latex-latex] (29.62,0.05) -- (70,0.05) node[below,midway]{$\mathcal{R}_4$};
 	\end{axis}

### 2022-07-22 assets/illustration/input_distribution.tex
:truck: Move assets

--- 2022-05-26 assets/reflection_state_distribution.tex
@@
 	\begin{groupplot}
-		[group style={%
+		[group style={
 					rows=3,

### 2022-07-22 main.tex
:package: Remove unused packages

@@
 \usepackage{algpseudocode}
-\usepackage{algorithmicx}
 \usepackage{amsfonts}
@@
 \usepackage{amsthm}
-\usepackage{array}
 \usepackage{bookmark}
-\usepackage{circuitikz}
+\usepackage[american]{circuitikz}
 \usepackage{cite}
-\usepackage{colortbl}
-\usepackage{environ}
 \usepackage{fixmath}
-\usepackage{grffile}
+\usepackage[acronym]{glossaries-extra}
 \usepackage{hyperref}
@@
 \usepackage{microtype}
-\usepackage{multirow}
-\usepackage{pgffor}
-\usepackage{pgfgantt}
+\usepackage[short]{optidef}
 \usepackage{pgfplots}
-\usepackage{physics}
+\usepackage[subtle]{savetrees}
 \usepackage{siunitx}
 \usepackage{stfloats}
-\usepackage{tcolorbox}
+\usepackage[caption=false,font=footnotesize,subrefformat=parens,labelformat=parens]{subfig}
 \usepackage{tikz}
-\usepackage{url}
 \usepackage{xcolor}
-\usepackage[T1]{fontenc}
-\usepackage[acronym]{glossaries-extra}
-\usepackage[caption=false,font=footnotesize,subrefformat=parens,labelformat=parens]{subfig}
-\usepackage[short]{optidef}
-\usepackage[subtle]{savetrees}
-
-\usepackage{xcolor} \pagecolor[rgb]{0,0,0} \color[rgb]{1,1,1}
-
-\listfiles
-\interdisplaylinepenalty=2500
-\pgfplotsset{compat=newest}
-\usepgfplotslibrary{patchplots,groupplots}
-\usetikzlibrary{decorations.pathreplacing,calligraphy}
-\usetikzlibrary{arrows,calc,matrix,plotmarks,patterns,positioning}
+
+% \usepackage{xcolor} \pagecolor[rgb]{0,0,0} \color[rgb]{1,1,1}
+
+% amsthm
 \newtheorem{proposition}{Proposition}
 \newtheorem{remark}{Remark}
-\newtheorem{theorem}{Theorem}
+
+% siunitx
 \DeclareSIUnit{\belm}{Bm}
@@
 \DeclareSIUnit{\dBi}{\deci\beli}
-\ctikzset{american}
-\usetikzlibrary{arrows,calc,matrix,patterns,pgfplots.groupplots,plotmarks,positioning}
-
-\DeclarePairedDelimiterX{\infdivx}[2]{(}{)}{%
-	#1\;\delimsize\|\;#2%
-}
-\newcommand{\infdiv}{D\infdivx}
-\renewcommand{\qedsymbol}{\hfill\ensuremath{\Box}}
-
+
+% PGF/TikZ
+\usetikzlibrary{arrows,calc,matrix,patterns,plotmarks,positioning}
+\usepgfplotslibrary{groupplots,patchplots}
+\pgfplotsset{compat=newest}
+
+% algpseudocode
 \makeatletter
 \renewcommand{\fnum@algorithm}{\fname@algorithm{} \thealgorithm:}
-\tikzset{
-	block/.style={draw,rectangle,align=center},
-    from/.style args={#1 to #2}{
-        above right={0cm of #1},
-        /utils/exec=\pgfpointdiff
-            {\tikz@scan@one@point\pgfutil@firstofone(#1)\relax}
-            {\tikz@scan@one@point\pgfutil@firstofone(#2)\relax},
-        minimum width/.expanded=\the\pgf@x,
-        minimum height/.expanded=\the\pgf@y
-	}
-}
 \makeatother
-
+\algrenewcommand{\algorithmicrequire}{\textbf{Input:}}
+\algrenewcommand{\algorithmicensure}{\textbf{Output:}}
 \algrenewcommand{\algorithmicwhile}{\textbf{While}}
-\algrenewcommand{\algorithmicif}{\textbf{If}}
-\algrenewcommand{\algorithmicthen}{\textbf{Then}}
-\algrenewcommand{\algorithmicelse}{\textbf{Else}}
 \algrenewcommand{\algorithmicend}{\textbf{End}}
@@
 
-% \algrenewcommand\algorithmicdo{}
-% \renewcommand\algorithmicdo{}
-
-\algrenewcommand{\algorithmicrequire}{\textbf{Input:}}
-\algrenewcommand{\algorithmicensure}{\textbf{Output:}}
-
+% glossaries-extra
 \setabbreviationstyle[acronym]{long-short}
-
 \newacronym{af}{AF}{Amplify-and-Forward}
@@
 \newacronym{psk}{PSK}{Phase Shift Keying}
-\newacronym{pin}{PIN}{Positive Intrinsic-Negative}
 \newacronym{qam}{QAM}{Quadrature Amplitude Modulation}
@@
 \newacronym{tdma}{TDMA}{Time-Division Multiple Access}
-\newacronym{tg}{TG}{tag}
 \newacronym{ue}{UE}{user}
@@
 	% A suboptimal \gls{bcd} algorithm was proposed, where the input distribution satisfying the \gls{kkt} conditions is evaluated in closed form, the transmit beamforming is optimized by \gls{pgd}, and the decision thresholds are optimized by \gls{dp}.
-	A suboptimal \gls{bcd} algorithm is proposed, where the \gls{kkt} input distribution is evaluated in closed form, the active beamforming is updated by \gls{pgd}, and the suboptimal convex decision regions are refined by \gls{dp}.
+	% A suboptimal \gls{bcd} algorithm is proposed, where the \gls{kkt} input distribution is numerically evaluated in closed form, the active beamforming is iteratively updated by \gls{pgd}, and the decision regions are restricted to convex and opty
+	% We then propose a suboptimal \gls{bcd} algorithm that numerically evaluates the \gls{kkt} input distribution in closed form, iteratively updates the active beamforming by \gls{pgd}, and employs existing thresholding schemes to refine suboptimal convex decision regions.
+	A suboptimal \gls{bcd} algorithm is proposed, which numerically evaluates the \gls{kkt} input distribution in closed form, iteratively updates the active beamforming by \gls{pgd}, and employs existing thresholding schemes for suboptimal convex decision regions.
 	% A suboptimal \gls{bcd} algorithm was proposed with the \gls{kkt} input distribution evaluated in closed form, the active beamforming updated by \gls{pgd}, and the decision regions restricted to convex then refined by \gls{dp}.
@@
 	\emph{Third,} we evaluate the achievable primary-(total-)backscatter rate region by optimizing the input distribution at Metascatters, the active beamforming at the \gls{ap}, and the decision regions at the user.
-Since the original problem is highly non-convex, we consider a suboptimal \gls{bcd} algorithm where the \gls{kkt} input distribution is numerically evaluated by limit of sequences, the active beamforming is sequentially updated by \gls{pgd} accelerated by backtracking line search, and the decision regions are first restricted to convex, then refined by \gls{dp} and \gls{smawk} algorithm.
+Since the original problem is highly non-convex, we consider a suboptimal \gls{bcd} algorithm where the \gls{kkt} input distribution is numerically evaluated by limit of sequences, the active beamforming is iteratively updated by \gls{pgd} accelerated by backtracking line search, and the decision regions are first restricted to convex, then refined by existing thresholding designs.
 
@@
 	% 		\resizebox{0.8\columnwidth}{!}{
-	% 			\input{assets/block_diagram.tex}
+	% 			\input{assets/illustration/block_diagram.tex}
 	% 		}
@@
 	% 		\resizebox{0.95\columnwidth}{!}{
-	% 			\input{assets/equivalent_circuit.tex}
+	% 			\input{assets/illustration/equivalent_circuit.tex}
 	% 		}
@@
 	% 		\resizebox{0.8\columnwidth}{!}{
-	% 			\input{assets/scatter_model.tex}
+	% 			\input{assets/illustration/scatter_model.tex}
 	% 		}
@@
 			\resizebox{0.32\linewidth}{!}{
-				\input{assets/block_diagram.tex}
+				\input{assets/illustration/block_diagram.tex}
 			}
@@
 			\resizebox{0.37\linewidth}{!}{
-				\input{assets/equivalent_circuit.tex}
+				\input{assets/illustration/equivalent_circuit.tex}
 			}
@@
 			\resizebox{0.28\linewidth}{!}{
-				\input{assets/scatter_model.tex}
+				\input{assets/illustration/scatter_model.tex}
 			}
@@
 			\centering
-			\subfloat[Reflection State Distribution]{
+			\subfloat[Input Distribution]{
 				\resizebox{0.8\columnwidth}{!}{
-					\input{assets/reflection_state_distribution.tex}
+					\input{assets/illustration/input_distribution.tex}
 				}
@@
 			\\
-			\subfloat[Time Slot Structure]{
+			\subfloat[Time Block]{
 				\resizebox{0.8\columnwidth}{!}{
-					\input{assets/time_block_structure.tex}
+					\input{assets/illustration/time_block.tex}
 				}
@@
 			\caption{
-				Reflection state distribution and time block structure of \gls{sr}, \gls{irs}, and Metascatter.
+				Input probability distribution and time block structure of \gls{sr}, \gls{irs}, and Metascatter.
 				$T_s$ and $T_c$ respectively denote the primary and backscatter symbol period.
@@
 			\footnotesize{
-				\import{assets/}{metascatter_network.eps_tex}
+				\import{assets/illustration/}{metascatter_network.eps_tex}
 			}
@@
 			\resizebox{0.9\columnwidth}{!}{
-				\input{assets/energy_distribution.tex}
+				\input{assets/illustration/energy_distribution.tex}
 			}
@@
 		\begin{equation}
-			P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}}) = \int_{\mathcal{R}_{m_{\mathcal{K}}'}} f(z|\mathcal{H}_{m_{\mathcal{K}}}) \dd z,
+			P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}}) = \int_{\mathcal{R}_{m_{\mathcal{K}}'}} f(z|\mathcal{H}_{m_{\mathcal{K}}}) \, d z,
 			\label{eq:dtmac}
@@
 		\begin{maxi!}
-			{\scriptstyle{\{\boldsymbol{p}_k\}_{k \in \mathcal{K}}}}{I(x_{\mathcal{K}})}{\label{op:input_probability_distribution}}{}
+			{\scriptstyle{\{\boldsymbol{p}_k\}_{k \in \mathcal{K}}}}{I(x_{\mathcal{K}})}{\label{op:input_distribution}}{}
 			\addConstraint{\eqref{co:sum_probability},\eqref{co:nonnegative_probability},}
@@
 			As pointed out in \cite{Buhler2011}, \gls{kkt} conditions are generally necessary but insufficient for total rate maximization in discrete memoryless \gls{mac}.
-Therefore, \gls{kkt} solutions may end up being saddle points of problem \eqref{op:input_probability_distribution}.
+Therefore, \gls{kkt} solutions may end up being saddle points of problem \eqref{op:input_distribution}.
 		\end{remark}
-		Following \cite{Rezaeian2004}, we first recast \gls{kkt} conditions to their equivalent form for problem \eqref{op:input_probability_distribution}, then propose an iterative method that guarantees input distribution satisfying above conditions on convergence.
-		% Interestingly, the total-rate optimal input design for general discrete memoryless \gls{mac} remains an open problem, and we instead propose a \gls{kkt} solution to problem \eqref{op:input_probability_distribution}.
+		Following \cite{Rezaeian2004}, we first recast \gls{kkt} conditions to their equivalent form for problem \eqref{op:input_distribution}, then propose an iterative method that guarantees input distribution satisfying above conditions on convergence.
+		% Interestingly, the total-rate optimal input design for general discrete memoryless \gls{mac} remains an open problem, and we instead propose a \gls{kkt} solution to problem \eqref{op:input_distribution}.
 		\begin{proposition}
-			% The \gls{kkt} optimality conditions for problem \eqref{op:input_probability_distribution} are equivalent to, $\forall k \in \mathcal{K}$ and $\forall m_k \in \mathcal{M}$,
-			The \gls{kkt} optimality conditions for problem \eqref{op:input_probability_distribution} are equivalent to, $\forall k,m_k$,
+			% The \gls{kkt} optimality conditions for problem \eqref{op:input_distribution} are equivalent to, $\forall k \in \mathcal{K}$ and $\forall m_k \in \mathcal{M}$,
+			The \gls{kkt} optimality conditions for problem \eqref{op:input_distribution} are equivalent to, $\forall k,m_k$,
 			\begin{subequations}
@@
 		\begin{equation}
-			Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr) = \frac{\int_{{t_{l-1}}/{\sigma_{m_{\mathcal{K}}}^2}}^{{t_l}/{\sigma_{m_{\mathcal{K}}}^2}} z^{N-1} \exp(-z) \dd z}{(N-1)!}
+			Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr) = \frac{\int_{{t_{l-1}}/{\sigma_{m_{\mathcal{K}}}^2}}^{{t_l}/{\sigma_{m_{\mathcal{K}}}^2}} z^{N-1} \exp(-z) \, d z}{(N-1)!}
 			\label{eq:regularized_incomplete_gamma}
@@
 					\State Update $r \gets r+1$
+					\State \phantom{Update} $\gamma^{(r)}\gets\gamma$
 					\State \phantom{Update} $\bar{\boldsymbol{w}}^{(r)} \gets \boldsymbol{w}^{(r-1)}+\gamma\nabla_{\boldsymbol{w}^*} I^{(r-1)}(x_{\mathcal{K}})$ \label{st:backtracking_line_search_begin}
@@
 					\While{$I^{(r)}(x_{\mathcal{K}})<I^{(r-1)}(x_{\mathcal{K}})-\alpha\gamma\lVert\nabla_{\boldsymbol{w}^*}I^{(r-1)}(x_{\mathcal{K}})\rVert^2$}
-						\State Set $\gamma\gets\beta\gamma$
+						\State Set $\gamma^{(r)}\gets\beta\gamma^{(r)}$
 						\State Redo step \ref{st:backtracking_line_search_begin}--\ref{st:backtracking_line_search_end}
@@
 		\begin{maxi!}
-			{\scriptstyle{\{\boldsymbol{p}_k\}_{k \in \mathcal{K}},\boldsymbol{w},\boldsymbol{t}\in\mathbb{R}_+^{L+1}}}{I(x_{\mathcal{K}})}{\label{op:decision_threshold}}{\label{ob:decision_threshold}}
-			\addConstraint{\eqref{co:decision_threshold}.}
+			{\scriptstyle{\boldsymbol{t}\in\mathbb{R}_+^{L+1}}}{I(x_{\mathcal{K}})}{\label{op:decision_threshold}}{\label{ob:decision_threshold}}
+			\addConstraint{\eqref{co:decision_threshold},}
 		\end{maxi!}
+		where it is trivial to conclude $t_0^\star=0$ and $t_L^\star=\infty$ for energy-based backscatter detection.
 
 		\begin{remark}
-			Ideally, backscatter detection (and decision design) has no impact on primary achievable rate.
-			When nodes transmit at non-zero total rate, the user can re-encode backscatter messages to recover coded backscatter symbol $x_{\mathcal{K}}$ at each block.
-Otherwise, $x_{\mathcal{K}}$ can be deterministic and known to the user.
+			Backscatter detection (and decision design) has no impact on primary achievable rate.
+			When nodes transmit at non-zero total rate, the user can re-encode backscatter messages to recover coded backscatter tuple $x_{\mathcal{K}}$ at each block.
+			Otherwise, $x_{\mathcal{K}}$ can be fully deterministic and known to the user.
+			% Once backscatter messages are successfully decoded, the user can re-encode backscatter messages to recover coded backscatter tuple $x_{\mathcal{K}}$ at each block.
+			% Upon successful backscatter detection, the user can re-encode backscatter messages to recover coded backscatter tuple $x_{\mathcal{K}}$ at each block.
+			% Therefore, decision design has no impact on primary achievable rate.
 			% Decision threshold only influences backscatter rate instead of primary rate.
+			\label{re:backscatter_detection}
 		\end{remark}
+
+		Remark \ref{re:backscatter_detection} suggests any $\boldsymbol{t}$ maximizes total backscatter mutual information $I^{\mathrm{B}}(x_{\mathcal{K}};\hat{x}_{\mathcal{K}})$ is also optimal for problem \eqref{op:decision_threshold}.
 
@@
 			% When input distribution of all nodes are available, we can think an equivalent information source with augmented alphabet of state tuple, in terms of total backscatter rate.
-			In terms of total backscatter rate, we can regard all nodes as an equivalent information source with augmented alphabet of node state tuple $x_{m_{\mathcal{K}}}$.
-			As such, the \gls{dtmac} \eqref{eq:dtmac} is essentially a \gls{dmtc}, and decision threshold design can be simplified accordingly.
+			% In terms of total backscatter rate, we can regard all nodes as an equivalent information source with augmented alphabet of node state tuple $x_{m_{\mathcal{K}}}$.
+			In terms of total backscatter rate, the nodes can be regarded as an equivalent source with augmented alphabet of symbol tuple $x_{m_{\mathcal{K}}}$, and the \gls{dtmac} \eqref{eq:dtmac} essentially reduces to a \gls{dmtc}.
+			% As such, the \gls{dtmac} \eqref{eq:dtmac} is essentially a \gls{dmtc}, and decision threshold design can be simplified accordingly.
 		\end{remark}
 
-		Interestingly, the optimal threshold design to maximize the mutual information for a general \gls{dmtc} with a fixed number of output letters remains an open issue.
-		The reason is that each decision region may contain more than one disjoint partitions (i.e., non-convex) and the number of thresholds are unknown.
-		Fortunately, for the proposed energy detection, we proved that the \gls{dmtc} capacity can be achieved using only convex decision regions.
-		This conclusion is summarized below.
-
-		\begin{proposition}
-			For a discrete-input continuous-output channel in Erlang distribution \eqref{eq:energy_distribution}, if the \gls{dmtc} is constructed for detection (i.e., same input/output alphabet) and $L$ input letters are with non-zero probability, then it is possible to achieve the \gls{dmtc} capacity by $L$ non-empty convex decision regions defined by $L+1$ distinct decision thresholds.
-			\label{pr:threshold}
-		\end{proposition}
-
-		\begin{proof}
-			Please refer to Appendix \ref{ap:threshold}.
-			\label{pf:threshold}
-		\end{proof}
-
-		Once the optimal number of decision threshold is determined, we can first discretize the output energy level into numerous bins, then obtain the optimal decision regions that maximizes the total backscatter rate by \gls{dp} accelerated by \gls{smawk} algorithm \cite{He2021}.
-
-		\begin{tcolorbox}
-			We may need to tailor threshold design for Metascatter as threshold design has potential impact on primary achievable rate, as implied by some simulation results.
-		\end{tcolorbox}
+		Finally, we can employ existing thresholding design for \gls{dmtc} to solve problem \eqref{op:decision_threshold}.
+		For example, \cite{He2021} first discretized the continuous energy $z$ into numerous output bins, then grouped adjacent bins to maximize mutual information using \gls{dp} accelerated by \gls{smawk} algorithm.
+		In \cite{Nguyen2020a}, the authors first proved the optimality condition for any three neighbor thresholds, then fix $t_0$, traverse $t_1$, and sequentially optimizes the others by bisection.
+		Both will be compared with \gls{ml} decision \cite{Qian2019}
+		\begin{equation}
+			t_{l}^{\mathrm{\gls{ml}}} = N \frac{\sigma_{l-1}^2 \sigma_{l}^2}{\sigma_{l-1}^2 - \sigma_{l}^2} \log \frac{\sigma_{l-1}^2}{\sigma_{l}^2}, \quad l \in \mathcal{L} \setminus \{0,L\},
+			\label{eq:detection_threshold_maximum_likelihood}
+		\end{equation}
+		which is generally suboptimal for problem \eqref{op:decision_threshold} except for equiprobable inputs at all nodes.
+
+		% \begin{remark}
+		% 	Although the \gls{ml} decision threshold is optimal in terms of the likelihood function, it is not necessarily capacity-achieving, although the performance gap can be negligible in the single-tag \gls{bibo} case.
+		% \end{remark}
+
+		% Interestingly, the optimal threshold design to maximize the mutual information for a general \gls{dmtc} with a fixed number of output letters remains an open issue.
+		% The reason is that each decision region may contain more than one disjoint partitions (i.e., non-convex) and the number of thresholds are unknown.
+		% Fortunately, for the proposed energy detection, we proved that the \gls{dmtc} capacity can be achieved using only convex decision regions.
+		% This conclusion is summarized below.
+
+		% \begin{proposition}
+		% 	For a discrete-input continuous-output channel in Erlang distribution \eqref{eq:energy_distribution}, if the \gls{dmtc} is constructed for detection (i.e., same input/output alphabet) and $L$ input letters are with non-zero probability, then it is possible to achieve the \gls{dmtc} capacity by $L$ non-empty convex decision regions defined by $L+1$ distinct decision thresholds.
+		% 	\label{pr:threshold}
+		% \end{proposition}
+
+		% \begin{proof}
+		% 	Please refer to Appendix \ref{ap:threshold}.
+		% 	\label{pf:threshold}
+		% \end{proof}
+
+		% Once the optimal number of decision threshold is determined, we can first discretize the output energy level into numerous bins, then obtain the optimal decision regions that maximizes the total backscatter rate by \gls{dp} accelerated by \gls{smawk} algorithm \cite{He2021}.
 	\end{subsection}
@@
 \ref{fi:metascatter_network}.
-
-	\begin{table}[t!]
-		\centering
-		\caption{Parameters in simulation}
-		\begin{tabular}{ll}
-			Transmit antenna $Q$     & 1   \\
-			Tags $K$                 & 2   \\
-			States $M$               & 2   \\
-			Reflect ratio $\alpha$   & 0.5 \\
-			Duration ratio $N$       & 10  \\
-			Noise power $\sigma_v^2$ & 1   \\
-			Discretization bins      & 256
-		\end{tabular}
-		\label{ta:parameters}
-	\end{table}
-	Table \ref{ta:parameters} shows the parameters used in simulation.
-	We assume all links are in standard \gls{cscg} distribution and evaluated the rate regions on two instances.
-	For the input design, ``Cooperation'' assumes full transmit cooperation at all tags (i.e., joint encoding), ``Exhaustion'' runs exhaustive search on all possible input distributions, ``\gls{kkt}'' is proposed \gls{kkt} input design \eqref{eq:input_kkt_solution}, and ``Marginalization'' marginalizes the joint input array by ``Cooperation'' to obtain independent tag input distribution.
-	For the threshold design, ``\gls{smawk}'' refers to the \gls{dp}-based quantization proposed in \cite{He2021}, ``Bisection'' sequentially optimizes each threshold by bisection \cite{Nguyen2020a}, and ``\gls{ml}'' is the \gls{ml} detector that requires no knowledge of input distribution.
-
-	Figs. \ref{fi:rate_region_1} and \ref{fi:rate_region_2} show two typical scenarios where joint encoding can be helpful and unnecessary, respectively.
-	Although the proposed \gls{kkt} input design converges to the optimal solutions in both examples, it may be trapped at saddle points under poor initialization, especially when the number of tags increases.
-
-	We believed threshold design has no impact on the primary achievable rate, because primary decoding acts on $\boldsymbol{y}$ while thresholding acts on $z$.
-	As such, the threshold that maximizes the total backscatter rate should also maximize the weighted sum rate.
-	Interestingly, this may not be the case because the \gls{smawk} and Bisection threshold designs, both maximizing the total backscatter rate, can be outperformed by the \gls{ml} when it comes to weighted sum primary-(total-)backscatter rate.
-	It may result from a precision issue, but inspires further research on threshold design for Metascatter.
-
-	\begin{figure}[!t]
-		\centering
-		\resizebox{\columnwidth}{!}{
-			\includegraphics{assets/rate_region_1.eps}
-		}
-		\caption{Achievable rate regions by input-threshold design: Case I.}
-		\label{fi:rate_region_1}
-	\end{figure}
-
-	\begin{figure}[!t]
-		\centering
-		\resizebox{\columnwidth}{!}{
-			\includegraphics{assets/rate_region_2.eps}
-		}
-		\caption{Achievable rate regions by input-threshold design: Case II.}
-		\label{fi:rate_region_2}
-	\end{figure}
 	The parameters remain fixed unless specified.
+
+	% \begin{table}[t!]
+	% 	\centering
+	% 	\caption{Parameters in simulation}
+	% 	\begin{tabular}{ll}
+	% 		Transmit antenna $Q$     & 1   \\
+	% 		Tags $K$                 & 2   \\
+	% 		States $M$               & 2   \\
+	% 		Reflect ratio $\alpha$   & 0.5 \\
+	% 		Duration ratio $N$       & 10  \\
+	% 		Noise power $\sigma_v^2$ & 1   \\
+	% 		Discretization bins      & 256
+	% 	\end{tabular}
+	% 	\label{ta:parameters}
+	% \end{table}
+	% Table \ref{ta:parameters} shows the parameters used in simulation.
+	% We assume all links are in standard \gls{cscg} distribution and evaluated the rate regions on two instances.
+	% For the input design, ``Cooperation'' assumes full transmit cooperation at all tags (i.e., joint encoding), ``Exhaustion'' runs exhaustive search on all possible input distributions, ``\gls{kkt}'' is proposed \gls{kkt} input design \eqref{eq:input_kkt_solution}, and ``Marginalization'' marginalizes the joint input array by ``Cooperation'' to obtain independent tag input distribution.
+	% For the threshold design, ``\gls{smawk}'' refers to the \gls{dp}-based quantization proposed in \cite{He2021}, ``Bisection'' sequentially optimizes each threshold by bisection \cite{Nguyen2020a}, and ``\gls{ml}'' is the \gls{ml} detector that requires no knowledge of input distribution.
+
+	% Figs. \ref{fi:rate_region_1} and \ref{fi:rate_region_2} show two typical scenarios where joint encoding can be helpful and unnecessary, respectively.
+	% Although the proposed \gls{kkt} input design converges to the optimal solutions in both examples, it may be trapped at saddle points under poor initialization, especially when the number of tags increases.
+
+	% We believed threshold design has no impact on the primary achievable rate, because primary decoding acts on $\boldsymbol{y}$ while thresholding acts on $z$.
+	% As such, the threshold that maximizes the total backscatter rate should also maximize the weighted sum rate.
+	% Interestingly, this may not be the case because the \gls{smawk} and Bisection threshold designs, both maximizing the total backscatter rate, can be outperformed by the \gls{ml} when it comes to weighted sum primary-(total-)backscatter rate.
+	% It may result from a precision issue, but inspires further research on threshold design for Metascatter.
+
+	% \begin{figure}[!t]
+	% 	\centering
+	% 	\resizebox{\columnwidth}{!}{
+	% 		\includegraphics{assets/illustration/rate_region_1.eps}
+	% 	}
+	% 	\caption{Achievable rate regions by input-threshold design: Case I.}
+	% 	\label{fi:rate_region_1}
+	% \end{figure}
+
+	% \begin{figure}[!t]
+	% 	\centering
+	% 	\resizebox{\columnwidth}{!}{
+	% 		\includegraphics{assets/illustration/rate_region_2.eps}
+	% 	}
+	% 	\caption{Achievable rate regions by input-threshold design: Case II.}
+	% 	\label{fi:rate_region_2}
+	% \end{figure}
+	% The parameters remain fixed unless specified.
 \end{section}
@@
 		Denote the Lagrange multipliers associated with \eqref{co:sum_probability} and \eqref{co:nonnegative_probability} as $\{\nu_k\}_{k \in \mathcal{K}}$ and $\{\lambda_{k,m_k}\}_{k \in \mathcal{K},m_k \in \mathcal{M}}$, respectively.
-		The Lagrangian function of problem \eqref{op:input_probability_distribution} is
+		The Lagrangian function of problem \eqref{op:input_distribution} is
 		\begin{align}
@@
 		\eqref{eq:input_kkt_condition_transformed}, \eqref{eq:input_kkt_condition_implied}, and \eqref{eq:weighted_sum_marginal_information_implied} together complete the proof.
-		\qedsymbol
 		\label{ap:input_kkt_condition}
@@
 		This completes the proof.
-		\qedsymbol
 		\label{ap:input_kkt_solution}
@@
 
-	\begin{subsection}{Proof of Proposition \ref{pr:threshold}}
-		Since $L$ input letters are with non-zero probability and $x \to z \to \hat{x}$ formulates a Markov chain, we need $L$ non-empty decision regions and at least $L+1$ distinct thresholds (including \num{0} and $\infty$) to minimize the distortion between source and decision.
-		On the other hand, the optimal decision regions are apparently empty for those unused letters.
-
-		Suppose the optimal number of thresholds is $S+1$ where $S \ge L$.
-		Let $\boldsymbol{t} \triangleq [t_0,\ldots,t_S]^T \in \mathbb{R}_{+}^{(S+1) \times 1}$ be the optimal threshold vector where $t_{s-1} < t_s$, $\forall s \in \mathcal{S} \triangleq \{1,\ldots,S\}$.
-		Since the optimal decision region for any letter may consist of multiple partitions, without loss of generality, we assume the mapping from threshold vector to decision region $l' \in \mathcal{L} \triangleq \{1,\ldots,L\}$ is given by $\mathcal{R}_{l'} = \bigcup_{s \equiv l' \pmod L} [t_{s-1},t_s)$.
-		\begin{footnote}
-			The proof holds for any valid mapping from threshold vector to decision regions, and we consider this specific case for the ease of presentation.
-		\end{footnote}
-		The threshold optimization problem is
-		\begin{maxi!}
-			{\scriptstyle{\boldsymbol{t}}}{I_{\mathrm{B}}(x;\hat{x})}{\label{op:decision_threshold}}{\label{ob:backscatter_mutual_information}}
-			\addConstraint{t_{s-1}}{< t_s,}{\quad \forall s \in \mathcal{S}.}{\label{co:strict_inequality}}
-		\end{maxi!}
-
-		Problem \eqref{op:decision_threshold} is intricate due to the strict inequality constraint \eqref{co:strict_inequality}.
-		Following \cite{Nguyen2020}, we first relax it to the convex counterpart, then discard the solutions that violate any original constraint.
-		The Lagrangian function for the relaxed problem is
-		\begin{equation}
-			L = - I_{\mathrm{B}}(x;\hat{x}) + \sum_{s \in \mathcal{S}} \mu_s (t_{s-1} - t_s),
-		\end{equation}
-		where $\mu_s$ is the Lagrange multiplier associated with the non-strict version of \eqref{co:strict_inequality}.
-		The \gls{kkt} conditions on the optimal primal and dual solutions are, $\forall s \in \mathcal{S}$,
-		\begin{subequations}
-			\label{eq:kkt_thresholding}
-			\begin{equation}
-				- \nabla_{t_s^\star} I^\star_{\mathrm{B}}(x;\hat{x}) + \mu_{s-1}^\star - \mu_s^\star = 0,
-				\label{eq:stationarity}
-			\end{equation}
-			\begin{equation}
-				\mu_s^\star \ge 0,
-				\label{eq:dual_feasibility}
-			\end{equation}
-			\begin{equation}
-				\mu_s^\star (t_{s-1}^\star - t_s^\star) = 0.
-				\label{eq:complementary_slackness}
-			\end{equation}
-
-		\end{subequations}
-		Due to the strict inequality constraint \eqref{co:strict_inequality}, conditions \eqref{eq:dual_feasibility} and \eqref{eq:complementary_slackness} together imply $\mu_s^\star = 0$, $\forall s \in \mathcal{S}$.
-		Besides, it is trivial to conclude $t_0^\star = 0$ for energy-based detection.
-		As such, the necessary optimality conditions for problem \eqref{op:decision_threshold}, $\forall s \in \mathcal{S}$,
-		\begin{equation}
-			\nabla_{t_{s}^\star} I^\star_{\mathrm{B}}(x;\hat{x}) = 0,
-		\end{equation}
-		which can be explicitly written as, $\forall s \equiv l' \pmod L$,
-		\begin{equation}
-			\sum_l P(x_l) \frac{(t_s^\star)^{N-1} \exp{-t_s^\star/\sigma_l^2}}{\sigma_l^{2N} (N-1)!} \log \frac{P(x_l|\hat{x}_{l'+1})}{P(x_l|\hat{x}_{l'})} = 0,
-			\label{eq:kkt_threshold_explicit}
-		\end{equation}
-
-		According to \cite{He2021}, the optimal backward channel quantizer is convex and separates each pair of posterior distribution by a hyperplane.
-		It implies, for a given output letter $l'$, the sequence $\{\log {P(x_l|\hat{x}_{l'+1})}/{P(x_l|\hat{x}_{l'})}\}_{l \in \mathcal{L}}$ changes sign exactly once.
-		We notice the left-hand side of \eqref{eq:kkt_threshold_explicit} is a generalized Dirichlet polynomial, and by Descartes' rule of signs \cite{Jameson2006}, has at most one positive solution.
-		% TODO
-		In other words, starting from $t_0^\star$, each optimal decision region requires at most one additional distinct threshold, and we have $S \le L$.
-		Therefore, we conclude $S = L$ and the proof is completed.
-		\qedsymbol
-		\label{ap:threshold}
-	\end{subsection}
+	% \begin{subsection}{Proof of Proposition \ref{pr:threshold}}
+	% 	Since $L$ input letters are with non-zero probability and $x \to z \to \hat{x}$ formulates a Markov chain, we need $L$ non-empty decision regions and at least $L+1$ distinct thresholds (including \num{0} and $\infty$) to minimize the distortion between source and decision.
+	% 	On the other hand, the optimal decision regions are apparently empty for those unused letters.
+
+	% 	Suppose the optimal number of thresholds is $S+1$ where $S \ge L$.
+	% 	Let $\boldsymbol{t} \triangleq [t_0,\ldots,t_S]^T \in \mathbb{R}_{+}^{(S+1) \times 1}$ be the optimal threshold vector where $t_{s-1} < t_s$, $\forall s \in \mathcal{S} \triangleq \{1,\ldots,S\}$.
+	% 	Since the optimal decision region for any letter may consist of multiple partitions, without loss of generality, we assume the mapping from threshold vector to decision region $l' \in \mathcal{L} \triangleq \{1,\ldots,L\}$ is given by $\mathcal{R}_{l'} = \bigcup_{s \equiv l' \pmod L} [t_{s-1},t_s)$.
+	% 	\begin{footnote}
+	% 		The proof holds for any valid mapping from threshold vector to decision regions, and we consider this specific case for the ease of presentation.
+	% 	\end{footnote}
+	% 	The threshold optimization problem is
+	% 	\begin{maxi!}
+	% 		{\scriptstyle{\boldsymbol{t}}}{I_{\mathrm{B}}(x;\hat{x})}{\label{op:decision_threshold}}{\label{ob:backscatter_mutual_information}}
+	% 		\addConstraint{t_{s-1}}{< t_s,}{\quad \forall s \in \mathcal{S}.}{\label{co:strict_inequality}}
+	% 	\end{maxi!}
+
+	% 	Problem \eqref{op:decision_threshold} is intricate due to the strict inequality constraint \eqref{co:strict_inequality}.
+	% 	Following \cite{Nguyen2020}, we first relax it to the convex counterpart, then discard the solutions that violate any original constraint.
+	% 	The Lagrangian function for the relaxed problem is
+	% 	\begin{equation}
+	% 		L = - I_{\mathrm{B}}(x;\hat{x}) + \sum_{s \in \mathcal{S}} \mu_s (t_{s-1} - t_s),
+	% 	\end{equation}
+	% 	where $\mu_s$ is the Lagrange multiplier associated with the non-strict version of \eqref{co:strict_inequality}.
+	% 	The \gls{kkt} conditions on the optimal primal and dual solutions are, $\forall s \in \mathcal{S}$,
+	% 	\begin{subequations}
+	% 		\label{eq:kkt_thresholding}
+	% 		\begin{equation}
+	% 			- \nabla_{t_s^\star} I^\star_{\mathrm{B}}(x;\hat{x}) + \mu_{s-1}^\star - \mu_s^\star = 0,
+	% 			\label{eq:stationarity}
+	% 		\end{equation}
+	% 		\begin{equation}
+	% 			\mu_s^\star \ge 0,
+	% 			\label{eq:dual_feasibility}
+	% 		\end{equation}
+	% 		\begin{equation}
+	% 			\mu_s^\star (t_{s-1}^\star - t_s^\star) = 0.
+	% 			\label{eq:complementary_slackness}
+	% 		\end{equation}
+
+	% 	\end{subequations}
+	% 	Due to the strict inequality constraint \eqref{co:strict_inequality}, conditions \eqref{eq:dual_feasibility} and \eqref{eq:complementary_slackness} together imply $\mu_s^\star = 0$, $\forall s \in \mathcal{S}$.
+	% 	Besides, it is trivial to conclude $t_0^\star = 0$ for energy-based detection.
+	% 	As such, the necessary optimality conditions for problem \eqref{op:decision_threshold}, $\forall s \in \mathcal{S}$,
+	% 	\begin{equation}
+	% 		\nabla_{t_{s}^\star} I^\star_{\mathrm{B}}(x;\hat{x}) = 0,
+	% 	\end{equation}
+	% 	which can be explicitly written as, $\forall s \equiv l' \pmod L$,
+	% 	\begin{equation}
+	% 		\sum_l P(x_l) \frac{(t_s^\star)^{N-1} \exp{-t_s^\star/\sigma_l^2}}{\sigma_l^{2N} (N-1)!} \log \frac{P(x_l|\hat{x}_{l'+1})}{P(x_l|\hat{x}_{l'})} = 0,
+	% 		\label{eq:kkt_threshold_explicit}
+	% 	\end{equation}
+
+	% 	According to \cite{He2021}, the optimal backward channel quantizer is convex and separates each pair of posterior distribution by a hyperplane.
+	% 	It implies, for a given output letter $l'$, the sequence $\{\log {P(x_l|\hat{x}_{l'+1})}/{P(x_l|\hat{x}_{l'})}\}_{l \in \mathcal{L}}$ changes sign exactly once.
+	% 	We notice the left-hand side of \eqref{eq:kkt_threshold_explicit} is a generalized Dirichlet polynomial, and by Descartes' rule of signs \cite{Jameson2006}, has at most one positive solution.
+	% 	% TODO
+	% 	In other words, starting from $t_0^\star$, each optimal decision region requires at most one additional distinct threshold, and we have $S \le L$.
+	% 	Therefore, we conclude $S = L$ and the proof is completed.
+	% 	\qedsymbol
+	% 	\label{ap:threshold}
+	% \end{subsection}
 \end{appendix}

### 2022-07-22 assets/simulation/distribution_weights_1.tex
:bento: Update input distribution vs weights

% This file was created by matlab2tikz.
%
%The latest updates can be retrieved from
%  http://www.mathworks.com/matlabcentral/fileexchange/22022-matlab2tikz-matlab2tikz
%where you can also make suggestions and rate matlab2tikz.
%
\definecolor{mycolor1}{rgb}{0.00000,0.44706,0.74118}%
\definecolor{mycolor2}{rgb}{0.85098,0.32549,0.09804}%
\definecolor{mycolor3}{rgb}{0.92941,0.69412,0.12549}%
\definecolor{mycolor4}{rgb}{0.49412,0.18431,0.55686}%
\definecolor{mycolor5}{rgb}{0.46667,0.67451,0.18824}%
%
\begin{tikzpicture}

\begin{axis}[%
width=3.907in,
height=3.328in,
at={(0.655in,0.449in)},
scale only axis,
xmin=1,
xmax=4,
xtick={1, 2, 3, 4},
xlabel style={font=\color{white!15!black}},
xlabel={Reflection State},
ymin=0,
ymax=1,
ylabel style={font=\color{white!15!black}},
ylabel={Probability Distribution},
axis background/.style={fill=white},
xmajorgrids,
xminorgrids,
ymajorgrids,
yminorgrids,
legend style={at={(0.03,0.97)}, anchor=north west, legend cell align=left, align=left, draw=white!15!black},
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
]
\addplot [color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}]
  table[row sep=crcr]{%
1	1.34887442178325e-06\\
2	0.401147907621958\\
3	0.346863819336987\\
4	0.251986924166634\\
};
\addlegendentry{$\rho =0$}

\addplot [color=mycolor2, dashed, line width=2.0pt, mark=+, mark options={solid, mycolor2}]
  table[row sep=crcr]{%
1	2.43160039284684e-06\\
2	0.373071655693474\\
3	0.387092084568394\\
4	0.239833828137739\\
};
\addlegendentry{$\rho =0.1$}

\addplot [color=mycolor3, dotted, line width=2.0pt, mark=square, mark options={solid, mycolor3}]
  table[row sep=crcr]{%
1	1.27356787994262e-05\\
2	0.337563209241624\\
3	0.428718130958926\\
4	0.23370592412065\\
};
\addlegendentry{$\rho =0.2$}

\addplot [color=mycolor4, dashdotted, line width=2.0pt, mark=x, mark options={solid, mycolor4}]
  table[row sep=crcr]{%
1	2.82495749022891e-05\\
2	0.293114805811411\\
3	0.479872318504251\\
4	0.226984626109436\\
};
\addlegendentry{$\rho =0.3$}

\addplot [color=mycolor5, line width=2.0pt, mark=triangle, mark options={solid, mycolor5}]
  table[row sep=crcr]{%
1	6.85130791403468e-06\\
2	8.96232761727522e-19\\
3	0.999993126219272\\
4	2.24728139461691e-08\\
};
\addlegendentry{$\rho =1$}

\end{axis}
\end{tikzpicture}%

### 2022-07-22 assets/simulation/distribution_weights_2.tex
:bento: Update input distribution vs weights

% This file was created by matlab2tikz.
%
%The latest updates can be retrieved from
%  http://www.mathworks.com/matlabcentral/fileexchange/22022-matlab2tikz-matlab2tikz
%where you can also make suggestions and rate matlab2tikz.
%
\definecolor{mycolor1}{rgb}{0.00000,0.44706,0.74118}%
\definecolor{mycolor2}{rgb}{0.85098,0.32549,0.09804}%
\definecolor{mycolor3}{rgb}{0.92941,0.69412,0.12549}%
\definecolor{mycolor4}{rgb}{0.49412,0.18431,0.55686}%
\definecolor{mycolor5}{rgb}{0.46667,0.67451,0.18824}%
%
\begin{tikzpicture}

\begin{axis}[%
width=4.036in,
height=3.396in,
at={(0.677in,0.458in)},
scale only axis,
xmin=1,
xmax=4,
xtick={1, 2, 3, 4},
xlabel style={font=\color{white!15!black}},
xlabel={Reflection State},
ymin=0,
ymax=1,
ytick={  0, 0.2, 0.4, 0.6, 0.8,   1},
ylabel style={font=\color{white!15!black}},
ylabel={Probability Distribution},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
legend style={legend cell align=left, align=left, draw=white!15!black},
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
]
\addplot [color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}]
  table[row sep=crcr]{%
1	5.30918114897011e-06\\
2	0.495119330815363\\
3	0.504872212458398\\
4	3.14754509004444e-06\\
};
\addlegendentry{$\rho =0$}

\addplot [color=mycolor2, dashed, line width=2.0pt, mark=+, mark options={solid, mycolor2}]
  table[row sep=crcr]{%
1	0.000625294168530938\\
2	0.592532362641568\\
3	0.406462931553826\\
4	0.000379411636074663\\
};
\addlegendentry{$\rho =0.1$}

\addplot [color=mycolor3, dotted, line width=2.0pt, mark=square, mark options={solid, mycolor3}]
  table[row sep=crcr]{%
1	0.00174982996918003\\
2	0.712164660502759\\
3	0.285208184690991\\
4	0.000877324837069957\\
};
\addlegendentry{$\rho =0.2$}

\addplot [color=mycolor4, dashdotted, line width=2.0pt, mark=x, mark options={solid, mycolor4}]
  table[row sep=crcr]{%
1	0.00211591879370998\\
2	0.875434320607714\\
3	0.12182468579724\\
4	0.000625074801335842\\
};
\addlegendentry{$\rho =0.3$}

\addplot [color=mycolor5, line width=2.0pt, mark=triangle, mark options={solid, mycolor5}]
  table[row sep=crcr]{%
1	0.0027167350471736\\
2	0.997283261010619\\
3	7.79158804448565e-12\\
4	3.93441517079322e-09\\
};
\addlegendentry{$\rho =1$}

\end{axis}
\end{tikzpicture}%

### 2022-07-22 main.tex
:pencil: Add simulation parameters

@@
 
-\begin{section}{Input Distribution, Active Beamforming, and Decision Threshold, Design}
+\begin{section}{Input Distribution, Active Beamforming, and Decision Threshold Design}
 	To characterize the achievable primary-(total-)backscatter rate region of the proposed Metascatter-enabled network, we aim to maximize the weighted sum mutual information with respect to node input distributions $\{\boldsymbol{p}_k\}_{k \in \mathcal{K}}$, active beamforming vector $\boldsymbol{w}$, and decision threshold vector $\boldsymbol{t}$ as
@@
 \begin{section}{Simulation Results}
-	In this section, we provide numerical results to evaluate the proposed input distribution, active beamforming and decision threshold designs over the Metascatter-enabled network in Fig.
-\ref{fi:metascatter_network}.
-	The parameters remain fixed unless specified.
-
+	In this section, we provide numerical results to evaluate the proposed input, beamforming and decision design over a single-user multi-node Metascatter-enabled network.
+	We assume the distance between \gls{ap} and user is \SI{10}{\meter}, and $K=2$ Metascatters are uniformly dropped within a disk of radius \SI{1}{\meter} centered at the user.
+	% The carrier frequency is $f=\SI{200}{\MHz}$, and we consider \gls{iid} Ricean fading for all channels.
+	The carrier frequency is $f=\SI{200}{\MHz}$, and we consider \gls{iid} Ricean fading between all terminals.
+	For direct, forward and backward links, the path loss exponents are \num{2.6}, \num{2.4} and \num{2}, while the Ricean factor are \num{5}, \num{5} and \num{10}, respectively.
+	% For direct, forward and backward links, we choose path loss exponents \num{2.6}, \num{2.4} and \num{2}, and Ricean factor \num{5}, \num{5} and \num{10}, respectively.
+	% and the path loss exponents for direct, forward and backward links are \num{2.6}, \num{2.4} and \num{2}, respectively.
+	% We consider \gls{iid} Ricean fading for all channels with Ricean factor set to \num{5}, \num{5} and \num{10}
+	The \gls{ap} has $Q=4$ antennas with maximum average transmit power $P=\SI{36}{\dBm}$.
+	All node perform \gls{qam} with $M=2$ input states, the amplitude reflect ratio is $\alpha=0.5$, and the symbol period ratio is $N=20$.
+	% and we consider amplitude reflect ratio $\alpha=0.5$ and symbol period ratio $N=20$.
+	% The user has a receive antenna gain of \SI{3}{\dBi} and average noise power
+	The user is with average noise power $\sigma_v^2=\SI{70}{\dBm}$ and receive antenna gain \SI{3}{\dBi}.
+	All rate regions are averaged over \num{1000} instances.
+	% Each node has $M=2$ candidate input states with amplitude reflect ratio $\alpha=0.5$.
+	The parameters remain fixed unless otherwise specified.
+
+	\begin{figure}[!t]
+		\centering
+		\subfloat[Instance 1]{
+			\resizebox{0.48\columnwidth}{!}{
+				\input{assets/simulation/distribution_weights_1.tex}
+			}
+		}
+		\subfloat[Instance 2]{
+			\resizebox{0.48\columnwidth}{!}{
+				\input{assets/simulation/distribution_weights_2.tex}
+			}
+		}
+		\caption{Input distribution vs weight $\rho$.}
+	\end{figure}
+
+	% \begin{figure}[!t]
+	% 	\centering
+	% 	\resizebox{0.8\columnwidth}{!}{
+	% 		\input{assets/simulation/distribution_weights.tex}
+	% 	}
+	% 	\caption{1}
+	% 	% \caption{Average primary-(total-)backscatter rate region.}
+	% \end{figure}
 	% \begin{table}[t!]

### 2022-07-23 main.tex
:pencil: Add simulation results

@@
 \newacronym{bpsphz}{\si{bps/Hz}}{bits per second per Hertz}
+\newacronym{cp}{CP}{Canonical Polyadic}
 \newacronym{cr}{CR}{Cognitive Radio}
@@
 \begin{section}{Simulation Results}
+	% TODO add distribution to initializer to smooth curves?
+	% TODO compare PGD and primary-MRT beamformers
 	In this section, we provide numerical results to evaluate the proposed input, beamforming and decision design over a single-user multi-node Metascatter-enabled network.
-	We assume the distance between \gls{ap} and user is \SI{10}{\meter}, and $K=2$ Metascatters are uniformly dropped within a disk of radius \SI{1}{\meter} centered at the user.
+	We assume the distance between \gls{ap} and user is \SI{10}{\meter}, and $K=2$ Metascatters are uniformly dropped within a disk centered at the user of radius \SI{1}{\meter}.
 	% The carrier frequency is $f=\SI{200}{\MHz}$, and we consider \gls{iid} Ricean fading for all channels.
 	The carrier frequency is $f=\SI{200}{\MHz}$, and we consider \gls{iid} Ricean fading between all terminals.
-	For direct, forward and backward links, the path loss exponents are \num{2.6}, \num{2.4} and \num{2}, while the Ricean factor are \num{5}, \num{5} and \num{10}, respectively.
+	For direct, forward and backward links, we set the path loss exponents to \num{2.6}, \num{2.4} and \num{2}, and the Ricean factor to \num{5}, \num{5} and \num{10}, respectively.
 	% For direct, forward and backward links, we choose path loss exponents \num{2.6}, \num{2.4} and \num{2}, and Ricean factor \num{5}, \num{5} and \num{10}, respectively.
@@
 	The \gls{ap} has $Q=4$ antennas with maximum average transmit power $P=\SI{36}{\dBm}$.
-	All node perform \gls{qam} with $M=2$ input states, the amplitude reflect ratio is $\alpha=0.5$, and the symbol period ratio is $N=20$.
+	All nodes have amplitude reflect ratio $\alpha=0.5$, symbol period ratio $N=20$, and perform \gls{qam} with $M=2$ input states.
 	% and we consider amplitude reflect ratio $\alpha=0.5$ and symbol period ratio $N=20$.
@@
 	The user is with average noise power $\sigma_v^2=\SI{70}{\dBm}$ and receive antenna gain \SI{3}{\dBi}.
-	All rate regions are averaged over \num{1000} instances.
-	% Each node has $M=2$ candidate input states with amplitude reflect ratio $\alpha=0.5$.
+	All rate regions are averaged over at least \num{1000} instances, where ``PSP'' and ``BSP'' means primary and backscatter symbol periods, respectively.
+	We choose decision design by \gls{smawk} \cite{He2021} as reference, and select discretize boundaries uniformly over the \qty{95}{\percent} confidence region of edge hypotheses.
 	The parameters remain fixed unless otherwise specified.
 
+	\begin{subsection}{Input Distribution vs. Weight}
 		\begin{figure}[!t]
 			\centering
-		\subfloat[Instance 1]{
+			\subfloat[Instance 1\label{fi:distribution_weights_1}]{
 				\resizebox{0.48\columnwidth}{!}{
@@
 			}
-		\subfloat[Instance 2]{
+			\subfloat[Instance 2\label{fi:distribution_weights_2}]{
 				\resizebox{0.48\columnwidth}{!}{
@@
 			}
-		\caption{Input distribution vs weight $\rho$.}
+			\caption{Typical input distributions vs. weight $\rho$ for a Metascatter with $M=4$ inputs.}
+			\label{fi:distribution_weights}
 		\end{figure}
-
+		% We consider a single Metascatter with $M=4$ inputs in this case of study.
+		In Fig. \ref{fi:distribution_weights}, we present typical input distributions of a single Metascatter with $M=4$ inputs under different weight $\rho$.
+		Fig. \subref*{fi:distribution_weights_1} and \subref*{fi:distribution_weights_2} are obtained from \gls{iid} drop and channel realizations.
+		We note that even for $\rho=0$ (i.e., best backscatter performance), the optimal input distribution is not equiprobable like \gls{sr}, and adaptive channel coding can further increase total backscatter rate based on \gls{csi}.
+		On the other hand, the optimal input distribution becomes fully deterministic at $\rho=1$ (i.e., best primary performance), where the state maximizes equivalent primary channel \eqref{eq:equivalent_channel} strength is chosen with probability \num{1}.
+		In this case, Metascatter boils down to an \gls{irs} element with $M$ discrete states.
+		As $\rho$ moves from \num{0} to \num{1}, the optimal input distribution becomes gradually biased to one state and flexibly balances the primary-backscatter tradeoff.
+	\end{subsection}
+
+	\begin{subsection}{Rate Region vs. Input, Beamforming, and Decision Schemes}
+		\begin{figure}[!t]
+			\centering
+			\subfloat[Input Distribution\label{fi:region_distribution}]{
+				\resizebox{0.48\columnwidth}{!}{
+					\input{assets/simulation/region_distribution.tex}
+				}
+			}
+			\subfloat[Decision Threshold\label{fi:region_threshold}]{
+				\resizebox{0.48\columnwidth}{!}{
+					\input{assets/simulation/region_threshold.tex}
+				}
+			}
+			\caption{Average primary-(total-)backscatter rate regions for different input distribution and decision threshold schemes.}
+		\end{figure}
+		Fig. \subref*{fi:region_distribution} compares the achievable rate regions by following input designs.
+		\begin{itemize}
+			% \item ``Exhaustion'' means $K$-dimensional grid search over probability simplex;
+			% \item ``\gls{kkt}'' corresponds to Algorithm \ref{al:input_distribution};
+			% \item ``Cooperation'' assumes backscatter cooperation/joint encoding at all Metascatters, and employs Blahut-Arimoto algorithm \cite{Arimoto1972,Blahut1972a} to determine \emph{tuple} input distribution;
+			\item \textbf{Exhaustion:} $K$-dimensional grid search over probability simplex;
+			\item \textbf{\gls{kkt}:} results of Algorithm \ref{al:input_distribution};
+					% \item \textbf{Cooperation:} with backscatter cooperation/joint encoding at all Metascatters, Blahut-Arimoto algorithm \cite{Arimoto1972,Blahut1972a} for \emph{tuple} input distribution;
+					% \item \textbf{Cooperation:} backscatter cooperation/joint encoding at all Metascatters, \emph{tuple input distribution} by Blahut-Arimoto algorithm \cite{Arimoto1972,Blahut1972a};
+					% \item \textbf{Cooperation:} with backscatter cooperation (i.e., joint encoding) at all Metascatters, \emph{tuple input distribution} by Blahut-Arimoto algorithm \cite{Arimoto1972,Blahut1972a};
+			\item \textbf{Cooperation:} backscatter cooperation/joint encoding at all Metascatters, tuple input distribution/joint probability array optimization by Blahut-Arimoto algorithm \cite{Arimoto1972,Blahut1972a};
+					% with backscatter cooperation (i.e., joint encoding) at all Metascatters, \emph{tuple input distribution} by Blahut-Arimoto algorithm \cite{Arimoto1972,Blahut1972a};
+			\item \textbf{Marginalization:} marginal distributions of joint probability array;
+			\item \textbf{Decomposition:} normalized tensors of rank-1 \gls{cp} decomposition of joint probability array;
+			\item \textbf{Randomization:} Gaussian recovery from joint probability array \cite{Calvo2010}.
+		\end{itemize}
+
+		We notice adaptive joint encoding at all Metascatters provides the outer bound of rate region.
+		However, it involves arbitrarily dependent codewords, and backscatter cooperation between passive nodes is generally unaffordable.
+		In contrast, the rate region of \gls{kkt} input design in Algorithm \ref{al:input_distribution} approaches that of exhaustive search, and the loss is negligible for $K=2$.
+		% Although the randomization method \cite{Calvo2010} achieves similar performance, the computational complexity is much higher as it involves solving $K+1$ linear programming problems
+		Although the randomization method \cite{Calvo2010} returns similar rate region, it requires solving $K+1$ linear programming problems before applying Gaussian recovery.
+		The marginal distribution is slightly worse than \gls{kkt} despite having the same computational complexity, while the approximation from \gls{cp} decomposition is unsatisfying.
+
+		% TODO: beamforming
+
+		Fig. \subref*{fi:region_threshold} compares the achievable rate region by following threshold schemes.
+		\begin{itemize}
+			\item \textbf{\gls{dp}:} sequential quantizer grouping by dynamic programming \cite{He2021};
+			\item \textbf{\gls{smawk}:} above accelerated by \gls{smawk} algorithm;
+			\item \textbf{Bisection:} sequential bisection threshold design \cite{Nguyen2020a};
+			\item \textbf{\gls{ml}:} maximum likelihood decision \eqref{eq:detection_threshold_maximum_likelihood} \cite{Qian2019}.
+		\end{itemize}
+
+		We observe that input-adaptive threshold designs achieve higher total backscatter rate than \gls{ml}.
+		This is because the decision regions can be flexibly adjusted to enhance the capacity of \gls{dtmac} \eqref{eq:dtmac}.
+		For example, the tuples with negligible input probability should have narrower decision regions than those frequently employed, in order to improve detection performance.
+		It emphasizes the importance of joint input distribution and decision region design.
+
+		% We note that ideal joint adaptive encoding at all Metascatters can further boost the total backscatter rate.
+		% However, this ideal upper bound requires real-time feedback
+		% ``Exhaustion'' means $K$-dimensional grid search over probability simplex, ``KKT'' corresponds to Algorithm \ref{ap:input_kkt_solution}, ``Cooperation'' assumes full backscatter cooperation and joint encoding at all Metascatters
+	\end{subsection}
+
+	\begin{subsection}{Rate Region vs. System Configuration}
+		\begin{figure}[!t]
+			\centering
+			\subfloat[Metscatter Nodes\label{fi:region_tags}]{
+				\resizebox{0.48\columnwidth}{!}{
+					\input{assets/simulation/region_tags.tex}
+				}
+			}
+			\subfloat[Input States\label{fi:region_states}]{
+				\resizebox{0.48\columnwidth}{!}{
+					\input{assets/simulation/region_states.tex}
+				}
+			}
+			\\
+			\subfloat[Transmit Antennas\label{fi:region_txs}]{
+				\resizebox{0.48\columnwidth}{!}{
+					\input{assets/simulation/region_txs.tex}
+				}
+			}
+			\subfloat[Scatter Ratio\label{fi:region_scatter}]{
+				\resizebox{0.48\columnwidth}{!}{
+					\input{assets/simulation/region_scatter.tex}
+				}
+			}
+			\caption{Average primary-(total-)backscatter rate regions.}
+			\label{fi:region_config_1}
+		\end{figure}
+
+		% Fig. \ref{fi:region_config_1} reveals the impact of Metascatter nodes, input states, transmit antennas and scatter ratio on the achievable rate region.
+		We present in \ref{fi:region_config_1} the impact of Metascatter nodes, input states, transmit antennas and scatter ratio on the achievable rate region.
+		For the specified scenario, Fig.
+\subref*{fi:region_tags} shows the total backscatter rate almost scales proportionally with the number of Metascatter nodes, and the decrease of individual backscatter rate is unobvious.
+		Besides, we conclude from \subref*{fi:region_states} that increasing the reflection states has a marginal effect on both primary and backscatter rates.
+		Those two facts motivates the use of numerous elementary/uncomplicated backscatter nodes, instead of high-order transponders or programmable high-resolution surfaces.
+		Figs. \subref*{fi:region_txs} and \subref*{fi:region_scatter} also prove increasing transmit antennas or scatter ratio can improve both primary and backscatter performance.
+
+		\begin{figure}[!t]
+			\centering
+			\subfloat[User Coverage\label{fi:region_coverage}]{
+				\resizebox{0.48\columnwidth}{!}{
+					\input{assets/simulation/region_coverage.tex}
+				}
+			}
+			\subfloat[Symbol Period Ratio\label{fi:region_duration}]{
+				\resizebox{0.48\columnwidth}{!}{
+					\input{assets/simulation/region_duration.tex}
+				}
+			}
+			\\
+			\subfloat[Carrier Frequency\label{fi:region_frequency}]{
+				\resizebox{0.48\columnwidth}{!}{
+					\input{assets/simulation/region_frequency.tex}
+				}
+			}
+			\subfloat[Average Noise Power\label{fi:region_noise}]{
+				\resizebox{0.48\columnwidth}{!}{
+					\input{assets/simulation/region_noise.tex}
+				}
+			}
+			\caption{Average primary-(total-)backscatter rate regions.}
+			\label{fi:region_config_2}
+		\end{figure}
+	\end{subsection}
 	% \begin{figure}[!t]

### 2022-07-24 main.tex
:pencil: Add conclusion

@@
 	% A suboptimal \gls{bcd} algorithm was proposed, where the \gls{kkt} input distribution is evaluated in closed form, the active beamforming is optimized by \gls{pgd} with backtracking line search, and the decision thresholds are optimized by \gls{dp}.
-	Simulation results demonstrate Metascatters can exploit additional propagation paths to transmit and assist via input design.
+	Simulation results demonstrate Metascatters can exploit additional propagation paths to transmit and assist via adaptive input design.
 \end{abstract}
@@
 	In this section, we provide numerical results to evaluate the proposed input, beamforming and decision design over a single-user multi-node Metascatter-enabled network.
-	We assume the distance between \gls{ap} and user is \SI{10}{\meter}, and $K=2$ Metascatters are uniformly dropped within a disk centered at the user of radius \SI{1}{\meter}.
-	% The carrier frequency is $f=\SI{200}{\MHz}$, and we consider \gls{iid} Ricean fading for all channels.
-	The carrier frequency is $f=\SI{200}{\MHz}$, and we consider \gls{iid} Ricean fading between all terminals.
+	We assume the distance between \gls{ap} and user is \qty{10}{\meter}, and $K=2$ Metascatters are uniformly dropped within a disk centered at the user of radius \qty{1}{\meter}.
+	% The carrier frequency is $f=\qty{200}{\MHz}$, and we consider \gls{iid} Ricean fading for all channels.
+	The carrier frequency is $f=\qty{200}{\MHz}$, and we consider \gls{iid} Ricean fading between all terminals.
 	For direct, forward and backward links, we set the path loss exponents to \num{2.6}, \num{2.4} and \num{2}, and the Ricean factor to \num{5}, \num{5} and \num{10}, respectively.
@@
 	% We consider \gls{iid} Ricean fading for all channels with Ricean factor set to \num{5}, \num{5} and \num{10}
-	The \gls{ap} has $Q=4$ antennas with maximum average transmit power $P=\SI{36}{\dBm}$.
+	The \gls{ap} has $Q=4$ antennas with maximum average transmit power $P=\qty{36}{\dBm}$.
 	All nodes have amplitude reflect ratio $\alpha=0.5$, symbol period ratio $N=20$, and perform \gls{qam} with $M=2$ input states.
 	% and we consider amplitude reflect ratio $\alpha=0.5$ and symbol period ratio $N=20$.
-	% The user has a receive antenna gain of \SI{3}{\dBi} and average noise power
-	The user is with average noise power $\sigma_v^2=\SI{70}{\dBm}$ and receive antenna gain \SI{3}{\dBi}.
+	% The user has a receive antenna gain of \qty{3}{\dBi} and average noise power
+	The user is with average noise power $\sigma_v^2=\qty{70}{\dBm}$ and receive antenna gain \qty{3}{\dBi}.
 	All rate regions are averaged over at least \num{1000} instances, where ``PSP'' and ``BSP'' means primary and backscatter symbol periods, respectively.
@@
 			\centering
-			\subfloat[User Coverage\label{fi:region_coverage}]{
+			\subfloat[Node Coverage\label{fi:region_coverage}]{
 				\resizebox{0.48\columnwidth}{!}{
@@
 		\end{figure}
+
+		Fig. \subref*{fi:region_coverage} shows the tradeoff between coverage disk radius $r$ and achievable rate region.
+		When nodes are far from the user, both primary and backscatter rates decrease due to the product pass loss of forward and backward channels.
+		Under the assumption of ideal backscatter decoding and re-encoding, Fig.
+\subref*{fi:region_duration} suggests using lower symbol period ratio $N$ can boost total backscatter rate per primary symbol.
+		However, it requires more frequent detection and re-encoding at the user to maintain the primary rate.
+		When $N$ becomes sufficiently large, total backscatter rate approaches \num{0} and Metascatters boil down to conventional \gls{irs} elements with fixed reflection patterns during whole channel block.
+		In Fig. \subref*{fi:region_frequency}, we observe that passive Metascatter achieves higher backscatter rate at lower carrier frequency because of preferable propagation loss.
+		Finally, \subref*{fi:region_noise} prove the performance of energy detection is robust for a wide range of noise power.
 	\end{subsection}
-	% \begin{figure}[!t]
-	% 	\centering
-	% 	\resizebox{0.8\columnwidth}{!}{
-	% 		\input{assets/simulation/distribution_weights.tex}
-	% 	}
-	% 	\caption{1}
-	% 	% \caption{Average primary-(total-)backscatter rate region.}
-	% \end{figure}
-	% \begin{table}[t!]
-	% 	\centering
-	% 	\caption{Parameters in simulation}
-	% 	\begin{tabular}{ll}
-	% 		Transmit antenna $Q$     & 1   \\
-	% 		Tags $K$                 & 2   \\
-	% 		States $M$               & 2   \\
-	% 		Reflect ratio $\alpha$   & 0.5 \\
-	% 		Duration ratio $N$       & 10  \\
-	% 		Noise power $\sigma_v^2$ & 1   \\
-	% 		Discretization bins      & 256
-	% 	\end{tabular}
-	% 	\label{ta:parameters}
-	% \end{table}
-	% Table \ref{ta:parameters} shows the parameters used in simulation.
-	% We assume all links are in standard \gls{cscg} distribution and evaluated the rate regions on two instances.
-	% For the input design, ``Cooperation'' assumes full transmit cooperation at all tags (i.e., joint encoding), ``Exhaustion'' runs exhaustive search on all possible input distributions, ``\gls{kkt}'' is proposed \gls{kkt} input design \eqref{eq:input_kkt_solution}, and ``Marginalization'' marginalizes the joint input array by ``Cooperation'' to obtain independent tag input distribution.
-	% For the threshold design, ``\gls{smawk}'' refers to the \gls{dp}-based quantization proposed in \cite{He2021}, ``Bisection'' sequentially optimizes each threshold by bisection \cite{Nguyen2020a}, and ``\gls{ml}'' is the \gls{ml} detector that requires no knowledge of input distribution.
-
-	% Figs. \ref{fi:rate_region_1} and \ref{fi:rate_region_2} show two typical scenarios where joint encoding can be helpful and unnecessary, respectively.
-	% Although the proposed \gls{kkt} input design converges to the optimal solutions in both examples, it may be trapped at saddle points under poor initialization, especially when the number of tags increases.
-
-	% We believed threshold design has no impact on the primary achievable rate, because primary decoding acts on $\boldsymbol{y}$ while thresholding acts on $z$.
-	% As such, the threshold that maximizes the total backscatter rate should also maximize the weighted sum rate.
-	% Interestingly, this may not be the case because the \gls{smawk} and Bisection threshold designs, both maximizing the total backscatter rate, can be outperformed by the \gls{ml} when it comes to weighted sum primary-(total-)backscatter rate.
-	% It may result from a precision issue, but inspires further research on threshold design for Metascatter.
-
-	% \begin{figure}[!t]
-	% 	\centering
-	% 	\resizebox{\columnwidth}{!}{
-	% 		\includegraphics{assets/illustration/rate_region_1.eps}
-	% 	}
-	% 	\caption{Achievable rate regions by input-threshold design: Case I.}
-	% 	\label{fi:rate_region_1}
-	% \end{figure}
-
-	% \begin{figure}[!t]
-	% 	\centering
-	% 	\resizebox{\columnwidth}{!}{
-	% 		\includegraphics{assets/illustration/rate_region_2.eps}
-	% 	}
-	% 	\caption{Achievable rate regions by input-threshold design: Case II.}
-	% 	\label{fi:rate_region_2}
-	% \end{figure}
-	% The parameters remain fixed unless specified.
+\end{section}
+
+\begin{section}{Conclusion}
+	This paper introduced Metascatter that adapts input distribution of passive backscatter nodes to simultaneously transmit and assist over existing wireless systems.
+	Starting from backscatter principles, we showed how Metascatters bridges and generalizes parasitic source of \gls{sr} and reflecting element of \gls{irs} via smart input design.
+	An application scenario was considered where multiple Metascatters ride over a point-to-point transmission to simultaneously encode self message and perform passive beamforming.
+	To characterize achievable primary-backscatter rate region, we proposed a \gls{bcd} algorithm that evaluates \gls{kkt} input distribution in closed form, optimizes active beamforming by \gls{pgd}, and refines decision regions by existing methods.
+	Numerical results demonstrated the advantage of adaptive node input distribution design for both primary and backscatter subsystems.
+
+	One particular interesting question is how to design Metascatters in a multi-user system.
+	If one node can contribute to and be decoded by multiple users, its input distribution may be further adjusted to mimic multi-beam gain of dynamic beamforming \cite{Qiu2022}.
 \end{section}

### 2022-07-30 main.tex
:pencil: Update BTLS
:construction: Add instructions

@@
 \newacronym{iid}{i.i.d.}{independent and identically distributed}
-\newacronym{irs}{IRS}{Intelligent Reflecting Surface}
 \newacronym{kkt}{KKT}{Karush–Kuhn–Tucker}
@@
 \newacronym{rf}{RF}{Radio-Frequency}
+\newacronym{ris}{RIS}{Reconfigurable Intelligent Surface}
 \newacronym{sc}{SC}{Superposition Coding}
@@
 \begin{document}
-\title{Metascatter: Unifying Symbiotic Radio and Intelligent Reflecting Surface}
+% \title{UniScatter: Unifying Backscatter Communication, Reconfigurable Intelligent Surface, and Symbiotic Radio}
+\title{UniScatter: Unifying Symbiotic Radio and Reconfigurable Intelligent Surface}
 \author{
@@
 	% Backscatter allows wireless nodes to harvest energy from, modulate information over, and reconfigure propagation of surrounding radio waves.
-	Backscatter nodes can harvest energy from, modulate information over, and reconfigure propagation of ambient signals.
+	% Backscatter nodes can harvest energy from, modulate information over, and reconfigure propagation of ambient signals.
 	% Backscatter nodes can harvest energy from, modulate information over, and reconfigure propagation of surrounding radio waves.
+	% Scattering/reflection elements to
+	% An RIS is a thin surface composed of N elements, each being a reconfigurable scatterer: a small antenna that receives and re-radiates without amplification, but with a configurable time delay [3].
+For narrowband signals, this delay corresponds to a phase shift.
+
+	Scatterers can harvest energy from, modulate information over, and reconfigure propagation of ambient radio waves.
+	In backscatter communication,
+	% ! Φ(c[n]) vs P
+
+	% TODO
+	back comms, symbiotic radio and RIS have appeared as three different and somewhat unrelated wireless technologies, explaining the key feature of each of them.
+Then I would say we introduce metascatter as a new paradigm that unifies and generalizes those three ...., explain the key feature of metascatter.
+
 	We uniquely introduce \emph{Metascatter} that adapts the input distribution of a finite-state passive backscatter node based on \gls{csi}, to \emph{simultaneously} encode self message and assist legacy transmission while powered by surrounding waves.
-	% Compared to conventional \gls{irs}-empowered \gls{sr} that encodes and precodes independently (e.g., overlay or parallel), Metascatter refines backscatter principles to bridge parasitic source of \gls{sr} and reflecting element of \gls{irs} as extreme cases.
-	Compared to existing \gls{irs}-empowered \gls{sr} that encodes and precodes independently using advanced architecture (e.g., overlay or parallel), Metascatter softly bridges and generalizes parasitic source of \gls{sr} and reflecting element of \gls{irs} via smart input design.
-	% Compared to \gls{irs}-empowered \gls{sr} that encodes and precodes independently (e.g., overlay or parallel), Metascatter refines backscatter principles to bridge parasitic source of \gls{sr} and reflecting element of \gls{irs} as extreme cases.
+	% Compared to conventional \gls{ris}-empowered \gls{sr} that encodes and precodes independently (e.g., overlay or parallel), Metascatter refines backscatter principles to bridge parasitic source of \gls{sr} and reflecting element of \gls{ris} as extreme cases.
+	Compared to existing \gls{ris}-empowered \gls{sr} that encodes and precodes independently using advanced architecture (e.g., overlay or parallel), Metascatter softly bridges and generalizes parasitic source of \gls{sr} and reflecting element of \gls{ris} via smart input design.
+	% Compared to \gls{ris}-empowered \gls{sr} that encodes and precodes independently (e.g., overlay or parallel), Metascatter refines backscatter principles to bridge parasitic source of \gls{sr} and reflecting element of \gls{ris} as extreme cases.
 	% Such an integrated distribution design not only yields universal modularity with reduced optimization cost, but also enables a flexible tradeoff between primary and backscatter links using shared spectrum, energy, and infrastructures.
@@
 
-	% On the other hand, \gls{irs} has recently emerged as a promising technique to enhance the energy efficiency.
-	% In practice, an \gls{irs} consists of multiple individual sub-wavelength reflecting elements to adjust the amplitude and phase of the incoming signal (i.e., passive beamforming).
-	% Different from relay, backscatter and frequency-selective surface \cite{Anwar2018}, \gls{irs} assists the primary transmission using passive components with much lower energy consumption and thermal noise, but is limited to frequency-dependent reflection.
-	% On the other hand, \gls{irs} consists of numerous sub-wavelength passive elements that alter propagation environment using adaptive backscatter pattern to assist existing networks.
+	% On the other hand, \gls{ris} has recently emerged as a promising technique to enhance the energy efficiency.
+	% In practice, an \gls{ris} consists of multiple individual sub-wavelength reflecting elements to adjust the amplitude and phase of the incoming signal (i.e., passive beamforming).
+	% Different from relay, backscatter and frequency-selective surface \cite{Anwar2018}, \gls{ris} assists the primary transmission using passive components with much lower energy consumption and thermal noise, but is limited to frequency-dependent reflection.
+	% On the other hand, \gls{ris} consists of numerous sub-wavelength passive elements that alter propagation environment using adaptive backscatter pattern to assist existing networks.
 Extensive research has been devoted to optimizing the reflection coefficient
-	% On the other hand, \gls{irs} consists of numerous sub-wavelength passive elements with adaptive amplitudes and/or phases that alter propagation environment to assist existing networks.
-	On the other hand, \gls{irs} alters propagation environment for legacy networks using numerous sub-wavelength passive elements with adaptive amplitudes and/or phases.
+	% On the other hand, \gls{ris} consists of numerous sub-wavelength passive elements with adaptive amplitudes and/or phases that alter propagation environment to assist existing networks.
+	On the other hand, \gls{ris} alters propagation environment for legacy networks using numerous sub-wavelength passive elements with adaptive amplitudes and/or phases.
 	Extensive research has been devoted to optimizing the phase shifts for the whole channel block to improve communication, sensing, and power performances \cite{Wu2018,Zhang2019a,Lin2022,Liu2022,Feng2022,Zhao2022}.
-	% In contrast, dynamic passive beamforming that adjusts \gls{irs} within channel block was proposed in \cite{Yang2020} to create diversity for \gls{ofdm} systems.
-	% In contrast, dynamic passive beamforming that adjusts \gls{irs} over finer time slots was proposed in \cite{Yang2020} to create diversity for \gls{ofdm} systems.
-	Besides, \cite{Yang2020} proposed a dynamic passive beamforming that further adjusts \gls{irs} over fine-grained time slots for \gls{ofdm} systems to balance beamforming gain and multiuser diversity.
+	% In contrast, dynamic passive beamforming that adjusts \gls{ris} within channel block was proposed in \cite{Yang2020} to create diversity for \gls{ofdm} systems.
+	% In contrast, dynamic passive beamforming that adjusts \gls{ris} over finer time slots was proposed in \cite{Yang2020} to create diversity for \gls{ofdm} systems.
+	Besides, \cite{Yang2020} proposed a dynamic passive beamforming that further adjusts \gls{ris} over fine-grained time slots for \gls{ofdm} systems to balance beamforming gain and multiuser diversity.
 	The idea was further applied to \gls{wpcn} to accommodate the downlink \gls{wpt} phase and uplink \gls{wit} phase of the ``harvest-then-transmit'' protocol \cite{Wu2021d,Hua2022a}.
-	% For multiuser \gls{wpt}, \cite{Qiu2022} also reported that despite \gls{irs} is restricted to single-beam reflection, dynamic beamforming can mimic multi-beam reflection in a time-division manner and reduce the phase extraction loss.
+	% For multiuser \gls{wpt}, \cite{Qiu2022} also reported that despite \gls{ris} is restricted to single-beam reflection, dynamic beamforming can mimic multi-beam reflection in a time-division manner and reduce the phase extraction loss.
 	For multiuser \gls{wpt}, \cite{Qiu2022} also reported that dynamic beamforming can mimic multi-beam reflection in a time-division manner and reduce the phase extraction loss.
-	% However, dynamic passive beamforming demands additional computational complexity and control overhead, and the performance-cost tradeoff needs reconsideration especially when the number of \gls{irs} elements is large.
+	% However, dynamic passive beamforming demands additional computational complexity and control overhead, and the performance-cost tradeoff needs reconsideration especially when the number of \gls{ris} elements is large.
 	% Although dynamic passive beamforming can artificially create time-varying channels for flexible channel reconfiguration and resource allocation, it demands additional computational complexity and control overhead, and the performance-cost tradeoff deserves further attention.
 	% Although dynamic passive beamforming can artificially introduce temporal diversity for flexible channel reconfiguration and resource allocation, it demands additional computational complexity and control overhead, and the performance-cost tradeoff deserves further attention.
-	Although dynamic passive beamforming artificially creates temporal diversity for flexible channel reconfiguration and resource allocation, it demands additional computational cost and control overhead, and the tradeoff deserves further attention especially for large \gls{irs}.
-	In \cite{Chen2021,Zhang2021d}, \gls{irs} was also introduced to single- and multi-node \gls{sr} systems to reduce the total transmit power.
-	When joint transmitter-\gls{irs} encoding is possible, \cite{Karasik2019} proved using \gls{irs} only for passive beamforming is generally suboptimal in terms of achievable rate for finite input constellations.
-	% The capacity-achieving \gls{irs} strategy was found to
-	Recently, \gls{irs}-empowered \gls{sr} was introduced in \cite{Xu2020b,Hua2022,Hu2021a} where independent passive beamforming and backscatter encoding were combined using advanced architectures.
-	The authors of \cite{Xu2020b,Hua2022} proposed the \gls{irs} to modulate binary message over the whole phase shift matrix and the receiver to decodes from (non-coherent) primary to (coherent) backscatter link.
-	In contrast, \cite{Hu2021a} divided the \gls{irs} into reflection and information elements, and evaluated the error performance of non-coherent backscatter detection.
-	% Compared to existing \gls{irs}-empowered \gls{sr} that encodes and precodes independently using advanced architecture (e.g., overlay or parallel), Metascatter softly bridges and generalizes parasitic source of \gls{sr} and reflecting element of \gls{irs} via smart input design.
+	Although dynamic passive beamforming artificially creates temporal diversity for flexible channel reconfiguration and resource allocation, it demands additional computational cost and control overhead, and the tradeoff deserves further attention especially for large \gls{ris}.
+	In \cite{Chen2021,Zhang2021d}, \gls{ris} was also introduced to single- and multi-node \gls{sr} systems to reduce the total transmit power.
+	When joint transmitter-\gls{ris} encoding is possible, \cite{Karasik2019} proved using \gls{ris} only for passive beamforming is generally suboptimal in terms of achievable rate for finite input constellations.
+	% The capacity-achieving \gls{ris} strategy was found to
+	Recently, \gls{ris}-empowered \gls{sr} was introduced in \cite{Xu2020b,Hua2022,Hu2021a} where independent passive beamforming and backscatter encoding were combined using advanced architectures.
+	The authors of \cite{Xu2020b,Hua2022} proposed the \gls{ris} to modulate binary message over the whole phase shift matrix and the receiver to decodes from (non-coherent) primary to (coherent) backscatter link.
+	In contrast, \cite{Hu2021a} divided the \gls{ris} into reflection and information elements, and evaluated the error performance of non-coherent backscatter detection.
+	% Compared to existing \gls{ris}-empowered \gls{sr} that encodes and precodes independently using advanced architecture (e.g., overlay or parallel), Metascatter softly bridges and generalizes parasitic source of \gls{sr} and reflecting element of \gls{ris} via smart input design.
 
@@
 	However, the advantage of \gls{sic} is questionable because 1) it requires non-coherent primary encoding at the transmitter and re-encoding, precoding, and subtraction at the receiver, 2) the primary and backscatter symbols are mixed by multiplication instead of superposition, and 3) the backscatter symbol period is typically much longer due to physical constraints.
-	% Motivated by above, we propose a novel Metascatter network where multiple battery-free tags ride over a conventional point-to-point system and adapt their input probability distribution to simultaneously act as backscatter tags of \gls{sr} and reflecting elements of \gls{irs}.
-	Motivated by those, we propose the concept of Metascatter, which adapts the input distribution of a passive backscatter node to generalize backscatter sources of \gls{sr} and reflecting elements of \gls{irs}.
-	% An application scenario was considered where multiple Metascatters are introduced to conventional point-to-point system and adapt their input probability distribution to simultaneously act as backscatter tags of \gls{sr} and reflecting elements of \gls{irs}.
+	% Motivated by above, we propose a novel Metascatter network where multiple battery-free tags ride over a conventional point-to-point system and adapt their input probability distribution to simultaneously act as backscatter tags of \gls{sr} and reflecting elements of \gls{ris}.
+	Motivated by those, we propose the concept of Metascatter, which adapts the input distribution of a passive backscatter node to generalize backscatter sources of \gls{sr} and reflecting elements of \gls{ris}.
+	% An application scenario was considered where multiple Metascatters are introduced to conventional point-to-point system and adapt their input probability distribution to simultaneously act as backscatter tags of \gls{sr} and reflecting elements of \gls{ris}.
 	% An application scenario was considered where multiple Metascatters ride over a point-to-point transmission and simultaneously perform backscatter encoding and passive beamforming.
@@
 
-	\emph{First,} Metascatter adapts the input probability distribution of a finite-state passive backscatter device based on primary and (cascaded) backscatter \gls{csi} to unify and generalize parasitic source of \gls{sr} and reflecting elements of \gls{irs}.
+	\emph{First,} Metascatter adapts the input probability distribution of a finite-state passive backscatter device based on primary and (cascaded) backscatter \gls{csi} to unify and generalize parasitic source of \gls{sr} and reflecting elements of \gls{ris}.
 	The reflection pattern over time is no longer fully random or deterministic, but can be flexibly distributed to balance backscatter encoding and passive beamforming.
-	For single-user scenario, when primary link is absolutely prioritized, the distribution falls on one state and Metascatter boils down to conventional \gls{irs}.
+	For single-user scenario, when primary link is absolutely prioritized, the distribution falls on one state and Metascatter boils down to conventional \gls{ris}.
 	When only considering backscatter performance, the distribution involves the highest entropy and Metascatter is essentially an \gls{ambc} node.
@@
 	\begin{subsection}{IRS: Channel Reconfiguration}
-		% \gls{irs} elements assist legacy transmission by \emph{deterministically choosing phase shifts} based on relevant \gls{csi}.
+		% \gls{ris} elements assist legacy transmission by \emph{deterministically choosing phase shifts} based on relevant \gls{csi}.
 For a reflecting element with $M$ candidate states, reflection coefficient $\Gamma_m$ maps to the corresponding phase shift $\theta_m$ by \cite{Wu2018}
-		\gls{irs} elements assist legacy transmission by \emph{deterministic phase shifts selection} based on relevant \gls{csi}.
+		\gls{ris} elements assist legacy transmission by \emph{deterministic phase shifts selection} based on relevant \gls{csi}.
 		For a reflecting element with $M$ candidate states, reflection coefficient $\Gamma_m$ relates to the corresponding \emph{phase shift $\theta_m$} by \cite{Wu2018}
@@
 			\caption{
-				Input probability distribution and time block structure of \gls{sr}, \gls{irs}, and Metascatter.
+				Input probability distribution and time block structure of \gls{sr}, \gls{ris}, and Metascatter.
 				$T_s$ and $T_c$ respectively denote the primary and backscatter symbol period.
@@
 \ref{fi:metascatter}, Metascatter semi-randomly selects reflection state for each backscatter block, with guidance from \emph{input probability distribution $P(\Gamma_m)$.} In other words, it flexibly controls input distribution of candidate reflection states to balance backscatter encoding and passive beamforming.
-\gls{sr} and \gls{irs} can be regarded as extreme cases of Metascatter, where node input distribution boils down to uniform and deterministically biased, respectively.
+\gls{sr} and \gls{ris} can be regarded as extreme cases of Metascatter, where node input distribution boils down to uniform and deterministically biased, respectively.
 		Instead of using fully random or deterministic reflection pattern over time, as shown in Fig.
@@
 In other words, it flexibly controls input distribution of candidate reflection states to balance backscatter encoding and passive beamforming.
-\gls{sr} and \gls{irs} can be regarded as extreme cases of Metascatter, where node input distribution boils down to uniform and deterministic, respectively.
+\gls{sr} and \gls{ris} can be regarded as extreme cases of Metascatter, where node input distribution boils down to uniform and deterministic, respectively.
 		% flexibly controls input distribution of candidate reflection states to balance backscatter encoding and passive beamforming.
@@
 		% % Based on \gls{csi}, Metascatter adapts the reflection state distribution to unify data transmission and channel reconfiguration.
-		% \gls{sr} and \gls{irs} can be regarded as its extreme cases, where node input distribution boils down to uniform and deterministically biased, respectively.
+		% \gls{sr} and \gls{ris} can be regarded as its extreme cases, where node input distribution boils down to uniform and deterministically biased, respectively.
 		% Within channel coherence time, Metascatter semi-randomly selects reflection state for each backscatter block, with guidance from \emph{input probability distribution $P(\Gamma_m)$.}
 		\begin{remark}
-			Compared to conventional \gls{irs} literatures that optimize phase shifts under unit-module constraint, Metascatter starts from predefined reflection coefficients and designs their input distribution under sum-probability constraint to achieve flexible primary-backscatter tradeoff.
+			Compared to conventional \gls{ris} literatures that optimize phase shifts under unit-module constraint, Metascatter starts from predefined reflection coefficients and designs their input distribution under sum-probability constraint to achieve flexible primary-backscatter tradeoff.
 		\end{remark}
@@
 					% \While{$I^{(r-1)}(x_{\mathcal{K}})>I^{(r)}(x_{\mathcal{K}})+\alpha\gamma\lVert\nabla_{\boldsymbol{w}^*}I^{(r-1)}(x_{\mathcal{K}})\rVert$}
-					\While{$I^{(r)}(x_{\mathcal{K}})<I^{(r-1)}(x_{\mathcal{K}})-\alpha\gamma\lVert\nabla_{\boldsymbol{w}^*}I^{(r-1)}(x_{\mathcal{K}})\rVert^2$}
+					\While{$I^{(r)}(x_{\mathcal{K}})<I^{(r-1)}(x_{\mathcal{K}})+\alpha\gamma\lVert\nabla_{\boldsymbol{w}^*}I^{(r-1)}(x_{\mathcal{K}})\rVert^2$}
 						\State Set $\gamma^{(r)}\gets\beta\gamma^{(r)}$
@@
 		On the other hand, the optimal input distribution becomes fully deterministic at $\rho=1$ (i.e., best primary performance), where the state maximizes equivalent primary channel \eqref{eq:equivalent_channel} strength is chosen with probability \num{1}.
-		In this case, Metascatter boils down to an \gls{irs} element with $M$ discrete states.
+		In this case, Metascatter boils down to an \gls{ris} element with $M$ discrete states.
 		As $\rho$ moves from \num{0} to \num{1}, the optimal input distribution becomes gradually biased to one state and flexibly balances the primary-backscatter tradeoff.
@@
 		However, it requires more frequent detection and re-encoding at the user to maintain the primary rate.
-		When $N$ becomes sufficiently large, total backscatter rate approaches \num{0} and Metascatters boil down to conventional \gls{irs} elements with fixed reflection patterns during whole channel block.
+		When $N$ becomes sufficiently large, total backscatter rate approaches \num{0} and Metascatters boil down to conventional \gls{ris} elements with fixed reflection patterns during whole channel block.
 		In Fig. \subref*{fi:region_frequency}, we observe that passive Metascatter achieves higher backscatter rate at lower carrier frequency because of preferable propagation loss.
@@
 	This paper introduced Metascatter that adapts input distribution of passive backscatter nodes to simultaneously transmit and assist over existing wireless systems.
-	Starting from backscatter principles, we showed how Metascatters bridges and generalizes parasitic source of \gls{sr} and reflecting element of \gls{irs} via smart input design.
+	Starting from backscatter principles, we showed how Metascatters bridges and generalizes parasitic source of \gls{sr} and reflecting element of \gls{ris} via smart input design.
 	An application scenario was considered where multiple Metascatters ride over a point-to-point transmission to simultaneously encode self message and perform passive beamforming.

### 2022-07-31 main.tex
:pencil: Update abstract

@@
 
-% \usepackage{xcolor} \pagecolor[rgb]{0,0,0} \color[rgb]{1,1,1}
+\usepackage{xcolor} \pagecolor[rgb]{0,0,0} \color[rgb]{1,1,1}
 
@@
 \newacronym{bcd}{BCD}{Block Coordinate Descent}
+\newacronym{bc}{BackCom}{Backscatter Communications}
 \newacronym{bibo}{BIBO}{Binary-Input Binary-Output}
@@
 \newacronym{iid}{i.i.d.}{independent and identically distributed}
-\newacronym{kkt}{KKT}{Karush–Kuhn–Tucker}
+\newacronym{kkt}{KKT}{Karush-Kuhn-Tucker}
 \newacronym{mac}{MAC}{Multiple Access Channel}
@@
 % \title{UniScatter: Unifying Backscatter Communication, Reconfigurable Intelligent Surface, and Symbiotic Radio}
-\title{UniScatter: Unifying Symbiotic Radio and Reconfigurable Intelligent Surface}
+% \title{UniScatter:\\Unifying Backscatter Communication, Reconfigurable Intelligent Surface, and Symbiotic Radio}
+\title{UniScatter: Unifying\\Backscatter Communications, Reconfigurable Intelligent Surface, and Symbiotic Radio}
+% \title{UniScatter: Unifying Symbiotic Radio, Reconfigurable Intelligent Surface, and Wireless Sensor Network}
+% \title{UniScatter: Unifying Symbiotic Radio and Reconfigurable Intelligent Surface}
 \author{
@@
 \begin{abstract}
-	% Backscatter allows wireless nodes to harvest energy from, modulate information over, and reconfigure propagation of surrounding radio waves.
-	% Backscatter nodes can harvest energy from, modulate information over, and reconfigure propagation of ambient signals.
-	% Backscatter nodes can harvest energy from, modulate information over, and reconfigure propagation of surrounding radio waves.
-	% Scattering/reflection elements to
-	% An RIS is a thin surface composed of N elements, each being a reconfigurable scatterer: a small antenna that receives and re-radiates without amplification, but with a configurable time delay [3].
-For narrowband signals, this delay corresponds to a phase shift.
-
-	Scatterers can harvest energy from, modulate information over, and reconfigure propagation of ambient radio waves.
-	In backscatter communication,
+
+	% Space-division multiple access (SDMA) utilizes linear precoding to separate users in the spatial domain and relies on fully treating any residual multi-user interference as noise.
+Non-orthogonal multiple access (NOMA) uses linearly precoded superposition coding with successive interference cancellation (SIC) to superpose users in the power domain and relies on user grouping and ordering to enforce some users to fully decode and cancel interference created by other users.
+In this paper, we argue that to efficiently cope with the high throughput, heterogeneity of quality of service (QoS), and massive connectivity requirements of future multi-antenna wireless networks, multiple access design needs to depart from those two extreme interference management strategies, namely fully treat interference as noise (as in SDMA) and fully decode interference (as in NOMA).
+Considering a multiple-input single-output broadcast channel, we develop a novel multiple access framework, called rate-splitting multiple access (RSMA).
+RSMA is a more general and more powerful multiple access for downlink multi-antenna systems that contains SDMA and NOMA as special cases.
+RSMA relies on linearly precoded rate-splitting with SIC to decode part of the interference and treat the remaining part of the interference as noise.
+This capability of RSMA to partially decode interference and partially treat interference as noise enables to softly bridge the two extremes of fully decoding interference and treating interference as noise and provides room for rate and QoS enhancements and complexity reduction.
+The three multiple access schemes are compared, and extensive numerical results show that RSMA provides a smooth transition between SDMA and NOMA and outperforms them both in a wide range of network loads (underloaded and overloaded regimes) and user deployments (with a diversity of channel directions, channel strengths, and qualities of channel state information at the transmitter).
+Moreover, RSMA provides rate and QoS enhancements over NOMA at a lower computational complexity for the transmit scheduler and the receivers (number of SIC layers).
+
+	% In the past few years, a large body of literature has been created on downlink Non-Orthogonal Multiple Access (NOMA), employing superposition coding and Successive Interference Cancellation (SIC), in multi-antenna wireless networks.
+Furthermore, the benefits of NOMA over Orthogonal Multiple Access (OMA) have been highlighted.
+In this paper, we take a critical and fresh look at the downlink Next Generation Multiple Access (NGMA) literature.
+Instead of contrasting NOMA with OMA, we contrast NOMA with two other multiple access baselines.
+The first is conventional Multi-User Linear Precoding (MU–LP), as used in Space-Division Multiple Access (SDMA) and multi-user Multiple-Input MultipleOutput (MIMO) in 4G and 5G.
+The second, called Rate-Splitting Multiple Access (RSMA), is based on multi-antenna Rate-Splitting (RS).
+It is also a non-orthogonal transmission strategy relying on SIC developed in the past few years in parallel and independently from NOMA.
+We show that there is some confusion about the benefits of NOMA, and we dispel the associated misconceptions.
+First, we highlight why NOMA is inefficient in multi-antenna settings based on basic multiplexing gain analysis.
+We stress that the issue lies in how the NOMA literature, originally developed for single-antenna setups, has been hastily applied to multi-antenna setups, resulting in a misuse of spatial dimensions and therefore loss in multiplexing gains and rate.
+Second, we show that NOMA incurs a severe multiplexing gain loss despite an increased receiver complexity due to an inefficient use of SIC receivers.
+Third, we emphasize that much of the merits of NOMA are due to the constant comparison to OMA instead of comparing it to MU–LP and RS baselines.
+We then expose the pivotal design constraint that multi-antenna NOMA requires one user to fully decode the messages of the other users.
+This design constraint is responsible for the multiplexing gain erosion, rate and spectral efficiency loss, ineffectiveness to serve a large number of users, and inefficient use of SIC receivers in multi-antenna settings.
+Our analysis and simulation results confirm that NOMA should not be applied blindly to multi-antenna settings, highlight the scenarios where MU–LP outperforms NOMA and vice versa, and demonstrate the inefficiency, performance loss, and complexity disadvantages of NOMA compared to RSMA.
+The first takeaway message is that, while NOMA is suited for single-antenna settings (as originally intended), it is not efficient in most multi-antenna deployments.
+The second takeaway message is that another non-orthogonal transmission framework, based on RSMA, exists which fully exploits the multiplexing gain and the benefits of SIC to boost the rate and the number of users to serve in multi-antenna settings and outperforms both NOMA and MU–LP.
+Indeed, RSMA achieves higher multiplexing gains and rates, serves a larger number of users, is more robust to user deployments, network loads and inaccurate channel state information and has a lower receiver complexity than NOMA.
+Consequently, RSMA is a promising technology for NGMA and future networks such as 6G and beyond.
+
+	Scatterers can harvest energy from, modulate information over, and influence propagation of surrounding radio waves.
+	% Conventional literatures treat backscatter communication,
+	% \gls{ris} employs scattering antennas or programmable metamaterial to control wireless channel of legacy networks.
+	% \gls{bc} varies the input impedance of physical objects to manipulate the magnitude, phase, and/or frequency of scattered signal to communicate within range.
+	\gls{bc} varies object impedance to manipulate the magnitude, phase, and/or frequency of scattered signal to encode information and deliver within coverage.
+	% \gls{bc} changes the magnitude, phase, and/or frequency of scattered signal of ph
+	% varies the input impedance of physical objects to manipulate the magnitude, phase, and/or frequency of the scattered signal to encode self information.
+	% a tag af- fixed to objects [1]. The information on EPC-tagged objects
+	% By varying the antenna impedance, a RFID tag can encode digital (typically binary) symbols onto the uplink signal, which is then decoded by the RFID reader.
+	% changes the scattered signal
+	\gls{ris} adapts scattering antennas or programmable metamaterial to control propagation environment and enhance signal strength in the desired direction.
+	% Conventional \gls{ris} and \gls{sr} appeared as
+	% \gls{sr} integrates scatter nodes into legacy systems to reuse
+	% Different from CR that uses power-consuming active RF chains at both PTx and STx shown in Fig.
+1(b), the SR uses backscattering radio technology to support the secondary transmission from STx to SRx, which greatly reduces the power consumption.
+In particular, STx transmits its messages to SRx over the RF signals received from PTx by varying the reflection coefficients, thus the secondary system shares the spectrum, energy, and infrastructure of the primary system with high spectrum- and power-efficiency.
+	\gls{sr} incorporates scatter nodes into active wireless networks and utilize recycled signal to transmit self information and enhance legacy multipath to the cooperative receiver.
+	% In this paper, we introduce UniScatter as a novel paradigm that bridges and generalizes those concepts to support the high throughput, ultralow power, and ubiquitous connectivity of future wireless networks.
+	In this paper, we introduce UniScatter as a novel paradigm that bridges and generalizes those three concepts to support the high throughput, ultralow power, and ubiquitous connectivity of future wireless networks using shared spectrum, energy, and infrastructures.
+	% Based on \gls{csi} and link priority, UniScatter nodes adapt input probability distribution of reflection states
+	% Based on \gls{csi}, each UniScatter node adapts probability distribution of reflection states to flexibly balance information encoding and passive beamforming in a mutualistic manner.
+	Based on \gls{csi}, each UniScatter node adapts probability distribution of reflection states to balance information encoding and passive beamforming in a mutualistic and flexible manner.
+	The scatter source of \gls{bc}/\gls{sr} and reflecting element of \gls{ris} can be regarded as extreme cases of UniScatter node, where the input distribution boils down to equiprobable and degenerate, respectively.
+	% Existing \gls{ris}-based \gls{bc}
+	% UniScatter unifies \gls{bc}, \gls{ris} and \gls{sr} f
+	% To evaluate the benefits of UniScatter, we consider
+	% To accommodate signal characteristics, the receiver first jointly and semi-coherently decodes all UniScatter nodes over accumulated energy, then re-encodes to retrieve
+	To accommodate signal characteristics, we propose a practical receiver that first semi-coherently decodes all nodes from accumulated energy, then re-encodes and determines the equivalent channel for primary decoding.
+	% It not only avoids high complexity of joint \gls{ml} and \gls{sic}, but also preserves the benefits of passive beamforming on primary link.
+	It reduces the complexity of cooperative decoding and preserves the benefit of passive beamforming on primary link.
+	Moreover, we consider a scenario where a multi-antenna \gls{ap} serves a single-antenna user surrounded by multiple UniScatter nodes, and characterize the achievable primary-(total-)backscatter rate region by optimizing input distribution at nodes, active beamforming at the \gls{ap}, and decision regions at the user.
+	Simulation results demonstrate UniScatter can unify \gls{bc}, \gls{ris} and \gls{sr} to flexibly control transmit-assist tradeoff via smart input distribution design.
+	% Simulation results demonstrate Metascatters can exploit additional propagation paths to transmit and assist via adaptive input design.
+
+	% characterize the achievable primary-(total-)backscatter rate region for a single-antenna user surrounded by multiple UniScatter nodes,
+
+	% Since UniScatter nodes ride over legacy signal and , backscatter decoding can be viewed as part of primary channel training
+
+	% To fully accommodate backscatter characteristics, we also propose a novel receiving strategy that first jointly decodes all Metascatter from accumulated energy, then models their reflection patterns and backscatter paths within equivalent channel for primary decoding.
+	% Since backscatter message is modulated over primary signal, backscatter decoding is indeed part of primary channel training, and there is no need for operation-intensive \gls{sic} at the receiver.
+	% To accommodate backscatter characteristics and reduce decoding complexity, we consider a joint semi-coherent detection for all Metascatters over accumulated energy $z$.
+
+	% Moreover, we consider a specific scenario where a multi-antenna \gls{ap} serves a single-antenna user surrounded by multiple Metascatters.
+	% For simplicity, it is assumed the user first jointly decodes all backscatter messages from accumulated energy, then models reflection patterns and backscatter paths within equivalent channel for primary decoding.
+	% % Once modulation uncertainty of Metascatters are eliminated, models contributions from additional paths within equivalent channel
+	% % decodes all Metascatters jointly by energy detection, then models their contribution within equivalent channel and decodes the primary link.
+	% % For simplicity, the user is assumed first decodes all Metascatters jointly by energy detection, then models their contribution within equivalent channel and decodes the primary link.
+	% We characterize the achievable primary-(total-)backscatter rate region by optimizing the input distribution at Metascatters, the active beamforming at the AP, and the decision regions at the user.
+	% % A suboptimal \gls{bcd} algorithm was proposed, where the input distribution satisfying the \gls{kkt} conditions is evaluated in closed form, the transmit beamforming is optimized by \gls{pgd}, and the decision thresholds are optimized by \gls{dp}.
+	% % A suboptimal \gls{bcd} algorithm is proposed, where the \gls{kkt} input distribution is numerically evaluated in closed form, the active beamforming is iteratively updated by \gls{pgd}, and the decision regions are restricted to convex and opty
+	% % We then propose a suboptimal \gls{bcd} algorithm that numerically evaluates the \gls{kkt} input distribution in closed form, iteratively updates the active beamforming by \gls{pgd}, and employs existing thresholding schemes to refine suboptimal convex decision regions.
+	% A suboptimal \gls{bcd} algorithm is proposed, which numerically evaluates the \gls{kkt} input distribution in closed form, iteratively updates the active beamforming by \gls{pgd}, and employs existing thresholding schemes for suboptimal convex decision regions.
+	% % A suboptimal \gls{bcd} algorithm was proposed with the \gls{kkt} input distribution evaluated in closed form, the active beamforming updated by \gls{pgd}, and the decision regions restricted to convex then refined by \gls{dp}.
+	% % the decision regions are restricted as convex then optimized by \gls{dp}.
+	% % A suboptimal \gls{bcd} algorithm was proposed, where the \gls{kkt} input distribution is evaluated in closed form, the active beamforming is optimized by \gls{pgd} with backtracking line search, and the decision thresholds are optimized by \gls{dp}.
+	% Simulation results demonstrate Metascatters can exploit additional propagation paths to transmit and assist via adaptive input design.
+
 	% ! Φ(c[n]) vs P
-
-	% TODO
-	back comms, symbiotic radio and RIS have appeared as three different and somewhat unrelated wireless technologies, explaining the key feature of each of them.
-Then I would say we introduce metascatter as a new paradigm that unifies and generalizes those three ...., explain the key feature of metascatter.
-
-	We uniquely introduce \emph{Metascatter} that adapts the input distribution of a finite-state passive backscatter node based on \gls{csi}, to \emph{simultaneously} encode self message and assist legacy transmission while powered by surrounding waves.
-	% Compared to conventional \gls{ris}-empowered \gls{sr} that encodes and precodes independently (e.g., overlay or parallel), Metascatter refines backscatter principles to bridge parasitic source of \gls{sr} and reflecting element of \gls{ris} as extreme cases.
-	Compared to existing \gls{ris}-empowered \gls{sr} that encodes and precodes independently using advanced architecture (e.g., overlay or parallel), Metascatter softly bridges and generalizes parasitic source of \gls{sr} and reflecting element of \gls{ris} via smart input design.
-	% Compared to \gls{ris}-empowered \gls{sr} that encodes and precodes independently (e.g., overlay or parallel), Metascatter refines backscatter principles to bridge parasitic source of \gls{sr} and reflecting element of \gls{ris} as extreme cases.
-	% Such an integrated distribution design not only yields universal modularity with reduced optimization cost, but also enables a flexible tradeoff between primary and backscatter links using shared spectrum, energy, and infrastructures.
-	This not only reduces hardware complexity and optimization cost, but also enables a flexible tradeoff between primary (legacy) and backscatter links using shared spectrum, energy, and infrastructures.
-	Moreover, we consider a specific scenario where a multi-antenna \gls{ap} serves a single-antenna user surrounded by multiple Metascatters.
-	For simplicity, it is assumed the user first jointly decodes all backscatter messages from accumulated energy, then models reflection patterns and backscatter paths within equivalent channel for primary decoding.
-	% Once modulation uncertainty of Metascatters are eliminated, models contributions from additional paths within equivalent channel
-	% decodes all Metascatters jointly by energy detection, then models their contribution within equivalent channel and decodes the primary link.
-	% For simplicity, the user is assumed first decodes all Metascatters jointly by energy detection, then models their contribution within equivalent channel and decodes the primary link.
-	We characterize the achievable primary-(total-)backscatter rate region by optimizing the input distribution at Metascatters, the active beamforming at the AP, and the decision regions at the user.
-	% A suboptimal \gls{bcd} algorithm was proposed, where the input distribution satisfying the \gls{kkt} conditions is evaluated in closed form, the transmit beamforming is optimized by \gls{pgd}, and the decision thresholds are optimized by \gls{dp}.
-	% A suboptimal \gls{bcd} algorithm is proposed, where the \gls{kkt} input distribution is numerically evaluated in closed form, the active beamforming is iteratively updated by \gls{pgd}, and the decision regions are restricted to convex and opty
-	% We then propose a suboptimal \gls{bcd} algorithm that numerically evaluates the \gls{kkt} input distribution in closed form, iteratively updates the active beamforming by \gls{pgd}, and employs existing thresholding schemes to refine suboptimal convex decision regions.
-	A suboptimal \gls{bcd} algorithm is proposed, which numerically evaluates the \gls{kkt} input distribution in closed form, iteratively updates the active beamforming by \gls{pgd}, and employs existing thresholding schemes for suboptimal convex decision regions.
-	% A suboptimal \gls{bcd} algorithm was proposed with the \gls{kkt} input distribution evaluated in closed form, the active beamforming updated by \gls{pgd}, and the decision regions restricted to convex then refined by \gls{dp}.
-	% the decision regions are restricted as convex then optimized by \gls{dp}.
-	% A suboptimal \gls{bcd} algorithm was proposed, where the \gls{kkt} input distribution is evaluated in closed form, the active beamforming is optimized by \gls{pgd} with backtracking line search, and the decision thresholds are optimized by \gls{dp}.
-	Simulation results demonstrate Metascatters can exploit additional propagation paths to transmit and assist via adaptive input design.
+	% In this paper, we argue that to efficiently cope with the high throughput, heterogeneity of quality of service (QoS), and massive connectivity requirements of future multi-antenna wireless networks, multiple access design needs to depart from those two extreme interference management strategies, namely fully treat interference as noise (as in SDMA) and fully decode interference (as in NOMA).
+Considering a multiple-input single-output broadcast channel, we develop a novel multiple access framework, called rate-splitting multiple access (RSMA).
+RSMA is a more general and more powerful multiple access for downlink multi-antenna systems that contains SDMA and NOMA as special cases.
+RSMA relies on linearly precoded rate-splitting with SIC to decode part of the interference and treat the remaining part of the interference as noise.
+This capability of RSMA to partially decode interference and partially treat interference as noise enables to softly bridge the two extremes of fully decoding interference and treating interference as noise and provides room for rate and QoS enhancements and complexity reduction.
+The three multiple access schemes are compared, and extensive numerical results show that RSMA provides a smooth transition between SDMA and NOMA and outperforms them both in a wide range of network loads (underloaded and overloaded regimes) and user deployments (with a diversity of channel directions, channel strengths, and qualities of channel state information at the transmitter).
+Moreover, RSMA provides rate and QoS enhancements over NOMA at a lower computational complexity for the transmit scheduler and the receivers (number of SIC layers).
+
+	% We uniquely introduce \emph{Metascatter} that adapts the input distribution of a finite-state passive backscatter node based on \gls{csi}, to \emph{simultaneously} encode self message and assist legacy transmission while powered by surrounding waves.
+	% % Compared to conventional \gls{ris}-empowered \gls{sr} that encodes and precodes independently (e.g., overlay or parallel), Metascatter refines backscatter principles to bridge parasitic source of \gls{sr} and reflecting element of \gls{ris} as extreme cases.
+	% Compared to existing \gls{ris}-empowered \gls{sr} that encodes and precodes independently using advanced architecture (e.g., overlay or parallel), Metascatter softly bridges and generalizes parasitic source of \gls{sr} and reflecting element of \gls{ris} via smart input design.
+	% % Compared to \gls{ris}-empowered \gls{sr} that encodes and precodes independently (e.g., overlay or parallel), Metascatter refines backscatter principles to bridge parasitic source of \gls{sr} and reflecting element of \gls{ris} as extreme cases.
+	% % Such an integrated distribution design not only yields universal modularity with reduced optimization cost, but also enables a flexible tradeoff between primary and backscatter links using shared spectrum, energy, and infrastructures.
+	% This not only reduces hardware complexity and optimization cost, but also enables a flexible tradeoff between primary (legacy) and backscatter links using shared spectrum, energy, and infrastructures.
+	% Moreover, we consider a specific scenario where a multi-antenna \gls{ap} serves a single-antenna user surrounded by multiple Metascatters.
+	% For simplicity, it is assumed the user first jointly decodes all backscatter messages from accumulated energy, then models reflection patterns and backscatter paths within equivalent channel for primary decoding.
+	% % Once modulation uncertainty of Metascatters are eliminated, models contributions from additional paths within equivalent channel
+	% % decodes all Metascatters jointly by energy detection, then models their contribution within equivalent channel and decodes the primary link.
+	% % For simplicity, the user is assumed first decodes all Metascatters jointly by energy detection, then models their contribution within equivalent channel and decodes the primary link.
+	% We characterize the achievable primary-(total-)backscatter rate region by optimizing the input distribution at Metascatters, the active beamforming at the AP, and the decision regions at the user.
+	% % A suboptimal \gls{bcd} algorithm was proposed, where the input distribution satisfying the \gls{kkt} conditions is evaluated in closed form, the transmit beamforming is optimized by \gls{pgd}, and the decision thresholds are optimized by \gls{dp}.
+	% % A suboptimal \gls{bcd} algorithm is proposed, where the \gls{kkt} input distribution is numerically evaluated in closed form, the active beamforming is iteratively updated by \gls{pgd}, and the decision regions are restricted to convex and opty
+	% % We then propose a suboptimal \gls{bcd} algorithm that numerically evaluates the \gls{kkt} input distribution in closed form, iteratively updates the active beamforming by \gls{pgd}, and employs existing thresholding schemes to refine suboptimal convex decision regions.
+	% A suboptimal \gls{bcd} algorithm is proposed, which numerically evaluates the \gls{kkt} input distribution in closed form, iteratively updates the active beamforming by \gls{pgd}, and employs existing thresholding schemes for suboptimal convex decision regions.
+	% % A suboptimal \gls{bcd} algorithm was proposed with the \gls{kkt} input distribution evaluated in closed form, the active beamforming updated by \gls{pgd}, and the decision regions restricted to convex then refined by \gls{dp}.
+	% % the decision regions are restricted as convex then optimized by \gls{dp}.
+	% % A suboptimal \gls{bcd} algorithm was proposed, where the \gls{kkt} input distribution is evaluated in closed form, the active beamforming is optimized by \gls{pgd} with backtracking line search, and the decision thresholds are optimized by \gls{dp}.
+	% Simulation results demonstrate Metascatters can exploit additional propagation paths to transmit and assist via adaptive input design.
+
+	% Symbiotic radio has emerged as a promising technology for spectrum- and energy-efficient wireless communications, where the passive secondary backscatter devices (BDs) reuse not only the spectrum but also the power of the active primary users to transmit their own information.
+In return, the primary communication links can be enhanced by the additional multipaths created by the BDs.
+This is known as the mutualism relationship of symbiotic radio.
+
+	% Symbiotic radio has emerged as a new paradigm to achieve both spectrum-efficient and energy-efficient wireless communications, for which the secondary user modulates its information over the radio frequency (RF) signals received from primary transmitter (PT) [1]–[3].
+As such, the secondary backscatter device (BD) in symbiotic radio systems leverages not only the spectrum as in the extensively studied cognitive radio systems [4]–[6], but also the energy of the primary signals via passive backscattering technology for its own information transmission
+
+	% Specifically, the passive secondary backscatter device (BD) in symbiotic radio systems reuses not only the spectrum of the active primary communication as in traditional CR systems, but also its power via passive backscattering technology [25].
+
+	% Recently, mutualistic spectrum sharing has been observed in cognitive backscatter communication (CBC) systems [5], in which the active transmission achieves multipath diversity with the help of the backscatter transmission, while the backscatter device gains the transmission opportunity using the RF source and radio spectrum of the active transmission.
+Such mutualism advocates the coexistence of cellular and Internet-of-Things (IoT) networks in the same spectrum [6].
+
+	% To be specific, there are two types of transmissions in SR: the primary transmission and the secondary transmission.
+In the primary transmission, a primary transmitter (PTx) transmits messages to its receiver by using the traditional active radio technology, while in the secondary transmission, a secondary transmitter (STx), operating as a passive device, pe- riodically switches its load impedance to change the amplitude and/or phase of its backscattered signal, thereby modulating its information bits over a signal received from PTx [6].
+The receiver in SR receives two types of signals: a direct link signal from PTx and a backscatter link signal from STx.
+Due to the use of backscatter, the backscatter link signal contains information from both PTx and STx.
+When the secondary transmission rate is much lower than the primary transmission rate, the backscatter link can be seen as an additional path for the primary transmission with a slow channel variation introduced by the changing of load impedance at STx.
+In this case, the secondary system obtains the transmission op- portunity without requiring additional spectrum and power- consuming active components, and in return the secondary transmission provides multipath gain instead of interference to the primary transmission, thereby yielding mutual benefits.
+
+	% opportunistically
+	% \gls{sr} introduces scatter nodes modulate over active legacy transmission
+
+	% \gls{sr} incorporates scatter nodes into active wireless systems to transmit over sh
+	% \gls{sr} incorporates scatter nodes into active wireless systems to operate over recycled radio wave and transmit self information and enhance legacy multipath to the cooperative receiver.
+	% In \gls{sr}, the scatter nodes are integrated with existing networks that transmit to legacy receiver
+
+	% the passive secondary backscatter devices (BDs) reuse not only the spectrum but also the power of the active primary users to transmit their own information.
+In return, the primary communication links can be enhanced by the additional multipaths created by the BDs.
+This is known as the mutualism relationship of symbiotic radio.
+
+	% to transmit to
 \end{abstract}

### 2022-08-01 main.tex
:pencil: Update abstract

@@
 	% changes the scattered signal
-	\gls{ris} adapts scattering antennas or programmable metamaterial to control propagation environment and enhance signal strength in the desired direction.
+	\gls{ris} adapts scattering antennas or programmable metamaterial to control propagation environment and boost signal strength in desired direction.
 	% Conventional \gls{ris} and \gls{sr} appeared as
@@
 In particular, STx transmits its messages to SRx over the RF signals received from PTx by varying the reflection coefficients, thus the secondary system shares the spectrum, energy, and infrastructure of the primary system with high spectrum- and power-efficiency.
-	\gls{sr} incorporates scatter nodes into active wireless networks and utilize recycled signal to transmit self information and enhance legacy multipath to the cooperative receiver.
+	\gls{sr} incorporates scatter nodes into active networks, which recycle ambient signal to transmit self information and enhance legacy multipath to the cooperative receiver.
 	% In this paper, we introduce UniScatter as a novel paradigm that bridges and generalizes those concepts to support the high throughput, ultralow power, and ubiquitous connectivity of future wireless networks.
-	In this paper, we introduce UniScatter as a novel paradigm that bridges and generalizes those three concepts to support the high throughput, ultralow power, and ubiquitous connectivity of future wireless networks using shared spectrum, energy, and infrastructures.
+	In this paper, we introduce UniScatter as a novel paradigm that bridges and generalizes those three concepts to support the high throughput, ultralow power, and ubiquitous connectivity of future wireless networks.
 	% Based on \gls{csi} and link priority, UniScatter nodes adapt input probability distribution of reflection states
 	% Based on \gls{csi}, each UniScatter node adapts probability distribution of reflection states to flexibly balance information encoding and passive beamforming in a mutualistic manner.
-	Based on \gls{csi}, each UniScatter node adapts probability distribution of reflection states to balance information encoding and passive beamforming in a mutualistic and flexible manner.
-	The scatter source of \gls{bc}/\gls{sr} and reflecting element of \gls{ris} can be regarded as extreme cases of UniScatter node, where the input distribution boils down to equiprobable and degenerate, respectively.
+	% Based on \gls{csi}, each UniScatter node adapts probability distribution of reflection states to balance information encoding and passive beamforming in a mutualistic and flexible manner.
+	Using shared spectrum, energy, and infrastructures, each UniScatter node adapts probability distribution of reflection states based on \gls{csi} to balance information encoding and passive beamforming in a mutualistic and flexible manner.
+	The scatter source of \gls{bc}/\gls{sr} and reflecting element of \gls{ris} can be viewed as extreme cases of UniScatter node, where the input distribution boils down to equiprobable and degenerate, respectively.
 	% Existing \gls{ris}-based \gls{bc}
@@
 	% To accommodate signal characteristics, the receiver first jointly and semi-coherently decodes all UniScatter nodes over accumulated energy, then re-encodes to retrieve
-	To accommodate signal characteristics, we propose a practical receiver that first semi-coherently decodes all nodes from accumulated energy, then re-encodes and determines the equivalent channel for primary decoding.
+	To accommodate signal characteristics, we propose a practical receiver that semi-coherently decodes all nodes from accumulated energy, re-encodes to determine the equivalent channel, then decodes the primary link.
+	% To accommodate signal characteristics, we propose a practical receiver that semi-coherently decodes all nodes from accumulated energy, re-encodes to determine the equivalent channel, and decodes the primary link.
+	% To accommodate signal characteristics, we propose a practical receiver that first semi-coherently decodes all nodes by energy detection, then re-encodes and determines the equivalent channel for primary decoding.
 	% It not only avoids high complexity of joint \gls{ml} and \gls{sic}, but also preserves the benefits of passive beamforming on primary link.
-	It reduces the complexity of cooperative decoding and preserves the benefit of passive beamforming on primary link.
-	Moreover, we consider a scenario where a multi-antenna \gls{ap} serves a single-antenna user surrounded by multiple UniScatter nodes, and characterize the achievable primary-(total-)backscatter rate region by optimizing input distribution at nodes, active beamforming at the \gls{ap}, and decision regions at the user.
-	Simulation results demonstrate UniScatter can unify \gls{bc}, \gls{ris} and \gls{sr} to flexibly control transmit-assist tradeoff via smart input distribution design.
+	It reduces the complexity of cooperative decoding while preserves the benefit of backscatter modulation and passive beamforming.
+	% Moreover, we consider an application scenario where a multi-antenna \gls{ap} serves a single-antenna user surrounded by multiple UniScatter nodes, and characterize the achievable primary-(total-)backscatter rate region by optimizing input distribution at nodes, active beamforming at the \gls{ap}, and decision regions at the user.
+	Moreover, we consider an application scenario where a multi-antenna \gls{ap} serves a single-antenna user surrounded by multiple UniScatter nodes, and characterize the achievable primary-(total-)backscatter rate region by designing input distribution at the nodes, active beamforming at the \gls{ap}, and backscatter decision design at the user.
+	Simulation results demonstrate UniScatter can unify \gls{bc}, \gls{ris} and \gls{sr} to flexibly control the transmit-assist tradeoff via smart input distribution design.
 	% Simulation results demonstrate Metascatters can exploit additional propagation paths to transmit and assist via adaptive input design.

### 2022-08-01 main.tex
:pencil: Update abstract

--- 2022-07-30 main.tex
@@
 \newacronym{qam}{QAM}{Quadrature Amplitude Modulation}
+\newacronym{qos}{QoS}{Quality of Service}
 \newacronym{rf}{RF}{Radio-Frequency}
@@
 \begin{abstract}
-	% Backscatter allows wireless nodes to harvest energy from, modulate information over, and reconfigure propagation of surrounding radio waves.
-	% Backscatter nodes can harvest energy from, modulate information over, and reconfigure propagation of ambient signals.
-	% Backscatter nodes can harvest energy from, modulate information over, and reconfigure propagation of surrounding radio waves.
-	% Scattering/reflection elements to
-	% An RIS is a thin surface composed of N elements, each being a reconfigurable scatterer: a small antenna that receives and re-radiates without amplification, but with a configurable time delay [3].
-For narrowband signals, this delay corresponds to a phase shift.
-
-	Scatterers can harvest energy from, modulate information over, and reconfigure propagation of ambient radio waves.
-	In backscatter communication,
-	% ! Φ(c[n]) vs P
-
-	% TODO
-	back comms, symbiotic radio and RIS have appeared as three different and somewhat unrelated wireless technologies, explaining the key feature of each of them.
-Then I would say we introduce metascatter as a new paradigm that unifies and generalizes those three ...., explain the key feature of metascatter.
-
-	We uniquely introduce \emph{Metascatter} that adapts the input distribution of a finite-state passive backscatter node based on \gls{csi}, to \emph{simultaneously} encode self message and assist legacy transmission while powered by surrounding waves.
-	% Compared to conventional \gls{ris}-empowered \gls{sr} that encodes and precodes independently (e.g., overlay or parallel), Metascatter refines backscatter principles to bridge parasitic source of \gls{sr} and reflecting element of \gls{ris} as extreme cases.
-	Compared to existing \gls{ris}-empowered \gls{sr} that encodes and precodes independently using advanced architecture (e.g., overlay or parallel), Metascatter softly bridges and generalizes parasitic source of \gls{sr} and reflecting element of \gls{ris} via smart input design.
-	% Compared to \gls{ris}-empowered \gls{sr} that encodes and precodes independently (e.g., overlay or parallel), Metascatter refines backscatter principles to bridge parasitic source of \gls{sr} and reflecting element of \gls{ris} as extreme cases.
-	% Such an integrated distribution design not only yields universal modularity with reduced optimization cost, but also enables a flexible tradeoff between primary and backscatter links using shared spectrum, energy, and infrastructures.
-	This not only reduces hardware complexity and optimization cost, but also enables a flexible tradeoff between primary (legacy) and backscatter links using shared spectrum, energy, and infrastructures.
-	Moreover, we consider a specific scenario where a multi-antenna \gls{ap} serves a single-antenna user surrounded by multiple Metascatters.
-	For simplicity, it is assumed the user first jointly decodes all backscatter messages from accumulated energy, then models reflection patterns and backscatter paths within equivalent channel for primary decoding.
-	% Once modulation uncertainty of Metascatters are eliminated, models contributions from additional paths within equivalent channel
-	% decodes all Metascatters jointly by energy detection, then models their contribution within equivalent channel and decodes the primary link.
-	% For simplicity, the user is assumed first decodes all Metascatters jointly by energy detection, then models their contribution within equivalent channel and decodes the primary link.
-	We characterize the achievable primary-(total-)backscatter rate region by optimizing the input distribution at Metascatters, the active beamforming at the AP, and the decision regions at the user.
-	% A suboptimal \gls{bcd} algorithm was proposed, where the input distribution satisfying the \gls{kkt} conditions is evaluated in closed form, the transmit beamforming is optimized by \gls{pgd}, and the decision thresholds are optimized by \gls{dp}.
-	% A suboptimal \gls{bcd} algorithm is proposed, where the \gls{kkt} input distribution is numerically evaluated in closed form, the active beamforming is iteratively updated by \gls{pgd}, and the decision regions are restricted to convex and opty
-	% We then propose a suboptimal \gls{bcd} algorithm that numerically evaluates the \gls{kkt} input distribution in closed form, iteratively updates the active beamforming by \gls{pgd}, and employs existing thresholding schemes to refine suboptimal convex decision regions.
-	A suboptimal \gls{bcd} algorithm is proposed, which numerically evaluates the \gls{kkt} input distribution in closed form, iteratively updates the active beamforming by \gls{pgd}, and employs existing thresholding schemes for suboptimal convex decision regions.
-	% A suboptimal \gls{bcd} algorithm was proposed with the \gls{kkt} input distribution evaluated in closed form, the active beamforming updated by \gls{pgd}, and the decision regions restricted to convex then refined by \gls{dp}.
-	% the decision regions are restricted as convex then optimized by \gls{dp}.
-	% A suboptimal \gls{bcd} algorithm was proposed, where the \gls{kkt} input distribution is evaluated in closed form, the active beamforming is optimized by \gls{pgd} with backtracking line search, and the decision thresholds are optimized by \gls{dp}.
-	Simulation results demonstrate Metascatters can exploit additional propagation paths to transmit and assist via adaptive input design.
+	% First, we highlight why NOMA is inefficient in multi-antenna settings based on basic multiplexing gain analysis.
+We stress that the issue lies in how the NOMA literature, originally developed for single-antenna setups, has been hastily applied to multi-antenna setups, resulting in a misuse of spatial dimensions and therefore loss in multiplexing gains and rate.
+Second, we show that NOMA incurs a severe multiplexing gain loss despite an increased receiver complexity due to an inefficient use of SIC receivers.
+Third, we emphasize that much of the merits of NOMA are due to the constant comparison to OMA instead of comparing it to MU–LP and RS baselines.
+We then expose the pivotal design constraint that multi-antenna NOMA requires one user to fully decode the messages of the other users.
+This design constraint is responsible for the multiplexing gain erosion, rate and spectral efficiency loss, ineffectiveness to serve a large number of users, and inefficient use of SIC receivers in multi-antenna settings.
+Our analysis and simulation results confirm that NOMA should not be applied blindly to multi-antenna settings, highlight the scenarios where MU–LP outperforms NOMA and vice versa, and demonstrate the inefficiency, performance loss, and complexity disadvantages of NOMA compared to RSMA.
+The first takeaway message is that, while NOMA is suited for single-antenna settings (as originally intended), it is not efficient in most multi-antenna deployments.
+The second takeaway message is that another non-orthogonal transmission framework, based on RSMA, exists which fully exploits the multiplexing gain and the benefits of SIC to boost the rate and the number of users to serve in multi-antenna settings and outperforms both NOMA and MU–LP.
+Indeed, RSMA achieves higher multiplexing gains and rates, serves a larger number of users, is more robust to user deployments, network loads and inaccurate channel state information and has a lower receiver complexity than NOMA.
+Consequently, RSMA is a promising technology for NGMA and future networks such as 6G and beyond.
+
+	Scatterers can harvest energy from, modulate information over, and influence propagation of surrounding radio waves.
+	\gls{bc} varies object impedance to manipulate the magnitude, phase, and/or frequency of scattered signal to encode information and deliver within coverage.
+	\gls{ris} adapts scattering antennas or programmable metamaterial to control propagation environment and boost/suppress signal strength in specific directions.
+	\gls{sr} incorporates scatter nodes into active networks, which recycle ambient signal to transmit self information and enhance legacy multipath to the cooperative receiver.
+	% In this paper, we depart from those concepts and introduce UniScatter as a new paradigm to support the high throughput, ultralow power, and ubiquitous connectivity of future wireless networks using shared spectrum, energy, and infrastructures.
+	In this paper, we depart from those concepts and introduce UniScatter as a new paradigm to support the high throughput, ultralow power, and ubiquitous connectivity of future wireless networks.
+	Instead of treating probability distribution of reflection states as equiprobable (as scattering source of \gls{bc}/\gls{sr}) or degenerate (as reflecting element of \gls{ris}), UniScatter node adapts input distribution based on \gls{csi} and link priority to balance information encoding and channel reconfiguration in a mutualistic and flexible manner.
+	% Accommodated to signal characteristics, UniScatter receiver semi-coherently decodes all nodes from accumulated energy, re-encodes to determine the equivalent channel, then decodes the primary link to support backscatter modulation and preserve passive beamforming.
+	% Accommodated to signal characteristics, UniScatter receiver semi-coherently decodes all nodes from accumulated energy, combines reflection pattern with \gls{csi} for the equivalent channel, then decodes the primary link to support backscatter modulation and preserve passive beamforming.
+	To accommodate signal characteristics, UniScatter receiver semi-coherently decodes all nodes from accumulated energy, acquires equivalent primary channel over reflection pattern, then coherently decodes the primary link under enhanced multipath.
+	It reduces the complexity of cooperative decoding while preserves the benefit of backscatter modulation and passive beamforming.
+	Using shared spectrum, energy, and infrastructures, UniScatter is a more general and powerful transmit-assist protocol that generalizes \gls{bc}, \gls{ris} and \gls{sr} with universal hardware design and augmented \gls{qos} control.
+	% Using shared spectrum, energy, and infrastructures, each UniScatter node adapts probability distribution of reflection states based on \gls{csi} to balance information encoding and passive beamforming in a mutualistic and flexible manner.
+	% The scatter source of \gls{bc}/\gls{sr} and reflecting element of \gls{ris} can be viewed as extreme cases of UniScatter node, where the input distribution boils down to equiprobable and degenerate, respectively.
+	% To accommodate signal characteristics, we propose a practical receiver that semi-coherently decodes all nodes from accumulated energy, re-encodes to determine the equivalent channel, then decodes the primary link.
+	% It reduces the complexity of cooperative decoding while preserves the benefit of backscatter modulation and passive beamforming.
+	Moreover, we consider an application scenario where a multi-antenna \gls{ap} serves a single-antenna user surrounded by multiple UniScatter nodes, and characterize the achievable primary-(total-)backscatter rate region by designing input distribution at the nodes, active beamforming at the \gls{ap}, and backscatter decision design at the user.
+	Simulation results demonstrate UniScatter can flexibly control the transmit-assist tradeoff via smart input distribution design.
+
+	% reduces the complexity of cooperative decoding while preserves the benefit of passive beamforming.
+	% reduces the complexity of cooperative decoding while preserves the benefit of backscatter modulation and passive beamforming.
+
+	% In this paper, we argue that to efficiently cope with the high throughput, heterogeneity of quality of service (QoS), and massive connectivity requirements of future multi-antenna wireless networks, multiple access design needs to depart from those two extreme interference management strategies, namely fully treat interference as noise (as in SDMA) and fully decode interference (as in NOMA).
+Considering a multiple-input single-output broadcast channel, we develop a novel multiple access framework, called rate-splitting multiple access (RSMA).
+RSMA is a more general and more powerful multiple access for downlink multi-antenna systems that contains SDMA and NOMA as special cases.
+RSMA relies on linearly precoded rate-splitting with SIC to decode part of the interference and treat the remaining part of the interference as noise.
+This capability of RSMA to partially decode interference and partially treat interference as noise enables to softly bridge the two extremes of fully decoding interference and treating interference as noise and provides room for rate and QoS enhancements and complexity reduction.
+The three multiple access schemes are compared, and extensive numerical results show that RSMA provides a smooth transition between SDMA and NOMA and outperforms them both in a wide range of network loads (underloaded and overloaded regimes) and user deployments (with a diversity of channel directions, channel strengths, and qualities of channel state information at the transmitter).
+Moreover, RSMA provides rate and QoS enhancements over NOMA at a lower computational complexity for the transmit scheduler and the receivers (number of SIC layers).
 \end{abstract}
@@
 
+	% ! Φ(c[n]) vs P
 	\emph{First,} Metascatter adapts the input probability distribution of a finite-state passive backscatter device based on primary and (cascaded) backscatter \gls{csi} to unify and generalize parasitic source of \gls{sr} and reflecting elements of \gls{ris}.

### 2022-08-02 main.tex
:pencil: Update abstract

@@
 \begin{document}
-% \title{UniScatter: Unifying Backscatter Communication, Reconfigurable Intelligent Surface, and Symbiotic Radio}
-% \title{UniScatter:\\Unifying Backscatter Communication, Reconfigurable Intelligent Surface, and Symbiotic Radio}
 \title{UniScatter: Unifying\\Backscatter Communications, Reconfigurable Intelligent Surface, and Symbiotic Radio}
-% \title{UniScatter: Unifying Symbiotic Radio, Reconfigurable Intelligent Surface, and Wireless Sensor Network}
-% \title{UniScatter: Unifying Symbiotic Radio and Reconfigurable Intelligent Surface}
 \author{
@@
 \begin{abstract}
-	% First, we highlight why NOMA is inefficient in multi-antenna settings based on basic multiplexing gain analysis.
-We stress that the issue lies in how the NOMA literature, originally developed for single-antenna setups, has been hastily applied to multi-antenna setups, resulting in a misuse of spatial dimensions and therefore loss in multiplexing gains and rate.
-Second, we show that NOMA incurs a severe multiplexing gain loss despite an increased receiver complexity due to an inefficient use of SIC receivers.
-Third, we emphasize that much of the merits of NOMA are due to the constant comparison to OMA instead of comparing it to MU–LP and RS baselines.
-We then expose the pivotal design constraint that multi-antenna NOMA requires one user to fully decode the messages of the other users.
-This design constraint is responsible for the multiplexing gain erosion, rate and spectral efficiency loss, ineffectiveness to serve a large number of users, and inefficient use of SIC receivers in multi-antenna settings.
-Our analysis and simulation results confirm that NOMA should not be applied blindly to multi-antenna settings, highlight the scenarios where MU–LP outperforms NOMA and vice versa, and demonstrate the inefficiency, performance loss, and complexity disadvantages of NOMA compared to RSMA.
-The first takeaway message is that, while NOMA is suited for single-antenna settings (as originally intended), it is not efficient in most multi-antenna deployments.
-The second takeaway message is that another non-orthogonal transmission framework, based on RSMA, exists which fully exploits the multiplexing gain and the benefits of SIC to boost the rate and the number of users to serve in multi-antenna settings and outperforms both NOMA and MU–LP.
-Indeed, RSMA achieves higher multiplexing gains and rates, serves a larger number of users, is more robust to user deployments, network loads and inaccurate channel state information and has a lower receiver complexity than NOMA.
-Consequently, RSMA is a promising technology for NGMA and future networks such as 6G and beyond.
-
 	Scatterers can harvest energy from, modulate information over, and influence propagation of surrounding radio waves.
@@
 	\gls{sr} incorporates scatter nodes into active networks, which recycle ambient signal to transmit self information and enhance legacy multipath to the cooperative receiver.
-	% In this paper, we depart from those concepts and introduce UniScatter as a new paradigm to support the high throughput, ultralow power, and ubiquitous connectivity of future wireless networks using shared spectrum, energy, and infrastructures.
-	In this paper, we depart from those concepts and introduce UniScatter as a new paradigm to support the high throughput, ultralow power, and ubiquitous connectivity of future wireless networks.
-	Instead of treating probability distribution of reflection states as equiprobable (as scattering source of \gls{bc}/\gls{sr}) or degenerate (as reflecting element of \gls{ris}), UniScatter node adapts input distribution based on \gls{csi} and link priority to balance information encoding and channel reconfiguration in a mutualistic and flexible manner.
-	% Accommodated to signal characteristics, UniScatter receiver semi-coherently decodes all nodes from accumulated energy, re-encodes to determine the equivalent channel, then decodes the primary link to support backscatter modulation and preserve passive beamforming.
-	% Accommodated to signal characteristics, UniScatter receiver semi-coherently decodes all nodes from accumulated energy, combines reflection pattern with \gls{csi} for the equivalent channel, then decodes the primary link to support backscatter modulation and preserve passive beamforming.
+	In this paper, we depart from those concepts and introduce UniScatter as a new paradigm for future wireless networks.
+	Instead of treating probability distribution of reflection states as equiprobable (as scattering source of \gls{bc}/\gls{sr}) or degenerate (as reflecting element of \gls{ris}), UniScatter node adapts input distribution of a passive device based on \gls{csi} and link priority, which balances information encoding and channel reconfiguration in a mutualistic and flexible manner.
 	To accommodate signal characteristics, UniScatter receiver semi-coherently decodes all nodes from accumulated energy, acquires equivalent primary channel over reflection pattern, then coherently decodes the primary link under enhanced multipath.
-	It reduces the complexity of cooperative decoding while preserves the benefit of backscatter modulation and passive beamforming.
+	It reduces the complexity of cooperative decoding while preserves the benefits of backscatter modulation and passive beamforming.
 	Using shared spectrum, energy, and infrastructures, UniScatter is a more general and powerful transmit-assist protocol that generalizes \gls{bc}, \gls{ris} and \gls{sr} with universal hardware design and augmented \gls{qos} control.
-	% Using shared spectrum, energy, and infrastructures, each UniScatter node adapts probability distribution of reflection states based on \gls{csi} to balance information encoding and passive beamforming in a mutualistic and flexible manner.
-	% The scatter source of \gls{bc}/\gls{sr} and reflecting element of \gls{ris} can be viewed as extreme cases of UniScatter node, where the input distribution boils down to equiprobable and degenerate, respectively.
-	% To accommodate signal characteristics, we propose a practical receiver that semi-coherently decodes all nodes from accumulated energy, re-encodes to determine the equivalent channel, then decodes the primary link.
-	% It reduces the complexity of cooperative decoding while preserves the benefit of backscatter modulation and passive beamforming.
-	Moreover, we consider an application scenario where a multi-antenna \gls{ap} serves a single-antenna user surrounded by multiple UniScatter nodes, and characterize the achievable primary-(total-)backscatter rate region by designing input distribution at the nodes, active beamforming at the \gls{ap}, and backscatter decision design at the user.
-	Simulation results demonstrate UniScatter can flexibly control the transmit-assist tradeoff via smart input distribution design.
-
-	% reduces the complexity of cooperative decoding while preserves the benefit of passive beamforming.
-	% reduces the complexity of cooperative decoding while preserves the benefit of backscatter modulation and passive beamforming.
-
-	% In this paper, we argue that to efficiently cope with the high throughput, heterogeneity of quality of service (QoS), and massive connectivity requirements of future multi-antenna wireless networks, multiple access design needs to depart from those two extreme interference management strategies, namely fully treat interference as noise (as in SDMA) and fully decode interference (as in NOMA).
-Considering a multiple-input single-output broadcast channel, we develop a novel multiple access framework, called rate-splitting multiple access (RSMA).
-RSMA is a more general and more powerful multiple access for downlink multi-antenna systems that contains SDMA and NOMA as special cases.
-RSMA relies on linearly precoded rate-splitting with SIC to decode part of the interference and treat the remaining part of the interference as noise.
-This capability of RSMA to partially decode interference and partially treat interference as noise enables to softly bridge the two extremes of fully decoding interference and treating interference as noise and provides room for rate and QoS enhancements and complexity reduction.
-The three multiple access schemes are compared, and extensive numerical results show that RSMA provides a smooth transition between SDMA and NOMA and outperforms them both in a wide range of network loads (underloaded and overloaded regimes) and user deployments (with a diversity of channel directions, channel strengths, and qualities of channel state information at the transmitter).
-Moreover, RSMA provides rate and QoS enhancements over NOMA at a lower computational complexity for the transmit scheduler and the receivers (number of SIC layers).
+	We consider an application scenario where a multi-antenna \gls{ap} serves a single-antenna user surrounded by multiple UniScatter nodes, and characterize the achievable primary-(total-)backscatter rate region by designing input distribution at the nodes, active beamforming at the \gls{ap}, and backscatter decision design at the user.
+	Simulation results demonstrate UniScatter nodes can flexibly control the transmit-assist tradeoff via smart input distribution design.
 \end{abstract}
 
+\glsresetall
+
 \begin{section}{Introduction}
-	\IEEEPARstart{B}{ackscatter} is recently re-innovated as a promising approach to support low-power communications and control wireless propagation environments.
+	% TODO You need to explain the key principle and benefits of backscatter, then symbiotic radio, then RIS.
+Then you need to explain about the apparent differences and similarities between those techniques.
+Then metascatter concept will appear.
+	% The evolution of wireless communications
+	% \IEEEPARstart{I}{nternet-of-Everything} is envisioned to provide high throughput, ultralow power, ubiquitous distribution, and connected intelligence for future wireless networks.
+	\IEEEPARstart{F}{uture} wireless network is envisioned to provide high throughput, ultralow power, ubiquitous deployment, and connected intelligence for trillions of portable devices.
+	% \gls{bc} is an emerging technique that allows low-power devices to transmit without power-hungry \gls{rf} components.
+	% An emerging technique for low-power communication is \gls{bc}, which allows backscatter node to embed its own message over
+	% An emerging technique for low-power communication is \gls{bc}, which allows information node to embed its own message over
+	% transmit without active \gls{rf} components
+	% \gls{bc} is an emerging technique that allows information nodes to alter scattered electromagnetic field and transmit without onboard \gls{rf} components (e.g., carrier syntheizer and power amplifier).
+	% \gls{bc} is an emerging technique that allows information nodes to operate over surrounding carrier wave and transmit without onboard \gls{rf} components.
+	\gls{bc} is an emerging technique that allows backscatter nodes to operate over dedicated carrier signal without onboard \gls{rf} components (e.g., carrier syntheizer and power amplifier).
+	The low-power nodes harvest energy from incident wave and modulate information over scattered signal.
+
+	% alter scattered electromagnetic field and transmit without onboard \gls{rf} components (e.g., carrier syntheizer and power amplifier).
+	% Passive backscatter nodes harvest energy from surrounding \gls{rf} waves
+
+	% The evolution in the field of wireless communications requires not only futuristic technologies but also, a change of mindset about how different technologies interact with each other like a well-oiled machine.
+In this backdrop, the deployment of massive Internet of things (IoT) networks poses significant challenges.
+While there have been numerous technologies proposed to improve the performance of such low-powered IoT networks, the current state of the art is still not mature enough to deploy commercial and large-scale networks.
+Rapid energy consumption along with miniature size of energy reservoirs naturally becomes an obstacle as these IoT devices are likely to be untethered when operating.
+Fortunately, recent research efforts have shown that radio backscatter communication can effectively offer near-zero-power (less than 1mW) connectivity to small devices.
+In this regard, this book explores the performance evaluation and optimization aspects of backscatter devices in outdoor and indoor environments, where it is not possible to set up a dedicated nearby transmitter.
+The book also sheds light on different cooperation techniques for backscatter communications.
+These techniques help analyze the reliability-energy trade-off for backscatter devices.
+Also, there are in-depth dis- cussions and recent studies on a variety of emerging wireless topics such as physical-layer security, non-orthogonal multiple access (NOMA), age of informa- tion, and multi-tone carrier techniques.
+
+	% \IEEEPARstart{S}{catterers} can harvest energy from, modulate information over, and influence propagation of surrounding radio waves.
+	% \IEEEPARstart{B}{ackscatter} is recently re-innovated as a promising approach to support low-power communications and control wireless propagation environments.
 	% \IEEEPARstart{B}{ackscatter} is re-innovated to support low-power communications and control wireless propagation environments.
-	% \IEEEPARstart{B}{ackscatter} allows wireless nodes to recycle existing .
-	% \IEEEPARstart{B}{ackscatter} allows wireless nodes to communicate without generating carrier.
-	% The concept of \gls{ambc} was first proposed in \cite{Liu2013b}, where battery-free communication between passive nodes was established by
 	\gls{ambc} that enables battery-free communication between interactive nodes was first introduced and prototyped in \cite{Liu2013b}, where devices harvest energy from and modulate information over ambient \gls{rf} signals by switching between reflecting and absorbing states.

### 2022-08-02 main.tex
:pencil: Update introduction

@@
 	% \IEEEPARstart{I}{nternet-of-Everything} is envisioned to provide high throughput, ultralow power, ubiquitous distribution, and connected intelligence for future wireless networks.
-	\IEEEPARstart{F}{uture} wireless network is envisioned to provide high throughput, ultralow power, ubiquitous deployment, and connected intelligence for trillions of portable devices.
-	% \gls{bc} is an emerging technique that allows low-power devices to transmit without power-hungry \gls{rf} components.
-	% An emerging technique for low-power communication is \gls{bc}, which allows backscatter node to embed its own message over
-	% An emerging technique for low-power communication is \gls{bc}, which allows information node to embed its own message over
-	% transmit without active \gls{rf} components
-	% \gls{bc} is an emerging technique that allows information nodes to alter scattered electromagnetic field and transmit without onboard \gls{rf} components (e.g., carrier syntheizer and power amplifier).
-	% \gls{bc} is an emerging technique that allows information nodes to operate over surrounding carrier wave and transmit without onboard \gls{rf} components.
-	\gls{bc} is an emerging technique that allows backscatter nodes to operate over dedicated carrier signal without onboard \gls{rf} components (e.g., carrier syntheizer and power amplifier).
-	The low-power nodes harvest energy from incident wave and modulate information over scattered signal.
+	% \IEEEPARstart{F}{uture} wireless network is envisioned to provide high throughput, uniform coverage, massive connectivity and heterogeneous control for trillions of portable devices with ultralow power consumption.
+	\IEEEPARstart{F}{uture} wireless network is envisioned to provide high throughput, uniform coverage, pervasive connectivity, heterogeneous control, and cognitive intelligence for trillions of portable devices.
+	% \gls{bc} is an emerging technique
+	% that enables low-power communication by separating the
+	% As an emerging low-power communication technique, \gls{bc} separates the power-hungry \gls{rf} components (i.e., synthesizer and amplifier) as dedicated carrier emitter, and employs passive energy harvester and impedance modulator to operate over incident and scattered signals.
+	% As an emerging low-power communication technique, \gls{bc} separates the power-hungry \gls{rf} components (i.e., synthesizer and amplifier) as dedicated carrier emitter, and equips the backscatter node with energy harvester and load-switching modulator to operate over incident and scattered signals, respectively.
+	As an emerging low-power communication technique, \gls{bc} separates the power-hungry \gls{rf} elements (e.g., synthesizer and amplifier) as dedicated carrier emitter, and leaves the passive components (e.g., harvester and modulator) at the backscatter node.
+	The node harvests energy from emitted \gls{rf} wave and embeds its information over scattered signal.
 

### 2022-08-02 main.tex
:pencil: Update introduction

@@
 \newacronym{iid}{i.i.d.}{independent and identically distributed}
+\newacronym{ioe}{IoE}{Internet of Everything}
+\newacronym{iot}{IoT}{Internet of Things}
 \newacronym{kkt}{KKT}{Karush-Kuhn-Tucker}
+\newacronym{m2m}{M2M}{Machine to Machine}
 \newacronym{mac}{MAC}{Multiple Access Channel}
@@
 \newacronym{rf}{RF}{Radio-Frequency}
+\newacronym{rfid}{RFID}{Radio-Frequency Identification}
 \newacronym{ris}{RIS}{Reconfigurable Intelligent Surface}
@@
 	\gls{ris} adapts scattering antennas or programmable metamaterial to control propagation environment and boost/suppress signal strength in specific directions.
-	\gls{sr} incorporates scatter nodes into active networks, which recycle ambient signal to transmit self information and enhance legacy multipath to the cooperative receiver.
+	\gls{sr} incorporates scatter nodes into active networks that recycle ambient signal to transmit self information and enhance legacy channel to the cooperative receiver.
 	In this paper, we depart from those concepts and introduce UniScatter as a new paradigm for future wireless networks.
-	Instead of treating probability distribution of reflection states as equiprobable (as scattering source of \gls{bc}/\gls{sr}) or degenerate (as reflecting element of \gls{ris}), UniScatter node adapts input distribution of a passive device based on \gls{csi} and link priority, which balances information encoding and channel reconfiguration in a mutualistic and flexible manner.
+	Instead of treating probability distribution of reflection states as equiprobable (as scattering source of \gls{bc}/\gls{sr}) or degenerate (as reflecting element of \gls{ris}), UniScatter node adapts input distribution of a passive scatter node based on link priority and \gls{csi}, which balances information encoding and channel reconfiguration in a flexible and mutualistic manner.
 	To accommodate signal characteristics, UniScatter receiver semi-coherently decodes all nodes from accumulated energy, acquires equivalent primary channel over reflection pattern, then coherently decodes the primary link under enhanced multipath.
@@
 	% As an emerging low-power communication technique, \gls{bc} separates the power-hungry \gls{rf} components (i.e., synthesizer and amplifier) as dedicated carrier emitter, and equips the backscatter node with energy harvester and load-switching modulator to operate over incident and scattered signals, respectively.
-	As an emerging low-power communication technique, \gls{bc} separates the power-hungry \gls{rf} elements (e.g., synthesizer and amplifier) as dedicated carrier emitter, and leaves the passive components (e.g., harvester and modulator) at the backscatter node.
-	The node harvests energy from emitted \gls{rf} wave and embeds its information over scattered signal.
+	% As an emerging low-power communication protocol, \gls{bc} divides transmitter into a dedicated carrier emitter with power-hungry \gls{rf} elements (e.g., synthesizer and amplifier) and an information-bearing node with passive components (e.g., harvester and modulator).
+	As an emerging low-power communication protocol, \gls{bc} divides transmitter into a \gls{rf} signal emitter with power-hungry elements (e.g., synthesizer and amplifier) and an information-bearing scatter node with passive components (e.g., harvester and modulator).
+	% \gls{bc} is an emerging low-power communication protocol that divides transmitter into a \gls{rf} signal emitter with power-hungry elements (e.g., synthesizer and amplifier) and an information-bearing scatter node with passive components (e.g., harvester and modulator).
+	% The node harvests energy from emitted \gls{rf} wave and embeds its information over scattered signal in a sustainable and controllable manner, bringing more possibilities to \gls{ioe} and \gls{m2m} networks.
+	% The node harvests energy from emitted \gls{rf} wave and embeds its information over scattered signal in a sustainable and controllable manner, which is widely applied in \gls{ioe} and \gls{m2m} networks.
+	The node harvests energy from emitted \gls{rf} wave and embeds its information over scattered signal in a sustainable and controllable manner.
+	% Dated back to early 1970's,
+	% \gls{rfid}, as a main application of \gls{bc}, has experienced great success
+	\gls{rfid}, as a main application of \gls{bc}, has been extensively developed and commonly employed even before the era of \gls{iot} and \gls{m2m}.
+	% It requires a dedicated sinusoidal source
+	Specifically, a dedicated emitter generates a sinusoidal carrier at reserved frequency, and \gls{rfid} tags reports their identifier to a nearby \gls{rfid} reader.
+	% Specifically, a dedicated emitter generates sinusoidal carrier at reserved frequency, and the node reports its identifier to a nearby \gls{rfid} reader.
+
+	% Recently, RFID has experienced a tremendous growth due to developments in integrated circuits and radios, and due to increased interest from retail industry and government [4].
+
+	% ? With the upsurge of wireless devices and the downtrend of circuit power consumption, \gls{rfid} has experienced great success in \gls{ioe} and \gls{m2m} networks.
+	% Since the node harvests energy from emitted \gls{rf} wave and embeds its information over scattered signal, such that
+	% The rapid growth of wireless devices and the steady decrease of electronic power consumption
+
+	% account for the
+	% Although \gls{bc} experienced
+
+	% the power-hungry \gls{rf} elements (e.g., synthesizer and amplifier) as dedicated carrier emitter, and leaves the passive components (e.g., harvester and modulator) at the backscatter node.
+	% The node harvests energy from emitted \gls{rf} wave and embeds its information over scattered signal.
 

### 2022-08-03 main.tex
:pencil: Update introduction

--- 2022-08-02 main.tex
@@
 \begin{document}
-\title{UniScatter: Unifying\\Backscatter Communications, Reconfigurable Intelligent Surface, and Symbiotic Radio}
+% \title{UniScatter: Unifying\\Backscatter Communications, Reconfigurable Intelligent Surface, and Symbiotic Radio}
+\title{UniScatter: Unifying\\Backscatter Communications, Symbiotic Radio, and Reconfigurable Intelligent Surface}
 \author{
@@
 Then metascatter concept will appear.
-	% The evolution of wireless communications
-	% \IEEEPARstart{I}{nternet-of-Everything} is envisioned to provide high throughput, ultralow power, ubiquitous distribution, and connected intelligence for future wireless networks.
-	% \IEEEPARstart{F}{uture} wireless network is envisioned to provide high throughput, uniform coverage, massive connectivity and heterogeneous control for trillions of portable devices with ultralow power consumption.
 	\IEEEPARstart{F}{uture} wireless network is envisioned to provide high throughput, uniform coverage, pervasive connectivity, heterogeneous control, and cognitive intelligence for trillions of portable devices.
-	% \gls{bc} is an emerging technique
-	% that enables low-power communication by separating the
-	% As an emerging low-power communication technique, \gls{bc} separates the power-hungry \gls{rf} components (i.e., synthesizer and amplifier) as dedicated carrier emitter, and employs passive energy harvester and impedance modulator to operate over incident and scattered signals.
-	% As an emerging low-power communication technique, \gls{bc} separates the power-hungry \gls{rf} components (i.e., synthesizer and amplifier) as dedicated carrier emitter, and equips the backscatter node with energy harvester and load-switching modulator to operate over incident and scattered signals, respectively.
-	As an emerging low-power communication technique, \gls{bc} separates the power-hungry \gls{rf} elements (e.g., synthesizer and amplifier) as dedicated carrier emitter, and leaves the passive components (e.g., harvester and modulator) at the backscatter node.
-	The node harvests energy from emitted \gls{rf} wave and embeds its information over scattered signal.
-
-	% alter scattered electromagnetic field and transmit without onboard \gls{rf} components (e.g., carrier syntheizer and power amplifier).
-	% Passive backscatter nodes harvest energy from surrounding \gls{rf} waves
-
-	% The evolution in the field of wireless communications requires not only futuristic technologies but also, a change of mindset about how different technologies interact with each other like a well-oiled machine.
-In this backdrop, the deployment of massive Internet of things (IoT) networks poses significant challenges.
-While there have been numerous technologies proposed to improve the performance of such low-powered IoT networks, the current state of the art is still not mature enough to deploy commercial and large-scale networks.
-Rapid energy consumption along with miniature size of energy reservoirs naturally becomes an obstacle as these IoT devices are likely to be untethered when operating.
-Fortunately, recent research efforts have shown that radio backscatter communication can effectively offer near-zero-power (less than 1mW) connectivity to small devices.
-In this regard, this book explores the performance evaluation and optimization aspects of backscatter devices in outdoor and indoor environments, where it is not possible to set up a dedicated nearby transmitter.
-The book also sheds light on different cooperation techniques for backscatter communications.
-These techniques help analyze the reliability-energy trade-off for backscatter devices.
-Also, there are in-depth dis- cussions and recent studies on a variety of emerging wireless topics such as physical-layer security, non-orthogonal multiple access (NOMA), age of informa- tion, and multi-tone carrier techniques.
-
-	% \IEEEPARstart{S}{catterers} can harvest energy from, modulate information over, and influence propagation of surrounding radio waves.
-	% \IEEEPARstart{B}{ackscatter} is recently re-innovated as a promising approach to support low-power communications and control wireless propagation environments.
-	% \IEEEPARstart{B}{ackscatter} is re-innovated to support low-power communications and control wireless propagation environments.
-	\gls{ambc} that enables battery-free communication between interactive nodes was first introduced and prototyped in \cite{Liu2013b}, where devices harvest energy from and modulate information over ambient \gls{rf} signals by switching between reflecting and absorbing states.
-	To combat the strong direct-link interference of \gls{ambc}, \cite{Yang2018d} exploited the repeating structure of \gls{ofdm} symbol and proposed a multi-antenna detector that only requires the backscatter channel strength.
-	% with periodical change of states.
-	% each tag harvests energy from and modulates information over ambient \gls{rf} signals by periodically switching between different reflection patterns.
-	% It enables battery-free communication between fully passive nodes, but the backscatter signal strength can be relatively weak and the decoding is subject to strong direct-link interference.
-	% To solve this, \cite{Yang2018d} exploited the repeating structure of \gls{ofdm} symbol for interference cancellation based on backscatter channel strength.
-	% Using co-located receiver to decode
-	Cooperative \gls{ambc} that decodes primary and backscatter links using co-located receiver was proposed in \cite{Yang2018}, where the authors evaluated the error performance of \gls{ml}, linear, and \gls{sic} detectors for flat fading channels and proposed a low-complexity \gls{ml} detector for frequency-selective fading channels.
-	The concept was then generalized to \gls{sr} in \cite{Liang2020} to ``exploit the benefits and address the drawbacks'' of \gls{cr} and \gls{ambc}.
-	% The concept of \gls{sr} was then proposed in \cite{Liang2020} to exploit
-	% symbiotic radio (SR), is proposed to ex- ploit the benefits and address the drawbacks of cognitive radio (CR) and ambient backscattering communications (AmBC)
-	% When transmit cooperation is also available, cooperative \gls{ambc} is also termed as \gls{sr} \cite{Liang2020}.
-	The authors of \cite{Guo2019b} classified \gls{sr} into commensal, parasitic, and competitive types based on link priority, and derived their instantaneous rates and optimal power allocations.
-	The corresponding outage probabilities were also studied in \cite{Ding2020}.
-	Besides, \cite{Long2020a} concluded that if the backscatter symbol period is sufficiently long, then the non-coherent primary rate would approach its coherent counterpart.
-	The authors thus proposed to decode the primary link under backscatter uncertainty, then perform \gls{sic} and decode the backscatter link.
+	As an emerging low-power communication technique, \gls{bc} separates conventional transmitter into a \gls{rf} emitter with power-hungry elements (e.g., synthesizer and amplifier), and an information-bearing node with power-efficient components (e.g., harvester and modulator) \cite{Boyer2014}.
+	The node harvests energy from incident wave and embeds information over scattered signal in a sustainable and controllable manner.
+	Termed as monostatic and bistatic, the backscatter reader can be either co-located or separated with the emitter.
+	\gls{bc} applications such as \gls{rfid} \cite{Dobkin2012,Landt2005} and sensor networks \cite{Vannucci2008,Assimonis2016} have been extensively researched, standardized, and commercialized to support \gls{iot} and \gls{m2m}.
+	% Specifically, a dedicated emitter generates a sinusoidal carrier at reserved frequency, and \gls{rfid} tags reports their identifier to a nearby \gls{rfid} reader.
+	% ? With the upsurge of wireless devices and the downtrend of circuit power consumption, \gls{rfid} has experienced great success in \gls{ioe} and \gls{m2m} networks.
+	However, traditional \gls{bc} requires dedicated carrier emitter and backscatter reader, while passive nodes only respond when externally inquired.
+	% In \gls{ambc} \cite{Liu2013b}, ambient signals (e.g., radio, television, and Wi-Fi) are recycled by interactive nodes to harvest energy and establish connection.
+	In \gls{ambc} \cite{Liu2013b}, interactive nodes recycle ambient signals generated by legacy transmitters (e.g., radio, television, and Wi-Fi) to harvest energy and establish connection.
+	% ambient signals (e.g., radio, television, and Wi-Fi) are recycled by interactive nodes to harvest energy and establish connection.
+	% It not only eliminates the need of power source and carrier emitter, but also avoid the cost of dedicated frequency spectrum.
+	It eliminates the need of dedicated power source, carrier emitter, and frequency spectrum, bringing more possibilities to low-power communications.
+	To combat the strong direct-link interference of \gls{ambc}, \cite{Yang2018} proposed a co-located receiver that cooperatively decodes both primary (legacy) and backscatter links.
+	The authors evaluated the error performance of \gls{ml}, linear, and \gls{sic} detectors for flat fading channel, and proposed a low-complexity detector for frequency-selective fading channel.
+	The concept of cooperative \gls{ambc} was then refined as \gls{sr} to cognitively incorporate \gls{ambc} with existing systems \cite{Liang2020}.
+	In \gls{sr}, the primary transmitter generates active radio carrying primary information, the scatter node modulates re-radiated component using secondary information, and the cooperative receiver decodes both links from two propagation paths.
+	The direct transmitter-receiver path contains only primary information, while the cascaded transmitter-node-receiver path preserves primary and backscatter information.
+	Such a coexistence was further classified into commensal, parasitic, and competitive relationships based on link priority \cite{Guo2019b}, and their instantaneous rates, optimal power allocations, and outage probabilities were subsequently derived in \cite{Guo2019b,Ding2020}.
+	However, one important issue of \gls{sr} is the practical cooperative receiver design.
+	Ideal joint \gls{ml} decoding achieves optimal performance with prohibitive computational complexity \cite{Yang2018,Zhang2022}.
+	% In contrast, sequential decoding is subject to uncertainty/interference at the first layer \cite{Ding2020,Long2020a,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Yang2018,Han2021,Zhang2022,Xu2020b,Hua2022}.
+	% Due to the physical constraint at the load-switching modulator, backscatter symbol duration can be much longer than primary.
+	Due to physical constraints at the load-switching modulator, backscatter symbol period is typically longer than primary symbol period.
+	% \cite{Long2020a} indicated if backscatter symbol is sufficiently long, its randomness can be modelled as channel uncertainty, and primary
+	% \cite{Long2020a} pointed out if backscatter symbol is sufficiently long, its randomness can be modelled as channel uncertainty, and
+	% \cite{Long2020a} pointed out when decoding the primary link first, the randomness of backscatter modulation can be modelled as channel uncertainty.
+	For sequential decoding from primary to backscatter, \cite{Long2020a} pointed out the randomness from backscatter modulation can be modelled as interference or channel uncertainty, depending on symbol period ratio.
+	The authors concluded if backscatter symbol period is sufficiently long, the non-coherent primary rate would approach its coherent counterpart.
+	This motivated \cite{Long2020a} and \cite{Ding2020,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Yang2018,Han2021,Zhang2022,Xu2020b,Hua2022} to decode the primary link, perform \gls{sic}, then decode the backscatter link.
+
+	% Besides, \cite{Long2020a} concluded if the backscatter symbol period is sufficiently long, then the non-coherent primary rate would approach its coherent counterpart.
+	% The authors thus proposed to decode the primary link under backscatter uncertainty, then perform \gls{sic} and decode the backscatter link.
 	% The authors also considered the transmit precoder design for weighted total-rate maximization and transmit power minimization problems.

### 2022-08-03 main.tex
:pencil: Update introduction

@@
 	This motivated \cite{Long2020a} and \cite{Ding2020,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Yang2018,Han2021,Zhang2022,Xu2020b,Hua2022} to decode the primary link, perform \gls{sic}, then decode the backscatter link.
+	% However, the advantage of this particular scheme is questionable because 1) it does not fully exploit backscatter pattern and signal characteristics; 2) it requires non-coherent encoding at the primary transmitter, and re-encoding, precoding, and subtraction at the receiver; 3) the primary and backscatter symbols are mixed by multiplication instead of superposition.
+	However, the advantage of this particular scheme is questionable because 1) it does not fully exploit backscatter pattern and signal characteristics; 2) non-coherent primary encoding is required at the transmitter while re-encoding, precoding, and subtraction are required at the receiver; 3) the primary and backscatter symbols are mixed by multiplication instead of superposition.
+
+	% This receiving scheme, as would be discussed later, may not fully
 

### 2022-08-04 main.tex
:pencil: Update introduction

--- 2022-08-03 main.tex
@@
 \newacronym{dp}{DP}{Dynamic Programming}
+\newacronym{fdma}{FDMA}{Frequency-Division Multiple Access}
 \newacronym{iid}{i.i.d.}{independent and identically distributed}
@@
 	\gls{bc} varies object impedance to manipulate the magnitude, phase, and/or frequency of scattered signal to encode information and deliver within coverage.
-	\gls{ris} adapts scattering antennas or programmable metamaterial to control propagation environment and boost/suppress signal strength in specific directions.
+	\gls{ris} adapts scattering antennas or programmable metamaterial to control propagation environment by boosting/suppressing signal strength in specific directions.
 	\gls{sr} incorporates scatter nodes into active networks that recycle ambient signal to transmit self information and enhance legacy channel to the cooperative receiver.
 	In this paper, we depart from those concepts and introduce UniScatter as a new paradigm for future wireless networks.
-	Instead of treating probability distribution of reflection states as equiprobable (as scattering source of \gls{bc}/\gls{sr}) or degenerate (as reflecting element of \gls{ris}), UniScatter node adapts input distribution of a passive scatter node based on link priority and \gls{csi}, which balances information encoding and channel reconfiguration in a flexible and mutualistic manner.
+	Instead of treating probability distribution of reflection states as equiprobable (as scattering source of \gls{bc}/\gls{sr}) or degenerate (as reflecting element of \gls{ris}), UniScatter node adapts input distribution of a passive scatter node based on link priority and \gls{csi}, balancing information encoding and channel reconfiguration in a flexible and mutualistic manner.
 	To accommodate signal characteristics, UniScatter receiver semi-coherently decodes all nodes from accumulated energy, acquires equivalent primary channel over reflection pattern, then coherently decodes the primary link under enhanced multipath.
@@
 	The node harvests energy from incident wave and embeds information over scattered signal in a sustainable and controllable manner.
-	Termed as monostatic and bistatic, the backscatter reader can be either co-located or separated with the emitter.
-	\gls{bc} applications such as \gls{rfid} \cite{Dobkin2012,Landt2005} and sensor networks \cite{Vannucci2008,Assimonis2016} have been extensively researched, standardized, and commercialized to support \gls{iot} and \gls{m2m}.
+	The backscatter reader can be either co-located or separated with the emitter, known as monostatic and bistatic \gls{bc}.
+	Its applications such as \gls{rfid} \cite{Dobkin2012,Landt2005} and sensor networks \cite{Vannucci2008,Assimonis2016} have been extensively researched, standardized, and commercialized to support \gls{iot} and \gls{m2m}.
 	% Specifically, a dedicated emitter generates a sinusoidal carrier at reserved frequency, and \gls{rfid} tags reports their identifier to a nearby \gls{rfid} reader.
@@
 	% It not only eliminates the need of power source and carrier emitter, but also avoid the cost of dedicated frequency spectrum.
-	It eliminates the need of dedicated power source, carrier emitter, and frequency spectrum, bringing more possibilities to low-power communications.
-	To combat the strong direct-link interference of \gls{ambc}, \cite{Yang2018} proposed a co-located receiver that cooperatively decodes both primary (legacy) and backscatter links.
+	It eliminates the need of dedicated power source, carrier emitter, and frequency spectrum, bringing more opportunities to low-power communications.
+	To combat the strong direct-link interference of \gls{ambc}, \cite{Yang2018} proposed a co-located receiver that cooperatively decodes the primary (legacy) and backscatter links.
 	The authors evaluated the error performance of \gls{ml}, linear, and \gls{sic} detectors for flat fading channel, and proposed a low-complexity detector for frequency-selective fading channel.
 	The concept of cooperative \gls{ambc} was then refined as \gls{sr} to cognitively incorporate \gls{ambc} with existing systems \cite{Liang2020}.
-	In \gls{sr}, the primary transmitter generates active radio carrying primary information, the scatter node modulates re-radiated component using secondary information, and the cooperative receiver decodes both links from two propagation paths.
-	The direct transmitter-receiver path contains only primary information, while the cascaded transmitter-node-receiver path preserves primary and backscatter information.
+	In \gls{sr}, the primary transmitter generates active radio carrying primary information, the secondary node modulates scattered component with backscatter information, and the cooperative receiver decodes both links from two propagation paths.
+	The direct transmitter-receiver path only contains primary information, while the cascaded transmitter-node-receiver path preserves both information due to backscatter principles.
 	Such a coexistence was further classified into commensal, parasitic, and competitive relationships based on link priority \cite{Guo2019b}, and their instantaneous rates, optimal power allocations, and outage probabilities were subsequently derived in \cite{Guo2019b,Ding2020}.
-	However, one important issue of \gls{sr} is the practical cooperative receiver design.
+	However, one important issue of \gls{sr} is practical cooperative receiver design.
 	Ideal joint \gls{ml} decoding achieves optimal performance with prohibitive computational complexity \cite{Yang2018,Zhang2022}.
-	% In contrast, sequential decoding is subject to uncertainty/interference at the first layer \cite{Ding2020,Long2020a,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Yang2018,Han2021,Zhang2022,Xu2020b,Hua2022}.
-	% Due to the physical constraint at the load-switching modulator, backscatter symbol duration can be much longer than primary.
-	Due to physical constraints at the load-switching modulator, backscatter symbol period is typically longer than primary symbol period.
-	% \cite{Long2020a} indicated if backscatter symbol is sufficiently long, its randomness can be modelled as channel uncertainty, and primary
-	% \cite{Long2020a} pointed out if backscatter symbol is sufficiently long, its randomness can be modelled as channel uncertainty, and
-	% \cite{Long2020a} pointed out when decoding the primary link first, the randomness of backscatter modulation can be modelled as channel uncertainty.
-	For sequential decoding from primary to backscatter, \cite{Long2020a} pointed out the randomness from backscatter modulation can be modelled as interference or channel uncertainty, depending on symbol period ratio.
-	The authors concluded if backscatter symbol period is sufficiently long, the non-coherent primary rate would approach its coherent counterpart.
-	This motivated \cite{Long2020a} and \cite{Ding2020,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Yang2018,Han2021,Zhang2022,Xu2020b,Hua2022} to decode the primary link, perform \gls{sic}, then decode the backscatter link.
-
-	% Besides, \cite{Long2020a} concluded if the backscatter symbol period is sufficiently long, then the non-coherent primary rate would approach its coherent counterpart.
-	% The authors thus proposed to decode the primary link under backscatter uncertainty, then perform \gls{sic} and decode the backscatter link.
-	% The authors also considered the transmit precoder design for weighted total-rate maximization and transmit power minimization problems.
-	% \cite{Zhou2019a} explored how the number of transmit antennas, receive antennas, and symbol period ratio asymptotically influence the ergodic rate of primary and backscatter links.
-	% For \gls{sr} with a single-antenna backscatter node,
-	\cite{Zhou2019a} also explored the asymptotic impact of transmit/receive antenna and backscatter symbol period on the ergodic rate of primary and backscatter links.
-	% When multi-antenna is available at the node, \cite{Wu2021a} proposed
-	For a \gls{mimo} \gls{sr} system with a multi-antenna backscatter node, \cite{Wu2021a} proposed a beamforming design to maximize the backscatter rate while guaranteeing the primary performance.
-	% For multi-antenna at all ends, \cite{Wu2021a} optimized transmit beamforming to maximize the backscatter achievable rate under primary rate constraint.
-	% For multi-antenna at all ends, \cite{Wu2021a} optimized transmit beamforming to maximize the backscatter achievable rate under primary rate constraint.
-	% For multi-antenna at all ends, \cite{Wu2021a} optimized transmit beamforming to enlarge the achievable rate region.
-	However, those paper only considered one backscatter node and backscatter multiple access remains an open issue.
-	In \cite{Xu2021a}, a \gls{noma}-based \gls{sr} was proposed and receive combining was investigated when \gls{sic} order follows equivalent channel strength.
-	% \cite{Xu2021a} proposed a \gls{noma}-based \gls{sr} and investigated receive beamforming when \gls{sic} order is determined by equivalent channel strength.
-	% \cite{Xu2021a} proposed a \gls{noma}-based \gls{sr} and studied the receive combiner design when the receiver decodes in the order of equivalent channel strength.
-	% A \gls{tdma}-based \gls{sr} with energy harvesting constraints was also presented in \cite{Yang2021a}, and energy efficiency maximization was considered with respect to transmit power, reflection efficiency, and time allocation design.
-	A \gls{tdma}-based \gls{sr} with energy harvesting constraints was also presented in \cite{Yang2021a}, where transmit power, reflection efficiency, and time allocation were jointly optimized to maximize energy efficiency.
-	% In \cite{Han2021}, random code-assisted backscatter multiple access was combined with \gls{sr}, and the authors evaluated the asymptotic \gls{sinr} performance using random matrix theory.
+	Due to physical constraints at the load-switching modulator, backscatter symbol period is typically longer than primary.
+	For sequential decoding from primary to backscatter, \cite{Long2020a} pointed out the randomness from backscatter modulation can be modelled as either interference or channel uncertainty, depending on symbol period ratio.
+	The authors concluded if this ratio is sufficiently long, the non-coherent primary rate would asymptotically approach its coherent counterpart.
+	This motivated \cite{Long2020a,Ding2020,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Yang2018,Han2021,Zhang2022,Xu2020b,Hua2022} to decode the primary link, perform \gls{sic}, then decode the backscatter link.
+	However, the advantage of \gls{sic} is questionable because 1) backscatter pattern and signal characteristics are not fully exploited; 2) non-coherent primary encoding is required at the transmitter while re-encoding, precoding, and subtraction are required at the receiver; 3) primary and backscatter symbols are mixed by multiplication instead of superposition.
+	Another open issue for \gls{sr} is backscatter multiple access.
+	% By extending the \gls{sic} scheme to multi-node scenario, \cite{Xu2021a} proposed a backscatter \gls{noma}-based \gls{sr} where the decoding order depends on backscatter channel strength.
+	\cite{Xu2021a} proposed a backscatter \gls{noma}-based \gls{sr} by extending the \gls{sic} scheme to multi-node scenario, where the decoding order depends on backscatter signal strength.
+	However, its performance deteriorates fast when the number of nodes increases.
+	Backscatter \gls{tdma} was also evaluated in \cite{Yang2021a}, where each node transmits information during its own slot and harvests energy during others.
+	Although transmission time and reflection ratio can be designed to boost energy efficiency, it requires frequent feedback to passive nodes and incurs high coordination cost.
+	In \cite{Vougioukas2019}, the nodes control the load-switching speed to shift the scattered signal to desired frequency band, enabling backscatter \gls{fdma}.
+	It requires extra bandwidth and consumes more power at passive nodes.
+	% In \cite{Han2021}, random code-assisted backscatter multiple access was introduced to \gls{sr}, and the authors evaluated the asymptotic \gls{sinr} performance using random matrix theory.
 	To reduce coordination between passive nodes, \cite{Han2021} proposed a random code-assisted multiple access for \gls{sr} and evaluated the asymptotic \gls{sinr} using random matrix theory.
+	However, it suffers from imperfect synchronization and the near-far problem.
+
+	% \cite{Zhou2019a} also explored the asymptotic impact of transmit/receive antenna and backscatter symbol period on the ergodic rate of primary and backscatter links.
+	% For a \gls{mimo} \gls{sr} system with a multi-antenna backscatter node, \cite{Wu2021a} proposed a beamforming design to maximize the backscatter rate while guaranteeing the primary performance.
+	% However, those paper only considered one backscatter node and backscatter multiple access remains an open issue.
+	% In \cite{Xu2021a}, a \gls{noma}-based \gls{sr} was proposed and receive combining was investigated when \gls{sic} order follows equivalent channel strength.
+	% A \gls{tdma}-based \gls{sr} with energy harvesting constraints was also presented in \cite{Yang2021a}, where transmit power, reflection efficiency, and time allocation were jointly optimized to maximize energy efficiency.
+	% To reduce coordination between passive nodes, \cite{Han2021} proposed a random code-assisted multiple access for \gls{sr} and evaluated the asymptotic \gls{sinr} using random matrix theory.
 

### 2022-08-04 main.tex
:pencil: Update introduction

@@
 
+% dark mode
 \usepackage{xcolor} \pagecolor[rgb]{0,0,0} \color[rgb]{1,1,1}
@@
 \newacronym{smawk}{SMAWK}{Shor-Moran-Aggarwal-Wilber-Klawe}
+\newacronym{snr}{SNR}{Signal-to-Noise Ratio}
 \newacronym{sr}{SR}{Symbiotic Radio}
@@
 \begin{document}
-% \title{UniScatter: Unifying\\Backscatter Communications, Reconfigurable Intelligent Surface, and Symbiotic Radio}
 \title{UniScatter: Unifying\\Backscatter Communications, Symbiotic Radio, and Reconfigurable Intelligent Surface}
@@
 	\gls{bc} varies object impedance to manipulate the magnitude, phase, and/or frequency of scattered signal to encode information and deliver within coverage.
-	\gls{ris} adapts scattering antennas or programmable metamaterial to control propagation environment by boosting/suppressing signal strength in specific directions.
+	\gls{ris} adapts scattering antennas or programmable metamaterial to control wireless propagation environment by boosting/suppressing signal strength in specific directions.
 	\gls{sr} incorporates scatter nodes into active networks that recycle ambient signal to transmit self information and enhance legacy channel to the cooperative receiver.
@@
 	For sequential decoding from primary to backscatter, \cite{Long2020a} pointed out the randomness from backscatter modulation can be modelled as either interference or channel uncertainty, depending on symbol period ratio.
-	The authors concluded if this ratio is sufficiently long, the non-coherent primary rate would asymptotically approach its coherent counterpart.
+	The authors concluded if this ratio is sufficiently large, the non-coherent primary achievable rate would asymptotically approach its coherent counterpart.
 	This motivated \cite{Long2020a,Ding2020,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Yang2018,Han2021,Zhang2022,Xu2020b,Hua2022} to decode the primary link, perform \gls{sic}, then decode the backscatter link.
-	However, the advantage of \gls{sic} is questionable because 1) backscatter pattern and signal characteristics are not fully exploited; 2) non-coherent primary encoding is required at the transmitter while re-encoding, precoding, and subtraction are required at the receiver; 3) primary and backscatter symbols are mixed by multiplication instead of superposition.
+	However, the advantage of \gls{sic} is questionable because 1) backscatter pattern and signal characteristics are not fully exploited; 2) primary rate analysis considers moderately long backscatter symbol period that constraints backscatter rate; 3) non-coherent primary encoding is required at the transmitter, while re-encoding, precoding, and subtraction are required at the receiver; 4) primary and backscatter symbols are mixed by multiplication instead of superposition.
 	Another open issue for \gls{sr} is backscatter multiple access.
 	% By extending the \gls{sic} scheme to multi-node scenario, \cite{Xu2021a} proposed a backscatter \gls{noma}-based \gls{sr} where the decoding order depends on backscatter channel strength.
-	\cite{Xu2021a} proposed a backscatter \gls{noma}-based \gls{sr} by extending the \gls{sic} scheme to multi-node scenario, where the decoding order depends on backscatter signal strength.
+	\cite{Xu2021a} proposed a backscatter \gls{noma}-based \gls{sr} by extending \gls{sic} to multi-node scenario, where the decoding order depends on backscatter signal strength.
 	However, its performance deteriorates fast when the number of nodes increases.
 	Backscatter \gls{tdma} was also evaluated in \cite{Yang2021a}, where each node transmits information during its own slot and harvests energy during others.
-	Although transmission time and reflection ratio can be designed to boost energy efficiency, it requires frequent feedback to passive nodes and incurs high coordination cost.
-	In \cite{Vougioukas2019}, the nodes control the load-switching speed to shift the scattered signal to desired frequency band, enabling backscatter \gls{fdma}.
-	It requires extra bandwidth and consumes more power at passive nodes.
+	Although energy efficiency can be enhanced by transmission time and reflection ratio design, it requires regular feedback to passive nodes and incurs high coordination cost.
+	% Although transmission time and reflection ratio can be designed to boost energy efficiency, it requires frequent feedback to passive nodes and incurs high coordination cost.
+	% In \cite{Vougioukas2019}, the nodes control the load-switching speed to shift the scattered signal to desired frequency band, enabling backscatter \gls{fdma}.
+	\cite{Vougioukas2019} controls the load-switching speed at nodes to shift the scattered signal to desired frequency bands, which enables backscatter \gls{fdma} at the cost of extra bandwidth and higher power consumption.
+	% It requires extra bandwidth and consumes more power at passive nodes.
 	% In \cite{Han2021}, random code-assisted backscatter multiple access was introduced to \gls{sr}, and the authors evaluated the asymptotic \gls{sinr} performance using random matrix theory.
@@
 	However, it suffers from imperfect synchronization and the near-far problem.
-
 	% \cite{Zhou2019a} also explored the asymptotic impact of transmit/receive antenna and backscatter symbol period on the ergodic rate of primary and backscatter links.
@@
 
-	% On the other hand, \gls{ris} has recently emerged as a promising technique to enhance the energy efficiency.
-	% In practice, an \gls{ris} consists of multiple individual sub-wavelength reflecting elements to adjust the amplitude and phase of the incoming signal (i.e., passive beamforming).
-	% Different from relay, backscatter and frequency-selective surface \cite{Anwar2018}, \gls{ris} assists the primary transmission using passive components with much lower energy consumption and thermal noise, but is limited to frequency-dependent reflection.
-	% On the other hand, \gls{ris} consists of numerous sub-wavelength passive elements that alter propagation environment using adaptive backscatter pattern to assist existing networks.
-Extensive research has been devoted to optimizing the reflection coefficient
-	% On the other hand, \gls{ris} consists of numerous sub-wavelength passive elements with adaptive amplitudes and/or phases that alter propagation environment to assist existing networks.
-	On the other hand, \gls{ris} alters propagation environment for legacy networks using numerous sub-wavelength passive elements with adaptive amplitudes and/or phases.
-	Extensive research has been devoted to optimizing the phase shifts for the whole channel block to improve communication, sensing, and power performances \cite{Wu2018,Zhang2019a,Lin2022,Liu2022,Feng2022,Zhao2022}.
+	On the other hand, \gls{ris} is a promising technology that evolves wireless propagation environment using numerous passive reflecting elements (e.g., scattering antenna or programmable metamaterial) with adjustable amplitudes and/or phases \cite{Wu2021b}.
+	% The scattered/reflected signals contain no additional information, but adds constructively (or destructively) with the direct component to enhance desired link (or suppress interference).
+	The scattered signals contain no additional information, but adds constructively or destructively with the direct component to enhance desired signal or suppress interference, improving spectrum and energy efficiency.
+	% Specifically, different IRS reflec- tion coefficients are set for different time slots in each channel coherence block to enable more flexible reflection design with generally less number of users selected to be served at each time slot, thus leading to a higher passive beamforming gain
+	% Extensive research has been devoted to optimizing \gls{ris} phase shifts to improve communication, sensing, and power performances.
+	Compared with backscatter nodes of \gls{bc} and \gls{sr}, the reflection pattern of \gls{ris} elements are deterministic and priorly known at transmitter and receiver.
+	It motivated the use of fixed reflection pattern during each channel block to improve communication, sensing, and power performances \cite{Wu2018,Zhang2019a,Lin2022,Liu2022,Feng2022,Zhao2022}.
+	% To create artificial diversity and enable flexible resource allocation, the concept of dynamic passive beamforming was first proposed for \gls{ofdm} systems \cite{Yang2020},
+	% The concept of dynamic passive beamforming that chooses \gls{ris} reflection coefficients independently over different time slots within each channel block was first proposed for \gls{ofdm} systems \cite{Yang2020}, then extended to multi-user \gls{wpt} \cite{Qiu2022} and \gls{wpcn} \cite{Wu2021d,Hua2022a} with dedicated downlink power and uplink information phases.
+	% The concept of dynamic passive beamforming, namely choosing \gls{ris} reflection coefficients independently over different time slots within each channel block, was first proposed for \gls{ofdm} systems \cite{Yang2020}, then extended to multi-user \gls{wpt} \cite{Qiu2022} and \gls{wpcn} \cite{Wu2021d,Hua2022a} with dedicated downlink power and uplink information phases.
+	The concept of dynamic \gls{ris}, namely choosing independent reflection coefficients for different time slots within channel block, was first proposed to assist \gls{ofdm} systems \cite{Yang2020}, then extended for the downlink power and uplink information phases of \gls{wpcn} \cite{Wu2021,Wu2021d,Hua2022a}.
+	Dynamic \gls{ris} introduced artificial channel diversity and flexible resource allocation, but missed the opportunity to encode its own message.
+	% Interestingly, \cite{Karasik2020} reported from information-theoretic perspective that if
+	From an information-theoretic perspective, \cite{Karasik2020} reported using \gls{ris} as an auxiliary equipment to maximize the \gls{snr} is generally rate-suboptimal for finite input constellations.
+	% From an information-theoretic perspective, \cite{Karasik2020} reported using \gls{ris} as a pure auxiliary device to maximize the \gls{snr} at the receiver is generally rate-suboptimal for finite input constellations.
+	% The capacity-achieving transmission scheme is to joint
+	Instead, joint transmitter-\gls{ris} encoding achieves the capacity of \gls{ris}-aided channel, while layered encoding with \gls{sic} decoding (i.e., \gls{sic}-based \gls{sr}) can outperform pure passive beamforming at high \gls{snr}.
+	Further attempts
+
+	How to combine backscatter modulation and passive beamforming
+
+	Although dynamic passive beamforming artificially creates temporal diversity for flexible channel reconfiguration and resource allocation, it demands additional computational cost and control overhead, and the tradeoff deserves further attention especially for large \gls{ris}.
+	In \cite{Chen2021,Zhang2021d}, \gls{ris} was also introduced to single- and multi-node \gls{sr} systems to reduce the total transmit power.
+	When joint transmitter-\gls{ris} encoding is possible, \cite{Karasik2020} proved using \gls{ris} only for passive beamforming is generally suboptimal in terms of achievable rate for finite input constellations.
+	% The capacity-achieving \gls{ris} strategy was found to
+	Recently, \gls{ris}-empowered \gls{sr} was introduced in \cite{Xu2020b,Hua2022,Hu2021a} where independent passive beamforming and backscatter encoding were combined using advanced architectures.
+	The authors of \cite{Xu2020b,Hua2022} proposed the \gls{ris} to modulate binary message over the whole phase shift matrix and the receiver to decodes from (non-coherent) primary to (coherent) backscatter link.
+	In contrast, \cite{Hu2021a} divided the \gls{ris} into reflection and information elements, and evaluated the error performance of non-coherent backscatter detection.
+
 	% In contrast, dynamic passive beamforming that adjusts \gls{ris} within channel block was proposed in \cite{Yang2020} to create diversity for \gls{ofdm} systems.
@@
 	In \cite{Chen2021,Zhang2021d}, \gls{ris} was also introduced to single- and multi-node \gls{sr} systems to reduce the total transmit power.
-	When joint transmitter-\gls{ris} encoding is possible, \cite{Karasik2019} proved using \gls{ris} only for passive beamforming is generally suboptimal in terms of achievable rate for finite input constellations.
+	When joint transmitter-\gls{ris} encoding is possible, \cite{Karasik2020} proved using \gls{ris} only for passive beamforming is generally suboptimal in terms of achievable rate for finite input constellations.
 	% The capacity-achieving \gls{ris} strategy was found to
@@
 		On the other hand, the optimal input distribution becomes fully deterministic at $\rho=1$ (i.e., best primary performance), where the state maximizes equivalent primary channel \eqref{eq:equivalent_channel} strength is chosen with probability \num{1}.
-		In this case, Metascatter boils down to an \gls{ris} element with $M$ discrete states.
+		In this case, Metascatter boils down to a \gls{ris} element with $M$ discrete states.
 		As $\rho$ moves from \num{0} to \num{1}, the optimal input distribution becomes gradually biased to one state and flexibly balances the primary-backscatter tradeoff.

### 2022-08-05 main.tex
:pencil: Update introduction

@@
 	The authors concluded if this ratio is sufficiently large, the non-coherent primary achievable rate would asymptotically approach its coherent counterpart.
-	This motivated \cite{Long2020a,Ding2020,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Yang2018,Han2021,Zhang2022,Xu2020b,Hua2022} to decode the primary link, perform \gls{sic}, then decode the backscatter link.
+	This motivated \cite{Long2020a,Ding2020,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Yang2018,Han2021,Zhang2022} to decode the primary link, perform \gls{sic}, then decode the backscatter link.
 	However, the advantage of \gls{sic} is questionable because 1) backscatter pattern and signal characteristics are not fully exploited; 2) primary rate analysis considers moderately long backscatter symbol period that constraints backscatter rate; 3) non-coherent primary encoding is required at the transmitter, while re-encoding, precoding, and subtraction are required at the receiver; 4) primary and backscatter symbols are mixed by multiplication instead of superposition.
@@
 	% The scattered/reflected signals contain no additional information, but adds constructively (or destructively) with the direct component to enhance desired link (or suppress interference).
-	The scattered signals contain no additional information, but adds constructively or destructively with the direct component to enhance desired signal or suppress interference, improving spectrum and energy efficiency.
+	% The scattered signals contain no additional information, but adds constructively or destructively with the direct component to enhance desired signal or suppress interference, improving spectrum and energy efficiency.
+	The scattered signals contain no additional information, but adds constructively or destructively with the direct component to enhance desired signal or suppress interference.
 	% Specifically, different IRS reflec- tion coefficients are set for different time slots in each channel coherence block to enable more flexible reflection design with generally less number of users selected to be served at each time slot, thus leading to a higher passive beamforming gain
@@
 	% The concept of dynamic passive beamforming, namely choosing \gls{ris} reflection coefficients independently over different time slots within each channel block, was first proposed for \gls{ofdm} systems \cite{Yang2020}, then extended to multi-user \gls{wpt} \cite{Qiu2022} and \gls{wpcn} \cite{Wu2021d,Hua2022a} with dedicated downlink power and uplink information phases.
-	The concept of dynamic \gls{ris}, namely choosing independent reflection coefficients for different time slots within channel block, was first proposed to assist \gls{ofdm} systems \cite{Yang2020}, then extended for the downlink power and uplink information phases of \gls{wpcn} \cite{Wu2021,Wu2021d,Hua2022a}.
-	Dynamic \gls{ris} introduced artificial channel diversity and flexible resource allocation, but missed the opportunity to encode its own message.
+	% The concept of dynamic \gls{ris}, namely choosing independent reflection coefficients for different time slots within channel block, was first proposed to assist \gls{ofdm} systems \cite{Yang2020}, then extended for the downlink power and uplink information phases of \gls{wpcn} \cite{Wu2021,Wu2021d,Hua2022a}.
+	The concept of dynamic \gls{ris}, namely choosing independent reflection coefficients over different time slots within channel block, was first considered for resource blocks of \gls{ofdm} systems, then extended to power and information phases of \gls{wpcn} \cite{Wu2021,Wu2021d,Hua2022a}.
+	Dynamic \gls{ris} provided artificial channel diversity and flexible resource allocation, but missed the opportunity to encode its own message.
 	% Interestingly, \cite{Karasik2020} reported from information-theoretic perspective that if
@@
 	% The capacity-achieving transmission scheme is to joint
-	Instead, joint transmitter-\gls{ris} encoding achieves the capacity of \gls{ris}-aided channel, while layered encoding with \gls{sic} decoding (i.e., \gls{sic}-based \gls{sr}) can outperform pure passive beamforming at high \gls{snr}.
-	Further attempts
-
-	How to combine backscatter modulation and passive beamforming
+	Instead, joint transmitter-\gls{ris} encoding achieves the capacity of \gls{ris}-aided channel, and layered encoding with \gls{sic} decoding (i.e., \gls{sic}-based \gls{sr}) can outperform pure passive beamforming at high \gls{snr}.
+	It inspired \cite{Liu2019d,Bereyhi2020,Xu2020b,Zhang2021d,Hu2021b,Hua2022,Basar2020,Ma2020a,Yuan2021,Hu2021a} to employ \gls{ris} as an information source that combines passive beamforming and backscatter modulation in the overall reflection pattern.
+	% In particular, \emph{overlay modulation} decouples the overall reflection pattern as the product of an information-bearing symbol and an auxiliary coefficient matrix.
+	% In particular, \emph{overlay modulation} superposes information-bearing symbols over a common auxiliary matrix \cite{Xu2020b,Zhang2021d,Hu2021b,Hua2022}, \emph{spatial modulation} designs the reflection coefficients to maximize the \gls{snr} of different
+	% In particular, \emph{overlay modulation} superposes information-bearing symbols over a common auxiliary matrix \cite{Xu2020b,Zhang2021d,Hu2021b,Hua2022}, \emph{spatial modulation} varies \gls{ris} reflection coefficients to maximize the \gls{snr} at different receive antennas \cite{Basar2020,Ma2020a,Yuan2021}, \emph{index modulation} divided the \gls{ris} into reflection and information elements, and evaluated the error performance of non-coherent backscatter detection.
+	% In particular, \emph{overlay modulation} superposes information-bearing symbols over a common auxiliary matrix \cite{Xu2020b,Zhang2021d,Hu2021b,Hua2022}, \emph{spatial modulation} varies \gls{ris} reflection coefficients to maximize the \gls{snr} at different receive antennas \cite{Basar2020,Ma2020a,Yuan2021}, \emph{index modulation} divided the \gls{ris} into reflection elements for passive beamforming and information elements
+	% In particular, \emph{overlay modulation} superposes information-bearing symbols over a common auxiliary matrix \cite{Xu2020b,Zhang2021d,Hu2021b,Hua2022}, \emph{spatial modulation} switches between reflection coefficient sets that maximize \gls{snr} at different receive antennas \cite{Basar2020,Ma2020a,Yuan2021}, \emph{index modulation} divides \gls{ris} into reflection elements for passive beamforming and information elements for on-off keying modulation \cite{Hu2021a}, and \emph{symbol level precoding} designs the reflection coefficients to
+	% In particular, \emph{overlay modulation} superposes information-bearing symbols over a common auxiliary matrix \cite{Xu2020b,Zhang2021d,Hu2021b,Hua2022}, \emph{spatial modulation} switches between reflection coefficient sets that maximize \gls{snr} at different receive antennas \cite{Basar2020,Ma2020a,Yuan2021}, \emph{index modulation} divides \gls{ris} into reflection elements for passive beamforming and information elements for on-off modulation \cite{Hu2021a}, and \emph{symbol level precoding} creates a mapping from reflection coefficients to backscatter symbol \cite{Liu2019d,Bereyhi2020} where .
+	% In particular, \emph{overlay modulation} superposes information-bearing symbols over a common auxiliary matrix \cite{Xu2020b,Zhang2021d,Hu2021b,Hua2022}, \emph{spatial modulation} switches between reflection coefficient sets that maximize \gls{snr} at different receive antennas \cite{Basar2020,Ma2020a,Yuan2021}, \emph{index modulation} divides \gls{ris} into reflection elements for passive beamforming and information elements for on-off modulation \cite{Hu2021a}, and \emph{symbol level precoding} maps reflection coefficients to backscatter symbols and optimizes to improve detection performance.
+	% In particular, \emph{overlay modulation} superposes information-bearing symbols over a common auxiliary matrix \cite{Xu2020b,Zhang2021d,Hu2021b,Hua2022}, \emph{spatial modulation} switches between reflection coefficient sets that maximize \gls{snr} at different receive antennas \cite{Basar2020,Ma2020a,Yuan2021}, \emph{index modulation} divides \gls{ris} into reflection elements for passive beamforming and information elements for on-off modulation \cite{Hu2021a}, and \emph{symbol level precoding} maps reflection coefficients to backscatter symbols and optimizes for detection performance.
+	% In particular, \emph{symbol level precoding} maps optimized \gls{ris} coefficient sets to backscatter symbols to improve detection performance,
+	% In particular, \emph{symbol level precoding} maps \gls{ris} coefficient sets to backscatter symbols and optimizes for detection performance,
+	% In particular, \emph{symbol level precoding} maps optimized \gls{ris} coefficient sets to backscatter symbols \cite{Liu2019d,Bereyhi2020}, \emph{overlay modulation} superposes information-bearing symbols over a common auxiliary matrix \cite{Xu2020b,Zhang2021d,Hu2021b,Hua2022}, \emph{spatial modulation} switches between reflection coefficient sets that maximize \gls{snr} at different receive antennas \cite{Basar2020,Ma2020a,Yuan2021}, and \emph{index modulation} divides \gls{ris} into reflection elements for passive beamforming and information elements for on-off modulation \cite{Hu2021a}.
+	In particular, \emph{symbol level precoding} maps backscatter symbols to optimized \gls{ris} coefficient sets \cite{Liu2019d,Bereyhi2020}, \emph{overlay modulation} superposes information-bearing symbols over a common auxiliary matrix \cite{Xu2020b,Zhang2021d,Hu2021b,Hua2022}, \emph{spatial modulation} switches between reflection coefficient sets that maximize \gls{snr} at different receive antennas \cite{Basar2020,Ma2020a,Yuan2021}, and \emph{index modulation} divides \gls{ris} into reflection elements for passive beamforming and information elements for on-off modulation \cite{Hu2021a}.
+
+	% \cite{Liu2019d,Bereyhi2020}
+
+	% How to combine backscatter modulation and passive beamforming
+
+	Recently, \gls{ris}-empowered \gls{sr} was introduced in \cite{Xu2020b,Hua2022,Hu2021a} where independent passive beamforming and backscatter encoding were combined using advanced architectures.
+	The authors of \cite{Xu2020b,Hua2022} proposed the \gls{ris} to modulate binary message over the whole phase shift matrix and the receiver to decodes from (non-coherent) primary to (coherent) backscatter link.
+	In contrast, \cite{Hu2021a} divided the \gls{ris} into reflection and information elements, and evaluated the error performance of non-coherent backscatter detection.
+	% Compared to existing \gls{ris}-empowered \gls{sr} that encodes and precodes independently using advanced architecture (e.g., overlay or parallel), Metascatter softly bridges and generalizes parasitic source of \gls{sr} and reflecting element of \gls{ris} via smart input design.
 

### 2022-08-05 main.tex
:pencil: Update introduction

--- 2022-08-04 main.tex
@@
 	However, traditional \gls{bc} requires dedicated carrier emitter and backscatter reader, while passive nodes only respond when externally inquired.
-	% In \gls{ambc} \cite{Liu2013b}, ambient signals (e.g., radio, television, and Wi-Fi) are recycled by interactive nodes to harvest energy and establish connection.
 	In \gls{ambc} \cite{Liu2013b}, interactive nodes recycle ambient signals generated by legacy transmitters (e.g., radio, television, and Wi-Fi) to harvest energy and establish connection.
-	% ambient signals (e.g., radio, television, and Wi-Fi) are recycled by interactive nodes to harvest energy and establish connection.
-	% It not only eliminates the need of power source and carrier emitter, but also avoid the cost of dedicated frequency spectrum.
 	It eliminates the need of dedicated power source, carrier emitter, and frequency spectrum, bringing more opportunities to low-power communications.
@@
 	The authors concluded if this ratio is sufficiently large, the non-coherent primary achievable rate would asymptotically approach its coherent counterpart.
-	This motivated \cite{Long2020a,Ding2020,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Yang2018,Han2021,Zhang2022,Xu2020b,Hua2022} to decode the primary link, perform \gls{sic}, then decode the backscatter link.
+	This motivated \cite{Long2020a,Ding2020,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Yang2018,Han2021,Zhang2022} to decode the primary link, perform \gls{sic}, then decode the backscatter link.
 	However, the advantage of \gls{sic} is questionable because 1) backscatter pattern and signal characteristics are not fully exploited; 2) primary rate analysis considers moderately long backscatter symbol period that constraints backscatter rate; 3) non-coherent primary encoding is required at the transmitter, while re-encoding, precoding, and subtraction are required at the receiver; 4) primary and backscatter symbols are mixed by multiplication instead of superposition.
 	Another open issue for \gls{sr} is backscatter multiple access.
-	% By extending the \gls{sic} scheme to multi-node scenario, \cite{Xu2021a} proposed a backscatter \gls{noma}-based \gls{sr} where the decoding order depends on backscatter channel strength.
 	\cite{Xu2021a} proposed a backscatter \gls{noma}-based \gls{sr} by extending \gls{sic} to multi-node scenario, where the decoding order depends on backscatter signal strength.
@@
 	Although energy efficiency can be enhanced by transmission time and reflection ratio design, it requires regular feedback to passive nodes and incurs high coordination cost.
-	% Although transmission time and reflection ratio can be designed to boost energy efficiency, it requires frequent feedback to passive nodes and incurs high coordination cost.
-	% In \cite{Vougioukas2019}, the nodes control the load-switching speed to shift the scattered signal to desired frequency band, enabling backscatter \gls{fdma}.
 	\cite{Vougioukas2019} controls the load-switching speed at nodes to shift the scattered signal to desired frequency bands, which enables backscatter \gls{fdma} at the cost of extra bandwidth and higher power consumption.
-	% It requires extra bandwidth and consumes more power at passive nodes.
-	% In \cite{Han2021}, random code-assisted backscatter multiple access was introduced to \gls{sr}, and the authors evaluated the asymptotic \gls{sinr} performance using random matrix theory.
 	To reduce coordination between passive nodes, \cite{Han2021} proposed a random code-assisted multiple access for \gls{sr} and evaluated the asymptotic \gls{sinr} using random matrix theory.
@@
 	On the other hand, \gls{ris} is a promising technology that evolves wireless propagation environment using numerous passive reflecting elements (e.g., scattering antenna or programmable metamaterial) with adjustable amplitudes and/or phases \cite{Wu2021b}.
-	% The scattered/reflected signals contain no additional information, but adds constructively (or destructively) with the direct component to enhance desired link (or suppress interference).
-	The scattered signals contain no additional information, but adds constructively or destructively with the direct component to enhance desired signal or suppress interference, improving spectrum and energy efficiency.
-	% Specifically, different IRS reflec- tion coefficients are set for different time slots in each channel coherence block to enable more flexible reflection design with generally less number of users selected to be served at each time slot, thus leading to a higher passive beamforming gain
-	% Extensive research has been devoted to optimizing \gls{ris} phase shifts to improve communication, sensing, and power performances.
+	The scattered signals contain no additional information, but adds constructively or destructively with the direct component to enhance desired signal or suppress interference.
 	Compared with backscatter nodes of \gls{bc} and \gls{sr}, the reflection pattern of \gls{ris} elements are deterministic and priorly known at transmitter and receiver.
 	It motivated the use of fixed reflection pattern during each channel block to improve communication, sensing, and power performances \cite{Wu2018,Zhang2019a,Lin2022,Liu2022,Feng2022,Zhao2022}.
-	% To create artificial diversity and enable flexible resource allocation, the concept of dynamic passive beamforming was first proposed for \gls{ofdm} systems \cite{Yang2020},
-	% The concept of dynamic passive beamforming that chooses \gls{ris} reflection coefficients independently over different time slots within each channel block was first proposed for \gls{ofdm} systems \cite{Yang2020}, then extended to multi-user \gls{wpt} \cite{Qiu2022} and \gls{wpcn} \cite{Wu2021d,Hua2022a} with dedicated downlink power and uplink information phases.
-	% The concept of dynamic passive beamforming, namely choosing \gls{ris} reflection coefficients independently over different time slots within each channel block, was first proposed for \gls{ofdm} systems \cite{Yang2020}, then extended to multi-user \gls{wpt} \cite{Qiu2022} and \gls{wpcn} \cite{Wu2021d,Hua2022a} with dedicated downlink power and uplink information phases.
-	The concept of dynamic \gls{ris}, namely choosing independent reflection coefficients for different time slots within channel block, was first proposed to assist \gls{ofdm} systems \cite{Yang2020}, then extended for the downlink power and uplink information phases of \gls{wpcn} \cite{Wu2021,Wu2021d,Hua2022a}.
-	Dynamic \gls{ris} introduced artificial channel diversity and flexible resource allocation, but missed the opportunity to encode its own message.
-	% Interestingly, \cite{Karasik2020} reported from information-theoretic perspective that if
+	The concept of dynamic \gls{ris}, namely choosing independent reflection coefficients over different time slots within channel block, was first considered for resource blocks of \gls{ofdm} systems, then extended to power and information phases of \gls{wpcn} \cite{Wu2021,Wu2021d,Hua2022a}.
+	Dynamic \gls{ris} provided artificial channel diversity and flexible resource allocation, but missed the opportunity to encode its own message.
 	From an information-theoretic perspective, \cite{Karasik2020} reported using \gls{ris} as an auxiliary equipment to maximize the \gls{snr} is generally rate-suboptimal for finite input constellations.
-	% From an information-theoretic perspective, \cite{Karasik2020} reported using \gls{ris} as a pure auxiliary device to maximize the \gls{snr} at the receiver is generally rate-suboptimal for finite input constellations.
-	% The capacity-achieving transmission scheme is to joint
-	Instead, joint transmitter-\gls{ris} encoding achieves the capacity of \gls{ris}-aided channel, while layered encoding with \gls{sic} decoding (i.e., \gls{sic}-based \gls{sr}) can outperform pure passive beamforming at high \gls{snr}.
-	Further attempts
-
-	How to combine backscatter modulation and passive beamforming
-
-	Although dynamic passive beamforming artificially creates temporal diversity for flexible channel reconfiguration and resource allocation, it demands additional computational cost and control overhead, and the tradeoff deserves further attention especially for large \gls{ris}.
-	In \cite{Chen2021,Zhang2021d}, \gls{ris} was also introduced to single- and multi-node \gls{sr} systems to reduce the total transmit power.
-	When joint transmitter-\gls{ris} encoding is possible, \cite{Karasik2020} proved using \gls{ris} only for passive beamforming is generally suboptimal in terms of achievable rate for finite input constellations.
-	% The capacity-achieving \gls{ris} strategy was found to
-	Recently, \gls{ris}-empowered \gls{sr} was introduced in \cite{Xu2020b,Hua2022,Hu2021a} where independent passive beamforming and backscatter encoding were combined using advanced architectures.
-	The authors of \cite{Xu2020b,Hua2022} proposed the \gls{ris} to modulate binary message over the whole phase shift matrix and the receiver to decodes from (non-coherent) primary to (coherent) backscatter link.
-	In contrast, \cite{Hu2021a} divided the \gls{ris} into reflection and information elements, and evaluated the error performance of non-coherent backscatter detection.
-
-	% In contrast, dynamic passive beamforming that adjusts \gls{ris} within channel block was proposed in \cite{Yang2020} to create diversity for \gls{ofdm} systems.
-	% In contrast, dynamic passive beamforming that adjusts \gls{ris} over finer time slots was proposed in \cite{Yang2020} to create diversity for \gls{ofdm} systems.
-	Besides, \cite{Yang2020} proposed a dynamic passive beamforming that further adjusts \gls{ris} over fine-grained time slots for \gls{ofdm} systems to balance beamforming gain and multiuser diversity.
-	The idea was further applied to \gls{wpcn} to accommodate the downlink \gls{wpt} phase and uplink \gls{wit} phase of the ``harvest-then-transmit'' protocol \cite{Wu2021d,Hua2022a}.
-	% For multiuser \gls{wpt}, \cite{Qiu2022} also reported that despite \gls{ris} is restricted to single-beam reflection, dynamic beamforming can mimic multi-beam reflection in a time-division manner and reduce the phase extraction loss.
-	For multiuser \gls{wpt}, \cite{Qiu2022} also reported that dynamic beamforming can mimic multi-beam reflection in a time-division manner and reduce the phase extraction loss.
-	% However, dynamic passive beamforming demands additional computational complexity and control overhead, and the performance-cost tradeoff needs reconsideration especially when the number of \gls{ris} elements is large.
-	% Although dynamic passive beamforming can artificially create time-varying channels for flexible channel reconfiguration and resource allocation, it demands additional computational complexity and control overhead, and the performance-cost tradeoff deserves further attention.
-	% Although dynamic passive beamforming can artificially introduce temporal diversity for flexible channel reconfiguration and resource allocation, it demands additional computational complexity and control overhead, and the performance-cost tradeoff deserves further attention.
-	Although dynamic passive beamforming artificially creates temporal diversity for flexible channel reconfiguration and resource allocation, it demands additional computational cost and control overhead, and the tradeoff deserves further attention especially for large \gls{ris}.
-	In \cite{Chen2021,Zhang2021d}, \gls{ris} was also introduced to single- and multi-node \gls{sr} systems to reduce the total transmit power.
-	When joint transmitter-\gls{ris} encoding is possible, \cite{Karasik2020} proved using \gls{ris} only for passive beamforming is generally suboptimal in terms of achievable rate for finite input constellations.
-	% The capacity-achieving \gls{ris} strategy was found to
-	Recently, \gls{ris}-empowered \gls{sr} was introduced in \cite{Xu2020b,Hua2022,Hu2021a} where independent passive beamforming and backscatter encoding were combined using advanced architectures.
-	The authors of \cite{Xu2020b,Hua2022} proposed the \gls{ris} to modulate binary message over the whole phase shift matrix and the receiver to decodes from (non-coherent) primary to (coherent) backscatter link.
-	In contrast, \cite{Hu2021a} divided the \gls{ris} into reflection and information elements, and evaluated the error performance of non-coherent backscatter detection.
+	Instead, joint transmitter-\gls{ris} encoding achieves the capacity of \gls{ris}-aided channel, and layered encoding with \gls{sic} decoding (i.e., \gls{sic}-based \gls{sr}) can outperform pure passive beamforming at high \gls{snr}.
+	It inspired \cite{Liu2019d,Bereyhi2020,Xu2020b,Zhang2021d,Hu2021b,Hua2022,Basar2020,Ma2020a,Yuan2021,Hu2021a} to employ \gls{ris} as an information source that combines passive beamforming and backscatter modulation in the overall reflection pattern.
+	In particular, \emph{symbol level precoding} maps backscatter symbols to optimized \gls{ris} coefficient sets \cite{Liu2019d,Bereyhi2020}, \emph{overlay modulation} superposes information-bearing symbols over a common auxiliary matrix \cite{Xu2020b,Zhang2021d,Hu2021b,Hua2022}, \emph{spatial modulation} switches between reflection coefficient sets that maximize \gls{snr} at different receive antennas \cite{Basar2020,Ma2020a,Yuan2021}, and \emph{index modulation} divides \gls{ris} into reflection elements for passive beamforming and information elements for on-off modulation \cite{Hu2021a}.
+	However, those \gls{ris}-empowered \gls{bc} and \gls{sr} designs involve advanced hardware architecture, high optimization complexity, and additional control overhead.
+
 	% Compared to existing \gls{ris}-empowered \gls{sr} that encodes and precodes independently using advanced architecture (e.g., overlay or parallel), Metascatter softly bridges and generalizes parasitic source of \gls{sr} and reflecting element of \gls{ris} via smart input design.

### 2022-08-06 main.tex
:pencil: Update introduction

@@
 	In this paper, we depart from those concepts and introduce UniScatter as a new paradigm for future wireless networks.
-	Instead of treating probability distribution of reflection states as equiprobable (as scattering source of \gls{bc}/\gls{sr}) or degenerate (as reflecting element of \gls{ris}), UniScatter node adapts input distribution of a passive scatter node based on link priority and \gls{csi}, balancing information encoding and channel reconfiguration in a flexible and mutualistic manner.
-	To accommodate signal characteristics, UniScatter receiver semi-coherently decodes all nodes from accumulated energy, acquires equivalent primary channel over reflection pattern, then coherently decodes the primary link under enhanced multipath.
+	Instead of treating probability distribution of reflection states as equiprobable (as scattering source of \gls{bc}/\gls{sr}) or degenerate (as reflecting element of \gls{ris}), UniScatter node adapts the input distribution of a passive scatterer based on link priority and \gls{csi}, balancing information encoding and channel reconfiguration in a flexible and mutualistic manner.
+	To accommodate signal characteristics, UniScatter receiver semi-coherently decodes all nodes from accumulated energy, determines equivalent primary channel over reflection pattern, then coherently decodes the primary link under enhanced multipath.
 	It reduces the complexity of cooperative decoding while preserves the benefits of backscatter modulation and passive beamforming.
-	Using shared spectrum, energy, and infrastructures, UniScatter is a more general and powerful transmit-assist protocol that generalizes \gls{bc}, \gls{ris} and \gls{sr} with universal hardware design and augmented \gls{qos} control.
+	Using shared spectrum, energy, and infrastructures, UniScatter is a general and powerful transmit-assist protocol that unifies \gls{bc}, \gls{ris} and \gls{sr} with universal hardware design and augmented \gls{qos} control.
 	We consider an application scenario where a multi-antenna \gls{ap} serves a single-antenna user surrounded by multiple UniScatter nodes, and characterize the achievable primary-(total-)backscatter rate region by designing input distribution at the nodes, active beamforming at the \gls{ap}, and backscatter decision design at the user.
@@
 	As an emerging low-power communication technique, \gls{bc} separates conventional transmitter into a \gls{rf} emitter with power-hungry elements (e.g., synthesizer and amplifier), and an information-bearing node with power-efficient components (e.g., harvester and modulator) \cite{Boyer2014}.
-	The node harvests energy from incident wave and embeds information over scattered signal in a sustainable and controllable manner.
+	The node harvests energy from emitted wave and embeds information over scattered signal in a sustainable and controllable manner.
 	The backscatter reader can be either co-located or separated with the emitter, known as monostatic and bistatic \gls{bc}.
-	Its applications such as \gls{rfid} \cite{Dobkin2012,Landt2005} and sensor networks \cite{Vannucci2008,Assimonis2016} have been extensively researched, standardized, and commercialized to support \gls{iot} and \gls{m2m}.
+	Its applications such as \gls{rfid} \cite{Dobkin2012,Landt2005} and passive sensor network \cite{Vannucci2008,Assimonis2016} have been extensively researched, standardized, and commercialized to support \gls{iot} and \gls{m2m}.
 	% Specifically, a dedicated emitter generates a sinusoidal carrier at reserved frequency, and \gls{rfid} tags reports their identifier to a nearby \gls{rfid} reader.
@@
 	However, traditional \gls{bc} requires dedicated carrier emitter and backscatter reader, while passive nodes only respond when externally inquired.
-	In \gls{ambc} \cite{Liu2013b}, interactive nodes recycle ambient signals generated by legacy transmitters (e.g., radio, television, and Wi-Fi) to harvest energy and establish connection.
+	In \gls{ambc} \cite{Liu2013b}, interactive nodes recycle ambient signals generated by legacy transmitters (e.g., radio, television, and Wi-Fi) to harvest energy and establish connection in between.
 	It eliminates the need of dedicated power source, carrier emitter, and frequency spectrum, bringing more opportunities to low-power communications.
@@
 	In \gls{sr}, the primary transmitter generates active radio carrying primary information, the secondary node modulates scattered component with backscatter information, and the cooperative receiver decodes both links from two propagation paths.
-	The direct transmitter-receiver path only contains primary information, while the cascaded transmitter-node-receiver path preserves both information due to backscatter principles.
+	The direct transmitter-receiver path only contains primary information, while the cascaded transmitter-node-receiver path preserves both thanks to signal characteristics.
 	Such a coexistence was further classified into commensal, parasitic, and competitive relationships based on link priority \cite{Guo2019b}, and their instantaneous rates, optimal power allocations, and outage probabilities were subsequently derived in \cite{Guo2019b,Ding2020}.
-	However, one important issue of \gls{sr} is practical cooperative receiver design.
+	However, one important issue of \gls{sr} is practical cooperative decoding design.
+	Due to physical constraints at the load-switching modulator, backscatter symbol period is typically longer than primary.
 	Ideal joint \gls{ml} decoding achieves optimal performance with prohibitive computational complexity \cite{Yang2018,Zhang2022}.
-	Due to physical constraints at the load-switching modulator, backscatter symbol period is typically longer than primary.
-	For sequential decoding from primary to backscatter, \cite{Long2020a} pointed out the randomness from backscatter modulation can be modelled as either interference or channel uncertainty, depending on symbol period ratio.
+	For sequential decoding from primary to backscatter, \cite{Long2020a} pointed out the randomness from backscatter modulation can be modelled as either interference or channel uncertainty, depending on the symbol period ratio.
 	The authors concluded if this ratio is sufficiently large, the non-coherent primary achievable rate would asymptotically approach its coherent counterpart.
-	This motivated \cite{Long2020a,Ding2020,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Yang2018,Han2021,Zhang2022} to decode the primary link, perform \gls{sic}, then decode the backscatter link.
-	However, the advantage of \gls{sic} is questionable because 1) backscatter pattern and signal characteristics are not fully exploited; 2) primary rate analysis considers moderately long backscatter symbol period that constraints backscatter rate; 3) non-coherent primary encoding is required at the transmitter, while re-encoding, precoding, and subtraction are required at the receiver; 4) primary and backscatter symbols are mixed by multiplication instead of superposition.
+	This motivated \cite{Long2020a,Ding2020,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Yang2018,Han2021,Zhang2022} to first decode the primary link, perform \gls{sic}, then decode the backscatter link.
+	However, the advantage of \gls{sic} is questionable because 1) sufficiently large symbol period ratio is assumed in primary rate analysis and constraints backscatter rate; 2) backscatter pattern and signal characteristics are not fully exploited; 3) non-coherent primary encoding is required at the transmitter, while re-encoding, precoding, and subtraction are required at the receiver; 4) primary and backscatter symbols are mixed by multiplication instead of superposition.
 	Another open issue for \gls{sr} is backscatter multiple access.
-	\cite{Xu2021a} proposed a backscatter \gls{noma}-based \gls{sr} by extending \gls{sic} to multi-node scenario, where the decoding order depends on backscatter signal strength.
+	\cite{Xu2021a} extended \gls{sic} to multi-node scenario and proposed a backscatter \gls{noma}-based \gls{sr} with decoding order following backscatter signal strength.
+	% \cite{Xu2021a} proposed a backscatter \gls{noma}-based \gls{sr} by extending \gls{sic} to multi-node scenario, where the decoding order depends on backscatter signal strength.
 	However, its performance deteriorates fast when the number of nodes increases.
-	Backscatter \gls{tdma} was also evaluated in \cite{Yang2021a}, where each node transmits information during its own slot and harvests energy during others.
-	Although energy efficiency can be enhanced by transmission time and reflection ratio design, it requires regular feedback to passive nodes and incurs high coordination cost.
-	\cite{Vougioukas2019} controls the load-switching speed at nodes to shift the scattered signal to desired frequency bands, which enables backscatter \gls{fdma} at the cost of extra bandwidth and higher power consumption.
+	Backscatter \gls{tdma} was also evaluated in \cite{Yang2021a}, where each node transmits information during dedicated slot and harvests energy during others.
+	% Although energy efficiency can be enhanced by transmission time and reflection ratio design, it requires regular feedback to passive nodes and incurs high coordination cost.
+	It enhances energy efficiency by transmission time and reflection ratio optimization, but requires regular feedback to passive nodes and incurs high coordination cost.
+	\cite{Vougioukas2019} controls the load-switching speed at nodes to shift the scattered signal to desired frequency bands.
+	This enables backscatter \gls{fdma} at the cost of extra bandwidth and higher power consumption.
 	To reduce coordination between passive nodes, \cite{Han2021} proposed a random code-assisted multiple access for \gls{sr} and evaluated the asymptotic \gls{sinr} using random matrix theory.
@@
 	The scattered signals contain no additional information, but adds constructively or destructively with the direct component to enhance desired signal or suppress interference.
-	Compared with backscatter nodes of \gls{bc} and \gls{sr}, the reflection pattern of \gls{ris} elements are deterministic and priorly known at transmitter and receiver.
-	It motivated the use of fixed reflection pattern during each channel block to improve communication, sensing, and power performances \cite{Wu2018,Zhang2019a,Lin2022,Liu2022,Feng2022,Zhao2022}.
+	% Compared with backscatter nodes of \gls{bc} and \gls{sr}, the reflection pattern of \gls{ris} elements are deterministic and priorly known at transmitter and receiver.
+	Compared with backscatter nodes of \gls{bc}/\gls{sr}, \gls{ris} elements employ deterministic reflection pattern priorly known at transmitter and receiver.
+	This motivated the use of fixed reflection coefficients during each channel block to improve communication, sensing, and power performances \cite{Wu2018,Zhang2019a,Lin2022,Liu2022,Feng2022,Zhao2022}.
 	The concept of dynamic \gls{ris}, namely choosing independent reflection coefficients over different time slots within channel block, was first considered for resource blocks of \gls{ofdm} systems, then extended to power and information phases of \gls{wpcn} \cite{Wu2021,Wu2021d,Hua2022a}.
-	Dynamic \gls{ris} provided artificial channel diversity and flexible resource allocation, but missed the opportunity to encode its own message.
-	From an information-theoretic perspective, \cite{Karasik2020} reported using \gls{ris} as an auxiliary equipment to maximize the \gls{snr} is generally rate-suboptimal for finite input constellations.
+	Dynamic \gls{ris} provides artificial channel diversity and flexible resource allocation, but misses the opportunity to encode its own message.
+	From an information-theoretic perspective, \cite{Karasik2020} reported using \gls{ris} as an auxiliary passive beamforming device to maximize the \gls{snr} is generally rate-suboptimal for finite input constellations.
 	Instead, joint transmitter-\gls{ris} encoding achieves the capacity of \gls{ris}-aided channel, and layered encoding with \gls{sic} decoding (i.e., \gls{sic}-based \gls{sr}) can outperform pure passive beamforming at high \gls{snr}.
-	It inspired \cite{Liu2019d,Bereyhi2020,Xu2020b,Zhang2021d,Hu2021b,Hua2022,Basar2020,Ma2020a,Yuan2021,Hu2021a} to employ \gls{ris} as an information source that combines passive beamforming and backscatter modulation in the overall reflection pattern.
-	In particular, \emph{symbol level precoding} maps backscatter symbols to optimized \gls{ris} coefficient sets \cite{Liu2019d,Bereyhi2020}, \emph{overlay modulation} superposes information-bearing symbols over a common auxiliary matrix \cite{Xu2020b,Zhang2021d,Hu2021b,Hua2022}, \emph{spatial modulation} switches between reflection coefficient sets that maximize \gls{snr} at different receive antennas \cite{Basar2020,Ma2020a,Yuan2021}, and \emph{index modulation} divides \gls{ris} into reflection elements for passive beamforming and information elements for on-off modulation \cite{Hu2021a}.
-	However, those \gls{ris}-empowered \gls{bc} and \gls{sr} designs involve advanced hardware architecture, high optimization complexity, and additional control overhead.
+	It inspired \cite{Liu2019d,Bereyhi2020,Xu2020b,Zhang2021d,Hu2021b,Hua2022,Basar2020,Ma2020a,Yuan2021,Hu2021a} to employ \gls{ris} also as an information source to combine passive beamforming and backscatter modulation in the overall reflection pattern.
+	% In particular, \emph{symbol level precoding} maps backscatter symbols to optimized \gls{ris} coefficient sets \cite{Liu2019d,Bereyhi2020}, \emph{overlay modulation} superposes information-bearing symbols over a common auxiliary matrix \cite{Xu2020b,Zhang2021d,Hu2021b,Hua2022}, \emph{spatial modulation} switches between reflection coefficient sets that maximize \gls{snr} at different receive antennas \cite{Basar2020,Ma2020a,Yuan2021}, and \emph{index modulation} divides \gls{ris} into reflection elements for passive beamforming and information elements for on-off modulation \cite{Hu2021a}.
+	In particular, \emph{symbol level precoding} maps backscatter symbols to \gls{ris} coefficient sets optimized for detection \cite{Liu2019d,Bereyhi2020}, \emph{overlay modulation} superposes information-bearing symbols over a common auxiliary matrix \cite{Xu2020b,Zhang2021d,Hu2021b,Hua2022}, \emph{spatial modulation} switches between reflection coefficient sets that maximize \gls{snr} at different receive antennas \cite{Basar2020,Ma2020a,Yuan2021}, and \emph{index modulation} divides \gls{ris} into reflection elements for passive beamforming and information elements for on-off modulation \cite{Hu2021a}.
+	% However, those \gls{ris}-empowered \gls{bc} and \gls{sr} designs involve advanced hardware architecture, high optimization complexity, and additional control overhead.
+	However, those \gls{ris}-empowered \gls{bc} and \gls{sr} designs involve advanced hardware architecture and high optimization complexity.
 
@@
 	% ! An application scenario was considered where multiple Metascatters ride over a point-to-point transmission to simultaneously encode self message and perform passive beamforming.
-	% To fully accommodate backscatter characteristics, we also propose a novel receiving strategy that first jointly decodes all Metascatter from accumulated energy, then models their reflection patterns and backscatter paths within equivalent channel for primary decoding.
+	% To fully accommodate backscatter characteristics, we also propose a novel receiving strategy that first jointly decodes all Metascatter from accumulated energy, then models their reflection pattern and backscatter paths within equivalent channel for primary decoding.
 	% minor modifications on existing receivers, easy to perform, fits backscatter characteristics.
@@
 	\emph{Second,} we consider an application scenario where multiple Metascatters ride over a point-to-point transmission, exploiting additional propagation paths to simultaneously transmit and assist.
-	To fully accommodate backscatter characteristics, we also propose a novel receiving strategy that first jointly decodes all Metascatter from accumulated energy, then models their reflection patterns and backscatter paths within equivalent channel for primary decoding.
+	To fully accommodate backscatter characteristics, we also propose a novel receiving strategy that first jointly decodes all Metascatter from accumulated energy, then models their reflection pattern and backscatter paths within equivalent channel for primary decoding.
 	Since backscatter message is modulated over primary signal, backscatter decoding is indeed part of primary channel training, and there is no need for operation-intensive \gls{sic} at the receiver.
@@
 		However, it requires more frequent detection and re-encoding at the user to maintain the primary rate.
-		When $N$ becomes sufficiently large, total backscatter rate approaches \num{0} and Metascatters boil down to conventional \gls{ris} elements with fixed reflection patterns during whole channel block.
+		When $N$ becomes sufficiently large, total backscatter rate approaches \num{0} and Metascatters boil down to conventional \gls{ris} elements with fixed reflection pattern during whole channel block.
 		In Fig. \subref*{fi:region_frequency}, we observe that passive Metascatter achieves higher backscatter rate at lower carrier frequency because of preferable propagation loss.

### 2022-08-07 main.tex
:pencil: Update contributions

@@
 \begin{section}{Introduction}
-	% TODO You need to explain the key principle and benefits of backscatter, then symbiotic radio, then RIS.
-Then you need to explain about the apparent differences and similarities between those techniques.
-Then metascatter concept will appear.
 	\IEEEPARstart{F}{uture} wireless network is envisioned to provide high throughput, uniform coverage, pervasive connectivity, heterogeneous control, and cognitive intelligence for trillions of portable devices.
@@
 	Its applications such as \gls{rfid} \cite{Dobkin2012,Landt2005} and passive sensor network \cite{Vannucci2008,Assimonis2016} have been extensively researched, standardized, and commercialized to support \gls{iot} and \gls{m2m}.
-	% Specifically, a dedicated emitter generates a sinusoidal carrier at reserved frequency, and \gls{rfid} tags reports their identifier to a nearby \gls{rfid} reader.
+	% ? Specifically, a dedicated emitter generates a sinusoidal carrier at reserved frequency, and \gls{rfid} tags reports their identifier to a nearby \gls{rfid} reader.
 	% ? With the upsurge of wireless devices and the downtrend of circuit power consumption, \gls{rfid} has experienced great success in \gls{ioe} and \gls{m2m} networks.
@@
 	Due to physical constraints at the load-switching modulator, backscatter symbol period is typically longer than primary.
-	Ideal joint \gls{ml} decoding achieves optimal performance with prohibitive computational complexity \cite{Yang2018,Zhang2022}.
+	Ideal joint \gls{ml} decoding achieves optimal performance with prohibitive computational complexity \cite{Yang2018,Liang2020,Zhang2022}.
 	For sequential decoding from primary to backscatter, \cite{Long2020a} pointed out the randomness from backscatter modulation can be modelled as either interference or channel uncertainty, depending on the symbol period ratio.
 	The authors concluded if this ratio is sufficiently large, the non-coherent primary achievable rate would asymptotically approach its coherent counterpart.
-	This motivated \cite{Long2020a,Ding2020,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Yang2018,Han2021,Zhang2022} to first decode the primary link, perform \gls{sic}, then decode the backscatter link.
+	This motivated \cite{Long2020a,Liang2020,Guo2019b,Ding2020,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Yang2018,Han2021,Zhang2022} to first decode the primary link, perform \gls{sic}, then decode the backscatter link.
 	However, the advantage of \gls{sic} is questionable because 1) sufficiently large symbol period ratio is assumed in primary rate analysis and constraints backscatter rate; 2) backscatter pattern and signal characteristics are not fully exploited; 3) non-coherent primary encoding is required at the transmitter, while re-encoding, precoding, and subtraction are required at the receiver; 4) primary and backscatter symbols are mixed by multiplication instead of superposition.
@@
 	\cite{Xu2021a} extended \gls{sic} to multi-node scenario and proposed a backscatter \gls{noma}-based \gls{sr} with decoding order following backscatter signal strength.
-	% \cite{Xu2021a} proposed a backscatter \gls{noma}-based \gls{sr} by extending \gls{sic} to multi-node scenario, where the decoding order depends on backscatter signal strength.
 	However, its performance deteriorates fast when the number of nodes increases.
 	Backscatter \gls{tdma} was also evaluated in \cite{Yang2021a}, where each node transmits information during dedicated slot and harvests energy during others.
-	% Although energy efficiency can be enhanced by transmission time and reflection ratio design, it requires regular feedback to passive nodes and incurs high coordination cost.
 	It enhances energy efficiency by transmission time and reflection ratio optimization, but requires regular feedback to passive nodes and incurs high coordination cost.
@@
 	However, it suffers from imperfect synchronization and the near-far problem.
-	% \cite{Zhou2019a} also explored the asymptotic impact of transmit/receive antenna and backscatter symbol period on the ergodic rate of primary and backscatter links.
-	% For a \gls{mimo} \gls{sr} system with a multi-antenna backscatter node, \cite{Wu2021a} proposed a beamforming design to maximize the backscatter rate while guaranteeing the primary performance.
-	% However, those paper only considered one backscatter node and backscatter multiple access remains an open issue.
-	% In \cite{Xu2021a}, a \gls{noma}-based \gls{sr} was proposed and receive combining was investigated when \gls{sic} order follows equivalent channel strength.
-	% A \gls{tdma}-based \gls{sr} with energy harvesting constraints was also presented in \cite{Yang2021a}, where transmit power, reflection efficiency, and time allocation were jointly optimized to maximize energy efficiency.
-	% To reduce coordination between passive nodes, \cite{Han2021} proposed a random code-assisted multiple access for \gls{sr} and evaluated the asymptotic \gls{sinr} using random matrix theory.
 
@@
 	The scattered signals contain no additional information, but adds constructively or destructively with the direct component to enhance desired signal or suppress interference.
-	% Compared with backscatter nodes of \gls{bc} and \gls{sr}, the reflection pattern of \gls{ris} elements are deterministic and priorly known at transmitter and receiver.
 	Compared with backscatter nodes of \gls{bc}/\gls{sr}, \gls{ris} elements employ deterministic reflection pattern priorly known at transmitter and receiver.
@@
 	It inspired \cite{Liu2019d,Bereyhi2020,Xu2020b,Zhang2021d,Hu2021b,Hua2022,Basar2020,Ma2020a,Yuan2021,Hu2021a} to employ \gls{ris} also as an information source to combine passive beamforming and backscatter modulation in the overall reflection pattern.
-	% In particular, \emph{symbol level precoding} maps backscatter symbols to optimized \gls{ris} coefficient sets \cite{Liu2019d,Bereyhi2020}, \emph{overlay modulation} superposes information-bearing symbols over a common auxiliary matrix \cite{Xu2020b,Zhang2021d,Hu2021b,Hua2022}, \emph{spatial modulation} switches between reflection coefficient sets that maximize \gls{snr} at different receive antennas \cite{Basar2020,Ma2020a,Yuan2021}, and \emph{index modulation} divides \gls{ris} into reflection elements for passive beamforming and information elements for on-off modulation \cite{Hu2021a}.
 	In particular, \emph{symbol level precoding} maps backscatter symbols to \gls{ris} coefficient sets optimized for detection \cite{Liu2019d,Bereyhi2020}, \emph{overlay modulation} superposes information-bearing symbols over a common auxiliary matrix \cite{Xu2020b,Zhang2021d,Hu2021b,Hua2022}, \emph{spatial modulation} switches between reflection coefficient sets that maximize \gls{snr} at different receive antennas \cite{Basar2020,Ma2020a,Yuan2021}, and \emph{index modulation} divides \gls{ris} into reflection elements for passive beamforming and information elements for on-off modulation \cite{Hu2021a}.
-	% However, those \gls{ris}-empowered \gls{bc} and \gls{sr} designs involve advanced hardware architecture, high optimization complexity, and additional control overhead.
-	However, those \gls{ris}-empowered \gls{bc} and \gls{sr} designs involve advanced hardware architecture and high optimization complexity.
-
-	% Compared to existing \gls{ris}-empowered \gls{sr} that encodes and precodes independently using advanced architecture (e.g., overlay or parallel), Metascatter softly bridges and generalizes parasitic source of \gls{sr} and reflecting element of \gls{ris} via smart input design.
-
-	To the best of our knowledge, all existing \gls{sr} literatures assumed backscatter modulation employs either Gaussian codebook \cite{Guo2019b,Ding2020,Long2020a,Zhou2019a,Wu2021a,Xu2021a,Yang2021a} or finite equiprobable inputs \cite{Yang2018,Han2021,Zhang2022,Xu2020b,Hua2022,Hu2021a}.
-	The former is impractical for passive nodes with constrained number of states, while the latter does not fully exploit \gls{csi} to boost achievable backscatter rate.
-	Besides, most relevant designs \cite{Guo2019b,Ding2020,Long2020a,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Yang2018,Han2021,Zhang2022,Xu2020b,Hua2022} were built over ideal \gls{ml} or \gls{sic} receiver.
-	However, the advantage of \gls{sic} is questionable because 1) it requires non-coherent primary encoding at the transmitter and re-encoding, precoding, and subtraction at the receiver, 2) the primary and backscatter symbols are mixed by multiplication instead of superposition, and 3) the backscatter symbol period is typically much longer due to physical constraints.
-	% Motivated by above, we propose a novel Metascatter network where multiple battery-free tags ride over a conventional point-to-point system and adapt their input probability distribution to simultaneously act as backscatter tags of \gls{sr} and reflecting elements of \gls{ris}.
-	Motivated by those, we propose the concept of Metascatter, which adapts the input distribution of a passive backscatter node to generalize backscatter sources of \gls{sr} and reflecting elements of \gls{ris}.
+	However, those \gls{ris}-empowered \gls{bc}/\gls{sr} designs involve advanced hardware architecture, high optimization complexity, and additional control overhead.
+
+	To the best of our knowledge, all relevant literatures assumed either Gaussian codebook \cite{Guo2019b,Ding2020,Long2020a,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Hu2021b} or finite equiprobable inputs \cite{Yang2018,Liang2020,Han2021,Zhang2022,Liu2019d,Bereyhi2020,Xu2020b,Zhang2021d,Hua2022,Basar2020,Ma2020a,Yuan2021,Hu2021a} at backscatter information sources.
+	The former is impractical for passive backscatter devices, while the latter does not fully exploit reflection pattern and \gls{csi}.
+	In this paper, we introduce the concept of UniScatter that generalizes \gls{bc}, \gls{sr}, and \gls{ris} to manipulate the transmit-assist tradeoff via smart input distribution and backscatter detector design.
+	The contributions of this paper are summarized as follows.
+
+	\emph{First,} we propose the UniScatter node that adapt input probability distribution of a finite-state passive scatter device based on link priority and \gls{csi}.
+	The reflection pattern over time is no longer fully random or deterministic, but can be flexibly distributed to unify and balance backscatter modulation and passive beamforming.
+	Scattering source of \gls{bc}/\gls{sr} and reflecting element of \gls{ris} can be regarded as its extreme cases, where the input distirbution boils down to equiprobable and degenerate, respectively.
+	Like aforementioned \gls{ris}-empowered \gls{bc}/\gls{sr} schemes, it requires regular coordination with passive nodes, but the advantages are 1) UniScatter nodes can be built over conventional load-switching scatterers instead of metamaterial; 2) the optimization cost of input distribution is much lower than that of \gls{ris} reflection coefficients; 3) adaptive backscatter channel coding can achieve higher instantaneous backscatter rate.
+
+	\emph{Second,} we propose a novel backscatter re
+
+	To fully accommodate backscatter characteristics, we also propose a novel receiving strategy that first jointly decodes all Metascatter from accumulated energy, then models their reflection pattern and backscatter paths within equivalent channel for primary decoding.
+	Since backscatter message is modulated over primary signal, backscatter decoding is indeed part of primary channel training, and there is no need for operation-intensive \gls{sic} at the receiver.
+
+	The reflection pattern over time is no longer fully random or deterministic, but can be flexibly distributed to balance backscatter encoding and passive beamforming.
+	For single-user scenario, when primary link is absolutely prioritized, the distribution falls on one state and Metascatter boils down to conventional \gls{ris}.
+	When only considering backscatter performance, the distribution involves the highest entropy and Metascatter is essentially an \gls{ambc} node.
+
+	nodes that adapts the input probability distribution of a finite-state passive backscatter device based on primary and (cascaded) backscatter \gls{csi} to unify and generalize parasitic source of \gls{sr} and reflecting elements of \gls{ris}.
+
+	% Motivated by those, we propose the concept of Metascatter, which adapts the input distribution of a passive backscatter node to generalize backscatter sources of \gls{sr} and reflecting elements of \gls{ris}.
 	% An application scenario was considered where multiple Metascatters are introduced to conventional point-to-point system and adapt their input probability distribution to simultaneously act as backscatter tags of \gls{sr} and reflecting elements of \gls{ris}.
 	% An application scenario was considered where multiple Metascatters ride over a point-to-point transmission and simultaneously perform backscatter encoding and passive beamforming.
+	% Compared to existing \gls{ris}-empowered \gls{sr} that encodes and precodes independently using advanced architecture (e.g., overlay or parallel), Metascatter softly bridges and generalizes parasitic source of \gls{sr} and reflecting element of \gls{ris} via smart input design.
 	% ! An application scenario was considered where multiple Metascatters ride over a point-to-point transmission to simultaneously encode self message and perform passive beamforming.
@@
 	% minor modifications on existing receivers, easy to perform, fits backscatter characteristics.
-	The contributions of this paper is summarized as follows.
+	% The contributions of this paper is summarized as follows.
 
@@
 	$\mathbb{R}_+^{x \times y}$ and $\mathbb{C}^{x \times y}$ respectively denote the space of real nonnegative and complex $x \times y$ matrices.
-	$\Delta^n = \left\{ (p_0,\dots,p_n) \in \mathbb{R}_+^{n+1}|\sum_{i=0}^n t_i = 1 \right\}$ denotes the standard $n$-simplex.
 	% $\Re\{\cdot\}$ retrieves the real part of a complex entity. $[\cdot]_{(n)}$ denotes the $n$-th entry of a vector and $[\cdot]_{(1:n)}$ denotes the first $n$ entries of a vector.

### 2022-08-08 src/region_tags.m
:truck: Rename files

@@ -6,7 +6,7 @@ Result(nVariables, nWeights) = struct('weight', [], 'rate', [], 'distribution', 
 % * Generate direct channel
 directChannel = rxGain * path_loss(frequency, directDistance, directExponent) * fading_ricean(nTxs, 1, directFactor);
 
-% * Evaluate rate region vs number of Metascatters
+% * Evaluate rate region vs number of tags
 for iVariable = 1 : nVariables
 	% * Set number of tags and update layout
 	nTags = Variable(iVariable).nTags;

### 2022-08-08 main.tex
:pencil: Update introduction

@@
 % dark mode
-\usepackage{xcolor} \pagecolor[rgb]{0,0,0} \color[rgb]{1,1,1}
+% \usepackage{xcolor} \pagecolor[rgb]{0,0,0} \color[rgb]{1,1,1}
 
@@
 \newacronym{ml}{ML}{Maximum-Likelihood}
+\newacronym{mrt}{MRT}{Maximum Ratio Transmission}
 \newacronym{noma}{NOMA}{Non-Orthogonal Multiple Access}
@@
 \begin{document}
-\title{UniScatter: Unifying\\Backscatter Communications, Symbiotic Radio, and Reconfigurable Intelligent Surface}
+\title{UniScatter: Unifying\\Backscatter Communications, Symbiotic Radio and Reconfigurable Intelligent Surface}
 \author{
@@
 	Using shared spectrum, energy, and infrastructures, UniScatter is a general and powerful transmit-assist protocol that unifies \gls{bc}, \gls{ris} and \gls{sr} with universal hardware design and augmented \gls{qos} control.
-	We consider an application scenario where a multi-antenna \gls{ap} serves a single-antenna user surrounded by multiple UniScatter nodes, and characterize the achievable primary-(total-)backscatter rate region by designing input distribution at the nodes, active beamforming at the \gls{ap}, and backscatter decision design at the user.
+	We consider an application scenario where a multi-antenna \gls{ap} serves a single-antenna user surrounded by multiple UniScatter nodes, and characterize the achievable primary-total-backscatter rate region by designing input distribution at the nodes, active beamforming at the \gls{ap}, and backscatter decision regions at the user.
 	Simulation results demonstrate UniScatter nodes can flexibly control the transmit-assist tradeoff via smart input distribution design.
@@
 	The former is impractical for passive backscatter devices, while the latter does not fully exploit reflection pattern and \gls{csi}.
-	In this paper, we introduce the concept of UniScatter that generalizes \gls{bc}, \gls{sr}, and \gls{ris} to manipulate the transmit-assist tradeoff via smart input distribution and backscatter detector design.
+	In this paper, we introduce UniScatter that generalizes \gls{bc}, \gls{sr}, and \gls{ris} to manipulate the transmit-assist tradeoff via smart input distribution and backscatter detector design.
 	The contributions of this paper are summarized as follows.
 
-	\emph{First,} we propose the UniScatter node that adapt input probability distribution of a finite-state passive scatter device based on link priority and \gls{csi}.
-	The reflection pattern over time is no longer fully random or deterministic, but can be flexibly distributed to unify and balance backscatter modulation and passive beamforming.
-	Scattering source of \gls{bc}/\gls{sr} and reflecting element of \gls{ris} can be regarded as its extreme cases, where the input distirbution boils down to equiprobable and degenerate, respectively.
-	Like aforementioned \gls{ris}-empowered \gls{bc}/\gls{sr} schemes, it requires regular coordination with passive nodes, but the advantages are 1) UniScatter nodes can be built over conventional load-switching scatterers instead of metamaterial; 2) the optimization cost of input distribution is much lower than that of \gls{ris} reflection coefficients; 3) adaptive backscatter channel coding can achieve higher instantaneous backscatter rate.
-
-	\emph{Second,} we propose a novel backscatter re
-
-	To fully accommodate backscatter characteristics, we also propose a novel receiving strategy that first jointly decodes all Metascatter from accumulated energy, then models their reflection pattern and backscatter paths within equivalent channel for primary decoding.
-	Since backscatter message is modulated over primary signal, backscatter decoding is indeed part of primary channel training, and there is no need for operation-intensive \gls{sic} at the receiver.
-
-	The reflection pattern over time is no longer fully random or deterministic, but can be flexibly distributed to balance backscatter encoding and passive beamforming.
-	For single-user scenario, when primary link is absolutely prioritized, the distribution falls on one state and Metascatter boils down to conventional \gls{ris}.
-	When only considering backscatter performance, the distribution involves the highest entropy and Metascatter is essentially an \gls{ambc} node.
-
-	nodes that adapts the input probability distribution of a finite-state passive backscatter device based on primary and (cascaded) backscatter \gls{csi} to unify and generalize parasitic source of \gls{sr} and reflecting elements of \gls{ris}.
-
-	% Motivated by those, we propose the concept of Metascatter, which adapts the input distribution of a passive backscatter node to generalize backscatter sources of \gls{sr} and reflecting elements of \gls{ris}.
-	% An application scenario was considered where multiple Metascatters are introduced to conventional point-to-point system and adapt their input probability distribution to simultaneously act as backscatter tags of \gls{sr} and reflecting elements of \gls{ris}.
-	% An application scenario was considered where multiple Metascatters ride over a point-to-point transmission and simultaneously perform backscatter encoding and passive beamforming.
-	% Compared to existing \gls{ris}-empowered \gls{sr} that encodes and precodes independently using advanced architecture (e.g., overlay or parallel), Metascatter softly bridges and generalizes parasitic source of \gls{sr} and reflecting element of \gls{ris} via smart input design.
-	% ! An application scenario was considered where multiple Metascatters ride over a point-to-point transmission to simultaneously encode self message and perform passive beamforming.
-	% To fully accommodate backscatter characteristics, we also propose a novel receiving strategy that first jointly decodes all Metascatter from accumulated energy, then models their reflection pattern and backscatter paths within equivalent channel for primary decoding.
-	% minor modifications on existing receivers, easy to perform, fits backscatter characteristics.
-	% The contributions of this paper is summarized as follows.
-
-	% ! Φ(c[n]) vs P
-	\emph{First,} Metascatter adapts the input probability distribution of a finite-state passive backscatter device based on primary and (cascaded) backscatter \gls{csi} to unify and generalize parasitic source of \gls{sr} and reflecting elements of \gls{ris}.
-	The reflection pattern over time is no longer fully random or deterministic, but can be flexibly distributed to balance backscatter encoding and passive beamforming.
-	For single-user scenario, when primary link is absolutely prioritized, the distribution falls on one state and Metascatter boils down to conventional \gls{ris}.
-	When only considering backscatter performance, the distribution involves the highest entropy and Metascatter is essentially an \gls{ambc} node.
-
-	\emph{Second,} we consider an application scenario where multiple Metascatters ride over a point-to-point transmission, exploiting additional propagation paths to simultaneously transmit and assist.
-	To fully accommodate backscatter characteristics, we also propose a novel receiving strategy that first jointly decodes all Metascatter from accumulated energy, then models their reflection pattern and backscatter paths within equivalent channel for primary decoding.
-	Since backscatter message is modulated over primary signal, backscatter decoding is indeed part of primary channel training, and there is no need for operation-intensive \gls{sic} at the receiver.
-
-	% \emph{Second,} we propose a novel receiving strategy where the backscatter symbol of all tags are first recovered by energy-based decoding, then modeled within equivalent \gls{csi} for primary decoding.
-	% When the ratio of backscatter symbol period over primary symbol period is large enough, the randomness of primary source can be averaged out and the performance of non-coherent backscatter decoding can be greatly improved.
-	% Since the primary and backscatter symbols are mixed by multiplication coding, the backscatter decoding can be viewed as part of primary channel training, which avoids non-coherent encoding at the transmitter and \gls{sic} at the receiver.
-
-	\emph{Third,} we evaluate the achievable primary-(total-)backscatter rate region by optimizing the input distribution at Metascatters, the active beamforming at the \gls{ap}, and the decision regions at the user.
-Since the original problem is highly non-convex, we consider a suboptimal \gls{bcd} algorithm where the \gls{kkt} input distribution is numerically evaluated by limit of sequences, the active beamforming is iteratively updated by \gls{pgd} accelerated by backtracking line search, and the decision regions are first restricted to convex, then refined by existing thresholding designs.
-
-	% \emph{Third,} we characterize the achievable primary-(total-)backscatter rate region by iteratively optimizing the tag input distribution, the backscatter decision threshold, and the transmit precoder.
-	% For the input design, we propose a numerical method to evaluate the \gls{kkt} solutions by limits of sequences.
-	% For the threshold design, we derive the minimum number of decision thresholds to maximize the total backscatter rate, and obtain the optimal thresholds by \gls{dp} accelerated by \gls{smawk} algorithm.
-	% However, the optimal precoder design can be non-trivial and we may end up with a low-complexity suboptimal solution.
+	\emph{First,} we propose UniScatter node to adapt the input probability distribution of a finite-state passive scatter device based on link priority and \gls{csi}.
+	The reflection pattern over time is no longer fully random or deterministic, but can be flexibly distributed to unify and balance backscatter modulation with passive beamforming.
+	Scattering source of \gls{bc}/\gls{sr} and reflecting element of \gls{ris} can be regarded as its extreme cases, where the input distribution boils down to equiprobable and degenerate, respectively.
+	Like aforementioned \gls{ris}-empowered \gls{bc}/\gls{sr} schemes, the passive nodes require regular coordination with active devices, but the advantages are 1) UniScatter nodes can be built over conventional load-switching scatterers instead of composite metamaterial; 2) the optimization cost of input distribution is much lower than that of \gls{ris} reflection coefficients; 3) adaptive channel coding at backscatter sources can exploit \gls{csi} to achieve higher instantaneous rate than conventional uncoded transmission.
+
+	\emph{Second,} we propose a practical receiving strategy that semi-coherently decodes all UniScatter messages from the received energy during each backscatter symbol block, re-encodes and recovers their reflection patterns at each primary block, combines those with relevant \gls{csi} to construct equivalent primary channels, then coherently decodes the primary link under adapted multipath.
+	The proposed receiver 1) preserves the benefits of backscatter modulation and passive beamforming; 2) enjoys lower computational and operational complexities than joint \gls{ml} and \gls{sic} schemes; 3) accommodates the difference of symbol period in backscatter decoding; 4) exploits the reflection patterns in primary decoding; 5) suits for diverse symbol period ratios.
+
+	\emph{Third,} we consider an application scenario where multiple UniScatter nodes ride over a point-to-point \gls{miso} transmission, performing backscatter modulation and passive beamforming to a nearby user using shared spectrum, energy, and infrastructures.
+	To investigate how UniScatter unifies \gls{bc}, \gls{sr} and \gls{ris} for the benefits of both coexisting subsystems, we provide primary and backscatter rate analyses and emphasize the contributions of input distribution at UniScatter nodes, active beamforming at the \gls{ap}, and backscatter decision regions at the user.
+	This is the first paper to reveal the importance of those factors in \gls{ris}-empowered \gls{bc}/\gls{sr}.
+
+	\emph{Fourth,} we characterize the achievable primary-total-backscatter rate region of the aforementioned system by optimizing the input distribution, active beamforming, and backscatter decision regions.
+	It is formulated as a weighted sum-rate maximization subject to input probability simplex, average transmit power, and sequential decision threshold constraints.
+	Since the original problem is highly non-convex, we decouple it into individual subproblems and constraint all decision regions to convex (connected) intervals.
+	A suboptimal \gls{bcd} algorithm is then proposed, where the \gls{kkt} input distribution is numerically evaluated by limit of sequences, the active beamforming is iteratively updated by \gls{pgd} accelerated by backtracking line search, and the decision regions are refined by existing thresholding designs.
+
+	\emph{Fifth,} we provide numerical results to demonstrate the benefits of UniScatter and proposed algorithms.
+	It is concluded that 1) UniScatter nodes provide flexible transmit-assist tradeoff using adaptive input distribution design; 2) when primary link is absolutely prioritized, the input probability of each node is \num{1} at one state and \num{0} at the others, which coincides with discretized \gls{ris}; 3) when backscatter link is absolutely prioritized, UniScatter nodes can exploit adaptive channel coding to achieve higher instantaneous rate than uncoded equiprobable transmission of \gls{bc}/\gls{sr}; 4) the proposed \gls{kkt} input distribution design converges to stationary points, whose average performance is very close to global optimal; 5) the \gls{pgd} beamforming achieves larger rate region than conventional \gls{mrt}; 6) the decision region schemes adapted to input distribution provide higher backscatter rates than the non-adaptive \gls{ml} detector; 7) cooperation between passive nodes in terms of joint encoding can further boost the total backscatter rate; 8) the low complexity of input distribution design and the marginal effect of increasing reflection states motivates the use of low-order scatter nodes to replace high-resolution \gls{ris}.
 
@@
 \begin{section}{Backscatter Principles}
-	% \begin{figure}[!t]
-	% 	\centering
-	% 	\subfloat[Block Diagram]{
-	% 		\resizebox{0.8\columnwidth}{!}{
-	% 			\input{assets/illustration/block_diagram.tex}
-	% 		}
-	% 		\label{fi:block_diagram}
-	% 	}
-	% 	\\
-	% 	\subfloat[Equivalent Circuit]{
-	% 		\resizebox{0.95\columnwidth}{!}{
-	% 			\input{assets/illustration/equivalent_circuit.tex}
-	% 		}
-	% 		\label{fi:equivalent_circuit}
-	% 	}
-	% 	\\
-	% 	\subfloat[Scatter Model]{
-	% 		\resizebox{0.8\columnwidth}{!}{
-	% 			\input{assets/illustration/scatter_model.tex}
-	% 		}
-	% 		\label{fi:scatter_model}
-	% 	}
-	% 	\caption{Block diagram, equivalent circuit, and scatter model of a typical passive tag.
-The solid and dashed vectors represent signal and energy flows.
-The backscatter antenna behaves as a constant power source, where the voltage $V_0$ and current $I_0$ are introduced by incident electric field $\vec{E}_{\mathrm{I}}$ and magnetic field $\vec{H}_{\mathrm{I}}$ \cite{Huang2021}.}
-	% \end{figure}
-
 	\begin{figure*}[!t]
@@
 
-	\begin{subsection}{SR: Backscatter Modulation}
+	\begin{subsection}{BackCom/SR: Backscatter Modulation}
 		% Backscatter sources encode self message by \emph{randomly changing reflection states.} For $M$-ary \gls{qam}, reflection coefficient $\Gamma_m$ maps to the corresponding complex constellation point $c_m$ by \cite{Thomas2012a}
@@
 
-	\begin{subsection}{IRS: Channel Reconfiguration}
+	\begin{subsection}{RIS: Channel Reconfiguration}
 		% \gls{ris} elements assist legacy transmission by \emph{deterministically choosing phase shifts} based on relevant \gls{csi}.
@@
 
-	\begin{subsection}{Metascatter: Bridge and Generalization}
+	\begin{subsection}{UniScatter: Bridge and Generalization}
 		\begin{figure}[!t]
@@
 			\caption{
-				Input probability distribution and time block structure of \gls{sr}, \gls{ris}, and Metascatter.
+				Input probability distribution and time block structure of \gls{sr}, \gls{ris}, and UniScatter.
 				$T_s$ and $T_c$ respectively denote the primary and backscatter symbol period.
-				Within channel coherence time, Metascatter semi-randomly selects reflection state for each backscatter block, with guidance from input probability distribution.
-			}
-			\label{fi:metascatter}
+				Within channel coherence time, UniScatter nodes semi-randomly select reflection state for each backscatter block, with guidance from input probability distribution.
+			}
+			\label{fi:uniscatter}
 		\end{figure}
 		% For a passive node with finite states, is it possible to unify backscatter modulation and channel reconfiguration by proper selection of reflection coefficient?
-		Metascatters simultaneously transmit and assist by \emph{adaptive input distribution design} based on primary and (cascaded) backscatter \gls{csi}.
+		UniScatter nodes simultaneously transmit and assist by \emph{adaptive input distribution design} based on primary and (cascaded) backscatter \gls{csi}.
 		% The reflection pattern is neither fully random nor fully deterministic, but flexibly distributed to balance backscatter encoding and passive beamforming.
 		% Instead of using fully random or deterministic reflection pattern over time, as shown in Fig.
-\ref{fi:metascatter}, Metascatter flexibly controls input distribution of candidate reflection states to balance backscatter encoding and passive beamforming.
+\ref{fi:uniscatter}, UniScatter flexibly controls input distribution of candidate reflection states to balance backscatter encoding and passive beamforming.
 		% Instead of using fully random or deterministic reflection pattern over time, as shown in Fig.
-\ref{fi:metascatter}, Metascatter semi-randomly selects reflection state for each backscatter block with guidance from \emph{input probability distribution $P(\Gamma_m)$.}
+\ref{fi:uniscatter}, UniScatter semi-randomly selects reflection state for each backscatter block with guidance from \emph{input probability distribution $P(\Gamma_m)$.}
 		% Instead of using fully random or deterministic reflection pattern over time, as shown in Fig.
-\ref{fi:metascatter}, Metascatter semi-randomly selects reflection state for each backscatter block, with guidance from \emph{input probability distribution $P(\Gamma_m)$.} In other words, it flexibly controls input distribution of candidate reflection states to balance backscatter encoding and passive beamforming.
-\gls{sr} and \gls{ris} can be regarded as extreme cases of Metascatter, where node input distribution boils down to uniform and deterministically biased, respectively.
+\ref{fi:uniscatter}, UniScatter semi-randomly selects reflection state for each backscatter block, with guidance from \emph{input probability distribution $P(\Gamma_m)$.} In other words, it flexibly controls input distribution of candidate reflection states to balance backscatter encoding and passive beamforming.
+\gls{sr} and \gls{ris} can be regarded as extreme cases of UniScatter, where node input distribution boils down to uniform and deterministically biased, respectively.
 		Instead of using fully random or deterministic reflection pattern over time, as shown in Fig.
-\ref{fi:metascatter}, Metascatter semi-randomly selects reflection state for each backscatter block, with \emph{guidance of input probability $P(\Gamma_m)$} for state $m$.
+\ref{fi:uniscatter}, UniScatter nodes semi-randomly select reflection state for each backscatter block, with \emph{guidance of input probability $P(\Gamma_m)$} for state $m$.
 In other words, it flexibly controls input distribution of candidate reflection states to balance backscatter encoding and passive beamforming.
-\gls{sr} and \gls{ris} can be regarded as extreme cases of Metascatter, where node input distribution boils down to uniform and deterministic, respectively.
+		% \gls{sr} and \gls{ris} can be regarded as extreme cases of UniScatter nodes, where node input distribution boils down to uniform and deterministic, respectively.
 		% flexibly controls input distribution of candidate reflection states to balance backscatter encoding and passive beamforming.
-		% Metascatter semi-randomly selects reflection state for each backscatter block, with guidance from \emph{input probability distribution $P(\Gamma_m)$.}
-		% % Based on \gls{csi}, Metascatter adapts the reflection state distribution to unify data transmission and channel reconfiguration.
+		% UniScatter semi-randomly selects reflection state for each backscatter block, with guidance from \emph{input probability distribution $P(\Gamma_m)$.}
+		% % Based on \gls{csi}, UniScatter adapts the reflection state distribution to unify data transmission and channel reconfiguration.
 		% \gls{sr} and \gls{ris} can be regarded as its extreme cases, where node input distribution boils down to uniform and deterministically biased, respectively.
-		% Within channel coherence time, Metascatter semi-randomly selects reflection state for each backscatter block, with guidance from \emph{input probability distribution $P(\Gamma_m)$.}
+		% Within channel coherence time, UniScatter semi-randomly selects reflection state for each backscatter block, with guidance from \emph{input probability distribution $P(\Gamma_m)$.}
 		\begin{remark}
-			Compared to conventional \gls{ris} literatures that optimize phase shifts under unit-module constraint, Metascatter starts from predefined reflection coefficients and designs their input distribution under sum-probability constraint to achieve flexible primary-backscatter tradeoff.
+			Compared to conventional \gls{ris} literatures that optimize phase shifts under unit-module constraint, UniScatter nodes start from predefined reflection coefficients and designs their input distribution under sum-probability constraint to achieve flexible primary-backscatter tradeoff.
 		\end{remark}
-		% Next, we will discuss the input design in a Metascatter-enabled network.
-		% consider a Metascatter-aided system to evaluate
+		% Next, we will discuss the input design in a UniScatter-enabled network.
+		% consider a UniScatter-aided system to evaluate
 	\end{subsection}
@@
 
-\begin{section}{Metascatter-Enabled Network}
+\begin{section}{UniScatter-Enabled Network}
 	\begin{subsection}{System Model}
@@
 			\footnotesize{
-				\import{assets/illustration/}{metascatter_network.eps_tex}
-			}
-			\caption{A Metascatter-enabled single-user multi-node network.}
-			\label{fi:metascatter_network}
+				\import{assets/illustration/}{uniscatter_network.eps_tex}
+			}
+			\caption{A UniScatter-enabled single-user multi-node network.}
+			\label{fi:uniscatter_network}
 		\end{figure}
-		% As shown in Fig. \ref{fi:metascatter_network}, we propose a Metascatter-enabled single-user multi-node network where the spectrum, energy and infrastructures are shared by two coexisting systems.
-		As shown in Fig. \ref{fi:metascatter_network}, we propose a Metascatter-enabled single-user multi-node network where two coexisting systems share spectrum, energy and infrastructures.
+		% As shown in Fig. \ref{fi:uniscatter_network}, we propose a UniScatter-enabled single-user multi-node network where the spectrum, energy and infrastructures are shared by two coexisting systems.
+		% UniScatter-enabled single-user multi-node \gls{miso} network where multiple UniScatter nodes ride over a point-to-point transmission to
+		As shown in Fig. \ref{fi:uniscatter_network}, we propose a UniScatter-enabled single-user multi-node \gls{miso} network where two coexisting systems share spectrum, energy and infrastructures.
 		% In the primary point-to-point system, the \gls{ap} transmits information to the single-antenna user.
-		% In the primary point-to-point system, a $Q$-antenna \gls{ap} transmit to a single-antenna user while assisted by $K$ nearby single-antenna Metascatters.
-		The primary point-to-point transmission from a $Q$-antenna \gls{ap} to a single-antenna user is assisted by $K$ nearby single-antenna Metascatters.
-		In the secondary backscatter \gls{mac} system, the \gls{ap} serves as the carrier emitter, $K$ nearby single-antenna Metascatters modulate information over reradiated \gls{rf} signals, and the user decodes their messages.
+		% In the primary point-to-point system, a $Q$-antenna \gls{ap} transmit to a single-antenna user while assisted by $K$ nearby single-antenna UniScatters.
+		The primary point-to-point transmission from a $Q$-antenna \gls{ap} to a single-antenna user is assisted by $K$ nearby single-antenna UniScatter nodes.
+		In the secondary backscatter \gls{mac} system, the \gls{ap} serves as the carrier emitter, $K$ nearby single-antenna UniScatter nodes modulate information over reradiated \gls{rf} signals, and the user decodes their messages.
 		For simplicity, we consider a quasi-static block fading model where channels remain constant within coherence interval while vary independently between consecutive blocks.
@@
 Also, define the cascaded channel of tag $k$ as $\boldsymbol{h}_{\mathrm{C},k}^H \triangleq h_{\mathrm{B},k} \boldsymbol{h}_{\mathrm{F},k}^H \in \mathbb{C}^{1 \times Q}$, and $\boldsymbol{H}_{\mathrm{C}} \triangleq [\boldsymbol{h}_{\mathrm{C},1},\ldots,\boldsymbol{h}_{\mathrm{C},K}]^H \in \mathbb{C}^{K \times Q}$.
-		% Let $x_{\mathcal{K}} \triangleq \{x_k : k \in \mathcal{K}\}$ be the backscatter symbols of all Metascatters.
-		Let $x_{\mathcal{K}} \triangleq (x_1,\ldots,x_K)$ be the backscatter symbol tuple of all Metascatters.
+		% Let $x_{\mathcal{K}} \triangleq \{x_k : k \in \mathcal{K}\}$ be the backscatter symbols of all UniScatters.
+		Let $x_{\mathcal{K}} \triangleq (x_1,\ldots,x_K)$ be the backscatter symbol tuple of all UniScatter nodes.
 		Consider the signal model during one backscatter block (i.e., $N$ primary blocks).
@@
 		\end{subequations}
-		where $\alpha_k$ is the amplitude reflect ratio of Metascatter $k$, $\boldsymbol{\alpha} \triangleq [\alpha_1,\ldots,\alpha_K]^T \in \mathbb{R}_+^{K \times 1}$, $x_k \in \mathcal{X} \triangleq \{c_1,\ldots,c_M\}$ is the coded backscatter symbol of Metascatter $k$, and $\boldsymbol{x} \triangleq [x_1,\ldots,x_K]^H \in \mathbb{C}^{K \times 1}$.
+		where $\alpha_k$ is the amplitude reflect ratio of UniScatter node $k$, $\boldsymbol{\alpha} \triangleq [\alpha_1,\ldots,\alpha_K]^T \in \mathbb{R}_+^{K \times 1}$, $x_k \in \mathcal{X} \triangleq \{c_1,\ldots,c_M\}$ is the coded backscatter symbol of node $k$, and $\boldsymbol{x} \triangleq [x_1,\ldots,x_K]^H \in \mathbb{C}^{K \times 1}$.
 The signal received by the user at primary block $n \in \mathcal{N} \triangleq \{1,\ldots,N\}$ is
@@
 		\begin{remark}
-			Metascatter involves a symbiotic \gls{mac} where the primary and backscatter symbols of different duration are mixed by \gls{mc} instead of \gls{sc}.
+			UniScatter involves a symbiotic \gls{mac} where the primary and backscatter symbols of different duration are mixed by \gls{mc} instead of \gls{sc}.
 			For each node, the reflection coefficient not only encodes the backscatter message, but also influences the equivalent primary channel \eqref{eq:equivalent_channel}.
@@
 	\begin{subsection}{Receiving Strategy}
-		We propose a Metascatter receiver where the backscatter messages of all Metascatters are first jointly and semi-coherently detected using total received energy per backscatter block, then modeled within equivalent channel \eqref{eq:equivalent_channel} as dynamic passive beamforming.
+		We propose a UniScatter receiver where the backscatter messages of all UniScatter nodes are first jointly and semi-coherently detected using total received energy per backscatter block, then modeled within equivalent channel \eqref{eq:equivalent_channel} as dynamic passive beamforming.
 		% identified by non-coherent energy detection, then
-		% Compared with conventional schemes as joint decoding and \gls{sic}, the Metascatter receiver may not achieve as high data rate for one tag, but it avoids non-coherent primary encoding and enables tag multiple access in a practical and low-complexity manner.
+		% Compared with conventional schemes as joint decoding and \gls{sic}, the UniScatter receiver may not achieve as high data rate for one tag, but it avoids non-coherent primary encoding and enables tag multiple access in a practical and low-complexity manner.
 		% Therefore, we believe it can be compatible to and readily implemented over legacy point-to-point systems.
-		Compared with \gls{ml} and \gls{sic}, Metascatter receiver allows practical and low-complexity node multiple access with minor adjustment over legacy equipments.
-
-		% At a specific backscatter block, denote $m_k \in \mathcal{M}$ as the state index of Metascatter $k$, and let $m_{\mathcal{K}} \triangleq \{m_k: k \in \mathcal{K}\}$ collect the state indexes of all Metascatters.
-		At a specific backscatter block, denote $m_k \in \mathcal{M}$ as the state index of Metascatter $k$, and let $m_{\mathcal{K}} \triangleq (m_1,\ldots,m_K)$ be the state index tuple of all Metascatters.
+		Compared with \gls{ml} and \gls{sic}, UniScatter receiver allows practical and low-complexity node multiple access with minor adjustment over legacy equipments.
+
+		% At a specific backscatter block, denote $m_k \in \mathcal{M}$ as the state index of UniScatter $k$, and let $m_{\mathcal{K}} \triangleq \{m_k: k \in \mathcal{K}\}$ collect the state indexes of all UniScatters.
+		At a specific backscatter block, denote $m_k \in \mathcal{M}$ as the state index of node $k$, and let $m_{\mathcal{K}} \triangleq (m_1,\ldots,m_K)$ be the state index tuple of all nodes.
 		% The received signal at primary block $n$ is subject to the variation of $s[n]$ and $v[n]$, and thus distributed as $y[n] \sim \mathcal{CN}(0,\sigma_v^2)$
@@
 		where $\mathcal{H}_{m_{\mathcal{K}}}$ denotes hypothesis $m_{\mathcal{K}}$.
-		% To accommodate backscatter characteristics and reduce decoding complexity, we consider a joint semi-coherent energy detection for all Metascatters based on disjoint decision regions over accumulated energy $z$.
-		To accommodate backscatter characteristics and reduce decoding complexity, we consider a joint semi-coherent detection for all Metascatters over accumulated energy $z$.
-		% To reduce decoding complexity, we consider a joint semi-coherent energy detection for all Metascatters based on disjoint decision regions over accumulated energy $z$.
+		% To accommodate backscatter characteristics and reduce decoding complexity, we consider a joint semi-coherent energy detection for all UniScatters based on disjoint decision regions over accumulated energy $z$.
+		To accommodate backscatter characteristics and reduce decoding complexity, we consider a joint semi-coherent detection for all UniScatter nodes over accumulated energy $z$.
+		% To reduce decoding complexity, we consider a joint semi-coherent energy detection for all UniScatters based on disjoint decision regions over accumulated energy $z$.
 		\begin{figure}[!t]
@@
 	\begin{subsection}{Achievable Rates}
-		Denote the input probability of state $m_k$ of Metascatter node $k$ as $P_k(x_{m_k})$, and define the input probability distribution vector of node $k$ as $\boldsymbol{p}_k \triangleq [P_k(c_1),\ldots,P_k(c_M)]^T \in \mathbb{R}^{M \times 1}$.
+		Denote the input probability of state $m_k$ of UniScatter node $k$ as $P_k(x_{m_k})$, and define the input probability distribution vector of node $k$ as $\boldsymbol{p}_k \triangleq [P_k(c_1),\ldots,P_k(c_M)]^T \in \mathbb{R}^{M \times 1}$.
 With independent encoding at all nodes, the probability of backscatter symbol tuple $x_{m_{\mathcal{K}}}$ is
@@
 \begin{section}{Input Distribution, Active Beamforming, and Decision Threshold Design}
-	To characterize the achievable primary-(total-)backscatter rate region of the proposed Metascatter-enabled network, we aim to maximize the weighted sum mutual information with respect to node input distributions $\{\boldsymbol{p}_k\}_{k \in \mathcal{K}}$, active beamforming vector $\boldsymbol{w}$, and decision threshold vector $\boldsymbol{t}$ as
+	To characterize the achievable primary-total-backscatter rate region of the proposed UniScatter-enabled network, we aim to maximize the weighted sum mutual information with respect to node input distributions $\{\boldsymbol{p}_k\}_{k \in \mathcal{K}}$, active beamforming vector $\boldsymbol{w}$, and decision threshold vector $\boldsymbol{t}$ as
 	\begin{maxi!}
@@
 	% TODO compare PGD and primary-MRT beamformers
-	In this section, we provide numerical results to evaluate the proposed input, beamforming and decision design over a single-user multi-node Metascatter-enabled network.
-	We assume the distance between \gls{ap} and user is \qty{10}{\meter}, and $K=2$ Metascatters are uniformly dropped within a disk centered at the user of radius \qty{1}{\meter}.
+	In this section, we provide numerical results to evaluate the proposed input, beamforming and decision design over a single-user multi-node UniScatter-enabled network.
+	We assume the distance between \gls{ap} and user is \qty{10}{\meter}, and $K=2$ UniScatter nodes are uniformly dropped within a disk centered at the user of radius \qty{1}{\meter}.
 	% The carrier frequency is $f=\qty{200}{\MHz}$, and we consider \gls{iid} Ricean fading for all channels.
@@
 	The \gls{ap} has $Q=4$ antennas with maximum average transmit power $P=\qty{36}{\dBm}$.
-	All nodes have amplitude reflect ratio $\alpha=0.5$, symbol period ratio $N=20$, and perform \gls{qam} with $M=2$ input states.
+	All nodes have amplitude reflect ratio $\alpha=0.5$, symbol period ratio $N=20$, and perform \gls{qam} with $M=4$ input states.
 	% and we consider amplitude reflect ratio $\alpha=0.5$ and symbol period ratio $N=20$.
@@
 			}
-			\caption{Typical input distributions vs. weight $\rho$ for a Metascatter with $M=4$ inputs.}
+			\caption{Typical input distributions vs. weight $\rho$ for a UniScatter node with $M=4$ inputs.}
 			\label{fi:distribution_weights}
 		\end{figure}
-		% We consider a single Metascatter with $M=4$ inputs in this case of study.
-		In Fig. \ref{fi:distribution_weights}, we present typical input distributions of a single Metascatter with $M=4$ inputs under different weight $\rho$.
+		% We consider a single UniScatter with $M=4$ inputs in this case of study.
+		In Fig. \ref{fi:distribution_weights}, we present typical input distributions of a single UniScatter node with $M=4$ inputs under different weight $\rho$.
 		Fig. \subref*{fi:distribution_weights_1} and \subref*{fi:distribution_weights_2} are obtained from \gls{iid} drop and channel realizations.
@@
 		On the other hand, the optimal input distribution becomes fully deterministic at $\rho=1$ (i.e., best primary performance), where the state maximizes equivalent primary channel \eqref{eq:equivalent_channel} strength is chosen with probability \num{1}.
-		In this case, Metascatter boils down to a \gls{ris} element with $M$ discrete states.
+		In this case, UniScatter node boils down to a \gls{ris} element with $M$ discrete states.
 		As $\rho$ moves from \num{0} to \num{1}, the optimal input distribution becomes gradually biased to one state and flexibly balances the primary-backscatter tradeoff.
@@
 			}
-			\caption{Average primary-(total-)backscatter rate regions for different input distribution and decision threshold schemes.}
+			\caption{Average primary-total-backscatter rate regions for different input distribution and decision threshold schemes.}
 		\end{figure}
@@
 			% \item ``\gls{kkt}'' corresponds to Algorithm \ref{al:input_distribution};
-			% \item ``Cooperation'' assumes backscatter cooperation/joint encoding at all Metascatters, and employs Blahut-Arimoto algorithm \cite{Arimoto1972,Blahut1972a} to determine \emph{tuple} input distribution;
+			% \item ``Cooperation'' assumes backscatter cooperation/joint encoding at all UniScatters, and employs Blahut-Arimoto algorithm \cite{Arimoto1972,Blahut1972a} to determine \emph{tuple} input distribution;
 			\item \textbf{Exhaustion:} $K$-dimensional grid search over probability simplex;
 			\item \textbf{\gls{kkt}:} results of Algorithm \ref{al:input_distribution};
-					% \item \textbf{Cooperation:} with backscatter cooperation/joint encoding at all Metascatters, Blahut-Arimoto algorithm \cite{Arimoto1972,Blahut1972a} for \emph{tuple} input distribution;
-					% \item \textbf{Cooperation:} backscatter cooperation/joint encoding at all Metascatters, \emph{tuple input distribution} by Blahut-Arimoto algorithm \cite{Arimoto1972,Blahut1972a};
-					% \item \textbf{Cooperation:} with backscatter cooperation (i.e., joint encoding) at all Metascatters, \emph{tuple input distribution} by Blahut-Arimoto algorithm \cite{Arimoto1972,Blahut1972a};
-			\item \textbf{Cooperation:} backscatter cooperation/joint encoding at all Metascatters, tuple input distribution/joint probability array optimization by Blahut-Arimoto algorithm \cite{Arimoto1972,Blahut1972a};
-					% with backscatter cooperation (i.e., joint encoding) at all Metascatters, \emph{tuple input distribution} by Blahut-Arimoto algorithm \cite{Arimoto1972,Blahut1972a};
+					% \item \textbf{Cooperation:} with backscatter cooperation/joint encoding at all UniScatters, Blahut-Arimoto algorithm \cite{Arimoto1972,Blahut1972a} for \emph{tuple} input distribution;
+					% \item \textbf{Cooperation:} backscatter cooperation/joint encoding at all UniScatters, \emph{tuple input distribution} by Blahut-Arimoto algorithm \cite{Arimoto1972,Blahut1972a};
+					% \item \textbf{Cooperation:} with backscatter cooperation (i.e., joint encoding) at all UniScatters, \emph{tuple input distribution} by Blahut-Arimoto algorithm \cite{Arimoto1972,Blahut1972a};
+			\item \textbf{Cooperation:} backscatter cooperation/joint encoding at all UniScatter nodes, tuple input distribution/joint probability array optimization by Blahut-Arimoto algorithm \cite{Arimoto1972,Blahut1972a};
+					% with backscatter cooperation (i.e., joint encoding) at all UniScatters, \emph{tuple input distribution} by Blahut-Arimoto algorithm \cite{Arimoto1972,Blahut1972a};
 			\item \textbf{Marginalization:} marginal distributions of joint probability array;
@@
 
-		We notice adaptive joint encoding at all Metascatters provides the outer bound of rate region.
+		We notice adaptive joint encoding at all nodes provides the outer bound of rate region.
 		However, it involves arbitrarily dependent codewords, and backscatter cooperation between passive nodes is generally unaffordable.
@@
 
-		We observe that input-adaptive threshold designs achieve higher total backscatter rate than \gls{ml}.
+		We observe that input distribution-adaptive threshold designs achieve higher total backscatter rate than \gls{ml}.
 		This is because the decision regions can be flexibly adjusted to enhance the capacity of \gls{dtmac} \eqref{eq:dtmac}.
@@
 
-		% We note that ideal joint adaptive encoding at all Metascatters can further boost the total backscatter rate.
+		% We note that ideal joint adaptive encoding at all UniScatters can further boost the total backscatter rate.
 		% However, this ideal upper bound requires real-time feedback
-		% ``Exhaustion'' means $K$-dimensional grid search over probability simplex, ``KKT'' corresponds to Algorithm \ref{ap:input_kkt_solution}, ``Cooperation'' assumes full backscatter cooperation and joint encoding at all Metascatters
+		% ``Exhaustion'' means $K$-dimensional grid search over probability simplex, ``KKT'' corresponds to Algorithm \ref{ap:input_kkt_solution}, ``Cooperation'' assumes full backscatter cooperation and joint encoding at all UniScatters
 	\end{subsection}
@@
 			}
-			\caption{Average primary-(total-)backscatter rate regions.}
+			\caption{Average primary-total-backscatter rate regions.}
 			\label{fi:region_config_1}
@@
 
-		% Fig. \ref{fi:region_config_1} reveals the impact of Metascatter nodes, input states, transmit antennas and scatter ratio on the achievable rate region.
-		We present in \ref{fi:region_config_1} the impact of Metascatter nodes, input states, transmit antennas and scatter ratio on the achievable rate region.
+		% Fig. \ref{fi:region_config_1} reveals the impact of UniScatter nodes, input states, transmit antennas and scatter ratio on the achievable rate region.
+		We present in \ref{fi:region_config_1} the impact of UniScatter nodes, input states, transmit antennas and scatter ratio on the achievable rate region.
 		For the specified scenario, Fig.
-\subref*{fi:region_tags} shows the total backscatter rate almost scales proportionally with the number of Metascatter nodes, and the decrease of individual backscatter rate is unobvious.
+\subref*{fi:region_tags} shows the total backscatter rate almost scales proportionally with the number of UniScatter nodes, and the decrease of individual backscatter rate is unobvious.
 		Besides, we conclude from \subref*{fi:region_states} that increasing the reflection states has a marginal effect on both primary and backscatter rates.
@@
 			}
-			\caption{Average primary-(total-)backscatter rate regions.}
+			\caption{Average primary-total-backscatter rate regions.}
 			\label{fi:region_config_2}
@@
 		However, it requires more frequent detection and re-encoding at the user to maintain the primary rate.
-		When $N$ becomes sufficiently large, total backscatter rate approaches \num{0} and Metascatters boil down to conventional \gls{ris} elements with fixed reflection pattern during whole channel block.
-		In Fig. \subref*{fi:region_frequency}, we observe that passive Metascatter achieves higher backscatter rate at lower carrier frequency because of preferable propagation loss.
+		When $N$ becomes sufficiently large, total backscatter rate approaches \num{0} and UniScatter nodes boil down to conventional \gls{ris} elements with fixed reflection pattern during whole channel block.
+		In Fig. \subref*{fi:region_frequency}, we observe that passive UniScatter nodes achieve higher backscatter rate at lower carrier frequency because of preferable propagation loss.
 		Finally, \subref*{fi:region_noise} prove the performance of energy detection is robust for a wide range of noise power.
@@
 \begin{section}{Conclusion}
-	This paper introduced Metascatter that adapts input distribution of passive backscatter nodes to simultaneously transmit and assist over existing wireless systems.
-	Starting from backscatter principles, we showed how Metascatters bridges and generalizes parasitic source of \gls{sr} and reflecting element of \gls{ris} via smart input design.
-	An application scenario was considered where multiple Metascatters ride over a point-to-point transmission to simultaneously encode self message and perform passive beamforming.
+	This paper introduced UniScatter that adapts input distribution of passive backscatter nodes to simultaneously transmit and assist over existing wireless systems.
+	Starting from backscatter principles, we showed how UniScatter nodes bridges and generalizes parasitic source of \gls{sr} and reflecting element of \gls{ris} via smart input design.
+	An application scenario was considered where multiple UniScatter nodes ride over a point-to-point transmission to simultaneously encode self message and perform passive beamforming.
 	To characterize achievable primary-backscatter rate region, we proposed a \gls{bcd} algorithm that evaluates \gls{kkt} input distribution in closed form, optimizes active beamforming by \gls{pgd}, and refines decision regions by existing methods.
@@
 
-	One particular interesting question is how to design Metascatters in a multi-user system.
+	One particular interesting question is how to design UniScatter node and receiver in a multi-user system.
 	If one node can contribute to and be decoded by multiple users, its input distribution may be further adjusted to mimic multi-beam gain of dynamic beamforming \cite{Qiu2022}.

### 2022-08-10 main.tex
:pencil: Update notations

@@
 % dark mode
-% \usepackage{xcolor} \pagecolor[rgb]{0,0,0} \color[rgb]{1,1,1}
+\usepackage{xcolor} \pagecolor[rgb]{0,0,0} \color[rgb]{1,1,1}
 
@@
 
-	\emph{Notations:} Scalars, vectors and matrices are respectively denoted by italic, bold lower-case, and bold upper-case letters.
-	$j$ represents the imaginary unit.
-	% $\boldsymbol{0}$ and $\boldsymbol{1}$ denote respectively zero and one vector or matrix.
-	% $\boldsymbol{I}$ represents the identity matrix.
-	% $\mathbb{R}_+^{x \times y}$ and $\mathbb{C}^{x \times y}$ denote respectively the space of real nonnegative and complex $x \times y$ matrices.
-	$\mathbb{R}_+^{x \times y}$ and $\mathbb{C}^{x \times y}$ respectively denote the space of real nonnegative and complex $x \times y$ matrices.
-	% $\Re\{\cdot\}$ retrieves the real part of a complex entity. $[\cdot]_{(n)}$ denotes the $n$-th entry of a vector and $[\cdot]_{(1:n)}$ denotes the first $n$ entries of a vector.
-	$(\cdot)^*$, $(\cdot)^T$, $(\cdot)^H$, $(\cdot)^+$, $\lvert{\cdot}\rvert$, $\lVert{\cdot}\rVert$ respectively represent the conjugate, transpose, conjugate transpose, ramp function, absolute value, and Euclidean norm.
-	% $\arg(\cdot)$, $\mathrm{rank}(\cdot)$, $\mathrm{tr}(\cdot)$, $\mathrm{diag}(\cdot)$ and $\mathrm{diag}^{-1}(\cdot)$ respectively denote the argument, rank, trace, a square matrix with input vector on the main diagonal, and a vector retrieving the main diagonal of the input matrix.
-	% $\odot$ denotes the Hadamard product.
-	% $\boldsymbol{S} \succeq \boldsymbol{0}$ means $\boldsymbol{S}$ is positive semi-definite.
-	% $\mathbb{A}\{\cdot\}$ extracts the DC component of a signal.
-	% $\mathbb{E}_X\{\cdot\}$ takes expectation w.r.t. random variable $X$ ($X$ is omitted for simplicity).
-	The distribution of a CSCG random vector with mean $\boldsymbol{0}$ and covariance $\boldsymbol{\Sigma}$ is denoted by $\mathcal{CN}(\boldsymbol{0},\boldsymbol{\Sigma})$.
-	$\sim$ means ``distributed as''.
-	$(\cdot)^{(i)}$ represents the $i$-th iterated value and $(\cdot)^{\star}$ represents the end solution.
+	\emph{Notations:}
+	Italic, bold lower-case, and bold upper-case letters denote scalars, vectors and matrices, respectively.
+	$\boldsymbol{0}$ and $\boldsymbol{1}$ denote zero and one array of appropriate size, respectively.
+	$\mathbb{R}_+^{x \times y}$ and $\mathbb{C}^{x \times y}$ denote the real nonnegative and complex spaces of dimension $x \times y$, respectively.
+	$j$ denotes the imaginary unit.
+	$(\cdot)^*$, $(\cdot)^T$, $(\cdot)^H$, $\lvert{\cdot}\rvert$, and $\lVert{\cdot}\rVert$ denote the conjugate, transpose, conjugate transpose, absolute value, and Euclidean norm operators, respectively.
+	$(\cdot)^{(r)}$ and $(\cdot)^{\star}$ denote the $r$-th iterated and terminal solutions, respectively.
+	The distribution of a \gls{cscg} random variable with zero mean and variance $\sigma^2$ is denoted by $\mathcal{CN}(0,\sigma^2)$, and $\sim$ means ``distributed as''.
 \end{section}

### 2022-08-11 main.tex
:pencil: Update scatter principles

@@
 	$j$ denotes the imaginary unit.
+	$\arg(\cdot)$, $\mathrm{rank}(\cdot)$, $\mathrm{tr}(\cdot)$, $\mathrm{diag}(\cdot)$ and $\mathrm{diag}^{-1}(\cdot)$ denote the argument, rank, trace, a square matrix with input vector on main diagonal, and a vector retrieving main diagonal of input square matrix, respectively.
 	$(\cdot)^*$, $(\cdot)^T$, $(\cdot)^H$, $\lvert{\cdot}\rvert$, and $\lVert{\cdot}\rVert$ denote the conjugate, transpose, conjugate transpose, absolute value, and Euclidean norm operators, respectively.
@@
 
-\begin{section}{Backscatter Principles}
+% \begin{section}{Scattering/Reflecting Principles}
+\begin{section}{Scattering Principles}
 	\begin{figure*}[!t]
@@
 	\end{figure*}
+	% The introduction of an obstacle in the path of a plane electromagnetic wave produces scattering.
+	Scattering is defined as a change of moving direction of particles after colliding with others.
+	% It often refers to the diffuse reflection where the incident particles are redistributed at many angles rather than the opposite direction.
+	It often refers to \emph{diffuse reflection} where an incident ray is redistributed at many angles.
+	An electromagnetic wave is scattered when an obstruction is placed in its path.
+	% In \gls{rf} applications such as \gls{bc}, \gls{sr} and \gls{ris}, the scatterer often includes integrated antenna or programmable metamaterial for controllable reflection pattern \cite{Liang2022}.
+	% In \gls{rf} applications such as \gls{bc}, \gls{sr} and \gls{ris}, the scatterer often includes integrated antenna or programmable metamaterial for the diversity of reflection patterns \cite{Liang2022}.
+	In \gls{rf} applications such as \gls{bc}, \gls{sr} and \gls{ris}, the scatterer often includes variable-load antenna or programmable metamaterial for various reflection patterns \cite{Liang2022}.
+	% For the former case, the signal impinging on the antenna is first received,
+	% For the former case, the antenna first receives the impinging signal, then reradiates a part and absorb the rest.
+	The antenna-based scatterer first receive the impinging signals, then reradiate a portion back to the space and absorb the remainder potentially for energy harvesting.
+	% According to \cite{Hansen1989}, the reradiated part can be decomposed into \emph{structural} component that consistently contributes to environment multipath and \emph{antenna} component that depends on antenna-load impedance mismatch.
+	According to \cite{Hansen1989}, its reradiated part can be decomposed into \emph{structural} component that consistently contributes to environment multipath and \emph{antenna} component that depends on antenna-load impedance mismatch.
+	The former is modelled within channel estimation while the latter is controlled by load switching \cite{Boyer2014}.
+	For antenna-based scatterers, the reflection coefficient at (load) state $m$ is%
+	\footnote{It corresponds to a linear scatter model where the reflection coefficient is irrelevant to incident electromagnetic field strength.}
+	\begin{equation}
+		\Gamma_m = \frac{Z_m - Z_{\mathrm{A}}^*}{Z_m + Z_{\mathrm{A}}},
+		\label{eq:reflection_coefficient}
+	\end{equation}
+	where $Z_m$ is the load impedance at state $m$ and $Z_{\mathrm{A}}$ is the antenna input impedance.
+	On the other hand, ideal metamaterial-based scatterers reflect the incident waves without receiving them, and the reflection happens at the interface between free space and metamaterial.
+	% The reflection happens at the interface between free space and metamaterial, and the reflection coefficient at metamaterial unit is
+	% The reflection happens at the interface between free space and metamaterial.
+	For metamaterial-based scatterers with a discrete impedance set, the reflection coefficient at (metamaterial) state $m$ is
+	\begin{equation}
+		\Gamma_m = \frac{Z_m - Z_0}{Z_m + Z_0},
+	\end{equation}
+	where $Z_0 = \qty{377}{\ohm}$ is the characteristic impedance of free space.
+
+	% When illuminated, the node absorbs a portion of the impinging wave for information decoding and energy harvesting \cite{Kim2021a}, while scatters the remaining back to the space.
+The scattered signal is further decomposed into the \emph{structural} component that consistently contributes to environment multipath and covered by channel estimation \cite{Boyer2014}, and the
+	When illuminated, the node absorbs a portion of the impinging wave for information decoding and/or energy harvesting \cite{Kim2021a}, and backscatters the remaining as \emph{structural} and \emph{antenna} components.
+	% The scattered signal is further decomposed into the \emph{structural} component that consistently contributes to environment multipath and covered by channel estimation \cite{Boyer2014}, and the \emph{antenna} mode component that
+	% and \emph{antenna} mode components \cite{Hansen1989}.
+	The former consistently contributes to environment multipath and can be modelled by channel estimation \cite{Boyer2014}, while the latter depends on antenna-load impedance mismatch and can be used for backscatter modulation \cite{Boyer2012} and/or channel reconfiguration \cite{Wu2021b}.
+	% Depending on structure, shape and material of general objects, structural scattering consistently contributes to environment multipath and is covered by channel estimation \cite{Boyer2014}.
+	% In contrast, antenna scattering models radiation pattern from antenna-load impedance mismatch and can be used for backscatter modulation \cite{Boyer2012} and/or channel reconfiguration \cite{Wu2021b}.
+
+	signal impinging on the antenna is first received,
+
+	Diffuse reflection is the reflection of light or other waves or particles from a surface such that a ray incident on the surface is scattered at many angles rather than at just one angle as in the case of specular reflection.
+
+	% By definition, reflection
+	% Scattering refers to a diffuse reflection
+	scattering, in physics, a change in the direction of motion of a particle because of a collision with another particle.
+	Scattering thus refers to particle-particle collisions between molecules, atoms, electrons, photons and other particles.
+	wave scattering corresponds to the collision and scattering of a wave with some material object, for instance (sunlight) scattered by rain drops to form a rainbow.
 
@@
 	Fig. \subref*{fi:scatter_model} illustrates the scatter model of a node with $M$ states, where the reflection coefficient of state $m \in \mathcal{M} \triangleq \{1,\ldots,M\}$ is defined as%
-	\footnote{It corresponds to a linear backscatter model where the reflection coefficient is irrelevant to incident electromagnetic field strength.}
-	\begin{equation}
-		\Gamma_m = \frac{Z_m - Z_{\mathrm{A}}^*}{Z_m + Z_{\mathrm{A}}},
-		\label{eq:reflection_coefficient}
-	\end{equation}
+	% \footnote{It corresponds to a linear backscatter model where the reflection coefficient is irrelevant to incident electromagnetic field strength.}
+	% \begin{equation}
+	% 	\Gamma_m = \frac{Z_m - Z_{\mathrm{A}}^*}{Z_m + Z_{\mathrm{A}}},
+	% 	\label{eq:reflection_coefficient}
+	% \end{equation}
 	where $Z_m$ is the load impedance at state $m$ and $Z_{\mathrm{A}}$ is the antenna input impedance.

### 2022-08-11 main.tex
:pencil: Update scatter principles

--- 2022-08-10 main.tex
@@
 	\end{figure*}
+	\begin{subsection}{Scatterer Categories}
+		Scattering is defined as a change of moving direction of particles after colliding with others.
+		It often refers to \emph{diffuse reflection} where an incident ray is redistributed at many angles.
+		An electromagnetic wave is scattered when an obstruction is placed in its path.
+		In \gls{rf} applications such as \gls{bc}, \gls{sr} and \gls{ris}, the scatterer often includes variable-load antenna or programmable metamaterial to realize various reflection patterns \cite{Liang2022}.
+		\begin{subsubsection}{Antenna-Based Scatterer}
+			Antenna-based scatterers first receive the impinging signals, then reradiate a portion back to the space and absorb the remainder potentially for energy harvesting.
+			According to \cite{Hansen1989}, its reradiated part can be decomposed into \emph{structural} component that consistently contributes to environment multipath, and \emph{antenna} component that depends on antenna-load impedance mismatch.
+			The former is modelled within channel estimation while the latter is controlled by load switching \cite{Boyer2014}.
+			For antenna-based scatterers, the reflection coefficient at (load) state $m$ is%
+			\footnote{It corresponds to a linear scatter model where the reflection coefficient is irrelevant to incident electromagnetic field strength.}
+			\begin{equation}
+				\Gamma_m = \frac{Z_m - Z_{\mathrm{A}}^*}{Z_m + Z_{\mathrm{A}}},
+				\label{eq:reflection_coefficient}
+			\end{equation}
+			where $Z_m$ is the load impedance at state $m$ and $Z_{\mathrm{A}}$ is the antenna input impedance.
+		\end{subsubsection}
+		\begin{subsubsection}{Metamaterial-Based Scatterer}
+			% ? [Do we discuss unit or surface here?] As shown in Fig. 3(a), the metamaterial-based RIS is realized by a metasurface, which is composed of a large number of periodic metamaterial units
+
+			Ideal metamaterial-based scatterers reflect the incident waves without receiving them, and the reflection happens at the interface between free space and metamaterial.
+			For metamaterial-based scatterers with a discrete impedance set, the reflection coefficient at (metamaterial) state $m$ is
+			\begin{equation}
+				\Gamma_m = \frac{Z_m - Z_0}{Z_m + Z_0},
+			\end{equation}
+			where $Z_m$ is the equivalent impedance of metamaterial unit at state $m$, and $Z_0 = \qty{377}{\ohm}$ is the characteristic impedance of free space.
+		\end{subsubsection}
+	\end{subsection}
 

### 2022-08-12 main.tex
:pencil: Update metamaterial-based scatterers

--- 2022-08-10 main.tex
@@
 	\end{figure*}
+	\begin{subsection}{Scatterer Categories}
+		Scattering refers to a change of moving direction of particles after colliding with others.
+		It often involves \emph{diffuse reflection} where an incident ray is redistributed at many angles.
+		An electromagnetic wave is scattered when an obstruction is placed in its path.
+		In \gls{rf} applications such as \gls{bc}, \gls{sr} and \gls{ris}, the scatterer often includes \emph{variable-load antenna} or \emph{programmable metamaterial} to produce various reflection patterns \cite{Liang2022}.
+		\begin{subsubsection}{Antenna-Based Scatterer}
+			Antenna-based scatterers first receive the impinging signals, then reradiate some back to the space and absorb the remainder potentially for energy harvesting.
+			According to \cite{Hansen1989}, the reradiated part can be decomposed into \emph{structural} component that consistently contributes to the environment multipath, and \emph{antenna} component that depends on the antenna-load impedance mismatch.
+			The former is modelled within channel estimation while the latter can be controlled by load switching \cite{Boyer2014}.
+			For antenna-based scatterers, the reflection coefficient at load state $m$ is%
+			\footnote{It corresponds to a linear scatter model where the reflection coefficient is irrelevant to incident electromagnetic field strength.}
+			\begin{equation}
+				\Gamma_m = \frac{Z_m - Z_{\mathrm{A}}^*}{Z_m + Z_{\mathrm{A}}},
+				\label{eq:reflection_coefficient}
+			\end{equation}
+			where $Z_m$ is the load impedance at state $m$ and $Z_{\mathrm{A}}$ is the antenna input impedance.
+		\end{subsubsection}
+		\begin{subsubsection}{Metamaterial-Based Scatterer}
+			% The core concept of metamaterials is to produce materi- als by using artificially designed and fabricated structural units made of metallic or dielectric materials to achieve the desired properties and functionalities.
+These subwave- length structural units—the constituent artificial “atoms” and “molecules” of the metamaterial—can be tailored in shape and size.
+
+			% The lattice constant and interatomic inter- action can be artificially tuned.
+They can be designed and placed at desired locations.
+By engineering the arrange- ment of these small unit cells into the desired architecture or geometry, one can tune the effective permittivity or permeability of the metamaterial to positive, near-zero, or negative values.
+Thus, metamaterials can be endowed with properties and functionalities unattainable in natural materials [11], [12].
+
+			% 2) Epsilon-negative (ENG) materials: They display a neg- ative permittivity ε but positive permeability μ.
+ENG could be formed using conducting rods (thin wires).
+In this case, the refractive index becomes imaginary, and EM waves cannot propagate in the material but are reflected at the boundary between air and the medium.
+Any propagation into the medium would be evanescent.
+3) Mu-negative (MNG) materials: They have a positive ε but negative μ.
+MNG and could be formed using split-ring resonators (SRRs).
+Again, in this case, the refractive index becomes imaginary, and EM waves cannot propagate in the material and will be reflected at the boundary between air and the material.
+
+			% The metamaterials, in general, are composite materials.
+Each unit cell (SRR or other designs) has an individually tailored response to the EM field.
+This is similar to how light interacts with everyday materials; materials such as glass or lenses are made of atoms.
+An averaging or macroscopic effect is produced.
+The cell of a metamaterial is designed to mimic the EM response of atoms, only on a much larger scale.
+Also, as part of periodic com- posite structures, these are designed to have a stronger EM coupling than that found in nature.
+The larger scale allows for more control over the EM response, while each unit is smaller than the wavelength of the radiated EM wave.
+Achieving fascinating functionalities of metamaterials typically entails multiple stacks of material layers, which not only leads to extensive loss but also brings a lot of challenges in fabrication.
+Many metamaterials consist of complex metallic wires and other structures that require sophisticated fabrication technology and are difficult to assemble.
+3-D metamaterials can be extended by arranging electrically small scatters or holes into a 2-D pattern at a surface or interface.
+This surface version of a metamaterial has been given the name metasurface.
+For many applica- tions, metasurfaces can be used in place of metamaterials.
+They have the advantage of taking up less physical space than full 3-D metamaterial structures do; consequently, they offer the possibility of less-lossy structures as well.
+
+			% In metamaterial-based RIS, the equivalent impedance depends on various factors related to the design of the metamaterial unit.
+Therefore, there exist several meth- ods to change the equivalent impedances and, thus, the reconfigurable reflection coefficients.
+The first one is to use functional materials, such as graphene [73] and liquid crystals [74], [75], whose relative permittivity can be var- ied with the applied voltage.
+The second one is to change the physical structure of the metamaterial unit, such as the physical dimension or orientation of the unit [76], [77].
+The third one is to vary the external biasing voltage applied on the tunable electronic devices, such as p-i-n diodes and varactor diodes [72], [78]–[82].
+
+			Metamaterial consists of numerous sub-wavelength structural units made of metallic or dielectric materials.
+			% The shape and size of each unit cell can be artificially altered for customized response to the electromagnetic field.
+			% One can change the effective permittivity or permeability of the metamaterial by manipulating the lattice constant and inter-atomic interaction \cite{Zhou2021}.
+			The properties of unit cells can be artificially tuned for unconventional effective permittivity $\epsilon$ and permeability $\mu$, bringing customizable response to the electromagnetic field \cite{Zhou2021}.
+			Using epsilon-negative material (e.g., conducing rods) or mu-negative material (e.g., split-ring resonators), ideal metamaterial-based scatterers can reflect the incident waves at the boundary between free space and metamaterial without receiving them \cite{Huang2021a}.
+			This mainly applies a phase shift on the reflected wave because any propagation into the metamaterial would be evanescent.
+			% It mainly applies a phase shift on the reflected wave, while any propagation into the metamaterial would be evanescent.
+			% The reflection happens at the boundary between free space and metamaterial, which mainly applies a phase shift on the reflected wave.
+			% There exists several methods to change the equivalent impedance of metamaterial unit, such as
+			% applied voltage on
+			% functional materials, such as graphene [73] and liquid crystals [74], [75]
+			Depending on the type of metamaterial, its equivalent impedance can be controlled by voltage (for functional materials \cite{Singh2020} and tunable diodes \cite{Costa2021}) or architecture (for resonant elements \cite{Bialkowski2008}).
+			For metamaterial-based scatterers with a discrete impedance set, the reflection coefficient at metamaterial state $m$ is
+			\begin{equation}
+				\Gamma_m = \frac{Z_m - Z_0}{Z_m + Z_0},
+			\end{equation}
+			where $Z_m$ is the equivalent impedance of metamaterial unit at state $m$, and $Z_0 = \qty{377}{\ohm}$ is the characteristic impedance of free space.
+		\end{subsubsection}
+		% TODO discuss how BC, SR, RIS relates to both
+	\end{subsection}
 

### 2022-08-13 main.tex
:pencil: Update metamaterial-based scatterers
:pencil: Update antenna-based scatterer

@@
 		It often involves \emph{diffuse reflection} where an incident ray is redistributed at many angles.
-		An electromagnetic wave is scattered when an obstruction is placed in its path.
-		In \gls{rf} applications such as \gls{bc}, \gls{sr} and \gls{ris}, the scatterer often includes \emph{variable-load antenna} or \emph{programmable metamaterial} to produce various reflection patterns \cite{Liang2022}.
+		An electromagnetic wave is scattered when an obstruction is placed in its propagation path.
+		In \gls{rf} applications such as \gls{bc}, \gls{sr} and \gls{ris}, the scatterer often includes \emph{variable-load antenna} or \emph{programmable metamaterial} with various reflection patterns \cite{Liang2022}.
 		\begin{subsubsection}{Antenna-Based Scatterer}
-			Antenna-based scatterers first receive the impinging signals, then reradiate some back to the space and absorb the remainder potentially for energy harvesting.
-			According to \cite{Hansen1989}, the reradiated part can be decomposed into \emph{structural} component that consistently contributes to the environment multipath, and \emph{antenna} component that depends on the antenna-load impedance mismatch.
-			The former is modelled within channel estimation while the latter can be controlled by load switching \cite{Boyer2014}.
+			A typical antenna-based scatterer consists of an integrated antenna, a load-switching modulator, an energy harvester, and on-chip components (e.g., microcontroller and sensors) \cite{Dobkin2012}.
+			It first receives the impinging signals, then reradiates some back to the space and dissipates the remainder.
+			According to transmission line theory, the scatter-absorb tradeoff depends on the impedance matching of the load and the antenna.
+			For passive scatterers without dedicated energy source, a majority of incident wave is harvested to support node operation and the reradiated part can be relatively weak \cite{Thomas2012a}.
+			% For passive tags, $\alpha \ll 1$ is commonly assumed as the majority of the incident wave can be harvested to support tag modules \cite{Thomas2012a}.
+			% To support the operation of on-chip components, the majority of incident wave is consumed for energy harvesting
+			% According to \cite{Hansen1989}, the reradiated part can be decomposed into \emph{structural} component that consistently contributes to the environment multipath, and \emph{antenna} component that depends on the antenna-load impedance mismatch.
+			At the receiver, the observed signal can be further decomposed into \emph{structural mode} and \emph{antenna mode} components \cite{Hansen1989}.
+			The former consistently contributes to environment multipath and is modelled within channel estimation, while the latter depends on impedance mismatch and can be used for backscatter modulation \cite{Boyer2014} and/or channel reconfiguration \cite{Liang2022}.
 			For antenna-based scatterers, the reflection coefficient at load state $m$ is%
@@
 			where $Z_m$ is the load impedance at state $m$ and $Z_{\mathrm{A}}$ is the antenna input impedance.
+			% Antenna-based scatterers are typically considered in \gls{bc} and \gls{sr} literatures, while some \gls{ris}
+			% BC and SR typically antenna-based, RIS both
 		\end{subsubsection}
@@
 
-			Metamaterial consists of numerous sub-wavelength structural units made of metallic or dielectric materials.
+			% Metamaterial consists of numerous sub-wavelength structural units made of metallic or dielectric materials.
+			A typical metamaterial-based scatterer consists of multiple material layers and a smart controller \cite{Wu2020}.
+			The outer metamaterial layer involves numerous sub-wavelength structural units made of metallic or dielectric materials.
 			% The shape and size of each unit cell can be artificially altered for customized response to the electromagnetic field.
 			% One can change the effective permittivity or permeability of the metamaterial by manipulating the lattice constant and inter-atomic interaction \cite{Zhou2021}.
-			The properties of unit cells can be artificially tuned for unconventional effective permittivity $\epsilon$ and permeability $\mu$, bringing customizable response to the electromagnetic field \cite{Zhou2021}.
+			The properties of unit cells can be artificially tuned for unconventional effective permittivity $\epsilon$ and permeability $\mu$, producing customizable response to the electromagnetic field \cite{Zhou2021}.
 			Using epsilon-negative material (e.g., conducing rods) or mu-negative material (e.g., split-ring resonators), ideal metamaterial-based scatterers can reflect the incident waves at the boundary between free space and metamaterial without receiving them \cite{Huang2021a}.
-			This mainly applies a phase shift on the reflected wave because any propagation into the metamaterial would be evanescent.
+			This mainly applies a phase shift on the reflected wave and any propagation into the metamaterial would be evanescent.
 			% It mainly applies a phase shift on the reflected wave, while any propagation into the metamaterial would be evanescent.
@@
 			\end{equation}
-			where $Z_m$ is the equivalent impedance of metamaterial unit at state $m$, and $Z_0 = \qty{377}{\ohm}$ is the characteristic impedance of free space.
+			where $Z_m$ is the equivalent impedance of metamaterial unit at state $m$ and $Z_0 = \qty{377}{\ohm}$ is the characteristic impedance of free space.
 		\end{subsubsection}
-		% TODO discuss how BC, SR, RIS relates to both
+		% TODO discuss how BC, SR, RIS relates to both: BC and SR typically antenna-based, RIS both
 	\end{subsection}
@@
 		\end{equation}
-		where $0 \le \alpha \le 1$ is the amplitude reflect ratio that controls the harvest-scatter tradeoff at the direction of interest.
+		where $0 \le \alpha \le 1$ is the amplitude scattering ratio that controls the harvest-scatter tradeoff at the direction of interest.
 		% When the \gls{csi} and reflection alphabet $\{\Gamma_1,\ldots,\Gamma_M\}$ are available at the reader, it can decode the tag message from the observed scattered signal.
@@
 		\end{equation}
-		where $0 \le \beta_m \le 1$ is overall amplitude reflect ratio of state $m$.
+		where $0 \le \beta_m \le 1$ is overall amplitude scattering ratio of state $m$.
 		% Based on relevant \gls{csi}
@@
 		\end{figure}
-		% For a passive node with finite states, is it possible to unify backscatter modulation and channel reconfiguration by proper selection of reflection coefficient?
+		% ? For a passive node with finite states, is it possible to unify backscatter modulation and channel reconfiguration by proper selection of reflection coefficient?
 		UniScatter nodes simultaneously transmit and assist by \emph{adaptive input distribution design} based on primary and (cascaded) backscatter \gls{csi}.
@@
 		\end{subequations}
-		where $\alpha_k$ is the amplitude reflect ratio of UniScatter node $k$, $\boldsymbol{\alpha} \triangleq [\alpha_1,\ldots,\alpha_K]^T \in \mathbb{R}_+^{K \times 1}$, $x_k \in \mathcal{X} \triangleq \{c_1,\ldots,c_M\}$ is the coded backscatter symbol of node $k$, and $\boldsymbol{x} \triangleq [x_1,\ldots,x_K]^H \in \mathbb{C}^{K \times 1}$.
+		where $\alpha_k$ is the amplitude scattering ratio of UniScatter node $k$, $\boldsymbol{\alpha} \triangleq [\alpha_1,\ldots,\alpha_K]^T \in \mathbb{R}_+^{K \times 1}$, $x_k \in \mathcal{X} \triangleq \{c_1,\ldots,c_M\}$ is the coded backscatter symbol of node $k$, and $\boldsymbol{x} \triangleq [x_1,\ldots,x_K]^H \in \mathbb{C}^{K \times 1}$.
 The signal received by the user at primary block $n \in \mathcal{N} \triangleq \{1,\ldots,N\}$ is
@@
 	The \gls{ap} has $Q=4$ antennas with maximum average transmit power $P=\qty{36}{\dBm}$.
-	All nodes have amplitude reflect ratio $\alpha=0.5$, symbol period ratio $N=20$, and perform \gls{qam} with $M=4$ input states.
-	% and we consider amplitude reflect ratio $\alpha=0.5$ and symbol period ratio $N=20$.
+	All nodes have amplitude scattering ratio $\alpha=0.5$, symbol period ratio $N=20$, and perform \gls{qam} with $M=4$ input states.
+	% and we consider amplitude scattering ratio $\alpha=0.5$ and symbol period ratio $N=20$.
 	% The user has a receive antenna gain of \qty{3}{\dBi} and average noise power

### 2022-08-13 main.tex
:pencil: Update scattering principles

@@
 	$j$ denotes the imaginary unit.
-	$\arg(\cdot)$, $\mathrm{rank}(\cdot)$, $\mathrm{tr}(\cdot)$, $\mathrm{diag}(\cdot)$ and $\mathrm{diag}^{-1}(\cdot)$ denote the argument, rank, trace, a square matrix with input vector on main diagonal, and a vector retrieving main diagonal of input square matrix, respectively.
+	% $\arg(\cdot)$, $\mathrm{rank}(\cdot)$, $\mathrm{tr}(\cdot)$, $\mathrm{diag}(\cdot)$ and $\mathrm{diag}^{-1}(\cdot)$ denote the argument, rank, trace, a square matrix with input vector on main diagonal, and a vector retrieving main diagonal of input square matrix, respectively.
+	$\mathrm{diag}(\cdot)$ returns a square matrix with the input vector on main diagonal.
 	$(\cdot)^*$, $(\cdot)^T$, $(\cdot)^H$, $\lvert{\cdot}\rvert$, and $\lVert{\cdot}\rVert$ denote the conjugate, transpose, conjugate transpose, absolute value, and Euclidean norm operators, respectively.
@@
 
-% \begin{section}{Scattering/Reflecting Principles}
 \begin{section}{Scattering Principles}
@@
 			For passive scatterers without dedicated energy source, a majority of incident wave is harvested to support node operation and the reradiated part can be relatively weak \cite{Thomas2012a}.
-			% For passive tags, $\alpha \ll 1$ is commonly assumed as the majority of the incident wave can be harvested to support tag modules \cite{Thomas2012a}.
-			% To support the operation of on-chip components, the majority of incident wave is consumed for energy harvesting
-			% According to \cite{Hansen1989}, the reradiated part can be decomposed into \emph{structural} component that consistently contributes to the environment multipath, and \emph{antenna} component that depends on the antenna-load impedance mismatch.
 			At the receiver, the observed signal can be further decomposed into \emph{structural mode} and \emph{antenna mode} components \cite{Hansen1989}.
@@
 			where $Z_m$ is the load impedance at state $m$ and $Z_{\mathrm{A}}$ is the antenna input impedance.
-			% Antenna-based scatterers are typically considered in \gls{bc} and \gls{sr} literatures, while some \gls{ris}
-			% BC and SR typically antenna-based, RIS both
 		\end{subsubsection}
 		\begin{subsubsection}{Metamaterial-Based Scatterer}
-			% The core concept of metamaterials is to produce materi- als by using artificially designed and fabricated structural units made of metallic or dielectric materials to achieve the desired properties and functionalities.
-These subwave- length structural units—the constituent artificial “atoms” and “molecules” of the metamaterial—can be tailored in shape and size.
-
-			% The lattice constant and interatomic inter- action can be artificially tuned.
-They can be designed and placed at desired locations.
-By engineering the arrange- ment of these small unit cells into the desired architecture or geometry, one can tune the effective permittivity or permeability of the metamaterial to positive, near-zero, or negative values.
-Thus, metamaterials can be endowed with properties and functionalities unattainable in natural materials [11], [12].
-
-			% 2) Epsilon-negative (ENG) materials: They display a neg- ative permittivity ε but positive permeability μ.
-ENG could be formed using conducting rods (thin wires).
-In this case, the refractive index becomes imaginary, and EM waves cannot propagate in the material but are reflected at the boundary between air and the medium.
-Any propagation into the medium would be evanescent.
-3) Mu-negative (MNG) materials: They have a positive ε but negative μ.
-MNG and could be formed using split-ring resonators (SRRs).
-Again, in this case, the refractive index becomes imaginary, and EM waves cannot propagate in the material and will be reflected at the boundary between air and the material.
-
-			% The metamaterials, in general, are composite materials.
-Each unit cell (SRR or other designs) has an individually tailored response to the EM field.
-This is similar to how light interacts with everyday materials; materials such as glass or lenses are made of atoms.
-An averaging or macroscopic effect is produced.
-The cell of a metamaterial is designed to mimic the EM response of atoms, only on a much larger scale.
-Also, as part of periodic com- posite structures, these are designed to have a stronger EM coupling than that found in nature.
-The larger scale allows for more control over the EM response, while each unit is smaller than the wavelength of the radiated EM wave.
-Achieving fascinating functionalities of metamaterials typically entails multiple stacks of material layers, which not only leads to extensive loss but also brings a lot of challenges in fabrication.
-Many metamaterials consist of complex metallic wires and other structures that require sophisticated fabrication technology and are difficult to assemble.
-3-D metamaterials can be extended by arranging electrically small scatters or holes into a 2-D pattern at a surface or interface.
-This surface version of a metamaterial has been given the name metasurface.
-For many applica- tions, metasurfaces can be used in place of metamaterials.
-They have the advantage of taking up less physical space than full 3-D metamaterial structures do; consequently, they offer the possibility of less-lossy structures as well.
-
-			% In metamaterial-based RIS, the equivalent impedance depends on various factors related to the design of the metamaterial unit.
-Therefore, there exist several meth- ods to change the equivalent impedances and, thus, the reconfigurable reflection coefficients.
-The first one is to use functional materials, such as graphene [73] and liquid crystals [74], [75], whose relative permittivity can be var- ied with the applied voltage.
-The second one is to change the physical structure of the metamaterial unit, such as the physical dimension or orientation of the unit [76], [77].
-The third one is to vary the external biasing voltage applied on the tunable electronic devices, such as p-i-n diodes and varactor diodes [72], [78]–[82].
-
-			% Metamaterial consists of numerous sub-wavelength structural units made of metallic or dielectric materials.
 			A typical metamaterial-based scatterer consists of multiple material layers and a smart controller \cite{Wu2020}.
 			The outer metamaterial layer involves numerous sub-wavelength structural units made of metallic or dielectric materials.
-			% The shape and size of each unit cell can be artificially altered for customized response to the electromagnetic field.
-			% One can change the effective permittivity or permeability of the metamaterial by manipulating the lattice constant and inter-atomic interaction \cite{Zhou2021}.
 			The properties of unit cells can be artificially tuned for unconventional effective permittivity $\epsilon$ and permeability $\mu$, producing customizable response to the electromagnetic field \cite{Zhou2021}.
@@
 			This mainly applies a phase shift on the reflected wave and any propagation into the metamaterial would be evanescent.
-			% It mainly applies a phase shift on the reflected wave, while any propagation into the metamaterial would be evanescent.
-			% The reflection happens at the boundary between free space and metamaterial, which mainly applies a phase shift on the reflected wave.
-			% There exists several methods to change the equivalent impedance of metamaterial unit, such as
-			% applied voltage on
-			% functional materials, such as graphene [73] and liquid crystals [74], [75]
 			Depending on the type of metamaterial, its equivalent impedance can be controlled by voltage (for functional materials \cite{Singh2020} and tunable diodes \cite{Costa2021}) or architecture (for resonant elements \cite{Bialkowski2008}).
@@
 		\end{subsubsection}
-		% TODO discuss how BC, SR, RIS relates to both: BC and SR typically antenna-based, RIS both
-	\end{subsection}
-
-	Passive backscatter nodes harvest energy from and modulate information over surrounding \gls{rf} signals.
-	As shown in Fig.
-\subref*{fi:block_diagram}, a typical passive node consists of a scattering antenna, an energy harvester, an integrated receiver, a load-switching modulator, and on-chip components (e.g., micro-controller and sensors) \cite{Dobkin2012}.
-	Its equivalent circuit is presented in Fig. \subref*{fi:equivalent_circuit}.
-	% When illuminated, the node absorbs a portion of the impinging wave for information decoding and energy harvesting \cite{Kim2021a}, while scatters the remaining back to the space.
-The scattered signal is further decomposed into the \emph{structural} component that consistently contributes to environment multipath and covered by channel estimation \cite{Boyer2014}, and the
-	When illuminated, the node absorbs a portion of the impinging wave for information decoding and/or energy harvesting \cite{Kim2021a}, and backscatters the remaining as \emph{structural} and \emph{antenna} components.
-	% The scattered signal is further decomposed into the \emph{structural} component that consistently contributes to environment multipath and covered by channel estimation \cite{Boyer2014}, and the \emph{antenna} mode component that
-	% and \emph{antenna} mode components \cite{Hansen1989}.
-	The former consistently contributes to environment multipath and can be modelled by channel estimation \cite{Boyer2014}, while the latter depends on antenna-load impedance mismatch and can be used for backscatter modulation \cite{Boyer2012} and/or channel reconfiguration \cite{Wu2021b}.
-	% Depending on structure, shape and material of general objects, structural scattering consistently contributes to environment multipath and is covered by channel estimation \cite{Boyer2014}.
-	% In contrast, antenna scattering models radiation pattern from antenna-load impedance mismatch and can be used for backscatter modulation \cite{Boyer2012} and/or channel reconfiguration \cite{Wu2021b}.
-	Fig. \subref*{fi:scatter_model} illustrates the scatter model of a node with $M$ states, where the reflection coefficient of state $m \in \mathcal{M} \triangleq \{1,\ldots,M\}$ is defined as%
-	% \footnote{It corresponds to a linear backscatter model where the reflection coefficient is irrelevant to incident electromagnetic field strength.}
-	% \begin{equation}
-	% 	\Gamma_m = \frac{Z_m - Z_{\mathrm{A}}^*}{Z_m + Z_{\mathrm{A}}},
-	% 	\label{eq:reflection_coefficient}
-	% \end{equation}
-	where $Z_m$ is the load impedance at state $m$ and $Z_{\mathrm{A}}$ is the antenna input impedance.
+	\end{subsection}
 
 	\begin{subsection}{BackCom/SR: Backscatter Modulation}
-		% Backscatter sources encode self message by \emph{randomly changing reflection states.} For $M$-ary \gls{qam}, reflection coefficient $\Gamma_m$ maps to the corresponding complex constellation point $c_m$ by \cite{Thomas2012a}
-		Backscatter sources encode self message by \emph{random reflection states variation.} For $M$-ary \gls{qam}, reflection coefficient $\Gamma_m$ maps to the corresponding \emph{complex constellation point $c_m$} by \cite{Thomas2012a}
+		\gls{bc} and \gls{sr} commonly employ antenna-based scatterers as backscatter information sources.
+		% Backscatter information sources of \gls{bc} and \gls{sr} encode self message by \emph{random reflection states variation.}
+		For $M$-ary \gls{qam}, reflection coefficient $\Gamma_m$ maps to the corresponding \emph{complex constellation point $c_m$} by \cite{Thomas2012a}
 		\begin{equation}
@@
 		\end{equation}
-		where $0 \le \alpha \le 1$ is the amplitude scattering ratio that controls the harvest-scatter tradeoff at the direction of interest.
+		where $0 \le \alpha \le 1$ is the amplitude scattering ratio at the direction of interest.
 		% When the \gls{csi} and reflection alphabet $\{\Gamma_1,\ldots,\Gamma_M\}$ are available at the reader, it can decode the tag message from the observed scattered signal.
 		% ! Use larger alpha in simulation: for high-order QAM, some constellation point may harvests more power than others
+		% TODO by switching between reflection states, backscatter modulation introduces uncertainty.
 
@@
 For a reflecting element with $M$ candidate states, reflection coefficient $\Gamma_m$ maps to the corresponding phase shift $\theta_m$ by \cite{Wu2018}
-		\gls{ris} elements assist legacy transmission by \emph{deterministic phase shifts selection} based on relevant \gls{csi}.
-		For a reflecting element with $M$ candidate states, reflection coefficient $\Gamma_m$ relates to the corresponding \emph{phase shift $\theta_m$} by \cite{Wu2018}
+		% \gls{ris} involves numerous
+		\gls{ris} involves either a planar scattering antenna array or a metasurface of numerous metamaterial units.
+		% Reflecting elements of \gls{ris} assist legacy transmission by \emph{deterministic phase shifts selection} based on relevant \gls{csi}.
+		For each unit with $M$ candidate states, reflection coefficient $\Gamma_m$ maps to the corresponding \emph{phase shift $\theta_m$} by \cite{Wu2018}
 		\begin{equation}
@@
 		\end{equation}
-		where $0 \le \beta_m \le 1$ is overall amplitude scattering ratio of state $m$.
+		where $0 \le \beta_m \le 1$ is the overall amplitude scattering ratio of state $m$.
 		% Based on relevant \gls{csi}
@@
 		\end{figure}
+		% ! Passive backscatter nodes harvest energy from and modulate information over surrounding \gls{rf} signals.
+		% As shown in Fig.
+\subref*{fi:block_diagram}, a typical passive node consists of a scattering antenna, an energy harvester, an integrated receiver, a load-switching modulator, and on-chip components (e.g., micro-controller and sensors) \cite{Dobkin2012}.
+		% Its equivalent circuit is presented in Fig. \subref*{fi:equivalent_circuit}.
+		% When illuminated, the node absorbs a portion of the impinging wave for information decoding and/or energy harvesting \cite{Kim2021a}, and backscatters the remaining as \emph{structural} and \emph{antenna} components.
+		% The former consistently contributes to environment multipath and can be modelled by channel estimation \cite{Boyer2014}, while the latter depends on antenna-load impedance mismatch and can be used for backscatter modulation \cite{Boyer2012} and/or channel reconfiguration \cite{Wu2021b}.
+		% Fig. \subref*{fi:scatter_model} illustrates the scatter model of a node with $M$ states.
+
 		% ? For a passive node with finite states, is it possible to unify backscatter modulation and channel reconfiguration by proper selection of reflection coefficient?
@@
 
-\begin{section}{UniScatter-Enabled Network}
+\begin{section}{UniScatter}
 	\begin{subsection}{System Model}

### 2022-08-14 main.tex
:pencil: Update scattering principles

@@
 	\begin{subsection}{BackCom/SR: Backscatter Modulation}
-		\gls{bc} and \gls{sr} commonly employ antenna-based scatterers as backscatter information sources.
-		% Backscatter information sources of \gls{bc} and \gls{sr} encode self message by \emph{random reflection states variation.}
+		\gls{bc} and \gls{sr} commonly employ antenna-based scatterers as passive information sources.
+		By \emph{frequently switching} between the available states, each backscatter node encodes self message over scattered signal and introduces backscatter uncertainty at the receiver.
 		For $M$-ary \gls{qam}, reflection coefficient $\Gamma_m$ maps to the corresponding \emph{complex constellation point $c_m$} by \cite{Thomas2012a}
@@
 		where $0 \le \alpha \le 1$ is the amplitude scattering ratio at the direction of interest.
-		% When the \gls{csi} and reflection alphabet $\{\Gamma_1,\ldots,\Gamma_M\}$ are available at the reader, it can decode the tag message from the observed scattered signal.
-		% ! Use larger alpha in simulation: for high-order QAM, some constellation point may harvests more power than others
-		% TODO by switching between reflection states, backscatter modulation introduces uncertainty.
-
 	\end{subsection}
@@
 		% \gls{ris} involves numerous
-		\gls{ris} involves either a planar scattering antenna array or a metasurface of numerous metamaterial units.
+		\gls{ris} typically involves a planar antenna array or metasurface of numerous metamaterial units as a passive channel reconfigurator.
+		% By \emph{adaptively deciding} the reflection pattern, each reflecting element alters the phase of reflected signal for constructive/destructive superposition at the receiver.
+		By \emph{adaptively choosing} the reflection pattern, each reflecting element alters the phase of scattered signal for constructive/destructive superposition at the receiver.
+		% Compared with backscatter nodes of \gls{bc}/\gls{sr}, \gls{ris} elements employ deterministic reflection pattern priorly known at transmitter and receiver.
 		% Reflecting elements of \gls{ris} assist legacy transmission by \emph{deterministic phase shifts selection} based on relevant \gls{csi}.
@@
 	\begin{subsection}{UniScatter: Bridge and Generalization}
+		% TODO compare BC, SR and IRS
 		\begin{figure}[!t]

### 2022-08-14 main.tex
:pencil: Add transition to UniScatter

@@
 				\Gamma_m = \frac{Z_m - Z_{\mathrm{A}}^*}{Z_m + Z_{\mathrm{A}}},
-				\label{eq:reflection_coefficient}
+				\label{eq:reflection_pattern_antenna}
 			\end{equation}
@@
 				\Gamma_m = \frac{Z_m - Z_0}{Z_m + Z_0},
+				\label{eq:reflection_pattern_metamaterial}
 			\end{equation}
@@
 	\begin{subsection}{RIS: Channel Reconfiguration}
-		% \gls{ris} elements assist legacy transmission by \emph{deterministically choosing phase shifts} based on relevant \gls{csi}.
-For a reflecting element with $M$ candidate states, reflection coefficient $\Gamma_m$ maps to the corresponding phase shift $\theta_m$ by \cite{Wu2018}
-		% \gls{ris} involves numerous
 		\gls{ris} typically involves a planar antenna array or metasurface of numerous metamaterial units as a passive channel reconfigurator.
-		% By \emph{adaptively deciding} the reflection pattern, each reflecting element alters the phase of reflected signal for constructive/destructive superposition at the receiver.
 		By \emph{adaptively choosing} the reflection pattern, each reflecting element alters the phase of scattered signal for constructive/destructive superposition at the receiver.
-		% Compared with backscatter nodes of \gls{bc}/\gls{sr}, \gls{ris} elements employ deterministic reflection pattern priorly known at transmitter and receiver.
-		% Reflecting elements of \gls{ris} assist legacy transmission by \emph{deterministic phase shifts selection} based on relevant \gls{csi}.
 		For each unit with $M$ candidate states, reflection coefficient $\Gamma_m$ maps to the corresponding \emph{phase shift $\theta_m$} by \cite{Wu2018}
@@
 			\Gamma_m = \beta_m \exp(j \theta_m),
+			\label{eq:passive_beamforming}
 		\end{equation}
 		where $0 \le \beta_m \le 1$ is the overall amplitude scattering ratio of state $m$.
-		% Based on relevant \gls{csi}
-	\end{subsection}
-	% Tags periodically switch between different states to perform backscatter modulation.
-	% For $M$-ary \gls{qam}, the complex constellation point $c_m \in \mathcal{C}$ maps to the reflection coefficient by \cite{Thomas2012a}
-	% \begin{equation}
-	% 	\Gamma_m = \alpha \frac{c_m}{\max_{m'} \lvert c_{m'} \rvert},
-	% 	\label{eq:backscatter_modulation}
-	% \end{equation}
-	% where $\alpha \in [0,1]$ models the harvest-backscatter ratio at the direction of interest.
-	% For passive tags, $\alpha \ll 1$ is commonly assumed as the majority of the incident wave can be harvested to support tag modules \cite{Thomas2012a}.
-
-	\begin{subsection}{UniScatter: Bridge and Generalization}
+	\end{subsection}
+
+	% \begin{subsection}{Opportunities and Challenges}
+	\begin{subsection}{Opportunities}
+		We have seen conventional scattering applications as \gls{bc}, \gls{sr} and \gls{ris} using the reflection pattern \eqref{eq:reflection_pattern_antenna}, \eqref{eq:reflection_pattern_metamaterial} for either backscatter modulation \eqref{eq:backscatter_modulation} or passive beamforming \eqref{eq:passive_beamforming}.
+		A natural but critical question is, for a given scatterer with pre-determined reflection pattern set, \emph{can we softly bridge backscatter modulation and passive beamforming by appropriate reflection design?}
+		This question is answered in Section \ref{se:uniscatter}.
+	\end{subsection}
+\end{section}
+
+\begin{section}{UniScatter}
+	\begin{subsection}{UniScatter Nodes}
 		% TODO compare BC, SR and IRS
@@
 	\end{subsection}
-\end{section}
-
-\begin{section}{UniScatter}
+
 	\begin{subsection}{System Model}
@@
 	\end{subsection}
+	\label{se:uniscatter}
 \end{section}

### 2022-08-14 main.tex
:pencil: Add introduction to UniScatter

@@
 \begin{section}{Scattering Principles}
-	\begin{figure*}[!t]
-		\centering
-		\subfloat[Block Diagram]{
-			\resizebox{0.32\linewidth}{!}{
-				\input{assets/illustration/block_diagram.tex}
-			}
-			\label{fi:block_diagram}
-		}
-		\subfloat[Equivalent Circuit]{
-			\resizebox{0.37\linewidth}{!}{
-				\input{assets/illustration/equivalent_circuit.tex}
-			}
-			\label{fi:equivalent_circuit}
-		}
-		\subfloat[Scatter Model]{
-			\resizebox{0.28\linewidth}{!}{
-				\input{assets/illustration/scatter_model.tex}
-			}
-			\label{fi:scatter_model}
-		}
-		\caption{Block diagram, equivalent circuit, and scatter model of a passive backscatter node.
-The solid and dashed vectors represent signal and energy flows.
-The backscatter antenna behaves as a constant power source, where the voltage $V_0$ and current $I_0$ are introduced by incident electric field $\vec{E}_{\mathrm{I}}$ and magnetic field $\vec{H}_{\mathrm{I}}$ \cite{Huang2021}.}
-	\end{figure*}
-	\begin{subsection}{Scatterer Categories}
 	Scattering refers to a change of moving direction of particles after colliding with others.
@@
 	An electromagnetic wave is scattered when an obstruction is placed in its propagation path.
+	% In this section, we first introduce the principles of two common scatterer categories, then briefly
+	In this section, we first introduce two common scatterer categories and review their operation principles, then briefly discuss how scatterers realize backscatter modulation and channel reconfiguration over reflection patterns.
+	\begin{subsection}{Scatterer Categories}
 		In \gls{rf} applications such as \gls{bc}, \gls{sr} and \gls{ris}, the scatterer often includes \emph{variable-load antenna} or \emph{programmable metamaterial} with various reflection patterns \cite{Liang2022}.
@@
 
-	% \begin{subsection}{Opportunities and Challenges}
 	\begin{subsection}{Opportunities}
@@
 \begin{section}{UniScatter}
+	We introduce UniScatter as a novel low-power communication/assistance protocol that generalizes \gls{bc}, \gls{sr} and \gls{ris} using shared spectrum, energy and infrastructures.
+	% In particular, the passive UniScatter nodes ride over an active legacy transmission to simultaneously encode self information and reconfigure wireless environment.
+	% Using shared spectrum, energy and infrastructures, the passive UniScatter nodes ride over an active legacy transmission for backscatter modulation and passive beamforming, while the low-complexity cooperative UniScatter receiver decodes both links
+	% In particular, the passive UniScatter nodes adapt input distribution based on link priority and \gls{csi}
+	In particular, the passive UniScatter nodes ride over an active legacy transmission in a flexible and mutualistic manner, while the practical cooperative UniScatter receiver decodes both links under the benefits of backscatter modulation and passive beamforming.
 	\begin{subsection}{UniScatter Nodes}
+		\begin{figure*}[!t]
+			\centering
+			\subfloat[Block Diagram]{
+				\resizebox{0.32\linewidth}{!}{
+					\input{assets/illustration/block_diagram.tex}
+				}
+				\label{fi:block_diagram}
+			}
+			\subfloat[Equivalent Circuit]{
+				\resizebox{0.37\linewidth}{!}{
+					\input{assets/illustration/equivalent_circuit.tex}
+				}
+				\label{fi:equivalent_circuit}
+			}
+			\subfloat[Scatter Model]{
+				\resizebox{0.28\linewidth}{!}{
+					\input{assets/illustration/scatter_model.tex}
+				}
+				\label{fi:scatter_model}
+			}
+			\caption{Block diagram, equivalent circuit, and scatter model of a passive backscatter node.
+The solid and dashed vectors represent signal and energy flows.
+The backscatter antenna behaves as a constant power source, where the voltage $V_0$ and current $I_0$ are introduced by incident electric field $\vec{E}_{\mathrm{I}}$ and magnetic field $\vec{H}_{\mathrm{I}}$ \cite{Huang2021}.}
+		\end{figure*}
 		% TODO compare BC, SR and IRS
@@
 		\end{figure}
+		% ! antenna-based
 		% ! Passive backscatter nodes harvest energy from and modulate information over surrounding \gls{rf} signals.

### 2022-08-15 main.tex
:pencil: Update UniScatter node

--- 2022-08-14 main.tex
@@
 \title{UniScatter: Unifying\\Backscatter Communications, Symbiotic Radio and Reconfigurable Intelligent Surface}
+% \title{UniScatter: Unifying Backcatter Modulation and Passive Beamforming by Adaptive Input Distribution}
 \author{
@@
 	% $\arg(\cdot)$, $\mathrm{rank}(\cdot)$, $\mathrm{tr}(\cdot)$, $\mathrm{diag}(\cdot)$ and $\mathrm{diag}^{-1}(\cdot)$ denote the argument, rank, trace, a square matrix with input vector on main diagonal, and a vector retrieving main diagonal of input square matrix, respectively.
-	$\mathrm{diag}(\cdot)$ returns a square matrix with the input vector on main diagonal.
+	$\mathrm{diag}(\cdot)$ returns a square matrix with the input vector on its main diagonal and zeros elsewhere.
 	$(\cdot)^*$, $(\cdot)^T$, $(\cdot)^H$, $\lvert{\cdot}\rvert$, and $\lVert{\cdot}\rVert$ denote the conjugate, transpose, conjugate transpose, absolute value, and Euclidean norm operators, respectively.
@@
 	An electromagnetic wave is scattered when an obstruction is placed in its propagation path.
+	In this section, we first introduce two common scatterer categories and review their operation principles, then briefly discuss how scatterers realize backscatter modulation and channel reconfiguration over reflection patterns.
+	\begin{subsection}{Scatterer Categories}
 		In \gls{rf} applications such as \gls{bc}, \gls{sr} and \gls{ris}, the scatterer often includes \emph{variable-load antenna} or \emph{programmable metamaterial} with various reflection patterns \cite{Liang2022}.
@@
 		By \emph{frequently switching} between the available states, each backscatter node encodes self message over scattered signal and introduces backscatter uncertainty at the receiver.
-		For $M$-ary \gls{qam}, reflection coefficient $\Gamma_m$ maps to the corresponding \emph{complex constellation point $c_m$} by \cite{Thomas2012a}
+		For $M$-ary \gls{qam}, reflection coefficient $\Gamma_m$ maps to the corresponding \emph{complex constellation point $c_m$} by
+		% \cite{Thomas2012a}
 		\begin{equation}
@@
 		By \emph{adaptively choosing} the reflection pattern, each reflecting element alters the phase of scattered signal for constructive/destructive superposition at the receiver.
-		For each unit with $M$ candidate states, reflection coefficient $\Gamma_m$ maps to the corresponding \emph{phase shift $\theta_m$} by \cite{Wu2018}
+		For each unit with $M$ candidate states, reflection coefficient $\Gamma_m$ maps to the corresponding \emph{phase shift $\theta_m$} by
+		% \cite{Wu2018}
 		\begin{equation}
@@
 \begin{section}{UniScatter}
+	Using shared spectrum, energy and infrastructures, UniScatter is a novel passive communication/assistance protocol that generalizes \gls{bc}, \gls{sr} and \gls{ris} from the perspective of distribution.
+	In particular, passive UniScatter nodes ride over an active legacy transmission in a flexible and mutualistic manner, while practical UniScatter receiver cooperatively decodes both links under the benefits of backscatter modulation and passive beamforming.
+	% TODO compare BC, SR and IRS
 	\begin{subsection}{UniScatter Nodes}
-		% TODO compare BC, SR and IRS
+		Based on link priority and \gls{csi}, UniScatter nodes adapt the \emph{state input probability distribution} of antenna-based scatterers to unify and generalize backscatter modulation and passive beamforming.
+		The scattering sources of \gls{bc}/\gls{sr} and reflecting elements of \gls{ris} can be viewed as its extreme cases, where the input distribution boils down to equiprobable and degenerate, respectively.
 		\begin{figure}[!t]
@@
 				}
+				\label{fi:input_distribution}
 			}
@@
 				}
+				\label{fi:time_block}
 			}
 			\caption{
-				Input probability distribution and time block structure of \gls{sr}, \gls{ris}, and UniScatter.
+				Input probability distribution and time block structure of \gls{bc}, \gls{sr}, \gls{ris}, and UniScatter.
 				$T_s$ and $T_c$ respectively denote the primary and backscatter symbol period.
-				Within channel coherence time, UniScatter nodes semi-randomly select reflection state for each backscatter block, with guidance from input probability distribution.
-			}
-			\label{fi:uniscatter}
+				Within channel coherence time, UniScatter nodes semi-randomly select reflection state for each backscatter symbol block with the guidance of input probability distribution.
+			}
+			\label{fi:uniscatter_distribution}
 		\end{figure}
-		% ! Passive backscatter nodes harvest energy from and modulate information over surrounding \gls{rf} signals.
-		% As shown in Fig.
-\subref*{fi:block_diagram}, a typical passive node consists of a scattering antenna, an energy harvester, an integrated receiver, a load-switching modulator, and on-chip components (e.g., micro-controller and sensors) \cite{Dobkin2012}.
-		% Its equivalent circuit is presented in Fig. \subref*{fi:equivalent_circuit}.
-		% When illuminated, the node absorbs a portion of the impinging wave for information decoding and/or energy harvesting \cite{Kim2021a}, and backscatters the remaining as \emph{structural} and \emph{antenna} components.
-		% The former consistently contributes to environment multipath and can be modelled by channel estimation \cite{Boyer2014}, while the latter depends on antenna-load impedance mismatch and can be used for backscatter modulation \cite{Boyer2012} and/or channel reconfiguration \cite{Wu2021b}.
-		% Fig. \subref*{fi:scatter_model} illustrates the scatter model of a node with $M$ states.
-
-		% ? For a passive node with finite states, is it possible to unify backscatter modulation and channel reconfiguration by proper selection of reflection coefficient?
-		UniScatter nodes simultaneously transmit and assist by \emph{adaptive input distribution design} based on primary and (cascaded) backscatter \gls{csi}.
-		% The reflection pattern is neither fully random nor fully deterministic, but flexibly distributed to balance backscatter encoding and passive beamforming.
-		% Instead of using fully random or deterministic reflection pattern over time, as shown in Fig.
-\ref{fi:uniscatter}, UniScatter flexibly controls input distribution of candidate reflection states to balance backscatter encoding and passive beamforming.
-		% Instead of using fully random or deterministic reflection pattern over time, as shown in Fig.
-\ref{fi:uniscatter}, UniScatter semi-randomly selects reflection state for each backscatter block with guidance from \emph{input probability distribution $P(\Gamma_m)$.}
-		% Instead of using fully random or deterministic reflection pattern over time, as shown in Fig.
-\ref{fi:uniscatter}, UniScatter semi-randomly selects reflection state for each backscatter block, with guidance from \emph{input probability distribution $P(\Gamma_m)$.} In other words, it flexibly controls input distribution of candidate reflection states to balance backscatter encoding and passive beamforming.
-\gls{sr} and \gls{ris} can be regarded as extreme cases of UniScatter, where node input distribution boils down to uniform and deterministically biased, respectively.
-		Instead of using fully random or deterministic reflection pattern over time, as shown in Fig.
-\ref{fi:uniscatter}, UniScatter nodes semi-randomly select reflection state for each backscatter block, with \emph{guidance of input probability $P(\Gamma_m)$} for state $m$.
-In other words, it flexibly controls input distribution of candidate reflection states to balance backscatter encoding and passive beamforming.
-		% \gls{sr} and \gls{ris} can be regarded as extreme cases of UniScatter nodes, where node input distribution boils down to uniform and deterministic, respectively.
-		% flexibly controls input distribution of candidate reflection states to balance backscatter encoding and passive beamforming.
-		% UniScatter semi-randomly selects reflection state for each backscatter block, with guidance from \emph{input probability distribution $P(\Gamma_m)$.}
-		% % Based on \gls{csi}, UniScatter adapts the reflection state distribution to unify data transmission and channel reconfiguration.
-		% \gls{sr} and \gls{ris} can be regarded as its extreme cases, where node input distribution boils down to uniform and deterministically biased, respectively.
-		% Within channel coherence time, UniScatter semi-randomly selects reflection state for each backscatter block, with guidance from \emph{input probability distribution $P(\Gamma_m)$.}
-		\begin{remark}
-			Compared to conventional \gls{ris} literatures that optimize phase shifts under unit-module constraint, UniScatter nodes start from predefined reflection coefficients and designs their input distribution under sum-probability constraint to achieve flexible primary-backscatter tradeoff.
-		\end{remark}
+		As illustrated in Fig.
+\ref{fi:uniscatter_distribution}, instead of always using fully random or deterministic reflection pattern over time, each UniScatter node can \emph{flexibly adjust} its input distribution to balance information encoding and channel reconfiguration.
+		That is, it semi-randomly select the reflection state during each backscatter symbol block with the guidance of input probability $P(\Gamma_m)$ for state $m$.
+		Such an adaptive backscatter channel coding coincides with \gls{ris} when primary link is absolutely prioritized, and outperforms the uncoded equiprobable transmission of \gls{bc}/\gls{sr} when backscatter link is absolutely prioritized.
+		UniScatter nodes can be implemented over readily available passive backscatter devices with energy harvester and integrated receiver \cite{Kim2021a}, while the relevant \gls{csi} can be efficiently and accurately acquired using the state-of-the-art parallel approach \cite{Jin2021a}.
+		\begin{figure*}[!t]
+			\centering
+			\subfloat[Block Diagram]{
+				\resizebox{0.32\linewidth}{!}{
+					\input{assets/illustration/block_diagram.tex}
+				}
+				\label{fi:block_diagram}
+			}
+			\subfloat[Equivalent Circuit]{
+				\resizebox{0.37\linewidth}{!}{
+					\input{assets/illustration/equivalent_circuit.tex}
+				}
+				\label{fi:equivalent_circuit}
+			}
+			\subfloat[Scatter Model]{
+				\resizebox{0.28\linewidth}{!}{
+					\input{assets/illustration/scatter_model.tex}
+				}
+				\label{fi:scatter_model}
+			}
+			\caption{Block diagram, equivalent circuit, and scatter model of a UniScatter node.
+The solid and dashed vectors represent signal and energy flows.
+The scattering antenna behaves as a constant power source, where the voltage $V_0$ and current $I_0$ are introduced by incident electric field $\vec{E}_{\mathrm{I}}$ and magnetic field $\vec{H}_{\mathrm{I}}$ \cite{Huang2021}.}
+			\label{fi:uniscatter_node}
+		\end{figure*}
+		The block diagram, equivalent circuit, and scatter model of a UniScatter node are illustrated in Fig. \ref{fi:uniscatter_node}.
+		A proportion of the impinging wave emitted by primary transmitter is harvested for the operation of UniScatter node, while reradiated component includes a (potentially) random phase shift due to backscatter message.
 		% Next, we will discuss the input design in a UniScatter-enabled network.
-		% consider a UniScatter-aided system to evaluate
+	\end{subsection}
+
+	\begin{subsection}{UniScatter Receiver}
+		TODO
 	\end{subsection}

### 2022-08-15 main.tex
:pencil: Update UniScatter receiver

@@
 	This motivated \cite{Long2020a,Liang2020,Guo2019b,Ding2020,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Yang2018,Han2021,Zhang2022} to first decode the primary link, perform \gls{sic}, then decode the backscatter link.
-	However, the advantage of \gls{sic} is questionable because 1) sufficiently large symbol period ratio is assumed in primary rate analysis and constraints backscatter rate; 2) backscatter pattern and signal characteristics are not fully exploited; 3) non-coherent primary encoding is required at the transmitter, while re-encoding, precoding, and subtraction are required at the receiver; 4) primary and backscatter symbols are mixed by multiplication instead of superposition.
+	However, the advantage of \gls{sic} is questionable because 1) sufficiently large symbol period ratio is assumed in primary rate analysis and constraints backscatter rate; 2) backscatter pattern and signal characteristics are not fully exploited; 3) non-coherent primary encoding is required at the transmitter, while re-encoding, precoding, and subtraction are required at the receiver; 4) primary and backscatter symbols are superimposed by multiplication instead of superposition.
 	Another open issue for \gls{sr} is backscatter multiple access.
@@
 
-	\emph{First,} we propose UniScatter node to adapt the input probability distribution of a finite-state passive scatter device based on link priority and \gls{csi}.
+	\emph{First,} we propose UniScatter nodes to adapt the input probability distribution of a finite-state passive scatter device based on link priority and \gls{csi}.
 	The reflection pattern over time is no longer fully random or deterministic, but can be flexibly distributed to unify and balance backscatter modulation with passive beamforming.
@@
 
-	\emph{Second,} we propose a practical receiving strategy that semi-coherently decodes all UniScatter messages from the received energy during each backscatter symbol block, re-encodes and recovers their reflection patterns at each primary block, combines those with relevant \gls{csi} to construct equivalent primary channels, then coherently decodes the primary link under adapted multipath.
-	The proposed receiver 1) preserves the benefits of backscatter modulation and passive beamforming; 2) enjoys lower computational and operational complexities than joint \gls{ml} and \gls{sic} schemes; 3) accommodates the difference of symbol period in backscatter decoding; 4) exploits the reflection patterns in primary decoding; 5) suits for diverse symbol period ratios.
+	% \emph{Second,} we propose a practical UniScatter receiver that semi-coherently decodes UniScatter nodes from the received energy during each backscatter symbol block, re-encodes and recovers their reflection patterns, combines with relevant \gls{csi} for equivalent primary channel as if dynamic passive beamforming, then coherently decodes the primary link under the enhanced multipath.
+	\emph{Second,} we propose a practical UniScatter receiver that semi-coherently decodes UniScatter nodes from the received energy during each backscatter symbol block, re-encodes for their reflection patterns, combines with relevant \gls{csi} as if dynamic passive beamforming, then coherently decodes the primary link under the enhanced multipath.
+	The proposed receiver 1) preserves the benefits of backscatter modulation and passive beamforming; 2) enjoys lower computational and operational complexities than joint \gls{ml} and \gls{sic} schemes; 3) accommodates the link difference and suits for diverse symbol period ratios; 4) requires minor modification over legacy hardware.
 
@@
 		A proportion of the impinging wave emitted by primary transmitter is harvested for the operation of UniScatter node, while reradiated component includes a (potentially) random phase shift due to backscatter message.
-		% Next, we will discuss the input design in a UniScatter-enabled network.
+		% Next, we will discuss the input design in a UniScatter network.
 	\end{subsection}
@@
 	\begin{subsection}{UniScatter Receiver}
-		TODO
+		Since each passive UniScatter node directly modulates its own message over the legacy signal, it involves a \emph{double modulation} where the primary and backscatter symbols are superimposed by \emph{multiplication coding} instead of superposition coding.
+		Besides, the backscatter symbol period is typically longer than primary due to the load switching constraint.
+		% ? In such case, the advantages of power-domain \gls{noma} with \gls{sic} receiver becomes questionable.
+		% Those facts imply if the backscatter messages can be decoded first, one can recover the reflection patterns of all UniScatters and model them within the equivalent primary channel as if dynamic passive beamforming.
+		Both facts imply backscatter detection under primary uncertainty is also part of equivalent primary channel training.
+		Hence, we propose a practical UniScatter receiver that semi-coherently decodes UniScatter nodes from the received energy during each backscatter symbol block, re-encodes for their reflection patterns, combines with relevant \gls{csi} as if dynamic passive beamforming, then coherently decodes the primary link under the enhanced multipath.
+		\begin{figure}[!t]
+			\centering
+			\resizebox{0.9\columnwidth}{!}{
+				\input{assets/illustration/energy_distribution.tex}
+			}
+			\caption{
+				\gls{pdf} of total received energy per backscatter block, conditioned on different input state hypotheses.
+				$t$ and $\mathcal{R}$ denote the energy decision thresholds and regions, respectively.
+			}
+			\label{fi:energy_distribution}
+		\end{figure}
+		As illustrated in Fig.
+\ref{fi:energy_distribution}, the total received energy during each backscatter symbol block is a random variable that follows different distributions conditioned on different input state hypotheses.
+		Compared with conventional joint \gls{ml} and \gls{sic} from stronger primary link to weaker backscatter links, UniScatter receiver not only preserves the benefits of backscatter modulation and passive beamforming, but also enjoys much lower computational and operational complexities.
 	\end{subsection}
@@
 			}
-			\caption{A UniScatter-enabled single-user multi-node network.}
+			\caption{A single-user multi-node UniScatter network.}
 			\label{fi:uniscatter_network}
 		\end{figure}
-		% As shown in Fig. \ref{fi:uniscatter_network}, we propose a UniScatter-enabled single-user multi-node network where the spectrum, energy and infrastructures are shared by two coexisting systems.
-		% UniScatter-enabled single-user multi-node \gls{miso} network where multiple UniScatter nodes ride over a point-to-point transmission to
-		As shown in Fig. \ref{fi:uniscatter_network}, we propose a UniScatter-enabled single-user multi-node \gls{miso} network where two coexisting systems share spectrum, energy and infrastructures.
+		In this subsection, we consider a single-user multi-node \gls{miso} UniScatter network as shown in Fig. \ref{fi:uniscatter_network}.
 		% In the primary point-to-point system, the \gls{ap} transmits information to the single-antenna user.
@@
 
-		\begin{remark}
-			UniScatter involves a symbiotic \gls{mac} where the primary and backscatter symbols of different duration are mixed by \gls{mc} instead of \gls{sc}.
-			For each node, the reflection coefficient not only encodes the backscatter message, but also influences the equivalent primary channel \eqref{eq:equivalent_channel}.
-			% As such, novel receiving strategy other than \gls{sic} should be tailored to signal characteristics to unveil how reflection pattern potentially influences the primary-backscatter tradeoff.
-			To accommodate such signal characteristics, novel receiving strategy apart from \gls{sic} is desired to better utilize the reflection pattern and boost the primary-backscatter tradeoff.
-		\end{remark}
-	\end{subsection}
-
-	\begin{subsection}{Receiving Strategy}
-		We propose a UniScatter receiver where the backscatter messages of all UniScatter nodes are first jointly and semi-coherently detected using total received energy per backscatter block, then modeled within equivalent channel \eqref{eq:equivalent_channel} as dynamic passive beamforming.
-		% identified by non-coherent energy detection, then
-		% Compared with conventional schemes as joint decoding and \gls{sic}, the UniScatter receiver may not achieve as high data rate for one tag, but it avoids non-coherent primary encoding and enables tag multiple access in a practical and low-complexity manner.
-		% Therefore, we believe it can be compatible to and readily implemented over legacy point-to-point systems.
-		Compared with \gls{ml} and \gls{sic}, UniScatter receiver allows practical and low-complexity node multiple access with minor adjustment over legacy equipments.
-
 		% At a specific backscatter block, denote $m_k \in \mathcal{M}$ as the state index of UniScatter $k$, and let $m_{\mathcal{K}} \triangleq \{m_k: k \in \mathcal{K}\}$ collect the state indexes of all UniScatters.
@@
 		% To accommodate backscatter characteristics and reduce decoding complexity, we consider a joint semi-coherent energy detection for all UniScatters based on disjoint decision regions over accumulated energy $z$.
-		To accommodate backscatter characteristics and reduce decoding complexity, we consider a joint semi-coherent detection for all UniScatter nodes over accumulated energy $z$.
-		% To reduce decoding complexity, we consider a joint semi-coherent energy detection for all UniScatters based on disjoint decision regions over accumulated energy $z$.
-		\begin{figure}[!t]
-			\centering
-			\resizebox{0.9\columnwidth}{!}{
-				\input{assets/illustration/energy_distribution.tex}
-			}
-			% \caption{\gls{pdf} of Average Received Power Conditioned on Different Input Hypothesis. Example \gls{ml}.}
-			\caption{
-				\gls{pdf} of total received energy per backscatter block, conditioned on different input hypothesis.
-				% This \gls{ml} decision consists of convex regions and is generally rate-suboptimal except for equiprobable inputs.}
-				Here, the convex \gls{ml} decision regions are generally rate-suboptimal except for equiprobable inputs.
-			}
-			\label{fi:energy_distribution}
-		\end{figure}
+		% !
+		% To accommodate backscatter characteristics and reduce decoding complexity, we consider a joint semi-coherent detection for all UniScatter nodes over accumulated energy $z$.
+		% % To reduce decoding complexity, we consider a joint semi-coherent energy detection for all UniScatters based on disjoint decision regions over accumulated energy $z$.
+		% \begin{figure}[!t]
+		% 	\centering
+		% 	\resizebox{0.9\columnwidth}{!}{
+		% 		\input{assets/illustration/energy_distribution.tex}
+		% 	}
+		% 	% \caption{\gls{pdf} of Average Received Power Conditioned on Different Input Hypothesis. Example \gls{ml}.}
+		% 	\caption{
+		% 		\gls{pdf} of total received energy per backscatter block, conditioned on different input hypothesis.
+		% 		% This \gls{ml} decision consists of convex regions and is generally rate-suboptimal except for equiprobable inputs.}
+		% 		Here, the convex \gls{ml} decision regions are generally rate-suboptimal except for equiprobable inputs.
+		% 	}
+		% 	\label{fi:energy_distribution}
+		% \end{figure}
 		% The idea is presented in Fig. \ref{fi:energy_distribution}.
+		% !
 		% As illustrated in Fig. \ref{fi:energy_distribution}, o
@@
 \begin{section}{Input Distribution, Active Beamforming, and Decision Threshold Design}
-	To characterize the achievable primary-total-backscatter rate region of the proposed UniScatter-enabled network, we aim to maximize the weighted sum mutual information with respect to node input distributions $\{\boldsymbol{p}_k\}_{k \in \mathcal{K}}$, active beamforming vector $\boldsymbol{w}$, and decision threshold vector $\boldsymbol{t}$ as
+	To characterize the achievable primary-total-backscatter rate region of the proposed UniScatter network, we aim to maximize the weighted sum mutual information with respect to node input distributions $\{\boldsymbol{p}_k\}_{k \in \mathcal{K}}$, active beamforming vector $\boldsymbol{w}$, and decision threshold vector $\boldsymbol{t}$ as
 	\begin{maxi!}
@@
 	% TODO compare PGD and primary-MRT beamformers
-	In this section, we provide numerical results to evaluate the proposed input, beamforming and decision design over a single-user multi-node UniScatter-enabled network.
+	In this section, we provide numerical results to evaluate the proposed input, beamforming and decision design over a single-user multi-node UniScatter network.
 	We assume the distance between \gls{ap} and user is \qty{10}{\meter}, and $K=2$ UniScatter nodes are uniformly dropped within a disk centered at the user of radius \qty{1}{\meter}.

### 2022-08-16 main.tex
:pencil: Update UniScatter characteristics

@@
 \newacronym{sr}{SR}{Symbiotic Radio}
+\newacronym{swipt}{SWIPT}{Simultaneous Wireless Information and Power Transfer}
 \newacronym{tdma}{TDMA}{Time-Division Multiple Access}
@@
 	In this paper, we depart from those concepts and introduce UniScatter as a new paradigm for future wireless networks.
-	Instead of treating probability distribution of reflection states as equiprobable (as scattering source of \gls{bc}/\gls{sr}) or degenerate (as reflecting element of \gls{ris}), UniScatter node adapts the input distribution of a passive scatterer based on link priority and \gls{csi}, balancing information encoding and channel reconfiguration in a flexible and mutualistic manner.
+	Instead of treating probability distribution of reflection states as equiprobable (as scattering source of \gls{bc}/\gls{sr}) or degenerate (as reflecting element of \gls{ris}), UniScatter nodes located at different places adapt the input distribution of passive scatterers based on link priority and \gls{csi}, balancing information encoding and channel reconfiguration in a flexible and mutualistic manner.
 	To accommodate signal characteristics, UniScatter receiver semi-coherently decodes all nodes from accumulated energy, determines equivalent primary channel over reflection pattern, then coherently decodes the primary link under enhanced multipath.
@@
 
-	To the best of our knowledge, all relevant literatures assumed either Gaussian codebook \cite{Guo2019b,Ding2020,Long2020a,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Hu2021b} or finite equiprobable inputs \cite{Yang2018,Liang2020,Han2021,Zhang2022,Liu2019d,Bereyhi2020,Xu2020b,Zhang2021d,Hua2022,Basar2020,Ma2020a,Yuan2021,Hu2021a} at backscatter information sources.
+	To the best of our knowledge, all relevant literatures assumed at backscatter information sources either Gaussian codebook \cite{Guo2019b,Ding2020,Long2020a,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Hu2021b} or finite equiprobable inputs \cite{Yang2018,Liang2020,Han2021,Zhang2022,Liu2019d,Bereyhi2020,Xu2020b,Zhang2021d,Hua2022,Basar2020,Ma2020a,Yuan2021,Hu2021a}.
 	The former is impractical for passive backscatter devices, while the latter does not fully exploit reflection pattern and \gls{csi}.
@@
 	Scattering source of \gls{bc}/\gls{sr} and reflecting element of \gls{ris} can be regarded as its extreme cases, where the input distribution boils down to equiprobable and degenerate, respectively.
-	Like aforementioned \gls{ris}-empowered \gls{bc}/\gls{sr} schemes, the passive nodes require regular coordination with active devices, but the advantages are 1) UniScatter nodes can be built over conventional load-switching scatterers instead of composite metamaterial; 2) the optimization cost of input distribution is much lower than that of \gls{ris} reflection coefficients; 3) adaptive channel coding at backscatter sources can exploit \gls{csi} to achieve higher instantaneous rate than conventional uncoded transmission.
-
-	% \emph{Second,} we propose a practical UniScatter receiver that semi-coherently decodes UniScatter nodes from the received energy during each backscatter symbol block, re-encodes and recovers their reflection patterns, combines with relevant \gls{csi} for equivalent primary channel as if dynamic passive beamforming, then coherently decodes the primary link under the enhanced multipath.
-	\emph{Second,} we propose a practical UniScatter receiver that semi-coherently decodes UniScatter nodes from the received energy during each backscatter symbol block, re-encodes for their reflection patterns, combines with relevant \gls{csi} as if dynamic passive beamforming, then coherently decodes the primary link under the enhanced multipath.
+	Like aforementioned \gls{ris}-empowered \gls{bc}/\gls{sr} schemes, the passive nodes require regular coordination with active devices, but the advantages are 1) UniScatter nodes can be built over conventional load-switching scatterers instead of composite metamaterial; 2) the optimization cost of input distribution is much lower than that of \gls{ris} reflection coefficients; 3) adaptive backscatter channel coding can exploit \gls{csi} to achieve higher instantaneous rate than conventional uncoded transmission; 4) the physically distributed characteristics of UniScatter nodes and legacy users avoids the development optimization and allows uniformly good performance for both links.
+
+	\emph{Second,} we propose a practical UniScatter receiver that semi-coherently decodes UniScatter nodes from the received energy per backscatter block, re-encodes for their reflection patterns, retrieves equivalent primary channel as if dynamic passive beamforming, then coherently decodes the primary link under the enhanced multipath.
 	The proposed receiver 1) preserves the benefits of backscatter modulation and passive beamforming; 2) enjoys lower computational and operational complexities than joint \gls{ml} and \gls{sic} schemes; 3) accommodates the link difference and suits for diverse symbol period ratios; 4) requires minor modification over legacy hardware.
@@
 	\emph{Fifth,} we provide numerical results to demonstrate the benefits of UniScatter and proposed algorithms.
-	It is concluded that 1) UniScatter nodes provide flexible transmit-assist tradeoff using adaptive input distribution design; 2) when primary link is absolutely prioritized, the input probability of each node is \num{1} at one state and \num{0} at the others, which coincides with discretized \gls{ris}; 3) when backscatter link is absolutely prioritized, UniScatter nodes can exploit adaptive channel coding to achieve higher instantaneous rate than uncoded equiprobable transmission of \gls{bc}/\gls{sr}; 4) the proposed \gls{kkt} input distribution design converges to stationary points, whose average performance is very close to global optimal; 5) the \gls{pgd} beamforming achieves larger rate region than conventional \gls{mrt}; 6) the decision region schemes adapted to input distribution provide higher backscatter rates than the non-adaptive \gls{ml} detector; 7) cooperation between passive nodes in terms of joint encoding can further boost the total backscatter rate; 8) the low complexity of input distribution design and the marginal effect of increasing reflection states motivates the use of low-order scatter nodes to replace high-resolution \gls{ris}.
+	It is concluded that 1) UniScatter nodes provide flexible transmit-assist tradeoff using adaptive input distribution design; 2) when primary link is absolutely prioritized, the input probability of each node is \num{1} at one state and \num{0} at the others, which coincides with discretized \gls{ris}; 3) when backscatter link is absolutely prioritized, UniScatter nodes can exploit adaptive channel coding to achieve higher instantaneous rate than uncoded equiprobable inputs of \gls{bc}/\gls{sr}; 4) the proposed \gls{kkt} input distribution design converges to stationary points, whose average performance is very close to global optimal; 5) the \gls{pgd} beamforming achieves larger rate region than conventional \gls{mrt}; 6) the decision region schemes adapted to input distribution provide higher backscatter rates than the non-adaptive \gls{ml} detector; 7) cooperation between passive nodes in terms of joint encoding can further boost the total backscatter rate; 8) the low complexity of input distribution design and the marginal effect of increasing reflection states motivates the use of low-order scatter nodes to replace high-resolution \gls{ris}.
 
@@
 \begin{section}{UniScatter}
-	Using shared spectrum, energy and infrastructures, UniScatter is a novel passive communication/assistance protocol that generalizes \gls{bc}, \gls{sr} and \gls{ris} from the perspective of distribution.
-	In particular, passive UniScatter nodes ride over an active legacy transmission in a flexible and mutualistic manner, while practical UniScatter receiver cooperatively decodes both links under the benefits of backscatter modulation and passive beamforming.
+	% Using shared spectrum, energy and infrastructures, UniScatter is a novel passive communication/assistance protocol that generalizes \gls{bc}, \gls{sr} and \gls{ris} from the perspective of distribution.
+	% Using shared spectrum, energy and infrastructures, UniScatter is a novel passive communication/assistance protocol that generalizes \gls{bc}, \gls{sr} and \gls{ris} via \emph{physical} and \emph{probability} distributions.
+	Using shared spectrum, energy and infrastructures, UniScatter is a novel passive communication/assistance protocol that generalizes \gls{bc}, \gls{sr} and \gls{ris} in a \emph{physically} and \emph{probabilistically} distributed manner.
+	In particular, passive UniScatter nodes located at different places ride over an active legacy transmission in a flexible and mutualistic manner, while practical UniScatter receiver cooperatively decodes both primary and backscatter links under the benefits of backscatter modulation and passive beamforming.
 	% TODO compare BC, SR and IRS
 	\begin{subsection}{UniScatter Nodes}
-		Based on link priority and \gls{csi}, UniScatter nodes adapt the \emph{state input probability distribution} of antenna-based scatterers to unify and generalize backscatter modulation and passive beamforming.
+		Based on link priority and \gls{csi}, UniScatter nodes adapt the \emph{state input probability distribution} of antenna-based scatterers to unify backscatter modulation and passive beamforming.
 		The scattering sources of \gls{bc}/\gls{sr} and reflecting elements of \gls{ris} can be viewed as its extreme cases, where the input distribution boils down to equiprobable and degenerate, respectively.
@@
 				$T_s$ and $T_c$ respectively denote the primary and backscatter symbol period.
-				Within channel coherence time, UniScatter nodes semi-randomly select reflection state for each backscatter symbol block with the guidance of input probability distribution.
+				Within channel coherence time, UniScatter nodes semi-randomly select reflection state for each backscatter symbol block under the guidance of input probability distribution.
 			}
@@
 \ref{fi:uniscatter_distribution}, instead of always using fully random or deterministic reflection pattern over time, each UniScatter node can \emph{flexibly adjust} its input distribution to balance information encoding and channel reconfiguration.
-		That is, it semi-randomly select the reflection state during each backscatter symbol block with the guidance of input probability $P(\Gamma_m)$ for state $m$.
-		Such an adaptive backscatter channel coding coincides with \gls{ris} when primary link is absolutely prioritized, and outperforms the uncoded equiprobable transmission of \gls{bc}/\gls{sr} when backscatter link is absolutely prioritized.
-		UniScatter nodes can be implemented over readily available passive backscatter devices with energy harvester and integrated receiver \cite{Kim2021a}, while the relevant \gls{csi} can be efficiently and accurately acquired using the state-of-the-art parallel approach \cite{Jin2021a}.
+		That is, it semi-randomly select the reflection state per backscatter symbol block under the guidance of input probability $P(\Gamma_m)$ for state $m$.
+		Such an adaptive backscatter channel coding coincides with \gls{ris} when primary link is absolutely prioritized, and outperforms the uncoded equiprobable inputs of \gls{bc}/\gls{sr} when backscatter link is absolutely prioritized.
+		Besides, the physically distributed characteristics of UniScatter nodes and legacy users avoids the development optimization and allows uniformly good performance for both links.
+
+		As shown in Fig. \subref*{fi:block_diagram}, UniScatter nodes can be implemented over readily available passive backscatter devices with energy harvester and information decoder.
+		Its equivalent circuit and scatter model are presented in Fig. \subref*{fi:equivalent_circuit} and \subref*{fi:scatter_model}.
+		When activated by primary transmitter, each node harvests a proportion of the impinging wave for its own operation, decode the embedded coordination information for input distribution control, then applies a potentially random phase shift on the reradiated signal due to backscatter modulation.
+		Energy harvesting and information decoding at passive UniScatter nodes can be realized using conventional power-splitting or time-sharing \gls{swipt} protocols \cite{Clerckx2019} or integrated energy-information receiver with pulse position modulated signal \cite{Kim2021a}.
+		Besides, relevant \gls{csi} can be acquired using either traditional sequential methods \cite{Bharadia2015,Yang2015b,Guo2019g} or the state-of-the-art parallel approach \cite{Jin2021a}.
+		In the following context, we assume perfect primary-backscatter coordination and perfect channel estimation for all links.
 		\begin{figure*}[!t]
@@
 		\end{figure*}
-		The block diagram, equivalent circuit, and scatter model of a UniScatter node are illustrated in Fig. \ref{fi:uniscatter_node}.
-		A proportion of the impinging wave emitted by primary transmitter is harvested for the operation of UniScatter node, while reradiated component includes a (potentially) random phase shift due to backscatter message.
-		% Next, we will discuss the input design in a UniScatter network.
 	\end{subsection}
@@
 		Since each passive UniScatter node directly modulates its own message over the legacy signal, it involves a \emph{double modulation} where the primary and backscatter symbols are superimposed by \emph{multiplication coding} instead of superposition coding.
-		Besides, the backscatter symbol period is typically longer than primary due to the load switching constraint.
-		% ? In such case, the advantages of power-domain \gls{noma} with \gls{sic} receiver becomes questionable.
-		% Those facts imply if the backscatter messages can be decoded first, one can recover the reflection patterns of all UniScatters and model them within the equivalent primary channel as if dynamic passive beamforming.
-		Both facts imply backscatter detection under primary uncertainty is also part of equivalent primary channel training.
-		Hence, we propose a practical UniScatter receiver that semi-coherently decodes UniScatter nodes from the received energy during each backscatter symbol block, re-encodes for their reflection patterns, combines with relevant \gls{csi} as if dynamic passive beamforming, then coherently decodes the primary link under the enhanced multipath.
+		Besides, the backscatter symbol period is typically longer than primary due to the load switching speed constraint.
+		Those facts imply \emph{backscatter detection} under primary uncertainty can be viewed as part of \emph{primary channel training}.
+		Hence, we propose a practical UniScatter receiver that semi-coherently decodes UniScatter nodes from the received energy per backscatter block, re-encodes for their reflection patterns, retrieves equivalent primary channel as if dynamic passive beamforming, then coherently decodes the primary link under the enhanced multipath.
 		\begin{figure}[!t]
@@
 		As illustrated in Fig.
-\ref{fi:energy_distribution}, the total received energy during each backscatter symbol block is a random variable that follows different distributions conditioned on different input state hypotheses.
+\ref{fi:energy_distribution}, the total received energy per backscatter block is a random variable that follows different distributions conditioned on different input state hypotheses.
 		Compared with conventional joint \gls{ml} and \gls{sic} from stronger primary link to weaker backscatter links, UniScatter receiver not only preserves the benefits of backscatter modulation and passive beamforming, but also enjoys much lower computational and operational complexities.
@@
 		\end{figure}
-		In this subsection, we consider a single-user multi-node \gls{miso} UniScatter network as shown in Fig. \ref{fi:uniscatter_network}.
-		% In the primary point-to-point system, the \gls{ap} transmits information to the single-antenna user.
-		% In the primary point-to-point system, a $Q$-antenna \gls{ap} transmit to a single-antenna user while assisted by $K$ nearby single-antenna UniScatters.
-		The primary point-to-point transmission from a $Q$-antenna \gls{ap} to a single-antenna user is assisted by $K$ nearby single-antenna UniScatter nodes.
-		In the secondary backscatter \gls{mac} system, the \gls{ap} serves as the carrier emitter, $K$ nearby single-antenna UniScatter nodes modulate information over reradiated \gls{rf} signals, and the user decodes their messages.
-		For simplicity, we consider a quasi-static block fading model where channels remain constant within coherence interval while vary independently between consecutive blocks.
-		% Since backscatter modulation involves load switching, tags typically transmit at much lower rate, and we assume the backscatter symbol period is $N \in \mathbb{Z}_{++}$ times the primary symbol period.
-		Due to physical constraints on load switching, we assume the backscatter symbol period is $N \gg 1$ times longer than primary and consider integer $N$ without loss of generality.
-		We also assume the direct channel and all cascaded channels can be estimated and fed back to the \gls{ap}.%
-		\footnote{
-			Due to the lack of \gls{rf} chains at the passive tag, accurate and efficient \gls{csi} acquisition at the \gls{ap} can be challenging.
-			One possibility is the \gls{ap} sends training pilots, the tags respond in predefined manners, and the user performs least-square estimation with feedbacks \cite{Bharadia2015,Yang2015b,Guo2019g}.
-		}
-		Besides, we omit the signal reflected by two or more times\cite{Wu2019} and ignore the time difference of arrival from different paths\cite{Guo2019b}.
-
-		Denote the \gls{ap}-user direct channel as $\boldsymbol{h}_{\mathrm{D}}^H \in \mathbb{C}^{1 \times Q}$, the \gls{ap}-node $k \in \mathcal{K} \triangleq \{1,\ldots,K\}$ forward channel as $\boldsymbol{h}_{\mathrm{F},k}^H \in \mathbb{C}^{1 \times Q}$, and the node $k$-user backward channel as $h_{\mathrm{B},k}$.
-Also, define the cascaded channel of tag $k$ as $\boldsymbol{h}_{\mathrm{C},k}^H \triangleq h_{\mathrm{B},k} \boldsymbol{h}_{\mathrm{F},k}^H \in \mathbb{C}^{1 \times Q}$, and $\boldsymbol{H}_{\mathrm{C}} \triangleq [\boldsymbol{h}_{\mathrm{C},1},\ldots,\boldsymbol{h}_{\mathrm{C},K}]^H \in \mathbb{C}^{K \times Q}$.
+		To demonstrate the advantages of UniScatter, we consider a single-user multi-node \gls{miso} UniScatter network as shown in Fig. \ref{fi:uniscatter_network}.
+		In the primary active point-to-point system, a $Q$-antenna \gls{ap} transmits to a single-antenna user assisted by $K$ nearby single-antenna UniScatter nodes with $M$ reflection states.
+		In the secondary backscatter \gls{mac} system, the \gls{ap} serves as the carrier emitter, the distributed UniScatter nodes modulate information over reradiated \gls{rf} signals, and the user decodes their messages.
+		For simplicity, we consider a quasi-static block fading model where channels remain constant within coherence block and vary independently between consecutive blocks.
+		Due to the physical constraints of load switching speed, we assume the backscatter over primary symbol period ratio is an integer $N \gg 1$.
+		We also omit the signal reflected by two or more times and ignore the propagation time difference of different paths.
+
+		Denote the \gls{ap}-user direct channel as $\boldsymbol{h}_{\mathrm{D}}^H \in \mathbb{C}^{1 \times Q}$, the \gls{ap}-node $k \in \mathcal{K} \triangleq \{1,\ldots,K\}$ forward channel as $\boldsymbol{h}_{\mathrm{F},k}^H \in \mathbb{C}^{1 \times Q}$, the node $k$-user backward channel as $h_{\mathrm{B},k}$, and the cascaded channel via tag $k$ as $\boldsymbol{h}_{\mathrm{C},k}^H \triangleq h_{\mathrm{B},k} \boldsymbol{h}_{\mathrm{F},k}^H \in \mathbb{C}^{1 \times Q}$.
 		% Let $x_{\mathcal{K}} \triangleq \{x_k : k \in \mathcal{K}\}$ be the backscatter symbols of all UniScatters.
@@
 		\end{subequations}
-		where $\alpha_k$ is the amplitude scattering ratio of UniScatter node $k$, $\boldsymbol{\alpha} \triangleq [\alpha_1,\ldots,\alpha_K]^T \in \mathbb{R}_+^{K \times 1}$, $x_k \in \mathcal{X} \triangleq \{c_1,\ldots,c_M\}$ is the coded backscatter symbol of node $k$, and $\boldsymbol{x} \triangleq [x_1,\ldots,x_K]^H \in \mathbb{C}^{K \times 1}$.
+		where $\alpha_k$ is the amplitude scattering ratio of UniScatter node $k$, $\boldsymbol{\alpha} \triangleq [\alpha_1,\ldots,\alpha_K]^T \in \mathbb{R}_+^{K \times 1}$, $x_k \in \mathcal{X} \triangleq \{c_1,\ldots,c_M\}$ is the coded backscatter symbol of node $k$, and $\boldsymbol{x} \triangleq [x_1,\ldots,x_K]^H \in \mathbb{C}^{K \times 1}$, $\boldsymbol{H}_{\mathrm{C}} \triangleq [\boldsymbol{h}_{\mathrm{C},1},\ldots,\boldsymbol{h}_{\mathrm{C},K}]^H \in \mathbb{C}^{K \times Q}$.
 The signal received by the user at primary block $n \in \mathcal{N} \triangleq \{1,\ldots,N\}$ is

### 2022-08-16 main.tex
:pencil: Update signal model

@@
 \newacronym{dmtmac}{DMTMAC}{Discrete Memoryless Thresholding Multiple Access Channel}
-\newacronym{dtmac}{DTMAC}{Discrete Thresholding Multiple Access Channel}
+% \newacronym{dtmac}{DTMAC}{Discrete Thresholding Multiple Access Channel}
 \newacronym{dp}{DP}{Dynamic Programming}
@@
 	$\boldsymbol{0}$ and $\boldsymbol{1}$ denote zero and one array of appropriate size, respectively.
-	$\mathbb{R}_+^{x \times y}$ and $\mathbb{C}^{x \times y}$ denote the real nonnegative and complex spaces of dimension $x \times y$, respectively.
+$\mathbb{I}^{x \times y}$, $\mathbb{R}_+^{x \times y}$, and $\mathbb{C}^{x \times y}$ denote the unit, real nonnegative, and complex spaces of dimension $x \times y$, respectively.
 	$j$ denotes the imaginary unit.
@@
 		\end{equation}
-		where $0 \le \alpha \le 1$ is the amplitude scattering ratio at the direction of interest.
+		where $\alpha \in \mathbb{I}$ is the amplitude scattering ratio at the direction of interest.
 	\end{subsection}
@@
 		\end{equation}
-		where $0 \le \beta_m \le 1$ is the overall amplitude scattering ratio of state $m$.
+		where $\beta_m \in \mathbb{I}$ is the overall amplitude scattering ratio of state $m$.
 	\end{subsection}
@@
 \begin{section}{UniScatter}
-	% Using shared spectrum, energy and infrastructures, UniScatter is a novel passive communication/assistance protocol that generalizes \gls{bc}, \gls{sr} and \gls{ris} from the perspective of distribution.
-	% Using shared spectrum, energy and infrastructures, UniScatter is a novel passive communication/assistance protocol that generalizes \gls{bc}, \gls{sr} and \gls{ris} via \emph{physical} and \emph{probability} distributions.
 	Using shared spectrum, energy and infrastructures, UniScatter is a novel passive communication/assistance protocol that generalizes \gls{bc}, \gls{sr} and \gls{ris} in a \emph{physically} and \emph{probabilistically} distributed manner.
@@
 		Denote the \gls{ap}-user direct channel as $\boldsymbol{h}_{\mathrm{D}}^H \in \mathbb{C}^{1 \times Q}$, the \gls{ap}-node $k \in \mathcal{K} \triangleq \{1,\ldots,K\}$ forward channel as $\boldsymbol{h}_{\mathrm{F},k}^H \in \mathbb{C}^{1 \times Q}$, the node $k$-user backward channel as $h_{\mathrm{B},k}$, and the cascaded channel via tag $k$ as $\boldsymbol{h}_{\mathrm{C},k}^H \triangleq h_{\mathrm{B},k} \boldsymbol{h}_{\mathrm{F},k}^H \in \mathbb{C}^{1 \times Q}$.
-		% Let $x_{\mathcal{K}} \triangleq \{x_k : k \in \mathcal{K}\}$ be the backscatter symbols of all UniScatters.
 		Let $x_{\mathcal{K}} \triangleq (x_1,\ldots,x_K)$ be the backscatter symbol tuple of all UniScatter nodes.
-		Consider the signal model during one backscatter block (i.e., $N$ primary blocks).
-		% We assume the primary symbol follows standard \gls{cscg} distribution and the backscatter symbol of all tags employs $M$-\gls{qam}.
-		Under perfect synchronization, the equivalent primary channel is a function of \emph{coded} backscatter symbols
+		Without loss of generality, we consider one specific backscatter block (i.e., $N$ primary blocks) in the following context.
+		Due to double modulation, the equivalent primary channel is a function of \emph{coded} backscatter symbols
 		\begin{subequations}
@@
 		\end{subequations}
-		where $\alpha_k$ is the amplitude scattering ratio of UniScatter node $k$, $\boldsymbol{\alpha} \triangleq [\alpha_1,\ldots,\alpha_K]^T \in \mathbb{R}_+^{K \times 1}$, $x_k \in \mathcal{X} \triangleq \{c_1,\ldots,c_M\}$ is the coded backscatter symbol of node $k$, and $\boldsymbol{x} \triangleq [x_1,\ldots,x_K]^H \in \mathbb{C}^{K \times 1}$, $\boldsymbol{H}_{\mathrm{C}} \triangleq [\boldsymbol{h}_{\mathrm{C},1},\ldots,\boldsymbol{h}_{\mathrm{C},K}]^H \in \mathbb{C}^{K \times Q}$.
+		where $\alpha_k \in \mathbb{I}$ is the amplitude scattering ratio of UniScatter node $k$, $x_k \in \mathcal{X} \triangleq \{c_1,\ldots,c_M\}$ is the coded backscatter symbol of node $k$, $\boldsymbol{\alpha} \triangleq [\alpha_1,\ldots,\alpha_K]^T \in \mathbb{I}^{K \times 1}$, $\boldsymbol{x} \triangleq [x_1,\ldots,x_K]^H \in \mathcal{X}^{K \times 1}$, and $\boldsymbol{H}_{\mathrm{C}} \triangleq [\boldsymbol{h}_{\mathrm{C},1},\ldots,\boldsymbol{h}_{\mathrm{C},K}]^H \in \mathbb{C}^{K \times Q}$.
 The signal received by the user at primary block $n \in \mathcal{N} \triangleq \{1,\ldots,N\}$ is
@@
 			y[n] = \boldsymbol{h}_{\mathrm{E}}^H(x_{\mathcal{K}}) \boldsymbol{w} s[n] + v[n],
-		\end{equation}
-		where $s \sim \mathcal{CN}(0,1)$ is the primary symbol, $v \sim \mathcal{CN}(0,\sigma_v^2)$ is the \gls{awgn}, and $\boldsymbol{w} \in \mathbb{C}^{Q \times 1}$ is the active beamforming vector with average power constraint $\lVert \boldsymbol{w} \rVert^2 \le P$.
-		% The equivalent channel for primary link is subject to backscatter uncertainty
-		% The equivalent primary channel is a function of backscatter symbols  as
-		% \begin{equation}
-		% 	% \boldsymbol{h}_{\mathrm{E}}^H(x_{\mathcal{K}}) \triangleq \boldsymbol{h}_{\mathrm{D}}^H + \sum_{k \in \mathcal{K}} \sqrt{\alpha_k} \boldsymbol{h}_{\mathrm{C},k}^H x_k.
-		% 	\boldsymbol{h}_{\mathrm{E}}^H(\boldsymbol{x}) \triangleq \boldsymbol{h}_{\mathrm{D}}^H + \boldsymbol{x}^H \mathrm{diag}(\boldsymbol{\alpha}) \boldsymbol{H}_{\mathrm{C}}.
-		% 	\label{eq:equivalent_channel}
-		% \end{equation}
-
-		% where $\alpha_k$ and $x_k$ denote respectively the harvest-backscatter efficiency and backscatter symbol of tag $k$, $s[n]$ and $w[n] \sim \mathcal{CN}(0,\sigma_v^2)$ denote respectively the primary symbol and \gls{awgn} at block $n$, and $\boldsymbol{w} \in \mathbb{C}^{Q \times 1}$ is the transmit precoder satisfying power constraint $\lVert \boldsymbol{w} \rVert^2 \le P$.
-		% For the ease of notation, we define $x_{\mathcal{K}} \triangleq \{x_k : k \in \mathcal{K}\}$ as the tag input combination, and $\boldsymbol{y} \triangleq \left[y[1],\ldots,y[N]\right]^T \in \mathbb{C}^{N \times 1}$ as the received signal per backscatter symbol period.
-		% For primary transmission, the equivalent channel is subject to backscatter modulation uncertainty as
-		% \begin{equation}
-		% 	\boldsymbol{h}_{\mathrm{E}}^H(x_{\mathcal{K}}) \triangleq \boldsymbol{h}_{\mathrm{D}}^H + \sum_{k \in \mathcal{K}} \sqrt{\alpha_k} \boldsymbol{h}_{\mathrm{C},k}^H x_k.
-		% 	\label{eq:equivalent_channel}
-		% \end{equation}
-
-		% At a specific backscatter block, denote $m_k \in \mathcal{M}$ as the state index of UniScatter $k$, and let $m_{\mathcal{K}} \triangleq \{m_k: k \in \mathcal{K}\}$ collect the state indexes of all UniScatters.
-		At a specific backscatter block, denote $m_k \in \mathcal{M}$ as the state index of node $k$, and let $m_{\mathcal{K}} \triangleq (m_1,\ldots,m_K)$ be the state index tuple of all nodes.
-		% The received signal at primary block $n$ is subject to the variation of $s[n]$ and $v[n]$, and thus distributed as $y[n] \sim \mathcal{CN}(0,\sigma_v^2)$
-		Conditioned on $m_{\mathcal{K}}$, the received signal at primary block $n$ is subject to the variation of $s[n]$ and $v[n]$, distributed as $y[n] \sim \mathcal{CN}(0,\sigma_{m_{\mathcal{K}}}^2)$ with
-		\begin{equation}
-			% \sigma_{m_{\mathcal{K}}}^2 = \Bigl\lvert \underbrace{\bigl(\boldsymbol{h}_{\mathrm{D}}^H + \sum_{k \in \mathcal{K}} \sqrt{\alpha_k} \boldsymbol{h}_{\mathrm{C},k}^H x_{m_k}\bigr)}_{\boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}})} \boldsymbol{w} \Bigr\rvert^2 + \sigma_v^2,
-			\sigma_{m_{\mathcal{K}}}^2 = \lvert \boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2 + \sigma_v^2,
+			\label{eq:receive_signal}
+		\end{equation}
+		where $s \sim \mathcal{CN}(0,1)$ is the primary symbol, $v \sim \mathcal{CN}(0,\sigma_v^2)$ is the \gls{awgn}, and $\boldsymbol{w} \in \mathbb{C}^{Q \times 1}$ is the active beamforming vector subject to average transmit power constraint $\lVert \boldsymbol{w} \rVert^2 \le P$.
+		Denote $m_k \in \mathcal{M} \triangleq \{1,\ldots,M\}$ as the reflection state index of node $k$, and $m_{\mathcal{K}} \triangleq (m_1,\ldots,m_K)$ as the state index tuple of all nodes.
+		Conditioned on backscatter index tuple $m_{\mathcal{K}}$, the received signal \eqref{eq:receive_signal} follows \gls{cscg} distribution $y[n] \sim \mathcal{CN}(0,\sigma_{m_{\mathcal{K}}}^2)$, where
+		\begin{equation}
+			\sigma_{m_{\mathcal{K}}}^2 = \lvert \boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2 + \sigma_v^2
 			\label{eq:receive_variance}
 		\end{equation}
-		where $x_{m_k}$ and $x_{m_\mathcal{K}}$ are the symbol and symbol tuple associated with state $m_k$ and state tuple $m_{\mathcal{K}}$, respectively.%
+		is the received variance and $x_{m_\mathcal{K}}$ is the backscatter symbol tuple associated with $m_{\mathcal{K}}$.
+		For node $k$, let $x_{m_k}$ be the backscatter symbol associated with index $m_k$.%
 		\footnote{
-			$x_k$ and $x_{\mathcal{K}}$ are random variables, while $x_{m_k}$ and $x_{m_{\mathcal{K}}}$ are their instances indexed by $m_k$ and $m_{\mathcal{K}}$.
-		}
-		Also, denote the total received energy within backscatter block as $z=\sum_{n=1}^N \lvert y[n] \rvert^2$.
-		% As the sum of $N$ \gls{iid} exponential variables, conditioned on $m_{\mathcal{K}}$, its \gls{pdf} follows Erlang distribution
-		As the sum of $N$ \gls{iid} exponential variables, the \gls{pdf} of $z$ conditioned on $m_{\mathcal{K}}$ follows Erlang distribution
+			Please note $x_k$ and $x_{\mathcal{K}}$ are random variable and tuple, while $x_{m_k}$ and $x_{m_{\mathcal{K}}}$ are their instances of index $m_k$ and $m_{\mathcal{K}}$.
+		}
+		Besides, we define the total received energy per backscatter block as $z=\sum_{n=1}^N \lvert y[n] \rvert^2$.
+		Since $z$ is the sum of $N$ \gls{iid} exponential variables, its \gls{pdf} conditioned on $m_{\mathcal{K}}$ follows Gamma distribution
 		\begin{equation}
 			f(z|\mathcal{H}_{m_{\mathcal{K}}}) = \frac{z^{N-1} \exp(-z/\sigma_{m_{\mathcal{K}}}^2)}{\sigma_{m_{\mathcal{K}}}^{2N} (N-1)!},
-			% f(z|\mathcal{H}_{m_{\mathcal{K}}}) = \frac{z^{N-1} \exp(\frac{-z}{\sigma_{m_{\mathcal{K}}}^2})}{\sigma_{m_{\mathcal{K}}}^{2N} (N-1)!},
 			\label{eq:energy_distribution}
@@
 		where $\mathcal{H}_{m_{\mathcal{K}}}$ denotes hypothesis $m_{\mathcal{K}}$.
-		% To accommodate backscatter characteristics and reduce decoding complexity, we consider a joint semi-coherent energy detection for all UniScatters based on disjoint decision regions over accumulated energy $z$.
-		% !
-		% To accommodate backscatter characteristics and reduce decoding complexity, we consider a joint semi-coherent detection for all UniScatter nodes over accumulated energy $z$.
-		% % To reduce decoding complexity, we consider a joint semi-coherent energy detection for all UniScatters based on disjoint decision regions over accumulated energy $z$.
-		% \begin{figure}[!t]
-		% 	\centering
-		% 	\resizebox{0.9\columnwidth}{!}{
-		% 		\input{assets/illustration/energy_distribution.tex}
-		% 	}
-		% 	% \caption{\gls{pdf} of Average Received Power Conditioned on Different Input Hypothesis. Example \gls{ml}.}
-		% 	\caption{
-		% 		\gls{pdf} of total received energy per backscatter block, conditioned on different input hypothesis.
-		% 		% This \gls{ml} decision consists of convex regions and is generally rate-suboptimal except for equiprobable inputs.}
-		% 		Here, the convex \gls{ml} decision regions are generally rate-suboptimal except for equiprobable inputs.
-		% 	}
-		% 	\label{fi:energy_distribution}
-		% \end{figure}
-		% The idea is presented in Fig. \ref{fi:energy_distribution}.
-		% !
-		% As illustrated in Fig. \ref{fi:energy_distribution}, o
-		Once disjoint energy decision regions are determined, we can construct a \gls{dtmac} and formulate the transition probability from input $x_{m_{\mathcal{K}}}$ to output $\hat{x}_{m_{\mathcal{K}}'}$ as
-		% it essentially formulates a \gls{dtmac}, and the transition probability from input $x_{m_{\mathcal{K}}}$ to output $\hat{x}_{m_{\mathcal{K}}'}$ is
+		As illustrated in Fig. \ref{fi:energy_distribution}, the UniScatter receiver divides the received energy space into disjoint decision regions associated with those hypotheses.
+		For example, if the total received energy during a backscatter block falls within region $\mathcal{R}_{m_{\mathcal{K}}}$, then the detector output would be $x_{m_{\mathcal{K}}}$.
+		\begin{remark}
+			Interestingly, the capacity-achieving decision design for \gls{dmtc} remains under-investigated, and some attempts were made for single source with binary inputs \cite{Qian2019b,Nguyen2021b}.
+			For non-binary inputs with arbitrary distribution, the optimal decision region for each letter can be non-convex (i.e., with non-adjacent partitions) and the optimal number of thresholds is still unknown \cite{Nguyen2018,Nguyen2021}.
+		\end{remark}
+		Like most existing literatures, we limit the scope of this paper to convex decision regions and consider sequential decision thresholds design therein.
+		% In particular, we define a general bijective mapping from backscatter index tuples to ordered indexes $f : m_{\mathcal{K}} \to \mathcal{L} \triangleq \{1,\ldots,L \triangleq M^K\}$, and use both notation interchangably in the following context.
+		% In particular, we define a general bijective mapping from backscatter index tuples to ordered indexes $\mathcal{M}^K \to \mathcal{L} \triangleq \{1,\ldots,L \triangleq M^K\}$, $m_{\mathcal{K}} \mapsto l$ and use both notation interchangably in the following context.
+		For the ease of notations, we define a general bijective function transforming backscatter index tuple $m_{\mathcal{K}}$ to integer $l \in \mathcal{L} \triangleq \{1,\ldots,L \triangleq M^K\}$, and use both notation interchangeably in the following context.
+		As such, the convex decision region of backscatter index tuple $m_{\mathcal{K}}$ or equivalent letter $l$ can be written as
+		\begin{equation}
+			\mathcal{R}_{m_{\mathcal{K}}} \triangleq [t_{l-1},t_l), \quad t_{l-1} \le t_l.
+		\end{equation}
+		Once the decision threshold vector $\boldsymbol{t} \triangleq [t_0,\ldots,t_L]^T \in \mathbb{R}_+^{(L+1) \times 1}$ is determined, we can formulate a \gls{dmtmac} with transition probability from input $x_{m_{\mathcal{K}}}$ to output $\hat{x}_{m_{\mathcal{K}}'}$
 		\begin{equation}
 			P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}}) = \int_{\mathcal{R}_{m_{\mathcal{K}}'}} f(z|\mathcal{H}_{m_{\mathcal{K}}}) \, d z,
-			\label{eq:dtmac}
-		\end{equation}
-		where $\mathcal{R}_{m_{\mathcal{K}}'}$ is the decision region of hypothesis $\mathcal{H}_{m_{\mathcal{K}}'}$.
-An example of \gls{ml} energy decision is illustrated in Fig.
-\ref{fi:energy_distribution}.
-
-		\begin{remark}
-			% For a general input distribution, not only the optimal decision thresholds
-			The rate-optimal thresholding channel design remains under-investigated, and some attempts were made for single source with binary inputs in \cite{Qian2019b,Nguyen2021b}.
-			% The question was only answered for single source with binary inputs in \cite{Qian2019b,Nguyen2021b}.
-			% Some attempts for single source with binary inputs were presented in \cite{Qian2019b,Nguyen2021b}.
-			For non-binary inputs with general distribution, the optimal decision region for each letter can be non-convex (i.e., with non-adjacent partitions) and the optimal number of thresholds is still unknown.
-			% Next, we will restrict the design over convex decision regions.
-			% For a general input distribution, not only the rate-optimal decision thresholds
-			% % Interestingly, the optimal threshold design to maximize the mutual information for a general \gls{dmtc} with a fixed number of output letters remains an open issue.
-			% % The reason is that each decision region may contain more than one disjoint partitions (i.e., non-convex) and the number of thresholds are unknown.
-			% % Fortunately, for the proposed energy detection, we proved that the \gls{dmtc} capacity can be achieved using only convex decision regions.
-			% not only the capacity-achieving thresholding design remains an open problem, but also the optimal number of thresholds for general non-binary-input channels remains unknown.
-		\end{remark}
-		In the following context, we restrict all decision regions to convex and optimize decision thresholds accordingly.
-That is, for any bijective mapping $f : m_{\mathcal{K}} \to \mathcal{L} \triangleq \{1,\ldots,M^K\}$, the decision region of letter $l \in \mathcal{L}$ is defined as $\mathcal{R}_l \triangleq [t_{l-1},t_l)$, where $t_{l-1} \le t_l$.
-We also define the decision threshold vector as $\boldsymbol{t} \triangleq [t_0,\ldots,t_L]^T \in \mathbb{R}_+^{(L+1) \times 1}$.
+			\label{eq:dmtmac}
+		\end{equation}
+		and backscatter channel coding can be performed on top of it.
 	\end{subsection}
@@
 		\begin{equation}
-			I^{\mathrm{B}}(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}}) \triangleq \sum_{m_{\mathcal{K}}'} P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}}) \log \frac{P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}})}{P(\hat{x}_{m_{\mathcal{K}}'})},
+			I_{\mathrm{B}}(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}}) \triangleq \sum_{m_{\mathcal{K}}'} P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}}) \log \frac{P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}})}{P(\hat{x}_{m_{\mathcal{K}}'})},
 			\label{eq:backscatter_information_function}
@@
 		\begin{equation}
-			% I_{\mathrm{B},k}(x_{m_k};\hat{x}_{\mathcal{K}}) \triangleq \sum_{m_{\mathcal{K} \setminus \{k\}}} P_{\mathcal{K} \setminus \{k\}}(x_{m_{\mathcal{K} \setminus \{k\}}}) I_{\mathrm{B}}(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}}),
-			I^{\mathrm{B}}_{k}(x_{m_k};\hat{x}_{\mathcal{K}}) \triangleq \sum_{m_{\mathcal{K} \setminus \{k\}}} P_{\mathcal{K} \setminus \{k\}}(x_{m_{\mathcal{K} \setminus \{k\}}}) I^{\mathrm{B}}(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}}),
+			I_{\mathrm{B},k}(x_{m_k};\hat{x}_{\mathcal{K}}) \triangleq \sum_{m_{\mathcal{K} \setminus \{k\}}} P_{\mathcal{K} \setminus \{k\}}(x_{m_{\mathcal{K} \setminus \{k\}}}) I_{\mathrm{B}}(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}}),
 			\label{eq:backscatter_marginal_information}
@@
 		\begin{equation}
-			% I^{\mathrm{B}}(x_{\mathcal{K}};\hat{x}_{\mathcal{K}}) = \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) \sum_{m_{\mathcal{K}}'} P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}}) \log \frac{P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}})}{P(\hat{x}_{m_{\mathcal{K}}'})}.
-			I^{\mathrm{B}}(x_{\mathcal{K}};\hat{x}_{\mathcal{K}}) = \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) I^{\mathrm{B}}(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}}).
+			I_{\mathrm{B}}(x_{\mathcal{K}};\hat{x}_{\mathcal{K}}) = \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) I_{\mathrm{B}}(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}}).
 			\label{eq:backscatter_mutual_information}
@@
 		\begin{equation}
-			I^{\mathrm{P}}(s;y|x_{m_{\mathcal{K}}}) \triangleq \log \Bigl(1 + \frac{\lvert \boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_v^2}\Bigr),
+			I_{\mathrm{P}}(s;y|x_{m_{\mathcal{K}}}) \triangleq \log \Bigl(1 + \frac{\lvert \boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_v^2}\Bigr),
 			\label{eq:primary_information_function}
@@
 		\begin{equation}
-			I^{\mathrm{P}}_{k}(s;y|x_{m_k}) \triangleq \sum_{m_{\mathcal{K} \setminus \{k\}}} P_{\mathcal{K} \setminus \{k\}}(x_{m_{\mathcal{K} \setminus \{k\}}}) I^{\mathrm{P}}(s;y|x_{m_{\mathcal{K}}}),
+			I_{\mathrm{P},k}(s;y|x_{m_k}) \triangleq \sum_{m_{\mathcal{K} \setminus \{k\}}} P_{\mathcal{K} \setminus \{k\}}(x_{m_{\mathcal{K} \setminus \{k\}}}) I_{\mathrm{P}}(s;y|x_{m_{\mathcal{K}}}),
 			\label{eq:primary_marginal_information}
@@
 		\begin{equation}
-			% I^{\mathrm{P}}(s;y|x_{\mathcal{K}}) = \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) \log \left(1 + \frac{\lvert \boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_v^2}\right).
-			I^{\mathrm{P}}(s;y|x_{\mathcal{K}}) = \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) I^{\mathrm{P}}(s;y|x_{m_{\mathcal{K}}}).
+			% I_{\mathrm{P}}(s;y|x_{\mathcal{K}}) = \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) \log \left(1 + \frac{\lvert \boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_v^2}\right).
+			I_{\mathrm{P}}(s;y|x_{\mathcal{K}}) = \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) I_{\mathrm{P}}(s;y|x_{m_{\mathcal{K}}}).
 			\label{eq:primary_mutual_information}
@@
 			I(x_{m_{\mathcal{K}}})
-			 & \triangleq \rho I^{\mathrm{P}}(s;y|x_{m_{\mathcal{K}}}) + (1 - \rho) I^{\mathrm{B}}(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}}),\label{eq:weighted_sum_information_function} \\
+			 & \triangleq \rho I_{\mathrm{P}}(s;y|x_{m_{\mathcal{K}}}) + (1 - \rho) I_{\mathrm{B}}(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}}),\label{eq:weighted_sum_information_function} \\
 			I_k(x_{m_k})
-			 & \triangleq \rho I^{\mathrm{P}}_{k}(s;y|x_{m_k}) + (1 - \rho) I^{\mathrm{B}}_{k}(x_{m_k};\hat{x}_{\mathcal{K}}),\label{eq:weighted_sum_marginal_information}                 \\
+			 & \triangleq \rho I_{\mathrm{P},k}(s;y|x_{m_k}) + (1 - \rho) I_{\mathrm{B},k}(x_{m_k};\hat{x}_{\mathcal{K}}),\label{eq:weighted_sum_marginal_information}                     \\
 			I(x_{\mathcal{K}})
-			 & \triangleq \rho I^{\mathrm{P}}(s;y|x_{\mathcal{K}}) + (1 - \rho) I^{\mathrm{B}}(x_{\mathcal{K}};\hat{x}_{\mathcal{K}}),\label{eq:weighted_sum_mutual_information}
+			 & \triangleq \rho I_{\mathrm{P}}(s;y|x_{\mathcal{K}}) + (1 - \rho) I_{\mathrm{B}}(x_{\mathcal{K}};\hat{x}_{\mathcal{K}}),\label{eq:weighted_sum_mutual_information}
 		\end{align}
-		where $0 \le \rho \le 1$ is the relative priority of the primary link.
+		where $\rho \in \mathbb{I}$ is the relative priority of the primary link.
 
@@
 	\begin{subsection}{Input Distribution}
-		% For any fixed decision boundary $\boldsymbol{t}$ and transmit precoder $\boldsymbol{w}$, the equivalent \gls{dtmac} can be formulated by \eqref{eq:dtmac} and problem \eqref{op:weighted_sum_rate} boils down to
-		For any given $\boldsymbol{w}$ and $\boldsymbol{t}$, we can construct the equivalent \gls{dtmac} by \eqref{eq:dtmac} and simplify \eqref{op:weighted_sum_rate} to
+		% For any fixed decision boundary $\boldsymbol{t}$ and transmit precoder $\boldsymbol{w}$, the equivalent \gls{dmtmac} can be formulated by \eqref{eq:dmtmac} and problem \eqref{op:weighted_sum_rate} boils down to
+		For any given $\boldsymbol{w}$ and $\boldsymbol{t}$, we can construct the equivalent \gls{dmtmac} by \eqref{eq:dmtmac} and simplify \eqref{op:weighted_sum_rate} to
 		\begin{maxi!}
@@
 				\State \phantom{Set} $f(z|\mathcal{H}_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}$ by \eqref{eq:energy_distribution}
-				\State \phantom{Set} $P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}, m_{\mathcal{K}}'$ by \eqref{eq:dtmac}
+				\State \phantom{Set} $P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}, m_{\mathcal{K}}'$ by \eqref{eq:dmtmac}
 				\State Initialize $r \gets 0$
@@
 		\end{equation}
-		is the regularized incomplete Gamma function that substitutes the \gls{dtmac} transition probability \eqref{eq:dtmac}.
+		is the regularized incomplete Gamma function that substitutes the \gls{dmtmac} transition probability \eqref{eq:dmtmac}.
 		Its series representation is given by \cite[Theorem~3]{Jameson2016}
@@
 
-		Remark \ref{re:backscatter_detection} suggests any $\boldsymbol{t}$ maximizes total backscatter mutual information $I^{\mathrm{B}}(x_{\mathcal{K}};\hat{x}_{\mathcal{K}})$ is also optimal for problem \eqref{op:decision_threshold}.
+		Remark \ref{re:backscatter_detection} suggests any $\boldsymbol{t}$ maximizes total backscatter mutual information $I_{\mathrm{B}}(x_{\mathcal{K}};\hat{x}_{\mathcal{K}})$ is also optimal for problem \eqref{op:decision_threshold}.
 
@@
 			% In terms of total backscatter rate, we can regard all nodes as an equivalent information source with augmented alphabet of node state tuple $x_{m_{\mathcal{K}}}$.
-			In terms of total backscatter rate, the nodes can be regarded as an equivalent source with augmented alphabet of symbol tuple $x_{m_{\mathcal{K}}}$, and the \gls{dtmac} \eqref{eq:dtmac} essentially reduces to a \gls{dmtc}.
-			% As such, the \gls{dtmac} \eqref{eq:dtmac} is essentially a \gls{dmtc}, and decision threshold design can be simplified accordingly.
+			In terms of total backscatter rate, the nodes can be regarded as an equivalent source with augmented alphabet of symbol tuple $x_{m_{\mathcal{K}}}$, and the \gls{dmtmac} \eqref{eq:dmtmac} essentially reduces to a \gls{dmtc}.
+			% As such, the \gls{dmtmac} \eqref{eq:dmtmac} is essentially a \gls{dmtc}, and decision threshold design can be simplified accordingly.
 		\end{remark}
@@
 		% \begin{proposition}
-		% 	For a discrete-input continuous-output channel in Erlang distribution \eqref{eq:energy_distribution}, if the \gls{dmtc} is constructed for detection (i.e., same input/output alphabet) and $L$ input letters are with non-zero probability, then it is possible to achieve the \gls{dmtc} capacity by $L$ non-empty convex decision regions defined by $L+1$ distinct decision thresholds.
+		% 	For a discrete-input continuous-output channel in Gamma distribution \eqref{eq:energy_distribution}, if the \gls{dmtc} is constructed for detection (i.e., same input/output alphabet) and $L$ input letters are with non-zero probability, then it is possible to achieve the \gls{dmtc} capacity by $L$ non-empty convex decision regions defined by $L+1$ distinct decision thresholds.
 		% 	\label{pr:threshold}
@@
 		We observe that input distribution-adaptive threshold designs achieve higher total backscatter rate than \gls{ml}.
-		This is because the decision regions can be flexibly adjusted to enhance the capacity of \gls{dtmac} \eqref{eq:dtmac}.
+		This is because the decision regions can be flexibly adjusted to enhance the capacity of \gls{dmtmac} \eqref{eq:dmtmac}.
 		For example, the tuples with negligible input probability should have narrower decision regions than those frequently employed, in order to improve detection performance.

### 2022-08-17 main.tex
:pencil: Update information theory and input design

@@
 		Due to double modulation, the equivalent primary channel is a function of \emph{coded} backscatter symbols
-		\begin{subequations}
+		% \begin{subequations}
+		% 	\label{eq:equivalent_channel}
+		% 	\begin{align}
+		% 		\boldsymbol{h}_{\mathrm{E}}^H(x_{\mathcal{K}})
+		% 		 & \triangleq \boldsymbol{h}_{\mathrm{D}}^H + \sum_{k \in \mathcal{K}} \alpha_k \boldsymbol{h}_{\mathrm{C},k}^H x_k   \\
+		% 		 & = \boldsymbol{h}_{\mathrm{D}}^H + \boldsymbol{x}^H \mathrm{diag}(\boldsymbol{\alpha}) \boldsymbol{H}_{\mathrm{C}},
+		% 	\end{align}
+		% \end{subequations}
+		\begin{equation}
+			\boldsymbol{h}_{\mathrm{E}}^H(x_{\mathcal{K}}) \triangleq \boldsymbol{h}_{\mathrm{D}}^H + \sum_{k \in \mathcal{K}} \alpha_k \boldsymbol{h}_{\mathrm{C},k}^H x_k = \boldsymbol{h}_{\mathrm{D}}^H + \boldsymbol{x}^H \mathrm{diag}(\boldsymbol{\alpha}) \boldsymbol{H}_{\mathrm{C}},
 			\label{eq:equivalent_channel}
-			\begin{align}
-				\boldsymbol{h}_{\mathrm{E}}^H(x_{\mathcal{K}})
-				 & \triangleq \boldsymbol{h}_{\mathrm{D}}^H + \sum_{k \in \mathcal{K}} \alpha_k \boldsymbol{h}_{\mathrm{C},k}^H x_k   \\
-				 & = \boldsymbol{h}_{\mathrm{D}}^H + \boldsymbol{x}^H \mathrm{diag}(\boldsymbol{\alpha}) \boldsymbol{H}_{\mathrm{C}},
-			\end{align}
-		\end{subequations}
-		where $\alpha_k \in \mathbb{I}$ is the amplitude scattering ratio of UniScatter node $k$, $x_k \in \mathcal{X} \triangleq \{c_1,\ldots,c_M\}$ is the coded backscatter symbol of node $k$, $\boldsymbol{\alpha} \triangleq [\alpha_1,\ldots,\alpha_K]^T \in \mathbb{I}^{K \times 1}$, $\boldsymbol{x} \triangleq [x_1,\ldots,x_K]^H \in \mathcal{X}^{K \times 1}$, and $\boldsymbol{H}_{\mathrm{C}} \triangleq [\boldsymbol{h}_{\mathrm{C},1},\ldots,\boldsymbol{h}_{\mathrm{C},K}]^H \in \mathbb{C}^{K \times Q}$.
+		\end{equation}
+		where $\alpha_k \in \mathbb{I}$ is the amplitude scattering ratio of UniScatter node $k$, $x_k \in \mathcal{X} \triangleq \{c_1,\ldots,c_M\}$ is the \emph{coded} backscatter symbol of node $k$, $\boldsymbol{\alpha} \triangleq [\alpha_1,\ldots,\alpha_K]^T \in \mathbb{I}^{K \times 1}$, $\boldsymbol{x} \triangleq [x_1,\ldots,x_K]^H \in \mathcal{X}^{K \times 1}$, and $\boldsymbol{H}_{\mathrm{C}} \triangleq [\boldsymbol{h}_{\mathrm{C},1},\ldots,\boldsymbol{h}_{\mathrm{C},K}]^H \in \mathbb{C}^{K \times Q}$.
 The signal received by the user at primary block $n \in \mathcal{N} \triangleq \{1,\ldots,N\}$ is
@@
 		\begin{remark}
-			Interestingly, the capacity-achieving decision design for \gls{dmtc} remains under-investigated, and some attempts were made for single source with binary inputs \cite{Qian2019b,Nguyen2021b}.
+			Interestingly, the capacity-achieving decision design for \gls{dmtc} remains under-investigated, and some attempts were made for a single source with binary inputs \cite{Qian2019b,Nguyen2021b}.
 			For non-binary inputs with arbitrary distribution, the optimal decision region for each letter can be non-convex (i.e., with non-adjacent partitions) and the optimal number of thresholds is still unknown \cite{Nguyen2018,Nguyen2021}.
@@
 		Like most existing literatures, we limit the scope of this paper to convex decision regions and consider sequential decision thresholds design therein.
-		% In particular, we define a general bijective mapping from backscatter index tuples to ordered indexes $f : m_{\mathcal{K}} \to \mathcal{L} \triangleq \{1,\ldots,L \triangleq M^K\}$, and use both notation interchangably in the following context.
-		% In particular, we define a general bijective mapping from backscatter index tuples to ordered indexes $\mathcal{M}^K \to \mathcal{L} \triangleq \{1,\ldots,L \triangleq M^K\}$, $m_{\mathcal{K}} \mapsto l$ and use both notation interchangably in the following context.
 		For the ease of notations, we define a general bijective function transforming backscatter index tuple $m_{\mathcal{K}}$ to integer $l \in \mathcal{L} \triangleq \{1,\ldots,L \triangleq M^K\}$, and use both notation interchangeably in the following context.
@@
 		\end{equation}
-		and backscatter channel coding can be performed on top of it.
-	\end{subsection}
-
-	\begin{subsection}{Achievable Rates}
-		Denote the input probability of state $m_k$ of UniScatter node $k$ as $P_k(x_{m_k})$, and define the input probability distribution vector of node $k$ as $\boldsymbol{p}_k \triangleq [P_k(c_1),\ldots,P_k(c_M)]^T \in \mathbb{R}^{M \times 1}$.
+		then perform backscatter channel coding on top of it.
+	\end{subsection}
+
+	\begin{subsection}{Information Theory}
+		Denote the input probability distribution vector of node $k$ as $\boldsymbol{p}_k \triangleq [P_k(c_1),\ldots,P_k(c_M)]^T \in \mathbb{I}^{M \times 1}$, and the probability of state $m_k$ as $P_k(x_{m_k})$.
 		With independent encoding at all nodes, the probability of backscatter symbol tuple $x_{m_{\mathcal{K}}}$ is
@@
 		\end{equation}
-		% Denote the input probability distribution vector of tag $k$ as $\boldsymbol{p}_k \triangleq [P_k(x_1),\ldots,P_k(x_M)]^T \in \mathbb{R}^{M \times 1}$, where $P_k(x_{m_k})$ is the probability at state $m_k$.
-		% Consider independent encoding at all tags such that the probability of input combination $x_{m_{\mathcal{K}}}$ is $P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) = \prod_{k \in \mathcal{K}} P_k(x_{m_k})$.
-		% The backscatter information function of input combination $x_{m_{\mathcal{K}}}$ is defined as
-		Similar to \cite{Rezaeian2004}, we define the backscatter information function between input symbol tuple instance $x_{m_{\mathcal{K}}}$ and output symbol tuple $\hat{x}_{\mathcal{K}}$ as
-		\begin{equation}
-			I_{\mathrm{B}}(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}}) \triangleq \sum_{m_{\mathcal{K}}'} P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}}) \log \frac{P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}})}{P(\hat{x}_{m_{\mathcal{K}}'})},
+
+		Similar to \cite{Rezaeian2004}, we define the backscatter information function between input symbol tuple instance $x_{m_{\mathcal{K}}}$ and output symbol tuple variable $\hat{x}_{\mathcal{K}}$ as
+		\begin{equation}
+			I_{\mathrm{B}}(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}}) \triangleq \sum_{m_{\mathcal{K}}'} P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}}) \log \frac{P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}})}{P_{\mathcal{K}}(\hat{x}_{m_{\mathcal{K}}'})},
 			\label{eq:backscatter_information_function}
 		\end{equation}
-		where $P(\hat{x}_{m_{\mathcal{K}}'}) = \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}})$.
+		where $P_{\mathcal{K}}(\hat{x}_{m_{\mathcal{K}}'}) = \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}})$ is the probability of channel output tuple $\hat{x}_{m_{\mathcal{K}}'}$.
 		We also define the backscatter marginal information of letter $x_{m_k}$ of node $k$ as
-		% Besides, the backscatter marginal information function associated with letter $x_{m_k}$ of tag $k$ is
 		\begin{equation}
@@
 		where $P_{\mathcal{K} \setminus \{k\}}(x_{m_{\mathcal{K} \setminus \{k\}}}) = \prod_{q \in \mathcal{K} \setminus \{k\}} P_{q}(x_{m_{q}})$.
-		Moreover, we can write the backscatter mutual information as
+		The backscatter mutual information can be written as
 		\begin{equation}
@@
 		\end{equation}
-
-		% Once the tag input combination is successfully decoded, the backscatter uncertainty can be eliminated and the equivalent channel for primary transmission can be updated by \eqref{eq:equivalent_channel}.
-
-		% eliminate modulation uncertainty
-		Once backscatter messages are successfully decoded, we can re-encode to determine $x_{\mathcal{K}}$ and retrieve equivalent primary channel by \eqref{eq:equivalent_channel}.
-We define the primary information function conditioned on backscatter symbol tuple $x_{m_{\mathcal{K}}}$ as
-		% Once backscatter symbols are successfully decoded, we can eliminate modulation uncertainty and retrieve equivalent primary channel by \eqref{eq:equivalent_channel}.
-We define the primary information function conditioned on backscatter symbol tuple $x_{m_{\mathcal{K}}}$ as
-		% \begin{equation}
-		% 	I_{\mathrm{P}}(x_{m_{\mathcal{K}}};\boldsymbol{y}) \triangleq \log \left(1 + \frac{\lvert \boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_v^2}\right),
-		% 	\label{eq:primary_information_function}
-		% \end{equation}
+		Once backscatter messages of all nodes are successfully decoded, we can re-code for backscatter symbol tuple $x_{\mathcal{K}}$, recover their reflection patterns by \eqref{eq:backscatter_modulation}, and retrieve the equivalent primary channel by \eqref{eq:equivalent_channel}.
+		Moreover, we define the primary information function conditioned on backscatter symbol tuple $x_{m_{\mathcal{K}}}$ as
 		\begin{equation}
@@
 		the primary marginal information conditioned on letter $x_{m_k}$ of node $k$ as
-		% the primary marginal information function associated with letter $x_{m_k}$ of tag $k$ is
 		\begin{equation}
@@
 		and the primary ergodic mutual information as
-		% and the primary (ergodic) mutual information is
-		\begin{equation}
-			% I_{\mathrm{P}}(s;y|x_{\mathcal{K}}) = \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) \log \left(1 + \frac{\lvert \boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_v^2}\right).
+		\begin{equation}
 			I_{\mathrm{P}}(s;y|x_{\mathcal{K}}) = \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) I_{\mathrm{P}}(s;y|x_{m_{\mathcal{K}}}).
@@
 
-		% Moreover, with $\rho \in [0,1]$ being the relative priority of the primary link, we define corresponding weighted sum information function, marginal information, and mutual information respectively as
-		Finally, with a slight abuse of notation, we define the corresponding weighted sum information function, marginal information, and mutual information respectively as
+		With a slight abuse of notation, we define the corresponding weighted sum information function, marginal information, and mutual information respectively as
 		\begin{align}
@@
 		where $\rho \in \mathbb{I}$ is the relative priority of the primary link.
-
-		% Therefore, the weighted sum information function, marginal information function, and mutual information of primary and backscatter links are respectively given by
-		% \begin{align}
-		% 	I(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}},\boldsymbol{y})
-		% 	 & \triangleq \rho I_{\mathrm{P}}(x_{m_{\mathcal{K}}};\boldsymbol{y}) + (1 - \rho) I_{\mathrm{B}}(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}}),\label{eq:weighted_sum_information_function} \\
-		% 	I_k(x_{m_k};\hat{x}_{\mathcal{K}},\boldsymbol{y})
-		% 	 & \triangleq \rho I_{\mathrm{P},k}(x_{m_k};\boldsymbol{y}) + (1 - \rho) I_{\mathrm{B},k}(x_{m_k};\hat{x}_{\mathcal{K}}),\label{eq:weighted_sum_marginal_information}                     \\
-		% 	I(x_{\mathcal{K}};\hat{x}_{\mathcal{K}},\boldsymbol{y})
-		% 	 & \triangleq \rho I_{\mathrm{P}}(x_{\mathcal{K}};\boldsymbol{y}) + (1 - \rho) I_{\mathrm{B}}(x_{\mathcal{K}};\hat{x}_{\mathcal{K}}),\label{eq:weighted_sum_mutual_information}
-		% \end{align}
-		% where $\rho \in [0,1]$ represents the priority of the primary link.
 	\end{subsection}
@@
 
-\begin{section}{Input Distribution, Active Beamforming, and Decision Threshold Design}
-	To characterize the achievable primary-total-backscatter rate region of the proposed UniScatter network, we aim to maximize the weighted sum mutual information with respect to node input distributions $\{\boldsymbol{p}_k\}_{k \in \mathcal{K}}$, active beamforming vector $\boldsymbol{w}$, and decision threshold vector $\boldsymbol{t}$ as
+\begin{section}{Rate-Region Characterization}
+	To characterize the achievable primary-total-backscatter rate region of the proposed UniScatter system, we aim to maximize the weighted sum mutual information with respect to input distribution $\{\boldsymbol{p}_k\}_{k \in \mathcal{K}}$, active beamforming $\boldsymbol{w}$, and decision thresholds $\boldsymbol{t}$ as
 	\begin{maxi!}
-		{\scriptstyle{\{\boldsymbol{p}_k\}_{k \in \mathcal{K}},\boldsymbol{w},\boldsymbol{t}\in\mathbb{R}_+^{L+1}}}{I(x_{\mathcal{K}})}{\label{op:weighted_sum_rate}}{\label{ob:weighted_sum_rate}}
-		% \addConstraint{\sum \nolimits_{m_k} P_k(x_{m_k})}{=1,}{\quad \forall k \in \mathcal{K}}{\label{co:sum_probability}}
-		\addConstraint{\sum \nolimits_{m_k} P_k(x_{m_k})}{=1,}{\quad \forall k}{\label{co:sum_probability}}
-		% \addConstraint{P_k(x_{m_k})}{\ge 0,}{\quad \forall k \in \mathcal{K}, \ \forall m_k \in \mathcal{M}}{\label{co:nonnegative_probability}}
-		\addConstraint{P_k(x_{m_k})}{\ge 0,}{\quad \forall k,m_k}{\label{co:nonnegative_probability}}
+		{\scriptstyle{\{\boldsymbol{p}_k\}_{k \in \mathcal{K}},\boldsymbol{w},\boldsymbol{t}}}{I(x_{\mathcal{K}})}{\label{op:weighted_sum_rate}}{\label{ob:weighted_sum_rate}}
+		\addConstraint{\boldsymbol{1}^T \boldsymbol{p}_k}{=1,}{\quad \forall k}{\label{co:sum_probability}}
+		\addConstraint{\boldsymbol{p}_k}{\ge \boldsymbol{0},}{\quad \forall k}{\label{co:nonnegative_probability}}
 		\addConstraint{\lVert \boldsymbol{w} \rVert^2}{\le P}{\label{co:transmit_power}}
@@
 	\end{maxi!}
-	% \begin{maxi!}
-	% 	{\scriptstyle{\{\boldsymbol{p}_k\}_{k \in \mathcal{K}},\boldsymbol{t},\boldsymbol{w}}}{I(x_{\mathcal{K}})}{\label{op:weighted_sum_rate}}{\label{ob:weighted_sum_rate}}
-	% 	\addConstraint{\boldsymbol{p}_k}{\in \Delta^{M-1},}{\quad \forall k \in \mathcal{K}}{\label{co:sum_probability}}
-	% 	% \addConstraint{P_k(x_{m_k})}{\ge 0,}{\quad \forall k \in \mathcal{K}, \ \forall m_k \in \mathcal{M}}{\label{co:nonnegative_probability}}
-	% 	\addConstraint{\lVert \boldsymbol{w} \rVert^2}{\le P.}{\label{co:transmit_power}}
-	% \end{maxi!}
-	% \begin{maxi!}
-	% 	{\scriptstyle{\boldsymbol{p}_k \in \Delta^{M-1},\boldsymbol{t},\boldsymbol{w}}}{I(x_{\mathcal{K}})}{\label{op:weighted_sum_rate}}{\label{ob:weighted_sum_rate}}
-	% 	% \addConstraint{\boldsymbol{p}_k}{\in \Delta^{M-1},}{\quad \forall k \in \mathcal{K}}{\label{co:sum_probability}}
-	% 	% \addConstraint{P_k(x_{m_k})}{\ge 0,}{\quad \forall k \in \mathcal{K}, \ \forall m_k \in \mathcal{M}}{\label{co:nonnegative_probability}}
-	% 	\addConstraint{\lVert \boldsymbol{w} \rVert^2}{\le P.}{\label{co:transmit_power}}
-	% \end{maxi!}
-	Problem \eqref{op:weighted_sum_rate} is highly non-convex, and we propose a \gls{bcd} algorithm that iteratively updates $\{\boldsymbol{p}_k\}_{k \in \mathcal{K}}$, $\boldsymbol{w}$ and $\boldsymbol{t}$ until convergence.
+	Since problem \eqref{op:weighted_sum_rate} is highly non-convex, we propose a \gls{bcd} algorithm that iteratively updates $\{\boldsymbol{p}_k\}_{k \in \mathcal{K}}$, $\boldsymbol{w}$ and $\boldsymbol{t}$ until convergence.
 
 	\begin{subsection}{Input Distribution}
-		% For any fixed decision boundary $\boldsymbol{t}$ and transmit precoder $\boldsymbol{w}$, the equivalent \gls{dmtmac} can be formulated by \eqref{eq:dmtmac} and problem \eqref{op:weighted_sum_rate} boils down to
 		For any given $\boldsymbol{w}$ and $\boldsymbol{t}$, we can construct the equivalent \gls{dmtmac} by \eqref{eq:dmtmac} and simplify \eqref{op:weighted_sum_rate} to
@@
 		\end{maxi!}
-		which involves coupled term $\prod_{k \in \mathcal{K}} P_k(x_{m_k})$ and is non-convex when $K > 1$.
-Next, we propose a numerical method that evaluate the \gls{kkt} input distribution by limit of sequences.
+		which involves the coupled term $\prod_{k \in \mathcal{K}} P_k(x_{m_k})$ and is non-convex when $K > 1$.
+		Following \cite{Rezaeian2004}, we first recast \gls{kkt} conditions of problem \eqref{op:input_distribution} to their equivalent forms, then propose a numerical method that guarantees those conditions on convergence of sequences.
+		% ? Next, we propose a numerical method that evaluate the \gls{kkt} input distribution by limit of sequences.
 		\begin{remark}
-			% As pointed out in \cite{Buhler2011}, \gls{kkt} conditions are only necessary for such kind of problems and these solutions may end up being saddle points.
-			As pointed out in \cite{Buhler2011}, \gls{kkt} conditions are generally necessary but insufficient for total rate maximization in discrete memoryless \gls{mac}.
-Therefore, \gls{kkt} solutions may end up being saddle points of problem \eqref{op:input_distribution}.
+			As demonstrated in \cite{Buhler2011}, \gls{kkt} conditions are generally necessary but insufficient for total rate maximization problems.
+			Although \gls{kkt} solutions to problem \eqref{op:input_distribution} may end up being saddle points, we will later show by simulation their average performance can be reasonably close to optimal for a moderate $K$.
 		\end{remark}
-		Following \cite{Rezaeian2004}, we first recast \gls{kkt} conditions to their equivalent form for problem \eqref{op:input_distribution}, then propose an iterative method that guarantees input distribution satisfying above conditions on convergence.
-		% Interestingly, the total-rate optimal input design for general discrete memoryless \gls{mac} remains an open problem, and we instead propose a \gls{kkt} solution to problem \eqref{op:input_distribution}.
 		\begin{proposition}
-			% The \gls{kkt} optimality conditions for problem \eqref{op:input_distribution} are equivalent to, $\forall k \in \mathcal{K}$ and $\forall m_k \in \mathcal{M}$,
 			The \gls{kkt} optimality conditions for problem \eqref{op:input_distribution} are equivalent to, $\forall k,m_k$,
@@
 
-		For each node, \eqref{eq:probable_states} suggests each probable state should produce the same marginal information (averaged over all states of other nodes), while \eqref{eq:dropped_states} implies any state with potentially less marginal information should not be used.
-		% We notice \eqref{eq:probable_states} means each probable state of each tag should produce the same marginal information (averaged over all states of other tags), while \eqref{eq:dropped_states} implies any state of any tag with potentially less marginal information than above should not be used.
-		% Next, we generalize the Blahut-Arimoto algorithm \cite{Arimoto1972,Blahut1972a} and propose a numerical evaluation of \gls{kkt} points by limits of sequences.
+		For each node, \eqref{eq:probable_states} suggests each probable state should produce the same marginal information (averaged over all states of other nodes), while \eqref{eq:dropped_states} suggests any state with potentially less marginal information should not be used.
 		\begin{proposition}
-			% The \gls{kkt} solution of input probability of tag $k$ at state $m_k$ is given by the converging point of the sequence
-			The \gls{kkt} input probability of node $k$ of state $m_k$ is given by the converging point of the sequence
-			% The \gls{kkt} solution of input probability of tag $k$ at state $m_k$ is given by the converging point of the sequence
+			For any strictly positive initializer $\{\boldsymbol{p}_k^{(0)}\}_{k \in \mathcal{K}}$, the \gls{kkt} input probability of node $k$ at state $m_k$ is given by the converging point of the sequence
 			\begin{equation}
@@
 			\end{equation}
-			% where $r$ is the iteration index and $\boldsymbol{p}_k^{(0)} > \boldsymbol{0}$, $\forall k \in \mathcal{K}$.
-			where $r$ is the iteration index and $\boldsymbol{p}_k^{(0)} > \boldsymbol{0}$, $\forall k$.
+			where $r$ is the iteration index.
 			\label{pr:input_kkt_solution}
@@
 
-		At each iteration, the input distribution of node $k$ is evaluated over updated input distribution of node $1$ to $k-1$, together with previous input distribution of node $k+1$ to $K$.
+		For \eqref{eq:input_kkt_solution} at iteration $r+1$, the input distribution of node $k$ is updated over $\bigl\{\{\boldsymbol{p}_q^{(r+1)}\}_{q=1}^{k-1},\{\boldsymbol{p}_q^{(r)}\}_{q=k}^{K}\bigr\}$.
 		The \gls{kkt} input distribution design is summarized in Algorithm \ref{al:input_distribution}.
@@
 		\begin{algorithm}[!t]
-			\caption{Numerical Evaluation of \gls{kkt} Input Distribution}
+			\caption{Numerical \gls{kkt} Input Distribution Evaluation by Limits of Sequence}
 			\label{al:input_distribution}
@@
 					\State Redo step \ref{st:input_distribution_begin}--\ref{st:input_distribution_end}
-					% \State Get $P_{\mathcal{K}}^{(r)}(x_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}$ by \eqref{eq:equivalent_distribution}
-					% \State \phantom{Get} $I^{(r)}(x_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}$ by \eqref{eq:backscatter_information_function}, \eqref{eq:primary_information_function}, \eqref{eq:weighted_sum_information_function}
-					% \State \phantom{Get} $I^{(r)}_k(x_{m_k})$, $\forall k,m_k$ by \eqref{eq:backscatter_marginal_information}, \eqref{eq:primary_marginal_information}, \eqref{eq:weighted_sum_marginal_information}
-					% \State \phantom{Get} $I^{(r)}(x_{\mathcal{K}})$ by \eqref{eq:backscatter_mutual_information}, \eqref{eq:primary_mutual_information}, \eqref{eq:weighted_sum_mutual_information}
 				\Until $I^{(r)}(x_{\mathcal{K}}) - I^{(r-1)}(x_{\mathcal{K}}) \le \epsilon$
@@
 		\end{maxi!}
-		which is still non-convex due to integration and entropy terms.
+		which is still non-convex due to the integration and entropy terms.
+		To tackle this, we rewrite the \gls{dmtmac} transition probability \eqref{eq:dmtmac} from input index tuple $m_{\mathcal{K}}$ to output index $l$ as a regularized incomplete Gamma function in the series representation \cite[Theorem~3]{Jameson2016}
+		\begin{equation}
+			\begin{gathered}
+				Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr) = \frac{\int_{{t_{l-1}}/{\sigma_{m_{\mathcal{K}}}^2}}^{{t_l}/{\sigma_{m_{\mathcal{K}}}^2}} z^{N-1} \exp(-z) \, d z}{(N-1)!}\\
+				= \exp \Bigl(-\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2}\Bigr) \sum_{n=0}^{N-1} \frac{\bigl(\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2}\bigr)^n}{n!} - \exp \Bigl(-\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr) \sum_{n=0}^{N-1} \frac{\bigl(\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\bigr)^n}{n!}.
+			\end{gathered}
+			\label{eq:regularized_incomplete_gamma}
+		\end{equation}
+		Its gradient with respect to $\boldsymbol{w}^*$ can be derived as
+		\begin{equation}
+			\nabla_{\boldsymbol{w}^*} Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr) = \frac{\boldsymbol{h}_{\mathrm{E}}(x_{m_{\mathcal{K}}})\boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}})\boldsymbol{w}}{(\sigma_{m_{\mathcal{K}}}^2)^2} g_{m_{\mathcal{K}}}(t_{l-1},t_l),
+			\label{eq:regularized_incomplete_gamma_gradient}
+		\end{equation}
+		where $g_{m_{\mathcal{K}}}(t_{l-1},t_l) \triangleq g_{m_{\mathcal{K}}}(t_l)-g_{m_{\mathcal{K}}}(t_{l-1})$ and
+		\begin{equation}
+			g_{m_{\mathcal{K}}}(t_l) = t_l\exp\Bigl(-\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr)\Bigl(-1+\sum_{n=1}^{N-1} \frac{\bigl(n - \frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\bigr) \bigl(\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\bigr)^{n-1}}{n!}\Bigr).
+			\label{eq:regularized_incomplete_gamma_gradient_component}
+		\end{equation}
+		On top of \eqref{eq:regularized_incomplete_gamma} and \eqref{eq:regularized_incomplete_gamma_gradient}, we explicitly express the objective function \eqref{ob:active_beamforming} and its gradient as \eqref{eq:weighted_sum_mutual_information_explicit} and \eqref{eq:weighted_sum_mutual_information_gradient} at the end of page \pageref{eq:weighted_sum_mutual_information_explicit}, respectively.
 		\begin{figure*}[!b]
@@
 			\end{equation}
-		\end{figure*}
-		To see this, we explicitly write \eqref{ob:active_beamforming} as \eqref{eq:weighted_sum_mutual_information_explicit} at the bottom of page \pageref{eq:regularized_incomplete_gamma}, where
-		\begin{equation}
-			Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr) = \frac{\int_{{t_{l-1}}/{\sigma_{m_{\mathcal{K}}}^2}}^{{t_l}/{\sigma_{m_{\mathcal{K}}}^2}} z^{N-1} \exp(-z) \, d z}{(N-1)!}
-			\label{eq:regularized_incomplete_gamma}
-		\end{equation}
-		is the regularized incomplete Gamma function that substitutes the \gls{dmtmac} transition probability \eqref{eq:dmtmac}.
-		Its series representation is given by \cite[Theorem~3]{Jameson2016}
-		\begin{align}
-			Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr)
-			 & = \exp \Bigl(-\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2}\Bigr) \sum_{n=0}^{N-1} \frac{\Bigl(\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2}\Bigr)^n}{n!} \nonumber \\
-			 & \quad - \exp \Bigl(-\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr) \sum_{n=0}^{N-1} \frac{\Bigl(\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr)^n}{n!}.
-			\label{eq:regularized_incomplete_gamma_series}
-		\end{align}
-		Next, we derive the gradients of \eqref{eq:regularized_incomplete_gamma_series} and \eqref{eq:weighted_sum_mutual_information_explicit} w.r.t.
-$\boldsymbol{w}^*$ as \eqref{eq:regularized_incomplete_gamma_gradient} and \eqref{eq:weighted_sum_mutual_information_gradient} at the end of page \pageref{eq:regularized_incomplete_gamma_gradient} and \pageref{eq:weighted_sum_mutual_information_gradient}, respectively.
-		\begin{figure*}[!b]
-			\begin{align}
-				\nabla_{\boldsymbol{w}^*} Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr)
-				 & = \frac{\boldsymbol{h}_{\mathrm{E}}(x_{m_{\mathcal{K}}})\boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}})\boldsymbol{w}}{\bigl(\lvert\boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}})\boldsymbol{w}\rvert^2+\sigma_v^2\bigr)^2}\nonumber                                                                                                                                                                                                        \\
-				 & \quad \times \Biggl(t_l\exp\Bigl(-\frac{t_l}{\lvert\boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}})\boldsymbol{w}\rvert^2+\sigma_v^2}\Bigr)\biggl(-1+\sum_{n=1}^{N-1} \frac{n\Bigl(\frac{t_l}{\lvert\boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}})\boldsymbol{w}\rvert^2+\sigma_v^2}\Bigr)^{n-1}-\Bigl(\frac{t_l}{\lvert\boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}})\boldsymbol{w}\rvert^2+\sigma_v^2}\Bigr)^n}{n!}\biggr)\nonumber    \\
-				 & \qquad - t_{l-1}\exp\Bigl(-\frac{t_{l-1}}{\lvert\boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}})\boldsymbol{w}\rvert^2+\sigma_v^2}\Bigr)\biggl(-1+\sum_{n=1}^{N-1} \frac{n\Bigl(\frac{t_{l-1}}{\lvert\boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}})\boldsymbol{w}\rvert^2+\sigma_v^2}\Bigr)^{n-1}-\Bigl(\frac{t_{l-1}}{\lvert\boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}})\boldsymbol{w}\rvert^2+\sigma_v^2}\Bigr)^n}{n!}\biggr)\Biggr)
-				\label{eq:regularized_incomplete_gamma_gradient}
-			\end{align}
-		\end{figure*}
-		\begin{figure*}[!b]
-			\hrule
 			\begin{align}
 				\nabla_{\boldsymbol{w}^*} I(x_{\mathcal{K}})
-				 & = \sum_{m_{\mathcal{K}}}P_{\mathcal{K}}(x_{m_{\mathcal{K}}})\Biggl(\rho\frac{\boldsymbol{h}_{\mathrm{E}}(x_{m_{\mathcal{K}}})\boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}})\boldsymbol{w}}{\lvert\boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}})\boldsymbol{w}\rvert^2+\sigma_v^2}+(1-\rho)\sum_l\biggl(\log\frac{Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr)}{\sum_{m_{\mathcal{K}}'}P_{\mathcal{K}}(x_{m_{\mathcal{K}}'})Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}'}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}'}^2}\Bigr)}+1\biggr)\nonumber   \\
+				 & = \sum_{m_{\mathcal{K}}}P_{\mathcal{K}}(x_{m_{\mathcal{K}}})\Biggl(\rho\frac{\boldsymbol{h}_{\mathrm{E}}(x_{m_{\mathcal{K}}})\boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}})\boldsymbol{w}}{\sigma_{m_{\mathcal{K}}}^2}+(1-\rho)\sum_l\biggl(\log\frac{Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr)}{\sum_{m_{\mathcal{K}}'}P_{\mathcal{K}}(x_{m_{\mathcal{K}}'})Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}'}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}'}^2}\Bigr)}+1\biggr)\nonumber                                                                  \\
 				 & \qquad \times \nabla_{\boldsymbol{w}^*} Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr)-\frac{Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr)\sum_{m_{\mathcal{K}}'}P_{\mathcal{K}}(x_{m_{\mathcal{K}}'})\nabla_{\boldsymbol{w}^*}Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}'}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}'}^2}\Bigr)}{\sum_{m_{\mathcal{K}}'}P_{\mathcal{K}}(x_{m_{\mathcal{K}}'})Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}'}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}'}^2}\Bigr)}\Biggr)
@@
 		\end{figure*}
-		% Next, we express the gradient of \eqref{eq:regularized_incomplete_gamma_series} and \eqref{eq:weighted_sum_mutual_information_explicit} w.r.t.
-$\boldsymbol{w}^*$ as \eqref{eq:regularized_incomplete_gamma_gradient} and \eqref{eq:weighted_sum_mutual_information_gradient} at the end of page \pageref{eq:regularized_incomplete_gamma_gradient},
-		It allows problem \eqref{op:active_beamforming} to be solved by the \gls{pgd} method, where any unregulated beamforming vector $\bar{\boldsymbol{w}}$ can be projected onto the feasible domain of average transmit power constraint \eqref{co:transmit_power} by
-		% the projection function associated with average transmit power constraint \eqref{co:transmit_power} is
+		Those allows problem \eqref{op:active_beamforming} to be solved by the \gls{pgd} method, where any unregulated beamforming vector $\bar{\boldsymbol{w}}$ can be projected onto the feasible domain of average transmit power constraint \eqref{co:transmit_power} by
 		\begin{equation}
@@
 		\end{equation}
-		We present the iterative active beamforming design accelerated by backtracking line search in Algorithm \ref{al:active_beamforming}.
+
+		The \gls{pgd} active beamforming optimization with step size determined by backtracking line search is summarized in Algorithm \ref{al:active_beamforming}.
 		\begin{algorithm}[!t]
-			\caption{Iterative Active Beamforming Design by \gls{pgd} with Backtracking Line Search}
+			\caption{Iterative Active Beamforming Optimization by \gls{pgd} with Backtracking Line Search}
 			\label{al:active_beamforming}
@@
 				\State Get $(\sigma_{m_{\mathcal{K}}}^{(r)})^2$, $\forall m_{\mathcal{K}}$ by \eqref{eq:receive_variance} \label{st:gradient_descent_begin}
-				\State \phantom{Get} $Q^{(r)}\bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\bigr)$, $\forall m_{\mathcal{K}},l$ by \eqref{eq:regularized_incomplete_gamma} or \eqref{eq:regularized_incomplete_gamma_series}
+				\State \phantom{Get} $Q^{(r)}\bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\bigr)$, $\forall m_{\mathcal{K}},l$ by \eqref{eq:regularized_incomplete_gamma}
 				\State \phantom{Get} $I^{(r)}(x_{\mathcal{K}})$ by \eqref{eq:weighted_sum_mutual_information_explicit} \label{st:gradient_descent_end}
@@
 					\State Redo step \ref{st:gradient_descent_begin}--\ref{st:gradient_descent_end} \label{st:backtracking_line_search_end}
-					% \State \phantom{Update} $(\sigma_{m_{\mathcal{K}}}^{(r)})^2$, $\forall m_{\mathcal{K}}$ by \eqref{eq:receive_variance}
-					% \State \phantom{Update} $Q^{(r)}\bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\bigr)$, $\forall m_{\mathcal{K}},l$ by \eqref{eq:regularized_incomplete_gamma} or \eqref{eq:regularized_incomplete_gamma_series}
-					% \State \phantom{Update} $I^{(r)}(x_{\mathcal{K}})$ by \eqref{eq:weighted_sum_mutual_information_explicit} \label{st:backtracking_line_search_end}
-					% \While{$I^{(r-1)}(x_{\mathcal{K}})>I^{(r)}(x_{\mathcal{K}})+\alpha\gamma\lVert\nabla_{\boldsymbol{w}^*}I^{(r-1)}(x_{\mathcal{K}})\rVert$}
 					\While{$I^{(r)}(x_{\mathcal{K}})<I^{(r-1)}(x_{\mathcal{K}})+\alpha\gamma\lVert\nabla_{\boldsymbol{w}^*}I^{(r-1)}(x_{\mathcal{K}})\rVert^2$}
@@
 	\begin{subsection}{Decision Threshold}
-		% Once node input distribution $\{\boldsymbol{p}_k\}_{k \in \mathcal{K}}$ and active beamforming vector $\boldsymbol{w}$ are obtained, problem \eqref{op:weighted_sum_rate}
 		For any given $\{\boldsymbol{p}_k\}_{k \in \mathcal{K}}$ and $\boldsymbol{w}$, problem \eqref{op:weighted_sum_rate} reduces to
 		\begin{maxi!}
-			{\scriptstyle{\boldsymbol{t}\in\mathbb{R}_+^{L+1}}}{I(x_{\mathcal{K}})}{\label{op:decision_threshold}}{\label{ob:decision_threshold}}
+			{\scriptstyle{\boldsymbol{t}}}{I(x_{\mathcal{K}})}{\label{op:decision_threshold}}{\label{ob:decision_threshold}}
 			\addConstraint{\eqref{co:decision_threshold},}
 		\end{maxi!}
-		where it is trivial to conclude $t_0^\star=0$ and $t_L^\star=\infty$ for energy-based backscatter detection.
+		and it is trivial to conclude $t_0^\star=0$ and $t_L^\star=\infty$ for energy-based backscatter detection.
 
@@
 		The Lagrangian function of problem \eqref{op:input_distribution} is
-		\begin{align}
-			% L(\{\boldsymbol{p}_k\}_{k \in \mathcal{K}},\{\nu_k\},\{\lambda_{k,m_k}\})
-			L
-			%  & = - I(x_{\mathcal{K}}) + \sum_{k \in \mathcal{K}} \nu_k \left( \sum_{m_k \in \mathcal{M}} P_k(x_{m_k}) - 1 \right)\nonumber \\
-			 & = - I(x_{\mathcal{K}}) + \sum_k \nu_k \left( \sum_{m_k \in \mathcal{M}} P_k(x_{m_k}) - 1 \right)\nonumber \\
-			%  & \quad - \sum_{k \in \mathcal{K}} \sum_{m_k \in \mathcal{M}} \lambda_{k,m_k} P_k(x_{m_k}),
-			 & \quad - \sum_k \sum_{m_k} \lambda_{k,m_k} P_k(x_{m_k}),
-		\end{align}
-		% and the \gls{kkt} conditions on the optimal primal and dual variables are, $\forall m_k \in \mathcal{M}$ and $\forall k \in \mathcal{K}$,
-		% and the \gls{kkt} conditions are, $\forall m_k \in \mathcal{M}$ and $\forall k \in \mathcal{K}$,
+		\begin{equation}
+			- I(x_{\mathcal{K}}) + \sum_k \nu_k \biggl( \sum_{m_k} P_k(x_{m_k}) - 1 \biggr) - \sum_k \sum_{m_k} \lambda_{k,m_k} P_k(x_{m_k})
+		\end{equation}
 		and the \gls{kkt} conditions are, $\forall k,m_k$,
@@
 			\begin{equation}
-				\lambda_{k,m_k}^\star \ge 0, \quad P_k^\star(x_{m_k}) = 0.
+				\lambda_{k,m_k}^\star \ge 0, \quad P_k^\star(x_{m_k}) = 0,
 			\end{equation}
 		\end{subequations}
-		The directional derivative can be explicitly expressed as
+		where directional derivative is explicitly written as
 		\begin{equation}
@@
 		\end{subequations}
-		which suggests
+		such that
 		\begin{equation}
@@
 		\end{equation}
-		On the other hand, by definition of weighted sum marginal information \eqref{eq:weighted_sum_marginal_information},
+		On the other hand, by definition \eqref{eq:weighted_sum_marginal_information} we have
 		\begin{equation}
@@
 		We first prove sequence \eqref{eq:input_kkt_solution} is non-decreasing in weighted sum mutual information.
-		Let $P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) = \prod_{q \in \mathcal{K}} P_q(x_{m_q})$ and $P_{\mathcal{K}}'(x_{m_{\mathcal{K}}}) = P_k'(x_{m_k}) \prod_{q \in \mathcal{K} \setminus \{k\}} P_q(x_{m_q})$ be two probability distributions with potentially different marginal for tag $k \in \mathcal{K}$ at state $m_k \in \mathcal{M}$, and define an intermediate function $J \left( P_{\mathcal{K}}(x_{m_{\mathcal{K}}}),P_{\mathcal{K}}'(x_{m_{\mathcal{K}}}) \right)$ as \eqref{eq:intermediate_information_function} at the end of page \pageref{eq:intermediate_information_function}.
+		Let $P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) = \prod_{q \in \mathcal{K}} P_q(x_{m_q})$ and $P_{\mathcal{K}}'(x_{m_{\mathcal{K}}}) = P_k'(x_{m_k}) \prod_{q \in \mathcal{K} \setminus \{k\}} P_q(x_{m_q})$ be two probability distributions with potentially different marginal for tag $k$ at state $m_k$, and define an intermediate function $J \bigl( P_{\mathcal{K}}(x_{m_{\mathcal{K}}}),P_{\mathcal{K}}'(x_{m_{\mathcal{K}}}) \bigr)$ as \eqref{eq:intermediate_information_function} at the end of page \pageref{eq:intermediate_information_function}.
 		\begin{figure*}[!b]
 			\hrule
-			% \begin{equation}
-			% 	J \left( P_{\mathcal{K}}(x_{m_{\mathcal{K}}}),P_{\mathcal{K}}'(x_{m_{\mathcal{K}}}) \right) \triangleq \rho \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) \log \left(1 + \frac{\lvert \boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_v^2}\right) + (1 - \rho) \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) \sum_{m_{\mathcal{K}}'} P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}}) \log \frac{P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}}) P_{\mathcal{K}}'(x_{m_{\mathcal{K}}})}{P'(\hat{x}_{m_{\mathcal{K}}'}) P_{\mathcal{K}}(x_{m_{\mathcal{K}}})}.
-			% 	\label{eq:intermediate_information_function}
-			% \end{equation}
-			\begin{align}
-				J \left( P_{\mathcal{K}}(x_{m_{\mathcal{K}}}),P_{\mathcal{K}}'(x_{m_{\mathcal{K}}}) \right)
-				 & \triangleq \rho \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) \log \left(1 + \frac{\lvert \boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_v^2}\right)\nonumber                                                                                                                    \\
-				 & \quad + (1 - \rho) \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) \sum_{m_{\mathcal{K}}'} P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}}) \log \frac{P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}}) P_{\mathcal{K}}'(x_{m_{\mathcal{K}}})}{P'(\hat{x}_{m_{\mathcal{K}}'}) P_{\mathcal{K}}(x_{m_{\mathcal{K}}})}.
+			\begin{equation}
+				J \bigl( P_{\mathcal{K}}(x_{m_{\mathcal{K}}}),P_{\mathcal{K}}'(x_{m_{\mathcal{K}}}) \bigr) \triangleq \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}})
+				\Biggl( \rho \log \Bigl(1 + \frac{\lvert \boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_v^2}\Bigr) + (1 - \rho) \sum_{m_{\mathcal{K}}'} P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}}) \log \frac{P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}}) P_{\mathcal{K}}'(x_{m_{\mathcal{K}}})}{P_{\mathcal{K}}'(\hat{x}_{m_{\mathcal{K}}'}) P_{\mathcal{K}}(x_{m_{\mathcal{K}}})} \Biggr).
 				\label{eq:intermediate_information_function}
-			\end{align}
+			\end{equation}
 		\end{figure*}
-		It is straightforward to verify $J \left( P_{\mathcal{K}}(x_{m_{\mathcal{K}}}),P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) \right) = I(x_{\mathcal{K}})$ and $J \left( P_{\mathcal{K}}(x_{m_{\mathcal{K}}}),P_{\mathcal{K}}'(x_{m_{\mathcal{K}}}) \right)$ is a concave function for a fixed $P_{\mathcal{K}}'(x_{m_{\mathcal{K}}})$.
-		By choosing $\nabla_{P_k^\star(x_{m_k})} J \left( P_{\mathcal{K}}(x_{m_{\mathcal{K}}}),P_{\mathcal{K}}'(x_{m_{\mathcal{K}}}) \right) = 0$, we have
+		It is straightforward to verify $J \bigl( P_{\mathcal{K}}(x_{m_{\mathcal{K}}}),P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) \bigr) = I(x_{\mathcal{K}})$ and $J \bigl( P_{\mathcal{K}}(x_{m_{\mathcal{K}}}),P_{\mathcal{K}}'(x_{m_{\mathcal{K}}}) \bigr)$ is a concave function for a fixed $P_{\mathcal{K}}'(x_{m_{\mathcal{K}}})$.
+		Setting $\nabla_{P_k^\star(x_{m_k})} J \bigl( P_{\mathcal{K}}(x_{m_{\mathcal{K}}}),P_{\mathcal{K}}'(x_{m_{\mathcal{K}}}) \bigr) = 0$, we have
 		\begin{equation}
@@
 		\begin{equation}
-			P_k^\star(x_{m_k}) = \frac{P_k'(x_{m_k}) \exp \left( \frac{\rho}{1 - \rho} I_k'(x_{m_k}) \right)}{\sum_{m_k'} P_k'(x_{m_k'}) \exp \left( \frac{\rho}{1 - \rho} I_k'(x_{m_k'}) \right)}.
+			P_k^\star(x_{m_k}) = \frac{P_k'(x_{m_k}) \exp \Bigl( \frac{\rho}{1 - \rho} I_k'(x_{m_k}) \Bigr)}{\sum_{m_k'} P_k'(x_{m_k'}) \exp \Bigl( \frac{\rho}{1 - \rho} I_k'(x_{m_k'}) \Bigr)}.
 			\label{eq:optimal_relative_distribution}
 		\end{equation}
-		We also notice $P_k(x_{i_k}) = 1 - \sum_{m_k \ne i_k} P_k^\star(x_{m_k})$ has exactly the same expression as \eqref{eq:optimal_relative_distribution}.
-		% We also notice $P_k(x_{i_k}) = 1 - \sum_{m_k \ne i_k} P_k^\star(x_{m_k})$ is in the same expression as \eqref{eq:optimal_relative_distribution}.
-		Therefore, the result is irrelevant to the choice of reference state, and \eqref{eq:optimal_relative_distribution} is indeed optimal $\forall m_k \in \mathcal{M}$.
-		% It implies the selection of reference state does not matter and \eqref{eq:optimal_relative_distribution} is indeed optimal $\forall m_k \in \mathcal{M}$.
+		Since $P_k(x_{i_k}) = 1 - \sum_{m_k \ne i_k} P_k^\star(x_{m_k})$ has exactly the same form as \eqref{eq:optimal_relative_distribution}, the choice of reference state $i_k$ does not matter and \eqref{eq:optimal_relative_distribution} is indeed optimal $\forall m_k \in \mathcal{M}$.
 		That is, for a fixed $P_{\mathcal{K}}'(x_{m_{\mathcal{K}}})$, choosing $P_k(x_{m_k})$ by \eqref{eq:optimal_relative_distribution} ensures
 		\begin{equation}
-			J \left( P_{\mathcal{K}}(x_{m_{\mathcal{K}}}),P_{\mathcal{K}}'(x_{m_{\mathcal{K}}}) \right) \ge I'(x_{\mathcal{K}}).
+			J \bigl( P_{\mathcal{K}}(x_{m_{\mathcal{K}}}),P_{\mathcal{K}}'(x_{m_{\mathcal{K}}}) \bigr) \ge I'(x_{\mathcal{K}}).
 			\label{eq:information_difference_lower}
 		\end{equation}
-		On the other hand, it also guarantees
+		On the other hand, we also have
 		\begin{subequations}
@@
 				\Delta
-				 & \triangleq I(x_{\mathcal{K}}) - J \left( P_{\mathcal{K}}(x_{m_{\mathcal{K}}}),P_{\mathcal{K}}'(x_{m_{\mathcal{K}}}) \right)                                                                                \\
+				 & \triangleq I(x_{\mathcal{K}}) - J \bigl( P_{\mathcal{K}}(x_{m_{\mathcal{K}}}),P_{\mathcal{K}}'(x_{m_{\mathcal{K}}}) \bigr)                                                                                  \\
 				 & = (1 - \rho) \sum_{m_k} \frac{P_k'(x_{m_k}) f_k'(x_{m_k})}{\sum_{m_k'} P_k'(x_{m_k'}) f_k'(x_{m_k'})} \sum_{m_{\mathcal{K}}''} P(\hat{x}_{m_{\mathcal{K}}''}|x_{m_k})\nonumber                              \\
@@
 				 & \ge (1 - \rho) \sum_{m_k} \frac{P_k'(x_{m_k}) f_k'(x_{m_k})}{\sum_{m_k'} P_k'(x_{m_k'}) f_k'(x_{m_k'})} \sum_{m_{\mathcal{K}}''} P(\hat{x}_{m_{\mathcal{K}}''}|x_{m_k})\nonumber                            \\
-				 & \quad \times \left( 1 - \frac{\sum_{m_k'} P_k'(x_{m_k'}) P(\hat{x}_{m_{\mathcal{K}}''}|x_{m_k'}) f_k'(x_{m_k'})}{\sum_{m_k'} P_k'(x_{m_k'}) P(\hat{x}_{m_{\mathcal{K}}''}|x_{m_k'}) f_k'(x_{m_k})} \right) \\
+				 & \quad \times \Biggl( 1 - \frac{\sum_{m_k'} P_k'(x_{m_k'}) P(\hat{x}_{m_{\mathcal{K}}''}|x_{m_k'}) f_k'(x_{m_k'})}{\sum_{m_k'} P_k'(x_{m_k'}) P(\hat{x}_{m_{\mathcal{K}}''}|x_{m_k'}) f_k'(x_{m_k})} \Biggr) \\
 				 & = 0,
@@
 		\end{subequations}
-		where $f_k'(x_{m_k}) \triangleq \exp \left( \frac{\rho}{1 - \rho} I_k'(x_{m_k}) \right)$ and the equality holds if and only if \eqref{eq:optimal_relative_distribution} converges.
+		where $f_k'(x_{m_k}) \triangleq \exp \bigl( \frac{\rho}{1 - \rho} I_k'(x_{m_k}) \bigr)$ and the equality holds if and only if \eqref{eq:optimal_relative_distribution} converges.
 		\eqref{eq:information_difference_lower} and \eqref{eq:information_difference_upper} together imply $I(x_{\mathcal{K}}) \ge I'(x_{\mathcal{K}})$.
@@
 		Next, we prove any converging point of sequence \eqref{eq:input_kkt_solution}, denoted as $P_k^\star(x_{m_k})$, fulfills \gls{kkt} conditions \eqref{eq:input_kkt_condition}.
-		% Next, we prove that sequence \eqref{eq:input_kkt_solution} fulfills \gls{kkt} conditions \eqref{eq:input_kkt_condition} on convergence.
-		% To see this, recall $P_k^{(0)}(x_{m_k}) > 0$ and define
-		To see this, define
-		% To see this, we define
+		To see this, let
 		\begin{equation}
@@
 		which is reminiscent of \eqref{eq:probable_states_marginal} and \eqref{eq:probable_states}.
-		That is to say, given $P_k^{(0)}(x_{m_k}) > 0$, any converging point with $P_k^\star(x_{m_k}) > 0$ must satisfy \eqref{eq:probable_states}.
+		That is, given $P_k^{(0)}(x_{m_k}) > 0$, any converging point with $P_k^\star(x_{m_k}) > 0$ must satisfy \eqref{eq:probable_states}.
 		On the other hand, we assume $P_k^\star(x_{m_k})$ does not satisfy \eqref{eq:dropped_states}, such that for any state with $P_k^\star(x_{m_k}) = 0$,
-		% On the other hand, we show if $P_k^\star(x_{m_k})$ does not satisfy \eqref{eq:dropped_states}, then it is not a converging point of sequence \eqref{eq:input_kkt_solution}.
-By this assumption, for any state with $P_k^\star(x_{m_k}) = 0$,
 		\begin{equation}
@@
 		where the equality inherits from \eqref{eq:weighted_sum_mutual_information}.
-		Since exponential function is monotonically increasing, we have $f_k^\star(x_{m_k}) > \sum_{m_k'} P_k^\star(x_{m_k'}) f_k^\star(x_{m_k'})$ and $D_k^\star(x_{m_k}) > 1$.
+		Since the exponential function is monotonically increasing, we have $f_k^\star(x_{m_k}) > \sum_{m_k'} P_k^\star(x_{m_k'}) f_k^\star(x_{m_k'})$ and $D_k^\star(x_{m_k}) > 1$.
 		Considering $P_k^{(0)}(x_{m_k}) > 0$ and $P_k^\star(x_{m_k}) = 0$, it contradicts with
@@
 		\end{equation}
-		Therefore, given $P_k^{(0)}(x_{m_k}) > 0$, any converging point with $P_k^\star(x_{m_k}) = 0$ must satisfy \eqref{eq:dropped_states}.
-		This completes the proof.
+		That is, given $P_k^{(0)}(x_{m_k}) > 0$, any converging point with $P_k^\star(x_{m_k}) = 0$ must satisfy \eqref{eq:dropped_states}.
+		The proof is thus completed.
 		\label{ap:input_kkt_solution}

### 2022-08-20 main.tex
:pencil: Add challenges of decision threshold design

@@
 		\end{maxi!}
-		and it is trivial to conclude $t_0^\star=0$ and $t_L^\star=\infty$ for energy-based backscatter detection.
+		which is still non-convex because variable $\boldsymbol{t}$ appear on the limits of integration \eqref{eq:dmtmac}.
+		% % To tackle this, we 1) reveal backscatter decision design has no impact on primary decoding, 2) constrain the feasible domain of problem \eqref{op:decision_threshold} from continuous space $\mathbb{R}_+$ to finite candidate set (i.e., fine-grained discrete output energy levels) $\mathcal{T}$,
+		% To tackle this, we 1) reveal backscatter decision design has no impact on primary decoding, 2) constrain the feasible domain of problem \eqref{op:decision_threshold} from continuous space $\mathbb{R}_+$ to finite candidate set of fine-grained discrete output energy levels $\mathcal{T}$, 3) regard UniScatter nodes with given input distribution as an equivalent augmented source in terms of total backscatter rate, 4) reuse existing quantization schemes for \gls{dmc} to solve problem \eqref{op:decision_threshold}.
+		% % 3) indicate the equivalence between multi and single in terms of total backscatter rate
+		% % 3) regard all UniScatter nodes as an equivalent augmented source in terms of total backscatter rate
+		To tackle this, we first reveal backscatter decision design has no impact on primary decoding, then constrain the feasible domain of problem \eqref{op:decision_threshold} from continuous space $\mathbb{R}_+$ to finite candidate set (i.e., fine-grained discrete energy levels) $\mathcal{T}$.
+		We also point out distributed nodes with given input distribution is equivalent to an augmented source of symbol tuples in terms of total rate, and reuse existing rate-optimal quantization schemes for \gls{dmc} to solve problem \eqref{op:decision_threshold}.
 
@@
 		Remark \ref{re:backscatter_detection} suggests any $\boldsymbol{t}$ maximizes total backscatter mutual information $I_{\mathrm{B}}(x_{\mathcal{K}};\hat{x}_{\mathcal{K}})$ is also optimal for problem \eqref{op:decision_threshold}.
+
+		where $t_0^\star=0$ and $t_L^\star=\infty$ for energy-based backscatter detection.
 

### 2022-08-20 main.tex
:pencil: Update remarks for threshold design

--- 2022-08-17 main.tex
@@
 		\end{equation}
-		where $\alpha_k \in \mathbb{I}$ is the amplitude scattering ratio of UniScatter node $k$, $x_k \in \mathcal{X} \triangleq \{c_1,\ldots,c_M\}$ is the \emph{coded} backscatter symbol of node $k$, $\boldsymbol{\alpha} \triangleq [\alpha_1,\ldots,\alpha_K]^T \in \mathbb{I}^{K \times 1}$, $\boldsymbol{x} \triangleq [x_1,\ldots,x_K]^H \in \mathcal{X}^{K \times 1}$, and $\boldsymbol{H}_{\mathrm{C}} \triangleq [\boldsymbol{h}_{\mathrm{C},1},\ldots,\boldsymbol{h}_{\mathrm{C},K}]^H \in \mathbb{C}^{K \times Q}$.
+		where $\alpha_k \in \mathbb{I}$ is the amplitude scattering ratio of UniScatter node $k$, $x_k \in \mathcal{X} \triangleq \{c_1,\ldots,c_M\}$ is the \emph{coded} backscatter symbol of node $k$, $\boldsymbol{\alpha} \triangleq [\alpha_1,\ldots,\alpha_K]^T \in \mathbb{I}^{K}$, $\boldsymbol{x} \triangleq [x_1,\ldots,x_K]^H \in \mathcal{X}^{K}$, and $\boldsymbol{H}_{\mathrm{C}} \triangleq [\boldsymbol{h}_{\mathrm{C},1},\ldots,\boldsymbol{h}_{\mathrm{C},K}]^H \in \mathbb{C}^{K \times Q}$.
 The signal received by the user at primary block $n \in \mathcal{N} \triangleq \{1,\ldots,N\}$ is
@@
 		\end{equation}
-		where $s \sim \mathcal{CN}(0,1)$ is the primary symbol, $v \sim \mathcal{CN}(0,\sigma_v^2)$ is the \gls{awgn}, and $\boldsymbol{w} \in \mathbb{C}^{Q \times 1}$ is the active beamforming vector subject to average transmit power constraint $\lVert \boldsymbol{w} \rVert^2 \le P$.
+		where $s \sim \mathcal{CN}(0,1)$ is the primary symbol, $v \sim \mathcal{CN}(0,\sigma_v^2)$ is the \gls{awgn}, and $\boldsymbol{w} \in \mathbb{C}^{Q}$ is the active beamforming vector subject to average transmit power constraint $\lVert \boldsymbol{w} \rVert^2 \le P$.
 		Denote $m_k \in \mathcal{M} \triangleq \{1,\ldots,M\}$ as the reflection state index of node $k$, and $m_{\mathcal{K}} \triangleq (m_1,\ldots,m_K)$ as the state index tuple of all nodes.
@@
 		\end{equation}
-		Once the decision threshold vector $\boldsymbol{t} \triangleq [t_0,\ldots,t_L]^T \in \mathbb{R}_+^{(L+1) \times 1}$ is determined, we can formulate a \gls{dmtmac} with transition probability from input $x_{m_{\mathcal{K}}}$ to output $\hat{x}_{m_{\mathcal{K}}'}$
+		Once the decision threshold vector $\boldsymbol{t} \triangleq [t_0,\ldots,t_L]^T \in \mathbb{R}_+^{(L+1)}$ is determined, we can formulate a \gls{dmtmac} with transition probability from input $x_{m_{\mathcal{K}}}$ to output $\hat{x}_{m_{\mathcal{K}}'}$
 		\begin{equation}
@@
 	\begin{subsection}{Information Theory}
-		Denote the input probability distribution vector of node $k$ as $\boldsymbol{p}_k \triangleq [P_k(c_1),\ldots,P_k(c_M)]^T \in \mathbb{I}^{M \times 1}$, and the probability of state $m_k$ as $P_k(x_{m_k})$.
+		Denote the input probability distribution vector of node $k$ as $\boldsymbol{p}_k \triangleq [P_k(c_1),\ldots,P_k(c_M)]^T \in \mathbb{I}^{M}$, and the probability of state $m_k$ as $P_k(x_{m_k})$.
 		With independent encoding at all nodes, the probability of backscatter symbol tuple $x_{m_{\mathcal{K}}}$ is
@@
 		which is still non-convex due to the integration and entropy terms.
-		To tackle this, we rewrite the \gls{dmtmac} transition probability \eqref{eq:dmtmac} from input index tuple $m_{\mathcal{K}}$ to output index $l$ as a regularized incomplete Gamma function in the series representation \cite[Theorem~3]{Jameson2016}
+		To tackle this, we rewrite the \gls{dmtmac} transition probability \eqref{eq:dmtmac} from input index tuple $m_{\mathcal{K}}$ to output index $l$ as a regularized incomplete Gamma function in the series representation \cite[Theorem 3]{Jameson2016}
 		\begin{equation}
@@
 		\end{maxi!}
-		and it is trivial to conclude $t_0^\star=0$ and $t_L^\star=\infty$ for energy-based backscatter detection.
+		which is still non-convex because variable $\boldsymbol{t}$ appear on the limits of integration \eqref{eq:dmtmac}.
+		To tackle this, we reveal backscatter decision design has no impact on primary achievable rate, and regard the dispersed nodes with given input distribution as an equivalent augmented source in terms of total rate.
+		% We then constrain the feasible domain of problem \eqref{op:decision_threshold} from continuous space $\mathbb{R}_+^{L+1}$ to finite candidate set (i.e., fine-grained discrete energy levels) $\mathcal{T}^{L+1}$, and reuse existing rate-optimal quantization schemes for \gls{dmc} to solve problem \eqref{op:decision_threshold}.
 
 		\begin{remark}
-			Backscatter detection (and decision design) has no impact on primary achievable rate.
-			When nodes transmit at non-zero total rate, the user can re-encode backscatter messages to recover coded backscatter tuple $x_{\mathcal{K}}$ at each block.
-			Otherwise, $x_{\mathcal{K}}$ can be fully deterministic and known to the user.
-			% Once backscatter messages are successfully decoded, the user can re-encode backscatter messages to recover coded backscatter tuple $x_{\mathcal{K}}$ at each block.
-			% Upon successful backscatter detection, the user can re-encode backscatter messages to recover coded backscatter tuple $x_{\mathcal{K}}$ at each block.
-			% Therefore, decision design has no impact on primary achievable rate.
-			% Decision threshold only influences backscatter rate instead of primary rate.
+			Upon successful backscatter decoding, UniScatter receiver can always re-encode node messages to recover their reflection patterns at each primary block.
+			Therefore, backscatter decision design has no impact on the primary achievable rate, and any thresholding scheme maximizing the total backscatter mutual information \eqref{eq:backscatter_mutual_information} is also optimal for problem \eqref{op:decision_threshold}.
 			\label{re:backscatter_detection}
@@
 
+		\begin{remark}
+			In terms of total backscatter rate, the dispersed nodes with given input distribution can be viewed as an equivalent source with augmented alphabet of backscatter symbol tuples $x_{m_{\mathcal{K}}}$.
+			As such, the \gls{dmtmac} \eqref{eq:dmtmac} is essentially a \gls{dmtc}, and problem \eqref{op:decision_threshold} reduces to rate-optimal quantization design for discrete-input continuous-output memoryless channel.
+		\end{remark}
+
+		Next, we constrain the feasible domain of problem \eqref{op:decision_threshold} from continuous space $\mathbb{R}_+^{L+1}$ to finite candidate set (i.e., fine-grained discrete energy levels) $\mathcal{T}^{L+1}$, and reuse existing rate-optimal quantization schemes for \gls{dmc} to solve problem \eqref{op:decision_threshold}.
+
 		Remark \ref{re:backscatter_detection} suggests any $\boldsymbol{t}$ maximizes total backscatter mutual information $I_{\mathrm{B}}(x_{\mathcal{K}};\hat{x}_{\mathcal{K}})$ is also optimal for problem \eqref{op:decision_threshold}.
+
+		where $t_0^\star=0$ and $t_L^\star=\infty$ for energy-based backscatter detection.
 
@@
 	% 	Suppose the optimal number of thresholds is $S+1$ where $S \ge L$.
-	% 	Let $\boldsymbol{t} \triangleq [t_0,\ldots,t_S]^T \in \mathbb{R}_{+}^{(S+1) \times 1}$ be the optimal threshold vector where $t_{s-1} < t_s$, $\forall s \in \mathcal{S} \triangleq \{1,\ldots,S\}$.
+	% 	Let $\boldsymbol{t} \triangleq [t_0,\ldots,t_S]^T \in \mathbb{R}_{+}^{(S+1)}$ be the optimal threshold vector where $t_{s-1} < t_s$, $\forall s \in \mathcal{S} \triangleq \{1,\ldots,S\}$.
 	% 	Since the optimal decision region for any letter may consist of multiple partitions, without loss of generality, we assume the mapping from threshold vector to decision region $l' \in \mathcal{L} \triangleq \{1,\ldots,L\}$ is given by $\mathcal{R}_{l'} = \bigcup_{s \equiv l' \pmod L} [t_{s-1},t_s)$.

### 2022-08-20 main.tex
:pencil: Update threshold design

@@
 	$\mathrm{diag}(\cdot)$ returns a square matrix with the input vector on its main diagonal and zeros elsewhere.
+	$\mathrm{card}(\cdot)$ returns the cardinality of a set.
 	$(\cdot)^*$, $(\cdot)^T$, $(\cdot)^H$, $\lvert{\cdot}\rvert$, and $\lVert{\cdot}\rVert$ denote the conjugate, transpose, conjugate transpose, absolute value, and Euclidean norm operators, respectively.
@@
 		Like most existing literatures, we limit the scope of this paper to convex decision regions and consider sequential decision thresholds design therein.
-		For the ease of notations, we define a general bijective function transforming backscatter index tuple $m_{\mathcal{K}}$ to integer $l \in \mathcal{L} \triangleq \{1,\ldots,L \triangleq M^K\}$, and use both notation interchangeably in the following context.
-		As such, the convex decision region of backscatter index tuple $m_{\mathcal{K}}$ or equivalent letter $l$ can be written as
-		\begin{equation}
-			\mathcal{R}_{m_{\mathcal{K}}} \triangleq [t_{l-1},t_l), \quad t_{l-1} \le t_l.
+		For the ease of notations, we define a general bijective function from backscatter index tuple $m_{\mathcal{K}}$ to integer $l \in \mathcal{L} \triangleq \{1,\ldots,L \triangleq M^K\}$, where $\{\sigma_l^2\}_{l \in \mathcal{L}}$ are sorted in an ascending order.
+		Both notations are used interchangeably in the following context.
+		As such, the convex decision region of backscatter tuple $l$ can be written as
+		\begin{equation}
+			\mathcal{R}_{l} \triangleq [t_{l-1},t_l), \quad t_{l-1} \le t_l.
 		\end{equation}
@@
 		\addConstraint{\lVert \boldsymbol{w} \rVert^2}{\le P}{\label{co:transmit_power}}
-		\addConstraint{t_{l-1}}{\le t_l,}{\quad \forall l.}{\label{co:decision_threshold}}
+		% \addConstraint{t_{l-1}}{\le t_l,}{\quad \forall l.}{\label{co:decision_threshold}}
+		\addConstraint{\boldsymbol{t}}{\ge \boldsymbol{0}.}{\label{co:decision_threshold}}
 	\end{maxi!}
@@
 		\end{maxi!}
-		which is still non-convex because variable $\boldsymbol{t}$ appear on the limits of integration \eqref{eq:dmtmac}.
-		To tackle this, we reveal backscatter decision design has no impact on primary achievable rate, and regard the dispersed nodes with given input distribution as an equivalent augmented source in terms of total rate.
-		% We then constrain the feasible domain of problem \eqref{op:decision_threshold} from continuous space $\mathbb{R}_+^{L+1}$ to finite candidate set (i.e., fine-grained discrete energy levels) $\mathcal{T}^{L+1}$, and reuse existing rate-optimal quantization schemes for \gls{dmc} to solve problem \eqref{op:decision_threshold}.
+		which is still non-convex because variable $\boldsymbol{t}$ appears on the limits of integration \eqref{eq:dmtmac}.
+		Fortunately, we can further simplify problem \eqref{op:decision_threshold} as a point-to-point rate-optimal quantization design for a discrete-input continuous-output memoryless channel, thanks to Remark \ref{re:backscatter_decision} and \ref{re:augmented_source}.
 
@@
 			Therefore, backscatter decision design has no impact on the primary achievable rate, and any thresholding scheme maximizing the total backscatter mutual information \eqref{eq:backscatter_mutual_information} is also optimal for problem \eqref{op:decision_threshold}.
-			\label{re:backscatter_detection}
+			\label{re:backscatter_decision}
 		\end{remark}
@@
 		\begin{remark}
-			In terms of total backscatter rate, the dispersed nodes with given input distribution can be viewed as an equivalent source with augmented alphabet of backscatter symbol tuples $x_{m_{\mathcal{K}}}$.
-			As such, the \gls{dmtmac} \eqref{eq:dmtmac} is essentially a \gls{dmtc}, and problem \eqref{op:decision_threshold} reduces to rate-optimal quantization design for discrete-input continuous-output memoryless channel.
+			In terms of total backscatter rate, the dispersed nodes with given input distribution can be viewed as an equivalent source with augmented alphabet of backscatter symbol tuples $\{x_{m_{\mathcal{K}}}\}$.
+			As such, the \gls{dmtmac} \eqref{eq:dmtmac} is essentially a \gls{dmtc}, and problem \eqref{op:decision_threshold} reduces to the rate-optimal quantization design for a discrete-input continuous-output memoryless channel.
+			\label{re:augmented_source}
 		\end{remark}
 
-		Next, we constrain the feasible domain of problem \eqref{op:decision_threshold} from continuous space $\mathbb{R}_+^{L+1}$ to finite candidate set (i.e., fine-grained discrete energy levels) $\mathcal{T}^{L+1}$, and reuse existing rate-optimal quantization schemes for \gls{dmc} to solve problem \eqref{op:decision_threshold}.
-
-		Remark \ref{re:backscatter_detection} suggests any $\boldsymbol{t}$ maximizes total backscatter mutual information $I_{\mathrm{B}}(x_{\mathcal{K}};\hat{x}_{\mathcal{K}})$ is also optimal for problem \eqref{op:decision_threshold}.
-
-		where $t_0^\star=0$ and $t_L^\star=\infty$ for energy-based backscatter detection.
-
-		\begin{remark}
-			% With input distribution of all nodes, we can formulate an equivalent information source with augmented alphabet of tag input combination.
-			% In terms of total backscatter rate, we can formulate an equivalent information source with augmented alphabet of tag input combination.
-			% When input distribution of all nodes are available, we can formulate an equivalent information source in terms of total backscatter rate.
-			% When input distribution of all nodes are available, we can think an equivalent information source with augmented alphabet of state tuple, in terms of total backscatter rate.
-			% In terms of total backscatter rate, we can regard all nodes as an equivalent information source with augmented alphabet of node state tuple $x_{m_{\mathcal{K}}}$.
-			In terms of total backscatter rate, the nodes can be regarded as an equivalent source with augmented alphabet of symbol tuple $x_{m_{\mathcal{K}}}$, and the \gls{dmtmac} \eqref{eq:dmtmac} essentially reduces to a \gls{dmtc}.
-			% As such, the \gls{dmtmac} \eqref{eq:dmtmac} is essentially a \gls{dmtc}, and decision threshold design can be simplified accordingly.
-		\end{remark}
-
-		Finally, we can employ existing thresholding design for \gls{dmtc} to solve problem \eqref{op:decision_threshold}.
-		For example, \cite{He2021} first discretized the continuous energy $z$ into numerous output bins, then grouped adjacent bins to maximize mutual information using \gls{dp} accelerated by \gls{smawk} algorithm.
-		In \cite{Nguyen2020a}, the authors first proved the optimality condition for any three neighbor thresholds, then fix $t_0$, traverse $t_1$, and sequentially optimizes the others by bisection.
-		Both will be compared with \gls{ml} decision \cite{Qian2019}
-		\begin{equation}
-			t_{l}^{\mathrm{\gls{ml}}} = N \frac{\sigma_{l-1}^2 \sigma_{l}^2}{\sigma_{l-1}^2 - \sigma_{l}^2} \log \frac{\sigma_{l-1}^2}{\sigma_{l}^2}, \quad l \in \mathcal{L} \setminus \{0,L\},
+		Next, we constrain the feasible domain of problem \eqref{op:decision_threshold} from continuous space $\mathbb{R}_+^{L+1}$ to finite candidate set (i.e., fine-grained discrete energy levels) $\mathcal{T}^{L+1}$.
+		\begin{figure}[!t]
+			\centering
+			\resizebox{0.9\columnwidth}{!}{
+				\input{assets/illustration/discrete_outputs.tex}
+			}
+			\caption{
+				The decision thresholds are selected from fine-grained discrete energy levels instead of continuous space, and each decision region consists of at least one neighbor energy bins.
+			}
+			\label{fi:discrete_outputs}
+		\end{figure}
+		As shown in Fig. \ref{fi:discrete_outputs}, by introducing the extra analog-to-digital conversion step, we can obtain decision regions by grouping adjacent high-resolution energy bins.
+		Thus, problem \eqref{op:decision_threshold} is recast as
+		\begin{maxi}
+			{\scriptstyle{\boldsymbol{t} \in \mathcal{T}^{L+1}}}{I_{\mathrm{B}}(x_{\mathcal{K}};\hat{x}_{\mathcal{K}}),}{\label{op:decision_threshold_recast}}{}
+		\end{maxi}
+		which can be solved by existing rate-optimal \gls{dmc} quantizer designs.
+		For global optimal solutions, \cite{He2021} proposed a \gls{dp} method accelerated by the \gls{smawk} algorithm with computational complexity $\mathcal{O}\bigl(L^2(\mathrm{card}(\mathcal{T})-L)\bigr)$, and \cite{Nguyen2020a} presented a traverse-bisection algorithm using the optimality condition of three neighbor thresholds with complexity $\mathcal{O}\bigl(\mathrm{card}(\mathcal{T})L\log(\mathrm{card}(\mathcal{T})L)\bigr)$.
+		In Section \ref{se:simulation_results}, both schemes will be compared with the \gls{ml} thresholding scheme \cite{Qian2019}
+		\begin{equation}
+			t_{l}^{\mathrm{\gls{ml}}} = N \frac{\sigma_{l-1}^2 \sigma_{l}^2}{\sigma_{l-1}^2 - \sigma_{l}^2} \log \frac{\sigma_{l-1}^2}{\sigma_{l}^2}, \quad l \in \mathcal{L} \setminus \{L\},
 			\label{eq:detection_threshold_maximum_likelihood}
 		\end{equation}
-		which is generally suboptimal for problem \eqref{op:decision_threshold} except for equiprobable inputs at all nodes.
-
-		% \begin{remark}
-		% 	Although the \gls{ml} decision threshold is optimal in terms of the likelihood function, it is not necessarily capacity-achieving, although the performance gap can be negligible in the single-tag \gls{bibo} case.
-		% \end{remark}
-
-		% Interestingly, the optimal threshold design to maximize the mutual information for a general \gls{dmtc} with a fixed number of output letters remains an open issue.
-		% The reason is that each decision region may contain more than one disjoint partitions (i.e., non-convex) and the number of thresholds are unknown.
-		% Fortunately, for the proposed energy detection, we proved that the \gls{dmtc} capacity can be achieved using only convex decision regions.
-		% This conclusion is summarized below.
-
-		% \begin{proposition}
-		% 	For a discrete-input continuous-output channel in Gamma distribution \eqref{eq:energy_distribution}, if the \gls{dmtc} is constructed for detection (i.e., same input/output alphabet) and $L$ input letters are with non-zero probability, then it is possible to achieve the \gls{dmtc} capacity by $L$ non-empty convex decision regions defined by $L+1$ distinct decision thresholds.
-		% 	\label{pr:threshold}
-		% \end{proposition}
-
-		% \begin{proof}
-		% 	Please refer to Appendix \ref{ap:threshold}.
-		% 	\label{pf:threshold}
-		% \end{proof}
-
-		% Once the optimal number of decision threshold is determined, we can first discretize the output energy level into numerous bins, then obtain the optimal decision regions that maximizes the total backscatter rate by \gls{dp} accelerated by \gls{smawk} algorithm \cite{He2021}.
+		which is generally suboptimal for problem \eqref{op:decision_threshold} except when all nodes are with equiprobable inputs.
 	\end{subsection}
@@
 \begin{section}{Simulation Results}
+	% TODO design $\mathcal{T}$
 	% TODO add distribution to initializer to smooth curves?
@@
 	\end{subsection}
+	\label{se:simulation_results}
 \end{section}

### 2022-08-21 src/region_distribution.m
:hammer: Update scripts

@@ -4,10 +4,10 @@ clear; setup; cvx_begin; cvx_end; clc; run(strcat('config_', erase(mfilename, 'r
 Result(nVariables, nWeights) = struct('weight', [], 'rate', [], 'distribution', [], 'threshold', [], 'beamforming', []);
 
 % * Generate channels
-directChannel = rxGain * path_loss(frequency, directDistance, directExponent) * fading_ricean(nTxs, 1, directFactor);
+directChannel = sqrt(path_loss(directDistance, directExponent)) * fading_ricean(nTxs, nRxs, directFactor);
 cascadedChannel = zeros(nTxs, nTags);
 for iTag = 1 : nTags
-	cascadedChannel(:, iTag) = rxGain * path_loss(frequency, forwardDistance(iTag), forwardExponent) * fading_ricean(nTxs, 1, forwardFactor) * path_loss(frequency, backwardDistance(iTag), backwardExponent) * fading_ricean(1, 1, backwardFactor);
+	cascadedChannel(:, iTag) = sqrt(path_loss(forwardDistance(iTag), forwardExponent)) * fading_ricean(nTxs, nSxs, forwardFactor) * sqrt(path_loss(backwardDistance(iTag), backwardExponent)) * fading_ricean(nSxs, nRxs, backwardFactor);
 end
 equivalentChannel = directChannel + scatterRatio * cascadedChannel * transpose(constellation(tuple_tag(repmat(transpose(1 : nStates), [1, nTags]))));
 

### 2022-08-21 src/region_scatter.m

@@ -4,10 +4,10 @@ clear; setup; cvx_begin; cvx_end; clc; run(strcat('config_', erase(mfilename, 'r
 Result(nVariables, nWeights) = struct('weight', [], 'rate', [], 'distribution', [], 'threshold', [], 'beamforming', []);
 
 % * Generate channels
-directChannel = rxGain * path_loss(frequency, directDistance, directExponent) * fading_ricean(nTxs, 1, directFactor);
+directChannel = sqrt(path_loss(directDistance, directExponent)) * fading_ricean(nTxs, nRxs, directFactor);
 cascadedChannel = zeros(nTxs, nTags);
 for iTag = 1 : nTags
-	cascadedChannel(:, iTag) = rxGain * path_loss(frequency, forwardDistance(iTag), forwardExponent) * fading_ricean(nTxs, 1, forwardFactor) * path_loss(frequency, backwardDistance(iTag), backwardExponent) * fading_ricean(1, 1, backwardFactor);
+	cascadedChannel(:, iTag) = sqrt(path_loss(forwardDistance(iTag), forwardExponent)) * fading_ricean(nTxs, nSxs, forwardFactor) * sqrt(path_loss(backwardDistance(iTag), backwardExponent)) * fading_ricean(nSxs, nRxs, backwardFactor);
 end
 
 % * Evaluate rate region vs tag scatter ratio

### 2022-08-21 main.tex
:pencil: Update parameters

@@
 			}
-			\caption{A single-user multi-node UniScatter network.}
+			\caption{A single-user multi-node UniScatter system.}
 			\label{fi:uniscatter_network}
 		\end{figure}
-		To demonstrate the advantages of UniScatter, we consider a single-user multi-node \gls{miso} UniScatter network as shown in Fig. \ref{fi:uniscatter_network}.
+		To demonstrate the advantages of UniScatter, we consider a single-user multi-node \gls{miso} UniScatter system as shown in Fig. \ref{fi:uniscatter_network}.
 		In the primary active point-to-point system, a $Q$-antenna \gls{ap} transmits to a single-antenna user assisted by $K$ nearby single-antenna UniScatter nodes with $M$ reflection states.
@@
 		which is still non-convex because variable $\boldsymbol{t}$ appears on the limits of integration \eqref{eq:dmtmac}.
-		Fortunately, we can further simplify problem \eqref{op:decision_threshold} as a point-to-point rate-optimal quantization design for a discrete-input continuous-output memoryless channel, thanks to Remark \ref{re:backscatter_decision} and \ref{re:augmented_source}.
+		Fortunately, we can further simplify problem \eqref{op:decision_threshold} as a point-to-point rate-optimal quantizer optimization for a discrete-input continuous-output memoryless channel, thanks to Remark \ref{re:backscatter_decision} and \ref{re:augmented_source}.
 
@@
 		\end{figure}
-		As shown in Fig. \ref{fi:discrete_outputs}, by introducing the extra analog-to-digital conversion step, we can obtain decision regions by grouping adjacent high-resolution energy bins.
+		As shown in Fig. \ref{fi:discrete_outputs}, by introducing the extra analog-to-digital conversion step, we can group adjacent high-resolution energy bins for backscatter decision regions.
 		Thus, problem \eqref{op:decision_threshold} is recast as
@@
 		which can be solved by existing rate-optimal \gls{dmc} quantizer designs.
-		For global optimal solutions, \cite{He2021} proposed a \gls{dp} method accelerated by the \gls{smawk} algorithm with computational complexity $\mathcal{O}\bigl(L^2(\mathrm{card}(\mathcal{T})-L)\bigr)$, and \cite{Nguyen2020a} presented a traverse-bisection algorithm using the optimality condition of three neighbor thresholds with complexity $\mathcal{O}\bigl(\mathrm{card}(\mathcal{T})L\log(\mathrm{card}(\mathcal{T})L)\bigr)$.
+		For global optimal solutions, \cite{He2021} proposed a \gls{dp} method accelerated by the \gls{smawk} algorithm with computational complexity $\mathcal{O}\bigl(L^2(\mathrm{card}(\mathcal{T})-L)\bigr)$, and \cite{Nguyen2020a} presented a traverse-then-bisect algorithm using the optimality condition of three neighbor thresholds with complexity $\mathcal{O}\bigl(\mathrm{card}(\mathcal{T})L\log(\mathrm{card}(\mathcal{T})L)\bigr)$.
 		In Section \ref{se:simulation_results}, both schemes will be compared with the \gls{ml} thresholding scheme \cite{Qian2019}
@@
 \begin{section}{Simulation Results}
-	% TODO design $\mathcal{T}$
-	% TODO add distribution to initializer to smooth curves?
 	% TODO compare PGD and primary-MRT beamformers
-	In this section, we provide numerical results to evaluate the proposed input, beamforming and decision design over a single-user multi-node UniScatter network.
-	We assume the distance between \gls{ap} and user is \qty{10}{\meter}, and $K=2$ UniScatter nodes are uniformly dropped within a disk centered at the user of radius \qty{1}{\meter}.
-	% The carrier frequency is $f=\qty{200}{\MHz}$, and we consider \gls{iid} Ricean fading for all channels.
-	The carrier frequency is $f=\qty{200}{\MHz}$, and we consider \gls{iid} Ricean fading between all terminals.
-	For direct, forward and backward links, we set the path loss exponents to \num{2.6}, \num{2.4} and \num{2}, and the Ricean factor to \num{5}, \num{5} and \num{10}, respectively.
-	% For direct, forward and backward links, we choose path loss exponents \num{2.6}, \num{2.4} and \num{2}, and Ricean factor \num{5}, \num{5} and \num{10}, respectively.
-	% and the path loss exponents for direct, forward and backward links are \num{2.6}, \num{2.4} and \num{2}, respectively.
-	% We consider \gls{iid} Ricean fading for all channels with Ricean factor set to \num{5}, \num{5} and \num{10}
-	The \gls{ap} has $Q=4$ antennas with maximum average transmit power $P=\qty{36}{\dBm}$.
-	All nodes have amplitude scattering ratio $\alpha=0.5$, symbol period ratio $N=20$, and perform \gls{qam} with $M=4$ input states.
-	% and we consider amplitude scattering ratio $\alpha=0.5$ and symbol period ratio $N=20$.
-	% The user has a receive antenna gain of \qty{3}{\dBi} and average noise power
-	The user is with average noise power $\sigma_v^2=\qty{70}{\dBm}$ and receive antenna gain \qty{3}{\dBi}.
-	All rate regions are averaged over at least \num{1000} instances, where ``PSP'' and ``BSP'' means primary and backscatter symbol periods, respectively.
-	We choose decision design by \gls{smawk} \cite{He2021} as reference, and select discretize boundaries uniformly over the \qty{95}{\percent} confidence region of edge hypotheses.
-	The parameters remain fixed unless otherwise specified.
+	In this section, we provide numerical results to evaluate the proposed input distribution, active beamforming, and backscatter decision design for the UniScatter system in Fig.
+\ref{fi:uniscatter_network}.
+	We assume the AP-user distance is \qty{10}{\meter}, $K=2$ UniScatter nodes are randomly dropped within a disk of radius \qty{2}{\meter} centered at the user, the \gls{ap} is with $Q=4$ transmit antennas and an average power budget $P=\qty{36}{\dBm}$, the nodes employs \num{4}-\gls{qam} with amplitude scattering ratio $\alpha=0.5$, the user is with average noise power $\sigma_v^2=\qty{-40}{\dBm}$, and the symbol period ratio is $N=20$.
+	For all channels involved, we consider a distance-dependent path loss model
+	\begin{equation}
+		L(d) = L_0 \biggl(\frac{d_0}{d}\biggr)^\gamma,
+	\end{equation}
+	together with a Ricean fading model
+	\begin{equation}
+		\boldsymbol{H} = \sqrt{\frac{\kappa}{1+\kappa}} \bar{\boldsymbol{H}} + \sqrt{\frac{1}{1+\kappa}} \tilde{\boldsymbol{H}}
+	\end{equation}
+	where $d$ is the transmission distance, $L_0=-\qty{30}{\dB}$ is the reference path loss at distance $d_0=\qty{1}{\meter}$, $\kappa$ is the Ricean $K$-factor, $\bar{\boldsymbol{H}}$ is the deterministic line-of-sight component with unit-magnitude entries, and $\tilde{\boldsymbol{H}}$ is the Rayleigh fading component with entries in standard \gls{iid} \gls{cscg} distribution.
+	We choose $\gamma_{\mathrm{D}}=2.6$, $\gamma_{\mathrm{F}}=2.4$, $\gamma_{\mathrm{B}}=2$, and $\kappa_{\mathrm{D}}=\kappa_{\mathrm{F}}=\kappa_{\mathrm{B}}=5$ for direct, forward and backward links.
+	The finite threshold domain $\mathcal{T}$ comes from $b$-bit uniform discretization over the critical interval defined by the confidence bounds of edge hypotheses (i.e., lower bound of $\mathcal{H}_1$ and upper bound of $\mathcal{H}_L$) with confidence level $1-\varepsilon$, where $b=8$ and $\varepsilon=\num{2.22e-16}$.
+	All achievable rate regions are averaged over \num{3000} realizations, and the parameters remain fixed unless otherwise specified.
 

### 2022-08-22 main.tex
:pencil: Discuss input distribution vs link priority

@@
 			}
-			\caption{Block diagram, equivalent circuit, and scatter model of a UniScatter node.
+			\caption{
+			Block diagram, equivalent circuit, and scatter model of a UniScatter node.
 			The solid and dashed vectors represent signal and energy flows.
-The scattering antenna behaves as a constant power source, where the voltage $V_0$ and current $I_0$ are introduced by incident electric field $\vec{E}_{\mathrm{I}}$ and magnetic field $\vec{H}_{\mathrm{I}}$ \cite{Huang2021}.}
+			The scattering antenna behaves as a constant power source, where the voltage $V_0$ and current $I_0$ are introduced by incident electric field $\vec{E}_{\mathrm{I}}$ and magnetic field $\vec{H}_{\mathrm{I}}$ \cite{Huang2021}.
+			}
 			\label{fi:uniscatter_node}
@@
 		\begin{equation}
-			\mathcal{R}_{l} \triangleq [t_{l-1},t_l), \quad t_{l-1} \le t_l.
+			\mathcal{R}_{l} \triangleq [t_{l-1},t_l), \quad 0 \le t_{l-1} \le t_l.
 		\end{equation}
@@
 		\addConstraint{\lVert \boldsymbol{w} \rVert^2}{\le P}{\label{co:transmit_power}}
-		% \addConstraint{t_{l-1}}{\le t_l,}{\quad \forall l.}{\label{co:decision_threshold}}
-		\addConstraint{\boldsymbol{t}}{\ge \boldsymbol{0}.}{\label{co:decision_threshold}}
+		\addConstraint{t_{l-1}}{\le t_l,}{\quad \forall l}{\label{co:sequential_threshold}}
+		\addConstraint{\boldsymbol{t}}{\ge \boldsymbol{0}.}{\label{co:nonnegative_threshold}}
 	\end{maxi!}
@@
 			Although \gls{kkt} solutions to problem \eqref{op:input_distribution} may end up being saddle points, we will later show by simulation their average performance can be reasonably close to optimal for a moderate $K$.
+			\label{re:input_kkt_distribution}
 		\end{remark}
@@
 			{\scriptstyle{\boldsymbol{t}}}{I(x_{\mathcal{K}})}{\label{op:decision_threshold}}{\label{ob:decision_threshold}}
-			\addConstraint{\eqref{co:decision_threshold},}
+			\addConstraint{\eqref{co:sequential_threshold},\eqref{co:nonnegative_threshold},}
 		\end{maxi!}
@@
 			}
-			\caption{
-				The decision thresholds are selected from fine-grained discrete energy levels instead of continuous space, and each decision region consists of at least one neighbor energy bins.
-			}
+			\caption{The decision thresholds are selected from fine-grained discrete energy levels instead of continuous space, and each decision region consists of at least one neighbor energy bins.}
 			\label{fi:discrete_outputs}
@@
 		Thus, problem \eqref{op:decision_threshold} is recast as
-		\begin{maxi}
-			{\scriptstyle{\boldsymbol{t} \in \mathcal{T}^{L+1}}}{I_{\mathrm{B}}(x_{\mathcal{K}};\hat{x}_{\mathcal{K}}),}{\label{op:decision_threshold_recast}}{}
-		\end{maxi}
-		which can be solved by existing rate-optimal \gls{dmc} quantizer designs.
-		For global optimal solutions, \cite{He2021} proposed a \gls{dp} method accelerated by the \gls{smawk} algorithm with computational complexity $\mathcal{O}\bigl(L^2(\mathrm{card}(\mathcal{T})-L)\bigr)$, and \cite{Nguyen2020a} presented a traverse-then-bisect algorithm using the optimality condition of three neighbor thresholds with complexity $\mathcal{O}\bigl(\mathrm{card}(\mathcal{T})L\log(\mathrm{card}(\mathcal{T})L)\bigr)$.
-		In Section \ref{se:simulation_results}, both schemes will be compared with the \gls{ml} thresholding scheme \cite{Qian2019}
+		\begin{maxi!}
+			{\scriptstyle{\boldsymbol{t} \in \mathcal{T}^{L+1}}}{I(x_{\mathcal{K}})}{\label{op:decision_threshold_discrete}}{\label{ob:decision_threshold_discrete}}
+			\addConstraint{\eqref{co:sequential_threshold},}
+		\end{maxi!}
+		which can be solved by existing rate-optimal sequential quantizer designs for \gls{dmc}.
+		To obtain global optimal solution, \cite{He2021} started from the quadrangle inequality and proposed a \gls{dp} method accelerated by the \gls{smawk} algorithm with computational complexity $\mathcal{O}\bigl(L^2(\mathrm{card}(\mathcal{T})-L)\bigr)$, while \cite{Nguyen2020a} started from the optimality condition for three neighbor thresholds and presented a traverse-then-bisect algorithm with complexity $\mathcal{O}\bigl(\mathrm{card}(\mathcal{T})L\log(\mathrm{card}(\mathcal{T})L)\bigr)$.
+		In Section \ref{se:simulation_results}, both schemes will be compared with the \gls{ml} thresholding \cite{Qian2019}
 		\begin{equation}
@@
 	\end{equation}
-	where $d$ is the transmission distance, $L_0=-\qty{30}{\dB}$ is the reference path loss at distance $d_0=\qty{1}{\meter}$, $\kappa$ is the Ricean $K$-factor, $\bar{\boldsymbol{H}}$ is the deterministic line-of-sight component with unit-magnitude entries, and $\tilde{\boldsymbol{H}}$ is the Rayleigh fading component with entries in standard \gls{iid} \gls{cscg} distribution.
+	where $d$ is the transmission distance, $L_0=-\qty{30}{\dB}$ is the reference path loss at distance $d_0=\qty{1}{\meter}$, $\kappa$ is the Ricean $K$-factor, $\bar{\boldsymbol{H}}$ is the deterministic line-of-sight component with entries of unit magnitude, and $\tilde{\boldsymbol{H}}$ is the Rayleigh fading component with entries in standard \gls{iid} \gls{cscg} distribution.
 	We choose $\gamma_{\mathrm{D}}=2.6$, $\gamma_{\mathrm{F}}=2.4$, $\gamma_{\mathrm{B}}=2$, and $\kappa_{\mathrm{D}}=\kappa_{\mathrm{F}}=\kappa_{\mathrm{B}}=5$ for direct, forward and backward links.
 	The finite threshold domain $\mathcal{T}$ comes from $b$-bit uniform discretization over the critical interval defined by the confidence bounds of edge hypotheses (i.e., lower bound of $\mathcal{H}_1$ and upper bound of $\mathcal{H}_L$) with confidence level $1-\varepsilon$, where $b=8$ and $\varepsilon=\num{2.22e-16}$.
-	All achievable rate regions are averaged over \num{3000} realizations, and the parameters remain fixed unless otherwise specified.
-
-	\begin{subsection}{Input Distribution vs. Weight}
+	All achievable rate curves/regions are averaged over \num{3000} realizations, and the parameters remain fixed unless otherwise specified.
+
+	\begin{subsection}{Input Distribution versus Link Priority}
 		\begin{figure}[!t]
@@
 			}
-			\caption{Typical input distributions vs. weight $\rho$ for a UniScatter node with $M=4$ inputs.}
+			\caption{Typical instances of node input distribution under different weights.}
 			\label{fi:distribution_weights}
 		\end{figure}
-		% We consider a single UniScatter with $M=4$ inputs in this case of study.
-		In Fig. \ref{fi:distribution_weights}, we present typical input distributions of a single UniScatter node with $M=4$ inputs under different weight $\rho$.
-		Fig. \subref*{fi:distribution_weights_1} and \subref*{fi:distribution_weights_2} are obtained from \gls{iid} drop and channel realizations.
-		We note that even for $\rho=0$ (i.e., best backscatter performance), the optimal input distribution is not equiprobable like \gls{sr}, and adaptive channel coding can further increase total backscatter rate based on \gls{csi}.
-		On the other hand, the optimal input distribution becomes fully deterministic at $\rho=1$ (i.e., best primary performance), where the state maximizes equivalent primary channel \eqref{eq:equivalent_channel} strength is chosen with probability \num{1}.
-		In this case, UniScatter node boils down to a \gls{ris} element with $M$ discrete states.
-		As $\rho$ moves from \num{0} to \num{1}, the optimal input distribution becomes gradually biased to one state and flexibly balances the primary-backscatter tradeoff.
-	\end{subsection}
-
-	\begin{subsection}{Rate Region vs. Input, Beamforming, and Decision Schemes}
+		The objective of this study is to demonstrate each UniScatter node can adjust its input distribution based on \gls{csi} and link priority to balance backscatter modulation and passive beamforming.
+		For this aim, we evaluate the \gls{kkt} input distribution by Algorithm \ref{al:input_distribution} for a single node under different weights $\rho=\{0,0.1,0.2,0.3,1\}$ in Fig.
+\ref{fi:distribution_weights}, where \subref*{fi:distribution_weights_1} and \subref*{fi:distribution_weights_2} are two representative instances.
+		We observe that as $\rho$ increases from \num{0} to \num{1}, the \gls{kkt} input distribution
+		gradually progresses from slightly skewed to completely biased.
+		For $\rho=0$ where backscatter performance is absolutely prioritized, the \gls{csi}-adaptive channel coding at the UniScatter node provides higher backscatter rate than conventional \gls{bc} and \gls{sr} nodes with uncoded equiprobable inputs.
+		On the other hand, for $\rho=1$ where primary performance is absolutely prioritized, the input probability is \num{1} at the state that maximizes the equivalent primary channel strength, and \num{0} at the others.
+		In this case, the reflection pattern over time is fully deterministic, and the UniScatter node indeed boils down to a \gls{ris} element with discrete phase shifts.
+		These observations meet our expectation that UniScatter nodes include scattering sources of \gls{bc}/\gls{sr} and reflecting elements of \gls{ris} as special cases, and generalize backscatter modulation and passive beamforming from the perspective of input distribution design.
+	\end{subsection}
+
+	\begin{subsection}{Backscatter Rate versus Output Discretization Bit}
+		Since the transformation from problem \eqref{op:decision_threshold} to \eqref{op:decision_threshold_discrete} introduces performance degradation, we investigate the impact of threshold domain discretization on the total backscatter rate.
+
+		% TODO Total Backscatter Rate versus Output Discretization Bit
+		TODO
+
+	\end{subsection}
+
+	\begin{subsection}{Rate Region under Different Schemes}
 		\begin{figure}[!t]
@@
 			}
+			\\
+			\subfloat[Active Beamforming\label{fi:region_beamforming}]{
+				\resizebox{0.48\columnwidth}{!}{
+					\input{assets/simulation/region_beamforming.tex}
+				}
+			}
 			\subfloat[Decision Threshold\label{fi:region_threshold}]{
@@
 			}
-			\caption{Average primary-total-backscatter rate regions for different input distribution and decision threshold schemes.}
+			\caption{
+				Average primary-total-backscatter rate regions for different input distribution, active beamforming, and decision threshold schemes.
+				``BSP'' means backscatter symbol period.
+			}
 		\end{figure}
-		Fig. \subref*{fi:region_distribution} compares the achievable rate regions by following input designs.
+		For the \gls{bcd} algorithm considered in the rest of this paper, we choose the \gls{kkt} input distribution by Algorithm \ref{al:input_distribution}, the \gls{pgd} active beamforming by Algorithm \ref{al:active_beamforming}, and the \gls{smawk} decision threshold by \cite{He2021} as reference.
+		The impact of different component schemes are explored below.
+
+		\begin{subsubsection}{Input Distribution}
+			We compare the following input distribution schemes for problem \eqref{op:input_distribution}:
 			\begin{itemize}
-			% \item ``Exhaustion'' means $K$-dimensional grid search over probability simplex;
-			% \item ``\gls{kkt}'' corresponds to Algorithm \ref{al:input_distribution};
-			% \item ``Cooperation'' assumes backscatter cooperation/joint encoding at all UniScatters, and employs Blahut-Arimoto algorithm \cite{Arimoto1972,Blahut1972a} to determine \emph{tuple} input distribution;
-			\item \textbf{Exhaustion:} $K$-dimensional grid search over probability simplex;
-			\item \textbf{\gls{kkt}:} results of Algorithm \ref{al:input_distribution};
-					% \item \textbf{Cooperation:} with backscatter cooperation/joint encoding at all UniScatters, Blahut-Arimoto algorithm \cite{Arimoto1972,Blahut1972a} for \emph{tuple} input distribution;
-					% \item \textbf{Cooperation:} backscatter cooperation/joint encoding at all UniScatters, \emph{tuple input distribution} by Blahut-Arimoto algorithm \cite{Arimoto1972,Blahut1972a};
-					% \item \textbf{Cooperation:} with backscatter cooperation (i.e., joint encoding) at all UniScatters, \emph{tuple input distribution} by Blahut-Arimoto algorithm \cite{Arimoto1972,Blahut1972a};
-			\item \textbf{Cooperation:} backscatter cooperation/joint encoding at all UniScatter nodes, tuple input distribution/joint probability array optimization by Blahut-Arimoto algorithm \cite{Arimoto1972,Blahut1972a};
-					% with backscatter cooperation (i.e., joint encoding) at all UniScatters, \emph{tuple input distribution} by Blahut-Arimoto algorithm \cite{Arimoto1972,Blahut1972a};
-			\item \textbf{Marginalization:} marginal distributions of joint probability array;
-			\item \textbf{Decomposition:} normalized tensors of rank-1 \gls{cp} decomposition of joint probability array;
-			\item \textbf{Randomization:} Gaussian recovery from joint probability array \cite{Calvo2010}.
+				\item \emph{Exhaustion:} Exhaustive grid search over the probability $K$-simplex with resolution $\Delta p = \num{1e-3}$;
+				% \item \emph{\gls{kkt}:} Numerical evaluation of the \gls{kkt} solutions by Algorithm \ref{al:input_distribution};
+				\item \emph{\gls{kkt}:} Numerical \gls{kkt} solution evaluation by Algorithm \ref{al:input_distribution};
+				\item \emph{Cooperation:} Numerical symbol tuple distribution (i.e., $K$-dimensional joint probability array) evaluation by the Blahut-Arimoto algorithm \cite{Arimoto1972,Blahut1972a}.
 			\end{itemize}
 
-		We notice adaptive joint encoding at all nodes provides the outer bound of rate region.
-		However, it involves arbitrarily dependent codewords, and backscatter cooperation between passive nodes is generally unaffordable.
-		In contrast, the rate region of \gls{kkt} input design in Algorithm \ref{al:input_distribution} approaches that of exhaustive search, and the loss is negligible for $K=2$.
-		% Although the randomization method \cite{Calvo2010} achieves similar performance, the computational complexity is much higher as it involves solving $K+1$ linear programming problems
-		Although the randomization method \cite{Calvo2010} returns similar rate region, it requires solving $K+1$ linear programming problems before applying Gaussian recovery.
-		The marginal distribution is slightly worse than \gls{kkt} despite having the same computational complexity, while the approximation from \gls{cp} decomposition is unsatisfying.
-
-		% TODO: beamforming
-
-		Fig. \subref*{fi:region_threshold} compares the achievable rate region by following threshold schemes.
+			Since \emph{Cooperation} involves full transmit cooperation of all nodes, we also propose the following recovery methods from the joint probability array for independent backscatter encoding:
 			\begin{itemize}
-			\item \textbf{\gls{dp}:} sequential quantizer grouping by dynamic programming \cite{He2021};
-			\item \textbf{\gls{smawk}:} above accelerated by \gls{smawk} algorithm;
-			\item \textbf{Bisection:} sequential bisection threshold design \cite{Nguyen2020a};
-			\item \textbf{\gls{ml}:} maximum likelihood decision \eqref{eq:detection_threshold_maximum_likelihood} \cite{Qian2019}.
+				\item \emph{Marginalization:} Marginal probability distributions;
+				\item \emph{Decomposition:} Normalized rank-\num{1} \gls{cp} decomposition tensors;
+				\item \emph{Randomization:} Random search with correlation matrix guidance \cite{Calvo2010}.
 			\end{itemize}
 
+			Fig. \subref*{fi:region_distribution} shows the achievable rate regions for those input distribution schemes.
+			We observe that \emph{Cooperation} provides the outer bound for all achievable rate regions.
+			Although transmit cooperation between UniScatter nodes can be generally helpful, it requires joint encoding with arbitrarily dependent codewords, which introduces extra coordination burden and may be unaffordable for a large $K$.
+			We also notice the average performance of \emph{\gls{kkt}} input distribution design by Algorithm \ref{al:input_distribution} is extremely close to that of \emph{Exhaustion}, and the loss is indistinguishable for $K=2$.
+			This verified our claim in Remark \ref{re:input_kkt_distribution}.
+			Despite \emph{Randomization} yields a similar result, the computational complexity is much higher (loops over $K+1$ linear programming problems) and the performance is backed by numerous random instances.
+			In contrast, the low-complexity \emph{Marginalization} returns a comparable result and the rate loss is insignificant when $K$ is small.
+			Finally, \emph{Decomposition} suffers from much lower average total backscatter rate, as the rank-\num{1} \gls{cp} approximation can be inaccurate for some channel-drop realizations.
+		\end{subsubsection}
+
+		\begin{subsubsection}{Active Beamforming}
+			% It is concluded that 1) UniScatter nodes provide flexible transmit-assist tradeoff using adaptive input distribution design; 2) when primary link is absolutely prioritized, the input probability of each node is \num{1} at one state and \num{0} at the others, which coincides with discretized \gls{ris}; 3) when backscatter link is absolutely prioritized, UniScatter nodes can exploit adaptive channel coding to achieve higher instantaneous rate than uncoded equiprobable inputs of \gls{bc}/\gls{sr}; 4) the proposed \gls{kkt} input distribution design converges to stationary points, whose average performance is very close to global optimal; 5) the \gls{pgd} beamforming achieves larger rate region than conventional \gls{mrt}; 6) the decision region schemes adapted to input distribution provide higher backscatter rates than the non-adaptive \gls{ml} detector; 7) cooperation between passive nodes in terms of joint encoding can further boost the total backscatter rate; 8) the low complexity of input distribution design and the marginal effect of increasing reflection states motivates the use of low-order scatter nodes to replace high-resolution \gls{ris}.
+			We compare the following active beamforming schemes for problem \eqref{op:active_beamforming}:
+			\begin{itemize}
+				\item \emph{\gls{pgd}:} Iterative \gls{pgd} optimization by Algorithm \ref{al:active_beamforming};
+				\item \emph{MRT:} Maximum ratio transmission to ergodic equivalent primary channel $\sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) \boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}})$.
+			\end{itemize}
+
+			Fig. \subref*{fi:region_beamforming} reveals the achievable regions for those active beamforming schemes.
+
+		\end{subsubsection}
+
+		\begin{subsubsection}{Decision Threshold}
+			We compare the following decision thresholds for problem \eqref{op:decision_threshold_discrete}:
+			\begin{itemize}
+				\item \emph{\gls{dp}:} Benchmark \gls{dp} method for sequential quantizer \cite{He2021};
+				\item \emph{\gls{smawk}:} \gls{dp} accelerated by the \gls{smawk} algorithm \cite{He2021};
+				\item \emph{Bisection:} The traverse-then-bisect algorithm \cite{Nguyen2020a};
+				\item \emph{\gls{ml}:} Maximum likelihood detector \eqref{eq:detection_threshold_maximum_likelihood} \cite{Qian2019}.
+			\end{itemize}
+
+			Fig. \subref*{fi:region_threshold} presents the achievable rate region for those decision threshold schemes.
 			We observe that input distribution-adaptive threshold designs achieve higher total backscatter rate than \gls{ml}.
@@
 			It emphasizes the importance of joint input distribution and decision region design.
-
-		% We note that ideal joint adaptive encoding at all UniScatters can further boost the total backscatter rate.
-		% However, this ideal upper bound requires real-time feedback
-		% ``Exhaustion'' means $K$-dimensional grid search over probability simplex, ``KKT'' corresponds to Algorithm \ref{ap:input_kkt_solution}, ``Cooperation'' assumes full backscatter cooperation and joint encoding at all UniScatters
+		\end{subsubsection}
+
 	\end{subsection}

### 2022-08-23 main.tex
:pencil: Discuss active beamforming

@@
 	Instead of treating probability distribution of reflection states as equiprobable (as scattering source of \gls{bc}/\gls{sr}) or degenerate (as reflecting element of \gls{ris}), UniScatter nodes located at different places adapt the input distribution of passive scatterers based on link priority and \gls{csi}, balancing information encoding and channel reconfiguration in a flexible and mutualistic manner.
-	To accommodate signal characteristics, UniScatter receiver semi-coherently decodes all nodes from accumulated energy, determines equivalent primary channel over reflection pattern, then coherently decodes the primary link under enhanced multipath.
+	To accommodate signal characteristics, UniScatter receiver semi-coherently decodes all nodes from accumulated energy, determines primary equivalent channel over reflection pattern, then coherently decodes the primary link under enhanced multipath.
 	It reduces the complexity of cooperative decoding while preserves the benefits of backscatter modulation and passive beamforming.
@@
 
-	\emph{Second,} we propose a practical UniScatter receiver that semi-coherently decodes UniScatter nodes from the received energy per backscatter block, re-encodes for their reflection patterns, retrieves equivalent primary channel as if dynamic passive beamforming, then coherently decodes the primary link under the enhanced multipath.
+	\emph{Second,} we propose a practical UniScatter receiver that semi-coherently decodes UniScatter nodes from the received energy per backscatter block, re-encodes for their reflection patterns, retrieves primary equivalent channel as if dynamic passive beamforming, then coherently decodes the primary link under the enhanced multipath.
 	The proposed receiver 1) preserves the benefits of backscatter modulation and passive beamforming; 2) enjoys lower computational and operational complexities than joint \gls{ml} and \gls{sic} schemes; 3) accommodates the link difference and suits for diverse symbol period ratios; 4) requires minor modification over legacy hardware.
@@
 	\emph{Fifth,} we provide numerical results to demonstrate the benefits of UniScatter and proposed algorithms.
-	It is concluded that 1) UniScatter nodes provide flexible transmit-assist tradeoff using adaptive input distribution design; 2) when primary link is absolutely prioritized, the input probability of each node is \num{1} at one state and \num{0} at the others, which coincides with discretized \gls{ris}; 3) when backscatter link is absolutely prioritized, UniScatter nodes can exploit adaptive channel coding to achieve higher instantaneous rate than uncoded equiprobable inputs of \gls{bc}/\gls{sr}; 4) the proposed \gls{kkt} input distribution design converges to stationary points, whose average performance is very close to global optimal; 5) the \gls{pgd} beamforming achieves larger rate region than conventional \gls{mrt}; 6) the decision region schemes adapted to input distribution provide higher backscatter rates than the non-adaptive \gls{ml} detector; 7) cooperation between passive nodes in terms of joint encoding can further boost the total backscatter rate; 8) the low complexity of input distribution design and the marginal effect of increasing reflection states motivates the use of low-order scatter nodes to replace high-resolution \gls{ris}.
+	It is concluded that 1) UniScatter nodes provide flexible transmit-assist tradeoff using adaptive input distribution design; 2) when primary link is absolutely prioritized, the input probability of each node is \num{1} at one state and \num{0} at the others, which coincides with discretized \gls{ris}; 3) when backscatter link is absolutely prioritized, UniScatter nodes can exploit adaptive channel coding to achieve higher instantaneous rate than uncoded equiprobable inputs of \gls{bc}/\gls{sr}; 4) the proposed \gls{kkt} input distribution design converges to stationary points, whose average performance is very close to global optimal; 5) the proposed \gls{pgd} beamforming achieves larger rate region than \gls{mrt} to ergodic primary equivalent channel; 6) the decision region schemes adapted to input distribution provide higher backscatter rates than the non-adaptive \gls{ml} detector; 7) cooperation between passive nodes in terms of joint encoding can further boost the total backscatter rate; 8) the low complexity of input distribution design and the marginal effect of increasing reflection states motivates the use of low-order scatter nodes to replace high-resolution \gls{ris}.
 
@@
 		Those facts imply \emph{backscatter detection} under primary uncertainty can be viewed as part of \emph{primary channel training}.
-		Hence, we propose a practical UniScatter receiver that semi-coherently decodes UniScatter nodes from the received energy per backscatter block, re-encodes for their reflection patterns, retrieves equivalent primary channel as if dynamic passive beamforming, then coherently decodes the primary link under the enhanced multipath.
+		Hence, we propose a practical UniScatter receiver that semi-coherently decodes UniScatter nodes from the received energy per backscatter block, re-encodes for their reflection patterns, retrieves primary equivalent channel as if dynamic passive beamforming, then coherently decodes the primary link under the enhanced multipath.
 		\begin{figure}[!t]
@@
 		Without loss of generality, we consider one specific backscatter block (i.e., $N$ primary blocks) in the following context.
-		Due to double modulation, the equivalent primary channel is a function of \emph{coded} backscatter symbols
+		Due to double modulation, the primary equivalent channel is a function of \emph{coded} backscatter symbols
 		% \begin{subequations}
@@
 		\end{equation}
-		Once backscatter messages of all nodes are successfully decoded, we can re-code for backscatter symbol tuple $x_{\mathcal{K}}$, recover their reflection patterns by \eqref{eq:backscatter_modulation}, and retrieve the equivalent primary channel by \eqref{eq:equivalent_channel}.
+		Once backscatter messages of all nodes are successfully decoded, we can re-code for backscatter symbol tuple $x_{\mathcal{K}}$, recover their reflection patterns by \eqref{eq:backscatter_modulation}, and retrieve the primary equivalent channel by \eqref{eq:equivalent_channel}.
 		Moreover, we define the primary information function conditioned on backscatter symbol tuple $x_{m_{\mathcal{K}}}$ as
@@
 \begin{section}{Simulation Results}
-	% TODO compare PGD and primary-MRT beamformers
 	In this section, we provide numerical results to evaluate the proposed input distribution, active beamforming, and backscatter decision design for the UniScatter system in Fig.
@@
 		For $\rho=0$ where backscatter performance is absolutely prioritized, the \gls{csi}-adaptive channel coding at the UniScatter node provides higher backscatter rate than conventional \gls{bc} and \gls{sr} nodes with uncoded equiprobable inputs.
-		On the other hand, for $\rho=1$ where primary performance is absolutely prioritized, the input probability is \num{1} at the state that maximizes the equivalent primary channel strength, and \num{0} at the others.
+		On the other hand, for $\rho=1$ where primary performance is absolutely prioritized, the input probability is \num{1} at the state that maximizes the primary equivalent channel strength, and \num{0} at the others.
 		In this case, the reflection pattern over time is fully deterministic, and the UniScatter node indeed boils down to a \gls{ris} element with discrete phase shifts.
-		These observations meet our expectation that UniScatter nodes include scattering sources of \gls{bc}/\gls{sr} and reflecting elements of \gls{ris} as special cases, and generalize backscatter modulation and passive beamforming from the perspective of input distribution design.
+		Those observations meet our expectation that UniScatter nodes include scattering sources of \gls{bc}/\gls{sr} and reflecting elements of \gls{ris} as special cases, and generalize backscatter modulation and passive beamforming from the perspective of input distribution design.
 	\end{subsection}
@@
 	\begin{subsection}{Backscatter Rate versus Output Discretization Bit}
-		Since the transformation from problem \eqref{op:decision_threshold} to \eqref{op:decision_threshold_discrete} introduces performance degradation, we investigate the impact of threshold domain discretization on the total backscatter rate.
+		Since the transformation from problem \eqref{op:decision_threshold} to \eqref{op:decision_threshold_discrete} introduces performance degradation, we now investigate the impact of threshold domain discretization on the total backscatter rate.
 
@@
 		For the \gls{bcd} algorithm considered in the rest of this paper, we choose the \gls{kkt} input distribution by Algorithm \ref{al:input_distribution}, the \gls{pgd} active beamforming by Algorithm \ref{al:active_beamforming}, and the \gls{smawk} decision threshold by \cite{He2021} as reference.
-		The impact of different component schemes are explored below.
+		The impacts of different schemes are explored below.
 
 		\begin{subsubsection}{Input Distribution}
-			We compare the following input distribution schemes for problem \eqref{op:input_distribution}:
+			We compare the following input distribution designs for problem \eqref{op:input_distribution}:
 			\begin{itemize}
 				\item \emph{Exhaustion:} Exhaustive grid search over the probability $K$-simplex with resolution $\Delta p = \num{1e-3}$;
-				% \item \emph{\gls{kkt}:} Numerical evaluation of the \gls{kkt} solutions by Algorithm \ref{al:input_distribution};
 				\item \emph{\gls{kkt}:} Numerical \gls{kkt} solution evaluation by Algorithm \ref{al:input_distribution};
@@
 
-			Since \emph{Cooperation} involves full transmit cooperation of all nodes, we also propose the following recovery methods from the joint probability array for independent backscatter encoding:
+			Since \emph{Cooperation} involves full transmit cooperation of all nodes, to support independent backscatter encoding, we also propose the following methods to recover individual input distributions from the joint probability array:
 			\begin{itemize}
@@
 				\item \emph{Decomposition:} Normalized rank-\num{1} \gls{cp} decomposition tensors;
-				\item \emph{Randomization:} Random search with correlation matrix guidance \cite{Calvo2010}.
+				\item \emph{Randomization:} Random search guided with correlation matrix \cite{Calvo2010}.
 			\end{itemize}
@@
 			Fig. \subref*{fi:region_distribution} shows the achievable rate regions for those input distribution schemes.
-			We observe that \emph{Cooperation} provides the outer bound for all achievable rate regions.
-			Although transmit cooperation between UniScatter nodes can be generally helpful, it requires joint encoding with arbitrarily dependent codewords, which introduces extra coordination burden and may be unaffordable for a large $K$.
+			We observe that \emph{Cooperation} provides the outer bound for all achievable rate regions, which suggests transmit cooperation between UniScatter nodes can be generally helpful.
+			However, it requires joint encoding with arbitrarily dependent codewords, and the extra coordination burden may be unaffordable for a large $K$.
 			We also notice the average performance of \emph{\gls{kkt}} input distribution design by Algorithm \ref{al:input_distribution} is extremely close to that of \emph{Exhaustion}, and the loss is indistinguishable for $K=2$.
-			This verified our claim in Remark \ref{re:input_kkt_distribution}.
-			Despite \emph{Randomization} yields a similar result, the computational complexity is much higher (loops over $K+1$ linear programming problems) and the performance is backed by numerous random instances.
+			This verified our claim in Remark \ref{re:input_kkt_distribution} that the average performance of \gls{kkt} solutions can be reasonably good for a moderate $K$.
+			Despite \emph{Randomization} yields a similar result, the computational complexity is much higher (loops over $K+1$ linear programming problems) and the performance is backed by numerous randomly generated instances.
 			In contrast, the low-complexity \emph{Marginalization} returns a comparable result and the rate loss is insignificant when $K$ is small.
 			Finally, \emph{Decomposition} suffers from much lower average total backscatter rate, as the rank-\num{1} \gls{cp} approximation can be inaccurate for some channel-drop realizations.
+			Those observations demonstrated the performance and complexity advantages of the proposed \gls{kkt} input distribution design, and reveals the potential of joint encoding at UniScatter nodes.
 		\end{subsubsection}
@@
 		\begin{subsubsection}{Active Beamforming}
-			% It is concluded that 1) UniScatter nodes provide flexible transmit-assist tradeoff using adaptive input distribution design; 2) when primary link is absolutely prioritized, the input probability of each node is \num{1} at one state and \num{0} at the others, which coincides with discretized \gls{ris}; 3) when backscatter link is absolutely prioritized, UniScatter nodes can exploit adaptive channel coding to achieve higher instantaneous rate than uncoded equiprobable inputs of \gls{bc}/\gls{sr}; 4) the proposed \gls{kkt} input distribution design converges to stationary points, whose average performance is very close to global optimal; 5) the \gls{pgd} beamforming achieves larger rate region than conventional \gls{mrt}; 6) the decision region schemes adapted to input distribution provide higher backscatter rates than the non-adaptive \gls{ml} detector; 7) cooperation between passive nodes in terms of joint encoding can further boost the total backscatter rate; 8) the low complexity of input distribution design and the marginal effect of increasing reflection states motivates the use of low-order scatter nodes to replace high-resolution \gls{ris}.
+			% It is concluded that 1) UniScatter nodes provide flexible transmit-assist tradeoff using adaptive input distribution design; 2) when primary link is absolutely prioritized, the input probability of each node is \num{1} at one state and \num{0} at the others, which coincides with discretized \gls{ris}; 3) when backscatter link is absolutely prioritized, UniScatter nodes can exploit adaptive channel coding to achieve higher instantaneous rate than uncoded equiprobable inputs of \gls{bc}/\gls{sr}; 4) the proposed \gls{kkt} input distribution design converges to stationary points, whose average performance is very close to global optimal; 5) the proposed \gls{pgd} beamforming achieves larger rate region than \gls{mrt} to ergodic primary equivalent channel; 6) the decision region schemes adapted to input distribution provide higher backscatter rates than the non-adaptive \gls{ml} detector; 7) cooperation between passive nodes in terms of joint encoding can further boost the total backscatter rate; 8) the low complexity of input distribution design and the marginal effect of increasing reflection states motivates the use of low-order scatter nodes to replace high-resolution \gls{ris}.
 			We compare the following active beamforming schemes for problem \eqref{op:active_beamforming}:
@@
 				\item \emph{\gls{pgd}:} Iterative \gls{pgd} optimization by Algorithm \ref{al:active_beamforming};
-				\item \emph{MRT:} Maximum ratio transmission to ergodic equivalent primary channel $\sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) \boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}})$.
+				\item \emph{\gls{mrt}:} Maximum ratio transmission to the ergodic primary equivalent channel $\sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) \boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}})$.
 			\end{itemize}
 
-			Fig. \subref*{fi:region_beamforming} reveals the achievable regions for those active beamforming schemes.
-
+			Fig. \subref*{fi:region_beamforming} plots the achievable regions for both active beamforming schemes.
+			In the low-$\rho$ regime, we observe the proposed \emph{\gls{pgd}} design by Algorithm \ref{al:active_beamforming} outperforms \emph{\gls{mrt}} in terms of backscatter rate.
+			This is because the performance of energy detection depends on the \emph{difference} of received variances under different backscatter symbol tuples.
+			Such a diversity of variance is not fully exploited by \emph{\gls{mrt}} that simply maximizes the ergodic \gls{snr}, but can be properly controlled by \emph{\gls{pgd}} to further boost the total backscatter rate.
+			As $\rho$ further increases, the input distribution becomes more biased to one state, and the primary equivalent \gls{snr} outweighs the backscatter variance difference in the weighted sum-rate expression \eqref{eq:weighted_sum_mutual_information_explicit}.
+			Therefore, the result of \emph{\gls{pgd}} approaches that of \emph{\gls{mrt}}.
+			For the extreme case $\rho=1$, the UniScatter nodes reduce to \gls{ris} elements and both active beamforming schemes boil down to \gls{mrt} to the deterministic primary equivalent channel.
+			Therefore, we conclude the proposed \emph{\gls{pgd}} active beamforming design by Algorithm \ref{al:active_beamforming} is more powerful than ergodic \emph{\gls{mrt}}.
 		\end{subsubsection}

### 2022-08-23 assets/illustration/discrete_outputs.tex

\begin{tikzpicture}
	\begin{axis}[width=8cm,height=4cm,xmin=0,xmax=6.5,xlabel=$z$,axis x line=middle,axis y line=none,xtick={0,2,3,4,6},xticklabels={$t_0$,$t_1$,$t_2$,$t_3$,$t_4$},xtick style={draw=none},every axis x label/.style={at=(current axis.right of origin),anchor=west},domain=0:6]
		\addplot[mark=*,mark size=1pt,only marks,color=gray] {0};
		\addplot[mark=*,mark size=1pt,only marks,color=black] coordinates{(0,0) (2,0) (3,0) (4,0) (6,0)};
		\draw[color=black,dashed] (0,0) -- (0,0.6);
		\draw[color=black,dashed] (2,0) -- (2,0.6);
		\draw[color=black,dashed] (3,0) -- (3,0.6);
		\draw[color=black,dashed] (4,0) -- (4,0.6);
		\draw[color=black,dashed] (6,0) -- (6,0.6);
		\draw[latex-latex] (0,0.6) -- (2,0.6) node[below,midway]{$\mathcal{R}_1$};
		\draw[latex-latex] (2,0.6) -- (3,0.6) node[below,midway]{$\mathcal{R}_2$};
		\draw[latex-latex] (3,0.6) -- (4,0.6) node[below,midway]{$\mathcal{R}_3$};
		\draw[latex-latex] (4,0.6) -- (6,0.6) node[below,midway]{$\mathcal{R}_4$};
	\end{axis}
\end{tikzpicture}

### 2022-08-23 main.tex
:pencil: Discuss decison threshold

@@
 \newacronym{dmtmac}{DMTMAC}{Discrete Memoryless Thresholding Multiple Access Channel}
-% \newacronym{dtmac}{DTMAC}{Discrete Thresholding Multiple Access Channel}
 \newacronym{dp}{DP}{Dynamic Programming}
@@
 \newacronym{mrt}{MRT}{Maximum Ratio Transmission}
+% \newacronym{emrt}{EMRT}{ergodic \gls{mrt}}
 \newacronym{noma}{NOMA}{Non-Orthogonal Multiple Access}
@@
 	\emph{Fifth,} we provide numerical results to demonstrate the benefits of UniScatter and proposed algorithms.
-	It is concluded that 1) UniScatter nodes provide flexible transmit-assist tradeoff using adaptive input distribution design; 2) when primary link is absolutely prioritized, the input probability of each node is \num{1} at one state and \num{0} at the others, which coincides with discretized \gls{ris}; 3) when backscatter link is absolutely prioritized, UniScatter nodes can exploit adaptive channel coding to achieve higher instantaneous rate than uncoded equiprobable inputs of \gls{bc}/\gls{sr}; 4) the proposed \gls{kkt} input distribution design converges to stationary points, whose average performance is very close to global optimal; 5) the proposed \gls{pgd} beamforming achieves larger rate region than \gls{mrt} to ergodic primary equivalent channel; 6) the decision region schemes adapted to input distribution provide higher backscatter rates than the non-adaptive \gls{ml} detector; 7) cooperation between passive nodes in terms of joint encoding can further boost the total backscatter rate; 8) the low complexity of input distribution design and the marginal effect of increasing reflection states motivates the use of low-order scatter nodes to replace high-resolution \gls{ris}.
+	It is concluded that 1) UniScatter nodes provide flexible transmit-assist tradeoff using adaptive input distribution design; 2) when primary link is absolutely prioritized, the input probability of each node is \num{1} at one state and \num{0} at the others, which coincides with discretized \gls{ris}; 3) when backscatter link is absolutely prioritized, UniScatter nodes can exploit adaptive channel coding to achieve higher instantaneous rate than uncoded equiprobable inputs of \gls{bc}/\gls{sr}; 4) the proposed \gls{kkt} input distribution design converges to stationary points, whose average performance is very close to global optimal; 5) the proposed \gls{pgd} beamforming provides larger rate region than \gls{mrt}-based schemes; 6) the decision region schemes adapted to input distribution provide higher backscatter rates than the non-adaptive \gls{ml} detector; 7) cooperation between passive nodes in terms of joint encoding can further boost the total backscatter rate; 8) the low complexity of input distribution design and the marginal effect of increasing reflection states motivates the use of low-order scatter nodes to replace high-resolution \gls{ris}.
 
@@
 		gradually progresses from slightly skewed to completely biased.
-		For $\rho=0$ where backscatter performance is absolutely prioritized, the \gls{csi}-adaptive channel coding at the UniScatter node provides higher backscatter rate than conventional \gls{bc} and \gls{sr} nodes with uncoded equiprobable inputs.
+		For $\rho=0$ where backscatter performance is absolutely prioritized, the \gls{csi}-adaptive channel coding at the UniScatter node provides higher backscatter rate than conventional \gls{bc} and \gls{sr} nodes with uncoded equiprobable inputs, and some states may end up unused since they cannot produce enough energy difference over the existing alphabet.
 		On the other hand, for $\rho=1$ where primary performance is absolutely prioritized, the input probability is \num{1} at the state that maximizes the primary equivalent channel strength, and \num{0} at the others.
@@
 
-	\begin{subsection}{Rate Region under Different Schemes}
+	\begin{subsection}{Rate Region of Different Schemes}
 		\begin{figure}[!t]
@@
 			Finally, \emph{Decomposition} suffers from much lower average total backscatter rate, as the rank-\num{1} \gls{cp} approximation can be inaccurate for some channel-drop realizations.
-			Those observations demonstrated the performance and complexity advantages of the proposed \gls{kkt} input distribution design, and reveals the potential of joint encoding at UniScatter nodes.
+			% Those observations demonstrate the performance and complexity advantages of the proposed \gls{kkt} input distribution design, and reveal the potential of joint encoding at UniScatter nodes.
+			Those observations demonstrate the high performance and low complexity of the proposed \gls{kkt} input distribution design, and reveal the potential of joint encoding at UniScatter nodes.
 		\end{subsubsection}
@@
 		\begin{subsubsection}{Active Beamforming}
-			% It is concluded that 1) UniScatter nodes provide flexible transmit-assist tradeoff using adaptive input distribution design; 2) when primary link is absolutely prioritized, the input probability of each node is \num{1} at one state and \num{0} at the others, which coincides with discretized \gls{ris}; 3) when backscatter link is absolutely prioritized, UniScatter nodes can exploit adaptive channel coding to achieve higher instantaneous rate than uncoded equiprobable inputs of \gls{bc}/\gls{sr}; 4) the proposed \gls{kkt} input distribution design converges to stationary points, whose average performance is very close to global optimal; 5) the proposed \gls{pgd} beamforming achieves larger rate region than \gls{mrt} to ergodic primary equivalent channel; 6) the decision region schemes adapted to input distribution provide higher backscatter rates than the non-adaptive \gls{ml} detector; 7) cooperation between passive nodes in terms of joint encoding can further boost the total backscatter rate; 8) the low complexity of input distribution design and the marginal effect of increasing reflection states motivates the use of low-order scatter nodes to replace high-resolution \gls{ris}.
+			% It is concluded that 1) UniScatter nodes provide flexible transmit-assist tradeoff using adaptive input distribution design; 2) when primary link is absolutely prioritized, the input probability of each node is \num{1} at one state and \num{0} at the others, which coincides with discretized \gls{ris}; 3) when backscatter link is absolutely prioritized, UniScatter nodes can exploit adaptive channel coding to achieve higher instantaneous rate than uncoded equiprobable inputs of \gls{bc}/\gls{sr}; 4) the proposed \gls{kkt} input distribution design converges to stationary points, whose average performance is very close to global optimal; 5) the proposed \gls{pgd} beamforming provides larger rate region than \gls{mrt}-based schemes; 6) the decision region schemes adapted to input distribution provide higher backscatter rates than the non-adaptive \gls{ml} detector; 7) cooperation between passive nodes in terms of joint encoding can further boost the total backscatter rate; 8) the low complexity of input distribution design and the marginal effect of increasing reflection states motivates the use of low-order scatter nodes to replace high-resolution \gls{ris}.
 			We compare the following active beamforming schemes for problem \eqref{op:active_beamforming}:
@@
 				\item \emph{\gls{pgd}:} Iterative \gls{pgd} optimization by Algorithm \ref{al:active_beamforming};
-				\item \emph{\gls{mrt}:} Maximum ratio transmission to the ergodic primary equivalent channel $\sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) \boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}})$.
+				\item \emph{E-\gls{mrt}:} \gls{mrt} towards the ergodic primary equivalent channel $\sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) \boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}})$;
+				\item \emph{D-\gls{mrt}:} \gls{mrt} towards the direct channel $\boldsymbol{h}_{\mathrm{D}}^H$.
 			\end{itemize}
 
-			Fig. \subref*{fi:region_beamforming} plots the achievable regions for both active beamforming schemes.
-			In the low-$\rho$ regime, we observe the proposed \emph{\gls{pgd}} design by Algorithm \ref{al:active_beamforming} outperforms \emph{\gls{mrt}} in terms of backscatter rate.
-			This is because the performance of energy detection depends on the \emph{difference} of received variances under different backscatter symbol tuples.
-			Such a diversity of variance is not fully exploited by \emph{\gls{mrt}} that simply maximizes the ergodic \gls{snr}, but can be properly controlled by \emph{\gls{pgd}} to further boost the total backscatter rate.
-			As $\rho$ further increases, the input distribution becomes more biased to one state, and the primary equivalent \gls{snr} outweighs the backscatter variance difference in the weighted sum-rate expression \eqref{eq:weighted_sum_mutual_information_explicit}.
-			Therefore, the result of \emph{\gls{pgd}} approaches that of \emph{\gls{mrt}}.
-			For the extreme case $\rho=1$, the UniScatter nodes reduce to \gls{ris} elements and both active beamforming schemes boil down to \gls{mrt} to the deterministic primary equivalent channel.
-			Therefore, we conclude the proposed \emph{\gls{pgd}} active beamforming design by Algorithm \ref{al:active_beamforming} is more powerful than ergodic \emph{\gls{mrt}}.
+			Fig. \subref*{fi:region_beamforming} plots the achievable rate regions for those active beamforming schemes.
+			In the low-$\rho$ regime, we observe the proposed \emph{\gls{pgd}} design by Algorithm \ref{al:active_beamforming} outperforms \emph{E-\gls{mrt}} and \emph{D-\gls{mrt}} in terms of backscatter rate.
+			This is because backscatter decoding relies on the \emph{difference} of received energy expectations under different backscatter symbol tuples.
+			Such an energy diversity is not fully exploited by simply maximizing the direct/ergodic equivalent \gls{snr}, but can be properly controlled by \emph{\gls{pgd}} for enhanced detection performance.
+			As $\rho$ further increases, the primary equivalent \gls{snr} outweighs the backscatter energy difference in the weighted sum-rate expression \eqref{eq:weighted_sum_mutual_information_explicit}, and the input distribution is gradually biased to the state that roughly align direct and scattered components.
+			Therefore, the advantages of distribution-adaptive schemes \emph{\gls{pgd}} and \emph{E-\gls{mrt}} become marginal, the ergodic equivalent and direct channels are closer in direction, and the bounds of all schemes approach each other.
+			For the extreme case $\rho=1$, both distribution-adaptive schemes boil down to \gls{mrt} towards the deterministic primary equivalent channel, as considered in \gls{ris} literatures.
+			Those observations prove the proposed \emph{\gls{pgd}} active beamforming design can balance the primary equivalent \gls{snr} and backscatter energy diversity for enlarged rate regions.
 		\end{subsubsection}
@@
 				\item \emph{\gls{dp}:} Benchmark \gls{dp} method for sequential quantizer \cite{He2021};
-				\item \emph{\gls{smawk}:} \gls{dp} accelerated by the \gls{smawk} algorithm \cite{He2021};
+				\item \emph{\gls{smawk}:} \emph{\gls{dp}} accelerated by the \gls{smawk} algorithm \cite{He2021};
 				\item \emph{Bisection:} The traverse-then-bisect algorithm \cite{Nguyen2020a};
@@
 			Fig. \subref*{fi:region_threshold} presents the achievable rate region for those decision threshold schemes.
-			We observe that input distribution-adaptive threshold designs achieve higher total backscatter rate than \gls{ml}.
-			This is because the decision regions can be flexibly adjusted to enhance the capacity of \gls{dmtmac} \eqref{eq:dmtmac}.
-			For example, the tuples with negligible input probability should have narrower decision regions than those frequently employed, in order to improve detection performance.
-			It emphasizes the importance of joint input distribution and decision region design.
+			We observe that the distribution-adaptive schemes \emph{\gls{dp}}, \emph{\gls{smawk}} and \emph{Bisection} achieve higher total backscatter rate than the non-adaptive \emph{\gls{ml}}.
+			This is because the total backscatter mutual information \eqref{eq:backscatter_mutual_information} is a function of both input distribution and decision regions, and the rate-optimal threshold design depends heavily on input distribution.
+			For example, the backscatter symbol tuples with zero input probability should never be detected and use empty decision regions, in order to increase the success detection chance of other tuples.
+			Those observations highlight the importance of joint input distribution and decision threshold design.
 		\end{subsubsection}
@@
 \begin{section}{Conclusion}
+	% TODO  binary input and signal output (BISO) channel, ML figure
 	This paper introduced UniScatter that adapts input distribution of passive backscatter nodes to simultaneously transmit and assist over existing wireless systems.

### 2022-08-24 main.tex
:construction: Update figures

@@
 			}
-			\caption{Typical instances of node input distribution under different weights.}
+			\caption{Typical instances of node input distribution for different weights.}
 			\label{fi:distribution_weights}
@@
 		Those observations meet our expectation that UniScatter nodes include scattering sources of \gls{bc}/\gls{sr} and reflecting elements of \gls{ris} as special cases, and generalize backscatter modulation and passive beamforming from the perspective of input distribution design.
-	\end{subsection}
-
-	\begin{subsection}{Backscatter Rate versus Output Discretization Bit}
+		For the \gls{bcd} algorithm, we choose the \gls{kkt} input distribution by Algorithm \ref{al:input_distribution}, the \gls{pgd} active beamforming by Algorithm \ref{al:active_beamforming}, and the \gls{smawk} decision threshold by \cite{He2021} as reference.
+	\end{subsection}
+
+	\begin{subsection}{Backscatter Rate versus Energy Discretization Bits}
+		\begin{figure}[!t]
+			\subfloat[Instance 1\label{fi:rate_bits_primary}]{
+				\resizebox{0.48\columnwidth}{!}{
+					\input{assets/simulation/rate_bits_primary.tex}
+				}
+			}
+			\subfloat[Instance 2\label{fi:rate_bits_backscatter}]{
+				\resizebox{0.48\columnwidth}{!}{
+					\input{assets/simulation/rate_bits_backscatter.tex}
+				}
+			}
+			\caption{Average achievable primary and total backscatter rates for different energy discretization bits.}
+			\label{fi:rate_bits}
+		\end{figure}
 		Since the transformation from problem \eqref{op:decision_threshold} to \eqref{op:decision_threshold_discrete} introduces performance degradation, we now investigate the impact of threshold domain discretization on the total backscatter rate.
@@
 
-	\begin{subsection}{Rate Region of Different Schemes}
+	\begin{subsection}{Rate Region by Different Schemes}
 		\begin{figure}[!t]
@@
 		\end{figure}
-		For the \gls{bcd} algorithm considered in the rest of this paper, we choose the \gls{kkt} input distribution by Algorithm \ref{al:input_distribution}, the \gls{pgd} active beamforming by Algorithm \ref{al:active_beamforming}, and the \gls{smawk} decision threshold by \cite{He2021} as reference.
-		The impacts of different schemes are explored below.
+		The impacts of different input distribution, active beamforming, and decision threshold schemes on the average primary-backscatter rate region are explored in this study.
 
@@
 
-	\begin{subsection}{Rate Region vs. System Configuration}
+	\begin{subsection}{Rate Region versus Configuration}
 		\begin{figure}[!t]
 			\centering
-			\subfloat[Metscatter Nodes\label{fi:region_tags}]{
+			\subfloat[Nodes\label{fi:region_tags}]{
 				\resizebox{0.48\columnwidth}{!}{
@@
 			}
-			\subfloat[Scatter Ratio\label{fi:region_scatter}]{
-				\resizebox{0.48\columnwidth}{!}{
-					\input{assets/simulation/region_scatter.tex}
-				}
-			}
-			\caption{Average primary-total-backscatter rate regions.}
-			\label{fi:region_config_1}
+			\subfloat[Symbol Period Ratio\label{fi:region_duration}]{
+				\resizebox{0.48\columnwidth}{!}{
+					\input{assets/simulation/region_duration.tex}
+				}
+			}
+			\\
+			\subfloat[Average Noise Power\label{fi:region_noise}]{
+				\resizebox{0.48\columnwidth}{!}{
+					\input{assets/simulation/region_noise.tex}
+				}
+			}
+			\subfloat[Coverage Radius\label{fi:region_coverage}]{
+				\resizebox{0.48\columnwidth}{!}{
+					\input{assets/simulation/region_coverage.tex}
+				}
+			}
+			\caption{
+				Average primary-total-backscatter rate regions for different system configurations.
+				``PSP'' means primary symbol period.
+			}
+			\label{fi:region_config}
 		\end{figure}
 
-		% Fig. \ref{fi:region_config_1} reveals the impact of UniScatter nodes, input states, transmit antennas and scatter ratio on the achievable rate region.
-		We present in \ref{fi:region_config_1} the impact of UniScatter nodes, input states, transmit antennas and scatter ratio on the achievable rate region.
-		For the specified scenario, Fig.
+		% % Fig. \ref{fi:region_config_1} reveals the impact of UniScatter nodes, input states, transmit antennas and scatter ratio on the achievable rate region.
+		% We present in \ref{fi:region_config_1} the impact of UniScatter nodes, input states, transmit antennas and scatter ratio on the achievable rate region.
+		% For the specified scenario, Fig.
 \subref*{fi:region_tags} shows the total backscatter rate almost scales proportionally with the number of UniScatter nodes, and the decrease of individual backscatter rate is unobvious.
-		Besides, we conclude from \subref*{fi:region_states} that increasing the reflection states has a marginal effect on both primary and backscatter rates.
-		Those two facts motivates the use of numerous elementary/uncomplicated backscatter nodes, instead of high-order transponders or programmable high-resolution surfaces.
-		Figs. \subref*{fi:region_txs} and \subref*{fi:region_scatter} also prove increasing transmit antennas or scatter ratio can improve both primary and backscatter performance.
-
-		\begin{figure}[!t]
-			\centering
-			\subfloat[Node Coverage\label{fi:region_coverage}]{
-				\resizebox{0.48\columnwidth}{!}{
-					\input{assets/simulation/region_coverage.tex}
-				}
-			}
-			\subfloat[Symbol Period Ratio\label{fi:region_duration}]{
-				\resizebox{0.48\columnwidth}{!}{
-					\input{assets/simulation/region_duration.tex}
-				}
-			}
-			\\
-			\subfloat[Carrier Frequency\label{fi:region_frequency}]{
-				\resizebox{0.48\columnwidth}{!}{
-					\input{assets/simulation/region_frequency.tex}
-				}
-			}
-			\subfloat[Average Noise Power\label{fi:region_noise}]{
-				\resizebox{0.48\columnwidth}{!}{
-					\input{assets/simulation/region_noise.tex}
-				}
-			}
-			\caption{Average primary-total-backscatter rate regions.}
-			\label{fi:region_config_2}
-		\end{figure}
-
-		Fig. \subref*{fi:region_coverage} shows the tradeoff between coverage disk radius $r$ and achievable rate region.
-		When nodes are far from the user, both primary and backscatter rates decrease due to the product pass loss of forward and backward channels.
-		Under the assumption of ideal backscatter decoding and re-encoding, Fig.
+		% Besides, we conclude from \subref*{fi:region_states} that increasing the reflection states has a marginal effect on both primary and backscatter rates.
+		% Those two facts motivates the use of numerous elementary/uncomplicated backscatter nodes, instead of high-order transponders or programmable high-resolution surfaces.
+		% Figs. \subref*{fi:region_txs} and \subref*{fi:region_scatter} also prove increasing transmit antennas or scatter ratio can improve both primary and backscatter performance.
+
+		% Fig. \subref*{fi:region_coverage} shows the tradeoff between coverage disk radius $r$ and achievable rate region.
+		% When nodes are far from the user, both primary and backscatter rates decrease due to the product pass loss of forward and backward channels.
+		% Under the assumption of ideal backscatter decoding and re-encoding, Fig.
 \subref*{fi:region_duration} suggests using lower symbol period ratio $N$ can boost total backscatter rate per primary symbol.
-		However, it requires more frequent detection and re-encoding at the user to maintain the primary rate.
-		When $N$ becomes sufficiently large, total backscatter rate approaches \num{0} and UniScatter nodes boil down to conventional \gls{ris} elements with fixed reflection pattern during whole channel block.
-		In Fig. \subref*{fi:region_frequency}, we observe that passive UniScatter nodes achieve higher backscatter rate at lower carrier frequency because of preferable propagation loss.
-		Finally, \subref*{fi:region_noise} prove the performance of energy detection is robust for a wide range of noise power.
+		% However, it requires more frequent detection and re-encoding at the user to maintain the primary rate.
+		% When $N$ becomes sufficiently large, total backscatter rate approaches \num{0} and UniScatter nodes boil down to conventional \gls{ris} elements with fixed reflection pattern during whole channel block.
+		% In Fig. \subref*{fi:region_frequency}, we observe that passive UniScatter nodes achieve higher backscatter rate at lower carrier frequency because of preferable propagation loss.
+		% Finally, \subref*{fi:region_noise} prove the performance of energy detection is robust for a wide range of noise power.
 	\end{subsection}

### 2022-08-25 main.tex
:pencil: Update results and conclusion

@@
 \newacronym{mrt}{MRT}{Maximum Ratio Transmission}
-% \newacronym{emrt}{EMRT}{ergodic \gls{mrt}}
 \newacronym{noma}{NOMA}{Non-Orthogonal Multiple Access}
@@
 	The former is impractical for passive backscatter devices, while the latter does not fully exploit reflection pattern and \gls{csi}.
-	In this paper, we introduce UniScatter that generalizes \gls{bc}, \gls{sr}, and \gls{ris} to manipulate the transmit-assist tradeoff via smart input distribution and backscatter detector design.
+	In this paper, we introduce UniScatter that generalizes \gls{bc}, \gls{sr}, and \gls{ris} to manipulate the transmit-assist tradeoff via smart input distribution and practical receiver design.
 	The contributions of this paper are summarized as follows.
@@
 	Scattering source of \gls{bc}/\gls{sr} and reflecting element of \gls{ris} can be regarded as its extreme cases, where the input distribution boils down to equiprobable and degenerate, respectively.
-	Like aforementioned \gls{ris}-empowered \gls{bc}/\gls{sr} schemes, the passive nodes require regular coordination with active devices, but the advantages are 1) UniScatter nodes can be built over conventional load-switching scatterers instead of composite metamaterial; 2) the optimization cost of input distribution is much lower than that of \gls{ris} reflection coefficients; 3) adaptive backscatter channel coding can exploit \gls{csi} to achieve higher instantaneous rate than conventional uncoded transmission; 4) the physically distributed characteristics of UniScatter nodes and legacy users avoids the development optimization and allows uniformly good performance for both links.
+	Like aforementioned \gls{ris}-empowered \gls{bc}/\gls{sr} schemes, the passive nodes require regular coordination with active devices, but the advantages are 1) UniScatter nodes can be built over conventional load-switching scatterers instead of composite metamaterial; 2) the optimization cost of input distribution is much lower than that of \gls{ris} reflection coefficients; 3) adaptive backscatter channel coding can exploit \gls{csi} to achieve higher instantaneous rate than conventional uncoded transmission; 4) the dispersed characteristics of UniScatter nodes and legacy users avoids the development optimization and allows uniformly good performance for both links.
 
@@
 \begin{section}{UniScatter}
-	Using shared spectrum, energy and infrastructures, UniScatter is a novel passive communication/assistance protocol that generalizes \gls{bc}, \gls{sr} and \gls{ris} in a \emph{physically} and \emph{probabilistically} distributed manner.
+	Using shared spectrum, energy and infrastructures, UniScatter is a novel passive communication/assistance protocol that generalizes \gls{bc}, \gls{sr} and \gls{ris} in a \emph{geographically} and \emph{probabilistically} distributed manner.
 	In particular, passive UniScatter nodes located at different places ride over an active legacy transmission in a flexible and mutualistic manner, while practical UniScatter receiver cooperatively decodes both primary and backscatter links under the benefits of backscatter modulation and passive beamforming.
@@
 		Such an adaptive backscatter channel coding coincides with \gls{ris} when primary link is absolutely prioritized, and outperforms the uncoded equiprobable inputs of \gls{bc}/\gls{sr} when backscatter link is absolutely prioritized.
-		Besides, the physically distributed characteristics of UniScatter nodes and legacy users avoids the development optimization and allows uniformly good performance for both links.
+		Besides, the dispersed characteristics of UniScatter nodes and legacy users avoids the development optimization and allows uniformly good performance for both links.
 
@@
 		Besides, relevant \gls{csi} can be acquired using either traditional sequential methods \cite{Bharadia2015,Yang2015b,Guo2019g} or the state-of-the-art parallel approach \cite{Jin2021a}.
-		In the following context, we assume perfect primary-backscatter coordination and perfect channel estimation for all links.
+		In the following context, we assume perfect primary-total-backscatter coordination and perfect channel estimation for all links.
 		\begin{figure*}[!t]
@@
 		Due to double modulation, the primary equivalent channel is a function of \emph{coded} backscatter symbols
-		% \begin{subequations}
-		% 	\label{eq:equivalent_channel}
-		% 	\begin{align}
-		% 		\boldsymbol{h}_{\mathrm{E}}^H(x_{\mathcal{K}})
-		% 		 & \triangleq \boldsymbol{h}_{\mathrm{D}}^H + \sum_{k \in \mathcal{K}} \alpha_k \boldsymbol{h}_{\mathrm{C},k}^H x_k   \\
-		% 		 & = \boldsymbol{h}_{\mathrm{D}}^H + \boldsymbol{x}^H \mathrm{diag}(\boldsymbol{\alpha}) \boldsymbol{H}_{\mathrm{C}},
-		% 	\end{align}
-		% \end{subequations}
 		\begin{equation}
@@
 		\begin{maxi!}
-			{\scriptstyle{\boldsymbol{t} \in \mathcal{T}^{L+1}}}{I(x_{\mathcal{K}})}{\label{op:decision_threshold_discrete}}{\label{ob:decision_threshold_discrete}}
+			{\scriptstyle{\boldsymbol{t} \in \mathcal{T}^{L+1}}}{I_{\mathrm{B}}(x_{\mathcal{K}};\hat{x}_{\mathcal{K}})}{\label{op:decision_threshold_discrete}}{\label{ob:decision_threshold_discrete}}
 			\addConstraint{\eqref{co:sequential_threshold},}
@@
 	We choose $\gamma_{\mathrm{D}}=2.6$, $\gamma_{\mathrm{F}}=2.4$, $\gamma_{\mathrm{B}}=2$, and $\kappa_{\mathrm{D}}=\kappa_{\mathrm{F}}=\kappa_{\mathrm{B}}=5$ for direct, forward and backward links.
-	The finite threshold domain $\mathcal{T}$ comes from $b$-bit uniform discretization over the critical interval defined by the confidence bounds of edge hypotheses (i.e., lower bound of $\mathcal{H}_1$ and upper bound of $\mathcal{H}_L$) with confidence level $1-\varepsilon$, where $b=8$ and $\varepsilon=\num{2.22e-16}$.
+	The finite threshold domain $\mathcal{T}$ comes from $b$-bit uniform discretization over the critical interval defined by the confidence bounds of edge hypotheses (i.e., lower bound of $\mathcal{H}_1$ and upper bound of $\mathcal{H}_L$) with confidence level $1-\varepsilon$, where $b=7$ and $\varepsilon=\num{1e-3}$.
 	All achievable rate curves/regions are averaged over \num{3000} realizations, and the parameters remain fixed unless otherwise specified.
@@
 		In this case, the reflection pattern over time is fully deterministic, and the UniScatter node indeed boils down to a \gls{ris} element with discrete phase shifts.
-		Those observations meet our expectation that UniScatter nodes include scattering sources of \gls{bc}/\gls{sr} and reflecting elements of \gls{ris} as special cases, and generalize backscatter modulation and passive beamforming from the perspective of input distribution design.
+		Those observations meet our s that UniScatter nodes include scattering sources of \gls{bc}/\gls{sr} and reflecting elements of \gls{ris} as special cases, and generalize backscatter modulation and passive beamforming from the perspective of input distribution design.
 		For the \gls{bcd} algorithm, we choose the \gls{kkt} input distribution by Algorithm \ref{al:input_distribution}, the \gls{pgd} active beamforming by Algorithm \ref{al:active_beamforming}, and the \gls{smawk} decision threshold by \cite{He2021} as reference.
@@
 
-	\begin{subsection}{Backscatter Rate versus Energy Discretization Bits}
+	\begin{subsection}{Achievable Rates versus Energy Discretization Bits}
 		\begin{figure}[!t]
-			\subfloat[Instance 1\label{fi:rate_bits_primary}]{
+			\subfloat[Primary Rate\label{fi:rate_bits_primary}]{
 				\resizebox{0.48\columnwidth}{!}{
@@
 			}
-			\subfloat[Instance 2\label{fi:rate_bits_backscatter}]{
+			\subfloat[Total Backscatter Rate\label{fi:rate_bits_backscatter}]{
 				\resizebox{0.48\columnwidth}{!}{
@@
 			}
-			\caption{Average achievable primary and total backscatter rates for different energy discretization bits.}
+			\caption{Average achievable primary and total backscatter rates for different energy discretization bits for $\rho=0$.}
 			\label{fi:rate_bits}
 		\end{figure}
-		Since the transformation from problem \eqref{op:decision_threshold} to \eqref{op:decision_threshold_discrete} introduces performance degradation, we now investigate the impact of threshold domain discretization on the total backscatter rate.
-
-		% TODO Total Backscatter Rate versus Output Discretization Bit
-		TODO
-
+		We now reveal how the analog-to-digital conversion of feasible threshold domain from $\mathbb{R}_+^{L+1}$ to $\mathcal{T}^{L+1}$ affects the average UniScatter performance.
+		For a fixed input distribution and active beamforming, Fig. \ref{fi:rate_bits} shows the impact of energy discretization bits $b$ on the average achievable rates when $\rho=0$.
+		We observe the primary rate is a constant for different $b$ as expected from Remark \ref{re:backscatter_decision}.
+		This conclusion holds for arbitrary $\rho$ because the randomness of reflection patterns over time can always be eliminated upon successful backscatter decoding.
+		When the nodes transmit at non-zero total rate, the user can re-encode backscatter messages to recover their reflection patterns at each primary block.
+		Otherwise, the reflection patterns of all nodes are fully deterministic, and the state index tuple can be fed back to the user together with \gls{csi}.
+		We also notice increasing $b$ boosts the total backscatter rate and the benefit becomes marginal when $b$ is sufficiently large ($2^b \gg \mathrm{card}(\mathcal{L})$).
+		This is because a larger $b$ allows the decision regions to be constructed from narrower energy bins, which mitigates the transformation loss from problem \eqref{op:decision_threshold} to \eqref{op:decision_threshold_discrete}.
+		Therefore, we conclude a proper selection of $b$ is the key to balance backscatter performance and computational complexity.
 	\end{subsection}
@@
 		\end{figure}
-		The impacts of different input distribution, active beamforming, and decision threshold schemes on the average primary-backscatter rate region are explored in this study.
+		The average achievable primary-total-backscatter rate regions of various input distribution, active beamforming, and decision threshold schemes are explored in this study.
 
@@
 			We also notice the average performance of \emph{\gls{kkt}} input distribution design by Algorithm \ref{al:input_distribution} is extremely close to that of \emph{Exhaustion}, and the loss is indistinguishable for $K=2$.
-			This verified our claim in Remark \ref{re:input_kkt_distribution} that the average performance of \gls{kkt} solutions can be reasonably good for a moderate $K$.
+			This verifies our claim in Remark \ref{re:input_kkt_distribution} that the average performance of \gls{kkt} solutions can be reasonably good for a moderate $K$.
 			Despite \emph{Randomization} yields a similar result, the computational complexity is much higher (loops over $K+1$ linear programming problems) and the performance is backed by numerous randomly generated instances.
@@
 		\begin{subsubsection}{Active Beamforming}
-			% It is concluded that 1) UniScatter nodes provide flexible transmit-assist tradeoff using adaptive input distribution design; 2) when primary link is absolutely prioritized, the input probability of each node is \num{1} at one state and \num{0} at the others, which coincides with discretized \gls{ris}; 3) when backscatter link is absolutely prioritized, UniScatter nodes can exploit adaptive channel coding to achieve higher instantaneous rate than uncoded equiprobable inputs of \gls{bc}/\gls{sr}; 4) the proposed \gls{kkt} input distribution design converges to stationary points, whose average performance is very close to global optimal; 5) the proposed \gls{pgd} beamforming provides larger rate region than \gls{mrt}-based schemes; 6) the decision region schemes adapted to input distribution provide higher backscatter rates than the non-adaptive \gls{ml} detector; 7) cooperation between passive nodes in terms of joint encoding can further boost the total backscatter rate; 8) the low complexity of input distribution design and the marginal effect of increasing reflection states motivates the use of low-order scatter nodes to replace high-resolution \gls{ris}.
 			We compare the following active beamforming schemes for problem \eqref{op:active_beamforming}:
@@
 			\centering
-			\subfloat[Nodes\label{fi:region_tags}]{
+			\subfloat[UniScatter Nodes\label{fi:region_tags}]{
 				\resizebox{0.48\columnwidth}{!}{
@@
 			}
-			\subfloat[Coverage Radius\label{fi:region_coverage}]{
+			\subfloat[Disk Radius\label{fi:region_coverage}]{
 				\resizebox{0.48\columnwidth}{!}{
@@
 		\end{figure}
-
-		% % Fig. \ref{fi:region_config_1} reveals the impact of UniScatter nodes, input states, transmit antennas and scatter ratio on the achievable rate region.
-		% We present in \ref{fi:region_config_1} the impact of UniScatter nodes, input states, transmit antennas and scatter ratio on the achievable rate region.
-		% For the specified scenario, Fig.
-\subref*{fi:region_tags} shows the total backscatter rate almost scales proportionally with the number of UniScatter nodes, and the decrease of individual backscatter rate is unobvious.
-		% Besides, we conclude from \subref*{fi:region_states} that increasing the reflection states has a marginal effect on both primary and backscatter rates.
-		% Those two facts motivates the use of numerous elementary/uncomplicated backscatter nodes, instead of high-order transponders or programmable high-resolution surfaces.
-		% Figs. \subref*{fi:region_txs} and \subref*{fi:region_scatter} also prove increasing transmit antennas or scatter ratio can improve both primary and backscatter performance.
-
-		% Fig. \subref*{fi:region_coverage} shows the tradeoff between coverage disk radius $r$ and achievable rate region.
-		% When nodes are far from the user, both primary and backscatter rates decrease due to the product pass loss of forward and backward channels.
-		% Under the assumption of ideal backscatter decoding and re-encoding, Fig.
-\subref*{fi:region_duration} suggests using lower symbol period ratio $N$ can boost total backscatter rate per primary symbol.
-		% However, it requires more frequent detection and re-encoding at the user to maintain the primary rate.
-		% When $N$ becomes sufficiently large, total backscatter rate approaches \num{0} and UniScatter nodes boil down to conventional \gls{ris} elements with fixed reflection pattern during whole channel block.
-		% In Fig. \subref*{fi:region_frequency}, we observe that passive UniScatter nodes achieve higher backscatter rate at lower carrier frequency because of preferable propagation loss.
-		% Finally, \subref*{fi:region_noise} prove the performance of energy detection is robust for a wide range of noise power.
-	\end{subsection}
+		In this study, we investigate the impact of system configuration on the average achievable rate regions.
+		\begin{subsubsection}{Number of Nodes}
+			Fig. \subref*{fi:region_tags} reveals how the number of two-state UniScatter nodes $K$ influence the primary-backscatter tradeoff.
+			We observe the total backscatter rate roughly scales proportionally with the number of nodes, and the decrease of individual rate is unobvious.
+			This demonstrates the proposed low-complexity semi-coherent energy detector performs reasonably well for a moderate $K$.
+			On the other hand, we observe adding UniScatter nodes can also boost the achievable primary rate.
+			The reason is the nodes can exploit the additional propagation path for a constructive primary signal superposition that enjoys a ``squared law'' similar to \gls{ris}.
+		\end{subsubsection}
+
+		\begin{subsubsection}{Number of States}
+			Fig. \subref*{fi:region_states} shows the relationship between available reflection states (i.e., \gls{qam} order) $M$ and achievable rate regions.
+			We notice increasing the reflection states has a marginal effect on both primary and total backscatter rates.
+			This is because once the scope is roughly determined, using denser constellation points may not create enough phase resolution and energy diversity for primary and backscatter links.
+			Another possible reason is the amplitude normalization step in the reflection-constellation mapping \eqref{eq:backscatter_modulation} grants less scattered (and more harvestable) power for the inner points, which are thus less frequently employed.
+			It motivates the use of numerous elementary UniScatter nodes, instead of high-order transponders or high-resolution metasurfaces.
+		\end{subsubsection}
+
+		\begin{subsubsection}{Number of Transmit Antennas}
+			Fig. \subref*{fi:region_txs} illustrates the impact of transmit antennas $Q$ on the average performance.
+			We observe larger $Q$ produces greater achievable rate regions.
+			Thanks to the \gls{pgd} active beamforming, the expectations of the received power under different backscatter symbol tuples can be flexibly controlled to satisfy the link priority requirements.
+			For example, beamforming towards the equivalent channel can produce higher primary \gls{snr}, while beamforming towards the cascaded channels can enhance the relative energy difference for better backscatter detection.
+			Those observations emphasize the importance of multi-antenna UniScatter systems and demonstrate the advantages of the proposed \gls{pgd} design.
+		\end{subsubsection}
+
+		\begin{subsubsection}{Symbol Period Ratio}
+			Fig. \subref*{fi:region_duration} presents how symbol period ratio $N$ affects the achievable rate region.
+			We notice using a small $N$ can effectively boost the total backscatter rate per primary symbol, and the conventional \gls{sr} literatures assuming sufficiently large $N$ is generally inefficient.
+			However, it not only requires a frequent change of reflection states that consumes more power at the passive nodes, but also involves more detection and re-encoding operations at the user to maintain the primary rate.
+			When $N$ becomes sufficiently large, the total backscatter rate approaches \num{0}, and UniScatter nodes boil down to \gls{ris} elements with fixed reflection pattern during whole channel block.
+			Therefore, we conclude $N$ should be properly tweaked based on the rate requirements and physical properties of the passive nodes.
+		\end{subsubsection}
+
+		\begin{subsubsection}{Average Noise Power}
+			Fig. \subref*{fi:region_noise} depicts the impact of average noise power $\sigma_v^2$ on average rate regions.
+			Despite the proposed low-complexity energy detection is suitable for a wide range of noise levels, there exists a backscatter performance upper bound due to its semi-coherent property.
+			When $\sigma_v^2$ relatively high, we can choose a longer backscatter symbol period (i.e., larger $N$) to maintain the backscatter \gls{snr} for better detection performance.
+		\end{subsubsection}
+
+		\begin{subsubsection}{Coverage Disk Radius}
+			Fig. \subref*{fi:region_coverage} shows the relationship between UniScatter cover disk radius and achievable rate regions.
+			We observe both primary and backscatter performance are enhanced when nodes are dropped closer to the user.
+			This is because the product path loss (a.k.a. double fading) model for finite-size scatterers is less severe for such near-far setups.
+			Thanks to the dispersed characteristics of UniScatter nodes and legacy users, each node can simply scatter and be decoded by the closest user, thus avoids the development optimization and allows uniformly good performance for both links.
+		\end{subsubsection}
+	\end{subsection}
+	% ? Channel estimation error, coordination issues
 	\label{se:simulation_results}
@@
 	% TODO  binary input and signal output (BISO) channel, ML figure
-	This paper introduced UniScatter that adapts input distribution of passive backscatter nodes to simultaneously transmit and assist over existing wireless systems.
-	Starting from backscatter principles, we showed how UniScatter nodes bridges and generalizes parasitic source of \gls{sr} and reflecting element of \gls{ris} via smart input design.
-	An application scenario was considered where multiple UniScatter nodes ride over a point-to-point transmission to simultaneously encode self message and perform passive beamforming.
-	To characterize achievable primary-backscatter rate region, we proposed a \gls{bcd} algorithm that evaluates \gls{kkt} input distribution in closed form, optimizes active beamforming by \gls{pgd}, and refines decision regions by existing methods.
-	Numerical results demonstrated the advantage of adaptive node input distribution design for both primary and backscatter subsystems.
-
-	One particular interesting question is how to design UniScatter node and receiver in a multi-user system.
-	If one node can contribute to and be decoded by multiple users, its input distribution may be further adjusted to mimic multi-beam gain of dynamic beamforming \cite{Qiu2022}.
+	This paper introduced UniScatter as a low-power transmit-assist protocol that generalizes \gls{bc}, \gls{sr} and \gls{ris} by smart input distribution and practical receiver design.
+	Starting from scattering principles, we showed how UniScatter nodes include scattering source of \gls{bc}/\gls{sr} and reflecting element of \gls{ris} as special cases, how they can be built over existing passive scatter devices, and how they simultaneously encode self information and assist legacy transmission.
+	We also propose a low-complexity UniScatter receiver that preserves the benefits of backscatter modulation and passive beamforming.
+	The achievable primary-total-backscatter rate region is then studied for a single-user multi-node UniScatter system, where the input distribution, active beamforming, and decision thresholds are iteratively updated.
+	Numerical results not only demonstrated the effectiveness of the proposed algorithms, but also emphasized the importance of adaptive input distribution and cooperative decoding on both primary and backscatter subsystems.
+
+	One possible direction is to consider backscatter detection over the received signal domain rather than energy domain.
+	Learning-based classification approaches can be prominsing in such cases.
+	Another interesting question is how to design UniScatter node and receiver in a multi-user system.
+	If one node can be decoded by multiple users, its input distribution may be further adjusted to mimic the multi-beam gain of dynamic passive beamforming \cite{Qiu2022}.
 \end{section}

### 2022-08-29 main.tex
:pencil: Update abstract

@@
 \begin{document}
-\title{UniScatter: Unifying\\Backscatter Communications, Symbiotic Radio and Reconfigurable Intelligent Surface}
-% \title{UniScatter: Unifying Backcatter Modulation and Passive Beamforming by Adaptive Input Distribution}
+\title{RIScatter: Unifying\\Backscatter Communications, Symbiotic Radio, and Reconfigurable Intelligent Surface}
+% \title{RIScatter: Unifying Backcatter Modulation and Passive Beamforming by Adaptive Input Distribution}
 \author{
@@
 \begin{abstract}
-	Scatterers can harvest energy from, modulate information over, and influence propagation of surrounding radio waves.
-	\gls{bc} varies object impedance to manipulate the magnitude, phase, and/or frequency of scattered signal to encode information and deliver within coverage.
-	\gls{ris} adapts scattering antennas or programmable metamaterial to control wireless propagation environment by boosting/suppressing signal strength in specific directions.
-	\gls{sr} incorporates scatter nodes into active networks that recycle ambient signal to transmit self information and enhance legacy channel to the cooperative receiver.
-	In this paper, we depart from those concepts and introduce UniScatter as a new paradigm for future wireless networks.
-	Instead of treating probability distribution of reflection states as equiprobable (as scattering source of \gls{bc}/\gls{sr}) or degenerate (as reflecting element of \gls{ris}), UniScatter nodes located at different places adapt the input distribution of passive scatterers based on link priority and \gls{csi}, balancing information encoding and channel reconfiguration in a flexible and mutualistic manner.
-	To accommodate signal characteristics, UniScatter receiver semi-coherently decodes all nodes from accumulated energy, determines primary equivalent channel over reflection pattern, then coherently decodes the primary link under enhanced multipath.
-	It reduces the complexity of cooperative decoding while preserves the benefits of backscatter modulation and passive beamforming.
-	Using shared spectrum, energy, and infrastructures, UniScatter is a general and powerful transmit-assist protocol that unifies \gls{bc}, \gls{ris} and \gls{sr} with universal hardware design and augmented \gls{qos} control.
-	We consider an application scenario where a multi-antenna \gls{ap} serves a single-antenna user surrounded by multiple UniScatter nodes, and characterize the achievable primary-total-backscatter rate region by designing input distribution at the nodes, active beamforming at the \gls{ap}, and backscatter decision regions at the user.
-	Simulation results demonstrate UniScatter nodes can flexibly control the transmit-assist tradeoff via smart input distribution design.
+	% Scatterers can harvest energy from, modulate information over, and influence propagation of surrounding radio waves.
+	% \gls{bc} varies object impedance to manipulate the magnitude, phase, and/or frequency of scattered signal to encode information and deliver within coverage.
+	% \gls{bc} switches load impedance that manipulates the magnitude, phase, and/or frequency responses to modulate information onto the scattered signal.
+	\gls{bc} switches load impedance to manipulate the magnitude, phase, and/or frequency responses and modulate information onto the scattered signal.
+	% \gls{ris} adapts scattering antennas/programmable metamaterial to control wireless environment by varying signal strength in specific directions.
+	% \gls{ris} programs antenna/metamaterial array that adjusts the scattering phase shifts to control signal strength in specific directions.
+	\gls{ris} programs antenna/metamaterial array to adjust the scattering phase shifts and control signal strength in specific directions.
+	% \gls{sr} incorporates scatter nodes into active networks that recycle ambient signal to transmit self information and enhance legacy channel to the cooperative receiver.
+	% \gls{sr} allows the transmission of a primary node using active radio carrying primary information and of a secondary node scattering information onto primary signal, and the reception of information of both nodes.
+	% \gls{sr} introduces a passive scatterer that rides secondary information over the primary signal from an active transmitter, and employs a co-located receiver to sequentially decode both links.
+	\gls{sr} introduces a passive scatterer to ride secondary information over the primary signal generated by an active transmitter, and employs a co-located receiver to sequentially decode both links.
+	% In this paper, we depart from those concepts and introduce RIScatter as a new paradigm for future wireless networks.
+	In this paper, we show how those three seemingly different technologies can be unified to leverage their benefits simultaneously into a single architecture called RIScatter.
+	RIScatter is a new paradigm for future wireless networks and consists of multiple passive scattering nodes, whose reflection states can be controlled to partially engineer the wireless channel and partially modulating information onto the scattered wave.
+	This contrasts with \gls{bc}/\gls{sr} (resp. \gls{ris}) where states are exclusively a function on information symbols (resp. \gls{csi}).
+	The key principle in RIScatter is to render the probability distribution of reflection states as a joint function of the \gls{csi} and input information source, allowing universal hardware design and heterogeneous traffic control.
+	% augmented \gls{qos} control.
+	This enables RISscatter to softly bridge, generalize, and outperform \gls{bc}, \gls{sr}, \gls{ris}; boil down to any of those three technologies under some specific reflection states; or evolve in a mixed state.
+	We show RIScatter is subject to a fundamental tradeoff that balances its information modulation and channel reconfiguration capabilities in a flexible and mutualistic manner.
+	% Instead of treating probability distribution of reflection states as equiprobable (as scattering source of \gls{bc}/\gls{sr}) or degenerate (as reflecting element of \gls{ris}), RIScatter nodes located at different places adapt the input distribution of passive scatterers based on link priority and \gls{csi}, balancing information encoding and channel reconfiguration in a flexible and mutualistic manner.
+	% RIScatter receiver semi-coherently decodes all nodes from accumulated energy, determines primary equivalent channel over reflection pattern, then coherently decodes the primary link under enhanced multipath.
+	% It reduces the complexity of cooperative decoding while preserves the benefits of backscatter modulation and passive beamforming.
+	% To accommodate signal characteristics, we also propose a low-complexity RIScatter receiver that preserves the aforementioned benefits.
+	% Using shared spectrum, energy, and infrastructures, RIScatter is a general and powerful transmit-assist protocol that unifies \gls{bc}, \gls{ris} and \gls{sr} with universal hardware design and augmented \gls{qos} control.
+	% We consider an application scenario where a multi-antenna \gls{ap} serves a single-antenna user surrounded by multiple RIScatter nodes, and characterize the achievable primary-total-backscatter rate region by designing input distribution at the nodes, active beamforming at the \gls{ap}, and backscatter decision regions at the user.
+	An application scenario is considered where a multi-antenna \gls{ap} serves a single-antenna user surrounded by multiple RIScatter nodes, and the achievable primary-total-backscatter rate region is characterized by optimizing input distribution at the nodes, active beamforming at the \gls{ap}, and backscatter decision regions at the user.
+	% Simulation results demonstrate RIScatter nodes can flexibly control the transmit-assist tradeoff via smart input distribution design.
+	% Simulation results demonstrate RIScatter can flexibly control the tradeoff between backscatter modulation and passive beamforming via smart input distribution design, which outperforms \gls{bc}, \gls{sr}, and \gls{ris}.
+	% Simulation results demonstrate RIScatter can exploit the additional propagation paths to provide a smooth transition between backscatter modulation and passive beamforming, which
+	Simulation results demonstrate RIScatter can exploit the additional propagation paths to provide a smooth transition between backscatter modulation and passive beamforming via smart input distribution design, which includes \gls{bc}, \gls{sr}, and \gls{ris} as special cases.
+	% Simulation results demonstrate RIScatter can exploit smart input distribution design to provide a smooth transition between backscatter modulation and passive beamforming, which outperforms \gls{bc}, \gls{sr}, and \gls{ris}.
+
+	% The three multiple access schemes are compared, and extensive numerical results show that RSMA provides a smooth transition between SDMA and NOMA and outperforms them both in a wide range of network loads (underloaded and overloaded regimes) and user deployments (with a diversity of channel directions, channel strengths, and qualities of channel state information at the transmitter).
+Moreover, RSMA provides rate and QoS enhancements over NOMA at a lower computational complexity for the transmit scheduler and the receivers (number of SIC layers).
+
 \end{abstract}
@@
 	The concept of cooperative \gls{ambc} was then refined as \gls{sr} to cognitively incorporate \gls{ambc} with existing systems \cite{Liang2020}.
-	In \gls{sr}, the primary transmitter generates active radio carrying primary information, the secondary node modulates scattered component with backscatter information, and the cooperative receiver decodes both links from two propagation paths.
+	In \gls{sr}, the primary transmitter generates active radio carrying primary information, the secondary node modulates backscatter information onto the scattered wave, and the cooperative receiver decodes both links from two propagation paths.
 	The direct transmitter-receiver path only contains primary information, while the cascaded transmitter-node-receiver path preserves both thanks to signal characteristics.
@@
 	The former is impractical for passive backscatter devices, while the latter does not fully exploit reflection pattern and \gls{csi}.
-	In this paper, we introduce UniScatter that generalizes \gls{bc}, \gls{sr}, and \gls{ris} to manipulate the transmit-assist tradeoff via smart input distribution and practical receiver design.
+	In this paper, we introduce RIScatter that generalizes \gls{bc}, \gls{sr}, and \gls{ris} to manipulate the transmit-assist tradeoff via smart input distribution and practical receiver design.
 	The contributions of this paper are summarized as follows.
 
-	\emph{First,} we propose UniScatter nodes to adapt the input probability distribution of a finite-state passive scatter device based on link priority and \gls{csi}.
+	\emph{First,} we propose RIScatter nodes to adapt the input probability distribution of a finite-state passive scatter device based on link priority and \gls{csi}.
 	The reflection pattern over time is no longer fully random or deterministic, but can be flexibly distributed to unify and balance backscatter modulation with passive beamforming.
 	Scattering source of \gls{bc}/\gls{sr} and reflecting element of \gls{ris} can be regarded as its extreme cases, where the input distribution boils down to equiprobable and degenerate, respectively.
-	Like aforementioned \gls{ris}-empowered \gls{bc}/\gls{sr} schemes, the passive nodes require regular coordination with active devices, but the advantages are 1) UniScatter nodes can be built over conventional load-switching scatterers instead of composite metamaterial; 2) the optimization cost of input distribution is much lower than that of \gls{ris} reflection coefficients; 3) adaptive backscatter channel coding can exploit \gls{csi} to achieve higher instantaneous rate than conventional uncoded transmission; 4) the dispersed characteristics of UniScatter nodes and legacy users avoids the development optimization and allows uniformly good performance for both links.
-
-	\emph{Second,} we propose a practical UniScatter receiver that semi-coherently decodes UniScatter nodes from the received energy per backscatter block, re-encodes for their reflection patterns, retrieves primary equivalent channel as if dynamic passive beamforming, then coherently decodes the primary link under the enhanced multipath.
+	Like aforementioned \gls{ris}-empowered \gls{bc}/\gls{sr} schemes, the passive nodes require regular coordination with active devices, but the advantages are 1) RIScatter nodes can be built over conventional load-switching scatterers instead of composite metamaterial; 2) the optimization cost of input distribution is much lower than that of \gls{ris} reflection coefficients; 3) adaptive backscatter channel coding can exploit \gls{csi} to achieve higher instantaneous rate than conventional uncoded transmission; 4) the dispersed characteristics of RIScatter nodes and legacy users avoids the development optimization and allows uniformly good performance for both links.
+
+	\emph{Second,} we propose a practical RIScatter receiver that semi-coherently decodes RIScatter nodes from the received energy per backscatter block, re-encodes for their reflection patterns, retrieves primary equivalent channel as if dynamic passive beamforming, then coherently decodes the primary link under the enhanced multipath.
 	The proposed receiver 1) preserves the benefits of backscatter modulation and passive beamforming; 2) enjoys lower computational and operational complexities than joint \gls{ml} and \gls{sic} schemes; 3) accommodates the link difference and suits for diverse symbol period ratios; 4) requires minor modification over legacy hardware.
 
-	\emph{Third,} we consider an application scenario where multiple UniScatter nodes ride over a point-to-point \gls{miso} transmission, performing backscatter modulation and passive beamforming to a nearby user using shared spectrum, energy, and infrastructures.
-	To investigate how UniScatter unifies \gls{bc}, \gls{sr} and \gls{ris} for the benefits of both coexisting subsystems, we provide primary and backscatter rate analyses and emphasize the contributions of input distribution at UniScatter nodes, active beamforming at the \gls{ap}, and backscatter decision regions at the user.
+	\emph{Third,} we consider an application scenario where multiple RIScatter nodes ride over a point-to-point \gls{miso} transmission, performing backscatter modulation and passive beamforming to a nearby user using shared spectrum, energy, and infrastructures.
+	To investigate how RIScatter unifies \gls{bc}, \gls{sr} and \gls{ris} for the benefits of both coexisting subsystems, we provide primary and backscatter rate analyses and emphasize the contributions of input distribution at RIScatter nodes, active beamforming at the \gls{ap}, and backscatter decision regions at the user.
 	This is the first paper to reveal the importance of those factors in \gls{ris}-empowered \gls{bc}/\gls{sr}.
@@
 
-	\emph{Fifth,} we provide numerical results to demonstrate the benefits of UniScatter and proposed algorithms.
-	It is concluded that 1) UniScatter nodes provide flexible transmit-assist tradeoff using adaptive input distribution design; 2) when primary link is absolutely prioritized, the input probability of each node is \num{1} at one state and \num{0} at the others, which coincides with discretized \gls{ris}; 3) when backscatter link is absolutely prioritized, UniScatter nodes can exploit adaptive channel coding to achieve higher instantaneous rate than uncoded equiprobable inputs of \gls{bc}/\gls{sr}; 4) the proposed \gls{kkt} input distribution design converges to stationary points, whose average performance is very close to global optimal; 5) the proposed \gls{pgd} beamforming provides larger rate region than \gls{mrt}-based schemes; 6) the decision region schemes adapted to input distribution provide higher backscatter rates than the non-adaptive \gls{ml} detector; 7) cooperation between passive nodes in terms of joint encoding can further boost the total backscatter rate; 8) the low complexity of input distribution design and the marginal effect of increasing reflection states motivates the use of low-order scatter nodes to replace high-resolution \gls{ris}.
+	\emph{Fifth,} we provide numerical results to demonstrate the benefits of RIScatter and proposed algorithms.
+	It is concluded that 1) RIScatter nodes provide flexible transmit-assist tradeoff using adaptive input distribution design; 2) when primary link is absolutely prioritized, the input probability of each node is \num{1} at one state and \num{0} at the others, which coincides with discretized \gls{ris}; 3) when backscatter link is absolutely prioritized, RIScatter nodes can exploit adaptive channel coding to achieve higher instantaneous rate than uncoded equiprobable inputs of \gls{bc}/\gls{sr}; 4) the proposed \gls{kkt} input distribution design converges to stationary points, whose average performance is very close to global optimal; 5) the proposed \gls{pgd} beamforming provides larger rate region than \gls{mrt}-based schemes; 6) the decision region schemes adapted to input distribution provide higher backscatter rates than the non-adaptive \gls{ml} detector; 7) cooperation between passive nodes in terms of joint encoding can further boost the total backscatter rate; 8) the low complexity of input distribution design and the marginal effect of increasing reflection states motivates the use of low-order scatter nodes to replace high-resolution \gls{ris}.
 
@@
 
-\begin{section}{UniScatter}
-	Using shared spectrum, energy and infrastructures, UniScatter is a novel passive communication/assistance protocol that generalizes \gls{bc}, \gls{sr} and \gls{ris} in a \emph{geographically} and \emph{probabilistically} distributed manner.
-	In particular, passive UniScatter nodes located at different places ride over an active legacy transmission in a flexible and mutualistic manner, while practical UniScatter receiver cooperatively decodes both primary and backscatter links under the benefits of backscatter modulation and passive beamforming.
+\begin{section}{RIScatter}
+	Using shared spectrum, energy and infrastructures, RIScatter is a novel passive communication/assistance protocol that generalizes \gls{bc}, \gls{sr} and \gls{ris} in a \emph{geographically} and \emph{probabilistically} distributed manner.
+	In particular, passive RIScatter nodes located at different places ride over an active legacy transmission in a flexible and mutualistic manner, while practical RIScatter receiver cooperatively decodes both primary and backscatter links under the benefits of backscatter modulation and passive beamforming.
 	% TODO compare BC, SR and IRS
-	\begin{subsection}{UniScatter Nodes}
-		Based on link priority and \gls{csi}, UniScatter nodes adapt the \emph{state input probability distribution} of antenna-based scatterers to unify backscatter modulation and passive beamforming.
+	\begin{subsection}{RIScatter Nodes}
+		Based on link priority and \gls{csi}, RIScatter nodes adapt the \emph{state input probability distribution} of antenna-based scatterers to unify backscatter modulation and passive beamforming.
 		The scattering sources of \gls{bc}/\gls{sr} and reflecting elements of \gls{ris} can be viewed as its extreme cases, where the input distribution boils down to equiprobable and degenerate, respectively.
@@
 			\caption{
-				Input probability distribution and time block structure of \gls{bc}, \gls{sr}, \gls{ris}, and UniScatter.
+				Input probability distribution and time block structure of \gls{bc}, \gls{sr}, \gls{ris}, and RIScatter.
 				$T_s$ and $T_c$ respectively denote the primary and backscatter symbol period.
-				Within channel coherence time, UniScatter nodes semi-randomly select reflection state for each backscatter symbol block under the guidance of input probability distribution.
+				Within channel coherence time, RIScatter nodes semi-randomly select reflection state for each backscatter symbol block under the guidance of input probability distribution.
 			}
@@
 		As illustrated in Fig.
-\ref{fi:uniscatter_distribution}, instead of always using fully random or deterministic reflection pattern over time, each UniScatter node can \emph{flexibly adjust} its input distribution to balance information encoding and channel reconfiguration.
+\ref{fi:uniscatter_distribution}, instead of always using fully random or deterministic reflection pattern over time, each RIScatter node can \emph{flexibly adjust} its input distribution to balance information encoding and channel reconfiguration.
 		That is, it semi-randomly select the reflection state per backscatter symbol block under the guidance of input probability $P(\Gamma_m)$ for state $m$.
 		Such an adaptive backscatter channel coding coincides with \gls{ris} when primary link is absolutely prioritized, and outperforms the uncoded equiprobable inputs of \gls{bc}/\gls{sr} when backscatter link is absolutely prioritized.
-		Besides, the dispersed characteristics of UniScatter nodes and legacy users avoids the development optimization and allows uniformly good performance for both links.
-
-		As shown in Fig. \subref*{fi:block_diagram}, UniScatter nodes can be implemented over readily available passive backscatter devices with energy harvester and information decoder.
+		Besides, the dispersed characteristics of RIScatter nodes and legacy users avoids the development optimization and allows uniformly good performance for both links.
+
+		As shown in Fig. \subref*{fi:block_diagram}, RIScatter nodes can be implemented over readily available passive backscatter devices with energy harvester and information decoder.
 		Its equivalent circuit and scatter model are presented in Fig. \subref*{fi:equivalent_circuit} and \subref*{fi:scatter_model}.
 		When activated by primary transmitter, each node harvests a proportion of the impinging wave for its own operation, decode the embedded coordination information for input distribution control, then applies a potentially random phase shift on the reradiated signal due to backscatter modulation.
-		Energy harvesting and information decoding at passive UniScatter nodes can be realized using conventional power-splitting or time-sharing \gls{swipt} protocols \cite{Clerckx2019} or integrated energy-information receiver with pulse position modulated signal \cite{Kim2021a}.
+		Energy harvesting and information decoding at passive RIScatter nodes can be realized using conventional power-splitting or time-sharing \gls{swipt} protocols \cite{Clerckx2019} or integrated energy-information receiver with pulse position modulated signal \cite{Kim2021a}.
 		Besides, relevant \gls{csi} can be acquired using either traditional sequential methods \cite{Bharadia2015,Yang2015b,Guo2019g} or the state-of-the-art parallel approach \cite{Jin2021a}.
@@
 			\caption{
-			Block diagram, equivalent circuit, and scatter model of a UniScatter node.
+			Block diagram, equivalent circuit, and scatter model of a RIScatter node.
 			The solid and dashed vectors represent signal and energy flows.
@@
 
-	\begin{subsection}{UniScatter Receiver}
-		Since each passive UniScatter node directly modulates its own message over the legacy signal, it involves a \emph{double modulation} where the primary and backscatter symbols are superimposed by \emph{multiplication coding} instead of superposition coding.
+	\begin{subsection}{RIScatter Receiver}
+		Since each passive RIScatter node directly modulates its own message over the legacy signal, it involves a \emph{double modulation} where the primary and backscatter symbols are superimposed by \emph{multiplication coding} instead of superposition coding.
 		Besides, the backscatter symbol period is typically longer than primary due to the load switching speed constraint.
 		Those facts imply \emph{backscatter detection} under primary uncertainty can be viewed as part of \emph{primary channel training}.
-		Hence, we propose a practical UniScatter receiver that semi-coherently decodes UniScatter nodes from the received energy per backscatter block, re-encodes for their reflection patterns, retrieves primary equivalent channel as if dynamic passive beamforming, then coherently decodes the primary link under the enhanced multipath.
+		Hence, we propose a practical RIScatter receiver that semi-coherently decodes RIScatter nodes from the received energy per backscatter block, re-encodes for their reflection patterns, retrieves primary equivalent channel as if dynamic passive beamforming, then coherently decodes the primary link under the enhanced multipath.
 		\begin{figure}[!t]
@@
 \ref{fi:energy_distribution}, the total received energy per backscatter block is a random variable that follows different distributions conditioned on different input state hypotheses.
-		Compared with conventional joint \gls{ml} and \gls{sic} from stronger primary link to weaker backscatter links, UniScatter receiver not only preserves the benefits of backscatter modulation and passive beamforming, but also enjoys much lower computational and operational complexities.
+		Compared with conventional joint \gls{ml} and \gls{sic} from stronger primary link to weaker backscatter links, RIScatter receiver not only preserves the benefits of backscatter modulation and passive beamforming, but also enjoys much lower computational and operational complexities.
 	\end{subsection}
@@
 			}
-			\caption{A single-user multi-node UniScatter system.}
+			\caption{A single-user multi-node RIScatter system.}
 			\label{fi:uniscatter_network}
 		\end{figure}
-		To demonstrate the advantages of UniScatter, we consider a single-user multi-node \gls{miso} UniScatter system as shown in Fig. \ref{fi:uniscatter_network}.
-		In the primary active point-to-point system, a $Q$-antenna \gls{ap} transmits to a single-antenna user assisted by $K$ nearby single-antenna UniScatter nodes with $M$ reflection states.
-		In the secondary backscatter \gls{mac} system, the \gls{ap} serves as the carrier emitter, the distributed UniScatter nodes modulate information over reradiated \gls{rf} signals, and the user decodes their messages.
+		To demonstrate the advantages of RIScatter, we consider a single-user multi-node \gls{miso} RIScatter system as shown in Fig. \ref{fi:uniscatter_network}.
+		In the primary active point-to-point system, a $Q$-antenna \gls{ap} transmits to a single-antenna user assisted by $K$ nearby single-antenna RIScatter nodes with $M$ reflection states.
+		In the secondary backscatter \gls{mac} system, the \gls{ap} serves as the carrier emitter, the distributed RIScatter nodes modulate information over reradiated \gls{rf} signals, and the user decodes their messages.
 		For simplicity, we consider a quasi-static block fading model where channels remain constant within coherence block and vary independently between consecutive blocks.
@@
 		Denote the \gls{ap}-user direct channel as $\boldsymbol{h}_{\mathrm{D}}^H \in \mathbb{C}^{1 \times Q}$, the \gls{ap}-node $k \in \mathcal{K} \triangleq \{1,\ldots,K\}$ forward channel as $\boldsymbol{h}_{\mathrm{F},k}^H \in \mathbb{C}^{1 \times Q}$, the node $k$-user backward channel as $h_{\mathrm{B},k}$, and the cascaded channel via tag $k$ as $\boldsymbol{h}_{\mathrm{C},k}^H \triangleq h_{\mathrm{B},k} \boldsymbol{h}_{\mathrm{F},k}^H \in \mathbb{C}^{1 \times Q}$.
-		Let $x_{\mathcal{K}} \triangleq (x_1,\ldots,x_K)$ be the backscatter symbol tuple of all UniScatter nodes.
+		Let $x_{\mathcal{K}} \triangleq (x_1,\ldots,x_K)$ be the backscatter symbol tuple of all RIScatter nodes.
 		Without loss of generality, we consider one specific backscatter block (i.e., $N$ primary blocks) in the following context.
@@
 		\end{equation}
-		where $\alpha_k \in \mathbb{I}$ is the amplitude scattering ratio of UniScatter node $k$, $x_k \in \mathcal{X} \triangleq \{c_1,\ldots,c_M\}$ is the \emph{coded} backscatter symbol of node $k$, $\boldsymbol{\alpha} \triangleq [\alpha_1,\ldots,\alpha_K]^T \in \mathbb{I}^{K}$, $\boldsymbol{x} \triangleq [x_1,\ldots,x_K]^H \in \mathcal{X}^{K}$, and $\boldsymbol{H}_{\mathrm{C}} \triangleq [\boldsymbol{h}_{\mathrm{C},1},\ldots,\boldsymbol{h}_{\mathrm{C},K}]^H \in \mathbb{C}^{K \times Q}$.
+		where $\alpha_k \in \mathbb{I}$ is the amplitude scattering ratio of RIScatter node $k$, $x_k \in \mathcal{X} \triangleq \{c_1,\ldots,c_M\}$ is the \emph{coded} backscatter symbol of node $k$, $\boldsymbol{\alpha} \triangleq [\alpha_1,\ldots,\alpha_K]^T \in \mathbb{I}^{K}$, $\boldsymbol{x} \triangleq [x_1,\ldots,x_K]^H \in \mathcal{X}^{K}$, and $\boldsymbol{H}_{\mathrm{C}} \triangleq [\boldsymbol{h}_{\mathrm{C},1},\ldots,\boldsymbol{h}_{\mathrm{C},K}]^H \in \mathbb{C}^{K \times Q}$.
 The signal received by the user at primary block $n \in \mathcal{N} \triangleq \{1,\ldots,N\}$ is
@@
 		where $\mathcal{H}_{m_{\mathcal{K}}}$ denotes hypothesis $m_{\mathcal{K}}$.
-		As illustrated in Fig. \ref{fi:energy_distribution}, the UniScatter receiver divides the received energy space into disjoint decision regions associated with those hypotheses.
+		As illustrated in Fig. \ref{fi:energy_distribution}, the RIScatter receiver divides the received energy space into disjoint decision regions associated with those hypotheses.
 		For example, if the total received energy during a backscatter block falls within region $\mathcal{R}_{m_{\mathcal{K}}}$, then the detector output would be $x_{m_{\mathcal{K}}}$.
@@
 \begin{section}{Rate-Region Characterization}
-	To characterize the achievable primary-total-backscatter rate region of the proposed UniScatter system, we aim to maximize the weighted sum mutual information with respect to input distribution $\{\boldsymbol{p}_k\}_{k \in \mathcal{K}}$, active beamforming $\boldsymbol{w}$, and decision thresholds $\boldsymbol{t}$ as
+	To characterize the achievable primary-total-backscatter rate region of the proposed RIScatter system, we aim to maximize the weighted sum mutual information with respect to input distribution $\{\boldsymbol{p}_k\}_{k \in \mathcal{K}}$, active beamforming $\boldsymbol{w}$, and decision thresholds $\boldsymbol{t}$ as
 	\begin{maxi!}
@@
 		\begin{remark}
-			Upon successful backscatter decoding, UniScatter receiver can always re-encode node messages to recover their reflection patterns at each primary block.
+			Upon successful backscatter decoding, RIScatter receiver can always re-encode node messages to recover their reflection patterns at each primary block.
 			Therefore, backscatter decision design has no impact on the primary achievable rate, and any thresholding scheme maximizing the total backscatter mutual information \eqref{eq:backscatter_mutual_information} is also optimal for problem \eqref{op:decision_threshold}.
@@
 \begin{section}{Simulation Results}
-	In this section, we provide numerical results to evaluate the proposed input distribution, active beamforming, and backscatter decision design for the UniScatter system in Fig.
+	In this section, we provide numerical results to evaluate the proposed input distribution, active beamforming, and backscatter decision design for the RIScatter system in Fig.
 \ref{fi:uniscatter_network}.
-	We assume the AP-user distance is \qty{10}{\meter}, $K=2$ UniScatter nodes are randomly dropped within a disk of radius \qty{2}{\meter} centered at the user, the \gls{ap} is with $Q=4$ transmit antennas and an average power budget $P=\qty{36}{\dBm}$, the nodes employs \num{4}-\gls{qam} with amplitude scattering ratio $\alpha=0.5$, the user is with average noise power $\sigma_v^2=\qty{-40}{\dBm}$, and the symbol period ratio is $N=20$.
+	We assume the AP-user distance is \qty{10}{\meter}, $K=2$ RIScatter nodes are randomly dropped within a disk of radius \qty{2}{\meter} centered at the user, the \gls{ap} is with $Q=4$ transmit antennas and an average power budget $P=\qty{36}{\dBm}$, the nodes employs \num{4}-\gls{qam} with amplitude scattering ratio $\alpha=0.5$, the user is with average noise power $\sigma_v^2=\qty{-40}{\dBm}$, and the symbol period ratio is $N=20$.
 	For all channels involved, we consider a distance-dependent path loss model
@@
 		\end{figure}
-		The objective of this study is to demonstrate each UniScatter node can adjust its input distribution based on \gls{csi} and link priority to balance backscatter modulation and passive beamforming.
+		The objective of this study is to demonstrate each RIScatter node can adjust its input distribution based on \gls{csi} and link priority to balance backscatter modulation and passive beamforming.
 		For this aim, we evaluate the \gls{kkt} input distribution by Algorithm \ref{al:input_distribution} for a single node under different weights $\rho=\{0,0.1,0.2,0.3,1\}$ in Fig.
@@
 		gradually progresses from slightly skewed to completely biased.
-		For $\rho=0$ where backscatter performance is absolutely prioritized, the \gls{csi}-adaptive channel coding at the UniScatter node provides higher backscatter rate than conventional \gls{bc} and \gls{sr} nodes with uncoded equiprobable inputs, and some states may end up unused since they cannot produce enough energy difference over the existing alphabet.
+		For $\rho=0$ where backscatter performance is absolutely prioritized, the \gls{csi}-adaptive channel coding at the RIScatter node provides higher backscatter rate than conventional \gls{bc} and \gls{sr} nodes with uncoded equiprobable inputs, and some states may end up unused since they cannot produce enough energy difference over the existing alphabet.
 		On the other hand, for $\rho=1$ where primary performance is absolutely prioritized, the input probability is \num{1} at the state that maximizes the primary equivalent channel strength, and \num{0} at the others.
-		In this case, the reflection pattern over time is fully deterministic, and the UniScatter node indeed boils down to a \gls{ris} element with discrete phase shifts.
-		Those observations meet our s that UniScatter nodes include scattering sources of \gls{bc}/\gls{sr} and reflecting elements of \gls{ris} as special cases, and generalize backscatter modulation and passive beamforming from the perspective of input distribution design.
+		In this case, the reflection pattern over time is fully deterministic, and the RIScatter node indeed boils down to a \gls{ris} element with discrete phase shifts.
+		Those observations meet our s that RIScatter nodes include scattering sources of \gls{bc}/\gls{sr} and reflecting elements of \gls{ris} as special cases, and generalize backscatter modulation and passive beamforming from the perspective of input distribution design.
 		For the \gls{bcd} algorithm, we choose the \gls{kkt} input distribution by Algorithm \ref{al:input_distribution}, the \gls{pgd} active beamforming by Algorithm \ref{al:active_beamforming}, and the \gls{smawk} decision threshold by \cite{He2021} as reference.
@@
 		\end{figure}
-		We now reveal how the analog-to-digital conversion of feasible threshold domain from $\mathbb{R}_+^{L+1}$ to $\mathcal{T}^{L+1}$ affects the average UniScatter performance.
+		We now reveal how the analog-to-digital conversion of feasible threshold domain from $\mathbb{R}_+^{L+1}$ to $\mathcal{T}^{L+1}$ affects the average RIScatter performance.
 		For a fixed input distribution and active beamforming, Fig. \ref{fi:rate_bits} shows the impact of energy discretization bits $b$ on the average achievable rates when $\rho=0$.
@@
 			Fig. \subref*{fi:region_distribution} shows the achievable rate regions for those input distribution schemes.
-			We observe that \emph{Cooperation} provides the outer bound for all achievable rate regions, which suggests transmit cooperation between UniScatter nodes can be generally helpful.
+			We observe that \emph{Cooperation} provides the outer bound for all achievable rate regions, which suggests transmit cooperation between RIScatter nodes can be generally helpful.
 			However, it requires joint encoding with arbitrarily dependent codewords, and the extra coordination burden may be unaffordable for a large $K$.
@@
 			Finally, \emph{Decomposition} suffers from much lower average total backscatter rate, as the rank-\num{1} \gls{cp} approximation can be inaccurate for some channel-drop realizations.
-			% Those observations demonstrate the performance and complexity advantages of the proposed \gls{kkt} input distribution design, and reveal the potential of joint encoding at UniScatter nodes.
-			Those observations demonstrate the high performance and low complexity of the proposed \gls{kkt} input distribution design, and reveal the potential of joint encoding at UniScatter nodes.
+			% Those observations demonstrate the performance and complexity advantages of the proposed \gls{kkt} input distribution design, and reveal the potential of joint encoding at RIScatter nodes.
+			Those observations demonstrate the high performance and low complexity of the proposed \gls{kkt} input distribution design, and reveal the potential of joint encoding at RIScatter nodes.
 		\end{subsubsection}
@@
 			\centering
-			\subfloat[UniScatter Nodes\label{fi:region_tags}]{
+			\subfloat[RIScatter Nodes\label{fi:region_tags}]{
 				\resizebox{0.48\columnwidth}{!}{
@@
 		\begin{subsubsection}{Number of Nodes}
-			Fig. \subref*{fi:region_tags} reveals how the number of two-state UniScatter nodes $K$ influence the primary-backscatter tradeoff.
+			Fig. \subref*{fi:region_tags} reveals how the number of two-state RIScatter nodes $K$ influence the primary-backscatter tradeoff.
 			We observe the total backscatter rate roughly scales proportionally with the number of nodes, and the decrease of individual rate is unobvious.
 			This demonstrates the proposed low-complexity semi-coherent energy detector performs reasonably well for a moderate $K$.
-			On the other hand, we observe adding UniScatter nodes can also boost the achievable primary rate.
+			On the other hand, we observe adding RIScatter nodes can also boost the achievable primary rate.
 			The reason is the nodes can exploit the additional propagation path for a constructive primary signal superposition that enjoys a ``squared law'' similar to \gls{ris}.
@@
 			Another possible reason is the amplitude normalization step in the reflection-constellation mapping \eqref{eq:backscatter_modulation} grants less scattered (and more harvestable) power for the inner points, which are thus less frequently employed.
-			It motivates the use of numerous elementary UniScatter nodes, instead of high-order transponders or high-resolution metasurfaces.
+			It motivates the use of numerous elementary RIScatter nodes, instead of high-order transponders or high-resolution metasurfaces.
 		\end{subsubsection}
@@
 			For example, beamforming towards the equivalent channel can produce higher primary \gls{snr}, while beamforming towards the cascaded channels can enhance the relative energy difference for better backscatter detection.
-			Those observations emphasize the importance of multi-antenna UniScatter systems and demonstrate the advantages of the proposed \gls{pgd} design.
+			Those observations emphasize the importance of multi-antenna RIScatter systems and demonstrate the advantages of the proposed \gls{pgd} design.
 		\end{subsubsection}
@@
 			However, it not only requires a frequent change of reflection states that consumes more power at the passive nodes, but also involves more detection and re-encoding operations at the user to maintain the primary rate.
-			When $N$ becomes sufficiently large, the total backscatter rate approaches \num{0}, and UniScatter nodes boil down to \gls{ris} elements with fixed reflection pattern during whole channel block.
+			When $N$ becomes sufficiently large, the total backscatter rate approaches \num{0}, and RIScatter nodes boil down to \gls{ris} elements with fixed reflection pattern during whole channel block.
 			Therefore, we conclude $N$ should be properly tweaked based on the rate requirements and physical properties of the passive nodes.
@@
 		\begin{subsubsection}{Coverage Disk Radius}
-			Fig. \subref*{fi:region_coverage} shows the relationship between UniScatter cover disk radius and achievable rate regions.
+			Fig. \subref*{fi:region_coverage} shows the relationship between RIScatter cover disk radius and achievable rate regions.
 			We observe both primary and backscatter performance are enhanced when nodes are dropped closer to the user.
 			This is because the product path loss (a.k.a. double fading) model for finite-size scatterers is less severe for such near-far setups.
-			Thanks to the dispersed characteristics of UniScatter nodes and legacy users, each node can simply scatter and be decoded by the closest user, thus avoids the development optimization and allows uniformly good performance for both links.
+			Thanks to the dispersed characteristics of RIScatter nodes and legacy users, each node can simply scatter and be decoded by the closest user, thus avoids the development optimization and allows uniformly good performance for both links.
 		\end{subsubsection}
@@
 	% TODO  binary input and signal output (BISO) channel, ML figure
-	This paper introduced UniScatter as a low-power transmit-assist protocol that generalizes \gls{bc}, \gls{sr} and \gls{ris} by smart input distribution and practical receiver design.
-	Starting from scattering principles, we showed how UniScatter nodes include scattering source of \gls{bc}/\gls{sr} and reflecting element of \gls{ris} as special cases, how they can be built over existing passive scatter devices, and how they simultaneously encode self information and assist legacy transmission.
-	We also propose a low-complexity UniScatter receiver that preserves the benefits of backscatter modulation and passive beamforming.
-	The achievable primary-total-backscatter rate region is then studied for a single-user multi-node UniScatter system, where the input distribution, active beamforming, and decision thresholds are iteratively updated.
+	This paper introduced RIScatter as a low-power transmit-assist protocol that generalizes \gls{bc}, \gls{sr} and \gls{ris} by smart input distribution and practical receiver design.
+	Starting from scattering principles, we showed how RIScatter nodes include scattering source of \gls{bc}/\gls{sr} and reflecting element of \gls{ris} as special cases, how they can be built over existing passive scatter devices, and how they simultaneously encode self information and assist legacy transmission.
+	We also propose a low-complexity RIScatter receiver that preserves the benefits of backscatter modulation and passive beamforming.
+	The achievable primary-total-backscatter rate region is then studied for a single-user multi-node RIScatter system, where the input distribution, active beamforming, and decision thresholds are iteratively updated.
 	Numerical results not only demonstrated the effectiveness of the proposed algorithms, but also emphasized the importance of adaptive input distribution and cooperative decoding on both primary and backscatter subsystems.
@@
 	Learning-based classification approaches can be prominsing in such cases.
-	Another interesting question is how to design UniScatter node and receiver in a multi-user system.
+	Another interesting question is how to design RIScatter node and receiver in a multi-user system.
 	If one node can be decoded by multiple users, its input distribution may be further adjusted to mimic the multi-beam gain of dynamic passive beamforming \cite{Qiu2022}.

### 2022-08-30 main.tex
:pencil: Update abstract

@@
 	% \gls{bc} switches load impedance that manipulates the magnitude, phase, and/or frequency responses to modulate information onto the scattered signal.
-	\gls{bc} switches load impedance to manipulate the magnitude, phase, and/or frequency responses and modulate information onto the scattered signal.
-	% \gls{ris} adapts scattering antennas/programmable metamaterial to control wireless environment by varying signal strength in specific directions.
-	% \gls{ris} programs antenna/metamaterial array that adjusts the scattering phase shifts to control signal strength in specific directions.
-	\gls{ris} programs antenna/metamaterial array to adjust the scattering phase shifts and control signal strength in specific directions.
+	% \gls{bc} switches load impedance to manipulate the magnitude, phase, and/or frequency responses and modulate information onto the scattered signal.
+	\gls{bc} switches device load impedance to manipulate the magnitude, phase, and/or frequency responses for information modulation on the scattered carrier.
 	% \gls{sr} incorporates scatter nodes into active networks that recycle ambient signal to transmit self information and enhance legacy channel to the cooperative receiver.
@@
 	% \gls{sr} introduces a passive scatterer that rides secondary information over the primary signal from an active transmitter, and employs a co-located receiver to sequentially decode both links.
-	\gls{sr} introduces a passive scatterer to ride secondary information over the primary signal generated by an active transmitter, and employs a co-located receiver to sequentially decode both links.
+	% \gls{sr} introduces a passive scatterer to ride secondary information over the primary radio from an active transmitter, and employs a co-located receiver to decode both links.
+	% \gls{sr} introduces a passive scatterer to ride secondary information over the primary radio from an active transmitter and employs a co-located receiver to decode both links.
+	\gls{sr} allows a passive scattering node to ride additional information over the primary radio emitted by an active transmitter, and employs a co-located receiver to decode both sources.
+	% ride secondary information over the primary radio from an active transmitter and employs a co-located receiver to decode both links.
+	% \gls{ris} adapts scattering antennas/programmable metamaterial to control wireless environment by varying signal strength in specific directions.
+	% \gls{ris} programs antenna/metamaterial array that adjusts the scattering phase shifts to control signal strength in specific directions.
+	\gls{ris} programs an antenna/metamaterial array to adjust the scattering phase shifts for signal propagation control in specific directions.
+	% and control signal strength in specific directions.
 	% In this paper, we depart from those concepts and introduce RIScatter as a new paradigm for future wireless networks.
 	In this paper, we show how those three seemingly different technologies can be unified to leverage their benefits simultaneously into a single architecture called RIScatter.
-	RIScatter is a new paradigm for future wireless networks and consists of multiple passive scattering nodes, whose reflection states can be controlled to partially engineer the wireless channel and partially modulating information onto the scattered wave.
-	This contrasts with \gls{bc}/\gls{sr} (resp. \gls{ris}) where states are exclusively a function on information symbols (resp. \gls{csi}).
-	The key principle in RIScatter is to render the probability distribution of reflection states as a joint function of the \gls{csi} and input information source, allowing universal hardware design and heterogeneous traffic control.
+	RIScatter is a new paradigm for future wireless networks and consists of multiple passive scattering nodes, whose reflection states can be controlled to partially engineer the wireless channel and partially modulate information onto the scattered wave.
+	This contrasts with \gls{bc}/\gls{sr} (resp. \gls{ris}) where states are exclusively a function of information symbols (resp. \gls{csi}).
+	The key principle in RIScatter is to render the probability distribution of reflection states as a joint function of the \gls{csi} and backscatter information source, allowing universal hardware design and heterogeneous traffic control.
 	% augmented \gls{qos} control.
-	This enables RISscatter to softly bridge, generalize, and outperform \gls{bc}, \gls{sr}, \gls{ris}; boil down to any of those three technologies under some specific reflection states; or evolve in a mixed state.
-	We show RIScatter is subject to a fundamental tradeoff that balances its information modulation and channel reconfiguration capabilities in a flexible and mutualistic manner.
+	This enables RISscatter to softly bridge, generalize, and outperform \gls{bc}, \gls{sr}, \gls{ris}; boil down to any of those under specific reflection states; or evolve in a mixed setup.
+	We reveal RIScatter experiences a fundamental tradeoff that balances information modulation and channel reconfiguration capabilities in a flexible and mutualistic manner.
 	% Instead of treating probability distribution of reflection states as equiprobable (as scattering source of \gls{bc}/\gls{sr}) or degenerate (as reflecting element of \gls{ris}), RIScatter nodes located at different places adapt the input distribution of passive scatterers based on link priority and \gls{csi}, balancing information encoding and channel reconfiguration in a flexible and mutualistic manner.
@@
 	% We consider an application scenario where a multi-antenna \gls{ap} serves a single-antenna user surrounded by multiple RIScatter nodes, and characterize the achievable primary-total-backscatter rate region by designing input distribution at the nodes, active beamforming at the \gls{ap}, and backscatter decision regions at the user.
-	An application scenario is considered where a multi-antenna \gls{ap} serves a single-antenna user surrounded by multiple RIScatter nodes, and the achievable primary-total-backscatter rate region is characterized by optimizing input distribution at the nodes, active beamforming at the \gls{ap}, and backscatter decision regions at the user.
+	An application scenario is also considered where a multi-antenna \gls{ap} serves a single-antenna user surrounded by multiple RIScatter nodes, and the achievable primary-total-backscatter rate region is characterized by optimizing input distribution at the nodes, active beamforming at the \gls{ap}, and backscatter decision regions at the user.
 	% Simulation results demonstrate RIScatter nodes can flexibly control the transmit-assist tradeoff via smart input distribution design.
@@
 	% Simulation results demonstrate RIScatter can exploit the additional propagation paths to provide a smooth transition between backscatter modulation and passive beamforming, which
-	Simulation results demonstrate RIScatter can exploit the additional propagation paths to provide a smooth transition between backscatter modulation and passive beamforming via smart input distribution design, which includes \gls{bc}, \gls{sr}, and \gls{ris} as special cases.
+	Simulation results demonstrate RIScatter can exploit the additional propagation paths to provide a smooth transition between backscatter modulation and passive beamforming through smart input distribution design, including \gls{bc}, \gls{sr}, \gls{ris} as special cases.
 	% Simulation results demonstrate RIScatter can exploit smart input distribution design to provide a smooth transition between backscatter modulation and passive beamforming, which outperforms \gls{bc}, \gls{sr}, and \gls{ris}.
@@
 	The scattered signals contain no additional information, but adds constructively or destructively with the direct component to enhance desired signal or suppress interference.
-	Compared with backscatter nodes of \gls{bc}/\gls{sr}, \gls{ris} elements employ deterministic reflection pattern priorly known at transmitter and receiver.
+	Compared with scattering nodes of \gls{bc}/\gls{sr}, \gls{ris} elements employ deterministic reflection pattern priorly known at transmitter and receiver.
 	This motivated the use of fixed reflection coefficients during each channel block to improve communication, sensing, and power performances \cite{Wu2018,Zhang2019a,Lin2022,Liu2022,Feng2022,Zhao2022}.
@@
 	\emph{Fifth,} we provide numerical results to demonstrate the benefits of RIScatter and proposed algorithms.
-	It is concluded that 1) RIScatter nodes provide flexible transmit-assist tradeoff using adaptive input distribution design; 2) when primary link is absolutely prioritized, the input probability of each node is \num{1} at one state and \num{0} at the others, which coincides with discretized \gls{ris}; 3) when backscatter link is absolutely prioritized, RIScatter nodes can exploit adaptive channel coding to achieve higher instantaneous rate than uncoded equiprobable inputs of \gls{bc}/\gls{sr}; 4) the proposed \gls{kkt} input distribution design converges to stationary points, whose average performance is very close to global optimal; 5) the proposed \gls{pgd} beamforming provides larger rate region than \gls{mrt}-based schemes; 6) the decision region schemes adapted to input distribution provide higher backscatter rates than the non-adaptive \gls{ml} detector; 7) cooperation between passive nodes in terms of joint encoding can further boost the total backscatter rate; 8) the low complexity of input distribution design and the marginal effect of increasing reflection states motivates the use of low-order scatter nodes to replace high-resolution \gls{ris}.
+	It is concluded that 1) RIScatter nodes provide flexible transmit-assist tradeoff using adaptive input distribution design; 2) when primary link is absolutely prioritized, the input probability of each node is \num{1} at one state and \num{0} at the others, which coincides with discretized \gls{ris}; 3) when backscatter link is absolutely prioritized, RIScatter nodes can exploit adaptive channel coding to achieve higher instantaneous rate than uncoded equiprobable inputs of \gls{bc}/\gls{sr}; 4) the proposed \gls{kkt} input distribution design converges to stationary points, whose average performance is very close to global optimal; 5) the proposed \gls{pgd} beamforming provides larger rate region than \gls{mrt}-based schemes; 6) the decision region schemes adapted to input distribution provide higher backscatter rates than the non-adaptive \gls{ml} detector; 7) cooperation between passive nodes in terms of joint encoding can further boost the total backscatter rate; 8) the low complexity of input distribution design and the marginal effect of increasing reflection states motivates the use of low-order scattering nodes to replace high-resolution \gls{ris}.
 
@@
 		\gls{bc} and \gls{sr} commonly employ antenna-based scatterers as passive information sources.
-		By \emph{frequently switching} between the available states, each backscatter node encodes self message over scattered signal and introduces backscatter uncertainty at the receiver.
+		By \emph{frequently switching} between the available states, each scattering node encodes self message over scattered signal and introduces backscatter uncertainty at the receiver.
 		For $M$-ary \gls{qam}, reflection coefficient $\Gamma_m$ maps to the corresponding \emph{complex constellation point $c_m$} by
@@
 	\begin{equation}
-		L(d) = L_0 \biggl(\frac{d_0}{d}\biggr)^\gamma,
+		L(d) = L_0 \biggl(\frac{d_0}{d}\biggr)^\gamma
 	\end{equation}
@@
 	\begin{equation}
-		\boldsymbol{H} = \sqrt{\frac{\kappa}{1+\kappa}} \bar{\boldsymbol{H}} + \sqrt{\frac{1}{1+\kappa}} \tilde{\boldsymbol{H}}
+		\boldsymbol{H} = \sqrt{\frac{\kappa}{1+\kappa}} \bar{\boldsymbol{H}} + \sqrt{\frac{1}{1+\kappa}} \tilde{\boldsymbol{H}},
 	\end{equation}

### 2022-08-30 assets/illustration/ambient_backscatter_communication.tex
:bento: Update illustration assets

\begin{tikzpicture}[every node/.style={draw}]
	\node at (0,0) [trapezium,minimum height=0.75cm,anchor=center] {};
	\node at (3,4.5) [isosceles triangle,isosceles triangle stretches,shape border rotate=+270,minimum size=1cm,minimum height=1cm,anchor=north] {};
	\node at (7,4) [rectangle,minimum size=1cm] {};
	\node at (10,0) [trapezium,rotate=180,minimum height=0.75cm,anchor=center] {};

	\node[draw=none] at (0,-0.75) {Legacy Transmitter};
	\node[draw=none] at (3,5) {Backscatter Reader};
	\node[draw=none] at (7,5) {Scattering Node};
	\node[draw=none] at (10,-0.75) {Legacy Receiver};

	\draw[loosely dashed,-latex] (1,0) -- (9,0);
	\draw[loosely dashed,-latex] (0,0.75) -- (2.5,4);
	\draw[loosely dashed,-latex] (0.75,0.5) -- (6.25,3.5);
	\draw[dashdotted,-latex] (6.25,4.5) -- (3.75,4.5);
	\draw[dashdotted,-latex] (7.75,4) -- (10,0.75);
\end{tikzpicture}

### 2022-08-30 assets/illustration/bistatic_backscatter_communication.tex
:bento: Update illustration assets

\begin{tikzpicture}[every node/.style={draw}]
	\node at (0,0) [isosceles triangle,isosceles triangle stretches,shape border rotate=+90,minimum size=1cm,minimum height=1cm,anchor=north] {};
	\node at (7,4) [rectangle,minimum size=1cm] {};
	\node at (10,0) [isosceles triangle,isosceles triangle stretches,shape border rotate=+270,minimum size=1cm,minimum height=1cm,anchor=north] {};

	\node[draw=none] at (0,-1.5) {Carrier Emitter};
	\node[draw=none] at (7,5) {Scattering Node};
	\node[draw=none] at (10,-1.5) {Backscatter Reader};

	\draw[-latex] (1,-1) -- (9.5,-1);
	\draw[-latex] (0.5,0) -- (6,4);
	\draw[loosely dotted,-latex] (8,4) -- (10,0.5);
\end{tikzpicture}

### 2022-08-30 assets/illustration/riscatter.tex
:bento: Update illustration assets

\begin{tikzpicture}[every node/.style={draw}]
	\node at (0,0) [dart,shape border rotate=90,minimum width=1cm] {};
	\node at (7,4) [circle,minimum size=1cm] {};
	\node at (10,0.35) [dart,shape border rotate=270,minimum width=1cm] {};

	\node[draw=none] at (0,-0.75) {Primary Transmitter};
	\node[draw=none] at (7,5) {RIScatter Node};
	\node[draw=none] at (10,-0.75) {Cooperative Receiver};
	\draw[loosely dashed,-latex] (0.75,0) -- (9.25,0);
	\draw[loosely dashed,-latex] (0.5,0.5) -- (6.25,4);
	\draw[dashdotted,-latex] (7.75,4) -- (10,1);
\end{tikzpicture}

### 2022-08-30 main.tex
:pencil: Add paradigm plots

@@
 % PGF/TikZ
-\usetikzlibrary{arrows,calc,matrix,patterns,plotmarks,positioning}
+\usetikzlibrary{arrows,calc,matrix,patterns,plotmarks,positioning,shapes}
 \usepgfplotslibrary{groupplots,patchplots}
@@
 	% Simulation results demonstrate RIScatter can flexibly control the tradeoff between backscatter modulation and passive beamforming via smart input distribution design, which outperforms \gls{bc}, \gls{sr}, and \gls{ris}.
-	% Simulation results demonstrate RIScatter can exploit the additional propagation paths to provide a smooth transition between backscatter modulation and passive beamforming, which
 	Simulation results demonstrate RIScatter can exploit the additional propagation paths to provide a smooth transition between backscatter modulation and passive beamforming through smart input distribution design, including \gls{bc}, \gls{sr}, \gls{ris} as special cases.
 	% Simulation results demonstrate RIScatter can exploit smart input distribution design to provide a smooth transition between backscatter modulation and passive beamforming, which outperforms \gls{bc}, \gls{sr}, and \gls{ris}.
-
-	% The three multiple access schemes are compared, and extensive numerical results show that RSMA provides a smooth transition between SDMA and NOMA and outperforms them both in a wide range of network loads (underloaded and overloaded regimes) and user deployments (with a diversity of channel directions, channel strengths, and qualities of channel state information at the transmitter).
-Moreover, RSMA provides rate and QoS enhancements over NOMA at a lower computational complexity for the transmit scheduler and the receivers (number of SIC layers).
-
 \end{abstract}
@@
 	As an emerging low-power communication technique, \gls{bc} separates conventional transmitter into a \gls{rf} emitter with power-hungry elements (e.g., synthesizer and amplifier), and an information-bearing node with power-efficient components (e.g., harvester and modulator) \cite{Boyer2014}.
-	The node harvests energy from emitted wave and embeds information over scattered signal in a sustainable and controllable manner.
+	The node harvests energy from impinging wave and embeds information over scattered signal in a sustainable and controllable manner.
 	The backscatter reader can be either co-located or separated with the emitter, known as monostatic and bistatic \gls{bc}.
@@
 	However, traditional \gls{bc} requires dedicated carrier emitter and backscatter reader, while passive nodes only respond when externally inquired.
-	In \gls{ambc} \cite{Liu2013b}, interactive nodes recycle ambient signals generated by legacy transmitters (e.g., radio, television, and Wi-Fi) to harvest energy and establish connection in between.
-	It eliminates the need of dedicated power source, carrier emitter, and frequency spectrum, bringing more opportunities to low-power communications.
+	In \gls{ambc} \cite{Liu2013b}, interactive nodes recycle ambient signals generated by legacy transmitters (e.g., radio, television, and Wi-Fi) to harvest energy and establish connections.
+	It eliminates the need of dedicated power source, carrier emitter and frequency spectrum, bringing more opportunities to low-power communications.
 	To combat the strong direct-link interference of \gls{ambc}, \cite{Yang2018} proposed a co-located receiver that cooperatively decodes the primary (legacy) and backscatter links.
@@
 
+	\begin{figure}[!t]
+		\centering
+		\subfloat[Monostatic \gls{bc}]{
+			\resizebox{0.48\linewidth}{!}{
+				\input{assets/illustration/monostatic_backscatter_communication.tex}
+			}
+			\label{fi:monostatic_backscatter_communication}
+		}
+		\subfloat[Bistatic \gls{bc}]{
+			\resizebox{0.48\linewidth}{!}{
+				\input{assets/illustration/bistatic_backscatter_communication.tex}
+			}
+			\label{fi:bistatic_backscatter_communication}
+		}
+		\\
+		\subfloat[\gls{ambc}]{
+			\resizebox{0.48\linewidth}{!}{
+				\input{assets/illustration/ambient_backscatter_communication.tex}
+			}
+			\label{fi:ambient_backscatter_communication}
+		}
+		\subfloat[\gls{sr}]{
+			\resizebox{0.48\linewidth}{!}{
+				\input{assets/illustration/symbiotic_radio.tex}
+			}
+			\label{fi:symbiotic_radio}
+		}
+		\\
+		\subfloat[\gls{ris}]{
+			\resizebox{0.48\linewidth}{!}{
+				\input{assets/illustration/reconfigurable_intelligent_surface.tex}
+			}
+			\label{fi:reconfigurable_intelligent_surface}
+		}
+		\subfloat[RIScatter]{
+			\resizebox{0.48\linewidth}{!}{
+				\input{assets/illustration/riscatter.tex}
+			}
+			\label{fi:riscatter}
+		}
+		\caption{
+			Paradigms for scattering applications.
+		}
+		\label{fi:scatter_comparison}
+	\end{figure}
+
 	To the best of our knowledge, all relevant literatures assumed at backscatter information sources either Gaussian codebook \cite{Guo2019b,Ding2020,Long2020a,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Hu2021b} or finite equiprobable inputs \cite{Yang2018,Liang2020,Han2021,Zhang2022,Liu2019d,Bereyhi2020,Xu2020b,Zhang2021d,Hua2022,Basar2020,Ma2020a,Yuan2021,Hu2021a}.
@@
 		A natural but critical question is, for a given scatterer with pre-determined reflection pattern set, \emph{can we softly bridge backscatter modulation and passive beamforming by appropriate reflection design?}
-		This question is answered in Section \ref{se:uniscatter}.
+		This question is answered in Section \ref{se:riscatter}.
 	\end{subsection}
@@
 			}
-			\label{fi:uniscatter_distribution}
+			\label{fi:riscatter_distribution}
 		\end{figure}
 		As illustrated in Fig.
-\ref{fi:uniscatter_distribution}, instead of always using fully random or deterministic reflection pattern over time, each RIScatter node can \emph{flexibly adjust} its input distribution to balance information encoding and channel reconfiguration.
+\ref{fi:riscatter_distribution}, instead of always using fully random or deterministic reflection pattern over time, each RIScatter node can \emph{flexibly adjust} its input distribution to balance information encoding and channel reconfiguration.
 		That is, it semi-randomly select the reflection state per backscatter symbol block under the guidance of input probability $P(\Gamma_m)$ for state $m$.
@@
 			}
-			\label{fi:uniscatter_node}
+			\label{fi:riscatter_node}
 		\end{figure*}
@@
 			\footnotesize{
-				\import{assets/illustration/}{uniscatter_network.eps_tex}
+				\import{assets/illustration/}{riscatter_network.pdf_tex}
 			}
 			\caption{A single-user multi-node RIScatter system.}
-			\label{fi:uniscatter_network}
+			\label{fi:riscatter_network}
 		\end{figure}
-		To demonstrate the advantages of RIScatter, we consider a single-user multi-node \gls{miso} RIScatter system as shown in Fig. \ref{fi:uniscatter_network}.
+		To demonstrate the advantages of RIScatter, we consider a single-user multi-node \gls{miso} RIScatter system as shown in Fig. \ref{fi:riscatter_network}.
 		In the primary active point-to-point system, a $Q$-antenna \gls{ap} transmits to a single-antenna user assisted by $K$ nearby single-antenna RIScatter nodes with $M$ reflection states.
@@
 	\end{subsection}
-	\label{se:uniscatter}
+	\label{se:riscatter}
 \end{section}
@@
 	In this section, we provide numerical results to evaluate the proposed input distribution, active beamforming, and backscatter decision design for the RIScatter system in Fig.
-\ref{fi:uniscatter_network}.
+\ref{fi:riscatter_network}.
 	We assume the AP-user distance is \qty{10}{\meter}, $K=2$ RIScatter nodes are randomly dropped within a disk of radius \qty{2}{\meter} centered at the user, the \gls{ap} is with $Q=4$ transmit antennas and an average power budget $P=\qty{36}{\dBm}$, the nodes employs \num{4}-\gls{qam} with amplitude scattering ratio $\alpha=0.5$, the user is with average noise power $\sigma_v^2=\qty{-40}{\dBm}$, and the symbol period ratio is $N=20$.

### 2022-08-31 assets/illustration/ambient_backscatter_communication.tex
:bento: Update scattering paradigms

@@
-\begin{tikzpicture}[every node/.style={draw}]
-	\node at (0,0) [trapezium,minimum height=0.75cm,anchor=center] {};
-	\node at (3,4.5) [isosceles triangle,isosceles triangle stretches,shape border rotate=+270,minimum size=1cm,minimum height=1cm,anchor=north] {};
-	\node at (7,4) [rectangle,minimum size=1cm] {};
-	\node at (10,0) [trapezium,rotate=180,minimum height=0.75cm,anchor=center] {};
+\begin{tikzpicture}[font=\LARGE,every node/.style={draw,ultra thick},every path/.style={ultra thick},every text node part/.style={align=center}]
+	\node at (0,0) [dart,shape border rotate=90,minimum width=1cm] {};
+	\node at (1.5,3.5) [isosceles triangle,isosceles triangle stretches,shape border rotate=+270,minimum size=1cm,minimum height=1cm,anchor=north] {};
+	\node at (6.5,3) [rectangle,minimum size=1cm] {};
+	\node at (8,0.35) [dart,shape border rotate=270,minimum width=1cm] {};
 
-	\node[draw=none] at (0,-0.75) {Legacy Transmitter};
-	\node[draw=none] at (3,5) {Backscatter Reader};
-	\node[draw=none] at (7,5) {Scattering Node};
-	\node[draw=none] at (10,-0.75) {Legacy Receiver};
+	\node[draw=none] at (0,-1.375) {Legacy\\Transmitter};
+	\node[draw=none] at (1,4.375) {Backscatter\\Reader};
+	\node[draw=none] at (7,4.375) {Scattering\\Node};
+	\node[draw=none] at (8,-1.375) {Legacy\\Receiver};
 
-	\draw[loosely dashed,-latex] (1,0) -- (9,0);
-	\draw[loosely dashed,-latex] (0,0.75) -- (2.5,4);
-	\draw[loosely dashed,-latex] (0.75,0.5) -- (6.25,3.5);
-	\draw[dashdotted,-latex] (6.25,4.5) -- (3.75,4.5);
-	\draw[dashdotted,-latex] (7.75,4) -- (10,0.75);
+	\draw[decorate,decoration={waves,segment length=5mm}] (1,-0.5) -- (7.5,-0.5);
+	\draw[decorate,decoration={waves,segment length=5mm}] (0.25,1) -- (0.75,3);
+	\draw[decorate,decoration={waves,segment length=5mm}] (0.75,0.25) -- (5.5,2.5);
+	\draw[decorate,decoration={triangles,segment length=2.5mm}] (5.5,3.5) -- (2.5,3.5);
+	\draw[decorate,decoration={triangles,segment length=2.5mm}] (7.5,3) -- (8,1);
+
+	\node[draw=none] at (4,0.35) {Modulated\\Signal};
+	\node[draw=none] at (4,3.5) {Superimposed\\Signal};
 \end{tikzpicture}

### 2022-08-31 assets/illustration/bistatic_backscatter_communication.tex
:bento: Update scattering paradigms

@@
-\begin{tikzpicture}[every node/.style={draw}]
+\begin{tikzpicture}[font=\LARGE,every node/.style={draw,ultra thick},every path/.style={ultra thick},every text node part/.style={align=center}]
 	\node at (0,0) [isosceles triangle,isosceles triangle stretches,shape border rotate=+90,minimum size=1cm,minimum height=1cm,anchor=north] {};
-	\node at (7,4) [rectangle,minimum size=1cm] {};
-	\node at (10,0) [isosceles triangle,isosceles triangle stretches,shape border rotate=+270,minimum size=1cm,minimum height=1cm,anchor=north] {};
+	\node at (5,3) [rectangle,minimum size=1cm] {};
+	\node at (8,0) [isosceles triangle,isosceles triangle stretches,shape border rotate=+270,minimum size=1cm,minimum height=1cm,anchor=north] {};
 
-	\node[draw=none] at (0,-1.5) {Carrier Emitter};
-	\node[draw=none] at (7,5) {Scattering Node};
-	\node[draw=none] at (10,-1.5) {Backscatter Reader};
+	\node[draw=none] at (0,-2) {Carrier\\Emitter};
+	\node[draw=none] at (5,4.5) {Scattering\\Node};
+	\node[draw=none] at (8,-2) {Backscatter\\Reader};
 
-	\draw[-latex] (1,-1) -- (9.5,-1);
-	\draw[-latex] (0.5,0) -- (6,4);
-	\draw[loosely dotted,-latex] (8,4) -- (10,0.5);
+	\draw[decorate,decoration={snake,post length=2.5mm},-latex] (1,-1) -- (7.5,-1);
+	\draw[decorate,decoration={snake,post length=2.5mm},-latex] (0.5,0) -- (4,3);
+	\draw[decorate,decoration={snake,pre length=1cm,post length=1cm},-latex] (6,3) -- (8,0.35);
+
+	\node[draw=none] at (1.5,2.2) {Carrier};
+	\node[draw=none] at (7.25,2.2) {1};
+	\node[draw=none] at (6.55,3.1) {0};
+	\node[draw=none] at (7.95,1.3) {0};
 \end{tikzpicture}

### 2022-08-31 assets/illustration/riscatter.tex
:bento: Update scattering paradigms

@@
-\begin{tikzpicture}[every node/.style={draw}]
-	\node at (0,0) [dart,shape border rotate=90,minimum width=1cm] {};
-	\node at (7,4) [circle,minimum size=1cm] {};
-	\node at (10,0.35) [dart,shape border rotate=270,minimum width=1cm] {};
+\begin{tikzpicture}[font=\LARGE,every node/.style={draw,ultra thick},every path/.style={ultra thick},every text node part/.style={align=center}]
+	\node at (0,0) [circular sector,shape border rotate=90,minimum width=2cm] {};
+	\node at (5,3) [circle,minimum size=1.25cm] {};
+	\node at (8,0.55) [circular sector,shape border rotate=270,minimum width=2cm] {};
 
-	\node[draw=none] at (0,-0.75) {Primary Transmitter};
-	\node[draw=none] at (7,5) {RIScatter Node};
-	\node[draw=none] at (10,-0.75) {Cooperative Receiver};
-	\draw[loosely dashed,-latex] (0.75,0) -- (9.25,0);
-	\draw[loosely dashed,-latex] (0.5,0.5) -- (6.25,4);
-	\draw[dashdotted,-latex] (7.75,4) -- (10,1);
+	\node[draw=none] at (0,-1.25) {Primary\\Transmitter};
+	\node[draw=none] at (5,4.5) {RIScatter\\Node};
+	\node[draw=none] at (8,-1.25) {Cooperative\\Receiver};
+
+	\draw[decorate,decoration={waves,segment length=5mm}] (1,-0.25) -- (7.375,-0.25);
+	\draw[decorate,decoration={waves,segment length=5mm}] (0.5,0.75) -- (4,3);
+	\draw[decorate,decoration={triangles,segment length=2.5mm}] (6,3) -- (8,1.25);
+
+	\node[draw=none] at (4,0.875) {Modulated\\Signal};
+	\node[draw=none] at (7.8,2.9) {Superimposed\\Signal};
 \end{tikzpicture}

### 2022-08-31 assets/illustration/symbiotic_radio.tex
:bento: Update illustration assets
:bento: Update scattering paradigms

--- 2022-08-30 assets/illustration/riscatter.tex
@@
-\begin{tikzpicture}[every node/.style={draw}]
-	\node at (0,0) [dart,shape border rotate=90,minimum width=1cm] {};
-	\node at (7,4) [circle,minimum size=1cm] {};
-	\node at (10,0.35) [dart,shape border rotate=270,minimum width=1cm] {};
+\begin{tikzpicture}[font=\LARGE,every node/.style={draw,ultra thick},every path/.style={ultra thick},every text node part/.style={align=center}]
+	\node at (0,0) [circular sector,shape border rotate=90,minimum width=2cm] {};
+	\node at (5,3) [rectangle,minimum size=1cm] {};
+	\node at (8,0.55) [circular sector,shape border rotate=270,minimum width=2cm] {};
 
-	\node[draw=none] at (0,-0.75) {Primary Transmitter};
-	\node[draw=none] at (7,5) {RIScatter Node};
-	\node[draw=none] at (10,-0.75) {Cooperative Receiver};
-	\draw[loosely dashed,-latex] (0.75,0) -- (9.25,0);
-	\draw[loosely dashed,-latex] (0.5,0.5) -- (6.25,4);
-	\draw[dashdotted,-latex] (7.75,4) -- (10,1);
+	\node[draw=none] at (0,-1.25) {Primary\\Transmitter};
+	\node[draw=none] at (5,4.375) {Scattering\\Node};
+	\node[draw=none] at (8,-1.25) {Cooperative\\Receiver};
+
+	\draw[decorate,decoration={waves,segment length=5mm}] (1,-0.25) -- (7.375,-0.25);
+	\draw[decorate,decoration={waves,segment length=5mm}] (0.5,0.75) -- (4,3);
+	\draw[decorate,decoration={triangles,segment length=2.5mm}] (6,3) -- (8,1.25);
+
+	\node[draw=none] at (4,0.875) {Modulated\\Signal};
+	\node[draw=none] at (7.8,2.9) {Superimposed\\Signal};
 \end{tikzpicture}

### 2022-09-02 main.tex
:pencil: Update paradigm plots
:pencil: Update introduction

@@
 \usetikzlibrary{arrows,calc,matrix,patterns,plotmarks,positioning,shapes}
+\usetikzlibrary{decorations.pathmorphing,decorations.pathreplacing,decorations.shapes,shapes.geometric}
 \usepgfplotslibrary{groupplots,patchplots}
 \pgfplotsset{compat=newest}
-
 % algpseudocode
@@
 	In this paper, we show how those three seemingly different technologies can be unified to leverage their benefits simultaneously into a single architecture called RIScatter.
-	RIScatter is a new paradigm for future wireless networks and consists of multiple passive scattering nodes, whose reflection states can be controlled to partially engineer the wireless channel and partially modulate information onto the scattered wave.
+	RIScatter is a new paradigm for future wireless networks and consists of multiple passive scattering nodes, whose reflection states can be adapted to partially engineer the wireless channel and partially modulate information onto the scattered wave.
 	This contrasts with \gls{bc}/\gls{sr} (resp. \gls{ris}) where states are exclusively a function of information symbols (resp. \gls{csi}).
-	The key principle in RIScatter is to render the probability distribution of reflection states as a joint function of the \gls{csi} and backscatter information source, allowing universal hardware design and heterogeneous traffic control.
+	The key principle in RIScatter is to render the probability distribution of reflection states as a joint function of the \gls{csi} and input information source, allowing universal hardware design and heterogeneous traffic control.
 	% augmented \gls{qos} control.
 	This enables RISscatter to softly bridge, generalize, and outperform \gls{bc}, \gls{sr}, \gls{ris}; boil down to any of those under specific reflection states; or evolve in a mixed setup.
-	We reveal RIScatter experiences a fundamental tradeoff that balances information modulation and channel reconfiguration capabilities in a flexible and mutualistic manner.
+	We reveal RIScatter provides a fundamental tradeoff that balances information modulation and channel reconfiguration capabilities in a flexible and mutualistic manner.
 	% Instead of treating probability distribution of reflection states as equiprobable (as scattering source of \gls{bc}/\gls{sr}) or degenerate (as reflecting element of \gls{ris}), RIScatter nodes located at different places adapt the input distribution of passive scatterers based on link priority and \gls{csi}, balancing information encoding and channel reconfiguration in a flexible and mutualistic manner.
@@
 	% We consider an application scenario where a multi-antenna \gls{ap} serves a single-antenna user surrounded by multiple RIScatter nodes, and characterize the achievable primary-total-backscatter rate region by designing input distribution at the nodes, active beamforming at the \gls{ap}, and backscatter decision regions at the user.
-	An application scenario is also considered where a multi-antenna \gls{ap} serves a single-antenna user surrounded by multiple RIScatter nodes, and the achievable primary-total-backscatter rate region is characterized by optimizing input distribution at the nodes, active beamforming at the \gls{ap}, and backscatter decision regions at the user.
+	An application scenario is considered where a multi-antenna \gls{ap} serves a single-antenna user surrounded by multiple RIScatter nodes, and the achievable primary-total-backscatter rate region is characterized by optimizing input distribution at the nodes, active beamforming at the \gls{ap}, and backscatter decision regions at the user.
 	% Simulation results demonstrate RIScatter nodes can flexibly control the transmit-assist tradeoff via smart input distribution design.
 	% Simulation results demonstrate RIScatter can flexibly control the tradeoff between backscatter modulation and passive beamforming via smart input distribution design, which outperforms \gls{bc}, \gls{sr}, and \gls{ris}.
-	Simulation results demonstrate RIScatter can exploit the additional propagation paths to provide a smooth transition between backscatter modulation and passive beamforming through smart input distribution design, including \gls{bc}, \gls{sr}, \gls{ris} as special cases.
+	Simulation results demonstrate RIScatter can exploit the additional propagation paths to provide a smooth transition between backscatter modulation and passive beamforming via smart input distribution design, which includes \gls{bc}, \gls{sr}, \gls{ris} as special cases.
 	% Simulation results demonstrate RIScatter can exploit smart input distribution design to provide a smooth transition between backscatter modulation and passive beamforming, which outperforms \gls{bc}, \gls{sr}, and \gls{ris}.
@@
 \begin{section}{Introduction}
+	\begin{subsection}{Fundamentals}
 		\IEEEPARstart{F}{uture} wireless network is envisioned to provide high throughput, uniform coverage, pervasive connectivity, heterogeneous control, and cognitive intelligence for trillions of portable devices.
-	As an emerging low-power communication technique, \gls{bc} separates conventional transmitter into a \gls{rf} emitter with power-hungry elements (e.g., synthesizer and amplifier), and an information-bearing node with power-efficient components (e.g., harvester and modulator) \cite{Boyer2014}.
+		As an emerging low-power communication technique, \gls{bc} separates conventional transmitter into a \gls{rf} carrier emitter with power-hungry elements (e.g., synthesizer and amplifier) and an information-bearing node with power-efficient components (e.g., harvester and modulator) \cite{Boyer2014}.
 		The node harvests energy from impinging wave and embeds information over scattered signal in a sustainable and controllable manner.
-	The backscatter reader can be either co-located or separated with the emitter, known as monostatic and bistatic \gls{bc}.
-	Its applications such as \gls{rfid} \cite{Dobkin2012,Landt2005} and passive sensor network \cite{Vannucci2008,Assimonis2016} have been extensively researched, standardized, and commercialized to support \gls{iot} and \gls{m2m}.
+		% The backscatter reader can be either co-located or separated with the carrier emitter, known as monostatic and bistatic \gls{bc}.
+		The backscatter reader can be either co-located or separated with the carrier emitter, known as monostatic and bistatic \gls{bc} in Fig.
+\subref*{fi:monostatic_backscatter_communication} and \subref*{fi:bistatic_backscatter_communication}, respectively.
+		Its applications such as \gls{rfid} \cite{Dobkin2012,Landt2005} and passive sensor network \cite{Vannucci2008,Assimonis2016} have been extensively researched, standardized, and commercialized to support \gls{iot} and \gls{m2m} networks.
 		% ? Specifically, a dedicated emitter generates a sinusoidal carrier at reserved frequency, and \gls{rfid} tags reports their identifier to a nearby \gls{rfid} reader.
 		% ? With the upsurge of wireless devices and the downtrend of circuit power consumption, \gls{rfid} has experienced great success in \gls{ioe} and \gls{m2m} networks.
-	However, traditional \gls{bc} requires dedicated carrier emitter and backscatter reader, while passive nodes only respond when externally inquired.
-	In \gls{ambc} \cite{Liu2013b}, interactive nodes recycle ambient signals generated by legacy transmitters (e.g., radio, television, and Wi-Fi) to harvest energy and establish connections.
-	It eliminates the need of dedicated power source, carrier emitter and frequency spectrum, bringing more opportunities to low-power communications.
-	To combat the strong direct-link interference of \gls{ambc}, \cite{Yang2018} proposed a co-located receiver that cooperatively decodes the primary (legacy) and backscatter links.
-	The authors evaluated the error performance of \gls{ml}, linear, and \gls{sic} detectors for flat fading channel, and proposed a low-complexity detector for frequency-selective fading channel.
-	The concept of cooperative \gls{ambc} was then refined as \gls{sr} to cognitively incorporate \gls{ambc} with existing systems \cite{Liang2020}.
-	In \gls{sr}, the primary transmitter generates active radio carrying primary information, the secondary node modulates backscatter information onto the scattered wave, and the cooperative receiver decodes both links from two propagation paths.
-	The direct transmitter-receiver path only contains primary information, while the cascaded transmitter-node-receiver path preserves both thanks to signal characteristics.
-	Such a coexistence was further classified into commensal, parasitic, and competitive relationships based on link priority \cite{Guo2019b}, and their instantaneous rates, optimal power allocations, and outage probabilities were subsequently derived in \cite{Guo2019b,Ding2020}.
-	However, one important issue of \gls{sr} is practical cooperative decoding design.
-	Due to physical constraints at the load-switching modulator, backscatter symbol period is typically longer than primary.
-	Ideal joint \gls{ml} decoding achieves optimal performance with prohibitive computational complexity \cite{Yang2018,Liang2020,Zhang2022}.
-	For sequential decoding from primary to backscatter, \cite{Long2020a} pointed out the randomness from backscatter modulation can be modelled as either interference or channel uncertainty, depending on the symbol period ratio.
-	The authors concluded if this ratio is sufficiently large, the non-coherent primary achievable rate would asymptotically approach its coherent counterpart.
-	This motivated \cite{Long2020a,Liang2020,Guo2019b,Ding2020,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Yang2018,Han2021,Zhang2022} to first decode the primary link, perform \gls{sic}, then decode the backscatter link.
-	However, the advantage of \gls{sic} is questionable because 1) sufficiently large symbol period ratio is assumed in primary rate analysis and constraints backscatter rate; 2) backscatter pattern and signal characteristics are not fully exploited; 3) non-coherent primary encoding is required at the transmitter, while re-encoding, precoding, and subtraction are required at the receiver; 4) primary and backscatter symbols are superimposed by multiplication instead of superposition.
-	Another open issue for \gls{sr} is backscatter multiple access.
-	\cite{Xu2021a} extended \gls{sic} to multi-node scenario and proposed a backscatter \gls{noma}-based \gls{sr} with decoding order following backscatter signal strength.
-	However, its performance deteriorates fast when the number of nodes increases.
-	Backscatter \gls{tdma} was also evaluated in \cite{Yang2021a}, where each node transmits information during dedicated slot and harvests energy during others.
-	It enhances energy efficiency by transmission time and reflection ratio optimization, but requires regular feedback to passive nodes and incurs high coordination cost.
-	\cite{Vougioukas2019} controls the load-switching speed at nodes to shift the scattered signal to desired frequency bands.
-	This enables backscatter \gls{fdma} at the cost of extra bandwidth and higher power consumption.
-	To reduce coordination between passive nodes, \cite{Han2021} proposed a random code-assisted multiple access for \gls{sr} and evaluated the asymptotic \gls{sinr} using random matrix theory.
-	However, it suffers from imperfect synchronization and the near-far problem.
-
-	On the other hand, \gls{ris} is a promising technology that evolves wireless propagation environment using numerous passive reflecting elements (e.g., scattering antenna or programmable metamaterial) with adjustable amplitudes and/or phases \cite{Wu2021b}.
-	The scattered signals contain no additional information, but adds constructively or destructively with the direct component to enhance desired signal or suppress interference.
-	Compared with scattering nodes of \gls{bc}/\gls{sr}, \gls{ris} elements employ deterministic reflection pattern priorly known at transmitter and receiver.
-	This motivated the use of fixed reflection coefficients during each channel block to improve communication, sensing, and power performances \cite{Wu2018,Zhang2019a,Lin2022,Liu2022,Feng2022,Zhao2022}.
-	The concept of dynamic \gls{ris}, namely choosing independent reflection coefficients over different time slots within channel block, was first considered for resource blocks of \gls{ofdm} systems, then extended to power and information phases of \gls{wpcn} \cite{Wu2021,Wu2021d,Hua2022a}.
-	Dynamic \gls{ris} provides artificial channel diversity and flexible resource allocation, but misses the opportunity to encode its own message.
-	From an information-theoretic perspective, \cite{Karasik2020} reported using \gls{ris} as an auxiliary passive beamforming device to maximize the \gls{snr} is generally rate-suboptimal for finite input constellations.
-	Instead, joint transmitter-\gls{ris} encoding achieves the capacity of \gls{ris}-aided channel, and layered encoding with \gls{sic} decoding (i.e., \gls{sic}-based \gls{sr}) can outperform pure passive beamforming at high \gls{snr}.
-	It inspired \cite{Liu2019d,Bereyhi2020,Xu2020b,Zhang2021d,Hu2021b,Hua2022,Basar2020,Ma2020a,Yuan2021,Hu2021a} to employ \gls{ris} also as an information source to combine passive beamforming and backscatter modulation in the overall reflection pattern.
-	In particular, \emph{symbol level precoding} maps backscatter symbols to \gls{ris} coefficient sets optimized for detection \cite{Liu2019d,Bereyhi2020}, \emph{overlay modulation} superposes information-bearing symbols over a common auxiliary matrix \cite{Xu2020b,Zhang2021d,Hu2021b,Hua2022}, \emph{spatial modulation} switches between reflection coefficient sets that maximize \gls{snr} at different receive antennas \cite{Basar2020,Ma2020a,Yuan2021}, and \emph{index modulation} divides \gls{ris} into reflection elements for passive beamforming and information elements for on-off modulation \cite{Hu2021a}.
-	However, those \gls{ris}-empowered \gls{bc}/\gls{sr} designs involve advanced hardware architecture, high optimization complexity, and additional control overhead.
+		However, traditional \gls{bc} nodes only respond when externally inquired.
+		In \gls{ambc} \cite{Liu2013b}, interactive nodes recycle ambient signals from legacy transmitters (e.g., radio, television and Wi-Fi) to harvest energy and establish connections.
+		As illustrated in Fig.
+\subref*{fi:ambient_backscatter_communication}, it eliminates the need of dedicated power supply, carrier emitter and frequency spectrum, bringing more opportunities to low-power communications.
+		To combat the strong direct-link interference of \gls{ambc}, \cite{Yang2018} proposed a co-located receiver that cooperatively decodes both primary (legacy) and backscatter links.
+		% The authors evaluated the error performance of \gls{ml}, linear, and \gls{sic} detectors for flat fading channel, and proposed a low-complexity detector for frequency-selective fading channel.
+		The concept of cooperative \gls{ambc} was further refined as \gls{sr} in Fig. \subref*{fi:symbiotic_radio} that cognitively incorporates \gls{ambc} with existing systems \cite{Liang2020}.
+		% In \gls{sr}, the primary transmitter generates active radio carrying primary information, the backscatter node modulates own information onto the scattered wave, and the co-located receiver decodes both links from two propagation paths.
+		% In \gls{sr}, the primary transmitter generates active radio and modulates primary information, the passive node scatters incoming wave and superimposes backscatter information, and the co-located receiver decodes both links from two propagation paths.
+		In \gls{sr}, the primary transmitter generates active radio and modulates primary information, the passive node scatters incoming wave and superimposes backscatter information, while the co-located receiver decodes both links from both propagation paths.
+		% The direct transmitter-receiver path only convey
+		% The component over the direct transmitter-receiver path only
+		% The direct transmitter-receiver path contains primary information, and the cascaded transmitter-node-receiver path preserves both information in a superimposed manner.
+		% The direct transmitter-receiver path only contains modulated primary signal while the cascaded transmitter-node-receiver path preserves superimposed signal
+		% both thanks to signal characteristics.
+		% Such a coexistence was further classified into commensal, parasitic, and competitive relationships based on link priority \cite{Guo2019b}, and their instantaneous rates, optimal power allocations, and outage probabilities were subsequently derived in \cite{Guo2019b,Ding2020}.
+		% However, one important issue of \gls{sr} is practical cooperative decoding design.
+		% Due to physical constraints at the load-switching modulator, backscatter symbol period is typically longer than primary.
+		% Ideal joint \gls{ml} decoding achieves optimal performance with prohibitive computational complexity \cite{Yang2018,Liang2020,Zhang2022}.
+		% For sequential decoding from primary to backscatter, \cite{Long2020a} pointed out the randomness from backscatter modulation can be modelled as either interference or channel uncertainty, depending on the symbol period ratio.
+		% The authors concluded if this ratio is sufficiently large, the non-coherent primary achievable rate would asymptotically approach its coherent counterpart.
+		% This motivated \cite{Long2020a,Liang2020,Guo2019b,Ding2020,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Yang2018,Han2021,Zhang2022} to first decode the primary link, perform \gls{sic}, then decode the backscatter link.
+		% However, the advantage of \gls{sic} is questionable because 1) sufficiently large symbol period ratio is assumed in primary rate analysis and constraints backscatter rate; 2) backscatter pattern and signal characteristics are not fully exploited; 3) non-coherent primary encoding is required at the transmitter, while re-encoding, precoding, and subtraction are required at the receiver; 4) primary and backscatter symbols are superimposed by multiplication instead of superposition.
+		% Another open issue for \gls{sr} is backscatter multiple access.
+		% \cite{Xu2021a} extended \gls{sic} to multi-node scenario and proposed a backscatter \gls{noma}-based \gls{sr} with decoding order following backscatter signal strength.
+		% However, its performance deteriorates fast when the number of nodes increases.
+		% Backscatter \gls{tdma} was also evaluated in \cite{Yang2021a}, where each node transmits information during dedicated slot and harvests energy during others.
+		% It enhances energy efficiency by transmission time and reflection ratio optimization, but requires regular feedback to passive nodes and incurs high coordination cost.
+		% \cite{Vougioukas2019} controls the load-switching speed at nodes to shift the scattered signal to desired frequency bands.
+		% This enables backscatter \gls{fdma} at the cost of extra bandwidth and higher power consumption.
+		% To reduce coordination between passive nodes, \cite{Han2021} proposed a random code-assisted multiple access for \gls{sr} and evaluated the asymptotic \gls{sinr} using random matrix theory.
+		% However, it suffers from imperfect synchronization and the near-far problem.
+		On the other hand, \gls{ris} in Fig.
+\subref*{fi:reconfigurable_intelligent_surface} is a promising technology that evolves wireless propagation environment using numerous passive reflecting elements (e.g., scattering antenna or programmable metamaterial) with adjustable amplitudes and/or phases \cite{Wu2021b}.
+		With proper phase shift design, the scattered components can add constructively/destructively with the direct component for signal enhancement/interference suppression.
+		% Compared with scattering nodes of \gls{bc}/\gls{sr}, \gls{ris} elements embed no additional information and use deterministic reflection pattern priorly known at the transmitter and receiver.
+		Compared with scattering nodes of \gls{bc}/\gls{sr}, \gls{ris} elements embed no additional information and use fixed reflection pattern over time, which can be optimized and fed back to the transmitter and receiver during coordination phase.
+		% , which can be priorly known at the transmitter and receiver.
+		% contain no additional information
+
+		% employ deterministic reflection pattern over time that contains no information
+
+		% and priorly known at transmitter and receiver.
+		% This motivated the use of fixed reflection coefficients during each channel block to improve communication, sensing, and power performances \cite{Wu2018,Zhang2019a,Lin2022,Liu2022,Feng2022,Zhao2022}.
+		% The concept of dynamic \gls{ris}, namely choosing independent reflection coefficients over different time slots within channel block, was first considered for resource blocks of \gls{ofdm} systems, then extended to power and information phases of \gls{wpcn} \cite{Wu2021,Wu2021d,Hua2022a}.
+		% Dynamic \gls{ris} provides artificial channel diversity and flexible resource allocation, but misses the opportunity to encode its own message.
+		% From an information-theoretic perspective, \cite{Karasik2020} reported using \gls{ris} as an auxiliary passive beamforming device to maximize the \gls{snr} is generally rate-suboptimal for finite input constellations.
+		% Instead, joint transmitter-\gls{ris} encoding achieves the capacity of \gls{ris}-aided channel, and layered encoding with \gls{sic} decoding (i.e., \gls{sic}-based \gls{sr}) can outperform pure passive beamforming at high \gls{snr}.
+		% It inspired \cite{Liu2019d,Bereyhi2020,Xu2020b,Zhang2021d,Hu2021b,Hua2022,Basar2020,Ma2020a,Yuan2021,Hu2021a} to employ \gls{ris} also as an information source to combine passive beamforming and backscatter modulation in the overall reflection pattern.
+		% In particular, \emph{symbol level precoding} maps backscatter symbols to \gls{ris} coefficient sets optimized for detection \cite{Liu2019d,Bereyhi2020}, \emph{overlay modulation} superposes information-bearing symbols over a common auxiliary matrix \cite{Xu2020b,Zhang2021d,Hu2021b,Hua2022}, \emph{spatial modulation} switches between reflection coefficient sets that maximize \gls{snr} at different receive antennas \cite{Basar2020,Ma2020a,Yuan2021}, and \emph{index modulation} divides \gls{ris} into reflection elements for passive beamforming and information elements for on-off modulation \cite{Hu2021a}.
+		% However, those \gls{ris}-empowered \gls{bc}/\gls{sr} designs involve advanced hardware architecture, high optimization complexity, and additional control overhead.
 
@@
 			\caption{
-			Paradigms for scattering applications.
+				Paradigms for various scattering applications.
 			}
@@
 		\end{figure}
-
-	To the best of our knowledge, all relevant literatures assumed at backscatter information sources either Gaussian codebook \cite{Guo2019b,Ding2020,Long2020a,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Hu2021b} or finite equiprobable inputs \cite{Yang2018,Liang2020,Han2021,Zhang2022,Liu2019d,Bereyhi2020,Xu2020b,Zhang2021d,Hua2022,Basar2020,Ma2020a,Yuan2021,Hu2021a}.
+	\end{subsection}
+
+	\begin{subsection}{Related Works}
+		Similar to \gls{cr}, the coexistence of primary and backscatter links in \gls{sr} can be classified into commensal, parasitic, and competitive relationships, whose instantaneous rates, power schemes, and outage probabilities were acquired in \cite{Guo2019b,Ding2020}.
+		To evaluate the performance of cooperative \gls{sr} receivers, \cite{Yang2018} derived the bit error rates of \gls{ml}, linear, and \gls{sic} detectors for flat fading channels, then proposed a low-complexity detector for frequency-selective fading channels.
+		However, it assumed equal symbol period of both links with perfect synchronization, which is impractical due to the load-switching speed constraint.
+		Although joint \gls{ml} decoding achieves the optimal detection performance for arbitrary backscatter-over-primary symbol period ratio, the computational complexity is prohibitive especially for high-order constellations \cite{Yang2018,Liang2020,Zhang2022}.
+		For sequential primary-backscatter decoding, the randomness of backscatter modulation can be modelled as either interference or channel uncertainty, depending on the symbol period ratio \cite{Long2020a}.
+		If this ratio is sufficiently large, the authors proved the non-coherent primary achievable rate would approach its coherent counterpart asymptotically.
+		This motivated \cite{Long2020a,Liang2020,Guo2019b,Ding2020,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Yang2018,Han2021,Zhang2022} to perform \gls{sic} from primary to backscatter links.
+		However, the advantages of such \gls{sic} remain questionable as
+		1) primary rate analysis is backed by long backscatter symbol period that constrains backscatter rate;
+		2) reflection pattern and signal characteristics are not fully exploited;
+		3) non-coherent primary encoding is required at the transmitter while re-encoding, precoding and subtraction are required at the receiver;
+		4) primary and backscatter symbols are superimposed by multiplication instead of superposition.
+
+		Another open issue for \gls{bc} and \gls{sr} is node multiple access.
+		\cite{Xu2021a} proposed a \gls{noma}-based \gls{sr} with \gls{sic} order in backscatter equivalent channel strength, whose performance deteriorates fast when the number of nodes increases.
+		\gls{tdma}-based \gls{sr} was also considered in \cite{Yang2021a} where each node transmits information during its dedicated slot and harvests energy during others.
+		It allows adaptive transmission time and reflection ratio optimization, but requires regular feedback and incurs high coordination cost.
+		\cite{Vougioukas2019} controls the load-switching speed to shift the scattered signal to the desired frequency band.
+		This enables backscatter \gls{fdma} at the cost of extra bandwidth and higher power consumption.
+		To reduce coordination burden for passive nodes, \cite{Han2021} proposed a random code-assisted multiple access for \gls{sr} and evaluated the asymptotic \gls{sinr} using random matrix theory.
+		However, this code-domain solution suffers from imperfect synchronization and the near-far problem.
+
+		Conventional \gls{ris} design with fixed reflection coefficients during each channel block has been extensively studied in communication, sensing, and power literatures \cite{Wu2018,Zhang2019a,Lin2022,Liu2022,Feng2022,Zhao2022}.
+		In contrast, dynamic \gls{ris} that chooses independent reflection coefficients over different time slots has gained recent attentions in multi-user and multi-purpose wireless networks.
+		The concept was first considered for resource blocks of \gls{ofdm} systems, then extended to power and information phases of \gls{wpcn} \cite{Wu2021,Wu2021d,Hua2022a}.
+		Dynamic \gls{ris} provides artificial channel diversity and flexible resource allocation, but misses the opportunity to encode its own message.
+		From an information-theoretic perspective, \cite{Karasik2020} reported using \gls{ris} as an auxiliary passive beamforming device to maximize the \gls{snr} is generally rate-suboptimal for finite input constellations.
+		Instead, joint transmitter-\gls{ris} encoding achieves the capacity of \gls{ris}-aided channel, and layered encoding with \gls{sic} decoding (i.e., \gls{sic}-based \gls{sr}) can outperform pure passive beamforming at high \gls{snr}.
+		It inspired \cite{Liu2019d,Bereyhi2020,Xu2020b,Zhang2021d,Hu2021b,Hua2022,Basar2020,Ma2020a,Yuan2021,Hu2021a} to employ \gls{ris} also as an information source to combine passive beamforming and backscatter modulation in the overall reflection pattern.
+		In particular, \emph{symbol level precoding} maps backscatter symbols to optimized \gls{ris} coefficient sets \cite{Liu2019d,Bereyhi2020}, \emph{overlay modulation} superposes information-bearing symbols over a common auxiliary matrix \cite{Xu2020b,Zhang2021d,Hu2021b,Hua2022}, \emph{spatial modulation} switches between reflection coefficient sets that maximize \gls{snr} at different receive antennas \cite{Basar2020,Ma2020a,Yuan2021}, and \emph{index modulation} divides \gls{ris} into reflection elements for passive beamforming and information elements for on-off modulation \cite{Hu2021a}.
+		However, those \gls{ris}-empowered \gls{bc}/\gls{sr} designs involve advanced hardware architecture, high optimization complexity, and additional control overhead.
+		Besides, all relevant literatures assumed at backscatter information sources either Gaussian codebook \cite{Guo2019b,Ding2020,Long2020a,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Hu2021b} or finite equiprobable inputs \cite{Yang2018,Liang2020,Han2021,Zhang2022,Liu2019d,Bereyhi2020,Xu2020b,Zhang2021d,Hua2022,Basar2020,Ma2020a,Yuan2021,Hu2021a}.
 		The former is impractical for passive backscatter devices, while the latter does not fully exploit reflection pattern and \gls{csi}.
-	In this paper, we introduce RIScatter that generalizes \gls{bc}, \gls{sr}, and \gls{ris} to manipulate the transmit-assist tradeoff via smart input distribution and practical receiver design.
-	The contributions of this paper are summarized as follows.
+	\end{subsection}
+
+	% To the best of our knowledge, all relevant literatures assumed at backscatter information sources either Gaussian codebook \cite{Guo2019b,Ding2020,Long2020a,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Hu2021b} or finite equiprobable inputs \cite{Yang2018,Liang2020,Han2021,Zhang2022,Liu2019d,Bereyhi2020,Xu2020b,Zhang2021d,Hua2022,Basar2020,Ma2020a,Yuan2021,Hu2021a}.
+	% The former is impractical for passive backscatter devices, while the latter does not fully exploit reflection pattern and \gls{csi}.
+	\begin{subsection}{Contributions}
+		We introduce RIScatter that generalizes \gls{bc}, \gls{sr}, and \gls{ris} to manipulate the transmit-assist tradeoff via smart input distribution and practical receiver design.
+		The paradigm of RIScatter is presented in Fig. \subref*{fi:riscatter}, and the contributions of this paper are summarized as follows.
 
@@
 		It is concluded that 1) RIScatter nodes provide flexible transmit-assist tradeoff using adaptive input distribution design; 2) when primary link is absolutely prioritized, the input probability of each node is \num{1} at one state and \num{0} at the others, which coincides with discretized \gls{ris}; 3) when backscatter link is absolutely prioritized, RIScatter nodes can exploit adaptive channel coding to achieve higher instantaneous rate than uncoded equiprobable inputs of \gls{bc}/\gls{sr}; 4) the proposed \gls{kkt} input distribution design converges to stationary points, whose average performance is very close to global optimal; 5) the proposed \gls{pgd} beamforming provides larger rate region than \gls{mrt}-based schemes; 6) the decision region schemes adapted to input distribution provide higher backscatter rates than the non-adaptive \gls{ml} detector; 7) cooperation between passive nodes in terms of joint encoding can further boost the total backscatter rate; 8) the low complexity of input distribution design and the marginal effect of increasing reflection states motivates the use of low-order scattering nodes to replace high-resolution \gls{ris}.
+	\end{subsection}
 

### 2022-09-02 main.tex
:pencil: Update problem description

@@
 		Scattering source of \gls{bc}/\gls{sr} and reflecting element of \gls{ris} can be regarded as its extreme cases, where the input distribution boils down to equiprobable and degenerate, respectively.
-		Like aforementioned \gls{ris}-empowered \gls{bc}/\gls{sr} schemes, the passive nodes require regular coordination with active devices, but the advantages are 1) RIScatter nodes can be built over conventional load-switching scatterers instead of composite metamaterial; 2) the optimization cost of input distribution is much lower than that of \gls{ris} reflection coefficients; 3) adaptive backscatter channel coding can exploit \gls{csi} to achieve higher instantaneous rate than conventional uncoded transmission; 4) the dispersed characteristics of RIScatter nodes and legacy users avoids the development optimization and allows uniformly good performance for both links.
+		Like aforementioned \gls{ris}-empowered \gls{bc}/\gls{sr} schemes, the passive nodes require regular coordination with active devices, but the advantages are 1) RIScatter nodes can be built over conventional load-switching scatterers instead of composite metamaterial; 2) the optimization cost of input distribution is much lower than that of \gls{ris} reflection coefficients; 3) adaptive backscatter channel coding can exploit \gls{csi} to achieve higher instantaneous rate than conventional uncoded transmission; 4) the potentially dispersed characteristics of RIScatter nodes (and legacy users) avoids the development optimization and allows uniformly good performance for both links.
 
@@
 		To investigate how RIScatter unifies \gls{bc}, \gls{sr} and \gls{ris} for the benefits of both coexisting subsystems, we provide primary and backscatter rate analyses and emphasize the contributions of input distribution at RIScatter nodes, active beamforming at the \gls{ap}, and backscatter decision regions at the user.
-		This is the first paper to reveal the importance of those factors in \gls{ris}-empowered \gls{bc}/\gls{sr}.
+		This is the first paper to reveal the importance of those factors in joint \gls{ris} and \gls{bc}/\gls{sr} design.
 
@@
 	Scattering refers to a change of moving direction of particles after colliding with others.
-	It often involves \emph{diffuse reflection} where an incident ray is redistributed at many angles.
-	An electromagnetic wave is scattered when an obstruction is placed in its propagation path.
+	An electromagnetic wave is scattered to many angles when an obstruction is placed in its propagation path.
 	In this section, we first introduce two common scatterer categories and review their operation principles, then briefly discuss how scatterers realize backscatter modulation and channel reconfiguration over reflection patterns.
@@
 		where $\beta_m \in \mathbb{I}$ is the overall amplitude scattering ratio of state $m$.
+		Lossless \gls{ris} assumes $\beta_m=1$ to maximize the available scattering power.
 	\end{subsection}
@@
 \begin{section}{RIScatter}
-	Using shared spectrum, energy and infrastructures, RIScatter is a novel passive communication/assistance protocol that generalizes \gls{bc}, \gls{sr} and \gls{ris} in a \emph{geographically} and \emph{probabilistically} distributed manner.
-	In particular, passive RIScatter nodes located at different places ride over an active legacy transmission in a flexible and mutualistic manner, while practical RIScatter receiver cooperatively decodes both primary and backscatter links under the benefits of backscatter modulation and passive beamforming.
+	Using shared spectrum, energy and infrastructures, RIScatter is a novel passive communication/assistance protocol that generalizes \gls{bc}, \gls{sr} and \gls{ris} from the perspective of input distribution.
+	In particular, the potentially dispersed passive RIScatter nodes ride over an active legacy transmission in a flexible and mutualistic manner, while the practical RIScatter receiver cooperatively decodes both primary and backscatter links under the benefits of backscatter modulation and passive beamforming.
 	% TODO compare BC, SR and IRS
@@
 		Such an adaptive backscatter channel coding coincides with \gls{ris} when primary link is absolutely prioritized, and outperforms the uncoded equiprobable inputs of \gls{bc}/\gls{sr} when backscatter link is absolutely prioritized.
-		Besides, the dispersed characteristics of RIScatter nodes and legacy users avoids the development optimization and allows uniformly good performance for both links.
+		Besides, the dispersed characteristics of RIScatter nodes (and legacy users) avoids the development optimization and allows uniformly good performance for both links.
 
@@
 		then perform backscatter channel coding on top of it.
+		\label{se:system_model}
 	\end{subsection}
@@
 		where $\rho \in \mathbb{I}$ is the relative priority of the primary link.
+		\label{se:information_theory}
 	\end{subsection}
@@
 \begin{section}{Rate-Region Characterization}
+	We notice the primary ergodic mutual information \eqref{eq:primary_mutual_information} relates to input distribution and active beamforming, while the total backscatter mutual information \eqref{eq:backscatter_mutual_information} depends explicitly on input distribution and implicitly on active beamforming and decision thresholds via backscatter \gls{dmtmac} \eqref{eq:dmtmac}.
 	To characterize the achievable primary-total-backscatter rate region of the proposed RIScatter system, we aim to maximize the weighted sum mutual information with respect to input distribution $\{\boldsymbol{p}_k\}_{k \in \mathcal{K}}$, active beamforming $\boldsymbol{w}$, and decision thresholds $\boldsymbol{t}$ as
@@
 	\end{maxi!}
+
+	Problem \eqref{op:weighted_sum_rate} introduces adaptive backscatter channel coding over conventional \gls{bc}/\gls{sr} designs.
+	% Problem \eqref{op:weighted_sum_rate} generalizes conventional \gls{bc}/\gls{sr} by allowing adaptive backscatter channel coding.
+	On the other hand, it also generalizes the discrete \gls{ris} phase shift selection problem by relaxing the feasible domain from the vertices of $M$-dimensional probability simplex to the simplex itself.
 	Since problem \eqref{op:weighted_sum_rate} is highly non-convex, we propose a \gls{bcd} algorithm that iteratively updates $\{\boldsymbol{p}_k\}_{k \in \mathcal{K}}$, $\boldsymbol{w}$ and $\boldsymbol{t}$ until convergence.
@@
 		\begin{remark}
-			In terms of total backscatter rate, the dispersed nodes with given input distribution can be viewed as an equivalent source with augmented alphabet of backscatter symbol tuples $\{x_{m_{\mathcal{K}}}\}$.
+			In terms of total backscatter rate, the potentially dispersed nodes with given input distribution can be viewed as an equivalent source with augmented alphabet of backscatter symbol tuples $\{x_{m_{\mathcal{K}}}\}$.
 			As such, the \gls{dmtmac} \eqref{eq:dmtmac} is essentially a \gls{dmtc}, and problem \eqref{op:decision_threshold} reduces to the rate-optimal quantization design for a discrete-input continuous-output memoryless channel.
@@
 			\begin{itemize}
-				\item \emph{Exhaustion:} Exhaustive grid search over the probability $K$-simplex with resolution $\Delta p = \num{1e-3}$;
+				\item \emph{Exhaustion:} Exhaustive grid search over the $M$-dimensional probability simplex with resolution $\Delta p = \num{1e-3}$;
 				\item \emph{\gls{kkt}:} Numerical \gls{kkt} solution evaluation by Algorithm \ref{al:input_distribution};

### 2022-09-03 main.tex
:pencil: Update discussion on coding

@@
 		Scattering source of \gls{bc}/\gls{sr} and reflecting element of \gls{ris} can be regarded as its extreme cases, where the input distribution boils down to equiprobable and degenerate, respectively.
-		Like aforementioned \gls{ris}-empowered \gls{bc}/\gls{sr} schemes, the passive nodes require regular coordination with active devices, but the advantages are 1) RIScatter nodes can be built over conventional load-switching scatterers instead of composite metamaterial; 2) the optimization cost of input distribution is much lower than that of \gls{ris} reflection coefficients; 3) adaptive backscatter channel coding can exploit \gls{csi} to achieve higher instantaneous rate than conventional uncoded transmission; 4) the potentially dispersed characteristics of RIScatter nodes (and legacy users) avoids the development optimization and allows uniformly good performance for both links.
+		Like aforementioned \gls{ris}-empowered \gls{bc}/\gls{sr} schemes, the passive nodes require regular coordination with active devices, but the advantages are 1) RIScatter nodes can be built over conventional load-switching scatterers instead of composite metamaterial; 2) the optimization cost of input distribution is much lower than that of \gls{ris} reflection coefficients; 3) adaptive backscatter channel coding can exploit \gls{csi} to achieve higher instantaneous rate than conventional equiprobable line coding in \gls{bc}/\gls{sr}; 4) the potentially dispersed characteristics of RIScatter nodes (and legacy users) avoids the development optimization and allows uniformly good performance for both links.
 
@@
 		\emph{Fifth,} we provide numerical results to demonstrate the benefits of RIScatter and proposed algorithms.
-		It is concluded that 1) RIScatter nodes provide flexible transmit-assist tradeoff using adaptive input distribution design; 2) when primary link is absolutely prioritized, the input probability of each node is \num{1} at one state and \num{0} at the others, which coincides with discretized \gls{ris}; 3) when backscatter link is absolutely prioritized, RIScatter nodes can exploit adaptive channel coding to achieve higher instantaneous rate than uncoded equiprobable inputs of \gls{bc}/\gls{sr}; 4) the proposed \gls{kkt} input distribution design converges to stationary points, whose average performance is very close to global optimal; 5) the proposed \gls{pgd} beamforming provides larger rate region than \gls{mrt}-based schemes; 6) the decision region schemes adapted to input distribution provide higher backscatter rates than the non-adaptive \gls{ml} detector; 7) cooperation between passive nodes in terms of joint encoding can further boost the total backscatter rate; 8) the low complexity of input distribution design and the marginal effect of increasing reflection states motivates the use of low-order scattering nodes to replace high-resolution \gls{ris}.
+		It is concluded that 1) RIScatter nodes provide flexible transmit-assist tradeoff using adaptive input distribution design; 2) when primary link is absolutely prioritized, the input probability of each node is \num{1} at one state and \num{0} at the others, which coincides with discretized \gls{ris}; 3) when backscatter link is absolutely prioritized, RIScatter nodes can exploit adaptive channel coding to achieve higher instantaneous rate than conventional equiprobable inputs of \gls{bc}/\gls{sr}; 4) the proposed \gls{kkt} input distribution design converges to stationary points, whose average performance is very close to global optimal; 5) the proposed \gls{pgd} beamforming provides larger rate region than \gls{mrt}-based schemes; 6) the decision region schemes adapted to input distribution provide higher backscatter rates than the non-adaptive \gls{ml} detector; 7) cooperation between passive nodes in terms of joint encoding can further boost the total backscatter rate; 8) the low complexity of input distribution design and the marginal effect of increasing reflection states motivates the use of low-order scattering nodes to replace high-resolution \gls{ris}.
 	\end{subsection}
@@
 		Based on link priority and \gls{csi}, RIScatter nodes adapt the \emph{state input probability distribution} of antenna-based scatterers to unify backscatter modulation and passive beamforming.
-		The scattering sources of \gls{bc}/\gls{sr} and reflecting elements of \gls{ris} can be viewed as its extreme cases, where the input distribution boils down to equiprobable and degenerate, respectively.
+		Conventional line-coded \gls{bc}/\gls{sr} nodes (e.g., EPC Gen 2 UHF \gls{rfid} using FM0) and deterministic \gls{ris} elements can be viewed as its extreme cases, where the input distribution boils down to equiprobable and degenerate, respectively.
 		\begin{figure}[!t]
@@
 		That is, it semi-randomly select the reflection state per backscatter symbol block under the guidance of input probability $P(\Gamma_m)$ for state $m$.
-		Such an adaptive backscatter channel coding coincides with \gls{ris} when primary link is absolutely prioritized, and outperforms the uncoded equiprobable inputs of \gls{bc}/\gls{sr} when backscatter link is absolutely prioritized.
+		Such an adaptive backscatter channel coding coincides with \gls{ris} when primary link is absolutely prioritized, and outperforms the conventional equiprobable line-coded \gls{bc}/\gls{sr} when backscatter link is absolutely prioritized.
 		Besides, the dispersed characteristics of RIScatter nodes (and legacy users) avoids the development optimization and allows uniformly good performance for both links.
@@
 		gradually progresses from slightly skewed to completely biased.
-		For $\rho=0$ where backscatter performance is absolutely prioritized, the \gls{csi}-adaptive channel coding at the RIScatter node provides higher backscatter rate than conventional \gls{bc} and \gls{sr} nodes with uncoded equiprobable inputs, and some states may end up unused since they cannot produce enough energy difference over the existing alphabet.
+		For $\rho=0$ where backscatter performance is absolutely prioritized, the \gls{csi}-adaptive channel coding at the RIScatter node provides higher backscatter rate than conventional \gls{bc} and \gls{sr} nodes with equiprobable inputs, and some states may end up unused since they cannot produce enough energy difference over the existing alphabet.
 		On the other hand, for $\rho=1$ where primary performance is absolutely prioritized, the input probability is \num{1} at the state that maximizes the primary equivalent channel strength, and \num{0} at the others.

### 2022-09-05 main.tex
:pencil: Update contributions

@@
 		Scattering source of \gls{bc}/\gls{sr} and reflecting element of \gls{ris} can be regarded as its extreme cases, where the input distribution boils down to equiprobable and degenerate, respectively.
-		Like aforementioned \gls{ris}-empowered \gls{bc}/\gls{sr} schemes, the passive nodes require regular coordination with active devices, but the advantages are 1) RIScatter nodes can be built over conventional load-switching scatterers instead of composite metamaterial; 2) the optimization cost of input distribution is much lower than that of \gls{ris} reflection coefficients; 3) adaptive backscatter channel coding can exploit \gls{csi} to achieve higher instantaneous rate than conventional equiprobable line coding in \gls{bc}/\gls{sr}; 4) the potentially dispersed characteristics of RIScatter nodes (and legacy users) avoids the development optimization and allows uniformly good performance for both links.
+		Like aforementioned \gls{ris}-empowered \gls{bc}/\gls{sr} schemes, the passive nodes require regular coordination with ambient devices, but the advantages are
+		1) RIScatter nodes can be built over universal load-switching scatterers instead of composite metamaterial;
+		2) backscatter modulation and passive beamforming are unified by input distribution instead of advanced hardware architecture;
+		3) optimization cost of input distribution is much lower than that of \gls{ris} reflection coefficients;
+		4) adaptive backscatter channel coding can exploit \gls{csi} to achieve higher instantaneous rate than conventional equiprobable line coding in \gls{bc}/\gls{sr};
+		5) the potentially dispersed characteristics of RIScatter nodes (and legacy users) avoids the development optimization and allows uniformly good performance for both links.
 
 		\emph{Second,} we propose a practical RIScatter receiver that semi-coherently decodes RIScatter nodes from the received energy per backscatter block, re-encodes for their reflection patterns, retrieves primary equivalent channel as if dynamic passive beamforming, then coherently decodes the primary link under the enhanced multipath.
-		The proposed receiver 1) preserves the benefits of backscatter modulation and passive beamforming; 2) enjoys lower computational and operational complexities than joint \gls{ml} and \gls{sic} schemes; 3) accommodates the link difference and suits for diverse symbol period ratios; 4) requires minor modification over legacy hardware.
+		The proposed receiver
+		1) preserves the benefits of backscatter modulation and passive beamforming;
+		2) enjoys lower computational and operational complexities than joint \gls{ml} and \gls{sic} schemes;
+		3) accommodates the link difference and suits for diverse symbol period ratios;
+		4) requires minor modification over legacy hardware.
 
@@
 		\emph{Fifth,} we provide numerical results to demonstrate the benefits of RIScatter and proposed algorithms.
-		It is concluded that 1) RIScatter nodes provide flexible transmit-assist tradeoff using adaptive input distribution design; 2) when primary link is absolutely prioritized, the input probability of each node is \num{1} at one state and \num{0} at the others, which coincides with discretized \gls{ris}; 3) when backscatter link is absolutely prioritized, RIScatter nodes can exploit adaptive channel coding to achieve higher instantaneous rate than conventional equiprobable inputs of \gls{bc}/\gls{sr}; 4) the proposed \gls{kkt} input distribution design converges to stationary points, whose average performance is very close to global optimal; 5) the proposed \gls{pgd} beamforming provides larger rate region than \gls{mrt}-based schemes; 6) the decision region schemes adapted to input distribution provide higher backscatter rates than the non-adaptive \gls{ml} detector; 7) cooperation between passive nodes in terms of joint encoding can further boost the total backscatter rate; 8) the low complexity of input distribution design and the marginal effect of increasing reflection states motivates the use of low-order scattering nodes to replace high-resolution \gls{ris}.
+		It is concluded that
+		1) RIScatter nodes provide flexible transmit-assist tradeoff using adaptive input distribution design;
+		2) when primary link is absolutely prioritized, the input probability of each node is \num{1} at one state and \num{0} at the others, which coincides with discretized \gls{ris};
+		3) when backscatter link is absolutely prioritized, RIScatter nodes can exploit adaptive channel coding to achieve higher instantaneous rate than conventional equiprobable inputs of \gls{bc}/\gls{sr};
+		4) the proposed \gls{kkt} input distribution design converges to stationary points, whose average performance is very close to global optimal;
+		5) the proposed \gls{pgd} beamforming provides larger rate region than \gls{mrt}-based schemes;
+		6) the decision region schemes adapted to input distribution provide higher backscatter rates than the non-adaptive \gls{ml} detector;
+		7) cooperation between passive nodes in terms of joint encoding can further boost the total backscatter rate;
+		8) the low complexity of input distribution design and the marginal effect of increasing reflection states motivates the use of low-order scattering nodes to replace high-resolution \gls{ris}.
 	\end{subsection}

### 2022-10-11 main.tex
:construction: Add notes
:paintbrush: Add scattering comparison

--- 2022-09-03 main.tex
@@
 \usepackage{bookmark}
+\usepackage{booktabs}
 \usepackage[american]{circuitikz}
@@
 \usepackage[caption=false,font=footnotesize,subrefformat=parens,labelformat=parens]{subfig}
+\usepackage{tabularx}
 \usepackage{tikz}
@@
 \newacronym{wpt}{WPT}{Wireless Power Transfer}
+\newacronym{mbc}{MBC}{Monostatic Backscatter Communications}
+\newacronym{bbc}{BBC}{Bistatic Backscatter Communications}
 
@@
 		% The backscatter reader can be either co-located or separated with the carrier emitter, known as monostatic and bistatic \gls{bc}.
-		The backscatter reader can be either co-located or separated with the carrier emitter, known as monostatic and bistatic \gls{bc} in Fig.
+		The backscatter reader can be either co-located or separated with the carrier emitter, known as \gls{mbc} and \gls{bbc} in Fig.
 \subref*{fi:monostatic_backscatter_communication} and \subref*{fi:bistatic_backscatter_communication}, respectively.
@@
 			\centering
-			\subfloat[Monostatic \gls{bc}]{
+			\subfloat[\gls{mbc}]{
 				\resizebox{0.48\linewidth}{!}{
@@
 			}
-			\subfloat[Bistatic \gls{bc}]{
+			\subfloat[\gls{bbc}]{
 				\resizebox{0.48\linewidth}{!}{
@@
 			\caption{
-				Paradigms for various scattering applications.
+				Illustration of scattering applications.
+				% Paradigms for various scattering applications.
 			}
@@
 	\end{subsection}
+
+	\begin{table*}[]
+		\caption{Comparison of Scattering Applications}
+		\begin{tabularx}{\textwidth}{XXXXXXX}
+			\toprule
+			                              & \gls{mbc}               & \gls{bbc}               & \gls{ambc}                                      & \gls{sr}                                     & \gls{ris}                       & RIScatter                                         \\ \midrule
+			Coexisting systems            & 1                       & 1                       & 2 (competitive)                                 & 2 (collaborative)                            & 1                               & 2 (collaborative)                                 \\ \midrule
+			Scatterer contribution        & Backscatter modulation  & Backscatter modulation  & Backscatter modulation and primary interference & Backscatter modulation and primary multipath & Passive beamforming             & Backscatter modulation and passive beamforming    \\ \midrule
+			Cooperative transmission      & ---                     & ---                     & No                                              & Active beamforming                           & ---                             & Active beamforming and smart reflection           \\ \midrule
+			Cooperative reception         & ---                     & ---                     & No                                              & Joint detection or \gls{sic}                 & ---                             & Backscatter detection as primary channel training \\ \midrule
+			Backscatter detection         & Coherent or noncoherent & Coherent or noncoherent & Semi-coherent or noncoherent                    & Coherent                                     & ---                             & Semi-coherent                                     \\ \midrule
+			Reflection state distribution & Equiprobable            & Equiprobable            & Equiprobable                                    & Gaussian or Equiprobable                     & Degenerate (\gls{csi}-adaptive) & Flexible (\gls{csi}- and link priority-adaptive)  \\ \midrule
+			Load-switching frequency      & Fast or slow            & Fast or slow            & Fast or slow                                    & Slow                                         & Slow (dynamic) or very slow     & Fast or slow                                      \\ \bottomrule
+		\end{tabularx}
+	\end{table*}
 
@@
 
+	% TODO why not use metamaterial? because high computational complexity and expectations of freedom (flexibility, reliability)
+	% TODO cooperative input design can be used for co-located RIScatter nodes.
+	% TODO hardward to modulate using RIS is already available.
+	% TODO RIScatter: enhance backscatter signal difference (suppress primary interference) or primary signal strength.
+	% TODO For Backscatter community: why not adaptive channel coding? For RIS community: why not add randomness for modulation?
+	% TODO RIS involves nonlinear circuits (e.g., diodes) and impedance design (i.e., perfect mismatching) is tricky for continuous phase shift; discrete candidate set is preferred (2-3 bits optimal)
+	% TODO Redefine RIS using book
+	% TODO Using RIS to encode is not very interesting as controller is anyway usable
+	% TODO Wi-Fi sampling rate 20 MHz (symbol period 50 nS), RFID symbol rate/load switching speed 100s KHz to 10s MHz [Backscatter Communications], fast load switching speed is key for high data rate - symbol ratio is not very large
+	% TODO Beamforming can cancel direct interference to avoid the collapse of non-coherent energy detection and enlarge energy gap.
+	% ?
+[Reconfigurable Intelligent Surface-Assisted Ambient Backscatter Communications Experimental Assessment]the authors of [5] show that, even in line-of-sight (LOS), the interferences and the desired signal can combine in such a way that the received signals at the reader side in the two states are close in power and only differ by their phases
+	% TODO Input probability distribution for discrete-value reflection (backscatter), constellation design for continue-value reflection (RIS)
+	% TODO convergence
+	% TODO channel coding: general non-adaptive (book) adaptive (DMC)
+	% ? [Turbocharging] Since averaging must be done over a significant period of time to smooth out the variation in the TV transmissions, averaging does not allow rates much higher than 10 kbps [24].
+	% TODO mu-code: use multiple Rxs for noncoherent direct interference cancellation (instead of receive diversity)
+	% TODO backscatter modulation <-> passive beamforming; add adaptive channel coding over (NRZ) line coding.
+	% TODO semicoherent: known CSI, unknown primary/backscatter symbols
+
 	% To the best of our knowledge, all relevant literatures assumed at backscatter information sources either Gaussian codebook \cite{Guo2019b,Ding2020,Long2020a,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Hu2021b} or finite equiprobable inputs \cite{Yang2018,Liang2020,Han2021,Zhang2022,Liu2019d,Bereyhi2020,Xu2020b,Zhang2021d,Hua2022,Basar2020,Ma2020a,Yuan2021,Hu2021a}.
@@
 		Scattering source of \gls{bc}/\gls{sr} and reflecting element of \gls{ris} can be regarded as its extreme cases, where the input distribution boils down to equiprobable and degenerate, respectively.
-		Like aforementioned \gls{ris}-empowered \gls{bc}/\gls{sr} schemes, the passive nodes require regular coordination with active devices, but the advantages are 1) RIScatter nodes can be built over conventional load-switching scatterers instead of composite metamaterial; 2) the optimization cost of input distribution is much lower than that of \gls{ris} reflection coefficients; 3) adaptive backscatter channel coding can exploit \gls{csi} to achieve higher instantaneous rate than conventional equiprobable line coding in \gls{bc}/\gls{sr}; 4) the potentially dispersed characteristics of RIScatter nodes (and legacy users) avoids the development optimization and allows uniformly good performance for both links.
+		Like aforementioned \gls{ris}-empowered \gls{bc}/\gls{sr} schemes, the passive nodes require regular coordination with ambient devices, but the advantages are
+		1) RIScatter nodes can be built over universal load-switching scatterers instead of composite metamaterial;
+		2) backscatter modulation and passive beamforming are unified by adaptive input distribution instead of advanced hardware architecture;
+		3) optimization cost of input distribution is much lower than that of \gls{ris} reflection coefficients;
+		4) adaptive backscatter channel coding can exploit \gls{csi} to achieve higher instantaneous rate than conventional equiprobable line coding in \gls{bc}/\gls{sr};
+		5) the potentially dispersed characteristics of RIScatter nodes (and legacy users) avoids the development optimization and allows uniformly good performance for both links.
 
 		\emph{Second,} we propose a practical RIScatter receiver that semi-coherently decodes RIScatter nodes from the received energy per backscatter block, re-encodes for their reflection patterns, retrieves primary equivalent channel as if dynamic passive beamforming, then coherently decodes the primary link under the enhanced multipath.
-		The proposed receiver 1) preserves the benefits of backscatter modulation and passive beamforming; 2) enjoys lower computational and operational complexities than joint \gls{ml} and \gls{sic} schemes; 3) accommodates the link difference and suits for diverse symbol period ratios; 4) requires minor modification over legacy hardware.
+		The proposed receiver
+		1) preserves the benefits of backscatter modulation and passive beamforming;
+		2) enjoys lower computational and operational complexities than joint \gls{ml} and \gls{sic} schemes;
+		3) accommodates the link difference and suits for diverse symbol period ratios;
+		4) requires minor modification over legacy hardware.
 

### 2022-10-11 main.tex
:paintbrush: Update table layout

@@
 \usepackage{pgfplots}
+\usepackage{ragged2e}
 \usepackage[subtle]{savetrees}
@@
 \pgfplotsset{compat=newest}
+
+% tabularx, ragged2e
+\newcolumntype{L}{>{\RaggedRight}X}
+\newcolumntype{C}{>{\centering\arraybackslash}X}
+\renewcommand\tabularxcolumn[1]{m{#1}}
+
 % algpseudocode
@@
 		\caption{Comparison of Scattering Applications}
-		\begin{tabularx}{\textwidth}{XXXXXXX}
+		% \begin{tabularx}{\textwidth}{LLLLLLL}
+		% 	\toprule
+		% 	                              & \gls{mbc}               & \gls{bbc}               & \gls{ambc}                                      & \gls{sr}                                     & \gls{ris}                       & RIScatter                                         \\ \midrule
+		% 	Coexisting systems            & 1                       & 1                       & 2 (competitive)                                 & 2 (collaborative)                            & 1                               & 2 (collaborative)                                 \\ \midrule
+		% 	Scatterer contribution        & Backscatter modulation  & Backscatter modulation  & Backscatter modulation and primary interference & Backscatter modulation and primary multipath & Passive beamforming             & Backscatter modulation and passive beamforming    \\ \midrule
+		% 	Cooperative transmission      & ---                     & ---                     & No                                              & Active beamforming                           & ---                             & Active beamforming and smart reflection           \\ \midrule
+		% 	Cooperative reception         & ---                     & ---                     & No                                              & Joint detection or \gls{sic}                 & ---                             & Backscatter detection as primary channel training \\ \midrule
+		% 	Backscatter detection         & Coherent or noncoherent & Coherent or noncoherent & Semi-coherent or noncoherent                    & Coherent                                     & ---                             & Semi-coherent                                     \\ \midrule
+		% 	Reflection state distribution & Equiprobable            & Equiprobable            & Equiprobable                                    & Gaussian or Equiprobable                     & Degenerate (\gls{csi}-adaptive) & Flexible (\gls{csi}- and link priority-adaptive)  \\ \midrule
+		% 	Load-switching frequency      & Fast or slow            & Fast or slow            & Fast or slow                                    & Slow                                         & Slow (dynamic) or very slow     & Fast or slow                                      \\ \bottomrule
+		% \end{tabularx}
+		\begin{tabularx}{\textwidth}{CCCCCCC}
 			\toprule

### 2022-10-13 assets/illustration/ambc.tex
:paintbrush: Update illustrations

--- 2022-08-31 assets/illustration/ambient_backscatter_communication.tex
@@
 	\draw[decorate,decoration={waves,segment length=5mm}] (0.75,0.25) -- (5.5,2.5);
-	\draw[decorate,decoration={triangles,segment length=2.5mm}] (5.5,3.5) -- (2.5,3.5);
-	\draw[decorate,decoration={triangles,segment length=2.5mm}] (7.5,3) -- (8,1);
+	\draw[decorate,decoration={triangles,segment length=5mm,shape size=1.5mm}] (5.5,3.5) -- (2.5,3.5);
+	\draw[decorate,decoration={triangles,segment length=5mm,shape size=1.5mm}] (7.5,3) -- (8,1);
 
 	\node[draw=none] at (4,0.35) {Modulated\\Signal};
-	\node[draw=none] at (4,3.5) {Superimposed\\Signal};
+	\node[draw=none] at (4,3.95) {Superimposed};
+	\node[draw=none] at (4,3) {Signal};
 \end{tikzpicture}

### 2022-10-13 assets/illustration/bbc.tex
:paintbrush: Update illustrations

--- 2022-08-31 assets/illustration/bistatic_backscatter_communication.tex
@@
 	\node at (0,0) [isosceles triangle,isosceles triangle stretches,shape border rotate=+90,minimum size=1cm,minimum height=1cm,anchor=north] {};
-	\node at (5,3) [rectangle,minimum size=1cm] {};
+	\node at (5,2) [rectangle,minimum size=1cm] {};
 	\node at (8,0) [isosceles triangle,isosceles triangle stretches,shape border rotate=+270,minimum size=1cm,minimum height=1cm,anchor=north] {};
 
-	\node[draw=none] at (0,-2) {Carrier\\Emitter};
-	\node[draw=none] at (5,4.5) {Scattering\\Node};
-	\node[draw=none] at (8,-2) {Backscatter\\Reader};
+	\node[draw=none] at (0,-1.95) {Carrier\\Emitter};
+	\node[draw=none] at (5,3.35) {Scattering\\Node};
+	\node[draw=none] at (8,-1.95) {Backscatter\\Reader};
 
 	\draw[decorate,decoration={snake,post length=2.5mm},-latex] (1,-1) -- (7.5,-1);
-	\draw[decorate,decoration={snake,post length=2.5mm},-latex] (0.5,0) -- (4,3);
-	\draw[decorate,decoration={snake,pre length=1cm,post length=1cm},-latex] (6,3) -- (8,0.35);
+	\draw[decorate,decoration={snake,post length=2.5mm},-latex] (0.5,0) -- (4,2);
+	\draw[decorate,decoration={snake,pre length=7.5mm,post length=7.5mm},-latex] (6,2) -- (8,0.35);
 
-	\node[draw=none] at (1.5,2.2) {Carrier};
-	\node[draw=none] at (7.25,2.2) {1};
-	\node[draw=none] at (6.55,3.1) {0};
-	\node[draw=none] at (7.95,1.3) {0};
+	\node[draw=none] at (1.5,1.75) {Carrier};
+	\node[draw=none] at (7.2,1.7) {1};
+	\node[draw=none] at (6.6,2.25) {0};
+	\node[draw=none] at (7.8,1.15) {0};
 \end{tikzpicture}

### 2022-10-13 assets/illustration/discrete_outputs.tex
:paintbrush: Update illustrations

@@
 \begin{tikzpicture}
-	\begin{axis}[width=8cm,height=4cm,xmin=0,xmax=6.5,xlabel=$z$,axis x line=middle,axis y line=none,xtick={0,2,3,4,6},xticklabels={$t_0$,$t_1$,$t_2$,$t_3$,$t_4$},xtick style={draw=none},every axis x label/.style={at=(current axis.right of origin),anchor=west},domain=0:6]
-		\addplot[mark=*,mark size=1pt,only marks,color=gray] {0};
+	\begin{axis}[width=10cm,height=5cm,xmin=0,xmax=6.5,xlabel=$z$,axis x line=middle,axis y line=none,xtick={0,2,3,4,6},xticklabels={$t_0$,$t_1$,$t_2$,$t_3$,$t_4$},xtick style={draw=none},every axis x label/.style={at=(current axis.right of origin),anchor=west},domain=0:6]
+		\addplot[mark=*,mark size=0.5pt,only marks,color=gray] {0};
 		\addplot[mark=*,mark size=1pt,only marks,color=black] coordinates{(0,0) (2,0) (3,0) (4,0) (6,0)};
-		\draw[color=black,dashed] (0,0) -- (0,0.6);
-		\draw[color=black,dashed] (2,0) -- (2,0.6);
-		\draw[color=black,dashed] (3,0) -- (3,0.6);
-		\draw[color=black,dashed] (4,0) -- (4,0.6);
-		\draw[color=black,dashed] (6,0) -- (6,0.6);
-		\draw[latex-latex] (0,0.6) -- (2,0.6) node[below,midway]{$\mathcal{R}_1$};
-		\draw[latex-latex] (2,0.6) -- (3,0.6) node[below,midway]{$\mathcal{R}_2$};
-		\draw[latex-latex] (3,0.6) -- (4,0.6) node[below,midway]{$\mathcal{R}_3$};
-		\draw[latex-latex] (4,0.6) -- (6,0.6) node[below,midway]{$\mathcal{R}_4$};
+		\draw[decorate,decoration={brace,amplitude=10}] (0,0) -- (2,0) node[above,midway,yshift=10]{$\mathcal{R}_1$};
+		\draw[decorate,decoration={brace,amplitude=10}] (2,0) -- (3,0) node[above,midway,yshift=10]{$\mathcal{R}_2$};
+		\draw[decorate,decoration={brace,amplitude=10}] (3,0) -- (4,0) node[above,midway,yshift=10]{$\mathcal{R}_3$};
+		\draw[decorate,decoration={brace,amplitude=10}] (4,0) -- (6,0) node[above,midway,yshift=10]{$\mathcal{R}_4$};
 	\end{axis}

### 2022-10-13 assets/illustration/energy_distribution.tex
:paintbrush: Update illustrations

@@
+\definecolor{color1}{HTML}{0072BD}
+\definecolor{color2}{HTML}{D95319}
+\definecolor{color3}{HTML}{EDB120}
+\definecolor{color4}{HTML}{7E2F8E}
+
 \begin{tikzpicture}
 	\begin{axis}[
+			clip mode=individual,
 			height=5cm,
@@
 			xticklabels={$t_0$,$t_1$,$t_2$,$t_3$,$t_4$},
-			yticklabels={},
+			yticklabels=\empty,
 			samples = 200
@@
 
-		\addplot+[thick] gnuplot[raw gnuplot] {%
+		\addplot+[very thick,solid,color1] gnuplot[raw gnuplot] {%
 				isint(x) = (int(x)==x);
@@
 
-		\addplot+[thick] gnuplot[raw gnuplot] {%
+		\addplot+[very thick,dashed,color2] gnuplot[raw gnuplot] {%
 				isint(x) = (int(x)==x);
@@
 
-		\addplot+[thick,color=brown] gnuplot[raw gnuplot] {%
+		\addplot+[very thick,dotted,color3] gnuplot[raw gnuplot] {%
 				isint(x) = (int(x)==x);
@@
 
-		\addplot+[thick,color=green!40!gray] gnuplot[raw gnuplot] {%
+		\addplot+[very thick,dashdotted,color4] gnuplot[raw gnuplot] {%
 				isint(x) = (int(x)==x);
@@
 		\addlegendentryexpanded{$f(z \mid \mathcal{H}_4)$}
-		\draw[color=gray,thick,dashed] (12.78,0) -- (12.78,0.1);
-		\draw[color=gray,thick,dashed] (20.28,0) -- (20.28,0.1);
-		\draw[color=gray,thick,dashed] (29.62,0) -- (29.62,0.1);
-		\draw[latex-latex] (0,0.05) -- (12.78,0.05) node[below,midway]{$\mathcal{R}_1$};
-		\draw[latex-latex] (12.78,0.05) -- (20.28,0.05) node[below,midway]{$\mathcal{R}_2$};
-		\draw[latex-latex] (20.28,0.05) -- (29.62,0.05) node[below,midway]{$\mathcal{R}_3$};
-		\draw[latex-latex] (29.62,0.05) -- (70,0.05) node[below,midway]{$\mathcal{R}_4$};
+		\draw[latex-latex] (0,0) -- (12.78,0) node[above,midway,yshift=-2]{$\mathcal{R}_1$};
+		\draw[latex-latex] (12.78,0) -- (20.28,0) node[above,midway,yshift=-2]{$\mathcal{R}_2$};
+		\draw[latex-latex] (20.28,0) -- (29.62,0) node[above,midway,yshift=-2]{$\mathcal{R}_3$};
+		\draw[latex-latex] (29.62,0) -- (70,0) node[above,midway,yshift=-2]{$\mathcal{R}_4$};
 	\end{axis}

### 2022-10-13 assets/illustration/mbc.tex
:paintbrush: Update illustrations

\begin{tikzpicture}[font=\LARGE,every node/.style={draw,ultra thick},every path/.style={ultra thick},every text node part/.style={align=center}]
	\node at (0,0) [kite,minimum size=0.75cm,kite vertex angles=60] {};
	\node at (8,3) [rectangle,minimum size=1cm] {};

	\node[draw=none] at (0,-1.125) {Interrogator};
	\node[draw=none] at (8,4.375) {Scattering\\Node};

	\draw[decorate,decoration={snake,post length=2.5mm},-latex] (0.5,0.75) -- (7,3);
	\draw[decorate,decoration={snake,pre length=2cm,post length=2cm},-latex] (7.25,2.25) -- (0.75,0);

	\node[draw=none] at (3.5,2.625) {Carrier};
	\node[draw=none] at (4.2,0.5) {1};
	\node[draw=none] at (2,-0.125) {0};
	\node[draw=none] at (6.4,1.3) {0};
\end{tikzpicture}

### 2022-10-13 assets/illustration/ris.tex
:paintbrush: Update illustrations

--- 2022-08-31 assets/illustration/symbiotic_radio.tex
@@
 \begin{tikzpicture}[font=\LARGE,every node/.style={draw,ultra thick},every path/.style={ultra thick},every text node part/.style={align=center}]
-	\node at (0,0) [circular sector,shape border rotate=90,minimum width=2cm] {};
-	\node at (5,3) [rectangle,minimum size=1cm] {};
-	\node at (8,0.55) [circular sector,shape border rotate=270,minimum width=2cm] {};
+	\node at (0,0) [dart,shape border rotate=90,minimum width=1cm] {};
+	\node at (5,3.25) [semicircle,shape border rotate=180,minimum width=1.5cm] {};
+	\node at (8,0.35) [dart,shape border rotate=270,minimum width=1cm] {};
 
-	\node[draw=none] at (0,-1.25) {Primary\\Transmitter};
-	\node[draw=none] at (5,4.375) {Scattering\\Node};
-	\node[draw=none] at (8,-1.25) {Cooperative\\Receiver};
+	\node[draw=none] at (0,-1) {Transmitter};
+	\node[draw=none] at (5,4.4375) {Reflecting\\Element};
+	\node[draw=none] at (8,-1) {Receiver};
 
@@
 	\draw[decorate,decoration={waves,segment length=5mm}] (0.5,0.75) -- (4,3);
-	\draw[decorate,decoration={triangles,segment length=2.5mm}] (6,3) -- (8,1.25);
+	\draw[decorate,decoration={waves,segment length=5mm}] (6,3) -- (8,1.25);
 
-	\node[draw=none] at (4,0.875) {Modulated\\Signal};
-	\node[draw=none] at (7.8,2.9) {Superimposed\\Signal};
+	\node[draw=none] at (4.875,1.125) {Modulated\\Signal};
 \end{tikzpicture}

### 2022-10-13 main.tex
:paintbrush: Update illustrations

--- 2022-10-11 main.tex
@@
 		% The backscatter reader can be either co-located or separated with the carrier emitter, known as monostatic and bistatic \gls{bc}.
-		The backscatter reader can be either co-located or separated with the carrier emitter, known as \gls{mbc} and \gls{bbc} in Fig.
-\subref*{fi:monostatic_backscatter_communication} and \subref*{fi:bistatic_backscatter_communication}, respectively.
+		The backscatter reader can be either co-located or separated with the carrier emitter, known as \gls{mbc} and \gls{bbc} in Fig. \subref*{fi:mbc} and \subref*{fi:bbc}, respectively.
 		Its applications such as \gls{rfid} \cite{Dobkin2012,Landt2005} and passive sensor network \cite{Vannucci2008,Assimonis2016} have been extensively researched, standardized, and commercialized to support \gls{iot} and \gls{m2m} networks.
@@
 		In \gls{ambc} \cite{Liu2013b}, interactive nodes recycle ambient signals from legacy transmitters (e.g., radio, television and Wi-Fi) to harvest energy and establish connections.
-		As illustrated in Fig.
-\subref*{fi:ambient_backscatter_communication}, it eliminates the need of dedicated power supply, carrier emitter and frequency spectrum, bringing more opportunities to low-power communications.
+		As illustrated in Fig. \subref*{fi:ambc}, it eliminates the need of dedicated power supply, carrier emitter and frequency spectrum, bringing more opportunities to low-power communications.
 		To combat the strong direct-link interference of \gls{ambc}, \cite{Yang2018} proposed a co-located receiver that cooperatively decodes both primary (legacy) and backscatter links.
 		% The authors evaluated the error performance of \gls{ml}, linear, and \gls{sic} detectors for flat fading channel, and proposed a low-complexity detector for frequency-selective fading channel.
-		The concept of cooperative \gls{ambc} was further refined as \gls{sr} in Fig. \subref*{fi:symbiotic_radio} that cognitively incorporates \gls{ambc} with existing systems \cite{Liang2020}.
+		The concept of cooperative \gls{ambc} was further refined as \gls{sr} in Fig. \subref*{fi:sr} that cognitively incorporates \gls{ambc} with existing systems \cite{Liang2020}.
 		% In \gls{sr}, the primary transmitter generates active radio carrying primary information, the backscatter node modulates own information onto the scattered wave, and the co-located receiver decodes both links from two propagation paths.
@@
 		On the other hand, \gls{ris} in Fig.
-\subref*{fi:reconfigurable_intelligent_surface} is a promising technology that evolves wireless propagation environment using numerous passive reflecting elements (e.g., scattering antenna or programmable metamaterial) with adjustable amplitudes and/or phases \cite{Wu2021b}.
+\subref*{fi:ris} is a promising technology that evolves wireless propagation environment using numerous passive reflecting elements (e.g., scattering antenna or programmable metamaterial) with adjustable amplitudes and/or phases \cite{Wu2021b}.
 		With proper phase shift design, the scattered components can add constructively/destructively with the direct component for signal enhancement/interference suppression.
@@
 				\resizebox{0.48\linewidth}{!}{
-					\input{assets/illustration/monostatic_backscatter_communication.tex}
-				}
-				\label{fi:monostatic_backscatter_communication}
+					\input{assets/illustration/mbc.tex}
+				}
+				\label{fi:mbc}
 			}
@@
 				\resizebox{0.48\linewidth}{!}{
-					\input{assets/illustration/bistatic_backscatter_communication.tex}
-				}
-				\label{fi:bistatic_backscatter_communication}
+					\input{assets/illustration/bbc.tex}
+				}
+				\label{fi:bbc}
 			}
@@
 				\resizebox{0.48\linewidth}{!}{
-					\input{assets/illustration/ambient_backscatter_communication.tex}
-				}
-				\label{fi:ambient_backscatter_communication}
+					\input{assets/illustration/ambc.tex}
+				}
+				\label{fi:ambc}
 			}
@@
 				\resizebox{0.48\linewidth}{!}{
-					\input{assets/illustration/symbiotic_radio.tex}
-				}
-				\label{fi:symbiotic_radio}
+					\input{assets/illustration/sr.tex}
+				}
+				\label{fi:sr}
 			}
@@
 				\resizebox{0.48\linewidth}{!}{
-					\input{assets/illustration/reconfigurable_intelligent_surface.tex}
-				}
-				\label{fi:reconfigurable_intelligent_surface}
+					\input{assets/illustration/ris.tex}
+				}
+				\label{fi:ris}
 			}
@@
 		\caption{Comparison of Scattering Applications}
-		\begin{tabularx}{\textwidth}{XXXXXXX}
+		\begin{tabularx}{\textwidth}{CCCCCCC}
 			\toprule
@@
 			Cooperative transmission      & ---                       & ---                       & No                                              & Active beamforming                           & ---                                     & Active beamforming and smart reflection           \\ \midrule
-			Cooperative reception         & ---                     & ---                     & No                                              & Joint detection or \gls{sic}                 & ---                             & Backscatter detection as primary channel training \\ \midrule
-			Backscatter detection         & Coherent or noncoherent & Coherent or noncoherent & Semi-coherent or noncoherent                    & Coherent                                     & ---                             & Semi-coherent                                     \\ \midrule
-			Reflection state distribution & Equiprobable            & Equiprobable            & Equiprobable                                    & Gaussian or Equiprobable                     & Degenerate (\gls{csi}-adaptive) & Flexible (\gls{csi}- and link priority-adaptive)  \\ \midrule
-			Load-switching frequency      & Fast or slow            & Fast or slow            & Fast or slow                                    & Slow                                         & Slow (dynamic) or very slow     & Fast or slow                                      \\ \bottomrule
+			Cooperative reception         & ---                       & ---                       & No (separated receivers)                        & Joint detection or \gls{sic}                 & ---                                     & Backscatter detection as primary channel training \\ \midrule
+			Primary detection             & ---                       & ---                       & Semi-coherent                                   & Coherent or semi-coherent                    & Coherent                                & Coherent                                          \\ \midrule
+			Backscatter detection         & Coherent                  & Coherent                  & Semi-coherent or noncoherent                    & Coherent                                     & ---                                     & Semi-coherent                                     \\ \midrule
+			Reflection state distribution & Equiprobable (line-coded) & Equiprobable (line-coded) & Equiprobable (line-coded)                       & Equiprobable or Gaussian                     & Degenerate (\gls{csi}-adaptive)         & Flexible (\gls{csi}- and link priority-adaptive)  \\ \midrule
+			Load-switching frequency      & Fast or slow              & Fast or slow              & Fast or slow                                    & Slow                                         & Slow (dynamic) or very slow (blockwise) & Fast or slow                                      \\ \bottomrule
 		\end{tabularx}

### 2022-10-13 src/config/config_convergence.m
:sparkles: Add convergence plots

@@ -1,0 +1,43 @@
+%% * System
+% number of transmit antennas
+nTxs = 4;
+% number of scatter antennas
+nSxs = 1;
+% number of receive antennas
+nRxs = 1;
+% number of tags
+nTags = 8;
+% number of available states at tags (i.e., modulation order)
+nStates = 2;
+% constellation diagram at tags
+constellation = normalize(qammod(transpose(0 : nStates - 1), nStates), 'norm', Inf);
+% amplitude scatter ratio at tags
+scatterRatio = 0.5;
+% backscatter/primary symbol duration ratio
+symbolRatio = 20;
+% average transmit power
+transmitPower = db2pow(6);
+% average noise power
+noisePower = db2pow(-70);
+% layout and distance
+directDistance = 10;
+coverage = 2;
+[forwardDistance, backwardDistance] = layout(directDistance, nTags, coverage);
+% path loss exponents
+directExponent = 2.6;
+forwardExponent = 2.4;
+backwardExponent = 2;
+% Ricean factors
+directFactor = 5;
+forwardFactor = 5;
+backwardFactor = 5;
+
+%% * Algorithm
+% relative priority of primary link
+weight = 0;
+% number of quantization bins
+nBins = 2 ^ 9;
+
+%% * PBS
+% number of instances
+nInstances = 1e3;

### 2022-10-13 src/lib/beamforming_pgd.m

@@ -1,4 +1,4 @@
-function [beamforming] = beamforming_pgd(symbolRatio, weight, transmitPower, noisePower, equivalentChannel, cascadedChannel, equivalentDistribution, threshold, tolerance, maxStep, alpha, beta)
+function [beamforming, convergence] = beamforming_pgd(symbolRatio, weight, transmitPower, noisePower, equivalentChannel, cascadedChannel, equivalentDistribution, threshold, tolerance, maxStep, alpha, beta)
 	% Function:
 	%	- optimize beamforming vector by projected gradient descent with step size determined by backtracking line search
     %
@@ -18,6 +18,7 @@ function [beamforming] = beamforming_pgd(symbolRatio, weight, transmitPower, noi
     %
     % Output:
 	%	- beamforming [nTxs x 1]: transmit beamforming vector
+	%	- convergence [1 x nIterations]: weighted sum-rate at each iteration
     %
 	% Comment:
 	%	- complex gradient w.r.t. beamforming vector is obtained in closed form
@@ -60,6 +61,7 @@ function [beamforming] = beamforming_pgd(symbolRatio, weight, transmitPower, noi
 	dmac = dmc_integration(symbolRatio, receivePower, threshold);
 	dmac(:, sortIndex) = dmac;
 	wsr = rate_weighted(weight, snr, equivalentDistribution, dmac);
+	convergence = wsr;
 
 	% * Projected gradient descent
 	isConverged = false;
@@ -89,6 +91,7 @@ function [beamforming] = beamforming_pgd(symbolRatio, weight, transmitPower, noi
 			isConverged = norm(beamformingPgd - beamforming) <= tolerance || norm(beamformingPgd + beamforming) <= tolerance;
 			beamforming = beamformingPgd;
 			wsr = wsrPgd;
+			convergence = [convergence, wsr];
 		else
 			error('PGD failed. Is any DMAC entry approaching 0?');
 		end

### 2022-10-13 src/lib/block_coordinate_descent.m

@@ -1,4 +1,4 @@
-function [rate, distribution, threshold, beamforming] = block_coordinate_descent(nTags, symbolRatio, transmitPower, noisePower, nBins, weight, equivalentChannel, cascadedChannel, tolerance, Options)
+function [rate, distribution, threshold, beamforming, convergence] = block_coordinate_descent(nTags, symbolRatio, transmitPower, noisePower, nBins, weight, equivalentChannel, cascadedChannel, tolerance, Options)
 	% Function:
 	%	- iteratively update the input distribution, detection threshold, and beamforming vector to maximize weighted sum rate
     %
@@ -19,6 +19,7 @@ function [rate, distribution, threshold, beamforming] = block_coordinate_descent
 	%	- distribution [nStates x nTags]: tag input (i.e., state) probability distribution
 	%	- threshold [1 x (nOutputs + 1)]: boundaries of decision regions (including 0 and Inf)
 	%	- beamforming [nTxs x 1]: transmit beamforming vector
+	%	- convergence [1 x nIterations]: weighted sum-rate at each iteration of BCD, (first) KKT and PGD
     %
     % Comment:
 	%	- user first jointly decode all tags by energy detection, then model backscatter contribution within equivalent channel
@@ -85,6 +86,8 @@ function [rate, distribution, threshold, beamforming] = block_coordinate_descent
 	% * Block coordinate descent
 	wsr = rate_weighted(weight, snr, equivalentDistribution, dmac);
 	isConverged = false;
+	isInitialized = true;
+	convergence.bcd = wsr;
 
 	while ~isConverged
 		% * Update iteration index
@@ -95,7 +98,11 @@ function [rate, distribution, threshold, beamforming] = block_coordinate_descent
 		case 'exhaustion'
 			[distribution, equivalentDistribution] = distribution_exhaustion(nTags, weight, snr, dmac);
 		case 'kkt'
-			[distribution, equivalentDistribution] = distribution_kkt(nTags, weight, snr, dmac);
+			if ~isInitialized
+				[distribution, equivalentDistribution] = distribution_kkt(nTags, weight, snr, dmac);
+			else
+				[distribution, equivalentDistribution, convergence.kkt] = distribution_kkt(nTags, weight, snr, dmac);
+			end
 		case 'sca'
 			[distribution, equivalentDistribution] = distribution_sca(nTags, weight, snr, dmac);
[…]

### 2022-10-13 src/lib/distribution_kkt.m

@@ -1,4 +1,4 @@
-function [distribution, equivalentDistribution] = distribution_kkt(nTags, weight, snr, dmac, tolerance)
+function [distribution, equivalentDistribution, convergence] = distribution_kkt(nTags, weight, snr, dmac, tolerance)
 	% Function:
 	%	- obtain KKT tag input probability distribution for maximizing weighted sum of primary and total backscatter rate
     %
@@ -12,6 +12,7 @@ function [distribution, equivalentDistribution] = distribution_kkt(nTags, weight
     % Output:
 	%	- distribution [nStates x nTags]: tag input (i.e., state) probability distribution
 	%	- equivalentDistribution [nInputs x 1]: equivalent single-source distribution for each tag input distribution tuple
+	%	- convergence [1 x nIterations]: weighted sum-rate at each iteration
     %
     % Comment:
     %	- iteratively update input distribution of each tag by coordinate descent
@@ -48,6 +49,7 @@ function [distribution, equivalentDistribution] = distribution_kkt(nTags, weight
 	informationFunction = weight * information_primary(snr) + (1 - weight) * information_backscatter(equivalentDistribution, dmac);
 	marginalInformation = marginal_information(distributionTuple, informationFunction);
 	wsr = equivalentDistribution' * informationFunction;
+	convergence = wsr;
 
 	% * Iteratively update input distribution for all tags
 	isConverged = false;
@@ -62,6 +64,7 @@ function [distribution, equivalentDistribution] = distribution_kkt(nTags, weight
 			marginalInformation = marginal_information(distributionTuple, informationFunction);
 			wsr = equivalentDistribution' * informationFunction;
 		end
+		convergence = [convergence, wsr];
 		isConverged = (wsr - wsr_) / wsr <= tolerance || isnan(wsr);
 	end
 

### 2022-10-13 src/plot/plot_convergence.m

@@ -1,0 +1,28 @@
+clear; run('../setup'); load('../data/wsr_convergence'); clc; close all;
+
+%% * Draw convergence curves
+figure('Name', 'Convergence behavior of the proposed algorithms', 'Position', [0, 0, 500, 400]);
+convergencePlot = tiledlayout(3, 1, 'tilespacing', 'compact');
+plotHandle = gobjects(1, 3);
+
+% * KKT (first call)
+nexttile;
+plotHandle(1) = plot(0 : 1e1 : 1.2e2, convergence.kkt(1 : 1e1 : 1.2e2 + 1), 'DisplayName', 'KKT (First Call)');
+hold off; legend('Location', 'se'); grid on; box on;
+
+% * PGD (first call)
+nexttile;
+plotHandle(2) = plot(0 : length(convergence.pgd) - 1, convergence.pgd, 'DisplayName', 'PGD (First Call)');
+hold off; legend('Location', 'se'); grid on; box on;
+ylabel('Weighed Sum-Rate');
+
+% * BCD
+nexttile;
+plotHandle(3) = plot(0 : length(convergence.bcd) - 1, convergence.bcd, 'DisplayName', 'BCD');
+hold off; legend('Location', 'se'); grid on; box on;
+xlabel('Number of Iterations');
+style_plot(plotHandle);
+
+savefig('figures/wsr_convergence');
+matlab2tikz('../../assets/simulation/wsr_convergence.tex', 'extraaxisoptions', ['title style={font=\Large}, ' 'label style={font=\Large}, ' 'ticklabel style={font=\large}, ' 'legend style={font=\large}, ' 'yticklabel=\pgfkeys{/pgf/number format/.cd,fixed,precision=3}\pgfmathprintnumber{\tick}']);
+% matlab2tikz('../../assets/channel_amplitude.tex', 'extraaxisoptions', ['title style={font=\large}, ' 'label style={font=\large}, ' 'ticklabel style={font=\large}, ' 'legend style={font=\large}, ' 'scaled y ticks=false, ' 'yticklabel=\pgfkeys{/pgf/number format/.cd,fixed,precision=2}\pgfmathprintnumber{\tick}']);

### 2022-10-13 src/wsr_convergence.m

@@ -1,0 +1,17 @@
+clear; setup; cvx_begin; cvx_end; clc; config_convergence;
+
+% * Generate channels
+directChannel = sqrt(path_loss(directDistance, directExponent)) * fading_ricean(nTxs, nRxs, directFactor);
+cascadedChannel = zeros(nTxs, nTags);
+for iTag = 1 : nTags
+	cascadedChannel(:, iTag) = sqrt(path_loss(forwardDistance(iTag), forwardExponent)) * fading_ricean(nTxs, nSxs, forwardFactor) * sqrt(path_loss(backwardDistance(iTag), backwardExponent)) * fading_ricean(nSxs, nRxs, backwardFactor);
+end
+equivalentChannel = directChannel + scatterRatio * cascadedChannel * transpose(constellation(tuple_tag(repmat(transpose(1 : nStates), [1, nTags]))));
+
+% * Clear persistent variables
+clear block_coordinate_descent distribution_kkt distribution_cooperation beamforming_pgd threshold_bisection;
+
+% * Evaluate convergence
+[~, ~, ~, ~, convergence] = block_coordinate_descent(nTags, symbolRatio, transmitPower, noisePower, nBins, weight, equivalentChannel, cascadedChannel, 'Distribution', 'kkt', 'Beamforming', 'pgd', 'Threshold', 'smawk');
+
+save(strcat('data/', mfilename));

### 2022-10-14 main.tex
:bento: Update assets
:pencil: Add initialization and convergence discussion

@@
 \newacronym{bbc}{BBC}{Bistatic Backscatter Communications}
+\newacronym{bls}{BLS}{Backtracking Line Search}
 
@@
 			                              & \gls{mbc}                 & \gls{bbc}                 & \gls{ambc}                                      & \gls{sr}                                     & \gls{ris}                               & RIScatter                                         \\ \midrule
-			Coexisting systems            & 1                         & 1                         & 2 (competitive)                                 & 2 (collaborative)                            & 1                                       & 2 (collaborative)                                 \\ \midrule
+			Coexisting systems            & 1                         & 1                         & 2 (competitive)                                 & 2 (?ly collaborative)                        & 1                                       & 2 (adaptively collaborative)                      \\ \midrule
 			Scatterer contribution        & Backscatter modulation    & Backscatter modulation    & Backscatter modulation and primary interference & Backscatter modulation and primary multipath & Passive beamforming                     & Backscatter modulation and passive beamforming    \\ \midrule
@@
 	% TODO semicoherent: known CSI, unknown primary/backscatter symbols
+	% TODO initialization, convergence
 
@@
 		Since the original problem is highly non-convex, we decouple it into individual subproblems and constraint all decision regions to convex (connected) intervals.
-		A suboptimal \gls{bcd} algorithm is then proposed, where the \gls{kkt} input distribution is numerically evaluated by limit of sequences, the active beamforming is iteratively updated by \gls{pgd} accelerated by backtracking line search, and the decision regions are refined by existing thresholding designs.
+		A suboptimal \gls{bcd} algorithm is then proposed, where the \gls{kkt} input distribution is numerically evaluated by limit of sequences, the active beamforming is iteratively updated by \gls{pgd} accelerated by \gls{bls}, and the decision regions are refined by existing thresholding designs.
 
@@
 		Denote $m_k \in \mathcal{M} \triangleq \{1,\ldots,M\}$ as the reflection state index of node $k$, and $m_{\mathcal{K}} \triangleq (m_1,\ldots,m_K)$ as the state index tuple of all nodes.
-		Conditioned on backscatter index tuple $m_{\mathcal{K}}$, the received signal \eqref{eq:receive_signal} follows \gls{cscg} distribution $y[n] \sim \mathcal{CN}(0,\sigma_{m_{\mathcal{K}}}^2)$, where
+		Conditioned on backscatter index tuple $m_{\mathcal{K}}$, the received signal at each primary block follows \gls{cscg} distribution $\mathcal{CN}(0,\sigma_{m_{\mathcal{K}}}^2)$, where
 		\begin{equation}
@@
 		}
-		Besides, we define the total received energy per backscatter block as $z=\sum_{n=1}^N \lvert y[n] \rvert^2$.
+		Besides, we define the total received energy per backscatter block as $z=\sum_{n \in \mathcal{N}} \lvert y[n] \rvert^2$.
 		Since $z$ is the sum of $N$ \gls{iid} exponential variables, its \gls{pdf} conditioned on $m_{\mathcal{K}}$ follows Gamma distribution
@@
 
-		The \gls{pgd} active beamforming optimization with step size determined by backtracking line search is summarized in Algorithm \ref{al:active_beamforming}.
+		The \gls{pgd} active beamforming optimization with step size determined by \gls{bls} is summarized in Algorithm \ref{al:active_beamforming}.
 		\begin{algorithm}[!t]
-			\caption{Iterative Active Beamforming Optimization by \gls{pgd} with Backtracking Line Search}
+			\caption{Iterative Active Beamforming Optimization by \gls{pgd} with \gls{bls}}
 			\label{al:active_beamforming}
@@
 	\end{equation}
-	together with a Ricean fading model
+	together with a Rician fading model
 	\begin{equation}
@@
 	\end{equation}
-	where $d$ is the transmission distance, $L_0=-\qty{30}{\dB}$ is the reference path loss at distance $d_0=\qty{1}{\meter}$, $\kappa$ is the Ricean $K$-factor, $\bar{\boldsymbol{H}}$ is the deterministic line-of-sight component with entries of unit magnitude, and $\tilde{\boldsymbol{H}}$ is the Rayleigh fading component with entries in standard \gls{iid} \gls{cscg} distribution.
+	where $d$ is the transmission distance, $L_0=-\qty{30}{\dB}$ is the reference path loss at distance $d_0=\qty{1}{\meter}$, $\kappa$ is the Rician $K$-factor, $\bar{\boldsymbol{H}}$ is the deterministic line-of-sight component with entries of unit magnitude, and $\tilde{\boldsymbol{H}}$ is the Rayleigh fading component with entries in standard \gls{iid} \gls{cscg} distribution.
 	We choose $\gamma_{\mathrm{D}}=2.6$, $\gamma_{\mathrm{F}}=2.4$, $\gamma_{\mathrm{B}}=2$, and $\kappa_{\mathrm{D}}=\kappa_{\mathrm{F}}=\kappa_{\mathrm{B}}=5$ for direct, forward and backward links.
 	The finite threshold domain $\mathcal{T}$ comes from $b$-bit uniform discretization over the critical interval defined by the confidence bounds of edge hypotheses (i.e., lower bound of $\mathcal{H}_1$ and upper bound of $\mathcal{H}_L$) with confidence level $1-\varepsilon$, where $b=7$ and $\varepsilon=\num{1e-3}$.
-	All achievable rate curves/regions are averaged over \num{3000} realizations, and the parameters remain fixed unless otherwise specified.
+	All achievable rate curves/regions are averaged over \num{1000} realizations, and the parameters remain fixed unless otherwise specified.
+
+	\begin{subsection}{Evaluation of Algorithms}
+		\begin{subsubsection}{Initialization}
+			To characterize the achievable rate region, we progressively obtain all boundary points by successively increasing the primary priority $\rho$ and solving problem \eqref{op:weighted_sum_rate}.
+			At $\rho=0$ where backscatter performance is absolutely prioritized, we initialize Algorithm \ref{al:input_distribution} and \ref{al:active_beamforming} by uniform input distribution and \gls{mrt} towards sum cascaded channel $\sum_{k \in \mathcal{K}} \boldsymbol{h}_{\mathrm{C},k}^H$, respectively.
+			At the following points, both algorithms are initialized by the solutions of the previous point.
+		\end{subsubsection}
+
+		\begin{subsubsection}{Convergence}
+			\begin{figure}[!t]
+				\centering
+				\resizebox{0.75\columnwidth}{!}{
+					\input{assets/simulation/wsr_convergence.tex}
+				}
+				\caption{Convergence behavior of the proposed algorithms for $\rho=0$.}
+				\label{fi:wsr_convergence}
+			\end{figure}
+
+			In Fig.
+\ref{fi:wsr_convergence}, we plot the weighted sum of primary and total backscatter rates for \gls{kkt}, \gls{pgd} (on the first call within \gls{bcd}) and \gls{bcd} algorithms in each iteration at $\rho=0$.
+			For $K=8$ and $M=2$, Algorithm \ref{al:input_distribution} typically takes around \num{100} fast iterations based on \eqref{eq:input_kkt_solution} to converge to the \gls{kkt} input distribution.
+			For $Q=4$, around \num{10} iterations are required for Algorithm \ref{al:active_beamforming} to converge, where the gradient needs to be evaluated by \eqref{eq:weighted_sum_mutual_information_gradient} and the step size needs to be refined by \gls{bls}.
+			The \gls{bcd} algorithm typically takes around \num{5} iterations to converge.
+			At the following points (not shown here), the convergence of all three algorithms are much faster thanks to the progressive initialization.
+			Overall, we conclude the proposed algorithms are able to converge within moderate iterations and provide significant rate gains for the RIScatter system.
+		\end{subsubsection}
+	\end{subsection}
+
+	\begin{subsection}{Comparison of Scattering Applications}
+		% AmBC: co-located non-cooperative receivers, use SINR to evaluate primary rate even if backscatter symbols are not Gaussian distributed
+		% For a fair comparison, we employ energy-based backscatter detection for scattering applications evaluated in this subsection.
+		% For a fair comparison, we evaluate different scattering applications with backscatter energy detection over the setup in Fig. \ref{fi:riscatter_network}.
+		For a fair comparison, we employ backscatter energy detection for these scattering applications over the setup in Fig. \ref{fi:riscatter_network}:
+		% employ energy-based backscatter detection for scattering applications evaluated in this subsection.
+		\begin{itemize}
+			\item \emph{\gls{bbc}:}
+			% The \gls{ap} becomes carrier emitter and the user becomes backscatter reader.
+			The primary symbol $s[n]$ becomes deterministic and the receive signal at each primary block is
+			\begin{equation}
+				y^{\text{\gls{bbc}}}[n] = \boldsymbol{h}_{\mathrm{E}}^H(x_{\mathcal{K}}) \boldsymbol{w} + v[n],
+			\end{equation}
+			% which follows non-zero mean complex Gaussian distribution $y_{m_{\mathcal{K}}}^{\text{BBC}}[n] \sim \mathcal{CN}\bigl(\boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}}) \boldsymbol{w},\sigma_v^2\bigr)$ under hypothesis $\mathcal{H}_{m_{\mathcal{K}}}$.
+			which follows non-zero mean complex Gaussian distribution $\mathcal{CN}\bigl(\boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}}) \boldsymbol{w},\sigma_v^2\bigr)$ under hypothesis $\mathcal{H}_{m_{\mathcal{K}}}$.
+			% The corresponding \gls{pdf} of receive energy over $N$ primary blocks is
+			The corresponding \gls{pdf} of accumulated receive energy over $N$ primary blocks is
+			\begin{equation}
+				f^{\text{\gls{bbc}}}(z|\mathcal{H}_{m_{\mathcal{K}}}) = \frac{(z-\mu_{m_{\mathcal{K}}})^{N-1} \exp(-(z-\mu_{m_{\mathcal{K}}})/\sigma_v^2)}{\sigma_v^{2N} (N-1)!},
+			\end{equation}
+			where $\mu_{m_{\mathcal{K}}} \triangleq N \lvert \boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2$.
+			\item \emph{\gls{ambc}:} The user decodes both links independently and semi-coherently by treating the other as interference or uncertainty.
+			% Hence, the primary achievable rate can be approximated by\footnote{To provide a preliminary benchmark, we approximate the interference from finite-input backscatter sources by those from independent Gaussian sources.}
+			Hence, the primary achievable rate can be approximated by\footnote{To provide a preliminary benchmark, we approximate the scattered signal components from finite-input backscatter sources by independent interference from Gaussian sources.}
+			\begin{equation}
+				I_P^{\text{\gls{ambc}}}(s;y) \approx \log \Bigl(1 + \frac{\lvert\boldsymbol{h}_{\mathrm{D}}^H\boldsymbol{w}\rvert^2}{\lvert\sum_{k \in \mathcal{K}} \alpha_k \boldsymbol{h}_{\mathrm{C},k}^H \boldsymbol{w}\rvert^2+\sigma_v^2}\Bigr),
+			\end{equation}
+			while the total backscatter rate is given by \eqref{eq:backscatter_mutual_information} with equiprobable inputs.
+			\item \emph{\gls{sr}:} When $N$ is sufficiently large, the primary ergodic rate can be approximated by \eqref{eq:primary_mutual_information} with equiprobable inputs.
+			The intermediate signal after perfect \gls{sic} is \cite{Long2020a}
+			\begin{equation}
+				\hat{y}^{\text{\gls{sr}}}[n] = \sum_{k \in \mathcal{K}} \alpha_k \boldsymbol{h}_{\mathrm{C},k}^H x_k \boldsymbol{w} s[n] + v[n],
+			\end{equation}
+			which follows \gls{cscg} distribution $\mathcal{CN}\bigl(0,\hat{\sigma}_{m_{\mathcal{K}}}^2\bigr)$ with $\hat{\sigma}_{m_{\mathcal{K}}}^2 \triangleq \lvert\sum_{k \in \mathcal{K}} \alpha_k \boldsymbol{h}_{\mathrm{C},k}^H \boldsymbol{w}\rvert^2+\sigma_v^2$ under hypothesis $\mathcal{H}_{m_{\mathcal{K}}}$.
+			The corresponding \gls{pdf} of intermediate energy over $N$ primary blocks is
+			\begin{equation}
+				f^{\text{\gls{sr}}}(\hat{z}|\mathcal{H}_{m_{\mathcal{K}}}) = \frac{\hat{z}^{N-1} \exp(-\hat{z}/\hat{\sigma}_{m_{\mathcal{K}}}^2)}{\hat{\sigma}_{m_{\mathcal{K}}}^{2N} (N-1)!},
+			\end{equation}
+		\end{itemize}
+	\end{subsection}
 

### 2022-10-15 main.tex
:pencil: Add descriptions for scattering applications

@@
 		Without loss of generality, we consider one specific backscatter block (i.e., $N$ primary blocks) in the following context.
-		Due to double modulation, the primary equivalent channel is a function of \emph{coded} backscatter symbols
-		\begin{equation}
-			\boldsymbol{h}_{\mathrm{E}}^H(x_{\mathcal{K}}) \triangleq \boldsymbol{h}_{\mathrm{D}}^H + \sum_{k \in \mathcal{K}} \alpha_k \boldsymbol{h}_{\mathrm{C},k}^H x_k = \boldsymbol{h}_{\mathrm{D}}^H + \boldsymbol{x}^H \mathrm{diag}(\boldsymbol{\alpha}) \boldsymbol{H}_{\mathrm{C}},
+		Due to double modulation, the primary equivalent channel is a function of \emph{coded} backscatter symbols\footnote{Expression \eqref{eq:equivalent_channel_bc} is often used in \gls{bc} literatures while expression \eqref{eq:equivalent_channel_ris} is commonly observed in \gls{ris} literatures.}
+		% \begin{equation}
+		% 	\boldsymbol{h}_{\mathrm{E}}^H(x_{\mathcal{K}}) \overset{\text{(a)}}{=} \boldsymbol{h}_{\mathrm{D}}^H + \sum_{k} \alpha_k \boldsymbol{h}_{\mathrm{C},k}^H x_k \overset{\text{(b)}}{=} \boldsymbol{h}_{\mathrm{D}}^H + \boldsymbol{x}^H \mathrm{diag}(\boldsymbol{\alpha}) \boldsymbol{H}_{\mathrm{C}},
+		% 	\label{eq:equivalent_channel}
+		% \end{equation}
+		\begin{subequations}
+			\begin{align}
+				\boldsymbol{h}_{\mathrm{E}}^H(x_{\mathcal{K}})
+				 & \triangleq \boldsymbol{h}_{\mathrm{D}}^H + \sum_{k} \alpha_k \boldsymbol{h}_{\mathrm{C},k}^H x_k \label{eq:equivalent_channel_bc}                    \\
+				 & = \boldsymbol{h}_{\mathrm{D}}^H + \boldsymbol{x}^H \mathrm{diag}(\boldsymbol{\alpha}) \boldsymbol{H}_{\mathrm{C}}, \label{eq:equivalent_channel_ris}
+			\end{align}
 			\label{eq:equivalent_channel}
-		\end{equation}
+		\end{subequations}
 		where $\alpha_k \in \mathbb{I}$ is the amplitude scattering ratio of RIScatter node $k$, $x_k \in \mathcal{X} \triangleq \{c_1,\ldots,c_M\}$ is the \emph{coded} backscatter symbol of node $k$, $\boldsymbol{\alpha} \triangleq [\alpha_1,\ldots,\alpha_K]^T \in \mathbb{I}^{K}$, $\boldsymbol{x} \triangleq [x_1,\ldots,x_K]^H \in \mathcal{X}^{K}$, and $\boldsymbol{H}_{\mathrm{C}} \triangleq [\boldsymbol{h}_{\mathrm{C},1},\ldots,\boldsymbol{h}_{\mathrm{C},K}]^H \in \mathbb{C}^{K \times Q}$.
@@
 		}
-		Besides, we define the total received energy per backscatter block as $z=\sum_{n \in \mathcal{N}} \lvert y[n] \rvert^2$.
+		Besides, we define the total received energy per backscatter block as $z=\sum_{n \in \mathcal{N}} \bigl\lvert y[n] \bigr\rvert^2$.
 		Since $z$ is the sum of $N$ \gls{iid} exponential variables, its \gls{pdf} conditioned on $m_{\mathcal{K}}$ follows Gamma distribution
@@
 		\begin{equation}
-			t_{l}^{\mathrm{\gls{ml}}} = N \frac{\sigma_{l-1}^2 \sigma_{l}^2}{\sigma_{l-1}^2 - \sigma_{l}^2} \log \frac{\sigma_{l-1}^2}{\sigma_{l}^2}, \quad l \in \mathcal{L} \setminus \{L\},
-			\label{eq:detection_threshold_maximum_likelihood}
+			t_{l}^{\text{\gls{ml}}} = N \frac{\sigma_{l-1}^2 \sigma_{l}^2}{\sigma_{l-1}^2 - \sigma_{l}^2} \log \frac{\sigma_{l-1}^2}{\sigma_{l}^2}, \quad l \in \mathcal{L} \setminus \{L\},
+			\label{eq:detection_threshold_ml}
 		\end{equation}
@@
 	We choose $\gamma_{\mathrm{D}}=2.6$, $\gamma_{\mathrm{F}}=2.4$, $\gamma_{\mathrm{B}}=2$, and $\kappa_{\mathrm{D}}=\kappa_{\mathrm{F}}=\kappa_{\mathrm{B}}=5$ for direct, forward and backward links.
-	The finite threshold domain $\mathcal{T}$ comes from $b$-bit uniform discretization over the critical interval defined by the confidence bounds of edge hypotheses (i.e., lower bound of $\mathcal{H}_1$ and upper bound of $\mathcal{H}_L$) with confidence level $1-\varepsilon$, where $b=7$ and $\varepsilon=\num{1e-3}$.
+	The finite threshold domain $\mathcal{T}$ comes from $b$-bit uniform discretization over the critical interval defined by the confidence bounds of edge hypotheses (i.e., lower bound of $\mathcal{H}_1$ and upper bound of $\mathcal{H}_L$) with confidence level $1-\varepsilon$, where $b=9$ and $\varepsilon=\num{1e-3}$.
 	All achievable rate curves/regions are averaged over \num{1000} realizations, and the parameters remain fixed unless otherwise specified.
 
-	\begin{subsection}{Evaluation of Algorithms}
+	\begin{subsection}{Evaluation of Proposed Algorithms}
 		\begin{subsubsection}{Initialization}
 			To characterize the achievable rate region, we progressively obtain all boundary points by successively increasing the primary priority $\rho$ and solving problem \eqref{op:weighted_sum_rate}.
-			At $\rho=0$ where backscatter performance is absolutely prioritized, we initialize Algorithm \ref{al:input_distribution} and \ref{al:active_beamforming} by uniform input distribution and \gls{mrt} towards sum cascaded channel $\sum_{k \in \mathcal{K}} \boldsymbol{h}_{\mathrm{C},k}^H$, respectively.
-			At the following points, both algorithms are initialized by the solutions of the previous point.
+			At $\rho=0$ where backscatter performance is absolutely prioritized, we initialize Algorithm \ref{al:input_distribution} and \ref{al:active_beamforming} by uniform input distribution and \gls{mrt} towards sum cascaded channel $\sum_{k} \boldsymbol{h}_{\mathrm{C},k}^H$, respectively.
+			At the following points, both algorithms are initialized by the final solutions at the previous point.
 		\end{subsubsection}
@@
 			In Fig.
-\ref{fi:wsr_convergence}, we plot the weighted sum of primary and total backscatter rates for \gls{kkt}, \gls{pgd} (on the first call within \gls{bcd}) and \gls{bcd} algorithms in each iteration at $\rho=0$.
-			For $K=8$ and $M=2$, Algorithm \ref{al:input_distribution} typically takes around \num{100} fast iterations based on \eqref{eq:input_kkt_solution} to converge to the \gls{kkt} input distribution.
+\ref{fi:wsr_convergence}, we plot the weighted sum of primary and total backscatter rates at $\rho=0$ for \gls{kkt}, \gls{pgd} (on the first call within \gls{bcd}) and \gls{bcd} algorithms in each iteration.
+			For $K=8$ and $M=2$, Algorithm \ref{al:input_distribution} typically takes around \num{100} fast iterations of closed-form expression \eqref{eq:input_kkt_solution} to converge to the \gls{kkt} input distribution.
 			For $Q=4$, around \num{10} iterations are required for Algorithm \ref{al:active_beamforming} to converge, where the gradient needs to be evaluated by \eqref{eq:weighted_sum_mutual_information_gradient} and the step size needs to be refined by \gls{bls}.
-			The \gls{bcd} algorithm typically takes around \num{5} iterations to converge.
+			In comparison, the \gls{bcd} algorithm typically requires no more than \num{5} iterations to converge.
 			At the following points (not shown here), the convergence of all three algorithms are much faster thanks to the progressive initialization.
-			Overall, we conclude the proposed algorithms are able to converge within moderate iterations and provide significant rate gains for the RIScatter system.
+			Overall, we conclude the proposed algorithms are able to converge within moderate iterations and provide significant rate benefits for the RIScatter system.
 		\end{subsubsection}
@@
 	\begin{subsection}{Comparison of Scattering Applications}
-		% AmBC: co-located non-cooperative receivers, use SINR to evaluate primary rate even if backscatter symbols are not Gaussian distributed
-		% For a fair comparison, we employ energy-based backscatter detection for scattering applications evaluated in this subsection.
-		% For a fair comparison, we evaluate different scattering applications with backscatter energy detection over the setup in Fig. \ref{fi:riscatter_network}.
-		For a fair comparison, we employ backscatter energy detection for these scattering applications over the setup in Fig. \ref{fi:riscatter_network}:
-		% employ energy-based backscatter detection for scattering applications evaluated in this subsection.
+		For a fair comparison, we consider the setup in Fig. \ref{fi:riscatter_network} and employ \gls{ml} backscatter energy detection for these scattering applications:
 		\begin{itemize}
 			\item \emph{\gls{bbc}:}
-			% The \gls{ap} becomes carrier emitter and the user becomes backscatter reader.
 			The primary symbol $s[n]$ becomes deterministic and the receive signal at each primary block is
 			\begin{equation}
-				y^{\text{\gls{bbc}}}[n] = \boldsymbol{h}_{\mathrm{E}}^H(x_{\mathcal{K}}) \boldsymbol{w} + v[n],
-			\end{equation}
-			% which follows non-zero mean complex Gaussian distribution $y_{m_{\mathcal{K}}}^{\text{BBC}}[n] \sim \mathcal{CN}\bigl(\boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}}) \boldsymbol{w},\sigma_v^2\bigr)$ under hypothesis $\mathcal{H}_{m_{\mathcal{K}}}$.
-			which follows non-zero mean complex Gaussian distribution $\mathcal{CN}\bigl(\boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}}) \boldsymbol{w},\sigma_v^2\bigr)$ under hypothesis $\mathcal{H}_{m_{\mathcal{K}}}$.
-			% The corresponding \gls{pdf} of receive energy over $N$ primary blocks is
+				% y^{\text{\gls{bbc}}}[n] = \boldsymbol{h}_{\mathrm{E}}^H(x_{\mathcal{K}}) \boldsymbol{w} + v[n],
+				y^{\text{\gls{bbc}}}[n] = \Bigl(\boldsymbol{h}_{\mathrm{D}}^H + \sum_{k} \alpha_k \boldsymbol{h}_{\mathrm{C},k}^H x_k\Bigr) \boldsymbol{w} + v[n],
+			\end{equation}
+			% which follows non-zero mean complex Gaussian distribution $\mathcal{CN}\bigl(\boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}}) \boldsymbol{w},\sigma_v^2\bigr)$ under hypothesis $\mathcal{H}_{m_{\mathcal{K}}}$.
+			which follows non-zero mean complex Gaussian distribution $\mathcal{CN}\bigl(\boldsymbol{h}_{\mathrm{D}}^H + \sum_{k} \alpha_k \boldsymbol{h}_{\mathrm{C},k}^H x_{m_k} \boldsymbol{w},\sigma_v^2\bigr)$ under hypothesis $\mathcal{H}_{m_{\mathcal{K}}}$.
+			% \sum_{k} \alpha_k \boldsymbol{h}_{\mathrm{C},k}^H x_k
 			The corresponding \gls{pdf} of accumulated receive energy over $N$ primary blocks is
 			\begin{equation}
-				f^{\text{\gls{bbc}}}(z|\mathcal{H}_{m_{\mathcal{K}}}) = \frac{(z-\mu_{m_{\mathcal{K}}})^{N-1} \exp(-(z-\mu_{m_{\mathcal{K}}})/\sigma_v^2)}{\sigma_v^{2N} (N-1)!},
-			\end{equation}
-			where $\mu_{m_{\mathcal{K}}} \triangleq N \lvert \boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2$.
+				f^{\text{\gls{bbc}}}(z|\mathcal{H}_{m_{\mathcal{K}}}) = \frac{(z-\mu_{m_{\mathcal{K}}}^{\text{\gls{bbc}}})^{N-1} \exp \bigl(-(z-\mu_{m_{\mathcal{K}}}^{\text{\gls{bbc}}})/\sigma_v^2 \bigr)}{\sigma_v^{2N} (N-1)!},
+				\label{eq:energy_distribution_bbc}
+			\end{equation}
+			% where $\mu_{m_{\mathcal{K}}}^{\text{\gls{bbc}}} \triangleq N \lvert \boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2$.
+			where $\mu_{m_{\mathcal{K}}}^{\text{\gls{bbc}}} \triangleq N \bigl\lvert \bigl(\boldsymbol{h}_{\mathrm{D}}^H + \sum_{k} \alpha_k \boldsymbol{h}_{\mathrm{C},k}^H x_{m_k}\bigr) \boldsymbol{w} \bigr\rvert^2$.
+			The \gls{ml} decision threshold is derived as, $\forall l \in \mathcal{L} \setminus \{L\}$,
+			\begin{equation}
+				t_l^{\text{\gls{bbc}}} = \frac{\mu_{l-1}^{\text{\gls{bbc}}} \exp \bigl((\mu_{l-1}^{\text{\gls{bbc}}}-\mu_{l}^{\text{\gls{bbc}}})/\sigma_v^2 (N-1)\bigr) - \mu_{l}^{\text{\gls{bbc}}}}{\exp \bigl((\mu_{l-1}^{\text{\gls{bbc}}}-\mu_{l}^{\text{\gls{bbc}}})/\sigma_v^2 (N-1)\bigr) - 1}.
+				\label{eq:detection_threshold_ml_bbc}
+			\end{equation}
 			\item \emph{\gls{ambc}:} The user decodes both links independently and semi-coherently by treating the other as interference or uncertainty.
-			% Hence, the primary achievable rate can be approximated by\footnote{To provide a preliminary benchmark, we approximate the interference from finite-input backscatter sources by those from independent Gaussian sources.}
 			Hence, the primary achievable rate can be approximated by\footnote{To provide a preliminary benchmark, we approximate the scattered signal components from finite-input backscatter sources by independent interference from Gaussian sources.}
 			\begin{equation}
-				I_P^{\text{\gls{ambc}}}(s;y) \approx \log \Bigl(1 + \frac{\lvert\boldsymbol{h}_{\mathrm{D}}^H\boldsymbol{w}\rvert^2}{\lvert\sum_{k \in \mathcal{K}} \alpha_k \boldsymbol{h}_{\mathrm{C},k}^H \boldsymbol{w}\rvert^2+\sigma_v^2}\Bigr),
-			\end{equation}
-			while the total backscatter rate is given by \eqref{eq:backscatter_mutual_information} with equiprobable inputs.
-			\item \emph{\gls{sr}:} When $N$ is sufficiently large, the primary ergodic rate can be approximated by \eqref{eq:primary_mutual_information} with equiprobable inputs.
-			The intermediate signal after perfect \gls{sic} is \cite{Long2020a}
-			\begin{equation}
-				\hat{y}^{\text{\gls{sr}}}[n] = \sum_{k \in \mathcal{K}} \alpha_k \boldsymbol{h}_{\mathrm{C},k}^H x_k \boldsymbol{w} s[n] + v[n],
-			\end{equation}
-			which follows \gls{cscg} distribution $\mathcal{CN}\bigl(0,\hat{\sigma}_{m_{\mathcal{K}}}^2\bigr)$ with $\hat{\sigma}_{m_{\mathcal{K}}}^2 \triangleq \lvert\sum_{k \in \mathcal{K}} \alpha_k \boldsymbol{h}_{\mathrm{C},k}^H \boldsymbol{w}\rvert^2+\sigma_v^2$ under hypothesis $\mathcal{H}_{m_{\mathcal{K}}}$.
-			The corresponding \gls{pdf} of intermediate energy over $N$ primary blocks is
-			\begin{equation}
-				f^{\text{\gls{sr}}}(\hat{z}|\mathcal{H}_{m_{\mathcal{K}}}) = \frac{\hat{z}^{N-1} \exp(-\hat{z}/\hat{\sigma}_{m_{\mathcal{K}}}^2)}{\hat{\sigma}_{m_{\mathcal{K}}}^{2N} (N-1)!},
+				I_P^{\text{\gls{ambc}}}(s;y) \approx \log \Bigl(1 + \frac{\lvert\boldsymbol{h}_{\mathrm{D}}^H\boldsymbol{w}\rvert^2}{\sum_{k}\lvert \alpha_k \boldsymbol{h}_{\mathrm{C},k}^H \boldsymbol{w}\rvert^2+\sigma_v^2}\Bigr),
+			\end{equation}
+			while the total backscatter rate follows \eqref{eq:backscatter_mutual_information} with uniform input distribution.
+			\item \emph{\gls{sr}:} When $N$ is sufficiently large, the primary ergodic rate under semi-coherent detection can be approximated by \eqref{eq:primary_mutual_information} with uniform input distribution \cite{Long2020a}.
+			When $s[n]$ is successfully decoded and the direct interference $\boldsymbol{h}_{\mathrm{D}}^H \boldsymbol{w} s[n]$ is perfectly cancelled, the intermediate signal used for backscatter detection is
+			\begin{equation}
+				\hat{y}^{\text{\gls{sr}}}[n] = \sum_{k} \alpha_k \boldsymbol{h}_{\mathrm{C},k}^H x_k \boldsymbol{w} s[n] + v[n],
+			\end{equation}
+			which, under hypothesis $\mathcal{H}_{m_{\mathcal{K}}}$, is only subject to the noise uncertainty and follows non-zero mean complex Gaussian distribution $\mathcal{CN}\bigl(\sum_{k} \alpha_k \boldsymbol{h}_{\mathrm{C},k}^H x_k \boldsymbol{w} s[n],\sigma_v^2\bigr)$.
+			By the law of large numbers, as $N$ goes to infinity, the \gls{pdf} of accumulated intermediate energy approaches
+			\begin{equation}
+				f^{\text{\gls{sr}}}(z|\mathcal{H}_{m_{\mathcal{K}}}) = \frac{(z-\mu_{m_{\mathcal{K}}}^{\text{\gls{sr}}})^{N-1} \exp \bigl(-(z-\mu_{m_{\mathcal{K}}}^{\text{\gls{sr}}})/\sigma_v^2 \bigr)}{\sigma_v^{2N} (N-1)!},
+				\label{eq:energy_distribution_sr}
+			\end{equation}
+			where $\mu_{m_{\mathcal{K}}}^{\text{\gls{sr}}} \triangleq N \bigl\lvert \sum_{k} \alpha_k \boldsymbol{h}_{\mathrm{C},k}^H x_{m_k} \boldsymbol{w} \bigr\rvert^2$.
+The \gls{ml} decision threshold is, $\forall l \in \mathcal{L} \setminus \{L\}$,
+			\begin{equation}
+				t_l^{\text{\gls{sr}}} = \frac{\mu_{l-1}^{\text{\gls{sr}}} \exp \bigl((\mu_{l-1}^{\text{\gls{sr}}}-\mu_{l}^{\text{\gls{sr}}})/\sigma_v^2 (N-1)\bigr) - \mu_{l}^{\text{\gls{sr}}}}{\exp \bigl((\mu_{l-1}^{\text{\gls{sr}}}-\mu_{l}^{\text{\gls{sr}}})/\sigma_v^2 (N-1)\bigr) - 1}.
+				\label{eq:detection_threshold_ml_sr}
 			\end{equation}
@@
 				\item \emph{Bisection:} The traverse-then-bisect algorithm \cite{Nguyen2020a};
-				\item \emph{\gls{ml}:} Maximum likelihood detector \eqref{eq:detection_threshold_maximum_likelihood} \cite{Qian2019}.
+				\item \emph{\gls{ml}:} Maximum likelihood detector \eqref{eq:detection_threshold_ml} \cite{Qian2019}.
 			\end{itemize}

### 2022-10-16 main.tex
:dizzy: Backscatter detection for SR

@@
 	\begin{equation}
-		L(d) = L_0 \biggl(\frac{d_0}{d}\biggr)^\gamma
+		L(d) = L_0 \biggl(\frac{d_0}{d}\biggr)^\gamma,
 	\end{equation}
@@
 			In comparison, the \gls{bcd} algorithm typically requires no more than \num{5} iterations to converge.
-			At the following points (not shown here), the convergence of all three algorithms are much faster thanks to the progressive initialization.
+			At the following points (not presented), the convergence of all three algorithms are much faster thanks to the progressive initialization.
 			Overall, we conclude the proposed algorithms are able to converge within moderate iterations and provide significant rate benefits for the RIScatter system.
@@
 	\begin{subsection}{Comparison of Scattering Applications}
-		For a fair comparison, we consider the setup in Fig. \ref{fi:riscatter_network} and employ \gls{ml} backscatter energy detection for these scattering applications:
+		% TODO SR analysis can achieve large rate at the cost of large N; RIScatter can achieve slightly lower rate at the same N, but also preserves primary performance for smaller N
+		% TODO tradeoff between primary (RIScatter, no SIC) and backscatter (SR, SIC)
+		% For a fair comparison, we consider the setup in Fig. \ref{fi:riscatter_network} and employ \gls{ml} backscatter energy detection for these scattering applications:
+		For a fair comparison, we consider the setup in Fig. \ref{fi:riscatter_network} with \gls{ml} backscatter energy detection for these scattering applications (except \gls{sr}):
 		\begin{itemize}
@@
 			% which follows non-zero mean complex Gaussian distribution $\mathcal{CN}\bigl(\boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}}) \boldsymbol{w},\sigma_v^2\bigr)$ under hypothesis $\mathcal{H}_{m_{\mathcal{K}}}$.
-			which follows non-zero mean complex Gaussian distribution $\mathcal{CN}\bigl(\boldsymbol{h}_{\mathrm{D}}^H + \sum_{k} \alpha_k \boldsymbol{h}_{\mathrm{C},k}^H x_{m_k} \boldsymbol{w},\sigma_v^2\bigr)$ under hypothesis $\mathcal{H}_{m_{\mathcal{K}}}$.
+			which follows non-zero mean complex Gaussian distribution $\mathcal{CN}\bigl((\boldsymbol{h}_{\mathrm{D}}^H + \sum_{k} \alpha_k \boldsymbol{h}_{\mathrm{C},k}^H x_{m_k}) \boldsymbol{w},\sigma_v^2\bigr)$ under hypothesis $\mathcal{H}_{m_{\mathcal{K}}}$.
 			% \sum_{k} \alpha_k \boldsymbol{h}_{\mathrm{C},k}^H x_k
@@
 			while the total backscatter rate follows \eqref{eq:backscatter_mutual_information} with uniform input distribution.
-			\item \emph{\gls{sr}:} When $N$ is sufficiently large, the primary ergodic rate under semi-coherent detection can be approximated by \eqref{eq:primary_mutual_information} with uniform input distribution \cite{Long2020a}.
-			When $s[n]$ is successfully decoded and the direct interference $\boldsymbol{h}_{\mathrm{D}}^H \boldsymbol{w} s[n]$ is perfectly cancelled, the intermediate signal used for backscatter detection is
+			\item \emph{\gls{sr}:}\footnote{Existing } For a sufficiently large $N$, the primary ergodic rate under semi-coherent detection can be approximated by \eqref{eq:primary_mutual_information} with uniform input distribution \cite{Long2020a}.
+			When $s[n]$ is successfully decoded and the direct interference $\boldsymbol{h}_{\mathrm{D}}^H \boldsymbol{w} s[n]$ is perfectly cancelled, the intermediate signal for backscatter detection is
 			\begin{equation}
@@
 			which, under hypothesis $\mathcal{H}_{m_{\mathcal{K}}}$, is only subject to the noise uncertainty and follows non-zero mean complex Gaussian distribution $\mathcal{CN}\bigl(\sum_{k} \alpha_k \boldsymbol{h}_{\mathrm{C},k}^H x_k \boldsymbol{w} s[n],\sigma_v^2\bigr)$.
-			By the law of large numbers, as $N$ goes to infinity, the \gls{pdf} of accumulated intermediate energy approaches
-			\begin{equation}
-				f^{\text{\gls{sr}}}(z|\mathcal{H}_{m_{\mathcal{K}}}) = \frac{(z-\mu_{m_{\mathcal{K}}}^{\text{\gls{sr}}})^{N-1} \exp \bigl(-(z-\mu_{m_{\mathcal{K}}}^{\text{\gls{sr}}})/\sigma_v^2 \bigr)}{\sigma_v^{2N} (N-1)!},
-				\label{eq:energy_distribution_sr}
-			\end{equation}
-			where $\mu_{m_{\mathcal{K}}}^{\text{\gls{sr}}} \triangleq N \bigl\lvert \sum_{k} \alpha_k \boldsymbol{h}_{\mathrm{C},k}^H x_{m_k} \boldsymbol{w} \bigr\rvert^2$.
+			Energy detection is generally suboptimal in this case
+			% By the law of large numbers, for a very large $N$, the \gls{pdf} of accumulated intermediate energy approaches
+			% \begin{equation}
+			% 	f^{\text{\gls{sr}}}(z|\mathcal{H}_{m_{\mathcal{K}}}) = \frac{(z-\mu_{m_{\mathcal{K}}}^{\text{\gls{sr}}})^{N-1} \exp \bigl(-(z-\mu_{m_{\mathcal{K}}}^{\text{\gls{sr}}})/\sigma_v^2 \bigr)}{\sigma_v^{2N} (N-1)!},
+			% 	\label{eq:energy_distribution_sr}
+			% \end{equation}
+			% where $\mu_{m_{\mathcal{K}}}^{\text{\gls{sr}}} \triangleq N \bigl\lvert \sum_{k} \alpha_k \boldsymbol{h}_{\mathrm{C},k}^H x_{m_k} \boldsymbol{w} \bigr\rvert^2$.
 The \gls{ml} decision threshold is, $\forall l \in \mathcal{L} \setminus \{L\}$,
-			\begin{equation}
-				t_l^{\text{\gls{sr}}} = \frac{\mu_{l-1}^{\text{\gls{sr}}} \exp \bigl((\mu_{l-1}^{\text{\gls{sr}}}-\mu_{l}^{\text{\gls{sr}}})/\sigma_v^2 (N-1)\bigr) - \mu_{l}^{\text{\gls{sr}}}}{\exp \bigl((\mu_{l-1}^{\text{\gls{sr}}}-\mu_{l}^{\text{\gls{sr}}})/\sigma_v^2 (N-1)\bigr) - 1}.
-				\label{eq:detection_threshold_ml_sr}
-			\end{equation}
+			% \begin{equation}
+			% 	t_l^{\text{\gls{sr}}} = \frac{\mu_{l-1}^{\text{\gls{sr}}} \exp \bigl((\mu_{l-1}^{\text{\gls{sr}}}-\mu_{l}^{\text{\gls{sr}}})/\sigma_v^2 (N-1)\bigr) - \mu_{l}^{\text{\gls{sr}}}}{\exp \bigl((\mu_{l-1}^{\text{\gls{sr}}}-\mu_{l}^{\text{\gls{sr}}})/\sigma_v^2 (N-1)\bigr) - 1}.
+			% 	\label{eq:detection_threshold_ml_sr}
+			% \end{equation}
 		\end{itemize}

### 2022-10-17 main.tex
:pencil: Update descriptions for scattering applications

@@
 \newacronym{bls}{BLS}{Backtracking Line Search}
+\newacronym{mrc}{MRC}{Maximal Ratio Combining}
 
@@
 	% TODO initialization, convergence
+	% TODO Base e, use 2 in simulation
 
@@
 			The outer metamaterial layer involves numerous sub-wavelength structural units made of metallic or dielectric materials.
-			The properties of unit cells can be artificially tuned for unconventional effective permittivity $\epsilon$ and permeability $\mu$, producing customizable response to the electromagnetic field \cite{Zhou2021}.
+			The properties of unit cells can be artificially tuned for unconventional effective permittivity (epsilon) and permeability (mu), producing customizable response to the electromagnetic field \cite{Zhou2021}.
 			Using epsilon-negative material (e.g., conducing rods) or mu-negative material (e.g., split-ring resonators), ideal metamaterial-based scatterers can reflect the incident waves at the boundary between free space and metamaterial without receiving them \cite{Huang2021a}.
@@
 			\begin{algorithmic}[1]
-				\Require $K$, $N$, $\boldsymbol{h}_{\mathrm{D}}^H$, $\boldsymbol{H}_{\mathrm{C}}$, $\boldsymbol{\alpha}$, $\mathcal{X}$, $\sigma_v^2$, $\rho$, $\boldsymbol{w}$, $\boldsymbol{t}$, $\epsilon$
+				\Require $K$, $N$, $\boldsymbol{h}_{\mathrm{D}}^H$, $\boldsymbol{H}_{\mathrm{C}}$, $\boldsymbol{\alpha}$, $\mathcal{X}$, $\sigma_v^2$, $\rho$, $\boldsymbol{w}$, $\boldsymbol{t}$, $\varepsilon$
 				\Ensure $\{\boldsymbol{p}_k^\star\}_{k \in \mathcal{K}}$
@@
 					\State Redo step \ref{st:input_distribution_begin}--\ref{st:input_distribution_end}
-				\Until $I^{(r)}(x_{\mathcal{K}}) - I^{(r-1)}(x_{\mathcal{K}}) \le \epsilon$
+				\Until $I^{(r)}(x_{\mathcal{K}}) - I^{(r-1)}(x_{\mathcal{K}}) \le \varepsilon$
 			\end{algorithmic}
@@
 			\begin{algorithmic}[1]
-				\Require $Q$, $N$, $\boldsymbol{h}_{\mathrm{D}}^H$, $\boldsymbol{H}_{\mathrm{C}}$, $\boldsymbol{\alpha}$, $\mathcal{X}$, $P$, $\sigma_v^2$, $\rho$, $\{\boldsymbol{p}_k\}_{k \in \mathcal{K}}$, $\boldsymbol{t}$, $\alpha$, $\beta$, $\gamma$, $\epsilon$
+				\Require $Q$, $N$, $\boldsymbol{h}_{\mathrm{D}}^H$, $\boldsymbol{H}_{\mathrm{C}}$, $\boldsymbol{\alpha}$, $\mathcal{X}$, $P$, $\sigma_v^2$, $\rho$, $\{\boldsymbol{p}_k\}_{k \in \mathcal{K}}$, $\boldsymbol{t}$, $\alpha$, $\beta$, $\gamma$, $\varepsilon$
 				\Ensure $\boldsymbol{w}^\star$
@@
 					\State Redo step \ref{st:gradient_update_start}, \ref{st:gradient_update_end}
-				\Until $\lVert\boldsymbol{w}^{(r)}-\boldsymbol{w}^{(r-1)}\rVert \le \epsilon$
+				\Until $\lVert\boldsymbol{w}^{(r)}-\boldsymbol{w}^{(r-1)}\rVert \le \varepsilon$
 			\end{algorithmic}
@@
 		% TODO tradeoff between primary (RIScatter, no SIC) and backscatter (SR, SIC)
+		% !
+SR assume very large N for primary rate analysis.
+However, in such cases SIC is questionable as energy detection over received signal as BBC is already good enough and non-coherent detection can also achieve reasonable performance?
+		% TODO when primary symbols are determined, optimal input distribution at high backscatter SNR is equiprobable for any detection (signal/energy)
 		% For a fair comparison, we consider the setup in Fig. \ref{fi:riscatter_network} and employ \gls{ml} backscatter energy detection for these scattering applications:
-		For a fair comparison, we consider the setup in Fig. \ref{fi:riscatter_network} with \gls{ml} backscatter energy detection for these scattering applications (except \gls{sr}):
+		% For a fair comparison, we consider the setup in Fig. \ref{fi:riscatter_network} with \gls{ml} backscatter energy detection for these scattering applications (except \gls{sr}):
+		% For a fair comparison with RIScatter, we consider the setup in Fig. \ref{fi:riscatter_network} and evaluate the achievable rate pairs for these scattering applications:
+		We consider the setup in Fig. \ref{fi:riscatter_network} and compare the achievable rate pairs of RIScatter and these scattering applications:
 		\begin{itemize}
 			\item \emph{\gls{bbc}:}
-			The primary symbol $s[n]$ becomes deterministic and the receive signal at each primary block is
+			The primary symbol becomes deterministic $s[n]=1$ and the receive signal at each primary block is
 			\begin{equation}
@@
 			\item \emph{\gls{ambc}:} The user decodes both links independently and semi-coherently by treating the other as interference or uncertainty.
-			Hence, the primary achievable rate can be approximated by\footnote{To provide a preliminary benchmark, we approximate the scattered signal components from finite-input backscatter sources by independent interference from Gaussian sources.}
+			Hence, the primary achievable rate can be approximated by\footnote{To provide a preliminary benchmark, we approximate the unknown signal components from finite-input backscatter sources by independent interference from Gaussian sources.}
 			\begin{equation}
@@
 			while the total backscatter rate follows \eqref{eq:backscatter_mutual_information} with uniform input distribution.
-			\item \emph{\gls{sr}:}\footnote{Existing } For a sufficiently large $N$, the primary ergodic rate under semi-coherent detection can be approximated by \eqref{eq:primary_mutual_information} with uniform input distribution \cite{Long2020a}.
+			\item \emph{\gls{sr}:} For a sufficiently large $N$, the primary ergodic rate under semi-coherent detection asymptotically approaches \eqref{eq:primary_mutual_information} with uniform input distribution \cite{Long2020a}.
 			When $s[n]$ is successfully decoded and the direct interference $\boldsymbol{h}_{\mathrm{D}}^H \boldsymbol{w} s[n]$ is perfectly cancelled, the intermediate signal for backscatter detection is
@@
 			\end{equation}
-			which, under hypothesis $\mathcal{H}_{m_{\mathcal{K}}}$, is only subject to the noise uncertainty and follows non-zero mean complex Gaussian distribution $\mathcal{CN}\bigl(\sum_{k} \alpha_k \boldsymbol{h}_{\mathrm{C},k}^H x_k \boldsymbol{w} s[n],\sigma_v^2\bigr)$.
-			Energy detection is generally suboptimal in this case
-			% By the law of large numbers, for a very large $N$, the \gls{pdf} of accumulated intermediate energy approaches
-			% \begin{equation}
-			% 	f^{\text{\gls{sr}}}(z|\mathcal{H}_{m_{\mathcal{K}}}) = \frac{(z-\mu_{m_{\mathcal{K}}}^{\text{\gls{sr}}})^{N-1} \exp \bigl(-(z-\mu_{m_{\mathcal{K}}}^{\text{\gls{sr}}})/\sigma_v^2 \bigr)}{\sigma_v^{2N} (N-1)!},
-			% 	\label{eq:energy_distribution_sr}
-			% \end{equation}
-			% where $\mu_{m_{\mathcal{K}}}^{\text{\gls{sr}}} \triangleq N \bigl\lvert \sum_{k} \alpha_k \boldsymbol{h}_{\mathrm{C},k}^H x_{m_k} \boldsymbol{w} \bigr\rvert^2$.
-The \gls{ml} decision threshold is, $\forall l \in \mathcal{L} \setminus \{L\}$,
-			% \begin{equation}
-			% 	t_l^{\text{\gls{sr}}} = \frac{\mu_{l-1}^{\text{\gls{sr}}} \exp \bigl((\mu_{l-1}^{\text{\gls{sr}}}-\mu_{l}^{\text{\gls{sr}}})/\sigma_v^2 (N-1)\bigr) - \mu_{l}^{\text{\gls{sr}}}}{\exp \bigl((\mu_{l-1}^{\text{\gls{sr}}}-\mu_{l}^{\text{\gls{sr}}})/\sigma_v^2 (N-1)\bigr) - 1}.
-			% 	\label{eq:detection_threshold_ml_sr}
-			% \end{equation}
+			which only involves noise uncertainty under hypothesis $\mathcal{H}_{m_{\mathcal{K}}}$.
+			% and follows non-zero mean complex Gaussian distribution $\mathcal{CN}\bigl(\sum_{k} \alpha_k \boldsymbol{h}_{\mathrm{C},k}^H x_k \boldsymbol{w} s[n],\sigma_v^2\bigr)$.
+			By \gls{mrc} over $N$ primary blocks, the effective backscatter \gls{snr} is increased by $N$ times, and the total achievable for nodes with equiprobable inputs is \cite{Wang2014a}
+			\begin{equation}
+				I_{\mathrm{B}}(x_{\mathcal{K}};\hat{y}_{\text{\gls{sr}}}) = K \log M - \frac{\epsilon}{M^K},
+			\end{equation}
+			where $\epsilon \triangleq \sum_{m_{\mathcal{K}}} \mathbb{E}_{\hat{v}} \log \sum_{m_{\mathcal{K}}'} \exp ( - {\lvert x_{m_{\mathcal{K}}} - x_{m_{\mathcal{K}}'} + \hat{v} \rvert^2}/{2 \sigma^2} )$ and $\hat{v} \sim \mathcal{CN}(0,\sigma_v^2/N)$.
+			For a sufficiently large $N$, $\epsilon$ is negligible and the total backscatter rate approaches $K \log M$.
+			\item \emph{\gls{ris}:} Since the backscatter symbol tuple $x_{\mathcal{K}}$ becomes deterministic, the total backscatter rate is zero and the primary achievable rate boils down to a special case of \eqref{eq:primary_mutual_information}
+			\begin{equation}
+				I_P^{\text{\gls{ris}}}(s;y|x_{\mathcal{K}}) = I_P(s;y|x_{m_{\mathcal{K}}^{\star}}) = \log \Bigl(1 + \frac{\lvert \boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}^{\star}}) \boldsymbol{w} \rvert^2}{\sigma_v^2}\Bigr),
+			\end{equation}
+			where $m_{\mathcal{K}}^{\star} = \arg \max_{m_{\mathcal{K}}} I_P(s;y|x_{m_{\mathcal{K}}})$.
 		\end{itemize}
@@
 				\item \emph{Cooperation:} Numerical symbol tuple distribution (i.e., $K$-dimensional joint probability array) evaluation by the Blahut-Arimoto algorithm \cite{Arimoto1972,Blahut1972a}.
+				% TODO MODIFIED BLAHUT-ARIMOTO, or modified algorithm 1 by treating as a single source
 			\end{itemize}

### 2022-10-18 src/plot/plot_comparison.m
:construction: Add rate comparison

@@ -1,0 +1,27 @@
+clear; run('../setup'); load('../data/region_comparison'); clc; close all;
+
+%% * Retrieve RIScatter rate region
+rate = zeros(2, nWeights + 3);
+for iWeight = 1 : nWeights
+	rate(:, iWeight) = ResultRiscatter(iWeight).rate;
+end
+[rate(1, nWeights + 1), rate(2, nWeights + 2)] = deal(max(rate(1, :)), max(rate(2, :)));
+regionRiscatter = rate(:, convhull(transpose(rate)));
+
+%% * Plot achievable rates
+figure('Name', 'Achievable Rates of Different Scattering Applications', 'Position', [0, 0, 500, 400]);
+plotHandle = gobjects(1, 5);
+hold all;
+plotHandle(1) = scatter(rateBbc(1, :) / log(2), rateBbc(2, :) / log(2), 'Marker', 'o', 'DisplayName', 'BBC');
+plotHandle(2) = scatter(rateAmbc(1, :) / log(2), rateAmbc(2, :) / log(2), 'Marker', '+', 'DisplayName', 'AmBC');
+plotHandle(3) = scatter(rateSr(1, :) / log(2), rateSr(2, :) / log(2), 'Marker', 'p', 'DisplayName', 'SR');
+plotHandle(4) = scatter(rateRis(1, :) / log(2), rateRis(2, :) / log(2), 'Marker', 'x', 'DisplayName', 'RIS');
+plotHandle(5) = plot(regionRiscatter(1, :) / log(2), regionRiscatter(2, :) / log(2), 'Marker', '^', 'DisplayName', 'RIScatter');
+uistack(plotHandle(4), 'top');
+hold off; legend(plotHandle, 'Location', 'sw'); grid on; box on; axis tight;
+xlabel('Primary Rate [bits/s/Hz]');
+ylabel('Total Backscatter Rate [bits/BSP]');
+
+savefig('figures/region_comparison');
+matlab2tikz('../../assets/simulation/region_comparison.tex', 'extraaxisoptions', ['title style={font=\Large}, ' 'label style={font=\Large}, ' 'ticklabel style={font=\large}, ' 'legend style={font=\large}']);
+

### 2022-10-18 src/region_comparison.m

@@ -1,7 +1,7 @@
 clear; setup; cvx_begin; cvx_end; clc; config_comparison;
 
 % * Initialize struct
-Result(nWeights) = struct('weight', [], 'rate', [], 'distribution', [], 'threshold', [], 'beamforming', []);
+ResultRiscatter(nWeights) = struct('weight', [], 'rate', [], 'distribution', [], 'threshold', [], 'beamforming', []);
 
 % * Generate channels
 directChannel = sqrt(path_loss(directDistance, directExponent)) * fading_ricean(nTxs, nRxs, directFactor);
@@ -14,14 +14,15 @@ equivalentChannel = directChannel + scatterRatio * cascadedChannel * transpose(c
 % * Clear persistent variables
 clear block_coordinate_descent distribution_kkt distribution_cooperation beamforming_pgd threshold_bisection;
 
+% * Obtain achievable rates for BBC, AmBC, SR, RIS and RIScatter
 [rateBbc, distributionBbc, thresholdBbc] = benchmark_bbc(nTags, symbolRatio, transmitPower, noisePower, equivalentChannel);
 [rateAmbc, distributionAmbc, thresholdAmbc] = benchmark_ambc(nTags, symbolRatio, transmitPower, noisePower, equivalentChannel, scatterRatio, directChannel, cascadedChannel);
 [rateSr, distributionSr] = benchmark_sr(nTags, transmitPower, noisePower, equivalentChannel);
-[rateRis, distributionRis] = benchmark_ris(nTags, transmitPower, noisePower, equivalentChannel);
-% * Evaluate rate region
+[rateRis, distributionRis] = benchmark_ris(nTags, transmitPower, noisePower, equivalentChannel);% * Evaluate rate region
 for iWeight = 1 : nWeights
 	weight = weightSet(iWeight);
 	[rateRiscatter, distributionRiscatter, thresholdRiscatter, beamformingRiscatter] = block_coordinate_descent(nTags, symbolRatio, transmitPower, noisePower, nBins, weight, equivalentChannel, cascadedChannel, 'Distribution', 'kkt', 'Beamforming', 'pgd', 'Threshold', 'smawk');
-	Result(iWeight) = struct('weight', weight, 'rate', rateRiscatter, 'distribution', distributionRiscatter, 'threshold', thresholdRiscatter, 'beamforming', beamformingRiscatter);
[…]

### 2022-10-18 assets/simulation/region_comparison.tex
:bento: Update assets

% This file was created by matlab2tikz.
%
%The latest updates can be retrieved from
%  http://www.mathworks.com/matlabcentral/fileexchange/22022-matlab2tikz-matlab2tikz
%where you can also make suggestions and rate matlab2tikz.
%
\definecolor{mycolor1}{rgb}{0.00000,0.44700,0.74100}%
\definecolor{mycolor2}{rgb}{0.85000,0.32500,0.09800}%
\definecolor{mycolor3}{rgb}{0.92900,0.69400,0.12500}%
\definecolor{mycolor4}{rgb}{0.46600,0.67400,0.18800}%
\definecolor{mycolor5}{rgb}{0.49400,0.18400,0.55600}%
%
\begin{tikzpicture}

\begin{axis}[%
width=4.036in,
height=3.396in,
at={(0.677in,0.458in)},
scale only axis,
xmin=0,
xmax=6.31753053408973,
xlabel style={font=\color{white!15!black}},
xlabel={Primary Rate [bits/s/Hz]},
ymin=0,
ymax=4,
ylabel style={font=\color{white!15!black}},
ylabel={Total Backscatter Rate [bits/BSP]},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
legend style={at={(0.03,0.03)}, anchor=south west, legend cell align=left, align=left, draw=white!15!black},
title style={font=\Large}, label style={font=\Large}, ticklabel style={font=\large}, legend style={font=\large}
]
\addplot[only marks, mark=o, mark options={}, mark size=1.5000pt, draw=mycolor1] table[row sep=crcr]{%
x	y\\
0	3.59312409820682\\
};
\addlegendentry{BBC}

\addplot[only marks, mark=+, mark options={}, mark size=1.5000pt, draw=mycolor2] table[row sep=crcr]{%
x	y\\
5.22509853007389	0.48870764883876\\
};
\addlegendentry{AmBC}

\addplot[only marks, mark=star, mark options={}, mark size=1.5000pt, draw=mycolor3] table[row sep=crcr]{%
x	y\\
6.23320855945527	4\\
};
\addlegendentry{SR}

\addplot [color=mycolor4, line width=2.0pt, mark=triangle, mark options={solid, mycolor4}]
  table[row sep=crcr]{%
6.2312470588505	0.763370378895508\\
0	0.763370378895508\\
0	0\\
6.31753037065033	0\\
6.31753037065033	2.89828758562747e-06\\
6.25236174872316	0.732006507235074\\
6.23838106449329	0.759813210567223\\
6.23600551868738	0.761788175170211\\
6.2343051569439	0.76271690446849\\
6.23362512288657	0.762975207316704\\
6.23302973681356	0.763148304111542\\
6.23250419898104	0.763259938452111\\
6.23203751322923	0.763326719439174\\
6.23182269048002	0.763347229570488\\
6.23161922496453	0.76336070790686\\
6.23154098505783	0.763364350445281\\
6.23146435792084	0.763367088213014\\
6.23138932037904	0.76336897307198\\
6.23131607523334	0.763370052183618\\
6.2312470588505	0.763370378895508\\
};
\addlegendentry{RIScatter}

\addplot[only marks, mark=x, mark options={}, mark size=1.5000pt, draw=mycolor5] table[row sep=crcr]{%
x	y\\
6.31753053408973	0\\
};
\addlegendentry{RIS}

\end{axis}
\end{tikzpicture}%

### 2022-10-18 assets/simulation/region_comparison.tex
:bento: Add scattering rates comparison

@@
 %
-\definecolor{mycolor1}{rgb}{0.00000,0.44700,0.74100}%
-\definecolor{mycolor2}{rgb}{0.85000,0.32500,0.09800}%
+\definecolor{mycolor1}{rgb}{0.46667,0.67451,0.18824}%
+\definecolor{mycolor2}{rgb}{0.49400,0.18400,0.55600}%
 \definecolor{mycolor3}{rgb}{0.92900,0.69400,0.12500}%
-\definecolor{mycolor4}{rgb}{0.46600,0.67400,0.18800}%
-\definecolor{mycolor5}{rgb}{0.49400,0.18400,0.55600}%
+\definecolor{mycolor4}{rgb}{0.85000,0.32500,0.09800}%
+\definecolor{mycolor5}{rgb}{0.00000,0.44700,0.74100}%
 %
@@
 \begin{axis}[%
-width=4.036in,
-height=3.396in,
-at={(0.677in,0.458in)},
+width=4.079in,
+height=3.432in,
+at={(0.684in,0.463in)},
 scale only axis,
 xmin=0,
-xmax=6.31753053408973,
+xmax=7.08488905081188,
 xlabel style={font=\color{white!15!black}},
@@
 ymin=0,
-ymax=4,
+ymax=2,
 ylabel style={font=\color{white!15!black}},
@@
 legend style={at={(0.03,0.03)}, anchor=south west, legend cell align=left, align=left, draw=white!15!black},
-title style={font=\Large}, label style={font=\Large}, ticklabel style={font=\large}, legend style={font=\large}
+title style={font=\Large}, label style={font=\Large}, ticklabel style={font=\large}, legend style={font=\large}, reverse legend, every axis plot/.append style={line width=2pt}
 ]
-\addplot[only marks, mark=o, mark options={}, mark size=1.5000pt, draw=mycolor1] table[row sep=crcr]{%
+\addplot [color=mycolor1, mark=triangle, mark options={solid, mycolor1}]
+  table[row sep=crcr]{%
+6.41670947751651	1.6054968458145\\
+0	1.6054968458145\\
+0	0\\
+7.08488904258997	0\\
+7.08488904258997	4.1836174712136e-07\\
+6.90245078291004	1.01381402853452\\
+6.6407882228124	1.4980015567956\\
+6.57239022993099	1.55479524496005\\
+6.51932412280019	1.58378871636645\\
+6.49722825073873	1.59220191008592\\
+6.4775306470264	1.59794430837116\\
+6.4598927531162	1.60170353740201\\
+6.44402970380102	1.60398330481762\\
+6.43668727400095	1.6046886802456\\
+6.42970223763566	1.60515550025508\\
+6.42700280669212	1.60528273332009\\
+6.42435520073694	1.60537879376922\\
+6.4217579842616	1.60544542043883\\
+6.41920966721981	1.60548425498564\\
+6.41670947751651	1.6054968458145\\
+};
+\addlegendentry{RIScatter}
+
+\addplot[only marks, mark=x, mark options={}, mark size=3.5355pt, draw=mycolor2] table[row sep=crcr]{%
 x	y\\
-0	3.59312409820682\\
+7.08488905081188	0\\
+};
+\addlegendentry{RIS}
+
+\addplot[only marks, mark=square, mark options={}, mark size=2.5000pt, draw=mycolor3] table[row sep=crcr]{%
+x	y\\
+6.44440818236646	2\\
+};
+\addlegendentry{SR}
+
+\addplot[only marks, mark=+, mark options={}, mark size=3.5355pt, draw=mycolor4] table[row sep=crcr]{%
+x	y\\
+3.85295770698096	1.53088335179488\\
+};
+\addlegendentry{AmBC}
+
+\addplot[only marks, mark=o, mark options={}, mark size=3.5355pt, draw=mycolor5] table[row sep=crcr]{%
+x	y\\
+0	1.99999999999997\\
 };
@@
 
-\addplot[only marks, mark=+, mark options={}, mark size=1.5000pt, draw=mycolor2] table[row sep=crcr]{%
-x	y\\
-5.22509853007389	0.48870764883876\\
-};
-\addlegendentry{AmBC}
-
-\addplot[only marks, mark=star, mark options={}, mark size=1.5000pt, draw=mycolor3] table[row sep=crcr]{%
-x	y\\
-6.23320855945527	4\\
-};
-\addlegendentry{SR}
-
-\addplot [color=mycolor4, line width=2.0pt, mark=triangle, mark options={solid, mycolor4}]
-  table[row sep=crcr]{%
-6.2312470588505	0.763370378895508\\
-0	0.763370378895508\\
-0	0\\
-6.31753037065033	0\\
-6.31753037065033	2.89828758562747e-06\\
-6.25236174872316	0.732006507235074\\
-6.23838106449329	0.759813210567223\\
-6.23600551868738	0.761788175170211\\
-6.2343051569439	0.76271690446849\\
-6.23362512288657	0.762975207316704\\
-6.23302973681356	0.763148304111542\\
-6.23250419898104	0.763259938452111\\
-6.23203751322923	0.763326719439174\\
-6.23182269048002	0.763347229570488\\
-6.23161922496453	0.76336070790686\\
-6.23154098505783	0.763364350445281\\
-6.23146435792084	0.763367088213014\\
-6.23138932037904	0.76336897307198\\
-6.23131607523334	0.763370052183618\\
-6.2312470588505	0.763370378895508\\
-};
-\addlegendentry{RIScatter}
-
-\addplot[only marks, mark=x, mark options={}, mark size=1.5000pt, draw=mycolor5] table[row sep=crcr]{%
-x	y\\
-6.31753053408973	0\\
-};
-\addlegendentry{RIS}
-
 \end{axis}

### 2022-10-18 main.tex
:pencil: Update configurations

@@
 \usepackage{xcolor}
-
 % dark mode
@@
 \ref{fi:riscatter_network}.
-	We assume the AP-user distance is \qty{10}{\meter}, $K=2$ RIScatter nodes are randomly dropped within a disk of radius \qty{2}{\meter} centered at the user, the \gls{ap} is with $Q=4$ transmit antennas and an average power budget $P=\qty{36}{\dBm}$, the nodes employs \num{4}-\gls{qam} with amplitude scattering ratio $\alpha=0.5$, the user is with average noise power $\sigma_v^2=\qty{-40}{\dBm}$, and the symbol period ratio is $N=20$.
+	We assume the AP-user distance is \qty{10}{\meter} and at least one RIScatter nodes are randomly dropped in a disk centered at the user with radius \qty{2}{\meter}.
+	% The \gls{ap} is with an average power budget $P=\qty{36}{\dBm}$, the nodes employs $M$-\gls{qam} with amplitude scattering ratio $\alpha=0.5$, the user is with average noise power $\sigma_v^2=\qty{-40}{\dBm}$, and the symbol period ratio is $N=20$.
+	The \gls{ap} is with an average transmit power budget $P=\qty{36}{\dBm}$, all nodes employs $M$-\gls{qam} with amplitude scattering ratio $\alpha=0.5$, and the user is with average noise power $\sigma_v^2=\qty{-40}{\dBm}$.
+	% Q=4 and symbol period ratio is $N=20$.
 	For all channels involved, we consider a distance-dependent path loss model
@@
 	We choose $\gamma_{\mathrm{D}}=2.6$, $\gamma_{\mathrm{F}}=2.4$, $\gamma_{\mathrm{B}}=2$, and $\kappa_{\mathrm{D}}=\kappa_{\mathrm{F}}=\kappa_{\mathrm{B}}=5$ for direct, forward and backward links.
-	The finite threshold domain $\mathcal{T}$ comes from $b$-bit uniform discretization over the critical interval defined by the confidence bounds of edge hypotheses (i.e., lower bound of $\mathcal{H}_1$ and upper bound of $\mathcal{H}_L$) with confidence level $1-\varepsilon$, where $b=9$ and $\varepsilon=\num{1e-3}$.
-	All achievable rate curves/regions are averaged over \num{1000} realizations, and the parameters remain fixed unless otherwise specified.
+	The finite threshold domain $\mathcal{T}$ is obtained by $b$-bit uniform discretization over the critical interval defined by the confidence bounds of edge hypotheses (i.e., lower bound of $\mathcal{H}_1$ and upper bound of $\mathcal{H}_L$) with confidence level $1-\varepsilon$, where $b=9$ and $\varepsilon=\num{1e-3}$.
+	% The achievable primary-(sum-)backscatter rate point is defined as $(I_{\mathrm{P}}(s;y),)$
+	All average achievable rate points/regions are evaluated over \num{1000} realizations, and the parameters remain fixed unless otherwise specified.
 
@@
 \ref{fi:wsr_convergence}, we plot the weighted sum of primary and total backscatter rates at $\rho=0$ for \gls{kkt}, \gls{pgd} (on the first call within \gls{bcd}) and \gls{bcd} algorithms in each iteration.
-			For $K=8$ and $M=2$, Algorithm \ref{al:input_distribution} typically takes around \num{100} fast iterations of closed-form expression \eqref{eq:input_kkt_solution} to converge to the \gls{kkt} input distribution.
-			For $Q=4$, around \num{10} iterations are required for Algorithm \ref{al:active_beamforming} to converge, where the gradient needs to be evaluated by \eqref{eq:weighted_sum_mutual_information_gradient} and the step size needs to be refined by \gls{bls}.
-			In comparison, the \gls{bcd} algorithm typically requires no more than \num{5} iterations to converge.
-			At the following points (not presented), the convergence of all three algorithms are much faster thanks to the progressive initialization.
+			For $K=8$ and $M=2$, Algorithm \ref{al:input_distribution} typically takes around \num{100} fast iterations over closed-form expression \eqref{eq:input_kkt_solution} to converge to the \gls{kkt} input distribution.
+			For $Q=4$, around \num{10} iterations are required for Algorithm \ref{al:active_beamforming} to converge, where the gradient needs to be computed by \eqref{eq:weighted_sum_mutual_information_gradient} and the step size needs to be refined by \gls{bls}.
+			In comparison, the \gls{bcd} algorithm typically requires at most \num{5} iterations to converge.
+			At the following rate points (not presented), the convergence of all three algorithms become much faster thanks to the progressive initialization.
 			Overall, we conclude the proposed algorithms are able to converge within moderate iterations and provide significant rate benefits for the RIScatter system.
@@
 		% TODO when primary symbols are determined, optimal input distribution at high backscatter SNR is equiprobable for any detection (signal/energy)
+		% TODO (I(X_1;Y_1),I(X_2;Y_2))
 		% For a fair comparison, we consider the setup in Fig. \ref{fi:riscatter_network} and employ \gls{ml} backscatter energy detection for these scattering applications:
@@
 		% For a fair comparison with RIScatter, we consider the setup in Fig. \ref{fi:riscatter_network} and evaluate the achievable rate pairs for these scattering applications:
-		We consider the setup in Fig. \ref{fi:riscatter_network} and compare the achievable rate pairs of RIScatter and these scattering applications:
+		% We consider the setup in Fig. \ref{fi:riscatter_network} and compare the achievable rate pairs of RIScatter and these scattering applications:
+		On top of the setup in Fig. \ref{fi:riscatter_network}, we compare the achievable rate pairs of RIScatter and these scattering applications:
 		\begin{itemize}
@@
 			\begin{equation}
-				I_P^{\text{\gls{ambc}}}(s;y) \approx \log \Bigl(1 + \frac{\lvert\boldsymbol{h}_{\mathrm{D}}^H\boldsymbol{w}\rvert^2}{\sum_{k}\lvert \alpha_k \boldsymbol{h}_{\mathrm{C},k}^H \boldsymbol{w}\rvert^2+\sigma_v^2}\Bigr),
+				I_{\mathrm{P}}^{\text{\gls{ambc}}}(s;y) \approx \log \Bigl(1 + \frac{\lvert\boldsymbol{h}_{\mathrm{D}}^H\boldsymbol{w}\rvert^2}{\sum_{k}\lvert \alpha_k \boldsymbol{h}_{\mathrm{C},k}^H \boldsymbol{w}\rvert^2+\sigma_v^2}\Bigr),
 			\end{equation}
@@
 			\begin{equation}
-				I_P^{\text{\gls{ris}}}(s;y|x_{\mathcal{K}}) = I_P(s;y|x_{m_{\mathcal{K}}^{\star}}) = \log \Bigl(1 + \frac{\lvert \boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}^{\star}}) \boldsymbol{w} \rvert^2}{\sigma_v^2}\Bigr),
-			\end{equation}
-			where $m_{\mathcal{K}}^{\star} = \arg \max_{m_{\mathcal{K}}} I_P(s;y|x_{m_{\mathcal{K}}})$.
+				I_{\mathrm{P}}^{\text{\gls{ris}}}(s;y|x_{\mathcal{K}}) = I_{\mathrm{P}}(s;y|x_{m_{\mathcal{K}}^{\star}}) = \log \Bigl(1 + \frac{\lvert \boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}^{\star}}) \boldsymbol{w} \rvert^2}{\sigma_v^2}\Bigr),
+			\end{equation}
+			where $m_{\mathcal{K}}^{\star} = \arg \max_{m_{\mathcal{K}}} I_{\mathrm{P}}(s;y|x_{m_{\mathcal{K}}})$.
 		\end{itemize}
+		\begin{figure}[!t]
+			\centering
+			\resizebox{0.75\columnwidth}{!}{
+				\input{assets/simulation/region_comparison.tex}
+			}
+			\caption{Typical achievable rate points of scattering applications for $Q=1$, $K=1$, $M=4$ and $N=1000$.}
+			\label{fi:region_comparison}
+		\end{figure}
+
+		Fig. \ref{fi:region_comparison} presents the achieve rate points by different scattering applications when $Q=1$, $K=1$, $M=4$ and $N=1000$.
 	\end{subsection}

### 2022-10-19 assets/simulation/region_comparison.tex
:bento: Update assets

@@
 legend style={at={(0.03,0.03)}, anchor=south west, legend cell align=left, align=left, draw=white!15!black},
-title style={font=\Large}, label style={font=\Large}, ticklabel style={font=\large}, legend style={font=\large}, reverse legend, every axis plot/.append style={line width=2pt}
+title style={font=\LARGE},
+label style={font=\LARGE},
+ticklabel style={font=\Large},
+legend style={font=\Large},
+reverse legend,
+every axis plot/.append style={line width=2pt}
 ]
-\addplot [color=mycolor1, mark=triangle, mark options={solid, mycolor1}]
+\addplot [color=mycolor1, line width=2.0pt, mark=triangle, mark options={solid, mycolor1}]
   table[row sep=crcr]{%

### 2022-10-19 main.tex
:construction: Update layout

@@
 \newacronym{mrc}{MRC}{Maximal Ratio Combining}
+\newacronym{sdma}{SDMA}{Space-Division Multiple Access}
 
@@
 			% and follows non-zero mean complex Gaussian distribution $\mathcal{CN}\bigl(\sum_{k} \alpha_k \boldsymbol{h}_{\mathrm{C},k}^H x_k \boldsymbol{w} s[n],\sigma_v^2\bigr)$.
-			By \gls{mrc} over $N$ primary blocks, the effective backscatter \gls{snr} is increased by $N$ times, and the total achievable for nodes with equiprobable inputs is \cite{Wang2014a}
+			By \gls{mrc} over $N$ primary blocks, the total achievable for nodes with equiprobable inputs is \cite{Wang2014a}
 			\begin{equation}
@@
 			\centering
-			\resizebox{0.75\columnwidth}{!}{
+			\resizebox{0.65\columnwidth}{!}{
 				\input{assets/simulation/region_comparison.tex}
@@
 
-		Fig. \ref{fi:region_comparison} presents the achieve rate points by different scattering applications when $Q=1$, $K=1$, $M=4$ and $N=1000$.
-	\end{subsection}
-
-	\begin{subsection}{Input Distribution versus Link Priority}
+		Fig. \ref{fi:region_comparison} presents the typical achieve rate points of different scattering applications for $Q=1$, $K=1$, $M=4$ and $N=1000$.
+		First, we observe both \gls{bbc} and \gls{sr} can achieve the highest backscatter rate with coherent detection over the receive energy and intermediate signal, respectively.
+		This is because repetition coding with \gls{mrc} over $N$ primary blocks effectively increases the backscatter \gls{snr} by $N$ times, and the information loss due to the signal-to-energy conversion on top may be insignificant.
+		However, the asymptotic primary and backscatter rate analysis only provides upper bounds for \gls{sr}.
+		Using a very large $N$ not only reduces the system throughput\footnote{For example, Wi-Fi sampling rate is \qty{20}{\MHz} while \gls{rfid} load switching speed varies between \num{100}s of \unit{\kHz} to \num{10}s of \unit{\MHz} \cite{Torres2021}, corresponding to a typical symbol period ratio $N$ between \num{1} and \num{100}.} but also requires the operation-intensive \gls{sic} over each primary block.
+		When the duration of primary and backscatter symbol are comparable, the randomly scattered signals should be modelled as interference to primary link rather than quasi-static multipath components, and the achievable rate point of \gls{sr} will move towards the origin.
+		On the other hand, RIScatter provides a lower backscatter rate than \gls{bbc} and \gls{sr} due to semi-coherent detection, but preserves the primary rate benefit for arbitrary $N$.
+
+		% TODO SR analysis can achieve large rate at the cost of large N; RIScatter can achieve slightly lower rate at the same N, but also preserves primary performance for smaller N
+		% TODO tradeoff between primary (RIScatter, no SIC) and backscatter (SR, SIC)
+		% !
+SR assume very large N for primary rate analysis.
+However, in such cases SIC is questionable as energy detection over received signal as BBC is already good enough and non-coherent detection can also achieve reasonable performance?
+		% TODO when primary symbols are determined, optimal input distribution at high backscatter SNR is equiprobable for any detection (signal/energy)
+		% TODO Wi-Fi sampling rate 20 MHz (symbol period 50 nS), RFID symbol rate/load switching speed 100s KHz to 10s MHz [Backscatter Communications], fast load switching speed is key for high data rate - symbol ratio is not very large
+
+		Backscatter advantage of SR using SIC is prominent for a smaller N
+		% correlation by double modulation improves the detection performance
+		% when $N$ is sufficiently large.
+	\end{subsection}
+
+	\begin{subsection}{Input Distribution under Different Weights}
 		\begin{figure}[!t]
 			\centering
-			\subfloat[Instance 1\label{fi:distribution_weights_1}]{
-				\resizebox{0.48\columnwidth}{!}{
-					\input{assets/simulation/distribution_weights_1.tex}
-				}
-			}
-			\subfloat[Instance 2\label{fi:distribution_weights_2}]{
-				\resizebox{0.48\columnwidth}{!}{
-					\input{assets/simulation/distribution_weights_2.tex}
-				}
-			}
-			\caption{Typical instances of node input distribution for different weights.}
+			\resizebox{0.65\columnwidth}{!}{
+				\input{assets/simulation/distribution_weights.tex}
+			}
+			\caption{Typical reflection state distribution under different weights for $Q=1$, $K=1$, $M=4$ and $N=20$.}
 			\label{fi:distribution_weights}
@@
 		The objective of this study is to demonstrate each RIScatter node can adjust its input distribution based on \gls{csi} and link priority to balance backscatter modulation and passive beamforming.
-		For this aim, we evaluate the \gls{kkt} input distribution by Algorithm \ref{al:input_distribution} for a single node under different weights $\rho=\{0,0.1,0.2,0.3,1\}$ in Fig.
-\ref{fi:distribution_weights}, where \subref*{fi:distribution_weights_1} and \subref*{fi:distribution_weights_2} are two representative instances.
+		For this aim, we evaluate the \gls{kkt} input distribution by Algorithm \ref{al:input_distribution} for a single node under different weights in Fig. \ref{fi:distribution_weights}.
 		We observe that as $\rho$ increases from \num{0} to \num{1}, the \gls{kkt} input distribution
@@
 
-	\begin{subsection}{Achievable Rates versus Energy Discretization Bits}
-		\begin{figure}[!t]
-			\subfloat[Primary Rate\label{fi:rate_bits_primary}]{
-				\resizebox{0.48\columnwidth}{!}{
-					\input{assets/simulation/rate_bits_primary.tex}
-				}
-			}
-			\subfloat[Total Backscatter Rate\label{fi:rate_bits_backscatter}]{
-				\resizebox{0.48\columnwidth}{!}{
-					\input{assets/simulation/rate_bits_backscatter.tex}
-				}
-			}
-			\caption{Average achievable primary and total backscatter rates for different energy discretization bits for $\rho=0$.}
-			\label{fi:rate_bits}
-		\end{figure}
-		We now reveal how the analog-to-digital conversion of feasible threshold domain from $\mathbb{R}_+^{L+1}$ to $\mathcal{T}^{L+1}$ affects the average RIScatter performance.
-		For a fixed input distribution and active beamforming, Fig. \ref{fi:rate_bits} shows the impact of energy discretization bits $b$ on the average achievable rates when $\rho=0$.
-		We observe the primary rate is a constant for different $b$ as expected from Remark \ref{re:backscatter_decision}.
-		This conclusion holds for arbitrary $\rho$ because the randomness of reflection patterns over time can always be eliminated upon successful backscatter decoding.
-		When the nodes transmit at non-zero total rate, the user can re-encode backscatter messages to recover their reflection patterns at each primary block.
-		Otherwise, the reflection patterns of all nodes are fully deterministic, and the state index tuple can be fed back to the user together with \gls{csi}.
-		We also notice increasing $b$ boosts the total backscatter rate and the benefit becomes marginal when $b$ is sufficiently large ($2^b \gg \mathrm{card}(\mathcal{L})$).
-		This is because a larger $b$ allows the decision regions to be constructed from narrower energy bins, which mitigates the transformation loss from problem \eqref{op:decision_threshold} to \eqref{op:decision_threshold_discrete}.
-		Therefore, we conclude a proper selection of $b$ is the key to balance backscatter performance and computational complexity.
-	\end{subsection}
+	% \begin{subsection}{Achievable Rates versus Energy Discretization Bits}
+	% 	\begin{figure}[!t]
+	% 		\subfloat[Primary Rate\label{fi:rate_bits_primary}]{
+	% 			\resizebox{0.48\columnwidth}{!}{
+	% 				\input{assets/simulation/rate_bits_primary.tex}
+	% 			}
+	% 		}
+	% 		\subfloat[Total Backscatter Rate\label{fi:rate_bits_backscatter}]{
+	% 			\resizebox{0.48\columnwidth}{!}{
+	% 				\input{assets/simulation/rate_bits_backscatter.tex}
+	% 			}
+	% 		}
+	% 		\caption{Average achievable primary and total backscatter rates for different energy discretization bits for $\rho=0$.}
+	% 		\label{fi:rate_bits}
+	% 	\end{figure}
+	% 	We now reveal how the analog-to-digital conversion of feasible threshold domain from $\mathbb{R}_+^{L+1}$ to $\mathcal{T}^{L+1}$ affects the average RIScatter performance.
+	% 	For a fixed input distribution and active beamforming, Fig. \ref{fi:rate_bits} shows the impact of energy discretization bits $b$ on the average achievable rates when $\rho=0$.
+	% 	We observe the primary rate is a constant for different $b$ as expected from Remark \ref{re:backscatter_decision}.
+	% 	This conclusion holds for arbitrary $\rho$ because the randomness of reflection patterns over time can always be eliminated upon successful backscatter decoding.
+	% 	When the nodes transmit at non-zero total rate, the user can re-encode backscatter messages to recover their reflection patterns at each primary block.
+	% 	Otherwise, the reflection patterns of all nodes are fully deterministic, and the state index tuple can be fed back to the user together with \gls{csi}.
+	% 	We also notice increasing $b$ boosts the total backscatter rate and the benefit becomes marginal when $b$ is sufficiently large ($2^b \gg \mathrm{card}(\mathcal{L})$).
+	% 	This is because a larger $b$ allows the decision regions to be constructed from narrower energy bins, which mitigates the transformation loss from problem \eqref{op:decision_threshold} to \eqref{op:decision_threshold_discrete}.
+	% 	Therefore, we conclude a proper selection of $b$ is the key to balance backscatter performance and computational complexity.
+	% \end{subsection}
 
 	\begin{subsection}{Rate Region by Different Schemes}
-		\begin{figure}[!t]
+		% \begin{figure}[!t]
+		% 	\centering
+		% 	\subfloat[Input Distribution\label{fi:region_distribution}]{
+		% 		\resizebox{0.65\columnwidth}{!}{
+		% 			\input{assets/simulation/region_distribution.tex}
+		% 		}
+		% 	}
+		% 	\\
+		% 	\subfloat[Active Beamforming\label{fi:region_beamforming}]{
+		% 		\resizebox{0.65\columnwidth}{!}{
+		% 			\input{assets/simulation/region_beamforming.tex}
+		% 		}
+		% 	}
+		% 	\\
+		% 	\subfloat[Decision Threshold\label{fi:region_threshold}]{
+		% 		\resizebox{0.65\columnwidth}{!}{
+		% 			\input{assets/simulation/region_threshold.tex}
+		% 		}
+		% 	}
+		% 	\caption{
+		% 		Average primary-total-backscatter rate regions for different input distribution, active beamforming, and decision threshold schemes.
+		% 		``BSP'' means backscatter symbol period.
+		% 	}
+		% \end{figure}
+		\begin{figure*}[!t]
 			\centering
 			\subfloat[Input Distribution\label{fi:region_distribution}]{
-				\resizebox{0.48\columnwidth}{!}{
+				\resizebox{0.32\textwidth}{!}{
 					\input{assets/simulation/region_distribution.tex}
@@
 			}
-			\\
 			\subfloat[Active Beamforming\label{fi:region_beamforming}]{
-				\resizebox{0.48\columnwidth}{!}{
+				\resizebox{0.32\textwidth}{!}{
 					\input{assets/simulation/region_beamforming.tex}
@@
 			\subfloat[Decision Threshold\label{fi:region_threshold}]{
-				\resizebox{0.48\columnwidth}{!}{
+				\resizebox{0.32\textwidth}{!}{
 					\input{assets/simulation/region_threshold.tex}
@@
 			}
-		\end{figure}
+		\end{figure*}
 		The average achievable primary-total-backscatter rate regions of various input distribution, active beamforming, and decision threshold schemes are explored in this study.
@@
 
-	\begin{subsection}{Rate Region versus Configuration}
+	\begin{subsection}{Rate Region under Different Configurations}
 		\begin{figure}[!t]

### 2022-10-20 main.tex
:pencil: Update abstract

@@
 \newacronym{sdma}{SDMA}{Space-Division Multiple Access}
+\newacronym{nlos}{NLoS}{Non-Line-of-Sight}
+\newacronym{zf}{ZF}{Zero-Forcing}
+\newacronym{mmse}{Minimum Mean-Square-Error}{MMSE}
 
@@
 \maketitle
-
+% TODO why not use metamaterial? because high computational complexity and expectations of freedom (flexibility, reliability)
+% TODO cooperative input design can be used for co-located RIScatter nodes.
+% TODO hardward to modulate using RIS is already available.
+% TODO RIScatter: enhance backscatter signal difference (suppress primary interference) or primary signal strength.
+% TODO For Backscatter community: why not adaptive channel coding? For RIS community: why not add randomness for modulation?
+% TODO RIS involves nonlinear circuits (e.g., diodes) and impedance design (i.e., perfect mismatching) is tricky for continuous phase shift; discrete candidate set is preferred (2-3 bits optimal)
+% TODO Redefine RIS using book
+% TODO Using RIS to encode is not very interesting as controller is anyway usable
+% TODO Wi-Fi sampling rate 20 MHz (symbol period 50 nS), RFID symbol rate/load switching speed 100s KHz to 10s MHz [Backscatter Communications], fast load switching speed is key for high data rate - symbol ratio is not very large
+% TODO Beamforming can cancel direct interference to avoid the collapse of non-coherent energy detection and enlarge energy gap.
+% ?
+[Reconfigurable Intelligent Surface-Assisted Ambient Backscatter Communications Experimental Assessment]the authors of [5] show that, even in line-of-sight (LOS), the interferences and the desired signal can combine in such a way that the received signals at the reader side in the two states are close in power and only differ by their phases
+% TODO Input probability distribution for discrete-value reflection (backscatter), constellation design for continue-value reflection (RIS)
+% * TODO convergence
+% TODO channel coding: general non-adaptive (book) adaptive (DMC)
+% ? [Turbocharging] Since averaging must be done over a significant period of time to smooth out the variation in the TV transmissions, averaging does not allow rates much higher than 10 kbps [24].
+% TODO mu-code: use multiple Rxs for noncoherent direct interference cancellation (instead of receive diversity)
+% TODO backscatter modulation <-> passive beamforming; add adaptive channel coding over (NRZ) line coding.
+% TODO semicoherent: known CSI, unknown primary/backscatter symbols
+% TODO initialization, convergence
+% TODO Base e, use 2 in simulation
+% TODO SR analysis can achieve large rate at the cost of large N; RIScatter can achieve slightly lower rate at the same N, but also preserves primary performance for smaller N
+% TODO tradeoff between primary (RIScatter, no SIC) and backscatter (SR, SIC)
+% !
+SR assume very large N for primary rate analysis.
+However, in such cases SIC is questionable as energy detection over received signal as BBC is already good enough and non-coherent detection can also achieve reasonable performance?
+% TODO when primary symbols are determined, optimal input distribution at high backscatter SNR is equiprobable for any detection (signal/energy)
+% TODO (I(X_1;Y_1),I(X_2;Y_2))
 \begin{abstract}
-	% Scatterers can harvest energy from, modulate information over, and influence propagation of surrounding radio waves.
-	% \gls{bc} varies object impedance to manipulate the magnitude, phase, and/or frequency of scattered signal to encode information and deliver within coverage.
-	% \gls{bc} switches load impedance that manipulates the magnitude, phase, and/or frequency responses to modulate information onto the scattered signal.
-	% \gls{bc} switches load impedance to manipulate the magnitude, phase, and/or frequency responses and modulate information onto the scattered signal.
-	\gls{bc} switches device load impedance to manipulate the magnitude, phase, and/or frequency responses for information modulation on the scattered carrier.
-	% \gls{sr} incorporates scatter nodes into active networks that recycle ambient signal to transmit self information and enhance legacy channel to the cooperative receiver.
-	% \gls{sr} allows the transmission of a primary node using active radio carrying primary information and of a secondary node scattering information onto primary signal, and the reception of information of both nodes.
-	% \gls{sr} introduces a passive scatterer that rides secondary information over the primary signal from an active transmitter, and employs a co-located receiver to sequentially decode both links.
-	% \gls{sr} introduces a passive scatterer to ride secondary information over the primary radio from an active transmitter, and employs a co-located receiver to decode both links.
-	% \gls{sr} introduces a passive scatterer to ride secondary information over the primary radio from an active transmitter and employs a co-located receiver to decode both links.
-	\gls{sr} allows a passive scattering node to ride additional information over the primary radio emitted by an active transmitter, and employs a co-located receiver to decode both sources.
-	% ride secondary information over the primary radio from an active transmitter and employs a co-located receiver to decode both links.
-	% \gls{ris} adapts scattering antennas/programmable metamaterial to control wireless environment by varying signal strength in specific directions.
-	% \gls{ris} programs antenna/metamaterial array that adjusts the scattering phase shifts to control signal strength in specific directions.
-	\gls{ris} programs an antenna/metamaterial array to adjust the scattering phase shifts for signal propagation control in specific directions.
-	% and control signal strength in specific directions.
-	% In this paper, we depart from those concepts and introduce RIScatter as a new paradigm for future wireless networks.
+	% % Scatterers can harvest energy from, modulate information over, and influence propagation of surrounding radio waves.
+	% % \gls{bc} varies object impedance to manipulate the magnitude, phase, and/or frequency of scattered signal to encode information and deliver within coverage.
+	% % \gls{bc} switches load impedance that manipulates the magnitude, phase, and/or frequency responses to modulate information onto the scattered signal.
+	% % \gls{bc} switches load impedance to manipulate the magnitude, phase, and/or frequency responses and modulate information onto the scattered signal.
+	% \gls{bc} switches device load impedance to manipulate the magnitude, phase, and/or frequency responses for information modulation on the scattered carrier.
+	% % \gls{sr} incorporates scatter nodes into active networks that recycle ambient signal to transmit self information and enhance legacy channel to the cooperative receiver.
+	% % \gls{sr} allows the transmission of a primary node using active radio carrying primary information and of a secondary node scattering information onto primary signal, and the reception of information of both nodes.
+	% % \gls{sr} introduces a passive scatterer that rides secondary information over the primary signal from an active transmitter, and employs a co-located receiver to sequentially decode both links.
+	% % \gls{sr} introduces a passive scatterer to ride secondary information over the primary radio from an active transmitter, and employs a co-located receiver to decode both links.
+	% % \gls{sr} introduces a passive scatterer to ride secondary information over the primary radio from an active transmitter and employs a co-located receiver to decode both links.
+	% \gls{sr} allows a passive scattering node to ride additional information over the primary radio emitted by an active transmitter, and employs a co-located receiver to decode both sources.
+	% % ride secondary information over the primary radio from an active transmitter and employs a co-located receiver to decode both links.
+	% % \gls{ris} adapts scattering antennas/programmable metamaterial to control wireless environment by varying signal strength in specific directions.
+	% % \gls{ris} programs antenna/metamaterial array that adjusts the scattering phase shifts to control signal strength in specific directions.
+	% \gls{ris} programs an antenna/metamaterial array to adjust the scattering phase shifts for signal propagation control in specific directions.
+	% % and control signal strength in specific directions.
+	% % In this paper, we depart from those concepts and introduce RIScatter as a new paradigm for future wireless networks.
+	% \gls{bc} devices vary load impedance to modulate and reflect the signals
+	% \gls{bc} nodes rely on dedicated carrier wave to
+	% \gls{bc} nodes manipulate the magnitude, phase, and/or frequency responses to harvest energy from and modulate information over the carrier wave from a nearby emitter.
+	\gls{bc} nodes harvest energy from and modulate information over an external carrier by manipulating the magnitude, phase, and/or frequency of the scattered signal.
+	\gls{sr} incorporates a passive scatterer into existing radio networks to create additional propagation path and ride its own information for the cooperative receiver.
+	\gls{ris} is a programmable reflector array that adapts the phase shift response to enhance or suppress signal strength in specific directions.
 	In this paper, we show how those three seemingly different technologies can be unified to leverage their benefits simultaneously into a single architecture called RIScatter.
-	RIScatter is a new paradigm for future wireless networks and consists of multiple passive scattering nodes, whose reflection states can be adapted to partially engineer the wireless channel and partially modulate information onto the scattered wave.
+	RIScatter is a new paradigm for future wireless networks and consists of multiple dispersed or co-located passive scattering nodes, whose reflection states can be adapted to partially engineer the wireless channel and partially modulate information onto the scattered wave.
 	This contrasts with \gls{bc}/\gls{sr} (resp. \gls{ris}) where states are exclusively a function of information symbols (resp. \gls{csi}).
-	The key principle in RIScatter is to render the probability distribution of reflection states as a joint function of the \gls{csi} and input information source, allowing universal hardware design and heterogeneous traffic control.
+	The key principle in RIScatter is to render the probability distribution of reflection states as a joint function of the \gls{csi} and input information source for heterogeneous traffic control and universal hardware design.
 	% augmented \gls{qos} control.
-	This enables RISscatter to softly bridge, generalize, and outperform \gls{bc}, \gls{sr}, \gls{ris}; boil down to any of those under specific reflection states; or evolve in a mixed setup.
-	We reveal RIScatter provides a fundamental tradeoff that balances information modulation and channel reconfiguration capabilities in a flexible and mutualistic manner.
+	This enables RISscatter to softly bridge, generalize, and outperform \gls{bc}, \gls{sr}, \gls{ris}; boil down to any of those under specific reflection states; or evolve in a mixed form.
+	We show RIScatter provides a fundamental tradeoff that balances information modulation and channel reconfiguration capabilities in a flexible and mutualistic manner.
 	% Instead of treating probability distribution of reflection states as equiprobable (as scattering source of \gls{bc}/\gls{sr}) or degenerate (as reflecting element of \gls{ris}), RIScatter nodes located at different places adapt the input distribution of passive scatterers based on link priority and \gls{csi}, balancing information encoding and channel reconfiguration in a flexible and mutualistic manner.
@@
 	% We consider an application scenario where a multi-antenna \gls{ap} serves a single-antenna user surrounded by multiple RIScatter nodes, and characterize the achievable primary-total-backscatter rate region by designing input distribution at the nodes, active beamforming at the \gls{ap}, and backscatter decision regions at the user.
-	An application scenario is considered where a multi-antenna \gls{ap} serves a single-antenna user surrounded by multiple RIScatter nodes, and the achievable primary-total-backscatter rate region is characterized by optimizing input distribution at the nodes, active beamforming at the \gls{ap}, and backscatter decision regions at the user.
+	% For a typical scenario
+	For a typical setup, we characterize the achievable primary-(total-)backscatter rate region by optimizing input distribution at the nodes, active beamforming at the \gls{ap}, and backscatter detector at the user.
+	% An application scenario is considered where a multi-antenna \gls{ap} serves a single-antenna user surrounded by dispersed RIScatter nodes, and the achievable primary-total-backscatter rate region is characterized by optimizing input distribution at the nodes, active beamforming at the \gls{ap}, and backscatter detector at the user.
 	% Simulation results demonstrate RIScatter nodes can flexibly control the transmit-assist tradeoff via smart input distribution design.
 	% Simulation results demonstrate RIScatter can flexibly control the tradeoff between backscatter modulation and passive beamforming via smart input distribution design, which outperforms \gls{bc}, \gls{sr}, and \gls{ris}.
-	Simulation results demonstrate RIScatter can exploit the additional propagation paths to provide a smooth transition between backscatter modulation and passive beamforming via smart input distribution design, which includes \gls{bc}, \gls{sr}, \gls{ris} as special cases.
+	Simulation results demonstrate RIScatter nodes can exploit the additional propagation paths to smoothly transit between backscatter modulation and passive beamforming via smart input distribution design.
 	% Simulation results demonstrate RIScatter can exploit smart input distribution design to provide a smooth transition between backscatter modulation and passive beamforming, which outperforms \gls{bc}, \gls{sr}, and \gls{ris}.
@@
 		\IEEEPARstart{F}{uture} wireless network is envisioned to provide high throughput, uniform coverage, pervasive connectivity, heterogeneous control, and cognitive intelligence for trillions of portable devices.
-		As an emerging low-power communication technique, \gls{bc} separates conventional transmitter into a \gls{rf} carrier emitter with power-hungry elements (e.g., synthesizer and amplifier) and an information-bearing node with power-efficient components (e.g., harvester and modulator) \cite{Boyer2014}.
-		The node harvests energy from impinging wave and embeds information over scattered signal in a sustainable and controllable manner.
-		% The backscatter reader can be either co-located or separated with the carrier emitter, known as monostatic and bistatic \gls{bc}.
-		The backscatter reader can be either co-located or separated with the carrier emitter, known as \gls{mbc} and \gls{bbc} in Fig. \subref*{fi:mbc} and \subref*{fi:bbc}, respectively.
+		As an emerging low-power communication technique, \gls{bc} divides conventional transmitter into a \gls{rf} carrier emitter with power-hungry elements (e.g., synthesizer and amplifier) and an information-bearing node with power-efficient components (e.g., harvester and modulator) \cite{Boyer2014}.
+		In particular, the node harvests energy from impinging wave and embeds information over scattered signal, while the backscatter reader can be either co-located or separated with the carrier emitter, shown as \gls{mbc} and \gls{bbc} in Fig.
+\subref*{fg:mbc} and \subref*{fg:bbc}, respectively.
 		Its applications such as \gls{rfid} \cite{Dobkin2012,Landt2005} and passive sensor network \cite{Vannucci2008,Assimonis2016} have been extensively researched, standardized, and commercialized to support \gls{iot} and \gls{m2m} networks.
@@
 		% ? With the upsurge of wireless devices and the downtrend of circuit power consumption, \gls{rfid} has experienced great success in \gls{ioe} and \gls{m2m} networks.
-		However, traditional \gls{bc} nodes only respond when externally inquired.
-		In \gls{ambc} \cite{Liu2013b}, interactive nodes recycle ambient signals from legacy transmitters (e.g., radio, television and Wi-Fi) to harvest energy and establish connections.
-		As illustrated in Fig. \subref*{fi:ambc}, it eliminates the need of dedicated power supply, carrier emitter and frequency spectrum, bringing more opportunities to low-power communications.
-		To combat the strong direct-link interference of \gls{ambc}, \cite{Yang2018} proposed a co-located receiver that cooperatively decodes both primary (legacy) and backscatter links.
+		However, conventional \gls{bc} nodes only respond when externally inquired by a nearby reader.
+		To tackle this, \cite{Liu2013b} proposed an \gls{ambc} system where interactive nodes recycle ambient legacy signals (e.g., radio, television and Wi-Fi) to harvest energy and establish connections, as shown in Fig.
+\subref*{fg:ambc}.
+		It eliminates the need of dedicated power supply, carrier emitter and frequency spectrum, but is subject to the strong direct-link interference.
+		In \cite{Yang2018}, the authors proposed a cooperative \gls{ambc} system where both primary (legacy) and backscatter links are decoded at the same user under various detection schemes.
+		% a cooperative receiver decodes both primary (legacy) and backscatter links using \gls{ml}, \gls{mrc}, \gls{zf}, \gls{mmse} and \gls{sic}
+		% co-located cooperative receiver to jointly or sequentially decode both primary (legacy) and backscatter links.
 		% The authors evaluated the error performance of \gls{ml}, linear, and \gls{sic} detectors for flat fading channel, and proposed a low-complexity detector for frequency-selective fading channel.
-		The concept of cooperative \gls{ambc} was further refined as \gls{sr} in Fig. \subref*{fi:sr} that cognitively incorporates \gls{ambc} with existing systems \cite{Liang2020}.
+		The concept of cooperative \gls{ambc} was further refined as \gls{sr} that cognitively incorporates \gls{ambc} with existing systems \cite{Liang2020}, which in shown Fig. \subref*{fg:sr}.
+		% shown in Fig. \subref*{fg:sr}, which cognitively incorporates \gls{ambc} with existing systems \cite{Liang2020}.
 		% In \gls{sr}, the primary transmitter generates active radio carrying primary information, the backscatter node modulates own information onto the scattered wave, and the co-located receiver decodes both links from two propagation paths.
 		% In \gls{sr}, the primary transmitter generates active radio and modulates primary information, the passive node scatters incoming wave and superimposes backscatter information, and the co-located receiver decodes both links from two propagation paths.
-		In \gls{sr}, the primary transmitter generates active radio and modulates primary information, the passive node scatters incoming wave and superimposes backscatter information, while the co-located receiver decodes both links from both propagation paths.
+		% An illustration of \gls{sr} is shown in \subref*{fg:sr}, where the primary transmitter generates active radio and modulates primary information, the passive node scatters incoming wave and superimposes backscatter information, and the co-located receiver decodes both links from both propagation paths.
+		In \gls{sr}, the active transmitter generates \gls{rf} wave carrying primary information, the passive node enhances the propagation environment and superimposes its own message on the scattered signal, and the cooperative receiver jointly or sequentially decodes both links.
 		% The direct transmitter-receiver path only convey
@@
 		% However, it suffers from imperfect synchronization and the near-far problem.
-		On the other hand, \gls{ris} in Fig.
-\subref*{fi:ris} is a promising technology that evolves wireless propagation environment using numerous passive reflecting elements (e.g., scattering antenna or programmable metamaterial) with adjustable amplitudes and/or phases \cite{Wu2021b}.
-		With proper phase shift design, the scattered components can add constructively/destructively with the direct component for signal enhancement/interference suppression.
+		% Above applications treat the scattering node as an information source.
+		On the other hand, \gls{ris} is a smart planar reflector that consists of numerous low-power and low-cost elements with adjustable amplitude and phase responses.
+		The reflection pattern over time is deterministic, which can be optimized and reported to the user before transmission.
+		\gls{ris} recycles and redistributes surrounding \gls{rf} waves to customize wireless propagation environment for signal enhancement, interference suppression, scattering enrichment and non-line-of-sight bypassing \cite{Wu2021b}.
+		% in Fig. \subref*{fg:ris} is a promising technology to recycle
+		% On the other hand, \gls{ris} in Fig.
+\subref*{fg:ris} is a promising technology that evolves wireless propagation environment using numerous passive reflecting elements (e.g., scattering antenna or programmable metamaterial) with adjustable amplitudes and/or phases \cite{Wu2021b}.
+		% With proper phase shift design, the scattered components can add constructively/destructively with the direct component for signal enhancement/interference suppression.
 		% Compared with scattering nodes of \gls{bc}/\gls{sr}, \gls{ris} elements embed no additional information and use deterministic reflection pattern priorly known at the transmitter and receiver.
-		Compared with scattering nodes of \gls{bc}/\gls{sr}, \gls{ris} elements embed no additional information and use fixed reflection pattern over time, which can be optimized and fed back to the transmitter and receiver during coordination phase.
+		% Compared with scattering nodes of \gls{bc}/\gls{sr}, \gls{ris}
+		% elements embed no additional information and use deterministic reflection pattern over time, which can be optimized and fed back to the transmitter and receiver during coordination phase.
+		A comparison of different scattering applications is summarized in Table \ref{tb:scattering_applications}.
 		% , which can be priorly known at the transmitter and receiver.
@@
 				}
-				\label{fi:mbc}
+				\label{fg:mbc}
 			}
@@
 				}
-				\label{fi:bbc}
+				\label{fg:bbc}
 			}
@@
 				}
-				\label{fi:ambc}
+				\label{fg:ambc}
 			}
@@
 				}
-				\label{fi:sr}
+				\label{fg:sr}
 			}
@@
 				}
-				\label{fi:ris}
+				\label{fg:ris}
 			}
@@
 				}
-				\label{fi:riscatter}
+				\label{fg:riscatter}
 			}
@@
 			}
-			\label{fi:scatter_comparison}
+			\label{fg:scatter_comparison}
 		\end{figure}
@@
 		\caption{Comparison of Scattering Applications}
+		\label{tb:scattering_applications}
 		\begin{tabularx}{\textwidth}{CCCCCCC}
@@
 			                              & \gls{mbc}                 & \gls{bbc}                 & \gls{ambc}                                      & \gls{sr}                                     & \gls{ris}                               & RIScatter                                         \\ \midrule
-			Coexisting systems            & 1                         & 1                         & 2 (competitive)                                 & 2 (?ly collaborative)                        & 1                                       & 2 (adaptively collaborative)                      \\ \midrule
+			Coexisting systems            & 1                         & 1                         & 2 (competitive)                                 & 2 (collaborative)                            & 1                                       & 2 (collaborative)                                 \\ \midrule
 			Scatterer contribution        & Backscatter modulation    & Backscatter modulation    & Backscatter modulation and primary interference & Backscatter modulation and primary multipath & Passive beamforming                     & Backscatter modulation and passive beamforming    \\ \midrule
@@
 		Similar to \gls{cr}, the coexistence of primary and backscatter links in \gls{sr} can be classified into commensal, parasitic, and competitive relationships, whose instantaneous rates, power schemes, and outage probabilities were acquired in \cite{Guo2019b,Ding2020}.
-		To evaluate the performance of cooperative \gls{sr} receivers, \cite{Yang2018} derived the bit error rates of \gls{ml}, linear, and \gls{sic} detectors for flat fading channels, then proposed a low-complexity detector for frequency-selective fading channels.
+		To evaluate the performance of cooperative receivers, \cite{Yang2018} derived the bit error rates of \gls{ml}, \gls{mrc}, \gls{zf}, \gls{mmse} and \gls{sic} detectors for flat fading channels, and proposed a low-complexity detector for frequency-selective fading channels.
 		However, it assumed equal symbol period of both links with perfect synchronization, which is impractical due to the load-switching speed constraint.
@@
 
-	% TODO why not use metamaterial? because high computational complexity and expectations of freedom (flexibility, reliability)
-	% TODO cooperative input design can be used for co-located RIScatter nodes.
-	% TODO hardward to modulate using RIS is already available.
-	% TODO RIScatter: enhance backscatter signal difference (suppress primary interference) or primary signal strength.
-	% TODO For Backscatter community: why not adaptive channel coding? For RIS community: why not add randomness for modulation?
-	% TODO RIS involves nonlinear circuits (e.g., diodes) and impedance design (i.e., perfect mismatching) is tricky for continuous phase shift; discrete candidate set is preferred (2-3 bits optimal)
-	% TODO Redefine RIS using book
-	% TODO Using RIS to encode is not very interesting as controller is anyway usable
-	% TODO Wi-Fi sampling rate 20 MHz (symbol period 50 nS), RFID symbol rate/load switching speed 100s KHz to 10s MHz [Backscatter Communications], fast load switching speed is key for high data rate - symbol ratio is not very large
-	% TODO Beamforming can cancel direct interference to avoid the collapse of non-coherent energy detection and enlarge energy gap.
-	% ?
-[Reconfigurable Intelligent Surface-Assisted Ambient Backscatter Communications Experimental Assessment]the authors of [5] show that, even in line-of-sight (LOS), the interferences and the desired signal can combine in such a way that the received signals at the reader side in the two states are close in power and only differ by their phases
-	% TODO Input probability distribution for discrete-value reflection (backscatter), constellation design for continue-value reflection (RIS)
-	% TODO convergence
-	% TODO channel coding: general non-adaptive (book) adaptive (DMC)
-	% ? [Turbocharging] Since averaging must be done over a significant period of time to smooth out the variation in the TV transmissions, averaging does not allow rates much higher than 10 kbps [24].
-	% TODO mu-code: use multiple Rxs for noncoherent direct interference cancellation (instead of receive diversity)
-	% TODO backscatter modulation <-> passive beamforming; add adaptive channel coding over (NRZ) line coding.
-	% TODO semicoherent: known CSI, unknown primary/backscatter symbols
-	% TODO initialization, convergence
-	% TODO Base e, use 2 in simulation
-
 	% To the best of our knowledge, all relevant literatures assumed at backscatter information sources either Gaussian codebook \cite{Guo2019b,Ding2020,Long2020a,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Hu2021b} or finite equiprobable inputs \cite{Yang2018,Liang2020,Han2021,Zhang2022,Liu2019d,Bereyhi2020,Xu2020b,Zhang2021d,Hua2022,Basar2020,Ma2020a,Yuan2021,Hu2021a}.
@@
 		We introduce RIScatter that generalizes \gls{bc}, \gls{sr}, and \gls{ris} to manipulate the transmit-assist tradeoff via smart input distribution and practical receiver design.
-		The paradigm of RIScatter is presented in Fig. \subref*{fi:riscatter}, and the contributions of this paper are summarized as follows.
+		The paradigm of RIScatter is presented in Fig. \subref*{fg:riscatter}, and the contributions of this paper are summarized as follows.
 
@@
 		A natural but critical question is, for a given scatterer with pre-determined reflection pattern set, \emph{can we softly bridge backscatter modulation and passive beamforming by appropriate reflection design?}
-		This question is answered in Section \ref{se:riscatter}.
+		This question is answered in Section \ref{st:riscatter}.
 	\end{subsection}
@@
 				}
-				\label{fi:input_distribution}
+				\label{fg:input_distribution}
 			}
@@
 				}
-				\label{fi:time_block}
+				\label{fg:time_block}
 			}
@@
 			}
-			\label{fi:riscatter_distribution}
+			\label{fg:riscatter_distribution}
 		\end{figure}
 		As illustrated in Fig.
-\ref{fi:riscatter_distribution}, instead of always using fully random or deterministic reflection pattern over time, each RIScatter node can \emph{flexibly adjust} its input distribution to balance information encoding and channel reconfiguration.
+\ref{fg:riscatter_distribution}, instead of always using fully random or deterministic reflection pattern over time, each RIScatter node can \emph{flexibly adjust} its input distribution to balance information encoding and channel reconfiguration.
 		That is, it semi-randomly select the reflection state per backscatter symbol block under the guidance of input probability $P(\Gamma_m)$ for state $m$.
@@
 
-		As shown in Fig. \subref*{fi:block_diagram}, RIScatter nodes can be implemented over readily available passive backscatter devices with energy harvester and information decoder.
-		Its equivalent circuit and scatter model are presented in Fig. \subref*{fi:equivalent_circuit} and \subref*{fi:scatter_model}.
+		As shown in Fig. \subref*{fg:block_diagram}, RIScatter nodes can be implemented over readily available passive backscatter devices with energy harvester and information decoder.
+		Its equivalent circuit and scatter model are presented in Fig. \subref*{fg:equivalent_circuit} and \subref*{fg:scatter_model}.
 		When activated by primary transmitter, each node harvests a proportion of the impinging wave for its own operation, decode the embedded coordination information for input distribution control, then applies a potentially random phase shift on the reradiated signal due to backscatter modulation.
@@
 				}
-				\label{fi:block_diagram}
+				\label{fg:block_diagram}
 			}
@@
 				}
-				\label{fi:equivalent_circuit}
+				\label{fg:equivalent_circuit}
 			}
@@
 				}
-				\label{fi:scatter_model}
+				\label{fg:scatter_model}
 			}
@@
 			}
-			\label{fi:riscatter_node}
+			\label{fg:riscatter_node}
 		\end{figure*}
@@
 			}
-			\label{fi:energy_distribution}
+			\label{fg:energy_distribution}
 		\end{figure}
 		As illustrated in Fig.
-\ref{fi:energy_distribution}, the total received energy per backscatter block is a random variable that follows different distributions conditioned on different input state hypotheses.
+\ref{fg:energy_distribution}, the total received energy per backscatter block is a random variable that follows different distributions conditioned on different input state hypotheses.
 		Compared with conventional joint \gls{ml} and \gls{sic} from stronger primary link to weaker backscatter links, RIScatter receiver not only preserves the benefits of backscatter modulation and passive beamforming, but also enjoys much lower computational and operational complexities.
@@
 			\caption{A single-user multi-node RIScatter system.}
-			\label{fi:riscatter_network}
+			\label{fg:riscatter_network}
 		\end{figure}
-		To demonstrate the advantages of RIScatter, we consider a single-user multi-node \gls{miso} RIScatter system as shown in Fig. \ref{fi:riscatter_network}.
+		To demonstrate the advantages of RIScatter, we consider a single-user multi-node \gls{miso} RIScatter system as shown in Fig. \ref{fg:riscatter_network}.
 		In the primary active point-to-point system, a $Q$-antenna \gls{ap} transmits to a single-antenna user assisted by $K$ nearby single-antenna RIScatter nodes with $M$ reflection states.
@@
 		where $\mathcal{H}_{m_{\mathcal{K}}}$ denotes hypothesis $m_{\mathcal{K}}$.
-		As illustrated in Fig. \ref{fi:energy_distribution}, the RIScatter receiver divides the received energy space into disjoint decision regions associated with those hypotheses.
+		As illustrated in Fig. \ref{fg:energy_distribution}, the RIScatter receiver divides the received energy space into disjoint decision regions associated with those hypotheses.
 		For example, if the total received energy during a backscatter block falls within region $\mathcal{R}_{m_{\mathcal{K}}}$, then the detector output would be $x_{m_{\mathcal{K}}}$.
@@
 		then perform backscatter channel coding on top of it.
-		\label{se:system_model}
+		\label{st:system_model}
 	\end{subsection}
@@
 		where $\rho \in \mathbb{I}$ is the relative priority of the primary link.
-		\label{se:information_theory}
-	\end{subsection}
-	\label{se:riscatter}
+		\label{st:information_theory}
+	\end{subsection}
+	\label{st:riscatter}
 \end{section}
@@
 			\caption{The decision thresholds are selected from fine-grained discrete energy levels instead of continuous space, and each decision region consists of at least one neighbor energy bins.}
-			\label{fi:discrete_outputs}
+			\label{fg:discrete_outputs}
 		\end{figure}
-		As shown in Fig. \ref{fi:discrete_outputs}, by introducing the extra analog-to-digital conversion step, we can group adjacent high-resolution energy bins for backscatter decision regions.
+		As shown in Fig. \ref{fg:discrete_outputs}, by introducing the extra analog-to-digital conversion step, we can group adjacent high-resolution energy bins for backscatter decision regions.
 		Thus, problem \eqref{op:decision_threshold} is recast as
@@
 		To obtain global optimal solution, \cite{He2021} started from the quadrangle inequality and proposed a \gls{dp} method accelerated by the \gls{smawk} algorithm with computational complexity $\mathcal{O}\bigl(L^2(\mathrm{card}(\mathcal{T})-L)\bigr)$, while \cite{Nguyen2020a} started from the optimality condition for three neighbor thresholds and presented a traverse-then-bisect algorithm with complexity $\mathcal{O}\bigl(\mathrm{card}(\mathcal{T})L\log(\mathrm{card}(\mathcal{T})L)\bigr)$.
-		In Section \ref{se:simulation_results}, both schemes will be compared with the \gls{ml} thresholding \cite{Qian2019}
+		In Section \ref{st:simulation_results}, both schemes will be compared with the \gls{ml} thresholding \cite{Qian2019}
 		\begin{equation}
@@
 	In this section, we provide numerical results to evaluate the proposed input distribution, active beamforming, and backscatter decision design for the RIScatter system in Fig.
-\ref{fi:riscatter_network}.
+\ref{fg:riscatter_network}.
 	We assume the AP-user distance is \qty{10}{\meter} and at least one RIScatter nodes are randomly dropped in a disk centered at the user with radius \qty{2}{\meter}.
@@
 				\caption{Convergence behavior of the proposed algorithms for $\rho=0$.}
-				\label{fi:wsr_convergence}
+				\label{fg:wsr_convergence}
 			\end{figure}
@@
 			In Fig.
-\ref{fi:wsr_convergence}, we plot the weighted sum of primary and total backscatter rates at $\rho=0$ for \gls{kkt}, \gls{pgd} (on the first call within \gls{bcd}) and \gls{bcd} algorithms in each iteration.
+\ref{fg:wsr_convergence}, we plot the weighted sum of primary and total backscatter rates at $\rho=0$ for \gls{kkt}, \gls{pgd} (on the first call within \gls{bcd}) and \gls{bcd} algorithms in each iteration.
 			For $K=8$ and $M=2$, Algorithm \ref{al:input_distribution} typically takes around \num{100} fast iterations over closed-form expression \eqref{eq:input_kkt_solution} to converge to the \gls{kkt} input distribution.
@@
 	\begin{subsection}{Comparison of Scattering Applications}
-		% TODO SR analysis can achieve large rate at the cost of large N; RIScatter can achieve slightly lower rate at the same N, but also preserves primary performance for smaller N
-		% TODO tradeoff between primary (RIScatter, no SIC) and backscatter (SR, SIC)
-		% !
-SR assume very large N for primary rate analysis.
-However, in such cases SIC is questionable as energy detection over received signal as BBC is already good enough and non-coherent detection can also achieve reasonable performance?
-		% TODO when primary symbols are determined, optimal input distribution at high backscatter SNR is equiprobable for any detection (signal/energy)
-		% TODO (I(X_1;Y_1),I(X_2;Y_2))
-		% For a fair comparison, we consider the setup in Fig. \ref{fi:riscatter_network} and employ \gls{ml} backscatter energy detection for these scattering applications:
-		% For a fair comparison, we consider the setup in Fig. \ref{fi:riscatter_network} with \gls{ml} backscatter energy detection for these scattering applications (except \gls{sr}):
-		% For a fair comparison with RIScatter, we consider the setup in Fig. \ref{fi:riscatter_network} and evaluate the achievable rate pairs for these scattering applications:
-		% We consider the setup in Fig. \ref{fi:riscatter_network} and compare the achievable rate pairs of RIScatter and these scattering applications:
-		On top of the setup in Fig. \ref{fi:riscatter_network}, we compare the achievable rate pairs of RIScatter and these scattering applications:
+
+		% For a fair comparison, we consider the setup in Fig. \ref{fg:riscatter_network} and employ \gls{ml} backscatter energy detection for these scattering applications:
+		% For a fair comparison, we consider the setup in Fig. \ref{fg:riscatter_network} with \gls{ml} backscatter energy detection for these scattering applications (except \gls{sr}):
+		% For a fair comparison with RIScatter, we consider the setup in Fig. \ref{fg:riscatter_network} and evaluate the achievable rate pairs for these scattering applications:
+		% We consider the setup in Fig. \ref{fg:riscatter_network} and compare the achievable rate pairs of RIScatter and these scattering applications:
+		On top of the setup in Fig. \ref{fg:riscatter_network}, we compare the achievable rate pairs of RIScatter and these scattering applications:
 		\begin{itemize}
@@
 			\caption{Typical achievable rate points of scattering applications for $Q=1$, $K=1$, $M=4$ and $N=1000$.}
-			\label{fi:region_comparison}
+			\label{fg:region_comparison}
 		\end{figure}
 
-		Fig. \ref{fi:region_comparison} presents the typical achieve rate points of different scattering applications for $Q=1$, $K=1$, $M=4$ and $N=1000$.
+		Fig. \ref{fg:region_comparison} presents typical achieve rate points of different scattering applications for $Q=1$, $K=1$, $M=4$ and $N=1000$.
 		First, we observe both \gls{bbc} and \gls{sr} can achieve the highest backscatter rate with coherent detection over the receive energy and intermediate signal, respectively.
@@
 		On the other hand, RIScatter provides a lower backscatter rate than \gls{bbc} and \gls{sr} due to semi-coherent detection, but preserves the primary rate benefit for arbitrary $N$.
-
-		% TODO SR analysis can achieve large rate at the cost of large N; RIScatter can achieve slightly lower rate at the same N, but also preserves primary performance for smaller N
-		% TODO tradeoff between primary (RIScatter, no SIC) and backscatter (SR, SIC)
-		% !
-SR assume very large N for primary rate analysis.
-However, in such cases SIC is questionable as energy detection over received signal as BBC is already good enough and non-coherent detection can also achieve reasonable performance?
-		% TODO when primary symbols are determined, optimal input distribution at high backscatter SNR is equiprobable for any detection (signal/energy)
-		% TODO Wi-Fi sampling rate 20 MHz (symbol period 50 nS), RFID symbol rate/load switching speed 100s KHz to 10s MHz [Backscatter Communications], fast load switching speed is key for high data rate - symbol ratio is not very large
-
-		Backscatter advantage of SR using SIC is prominent for a smaller N
+		% Backscatter advantage of SR using SIC is prominent for a smaller N
 		% correlation by double modulation improves the detection performance
@@
 			\caption{Typical reflection state distribution under different weights for $Q=1$, $K=1$, $M=4$ and $N=20$.}
-			\label{fi:distribution_weights}
+			\label{fg:distribution_weights}
 		\end{figure}
 		The objective of this study is to demonstrate each RIScatter node can adjust its input distribution based on \gls{csi} and link priority to balance backscatter modulation and passive beamforming.
-		For this aim, we evaluate the \gls{kkt} input distribution by Algorithm \ref{al:input_distribution} for a single node under different weights in Fig. \ref{fi:distribution_weights}.
+		For this aim, we evaluate the \gls{kkt} input distribution by Algorithm \ref{al:input_distribution} for a single node under different weights in Fig. \ref{fg:distribution_weights}.
 		We observe that as $\rho$ increases from \num{0} to \num{1}, the \gls{kkt} input distribution
@@
 	% 	\begin{figure}[!t]
-	% 		\subfloat[Primary Rate\label{fi:rate_bits_primary}]{
+	% 		\subfloat[Primary Rate\label{fg:rate_bits_primary}]{
 	% 			\resizebox{0.48\columnwidth}{!}{
@@
 	% 		}
-	% 		\subfloat[Total Backscatter Rate\label{fi:rate_bits_backscatter}]{
+	% 		\subfloat[Total Backscatter Rate\label{fg:rate_bits_backscatter}]{
 	% 			\resizebox{0.48\columnwidth}{!}{
@@
 	% 		\caption{Average achievable primary and total backscatter rates for different energy discretization bits for $\rho=0$.}
-	% 		\label{fi:rate_bits}
+	% 		\label{fg:rate_bits}
 	% 	\end{figure}
 	% 	We now reveal how the analog-to-digital conversion of feasible threshold domain from $\mathbb{R}_+^{L+1}$ to $\mathcal{T}^{L+1}$ affects the average RIScatter performance.
-	% 	For a fixed input distribution and active beamforming, Fig. \ref{fi:rate_bits} shows the impact of energy discretization bits $b$ on the average achievable rates when $\rho=0$.
+	% 	For a fixed input distribution and active beamforming, Fig. \ref{fg:rate_bits} shows the impact of energy discretization bits $b$ on the average achievable rates when $\rho=0$.
 	% 	We observe the primary rate is a constant for different $b$ as expected from Remark \ref{re:backscatter_decision}.
@@
 		% 	\centering
-		% 	\subfloat[Input Distribution\label{fi:region_distribution}]{
+		% 	\subfloat[Input Distribution\label{fg:region_distribution}]{
 		% 		\resizebox{0.65\columnwidth}{!}{
@@
 		% 	\\
-		% 	\subfloat[Active Beamforming\label{fi:region_beamforming}]{
+		% 	\subfloat[Active Beamforming\label{fg:region_beamforming}]{
 		% 		\resizebox{0.65\columnwidth}{!}{
@@
 		% 	\\
-		% 	\subfloat[Decision Threshold\label{fi:region_threshold}]{
+		% 	\subfloat[Decision Threshold\label{fg:region_threshold}]{
 		% 		\resizebox{0.65\columnwidth}{!}{
@@
 			\centering
-			\subfloat[Input Distribution\label{fi:region_distribution}]{
-				\resizebox{0.32\textwidth}{!}{
+			\subfloat[Input Distribution\label{fg:region_distribution}]{
+				\resizebox{0.28\textwidth}{!}{
 					\input{assets/simulation/region_distribution.tex}
@@
 			}
-			\subfloat[Active Beamforming\label{fi:region_beamforming}]{
-				\resizebox{0.32\textwidth}{!}{
+			\subfloat[Active Beamforming\label{fg:region_beamforming}]{
+				\resizebox{0.28\textwidth}{!}{
 					\input{assets/simulation/region_beamforming.tex}
@@
 			}
-			\subfloat[Decision Threshold\label{fi:region_threshold}]{
-				\resizebox{0.32\textwidth}{!}{
+			\subfloat[Decision Threshold\label{fg:region_threshold}]{
+				\resizebox{0.28\textwidth}{!}{
 					\input{assets/simulation/region_threshold.tex}
@@
 
-			Fig. \subref*{fi:region_distribution} shows the achievable rate regions for those input distribution schemes.
+			Fig. \subref*{fg:region_distribution} shows the achievable rate regions for those input distribution schemes.
 			We observe that \emph{Cooperation} provides the outer bound for all achievable rate regions, which suggests transmit cooperation between RIScatter nodes can be generally helpful.
@@
 
-			Fig. \subref*{fi:region_beamforming} plots the achievable rate regions for those active beamforming schemes.
+			Fig. \subref*{fg:region_beamforming} plots the achievable rate regions for those active beamforming schemes.
 			In the low-$\rho$ regime, we observe the proposed \emph{\gls{pgd}} design by Algorithm \ref{al:active_beamforming} outperforms \emph{E-\gls{mrt}} and \emph{D-\gls{mrt}} in terms of backscatter rate.
@@
 
-			Fig. \subref*{fi:region_threshold} presents the achievable rate region for those decision threshold schemes.
+			Fig. \subref*{fg:region_threshold} presents the achievable rate region for those decision threshold schemes.
 			We observe that the distribution-adaptive schemes \emph{\gls{dp}}, \emph{\gls{smawk}} and \emph{Bisection} achieve higher total backscatter rate than the non-adaptive \emph{\gls{ml}}.
@@
 			\centering
-			\subfloat[RIScatter Nodes\label{fi:region_tags}]{
+			\subfloat[RIScatter Nodes\label{fg:region_tags}]{
 				\resizebox{0.48\columnwidth}{!}{
@@
 			}
-			\subfloat[Input States\label{fi:region_states}]{
+			\subfloat[Input States\label{fg:region_states}]{
 				\resizebox{0.48\columnwidth}{!}{
@@
 			\\
-			\subfloat[Transmit Antennas\label{fi:region_txs}]{
+			\subfloat[Transmit Antennas\label{fg:region_txs}]{
 				\resizebox{0.48\columnwidth}{!}{
@@
 			}
-			\subfloat[Symbol Period Ratio\label{fi:region_duration}]{
+			\subfloat[Symbol Period Ratio\label{fg:region_duration}]{
 				\resizebox{0.48\columnwidth}{!}{
@@
 			\\
-			\subfloat[Average Noise Power\label{fi:region_noise}]{
+			\subfloat[Average Noise Power\label{fg:region_noise}]{
 				\resizebox{0.48\columnwidth}{!}{
@@
 			}
-			\subfloat[Disk Radius\label{fi:region_coverage}]{
+			\subfloat[Disk Radius\label{fg:region_coverage}]{
 				\resizebox{0.48\columnwidth}{!}{
@@
 			}
-			\label{fi:region_config}
+			\label{fg:region_config}
 		\end{figure}
@@
 		\begin{subsubsection}{Number of Nodes}
-			Fig. \subref*{fi:region_tags} reveals how the number of two-state RIScatter nodes $K$ influence the primary-backscatter tradeoff.
+			Fig. \subref*{fg:region_tags} reveals how the number of two-state RIScatter nodes $K$ influence the primary-backscatter tradeoff.
 			We observe the total backscatter rate roughly scales proportionally with the number of nodes, and the decrease of individual rate is unobvious.
@@
 		\begin{subsubsection}{Number of States}
-			Fig. \subref*{fi:region_states} shows the relationship between available reflection states (i.e., \gls{qam} order) $M$ and achievable rate regions.
+			Fig. \subref*{fg:region_states} shows the relationship between available reflection states (i.e., \gls{qam} order) $M$ and achievable rate regions.
 			We notice increasing the reflection states has a marginal effect on both primary and total backscatter rates.
@@
 		\begin{subsubsection}{Number of Transmit Antennas}
-			Fig. \subref*{fi:region_txs} illustrates the impact of transmit antennas $Q$ on the average performance.
+			Fig. \subref*{fg:region_txs} illustrates the impact of transmit antennas $Q$ on the average performance.
 			We observe larger $Q$ produces greater achievable rate regions.
@@
 		\begin{subsubsection}{Symbol Period Ratio}
-			Fig. \subref*{fi:region_duration} presents how symbol period ratio $N$ affects the achievable rate region.
+			Fig. \subref*{fg:region_duration} presents how symbol period ratio $N$ affects the achievable rate region.
 			We notice using a small $N$ can effectively boost the total backscatter rate per primary symbol, and the conventional \gls{sr} literatures assuming sufficiently large $N$ is generally inefficient.
@@
 		\begin{subsubsection}{Average Noise Power}
-			Fig. \subref*{fi:region_noise} depicts the impact of average noise power $\sigma_v^2$ on average rate regions.
+			Fig. \subref*{fg:region_noise} depicts the impact of average noise power $\sigma_v^2$ on average rate regions.
 			Despite the proposed low-complexity energy detection is suitable for a wide range of noise levels, there exists a backscatter performance upper bound due to its semi-coherent property.
@@
 		\begin{subsubsection}{Coverage Disk Radius}
-			Fig. \subref*{fi:region_coverage} shows the relationship between RIScatter cover disk radius and achievable rate regions.
+			Fig. \subref*{fg:region_coverage} shows the relationship between RIScatter cover disk radius and achievable rate regions.
 			We observe both primary and backscatter performance are enhanced when nodes are dropped closer to the user.
@@
 	% ? Channel estimation error, coordination issues
-	\label{se:simulation_results}
+	\label{st:simulation_results}
 \end{section}

### 2022-10-20 main.tex
:pencil: Update fundamentals

@@
 % TODO Wi-Fi sampling rate 20 MHz (symbol period 50 nS), RFID symbol rate/load switching speed 100s KHz to 10s MHz [Backscatter Communications], fast load switching speed is key for high data rate - symbol ratio is not very large
-% TODO Beamforming can cancel direct interference to avoid the collapse of non-coherent energy detection and enlarge energy gap.
+% TODO Beamforming can cancel direct interference to avoid the collapse of noncoherent energy detection and enlarge energy gap.
 % ?
@@
 SR assume very large N for primary rate analysis.
-However, in such cases SIC is questionable as energy detection over received signal as BBC is already good enough and non-coherent detection can also achieve reasonable performance?
+However, in such cases SIC is questionable as energy detection over received signal as BBC is already good enough and noncoherent detection can also achieve reasonable performance?
 % TODO when primary symbols are determined, optimal input distribution at high backscatter SNR is equiprobable for any detection (signal/energy)
@@
 		% For sequential decoding from primary to backscatter, \cite{Long2020a} pointed out the randomness from backscatter modulation can be modelled as either interference or channel uncertainty, depending on the symbol period ratio.
-		% The authors concluded if this ratio is sufficiently large, the non-coherent primary achievable rate would asymptotically approach its coherent counterpart.
+		% The authors concluded if this ratio is sufficiently large, the noncoherent primary achievable rate would asymptotically approach its coherent counterpart.
 		% This motivated \cite{Long2020a,Liang2020,Guo2019b,Ding2020,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Yang2018,Han2021,Zhang2022} to first decode the primary link, perform \gls{sic}, then decode the backscatter link.
-		% However, the advantage of \gls{sic} is questionable because 1) sufficiently large symbol period ratio is assumed in primary rate analysis and constraints backscatter rate; 2) backscatter pattern and signal characteristics are not fully exploited; 3) non-coherent primary encoding is required at the transmitter, while re-encoding, precoding, and subtraction are required at the receiver; 4) primary and backscatter symbols are superimposed by multiplication instead of superposition.
+		% However, the advantage of \gls{sic} is questionable because 1) sufficiently large symbol period ratio is assumed in primary rate analysis and constraints backscatter rate; 2) backscatter pattern and signal characteristics are not fully exploited; 3) noncoherent primary encoding is required at the transmitter, while re-encoding, precoding, and subtraction are required at the receiver; 4) primary and backscatter symbols are superimposed by multiplication instead of superposition.
 		% Another open issue for \gls{sr} is backscatter multiple access.
@@
 		Similar to \gls{cr}, the coexistence of primary and backscatter links in \gls{sr} can be classified into commensal, parasitic, and competitive relationships, whose instantaneous rates, power schemes, and outage probabilities were acquired in \cite{Guo2019b,Ding2020}.
-		To evaluate the performance of cooperative receivers, \cite{Yang2018} derived the bit error rates of \gls{ml}, \gls{mrc}, \gls{zf}, \gls{mmse} and \gls{sic} detectors for flat fading channels, and proposed a low-complexity detector for frequency-selective fading channels.
-		However, it assumed equal symbol period of both links with perfect synchronization, which is impractical due to the load-switching speed constraint.
-		Although joint \gls{ml} decoding achieves the optimal detection performance for arbitrary backscatter-over-primary symbol period ratio, the computational complexity is prohibitive especially for high-order constellations \cite{Yang2018,Liang2020,Zhang2022}.
-		For sequential primary-backscatter decoding, the randomness of backscatter modulation can be modelled as either interference or channel uncertainty, depending on the symbol period ratio \cite{Long2020a}.
-		If this ratio is sufficiently large, the authors proved the non-coherent primary achievable rate would approach its coherent counterpart asymptotically.
-		This motivated \cite{Long2020a,Liang2020,Guo2019b,Ding2020,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Yang2018,Han2021,Zhang2022} to perform \gls{sic} from primary to backscatter links.
-		However, the advantages of such \gls{sic} remain questionable as
+		% To evaluate the performance of cooperative receivers, \cite{Yang2018} derived the bit error rates of \gls{ml}, \gls{mrc}, \gls{zf}, \gls{mmse} and \gls{sic} detectors for flat fading channels, and proposed a low-complexity detector for frequency-selective fading channels.
+		To evaluate the performance of cooperative receivers, \cite{Yang2018} derived the bit error rates of \gls{ml} and \gls{sic} detectors for flat fading channels, and proposed a low-complexity detector for frequency-selective fading channels.
+		% However, it assumed equal symbol period of both links with perfect synchronization, which is impractical due to the load-switching speed constraint.
+		% However, it assumed the primary and backscatter symbol periods are equal and
+		% However, it only considered the case where primary and backscatter symbols have the same period.
+		However, it only considered the case where the primary and backscatter symbols of the same period are perfectly aligned in time.
+		Joint \gls{ml} decoding can achieve the best error performance in general, but its computational complexity is prohibitive especially for nodes with high-order constellation \cite{Yang2018,Liang2020,Zhang2022}.
+		One special property of \gls{sr} is the backscatter signal strength is significantly weaker than primary due to the double fading effect.
+		It motivated \cite{Long2020a,Liang2020,Guo2019b,Ding2020,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Yang2018,Han2021,Zhang2022} to view \gls{sr} as a multiplicative \gls{noma} and perform sequential primary-backscatter decoding with \gls{sic}.
+		During primary decoding, the randomness from backscatter modulation can be modelled as either interference or channel uncertainty, depending on the relationship between primary sampling rate and backscatter switching speed.
+		If the former is much higher, then the average primary achievable rate under noncoherent detection would approach its coherent counterpart asymptotically \cite{Long2020a}, and both links may be decoded in an interference-free manner.
+		% For sequential primary-backscatter decoding, the randomness of backscatter modulation can be modelled as either interference or channel uncertainty, depending on the symbol period ratio \cite{Long2020a}.
+		% If this ratio is sufficiently large, the authors proved the noncoherent primary achievable rate would approach its coherent counterpart asymptotically.
+		% This motivated \cite{Long2020a,Liang2020,Guo2019b,Ding2020,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Yang2018,Han2021,Zhang2022} to perform \gls{sic} from primary to backscatter links.
+		However, the disadvantage of such \gls{sic} includes:
 		1) primary rate analysis is backed by long backscatter symbol period that constrains backscatter rate;
 		2) reflection pattern and signal characteristics are not fully exploited;
-		3) non-coherent primary encoding is required at the transmitter while re-encoding, precoding and subtraction are required at the receiver;
+		3) noncoherent primary encoding is required at the transmitter while re-encoding, precoding and subtraction are required at the receiver;
 		4) primary and backscatter symbols are superimposed by multiplication instead of superposition.

### 2022-10-21 main.tex
:pencil: Updating related works

@@
 	\gls{bc} nodes harvest energy from and modulate information over an external carrier by manipulating the magnitude, phase, and/or frequency of the scattered signal.
-	\gls{sr} incorporates a passive scatterer into existing radio networks to create additional propagation path and ride its own information for the cooperative receiver.
+	\gls{sr} incorporates a passive scatter node into existing radio networks to create additional propagation path and ride its own information towards the cooperative receiver.
 	\gls{ris} is a programmable reflector array that adapts the phase shift response to enhance or suppress signal strength in specific directions.
@@
 	This contrasts with \gls{bc}/\gls{sr} (resp. \gls{ris}) where states are exclusively a function of information symbols (resp. \gls{csi}).
-	The key principle in RIScatter is to render the probability distribution of reflection states as a joint function of the \gls{csi} and input information source for heterogeneous traffic control and universal hardware design.
+	The key principle in RIScatter is to render the probability distribution of reflection states as a joint function of the \gls{csi} and input information source.
 	% augmented \gls{qos} control.
-	This enables RISscatter to softly bridge, generalize, and outperform \gls{bc}, \gls{sr}, \gls{ris}; boil down to any of those under specific reflection states; or evolve in a mixed form.
-	We show RIScatter provides a fundamental tradeoff that balances information modulation and channel reconfiguration capabilities in a flexible and mutualistic manner.
+	This enables RISscatter to softly bridge, generalize, and outperform \gls{bc}, \gls{sr}, \gls{ris}; boil down to any of those under specific reflection states; or evolve in a mixed form for universal hardware design and heterogeneous traffic control.
+	% ? We show RIScatter provides a fundamental tradeoff that balances information modulation and channel reconfiguration capabilities in a flexible and mutualistic manner.
 	% Instead of treating probability distribution of reflection states as equiprobable (as scattering source of \gls{bc}/\gls{sr}) or degenerate (as reflecting element of \gls{ris}), RIScatter nodes located at different places adapt the input distribution of passive scatterers based on link priority and \gls{csi}, balancing information encoding and channel reconfiguration in a flexible and mutualistic manner.
@@
 	% We consider an application scenario where a multi-antenna \gls{ap} serves a single-antenna user surrounded by multiple RIScatter nodes, and characterize the achievable primary-total-backscatter rate region by designing input distribution at the nodes, active beamforming at the \gls{ap}, and backscatter decision regions at the user.
-	% For a typical scenario
 	For a typical setup, we characterize the achievable primary-(total-)backscatter rate region by optimizing input distribution at the nodes, active beamforming at the \gls{ap}, and backscatter detector at the user.
@@
 	% Simulation results demonstrate RIScatter can flexibly control the tradeoff between backscatter modulation and passive beamforming via smart input distribution design, which outperforms \gls{bc}, \gls{sr}, and \gls{ris}.
-	Simulation results demonstrate RIScatter nodes can exploit the additional propagation paths to smoothly transit between backscatter modulation and passive beamforming via smart input distribution design.
+	Simulation results demonstrate RIScatter nodes can exploit the additional propagation paths to smoothly transition between backscatter modulation and passive beamforming via smart input distribution design,
 	% Simulation results demonstrate RIScatter can exploit smart input distribution design to provide a smooth transition between backscatter modulation and passive beamforming, which outperforms \gls{bc}, \gls{sr}, and \gls{ris}.
+	and the proposed practical receiver effectively accommodates the double modulation and signal characteristics in scatter-based cooperative networks.
+	% with low complexity.
 \end{abstract}
@@
 		\IEEEPARstart{F}{uture} wireless network is envisioned to provide high throughput, uniform coverage, pervasive connectivity, heterogeneous control, and cognitive intelligence for trillions of portable devices.
-		As an emerging low-power communication technique, \gls{bc} divides conventional transmitter into a \gls{rf} carrier emitter with power-hungry elements (e.g., synthesizer and amplifier) and an information-bearing node with power-efficient components (e.g., harvester and modulator) \cite{Boyer2014}.
+		As a mature low-power communication technique, \gls{bc} separates conventional transmitter into a \gls{rf} carrier emitter with power-hungry elements (e.g., synthesizer and amplifier) and an information-bearing node with power-efficient components (e.g., harvester and modulator) \cite{Boyer2014}.
 		In particular, the node harvests energy from impinging wave and embeds information over scattered signal, while the backscatter reader can be either co-located or separated with the carrier emitter, shown as \gls{mbc} and \gls{bbc} in Fig.
@@
 		However, conventional \gls{bc} nodes only respond when externally inquired by a nearby reader.
-		To tackle this, \cite{Liu2013b} proposed an \gls{ambc} system where interactive nodes recycle ambient legacy signals (e.g., radio, television and Wi-Fi) to harvest energy and establish connections, as shown in Fig.
+		To tackle this, \cite{Liu2013b} proposed an \gls{ambc} system where interactive nodes recycle ambient legacy signals (e.g., radio, television and Wi-Fi) to harvest energy and establish connections, and the idea is shown in Fig.
 \subref*{fg:ambc}.
@@
 		% The authors evaluated the error performance of \gls{ml}, linear, and \gls{sic} detectors for flat fading channel, and proposed a low-complexity detector for frequency-selective fading channel.
-		The concept of cooperative \gls{ambc} was further refined as \gls{sr} that cognitively incorporates \gls{ambc} with existing systems \cite{Liang2020}, which in shown Fig. \subref*{fg:sr}.
+		The concept of cooperative \gls{ambc} was further refined as \gls{sr} that cognitively incorporates \gls{ambc} with existing systems \cite{Liang2020}, as shown in Fig. \subref*{fg:sr}.
 		% shown in Fig. \subref*{fg:sr}, which cognitively incorporates \gls{ambc} with existing systems \cite{Liang2020}.
@@
 		% An illustration of \gls{sr} is shown in \subref*{fg:sr}, where the primary transmitter generates active radio and modulates primary information, the passive node scatters incoming wave and superimposes backscatter information, and the co-located receiver decodes both links from both propagation paths.
-		In \gls{sr}, the active transmitter generates \gls{rf} wave carrying primary information, the passive node enhances the propagation environment and superimposes its own message on the scattered signal, and the cooperative receiver jointly or sequentially decodes both links.
+		In \gls{sr}, the active transmitter generates \gls{rf} wave carrying primary information, the passive node enhances the radio propagation and superimposes its own message on the scattered signal, and the cooperative receiver jointly or sequentially decodes both links.
 		% The direct transmitter-receiver path only convey
@@
 		On the other hand, \gls{ris} is a smart planar reflector that consists of numerous low-power and low-cost elements with adjustable amplitude and phase responses.
-		The reflection pattern over time is deterministic, which can be optimized and reported to the user before transmission.
+		The reflection pattern is deterministic over time, which can be optimized and reported to the user before the transmission.
 		\gls{ris} recycles and redistributes surrounding \gls{rf} waves to customize wireless propagation environment for signal enhancement, interference suppression, scattering enrichment and non-line-of-sight bypassing \cite{Wu2021b}.
@@
 			Scatterer contribution        & Backscatter modulation    & Backscatter modulation    & Backscatter modulation and primary interference & Backscatter modulation and primary multipath & Passive beamforming                        & Backscatter modulation and passive beamforming    \\ \midrule
-			Cooperative transmission      & ---                       & ---                       & No                                              & Active beamforming                           & ---                                     & Active beamforming and smart reflection           \\ \midrule
+			Cooperative transmissions     & ---                       & ---                       & No (individual transmitters)                    & Active beamforming                           & ---                                        & Active beamforming and smart reflection           \\ \midrule
 			Cooperative reception         & ---                       & ---                       & No (separated receivers)                        & Joint detection or \gls{sic}                 & ---                                        & Backscatter detection as primary channel training \\ \midrule
@@
 			Reflection state distribution & Equiprobable (line-coded) & Equiprobable (line-coded) & Equiprobable (line-coded)                       & Equiprobable or Gaussian                     & Degenerate (\gls{csi}-adaptive)            & Flexible (\gls{csi}- and link priority-adaptive)  \\ \midrule
-			Load-switching frequency      & Fast or slow              & Fast or slow              & Fast or slow                                    & Slow                                         & Slow (dynamic) or very slow (blockwise) & Fast or slow                                      \\ \bottomrule
+			Load-switching frequency      & Fast or slow              & Fast or slow              & Fast or slow                                    & Slow                                         & Slow (dynamic) or quasi-static (blockwise) & Fast or slow                                      \\ \bottomrule
 		\end{tabularx}
@@
 		However, it only considered the case where the primary and backscatter symbols of the same period are perfectly aligned in time.
-		Joint \gls{ml} decoding can achieve the best error performance in general, but its computational complexity is prohibitive especially for nodes with high-order constellation \cite{Yang2018,Liang2020,Zhang2022}.
-		One special property of \gls{sr} is the backscatter signal strength is significantly weaker than primary due to the double fading effect.
-		It motivated \cite{Long2020a,Liang2020,Guo2019b,Ding2020,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Yang2018,Han2021,Zhang2022} to view \gls{sr} as a multiplicative \gls{noma} and perform sequential primary-backscatter decoding with \gls{sic}.
-		During primary decoding, the randomness from backscatter modulation can be modelled as either interference or channel uncertainty, depending on the relationship between primary sampling rate and backscatter switching speed.
-		If the former is much higher, then the average primary achievable rate under noncoherent detection would approach its coherent counterpart asymptotically \cite{Long2020a}, and both links may be decoded in an interference-free manner.
+		Joint \gls{ml} decoding achieves the best error performance in general, but its computational complexity can be prohibitive especially for sources with high-order constellation \cite{Yang2018,Liang2020,Zhang2022}.
+		One special property of scatter-based cooperative networks is the backscatter signal strength is significantly weaker than primary due to the double fading effect.
+		It motivated \cite{Long2020a,Liang2020,Guo2019b,Ding2020,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Yang2018,Han2021,Zhang2022} to view \gls{sr} as a multiplicative \gls{noma} and perform sequential \gls{sic}-based primary-backscatter decoding.
+		During primary decoding, the randomness from backscatter modulation can be modelled as either interference or channel uncertainty, depending on the relationship between the primary sampling rate and backscatter switching speed.
+		% During primary decoding, the randomness from backscatter modulation can be modelled as either interference or channel uncertainty, depending on the relationship between backscatter switching speed and primary sampling rate.
+		% If the backscatter-over-primary symbol period ratio $N$ is sufficiently large (i.e., commensal \gls{sr}), then the average primary achievable rate under noncoherent detection would asymptotically approach its coherent counterpart \cite{Long2020a}, and both links may be decoded in an interference-free manner.
+		If the former is much higher (i.e., commensal \gls{sr}), then the average primary achievable rate under noncoherent detection would asymptotically approach its coherent counterpart \cite{Long2020a}, and both links may be decoded in an interference-free manner.
 		% For sequential primary-backscatter decoding, the randomness of backscatter modulation can be modelled as either interference or channel uncertainty, depending on the symbol period ratio \cite{Long2020a}.
@@
 		% This motivated \cite{Long2020a,Liang2020,Guo2019b,Ding2020,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Yang2018,Han2021,Zhang2022} to perform \gls{sic} from primary to backscatter links.
-		However, the disadvantage of such \gls{sic} includes:
-		1) primary rate analysis is backed by long backscatter symbol period that constrains backscatter rate;
+		% However, the disadvantage of \gls{sic}-based sequential detection includes:
+		% 1) the achievable primary and backscatter rate analysis for commensal \gls{sr} only holds for a sufficiently large $N$;
+		% 1) the asymptotic rate analysis for commensal \gls{sr} is inapplicable when primary and backscatter symbol periods are comparable; \footnote{For example, Wi-Fi sampling rate is \qty{20}{\MHz} while \gls{rfid} load switching speed varies between \num{100}s of \unit{\kHz} to \num{10}s of \unit{\MHz} \cite{Torres2021}, corresponding to a typical symbol period ratio between \num{1} and \num{100}.}
+		% ! However, the disadvantage of \gls{sic}-based sequential detection includes:
+		% 1) the asymptotic rate analysis for commensal \gls{sr} is inapplicable when symbol periods are comparable \footnote{For example, Wi-Fi sampling rate is \qty{20}{\MHz} while \gls{rfid} load switching speed varies between \num{100}s of \unit{\kHz} to \num{10}s of \unit{\MHz} \cite{Torres2021}, corresponding to a typical symbol period ratio between \num{1} and \num{100}.};
+		% 2) using a large symbol period ratio not only reduces backscatter throughput, but also requires \gls{sic} over every primary block
+		However, it requires \gls{sic} over all primary symbol blocks followed by a time-domain \gls{mrc}, which is
+		% computationally expensive
+		operation-intensive and \gls{csi}-sensitive.
+		Besides, the assumption of very large backscatter-over-primary symbol period ratio not always hold in modern wireless systems \footnote{For example, Wi-Fi sampling rate is \qty{20}{\MHz} while \gls{rfid} load switching speed varies between \num{100}s of \unit{\kHz} to \num{10}s of \unit{\MHz} \cite{Torres2021}, corresponding to a typical symbol period ratio between \num{1} and \num{100}.}.
+
+		% the assumption of long backscatter symbol constrains the backscatter data rate\footnote{For example, Wi-Fi sampling rate is \qty{20}{\MHz} while \gls{rfid} load switching speed varies between \num{100}s of \unit{\kHz} to \num{10}s of \unit{\MHz} \cite{Torres2021}, corresponding to a typical (backscatter-over-primary) symbol period ratio between \num{1} and \num{100}.}
+
+		% First, we observe both \gls{bbc} and \gls{sr} can achieve the highest backscatter rate with coherent detection over the receive energy and intermediate signal, respectively.
+		% This is because repetition coding with \gls{mrc} over $N$ primary blocks effectively increases the backscatter \gls{snr} by $N$ times, and the information loss due to the signal-to-energy conversion on top may be insignificant.
+		% However, the asymptotic primary and backscatter rate analysis only provides upper bounds for \gls{sr}.
+		% Using a very large $N$ not only reduces the system throughput\footnote{For example, Wi-Fi sampling rate is \qty{20}{\MHz} while \gls{rfid} load switching speed varies between \num{100}s of \unit{\kHz} to \num{10}s of \unit{\MHz} \cite{Torres2021}, corresponding to a typical symbol period ratio $N$ between \num{1} and \num{100}.} but also requires the operation-intensive \gls{sic} over each primary block.
+		% When the duration of primary and backscatter symbol are comparable, the randomly scattered signals should be modelled as interference to primary link rather than quasi-static multipath components, and the achievable rate point of \gls{sr} will move towards the origin.
+
+		primary rate analysis is backed by long backscatter symbol period that constrains backscatter rate;
 		2) reflection pattern and signal characteristics are not fully exploited;

### 2022-10-22 main.tex
:pencil: Update related works

--- 2022-10-20 main.tex
@@
 \title{RIScatter: Unifying\\Backscatter Communications, Symbiotic Radio, and Reconfigurable Intelligent Surface}
-% \title{RIScatter: Unifying Backcatter Modulation and Passive Beamforming by Adaptive Input Distribution}
 \author{
@@
 % TODO cooperative input design can be used for co-located RIScatter nodes.
-% TODO hardward to modulate using RIS is already available.
+% * hardward to modulate using RIS is already available.
 % TODO RIScatter: enhance backscatter signal difference (suppress primary interference) or primary signal strength.
-% TODO For Backscatter community: why not adaptive channel coding? For RIS community: why not add randomness for modulation?
+% ? For Backscatter community: why not adaptive channel coding? For RIS community: why not add randomness for modulation?
 % TODO RIS involves nonlinear circuits (e.g., diodes) and impedance design (i.e., perfect mismatching) is tricky for continuous phase shift; discrete candidate set is preferred (2-3 bits optimal)
-% TODO Redefine RIS using book
-% TODO Using RIS to encode is not very interesting as controller is anyway usable
-% TODO Wi-Fi sampling rate 20 MHz (symbol period 50 nS), RFID symbol rate/load switching speed 100s KHz to 10s MHz [Backscatter Communications], fast load switching speed is key for high data rate - symbol ratio is not very large
+% * Redefine RIS using book
+% ? Using RIS to encode is not very interesting as controller is anyway usable
+% * Wi-Fi sampling rate 20 MHz (symbol period 50 nS), RFID symbol rate/load switching speed 100s KHz to 10s MHz [Backscatter Communications], fast load switching speed is key for high data rate - symbol ratio is not very large
 % TODO Beamforming can cancel direct interference to avoid the collapse of noncoherent energy detection and enlarge energy gap.
@@
 % TODO Input probability distribution for discrete-value reflection (backscatter), constellation design for continue-value reflection (RIS)
-% * TODO convergence
 % TODO channel coding: general non-adaptive (book) adaptive (DMC)
@@
 % TODO semicoherent: known CSI, unknown primary/backscatter symbols
-% TODO initialization, convergence
-% TODO Base e, use 2 in simulation
+% * initialization, convergence
+% * Base e, use 2 in simulation
 % TODO SR analysis can achieve large rate at the cost of large N; RIScatter can achieve slightly lower rate at the same N, but also preserves primary performance for smaller N
@@
 % TODO when primary symbols are determined, optimal input distribution at high backscatter SNR is equiprobable for any detection (signal/energy)
-% TODO (I(X_1;Y_1),I(X_2;Y_2))
+% * (I(X_1;Y_1),I(X_2;Y_2))
 \begin{abstract}
-	% % Scatterers can harvest energy from, modulate information over, and influence propagation of surrounding radio waves.
-	% % \gls{bc} varies object impedance to manipulate the magnitude, phase, and/or frequency of scattered signal to encode information and deliver within coverage.
-	% % \gls{bc} switches load impedance that manipulates the magnitude, phase, and/or frequency responses to modulate information onto the scattered signal.
-	% % \gls{bc} switches load impedance to manipulate the magnitude, phase, and/or frequency responses and modulate information onto the scattered signal.
-	% \gls{bc} switches device load impedance to manipulate the magnitude, phase, and/or frequency responses for information modulation on the scattered carrier.
-	% % \gls{sr} incorporates scatter nodes into active networks that recycle ambient signal to transmit self information and enhance legacy channel to the cooperative receiver.
-	% % \gls{sr} allows the transmission of a primary node using active radio carrying primary information and of a secondary node scattering information onto primary signal, and the reception of information of both nodes.
-	% % \gls{sr} introduces a passive scatterer that rides secondary information over the primary signal from an active transmitter, and employs a co-located receiver to sequentially decode both links.
-	% % \gls{sr} introduces a passive scatterer to ride secondary information over the primary radio from an active transmitter, and employs a co-located receiver to decode both links.
-	% % \gls{sr} introduces a passive scatterer to ride secondary information over the primary radio from an active transmitter and employs a co-located receiver to decode both links.
-	% \gls{sr} allows a passive scattering node to ride additional information over the primary radio emitted by an active transmitter, and employs a co-located receiver to decode both sources.
-	% % ride secondary information over the primary radio from an active transmitter and employs a co-located receiver to decode both links.
-	% % \gls{ris} adapts scattering antennas/programmable metamaterial to control wireless environment by varying signal strength in specific directions.
-	% % \gls{ris} programs antenna/metamaterial array that adjusts the scattering phase shifts to control signal strength in specific directions.
-	% \gls{ris} programs an antenna/metamaterial array to adjust the scattering phase shifts for signal propagation control in specific directions.
-	% % and control signal strength in specific directions.
-	% % In this paper, we depart from those concepts and introduce RIScatter as a new paradigm for future wireless networks.
-	% \gls{bc} devices vary load impedance to modulate and reflect the signals
-	% \gls{bc} nodes rely on dedicated carrier wave to
-	% \gls{bc} nodes manipulate the magnitude, phase, and/or frequency responses to harvest energy from and modulate information over the carrier wave from a nearby emitter.
 	\gls{bc} nodes harvest energy from and modulate information over an external carrier by manipulating the magnitude, phase, and/or frequency of the scattered signal.
-	\gls{sr} incorporates a passive scatterer into existing radio networks to create additional propagation path and ride its own information for the cooperative receiver.
+	\gls{sr} incorporates a passive scatter node into existing radio networks to create additional propagation path and ride its own information towards the cooperative receiver.
 	\gls{ris} is a programmable reflector array that adapts the phase shift response to enhance or suppress signal strength in specific directions.
 	In this paper, we show how those three seemingly different technologies can be unified to leverage their benefits simultaneously into a single architecture called RIScatter.
-	RIScatter is a new paradigm for future wireless networks and consists of multiple dispersed or co-located passive scattering nodes, whose reflection states can be adapted to partially engineer the wireless channel and partially modulate information onto the scattered wave.
+	RIScatter is a new paradigm for future wireless networks and consists of multiple dispersed or co-located passive scatter nodes, whose reflection states can be adapted to partially engineer the wireless channel and partially modulate information onto the scattered wave.
 	This contrasts with \gls{bc}/\gls{sr} (resp. \gls{ris}) where states are exclusively a function of information symbols (resp. \gls{csi}).
-	The key principle in RIScatter is to render the probability distribution of reflection states as a joint function of the \gls{csi} and input information source for heterogeneous traffic control and universal hardware design.
-	% augmented \gls{qos} control.
-	This enables RISscatter to softly bridge, generalize, and outperform \gls{bc}, \gls{sr}, \gls{ris}; boil down to any of those under specific reflection states; or evolve in a mixed form.
-	We show RIScatter provides a fundamental tradeoff that balances information modulation and channel reconfiguration capabilities in a flexible and mutualistic manner.
-	% Instead of treating probability distribution of reflection states as equiprobable (as scattering source of \gls{bc}/\gls{sr}) or degenerate (as reflecting element of \gls{ris}), RIScatter nodes located at different places adapt the input distribution of passive scatterers based on link priority and \gls{csi}, balancing information encoding and channel reconfiguration in a flexible and mutualistic manner.
-	% RIScatter receiver semi-coherently decodes all nodes from accumulated energy, determines primary equivalent channel over reflection pattern, then coherently decodes the primary link under enhanced multipath.
-	% It reduces the complexity of cooperative decoding while preserves the benefits of backscatter modulation and passive beamforming.
-	% To accommodate signal characteristics, we also propose a low-complexity RIScatter receiver that preserves the aforementioned benefits.
-	% Using shared spectrum, energy, and infrastructures, RIScatter is a general and powerful transmit-assist protocol that unifies \gls{bc}, \gls{ris} and \gls{sr} with universal hardware design and augmented \gls{qos} control.
-	% We consider an application scenario where a multi-antenna \gls{ap} serves a single-antenna user surrounded by multiple RIScatter nodes, and characterize the achievable primary-total-backscatter rate region by designing input distribution at the nodes, active beamforming at the \gls{ap}, and backscatter decision regions at the user.
-	% For a typical scenario
+	The key principle in RIScatter is to render the probability distribution of reflection states as a joint function of the \gls{csi} and input information source.
+	This enables RISscatter to softly bridge, generalize, and outperform \gls{bc}, \gls{sr}, \gls{ris}; boil down to any of those under specific reflection states; or evolve in a mixed form for universal hardware design and heterogeneous traffic control.
 	For a typical setup, we characterize the achievable primary-(total-)backscatter rate region by optimizing input distribution at the nodes, active beamforming at the \gls{ap}, and backscatter detector at the user.
-	% An application scenario is considered where a multi-antenna \gls{ap} serves a single-antenna user surrounded by dispersed RIScatter nodes, and the achievable primary-total-backscatter rate region is characterized by optimizing input distribution at the nodes, active beamforming at the \gls{ap}, and backscatter detector at the user.
-	% Simulation results demonstrate RIScatter nodes can flexibly control the transmit-assist tradeoff via smart input distribution design.
-	% Simulation results demonstrate RIScatter can flexibly control the tradeoff between backscatter modulation and passive beamforming via smart input distribution design, which outperforms \gls{bc}, \gls{sr}, and \gls{ris}.
-	Simulation results demonstrate RIScatter nodes can exploit the additional propagation paths to smoothly transit between backscatter modulation and passive beamforming via smart input distribution design.
-	% Simulation results demonstrate RIScatter can exploit smart input distribution design to provide a smooth transition between backscatter modulation and passive beamforming, which outperforms \gls{bc}, \gls{sr}, and \gls{ris}.
+	Simulation results demonstrate RIScatter nodes can exploit the additional propagation paths to smoothly transition between backscatter modulation and passive beamforming via smart input distribution design, and RIScatter receiver significantly reduces the decoding complexity and effectively accommodates the double modulation and signal characteristics in scatter-based cooperative networks.
 \end{abstract}
@@
 		\IEEEPARstart{F}{uture} wireless network is envisioned to provide high throughput, uniform coverage, pervasive connectivity, heterogeneous control, and cognitive intelligence for trillions of portable devices.
-		As an emerging low-power communication technique, \gls{bc} divides conventional transmitter into a \gls{rf} carrier emitter with power-hungry elements (e.g., synthesizer and amplifier) and an information-bearing node with power-efficient components (e.g., harvester and modulator) \cite{Boyer2014}.
+		As a mature low-power communication technique, \gls{bc} separates conventional transmitter into a \gls{rf} carrier emitter with power-hungry elements (e.g., synthesizer and amplifier) and an information-bearing node with power-efficient components (e.g., harvester and modulator) \cite{Boyer2014}.
 		In particular, the node harvests energy from impinging wave and embeds information over scattered signal, while the backscatter reader can be either co-located or separated with the carrier emitter, shown as \gls{mbc} and \gls{bbc} in Fig.
 \subref*{fg:mbc} and \subref*{fg:bbc}, respectively.
-		Its applications such as \gls{rfid} \cite{Dobkin2012,Landt2005} and passive sensor network \cite{Vannucci2008,Assimonis2016} have been extensively researched, standardized, and commercialized to support \gls{iot} and \gls{m2m} networks.
-		% ? Specifically, a dedicated emitter generates a sinusoidal carrier at reserved frequency, and \gls{rfid} tags reports their identifier to a nearby \gls{rfid} reader.
-		% ? With the upsurge of wireless devices and the downtrend of circuit power consumption, \gls{rfid} has experienced great success in \gls{ioe} and \gls{m2m} networks.
+		Its applications such as \gls{rfid} \cite{Dobkin2012,Landt2005} and passive sensor network \cite{Vannucci2008,Assimonis2016} have been researched, standardized, and commercialized in the era of \gls{ioe}.
 		However, conventional \gls{bc} nodes only respond when externally inquired by a nearby reader.
-		To tackle this, \cite{Liu2013b} proposed an \gls{ambc} system where interactive nodes recycle ambient legacy signals (e.g., radio, television and Wi-Fi) to harvest energy and establish connections, as shown in Fig.
-\subref*{fg:ambc}.
+		To tackle this, \cite{Liu2013b} proposed an \gls{ambc} system in Fig.
+\subref*{fg:ambc}, where battery-free nodes recycle ambient legacy signals (e.g., radio, television and Wi-Fi) to harvest energy and establish connections in between.
 		It eliminates the need of dedicated power supply, carrier emitter and frequency spectrum, but is subject to the strong direct-link interference.
-		In \cite{Yang2018}, the authors proposed a cooperative \gls{ambc} system where both primary (legacy) and backscatter links are decoded at the same user under various detection schemes.
-		% a cooperative receiver decodes both primary (legacy) and backscatter links using \gls{ml}, \gls{mrc}, \gls{zf}, \gls{mmse} and \gls{sic}
-		% co-located cooperative receiver to jointly or sequentially decode both primary (legacy) and backscatter links.
-		% The authors evaluated the error performance of \gls{ml}, linear, and \gls{sic} detectors for flat fading channel, and proposed a low-complexity detector for frequency-selective fading channel.
-		The concept of cooperative \gls{ambc} was further refined as \gls{sr} that cognitively incorporates \gls{ambc} with existing systems \cite{Liang2020}, which in shown Fig. \subref*{fg:sr}.
-		% shown in Fig. \subref*{fg:sr}, which cognitively incorporates \gls{ambc} with existing systems \cite{Liang2020}.
-		% In \gls{sr}, the primary transmitter generates active radio carrying primary information, the backscatter node modulates own information onto the scattered wave, and the co-located receiver decodes both links from two propagation paths.
-		% In \gls{sr}, the primary transmitter generates active radio and modulates primary information, the passive node scatters incoming wave and superimposes backscatter information, and the co-located receiver decodes both links from two propagation paths.
-		% An illustration of \gls{sr} is shown in \subref*{fg:sr}, where the primary transmitter generates active radio and modulates primary information, the passive node scatters incoming wave and superimposes backscatter information, and the co-located receiver decodes both links from both propagation paths.
-		In \gls{sr}, the active transmitter generates \gls{rf} wave carrying primary information, the passive node enhances the propagation environment and superimposes its own message on the scattered signal, and the cooperative receiver jointly or sequentially decodes both links.
-		% The direct transmitter-receiver path only convey
-		% The component over the direct transmitter-receiver path only
-		% The direct transmitter-receiver path contains primary information, and the cascaded transmitter-node-receiver path preserves both information in a superimposed manner.
-		% The direct transmitter-receiver path only contains modulated primary signal while the cascaded transmitter-node-receiver path preserves superimposed signal
-		% both thanks to signal characteristics.
-		% Such a coexistence was further classified into commensal, parasitic, and competitive relationships based on link priority \cite{Guo2019b}, and their instantaneous rates, optimal power allocations, and outage probabilities were subsequently derived in \cite{Guo2019b,Ding2020}.
-		% However, one important issue of \gls{sr} is practical cooperative decoding design.
-		% Due to physical constraints at the load-switching modulator, backscatter symbol period is typically longer than primary.
-		% Ideal joint \gls{ml} decoding achieves optimal performance with prohibitive computational complexity \cite{Yang2018,Liang2020,Zhang2022}.
-		% For sequential decoding from primary to backscatter, \cite{Long2020a} pointed out the randomness from backscatter modulation can be modelled as either interference or channel uncertainty, depending on the symbol period ratio.
-		% The authors concluded if this ratio is sufficiently large, the noncoherent primary achievable rate would asymptotically approach its coherent counterpart.
-		% This motivated \cite{Long2020a,Liang2020,Guo2019b,Ding2020,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Yang2018,Han2021,Zhang2022} to first decode the primary link, perform \gls{sic}, then decode the backscatter link.
-		% However, the advantage of \gls{sic} is questionable because 1) sufficiently large symbol period ratio is assumed in primary rate analysis and constraints backscatter rate; 2) backscatter pattern and signal characteristics are not fully exploited; 3) noncoherent primary encoding is required at the transmitter, while re-encoding, precoding, and subtraction are required at the receiver; 4) primary and backscatter symbols are superimposed by multiplication instead of superposition.
-		% Another open issue for \gls{sr} is backscatter multiple access.
-		% \cite{Xu2021a} extended \gls{sic} to multi-node scenario and proposed a backscatter \gls{noma}-based \gls{sr} with decoding order following backscatter signal strength.
-		% However, its performance deteriorates fast when the number of nodes increases.
-		% Backscatter \gls{tdma} was also evaluated in \cite{Yang2021a}, where each node transmits information during dedicated slot and harvests energy during others.
-		% It enhances energy efficiency by transmission time and reflection ratio optimization, but requires regular feedback to passive nodes and incurs high coordination cost.
-		% \cite{Vougioukas2019} controls the load-switching speed at nodes to shift the scattered signal to desired frequency bands.
-		% This enables backscatter \gls{fdma} at the cost of extra bandwidth and higher power consumption.
-		% To reduce coordination between passive nodes, \cite{Han2021} proposed a random code-assisted multiple access for \gls{sr} and evaluated the asymptotic \gls{sinr} using random matrix theory.
-		% However, it suffers from imperfect synchronization and the near-far problem.
-		% Above applications treat the scattering node as an information source.
+		In \cite{Yang2018}, the authors proposed a cooperative \gls{ambc} system where both primary (legacy) and backscatter links are decoded by the same receiver under various detection schemes.
+		The concept of cooperative \gls{ambc} was further refined as \gls{sr} in Fig. \subref*{fg:sr} that cognitively incorporates \gls{ambc} with existing systems \cite{Liang2020}.
+		In a \gls{sr} system, the active transmitter generates \gls{rf} wave carrying primary information, the passive node enhances the radio propagation and superimposes its own message on the scattered signal, and the cooperative receiver jointly or sequentially decodes both links.
+		The applications above employ scatter node as information sources, and the active primary link (if exists) is subject to the influence of backscatter randomness.
 		On the other hand, \gls{ris} is a smart planar reflector that consists of numerous low-power and low-cost elements with adjustable amplitude and phase responses.
-		The reflection pattern over time is deterministic, which can be optimized and reported to the user before transmission.
+		The reflection pattern is deterministic over time, which can be optimized and coordinated before the transmission.
 		\gls{ris} recycles and redistributes surrounding \gls{rf} waves to customize wireless propagation environment for signal enhancement, interference suppression, scattering enrichment and non-line-of-sight bypassing \cite{Wu2021b}.
-		% in Fig. \subref*{fg:ris} is a promising technology to recycle
-		% On the other hand, \gls{ris} in Fig.
-\subref*{fg:ris} is a promising technology that evolves wireless propagation environment using numerous passive reflecting elements (e.g., scattering antenna or programmable metamaterial) with adjustable amplitudes and/or phases \cite{Wu2021b}.
-		% With proper phase shift design, the scattered components can add constructively/destructively with the direct component for signal enhancement/interference suppression.
-		% Compared with scattering nodes of \gls{bc}/\gls{sr}, \gls{ris} elements embed no additional information and use deterministic reflection pattern priorly known at the transmitter and receiver.
-		% Compared with scattering nodes of \gls{bc}/\gls{sr}, \gls{ris}
-		% elements embed no additional information and use deterministic reflection pattern over time, which can be optimized and fed back to the transmitter and receiver during coordination phase.
 		A comparison of different scattering applications is summarized in Table \ref{tb:scattering_applications}.
-		% , which can be priorly known at the transmitter and receiver.
-		% contain no additional information
-
-		% employ deterministic reflection pattern over time that contains no information
-
-		% and priorly known at transmitter and receiver.
-		% This motivated the use of fixed reflection coefficients during each channel block to improve communication, sensing, and power performances \cite{Wu2018,Zhang2019a,Lin2022,Liu2022,Feng2022,Zhao2022}.
-		% The concept of dynamic \gls{ris}, namely choosing independent reflection coefficients over different time slots within channel block, was first considered for resource blocks of \gls{ofdm} systems, then extended to power and information phases of \gls{wpcn} \cite{Wu2021,Wu2021d,Hua2022a}.
-		% Dynamic \gls{ris} provides artificial channel diversity and flexible resource allocation, but misses the opportunity to encode its own message.
-		% From an information-theoretic perspective, \cite{Karasik2020} reported using \gls{ris} as an auxiliary passive beamforming device to maximize the \gls{snr} is generally rate-suboptimal for finite input constellations.
-		% Instead, joint transmitter-\gls{ris} encoding achieves the capacity of \gls{ris}-aided channel, and layered encoding with \gls{sic} decoding (i.e., \gls{sic}-based \gls{sr}) can outperform pure passive beamforming at high \gls{snr}.
-		% It inspired \cite{Liu2019d,Bereyhi2020,Xu2020b,Zhang2021d,Hu2021b,Hua2022,Basar2020,Ma2020a,Yuan2021,Hu2021a} to employ \gls{ris} also as an information source to combine passive beamforming and backscatter modulation in the overall reflection pattern.
-		% In particular, \emph{symbol level precoding} maps backscatter symbols to \gls{ris} coefficient sets optimized for detection \cite{Liu2019d,Bereyhi2020}, \emph{overlay modulation} superposes information-bearing symbols over a common auxiliary matrix \cite{Xu2020b,Zhang2021d,Hu2021b,Hua2022}, \emph{spatial modulation} switches between reflection coefficient sets that maximize \gls{snr} at different receive antennas \cite{Basar2020,Ma2020a,Yuan2021}, and \emph{index modulation} divides \gls{ris} into reflection elements for passive beamforming and information elements for on-off modulation \cite{Hu2021a}.
-		% However, those \gls{ris}-empowered \gls{bc}/\gls{sr} designs involve advanced hardware architecture, high optimization complexity, and additional control overhead.
-
 		\begin{figure}[!t]
@@
 				Illustration of scattering applications.
-				% Paradigms for various scattering applications.
 			}
@@
 			Backscatter detection         & Coherent                  & Coherent                  & Semi-coherent or noncoherent                    & Coherent                                     & ---                                        & Semi-coherent                                     \\ \midrule
-			Reflection state distribution & Equiprobable (line-coded) & Equiprobable (line-coded) & Equiprobable (line-coded)                       & Equiprobable or Gaussian                     & Degenerate (\gls{csi}-adaptive)         & Flexible (\gls{csi}- and link priority-adaptive)  \\ \midrule
-			Load-switching frequency      & Fast or slow              & Fast or slow              & Fast or slow                                    & Slow                                         & Slow (dynamic) or very slow (blockwise) & Fast or slow                                      \\ \bottomrule
+			Reflection state distribution & Equiprobable (line-coded) & Equiprobable (line-coded) & Equiprobable (line-coded)                       & Equiprobable or Gaussian                     & Degenerate (\gls{csi}-adaptive)            & Flexible (\gls{csi}- and traffic-adaptive)        \\ \midrule
+			Load-switching frequency      & Fast or slow              & Fast or slow              & Fast or slow                                    & Slow                                         & Slow (dynamic) or quasi-static (blockwise) & Fast or slow                                      \\ \bottomrule
 		\end{tabularx}
@@
 		Similar to \gls{cr}, the coexistence of primary and backscatter links in \gls{sr} can be classified into commensal, parasitic, and competitive relationships, whose instantaneous rates, power schemes, and outage probabilities were acquired in \cite{Guo2019b,Ding2020}.
-		% To evaluate the performance of cooperative receivers, \cite{Yang2018} derived the bit error rates of \gls{ml}, \gls{mrc}, \gls{zf}, \gls{mmse} and \gls{sic} detectors for flat fading channels, and proposed a low-complexity detector for frequency-selective fading channels.
 		To evaluate the performance of cooperative receivers, \cite{Yang2018} derived the bit error rates of \gls{ml} and \gls{sic} detectors for flat fading channels, and proposed a low-complexity detector for frequency-selective fading channels.
-		% However, it assumed equal symbol period of both links with perfect synchronization, which is impractical due to the load-switching speed constraint.
-		% However, it assumed the primary and backscatter symbol periods are equal and
-		% However, it only considered the case where primary and backscatter symbols have the same period.
 		However, it only considered the case where the primary and backscatter symbols of the same period are perfectly aligned in time.
-		Joint \gls{ml} decoding can achieve the best error performance in general, but its computational complexity is prohibitive especially for nodes with high-order constellation \cite{Yang2018,Liang2020,Zhang2022}.
-		One special property of \gls{sr} is the backscatter signal strength is significantly weaker than primary due to the double fading effect.
-		It motivated \cite{Long2020a,Liang2020,Guo2019b,Ding2020,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Yang2018,Han2021,Zhang2022} to view \gls{sr} as a multiplicative \gls{noma} and perform sequential primary-backscatter decoding with \gls{sic}.
-		During primary decoding, the randomness from backscatter modulation can be modelled as either interference or channel uncertainty, depending on the relationship between primary sampling rate and backscatter switching speed.
-		If the former is much higher, then the average primary achievable rate under noncoherent detection would approach its coherent counterpart asymptotically \cite{Long2020a}, and both links may be decoded in an interference-free manner.
-		% For sequential primary-backscatter decoding, the randomness of backscatter modulation can be modelled as either interference or channel uncertainty, depending on the symbol period ratio \cite{Long2020a}.
-		% If this ratio is sufficiently large, the authors proved the noncoherent primary achievable rate would approach its coherent counterpart asymptotically.
-		% This motivated \cite{Long2020a,Liang2020,Guo2019b,Ding2020,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Yang2018,Han2021,Zhang2022} to perform \gls{sic} from primary to backscatter links.
-		However, the disadvantage of such \gls{sic} includes:
-		1) primary rate analysis is backed by long backscatter symbol period that constrains backscatter rate;
-		2) reflection pattern and signal characteristics are not fully exploited;
-		3) noncoherent primary encoding is required at the transmitter while re-encoding, precoding and subtraction are required at the receiver;
-		4) primary and backscatter symbols are superimposed by multiplication instead of superposition.
-
-		Another open issue for \gls{bc} and \gls{sr} is node multiple access.
-		\cite{Xu2021a} proposed a \gls{noma}-based \gls{sr} with \gls{sic} order in backscatter equivalent channel strength, whose performance deteriorates fast when the number of nodes increases.
+		Joint \gls{ml} decoding can achieve the best error performance but comes with prohibitive computational complexity especially for sources with high-order constellation \cite{Yang2018,Liang2020,Zhang2022}.
+		One special property of scatter-based cooperative networks is the backscatter signal strength is significantly weaker than primary due to the double fading effect.
+		It motivated \cite{Long2020a,Liang2020,Guo2019b,Ding2020,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Yang2018,Han2021,Zhang2022} to view \gls{sr} as a multiplicative \gls{noma} and perform sequential primary-backscatter decoding based on \gls{sic}.
+		During primary decoding, the randomness from backscatter modulation can be modelled as either interference or channel uncertainty, depending on the relationship between the primary sampling rate and backscatter switching speed.
+		If the former is much higher (i.e., commensal \gls{sr}), the average primary achievable rate under noncoherent detection would asymptotically approach its coherent counterpart \cite{Long2020a}, and both links may be decoded in an interference-free manner.
+		However, the assumption of very large backscatter-over-primary symbol period ratio may not hold in practice \footnote{For example, Wi-Fi sampling rate is \qty{20}{\MHz} while \gls{rfid} load switching speed varies between \num{100}s of \unit{\kHz} to \num{10}s of \unit{\MHz} \cite{Torres2021}, corresponding to a typical symbol period ratio between \num{1} and \num{100}.}, and such a \gls{sic}-based sequential decoding requires re-encoding, precoding, and subtraction at each primary symbol block with a time-domain \gls{mrc}, which can be operation-intensive and \gls{csi}-sensitive.
+		Another open issue for \gls{bc} and \gls{sr} is efficient node multiple access.
+		\cite{Xu2021a} proposed a \gls{noma}-based \gls{sr} where the \gls{sic} order depends on the backscatter channel strength, and the performance deteriorates fast as the number of nodes increases.
 		\gls{tdma}-based \gls{sr} was also considered in \cite{Yang2021a} where each node transmits information during its dedicated slot and harvests energy during others.
-		It allows adaptive transmission time and reflection ratio optimization, but requires regular feedback and incurs high coordination cost.
+		It enables adaptive transmission time and reflection ratio optimization but requires regular coordination and incurs high coordination cost.
 		\cite{Vougioukas2019} controls the load-switching speed to shift the scattered signal to the desired frequency band.
-		This enables backscatter \gls{fdma} at the cost of extra bandwidth and higher power consumption.
+		This enables backscatter \gls{fdma} at the cost of extra bandwidth and higher node power consumption.
 		To reduce coordination burden for passive nodes, \cite{Han2021} proposed a random code-assisted multiple access for \gls{sr} and evaluated the asymptotic \gls{sinr} using random matrix theory.
-		However, this code-domain solution suffers from imperfect synchronization and the near-far problem.
-
-		Conventional \gls{ris} design with fixed reflection coefficients during each channel block has been extensively studied in communication, sensing, and power literatures \cite{Wu2018,Zhang2019a,Lin2022,Liu2022,Feng2022,Zhao2022}.
-		In contrast, dynamic \gls{ris} that chooses independent reflection coefficients over different time slots has gained recent attentions in multi-user and multi-purpose wireless networks.
-		The concept was first considered for resource blocks of \gls{ofdm} systems, then extended to power and information phases of \gls{wpcn} \cite{Wu2021,Wu2021d,Hua2022a}.
-		Dynamic \gls{ris} provides artificial channel diversity and flexible resource allocation, but misses the opportunity to encode its own message.
-		From an information-theoretic perspective, \cite{Karasik2020} reported using \gls{ris} as an auxiliary passive beamforming device to maximize the \gls{snr} is generally rate-suboptimal for finite input constellations.
-		Instead, joint transmitter-\gls{ris} encoding achieves the capacity of \gls{ris}-aided channel, and layered encoding with \gls{sic} decoding (i.e., \gls{sic}-based \gls{sr}) can outperform pure passive beamforming at high \gls{snr}.
-		It inspired \cite{Liu2019d,Bereyhi2020,Xu2020b,Zhang2021d,Hu2021b,Hua2022,Basar2020,Ma2020a,Yuan2021,Hu2021a} to employ \gls{ris} also as an information source to combine passive beamforming and backscatter modulation in the overall reflection pattern.
-		In particular, \emph{symbol level precoding} maps backscatter symbols to optimized \gls{ris} coefficient sets \cite{Liu2019d,Bereyhi2020}, \emph{overlay modulation} superposes information-bearing symbols over a common auxiliary matrix \cite{Xu2020b,Zhang2021d,Hu2021b,Hua2022}, \emph{spatial modulation} switches between reflection coefficient sets that maximize \gls{snr} at different receive antennas \cite{Basar2020,Ma2020a,Yuan2021}, and \emph{index modulation} divides \gls{ris} into reflection elements for passive beamforming and information elements for on-off modulation \cite{Hu2021a}.
-		However, those \gls{ris}-empowered \gls{bc}/\gls{sr} designs involve advanced hardware architecture, high optimization complexity, and additional control overhead.
-		Besides, all relevant literatures assumed at backscatter information sources either Gaussian codebook \cite{Guo2019b,Ding2020,Long2020a,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Hu2021b} or finite equiprobable inputs \cite{Yang2018,Liang2020,Han2021,Zhang2022,Liu2019d,Bereyhi2020,Xu2020b,Zhang2021d,Hua2022,Basar2020,Ma2020a,Yuan2021,Hu2021a}.
-		The former is impractical for passive backscatter devices, while the latter does not fully exploit reflection pattern and \gls{csi}.
-	\end{subsection}
-
-	% To the best of our knowledge, all relevant literatures assumed at backscatter information sources either Gaussian codebook \cite{Guo2019b,Ding2020,Long2020a,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Hu2021b} or finite equiprobable inputs \cite{Yang2018,Liang2020,Han2021,Zhang2022,Liu2019d,Bereyhi2020,Xu2020b,Zhang2021d,Hua2022,Basar2020,Ma2020a,Yuan2021,Hu2021a}.
-	% The former is impractical for passive backscatter devices, while the latter does not fully exploit reflection pattern and \gls{csi}.
+		However, this code-domain solution suffers from the near-far problem and imperfect synchronization.
+		On the other hand, conventional \gls{ris} design with fixed reflection coefficients during each channel block has been extensively studied in communication, sensing, and power literatures \cite{Wu2018,Zhang2019a,Lin2022,Liu2022,Feng2022,Zhao2022}.
+		Dynamic \gls{ris}, which employs independent reflection patterns during different time slots, has gained recent attentions in multi-user and multi-purpose wireless networks.
+		The concept was first proposed in \cite{Yang2020} to fine tune the resource blocks for \gls{ofdm} systems, then extended to the downlink power and uplink information phases of \gls{wpcn} \cite{Wu2021,Wu2021d,Hua2022a}.
+		It creates artificial channel diversity and enables flexible resource allocation, but misses the opportunity to encode its own message.
+		\gls{ris} can also be used a transmitter when placed in the near field of a carrier emitter, and prototypes for \gls{psk} and \gls{qam} have been implemented in \cite{Tang2019a,Dai2020a}.
+		From an information-theoretic perspective, \cite{Karasik2020} reported using \gls{ris} as a passive beamformer to maximize the \gls{snr} is generally rate-suboptimal for finite input constellations.
+		Instead, the capacity of \gls{ris}-aided channel is achieved by joint transmitter-\gls{ris} encoding, and multiplicative coding with \gls{sic} decoding (i.e., \gls{sic}-based \gls{sr}) can outperform pure passive beamforming at high \gls{snr}.
+		It inspired \cite{Liu2019d,Bereyhi2020,Xu2020b,Zhang2021d,Hu2021b,Hua2022,Basar2020,Ma2020a,Yuan2021,Hu2021a} to combine passive beamforming and backscatter modulation in the overall reflection pattern.
+		In particular, \emph{symbol level precoding} maps backscatter symbols to optimized \gls{ris} coefficient sets \cite{Liu2019d,Bereyhi2020}, \emph{overlay modulation} superposes information-bearing symbols over a common auxiliary matrix \cite{Xu2020b,Zhang2021d,Hu2021b,Hua2022}, \emph{spatial modulation} switches between reflection coefficient sets that maximize \gls{snr} at different receive antennas \cite{Basar2020,Ma2020a,Yuan2021}, and \emph{index modulation} employs dedicated reflection elements for passive beamforming and dedicated information elements for backscatter modulation \cite{Hu2021a}.
+		Those \gls{ris}-empowered \gls{bc}/\gls{sr} designs involve advanced hardware architecture and high optimization complexity.
+		Besides, all relevant literatures considered either Gaussian codebook \cite{Guo2019b,Ding2020,Long2020a,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Hu2021b} or finite equiprobable inputs \cite{Yang2018,Liang2020,Han2021,Zhang2022,Liu2019d,Bereyhi2020,Xu2020b,Zhang2021d,Hua2022,Basar2020,Ma2020a,Yuan2021,Hu2021a} for backscatter information sources.
+		The former is impractical for passive backscatter devices while the latter does not fully exploit \gls{csi} and signal characteristics.
+	\end{subsection}
+
 	\begin{subsection}{Contributions}
-		We introduce RIScatter that generalizes \gls{bc}, \gls{sr}, and \gls{ris} to manipulate the transmit-assist tradeoff via smart input distribution and practical receiver design.
-		The paradigm of RIScatter is presented in Fig. \subref*{fg:riscatter}, and the contributions of this paper are summarized as follows.
-
-		\emph{First,} we propose RIScatter nodes to adapt the input probability distribution of a finite-state passive scatter device based on link priority and \gls{csi}.
-		The reflection pattern over time is no longer fully random or deterministic, but can be flexibly distributed to unify and balance backscatter modulation with passive beamforming.
-		Scattering source of \gls{bc}/\gls{sr} and reflecting element of \gls{ris} can be regarded as its extreme cases, where the input distribution boils down to equiprobable and degenerate, respectively.
-		Like aforementioned \gls{ris}-empowered \gls{bc}/\gls{sr} schemes, the passive nodes require regular coordination with ambient devices, but the advantages are
-		1) RIScatter nodes can be built over universal load-switching scatterers instead of composite metamaterial;
-		2) backscatter modulation and passive beamforming are unified by adaptive input distribution instead of advanced hardware architecture;
-		3) optimization cost of input distribution is much lower than that of \gls{ris} reflection coefficients;
-		4) adaptive backscatter channel coding can exploit \gls{csi} to achieve higher instantaneous rate than conventional equiprobable line coding in \gls{bc}/\gls{sr};
-		5) the potentially dispersed characteristics of RIScatter nodes (and legacy users) avoids the development optimization and allows uniformly good performance for both links.
+		As presented in Fig. \subref*{fg:riscatter}, we propose RIScatter as a novel scattering protocol that generalizes \gls{bc}, \gls{sr}, and \gls{ris}.
+		The contributions of this paper are summarized as follows.
+
+		\emph{First,} we propose RIScatter nodes that adapt the reflection state distribution of passive scatter devices based on \gls{csi} and link weights to flexibly transition between backscatter modulation and passive beamforming.
+		Scattering sources of \gls{bc}/\gls{sr} and reflecting elements of \gls{ris} can be regarded as special cases where the input distribution becomes equiprobable and degenerate, respectively.
+		On the contrary, adaptive RIScatter encoding can achieve higher backscatter rate than conventional line coding.
+		The RIScatter nodes can be either co-located to enable joint distribution design for improved total backscatter rate, or dispersed to guarantee uniformly good primary and backscatter performances.
 

### 2022-10-24 assets/illustration/time_structure.tex
:bento: Update illustrations

\begin{tikzpicture}
	% BC/AmBC/SR
	\foreach \x in {0,...,3}{
			\draw[blue,fill=blue!30!white,postaction={pattern=horizontal lines},pattern color=.] (0.5*\x,3) rectangle ++(0.5,0.5);
		}
	\foreach \x in {4,...,7}{
			\draw[blue,fill=blue!30!white,postaction={pattern=north west lines},pattern color=.] (0.5*\x,3) rectangle ++(0.5,0.5);
		}
	\foreach \x in {8,...,11}{
			\draw[blue,fill=blue!30!white,postaction={pattern=vertical lines},pattern color=.] (0.5*\x,3) rectangle ++(0.5,0.5);
		}
	\foreach \x in {12,...,15}{
			\draw[blue,fill=blue!30!white,postaction={pattern=north east lines},pattern color=.] (0.5*\x,3) rectangle ++(0.5,0.5);
		}

	% RIS
	\foreach \x in {0,...,15}{
			\draw[red,fill=red!30!white,postaction={pattern=north west lines},pattern color=.] (0.5*\x,2) rectangle ++(0.5,0.5);
		}

	% RIScatter
	\foreach \x in {0,...,1}{
			\draw[brown,fill=brown!30!white,postaction={pattern=horizontal lines},pattern color=.] (0.5*\x,1) rectangle ++(0.5,0.5);
		}
	\foreach \x in {2,...,7}{
			\draw[brown,fill=brown!30!white,postaction={pattern=north west lines},pattern color=.] (0.5*\x,1) rectangle ++(0.5,0.5);
		}
	\foreach \x in {8,...,11}{
			\draw[brown,fill=brown!30!white,postaction={pattern=vertical lines},pattern color=.] (0.5*\x,1) rectangle ++(0.5,0.5);
		}
	\foreach \x in {12,...,15}{
			\draw[brown,fill=brown!30!white,postaction={pattern=north west lines},pattern color=.] (0.5*\x,1) rectangle ++(0.5,0.5);
		}

	\foreach \x in {1,...,7}{
			\draw[dotted] (\x,0.5) -- (\x,4);
		}
	\draw[latex-latex] (0,3.7) -- (0.5,3.7) node[above,midway,yshift=1]{PB};
	\draw[latex-latex] (0,4.3) -- (1,4.3) node[above,midway,yshift=1]{BB};
	\draw[latex-latex] (0,4.9) -- (8,4.9) node[above,midway,yshift=1]{Channel Block};

	\node at (-2,3.25) {BackCom/AmBC/SR};
	\node at (-2,2.25) {RIS};
	\node at (-2,1.25) {RIScatter};

	\draw [pattern=horizontal lines](0.15,0) rectangle ++(0.5,0.25) node[xshift=20,yshift=-3.5] {State 1};
	\draw [pattern=north west lines](2.15,0) rectangle ++(0.5,0.25) node[xshift=20,yshift=-3.5] {State 2};
	\draw [pattern=vertical lines](4.15,0) rectangle ++(0.5,0.25) node[xshift=20,yshift=-3.5] {State 3};
	\draw [pattern=north east lines](6.15,0) rectangle ++(0.5,0.25) node[xshift=20,yshift=-3.5] {State 4};
\end{tikzpicture}

### 2022-10-24 main.tex
:pencil: Update contributions

@@
 \begin{document}
-\title{RIScatter: Unifying\\Backscatter Communications, Symbiotic Radio, and Reconfigurable Intelligent Surface}
+\title{RIScatter: Unifying Backscatter Communications, Symbiotic Radio, and Reconfigurable Intelligent Surface}
+% \title{RIScatter: Unifying\\Backscatter Communications, Symbiotic Radio, and Reconfigurable Intelligent Surface}
 \author{
@@
 % TODO Input probability distribution for discrete-value reflection (backscatter), constellation design for continue-value reflection (RIS)
-% TODO channel coding: general non-adaptive (book) adaptive (DMC)
+% * channel coding: general non-adaptive (book) adaptive (DMC)
 % ? [Turbocharging] Since averaging must be done over a significant period of time to smooth out the variation in the TV transmissions, averaging does not allow rates much higher than 10 kbps [24].
@@
 	For a typical setup, we characterize the achievable primary-(total-)backscatter rate region by optimizing input distribution at the nodes, active beamforming at the \gls{ap}, and backscatter detector at the user.
-	Simulation results demonstrate RIScatter nodes can exploit the additional propagation paths to smoothly transition between backscatter modulation and passive beamforming via smart input distribution design, and RIScatter receiver significantly reduces the decoding complexity and effectively accommodates the double modulation and signal characteristics in scatter-based cooperative networks.
+	Simulation results demonstrate RIScatter nodes can exploit the additional propagation paths to smoothly transition between backscatter modulation and passive beamforming via smart input distribution design, and the proposed receiver significantly reduces the decoding complexity and effectively accommodates the double modulation and signal difference in scatter-based cooperative networks.
 \end{abstract}
@@
 		From an information-theoretic perspective, \cite{Karasik2020} reported using \gls{ris} as a passive beamformer to maximize the \gls{snr} is generally rate-suboptimal for finite input constellations.
-		Instead, the capacity of \gls{ris}-aided channel is achieved by joint transmitter-\gls{ris} encoding, and multiplicative coding with \gls{sic} decoding (i.e., \gls{sic}-based \gls{sr}) can outperform pure passive beamforming at high \gls{snr}.
+		Instead, the capacity of \gls{ris}-aided channel is achieved by joint transmitter-\gls{ris} encoding, and multiplication coding with \gls{sic} decoding (i.e., \gls{sic}-based \gls{sr}) can outperform pure passive beamforming at high \gls{snr}.
 		It inspired \cite{Liu2019d,Bereyhi2020,Xu2020b,Zhang2021d,Hu2021b,Hua2022,Basar2020,Ma2020a,Yuan2021,Hu2021a} to combine passive beamforming and backscatter modulation in the overall reflection pattern.
@@
 
-		\emph{First,} we propose RIScatter nodes that adapt the reflection state distribution of passive scatter devices based on \gls{csi} and link weights to flexibly transition between backscatter modulation and passive beamforming.
-		Scattering sources of \gls{bc}/\gls{sr} and reflecting elements of \gls{ris} can be regarded as special cases where the input distribution becomes equiprobable and degenerate, respectively.
-		On the contrary, adaptive RIScatter encoding can achieve higher backscatter rate than conventional line coding.
-		The RIScatter nodes can be either co-located to enable joint distribution design for improved total backscatter rate, or dispersed to guarantee uniformly good primary and backscatter performances.
-
-		\emph{Second,} we propose a practical RIScatter receiver that semi-coherently decodes RIScatter nodes from the received energy per backscatter block, re-encodes for their reflection patterns, retrieves primary equivalent channel as if dynamic passive beamforming, then coherently decodes the primary link under the enhanced multipath.
-		The proposed receiver
-		1) preserves the benefits of backscatter modulation and passive beamforming;
-		2) enjoys lower computational and operational complexities than joint \gls{ml} and \gls{sic} schemes;
-		3) accommodates the link difference and suits for diverse symbol period ratios;
-		4) requires minor modification over legacy hardware.
-
-		\emph{Third,} we consider an application scenario where multiple RIScatter nodes ride over a point-to-point \gls{miso} transmission, performing backscatter modulation and passive beamforming to a nearby user using shared spectrum, energy, and infrastructures.
-		To investigate how RIScatter unifies \gls{bc}, \gls{sr} and \gls{ris} for the benefits of both coexisting subsystems, we provide primary and backscatter rate analyses and emphasize the contributions of input distribution at RIScatter nodes, active beamforming at the \gls{ap}, and backscatter decision regions at the user.
-		This is the first paper to reveal the importance of those factors in joint \gls{ris} and \gls{bc}/\gls{sr} design.
-
-		\emph{Fourth,} we characterize the achievable primary-total-backscatter rate region of the aforementioned system by optimizing the input distribution, active beamforming, and backscatter decision regions.
-		It is formulated as a weighted sum-rate maximization subject to input probability simplex, average transmit power, and sequential decision threshold constraints.
-		Since the original problem is highly non-convex, we decouple it into individual subproblems and constraint all decision regions to convex (connected) intervals.
-		A suboptimal \gls{bcd} algorithm is then proposed, where the \gls{kkt} input distribution is numerically evaluated by limit of sequences, the active beamforming is iteratively updated by \gls{pgd} accelerated by \gls{bls}, and the decision regions are refined by existing thresholding designs.
-
-		\emph{Fifth,} we provide numerical results to demonstrate the benefits of RIScatter and proposed algorithms.
-		It is concluded that
-		1) RIScatter nodes provide flexible transmit-assist tradeoff using adaptive input distribution design;
-		2) when primary link is absolutely prioritized, the input probability of each node is \num{1} at one state and \num{0} at the others, which coincides with discretized \gls{ris};
-		3) when backscatter link is absolutely prioritized, RIScatter nodes can exploit adaptive channel coding to achieve higher instantaneous rate than conventional equiprobable inputs of \gls{bc}/\gls{sr};
-		4) the proposed \gls{kkt} input distribution design converges to stationary points, whose average performance is very close to global optimal;
-		5) the proposed \gls{pgd} beamforming provides larger rate region than \gls{mrt}-based schemes;
-		6) the decision region schemes adapted to input distribution provide higher backscatter rates than the non-adaptive \gls{ml} detector;
-		7) cooperation between passive nodes in terms of joint encoding can further boost the total backscatter rate;
-		8) the low complexity of input distribution design and the marginal effect of increasing reflection states motivates the use of low-order scattering nodes to replace high-resolution \gls{ris}.
+		\emph{First,} we propose RIScatter nodes that adapt the reflection state distribution of passive scatter devices based on \gls{csi} and link weights, in order to flexibly transition between backscatter modulation and passive beamforming.
+		Scattering sources of \gls{bc}/\gls{sr} and reflecting elements of \gls{ris} can be regarded as special cases with uniform and degenerate input distributions, respectively.
+		On the contrary, adaptive RIScatter encoding boils down to deterministic \gls{ris} when primary link is prioritized, and achieves higher backscatter rate than conventional line coding when backscatter link is prioritized.
+		Multiple RIScatter nodes can be either co-located to enable joint distribution design for improved total backscatter rate, or dispersed to guarantee uniformly good performance for both links.
+
+		\emph{Second,} we propose a practical receiver that accommodates the double modulation and signal difference in scatter-based cooperative networks.
+		Since the primary and backscatter messages are superimposed by multiplication coding and the backscatter symbol is typically longer than primary, the scattered signals from RIScatter nodes can be treated as multipath components during primary decoding, and the primary message can be viewed as a spreading code during backscatter decoding.
+		Conventional sequential primary-backscatter decoder eliminates primary interference by \gls{sic} at each primary block, while our sequential backscatter-primary detector semi-coherently decodes RIScatter nodes from the received energy, re-encodes to recover exact reflection patterns, and models the deterministic multipath in the primary equivalent channel as dynamic passive beamforming at each backscatter block.
+		It enables backscatter modulation and dynamic passive beamforming at much lower operational complexity, and is suitable for scatter nodes with various load switching speeds.
+
+		\emph{Third,} we consider a scenario where multiple RIScatter nodes ride over an active point-to-point \gls{miso} transmission to perform backscatter modulation and passive beamforming towards a nearby user using shared spectrum, energy, and infrastructures.
+		We provide primary and total backscatter rate analyses and characterize the achievable rate region by optimizing input distribution at RIScatter nodes, active beamforming at the \gls{ap}, and backscatter decision regions at the user.
+		Since the original problem is highly non-convex, we decouple it into individual subproblems and propose a suboptimal \gls{bcd} algorithm, where the \gls{kkt} input distribution is numerically evaluated by limit of sequences, the active beamforming is iteratively updated by \gls{pgd} accelerated by \gls{bls}, and the decision regions are refined by existing sequential quantization methods for \gls{dmc}.
+		This is the first paper to reveal the importance of input distribution and decision region designs in relevant literatures.
+
+		\emph{Fourth,} we provide numerical results to demonstrate the benefits of RIScatter and proposed algorithms.
+		We conclude:
+		1) adaptive reflection state distribution design can flexibly transition between backscatter modulation and passive beamforming;
+		2) when primary link is prioritized, input distribution becomes degenerate and RIScatter nodes coincide with discrete \gls{ris};
+		3) when backscatter link is prioritized, adaptive RIScatter encoding achieves higher backscatter rate than conventional line coding with equiprobable inputs;
+		4) co-located RIScatter nodes can further leverage total backscatter rate by joint encoding;
+		5) the proposed receiver provides comparable backscatter detection performance than \gls{sic}-based \gls{sr} while significantly reduces the encoding and precoding (and avoids subtraction) costs;
+		6) it also supports fast-switching nodes and allows higher backscatter rate per unit time;
+		7) \gls{pgd} active beamformer enlarges achievable rate region by boosting the receive \gls{snr} and/or widening the energy gap under different reflection states;
+		8) distribution-adaptive backscatter detectors provide higher total backscatter rate than the conventional \gls{ml} detector.
 	\end{subsection}
@@
 	$j$ denotes the imaginary unit.
-	% $\arg(\cdot)$, $\mathrm{rank}(\cdot)$, $\mathrm{tr}(\cdot)$, $\mathrm{diag}(\cdot)$ and $\mathrm{diag}^{-1}(\cdot)$ denote the argument, rank, trace, a square matrix with input vector on main diagonal, and a vector retrieving main diagonal of input square matrix, respectively.
 	$\mathrm{diag}(\cdot)$ returns a square matrix with the input vector on its main diagonal and zeros elsewhere.
@@
 	In particular, the potentially dispersed passive RIScatter nodes ride over an active legacy transmission in a flexible and mutualistic manner, while the practical RIScatter receiver cooperatively decodes both primary and backscatter links under the benefits of backscatter modulation and passive beamforming.
-	% TODO compare BC, SR and IRS
 	\begin{subsection}{RIScatter Nodes}
@@
 			\subfloat[Input Distribution]{
-				\resizebox{0.8\columnwidth}{!}{
+				\resizebox{0.85\columnwidth}{!}{
 					\input{assets/illustration/input_distribution.tex}
@@
 			\\
-			\subfloat[Time Block]{
-				\resizebox{0.8\columnwidth}{!}{
-					\input{assets/illustration/time_block.tex}
-				}
-				\label{fg:time_block}
+			\subfloat[Time Structure]{
+				\resizebox{0.9\columnwidth}{!}{
+					\input{assets/illustration/time_structure.tex}
+				}
+				\label{fg:time_structure}
 			}

### 2022-10-25 main.tex
:pencil: Update scattering principles

@@
 \newacronym{zf}{ZF}{Zero-Forcing}
-\newacronym{mmse}{Minimum Mean-Square-Error}{MMSE}
+\newacronym{mmse}{MMSE}{Minimum Mean-Square-Error}
+\newacronym{fpga}{FPGA}{Field-Programmable Gate Array}
 
@@
 \title{RIScatter: Unifying Backscatter Communications, Symbiotic Radio, and Reconfigurable Intelligent Surface}
-% \title{RIScatter: Unifying\\Backscatter Communications, Symbiotic Radio, and Reconfigurable Intelligent Surface}
 \author{
@@
 % * hardward to modulate using RIS is already available.
-% TODO RIScatter: enhance backscatter signal difference (suppress primary interference) or primary signal strength.
+% * RIScatter: enhance backscatter signal difference (suppress primary interference) or primary signal strength.
 % ? For Backscatter community: why not adaptive channel coding? For RIS community: why not add randomness for modulation?
@@
 \begin{section}{Scattering Principles}
-	Scattering refers to a change of moving direction of particles after colliding with others.
-	An electromagnetic wave is scattered to many angles when an obstruction is placed in its propagation path.
-	In this section, we first introduce two common scatterer categories and review their operation principles, then briefly discuss how scatterers realize backscatter modulation and channel reconfiguration over reflection patterns.
-	\begin{subsection}{Scatterer Categories}
-		In \gls{rf} applications such as \gls{bc}, \gls{sr} and \gls{ris}, the scatterer often includes \emph{variable-load antenna} or \emph{programmable metamaterial} with various reflection patterns \cite{Liang2022}.
-		\begin{subsubsection}{Antenna-Based Scatterer}
+	\gls{rf} wave scattering and reflecting are usually realized by a \emph{variable-load antenna} or \emph{programmable metamaterial} and described by a unified signal model \cite{Liang2022}.
 	A typical antenna-based scatterer consists of an integrated antenna, a load-switching modulator, an energy harvester, and on-chip components (e.g., microcontroller and sensors) \cite{Dobkin2012}.
 	It first receives the impinging signals, then reradiates some back to the space and dissipates the remainder.
-			According to transmission line theory, the scatter-absorb tradeoff depends on the impedance matching of the load and the antenna.
-			For passive scatterers without dedicated energy source, a majority of incident wave is harvested to support node operation and the reradiated part can be relatively weak \cite{Thomas2012a}.
-			At the receiver, the observed signal can be further decomposed into \emph{structural mode} and \emph{antenna mode} components \cite{Hansen1989}.
-			The former consistently contributes to environment multipath and is modelled within channel estimation, while the latter depends on impedance mismatch and can be used for backscatter modulation \cite{Boyer2014} and/or channel reconfiguration \cite{Liang2022}.
-			For antenna-based scatterers, the reflection coefficient at load state $m$ is%
-			\footnote{It corresponds to a linear scatter model where the reflection coefficient is irrelevant to incident electromagnetic field strength.}
-			\begin{equation}
-				\Gamma_m = \frac{Z_m - Z_{\mathrm{A}}^*}{Z_m + Z_{\mathrm{A}}},
-				\label{eq:reflection_pattern_antenna}
-			\end{equation}
-			where $Z_m$ is the load impedance at state $m$ and $Z_{\mathrm{A}}$ is the antenna input impedance.
-		\end{subsubsection}
-		\begin{subsubsection}{Metamaterial-Based Scatterer}
-			A typical metamaterial-based scatterer consists of multiple material layers and a smart controller \cite{Wu2020}.
-			The outer metamaterial layer involves numerous sub-wavelength structural units made of metallic or dielectric materials.
-			The properties of unit cells can be artificially tuned for unconventional effective permittivity (epsilon) and permeability (mu), producing customizable response to the electromagnetic field \cite{Zhou2021}.
-			Using epsilon-negative material (e.g., conducing rods) or mu-negative material (e.g., split-ring resonators), ideal metamaterial-based scatterers can reflect the incident waves at the boundary between free space and metamaterial without receiving them \cite{Huang2021a}.
-			This mainly applies a phase shift on the reflected wave and any propagation into the metamaterial would be evanescent.
-			Depending on the type of metamaterial, its equivalent impedance can be controlled by voltage (for functional materials \cite{Singh2020} and tunable diodes \cite{Costa2021}) or architecture (for resonant elements \cite{Bialkowski2008}).
-			For metamaterial-based scatterers with a discrete impedance set, the reflection coefficient at metamaterial state $m$ is
-			\begin{equation}
-				\Gamma_m = \frac{Z_m - Z_0}{Z_m + Z_0},
-				\label{eq:reflection_pattern_metamaterial}
-			\end{equation}
-			where $Z_m$ is the equivalent impedance of metamaterial unit at state $m$ and $Z_0 = \qty{377}{\ohm}$ is the characteristic impedance of free space.
-		\end{subsubsection}
-	\end{subsection}
-
-	\begin{subsection}{BackCom/SR: Backscatter Modulation}
-		\gls{bc} and \gls{sr} commonly employ antenna-based scatterers as passive information sources.
-		By \emph{frequently switching} between the available states, each scattering node encodes self message over scattered signal and introduces backscatter uncertainty at the receiver.
+	In comparison, a typical metamaterial-based scatterer comprises an outer metamaterial layer of numerous sub-wavelength metallic/dielectric patches with tunable permittivity/permeability, a middle copper plate layer that reflects residual and avoids leakage, an inner circuit board layer that adjusts the amplitude and phase responses of patches, and an integrated microcontroller/\glsentryshort{fpga} that coordinates with the network and controls the circuit \cite{Wu2020}.
+	Ideally, it reflects the incident waves at the air-metamaterial boundary without receiving them and mainly applies a phase shift on the reflected wave.
+	In practice, both kinds of scatterers should have finite reflection states and non-zero reflection loss, and the scatter-absorb tradeoff depends on impedance matching.
+	For a scatter node with $M$ reflection states, the reflection coefficient at state $m \in \mathcal{M} \triangleq \{1,\ldots,M\}$ is
+	\begin{equation}
+		\Gamma_m = \frac{Z_m - Z^*}{Z_m + Z},
+		\label{eq:reflection_coefficient}
+	\end{equation}
+	where $Z_m$ is the antenna load (resp. metamaterial unit) impedance at state $m$ and $Z$ is the antenna input (resp. medium characteristic) impedance.
+	Both backscatter modulation and passive beamforming are realized by manipulating the reflection coefficient.
+	Specifically, \gls{bc}, \gls{ambc} and \gls{sr} employ scatter nodes as information sources that encode by frequently switching between available states.
 	For $M$-ary \gls{qam}, reflection coefficient $\Gamma_m$ maps to the corresponding \emph{complex constellation point $c_m$} by
@@
 	where $\alpha \in \mathbb{I}$ is the amplitude scattering ratio at the direction of interest.
-	\end{subsection}
+
+	% \begin{subsection}{Scatterer Categories}
+	% 	% In \gls{rf} applications such as \gls{bc}, \gls{sr} and \gls{ris}, the scatterer often includes \emph{variable-load antenna} or \emph{programmable metamaterial} with various reflection patterns \cite{Liang2022}.
+	% 	\begin{subsubsection}{Antenna-Based Scatterer}
+	% 		A typical antenna-based scatterer consists of an integrated antenna, a load-switching modulator, an energy harvester, and on-chip components (e.g., microcontroller and sensors) \cite{Dobkin2012}.
+	% 		It first receives the impinging signals, then reradiates some back to the space and dissipates the remainder.
+	% 		According to transmission line theory, the scatter-absorb tradeoff depends on the impedance matching of the load and the antenna.
+	% 		For passive scatterers without dedicated energy source, a majority of incident wave is harvested to support node operation and the reradiated part can be relatively weak \cite{Thomas2012a}.
+	% 		At the receiver, the observed signal can be further decomposed into \emph{structural mode} and \emph{antenna mode} components \cite{Hansen1989}.
+	% 		The former consistently contributes to environment multipath and is modelled within channel estimation, while the latter depends on impedance mismatch and can be used for backscatter modulation \cite{Boyer2014} and/or channel reconfiguration \cite{Liang2022}.
+	% 		For antenna-based scatterers, the reflection coefficient at load state $m$ is%
+	% 		\footnote{It corresponds to a linear scatter model where the reflection coefficient is irrelevant to incident electromagnetic field strength.}
+	% 		\begin{equation}
+	% 			\Gamma_m = \frac{Z_m - Z_{\mathrm{A}}^*}{Z_m + Z_{\mathrm{A}}},
+	% 			\label{eq:reflection_pattern_antenna}
+	% 		\end{equation}
+	% 		where $Z_m$ is the load impedance at state $m$ and $Z_{\mathrm{A}}$ is the antenna input impedance.
+	% 	\end{subsubsection}
+	% 	\begin{subsubsection}{Metamaterial-Based Scatterer}
+	% 		A typical metamaterial-based scatterer consists of multiple material layers and a smart controller \cite{Wu2020}.
+	% 		The outer metamaterial layer involves numerous sub-wavelength structural units made of metallic or dielectric materials.
+	% 		The properties of unit cells can be artificially tuned for unconventional effective permittivity (epsilon) and permeability (mu), producing customizable response to the electromagnetic field \cite{Zhou2021}.
+	% 		Using epsilon-negative material (e.g., conducing rods) or mu-negative material (e.g., split-ring resonators), ideal metamaterial-based scatterers can reflect the incident waves at the boundary between free space and metamaterial without receiving them \cite{Huang2021a}.
+	% 		This mainly applies a phase shift on the reflected wave and any propagation into the metamaterial would be evanescent.
+	% 		Depending on the type of metamaterial, its equivalent impedance can be controlled by voltage (for functional materials \cite{Singh2020} and tunable diodes \cite{Costa2021}) or architecture (for resonant elements \cite{Bialkowski2008}).
+	% 		For metamaterial-based scatterers with a discrete impedance set, the reflection coefficient at metamaterial state $m$ is
+	% 		\begin{equation}
+	% 			\Gamma_m = \frac{Z_m - Z_0}{Z_m + Z_0},
+	% 			\label{eq:reflection_pattern_metamaterial}
+	% 		\end{equation}
+	% 		where $Z_m$ is the equivalent impedance of metamaterial unit at state $m$ and $Z_0 = \qty{377}{\ohm}$ is the characteristic impedance of free space.
+	% 	\end{subsubsection}
+	% \end{subsection}
+
+	% \begin{subsection}{BackCom/SR: Backscatter Modulation}
+	% 	\gls{bc} and \gls{sr} commonly employ antenna-based scatterers as passive information sources.
+	% 	By \emph{frequently switching} between the available states, each scattering node encodes self message over scattered signal and introduces backscatter uncertainty at the receiver.
+	% 	For $M$-ary \gls{qam}, reflection coefficient $\Gamma_m$ maps to the corresponding \emph{complex constellation point $c_m$} by
+	% 	% \cite{Thomas2012a}
+	% 	\begin{equation}
+	% 		\Gamma_m = \alpha \frac{c_m}{\max_{m'} \lvert c_{m'} \rvert},
+	% 		\label{eq:backscatter_modulation}
+	% 	\end{equation}
+	% 	where $\alpha \in \mathbb{I}$ is the amplitude scattering ratio at the direction of interest.
+	% \end{subsection}
 

### 2022-10-26 main.tex
:pencil: Update scattering principles

@@
 	A typical antenna-based scatterer consists of an integrated antenna, a load-switching modulator, an energy harvester, and on-chip components (e.g., microcontroller and sensors) \cite{Dobkin2012}.
-	It first receives the impinging signals, then reradiates some back to the space and dissipates the remainder.
-	In comparison, a typical metamaterial-based scatterer comprises an outer metamaterial layer of numerous sub-wavelength metallic/dielectric patches with tunable permittivity/permeability, a middle copper plate layer that reflects residual and avoids leakage, an inner circuit board layer that adjusts the amplitude and phase responses of patches, and an integrated microcontroller/\glsentryshort{fpga} that coordinates with the network and controls the circuit \cite{Wu2020}.
-	Ideally, it reflects the incident waves at the air-metamaterial boundary without receiving them and mainly applies a phase shift on the reflected wave.
-	In practice, both kinds of scatterers should have finite reflection states and non-zero reflection loss, and the scatter-absorb tradeoff depends on impedance matching.
+	It first receives the impinging signals, then reradiates some back to the space and dissipates the remaining.
+	In comparison, a typical metamaterial-based scatterer comprises an outer metamaterial layer of numerous sub-wavelength metallic/dielectric patches with tunable permittivity/permeability, a middle copper plate layer that reflects residual to avoid leakage, an inner circuit board layer that adjusts the amplitude and phase responses of patches, and an integrated microcontroller/\glsentryshort{fpga} that coordinates with the network and controls the circuit \cite{Wu2020}.
+	Ideally, it reflects the incident waves at the air-metamaterial boundary without receiving them, and mainly applies a phase shift on the reflected wave.
+	In practice, both kinds of scatterers have finite reflection states with non-zero reflection loss, and the scatter-absorb tradeoff depends on impedance matching.
 	For a scatter node with $M$ reflection states, the reflection coefficient at state $m \in \mathcal{M} \triangleq \{1,\ldots,M\}$ is
@@
 	where $Z_m$ is the antenna load (resp. metamaterial unit) impedance at state $m$ and $Z$ is the antenna input (resp. medium characteristic) impedance.
-	Both backscatter modulation and passive beamforming are realized by manipulating the reflection coefficient.
-	Specifically, \gls{bc}, \gls{ambc} and \gls{sr} employ scatter nodes as information sources that encode by frequently switching between available states.
-	For $M$-ary \gls{qam}, reflection coefficient $\Gamma_m$ maps to the corresponding \emph{complex constellation point $c_m$} by
-	% \cite{Thomas2012a}
+	Backscatter modulation and passive beamforming are realized by manipulating the reflection coefficient.
+	Specifically, \gls{bc}, \gls{ambc} and \gls{sr} employ scatter nodes as information sources that encode message by \emph{probabilistically switching} between different states.
+	For $M$-ary \gls{qam}, constellation point $c_m$ maps to reflection coefficient $\Gamma_m$ by \cite{Thomas2012a}
 	\begin{equation}
@@
 	where $\alpha \in \mathbb{I}$ is the amplitude scattering ratio at the direction of interest.
-
-	% \begin{subsection}{Scatterer Categories}
-	% 	% In \gls{rf} applications such as \gls{bc}, \gls{sr} and \gls{ris}, the scatterer often includes \emph{variable-load antenna} or \emph{programmable metamaterial} with various reflection patterns \cite{Liang2022}.
-	% 	\begin{subsubsection}{Antenna-Based Scatterer}
-	% 		A typical antenna-based scatterer consists of an integrated antenna, a load-switching modulator, an energy harvester, and on-chip components (e.g., microcontroller and sensors) \cite{Dobkin2012}.
-	% 		It first receives the impinging signals, then reradiates some back to the space and dissipates the remainder.
-	% 		According to transmission line theory, the scatter-absorb tradeoff depends on the impedance matching of the load and the antenna.
-	% 		For passive scatterers without dedicated energy source, a majority of incident wave is harvested to support node operation and the reradiated part can be relatively weak \cite{Thomas2012a}.
-	% 		At the receiver, the observed signal can be further decomposed into \emph{structural mode} and \emph{antenna mode} components \cite{Hansen1989}.
-	% 		The former consistently contributes to environment multipath and is modelled within channel estimation, while the latter depends on impedance mismatch and can be used for backscatter modulation \cite{Boyer2014} and/or channel reconfiguration \cite{Liang2022}.
-	% 		For antenna-based scatterers, the reflection coefficient at load state $m$ is%
-	% 		\footnote{It corresponds to a linear scatter model where the reflection coefficient is irrelevant to incident electromagnetic field strength.}
-	% 		\begin{equation}
-	% 			\Gamma_m = \frac{Z_m - Z_{\mathrm{A}}^*}{Z_m + Z_{\mathrm{A}}},
-	% 			\label{eq:reflection_pattern_antenna}
-	% 		\end{equation}
-	% 		where $Z_m$ is the load impedance at state $m$ and $Z_{\mathrm{A}}$ is the antenna input impedance.
-	% 	\end{subsubsection}
-	% 	\begin{subsubsection}{Metamaterial-Based Scatterer}
-	% 		A typical metamaterial-based scatterer consists of multiple material layers and a smart controller \cite{Wu2020}.
-	% 		The outer metamaterial layer involves numerous sub-wavelength structural units made of metallic or dielectric materials.
-	% 		The properties of unit cells can be artificially tuned for unconventional effective permittivity (epsilon) and permeability (mu), producing customizable response to the electromagnetic field \cite{Zhou2021}.
-	% 		Using epsilon-negative material (e.g., conducing rods) or mu-negative material (e.g., split-ring resonators), ideal metamaterial-based scatterers can reflect the incident waves at the boundary between free space and metamaterial without receiving them \cite{Huang2021a}.
-	% 		This mainly applies a phase shift on the reflected wave and any propagation into the metamaterial would be evanescent.
-	% 		Depending on the type of metamaterial, its equivalent impedance can be controlled by voltage (for functional materials \cite{Singh2020} and tunable diodes \cite{Costa2021}) or architecture (for resonant elements \cite{Bialkowski2008}).
-	% 		For metamaterial-based scatterers with a discrete impedance set, the reflection coefficient at metamaterial state $m$ is
-	% 		\begin{equation}
-	% 			\Gamma_m = \frac{Z_m - Z_0}{Z_m + Z_0},
-	% 			\label{eq:reflection_pattern_metamaterial}
-	% 		\end{equation}
-	% 		where $Z_m$ is the equivalent impedance of metamaterial unit at state $m$ and $Z_0 = \qty{377}{\ohm}$ is the characteristic impedance of free space.
-	% 	\end{subsubsection}
-	% \end{subsection}
-
-	% \begin{subsection}{BackCom/SR: Backscatter Modulation}
-	% 	\gls{bc} and \gls{sr} commonly employ antenna-based scatterers as passive information sources.
-	% 	By \emph{frequently switching} between the available states, each scattering node encodes self message over scattered signal and introduces backscatter uncertainty at the receiver.
-	% 	For $M$-ary \gls{qam}, reflection coefficient $\Gamma_m$ maps to the corresponding \emph{complex constellation point $c_m$} by
-	% 	% \cite{Thomas2012a}
-	% 	\begin{equation}
-	% 		\Gamma_m = \alpha \frac{c_m}{\max_{m'} \lvert c_{m'} \rvert},
-	% 		\label{eq:backscatter_modulation}
-	% 	\end{equation}
-	% 	where $\alpha \in \mathbb{I}$ is the amplitude scattering ratio at the direction of interest.
-	% \end{subsection}
-
-	\begin{subsection}{RIS: Channel Reconfiguration}
-		\gls{ris} typically involves a planar antenna array or metasurface of numerous metamaterial units as a passive channel reconfigurator.
-		By \emph{adaptively choosing} the reflection pattern, each reflecting element alters the phase of scattered signal for constructive/destructive superposition at the receiver.
-		For each unit with $M$ candidate states, reflection coefficient $\Gamma_m$ maps to the corresponding \emph{phase shift $\theta_m$} by
-		% \cite{Wu2018}
+	In contrast, \gls{ris} employ reflecting elements as channel reconfigurators that enable constructive/destructive signal superposition by \emph{deterministically choosing} the reflection pattern.
+	For a \gls{ris} element with $M$ available states, phase shift $\theta_m$ maps to reflection coefficient $\Gamma_m$ by \cite{Wu2018}
 	\begin{equation}
@@
 	\end{equation}
-		where $\beta_m \in \mathbb{I}$ is the overall amplitude scattering ratio of state $m$.
-		Lossless \gls{ris} assumes $\beta_m=1$ to maximize the available scattering power.
-	\end{subsection}
-
-	\begin{subsection}{Opportunities}
-		We have seen conventional scattering applications as \gls{bc}, \gls{sr} and \gls{ris} using the reflection pattern \eqref{eq:reflection_pattern_antenna}, \eqref{eq:reflection_pattern_metamaterial} for either backscatter modulation \eqref{eq:backscatter_modulation} or passive beamforming \eqref{eq:passive_beamforming}.
-		A natural but critical question is, for a given scatterer with pre-determined reflection pattern set, \emph{can we softly bridge backscatter modulation and passive beamforming by appropriate reflection design?}
-		This question is answered in Section \ref{st:riscatter}.
-	\end{subsection}
+	where $\beta_m \in \mathbb{I}$ is the amplitude scattering ratio of state $m$.\footnote{Most existing \gls{ris} literatures assume lossless reflection $\beta_m=1$, $\forall m$.}
 \end{section}
@@
 \begin{section}{RIScatter}
-	Using shared spectrum, energy and infrastructures, RIScatter is a novel passive communication/assistance protocol that generalizes \gls{bc}, \gls{sr} and \gls{ris} from the perspective of input distribution.
-	In particular, the potentially dispersed passive RIScatter nodes ride over an active legacy transmission in a flexible and mutualistic manner, while the practical RIScatter receiver cooperatively decodes both primary and backscatter links under the benefits of backscatter modulation and passive beamforming.
+	As a generalization of \gls{bc}, \gls{sr} and \gls{ris}, RIScatter is a passive scattering protocol that rides over an active primary link in a flexible and mutualistic manner.
+	Specifically, RIScatter nodes utilize scattered multipath to smoothly transition between backscatter modulation and passive beamforming by \gls{csi}- and weight-based input distribution design, and a tailored cooperative receiver exploits signal properties (i.e., double modulation and symbol period difference) to effectively decode both primary and backscatter links.
+	RIScatter nodes can be implemented by adding an adaptive encoder to off-the-shelf passive backscatter tags with an integrated receiver, and the cascaded \gls{csi} acquisition
+
+	acquisition depends on the geometry of nodes.
+	For co-located RIScatter nodes,
+
+	can be acquired by
+
+	acquisition depends on the geometry of nodes.
+	For co-located
+
+	can be acquired using sequential methods \cite{Bharadia2015,Yang2015b,Guo2019g} or the state-of-the-art parallel approach \cite{Jin2021a}.
+
+	the block diagram, equivalent circuit, and scatter model are illustrated in Fig. \ref{fg:riscatter_node}.
+
+	As shown in Fig. \subref*{fg:block_diagram}, RIScatter nodes can be implemented over readily available passive backscatter devices with energy harvester and information decoder.
+	Its equivalent circuit and scatter model are presented in Fig. \subref*{fg:equivalent_circuit} and \subref*{fg:scatter_model}.
+	When activated by primary transmitter, each node harvests a proportion of the impinging wave for its own operation, decode the embedded coordination information for input distribution control, then applies a potentially random phase shift on the reradiated signal due to backscatter modulation.
+	Energy harvesting and information decoding at passive RIScatter nodes can be realized using conventional power-splitting or time-sharing \gls{swipt} protocols \cite{Clerckx2019} or integrated energy-information receiver with pulse position modulated signal \cite{Kim2021a}.
+	Besides, relevant \gls{csi} can be acquired using either traditional sequential methods \cite{Bharadia2015,Yang2015b,Guo2019g} or the state-of-the-art parallel approach \cite{Jin2021a}.
+	In the following context, we assume perfect primary-total-backscatter coordination and perfect channel estimation for all links.
+
 	\begin{subsection}{RIScatter Nodes}
@@
 
-		As shown in Fig. \subref*{fg:block_diagram}, RIScatter nodes can be implemented over readily available passive backscatter devices with energy harvester and information decoder.
-		Its equivalent circuit and scatter model are presented in Fig. \subref*{fg:equivalent_circuit} and \subref*{fg:scatter_model}.
-		When activated by primary transmitter, each node harvests a proportion of the impinging wave for its own operation, decode the embedded coordination information for input distribution control, then applies a potentially random phase shift on the reradiated signal due to backscatter modulation.
-		Energy harvesting and information decoding at passive RIScatter nodes can be realized using conventional power-splitting or time-sharing \gls{swipt} protocols \cite{Clerckx2019} or integrated energy-information receiver with pulse position modulated signal \cite{Kim2021a}.
-		Besides, relevant \gls{csi} can be acquired using either traditional sequential methods \cite{Bharadia2015,Yang2015b,Guo2019g} or the state-of-the-art parallel approach \cite{Jin2021a}.
-		In the following context, we assume perfect primary-total-backscatter coordination and perfect channel estimation for all links.
 		\begin{figure*}[!t]

### 2022-10-27 main.tex
:pencil: Add RIScatter concept

@@
 			}
-			\label{fg:scatter_comparison}
+			\label{fg:scatter_illustration}
 		\end{figure}
@@
 		\emph{First,} we propose RIScatter nodes that adapt the reflection state distribution of passive scatter devices based on \gls{csi} and link weights, in order to flexibly transition between backscatter modulation and passive beamforming.
-		Scattering sources of \gls{bc}/\gls{sr} and reflecting elements of \gls{ris} can be regarded as special cases with uniform and degenerate input distributions, respectively.
+		Scattering sources of \gls{bc}/\gls{ambc}/\gls{sr} and reflecting elements of \gls{ris} can be regarded as special cases with uniform and degenerate input distributions, respectively.
 		On the contrary, adaptive RIScatter encoding boils down to deterministic \gls{ris} when primary link is prioritized, and achieves higher backscatter rate than conventional line coding when backscatter link is prioritized.
@@
 \begin{section}{RIScatter}
-	As a generalization of \gls{bc}, \gls{sr} and \gls{ris}, RIScatter is a passive scattering protocol that rides over an active primary link in a flexible and mutualistic manner.
-	Specifically, RIScatter nodes utilize scattered multipath to smoothly transition between backscatter modulation and passive beamforming by \gls{csi}- and weight-based input distribution design, and a tailored cooperative receiver exploits signal properties (i.e., double modulation and symbol period difference) to effectively decode both primary and backscatter links.
-	RIScatter nodes can be implemented by adding an adaptive encoder to off-the-shelf passive backscatter tags with an integrated receiver, and the cascaded \gls{csi} acquisition
-
-	acquisition depends on the geometry of nodes.
-	For co-located RIScatter nodes,
-
-	can be acquired by
-
-	acquisition depends on the geometry of nodes.
-	For co-located
-
-	can be acquired using sequential methods \cite{Bharadia2015,Yang2015b,Guo2019g} or the state-of-the-art parallel approach \cite{Jin2021a}.
-
-	the block diagram, equivalent circuit, and scatter model are illustrated in Fig. \ref{fg:riscatter_node}.
-
-	As shown in Fig. \subref*{fg:block_diagram}, RIScatter nodes can be implemented over readily available passive backscatter devices with energy harvester and information decoder.
-	Its equivalent circuit and scatter model are presented in Fig. \subref*{fg:equivalent_circuit} and \subref*{fg:scatter_model}.
-	When activated by primary transmitter, each node harvests a proportion of the impinging wave for its own operation, decode the embedded coordination information for input distribution control, then applies a potentially random phase shift on the reradiated signal due to backscatter modulation.
-	Energy harvesting and information decoding at passive RIScatter nodes can be realized using conventional power-splitting or time-sharing \gls{swipt} protocols \cite{Clerckx2019} or integrated energy-information receiver with pulse position modulated signal \cite{Kim2021a}.
-	Besides, relevant \gls{csi} can be acquired using either traditional sequential methods \cite{Bharadia2015,Yang2015b,Guo2019g} or the state-of-the-art parallel approach \cite{Jin2021a}.
-	In the following context, we assume perfect primary-total-backscatter coordination and perfect channel estimation for all links.
-
-	\begin{subsection}{RIScatter Nodes}
-		Based on link priority and \gls{csi}, RIScatter nodes adapt the \emph{state input probability distribution} of antenna-based scatterers to unify backscatter modulation and passive beamforming.
-		Conventional line-coded \gls{bc}/\gls{sr} nodes (e.g., EPC Gen 2 UHF \gls{rfid} using FM0) and deterministic \gls{ris} elements can be viewed as its extreme cases, where the input distribution boils down to equiprobable and degenerate, respectively.
+	\begin{subsection}{Concepts}
+		% As a generalization of \gls{bc}, \gls{sr} and \gls{ris}, RIScatter is a passive scattering protocol that cooperatives with an active primary link in a flexible and mutualistic manner.
+		% Specifically, RIScatter nodes utilizes \gls{csi}- and weight-based input distribution design to smoothly transition between backscatter modulation and passive beamforming, and a tailored cooperative receiver exploits signal properties (i.e., double modulation and symbol period difference) to effectively decode both primary and backscatter links.
+		% RIScatter nodes can be implemented by adding an integrated receiver \cite{Kim2021a} and adaptive encoder \cite{He2020e} to off-the-shelf passive backscatter tags, and relevant \gls{csi} can be acquired by existing low-power estimation techniques.
+		% For dispersed RIScatter nodes, the cascaded transmitter-node-receiver channels can be estimated by sequential \cite{Bharadia2015,Yang2015b,Guo2019g} or parallel approaches \cite{Jin2021a} originally proposed for \gls{bc}.
+		% For co-located RIScatter nodes, channel estimation can be simplified by group-based \cite{Zheng2019} and hierarchical \cite{You2019} trainings originally proposed for \gls{ris}.
+		% The block diagram, equivalent circuit, and scatter model of a RIScatter node are illustrated in Fig.
+\ref{fg:riscatter_node}, while the input distribution and time structure comparison of scattering applications are shown in Fig.
+\ref{fg:scatter_comparison}.
+		% Instead of using fully random or fully deterministic reflection pattern over time, each RIScatter node semi-randomly chooses the reflection state for each backscatter block with the guidance of input probability distribution $P(\Gamma_m)$ at state $m$.
+		% Such an adaptive backscatter coding boils down to degenerate distribution of \gls{ris} when primary link is prioritized, and outperforms line coding with equiprobable inputs (e.g., FM0 for \gls{rfid}) when backscatter link is prioritized.
+		% Besides, joint encoding over multiple co-located RIScatter nodes can further improve the total backscatter rate.
+
+		As a generalization of \gls{bc}, \gls{sr} and \gls{ris}, RIScatter is a passive scattering protocol that cooperatives with an active primary link in a flexible and mutualistic manner.
+		RIScatter nodes utilizes \gls{csi}- and weight-based input distribution design to smoothly transition between backscatter modulation and passive beamforming.
+		It can be implemented by adding an integrated receiver \cite{Kim2021a} and adaptive encoder \cite{He2020e} to off-the-shelf passive backscatter tags.
+		The block diagram, equivalent circuit, and scatter model of a RIScatter node are illustrated in Fig.
+\ref{fg:riscatter_node}, while the input distribution and time structure comparison of scattering applications are shown in Fig.
+\ref{fg:scatter_comparison}.
+		Instead of using fully random or fully deterministic reflection pattern over time, each RIScatter node semi-randomly chooses the reflection state for each backscatter block with the guidance of input probability distribution $P(\Gamma_m)$ at state $m$.
+		Such an adaptive backscatter coding boils down to degenerate distribution of \gls{ris} when primary link is prioritized, and outperforms line coding with equiprobable inputs (e.g., FM0 for \gls{rfid}) when backscatter link is prioritized.
+		Besides, joint encoding over multiple co-located RIScatter nodes can further improve the total backscatter rate.
+		Relevant \gls{csi} can be acquired by existing low-power estimation techniques.
+		For dispersed RIScatter nodes, the cascaded transmitter-node-receiver channels can be estimated by sequential \cite{Bharadia2015,Yang2015b,Guo2019g} or parallel approaches \cite{Jin2021a} originally proposed for \gls{bc}.
+		For co-located RIScatter nodes, the estimation can be simplified by group-based \cite{Zheng2019} and hierarchical \cite{You2019} trainings originally proposed for \gls{ris}.
+
+		% , and a tailored cooperative receiver exploits signal properties (i.e., double modulation and symbol period difference) to effectively decode both primary and backscatter links.
+		% RIScatter nodes can be implemented by adding an integrated receiver \cite{Kim2021a} and adaptive encoder \cite{He2020e} to off-the-shelf passive backscatter tags, and relevant \gls{csi} can be acquired by existing low-power estimation techniques.
+		% For dispersed RIScatter nodes, the cascaded transmitter-node-receiver channels can be estimated by sequential \cite{Bharadia2015,Yang2015b,Guo2019g} or parallel approaches \cite{Jin2021a} originally proposed for \gls{bc}.
+		% For co-located RIScatter nodes, channel estimation can be simplified by group-based \cite{Zheng2019} and hierarchical \cite{You2019} trainings originally proposed for \gls{ris}.
+
+		\begin{figure*}[!t]
+			\centering
+			\subfloat[Block Diagram]{
+				\resizebox{0.32\linewidth}{!}{
+					\input{assets/illustration/block_diagram.tex}
+				}
+				\label{fg:block_diagram}
+			}
+			\subfloat[Equivalent Circuit]{
+				\resizebox{0.37\linewidth}{!}{
+					\input{assets/illustration/equivalent_circuit.tex}
+				}
+				\label{fg:equivalent_circuit}
+			}
+			\subfloat[Scatter Model]{
+				\resizebox{0.28\linewidth}{!}{
+					\input{assets/illustration/scatter_model.tex}
+				}
+				\label{fg:scatter_model}
+			}
+			\caption{
+			Block diagram, equivalent circuit, and scatter model of a RIScatter node.
+			The solid and dashed vectors represent signal and energy flows.
+			The scattering antenna behaves as a constant power source, where the voltage $V_0$ and current $I_0$ are introduced by incident electric field $\vec{E}_{\mathrm{I}}$ and magnetic field $\vec{H}_{\mathrm{I}}$ \cite{Huang2021}.
+			}
+			\label{fg:riscatter_node}
+		\end{figure*}
+
 		\begin{figure}[!t]
@@
 			}
-			\label{fg:riscatter_distribution}
+			\label{fg:scatter_comparison}
+		\end{figure}
+		% The block diagram, equivalent circuit, and scatter model of a RIScatter node are illustrated in Fig.
+\ref{fg:riscatter_node}, while the input distribution and time structure comparison of scattering applications are shown in Fig.
+\ref{fg:scatter_comparison}.
+		% Instead of using fully random or fully deterministic reflection pattern over time, each RIScatter node semi-randomly chooses the reflection state for each backscatter block with the guidance of input probability distribution $P(\Gamma_m)$ at state $m$.
+		% Such an adaptive backscatter coding boils down to degenerate distribution of \gls{ris} when primary link is prioritized, and outperforms line coding with equiprobable inputs (e.g., FM0 for \gls{rfid}) when backscatter link is prioritized.
+		% Besides, joint encoding over multiple co-located RIScatter nodes can further improve the total backscatter rate.
+
+		\begin{remark}
+			Metascatter involves a symbiotic MAC where the primary and backscatter symbols of different duration are mixed by Multiplication Coding (MC) instead of Superposition Coding (SC).
+For each node, the reflection coefficient not only encodes the backscatter message, but also influences the equivalent primary channel (4).
+To accommodate such signal characteristics, novel receiving strategy apart from SIC is desired to better utilize the reflection pattern and boost the primary-backscatter tradeoff.
+		\end{remark}
+		Since each passive RIScatter node directly modulates its own message over the legacy signal, it involves a \emph{double modulation} where the primary and backscatter symbols are superimposed by \emph{multiplication coding} instead of superposition coding.
+		Besides, the backscatter symbol period is typically longer than primary due to the load switching speed constraint.
+		Those facts imply \emph{backscatter detection} under primary uncertainty can be viewed as part of \emph{primary channel training}.
+		Hence, we propose a practical RIScatter receiver that semi-coherently decodes RIScatter nodes from the received energy per backscatter block, re-encodes for their reflection patterns, retrieves primary equivalent channel as if dynamic passive beamforming, then coherently decodes the primary link under the enhanced multipath.
+		\begin{figure}[!t]
+			\centering
+			\resizebox{0.9\columnwidth}{!}{
+				\input{assets/illustration/energy_distribution.tex}
+			}
+			\caption{
+				\gls{pdf} of total received energy per backscatter block, conditioned on different input state hypotheses.
+				$t$ and $\mathcal{R}$ denote the energy decision thresholds and regions, respectively.
+			}
+			\label{fg:energy_distribution}
 		\end{figure}
 		As illustrated in Fig.
-\ref{fg:riscatter_distribution}, instead of always using fully random or deterministic reflection pattern over time, each RIScatter node can \emph{flexibly adjust} its input distribution to balance information encoding and channel reconfiguration.
+\ref{fg:energy_distribution}, the total received energy per backscatter block is a random variable that follows different distributions conditioned on different input state hypotheses.
+		Compared with conventional joint \gls{ml} and \gls{sic} from stronger primary link to weaker backscatter links, RIScatter receiver not only preserves the benefits of backscatter modulation and passive beamforming, but also enjoys much lower computational and operational complexities.
+	\end{subsection}
+
+	\begin{subsection}{RIScatter Nodes}
+		Based on link priority and \gls{csi}, RIScatter nodes adapt the \emph{state input probability distribution} of antenna-based scatterers to unify backscatter modulation and passive beamforming.
+		Conventional line-coded \gls{bc}/\gls{sr} nodes (e.g., EPC Gen 2 UHF \gls{rfid} using FM0) and deterministic \gls{ris} elements can be viewed as its extreme cases, where the input distribution boils down to equiprobable and degenerate, respectively.
+
+		As illustrated in Fig.
+\ref{fg:scatter_comparison}, instead of always using fully random or deterministic reflection pattern over time, each RIScatter node can \emph{flexibly adjust} its input distribution to balance information encoding and channel reconfiguration.
 		That is, it semi-randomly select the reflection state per backscatter symbol block under the guidance of input probability $P(\Gamma_m)$ for state $m$.
@@
 
-		\begin{figure*}[!t]
-			\centering
-			\subfloat[Block Diagram]{
-				\resizebox{0.32\linewidth}{!}{
-					\input{assets/illustration/block_diagram.tex}
-				}
-				\label{fg:block_diagram}
-			}
-			\subfloat[Equivalent Circuit]{
-				\resizebox{0.37\linewidth}{!}{
-					\input{assets/illustration/equivalent_circuit.tex}
-				}
-				\label{fg:equivalent_circuit}
-			}
-			\subfloat[Scatter Model]{
-				\resizebox{0.28\linewidth}{!}{
-					\input{assets/illustration/scatter_model.tex}
-				}
-				\label{fg:scatter_model}
-			}
-			\caption{
-			Block diagram, equivalent circuit, and scatter model of a RIScatter node.
-			The solid and dashed vectors represent signal and energy flows.
-			The scattering antenna behaves as a constant power source, where the voltage $V_0$ and current $I_0$ are introduced by incident electric field $\vec{E}_{\mathrm{I}}$ and magnetic field $\vec{H}_{\mathrm{I}}$ \cite{Huang2021}.
-			}
-			\label{fg:riscatter_node}
-		\end{figure*}
 	\end{subsection}

### 2022-10-27 main.tex
:pencil: Add remark on SIC

@@
 	For a typical setup, we characterize the achievable primary-(total-)backscatter rate region by optimizing input distribution at the nodes, active beamforming at the \gls{ap}, and backscatter detector at the user.
-	Simulation results demonstrate RIScatter nodes can exploit the additional propagation paths to smoothly transition between backscatter modulation and passive beamforming via smart input distribution design, and the proposed receiver significantly reduces the decoding complexity and effectively accommodates the double modulation and signal difference in scatter-based cooperative networks.
+	Simulation results demonstrate RIScatter nodes can exploit the additional propagation paths to smoothly transition between backscatter modulation and passive beamforming via smart input distribution design, and the proposed receiver significantly reduces the decoding complexity and effectively accommodates the double modulation and signal difference in scatter-based multiple access.
 \end{abstract}
@@
 		Joint \gls{ml} decoding can achieve the best error performance but comes with prohibitive computational complexity especially for sources with high-order constellation \cite{Yang2018,Liang2020,Zhang2022}.
-		One special property of scatter-based cooperative networks is the backscatter signal strength is significantly weaker than primary due to the double fading effect.
+		One special property of scatter-based multiple access is the backscatter signal strength is significantly weaker than primary due to the double fading effect.
 		It motivated \cite{Long2020a,Liang2020,Guo2019b,Ding2020,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Yang2018,Han2021,Zhang2022} to view \gls{sr} as a multiplicative \gls{noma} and perform sequential primary-backscatter decoding based on \gls{sic}.
@@
 		If the former is much higher (i.e., commensal \gls{sr}), the average primary achievable rate under noncoherent detection would asymptotically approach its coherent counterpart \cite{Long2020a}, and both links may be decoded in an interference-free manner.
-		However, the assumption of very large backscatter-over-primary symbol period ratio may not hold in practice \footnote{For example, Wi-Fi sampling rate is \qty{20}{\MHz} while \gls{rfid} load switching speed varies between \num{100}s of \unit{\kHz} to \num{10}s of \unit{\MHz} \cite{Torres2021}, corresponding to a typical symbol period ratio between \num{1} and \num{100}.}, and such a \gls{sic}-based sequential decoding requires re-encoding, precoding, and subtraction at each primary symbol block with a time-domain \gls{mrc}, which can be operation-intensive and \gls{csi}-sensitive.
+		However, the assumption of very large backscatter-over-primary symbol period ratio $N$ may not hold in practice \footnote{For example, Wi-Fi sampling rate is \qty{20}{\MHz} while \gls{rfid} load switching speed varies between \num{100}s of \unit{\kHz} to \num{10}s of \unit{\MHz} \cite{Torres2021}, corresponding to a typical $N$ between \num{1} and \num{100}.}, and such a \gls{sic}-based sequential decoding requires re-encoding, precoding, and subtraction at each primary symbol block with a time-domain \gls{mrc}, which can be operation-intensive and \gls{csi}-sensitive.
 		Another open issue for \gls{bc} and \gls{sr} is efficient node multiple access.
@@
 		Those \gls{ris}-empowered \gls{bc}/\gls{sr} designs involve advanced hardware architecture and high optimization complexity.
-		Besides, all relevant literatures considered either Gaussian codebook \cite{Guo2019b,Ding2020,Long2020a,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Hu2021b} or finite equiprobable inputs \cite{Yang2018,Liang2020,Han2021,Zhang2022,Liu2019d,Bereyhi2020,Xu2020b,Zhang2021d,Hua2022,Basar2020,Ma2020a,Yuan2021,Hu2021a} for backscatter information sources.
+		Besides, all relevant literatures consider either Gaussian codebook \cite{Guo2019b,Ding2020,Long2020a,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Hu2021b} or finite equiprobable inputs \cite{Yang2018,Liang2020,Han2021,Zhang2022,Liu2019d,Bereyhi2020,Xu2020b,Zhang2021d,Hua2022,Basar2020,Ma2020a,Yuan2021,Hu2021a} for backscatter information sources.
 		The former is impractical for passive backscatter devices while the latter does not fully exploit \gls{csi} and signal characteristics.
@@
 
-		\emph{Second,} we propose a practical receiver that accommodates the double modulation and signal difference in scatter-based cooperative networks.
+		\emph{Second,} we propose a practical receiver that accommodates the double modulation and signal difference in scatter-based multiple access.
 		Since the primary and backscatter messages are superimposed by multiplication coding and the backscatter symbol is typically longer than primary, the scattered signals from RIScatter nodes can be treated as multipath components during primary decoding, and the primary message can be viewed as a spreading code during backscatter decoding.
@@
 \ref{fg:scatter_comparison}.
-		Instead of using fully random or fully deterministic reflection pattern over time, each RIScatter node semi-randomly chooses the reflection state for each backscatter block with the guidance of input probability distribution $P(\Gamma_m)$ at state $m$.
-		Such an adaptive backscatter coding boils down to degenerate distribution of \gls{ris} when primary link is prioritized, and outperforms line coding with equiprobable inputs (e.g., FM0 for \gls{rfid}) when backscatter link is prioritized.
-		Besides, joint encoding over multiple co-located RIScatter nodes can further improve the total backscatter rate.
+		Instead of using fully random or fully deterministic reflection pattern over time, each RIScatter node semi-randomly chooses the reflection state for each backscatter block with guidance of input probability distribution $P(\Gamma_m)$ at state $m$.
+		Such an adaptive backscatter coding boils down to degenerate distribution of \gls{ris} when primary link is prioritized, and outperforms conventional line coding with equiprobable inputs (e.g., FM0 for \gls{rfid}) when backscatter link is prioritized.
+		Besides, joint encoding over multiple co-located RIScatter nodes can further boost the total backscatter rate.
 		Relevant \gls{csi} can be acquired by existing low-power estimation techniques.
@@
 			\caption{
-				Input probability distribution and time block structure of \gls{bc}, \gls{sr}, \gls{ris}, and RIScatter.
-				$T_s$ and $T_c$ respectively denote the primary and backscatter symbol period.
-				Within channel coherence time, RIScatter nodes semi-randomly select reflection state for each backscatter symbol block under the guidance of input probability distribution.
+				Input distribution and time structure of \gls{bc}, \gls{ambc}, \gls{sr}, \gls{ris}, and RIScatter.
+				``PB'' means primary block and ``BB'' means backscatter block.
 			}
@@
 		\begin{remark}
-			Metascatter involves a symbiotic MAC where the primary and backscatter symbols of different duration are mixed by Multiplication Coding (MC) instead of Superposition Coding (SC).
+			Scatter-based multiple access involves a double modulation where the primary and backscatter symbols of different length are superimposed by multiplication coding.
+			The reflection pattern not only encodes the backscatter message, but also affects the primary equivalent channel.
+			% Hence, \gls{sic}, which was originally proposed for superposition coding,
+			It suggests backscatter detection under primary uncertainty can be viewed as part of primary channel training, and novel decoding strategies apart from \gls{sic}
+			\footnote{
+				Recall that \gls{sic} was proposed to achieve the capacity vertices for \gls{mac} with superposition coding.
+				For scatter-based multiple access, \gls{sic} not only fails to exploit the double modulation effect, but also requires $N$ re-encoding, precoding and subtraction steps with a time-domain \gls{mrc} during each backscatter symbol block.
+			}
+			is desired to fully exploit signal characteristics and improve the primary-backscatter tradeoff.
+
+			% Since scatter nodes directly modulate their message over the legacy signal, it involves a \emph{double modulation} where the primary and backscatter symbols are superimposed by \emph{multiplication coding} instead of superposition coding.
+			% Besides, the backscatter symbol period is typically longer than primary due to the load switching speed constraint.
+			% Those facts imply \emph{backscatter detection} under primary uncertainty can be viewed as part of \emph{primary channel training}.
+
+			% Metascatter involves a symbiotic MAC where the primary and backscatter symbols of different duration are mixed by Multiplication Coding (MC) instead of Superposition Coding (SC).
 For each node, the reflection coefficient not only encodes the backscatter message, but also influences the equivalent primary channel (4).

### 2022-10-27 main.tex
:pencil: Update RIScatter concept

@@
 		Since the primary and backscatter messages are superimposed by multiplication coding and the backscatter symbol is typically longer than primary, the scattered signals from RIScatter nodes can be treated as multipath components during primary decoding, and the primary message can be viewed as a spreading code during backscatter decoding.
-		Conventional sequential primary-backscatter decoder eliminates primary interference by \gls{sic} at each primary block, while our sequential backscatter-primary detector semi-coherently decodes RIScatter nodes from the received energy, re-encodes to recover exact reflection patterns, and models the deterministic multipath in the primary equivalent channel as dynamic passive beamforming at each backscatter block.
+		Conventional sequential primary-backscatter decoder eliminates primary interference by \gls{sic} at each primary block, while our sequential backscatter-primary detector semi-coherently decodes RIScatter nodes from the received energy, re-encodes to recover exact reflection patterns, and models the deterministic multipath within primary equivalent channel as dynamic passive beamforming at each backscatter block.
 		It enables backscatter modulation and dynamic passive beamforming at much lower operational complexity, and is suitable for scatter nodes with various load switching speeds.
@@
 	\begin{subsection}{Concepts}
-		% As a generalization of \gls{bc}, \gls{sr} and \gls{ris}, RIScatter is a passive scattering protocol that cooperatives with an active primary link in a flexible and mutualistic manner.
-		% Specifically, RIScatter nodes utilizes \gls{csi}- and weight-based input distribution design to smoothly transition between backscatter modulation and passive beamforming, and a tailored cooperative receiver exploits signal properties (i.e., double modulation and symbol period difference) to effectively decode both primary and backscatter links.
-		% RIScatter nodes can be implemented by adding an integrated receiver \cite{Kim2021a} and adaptive encoder \cite{He2020e} to off-the-shelf passive backscatter tags, and relevant \gls{csi} can be acquired by existing low-power estimation techniques.
-		% For dispersed RIScatter nodes, the cascaded transmitter-node-receiver channels can be estimated by sequential \cite{Bharadia2015,Yang2015b,Guo2019g} or parallel approaches \cite{Jin2021a} originally proposed for \gls{bc}.
-		% For co-located RIScatter nodes, channel estimation can be simplified by group-based \cite{Zheng2019} and hierarchical \cite{You2019} trainings originally proposed for \gls{ris}.
-		% The block diagram, equivalent circuit, and scatter model of a RIScatter node are illustrated in Fig.
-\ref{fg:riscatter_node}, while the input distribution and time structure comparison of scattering applications are shown in Fig.
-\ref{fg:scatter_comparison}.
-		% Instead of using fully random or fully deterministic reflection pattern over time, each RIScatter node semi-randomly chooses the reflection state for each backscatter block with the guidance of input probability distribution $P(\Gamma_m)$ at state $m$.
-		% Such an adaptive backscatter coding boils down to degenerate distribution of \gls{ris} when primary link is prioritized, and outperforms line coding with equiprobable inputs (e.g., FM0 for \gls{rfid}) when backscatter link is prioritized.
-		% Besides, joint encoding over multiple co-located RIScatter nodes can further improve the total backscatter rate.
-
-		As a generalization of \gls{bc}, \gls{sr} and \gls{ris}, RIScatter is a passive scattering protocol that cooperatives with an active primary link in a flexible and mutualistic manner.
+		As a generalization of \gls{bc}, \gls{sr} and \gls{ris}, RIScatter is a passive scattering protocol that coexists with an active primary link in a flexible and mutualistic manner.
 		RIScatter nodes utilizes \gls{csi}- and weight-based input distribution design to smoothly transition between backscatter modulation and passive beamforming.
@@
 \ref{fg:scatter_comparison}.
+		\begin{figure*}[!t]
+			\centering
+			\subfloat[Block Diagram]{
+				\resizebox{0.32\linewidth}{!}{
+					\input{assets/illustration/block_diagram.tex}
+				}
+				\label{fg:block_diagram}
+			}
+			\subfloat[Equivalent Circuit]{
+				\resizebox{0.37\linewidth}{!}{
+					\input{assets/illustration/equivalent_circuit.tex}
+				}
+				\label{fg:equivalent_circuit}
+			}
+			\subfloat[Scatter Model]{
+				\resizebox{0.28\linewidth}{!}{
+					\input{assets/illustration/scatter_model.tex}
+				}
+				\label{fg:scatter_model}
+			}
+			\caption{
+			Block diagram, equivalent circuit, and scatter model of a RIScatter node.
+			The solid and dashed vectors represent signal and energy flows.
+			The scattering antenna behaves as a constant power source, where the voltage $V_0$ and current $I_0$ are introduced by incident electric field $\vec{E}_{\mathrm{I}}$ and magnetic field $\vec{H}_{\mathrm{I}}$ \cite{Huang2021}.
+			}
+			\label{fg:riscatter_node}
+		\end{figure*}
+		\begin{figure}[!t]
+			\centering
+			\subfloat[Input Distribution]{
+				\resizebox{0.85\columnwidth}{!}{
+					\input{assets/illustration/input_distribution.tex}
+				}
+				\label{fg:input_distribution}
+			}
+			\\
+			\subfloat[Time Structure]{
+				\resizebox{0.9\columnwidth}{!}{
+					\input{assets/illustration/time_structure.tex}
+				}
+				\label{fg:time_structure}
+			}
+			\caption{
+				Input distribution and time structure of \gls{bc}, \gls{ambc}, \gls{sr}, \gls{ris}, and RIScatter.
+				``PB'' means primary block and ``BB'' means backscatter block.
+			}
+			\label{fg:scatter_comparison}
+		\end{figure}
 		Instead of using fully random or fully deterministic reflection pattern over time, each RIScatter node semi-randomly chooses the reflection state for each backscatter block with guidance of input probability distribution $P(\Gamma_m)$ at state $m$.
@@
 
-		% , and a tailored cooperative receiver exploits signal properties (i.e., double modulation and symbol period difference) to effectively decode both primary and backscatter links.
-		% RIScatter nodes can be implemented by adding an integrated receiver \cite{Kim2021a} and adaptive encoder \cite{He2020e} to off-the-shelf passive backscatter tags, and relevant \gls{csi} can be acquired by existing low-power estimation techniques.
-		% For dispersed RIScatter nodes, the cascaded transmitter-node-receiver channels can be estimated by sequential \cite{Bharadia2015,Yang2015b,Guo2019g} or parallel approaches \cite{Jin2021a} originally proposed for \gls{bc}.
-		% For co-located RIScatter nodes, channel estimation can be simplified by group-based \cite{Zheng2019} and hierarchical \cite{You2019} trainings originally proposed for \gls{ris}.
-
-		\begin{figure*}[!t]
-			\centering
-			\subfloat[Block Diagram]{
-				\resizebox{0.32\linewidth}{!}{
-					\input{assets/illustration/block_diagram.tex}
-				}
-				\label{fg:block_diagram}
-			}
-			\subfloat[Equivalent Circuit]{
-				\resizebox{0.37\linewidth}{!}{
-					\input{assets/illustration/equivalent_circuit.tex}
-				}
-				\label{fg:equivalent_circuit}
-			}
-			\subfloat[Scatter Model]{
-				\resizebox{0.28\linewidth}{!}{
-					\input{assets/illustration/scatter_model.tex}
-				}
-				\label{fg:scatter_model}
-			}
-			\caption{
-			Block diagram, equivalent circuit, and scatter model of a RIScatter node.
-			The solid and dashed vectors represent signal and energy flows.
-			The scattering antenna behaves as a constant power source, where the voltage $V_0$ and current $I_0$ are introduced by incident electric field $\vec{E}_{\mathrm{I}}$ and magnetic field $\vec{H}_{\mathrm{I}}$ \cite{Huang2021}.
-			}
-			\label{fg:riscatter_node}
-		\end{figure*}
-
-		\begin{figure}[!t]
-			\centering
-			\subfloat[Input Distribution]{
-				\resizebox{0.85\columnwidth}{!}{
-					\input{assets/illustration/input_distribution.tex}
-				}
-				\label{fg:input_distribution}
-			}
-			\\
-			\subfloat[Time Structure]{
-				\resizebox{0.9\columnwidth}{!}{
-					\input{assets/illustration/time_structure.tex}
-				}
-				\label{fg:time_structure}
-			}
-			\caption{
-				Input distribution and time structure of \gls{bc}, \gls{ambc}, \gls{sr}, \gls{ris}, and RIScatter.
-				``PB'' means primary block and ``BB'' means backscatter block.
-			}
-			\label{fg:scatter_comparison}
-		\end{figure}
-		% The block diagram, equivalent circuit, and scatter model of a RIScatter node are illustrated in Fig.
-\ref{fg:riscatter_node}, while the input distribution and time structure comparison of scattering applications are shown in Fig.
-\ref{fg:scatter_comparison}.
-		% Instead of using fully random or fully deterministic reflection pattern over time, each RIScatter node semi-randomly chooses the reflection state for each backscatter block with the guidance of input probability distribution $P(\Gamma_m)$ at state $m$.
-		% Such an adaptive backscatter coding boils down to degenerate distribution of \gls{ris} when primary link is prioritized, and outperforms line coding with equiprobable inputs (e.g., FM0 for \gls{rfid}) when backscatter link is prioritized.
-		% Besides, joint encoding over multiple co-located RIScatter nodes can further improve the total backscatter rate.
-
 		\begin{remark}
@@
 			The reflection pattern not only encodes the backscatter message, but also affects the primary equivalent channel.
-			% Hence, \gls{sic}, which was originally proposed for superposition coding,
-			It suggests backscatter detection under primary uncertainty can be viewed as part of primary channel training, and novel decoding strategies apart from \gls{sic}
+			Therefore, backscatter detection under primary uncertainty can be viewed as part of primary channel training, and novel decoding strategies apart from \gls{sic}
 			\footnote{
 				Recall that \gls{sic} was proposed to achieve the capacity vertices for \gls{mac} with superposition coding.
-				For scatter-based multiple access, \gls{sic} not only fails to exploit the double modulation effect, but also requires $N$ re-encoding, precoding and subtraction steps with a time-domain \gls{mrc} during each backscatter symbol block.
-			}
-			is desired to fully exploit signal characteristics and improve the primary-backscatter tradeoff.
-
-			% Since scatter nodes directly modulate their message over the legacy signal, it involves a \emph{double modulation} where the primary and backscatter symbols are superimposed by \emph{multiplication coding} instead of superposition coding.
-			% Besides, the backscatter symbol period is typically longer than primary due to the load switching speed constraint.
-			% Those facts imply \emph{backscatter detection} under primary uncertainty can be viewed as part of \emph{primary channel training}.
-
-			% Metascatter involves a symbiotic MAC where the primary and backscatter symbols of different duration are mixed by Multiplication Coding (MC) instead of Superposition Coding (SC).
-For each node, the reflection coefficient not only encodes the backscatter message, but also influences the equivalent primary channel (4).
-To accommodate such signal characteristics, novel receiving strategy apart from SIC is desired to better utilize the reflection pattern and boost the primary-backscatter tradeoff.
+				For scatter-based multiple access, \gls{sic} not only fails to utilize the double modulation, but also requires $N$ re-encoding, precoding and subtraction with a time-domain \gls{mrc} during each backscatter block.
+			}
+			is desired for RIScatter.
 		\end{remark}
-		Since each passive RIScatter node directly modulates its own message over the legacy signal, it involves a \emph{double modulation} where the primary and backscatter symbols are superimposed by \emph{multiplication coding} instead of superposition coding.
-		Besides, the backscatter symbol period is typically longer than primary due to the load switching speed constraint.
-		Those facts imply \emph{backscatter detection} under primary uncertainty can be viewed as part of \emph{primary channel training}.
-		Hence, we propose a practical RIScatter receiver that semi-coherently decodes RIScatter nodes from the received energy per backscatter block, re-encodes for their reflection patterns, retrieves primary equivalent channel as if dynamic passive beamforming, then coherently decodes the primary link under the enhanced multipath.
+
+		Next, we propose a cooperative receiver that effectively exploit signal characteristics (i.e., double modulation and symbol period difference) to reduce the decoding complexity and improve the primary-backscatter tradeoff.
+		As illustrated in Fig.
+\ref{fg:energy_distribution}, conditioned on different reflection state hypotheses, the accumulated receive energy per backscatter block follows Gamma distribution with different scale parameters \cite{Qian2017b}.
 		\begin{figure}[!t]
@@
 			\caption{
-				\gls{pdf} of total received energy per backscatter block, conditioned on different input state hypotheses.
-				$t$ and $\mathcal{R}$ denote the energy decision thresholds and regions, respectively.
+				\gls{pdf} of accumulated receive energy per backscatter block conditioned on different reflection state hypotheses.
+				$z$, $t$, $\mathcal{H}$ and $\mathcal{R}$ denote the accumulated receive energy, decision threshold, reflection state hypothesis, and decision regions, respectively.
 			}
@@
 		\end{figure}
-		As illustrated in Fig.
-\ref{fg:energy_distribution}, the total received energy per backscatter block is a random variable that follows different distributions conditioned on different input state hypotheses.
-		Compared with conventional joint \gls{ml} and \gls{sic} from stronger primary link to weaker backscatter links, RIScatter receiver not only preserves the benefits of backscatter modulation and passive beamforming, but also enjoys much lower computational and operational complexities.
-	\end{subsection}
-
-	\begin{subsection}{RIScatter Nodes}
-		Based on link priority and \gls{csi}, RIScatter nodes adapt the \emph{state input probability distribution} of antenna-based scatterers to unify backscatter modulation and passive beamforming.
-		Conventional line-coded \gls{bc}/\gls{sr} nodes (e.g., EPC Gen 2 UHF \gls{rfid} using FM0) and deterministic \gls{ris} elements can be viewed as its extreme cases, where the input distribution boils down to equiprobable and degenerate, respectively.
-
-		As illustrated in Fig.
-\ref{fg:scatter_comparison}, instead of always using fully random or deterministic reflection pattern over time, each RIScatter node can \emph{flexibly adjust} its input distribution to balance information encoding and channel reconfiguration.
-		That is, it semi-randomly select the reflection state per backscatter symbol block under the guidance of input probability $P(\Gamma_m)$ for state $m$.
-		Such an adaptive backscatter channel coding coincides with \gls{ris} when primary link is absolutely prioritized, and outperforms the conventional equiprobable line-coded \gls{bc}/\gls{sr} when backscatter link is absolutely prioritized.
-		Besides, the dispersed characteristics of RIScatter nodes (and legacy users) avoids the development optimization and allows uniformly good performance for both links.
-
-	\end{subsection}
-
-	\begin{subsection}{RIScatter Receiver}
-		Since each passive RIScatter node directly modulates its own message over the legacy signal, it involves a \emph{double modulation} where the primary and backscatter symbols are superimposed by \emph{multiplication coding} instead of superposition coding.
-		Besides, the backscatter symbol period is typically longer than primary due to the load switching speed constraint.
-		Those facts imply \emph{backscatter detection} under primary uncertainty can be viewed as part of \emph{primary channel training}.
-		Hence, we propose a practical RIScatter receiver that semi-coherently decodes RIScatter nodes from the received energy per backscatter block, re-encodes for their reflection patterns, retrieves primary equivalent channel as if dynamic passive beamforming, then coherently decodes the primary link under the enhanced multipath.
-		\begin{figure}[!t]
-			\centering
-			\resizebox{0.9\columnwidth}{!}{
-				\input{assets/illustration/energy_distribution.tex}
-			}
-			\caption{
-				\gls{pdf} of total received energy per backscatter block, conditioned on different input state hypotheses.
-				$t$ and $\mathcal{R}$ denote the energy decision thresholds and regions, respectively.
-			}
-			\label{fg:energy_distribution}
-		\end{figure}
-		As illustrated in Fig.
-\ref{fg:energy_distribution}, the total received energy per backscatter block is a random variable that follows different distributions conditioned on different input state hypotheses.
-		Compared with conventional joint \gls{ml} and \gls{sic} from stronger primary link to weaker backscatter links, RIScatter receiver not only preserves the benefits of backscatter modulation and passive beamforming, but also enjoys much lower computational and operational complexities.
+		Hence, the receiver can semi-coherently (in the presence of primary uncertainty) decode node messages from the accumulated receive energy, re-encode to recover actual reflection patterns, and model the deterministic multipath within primary equivalent channel.
+		It enables backscatter modulation and dynamic passive beamforming using only one energy level comparison, re-encoding and precoding for each backscatter block (instead of primary block as \gls{sic}), and is suitable for arbitrary primary and backscatter symbol periods.
 	\end{subsection}

### 2022-10-28 assets/illustration/time_structure.tex
:bento: Update time structure

@@
 	\foreach \x in {0,...,3}{
-			\draw[blue,fill=blue!30!white,postaction={pattern=horizontal lines},pattern color=.] (0.5*\x,3) rectangle ++(0.5,0.5);
+			\draw[blue,fill=blue!30!white,postaction={pattern=horizontal lines},pattern color=.] (0.5*\x,3) rectangle ++(0.5,0.25);
 		}
 	\foreach \x in {4,...,7}{
-			\draw[blue,fill=blue!30!white,postaction={pattern=north west lines},pattern color=.] (0.5*\x,3) rectangle ++(0.5,0.5);
+			\draw[blue,fill=blue!30!white,postaction={pattern=north west lines},pattern color=.] (0.5*\x,3) rectangle ++(0.5,0.25);
 		}
 	\foreach \x in {8,...,11}{
-			\draw[blue,fill=blue!30!white,postaction={pattern=vertical lines},pattern color=.] (0.5*\x,3) rectangle ++(0.5,0.5);
+			\draw[blue,fill=blue!30!white,postaction={pattern=vertical lines},pattern color=.] (0.5*\x,3) rectangle ++(0.5,0.25);
 		}
 	\foreach \x in {12,...,15}{
-			\draw[blue,fill=blue!30!white,postaction={pattern=north east lines},pattern color=.] (0.5*\x,3) rectangle ++(0.5,0.5);
+			\draw[blue,fill=blue!30!white,postaction={pattern=north east lines},pattern color=.] (0.5*\x,3) rectangle ++(0.5,0.25);
 		}
@@
 	\foreach \x in {0,...,15}{
-			\draw[red,fill=red!30!white,postaction={pattern=north west lines},pattern color=.] (0.5*\x,2) rectangle ++(0.5,0.5);
+			\draw[red,fill=red!30!white,postaction={pattern=north west lines},pattern color=.] (0.5*\x,2) rectangle ++(0.5,0.25);
 		}
@@
 	\foreach \x in {0,...,1}{
-			\draw[brown,fill=brown!30!white,postaction={pattern=horizontal lines},pattern color=.] (0.5*\x,1) rectangle ++(0.5,0.5);
+			\draw[brown,fill=brown!30!white,postaction={pattern=horizontal lines},pattern color=.] (0.5*\x,1) rectangle ++(0.5,0.25);
 		}
 	\foreach \x in {2,...,7}{
-			\draw[brown,fill=brown!30!white,postaction={pattern=north west lines},pattern color=.] (0.5*\x,1) rectangle ++(0.5,0.5);
+			\draw[brown,fill=brown!30!white,postaction={pattern=north west lines},pattern color=.] (0.5*\x,1) rectangle ++(0.5,0.25);
 		}
 	\foreach \x in {8,...,11}{
-			\draw[brown,fill=brown!30!white,postaction={pattern=vertical lines},pattern color=.] (0.5*\x,1) rectangle ++(0.5,0.5);
+			\draw[brown,fill=brown!30!white,postaction={pattern=vertical lines},pattern color=.] (0.5*\x,1) rectangle ++(0.5,0.25);
 		}
 	\foreach \x in {12,...,15}{
-			\draw[brown,fill=brown!30!white,postaction={pattern=north west lines},pattern color=.] (0.5*\x,1) rectangle ++(0.5,0.5);
+			\draw[brown,fill=brown!30!white,postaction={pattern=north west lines},pattern color=.] (0.5*\x,1) rectangle ++(0.5,0.25);
 		}
@@
 	\foreach \x in {1,...,7}{
-			\draw[dotted] (\x,0.5) -- (\x,4);
+			\draw[dotted] (\x,1) -- (\x,3.75);
 		}
-	\draw[latex-latex] (0,3.7) -- (0.5,3.7) node[above,midway,yshift=1]{PB};
-	\draw[latex-latex] (0,4.3) -- (1,4.3) node[above,midway,yshift=1]{BB};
-	\draw[latex-latex] (0,4.9) -- (8,4.9) node[above,midway,yshift=1]{Channel Block};
+	\draw[latex-latex] (0,3.5) -- (0.5,3.5) node[above,midway,yshift=1]{PB};
+	\draw[latex-latex] (0,4.1) -- (1,4.1) node[above,midway,yshift=1]{BB};
+	\draw[latex-latex] (0,4.7) -- (8,4.7) node[above,midway,yshift=1]{Channel Block};
 
-	\node at (-2,3.25) {BackCom/AmBC/SR};
-	\node at (-2,2.25) {RIS};
-	\node at (-2,1.25) {RIScatter};
+	\node at (-2,3.125) {BackCom/AmBC/SR};
+	\node at (-2,2.125) {RIS};
+	\node at (-2,1.125) {RIScatter};
 

### 2022-10-28 main.tex
:pencil: Update system model and achievable rates

@@
 	For a typical setup, we characterize the achievable primary-(total-)backscatter rate region by optimizing input distribution at the nodes, active beamforming at the \gls{ap}, and backscatter detector at the user.
-	Simulation results demonstrate RIScatter nodes can exploit the additional propagation paths to smoothly transition between backscatter modulation and passive beamforming via smart input distribution design, and the proposed receiver significantly reduces the decoding complexity and effectively accommodates the double modulation and signal difference in scatter-based multiple access.
+	Simulation results demonstrate RIScatter nodes can exploit the additional propagation paths to smoothly transition between backscatter modulation and passive beamforming via smart input distribution design, and the proposed receiver significantly reduces the decoding complexity and effectively accommodates the double modulation and signal difference in active-passive coexisting network.
 \end{abstract}
@@
 		Joint \gls{ml} decoding can achieve the best error performance but comes with prohibitive computational complexity especially for sources with high-order constellation \cite{Yang2018,Liang2020,Zhang2022}.
-		One special property of scatter-based multiple access is the backscatter signal strength is significantly weaker than primary due to the double fading effect.
+		One special property of active-passive coexisting network is the backscatter signal strength is significantly weaker than primary due to the double fading effect.
 		It motivated \cite{Long2020a,Liang2020,Guo2019b,Ding2020,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Yang2018,Han2021,Zhang2022} to view \gls{sr} as a multiplicative \gls{noma} and perform sequential primary-backscatter decoding based on \gls{sic}.
@@
 
-		\emph{Second,} we propose a practical receiver that accommodates the double modulation and signal difference in scatter-based multiple access.
+		\emph{Second,} we propose a practical receiver that accommodates the double modulation and signal difference in active-passive coexisting network.
 		Since the primary and backscatter messages are superimposed by multiplication coding and the backscatter symbol is typically longer than primary, the scattered signals from RIScatter nodes can be treated as multipath components during primary decoding, and the primary message can be viewed as a spreading code during backscatter decoding.
@@
 		We provide primary and total backscatter rate analyses and characterize the achievable rate region by optimizing input distribution at RIScatter nodes, active beamforming at the \gls{ap}, and backscatter decision regions at the user.
-		Since the original problem is highly non-convex, we decouple it into individual subproblems and propose a suboptimal \gls{bcd} algorithm, where the \gls{kkt} input distribution is numerically evaluated by limit of sequences, the active beamforming is iteratively updated by \gls{pgd} accelerated by \gls{bls}, and the decision regions are refined by existing sequential quantization methods for \gls{dmc}.
+		Since the original problem is highly non-convex, we decouple it into individual subproblems and propose a suboptimal \gls{bcd} algorithm, where the \gls{kkt} input distribution is numerically evaluated by limit of sequences, the active beamforming is iteratively updated by \gls{pgd} accelerated by \gls{bls}, and the decision regions are refined by existing sequential quantization methods for \gls{dmtc}.
 		This is the first paper to reveal the importance of input distribution and decision region designs in relevant literatures.
@@
 	\begin{subsection}{Concepts}
-		As a generalization of \gls{bc}, \gls{sr} and \gls{ris}, RIScatter is a passive scattering protocol that coexists with an active primary link in a flexible and mutualistic manner.
-		RIScatter nodes utilizes \gls{csi}- and weight-based input distribution design to smoothly transition between backscatter modulation and passive beamforming.
+		As a generalization of \gls{bc}, \gls{sr} and \gls{ris}, RIScatter is a passive scattering protocol that coexists with an active primary system in a flexible and mutualistic manner.
+		RIScatter nodes leverage \gls{csi}- and weight-based input distribution design to smoothly transition between backscatter modulation and passive beamforming.
 		It can be implemented by adding an integrated receiver \cite{Kim2021a} and adaptive encoder \cite{He2020e} to off-the-shelf passive backscatter tags.
@@
 			\footnote{
-				Recall that \gls{sic} was proposed to achieve the capacity vertices for \gls{mac} with superposition coding.
-				For scatter-based multiple access, \gls{sic} not only fails to utilize the double modulation, but also requires $N$ re-encoding, precoding and subtraction with a time-domain \gls{mrc} during each backscatter block.
+				Superposition coding and \gls{sic} was originally proposed to achieve the capacity vertices of Gaussian \gls{mac}.
+				For active-passive coexisting network, \gls{sic} not only fails to utilize the multiplication coding/double modulation, but also requires $N$ re-encoding, precoding and subtraction with a time-domain \gls{mrc} during each backscatter block.
 			}
@@
 		Hence, the receiver can semi-coherently (in the presence of primary uncertainty) decode node messages from the accumulated receive energy, re-encode to recover actual reflection patterns, and model the deterministic multipath within primary equivalent channel.
-		It enables backscatter modulation and dynamic passive beamforming using only one energy level comparison, re-encoding and precoding for each backscatter block (instead of primary block as \gls{sic}), and is suitable for arbitrary primary and backscatter symbol periods.
+		It enables simultaneous backscatter modulation and dynamic passive beamforming by only one energy level comparison, re-encoding and precoding for each backscatter block (instead of primary block), and is suitable for arbitrary primary sampling rate and backscatter switching speed.
 	\end{subsection}
@@
 		\end{figure}
-		To demonstrate the advantages of RIScatter, we consider a single-user multi-node \gls{miso} RIScatter system as shown in Fig. \ref{fg:riscatter_network}.
-		In the primary active point-to-point system, a $Q$-antenna \gls{ap} transmits to a single-antenna user assisted by $K$ nearby single-antenna RIScatter nodes with $M$ reflection states.
-		In the secondary backscatter \gls{mac} system, the \gls{ap} serves as the carrier emitter, the distributed RIScatter nodes modulate information over reradiated \gls{rf} signals, and the user decodes their messages.
-		For simplicity, we consider a quasi-static block fading model where channels remain constant within coherence block and vary independently between consecutive blocks.
-		Due to the physical constraints of load switching speed, we assume the backscatter over primary symbol period ratio is an integer $N \gg 1$.
+		As shown in Fig.
+\ref{fg:riscatter_network}, we consider an active-passive coexisting network where a $Q$-antenna \gls{ap} serves a single-antenna user and $K$ nearby dispersed and/or co-located single-antenna RIScatter nodes each with $M$ available states.
+		In the primary point-to-point system, the \gls{ap} transmits information to the user over the multipath channel enhanced by RIScatter nodes.
+		In the backscatter \gls{mac} system, the \gls{ap} and user become carrier emitter and backscatter reader, and the RIScatter nodes modulate over scattered \gls{rf} signals.
+		For simplicity, we consider a quasi-static block fading model where channels remain constant within each block and vary independently between consecutive blocks, and assume the backscatter-over-primary symbol period ratio $N$ is an integer.
 		We also omit the signal reflected by two or more times and ignore the propagation time difference of different paths.
-
-		Denote the \gls{ap}-user direct channel as $\boldsymbol{h}_{\mathrm{D}}^H \in \mathbb{C}^{1 \times Q}$, the \gls{ap}-node $k \in \mathcal{K} \triangleq \{1,\ldots,K\}$ forward channel as $\boldsymbol{h}_{\mathrm{F},k}^H \in \mathbb{C}^{1 \times Q}$, the node $k$-user backward channel as $h_{\mathrm{B},k}$, and the cascaded channel via tag $k$ as $\boldsymbol{h}_{\mathrm{C},k}^H \triangleq h_{\mathrm{B},k} \boldsymbol{h}_{\mathrm{F},k}^H \in \mathbb{C}^{1 \times Q}$.
-		Let $x_{\mathcal{K}} \triangleq (x_1,\ldots,x_K)$ be the backscatter symbol tuple of all RIScatter nodes.
-		Without loss of generality, we consider one specific backscatter block (i.e., $N$ primary blocks) in the following context.
-		Due to double modulation, the primary equivalent channel is a function of \emph{coded} backscatter symbols\footnote{Expression \eqref{eq:equivalent_channel_bc} is often used in \gls{bc} literatures while expression \eqref{eq:equivalent_channel_ris} is commonly observed in \gls{ris} literatures.}
-		% \begin{equation}
-		% 	\boldsymbol{h}_{\mathrm{E}}^H(x_{\mathcal{K}}) \overset{\text{(a)}}{=} \boldsymbol{h}_{\mathrm{D}}^H + \sum_{k} \alpha_k \boldsymbol{h}_{\mathrm{C},k}^H x_k \overset{\text{(b)}}{=} \boldsymbol{h}_{\mathrm{D}}^H + \boldsymbol{x}^H \mathrm{diag}(\boldsymbol{\alpha}) \boldsymbol{H}_{\mathrm{C}},
-		% 	\label{eq:equivalent_channel}
-		% \end{equation}
+		Denote the \gls{ap}-user direct channel as $\boldsymbol{h}_{\mathrm{D}}^H \in \mathbb{C}^{1 \times Q}$, the \gls{ap}-node $k \in \mathcal{K} \triangleq \{1,\ldots,K\}$ forward channel as $\boldsymbol{h}_{\mathrm{F},k}^H \in \mathbb{C}^{1 \times Q}$, the node $k$-user backward channel as $h_{\mathrm{B},k}$, and the cascaded \gls{ap}-node $k$-user channel as $\boldsymbol{h}_{\mathrm{C},k}^H \triangleq h_{\mathrm{B},k} \boldsymbol{h}_{\mathrm{F},k}^H \in \mathbb{C}^{1 \times Q}$.
+		Let $x_k \in \mathcal{X} \triangleq \{c_1,\ldots,c_M\}$ be the coded backscatter symbol of node $k$ and $x_{\mathcal{K}} \triangleq (x_1,\ldots,x_K)$ be the backscatter symbol tuple of all nodes.
+		Without loss of generality, we consider one backscatter block (i.e., $N$ primary blocks) in the following context.
+		Due to double modulation, the primary equivalent channel is a function of backscatter symbol tuple\footnote{\eqref{eq:equivalent_channel_bc} and \eqref{eq:equivalent_channel_ris} are often used in \gls{bc} and \gls{ris} literatures, respectively.}
 		\begin{subequations}
+			\label{eq:equivalent_channel}
 			\begin{align}
@@
 			\end{align}
-			\label{eq:equivalent_channel}
 		\end{subequations}
-		where $\alpha_k \in \mathbb{I}$ is the amplitude scattering ratio of RIScatter node $k$, $x_k \in \mathcal{X} \triangleq \{c_1,\ldots,c_M\}$ is the \emph{coded} backscatter symbol of node $k$, $\boldsymbol{\alpha} \triangleq [\alpha_1,\ldots,\alpha_K]^T \in \mathbb{I}^{K}$, $\boldsymbol{x} \triangleq [x_1,\ldots,x_K]^H \in \mathcal{X}^{K}$, and $\boldsymbol{H}_{\mathrm{C}} \triangleq [\boldsymbol{h}_{\mathrm{C},1},\ldots,\boldsymbol{h}_{\mathrm{C},K}]^H \in \mathbb{C}^{K \times Q}$.
+		where $\alpha_k \in \mathbb{I}$ is the amplitude scattering ratio of node $k$, $\boldsymbol{\alpha} \triangleq [\alpha_1,\ldots,\alpha_K]^T \in \mathbb{I}^{K}$, $\boldsymbol{x} \triangleq [x_1,\ldots,x_K]^H \in \mathcal{X}^{K}$, and $\boldsymbol{H}_{\mathrm{C}} \triangleq [\boldsymbol{h}_{\mathrm{C},1},\ldots,\boldsymbol{h}_{\mathrm{C},K}]^H \in \mathbb{C}^{K \times Q}$.
 		The signal received by the user at primary block $n \in \mathcal{N} \triangleq \{1,\ldots,N\}$ is
@@
 		\end{equation}
-		where $s \sim \mathcal{CN}(0,1)$ is the primary symbol, $v \sim \mathcal{CN}(0,\sigma_v^2)$ is the \gls{awgn}, and $\boldsymbol{w} \in \mathbb{C}^{Q}$ is the active beamforming vector subject to average transmit power constraint $\lVert \boldsymbol{w} \rVert^2 \le P$.
-		Denote $m_k \in \mathcal{M} \triangleq \{1,\ldots,M\}$ as the reflection state index of node $k$, and $m_{\mathcal{K}} \triangleq (m_1,\ldots,m_K)$ as the state index tuple of all nodes.
-		Conditioned on backscatter index tuple $m_{\mathcal{K}}$, the received signal at each primary block follows \gls{cscg} distribution $\mathcal{CN}(0,\sigma_{m_{\mathcal{K}}}^2)$, where
+		where $\boldsymbol{w} \in \mathbb{C}^{Q}$ is the active beamformer satisfying average transmit power constraint $\lVert \boldsymbol{w} \rVert^2 \le P$, $s \sim \mathcal{CN}(0,1)$ is the primary symbol, and $v \sim \mathcal{CN}(0,\sigma_v^2)$ is the \gls{awgn} with average power $\sigma_v^2$.
+		Let $m_k \in \mathcal{M} \triangleq \{1,\ldots,M\}$ be the reflection state index of node $k$, $m_{\mathcal{K}} \triangleq (m_1,\ldots,m_K)$ be the state index tuple of all nodes, $x_{m_k}$ be the backscatter symbol of node $k$ indexed by $m_k$, and $x_{m_\mathcal{K}}$ be the backscatter symbol tuple indexed by $m_{\mathcal{K}}$.\footnote{Please note $x_k$ and $x_{\mathcal{K}}$ are discrete random variable and tuple, while $x_{m_k}$ and $x_{m_{\mathcal{K}}}$ are their values indexed by $m_k$ and $m_{\mathcal{K}}$.}
+		Conditioned on $m_{\mathcal{K}}$, the receive signal at each primary block follows \gls{cscg} distribution $\mathcal{CN}(0,\sigma_{m_{\mathcal{K}}}^2)$, where
 		\begin{equation}
@@
 		\end{equation}
-		is the received variance and $x_{m_\mathcal{K}}$ is the backscatter symbol tuple associated with $m_{\mathcal{K}}$.
-		For node $k$, let $x_{m_k}$ be the backscatter symbol associated with index $m_k$.%
-		\footnote{
-			Please note $x_k$ and $x_{\mathcal{K}}$ are random variable and tuple, while $x_{m_k}$ and $x_{m_{\mathcal{K}}}$ are their instances of index $m_k$ and $m_{\mathcal{K}}$.
-		}
-		Besides, we define the total received energy per backscatter block as $z=\sum_{n \in \mathcal{N}} \bigl\lvert y[n] \bigr\rvert^2$.
-		Since $z$ is the sum of $N$ \gls{iid} exponential variables, its \gls{pdf} conditioned on $m_{\mathcal{K}}$ follows Gamma distribution
+		is the received variance.
+		Let $z=\sum_{n} \bigl\lvert y[n] \bigr\rvert^2$ be the accumulated receive energy per backscatter block.
+		Since $z$ is the sum of $N$ \gls{iid} exponential variables, its conditional \gls{pdf} follows Gamma distribution
 		\begin{equation}
@@
 		where $\mathcal{H}_{m_{\mathcal{K}}}$ denotes hypothesis $m_{\mathcal{K}}$.
-		As illustrated in Fig. \ref{fg:energy_distribution}, the RIScatter receiver divides the received energy space into disjoint decision regions associated with those hypotheses.
-		For example, if the total received energy during a backscatter block falls within region $\mathcal{R}_{m_{\mathcal{K}}}$, then the detector output would be $x_{m_{\mathcal{K}}}$.
+		At the receiver, the energy space is divided into disjoint decision regions associated with different hypotheses, as illustrated in Fig. \ref{fg:energy_distribution}.
 		\begin{remark}
-			Interestingly, the capacity-achieving decision design for \gls{dmtc} remains under-investigated, and some attempts were made for a single source with binary inputs \cite{Qian2019b,Nguyen2021b}.
-			For non-binary inputs with arbitrary distribution, the optimal decision region for each letter can be non-convex (i.e., with non-adjacent partitions) and the optimal number of thresholds is still unknown \cite{Nguyen2018,Nguyen2021}.
+			The capacity-achieving decision region design for \gls{dmtc} with non-binary inputs in arbitrary distribution remains an open issue.
+			It was proved deterministic detector can be rate-optimal, but non-convex decision regions (i.e., comprise non-adjacent partitions) are generally required and the optimal number of thresholds is still unknown \cite{Nguyen2018,Nguyen2021}.
+			Hence, we limit the backscatter energy detector to convex deterministic decision regions and consider sequential threshold design in the following context.
 		\end{remark}
-		Like most existing literatures, we limit the scope of this paper to convex decision regions and consider sequential decision thresholds design therein.
-		For the ease of notations, we define a general bijective function from backscatter index tuple $m_{\mathcal{K}}$ to integer $l \in \mathcal{L} \triangleq \{1,\ldots,L \triangleq M^K\}$, where $\{\sigma_l^2\}_{l \in \mathcal{L}}$ are sorted in an ascending order.
+
+		For the ease of notations, we map the state index tuple $m_{\mathcal{K}}$ to the corresponding index $l \in \mathcal{L} \triangleq \{1,\ldots,L \triangleq M^K\}$, where $\sigma_1^2,\ldots,\sigma_L^2$ is an ascending sequence.
 		Both notations are used interchangeably in the following context.
-		As such, the convex decision region of backscatter tuple $l$ can be written as
-		\begin{equation}
-			\mathcal{R}_{l} \triangleq [t_{l-1},t_l), \quad 0 \le t_{l-1} \le t_l.
-		\end{equation}
-		Once the decision threshold vector $\boldsymbol{t} \triangleq [t_0,\ldots,t_L]^T \in \mathbb{R}_+^{(L+1)}$ is determined, we can formulate a \gls{dmtmac} with transition probability from input $x_{m_{\mathcal{K}}}$ to output $\hat{x}_{m_{\mathcal{K}}'}$
+		As such, the decision region of backscatter symbol tuple $l$ can be written as
+		\begin{equation}
+			\mathcal{R}_{l} \triangleq [t_{l-1},t_l), \quad 0 \le t_{l-1} \le t_l,
+		\end{equation}
+		where $t_l$ is the energy decision threshold between hypotheses $\mathcal{H}_{l}$ and $\mathcal{H}_{l+1}$.
+		For a given decision threshold vector $\boldsymbol{t} \triangleq [t_0,\ldots,t_L]^T \in \mathbb{R}_+^{(L+1)}$, we can formulate a \gls{dmtmac} with transition probability from input $x_{m_{\mathcal{K}}}$ to output $\hat{x}_{m_{\mathcal{K}}'}$ given by
 		\begin{equation}
@@
 		\end{equation}
-		then perform backscatter channel coding on top of it.
+		over which adaptive input distribution design and backscatter channel coding can be performed.
 		\label{st:system_model}
@@
 
-	\begin{subsection}{Information Theory}
-		Denote the input probability distribution vector of node $k$ as $\boldsymbol{p}_k \triangleq [P_k(c_1),\ldots,P_k(c_M)]^T \in \mathbb{I}^{M}$, and the probability of state $m_k$ as $P_k(x_{m_k})$.
-		With independent encoding at all nodes, the probability of backscatter symbol tuple $x_{m_{\mathcal{K}}}$ is
+	\begin{subsection}{Achievable Rates}
+		Let $P_k(x_{m_k})$ be the input probability of node $k$ at state $m_k$, and $\boldsymbol{p}_k \triangleq [P_k(c_1),\ldots,P_k(c_M)]^T \in \mathbb{I}^{M}$ be the input distribution vector.
+		% Denote the input probability of node $k$ at state $m_k$ as $P_k(x_{m_k})$, and the input distribution vector as $\boldsymbol{p}_k \triangleq [P_k(c_1),\ldots,P_k(c_M)]^T \in \mathbb{I}^{M}$.
+		For dispersed nodes with independent encoding, the probability of backscatter symbol tuple $x_{m_{\mathcal{K}}}$ is
 		\begin{equation}
@@
 		\end{equation}
-
-		Similar to \cite{Rezaeian2004}, we define the backscatter information function between input symbol tuple instance $x_{m_{\mathcal{K}}}$ and output symbol tuple variable $\hat{x}_{\mathcal{K}}$ as
+		Following \cite{Rezaeian2004}, we define the backscatter information function between input symbol tuple instance $x_{m_{\mathcal{K}}}$ and output symbol tuple variable $\hat{x}_{\mathcal{K}}$ as
 		\begin{equation}
@@
 		\end{equation}
-		where $P_{\mathcal{K}}(\hat{x}_{m_{\mathcal{K}}'}) = \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}})$ is the probability of channel output tuple $\hat{x}_{m_{\mathcal{K}}'}$.
-		We also define the backscatter marginal information of letter $x_{m_k}$ of node $k$ as
+		where $P_{\mathcal{K}}(\hat{x}_{m_{\mathcal{K}}'}) = \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}})$ is the probability of output tuple $\hat{x}_{m_{\mathcal{K}}'}$.
+		We also define the backscatter marginal information of letter $x_{m_k}$ as
 		\begin{equation}
@@
 		where $P_{\mathcal{K} \setminus \{k\}}(x_{m_{\mathcal{K} \setminus \{k\}}}) = \prod_{q \in \mathcal{K} \setminus \{k\}} P_{q}(x_{m_{q}})$.
-		The backscatter mutual information can be written as
+		Hence, the backscatter mutual information can be written as
 		\begin{equation}
@@
 		\end{equation}
-		Once backscatter messages of all nodes are successfully decoded, we can re-code for backscatter symbol tuple $x_{\mathcal{K}}$, recover their reflection patterns by \eqref{eq:backscatter_modulation}, and retrieve the primary equivalent channel by \eqref{eq:equivalent_channel}.
-		Moreover, we define the primary information function conditioned on backscatter symbol tuple $x_{m_{\mathcal{K}}}$ as
+
+		Once node messages are successfully decoded, we can re-encode for exact backscatter symbol tuple $x_{\mathcal{K}}$, recover their reflection patterns by \eqref{eq:backscatter_modulation}, and retrieve the primary equivalent channel by \eqref{eq:equivalent_channel}.
+		Therefore, the primary information function conditioned on backscatter symbol tuple $x_{m_{\mathcal{K}}}$ is
 		\begin{equation}
@@
 		\end{equation}
-		the primary marginal information conditioned on letter $x_{m_k}$ of node $k$ as
+		the primary marginal information of letter $x_{m_k}$ is
+		% the primary marginal information conditioned on letter $x_{m_k}$ of node $k$ as
 		\begin{equation}
@@
 		\end{equation}
-		and the primary ergodic mutual information as
+		and the primary ergodic mutual information is
 		\begin{equation}
@@
 
-		With a slight abuse of notation, we define the corresponding weighted sum information function, marginal information, and mutual information respectively as
+		With a slight abuse of notation, we define the corresponding weighted sum information function, marginal information, and mutual information as
 		\begin{align}
@@
 		\end{align}
-		where $\rho \in \mathbb{I}$ is the relative priority of the primary link.
+		where $\rho \in \mathbb{I}$ is the weight of the primary link.
+		We notice the primary ergodic rate \eqref{eq:primary_mutual_information} depends on the input distribution and active beamforming, while the total backscatter rate depends on the input distribution and \gls{dmtmac} \eqref{eq:dmtmac} that relates to active beamforming and decision thresholds.
 		\label{st:information_theory}
@@
 \begin{section}{Rate-Region Characterization}
-	We notice the primary ergodic mutual information \eqref{eq:primary_mutual_information} relates to input distribution and active beamforming, while the total backscatter mutual information \eqref{eq:backscatter_mutual_information} depends explicitly on input distribution and implicitly on active beamforming and decision thresholds via backscatter \gls{dmtmac} \eqref{eq:dmtmac}.
-	To characterize the achievable primary-total-backscatter rate region of the proposed RIScatter system, we aim to maximize the weighted sum mutual information with respect to input distribution $\{\boldsymbol{p}_k\}_{k \in \mathcal{K}}$, active beamforming $\boldsymbol{w}$, and decision thresholds $\boldsymbol{t}$ as
+	To characterize the achievable primary-(total-)backscatter rate region for the RIScatter system in Fig.
+\ref{fg:riscatter_network}, we aim to maximize the weighted sum rate with respect to input distribution $\{\boldsymbol{p}_k\}_{k \in \mathcal{K}}$, active beamforming $\boldsymbol{w}$, and decision thresholds $\boldsymbol{t}$ by
 	\begin{maxi!}
@@
 
-	Problem \eqref{op:weighted_sum_rate} introduces adaptive backscatter channel coding over conventional \gls{bc}/\gls{sr} designs.
-	% Problem \eqref{op:weighted_sum_rate} generalizes conventional \gls{bc}/\gls{sr} by allowing adaptive backscatter channel coding.
-	On the other hand, it also generalizes the discrete \gls{ris} phase shift selection problem by relaxing the feasible domain from the vertices of $M$-dimensional probability simplex to the simplex itself.
+	Problem \eqref{op:weighted_sum_rate} generalizes conventional \gls{bc}/\gls{sr} by allowing \gls{csi}- and weight-adaptive input distribution and detection region design.
+	It also generalizes the discrete \gls{ris} phase shift selection by allowing stochastic reflection (i.e., relaxing the feasible domain from the vertices of $M$-dimensional probability simplex to the simplex itself).
 	Since problem \eqref{op:weighted_sum_rate} is highly non-convex, we propose a \gls{bcd} algorithm that iteratively updates $\{\boldsymbol{p}_k\}_{k \in \mathcal{K}}$, $\boldsymbol{w}$ and $\boldsymbol{t}$ until convergence.
@@
 		\end{maxi!}
-		which involves the coupled term $\prod_{k \in \mathcal{K}} P_k(x_{m_k})$ and is non-convex when $K > 1$.
-		Following \cite{Rezaeian2004}, we first recast \gls{kkt} conditions of problem \eqref{op:input_distribution} to their equivalent forms, then propose a numerical method that guarantees those conditions on convergence of sequences.
+		which is convex when $K=1$ or joint encoding\footnote{Joint encoding formulates an equivalent source of $M^K$ valid codewords, such that one can directly design $P_{\mathcal{K}}(x_{m_{\mathcal{K}}})$ instead of $P_k(x_{m_k})$.} over $K>1$ co-located nodes is available.
+		When the nodes are dispersed, problem \eqref{op:input_distribution} involves coupled term $\prod_{k \in \mathcal{K}} P_k(x_{m_k})$ and is non-convex.
+		Following \cite{Rezaeian2004}, we first recast the \gls{kkt} conditions to their equivalent forms, then propose a numerical method that guarantees those conditions by limit of sequences.
 		% ? Next, we propose a numerical method that evaluate the \gls{kkt} input distribution by limit of sequences.
 		\begin{remark}
-			As demonstrated in \cite{Buhler2011}, \gls{kkt} conditions are generally necessary but insufficient for total rate maximization problems.
-			Although \gls{kkt} solutions to problem \eqref{op:input_distribution} may end up being saddle points, we will later show by simulation their average performance can be reasonably close to optimal for a moderate $K$.
+			As demonstrated in \cite{Buhler2011}, \gls{kkt} conditions are generally necessary but insufficient for total rate maximization of discrete \gls{mac}.
+			We will show in the simulation part that, for a moderate $K$, the average achievable rate regions of \gls{kkt} and global-optimal input distributions almost overlap with each other.
 			\label{re:input_kkt_distribution}
@@
 		\end{figure*}
-		Those allows problem \eqref{op:active_beamforming} to be solved by the \gls{pgd} method, where any unregulated beamforming vector $\bar{\boldsymbol{w}}$ can be projected onto the feasible domain of average transmit power constraint \eqref{co:transmit_power} by
+		They allows problem \eqref{op:active_beamforming} to be solved by the \gls{pgd} method, where any unregulated beamformer $\bar{\boldsymbol{w}}$ can be projected onto the feasible domain of average transmit power constraint \eqref{co:transmit_power} by
 		\begin{equation}
@@
 		\end{equation}
-
 		The \gls{pgd} active beamforming optimization with step size determined by \gls{bls} is summarized in Algorithm \ref{al:active_beamforming}.
@@
 		which is still non-convex because variable $\boldsymbol{t}$ appears on the limits of integration \eqref{eq:dmtmac}.
-		Fortunately, we can further simplify problem \eqref{op:decision_threshold} as a point-to-point rate-optimal quantizer optimization for a discrete-input continuous-output memoryless channel, thanks to Remark \ref{re:backscatter_decision} and \ref{re:augmented_source}.
+		Fortunately, we can further simplify problem \eqref{op:decision_threshold} as a point-to-point rate-optimal quantizer design for a discrete-input continuous-output memoryless channel, thanks to Remark \ref{re:backscatter_decision} and \ref{re:augmented_source}.
 
 		\begin{remark}
-			Upon successful backscatter decoding, RIScatter receiver can always re-encode node messages to recover their reflection patterns at each primary block.
-			Therefore, backscatter decision design has no impact on the primary achievable rate, and any thresholding scheme maximizing the total backscatter mutual information \eqref{eq:backscatter_mutual_information} is also optimal for problem \eqref{op:decision_threshold}.
+			Upon successful backscatter decoding, the user can always re-encode node messages to recover the exact reflection patterns and determine the primary equivalent channel at each backscatter block.
+			Thus, backscatter decision design has no impact on the primary achievable rate, and any thresholding that maximize the total backscatter rate \eqref{eq:backscatter_mutual_information} is also optimal for problem \eqref{op:decision_threshold}.
 			\label{re:backscatter_decision}
@@
 		\begin{remark}
-			In terms of total backscatter rate, the potentially dispersed nodes with given input distribution can be viewed as an equivalent source with augmented alphabet of backscatter symbol tuples $\{x_{m_{\mathcal{K}}}\}$.
-			As such, the \gls{dmtmac} \eqref{eq:dmtmac} is essentially a \gls{dmtc}, and problem \eqref{op:decision_threshold} reduces to the rate-optimal quantization design for a discrete-input continuous-output memoryless channel.
+			In terms of total backscatter rate, the potentially dispersed nodes with known input distribution can be viewed as an equivalent source with backscatter symbol tuples as codewords.
+			As such, the \gls{dmtmac} \eqref{eq:dmtmac} becomes a \gls{dmtc} and problem \eqref{op:decision_threshold} reduces to the rate-optimal quantization design for a discrete-input continuous-output memoryless channel.
 			\label{re:augmented_source}
@@
 		\end{figure}
-		As shown in Fig. \ref{fg:discrete_outputs}, by introducing the extra analog-to-digital conversion step, we can group adjacent high-resolution energy bins for backscatter decision regions.
-		Thus, problem \eqref{op:decision_threshold} is recast as
+		As shown in Fig. \ref{fg:discrete_outputs}, by introducing the extra analog-to-digital conversion, we can group adjacent high-resolution energy bins to construct backscatter decision regions.
+		Thus, problem \eqref{op:decision_threshold} can be recast as
 		\begin{maxi!}
@@
 		\end{maxi!}
-		which can be solved by existing rate-optimal sequential quantizer designs for \gls{dmc}.
+		which can be solved by existing rate-optimal sequential quantizer designs for \gls{dmtc}.
 		To obtain global optimal solution, \cite{He2021} started from the quadrangle inequality and proposed a \gls{dp} method accelerated by the \gls{smawk} algorithm with computational complexity $\mathcal{O}\bigl(L^2(\mathrm{card}(\mathcal{T})-L)\bigr)$, while \cite{Nguyen2020a} started from the optimality condition for three neighbor thresholds and presented a traverse-then-bisect algorithm with complexity $\mathcal{O}\bigl(\mathrm{card}(\mathcal{T})L\log(\mathrm{card}(\mathcal{T})L)\bigr)$.
-		In Section \ref{st:simulation_results}, both schemes will be compared with the \gls{ml} thresholding \cite{Qian2019}
+		In Section \ref{st:simulation_results}, both schemes will be compared with the \gls{ml} scheme \cite{Qian2019}
 		\begin{equation}
@@
 			We observe that the distribution-adaptive schemes \emph{\gls{dp}}, \emph{\gls{smawk}} and \emph{Bisection} achieve higher total backscatter rate than the non-adaptive \emph{\gls{ml}}.
-			This is because the total backscatter mutual information \eqref{eq:backscatter_mutual_information} is a function of both input distribution and decision regions, and the rate-optimal threshold design depends heavily on input distribution.
+			This is because the total backscatter rate \eqref{eq:backscatter_mutual_information} is a function of both input distribution and decision regions, and the rate-optimal threshold design depends heavily on input distribution.
 			For example, the backscatter symbol tuples with zero input probability should never be detected and use empty decision regions, in order to increase the success detection chance of other tuples.

### 2022-10-29 assets/illustration/energy_distribution.tex
:bento: Update assets

@@
 			clip mode=individual,
-			height=5cm,
-			width=9cm,
+			height=4cm,
+			width=10cm,
 			xlabel = $z$,
 			ylabel = {Probability Density},
-			font=\scriptsize,
+			font=\normalsize,
 			no markers,

### 2022-10-29 assets/illustration/input_distribution.tex
:truck: Rename files
:bento: Update assets
:bento: Update illustrations

@@
 			width=10cm,
-			height=3cm,
+			height=2.6cm,
 			every axis plot/.append style={bar shift=0}
@@
 		\addplot[blue,fill=blue!30!white,postaction={pattern=north east lines},pattern color=.] coordinates {(4,0.25)};
-		\legend{SR}
+		\legend{BackCom/AmBC/SR}
 		\nextgroupplot[ylabel={Probability Distribution}]
@@
 		\addplot[red,fill=red!30!white,postaction={pattern=north east lines},pattern color=.] coordinates {(4,0)};
-		\legend{IRS}
+		\legend{RIS}
 		\nextgroupplot
@@
 		\addplot[brown,fill=brown!30!white,postaction={pattern=north east lines},pattern color=.] coordinates {(4,0)};
-		\legend{Metascatter}
+		\legend{RIScatter}
 	\end{groupplot}

### 2022-10-29 assets/illustration/time_structure.tex
:bento: Update assets

@@
-\begin{tikzpicture}
+\begin{tikzpicture}[font=\large]
 	% BC/AmBC/SR
@@
 	\foreach \x in {1,...,7}{
-			\draw[dotted] (\x,1) -- (\x,3.75);
+			% \draw[dotted] (\x,1) -- (\x,3.75);
+			\draw[dotted] (\x,1) -- (\x,3.25);
 		}
-	\draw[latex-latex] (0,3.5) -- (0.5,3.5) node[above,midway,yshift=1]{PB};
-	\draw[latex-latex] (0,4.1) -- (1,4.1) node[above,midway,yshift=1]{BB};
-	\draw[latex-latex] (0,4.7) -- (8,4.7) node[above,midway,yshift=1]{Channel Block};
+	\draw[latex-latex] (0,1.4) -- (0.5,1.4) node[above,midway,yshift=1]{PB};
+	% \draw[latex-latex] (0,4.1) -- (1,4.1) node[above,midway,yshift=1]{BB};
+	\draw[latex-latex] (0,2.4) -- (1,2.4) node[above,midway,yshift=1]{BB};
+	\draw[latex-latex] (0,3.4) -- (8,3.4) node[above,midway,yshift=1]{Channel Block};
 

### 2022-10-29 assets/simulation/region_comparison.tex
:bento: Update assets

@@
 			width=4.079in,
-height=3.432in,
-at={(0.684in,0.463in)},
+			height=1.587in,
+			at={(0.684in,0.361in)},
 			scale only axis,
@@
 			ylabel style={font=\color{white!15!black}},
-ylabel={Total Backscatter Rate [bits/BSP]},
+			ylabel={Total Backscatter\\Rate [bits/BB]},
 			axis background/.style={fill=white},
@@
 			reverse legend,
-every axis plot/.append style={line width=2pt}
+			every axis plot/.append style={line width=2pt},
+			align=center
 		]

### 2022-10-29 main.tex
:pencil: Shrink length

@@
 			\subfloat[Input Distribution]{
-				\resizebox{0.85\columnwidth}{!}{
+				\resizebox{0.8\columnwidth}{!}{
 					\input{assets/illustration/input_distribution.tex}
@@
 			\subfloat[Time Structure]{
-				\resizebox{0.9\columnwidth}{!}{
+				\resizebox{0.8\columnwidth}{!}{
 					\input{assets/illustration/time_structure.tex}
@@
 			\centering
-			\resizebox{0.9\columnwidth}{!}{
+			\resizebox{0.8\columnwidth}{!}{
 				\input{assets/illustration/energy_distribution.tex}
@@
 			\centering
-			\def\svgwidth{0.8\columnwidth}
+			\def\svgwidth{0.7\columnwidth}
 			\footnotesize{
@@
 	\begin{subsection}{Rate Region by Different Schemes}
-		% \begin{figure}[!t]
+		\begin{figure}[!t]
+			\centering
+			\subfloat[Input Distribution\label{fg:region_distribution}]{
+				\resizebox{0.6\columnwidth}{!}{
+					\input{assets/simulation/region_distribution.tex}
+				}
+			}
+			\\
+			\subfloat[Active Beamforming\label{fg:region_beamforming}]{
+				\resizebox{0.48\columnwidth}{!}{
+					\input{assets/simulation/region_beamforming.tex}
+				}
+			}
+			\subfloat[Decision Threshold\label{fg:region_threshold}]{
+				\resizebox{0.48\columnwidth}{!}{
+					\input{assets/simulation/region_threshold.tex}
+				}
+			}
+			\caption{
+				Average primary-total-backscatter rate regions for different input distribution, active beamforming, and decision threshold schemes.
+			}
+		\end{figure}
+		% \begin{figure*}[!t]
 		% 	\centering
 		% 	\subfloat[Input Distribution\label{fg:region_distribution}]{
-		% 		\resizebox{0.65\columnwidth}{!}{
+		% 		\resizebox{0.28\textwidth}{!}{
 		% 			\input{assets/simulation/region_distribution.tex}
@@
 		% 	}
-		% 	\\
 		% 	\subfloat[Active Beamforming\label{fg:region_beamforming}]{
-		% 		\resizebox{0.65\columnwidth}{!}{
+		% 		\resizebox{0.28\textwidth}{!}{
 		% 			\input{assets/simulation/region_beamforming.tex}
@@
 		% 	}
-		% 	\\
 		% 	\subfloat[Decision Threshold\label{fg:region_threshold}]{
-		% 		\resizebox{0.65\columnwidth}{!}{
+		% 		\resizebox{0.28\textwidth}{!}{
 		% 			\input{assets/simulation/region_threshold.tex}
@@
 		% 	}
-		% \end{figure}
-		\begin{figure*}[!t]
-			\centering
-			\subfloat[Input Distribution\label{fg:region_distribution}]{
-				\resizebox{0.28\textwidth}{!}{
-					\input{assets/simulation/region_distribution.tex}
-				}
-			}
-			\subfloat[Active Beamforming\label{fg:region_beamforming}]{
-				\resizebox{0.28\textwidth}{!}{
-					\input{assets/simulation/region_beamforming.tex}
-				}
-			}
-			\subfloat[Decision Threshold\label{fg:region_threshold}]{
-				\resizebox{0.28\textwidth}{!}{
-					\input{assets/simulation/region_threshold.tex}
-				}
-			}
-			\caption{
-				Average primary-total-backscatter rate regions for different input distribution, active beamforming, and decision threshold schemes.
-				``BSP'' means backscatter symbol period.
-			}
-		\end{figure*}
+		% \end{figure*}
 		The average achievable primary-total-backscatter rate regions of various input distribution, active beamforming, and decision threshold schemes are explored in this study.

### 2022-10-29 src/plot/plot_weights.m
:paintbrush: Update plot functions

@@ -11,9 +11,9 @@ for iWeight = 1 : nWeights
 end
 hold off; legend('Location', 'ne'); grid on; box on;
 xlabel('Reflection State');
-ylabel('Probability Distribution');
+ylabel('Probability\\Distribution');
 xticks(1 : nStates);
 yticks(0 : 0.2 : 1);
 style_plot(plotHandle);
 savefig(strcat('figures/distribution_', erase(mfilename, 'plot_')));
-matlab2tikz(strcat('../../assets/simulation/distribution_', erase(mfilename, 'plot_'), '.tex'), 'extraaxisoptions', {'title style={font=\LARGE}', 'label style={font=\LARGE}', 'ticklabel style={font=\Large}', 'legend style={font=\Large}'});
+matlab2tikz(strcat('../../assets/simulation/distribution_', erase(mfilename, 'plot_'), '.tex'), 'extraaxisoptions', {'align=center', 'title style={font=\LARGE}', 'label style={font=\LARGE}', 'ticklabel style={font=\Large}', 'legend style={font=\Large}'});

### 2022-10-29 assets/simulation/region_comparison.tex
:bento: Update assets

--- 2022-10-19 assets/simulation/region_comparison.tex
@@
 \begin{axis}[%
-width=4.079in,
-height=3.432in,
-at={(0.684in,0.463in)},
+width=4.036in,
+height=1.566in,
+at={(0.677in,0.361in)},
 scale only axis,
@@
 ylabel style={font=\color{white!15!black}},
-ylabel={Total Backscatter Rate [bits/BSP]},
+ylabel={Backscatter\\Rate [bits/BB]},
 axis background/.style={fill=white},
@@
 legend style={at={(0.03,0.03)}, anchor=south west, legend cell align=left, align=left, draw=white!15!black},
+align=center,
 title style={font=\LARGE},

### 2022-10-29 main.tex
:pencil: Update scattering comparison

@@
 % TODO why not use metamaterial? because high computational complexity and expectations of freedom (flexibility, reliability)
-% TODO cooperative input design can be used for co-located RIScatter nodes.
+% * cooperative input design can be used for co-located RIScatter nodes.
 % * hardward to modulate using RIS is already available.
@@
 
-	\begin{table*}[]
+	\begin{table*}[!t]
 		\caption{Comparison of Scattering Applications}
@@
 		\emph{Second,} we propose a practical receiver that accommodates the double modulation and signal difference in active-passive coexisting network.
-		Since the primary and backscatter messages are superimposed by multiplication coding and the backscatter symbol is typically longer than primary, the scattered signals from RIScatter nodes can be treated as multipath components during primary decoding, and the primary message can be viewed as a spreading code during backscatter decoding.
+		Since the primary and backscatter messages are superimposed by multiplication coding and the backscatter symbol is typically longer than primary, the scattered signals from RIScatter nodes can be treated as multipath components during primary decoding, and the primary symbols can be viewed as a spreading code during backscatter decoding.
 		Conventional sequential primary-backscatter decoder eliminates primary interference by \gls{sic} at each primary block, while our sequential backscatter-primary detector semi-coherently decodes RIScatter nodes from the received energy, re-encodes to recover exact reflection patterns, and models the deterministic multipath within primary equivalent channel as dynamic passive beamforming at each backscatter block.
@@
 		\end{equation}
-		The \gls{pgd} active beamforming optimization with step size determined by \gls{bls} is summarized in Algorithm \ref{al:active_beamforming}.
+		The \gls{pgd} active beamforming optimization with adaptive \gls{bls} step size \cite[Section 9.2]{Boyd2004} is summarized in Algorithm \ref{al:active_beamforming}.
 		\begin{algorithm}[!t]
@@
 \begin{section}{Simulation Results}
-	In this section, we provide numerical results to evaluate the proposed input distribution, active beamforming, and backscatter decision design for the RIScatter system in Fig.
+	In this section, we provide numerical results to evaluate the proposed input distribution, active beamforming, and backscatter decision designs for the RIScatter system in Fig.
 \ref{fg:riscatter_network}.
 	We assume the AP-user distance is \qty{10}{\meter} and at least one RIScatter nodes are randomly dropped in a disk centered at the user with radius \qty{2}{\meter}.
-	% The \gls{ap} is with an average power budget $P=\qty{36}{\dBm}$, the nodes employs $M$-\gls{qam} with amplitude scattering ratio $\alpha=0.5$, the user is with average noise power $\sigma_v^2=\qty{-40}{\dBm}$, and the symbol period ratio is $N=20$.
-	The \gls{ap} is with an average transmit power budget $P=\qty{36}{\dBm}$, all nodes employs $M$-\gls{qam} with amplitude scattering ratio $\alpha=0.5$, and the user is with average noise power $\sigma_v^2=\qty{-40}{\dBm}$.
-	% Q=4 and symbol period ratio is $N=20$.
+	% The \gls{ap} is with an average transmit power budget $P=\qty{36}{\dBm}$, all nodes employs $M$-\gls{qam} with amplitude scattering ratio $\alpha=0.5$, and the user is with average noise power $\sigma_v^2=\qty{-40}{\dBm}$.
+	The \gls{ap} is with an average transmit power budget $P=\qty{36}{\dBm}$ and all nodes employs $M$-\gls{qam} with amplitude scattering ratio $\alpha=0.5$.
 	For all channels involved, we consider a distance-dependent path loss model
@@
 	\end{equation}
-	where $d$ is the transmission distance, $L_0=-\qty{30}{\dB}$ is the reference path loss at distance $d_0=\qty{1}{\meter}$, $\kappa$ is the Rician $K$-factor, $\bar{\boldsymbol{H}}$ is the deterministic line-of-sight component with entries of unit magnitude, and $\tilde{\boldsymbol{H}}$ is the Rayleigh fading component with entries in standard \gls{iid} \gls{cscg} distribution.
+	where $d$ is the transmission distance, $L_0=-\qty{30}{\dB}$ is the reference path loss at $d_0=\qty{1}{\meter}$, $\kappa$ is the Rician $K$-factor, $\bar{\boldsymbol{H}}$ is the deterministic line-of-sight component with unit-magnitude entries, and $\tilde{\boldsymbol{H}}$ is the Rayleigh fading component with standard \gls{iid} \gls{cscg} entries.
 	We choose $\gamma_{\mathrm{D}}=2.6$, $\gamma_{\mathrm{F}}=2.4$, $\gamma_{\mathrm{B}}=2$, and $\kappa_{\mathrm{D}}=\kappa_{\mathrm{F}}=\kappa_{\mathrm{B}}=5$ for direct, forward and backward links.
-	The finite threshold domain $\mathcal{T}$ is obtained by $b$-bit uniform discretization over the critical interval defined by the confidence bounds of edge hypotheses (i.e., lower bound of $\mathcal{H}_1$ and upper bound of $\mathcal{H}_L$) with confidence level $1-\varepsilon$, where $b=9$ and $\varepsilon=\num{1e-3}$.
-	% The achievable primary-(sum-)backscatter rate point is defined as $(I_{\mathrm{P}}(s;y),)$
-	All average achievable rate points/regions are evaluated over \num{1000} realizations, and the parameters remain fixed unless otherwise specified.
+	The finite decision threshold domain $\mathcal{T}$ is obtained by $b$-bit uniform discretization over the critical interval defined by the confidence bounds of edge hypotheses (i.e., lower bound of $\mathcal{H}_1$ and upper bound of $\mathcal{H}_L$) with confidence $1-\varepsilon$, and we choose $b=9$ and $\varepsilon=\num{e-3}$.
+	All achievable rate points/regions are averaged over \num{1000} realizations.
 
@@
 		\begin{subsubsection}{Initialization}
-			To characterize the achievable rate region, we progressively obtain all boundary points by successively increasing the primary priority $\rho$ and solving problem \eqref{op:weighted_sum_rate}.
-			At $\rho=0$ where backscatter performance is absolutely prioritized, we initialize Algorithm \ref{al:input_distribution} and \ref{al:active_beamforming} by uniform input distribution and \gls{mrt} towards sum cascaded channel $\sum_{k} \boldsymbol{h}_{\mathrm{C},k}^H$, respectively.
+			To characterize each achievable rate region, we progressively obtain all boundary points by successively increasing weight $\rho$ and solving problem \eqref{op:weighted_sum_rate}.
+			For $\rho=0$ where backscatter link is prioritized, we initialize Algorithm \ref{al:input_distribution} and \ref{al:active_beamforming} by uniform input distribution and \gls{mrt} towards sum cascaded channel $\sum_{k} \boldsymbol{h}_{\mathrm{C},k}^H$, respectively.
 			At the following points, both algorithms are initialized by the final solutions at the previous point.
@@
 				}
-				\caption{Convergence behavior of the proposed algorithms for $\rho=0$.}
+				\caption{Typical convergence curves at $\rho=0$ for $Q=4$, $K=8$, $M=2$, $N=20$ and $\sigma_v^2=\qty{-40}{\dBm}$.}
 				\label{fg:wsr_convergence}
@@
 
-			In Fig.
-\ref{fg:wsr_convergence}, we plot the weighted sum of primary and total backscatter rates at $\rho=0$ for \gls{kkt}, \gls{pgd} (on the first call within \gls{bcd}) and \gls{bcd} algorithms in each iteration.
-			For $K=8$ and $M=2$, Algorithm \ref{al:input_distribution} typically takes around \num{100} fast iterations over closed-form expression \eqref{eq:input_kkt_solution} to converge to the \gls{kkt} input distribution.
+			In Fig. \ref{fg:wsr_convergence}, we plot the weighted sum of primary and total backscatter rates at $\rho=0$ for \gls{kkt}, \gls{pgd} and \gls{bcd} algorithms on the first call.
+			For $K=8$ and $M=2$, Algorithm \ref{al:input_distribution} typically takes around \num{100} fast closed-form iterations by \eqref{eq:input_kkt_solution} to converge to the \gls{kkt} input distribution.
 			For $Q=4$, around \num{10} iterations are required for Algorithm \ref{al:active_beamforming} to converge, where the gradient needs to be computed by \eqref{eq:weighted_sum_mutual_information_gradient} and the step size needs to be refined by \gls{bls}.
-			In comparison, the \gls{bcd} algorithm typically requires at most \num{5} iterations to converge.
-			At the following rate points (not presented), the convergence of all three algorithms become much faster thanks to the progressive initialization.
-			Overall, we conclude the proposed algorithms are able to converge within moderate iterations and provide significant rate benefits for the RIScatter system.
+			Overall, the \gls{bcd} algorithm initially requires at most \num{5} iterations to converge.
+			At the following points (not presented here), the convergence of all three algorithms are much faster thanks to the progressive initialization.
+			Hence, we conclude the proposed algorithms are able to converge within moderate iterations and provide significant rate benefits for RIScatter systems.
 		\end{subsubsection}
@@
 	\begin{subsection}{Comparison of Scattering Applications}
-
-		% For a fair comparison, we consider the setup in Fig. \ref{fg:riscatter_network} and employ \gls{ml} backscatter energy detection for these scattering applications:
-		% For a fair comparison, we consider the setup in Fig. \ref{fg:riscatter_network} with \gls{ml} backscatter energy detection for these scattering applications (except \gls{sr}):
-		% For a fair comparison with RIScatter, we consider the setup in Fig. \ref{fg:riscatter_network} and evaluate the achievable rate pairs for these scattering applications:
-		% We consider the setup in Fig. \ref{fg:riscatter_network} and compare the achievable rate pairs of RIScatter and these scattering applications:
-		On top of the setup in Fig. \ref{fg:riscatter_network}, we compare the achievable rate pairs of RIScatter and these scattering applications:
+		Based on the setup in Fig. \ref{fg:riscatter_network}, we compare the achievable rates of RIScatter and different scattering applications:
 		\begin{itemize}
@@
 			\begin{equation}
-				% y^{\text{\gls{bbc}}}[n] = \boldsymbol{h}_{\mathrm{E}}^H(x_{\mathcal{K}}) \boldsymbol{w} + v[n],
 				y^{\text{\gls{bbc}}}[n] = \Bigl(\boldsymbol{h}_{\mathrm{D}}^H + \sum_{k} \alpha_k \boldsymbol{h}_{\mathrm{C},k}^H x_k\Bigr) \boldsymbol{w} + v[n],
 			\end{equation}
-			% which follows non-zero mean complex Gaussian distribution $\mathcal{CN}\bigl(\boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}}) \boldsymbol{w},\sigma_v^2\bigr)$ under hypothesis $\mathcal{H}_{m_{\mathcal{K}}}$.
 			which follows non-zero mean complex Gaussian distribution $\mathcal{CN}\bigl((\boldsymbol{h}_{\mathrm{D}}^H + \sum_{k} \alpha_k \boldsymbol{h}_{\mathrm{C},k}^H x_{m_k}) \boldsymbol{w},\sigma_v^2\bigr)$ under hypothesis $\mathcal{H}_{m_{\mathcal{K}}}$.
-			% \sum_{k} \alpha_k \boldsymbol{h}_{\mathrm{C},k}^H x_k
 			The corresponding \gls{pdf} of accumulated receive energy over $N$ primary blocks is
@@
 			\end{equation}
-			% where $\mu_{m_{\mathcal{K}}}^{\text{\gls{bbc}}} \triangleq N \lvert \boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2$.
 			where $\mu_{m_{\mathcal{K}}}^{\text{\gls{bbc}}} \triangleq N \bigl\lvert \bigl(\boldsymbol{h}_{\mathrm{D}}^H + \sum_{k} \alpha_k \boldsymbol{h}_{\mathrm{C},k}^H x_{m_k}\bigr) \boldsymbol{w} \bigr\rvert^2$.
@@
 			\end{equation}
-			\item \emph{\gls{ambc}:} The user decodes both links independently and semi-coherently by treating the other as interference or uncertainty.
-			Hence, the primary achievable rate can be approximated by\footnote{To provide a preliminary benchmark, we approximate the unknown signal components from finite-input backscatter sources by independent interference from Gaussian sources.}
+			\item \emph{\gls{ambc}:} The user decodes both links independently and semi-coherently by treating the other as interference.
+			Hence, the primary achievable rate can be approximated by\footnote{To provide a preliminary benchmark, we consider the (correlated) scattered signal from finite-input backscatter sources as independent interference from Gaussian sources during primary decoding.}
 			\begin{equation}
@@
 			\item \emph{\gls{sr}:} For a sufficiently large $N$, the primary ergodic rate under semi-coherent detection asymptotically approaches \eqref{eq:primary_mutual_information} with uniform input distribution \cite{Long2020a}.
-			When $s[n]$ is successfully decoded and the direct interference $\boldsymbol{h}_{\mathrm{D}}^H \boldsymbol{w} s[n]$ is perfectly cancelled, the intermediate signal for backscatter detection is
+			When $s[n]$ is successfully decoded and the direct interference $\boldsymbol{h}_{\mathrm{D}}^H \boldsymbol{w} s[n]$ is perfectly cancelled, the intermediate signal is
 			\begin{equation}
 				\hat{y}^{\text{\gls{sr}}}[n] = \sum_{k} \alpha_k \boldsymbol{h}_{\mathrm{C},k}^H x_k \boldsymbol{w} s[n] + v[n],
+				\label{eq:intermediate_signal}
 			\end{equation}
 			which only involves noise uncertainty under hypothesis $\mathcal{H}_{m_{\mathcal{K}}}$.
-			% and follows non-zero mean complex Gaussian distribution $\mathcal{CN}\bigl(\sum_{k} \alpha_k \boldsymbol{h}_{\mathrm{C},k}^H x_k \boldsymbol{w} s[n],\sigma_v^2\bigr)$.
-			By \gls{mrc} over $N$ primary blocks, the total achievable for nodes with equiprobable inputs is \cite{Wang2014a}
+			During backscatter detection, the primary symbols $s[1],\ldots,s[n]$ can be viewed as a spreading code, and the receiver can perform \gls{mrc} over $N$ primary blocks.
+			The total achievable for nodes with equiprobable inputs is \cite{Wang2014a}
 			\begin{equation}
@@
 			where $\epsilon \triangleq \sum_{m_{\mathcal{K}}} \mathbb{E}_{\hat{v}} \log \sum_{m_{\mathcal{K}}'} \exp ( - {\lvert x_{m_{\mathcal{K}}} - x_{m_{\mathcal{K}}'} + \hat{v} \rvert^2}/{2 \sigma^2} )$ and $\hat{v} \sim \mathcal{CN}(0,\sigma_v^2/N)$.
-			For a sufficiently large $N$, $\epsilon$ is negligible and the total backscatter rate approaches $K \log M$.
-			\item \emph{\gls{ris}:} Since the backscatter symbol tuple $x_{\mathcal{K}}$ becomes deterministic, the total backscatter rate is zero and the primary achievable rate boils down to a special case of \eqref{eq:primary_mutual_information}
+			% For a sufficiently large $N$, $\epsilon$ is negligible and the total backscatter rate approaches $K \log M$.
+			\item \emph{\gls{ris}:} Since the backscatter symbol tuple $x_{\mathcal{K}}$ is deterministic, the total backscatter rate is zero and the primary achievable rate becomes a special case of \eqref{eq:primary_mutual_information}
 			\begin{equation}
@@
 
-		Fig. \ref{fg:region_comparison} presents typical achieve rate points of different scattering applications for $Q=1$, $K=1$, $M=4$ and $N=1000$.
-		First, we observe both \gls{bbc} and \gls{sr} can achieve the highest backscatter rate with coherent detection over the receive energy and intermediate signal, respectively.
-		This is because repetition coding with \gls{mrc} over $N$ primary blocks effectively increases the backscatter \gls{snr} by $N$ times, and the information loss due to the signal-to-energy conversion on top may be insignificant.
-		However, the asymptotic primary and backscatter rate analysis only provides upper bounds for \gls{sr}.
-		Using a very large $N$ not only reduces the system throughput\footnote{For example, Wi-Fi sampling rate is \qty{20}{\MHz} while \gls{rfid} load switching speed varies between \num{100}s of \unit{\kHz} to \num{10}s of \unit{\MHz} \cite{Torres2021}, corresponding to a typical symbol period ratio $N$ between \num{1} and \num{100}.} but also requires the operation-intensive \gls{sic} over each primary block.
-		When the duration of primary and backscatter symbol are comparable, the randomly scattered signals should be modelled as interference to primary link rather than quasi-static multipath components, and the achievable rate point of \gls{sr} will move towards the origin.
+		Fig. \ref{fg:region_comparison} compares typical achieve rate points of different scattering applications.
+		First, we observe both \gls{bbc} and \gls{sr} almost reach the noise-free backscatter rate when $N$ is sufficiently large.
+		For \gls{bbc} with coherent energy detection, the processing loss of signal-to-energy conversion can be insignificant, thanks to the noise hardening effect at large $N$.
+		For \gls{sr}, \gls{mrc} increases the equivalent backscatter \gls{snr} by $N$ times and the penalty term $\epsilon$ becomes negligible at large $N$.
+		However, the backscatter rate benefit requires $N$ \gls{sic} processes per backscatter block, and the primary rate benefit under semi-coherent detection requires a very large $N$.
+		When $N$ is moderate, the randomly scattered signals should be modelled as interference rather than quasi-static multipath components during primary decoding, and the \gls{sr} point will move towards \gls{ambc}.
+		% Using a very large $N$ not only reduces the system throughput but also requires the operation-intensive \gls{sic} over each primary block.
+		% When the primary and backscatter symbol periods are comparable, the randomly scattered signals should be modelled as interference rather than quasi-static multipath components during semi-coherent primary decoding, and the achievable rate point of \gls{sr} will move towards \gls{ambc}.
+		% For a moderate $N$, the randomly scattered signals should be modelled as interference rather than quasi-static multipath components during primary decoding, and the \gls{sr} rate point will move towards \gls{ambc}.
+
 		On the other hand, RIScatter provides a lower backscatter rate than \gls{bbc} and \gls{sr} due to semi-coherent detection, but preserves the primary rate benefit for arbitrary $N$.
@@
 			\end{itemize}
-
+			% TODO SR analysis can achieve large rate at the cost of large N; RIScatter can achieve slightly lower rate at the same N, but also preserves primary performance for smaller N
+			% TODO tradeoff between primary (RIScatter, no SIC) and backscatter (SR, SIC)
+			% !
+SR assume very large N for primary rate analysis.
+However, in such cases SIC is questionable as energy detection over received signal as BBC is already good enough and noncoherent detection can also achieve reasonable performance?
+			% TODO when primary symbols are determined, optimal input distribution at high backscatter SNR is equiprobable for any detection (signal/energy)
 			Fig. \subref*{fg:region_distribution} shows the achievable rate regions for those input distribution schemes.

### 2022-10-31 src/lib/benchmark_legacy.m
:sparkles: Add legacy to comparison

@@ -1,0 +1,27 @@
+function [rate] = benchmark_legacy(transmitPower, noisePower, directChannel)
+	% Function:
+	%	- evaluate the achievable primary and total backscatter rate for legacy transmission
+    %
+    % Input:
+	%	- transmitPower: average transmit power
+	%	- noisePower: average noise power
+	%	- directChannel [nTxs x 1]: direct AP-user channel
+    %
+    % Output:
+	%	- rate [2 x 1]: primary rate (nats/s/Hz) and total backscatter rate (nats/cu)
+    %
+    %
+    % Author & Date: Yang (i@snowztail.com), 22 Oct 31
+
+	% * No beamformer
+	beamforming = sqrt(transmitPower);
+
+	% * Compute signal power and SNR
+	signalPower = abs(directChannel' * beamforming) .^ 2;
+	snr = signalPower / noisePower;
+
+	% * Compute achievable rates
+	primaryRate = log(1 + snr);
+	backscatterRate = 0;
+	rate = [primaryRate; backscatterRate];
+end

### 2022-10-31 src/plot/plot_comparison.m

@@ -10,13 +10,14 @@ regionRiscatter = rate(:, convhull(transpose(rate)));
 
 %% * Plot achievable rates
 figure('Name', 'Achievable Rates of Different Scattering Applications', 'Position', [0, 0, 500, 200]);
-plotHandle = gobjects(1, 5);
+plotHandle = gobjects(1, 6);
 hold all;
-plotHandle(5) = plot(regionRiscatter(1, :) / log(2), regionRiscatter(2, :) / log(2), 'Color', '#77AC30', 'Marker', '^', 'DisplayName', 'RIScatter');
-plotHandle(4) = scatter(rateRis(1, :) / log(2), rateRis(2, :) / log(2), 200, [0.4940 0.1840 0.5560], 'Marker', 'x', 'DisplayName', 'RIS');
-plotHandle(3) = scatter(rateSr(1, :) / log(2), rateSr(2, :) / log(2), 200, [0.9290 0.6940 0.1250], 'Marker', 's', 'DisplayName', 'SR');
-plotHandle(2) = scatter(rateAmbc(1, :) / log(2), rateAmbc(2, :) / log(2), 200, [0.8500 0.3250 0.0980], 'Marker', '+', 'DisplayName', 'AmBC');
-plotHandle(1) = scatter(rateBbc(1, :) / log(2), rateBbc(2, :) / log(2), 200, [0 0.4470 0.7410], 'Marker', 'o', 'DisplayName', 'BBC');
+plotHandle(6) = plot(regionRiscatter(1, :) / log(2), regionRiscatter(2, :) / log(2), 'Color', [0.3010, 0.7450, 0.9330], 'Marker', 'v', 'DisplayName', 'RIScatter');
+plotHandle(5) = scatter(rateRis(1, :) / log(2), rateRis(2, :) / log(2), 200, [0.4660, 0.6740, 0.1880], 'Marker', '^', 'DisplayName', 'RIS');
+plotHandle(4) = scatter(rateSr(1, :) / log(2), rateSr(2, :) / log(2), 200, [0.4940 0.1840 0.5560], 'Marker', '+', 'DisplayName', 'SR');
+plotHandle(3) = scatter(rateAmbc(1, :) / log(2), rateAmbc(2, :) / log(2), 200, [0.9290 0.6940 0.1250], 'Marker', 'x', 'DisplayName', 'AmBC');
[…]

### 2022-10-31 src/region_comparison.m

@@ -15,11 +15,12 @@ equivalentChannel = directChannel + scatterRatio * cascadedChannel * transpose(c
 % * Clear persistent variables
 clear block_coordinate_descent distribution_kkt distribution_cooperation beamforming_pgd threshold_bisection;
 
-% * Obtain achievable rates for BBC, AmBC, SR, RIS and RIScatter
+% * Obtain achievable rates for legacy, BBC, AmBC, SR, RIS and RIScatter
+[rateLegacy] = benchmark_legacy(transmitPower, noisePower, directChannel);
 [rateBbc, distributionBbc, thresholdBbc] = benchmark_bbc(nTags, symbolRatio, transmitPower, noisePower, equivalentChannel);
 [rateAmbc, distributionAmbc, thresholdAmbc] = benchmark_ambc(nTags, symbolRatio, transmitPower, noisePower, equivalentChannel, scatterRatio, directChannel, cascadedChannel);
 [rateSr, distributionSr] = benchmark_sr(nTags, transmitPower, noisePower, equivalentChannel);
-[rateRis, distributionRis] = benchmark_ris(nTags, transmitPower, noisePower, equivalentChannel);% * Evaluate rate region
+[rateRis, distributionRis] = benchmark_ris(nTags, transmitPower, noisePower, equivalentChannel);
 for iWeight = 1 : nWeights
 	weight = weightSet(iWeight);
 	[rateRiscatter, distributionRiscatter, thresholdRiscatter, beamformingRiscatter] = block_coordinate_descent(nTags, symbolRatio, transmitPower, noisePower, nBins, weight, equivalentChannel, cascadedChannel, 'Distribution', 'kkt', 'Beamforming', 'pgd', 'Threshold', 'smawk');

### 2022-10-31 assets/simulation/region_comparison.tex
:bento: Update assets

--- 2022-10-19 assets/simulation/region_comparison.tex
@@
 %
-\definecolor{mycolor1}{rgb}{0.46667,0.67451,0.18824}%
-\definecolor{mycolor2}{rgb}{0.49400,0.18400,0.55600}%
-\definecolor{mycolor3}{rgb}{0.92900,0.69400,0.12500}%
-\definecolor{mycolor4}{rgb}{0.85000,0.32500,0.09800}%
-\definecolor{mycolor5}{rgb}{0.00000,0.44700,0.74100}%
+\definecolor{mycolor1}{rgb}{0.30100,0.74500,0.93300}%
+\definecolor{mycolor2}{rgb}{0.46600,0.67400,0.18800}%
+\definecolor{mycolor3}{rgb}{0.49400,0.18400,0.55600}%
+\definecolor{mycolor4}{rgb}{0.92900,0.69400,0.12500}%
+\definecolor{mycolor5}{rgb}{0.85000,0.32500,0.09800}%
+\definecolor{mycolor6}{rgb}{0.00000,0.44700,0.74100}%
 %
@@
 width=4.079in,
-height=3.432in,
-at={(0.684in,0.463in)},
+height=1.587in,
+at={(0.684in,0.361in)},
 scale only axis,
 xmin=0,
-xmax=7.08488905081188,
+xmax=6.5227548374066,
 xlabel style={font=\color{white!15!black}},
@@
 ]
-\addplot [color=mycolor1, line width=2.0pt, mark=triangle, mark options={solid, mycolor1}]
+\addplot [color=mycolor1, line width=2.0pt, mark=triangle, mark options={solid, rotate=180, mycolor1}]
   table[row sep=crcr]{%
-6.41670947751651	1.6054968458145\\
-0	1.6054968458145\\
+6.33724402501803	1.39764296268229\\
+0	1.39764296268229\\
 0	0\\
-7.08488904258997	0\\
-7.08488904258997	4.1836174712136e-07\\
-6.90245078291004	1.01381402853452\\
-6.6407882228124	1.4980015567956\\
-6.57239022993099	1.55479524496005\\
-6.51932412280019	1.58378871636645\\
-6.49722825073873	1.59220191008592\\
-6.4775306470264	1.59794430837116\\
-6.4598927531162	1.60170353740201\\
-6.44402970380102	1.60398330481762\\
-6.43668727400095	1.6046886802456\\
-6.42970223763566	1.60515550025508\\
-6.42700280669212	1.60528273332009\\
-6.42435520073694	1.60537879376922\\
-6.4217579842616	1.60544542043883\\
-6.41920966721981	1.60548425498564\\
-6.41670947751651	1.6054968458145\\
+6.52275483678685	0\\
+6.52275483678685	2.37312052924553e-08\\
+6.38739454470992	1.3235811846854\\
+6.35422040211439	1.38916612409166\\
+6.34857862205488	1.39386686170527\\
+6.3445353675389	1.39608085009443\\
+6.34291602910554	1.3966977322109\\
+6.34149846039129	1.39711118534274\\
+6.34024731759122	1.39737797077851\\
+6.3391350240222	1.3975379071887\\
+6.33862394227692	1.39758701988787\\
+6.33813974610465	1.39761939115801\\
+6.33795313341839	1.39762818964178\\
+6.33777036860279	1.39763482338317\\
+6.3375913342378	1.3976394187338\\
+6.33741590881855	1.39764209463684\\
+6.33724402501803	1.39764296268229\\
 };
@@
 
-\addplot[only marks, mark=x, mark options={}, mark size=3.5355pt, draw=mycolor2] table[row sep=crcr]{%
+\addplot[only marks, mark=triangle, mark options={}, mark size=2.3570pt, draw=mycolor2] table[row sep=crcr]{%
 x	y\\
-7.08488905081188	0\\
+6.5227548374066	0\\
 };
@@
 
-\addplot[only marks, mark=square, mark options={}, mark size=2.5000pt, draw=mycolor3] table[row sep=crcr]{%
+\addplot[only marks, mark=+, mark options={}, mark size=3.5355pt, draw=mycolor3] table[row sep=crcr]{%
 x	y\\
-6.44440818236646	2\\
+6.34321982467796	2\\
 };
@@
 
-\addplot[only marks, mark=+, mark options={}, mark size=3.5355pt, draw=mycolor4] table[row sep=crcr]{%
+\addplot[only marks, mark=x, mark options={}, mark size=3.5355pt, draw=mycolor4] table[row sep=crcr]{%
 x	y\\
-3.85295770698096	1.53088335179488\\
+5.90778796357092	1.34857377961699\\
 };
@@
 
-\addplot[only marks, mark=o, mark options={}, mark size=3.5355pt, draw=mycolor5] table[row sep=crcr]{%
+\addplot[only marks, mark=square, mark options={}, mark size=2.5000pt, draw=mycolor5] table[row sep=crcr]{%
 x	y\\
@@
 
+\addplot[only marks, mark=o, mark options={}, mark size=2.7386pt, draw=mycolor6] table[row sep=crcr]{%
+x	y\\
+6.34314881160129	0\\
+};
+\addlegendentry{Legacy}
+
 \end{axis}

### 2022-10-31 main.tex
:pencil: Update scattering comparison

@@
 			where $\mu_{m_{\mathcal{K}}}^{\text{\gls{bbc}}} \triangleq N \bigl\lvert \bigl(\boldsymbol{h}_{\mathrm{D}}^H + \sum_{k} \alpha_k \boldsymbol{h}_{\mathrm{C},k}^H x_{m_k}\bigr) \boldsymbol{w} \bigr\rvert^2$.
-			The \gls{ml} decision threshold is derived as, $\forall l \in \mathcal{L} \setminus \{L\}$,
+			The \gls{ml} decision threshold is consequently derived as, $\forall l \in \mathcal{L} \setminus \{L\}$,
 			\begin{equation}
@@
 			\item \emph{\gls{ambc}:} The user decodes both links independently and semi-coherently by treating the other as interference.
-			Hence, the primary achievable rate can be approximated by\footnote{To provide a preliminary benchmark, we consider the (correlated) scattered signal from finite-input backscatter sources as independent interference from Gaussian sources during primary decoding.}
+			Hence, the primary achievable rate is approximately\footnote{To provide a preliminary benchmark, we consider the (correlated) scattered signal from finite-input backscatter sources as independent interference from Gaussian sources during primary decoding.}
 			\begin{equation}
@@
 
+		% TODO SR analysis can achieve large rate at the cost of large N; RIScatter can achieve slightly lower rate at the same N, but also preserves primary performance for smaller N
+		% TODO tradeoff between primary (RIScatter, no SIC) and backscatter (SR, SIC)
+		% !
+SR assume very large N for primary rate analysis.
+However, in such cases SIC is questionable as energy detection over received signal as BBC is already good enough and noncoherent detection can also achieve reasonable performance?
+		% TODO when primary symbols are determined, optimal input distribution at high backscatter SNR is equiprobable for any detection (signal/energy)
+
 		Fig. \ref{fg:region_comparison} compares typical achieve rate points of different scattering applications.
-		First, we observe both \gls{bbc} and \gls{sr} almost reach the noise-free backscatter rate when $N$ is sufficiently large.
-		For \gls{bbc} with coherent energy detection, the processing loss of signal-to-energy conversion can be insignificant, thanks to the noise hardening effect at large $N$.
-		For \gls{sr}, \gls{mrc} increases the equivalent backscatter \gls{snr} by $N$ times and the penalty term $\epsilon$ becomes negligible at large $N$.
-		However, the backscatter rate benefit requires $N$ \gls{sic} processes per backscatter block, and the primary rate benefit under semi-coherent detection requires a very large $N$.
-		When $N$ is moderate, the randomly scattered signals should be modelled as interference rather than quasi-static multipath components during primary decoding, and the \gls{sr} point will move towards \gls{ambc}.
-		% Using a very large $N$ not only reduces the system throughput but also requires the operation-intensive \gls{sic} over each primary block.
-		% When the primary and backscatter symbol periods are comparable, the randomly scattered signals should be modelled as interference rather than quasi-static multipath components during semi-coherent primary decoding, and the achievable rate point of \gls{sr} will move towards \gls{ambc}.
-		% For a moderate $N$, the randomly scattered signals should be modelled as interference rather than quasi-static multipath components during primary decoding, and the \gls{sr} rate point will move towards \gls{ambc}.
-
-		On the other hand, RIScatter provides a lower backscatter rate than \gls{bbc} and \gls{sr} due to semi-coherent detection, but preserves the primary rate benefit for arbitrary $N$.
+		First, we observe both \gls{bbc} and \gls{sr} almost achieve noise-free backscatter transmission when $N$ is sufficiently large.
+		For \gls{bbc} using coherent energy detection, the conditional \gls{pdf} of accumulated receive energy \eqref{eq:energy_distribution_bbc} is more skewed at a large $N$, such that the equivalent \gls{dmtmac} \eqref{eq:dmtmac} becomes more reliable.
+		For \gls{sr} with \gls{sic} and \gls{mrc}, the effective backscatter \gls{snr} is increased by $N$ times and the penalty term $\epsilon$ becomes insignificant.
+		However, such an \gls{sr} requires $N$ \gls{sic} processes to detect one backscatter symbol (tuple), and the semi-coherent primary rate benefit only appears at a very large $N$.
+		When $N$ is moderate, the randomly scattered signals should be modelled as primary interference rather than quasi-static multipath components, and the \gls{sr} point will move towards the \gls{ambc} point.
+		% \footnote{\gls{sr} is essentially a multiplicative \gls{noma} that cancels interference, while \gls{ambc} is essentially a multiplicative \gls{sdma} that treats interference as noise.}
+		% Besides, the deterministic reflection pattern of \gls{ris} provides constructive primary signal superposition
+		% \gls{ris} achieves the highest primary achievable rate using deterministic reflection pattern.
+		In comparison, RIScatter performs semi-coherent backscatter detection and coherent primary detection to enable backscatter modulation and passive beamforming for arbitrary $N$, and the primary-backscatter tradeoff can be controlled by \gls{csi}- and weight-adaptive input distribution design.
+
+		% , and different rate points can be achieved by different node input distributions.
+
+		% coherent primary detection, and the
+
+		% RIScatter includes
+
+		% On the other hand, RIScatter provides a lower backscatter rate than \gls{bbc} and \gls{sr} due to semi-coherent detection, but preserves the primary rate benefit for arbitrary $N$.
 		% Backscatter advantage of SR using SIC is prominent for a smaller N
@@
 			\end{itemize}
-			% TODO SR analysis can achieve large rate at the cost of large N; RIScatter can achieve slightly lower rate at the same N, but also preserves primary performance for smaller N
-			% TODO tradeoff between primary (RIScatter, no SIC) and backscatter (SR, SIC)
-			% !
-SR assume very large N for primary rate analysis.
-However, in such cases SIC is questionable as energy detection over received signal as BBC is already good enough and noncoherent detection can also achieve reasonable performance?
-			% TODO when primary symbols are determined, optimal input distribution at high backscatter SNR is equiprobable for any detection (signal/energy)
 			Fig. \subref*{fg:region_distribution} shows the achievable rate regions for those input distribution schemes.

### 2022-11-01 main.tex
:lipstick: Update table style

@@
 \usepackage{xcolor}
+\usepackage{colortbl}
 % dark mode
@@
 \begin{document}
-\title{RIScatter: Unifying Backscatter Communications, Symbiotic Radio, and Reconfigurable Intelligent Surface}
+% \title{RIScatter: Unifying Scattering Techniques From a Distribution Perspective}
+\title{RIScatter: Unifying BackCom, AmBC, SR and RIS From a Distribution Perspective}
+% \title{RIScatter: Unifying Backscatter Communications, Symbiotic Radio, and Reconfigurable Intelligent Surface}
 \author{
@@
 		\label{tb:scattering_applications}
+		\renewcommand{\arraystretch}{1.25}
 		\begin{tabularx}{\textwidth}{CCCCCCC}
 			\toprule
+			% \rowcolor{gray!25}
 			                              & \gls{mbc}                 & \gls{bbc}                 & \gls{ambc}                                      & \gls{sr}                                     & \gls{ris}                                  & RIScatter                                         \\ \midrule
-			Coexisting systems            & 1                         & 1                         & 2 (competitive)                                 & 2 (collaborative)                            & 1                                          & 2 (collaborative)                                 \\ \midrule
-			Scatterer contribution        & Backscatter modulation    & Backscatter modulation    & Backscatter modulation and primary interference & Backscatter modulation and primary multipath & Passive beamforming                        & Backscatter modulation and passive beamforming    \\ \midrule
-			Cooperative transmissions     & ---                       & ---                       & No (individual transmitters)                    & Active beamforming                           & ---                                        & Active beamforming and smart reflection           \\ \midrule
-			Cooperative reception         & ---                       & ---                       & No (separated receivers)                        & Joint detection or \gls{sic}                 & ---                                        & Backscatter detection as primary channel training \\ \midrule
-			Primary detection             & ---                       & ---                       & Semi-coherent                                   & Coherent or semi-coherent                    & Coherent                                   & Coherent                                          \\ \midrule
-			Backscatter detection         & Coherent                  & Coherent                  & Semi-coherent or noncoherent                    & Coherent                                     & ---                                        & Semi-coherent                                     \\ \midrule
-			Reflection state distribution & Equiprobable (line-coded) & Equiprobable (line-coded) & Equiprobable (line-coded)                       & Equiprobable or Gaussian                     & Degenerate (\gls{csi}-adaptive)            & Flexible (\gls{csi}- and traffic-adaptive)        \\ \midrule
+			Coexisting systems            & 1                         & 1                         & 2 (competitive)                                 & 2 (collaborative)                            & 1                                          & 2 (collaborative)                                 \\
+			\rowcolor{gray!25}
+			Scatterer contribution        & Backscatter modulation    & Backscatter modulation    & Backscatter modulation and primary interference & Backscatter modulation and primary multipath & Passive beamforming                        & Backscatter modulation and passive beamforming    \\
+			Cooperative transmissions     & ---                       & ---                       & No (individual transmitters)                    & Active beamforming                           & ---                                        & Active beamforming and smart reflection           \\
+			\rowcolor{gray!25}
+			Cooperative reception         & ---                       & ---                       & No (separated receivers)                        & Joint detection or \gls{sic}                 & ---                                        & Backscatter detection as primary channel training \\
+			Primary detection             & ---                       & ---                       & Semi-coherent                                   & Coherent or semi-coherent                    & Coherent                                   & Coherent                                          \\
+			\rowcolor{gray!25}
+			Backscatter detection         & Coherent                  & Coherent                  & Semi-coherent or noncoherent                    & Coherent                                     & ---                                        & Semi-coherent                                     \\
+			Reflection state distribution & Equiprobable (line-coded) & Equiprobable (line-coded) & Equiprobable (line-coded)                       & Equiprobable or Gaussian                     & Degenerate (\gls{csi}-adaptive)            & Flexible (\gls{csi}- and traffic-adaptive)        \\
+			\rowcolor{gray!25}
 			Load-switching frequency      & Fast or slow              & Fast or slow              & Fast or slow                                    & Slow                                         & Slow (dynamic) or quasi-static (blockwise) & Fast or slow                                      \\ \bottomrule
@@
 	Ideally, it reflects the incident waves at the air-metamaterial boundary without receiving them, and mainly applies a phase shift on the reflected wave.
-	In practice, both kinds of scatterers have finite reflection states with non-zero reflection loss, and the scatter-absorb tradeoff depends on impedance matching.
+	In practice, both types of scatterers have finite reflection states with non-zero reflection loss, and the scattered signal can be decomposed into the \emph{structural} and \emph{antenna} mode components \cite{Hansen1989}.
+	The former consistently contributes to environment multipath and can be modelled within \gls{csi}, while the latter depends on impedance mismatch and can be used for backscatter modulation and/or passive beamforming.
 	For a scatter node with $M$ reflection states, the reflection coefficient at state $m \in \mathcal{M} \triangleq \{1,\ldots,M\}$ is
@@
 	where $Z_m$ is the antenna load (resp. metamaterial unit) impedance at state $m$ and $Z$ is the antenna input (resp. medium characteristic) impedance.
-	Backscatter modulation and passive beamforming are realized by manipulating the reflection coefficient.
-	Specifically, \gls{bc}, \gls{ambc} and \gls{sr} employ scatter nodes as information sources that encode message by \emph{probabilistically switching} between different states.
+	% Backscatter modulation and passive beamforming are realized by manipulating the reflection coefficient.
+	\gls{bc}, \gls{ambc} and \gls{sr} employ scatter nodes as information sources that encode message by \emph{probabilistically switching} between different states.
 	For $M$-ary \gls{qam}, constellation point $c_m$ maps to reflection coefficient $\Gamma_m$ by \cite{Thomas2012a}
@@
 	\begin{subsection}{Comparison of Scattering Applications}
-		Based on the setup in Fig. \ref{fg:riscatter_network}, we compare the achievable rates of RIScatter and different scattering applications:
+		Based on the setup in Fig. \ref{fg:riscatter_network}, we compare the achievable rates of RIScatter for different applications:
 		\begin{itemize}
-			\item \emph{\gls{bbc}:}
-			The primary symbol becomes deterministic $s[n]=1$ and the receive signal at each primary block is
+			\item \emph{Legacy:} Conventional active transmission without antenna mode scattering, $\alpha=0$.
+			\item \emph{\gls{bbc}:} The primary symbol becomes deterministic $s[n]=1$ and the receive signal at each primary block is
 			\begin{equation}
@@
 
-		Fig. \ref{fg:region_comparison} compares typical achieve rate points of different scattering applications.
+		The simulation results are shown in Fig. \ref{fg:region_comparison}.
 		First, we observe both \gls{bbc} and \gls{sr} almost achieve noise-free backscatter transmission when $N$ is sufficiently large.
@@
 		% \gls{ris} achieves the highest primary achievable rate using deterministic reflection pattern.
+		% Second, the passive beamforming gain by a single \gls{ris} node
+		% Second, the average primary achievable rate decreases in the presence of a \gls{ambc} node and subtly/notably increases in the presence of a \gls{sr}/\gls{ris} node.
+		Second, the average primary rate slightly increases/decreases in the presence of a \gls{ambc}/\gls{ris} node, while the multipath benefit of \gls{sr} is indistinguishable for a small $K$.
+		This is because the cascaded channel strength can be orders of magnitude lower than the direct channel strength due to the double fading effect.
+		\gls{ris} always ensures constructive superposition of direct and scattered signal components, while \gls{sr} only creates a rich-scattering environment that stochastically enhances the average primary rate.
+
+		Third, RIScatter enables flexible
+		% adapt the reflection state distribution of passive scatter devices based on \gls{csi} and link weights, in order to flexibly transition between backscatter modulation and passive beamforming.
+
+		% the inter \gls{ambc} node decreases
+
 		In comparison, RIScatter performs semi-coherent backscatter detection and coherent primary detection to enable backscatter modulation and passive beamforming for arbitrary $N$, and the primary-backscatter tradeoff can be controlled by \gls{csi}- and weight-adaptive input distribution design.

### 2022-11-01 main.tex
:pencil: Update scattering comparison

@@
 % \title{RIScatter: Unifying Scattering Techniques From a Distribution Perspective}
-\title{RIScatter: Unifying BackCom, AmBC, SR and RIS From a Distribution Perspective}
+% \title{RIScatter: Unifying BackCom, AmBC, SR and RIS From a Distribution Perspective}
+% \title{RIScatter: Unifying Backscatter Communications and Reconfigurable Intelligent Surface From a Probabilistic Perspective}
+\title{RIScatter: Unifying BackCom and RIS From a Probabilistic Perspective}
 % \title{RIScatter: Unifying Backscatter Communications, Symbiotic Radio, and Reconfigurable Intelligent Surface}
@@
 		5) the proposed receiver provides comparable backscatter detection performance than \gls{sic}-based \gls{sr} while significantly reduces the encoding and precoding (and avoids subtraction) costs;
-		6) it also supports fast-switching nodes and allows higher backscatter rate per unit time;
+		6) it also supports fast-switching nodes for higher backscatter throughput per unit time;
 		7) \gls{pgd} active beamformer enlarges achievable rate region by boosting the receive \gls{snr} and/or widening the energy gap under different reflection states;
@@
 		Hence, the receiver can semi-coherently (in the presence of primary uncertainty) decode node messages from the accumulated receive energy, re-encode to recover actual reflection patterns, and model the deterministic multipath within primary equivalent channel.
-		It enables simultaneous backscatter modulation and dynamic passive beamforming by only one energy level comparison, re-encoding and precoding for each backscatter block (instead of primary block), and is suitable for arbitrary primary sampling rate and backscatter switching speed.
+		It enables simultaneous backscatter modulation and dynamic passive beamforming by only one energy comparison, re-encoding, and precoding operations for each backscatter block (instead of primary block), and is suitable for arbitrary primary sampling rate and backscatter switching speed.
 	\end{subsection}
@@
 		\end{equation}
-		and the primary ergodic mutual information is
+		and the average primary mutual information is
 		\begin{equation}
@@
 		where $\rho \in \mathbb{I}$ is the weight of the primary link.
-		We notice the primary ergodic rate \eqref{eq:primary_mutual_information} depends on the input distribution and active beamforming, while the total backscatter rate depends on the input distribution and \gls{dmtmac} \eqref{eq:dmtmac} that relates to active beamforming and decision thresholds.
+		We notice the average primary rate \eqref{eq:primary_mutual_information} depends on the input distribution and active beamforming, while the total backscatter rate depends on the input distribution and \gls{dmtmac} \eqref{eq:dmtmac} that relates to active beamforming and decision thresholds.
 		\label{st:information_theory}
@@
 	\begin{subsection}{Comparison of Scattering Applications}
-		Based on the setup in Fig. \ref{fg:riscatter_network}, we compare the achievable rates of RIScatter for different applications:
+		On top of the setup in Fig. \ref{fg:riscatter_network}, we consider RIScatter and the following benchmark applications:
 		\begin{itemize}
@@
 			while the total backscatter rate follows \eqref{eq:backscatter_mutual_information} with uniform input distribution.
-			\item \emph{\gls{sr}:} For a sufficiently large $N$, the primary ergodic rate under semi-coherent detection asymptotically approaches \eqref{eq:primary_mutual_information} with uniform input distribution \cite{Long2020a}.
+			\item \emph{\gls{sr}:} For a sufficiently large $N$, the average primary rate under semi-coherent detection asymptotically approaches \eqref{eq:primary_mutual_information} with uniform input distribution \cite{Long2020a}.
 			When $s[n]$ is successfully decoded and the direct interference $\boldsymbol{h}_{\mathrm{D}}^H \boldsymbol{w} s[n]$ is perfectly cancelled, the intermediate signal is
@@
 			}
-			\caption{Typical achievable rate points of scattering applications for $Q=1$, $K=1$, $M=4$ and $N=1000$.}
+			\caption{Typical achievable rate region/points of scattering applications for $Q=1$, $K=1$, $M=4$ and $N=1000$.}
 			\label{fg:region_comparison}
@@
 		% TODO when primary symbols are determined, optimal input distribution at high backscatter SNR is equiprobable for any detection (signal/energy)
-
-		The simulation results are shown in Fig. \ref{fg:region_comparison}.
-		First, we observe both \gls{bbc} and \gls{sr} almost achieve noise-free backscatter transmission when $N$ is sufficiently large.
-		For \gls{bbc} using coherent energy detection, the conditional \gls{pdf} of accumulated receive energy \eqref{eq:energy_distribution_bbc} is more skewed at a large $N$, such that the equivalent \gls{dmtmac} \eqref{eq:dmtmac} becomes more reliable.
+		Fig. \ref{fg:region_comparison} compares the typical achievable rate region/points of RIScatter and those applications.
+		\emph{First,} we observe both \gls{bbc} and \gls{sr} almost ensure noise-free backscatter transmission when $N$ is sufficiently large.
+		For \gls{bbc} with coherent energy detection, the conditional \gls{pdf} of accumulated receive energy \eqref{eq:energy_distribution_bbc} is more skewed at a large $N$, such that the equivalent \gls{dmtmac} \eqref{eq:dmtmac} becomes more reliable.
 		For \gls{sr} with \gls{sic} and \gls{mrc}, the effective backscatter \gls{snr} is increased by $N$ times and the penalty term $\epsilon$ becomes insignificant.
-		However, such an \gls{sr} requires $N$ \gls{sic} processes to detect one backscatter symbol (tuple), and the semi-coherent primary rate benefit only appears at a very large $N$.
-		When $N$ is moderate, the randomly scattered signals should be modelled as primary interference rather than quasi-static multipath components, and the \gls{sr} point will move towards the \gls{ambc} point.
-		% \footnote{\gls{sr} is essentially a multiplicative \gls{noma} that cancels interference, while \gls{ambc} is essentially a multiplicative \gls{sdma} that treats interference as noise.}
-		% Besides, the deterministic reflection pattern of \gls{ris} provides constructive primary signal superposition
-		% \gls{ris} achieves the highest primary achievable rate using deterministic reflection pattern.
-		% Second, the passive beamforming gain by a single \gls{ris} node
-		% Second, the average primary achievable rate decreases in the presence of a \gls{ambc} node and subtly/notably increases in the presence of a \gls{sr}/\gls{ris} node.
-		Second, the average primary rate slightly increases/decreases in the presence of a \gls{ambc}/\gls{ris} node, while the multipath benefit of \gls{sr} is indistinguishable for a small $K$.
-		This is because the cascaded channel strength can be orders of magnitude lower than the direct channel strength due to the double fading effect.
-		\gls{ris} always ensures constructive superposition of direct and scattered signal components, while \gls{sr} only creates a rich-scattering environment that stochastically enhances the average primary rate.
-
-		Third, RIScatter enables flexible
-		% adapt the reflection state distribution of passive scatter devices based on \gls{csi} and link weights, in order to flexibly transition between backscatter modulation and passive beamforming.
-
-		% the inter \gls{ambc} node decreases
-
-		In comparison, RIScatter performs semi-coherent backscatter detection and coherent primary detection to enable backscatter modulation and passive beamforming for arbitrary $N$, and the primary-backscatter tradeoff can be controlled by \gls{csi}- and weight-adaptive input distribution design.
-
-		% , and different rate points can be achieved by different node input distributions.
-
-		% coherent primary detection, and the
-
-		% RIScatter includes
-
-		% On the other hand, RIScatter provides a lower backscatter rate than \gls{bbc} and \gls{sr} due to semi-coherent detection, but preserves the primary rate benefit for arbitrary $N$.
-		% Backscatter advantage of SR using SIC is prominent for a smaller N
-		% correlation by double modulation improves the detection performance
-		% when $N$ is sufficiently large.
+		Such an \gls{sr} requires a sufficiently large $N$ to guarantee the primary performance, but decreases the backscatter symbol rate by a factor of $N$ and requires $N$ \gls{sic} processes to decode each backscatter symbol (tuple).
+		\emph{Second,} the average primary rate slightly increases/decreases in the presence of a \gls{ambc}/\gls{ris} node, but the multipath benefit of \gls{sr} is unobvious.
+		This is because the cascaded channel can be orders of magnitude weaker than the direct channel due to the double fading effect.
+		\gls{ris} always ensures constructive superposition of direct and scattered components, but \gls{sr} only creates a quasi-static rich-scattering environment that stochastically enhances the average primary rate.
+		When $N$ is moderate, the randomly scattered signals should be modelled as primary interference rather than multipath components, and the \gls{sr} point will move towards the \gls{ambc} point.
+		\emph{Third,} RIScatter enables a flexible primary-backscatter tradeoff by smart input distribution design.
+		In terms of maximum primary achievable rate, RIScatter coincides with \gls{ris} and outperforms the others using deterministic reflection pattern (no need for backscatter detection) when the primary link is prioritized.
+		On the other hand, for a large $N$, the maximum backscatter achievable rate of RIScatter is higher than \gls{ambc} but lower than \gls{bbc} and \gls{sr}.
+		This is because both RIScatter and \gls{ambc} employ semi-coherent (instead of coherent) energy detection in the presence of primary uncertainty, and RIScatter with adaptive channel coding achieves higher backscatter rate than \gls{ambc} with equiprobable inputs.
+		Importantly, such a semi-coherent backscatter detection is feasible for arbitrary $N$, and using a fast-switching node with small $N$ can increase the backscatter throughput per unit time and preserve the dynamic passive beamforming gain.
+		% It only requires one energy comparison, re-encoding, and precoding operations to decode each backscatter symbol (tuple).
 	\end{subsection}

### 2022-11-02 main.tex
:pencil: Input distribution vs weights

@@
 % \title{RIScatter: Unifying BackCom, AmBC, SR and RIS From a Distribution Perspective}
-% \title{RIScatter: Unifying Backscatter Communications and Reconfigurable Intelligent Surface From a Probabilistic Perspective}
-\title{RIScatter: Unifying BackCom and RIS From a Probabilistic Perspective}
+\title{RIScatter: Unifying Backscatter Communications and Reconfigurable Intelligent Surface From a Probabilistic Perspective}
+% \title{RIScatter: Unifying BackCom and RIS From a Probabilistic Perspective}
 % \title{RIScatter: Unifying Backscatter Communications, Symbiotic Radio, and Reconfigurable Intelligent Surface}
@@
 		\emph{Third,} RIScatter enables a flexible primary-backscatter tradeoff by smart input distribution design.
-		In terms of maximum primary achievable rate, RIScatter coincides with \gls{ris} and outperforms the others using deterministic reflection pattern (no need for backscatter detection) when the primary link is prioritized.
+		In terms of maximum primary achievable rate, RIScatter coincides with \gls{ris} and outperforms the others by deterministic reflection pattern (no need for backscatter detection).
 		On the other hand, for a large $N$, the maximum backscatter achievable rate of RIScatter is higher than \gls{ambc} but lower than \gls{bbc} and \gls{sr}.
 		This is because both RIScatter and \gls{ambc} employ semi-coherent (instead of coherent) energy detection in the presence of primary uncertainty, and RIScatter with adaptive channel coding achieves higher backscatter rate than \gls{ambc} with equiprobable inputs.
-		Importantly, such a semi-coherent backscatter detection is feasible for arbitrary $N$, and using a fast-switching node with small $N$ can increase the backscatter throughput per unit time and preserve the dynamic passive beamforming gain.
-		% It only requires one energy comparison, re-encoding, and precoding operations to decode each backscatter symbol (tuple).
+		Importantly, such a practical RIScatter detection is feasible for arbitrary $N$, and using a fast-switching node with smaller $N$ can increase the backscatter throughput per unit time while preserving the dynamic passive beamforming gain on the primary link.
 	\end{subsection}
@@
 			}
-			\caption{Typical reflection state distribution under different weights for $Q=1$, $K=1$, $M=4$ and $N=20$.}
+			\caption{Typical RIScatter reflection state distribution under different weights for $Q=1$, $K=1$, $M=4$ and $N=20$.}
 			\label{fg:distribution_weights}
 		\end{figure}
-		The objective of this study is to demonstrate each RIScatter node can adjust its input distribution based on \gls{csi} and link priority to balance backscatter modulation and passive beamforming.
-		For this aim, we evaluate the \gls{kkt} input distribution by Algorithm \ref{al:input_distribution} for a single node under different weights in Fig. \ref{fg:distribution_weights}.
-		We observe that as $\rho$ increases from \num{0} to \num{1}, the \gls{kkt} input distribution
-		gradually progresses from slightly skewed to completely biased.
-		For $\rho=0$ where backscatter performance is absolutely prioritized, the \gls{csi}-adaptive channel coding at the RIScatter node provides higher backscatter rate than conventional \gls{bc} and \gls{sr} nodes with equiprobable inputs, and some states may end up unused since they cannot produce enough energy difference over the existing alphabet.
-		On the other hand, for $\rho=1$ where primary performance is absolutely prioritized, the input probability is \num{1} at the state that maximizes the primary equivalent channel strength, and \num{0} at the others.
-		In this case, the reflection pattern over time is fully deterministic, and the RIScatter node indeed boils down to a \gls{ris} element with discrete phase shifts.
-		Those observations meet our s that RIScatter nodes include scattering sources of \gls{bc}/\gls{sr} and reflecting elements of \gls{ris} as special cases, and generalize backscatter modulation and passive beamforming from the perspective of input distribution design.
-		For the \gls{bcd} algorithm, we choose the \gls{kkt} input distribution by Algorithm \ref{al:input_distribution}, the \gls{pgd} active beamforming by Algorithm \ref{al:active_beamforming}, and the \gls{smawk} decision threshold by \cite{He2021} as reference.
+		The objective of this study is to demonstrate RIScatter nodes can leverage \gls{csi}- and weight-adaptive input distribution design to balance backscatter modulation and passive beamforming.
+		For one RIScatter node with $M=4$, we evaluate the \gls{kkt} input distribution\footnote{Since problem \eqref{op:input_distribution} is convex when $K=1$, the \gls{kkt} solution is also global optimal in this example.} under different weights and present the result in Fig.
+\ref{fg:distribution_weights}.
+		At $\rho=0$ where backscatter performance is prioritized, the optimal input distribution is zero on two states and nearly uniform on the other two.
+		This is because, due to the weak scattered signal, the conditional energy \gls{pdf} under different hypotheses can be closely spaced as illustrated in Fig. \ref{fg:energy_distribution}.
+		In such cases, the extreme states producing the lowest/highest energy are always assigned with non-zero probability, while the others may not provide enough energy difference and end up unused.
+		At $\rho=1$ where primary performance is prioritized, the optimal input distribution is \num{1} at the state that maximizes the primary \gls{snr} and \num{0} at the others.
+		That is, the reflection pattern becomes deterministic and the RIScatter node boils down to a discrete \gls{ris} element.
+		Increasing $\rho$ from \num{0} to \num{1} provides a smooth transition from backscatter modulation to passive beamforming, which demonstrates RIScatter unifies \gls{bc} and \gls{ris} from a probabilistic perspective.
+
+		% gradually progresses from slightly skewed to completely biased.
+		% For $\rho=0$ where backscatter performance is absolutely prioritized, the \gls{csi}-adaptive channel coding at the RIScatter node provides higher backscatter rate than conventional \gls{bc} and \gls{sr} nodes with equiprobable inputs, and some states may end up unused since they cannot produce enough energy difference over the existing alphabet.
+		% On the other hand, for $\rho=1$ where primary performance is absolutely prioritized, the input probability is \num{1} at the state that maximizes the primary equivalent channel strength, and \num{0} at the others.
+		% In this case, the reflection pattern over time is fully deterministic, and the RIScatter node indeed boils down to a \gls{ris} element with discrete phase shifts.
+		% Those observations meet our s that RIScatter nodes include scattering sources of \gls{bc}/\gls{sr} and reflecting elements of \gls{ris} as special cases, and generalize backscatter modulation and passive beamforming from the perspective of input distribution design.
+		% For the \gls{bcd} algorithm, we choose the \gls{kkt} input distribution by Algorithm \ref{al:input_distribution}, the \gls{pgd} active beamforming by Algorithm \ref{al:active_beamforming}, and the \gls{smawk} decision threshold by \cite{He2021} as reference.
 	\end{subsection}

### 2022-11-02 main.tex
:pencil: Rate region by different schemes

@@
 	The finite decision threshold domain $\mathcal{T}$ is obtained by $b$-bit uniform discretization over the critical interval defined by the confidence bounds of edge hypotheses (i.e., lower bound of $\mathcal{H}_1$ and upper bound of $\mathcal{H}_L$) with confidence $1-\varepsilon$, and we choose $b=9$ and $\varepsilon=\num{e-3}$.
-	All achievable rate points/regions are averaged over \num{1000} realizations.
+	All achievable rate points/regions are averaged over \num{1000} channel realizations.
 
@@
 
-		% TODO SR analysis can achieve large rate at the cost of large N; RIScatter can achieve slightly lower rate at the same N, but also preserves primary performance for smaller N
-		% TODO tradeoff between primary (RIScatter, no SIC) and backscatter (SR, SIC)
-		% !
-SR assume very large N for primary rate analysis.
-However, in such cases SIC is questionable as energy detection over received signal as BBC is already good enough and noncoherent detection can also achieve reasonable performance?
-		% TODO when primary symbols are determined, optimal input distribution at high backscatter SNR is equiprobable for any detection (signal/energy)
 		Fig. \ref{fg:region_comparison} compares the typical achievable rate region/points of RIScatter and those applications.
@@
 		Increasing $\rho$ from \num{0} to \num{1} provides a smooth transition from backscatter modulation to passive beamforming, which demonstrates RIScatter unifies \gls{bc} and \gls{ris} from a probabilistic perspective.
-
-		% gradually progresses from slightly skewed to completely biased.
-		% For $\rho=0$ where backscatter performance is absolutely prioritized, the \gls{csi}-adaptive channel coding at the RIScatter node provides higher backscatter rate than conventional \gls{bc} and \gls{sr} nodes with equiprobable inputs, and some states may end up unused since they cannot produce enough energy difference over the existing alphabet.
-		% On the other hand, for $\rho=1$ where primary performance is absolutely prioritized, the input probability is \num{1} at the state that maximizes the primary equivalent channel strength, and \num{0} at the others.
-		% In this case, the reflection pattern over time is fully deterministic, and the RIScatter node indeed boils down to a \gls{ris} element with discrete phase shifts.
-		% Those observations meet our s that RIScatter nodes include scattering sources of \gls{bc}/\gls{sr} and reflecting elements of \gls{ris} as special cases, and generalize backscatter modulation and passive beamforming from the perspective of input distribution design.
-		% For the \gls{bcd} algorithm, we choose the \gls{kkt} input distribution by Algorithm \ref{al:input_distribution}, the \gls{pgd} active beamforming by Algorithm \ref{al:active_beamforming}, and the \gls{smawk} decision threshold by \cite{He2021} as reference.
-	\end{subsection}
-
-	% \begin{subsection}{Achievable Rates versus Energy Discretization Bits}
-	% 	\begin{figure}[!t]
-	% 		\subfloat[Primary Rate\label{fg:rate_bits_primary}]{
-	% 			\resizebox{0.48\columnwidth}{!}{
-	% 				\input{assets/simulation/rate_bits_primary.tex}
-	% 			}
-	% 		}
-	% 		\subfloat[Total Backscatter Rate\label{fg:rate_bits_backscatter}]{
-	% 			\resizebox{0.48\columnwidth}{!}{
-	% 				\input{assets/simulation/rate_bits_backscatter.tex}
-	% 			}
-	% 		}
-	% 		\caption{Average achievable primary and total backscatter rates for different energy discretization bits for $\rho=0$.}
-	% 		\label{fg:rate_bits}
-	% 	\end{figure}
-	% 	We now reveal how the analog-to-digital conversion of feasible threshold domain from $\mathbb{R}_+^{L+1}$ to $\mathcal{T}^{L+1}$ affects the average RIScatter performance.
-	% 	For a fixed input distribution and active beamforming, Fig. \ref{fg:rate_bits} shows the impact of energy discretization bits $b$ on the average achievable rates when $\rho=0$.
-	% 	We observe the primary rate is a constant for different $b$ as expected from Remark \ref{re:backscatter_decision}.
-	% 	This conclusion holds for arbitrary $\rho$ because the randomness of reflection patterns over time can always be eliminated upon successful backscatter decoding.
-	% 	When the nodes transmit at non-zero total rate, the user can re-encode backscatter messages to recover their reflection patterns at each primary block.
-	% 	Otherwise, the reflection patterns of all nodes are fully deterministic, and the state index tuple can be fed back to the user together with \gls{csi}.
-	% 	We also notice increasing $b$ boosts the total backscatter rate and the benefit becomes marginal when $b$ is sufficiently large ($2^b \gg \mathrm{card}(\mathcal{L})$).
-	% 	This is because a larger $b$ allows the decision regions to be constructed from narrower energy bins, which mitigates the transformation loss from problem \eqref{op:decision_threshold} to \eqref{op:decision_threshold_discrete}.
-	% 	Therefore, we conclude a proper selection of $b$ is the key to balance backscatter performance and computational complexity.
-	% \end{subsection}
+	\end{subsection}
 
@@
 			\centering
-			\subfloat[Input Distribution\label{fg:region_distribution}]{
+			\subfloat[Input Distribution, $Q=1$\label{fg:region_distribution}]{
 				\resizebox{0.6\columnwidth}{!}{
@@
 			\\
-			\subfloat[Active Beamforming\label{fg:region_beamforming}]{
+			\subfloat[Active Beamforming, $Q=4$\label{fg:region_beamforming}]{
 				\resizebox{0.48\columnwidth}{!}{
@@
 			}
-			\subfloat[Decision Threshold\label{fg:region_threshold}]{
+			\subfloat[Decision Threshold, $Q=4$\label{fg:region_threshold}]{
 				\resizebox{0.48\columnwidth}{!}{
@@
 			\caption{
-				Average primary-total-backscatter rate regions for different input distribution, active beamforming, and decision threshold schemes.
+				Average primary-total-backscatter rate regions by different input distribution, active beamforming, and decision threshold schemes for $K=2$, $M=4$ and $N=20$.
 			}
 		\end{figure}
-		% \begin{figure*}[!t]
-		% 	\centering
-		% 	\subfloat[Input Distribution\label{fg:region_distribution}]{
-		% 		\resizebox{0.28\textwidth}{!}{
-		% 			\input{assets/simulation/region_distribution.tex}
-		% 		}
-		% 	}
-		% 	\subfloat[Active Beamforming\label{fg:region_beamforming}]{
-		% 		\resizebox{0.28\textwidth}{!}{
-		% 			\input{assets/simulation/region_beamforming.tex}
-		% 		}
-		% 	}
-		% 	\subfloat[Decision Threshold\label{fg:region_threshold}]{
-		% 		\resizebox{0.28\textwidth}{!}{
-		% 			\input{assets/simulation/region_threshold.tex}
-		% 		}
-		% 	}
-		% 	\caption{
-		% 		Average primary-total-backscatter rate regions for different input distribution, active beamforming, and decision threshold schemes.
-		% 		``BSP'' means backscatter symbol period.
-		% 	}
-		% \end{figure*}
-		The average achievable primary-total-backscatter rate regions of various input distribution, active beamforming, and decision threshold schemes are explored in this study.
-
 		\begin{subsubsection}{Input Distribution}
-			We compare the following input distribution designs for problem \eqref{op:input_distribution}:
+			We compare these input distribution designs for problem \eqref{op:input_distribution}:
 			\begin{itemize}
-				\item \emph{Exhaustion:} Exhaustive grid search over the $M$-dimensional probability simplex with resolution $\Delta p = \num{1e-3}$;
-				\item \emph{\gls{kkt}:} Numerical \gls{kkt} solution evaluation by Algorithm \ref{al:input_distribution};
-				\item \emph{Cooperation:} Numerical symbol tuple distribution (i.e., $K$-dimensional joint probability array) evaluation by the Blahut-Arimoto algorithm \cite{Arimoto1972,Blahut1972a}.
-				% TODO MODIFIED BLAHUT-ARIMOTO, or modified algorithm 1 by treating as a single source
+				\item \emph{Cooperation:} Joint encoding with a $K$-dimensional probability array $P_{\mathcal{K}}(x_{m_{\mathcal{K}}})$ by Algorithm \ref{al:input_distribution};
+				\item \emph{Exhaustion:} Exhaustive search over the $M$-dimensional probability simplex with resolution $\Delta p = \num{e-2}$;
+				\item \emph{\gls{kkt}:} Numerical \gls{kkt} evaluation by Algorithm \ref{al:input_distribution};
+				\item \emph{Equiprobable:} Uniform input distribution for all nodes.
 			\end{itemize}
-
-			Since \emph{Cooperation} involves full transmit cooperation of all nodes, to support independent backscatter encoding, we also propose the following methods to recover individual input distributions from the joint probability array:
+			Since scatter cooperation is unavailable for dispersed nodes, we also propose these methods to recover input distributions (for independent encoding) from the joint probability array:
 			\begin{itemize}
 				\item \emph{Marginalization:} Marginal probability distributions;
-				\item \emph{Decomposition:} Normalized rank-\num{1} \gls{cp} decomposition tensors;
-				\item \emph{Randomization:} Random search guided with correlation matrix \cite{Calvo2010}.
+				\item \emph{Decomposition:} Normalized rank-\num{1} \gls{cp} decomposition tensors \cite{Bader2022};
+				\item \emph{Randomization:} Random search guided by correlation matrix \cite{Calvo2010}.
 			\end{itemize}
-			Fig. \subref*{fg:region_distribution} shows the achievable rate regions for those input distribution schemes.
-			We observe that \emph{Cooperation} provides the outer bound for all achievable rate regions, which suggests transmit cooperation between RIScatter nodes can be generally helpful.
-			However, it requires joint encoding with arbitrarily dependent codewords, and the extra coordination burden may be unaffordable for a large $K$.
-			We also notice the average performance of \emph{\gls{kkt}} input distribution design by Algorithm \ref{al:input_distribution} is extremely close to that of \emph{Exhaustion}, and the loss is indistinguishable for $K=2$.
-			This verifies our claim in Remark \ref{re:input_kkt_distribution} that the average performance of \gls{kkt} solutions can be reasonably good for a moderate $K$.
-			Despite \emph{Randomization} yields a similar result, the computational complexity is much higher (loops over $K+1$ linear programming problems) and the performance is backed by numerous randomly generated instances.
-			In contrast, the low-complexity \emph{Marginalization} returns a comparable result and the rate loss is insignificant when $K$ is small.
-			Finally, \emph{Decomposition} suffers from much lower average total backscatter rate, as the rank-\num{1} \gls{cp} approximation can be inaccurate for some channel-drop realizations.
-			% Those observations demonstrate the performance and complexity advantages of the proposed \gls{kkt} input distribution design, and reveal the potential of joint encoding at RIScatter nodes.
-			Those observations demonstrate the high performance and low complexity of the proposed \gls{kkt} input distribution design, and reveal the potential of joint encoding at RIScatter nodes.
+
+			Fig. \subref*{fg:region_distribution} shows the average achievable rate regions for those designs.
+			\emph{Cooperation} provides the rate region outer bound since joint encoding is generally beneficial for co-located RIScatter nodes.
+			The average rate performance of \emph{Exhaustion} and \emph{\gls{kkt}} coincide with each other, which verifies Remark \ref{re:input_kkt_distribution} that \gls{kkt} input distribution can be reasonably good for a moderate $K$.
+			\emph{Equiprobable} experiences minor backscatter and major primary rate losses without \gls{csi}- and weight-adaptive backscatter encoding.
+			As for the recovery methods, the simple \emph{Marginalization} provides a close result to \emph{\gls{kkt}}, but \emph{Randomization} and \emph{Decomposition} fail our expectations for most channel realizations.
+			Those observations emphasize the importance of (joint) adaptive RIScatter encoding and demonstrate the advantages of the proposed \gls{kkt} input distribution design.
 		\end{subsubsection}
@@
 		\begin{subsubsection}{Active Beamforming}
-			We compare the following active beamforming schemes for problem \eqref{op:active_beamforming}:
+			We consider three typical active beamforming schemes for problem \eqref{op:active_beamforming}:
 			\begin{itemize}
@@
 
-			Fig. \subref*{fg:region_beamforming} plots the achievable rate regions for those active beamforming schemes.
-			In the low-$\rho$ regime, we observe the proposed \emph{\gls{pgd}} design by Algorithm \ref{al:active_beamforming} outperforms \emph{E-\gls{mrt}} and \emph{D-\gls{mrt}} in terms of backscatter rate.
-			This is because backscatter decoding relies on the \emph{difference} of received energy expectations under different backscatter symbol tuples.
-			Such an energy diversity is not fully exploited by simply maximizing the direct/ergodic equivalent \gls{snr}, but can be properly controlled by \emph{\gls{pgd}} for enhanced detection performance.
-			As $\rho$ further increases, the primary equivalent \gls{snr} outweighs the backscatter energy difference in the weighted sum-rate expression \eqref{eq:weighted_sum_mutual_information_explicit}, and the input distribution is gradually biased to the state that roughly align direct and scattered components.
-			Therefore, the advantages of distribution-adaptive schemes \emph{\gls{pgd}} and \emph{E-\gls{mrt}} become marginal, the ergodic equivalent and direct channels are closer in direction, and the bounds of all schemes approach each other.
-			For the extreme case $\rho=1$, both distribution-adaptive schemes boil down to \gls{mrt} towards the deterministic primary equivalent channel, as considered in \gls{ris} literatures.
-			Those observations prove the proposed \emph{\gls{pgd}} active beamforming design can balance the primary equivalent \gls{snr} and backscatter energy diversity for enlarged rate regions.
+			Fig. \subref*{fg:region_beamforming} presents the average achievable rate regions for those schemes.
+			In the low-$\rho$ regime, the proposed \emph{\gls{pgd}} beamformer significantly outperforms both \gls{mrt} schemes in terms of backscatter rate.
+			This is because backscatter detection relies on the \emph{relative difference} of accumulated receive energy under different hypotheses.
+			Such an energy diversity is effectively enhanced by \emph{\gls{pgd}} that exploits backscatter constellation and input distribution knowledge, rather than simply maximizing the direct/ergodic equivalent \gls{snr}.
+			As $\rho$ increases, the primary equivalent \gls{snr} outweighs the backscatter energy difference in \eqref{eq:weighted_sum_mutual_information_explicit}, and \emph{\gls{pgd}} beamformer becomes closer to both \gls{mrt} schemes.
+			At $\rho=1$, \emph{\gls{pgd}} and \emph{E-\gls{mrt}:} boil down to \gls{mrt} towards the deterministic primary equivalent channel as commonly considered in \gls{ris} literatures.
+			Besides, the difference between \emph{E-\gls{mrt}} and \emph{D-\gls{mrt}} can be insignificant for dispersed RIScatter nodes.
+			Those observations prove the proposed \emph{\gls{pgd}} active beamforming design can flexibly improve primary equivalent \gls{snr} and enhance backscatter energy difference to enlarge RIScatter achievable rate region.
 		\end{subsubsection}
@@
 		\begin{subsubsection}{Decision Threshold}
-			We compare the following decision thresholds for problem \eqref{op:decision_threshold_discrete}:
+			We evaluate the following decision threshold strategies for problem \eqref{op:decision_threshold_discrete}:
 			\begin{itemize}
@@
 
-			Fig. \subref*{fg:region_threshold} presents the achievable rate region for those decision threshold schemes.
-			We observe that the distribution-adaptive schemes \emph{\gls{dp}}, \emph{\gls{smawk}} and \emph{Bisection} achieve higher total backscatter rate than the non-adaptive \emph{\gls{ml}}.
-			This is because the total backscatter rate \eqref{eq:backscatter_mutual_information} is a function of both input distribution and decision regions, and the rate-optimal threshold design depends heavily on input distribution.
-			For example, the backscatter symbol tuples with zero input probability should never be detected and use empty decision regions, in order to increase the success detection chance of other tuples.
-			Those observations highlight the importance of joint input distribution and decision threshold design.
+			Fig. \subref*{fg:region_threshold} reveals the average achievable rate region for those strategies.
+			% We observe that the distribution-adaptive schemes \emph{\gls{dp}}, \emph{\gls{smawk}} and \emph{Bisection} achieve higher total backscatter rate than the non-adaptive \emph{\gls{ml}}.
+			The distribution-adaptive schemes \emph{\gls{dp}}, \emph{\gls{smawk}} and \emph{Bisection} ensure higher total backscatter rate than the non-adaptive \emph{\gls{ml}}.
+			This is because the total backscatter rate \eqref{eq:backscatter_mutual_information} is a function of both input distribution and decision regions, and the rate-optimal threshold design heavily depends on input distribution.
+			For example, the backscatter symbol tuples with zero input probability should be assigned with empty decision regions, in order to increase the success detection rates of other tuples.
+			It highlights the importance of joint input distribution and decision threshold design in rate maximization problems.
 		\end{subsubsection}

### 2022-11-03 main.tex
:pencil: Rate region vs configurations

@@
 % * (I(X_1;Y_1),I(X_2;Y_2))
+% ? Channel estimation error, coordination issues
+% TODO  binary input and signal output (BISO) channel, ML figure
 \begin{abstract}
-	\gls{bc} nodes harvest energy from and modulate information over an external carrier by manipulating the magnitude, phase, and/or frequency of the scattered signal.
-	\gls{sr} incorporates a passive scatter node into existing radio networks to create additional propagation path and ride its own information towards the cooperative receiver.
+	\gls{bc} nodes harvest energy from and modulate information over an external radio wave by manipulating the magnitude, phase, and/or frequency of the scattered signal.
+	% \gls{sr} incorporates a passive scatter node into existing radio networks to create additional propagation path and ride its own information towards the cooperative receiver.
 	\gls{ris} is a programmable reflector array that adapts the phase shift response to enhance or suppress signal strength in specific directions.
@@
 \ref{fg:riscatter_network}.
-	We assume the AP-user distance is \qty{10}{\meter} and at least one RIScatter nodes are randomly dropped in a disk centered at the user with radius \qty{2}{\meter}.
+	We assume the AP-user distance is \qty{10}{\meter} and at least one RIScatter nodes are randomly dropped in a disk centered at the user with radius $r$.
 	% The \gls{ap} is with an average transmit power budget $P=\qty{36}{\dBm}$, all nodes employs $M$-\gls{qam} with amplitude scattering ratio $\alpha=0.5$, and the user is with average noise power $\sigma_v^2=\qty{-40}{\dBm}$.
@@
 				}
-				\caption{Typical convergence curves at $\rho=0$ for $Q=4$, $K=8$, $M=2$, $N=20$ and $\sigma_v^2=\qty{-40}{\dBm}$.}
+				\caption{Typical convergence curves at $\rho=0$ for $Q=4$, $K=8$, $M=2$, $N=20$, $\sigma_v^2=\qty{-40}{\dBm}$ and $r=\qty{2}{\meter}$.}
 				\label{fg:wsr_convergence}
@@
 			In Fig. \ref{fg:wsr_convergence}, we plot the weighted sum of primary and total backscatter rates at $\rho=0$ for \gls{kkt}, \gls{pgd} and \gls{bcd} algorithms on the first call.
-			For $K=8$ and $M=2$, Algorithm \ref{al:input_distribution} typically takes around \num{100} fast closed-form iterations by \eqref{eq:input_kkt_solution} to converge to the \gls{kkt} input distribution.
-			For $Q=4$, around \num{10} iterations are required for Algorithm \ref{al:active_beamforming} to converge, where the gradient needs to be computed by \eqref{eq:weighted_sum_mutual_information_gradient} and the step size needs to be refined by \gls{bls}.
+			For $K=8$ and $M=2$, Algorithm \ref{al:input_distribution} typically takes around \num{100} fast iterations by \eqref{eq:input_kkt_solution} to converge to the \gls{kkt} input distribution.
+			For $Q=4$, around \num{10} iterations are required for Algorithm \ref{al:active_beamforming} to converge, where the gradient is computed by \eqref{eq:weighted_sum_mutual_information_gradient} and the step size is refined by \gls{bls}.
 			Overall, the \gls{bcd} algorithm initially requires at most \num{5} iterations to converge.
 			At the following points (not presented here), the convergence of all three algorithms are much faster thanks to the progressive initialization.
-			Hence, we conclude the proposed algorithms are able to converge within moderate iterations and provide significant rate benefits for RIScatter systems.
+			Hence, we conclude the proposed algorithms are able to converge fast.
 		\end{subsubsection}
@@
 			where $\mu_{m_{\mathcal{K}}}^{\text{\gls{bbc}}} \triangleq N \bigl\lvert \bigl(\boldsymbol{h}_{\mathrm{D}}^H + \sum_{k} \alpha_k \boldsymbol{h}_{\mathrm{C},k}^H x_{m_k}\bigr) \boldsymbol{w} \bigr\rvert^2$.
-			The \gls{ml} decision threshold is consequently derived as, $\forall l \in \mathcal{L} \setminus \{L\}$,
+			The \gls{ml} decision threshold is derived as, $\forall l \in \mathcal{L} \setminus \{L\}$,
 			\begin{equation}
@@
 			which only involves noise uncertainty under hypothesis $\mathcal{H}_{m_{\mathcal{K}}}$.
-			During backscatter detection, the primary symbols $s[1],\ldots,s[n]$ can be viewed as a spreading code, and the receiver can perform \gls{mrc} over $N$ primary blocks.
+			During backscatter detection, the primary symbols $s[1],\ldots,s[n]$ can be viewed as a spreading code, and the receiver employs \gls{mrc} over $N$ primary blocks.
 			The total achievable for nodes with equiprobable inputs is \cite{Wang2014a}
@@
 			}
-			\caption{Typical achievable rate region/points of scattering applications for $Q=1$, $K=1$, $M=4$ and $N=1000$.}
+			\caption{Typical achievable rate region/points of scattering applications for $Q=1$, $K=1$, $M=4$, $N=1000$, $\sigma_v^2=\qty{-40}{\dBm}$ and $r=\qty{2}{\meter}$.}
 			\label{fg:region_comparison}
@@
 		For \gls{sr} with \gls{sic} and \gls{mrc}, the effective backscatter \gls{snr} is increased by $N$ times and the penalty term $\epsilon$ becomes insignificant.
-		Such an \gls{sr} requires a sufficiently large $N$ to guarantee the primary performance, but decreases the backscatter symbol rate by a factor of $N$ and requires $N$ \gls{sic} processes to decode each backscatter symbol (tuple).
-		\emph{Second,} the average primary rate slightly increases/decreases in the presence of a \gls{ambc}/\gls{ris} node, but the multipath benefit of \gls{sr} is unobvious.
+		Such an \gls{sr} only guarantees the primary benefit with a large $N$, but decreases the backscatter symbol rate by a factor of $N$ and requires $N$ \gls{sic} processes to decode each backscatter symbol (tuple).
+		\emph{Second,} the average primary rate slightly increases/decreases in the presence of a \gls{ambc}/\gls{ris} node, and the multipath benefit of \gls{sr} is unobvious.
 		This is because the cascaded channel can be orders of magnitude weaker than the direct channel due to the double fading effect.
-		\gls{ris} always ensures constructive superposition of direct and scattered components, but \gls{sr} only creates a quasi-static rich-scattering environment that stochastically enhances the average primary rate.
+		\gls{ris} always ensures constructive superposition of direct and scattered components, while \gls{sr} only creates a quasi-static rich-scattering environment that stochastically enhances the average primary rate.
 		When $N$ is moderate, the randomly scattered signals should be modelled as primary interference rather than multipath components, and the \gls{sr} point will move towards the \gls{ambc} point.
@@
 		On the other hand, for a large $N$, the maximum backscatter achievable rate of RIScatter is higher than \gls{ambc} but lower than \gls{bbc} and \gls{sr}.
-		This is because both RIScatter and \gls{ambc} employ semi-coherent (instead of coherent) energy detection in the presence of primary uncertainty, and RIScatter with adaptive channel coding achieves higher backscatter rate than \gls{ambc} with equiprobable inputs.
+		This is because both RIScatter and \gls{ambc} employ semi-coherent (instead of coherent) energy detection in the presence of primary uncertainty, and RIScatter with adaptive channel coding can achieve higher backscatter rate than \gls{ambc} with equiprobable inputs.
 		Importantly, such a practical RIScatter detection is feasible for arbitrary $N$, and using a fast-switching node with smaller $N$ can increase the backscatter throughput per unit time while preserving the dynamic passive beamforming gain on the primary link.
@@
 			}
-			\caption{Typical RIScatter reflection state distribution under different weights for $Q=1$, $K=1$, $M=4$ and $N=20$.}
+			\caption{Typical RIScatter reflection state distribution under different weights for $Q=1$, $K=1$, $M=4$, $N=20$, $\sigma_v^2=\qty{-40}{\dBm}$ and $r=\qty{2}{\meter}$.}
 			\label{fg:distribution_weights}
@@
 		This is because, due to the weak scattered signal, the conditional energy \gls{pdf} under different hypotheses can be closely spaced as illustrated in Fig. \ref{fg:energy_distribution}.
-		In such cases, the extreme states producing the lowest/highest energy are always assigned with non-zero probability, while the others may not provide enough energy difference and end up unused.
+		In such cases, the extreme states producing the lowest/highest energy are always assigned with non-zero probability, while the middle ones may not provide enough energy difference and end up unused.
 		At $\rho=1$ where primary performance is prioritized, the optimal input distribution is \num{1} at the state that maximizes the primary \gls{snr} and \num{0} at the others.
@@
 			\caption{
-				Average primary-total-backscatter rate regions by different input distribution, active beamforming, and decision threshold schemes for $K=2$, $M=4$ and $N=20$.
+				Average primary-total-backscatter rate regions by different input distribution, active beamforming, and decision threshold schemes for $K=2$, $M=4$, $N=20$, $\sigma_v^2=\qty{-40}{\dBm}$ and $r=\qty{2}{\meter}$.
 			}
@@
 			\begin{itemize}
-				\item \emph{Cooperation:} Joint encoding with a $K$-dimensional probability array $P_{\mathcal{K}}(x_{m_{\mathcal{K}}})$ by Algorithm \ref{al:input_distribution};
+				\item \emph{Cooperation:} Joint encoding using a $K$-dimensional probability array $P_{\mathcal{K}}(x_{m_{\mathcal{K}}})$ by Algorithm \ref{al:input_distribution};
 				\item \emph{Exhaustion:} Exhaustive search over the $M$-dimensional probability simplex with resolution $\Delta p = \num{e-2}$;
-				\item \emph{\gls{kkt}:} Numerical \gls{kkt} evaluation by Algorithm \ref{al:input_distribution};
+				\item \emph{\gls{kkt}:} Numerical \gls{kkt} result evaluation by Algorithm \ref{al:input_distribution};
 				\item \emph{Equiprobable:} Uniform input distribution for all nodes.
 			\end{itemize}
-			Since scatter cooperation is unavailable for dispersed nodes, we also propose these methods to recover input distributions (for independent encoding) from the joint probability array:
+			Since scatter cooperation is unavailable for dispersed nodes, to support independent encoding, we also consider these input distribution recovery methods over the joint probability array:
 			\begin{itemize}
 				\item \emph{Marginalization:} Marginal probability distributions;
-				\item \emph{Decomposition:} Normalized rank-\num{1} \gls{cp} decomposition tensors \cite{Bader2022};
+				\item \emph{Decomposition:} Normalized rank-\num{1} \gls{cp} decomposition tensors by \texttt{Tensor Toolbox} \cite{Bader2022};
 				\item \emph{Randomization:} Random search guided by correlation matrix \cite{Calvo2010}.
@@
 			\emph{Cooperation} provides the rate region outer bound since joint encoding is generally beneficial for co-located RIScatter nodes.
-			The average rate performance of \emph{Exhaustion} and \emph{\gls{kkt}} coincide with each other, which verifies Remark \ref{re:input_kkt_distribution} that \gls{kkt} input distribution can be reasonably good for a moderate $K$.
+			The average rate performance of \emph{Exhaustion} and \emph{\gls{kkt}} coincide with each other, which demonstrates \gls{kkt} input distribution can be reasonably good for a moderate $K$ as stated in Remark \ref{re:input_kkt_distribution}.
 			\emph{Equiprobable} experiences minor backscatter and major primary rate losses without \gls{csi}- and weight-adaptive backscatter encoding.
@@
 			Fig. \subref*{fg:region_beamforming} presents the average achievable rate regions for those schemes.
-			In the low-$\rho$ regime, the proposed \emph{\gls{pgd}} beamformer significantly outperforms both \gls{mrt} schemes in terms of backscatter rate.
+			In the low-$\rho$ regime, the proposed \emph{\gls{pgd}} beamformer significantly outperforms both \gls{mrt} schemes in terms of total backscatter rate.
 			This is because backscatter detection relies on the \emph{relative difference} of accumulated receive energy under different hypotheses.
-			Such an energy diversity is effectively enhanced by \emph{\gls{pgd}} that exploits backscatter constellation and input distribution knowledge, rather than simply maximizing the direct/ergodic equivalent \gls{snr}.
+			Such an energy diversity is enhanced by \emph{\gls{pgd}} that effectively exploits backscatter constellation and input distribution knowledge, rather than simply maximizing the direct/ergodic equivalent \gls{snr}.
 			As $\rho$ increases, the primary equivalent \gls{snr} outweighs the backscatter energy difference in \eqref{eq:weighted_sum_mutual_information_explicit}, and \emph{\gls{pgd}} beamformer becomes closer to both \gls{mrt} schemes.
-			At $\rho=1$, \emph{\gls{pgd}} and \emph{E-\gls{mrt}:} boil down to \gls{mrt} towards the deterministic primary equivalent channel as commonly considered in \gls{ris} literatures.
+			At $\rho=1$, \emph{\gls{pgd}} and \emph{E-\gls{mrt}:} boil down to \gls{mrt} towards the deterministic primary equivalent channel as in \gls{ris} literature \cite{Wu2019}.
 			Besides, the difference between \emph{E-\gls{mrt}} and \emph{D-\gls{mrt}} can be insignificant for dispersed RIScatter nodes.
-			Those observations prove the proposed \emph{\gls{pgd}} active beamforming design can flexibly improve primary equivalent \gls{snr} and enhance backscatter energy difference to enlarge RIScatter achievable rate region.
+			Those observations prove the proposed \emph{\gls{pgd}} active beamforming design can flexibly improve primary equivalent \gls{snr} and enhance backscatter energy difference to enlarge the achievable rate region for RIScatter.
 		\end{subsubsection}
@@
 			Fig. \subref*{fg:region_threshold} reveals the average achievable rate region for those strategies.
-			% We observe that the distribution-adaptive schemes \emph{\gls{dp}}, \emph{\gls{smawk}} and \emph{Bisection} achieve higher total backscatter rate than the non-adaptive \emph{\gls{ml}}.
 			The distribution-adaptive schemes \emph{\gls{dp}}, \emph{\gls{smawk}} and \emph{Bisection} ensure higher total backscatter rate than the non-adaptive \emph{\gls{ml}}.
 			This is because the total backscatter rate \eqref{eq:backscatter_mutual_information} is a function of both input distribution and decision regions, and the rate-optimal threshold design heavily depends on input distribution.
-			For example, the backscatter symbol tuples with zero input probability should be assigned with empty decision regions, in order to increase the success detection rates of other tuples.
+			For example, the backscatter symbol tuples with zero input probability should be assigned with empty decision regions in order to increase the success detection rates of other tuples.
 			It highlights the importance of joint input distribution and decision threshold design in rate maximization problems.
@@
 				Average primary-total-backscatter rate regions for different system configurations.
-				``PSP'' means primary symbol period.
 			}
@@
 		\end{figure}
-		In this study, we investigate the impact of system configuration on the average achievable rate regions.
+		In this study, we choose $Q=4$, $K=8$, $M=2$, $N=20$, $\sigma_v^2=\qty{-40}{\dBm}$ and $r=\qty{2}{\meter}$ as a reference.
 		\begin{subsubsection}{Number of Nodes}
-			Fig. \subref*{fg:region_tags} reveals how the number of two-state RIScatter nodes $K$ influence the primary-backscatter tradeoff.
-			We observe the total backscatter rate roughly scales proportionally with the number of nodes, and the decrease of individual rate is unobvious.
-			This demonstrates the proposed low-complexity semi-coherent energy detector performs reasonably well for a moderate $K$.
-			On the other hand, we observe adding RIScatter nodes can also boost the achievable primary rate.
-			The reason is the nodes can exploit the additional propagation path for a constructive primary signal superposition that enjoys a ``squared law'' similar to \gls{ris}.
+			Fig. \subref*{fg:region_tags} reveals how the number RIScatter nodes $K$ influence the primary-backscatter tradeoff.
+			Interestingly, we observe that increasing $K$ has a larger benefit on the total backscatter rate than primary.
+			When multiple nodes are present, each RIScatter node is indeed performing passive beamforming for primary as well as other backscatter links.
+			To maximize the total backscatter rate, some nodes closer to the user may need to sacrifice their own rate and use the state that minimizes the primary equivalent channel strength, in order to enlarge the relative energy difference under different hypotheses of other nodes (and increase their rates).
+			This accounts for the significant primary rate decrease in the low-$\rho$ regime.
+			On the other hand, when the primary link is prioritized, the RIScatter nodes boil down to \gls{ris} elements and enjoy a passive array gain of $N^2$.
 		\end{subsubsection}
@@
 			We notice increasing the reflection states has a marginal effect on both primary and total backscatter rates.
-			This is because once the scope is roughly determined, using denser constellation points may not create enough phase resolution and energy diversity for primary and backscatter links.
-			Another possible reason is the amplitude normalization step in the reflection-constellation mapping \eqref{eq:backscatter_modulation} grants less scattered (and more harvestable) power for the inner points, which are thus less frequently employed.
-			It motivates the use of numerous elementary RIScatter nodes, instead of high-order transponders or high-resolution metasurfaces.
+			This is because once the scope of reflection coefficient is determined, using denser constellation points may not create enough phase resolution and energy diversity for primary and backscatter links.
+			Due to the maximum amplitude normalization in \eqref{eq:backscatter_modulation}, the average rate region of \num{8}-\gls{qam} with rectangular frame is smaller than that of \num{4}-\gls{qam} with square frame, and the inner constellation points with smaller amplitudes are less frequently used.
+			The results in this and previous paragraphs motivate one to replace the high-resolution metamaterial units of RIS by multiple low-order scatter nodes.
 		\end{subsubsection}
@@
 			Fig. \subref*{fg:region_txs} illustrates the impact of transmit antennas $Q$ on the average performance.
-			We observe larger $Q$ produces greater achievable rate regions.
-			Thanks to the \gls{pgd} active beamforming, the expectations of the received power under different backscatter symbol tuples can be flexibly controlled to satisfy the link priority requirements.
-			For example, beamforming towards the equivalent channel can produce higher primary \gls{snr}, while beamforming towards the cascaded channels can enhance the relative energy difference for better backscatter detection.
-			Those observations emphasize the importance of multi-antenna RIScatter systems and demonstrate the advantages of the proposed \gls{pgd} design.
+			Increasing $Q$ enlarges the achievable rate region because \gls{pgd} provides a flexible tradeoff between primary equivalent \gls{snr} and backscatter energy difference.
+			It emphasizes the importance of multi-antenna RIScatter systems and demonstrate the effectiveness of the proposed \gls{pgd} design.
 		\end{subsubsection}
@@
 			Fig. \subref*{fg:region_duration} presents how symbol period ratio $N$ affects the achievable rate region.
-			We notice using a small $N$ can effectively boost the total backscatter rate per primary symbol, and the conventional \gls{sr} literatures assuming sufficiently large $N$ is generally inefficient.
-			However, it not only requires a frequent change of reflection states that consumes more power at the passive nodes, but also involves more detection and re-encoding operations at the user to maintain the primary rate.
-			When $N$ becomes sufficiently large, the total backscatter rate approaches \num{0}, and RIScatter nodes boil down to \gls{ris} elements with fixed reflection pattern during whole channel block.
-			Therefore, we conclude $N$ should be properly tweaked based on the rate requirements and physical properties of the passive nodes.
+			As mentioned above, the conventional \gls{sr} scheme with a large $N$ is generally inefficient while RIScatter with a small $N$ can effectively boost the backscatter throughput per unit time.
+			However, it $N$ requires frequent state change that consumes more power at the passive nodes and involves more detection and re-encoding operations at the user.
+			As $N \to \infty$, RIScatter nodes boil down to \gls{ris} elements with fixed reflection pattern during whole channel block and the total backscatter rate approaches \num{0}.
+			Therefore, we conclude $N$ should be properly designed in a practical RIScatter system based on the data rate requirements, physical constraints at the nodes, and signal processing capability at the user.
 		\end{subsubsection}
@@
 			Fig. \subref*{fg:region_noise} depicts the impact of average noise power $\sigma_v^2$ on average rate regions.
-			Despite the proposed low-complexity energy detection is suitable for a wide range of noise levels, there exists a backscatter performance upper bound due to its semi-coherent property.
+			It shows the proposed low-complexity semi-coherent backscatter energy detection is suitable for a wide range of noise levels.
 			When $\sigma_v^2$ relatively high, we can choose a longer backscatter symbol period (i.e., larger $N$) to maintain the backscatter \gls{snr} for better detection performance.
@@
 		\begin{subsubsection}{Coverage Disk Radius}
-			Fig. \subref*{fg:region_coverage} shows the relationship between RIScatter cover disk radius and achievable rate regions.
+			Fig. \subref*{fg:region_coverage} shows the relationship between disk radius $r$ and achievable rate region.
 			We observe both primary and backscatter performance are enhanced when nodes are dropped closer to the user.
-			This is because the product path loss (a.k.a. double fading) model for finite-size scatterers is less severe for such near-far setups.
-			Thanks to the dispersed characteristics of RIScatter nodes and legacy users, each node can simply scatter and be decoded by the closest user, thus avoids the development optimization and allows uniformly good performance for both links.
+			This is because the double fading effect for finite-size scatterers is less severe for near-far setups.
+			In a multi-user RIScatter system with dispersed nodes, each node can be decoded by the nearest user to guarantee uniformly good performance for both links.
 		\end{subsubsection}
 	\end{subsection}
-	% ? Channel estimation error, coordination issues
 	\label{st:simulation_results}
@@
 \begin{section}{Conclusion}
-	% TODO  binary input and signal output (BISO) channel, ML figure
-	This paper introduced RIScatter as a low-power transmit-assist protocol that generalizes \gls{bc}, \gls{sr} and \gls{ris} by smart input distribution and practical receiver design.
+	This paper introduced RIScatter as a low-power scattering protocol that unifies backscatter modulation and dymanic passive beamforming by smart input distribution and practical receiver design.
 	Starting from scattering principles, we showed how RIScatter nodes include scattering source of \gls{bc}/\gls{sr} and reflecting element of \gls{ris} as special cases, how they can be built over existing passive scatter devices, and how they simultaneously encode self information and assist legacy transmission.
@@
 	One possible direction is to consider backscatter detection over the received signal domain rather than energy domain.
-	Learning-based classification approaches can be prominsing in such cases.
+	Learning-based classification approaches can be promising in such cases.
 	Another interesting question is how to design RIScatter node and receiver in a multi-user system.

### 2022-11-03 main.tex
:dizzy: Manuscript 221103

@@
 \begin{abstract}
-	\gls{bc} nodes harvest energy from and modulate information over an external radio wave by manipulating the magnitude, phase, and/or frequency of the scattered signal.
+	% \gls{bc} nodes harvest energy from and modulate information over an external radio wave by manipulating the magnitude, phase, and/or frequency of the scattered signal.
+	% \gls{bc} nodes harvest energy from and modulate information over an external electromagnetic wave by manipulating the magnitude, phase, and/or frequency of the scattered signal.
+	\gls{bc} nodes harvest energy from and modulate information over an external electromagnetic wave.
 	% \gls{sr} incorporates a passive scatter node into existing radio networks to create additional propagation path and ride its own information towards the cooperative receiver.
-	\gls{ris} is a programmable reflector array that adapts the phase shift response to enhance or suppress signal strength in specific directions.
-	In this paper, we show how those three seemingly different technologies can be unified to leverage their benefits simultaneously into a single architecture called RIScatter.
-	RIScatter is a new paradigm for future wireless networks and consists of multiple dispersed or co-located passive scatter nodes, whose reflection states can be adapted to partially engineer the wireless channel and partially modulate information onto the scattered wave.
-	This contrasts with \gls{bc}/\gls{sr} (resp. \gls{ris}) where states are exclusively a function of information symbols (resp. \gls{csi}).
+	% \gls{ris} is a programmable reflector array that adapts the phase shift response to enhance or suppress signal strength in specific directions.
+	\gls{ris} adapts its phase shift response to enhance or suppress signal strength in specific directions.
+	In this paper, we show how those two seemingly different technologies (and their derivatives) can be unified to leverage their benefits simultaneously into a single architecture called RIScatter.
+	As a new paradigm for future wireless networks, RIScatter consists of multiple dispersed or co-located passive scatter nodes whose reflection states can be adapted to partially engineer the wireless channel and partially modulate information onto the scattered wave.
+	This contrasts with \gls{bc} (resp. \gls{ris}) where states are exclusively a function of information symbols (resp. \gls{csi}).
 	The key principle in RIScatter is to render the probability distribution of reflection states as a joint function of the \gls{csi} and input information source.
-	This enables RISscatter to softly bridge, generalize, and outperform \gls{bc}, \gls{sr}, \gls{ris}; boil down to any of those under specific reflection states; or evolve in a mixed form for universal hardware design and heterogeneous traffic control.
-	For a typical setup, we characterize the achievable primary-(total-)backscatter rate region by optimizing input distribution at the nodes, active beamforming at the \gls{ap}, and backscatter detector at the user.
-	Simulation results demonstrate RIScatter nodes can exploit the additional propagation paths to smoothly transition between backscatter modulation and passive beamforming via smart input distribution design, and the proposed receiver significantly reduces the decoding complexity and effectively accommodates the double modulation and signal difference in active-passive coexisting network.
+	This enables RISscatter to softly bridge, generalize, and outperform \gls{bc} and \gls{ris}; boil down to any of those under specific reflection states; or evolve in a mixed form for universal hardware design and heterogeneous traffic control.
+	For a single-user multi-node RIScatter network, we characterize the achievable primary-(total-)backscatter rate region by optimizing input distribution at the nodes, active beamforming at the \gls{ap}, and backscatter detection region at the user.
+	Simulation results demonstrate RIScatter nodes can exploit the additional propagation paths to smoothly transition between backscatter modulation and passive beamforming via smart input distribution design, and the proposed practical receiver effectively accommodates the double modulation and signal difference in active-passive coexisting networks.
 \end{abstract}
@@
 		In particular, \emph{symbol level precoding} maps backscatter symbols to optimized \gls{ris} coefficient sets \cite{Liu2019d,Bereyhi2020}, \emph{overlay modulation} superposes information-bearing symbols over a common auxiliary matrix \cite{Xu2020b,Zhang2021d,Hu2021b,Hua2022}, \emph{spatial modulation} switches between reflection coefficient sets that maximize \gls{snr} at different receive antennas \cite{Basar2020,Ma2020a,Yuan2021}, and \emph{index modulation} employs dedicated reflection elements for passive beamforming and dedicated information elements for backscatter modulation \cite{Hu2021a}.
-		Those \gls{ris}-empowered \gls{bc}/\gls{sr} designs involve advanced hardware architecture and high optimization complexity.
+		Those \gls{ris}-empowered \gls{bc} designs involve advanced hardware architecture and high optimization complexity.
 		Besides, all relevant literatures consider either Gaussian codebook \cite{Guo2019b,Ding2020,Long2020a,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Hu2021b} or finite equiprobable inputs \cite{Yang2018,Liang2020,Han2021,Zhang2022,Liu2019d,Bereyhi2020,Xu2020b,Zhang2021d,Hua2022,Basar2020,Ma2020a,Yuan2021,Hu2021a} for backscatter information sources.
@@
 	\begin{subsection}{Contributions}
-		As presented in Fig. \subref*{fg:riscatter}, we propose RIScatter as a novel scattering protocol that generalizes \gls{bc}, \gls{sr}, and \gls{ris}.
+		As presented in Fig. \subref*{fg:riscatter}, we propose RIScatter as a novel scattering protocol that generalizes \gls{bc} and \gls{ris}.
 		The contributions of this paper are summarized as follows.
@@
 		\emph{First,} we propose RIScatter nodes that adapt the reflection state distribution of passive scatter devices based on \gls{csi} and link weights, in order to flexibly transition between backscatter modulation and passive beamforming.
-		Scattering sources of \gls{bc}/\gls{ambc}/\gls{sr} and reflecting elements of \gls{ris} can be regarded as special cases with uniform and degenerate input distributions, respectively.
+		Scattering sources of \gls{bc} and reflecting elements of \gls{ris} can be regarded as special cases with uniform and degenerate input distributions, respectively.
 		On the contrary, adaptive RIScatter encoding boils down to deterministic \gls{ris} when primary link is prioritized, and achieves higher backscatter rate than conventional line coding when backscatter link is prioritized.
@@
 	% Backscatter modulation and passive beamforming are realized by manipulating the reflection coefficient.
-	\gls{bc}, \gls{ambc} and \gls{sr} employ scatter nodes as information sources that encode message by \emph{probabilistically switching} between different states.
+	\gls{bc} employ scatter nodes as information sources that encode message by \emph{probabilistically switching} between different states.
 	For $M$-ary \gls{qam}, constellation point $c_m$ maps to reflection coefficient $\Gamma_m$ by \cite{Thomas2012a}
@@
 	\begin{subsection}{Concepts}
-		As a generalization of \gls{bc}, \gls{sr} and \gls{ris}, RIScatter is a passive scattering protocol that coexists with an active primary system in a flexible and mutualistic manner.
+		As a generalization of \gls{bc} and \gls{ris}, RIScatter is a passive scattering protocol that coexists with an active primary system in a flexible and mutualistic manner.
 		RIScatter nodes leverage \gls{csi}- and weight-based input distribution design to smoothly transition between backscatter modulation and passive beamforming.
@@
 			\caption{
-				Input distribution and time structure of \gls{bc}, \gls{ambc}, \gls{sr}, \gls{ris}, and RIScatter.
+				Input distribution and time structure of \gls{bc}, \gls{ris}, and RIScatter.
 				``PB'' means primary block and ``BB'' means backscatter block.
@@
 
-	Problem \eqref{op:weighted_sum_rate} generalizes conventional \gls{bc}/\gls{sr} by allowing \gls{csi}- and weight-adaptive input distribution and detection region design.
+	Problem \eqref{op:weighted_sum_rate} generalizes conventional \gls{bc} by allowing \gls{csi}- and weight-adaptive input distribution and detection region design.
 	It also generalizes the discrete \gls{ris} phase shift selection by allowing stochastic reflection (i.e., relaxing the feasible domain from the vertices of $M$-dimensional probability simplex to the simplex itself).
@@
 	This paper introduced RIScatter as a low-power scattering protocol that unifies backscatter modulation and dymanic passive beamforming by smart input distribution and practical receiver design.
-	Starting from scattering principles, we showed how RIScatter nodes include scattering source of \gls{bc}/\gls{sr} and reflecting element of \gls{ris} as special cases, how they can be built over existing passive scatter devices, and how they simultaneously encode self information and assist legacy transmission.
+	Starting from scattering principles, we showed how RIScatter nodes include scattering source of \gls{bc} and reflecting element of \gls{ris} as special cases, how they can be built over existing passive scatter devices, and how they simultaneously encode self information and assist legacy transmission.
 	We also propose a low-complexity RIScatter receiver that preserves the benefits of backscatter modulation and passive beamforming.

### 2022-11-04 main.tex
:pencil: Rate region vs nodes

@@
 		\renewcommand{\arraystretch}{1.25}
-		\begin{tabularx}{\textwidth}{CCCCCCC}
+		\begin{tabularx}{\textwidth}{CCCCCC}
 			\toprule
 			% \rowcolor{gray!25}
-			                              & \gls{mbc}                 & \gls{bbc}                 & \gls{ambc}                                      & \gls{sr}                                     & \gls{ris}                                  & RIScatter                                         \\ \midrule
-			Coexisting systems            & 1                         & 1                         & 2 (competitive)                                 & 2 (collaborative)                            & 1                                          & 2 (collaborative)                                 \\
+			                              & \gls{mbc}/\gls{bbc}       & \gls{ambc}                                      & \gls{sr}                                     & \gls{ris}                                  & RIScatter                                         \\ \midrule
+			Coexisting systems            & 1                         & 2 (competitive)                                 & 2 (collaborative)                            & 1                                          & 2 (collaborative)                                 \\
 			\rowcolor{gray!25}
-			Scatterer contribution        & Backscatter modulation    & Backscatter modulation    & Backscatter modulation and primary interference & Backscatter modulation and primary multipath & Passive beamforming                        & Backscatter modulation and passive beamforming    \\
-			Cooperative transmissions     & ---                       & ---                       & No (individual transmitters)                    & Active beamforming                           & ---                                        & Active beamforming and smart reflection           \\
+			Scatterer contribution        & Backscatter modulation    & Backscatter modulation and primary interference & Backscatter modulation and primary multipath & Passive beamforming                        & Backscatter modulation and passive beamforming    \\
+			Cooperative transmissions     & ---                       & No (individual transmitters)                    & Active beamforming                           & ---                                        & Active beamforming and smart reflection           \\
 			\rowcolor{gray!25}
-			Cooperative reception         & ---                       & ---                       & No (separated receivers)                        & Joint detection or \gls{sic}                 & ---                                        & Backscatter detection as primary channel training \\
-			Primary detection             & ---                       & ---                       & Semi-coherent                                   & Coherent or semi-coherent                    & Coherent                                   & Coherent                                          \\
+			Cooperative reception         & ---                       & No (separated receivers)                        & Joint detection or \gls{sic}                 & ---                                        & Backscatter detection as primary channel training \\
+			Primary detection             & ---                       & Semi-coherent                                   & Coherent or semi-coherent                    & Coherent                                   & Coherent                                          \\
 			\rowcolor{gray!25}
-			Backscatter detection         & Coherent                  & Coherent                  & Semi-coherent or noncoherent                    & Coherent                                     & ---                                        & Semi-coherent                                     \\
-			Reflection state distribution & Equiprobable (line-coded) & Equiprobable (line-coded) & Equiprobable (line-coded)                       & Equiprobable or Gaussian                     & Degenerate (\gls{csi}-adaptive)            & Flexible (\gls{csi}- and traffic-adaptive)        \\
+			Backscatter detection         & Coherent                  & Semi-coherent or noncoherent                    & Coherent                                     & ---                                        & Semi-coherent                                     \\
+			Reflection state distribution & Equiprobable (line-coded) & Equiprobable (line-coded)                       & Equiprobable or Gaussian                     & Degenerate (\gls{csi}-adaptive)            & Flexible (\gls{csi}- and traffic-adaptive)        \\
 			\rowcolor{gray!25}
-			Load-switching frequency      & Fast or slow              & Fast or slow              & Fast or slow                                    & Slow                                         & Slow (dynamic) or quasi-static (blockwise) & Fast or slow                                      \\ \bottomrule
+			Load-switching frequency      & Fast or slow              & Fast or slow                                    & Slow                                         & Slow (dynamic) or quasi-static (blockwise) & Fast or slow                                      \\ \bottomrule
 		\end{tabularx}
@@
 			Interestingly, we observe that increasing $K$ has a larger benefit on the total backscatter rate than primary.
-			When multiple nodes are present, each RIScatter node is indeed performing passive beamforming for primary as well as other backscatter links.
-			To maximize the total backscatter rate, some nodes closer to the user may need to sacrifice their own rate and use the state that minimizes the primary equivalent channel strength, in order to enlarge the relative energy difference under different hypotheses of other nodes (and increase their rates).
+			This is because each RIScatter node not only affects the primary equivalent \gls{snr} but also influences the relative energy difference that other nodes can create.
+			To maximize the total backscatter rate, some nodes closer to the user may need to sacrifice their own rate and use the state that \emph{minimizes} the primary equivalent channel strength, in order to increase the backscatter rate of other nodes.
 			This accounts for the significant primary rate decrease in the low-$\rho$ regime.

### 2022-11-11 assets/illustration/energy_distribution.tex
:paintbrush: Update illustration function

@@
 
-		\addplot+[very thick,solid,color1] gnuplot[raw gnuplot] {%
+		\addplot+[very thick,solid,color1] gnuplot[raw gnuplot,smooth] {%
 				isint(x) = (int(x)==x);
@@
 
-		\addplot+[very thick,dashed,color2] gnuplot[raw gnuplot] {%
+		\addplot+[very thick,dashed,color2] gnuplot[raw gnuplot,smooth] {%
 				isint(x) = (int(x)==x);
@@
 
-		\addplot+[very thick,dotted,color3] gnuplot[raw gnuplot] {%
+		\addplot+[very thick,dotted,color3] gnuplot[raw gnuplot,smooth] {%
 				isint(x) = (int(x)==x);
@@
 
-		\addplot+[very thick,dashdotted,color4] gnuplot[raw gnuplot] {%
+		\addplot+[very thick,dashdotted,color4] gnuplot[raw gnuplot,smooth] {%
 				isint(x) = (int(x)==x);

### 2022-11-16 main.tex
:dizzy: Update literature review

@@
 % glossaries-extra
+\glsdisablehyper
 \setabbreviationstyle[acronym]{long-short}
 \newacronym{af}{AF}{Amplify-and-Forward}
-\newacronym{ambc}{AmBC}{Ambient Backscatter Communications}
+\newacronym{ambc}{AmBC}{Ambient Backscatter Communication}
 \newacronym{ap}{AP}{Access Point}
@@
 \newacronym{bcd}{BCD}{Block Coordinate Descent}
-\newacronym{bc}{BackCom}{Backscatter Communications}
+\newacronym{bc}{BackCom}{Backscatter Communication}
 \newacronym{bibo}{BIBO}{Binary-Input Binary-Output}
@@
 \newacronym{wpt}{WPT}{Wireless Power Transfer}
-\newacronym{mbc}{MBC}{Monostatic Backscatter Communications}
-\newacronym{bbc}{BBC}{Bistatic Backscatter Communications}
+\newacronym{mbc}{MBC}{Monostatic Backscatter Communication}
+\newacronym{bbc}{BBC}{Bistatic Backscatter Communication}
 \newacronym{bls}{BLS}{Backtracking Line Search}
@@
 % \title{RIScatter: Unifying BackCom, AmBC, SR and RIS From a Distribution Perspective}
-\title{RIScatter: Unifying Backscatter Communications and Reconfigurable Intelligent Surface From a Probabilistic Perspective}
 % \title{RIScatter: Unifying BackCom and RIS From a Probabilistic Perspective}
-% \title{RIScatter: Unifying Backscatter Communications, Symbiotic Radio, and Reconfigurable Intelligent Surface}
+% \title{RIScatter: Unifying Backscatter Communication, Symbiotic Radio, and Reconfigurable Intelligent Surface}
+% \title{RIScatter: Unifying Backscatter Communication and Reconfigurable Intelligent Surface From a Probabilistic Perspective}
+\title{RIScatter: Unifying Backscatter Communication and Reconfigurable Intelligent Surface From an Input Distribution Perspective}
 \author{
@@
 % ? Using RIS to encode is not very interesting as controller is anyway usable
-% * Wi-Fi sampling rate 20 MHz (symbol period 50 nS), RFID symbol rate/load switching speed 100s KHz to 10s MHz [Backscatter Communications], fast load switching speed is key for high data rate - symbol ratio is not very large
+% * Wi-Fi sampling rate 20 MHz (symbol period 50 nS), RFID symbol rate/load switching speed 100s KHz to 10s MHz [Backscatter Communication], fast load switching speed is key for high data rate - symbol ratio is not very large
 % TODO Beamforming can cancel direct interference to avoid the collapse of noncoherent energy detection and enlarge energy gap.
 % ?
-[Reconfigurable Intelligent Surface-Assisted Ambient Backscatter Communications Experimental Assessment]the authors of [5] show that, even in line-of-sight (LOS), the interferences and the desired signal can combine in such a way that the received signals at the reader side in the two states are close in power and only differ by their phases
+[Reconfigurable Intelligent Surface-Assisted Ambient Backscatter Communication Experimental Assessment]the authors of [5] show that, even in line-of-sight (LOS), the interferences and the desired signal can combine in such a way that the received signals at the reader side in the two states are close in power and only differ by their phases
 % TODO Input probability distribution for discrete-value reflection (backscatter), constellation design for continue-value reflection (RIS)
@@
 	\gls{ris} adapts its phase shift response to enhance or suppress signal strength in specific directions.
-	In this paper, we show how those two seemingly different technologies (and their derivatives) can be unified to leverage their benefits simultaneously into a single architecture called RIScatter.
-	As a new paradigm for future wireless networks, RIScatter consists of multiple dispersed or co-located passive scatter nodes whose reflection states can be adapted to partially engineer the wireless channel and partially modulate information onto the scattered wave.
-	This contrasts with \gls{bc} (resp. \gls{ris}) where states are exclusively a function of information symbols (resp. \gls{csi}).
+	In this paper, we show how both seemingly different technologies and their derivatives can be unified to leverage their benefits simultaneously into a single architecture called RIScatter.
+	Envisioned as a scatter protocol, RIScatter consists of multiple dispersed or co-located passive scatter nodes whose reflection states can be adapted to partially engineer the wireless channel and partially modulate information onto the scattered wave.
+	This contrasts with \gls{bc} (resp. \gls{ris}) where reflection states are exclusively a function of information symbols (resp. \gls{csi}).
 	The key principle in RIScatter is to render the probability distribution of reflection states as a joint function of the \gls{csi} and input information source.
-	This enables RISscatter to softly bridge, generalize, and outperform \gls{bc} and \gls{ris}; boil down to any of those under specific reflection states; or evolve in a mixed form for universal hardware design and heterogeneous traffic control.
+	This enables RISscatter to softly bridge, generalize, and outperform \gls{bc} and \gls{ris}; boil down to any of those under specific reflection states; or evolve in a mixed form for heterogeneous traffic control and universal hardware design.
 	For a single-user multi-node RIScatter network, we characterize the achievable primary-(total-)backscatter rate region by optimizing input distribution at the nodes, active beamforming at the \gls{ap}, and backscatter detection region at the user.
-	Simulation results demonstrate RIScatter nodes can exploit the additional propagation paths to smoothly transition between backscatter modulation and passive beamforming via smart input distribution design, and the proposed practical receiver effectively accommodates the double modulation and signal difference in active-passive coexisting networks.
+	Simulation results demonstrate RIScatter nodes can exploit additional propagation path to smoothly transition between backscatter modulation and passive beamforming via smart input distribution design, and the proposed practical receiver effectively accommodates the double modulation and signal difference in active-passive coexisting networks.
 \end{abstract}
@@
 		\IEEEPARstart{F}{uture} wireless network is envisioned to provide high throughput, uniform coverage, pervasive connectivity, heterogeneous control, and cognitive intelligence for trillions of portable devices.
-		As a mature low-power communication technique, \gls{bc} separates conventional transmitter into a \gls{rf} carrier emitter with power-hungry elements (e.g., synthesizer and amplifier) and an information-bearing node with power-efficient components (e.g., harvester and modulator) \cite{Boyer2014}.
-		In particular, the node harvests energy from impinging wave and embeds information over scattered signal, while the backscatter reader can be either co-located or separated with the carrier emitter, shown as \gls{mbc} and \gls{bbc} in Fig.
+		As a mature low-power communication technique, \gls{bc} separates a conventional transmitter into a \gls{rf} carrier emitter with power-hungry elements (e.g., synthesizer and amplifier) and an information-bearing node with power-efficient components (e.g., harvester and modulator) \cite{Boyer2014}.
+		In particular, the node harvests energy from impinging wave and embeds information over scattered signal, while the backscatter reader can be either co-located or separated with the carrier emitter, known as \gls{mbc} and \gls{bbc} in Fig.
 \subref*{fg:mbc} and \subref*{fg:bbc}, respectively.
-		Its applications such as \gls{rfid} \cite{Dobkin2012,Landt2005} and passive sensor network \cite{Vannucci2008,Assimonis2016} have been researched, standardized, and commercialized in the era of \gls{ioe}.
+		Its applications such as \gls{rfid} \cite{Dobkin2012,Landt2005} and passive sensor network \cite{Vannucci2008,Assimonis2016} have been extensively researched, standardized, and commercialized in the era of \gls{ioe}.
 		However, conventional \gls{bc} nodes only respond when externally inquired by a nearby reader.
-		To tackle this, \cite{Liu2013b} proposed an \gls{ambc} system in Fig.
-\subref*{fg:ambc}, where battery-free nodes recycle ambient legacy signals (e.g., radio, television and Wi-Fi) to harvest energy and establish connections in between.
-		It eliminates the need of dedicated power supply, carrier emitter and frequency spectrum, but is subject to the strong direct-link interference.
-		In \cite{Yang2018}, the authors proposed a cooperative \gls{ambc} system where both primary (legacy) and backscatter links are decoded by the same receiver under various detection schemes.
-		The concept of cooperative \gls{ambc} was further refined as \gls{sr} in Fig. \subref*{fg:sr} that cognitively incorporates \gls{ambc} with existing systems \cite{Liang2020}.
-		In a \gls{sr} system, the active transmitter generates \gls{rf} wave carrying primary information, the passive node enhances the radio propagation and superimposes its own message on the scattered signal, and the cooperative receiver jointly or sequentially decodes both links.
-		The applications above employ scatter node as information sources, and the active primary link (if exists) is subject to the influence of backscatter randomness.
-		On the other hand, \gls{ris} is a smart planar reflector that consists of numerous low-power and low-cost elements with adjustable amplitude and phase responses.
-		The reflection pattern is deterministic over time, which can be optimized and coordinated before the transmission.
-		\gls{ris} recycles and redistributes surrounding \gls{rf} waves to customize wireless propagation environment for signal enhancement, interference suppression, scattering enrichment and non-line-of-sight bypassing \cite{Wu2021b}.
+		% \cite{Liu2013b} proposed an \gls{ambc} system in Fig.
+\subref*{fg:ambc}, where battery-free nodes recycle ambient signals (e.g., radio, television and Wi-Fi) to harvest energy and establish connection in between.
+		\gls{ambc} was then proposed in \cite{Liu2013b} where battery-free nodes recycle ambient signals (e.g., radio, television and Wi-Fi) to harvest energy and establish connection in between.
+		As shown in Fig. \subref*{fg:ambc}, it eliminates the need of dedicated power supply, carrier emitter and frequency spectrum but is subject to the strong direct-link interference.
+		To tackle this, \cite{Yang2018} proposed cooperative \gls{ambc} where both primary (legacy) and backscatter links are decoded by the same receiver under various detection schemes.
+		% The concept of cooperative \gls{ambc} was further refined as \gls{sr} in Fig. \subref*{fg:sr} that cognitively incorporates \gls{ambc} with existing systems \cite{Liang2020}.
+		The concept was further refined as \gls{sr} illustrated in Fig. \subref*{fg:sr} that cognitively incorporates \gls{ambc} with existing systems \cite{Liang2020}.
+		% In a \gls{sr} system, the active transmitter generates \gls{rf} wave carrying primary information, the passive node creates extra primary propagation path and superimposes its own message on the scattered signal, while the cooperative receiver jointly or sequentially decodes both links.
+		In a \gls{sr} system, the active transmitter generates \gls{rf} wave carrying primary information, the passive node creates extra propagation path and ride its information over scattered signal, while the cooperative receiver jointly or sequentially decodes both links.
+		Those \gls{bc} applications employ scatter nodes as pure information sources such that the active primary link (if it exists) is influenced by backscatter randomness (often modelled as interference or channel uncertainty).
+		On the other hand, \gls{ris} is a smart planar wave reflector that consists of numerous compact passive elements with adjustable amplitude and phase responses.
+		The reflection pattern is deterministic over time that can be optimized and coordinated before the transmission.
+		\gls{ris} recycles and redistributes surrounding \gls{rf} waves to customize the wireless propagation environment for signal enhancement, interference suppression, scattering enrichment and non-line-of-sight bypassing \cite{Wu2021b}.
 		A comparison of different scattering applications is summarized in Table \ref{tb:scattering_applications}.
@@
 		Similar to \gls{cr}, the coexistence of primary and backscatter links in \gls{sr} can be classified into commensal, parasitic, and competitive relationships, whose instantaneous rates, power schemes, and outage probabilities were acquired in \cite{Guo2019b,Ding2020}.
-		To evaluate the performance of cooperative receivers, \cite{Yang2018} derived the bit error rates of \gls{ml} and \gls{sic} detectors for flat fading channels, and proposed a low-complexity detector for frequency-selective fading channels.
-		However, it only considered the case where the primary and backscatter symbols of the same period are perfectly aligned in time.
-		Joint \gls{ml} decoding can achieve the best error performance but comes with prohibitive computational complexity especially for sources with high-order constellation \cite{Yang2018,Liang2020,Zhang2022}.
-		One special property of active-passive coexisting network is the backscatter signal strength is significantly weaker than primary due to the double fading effect.
-		It motivated \cite{Long2020a,Liang2020,Guo2019b,Ding2020,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Yang2018,Han2021,Zhang2022} to view \gls{sr} as a multiplicative \gls{noma} and perform sequential primary-backscatter decoding based on \gls{sic}.
-		During primary decoding, the randomness from backscatter modulation can be modelled as either interference or channel uncertainty, depending on the relationship between the primary sampling rate and backscatter switching speed.
-		If the former is much higher (i.e., commensal \gls{sr}), the average primary achievable rate under noncoherent detection would asymptotically approach its coherent counterpart \cite{Long2020a}, and both links may be decoded in an interference-free manner.
-		However, the assumption of very large backscatter-over-primary symbol period ratio $N$ may not hold in practice \footnote{For example, Wi-Fi sampling rate is \qty{20}{\MHz} while \gls{rfid} load switching speed varies between \num{100}s of \unit{\kHz} to \num{10}s of \unit{\MHz} \cite{Torres2021}, corresponding to a typical $N$ between \num{1} and \num{100}.}, and such a \gls{sic}-based sequential decoding requires re-encoding, precoding, and subtraction at each primary symbol block with a time-domain \gls{mrc}, which can be operation-intensive and \gls{csi}-sensitive.
-		Another open issue for \gls{bc} and \gls{sr} is efficient node multiple access.
-		\cite{Xu2021a} proposed a \gls{noma}-based \gls{sr} where the \gls{sic} order depends on the backscatter channel strength, and the performance deteriorates fast as the number of nodes increases.
+		% To evaluate the performance of cooperative receivers, \cite{Yang2018} derived the bit error rates of \gls{ml}, linear and \gls{sic} detectors for flat fading channels, and proposed a low-complexity detector for frequency-selective fading channels.
+		% However, it only considered the case where the primary and backscatter symbols of the same period are perfectly aligned in time.
+		% However, it assumed the primary and backscatter symbols of the same period are perfectly aligned in time.
+		Joint \gls{ml} decoding provides the best error performance for \gls{sr} but requires prohibitive computational complexity especially for high-order modulations \cite{Yang2018}.
+		One special property of such an active-passive coexisting network is that the backscatter signal strength can be relatively weak due to the double fading effect.
+		It motivated \cite{Long2020a,Liang2020,Guo2019b,Ding2020,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Yang2018,Han2021,Zhang2022} to view \gls{sr} as a multiplicative \gls{noma} and perform \gls{sic} from primary to backscatter link.
+		% sequential primary-backscatter decoding based on \gls{sic}.
+		During primary decoding, the backscatter randomness can be modelled as either interference or channel uncertainty, depending on the ratio $N$ of primary sampling rate over backscatter switching speed\footnote{For state-of-the-art low-power \gls{rfid} tags, the load switching speed typically varies between \num{100}s of \unit{\kHz} to \num{10}s of \unit{\MHz} \cite{Torres2021}}.
+		Such a sequential \gls{sic} involves $N$ re-encoding, precoding, subtraction together with a time-domain \gls{mrc} to decode each backscatter symbol, which can be operation-intensive and \gls{csi}-sensitive.
+		When $N$ is sufficiently large (i.e., commensal \gls{sr}), the average primary achievable rate under noncoherent detection asymptotically approaches its coherent counterpart, and both links can be decoded in an interference-free manner \cite{Long2020a}.
+		% However, the assumption of very large backscatter-over-primary symbol period ratio $N$ may not hold in practice\footnote{For example, Wi-Fi sampling rate is \qty{20}{\MHz} while \gls{rfid} load switching speed varies between \num{100}s of \unit{\kHz} to \num{10}s of \unit{\MHz} \cite{Torres2021}, corresponding to a typical $N$ between \num{1} and \num{100}.}, and such a \gls{sic}-based sequential decoding requires re-encoding, precoding, and subtraction at each primary symbol block with a time-domain \gls{mrc}, which can be operation-intensive and \gls{csi}-sensitive.
+		Another open issue for \gls{bc} and \gls{sr} is efficient backscatter multiple access design.
+		\cite{Xu2021a} proposed a \gls{noma}-based \gls{sr} where the \gls{sic} order depends on the backscatter channel strength, but the performance deteriorates fast as the number of nodes increases.
 		\gls{tdma}-based \gls{sr} was also considered in \cite{Yang2021a} where each node transmits information during its dedicated slot and harvests energy during others.
-		It enables adaptive transmission time and reflection ratio optimization but requires regular coordination and incurs high coordination cost.
-		\cite{Vougioukas2019} controls the load-switching speed to shift the scattered signal to the desired frequency band.
+		It enables adaptive transmission time and reflection ratio optimization but incurs high coordination cost.
+		\cite{Vougioukas2019} modifies the load-switching speed to shift the scattered signal to the desired frequency band.
 		This enables backscatter \gls{fdma} at the cost of extra bandwidth and higher node power consumption.
@@
 		However, this code-domain solution suffers from the near-far problem and imperfect synchronization.
-		On the other hand, conventional \gls{ris} design with fixed reflection coefficients during each channel block has been extensively studied in communication, sensing, and power literatures \cite{Wu2018,Zhang2019a,Lin2022,Liu2022,Feng2022,Zhao2022}.
-		Dynamic \gls{ris}, which employs independent reflection patterns during different time slots, has gained recent attentions in multi-user and multi-purpose wireless networks.
-		The concept was first proposed in \cite{Yang2020} to fine tune the resource blocks for \gls{ofdm} systems, then extended to the downlink power and uplink information phases of \gls{wpcn} \cite{Wu2021,Wu2021d,Hua2022a}.
-		It creates artificial channel diversity and enables flexible resource allocation, but misses the opportunity to encode its own message.
-		\gls{ris} can also be used a transmitter when placed in the near field of a carrier emitter, and prototypes for \gls{psk} and \gls{qam} have been implemented in \cite{Tang2019a,Dai2020a}.
-		From an information-theoretic perspective, \cite{Karasik2020} reported using \gls{ris} as a passive beamformer to maximize the \gls{snr} is generally rate-suboptimal for finite input constellations.
-		Instead, the capacity of \gls{ris}-aided channel is achieved by joint transmitter-\gls{ris} encoding, and multiplication coding with \gls{sic} decoding (i.e., \gls{sic}-based \gls{sr}) can outperform pure passive beamforming at high \gls{snr}.
-		It inspired \cite{Liu2019d,Bereyhi2020,Xu2020b,Zhang2021d,Hu2021b,Hua2022,Basar2020,Ma2020a,Yuan2021,Hu2021a} to combine passive beamforming and backscatter modulation in the overall reflection pattern.
-		In particular, \emph{symbol level precoding} maps backscatter symbols to optimized \gls{ris} coefficient sets \cite{Liu2019d,Bereyhi2020}, \emph{overlay modulation} superposes information-bearing symbols over a common auxiliary matrix \cite{Xu2020b,Zhang2021d,Hu2021b,Hua2022}, \emph{spatial modulation} switches between reflection coefficient sets that maximize \gls{snr} at different receive antennas \cite{Basar2020,Ma2020a,Yuan2021}, and \emph{index modulation} employs dedicated reflection elements for passive beamforming and dedicated information elements for backscatter modulation \cite{Hu2021a}.
-		Those \gls{ris}-empowered \gls{bc} designs involve advanced hardware architecture and high optimization complexity.
-		Besides, all relevant literatures consider either Gaussian codebook \cite{Guo2019b,Ding2020,Long2020a,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Hu2021b} or finite equiprobable inputs \cite{Yang2018,Liang2020,Han2021,Zhang2022,Liu2019d,Bereyhi2020,Xu2020b,Zhang2021d,Hua2022,Basar2020,Ma2020a,Yuan2021,Hu2021a} for backscatter information sources.
-		The former is impractical for passive backscatter devices while the latter does not fully exploit \gls{csi} and signal characteristics.
+
+		Conventional \gls{ris} design with fixed reflection coefficients during each channel block has been extensively studied in communication, sensing, and power literatures \cite{Wu2018,Zhang2019a,Lin2022,Liu2022,Feng2022,Zhao2022}.
+		On the other hand, dynamic \gls{ris} with independent reflection patterns at different frames has gained recent attentions in multi-user and multi-purpose wireless networks.
+		The concept was first proposed in \cite{Yang2020} to fine-tune the \gls{ofdm} resource blocks, then extended to the downlink power and uplink information phases of \gls{wpcn} \cite{Wu2021,Wu2021d,Hua2022a}.
+		It introduces artificial channel diversity and enables flexible resource allocation, but misses the opportunity to encode its own message.
+		\gls{ris} can also be used as a transmitter when placed in the near field of a carrier emitter, and prototypes for \gls{psk} and \gls{qam} have been implemented in \cite{Tang2019a,Dai2020a}.
+		From an information-theoretic perspective, \cite{Karasik2020} reported that using \gls{ris} as a naive passive beamformer to maximize the \gls{snr} is generally rate-suboptimal for finite input constellations.
+		Instead, the capacity of \gls{ris}-aided channel is achieved by joint transmitter-\gls{ris} encoding, and multiplication coding with \gls{sic} decoding (i.e., \gls{sic}-based \gls{sr}) can outperform passive beamforming at high \gls{snr}.
+		It inspired \gls{ris}-empowered \gls{bc} \cite{Liu2019d,Bereyhi2020,Xu2020b,Zhang2021d,Hu2021b,Hua2022,Basar2020,Ma2020a,Yuan2021,Hu2021a} to combine passive beamforming and backscatter modulation in the overall reflection pattern.
+		In particular, \emph{symbol level precoding} maps the information symbols to the optimized \gls{ris} coefficient sets \cite{Liu2019d,Bereyhi2020}, \emph{overlay modulation} superposes the information symbols over a common auxiliary matrix \cite{Xu2020b,Zhang2021d,Hu2021b,Hua2022}, \emph{spatial modulation} switches between the reflection coefficient sets that maximize \gls{snr} at different receive antennas \cite{Basar2020,Ma2020a,Yuan2021}, and \emph{index modulation} employs dedicated reflection elements (resp.
+information elements) for passive beamforming (resp.
+backscatter modulation) \cite{Hu2021a}.
+		% Those smart passive reflect elements/scatter nodes can recycle electromagnetic wave on the air to boost wireless channels and establish new connections, but incurs advanced hardware architecture and high optimization complexity.
+		% Those \gls{ris}-empowered \gls{bc} can recycle electromagnetic wave on the air to simultaneously boost wireless channels and establish new connections, but the reflect elements or scatter nodes incurs advanced hardware architecture and high optimization complexity.
+		Those \gls{ris}-empowered \gls{bc} designs can recycle electromagnetic wave on the air to simultaneously boost wireless channels and establish new connections, but incurs advanced hardware architecture and high optimization complexity.
+		% the reflect elements or scatter nodes incurs advanced hardware architecture and high optimization complexity.
+		% For backscatter information sources,
+		% Besides,
+		% Relevant literatures also consider either Gaussian codebook \cite{Guo2019b,Ding2020,Long2020a,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Hu2021b} or finite equiprobable inputs \cite{Yang2018,Liang2020,Han2021,Zhang2022,Liu2019d,Bereyhi2020,Xu2020b,Zhang2021d,Hua2022,Basar2020,Ma2020a,Yuan2021,Hu2021a} for backscatter information sources.
+		% The former is impractical for passive backscatter devices while the latter does not fully exploit \gls{csi} and signal characteristics.
 	\end{subsection}
@@
 	\begin{subsection}{Contributions}
-		As presented in Fig. \subref*{fg:riscatter}, we propose RIScatter as a novel scattering protocol that generalizes \gls{bc} and \gls{ris}.
-		The contributions of this paper are summarized as follows.
+		% The concept of RIScatter is illustrated in Fig. \subref*{fg:riscatter} and the contributions of this paper are summarized below.
+		% As presented in Fig. \subref*{fg:riscatter}, we envision RIScatter as a novel scatter protocol that generalizes \gls{bc} and \gls{ris}.
+		% We envision RIScatter in Fig. \subref*{fg:riscatter} as a novel scatter protocol that generalizes \gls{bc} and \gls{ris}.
+		% The contributions of this paper are summarized below.
 
 		\emph{First,} we propose RIScatter nodes that adapt the reflection state distribution of passive scatter devices based on \gls{csi} and link weights, in order to flexibly transition between backscatter modulation and passive beamforming.
-		Scattering sources of \gls{bc} and reflecting elements of \gls{ris} can be regarded as special cases with uniform and degenerate input distributions, respectively.
+		Scatter node of \gls{bc} and reflect elements of \gls{ris} can be regarded as special cases with uniform and degenerate input distributions, respectively.
 		On the contrary, adaptive RIScatter encoding boils down to deterministic \gls{ris} when primary link is prioritized, and achieves higher backscatter rate than conventional line coding when backscatter link is prioritized.
@@
 
-		\emph{Second,} we propose a practical receiver that accommodates the double modulation and signal difference in active-passive coexisting network.
+		\emph{First,} we propose RIScatter that unifies \gls{bc} and \gls{ris} and leverages their benefits from an input distribution perspective.
+		The concept is presented in Fig. \subref*{fg:riscatter}.
+		In part
+
+		multiple dispersed or co-located passive scatter nodes whose
+
+		\gls{bc} nodes harvest energy from and modulate information over an external electromagnetic wave.
+		% \gls{sr} incorporates a passive scatter node into existing radio networks to create additional propagation path and ride its own information towards the cooperative receiver.
+		% \gls{ris} is a programmable reflector array that adapts the phase shift response to enhance or suppress signal strength in specific directions.
+		\gls{ris} adapts its phase shift response to enhance or suppress signal strength in specific directions.
+		In this paper, we show how both seemingly different technologies and their derivatives can be unified to leverage their benefits simultaneously into a single architecture called RIScatter.
+		Envisioned as a scatter protocol, RIScatter consists of multiple dispersed or co-located passive scatter nodes whose reflection states can be adapted to partially engineer the wireless channel and partially modulate information onto the scattered wave.
+		This contrasts with \gls{bc} (resp. \gls{ris}) where reflection states are exclusively a function of information symbols (resp. \gls{csi}).
+		The key principle in RIScatter is to render the probability distribution of reflection states as a joint function of the \gls{csi} and input information source.
+		This enables RISscatter to softly bridge, generalize, and outperform \gls{bc} and \gls{ris}; boil down to any of those under specific reflection states; or evolve in a mixed form for heterogeneous traffic control and universal hardware design.
+
+		\emph{Second,} we propose a practical receiver that accommodates the double modulation and signal difference in active-passive coexisting networks.
 		Since the primary and backscatter messages are superimposed by multiplication coding and the backscatter symbol is typically longer than primary, the scattered signals from RIScatter nodes can be treated as multipath components during primary decoding, and the primary symbols can be viewed as a spreading code during backscatter decoding.
@@
 	$\boldsymbol{0}$ and $\boldsymbol{1}$ denote zero and one array of appropriate size, respectively.
-$\mathbb{I}^{x \times y}$, $\mathbb{R}_+^{x \times y}$, and $\mathbb{C}^{x \times y}$ denote the unit, real nonnegative, and complex spaces of dimension $x \times y$, respectively.
+$\mathbb{I}^{x \times y}$, $\mathbb{R}_+^{x \times y}$, and $\mathbb{C}^{x \times y}$ denote the real unit, real nonnegative, and complex spaces of dimension $x \times y$, respectively.
 	$j$ denotes the imaginary unit.
@@
 	where $\alpha \in \mathbb{I}$ is the amplitude scattering ratio at the direction of interest.
-	In contrast, \gls{ris} employ reflecting elements as channel reconfigurators that enable constructive/destructive signal superposition by \emph{deterministically choosing} the reflection pattern.
+	In contrast, \gls{ris} employ reflect elements as channel reconfigurators that enable constructive/destructive signal superposition by \emph{deterministically choosing} the reflection pattern.
 	For a \gls{ris} element with $M$ available states, phase shift $\theta_m$ maps to reflection coefficient $\Gamma_m$ by \cite{Wu2018}
@@
 	\end{equation}
-	where $\beta_m \in \mathbb{I}$ is the amplitude scattering ratio of state $m$.\footnote{Most existing \gls{ris} literatures assume lossless reflection $\beta_m=1$, $\forall m$.}
+	where $\beta_m \in \mathbb{I}$ is the overall amplitude scattering ratio of state $m$.\footnote{Most existing \gls{ris} literatures assume lossless reflection $\beta_m=1$, $\forall m$.}
 \end{section}
@@
 	\begin{subsection}{Concepts}
-		As a generalization of \gls{bc} and \gls{ris}, RIScatter is a passive scattering protocol that coexists with an active primary system in a flexible and mutualistic manner.
+		As a generalization of \gls{bc} and \gls{ris}, RIScatter is a passive scatter protocol that coexists with an active primary system in a flexible and mutualistic manner.
 		RIScatter nodes leverage \gls{csi}- and weight-based input distribution design to smoothly transition between backscatter modulation and passive beamforming.
@@
 			The solid and dashed vectors represent signal and energy flows.
-			The scattering antenna behaves as a constant power source, where the voltage $V_0$ and current $I_0$ are introduced by incident electric field $\vec{E}_{\mathrm{I}}$ and magnetic field $\vec{H}_{\mathrm{I}}$ \cite{Huang2021}.
+			The scatter antenna behaves as a constant power source, where the voltage $V_0$ and current $I_0$ are introduced by incident electric field $\vec{E}_{\mathrm{I}}$ and magnetic field $\vec{H}_{\mathrm{I}}$ \cite{Huang2021}.
 			}
@@
 				Superposition coding and \gls{sic} was originally proposed to achieve the capacity vertices of Gaussian \gls{mac}.
-				For active-passive coexisting network, \gls{sic} not only fails to utilize the multiplication coding/double modulation, but also requires $N$ re-encoding, precoding and subtraction with a time-domain \gls{mrc} during each backscatter block.
+				For active-passive coexisting networks, \gls{sic} not only fails to utilize the multiplication coding/double modulation, but also requires $N$ re-encoding, precoding and subtraction with a time-domain \gls{mrc} during each backscatter block.
 			}
@@
 \begin{section}{Conclusion}
-	This paper introduced RIScatter as a low-power scattering protocol that unifies backscatter modulation and dymanic passive beamforming by smart input distribution and practical receiver design.
-	Starting from scattering principles, we showed how RIScatter nodes include scattering source of \gls{bc} and reflecting element of \gls{ris} as special cases, how they can be built over existing passive scatter devices, and how they simultaneously encode self information and assist legacy transmission.
+	This paper introduced RIScatter as a low-power scatter protocol that unifies backscatter modulation and dymanic passive beamforming by smart input distribution and practical receiver design.
+	Starting from scattering principles, we showed how RIScatter nodes include information node of \gls{bc} and reflect element of \gls{ris} as special cases, how they can be built over existing passive scatter devices, and how they simultaneously encode self information and assist legacy transmission.
 	We also propose a low-complexity RIScatter receiver that preserves the benefits of backscatter modulation and passive beamforming.

### 2022-11-16 main.tex
:dizzy: Contribution 1

@@
 		% Those \gls{ris}-empowered \gls{bc} can recycle electromagnetic wave on the air to simultaneously boost wireless channels and establish new connections, but the reflect elements or scatter nodes incurs advanced hardware architecture and high optimization complexity.
-		Those \gls{ris}-empowered \gls{bc} designs can recycle electromagnetic wave on the air to simultaneously boost wireless channels and establish new connections, but incurs advanced hardware architecture and high optimization complexity.
+		Those \gls{ris}-empowered \gls{bc} designs can recycle electromagnetic wave on the air and employ scattered paths to boost wireless channels and establish new connections, but incurs advanced hardware architecture and high optimization complexity.
 		% the reflect elements or scatter nodes incurs advanced hardware architecture and high optimization complexity.
@@
 
-		\emph{First,} we propose RIScatter nodes that adapt the reflection state distribution of passive scatter devices based on \gls{csi} and link weights, in order to flexibly transition between backscatter modulation and passive beamforming.
-		Scatter node of \gls{bc} and reflect elements of \gls{ris} can be regarded as special cases with uniform and degenerate input distributions, respectively.
-		On the contrary, adaptive RIScatter encoding boils down to deterministic \gls{ris} when primary link is prioritized, and achieves higher backscatter rate than conventional line coding when backscatter link is prioritized.
-		Multiple RIScatter nodes can be either co-located to enable joint distribution design for improved total backscatter rate, or dispersed to guarantee uniformly good performance for both links.
-
-		\emph{First,} we propose RIScatter that unifies \gls{bc} and \gls{ris} and leverages their benefits from an input distribution perspective.
-		The concept is presented in Fig. \subref*{fg:riscatter}.
-		In part
-
-		multiple dispersed or co-located passive scatter nodes whose
-
-		\gls{bc} nodes harvest energy from and modulate information over an external electromagnetic wave.
-		% \gls{sr} incorporates a passive scatter node into existing radio networks to create additional propagation path and ride its own information towards the cooperative receiver.
-		% \gls{ris} is a programmable reflector array that adapts the phase shift response to enhance or suppress signal strength in specific directions.
-		\gls{ris} adapts its phase shift response to enhance or suppress signal strength in specific directions.
-		In this paper, we show how both seemingly different technologies and their derivatives can be unified to leverage their benefits simultaneously into a single architecture called RIScatter.
-		Envisioned as a scatter protocol, RIScatter consists of multiple dispersed or co-located passive scatter nodes whose reflection states can be adapted to partially engineer the wireless channel and partially modulate information onto the scattered wave.
-		This contrasts with \gls{bc} (resp. \gls{ris}) where reflection states are exclusively a function of information symbols (resp. \gls{csi}).
-		The key principle in RIScatter is to render the probability distribution of reflection states as a joint function of the \gls{csi} and input information source.
-		This enables RISscatter to softly bridge, generalize, and outperform \gls{bc} and \gls{ris}; boil down to any of those under specific reflection states; or evolve in a mixed form for heterogeneous traffic control and universal hardware design.
+		% \emph{First,} we propose RIScatter nodes that adapt the reflection state distribution of passive scatter devices based on \gls{csi} and link weights, in order to flexibly transition between backscatter modulation and passive beamforming.
+		% Scatter node of \gls{bc} and reflect elements of \gls{ris} can be regarded as special cases with uniform and degenerate input distributions, respectively.
+		% On the contrary, adaptive RIScatter encoding boils down to deterministic \gls{ris} when primary link is prioritized, and achieves higher backscatter rate than conventional line coding when backscatter link is prioritized.
+		% Multiple RIScatter nodes can be either co-located to enable joint distribution design for improved total backscatter rate, or dispersed to guarantee uniformly good performance for both links.
+
+		\emph{First,} we propose RIScatter as a novel scatter protocol that unifies \gls{bc} and \gls{ris} from a distribution perspective.
+		As shown in Fig. \subref*{fg:riscatter}, the passive RIScatter node rides over an active transmission and controls the scattered wave to
+		partially engineer the wireless channel and partially modulate its own information.
+		This is accomplished by incorporating both the \gls{csi} and link weights into the reflection state distribution design.
+		As such, RIScatter can generalize \gls{bc} (uniform distribution) and \gls{ris} (degenerate distribution) to create a tradeoff between backscatter modulation and passive beamforming.
+		This is the first paper to associate \gls{bc} and \gls{ris} from a distribution perspective.
+		% heterogeneous traffic control and universal hardware design
+
+		% I think you need to reemphasize what is the abstract and explain it further in light of the general observations you have drawn from the related works
+		% IScatter design compared to backcom and RIS. How to tackle those challenges would then be explained in the subsequent contributions.
 

### 2022-11-17 main.tex
:speech_balloon: Add TODOs

@@
 % TODO  binary input and signal output (BISO) channel, ML figure
+
+% ! add table row: adaptive to information source/csi/link weights
+% ! explain link weights
+% ! add table row: distributions
+% ! table to sentences
+% ! add primary and backscatter flows to illustrations
+% ! discuss table and add challenges in contribution 1
+% ! transition challenges (distribution and constellation-adaptive) to contribution 2, 3
+% ! think RIScatter applications (use Rui's slides)
 \begin{abstract}

### 2022-11-25 assets/illustration/ambc.tex
:lipstick: Update illustrations

--- 2022-08-31 assets/illustration/ambient_backscatter_communication.tex
@@
 
-	\node[draw=none] at (0,-1.375) {Legacy\\Transmitter};
+	\node[draw=none] at (0,-1.375) {Primary\\Transmitter};
 	\node[draw=none] at (1,4.375) {Backscatter\\Reader};
-	\node[draw=none] at (7,4.375) {Scattering\\Node};
-	\node[draw=none] at (8,-1.375) {Legacy\\Receiver};
+	\node[draw=none] at (7,4.375) {Scatter\\Node};
+	\node[draw=none] at (8,-1.375) {Primary\\Receiver};
 
-	\draw[decorate,decoration={waves,segment length=5mm}] (1,-0.5) -- (7.5,-0.5);
-	\draw[decorate,decoration={waves,segment length=5mm}] (0.25,1) -- (0.75,3);
-	\draw[decorate,decoration={waves,segment length=5mm}] (0.75,0.25) -- (5.5,2.5);
-	\draw[decorate,decoration={triangles,segment length=2.5mm}] (5.5,3.5) -- (2.5,3.5);
-	\draw[decorate,decoration={triangles,segment length=2.5mm}] (7.5,3) -- (8,1);
+	\draw[blue,decorate,decoration={waves,segment length=4mm,radius=2mm}] (1,-0.5) -- (7.5,-0.5);
+	\draw[lightgray,decorate,decoration={waves,segment length=4mm,radius=2mm}] (0.25,1) -- (0.75,3);
+	\draw[lightgray,decorate,decoration={waves,segment length=4mm,radius=2mm}] (0.75,0.25) -- (5.5,2.5);
+	\draw[lightgray,decorate,decoration={waves,segment length=4mm,radius=2mm}] (5.5,3.5) -- (2.5,3.5);
+	\draw[magenta,decorate,decoration={crosses,segment length=8mm,shape size=1.5mm}] (5.11,3.5) -- (2.5,3.5);
+	\draw[lightgray,decorate,decoration={waves,segment length=4mm,radius=2mm}] (7.43,3.28) -- (8,1);
+	\draw[lightgray,decorate,decoration={crosses,segment length=8mm,shape size=1.5mm}] (7.525,2.9) -- (8,1);
 
-	\node[draw=none] at (4,0.35) {Modulated\\Signal};
-	\node[draw=none] at (4,3.5) {Superimposed\\Signal};
+	\node[draw=none] at (4,0.35) {Modulated};
+	\node[draw=none] at (4,3.95) {Doubly-};
+	\node[draw=none] at (4,3) {Modulated};
 \end{tikzpicture}

### 2022-11-25 assets/illustration/bbc.tex
:lipstick: Update illustrations

@@
 	\node[draw=none] at (0,-1.95) {Carrier\\Emitter};
-	\node[draw=none] at (5,3.35) {Scattering\\Node};
+	\node[draw=none] at (5,3.35) {Scatter\\Node};
 	\node[draw=none] at (8,-1.95) {Backscatter\\Reader};
 
-	\draw[decorate,decoration={snake,post length=2.5mm},-latex] (1,-1) -- (7.5,-1);
-	\draw[decorate,decoration={snake,post length=2.5mm},-latex] (0.5,0) -- (4,2);
-	\draw[decorate,decoration={snake,pre length=7.5mm,post length=7.5mm},-latex] (6,2) -- (8,0.35);
+	\draw[lightgray,decorate,decoration={snake,post length=2.5mm},-latex] (1,-1) -- (7.5,-1);
+	\draw[lightgray,decorate,decoration={snake,post length=2.5mm},-latex] (0.5,0) -- (4,2);
+	\draw[magenta,decorate,decoration={snake,pre length=7.5mm,post length=7.5mm},-latex] (6,2) -- (8,0.35);
 

### 2022-11-25 assets/illustration/discrete_outputs.tex
:lipstick: Update illustrations

@@
 \begin{tikzpicture}
-	\begin{axis}[width=10cm,height=5cm,xmin=0,xmax=6.5,xlabel=$z$,axis x line=middle,axis y line=none,xtick={0,2,3,4,6},xticklabels={$t_0$,$t_1$,$t_2$,$t_3$,$t_4$},xtick style={draw=none},every axis x label/.style={at=(current axis.right of origin),anchor=west},domain=0:6]
+	\begin{axis}[width=10cm,height=5cm,xmin=0,xmax=6.5,ymin=-0.1,ymax=0.1,xlabel=$z$,axis x line=middle,axis y line=none,xtick={0,2,3,4,6},xticklabels={$t_0$,$t_1$,$t_2$,$t_3$,$t_4$},xtick style={draw=none},every axis x label/.style={at=(current axis.right of origin),anchor=west},domain=0:6]
 		\addplot[mark=*,mark size=0.5pt,only marks,color=gray] {0};

### 2022-11-25 assets/illustration/mbc.tex
:lipstick: Update illustrations

@@
 	\node[draw=none] at (0,-1.125) {Interrogator};
-	\node[draw=none] at (8,4.375) {Scattering\\Node};
+	\node[draw=none] at (8,4.375) {Scatter\\Node};
 
-	\draw[decorate,decoration={snake,post length=2.5mm},-latex] (0.5,0.75) -- (7,3);
-	\draw[decorate,decoration={snake,pre length=2cm,post length=2cm},-latex] (7.25,2.25) -- (0.75,0);
+	\draw[lightgray,decorate,decoration={snake,post length=2.5mm},-latex] (0.5,0.75) -- (7,3);
+	\draw[magenta,decorate,decoration={snake,pre length=2cm,post length=2cm},-latex] (7.25,2.25) -- (0.75,0);
 

### 2022-11-25 assets/illustration/ris.tex
:lipstick: Update illustrations

@@
 	\node[draw=none] at (0,-1) {Transmitter};
-	\node[draw=none] at (5,4.4375) {Reflecting\\Element};
+	\node[draw=none] at (5,4.4375) {Reflect\\Element};
 	\node[draw=none] at (8,-1) {Receiver};
 
-	\draw[decorate,decoration={waves,segment length=5mm}] (1,-0.25) -- (7.375,-0.25);
-	\draw[decorate,decoration={waves,segment length=5mm}] (0.5,0.75) -- (4,3);
-	\draw[decorate,decoration={waves,segment length=5mm}] (6,3) -- (8,1.25);
+	\draw[blue,decorate,decoration={waves,segment length=4mm,radius=2mm}] (1,-0.25) -- (7.375,-0.25);
+	\draw[blue,decorate,decoration={waves,segment length=4mm,radius=2mm}] (0.5,0.75) -- (4,3);
+	\draw[blue,decorate,decoration={waves,segment length=4mm,radius=2mm}] (6,3.1625) -- (8,1.25);
 
-	\node[draw=none] at (4.875,1.125) {Modulated\\Signal};
+	\node[draw=none] at (4.625,1) {Modulated};
 \end{tikzpicture}

### 2022-11-25 assets/illustration/riscatter.tex
:bento: Update scattering paradigms
:lipstick: Update illustrations

@@
 	\node[draw=none] at (5,4.5) {RIScatter\\Node};
-	\node[draw=none] at (8,-1.25) {Cooperative\\Receiver};
+	\node[draw=none] at (8,-1.25) {Co-located\\Receiver};
 
-	\draw[decorate,decoration={waves,segment length=5mm}] (1,-0.25) -- (7.375,-0.25);
-	\draw[decorate,decoration={waves,segment length=5mm}] (0.5,0.75) -- (4,3);
-	\draw[decorate,decoration={triangles,segment length=2.5mm}] (6,3) -- (8,1.25);
+	\draw[blue,decorate,decoration={waves,segment length=4mm,radius=2mm}] (1,-0.25) -- (7.375,-0.25);
+	\draw[blue,decorate,decoration={waves,segment length=4mm,radius=2mm}] (0.5,0.75) -- (4,3);
+	\draw[blue,decorate,decoration={waves,segment length=4mm,radius=2mm}] (6,3.1625) -- (8,1.25);
+	\draw[green,decorate,decoration={crosses,segment length=8mm,shape size=1.5mm}] (6.29,2.885) -- (8,1.25);
 
-	\node[draw=none] at (4,0.875) {Modulated\\Signal};
-	\node[draw=none] at (7.8,2.9) {Superimposed\\Signal};
+	\node[draw=none] at (3.5,0.75) {Modulated};
+	\node[draw=none] at (8,2.76) {Flexible};
 \end{tikzpicture}

### 2022-11-25 assets/illustration/sr.tex
:paintbrush: Update illustrations
:lipstick: Update illustrations

--- 2022-08-31 assets/illustration/symbiotic_radio.tex
@@
 	\node[draw=none] at (0,-1.25) {Primary\\Transmitter};
-	\node[draw=none] at (5,4.375) {Scattering\\Node};
-	\node[draw=none] at (8,-1.25) {Cooperative\\Receiver};
+	\node[draw=none] at (5,4.375) {Scatter\\Node};
+	\node[draw=none] at (8,-1.25) {Co-located\\Receiver};
 
-	\draw[decorate,decoration={waves,segment length=5mm}] (1,-0.25) -- (7.375,-0.25);
-	\draw[decorate,decoration={waves,segment length=5mm}] (0.5,0.75) -- (4,3);
-	\draw[decorate,decoration={triangles,segment length=2.5mm}] (6,3) -- (8,1.25);
+	\draw[blue,decorate,decoration={waves,segment length=4mm,radius=2mm}] (1,-0.25) -- (7.375,-0.25);
+	\draw[blue,decorate,decoration={waves,segment length=4mm,radius=2mm}] (0.5,0.75) -- (4,3);
+	\draw[blue,decorate,decoration={waves,segment length=4mm,radius=2mm}] (6,3.1625) -- (8,1.25);
+	\draw[magenta,decorate,decoration={crosses,segment length=20mm,shape size=1.5mm}] (6.29,2.885) -- (8,1.25);
 
-	\node[draw=none] at (4,0.875) {Modulated\\Signal};
-	\node[draw=none] at (7.8,2.9) {Superimposed\\Signal};
+	\node[draw=none] at (3.5,0.75) {Modulated};
+	\node[draw=none] at (8,3.15) {Doubly-\\Modulated};
 \end{tikzpicture}

### 2022-11-25 main.tex
:lipstick: Update illustrations

@@
 
+\usepackage[table]{xcolor}
 \usepackage{adjustbox}
@@
 \usepackage{tikz}
-\usepackage{xcolor}
-\usepackage{colortbl}
 % dark mode
@@
 \begin{document}
-% \title{RIScatter: Unifying Scattering Techniques From a Distribution Perspective}
-% \title{RIScatter: Unifying BackCom, AmBC, SR and RIS From a Distribution Perspective}
-% \title{RIScatter: Unifying BackCom and RIS From a Probabilistic Perspective}
-% \title{RIScatter: Unifying Backscatter Communication, Symbiotic Radio, and Reconfigurable Intelligent Surface}
-% \title{RIScatter: Unifying Backscatter Communication and Reconfigurable Intelligent Surface From a Probabilistic Perspective}
-\title{RIScatter: Unifying Backscatter Communication and Reconfigurable Intelligent Surface From an Input Distribution Perspective}
+\title{RIScatter: Unifying Backscatter Communication and Reconfigurable Intelligent Surface From a Distribution Perspective}
 \author{
@@
 		Yang~Zhao,~\IEEEmembership{Member,~IEEE,}
-		and~Bruno~Clerckx,~\IEEEmembership{Fellow,~IEEE}
+		and~Bruno~Clerckx,~\IEEEmembership{Fellow,~IEEE,}
+		TODO
 	}
 	\thanks{
-		The authors are with the Department of Electrical and Electronic Engineering, Imperial College London, London SW7 2AZ, U.K. (e-mail: \{yang.zhao18, b.clerckx\}@imperial.ac.uk).
+		The authors are with the Department of Electrical and Electronic Engineering, Imperial College London, London SW7 2AZ, U.K. (e-mail: \{yang.zhao18, b.clerckx,TODO\}@imperial.ac.uk).
 	}
@@
 % ? For Backscatter community: why not adaptive channel coding? For RIS community: why not add randomness for modulation?
-% TODO RIS involves nonlinear circuits (e.g., diodes) and impedance design (i.e., perfect mismatching) is tricky for continuous phase shift; discrete candidate set is preferred (2-3 bits optimal)
+% ? RIS involves nonlinear circuits (e.g., diodes) and impedance design (i.e., perfect mismatching) is tricky for continuous phase shift; discrete candidate set is preferred (2-3 bits optimal)
 % * Redefine RIS using book
-% ? Using RIS to encode is not very interesting as controller is anyway usable
-% * Wi-Fi sampling rate 20 MHz (symbol period 50 nS), RFID symbol rate/load switching speed 100s KHz to 10s MHz [Backscatter Communication], fast load switching speed is key for high data rate - symbol ratio is not very large
-% TODO Beamforming can cancel direct interference to avoid the collapse of noncoherent energy detection and enlarge energy gap.
+% x Using RIS to encode is not very interesting as controller is anyway usable
+% * Wi-Fi sampling rate 20 MHz (symbol period 50 nS), RFID symbol rate/load-switching speed 100s KHz to 10s MHz [Backscatter Communication], fast load-switching speed is key for high data rate - symbol ratio is not very large
+% * Beamforming can cancel direct interference to avoid the collapse of noncoherent energy detection and enlarge energy gap.
 % ?
@@
 % TODO Input probability distribution for discrete-value reflection (backscatter), constellation design for continue-value reflection (RIS)
-% * channel coding: general non-adaptive (book) adaptive (DMC)
+% * channel coding: non-adaptive (line-coding) or adaptive (DMC)
 % ? [Turbocharging] Since averaging must be done over a significant period of time to smooth out the variation in the TV transmissions, averaging does not allow rates much higher than 10 kbps [24].
-% TODO mu-code: use multiple Rxs for noncoherent direct interference cancellation (instead of receive diversity)
-% TODO backscatter modulation <-> passive beamforming; add adaptive channel coding over (NRZ) line coding.
-% TODO semicoherent: known CSI, unknown primary/backscatter symbols
-% * initialization, convergence
-% * Base e, use 2 in simulation
-% TODO SR analysis can achieve large rate at the cost of large N; RIScatter can achieve slightly lower rate at the same N, but also preserves primary performance for smaller N
+% ? [mu-code]: use multiple Rxs for noncoherent direct interference cancellation (instead of receive diversity)
+% * backscatter modulation <-> passive beamforming; add adaptive channel coding over (NRZ) line coding.
+% ? semicoherent: known CSI, unknown primary/backscatter symbols
+% * initialization, convergence, base 2 in simulation
+% * SR analysis can achieve large rate at the cost of large N; RIScatter can achieve slightly lower rate at the same N, but also preserves primary performance for smaller N
 % TODO tradeoff between primary (RIScatter, no SIC) and backscatter (SR, SIC)
-% !
-SR assume very large N for primary rate analysis.
+% * SR assume very large N for primary rate analysis.
 However, in such cases SIC is questionable as energy detection over received signal as BBC is already good enough and noncoherent detection can also achieve reasonable performance?
-% TODO when primary symbols are determined, optimal input distribution at high backscatter SNR is equiprobable for any detection (signal/energy)
-% * (I(X_1;Y_1),I(X_2;Y_2))
+% x when primary symbols are determined, optimal input distribution at high backscatter SNR is equiprobable for any detection (signal/energy)
 % ? Channel estimation error, coordination issues
-% TODO  binary input and signal output (BISO) channel, ML figure
-
-% ! add table row: adaptive to information source/csi/link weights
-% ! explain link weights
-% ! add table row: distributions
-% ! table to sentences
-% ! add primary and backscatter flows to illustrations
+
+% * add table row: adaptive to information source/csi/link weights
+% * explain link weights
+% * add table row: distributions
+% * table to sentences
+% * add primary and backscatter flows to illustrations
 % ! discuss table and add challenges in contribution 1
 % ! transition challenges (distribution and constellation-adaptive) to contribution 2, 3
-% ! think RIScatter applications (use Rui's slides)
+% * think RIScatter applications (use Rui's slides)
+
 \begin{abstract}
-	% \gls{bc} nodes harvest energy from and modulate information over an external radio wave by manipulating the magnitude, phase, and/or frequency of the scattered signal.
 	% \gls{bc} nodes harvest energy from and modulate information over an external electromagnetic wave by manipulating the magnitude, phase, and/or frequency of the scattered signal.
-	\gls{bc} nodes harvest energy from and modulate information over an external electromagnetic wave.
 	% \gls{sr} incorporates a passive scatter node into existing radio networks to create additional propagation path and ride its own information towards the cooperative receiver.
 	% \gls{ris} is a programmable reflector array that adapts the phase shift response to enhance or suppress signal strength in specific directions.
-	\gls{ris} adapts its phase shift response to enhance or suppress signal strength in specific directions.
+	\gls{bc} nodes harvest energy from and modulate information over an external electromagnetic wave.
+	\gls{ris} adapts its phase shift response to enhance or suppress equivalent channel strength in specific directions.
 	In this paper, we show how both seemingly different technologies and their derivatives can be unified to leverage their benefits simultaneously into a single architecture called RIScatter.
-	Envisioned as a scatter protocol, RIScatter consists of multiple dispersed or co-located passive scatter nodes whose reflection states can be adapted to partially engineer the wireless channel and partially modulate information onto the scattered wave.
-	This contrasts with \gls{bc} (resp. \gls{ris}) where reflection states are exclusively a function of information symbols (resp. \gls{csi}).
-	The key principle in RIScatter is to render the probability distribution of reflection states as a joint function of the \gls{csi} and input information source.
-	This enables RISscatter to softly bridge, generalize, and outperform \gls{bc} and \gls{ris}; boil down to any of those under specific reflection states; or evolve in a mixed form for heterogeneous traffic control and universal hardware design.
-	For a single-user multi-node RIScatter network, we characterize the achievable primary-(total-)backscatter rate region by optimizing input distribution at the nodes, active beamforming at the \gls{ap}, and backscatter detection region at the user.
-	Simulation results demonstrate RIScatter nodes can exploit additional propagation path to smoothly transition between backscatter modulation and passive beamforming via smart input distribution design, and the proposed practical receiver effectively accommodates the double modulation and signal difference in active-passive coexisting networks.
+	Envisioned as a next-generation communication protocol, RIScatter consists of multiple dispersed or co-located scatter nodes whose reflection states can be adapted to partially engineer the equivalent channel of the existing link and partially modulate their own information onto the scattered wave.
+	This contrasts with \gls{bc} (resp. \gls{ris}) where the reflection pattern is exclusively a function of the information symbol (resp. \gls{csi}).
+	The key principle in RIScatter is to render the probability distribution of reflection states as a joint function of the information source, \gls{csi}, and \gls{qos} of both coexisting links.
+	This enables RISscatter to softly bridge, generalize, and outperform \gls{bc} and \gls{ris}; boil down to either under specific reflection states; or evolve in a mixed form for heterogeneous traffic control and universal hardware design.
+	For a single-user multi-node RIScatter network, we characterize the achievable primary-(total-)backscatter rate region by optimizing the input distribution at the nodes, the active beamforming at the \gls{ap}, and the backscatter detection regions at the user.
+	Simulation results demonstrate RIScatter nodes can exploit the additional propagation paths to smoothly transition between backscatter modulation and passive beamforming via smart input distribution design, and the proposed practical receiver effectively accommodates the double modulation and signal difference in active-passive coexisting networks.
 \end{abstract}
@@
 		A comparison of different scattering applications is summarized in Table \ref{tb:scattering_applications}.
+
 		\begin{figure}[!t]
@@
 				Illustration of scattering applications.
+				The blue paths constitute the primary link while the magenta/green paths denote the backscatter link.
 			}
@@
 		\label{tb:scattering_applications}
-		\renewcommand{\arraystretch}{1.25}
+		\rowcolors{2}{gray!25}{white}
+		\renewcommand{\arraystretch}{1.5}
 		\begin{tabularx}{\textwidth}{CCCCCC}
 			\toprule
-			% \rowcolor{gray!25}
+			\hiderowcolors
 			                                 & \gls{mbc}/\gls{bbc} & \gls{ambc}         & \gls{sr}                                      & \gls{ris}           & RIScatter                                                               \\ \midrule
-			Coexisting systems            & 1                         & 2 (competitive)                                 & 2 (collaborative)                            & 1                                          & 2 (collaborative)                                 \\
-			\rowcolor{gray!25}
-			Scatterer contribution        & Backscatter modulation    & Backscatter modulation and primary interference & Backscatter modulation and primary multipath & Passive beamforming                        & Backscatter modulation and passive beamforming    \\
-			Cooperative transmissions     & ---                       & No (individual transmitters)                    & Active beamforming                           & ---                                        & Active beamforming and smart reflection           \\
-			\rowcolor{gray!25}
-			Cooperative reception         & ---                       & No (separated receivers)                        & Joint detection or \gls{sic}                 & ---                                        & Backscatter detection as primary channel training \\
-			Primary detection             & ---                       & Semi-coherent                                   & Coherent or semi-coherent                    & Coherent                                   & Coherent                                          \\
-			\rowcolor{gray!25}
-			Backscatter detection         & Coherent                  & Semi-coherent or noncoherent                    & Coherent                                     & ---                                        & Semi-coherent                                     \\
-			Reflection state distribution & Equiprobable (line-coded) & Equiprobable (line-coded)                       & Equiprobable or Gaussian                     & Degenerate (\gls{csi}-adaptive)            & Flexible (\gls{csi}- and traffic-adaptive)        \\
-			\rowcolor{gray!25}
-			Load-switching frequency      & Fast or slow              & Fast or slow                                    & Slow                                         & Slow (dynamic) or quasi-static (blockwise) & Fast or slow                                      \\ \bottomrule
+			\showrowcolors
+			Coexisting link(s)               & 1                   & 2 (competitive)    & 2 (collaborative)                             & 1                   & 2 (collaborative)                                                       \\
+			Backscatter modulation           & Yes                 & Yes                & Yes                                           & No                  & Yes                                                                     \\
+			Scatterer impact on primary link & ---                 & Interference       & Channel uncertainty                           & Passive beamforming & Dynamic passive beamforming                                             \\
+			Cooperative transmission(s)      & ---                 & No                 & Primary transmitter (active beamforming)      & ---                 & Primary transmitter and scatter nodes                                   \\
+			Co-located receiver              & ---                 & No                 & Usually \gls{sic} from primary to backscatter & ---                 & No \gls{sic}, backscatter detection as part of primary channel training \\
+			Primary detection                & ---                 & Semi-coherent      & Semi-coherent                                 & Coherent            & Coherent                                                                \\
+			Backscatter detection            & Coherent            & Semi-coherent      & Coherent                                      & ---                 & Semi-coherent                                                           \\
+			Reflection pattern depends on    & Information source  & Information source & Information source                            & \gls{csi}           & Information source, \gls{csi}, and \gls{qos}                            \\
+			Input distribution               & Equiprobable        & Equiprobable       & Equiprobable or Gaussian                      & Degenerate          & Flexible                                                                \\
+			Load-switching speed             & Fast                & Fast or slow       & Very slow                                     & Quasi-static        & Flexible                                                                \\ \bottomrule
 		\end{tabularx}
@@
 		% sequential primary-backscatter decoding based on \gls{sic}.
-		During primary decoding, the backscatter randomness can be modelled as either interference or channel uncertainty, depending on the ratio $N$ of primary sampling rate over backscatter switching speed\footnote{For state-of-the-art low-power \gls{rfid} tags, the load switching speed typically varies between \num{100}s of \unit{\kHz} to \num{10}s of \unit{\MHz} \cite{Torres2021}}.
+		During primary decoding, the backscatter randomness can be modelled as either interference or channel uncertainty, depending on the ratio $N$ of primary sampling rate over backscatter load-switching speed\footnote{For state-of-the-art low-power \gls{rfid} tags, the load-switching speed typically varies between \num{100}s of \unit{\kHz} to \num{10}s of \unit{\MHz} \cite{Torres2021}}.
 		Such a sequential \gls{sic} involves $N$ re-encoding, precoding, subtraction together with a time-domain \gls{mrc} to decode each backscatter symbol, which can be operation-intensive and \gls{csi}-sensitive.
 		When $N$ is sufficiently large (i.e., commensal \gls{sr}), the average primary achievable rate under noncoherent detection asymptotically approaches its coherent counterpart, and both links can be decoded in an interference-free manner \cite{Long2020a}.
-		% However, the assumption of very large backscatter-over-primary symbol period ratio $N$ may not hold in practice\footnote{For example, Wi-Fi sampling rate is \qty{20}{\MHz} while \gls{rfid} load switching speed varies between \num{100}s of \unit{\kHz} to \num{10}s of \unit{\MHz} \cite{Torres2021}, corresponding to a typical $N$ between \num{1} and \num{100}.}, and such a \gls{sic}-based sequential decoding requires re-encoding, precoding, and subtraction at each primary symbol block with a time-domain \gls{mrc}, which can be operation-intensive and \gls{csi}-sensitive.
+		% However, the assumption of very large backscatter-over-primary symbol period ratio $N$ may not hold in practice\footnote{For example, Wi-Fi sampling rate is \qty{20}{\MHz} while \gls{rfid} load-switching speed varies between \num{100}s of \unit{\kHz} to \num{10}s of \unit{\MHz} \cite{Torres2021}, corresponding to a typical $N$ between \num{1} and \num{100}.}, and such a \gls{sic}-based sequential decoding requires re-encoding, precoding, and subtraction at each primary symbol block with a time-domain \gls{mrc}, which can be operation-intensive and \gls{csi}-sensitive.
 		Another open issue for \gls{bc} and \gls{sr} is efficient backscatter multiple access design.
@@
 		partially engineer the wireless channel and partially modulate its own information.
-		This is accomplished by incorporating both the \gls{csi} and link weights into the reflection state distribution design.
+		This is accomplished by incorporating both the \gls{csi} and \gls{qos} into the reflection state distribution design.
 		As such, RIScatter can generalize \gls{bc} (uniform distribution) and \gls{ris} (degenerate distribution) to create a tradeoff between backscatter modulation and passive beamforming.
@@
 		Conventional sequential primary-backscatter decoder eliminates primary interference by \gls{sic} at each primary block, while our sequential backscatter-primary detector semi-coherently decodes RIScatter nodes from the received energy, re-encodes to recover exact reflection patterns, and models the deterministic multipath within primary equivalent channel as dynamic passive beamforming at each backscatter block.
-		It enables backscatter modulation and dynamic passive beamforming at much lower operational complexity, and is suitable for scatter nodes with various load switching speeds.
+		It enables backscatter modulation and dynamic passive beamforming at much lower operational complexity, and is suitable for scatter nodes with various load-switching speeds.
 
@@
 		As a generalization of \gls{bc} and \gls{ris}, RIScatter is a passive scatter protocol that coexists with an active primary system in a flexible and mutualistic manner.
-		RIScatter nodes leverage \gls{csi}- and weight-based input distribution design to smoothly transition between backscatter modulation and passive beamforming.
+		RIScatter nodes leverage \gls{csi}- and \gls{qos}-based input distribution design to smoothly transition between backscatter modulation and passive beamforming.
 		It can be implemented by adding an integrated receiver \cite{Kim2021a} and adaptive encoder \cite{He2020e} to off-the-shelf passive backscatter tags.
@@
 		Hence, the receiver can semi-coherently (in the presence of primary uncertainty) decode node messages from the accumulated receive energy, re-encode to recover actual reflection patterns, and model the deterministic multipath within primary equivalent channel.
-		It enables simultaneous backscatter modulation and dynamic passive beamforming by only one energy comparison, re-encoding, and precoding operations for each backscatter block (instead of primary block), and is suitable for arbitrary primary sampling rate and backscatter switching speed.
+		It enables simultaneous backscatter modulation and dynamic passive beamforming by only one energy comparison, re-encoding, and precoding operations for each backscatter block (instead of primary block), and is suitable for arbitrary primary sampling rate and backscatter load-switching speed.
 	\end{subsection}
@@
 		\end{align}
-		where $\rho \in \mathbb{I}$ is the weight of the primary link.
+		where $\rho \in \mathbb{I}$ is the \gls{qos} of the primary link.
 		We notice the average primary rate \eqref{eq:primary_mutual_information} depends on the input distribution and active beamforming, while the total backscatter rate depends on the input distribution and \gls{dmtmac} \eqref{eq:dmtmac} that relates to active beamforming and decision thresholds.
@@
 
-	Problem \eqref{op:weighted_sum_rate} generalizes conventional \gls{bc} by allowing \gls{csi}- and weight-adaptive input distribution and detection region design.
+	Problem \eqref{op:weighted_sum_rate} generalizes conventional \gls{bc} by allowing \gls{csi}- and \gls{qos}-adaptive input distribution and detection region design.
 	It also generalizes the discrete \gls{ris} phase shift selection by allowing stochastic reflection (i.e., relaxing the feasible domain from the vertices of $M$-dimensional probability simplex to the simplex itself).
@@
 		\begin{subsubsection}{Initialization}
-			To characterize each achievable rate region, we progressively obtain all boundary points by successively increasing weight $\rho$ and solving problem \eqref{op:weighted_sum_rate}.
+			To characterize each achievable rate region, we progressively obtain all boundary points by successively increasing the primary \gls{qos} $\rho$ and solving problem \eqref{op:weighted_sum_rate}.
 			For $\rho=0$ where backscatter link is prioritized, we initialize Algorithm \ref{al:input_distribution} and \ref{al:active_beamforming} by uniform input distribution and \gls{mrt} towards sum cascaded channel $\sum_{k} \boldsymbol{h}_{\mathrm{C},k}^H$, respectively.
@@
 
-	\begin{subsection}{Input Distribution under Different Weights}
+	\begin{subsection}{Input Distribution under Different \gls{qos}}
 		\begin{figure}[!t]
@@
 			}
-			\caption{Typical RIScatter reflection state distribution under different weights for $Q=1$, $K=1$, $M=4$, $N=20$, $\sigma_v^2=\qty{-40}{\dBm}$ and $r=\qty{2}{\meter}$.}
+			\caption{Typical RIScatter reflection state distribution at different $\rho$ for $Q=1$, $K=1$, $M=4$, $N=20$, $\sigma_v^2=\qty{-40}{\dBm}$ and $r=\qty{2}{\meter}$.}
 			\label{fg:distribution_weights}
 		\end{figure}
-		The objective of this study is to demonstrate RIScatter nodes can leverage \gls{csi}- and weight-adaptive input distribution design to balance backscatter modulation and passive beamforming.
-		For one RIScatter node with $M=4$, we evaluate the \gls{kkt} input distribution\footnote{Since problem \eqref{op:input_distribution} is convex when $K=1$, the \gls{kkt} solution is also global optimal in this example.} under different weights and present the result in Fig.
+		The objective of this study is to demonstrate RIScatter nodes can leverage \gls{csi}- and \gls{qos}-adaptive input distribution design to balance backscatter modulation and passive beamforming.
+		For one RIScatter node with $M=4$, we evaluate the \gls{kkt} input distribution\footnote{Since problem \eqref{op:input_distribution} is convex when $K=1$, the \gls{kkt} solution is also global optimal in this example.} at different primary \gls{qos} and present the result in Fig.
 \ref{fg:distribution_weights}.
@@
 			The average rate performance of \emph{Exhaustion} and \emph{\gls{kkt}} coincide with each other, which demonstrates \gls{kkt} input distribution can be reasonably good for a moderate $K$ as stated in Remark \ref{re:input_kkt_distribution}.
-			\emph{Equiprobable} experiences minor backscatter and major primary rate losses without \gls{csi}- and weight-adaptive backscatter encoding.
+			\emph{Equiprobable} experiences minor backscatter and major primary rate losses without \gls{csi}- and \gls{qos}-adaptive backscatter encoding.
 			As for the recovery methods, the simple \emph{Marginalization} provides a close result to \emph{\gls{kkt}}, but \emph{Randomization} and \emph{Decomposition} fail our expectations for most channel realizations.

### 2022-11-25 main.tex
:dizzy: Update literature review

@@
 	The key principle in RIScatter is to render the probability distribution of reflection states as a joint function of the information source, \gls{csi}, and \gls{qos} of both coexisting links.
-	This enables RISscatter to softly bridge, generalize, and outperform \gls{bc} and \gls{ris}; boil down to either under specific reflection states; or evolve in a mixed form for heterogeneous traffic control and universal hardware design.
+	This enables RISscatter to softly bridge, generalize, and outperform \gls{bc} and \gls{ris}; boil down to either under specific input distribution; or evolve in a mixed form for heterogeneous traffic control and universal hardware design.
 	For a single-user multi-node RIScatter network, we characterize the achievable primary-(total-)backscatter rate region by optimizing the input distribution at the nodes, the active beamforming at the \gls{ap}, and the backscatter detection regions at the user.
@@
 		\gls{ambc} was then proposed in \cite{Liu2013b} where battery-free nodes recycle ambient signals (e.g., radio, television and Wi-Fi) to harvest energy and establish connection in between.
-		As shown in Fig. \subref*{fg:ambc}, it eliminates the need of dedicated power supply, carrier emitter and frequency spectrum but is subject to the strong direct-link interference.
+		As shown in Fig. \subref*{fg:ambc}, it eliminates the need of dedicated power supply, carrier emitter and frequency spectrum, but is subject to the strong direct-link interference.
 		To tackle this, \cite{Yang2018} proposed cooperative \gls{ambc} where both primary (legacy) and backscatter links are decoded by the same receiver under various detection schemes.
@@
 		% In a \gls{sr} system, the active transmitter generates \gls{rf} wave carrying primary information, the passive node creates extra primary propagation path and superimposes its own message on the scattered signal, while the cooperative receiver jointly or sequentially decodes both links.
-		In a \gls{sr} system, the active transmitter generates \gls{rf} wave carrying primary information, the passive node creates extra propagation path and ride its information over scattered signal, while the cooperative receiver jointly or sequentially decodes both links.
-		Those \gls{bc} applications employ scatter nodes as pure information sources such that the active primary link (if it exists) is influenced by backscatter randomness (often modelled as interference or channel uncertainty).
-		On the other hand, \gls{ris} is a smart planar wave reflector that consists of numerous compact passive elements with adjustable amplitude and phase responses.
-		The reflection pattern is deterministic over time that can be optimized and coordinated before the transmission.
-		\gls{ris} recycles and redistributes surrounding \gls{rf} waves to customize the wireless propagation environment for signal enhancement, interference suppression, scattering enrichment and non-line-of-sight bypassing \cite{Wu2021b}.
+		In a \gls{sr} system, the active transmitter generates \gls{rf} wave carrying primary information, the passive node provides extra propagation path and ride its information over scattered signal, while the cooperative receiver jointly or sequentially decodes both links.
+		Those \gls{bc} applications employ scatter nodes as pure information sources, and the primary link (if it exists) is indeed influenced by the randomness of backscatter modulation.
+		On the other hand, \gls{ris} is a smart planar signal reflector that consists of numerous compact passive elements with adjustable amplitude and phase responses.
+		The reflection pattern is deterministic over time that can be adaptively optimized and coordinated in real time.
+		\gls{ris} recycles and redistributes the surrounding \gls{rf} waves to customize the wireless propagation environment for signal enhancement, interference suppression, scattering enrichment and non-line-of-sight bypassing \cite{Wu2021b}.
+
 		A comparison of different scattering applications is summarized in Table \ref{tb:scattering_applications}.
@@
 		Joint \gls{ml} decoding provides the best error performance for \gls{sr} but requires prohibitive computational complexity especially for high-order modulations \cite{Yang2018}.
-		One special property of such an active-passive coexisting network is that the backscatter signal strength can be relatively weak due to the double fading effect.
+		One special property of those active-passive coexisting networks is that the backscatter signal strength can be relatively weak due to the double fading effect.
 		It motivated \cite{Long2020a,Liang2020,Guo2019b,Ding2020,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Yang2018,Han2021,Zhang2022} to view \gls{sr} as a multiplicative \gls{noma} and perform \gls{sic} from primary to backscatter link.
 		% sequential primary-backscatter decoding based on \gls{sic}.
-		During primary decoding, the backscatter randomness can be modelled as either interference or channel uncertainty, depending on the ratio $N$ of primary sampling rate over backscatter load-switching speed\footnote{For state-of-the-art low-power \gls{rfid} tags, the load-switching speed typically varies between \num{100}s of \unit{\kHz} to \num{10}s of \unit{\MHz} \cite{Torres2021}}.
+		During primary decoding, the backscatter randomness can be modelled as either interference or channel uncertainty, depending on the ratio $N$ of primary sampling rate over backscatter load-switching speed\footnote{For state-of-the-art low-power \gls{rfid} tags, the load-switching speed usually varies between \num{100}s of \unit{\kHz} to \num{10}s of \unit{\MHz} \cite{Torres2021}, suggesting a typical $N$ between \num{10} and \num{1000}.}.
 		Such a sequential \gls{sic} involves $N$ re-encoding, precoding, subtraction together with a time-domain \gls{mrc} to decode each backscatter symbol, which can be operation-intensive and \gls{csi}-sensitive.
@@
 		% However, the assumption of very large backscatter-over-primary symbol period ratio $N$ may not hold in practice\footnote{For example, Wi-Fi sampling rate is \qty{20}{\MHz} while \gls{rfid} load-switching speed varies between \num{100}s of \unit{\kHz} to \num{10}s of \unit{\MHz} \cite{Torres2021}, corresponding to a typical $N$ between \num{1} and \num{100}.}, and such a \gls{sic}-based sequential decoding requires re-encoding, precoding, and subtraction at each primary symbol block with a time-domain \gls{mrc}, which can be operation-intensive and \gls{csi}-sensitive.
-		Another open issue for \gls{bc} and \gls{sr} is efficient backscatter multiple access design.
+		Another open issue for \gls{bc} is the efficient backscatter multiple access design.
 		\cite{Xu2021a} proposed a \gls{noma}-based \gls{sr} where the \gls{sic} order depends on the backscatter channel strength, but the performance deteriorates fast as the number of nodes increases.
@@
 		To reduce coordination burden for passive nodes, \cite{Han2021} proposed a random code-assisted multiple access for \gls{sr} and evaluated the asymptotic \gls{sinr} using random matrix theory.
-		However, this code-domain solution suffers from the near-far problem and imperfect synchronization.
+		However, this code-domain solution suffers from the near-far problem and imperfect synchronization, both can be very severe in practical scenarios.
 
 		Conventional \gls{ris} design with fixed reflection coefficients during each channel block has been extensively studied in communication, sensing, and power literatures \cite{Wu2018,Zhang2019a,Lin2022,Liu2022,Feng2022,Zhao2022}.
-		On the other hand, dynamic \gls{ris} with independent reflection patterns at different frames has gained recent attentions in multi-user and multi-purpose wireless networks.
+		On the other hand, dynamic \gls{ris} with independent reflection patterns at different transmission phases has gained recent attentions in multi-user and multi-purpose wireless networks.
 		The concept was first proposed in \cite{Yang2020} to fine-tune the \gls{ofdm} resource blocks, then extended to the downlink power and uplink information phases of \gls{wpcn} \cite{Wu2021,Wu2021d,Hua2022a}.
-		It introduces artificial channel diversity and enables flexible resource allocation, but misses the opportunity to encode its own message.
-		\gls{ris} can also be used as a transmitter when placed in the near field of a carrier emitter, and prototypes for \gls{psk} and \gls{qam} have been implemented in \cite{Tang2019a,Dai2020a}.
+		It introduces artificial channel diversity and enables flexible resource allocation, but misses the opportunity to encode message at the \gls{ris}.
+		% \gls{ris} can also be used as a transmitter when placed in the near field of a carrier emitter, and prototypes for \gls{psk} and \gls{qam} have been implemented in \cite{Tang2019a,Dai2020a}.
+		When placed in the near field of a carrier emitter, \gls{ris} can also be used as a transmitter, and prototypes for \gls{psk} and \gls{qam} have been implemented in \cite{Tang2019a,Dai2020a}.
 		From an information-theoretic perspective, \cite{Karasik2020} reported that using \gls{ris} as a naive passive beamformer to maximize the \gls{snr} is generally rate-suboptimal for finite input constellations.
@@
 		% Those \gls{ris}-empowered \gls{bc} can recycle electromagnetic wave on the air to simultaneously boost wireless channels and establish new connections, but the reflect elements or scatter nodes incurs advanced hardware architecture and high optimization complexity.
-		Those \gls{ris}-empowered \gls{bc} designs can recycle electromagnetic wave on the air and employ scattered paths to boost wireless channels and establish new connections, but incurs advanced hardware architecture and high optimization complexity.
+		Those \gls{ris}-empowered \gls{bc} designs can recycle \gls{rf} wave on the air and employ scattered paths to boost wireless channels and establish new connections, but incurs advanced hardware architecture and high optimization complexity.
+
 		% the reflect elements or scatter nodes incurs advanced hardware architecture and high optimization complexity.
@@
 			This is because once the scope of reflection coefficient is determined, using denser constellation points may not create enough phase resolution and energy diversity for primary and backscatter links.
-			Due to the maximum amplitude normalization in \eqref{eq:backscatter_modulation}, the average rate region of \num{8}-\gls{qam} with rectangular frame is smaller than that of \num{4}-\gls{qam} with square frame, and the inner constellation points with smaller amplitudes are less frequently used.
+			Due to the maximum amplitude normalization in \eqref{eq:backscatter_modulation}, the average rate region of \num{8}-\gls{qam} with rectangular boundary is smaller than that of \num{4}-\gls{qam} with square boundary, and the inner constellation points with smaller amplitudes are less frequently used.
 			The results in this and previous paragraphs motivate one to replace the high-resolution metamaterial units of RIS by multiple low-order scatter nodes.

### 2022-11-26 assets/illustration/input_distribution.tex
:dizzy: Manuscript 221103
:lipstick: Update illustrations

@@
 		\addplot[blue,fill=blue!30!white] coordinates {(-1,-1)};
-		\addplot[blue,fill=blue!30!white,postaction={pattern=horizontal lines},pattern color=.] coordinates {(1,0.25)};
-		\addplot[blue,fill=blue!30!white,postaction={pattern=north west lines},pattern color=.] coordinates {(2,0.25)};
+		\addplot[blue,fill=blue!30!white,postaction={pattern=north west lines},pattern color=.] coordinates {(1,0.25)};
+		\addplot[blue,fill=blue!30!white,postaction={pattern=north east lines},pattern color=.] coordinates {(2,0.25)};
 		\addplot[blue,fill=blue!30!white,postaction={pattern=vertical lines},pattern color=.] coordinates {(3,0.25)};
-		\addplot[blue,fill=blue!30!white,postaction={pattern=north east lines},pattern color=.] coordinates {(4,0.25)};
-		\legend{BackCom/AmBC/SR}
+		\addplot[blue,fill=blue!30!white,postaction={pattern=horizontal lines},pattern color=.] coordinates {(4,0.25)};
+		\legend{BackCom}
 		\nextgroupplot[ylabel={Probability Distribution}]
 		\addplot[red,fill=red!30!white] coordinates {(-1,-1)};
-		\addplot[red,fill=red!30!white,postaction={pattern=horizontal lines},pattern color=.] coordinates {(1,0)};
-		\addplot[red,fill=red!30!white,postaction={pattern=north west lines},pattern color=.] coordinates {(2,1)};
+		\addplot[red,fill=red!30!white,postaction={pattern=north west lines},pattern color=.] coordinates {(1,0)};
+		\addplot[red,fill=red!30!white,postaction={pattern=north east lines},pattern color=.] coordinates {(2,1)};
 		\addplot[red,fill=red!30!white,postaction={pattern=vertical lines},pattern color=.] coordinates {(3,0)};
-		\addplot[red,fill=red!30!white,postaction={pattern=north east lines},pattern color=.] coordinates {(4,0)};
+		\addplot[red,fill=red!30!white,postaction={pattern=horizontal lines},pattern color=.] coordinates {(4,0)};
 		\legend{RIS}
@@
 		\addplot[brown,fill=brown!30!white] coordinates {(-1,-1)};
-		\addplot[brown,fill=brown!30!white,postaction={pattern=horizontal lines},pattern color=.] coordinates {(1,0.125)};
-		\addplot[brown,fill=brown!30!white,postaction={pattern=north west lines},pattern color=.] coordinates {(2,0.625)};
+		\addplot[brown,fill=brown!30!white,postaction={pattern=north west lines},pattern color=.] coordinates {(1,0.125)};
+		\addplot[brown,fill=brown!30!white,postaction={pattern=north east lines},pattern color=.] coordinates {(2,0.625)};
 		\addplot[brown,fill=brown!30!white,postaction={pattern=vertical lines},pattern color=.] coordinates {(3,0.25)};
-		\addplot[brown,fill=brown!30!white,postaction={pattern=north east lines},pattern color=.] coordinates {(4,0)};
+		\addplot[brown,fill=brown!30!white,postaction={pattern=horizontal lines},pattern color=.] coordinates {(4,0)};
 		\legend{RIScatter}

### 2022-11-26 assets/illustration/time_structure.tex
:dizzy: Manuscript 221103
:lipstick: Update illustrations

@@
 	\foreach \x in {0,...,3}{
-			\draw[blue,fill=blue!30!white,postaction={pattern=horizontal lines},pattern color=.] (0.5*\x,3) rectangle ++(0.5,0.25);
+			\draw[blue,fill=blue!30!white,postaction={pattern=north west lines},pattern color=.] (0.5*\x,3) rectangle ++(0.5,0.25);
 		}
 	\foreach \x in {4,...,7}{
-			\draw[blue,fill=blue!30!white,postaction={pattern=north west lines},pattern color=.] (0.5*\x,3) rectangle ++(0.5,0.25);
+			\draw[blue,fill=blue!30!white,postaction={pattern=north east lines},pattern color=.] (0.5*\x,3) rectangle ++(0.5,0.25);
 		}
@@
 	\foreach \x in {12,...,15}{
-			\draw[blue,fill=blue!30!white,postaction={pattern=north east lines},pattern color=.] (0.5*\x,3) rectangle ++(0.5,0.25);
+			\draw[blue,fill=blue!30!white,postaction={pattern=horizontal lines},pattern color=.] (0.5*\x,3) rectangle ++(0.5,0.25);
 		}
@@
 	\foreach \x in {0,...,15}{
-			\draw[red,fill=red!30!white,postaction={pattern=north west lines},pattern color=.] (0.5*\x,2) rectangle ++(0.5,0.25);
+			\draw[red,fill=red!30!white,postaction={pattern=north east lines},pattern color=.] (0.5*\x,2) rectangle ++(0.5,0.25);
 		}
@@
 	\foreach \x in {0,...,1}{
-			\draw[brown,fill=brown!30!white,postaction={pattern=horizontal lines},pattern color=.] (0.5*\x,1) rectangle ++(0.5,0.25);
+			\draw[brown,fill=brown!30!white,postaction={pattern=north west lines},pattern color=.] (0.5*\x,1) rectangle ++(0.5,0.25);
 		}
 	\foreach \x in {2,...,7}{
-			\draw[brown,fill=brown!30!white,postaction={pattern=north west lines},pattern color=.] (0.5*\x,1) rectangle ++(0.5,0.25);
+			\draw[brown,fill=brown!30!white,postaction={pattern=north east lines},pattern color=.] (0.5*\x,1) rectangle ++(0.5,0.25);
 		}
@@
 	\foreach \x in {12,...,15}{
-			\draw[brown,fill=brown!30!white,postaction={pattern=north west lines},pattern color=.] (0.5*\x,1) rectangle ++(0.5,0.25);
+			\draw[brown,fill=brown!30!white,postaction={pattern=north east lines},pattern color=.] (0.5*\x,1) rectangle ++(0.5,0.25);
 		}
@@
 
-	\node at (-2,3.125) {BackCom/AmBC/SR};
+	\node at (-2,3.125) {BackCom};
 	\node at (-2,2.125) {RIS};
@@
 
-	\draw [pattern=horizontal lines](0.15,0) rectangle ++(0.5,0.25) node[xshift=20,yshift=-3.5] {State 1};
-	\draw [pattern=north west lines](2.15,0) rectangle ++(0.5,0.25) node[xshift=20,yshift=-3.5] {State 2};
+	\draw [pattern=north west lines](0.15,0) rectangle ++(0.5,0.25) node[xshift=20,yshift=-3.5] {State 1};
+	\draw [pattern=north east lines](2.15,0) rectangle ++(0.5,0.25) node[xshift=20,yshift=-3.5] {State 2};
 	\draw [pattern=vertical lines](4.15,0) rectangle ++(0.5,0.25) node[xshift=20,yshift=-3.5] {State 3};
-	\draw [pattern=north east lines](6.15,0) rectangle ++(0.5,0.25) node[xshift=20,yshift=-3.5] {State 4};
+	\draw [pattern=horizontal lines](6.15,0) rectangle ++(0.5,0.25) node[xshift=20,yshift=-3.5] {State 4};
 \end{tikzpicture}

### 2022-11-26 main.tex
:construction: Update table and contributions

@@
 		Yang~Zhao,~\IEEEmembership{Member,~IEEE,}
-		and~Bruno~Clerckx,~\IEEEmembership{Fellow,~IEEE,}
-		TODO
+		and~Bruno~Clerckx,~\IEEEmembership{Fellow,~IEEE}
 	}
 	\thanks{
-		The authors are with the Department of Electrical and Electronic Engineering, Imperial College London, London SW7 2AZ, U.K. (e-mail: \{yang.zhao18, b.clerckx,TODO\}@imperial.ac.uk).
+		The authors are with the Department of Electrical and Electronic Engineering, Imperial College London, London SW7 2AZ, U.K. (e-mail: \{yang.zhao18, b.clerckx\}@imperial.ac.uk).
 	}
@@
 % * add primary and backscatter flows to illustrations
-% ! discuss table and add challenges in contribution 1
-% ! transition challenges (distribution and constellation-adaptive) to contribution 2, 3
+% * discuss table and add challenges in contribution 1
+% * transition challenges (distribution and constellation-adaptive) to contribution 2, 3
 % * think RIScatter applications (use Rui's slides)
@@
 	For a single-user multi-node RIScatter network, we characterize the achievable primary-(total-)backscatter rate region by optimizing the input distribution at the nodes, the active beamforming at the \gls{ap}, and the backscatter detection regions at the user.
-	Simulation results demonstrate RIScatter nodes can exploit the additional propagation paths to smoothly transition between backscatter modulation and passive beamforming via smart input distribution design, and the proposed practical receiver effectively accommodates the double modulation and signal difference in active-passive coexisting networks.
+	Simulation results demonstrate RIScatter nodes can exploit the additional propagation paths to smoothly transition between backscatter modulation and passive beamforming via smart input distribution design, and the tailored receiver effectively accommodates the double modulation and signal difference in active-passive coexisting networks without \gls{sic}.
 \end{abstract}
@@
 		However, conventional \gls{bc} nodes only respond when externally inquired by a nearby reader.
-		% \cite{Liu2013b} proposed an \gls{ambc} system in Fig.
-\subref*{fg:ambc}, where battery-free nodes recycle ambient signals (e.g., radio, television and Wi-Fi) to harvest energy and establish connection in between.
 		\gls{ambc} was then proposed in \cite{Liu2013b} where battery-free nodes recycle ambient signals (e.g., radio, television and Wi-Fi) to harvest energy and establish connection in between.
@@
 		To tackle this, \cite{Yang2018} proposed cooperative \gls{ambc} where both primary (legacy) and backscatter links are decoded by the same receiver under various detection schemes.
-		% The concept of cooperative \gls{ambc} was further refined as \gls{sr} in Fig. \subref*{fg:sr} that cognitively incorporates \gls{ambc} with existing systems \cite{Liang2020}.
 		The concept was further refined as \gls{sr} illustrated in Fig. \subref*{fg:sr} that cognitively incorporates \gls{ambc} with existing systems \cite{Liang2020}.
-		% In a \gls{sr} system, the active transmitter generates \gls{rf} wave carrying primary information, the passive node creates extra primary propagation path and superimposes its own message on the scattered signal, while the cooperative receiver jointly or sequentially decodes both links.
 		In a \gls{sr} system, the active transmitter generates \gls{rf} wave carrying primary information, the passive node provides extra propagation path and ride its information over scattered signal, while the cooperative receiver jointly or sequentially decodes both links.
-		Those \gls{bc} applications employ scatter nodes as pure information sources, and the primary link (if it exists) is indeed influenced by the randomness of backscatter modulation.
+		Those \gls{bc} applications employ scatter nodes as pure information sources, and the active transmission (if it exists) is indeed influenced by the randomness of backscatter modulation.
 		On the other hand, \gls{ris} is a smart planar signal reflector that consists of numerous compact passive elements with adjustable amplitude and phase responses.
@@
 
+		Depending on the number of coexisting links, those scattering applications are divided into two categories that involve either active or passive transmission, or both active and passive transmissions.
+		The corresponding information flows are illustrated in Fig. \ref{fg:scatter_illustration}.
+		In \gls{mbc}/\gls{bbc} (resp. \gls{ris}), the passive device modulates information (resp. enhances propagation) while the active device generates carrier wave (resp. modulated signal).
+		There is only the backscatter (resp. primary) link and the detection can be coherent.
+		On the other hand, \gls{ambc} and \gls{sr} involve both links simultaneously, but the relationship in between is different.
+		For \gls{ambc}, the primary link does not need to be aware of the backscatter link and both links are interfering each other.
+		For \gls{sr}, both links are decoded by a co-located receiver, and cooperative transmission and reception become possible.
 		A comparison of different scattering applications is summarized in Table \ref{tb:scattering_applications}.
@@
 				Illustration of scattering applications.
-				The blue paths constitute the primary link while the magenta/green paths denote the backscatter link.
+				For each, the blue flow(s) constitute the primary link while the magenta/green flow denotes the backscatter link.
 			}
@@
 			Coexisting link(s)                      & 1                   & 2 (competitive)    & 2 (collaborative)                             & 1                   & 2 (collaborative)                                                       \\
-			Backscatter modulation           & Yes                 & Yes                & Yes                                           & No                  & Yes                                                                     \\
-			Scatterer impact on primary link & ---                 & Interference       & Channel uncertainty                           & Passive beamforming & Dynamic passive beamforming                                             \\
+			Primary/Backscatter modulation          & No/Yes              & Yes/Yes            & Yes/Yes                                       & Yes/No              & Yes/Yes                                                                 \\
+			Primary impact on backscatter detection & Carrier             & Interference       & Spreading code                                & ---                 & Energy uncertainty                                                      \\
+			Scatterer impact on primary detection   & ---                 & Interference       & Channel uncertainty                           & Passive beamforming & Dynamic passive beamforming                                             \\
 			Cooperative transmission(s)             & ---                 & No                 & Primary transmitter (active beamforming)      & ---                 & Primary transmitter and scatter nodes                                   \\
@@
 		% sequential primary-backscatter decoding based on \gls{sic}.
-		During primary decoding, the backscatter randomness can be modelled as either interference or channel uncertainty, depending on the ratio $N$ of primary sampling rate over backscatter load-switching speed\footnote{For state-of-the-art low-power \gls{rfid} tags, the load-switching speed usually varies between \num{100}s of \unit{\kHz} to \num{10}s of \unit{\MHz} \cite{Torres2021}, suggesting a typical $N$ between \num{10} and \num{1000}.}.
+		During primary decoding, the backscatter randomness can be modelled as either interference or channel uncertainty, depending on the ratio $N$ of primary sampling rate over backscatter load-switching speed\footnote{For state-of-the-art low-power \gls{rfid} tags, the load-switching speed usually varies between \num{100}s of \unit{\kHz} to \num{10}s of \unit{\MHz} \cite{Torres2021}, corresponding to a typical $N$ between \num{10} and \num{1000}.}.
 		Such a sequential \gls{sic} involves $N$ re-encoding, precoding, subtraction together with a time-domain \gls{mrc} to decode each backscatter symbol, which can be operation-intensive and \gls{csi}-sensitive.
@@
 		Those \gls{ris}-empowered \gls{bc} designs can recycle \gls{rf} wave on the air and employ scattered paths to boost wireless channels and establish new connections, but incurs advanced hardware architecture and high optimization complexity.
-
-		% the reflect elements or scatter nodes incurs advanced hardware architecture and high optimization complexity.
-		% For backscatter information sources,
-		% Besides,
-		% Relevant literatures also consider either Gaussian codebook \cite{Guo2019b,Ding2020,Long2020a,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Hu2021b} or finite equiprobable inputs \cite{Yang2018,Liang2020,Han2021,Zhang2022,Liu2019d,Bereyhi2020,Xu2020b,Zhang2021d,Hua2022,Basar2020,Ma2020a,Yuan2021,Hu2021a} for backscatter information sources.
-		% The former is impractical for passive backscatter devices while the latter does not fully exploit \gls{csi} and signal characteristics.
+		Relevant literatures also consider either Gaussian codebook \cite{Guo2019b,Ding2020,Long2020a,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Hu2021b} or finite equiprobable inputs \cite{Yang2018,Liang2020,Han2021,Zhang2022,Liu2019d,Bereyhi2020,Xu2020b,Zhang2021d,Hua2022,Basar2020,Ma2020a,Yuan2021,Hu2021a} for backscatter information sources.
+		The former is impractical for passive backscatter devices while the latter does not fully exploit \gls{csi} and signal characteristics.
 	\end{subsection}
@@
 
+		% \emph{First,} we propose RIScatter as a novel scatter protocol that unifies \gls{bc} and \gls{ris} from a distribution perspective.
+		% As shown in Fig. \subref*{fg:riscatter}, the passive RIScatter node rides over an active transmission and controls the scattered wave to
+		% partially engineer the wireless channel and partially modulate its own information.
+		% This is accomplished by incorporating both the \gls{csi} and \gls{qos} into the reflection state distribution design.
+		% As such, RIScatter can generalize \gls{bc} (uniform distribution) and \gls{ris} (degenerate distribution) to create a tradeoff between backscatter modulation and passive beamforming.
+		% This is the first paper to associate \gls{bc} and \gls{ris} from a distribution perspective.
+
 		\emph{First,} we propose RIScatter as a novel scatter protocol that unifies \gls{bc} and \gls{ris} from a distribution perspective.
-		As shown in Fig. \subref*{fg:riscatter}, the passive RIScatter node rides over an active transmission and controls the scattered wave to
-		partially engineer the wireless channel and partially modulate its own information.
-		This is accomplished by incorporating both the \gls{csi} and \gls{qos} into the reflection state distribution design.
-		As such, RIScatter can generalize \gls{bc} (uniform distribution) and \gls{ris} (degenerate distribution) to create a tradeoff between backscatter modulation and passive beamforming.
+		As shown in Fig.
+\subref*{fg:riscatter}, the passive RIScatter node rides over an active transmission and controls the scattered wave to simultaneously engineer the wireless channel and modulate its own information, while a co-located receiver decodes both primary and backscatter links in a cooperative manner.
+		The reflection pattern of each RIScatter node is no longer fully random like \gls{bc} or fully deterministic like \gls{ris}, but can be semi-randomly chosen with the guidance of adaptive input state distribution, whose design incorporates the impact of information source, \gls{csi}, and \gls{qos} of both coexisting links.
+		Such an adaptive backscatter channel coding boils down to the degenerate distribution of \gls{ris} when primary link is prioritized, and outperforms the conventional line coding with equiprobable inputs of \gls{bc} (by accounting the \gls{csi}) when backscatter link is prioritized.
+		Besides, joint encoding over multiple co-located RIScatter nodes can further boost the total backscatter rate.
+		RIScatter enables simultaneous backscatter modulation and dynamic passive beamforming, and can smoothly transition in between under different \gls{qos}.
+		However, such a novel active-passive coexisting system encounters two major challenges, namely the cooperative receiver and input distribution designs.
 		This is the first paper to associate \gls{bc} and \gls{ris} from a distribution perspective.
-		% heterogeneous traffic control and universal hardware design
-
-		% I think you need to reemphasize what is the abstract and explain it further in light of the general observations you have drawn from the related works
-		% IScatter design compared to backcom and RIS. How to tackle those challenges would then be explained in the subsequent contributions.
-
-		\emph{Second,} we propose a practical receiver that accommodates the double modulation and signal difference in active-passive coexisting networks.
-		Since the primary and backscatter messages are superimposed by multiplication coding and the backscatter symbol is typically longer than primary, the scattered signals from RIScatter nodes can be treated as multipath components during primary decoding, and the primary symbols can be viewed as a spreading code during backscatter decoding.
-		Conventional sequential primary-backscatter decoder eliminates primary interference by \gls{sic} at each primary block, while our sequential backscatter-primary detector semi-coherently decodes RIScatter nodes from the received energy, re-encodes to recover exact reflection patterns, and models the deterministic multipath within primary equivalent channel as dynamic passive beamforming at each backscatter block.
-		It enables backscatter modulation and dynamic passive beamforming at much lower operational complexity, and is suitable for scatter nodes with various load-switching speeds.
-
-		\emph{Third,} we consider a scenario where multiple RIScatter nodes ride over an active point-to-point \gls{miso} transmission to perform backscatter modulation and passive beamforming towards a nearby user using shared spectrum, energy, and infrastructures.
+
+		\emph{Second,} we address the first challenge by proposing a practical receiver that effectively accommodates the double modulation and signal difference of RIScatter without \gls{sic}.
+		In active-passive coexisting networks, since the primary and backscatter messages are superimposed by multiplication and the backscatter symbol can be much longer than primary, the scattered signals from RIScatter nodes can be treated as (potentially random) multipath components during primary decoding, and the primary symbols can be viewed as a (potentially random) spreading code during backscatter decoding.
+		Both randomness cannot be eliminated simultaneously by sequential decoding.
+		Conventional \gls{sic}-based receiver that decodes from primary to backscatter link requires $N$ re-encoding, precoding, subtraction together with a time-domain \gls{mrc} to decode each backscatter symbol.
+		In contrast, the proposed practical receiver semi-coherently detects backscatter message from the accumulated receive energy, re-encodes to recover exact reflection patterns, and models the deterministic multipath within primary equivalent channel.
+		It preserves simultaneous backscatter modulation and dynamic passive beamforming by only one energy comparison, re-encoding, and precoding per backscatter symbol, and is suitable for arbitrary primary sampling rate and backscatter load-switching speed.
+
+		\emph{Third,} we address the second challenge by considering a scenario where multiple RIScatter nodes ride over an active point-to-point \gls{miso} transmission to perform backscatter modulation and passive beamforming towards a nearby user using shared spectrum, energy, and infrastructures.
 		We provide primary and total backscatter rate analyses and characterize the achievable rate region by optimizing input distribution at RIScatter nodes, active beamforming at the \gls{ap}, and backscatter decision regions at the user.
@@
 		\end{figure}
-		Instead of using fully random or fully deterministic reflection pattern over time, each RIScatter node semi-randomly chooses the reflection state for each backscatter block with guidance of input probability distribution $P(\Gamma_m)$ at state $m$.
+		Instead of using fully random or fully deterministic reflection pattern over time, each RIScatter node semi-randomly chooses the reflection state for each backscatter block with the guidance of input probability distribution $P(\Gamma_m)$ at state $m$.
 		Such an adaptive backscatter coding boils down to degenerate distribution of \gls{ris} when primary link is prioritized, and outperforms conventional line coding with equiprobable inputs (e.g., FM0 for \gls{rfid}) when backscatter link is prioritized.
@@
 			Fig. \subref*{fg:region_noise} depicts the impact of average noise power $\sigma_v^2$ on average rate regions.
-			It shows the proposed low-complexity semi-coherent backscatter energy detection is suitable for a wide range of noise levels.
+			It shows the proposed practical semi-coherent backscatter energy detection is suitable for a wide range of noise levels.
 			When $\sigma_v^2$ relatively high, we can choose a longer backscatter symbol period (i.e., larger $N$) to maintain the backscatter \gls{snr} for better detection performance.
@@
 	Starting from scattering principles, we showed how RIScatter nodes include information node of \gls{bc} and reflect element of \gls{ris} as special cases, how they can be built over existing passive scatter devices, and how they simultaneously encode self information and assist legacy transmission.
-	We also propose a low-complexity RIScatter receiver that preserves the benefits of backscatter modulation and passive beamforming.
+	We also propose a practical RIScatter receiver that preserves the benefits of backscatter modulation and dynamic passive beamforming without \gls{sic}.
 	The achievable primary-total-backscatter rate region is then studied for a single-user multi-node RIScatter system, where the input distribution, active beamforming, and decision thresholds are iteratively updated.
-	Numerical results not only demonstrated the effectiveness of the proposed algorithms, but also emphasized the importance of adaptive input distribution and cooperative decoding on both primary and backscatter subsystems.
+	Numerical results not only demonstrated the effectiveness of the proposed algorithms, but also emphasized the importance of adaptive input distribution and cooperative decoding on both primary and backscatter links.
 
@@
 	If one node can be decoded by multiple users, its input distribution may be further adjusted to mimic the multi-beam gain of dynamic passive beamforming \cite{Qiu2022}.
+	This will be answered in our future work.
 \end{section}

### 2022-11-28 assets/illustration/equivalent_circuit.tex
:paintbrush: Update illustrations
:mag: Update notations

--- 2022-05-26 assets/equivalent_circuit.tex
@@
 	to [sV,l=$V_0$] ++(0,1.5)
-	to [L,l=$X_{\mathrm{A}}$] ++(0,1.5)
-	to [R=$R_{\mathrm{A}}$,-*] ++(3,0) coordinate(AM)
+	to [L,l=$X_{\text{A}}$] ++(0,1.5)
+	to [R=$R_{\text{A}}$,-*] ++(3,0) coordinate(AM)
 	to [sI,l_=$I_0$,-*] ++(0,-3)
@@
 	to [L,l=$X_m$,-*] ++(3,0) coordinate(M)
-	to [R=$R_m^{\mathrm{S}}$] ++(3,0) coordinate(MH);
+	to [R=$R_{\text{S},m}$] ++(3,0) coordinate(MH);
 	\draw (M)
-	to [R=$R_m^{\mathrm{P}}$,-*] ++(0,-3);
+	to [R=$R_{\text{P},m}$,-*] ++(0,-3);
 	\draw (MH)
 	to [D,-*] ++(1.5,0) coordinate(H)
-	to [C=$X_{\mathrm{H}}$,-*] ++(0,-3);
+	to [C=$X_{\text{H}}$,-*] ++(0,-3);
 	\draw (H)
 	to [short] ++(1.5,0)
-	to [R=$R_{\mathrm{H}}$] ++(0,-3)
+	to [R=$R_{\text{H}}$] ++(0,-3)
 	to [short] (O);
 
-	\draw [blue,dashed] (-1.125,-0.5) rectangle (3.5,4);
-	\draw [yellow,dashed] (4,-0.5) rectangle (9,4);
-	\draw [red,dashed] (9.5,-0.5) rectangle (13.5,4);
+	\draw [dashed] (-1.125,-0.5) rectangle (3.5,4);
+	\draw [dashed] (4,-0.5) rectangle (9,4);
+	\draw [dashed] (9.5,-0.5) rectangle (13.5,4);
 
-	\draw [blue] (1.125,4.25) node[]{Antenna};
-	\draw [yellow] (6.5,4.25) node[]{Modulator};
-	\draw [red] (11.5,4.25) node[]{Harvester \& Chip};
+	\draw (1.125,4.25) node[]{Antenna};
+	\draw (6.5,4.25) node[]{Modulator};
+	\draw (11.5,4.25) node[]{Harvester \& Chip};
 
-	\draw (3.375,2.675) to [short] (3.375,3.175) to [short] (3.25,3.175) to [short,i_=$Z_{\mathrm{A}}$] (3.125,3.175);
+	\draw (3.375,2.675) to [short] (3.375,3.175) to [short] (3.25,3.175) to [short,i_=$Z_{\text{A}}$] (3.125,3.175);
 	\draw (4.125,-0.125) to [short] (4.125,0.375) to [short] (4.25,0.375) to [short,i=$Z_m$] (4.375,0.375);
-	\draw (9.625,-0.125) to [short] (9.625,0.375) to [short] (9.75,0.375) to [short,i=$Z_{\mathrm{H}}$] (9.875,0.375);
+	\draw (9.625,-0.125) to [short] (9.625,0.375) to [short] (9.75,0.375) to [short,i=$Z_{\text{H}}$] (9.875,0.375);
 \end{circuitikz}

### 2022-11-28 assets/illustration/scatter_model.tex
:truck: Move assets
:paintbrush: Update scatter model
:mag: Update notations

--- 2022-07-16 assets/scatter_model.tex
@@
-% \begin{circuitikz}[transform shape]
-% 	\tikzstyle{every node}=[font=\Large]
-% 	\draw (0,0) node[bareantenna](bareantenna){};
-% 	\draw (bareantenna.west) ++(-1.5,0) node[waves](WI){};
-% 	\draw (WI.north east) ++(0.25,0) node[font=\Large]{$\vec{E}_{\mathrm{I}}$};
-% 	\draw (WI.south east) ++(0.25,0) node[font=\Large]{$\vec{H}_{\mathrm{I}}$};
-% 	\draw (bareantenna.east) ++(0.875,0) node[waves](WR){};
-% 	\draw (WR.north east) ++(0.35,0) node[font=\Large]{$\vec{E}_m$};
-% 	\draw (WR.south east) ++(0.35,0) node[font=\Large]{$\vec{H}_m$};
-% 	\draw (bareantenna)
-% 	to [R=$Z_{\mathrm{A}}$] ++(0,-1.5) node[rotary switch=4 in 90 wiper 30,anchor=ext center,rotate=270](SW){};
-% 	\draw (SW.cout 2) node[below=0.1cm,font=\Large]{$m$}
-% 	to [R=$Z_m$] ++(2,0) node[ground]{};
-% \end{circuitikz}
-
 \begin{circuitikz}[transform shape]
 	\tikzstyle{every node}=[font=\large]
+	\ctikzset{multipoles/rotary/arrow=both}
 	\draw (0,0) node[bareantenna](bareantenna){};
 	\draw (bareantenna.west) ++(-1,0) node[waves](WI){};
-	\draw (WI.north east) ++(0.25,0) node{$\vec{E}_{\mathrm{I}}$};
-	\draw (WI.south east) ++(0.25,0) node{$\vec{H}_{\mathrm{I}}$};
+	\draw (WI.north east) ++(0.25,0) node{$\vec{E}_{\text{I}}$};
+	\draw (WI.south east) ++(0.25,0) node{$\vec{H}_{\text{I}}$};
 	\draw (bareantenna.east) ++(0.5,0) node[waves](WR){};
@@
 	\draw (WR.south east) ++(0.35,0) node{$\vec{H}_m$};
-	\draw (bareantenna) to ++(0,-1.1) to [generic,l=$Z_{\mathrm{A}}$,/tikz/circuitikz/bipoles/length=0.75cm] ++(2.3,0) node[rotary switch=4 in 90 wiper 30,anchor=ext center,rotate=0](SW){};
+	\draw (bareantenna) to ++(0,-1.1) to [generic,l=$Z_{\text{A}}$,/tikz/circuitikz/bipoles/length=0.75cm] ++(2.3,0) node[rotary switch=4 in 90 wiper 30,anchor=ext center,rotate=0](SW){};
 	\draw (SW.cout 1) to ++(0.625,+0.5) to [generic,/tikz/circuitikz/bipoles/length=0.75cm] ++(2.2,0) coordinate(E1);
@@
 	\draw (SW.cout 4) to ++(0.625,-0.5) to [generic,/tikz/circuitikz/bipoles/length=0.75cm] ++(2.2,0) coordinate(E4);
-	% \coordinate (E) at ($(E2)! 0.5!(E3)$);
 	\draw (E1) to[short,-*] (E2);
 	\draw (E2) to[short,-*] (E3);
-	% \draw (E2) to[short,-*] (E);
-	% \draw (E) to[short,-*] (E3);
 	\draw (E3) to[short] (E4);

### 2022-11-28 main.tex
:mag: Update notations

@@
 	$\mathrm{card}(\cdot)$ returns the cardinality of a set.
-	$(\cdot)^*$, $(\cdot)^T$, $(\cdot)^H$, $\lvert{\cdot}\rvert$, and $\lVert{\cdot}\rVert$ denote the conjugate, transpose, conjugate transpose, absolute value, and Euclidean norm operators, respectively.
+	$(\cdot)^*$, $(\cdot)^\mathsf{T}$, $(\cdot)^\mathsf{H}$, $\lvert{\cdot}\rvert$, and $\lVert{\cdot}\rVert$ denote the conjugate, transpose, conjugate transpose, absolute value, and Euclidean norm operators, respectively.
 	$(\cdot)^{(r)}$ and $(\cdot)^{\star}$ denote the $r$-th iterated and terminal solutions, respectively.
@@
 			The solid and dashed vectors represent signal and energy flows.
-			The scatter antenna behaves as a constant power source, where the voltage $V_0$ and current $I_0$ are introduced by incident electric field $\vec{E}_{\mathrm{I}}$ and magnetic field $\vec{H}_{\mathrm{I}}$ \cite{Huang2021}.
+			The scatter antenna behaves as a constant power source, where the voltage $V_0$ and current $I_0$ are introduced by incident electric field $\vec{E}_{\text{I}}$ and magnetic field $\vec{H}_{\text{I}}$ \cite{Huang2021}.
 			}
@@
 		We also omit the signal reflected by two or more times and ignore the propagation time difference of different paths.
-		Denote the \gls{ap}-user direct channel as $\boldsymbol{h}_{\mathrm{D}}^H \in \mathbb{C}^{1 \times Q}$, the \gls{ap}-node $k \in \mathcal{K} \triangleq \{1,\ldots,K\}$ forward channel as $\boldsymbol{h}_{\mathrm{F},k}^H \in \mathbb{C}^{1 \times Q}$, the node $k$-user backward channel as $h_{\mathrm{B},k}$, and the cascaded \gls{ap}-node $k$-user channel as $\boldsymbol{h}_{\mathrm{C},k}^H \triangleq h_{\mathrm{B},k} \boldsymbol{h}_{\mathrm{F},k}^H \in \mathbb{C}^{1 \times Q}$.
+		Denote the \gls{ap}-user direct channel as $\boldsymbol{h}_{\text{D}}^\mathsf{H} \in \mathbb{C}^{1 \times Q}$, the \gls{ap}-node $k \in \mathcal{K} \triangleq \{1,\ldots,K\}$ forward channel as $\boldsymbol{h}_{\text{F},k}^\mathsf{H} \in \mathbb{C}^{1 \times Q}$, the node $k$-user backward channel as $h_{\text{B},k}$, and the cascaded \gls{ap}-node $k$-user channel as $\boldsymbol{h}_{\text{C},k}^\mathsf{H} \triangleq h_{\text{B},k} \boldsymbol{h}_{\text{F},k}^\mathsf{H} \in \mathbb{C}^{1 \times Q}$.
 		Let $x_k \in \mathcal{X} \triangleq \{c_1,\ldots,c_M\}$ be the coded backscatter symbol of node $k$ and $x_{\mathcal{K}} \triangleq (x_1,\ldots,x_K)$ be the backscatter symbol tuple of all nodes.
@@
 			\begin{align}
-				\boldsymbol{h}_{\mathrm{E}}^H(x_{\mathcal{K}})
-				 & \triangleq \boldsymbol{h}_{\mathrm{D}}^H + \sum_{k} \alpha_k \boldsymbol{h}_{\mathrm{C},k}^H x_k \label{eq:equivalent_channel_bc}                    \\
-				 & = \boldsymbol{h}_{\mathrm{D}}^H + \boldsymbol{x}^H \mathrm{diag}(\boldsymbol{\alpha}) \boldsymbol{H}_{\mathrm{C}}, \label{eq:equivalent_channel_ris}
+				\boldsymbol{h}_{\text{E}}^\mathsf{H}(x_{\mathcal{K}})
+				 & \triangleq \boldsymbol{h}_{\text{D}}^\mathsf{H} + \sum_{k} \alpha_k \boldsymbol{h}_{\text{C},k}^\mathsf{H} x_k \label{eq:equivalent_channel_bc}                    \\
+				 & = \boldsymbol{h}_{\text{D}}^\mathsf{H} + \boldsymbol{x}^\mathsf{H} \mathrm{diag}(\boldsymbol{\alpha}) \boldsymbol{H}_{\text{C}}, \label{eq:equivalent_channel_ris}
 			\end{align}
 		\end{subequations}
-		where $\alpha_k \in \mathbb{I}$ is the amplitude scattering ratio of node $k$, $\boldsymbol{\alpha} \triangleq [\alpha_1,\ldots,\alpha_K]^T \in \mathbb{I}^{K}$, $\boldsymbol{x} \triangleq [x_1,\ldots,x_K]^H \in \mathcal{X}^{K}$, and $\boldsymbol{H}_{\mathrm{C}} \triangleq [\boldsymbol{h}_{\mathrm{C},1},\ldots,\boldsymbol{h}_{\mathrm{C},K}]^H \in \mathbb{C}^{K \times Q}$.
+		where $\alpha_k \in \mathbb{I}$ is the amplitude scattering ratio of node $k$, $\boldsymbol{\alpha} \triangleq [\alpha_1,\ldots,\alpha_K]^\mathsf{T} \in \mathbb{I}^{K}$, $\boldsymbol{x} \triangleq [x_1,\ldots,x_K]^\mathsf{H} \in \mathcal{X}^{K}$, and $\boldsymbol{H}_{\text{C}} \triangleq [\boldsymbol{h}_{\text{C},1},\ldots,\boldsymbol{h}_{\text{C},K}]^\mathsf{H} \in \mathbb{C}^{K \times Q}$.
 		The signal received by the user at primary block $n \in \mathcal{N} \triangleq \{1,\ldots,N\}$ is
 		\begin{equation}
-			y[n] = \boldsymbol{h}_{\mathrm{E}}^H(x_{\mathcal{K}}) \boldsymbol{w} s[n] + v[n],
+			y[n] = \boldsymbol{h}_{\text{E}}^\mathsf{H}(x_{\mathcal{K}}) \boldsymbol{w} s[n] + v[n],
 			\label{eq:receive_signal}
@@
 		\begin{equation}
-			\sigma_{m_{\mathcal{K}}}^2 = \lvert \boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2 + \sigma_v^2
+			\sigma_{m_{\mathcal{K}}}^2 = \lvert \boldsymbol{h}_{\text{E}}^\mathsf{H}(x_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2 + \sigma_v^2
 			\label{eq:receive_variance}
@@
 		where $t_l$ is the energy decision threshold between hypotheses $\mathcal{H}_{l}$ and $\mathcal{H}_{l+1}$.
-		For a given decision threshold vector $\boldsymbol{t} \triangleq [t_0,\ldots,t_L]^T \in \mathbb{R}_+^{(L+1)}$, we can formulate a \gls{dmtmac} with transition probability from input $x_{m_{\mathcal{K}}}$ to output $\hat{x}_{m_{\mathcal{K}}'}$ given by
+		For a given decision threshold vector $\boldsymbol{t} \triangleq [t_0,\ldots,t_L]^\mathsf{T} \in \mathbb{R}_+^{(L+1)}$, we can formulate a \gls{dmtmac} with transition probability from input $x_{m_{\mathcal{K}}}$ to output $\hat{x}_{m_{\mathcal{K}}'}$ given by
 		\begin{equation}
@@
 	\begin{subsection}{Achievable Rates}
-		Let $P_k(x_{m_k})$ be the input probability of node $k$ at state $m_k$, and $\boldsymbol{p}_k \triangleq [P_k(c_1),\ldots,P_k(c_M)]^T \in \mathbb{I}^{M}$ be the input distribution vector.
-		% Denote the input probability of node $k$ at state $m_k$ as $P_k(x_{m_k})$, and the input distribution vector as $\boldsymbol{p}_k \triangleq [P_k(c_1),\ldots,P_k(c_M)]^T \in \mathbb{I}^{M}$.
+		Let $P_k(x_{m_k})$ be the input probability of node $k$ at state $m_k$, and $\boldsymbol{p}_k \triangleq [P_k(c_1),\ldots,P_k(c_M)]^\mathsf{T} \in \mathbb{I}^{M}$ be the input distribution vector.
+		% Denote the input probability of node $k$ at state $m_k$ as $P_k(x_{m_k})$, and the input distribution vector as $\boldsymbol{p}_k \triangleq [P_k(c_1),\ldots,P_k(c_M)]^\mathsf{T} \in \mathbb{I}^{M}$.
 		For dispersed nodes with independent encoding, the probability of backscatter symbol tuple $x_{m_{\mathcal{K}}}$ is
@@
 		\begin{equation}
-			I_{\mathrm{B}}(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}}) \triangleq \sum_{m_{\mathcal{K}}'} P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}}) \log \frac{P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}})}{P_{\mathcal{K}}(\hat{x}_{m_{\mathcal{K}}'})},
+			I_{\text{B}}(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}}) \triangleq \sum_{m_{\mathcal{K}}'} P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}}) \log \frac{P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}})}{P_{\mathcal{K}}(\hat{x}_{m_{\mathcal{K}}'})},
 			\label{eq:backscatter_information_function}
@@
 		\begin{equation}
-			I_{\mathrm{B},k}(x_{m_k};\hat{x}_{\mathcal{K}}) \triangleq \sum_{m_{\mathcal{K} \setminus \{k\}}} P_{\mathcal{K} \setminus \{k\}}(x_{m_{\mathcal{K} \setminus \{k\}}}) I_{\mathrm{B}}(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}}),
+			I_{\text{B},k}(x_{m_k};\hat{x}_{\mathcal{K}}) \triangleq \sum_{m_{\mathcal{K} \setminus \{k\}}} P_{\mathcal{K} \setminus \{k\}}(x_{m_{\mathcal{K} \setminus \{k\}}}) I_{\text{B}}(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}}),
 			\label{eq:backscatter_marginal_information}
@@
 		\begin{equation}
-			I_{\mathrm{B}}(x_{\mathcal{K}};\hat{x}_{\mathcal{K}}) = \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) I_{\mathrm{B}}(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}}).
+			I_{\text{B}}(x_{\mathcal{K}};\hat{x}_{\mathcal{K}}) = \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) I_{\text{B}}(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}}).
 			\label{eq:backscatter_mutual_information}
@@
 		\begin{equation}
-			I_{\mathrm{P}}(s;y|x_{m_{\mathcal{K}}}) \triangleq \log \Bigl(1 + \frac{\lvert \boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_v^2}\Bigr),
+			I_{\text{P}}(s;y|x_{m_{\mathcal{K}}}) \triangleq \log \Bigl(1 + \frac{\lvert \boldsymbol{h}_{\text{E}}^\mathsf{H}(x_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_v^2}\Bigr),
 			\label{eq:primary_information_function}
@@
 		\begin{equation}
-			I_{\mathrm{P},k}(s;y|x_{m_k}) \triangleq \sum_{m_{\mathcal{K} \setminus \{k\}}} P_{\mathcal{K} \setminus \{k\}}(x_{m_{\mathcal{K} \setminus \{k\}}}) I_{\mathrm{P}}(s;y|x_{m_{\mathcal{K}}}),
+			I_{\text{P},k}(s;y|x_{m_k}) \triangleq \sum_{m_{\mathcal{K} \setminus \{k\}}} P_{\mathcal{K} \setminus \{k\}}(x_{m_{\mathcal{K} \setminus \{k\}}}) I_{\text{P}}(s;y|x_{m_{\mathcal{K}}}),
 			\label{eq:primary_marginal_information}
@@
 		\begin{equation}
-			I_{\mathrm{P}}(s;y|x_{\mathcal{K}}) = \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) I_{\mathrm{P}}(s;y|x_{m_{\mathcal{K}}}).
+			I_{\text{P}}(s;y|x_{\mathcal{K}}) = \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) I_{\text{P}}(s;y|x_{m_{\mathcal{K}}}).
 			\label{eq:primary_mutual_information}
@@
 			I(x_{m_{\mathcal{K}}})
-			 & \triangleq \rho I_{\mathrm{P}}(s;y|x_{m_{\mathcal{K}}}) + (1 - \rho) I_{\mathrm{B}}(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}}),\label{eq:weighted_sum_information_function} \\
+			 & \triangleq \rho I_{\text{P}}(s;y|x_{m_{\mathcal{K}}}) + (1 - \rho) I_{\text{B}}(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}}),\label{eq:weighted_sum_information_function} \\
 			I_k(x_{m_k})
-			 & \triangleq \rho I_{\mathrm{P},k}(s;y|x_{m_k}) + (1 - \rho) I_{\mathrm{B},k}(x_{m_k};\hat{x}_{\mathcal{K}}),\label{eq:weighted_sum_marginal_information}                     \\
+			 & \triangleq \rho I_{\text{P},k}(s;y|x_{m_k}) + (1 - \rho) I_{\text{B},k}(x_{m_k};\hat{x}_{\mathcal{K}}),\label{eq:weighted_sum_marginal_information}                     \\
 			I(x_{\mathcal{K}})
-			 & \triangleq \rho I_{\mathrm{P}}(s;y|x_{\mathcal{K}}) + (1 - \rho) I_{\mathrm{B}}(x_{\mathcal{K}};\hat{x}_{\mathcal{K}}),\label{eq:weighted_sum_mutual_information}
+			 & \triangleq \rho I_{\text{P}}(s;y|x_{\mathcal{K}}) + (1 - \rho) I_{\text{B}}(x_{\mathcal{K}};\hat{x}_{\mathcal{K}}),\label{eq:weighted_sum_mutual_information}
 		\end{align}
@@
 		{\scriptstyle{\{\boldsymbol{p}_k\}_{k \in \mathcal{K}},\boldsymbol{w},\boldsymbol{t}}}{I(x_{\mathcal{K}})}{\label{op:weighted_sum_rate}}{\label{ob:weighted_sum_rate}}
-		\addConstraint{\boldsymbol{1}^T \boldsymbol{p}_k}{=1,}{\quad \forall k}{\label{co:sum_probability}}
+		\addConstraint{\boldsymbol{1}^\mathsf{T} \boldsymbol{p}_k}{=1,}{\quad \forall k}{\label{co:sum_probability}}
 		\addConstraint{\boldsymbol{p}_k}{\ge \boldsymbol{0},}{\quad \forall k}{\label{co:nonnegative_probability}}
@@
 			\begin{algorithmic}[1]
-				\Require $K$, $N$, $\boldsymbol{h}_{\mathrm{D}}^H$, $\boldsymbol{H}_{\mathrm{C}}$, $\boldsymbol{\alpha}$, $\mathcal{X}$, $\sigma_v^2$, $\rho$, $\boldsymbol{w}$, $\boldsymbol{t}$, $\varepsilon$
+				\Require $K$, $N$, $\boldsymbol{h}_{\text{D}}^\mathsf{H}$, $\boldsymbol{H}_{\text{C}}$, $\boldsymbol{\alpha}$, $\mathcal{X}$, $\sigma_v^2$, $\rho$, $\boldsymbol{w}$, $\boldsymbol{t}$, $\varepsilon$
 				\Ensure $\{\boldsymbol{p}_k^\star\}_{k \in \mathcal{K}}$
-				\State Set $\boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}$ by \eqref{eq:equivalent_channel}
+				\State Set $\boldsymbol{h}_{\text{E}}^\mathsf{H}(x_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}$ by \eqref{eq:equivalent_channel}
 				\State \phantom{Set} $\sigma^2_{m_{\mathcal{K}}}$, $\forall m_{\mathcal{K}}$ by \eqref{eq:receive_variance}
@@
 		\begin{equation}
-			\nabla_{\boldsymbol{w}^*} Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr) = \frac{\boldsymbol{h}_{\mathrm{E}}(x_{m_{\mathcal{K}}})\boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}})\boldsymbol{w}}{(\sigma_{m_{\mathcal{K}}}^2)^2} g_{m_{\mathcal{K}}}(t_{l-1},t_l),
+			\nabla_{\boldsymbol{w}^*} Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr) = \frac{\boldsymbol{h}_{\text{E}}(x_{m_{\mathcal{K}}})\boldsymbol{h}_{\text{E}}^\mathsf{H}(x_{m_{\mathcal{K}}})\boldsymbol{w}}{(\sigma_{m_{\mathcal{K}}}^2)^2} g_{m_{\mathcal{K}}}(t_{l-1},t_l),
 			\label{eq:regularized_incomplete_gamma_gradient}
@@
 			\begin{equation}
-				I(x_{\mathcal{K}})=\sum_{m_{\mathcal{K}}}P_{\mathcal{K}}(x_{m_{\mathcal{K}}})\Biggl(\rho\log\Bigl(1+\frac{\lvert\boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}})\boldsymbol{w}\rvert^2}{\sigma_v^2}\Bigr)+(1-\rho)\sum_l Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr) \log \frac{Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr)}{\sum_{m_{\mathcal{K}}'} P_{\mathcal{K}}(x_{m_{\mathcal{K}}'}) Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}'}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}'}^2}\Bigr)}\Biggr)
+				I(x_{\mathcal{K}})=\sum_{m_{\mathcal{K}}}P_{\mathcal{K}}(x_{m_{\mathcal{K}}})\Biggl(\rho\log\Bigl(1+\frac{\lvert\boldsymbol{h}_{\text{E}}^\mathsf{H}(x_{m_{\mathcal{K}}})\boldsymbol{w}\rvert^2}{\sigma_v^2}\Bigr)+(1-\rho)\sum_l Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr) \log \frac{Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr)}{\sum_{m_{\mathcal{K}}'} P_{\mathcal{K}}(x_{m_{\mathcal{K}}'}) Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}'}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}'}^2}\Bigr)}\Biggr)
 				\label{eq:weighted_sum_mutual_information_explicit}
@@
 				\nabla_{\boldsymbol{w}^*} I(x_{\mathcal{K}})
-				 & = \sum_{m_{\mathcal{K}}}P_{\mathcal{K}}(x_{m_{\mathcal{K}}})\Biggl(\rho\frac{\boldsymbol{h}_{\mathrm{E}}(x_{m_{\mathcal{K}}})\boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}})\boldsymbol{w}}{\sigma_{m_{\mathcal{K}}}^2}+(1-\rho)\sum_l\biggl(\log\frac{Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr)}{\sum_{m_{\mathcal{K}}'}P_{\mathcal{K}}(x_{m_{\mathcal{K}}'})Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}'}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}'}^2}\Bigr)}+1\biggr)\nonumber                                                                  \\
+				 & = \sum_{m_{\mathcal{K}}}P_{\mathcal{K}}(x_{m_{\mathcal{K}}})\Biggl(\rho\frac{\boldsymbol{h}_{\text{E}}(x_{m_{\mathcal{K}}})\boldsymbol{h}_{\text{E}}^\mathsf{H}(x_{m_{\mathcal{K}}})\boldsymbol{w}}{\sigma_{m_{\mathcal{K}}}^2}+(1-\rho)\sum_l\biggl(\log\frac{Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr)}{\sum_{m_{\mathcal{K}}'}P_{\mathcal{K}}(x_{m_{\mathcal{K}}'})Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}'}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}'}^2}\Bigr)}+1\biggr)\nonumber                                                                  \\
 				 & \qquad \times \nabla_{\boldsymbol{w}^*} Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr)-\frac{Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr)\sum_{m_{\mathcal{K}}'}P_{\mathcal{K}}(x_{m_{\mathcal{K}}'})\nabla_{\boldsymbol{w}^*}Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}'}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}'}^2}\Bigr)}{\sum_{m_{\mathcal{K}}'}P_{\mathcal{K}}(x_{m_{\mathcal{K}}'})Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}'}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}'}^2}\Bigr)}\Biggr)
@@
 			\begin{algorithmic}[1]
-				\Require $Q$, $N$, $\boldsymbol{h}_{\mathrm{D}}^H$, $\boldsymbol{H}_{\mathrm{C}}$, $\boldsymbol{\alpha}$, $\mathcal{X}$, $P$, $\sigma_v^2$, $\rho$, $\{\boldsymbol{p}_k\}_{k \in \mathcal{K}}$, $\boldsymbol{t}$, $\alpha$, $\beta$, $\gamma$, $\varepsilon$
+				\Require $Q$, $N$, $\boldsymbol{h}_{\text{D}}^\mathsf{H}$, $\boldsymbol{H}_{\text{C}}$, $\boldsymbol{\alpha}$, $\mathcal{X}$, $P$, $\sigma_v^2$, $\rho$, $\{\boldsymbol{p}_k\}_{k \in \mathcal{K}}$, $\boldsymbol{t}$, $\alpha$, $\beta$, $\gamma$, $\varepsilon$
 				\Ensure $\boldsymbol{w}^\star$
-				\State Set $\boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}$ by \eqref{eq:equivalent_channel}
+				\State Set $\boldsymbol{h}_{\text{E}}^\mathsf{H}(x_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}$ by \eqref{eq:equivalent_channel}
 				\State \phantom{Set} $P_{\mathcal{K}}(x_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}$ by \eqref{eq:equivalent_distribution}
@@
 		\begin{maxi!}
-			{\scriptstyle{\boldsymbol{t} \in \mathcal{T}^{L+1}}}{I_{\mathrm{B}}(x_{\mathcal{K}};\hat{x}_{\mathcal{K}})}{\label{op:decision_threshold_discrete}}{\label{ob:decision_threshold_discrete}}
+			{\scriptstyle{\boldsymbol{t} \in \mathcal{T}^{L+1}}}{I_{\text{B}}(x_{\mathcal{K}};\hat{x}_{\mathcal{K}})}{\label{op:decision_threshold_discrete}}{\label{ob:decision_threshold_discrete}}
 			\addConstraint{\eqref{co:sequential_threshold},}
@@
 	where $d$ is the transmission distance, $L_0=-\qty{30}{\dB}$ is the reference path loss at $d_0=\qty{1}{\meter}$, $\kappa$ is the Rician $K$-factor, $\bar{\boldsymbol{H}}$ is the deterministic line-of-sight component with unit-magnitude entries, and $\tilde{\boldsymbol{H}}$ is the Rayleigh fading component with standard \gls{iid} \gls{cscg} entries.
-	We choose $\gamma_{\mathrm{D}}=2.6$, $\gamma_{\mathrm{F}}=2.4$, $\gamma_{\mathrm{B}}=2$, and $\kappa_{\mathrm{D}}=\kappa_{\mathrm{F}}=\kappa_{\mathrm{B}}=5$ for direct, forward and backward links.
+	We choose $\gamma_{\text{D}}=2.6$, $\gamma_{\text{F}}=2.4$, $\gamma_{\text{B}}=2$, and $\kappa_{\text{D}}=\kappa_{\text{F}}=\kappa_{\text{B}}=5$ for direct, forward and backward links.
 	The finite decision threshold domain $\mathcal{T}$ is obtained by $b$-bit uniform discretization over the critical interval defined by the confidence bounds of edge hypotheses (i.e., lower bound of $\mathcal{H}_1$ and upper bound of $\mathcal{H}_L$) with confidence $1-\varepsilon$, and we choose $b=9$ and $\varepsilon=\num{e-3}$.
@@
 			To characterize each achievable rate region, we progressively obtain all boundary points by successively increasing the primary \gls{qos} $\rho$ and solving problem \eqref{op:weighted_sum_rate}.
-			For $\rho=0$ where backscatter link is prioritized, we initialize Algorithm \ref{al:input_distribution} and \ref{al:active_beamforming} by uniform input distribution and \gls{mrt} towards sum cascaded channel $\sum_{k} \boldsymbol{h}_{\mathrm{C},k}^H$, respectively.
+			For $\rho=0$ where backscatter link is prioritized, we initialize Algorithm \ref{al:input_distribution} and \ref{al:active_beamforming} by uniform input distribution and \gls{mrt} towards sum cascaded channel $\sum_{k} \boldsymbol{h}_{\text{C},k}^\mathsf{H}$, respectively.
 			At the following points, both algorithms are initialized by the final solutions at the previous point.
@@
 			\begin{equation}
-				y^{\text{\gls{bbc}}}[n] = \Bigl(\boldsymbol{h}_{\mathrm{D}}^H + \sum_{k} \alpha_k \boldsymbol{h}_{\mathrm{C},k}^H x_k\Bigr) \boldsymbol{w} + v[n],
-			\end{equation}
-			which follows non-zero mean complex Gaussian distribution $\mathcal{CN}\bigl((\boldsymbol{h}_{\mathrm{D}}^H + \sum_{k} \alpha_k \boldsymbol{h}_{\mathrm{C},k}^H x_{m_k}) \boldsymbol{w},\sigma_v^2\bigr)$ under hypothesis $\mathcal{H}_{m_{\mathcal{K}}}$.
+				y^{\text{\gls{bbc}}}[n] = \Bigl(\boldsymbol{h}_{\text{D}}^\mathsf{H} + \sum_{k} \alpha_k \boldsymbol{h}_{\text{C},k}^\mathsf{H} x_k\Bigr) \boldsymbol{w} + v[n],
+			\end{equation}
+			which follows non-zero mean complex Gaussian distribution $\mathcal{CN}\bigl((\boldsymbol{h}_{\text{D}}^\mathsf{H} + \sum_{k} \alpha_k \boldsymbol{h}_{\text{C},k}^\mathsf{H} x_{m_k}) \boldsymbol{w},\sigma_v^2\bigr)$ under hypothesis $\mathcal{H}_{m_{\mathcal{K}}}$.
 			The corresponding \gls{pdf} of accumulated receive energy over $N$ primary blocks is
@@
 			\end{equation}
-			where $\mu_{m_{\mathcal{K}}}^{\text{\gls{bbc}}} \triangleq N \bigl\lvert \bigl(\boldsymbol{h}_{\mathrm{D}}^H + \sum_{k} \alpha_k \boldsymbol{h}_{\mathrm{C},k}^H x_{m_k}\bigr) \boldsymbol{w} \bigr\rvert^2$.
+			where $\mu_{m_{\mathcal{K}}}^{\text{\gls{bbc}}} \triangleq N \bigl\lvert \bigl(\boldsymbol{h}_{\text{D}}^\mathsf{H} + \sum_{k} \alpha_k \boldsymbol{h}_{\text{C},k}^\mathsf{H} x_{m_k}\bigr) \boldsymbol{w} \bigr\rvert^2$.
 			The \gls{ml} decision threshold is derived as, $\forall l \in \mathcal{L} \setminus \{L\}$,
@@
 			\begin{equation}
-				I_{\mathrm{P}}^{\text{\gls{ambc}}}(s;y) \approx \log \Bigl(1 + \frac{\lvert\boldsymbol{h}_{\mathrm{D}}^H\boldsymbol{w}\rvert^2}{\sum_{k}\lvert \alpha_k \boldsymbol{h}_{\mathrm{C},k}^H \boldsymbol{w}\rvert^2+\sigma_v^2}\Bigr),
+				I_{\text{P}}^{\text{\gls{ambc}}}(s;y) \approx \log \Bigl(1 + \frac{\lvert\boldsymbol{h}_{\text{D}}^\mathsf{H}\boldsymbol{w}\rvert^2}{\sum_{k}\lvert \alpha_k \boldsymbol{h}_{\text{C},k}^\mathsf{H} \boldsymbol{w}\rvert^2+\sigma_v^2}\Bigr),
 			\end{equation}
@@
 			\item \emph{\gls{sr}:} For a sufficiently large $N$, the average primary rate under semi-coherent detection asymptotically approaches \eqref{eq:primary_mutual_information} with uniform input distribution \cite{Long2020a}.
-			When $s[n]$ is successfully decoded and the direct interference $\boldsymbol{h}_{\mathrm{D}}^H \boldsymbol{w} s[n]$ is perfectly cancelled, the intermediate signal is
-			\begin{equation}
-				\hat{y}^{\text{\gls{sr}}}[n] = \sum_{k} \alpha_k \boldsymbol{h}_{\mathrm{C},k}^H x_k \boldsymbol{w} s[n] + v[n],
+			When $s[n]$ is successfully decoded and the direct interference $\boldsymbol{h}_{\text{D}}^\mathsf{H} \boldsymbol{w} s[n]$ is perfectly cancelled, the intermediate signal is
+			\begin{equation}
+				\hat{y}^{\text{\gls{sr}}}[n] = \sum_{k} \alpha_k \boldsymbol{h}_{\text{C},k}^\mathsf{H} x_k \boldsymbol{w} s[n] + v[n],
 				\label{eq:intermediate_signal}
@@
 			\begin{equation}
-				I_{\mathrm{B}}(x_{\mathcal{K}};\hat{y}_{\text{\gls{sr}}}) = K \log M - \frac{\epsilon}{M^K},
+				I_{\text{B}}(x_{\mathcal{K}};\hat{y}_{\text{\gls{sr}}}) = K \log M - \frac{\epsilon}{M^K},
 			\end{equation}
@@
 			\begin{equation}
-				I_{\mathrm{P}}^{\text{\gls{ris}}}(s;y|x_{\mathcal{K}}) = I_{\mathrm{P}}(s;y|x_{m_{\mathcal{K}}^{\star}}) = \log \Bigl(1 + \frac{\lvert \boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}^{\star}}) \boldsymbol{w} \rvert^2}{\sigma_v^2}\Bigr),
-			\end{equation}
-			where $m_{\mathcal{K}}^{\star} = \arg \max_{m_{\mathcal{K}}} I_{\mathrm{P}}(s;y|x_{m_{\mathcal{K}}})$.
+				I_{\text{P}}^{\text{\gls{ris}}}(s;y|x_{\mathcal{K}}) = I_{\text{P}}(s;y|x_{m_{\mathcal{K}}^{\star}}) = \log \Bigl(1 + \frac{\lvert \boldsymbol{h}_{\text{E}}^\mathsf{H}(x_{m_{\mathcal{K}}^{\star}}) \boldsymbol{w} \rvert^2}{\sigma_v^2}\Bigr),
+			\end{equation}
+			where $m_{\mathcal{K}}^{\star} = \arg \max_{m_{\mathcal{K}}} I_{\text{P}}(s;y|x_{m_{\mathcal{K}}})$.
 		\end{itemize}
@@
 				\item \emph{\gls{pgd}:} Iterative \gls{pgd} optimization by Algorithm \ref{al:active_beamforming};
-				\item \emph{E-\gls{mrt}:} \gls{mrt} towards the ergodic primary equivalent channel $\sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) \boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}})$;
-				\item \emph{D-\gls{mrt}:} \gls{mrt} towards the direct channel $\boldsymbol{h}_{\mathrm{D}}^H$.
+				\item \emph{E-\gls{mrt}:} \gls{mrt} towards the ergodic primary equivalent channel $\sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) \boldsymbol{h}_{\text{E}}^\mathsf{H}(x_{m_{\mathcal{K}}})$;
+				\item \emph{D-\gls{mrt}:} \gls{mrt} towards the direct channel $\boldsymbol{h}_{\text{D}}^\mathsf{H}$.
 			\end{itemize}
@@
 				J \bigl( P_{\mathcal{K}}(x_{m_{\mathcal{K}}}),P_{\mathcal{K}}'(x_{m_{\mathcal{K}}}) \bigr) \triangleq \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}})
-				\Biggl( \rho \log \Bigl(1 + \frac{\lvert \boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_v^2}\Bigr) + (1 - \rho) \sum_{m_{\mathcal{K}}'} P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}}) \log \frac{P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}}) P_{\mathcal{K}}'(x_{m_{\mathcal{K}}})}{P_{\mathcal{K}}'(\hat{x}_{m_{\mathcal{K}}'}) P_{\mathcal{K}}(x_{m_{\mathcal{K}}})} \Biggr).
+				\Biggl( \rho \log \Bigl(1 + \frac{\lvert \boldsymbol{h}_{\text{E}}^\mathsf{H}(x_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_v^2}\Bigr) + (1 - \rho) \sum_{m_{\mathcal{K}}'} P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}}) \log \frac{P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}}) P_{\mathcal{K}}'(x_{m_{\mathcal{K}}})}{P_{\mathcal{K}}'(\hat{x}_{m_{\mathcal{K}}'}) P_{\mathcal{K}}(x_{m_{\mathcal{K}}})} \Biggr).
 				\label{eq:intermediate_information_function}
@@
 	% 	Suppose the optimal number of thresholds is $S+1$ where $S \ge L$.
-	% 	Let $\boldsymbol{t} \triangleq [t_0,\ldots,t_S]^T \in \mathbb{R}_{+}^{(S+1)}$ be the optimal threshold vector where $t_{s-1} < t_s$, $\forall s \in \mathcal{S} \triangleq \{1,\ldots,S\}$.
+	% 	Let $\boldsymbol{t} \triangleq [t_0,\ldots,t_S]^\mathsf{T} \in \mathbb{R}_{+}^{(S+1)}$ be the optimal threshold vector where $t_{s-1} < t_s$, $\forall s \in \mathcal{S} \triangleq \{1,\ldots,S\}$.
 	% 	Since the optimal decision region for any letter may consist of multiple partitions, without loss of generality, we assume the mapping from threshold vector to decision region $l' \in \mathcal{L} \triangleq \{1,\ldots,L\}$ is given by $\mathcal{R}_{l'} = \bigcup_{s \equiv l' \pmod L} [t_{s-1},t_s)$.
@@
 	% 	\begin{maxi!}
-	% 		{\scriptstyle{\boldsymbol{t}}}{I_{\mathrm{B}}(x;\hat{x})}{\label{op:decision_threshold}}{\label{ob:backscatter_mutual_information}}
+	% 		{\scriptstyle{\boldsymbol{t}}}{I_{\text{B}}(x;\hat{x})}{\label{op:decision_threshold}}{\label{ob:backscatter_mutual_information}}
 	% 		\addConstraint{t_{s-1}}{< t_s,}{\quad \forall s \in \mathcal{S}.}{\label{co:strict_inequality}}
@@
 	% 	\begin{equation}
-	% 		L = - I_{\mathrm{B}}(x;\hat{x}) + \sum_{s \in \mathcal{S}} \mu_s (t_{s-1} - t_s),
+	% 		L = - I_{\text{B}}(x;\hat{x}) + \sum_{s \in \mathcal{S}} \mu_s (t_{s-1} - t_s),
 	% 	\end{equation}
@@
 	% 		\begin{equation}
-	% 			- \nabla_{t_s^\star} I^\star_{\mathrm{B}}(x;\hat{x}) + \mu_{s-1}^\star - \mu_s^\star = 0,
+	% 			- \nabla_{t_s^\star} I^\star_{\text{B}}(x;\hat{x}) + \mu_{s-1}^\star - \mu_s^\star = 0,
 	% 			\label{eq:stationarity}
@@
 	% 	\begin{equation}
-	% 		\nabla_{t_{s}^\star} I^\star_{\mathrm{B}}(x;\hat{x}) = 0,
+	% 		\nabla_{t_{s}^\star} I^\star_{\text{B}}(x;\hat{x}) = 0,
 	% 	\end{equation}

### 2022-12-01 main.tex
:construction: Update abstract

@@
 \begin{document}
-\title{RIScatter: Unifying Backscatter Communication and Reconfigurable Intelligent Surface From a Distribution Perspective}
+% \title{RIScatter: Unifying Backscatter Communication and Reconfigurable Intelligent Surface From a Distribution Perspective}
+\title{RIScatter: Unifying Backscatter Communication and Reconfigurable Intelligent Surface}
 \author{
@@
 	\gls{bc} nodes harvest energy from and modulate information over an external electromagnetic wave.
-	\gls{ris} adapts its phase shift response to enhance or suppress equivalent channel strength in specific directions.
+	\gls{ris} adapts its phase shift response to enhance channel strength in specific directions.
 	In this paper, we show how both seemingly different technologies and their derivatives can be unified to leverage their benefits simultaneously into a single architecture called RIScatter.
-	Envisioned as a next-generation communication protocol, RIScatter consists of multiple dispersed or co-located scatter nodes whose reflection states can be adapted to partially engineer the equivalent channel of the existing link and partially modulate their own information onto the scattered wave.
+	RIScatter consists of multiple dispersed or co-located scatter nodes whose reflection states can be adapted to partially engineer the channel of the existing link and partially modulate their own information onto the scattered wave.
 	This contrasts with \gls{bc} (resp. \gls{ris}) where the reflection pattern is exclusively a function of the information symbol (resp. \gls{csi}).
@@
 	For a single-user multi-node RIScatter network, we characterize the achievable primary-(total-)backscatter rate region by optimizing the input distribution at the nodes, the active beamforming at the \gls{ap}, and the backscatter detection regions at the user.
-	Simulation results demonstrate RIScatter nodes can exploit the additional propagation paths to smoothly transition between backscatter modulation and passive beamforming via smart input distribution design, and the tailored receiver effectively accommodates the double modulation and signal difference in active-passive coexisting networks without \gls{sic}.
+	Simulation results demonstrate RIScatter nodes can exploit the additional propagation paths to smoothly transition between backscatter modulation and passive beamforming via smart input distribution design, and the proposed practical receiver effectively accommodates the double modulation and signal difference in active-passive coexisting networks without \gls{sic}.
 \end{abstract}
@@
 
-		\emph{Fourth,} we provide numerical results to demonstrate the benefits of RIScatter and proposed algorithms.
-		We conclude:
+		\emph{Fourth,} we provide numerical results to demonstrate the benefits of RIScatter and proposed algorithms and make the following conclusions:
 		1) adaptive reflection state distribution design can flexibly transition between backscatter modulation and passive beamforming;

### 2022-12-06 main.tex
:dizzy: Update literature review

@@
 % \title{RIScatter: Unifying Backscatter Communication and Reconfigurable Intelligent Surface From a Distribution Perspective}
+% \title{RIScatter: Unifying Backscatter Communication and Reconfigurable Intelligent Surface}
+% \title{RIScatter: Unifying Backscatter Communication and Reconfigurable Intelligent Surface From State Distribution}
+% \title{RIScatter: Bridging Backscatter Modulation and Passive Beamforming With Adaptive State Distribution}
 \title{RIScatter: Unifying Backscatter Communication and Reconfigurable Intelligent Surface}
@@
 		The authors are with the Department of Electrical and Electronic Engineering, Imperial College London, London SW7 2AZ, U.K. (e-mail: \{yang.zhao18, b.clerckx\}@imperial.ac.uk).
+		B. Clerckx is also with Silicon Austria Labs (SAL), Graz A-8010, Austria.
 	}
@@
 % * hardward to modulate using RIS is already available.
-% * RIScatter: enhance backscatter signal difference (suppress primary interference) or primary signal strength.
+% * RIScatter: enhance backscatter signal characteristics (suppress primary interference) or primary signal strength.
 % ? For Backscatter community: why not adaptive channel coding? For RIS community: why not add randomness for modulation?
@@
 	\gls{bc} nodes harvest energy from and modulate information over an external electromagnetic wave.
-	\gls{ris} adapts its phase shift response to enhance channel strength in specific directions.
-	In this paper, we show how both seemingly different technologies and their derivatives can be unified to leverage their benefits simultaneously into a single architecture called RIScatter.
-	RIScatter consists of multiple dispersed or co-located scatter nodes whose reflection states can be adapted to partially engineer the channel of the existing link and partially modulate their own information onto the scattered wave.
+	\gls{ris} adapts its phase shift response to enhance or attenuate channel strength in specific directions.
+	In this paper, we show how those two seemingly different technologies (and their derivatives) can be unified to leverage their benefits simultaneously into a single architecture called RIScatter.
+	RIScatter consists of multiple dispersed or co-located scatter nodes whose reflection states can be adapted to partially engineer the wireless channel of the existing link and partially modulate their own information onto the scattered wave.
 	This contrasts with \gls{bc} (resp. \gls{ris}) where the reflection pattern is exclusively a function of the information symbol (resp. \gls{csi}).
@@
 	For a single-user multi-node RIScatter network, we characterize the achievable primary-(total-)backscatter rate region by optimizing the input distribution at the nodes, the active beamforming at the \gls{ap}, and the backscatter detection regions at the user.
-	Simulation results demonstrate RIScatter nodes can exploit the additional propagation paths to smoothly transition between backscatter modulation and passive beamforming via smart input distribution design, and the proposed practical receiver effectively accommodates the double modulation and signal difference in active-passive coexisting networks without \gls{sic}.
+	Simulation results demonstrate RIScatter nodes can exploit the additional propagation paths to smoothly transition between backscatter modulation and passive beamforming via smart input distribution design, and the proposed practical receiver effectively accommodates the double modulation and signal characteristics in active-passive coexisting networks without \gls{sic}.
 \end{abstract}
@@
 		In a \gls{sr} system, the active transmitter generates \gls{rf} wave carrying primary information, the passive node provides extra propagation path and ride its information over scattered signal, while the cooperative receiver jointly or sequentially decodes both links.
-		Those \gls{bc} applications employ scatter nodes as pure information sources, and the active transmission (if it exists) is indeed influenced by the randomness of backscatter modulation.
-		On the other hand, \gls{ris} is a smart planar signal reflector that consists of numerous compact passive elements with adjustable amplitude and phase responses.
+		Those \gls{bc} applications employ scatter nodes as pure information sources, and the active transmission (if it exists) is influenced by the randomness of backscatter modulation.
+		On the other hand, \gls{ris} in Fig. \ref{fg:ris} is a smart planar signal reflector that consists of numerous compact passive elements with adjustable amplitude and phase responses.
 		The reflection pattern is deterministic over time that can be adaptively optimized and coordinated in real time.
@@
 
-		Depending on the number of coexisting links, those scattering applications are divided into two categories that involve either active or passive transmission, or both active and passive transmissions.
-		The corresponding information flows are illustrated in Fig. \ref{fg:scatter_illustration}.
-		In \gls{mbc}/\gls{bbc} (resp. \gls{ris}), the passive device modulates information (resp. enhances propagation) while the active device generates carrier wave (resp. modulated signal).
-		There is only the backscatter (resp. primary) link and the detection can be coherent.
-		On the other hand, \gls{ambc} and \gls{sr} involve both links simultaneously, but the relationship in between is different.
-		For \gls{ambc}, the primary link does not need to be aware of the backscatter link and both links are interfering each other.
-		For \gls{sr}, both links are decoded by a co-located receiver, and cooperative transmission and reception become possible.
+		As illustrated in Fig. \ref{fg:scatter_illustration}, the scattering applications above involve either \emph{single active/passive link} or \emph{coexisting active and passive links}.
+		In \gls{mbc}/\gls{bbc} (resp.
+\gls{ris}), the passive device modulates information (resp.
+enhances propagation) and the active device generates carrier wave (resp.
+modulated signal), where the detection for the only passive backscatter (resp.
+active primary) link can be coherent.
+		On the other hand, \gls{ambc} and \gls{sr} simultaneously involve both links but the relationships in between are different.
+		For \gls{ambc}, the primary system does not need to be aware of the backscatter system and both links are interfering each other.
+		For \gls{sr}, both links are decoded by a co-located receiver such that cooperative transmission and reception become possible.
 		A comparison of different scattering applications is summarized in Table \ref{tb:scattering_applications}.
@@
 				Illustration of scattering applications.
-				For each, the blue flow(s) constitute the primary link while the magenta/green flow denotes the backscatter link.
+				For each, the blue flow(s) constitute the active primary link while the magenta/green flow denotes the passive backscatter link.
 			}
@@
 			Backscatter detection                           & Coherent            & Semi-coherent      & Coherent                                      & ---                 & Semi-coherent                                                           \\
-			Reflection pattern depends on           & Information source  & Information source & Information source                            & \gls{csi}           & Information source, \gls{csi}, and \gls{qos}                            \\
-			Input distribution                      & Equiprobable        & Equiprobable       & Equiprobable or Gaussian                      & Degenerate          & Flexible                                                                \\
+			Reflection pattern over time depends on         & Information source  & Information source & Information source                            & \gls{csi}           & Information source, \gls{csi}, and \gls{qos}                            \\
+			Reflection state (i.e.
+node input) distribution & Equiprobable        & Equiprobable       & Equiprobable or Gaussian                      & Degenerate          & Flexible                                                                \\
 			Load-switching speed                            & Fast                & Fast or slow       & Very slow                                     & Quasi-static        & Flexible                                                                \\ \bottomrule
@@
 		% However, it only considered the case where the primary and backscatter symbols of the same period are perfectly aligned in time.
-		% However, it assumed the primary and backscatter symbols of the same period are perfectly aligned in time.
 		Joint \gls{ml} decoding provides the best error performance for \gls{sr} but requires prohibitive computational complexity especially for high-order modulations \cite{Yang2018}.
@@
 		It motivated \cite{Long2020a,Liang2020,Guo2019b,Ding2020,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Yang2018,Han2021,Zhang2022} to view \gls{sr} as a multiplicative \gls{noma} and perform \gls{sic} from primary to backscatter link.
-		% sequential primary-backscatter decoding based on \gls{sic}.
 		During primary decoding, the backscatter randomness can be modelled as either interference or channel uncertainty, depending on the ratio $N$ of primary sampling rate over backscatter load-switching speed\footnote{For state-of-the-art low-power \gls{rfid} tags, the load-switching speed usually varies between \num{100}s of \unit{\kHz} to \num{10}s of \unit{\MHz} \cite{Torres2021}, corresponding to a typical $N$ between \num{10} and \num{1000}.}.
 		Such a sequential \gls{sic} involves $N$ re-encoding, precoding, subtraction together with a time-domain \gls{mrc} to decode each backscatter symbol, which can be operation-intensive and \gls{csi}-sensitive.
-		When $N$ is sufficiently large (i.e., commensal \gls{sr}), the average primary achievable rate under noncoherent detection asymptotically approaches its coherent counterpart, and both links can be decoded in an interference-free manner \cite{Long2020a}.
-		% However, the assumption of very large backscatter-over-primary symbol period ratio $N$ may not hold in practice\footnote{For example, Wi-Fi sampling rate is \qty{20}{\MHz} while \gls{rfid} load-switching speed varies between \num{100}s of \unit{\kHz} to \num{10}s of \unit{\MHz} \cite{Torres2021}, corresponding to a typical $N$ between \num{1} and \num{100}.}, and such a \gls{sic}-based sequential decoding requires re-encoding, precoding, and subtraction at each primary symbol block with a time-domain \gls{mrc}, which can be operation-intensive and \gls{csi}-sensitive.
+		When $N$ is sufficiently large (i.e., commensal \gls{sr}), the average primary achievable rate under noncoherent detection asymptotically approaches its coherent counterpart, and both links may be decoded in an interference-free manner \cite{Long2020a}.
 		Another open issue for \gls{bc} is the efficient backscatter multiple access design.
@@
 		To reduce coordination burden for passive nodes, \cite{Han2021} proposed a random code-assisted multiple access for \gls{sr} and evaluated the asymptotic \gls{sinr} using random matrix theory.
-		However, this code-domain solution suffers from the near-far problem and imperfect synchronization, both can be very severe in practical scenarios.
+		This code-domain solution suffers from the near-far problem and imperfect synchronization, both can be very severe in low-power backscatter scenarios.
 
@@
 		It introduces artificial channel diversity and enables flexible resource allocation, but misses the opportunity to encode message at the \gls{ris}.
-		% \gls{ris} can also be used as a transmitter when placed in the near field of a carrier emitter, and prototypes for \gls{psk} and \gls{qam} have been implemented in \cite{Tang2019a,Dai2020a}.
-		When placed in the near field of a carrier emitter, \gls{ris} can also be used as a transmitter, and prototypes for \gls{psk} and \gls{qam} have been implemented in \cite{Tang2019a,Dai2020a}.
-		From an information-theoretic perspective, \cite{Karasik2020} reported that using \gls{ris} as a naive passive beamformer to maximize the \gls{snr} is generally rate-suboptimal for finite input constellations.
-		Instead, the capacity of \gls{ris}-aided channel is achieved by joint transmitter-\gls{ris} encoding, and multiplication coding with \gls{sic} decoding (i.e., \gls{sic}-based \gls{sr}) can outperform passive beamforming at high \gls{snr}.
+		\gls{ris} can also be used as a transmitter when placed in the near field of a carrier emitter, and prototypes for \gls{psk} and \gls{qam} have been implemented in \cite{Tang2019a,Dai2020a}.
+		From an information-theoretic perspective, \cite{Karasik2020} reported that using \gls{ris} as a naive passive beamformer to maximize the receive \gls{snr} is generally rate-suboptimal for finite input constellations.
+		Instead, the capacity of \gls{ris}-aided channel is achieved by joint transmitter-\gls{ris} encoding, and multiplication coding with \gls{sic} decoding (i.e., \gls{sic}-based \gls{sr}) can indeed outperform passive beamforming at high \gls{snr}.
 		It inspired \gls{ris}-empowered \gls{bc} \cite{Liu2019d,Bereyhi2020,Xu2020b,Zhang2021d,Hu2021b,Hua2022,Basar2020,Ma2020a,Yuan2021,Hu2021a} to combine passive beamforming and backscatter modulation in the overall reflection pattern.
@@
 backscatter modulation) \cite{Hu2021a}.
-		% Those smart passive reflect elements/scatter nodes can recycle electromagnetic wave on the air to boost wireless channels and establish new connections, but incurs advanced hardware architecture and high optimization complexity.
-		% Those \gls{ris}-empowered \gls{bc} can recycle electromagnetic wave on the air to simultaneously boost wireless channels and establish new connections, but the reflect elements or scatter nodes incurs advanced hardware architecture and high optimization complexity.
-		Those \gls{ris}-empowered \gls{bc} designs can recycle \gls{rf} wave on the air and employ scattered paths to boost wireless channels and establish new connections, but incurs advanced hardware architecture and high optimization complexity.
-		Relevant literatures also consider either Gaussian codebook \cite{Guo2019b,Ding2020,Long2020a,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Hu2021b} or finite equiprobable inputs \cite{Yang2018,Liang2020,Han2021,Zhang2022,Liu2019d,Bereyhi2020,Xu2020b,Zhang2021d,Hua2022,Basar2020,Ma2020a,Yuan2021,Hu2021a} for backscatter information sources.
-		The former is impractical for passive backscatter devices while the latter does not fully exploit \gls{csi} and signal characteristics.
+		However, those \gls{ris}-empowered \gls{bc} designs incurs advanced hardware architecture and high optimization complexity.
+		Relevant literatures also consider either Gaussian codebook \cite{Guo2019b,Ding2020,Long2020a,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Hu2021b} or finite equiprobable inputs \cite{Yang2018,Liang2020,Han2021,Zhang2022,Liu2019d,Bereyhi2020,Xu2020b,Zhang2021d,Hua2022,Basar2020,Ma2020a,Yuan2021,Hu2021a} at backscatter information sources.
+		% The former is impractical for low-power node while the latter does not fully exploit \gls{csi} and signal characteristics in active-passive coexisting networks.
+		The former is impractical for low-power node while the latter does not fully exploit \gls{csi} and signal characteristics.
+
+		% Those \gls{ris}-empowered \gls{bc} designs demonstrate the active-passive coexisting networks
+		It has been observed for active-passive coexisting networks that
+		% 1) the transmitter-scatter-receiver path can be used simultaneously for backscatter modulation and passive beamforming;
+		1) the transmitter-scatter-receiver path can be used to simultaneously control wireless channels and establish passive connections;
+		2) co-located receiver enables cooperative primary and backscatter decoding;
+		3) it involves a double modulation of primary and backscatter symbols with different period;
+
+		% Relevant literatures also consider either Gaussian codebook \cite{Guo2019b,Ding2020,Long2020a,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Hu2021b} or finite equiprobable inputs \cite{Yang2018,Liang2020,Han2021,Zhang2022,Liu2019d,Bereyhi2020,Xu2020b,Zhang2021d,Hua2022,Basar2020,Ma2020a,Yuan2021,Hu2021a} at backscatter information sources.
+		% % The former is impractical for low-power node while the latter does not fully exploit \gls{csi} and signal characteristics in active-passive coexisting networks.
+		% The former is impractical for low-power node while the latter does not fully exploit \gls{csi} and signal characteristics.
+		Those \gls{ris}-empowered \gls{bc} designs
+		simultaneously enhance
+		can recycle \gls{rf} wave on the air and employ scattered paths to boost wireless channels and establish new connections, but incurs advanced hardware architecture and high optimization complexity.
+
+		Beyond WPT, [14] uniquely showed that the rectifier nonlinearity brings radical changes to SWIPT design, namely (i) modulated and unmodulated waveforms are not equally suitable for wireless power delivery; (ii) a multi-carrier unmodulated waveform superposed to a multi-carrier modulated waveform can enlarge the R-E region; (iii) a combination of PS and TS is generally the best strategy; (iv) the optimal input distribution is not the conventional Circularly Symmetric Complex Gaussian (CSCG); (v) modeling rectifier nonlinearity is beneficial to system performance and essential to efficient SWIPT design.
+Those observations, validated experimentally in [9], led to the question: What is the optimal input distribution for SWIPT under nonlinearity?
+This question was answered in [15] for single-carrier SWIPT, and some attempts were further made in [16] for multi-carrier SWIPT.
+The answers shed new light to the fundamental limits of SWIPT and practical signaling (e.g., modulation and waveform) strategies.
+It is now well understood from [14]–[16] that, due to harvester nonlinearity, a combination of CSCG and on-off keying in single-carrier setting and non-zero mean asymmetric inputs in multi-carrier setting lead to significantly larger R-E region compared to conventional CSCG.
+
+		It is now well understood from [14]–[16] that, due to harvester nonlinearity, a combination of CSCG and on-off keying in single-carrier setting and non-zero mean asymmetric inputs in multi-carrier setting lead to significantly larger R-E region compared to conventional CSCG
 	\end{subsection}
@@
 
-		\emph{Second,} we address the first challenge by proposing a practical receiver that effectively accommodates the double modulation and signal difference of RIScatter without \gls{sic}.
+		\emph{Second,} we address the first challenge by proposing a practical receiver that effectively accommodates the double modulation and signal characteristics of RIScatter without \gls{sic}.
 		In active-passive coexisting networks, since the primary and backscatter messages are superimposed by multiplication and the backscatter symbol can be much longer than primary, the scattered signals from RIScatter nodes can be treated as (potentially random) multipath components during primary decoding, and the primary symbols can be viewed as a (potentially random) spreading code during backscatter decoding.

### 2022-12-06 main.tex
:construction: Add observations

@@
 		Conventional \gls{ris} design with fixed reflection coefficients during each channel block has been extensively studied in communication, sensing, and power literatures \cite{Wu2018,Zhang2019a,Lin2022,Liu2022,Feng2022,Zhao2022}.
-		On the other hand, dynamic \gls{ris} with independent reflection patterns at different transmission phases has gained recent attentions in multi-user and multi-purpose wireless networks.
+		On the other hand, dynamic \gls{ris} with independent reflection patterns at different time slots has gained recent attentions in multi-user and multi-purpose wireless networks.
 		The concept was first proposed in \cite{Yang2020} to fine-tune the \gls{ofdm} resource blocks, then extended to the downlink power and uplink information phases of \gls{wpcn} \cite{Wu2021,Wu2021d,Hua2022a}.
@@
 backscatter modulation) \cite{Hu2021a}.
-		However, those \gls{ris}-empowered \gls{bc} designs incurs advanced hardware architecture and high optimization complexity.
-		Relevant literatures also consider either Gaussian codebook \cite{Guo2019b,Ding2020,Long2020a,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Hu2021b} or finite equiprobable inputs \cite{Yang2018,Liang2020,Han2021,Zhang2022,Liu2019d,Bereyhi2020,Xu2020b,Zhang2021d,Hua2022,Basar2020,Ma2020a,Yuan2021,Hu2021a} at backscatter information sources.
-		% The former is impractical for low-power node while the latter does not fully exploit \gls{csi} and signal characteristics in active-passive coexisting networks.
-		The former is impractical for low-power node while the latter does not fully exploit \gls{csi} and signal characteristics.
-
-		% Those \gls{ris}-empowered \gls{bc} designs demonstrate the active-passive coexisting networks
-		It has been observed for active-passive coexisting networks that
-		% 1) the transmitter-scatter-receiver path can be used simultaneously for backscatter modulation and passive beamforming;
-		1) the transmitter-scatter-receiver path can be used to simultaneously control wireless channels and establish passive connections;
-		2) co-located receiver enables cooperative primary and backscatter decoding;
-		3) it involves a double modulation of primary and backscatter symbols with different period;
-
-		% Relevant literatures also consider either Gaussian codebook \cite{Guo2019b,Ding2020,Long2020a,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Hu2021b} or finite equiprobable inputs \cite{Yang2018,Liang2020,Han2021,Zhang2022,Liu2019d,Bereyhi2020,Xu2020b,Zhang2021d,Hua2022,Basar2020,Ma2020a,Yuan2021,Hu2021a} at backscatter information sources.
-		% % The former is impractical for low-power node while the latter does not fully exploit \gls{csi} and signal characteristics in active-passive coexisting networks.
-		% The former is impractical for low-power node while the latter does not fully exploit \gls{csi} and signal characteristics.
-		Those \gls{ris}-empowered \gls{bc} designs
-		simultaneously enhance
-		can recycle \gls{rf} wave on the air and employ scattered paths to boost wireless channels and establish new connections, but incurs advanced hardware architecture and high optimization complexity.
-
-		Beyond WPT, [14] uniquely showed that the rectifier nonlinearity brings radical changes to SWIPT design, namely (i) modulated and unmodulated waveforms are not equally suitable for wireless power delivery; (ii) a multi-carrier unmodulated waveform superposed to a multi-carrier modulated waveform can enlarge the R-E region; (iii) a combination of PS and TS is generally the best strategy; (iv) the optimal input distribution is not the conventional Circularly Symmetric Complex Gaussian (CSCG); (v) modeling rectifier nonlinearity is beneficial to system performance and essential to efficient SWIPT design.
-Those observations, validated experimentally in [9], led to the question: What is the optimal input distribution for SWIPT under nonlinearity?
-This question was answered in [15] for single-carrier SWIPT, and some attempts were further made in [16] for multi-carrier SWIPT.
-The answers shed new light to the fundamental limits of SWIPT and practical signaling (e.g., modulation and waveform) strategies.
-It is now well understood from [14]–[16] that, due to harvester nonlinearity, a combination of CSCG and on-off keying in single-carrier setting and non-zero mean asymmetric inputs in multi-carrier setting lead to significantly larger R-E region compared to conventional CSCG.
-
-		It is now well understood from [14]–[16] that, due to harvester nonlinearity, a combination of CSCG and on-off keying in single-carrier setting and non-zero mean asymmetric inputs in multi-carrier setting lead to significantly larger R-E region compared to conventional CSCG
+		However, those joint designs incur advanced hardware architecture and high optimization complexity.
+		Relevant \gls{bc} literatures also consider either \emph{Gaussian} codebook \cite{Guo2019b,Ding2020,Long2020a,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Hu2021b} that is impractical for low-power nodes, or finite equiprobable inputs \cite{Yang2018,Liang2020,Han2021,Zhang2022,Liu2019d,Bereyhi2020,Xu2020b,Zhang2021d,Hua2022,Basar2020,Ma2020a,Yuan2021,Hu2021a} that does not fully exploit \gls{csi} and signal characteristics.
+		For active-passive coexisting networks, it has been observed that:
+		1) \gls{rf} waves on the air can be effectively recycled by smart scattering;
+		% 2) transmitter-scatter-receiver paths can be used to simultaneously control wireless channels and establish passive connections;
+		2) transmitter-scatter-receiver paths can be exploited simultaneously for backscatter modulation and passive beamforming;
+		3) co-located primary and backscatter receiver enables interference cancellation and cooperative decoding;
+		4) the primary and backscatter symbols are superimposed by multiplication (i.e., double modulation).
 	\end{subsection}

### 2022-12-07 main.tex
:pencil: Update scattering comparison

@@
 \newacronym{wpt}{WPT}{Wireless Power Transfer}
-\newacronym{mbc}{MBC}{Monostatic Backscatter Communication}
-\newacronym{bbc}{BBC}{Bistatic Backscatter Communication}
+\newacronym{mbc}{MBC}{Monostatic \glsentryshort{bc}}
+\newacronym{bbc}{BBC}{Bistatic \glsentryshort{bc}}
 \newacronym{bls}{BLS}{Backtracking Line Search}
@@
 	This contrasts with \gls{bc} (resp. \gls{ris}) where the reflection pattern is exclusively a function of the information symbol (resp. \gls{csi}).
-	The key principle in RIScatter is to render the probability distribution of reflection states as a joint function of the information source, \gls{csi}, and \gls{qos} of both coexisting links.
+	The key principle in RIScatter is to render the probability distribution of reflection states as a joint function of the information source, \gls{csi}, and \gls{qos} of the active primary and passive backscatter links.
 	This enables RISscatter to softly bridge, generalize, and outperform \gls{bc} and \gls{ris}; boil down to either under specific input distribution; or evolve in a mixed form for heterogeneous traffic control and universal hardware design.
 	For a single-user multi-node RIScatter network, we characterize the achievable primary-(total-)backscatter rate region by optimizing the input distribution at the nodes, the active beamforming at the \gls{ap}, and the backscatter detection regions at the user.
-	Simulation results demonstrate RIScatter nodes can exploit the additional propagation paths to smoothly transition between backscatter modulation and passive beamforming via smart input distribution design, and the proposed practical receiver effectively accommodates the double modulation and signal characteristics in active-passive coexisting networks without \gls{sic}.
+	% Simulation results demonstrate RIScatter nodes can exploit the additional propagation paths to smoothly transition between backscatter modulation and passive beamforming via smart input distribution design, and the proposed practical receiver effectively accommodates the double modulation and signal characteristics in active-passive coexisting networks without \gls{sic}.
+	Simulation results demonstrate RIScatter nodes can exploit the additional propagation paths to smoothly transition between backscatter modulation and passive beamforming, and the proposed practical receiver accommodates the double modulation and signal characteristics in active-passive coexisting networks without \gls{sic}.
 \end{abstract}
@@
 		As a mature low-power communication technique, \gls{bc} separates a conventional transmitter into a \gls{rf} carrier emitter with power-hungry elements (e.g., synthesizer and amplifier) and an information-bearing node with power-efficient components (e.g., harvester and modulator) \cite{Boyer2014}.
-		In particular, the node harvests energy from impinging wave and embeds information over scattered signal, while the backscatter reader can be either co-located or separated with the carrier emitter, known as \gls{mbc} and \gls{bbc} in Fig.
-\subref*{fg:mbc} and \subref*{fg:bbc}, respectively.
-		Its applications such as \gls{rfid} \cite{Dobkin2012,Landt2005} and passive sensor network \cite{Vannucci2008,Assimonis2016} have been extensively researched, standardized, and commercialized in the era of \gls{ioe}.
+		In particular, the node harvests energy from impinging wave and embeds information over scattered signal, while the backscatter reader can be either co-located or separated with the carrier emitter, known as \gls{mbc} in Fig.
+\subref*{fg:mbc} and \gls{bbc} in Fig.
+\subref*{fg:bbc}.
+		Relevant applications such as \gls{rfid} \cite{Dobkin2012,Landt2005} and passive sensor network \cite{Vannucci2008,Assimonis2016} have been extensively researched, standardized, and commercialized in the era of \gls{ioe}.
 		However, conventional \gls{bc} nodes only respond when externally inquired by a nearby reader.
-		\gls{ambc} was then proposed in \cite{Liu2013b} where battery-free nodes recycle ambient signals (e.g., radio, television and Wi-Fi) to harvest energy and establish connection in between.
-		As shown in Fig. \subref*{fg:ambc}, it eliminates the need of dedicated power supply, carrier emitter and frequency spectrum, but is subject to the strong direct-link interference.
-		To tackle this, \cite{Yang2018} proposed cooperative \gls{ambc} where both primary (legacy) and backscatter links are decoded by the same receiver under various detection schemes.
-		The concept was further refined as \gls{sr} illustrated in Fig. \subref*{fg:sr} that cognitively incorporates \gls{ambc} with existing systems \cite{Liang2020}.
-		In a \gls{sr} system, the active transmitter generates \gls{rf} wave carrying primary information, the passive node provides extra propagation path and ride its information over scattered signal, while the cooperative receiver jointly or sequentially decodes both links.
-		Those \gls{bc} applications employ scatter nodes as pure information sources, and the active transmission (if it exists) is influenced by the randomness of backscatter modulation.
-		On the other hand, \gls{ris} in Fig. \ref{fg:ris} is a smart planar signal reflector that consists of numerous compact passive elements with adjustable amplitude and phase responses.
-		The reflection pattern is deterministic over time that can be adaptively optimized and coordinated in real time.
-		\gls{ris} recycles and redistributes the surrounding \gls{rf} waves to customize the wireless propagation environment for signal enhancement, interference suppression, scattering enrichment and non-line-of-sight bypassing \cite{Wu2021b}.
-
-		As illustrated in Fig. \ref{fg:scatter_illustration}, the scattering applications above involve either \emph{single active/passive link} or \emph{coexisting active and passive links}.
-		In \gls{mbc}/\gls{bbc} (resp.
-\gls{ris}), the passive device modulates information (resp.
+		To tackle this, \cite{Liu2013b} proposed \gls{ambc} where battery-free nodes recycle ambient signals (e.g., radio, television and Wi-Fi) to harvest energy and establish connection in between.
+		As shown in Fig.
+\subref*{fg:ambc}, it eliminates the need of dedicated power supply, carrier emitter and frequency spectrum, but backscatter decoding is subject to the strong interference from the primary (legacy) link.
+		Cooperative \gls{ambc} was then proposed where a co-located receiver decodes both active primary and passive backscatter links, where the rate and error performance are evaluated for various detection schemes \cite{Yang2018}.
+		This concept was further refined by \cite{Liang2020} as \gls{sr} in Fig. \subref*{fg:sr} that cognitively incorporates \gls{ambc} with existing systems.
+		In a \gls{sr} system, the active transmitter generates \gls{rf} wave carrying primary information, the passive node provides additional propagation path and ride its information over scattered signal, while the cooperative receiver jointly or sequentially decodes both links.
+		Those \gls{bc} applications employ scatter nodes as pure information sources, and the active primary transmission (if it exists) can be influenced by the randomness of backscatter modulation.
+		On the other hand, \gls{ris} in Fig.
+\ref{fg:ris} is a smart planar signal reflector that consists of numerous compact passive elements with adjustable amplitude and phase responses, whose reflection pattern over time is deterministic and optimized based on \gls{csi}.
+		\gls{ris} smartly reflects the surrounding \gls{rf} waves to customize the wireless propagation environment for signal enhancement, interference suppression, scattering enrichment and non-line-of-sight bypassing \cite{Wu2021b}.
+		In summary, \gls{mbc}/\gls{bbc} (resp.
+\gls{ris}) involves a \emph{single} passive backscatter (resp.
+active primary) link where the passive device modulates information (resp.
 enhances propagation) and the active device generates carrier wave (resp.
-modulated signal), where the detection for the only passive backscatter (resp.
-active primary) link can be coherent.
-		On the other hand, \gls{ambc} and \gls{sr} simultaneously involve both links but the relationships in between are different.
-		For \gls{ambc}, the primary system does not need to be aware of the backscatter system and both links are interfering each other.
-		For \gls{sr}, both links are decoded by a co-located receiver such that cooperative transmission and reception become possible.
-		A comparison of different scattering applications is summarized in Table \ref{tb:scattering_applications}.
+modulated signal).
+		% On the other hand, \gls{ambc} and \gls{sr} involve \emph{coexisting} active primary and passive backscatter links with different relationships in between.
+		On the other hand, \gls{ambc} (resp. \gls{sr}) involves \emph{coexisting} active primary and passive backscatter links in a competitive (resp. collaborative) relationship.
+		In \gls{ambc}, the backscatter link only needs to know the basic information (e.g., operating frequency and input distribution) of the primary link, and the primary link does not need to know the existence of the backscatter link.
+		% In \gls{sr}, relevant \gls{csi} of both links should be available at the co-located receiver for cooperative decoding
+		% In \gls{sr}, the co-located receiver needs to know the \gls{csi} of both links for cooperative decoding, and the primary transmitter may know
+		In \gls{sr}, relevant \gls{csi} is exploited at the co-located receiver for cooperative decoding, and may also be exploited at the primary transmitter for cooperative active beamforming.
+		A comparison of those scattering applications is summarized in Table \ref{tb:scattering_applications}.
 
@@
 	\end{subsection}
+
+	% \begin{table*}[!t]
+	% 	\caption{Comparison of Scattering Applications}
+	% 	\label{tb:scattering_applications}
+	% 	\rowcolors{2}{gray!25}{white}
+	% 	\renewcommand{\arraystretch}{1.5}
+	% 	\begin{tabularx}{\textwidth}{CCCCCC}
+	% 		\toprule
+	% 		\hiderowcolors
+	% 		                                                & \gls{mbc}/\gls{bbc} & \gls{ambc}         & \gls{sr}                                      & \gls{ris}           & RIScatter                                                               \\ \midrule
+	% 		\showrowcolors
+	% 		Coexisting link(s)                              & 1                   & 2 (competitive)    & 2 (collaborative)                             & 1                   & 2 (collaborative)                                                       \\
+	% 		Primary/Backscatter modulation                  & No/Yes              & Yes/Yes            & Yes/Yes                                       & Yes/No              & Yes/Yes                                                                 \\
+	% 		Primary impact on backscatter detection         & Carrier             & Interference       & Spreading code                                & ---                 & Energy uncertainty                                                      \\
+	% 		Backscatter impact on primary detection         & ---                 & Interference       & Channel uncertainty                           & Passive beamforming & Dynamic passive beamforming                                             \\
+	% 		Cooperative transmission(s)                     & ---                 & No                 & Primary transmitter (active beamforming)      & ---                 & Primary transmitter and scatter nodes                                   \\
+	% 		Co-located receiver                             & ---                 & No                 & Usually \gls{sic} from primary to backscatter & ---                 & No \gls{sic}, backscatter detection as part of primary channel training \\
+	% 		Primary detection                               & ---                 & Semi-coherent      & Semi-coherent                                 & Coherent            & Coherent                                                                \\
+	% 		Backscatter detection                           & Coherent            & Semi-coherent      & Coherent                                      & ---                 & Semi-coherent                                                           \\
+	% 		Reflection pattern over time depends on         & Information source  & Information source & Information source                            & \gls{csi}           & Information source, \gls{csi}, and \gls{qos}                            \\
+	% 		Reflection state (i.e.
+node input) distribution & Equiprobable        & Equiprobable       & Equiprobable or Gaussian                      & Degenerate          & Flexible                                                                \\
+	% 		Load-switching speed                            & Fast                & Fast or slow       & Very slow                                     & Quasi-static        & Flexible                                                                \\ \bottomrule
+	% 	\end{tabularx}
+	% \end{table*}
 
@@
 			Primary impact on backscatter detection                 & Carrier             & Interference       & Spreading code                                & ---                 & Energy uncertainty                                                      \\
-			Scatterer impact on primary detection           & ---                 & Interference       & Channel uncertainty                           & Passive beamforming & Dynamic passive beamforming                                             \\
-			Cooperative transmission(s)                     & ---                 & No                 & Primary transmitter (active beamforming)      & ---                 & Primary transmitter and scatter nodes                                   \\
-			Co-located receiver                             & ---                 & No                 & Usually \gls{sic} from primary to backscatter & ---                 & No \gls{sic}, backscatter detection as part of primary channel training \\
+			Backscatter impact on primary detection                 & ---                 & Interference       & Channel uncertainty                           & Passive beamforming & Dynamic passive beamforming                                             \\
+			Cooperation devices                                     & ---                 & No                 & Co-located receiver (and primary transmitter) & ---                 & Primary transmitter, scatter nodes, and co-located receiver             \\
+			Cooperative decoding strategy                           & ---                 & No                 & Usually \gls{sic} from primary to backscatter & ---                 & No \gls{sic}, backscatter detection as part of primary channel training \\
 			Primary detection                                       & ---                 & Semi-coherent      & Semi-coherent                                 & Coherent            & Coherent                                                                \\
@@
 			Reflection pattern over time depends on                 & Information source  & Information source & Information source                            & \gls{csi}           & Information source, \gls{csi}, and \gls{qos}                            \\
-			Reflection state (i.e.
-node input) distribution & Equiprobable        & Equiprobable       & Equiprobable or Gaussian                      & Degenerate          & Flexible                                                                \\
+			Reflection state (i.e., backscatter input) distribution & Equiprobable        & Equiprobable       & Equiprobable or Gaussian                      & Degenerate          & Flexible                                                                \\
 			Load-switching speed                                    & Fast                & Fast or slow       & Very slow                                     & Quasi-static        & Flexible                                                                \\ \bottomrule
@@
 	\end{table*}
+
+	% ! cooperation:
+	% - ambc: none
+	% - sr: rx (possibly tx)
+	% - riscatter: rx, tx, sx
+	% ! csi, qos and backscatter constellation-aware input distribution + beamforming
+	% ! csi and backscatter constellation-aware detection
 
@@
 		In contrast, the proposed practical receiver semi-coherently detects backscatter message from the accumulated receive energy, re-encodes to recover exact reflection patterns, and models the deterministic multipath within primary equivalent channel.
+		The semi-coherent backscatter detection is indeed part of primary channel estimation.
 		It preserves simultaneous backscatter modulation and dynamic passive beamforming by only one energy comparison, re-encoding, and precoding per backscatter symbol, and is suitable for arbitrary primary sampling rate and backscatter load-switching speed.

### 2022-12-08 main.tex
:pencil: Update literature review

@@
 % * backscatter modulation <-> passive beamforming; add adaptive channel coding over (NRZ) line coding.
-% ? semicoherent: known CSI, unknown primary/backscatter symbols
+% ? semi-coherent: known CSI, unknown primary/backscatter symbols
 % * initialization, convergence, base 2 in simulation
@@
 	In this paper, we show how those two seemingly different technologies (and their derivatives) can be unified to leverage their benefits simultaneously into a single architecture called RIScatter.
-	RIScatter consists of multiple dispersed or co-located scatter nodes whose reflection states can be adapted to partially engineer the wireless channel of the existing link and partially modulate their own information onto the scattered wave.
+	RIScatter consists of multiple dispersed or co-located scatter nodes, whose reflection states can be adapted to partially engineer the wireless channel of the existing link and partially modulate their own information onto the scattered wave.
 	This contrasts with \gls{bc} (resp. \gls{ris}) where the reflection pattern is exclusively a function of the information symbol (resp. \gls{csi}).
-	The key principle in RIScatter is to render the probability distribution of reflection states as a joint function of the information source, \gls{csi}, and \gls{qos} of the active primary and passive backscatter links.
+	The key principle in RIScatter is to render the probability distribution of reflection states as a joint function of the information source, \gls{csi}, and \gls{qos} of the coexisting active primary and passive backscatter links.
 	This enables RISscatter to softly bridge, generalize, and outperform \gls{bc} and \gls{ris}; boil down to either under specific input distribution; or evolve in a mixed form for heterogeneous traffic control and universal hardware design.
@@
 	% Simulation results demonstrate RIScatter nodes can exploit the additional propagation paths to smoothly transition between backscatter modulation and passive beamforming via smart input distribution design, and the proposed practical receiver effectively accommodates the double modulation and signal characteristics in active-passive coexisting networks without \gls{sic}.
-	Simulation results demonstrate RIScatter nodes can exploit the additional propagation paths to smoothly transition between backscatter modulation and passive beamforming, and the proposed practical receiver accommodates the double modulation and signal characteristics in active-passive coexisting networks without \gls{sic}.
+	Simulation results demonstrate RIScatter nodes can exploit the additional propagation paths to smoothly transition between backscatter modulation and passive beamforming, and the proposed practical receiver accommodates the double fading, double modulation, and symbol period difference of active-passive coexisting networks without \gls{sic}.
 \end{abstract}
@@
 		As a mature low-power communication technique, \gls{bc} separates a conventional transmitter into a \gls{rf} carrier emitter with power-hungry elements (e.g., synthesizer and amplifier) and an information-bearing node with power-efficient components (e.g., harvester and modulator) \cite{Boyer2014}.
-		In particular, the node harvests energy from impinging wave and embeds information over scattered signal, while the backscatter reader can be either co-located or separated with the carrier emitter, known as \gls{mbc} in Fig.
-\subref*{fg:mbc} and \gls{bbc} in Fig.
-\subref*{fg:bbc}.
+		In particular, the node harvests energy from impinging wave and embeds information over scattered signal, and the backscatter reader can be either co-located or separated with the carrier emitter, known as \gls{mbc} in Fig.~\subref*{fg:mbc} and \gls{bbc} in Fig.~\subref*{fg:bbc}.
 		Relevant applications such as \gls{rfid} \cite{Dobkin2012,Landt2005} and passive sensor network \cite{Vannucci2008,Assimonis2016} have been extensively researched, standardized, and commercialized in the era of \gls{ioe}.
@@
 		To tackle this, \cite{Liu2013b} proposed \gls{ambc} where battery-free nodes recycle ambient signals (e.g., radio, television and Wi-Fi) to harvest energy and establish connection in between.
-		As shown in Fig.
-\subref*{fg:ambc}, it eliminates the need of dedicated power supply, carrier emitter and frequency spectrum, but backscatter decoding is subject to the strong interference from the primary (legacy) link.
-		Cooperative \gls{ambc} was then proposed where a co-located receiver decodes both active primary and passive backscatter links, where the rate and error performance are evaluated for various detection schemes \cite{Yang2018}.
-		This concept was further refined by \cite{Liang2020} as \gls{sr} in Fig. \subref*{fg:sr} that cognitively incorporates \gls{ambc} with existing systems.
-		In a \gls{sr} system, the active transmitter generates \gls{rf} wave carrying primary information, the passive node provides additional propagation path and ride its information over scattered signal, while the cooperative receiver jointly or sequentially decodes both links.
+		As shown in Fig.~\subref*{fg:ambc}, it eliminates the need of dedicated power supply, carrier emitter and frequency spectrum for \gls{bc}, but the decoding is subject to a strong interference from the primary (legacy) link.
+		Cooperative \gls{ambc} was then proposed where a co-located receiver decodes both active primary and passive backscatter links, and the rate and error performance are evaluated for various detection schemes \cite{Yang2018}.
+		This concept was further refined by \cite{Liang2020} as \gls{sr} in Fig.~\subref*{fg:sr} that cognitively incorporates \gls{ambc} with existing systems.
+		In a \gls{sr} system, the active transmitter generates \gls{rf} wave carrying primary information, the passive node creates additional propagation path and ride its information over scattered signal, while the cooperative receiver jointly, individually or sequentially decodes both links.
 		Those \gls{bc} applications employ scatter nodes as pure information sources, and the active primary transmission (if it exists) can be influenced by the randomness of backscatter modulation.
-		On the other hand, \gls{ris} in Fig.
-\ref{fg:ris} is a smart planar signal reflector that consists of numerous compact passive elements with adjustable amplitude and phase responses, whose reflection pattern over time is deterministic and optimized based on \gls{csi}.
+		On the other hand, \gls{ris} in Fig.~\ref{fg:ris} is a smart planar signal reflector that consists of numerous compact passive elements with adjustable amplitude and phase responses, whose reflection pattern over time is deterministic and optimized based on \gls{csi}.
 		\gls{ris} smartly reflects the surrounding \gls{rf} waves to customize the wireless propagation environment for signal enhancement, interference suppression, scattering enrichment and non-line-of-sight bypassing \cite{Wu2021b}.
@@
 		% In \gls{sr}, the co-located receiver needs to know the \gls{csi} of both links for cooperative decoding, and the primary transmitter may know
-		In \gls{sr}, relevant \gls{csi} is exploited at the co-located receiver for cooperative decoding, and may also be exploited at the primary transmitter for cooperative active beamforming.
-		A comparison of those scattering applications is summarized in Table \ref{tb:scattering_applications}.
+		In \gls{sr}, relevant \gls{csi} is exploited at the co-located receiver for cooperative decoding, which may also be exploited at the primary transmitter for cooperative active beamforming.
+		A comparison of scattering applications is summarized in Table~\ref{tb:scattering_applications}.
 
@@
 		\rowcolors{2}{gray!25}{white}
-		\renewcommand{\arraystretch}{1.5}
+		\renewcommand{\arraystretch}{1.4}
 		\begin{tabularx}{\textwidth}{CCCCCC}
@@
 			Backscatter impact on primary detection          & ---                 & Interference       & Channel uncertainty                           & Passive beamforming & Dynamic passive beamforming                                             \\
-			Cooperation devices                                     & ---                 & No                 & Co-located receiver (and primary transmitter) & ---                 & Primary transmitter, scatter nodes, and co-located receiver             \\
+			Cooperative devices                              & ---                 & No                 & Primary transmitter and co-located receiver   & ---                 & Primary transmitter, scatter nodes, and co-located receiver             \\
 			Cooperative decoding strategy                    & ---                 & No                 & Usually \gls{sic} from primary to backscatter & ---                 & No \gls{sic}, backscatter detection as part of primary channel training \\
@@
 			Reflection pattern over time depends on          & Information source  & Information source & Information source                            & \gls{csi}           & Information source, \gls{csi}, and \gls{qos}                            \\
-			Reflection state (i.e., backscatter input) distribution & Equiprobable        & Equiprobable       & Equiprobable or Gaussian                      & Degenerate          & Flexible                                                                \\
-			Load-switching speed                                    & Fast                & Fast or slow       & Very slow                                     & Quasi-static        & Flexible                                                                \\ \bottomrule
+			Reflection state (i.e., node input) distribution & Equiprobable        & Equiprobable       & Equiprobable or Gaussian                      & Degenerate          & Flexible                                                                \\
+			Load-switching speed                             & Fast                & Fast or slow       & Very slow                                     & Quasi-static        & Arbitrary                                                               \\ \bottomrule
 		\end{tabularx}
@@
 	\begin{subsection}{Related Works}
-		Similar to \gls{cr}, the coexistence of primary and backscatter links in \gls{sr} can be classified into commensal, parasitic, and competitive relationships, whose instantaneous rates, power schemes, and outage probabilities were acquired in \cite{Guo2019b,Ding2020}.
+		Similar to \gls{cr}, active-passive coexisting networks can be classified into commensal, parasitic, and competitive relationships, whose instantaneous rates, power schemes, and outage probabilities were acquired in \cite{Guo2019b,Ding2020}.
 		% To evaluate the performance of cooperative receivers, \cite{Yang2018} derived the bit error rates of \gls{ml}, linear and \gls{sic} detectors for flat fading channels, and proposed a low-complexity detector for frequency-selective fading channels.
 		% However, it only considered the case where the primary and backscatter symbols of the same period are perfectly aligned in time.
-		Joint \gls{ml} decoding provides the best error performance for \gls{sr} but requires prohibitive computational complexity especially for high-order modulations \cite{Yang2018}.
-		One special property of those active-passive coexisting networks is that the backscatter signal strength can be relatively weak due to the double fading effect.
-		It motivated \cite{Long2020a,Liang2020,Guo2019b,Ding2020,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Yang2018,Han2021,Zhang2022} to view \gls{sr} as a multiplicative \gls{noma} and perform \gls{sic} from primary to backscatter link.
-		During primary decoding, the backscatter randomness can be modelled as either interference or channel uncertainty, depending on the ratio $N$ of primary sampling rate over backscatter load-switching speed\footnote{For state-of-the-art low-power \gls{rfid} tags, the load-switching speed usually varies between \num{100}s of \unit{\kHz} to \num{10}s of \unit{\MHz} \cite{Torres2021}, corresponding to a typical $N$ between \num{10} and \num{1000}.}.
-		Such a sequential \gls{sic} involves $N$ re-encoding, precoding, subtraction together with a time-domain \gls{mrc} to decode each backscatter symbol, which can be operation-intensive and \gls{csi}-sensitive.
-		When $N$ is sufficiently large (i.e., commensal \gls{sr}), the average primary achievable rate under noncoherent detection asymptotically approaches its coherent counterpart, and both links may be decoded in an interference-free manner \cite{Long2020a}.
-		Another open issue for \gls{bc} is the efficient backscatter multiple access design.
+		Joint \gls{ml} decoding provides the best error performance but requires prohibitive computational complexity especially for high-order modulations \cite{Yang2018}.
+		Indeed, active-passive coexisting networks have three special and important properties:
+		% 1) there exists a \emph{double modulation} where primary and backscatter symbols are superimposed by multiplication coding;
+		1) primary and backscatter symbols are superimposed by \emph{double modulation} (i.e., multiplication coding);
+		2) backscatter \emph{signal strength} is much weaker than primary because of the double fading effect;
+		3) backscatter \emph{symbol period} is longer than primary because of the load switching constraint.
+		% ! double modulation, double fading, symbol period difference
+		The last two motivated \cite{Long2020a,Liang2020,Guo2019b,Ding2020,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Yang2018,Han2021,Zhang2022} to view \gls{sr} as a multiplicative \gls{noma} and perform \gls{sic} from primary to backscatter link.
+		% During primary decoding, the randomness of backscatter modulation can be modelled as either interference or channel uncertainty, depending on the backscatter-over-primary symbol period ratio $N$\footnote{For state-of-the-art low-power \gls{rfid} tags, the load-switching speed usually varies between \num{100}s of \unit{\kHz} to \num{10}s of \unit{\MHz} \cite{Torres2021}, corresponding to a typical $N$ between \num{10} and \num{1000}.}.
+		During primary decoding, the randomness of backscatter modulation can be modelled as channel uncertainty (resp.
+multiplicative interference) when the backscatter-over-primary symbol period ratio $N$ is large (resp.
+small)\footnote{For state-of-the-art low-power \gls{rfid} tags, the load-switching speed usually varies between \num{100}s of \unit{\kHz} to \num{10}s of \unit{\MHz} \cite{Torres2021}, corresponding to a typical $N$ between \num{10} and \num{1000}.}.
+		% , depending on the backscatter-over-primary symbol period ratio $N$\footnote{For state-of-the-art low-power \gls{rfid} tags, the load-switching speed usually varies between \num{100}s of \unit{\kHz} to \num{10}s of \unit{\MHz} \cite{Torres2021}, corresponding to a typical $N$ between \num{10} and \num{1000}.}.
+		Such a \gls{sic} receiver is operation-intensive and \gls{csi}-sensitive, since it involves $N$ re-encoding, precoding, subtraction together with a time-domain \gls{mrc} to decode each backscatter symbol.
+		When $N$ is sufficiently large (i.e., commensal \gls{sr}), the average primary achievable rate under semi-coherent detection\footnote{In this paper, semi-coherent detection refers to the primary/backscatter decoding based on known \gls{csi} and unknown backscatter/primary symbols.} asymptotically approaches its coherent counterpart, and both links may be decoded in an interference-free manner \cite{Long2020a}.
+		On the other hand, efficient backscatter multiple access design remains an open issue for \gls{bc}.
 		\cite{Xu2021a} proposed a \gls{noma}-based \gls{sr} where the \gls{sic} order depends on the backscatter channel strength, but the performance deteriorates fast as the number of nodes increases.
-		\gls{tdma}-based \gls{sr} was also considered in \cite{Yang2021a} where each node transmits information during its dedicated slot and harvests energy during others.
-		It enables adaptive transmission time and reflection ratio optimization but incurs high coordination cost.
+		\gls{tdma}-based \gls{sr} was also considered in \cite{Yang2021a} where each node transmits information during its dedicated slot and harvests energy otherwise.
+		It enables adaptive transmission time and reflection ratio design but introduces extra coordination cost.
 		\cite{Vougioukas2019} modifies the load-switching speed to shift the scattered signal to the desired frequency band.
-		This enables backscatter \gls{fdma} at the cost of extra bandwidth and higher node power consumption.
+		This enables backscatter \gls{fdma} at the cost of larger bandwidth and higher node power consumption.
 		To reduce coordination burden for passive nodes, \cite{Han2021} proposed a random code-assisted multiple access for \gls{sr} and evaluated the asymptotic \gls{sinr} using random matrix theory.
-		This code-domain solution suffers from the near-far problem and imperfect synchronization, both can be very severe in low-power backscatter scenarios.
+		This code-domain solution suffers from the near-far problem and imperfect synchronization, both being severe in low-power backscatter scenarios.
 
 		Conventional \gls{ris} design with fixed reflection coefficients during each channel block has been extensively studied in communication, sensing, and power literatures \cite{Wu2018,Zhang2019a,Lin2022,Liu2022,Feng2022,Zhao2022}.
-		On the other hand, dynamic \gls{ris} with independent reflection patterns at different time slots has gained recent attentions in multi-user and multi-purpose wireless networks.
+		On the other hand, dynamic \gls{ris} with independent reflection patterns in different time slots has gained recent attentions in multi-user and multi-purpose wireless networks.
 		The concept was first proposed in \cite{Yang2020} to fine-tune the \gls{ofdm} resource blocks, then extended to the downlink power and uplink information phases of \gls{wpcn} \cite{Wu2021,Wu2021d,Hua2022a}.
-		It introduces artificial channel diversity and enables flexible resource allocation, but misses the opportunity to encode message at the \gls{ris}.
+		It introduces artificial channel diversity and enables flexible resource allocation, but misses the opportunity to encode its own message.
 		\gls{ris} can also be used as a transmitter when placed in the near field of a carrier emitter, and prototypes for \gls{psk} and \gls{qam} have been implemented in \cite{Tang2019a,Dai2020a}.
 		From an information-theoretic perspective, \cite{Karasik2020} reported that using \gls{ris} as a naive passive beamformer to maximize the receive \gls{snr} is generally rate-suboptimal for finite input constellations.
-		Instead, the capacity of \gls{ris}-aided channel is achieved by joint transmitter-\gls{ris} encoding, and multiplication coding with \gls{sic} decoding (i.e., \gls{sic}-based \gls{sr}) can indeed outperform passive beamforming at high \gls{snr}.
+		Instead, the capacity of \gls{ris}-aided channel is achieved by joint transmitter-\gls{ris} encoding, and \gls{sic}-based \gls{sr} can outperform passive beamforming at high \gls{snr}.
 		It inspired \gls{ris}-empowered \gls{bc} \cite{Liu2019d,Bereyhi2020,Xu2020b,Zhang2021d,Hu2021b,Hua2022,Basar2020,Ma2020a,Yuan2021,Hu2021a} to combine passive beamforming and backscatter modulation in the overall reflection pattern.
@@
 		However, those joint designs incur advanced hardware architecture and high optimization complexity.
-		Relevant \gls{bc} literatures also consider either \emph{Gaussian} codebook \cite{Guo2019b,Ding2020,Long2020a,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Hu2021b} that is impractical for low-power nodes, or finite equiprobable inputs \cite{Yang2018,Liang2020,Han2021,Zhang2022,Liu2019d,Bereyhi2020,Xu2020b,Zhang2021d,Hua2022,Basar2020,Ma2020a,Yuan2021,Hu2021a} that does not fully exploit \gls{csi} and signal characteristics.
-		For active-passive coexisting networks, it has been observed that:
-		1) \gls{rf} waves on the air can be effectively recycled by smart scattering;
-		% 2) transmitter-scatter-receiver paths can be used to simultaneously control wireless channels and establish passive connections;
-		2) transmitter-scatter-receiver paths can be exploited simultaneously for backscatter modulation and passive beamforming;
-		3) co-located primary and backscatter receiver enables interference cancellation and cooperative decoding;
-		4) the primary and backscatter symbols are superimposed by multiplication (i.e., double modulation).
+		Relevant literatures also consider either \emph{Gaussian} codebook \cite{Guo2019b,Ding2020,Long2020a,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Hu2021b} that is impractical for low-power nodes, or finite \emph{equiprobable} inputs \cite{Yang2018,Liang2020,Han2021,Zhang2022,Liu2019d,Bereyhi2020,Xu2020b,Zhang2021d,Hua2022,Basar2020,Ma2020a,Yuan2021,Hu2021a} that does not fully exploit \gls{csi} and signal properties.
+		% For active-passive coexisting networks, it has been observed that:
+		% 1) the transmitter-scatter-receiver path can be exploited to adjust wireless channel and establish passive connection;
+		% 2) co-located receiver enables interference cancellation and cooperative decoding;
+		% 3) the primary and backscatter symbols are superimposed by multiplication (i.e., double modulation).
 	\end{subsection}
@@
 	\begin{subsection}{Contributions}
-		% The concept of RIScatter is illustrated in Fig. \subref*{fg:riscatter} and the contributions of this paper are summarized below.
-		% As presented in Fig. \subref*{fg:riscatter}, we envision RIScatter as a novel scatter protocol that generalizes \gls{bc} and \gls{ris}.
-		% We envision RIScatter in Fig. \subref*{fg:riscatter} as a novel scatter protocol that generalizes \gls{bc} and \gls{ris}.
+		% The concept of RIScatter is illustrated in Fig.~\subref*{fg:riscatter} and the contributions of this paper are summarized below.
+		% As presented in Fig.~\subref*{fg:riscatter}, we envision RIScatter as a novel scatter protocol that generalizes \gls{bc} and \gls{ris}.
+		% We envision RIScatter in Fig.~\subref*{fg:riscatter} as a novel scatter protocol that generalizes \gls{bc} and \gls{ris}.
 		% The contributions of this paper are summarized below.
@@
 		% \emph{First,} we propose RIScatter as a novel scatter protocol that unifies \gls{bc} and \gls{ris} from a distribution perspective.
-		% As shown in Fig. \subref*{fg:riscatter}, the passive RIScatter node rides over an active transmission and controls the scattered wave to
+		% As shown in Fig.~\subref*{fg:riscatter}, the passive RIScatter node rides over an active transmission and controls the scattered wave to
 		% partially engineer the wireless channel and partially modulate its own information.
@@
 		\emph{First,} we propose RIScatter as a novel scatter protocol that unifies \gls{bc} and \gls{ris} from a distribution perspective.
-		As shown in Fig.
-\subref*{fg:riscatter}, the passive RIScatter node rides over an active transmission and controls the scattered wave to simultaneously engineer the wireless channel and modulate its own information, while a co-located receiver decodes both primary and backscatter links in a cooperative manner.
+		As shown in Fig.~\subref*{fg:riscatter}, the passive RIScatter node rides over an active transmission and controls the scattered wave to simultaneously engineer the wireless channel and modulate its own information, while a co-located receiver decodes both primary and backscatter links in a cooperative manner.
 		The reflection pattern of each RIScatter node is no longer fully random like \gls{bc} or fully deterministic like \gls{ris}, but can be semi-randomly chosen with the guidance of adaptive input state distribution, whose design incorporates the impact of information source, \gls{csi}, and \gls{qos} of both coexisting links.
@@
 
-		\emph{Second,} we address the first challenge by proposing a practical receiver that effectively accommodates the double modulation and signal characteristics of RIScatter without \gls{sic}.
+		\emph{Second,} we address the first challenge by proposing a practical receiver that effectively accommodates the signal properties of active-passive coexisting networks without \gls{sic}.
 		In active-passive coexisting networks, since the primary and backscatter messages are superimposed by multiplication and the backscatter symbol can be much longer than primary, the scattered signals from RIScatter nodes can be treated as (potentially random) multipath components during primary decoding, and the primary symbols can be viewed as a (potentially random) spreading code during backscatter decoding.
@@
 		It can be implemented by adding an integrated receiver \cite{Kim2021a} and adaptive encoder \cite{He2020e} to off-the-shelf passive backscatter tags.
-		The block diagram, equivalent circuit, and scatter model of a RIScatter node are illustrated in Fig.
-\ref{fg:riscatter_node}, while the input distribution and time structure comparison of scattering applications are shown in Fig.
-\ref{fg:scatter_comparison}.
+		The block diagram, equivalent circuit, and scatter model of a RIScatter node are illustrated in Fig.~\ref{fg:riscatter_node}, while the input distribution and time structure comparison of scattering applications are shown in Fig.~\ref{fg:scatter_comparison}.
 		\begin{figure*}[!t]
@@
 
-		Next, we propose a cooperative receiver that effectively exploit signal characteristics (i.e., double modulation and symbol period difference) to reduce the decoding complexity and improve the primary-backscatter tradeoff.
-		As illustrated in Fig.
-\ref{fg:energy_distribution}, conditioned on different reflection state hypotheses, the accumulated receive energy per backscatter block follows Gamma distribution with different scale parameters \cite{Qian2017b}.
+		Next, we propose a cooperative receiver that effectively exploit the signal properties to reduce the decoding complexity and improve the primary-backscatter tradeoff.
+		As illustrated in Fig.~\ref{fg:energy_distribution}, conditioned on different reflection state hypotheses, the accumulated receive energy per backscatter block follows Gamma distribution with different scale parameters \cite{Qian2017b}.
 		\begin{figure}[!t]
@@
 		\end{figure}
-		As shown in Fig.
-\ref{fg:riscatter_network}, we consider an active-passive coexisting network where a $Q$-antenna \gls{ap} serves a single-antenna user and $K$ nearby dispersed and/or co-located single-antenna RIScatter nodes each with $M$ available states.
+		As shown in Fig.~\ref{fg:riscatter_network}, we consider an active-passive coexisting network where a $Q$-antenna \gls{ap} serves a single-antenna user and $K$ nearby dispersed and/or co-located single-antenna RIScatter nodes each with $M$ available states.
 		In the primary point-to-point system, the \gls{ap} transmits information to the user over the multipath channel enhanced by RIScatter nodes.
@@
 		where $\mathcal{H}_{m_{\mathcal{K}}}$ denotes hypothesis $m_{\mathcal{K}}$.
-		At the receiver, the energy space is divided into disjoint decision regions associated with different hypotheses, as illustrated in Fig. \ref{fg:energy_distribution}.
+		At the receiver, the energy space is divided into disjoint decision regions associated with different hypotheses, as illustrated in Fig.~\ref{fg:energy_distribution}.
 		\begin{remark}
@@
 \begin{section}{Rate-Region Characterization}
-	To characterize the achievable primary-(total-)backscatter rate region for the RIScatter system in Fig.
-\ref{fg:riscatter_network}, we aim to maximize the weighted sum rate with respect to input distribution $\{\boldsymbol{p}_k\}_{k \in \mathcal{K}}$, active beamforming $\boldsymbol{w}$, and decision thresholds $\boldsymbol{t}$ by
+	To characterize the achievable primary-(total-)backscatter rate region for the RIScatter system in Fig.~\ref{fg:riscatter_network}, we aim to maximize the weighted sum rate with respect to input distribution $\{\boldsymbol{p}_k\}_{k \in \mathcal{K}}$, active beamforming $\boldsymbol{w}$, and decision thresholds $\boldsymbol{t}$ by
 	\begin{maxi!}
@@
 		\end{figure}
-		As shown in Fig. \ref{fg:discrete_outputs}, by introducing the extra analog-to-digital conversion, we can group adjacent high-resolution energy bins to construct backscatter decision regions.
+		As shown in Fig.~\ref{fg:discrete_outputs}, by introducing the extra analog-to-digital conversion, we can group adjacent high-resolution energy bins to construct backscatter decision regions.
 		Thus, problem \eqref{op:decision_threshold} can be recast as
@@
 \begin{section}{Simulation Results}
-	In this section, we provide numerical results to evaluate the proposed input distribution, active beamforming, and backscatter decision designs for the RIScatter system in Fig.
-\ref{fg:riscatter_network}.
+	In this section, we provide numerical results to evaluate the proposed input distribution, active beamforming, and backscatter decision designs for the RIScatter system in Fig.~\ref{fg:riscatter_network}.
 	We assume the AP-user distance is \qty{10}{\meter} and at least one RIScatter nodes are randomly dropped in a disk centered at the user with radius $r$.
@@
 
-			In Fig. \ref{fg:wsr_convergence}, we plot the weighted sum of primary and total backscatter rates at $\rho=0$ for \gls{kkt}, \gls{pgd} and \gls{bcd} algorithms on the first call.
+			In Fig.~\ref{fg:wsr_convergence}, we plot the weighted sum of primary and total backscatter rates at $\rho=0$ for \gls{kkt}, \gls{pgd} and \gls{bcd} algorithms on the first call.
 			For $K=8$ and $M=2$, Algorithm \ref{al:input_distribution} typically takes around \num{100} fast iterations by \eqref{eq:input_kkt_solution} to converge to the \gls{kkt} input distribution.
@@
 	\begin{subsection}{Comparison of Scattering Applications}
-		On top of the setup in Fig. \ref{fg:riscatter_network}, we consider RIScatter and the following benchmark applications:
+		On top of the setup in Fig.~\ref{fg:riscatter_network}, we consider RIScatter and the following benchmark applications:
 		\begin{itemize}
@@
 
-		Fig. \ref{fg:region_comparison} compares the typical achievable rate region/points of RIScatter and those applications.
+		Fig.~\ref{fg:region_comparison} compares the typical achievable rate region/points of RIScatter and those applications.
 		\emph{First,} we observe both \gls{bbc} and \gls{sr} almost ensure noise-free backscatter transmission when $N$ is sufficiently large.
@@
 		The objective of this study is to demonstrate RIScatter nodes can leverage \gls{csi}- and \gls{qos}-adaptive input distribution design to balance backscatter modulation and passive beamforming.
-		For one RIScatter node with $M=4$, we evaluate the \gls{kkt} input distribution\footnote{Since problem \eqref{op:input_distribution} is convex when $K=1$, the \gls{kkt} solution is also global optimal in this example.} at different primary \gls{qos} and present the result in Fig.
-\ref{fg:distribution_weights}.
+		For one RIScatter node with $M=4$, we evaluate the \gls{kkt} input distribution\footnote{Since problem \eqref{op:input_distribution} is convex when $K=1$, the \gls{kkt} solution is also global optimal in this example.} at different primary \gls{qos} and present the result in Fig.~\ref{fg:distribution_weights}.
 		At $\rho=0$ where backscatter performance is prioritized, the optimal input distribution is zero on two states and nearly uniform on the other two.
-		This is because, due to the weak scattered signal, the conditional energy \gls{pdf} under different hypotheses can be closely spaced as illustrated in Fig. \ref{fg:energy_distribution}.
+		This is because, due to the weak scattered signal, the conditional energy \gls{pdf} under different hypotheses can be closely spaced as illustrated in Fig.~\ref{fg:energy_distribution}.
 		In such cases, the extreme states producing the lowest/highest energy are always assigned with non-zero probability, while the middle ones may not provide enough energy difference and end up unused.
@@
 
-			Fig. \subref*{fg:region_distribution} shows the average achievable rate regions for those designs.
+			Fig.~\subref*{fg:region_distribution} shows the average achievable rate regions for those designs.
 			\emph{Cooperation} provides the rate region outer bound since joint encoding is generally beneficial for co-located RIScatter nodes.
@@
 
-			Fig. \subref*{fg:region_beamforming} presents the average achievable rate regions for those schemes.
+			Fig.~\subref*{fg:region_beamforming} presents the average achievable rate regions for those schemes.
 			In the low-$\rho$ regime, the proposed \emph{\gls{pgd}} beamformer significantly outperforms both \gls{mrt} schemes in terms of total backscatter rate.
@@
 
-			Fig. \subref*{fg:region_threshold} reveals the average achievable rate region for those strategies.
+			Fig.~\subref*{fg:region_threshold} reveals the average achievable rate region for those strategies.
 			The distribution-adaptive schemes \emph{\gls{dp}}, \emph{\gls{smawk}} and \emph{Bisection} ensure higher total backscatter rate than the non-adaptive \emph{\gls{ml}}.
@@
 		\begin{subsubsection}{Number of Nodes}
-			Fig. \subref*{fg:region_tags} reveals how the number RIScatter nodes $K$ influence the primary-backscatter tradeoff.
+			Fig.~\subref*{fg:region_tags} reveals how the number RIScatter nodes $K$ influence the primary-backscatter tradeoff.
 			Interestingly, we observe that increasing $K$ has a larger benefit on the total backscatter rate than primary.
@@
 		\begin{subsubsection}{Number of States}
-			Fig. \subref*{fg:region_states} shows the relationship between available reflection states (i.e., \gls{qam} order) $M$ and achievable rate regions.
+			Fig.~\subref*{fg:region_states} shows the relationship between available reflection states (i.e., \gls{qam} order) $M$ and achievable rate regions.
 			We notice increasing the reflection states has a marginal effect on both primary and total backscatter rates.
@@
 		\begin{subsubsection}{Number of Transmit Antennas}
-			Fig. \subref*{fg:region_txs} illustrates the impact of transmit antennas $Q$ on the average performance.
+			Fig.~\subref*{fg:region_txs} illustrates the impact of transmit antennas $Q$ on the average performance.
 			Increasing $Q$ enlarges the achievable rate region because \gls{pgd} provides a flexible tradeoff between primary equivalent \gls{snr} and backscatter energy difference.
@@
 		\begin{subsubsection}{Symbol Period Ratio}
-			Fig. \subref*{fg:region_duration} presents how symbol period ratio $N$ affects the achievable rate region.
+			Fig.~\subref*{fg:region_duration} presents how symbol period ratio $N$ affects the achievable rate region.
 			As mentioned above, the conventional \gls{sr} scheme with a large $N$ is generally inefficient while RIScatter with a small $N$ can effectively boost the backscatter throughput per unit time.
@@
 		\begin{subsubsection}{Average Noise Power}
-			Fig. \subref*{fg:region_noise} depicts the impact of average noise power $\sigma_v^2$ on average rate regions.
+			Fig.~\subref*{fg:region_noise} depicts the impact of average noise power $\sigma_v^2$ on average rate regions.
 			It shows the proposed practical semi-coherent backscatter energy detection is suitable for a wide range of noise levels.
@@
 		\begin{subsubsection}{Coverage Disk Radius}
-			Fig. \subref*{fg:region_coverage} shows the relationship between disk radius $r$ and achievable rate region.
+			Fig.~\subref*{fg:region_coverage} shows the relationship between disk radius $r$ and achievable rate region.
 			We observe both primary and backscatter performance are enhanced when nodes are dropped closer to the user.

### 2022-12-09 main.tex
:construction: Contribution 1 and 2

@@
 	This contrasts with \gls{bc} (resp. \gls{ris}) where the reflection pattern is exclusively a function of the information symbol (resp. \gls{csi}).
-	The key principle in RIScatter is to render the probability distribution of reflection states as a joint function of the information source, \gls{csi}, and \gls{qos} of the coexisting active primary and passive backscatter links.
+	The key principle in RIScatter is to render the probability distribution of reflection states (i.e., backscatter channel input) as a joint function of the information source, \gls{csi}, and \gls{qos} of the coexisting active primary and passive backscatter links.
 	This enables RISscatter to softly bridge, generalize, and outperform \gls{bc} and \gls{ris}; boil down to either under specific input distribution; or evolve in a mixed form for heterogeneous traffic control and universal hardware design.
 	For a single-user multi-node RIScatter network, we characterize the achievable primary-(total-)backscatter rate region by optimizing the input distribution at the nodes, the active beamforming at the \gls{ap}, and the backscatter detection regions at the user.
-	% Simulation results demonstrate RIScatter nodes can exploit the additional propagation paths to smoothly transition between backscatter modulation and passive beamforming via smart input distribution design, and the proposed practical receiver effectively accommodates the double modulation and signal characteristics in active-passive coexisting networks without \gls{sic}.
 	Simulation results demonstrate RIScatter nodes can exploit the additional propagation paths to smoothly transition between backscatter modulation and passive beamforming, and the proposed practical receiver accommodates the double fading, double modulation, and symbol period difference of active-passive coexisting networks without \gls{sic}.
@@
 		Cooperative \gls{ambc} was then proposed where a co-located receiver decodes both active primary and passive backscatter links, and the rate and error performance are evaluated for various detection schemes \cite{Yang2018}.
-		This concept was further refined by \cite{Liang2020} as \gls{sr} in Fig.~\subref*{fg:sr} that cognitively incorporates \gls{ambc} with existing systems.
-		In a \gls{sr} system, the active transmitter generates \gls{rf} wave carrying primary information, the passive node creates additional propagation path and ride its information over scattered signal, while the cooperative receiver jointly, individually or sequentially decodes both links.
+		The concept was further refined by \cite{Liang2020} as \gls{sr} in Fig.~\subref*{fg:sr} that cognitively incorporates \gls{ambc} with existing systems.
+		In a \gls{sr} system, the active transmitter generates \gls{rf} wave carrying primary information, the passive node creates additional propagation path and ride its information over scattered signal, while the cooperative receiver jointly, individually, or sequentially decodes both links.
 		Those \gls{bc} applications employ scatter nodes as pure information sources, and the active primary transmission (if it exists) can be influenced by the randomness of backscatter modulation.
-		On the other hand, \gls{ris} in Fig.~\ref{fg:ris} is a smart planar signal reflector that consists of numerous compact passive elements with adjustable amplitude and phase responses, whose reflection pattern over time is deterministic and optimized based on \gls{csi}.
+		On the other hand, \gls{ris} in Fig.~\ref{fg:ris} is a smart planar signal reflector that consists of numerous compact passive elements with adjustable amplitude and phase responses, whose reflection pattern over time is deterministic and adaptively optimized based on \gls{csi}.
 		\gls{ris} smartly reflects the surrounding \gls{rf} waves to customize the wireless propagation environment for signal enhancement, interference suppression, scattering enrichment and non-line-of-sight bypassing \cite{Wu2021b}.
@@
 modulated signal).
-		% On the other hand, \gls{ambc} and \gls{sr} involve \emph{coexisting} active primary and passive backscatter links with different relationships in between.
 		On the other hand, \gls{ambc} (resp. \gls{sr}) involves \emph{coexisting} active primary and passive backscatter links in a competitive (resp. collaborative) relationship.
-		In \gls{ambc}, the backscatter link only needs to know the basic information (e.g., operating frequency and input distribution) of the primary link, and the primary link does not need to know the existence of the backscatter link.
-		% In \gls{sr}, relevant \gls{csi} of both links should be available at the co-located receiver for cooperative decoding
-		% In \gls{sr}, the co-located receiver needs to know the \gls{csi} of both links for cooperative decoding, and the primary transmitter may know
-		In \gls{sr}, relevant \gls{csi} is exploited at the co-located receiver for cooperative decoding, which may also be exploited at the primary transmitter for cooperative active beamforming.
+		In \gls{ambc}, the backscatter link only needs to know the basic information (e.g., operating frequency and input distribution) of the primary link, while the primary link does not need to know the existence of the backscatter link.
+		In \gls{sr}, relevant \gls{csi} is exploited at the co-located receiver for cooperative decoding, and may also be exploited at the primary transmitter for cooperative active beamforming.
 		A comparison of scattering applications is summarized in Table~\ref{tb:scattering_applications}.
@@
 	\end{subsection}
-
-	% \begin{table*}[!t]
-	% 	\caption{Comparison of Scattering Applications}
-	% 	\label{tb:scattering_applications}
-	% 	\rowcolors{2}{gray!25}{white}
-	% 	\renewcommand{\arraystretch}{1.5}
-	% 	\begin{tabularx}{\textwidth}{CCCCCC}
-	% 		\toprule
-	% 		\hiderowcolors
-	% 		                                                & \gls{mbc}/\gls{bbc} & \gls{ambc}         & \gls{sr}                                      & \gls{ris}           & RIScatter                                                               \\ \midrule
-	% 		\showrowcolors
-	% 		Coexisting link(s)                              & 1                   & 2 (competitive)    & 2 (collaborative)                             & 1                   & 2 (collaborative)                                                       \\
-	% 		Primary/Backscatter modulation                  & No/Yes              & Yes/Yes            & Yes/Yes                                       & Yes/No              & Yes/Yes                                                                 \\
-	% 		Primary impact on backscatter detection         & Carrier             & Interference       & Spreading code                                & ---                 & Energy uncertainty                                                      \\
-	% 		Backscatter impact on primary detection         & ---                 & Interference       & Channel uncertainty                           & Passive beamforming & Dynamic passive beamforming                                             \\
-	% 		Cooperative transmission(s)                     & ---                 & No                 & Primary transmitter (active beamforming)      & ---                 & Primary transmitter and scatter nodes                                   \\
-	% 		Co-located receiver                             & ---                 & No                 & Usually \gls{sic} from primary to backscatter & ---                 & No \gls{sic}, backscatter detection as part of primary channel training \\
-	% 		Primary detection                               & ---                 & Semi-coherent      & Semi-coherent                                 & Coherent            & Coherent                                                                \\
-	% 		Backscatter detection                           & Coherent            & Semi-coherent      & Coherent                                      & ---                 & Semi-coherent                                                           \\
-	% 		Reflection pattern over time depends on         & Information source  & Information source & Information source                            & \gls{csi}           & Information source, \gls{csi}, and \gls{qos}                            \\
-	% 		Reflection state (i.e.
-node input) distribution & Equiprobable        & Equiprobable       & Equiprobable or Gaussian                      & Degenerate          & Flexible                                                                \\
-	% 		Load-switching speed                            & Fast                & Fast or slow       & Very slow                                     & Quasi-static        & Flexible                                                                \\ \bottomrule
-	% 	\end{tabularx}
-	% \end{table*}
 
@@
 			Primary/Backscatter modulation                                  & No/Yes              & Yes/Yes                     & Yes/Yes                                               & Yes/No              & Yes/Yes                                                                 \\
-			Primary impact on backscatter detection          & Carrier             & Interference       & Spreading code                                & ---                 & Energy uncertainty                                                      \\
-			Backscatter impact on primary detection          & ---                 & Interference       & Channel uncertainty                           & Passive beamforming & Dynamic passive beamforming                                             \\
-			Cooperative devices                              & ---                 & No                 & Primary transmitter and co-located receiver   & ---                 & Primary transmitter, scatter nodes, and co-located receiver             \\
+			Primary impact on backscatter detection                         & Carrier             & Multiplicative interference & Spreading code or multiplicative interference         & ---                 & Energy uncertainty                                                      \\
+			Backscatter impact on primary detection                         & ---                 & Multiplicative interference & \gls{csi} uncertainty or multiplicative interference  & Passive beamforming & Dynamic passive beamforming                                             \\
+			Collaborative devices based on \gls{csi}                        & ---                 & ---                         & Co-located receiver (potentially primary transmitter) & ---                 & Primary transmitter, scatter nodes, and co-located receiver             \\
 			Cooperative decoding strategy                                   & ---                 & No                          & Usually \gls{sic} from primary to backscatter         & ---                 & No \gls{sic}, backscatter detection as part of primary channel training \\
@@
 			Reflection pattern over time depends on                         & Information source  & Information source          & Information source                                    & \gls{csi}           & Information source, \gls{csi}, and \gls{qos}                            \\
-			Reflection state (i.e., node input) distribution & Equiprobable        & Equiprobable       & Equiprobable or Gaussian                      & Degenerate          & Flexible                                                                \\
+			Reflection state (i.e., backscatter channel input) distribution & Equiprobable        & Equiprobable                & Equiprobable or Gaussian                              & Degenerate          & Flexible                                                                \\
 			Load-switching speed                                            & Fast                & Fast or slow                & Very slow                                             & Quasi-static        & Arbitrary                                                               \\ \bottomrule
@@
 
-	% ! cooperation:
-	% - ambc: none
-	% - sr: rx (possibly tx)
-	% - riscatter: rx, tx, sx
 	% ! csi, qos and backscatter constellation-aware input distribution + beamforming
@@
 		Indeed, active-passive coexisting networks have three special and important properties:
-		% 1) there exists a \emph{double modulation} where primary and backscatter symbols are superimposed by multiplication coding;
 		1) primary and backscatter symbols are superimposed by \emph{double modulation} (i.e., multiplication coding);
-		2) backscatter \emph{signal strength} is much weaker than primary because of the double fading effect;
-		3) backscatter \emph{symbol period} is longer than primary because of the load switching constraint.
+		2) backscatter signal strength is much weaker than primary due to the \emph{double fading} effect;
+		3) backscatter \emph{symbol period} is longer than primary due to the load switching constraint.
 		% ! double modulation, double fading, symbol period difference
 		The last two motivated \cite{Long2020a,Liang2020,Guo2019b,Ding2020,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Yang2018,Han2021,Zhang2022} to view \gls{sr} as a multiplicative \gls{noma} and perform \gls{sic} from primary to backscatter link.
-		% During primary decoding, the randomness of backscatter modulation can be modelled as either interference or channel uncertainty, depending on the backscatter-over-primary symbol period ratio $N$\footnote{For state-of-the-art low-power \gls{rfid} tags, the load-switching speed usually varies between \num{100}s of \unit{\kHz} to \num{10}s of \unit{\MHz} \cite{Torres2021}, corresponding to a typical $N$ between \num{10} and \num{1000}.}.
 		During primary decoding, the randomness of backscatter modulation can be modelled as channel uncertainty (resp.
@@
 small)\footnote{For state-of-the-art low-power \gls{rfid} tags, the load-switching speed usually varies between \num{100}s of \unit{\kHz} to \num{10}s of \unit{\MHz} \cite{Torres2021}, corresponding to a typical $N$ between \num{10} and \num{1000}.}.
-		% , depending on the backscatter-over-primary symbol period ratio $N$\footnote{For state-of-the-art low-power \gls{rfid} tags, the load-switching speed usually varies between \num{100}s of \unit{\kHz} to \num{10}s of \unit{\MHz} \cite{Torres2021}, corresponding to a typical $N$ between \num{10} and \num{1000}.}.
-		Such a \gls{sic} receiver is operation-intensive and \gls{csi}-sensitive, since it involves $N$ re-encoding, precoding, subtraction together with a time-domain \gls{mrc} to decode each backscatter symbol.
+		Such a \gls{sic} receiver is operation-intensive and \gls{csi}-sensitive, which involves $N$ re-encoding, precoding, subtraction together with a time-domain \gls{mrc} to decode each backscatter symbol.
 		When $N$ is sufficiently large (i.e., commensal \gls{sr}), the average primary achievable rate under semi-coherent detection\footnote{In this paper, semi-coherent detection refers to the primary/backscatter decoding based on known \gls{csi} and unknown backscatter/primary symbols.} asymptotically approaches its coherent counterpart, and both links may be decoded in an interference-free manner \cite{Long2020a}.
@@
 		It introduces artificial channel diversity and enables flexible resource allocation, but misses the opportunity to encode its own message.
-		\gls{ris} can also be used as a transmitter when placed in the near field of a carrier emitter, and prototypes for \gls{psk} and \gls{qam} have been implemented in \cite{Tang2019a,Dai2020a}.
-		From an information-theoretic perspective, \cite{Karasik2020} reported that using \gls{ris} as a naive passive beamformer to maximize the receive \gls{snr} is generally rate-suboptimal for finite input constellations.
+		\gls{ris} can also be used as a transmitter when placed in the near field of a carrier emitter, and prototypes have been implemented for \gls{psk} \cite{Tang2019a} and \gls{qam} \cite{Dai2020a}.
+		From an information-theoretic perspective, \cite{Karasik2020} reported that using \gls{ris} as a naive passive beamformer to maximize the receive \gls{snr} is generally rate-suboptimal for finite-input constellations.
 		Instead, the capacity of \gls{ris}-aided channel is achieved by joint transmitter-\gls{ris} encoding, and \gls{sic}-based \gls{sr} can outperform passive beamforming at high \gls{snr}.
@@
 		However, those joint designs incur advanced hardware architecture and high optimization complexity.
-		Relevant literatures also consider either \emph{Gaussian} codebook \cite{Guo2019b,Ding2020,Long2020a,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Hu2021b} that is impractical for low-power nodes, or finite \emph{equiprobable} inputs \cite{Yang2018,Liang2020,Han2021,Zhang2022,Liu2019d,Bereyhi2020,Xu2020b,Zhang2021d,Hua2022,Basar2020,Ma2020a,Yuan2021,Hu2021a} that does not fully exploit \gls{csi} and signal properties.
+		Relevant literatures also consider either \emph{Gaussian} codebook \cite{Guo2019b,Ding2020,Long2020a,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Hu2021b} that is impractical for low-power nodes, or finite \emph{equiprobable} inputs \cite{Yang2018,Liang2020,Han2021,Zhang2022,Liu2019d,Bereyhi2020,Xu2020b,Zhang2021d,Hua2022,Basar2020,Ma2020a,Yuan2021,Hu2021a} that does not fully exploit the \gls{csi} and signal properties of active-passive coexisting networks.
 		% For active-passive coexisting networks, it has been observed that:
@@
 		% 2) co-located receiver enables interference cancellation and cooperative decoding;
-		% 3) the primary and backscatter symbols are superimposed by multiplication (i.e., double modulation).
 	\end{subsection}
@@
 	\begin{subsection}{Contributions}
-		% The concept of RIScatter is illustrated in Fig.~\subref*{fg:riscatter} and the contributions of this paper are summarized below.
-		% As presented in Fig.~\subref*{fg:riscatter}, we envision RIScatter as a novel scatter protocol that generalizes \gls{bc} and \gls{ris}.
-		% We envision RIScatter in Fig.~\subref*{fg:riscatter} as a novel scatter protocol that generalizes \gls{bc} and \gls{ris}.
-		% The contributions of this paper are summarized below.
-
-		% \emph{First,} we propose RIScatter nodes that adapt the reflection state distribution of passive scatter devices based on \gls{csi} and link weights, in order to flexibly transition between backscatter modulation and passive beamforming.
-		% Scatter node of \gls{bc} and reflect elements of \gls{ris} can be regarded as special cases with uniform and degenerate input distributions, respectively.
-		% On the contrary, adaptive RIScatter encoding boils down to deterministic \gls{ris} when primary link is prioritized, and achieves higher backscatter rate than conventional line coding when backscatter link is prioritized.
-		% Multiple RIScatter nodes can be either co-located to enable joint distribution design for improved total backscatter rate, or dispersed to guarantee uniformly good performance for both links.
-
 		% \emph{First,} we propose RIScatter as a novel scatter protocol that unifies \gls{bc} and \gls{ris} from a distribution perspective.
@@
 
-		\emph{First,} we propose RIScatter as a novel scatter protocol that unifies \gls{bc} and \gls{ris} from a distribution perspective.
-		As shown in Fig.~\subref*{fg:riscatter}, the passive RIScatter node rides over an active transmission and controls the scattered wave to simultaneously engineer the wireless channel and modulate its own information, while a co-located receiver decodes both primary and backscatter links in a cooperative manner.
-		The reflection pattern of each RIScatter node is no longer fully random like \gls{bc} or fully deterministic like \gls{ris}, but can be semi-randomly chosen with the guidance of adaptive input state distribution, whose design incorporates the impact of information source, \gls{csi}, and \gls{qos} of both coexisting links.
-		Such an adaptive backscatter channel coding boils down to the degenerate distribution of \gls{ris} when primary link is prioritized, and outperforms the conventional line coding with equiprobable inputs of \gls{bc} (by accounting the \gls{csi}) when backscatter link is prioritized.
-		Besides, joint encoding over multiple co-located RIScatter nodes can further boost the total backscatter rate.
-		RIScatter enables simultaneous backscatter modulation and dynamic passive beamforming, and can smoothly transition in between under different \gls{qos}.
-		However, such a novel active-passive coexisting system encounters two major challenges, namely the cooperative receiver and input distribution designs.
-		This is the first paper to associate \gls{bc} and \gls{ris} from a distribution perspective.
-
-		\emph{Second,} we address the first challenge by proposing a practical receiver that effectively accommodates the signal properties of active-passive coexisting networks without \gls{sic}.
-		In active-passive coexisting networks, since the primary and backscatter messages are superimposed by multiplication and the backscatter symbol can be much longer than primary, the scattered signals from RIScatter nodes can be treated as (potentially random) multipath components during primary decoding, and the primary symbols can be viewed as a (potentially random) spreading code during backscatter decoding.
-		Both randomness cannot be eliminated simultaneously by sequential decoding.
-		Conventional \gls{sic}-based receiver that decodes from primary to backscatter link requires $N$ re-encoding, precoding, subtraction together with a time-domain \gls{mrc} to decode each backscatter symbol.
-		In contrast, the proposed practical receiver semi-coherently detects backscatter message from the accumulated receive energy, re-encodes to recover exact reflection patterns, and models the deterministic multipath within primary equivalent channel.
-		The semi-coherent backscatter detection is indeed part of primary channel estimation.
-		It preserves simultaneous backscatter modulation and dynamic passive beamforming by only one energy comparison, re-encoding, and precoding per backscatter symbol, and is suitable for arbitrary primary sampling rate and backscatter load-switching speed.
+		\emph{First,} we propose RIScatter as a novel scatter protocol that unifies \gls{bc} and \gls{ris} by adaptive reflection state (i.e., backscatter channel input) distribution design.
+		As shown in Fig.~\subref*{fg:riscatter}, the passive RIScatter node rides over an active transmission and smartly scatters the incident wave to simultaneously engineer the primary channel and modulate its own information, while a co-located receiver cooperatively decodes both coexisting links.
+		The reflection pattern of each RIScatter node is neither fully random like \gls{bc} nor fully deterministic like \gls{ris}, but semi-randomly chosen with the guidance of input state distribution, whose design accommodates the impact of information source, \gls{csi}, and \gls{qos} of both links.
+		Such an adaptive backscatter channel coding boils down to the degenerate distribution of \gls{ris} when the primary link is prioritized, and outperforms the uniform distribution of line-coded \gls{bc} (by accounting the \gls{csi}) when the backscatter link is prioritized.
+		Besides, when multiple RIScatter nodes are co-located, joint encoding can further increase the total backscatter rate.
+		RIScatter exploits the transmitter-scatter-receiver path for simultaneous backscatter modulation and dynamic passive beamforming, and can smoothly transition in between under different \gls{qos}.
+		However, such a novel active-passive coexisting network encounters two major challenges, namely the cooperative receiver design and the adaptive backscatter input distribution design.
+		This is the first paper to associate \gls{bc} and \gls{ris} from the perspective of reflection state distribution.
+
+		\emph{Second,} we address the first challenge by proposing a practical receiver that accommodates the double fading, double modulation, and symbol period difference in active-passive coexisting networks.
+		Since joint decoding involves high complexity and individual decoding is neither cooperative nor exploiting signal properties, most relevant literature consider a sequential \gls{sic}-based primary-backscatter decoding.
+		As such, the decoding of each backscatter symbol requires $N$ re-encoding, precoding, subtraction together with a time-domain \gls{mrc}, which can be operation-intensive and \gls{csi}-sensitive.
+		In contrast, the proposed RIScatter receiver semi-coherently decodes the backscatter symbol from the accumulated receive energy, re-encodes to recover the exact reflection pattern, and combine it with relevant \gls{csi} to determine the transmitter-scatter-receiver path.
+		That is, the semi-coherent energy-based backscatter detection becomes part of primary channel training, such that backscatter modulation and dynamic passive beamforming are simultaneously enabled by only one energy comparison, re-encoding, and precoding per backscatter symbol without \gls{sic}.
+		It is also suitable for arbitrary primary sampling rate and backscatter load-switching speed (i.e., arbitrary $N$).
+		This is the first paper to consider sequential backscatter-primary decoding at the cooperative receiver and view semi-coherent backscatter detection as part of primary channel training.
 
@@
 	$(\cdot)^*$, $(\cdot)^\mathsf{T}$, $(\cdot)^\mathsf{H}$, $\lvert{\cdot}\rvert$, and $\lVert{\cdot}\rVert$ denote the conjugate, transpose, conjugate transpose, absolute value, and Euclidean norm operators, respectively.
-	$(\cdot)^{(r)}$ and $(\cdot)^{\star}$ denote the $r$-th iterated and terminal solutions, respectively.
+	$(\cdot)^{(r)}$ and $(\cdot)^{\star}$ denote the $r$-th iterated and optimal results, respectively.
 	The distribution of a \gls{cscg} random variable with zero mean and variance $\sigma^2$ is denoted by $\mathcal{CN}(0,\sigma^2)$, and $\sim$ means ``distributed as''.

### 2022-12-10 main.tex
:construction: Update manuscript

@@
 			\showrowcolors
-			Coexisting link(s)                                              & 1                   & 2 (competitive)             & 2 (collaborative)                                     & 1                   & 2 (collaborative)                                                       \\
-			Primary/Backscatter modulation                                  & No/Yes              & Yes/Yes                     & Yes/Yes                                               & Yes/No              & Yes/Yes                                                                 \\
+			% Coexisting link(s)                                              & 1                   & 2 (competitive)             & 2 (collaborative)                                     & 1                   & 2 (collaborative)                                                       \\
+			Information link(s)                                     & Passive backscatter only & Active-passive coexisting (competitive) & Active-passive coexisting (collaborative)             & Active primary only & Active-passive coexisting (collaborative)                               \\
+			% Primary/Backscatter modulation                                  & No/Yes              & Yes/Yes                     & Yes/Yes                                               & Yes/No              & Yes/Yes                                                                 \\
 			Primary impact on backscatter detection                 & Carrier                  & Multiplicative interference             & Spreading code or multiplicative interference         & ---                 & Energy uncertainty                                                      \\
@@
 			Reflection pattern over time depends on                 & Information source       & Information source                      & Information source                                    & \gls{csi}           & Information source, \gls{csi}, and \gls{qos}                            \\
-			Reflection state (i.e., backscatter channel input) distribution & Equiprobable        & Equiprobable                & Equiprobable or Gaussian                              & Degenerate          & Flexible                                                                \\
+			Reflection state (i.e., backscatter input) distribution & Equiprobable             & Equiprobable                            & Equiprobable or Gaussian                              & Degenerate          & Flexible                                                                \\
 			Load-switching speed                                    & Fast                     & Fast or slow                            & Very slow                                             & Quasi-static        & Arbitrary                                                               \\ \bottomrule
@@
 	\end{table*}
-
-	% ! csi, qos and backscatter constellation-aware input distribution + beamforming
-	% ! csi and backscatter constellation-aware detection
 
@@
 
-		\emph{First,} we propose RIScatter as a novel scatter protocol that unifies \gls{bc} and \gls{ris} by adaptive reflection state (i.e., backscatter channel input) distribution design.
+		\emph{First,} we propose RIScatter as a novel scatter protocol that unifies \gls{bc} and \gls{ris} by adaptive reflection state (i.e., backscatter input) distribution design.
 		As shown in Fig.~\subref*{fg:riscatter}, the passive RIScatter node rides over an active transmission and smartly scatters the incident wave to simultaneously engineer the primary channel and modulate its own information, while a co-located receiver cooperatively decodes both coexisting links.
-		The reflection pattern of each RIScatter node is neither fully random like \gls{bc} nor fully deterministic like \gls{ris}, but semi-randomly chosen with the guidance of input state distribution, whose design accommodates the impact of information source, \gls{csi}, and \gls{qos} of both links.
+		The reflection pattern of each RIScatter node is neither fully random like \gls{bc} nor fully deterministic like \gls{ris}, but semi-randomly chosen with the guidance of reflection state distribution, whose design accommodates the impact of information source, \gls{csi}, and \gls{qos} of both links.
 		Such an adaptive backscatter channel coding boils down to the degenerate distribution of \gls{ris} when the primary link is prioritized, and outperforms the uniform distribution of line-coded \gls{bc} (by accounting the \gls{csi}) when the backscatter link is prioritized.
@@
 		RIScatter exploits the transmitter-scatter-receiver path for simultaneous backscatter modulation and dynamic passive beamforming, and can smoothly transition in between under different \gls{qos}.
-		However, such a novel active-passive coexisting network encounters two major challenges, namely the cooperative receiver design and the adaptive backscatter input distribution design.
+		However, such a novel scatter protocol encounters two major challenges, namely the cooperative receiver design and the adaptive backscatter input distribution design.
 		This is the first paper to associate \gls{bc} and \gls{ris} from the perspective of reflection state distribution.
 
-		\emph{Second,} we address the first challenge by proposing a practical receiver that accommodates the double fading, double modulation, and symbol period difference in active-passive coexisting networks.
-		Since joint decoding involves high complexity and individual decoding is neither cooperative nor exploiting signal properties, most relevant literature consider a sequential \gls{sic}-based primary-backscatter decoding.
-		As such, the decoding of each backscatter symbol requires $N$ re-encoding, precoding, subtraction together with a time-domain \gls{mrc}, which can be operation-intensive and \gls{csi}-sensitive.
-		In contrast, the proposed RIScatter receiver semi-coherently decodes the backscatter symbol from the accumulated receive energy, re-encodes to recover the exact reflection pattern, and combine it with relevant \gls{csi} to determine the transmitter-scatter-receiver path.
-		That is, the semi-coherent energy-based backscatter detection becomes part of primary channel training, such that backscatter modulation and dynamic passive beamforming are simultaneously enabled by only one energy comparison, re-encoding, and precoding per backscatter symbol without \gls{sic}.
-		It is also suitable for arbitrary primary sampling rate and backscatter load-switching speed (i.e., arbitrary $N$).
-		This is the first paper to consider sequential backscatter-primary decoding at the cooperative receiver and view semi-coherent backscatter detection as part of primary channel training.
-
-		\emph{Third,} we address the second challenge by considering a scenario where multiple RIScatter nodes ride over an active point-to-point \gls{miso} transmission to perform backscatter modulation and passive beamforming towards a nearby user using shared spectrum, energy, and infrastructures.
-		We provide primary and total backscatter rate analyses and characterize the achievable rate region by optimizing input distribution at RIScatter nodes, active beamforming at the \gls{ap}, and backscatter decision regions at the user.
-		Since the original problem is highly non-convex, we decouple it into individual subproblems and propose a suboptimal \gls{bcd} algorithm, where the \gls{kkt} input distribution is numerically evaluated by limit of sequences, the active beamforming is iteratively updated by \gls{pgd} accelerated by \gls{bls}, and the decision regions are refined by existing sequential quantization methods for \gls{dmtc}.
-		This is the first paper to reveal the importance of input distribution and decision region designs in relevant literatures.
-
-		\emph{Fourth,} we provide numerical results to demonstrate the benefits of RIScatter and proposed algorithms and make the following conclusions:
+		\emph{Second,} we address the first challenge by proposing a practical receiver that accommodates the double fading, double modulation, and symbol period difference of active-passive coexisting networks.
+		Since joint decoding involves high complexity and individual decoding is very inefficient (neither cooperative nor exploiting signal properties), most relevant literatures consider a sequential primary-backscatter decoding based on \gls{sic}.
+		Specifically, the decoding of each backscatter symbol requires $N$ re-encoding, precoding, subtraction together with a time-domain \gls{mrc}, which can be operation-intensive and \gls{csi}-sensitive.
+		In contrast, the proposed RIScatter receiver semi-coherently decodes the backscatter symbol from the accumulated receive energy, re-encodes to recover the exact reflection pattern, and combine it with relevant \gls{csi} to determine the transmitter-scatter-receiver path response.
+		That is, the semi-coherent energy-based backscatter detection becomes part of primary channel training, enabling simultaneous backscatter modulation and dynamic passive beamforming by only one energy comparison, re-encoding, and precoding per backscatter symbol without \gls{sic}.
+		The strategy is suitable for arbitrary primary sampling rate and backscatter load-switching speed (i.e., arbitrary $N$).
+		This is the first paper to consider such a sequential backscatter-primary decoding and treat semi-coherent backscatter detection as part of primary channel training.
+
+		\emph{Third,} we address the second challenge by considering a specific scenario where multiple co-located/dispersed RIScatter nodes ride over an active point-to-point \gls{miso} transmission to perform backscatter modulation and dynamic passive beamforming towards a nearby user.
+		% We first express the achievable primary and total backscatter rates under given \gls{qos} as functions of active beamforming at the \gls{ap}, input distribution at RIScatter nodes, and backscatter decision regions at the user.
+		We first express the primary and total backscatter rates under given \gls{qos} as functions of \emph{input distribution} at RIScatter nodes, \emph{active beamforming} at the \gls{ap}, and \emph{backscatter decision regions} at the user.
+		Then, we characterize the achievable rate region by optimizing those variables under different \gls{qos}.
+		Since the original problem is highly non-convex, we propose a suboptimal \gls{bcd} algorithm where the \gls{kkt} input distribution is numerically evaluated by limit of sequences, the active beamforming is iteratively updated by \gls{pgd} accelerated by \gls{bls}, and the decision regions are refined by existing sequential quantization methods for \gls{dmtc}.
+		% The proposed backscatter input distribution design can also be generalized to other setups.
+		Uniquely, we account for \gls{csi}, \gls{qos}, and backscatter constellation in those optimizations, and the proposed backscatter input distribution design is applicable to more general scenarios.
+		This is also the first paper to reveal the importance of backscatter input distribution and decision region designs in active-passive coexisting networks.
+
+		\emph{Fourth,} we provide numerical results to demonstrate the benefits of RIScatter and proposed algorithms.
+		The observations include:
 		1) adaptive reflection state distribution design can flexibly transition between backscatter modulation and passive beamforming;
 		2) when primary link is prioritized, input distribution becomes degenerate and RIScatter nodes coincide with discrete \gls{ris};
-		3) when backscatter link is prioritized, adaptive RIScatter encoding achieves higher backscatter rate than conventional line coding with equiprobable inputs;
+		3) when backscatter link is prioritized, adaptive RIScatter encoding achieves higher backscatter rate than conventional line-coded \gls{bc} (with equiprobable inputs);
 		4) co-located RIScatter nodes can further leverage total backscatter rate by joint encoding;
-		5) the proposed receiver provides comparable backscatter detection performance than \gls{sic}-based \gls{sr} while significantly reduces the encoding and precoding (and avoids subtraction) costs;
-		6) it also supports fast-switching nodes for higher backscatter throughput per unit time;
-		7) \gls{pgd} active beamformer enlarges achievable rate region by boosting the receive \gls{snr} and/or widening the energy gap under different reflection states;
-		8) distribution-adaptive backscatter detectors provide higher total backscatter rate than the conventional \gls{ml} detector.
+		5) the proposed receiver maintains the passive beamforming benefit and provides comparable backscatter rate to \gls{sic}-based \gls{sr}, with encoding and precoding costs reduced to $1/N$;
+		6) it also supports scatter nodes with faster load-switching speed for higher throughput;
+		% 7) \gls{pgd} active beamformer enlarges achievable rate region by boosting the receive \gls{snr} and/or widening the energy gap under different reflection states;
+		7) \gls{pgd} active beamformer effectively increases the primary (resp.
+backscatter) rate by boosting the receive \gls{snr} (resp.
+widening the energy gap under different reflection states), and can smoothly transition in between under different \gls{qos};
+		8) distribution-adaptive backscatter detectors provide higher backscatter rate than the conventional \gls{ml} detector.
 	\end{subsection}
@@
 \begin{section}{Scattering Principles}
-	\gls{rf} wave scattering and reflecting are usually realized by a \emph{variable-load antenna} or \emph{programmable metamaterial} and described by a unified signal model \cite{Liang2022}.
+	\gls{rf} wave scattering and reflecting are usually realized by a {variable-load antenna} or {programmable metamaterial} and can be described by a unified signal model \cite{Liang2022}.
 	A typical antenna-based scatterer consists of an integrated antenna, a load-switching modulator, an energy harvester, and on-chip components (e.g., microcontroller and sensors) \cite{Dobkin2012}.
@@
 	% Backscatter modulation and passive beamforming are realized by manipulating the reflection coefficient.
-	\gls{bc} employ scatter nodes as information sources that encode message by \emph{probabilistically switching} between different states.
+	\gls{bc} employ scatter nodes as information sources that \emph{randomly switching} between different states.
 	For $M$-ary \gls{qam}, constellation point $c_m$ maps to reflection coefficient $\Gamma_m$ by \cite{Thomas2012a}
@@
 	\end{equation}
-	where $\alpha \in \mathbb{I}$ is the amplitude scattering ratio at the direction of interest.
-	In contrast, \gls{ris} employ reflect elements as channel reconfigurators that enable constructive/destructive signal superposition by \emph{deterministically choosing} the reflection pattern.
+	where $\alpha \in \mathbb{I}$ is the common amplitude scattering ratio at the direction of interest.
+	In contrast, \gls{ris} employ reflect elements as channel reconfigurators \emph{deterministically choosing} the reflection state based on \gls{csi}.
 	For a \gls{ris} element with $M$ available states, phase shift $\theta_m$ maps to reflection coefficient $\Gamma_m$ by \cite{Wu2018}
@@
 	\end{equation}
-	where $\beta_m \in \mathbb{I}$ is the overall amplitude scattering ratio of state $m$.\footnote{Most existing \gls{ris} literatures assume lossless reflection $\beta_m=1$, $\forall m$.}
+	where $\beta_m \in \mathbb{I}$ is the total amplitude scattering ratio at state $m$.\footnote{Most existing \gls{ris} literatures assume lossless reflection $\beta_m=1$, $\forall m$.}
 \end{section}
@@
 	\begin{subsection}{Concepts}
-		As a generalization of \gls{bc} and \gls{ris}, RIScatter is a passive scatter protocol that coexists with an active primary system in a flexible and mutualistic manner.
-		RIScatter nodes leverage \gls{csi}- and \gls{qos}-based input distribution design to smoothly transition between backscatter modulation and passive beamforming.
-		It can be implemented by adding an integrated receiver \cite{Kim2021a} and adaptive encoder \cite{He2020e} to off-the-shelf passive backscatter tags.
-		The block diagram, equivalent circuit, and scatter model of a RIScatter node are illustrated in Fig.~\ref{fg:riscatter_node}, while the input distribution and time structure comparison of scattering applications are shown in Fig.~\ref{fg:scatter_comparison}.
+		As a generalization of \gls{bc} and \gls{ris}, RIScatter involves coexisting active primary and passive backscatter links in a flexible and mutualistic manner.
+		RIScatter nodes leverage \gls{csi}- and \gls{qos}-based reflection state (i.e., backscatter input) distribution design to smoothly transition between backscatter modulation and passive beamforming.
+		It can be implemented by adding an integrated receiver \cite{Kim2021a} and adaptive encoder \cite{He2020e} to off-the-shelf passive \gls{rfid} tags.
+		The block diagram, equivalent circuit, and scatter model of a RIScatter node are illustrated in Fig.~\ref{fg:riscatter_node}, while the reflection state distribution and reflection pattern of scattering applications are shown in Fig.~\ref{fg:scatter_comparison}.
 		\begin{figure*}[!t]
@@
 			\centering
-			\subfloat[Input Distribution]{
+			\subfloat[Reflection State Distribution]{
 				\resizebox{0.8\columnwidth}{!}{
@@
 			\\
-			\subfloat[Time Structure]{
+			\subfloat[Reflection Pattern]{
 				\resizebox{0.8\columnwidth}{!}{
@@
 			\caption{
-				Input distribution and time structure of \gls{bc}, \gls{ris}, and RIScatter.
+				Reflection state distribution and reflection pattern over time of \gls{bc}, \gls{ris}, and RIScatter.
 				``PB'' means primary block and ``BB'' means backscatter block.
@@
 		\end{figure}
-		Instead of using fully random or fully deterministic reflection pattern over time, each RIScatter node semi-randomly chooses the reflection state for each backscatter block with the guidance of input probability distribution $P(\Gamma_m)$ at state $m$.
-		Such an adaptive backscatter coding boils down to degenerate distribution of \gls{ris} when primary link is prioritized, and outperforms conventional line coding with equiprobable inputs (e.g., FM0 for \gls{rfid}) when backscatter link is prioritized.
-		Besides, joint encoding over multiple co-located RIScatter nodes can further boost the total backscatter rate.
+		Instead of using fully random or fully deterministic reflection pattern over time, each RIScatter node semi-randomly chooses the reflection state for each backscatter block with the guidance of input probability $P(\Gamma_m)$ at state $m$.
+		Such an adaptive backscatter channel coding boils down to degenerate distribution of \gls{ris} when primary link is prioritized, and outperforms conventional line-coded \gls{bc} with equiprobable inputs (e.g., FM0 for \gls{rfid}) when backscatter link is prioritized.
 		Relevant \gls{csi} can be acquired by existing low-power estimation techniques.
-		For dispersed RIScatter nodes, the cascaded transmitter-node-receiver channels can be estimated by sequential \cite{Bharadia2015,Yang2015b,Guo2019g} or parallel approaches \cite{Jin2021a} originally proposed for \gls{bc}.
+		For dispersed RIScatter nodes, the cascaded transmitter-scatter-receiver channels can be estimated by sequential \cite{Bharadia2015,Yang2015b,Guo2019g} or parallel approaches \cite{Jin2021a} originally proposed for \gls{bc}.
 		For co-located RIScatter nodes, the estimation can be simplified by group-based \cite{Zheng2019} and hierarchical \cite{You2019} trainings originally proposed for \gls{ris}.
@@
 		\begin{remark}
-			Scatter-based multiple access involves a double modulation where the primary and backscatter symbols of different length are superimposed by multiplication coding.
-			The reflection pattern not only encodes the backscatter message, but also affects the primary equivalent channel.
-			Therefore, backscatter detection under primary uncertainty can be viewed as part of primary channel training, and novel decoding strategies apart from \gls{sic}
+			Active-passive coexisting networks involve a double modulation where the primary and backscatter symbols of different period are superimposed by multiplication coding.
+			The reflection pattern not only encodes the backscatter message, but also affects the channel for primary link.
+			Therefore, backscatter detection under primary uncertainty can be viewed as part of primary channel training, and novel decoding strategies apart from \gls{sic}%
 			\footnote{
@@
 
-		Next, we propose a cooperative receiver that effectively exploit the signal properties to reduce the decoding complexity and improve the primary-backscatter tradeoff.
+		Next, we propose a cooperative receiver that effectively exploit the double modulation, double fading and symbol period difference to reduce the decoding complexity and improve the primary-backscatter tradeoff.
 		As illustrated in Fig.~\ref{fg:energy_distribution}, conditioned on different reflection state hypotheses, the accumulated receive energy per backscatter block follows Gamma distribution with different scale parameters \cite{Qian2017b}.
@@
 		\end{figure}
-		Hence, the receiver can semi-coherently (in the presence of primary uncertainty) decode node messages from the accumulated receive energy, re-encode to recover actual reflection patterns, and model the deterministic multipath within primary equivalent channel.
+		Hence, the receiver can semi-coherently (in the presence of primary uncertainty) decode node messages from the accumulated receive energy, re-encode to recover actual reflection patterns, and model the deterministic multipath within the primary channel.
 		It enables simultaneous backscatter modulation and dynamic passive beamforming by only one energy comparison, re-encoding, and precoding operations for each backscatter block (instead of primary block), and is suitable for arbitrary primary sampling rate and backscatter load-switching speed.
@@
 		\end{figure}
-		As shown in Fig.~\ref{fg:riscatter_network}, we consider an active-passive coexisting network where a $Q$-antenna \gls{ap} serves a single-antenna user and $K$ nearby dispersed and/or co-located single-antenna RIScatter nodes each with $M$ available states.
+		As shown in Fig.~\ref{fg:riscatter_network}, we consider a RIScatter system where a $Q$-antenna \gls{ap} serves a single-antenna user as well as $K$ nearby dispersed/co-located single-antenna $M$-state RIScatter nodes.
 		In the primary point-to-point system, the \gls{ap} transmits information to the user over the multipath channel enhanced by RIScatter nodes.
-		In the backscatter \gls{mac} system, the \gls{ap} and user become carrier emitter and backscatter reader, and the RIScatter nodes modulate over scattered \gls{rf} signals.
-		For simplicity, we consider a quasi-static block fading model where channels remain constant within each block and vary independently between consecutive blocks, and assume the backscatter-over-primary symbol period ratio $N$ is an integer.
+		In the backscatter \gls{mac} system, the \gls{ap} and user become carrier emitter and backscatter reader, and the RIScatter nodes modulate over the scattered \gls{rf} signals.
+		% For simplicity, we consider a quasi-static block fading model where channels remain constant within each block and vary independently between consecutive blocks, and assume the backscatter-over-primary symbol period ratio $N$ is an integer.
+		For simplicity, we consider a quasi-static block fading model and focus on one specific block where all \gls{csi} remain constant.
+		Let the backscatter-over-primary symbol period ratio $N$ be an positive integer.
 		We also omit the signal reflected by two or more times and ignore the propagation time difference of different paths.
@@
 		where $\boldsymbol{w} \in \mathbb{C}^{Q}$ is the active beamformer satisfying average transmit power constraint $\lVert \boldsymbol{w} \rVert^2 \le P$, $s \sim \mathcal{CN}(0,1)$ is the primary symbol, and $v \sim \mathcal{CN}(0,\sigma_v^2)$ is the \gls{awgn} with average power $\sigma_v^2$.
-		Let $m_k \in \mathcal{M} \triangleq \{1,\ldots,M\}$ be the reflection state index of node $k$, $m_{\mathcal{K}} \triangleq (m_1,\ldots,m_K)$ be the state index tuple of all nodes, $x_{m_k}$ be the backscatter symbol of node $k$ indexed by $m_k$, and $x_{m_\mathcal{K}}$ be the backscatter symbol tuple indexed by $m_{\mathcal{K}}$.\footnote{Please note $x_k$ and $x_{\mathcal{K}}$ are discrete random variable and tuple, while $x_{m_k}$ and $x_{m_{\mathcal{K}}}$ are their values indexed by $m_k$ and $m_{\mathcal{K}}$.}
+		Let $m_k \in \mathcal{M} \triangleq \{1,\ldots,M\}$ be the reflection state index of node $k$ and $m_{\mathcal{K}} \triangleq (m_1,\ldots,m_K)$ be the reflection state index tuple of all nodes.
+		The backscatter symbol $x_k$ (resp.
+symbol tuple $x_{\mathcal{K}}$) is a random variable (resp.
+variable tuple) that takes value $x_{m_k}$ (resp.
+value tuple $x_{m_{\mathcal{K}}}$) when state $m_k$ (resp.
+state tuple $m_{\mathcal{K}}$) is employed.
 		Conditioned on $m_{\mathcal{K}}$, the receive signal at each primary block follows \gls{cscg} distribution $\mathcal{CN}(0,\sigma_{m_{\mathcal{K}}}^2)$, where
@@
 			The capacity-achieving decision region design for \gls{dmtc} with non-binary inputs in arbitrary distribution remains an open issue.
-			It was proved deterministic detector can be rate-optimal, but non-convex decision regions (i.e., comprise non-adjacent partitions) are generally required and the optimal number of thresholds is still unknown \cite{Nguyen2018,Nguyen2021}.
+			It was proved deterministic detector can be rate-optimal, but non-convex decision regions (i.e., comprise non-adjacent partitions) are generally involved and the optimal number of thresholds remains unknown \cite{Nguyen2018,Nguyen2021}.
 			Hence, we limit the backscatter energy detector to convex deterministic decision regions and consider sequential threshold design in the following context.
@@
 	\begin{subsection}{Achievable Rates}
-		Let $P_k(x_{m_k})$ be the input probability of node $k$ at state $m_k$, and $\boldsymbol{p}_k \triangleq [P_k(c_1),\ldots,P_k(c_M)]^\mathsf{T} \in \mathbb{I}^{M}$ be the input distribution vector.
-		% Denote the input probability of node $k$ at state $m_k$ as $P_k(x_{m_k})$, and the input distribution vector as $\boldsymbol{p}_k \triangleq [P_k(c_1),\ldots,P_k(c_M)]^\mathsf{T} \in \mathbb{I}^{M}$.
-		For dispersed nodes with independent encoding, the probability of backscatter symbol tuple $x_{m_{\mathcal{K}}}$ is
+		Denote the probability of node $k$ choosing reflection state $m_k$ as $P_k(x_{m_k})$, and let $\boldsymbol{p}_k \triangleq [P_k(c_1),\ldots,P_k(c_M)]^\mathsf{T} \in \mathbb{I}^{M}$.
+		For dispersed nodes with independent encoding, the probability of backscatter symbol value tuple $x_{m_{\mathcal{K}}}$ is
 		\begin{equation}
@@
 		\end{equation}
-		Following \cite{Rezaeian2004}, we define the backscatter information function between input symbol tuple instance $x_{m_{\mathcal{K}}}$ and output symbol tuple variable $\hat{x}_{\mathcal{K}}$ as
+		Following \cite{Rezaeian2004}, we define the backscatter information function between input value tuple $x_{m_{\mathcal{K}}}$ and output variable tuple $\hat{x}_{\mathcal{K}}$ as
 		\begin{equation}
@@
 		\end{equation}
-		where $P_{\mathcal{K}}(\hat{x}_{m_{\mathcal{K}}'}) = \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}})$ is the probability of output tuple $\hat{x}_{m_{\mathcal{K}}'}$.
-		We also define the backscatter marginal information of letter $x_{m_k}$ as
+		where $P_{\mathcal{K}}(\hat{x}_{m_{\mathcal{K}}'}) = \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}})$ is the probability of output value tuple $\hat{x}_{m_{\mathcal{K}}'}$.
+		We also define the backscatter marginal information of $x_{m_k}$ as
 		\begin{equation}
@@
 
-		Once node messages are successfully decoded, we can re-encode for exact backscatter symbol tuple $x_{\mathcal{K}}$, recover their reflection patterns by \eqref{eq:backscatter_modulation}, and retrieve the primary equivalent channel by \eqref{eq:equivalent_channel}.
-		Therefore, the primary information function conditioned on backscatter symbol tuple $x_{m_{\mathcal{K}}}$ is
+		Once nodes are successfully decoded, we can re-encode for exact $x_{\mathcal{K}}$, recover their reflection patterns by \eqref{eq:backscatter_modulation}, and determine the primary equivalent channel by \eqref{eq:equivalent_channel}.
+		Therefore, the primary information function conditioned on $x_{m_{\mathcal{K}}}$ is
 		\begin{equation}
@@
 		\end{equation}
-		the primary marginal information of letter $x_{m_k}$ is
+		the primary marginal information of $x_{m_k}$ is
 		% the primary marginal information conditioned on letter $x_{m_k}$ of node $k$ as
@@
 		where $\rho \in \mathbb{I}$ is the \gls{qos} of the primary link.
-		We notice the average primary rate \eqref{eq:primary_mutual_information} depends on the input distribution and active beamforming, while the total backscatter rate depends on the input distribution and \gls{dmtmac} \eqref{eq:dmtmac} that relates to active beamforming and decision thresholds.
+		We notice the average primary rate \eqref{eq:primary_mutual_information} depends on the backscatter input distribution and active beamforming, while the total backscatter rate depends on the input distribution and \gls{dmtmac} \eqref{eq:dmtmac} that relates to the active beamforming and decision thresholds.
 		\label{st:information_theory}
@@
 			As $\rho$ increases, the primary equivalent \gls{snr} outweighs the backscatter energy difference in \eqref{eq:weighted_sum_mutual_information_explicit}, and \emph{\gls{pgd}} beamformer becomes closer to both \gls{mrt} schemes.
-			At $\rho=1$, \emph{\gls{pgd}} and \emph{E-\gls{mrt}:} boil down to \gls{mrt} towards the deterministic primary equivalent channel as in \gls{ris} literature \cite{Wu2019}.
+			At $\rho=1$, \emph{\gls{pgd}} and \emph{E-\gls{mrt}:} boil down to \gls{mrt} towards the deterministic primary equivalent channel as in \gls{ris} literatures \cite{Wu2019}.
 			Besides, the difference between \emph{E-\gls{mrt}} and \emph{D-\gls{mrt}} can be insignificant for dispersed RIScatter nodes.
@@
 \begin{section}{Conclusion}
-	This paper introduced RIScatter as a low-power scatter protocol that unifies backscatter modulation and dymanic passive beamforming by smart input distribution and practical receiver design.
+	This paper introduced RIScatter as a low-power scatter protocol that unifies backscatter modulation and dynamic passive beamforming by smart input distribution and practical receiver design.
 	Starting from scattering principles, we showed how RIScatter nodes include information node of \gls{bc} and reflect element of \gls{ris} as special cases, how they can be built over existing passive scatter devices, and how they simultaneously encode self information and assist legacy transmission.
@@
 
-	One possible direction is to consider backscatter detection over the received signal domain rather than energy domain.
-	Learning-based classification approaches can be promising in such cases.
-	Another interesting question is how to design RIScatter node and receiver in a multi-user system.
-	If one node can be decoded by multiple users, its input distribution may be further adjusted to mimic the multi-beam gain of dynamic passive beamforming \cite{Qiu2022}.
-	This will be answered in our future work.
+	One possible direction is to consider backscatter detection over the received signal domain rather than energy domain, where multi-antenna and learning-based approaches can be promising.
+	Another interesting question is how to design RIScatter node and receiver in a multi-user system to fully exploit the dynamic passive beamforming that naturally origins from the backscatter modulation.
+	% If one node can be decoded by multiple users, its input distribution may be further adjusted to mimic the multi-beam gain of dynamic passive beamforming \cite{Qiu2022}.
+	% This will be answered in our future work.
 \end{section}

### 2022-12-16 main.tex
:bento: Update simulation results

@@
 			\begin{algorithmic}[1]
-				\Require $K$, $N$, $\boldsymbol{h}_{\text{D}}^\mathsf{H}$, $\boldsymbol{H}_{\text{C}}$, $\boldsymbol{\alpha}$, $\mathcal{X}$, $\sigma_v^2$, $\rho$, $\boldsymbol{w}$, $\boldsymbol{t}$, $\varepsilon$
+				\Require $K$, $N$, $\boldsymbol{h}_{\text{D}}^\mathsf{H}$, $\boldsymbol{H}_{\text{C}}$, $\boldsymbol{\alpha}$, $\mathcal{X}$, $\sigma_v^2$, $\rho$, $\boldsymbol{w}$, $\boldsymbol{t}$, $\epsilon$
 				\Ensure $\{\boldsymbol{p}_k^\star\}_{k \in \mathcal{K}}$
@@
 					\State Redo step \ref{st:input_distribution_begin}--\ref{st:input_distribution_end}
-				\Until $I^{(r)}(x_{\mathcal{K}}) - I^{(r-1)}(x_{\mathcal{K}}) \le \varepsilon$
+				\Until $I^{(r)}(x_{\mathcal{K}}) - I^{(r-1)}(x_{\mathcal{K}}) \le \epsilon$
 			\end{algorithmic}
@@
 			\begin{algorithmic}[1]
-				\Require $Q$, $N$, $\boldsymbol{h}_{\text{D}}^\mathsf{H}$, $\boldsymbol{H}_{\text{C}}$, $\boldsymbol{\alpha}$, $\mathcal{X}$, $P$, $\sigma_v^2$, $\rho$, $\{\boldsymbol{p}_k\}_{k \in \mathcal{K}}$, $\boldsymbol{t}$, $\alpha$, $\beta$, $\gamma$, $\varepsilon$
+				\Require $Q$, $N$, $\boldsymbol{h}_{\text{D}}^\mathsf{H}$, $\boldsymbol{H}_{\text{C}}$, $\boldsymbol{\alpha}$, $\mathcal{X}$, $P$, $\sigma_v^2$, $\rho$, $\{\boldsymbol{p}_k\}_{k \in \mathcal{K}}$, $\boldsymbol{t}$, $\alpha$, $\beta$, $\gamma$, $\epsilon$
 				\Ensure $\boldsymbol{w}^\star$
@@
 					\State Redo step \ref{st:gradient_update_start}, \ref{st:gradient_update_end}
-				\Until $\lVert\boldsymbol{w}^{(r)}-\boldsymbol{w}^{(r-1)}\rVert \le \varepsilon$
+				\Until $\lVert\boldsymbol{w}^{(r)}-\boldsymbol{w}^{(r-1)}\rVert \le \epsilon$
 			\end{algorithmic}
@@
 	We choose $\gamma_{\text{D}}=2.6$, $\gamma_{\text{F}}=2.4$, $\gamma_{\text{B}}=2$, and $\kappa_{\text{D}}=\kappa_{\text{F}}=\kappa_{\text{B}}=5$ for direct, forward and backward links.
-	The finite decision threshold domain $\mathcal{T}$ is obtained by $b$-bit uniform discretization over the critical interval defined by the confidence bounds of edge hypotheses (i.e., lower bound of $\mathcal{H}_1$ and upper bound of $\mathcal{H}_L$) with confidence $1-\varepsilon$, and we choose $b=9$ and $\varepsilon=\num{e-3}$.
+	The finite decision threshold domain $\mathcal{T}$ is obtained by $b$-bit uniform discretization over the critical interval defined by the confidence bounds of edge hypotheses (i.e., lower bound of $\mathcal{H}_1$ and upper bound of $\mathcal{H}_L$) with confidence $1-\epsilon$, and we choose $b=9$ and $\epsilon=\num{e-3}$.
 	All achievable rate points/regions are averaged over \num{1000} channel realizations.
@@
 			\begin{equation}
-				I_{\text{B}}(x_{\mathcal{K}};\hat{y}_{\text{\gls{sr}}}) = K \log M - \frac{\epsilon}{M^K},
-			\end{equation}
-			where $\epsilon \triangleq \sum_{m_{\mathcal{K}}} \mathbb{E}_{\hat{v}} \log \sum_{m_{\mathcal{K}}'} \exp ( - {\lvert x_{m_{\mathcal{K}}} - x_{m_{\mathcal{K}}'} + \hat{v} \rvert^2}/{2 \sigma^2} )$ and $\hat{v} \sim \mathcal{CN}(0,\sigma_v^2/N)$.
-			% For a sufficiently large $N$, $\epsilon$ is negligible and the total backscatter rate approaches $K \log M$.
+				I_{\text{B}}(x_{\mathcal{K}};\hat{y}^{\text{\gls{sr}}}) = K \log M - \frac{\iota}{M^K},
+			\end{equation}
+			where $\iota \triangleq \sum_{m_{\mathcal{K}}} \mathbb{E}_{\hat{v}} \log \sum_{m_{\mathcal{K}}'} \exp ( - {\lvert x_{m_{\mathcal{K}}} - x_{m_{\mathcal{K}}'} + \hat{v} \rvert^2}/{2 \sigma^2} )$ and $\hat{v} \sim \mathcal{CN}(0,\sigma_v^2/N)$.
+			% For a sufficiently large $N$, $\iota$ is negligible and the total backscatter rate approaches $K \log M$.
 			\item \emph{\gls{ris}:} Since the backscatter symbol tuple $x_{\mathcal{K}}$ is deterministic, the total backscatter rate is zero and the primary achievable rate becomes a special case of \eqref{eq:primary_mutual_information}
@@
 		For \gls{bbc} with coherent energy detection, the conditional \gls{pdf} of accumulated receive energy \eqref{eq:energy_distribution_bbc} is more skewed at a large $N$, such that the equivalent \gls{dmtmac} \eqref{eq:dmtmac} becomes more reliable.
-		For \gls{sr} with \gls{sic} and \gls{mrc}, the effective backscatter \gls{snr} is increased by $N$ times and the penalty term $\epsilon$ becomes insignificant.
+		For \gls{sr} with \gls{sic} and \gls{mrc}, the effective backscatter \gls{snr} is increased by $N$ times and the penalty term $\iota$ becomes insignificant.
 		Such an \gls{sr} only guarantees the primary benefit with a large $N$, but decreases the backscatter symbol rate by a factor of $N$ and requires $N$ \gls{sic} processes to decode each backscatter symbol (tuple).

### 2022-12-18 main.tex
:construction: Update manuscript

@@
 \documentclass[journal]{IEEEtran}
+% \documentclass[journal,12pt,onecolumn,draftclsnofoot]{IEEEtran}
 
@@
 		On the other hand, \gls{ambc} (resp. \gls{sr}) involves \emph{coexisting} active primary and passive backscatter links in a competitive (resp. collaborative) relationship.
-		In \gls{ambc}, the backscatter link only needs to know the basic information (e.g., operating frequency and input distribution) of the primary link, while the primary link does not need to know the existence of the backscatter link.
+		In \gls{ambc}, the backscatter link only needs to know the basic information (e.g., operating frequency) of the primary link, while the primary link may be completely unaware of the backscatter link.
 		In \gls{sr}, relevant \gls{csi} is exploited at the co-located receiver for cooperative decoding, and may also be exploited at the primary transmitter for cooperative active beamforming.
@@
 			% Coexisting link(s)                                              & 1                   & 2 (competitive)             & 2 (collaborative)                                     & 1                   & 2 (collaborative)                                                       \\
-			Information link(s)                                     & Passive backscatter only & Active-passive coexisting (competitive) & Active-passive coexisting (collaborative)             & Active primary only & Active-passive coexisting (collaborative)                               \\
+			Information link(s)                                     & Passive backscatter & Active-passive coexisting (competitive) & Active-passive coexisting (collaborative)             & Active primary      & Active-passive coexisting (collaborative)                               \\
 			% Primary/Backscatter modulation                                  & No/Yes              & Yes/Yes                     & Yes/Yes                                               & Yes/No              & Yes/Yes                                                                 \\
@@
 		% ! double modulation, double fading, symbol period difference
-		The last two motivated \cite{Long2020a,Liang2020,Guo2019b,Ding2020,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Yang2018,Han2021,Zhang2022} to view \gls{sr} as a multiplicative \gls{noma} and perform \gls{sic} from primary to backscatter link.
-		During primary decoding, the randomness of backscatter modulation can be modelled as channel uncertainty (resp.
-multiplicative interference) when the backscatter-over-primary symbol period ratio $N$ is large (resp.
-small)\footnote{For state-of-the-art low-power \gls{rfid} tags, the load-switching speed usually varies between \num{100}s of \unit{\kHz} to \num{10}s of \unit{\MHz} \cite{Torres2021}, corresponding to a typical $N$ between \num{10} and \num{1000}.}.
-		Such a \gls{sic} receiver is operation-intensive and \gls{csi}-sensitive, which involves $N$ re-encoding, precoding, subtraction together with a time-domain \gls{mrc} to decode each backscatter symbol.
+		The second property motivated \cite{Long2020a,Liang2020,Guo2019b,Ding2020,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Yang2018,Han2021,Zhang2022} to view \gls{sr} as a multiplicative \gls{noma} and perform \gls{sic} from primary to backscatter link.
+		During primary decoding, the randomness of backscatter modulation can be modelled as channel uncertainty or multiplicative interference when the backscatter-over-primary symbol period ratio $N$ is large or small\footnote{For state-of-the-art low-power \gls{rfid} tags, the load-switching speed usually varies between \num{100}s of \unit{\kHz} to \num{10}s of \unit{\MHz} \cite{Torres2021}, corresponding to a typical $N$ between \num{10} and \num{1000}.}.
+		Such a \gls{sic} receiver is operation-intensive and \gls{csi}-sensitive because it involves $N$ re-encoding, precoding, subtraction together with a time-domain \gls{mrc} to decode each backscatter symbol.
 		When $N$ is sufficiently large (i.e., commensal \gls{sr}), the average primary achievable rate under semi-coherent detection\footnote{In this paper, semi-coherent detection refers to the primary/backscatter decoding based on known \gls{csi} and unknown backscatter/primary symbols.} asymptotically approaches its coherent counterpart, and both links may be decoded in an interference-free manner \cite{Long2020a}.
@@
 		\cite{Vougioukas2019} modifies the load-switching speed to shift the scattered signal to the desired frequency band.
-		This enables backscatter \gls{fdma} at the cost of larger bandwidth and higher node power consumption.
-		To reduce coordination burden for passive nodes, \cite{Han2021} proposed a random code-assisted multiple access for \gls{sr} and evaluated the asymptotic \gls{sinr} using random matrix theory.
-		This code-domain solution suffers from the near-far problem and imperfect synchronization, both being severe in low-power backscatter scenarios.
+		This enables backscatter \gls{fdma} at the cost of larger bandwidth and higher power consumption at the scatter nodes.
+		To reduce the coordination cost, \cite{Han2021} proposed a random code-assisted multiple access for \gls{sr} and evaluated the asymptotic \gls{sinr} using random matrix theory.
+		This code-domain solution suffers from the near-far problem and imperfect synchronization, both being severe in \gls{bc}.
 
@@
 		Relevant literatures also consider either \emph{Gaussian} codebook \cite{Guo2019b,Ding2020,Long2020a,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Hu2021b} that is impractical for low-power nodes, or finite \emph{equiprobable} inputs \cite{Yang2018,Liang2020,Han2021,Zhang2022,Liu2019d,Bereyhi2020,Xu2020b,Zhang2021d,Hua2022,Basar2020,Ma2020a,Yuan2021,Hu2021a} that does not fully exploit the \gls{csi} and signal properties of active-passive coexisting networks.
-		% For active-passive coexisting networks, it has been observed that:
-		% 1) the transmitter-scatter-receiver path can be exploited to adjust wireless channel and establish passive connection;
-		% 2) co-located receiver enables interference cancellation and cooperative decoding;
 	\end{subsection}
@@
 	\begin{subsection}{Contributions}
-		% \emph{First,} we propose RIScatter as a novel scatter protocol that unifies \gls{bc} and \gls{ris} from a distribution perspective.
-		% As shown in Fig.~\subref*{fg:riscatter}, the passive RIScatter node rides over an active transmission and controls the scattered wave to
-		% partially engineer the wireless channel and partially modulate its own information.
-		% This is accomplished by incorporating both the \gls{csi} and \gls{qos} into the reflection state distribution design.
-		% As such, RIScatter can generalize \gls{bc} (uniform distribution) and \gls{ris} (degenerate distribution) to create a tradeoff between backscatter modulation and passive beamforming.
-		% This is the first paper to associate \gls{bc} and \gls{ris} from a distribution perspective.
-
 		\emph{First,} we propose RIScatter as a novel scatter protocol that unifies \gls{bc} and \gls{ris} by adaptive reflection state (i.e., backscatter input) distribution design.
-		As shown in Fig.~\subref*{fg:riscatter}, the passive RIScatter node rides over an active transmission and smartly scatters the incident wave to simultaneously engineer the primary channel and modulate its own information, while a co-located receiver cooperatively decodes both coexisting links.
-		The reflection pattern of each RIScatter node is neither fully random like \gls{bc} nor fully deterministic like \gls{ris}, but semi-randomly chosen with the guidance of reflection state distribution, whose design accommodates the impact of information source, \gls{csi}, and \gls{qos} of both links.
+		As shown in Fig.~\subref*{fg:riscatter}, one or more passive RIScatter nodes ride over an active transmission and smartly scatters the incident wave to simultaneously engineer the primary channel and modulate its own information, while a co-located receiver cooperatively decodes both coexisting links.
+		The reflection pattern over time is neither fully random like \gls{bc} nor fully deterministic like \gls{ris}, but semi-randomly chosen with the guidance of reflection state distribution, whose design accommodates the impact of information source, \gls{csi}, and \gls{qos} of both links.
 		Such an adaptive backscatter channel coding boils down to the degenerate distribution of \gls{ris} when the primary link is prioritized, and outperforms the uniform distribution of line-coded \gls{bc} (by accounting the \gls{csi}) when the backscatter link is prioritized.
@@
 		However, such a novel scatter protocol encounters two major challenges, namely the cooperative receiver design and the adaptive backscatter input distribution design.
-		This is the first paper to associate \gls{bc} and \gls{ris} from the perspective of reflection state distribution.
+		This is the first paper to unify \gls{bc} and \gls{ris} from the perspective of reflection state distribution.
 
 		\emph{Second,} we address the first challenge by proposing a practical receiver that accommodates the double fading, double modulation, and symbol period difference of active-passive coexisting networks.
-		Since joint decoding involves high complexity and individual decoding is very inefficient (neither cooperative nor exploiting signal properties), most relevant literatures consider a sequential primary-backscatter decoding based on \gls{sic}.
+		Since joint decoding involves high complexity while individual decoding can be inefficient (neither cooperative nor exploiting signal properties), most relevant literatures consider a sequential primary-backscatter decoding based on \gls{sic}.
 		Specifically, the decoding of each backscatter symbol requires $N$ re-encoding, precoding, subtraction together with a time-domain \gls{mrc}, which can be operation-intensive and \gls{csi}-sensitive.
 		In contrast, the proposed RIScatter receiver semi-coherently decodes the backscatter symbol from the accumulated receive energy, re-encodes to recover the exact reflection pattern, and combine it with relevant \gls{csi} to determine the transmitter-scatter-receiver path response.
-		That is, the semi-coherent energy-based backscatter detection becomes part of primary channel training, enabling simultaneous backscatter modulation and dynamic passive beamforming by only one energy comparison, re-encoding, and precoding per backscatter symbol without \gls{sic}.
+		Thanks to the double modulation and symbol period difference, the backscatter symbol can be modelled within primary channel (similar to \gls{ris}) rather than being re-precoded and cancelled, and the semi-coherent energy-based backscatter detection indeed becomes part of primary channel training.
 		The strategy is suitable for arbitrary primary sampling rate and backscatter load-switching speed (i.e., arbitrary $N$).
@@
 		\emph{Third,} we address the second challenge by considering a specific scenario where multiple co-located/dispersed RIScatter nodes ride over an active point-to-point \gls{miso} transmission to perform backscatter modulation and dynamic passive beamforming towards a nearby user.
-		% We first express the achievable primary and total backscatter rates under given \gls{qos} as functions of active beamforming at the \gls{ap}, input distribution at RIScatter nodes, and backscatter decision regions at the user.
-		We first express the primary and total backscatter rates under given \gls{qos} as functions of \emph{input distribution} at RIScatter nodes, \emph{active beamforming} at the \gls{ap}, and \emph{backscatter decision regions} at the user.
+		For a given \gls{qos}, we first express the primary and total backscatter rates as functions of \emph{input distribution} at RIScatter nodes, \emph{active beamforming} at the \gls{ap}, and \emph{backscatter decision regions} at the user.
 		Then, we characterize the achievable rate region by optimizing those variables under different \gls{qos}.
 		Since the original problem is highly non-convex, we propose a suboptimal \gls{bcd} algorithm where the \gls{kkt} input distribution is numerically evaluated by limit of sequences, the active beamforming is iteratively updated by \gls{pgd} accelerated by \gls{bls}, and the decision regions are refined by existing sequential quantization methods for \gls{dmtc}.
-		% The proposed backscatter input distribution design can also be generalized to other setups.
 		Uniquely, we account for \gls{csi}, \gls{qos}, and backscatter constellation in those optimizations, and the proposed backscatter input distribution design is applicable to more general scenarios.
@@
 		1) adaptive reflection state distribution design can flexibly transition between backscatter modulation and passive beamforming;
-		2) when primary link is prioritized, input distribution becomes degenerate and RIScatter nodes coincide with discrete \gls{ris};
-		3) when backscatter link is prioritized, adaptive RIScatter encoding achieves higher backscatter rate than conventional line-coded \gls{bc} (with equiprobable inputs);
+		2) when the primary link is prioritized, input distribution becomes degenerate and RIScatter nodes coincide with discrete \gls{ris};
+		3) when the backscatter link is prioritized, adaptive RIScatter encoding achieves higher backscatter rate than conventional line-coded \gls{bc} with equiprobable inputs;
 		4) co-located RIScatter nodes can further leverage total backscatter rate by joint encoding;
-		5) the proposed receiver maintains the passive beamforming benefit and provides comparable backscatter rate to \gls{sic}-based \gls{sr}, with encoding and precoding costs reduced to $1/N$;
-		6) it also supports scatter nodes with faster load-switching speed for higher throughput;
-		% 7) \gls{pgd} active beamformer enlarges achievable rate region by boosting the receive \gls{snr} and/or widening the energy gap under different reflection states;
+		5) the proposed receiver maintains the passive beamforming benefit and provides comparable backscatter rate to \gls{sic}-based \gls{sr}, with re-encoding costs reduced to $1/N$ and no re-precoding/cancellation;
+		6) it also supports scatter nodes with faster load-switching speed for potentially higher throughput;
 		7) \gls{pgd} active beamformer effectively increases the primary (resp.
@@
 widening the energy gap under different reflection states), and can smoothly transition in between under different \gls{qos};
-		8) distribution-adaptive backscatter detectors provide higher backscatter rate than the conventional \gls{ml} detector.
+		8) distribution-aware backscatter detectors provide higher backscatter rate than the conventional \gls{ml} detector.
 	\end{subsection}
@@
 \begin{section}{Scattering Principles}
-	\gls{rf} wave scattering and reflecting are usually realized by a {variable-load antenna} or {programmable metamaterial} and can be described by a unified signal model \cite{Liang2022}.
-	A typical antenna-based scatterer consists of an integrated antenna, a load-switching modulator, an energy harvester, and on-chip components (e.g., microcontroller and sensors) \cite{Dobkin2012}.
+	\gls{rf} wave scattering and reflecting can be described by a unified model and realized by {variable-load antennas} or {programmable metamaterial} \cite{Liang2022}.
+	An antenna-based scatterer usually consists of an integrated antenna, a load-switching modulator, an energy harvester, and on-chip components (e.g., microcontroller and sensors) \cite{Dobkin2012}.
 	It first receives the impinging signals, then reradiates some back to the space and dissipates the remaining.
-	In comparison, a typical metamaterial-based scatterer comprises an outer metamaterial layer of numerous sub-wavelength metallic/dielectric patches with tunable permittivity/permeability, a middle copper plate layer that reflects residual to avoid leakage, an inner circuit board layer that adjusts the amplitude and phase responses of patches, and an integrated microcontroller/\glsentryshort{fpga} that coordinates with the network and controls the circuit \cite{Wu2020}.
-	Ideally, it reflects the incident waves at the air-metamaterial boundary without receiving them, and mainly applies a phase shift on the reflected wave.
-	In practice, both types of scatterers have finite reflection states with non-zero reflection loss, and the scattered signal can be decomposed into the \emph{structural} and \emph{antenna} mode components \cite{Hansen1989}.
-	The former consistently contributes to environment multipath and can be modelled within \gls{csi}, while the latter depends on impedance mismatch and can be used for backscatter modulation and/or passive beamforming.
-	For a scatter node with $M$ reflection states, the reflection coefficient at state $m \in \mathcal{M} \triangleq \{1,\ldots,M\}$ is
+	In comparison, a typical metamaterial-based scatterer comprises an outer metamaterial layer of numerous sub-wavelength metallic/dielectric patches (with tunable permittivity/permeability), a middle copper plate layer that avoids leakage, an inner circuit board layer that adjusts patch responses, and an integrated microcontroller/\glsentryshort{fpga} for coordination and control \cite{Wu2020}.
+	Ideally, it reflects the wave at the space-metamaterial boundary without receiving them and mainly applies a phase shift.
+	In practice, both types of scatterers have {finite} reflection states with non-zero reflection loss.
+	The scattered signal can be decomposed into a {structural} mode component that consistently contributes to environment multipath and can be modelled within \gls{csi}, and an \emph{antenna} mode component that depends on the impedance mismatch and can be used for backscatter modulation and/or passive beamforming \cite{Hansen1989}.
+	For an antenna-based (resp. metamaterial-based) scatter node with $M$ reflection states, the reflection coefficient at state $m \in \mathcal{M} \triangleq \{1,\ldots,M\}$ is
 	\begin{equation}
@@
 	where $Z_m$ is the antenna load (resp. metamaterial unit) impedance at state $m$ and $Z$ is the antenna input (resp. medium characteristic) impedance.
-	% Backscatter modulation and passive beamforming are realized by manipulating the reflection coefficient.
 	\gls{bc} employ scatter nodes as information sources that \emph{randomly switching} between different states.
@@
 	where $\alpha \in \mathbb{I}$ is the common amplitude scattering ratio at the direction of interest.
-	In contrast, \gls{ris} employ reflect elements as channel reconfigurators \emph{deterministically choosing} the reflection state based on \gls{csi}.
+	In contrast, \gls{ris} employ reflect elements as channel adaptors that \emph{deterministically choosing} the reflection state based on \gls{csi}.
 	For a \gls{ris} element with $M$ available states, phase shift $\theta_m$ maps to reflection coefficient $\Gamma_m$ by \cite{Wu2018}
@@
 	\end{equation}
-	where $\beta_m \in \mathbb{I}$ is the total amplitude scattering ratio at state $m$.\footnote{Most existing \gls{ris} literatures assume lossless reflection $\beta_m=1$, $\forall m$.}
+	where $\beta_m \in \mathbb{I}$ is the overall amplitude scattering ratio at state $m$.\footnote{Most existing \gls{ris} literatures assume lossless reflection $\beta_m=1$, $\forall m$.}
 \end{section}
@@
 	\begin{subsection}{Concepts}
-		As a generalization of \gls{bc} and \gls{ris}, RIScatter involves coexisting active primary and passive backscatter links in a flexible and mutualistic manner.
-		RIScatter nodes leverage \gls{csi}- and \gls{qos}-based reflection state (i.e., backscatter input) distribution design to smoothly transition between backscatter modulation and passive beamforming.
+		We propose RIScatter in Fig.~\subref*{fg:riscatter} as a generalization of \gls{bc} and \gls{ris}, which involves coexisting active primary and passive backscatter links in a flexible and mutualistic manner.
+		RIScatter nodes leverage \gls{csi}- and \gls{qos}-based reflection state distribution design to smoothly transition between backscatter modulation and passive beamforming.
+		Fig.~\ref{fg:riscatter_node} illustrates the block diagram, equivalent circuit, and scatter model of a RIScatter node.
 		It can be implemented by adding an integrated receiver \cite{Kim2021a} and adaptive encoder \cite{He2020e} to off-the-shelf passive \gls{rfid} tags.
-		The block diagram, equivalent circuit, and scatter model of a RIScatter node are illustrated in Fig.~\ref{fg:riscatter_node}, while the reflection state distribution and reflection pattern of scattering applications are shown in Fig.~\ref{fg:scatter_comparison}.
 		\begin{figure*}[!t]
@@
 		\end{figure*}
+		Fig.~\ref{fg:scatter_comparison} compares the reflection state distribution and reflection pattern of RIScatter and other applications.
 		\begin{figure}[!t]
@@
 		\end{figure}
-		Instead of using fully random or fully deterministic reflection pattern over time, each RIScatter node semi-randomly chooses the reflection state for each backscatter block with the guidance of input probability $P(\Gamma_m)$ at state $m$.
-		Such an adaptive backscatter channel coding boils down to degenerate distribution of \gls{ris} when primary link is prioritized, and outperforms conventional line-coded \gls{bc} with equiprobable inputs (e.g., FM0 for \gls{rfid}) when backscatter link is prioritized.
-		Relevant \gls{csi} can be acquired by existing low-power estimation techniques.
-		For dispersed RIScatter nodes, the cascaded transmitter-scatter-receiver channels can be estimated by sequential \cite{Bharadia2015,Yang2015b,Guo2019g} or parallel approaches \cite{Jin2021a} originally proposed for \gls{bc}.
+		Instead of using fully random or fully deterministic reflection pattern over time, each RIScatter node \emph{semi-randomly} chooses the reflection state for each backscatter block with \emph{guidance of input probability} $P(\Gamma_m)$ at state $m$.
+		Such an adaptive backscatter channel coding includes the degenerate distribution of \gls{ris} and the uniform distribution of line-coded \gls{bc} as special cases.
+		Importantly, RIScatter system design only requires the \emph{direct} transmitter-receiver and \emph{cascaded} transmitter-scatter-receiver \gls{csi}.
+		For dispersed RIScatter nodes, relevant \gls{csi} can be estimated by sequential \cite{Bharadia2015,Yang2015b,Guo2019g} or parallel approaches \cite{Jin2021a} originally proposed for \gls{bc}.
 		For co-located RIScatter nodes, the estimation can be simplified by group-based \cite{Zheng2019} and hierarchical \cite{You2019} trainings originally proposed for \gls{ris}.
 
-		\begin{remark}
-			Active-passive coexisting networks involve a double modulation where the primary and backscatter symbols of different period are superimposed by multiplication coding.
-			The reflection pattern not only encodes the backscatter message, but also affects the channel for primary link.
-			Therefore, backscatter detection under primary uncertainty can be viewed as part of primary channel training, and novel decoding strategies apart from \gls{sic}%
-			\footnote{
-				Superposition coding and \gls{sic} was originally proposed to achieve the capacity vertices of Gaussian \gls{mac}.
-				For active-passive coexisting networks, \gls{sic} not only fails to utilize the multiplication coding/double modulation, but also requires $N$ re-encoding, precoding and subtraction with a time-domain \gls{mrc} during each backscatter block.
-			}
-			is desired for RIScatter.
-		\end{remark}
-
-		Next, we propose a cooperative receiver that effectively exploit the double modulation, double fading and symbol period difference to reduce the decoding complexity and improve the primary-backscatter tradeoff.
+		% \begin{remark}
+		% 	Active-passive coexisting networks involve a double modulation where the primary and backscatter symbols of different period are superimposed by multiplication coding.
+		% 	The reflection pattern not only encodes the backscatter message, but also affects the channel for primary link.
+		% 	Therefore, backscatter detection under primary uncertainty can be viewed as part of primary channel training, and novel decoding strategies apart from \gls{sic}%
+		% 	\footnote{
+		% 		Superposition coding and \gls{sic} was originally proposed to achieve the capacity vertices of Gaussian \gls{mac}.
+		% 		For active-passive coexisting networks, \gls{sic} not only fails to utilize the multiplication coding/double modulation, but also requires $N$ re-encoding, precoding and subtraction with a time-domain \gls{mrc} during each backscatter block.
+		% 	}
+		% 	is desired for RIScatter.
+		% \end{remark}
+
+		% ? Add an illustration here if space allows
+		We also propose a novel cooperative receiver that exploits the double modulation, double fading and symbol period difference to reduce the decoding complexity and improve the primary-backscatter tradeoff.
 		As illustrated in Fig.~\ref{fg:energy_distribution}, conditioned on different reflection state hypotheses, the accumulated receive energy per backscatter block follows Gamma distribution with different scale parameters \cite{Qian2017b}.
@@
 		\end{figure}
-		Hence, the receiver can semi-coherently (in the presence of primary uncertainty) decode node messages from the accumulated receive energy, re-encode to recover actual reflection patterns, and model the deterministic multipath within the primary channel.
-		It enables simultaneous backscatter modulation and dynamic passive beamforming by only one energy comparison, re-encoding, and precoding operations for each backscatter block (instead of primary block), and is suitable for arbitrary primary sampling rate and backscatter load-switching speed.
+		Hence, the receiver can semi-coherently (under primary uncertainty) decode RIScatter nodes from the accumulated receive energy, re-encode to recover the exact reflection patterns, and combine those with cascaded \gls{csi} to determine the multipath response and model within the primary channel.
+		Such a backscatter-primary decoding enables simultaneous backscatter modulation and dynamic passive beamforming by only one energy comparison, re-encoding, and precoding during each backscatter (instead of primary) block.
+		It enjoys a three-fold benefit compared to conventional primary-backscatter decoding with \gls{sic}, namely
+		1) reduces the re-encoding frequencies to $1/N$;
+		2) requires no re-precoding, cancellation, or \gls{mrc};
+		3) preserves backscatter modulation and passive beamforming at smaller $N$ for potentially higher backscatter throughput.
 	\end{subsection}
@@
 		In the primary point-to-point system, the \gls{ap} transmits information to the user over the multipath channel enhanced by RIScatter nodes.
-		In the backscatter \gls{mac} system, the \gls{ap} and user become carrier emitter and backscatter reader, and the RIScatter nodes modulate over the scattered \gls{rf} signals.
-		% For simplicity, we consider a quasi-static block fading model where channels remain constant within each block and vary independently between consecutive blocks, and assume the backscatter-over-primary symbol period ratio $N$ is an integer.
-		For simplicity, we consider a quasi-static block fading model and focus on one specific block where all \gls{csi} remain constant.
-		Let the backscatter-over-primary symbol period ratio $N$ be an positive integer.
-		We also omit the signal reflected by two or more times and ignore the propagation time difference of different paths.
+		In the backscatter multiple access system, the \gls{ap} and user become carrier emitter and backscatter reader, and the RIScatter nodes modulate over the scattered \gls{rf} signals.
+		For simplicity, we consider a quasi-static block fading model and focus on a specific block where all \gls{csi} remain constant.
+		Without loss of generality, let the backscatter-over-primary symbol period ratio $N$ be a positive integer.
+		We also omit the signal reflected by two or more times and ignore the multipath propagation time difference.
 		Denote the \gls{ap}-user direct channel as $\boldsymbol{h}_{\text{D}}^\mathsf{H} \in \mathbb{C}^{1 \times Q}$, the \gls{ap}-node $k \in \mathcal{K} \triangleq \{1,\ldots,K\}$ forward channel as $\boldsymbol{h}_{\text{F},k}^\mathsf{H} \in \mathbb{C}^{1 \times Q}$, the node $k$-user backward channel as $h_{\text{B},k}$, and the cascaded \gls{ap}-node $k$-user channel as $\boldsymbol{h}_{\text{C},k}^\mathsf{H} \triangleq h_{\text{B},k} \boldsymbol{h}_{\text{F},k}^\mathsf{H} \in \mathbb{C}^{1 \times Q}$.
 		Let $x_k \in \mathcal{X} \triangleq \{c_1,\ldots,c_M\}$ be the coded backscatter symbol of node $k$ and $x_{\mathcal{K}} \triangleq (x_1,\ldots,x_K)$ be the backscatter symbol tuple of all nodes.
-		Without loss of generality, we consider one backscatter block (i.e., $N$ primary blocks) in the following context.
 		Due to double modulation, the primary equivalent channel is a function of backscatter symbol tuple\footnote{\eqref{eq:equivalent_channel_bc} and \eqref{eq:equivalent_channel_ris} are often used in \gls{bc} and \gls{ris} literatures, respectively.}
@@
 		\end{subequations}
-		where $\alpha_k \in \mathbb{I}$ is the amplitude scattering ratio of node $k$, $\boldsymbol{\alpha} \triangleq [\alpha_1,\ldots,\alpha_K]^\mathsf{T} \in \mathbb{I}^{K}$, $\boldsymbol{x} \triangleq [x_1,\ldots,x_K]^\mathsf{H} \in \mathcal{X}^{K}$, and $\boldsymbol{H}_{\text{C}} \triangleq [\boldsymbol{h}_{\text{C},1},\ldots,\boldsymbol{h}_{\text{C},K}]^\mathsf{H} \in \mathbb{C}^{K \times Q}$.
+		where $\alpha_k \in \mathbb{I}$ is the common amplitude scattering ratio of node $k$, $\boldsymbol{\alpha} \triangleq [\alpha_1,\ldots,\alpha_K]^\mathsf{T} \in \mathbb{I}^{K}$, $\boldsymbol{x} \triangleq [x_1,\ldots,x_K]^\mathsf{H} \in \mathcal{X}^{K}$, and $\boldsymbol{H}_{\text{C}} \triangleq [\boldsymbol{h}_{\text{C},1},\ldots,\boldsymbol{h}_{\text{C},K}]^\mathsf{H} \in \mathbb{C}^{K \times Q}$.
+		In the following context, we focus on one backscatter block (i.e., $N$ primary blocks).
 		The signal received by the user at primary block $n \in \mathcal{N} \triangleq \{1,\ldots,N\}$ is
@@
 
-		For the ease of notations, we map the state index tuple $m_{\mathcal{K}}$ to the corresponding index $l \in \mathcal{L} \triangleq \{1,\ldots,L \triangleq M^K\}$, where $\sigma_1^2,\ldots,\sigma_L^2$ is an ascending sequence.
+		For the ease of notations, we map the state index tuple $m_{\mathcal{K}}$ to $l \in \mathcal{L} \triangleq \{1,\ldots,L \triangleq M^K\}$, where $\sigma_1^2,\ldots,\sigma_L^2$ is a non-decreasing sequence.
 		Both notations are used interchangeably in the following context.
@@
 		where $t_l$ is the energy decision threshold between hypotheses $\mathcal{H}_{l}$ and $\mathcal{H}_{l+1}$.
-		For a given decision threshold vector $\boldsymbol{t} \triangleq [t_0,\ldots,t_L]^\mathsf{T} \in \mathbb{R}_+^{(L+1)}$, we can formulate a \gls{dmtmac} with transition probability from input $x_{m_{\mathcal{K}}}$ to output $\hat{x}_{m_{\mathcal{K}}'}$ given by
+		For a given decision threshold vector $\boldsymbol{t} \triangleq [t_0,\ldots,t_L]^\mathsf{T} \in \mathbb{R}_+^{(L+1)}$, we can formulate a \gls{dmtmac} with transition probability from input tuple $x_{m_{\mathcal{K}}}$ to output tuple $\hat{x}_{m_{\mathcal{K}}'}$ as
 		\begin{equation}
@@
 		\end{equation}
-		over which adaptive input distribution design and backscatter channel coding can be performed.
+		over which adaptive backscatter channel coding can be performed.
 		\label{st:system_model}
@@
 
-		Once nodes are successfully decoded, we can re-encode for exact $x_{\mathcal{K}}$, recover their reflection patterns by \eqref{eq:backscatter_modulation}, and determine the primary equivalent channel by \eqref{eq:equivalent_channel}.
+		Once nodes are successfully decoded, we can re-encode and determine the primary equivalent channel by \eqref{eq:equivalent_channel}.
 		Therefore, the primary information function conditioned on $x_{m_{\mathcal{K}}}$ is
@@
 		\end{align}
-		where $\rho \in \mathbb{I}$ is the \gls{qos} of the primary link.
+		where $\rho \in \mathbb{I}$ is the relative \gls{qos} of the primary link.
 		We notice the average primary rate \eqref{eq:primary_mutual_information} depends on the backscatter input distribution and active beamforming, while the total backscatter rate depends on the input distribution and \gls{dmtmac} \eqref{eq:dmtmac} that relates to the active beamforming and decision thresholds.
@@
 	Problem \eqref{op:weighted_sum_rate} generalizes conventional \gls{bc} by allowing \gls{csi}- and \gls{qos}-adaptive input distribution and detection region design.
-	It also generalizes the discrete \gls{ris} phase shift selection by allowing stochastic reflection (i.e., relaxing the feasible domain from the vertices of $M$-dimensional probability simplex to the simplex itself).
+	It also generalizes the discrete \gls{ris} phase shift selection by allowing stochastic reflection (i.e., relaxing the feasible domain from the \emph{vertices} of $M$-dimensional probability simplex to the simplex itself).
 	Since problem \eqref{op:weighted_sum_rate} is highly non-convex, we propose a \gls{bcd} algorithm that iteratively updates $\{\boldsymbol{p}_k\}_{k \in \mathcal{K}}$, $\boldsymbol{w}$ and $\boldsymbol{t}$ until convergence.
@@
 		\end{maxi!}
-		which is convex when $K=1$ or joint encoding\footnote{Joint encoding formulates an equivalent source of $M^K$ valid codewords, such that one can directly design $P_{\mathcal{K}}(x_{m_{\mathcal{K}}})$ instead of $P_k(x_{m_k})$.} over $K>1$ co-located nodes is available.
+		which is convex when $K=1$ or joint encoding\footnote{Joint encoding formulates an equivalent source of $M^K$ codewords, such that one can directly design $P_{\mathcal{K}}(x_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}$ instead of $P_k(x_{m_k})$, $\forall k,m_k$.} over $K>1$ co-located nodes is available.
 		When the nodes are dispersed, problem \eqref{op:input_distribution} involves coupled term $\prod_{k \in \mathcal{K}} P_k(x_{m_k})$ and is non-convex.
-		Following \cite{Rezaeian2004}, we first recast the \gls{kkt} conditions to their equivalent forms, then propose a numerical method that guarantees those conditions by limit of sequences.
+		Following \cite{Rezaeian2004}, we first recast the \gls{kkt} conditions to their equivalent forms, then propose a numerical method that guarantees those conditions on convergence of sequences.
 		% ? Next, we propose a numerical method that evaluate the \gls{kkt} input distribution by limit of sequences.
@@
 			As demonstrated in \cite{Buhler2011}, \gls{kkt} conditions are generally necessary but insufficient for total rate maximization of discrete \gls{mac}.
-			We will show in the simulation part that, for a moderate $K$, the average achievable rate regions of \gls{kkt} and global-optimal input distributions almost overlap with each other.
+			We will show by numerical results that, for a moderate $K$, the average achievable rate regions of \gls{kkt} and global-optimal input distributions completely coincide with each other.
 			\label{re:input_kkt_distribution}
@@
 		\end{equation}
-		The \gls{pgd} active beamforming optimization with adaptive \gls{bls} step size \cite[Section 9.2]{Boyd2004} is summarized in Algorithm \ref{al:active_beamforming}.
+		The \gls{pgd} active beamforming optimization with step size by \gls{bls} \cite[Section 9.2]{Boyd2004} is summarized in Algorithm \ref{al:active_beamforming}.
 		\begin{algorithm}[!t]
@@
 		\begin{remark}
-			Upon successful backscatter decoding, the user can always re-encode node messages to recover the exact reflection patterns and determine the primary equivalent channel at each backscatter block.
-			Thus, backscatter decision design has no impact on the primary achievable rate, and any thresholding that maximize the total backscatter rate \eqref{eq:backscatter_mutual_information} is also optimal for problem \eqref{op:decision_threshold}.
+			Backscatter decision design has no impact on the primary achievable rate, because the primary equivalent channel \eqref{eq:equivalent_channel} at each backscatter block can always be determined upon successful backscatter decoding.
+			It suggests any thresholding scheme that maximize the total backscatter rate \eqref{eq:backscatter_mutual_information} is also optimal for problem \eqref{op:decision_threshold}.
 			\label{re:backscatter_decision}
@@
 		\begin{remark}
-			In terms of total backscatter rate, the potentially dispersed nodes with known input distribution can be viewed as an equivalent source with backscatter symbol tuples as codewords.
+			In terms of total backscatter rate, the potentially dispersed nodes with known input distribution can be viewed as an equivalent source with symbol tuples as codewords.
 			As such, the \gls{dmtmac} \eqref{eq:dmtmac} becomes a \gls{dmtc} and problem \eqref{op:decision_threshold} reduces to the rate-optimal quantization design for a discrete-input continuous-output memoryless channel.
@@
 		\end{figure}
-		As shown in Fig.~\ref{fg:discrete_outputs}, by introducing the extra analog-to-digital conversion, we can group adjacent high-resolution energy bins to construct backscatter decision regions.
+		As shown in Fig.~\ref{fg:discrete_outputs}, by introducing an extra analog-to-digital conversion, we can group adjacent high-resolution energy bins to construct backscatter decision regions.
 		Thus, problem \eqref{op:decision_threshold} can be recast as
@@
 		\end{maxi!}
-		which can be solved by existing rate-optimal sequential quantizer designs for \gls{dmtc}.
+		which is solvable using existing rate-optimal sequential quantizer designs for \gls{dmtc}.
 		To obtain global optimal solution, \cite{He2021} started from the quadrangle inequality and proposed a \gls{dp} method accelerated by the \gls{smawk} algorithm with computational complexity $\mathcal{O}\bigl(L^2(\mathrm{card}(\mathcal{T})-L)\bigr)$, while \cite{Nguyen2020a} started from the optimality condition for three neighbor thresholds and presented a traverse-then-bisect algorithm with complexity $\mathcal{O}\bigl(\mathrm{card}(\mathcal{T})L\log(\mathrm{card}(\mathcal{T})L)\bigr)$.
@@
 \begin{section}{Simulation Results}
-	In this section, we provide numerical results to evaluate the proposed input distribution, active beamforming, and backscatter decision designs for the RIScatter system in Fig.~\ref{fg:riscatter_network}.
+	In this section, we provide numerical results to evaluate the proposed input distribution, active beamforming, and backscatter decision designs for the considered RIScatter system.
 	We assume the AP-user distance is \qty{10}{\meter} and at least one RIScatter nodes are randomly dropped in a disk centered at the user with radius $r$.
 	% The \gls{ap} is with an average transmit power budget $P=\qty{36}{\dBm}$, all nodes employs $M$-\gls{qam} with amplitude scattering ratio $\alpha=0.5$, and the user is with average noise power $\sigma_v^2=\qty{-40}{\dBm}$.
-	The \gls{ap} is with an average transmit power budget $P=\qty{36}{\dBm}$ and all nodes employs $M$-\gls{qam} with amplitude scattering ratio $\alpha=0.5$.
+	The \gls{ap} is with an average transmit power budget $P=\qty{36}{\dBm}$ and all nodes employs $M$-\gls{qam} with common amplitude scattering ratio $\alpha=0.5$.
 	For all channels involved, we consider a distance-dependent path loss model
@@
 			To characterize each achievable rate region, we progressively obtain all boundary points by successively increasing the primary \gls{qos} $\rho$ and solving problem \eqref{op:weighted_sum_rate}.
-			For $\rho=0$ where backscatter link is prioritized, we initialize Algorithm \ref{al:input_distribution} and \ref{al:active_beamforming} by uniform input distribution and \gls{mrt} towards sum cascaded channel $\sum_{k} \boldsymbol{h}_{\text{C},k}^\mathsf{H}$, respectively.
+			For $\rho=0$ where the backscatter link is prioritized, we initialize Algorithm \ref{al:input_distribution} and \ref{al:active_beamforming} by uniform input distribution and \gls{mrt} towards the sum cascaded channel $\sum_{k} \boldsymbol{h}_{\text{C},k}^\mathsf{H}$, respectively.
 			At the following points, both algorithms are initialized by the final solutions at the previous point.
@@
 			At the following points (not presented here), the convergence of all three algorithms are much faster thanks to the progressive initialization.
-			Hence, we conclude the proposed algorithms are able to converge fast.
+			Hence, we conclude the proposed algorithms have good convergence performances.
 		\end{subsubsection}
@@
 			\item \emph{\gls{ambc}:} The user decodes both links independently and semi-coherently by treating the other as interference.
-			Hence, the primary achievable rate is approximately\footnote{To provide a preliminary benchmark, we consider the (correlated) scattered signal from finite-input backscatter sources as independent interference from Gaussian sources during primary decoding.}
+			Hence, the primary achievable rate is approximately\footnote{To provide a preliminary benchmark, we consider the (correlated) scattered signal from finite-input backscatter sources as independent interference from Gaussian sources during primary decoding \cite{Long2020a}.}
 			\begin{equation}
@@
 
-		Fig.~\ref{fg:region_comparison} compares the typical achievable rate region/points of RIScatter and those applications.
+		Fig.~\ref{fg:region_comparison} compares the typical achievable rate region/points of RIScatter and above.
 		\emph{First,} we observe both \gls{bbc} and \gls{sr} almost ensure noise-free backscatter transmission when $N$ is sufficiently large.
-		For \gls{bbc} with coherent energy detection, the conditional \gls{pdf} of accumulated receive energy \eqref{eq:energy_distribution_bbc} is more skewed at a large $N$, such that the equivalent \gls{dmtmac} \eqref{eq:dmtmac} becomes more reliable.
-		For \gls{sr} with \gls{sic} and \gls{mrc}, the effective backscatter \gls{snr} is increased by $N$ times and the penalty term $\iota$ becomes insignificant.
-		Such an \gls{sr} only guarantees the primary benefit with a large $N$, but decreases the backscatter symbol rate by a factor of $N$ and requires $N$ \gls{sic} processes to decode each backscatter symbol (tuple).
+		For \gls{bbc} with coherent energy detection, the conditional \gls{pdf} of accumulated receive energy \eqref{eq:energy_distribution_bbc} is more skewed at a large $N$, such that the equivalent \gls{dmtmac} \eqref{eq:dmtmac} has lower error probabilities.
+		For \gls{sic}-based \gls{sr}, the effective backscatter \gls{snr} is increased by $N$ times and the penalty term $\iota$ becomes insignificant.
+		However, the primary rate is only maintained at a very large $N$, which significantly constrains the backscatter \emph{throughput}.
 		\emph{Second,} the average primary rate slightly increases/decreases in the presence of a \gls{ambc}/\gls{ris} node, and the multipath benefit of \gls{sr} is unobvious.
 		This is because the cascaded channel can be orders of magnitude weaker than the direct channel due to the double fading effect.
-		\gls{ris} always ensures constructive superposition of direct and scattered components, while \gls{sr} only creates a quasi-static rich-scattering environment that stochastically enhances the average primary rate.
+		\gls{ris} always ensures constructive superposition of direct and scattered components, while \gls{sr} only creates a quasi-static rich-scattering environment that \emph{stochastically} enhances the average primary rate.
 		When $N$ is moderate, the randomly scattered signals should be modelled as primary interference rather than multipath components, and the \gls{sr} point will move towards the \gls{ambc} point.
-		\emph{Third,} RIScatter enables a flexible primary-backscatter tradeoff by smart input distribution design.
-		In terms of maximum primary achievable rate, RIScatter coincides with \gls{ris} and outperforms the others by deterministic reflection pattern (no need for backscatter detection).
+		\emph{Third,} RIScatter enables a flexible primary-backscatter tradeoff with adaptive input distribution design.
+		In terms of maximum primary achievable rate, RIScatter coincides with \gls{ris} and outperforms the others with passive beamforming provided by deterministic reflection pattern.
 		On the other hand, for a large $N$, the maximum backscatter achievable rate of RIScatter is higher than \gls{ambc} but lower than \gls{bbc} and \gls{sr}.
-		This is because both RIScatter and \gls{ambc} employ semi-coherent (instead of coherent) energy detection in the presence of primary uncertainty, and RIScatter with adaptive channel coding can achieve higher backscatter rate than \gls{ambc} with equiprobable inputs.
-		Importantly, such a practical RIScatter detection is feasible for arbitrary $N$, and using a fast-switching node with smaller $N$ can increase the backscatter throughput per unit time while preserving the dynamic passive beamforming gain on the primary link.
+		This is because both RIScatter and \gls{ambc} (resp.
+\gls{bbc} and \gls{sr}) employ semi-coherent (resp.
+coherent) energy detection, while RIScatter with adaptive channel coding can achieve higher backscatter rate than \gls{ambc} with equiprobable inputs.
+		Importantly, such a practical RIScatter detection is feasible for arbitrary $N$, which unleashes the potential of fast-switching nodes.
+		% , and using a fast-switching node with smaller $N$ can increase the backscatter throughput per unit time while preserving the dynamic passive beamforming gain on the primary link.
 	\end{subsection}
@@
 		The objective of this study is to demonstrate RIScatter nodes can leverage \gls{csi}- and \gls{qos}-adaptive input distribution design to balance backscatter modulation and passive beamforming.
-		For one RIScatter node with $M=4$, we evaluate the \gls{kkt} input distribution\footnote{Since problem \eqref{op:input_distribution} is convex when $K=1$, the \gls{kkt} solution is also global optimal in this example.} at different primary \gls{qos} and present the result in Fig.~\ref{fg:distribution_weights}.
-		At $\rho=0$ where backscatter performance is prioritized, the optimal input distribution is zero on two states and nearly uniform on the other two.
+		For one RIScatter node with $M=4$, we evaluate the \gls{kkt} input distribution\footnote{Since problem \eqref{op:input_distribution} is convex when $K=1$, the \gls{kkt} solution is always global optimal in this case.} at different primary \gls{qos} and present the result in Fig.~\ref{fg:distribution_weights}.
+		At $\rho=0$ where the backscatter performance is prioritized, the optimal input distribution is zero on two states and nearly uniform on the other two.
 		This is because, due to the weak scattered signal, the conditional energy \gls{pdf} under different hypotheses can be closely spaced as illustrated in Fig.~\ref{fg:energy_distribution}.
-		In such cases, the extreme states producing the lowest/highest energy are always assigned with non-zero probability, while the middle ones may not provide enough energy difference and end up unused.
-		At $\rho=1$ where primary performance is prioritized, the optimal input distribution is \num{1} at the state that maximizes the primary \gls{snr} and \num{0} at the others.
+		In such cases, the extreme states producing the lowest/highest energy are always assigned with non-zero probability, while the middle ones may not provide enough energy difference and thus end up unused.
+		At $\rho=1$ where the primary performance is prioritized, the optimal input distribution is \num{1} at the state that maximizes the primary \gls{snr} and \num{0} at the others.
 		That is, the reflection pattern becomes deterministic and the RIScatter node boils down to a discrete \gls{ris} element.
-		Increasing $\rho$ from \num{0} to \num{1} provides a smooth transition from backscatter modulation to passive beamforming, which demonstrates RIScatter unifies \gls{bc} and \gls{ris} from a probabilistic perspective.
+		Increasing $\rho$ from \num{0} to \num{1} provides a smooth transition from backscatter modulation to passive beamforming, which suggests RIScatter unifies \gls{bc} and \gls{ris} from a probabilistic perspective.
 	\end{subsection}
@@
 			\begin{itemize}
-				\item \emph{Cooperation:} Joint encoding using a $K$-dimensional probability array $P_{\mathcal{K}}(x_{m_{\mathcal{K}}})$ by Algorithm \ref{al:input_distribution};
+				\item \emph{Cooperation:} Joint nodes encoding using a $K$-dimensional probability array $P_{\mathcal{K}}(x_{m_{\mathcal{K}}})$ by Algorithm \ref{al:input_distribution};
 				\item \emph{Exhaustion:} Exhaustive search over the $M$-dimensional probability simplex with resolution $\Delta p = \num{e-2}$;
@@
 			\end{itemize}
-			Since scatter cooperation is unavailable for dispersed nodes, to support independent encoding, we also consider these input distribution recovery methods over the joint probability array:
+			For dispersed nodes, joint encoding is inapplicable and we consider these independent input distribution recovery methods (from the joint probability array):
 			\begin{itemize}
@@
 				\item \emph{Decomposition:} Normalized rank-\num{1} \gls{cp} decomposition tensors by \texttt{Tensor Toolbox} \cite{Bader2022};
-				\item \emph{Randomization:} Random search guided by correlation matrix \cite{Calvo2010}.
+				\item \emph{Randomization:} Gaussian randomization-based exhaustive search with the guidance of correlation matrix \cite{Calvo2010}.
+				% guided by correlation matrix \cite{Calvo2010}.
 			\end{itemize}
@@
 			Fig.~\subref*{fg:region_distribution} shows the average achievable rate regions for those designs.
-			\emph{Cooperation} provides the rate region outer bound since joint encoding is generally beneficial for co-located RIScatter nodes.
-			The average rate performance of \emph{Exhaustion} and \emph{\gls{kkt}} coincide with each other, which demonstrates \gls{kkt} input distribution can be reasonably good for a moderate $K$ as stated in Remark \ref{re:input_kkt_distribution}.
+			We observe \emph{Cooperation} provides the outer bound since joint encoding is always beneficial.
+			The \emph{average} rate performance of \emph{Exhaustion} and \emph{\gls{kkt}} completely coincide with each other, demonstrating \gls{kkt} input distribution is favorable for a moderate $K$ as stated in Remark \ref{re:input_kkt_distribution}.
 			\emph{Equiprobable} experiences minor backscatter and major primary rate losses without \gls{csi}- and \gls{qos}-adaptive backscatter encoding.
-			As for the recovery methods, the simple \emph{Marginalization} provides a close result to \emph{\gls{kkt}}, but \emph{Randomization} and \emph{Decomposition} fail our expectations for most channel realizations.
+			Both gaps should become larger when $M$ and $K$ increase.
+			For the recovery methods, the simple \emph{Marginalization} provides a close result to \emph{\gls{kkt}}, but \emph{Randomization} and \emph{Decomposition} fail our expectations for most channel realizations.
 			Those observations emphasize the importance of (joint) adaptive RIScatter encoding and demonstrate the advantages of the proposed \gls{kkt} input distribution design.
@@
 			In the low-$\rho$ regime, the proposed \emph{\gls{pgd}} beamformer significantly outperforms both \gls{mrt} schemes in terms of total backscatter rate.
-			This is because backscatter detection relies on the \emph{relative difference} of accumulated receive energy under different hypotheses.
+			This is because backscatter detection relies on the \emph{relative difference} of accumulated receive energy under different symbol tuples.
 			Such an energy diversity is enhanced by \emph{\gls{pgd}} that effectively exploits backscatter constellation and input distribution knowledge, rather than simply maximizing the direct/ergodic equivalent \gls{snr}.
 			As $\rho$ increases, the primary equivalent \gls{snr} outweighs the backscatter energy difference in \eqref{eq:weighted_sum_mutual_information_explicit}, and \emph{\gls{pgd}} beamformer becomes closer to both \gls{mrt} schemes.
-			At $\rho=1$, \emph{\gls{pgd}} and \emph{E-\gls{mrt}:} boil down to \gls{mrt} towards the deterministic primary equivalent channel as in \gls{ris} literatures \cite{Wu2019}.
+			At $\rho=1$, \emph{\gls{pgd}} and \emph{E-\gls{mrt}} boil down to \gls{mrt} towards the deterministic primary equivalent channel as in \gls{ris} literatures \cite{Wu2019}.
 			Besides, the difference between \emph{E-\gls{mrt}} and \emph{D-\gls{mrt}} can be insignificant for dispersed RIScatter nodes.
-			Those observations prove the proposed \emph{\gls{pgd}} active beamforming design can flexibly improve primary equivalent \gls{snr} and enhance backscatter energy difference to enlarge the achievable rate region for RIScatter.
+			Those observations prove the proposed \emph{\gls{pgd}} active beamforming design can exploit the \gls{csi}, \gls{qos}, and backscatter constellation to balance the primary equivalent \gls{snr} and backscatter energy difference and enlarge the achievable rate region for RIScatter.
 		\end{subsubsection}
@@
 			Fig.~\subref*{fg:region_threshold} reveals the average achievable rate region for those strategies.
-			The distribution-adaptive schemes \emph{\gls{dp}}, \emph{\gls{smawk}} and \emph{Bisection} ensure higher total backscatter rate than the non-adaptive \emph{\gls{ml}}.
+			The distribution-aware schemes \emph{\gls{dp}}, \emph{\gls{smawk}} and \emph{Bisection} ensure higher total backscatter rate than the non-adaptive \emph{\gls{ml}}.
 			This is because the total backscatter rate \eqref{eq:backscatter_mutual_information} is a function of both input distribution and decision regions, and the rate-optimal threshold design heavily depends on input distribution.
-			For example, the backscatter symbol tuples with zero input probability should be assigned with empty decision regions in order to increase the success detection rates of other tuples.
+			For example, the backscatter symbol tuples with zero input probability should be assigned with empty decision regions, in order to increase the success detection chances of other hypotheses.
 			It highlights the importance of joint input distribution and decision threshold design in rate maximization problems.
@@
 			This accounts for the significant primary rate decrease in the low-$\rho$ regime.
-			On the other hand, when the primary link is prioritized, the RIScatter nodes boil down to \gls{ris} elements and enjoy a passive array gain of $N^2$.
+			On the other hand, when the primary link is prioritized, the RIScatter nodes boil down to \gls{ris} elements and enjoy a classic passive array gain of $N^2$.
 		\end{subsubsection}
@@
 			This is because once the scope of reflection coefficient is determined, using denser constellation points may not create enough phase resolution and energy diversity for primary and backscatter links.
-			Due to the maximum amplitude normalization in \eqref{eq:backscatter_modulation}, the average rate region of \num{8}-\gls{qam} with rectangular boundary is smaller than that of \num{4}-\gls{qam} with square boundary, and the inner constellation points with smaller amplitudes are less frequently used.
-			The results in this and previous paragraphs motivate one to replace the high-resolution metamaterial units of RIS by multiple low-order scatter nodes.
+			Due to the maximum amplitude normalization in \eqref{eq:backscatter_modulation}, the average rate region of \num{8}-\gls{qam} (points on rectangle border) is smaller than that of \num{4}-\gls{qam} (points on square vertices), and the inner constellation points with smaller amplitudes are less frequently used.
+			On the other hand, \num{16}-\gls{qam} provides significant higher backscatter rate benefit than primary.
+			It motivates one to use high-resolution metamaterial units as RIScatter nodes.
+			% The results in this and previous paragraphs motivate one to replace the high-resolution metamaterial units by multiple low-order scatter nodes.
 		\end{subsubsection}
@@
 			Fig.~\subref*{fg:region_txs} illustrates the impact of transmit antennas $Q$ on the average performance.
-			Increasing $Q$ enlarges the achievable rate region because \gls{pgd} provides a flexible tradeoff between primary equivalent \gls{snr} and backscatter energy difference.
+			As $Q$ increases, more transmitter-scatter-receiver paths become available to \emph{\gls{pgd}} and their diversity can be further exploited to enhance the primary equivalent \gls{snr} and backscatter energy difference, which leads to a larger achievable rate region.
 			It emphasizes the importance of multi-antenna RIScatter systems and demonstrate the effectiveness of the proposed \gls{pgd} design.
@@
 		\begin{subsubsection}{Symbol Period Ratio}
-			Fig.~\subref*{fg:region_duration} presents how symbol period ratio $N$ affects the achievable rate region.
-			As mentioned above, the conventional \gls{sr} scheme with a large $N$ is generally inefficient while RIScatter with a small $N$ can effectively boost the backscatter throughput per unit time.
-			However, it $N$ requires frequent state change that consumes more power at the passive nodes and involves more detection and re-encoding operations at the user.
+			Fig.~\subref*{fg:region_duration} presents how symbol period ratio $N$ affects the achievable rate region, where the unit of total backscatter rate is bits per primary block (to indicate throughput).
+			Apparently, using a very large $N$ can severely constrain the backscatter throughput, since the gain in energy certainty (by law of large numbers) cannot withstand the loss in gross rate.
 			As $N \to \infty$, RIScatter nodes boil down to \gls{ris} elements with fixed reflection pattern during whole channel block and the total backscatter rate approaches \num{0}.
-			Therefore, we conclude $N$ should be properly designed in a practical RIScatter system based on the data rate requirements, physical constraints at the nodes, and signal processing capability at the user.
+			On the other hand, when $N$ is too small, the equivalent \gls{dmtmac} \eqref{eq:dmtmac} has very high error probabilities and the energy detection can be unreliable.
+			It explains the observation that $N=10$ provides lower backscatter achievable rate than $N=20$, although nodes are encoding at higher gross rate.
+			Therefore, we conclude the design of symbol period ratio $N$ in RIScatter systems should account for multiple factors (e.g., data rate requirements, physical constraints at the nodes, and signal processing capability at the user).
 		\end{subsubsection}
@@
 			It shows the proposed practical semi-coherent backscatter energy detection is suitable for a wide range of noise levels.
-			When $\sigma_v^2$ relatively high, we can choose a longer backscatter symbol period (i.e., larger $N$) to maintain the backscatter \gls{snr} for better detection performance.
+			When $\sigma_v^2$ relatively high, one can choose a larger $N$ to maintain the backscatter \gls{snr} for better detection performance.
 		\end{subsubsection}
@@
 			Fig.~\subref*{fg:region_coverage} shows the relationship between disk radius $r$ and achievable rate region.
-			We observe both primary and backscatter performance are enhanced when nodes are dropped closer to the user.
-			This is because the double fading effect for finite-size scatterers is less severe for near-far setups.
-			In a multi-user RIScatter system with dispersed nodes, each node can be decoded by the nearest user to guarantee uniformly good performance for both links.
+			We observe both primary and backscatter performance are enhanced when nodes are located closer to the user.
+			This is because the double fading effect is less severe for near-far setups.
+			In a multi-user RIScatter system with dispersed nodes, each node may be allocated to the nearest user to guarantee uniformly good performance for both links.
 		\end{subsubsection}
@@
 	The achievable primary-total-backscatter rate region is then studied for a single-user multi-node RIScatter system, where the input distribution, active beamforming, and decision thresholds are iteratively updated.
-	Numerical results not only demonstrated the effectiveness of the proposed algorithms, but also emphasized the importance of adaptive input distribution and cooperative decoding on both primary and backscatter links.
+	Numerical results not only validated the proposed algorithms, but also emphasized the importance of adaptive input distribution and cooperative decoding on both primary and backscatter links.
 
 	One possible direction is to consider backscatter detection over the received signal domain rather than energy domain, where multi-antenna and learning-based approaches can be promising.
-	Another interesting question is how to design RIScatter node and receiver in a multi-user system to fully exploit the dynamic passive beamforming that naturally origins from the backscatter modulation.
+	Another interesting question is how to design RIScatter node and receiver in a multi-user system to fully exploit the dynamic passive beamforming that naturally origins from backscatter modulation.
 	% If one node can be decoded by multiple users, its input distribution may be further adjusted to mimic the multi-beam gain of dynamic passive beamforming \cite{Qiu2022}.

### 2022-12-18 jsac_221218.tex
:construction: Add JSAC version [in progress]

--- 2022-12-18 main.tex
@@
-\documentclass[journal]{IEEEtran}
-% \documentclass[journal,12pt,onecolumn,draftclsnofoot]{IEEEtran}
+% \documentclass[journal]{IEEEtran}
+\documentclass[journal,12pt,onecolumn,draftclsnofoot]{IEEEtran}
 
@@
 \usepackage[subtle]{savetrees}
+\usepackage{setspace}
 \usepackage{siunitx}
@@
 \usepackage{tikz}
+
 % dark mode
@@
 \begin{section}{Introduction}
-	\begin{subsection}{Fundamentals}
+	% \begin{subsection}{Fundamentals}
 	\IEEEPARstart{F}{uture} wireless network is envisioned to provide high throughput, uniform coverage, pervasive connectivity, heterogeneous control, and cognitive intelligence for trillions of portable devices.
@@
 		\subfloat[\gls{mbc}]{
-				\resizebox{0.48\linewidth}{!}{
+			\resizebox{0.25\linewidth}{!}{
 				\input{assets/illustration/mbc.tex}
@@
 		\subfloat[\gls{bbc}]{
-				\resizebox{0.48\linewidth}{!}{
+			\resizebox{0.25\linewidth}{!}{
 				\input{assets/illustration/bbc.tex}
@@
 		}
+		\subfloat[\gls{ambc}]{
+			\resizebox{0.25\linewidth}{!}{
+				\input{assets/illustration/ambc.tex}
+			}
+			\label{fg:ambc}
+		}
 		\\
-			\subfloat[\gls{ambc}]{
-				\resizebox{0.48\linewidth}{!}{
-					\input{assets/illustration/ambc.tex}
-				}
-				\label{fg:ambc}
-			}
 		\subfloat[\gls{sr}]{
-				\resizebox{0.48\linewidth}{!}{
+			\resizebox{0.25\linewidth}{!}{
 				\input{assets/illustration/sr.tex}
@@
 		}
-			\\
 		\subfloat[\gls{ris}]{
-				\resizebox{0.48\linewidth}{!}{
+			\resizebox{0.25\linewidth}{!}{
 				\input{assets/illustration/ris.tex}
@@
 		\subfloat[RIScatter]{
-				\resizebox{0.48\linewidth}{!}{
+			\resizebox{0.25\linewidth}{!}{
 				\input{assets/illustration/riscatter.tex}
@@
 	\end{figure}
-	\end{subsection}
+	% \end{subsection}
 
@@
 		\rowcolors{2}{gray!25}{white}
-		\renewcommand{\arraystretch}{1.4}
+		\scriptsize
 		\begin{tabularx}{\textwidth}{CCCCCC}
@@
 
-	\begin{subsection}{Related Works}
+	% \begin{subsection}{Related Works}
 	Similar to \gls{cr}, active-passive coexisting networks can be classified into commensal, parasitic, and competitive relationships, whose instantaneous rates, power schemes, and outage probabilities were acquired in \cite{Guo2019b,Ding2020}.
@@
 	Relevant literatures also consider either \emph{Gaussian} codebook \cite{Guo2019b,Ding2020,Long2020a,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Hu2021b} that is impractical for low-power nodes, or finite \emph{equiprobable} inputs \cite{Yang2018,Liang2020,Han2021,Zhang2022,Liu2019d,Bereyhi2020,Xu2020b,Zhang2021d,Hua2022,Basar2020,Ma2020a,Yuan2021,Hu2021a} that does not fully exploit the \gls{csi} and signal properties of active-passive coexisting networks.
-	\end{subsection}
-
-	\begin{subsection}{Contributions}
+	% \end{subsection}
+
+	% \begin{subsection}{Contributions}
 	\emph{First,} we propose RIScatter as a novel scatter protocol that unifies \gls{bc} and \gls{ris} by adaptive reflection state (i.e., backscatter input) distribution design.
@@
 	8) distribution-aware backscatter detectors provide higher backscatter rate than the conventional \gls{ml} detector.
-	\end{subsection}
+	% \end{subsection}
 
@@
 \begin{section}{RIScatter}
-	\begin{subsection}{Concepts}
+	% \begin{subsection}{Concepts}
 	We propose RIScatter in Fig.~\subref*{fg:riscatter} as a generalization of \gls{bc} and \gls{ris}, which involves coexisting active primary and passive backscatter links in a flexible and mutualistic manner.
@@
 		\subfloat[Reflection State Distribution]{
-				\resizebox{0.8\columnwidth}{!}{
+			\resizebox{0.32\columnwidth}{!}{
 				\input{assets/illustration/input_distribution.tex}
@@
 		}
-			\\
 		\subfloat[Reflection Pattern]{
-				\resizebox{0.8\columnwidth}{!}{
+			\resizebox{0.32\columnwidth}{!}{
 				\input{assets/illustration/time_structure.tex}
@@
 
-		% \begin{remark}
-		% 	Active-passive coexisting networks involve a double modulation where the primary and backscatter symbols of different period are superimposed by multiplication coding.
-		% 	The reflection pattern not only encodes the backscatter message, but also affects the channel for primary link.
-		% 	Therefore, backscatter detection under primary uncertainty can be viewed as part of primary channel training, and novel decoding strategies apart from \gls{sic}%
-		% 	\footnote{
-		% 		Superposition coding and \gls{sic} was originally proposed to achieve the capacity vertices of Gaussian \gls{mac}.
-		% 		For active-passive coexisting networks, \gls{sic} not only fails to utilize the multiplication coding/double modulation, but also requires $N$ re-encoding, precoding and subtraction with a time-domain \gls{mrc} during each backscatter block.
-		% 	}
-		% 	is desired for RIScatter.
-		% \end{remark}
-
 	% ? Add an illustration here if space allows
@@
 		\centering
-			\resizebox{0.8\columnwidth}{!}{
+		\resizebox{0.4\columnwidth}{!}{
 			\input{assets/illustration/energy_distribution.tex}
@@
 			\gls{pdf} of accumulated receive energy per backscatter block conditioned on different reflection state hypotheses.
-				$z$, $t$, $\mathcal{H}$ and $\mathcal{R}$ denote the accumulated receive energy, decision threshold, reflection state hypothesis, and decision regions, respectively.
+			% $z$, $t$, $\mathcal{H}$ and $\mathcal{R}$ denote the accumulated receive energy, decision threshold, reflection state hypothesis, and decision regions, respectively.
 		}
@@
 	3) preserves backscatter modulation and passive beamforming at smaller $N$ for potentially higher backscatter throughput.
-	\end{subsection}
-
-	\begin{subsection}{System Model}
+	% \end{subsection}
+
+	% \begin{subsection}{System Model}
 	\begin{figure}[!t]
 		\centering
-			\def\svgwidth{0.7\columnwidth}
+		\def\svgwidth{0.4\columnwidth}
 		\footnotesize{
@@
 	Let $x_k \in \mathcal{X} \triangleq \{c_1,\ldots,c_M\}$ be the coded backscatter symbol of node $k$ and $x_{\mathcal{K}} \triangleq (x_1,\ldots,x_K)$ be the backscatter symbol tuple of all nodes.
-		Due to double modulation, the primary equivalent channel is a function of backscatter symbol tuple\footnote{\eqref{eq:equivalent_channel_bc} and \eqref{eq:equivalent_channel_ris} are often used in \gls{bc} and \gls{ris} literatures, respectively.}
-		\begin{subequations}
+	Due to double modulation, the primary equivalent channel is a function of backscatter symbol tuple
+	\begin{equation}
+		\boldsymbol{h}_{\text{E}}^\mathsf{H}(x_{\mathcal{K}}) \triangleq \boldsymbol{h}_{\text{D}}^\mathsf{H} + \sum_{k} \alpha_k \boldsymbol{h}_{\text{C},k}^\mathsf{H} x_k = \boldsymbol{h}_{\text{D}}^\mathsf{H} + \boldsymbol{x}^\mathsf{H} \mathrm{diag}(\boldsymbol{\alpha}) \boldsymbol{H}_{\text{C}},
 		\label{eq:equivalent_channel}
-			\begin{align}
-				\boldsymbol{h}_{\text{E}}^\mathsf{H}(x_{\mathcal{K}})
-				 & \triangleq \boldsymbol{h}_{\text{D}}^\mathsf{H} + \sum_{k} \alpha_k \boldsymbol{h}_{\text{C},k}^\mathsf{H} x_k \label{eq:equivalent_channel_bc}                    \\
-				 & = \boldsymbol{h}_{\text{D}}^\mathsf{H} + \boldsymbol{x}^\mathsf{H} \mathrm{diag}(\boldsymbol{\alpha}) \boldsymbol{H}_{\text{C}}, \label{eq:equivalent_channel_ris}
-			\end{align}
-		\end{subequations}
+	\end{equation}
 	where $\alpha_k \in \mathbb{I}$ is the common amplitude scattering ratio of node $k$, $\boldsymbol{\alpha} \triangleq [\alpha_1,\ldots,\alpha_K]^\mathsf{T} \in \mathbb{I}^{K}$, $\boldsymbol{x} \triangleq [x_1,\ldots,x_K]^\mathsf{H} \in \mathcal{X}^{K}$, and $\boldsymbol{H}_{\text{C}} \triangleq [\boldsymbol{h}_{\text{C},1},\ldots,\boldsymbol{h}_{\text{C},K}]^\mathsf{H} \in \mathbb{C}^{K \times Q}$.
@@
 	\label{st:system_model}
-	\end{subsection}
-
-	\begin{subsection}{Achievable Rates}
+	% \end{subsection}
+
+	% \begin{subsection}{Achievable Rates}
 	Denote the probability of node $k$ choosing reflection state $m_k$ as $P_k(x_{m_k})$, and let $\boldsymbol{p}_k \triangleq [P_k(c_1),\ldots,P_k(c_M)]^\mathsf{T} \in \mathbb{I}^{M}$.
@@
 	\label{st:information_theory}
-	\end{subsection}
+	% \end{subsection}
 	\label{st:riscatter}
@@
 		\addConstraint{\lVert \boldsymbol{w} \rVert^2}{\le P}{\label{co:transmit_power}}
-		\addConstraint{t_{l-1}}{\le t_l,}{\quad \forall l}{\label{co:sequential_threshold}}
-		\addConstraint{\boldsymbol{t}}{\ge \boldsymbol{0}.}{\label{co:nonnegative_threshold}}
+		\addConstraint{0}{\le t_{l-1}}{\le t_l,}{\quad \forall l.}{\label{co:sequential_threshold}}
+		% \addConstraint{\boldsymbol{t}}{\ge \boldsymbol{0}.}{\label{co:nonnegative_threshold}}
 	\end{maxi!}
@@
 		\begin{equation}
-			\begin{gathered}
-				Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr) = \frac{\int_{{t_{l-1}}/{\sigma_{m_{\mathcal{K}}}^2}}^{{t_l}/{\sigma_{m_{\mathcal{K}}}^2}} z^{N-1} \exp(-z) \, d z}{(N-1)!}\\
-				= \exp \Bigl(-\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2}\Bigr) \sum_{n=0}^{N-1} \frac{\bigl(\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2}\bigr)^n}{n!} - \exp \Bigl(-\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr) \sum_{n=0}^{N-1} \frac{\bigl(\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\bigr)^n}{n!}.
-			\end{gathered}
+			% \begin{gathered}
+			% 	Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr) = \frac{\int_{{t_{l-1}}/{\sigma_{m_{\mathcal{K}}}^2}}^{{t_l}/{\sigma_{m_{\mathcal{K}}}^2}} z^{N-1} \exp(-z) \, d z}{(N-1)!}\\
+			% 	= \exp \Bigl(-\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2}\Bigr) \sum_{n=0}^{N-1} \frac{\bigl(\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2}\bigr)^n}{n!} - \exp \Bigl(-\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr) \sum_{n=0}^{N-1} \frac{\bigl(\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\bigr)^n}{n!}.
+			% \end{gathered}
+			Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr) = \frac{\int_{{t_{l-1}}/{\sigma_{m_{\mathcal{K}}}^2}}^{{t_l}/{\sigma_{m_{\mathcal{K}}}^2}} z^{N-1} \exp(-z) \, d z}{(N-1)!} = \exp \Bigl(-\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2}\Bigr) \sum_{n=0}^{N-1} \frac{\bigl(\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2}\bigr)^n}{n!} - \exp \Bigl(-\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr) \sum_{n=0}^{N-1} \frac{\bigl(\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\bigr)^n}{n!}.
 			\label{eq:regularized_incomplete_gamma}
@@
 		\end{equation}
-		On top of \eqref{eq:regularized_incomplete_gamma} and \eqref{eq:regularized_incomplete_gamma_gradient}, we explicitly express the objective function \eqref{ob:active_beamforming} and its gradient as \eqref{eq:weighted_sum_mutual_information_explicit} and \eqref{eq:weighted_sum_mutual_information_gradient} at the end of page \pageref{eq:weighted_sum_mutual_information_explicit}, respectively.
-		\begin{figure*}[!b]
-			\hrule
-			\begin{equation}
-				I(x_{\mathcal{K}})=\sum_{m_{\mathcal{K}}}P_{\mathcal{K}}(x_{m_{\mathcal{K}}})\Biggl(\rho\log\Bigl(1+\frac{\lvert\boldsymbol{h}_{\text{E}}^\mathsf{H}(x_{m_{\mathcal{K}}})\boldsymbol{w}\rvert^2}{\sigma_v^2}\Bigr)+(1-\rho)\sum_l Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr) \log \frac{Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr)}{\sum_{m_{\mathcal{K}}'} P_{\mathcal{K}}(x_{m_{\mathcal{K}}'}) Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}'}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}'}^2}\Bigr)}\Biggr)
+		On top of \eqref{eq:regularized_incomplete_gamma} and \eqref{eq:regularized_incomplete_gamma_gradient}, we explicitly express the objective function \eqref{ob:active_beamforming} and its gradient as
+		\begin{align}
+			I(x_{\mathcal{K}})
+			 & =\sum_{m_{\mathcal{K}}}P_{\mathcal{K}}(x_{m_{\mathcal{K}}})\Biggl(\rho\log\Bigl(1+\frac{\lvert\boldsymbol{h}_{\text{E}}^\mathsf{H}(x_{m_{\mathcal{K}}})\boldsymbol{w}\rvert^2}{\sigma_v^2}\Bigr)                                                                                                                                                                                                                \\
+			 & \qquad + (1-\rho)\sum_l Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr) \log \frac{Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr)}{\sum_{m_{\mathcal{K}}'} P_{\mathcal{K}}(x_{m_{\mathcal{K}}'}) Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}'}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}'}^2}\Bigr)}\Biggr),
 			\label{eq:weighted_sum_mutual_information_explicit}
-			\end{equation}
+		\end{align}
 		\begin{align}
@@
 			 & = \sum_{m_{\mathcal{K}}}P_{\mathcal{K}}(x_{m_{\mathcal{K}}})\Biggl(\rho\frac{\boldsymbol{h}_{\text{E}}(x_{m_{\mathcal{K}}})\boldsymbol{h}_{\text{E}}^\mathsf{H}(x_{m_{\mathcal{K}}})\boldsymbol{w}}{\sigma_{m_{\mathcal{K}}}^2}+(1-\rho)\sum_l\biggl(\log\frac{Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr)}{\sum_{m_{\mathcal{K}}'}P_{\mathcal{K}}(x_{m_{\mathcal{K}}'})Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}'}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}'}^2}\Bigr)}+1\biggr)\nonumber                                                              \\
-				 & \qquad \times \nabla_{\boldsymbol{w}^*} Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr)-\frac{Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr)\sum_{m_{\mathcal{K}}'}P_{\mathcal{K}}(x_{m_{\mathcal{K}}'})\nabla_{\boldsymbol{w}^*}Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}'}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}'}^2}\Bigr)}{\sum_{m_{\mathcal{K}}'}P_{\mathcal{K}}(x_{m_{\mathcal{K}}'})Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}'}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}'}^2}\Bigr)}\Biggr)
+			 & \qquad \times \nabla_{\boldsymbol{w}^*} Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr)-\frac{Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr)\sum_{m_{\mathcal{K}}'}P_{\mathcal{K}}(x_{m_{\mathcal{K}}'})\nabla_{\boldsymbol{w}^*}Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}'}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}'}^2}\Bigr)}{\sum_{m_{\mathcal{K}}'}P_{\mathcal{K}}(x_{m_{\mathcal{K}}'})Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}'}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}'}^2}\Bigr)}\Biggr).
 			\label{eq:weighted_sum_mutual_information_gradient}
 		\end{align}
-		\end{figure*}
 		They allows problem \eqref{op:active_beamforming} to be solved by the \gls{pgd} method, where any unregulated beamformer $\bar{\boldsymbol{w}}$ can be projected onto the feasible domain of average transmit power constraint \eqref{co:transmit_power} by
@@
 			{\scriptstyle{\boldsymbol{t}}}{I(x_{\mathcal{K}})}{\label{op:decision_threshold}}{\label{ob:decision_threshold}}
-			\addConstraint{\eqref{co:sequential_threshold},\eqref{co:nonnegative_threshold},}
+			% \addConstraint{\eqref{co:sequential_threshold},\eqref{co:nonnegative_threshold},}
+			\addConstraint{\eqref{co:sequential_threshold},}
 		\end{maxi!}
@@
 			\centering
-			\resizebox{0.9\columnwidth}{!}{
+			\resizebox{0.5\columnwidth}{!}{
 				\input{assets/illustration/discrete_outputs.tex}
@@
 		\end{equation}
-		which is generally suboptimal for problem \eqref{op:decision_threshold} except when all nodes are with equiprobable inputs.
+		which is suboptimal for problem \eqref{op:decision_threshold} except when all nodes are with equiprobable inputs.
 	\end{subsection}
@@
 				\centering
-				\resizebox{0.75\columnwidth}{!}{
+				\resizebox{0.4\columnwidth}{!}{
 					\input{assets/simulation/wsr_convergence.tex}
@@
 			\centering
-			\resizebox{0.65\columnwidth}{!}{
+			\resizebox{0.4\columnwidth}{!}{
 				\input{assets/simulation/region_comparison.tex}
@@
 
-	\begin{subsection}{Input Distribution under Different \gls{qos}}
+	\begin{subsection}{Input Distribution under Different QoS}
 		\begin{figure}[!t]
 			\centering
-			\resizebox{0.65\columnwidth}{!}{
+			\resizebox{0.4\columnwidth}{!}{
 				\input{assets/simulation/distribution_weights.tex}
@@
 			\subfloat[Input Distribution, $Q=1$\label{fg:region_distribution}]{
-				\resizebox{0.6\columnwidth}{!}{
+				\resizebox{0.32\columnwidth}{!}{
 					\input{assets/simulation/region_distribution.tex}
@@
 			}
-			\\
 			\subfloat[Active Beamforming, $Q=4$\label{fg:region_beamforming}]{
-				\resizebox{0.48\columnwidth}{!}{
+				\resizebox{0.32\columnwidth}{!}{
 					\input{assets/simulation/region_beamforming.tex}
@@
 			\subfloat[Decision Threshold, $Q=4$\label{fg:region_threshold}]{
-				\resizebox{0.48\columnwidth}{!}{
+				\resizebox{0.32\columnwidth}{!}{
 					\input{assets/simulation/region_threshold.tex}
@@
 			\subfloat[RIScatter Nodes\label{fg:region_tags}]{
-				\resizebox{0.48\columnwidth}{!}{
+				\resizebox{0.32\columnwidth}{!}{
 					\input{assets/simulation/region_tags.tex}
@@
 			\subfloat[Input States\label{fg:region_states}]{
-				\resizebox{0.48\columnwidth}{!}{
+				\resizebox{0.32\columnwidth}{!}{
 					\input{assets/simulation/region_states.tex}
@@
 			}
+			\subfloat[Transmit Antennas\label{fg:region_txs}]{
+				\resizebox{0.32\columnwidth}{!}{
+					\input{assets/simulation/region_txs.tex}
+				}
+			}
 			\\
-			\subfloat[Transmit Antennas\label{fg:region_txs}]{
-				\resizebox{0.48\columnwidth}{!}{
-					\input{assets/simulation/region_txs.tex}
-				}
-			}
 			\subfloat[Symbol Period Ratio\label{fg:region_duration}]{
-				\resizebox{0.48\columnwidth}{!}{
+				\resizebox{0.32\columnwidth}{!}{
 					\input{assets/simulation/region_duration.tex}
@@
 			}
-			\\
 			\subfloat[Average Noise Power\label{fg:region_noise}]{
-				\resizebox{0.48\columnwidth}{!}{
+				\resizebox{0.32\columnwidth}{!}{
 					\input{assets/simulation/region_noise.tex}
@@
 			\subfloat[Disk Radius\label{fg:region_coverage}]{
-				\resizebox{0.48\columnwidth}{!}{
+				\resizebox{0.32\columnwidth}{!}{
 					\input{assets/simulation/region_coverage.tex}
@@
 			\label{eq:input_kkt_condition_original}
-			\begin{equation}
-				- \nabla_{P_k^\star(x_{m_k})} I^\star(x_{\mathcal{K}}) + \nu_k^\star - \lambda_{k,m_k}^\star = 0,
-			\end{equation}
-			\begin{equation}
-				\lambda_{k,m_k}^\star = 0, \quad P_k^\star(x_{m_k}) > 0,
-			\end{equation}
-			\begin{equation}
+			\begin{gather}
+				- \nabla_{P_k^\star(x_{m_k})} I^\star(x_{\mathcal{K}}) + \nu_k^\star - \lambda_{k,m_k}^\star = 0, \\
+				\lambda_{k,m_k}^\star = 0, \quad P_k^\star(x_{m_k}) > 0, \\
 				\lambda_{k,m_k}^\star \ge 0, \quad P_k^\star(x_{m_k}) = 0,
-			\end{equation}
+			\end{gather}
 		\end{subequations}
@@
 		We first prove sequence \eqref{eq:input_kkt_solution} is non-decreasing in weighted sum mutual information.
-		Let $P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) = \prod_{q \in \mathcal{K}} P_q(x_{m_q})$ and $P_{\mathcal{K}}'(x_{m_{\mathcal{K}}}) = P_k'(x_{m_k}) \prod_{q \in \mathcal{K} \setminus \{k\}} P_q(x_{m_q})$ be two probability distributions with potentially different marginal for tag $k$ at state $m_k$, and define an intermediate function $J \bigl( P_{\mathcal{K}}(x_{m_{\mathcal{K}}}),P_{\mathcal{K}}'(x_{m_{\mathcal{K}}}) \bigr)$ as \eqref{eq:intermediate_information_function} at the end of page \pageref{eq:intermediate_information_function}.
-		\begin{figure*}[!b]
-			\hrule
-			\begin{equation}
-				J \bigl( P_{\mathcal{K}}(x_{m_{\mathcal{K}}}),P_{\mathcal{K}}'(x_{m_{\mathcal{K}}}) \bigr) \triangleq \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}})
-				\Biggl( \rho \log \Bigl(1 + \frac{\lvert \boldsymbol{h}_{\text{E}}^\mathsf{H}(x_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_v^2}\Bigr) + (1 - \rho) \sum_{m_{\mathcal{K}}'} P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}}) \log \frac{P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}}) P_{\mathcal{K}}'(x_{m_{\mathcal{K}}})}{P_{\mathcal{K}}'(\hat{x}_{m_{\mathcal{K}}'}) P_{\mathcal{K}}(x_{m_{\mathcal{K}}})} \Biggr).
+		Let $P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) = \prod_{q \in \mathcal{K}} P_q(x_{m_q})$ and $P_{\mathcal{K}}'(x_{m_{\mathcal{K}}}) = P_k'(x_{m_k}) \prod_{q \in \mathcal{K} \setminus \{k\}} P_q(x_{m_q})$ be two probability distributions with potentially different marginal for tag $k$ at state $m_k$, and define an intermediate function $J \bigl( P_{\mathcal{K}}(x_{m_{\mathcal{K}}}),P_{\mathcal{K}}'(x_{m_{\mathcal{K}}}) \bigr)$ as
+		\begin{align}
+			J \bigl( P_{\mathcal{K}}(x_{m_{\mathcal{K}}}),P_{\mathcal{K}}'(x_{m_{\mathcal{K}}}) \bigr)
+			 & \triangleq \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}})
+			\Biggl( \rho \log \Bigl(1 + \frac{\lvert \boldsymbol{h}_{\text{E}}^\mathsf{H}(x_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_v^2}\Bigr)                                                                                                                                                    \\
+			 & \qquad + (1 - \rho) \sum_{m_{\mathcal{K}}'} P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}}) \log \frac{P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}}) P_{\mathcal{K}}'(x_{m_{\mathcal{K}}})}{P_{\mathcal{K}}'(\hat{x}_{m_{\mathcal{K}}'}) P_{\mathcal{K}}(x_{m_{\mathcal{K}}})} \Biggr).
 			\label{eq:intermediate_information_function}
-			\end{equation}
-		\end{figure*}
+		\end{align}
 		It is straightforward to verify $J \bigl( P_{\mathcal{K}}(x_{m_{\mathcal{K}}}),P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) \bigr) = I(x_{\mathcal{K}})$ and $J \bigl( P_{\mathcal{K}}(x_{m_{\mathcal{K}}}),P_{\mathcal{K}}'(x_{m_{\mathcal{K}}}) \bigr)$ is a concave function for a fixed $P_{\mathcal{K}}'(x_{m_{\mathcal{K}}})$.
@@
 		where $i_k \ne m_k$ is the reference state and
-		\begin{align}
-			S_k'(x_{m_k})
-			 & \triangleq I_k'(x_{m_k}) + (1 - \rho) \sum_{m_{\mathcal{K} \setminus \{k\}}} P_{\mathcal{K} \setminus \{k\}}(x_{m_{\mathcal{K} \setminus \{k\}}})\nonumber \\
-			 & \quad \times \sum_{m_{\mathcal{K}}'} P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}}) \log P_{\mathcal{K}}'(x_{m_{\mathcal{K}}}).
-		\end{align}
+		\begin{equation}
+			S_k'(x_{m_k}) \triangleq I_k'(x_{m_k}) + (1 - \rho) \sum_{m_{\mathcal{K} \setminus \{k\}}} P_{\mathcal{K} \setminus \{k\}}(x_{m_{\mathcal{K} \setminus \{k\}}}) \sum_{m_{\mathcal{K}}'} P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}}) \log P_{\mathcal{K}}'(x_{m_{\mathcal{K}}}).
+		\end{equation}
 		Evidently, $\forall m_k \ne i_k$, \eqref{eq:optimal_intermediate_information_condition} boils down to
@@
 				 & \triangleq I(x_{\mathcal{K}}) - J \bigl( P_{\mathcal{K}}(x_{m_{\mathcal{K}}}),P_{\mathcal{K}}'(x_{m_{\mathcal{K}}}) \bigr)                                                                                                                                                                                                                                             \\
-				 & = (1 - \rho) \sum_{m_k} \frac{P_k'(x_{m_k}) f_k'(x_{m_k})}{\sum_{m_k'} P_k'(x_{m_k'}) f_k'(x_{m_k'})} \sum_{m_{\mathcal{K}}''} P(\hat{x}_{m_{\mathcal{K}}''}|x_{m_k})\nonumber                              \\
-				 & \quad \times \log \frac{\sum_{m_k'} P_k'(x_{m_k'}) P(\hat{x}_{m_{\mathcal{K}}''}|x_{m_k'}) f_k'(x_{m_k})}{\sum_{m_k'} P_k'(x_{m_k'}) P(\hat{x}_{m_{\mathcal{K}}''}|x_{m_k'}) f_k'(x_{m_k'})}                \\
-				 & \ge (1 - \rho) \sum_{m_k} \frac{P_k'(x_{m_k}) f_k'(x_{m_k})}{\sum_{m_k'} P_k'(x_{m_k'}) f_k'(x_{m_k'})} \sum_{m_{\mathcal{K}}''} P(\hat{x}_{m_{\mathcal{K}}''}|x_{m_k})\nonumber                            \\
-				 & \quad \times \Biggl( 1 - \frac{\sum_{m_k'} P_k'(x_{m_k'}) P(\hat{x}_{m_{\mathcal{K}}''}|x_{m_k'}) f_k'(x_{m_k'})}{\sum_{m_k'} P_k'(x_{m_k'}) P(\hat{x}_{m_{\mathcal{K}}''}|x_{m_k'}) f_k'(x_{m_k})} \Biggr) \\
+				 & = (1 - \rho) \sum_{m_k} \frac{P_k'(x_{m_k}) f_k'(x_{m_k})}{\sum_{m_k'} P_k'(x_{m_k'}) f_k'(x_{m_k'})} \sum_{m_{\mathcal{K}}''} P(\hat{x}_{m_{\mathcal{K}}''}|x_{m_k}) \log \frac{\sum_{m_k'} P_k'(x_{m_k'}) P(\hat{x}_{m_{\mathcal{K}}''}|x_{m_k'}) f_k'(x_{m_k})}{\sum_{m_k'} P_k'(x_{m_k'}) P(\hat{x}_{m_{\mathcal{K}}''}|x_{m_k'}) f_k'(x_{m_k'})}                  \\
+				 & \ge (1 - \rho) \sum_{m_k} \frac{P_k'(x_{m_k}) f_k'(x_{m_k})}{\sum_{m_k'} P_k'(x_{m_k'}) f_k'(x_{m_k'})} \sum_{m_{\mathcal{K}}''} P(\hat{x}_{m_{\mathcal{K}}''}|x_{m_k}) \Biggl( 1 - \frac{\sum_{m_k'} P_k'(x_{m_k'}) P(\hat{x}_{m_{\mathcal{K}}''}|x_{m_k'}) f_k'(x_{m_k'})}{\sum_{m_k'} P_k'(x_{m_k'}) P(\hat{x}_{m_{\mathcal{K}}''}|x_{m_k'}) f_k'(x_{m_k})} \Biggr) \\
 				 & = 0,
@@
 	\end{subsection}
-
-	% \begin{subsection}{Proof of Proposition \ref{pr:threshold}}
-	% 	Since $L$ input letters are with non-zero probability and $x \to z \to \hat{x}$ formulates a Markov chain, we need $L$ non-empty decision regions and at least $L+1$ distinct thresholds (including \num{0} and $\infty$) to minimize the distortion between source and decision.
-	% 	On the other hand, the optimal decision regions are apparently empty for those unused letters.
-
-	% 	Suppose the optimal number of thresholds is $S+1$ where $S \ge L$.
-	% 	Let $\boldsymbol{t} \triangleq [t_0,\ldots,t_S]^\mathsf{T} \in \mathbb{R}_{+}^{(S+1)}$ be the optimal threshold vector where $t_{s-1} < t_s$, $\forall s \in \mathcal{S} \triangleq \{1,\ldots,S\}$.
-	% 	Since the optimal decision region for any letter may consist of multiple partitions, without loss of generality, we assume the mapping from threshold vector to decision region $l' \in \mathcal{L} \triangleq \{1,\ldots,L\}$ is given by $\mathcal{R}_{l'} = \bigcup_{s \equiv l' \pmod L} [t_{s-1},t_s)$.
-	% 	\begin{footnote}
-	% 		The proof holds for any valid mapping from threshold vector to decision regions, and we consider this specific case for the ease of presentation.
-	% 	\end{footnote}
-	% 	The threshold optimization problem is
-	% 	\begin{maxi!}
-	% 		{\scriptstyle{\boldsymbol{t}}}{I_{\text{B}}(x;\hat{x})}{\label{op:decision_threshold}}{\label{ob:backscatter_mutual_information}}
-	% 		\addConstraint{t_{s-1}}{< t_s,}{\quad \forall s \in \mathcal{S}.}{\label{co:strict_inequality}}
-	% 	\end{maxi!}
-
-	% 	Problem \eqref{op:decision_threshold} is intricate due to the strict inequality constraint \eqref{co:strict_inequality}.
-	% 	Following \cite{Nguyen2020}, we first relax it to the convex counterpart, then discard the solutions that violate any original constraint.
-	% 	The Lagrangian function for the relaxed problem is
-	% 	\begin{equation}
-	% 		L = - I_{\text{B}}(x;\hat{x}) + \sum_{s \in \mathcal{S}} \mu_s (t_{s-1} - t_s),
-	% 	\end{equation}
-	% 	where $\mu_s$ is the Lagrange multiplier associated with the non-strict version of \eqref{co:strict_inequality}.
-	% 	The \gls{kkt} conditions on the optimal primal and dual solutions are, $\forall s \in \mathcal{S}$,
-	% 	\begin{subequations}
-	% 		\label{eq:kkt_thresholding}
-	% 		\begin{equation}
-	% 			- \nabla_{t_s^\star} I^\star_{\text{B}}(x;\hat{x}) + \mu_{s-1}^\star - \mu_s^\star = 0,
-	% 			\label{eq:stationarity}
-	% 		\end{equation}
-	% 		\begin{equation}
-	% 			\mu_s^\star \ge 0,
-	% 			\label{eq:dual_feasibility}
-	% 		\end{equation}
-	% 		\begin{equation}
-	% 			\mu_s^\star (t_{s-1}^\star - t_s^\star) = 0.
-	% 			\label{eq:complementary_slackness}
-	% 		\end{equation}
-
-	% 	\end{subequations}
-	% 	Due to the strict inequality constraint \eqref{co:strict_inequality}, conditions \eqref{eq:dual_feasibility} and \eqref{eq:complementary_slackness} together imply $\mu_s^\star = 0$, $\forall s \in \mathcal{S}$.
-	% 	Besides, it is trivial to conclude $t_0^\star = 0$ for energy-based detection.
-	% 	As such, the necessary optimality conditions for problem \eqref{op:decision_threshold}, $\forall s \in \mathcal{S}$,
-	% 	\begin{equation}
-	% 		\nabla_{t_{s}^\star} I^\star_{\text{B}}(x;\hat{x}) = 0,
-	% 	\end{equation}
-	% 	which can be explicitly written as, $\forall s \equiv l' \pmod L$,
-	% 	\begin{equation}
-	% 		\sum_l P(x_l) \frac{(t_s^\star)^{N-1} \exp{-t_s^\star/\sigma_l^2}}{\sigma_l^{2N} (N-1)!} \log \frac{P(x_l|\hat{x}_{l'+1})}{P(x_l|\hat{x}_{l'})} = 0,
-	% 		\label{eq:kkt_threshold_explicit}
-	% 	\end{equation}
-
-	% 	According to \cite{He2021}, the optimal backward channel quantizer is convex and separates each pair of posterior distribution by a hyperplane.
-	% 	It implies, for a given output letter $l'$, the sequence $\{\log {P(x_l|\hat{x}_{l'+1})}/{P(x_l|\hat{x}_{l'})}\}_{l \in \mathcal{L}}$ changes sign exactly once.
-	% 	We notice the left-hand side of \eqref{eq:kkt_threshold_explicit} is a generalized Dirichlet polynomial, and by Descartes' rule of signs \cite{Jameson2006}, has at most one positive solution.
-	% 	% TODO
-	% 	In other words, starting from $t_0^\star$, each optimal decision region requires at most one additional distinct threshold, and we have $S \le L$.
-	% 	Therefore, we conclude $S = L$ and the proof is completed.
-	% 	\qedsymbol
-	% 	\label{ap:threshold}
-	% \end{subsection}
 \end{appendix}
@@
 \bibliographystyle{IEEEtran}
-\bibliography{library.bib}
+\bibliography{IEEEabrv,library.bib}
 \end{document}

### 2022-12-18 jsac_221218.tex
:triangular_flag_on_post: JSAC and arXiv 221218

@@
 \usepackage{mathtools}
-\usepackage{microtype}
 \usepackage[short]{optidef}
@@
 
+% page limit hacks
+% \usepackage[top=1cm, bottom=1cm, left=1cm, right=1cm]{geometry}
+\abovedisplayskip=1mm
+\belowdisplayskip=1mm
+\abovedisplayshortskip=1mm
+\belowdisplayshortskip=1mm
+\setlength{\jot}{0.1mm}
+\setlength{\floatsep}{1mm}
+\setlength{\textfloatsep}{1mm}
+\setlength{\intextsep}{1mm}
+\setlength{\skip\footins}{1mm}
+\theoremstyle{remark}
+
 % dark mode
@@
 \renewcommand{\fnum@algorithm}{\fname@algorithm{} \thealgorithm:}
+\newcommand\setalgorithmcaptionfont[1]{%
+	\let\my@floatc@ruled\floatc@ruled          % save \floatc@ruled
+	\def\floatc@ruled{%
+		\global\let\floatc@ruled\my@floatc@ruled % restore \floatc@ruled
+		#1\floatc@ruled}}
 \makeatother
+
 \algrenewcommand{\algorithmicrequire}{\textbf{Input:}}
@@
 	The key principle in RIScatter is to render the probability distribution of reflection states (i.e., backscatter channel input) as a joint function of the information source, \gls{csi}, and \gls{qos} of the coexisting active primary and passive backscatter links.
-	This enables RISscatter to softly bridge, generalize, and outperform \gls{bc} and \gls{ris}; boil down to either under specific input distribution; or evolve in a mixed form for heterogeneous traffic control and universal hardware design.
+	This enables RIScatter to softly bridge, generalize, and outperform \gls{bc} and \gls{ris}; boil down to either under specific input distribution; or evolve in a mixed form for heterogeneous traffic control and universal hardware design.
 	For a single-user multi-node RIScatter network, we characterize the achievable primary-(total-)backscatter rate region by optimizing the input distribution at the nodes, the active beamforming at the \gls{ap}, and the backscatter detection regions at the user.
@@
 \end{abstract}
+
+\begin{IEEEkeywords}
+	Backscatter communication, reconfigurable intelligent surface, ambient backscatter communication, symbiotic radio.
+\end{IEEEkeywords}
 
@@
 	Those \gls{bc} applications employ scatter nodes as pure information sources, and the active primary transmission (if it exists) can be influenced by the randomness of backscatter modulation.
-	On the other hand, \gls{ris} in Fig.~\ref{fg:ris} is a smart planar signal reflector that consists of numerous compact passive elements with adjustable amplitude and phase responses, whose reflection pattern over time is deterministic and adaptively optimized based on \gls{csi}.
+	On the other hand, \gls{ris} in Fig.~\subref*{fg:ris} is a smart planar signal reflector that consists of numerous compact passive elements with adjustable amplitude and phase responses, whose reflection pattern over time is deterministic and adaptively optimized based on \gls{csi}.
 	\gls{ris} smartly reflects the surrounding \gls{rf} waves to customize the wireless propagation environment for signal enhancement, interference suppression, scattering enrichment and non-line-of-sight bypassing \cite{Wu2021b}.
@@
 	Let $x_k \in \mathcal{X} \triangleq \{c_1,\ldots,c_M\}$ be the coded backscatter symbol of node $k$ and $x_{\mathcal{K}} \triangleq (x_1,\ldots,x_K)$ be the backscatter symbol tuple of all nodes.
-	Due to double modulation, the primary equivalent channel is a function of backscatter symbol tuple
-	\begin{equation}
-		\boldsymbol{h}_{\text{E}}^\mathsf{H}(x_{\mathcal{K}}) \triangleq \boldsymbol{h}_{\text{D}}^\mathsf{H} + \sum_{k} \alpha_k \boldsymbol{h}_{\text{C},k}^\mathsf{H} x_k = \boldsymbol{h}_{\text{D}}^\mathsf{H} + \boldsymbol{x}^\mathsf{H} \mathrm{diag}(\boldsymbol{\alpha}) \boldsymbol{H}_{\text{C}},
+	Due to double modulation, the primary equivalent channel is a function of backscatter symbol tuple\footnote{\eqref{eq:equivalent_channel_bc} and \eqref{eq:equivalent_channel_ris} are often used in \gls{bc} and \gls{ris} literatures, respectively.}
+	\begin{subequations}
 		\label{eq:equivalent_channel}
-	\end{equation}
+		\begin{align}
+			\boldsymbol{h}_{\text{E}}^\mathsf{H}(x_{\mathcal{K}})
+			 & \triangleq \boldsymbol{h}_{\text{D}}^\mathsf{H} + \sum_{k} \alpha_k \boldsymbol{h}_{\text{C},k}^\mathsf{H} x_k \label{eq:equivalent_channel_bc}                    \\
+			 & = \boldsymbol{h}_{\text{D}}^\mathsf{H} + \boldsymbol{x}^\mathsf{H} \mathrm{diag}(\boldsymbol{\alpha}) \boldsymbol{H}_{\text{C}}, \label{eq:equivalent_channel_ris}
+		\end{align}
+	\end{subequations}
 	where $\alpha_k \in \mathbb{I}$ is the common amplitude scattering ratio of node $k$, $\boldsymbol{\alpha} \triangleq [\alpha_1,\ldots,\alpha_K]^\mathsf{T} \in \mathbb{I}^{K}$, $\boldsymbol{x} \triangleq [x_1,\ldots,x_K]^\mathsf{H} \in \mathcal{X}^{K}$, and $\boldsymbol{H}_{\text{C}} \triangleq [\boldsymbol{h}_{\text{C},1},\ldots,\boldsymbol{h}_{\text{C},K}]^\mathsf{H} \in \mathbb{C}^{K \times Q}$.
@@
 
+		\setalgorithmcaptionfont{\small}
 		\begin{algorithm}[!t]
+			\small
 			\caption{Numerical \gls{kkt} Input Distribution Evaluation by Limits of Sequence}
@@
 		\end{equation}
-		where $g_{m_{\mathcal{K}}}(t_{l-1},t_l) \triangleq g_{m_{\mathcal{K}}}(t_l)-g_{m_{\mathcal{K}}}(t_{l-1})$ and
-		\begin{equation}
-			g_{m_{\mathcal{K}}}(t_l) = t_l\exp\Bigl(-\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr)\Bigl(-1+\sum_{n=1}^{N-1} \frac{\bigl(n - \frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\bigr) \bigl(\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\bigr)^{n-1}}{n!}\Bigr).
-			\label{eq:regularized_incomplete_gamma_gradient_component}
-		\end{equation}
+		where $g_{m_{\mathcal{K}}}(t_{l-1},t_l) \triangleq g_{m_{\mathcal{K}}}(t_l)-g_{m_{\mathcal{K}}}(t_{l-1})$ and $g_{m_{\mathcal{K}}}(t_l) = t_l\exp\Bigl(-\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr)\Bigl(-1+\sum_{n=1}^{N-1} \frac{\bigl(n - \frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\bigr) \bigl(\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\bigr)^{n-1}}{n!}\Bigr)$.
+		% \begin{equation}
+		% 	g_{m_{\mathcal{K}}}(t_l) = t_l\exp\Bigl(-\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr)\Bigl(-1+\sum_{n=1}^{N-1} \frac{\bigl(n - \frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\bigr) \bigl(\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\bigr)^{n-1}}{n!}\Bigr).
+		% 	\label{eq:regularized_incomplete_gamma_gradient_component}
+		% \end{equation}
 		On top of \eqref{eq:regularized_incomplete_gamma} and \eqref{eq:regularized_incomplete_gamma_gradient}, we explicitly express the objective function \eqref{ob:active_beamforming} and its gradient as
@@
 			I(x_{\mathcal{K}})
-			 & =\sum_{m_{\mathcal{K}}}P_{\mathcal{K}}(x_{m_{\mathcal{K}}})\Biggl(\rho\log\Bigl(1+\frac{\lvert\boldsymbol{h}_{\text{E}}^\mathsf{H}(x_{m_{\mathcal{K}}})\boldsymbol{w}\rvert^2}{\sigma_v^2}\Bigr)                                                                                                                                                                                                                \\
+			 & =\sum_{m_{\mathcal{K}}}P_{\mathcal{K}}(x_{m_{\mathcal{K}}})\Biggl(\rho\log\Bigl(1+\frac{\lvert\boldsymbol{h}_{\text{E}}^\mathsf{H}(x_{m_{\mathcal{K}}})\boldsymbol{w}\rvert^2}{\sigma_v^2}\Bigr) \nonumber                                                                                                                                                                                                      \\
 			 & \qquad + (1-\rho)\sum_l Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr) \log \frac{Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr)}{\sum_{m_{\mathcal{K}}'} P_{\mathcal{K}}(x_{m_{\mathcal{K}}'}) Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}'}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}'}^2}\Bigr)}\Biggr),
@@
 		The \gls{pgd} active beamforming optimization with step size by \gls{bls} \cite[Section 9.2]{Boyd2004} is summarized in Algorithm \ref{al:active_beamforming}.
+
+		\setalgorithmcaptionfont{\small}
 		\begin{algorithm}[!t]
+			\small
 			\caption{Iterative Active Beamforming Optimization by \gls{pgd} with \gls{bls}}
@@
 			\subfloat[Input Distribution, $Q=1$\label{fg:region_distribution}]{
-				\resizebox{0.32\columnwidth}{!}{
+				\resizebox{0.27\columnwidth}{!}{
 					\input{assets/simulation/region_distribution.tex}
@@
 			\subfloat[Active Beamforming, $Q=4$\label{fg:region_beamforming}]{
-				\resizebox{0.32\columnwidth}{!}{
+				\resizebox{0.27\columnwidth}{!}{
 					\input{assets/simulation/region_beamforming.tex}
@@
 			\subfloat[Decision Threshold, $Q=4$\label{fg:region_threshold}]{
-				\resizebox{0.32\columnwidth}{!}{
+				\resizebox{0.27\columnwidth}{!}{
 					\input{assets/simulation/region_threshold.tex}
@@
 			\begin{itemize}
-				\item \emph{Cooperation:} Joint nodes encoding using a $K$-dimensional probability array $P_{\mathcal{K}}(x_{m_{\mathcal{K}}})$ by Algorithm \ref{al:input_distribution};
-				\item \emph{Exhaustion:} Exhaustive search over the $M$-dimensional probability simplex with resolution $\Delta p = \num{e-2}$;
+				\item \emph{Cooperation:} Joint node encoding with a $K$-dimensional probability array $P_{\mathcal{K}}(x_{m_{\mathcal{K}}})$ by Algorithm \ref{al:input_distribution};
+				\item \emph{Exhaustion:} Exhaustive search over $M$-dimensional probability simplex with step $\Delta p = \num{e-2}$;
 				\item \emph{\gls{kkt}:} Numerical \gls{kkt} result evaluation by Algorithm \ref{al:input_distribution};
@@
 				\item \emph{Decomposition:} Normalized rank-\num{1} \gls{cp} decomposition tensors by \texttt{Tensor Toolbox} \cite{Bader2022};
-				\item \emph{Randomization:} Gaussian randomization-based exhaustive search with the guidance of correlation matrix \cite{Calvo2010}.
+				\item \emph{Randomization:} Gaussian randomization with the guidance of correlation matrix \cite{Calvo2010}.
 				% guided by correlation matrix \cite{Calvo2010}.
@@
 			\subfloat[RIScatter Nodes\label{fg:region_tags}]{
-				\resizebox{0.32\columnwidth}{!}{
+				\resizebox{0.27\columnwidth}{!}{
 					\input{assets/simulation/region_tags.tex}
@@
 			\subfloat[Input States\label{fg:region_states}]{
-				\resizebox{0.32\columnwidth}{!}{
+				\resizebox{0.27\columnwidth}{!}{
 					\input{assets/simulation/region_states.tex}
@@
 			\subfloat[Transmit Antennas\label{fg:region_txs}]{
-				\resizebox{0.32\columnwidth}{!}{
+				\resizebox{0.27\columnwidth}{!}{
 					\input{assets/simulation/region_txs.tex}
@@
 			\subfloat[Symbol Period Ratio\label{fg:region_duration}]{
-				\resizebox{0.32\columnwidth}{!}{
+				\resizebox{0.27\columnwidth}{!}{
 					\input{assets/simulation/region_duration.tex}
@@
 			\subfloat[Average Noise Power\label{fg:region_noise}]{
-				\resizebox{0.32\columnwidth}{!}{
+				\resizebox{0.27\columnwidth}{!}{
 					\input{assets/simulation/region_noise.tex}
@@
 			\subfloat[Disk Radius\label{fg:region_coverage}]{
-				\resizebox{0.32\columnwidth}{!}{
+				\resizebox{0.27\columnwidth}{!}{
 					\input{assets/simulation/region_coverage.tex}
@@
 		Denote the Lagrange multipliers associated with \eqref{co:sum_probability} and \eqref{co:nonnegative_probability} as $\{\nu_k\}_{k \in \mathcal{K}}$ and $\{\lambda_{k,m_k}\}_{k \in \mathcal{K},m_k \in \mathcal{M}}$, respectively.
-		The Lagrangian function of problem \eqref{op:input_distribution} is
-		\begin{equation}
-			- I(x_{\mathcal{K}}) + \sum_k \nu_k \biggl( \sum_{m_k} P_k(x_{m_k}) - 1 \biggr) - \sum_k \sum_{m_k} \lambda_{k,m_k} P_k(x_{m_k})
-		\end{equation}
-		and the \gls{kkt} conditions are, $\forall k,m_k$,
+		The \gls{kkt} conditions of problem \eqref{op:input_distribution} are, $\forall k,m_k$,
 		\begin{subequations}
@@
 		\end{subequations}
-		where directional derivative is explicitly written as
-		\begin{equation}
-			\nabla_{P_k^\star(x_{m_k})} I^\star(x_{\mathcal{K}}) = I_k^\star(x_{m_k}) - (1 - \rho).
-			\label{eq:input_directional_derivative}
-		\end{equation}
-		Combining \eqref{eq:input_kkt_condition_original} and \eqref{eq:input_directional_derivative}, we have
+		where $\nabla_{P_k^\star(x_{m_k})} I^\star(x_{\mathcal{K}}) = I_k^\star(x_{m_k}) - (1 - \rho)$.
+		Therefore, we have
 		\begin{subequations}
@@
 		\end{subequations}
-		such that
-		\begin{equation}
-			\sum_{m_k} P_k^\star(x_{m_k}) I_k^\star(x_{m_k}) = \nu_k^\star + (1 - \rho).
-			\label{eq:input_kkt_condition_implied}
-		\end{equation}
-		On the other hand, by definition \eqref{eq:weighted_sum_marginal_information} we have
-		\begin{equation}
-			\sum_{m_k} P_k^\star(x_{m_k}) I_k^\star(x_{m_k}) = I^\star(x_{\mathcal{K}}),
-			\label{eq:weighted_sum_marginal_information_implied}
-		\end{equation}
-		where the right-hand side is irrelevant to $k$.
-		\eqref{eq:input_kkt_condition_transformed}, \eqref{eq:input_kkt_condition_implied}, and \eqref{eq:weighted_sum_marginal_information_implied} together complete the proof.
+		such that $\sum_{m_k} P_k^\star(x_{m_k}) I_k^\star(x_{m_k}) = \nu_k^\star + (1 - \rho)$.
+		On the other hand, by definition \eqref{eq:weighted_sum_marginal_information} we have $\sum_{m_k} P_k^\star(x_{m_k}) I_k^\star(x_{m_k}) = I^\star(x_{\mathcal{K}})$, where the right-hand side is irrelevant to $k$.
+		This complete the proof.
 		\label{ap:input_kkt_condition}
@@
 		We first prove sequence \eqref{eq:input_kkt_solution} is non-decreasing in weighted sum mutual information.
-		Let $P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) = \prod_{q \in \mathcal{K}} P_q(x_{m_q})$ and $P_{\mathcal{K}}'(x_{m_{\mathcal{K}}}) = P_k'(x_{m_k}) \prod_{q \in \mathcal{K} \setminus \{k\}} P_q(x_{m_q})$ be two probability distributions with potentially different marginal for tag $k$ at state $m_k$, and define an intermediate function $J \bigl( P_{\mathcal{K}}(x_{m_{\mathcal{K}}}),P_{\mathcal{K}}'(x_{m_{\mathcal{K}}}) \bigr)$ as
+		Let $P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) = \prod_{q \in \mathcal{K}} P_q(x_{m_q})$ and $P_{\mathcal{K}}'(x_{m_{\mathcal{K}}}) = P_k'(x_{m_k}) \prod_{q \in \mathcal{K} \setminus \{k\}} P_q(x_{m_q})$ be two probability distributions with potentially different marginal for tag $k$ at state $m_k$, and define an intermediate function
 		\begin{align}
@@
 			 & \triangleq \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}})
-			\Biggl( \rho \log \Bigl(1 + \frac{\lvert \boldsymbol{h}_{\text{E}}^\mathsf{H}(x_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_v^2}\Bigr)                                                                                                                                                    \\
+			\Biggl( \rho \log \Bigl(1 + \frac{\lvert \boldsymbol{h}_{\text{E}}^\mathsf{H}(x_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_v^2}\Bigr) \nonumber                                                                                                                                          \\
 			 & \qquad + (1 - \rho) \sum_{m_{\mathcal{K}}'} P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}}) \log \frac{P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}}) P_{\mathcal{K}}'(x_{m_{\mathcal{K}}})}{P_{\mathcal{K}}'(\hat{x}_{m_{\mathcal{K}}'}) P_{\mathcal{K}}(x_{m_{\mathcal{K}}})} \Biggr).
@@
 		\end{equation}
-		where $i_k \ne m_k$ is the reference state and
-		\begin{equation}
-			S_k'(x_{m_k}) \triangleq I_k'(x_{m_k}) + (1 - \rho) \sum_{m_{\mathcal{K} \setminus \{k\}}} P_{\mathcal{K} \setminus \{k\}}(x_{m_{\mathcal{K} \setminus \{k\}}}) \sum_{m_{\mathcal{K}}'} P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}}) \log P_{\mathcal{K}}'(x_{m_{\mathcal{K}}}).
-		\end{equation}
+		where $S_k'(x_{m_k}) \triangleq I_k'(x_{m_k}) + (1 - \rho) \sum_{m_{\mathcal{K} \setminus \{k\}}} P_{\mathcal{K} \setminus \{k\}}(x_{m_{\mathcal{K} \setminus \{k\}}}) \sum_{m_{\mathcal{K}}'} P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}}) \log P_{\mathcal{K}}'(x_{m_{\mathcal{K}}})$ and $i_k \ne m_k$ is the reference state.
 		Evidently, $\forall m_k \ne i_k$, \eqref{eq:optimal_intermediate_information_condition} boils down to
@@
 		Since $P_k(x_{i_k}) = 1 - \sum_{m_k \ne i_k} P_k^\star(x_{m_k})$ has exactly the same form as \eqref{eq:optimal_relative_distribution}, the choice of reference state $i_k$ does not matter and \eqref{eq:optimal_relative_distribution} is indeed optimal $\forall m_k \in \mathcal{M}$.
-		That is, for a fixed $P_{\mathcal{K}}'(x_{m_{\mathcal{K}}})$, choosing $P_k(x_{m_k})$ by \eqref{eq:optimal_relative_distribution} ensures
-		\begin{equation}
-			J \bigl( P_{\mathcal{K}}(x_{m_{\mathcal{K}}}),P_{\mathcal{K}}'(x_{m_{\mathcal{K}}}) \bigr) \ge I'(x_{\mathcal{K}}).
-			\label{eq:information_difference_lower}
-		\end{equation}
+		That is, for a fixed $P_{\mathcal{K}}'(x_{m_{\mathcal{K}}})$, choosing $P_k(x_{m_k})$ by \eqref{eq:optimal_relative_distribution} ensures $J \bigl( P_{\mathcal{K}}(x_{m_{\mathcal{K}}}),P_{\mathcal{K}}'(x_{m_{\mathcal{K}}}) \bigr) \ge I'(x_{\mathcal{K}})$.
 		On the other hand, we also have
@@
 				 & = (1 - \rho) \sum_{m_k} \frac{P_k'(x_{m_k}) f_k'(x_{m_k})}{\sum_{m_k'} P_k'(x_{m_k'}) f_k'(x_{m_k'})} \sum_{m_{\mathcal{K}}''} P(\hat{x}_{m_{\mathcal{K}}''}|x_{m_k}) \log \frac{\sum_{m_k'} P_k'(x_{m_k'}) P(\hat{x}_{m_{\mathcal{K}}''}|x_{m_k'}) f_k'(x_{m_k})}{\sum_{m_k'} P_k'(x_{m_k'}) P(\hat{x}_{m_{\mathcal{K}}''}|x_{m_k'}) f_k'(x_{m_k'})}                       \\
-				 & \ge (1 - \rho) \sum_{m_k} \frac{P_k'(x_{m_k}) f_k'(x_{m_k})}{\sum_{m_k'} P_k'(x_{m_k'}) f_k'(x_{m_k'})} \sum_{m_{\mathcal{K}}''} P(\hat{x}_{m_{\mathcal{K}}''}|x_{m_k}) \Biggl( 1 - \frac{\sum_{m_k'} P_k'(x_{m_k'}) P(\hat{x}_{m_{\mathcal{K}}''}|x_{m_k'}) f_k'(x_{m_k'})}{\sum_{m_k'} P_k'(x_{m_k'}) P(\hat{x}_{m_{\mathcal{K}}''}|x_{m_k'}) f_k'(x_{m_k})} \Biggr) \\
-				 & = 0,
+				 & \ge (1 - \rho) \sum_{m_k} \frac{P_k'(x_{m_k}) f_k'(x_{m_k})}{\sum_{m_k'} P_k'(x_{m_k'}) f_k'(x_{m_k'})} \sum_{m_{\mathcal{K}}''} P(\hat{x}_{m_{\mathcal{K}}''}|x_{m_k}) \Biggl( 1 - \frac{\sum_{m_k'} P_k'(x_{m_k'}) P(\hat{x}_{m_{\mathcal{K}}''}|x_{m_k'}) f_k'(x_{m_k'})}{\sum_{m_k'} P_k'(x_{m_k'}) P(\hat{x}_{m_{\mathcal{K}}''}|x_{m_k'}) f_k'(x_{m_k})} \Biggr) = 0,
 			\end{align}
@@
 		where $f_k'(x_{m_k}) \triangleq \exp \bigl( \frac{\rho}{1 - \rho} I_k'(x_{m_k}) \bigr)$ and the equality holds if and only if \eqref{eq:optimal_relative_distribution} converges.
-		\eqref{eq:information_difference_lower} and \eqref{eq:information_difference_upper} together imply $I(x_{\mathcal{K}}) \ge I'(x_{\mathcal{K}})$.
+		Therefore, we have $I(x_{\mathcal{K}}) \ge I'(x_{\mathcal{K}})$.
 		Since mutual information is bounded above, we conclude the sequence \eqref{eq:input_kkt_solution} is non-decreasing and convergent in mutual information.
-
 		Next, we prove any converging point of sequence \eqref{eq:input_kkt_solution}, denoted as $P_k^\star(x_{m_k})$, fulfills \gls{kkt} conditions \eqref{eq:input_kkt_condition}.
@@
 		\end{equation}
-		As sequence \eqref{eq:input_kkt_solution} is convergent, any state with $P_k^\star(x_{m_k}) > 0$ need to satisfy $D_k^\star(x_{m_k}) \triangleq \lim_{r \to \infty} D_k^{(r)}(x_{m_k}) = 1$, namely
-		\begin{equation}
-			I_k^\star(x_{m_k}) = \frac{1 - \rho}{\rho} \log \sum_{m_k'} P_k^\star(x_{m_k'}) f_k^\star(x_{m_k'}),
-		\end{equation}
-		which is reminiscent of \eqref{eq:probable_states_marginal} and \eqref{eq:probable_states}.
+		As sequence \eqref{eq:input_kkt_solution} is convergent, any state with $P_k^\star(x_{m_k}) > 0$ need to satisfy $D_k^\star(x_{m_k}) \triangleq \lim_{r \to \infty} D_k^{(r)}(x_{m_k}) = 1$, namely $I_k^\star(x_{m_k}) = \frac{1 - \rho}{\rho} \log \sum_{m_k'} P_k^\star(x_{m_k'}) f_k^\star(x_{m_k'})$, which is reminiscent of \eqref{eq:probable_states_marginal} and \eqref{eq:probable_states}.
 		That is, given $P_k^{(0)}(x_{m_k}) > 0$, any converging point with $P_k^\star(x_{m_k}) > 0$ must satisfy \eqref{eq:probable_states}.
-		On the other hand, we assume $P_k^\star(x_{m_k})$ does not satisfy \eqref{eq:dropped_states}, such that for any state with $P_k^\star(x_{m_k}) = 0$,
-		\begin{equation}
-			I_k^\star(x_{m_k}) > I^\star(x_{\mathcal{K}}) = \sum_{m_k'} P_k^\star(x_{m_k'}) I_k^\star(x_{m_k'}),
-		\end{equation}
-		where the equality inherits from \eqref{eq:weighted_sum_mutual_information}.
+		On the other hand, we assume $P_k^\star(x_{m_k})$ does not satisfy \eqref{eq:dropped_states}, such that for any state with $P_k^\star(x_{m_k}) = 0$, $I_k^\star(x_{m_k}) > I^\star(x_{\mathcal{K}}) = \sum_{m_k'} P_k^\star(x_{m_k'}) I_k^\star(x_{m_k'})$, where the equality inherits from \eqref{eq:weighted_sum_mutual_information}.
 		Since the exponential function is monotonically increasing, we have $f_k^\star(x_{m_k}) > \sum_{m_k'} P_k^\star(x_{m_k'}) f_k^\star(x_{m_k'})$ and $D_k^\star(x_{m_k}) > 1$.
-		Considering $P_k^{(0)}(x_{m_k}) > 0$ and $P_k^\star(x_{m_k}) = 0$, it contradicts with
-		\begin{equation}
-			P_k^{(r)}(x_{m_k}) = P_k^{(0)}(x_{m_k}) \prod_{n=1}^r D_k^{(n)}(x_{m_k}).
-		\end{equation}
+		Considering $P_k^{(0)}(x_{m_k}) > 0$ and $P_k^\star(x_{m_k}) = 0$, it contradicts with $P_k^{(r)}(x_{m_k}) = P_k^{(0)}(x_{m_k}) \prod_{n=1}^r D_k^{(n)}(x_{m_k})$.
 		That is, given $P_k^{(0)}(x_{m_k}) > 0$, any converging point with $P_k^\star(x_{m_k}) = 0$ must satisfy \eqref{eq:dropped_states}.
-		The proof is thus completed.
+		The proof is completed.
 		\label{ap:input_kkt_solution}

### 2022-12-18 main.tex
:triangular_flag_on_post: JSAC and arXiv 221218

@@
 		B. Clerckx is also with Silicon Austria Labs (SAL), Graz A-8010, Austria.
+
+		This article has been submitted for potential publications.
 	}
@@
 		Those \gls{bc} applications employ scatter nodes as pure information sources, and the active primary transmission (if it exists) can be influenced by the randomness of backscatter modulation.
-		On the other hand, \gls{ris} in Fig.~\ref{fg:ris} is a smart planar signal reflector that consists of numerous compact passive elements with adjustable amplitude and phase responses, whose reflection pattern over time is deterministic and adaptively optimized based on \gls{csi}.
+		On the other hand, \gls{ris} in Fig.~\subref*{fg:ris} is a smart planar signal reflector that consists of numerous compact passive elements with adjustable amplitude and phase responses, whose reflection pattern over time is deterministic and adaptively optimized based on \gls{csi}.
 		\gls{ris} smartly reflects the surrounding \gls{rf} waves to customize the wireless propagation environment for signal enhancement, interference suppression, scattering enrichment and non-line-of-sight bypassing \cite{Wu2021b}.

### 2023-01-04 jsac.tex
:triangular_flag_on_post: JSAC 230104

--- 2022-12-18 jsac_221218.tex
@@
 	The second property motivated \cite{Long2020a,Liang2020,Guo2019b,Ding2020,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Yang2018,Han2021,Zhang2022} to view \gls{sr} as a multiplicative \gls{noma} and perform \gls{sic} from primary to backscatter link.
-	During primary decoding, the randomness of backscatter modulation can be modelled as channel uncertainty or multiplicative interference when the backscatter-over-primary symbol period ratio $N$ is large or small\footnote{For state-of-the-art low-power \gls{rfid} tags, the load-switching speed usually varies between \num{100}s of \unit{\kHz} to \num{10}s of \unit{\MHz} \cite{Torres2021}, corresponding to a typical $N$ between \num{10} and \num{1000}.}.
+	During primary decoding, the randomness of backscatter modulation can be modelled as either channel uncertainty or multiplicative interference, when the spreading factor (i.e., backscatter-over-primary symbol period ratio) $N$ is large or small, respectively\footnote{For state-of-the-art low-power \gls{rfid} tags, the load-switching speed usually varies between \num{100}s of \unit{\kHz} to \num{10}s of \unit{\MHz} \cite{Torres2021}, corresponding to a typical spreading factor between \num{10} and \num{1000}.}.
 	Such a \gls{sic} receiver is operation-intensive and \gls{csi}-sensitive because it involves $N$ re-encoding, precoding, subtraction together with a time-domain \gls{mrc} to decode each backscatter symbol.
-	When $N$ is sufficiently large (i.e., commensal \gls{sr}), the average primary achievable rate under semi-coherent detection\footnote{In this paper, semi-coherent detection refers to the primary/backscatter decoding based on known \gls{csi} and unknown backscatter/primary symbols.} asymptotically approaches its coherent counterpart, and both links may be decoded in an interference-free manner \cite{Long2020a}.
+	When the spreading factor is sufficiently large (i.e., commensal \gls{sr}), the average primary achievable rate under semi-coherent detection\footnote{In this paper, semi-coherent detection refers to the primary/backscatter decoding based on known \gls{csi} and unknown backscatter/primary symbols.} asymptotically approaches its coherent counterpart, and both links may be decoded in an interference-free manner \cite{Long2020a}.
 	On the other hand, efficient backscatter multiple access design remains an open issue for \gls{bc}.
@@
 	Thanks to the double modulation and symbol period difference, the backscatter symbol can be modelled within primary channel (similar to \gls{ris}) rather than being re-precoded and cancelled, and the semi-coherent energy-based backscatter detection indeed becomes part of primary channel training.
-	The strategy is suitable for arbitrary primary sampling rate and backscatter load-switching speed (i.e., arbitrary $N$).
+	The strategy is suitable for arbitrary primary sampling rate and backscatter load-switching speed (i.e., arbitrary spreading factor).
 	This is the first paper to consider such a sequential backscatter-primary decoding and treat semi-coherent backscatter detection as part of primary channel training.
@@
 			``PB'' means primary block and ``BB'' means backscatter block.
+			Spreading factor is 2 in this example.
 		}
@@
 	2) requires no re-precoding, cancellation, or \gls{mrc};
-	3) preserves backscatter modulation and passive beamforming at smaller $N$ for potentially higher backscatter throughput.
+	3) preserves backscatter modulation and passive beamforming at smaller spreading factors for potentially higher backscatter throughput.
 	% \end{subsection}
@@
 	For simplicity, we consider a quasi-static block fading model and focus on a specific block where all \gls{csi} remain constant.
-	Without loss of generality, let the backscatter-over-primary symbol period ratio $N$ be a positive integer.
+	Without loss of generality, let the spreading factor $N$ be a positive integer.
 	We also omit the signal reflected by two or more times and ignore the multipath propagation time difference.
@@
 		Fig.~\ref{fg:region_comparison} compares the typical achievable rate region/points of RIScatter and above.
-		\emph{First,} we observe both \gls{bbc} and \gls{sr} almost ensure noise-free backscatter transmission when $N$ is sufficiently large.
+		\emph{First,} we observe both \gls{bbc} and \gls{sr} almost ensure noise-free backscatter transmission when the spreading factor $N$ is sufficiently large.
 		For \gls{bbc} with coherent energy detection, the conditional \gls{pdf} of accumulated receive energy \eqref{eq:energy_distribution_bbc} is more skewed at a large $N$, such that the equivalent \gls{dmtmac} \eqref{eq:dmtmac} has lower error probabilities.
 		For \gls{sic}-based \gls{sr}, the effective backscatter \gls{snr} is increased by $N$ times and the penalty term $\iota$ becomes insignificant.
-		However, the primary rate is only maintained at a very large $N$, which significantly constrains the backscatter \emph{throughput}.
+		However, the primary rate is only maintained at a very large spreading factor, which significantly constrains the backscatter \emph{throughput}.
 		\emph{Second,} the average primary rate slightly increases/decreases in the presence of a \gls{ambc}/\gls{ris} node, and the multipath benefit of \gls{sr} is unobvious.
@@
 coherent) energy detection, while RIScatter with adaptive channel coding can achieve higher backscatter rate than \gls{ambc} with equiprobable inputs.
-		Importantly, such a practical RIScatter detection is feasible for arbitrary $N$, which unleashes the potential of fast-switching nodes.
+		Importantly, such a practical RIScatter detection is feasible for arbitrary spreading factor, which unleashes the potential of fast-switching nodes.
 		% , and using a fast-switching node with smaller $N$ can increase the backscatter throughput per unit time while preserving the dynamic passive beamforming gain on the primary link.
@@
 			\\
-			\subfloat[Symbol Period Ratio\label{fg:region_duration}]{
+			\subfloat[Spreading Factor\label{fg:region_duration}]{
 				\resizebox{0.27\columnwidth}{!}{
@@
 
-		\begin{subsubsection}{Symbol Period Ratio}
-			Fig.~\subref*{fg:region_duration} presents how symbol period ratio $N$ affects the achievable rate region, where the unit of total backscatter rate is bits per primary block (to indicate throughput).
+		\begin{subsubsection}{Spreading factor}
+			Fig.~\subref*{fg:region_duration} presents how the spreading factor $N$ affects the achievable rate region, where the unit of total backscatter rate is bits per primary block (to indicate throughput).
 			Apparently, using a very large $N$ can severely constrain the backscatter throughput, since the gain in energy certainty (by law of large numbers) cannot withstand the loss in gross rate.
 			As $N \to \infty$, RIScatter nodes boil down to \gls{ris} elements with fixed reflection pattern during whole channel block and the total backscatter rate approaches \num{0}.
-			On the other hand, when $N$ is too small, the equivalent \gls{dmtmac} \eqref{eq:dmtmac} has very high error probabilities and the energy detection can be unreliable.
+			On the other hand, when $N$ is too small, the equivalent \gls{dmtmac} \eqref{eq:dmtmac} has very high error probabilities and the energy detection can thus be unreliable.
 			It explains the observation that $N=10$ provides lower backscatter achievable rate than $N=20$, although nodes are encoding at higher gross rate.
-			Therefore, we conclude the design of symbol period ratio $N$ in RIScatter systems should account for multiple factors (e.g., data rate requirements, physical constraints at the nodes, and signal processing capability at the user).
+			Therefore, we conclude the design of spreading factor $N$ in RIScatter systems should account for multiple factors (e.g., data rate requirements, load switching constraints at the nodes, and signal processing capability at the user).
 		\end{subsubsection}

### 2023-01-04 main.tex
:triangular_flag_on_post: JSAC 230104

@@
 		The second property motivated \cite{Long2020a,Liang2020,Guo2019b,Ding2020,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Yang2018,Han2021,Zhang2022} to view \gls{sr} as a multiplicative \gls{noma} and perform \gls{sic} from primary to backscatter link.
-		During primary decoding, the randomness of backscatter modulation can be modelled as channel uncertainty or multiplicative interference when the backscatter-over-primary symbol period ratio $N$ is large or small\footnote{For state-of-the-art low-power \gls{rfid} tags, the load-switching speed usually varies between \num{100}s of \unit{\kHz} to \num{10}s of \unit{\MHz} \cite{Torres2021}, corresponding to a typical $N$ between \num{10} and \num{1000}.}.
+		During primary decoding, the randomness of backscatter modulation can be modelled as either channel uncertainty or multiplicative interference, when the spreading factor (i.e., backscatter-over-primary symbol period ratio) $N$ is large or small, respectively\footnote{For state-of-the-art low-power \gls{rfid} tags, the load-switching speed usually varies between \num{100}s of \unit{\kHz} to \num{10}s of \unit{\MHz} \cite{Torres2021}, corresponding to a typical spreading factor between \num{10} and \num{1000}.}.
 		Such a \gls{sic} receiver is operation-intensive and \gls{csi}-sensitive because it involves $N$ re-encoding, precoding, subtraction together with a time-domain \gls{mrc} to decode each backscatter symbol.
-		When $N$ is sufficiently large (i.e., commensal \gls{sr}), the average primary achievable rate under semi-coherent detection\footnote{In this paper, semi-coherent detection refers to the primary/backscatter decoding based on known \gls{csi} and unknown backscatter/primary symbols.} asymptotically approaches its coherent counterpart, and both links may be decoded in an interference-free manner \cite{Long2020a}.
+		When the spreading factor is sufficiently large (i.e., commensal \gls{sr}), the average primary achievable rate under semi-coherent detection\footnote{In this paper, semi-coherent detection refers to the primary/backscatter decoding based on known \gls{csi} and unknown backscatter/primary symbols.} asymptotically approaches its coherent counterpart, and both links may be decoded in an interference-free manner \cite{Long2020a}.
 		On the other hand, efficient backscatter multiple access design remains an open issue for \gls{bc}.
@@
 		Thanks to the double modulation and symbol period difference, the backscatter symbol can be modelled within primary channel (similar to \gls{ris}) rather than being re-precoded and cancelled, and the semi-coherent energy-based backscatter detection indeed becomes part of primary channel training.
-		The strategy is suitable for arbitrary primary sampling rate and backscatter load-switching speed (i.e., arbitrary $N$).
+		The strategy is suitable for arbitrary primary sampling rate and backscatter load-switching speed (i.e., arbitrary spreading factor).
 		This is the first paper to consider such a sequential backscatter-primary decoding and treat semi-coherent backscatter detection as part of primary channel training.
@@
 				``PB'' means primary block and ``BB'' means backscatter block.
+				Spreading factor is 2 in this example.
 			}
@@
 		2) requires no re-precoding, cancellation, or \gls{mrc};
-		3) preserves backscatter modulation and passive beamforming at smaller $N$ for potentially higher backscatter throughput.
+		3) preserves backscatter modulation and passive beamforming at smaller spreading factors for potentially higher backscatter throughput.
 	\end{subsection}
@@
 		For simplicity, we consider a quasi-static block fading model and focus on a specific block where all \gls{csi} remain constant.
-		Without loss of generality, let the backscatter-over-primary symbol period ratio $N$ be a positive integer.
+		Without loss of generality, let the spreading factor $N$ be a positive integer.
 		We also omit the signal reflected by two or more times and ignore the multipath propagation time difference.
@@
 			}
-			\subfloat[Symbol Period Ratio\label{fg:region_duration}]{
+			\subfloat[Spreading Factor\label{fg:region_duration}]{
 				\resizebox{0.48\columnwidth}{!}{

### 2023-01-14 jsac.tex
:triangular_flag_on_post: JSAC 230114

@@
 	From an information-theoretic perspective, \cite{Karasik2020} reported that using \gls{ris} as a naive passive beamformer to maximize the receive \gls{snr} is generally rate-suboptimal for finite-input constellations.
-	Instead, the capacity of \gls{ris}-aided channel is achieved by joint transmitter-\gls{ris} encoding, and \gls{sic}-based \gls{sr} can outperform passive beamforming at high \gls{snr}.
+	Instead, the capacity of \gls{ris}-aided channel is achieved by joint transmitter-\gls{ris} encoding, and even layered encoding with pilots can outperform passive beamforming at high \gls{snr}.
 	It inspired \gls{ris}-empowered \gls{bc} \cite{Liu2019d,Bereyhi2020,Xu2020b,Zhang2021d,Hu2021b,Hua2022,Basar2020,Ma2020a,Yuan2021,Hu2021a} to combine passive beamforming and backscatter modulation in the overall reflection pattern.

### 2023-01-14 main.tex
:triangular_flag_on_post: JSAC 230114

@@
 		From an information-theoretic perspective, \cite{Karasik2020} reported that using \gls{ris} as a naive passive beamformer to maximize the receive \gls{snr} is generally rate-suboptimal for finite-input constellations.
-		Instead, the capacity of \gls{ris}-aided channel is achieved by joint transmitter-\gls{ris} encoding, and \gls{sic}-based \gls{sr} can outperform passive beamforming at high \gls{snr}.
+		Instead, the capacity of \gls{ris}-aided channel is achieved by joint transmitter-\gls{ris} encoding, and even layered encoding with pilots can outperform passive beamforming at high \gls{snr}.
 		It inspired \gls{ris}-empowered \gls{bc} \cite{Liu2019d,Bereyhi2020,Xu2020b,Zhang2021d,Hu2021b,Hua2022,Basar2020,Ma2020a,Yuan2021,Hu2021a} to combine passive beamforming and backscatter modulation in the overall reflection pattern.

### 2023-01-17 jsac.tex
:triangular_flag_on_post: JSAC 230117

@@
 	Hence, the receiver can semi-coherently (under primary uncertainty) decode RIScatter nodes from the accumulated receive energy, re-encode to recover the exact reflection patterns, and combine those with cascaded \gls{csi} to determine the multipath response and model within the primary channel.
-	Such a backscatter-primary decoding enables simultaneous backscatter modulation and dynamic passive beamforming by only one energy comparison, re-encoding, and precoding during each backscatter (instead of primary) block.
+	Such a backscatter-primary decoding enables simultaneous backscatter modulation and dynamic passive beamforming by only one energy comparison and re-encoding during each backscatter (instead of primary) block.
 	It enjoys a three-fold benefit compared to conventional primary-backscatter decoding with \gls{sic}, namely

### 2023-01-17 main.tex
:triangular_flag_on_post: JSAC 230117

@@
 		Hence, the receiver can semi-coherently (under primary uncertainty) decode RIScatter nodes from the accumulated receive energy, re-encode to recover the exact reflection patterns, and combine those with cascaded \gls{csi} to determine the multipath response and model within the primary channel.
-		Such a backscatter-primary decoding enables simultaneous backscatter modulation and dynamic passive beamforming by only one energy comparison, re-encoding, and precoding during each backscatter (instead of primary) block.
+		Such a backscatter-primary decoding enables simultaneous backscatter modulation and dynamic passive beamforming by only one energy comparison and re-encoding during each backscatter (instead of primary) block.
 		It enjoys a three-fold benefit compared to conventional primary-backscatter decoding with \gls{sic}, namely

### 2023-01-29 assets/illustration/time_structure.tex
:lipstick: Update illustrations

@@
-\begin{tikzpicture}[font=\large]
-	% BC/AmBC/SR
-	\foreach \x in {0,...,3}{
-			\draw[blue,fill=blue!30!white,postaction={pattern=north west lines},pattern color=.] (0.5*\x,3) rectangle ++(0.5,0.25);
+\begin{tikzpicture}[font=\small]
+	% MBC/BBC
+	\foreach \x in {0}{
+			\draw[blue,ultra thick,postaction={pattern=north west lines},pattern color=.] (2*\x,4) rectangle ++(2,0.25);
 		}
-	\foreach \x in {4,...,7}{
-			\draw[blue,fill=blue!30!white,postaction={pattern=north east lines},pattern color=.] (0.5*\x,3) rectangle ++(0.5,0.25);
+	\foreach \x in {1}{
+			\draw[blue,ultra thick,postaction={pattern=north east lines},pattern color=.] (2*\x,4) rectangle ++(2,0.25);
 		}
-	\foreach \x in {8,...,11}{
-			\draw[blue,fill=blue!30!white,postaction={pattern=vertical lines},pattern color=.] (0.5*\x,3) rectangle ++(0.5,0.25);
+	\foreach \x in {2}{
+			\draw[blue,ultra thick,postaction={pattern=vertical lines},pattern color=.] (2*\x,4) rectangle ++(2,0.25);
 		}
-	\foreach \x in {12,...,15}{
-			\draw[blue,fill=blue!30!white,postaction={pattern=horizontal lines},pattern color=.] (0.5*\x,3) rectangle ++(0.5,0.25);
+	\foreach \x in {3}{
+			\draw[blue,ultra thick,postaction={pattern=horizontal lines},pattern color=.] (2*\x,4) rectangle ++(2,0.25);
 		}
+	\draw[latex-latex] (0,4.35) -- (2,4.35) node[above,midway]{BB};
+	\node at (-1.5,4.125) {MBC/BBC};
+
+	% AmBC/SR
+	\foreach \x in {0,...,7}{
+			\draw[teal,fill=teal!30!white,postaction={pattern=north west lines},pattern color=.] (0.5*\x,3) rectangle ++(0.5,0.25);
+		}
+	\foreach \x in {8,...,15}{
+			\draw[teal,fill=teal!30!white,postaction={pattern=vertical lines},pattern color=.] (0.5*\x,3) rectangle ++(0.5,0.25);
+		}
+	\foreach \x in {0,...,1}{
+			\draw[teal,ultra thick] (4*\x,3) rectangle ++(4,0.25);
+		}
+	\draw[latex-latex] (0,3.35) -- (4,3.35) node[above,midway]{BB};
+	\draw[latex-latex] (0,2.9) -- (0.5,2.9) node[below,midway]{PB};
+	\node at (-1.5,3.125) {AmBC/SR};
 
@@
 		}
+	\draw[red,ultra thick] (0,2) rectangle ++(8,0.25);
+	\draw[latex-latex] (0,2.35) -- (8,2.35) node[above,midway]{CB};
+	\draw[latex-latex] (0,1.9) -- (0.5,1.9) node[below,midway]{PB};
+	\node at (-1.5,2.125) {RIS};
 
 	% RIScatter
-	\foreach \x in {0,...,1}{
-			\draw[brown,fill=brown!30!white,postaction={pattern=north west lines},pattern color=.] (0.5*\x,1) rectangle ++(0.5,0.25);
-		}
-	\foreach \x in {2,...,7}{
+	\foreach \x in {0,...,7,12,13,...,15}{
 			\draw[brown,fill=brown!30!white,postaction={pattern=north east lines},pattern color=.] (0.5*\x,1) rectangle ++(0.5,0.25);
@@
 	\foreach \x in {8,...,11}{
-			\draw[brown,fill=brown!30!white,postaction={pattern=vertical lines},pattern color=.] (0.5*\x,1) rectangle ++(0.5,0.25);
+			\draw[brown,fill=brown!30!white,postaction={pattern=north west lines},pattern color=.] (0.5*\x,1) rectangle ++(0.5,0.25);
 		}
-	\foreach \x in {12,...,15}{
-			\draw[brown,fill=brown!30!white,postaction={pattern=north east lines},pattern color=.] (0.5*\x,1) rectangle ++(0.5,0.25);
+	\foreach \x in {0,...,3}{
+			\draw[brown,ultra thick] (2*\x,1) rectangle ++(2,0.25);
 		}
+	\draw[latex-latex] (0,1.35) -- (2,1.35) node[above,midway]{BB};
+	\draw[latex-latex] (0,0.9) -- (0.5,0.9) node[below,midway]{PB};
 
-	\foreach \x in {1,...,7}{
-			% \draw[dotted] (\x,1) -- (\x,3.75);
-			\draw[dotted] (\x,1) -- (\x,3.25);
-		}
-	\draw[latex-latex] (0,1.4) -- (0.5,1.4) node[above,midway,yshift=1]{PB};
-	% \draw[latex-latex] (0,4.1) -- (1,4.1) node[above,midway,yshift=1]{BB};
-	\draw[latex-latex] (0,2.4) -- (1,2.4) node[above,midway,yshift=1]{BB};
-	\draw[latex-latex] (0,3.4) -- (8,3.4) node[above,midway,yshift=1]{Channel Block};
+	\node at (-1.5,1.125) {RIScatter};
 
-	\node at (-2,3.125) {BackCom};
-	\node at (-2,2.125) {RIS};
-	\node at (-2,1.125) {RIScatter};
-
-	\draw [pattern=north west lines](0.15,0) rectangle ++(0.5,0.25) node[xshift=20,yshift=-3.5] {State 1};
-	\draw [pattern=north east lines](2.15,0) rectangle ++(0.5,0.25) node[xshift=20,yshift=-3.5] {State 2};
-	\draw [pattern=vertical lines](4.15,0) rectangle ++(0.5,0.25) node[xshift=20,yshift=-3.5] {State 3};
-	\draw [pattern=horizontal lines](6.15,0) rectangle ++(0.5,0.25) node[xshift=20,yshift=-3.5] {State 4};
+	\draw [pattern=north west lines,ultra thick](0.15,5) rectangle ++(0.5,0.25) node[xshift=20,yshift=-3.5] {State 1};
+	\draw [pattern=north east lines,ultra thick](2.15,5) rectangle ++(0.5,0.25) node[xshift=20,yshift=-3.5] {State 2};
+	\draw [pattern=vertical lines,ultra thick](4.15,5) rectangle ++(0.5,0.25) node[xshift=20,yshift=-3.5] {State 3};
+	\draw [pattern=horizontal lines,ultra thick](6.15,5) rectangle ++(0.5,0.25) node[xshift=20,yshift=-3.5] {State 4};
 \end{tikzpicture}

### 2023-01-29 jsac.tex
:lipstick: Update illustrations

@@
 	In a \gls{sr} system, the active transmitter generates \gls{rf} wave carrying primary information, the passive node creates additional propagation path and ride its information over scattered signal, while the cooperative receiver jointly, individually, or sequentially decodes both links.
-	Those \gls{bc} applications employ scatter nodes as pure information sources, and the active primary transmission (if it exists) can be influenced by the randomness of backscatter modulation.
+	Those \gls{bc} applications\footnote{In this paper, \gls{bc} refers to \gls{mbc}, \gls{bbc}, \gls{ambc} and \gls{sr}.} employ scatter nodes as pure information sources, and the active primary transmission (if it exists) can be influenced by the randomness of backscatter modulation.
 	On the other hand, \gls{ris} in Fig.~\subref*{fg:ris} is a smart planar signal reflector that consists of numerous compact passive elements with adjustable amplitude and phase responses, whose reflection pattern over time is deterministic and adaptively optimized based on \gls{csi}.
@@
 		\caption{
-			Reflection state distribution and reflection pattern over time of \gls{bc}, \gls{ris}, and RIScatter.
-			``PB'' means primary block and ``BB'' means backscatter block.
-			Spreading factor is 2 in this example.
+			Reflection state distribution and reflection pattern over time of scattering applications.
+			``PB'', ``BB'', and ``CB'' means primary block, backscatter block, and channel block, respectively.
+			\gls{bc} employs all possible states only as information codewords, \gls{ris} treats them only as beamformer codewords, and RIScatter simultaneously exploits both benefits.
 		}

### 2023-01-29 main.tex
:lipstick: Update illustrations

@@
 		In a \gls{sr} system, the active transmitter generates \gls{rf} wave carrying primary information, the passive node creates additional propagation path and ride its information over scattered signal, while the cooperative receiver jointly, individually, or sequentially decodes both links.
-		Those \gls{bc} applications employ scatter nodes as pure information sources, and the active primary transmission (if it exists) can be influenced by the randomness of backscatter modulation.
+		Those \gls{bc} applications\footnote{In this paper, \gls{bc} refers to \gls{mbc}, \gls{bbc}, \gls{ambc} and \gls{sr}.} employ scatter nodes as pure information sources, and the active primary transmission (if it exists) can be influenced by the randomness of backscatter modulation.
 		On the other hand, \gls{ris} in Fig.~\subref*{fg:ris} is a smart planar signal reflector that consists of numerous compact passive elements with adjustable amplitude and phase responses, whose reflection pattern over time is deterministic and adaptively optimized based on \gls{csi}.
@@
 			\caption{
-				Reflection state distribution and reflection pattern over time of \gls{bc}, \gls{ris}, and RIScatter.
-				``PB'' means primary block and ``BB'' means backscatter block.
-				Spreading factor is 2 in this example.
+				Reflection state distribution and reflection pattern over time of scattering applications.
+				``PB'', ``BB'', and ``CB'' means primary block, backscatter block, and channel block, respectively.
+				\gls{bc} employs all possible states only as information codewords, \gls{ris} treats them only as beamformer codewords, and RIScatter simultaneously exploits both benefits.
 			}

### 2023-02-02 jsac.tex
:lipstick: Update illustrations

@@
 			Reflection state distribution and reflection pattern over time of scattering applications.
-			``PB'', ``BB'', and ``CB'' means primary block, backscatter block, and channel block, respectively.
-			\gls{bc} employs all possible states only as information codewords, \gls{ris} treats them only as beamformer codewords, and RIScatter simultaneously exploits both benefits.
+			``PB'', ``BB'', and ``CB'' refer to primary block, backscatter block, and channel block, respectively.
+			\gls{bc} employs all possible states as information codewords, \gls{ris} treats them as beamformer codewords, and RIScatter simultaneously exploits both benefits.
 		}

### 2023-02-02 main.tex
:lipstick: Update illustrations

@@
 				Reflection state distribution and reflection pattern over time of scattering applications.
-				``PB'', ``BB'', and ``CB'' means primary block, backscatter block, and channel block, respectively.
-				\gls{bc} employs all possible states only as information codewords, \gls{ris} treats them only as beamformer codewords, and RIScatter simultaneously exploits both benefits.
+				``PB'', ``BB'', and ``CB'' refer to primary block, backscatter block, and channel block, respectively.
+				\gls{bc} employs all possible states as information codewords, \gls{ris} treats them as beamformer codewords, and RIScatter simultaneously exploits both benefits.
 			}

### 2023-02-03 assets/illustration/ambc.tex
:lipstick: Update illustrations and reference

@@
 	\draw[lightgray,decorate,decoration={waves,segment length=4mm,radius=2mm}] (5.5,3.5) -- (2.5,3.5);
-	\draw[magenta,decorate,decoration={crosses,segment length=8mm,shape size=1.5mm}] (5.11,3.5) -- (2.5,3.5);
+	\draw[magenta,decorate,decoration={crosses,segment length=16mm,shape size=1.5mm}] (5.11,3.5) -- (2.5,3.5);
 	\draw[lightgray,decorate,decoration={waves,segment length=4mm,radius=2mm}] (7.43,3.28) -- (8,1);
-	\draw[lightgray,decorate,decoration={crosses,segment length=8mm,shape size=1.5mm}] (7.525,2.9) -- (8,1);
+	\draw[lightgray,decorate,decoration={crosses,segment length=16mm,shape size=1.5mm}] (7.525,2.9) -- (8,1);
 

### 2023-02-16 jsac.tex
:pencil: Update reference for DCMC capacity

@@
 			which only involves noise uncertainty under hypothesis $\mathcal{H}_{m_{\mathcal{K}}}$.
-			During backscatter detection, the primary symbols $s[1],\ldots,s[n]$ can be viewed as a spreading code, and the receiver employs \gls{mrc} over $N$ primary blocks.
-			The total achievable for nodes with equiprobable inputs is \cite{Wang2014a}
+			During backscatter detection, the primary symbols $s[1],\ldots,s[N]$ function as a spreading code and the receiver performs \gls{mrc} on $\hat{y}^{\text{\gls{sr}}}[n]$ over $N$ primary blocks.
+			This essentially formulates a discrete-input continuous-output memoryless channel and the total backscatter achievable rate is maximized with equiprobable inputs as \cite{Ng2006}
 			\begin{equation}

### 2023-02-24 main.tex
:construction: Updating contributions

@@
 \newacronym{fpga}{FPGA}{Field-Programmable Gate Array}
+\newacronym{ber}{BER}{Bit Error Rate}
 
@@
 
-		This article has been submitted for potential publications.
+		% This article has been submitted for potential publications.
 	}
@@
 	\gls{ris} adapts its phase shift response to enhance or attenuate channel strength in specific directions.
-	In this paper, we show how those two seemingly different technologies (and their derivatives) can be unified to leverage their benefits simultaneously into a single architecture called RIScatter.
-	RIScatter consists of multiple dispersed or co-located scatter nodes, whose reflection states can be adapted to partially engineer the wireless channel of the existing link and partially modulate their own information onto the scattered wave.
-	This contrasts with \gls{bc} (resp. \gls{ris}) where the reflection pattern is exclusively a function of the information symbol (resp. \gls{csi}).
-	The key principle in RIScatter is to render the probability distribution of reflection states (i.e., backscatter channel input) as a joint function of the information source, \gls{csi}, and \gls{qos} of the coexisting active primary and passive backscatter links.
-	This enables RIScatter to softly bridge, generalize, and outperform \gls{bc} and \gls{ris}; boil down to either under specific input distribution; or evolve in a mixed form for heterogeneous traffic control and universal hardware design.
-	For a single-user multi-node RIScatter network, we characterize the achievable primary-(total-)backscatter rate region by optimizing the input distribution at the nodes, the active beamforming at the \gls{ap}, and the backscatter detection regions at the user.
-	Simulation results demonstrate RIScatter nodes can exploit the additional propagation paths to smoothly transition between backscatter modulation and passive beamforming, and the proposed practical receiver accommodates the double fading, double modulation, and symbol period difference of active-passive coexisting networks without \gls{sic}.
+	In this paper, we show how those two seemingly different technologies (and their derivatives) can be unified into a single architecture called RIScatter.
+	RIScatter consists of multiple dispersed or co-located scatter nodes, whose reflection states are adapted to partially modulate their own information and partially engineer the wireless channel.
+	% This contrasts with \gls{bc} (resp. \gls{ris}) where the reflection pattern is exclusively a function of the information symbol (resp. \gls{csi}).
+	The key principle is to render the probability distribution of reflection states as a joint function of the information source, \gls{csi}, and \gls{qos} of coexisting active primary and passive backscatter links.
+	This enables RIScatter to softly bridge \gls{bc} and \gls{ris}; boil down to either under specific input distribution; or evolve in a mixed form for heterogeneous traffic control and universal hardware design.
+	% To accommodate the characteristics of active-passive coexisting networks, we propose a practical \gls{sic}-free receiver
+	To reap the benefits of RIScatter, we also propose a co-located \gls{sic}-free receiver that semi-coherently decodes the backscatter information, recovers the reflection pattern, and coherently decodes the primary link.
+	For a single-user multi-node RIScatter network, we characterize the achievable primary-(total-)backscatter rate region by designing the input distribution at scatter nodes, the active beamforming at the \gls{ap}, and the energy detection regions at the user.
+	Simulation results demonstrate RIScatter nodes can exploit the scattered paths to smoothly shift between backscatter modulation and passive beamforming.
 \end{abstract}
@@
 \begin{IEEEkeywords}
-	Backscatter communication, reconfigurable intelligent surface, ambient backscatter communication, symbiotic radio.
+	Input distribution design, energy detection, \gls{sic}-free receiver, active-passive coexisting network, backscatter communication, reconfigurable intelligent surface, ambient backscatter communication, symbiotic radio.
 \end{IEEEkeywords}
@@
 \begin{section}{Introduction}
-	\begin{subsection}{Fundamentals}
-		\IEEEPARstart{F}{uture} wireless network is envisioned to provide high throughput, uniform coverage, pervasive connectivity, heterogeneous control, and cognitive intelligence for trillions of portable devices.
-		As a mature low-power communication technique, \gls{bc} separates a conventional transmitter into a \gls{rf} carrier emitter with power-hungry elements (e.g., synthesizer and amplifier) and an information-bearing node with power-efficient components (e.g., harvester and modulator) \cite{Boyer2014}.
-		In particular, the node harvests energy from impinging wave and embeds information over scattered signal, and the backscatter reader can be either co-located or separated with the carrier emitter, known as \gls{mbc} in Fig.~\subref*{fg:mbc} and \gls{bbc} in Fig.~\subref*{fg:bbc}.
-		Relevant applications such as \gls{rfid} \cite{Dobkin2012,Landt2005} and passive sensor network \cite{Vannucci2008,Assimonis2016} have been extensively researched, standardized, and commercialized in the era of \gls{ioe}.
-		However, conventional \gls{bc} nodes only respond when externally inquired by a nearby reader.
-		To tackle this, \cite{Liu2013b} proposed \gls{ambc} where battery-free nodes recycle ambient signals (e.g., radio, television and Wi-Fi) to harvest energy and establish connection in between.
-		As shown in Fig.~\subref*{fg:ambc}, it eliminates the need of dedicated power supply, carrier emitter and frequency spectrum for \gls{bc}, but the decoding is subject to a strong interference from the primary (legacy) link.
-		Cooperative \gls{ambc} was then proposed where a co-located receiver decodes both active primary and passive backscatter links, and the rate and error performance are evaluated for various detection schemes \cite{Yang2018}.
-		The concept was further refined by \cite{Liang2020} as \gls{sr} in Fig.~\subref*{fg:sr} that cognitively incorporates \gls{ambc} with existing systems.
-		In a \gls{sr} system, the active transmitter generates \gls{rf} wave carrying primary information, the passive node creates additional propagation path and ride its information over scattered signal, while the cooperative receiver jointly, individually, or sequentially decodes both links.
-		Those \gls{bc} applications\footnote{In this paper, \gls{bc} refers to \gls{mbc}, \gls{bbc}, \gls{ambc} and \gls{sr}.} employ scatter nodes as pure information sources, and the active primary transmission (if it exists) can be influenced by the randomness of backscatter modulation.
-		On the other hand, \gls{ris} in Fig.~\subref*{fg:ris} is a smart planar signal reflector that consists of numerous compact passive elements with adjustable amplitude and phase responses, whose reflection pattern over time is deterministic and adaptively optimized based on \gls{csi}.
-		\gls{ris} smartly reflects the surrounding \gls{rf} waves to customize the wireless propagation environment for signal enhancement, interference suppression, scattering enrichment and non-line-of-sight bypassing \cite{Wu2021b}.
-		In summary, \gls{mbc}/\gls{bbc} (resp.
+	% \begin{subsection}{Fundamentals}
+	\IEEEPARstart{F}{uture} wireless network is envisioned to provide high throughput, uniform coverage, pervasive connectivity, heterogeneous control, and cognitive intelligence for trillions of low-power devices.
+	% As a mature low-power communication technique,
+	\gls{bc} separates a transmitter into a \gls{rf} carrier emitter with power-hungry elements (e.g., synthesizer and amplifier) and an information-bearing node with power-efficient components (e.g., harvester and modulator) \cite{Boyer2014}.
+	% In particular, the node harvests energy from impinging wave and embeds information over scattered signal, and
+	The receiver (reader) can be either co-located or separated with the carrier emitter, known as \gls{mbc} and \gls{bbc} in Fig.~\subref*{fg:mbc} and \subref*{fg:bbc}, respectively.
+	Relevant applications such as \gls{rfid} \cite{Dobkin2012,Landt2005} and passive sensor network \cite{Vannucci2008,Assimonis2016} have been extensively researched, standardized, and commercialized to embrace \gls{ioe}.
+	However, conventional backscatter nodes only respond when externally inquired by a nearby reader.
+	% To tackle this, \cite{Liu2013b} proposed \gls{ambc} where battery-free nodes recycle ambient signals (e.g., radio, television and Wi-Fi) to harvest energy and establish connection in between.
+	\gls{ambc} in Fig.~\subref*{fg:ambc} was proposed a decade ago where battery-free nodes recycle ambient signals (e.g., radio, television and Wi-Fi) to harvest energy and establish connections \cite{Liu2013b}.
+	It does not require dedicated power source, carrier emitter, or frequency spectrum, but the backscatter decoding is subject to the strong interference from the primary (legacy) link.
+	% Cooperative \gls{ambc} that employs a co-located receiver to decode both coexisting links was considered in \cite{Yang2018}, and the rate and error performance are evaluated for various detection schemes.
+	To tackle this, cooperative \gls{ambc} \cite{Yang2018} employs a co-located receiver to decode both coexisting links and the concept was further refined as \gls{sr} in Fig.~\subref*{fg:sr} \cite{Liang2020}.
+	% Specifically, the active transmitter generates \gls{rf} wave carrying primary information, the passive node ride extra information over the scattered signal, and the cooperative receiver jointly, individually, or sequentially decodes both links.
+	Specifically, the active transmitter generates \gls{rf} wave carrying primary information, the passive node creates a rich-scattering environment and rides its own information, and the co-located receiver cooperatively decodes both links.
+	In those \gls{bc} applications, the scatter node is considered as an \emph{information source} and the reflection pattern depends exclusively on the information symbol.
+	% Those \gls{bc} applications employ scatter nodes as pure information sources, and the active primary transmission (if it exists) can be influenced by the randomness of backscatter modulation.
+	On the other hand, \gls{ris} in Fig.~\subref*{fg:ris} is a smart signal reflector with numerous passive elements of adjustable phase shifts.
+	It customizes the wireless environment for signal enhancement, interference suppression, scattering enrichment, and/or non-line-of-sight bypassing \cite{Wu2021b}.
+	Each \gls{ris} element is considered as a \emph{channel adaptor} and the reflection pattern depends exclusively on the \gls{csi}.
+	% In summary, \gls{mbc}/\gls{bbc} (resp.
 \gls{ris}) involves a \emph{single} passive backscatter (resp.
@@
 modulated signal).
-		On the other hand, \gls{ambc} (resp. \gls{sr}) involves \emph{coexisting} active primary and passive backscatter links in a competitive (resp. collaborative) relationship.
-		In \gls{ambc}, the backscatter link only needs to know the basic information (e.g., operating frequency) of the primary link, while the primary link may be completely unaware of the backscatter link.
-		In \gls{sr}, relevant \gls{csi} is exploited at the co-located receiver for cooperative decoding, and may also be exploited at the primary transmitter for cooperative active beamforming.
-		A comparison of scattering applications is summarized in Table~\ref{tb:scattering_applications}.
+	% On the other hand, \gls{ambc} (resp. \gls{sr}) involves \emph{coexisting} active primary and passive backscatter links in a competitive (resp. collaborative) relationship.
+	% In \gls{ambc}, the backscatter link only needs to know the basic information (e.g., operating frequency) of the primary link, while the primary link may be completely unaware of the backscatter link.
+	% In \gls{sr}, relevant \gls{csi} is exploited at the co-located receiver for cooperative decoding, and may also be exploited at the primary transmitter for cooperative active beamforming.
 
@@
 			Illustration of scattering applications.
-				For each, the blue flow(s) constitute the active primary link while the magenta/green flow denotes the passive backscatter link.
+			The blue flow(s) constitutes the primary link while the magenta/green flow denotes the backscatter link.
 		}
@@
 			\hiderowcolors
-			                                                        & \gls{mbc}/\gls{bbc} & \gls{ambc}                              & \gls{sr}                                              & \gls{ris}           & RIScatter                                                               \\ \midrule
+			                                       & \gls{mbc}/\gls{bbc} & \gls{ambc}                  & \gls{sr} (large spreading factor)               & \gls{ris}           & RIScatter                                                   \\ \midrule
 			\showrowcolors
-			% Coexisting link(s)                                              & 1                   & 2 (competitive)             & 2 (collaborative)                                     & 1                   & 2 (collaborative)                                                       \\
-			Information link(s)                                     & Passive backscatter & Active-passive coexisting (competitive) & Active-passive coexisting (collaborative)             & Active primary      & Active-passive coexisting (collaborative)                               \\
-			% Primary/Backscatter modulation                                  & No/Yes              & Yes/Yes                     & Yes/Yes                                               & Yes/No              & Yes/Yes                                                                 \\
-			Primary impact on backscatter detection                 & Carrier             & Multiplicative interference             & Spreading code or multiplicative interference         & ---                 & Energy uncertainty                                                      \\
-			Backscatter impact on primary detection                 & ---                 & Multiplicative interference             & \gls{csi} uncertainty or multiplicative interference  & Passive beamforming & Dynamic passive beamforming                                             \\
-			Collaborative devices based on \gls{csi}                & ---                 & ---                                     & Co-located receiver (potentially primary transmitter) & ---                 & Primary transmitter, scatter nodes, and co-located receiver             \\
-			Cooperative decoding strategy                           & ---                 & No                                      & Usually \gls{sic} from primary to backscatter         & ---                 & No \gls{sic}, backscatter detection as part of primary channel training \\
-			Primary detection                                       & ---                 & Semi-coherent                           & Semi-coherent                                         & Coherent            & Coherent                                                                \\
-			Backscatter detection                                   & Coherent            & Semi-coherent                           & Coherent                                              & ---                 & Semi-coherent                                                           \\
-			Reflection pattern over time depends on                 & Information source  & Information source                      & Information source                                    & \gls{csi}           & Information source, \gls{csi}, and \gls{qos}                            \\
-			Reflection state (i.e., backscatter input) distribution & Equiprobable        & Equiprobable                            & Equiprobable or Gaussian                              & Degenerate          & Flexible                                                                \\
-			Load-switching speed                                    & Fast                & Fast or slow                            & Very slow                                             & Quasi-static        & Arbitrary                                                               \\ \bottomrule
+			Information link(s)                    & Backscatter         & Coexisting                  & Coexisting                                      & Primary             & Coexisting                                                  \\
+			Primary signal on backscatter decoding & Carrier             & Multiplicative interference & Spreading code                                  & ---                 & Energy uncertainty                                          \\
+			Backscatter signal on primary decoding & ---                 & Multiplicative interference & \gls{csi} uncertainty                           & Passive beamforming & Dynamic passive beamforming                                 \\
+			Cooperative devices                    & ---                 & No                          & Primary transmitter and co-located receiver     & ---                 & Primary transmitter, scatter nodes, and co-located receiver \\
+			Sequential decoding                    & ---                 & No                          & Primary-to-backscatter, \gls{sic} and \gls{mrc} & ---                 & Backscatter-to-primary, no \gls{sic}/\gls{mrc}              \\
+			% Primary decoding                        & ---                 & Semi-coherent               & Semi-coherent                                   & Coherent            & Coherent                                                    \\
+			% Backscatter decoding                    & Coherent            & Semi-coherent               & Coherent                                        & ---                 & Semi-coherent                                               \\
+			Reflection pattern depends on          & Information source  & Information source          & Information source                              & \gls{csi}           & Information source, \gls{csi}, and \gls{qos}                \\
+			Reflection state distribution          & Equiprobable        & Equiprobable                & Equiprobable or Gaussian                        & Degenerate          & Flexible                                                    \\
+			Load-switching speed                   & Fast                & Slow                        & Slow                                            & Quasi-static        & Arbitrary                                                   \\ \bottomrule
 		\end{tabularx}
@@
 
-	\begin{subsection}{Related Works}
-		Similar to \gls{cr}, active-passive coexisting networks can be classified into commensal, parasitic, and competitive relationships, whose instantaneous rates, power schemes, and outage probabilities were acquired in \cite{Guo2019b,Ding2020}.
-		% To evaluate the performance of cooperative receivers, \cite{Yang2018} derived the bit error rates of \gls{ml}, linear and \gls{sic} detectors for flat fading channels, and proposed a low-complexity detector for frequency-selective fading channels.
-		% However, it only considered the case where the primary and backscatter symbols of the same period are perfectly aligned in time.
-		Joint \gls{ml} decoding provides the best error performance but requires prohibitive computational complexity especially for high-order modulations \cite{Yang2018}.
-		Indeed, active-passive coexisting networks have three special and important properties:
-		1) primary and backscatter symbols are superimposed by \emph{double modulation} (i.e., multiplication coding);
-		2) backscatter signal strength is much weaker than primary due to the \emph{double fading} effect;
-		3) backscatter \emph{symbol period} is longer than primary due to the load switching constraint.
-		% ! double modulation, double fading, symbol period difference
+	% \begin{subsection}{Related Works}
+	As a special case of \gls{cr}, active and passive transmissions coexist and interplay in \gls{ambc} and \gls{sr}.
+	Such a coexistence is classified into commensal (overlay), parasitic (underlay), and competitive paradigms, and their achievable rate and outage performance were investigated in \cite{Guo2019b,Ding2020}.
+	For the co-located cooperative receiver, the \gls{ber} performance of \gls{ml}, linear, and \gls{sic} detectors are derived over flat fading channels \cite{Yang2018}.
+	However, the work assumed equal symbol period and perfect synchronization for primary and backscatter links.
+	Importantly, active-passive coexisting networks have three special and important properties:
+	\begin{enumerate}
+		\item Primary and backscatter symbols are superimposed by \emph{double modulation} (i.e., multiplication coding);
+		\item Backscatter signal strength is much weaker than primary due to the \emph{double fading} effect;
+		\item The spreading factor (i.e., backscatter symbol period over primary) is usually large\footnote{The load-switching interval of low-power backscatter modulators is usually \num{0.1} to \qty{10}{\us} \cite{Torres2021}, accounting for a typical spreading factor between \num{10} and \num{e3}.}.
+	\end{enumerate}
 	The second property motivated \cite{Long2020a,Liang2020,Guo2019b,Ding2020,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Yang2018,Han2021,Zhang2022} to view \gls{sr} as a multiplicative \gls{noma} and perform \gls{sic} from primary to backscatter link.
-		During primary decoding, the randomness of backscatter modulation can be modelled as either channel uncertainty or multiplicative interference, when the spreading factor (i.e., backscatter-over-primary symbol period ratio) $N$ is large or small, respectively\footnote{For state-of-the-art low-power \gls{rfid} tags, the load-switching speed usually varies between \num{100}s of \unit{\kHz} to \num{10}s of \unit{\MHz} \cite{Torres2021}, corresponding to a typical spreading factor between \num{10} and \num{1000}.}.
-		Such a \gls{sic} receiver is operation-intensive and \gls{csi}-sensitive because it involves $N$ re-encoding, precoding, subtraction together with a time-domain \gls{mrc} to decode each backscatter symbol.
-		When the spreading factor is sufficiently large (i.e., commensal \gls{sr}), the average primary achievable rate under semi-coherent detection\footnote{In this paper, semi-coherent detection refers to the primary/backscatter decoding based on known \gls{csi} and unknown backscatter/primary symbols.} asymptotically approaches its coherent counterpart, and both links may be decoded in an interference-free manner \cite{Long2020a}.
-		On the other hand, efficient backscatter multiple access design remains an open issue for \gls{bc}.
-		\cite{Xu2021a} proposed a \gls{noma}-based \gls{sr} where the \gls{sic} order depends on the backscatter channel strength, but the performance deteriorates fast as the number of nodes increases.
-		\gls{tdma}-based \gls{sr} was also considered in \cite{Yang2021a} where each node transmits information during its dedicated slot and harvests energy otherwise.
-		It enables adaptive transmission time and reflection ratio design but introduces extra coordination cost.
-		\cite{Vougioukas2019} modifies the load-switching speed to shift the scattered signal to the desired frequency band.
-		This enables backscatter \gls{fdma} at the cost of larger bandwidth and higher power consumption at the scatter nodes.
-		To reduce the coordination cost, \cite{Han2021} proposed a random code-assisted multiple access for \gls{sr} and evaluated the asymptotic \gls{sinr} using random matrix theory.
-		This code-domain solution suffers from the near-far problem and imperfect synchronization, both being severe in \gls{bc}.
-
-		Conventional \gls{ris} design with fixed reflection coefficients during each channel block has been extensively studied in communication, sensing, and power literatures \cite{Wu2018,Zhang2019a,Lin2022,Liu2022,Feng2022,Zhao2022}.
-		On the other hand, dynamic \gls{ris} with independent reflection patterns in different time slots has gained recent attentions in multi-user and multi-purpose wireless networks.
-		The concept was first proposed in \cite{Yang2020} to fine-tune the \gls{ofdm} resource blocks, then extended to the downlink power and uplink information phases of \gls{wpcn} \cite{Wu2021,Wu2021d,Hua2022a}.
-		It introduces artificial channel diversity and enables flexible resource allocation, but misses the opportunity to encode its own message.
-		\gls{ris} can also be used as a transmitter when placed in the near field of a carrier emitter, and prototypes have been implemented for \gls{psk} \cite{Tang2019a} and \gls{qam} \cite{Dai2020a}.
-		From an information-theoretic perspective, \cite{Karasik2020} reported that using \gls{ris} as a naive passive beamformer to maximize the receive \gls{snr} is generally rate-suboptimal for finite-input constellations.
-		Instead, the capacity of \gls{ris}-aided channel is achieved by joint transmitter-\gls{ris} encoding, and even layered encoding with pilots can outperform passive beamforming at high \gls{snr}.
-		It inspired \gls{ris}-empowered \gls{bc} \cite{Liu2019d,Bereyhi2020,Xu2020b,Zhang2021d,Hu2021b,Hua2022,Basar2020,Ma2020a,Yuan2021,Hu2021a} to combine passive beamforming and backscatter modulation in the overall reflection pattern.
+	During primary decoding, the backscatter signal can be modelled as channel uncertainty or multiplicative interference when the spreading factor is large or small, respectively.
+	Decoding each backscatter symbol also requires multiple \gls{sic} followed by a \gls{mrc} and is operation-intensive and \gls{csi}-sensitive.
+	% Such a \gls{sic} receiver is operation-intensive and \gls{csi}-sensitive because it involves $N$ re-encoding, precoding, subtraction together with a time-domain \gls{mrc} to decode each backscatter symbol.
+	When the spreading factor is sufficiently large, the primary achievable rate under semi-coherent detection\footnote{In this paper, semi-coherent detection refers to the primary/backscatter decoding with known \gls{csi} and unknown backscatter/primary symbols.} asymptotically approaches its coherent counterpart and both links are decoded interference-free \cite{Long2020a}.
+	% However, it significantly increases \gls{sic} operations per backscatter symbol and severely limits the backscatter \emph{throughput}.
+	However, it severely limits the backscatter throughput and requires more \gls{sic} per backscatter symbol.
+
+	% On the other hand, efficient backscatter multiple access design remains an open issue for \gls{bc}.
+	% \cite{Xu2021a} proposed a \gls{noma}-based \gls{sr} where the \gls{sic} order depends on the backscatter channel strength, but the performance deteriorates fast as the number of nodes increases.
+	% \gls{tdma}-based \gls{sr} was also considered in \cite{Yang2021a} where each node transmits information during its dedicated slot and harvests energy otherwise.
+	% It enables adaptive transmission time and reflection ratio design but introduces extra coordination cost.
+	% \cite{Vougioukas2019} modifies the load-switching speed to shift the scattered signal to the desired frequency band.
+	% This enables backscatter \gls{fdma} at the cost of larger bandwidth and higher power consumption at the scatter nodes.
+	% To reduce the coordination cost, \cite{Han2021} proposed a random code-assisted multiple access for \gls{sr} and evaluated the asymptotic \gls{sinr} using random matrix theory.
+	% This code-domain solution suffers from the near-far problem and imperfect synchronization, both being severe in \gls{bc}.
+
+	% A comparison of scattering applications is summarized in Table~\ref{tb:scattering_applications}.
+
+	On the other hand, static \gls{ris} design with fixed reflection pattern per channel block has been extensively studied in wireless communication, sensing, and power literature \cite{Wu2018,Zhang2019a,Lin2022,Liu2022,Feng2022,Zhao2022}.
+	Dynamic \gls{ris} performs time sharing between different phase shifts and introduces artificial channel diversity within each channel block.
+	It was first proposed to fine-tune the \gls{ofdm} resource blocks \cite{Yang2020} then extended to the downlink power and uplink information phases of \gls{wpcn} \cite{Wu2021,Wu2021d,Hua2022a}.
+	However, dynamic \gls{ris} carries no information since the reflection state at each time slot is known to the receiver.
+	\gls{ris} can also be used as an index-modulated information source and prototypes are already available for \gls{psk} \cite{Tang2019a} and \gls{qam} \cite{Dai2020a}.
+	From an information-theoretic perspective, the authors of \cite{Karasik2020} reported that joint transmitter-\gls{ris} encoding achieves the capacity of \gls{ris}-aided finite-input channel and using \gls{ris} as a naive passive beamformer to maximize the receive \gls{snr} is generally suboptimal.
+	This inspired \gls{ris}-empowered \gls{bc} \cite{Liu2019d,Bereyhi2020,Xu2020b,Zhang2021d,Hu2021b,Hua2022,Basar2020,Ma2020a,Yuan2021,Hu2021a} to combine passive beamforming and backscatter modulation in the overall reflection pattern.
 	In particular, \emph{symbol level precoding} maps the information symbols to the optimized \gls{ris} coefficient sets \cite{Liu2019d,Bereyhi2020}, \emph{overlay modulation} superposes the information symbols over a common auxiliary matrix \cite{Xu2020b,Zhang2021d,Hu2021b,Hua2022}, \emph{spatial modulation} switches between the reflection coefficient sets that maximize \gls{snr} at different receive antennas \cite{Basar2020,Ma2020a,Yuan2021}, and \emph{index modulation} employs dedicated reflection elements (resp.
@@
 	However, those joint designs incur advanced hardware architecture and high optimization complexity.
-		Relevant literatures also consider either \emph{Gaussian} codebook \cite{Guo2019b,Ding2020,Long2020a,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Hu2021b} that is impractical for low-power nodes, or finite \emph{equiprobable} inputs \cite{Yang2018,Liang2020,Han2021,Zhang2022,Liu2019d,Bereyhi2020,Xu2020b,Zhang2021d,Hua2022,Basar2020,Ma2020a,Yuan2021,Hu2021a} that does not fully exploit the \gls{csi} and signal properties of active-passive coexisting networks.
-	\end{subsection}
-
-	\begin{subsection}{Contributions}
-		\emph{First,} we propose RIScatter as a novel scatter protocol that unifies \gls{bc} and \gls{ris} by adaptive reflection state (i.e., backscatter input) distribution design.
-		As shown in Fig.~\subref*{fg:riscatter}, one or more passive RIScatter nodes ride over an active transmission and smartly scatters the incident wave to simultaneously engineer the primary channel and modulate its own information, while a co-located receiver cooperatively decodes both coexisting links.
-		The reflection pattern over time is neither fully random like \gls{bc} nor fully deterministic like \gls{ris}, but semi-randomly chosen with the guidance of reflection state distribution, whose design accommodates the impact of information source, \gls{csi}, and \gls{qos} of both links.
-		Such an adaptive backscatter channel coding boils down to the degenerate distribution of \gls{ris} when the primary link is prioritized, and outperforms the uniform distribution of line-coded \gls{bc} (by accounting the \gls{csi}) when the backscatter link is prioritized.
-		Besides, when multiple RIScatter nodes are co-located, joint encoding can further increase the total backscatter rate.
-		RIScatter exploits the transmitter-scatter-receiver path for simultaneous backscatter modulation and dynamic passive beamforming, and can smoothly transition in between under different \gls{qos}.
-		However, such a novel scatter protocol encounters two major challenges, namely the cooperative receiver design and the adaptive backscatter input distribution design.
-		This is the first paper to unify \gls{bc} and \gls{ris} from the perspective of reflection state distribution.
-
-		\emph{Second,} we address the first challenge by proposing a practical receiver that accommodates the double fading, double modulation, and symbol period difference of active-passive coexisting networks.
-		Since joint decoding involves high complexity while individual decoding can be inefficient (neither cooperative nor exploiting signal properties), most relevant literatures consider a sequential primary-backscatter decoding based on \gls{sic}.
-		Specifically, the decoding of each backscatter symbol requires $N$ re-encoding, precoding, subtraction together with a time-domain \gls{mrc}, which can be operation-intensive and \gls{csi}-sensitive.
-		In contrast, the proposed RIScatter receiver semi-coherently decodes the backscatter symbol from the accumulated receive energy, re-encodes to recover the exact reflection pattern, and combine it with relevant \gls{csi} to determine the transmitter-scatter-receiver path response.
-		Thanks to the double modulation and symbol period difference, the backscatter symbol can be modelled within primary channel (similar to \gls{ris}) rather than being re-precoded and cancelled, and the semi-coherent energy-based backscatter detection indeed becomes part of primary channel training.
-		The strategy is suitable for arbitrary primary sampling rate and backscatter load-switching speed (i.e., arbitrary spreading factor).
-		This is the first paper to consider such a sequential backscatter-primary decoding and treat semi-coherent backscatter detection as part of primary channel training.
+	Relevant literature also considers either Gaussian codebook \cite{Guo2019b,Ding2020,Long2020a,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Hu2021b} that is impractical for low-power nodes or finite equiprobable inputs \cite{Yang2018,Liang2020,Han2021,Zhang2022,Liu2019d,Bereyhi2020,Xu2020b,Zhang2021d,Hua2022,Basar2020,Ma2020a,Yuan2021,Hu2021a} that does not fully exploit the \gls{csi} and properties of active-passive coexisting networks.
+	% \end{subsection}
+	Those problems are addressed in this paper and the contributions are summarized below.
+
+	% \begin{subsection}{Contributions}
+	% \emph{First,} we propose RIScatter as a novel scatter protocol that unifies \gls{bc} and \gls{ris} by adaptive reflection state (backscatter input) distribution design.
+	% \emph{First,} we propose RIScatter as a novel scatter protocol that simultaneously modulates the nodes information and engineers the wireless channel via adaptive reflection state (backscatter input) distribution design.
+	\emph{First,} we propose RIScatter as a novel scatter protocol that simultaneously modulates the node information and engineers the wireless channel via adaptive reflection state (backscatter input) distribution design.
+	The concept is shown in Fig.~\subref*{fg:riscatter} where the message of one or more RIScatter nodes and a primary transmitter are sequentially decoded by a co-located receiver.
+	% The reflection pattern is random with the guidance of input distribution as a joint function of the information source, \gls{csi}, and \gls{qos}
+	% The reflection pattern is a discrete random variable with probability mass function
+	% (co-located or dispersed)
+	Each reflection state simultaneously acts as information codeword and passive beamforming codeword.
+	The reflection pattern of each node is randomly chosen with the guidance of reflection state distribution, which is designed as a joint function of the information source, \gls{csi}, and \gls{qos}.
+	% That is, each reflection state simultaneously acts as information codeword and passive beamforming codeword (symbol-level passive precoding).
+	% Since each reflection state simultaneously acts as information codeword and passive beamforming codeword (symbol-level passive precoding).
+	Such an adaptive channel coding boils down to the degenerate distribution of \gls{ris} when the primary link is prioritized, and outperforms the uniform distribution of line-coded \gls{bc} (by accounting the \gls{csi}) when the backscatter link is prioritized.
+	% Joint and independent encoding are available when multiple RIScatter nodes are
+	Multiple RIScatter nodes can be co-located with joint encoding or dispersed with independent encoding.
+	% The reflection state is neither fully random (cf. \gls{bc}) nor fully deterministic (cf. \gls{ris}), but semi-random in reflection state distribution.
+	% RIScatter exploits the transmitter-scatter-receiver path for simultaneous backscatter modulation and dynamic passive beamforming, and can smoothly transition in between under different \gls{qos}.
+	% A comparison of RIScatter to \gls{bc} and \gls{ris} is summarized in Table~\ref{tb:scattering_applications}.
+	Table~\ref{tb:scattering_applications} compares RIScatter to \gls{bc} and \gls{ris}.
+	However, two major challenges for RIScatter are the cooperative receiver design and the backscatter input distribution design.
+	% such a novel scatter protocol encounters two major challenges, namely the cooperative receiver design and the adaptive backscatter input distribution design.
+	This is the first paper to unify \gls{bc} and \gls{ris} from the perspective of input distribution.
+
+	\emph{Second,} we address the first challenge and propose a practical receiver that accommodates the properties of active-passive coexisting networks.
+	It semi-coherently decodes the backscatter information by energy detection, recovers the exact reflection pattern, and coherently decodes the primary link.
+	% Double modulation enables symbol-level passive precoding such that the
+	Once successfully decoded, the multiplicative backscatter interference can be modelled as dynamic passive beamforming (rather than being re-precoded and cancelled), and thus the energy detection becomes part of channel training.
+	The proposed receiver significantly improves backscatter throughput since it is suitable for arbitrary input distribution and spreading factor.
+	This is the first paper to consider practical backscatter-primary decoding and treat semi-coherent backscatter detection as part of primary channel training.
 
@@
 
-		\emph{Fourth,} we provide numerical results to demonstrate the benefits of RIScatter and proposed algorithms.
-		The observations include:
-		1) adaptive reflection state distribution design can flexibly transition between backscatter modulation and passive beamforming;
-		2) when the primary link is prioritized, input distribution becomes degenerate and RIScatter nodes coincide with discrete \gls{ris};
-		3) when the backscatter link is prioritized, adaptive RIScatter encoding achieves higher backscatter rate than conventional line-coded \gls{bc} with equiprobable inputs;
-		4) co-located RIScatter nodes can further leverage total backscatter rate by joint encoding;
-		5) the proposed receiver maintains the passive beamforming benefit and provides comparable backscatter rate to \gls{sic}-based \gls{sr}, with re-encoding costs reduced to $1/N$ and no re-precoding/cancellation;
-		6) it also supports scatter nodes with faster load-switching speed for potentially higher throughput;
-		7) \gls{pgd} active beamformer effectively increases the primary (resp.
+	% \emph{Fourth,} we provide numerical results to demonstrate the benefits of RIScatter and proposed algorithms.
+	% The observations include:
+	% 1) adaptive reflection state distribution design can flexibly shift between backscatter modulation and passive beamforming;
+	% 2) when the primary link is prioritized, input distribution becomes degenerate and RIScatter nodes coincide with discrete \gls{ris};
+	% 3) when the backscatter link is prioritized, adaptive RIScatter encoding achieves higher backscatter rate than conventional line-coded \gls{bc} with equiprobable inputs;
+	% 4) co-located RIScatter nodes can further leverage total backscatter rate by joint encoding;
+	% 5) the proposed receiver maintains the passive beamforming benefit and provides comparable backscatter rate to \gls{sic}-based \gls{sr}, with re-encoding costs reduced to $1/N$ and no re-precoding/cancellation;
+	% 6) it also supports scatter nodes with faster load-switching speed for potentially higher throughput;
+	% 7) \gls{pgd} active beamformer effectively increases the primary (resp.
 backscatter) rate by boosting the receive \gls{snr} (resp.
 widening the energy gap under different reflection states), and can smoothly transition in between under different \gls{qos};
-		8) distribution-aware backscatter detectors provide higher backscatter rate than the conventional \gls{ml} detector.
-	\end{subsection}
+	% 8) distribution-aware backscatter detectors provide higher backscatter rate than the conventional \gls{ml} detector.
+	% \end{subsection}
 
@@
 	$\boldsymbol{0}$ and $\boldsymbol{1}$ denote zero and one array of appropriate size, respectively.
-$\mathbb{I}^{x \times y}$, $\mathbb{R}_+^{x \times y}$, and $\mathbb{C}^{x \times y}$ denote the real unit, real nonnegative, and complex spaces of dimension $x \times y$, respectively.
+$\mathbb{I}^{x \times y}$, $\mathbb{R}_+^{x \times y}$, and $\mathbb{C}^{x \times y}$ denote the unit, real nonnegative, and complex spaces of dimension $x \times y$, respectively.
 	$j$ denotes the imaginary unit.
@@
 	$\mathrm{card}(\cdot)$ returns the cardinality of a set.
-	$(\cdot)^*$, $(\cdot)^\mathsf{T}$, $(\cdot)^\mathsf{H}$, $\lvert{\cdot}\rvert$, and $\lVert{\cdot}\rVert$ denote the conjugate, transpose, conjugate transpose, absolute value, and Euclidean norm operators, respectively.
+	$(\cdot)^*$, $(\cdot)^\mathsf{T}$, $(\cdot)^\mathsf{H}$, $\lvert{\cdot}\rvert$, and $\lVert{\cdot}\rVert$ denote the conjugate, transpose, conjugate transpose (Hermitian), absolute value, and Euclidean norm operators, respectively.
 	$(\cdot)^{(r)}$ and $(\cdot)^{\star}$ denote the $r$-th iterated and optimal results, respectively.
@@
 	\end{equation}
-	where $\beta_m \in \mathbb{I}$ is the overall amplitude scattering ratio at state $m$.\footnote{Most existing \gls{ris} literatures assume lossless reflection $\beta_m=1$, $\forall m$.}
+	where $\beta_m \in \mathbb{I}$ is the overall amplitude scattering ratio at state $m$.\footnote{Most existing \gls{ris} literature assumes lossless reflection $\beta_m=1$, $\forall m$.}
 \end{section}
@@
 		We propose RIScatter in Fig.~\subref*{fg:riscatter} as a generalization of \gls{bc} and \gls{ris}, which involves coexisting active primary and passive backscatter links in a flexible and mutualistic manner.
-		RIScatter nodes leverage \gls{csi}- and \gls{qos}-based reflection state distribution design to smoothly transition between backscatter modulation and passive beamforming.
+		RIScatter nodes leverage \gls{csi}- and \gls{qos}-based reflection state distribution design to smoothly shift between backscatter modulation and passive beamforming.
 		Fig.~\ref{fg:riscatter_node} illustrates the block diagram, equivalent circuit, and scatter model of a RIScatter node.
@@
 		Let $x_k \in \mathcal{X} \triangleq \{c_1,\ldots,c_M\}$ be the coded backscatter symbol of node $k$ and $x_{\mathcal{K}} \triangleq (x_1,\ldots,x_K)$ be the backscatter symbol tuple of all nodes.
-		Due to double modulation, the primary equivalent channel is a function of backscatter symbol tuple\footnote{\eqref{eq:equivalent_channel_bc} and \eqref{eq:equivalent_channel_ris} are often used in \gls{bc} and \gls{ris} literatures, respectively.}
+		Due to double modulation, the primary equivalent channel is a function of backscatter symbol tuple\footnote{\eqref{eq:equivalent_channel_bc} and \eqref{eq:equivalent_channel_ris} are often used in \gls{bc} and \gls{ris} literature, respectively.}
 		\begin{subequations}
@@
 	The finite decision threshold domain $\mathcal{T}$ is obtained by $b$-bit uniform discretization over the critical interval defined by the confidence bounds of edge hypotheses (i.e., lower bound of $\mathcal{H}_1$ and upper bound of $\mathcal{H}_L$) with confidence $1-\epsilon$, and we choose $b=9$ and $\epsilon=\num{e-3}$.
-	All achievable rate points/regions are averaged over \num{1000} channel realizations.
+	All achievable rate points/regions are averaged over \num{e3} channel realizations.
 
@@
 			}
-			\caption{Typical achievable rate region/points of scattering applications for $Q=1$, $K=1$, $M=4$, $N=1000$, $\sigma_v^2=\qty{-40}{\dBm}$ and $r=\qty{2}{\meter}$.}
+			\caption{Typical achievable rate region/points of scattering applications for $Q=1$, $K=1$, $M=4$, $N=e3$, $\sigma_v^2=\qty{-40}{\dBm}$ and $r=\qty{2}{\meter}$.}
 			\label{fg:region_comparison}
@@
 			As $\rho$ increases, the primary equivalent \gls{snr} outweighs the backscatter energy difference in \eqref{eq:weighted_sum_mutual_information_explicit}, and \emph{\gls{pgd}} beamformer becomes closer to both \gls{mrt} schemes.
-			At $\rho=1$, \emph{\gls{pgd}} and \emph{E-\gls{mrt}} boil down to \gls{mrt} towards the deterministic primary equivalent channel as in \gls{ris} literatures \cite{Wu2019}.
+			At $\rho=1$, \emph{\gls{pgd}} and \emph{E-\gls{mrt}} boil down to \gls{mrt} towards the deterministic primary equivalent channel as in \gls{ris} literature \cite{Wu2019}.
 			Besides, the difference between \emph{E-\gls{mrt}} and \emph{D-\gls{mrt}} can be insignificant for dispersed RIScatter nodes.

### 2023-02-24 main.tex
:construction: Update contribution

@@
 	% To accommodate the characteristics of active-passive coexisting networks, we propose a practical \gls{sic}-free receiver
-	To reap the benefits of RIScatter, we also propose a co-located \gls{sic}-free receiver that semi-coherently decodes the backscatter information, recovers the reflection pattern, and coherently decodes the primary link.
+	To reap the benefits of RIScatter, we also propose a co-located \gls{sic}-free receiver that semi-coherently decodes the backscatter information, recovers the reflection pattern (and composite channel), and coherently decodes the primary link.
 	For a single-user multi-node RIScatter network, we characterize the achievable primary-(total-)backscatter rate region by designing the input distribution at scatter nodes, the active beamforming at the \gls{ap}, and the energy detection regions at the user.
@@
 	% (co-located or dispersed)
-	Each reflection state simultaneously acts as information codeword and passive beamforming codeword.
-	The reflection pattern of each node is randomly chosen with the guidance of reflection state distribution, which is designed as a joint function of the information source, \gls{csi}, and \gls{qos}.
+	Each reflection state simultaneously acts as an information codeword and a passive beamforming codeword.
+	The reflection pattern of each node is randomly chosen with the guidance of input distribution that is designed as a joint function of the information source, \gls{csi}, and \gls{qos}.
 	% That is, each reflection state simultaneously acts as information codeword and passive beamforming codeword (symbol-level passive precoding).
@@
 
-	\emph{Second,} we address the first challenge and propose a practical receiver that accommodates the properties of active-passive coexisting networks.
-	It semi-coherently decodes the backscatter information by energy detection, recovers the exact reflection pattern, and coherently decodes the primary link.
+	\emph{Second,} we address the first challenge and propose a practical receiver that semi-coherently decodes the backscatter information, recovers the exact reflection pattern (and composite channel), and coherently decodes the primary link.
+	% Energy detection is used to decode the multiplicative backscatter information under primary uncertainty, and disjoint decision regions are formulated
+	% Energy detection is used to decode the multiplicative backscatter information under primary uncertainty, and it divides the accumulated energy domain into disjoint decision regions to construct \gls{dmc}
+	% Energy detection is used for backscatter decoding that
+	We consider backscatter energy detection with disjoint decision regions and formulates a \gls{dmtmac}.
+	% Specifically, energy detection
+	to decode the multiplicative backscatter information under primary uncertainty, and it divides the accumulated energy domain into disjoint decision regions to construct \gls{dmc}
+	% , and we design disjoint detection regions to transform the \gls{dcmc} channel to \gls{dmtc}
+
+	Hence, the receiver can semi-coherently (under primary uncertainty) decode RIScatter nodes from the accumulated receive energy, re-encode to recover the exact reflection patterns, and combine those with cascaded \gls{csi} to determine the multipath response and model within the primary channel.
+	Such a backscatter-primary decoding enables simultaneous backscatter modulation and dynamic passive beamforming by only one energy comparison and re-encoding during each backscatter (instead of primary) block.
+
+	exploits the properties of active-passive coexisting networks and
+	% \emph{Second,} we address the first challenge and propose a practical receiver that exploits the three properties
+
+	It semi-coherently decodes the backscatter information, recovers the exact reflection pattern, and coherently decodes the primary link.
+	Thanks to the double modulation effect, once the multiplicative backscatter information is successfully decoded, the contribution is modelled within channel as dynamic passive beamforming rather than re-precoded and cancelled.
+
+	% The semi-coherent backscatter decoding is based on
+	% For the semi-coherent backscatter decoding, we
+	% Specifically, the backscatter decoding relys on energy
+	% we transform the discrete-input continuous-output backscatter channel
+	We use energy detection to decode the multiplicative backscatter information under primary uncertainty, and transform the
+
+	we transform the discrete-input continuous-output backscatter channel
+	the energy space is divided into disjoint decision regions associated with different hypothese
 	% Double modulation enables symbol-level passive precoding such that the
-	Once successfully decoded, the multiplicative backscatter interference can be modelled as dynamic passive beamforming (rather than being re-precoded and cancelled), and thus the energy detection becomes part of channel training.
+	The multiplicative backscatter information, once successfully decoded, can be modelled as dynamic passive beamforming (rather than being re-precoded and cancelled) and thus the energy detection becomes part of channel training.
 	The proposed receiver significantly improves backscatter throughput since it is suitable for arbitrary input distribution and spreading factor.
-	This is the first paper to consider practical backscatter-primary decoding and treat semi-coherent backscatter detection as part of primary channel training.
-
-	\emph{Third,} we address the second challenge by considering a specific scenario where multiple co-located/dispersed RIScatter nodes ride over an active point-to-point \gls{miso} transmission to perform backscatter modulation and dynamic passive beamforming towards a nearby user.
+	This is the first paper to consider practical backscatter-primary decoding scheme at the co-located receiver.
+
+	\emph{Third,} we address the second challenge and
+
+	by considering a specific scenario where multiple co-located/dispersed RIScatter nodes ride over an active point-to-point \gls{miso} transmission to perform backscatter modulation and dynamic passive beamforming towards a nearby user.
 	For a given \gls{qos}, we first express the primary and total backscatter rates as functions of \emph{input distribution} at RIScatter nodes, \emph{active beamforming} at the \gls{ap}, and \emph{backscatter decision regions} at the user.

### 2023-02-25 assets/illustration/input_distribution.tex
:construction: Update introduction

@@
 		\addplot[brown,fill=brown!30!white] coordinates {(-1,-1)};
-		\addplot[brown,fill=brown!30!white,postaction={pattern=north west lines},pattern color=.] coordinates {(1,0.125)};
-		\addplot[brown,fill=brown!30!white,postaction={pattern=north east lines},pattern color=.] coordinates {(2,0.625)};
-		\addplot[brown,fill=brown!30!white,postaction={pattern=vertical lines},pattern color=.] coordinates {(3,0.25)};
+		\addplot[brown,fill=brown!30!white,postaction={pattern=north west lines},pattern color=.] coordinates {(1,0.25)};
+		\addplot[brown,fill=brown!30!white,postaction={pattern=north east lines},pattern color=.] coordinates {(2,0.75)};
+		\addplot[brown,fill=brown!30!white,postaction={pattern=vertical lines},pattern color=.] coordinates {(3,0)};
 		\addplot[brown,fill=brown!30!white,postaction={pattern=horizontal lines},pattern color=.] coordinates {(4,0)};

### 2023-02-25 assets/illustration/time_structure.tex
:lipstick: Update illustrations
:construction: Update introduction

@@
 	\foreach \x in {0,...,7}{
-			\draw[teal,fill=teal!30!white,postaction={pattern=north west lines},pattern color=.] (0.5*\x,3) rectangle ++(0.5,0.25);
+			\draw[teal,fill=teal!25!white,postaction={pattern=north west lines},pattern color=.] (0.5*\x,3) rectangle ++(0.5,0.25);
 		}
 	\foreach \x in {8,...,15}{
-			\draw[teal,fill=teal!30!white,postaction={pattern=vertical lines},pattern color=.] (0.5*\x,3) rectangle ++(0.5,0.25);
+			\draw[teal,fill=teal!25!white,postaction={pattern=north east lines},pattern color=.] (0.5*\x,3) rectangle ++(0.5,0.25);
 		}
@@
 	\foreach \x in {0,...,15}{
-			\draw[red,fill=red!30!white,postaction={pattern=north east lines},pattern color=.] (0.5*\x,2) rectangle ++(0.5,0.25);
+			\draw[red,fill=red!25!white,postaction={pattern=north east lines},pattern color=.] (0.5*\x,2) rectangle ++(0.5,0.25);
 		}
@@
 	% RIScatter
-	\foreach \x in {0,...,7,12,13,...,15}{
-			\draw[brown,fill=brown!30!white,postaction={pattern=north east lines},pattern color=.] (0.5*\x,1) rectangle ++(0.5,0.25);
+	\foreach \x in {0,...,3}{
+			\draw[brown,fill=brown!25!white,postaction={pattern=north west lines},pattern color=.] (0.5*\x,1) rectangle ++(0.5,0.25);
 		}
-	\foreach \x in {8,...,11}{
-			\draw[brown,fill=brown!30!white,postaction={pattern=north west lines},pattern color=.] (0.5*\x,1) rectangle ++(0.5,0.25);
+	\foreach \x in {4,...,15}{
+			\draw[brown,fill=brown!25!white,postaction={pattern=north east lines},pattern color=.] (0.5*\x,1) rectangle ++(0.5,0.25);
 		}

### 2023-02-25 main.tex
:construction: Update introduction

--- 2023-02-24 main.tex
@@
 \newacronym{dmtmac}{DMTMAC}{Discrete Memoryless Thresholding Multiple Access Channel}
+\newacronym{dmmac}{DMMAC}{Discrete Memoryless Multiple Access Channel}
 \newacronym{dp}{DP}{Dynamic Programming}
@@
 \begin{IEEEkeywords}
-	Input distribution design, energy detection, \gls{sic}-free receiver, active-passive coexisting network, backscatter communication, reconfigurable intelligent surface, ambient backscatter communication, symbiotic radio.
+	Input distribution design, energy detection, \gls{sic}-free receiver, symbol-level precoding, active-passive coexisting network, backscatter communication, reconfigurable intelligent surface, ambient backscatter communication, symbiotic radio.
 \end{IEEEkeywords}
@@
 	The receiver (reader) can be either co-located or separated with the carrier emitter, known as \gls{mbc} and \gls{bbc} in Fig.~\subref*{fg:mbc} and \subref*{fg:bbc}, respectively.
-	Relevant applications such as \gls{rfid} \cite{Dobkin2012,Landt2005} and passive sensor network \cite{Vannucci2008,Assimonis2016} have been extensively researched, standardized, and commercialized to embrace \gls{ioe}.
+	Relevant applications such as \gls{rfid} \cite{Dobkin2012,Landt2005} and passive sensor network \cite{Vannucci2008,Assimonis2016} have been extensively researched, standardized, and commercialized to embrace the \gls{ioe}.
 	However, conventional backscatter nodes only respond when externally inquired by a nearby reader.
@@
 	% However, it significantly increases \gls{sic} operations per backscatter symbol and severely limits the backscatter \emph{throughput}.
-	However, it severely limits the backscatter throughput and requires more \gls{sic} per backscatter symbol.
+	However, it severely limits the backscatter throughput and requires numerous \gls{sic} per backscatter symbol.
 
@@
 	However, dynamic \gls{ris} carries no information since the reflection state at each time slot is known to the receiver.
-	\gls{ris} can also be used as an index-modulated information source and prototypes are already available for \gls{psk} \cite{Tang2019a} and \gls{qam} \cite{Dai2020a}.
+	\gls{ris} can also be used as an index-modulated information source and prototypes have been developed for \gls{psk} \cite{Tang2019a} and \gls{qam} \cite{Dai2020a}.
 	From an information-theoretic perspective, the authors of \cite{Karasik2020} reported that joint transmitter-\gls{ris} encoding achieves the capacity of \gls{ris}-aided finite-input channel and using \gls{ris} as a naive passive beamformer to maximize the receive \gls{snr} is generally suboptimal.
@@
 	% \begin{subsection}{Contributions}
-	% \emph{First,} we propose RIScatter as a novel scatter protocol that unifies \gls{bc} and \gls{ris} by adaptive reflection state (backscatter input) distribution design.
-	% \emph{First,} we propose RIScatter as a novel scatter protocol that simultaneously modulates the nodes information and engineers the wireless channel via adaptive reflection state (backscatter input) distribution design.
-	\emph{First,} we propose RIScatter as a novel scatter protocol that simultaneously modulates the node information and engineers the wireless channel via adaptive reflection state (backscatter input) distribution design.
-	The concept is shown in Fig.~\subref*{fg:riscatter} where the message of one or more RIScatter nodes and a primary transmitter are sequentially decoded by a co-located receiver.
-	% The reflection pattern is random with the guidance of input distribution as a joint function of the information source, \gls{csi}, and \gls{qos}
-	% The reflection pattern is a discrete random variable with probability mass function
-	% (co-located or dispersed)
-	Each reflection state simultaneously acts as information codeword and passive beamforming codeword.
-	The reflection pattern of each node is randomly chosen with the guidance of reflection state distribution, which is designed as a joint function of the information source, \gls{csi}, and \gls{qos}.
-	% That is, each reflection state simultaneously acts as information codeword and passive beamforming codeword (symbol-level passive precoding).
-	% Since each reflection state simultaneously acts as information codeword and passive beamforming codeword (symbol-level passive precoding).
-	Such an adaptive channel coding boils down to the degenerate distribution of \gls{ris} when the primary link is prioritized, and outperforms the uniform distribution of line-coded \gls{bc} (by accounting the \gls{csi}) when the backscatter link is prioritized.
-	% Joint and independent encoding are available when multiple RIScatter nodes are
-	Multiple RIScatter nodes can be co-located with joint encoding or dispersed with independent encoding.
-	% The reflection state is neither fully random (cf. \gls{bc}) nor fully deterministic (cf. \gls{ris}), but semi-random in reflection state distribution.
-	% RIScatter exploits the transmitter-scatter-receiver path for simultaneous backscatter modulation and dynamic passive beamforming, and can smoothly transition in between under different \gls{qos}.
-	% A comparison of RIScatter to \gls{bc} and \gls{ris} is summarized in Table~\ref{tb:scattering_applications}.
+	\emph{First,} we propose RIScatter as a novel protocol that unifies \gls{bc} and \gls{ris} by adaptive reflection state (backscatter input) distribution design.
+	% \emph{First,} we propose RIScatter as a novel scatter protocol that simultaneously modulates the node information and engineers the wireless channel via adaptive reflection state (backscatter input) distribution design.
+	The concept is shown in Fig.~\subref*{fg:riscatter} where one or more RIScatter nodes ride over an active transmission and simultaneously modulate their information and engineer the wireless channel.
+	A co-located receiver cooperatively decodes both coexisting links and each reflection state simultaneously acts as information and passive beamforming codewords.
+	The reflection pattern of each node is semi-randomly chosen with the guidance of input distribution as a joint function of the information source, \gls{csi}, and \gls{qos}.
+	Such an adaptive channel coding boils down to the degenerate distribution of \gls{ris} when the primary link is prioritized, and outperforms the uniform distribution of \gls{bc} (by accounting the \gls{csi}) when the backscatter link is prioritized.
+	Joint and independent encoding are available when multiple RIScatter nodes are co-located and dispersed, respectively.
 	Table~\ref{tb:scattering_applications} compares RIScatter to \gls{bc} and \gls{ris}.
-	However, two major challenges for RIScatter are the cooperative receiver design and the backscatter input distribution design.
-	% such a novel scatter protocol encounters two major challenges, namely the cooperative receiver design and the adaptive backscatter input distribution design.
+	However, two major challenges for RIScatter are the practical receiver and input distribution design.
 	This is the first paper to unify \gls{bc} and \gls{ris} from the perspective of input distribution.
 
-	\emph{Second,} we address the first challenge and propose a practical receiver that accommodates the properties of active-passive coexisting networks.
-	It semi-coherently decodes the backscatter information by energy detection, recovers the exact reflection pattern, and coherently decodes the primary link.
-	% Double modulation enables symbol-level passive precoding such that the
-	Once successfully decoded, the multiplicative backscatter interference can be modelled as dynamic passive beamforming (rather than being re-precoded and cancelled), and thus the energy detection becomes part of channel training.
-	The proposed receiver significantly improves backscatter throughput since it is suitable for arbitrary input distribution and spreading factor.
-	This is the first paper to consider practical backscatter-primary decoding and treat semi-coherent backscatter detection as part of primary channel training.
-
-	\emph{Third,} we address the second challenge by considering a specific scenario where multiple co-located/dispersed RIScatter nodes ride over an active point-to-point \gls{miso} transmission to perform backscatter modulation and dynamic passive beamforming towards a nearby user.
-	For a given \gls{qos}, we first express the primary and total backscatter rates as functions of \emph{input distribution} at RIScatter nodes, \emph{active beamforming} at the \gls{ap}, and \emph{backscatter decision regions} at the user.
-	Then, we characterize the achievable rate region by optimizing those variables under different \gls{qos}.
-	Since the original problem is highly non-convex, we propose a suboptimal \gls{bcd} algorithm where the \gls{kkt} input distribution is numerically evaluated by limit of sequences, the active beamforming is iteratively updated by \gls{pgd} accelerated by \gls{bls}, and the decision regions are refined by existing sequential quantization methods for \gls{dmtc}.
-	Uniquely, we account for \gls{csi}, \gls{qos}, and backscatter constellation in those optimizations, and the proposed backscatter input distribution design is applicable to more general scenarios.
+	\emph{Second,} we address the first challenge and propose a practical receiver that semi-coherently decodes the backscatter information, recovers the reflection pattern, and coherently decodes the primary link.
+	We consider backscatter energy detection and formulate a \gls{dmmac} over disjoint decision regions.
+	Thanks to the double modulation and symbol-level passive precoding, the semi-coherent backscatter decoding also acts as part of channel training.
+	Once the backscatter information is successfully decoded, its contribution can be modelled within composite channel as dynamic passive beamforming rather than re-precoded and cancelled.
+	It requires only one energy comparison and re-encoding per backscatter symbol and is much efficient than conventional decoding based on \gls{sic} and \gls{mrc}.
+	It is also suitable for arbitrary input distribution and spreading factor, which significantly improves backscatter throughput.
+	This is the first paper to consider practical backscatter-primary decoding scheme to exploit dynamic passive beamforming at the co-located receiver.
+
+	\emph{Third,} we address the second challenge and consider a single-user multi-node \gls{miso} scenario.
+	We characterize the achievable primary-(total-)backscatter rate region by optimizing the input distribution at RIScatter nodes, the active beamforming at the \gls{ap}, and the energy decision regions at the user under different \gls{qos}.
+	A \gls{bcd} algorithm is proposed where the \gls{kkt} input distribution is numerically evaluated by limit of sequences, the active beamforming is optimized by \gls{pgd}, and the decision regions are refined by existing sequential quantizer for \gls{dmtc}.
+	Uniquely, we consider \gls{csi}, \gls{qos}, and backscatter constellation in the optimization and the input distribution result is applicable to general detection schemes.
 	This is also the first paper to reveal the importance of backscatter input distribution and decision region designs in active-passive coexisting networks.
@@
 
-\begin{section}{Scattering Principles}
-	\gls{rf} wave scattering and reflecting can be described by a unified model and realized by {variable-load antennas} or {programmable metamaterial} \cite{Liang2022}.
-	An antenna-based scatterer usually consists of an integrated antenna, a load-switching modulator, an energy harvester, and on-chip components (e.g., microcontroller and sensors) \cite{Dobkin2012}.
-	It first receives the impinging signals, then reradiates some back to the space and dissipates the remaining.
-	In comparison, a typical metamaterial-based scatterer comprises an outer metamaterial layer of numerous sub-wavelength metallic/dielectric patches (with tunable permittivity/permeability), a middle copper plate layer that avoids leakage, an inner circuit board layer that adjusts patch responses, and an integrated microcontroller/\glsentryshort{fpga} for coordination and control \cite{Wu2020}.
-	Ideally, it reflects the wave at the space-metamaterial boundary without receiving them and mainly applies a phase shift.
-	In practice, both types of scatterers have {finite} reflection states with non-zero reflection loss.
-	The scattered signal can be decomposed into a {structural} mode component that consistently contributes to environment multipath and can be modelled within \gls{csi}, and an \emph{antenna} mode component that depends on the impedance mismatch and can be used for backscatter modulation and/or passive beamforming \cite{Hansen1989}.
-	For an antenna-based (resp. metamaterial-based) scatter node with $M$ reflection states, the reflection coefficient at state $m \in \mathcal{M} \triangleq \{1,\ldots,M\}$ is
+\begin{section}{RIScatter}
+	\begin{subsection}{Principles}
+		\gls{rf} wave scattering/reflecting are often manipulated by passive antennas or programmable metamaterial \cite{Liang2022}.
+		% can be described by a unified signal model and implemented by passive antennas or programmable metamaterial \cite{Liang2022}.
+		% An antenna-based scatterer usually consists of an integrated antenna, a load-switching modulator, an energy harvester, and on-chip components (e.g., microcontroller and sensors) \cite{Dobkin2012}.
+		% An antenna-based scatterer usually consists of an integrated antenna, a load-switching modulator, an energy harvester, and on-chip components (e.g., microcontroller and sensors) \cite{Dobkin2012}.
+		An antenna scatterer first receives the impinging signals then reradiates some back to the space and dissipates the remaining \cite{Dobkin2012}.
+		% In comparison, a typical metamaterial-based scatterer comprises an outer metamaterial layer of numerous sub-wavelength metallic/dielectric patches (with tunable permittivity/permeability), a middle copper plate layer that avoids leakage, an inner circuit board layer that adjusts patch responses, and an integrated microcontroller/\glsentryshort{fpga} for coordination and control \cite{Wu2020}.
+		% In comparison, a typical metamaterial-based scatterer comprises an outer metamaterial layer of numerous sub-wavelength metallic/dielectric patches (with tunable permittivity/permeability), a middle copper plate layer that avoids leakage, an inner circuit board layer that adjusts patch responses, and an integrated microcontroller/\glsentryshort{fpga} for coordination and control \cite{Wu2020}.
+		An ideal metamaterial scatterer reflects the wave at the space-metamaterial boundary without receiving them and mainly applies a phase shift on top.
+		% In practice, both types of scatterers have {finite} reflection states with non-zero reflection loss.
+		% In general, the scattered signal consists of a structural mode component that consistently contributes to environment multipath and can be modelled within \gls{csi}, and an \emph{antenna} mode component that depends on the impedance mismatch and can be used for backscatter modulation and/or passive beamforming \cite{Hansen1989}.
+		In general, the scattered signal consists of a structural mode component that consistently contributes to environment multipath and an antenna mode component that depends on the impedance mismatch \cite{Hansen1989}.
+		The former is usually modelled within \gls{csi} while the latter is mainly used for backscatter modulation and/or passive beamforming.
+		For an antenna (resp. metamaterial) scatterer with $M$ reflection states, the reflection coefficient at state $m \in \mathcal{M} \triangleq \{1,\ldots,M\}$ is
 		\begin{equation}
@@
 		where $Z_m$ is the antenna load (resp. metamaterial unit) impedance at state $m$ and $Z$ is the antenna input (resp. medium characteristic) impedance.
-	\gls{bc} employ scatter nodes as information sources that \emph{randomly switching} between different states.
+		\gls{bc} treats scatterers as information sources that \emph{randomly} choosing the reflection state based on information symbol.
 		For $M$-ary \gls{qam}, constellation point $c_m$ maps to reflection coefficient $\Gamma_m$ by \cite{Thomas2012a}
@@
 		where $\alpha \in \mathbb{I}$ is the common amplitude scattering ratio at the direction of interest.
-	In contrast, \gls{ris} employ reflect elements as channel adaptors that \emph{deterministically choosing} the reflection state based on \gls{csi}.
+		In contrast, \gls{ris} treats scatterers as channel adaptors that \emph{deterministically} choosing the reflection state based on \gls{csi}.
 		For a \gls{ris} element with $M$ available states, phase shift $\theta_m$ maps to reflection coefficient $\Gamma_m$ by \cite{Wu2018}
@@
 		where $\beta_m \in \mathbb{I}$ is the overall amplitude scattering ratio at state $m$.\footnote{Most existing \gls{ris} literature assumes lossless reflection $\beta_m=1$, $\forall m$.}
-\end{section}
-
-\begin{section}{RIScatter}
-	\begin{subsection}{Concepts}
-		We propose RIScatter in Fig.~\subref*{fg:riscatter} as a generalization of \gls{bc} and \gls{ris}, which involves coexisting active primary and passive backscatter links in a flexible and mutualistic manner.
-		RIScatter nodes leverage \gls{csi}- and \gls{qos}-based reflection state distribution design to smoothly shift between backscatter modulation and passive beamforming.
-		Fig.~\ref{fg:riscatter_node} illustrates the block diagram, equivalent circuit, and scatter model of a RIScatter node.
-		It can be implemented by adding an integrated receiver \cite{Kim2021a} and adaptive encoder \cite{He2020e} to off-the-shelf passive \gls{rfid} tags.
+		% A natural question is, is it possible to use a scatterer
+		For a scatter node with given load impedance set, \gls{bc} employs $\Gamma_m$ only as an information codeword while \gls{ris} employs $\Gamma_m$ only as a passive beamforming codeword.
+		RIScatter generalizes both from a probabilistic perspective where each node \emph{semi-randomly} chooses the reflection state with the guidance of probability $P(\Gamma_m)$.
+		The input distribution is flexibly designed as a joint function of the information source, \gls{csi}, and \gls{qos}.
+		\gls{bc} and (static) \gls{ris} can be regarded as its extreme cases where the input distribution boils down to uniform and degenerate, respectively.
+		Fig.~\ref{fg:scatter_comparison} compares the input distribution and reflection pattern of RIScatter to \gls{bc} and \gls{ris}.
+		\begin{figure}[!t]
+			\centering
+			\subfloat[Input Distribution]{
+				\resizebox{0.8\columnwidth}{!}{
+					\input{assets/illustration/input_distribution.tex}
+				}
+				\label{fg:input_distribution}
+			}
+			\\
+			\subfloat[Reflection Pattern]{
+				\resizebox{0.8\columnwidth}{!}{
+					\input{assets/illustration/time_structure.tex}
+				}
+				\label{fg:time_structure}
+			}
+			\caption{
+				Input distribution and reflection pattern of scattering applications.
+				``PB'', ``BB'', and ``CB'' refer to primary symbol block, backscatter symbol block, and channel block, respectively.
+				Shadowing means presence of primary link.
+				In this example, the optimal passive beamformer is state \num{2} and its input probability for RIScatter is \num{0.75}.
+				% RIScatter node transmit symbol \num{1}
+				The spreading factor is \num{4} for RIScatter and \num{8} for \gls{ambc}/\gls{sr}.
+			}
+			\label{fg:scatter_comparison}
+		\end{figure}
+		\begin{remark}
+			RIScatter is different from conventional dynamic passive beamforming since the reflection pattern conveys additional information.
+			% There are many ways to order
+			% The latter only involves time sharing between different states but there are many ways to ensure within a channel block.
+			The latter only involves time sharing between different states and the actual order has no impact on the (ergodic) primary performance.
+			For RIScatter, different state combinations correspond to different messages and the impact reduces to dynamic passive beamforming upon successful backscatter decoding.
+			% However, different combinations correspond to different backscatter messages and RIScatter impact is determined dynamic passive beamforming once successfully decoded.
+		\end{remark}
+
+		RIScatter nodes can be implemented, for example, by adding an integrated receiver \cite{Kim2021a} and adaptive encoder \cite{He2020e} to off-the-shelf passive \gls{rfid} tags.
+		The block diagram, equivalent circuit, and scatter model are illustrated in Fig.~\ref{fg:riscatter_node}.
 		\begin{figure*}[!t]
@@
 		\end{figure*}
-		Fig.~\ref{fg:scatter_comparison} compares the reflection state distribution and reflection pattern of RIScatter and other applications.
-		\begin{figure}[!t]
-			\centering
-			\subfloat[Reflection State Distribution]{
-				\resizebox{0.8\columnwidth}{!}{
-					\input{assets/illustration/input_distribution.tex}
-				}
-				\label{fg:input_distribution}
-			}
-			\\
-			\subfloat[Reflection Pattern]{
-				\resizebox{0.8\columnwidth}{!}{
-					\input{assets/illustration/time_structure.tex}
-				}
-				\label{fg:time_structure}
-			}
-			\caption{
-				Reflection state distribution and reflection pattern over time of scattering applications.
-				``PB'', ``BB'', and ``CB'' refer to primary block, backscatter block, and channel block, respectively.
-				\gls{bc} employs all possible states as information codewords, \gls{ris} treats them as beamformer codewords, and RIScatter simultaneously exploits both benefits.
-			}
-			\label{fg:scatter_comparison}
-		\end{figure}
-		Instead of using fully random or fully deterministic reflection pattern over time, each RIScatter node \emph{semi-randomly} chooses the reflection state for each backscatter block with \emph{guidance of input probability} $P(\Gamma_m)$ at state $m$.
-		Such an adaptive backscatter channel coding includes the degenerate distribution of \gls{ris} and the uniform distribution of line-coded \gls{bc} as special cases.
-		Importantly, RIScatter system design only requires the \emph{direct} transmitter-receiver and \emph{cascaded} transmitter-scatter-receiver \gls{csi}.
-		For dispersed RIScatter nodes, relevant \gls{csi} can be estimated by sequential \cite{Bharadia2015,Yang2015b,Guo2019g} or parallel approaches \cite{Jin2021a} originally proposed for \gls{bc}.
-		For co-located RIScatter nodes, the estimation can be simplified by group-based \cite{Zheng2019} and hierarchical \cite{You2019} trainings originally proposed for \gls{ris}.
-
-		% \begin{remark}
-		% 	Active-passive coexisting networks involve a double modulation where the primary and backscatter symbols of different period are superimposed by multiplication coding.
-		% 	The reflection pattern not only encodes the backscatter message, but also affects the channel for primary link.
-		% 	Therefore, backscatter detection under primary uncertainty can be viewed as part of primary channel training, and novel decoding strategies apart from \gls{sic}%
-		% 	\footnote{
-		% 		Superposition coding and \gls{sic} was originally proposed to achieve the capacity vertices of Gaussian \gls{mac}.
-		% 		For active-passive coexisting networks, \gls{sic} not only fails to utilize the multiplication coding/double modulation, but also requires $N$ re-encoding, precoding and subtraction with a time-domain \gls{mrc} during each backscatter block.
+		To exploit the benefits of RIScatter, we also propose a practical co-located receiver that semi-coherently decodes the backscatter information, recovers the reflection pattern, and coherently decodes the primary link.
+		The detail will be covered in the next section.
+	\end{subsection}
+
+	% As illustrated in Fig.~\ref{fg:energy_distribution}, conditioned on different reflection state hypotheses, the accumulated receive energy per backscatter block follows Gamma distribution with different scale parameters \cite{Qian2017b}.
+	% \begin{figure}[!t]
+	% 	\centering
+	% 	\resizebox{0.8\columnwidth}{!}{
+	% 		\input{assets/illustration/energy_distribution.tex}
 	% 	}
-		% 	is desired for RIScatter.
-		% \end{remark}
-
-		% ? Add an illustration here if space allows
-		We also propose a novel cooperative receiver that exploits the double modulation, double fading and symbol period difference to reduce the decoding complexity and improve the primary-backscatter tradeoff.
-		As illustrated in Fig.~\ref{fg:energy_distribution}, conditioned on different reflection state hypotheses, the accumulated receive energy per backscatter block follows Gamma distribution with different scale parameters \cite{Qian2017b}.
-		\begin{figure}[!t]
-			\centering
-			\resizebox{0.8\columnwidth}{!}{
-				\input{assets/illustration/energy_distribution.tex}
-			}
-			\caption{
-				\gls{pdf} of accumulated receive energy per backscatter block conditioned on different reflection state hypotheses.
-				$z$, $t$, $\mathcal{H}$ and $\mathcal{R}$ denote the accumulated receive energy, decision threshold, reflection state hypothesis, and decision regions, respectively.
-			}
-			\label{fg:energy_distribution}
-		\end{figure}
-		Hence, the receiver can semi-coherently (under primary uncertainty) decode RIScatter nodes from the accumulated receive energy, re-encode to recover the exact reflection patterns, and combine those with cascaded \gls{csi} to determine the multipath response and model within the primary channel.
-		Such a backscatter-primary decoding enables simultaneous backscatter modulation and dynamic passive beamforming by only one energy comparison and re-encoding during each backscatter (instead of primary) block.
-		It enjoys a three-fold benefit compared to conventional primary-backscatter decoding with \gls{sic}, namely
-		1) reduces the re-encoding frequencies to $1/N$;
-		2) requires no re-precoding, cancellation, or \gls{mrc};
-		3) preserves backscatter modulation and passive beamforming at smaller spreading factors for potentially higher backscatter throughput.
-	\end{subsection}
+	% 	\caption{
+	% 		\gls{pdf} of accumulated receive energy per backscatter block conditioned on different reflection state hypotheses.
+	% 		$z$, $t$, $\mathcal{H}$ and $\mathcal{R}$ denote the accumulated receive energy, decision threshold, reflection state hypothesis, and decision regions, respectively.
+	% 	}
+	% 	\label{fg:energy_distribution}
+	% \end{figure}
+
+	% Hence, the receiver can semi-coherently (under primary uncertainty) decode RIScatter nodes from the accumulated receive energy, re-encode to recover the reflection patterns, and combine those with cascaded \gls{csi} to determine the multipath response and model within the primary channel.
+	% Such a backscatter-primary decoding enables simultaneous backscatter modulation and dynamic passive beamforming by only one energy comparison and re-encoding during each backscatter (instead of primary) block.
+	% It enjoys a three-fold benefit compared to conventional primary-backscatter decoding with \gls{sic}, namely
+	% 1) reduces the re-encoding frequencies to $1/N$;
+	% 2) requires no re-precoding, cancellation, or \gls{mrc};
+	% 3) preserves backscatter modulation and passive beamforming at smaller spreading factors for potentially higher backscatter throughput.
+
+	% % ! add to signal model
+	% % Importantly, RIScatter system design only requires the \emph{direct} transmitter-receiver and \emph{cascaded} transmitter-scatter-receiver \gls{csi}.
+	% % For dispersed RIScatter nodes, relevant \gls{csi} can be estimated by sequential \cite{Bharadia2015,Yang2015b,Guo2019g} or parallel approaches \cite{Jin2021a} originally proposed for \gls{bc}.
+	% % For co-located RIScatter nodes, the estimation can be simplified by group-based \cite{Zheng2019} and hierarchical \cite{You2019} trainings originally proposed for \gls{ris}.
 

### 2023-02-25 main.tex
:construction: Update model

@@
 \newacronym{dmtc}{DMTC}{Discrete Memoryless Thresholding Channel}
-\newacronym{dmtmac}{DMTMAC}{Discrete Memoryless Thresholding Multiple Access Channel}
 \newacronym{dmmac}{DMMAC}{Discrete Memoryless Multiple Access Channel}
+\newacronym{dcmc}{DCMC}{Discrete-input Continuous-output Memoryless Channel}
 \newacronym{dp}{DP}{Dynamic Programming}
@@
 	To reap the benefits of RIScatter, we also propose a co-located \gls{sic}-free receiver that semi-coherently decodes the backscatter information, recovers the reflection pattern, and coherently decodes the primary link.
-	For a single-user multi-node RIScatter network, we characterize the achievable primary-(total-)backscatter rate region by designing the input distribution at scatter nodes, the active beamforming at the \gls{ap}, and the energy detection regions at the user.
+	For a single-user multi-node RIScatter network, we characterize the achievable primary-(total-)backscatter rate region by designing the input distribution at scatter nodes, the active beamforming at the \gls{ap}, and the energy decision regions at the user.
 	Simulation results demonstrate RIScatter nodes can exploit the scattered paths to smoothly shift between backscatter modulation and passive beamforming.
@@
 	For the co-located cooperative receiver, the \gls{ber} performance of \gls{ml}, linear, and \gls{sic} detectors are derived over flat fading channels \cite{Yang2018}.
-	However, the work assumed equal symbol period and perfect synchronization for primary and backscatter links.
+	However, the work assumed equal symbol duration and perfect synchronization for primary and backscatter links.
 	Importantly, active-passive coexisting networks have three special and important properties:
@@
 		\item Backscatter signal strength is much weaker than primary due to the \emph{double fading} effect;
-		\item The spreading factor (i.e., backscatter symbol period over primary) is usually large\footnote{The load-switching interval of low-power backscatter modulators is usually \num{0.1} to \qty{10}{\us} \cite{Torres2021}, accounting for a typical spreading factor between \num{10} and \num{e3}.}.
+		\item The spreading factor (i.e., backscatter symbol duration over primary) is usually large\footnote{The load-switching interval of low-power backscatter modulators is usually \num{0.1} to \qty{10}{\us} \cite{Torres2021}, accounting for a typical spreading factor between \num{10} and \num{e3}.}.
 	\end{enumerate}
@@
 	$\mathrm{card}(\cdot)$ returns the cardinality of a set.
+	$\log(\cdot)$ denotes logarithm of base $e$.
 	$(\cdot)^*$, $(\cdot)^\mathsf{T}$, $(\cdot)^\mathsf{H}$, $\lvert{\cdot}\rvert$, and $\lVert{\cdot}\rVert$ denote the conjugate, transpose, conjugate transpose (Hermitian), absolute value, and Euclidean norm operators, respectively.
@@
 		To exploit the benefits of RIScatter, we also propose a practical co-located receiver that semi-coherently decodes the backscatter information, recovers the reflection pattern, and coherently decodes the primary link.
-		The detail will be covered in the next section.
+		The detail will be covered in Section~\ref{se:system_model}.
+		% We also propose a practical co-located receiver to exploit the benefits of RIScatter and the detail will be covered in Section~\ref{se:system_model}.
 	\end{subsection}
 
-	% As illustrated in Fig.~\ref{fg:energy_distribution}, conditioned on different reflection state hypotheses, the accumulated receive energy per backscatter block follows Gamma distribution with different scale parameters \cite{Qian2017b}.
+	% As illustrated in Fig.~\ref{fg:energy_distribution}, conditioned on different reflection state hypotheses, the accumulated energy per backscatter block follows Gamma distribution with different scale parameters \cite{Qian2017b}.
 	% \begin{figure}[!t]
@@
 	% 	\caption{
-	% 		\gls{pdf} of accumulated receive energy per backscatter block conditioned on different reflection state hypotheses.
-	% 		$z$, $t$, $\mathcal{H}$ and $\mathcal{R}$ denote the accumulated receive energy, decision threshold, reflection state hypothesis, and decision regions, respectively.
+	% 		\gls{pdf} of accumulated energy per backscatter block conditioned on different reflection state hypotheses.
+	% 		$z$, $t$, $\mathcal{H}$ and $\mathcal{R}$ denote the accumulated energy, decision threshold, reflection state hypothesis, and decision regions, respectively.
 	% 	}
@@
 
-	% Hence, the receiver can semi-coherently (under primary uncertainty) decode RIScatter nodes from the accumulated receive energy, re-encode to recover the reflection patterns, and combine those with cascaded \gls{csi} to determine the multipath response and model within the primary channel.
+	% Hence, the receiver can semi-coherently (under primary uncertainty) decode RIScatter nodes from the accumulated energy, re-encode to recover the reflection patterns, and combine those with cascaded \gls{csi} to determine the multipath response and model within the primary channel.
 	% Such a backscatter-primary decoding enables simultaneous backscatter modulation and dynamic passive beamforming by only one energy comparison and re-encoding during each backscatter (instead of primary) block.
@@
 	\begin{subsection}{System Model}
+		\label{se:system_model}
 		\begin{figure}[!t]
@@
 		\end{figure}
-		As shown in Fig.~\ref{fg:riscatter_network}, we consider a RIScatter system where a $Q$-antenna \gls{ap} serves a single-antenna user as well as $K$ nearby dispersed/co-located single-antenna $M$-state RIScatter nodes.
-		In the primary point-to-point system, the \gls{ap} transmits information to the user over the multipath channel enhanced by RIScatter nodes.
-		In the backscatter multiple access system, the \gls{ap} and user become carrier emitter and backscatter reader, and the RIScatter nodes modulate over the scattered \gls{rf} signals.
-		For simplicity, we consider a quasi-static block fading model and focus on a specific block where all \gls{csi} remain constant.
-		Without loss of generality, let the spreading factor $N$ be a positive integer.
-		We also omit the signal reflected by two or more times and ignore the multipath propagation time difference.
+		As shown in Fig.~\ref{fg:riscatter_network}, we consider a RIScatter system where a $Q$-antenna \gls{ap} serves a single-antenna user and $K$ nearby dispersed or co-located RIScatter nodes.
+		All nodes have $M$ available reflection states.
+		In the primary point-to-point system, the \gls{ap} transmits information to the user over a multipath channel enhanced by RIScatter nodes.
+		In the backscatter multiple access system, the \gls{ap} acts as carrier emitter, the RIScatter nodes modulate over scattered signal, and the user jointly decodes all node messages.
+		For simplicity, we consider a quasi-static block fading model and focus on a specific block where the \gls{csi} remains constant.
+		It is assumed the signal reflected by two or more times is negligible, the primary symbol duration is much longer than multipath delay spread (no inter-symbol interference), and the spreading factor $N$ is a positive integer.
 		Denote the \gls{ap}-user direct channel as $\boldsymbol{h}_{\text{D}}^\mathsf{H} \in \mathbb{C}^{1 \times Q}$, the \gls{ap}-node $k \in \mathcal{K} \triangleq \{1,\ldots,K\}$ forward channel as $\boldsymbol{h}_{\text{F},k}^\mathsf{H} \in \mathbb{C}^{1 \times Q}$, the node $k$-user backward channel as $h_{\text{B},k}$, and the cascaded \gls{ap}-node $k$-user channel as $\boldsymbol{h}_{\text{C},k}^\mathsf{H} \triangleq h_{\text{B},k} \boldsymbol{h}_{\text{F},k}^\mathsf{H} \in \mathbb{C}^{1 \times Q}$.
+		We assume perfect direct and cascaded \gls{csi} are available at the \gls{ap} and the user\footnote{The cascaded \gls{csi} can be estimated by sequential \cite{Bharadia2015,Yang2015b,Guo2019g} or parallel \cite{Jin2021a} approaches for dispersed nodes, or group-based \cite{Zheng2019} or hierarchical \cite{You2019} approaches for co-located nodes.}.
+		% For dispersed RIScatter nodes, relevant \gls{csi} can be estimated by sequential \cite{Bharadia2015,Yang2015b,Guo2019g} or parallel approaches \cite{Jin2021a} originally proposed for \gls{bc}.
+For co-located RIScatter nodes, the estimation can be simplified by group-based \cite{Zheng2019} and hierarchical \cite{You2019} trainings originally proposed for \gls{ris}.}.
 		Let $x_k \in \mathcal{X} \triangleq \{c_1,\ldots,c_M\}$ be the coded backscatter symbol of node $k$ and $x_{\mathcal{K}} \triangleq (x_1,\ldots,x_K)$ be the backscatter symbol tuple of all nodes.
-		Due to double modulation, the primary equivalent channel is a function of backscatter symbol tuple\footnote{\eqref{eq:equivalent_channel_bc} and \eqref{eq:equivalent_channel_ris} are often used in \gls{bc} and \gls{ris} literature, respectively.}
+		Due to double modulation, the composite channel is a function of backscatter symbol tuple\footnote{\eqref{eq:equivalent_channel_bc} and \eqref{eq:equivalent_channel_ris} are often used in \gls{bc} and \gls{ris} literature, respectively.}
 		\begin{subequations}
@@
 			\begin{align}
-				\boldsymbol{h}_{\text{E}}^\mathsf{H}(x_{\mathcal{K}})
+				\boldsymbol{h}^\mathsf{H}(x_{\mathcal{K}})
 				 & \triangleq \boldsymbol{h}_{\text{D}}^\mathsf{H} + \sum_{k} \alpha_k \boldsymbol{h}_{\text{C},k}^\mathsf{H} x_k \label{eq:equivalent_channel_bc}                    \\
@@
 		where $\alpha_k \in \mathbb{I}$ is the common amplitude scattering ratio of node $k$, $\boldsymbol{\alpha} \triangleq [\alpha_1,\ldots,\alpha_K]^\mathsf{T} \in \mathbb{I}^{K}$, $\boldsymbol{x} \triangleq [x_1,\ldots,x_K]^\mathsf{H} \in \mathcal{X}^{K}$, and $\boldsymbol{H}_{\text{C}} \triangleq [\boldsymbol{h}_{\text{C},1},\ldots,\boldsymbol{h}_{\text{C},K}]^\mathsf{H} \in \mathbb{C}^{K \times Q}$.
-		In the following context, we focus on one backscatter block (i.e., $N$ primary blocks).
+		Next, we consider the signal model within one backscatter block.
 		The signal received by the user at primary block $n \in \mathcal{N} \triangleq \{1,\ldots,N\}$ is
 		\begin{equation}
-			y[n] = \boldsymbol{h}_{\text{E}}^\mathsf{H}(x_{\mathcal{K}}) \boldsymbol{w} s[n] + v[n],
+			y[n] = \boldsymbol{h}^\mathsf{H}(x_{\mathcal{K}}) \boldsymbol{w} s[n] + v[n],
 			\label{eq:receive_signal}
@@
 		where $\boldsymbol{w} \in \mathbb{C}^{Q}$ is the active beamformer satisfying average transmit power constraint $\lVert \boldsymbol{w} \rVert^2 \le P$, $s \sim \mathcal{CN}(0,1)$ is the primary symbol, and $v \sim \mathcal{CN}(0,\sigma_v^2)$ is the \gls{awgn} with average power $\sigma_v^2$.
-		Let $m_k \in \mathcal{M} \triangleq \{1,\ldots,M\}$ be the reflection state index of node $k$ and $m_{\mathcal{K}} \triangleq (m_1,\ldots,m_K)$ be the reflection state index tuple of all nodes.
-		The backscatter symbol $x_k$ (resp.
+		Let $m_k \in \mathcal{M} \triangleq \{1,\ldots,M\}$ be the reflection state index of node $k$ and $m_{\mathcal{K}} \triangleq (m_1,\ldots,m_K)$ be the state index tuple of all nodes.
+		% The backscatter symbol $x_k$ (resp.
 symbol tuple $x_{\mathcal{K}}$) is a random variable (resp.
@@
 state tuple $m_{\mathcal{K}}$) is employed.
-		Conditioned on $m_{\mathcal{K}}$, the receive signal at each primary block follows \gls{cscg} distribution $\mathcal{CN}(0,\sigma_{m_{\mathcal{K}}}^2)$, where
-		\begin{equation}
-			\sigma_{m_{\mathcal{K}}}^2 = \lvert \boldsymbol{h}_{\text{E}}^\mathsf{H}(x_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2 + \sigma_v^2
+		The backscatter symbol tuple $x_{\mathcal{K}}$ is a random variable that takes value $x_{m_{\mathcal{K}}}$ when state tuple $m_{\mathcal{K}}$ is used.
+		Conditioned on hypothesis $\mathcal{H}_{m_{\mathcal{K}}}$, the receive signal per primary block follows \gls{cscg} distribution $\mathcal{CN}(0,\sigma_{m_{\mathcal{K}}}^2)$, where
+		\begin{equation}
+			\sigma_{m_{\mathcal{K}}}^2 = \lvert \boldsymbol{h}^\mathsf{H}(x_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2 + \sigma_v^2
 			\label{eq:receive_variance}
 		\end{equation}
-		is the received variance.
-		Let $z=\sum_{n} \bigl\lvert y[n] \bigr\rvert^2$ be the accumulated receive energy per backscatter block.
-		Since $z$ is the sum of $N$ \gls{iid} exponential variables, its conditional \gls{pdf} follows Gamma distribution
-		\begin{equation}
-			f(z|\mathcal{H}_{m_{\mathcal{K}}}) = \frac{z^{N-1} \exp(-z/\sigma_{m_{\mathcal{K}}}^2)}{\sigma_{m_{\mathcal{K}}}^{2N} (N-1)!},
+		is its variance.
+		Let $z=\sum_{n} \bigl\lvert y[n] \bigr\rvert^2$ be the accumulated energy per backscatter block.
+		Since $z$ is the sum of $N$ \gls{iid} exponential variables, the conditional \gls{pdf} follows Gamma distribution
+		\begin{equation}
+			f(z|\mathcal{H}_{m_{\mathcal{K}}}) = \frac{z^{N-1} \exp(-z/\sigma_{m_{\mathcal{K}}}^2)}{\sigma_{m_{\mathcal{K}}}^{2N} (N-1)!}.
 			\label{eq:energy_distribution}
 		\end{equation}
-		where $\mathcal{H}_{m_{\mathcal{K}}}$ denotes hypothesis $m_{\mathcal{K}}$.
-		At the receiver, the energy space is divided into disjoint decision regions associated with different hypotheses, as illustrated in Fig.~\ref{fg:energy_distribution}.
+		% The receiver first jointly decodes all backscatter messages under primary interference by energy detection.
+		% This essentially formulates a \gls{dmmac} over disjoint energy decision regions.
+		The user first jointly decodes all backscatter messages under primary interference by performing energy detection over disjoint decision regions.
+		For the ease of notation, we map the state index tuple $m_{\mathcal{K}}$ to $l \in \mathcal{L} \triangleq \{1,\ldots,L\}$, where $L \triangleq M^K$ and $\sigma_1^2,\ldots,\sigma_L^2$ forms an increasing sequence.
+		Both notations are used interchangeably in the following context.
+		The decision region of backscatter symbol tuple $l$ is
+		\begin{equation}
+			\mathcal{R}_{l} \triangleq [t_{l-1},t_l), \quad 0 \le t_{l-1} \le t_l,
+		\end{equation}
+		where $t_l$ is the energy decision threshold between hypotheses $\mathcal{H}_{l}$ and $\mathcal{H}_{l+1}$.
+		For a given decision threshold vector $\boldsymbol{t} \triangleq [t_0,\ldots,t_L]^\mathsf{T} \in \mathbb{R}_+^{(L+1)}$, we can formulate a \gls{dmmac} with transition probability from input $x_{m_{\mathcal{K}}}$ to output $\hat{x}_{m_{\mathcal{K}}'}$ as
+		\begin{equation}
+			P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}}) = \int_{\mathcal{R}_{m_{\mathcal{K}}'}} f(z|\mathcal{H}_{m_{\mathcal{K}}}) \, d z,
+			\label{eq:dmmac}
+		\end{equation}
+		over which input distribution of all RIScatter nodes can be designed.
+		An example of energy detection is illustrated in Fig.~\ref{fg:energy_distribution}.
+		% Conditioned on different reflection state hypotheses, the accumulated energy per backscatter block follows Gamma distribution with different scale parameters.
+		\begin{figure}[!t]
+			\centering
+			\resizebox{0.8\columnwidth}{!}{
+				\input{assets/illustration/energy_distribution.tex}
+			}
+			\caption{
+				\gls{pdf} of accumulated energy per backscatter block conditioned on different reflection state hypotheses.
+			}
+			\label{fg:energy_distribution}
+		\end{figure}
 		\begin{remark}
 			The capacity-achieving decision region design for \gls{dmtc} with non-binary inputs in arbitrary distribution remains an open issue.
-			It was proved deterministic detector can be rate-optimal, but non-convex decision regions (i.e., comprise non-adjacent partitions) are generally involved and the optimal number of thresholds remains unknown \cite{Nguyen2018,Nguyen2021}.
-			Hence, we limit the backscatter energy detector to convex deterministic decision regions and consider sequential threshold design in the following context.
+			It was proved deterministic detectors can be rate-optimal, but non-convex decision regions (comprise non-adjacent partitions) are generally required and the optimal number of thresholds remains unknown \cite{Nguyen2018,Nguyen2021}.
+			Hence, we limit the energy detector to convex deterministic decision regions and consider sequential threshold design.
 		\end{remark}
-
-		For the ease of notations, we map the state index tuple $m_{\mathcal{K}}$ to $l \in \mathcal{L} \triangleq \{1,\ldots,L \triangleq M^K\}$, where $\sigma_1^2,\ldots,\sigma_L^2$ is a non-decreasing sequence.
-		Both notations are used interchangeably in the following context.
-		As such, the decision region of backscatter symbol tuple $l$ can be written as
-		\begin{equation}
-			\mathcal{R}_{l} \triangleq [t_{l-1},t_l), \quad 0 \le t_{l-1} \le t_l,
-		\end{equation}
-		where $t_l$ is the energy decision threshold between hypotheses $\mathcal{H}_{l}$ and $\mathcal{H}_{l+1}$.
-		For a given decision threshold vector $\boldsymbol{t} \triangleq [t_0,\ldots,t_L]^\mathsf{T} \in \mathbb{R}_+^{(L+1)}$, we can formulate a \gls{dmtmac} with transition probability from input tuple $x_{m_{\mathcal{K}}}$ to output tuple $\hat{x}_{m_{\mathcal{K}}'}$ as
-		\begin{equation}
-			P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}}) = \int_{\mathcal{R}_{m_{\mathcal{K}}'}} f(z|\mathcal{H}_{m_{\mathcal{K}}}) \, d z,
-			\label{eq:dmtmac}
-		\end{equation}
-		over which adaptive backscatter channel coding can be performed.
+		After successful backscatter decoding, the user can re-encode for exact reflection pattern and obtain the composite channel by \eqref{eq:equivalent_channel}, then coherently decode the primary link.
+		Such an \gls{sic}-free sequential decoding enables backscatter modulation and dynamic passive beamforming by only one energy comparison and re-encoding per backscatter symbol.
+		It also supports arbitrary input distribution and spreading factor for higher backscatter throughput.
 		\label{st:system_model}
@@
 	\begin{subsection}{Achievable Rates}
-		Denote the probability of node $k$ choosing reflection state $m_k$ as $P_k(x_{m_k})$, and let $\boldsymbol{p}_k \triangleq [P_k(c_1),\ldots,P_k(c_M)]^\mathsf{T} \in \mathbb{I}^{M}$.
-		For dispersed nodes with independent encoding, the probability of backscatter symbol value tuple $x_{m_{\mathcal{K}}}$ is
+		Denote the probability of node $k$ choosing reflection state $m_k$ as $P_k(x_{m_k})$ and let $\boldsymbol{p}_k \triangleq [P_k(c_1),\ldots,P_k(c_M)]^\mathsf{T} \in \mathbb{I}^{M}$.
+		For dispersed nodes with independent encoding, the probability of backscatter symbol tuple $x_{m_{\mathcal{K}}}$ is
 		\begin{equation}
@@
 		\end{equation}
-		where $P_{\mathcal{K}}(\hat{x}_{m_{\mathcal{K}}'}) = \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}})$ is the probability of output value tuple $\hat{x}_{m_{\mathcal{K}}'}$.
+		where $P_{\mathcal{K}}(\hat{x}_{m_{\mathcal{K}}'}) = \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}})$.
 		We also define the backscatter marginal information of $x_{m_k}$ as
@@
 
-		Once nodes are successfully decoded, we can re-encode and determine the primary equivalent channel by \eqref{eq:equivalent_channel}.
-		Therefore, the primary information function conditioned on $x_{m_{\mathcal{K}}}$ is
-		\begin{equation}
-			I_{\text{P}}(s;y|x_{m_{\mathcal{K}}}) \triangleq \log \Bigl(1 + \frac{\lvert \boldsymbol{h}_{\text{E}}^\mathsf{H}(x_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_v^2}\Bigr),
+		Once nodes are successfully decoded, we can re-encode and determine the composite channel by \eqref{eq:equivalent_channel}.
+		The primary information function conditioned on $x_{m_{\mathcal{K}}}$ is
+		\begin{equation}
+			I_{\text{P}}(s;y|x_{m_{\mathcal{K}}}) \triangleq \log \Bigl(1 + \frac{\lvert \boldsymbol{h}^\mathsf{H}(x_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_v^2}\Bigr),
 			\label{eq:primary_information_function}
@@
 
-		With a slight abuse of notation, we define the corresponding weighted sum information function, marginal information, and mutual information as
+		With a slight abuse of notation, we define the weighted sum information function, marginal information, and mutual information as
 		\begin{align}
@@
 		where $\rho \in \mathbb{I}$ is the relative \gls{qos} of the primary link.
-		We notice the average primary rate \eqref{eq:primary_mutual_information} depends on the backscatter input distribution and active beamforming, while the total backscatter rate depends on the input distribution and \gls{dmtmac} \eqref{eq:dmtmac} that relates to the active beamforming and decision thresholds.
+		We notice the average primary rate \eqref{eq:primary_mutual_information} depends on the backscatter input distribution and active beamforming, while the total backscatter rate depends on the input distribution and \gls{dmmac} \eqref{eq:dmmac} that relates to the active beamforming and decision thresholds.
 		\label{st:information_theory}
@@
 \begin{section}{Rate-Region Characterization}
-	To characterize the achievable primary-(total-)backscatter rate region for the RIScatter system in Fig.~\ref{fg:riscatter_network}, we aim to maximize the weighted sum rate with respect to input distribution $\{\boldsymbol{p}_k\}_{k \in \mathcal{K}}$, active beamforming $\boldsymbol{w}$, and decision thresholds $\boldsymbol{t}$ by
+	To characterize the achievable primary-(total-)backscatter rate region for the RIScatter system, we aim to maximize the weighted sum rate with respect to input distribution $\{\boldsymbol{p}_k\}_{k \in \mathcal{K}}$, active beamforming $\boldsymbol{w}$, and decision thresholds $\boldsymbol{t}$ by
 	\begin{maxi!}
@@
 
-	Problem \eqref{op:weighted_sum_rate} generalizes conventional \gls{bc} by allowing \gls{csi}- and \gls{qos}-adaptive input distribution and detection region design.
-	It also generalizes the discrete \gls{ris} phase shift selection by allowing stochastic reflection (i.e., relaxing the feasible domain from the \emph{vertices} of $M$-dimensional probability simplex to the simplex itself).
-	Since problem \eqref{op:weighted_sum_rate} is highly non-convex, we propose a \gls{bcd} algorithm that iteratively updates $\{\boldsymbol{p}_k\}_{k \in \mathcal{K}}$, $\boldsymbol{w}$ and $\boldsymbol{t}$ until convergence.
+	Problem \eqref{op:weighted_sum_rate} generalizes conventional \gls{bc} by allowing \gls{csi}- and \gls{qos}-adaptive input distribution and decision region design.
+	It also generalizes the discrete \gls{ris} phase shift selection by allowing stochastic reflection, relaxing the feasible domain from the vertices of $M$-dimensional probability simplex to the simplex itself.
+	Problem \eqref{op:weighted_sum_rate} is highly non-convex and we propose a \gls{bcd} algorithm that iteratively updates $\{\boldsymbol{p}_k\}_{k \in \mathcal{K}}$, $\boldsymbol{w}$ and $\boldsymbol{t}$.
 
 	\begin{subsection}{Input Distribution}
-		For any given $\boldsymbol{w}$ and $\boldsymbol{t}$, we can construct the equivalent \gls{dmtmac} by \eqref{eq:dmtmac} and simplify \eqref{op:weighted_sum_rate} to
+		For any given $\boldsymbol{w}$ and $\boldsymbol{t}$, we can construct the equivalent \gls{dmmac} by \eqref{eq:dmmac} and simplify \eqref{op:weighted_sum_rate} to
 		\begin{maxi!}
@@
 		\end{maxi!}
-		which is convex when $K=1$ or joint encoding\footnote{Joint encoding formulates an equivalent source of $M^K$ codewords, such that one can directly design $P_{\mathcal{K}}(x_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}$ instead of $P_k(x_{m_k})$, $\forall k,m_k$.} over $K>1$ co-located nodes is available.
-		When the nodes are dispersed, problem \eqref{op:input_distribution} involves coupled term $\prod_{k \in \mathcal{K}} P_k(x_{m_k})$ and is non-convex.
-		Following \cite{Rezaeian2004}, we first recast the \gls{kkt} conditions to their equivalent forms, then propose a numerical method that guarantees those conditions on convergence of sequences.
+		which is convex when $K=1$ or joint encoding\footnote{Joint encoding formulates an equivalent source of $M^K$ codewords, such that one can directly design $P_{\mathcal{K}}(x_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}$ instead of $P_k(x_{m_k})$, $\forall k,m_k$.} over $K>1$ co-located nodes.
+		When the nodes are dispersed, problem \eqref{op:input_distribution} involves product term $\prod_{k \in \mathcal{K}} P_k(x_{m_k})$ and is non-convex.
+		Following \cite{Rezaeian2004}, we first recast the \gls{kkt} conditions to their equivalent forms then propose a numerical method that guarantees those conditions on convergence of sequences.
 		% ? Next, we propose a numerical method that evaluate the \gls{kkt} input distribution by limit of sequences.
 		\begin{remark}
-			As demonstrated in \cite{Buhler2011}, \gls{kkt} conditions are generally necessary but insufficient for total rate maximization of discrete \gls{mac}.
-			We will show by numerical results that, for a moderate $K$, the average achievable rate regions of \gls{kkt} and global-optimal input distributions completely coincide with each other.
+			As demonstrated in \cite{Buhler2011}, \gls{kkt} conditions are generally necessary but insufficient for total rate maximization of \gls{dmmac}.
+			We will later show by simulation that, for a moderate $K$, the average achievable rate regions of \gls{kkt} and global-optimal input distributions completely coincide with each other.
 			\label{re:input_kkt_distribution}
@@
 
-		For each node, \eqref{eq:probable_states} suggests each probable state should produce the same marginal information (averaged over all states of other nodes), while \eqref{eq:dropped_states} suggests any state with potentially less marginal information should not be used.
+		For each RIScatter node, \eqref{eq:probable_states} suggests each probable state should produce the same marginal information (averaged over all states of other nodes) while \eqref{eq:dropped_states} suggests any state with potentially less marginal information should not be used.
 		\begin{proposition}
@@
 				\Ensure $\{\boldsymbol{p}_k^\star\}_{k \in \mathcal{K}}$
-				\State Set $\boldsymbol{h}_{\text{E}}^\mathsf{H}(x_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}$ by \eqref{eq:equivalent_channel}
+				\State Set $\boldsymbol{h}^\mathsf{H}(x_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}$ by \eqref{eq:equivalent_channel}
 				\State \phantom{Set} $\sigma^2_{m_{\mathcal{K}}}$, $\forall m_{\mathcal{K}}$ by \eqref{eq:receive_variance}
 				\State \phantom{Set} $f(z|\mathcal{H}_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}$ by \eqref{eq:energy_distribution}
-				\State \phantom{Set} $P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}, m_{\mathcal{K}}'$ by \eqref{eq:dmtmac}
+				\State \phantom{Set} $P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}, m_{\mathcal{K}}'$ by \eqref{eq:dmmac}
 				\State Initialize $r \gets 0$
@@
 		which is still non-convex due to the integration and entropy terms.
-		To tackle this, we rewrite the \gls{dmtmac} transition probability \eqref{eq:dmtmac} from input index tuple $m_{\mathcal{K}}$ to output index $l$ as a regularized incomplete Gamma function in the series representation \cite[Theorem 3]{Jameson2016}
+		To tackle this, we rewrite the \gls{dmmac} transition probability \eqref{eq:dmmac} as a regularized incomplete Gamma function in the series representation \cite[Theorem 3]{Jameson2016}
 		\begin{equation}
@@
 		\begin{equation}
-			\nabla_{\boldsymbol{w}^*} Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr) = \frac{\boldsymbol{h}_{\text{E}}(x_{m_{\mathcal{K}}})\boldsymbol{h}_{\text{E}}^\mathsf{H}(x_{m_{\mathcal{K}}})\boldsymbol{w}}{(\sigma_{m_{\mathcal{K}}}^2)^2} g_{m_{\mathcal{K}}}(t_{l-1},t_l),
+			\nabla_{\boldsymbol{w}^*} Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr) = \frac{\boldsymbol{h}(x_{m_{\mathcal{K}}})\boldsymbol{h}^\mathsf{H}(x_{m_{\mathcal{K}}})\boldsymbol{w}}{(\sigma_{m_{\mathcal{K}}}^2)^2} g_{m_{\mathcal{K}}}(t_{l-1},t_l),
 			\label{eq:regularized_incomplete_gamma_gradient}
@@
 			\begin{equation}
-				I(x_{\mathcal{K}})=\sum_{m_{\mathcal{K}}}P_{\mathcal{K}}(x_{m_{\mathcal{K}}})\Biggl(\rho\log\Bigl(1+\frac{\lvert\boldsymbol{h}_{\text{E}}^\mathsf{H}(x_{m_{\mathcal{K}}})\boldsymbol{w}\rvert^2}{\sigma_v^2}\Bigr)+(1-\rho)\sum_l Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr) \log \frac{Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr)}{\sum_{m_{\mathcal{K}}'} P_{\mathcal{K}}(x_{m_{\mathcal{K}}'}) Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}'}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}'}^2}\Bigr)}\Biggr)
+				I(x_{\mathcal{K}})=\sum_{m_{\mathcal{K}}}P_{\mathcal{K}}(x_{m_{\mathcal{K}}})\Biggl(\rho\log\Bigl(1+\frac{\lvert\boldsymbol{h}^\mathsf{H}(x_{m_{\mathcal{K}}})\boldsymbol{w}\rvert^2}{\sigma_v^2}\Bigr)+(1-\rho)\sum_l Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr) \log \frac{Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr)}{\sum_{m_{\mathcal{K}}'} P_{\mathcal{K}}(x_{m_{\mathcal{K}}'}) Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}'}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}'}^2}\Bigr)}\Biggr)
 				\label{eq:weighted_sum_mutual_information_explicit}
@@
 				\nabla_{\boldsymbol{w}^*} I(x_{\mathcal{K}})
-				 & = \sum_{m_{\mathcal{K}}}P_{\mathcal{K}}(x_{m_{\mathcal{K}}})\Biggl(\rho\frac{\boldsymbol{h}_{\text{E}}(x_{m_{\mathcal{K}}})\boldsymbol{h}_{\text{E}}^\mathsf{H}(x_{m_{\mathcal{K}}})\boldsymbol{w}}{\sigma_{m_{\mathcal{K}}}^2}+(1-\rho)\sum_l\biggl(\log\frac{Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr)}{\sum_{m_{\mathcal{K}}'}P_{\mathcal{K}}(x_{m_{\mathcal{K}}'})Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}'}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}'}^2}\Bigr)}+1\biggr)\nonumber                                                             \\
+				 & = \sum_{m_{\mathcal{K}}}P_{\mathcal{K}}(x_{m_{\mathcal{K}}})\Biggl(\rho\frac{\boldsymbol{h}(x_{m_{\mathcal{K}}})\boldsymbol{h}^\mathsf{H}(x_{m_{\mathcal{K}}})\boldsymbol{w}}{\sigma_{m_{\mathcal{K}}}^2}+(1-\rho)\sum_l\biggl(\log\frac{Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr)}{\sum_{m_{\mathcal{K}}'}P_{\mathcal{K}}(x_{m_{\mathcal{K}}'})Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}'}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}'}^2}\Bigr)}+1\biggr)\nonumber                                                                                   \\
 				 & \qquad \times \nabla_{\boldsymbol{w}^*} Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr)-\frac{Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr)\sum_{m_{\mathcal{K}}'}P_{\mathcal{K}}(x_{m_{\mathcal{K}}'})\nabla_{\boldsymbol{w}^*}Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}'}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}'}^2}\Bigr)}{\sum_{m_{\mathcal{K}}'}P_{\mathcal{K}}(x_{m_{\mathcal{K}}'})Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}'}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}'}^2}\Bigr)}\Biggr)
@@
 		\end{equation}
-		The \gls{pgd} active beamforming optimization with step size by \gls{bls} \cite[Section 9.2]{Boyd2004} is summarized in Algorithm \ref{al:active_beamforming}.
+		The \gls{pgd} active beamforming optimization with step size $\gamma$ refined by \gls{bls} \cite[Section 9.2]{Boyd2004} is summarized in Algorithm \ref{al:active_beamforming}.
 		\begin{algorithm}[!t]
@@
 				\Ensure $\boldsymbol{w}^\star$
-				\State Set $\boldsymbol{h}_{\text{E}}^\mathsf{H}(x_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}$ by \eqref{eq:equivalent_channel}
+				\State Set $\boldsymbol{h}^\mathsf{H}(x_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}$ by \eqref{eq:equivalent_channel}
 				\State \phantom{Set} $P_{\mathcal{K}}(x_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}$ by \eqref{eq:equivalent_distribution}
@@
 		\end{maxi!}
-		which is still non-convex because variable $\boldsymbol{t}$ appears on the limits of integration \eqref{eq:dmtmac}.
-		Fortunately, we can further simplify problem \eqref{op:decision_threshold} as a point-to-point rate-optimal quantizer design for a discrete-input continuous-output memoryless channel, thanks to Remark \ref{re:backscatter_decision} and \ref{re:augmented_source}.
+		which is still non-convex because variable $\boldsymbol{t}$ appears on the limits of integration \eqref{eq:dmmac}.
+		Fortunately, we can further simplify problem \eqref{op:decision_threshold} as a point-to-point rate-optimal quantizer design for a \gls{dcmc}, thanks to Remark \ref{re:backscatter_decision} and \ref{re:augmented_source}.
 
 		\begin{remark}
-			Backscatter decision design has no impact on the primary achievable rate, because the primary equivalent channel \eqref{eq:equivalent_channel} at each backscatter block can always be determined upon successful backscatter decoding.
+			Energy detector design has no impact on the primary achievable rate since the composite channel \eqref{eq:equivalent_channel} can always be reconstructed by re-encoding.
 			It suggests any thresholding scheme that maximize the total backscatter rate \eqref{eq:backscatter_mutual_information} is also optimal for problem \eqref{op:decision_threshold}.
@@
 		\begin{remark}
-			In terms of total backscatter rate, the potentially dispersed nodes with known input distribution can be viewed as an equivalent source with symbol tuples as codewords.
-			As such, the \gls{dmtmac} \eqref{eq:dmtmac} becomes a \gls{dmtc} and problem \eqref{op:decision_threshold} reduces to the rate-optimal quantization design for a discrete-input continuous-output memoryless channel.
+			In terms of total backscatter rate, the potentially dispersed nodes with known input distribution can be viewed as an equivalent source with tuple codewords.
+			As such, the \gls{dmmac} \eqref{eq:dmmac} becomes a \gls{dmtc} and problem \eqref{op:decision_threshold} reduces to the rate-optimal quantization design for a \gls{dcmc}.
 			\label{re:augmented_source}
@@
 			}
-			\caption{The decision thresholds are selected from fine-grained discrete energy levels instead of continuous space, and each decision region consists of at least one neighbor energy bins.}
+			\caption{The decision thresholds are selected from fine-grained discrete energy levels instead of continuous space. Each decision region consists of at least one neighbor energy bins.}
 			\label{fg:discrete_outputs}
 		\end{figure}
-		As shown in Fig.~\ref{fg:discrete_outputs}, by introducing an extra analog-to-digital conversion, we can group adjacent high-resolution energy bins to construct backscatter decision regions.
+		As shown in Fig.~\ref{fg:discrete_outputs}, by introducing this extra analog-to-digital conversion, we can group adjacent high-resolution energy bins to construct backscatter decision regions.
 		Thus, problem \eqref{op:decision_threshold} can be recast as
@@
 		\end{maxi!}
-		which is solvable using existing rate-optimal sequential quantizer designs for \gls{dmtc}.
+		which can be solved by existing rate-optimal sequential quantizer designs for \gls{dmtc}.
 		To obtain global optimal solution, \cite{He2021} started from the quadrangle inequality and proposed a \gls{dp} method accelerated by the \gls{smawk} algorithm with computational complexity $\mathcal{O}\bigl(L^2(\mathrm{card}(\mathcal{T})-L)\bigr)$, while \cite{Nguyen2020a} started from the optimality condition for three neighbor thresholds and presented a traverse-then-bisect algorithm with complexity $\mathcal{O}\bigl(\mathrm{card}(\mathcal{T})L\log(\mathrm{card}(\mathcal{T})L)\bigr)$.
@@
 		\end{equation}
-		which is generally suboptimal for problem \eqref{op:decision_threshold} except when all nodes are with equiprobable inputs.
+		which is generally suboptimal for problem \eqref{op:decision_threshold} unless all RIScatter nodes are with equiprobable inputs.
 	\end{subsection}
@@
 	\end{equation}
-	where $d$ is the transmission distance, $L_0=-\qty{30}{\dB}$ is the reference path loss at $d_0=\qty{1}{\meter}$, $\kappa$ is the Rician $K$-factor, $\bar{\boldsymbol{H}}$ is the deterministic line-of-sight component with unit-magnitude entries, and $\tilde{\boldsymbol{H}}$ is the Rayleigh fading component with standard \gls{iid} \gls{cscg} entries.
+	where $d$ is the transmission distance, $L_0=-\qty{30}{\dB}$ is the reference path loss at $d_0=\qty{1}{\meter}$, $\kappa$ is the Rician K-factor, $\bar{\boldsymbol{H}}$ is the deterministic line-of-sight component with unit-magnitude entries, and $\tilde{\boldsymbol{H}}$ is the Rayleigh fading component with standard \gls{iid} \gls{cscg} entries.
 	We choose $\gamma_{\text{D}}=2.6$, $\gamma_{\text{F}}=2.4$, $\gamma_{\text{B}}=2$, and $\kappa_{\text{D}}=\kappa_{\text{F}}=\kappa_{\text{B}}=5$ for direct, forward and backward links.
-	The finite decision threshold domain $\mathcal{T}$ is obtained by $b$-bit uniform discretization over the critical interval defined by the confidence bounds of edge hypotheses (i.e., lower bound of $\mathcal{H}_1$ and upper bound of $\mathcal{H}_L$) with confidence $1-\epsilon$, and we choose $b=9$ and $\epsilon=\num{e-3}$.
+	The finite decision threshold domain $\mathcal{T}$ is obtained by $b$-bit uniform discretization over the critical interval defined by the confidence bounds of edge hypotheses (i.e., lower bound of $\mathcal{H}_1$ and upper bound of $\mathcal{H}_L$) with confidence $1-\varepsilon$.
+	We choose $b=9$ and $\varepsilon=\num{e-3}$.
 	All achievable rate points/regions are averaged over \num{e3} channel realizations.
@@
 			In Fig.~\ref{fg:wsr_convergence}, we plot the weighted sum of primary and total backscatter rates at $\rho=0$ for \gls{kkt}, \gls{pgd} and \gls{bcd} algorithms on the first call.
-			For $K=8$ and $M=2$, Algorithm \ref{al:input_distribution} typically takes around \num{100} fast iterations by \eqref{eq:input_kkt_solution} to converge to the \gls{kkt} input distribution.
-			For $Q=4$, around \num{10} iterations are required for Algorithm \ref{al:active_beamforming} to converge, where the gradient is computed by \eqref{eq:weighted_sum_mutual_information_gradient} and the step size is refined by \gls{bls}.
-			Overall, the \gls{bcd} algorithm initially requires at most \num{5} iterations to converge.
+			For $K=8$ and $M=2$, Algorithm \ref{al:input_distribution} typically takes around \num{100} fast iterations to converge to the \gls{kkt} input distribution.
+			For $Q=4$, around \num{10} iterations are required for Algorithm \ref{al:active_beamforming} to converge.
+			Overall, the initial \gls{bcd} algorithm requires at most \num{5} iterations to converge.
 			At the following points (not presented here), the convergence of all three algorithms are much faster thanks to the progressive initialization.
-			Hence, we conclude the proposed algorithms have good convergence performances.
+			We conclude the proposed algorithms have good convergence performances.
 		\end{subsubsection}
@@
 		\begin{itemize}
-			\item \emph{Legacy:} Conventional active transmission without antenna mode scattering, $\alpha=0$.
-			\item \emph{\gls{bbc}:} The primary symbol becomes deterministic $s[n]=1$ and the receive signal at each primary block is
-			\begin{equation}
-				y^{\text{\gls{bbc}}}[n] = \Bigl(\boldsymbol{h}_{\text{D}}^\mathsf{H} + \sum_{k} \alpha_k \boldsymbol{h}_{\text{C},k}^\mathsf{H} x_k\Bigr) \boldsymbol{w} + v[n],
-			\end{equation}
-			which follows non-zero mean complex Gaussian distribution $\mathcal{CN}\bigl((\boldsymbol{h}_{\text{D}}^\mathsf{H} + \sum_{k} \alpha_k \boldsymbol{h}_{\text{C},k}^\mathsf{H} x_{m_k}) \boldsymbol{w},\sigma_v^2\bigr)$ under hypothesis $\mathcal{H}_{m_{\mathcal{K}}}$.
-			The corresponding \gls{pdf} of accumulated receive energy over $N$ primary blocks is
-			\begin{equation}
-				f^{\text{\gls{bbc}}}(z|\mathcal{H}_{m_{\mathcal{K}}}) = \frac{(z-\mu_{m_{\mathcal{K}}}^{\text{\gls{bbc}}})^{N-1} \exp \bigl(-(z-\mu_{m_{\mathcal{K}}}^{\text{\gls{bbc}}})/\sigma_v^2 \bigr)}{\sigma_v^{2N} (N-1)!},
-				\label{eq:energy_distribution_bbc}
-			\end{equation}
-			where $\mu_{m_{\mathcal{K}}}^{\text{\gls{bbc}}} \triangleq N \bigl\lvert \bigl(\boldsymbol{h}_{\text{D}}^\mathsf{H} + \sum_{k} \alpha_k \boldsymbol{h}_{\text{C},k}^\mathsf{H} x_{m_k}\bigr) \boldsymbol{w} \bigr\rvert^2$.
-			The \gls{ml} decision threshold is derived as, $\forall l \in \mathcal{L} \setminus \{L\}$,
-			\begin{equation}
-				t_l^{\text{\gls{bbc}}} = \frac{\mu_{l-1}^{\text{\gls{bbc}}} \exp \bigl((\mu_{l-1}^{\text{\gls{bbc}}}-\mu_{l}^{\text{\gls{bbc}}})/\sigma_v^2 (N-1)\bigr) - \mu_{l}^{\text{\gls{bbc}}}}{\exp \bigl((\mu_{l-1}^{\text{\gls{bbc}}}-\mu_{l}^{\text{\gls{bbc}}})/\sigma_v^2 (N-1)\bigr) - 1}.
-				\label{eq:detection_threshold_ml_bbc}
-			\end{equation}
+			\item \emph{Legacy:} Active transmission without scatterers.
+			\item \emph{\gls{bbc}:} The primary symbol becomes deterministic $s[n]=1$ and the receive signal becomes
+			\begin{equation}
+				y^{\text{\gls{bbc}}}[n] = \Bigl(\boldsymbol{h}_{\text{D}}^\mathsf{H} + \sum_{k} \alpha_k \boldsymbol{h}_{\text{C},k}^\mathsf{H} x_k\Bigr) \boldsymbol{w} + v[n].
+			\end{equation}
+			The total backscatter rate of coherent decoding approaches $K \log M$ when $N$ is sufficiently large.
+			% which follows non-zero mean complex Gaussian distribution $\mathcal{CN}\bigl((\boldsymbol{h}_{\text{D}}^\mathsf{H} + \sum_{k} \alpha_k \boldsymbol{h}_{\text{C},k}^\mathsf{H} x_{m_k}) \boldsymbol{w},\sigma_v^2\bigr)$ under hypothesis $\mathcal{H}_{m_{\mathcal{K}}}$.
+			% The corresponding \gls{pdf} of accumulated energy over $N$ primary blocks is
+			% \begin{equation}
+			% 	f^{\text{\gls{bbc}}}(z|\mathcal{H}_{m_{\mathcal{K}}}) = \frac{(z-\mu_{m_{\mathcal{K}}}^{\text{\gls{bbc}}})^{N-1} \exp \bigl(-(z-\mu_{m_{\mathcal{K}}}^{\text{\gls{bbc}}})/\sigma_v^2 \bigr)}{\sigma_v^{2N} (N-1)!},
+			% 	\label{eq:energy_distribution_bbc}
+			% \end{equation}
+			% where $\mu_{m_{\mathcal{K}}}^{\text{\gls{bbc}}} \triangleq N \bigl\lvert \bigl(\boldsymbol{h}_{\text{D}}^\mathsf{H} + \sum_{k} \alpha_k \boldsymbol{h}_{\text{C},k}^\mathsf{H} x_{m_k}\bigr) \boldsymbol{w} \bigr\rvert^2$.
+			% The \gls{ml} decision threshold is derived as, $\forall l \in \mathcal{L} \setminus \{L\}$,
+			% \begin{equation}
+			% 	t_l^{\text{\gls{bbc}}} = \frac{\mu_{l-1}^{\text{\gls{bbc}}} \exp \bigl((\mu_{l-1}^{\text{\gls{bbc}}}-\mu_{l}^{\text{\gls{bbc}}})/\sigma_v^2 (N-1)\bigr) - \mu_{l}^{\text{\gls{bbc}}}}{\exp \bigl((\mu_{l-1}^{\text{\gls{bbc}}}-\mu_{l}^{\text{\gls{bbc}}})/\sigma_v^2 (N-1)\bigr) - 1}.
+			% 	\label{eq:detection_threshold_ml_bbc}
+			% \end{equation}
 			\item \emph{\gls{ambc}:} The user decodes both links independently and semi-coherently by treating the other as interference.
-			Hence, the primary achievable rate is approximately\footnote{To provide a preliminary benchmark, we consider the (correlated) scattered signal from finite-input backscatter sources as independent interference from Gaussian sources during primary decoding \cite{Long2020a}.}
+			Hence, the primary achievable rate is approximately\footnote{To provide a preliminary benchmark, we regard the scattered component $\sum_{k} \alpha_k \boldsymbol{h}_{\text{C},k}^\mathsf{H} x_k \boldsymbol{w}s[n]$ as \gls{awgn} during primary decoding \cite{Long2020a}.}
 			\begin{equation}
@@
 			\begin{equation}
-				\hat{y}^{\text{\gls{sr}}}[n] = \sum_{k} \alpha_k \boldsymbol{h}_{\text{C},k}^\mathsf{H} x_k \boldsymbol{w} s[n] + v[n],
+				\hat{y}^{\text{\gls{sr}}}[n] = \sum_{k} \alpha_k \boldsymbol{h}_{\text{C},k}^\mathsf{H} x_k \boldsymbol{w} s[n] + v[n].
 				\label{eq:intermediate_signal}
 			\end{equation}
-			which only involves noise uncertainty under hypothesis $\mathcal{H}_{m_{\mathcal{K}}}$.
-			During backscatter detection, the primary symbols $s[1],\ldots,s[N]$ function as a spreading code and the receiver performs \gls{mrc} on $\hat{y}^{\text{\gls{sr}}}[n]$ over $N$ primary blocks.
-			This essentially formulates a discrete-input continuous-output memoryless channel and the total backscatter achievable rate is maximized with equiprobable inputs as \cite{Ng2006}
-			\begin{equation}
-				I_{\text{B}}(x_{\mathcal{K}};\hat{y}^{\text{\gls{sr}}}) = K \log M - \frac{\iota}{M^K},
-			\end{equation}
-			where $\iota \triangleq \sum_{m_{\mathcal{K}}} \mathbb{E}_{\hat{v}} \log \sum_{m_{\mathcal{K}}'} \exp ( - {\lvert x_{m_{\mathcal{K}}} - x_{m_{\mathcal{K}}'} + \hat{v} \rvert^2}/{2 \sigma^2} )$ and $\hat{v} \sim \mathcal{CN}(0,\sigma_v^2/N)$.
+			The total backscatter rate of coherent decoding approaches $K \log M$ when $N$ is sufficiently large.
+			% which only involves noise uncertainty under hypothesis $\mathcal{H}_{m_{\mathcal{K}}}$.
+			% During backscatter detection, the primary symbols $s[1],\ldots,s[N]$ function as a spreading code and the receiver performs \gls{mrc} on $\hat{y}^{\text{\gls{sr}}}[n]$ over $N$ primary blocks.
+			% This essentially formulates a \gls{dcmc} and the total backscatter achievable rate is maximized with equiprobable inputs as \cite{Ng2006}
+			% \begin{equation}
+			% 	I_{\text{B}}(x_{\mathcal{K}};\hat{y}^{\text{\gls{sr}}}) = K \log M - \frac{\iota}{M^K},
+			% \end{equation}
+			% where $\iota \triangleq \sum_{m_{\mathcal{K}}} \mathbb{E}_{\hat{v}} \log \sum_{m_{\mathcal{K}}'} \exp ( - {\lvert x_{m_{\mathcal{K}}} - x_{m_{\mathcal{K}}'} + \hat{v} \rvert^2}/{2 \sigma^2} )$ and $\hat{v} \sim \mathcal{CN}(0,\sigma_v^2/N)$.
 			% For a sufficiently large $N$, $\iota$ is negligible and the total backscatter rate approaches $K \log M$.
@@
 			\begin{equation}
-				I_{\text{P}}^{\text{\gls{ris}}}(s;y|x_{\mathcal{K}}) = I_{\text{P}}(s;y|x_{m_{\mathcal{K}}^{\star}}) = \log \Bigl(1 + \frac{\lvert \boldsymbol{h}_{\text{E}}^\mathsf{H}(x_{m_{\mathcal{K}}^{\star}}) \boldsymbol{w} \rvert^2}{\sigma_v^2}\Bigr),
-			\end{equation}
-			where $m_{\mathcal{K}}^{\star} = \arg \max_{m_{\mathcal{K}}} I_{\text{P}}(s;y|x_{m_{\mathcal{K}}})$.
+				I_{\text{P}}^{\text{\gls{ris}}}(s;y|x_{\mathcal{K}}) = I_{\text{P}}(s;y|x_{m_{\mathcal{K}}^{\star}}) = \log \Bigl(1 + \frac{\lvert \boldsymbol{h}^\mathsf{H}(x_{m_{\mathcal{K}}^{\star}}) \boldsymbol{w} \rvert^2}{\sigma_v^2}\Bigr),
+			\end{equation}
+			where $m_{\mathcal{K}}^{\star} = \arg \max_{m_{\mathcal{K}}} I_{\text{P}}^{\text{\gls{ris}}}(s;y|x_{m_{\mathcal{K}}})$.
 		\end{itemize}
@@
 
-		Fig.~\ref{fg:region_comparison} compares the typical achievable rate region/points of RIScatter and above.
-		\emph{First,} we observe both \gls{bbc} and \gls{sr} almost ensure noise-free backscatter transmission when the spreading factor $N$ is sufficiently large.
-		For \gls{bbc} with coherent energy detection, the conditional \gls{pdf} of accumulated receive energy \eqref{eq:energy_distribution_bbc} is more skewed at a large $N$, such that the equivalent \gls{dmtmac} \eqref{eq:dmtmac} has lower error probabilities.
-		For \gls{sic}-based \gls{sr}, the effective backscatter \gls{snr} is increased by $N$ times and the penalty term $\iota$ becomes insignificant.
-		However, the primary rate is only maintained at a very large spreading factor, which significantly constrains the backscatter \emph{throughput}.
-		\emph{Second,} the average primary rate slightly increases/decreases in the presence of a \gls{ambc}/\gls{ris} node, and the multipath benefit of \gls{sr} is unobvious.
-		This is because the cascaded channel can be orders of magnitude weaker than the direct channel due to the double fading effect.
-		\gls{ris} always ensures constructive superposition of direct and scattered components, while \gls{sr} only creates a quasi-static rich-scattering environment that \emph{stochastically} enhances the average primary rate.
-		When $N$ is moderate, the randomly scattered signals should be modelled as primary interference rather than multipath components, and the \gls{sr} point will move towards the \gls{ambc} point.
+		Fig.~\ref{fg:region_comparison} compares the typical achievable rate region/points of RIScatter and the strategies above.
+		% \emph{First,} we observe both \gls{bbc} and \gls{sr} achieves when the spreading factor $N$ is sufficiently large.
+		\emph{First,} we observe \gls{bbc} and \gls{sr} achieve the best backscatter performance thanks to coherent decoding.
+		% However, \gls{sr} requires $N$ \gls{sic} followed by a \gls
+		% However, \gls{sr} requires $N$ re-encoding, precoding, subtraction together with a time-domain \gls{mrc} to decode each backscatter symbol and the cost can be prohibitive.
+		For \gls{sr}, this comes with the cost of $N$ re-encoding, precoding, subtraction together with a time-domain \gls{mrc} per backscatter symbol.
+		% However, the primary rate benefit
+		% For \gls{bbc} with coherent energy detection, the conditional \gls{pdf} of accumulated energy \eqref{eq:energy_distribution_bbc} is more skewed at a large $N$, such that the equivalent \gls{dmmac} \eqref{eq:dmmac} has lower error probabilities.
+		% For \gls{sic}-based \gls{sr}, the effective backscatter \gls{snr} is increased by $N$ times and the penalty term $\iota$ becomes insignificant.
+		% However, the primary rate is only maintained at a very large spreading factor, which significantly constrains the backscatter \emph{throughput}.
+		\emph{Second,} the average primary rate slightly decreases/increases in the presence of a \gls{ambc}/\gls{ris} node and the benefit of \gls{sr} is not obvious.
+		This is because the cascaded channel is usually orders of magnitude weaker than the direct channel.
+		\gls{ris} always ensures constructive superposition of direct and scattered components while \gls{sr} only creates a quasi-static rich-scattering environment that marginally enhances the average primary rate.
+		When $N$ is moderate, the randomly scattered signals should be modelled as interference rather than multipath components and the \gls{sr} point should move towards the \gls{ambc} point.
 		\emph{Third,} RIScatter enables a flexible primary-backscatter tradeoff with adaptive input distribution design.
-		In terms of maximum primary achievable rate, RIScatter coincides with \gls{ris} and outperforms the others with passive beamforming provided by deterministic reflection pattern.
-		On the other hand, for a large $N$, the maximum backscatter achievable rate of RIScatter is higher than \gls{ambc} but lower than \gls{bbc} and \gls{sr}.
-		This is because both RIScatter and \gls{ambc} (resp.
-\gls{bbc} and \gls{sr}) employ semi-coherent (resp.
-coherent) energy detection, while RIScatter with adaptive channel coding can achieve higher backscatter rate than \gls{ambc} with equiprobable inputs.
-		Importantly, such a practical RIScatter detection is feasible for arbitrary spreading factor, which unleashes the potential of fast-switching nodes.
-		% , and using a fast-switching node with smaller $N$ can increase the backscatter throughput per unit time while preserving the dynamic passive beamforming gain on the primary link.
+		In terms of maximum primary achievable rate, RIScatter coincides with \gls{ris} and outperforms the others using deterministic reflection pattern.
+		On the other hand, for a large $N$, the maximum backscatter achievable rate of RIScatter is lower than \gls{bbc} and \gls{sr} but higher than \gls{ambc}.
+		This is because both RIScatter and \gls{ambc} employ semi-coherent energy detection and the adaptive channel coding of RIScatter provides better performance than equiprobable inputs of \gls{ambc} (especially at low \gls{snr}).
 	\end{subsection}
@@
 				\item \emph{\gls{pgd}:} Iterative \gls{pgd} optimization by Algorithm \ref{al:active_beamforming};
-				\item \emph{E-\gls{mrt}:} \gls{mrt} towards the ergodic primary equivalent channel $\sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) \boldsymbol{h}_{\text{E}}^\mathsf{H}(x_{m_{\mathcal{K}}})$;
+				\item \emph{E-\gls{mrt}:} \gls{mrt} towards the ergodic composite channel $\sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) \boldsymbol{h}^\mathsf{H}(x_{m_{\mathcal{K}}})$;
 				\item \emph{D-\gls{mrt}:} \gls{mrt} towards the direct channel $\boldsymbol{h}_{\text{D}}^\mathsf{H}$.
@@
 			In the low-$\rho$ regime, the proposed \emph{\gls{pgd}} beamformer significantly outperforms both \gls{mrt} schemes in terms of total backscatter rate.
-			This is because backscatter detection relies on the \emph{relative difference} of accumulated receive energy under different symbol tuples.
+			This is because backscatter detection relies on the \emph{relative difference} of accumulated energy under different symbol tuples.
 			Such an energy diversity is enhanced by \emph{\gls{pgd}} that effectively exploits backscatter constellation and input distribution knowledge, rather than simply maximizing the direct/ergodic equivalent \gls{snr}.
 			As $\rho$ increases, the primary equivalent \gls{snr} outweighs the backscatter energy difference in \eqref{eq:weighted_sum_mutual_information_explicit}, and \emph{\gls{pgd}} beamformer becomes closer to both \gls{mrt} schemes.
-			At $\rho=1$, \emph{\gls{pgd}} and \emph{E-\gls{mrt}} boil down to \gls{mrt} towards the deterministic primary equivalent channel as in \gls{ris} literature \cite{Wu2019}.
+			At $\rho=1$, \emph{\gls{pgd}} and \emph{E-\gls{mrt}} boil down to \gls{mrt} towards the deterministic composite channel as in \gls{ris} literature \cite{Wu2019}.
 			Besides, the difference between \emph{E-\gls{mrt}} and \emph{D-\gls{mrt}} can be insignificant for dispersed RIScatter nodes.
@@
 			This is because each RIScatter node not only affects the primary equivalent \gls{snr} but also influences the relative energy difference that other nodes can create.
-			To maximize the total backscatter rate, some nodes closer to the user may need to sacrifice their own rate and use the state that \emph{minimizes} the primary equivalent channel strength, in order to increase the backscatter rate of other nodes.
+			To maximize the total backscatter rate, some nodes closer to the user may need to sacrifice their own rate and use the state that \emph{minimizes} the composite channel strength, in order to increase the backscatter rate of other nodes.
 			This accounts for the significant primary rate decrease in the low-$\rho$ regime.
@@
 			As $N \to \infty$, RIScatter nodes boil down to \gls{ris} elements with fixed reflection pattern during whole channel block and the total backscatter rate approaches \num{0}.
-			On the other hand, when $N$ is too small, the equivalent \gls{dmtmac} \eqref{eq:dmtmac} has very high error probabilities and the energy detection can thus be unreliable.
+			On the other hand, when $N$ is too small, the equivalent \gls{dmmac} \eqref{eq:dmmac} has very high error probabilities and the energy detection can thus be unreliable.
 			It explains the observation that $N=10$ provides lower backscatter achievable rate than $N=20$, although nodes are encoding at higher gross rate.
@@
 				J \bigl( P_{\mathcal{K}}(x_{m_{\mathcal{K}}}),P_{\mathcal{K}}'(x_{m_{\mathcal{K}}}) \bigr) \triangleq \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}})
-				\Biggl( \rho \log \Bigl(1 + \frac{\lvert \boldsymbol{h}_{\text{E}}^\mathsf{H}(x_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_v^2}\Bigr) + (1 - \rho) \sum_{m_{\mathcal{K}}'} P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}}) \log \frac{P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}}) P_{\mathcal{K}}'(x_{m_{\mathcal{K}}})}{P_{\mathcal{K}}'(\hat{x}_{m_{\mathcal{K}}'}) P_{\mathcal{K}}(x_{m_{\mathcal{K}}})} \Biggr).
+				\Biggl( \rho \log \Bigl(1 + \frac{\lvert \boldsymbol{h}^\mathsf{H}(x_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_v^2}\Bigr) + (1 - \rho) \sum_{m_{\mathcal{K}}'} P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}}) \log \frac{P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}}) P_{\mathcal{K}}'(x_{m_{\mathcal{K}}})}{P_{\mathcal{K}}'(\hat{x}_{m_{\mathcal{K}}'}) P_{\mathcal{K}}(x_{m_{\mathcal{K}}})} \Biggr).
 				\label{eq:intermediate_information_function}

### 2023-02-26 main.tex
:triangular_flag_on_post: Geoffrey 230226

@@
 	% The \gls{ap} is with an average transmit power budget $P=\qty{36}{\dBm}$, all nodes employs $M$-\gls{qam} with amplitude scattering ratio $\alpha=0.5$, and the user is with average noise power $\sigma_v^2=\qty{-40}{\dBm}$.
-	The \gls{ap} is with an average transmit power budget $P=\qty{36}{\dBm}$ and all nodes employs $M$-\gls{qam} with common amplitude scattering ratio $\alpha=0.5$.
+	The \gls{ap} is with an average transmit power budget $P=\qty{36}{\dBm}$ and all nodes employs $M$-\gls{qam} with $\alpha=0.5$.
 	For all channels involved, we consider a distance-dependent path loss model
@@
 			\item \emph{\gls{ambc}:} The user decodes both links independently and semi-coherently by treating the other as interference.
-			Hence, the primary achievable rate is approximately\footnote{To provide a preliminary benchmark, we regard the scattered component $\sum_{k} \alpha_k \boldsymbol{h}_{\text{C},k}^\mathsf{H} x_k \boldsymbol{w}s[n]$ as \gls{awgn} during primary decoding \cite{Long2020a}.}
+			The primary achievable rate is approximately\footnote{To provide a preliminary benchmark, we regard the scattered component $\sum_{k} \alpha_k \boldsymbol{h}_{\text{C},k}^\mathsf{H} x_k \boldsymbol{w}s[n]$ as \gls{awgn} during primary decoding \cite{Long2020a}.}
 			\begin{equation}
@@
 			% For a sufficiently large $N$, $\iota$ is negligible and the total backscatter rate approaches $K \log M$.
-			\item \emph{\gls{ris}:} Since the backscatter symbol tuple $x_{\mathcal{K}}$ is deterministic, the total backscatter rate is zero and the primary achievable rate becomes a special case of \eqref{eq:primary_mutual_information}
+			\item \emph{\gls{ris}:} The reflection pattern is deterministic and the total backscatter rate is zero.
+			The primary achievable rate is a special case of \eqref{eq:primary_mutual_information}
 			\begin{equation}
@@
 		On the other hand, for a large $N$, the maximum backscatter achievable rate of RIScatter is lower than \gls{bbc} and \gls{sr} but higher than \gls{ambc}.
-		This is because both RIScatter and \gls{ambc} employ semi-coherent energy detection and the adaptive channel coding of RIScatter provides better performance than equiprobable inputs of \gls{ambc} (especially at low \gls{snr}).
+		This is because both RIScatter and \gls{ambc} employ semi-coherent energy detection, and the adaptive channel coding of RIScatter provides better performance than equiprobable inputs of \gls{ambc} especially at the low \gls{snr} of double fading.
 	\end{subsection}
@@
 		\end{figure}
-		The objective of this study is to demonstrate RIScatter nodes can leverage \gls{csi}- and \gls{qos}-adaptive input distribution design to balance backscatter modulation and passive beamforming.
-		For one RIScatter node with $M=4$, we evaluate the \gls{kkt} input distribution\footnote{Since problem \eqref{op:input_distribution} is convex when $K=1$, the \gls{kkt} solution is always global optimal in this case.} at different primary \gls{qos} and present the result in Fig.~\ref{fg:distribution_weights}.
-		At $\rho=0$ where the backscatter performance is prioritized, the optimal input distribution is zero on two states and nearly uniform on the other two.
-		This is because, due to the weak scattered signal, the conditional energy \gls{pdf} under different hypotheses can be closely spaced as illustrated in Fig.~\ref{fg:energy_distribution}.
-		In such cases, the extreme states producing the lowest/highest energy are always assigned with non-zero probability, while the middle ones may not provide enough energy difference and thus end up unused.
+		The objective is to demonstrate RIScatter nodes can leverage \gls{csi}- and \gls{qos}-adaptive input distribution design to balance backscatter modulation and passive beamforming.
+		For one RIScatter node with $M=4$, we evaluate the \gls{kkt} input distribution\footnote{Problem \eqref{op:input_distribution} is convex when $K=1$ and the \gls{kkt} solution is global optimal.} at different \gls{qos} and present the result in Fig.~\ref{fg:distribution_weights}.
+		At $\rho=0$ where the backscatter performance is prioritized, the optimal input distribution is \num{0} on two states and nearly uniform on the other two.
+		This is inline with Shannon's observation that binary antipodal inputs can be good enough for channel capacity at the low \gls{snr} \cite{Shannon1948}.
+		Due to the weak scattered signal, the conditional energy \gls{pdf} under different hypotheses can be closely spaced as in Fig.~\ref{fg:energy_distribution}.
+		The extreme states producing the lowest/highest energy are always assigned with non-zero probability and the middle ones may not provide enough energy difference and thus end up unused.
 		At $\rho=1$ where the primary performance is prioritized, the optimal input distribution is \num{1} at the state that maximizes the primary \gls{snr} and \num{0} at the others.
 		That is, the reflection pattern becomes deterministic and the RIScatter node boils down to a discrete \gls{ris} element.
-		Increasing $\rho$ from \num{0} to \num{1} provides a smooth transition from backscatter modulation to passive beamforming, which suggests RIScatter unifies \gls{bc} and \gls{ris} from a probabilistic perspective.
+		Increasing $\rho$ from \num{0} to \num{1} provides a smooth transition from backscatter modulation to passive beamforming and proves RIScatter unifies \gls{bc} and \gls{ris} from a probabilistic perspective.
 	\end{subsection}
@@
 				\item \emph{Exhaustion:} Exhaustive search over the $M$-dimensional probability simplex with resolution $\Delta p = \num{e-2}$;
-				\item \emph{\gls{kkt}:} Numerical \gls{kkt} result evaluation by Algorithm \ref{al:input_distribution};
+				\item \emph{\gls{kkt}:} Numerical \gls{kkt} evaluation by Algorithm \ref{al:input_distribution};
 				\item \emph{Equiprobable:} Uniform input distribution for all nodes.
@@
 			Fig.~\subref*{fg:region_distribution} shows the average achievable rate regions for those designs.
-			We observe \emph{Cooperation} provides the outer bound since joint encoding is always beneficial.
-			The \emph{average} rate performance of \emph{Exhaustion} and \emph{\gls{kkt}} completely coincide with each other, demonstrating \gls{kkt} input distribution is favorable for a moderate $K$ as stated in Remark \ref{re:input_kkt_distribution}.
-			\emph{Equiprobable} experiences minor backscatter and major primary rate losses without \gls{csi}- and \gls{qos}-adaptive backscatter encoding.
-			Both gaps should become larger when $M$ and $K$ increase.
-			For the recovery methods, the simple \emph{Marginalization} provides a close result to \emph{\gls{kkt}}, but \emph{Randomization} and \emph{Decomposition} fail our expectations for most channel realizations.
-			Those observations emphasize the importance of (joint) adaptive RIScatter encoding and demonstrate the advantages of the proposed \gls{kkt} input distribution design.
+			We observe Cooperation provides the outer bound since joint encoding is always beneficial.
+			The average rate performance of Exhaustion and \gls{kkt} completely coincide with each other, demonstrating \gls{kkt} input distribution is favorable for a moderate $K$ as stated in Remark \ref{re:input_kkt_distribution}.
+			Equiprobable experiences minor backscatter and major primary rate losses without exploiting \gls{csi} and \gls{qos}.
+			Both rate gaps should be larger when $M$ and/or $K$ increase.
+			For the recovery methods, the simple Marginalization provides a close performance to \gls{kkt}, but Randomization and Decomposition fail our expectations for most channel realizations.
+			Those observations emphasize the importance of (joint) adaptive RIScatter encoding and demonstrate the advantage of the proposed \gls{kkt} input distribution design.
 		\end{subsubsection}
@@
 			Fig.~\subref*{fg:region_beamforming} presents the average achievable rate regions for those schemes.
-			In the low-$\rho$ regime, the proposed \emph{\gls{pgd}} beamformer significantly outperforms both \gls{mrt} schemes in terms of total backscatter rate.
-			This is because backscatter detection relies on the \emph{relative difference} of accumulated energy under different symbol tuples.
-			Such an energy diversity is enhanced by \emph{\gls{pgd}} that effectively exploits backscatter constellation and input distribution knowledge, rather than simply maximizing the direct/ergodic equivalent \gls{snr}.
-			As $\rho$ increases, the primary equivalent \gls{snr} outweighs the backscatter energy difference in \eqref{eq:weighted_sum_mutual_information_explicit}, and \emph{\gls{pgd}} beamformer becomes closer to both \gls{mrt} schemes.
-			At $\rho=1$, \emph{\gls{pgd}} and \emph{E-\gls{mrt}} boil down to \gls{mrt} towards the deterministic composite channel as in \gls{ris} literature \cite{Wu2019}.
-			Besides, the difference between \emph{E-\gls{mrt}} and \emph{D-\gls{mrt}} can be insignificant for dispersed RIScatter nodes.
-			Those observations prove the proposed \emph{\gls{pgd}} active beamforming design can exploit the \gls{csi}, \gls{qos}, and backscatter constellation to balance the primary equivalent \gls{snr} and backscatter energy difference and enlarge the achievable rate region for RIScatter.
+			In the low-$\rho$ regime, the proposed \gls{pgd} beamformer significantly outperforms both \gls{mrt} schemes in terms of total backscatter rate.
+			This is because the semi-coherent backscatter decoding relies on the \emph{relative difference} of accumulated energy under different symbol tuples.
+			Such an energy diversity is enhanced by \gls{pgd} that effectively exploits backscatter constellation and input distribution knowledge rather than simply maximizing the direct/ergodic \gls{snr}.
+			As $\rho$ increases, the primary equivalent \gls{snr} outweighs the backscatter energy difference in \eqref{eq:weighted_sum_mutual_information_explicit} and \gls{pgd} beamformer becomes closer to both \gls{mrt} schemes.
+			At $\rho=1$, both \gls{pgd} and E-\gls{mrt} boil down to \gls{mrt} towards the composite channel.
+			The difference between E-\gls{mrt} and D-\gls{mrt} is insignificant when RIScatter nodes are dispersed.
+			Those observations prove the proposed \gls{pgd} active beamforming design can exploit the \gls{csi}, \gls{qos}, and backscatter constellation to balance the primary equivalent \gls{snr} and backscatter energy difference and enlarge the achievable rate region.
 		\end{subsubsection}
@@
 			Fig.~\subref*{fg:region_threshold} reveals the average achievable rate region for those strategies.
-			The distribution-aware schemes \emph{\gls{dp}}, \emph{\gls{smawk}} and \emph{Bisection} ensure higher total backscatter rate than the non-adaptive \emph{\gls{ml}}.
+			The distribution-aware schemes \gls{dp}, \gls{smawk} and Bisection ensure higher total backscatter rate than \gls{ml}.
 			This is because the total backscatter rate \eqref{eq:backscatter_mutual_information} is a function of both input distribution and decision regions, and the rate-optimal threshold design heavily depends on input distribution.
-			For example, the backscatter symbol tuples with zero input probability should be assigned with empty decision regions, in order to increase the success detection chances of other hypotheses.
+			For example, the backscatter symbol tuples with zero input probability should be assigned with empty decision regions in order to increase the success detection rates of other hypotheses.
 			It highlights the importance of joint input distribution and decision threshold design in rate maximization problems.
@@
 			This accounts for the significant primary rate decrease in the low-$\rho$ regime.
-			On the other hand, when the primary link is prioritized, the RIScatter nodes boil down to \gls{ris} elements and enjoy a classic passive array gain of $N^2$.
+			On the other hand, when the primary link is prioritized, the RIScatter nodes boil down to \gls{ris} elements and enjoy a conventional passive array gain $N^2$.
 		\end{subsubsection}
@@
 			Fig.~\subref*{fg:region_txs} illustrates the impact of transmit antennas $Q$ on the average performance.
-			As $Q$ increases, more transmitter-scatter-receiver paths become available to \emph{\gls{pgd}} and their diversity can be further exploited to enhance the primary equivalent \gls{snr} and backscatter energy difference, which leads to a larger achievable rate region.
+			As $Q$ increases, more scattered paths are available to \gls{pgd} and the channel diversity can be further exploited to enhance the primary equivalent \gls{snr} and backscatter energy difference, which enlarges the achievable rate region.
 			It emphasizes the importance of multi-antenna RIScatter systems and demonstrate the effectiveness of the proposed \gls{pgd} design.
@@
 		\begin{subsubsection}{Spreading factor}
-			Fig.~\subref*{fg:region_duration} presents how the spreading factor $N$ affects the achievable rate region, where the unit of total backscatter rate is bits per primary block (to indicate throughput).
+			Fig.~\subref*{fg:region_duration} presents how the spreading factor $N$ affects the achievable rate region.
+			Please notice here the unit of total backscatter rate is bits per primary block to indicate throughput.
 			Apparently, using a very large $N$ can severely constrain the backscatter throughput, since the gain in energy certainty (by law of large numbers) cannot withstand the loss in gross rate.
 			As $N \to \infty$, RIScatter nodes boil down to \gls{ris} elements with fixed reflection pattern during whole channel block and the total backscatter rate approaches \num{0}.
-			On the other hand, when $N$ is too small, the equivalent \gls{dmmac} \eqref{eq:dmmac} has very high error probabilities and the energy detection can thus be unreliable.
-			It explains the observation that $N=10$ provides lower backscatter achievable rate than $N=20$, although nodes are encoding at higher gross rate.
-			Therefore, we conclude the design of spreading factor $N$ in RIScatter systems should account for multiple factors (e.g., data rate requirements, load switching constraints at the nodes, and signal processing capability at the user).
+			On the other hand, when $N$ is too small, the equivalent \gls{dmmac} \eqref{eq:dmmac} has very high error probabilities and the energy detection is thus unreliable.
+			It explains the observation that $N=10$ provides lower backscatter achievable rate than $N=20$.
+			Therefore, we conclude the design of spreading factor $N$ in RIScatter systems should accommodate multiple factors (e.g., data rate requirements, load switching constraints at the nodes, and signal processing capability at the user).
 		\end{subsubsection}
@@
 			It shows the proposed practical semi-coherent backscatter energy detection is suitable for a wide range of noise levels.
-			When $\sigma_v^2$ relatively high, one can choose a larger $N$ to maintain the backscatter \gls{snr} for better detection performance.
+			When $\sigma_v^2$ relatively high, one can choose a larger $N$ to maintain the backscatter \gls{snr} for better energy detection performance.
 		\end{subsubsection}
@@
 			This is because the double fading effect is less severe for near-far setups.
-			In a multi-user RIScatter system with dispersed nodes, each node may be allocated to the nearest user to guarantee uniformly good performance for both links.
+			In a multi-user RIScatter system with dispersed nodes, each node may be assigned to the nearest user to guarantee uniformly good performance for both links.
 		\end{subsubsection}
@@
 \begin{section}{Conclusion}
-	This paper introduced RIScatter as a low-power scatter protocol that unifies backscatter modulation and dynamic passive beamforming by smart input distribution and practical receiver design.
-	Starting from scattering principles, we showed how RIScatter nodes include information node of \gls{bc} and reflect element of \gls{ris} as special cases, how they can be built over existing passive scatter devices, and how they simultaneously encode self information and assist legacy transmission.
-	We also propose a practical RIScatter receiver that preserves the benefits of backscatter modulation and dynamic passive beamforming without \gls{sic}.
+	This paper introduced RIScatter as a low-power scatter protocol that simultaneously enables backscatter modulation and dynamic passive beamforming by smart input distribution design.
+	Starting from scattering principles, we showed how RIScatter nodes generalize information nodes of \gls{bc} and reflect elements of \gls{ris} as special cases, how they can be built over existing passive scatter devices, and how they simultaneously encode self information and assist legacy transmission.
+	We also propose a practical \gls{sic}-free receiver that exploits the properties of active-passive coexisting networks to guarantee primary benefit and improve backscatter throughput.
 	The achievable primary-total-backscatter rate region is then studied for a single-user multi-node RIScatter system, where the input distribution, active beamforming, and decision thresholds are iteratively updated.
-	Numerical results not only validated the proposed algorithms, but also emphasized the importance of adaptive input distribution and cooperative decoding on both primary and backscatter links.
-
-	One possible direction is to consider backscatter detection over the received signal domain rather than energy domain, where multi-antenna and learning-based approaches can be promising.
+	Numerical results not only validated the proposed algorithms but also emphasized the importance of adaptive input distribution and cooperative decoding for both primary and backscatter links.
+
+	One possible future direction is to consider backscatter detection over the received signal domain rather than energy domain, where multi-antenna \cite{Liu2022c} and learning-based approaches can be promising.
 	Another interesting question is how to design RIScatter node and receiver in a multi-user system to fully exploit the dynamic passive beamforming that naturally origins from backscatter modulation.
@@
 
+\begin{section}{Acknowledgement}
+	The authors would like to thank Prof. Geoffrey Ye Li for his clinical comments on earlier versions of the manuscript.
+\end{section}
+
 \bibliographystyle{IEEEtran}

### 2023-03-01 arxiv.tex
:triangular_flag_on_post: JSAC 230301

--- 2023-02-26 main.tex
@@
 \makeatother
+
 \algrenewcommand{\algorithmicrequire}{\textbf{Input:}}
@@
 \begin{IEEEkeywords}
-	Input distribution design, energy detection, \gls{sic}-free receiver, symbol-level precoding, active-passive coexisting network, backscatter communication, reconfigurable intelligent surface, ambient backscatter communication, symbiotic radio.
+	Input distribution design, symbol-level precoding, active-passive coexisting network, \gls{sic}-free receiver, energy detection, backscatter communication, reconfigurable intelligent surface, ambient backscatter communication, symbiotic radio.
 \end{IEEEkeywords}
@@
 	As a special case of \gls{cr}, active and passive transmissions coexist and interplay in \gls{ambc} and \gls{sr}.
-	Such a coexistence is classified into commensal (overlay), parasitic (underlay), and competitive paradigms, and their achievable rate and outage performance were investigated in \cite{Guo2019b,Ding2020}.
+	Such a coexistence is classified into commensal (overlay), parasitic (underlay), and competitive (interfering) paradigms, and their achievable rate and outage performance were investigated in \cite{Guo2019b,Ding2020}.
 	For the co-located cooperative receiver, the \gls{ber} performance of \gls{ml}, linear, and \gls{sic} detectors are derived over flat fading channels \cite{Yang2018}.
@@
 		\item Backscatter signal strength is much weaker than primary due to the \emph{double fading} effect;
-		\item The spreading factor (i.e., backscatter symbol duration over primary) is usually large\footnote{The load-switching interval of low-power backscatter modulators is usually \num{0.1} to \qty{10}{\us} \cite{Torres2021}, accounting for a typical spreading factor between \num{10} and \num{e3}.}.
+		\item The spreading factor (i.e., backscatter symbol duration over primary) is usually large\footnote{The load-switching interval of low-power backscatter modulators is usually {0.1} to \SI{10}{\us} \cite{Torres2021}, accounting for a typical spreading factor between $10$ and $10^3$.}.
 	\end{enumerate}
@@
 	% However, it significantly increases \gls{sic} operations per backscatter symbol and severely limits the backscatter \emph{throughput}.
-	However, it severely limits the backscatter throughput and requires numerous \gls{sic} per backscatter symbol.
+	However, this severely limits the backscatter throughput and requires numerous \gls{sic} per backscatter symbol.
 
@@
 	It was first proposed to fine-tune the \gls{ofdm} resource blocks \cite{Yang2020} then extended to the downlink power and uplink information phases of \gls{wpcn} \cite{Wu2021,Wu2021d,Hua2022a}.
-	However, dynamic \gls{ris} carries no information since the reflection state at each time slot is known to the receiver.
-	\gls{ris} can also be used as an index-modulated information source and prototypes have been developed for \gls{psk} \cite{Tang2019a} and \gls{qam} \cite{Dai2020a}.
+	However, dynamic \gls{ris} carries \emph{no} additional information since the reflection state at each time slot is known to the receiver.
+	\gls{ris} can also be used as an information source and prototypes have been developed for \gls{psk} \cite{Tang2019a} and \gls{qam} \cite{Dai2020a}.
 	From an information-theoretic perspective, the authors of \cite{Karasik2020} reported that joint transmitter-\gls{ris} encoding achieves the capacity of \gls{ris}-aided finite-input channel and using \gls{ris} as a naive passive beamformer to maximize the receive \gls{snr} is generally suboptimal.
@@
 	We consider backscatter energy detection and formulate a \gls{dmmac} over disjoint decision regions.
-	Thanks to the double modulation and symbol-level passive precoding, the semi-coherent backscatter decoding also acts as part of channel training.
-	Once the backscatter information is successfully decoded, its contribution can be modelled within composite channel as dynamic passive beamforming rather than re-precoded and cancelled.
+	Thanks to the double modulation and symbol-level passive precoding, the semi-coherent backscatter decoding is essentially part of channel training.
+	Once the backscatter information is successfully decoded, its contribution can be modelled within composite channel as dynamic passive beamforming (rather than re-precoded and cancelled).
 	It requires only one energy comparison and re-encoding per backscatter symbol and is much efficient than conventional decoding based on \gls{sic} and \gls{mrc}.
 	It is also suitable for arbitrary input distribution and spreading factor, which significantly improves backscatter throughput.
-	This is the first paper to consider practical backscatter-primary decoding scheme to exploit dynamic passive beamforming at the co-located receiver.
+	This is the first paper to consider practical backscatter-primary decoding scheme to exploit backscatter modulation as dynamic passive beamforming at the co-located receiver.
 
@@
 		% An antenna-based scatterer usually consists of an integrated antenna, a load-switching modulator, an energy harvester, and on-chip components (e.g., microcontroller and sensors) \cite{Dobkin2012}.
-		An antenna scatterer first receives the impinging signals then reradiates some back to the space and dissipates the remaining \cite{Dobkin2012}.
+		The former first receives the impinging signals then reradiates some back to the space and dissipates the remaining \cite{Dobkin2012}.
 		% In comparison, a typical metamaterial-based scatterer comprises an outer metamaterial layer of numerous sub-wavelength metallic/dielectric patches (with tunable permittivity/permeability), a middle copper plate layer that avoids leakage, an inner circuit board layer that adjusts patch responses, and an integrated microcontroller/\glsentryshort{fpga} for coordination and control \cite{Wu2020}.
 		% In comparison, a typical metamaterial-based scatterer comprises an outer metamaterial layer of numerous sub-wavelength metallic/dielectric patches (with tunable permittivity/permeability), a middle copper plate layer that avoids leakage, an inner circuit board layer that adjusts patch responses, and an integrated microcontroller/\glsentryshort{fpga} for coordination and control \cite{Wu2020}.
-		An ideal metamaterial scatterer reflects the wave at the space-metamaterial boundary without receiving them and mainly applies a phase shift on top.
+		In contrast, the latter reflects the wave at the space-metamaterial boundary without receiving them and mainly applies a phase shift.
 		% In practice, both types of scatterers have {finite} reflection states with non-zero reflection loss.
 		% In general, the scattered signal consists of a structural mode component that consistently contributes to environment multipath and can be modelled within \gls{csi}, and an \emph{antenna} mode component that depends on the impedance mismatch and can be used for backscatter modulation and/or passive beamforming \cite{Hansen1989}.
-		In general, the scattered signal consists of a structural mode component that consistently contributes to environment multipath and an antenna mode component that depends on the impedance mismatch \cite{Hansen1989}.
-		The former is usually modelled within \gls{csi} while the latter is mainly used for backscatter modulation and/or passive beamforming.
+		The scattered signal consists of a structural mode component that consistently contributes to environment multipath (usually modelled within \gls{csi}) and an antenna mode component that depends on the impedance mismatch (mainly used for backscatter modulation and/or passive beamforming) \cite{Hansen1989}.
+		% The former is usually modelled within \gls{csi} while the latter is mainly used for backscatter modulation and/or passive beamforming.
 		For an antenna (resp. metamaterial) scatterer with $M$ reflection states, the reflection coefficient at state $m \in \mathcal{M} \triangleq \{1,\ldots,M\}$ is
@@
 		where $Z_m$ is the antenna load (resp. metamaterial unit) impedance at state $m$ and $Z$ is the antenna input (resp. medium characteristic) impedance.
+
 		\gls{bc} treats scatterers as information sources that \emph{randomly} choosing the reflection state based on information symbol.
@@
 		RIScatter generalizes both from a probabilistic perspective where each node \emph{semi-randomly} chooses the reflection state with the guidance of probability $P(\Gamma_m)$.
-		The input distribution is flexibly designed as a joint function of the information source, \gls{csi}, and \gls{qos}.
+		The input distribution is flexibly designed as a joint function of the information source, \gls{csi}, and \gls{qos} of both links.
 		\gls{bc} and (static) \gls{ris} can be regarded as its extreme cases where the input distribution boils down to uniform and degenerate, respectively.
@@
 				Shadowing means presence of primary link.
-				In this example, the optimal passive beamformer is state \num{2} and its input probability for RIScatter is \num{0.75}.
-				% RIScatter node transmit symbol \num{1}
-				The spreading factor is \num{4} for RIScatter and \num{8} for \gls{ambc}/\gls{sr}.
+				In this example, the optimal passive beamformer is state {2} and its input probability for RIScatter is {0.75}.
+				% RIScatter node transmit symbol {1}
+				The spreading factor is {4} for RIScatter and {8} for \gls{ambc}/\gls{sr}.
 			}
@@
 			\centering
-			\resizebox{0.8\columnwidth}{!}{
-				\input{assets/illustration/energy_distribution.tex}
-			}
+			% \resizebox{0.8\columnwidth}{!}{
+			% 	\input{assets/illustration/energy_distribution.tex}
+			% }
+			\includegraphics[width=0.8\columnwidth]{assets/illustration/energy_distribution.jpg}
 			\caption{
@@
 	Problem \eqref{op:weighted_sum_rate} generalizes conventional \gls{bc} by allowing \gls{csi}- and \gls{qos}-adaptive input distribution and decision region design.
-	It also generalizes the discrete \gls{ris} phase shift selection by allowing stochastic reflection, relaxing the feasible domain from the vertices of $M$-dimensional probability simplex to the simplex itself.
+	It also generalizes the discrete \gls{ris} phase shift selection problem by stochastic reflection that relaxes the feasible domain from the vertices of $M$-dimensional probability simplex to the simplex itself.
 	Problem \eqref{op:weighted_sum_rate} is highly non-convex and we propose a \gls{bcd} algorithm that iteratively updates $\{\boldsymbol{p}_k\}_{k \in \mathcal{K}}$, $\boldsymbol{w}$ and $\boldsymbol{t}$.
@@
 		\begin{remark}
-			Energy detector design has no impact on the primary achievable rate since the composite channel \eqref{eq:equivalent_channel} can always be reconstructed by re-encoding.
-			It suggests any thresholding scheme that maximize the total backscatter rate \eqref{eq:backscatter_mutual_information} is also optimal for problem \eqref{op:decision_threshold}.
+			Energy detector design has no impact on the primary achievable rate since the composite channel \eqref{eq:equivalent_channel} can always be reconstructed after backscatter decoding and re-encoding.
+			It suggests any thresholding scheme maximizing the total backscatter rate \eqref{eq:backscatter_mutual_information} is also optimal for problem \eqref{op:decision_threshold}.
 			\label{re:backscatter_decision}
@@
 	In this section, we provide numerical results to evaluate the proposed input distribution, active beamforming, and backscatter decision designs for the considered RIScatter system.
-	We assume the AP-user distance is \qty{10}{\meter} and at least one RIScatter nodes are randomly dropped in a disk centered at the user with radius $r$.
-	% The \gls{ap} is with an average transmit power budget $P=\qty{36}{\dBm}$, all nodes employs $M$-\gls{qam} with amplitude scattering ratio $\alpha=0.5$, and the user is with average noise power $\sigma_v^2=\qty{-40}{\dBm}$.
-	The \gls{ap} is with an average transmit power budget $P=\qty{36}{\dBm}$ and all nodes employs $M$-\gls{qam} with $\alpha=0.5$.
+	We assume the AP-user distance is \SI{10}{\meter} and at least one RIScatter nodes are randomly dropped in a disk centered at the user with radius $r$.
+	% The \gls{ap} is with an average transmit power budget $P=\SI{36}{\dBm}$, all nodes employs $M$-\gls{qam} with amplitude scattering ratio $\alpha=0.5$, and the user is with average noise power $\sigma_v^2=\SI{-40}{\dBm}$.
+	The \gls{ap} is with an average transmit power budget $P=\SI{36}{\dBm}$ and all nodes employs $M$-\gls{qam} with $\alpha=0.5$.
 	For all channels involved, we consider a distance-dependent path loss model
@@
 	\end{equation}
-	where $d$ is the transmission distance, $L_0=-\qty{30}{\dB}$ is the reference path loss at $d_0=\qty{1}{\meter}$, $\kappa$ is the Rician K-factor, $\bar{\boldsymbol{H}}$ is the deterministic line-of-sight component with unit-magnitude entries, and $\tilde{\boldsymbol{H}}$ is the Rayleigh fading component with standard \gls{iid} \gls{cscg} entries.
+	where $d$ is the transmission distance, $L_0=-\SI{30}{\dB}$ is the reference path loss at $d_0=\SI{1}{\meter}$, $\kappa$ is the Rician K-factor, $\bar{\boldsymbol{H}}$ is the deterministic line-of-sight component with unit-magnitude entries, and $\tilde{\boldsymbol{H}}$ is the Rayleigh fading component with standard \gls{iid} \gls{cscg} entries.
 	We choose $\gamma_{\text{D}}=2.6$, $\gamma_{\text{F}}=2.4$, $\gamma_{\text{B}}=2$, and $\kappa_{\text{D}}=\kappa_{\text{F}}=\kappa_{\text{B}}=5$ for direct, forward and backward links.
 	The finite decision threshold domain $\mathcal{T}$ is obtained by $b$-bit uniform discretization over the critical interval defined by the confidence bounds of edge hypotheses (i.e., lower bound of $\mathcal{H}_1$ and upper bound of $\mathcal{H}_L$) with confidence $1-\varepsilon$.
-	We choose $b=9$ and $\varepsilon=\num{e-3}$.
-	All achievable rate points/regions are averaged over \num{e3} channel realizations.
+	We set $b=9$ and $\varepsilon={e-3}$.
+	All achievable rate points/regions are averaged over $10^3$ channel realizations.
 
@@
 				}
-				\caption{Typical convergence curves at $\rho=0$ for $Q=4$, $K=8$, $M=2$, $N=20$, $\sigma_v^2=\qty{-40}{\dBm}$ and $r=\qty{2}{\meter}$.}
+				\caption{Typical convergence curves at $\rho=0$ for $Q=4$, $K=8$, $M=2$, $N=20$, $\sigma_v^2=\SI{-40}{\dBm}$ and $r=\SI{2}{\meter}$.}
 				\label{fg:wsr_convergence}
@@
 			In Fig.~\ref{fg:wsr_convergence}, we plot the weighted sum of primary and total backscatter rates at $\rho=0$ for \gls{kkt}, \gls{pgd} and \gls{bcd} algorithms on the first call.
-			For $K=8$ and $M=2$, Algorithm \ref{al:input_distribution} typically takes around \num{100} fast iterations to converge to the \gls{kkt} input distribution.
-			For $Q=4$, around \num{10} iterations are required for Algorithm \ref{al:active_beamforming} to converge.
-			Overall, the initial \gls{bcd} algorithm requires at most \num{5} iterations to converge.
+			For $K=8$ and $M=2$, Algorithm \ref{al:input_distribution} typically takes around {100} fast iterations to converge to the \gls{kkt} input distribution.
+			For $Q=4$, around {10} iterations are required for Algorithm \ref{al:active_beamforming} to converge.
+			Overall, the initial \gls{bcd} algorithm requires at most {5} iterations to converge.
 			At the following points (not presented here), the convergence of all three algorithms are much faster thanks to the progressive initialization.
@@
 			}
-			\caption{Typical achievable rate region/points of scattering applications for $Q=1$, $K=1$, $M=4$, $N=e3$, $\sigma_v^2=\qty{-40}{\dBm}$ and $r=\qty{2}{\meter}$.}
+			\caption{Typical achievable rate region/points of scattering applications for $Q=1$, $K=1$, $M=4$, $N=10^3$, $\sigma_v^2=\SI{-40}{\dBm}$ and $r=\SI{2}{\meter}$.}
 			\label{fg:region_comparison}
@@
 		This is because both RIScatter and \gls{ambc} employ semi-coherent energy detection, and the adaptive channel coding of RIScatter provides better performance than equiprobable inputs of \gls{ambc} especially at the low \gls{snr} of double fading.
+		When multiple antenna is available at the \gls{ap}, active beamforming can be optimized for RIScatter nodes and the backscatter rate gain over \gls{ambc} can be even larger.
 	\end{subsection}
@@
 			}
-			\caption{Typical RIScatter reflection state distribution at different $\rho$ for $Q=1$, $K=1$, $M=4$, $N=20$, $\sigma_v^2=\qty{-40}{\dBm}$ and $r=\qty{2}{\meter}$.}
+			\caption{Typical RIScatter reflection state distribution at different $\rho$ for $Q=1$, $K=1$, $M=4$, $N=20$, $\sigma_v^2=\SI{-40}{\dBm}$ and $r=\SI{2}{\meter}$.}
 			\label{fg:distribution_weights}
@@
 		For one RIScatter node with $M=4$, we evaluate the \gls{kkt} input distribution\footnote{Problem \eqref{op:input_distribution} is convex when $K=1$ and the \gls{kkt} solution is global optimal.} at different \gls{qos} and present the result in Fig.~\ref{fg:distribution_weights}.
-		At $\rho=0$ where the backscatter performance is prioritized, the optimal input distribution is \num{0} on two states and nearly uniform on the other two.
+		At $\rho=0$ where the backscatter performance is prioritized, the optimal input distribution is {0} on two states and nearly uniform on the other two.
 		This is inline with Shannon's observation that binary antipodal inputs can be good enough for channel capacity at the low \gls{snr} \cite{Shannon1948}.
@@
 		The extreme states producing the lowest/highest energy are always assigned with non-zero probability and the middle ones may not provide enough energy difference and thus end up unused.
-		At $\rho=1$ where the primary performance is prioritized, the optimal input distribution is \num{1} at the state that maximizes the primary \gls{snr} and \num{0} at the others.
+		At $\rho=1$ where the primary performance is prioritized, the optimal input distribution is {1} at the state that maximizes the primary \gls{snr} and {0} at the others.
 		That is, the reflection pattern becomes deterministic and the RIScatter node boils down to a discrete \gls{ris} element.
-		Increasing $\rho$ from \num{0} to \num{1} provides a smooth transition from backscatter modulation to passive beamforming and proves RIScatter unifies \gls{bc} and \gls{ris} from a probabilistic perspective.
+		Increasing $\rho$ from {0} to {1} provides a smooth transition from backscatter modulation to passive beamforming and proves RIScatter unifies \gls{bc} and \gls{ris} from a probabilistic perspective.
 	\end{subsection}
@@
 			\caption{
-				Average primary-total-backscatter rate regions by different input distribution, active beamforming, and decision threshold schemes for $K=2$, $M=4$, $N=20$, $\sigma_v^2=\qty{-40}{\dBm}$ and $r=\qty{2}{\meter}$.
+				Average primary-total-backscatter rate regions by different input distribution, active beamforming, and decision threshold schemes for $K=2$, $M=4$, $N=20$, $\sigma_v^2=\SI{-40}{\dBm}$ and $r=\SI{2}{\meter}$.
 			}
@@
 				\item \emph{Cooperation:} Joint nodes encoding using a $K$-dimensional probability array $P_{\mathcal{K}}(x_{m_{\mathcal{K}}})$ by Algorithm \ref{al:input_distribution};
-				\item \emph{Exhaustion:} Exhaustive search over the $M$-dimensional probability simplex with resolution $\Delta p = \num{e-2}$;
+				\item \emph{Exhaustion:} Exhaustive search over the $M$-dimensional probability simplex with resolution $\Delta p = {e-2}$;
 				\item \emph{\gls{kkt}:} Numerical \gls{kkt} evaluation by Algorithm \ref{al:input_distribution};
@@
 				\item \emph{Marginalization:} Marginal probability distributions;
-				\item \emph{Decomposition:} Normalized rank-\num{1} \gls{cp} decomposition tensors by \texttt{Tensor Toolbox} \cite{Bader2022};
+				\item \emph{Decomposition:} Normalized rank-{1} \gls{cp} decomposition tensors by \texttt{Tensor Toolbox} \cite{Bader2022};
 				\item \emph{Randomization:} Gaussian randomization with the guidance of correlation matrix \cite{Calvo2010}.
@@
 			Fig.~\subref*{fg:region_distribution} shows the average achievable rate regions for those designs.
-			We observe Cooperation provides the outer bound since joint encoding is always beneficial.
-			The average rate performance of Exhaustion and \gls{kkt} completely coincide with each other, demonstrating \gls{kkt} input distribution is favorable for a moderate $K$ as stated in Remark \ref{re:input_kkt_distribution}.
+			We observe Cooperation provides the outer bound and joint encoding can be beneficial.
+			The average rate performance of Exhaustion and \gls{kkt} completely coincide with each other, demonstrating \gls{kkt} input distribution is favorable for a moderate $K$ as mentioned in Remark \ref{re:input_kkt_distribution}.
 			Equiprobable experiences minor backscatter and major primary rate losses without exploiting \gls{csi} and \gls{qos}.
@@
 		\end{figure}
-		In this study, we choose $Q=4$, $K=8$, $M=2$, $N=20$, $\sigma_v^2=\qty{-40}{\dBm}$ and $r=\qty{2}{\meter}$ as a reference.
+		In this study, we choose $Q=4$, $K=8$, $M=2$, $N=20$, $\sigma_v^2=\SI{-40}{\dBm}$ and $r=\SI{2}{\meter}$ as a reference.
 		\begin{subsubsection}{Number of Nodes}
@@
 			We notice increasing the reflection states has a marginal effect on both primary and total backscatter rates.
-			This is because once the scope of reflection coefficient is determined, using denser constellation points may not create enough phase resolution and energy diversity for primary and backscatter links.
-			Due to the maximum amplitude normalization in \eqref{eq:backscatter_modulation}, the average rate region of \num{8}-\gls{qam} (points on rectangle border) is smaller than that of \num{4}-\gls{qam} (points on square vertices), and the inner constellation points with smaller amplitudes are less frequently used.
-			On the other hand, \num{16}-\gls{qam} provides significant higher backscatter rate benefit than primary.
+			This is because once the scope of reflection coefficient is determined, using denser constellation points only creates marginal phase resolution and energy diversity for primary and backscatter links.
+			Due to the maximum amplitude normalization in \eqref{eq:backscatter_modulation}, the average rate region of {8}-\gls{qam} (points on rectangle border) is smaller than that of {4}-\gls{qam} (points on square vertices), and the {4} points on the rectangle edges are less frequently used.
+			On the other hand, {16}-\gls{qam} provides significant higher backscatter rate benefit than primary.
 			It motivates one to use high-resolution metamaterial units as RIScatter nodes.
@@
 			Apparently, using a very large $N$ can severely constrain the backscatter throughput, since the gain in energy certainty (by law of large numbers) cannot withstand the loss in gross rate.
-			As $N \to \infty$, RIScatter nodes boil down to \gls{ris} elements with fixed reflection pattern during whole channel block and the total backscatter rate approaches \num{0}.
+			As $N \to \infty$, RIScatter nodes boil down to \gls{ris} elements with fixed reflection pattern during whole channel block and the total backscatter rate approaches {0}.
 			On the other hand, when $N$ is too small, the equivalent \gls{dmmac} \eqref{eq:dmmac} has very high error probabilities and the energy detection is thus unreliable.
-			It explains the observation that $N=10$ provides lower backscatter achievable rate than $N=20$.
+			It explains the observation that $N=10$ provides lower backscatter throughput than $N=20$.
 			Therefore, we conclude the design of spreading factor $N$ in RIScatter systems should accommodate multiple factors (e.g., data rate requirements, load switching constraints at the nodes, and signal processing capability at the user).
@@
 \begin{section}{Conclusion}
-	This paper introduced RIScatter as a low-power scatter protocol that simultaneously enables backscatter modulation and dynamic passive beamforming by smart input distribution design.
+	This paper introduced RIScatter as a low-power scatter protocol that simultaneously provides backscatter modulation and passive beamforming by smart input distribution design.
 	Starting from scattering principles, we showed how RIScatter nodes generalize information nodes of \gls{bc} and reflect elements of \gls{ris} as special cases, how they can be built over existing passive scatter devices, and how they simultaneously encode self information and assist legacy transmission.
-	We also propose a practical \gls{sic}-free receiver that exploits the properties of active-passive coexisting networks to guarantee primary benefit and improve backscatter throughput.
+	We also propose a practical \gls{sic}-free receiver that exploits the properties of active-passive coexisting networks to maintain primary benefit and improve backscatter throughput.
 	The achievable primary-total-backscatter rate region is then studied for a single-user multi-node RIScatter system, where the input distribution, active beamforming, and decision thresholds are iteratively updated.
@@
 	% \begin{subsection}{Proof of Proposition \ref{pr:threshold}}
-	% 	Since $L$ input letters are with non-zero probability and $x \to z \to \hat{x}$ formulates a Markov chain, we need $L$ non-empty decision regions and at least $L+1$ distinct thresholds (including \num{0} and $\infty$) to minimize the distortion between source and decision.
+	% 	Since $L$ input letters are with non-zero probability and $x \to z \to \hat{x}$ formulates a Markov chain, we need $L$ non-empty decision regions and at least $L+1$ distinct thresholds (including {0} and $\infty$) to minimize the distortion between source and decision.
 	% 	On the other hand, the optimal decision regions are apparently empty for those unused letters.

### 2023-03-01 assets/illustration/time_structure.tex
:triangular_flag_on_post: JSAC 230301

@@
 	\foreach \x in {0,...,7}{
-			\draw[teal,fill=teal!25!white,postaction={pattern=north west lines},pattern color=.] (0.5*\x,3) rectangle ++(0.5,0.25);
+			\draw[teal,fill=teal!35!white,postaction={pattern=north west lines},pattern color=.] (0.5*\x,3) rectangle ++(0.5,0.25);
 		}
 	\foreach \x in {8,...,15}{
-			\draw[teal,fill=teal!25!white,postaction={pattern=north east lines},pattern color=.] (0.5*\x,3) rectangle ++(0.5,0.25);
+			\draw[teal,fill=teal!35!white,postaction={pattern=north east lines},pattern color=.] (0.5*\x,3) rectangle ++(0.5,0.25);
 		}
@@
 	\foreach \x in {0,...,15}{
-			\draw[red,fill=red!25!white,postaction={pattern=north east lines},pattern color=.] (0.5*\x,2) rectangle ++(0.5,0.25);
+			\draw[red,fill=red!35!white,postaction={pattern=north east lines},pattern color=.] (0.5*\x,2) rectangle ++(0.5,0.25);
 		}
@@
 	\foreach \x in {0,...,3}{
-			\draw[brown,fill=brown!25!white,postaction={pattern=north west lines},pattern color=.] (0.5*\x,1) rectangle ++(0.5,0.25);
+			\draw[brown,fill=brown!35!white,postaction={pattern=north west lines},pattern color=.] (0.5*\x,1) rectangle ++(0.5,0.25);
 		}
 	\foreach \x in {4,...,15}{
-			\draw[brown,fill=brown!25!white,postaction={pattern=north east lines},pattern color=.] (0.5*\x,1) rectangle ++(0.5,0.25);
+			\draw[brown,fill=brown!35!white,postaction={pattern=north east lines},pattern color=.] (0.5*\x,1) rectangle ++(0.5,0.25);
 		}

### 2023-03-01 main.tex
:triangular_flag_on_post: JSAC 230301

@@
 		\item Backscatter signal strength is much weaker than primary due to the \emph{double fading} effect;
-		\item The spreading factor (i.e., backscatter symbol duration over primary) is usually large\footnote{The load-switching interval of low-power backscatter modulators is usually \num{0.1} to \qty{10}{\us} \cite{Torres2021}, accounting for a typical spreading factor between \num{10} and \num{e3}.}.
+		\item The spreading factor (i.e., backscatter symbol duration over primary) is usually large\footnote{The load-switching interval of low-power backscatter modulators is usually \num{0.1} to \SI{10}{\us} \cite{Torres2021}, accounting for a typical spreading factor between \num{10} and \num{e3}.}.
 	\end{enumerate}
@@
 	\end{equation}
-	where $d$ is the transmission distance, $L_0=-\qty{30}{\dB}$ is the reference path loss at $d_0=\qty{1}{\meter}$, $\kappa$ is the Rician K-factor, $\bar{\boldsymbol{H}}$ is the deterministic line-of-sight component with unit-magnitude entries, and $\tilde{\boldsymbol{H}}$ is the Rayleigh fading component with standard \gls{iid} \gls{cscg} entries.
+	where $d$ is the transmission distance, $L_0=-\SI{30}{\dB}$ is the reference path loss at $d_0=\SI{1}{\meter}$, $\kappa$ is the Rician K-factor, $\bar{\boldsymbol{H}}$ is the deterministic line-of-sight component with unit-magnitude entries, and $\tilde{\boldsymbol{H}}$ is the Rayleigh fading component with standard \gls{iid} \gls{cscg} entries.
 	We choose $\gamma_{\text{D}}=2.6$, $\gamma_{\text{F}}=2.4$, $\gamma_{\text{B}}=2$, and $\kappa_{\text{D}}=\kappa_{\text{F}}=\kappa_{\text{B}}=5$ for direct, forward and backward links.
 	The finite decision threshold domain $\mathcal{T}$ is obtained by $b$-bit uniform discretization over the critical interval defined by the confidence bounds of edge hypotheses (i.e., lower bound of $\mathcal{H}_1$ and upper bound of $\mathcal{H}_L$) with confidence $1-\varepsilon$.
-	We choose $b=9$ and $\varepsilon=\num{e-3}$.
+	We set $b=9$ and $\varepsilon=\num{e-3}$.
 	All achievable rate points/regions are averaged over \num{e3} channel realizations.
@@
 			}
-			\caption{Typical achievable rate region/points of scattering applications for $Q=1$, $K=1$, $M=4$, $N=e3$, $\sigma_v^2=\qty{-40}{\dBm}$ and $r=\qty{2}{\meter}$.}
+			\caption{Typical achievable rate region/points of scattering applications for $Q=1$, $K=1$, $M=4$, $N=\num{e3}$, $\sigma_v^2=\SI{-40}{\dBm}$ and $r=\SI{2}{\meter}$.}
 			\label{fg:region_comparison}
@@
 			We notice increasing the reflection states has a marginal effect on both primary and total backscatter rates.
-			This is because once the scope of reflection coefficient is determined, using denser constellation points may not create enough phase resolution and energy diversity for primary and backscatter links.
-			Due to the maximum amplitude normalization in \eqref{eq:backscatter_modulation}, the average rate region of \num{8}-\gls{qam} (points on rectangle border) is smaller than that of \num{4}-\gls{qam} (points on square vertices), and the inner constellation points with smaller amplitudes are less frequently used.
+			This is because once the scope of reflection coefficient is determined, using denser constellation points only creates marginal phase resolution and energy diversity for primary and backscatter links.
+			Due to the maximum amplitude normalization in \eqref{eq:backscatter_modulation}, the average rate region of \num{8}-\gls{qam} (points on rectangle border) is smaller than that of \num{4}-\gls{qam} (points on square vertices), and the \num{4} points on the rectangle edges are less frequently used.
 			On the other hand, \num{16}-\gls{qam} provides significant higher backscatter rate benefit than primary.
@@
 			On the other hand, when $N$ is too small, the equivalent \gls{dmmac} \eqref{eq:dmmac} has very high error probabilities and the energy detection is thus unreliable.
-			It explains the observation that $N=10$ provides lower backscatter achievable rate than $N=20$.
+			It explains the observation that $N=10$ provides lower backscatter throughput than $N=20$.
 			Therefore, we conclude the design of spreading factor $N$ in RIScatter systems should accommodate multiple factors (e.g., data rate requirements, load switching constraints at the nodes, and signal processing capability at the user).

### 2023-03-10 arxiv.tex
:construction: Add keywords

@@
 \begin{IEEEkeywords}
-	Input distribution design, symbol-level precoding, active-passive coexisting network, \gls{sic}-free receiver, energy detection, backscatter communication, reconfigurable intelligent surface, ambient backscatter communication, symbiotic radio.
+	Input distribution design, symbol-level precoding, index modulation, active-passive coexisting network, \gls{sic}-free receiver, energy detection, backscatter communication, reconfigurable intelligent surface, ambient backscatter communication, symbiotic radio.
 \end{IEEEkeywords}

### 2023-03-10 jsac.tex
:construction: Add keywords

--- 2023-02-02 jsac.tex
@@
 \usepackage{mathtools}
+% \usepackage{microtype}
 \usepackage[short]{optidef}
@@
 % page limit hacks
-% \usepackage[top=1cm, bottom=1cm, left=1cm, right=1cm]{geometry}
-\abovedisplayskip=1mm
-\belowdisplayskip=1mm
-\abovedisplayshortskip=1mm
-\belowdisplayshortskip=1mm
+% ! \usepackage[top=1cm, bottom=1cm, left=1cm, right=1cm]{geometry}
+% \abovedisplayskip=1mm
+% \belowdisplayskip=1mm
+% \abovedisplayshortskip=1mm
+% \belowdisplayshortskip=1mm
 \setlength{\jot}{0.1mm}
@@
 \setlength{\intextsep}{1mm}
-\setlength{\skip\footins}{1mm}
-\theoremstyle{remark}
-
+\setlength{\skip\footins}{2mm}
 % dark mode
@@
 \newacronym{dmtc}{DMTC}{Discrete Memoryless Thresholding Channel}
-\newacronym{dmtmac}{DMTMAC}{Discrete Memoryless Thresholding Multiple Access Channel}
+\newacronym{dmmac}{DMMAC}{Discrete Memoryless Multiple Access Channel}
+\newacronym{dcmc}{DCMC}{Discrete-input Continuous-output Memoryless Channel}
 \newacronym{dp}{DP}{Dynamic Programming}
@@
 	\gls{ris} adapts its phase shift response to enhance or attenuate channel strength in specific directions.
-	In this paper, we show how those two seemingly different technologies (and their derivatives) can be unified to leverage their benefits simultaneously into a single architecture called RIScatter.
-	RIScatter consists of multiple dispersed or co-located scatter nodes, whose reflection states can be adapted to partially engineer the wireless channel of the existing link and partially modulate their own information onto the scattered wave.
-	This contrasts with \gls{bc} (resp. \gls{ris}) where the reflection pattern is exclusively a function of the information symbol (resp. \gls{csi}).
-	The key principle in RIScatter is to render the probability distribution of reflection states (i.e., backscatter channel input) as a joint function of the information source, \gls{csi}, and \gls{qos} of the coexisting active primary and passive backscatter links.
-	This enables RIScatter to softly bridge, generalize, and outperform \gls{bc} and \gls{ris}; boil down to either under specific input distribution; or evolve in a mixed form for heterogeneous traffic control and universal hardware design.
-	For a single-user multi-node RIScatter network, we characterize the achievable primary-(total-)backscatter rate region by optimizing the input distribution at the nodes, the active beamforming at the \gls{ap}, and the backscatter detection regions at the user.
-	Simulation results demonstrate RIScatter nodes can exploit the additional propagation paths to smoothly transition between backscatter modulation and passive beamforming, and the proposed practical receiver accommodates the double fading, double modulation, and symbol period difference of active-passive coexisting networks without \gls{sic}.
+	In this paper, we show how those two seemingly different technologies (and their derivatives) can be unified into a single architecture called RIScatter.
+	RIScatter consists of multiple dispersed or co-located scatter nodes, whose reflection states are adapted to partially modulate their own information and partially engineer the wireless channel.
+	% This contrasts with \gls{bc} (resp. \gls{ris}) where the reflection pattern is exclusively a function of the information symbol (resp. \gls{csi}).
+	The key principle is to render the probability distribution of reflection states as a joint function of the information source, \gls{csi}, and \gls{qos} of coexisting active primary and passive backscatter links.
+	This enables RIScatter to softly bridge \gls{bc} and \gls{ris}; boil down to either under specific input distribution; or evolve in a mixed form for heterogeneous traffic control and universal hardware design.
+	% To accommodate the characteristics of active-passive coexisting networks, we propose a practical \gls{sic}-free receiver
+	To reap the benefits of RIScatter, we also propose a co-located \gls{sic}-free receiver that semi-coherently decodes the backscatter information, recovers the reflection pattern, and coherently decodes the primary link.
+	For a single-user multi-node RIScatter network, we characterize the achievable primary-(total-)backscatter rate region by designing the input distribution at scatter nodes, the active beamforming at the \gls{ap}, and the energy decision regions at the user.
+	Simulation results demonstrate RIScatter nodes can exploit the scattered paths to smoothly shift between backscatter modulation and passive beamforming.
 \end{abstract}
@@
 \begin{IEEEkeywords}
-	Backscatter communication, reconfigurable intelligent surface, ambient backscatter communication, symbiotic radio.
+	Input distribution design, symbol-level precoding, index modulation, active-passive coexisting network, \gls{sic}-free receiver, energy detection, backscatter communication, reconfigurable intelligent surface, ambient backscatter communication, symbiotic radio.
 \end{IEEEkeywords}
@@
 	% \begin{subsection}{Fundamentals}
-	\IEEEPARstart{F}{uture} wireless network is envisioned to provide high throughput, uniform coverage, pervasive connectivity, heterogeneous control, and cognitive intelligence for trillions of portable devices.
-	As a mature low-power communication technique, \gls{bc} separates a conventional transmitter into a \gls{rf} carrier emitter with power-hungry elements (e.g., synthesizer and amplifier) and an information-bearing node with power-efficient components (e.g., harvester and modulator) \cite{Boyer2014}.
-	In particular, the node harvests energy from impinging wave and embeds information over scattered signal, and the backscatter reader can be either co-located or separated with the carrier emitter, known as \gls{mbc} in Fig.~\subref*{fg:mbc} and \gls{bbc} in Fig.~\subref*{fg:bbc}.
-	Relevant applications such as \gls{rfid} \cite{Dobkin2012,Landt2005} and passive sensor network \cite{Vannucci2008,Assimonis2016} have been extensively researched, standardized, and commercialized in the era of \gls{ioe}.
-	However, conventional \gls{bc} nodes only respond when externally inquired by a nearby reader.
-	To tackle this, \cite{Liu2013b} proposed \gls{ambc} where battery-free nodes recycle ambient signals (e.g., radio, television and Wi-Fi) to harvest energy and establish connection in between.
-	As shown in Fig.~\subref*{fg:ambc}, it eliminates the need of dedicated power supply, carrier emitter and frequency spectrum for \gls{bc}, but the decoding is subject to a strong interference from the primary (legacy) link.
-	Cooperative \gls{ambc} was then proposed where a co-located receiver decodes both active primary and passive backscatter links, and the rate and error performance are evaluated for various detection schemes \cite{Yang2018}.
-	The concept was further refined by \cite{Liang2020} as \gls{sr} in Fig.~\subref*{fg:sr} that cognitively incorporates \gls{ambc} with existing systems.
-	In a \gls{sr} system, the active transmitter generates \gls{rf} wave carrying primary information, the passive node creates additional propagation path and ride its information over scattered signal, while the cooperative receiver jointly, individually, or sequentially decodes both links.
-	Those \gls{bc} applications\footnote{In this paper, \gls{bc} refers to \gls{mbc}, \gls{bbc}, \gls{ambc} and \gls{sr}.} employ scatter nodes as pure information sources, and the active primary transmission (if it exists) can be influenced by the randomness of backscatter modulation.
-	On the other hand, \gls{ris} in Fig.~\subref*{fg:ris} is a smart planar signal reflector that consists of numerous compact passive elements with adjustable amplitude and phase responses, whose reflection pattern over time is deterministic and adaptively optimized based on \gls{csi}.
-	\gls{ris} smartly reflects the surrounding \gls{rf} waves to customize the wireless propagation environment for signal enhancement, interference suppression, scattering enrichment and non-line-of-sight bypassing \cite{Wu2021b}.
-	In summary, \gls{mbc}/\gls{bbc} (resp.
+	\IEEEPARstart{F}{uture} wireless network is envisioned to provide high throughput, uniform coverage, pervasive connectivity, heterogeneous control, and cognitive intelligence for trillions of low-power devices.
+	% As a mature low-power communication technique,
+	\gls{bc} separates a transmitter into a \gls{rf} carrier emitter with power-hungry elements (e.g., synthesizer and amplifier) and an information-bearing node with power-efficient components (e.g., harvester and modulator) \cite{Boyer2014}.
+	% In particular, the node harvests energy from impinging wave and embeds information over scattered signal, and
+	The receiver (reader) can be either co-located or separated with the carrier emitter, known as \gls{mbc} and \gls{bbc} in Fig.~\subref*{fg:mbc} and \subref*{fg:bbc}, respectively.
+	Relevant applications such as \gls{rfid} \cite{Dobkin2012,Landt2005} and passive sensor network \cite{Vannucci2008,Assimonis2016} have been extensively researched, standardized, and commercialized to embrace the \gls{ioe}.
+	However, conventional backscatter nodes only respond when externally inquired by a nearby reader.
+	% To tackle this, \cite{Liu2013b} proposed \gls{ambc} where battery-free nodes recycle ambient signals (e.g., radio, television and Wi-Fi) to harvest energy and establish connection in between.
+	\gls{ambc} in Fig.~\subref*{fg:ambc} was proposed a decade ago where battery-free nodes recycle ambient signals (e.g., radio, television and Wi-Fi) to harvest energy and establish connections \cite{Liu2013b}.
+	It does not require dedicated power source, carrier emitter, or frequency spectrum, but the backscatter decoding is subject to the strong interference from the primary (legacy) link.
+	% Cooperative \gls{ambc} that employs a co-located receiver to decode both coexisting links was considered in \cite{Yang2018}, and the rate and error performance are evaluated for various detection schemes.
+	To tackle this, cooperative \gls{ambc} \cite{Yang2018} employs a co-located receiver to decode both coexisting links and the concept was further refined as \gls{sr} in Fig.~\subref*{fg:sr} \cite{Liang2020}.
+	% Specifically, the active transmitter generates \gls{rf} wave carrying primary information, the passive node ride extra information over the scattered signal, and the cooperative receiver jointly, individually, or sequentially decodes both links.
+	Specifically, the active transmitter generates \gls{rf} wave carrying primary information, the passive node creates a rich-scattering environment and rides its own information, and the co-located receiver cooperatively decodes both links.
+	In those \gls{bc} applications, the scatter node is considered as an \emph{information source} and the reflection pattern depends exclusively on the information symbol.
+	% Those \gls{bc} applications employ scatter nodes as pure information sources, and the active primary transmission (if it exists) can be influenced by the randomness of backscatter modulation.
+	On the other hand, \gls{ris} in Fig.~\subref*{fg:ris} is a smart signal reflector with numerous passive elements of adjustable phase shifts.
+	It customizes the wireless environment for signal enhancement, interference suppression, scattering enrichment, and/or non-line-of-sight bypassing \cite{Wu2021b}.
+	Each \gls{ris} element is considered as a \emph{channel adaptor} and the reflection pattern depends exclusively on the \gls{csi}.
+	% In summary, \gls{mbc}/\gls{bbc} (resp.
 \gls{ris}) involves a \emph{single} passive backscatter (resp.
@@
 modulated signal).
-	On the other hand, \gls{ambc} (resp. \gls{sr}) involves \emph{coexisting} active primary and passive backscatter links in a competitive (resp. collaborative) relationship.
-	In \gls{ambc}, the backscatter link only needs to know the basic information (e.g., operating frequency) of the primary link, while the primary link may be completely unaware of the backscatter link.
-	In \gls{sr}, relevant \gls{csi} is exploited at the co-located receiver for cooperative decoding, and may also be exploited at the primary transmitter for cooperative active beamforming.
-	A comparison of scattering applications is summarized in Table~\ref{tb:scattering_applications}.
+	% On the other hand, \gls{ambc} (resp. \gls{sr}) involves \emph{coexisting} active primary and passive backscatter links in a competitive (resp. collaborative) relationship.
+	% In \gls{ambc}, the backscatter link only needs to know the basic information (e.g., operating frequency) of the primary link, while the primary link may be completely unaware of the backscatter link.
+	% In \gls{sr}, relevant \gls{csi} is exploited at the co-located receiver for cooperative decoding, and may also be exploited at the primary transmitter for cooperative active beamforming.
 
@@
 			Illustration of scattering applications.
-			For each, the blue flow(s) constitute the active primary link while the magenta/green flow denotes the passive backscatter link.
+			The blue flow(s) constitutes the primary link while the magenta/green flow denotes the backscatter link.
 		}
@@
 	% \begin{subsection}{Related Works}
-	Similar to \gls{cr}, active-passive coexisting networks can be classified into commensal, parasitic, and competitive relationships, whose instantaneous rates, power schemes, and outage probabilities were acquired in \cite{Guo2019b,Ding2020}.
-	% To evaluate the performance of cooperative receivers, \cite{Yang2018} derived the bit error rates of \gls{ml}, linear and \gls{sic} detectors for flat fading channels, and proposed a low-complexity detector for frequency-selective fading channels.
-	% However, it only considered the case where the primary and backscatter symbols of the same period are perfectly aligned in time.
-	Joint \gls{ml} decoding provides the best error performance but requires prohibitive computational complexity especially for high-order modulations \cite{Yang2018}.
-	Indeed, active-passive coexisting networks have three special and important properties:
-	1) primary and backscatter symbols are superimposed by \emph{double modulation} (i.e., multiplication coding);
-	2) backscatter signal strength is much weaker than primary due to the \emph{double fading} effect;
-	3) backscatter \emph{symbol period} is longer than primary due to the load switching constraint.
-	% ! double modulation, double fading, symbol period difference
+	As a special case of \gls{cr}, active and passive transmissions coexist and interplay in \gls{ambc} and \gls{sr}.
+	Such a coexistence is classified into commensal (overlay), parasitic (underlay), and competitive (interfering) paradigms, and their achievable rate and outage performance were investigated in \cite{Guo2019b,Ding2020}.
+	For the co-located cooperative receiver, the \gls{ber} performance of \gls{ml}, linear, and \gls{sic} detectors are derived over flat fading channels \cite{Yang2018}.
+	However, the work assumed equal symbol duration and perfect synchronization for primary and backscatter links.
+	Importantly, active-passive coexisting networks have three special and important properties:
+	\begin{enumerate}
+		\item Primary and backscatter symbols are superimposed by \emph{double modulation} (i.e., multiplication coding);
+		\item Backscatter signal strength is much weaker than primary due to the \emph{double fading} effect;
+		\item The spreading factor (i.e., backscatter symbol duration over primary) is usually large\footnote{The load-switching interval of low-power backscatter modulators is usually \num{0.1} to \SI{10}{\us} \cite{Torres2021}, accounting for a typical spreading factor between \num{10} and \num{e3}.}.
+	\end{enumerate}
 	The second property motivated \cite{Long2020a,Liang2020,Guo2019b,Ding2020,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Yang2018,Han2021,Zhang2022} to view \gls{sr} as a multiplicative \gls{noma} and perform \gls{sic} from primary to backscatter link.
-	During primary decoding, the randomness of backscatter modulation can be modelled as either channel uncertainty or multiplicative interference, when the spreading factor (i.e., backscatter-over-primary symbol period ratio) $N$ is large or small, respectively\footnote{For state-of-the-art low-power \gls{rfid} tags, the load-switching speed usually varies between \num{100}s of \unit{\kHz} to \num{10}s of \unit{\MHz} \cite{Torres2021}, corresponding to a typical spreading factor between \num{10} and \num{1000}.}.
-	Such a \gls{sic} receiver is operation-intensive and \gls{csi}-sensitive because it involves $N$ re-encoding, precoding, subtraction together with a time-domain \gls{mrc} to decode each backscatter symbol.
-	When the spreading factor is sufficiently large (i.e., commensal \gls{sr}), the average primary achievable rate under semi-coherent detection\footnote{In this paper, semi-coherent detection refers to the primary/backscatter decoding based on known \gls{csi} and unknown backscatter/primary symbols.} asymptotically approaches its coherent counterpart, and both links may be decoded in an interference-free manner \cite{Long2020a}.
-	On the other hand, efficient backscatter multiple access design remains an open issue for \gls{bc}.
-	\cite{Xu2021a} proposed a \gls{noma}-based \gls{sr} where the \gls{sic} order depends on the backscatter channel strength, but the performance deteriorates fast as the number of nodes increases.
-	\gls{tdma}-based \gls{sr} was also considered in \cite{Yang2021a} where each node transmits information during its dedicated slot and harvests energy otherwise.
-	It enables adaptive transmission time and reflection ratio design but introduces extra coordination cost.
-	\cite{Vougioukas2019} modifies the load-switching speed to shift the scattered signal to the desired frequency band.
-	This enables backscatter \gls{fdma} at the cost of larger bandwidth and higher power consumption at the scatter nodes.
-	To reduce the coordination cost, \cite{Han2021} proposed a random code-assisted multiple access for \gls{sr} and evaluated the asymptotic \gls{sinr} using random matrix theory.
-	This code-domain solution suffers from the near-far problem and imperfect synchronization, both being severe in \gls{bc}.
-
-	Conventional \gls{ris} design with fixed reflection coefficients during each channel block has been extensively studied in communication, sensing, and power literatures \cite{Wu2018,Zhang2019a,Lin2022,Liu2022,Feng2022,Zhao2022}.
-	On the other hand, dynamic \gls{ris} with independent reflection patterns in different time slots has gained recent attentions in multi-user and multi-purpose wireless networks.
-	The concept was first proposed in \cite{Yang2020} to fine-tune the \gls{ofdm} resource blocks, then extended to the downlink power and uplink information phases of \gls{wpcn} \cite{Wu2021,Wu2021d,Hua2022a}.
-	It introduces artificial channel diversity and enables flexible resource allocation, but misses the opportunity to encode its own message.
-	\gls{ris} can also be used as a transmitter when placed in the near field of a carrier emitter, and prototypes have been implemented for \gls{psk} \cite{Tang2019a} and \gls{qam} \cite{Dai2020a}.
-	From an information-theoretic perspective, \cite{Karasik2020} reported that using \gls{ris} as a naive passive beamformer to maximize the receive \gls{snr} is generally rate-suboptimal for finite-input constellations.
-	Instead, the capacity of \gls{ris}-aided channel is achieved by joint transmitter-\gls{ris} encoding, and even layered encoding with pilots can outperform passive beamforming at high \gls{snr}.
-	It inspired \gls{ris}-empowered \gls{bc} \cite{Liu2019d,Bereyhi2020,Xu2020b,Zhang2021d,Hu2021b,Hua2022,Basar2020,Ma2020a,Yuan2021,Hu2021a} to combine passive beamforming and backscatter modulation in the overall reflection pattern.
+	During primary decoding, the backscatter signal can be modelled as channel uncertainty or multiplicative interference when the spreading factor is large or small, respectively.
+	Decoding each backscatter symbol also requires multiple \gls{sic} followed by a \gls{mrc} and is operation-intensive and \gls{csi}-sensitive.
+	% Such a \gls{sic} receiver is operation-intensive and \gls{csi}-sensitive because it involves $N$ re-encoding, precoding, subtraction together with a time-domain \gls{mrc} to decode each backscatter symbol.
+	When the spreading factor is sufficiently large, the primary achievable rate under semi-coherent detection\footnote{In this paper, semi-coherent detection refers to the primary/backscatter decoding with known \gls{csi} and unknown backscatter/primary symbols.} asymptotically approaches its coherent counterpart and both links are decoded interference-free \cite{Long2020a}.
+	% However, it significantly increases \gls{sic} operations per backscatter symbol and severely limits the backscatter \emph{throughput}.
+	However, this severely limits the backscatter throughput and requires numerous \gls{sic} per backscatter symbol.
+
+	% On the other hand, efficient backscatter multiple access design remains an open issue for \gls{bc}.
+	% \cite{Xu2021a} proposed a \gls{noma}-based \gls{sr} where the \gls{sic} order depends on the backscatter channel strength, but the performance deteriorates fast as the number of nodes increases.
+	% \gls{tdma}-based \gls{sr} was also considered in \cite{Yang2021a} where each node transmits information during its dedicated slot and harvests energy otherwise.
+	% It enables adaptive transmission time and reflection ratio design but introduces extra coordination cost.
+	% \cite{Vougioukas2019} modifies the load-switching speed to shift the scattered signal to the desired frequency band.
+	% This enables backscatter \gls{fdma} at the cost of larger bandwidth and higher power consumption at the scatter nodes.
+	% To reduce the coordination cost, \cite{Han2021} proposed a random code-assisted multiple access for \gls{sr} and evaluated the asymptotic \gls{sinr} using random matrix theory.
+	% This code-domain solution suffers from the near-far problem and imperfect synchronization, both being severe in \gls{bc}.
+
+	% A comparison of scattering applications is summarized in Table~\ref{tb:scattering_applications}.
+
+	On the other hand, static \gls{ris} design with fixed reflection pattern per channel block has been extensively studied in wireless communication, sensing, and power literature \cite{Wu2018,Zhang2019a,Lin2022,Liu2022,Feng2022,Zhao2022}.
+	Dynamic \gls{ris} performs time sharing between different phase shifts and introduces artificial channel diversity within each channel block.
+	It was first proposed to fine-tune the \gls{ofdm} resource blocks \cite{Yang2020} then extended to the downlink power and uplink information phases of \gls{wpcn} \cite{Wu2021,Wu2021d,Hua2022a}.
+	However, dynamic \gls{ris} carries \emph{no} additional information since the reflection state at each time slot is known to the receiver.
+	\gls{ris} can also be used as an information source and prototypes have been developed for \gls{psk} \cite{Tang2019a} and \gls{qam} \cite{Dai2020a}.
+	From an information-theoretic perspective, the authors of \cite{Karasik2020} reported that joint transmitter-\gls{ris} encoding achieves the capacity of \gls{ris}-aided finite-input channel and using \gls{ris} as a naive passive beamformer to maximize the receive \gls{snr} is generally suboptimal.
+	This inspired \gls{ris}-empowered \gls{bc} \cite{Liu2019d,Bereyhi2020,Xu2020b,Zhang2021d,Hu2021b,Hua2022,Basar2020,Ma2020a,Yuan2021,Hu2021a} to combine passive beamforming and backscatter modulation in the overall reflection pattern.
 	In particular, \emph{symbol level precoding} maps the information symbols to the optimized \gls{ris} coefficient sets \cite{Liu2019d,Bereyhi2020}, \emph{overlay modulation} superposes the information symbols over a common auxiliary matrix \cite{Xu2020b,Zhang2021d,Hu2021b,Hua2022}, \emph{spatial modulation} switches between the reflection coefficient sets that maximize \gls{snr} at different receive antennas \cite{Basar2020,Ma2020a,Yuan2021}, and \emph{index modulation} employs dedicated reflection elements (resp.
@@
 	However, those joint designs incur advanced hardware architecture and high optimization complexity.
-	Relevant literatures also consider either \emph{Gaussian} codebook \cite{Guo2019b,Ding2020,Long2020a,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Hu2021b} that is impractical for low-power nodes, or finite \emph{equiprobable} inputs \cite{Yang2018,Liang2020,Han2021,Zhang2022,Liu2019d,Bereyhi2020,Xu2020b,Zhang2021d,Hua2022,Basar2020,Ma2020a,Yuan2021,Hu2021a} that does not fully exploit the \gls{csi} and signal properties of active-passive coexisting networks.
+	Relevant literature also considers either Gaussian codebook \cite{Guo2019b,Ding2020,Long2020a,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Hu2021b} that is impractical for low-power nodes or finite equiprobable inputs \cite{Yang2018,Liang2020,Han2021,Zhang2022,Liu2019d,Bereyhi2020,Xu2020b,Zhang2021d,Hua2022,Basar2020,Ma2020a,Yuan2021,Hu2021a} that does not fully exploit the \gls{csi} and properties of active-passive coexisting networks.
 	% \end{subsection}
+	Those problems are addressed in this paper and the contributions are summarized below.
 
 	% \begin{subsection}{Contributions}
-	\emph{First,} we propose RIScatter as a novel scatter protocol that unifies \gls{bc} and \gls{ris} by adaptive reflection state (i.e., backscatter input) distribution design.
-	As shown in Fig.~\subref*{fg:riscatter}, one or more passive RIScatter nodes ride over an active transmission and smartly scatters the incident wave to simultaneously engineer the primary channel and modulate its own information, while a co-located receiver cooperatively decodes both coexisting links.
-	The reflection pattern over time is neither fully random like \gls{bc} nor fully deterministic like \gls{ris}, but semi-randomly chosen with the guidance of reflection state distribution, whose design accommodates the impact of information source, \gls{csi}, and \gls{qos} of both links.
-	Such an adaptive backscatter channel coding boils down to the degenerate distribution of \gls{ris} when the primary link is prioritized, and outperforms the uniform distribution of line-coded \gls{bc} (by accounting the \gls{csi}) when the backscatter link is prioritized.
-	Besides, when multiple RIScatter nodes are co-located, joint encoding can further increase the total backscatter rate.
-	RIScatter exploits the transmitter-scatter-receiver path for simultaneous backscatter modulation and dynamic passive beamforming, and can smoothly transition in between under different \gls{qos}.
-	However, such a novel scatter protocol encounters two major challenges, namely the cooperative receiver design and the adaptive backscatter input distribution design.
-	This is the first paper to unify \gls{bc} and \gls{ris} from the perspective of reflection state distribution.
-
-	\emph{Second,} we address the first challenge by proposing a practical receiver that accommodates the double fading, double modulation, and symbol period difference of active-passive coexisting networks.
-	Since joint decoding involves high complexity while individual decoding can be inefficient (neither cooperative nor exploiting signal properties), most relevant literatures consider a sequential primary-backscatter decoding based on \gls{sic}.
-	Specifically, the decoding of each backscatter symbol requires $N$ re-encoding, precoding, subtraction together with a time-domain \gls{mrc}, which can be operation-intensive and \gls{csi}-sensitive.
-	In contrast, the proposed RIScatter receiver semi-coherently decodes the backscatter symbol from the accumulated receive energy, re-encodes to recover the exact reflection pattern, and combine it with relevant \gls{csi} to determine the transmitter-scatter-receiver path response.
-	Thanks to the double modulation and symbol period difference, the backscatter symbol can be modelled within primary channel (similar to \gls{ris}) rather than being re-precoded and cancelled, and the semi-coherent energy-based backscatter detection indeed becomes part of primary channel training.
-	The strategy is suitable for arbitrary primary sampling rate and backscatter load-switching speed (i.e., arbitrary spreading factor).
-	This is the first paper to consider such a sequential backscatter-primary decoding and treat semi-coherent backscatter detection as part of primary channel training.
-
-	\emph{Third,} we address the second challenge by considering a specific scenario where multiple co-located/dispersed RIScatter nodes ride over an active point-to-point \gls{miso} transmission to perform backscatter modulation and dynamic passive beamforming towards a nearby user.
-	For a given \gls{qos}, we first express the primary and total backscatter rates as functions of \emph{input distribution} at RIScatter nodes, \emph{active beamforming} at the \gls{ap}, and \emph{backscatter decision regions} at the user.
-	Then, we characterize the achievable rate region by optimizing those variables under different \gls{qos}.
-	Since the original problem is highly non-convex, we propose a suboptimal \gls{bcd} algorithm where the \gls{kkt} input distribution is numerically evaluated by limit of sequences, the active beamforming is iteratively updated by \gls{pgd} accelerated by \gls{bls}, and the decision regions are refined by existing sequential quantization methods for \gls{dmtc}.
-	Uniquely, we account for \gls{csi}, \gls{qos}, and backscatter constellation in those optimizations, and the proposed backscatter input distribution design is applicable to more general scenarios.
+	\emph{First,} we propose RIScatter as a novel protocol that unifies \gls{bc} and \gls{ris} by adaptive reflection state (backscatter input) distribution design.
+	% \emph{First,} we propose RIScatter as a novel scatter protocol that simultaneously modulates the node information and engineers the wireless channel via adaptive reflection state (backscatter input) distribution design.
+	The concept is shown in Fig.~\subref*{fg:riscatter} where one or more RIScatter nodes ride over an active transmission and simultaneously modulate their information and engineer the wireless channel.
+	A co-located receiver cooperatively decodes both coexisting links and each reflection state simultaneously acts as information and passive beamforming codewords.
+	The reflection pattern of each node is semi-randomly chosen with the guidance of input distribution as a joint function of the information source, \gls{csi}, and \gls{qos}.
+	Such an adaptive channel coding boils down to the degenerate distribution of \gls{ris} when the primary link is prioritized, and outperforms the uniform distribution of \gls{bc} (by accounting the \gls{csi}) when the backscatter link is prioritized.
+	Joint and independent encoding are available when multiple RIScatter nodes are co-located and dispersed, respectively.
+	Table~\ref{tb:scattering_applications} compares RIScatter to \gls{bc} and \gls{ris}.
+	However, two major challenges for RIScatter are the practical receiver and input distribution design.
+	This is the first paper to unify \gls{bc} and \gls{ris} from the perspective of input distribution.
+
+	\emph{Second,} we address the first challenge and propose a practical receiver that semi-coherently decodes the backscatter information, recovers the reflection pattern, and coherently decodes the primary link.
+	We consider backscatter energy detection and formulate a \gls{dmmac} over disjoint decision regions.
+	Thanks to the double modulation and symbol-level passive precoding, the semi-coherent backscatter decoding is essentially part of channel training.
+	Once the backscatter information is successfully decoded, its contribution can be modelled within composite channel as dynamic passive beamforming (rather than re-precoded and cancelled).
+	It requires only one energy comparison and re-encoding per backscatter symbol and is much efficient than conventional decoding based on \gls{sic} and \gls{mrc}.
+	It is also suitable for arbitrary input distribution and spreading factor, which significantly improves backscatter throughput.
+	This is the first paper to consider practical backscatter-primary decoding scheme to exploit backscatter modulation as dynamic passive beamforming at the co-located receiver.
+
+	\emph{Third,} we address the second challenge and consider a single-user multi-node \gls{miso} scenario.
+	We characterize the achievable primary-(total-)backscatter rate region by optimizing the input distribution at RIScatter nodes, the active beamforming at the \gls{ap}, and the energy decision regions at the user under different \gls{qos}.
+	A \gls{bcd} algorithm is proposed where the \gls{kkt} input distribution is numerically evaluated by limit of sequences, the active beamforming is optimized by \gls{pgd}, and the decision regions are refined by existing sequential quantizer for \gls{dmtc}.
+	Uniquely, we consider \gls{csi}, \gls{qos}, and backscatter constellation in the optimization and the input distribution result is applicable to general detection schemes.
 	This is also the first paper to reveal the importance of backscatter input distribution and decision region designs in active-passive coexisting networks.
 
-	\emph{Fourth,} we provide numerical results to demonstrate the benefits of RIScatter and proposed algorithms.
-	The observations include:
-	1) adaptive reflection state distribution design can flexibly transition between backscatter modulation and passive beamforming;
-	2) when the primary link is prioritized, input distribution becomes degenerate and RIScatter nodes coincide with discrete \gls{ris};
-	3) when the backscatter link is prioritized, adaptive RIScatter encoding achieves higher backscatter rate than conventional line-coded \gls{bc} with equiprobable inputs;
-	4) co-located RIScatter nodes can further leverage total backscatter rate by joint encoding;
-	5) the proposed receiver maintains the passive beamforming benefit and provides comparable backscatter rate to \gls{sic}-based \gls{sr}, with re-encoding costs reduced to $1/N$ and no re-precoding/cancellation;
-	6) it also supports scatter nodes with faster load-switching speed for potentially higher throughput;
-	7) \gls{pgd} active beamformer effectively increases the primary (resp.
+	% \emph{Fourth,} we provide numerical results to demonstrate the benefits of RIScatter and proposed algorithms.
+	% The observations include:
+	% 1) adaptive reflection state distribution design can flexibly shift between backscatter modulation and passive beamforming;
+	% 2) when the primary link is prioritized, input distribution becomes degenerate and RIScatter nodes coincide with discrete \gls{ris};
+	% 3) when the backscatter link is prioritized, adaptive RIScatter encoding achieves higher backscatter rate than conventional line-coded \gls{bc} with equiprobable inputs;
+	% 4) co-located RIScatter nodes can further leverage total backscatter rate by joint encoding;
+	% 5) the proposed receiver maintains the passive beamforming benefit and provides comparable backscatter rate to \gls{sic}-based \gls{sr}, with re-encoding costs reduced to $1/N$ and no re-precoding/cancellation;
+	% 6) it also supports scatter nodes with faster load-switching speed for potentially higher throughput;
+	% 7) \gls{pgd} active beamformer effectively increases the primary (resp.
 backscatter) rate by boosting the receive \gls{snr} (resp.
 widening the energy gap under different reflection states), and can smoothly transition in between under different \gls{qos};
-	8) distribution-aware backscatter detectors provide higher backscatter rate than the conventional \gls{ml} detector.
+	% 8) distribution-aware backscatter detectors provide higher backscatter rate than the conventional \gls{ml} detector.
 	% \end{subsection}
@@
 	$\mathrm{card}(\cdot)$ returns the cardinality of a set.
-	$(\cdot)^*$, $(\cdot)^\mathsf{T}$, $(\cdot)^\mathsf{H}$, $\lvert{\cdot}\rvert$, and $\lVert{\cdot}\rVert$ denote the conjugate, transpose, conjugate transpose, absolute value, and Euclidean norm operators, respectively.
+	$\log(\cdot)$ denotes logarithm of base $e$.
+	$(\cdot)^*$, $(\cdot)^\mathsf{T}$, $(\cdot)^\mathsf{H}$, $\lvert{\cdot}\rvert$, and $\lVert{\cdot}\rVert$ denote the conjugate, transpose, conjugate transpose (Hermitian), absolute value, and Euclidean norm operators, respectively.
 	$(\cdot)^{(r)}$ and $(\cdot)^{\star}$ denote the $r$-th iterated and optimal results, respectively.
@@
 
-\begin{section}{Scattering Principles}
-	\gls{rf} wave scattering and reflecting can be described by a unified model and realized by {variable-load antennas} or {programmable metamaterial} \cite{Liang2022}.
-	An antenna-based scatterer usually consists of an integrated antenna, a load-switching modulator, an energy harvester, and on-chip components (e.g., microcontroller and sensors) \cite{Dobkin2012}.
-	It first receives the impinging signals, then reradiates some back to the space and dissipates the remaining.
-	In comparison, a typical metamaterial-based scatterer comprises an outer metamaterial layer of numerous sub-wavelength metallic/dielectric patches (with tunable permittivity/permeability), a middle copper plate layer that avoids leakage, an inner circuit board layer that adjusts patch responses, and an integrated microcontroller/\glsentryshort{fpga} for coordination and control \cite{Wu2020}.
-	Ideally, it reflects the wave at the space-metamaterial boundary without receiving them and mainly applies a phase shift.
-	In practice, both types of scatterers have {finite} reflection states with non-zero reflection loss.
-	The scattered signal can be decomposed into a {structural} mode component that consistently contributes to environment multipath and can be modelled within \gls{csi}, and an \emph{antenna} mode component that depends on the impedance mismatch and can be used for backscatter modulation and/or passive beamforming \cite{Hansen1989}.
-	For an antenna-based (resp. metamaterial-based) scatter node with $M$ reflection states, the reflection coefficient at state $m \in \mathcal{M} \triangleq \{1,\ldots,M\}$ is
+\begin{section}{RIScatter}
+	\begin{subsection}{Principles}
+		\gls{rf} wave scattering/reflecting are often manipulated by passive antennas or programmable metamaterial \cite{Liang2022}.
+		% can be described by a unified signal model and implemented by passive antennas or programmable metamaterial \cite{Liang2022}.
+		% An antenna-based scatterer usually consists of an integrated antenna, a load-switching modulator, an energy harvester, and on-chip components (e.g., microcontroller and sensors) \cite{Dobkin2012}.
+		% An antenna-based scatterer usually consists of an integrated antenna, a load-switching modulator, an energy harvester, and on-chip components (e.g., microcontroller and sensors) \cite{Dobkin2012}.
+		The former first receives the impinging signals then reradiates some back to the space and dissipates the remaining \cite{Dobkin2012}.
+		% In comparison, a typical metamaterial-based scatterer comprises an outer metamaterial layer of numerous sub-wavelength metallic/dielectric patches (with tunable permittivity/permeability), a middle copper plate layer that avoids leakage, an inner circuit board layer that adjusts patch responses, and an integrated microcontroller/\glsentryshort{fpga} for coordination and control \cite{Wu2020}.
+		% In comparison, a typical metamaterial-based scatterer comprises an outer metamaterial layer of numerous sub-wavelength metallic/dielectric patches (with tunable permittivity/permeability), a middle copper plate layer that avoids leakage, an inner circuit board layer that adjusts patch responses, and an integrated microcontroller/\glsentryshort{fpga} for coordination and control \cite{Wu2020}.
+		In contrast, the latter reflects the wave at the space-metamaterial boundary without receiving them and mainly applies a phase shift.
+		% In practice, both types of scatterers have {finite} reflection states with non-zero reflection loss.
+		% In general, the scattered signal consists of a structural mode component that consistently contributes to environment multipath and can be modelled within \gls{csi}, and an \emph{antenna} mode component that depends on the impedance mismatch and can be used for backscatter modulation and/or passive beamforming \cite{Hansen1989}.
+		The scattered signal consists of a structural mode component that consistently contributes to environment multipath (usually modelled within \gls{csi}) and an antenna mode component that depends on the impedance mismatch (mainly used for backscatter modulation and/or passive beamforming) \cite{Hansen1989}.
+		% The former is usually modelled within \gls{csi} while the latter is mainly used for backscatter modulation and/or passive beamforming.
+		For an antenna (resp. metamaterial) scatterer with $M$ reflection states, the reflection coefficient at state $m \in \mathcal{M} \triangleq \{1,\ldots,M\}$ is
 		\begin{equation}
@@
 		where $Z_m$ is the antenna load (resp. metamaterial unit) impedance at state $m$ and $Z$ is the antenna input (resp. medium characteristic) impedance.
-	\gls{bc} employ scatter nodes as information sources that \emph{randomly switching} between different states.
+
+		\gls{bc} treats scatterers as information sources that \emph{randomly} choosing the reflection state based on information symbol.
 		For $M$-ary \gls{qam}, constellation point $c_m$ maps to reflection coefficient $\Gamma_m$ by \cite{Thomas2012a}
@@
 		\end{equation}
-	where $\beta_m \in \mathbb{I}$ is the overall amplitude scattering ratio at state $m$.\footnote{Most existing \gls{ris} literatures assume lossless reflection $\beta_m=1$, $\forall m$.}
-\end{section}
-
-\begin{section}{RIScatter}
-	% \begin{subsection}{Concepts}
-	We propose RIScatter in Fig.~\subref*{fg:riscatter} as a generalization of \gls{bc} and \gls{ris}, which involves coexisting active primary and passive backscatter links in a flexible and mutualistic manner.
-	RIScatter nodes leverage \gls{csi}- and \gls{qos}-based reflection state distribution design to smoothly transition between backscatter modulation and passive beamforming.
-	Fig.~\ref{fg:riscatter_node} illustrates the block diagram, equivalent circuit, and scatter model of a RIScatter node.
-	It can be implemented by adding an integrated receiver \cite{Kim2021a} and adaptive encoder \cite{He2020e} to off-the-shelf passive \gls{rfid} tags.
+		where $\beta_m \in \mathbb{I}$ is the overall amplitude scattering ratio at state $m$.\footnote{Most existing \gls{ris} literature assumes lossless reflection $\beta_m=1$, $\forall m$.}
+		% A natural question is, is it possible to use a scatterer
+		For a scatter node with given load impedance set, \gls{bc} employs $\Gamma_m$ only as an information codeword while \gls{ris} employs $\Gamma_m$ only as a passive beamforming codeword.
+		RIScatter generalizes both from a probabilistic perspective where each node \emph{semi-randomly} chooses the reflection state with the guidance of probability $P(\Gamma_m)$.
+		The input distribution is flexibly designed as a joint function of the information source, \gls{csi}, and \gls{qos} of both links.
+		\gls{bc} and (static) \gls{ris} can be regarded as its extreme cases where the input distribution boils down to uniform and degenerate, respectively.
+		Fig.~\ref{fg:scatter_comparison} compares the input distribution and reflection pattern of RIScatter to \gls{bc} and \gls{ris}.
+		\begin{figure}[!t]
+			\centering
+			\subfloat[Input Distribution]{
+				\resizebox{0.44\columnwidth}{!}{
+					\input{assets/illustration/input_distribution.tex}
+				}
+				\label{fg:input_distribution}
+			}
+			\subfloat[Reflection Pattern]{
+				\resizebox{0.48\columnwidth}{!}{
+					\input{assets/illustration/time_structure.tex}
+				}
+				\label{fg:time_structure}
+			}
+			\caption{
+				Input distribution and reflection pattern of scattering applications.
+				``PB'', ``BB'', and ``CB'' refer to primary symbol block, backscatter symbol block, and channel block, respectively.
+				Shadowing means presence of primary link.
+				In this example, the optimal passive beamformer is state \num{2} and its input probability for RIScatter is \num{0.75}.
+				% RIScatter node transmit symbol \num{1}
+				The spreading factor is \num{4} for RIScatter and \num{8} for \gls{ambc}/\gls{sr}.
+			}
+			\label{fg:scatter_comparison}
+		\end{figure}
+		\begin{remark}
+			RIScatter is different from conventional dynamic passive beamforming since the reflection pattern conveys additional information.
+			% There are many ways to order
+			% The latter only involves time sharing between different states but there are many ways to ensure within a channel block.
+			The latter only involves time sharing between different states and the actual order has no impact on the (ergodic) primary performance.
+			For RIScatter, different state combinations correspond to different messages and the impact reduces to dynamic passive beamforming upon successful backscatter decoding.
+			% However, different combinations correspond to different backscatter messages and RIScatter impact is determined dynamic passive beamforming once successfully decoded.
+		\end{remark}
+
+		RIScatter nodes can be implemented, for example, by adding an integrated receiver \cite{Kim2021a} and adaptive encoder \cite{He2020e} to off-the-shelf passive \gls{rfid} tags.
+		The block diagram, equivalent circuit, and scatter model are illustrated in Fig.~\ref{fg:riscatter_node}.
 		\begin{figure*}[!t]
@@
 		\end{figure*}
-	Fig.~\ref{fg:scatter_comparison} compares the reflection state distribution and reflection pattern of RIScatter and other applications.
-	\begin{figure}[!t]
-		\centering
-		\subfloat[Reflection State Distribution]{
-			\resizebox{0.32\columnwidth}{!}{
-				\input{assets/illustration/input_distribution.tex}
-			}
-			\label{fg:input_distribution}
-		}
-		\subfloat[Reflection Pattern]{
-			\resizebox{0.32\columnwidth}{!}{
-				\input{assets/illustration/time_structure.tex}
-			}
-			\label{fg:time_structure}
-		}
-		\caption{
-			Reflection state distribution and reflection pattern over time of scattering applications.
-			``PB'', ``BB'', and ``CB'' refer to primary block, backscatter block, and channel block, respectively.
-			\gls{bc} employs all possible states as information codewords, \gls{ris} treats them as beamformer codewords, and RIScatter simultaneously exploits both benefits.
-		}
-		\label{fg:scatter_comparison}
-	\end{figure}
-	Instead of using fully random or fully deterministic reflection pattern over time, each RIScatter node \emph{semi-randomly} chooses the reflection state for each backscatter block with \emph{guidance of input probability} $P(\Gamma_m)$ at state $m$.
-	Such an adaptive backscatter channel coding includes the degenerate distribution of \gls{ris} and the uniform distribution of line-coded \gls{bc} as special cases.
-	Importantly, RIScatter system design only requires the \emph{direct} transmitter-receiver and \emph{cascaded} transmitter-scatter-receiver \gls{csi}.
-	For dispersed RIScatter nodes, relevant \gls{csi} can be estimated by sequential \cite{Bharadia2015,Yang2015b,Guo2019g} or parallel approaches \cite{Jin2021a} originally proposed for \gls{bc}.
-	For co-located RIScatter nodes, the estimation can be simplified by group-based \cite{Zheng2019} and hierarchical \cite{You2019} trainings originally proposed for \gls{ris}.
-
-	% ? Add an illustration here if space allows
-	We also propose a novel cooperative receiver that exploits the double modulation, double fading and symbol period difference to reduce the decoding complexity and improve the primary-backscatter tradeoff.
-	As illustrated in Fig.~\ref{fg:energy_distribution}, conditioned on different reflection state hypotheses, the accumulated receive energy per backscatter block follows Gamma distribution with different scale parameters \cite{Qian2017b}.
-	\begin{figure}[!t]
-		\centering
-		\resizebox{0.4\columnwidth}{!}{
-			\input{assets/illustration/energy_distribution.tex}
-		}
-		\caption{
-			\gls{pdf} of accumulated receive energy per backscatter block conditioned on different reflection state hypotheses.
-			% $z$, $t$, $\mathcal{H}$ and $\mathcal{R}$ denote the accumulated receive energy, decision threshold, reflection state hypothesis, and decision regions, respectively.
-		}
-		\label{fg:energy_distribution}
-	\end{figure}
-	Hence, the receiver can semi-coherently (under primary uncertainty) decode RIScatter nodes from the accumulated receive energy, re-encode to recover the exact reflection patterns, and combine those with cascaded \gls{csi} to determine the multipath response and model within the primary channel.
-	Such a backscatter-primary decoding enables simultaneous backscatter modulation and dynamic passive beamforming by only one energy comparison and re-encoding during each backscatter (instead of primary) block.
-	It enjoys a three-fold benefit compared to conventional primary-backscatter decoding with \gls{sic}, namely
-	1) reduces the re-encoding frequencies to $1/N$;
-	2) requires no re-precoding, cancellation, or \gls{mrc};
-	3) preserves backscatter modulation and passive beamforming at smaller spreading factors for potentially higher backscatter throughput.
-	% \end{subsection}
-
-	% \begin{subsection}{System Model}
+		To exploit the benefits of RIScatter, we also propose a practical co-located receiver that semi-coherently decodes the backscatter information, recovers the reflection pattern, and coherently decodes the primary link.
+		The detail will be covered in Section~\ref{se:system_model}.
+		% We also propose a practical co-located receiver to exploit the benefits of RIScatter and the detail will be covered in Section~\ref{se:system_model}.
+	\end{subsection}
+
+	% As illustrated in Fig.~\ref{fg:energy_distribution}, conditioned on different reflection state hypotheses, the accumulated energy per backscatter block follows Gamma distribution with different scale parameters \cite{Qian2017b}.
+	% \begin{figure}[!t]
+	% 	\centering
+	% 	\resizebox{0.8\columnwidth}{!}{
+	% 		\input{assets/illustration/energy_distribution.tex}
+	% 	}
+	% 	\caption{
+	% 		\gls{pdf} of accumulated energy per backscatter block conditioned on different reflection state hypotheses.
+	% 		$z$, $t$, $\mathcal{H}$ and $\mathcal{R}$ denote the accumulated energy, decision threshold, reflection state hypothesis, and decision regions, respectively.
+	% 	}
+	% 	\label{fg:energy_distribution}
+	% \end{figure}
+
+	% Hence, the receiver can semi-coherently (under primary uncertainty) decode RIScatter nodes from the accumulated energy, re-encode to recover the reflection patterns, and combine those with cascaded \gls{csi} to determine the multipath response and model within the primary channel.
+	% Such a backscatter-primary decoding enables simultaneous backscatter modulation and dynamic passive beamforming by only one energy comparison and re-encoding during each backscatter (instead of primary) block.
+	% It enjoys a three-fold benefit compared to conventional primary-backscatter decoding with \gls{sic}, namely
+	% 1) reduces the re-encoding frequencies to $1/N$;
+	% 2) requires no re-precoding, cancellation, or \gls{mrc};
+	% 3) preserves backscatter modulation and passive beamforming at smaller spreading factors for potentially higher backscatter throughput.
+
+	% % ! add to signal model
+	% % Importantly, RIScatter system design only requires the \emph{direct} transmitter-receiver and \emph{cascaded} transmitter-scatter-receiver \gls{csi}.
+	% % For dispersed RIScatter nodes, relevant \gls{csi} can be estimated by sequential \cite{Bharadia2015,Yang2015b,Guo2019g} or parallel approaches \cite{Jin2021a} originally proposed for \gls{bc}.
+	% % For co-located RIScatter nodes, the estimation can be simplified by group-based \cite{Zheng2019} and hierarchical \cite{You2019} trainings originally proposed for \gls{ris}.
+
+	\begin{subsection}{System Model}
+		\label{se:system_model}
 		\begin{figure}[!t]
@@
 		\end{figure}
-	As shown in Fig.~\ref{fg:riscatter_network}, we consider a RIScatter system where a $Q$-antenna \gls{ap} serves a single-antenna user as well as $K$ nearby dispersed/co-located single-antenna $M$-state RIScatter nodes.
-	In the primary point-to-point system, the \gls{ap} transmits information to the user over the multipath channel enhanced by RIScatter nodes.
-	In the backscatter multiple access system, the \gls{ap} and user become carrier emitter and backscatter reader, and the RIScatter nodes modulate over the scattered \gls{rf} signals.
-	For simplicity, we consider a quasi-static block fading model and focus on a specific block where all \gls{csi} remain constant.
-	Without loss of generality, let the spreading factor $N$ be a positive integer.
-	We also omit the signal reflected by two or more times and ignore the multipath propagation time difference.
+		As shown in Fig.~\ref{fg:riscatter_network}, we consider a RIScatter system where a $Q$-antenna \gls{ap} serves a single-antenna user and $K$ nearby dispersed or co-located RIScatter nodes.
+		All nodes have $M$ available reflection states.
+		In the primary point-to-point system, the \gls{ap} transmits information to the user over a multipath channel enhanced by RIScatter nodes.
+		In the backscatter multiple access system, the \gls{ap} acts as carrier emitter, the RIScatter nodes modulate over scattered signal, and the user jointly decodes all node messages.
+		For simplicity, we consider a quasi-static block fading model and focus on a specific block where the \gls{csi} remains constant.
+		It is assumed the signal reflected by two or more times is negligible, the primary symbol duration is much longer than multipath delay spread (no inter-symbol interference), and the spreading factor $N$ is a positive integer.
 		Denote the \gls{ap}-user direct channel as $\boldsymbol{h}_{\text{D}}^\mathsf{H} \in \mathbb{C}^{1 \times Q}$, the \gls{ap}-node $k \in \mathcal{K} \triangleq \{1,\ldots,K\}$ forward channel as $\boldsymbol{h}_{\text{F},k}^\mathsf{H} \in \mathbb{C}^{1 \times Q}$, the node $k$-user backward channel as $h_{\text{B},k}$, and the cascaded \gls{ap}-node $k$-user channel as $\boldsymbol{h}_{\text{C},k}^\mathsf{H} \triangleq h_{\text{B},k} \boldsymbol{h}_{\text{F},k}^\mathsf{H} \in \mathbb{C}^{1 \times Q}$.
+		We assume perfect direct and cascaded \gls{csi} are available at the \gls{ap} and the user\footnote{The cascaded \gls{csi} can be estimated by sequential \cite{Bharadia2015,Yang2015b,Guo2019g} or parallel \cite{Jin2021a} approaches for dispersed nodes, or group-based \cite{Zheng2019} or hierarchical \cite{You2019} approaches for co-located nodes.}.
+		% For dispersed RIScatter nodes, relevant \gls{csi} can be estimated by sequential \cite{Bharadia2015,Yang2015b,Guo2019g} or parallel approaches \cite{Jin2021a} originally proposed for \gls{bc}.
+For co-located RIScatter nodes, the estimation can be simplified by group-based \cite{Zheng2019} and hierarchical \cite{You2019} trainings originally proposed for \gls{ris}.}.
 		Let $x_k \in \mathcal{X} \triangleq \{c_1,\ldots,c_M\}$ be the coded backscatter symbol of node $k$ and $x_{\mathcal{K}} \triangleq (x_1,\ldots,x_K)$ be the backscatter symbol tuple of all nodes.
-	Due to double modulation, the primary equivalent channel is a function of backscatter symbol tuple\footnote{\eqref{eq:equivalent_channel_bc} and \eqref{eq:equivalent_channel_ris} are often used in \gls{bc} and \gls{ris} literatures, respectively.}
+		Due to double modulation, the composite channel is a function of backscatter symbol tuple\footnote{\eqref{eq:equivalent_channel_bc} and \eqref{eq:equivalent_channel_ris} are often used in \gls{bc} and \gls{ris} literature, respectively.}
 		\begin{subequations}
@@
 			\begin{align}
-			\boldsymbol{h}_{\text{E}}^\mathsf{H}(x_{\mathcal{K}})
+				\boldsymbol{h}^\mathsf{H}(x_{\mathcal{K}})
 				 & \triangleq \boldsymbol{h}_{\text{D}}^\mathsf{H} + \sum_{k} \alpha_k \boldsymbol{h}_{\text{C},k}^\mathsf{H} x_k \label{eq:equivalent_channel_bc}                    \\
@@
 		where $\alpha_k \in \mathbb{I}$ is the common amplitude scattering ratio of node $k$, $\boldsymbol{\alpha} \triangleq [\alpha_1,\ldots,\alpha_K]^\mathsf{T} \in \mathbb{I}^{K}$, $\boldsymbol{x} \triangleq [x_1,\ldots,x_K]^\mathsf{H} \in \mathcal{X}^{K}$, and $\boldsymbol{H}_{\text{C}} \triangleq [\boldsymbol{h}_{\text{C},1},\ldots,\boldsymbol{h}_{\text{C},K}]^\mathsf{H} \in \mathbb{C}^{K \times Q}$.
-	In the following context, we focus on one backscatter block (i.e., $N$ primary blocks).
+		Next, we consider the signal model within one backscatter block.
 		The signal received by the user at primary block $n \in \mathcal{N} \triangleq \{1,\ldots,N\}$ is
 		\begin{equation}
-		y[n] = \boldsymbol{h}_{\text{E}}^\mathsf{H}(x_{\mathcal{K}}) \boldsymbol{w} s[n] + v[n],
+			y[n] = \boldsymbol{h}^\mathsf{H}(x_{\mathcal{K}}) \boldsymbol{w} s[n] + v[n],
 			\label{eq:receive_signal}
@@
 		where $\boldsymbol{w} \in \mathbb{C}^{Q}$ is the active beamformer satisfying average transmit power constraint $\lVert \boldsymbol{w} \rVert^2 \le P$, $s \sim \mathcal{CN}(0,1)$ is the primary symbol, and $v \sim \mathcal{CN}(0,\sigma_v^2)$ is the \gls{awgn} with average power $\sigma_v^2$.
-	Let $m_k \in \mathcal{M} \triangleq \{1,\ldots,M\}$ be the reflection state index of node $k$ and $m_{\mathcal{K}} \triangleq (m_1,\ldots,m_K)$ be the reflection state index tuple of all nodes.
-	The backscatter symbol $x_k$ (resp.
+		Let $m_k \in \mathcal{M} \triangleq \{1,\ldots,M\}$ be the reflection state index of node $k$ and $m_{\mathcal{K}} \triangleq (m_1,\ldots,m_K)$ be the state index tuple of all nodes.
+		% The backscatter symbol $x_k$ (resp.
 symbol tuple $x_{\mathcal{K}}$) is a random variable (resp.
@@
 state tuple $m_{\mathcal{K}}$) is employed.
-	Conditioned on $m_{\mathcal{K}}$, the receive signal at each primary block follows \gls{cscg} distribution $\mathcal{CN}(0,\sigma_{m_{\mathcal{K}}}^2)$, where
-	\begin{equation}
-		\sigma_{m_{\mathcal{K}}}^2 = \lvert \boldsymbol{h}_{\text{E}}^\mathsf{H}(x_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2 + \sigma_v^2
+		The backscatter symbol tuple $x_{\mathcal{K}}$ is a random variable that takes value $x_{m_{\mathcal{K}}}$ when state tuple $m_{\mathcal{K}}$ is used.
+		Conditioned on hypothesis $\mathcal{H}_{m_{\mathcal{K}}}$, the receive signal per primary block follows \gls{cscg} distribution $\mathcal{CN}(0,\sigma_{m_{\mathcal{K}}}^2)$, where
+		\begin{equation}
+			\sigma_{m_{\mathcal{K}}}^2 = \lvert \boldsymbol{h}^\mathsf{H}(x_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2 + \sigma_v^2
 			\label{eq:receive_variance}
 		\end{equation}
-	is the received variance.
-	Let $z=\sum_{n} \bigl\lvert y[n] \bigr\rvert^2$ be the accumulated receive energy per backscatter block.
-	Since $z$ is the sum of $N$ \gls{iid} exponential variables, its conditional \gls{pdf} follows Gamma distribution
-	\begin{equation}
-		f(z|\mathcal{H}_{m_{\mathcal{K}}}) = \frac{z^{N-1} \exp(-z/\sigma_{m_{\mathcal{K}}}^2)}{\sigma_{m_{\mathcal{K}}}^{2N} (N-1)!},
+		is its variance.
+		Let $z=\sum_{n} \bigl\lvert y[n] \bigr\rvert^2$ be the accumulated energy per backscatter block.
+		Since $z$ is the sum of $N$ \gls{iid} exponential variables, the conditional \gls{pdf} follows Gamma distribution
+		\begin{equation}
+			f(z|\mathcal{H}_{m_{\mathcal{K}}}) = \frac{z^{N-1} \exp(-z/\sigma_{m_{\mathcal{K}}}^2)}{\sigma_{m_{\mathcal{K}}}^{2N} (N-1)!}.
 			\label{eq:energy_distribution}
 		\end{equation}
-	where $\mathcal{H}_{m_{\mathcal{K}}}$ denotes hypothesis $m_{\mathcal{K}}$.
-	At the receiver, the energy space is divided into disjoint decision regions associated with different hypotheses, as illustrated in Fig.~\ref{fg:energy_distribution}.
+		% The receiver first jointly decodes all backscatter messages under primary interference by energy detection.
+		% This essentially formulates a \gls{dmmac} over disjoint energy decision regions.
+		The user first jointly decodes all backscatter messages under primary interference by performing energy detection over disjoint decision regions.
+		For the ease of notation, we map the state index tuple $m_{\mathcal{K}}$ to $l \in \mathcal{L} \triangleq \{1,\ldots,L\}$, where $L \triangleq M^K$ and $\sigma_1^2,\ldots,\sigma_L^2$ forms an increasing sequence.
+		Both notations are used interchangeably in the following context.
+		The decision region of backscatter symbol tuple $l$ is
+		\begin{equation}
+			\mathcal{R}_{l} \triangleq [t_{l-1},t_l), \quad 0 \le t_{l-1} \le t_l,
+		\end{equation}
+		where $t_l$ is the energy decision threshold between hypotheses $\mathcal{H}_{l}$ and $\mathcal{H}_{l+1}$.
+		For a given decision threshold vector $\boldsymbol{t} \triangleq [t_0,\ldots,t_L]^\mathsf{T} \in \mathbb{R}_+^{(L+1)}$, we can formulate a \gls{dmmac} with transition probability from input $x_{m_{\mathcal{K}}}$ to output $\hat{x}_{m_{\mathcal{K}}'}$ as
+		\begin{equation}
+			P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}}) = \int_{\mathcal{R}_{m_{\mathcal{K}}'}} f(z|\mathcal{H}_{m_{\mathcal{K}}}) \, d z,
+			\label{eq:dmmac}
+		\end{equation}
+		over which input distribution of all RIScatter nodes can be designed.
+		An example of energy detection is illustrated in Fig.~\ref{fg:energy_distribution}.
+		% Conditioned on different reflection state hypotheses, the accumulated energy per backscatter block follows Gamma distribution with different scale parameters.
+		\begin{figure}[!t]
+			\centering
+			\resizebox{0.4\columnwidth}{!}{
+				\input{assets/illustration/energy_distribution.tex}
+			}
+			\caption{
+				\gls{pdf} of accumulated energy per backscatter block conditioned on different reflection state hypotheses.
+			}
+			\label{fg:energy_distribution}
+		\end{figure}
 		\begin{remark}
 			The capacity-achieving decision region design for \gls{dmtc} with non-binary inputs in arbitrary distribution remains an open issue.
-		It was proved deterministic detector can be rate-optimal, but non-convex decision regions (i.e., comprise non-adjacent partitions) are generally involved and the optimal number of thresholds remains unknown \cite{Nguyen2018,Nguyen2021}.
-		Hence, we limit the backscatter energy detector to convex deterministic decision regions and consider sequential threshold design in the following context.
+			It was proved deterministic detectors can be rate-optimal, but non-convex decision regions (comprise non-adjacent partitions) are generally required and the optimal number of thresholds remains unknown \cite{Nguyen2018,Nguyen2021}.
+			Hence, we limit the energy detector to convex deterministic decision regions and consider sequential threshold design.
 		\end{remark}
-
-	For the ease of notations, we map the state index tuple $m_{\mathcal{K}}$ to $l \in \mathcal{L} \triangleq \{1,\ldots,L \triangleq M^K\}$, where $\sigma_1^2,\ldots,\sigma_L^2$ is a non-decreasing sequence.
-	Both notations are used interchangeably in the following context.
-	As such, the decision region of backscatter symbol tuple $l$ can be written as
-	\begin{equation}
-		\mathcal{R}_{l} \triangleq [t_{l-1},t_l), \quad 0 \le t_{l-1} \le t_l,
-	\end{equation}
-	where $t_l$ is the energy decision threshold between hypotheses $\mathcal{H}_{l}$ and $\mathcal{H}_{l+1}$.
-	For a given decision threshold vector $\boldsymbol{t} \triangleq [t_0,\ldots,t_L]^\mathsf{T} \in \mathbb{R}_+^{(L+1)}$, we can formulate a \gls{dmtmac} with transition probability from input tuple $x_{m_{\mathcal{K}}}$ to output tuple $\hat{x}_{m_{\mathcal{K}}'}$ as
-	\begin{equation}
-		P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}}) = \int_{\mathcal{R}_{m_{\mathcal{K}}'}} f(z|\mathcal{H}_{m_{\mathcal{K}}}) \, d z,
-		\label{eq:dmtmac}
-	\end{equation}
-	over which adaptive backscatter channel coding can be performed.
+		After successful backscatter decoding, the user can re-encode for exact reflection pattern and obtain the composite channel by \eqref{eq:equivalent_channel}, then coherently decode the primary link.
+		Such an \gls{sic}-free sequential decoding enables backscatter modulation and dynamic passive beamforming by only one energy comparison and re-encoding per backscatter symbol.
+		It also supports arbitrary input distribution and spreading factor for higher backscatter throughput.
 		\label{st:system_model}
-	% \end{subsection}
-
-	% \begin{subsection}{Achievable Rates}
-	Denote the probability of node $k$ choosing reflection state $m_k$ as $P_k(x_{m_k})$, and let $\boldsymbol{p}_k \triangleq [P_k(c_1),\ldots,P_k(c_M)]^\mathsf{T} \in \mathbb{I}^{M}$.
-	For dispersed nodes with independent encoding, the probability of backscatter symbol value tuple $x_{m_{\mathcal{K}}}$ is
+	\end{subsection}
+
+	\begin{subsection}{Achievable Rates}
+		Denote the probability of node $k$ choosing reflection state $m_k$ as $P_k(x_{m_k})$ and let $\boldsymbol{p}_k \triangleq [P_k(c_1),\ldots,P_k(c_M)]^\mathsf{T} \in \mathbb{I}^{M}$.
+		For dispersed nodes with independent encoding, the probability of backscatter symbol tuple $x_{m_{\mathcal{K}}}$ is
 		\begin{equation}
@@
 		\end{equation}
-	where $P_{\mathcal{K}}(\hat{x}_{m_{\mathcal{K}}'}) = \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}})$ is the probability of output value tuple $\hat{x}_{m_{\mathcal{K}}'}$.
+		where $P_{\mathcal{K}}(\hat{x}_{m_{\mathcal{K}}'}) = \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}})$.
 		We also define the backscatter marginal information of $x_{m_k}$ as
@@
 
-	Once nodes are successfully decoded, we can re-encode and determine the primary equivalent channel by \eqref{eq:equivalent_channel}.
-	Therefore, the primary information function conditioned on $x_{m_{\mathcal{K}}}$ is
-	\begin{equation}
-		I_{\text{P}}(s;y|x_{m_{\mathcal{K}}}) \triangleq \log \Bigl(1 + \frac{\lvert \boldsymbol{h}_{\text{E}}^\mathsf{H}(x_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_v^2}\Bigr),
+		Once nodes are successfully decoded, we can re-encode and determine the composite channel by \eqref{eq:equivalent_channel}.
+		The primary information function conditioned on $x_{m_{\mathcal{K}}}$ is
+		\begin{equation}
+			I_{\text{P}}(s;y|x_{m_{\mathcal{K}}}) \triangleq \log \Bigl(1 + \frac{\lvert \boldsymbol{h}^\mathsf{H}(x_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_v^2}\Bigr),
 			\label{eq:primary_information_function}
@@
 
-	With a slight abuse of notation, we define the corresponding weighted sum information function, marginal information, and mutual information as
+		With a slight abuse of notation, we define the weighted sum information function, marginal information, and mutual information as
 		\begin{align}
@@
 		where $\rho \in \mathbb{I}$ is the relative \gls{qos} of the primary link.
-	We notice the average primary rate \eqref{eq:primary_mutual_information} depends on the backscatter input distribution and active beamforming, while the total backscatter rate depends on the input distribution and \gls{dmtmac} \eqref{eq:dmtmac} that relates to the active beamforming and decision thresholds.
+		We notice the average primary rate \eqref{eq:primary_mutual_information} depends on the backscatter input distribution and active beamforming, while the total backscatter rate depends on the input distribution and \gls{dmmac} \eqref{eq:dmmac} that relates to the active beamforming and decision thresholds.
 		\label{st:information_theory}
-	% \end{subsection}
+	\end{subsection}
 	\label{st:riscatter}
@@
 		\addConstraint{\lVert \boldsymbol{w} \rVert^2}{\le P}{\label{co:transmit_power}}
-		\addConstraint{0}{\le t_{l-1}}{\le t_l,}{\quad \forall l.}{\label{co:sequential_threshold}}
-		% \addConstraint{\boldsymbol{t}}{\ge \boldsymbol{0}.}{\label{co:nonnegative_threshold}}
+		\addConstraint{t_{l-1}}{\le t_l,}{\quad \forall l}{\label{co:sequential_threshold}}
+		\addConstraint{\boldsymbol{t}}{\ge \boldsymbol{0}.}{\label{co:nonnegative_threshold}}
 	\end{maxi!}
 
-	Problem \eqref{op:weighted_sum_rate} generalizes conventional \gls{bc} by allowing \gls{csi}- and \gls{qos}-adaptive input distribution and detection region design.
-	It also generalizes the discrete \gls{ris} phase shift selection by allowing stochastic reflection (i.e., relaxing the feasible domain from the \emph{vertices} of $M$-dimensional probability simplex to the simplex itself).
-	Since problem \eqref{op:weighted_sum_rate} is highly non-convex, we propose a \gls{bcd} algorithm that iteratively updates $\{\boldsymbol{p}_k\}_{k \in \mathcal{K}}$, $\boldsymbol{w}$ and $\boldsymbol{t}$ until convergence.
+	Problem \eqref{op:weighted_sum_rate} generalizes conventional \gls{bc} by allowing \gls{csi}- and \gls{qos}-adaptive input distribution and decision region design.
+	It also generalizes the discrete \gls{ris} phase shift selection problem by stochastic reflection that relaxes the feasible domain from the vertices of $M$-dimensional probability simplex to the simplex itself.
+	Problem \eqref{op:weighted_sum_rate} is highly non-convex and we propose a \gls{bcd} algorithm that iteratively updates $\{\boldsymbol{p}_k\}_{k \in \mathcal{K}}$, $\boldsymbol{w}$ and $\boldsymbol{t}$.
 
 	\begin{subsection}{Input Distribution}
-		For any given $\boldsymbol{w}$ and $\boldsymbol{t}$, we can construct the equivalent \gls{dmtmac} by \eqref{eq:dmtmac} and simplify \eqref{op:weighted_sum_rate} to
+		For any given $\boldsymbol{w}$ and $\boldsymbol{t}$, we can construct the equivalent \gls{dmmac} by \eqref{eq:dmmac} and simplify \eqref{op:weighted_sum_rate} to
 		\begin{maxi!}
@@
 		\begin{algorithm}[!t]
-			\small
 			\caption{Numerical \gls{kkt} Input Distribution Evaluation by Limits of Sequence}
@@
 		\begin{equation}
-			\nabla_{\boldsymbol{w}^*} Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr) = \frac{\boldsymbol{h}_{\text{E}}(x_{m_{\mathcal{K}}})\boldsymbol{h}_{\text{E}}^\mathsf{H}(x_{m_{\mathcal{K}}})\boldsymbol{w}}{(\sigma_{m_{\mathcal{K}}}^2)^2} g_{m_{\mathcal{K}}}(t_{l-1},t_l),
+			\nabla_{\boldsymbol{w}^*} Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr) = \frac{\boldsymbol{h}(x_{m_{\mathcal{K}}})\boldsymbol{h}^\mathsf{H}(x_{m_{\mathcal{K}}})\boldsymbol{w}}{(\sigma_{m_{\mathcal{K}}}^2)^2} g_{m_{\mathcal{K}}}(t_{l-1},t_l),
 			\label{eq:regularized_incomplete_gamma_gradient}
 		\end{equation}
-		where $g_{m_{\mathcal{K}}}(t_{l-1},t_l) \triangleq g_{m_{\mathcal{K}}}(t_l)-g_{m_{\mathcal{K}}}(t_{l-1})$ and $g_{m_{\mathcal{K}}}(t_l) = t_l\exp\Bigl(-\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr)\Bigl(-1+\sum_{n=1}^{N-1} \frac{\bigl(n - \frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\bigr) \bigl(\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\bigr)^{n-1}}{n!}\Bigr)$.
-		% \begin{equation}
-		% 	g_{m_{\mathcal{K}}}(t_l) = t_l\exp\Bigl(-\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr)\Bigl(-1+\sum_{n=1}^{N-1} \frac{\bigl(n - \frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\bigr) \bigl(\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\bigr)^{n-1}}{n!}\Bigr).
-		% 	\label{eq:regularized_incomplete_gamma_gradient_component}
-		% \end{equation}
+		where $g_{m_{\mathcal{K}}}(t_{l-1},t_l) \triangleq g_{m_{\mathcal{K}}}(t_l)-g_{m_{\mathcal{K}}}(t_{l-1})$ and
+		\begin{equation}
+			g_{m_{\mathcal{K}}}(t_l) = t_l\exp\Bigl(-\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr)\Bigl(-1+\sum_{n=1}^{N-1} \frac{\bigl(n - \frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\bigr) \bigl(\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\bigr)^{n-1}}{n!}\Bigr).
+			\label{eq:regularized_incomplete_gamma_gradient_component}
+		\end{equation}
 		On top of \eqref{eq:regularized_incomplete_gamma} and \eqref{eq:regularized_incomplete_gamma_gradient}, we explicitly express the objective function \eqref{ob:active_beamforming} and its gradient as
@@
 			I(x_{\mathcal{K}})
-			 & =\sum_{m_{\mathcal{K}}}P_{\mathcal{K}}(x_{m_{\mathcal{K}}})\Biggl(\rho\log\Bigl(1+\frac{\lvert\boldsymbol{h}_{\text{E}}^\mathsf{H}(x_{m_{\mathcal{K}}})\boldsymbol{w}\rvert^2}{\sigma_v^2}\Bigr) \nonumber                                                                                                                                                                                                      \\
+			 & =\sum_{m_{\mathcal{K}}}P_{\mathcal{K}}(x_{m_{\mathcal{K}}})\Biggl(\rho\log\Bigl(1+\frac{\lvert\boldsymbol{h}^\mathsf{H}(x_{m_{\mathcal{K}}})\boldsymbol{w}\rvert^2}{\sigma_v^2}\Bigr) \nonumber                                                                                                                                                                                                                 \\
 			 & \qquad + (1-\rho)\sum_l Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr) \log \frac{Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr)}{\sum_{m_{\mathcal{K}}'} P_{\mathcal{K}}(x_{m_{\mathcal{K}}'}) Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}'}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}'}^2}\Bigr)}\Biggr),
@@
 			\nabla_{\boldsymbol{w}^*} I(x_{\mathcal{K}})
-			 & = \sum_{m_{\mathcal{K}}}P_{\mathcal{K}}(x_{m_{\mathcal{K}}})\Biggl(\rho\frac{\boldsymbol{h}_{\text{E}}(x_{m_{\mathcal{K}}})\boldsymbol{h}_{\text{E}}^\mathsf{H}(x_{m_{\mathcal{K}}})\boldsymbol{w}}{\sigma_{m_{\mathcal{K}}}^2}+(1-\rho)\sum_l\biggl(\log\frac{Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr)}{\sum_{m_{\mathcal{K}}'}P_{\mathcal{K}}(x_{m_{\mathcal{K}}'})Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}'}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}'}^2}\Bigr)}+1\biggr)\nonumber                                                              \\
+			 & = \sum_{m_{\mathcal{K}}}P_{\mathcal{K}}(x_{m_{\mathcal{K}}})\Biggl(\rho\frac{\boldsymbol{h}(x_{m_{\mathcal{K}}})\boldsymbol{h}^\mathsf{H}(x_{m_{\mathcal{K}}})\boldsymbol{w}}{\sigma_{m_{\mathcal{K}}}^2}+(1-\rho)\sum_l\biggl(\log\frac{Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr)}{\sum_{m_{\mathcal{K}}'}P_{\mathcal{K}}(x_{m_{\mathcal{K}}'})Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}'}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}'}^2}\Bigr)}+1\biggr)\nonumber                                                                                    \\
 			 & \qquad \times \nabla_{\boldsymbol{w}^*} Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr)-\frac{Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr)\sum_{m_{\mathcal{K}}'}P_{\mathcal{K}}(x_{m_{\mathcal{K}}'})\nabla_{\boldsymbol{w}^*}Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}'}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}'}^2}\Bigr)}{\sum_{m_{\mathcal{K}}'}P_{\mathcal{K}}(x_{m_{\mathcal{K}}'})Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}'}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}'}^2}\Bigr)}\Biggr).
@@
 		\end{equation}
-		The \gls{pgd} active beamforming optimization with step size by \gls{bls} \cite[Section 9.2]{Boyd2004} is summarized in Algorithm \ref{al:active_beamforming}.
-
+		The \gls{pgd} active beamforming optimization with step size $\gamma$ refined by \gls{bls} \cite[Section 9.2]{Boyd2004} is summarized in Algorithm \ref{al:active_beamforming}.
 		\setalgorithmcaptionfont{\small}
 		\begin{algorithm}[!t]
-			\small
 			\caption{Iterative Active Beamforming Optimization by \gls{pgd} with \gls{bls}}
@@
 			{\scriptstyle{\boldsymbol{t}}}{I(x_{\mathcal{K}})}{\label{op:decision_threshold}}{\label{ob:decision_threshold}}
-			% \addConstraint{\eqref{co:sequential_threshold},\eqref{co:nonnegative_threshold},}
-			\addConstraint{\eqref{co:sequential_threshold},}
+			\addConstraint{\eqref{co:sequential_threshold},\eqref{co:nonnegative_threshold},}
 		\end{maxi!}
-		which is still non-convex because variable $\boldsymbol{t}$ appears on the limits of integration \eqref{eq:dmtmac}.
-		Fortunately, we can further simplify problem \eqref{op:decision_threshold} as a point-to-point rate-optimal quantizer design for a discrete-input continuous-output memoryless channel, thanks to Remark \ref{re:backscatter_decision} and \ref{re:augmented_source}.
+		which is still non-convex because variable $\boldsymbol{t}$ appears on the limits of integration \eqref{eq:dmmac}.
+		Fortunately, we can further simplify problem \eqref{op:decision_threshold} as a point-to-point rate-optimal quantizer design for a \gls{dcmc}, thanks to Remark \ref{re:backscatter_decision} and \ref{re:augmented_source}.
 
 		\begin{remark}
-			Backscatter decision design has no impact on the primary achievable rate, because the primary equivalent channel \eqref{eq:equivalent_channel} at each backscatter block can always be determined upon successful backscatter decoding.
-			It suggests any thresholding scheme that maximize the total backscatter rate \eqref{eq:backscatter_mutual_information} is also optimal for problem \eqref{op:decision_threshold}.
+			Energy detector design has no impact on the primary achievable rate since the composite channel \eqref{eq:equivalent_channel} can always be reconstructed after backscatter decoding and re-encoding.
+			It suggests any thresholding scheme maximizing the total backscatter rate \eqref{eq:backscatter_mutual_information} is also optimal for problem \eqref{op:decision_threshold}.
 			\label{re:backscatter_decision}
@@
 		\end{equation}
-		which is suboptimal for problem \eqref{op:decision_threshold} except when all nodes are with equiprobable inputs.
+		which is generally suboptimal for problem \eqref{op:decision_threshold} unless all RIScatter nodes are with equiprobable inputs.
 	\end{subsection}
@@
 	In this section, we provide numerical results to evaluate the proposed input distribution, active beamforming, and backscatter decision designs for the considered RIScatter system.
-	We assume the AP-user distance is \qty{10}{\meter} and at least one RIScatter nodes are randomly dropped in a disk centered at the user with radius $r$.
-	% The \gls{ap} is with an average transmit power budget $P=\qty{36}{\dBm}$, all nodes employs $M$-\gls{qam} with amplitude scattering ratio $\alpha=0.5$, and the user is with average noise power $\sigma_v^2=\qty{-40}{\dBm}$.
-	The \gls{ap} is with an average transmit power budget $P=\qty{36}{\dBm}$ and all nodes employs $M$-\gls{qam} with common amplitude scattering ratio $\alpha=0.5$.
+	We assume the AP-user distance is \SI{10}{\meter} and at least one RIScatter nodes are randomly dropped in a disk centered at the user with radius $r$.
+	% The \gls{ap} is with an average transmit power budget $P=\SI{36}{\dBm}$, all nodes employs $M$-\gls{qam} with amplitude scattering ratio $\alpha=0.5$, and the user is with average noise power $\sigma_v^2=\SI{-40}{\dBm}$.
+	The \gls{ap} is with an average transmit power budget $P=\SI{36}{\dBm}$ and all nodes employs $M$-\gls{qam} with $\alpha=0.5$.
 	For all channels involved, we consider a distance-dependent path loss model
@@
 	\end{equation}
-	where $d$ is the transmission distance, $L_0=-\qty{30}{\dB}$ is the reference path loss at $d_0=\qty{1}{\meter}$, $\kappa$ is the Rician $K$-factor, $\bar{\boldsymbol{H}}$ is the deterministic line-of-sight component with unit-magnitude entries, and $\tilde{\boldsymbol{H}}$ is the Rayleigh fading component with standard \gls{iid} \gls{cscg} entries.
+	where $d$ is the transmission distance, $L_0=-\SI{30}{\dB}$ is the reference path loss at $d_0=\SI{1}{\meter}$, $\kappa$ is the Rician K-factor, $\bar{\boldsymbol{H}}$ is the deterministic line-of-sight component with unit-magnitude entries, and $\tilde{\boldsymbol{H}}$ is the Rayleigh fading component with standard \gls{iid} \gls{cscg} entries.
 	We choose $\gamma_{\text{D}}=2.6$, $\gamma_{\text{F}}=2.4$, $\gamma_{\text{B}}=2$, and $\kappa_{\text{D}}=\kappa_{\text{F}}=\kappa_{\text{B}}=5$ for direct, forward and backward links.
-	The finite decision threshold domain $\mathcal{T}$ is obtained by $b$-bit uniform discretization over the critical interval defined by the confidence bounds of edge hypotheses (i.e., lower bound of $\mathcal{H}_1$ and upper bound of $\mathcal{H}_L$) with confidence $1-\epsilon$, and we choose $b=9$ and $\epsilon=\num{e-3}$.
-	All achievable rate points/regions are averaged over \num{1000} channel realizations.
+	The finite decision threshold domain $\mathcal{T}$ is obtained by $b$-bit uniform discretization over the critical interval defined by the confidence bounds of edge hypotheses (i.e., lower bound of $\mathcal{H}_1$ and upper bound of $\mathcal{H}_L$) with confidence $1-\varepsilon$.
+	We set $b=9$ and $\varepsilon=\num{e-3}$.
+	All achievable rate points/regions are averaged over \num{e3} channel realizations.
 
@@
 		\begin{itemize}
-			\item \emph{Legacy:} Conventional active transmission without antenna mode scattering, $\alpha=0$.
-			\item \emph{\gls{bbc}:} The primary symbol becomes deterministic $s[n]=1$ and the receive signal at each primary block is
-			\begin{equation}
-				y^{\text{\gls{bbc}}}[n] = \Bigl(\boldsymbol{h}_{\text{D}}^\mathsf{H} + \sum_{k} \alpha_k \boldsymbol{h}_{\text{C},k}^\mathsf{H} x_k\Bigr) \boldsymbol{w} + v[n],
-			\end{equation}
-			which follows non-zero mean complex Gaussian distribution $\mathcal{CN}\bigl((\boldsymbol{h}_{\text{D}}^\mathsf{H} + \sum_{k} \alpha_k \boldsymbol{h}_{\text{C},k}^\mathsf{H} x_{m_k}) \boldsymbol{w},\sigma_v^2\bigr)$ under hypothesis $\mathcal{H}_{m_{\mathcal{K}}}$.
-			The corresponding \gls{pdf} of accumulated receive energy over $N$ primary blocks is
-			\begin{equation}
-				f^{\text{\gls{bbc}}}(z|\mathcal{H}_{m_{\mathcal{K}}}) = \frac{(z-\mu_{m_{\mathcal{K}}}^{\text{\gls{bbc}}})^{N-1} \exp \bigl(-(z-\mu_{m_{\mathcal{K}}}^{\text{\gls{bbc}}})/\sigma_v^2 \bigr)}{\sigma_v^{2N} (N-1)!},
-				\label{eq:energy_distribution_bbc}
-			\end{equation}
-			where $\mu_{m_{\mathcal{K}}}^{\text{\gls{bbc}}} \triangleq N \bigl\lvert \bigl(\boldsymbol{h}_{\text{D}}^\mathsf{H} + \sum_{k} \alpha_k \boldsymbol{h}_{\text{C},k}^\mathsf{H} x_{m_k}\bigr) \boldsymbol{w} \bigr\rvert^2$.
-			The \gls{ml} decision threshold is derived as, $\forall l \in \mathcal{L} \setminus \{L\}$,
-			\begin{equation}
-				t_l^{\text{\gls{bbc}}} = \frac{\mu_{l-1}^{\text{\gls{bbc}}} \exp \bigl((\mu_{l-1}^{\text{\gls{bbc}}}-\mu_{l}^{\text{\gls{bbc}}})/\sigma_v^2 (N-1)\bigr) - \mu_{l}^{\text{\gls{bbc}}}}{\exp \bigl((\mu_{l-1}^{\text{\gls{bbc}}}-\mu_{l}^{\text{\gls{bbc}}})/\sigma_v^2 (N-1)\bigr) - 1}.
-				\label{eq:detection_threshold_ml_bbc}
-			\end{equation}
+			\item \emph{Legacy:} Active transmission without scatterers.
+			\item \emph{\gls{bbc}:} The primary symbol becomes deterministic $s[n]=1$ and the receive signal becomes
+			\begin{equation}
+				y^{\text{\gls{bbc}}}[n] = \Bigl(\boldsymbol{h}_{\text{D}}^\mathsf{H} + \sum_{k} \alpha_k \boldsymbol{h}_{\text{C},k}^\mathsf{H} x_k\Bigr) \boldsymbol{w} + v[n].
+			\end{equation}
+			The total backscatter rate of coherent decoding approaches $K \log M$ when $N$ is sufficiently large.
+			% which follows non-zero mean complex Gaussian distribution $\mathcal{CN}\bigl((\boldsymbol{h}_{\text{D}}^\mathsf{H} + \sum_{k} \alpha_k \boldsymbol{h}_{\text{C},k}^\mathsf{H} x_{m_k}) \boldsymbol{w},\sigma_v^2\bigr)$ under hypothesis $\mathcal{H}_{m_{\mathcal{K}}}$.
+			% The corresponding \gls{pdf} of accumulated energy over $N$ primary blocks is
+			% \begin{equation}
+			% 	f^{\text{\gls{bbc}}}(z|\mathcal{H}_{m_{\mathcal{K}}}) = \frac{(z-\mu_{m_{\mathcal{K}}}^{\text{\gls{bbc}}})^{N-1} \exp \bigl(-(z-\mu_{m_{\mathcal{K}}}^{\text{\gls{bbc}}})/\sigma_v^2 \bigr)}{\sigma_v^{2N} (N-1)!},
+			% 	\label{eq:energy_distribution_bbc}
+			% \end{equation}
+			% where $\mu_{m_{\mathcal{K}}}^{\text{\gls{bbc}}} \triangleq N \bigl\lvert \bigl(\boldsymbol{h}_{\text{D}}^\mathsf{H} + \sum_{k} \alpha_k \boldsymbol{h}_{\text{C},k}^\mathsf{H} x_{m_k}\bigr) \boldsymbol{w} \bigr\rvert^2$.
+			% The \gls{ml} decision threshold is derived as, $\forall l \in \mathcal{L} \setminus \{L\}$,
+			% \begin{equation}
+			% 	t_l^{\text{\gls{bbc}}} = \frac{\mu_{l-1}^{\text{\gls{bbc}}} \exp \bigl((\mu_{l-1}^{\text{\gls{bbc}}}-\mu_{l}^{\text{\gls{bbc}}})/\sigma_v^2 (N-1)\bigr) - \mu_{l}^{\text{\gls{bbc}}}}{\exp \bigl((\mu_{l-1}^{\text{\gls{bbc}}}-\mu_{l}^{\text{\gls{bbc}}})/\sigma_v^2 (N-1)\bigr) - 1}.
+			% 	\label{eq:detection_threshold_ml_bbc}
+			% \end{equation}
 			\item \emph{\gls{ambc}:} The user decodes both links independently and semi-coherently by treating the other as interference.
-			Hence, the primary achievable rate is approximately\footnote{To provide a preliminary benchmark, we consider the (correlated) scattered signal from finite-input backscatter sources as independent interference from Gaussian sources during primary decoding \cite{Long2020a}.}
+			The primary achievable rate is approximately\footnote{To provide a preliminary benchmark, we regard the scattered component $\sum_{k} \alpha_k \boldsymbol{h}_{\text{C},k}^\mathsf{H} x_k \boldsymbol{w}s[n]$ as \gls{awgn} during primary decoding \cite{Long2020a}.}
 			\begin{equation}
@@
 			\begin{equation}
-				\hat{y}^{\text{\gls{sr}}}[n] = \sum_{k} \alpha_k \boldsymbol{h}_{\text{C},k}^\mathsf{H} x_k \boldsymbol{w} s[n] + v[n],
+				\hat{y}^{\text{\gls{sr}}}[n] = \sum_{k} \alpha_k \boldsymbol{h}_{\text{C},k}^\mathsf{H} x_k \boldsymbol{w} s[n] + v[n].
 				\label{eq:intermediate_signal}
 			\end{equation}
-			which only involves noise uncertainty under hypothesis $\mathcal{H}_{m_{\mathcal{K}}}$.
-			During backscatter detection, the primary symbols $s[1],\ldots,s[n]$ can be viewed as a spreading code, and the receiver employs \gls{mrc} over $N$ primary blocks.
-			The total achievable for nodes with equiprobable inputs is \cite{Wang2014a}
-			\begin{equation}
-				I_{\text{B}}(x_{\mathcal{K}};\hat{y}^{\text{\gls{sr}}}) = K \log M - \frac{\iota}{M^K},
-			\end{equation}
-			where $\iota \triangleq \sum_{m_{\mathcal{K}}} \mathbb{E}_{\hat{v}} \log \sum_{m_{\mathcal{K}}'} \exp ( - {\lvert x_{m_{\mathcal{K}}} - x_{m_{\mathcal{K}}'} + \hat{v} \rvert^2}/{2 \sigma^2} )$ and $\hat{v} \sim \mathcal{CN}(0,\sigma_v^2/N)$.
+			The total backscatter rate of coherent decoding approaches $K \log M$ when $N$ is sufficiently large.
+			% which only involves noise uncertainty under hypothesis $\mathcal{H}_{m_{\mathcal{K}}}$.
+			% During backscatter detection, the primary symbols $s[1],\ldots,s[N]$ function as a spreading code and the receiver performs \gls{mrc} on $\hat{y}^{\text{\gls{sr}}}[n]$ over $N$ primary blocks.
+			% This essentially formulates a \gls{dcmc} and the total backscatter achievable rate is maximized with equiprobable inputs as \cite{Ng2006}
+			% \begin{equation}
+			% 	I_{\text{B}}(x_{\mathcal{K}};\hat{y}^{\text{\gls{sr}}}) = K \log M - \frac{\iota}{M^K},
+			% \end{equation}
+			% where $\iota \triangleq \sum_{m_{\mathcal{K}}} \mathbb{E}_{\hat{v}} \log \sum_{m_{\mathcal{K}}'} \exp ( - {\lvert x_{m_{\mathcal{K}}} - x_{m_{\mathcal{K}}'} + \hat{v} \rvert^2}/{2 \sigma^2} )$ and $\hat{v} \sim \mathcal{CN}(0,\sigma_v^2/N)$.
 			% For a sufficiently large $N$, $\iota$ is negligible and the total backscatter rate approaches $K \log M$.
-			\item \emph{\gls{ris}:} Since the backscatter symbol tuple $x_{\mathcal{K}}$ is deterministic, the total backscatter rate is zero and the primary achievable rate becomes a special case of \eqref{eq:primary_mutual_information}
-			\begin{equation}
-				I_{\text{P}}^{\text{\gls{ris}}}(s;y|x_{\mathcal{K}}) = I_{\text{P}}(s;y|x_{m_{\mathcal{K}}^{\star}}) = \log \Bigl(1 + \frac{\lvert \boldsymbol{h}_{\text{E}}^\mathsf{H}(x_{m_{\mathcal{K}}^{\star}}) \boldsymbol{w} \rvert^2}{\sigma_v^2}\Bigr),
-			\end{equation}
-			where $m_{\mathcal{K}}^{\star} = \arg \max_{m_{\mathcal{K}}} I_{\text{P}}(s;y|x_{m_{\mathcal{K}}})$.
+			\item \emph{\gls{ris}:} The reflection pattern is deterministic and the total backscatter rate is zero.
+			The primary achievable rate is a special case of \eqref{eq:primary_mutual_information}
+			\begin{equation}
+				I_{\text{P}}^{\text{\gls{ris}}}(s;y|x_{\mathcal{K}}) = I_{\text{P}}(s;y|x_{m_{\mathcal{K}}^{\star}}) = \log \Bigl(1 + \frac{\lvert \boldsymbol{h}^\mathsf{H}(x_{m_{\mathcal{K}}^{\star}}) \boldsymbol{w} \rvert^2}{\sigma_v^2}\Bigr),
+			\end{equation}
+			where $m_{\mathcal{K}}^{\star} = \arg \max_{m_{\mathcal{K}}} I_{\text{P}}^{\text{\gls{ris}}}(s;y|x_{m_{\mathcal{K}}})$.
 		\end{itemize}
@@
 			}
-			\caption{Typical achievable rate region/points of scattering applications for $Q=1$, $K=1$, $M=4$, $N=1000$, $\sigma_v^2=\qty{-40}{\dBm}$ and $r=\qty{2}{\meter}$.}
+			\caption{Typical achievable rate region/points of scattering applications for $Q=1$, $K=1$, $M=4$, $N=\num{e3}$, $\sigma_v^2=\SI{-40}{\dBm}$ and $r=\SI{2}{\meter}$.}
 			\label{fg:region_comparison}
@@
 
-		Fig.~\ref{fg:region_comparison} compares the typical achievable rate region/points of RIScatter and above.
-		\emph{First,} we observe both \gls{bbc} and \gls{sr} almost ensure noise-free backscatter transmission when the spreading factor $N$ is sufficiently large.
-		For \gls{bbc} with coherent energy detection, the conditional \gls{pdf} of accumulated receive energy \eqref{eq:energy_distribution_bbc} is more skewed at a large $N$, such that the equivalent \gls{dmtmac} \eqref{eq:dmtmac} has lower error probabilities.
-		For \gls{sic}-based \gls{sr}, the effective backscatter \gls{snr} is increased by $N$ times and the penalty term $\iota$ becomes insignificant.
-		However, the primary rate is only maintained at a very large spreading factor, which significantly constrains the backscatter \emph{throughput}.
-		\emph{Second,} the average primary rate slightly increases/decreases in the presence of a \gls{ambc}/\gls{ris} node, and the multipath benefit of \gls{sr} is unobvious.
-		This is because the cascaded channel can be orders of magnitude weaker than the direct channel due to the double fading effect.
-		\gls{ris} always ensures constructive superposition of direct and scattered components, while \gls{sr} only creates a quasi-static rich-scattering environment that \emph{stochastically} enhances the average primary rate.
-		When $N$ is moderate, the randomly scattered signals should be modelled as primary interference rather than multipath components, and the \gls{sr} point will move towards the \gls{ambc} point.
+		Fig.~\ref{fg:region_comparison} compares the typical achievable rate region/points of RIScatter and the strategies above.
+		% \emph{First,} we observe both \gls{bbc} and \gls{sr} achieves when the spreading factor $N$ is sufficiently large.
+		\emph{First,} we observe \gls{bbc} and \gls{sr} achieve the best backscatter performance thanks to coherent decoding.
+		% However, \gls{sr} requires $N$ \gls{sic} followed by a \gls
+		% However, \gls{sr} requires $N$ re-encoding, precoding, subtraction together with a time-domain \gls{mrc} to decode each backscatter symbol and the cost can be prohibitive.
+		For \gls{sr}, this comes with the cost of $N$ re-encoding, precoding, subtraction together with a time-domain \gls{mrc} per backscatter symbol.
+		% However, the primary rate benefit
+		% For \gls{bbc} with coherent energy detection, the conditional \gls{pdf} of accumulated energy \eqref{eq:energy_distribution_bbc} is more skewed at a large $N$, such that the equivalent \gls{dmmac} \eqref{eq:dmmac} has lower error probabilities.
+		% For \gls{sic}-based \gls{sr}, the effective backscatter \gls{snr} is increased by $N$ times and the penalty term $\iota$ becomes insignificant.
+		% However, the primary rate is only maintained at a very large spreading factor, which significantly constrains the backscatter \emph{throughput}.
+		\emph{Second,} the average primary rate slightly decreases/increases in the presence of a \gls{ambc}/\gls{ris} node and the benefit of \gls{sr} is not obvious.
+		This is because the cascaded channel is usually orders of magnitude weaker than the direct channel.
+		\gls{ris} always ensures constructive superposition of direct and scattered components while \gls{sr} only creates a quasi-static rich-scattering environment that marginally enhances the average primary rate.
+		When $N$ is moderate, the randomly scattered signals should be modelled as interference rather than multipath components and the \gls{sr} point should move towards the \gls{ambc} point.
 		\emph{Third,} RIScatter enables a flexible primary-backscatter tradeoff with adaptive input distribution design.
-		In terms of maximum primary achievable rate, RIScatter coincides with \gls{ris} and outperforms the others with passive beamforming provided by deterministic reflection pattern.
-		On the other hand, for a large $N$, the maximum backscatter achievable rate of RIScatter is higher than \gls{ambc} but lower than \gls{bbc} and \gls{sr}.
-		This is because both RIScatter and \gls{ambc} (resp.
-\gls{bbc} and \gls{sr}) employ semi-coherent (resp.
-coherent) energy detection, while RIScatter with adaptive channel coding can achieve higher backscatter rate than \gls{ambc} with equiprobable inputs.
-		Importantly, such a practical RIScatter detection is feasible for arbitrary spreading factor, which unleashes the potential of fast-switching nodes.
-		% , and using a fast-switching node with smaller $N$ can increase the backscatter throughput per unit time while preserving the dynamic passive beamforming gain on the primary link.
+		In terms of maximum primary achievable rate, RIScatter coincides with \gls{ris} and outperforms the others using deterministic reflection pattern.
+		On the other hand, for a large $N$, the maximum backscatter achievable rate of RIScatter is lower than \gls{bbc} and \gls{sr} but higher than \gls{ambc}.
+		This is because both RIScatter and \gls{ambc} employ semi-coherent energy detection, and the adaptive channel coding of RIScatter provides better performance than equiprobable inputs of \gls{ambc} especially at the low \gls{snr} of double fading.
+		When multiple antenna is available at the \gls{ap}, active beamforming can be optimized for RIScatter nodes and the backscatter rate gain over \gls{ambc} can be even larger.
 	\end{subsection}
 
-	\begin{subsection}{Input Distribution under Different QoS}
+	\begin{subsection}{Input Distribution under Different \gls{qos}}
 		\begin{figure}[!t]
@@
 			}
-			\caption{Typical RIScatter reflection state distribution at different $\rho$ for $Q=1$, $K=1$, $M=4$, $N=20$, $\sigma_v^2=\qty{-40}{\dBm}$ and $r=\qty{2}{\meter}$.}
+			\caption{Typical RIScatter reflection state distribution at different $\rho$ for $Q=1$, $K=1$, $M=4$, $N=20$, $\sigma_v^2=\SI{-40}{\dBm}$ and $r=\SI{2}{\meter}$.}
 			\label{fg:distribution_weights}
 		\end{figure}
-		The objective of this study is to demonstrate RIScatter nodes can leverage \gls{csi}- and \gls{qos}-adaptive input distribution design to balance backscatter modulation and passive beamforming.
-		For one RIScatter node with $M=4$, we evaluate the \gls{kkt} input distribution\footnote{Since problem \eqref{op:input_distribution} is convex when $K=1$, the \gls{kkt} solution is always global optimal in this case.} at different primary \gls{qos} and present the result in Fig.~\ref{fg:distribution_weights}.
-		At $\rho=0$ where the backscatter performance is prioritized, the optimal input distribution is zero on two states and nearly uniform on the other two.
-		This is because, due to the weak scattered signal, the conditional energy \gls{pdf} under different hypotheses can be closely spaced as illustrated in Fig.~\ref{fg:energy_distribution}.
-		In such cases, the extreme states producing the lowest/highest energy are always assigned with non-zero probability, while the middle ones may not provide enough energy difference and thus end up unused.
+		The objective is to demonstrate RIScatter nodes can leverage \gls{csi}- and \gls{qos}-adaptive input distribution design to balance backscatter modulation and passive beamforming.
+		For one RIScatter node with $M=4$, we evaluate the \gls{kkt} input distribution\footnote{Problem \eqref{op:input_distribution} is convex when $K=1$ and the \gls{kkt} solution is global optimal.} at different \gls{qos} and present the result in Fig.~\ref{fg:distribution_weights}.
+		At $\rho=0$ where the backscatter performance is prioritized, the optimal input distribution is \num{0} on two states and nearly uniform on the other two.
+		This is inline with Shannon's observation that binary antipodal inputs can be good enough for channel capacity at the low \gls{snr} \cite{Shannon1948}.
+		Due to the weak scattered signal, the conditional energy \gls{pdf} under different hypotheses can be closely spaced as in Fig.~\ref{fg:energy_distribution}.
+		The extreme states producing the lowest/highest energy are always assigned with non-zero probability and the middle ones may not provide enough energy difference and thus end up unused.
 		At $\rho=1$ where the primary performance is prioritized, the optimal input distribution is \num{1} at the state that maximizes the primary \gls{snr} and \num{0} at the others.
 		That is, the reflection pattern becomes deterministic and the RIScatter node boils down to a discrete \gls{ris} element.
-		Increasing $\rho$ from \num{0} to \num{1} provides a smooth transition from backscatter modulation to passive beamforming, which suggests RIScatter unifies \gls{bc} and \gls{ris} from a probabilistic perspective.
+		Increasing $\rho$ from \num{0} to \num{1} provides a smooth transition from backscatter modulation to passive beamforming and proves RIScatter unifies \gls{bc} and \gls{ris} from a probabilistic perspective.
 	\end{subsection}
@@
 			\begin{itemize}
-				\item \emph{Cooperation:} Joint node encoding with a $K$-dimensional probability array $P_{\mathcal{K}}(x_{m_{\mathcal{K}}})$ by Algorithm \ref{al:input_distribution};
-				\item \emph{Exhaustion:} Exhaustive search over $M$-dimensional probability simplex with step $\Delta p = \num{e-2}$;
-				\item \emph{\gls{kkt}:} Numerical \gls{kkt} result evaluation by Algorithm \ref{al:input_distribution};
+				\item \emph{Cooperation:} Joint nodes encoding using a $K$-dimensional probability array $P_{\mathcal{K}}(x_{m_{\mathcal{K}}})$ by Algorithm \ref{al:input_distribution};
+				\item \emph{Exhaustion:} Exhaustive search over the $M$-dimensional probability simplex with resolution $\Delta p = \num{e-2}$;
+				\item \emph{\gls{kkt}:} Numerical \gls{kkt} evaluation by Algorithm \ref{al:input_distribution};
 				\item \emph{Equiprobable:} Uniform input distribution for all nodes.
@@
 			Fig.~\subref*{fg:region_distribution} shows the average achievable rate regions for those designs.
-			We observe \emph{Cooperation} provides the outer bound since joint encoding is always beneficial.
-			The \emph{average} rate performance of \emph{Exhaustion} and \emph{\gls{kkt}} completely coincide with each other, demonstrating \gls{kkt} input distribution is favorable for a moderate $K$ as stated in Remark \ref{re:input_kkt_distribution}.
-			\emph{Equiprobable} experiences minor backscatter and major primary rate losses without \gls{csi}- and \gls{qos}-adaptive backscatter encoding.
-			Both gaps should become larger when $M$ and $K$ increase.
-			For the recovery methods, the simple \emph{Marginalization} provides a close result to \emph{\gls{kkt}}, but \emph{Randomization} and \emph{Decomposition} fail our expectations for most channel realizations.
-			Those observations emphasize the importance of (joint) adaptive RIScatter encoding and demonstrate the advantages of the proposed \gls{kkt} input distribution design.
+			We observe Cooperation provides the outer bound and joint encoding can be beneficial.
+			The average rate performance of Exhaustion and \gls{kkt} completely coincide with each other, demonstrating \gls{kkt} input distribution is favorable for a moderate $K$ as mentioned in Remark \ref{re:input_kkt_distribution}.
+			Equiprobable experiences minor backscatter and major primary rate losses without exploiting \gls{csi} and \gls{qos}.
+			Both rate gaps should be larger when $M$ and/or $K$ increase.
+			For the recovery methods, the simple Marginalization provides a close performance to \gls{kkt}, but Randomization and Decomposition fail our expectations for most channel realizations.
+			Those observations emphasize the importance of (joint) adaptive RIScatter encoding and demonstrate the advantage of the proposed \gls{kkt} input distribution design.
 		\end{subsubsection}
@@
 			Fig.~\subref*{fg:region_beamforming} presents the average achievable rate regions for those schemes.
-			In the low-$\rho$ regime, the proposed \emph{\gls{pgd}} beamformer significantly outperforms both \gls{mrt} schemes in terms of total backscatter rate.
-			This is because backscatter detection relies on the \emph{relative difference} of accumulated receive energy under different symbol tuples.
-			Such an energy diversity is enhanced by \emph{\gls{pgd}} that effectively exploits backscatter constellation and input distribution knowledge, rather than simply maximizing the direct/ergodic equivalent \gls{snr}.
-			As $\rho$ increases, the primary equivalent \gls{snr} outweighs the backscatter energy difference in \eqref{eq:weighted_sum_mutual_information_explicit}, and \emph{\gls{pgd}} beamformer becomes closer to both \gls{mrt} schemes.
-			At $\rho=1$, \emph{\gls{pgd}} and \emph{E-\gls{mrt}} boil down to \gls{mrt} towards the deterministic primary equivalent channel as in \gls{ris} literatures \cite{Wu2019}.
-			Besides, the difference between \emph{E-\gls{mrt}} and \emph{D-\gls{mrt}} can be insignificant for dispersed RIScatter nodes.
-			Those observations prove the proposed \emph{\gls{pgd}} active beamforming design can exploit the \gls{csi}, \gls{qos}, and backscatter constellation to balance the primary equivalent \gls{snr} and backscatter energy difference and enlarge the achievable rate region for RIScatter.
+			In the low-$\rho$ regime, the proposed \gls{pgd} beamformer significantly outperforms both \gls{mrt} schemes in terms of total backscatter rate.
+			This is because the semi-coherent backscatter decoding relies on the \emph{relative difference} of accumulated energy under different symbol tuples.
+			Such an energy diversity is enhanced by \gls{pgd} that effectively exploits backscatter constellation and input distribution knowledge rather than simply maximizing the direct/ergodic \gls{snr}.
+			As $\rho$ increases, the primary equivalent \gls{snr} outweighs the backscatter energy difference in \eqref{eq:weighted_sum_mutual_information_explicit} and \gls{pgd} beamformer becomes closer to both \gls{mrt} schemes.
+			At $\rho=1$, both \gls{pgd} and E-\gls{mrt} boil down to \gls{mrt} towards the composite channel.
+			The difference between E-\gls{mrt} and D-\gls{mrt} is insignificant when RIScatter nodes are dispersed.
+			Those observations prove the proposed \gls{pgd} active beamforming design can exploit the \gls{csi}, \gls{qos}, and backscatter constellation to balance the primary equivalent \gls{snr} and backscatter energy difference and enlarge the achievable rate region.
 		\end{subsubsection}
@@
 			This is because each RIScatter node not only affects the primary equivalent \gls{snr} but also influences the relative energy difference that other nodes can create.
-			To maximize the total backscatter rate, some nodes closer to the user may need to sacrifice their own rate and use the state that \emph{minimizes} the primary equivalent channel strength, in order to increase the backscatter rate of other nodes.
+			To maximize the total backscatter rate, some nodes closer to the user may need to sacrifice their own rate and use the state that \emph{minimizes} the composite channel strength, in order to increase the backscatter rate of other nodes.
 			This accounts for the significant primary rate decrease in the low-$\rho$ regime.
-			On the other hand, when the primary link is prioritized, the RIScatter nodes boil down to \gls{ris} elements and enjoy a classic passive array gain of $N^2$.
+			On the other hand, when the primary link is prioritized, the RIScatter nodes boil down to \gls{ris} elements and enjoy a conventional passive array gain $N^2$.
 		\end{subsubsection}
@@
 		\begin{subsubsection}{Spreading factor}
-			Fig.~\subref*{fg:region_duration} presents how the spreading factor $N$ affects the achievable rate region, where the unit of total backscatter rate is bits per primary block (to indicate throughput).
+			Fig.~\subref*{fg:region_duration} presents how the spreading factor $N$ affects the achievable rate region.
+			Please notice here the unit of total backscatter rate is bits per primary block to indicate throughput.
 			Apparently, using a very large $N$ can severely constrain the backscatter throughput, since the gain in energy certainty (by law of large numbers) cannot withstand the loss in gross rate.
 			As $N \to \infty$, RIScatter nodes boil down to \gls{ris} elements with fixed reflection pattern during whole channel block and the total backscatter rate approaches \num{0}.
-			On the other hand, when $N$ is too small, the equivalent \gls{dmtmac} \eqref{eq:dmtmac} has very high error probabilities and the energy detection can thus be unreliable.
-			It explains the observation that $N=10$ provides lower backscatter achievable rate than $N=20$, although nodes are encoding at higher gross rate.
-			Therefore, we conclude the design of spreading factor $N$ in RIScatter systems should account for multiple factors (e.g., data rate requirements, load switching constraints at the nodes, and signal processing capability at the user).
+			On the other hand, when $N$ is too small, the equivalent \gls{dmmac} \eqref{eq:dmmac} has very high error probabilities and the energy detection is thus unreliable.
+			It explains the observation that $N=10$ provides lower backscatter throughput than $N=20$.
+			Therefore, we conclude the design of spreading factor $N$ in RIScatter systems should accommodate multiple factors (e.g., data rate requirements, load switching constraints at the nodes, and signal processing capability at the user).
 		\end{subsubsection}
@@
 \begin{section}{Conclusion}
-	This paper introduced RIScatter as a low-power scatter protocol that unifies backscatter modulation and dynamic passive beamforming by smart input distribution and practical receiver design.
-	Starting from scattering principles, we showed how RIScatter nodes include information node of \gls{bc} and reflect element of \gls{ris} as special cases, how they can be built over existing passive scatter devices, and how they simultaneously encode self information and assist legacy transmission.
-	We also propose a practical RIScatter receiver that preserves the benefits of backscatter modulation and dynamic passive beamforming without \gls{sic}.
+	This paper introduced RIScatter as a low-power scatter protocol that simultaneously provides backscatter modulation and passive beamforming by smart input distribution design.
+	Starting from scattering principles, we showed how RIScatter nodes generalize information nodes of \gls{bc} and reflect elements of \gls{ris} as special cases, how they can be built over existing passive scatter devices, and how they simultaneously encode self information and assist legacy transmission.
+	We also propose a practical \gls{sic}-free receiver that exploits the properties of active-passive coexisting networks to maintain primary benefit and improve backscatter throughput.
 	The achievable primary-total-backscatter rate region is then studied for a single-user multi-node RIScatter system, where the input distribution, active beamforming, and decision thresholds are iteratively updated.
-	Numerical results not only validated the proposed algorithms, but also emphasized the importance of adaptive input distribution and cooperative decoding on both primary and backscatter links.
-
-	One possible direction is to consider backscatter detection over the received signal domain rather than energy domain, where multi-antenna and learning-based approaches can be promising.
+	Numerical results not only validated the proposed algorithms but also emphasized the importance of adaptive input distribution and cooperative decoding for both primary and backscatter links.
+
+	One possible future direction is to consider backscatter detection over the received signal domain rather than energy domain, where multi-antenna \cite{Liu2022c} and learning-based approaches can be promising.
 	Another interesting question is how to design RIScatter node and receiver in a multi-user system to fully exploit the dynamic passive beamforming that naturally origins from backscatter modulation.
@@
 		Denote the Lagrange multipliers associated with \eqref{co:sum_probability} and \eqref{co:nonnegative_probability} as $\{\nu_k\}_{k \in \mathcal{K}}$ and $\{\lambda_{k,m_k}\}_{k \in \mathcal{K},m_k \in \mathcal{M}}$, respectively.
-		The \gls{kkt} conditions of problem \eqref{op:input_distribution} are, $\forall k,m_k$,
+		The Lagrangian function of problem \eqref{op:input_distribution} is
+		\begin{equation}
+			- I(x_{\mathcal{K}}) + \sum_k \nu_k \biggl( \sum_{m_k} P_k(x_{m_k}) - 1 \biggr) - \sum_k \sum_{m_k} \lambda_{k,m_k} P_k(x_{m_k})
+		\end{equation}
+		and the \gls{kkt} conditions are, $\forall k,m_k$,
 		\begin{subequations}
 			\label{eq:input_kkt_condition_original}
-			\begin{gather}
-				- \nabla_{P_k^\star(x_{m_k})} I^\star(x_{\mathcal{K}}) + \nu_k^\star - \lambda_{k,m_k}^\star = 0, \\
-				\lambda_{k,m_k}^\star = 0, \quad P_k^\star(x_{m_k}) > 0, \\
+			\begin{equation}
+				- \nabla_{P_k^\star(x_{m_k})} I^\star(x_{\mathcal{K}}) + \nu_k^\star - \lambda_{k,m_k}^\star = 0,
+			\end{equation}
+			\begin{equation}
+				\lambda_{k,m_k}^\star = 0, \quad P_k^\star(x_{m_k}) > 0,
+			\end{equation}
+			\begin{equation}
 				\lambda_{k,m_k}^\star \ge 0, \quad P_k^\star(x_{m_k}) = 0,
-			\end{gather}
+			\end{equation}
 		\end{subequations}
-		where $\nabla_{P_k^\star(x_{m_k})} I^\star(x_{\mathcal{K}}) = I_k^\star(x_{m_k}) - (1 - \rho)$.
-		Therefore, we have
+		where directional derivative is explicitly written as
+		\begin{equation}
+			\nabla_{P_k^\star(x_{m_k})} I^\star(x_{\mathcal{K}}) = I_k^\star(x_{m_k}) - (1 - \rho).
+			\label{eq:input_directional_derivative}
+		\end{equation}
+		Combining \eqref{eq:input_kkt_condition_original} and \eqref{eq:input_directional_derivative}, we have
 		\begin{subequations}
@@
 		\end{subequations}
-		such that $\sum_{m_k} P_k^\star(x_{m_k}) I_k^\star(x_{m_k}) = \nu_k^\star + (1 - \rho)$.
-		On the other hand, by definition \eqref{eq:weighted_sum_marginal_information} we have $\sum_{m_k} P_k^\star(x_{m_k}) I_k^\star(x_{m_k}) = I^\star(x_{\mathcal{K}})$, where the right-hand side is irrelevant to $k$.
-		This complete the proof.
+		such that
+		\begin{equation}
+			\sum_{m_k} P_k^\star(x_{m_k}) I_k^\star(x_{m_k}) = \nu_k^\star + (1 - \rho).
+			\label{eq:input_kkt_condition_implied}
+		\end{equation}
+		On the other hand, by definition \eqref{eq:weighted_sum_marginal_information} we have
+		\begin{equation}
+			\sum_{m_k} P_k^\star(x_{m_k}) I_k^\star(x_{m_k}) = I^\star(x_{\mathcal{K}}),
+			\label{eq:weighted_sum_marginal_information_implied}
+		\end{equation}
+		where the right-hand side is irrelevant to $k$.
+		\eqref{eq:input_kkt_condition_transformed}, \eqref{eq:input_kkt_condition_implied}, and \eqref{eq:weighted_sum_marginal_information_implied} together complete the proof.
 		\label{ap:input_kkt_condition}
@@
 		\end{equation}
-		where $S_k'(x_{m_k}) \triangleq I_k'(x_{m_k}) + (1 - \rho) \sum_{m_{\mathcal{K} \setminus \{k\}}} P_{\mathcal{K} \setminus \{k\}}(x_{m_{\mathcal{K} \setminus \{k\}}}) \sum_{m_{\mathcal{K}}'} P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}}) \log P_{\mathcal{K}}'(x_{m_{\mathcal{K}}})$ and $i_k \ne m_k$ is the reference state.
+		where $i_k \ne m_k$ is the reference state and
+		\begin{align}
+			S_k'(x_{m_k})
+			 & \triangleq I_k'(x_{m_k}) + (1 - \rho) \sum_{m_{\mathcal{K} \setminus \{k\}}} P_{\mathcal{K} \setminus \{k\}}(x_{m_{\mathcal{K} \setminus \{k\}}})\nonumber \\
+			 & \quad \times \sum_{m_{\mathcal{K}}'} P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}}) \log P_{\mathcal{K}}'(x_{m_{\mathcal{K}}}).
+		\end{align}
 		Evidently, $\forall m_k \ne i_k$, \eqref{eq:optimal_intermediate_information_condition} boils down to
@@
 		Since $P_k(x_{i_k}) = 1 - \sum_{m_k \ne i_k} P_k^\star(x_{m_k})$ has exactly the same form as \eqref{eq:optimal_relative_distribution}, the choice of reference state $i_k$ does not matter and \eqref{eq:optimal_relative_distribution} is indeed optimal $\forall m_k \in \mathcal{M}$.
-		That is, for a fixed $P_{\mathcal{K}}'(x_{m_{\mathcal{K}}})$, choosing $P_k(x_{m_k})$ by \eqref{eq:optimal_relative_distribution} ensures $J \bigl( P_{\mathcal{K}}(x_{m_{\mathcal{K}}}),P_{\mathcal{K}}'(x_{m_{\mathcal{K}}}) \bigr) \ge I'(x_{\mathcal{K}})$.
+		That is, for a fixed $P_{\mathcal{K}}'(x_{m_{\mathcal{K}}})$, choosing $P_k(x_{m_k})$ by \eqref{eq:optimal_relative_distribution} ensures
+		\begin{equation}
+			J \bigl( P_{\mathcal{K}}(x_{m_{\mathcal{K}}}),P_{\mathcal{K}}'(x_{m_{\mathcal{K}}}) \bigr) \ge I'(x_{\mathcal{K}}).
+			\label{eq:information_difference_lower}
+		\end{equation}
 		On the other hand, we also have
@@
 		where $f_k'(x_{m_k}) \triangleq \exp \bigl( \frac{\rho}{1 - \rho} I_k'(x_{m_k}) \bigr)$ and the equality holds if and only if \eqref{eq:optimal_relative_distribution} converges.
-		Therefore, we have $I(x_{\mathcal{K}}) \ge I'(x_{\mathcal{K}})$.
+		\eqref{eq:information_difference_lower} and \eqref{eq:information_difference_upper} together imply $I(x_{\mathcal{K}}) \ge I'(x_{\mathcal{K}})$.
 		Since mutual information is bounded above, we conclude the sequence \eqref{eq:input_kkt_solution} is non-decreasing and convergent in mutual information.
+
 		Next, we prove any converging point of sequence \eqref{eq:input_kkt_solution}, denoted as $P_k^\star(x_{m_k})$, fulfills \gls{kkt} conditions \eqref{eq:input_kkt_condition}.
@@
 		\end{equation}
-		As sequence \eqref{eq:input_kkt_solution} is convergent, any state with $P_k^\star(x_{m_k}) > 0$ need to satisfy $D_k^\star(x_{m_k}) \triangleq \lim_{r \to \infty} D_k^{(r)}(x_{m_k}) = 1$, namely $I_k^\star(x_{m_k}) = \frac{1 - \rho}{\rho} \log \sum_{m_k'} P_k^\star(x_{m_k'}) f_k^\star(x_{m_k'})$, which is reminiscent of \eqref{eq:probable_states_marginal} and \eqref{eq:probable_states}.
+		As sequence \eqref{eq:input_kkt_solution} is convergent, any state with $P_k^\star(x_{m_k}) > 0$ need to satisfy $D_k^\star(x_{m_k}) \triangleq \lim_{r \to \infty} D_k^{(r)}(x_{m_k}) = 1$, namely
+		\begin{equation}
+			I_k^\star(x_{m_k}) = \frac{1 - \rho}{\rho} \log \sum_{m_k'} P_k^\star(x_{m_k'}) f_k^\star(x_{m_k'}),
+		\end{equation}
+		which is reminiscent of \eqref{eq:probable_states_marginal} and \eqref{eq:probable_states}.
 		That is, given $P_k^{(0)}(x_{m_k}) > 0$, any converging point with $P_k^\star(x_{m_k}) > 0$ must satisfy \eqref{eq:probable_states}.
-		On the other hand, we assume $P_k^\star(x_{m_k})$ does not satisfy \eqref{eq:dropped_states}, such that for any state with $P_k^\star(x_{m_k}) = 0$, $I_k^\star(x_{m_k}) > I^\star(x_{\mathcal{K}}) = \sum_{m_k'} P_k^\star(x_{m_k'}) I_k^\star(x_{m_k'})$, where the equality inherits from \eqref{eq:weighted_sum_mutual_information}.
+		On the other hand, we assume $P_k^\star(x_{m_k})$ does not satisfy \eqref{eq:dropped_states}, such that for any state with $P_k^\star(x_{m_k}) = 0$,
+		\begin{equation}
+			I_k^\star(x_{m_k}) > I^\star(x_{\mathcal{K}}) = \sum_{m_k'} P_k^\star(x_{m_k'}) I_k^\star(x_{m_k'}),
+		\end{equation}
+		where the equality inherits from \eqref{eq:weighted_sum_mutual_information}.
 		Since the exponential function is monotonically increasing, we have $f_k^\star(x_{m_k}) > \sum_{m_k'} P_k^\star(x_{m_k'}) f_k^\star(x_{m_k'})$ and $D_k^\star(x_{m_k}) > 1$.
-		Considering $P_k^{(0)}(x_{m_k}) > 0$ and $P_k^\star(x_{m_k}) = 0$, it contradicts with $P_k^{(r)}(x_{m_k}) = P_k^{(0)}(x_{m_k}) \prod_{n=1}^r D_k^{(n)}(x_{m_k})$.
+		Considering $P_k^{(0)}(x_{m_k}) > 0$ and $P_k^\star(x_{m_k}) = 0$, it contradicts with
+		\begin{equation}
+			P_k^{(r)}(x_{m_k}) = P_k^{(0)}(x_{m_k}) \prod_{n=1}^r D_k^{(n)}(x_{m_k}).
+		\end{equation}
 		That is, given $P_k^{(0)}(x_{m_k}) > 0$, any converging point with $P_k^\star(x_{m_k}) = 0$ must satisfy \eqref{eq:dropped_states}.
-		The proof is completed.
+		The proof is thus completed.
 		\label{ap:input_kkt_solution}
 	\end{subsection}
+
+	% \begin{subsection}{Proof of Proposition \ref{pr:threshold}}
+	% 	Since $L$ input letters are with non-zero probability and $x \to z \to \hat{x}$ formulates a Markov chain, we need $L$ non-empty decision regions and at least $L+1$ distinct thresholds (including \num{0} and $\infty$) to minimize the distortion between source and decision.
+	% 	On the other hand, the optimal decision regions are apparently empty for those unused letters.
+
+	% 	Suppose the optimal number of thresholds is $S+1$ where $S \ge L$.
+	% 	Let $\boldsymbol{t} \triangleq [t_0,\ldots,t_S]^\mathsf{T} \in \mathbb{R}_{+}^{(S+1)}$ be the optimal threshold vector where $t_{s-1} < t_s$, $\forall s \in \mathcal{S} \triangleq \{1,\ldots,S\}$.
+	% 	Since the optimal decision region for any letter may consist of multiple partitions, without loss of generality, we assume the mapping from threshold vector to decision region $l' \in \mathcal{L} \triangleq \{1,\ldots,L\}$ is given by $\mathcal{R}_{l'} = \bigcup_{s \equiv l' \pmod L} [t_{s-1},t_s)$.
+	% 	\begin{footnote}
+	% 		The proof holds for any valid mapping from threshold vector to decision regions, and we consider this specific case for the ease of presentation.
+	% 	\end{footnote}
+	% 	The threshold optimization problem is
+	% 	\begin{maxi!}
+	% 		{\scriptstyle{\boldsymbol{t}}}{I_{\text{B}}(x;\hat{x})}{\label{op:decision_threshold}}{\label{ob:backscatter_mutual_information}}
+	% 		\addConstraint{t_{s-1}}{< t_s,}{\quad \forall s \in \mathcal{S}.}{\label{co:strict_inequality}}
+	% 	\end{maxi!}
+
+	% 	Problem \eqref{op:decision_threshold} is intricate due to the strict inequality constraint \eqref{co:strict_inequality}.
+	% 	Following \cite{Nguyen2020}, we first relax it to the convex counterpart, then discard the solutions that violate any original constraint.
+	% 	The Lagrangian function for the relaxed problem is
+	% 	\begin{equation}
+	% 		L = - I_{\text{B}}(x;\hat{x}) + \sum_{s \in \mathcal{S}} \mu_s (t_{s-1} - t_s),
+	% 	\end{equation}
+	% 	where $\mu_s$ is the Lagrange multiplier associated with the non-strict version of \eqref{co:strict_inequality}.
+	% 	The \gls{kkt} conditions on the optimal primal and dual solutions are, $\forall s \in \mathcal{S}$,
+	% 	\begin{subequations}
+	% 		\label{eq:kkt_thresholding}
+	% 		\begin{equation}
+	% 			- \nabla_{t_s^\star} I^\star_{\text{B}}(x;\hat{x}) + \mu_{s-1}^\star - \mu_s^\star = 0,
+	% 			\label{eq:stationarity}
+	% 		\end{equation}
+	% 		\begin{equation}
+	% 			\mu_s^\star \ge 0,
+	% 			\label{eq:dual_feasibility}
+	% 		\end{equation}
+	% 		\begin{equation}
+	% 			\mu_s^\star (t_{s-1}^\star - t_s^\star) = 0.
+	% 			\label{eq:complementary_slackness}
+	% 		\end{equation}
+
+	% 	\end{subequations}
+	% 	Due to the strict inequality constraint \eqref{co:strict_inequality}, conditions \eqref{eq:dual_feasibility} and \eqref{eq:complementary_slackness} together imply $\mu_s^\star = 0$, $\forall s \in \mathcal{S}$.
+	% 	Besides, it is trivial to conclude $t_0^\star = 0$ for energy-based detection.
+	% 	As such, the necessary optimality conditions for problem \eqref{op:decision_threshold}, $\forall s \in \mathcal{S}$,
+	% 	\begin{equation}
+	% 		\nabla_{t_{s}^\star} I^\star_{\text{B}}(x;\hat{x}) = 0,
+	% 	\end{equation}
+	% 	which can be explicitly written as, $\forall s \equiv l' \pmod L$,
+	% 	\begin{equation}
+	% 		\sum_l P(x_l) \frac{(t_s^\star)^{N-1} \exp{-t_s^\star/\sigma_l^2}}{\sigma_l^{2N} (N-1)!} \log \frac{P(x_l|\hat{x}_{l'+1})}{P(x_l|\hat{x}_{l'})} = 0,
+	% 		\label{eq:kkt_threshold_explicit}
+	% 	\end{equation}
+
+	% 	According to \cite{He2021}, the optimal backward channel quantizer is convex and separates each pair of posterior distribution by a hyperplane.
+	% 	It implies, for a given output letter $l'$, the sequence $\{\log {P(x_l|\hat{x}_{l'+1})}/{P(x_l|\hat{x}_{l'})}\}_{l \in \mathcal{L}}$ changes sign exactly once.
+	% 	We notice the left-hand side of \eqref{eq:kkt_threshold_explicit} is a generalized Dirichlet polynomial, and by Descartes' rule of signs \cite{Jameson2006}, has at most one positive solution.
+	% 	% TODO
+	% 	In other words, starting from $t_0^\star$, each optimal decision region requires at most one additional distinct threshold, and we have $S \le L$.
+	% 	Therefore, we conclude $S = L$ and the proof is completed.
+	% 	\qedsymbol
+	% 	\label{ap:threshold}
+	% \end{subsection}
 \end{appendix}
 
+\begin{section}{Acknowledgement}
+	The authors would like to thank Prof. Geoffrey Ye Li for his clinical comments on earlier versions of the manuscript.
+\end{section}
+
 \bibliographystyle{IEEEtran}
-\bibliography{IEEEabrv,library.bib}
+\bibliography{library.bib}
 \end{document}

### 2023-07-26 review/response.tex
:speech_balloon: Add comments

\documentclass[10pt]{scrartcl}

\usepackage{scrletter}
\usepackage{parskip}

\usepackage[table]{xcolor}
\usepackage{adjustbox}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{bookmark}
\usepackage{booktabs}
\usepackage[american]{circuitikz}
\usepackage{cite}
\usepackage{fixmath}
\usepackage[acronym]{glossaries-extra}
\usepackage{hyperref}
\usepackage{import}
\usepackage{mathtools}
% \usepackage{microtype}
\usepackage[short]{optidef}
\usepackage{pgfplots}
\usepackage{ragged2e}
\usepackage[subtle]{savetrees}
\usepackage{setspace}
\usepackage{siunitx}
\usepackage{stfloats}
\usepackage[caption=false,font=footnotesize,subrefformat=parens,labelformat=parens]{subfig}
\usepackage{tabularx}
\usepackage{tikz}

% letter signature
\renewcommand*{\raggedsignature}{\raggedright}

% line referencing
\newcommand{\R}[1]{\label{#1}\linelabel{#1}} % use this to set the placement of the line reference tags
\newcommand{\lr}[1]{page~\pageref{#1}, line~\lineref{#1}} % use this to reference the tags (print line numbers)

% quoting
\newcommand\declquotedtext[2]{\expandafter\def\csname quotedtext@#1 \endcsname{#2}} % use around text you may want to quote later, but don't want printed in the main text
\newcommand\defquotedtext[2]{\declquotedtext{#1}{#2}#2} % use around text you want to appear in the main text and that you want to quote later
\newcommand\usequotedtext[1]{\csname quotedtext@#1 \endcsname} % use to print the quoted text
\newcommand{\q}[1]{“#1”} % easier way to get double quotes

\usepackage{geometry}
\usepackage[most]{tcolorbox}

% Colors
\definecolor{lightgray}{rgb}{0.9, 0.9, 0.9}
\definecolor{lightyellow}{rgb}{0.98,0.91,0.71}
\definecolor{lightred}{rgb}{0.8,0.4,0.4}

% Boxes
\newtcolorbox{replybox}{colback=lightgray, grow to right by=-2.5mm, grow to
	left by=-2.5mm, boxrule=0pt, boxsep=0pt, breakable, before skip=10pt}
\newtcolorbox{partialbox}{colback=lightyellow, grow to right by=-2.5mm, grow to
	left by=-2.5mm, boxrule=0pt, boxsep=0pt, breakable, before skip=10pt}
\newtcolorbox{todobox}{colback=lightred, grow to right by=-2.5mm, grow to left
	by=-2.5mm, boxrule=0pt, boxsep=0pt, breakable, before skip=10pt}

% Counters
\newcounter{epntcnt}
\newcounter{rpntcnt}
\newcounter{revcnt}

% Environments
\newenvironment{reviewer}{%
	\refstepcounter{revcnt}%
	\setcounter{rpntcnt}{0}%
	\section*{Reviewer \therevcnt}%
}{}
% Editor environment takes an optional argument
\newenvironment{editor}[1][Editorial Decision]{%
	\setcounter{epntcnt}{0}%
	\section*{#1}%
}{}

% Reply Commands
\newcommand{\reply}[1]{%
	\begin{replybox}%
		#1
	\end{replybox}%
}
\newcommand{\partialreply}[1]{%
	\begin{partialbox}%
		Partial reply: \emph{#1}
	\end{partialbox}%
}
\newcommand{\todoreply}[1]{%
	\begin{todobox}%
		Todo reply: \emph{#1}
	\end{todobox}%
}
\newcommand{\needsreply}{%
	\todoreply{This comment needs a reply.}%
}

% Point command differs depending on the environment
\makeatletter
\newcommand{\point}{%
	\medskip\noindent%
	\def\@tmp{editor}%
	\ifx\@tmp\@currenvir \refstepcounter{epntcnt}\theepntcnt\textbf{.}
	\else%
	\def\@tmp{reviewer}%
	\ifx\@tmp\@currenvir \refstepcounter{rpntcnt}\therpntcnt\textbf{.}
	\else\fi\fi%
}
\makeatother

% Renew the commands for the point counters to get the formatting we want in
% both the references and the item labels.
\renewcommand{\therpntcnt}{\textbf{\textup{\therevcnt.\arabic{rpntcnt}}}}
\renewcommand{\theepntcnt}{\textbf{\textup{E.\arabic{epntcnt}}}}

\setlength\parindent{0pt}
\newcommand{\bft}[1]{\mathbf{#1}}

\begin{document}

\setkomavar{date}{\today}
\setkomavar{signature}{Yang Zhao and Bruno Clerckx}
\setkomavar{subject}{Re: Major revision of manuscript JSAC-SI-ESIT-1570874111}

\begin{letter}{%
		Guest Editors\\
		IEEE Journal on Selected Areas in Communications
	}
	\opening{Dear Editors and Reviewers,}
	Thank you for giving us the opportunity to submit a revised version of ``RIScatter: Unifying Backscatter Communication and Reconfigurable Intelligent Surface''.
	We would like to express our sincere gratitude to you for the valuable comments and suggestions, which helped us improve the quality of the manuscript significantly.
	Below, we prepare a point-to-point response and describe all the changes made to the manuscript.
	We hope that the revisions and clarifications make the manuscript meet the standards of JSAC publications.
	\closing{Yours sincerely,}
\end{letter}

\begin{reviewer}
	This paper introduces the concept of RIScatter, a unified architecture that combines Backscatter Communication (BackCom) and Reconfigurable Intelligent Surface (RIS) technologies, where the scatter nodes can modulate their own information and in the same time manipulate the wireless channel based on the information source, channel state information (CSI), and quality of service (QoS). The achievable primary-total-backscatter rate region in a single-user multi-node RIScatter system is investigated by designing the input distribution at scatter nodes, the active beamforming at the Access Point (AP), and the energy decision regions at the user. Numerical results show that RIScatter nodes can effectively utilize the scattered paths, enabling seamless transitions between backscatter modulation and passive beamforming techniques.

	Although the paper presents a novel idea and tackles an interesting problem, it requires great effort to improve the presentation, the language, and the mathematical derivations. Detailed comments are given as follows:

	\point The abstract and the number of keywords exceed the specified authorized limit. Please check IEEE JSAC guidelines.

	\point The manuscript contains multiple grammatical errors and unclear sentences that require correction. Please revise the manuscript for improved clarity. For instance, in the first paragraph of Section II, Subsection B, the sentence "It is assumed that the signal reflected by two or more times is negligible" is not clear.

	\point Please consider defining all acronyms (e.g., MRC) and all the notations in Section I (e.g., the mutual information, probabilities, etc.,).

	\point Please ensure that all variables and symbols are properly defined and explained before their usage (e.g., $P$, $\sigma_1^2, \ldots, \sigma_L^2$, etc.). Also, $\mathbf{h}_E^H$ in eq. (46) is used without prior definition.

	\point Please ensure consistency with the notation introduced in Section I throughout the manuscript. For instance, in Section II, Subsection B, after eq. (4b), the dimensions for $\mathbb{I}$ are not defined.

	\point To ensure consistency and clarity, please maintain uniformity in the usage of mathematical symbols and technical terms throughout the paper. For example, in eq. (3), the amplitude scattering ratio of the node is defined as $\beta_m$, while in eq. (4a), it is referred to as $\alpha_k$. Additionally, there is a discrepancy in the usage of the term 'node' throughout the manuscript and 'tag' in the appendix. Please use a consistent term to refer to the same entity throughout the entire paper to avoid confusion and improve clarity.

	\point The expression in eq. (1) represents the conjugate of the reflection coefficient, not the reflection coefficient itself.

	\point It is unclear what is meant by relative QoS. Additionally, there is a lack of clarity regarding the derivation of eqs. (17-19) and how the relative QoS of the primary link is incorporated in those equations. The defined expressions should be clearly explained and justified. Please provide additional details and reasoning.

	\point The link between eq. (9) and eq. (25) lacks clarity and misses intermediate steps. Also, the expression of the function Q provided in eq. (25) appears to be independent of the active beamforming `w'.  It is unclear how the derivation of Q with respect to 'w' is performed in this case. Please clarify the relationship between Q and 'w' and provide a clear derivation for better understanding. The same remark about clarity applies to eq. (28) and eq. (33).

	\point Is the BCD algorithm convergent for the optimization problem (20)?

	\point Please write the mathematical expression of eq. (40) properly. Moreover, there appears to be a mistake in the sign of the Lagrangian function of the optimization problem stated in Equation (21). If the optimization problem is intended to be a minimization problem, it should be explicitly mentioned to avoid any ambiguity or confusion.

	\point The expression of the primary achievable rate in eq. (37) seems to be wrong since the primary message is also included in the cascaded channel and cannot be ignored.

	\point In Figure 7, it is unclear why the KKT, PGD, and BCD algorithms are plotted separately since the BCD algorithm encompasses both the KKT and PGD algorithms. If there is a specific reason for displaying them separately, please provide a justification to enhance the understanding of the reader. Additionally, please provide the unit for the weighted sum rate axis.

	\point Is the decoding of the backscatter information based on an energy detector reliable in this case, especially with high-order modulation or large number of scatter nodes? In other words, can the user in practice decode the backscatter information especially in the presence of the noise and signal variations due to the fading or the interference, etc.?

	\point In Section III, the aim is to characterize the primary-total-backscatter rate region where the user retrieves both the backscatter information and the primary message. Why is the weighted sum mutual information maximized with respect to only the input distribution of the backscatter information and not jointly with respect to the input distribution of the primary message `s' as well? In other words, is the choice of $s \sim \mathcal{CN} (0,1)$ optimal?

	\point In Section IV, Subsection B, it is stated that the RIS always ensures constructive superposition of direct and scattered components which is not true. The RIS can also add those components destructively which could be used for example to enhance the physical layer security of a system in the presence of an eavesdropper.
\end{reviewer}

\begin{reviewer}
	The paper studies the achievable rates for both primary transmission and backscatter information, assuming a Gaussian distribution for primary transmission and K tags (with M loads each) and a single source-destination primary link; the authors assume full CSI knowledge and formulate a mutual information maximization problem, with probability distribution of loads per tag as a function to be optimized (in conjunction with beamforming weights for the multi-antenna transmitter and energy thresholds for the energy-based detector for the backscatter information). The problem is non-convex and challenging, and the authors revert to a series of approximations to relax it and offer a solution. The methodology is interesting in two ways: a) the authors do not employ SIC, but instead focus first on the tags' (weak) information signal, since its knowledge renders the detection of the primary information as a simple coherent detection problem, and b) borrow techniques from the discrete memoryless MAC/discrete memoryless thresholding channel literature, in order to calculate the average rate of the backscattered information.

	The authors balance rate of primary transmission with rate of backscattered tags in a unified, user-controlled way and offer comparison results with prior art in the field (e.g., bistatic backscatter, where no primary link information is present, ambient backscatter, symbiotic (cooperative) ambient backscatter and RIS). Of particular importance is the fact that the authors have modeled both small-scale (through Rice) and large-scale (through distance) fading link parameters, typically omitted in many comm theory papers, even though backscattered links are operating in the presence of the much stronger primary link.

	Overall, the methodology and overall presentation is rigorous and deserves further attention. Having said that, the following remarks are offered:

	\point CSI estimation impact: the notion of full and perfect CSI knowledge is a very strong assumption; the authors do point at footnote 4, page 8 (single column version) to CSI estimation literature. However, CSI estimation for ambient backscatter employs several assumptions and simplifications and it is not perfect or ideal. The authors should perhaps study in terms of simulations the impact of imperfect CSI and necessary degrees of freedom (for channel estimation) on the achieved rates, carefully taking into account the tag(s) small SNR as well as the primary link much stronger SNR.

	\point Modeling assumptions: the overall model is based on Gaussian codebooks for the primary link and lack of structural mode for backscattering; the latter is assumed absorbed by the channel parameters (Section II.A), while the tags are assumed with a demodulator/receiver of the primary information; it is also assumed that both full CSI and reflection efficiency parameters $\{\alpha_k\}, k \in \{1, 2, \ldots, K\}$ are known for all tags, while each tag is equipped with a receiver/demodulator (for the primary information). The reviewer believes that the structural mode cannot be absorbed by the channel parameters, since it offers a DC term, while there is no practical way to estimate separately the cascaded channel from the reflection efficiency; moreover, receivers in tags either increase the complexity or reduce the tag's sensitivity, especially when envelope detectors are used (as in Fig. 3). Moreover, the assumption for perfect symbol-level synchronization between tags and source, or the integer ratio between tags and source symbol duration is also very strong. Some discussion on the above is necessary, while some thoughts on non-Gaussian codebooks and how the methodology could be extended is perhaps important.

	\point Independent distributions across tags: (10) assumes independence among distributions of tag loads across tags; IV.D.1 talks about joint nodes encoding; pls clarify. In addition, some more discussion is needed at IV.C and Fig. 9; for $\rho=1$, i.e., primary transmission maximum prioritization, Fig. 9 shows that only one load (out of 4) should be used. The reviewer was puzzled by this. Perhaps, values of the loads used in the simulations and respective reflection coefficients should be explicitly offered, in conjunction with more discussion regarding the wireless channel impact. When the channel changes, one would expect the distribution of the tags' loads to be sensitive on channel statistics.

	\point All simulation results and respective optimization solutions are offered with relatively small number of K and M; some discussion on ways to extend the methodology for larger networks and loads should be helpful.

	\point Finally, the list of references is perhaps incomplete; many references do not include publication venues, while prior art backscatter radio, including coherent as well as non-coherent detection, structural mode, receiverless tags etc., both in terms of theory as well as experimentation, are not given. For example see work that bridges backscatter radio and RIS, including theory and experimental results for any number of tags and loads in the following: "Intelligently Wireless Batteryless RF-Powered Reconfigurable Surface: Theory, Implementation \& Limitations", IEEE Transactions on Wireless Communications (TWC), available as early access in ieeexplore, Nov. 2022, conference version available at IEEE Globecom 2021.
\end{reviewer}

\begin{reviewer}
	This paper introduces the concept of RIScatter, a unified architecture that combines Backscatter Communication (BackCom) and Reconfigurable Intelligent Surface (RIS) technologies, where the scatter nodes can modulate their own information and in the same time manipulate the wireless channel based on the information source, channel state information (CSI), and quality of service (QoS). The achievable primary-total-backscatter rate region in a single-user multi-node RIScatter system is investigated by designing the input distribution at scatter nodes, the active beamforming at the Access Point (AP), and the energy decision regions at the user. Numerical results show that RIScatter nodes can effectively utilize the scattered paths, enabling seamless transitions between backscatter modulation and passive beamforming techniques.

	The manuscript presents a novel concept, i.e., RIScatter, and studies an interesting problem. However, there are several problems with the manuscript, namely:

	\point Literature review: the literature review on rate characterization for backscatter communications is deficient. Some recent and closely related works are missing:
	\begin{itemize}
		\item J. Qian, Y. Zhu, C. He, F. Gao and S. Jin, "Achievable Rate and Capacity Analysis for Ambient Backscatter Communications," in IEEE Transactions on Communications, vol. 67, no. 9, pp. 6299-6310, Sept. 2019.
		\item Z. Dai, R. Li, J. Xu, Y. Zeng and S. Jin, "Rate-Region Characterization and Channel Estimation for Cell-Free Symbiotic Radio Communications," in IEEE Transactions on Communications, vol. 71, no. 2, pp. 674-687, Feb. 2023.
		\item H. E. Hassani, A. Savard, E. V. Belmega and R. C. de Lamare, "Multi-user downlink NOMA systems aided by ambient backscattering: achievable rate regions and energy-efficiency maximization," in IEEE Transactions on Green Communications and Networking, 2023.
	\end{itemize}

	\point Technical aspects: RIScatter is able to balance rate of primary transmission with rate of backscattered tags in a unified, user-controlled way, which brings technical advantages over existing approaches. This reviewer wonders why the authors only considered perfect CSI and did not assessed the impact of imperfect CSI on information rates (not the region!) given the limitations of tags and devices. Moreover, this reviewer is also sceptical about the assumption of perfect synchronization between the tags and the source. Can you explain why this is reasonable?

	\point Simulation results: the authors opted for showing the results in terms of rate regions for several existing schemes and the proposed RISscatter. This is not properly motivated. Could explain why not include results such as information rates versus SNR or BER versus SNR?

	\point Overall, the technical approach of the paper is credible, there is a clear technical contribution although there are aspects related to the use of English and presentation that must be revised.
\end{reviewer}
\end{document}

### 2023-07-27 review/response.tex
:speech_balloon: Update RIScatter principles

@@
 	\point The abstract and the number of keywords exceed the specified authorized limit. Please check IEEE JSAC guidelines.
+	\reply {We apologize for the mistake. The abstract and the number of keywords have been revised to meet the specifications.}
 
@@
 For instance, in the first paragraph of Section II, Subsection B, the sentence "It is assumed that the signal reflected by two or more times is negligible" is not clear.
+	\reply {We have thoroughly revised the manuscript to address the grammatical errors and improve sentence clarity.
+The example sentence has been revised to ``It is assumed that the signal going through two or more RIScatter nodes is too weak to be received by the user.''}
 
 	\point Please consider defining all acronyms (e.g., MRC) and all the notations in Section I (e.g., the mutual information, probabilities, etc.,).
+	\reply {Thank you for the suggestion and we understand it can be very difficult for readers to keep track of all acronyms and notations throughout the paper.
+We tried to add a list of acronyms and notations, but it would violate the 30-page limit and we cannot squeeze enough space from other places.
+Therefore, we decided not to include the list.
+We have ensured that all acronyms are defined before their first usage.}
 

### 2023-07-27 main.tex
:speech_balloon: Update RIScatter principles

--- 2023-03-01 main.tex
@@
 \usepackage{tikz}
-% dark mode
-% \usepackage{xcolor} \pagecolor[rgb]{0,0,0} \color[rgb]{1,1,1}
 
@@
 \begin{document}
-% \title{RIScatter: Unifying Backscatter Communication and Reconfigurable Intelligent Surface From a Distribution Perspective}
-% \title{RIScatter: Unifying Backscatter Communication and Reconfigurable Intelligent Surface}
-% \title{RIScatter: Unifying Backscatter Communication and Reconfigurable Intelligent Surface From State Distribution}
-% \title{RIScatter: Bridging Backscatter Modulation and Passive Beamforming With Adaptive State Distribution}
 \title{RIScatter: Unifying Backscatter Communication and Reconfigurable Intelligent Surface}
@@
 		B. Clerckx is also with Silicon Austria Labs (SAL), Graz A-8010, Austria.
-
-		% This article has been submitted for potential publications.
 	}
@@
 \maketitle
-% TODO why not use metamaterial? because high computational complexity and expectations of freedom (flexibility, reliability)
-% * cooperative input design can be used for co-located RIScatter nodes.
-% * hardward to modulate using RIS is already available.
-% * RIScatter: enhance backscatter signal characteristics (suppress primary interference) or primary signal strength.
-% ? For Backscatter community: why not adaptive channel coding? For RIS community: why not add randomness for modulation?
-% ? RIS involves nonlinear circuits (e.g., diodes) and impedance design (i.e., perfect mismatching) is tricky for continuous phase shift; discrete candidate set is preferred (2-3 bits optimal)
-% * Redefine RIS using book
-% x Using RIS to encode is not very interesting as controller is anyway usable
-% * Wi-Fi sampling rate 20 MHz (symbol period 50 nS), RFID symbol rate/load-switching speed 100s KHz to 10s MHz [Backscatter Communication], fast load-switching speed is key for high data rate - symbol ratio is not very large
-% * Beamforming can cancel direct interference to avoid the collapse of noncoherent energy detection and enlarge energy gap.
-% ?
-[Reconfigurable Intelligent Surface-Assisted Ambient Backscatter Communication Experimental Assessment]the authors of [5] show that, even in line-of-sight (LOS), the interferences and the desired signal can combine in such a way that the received signals at the reader side in the two states are close in power and only differ by their phases
-% TODO Input probability distribution for discrete-value reflection (backscatter), constellation design for continue-value reflection (RIS)
-% * channel coding: non-adaptive (line-coding) or adaptive (DMC)
-% ? [Turbocharging] Since averaging must be done over a significant period of time to smooth out the variation in the TV transmissions, averaging does not allow rates much higher than 10 kbps [24].
-% ? [mu-code]: use multiple Rxs for noncoherent direct interference cancellation (instead of receive diversity)
-% * backscatter modulation <-> passive beamforming; add adaptive channel coding over (NRZ) line coding.
-% ? semi-coherent: known CSI, unknown primary/backscatter symbols
-% * initialization, convergence, base 2 in simulation
-% * SR analysis can achieve large rate at the cost of large N; RIScatter can achieve slightly lower rate at the same N, but also preserves primary performance for smaller N
-% TODO tradeoff between primary (RIScatter, no SIC) and backscatter (SR, SIC)
-% * SR assume very large N for primary rate analysis.
-However, in such cases SIC is questionable as energy detection over received signal as BBC is already good enough and noncoherent detection can also achieve reasonable performance?
-% x when primary symbols are determined, optimal input distribution at high backscatter SNR is equiprobable for any detection (signal/energy)
-% ? Channel estimation error, coordination issues
-
-% * add table row: adaptive to information source/csi/link weights
-% * explain link weights
-% * add table row: distributions
-% * table to sentences
-% * add primary and backscatter flows to illustrations
-% * discuss table and add challenges in contribution 1
-% * transition challenges (distribution and constellation-adaptive) to contribution 2, 3
-% * think RIScatter applications (use Rui's slides)
 
 \begin{abstract}
-	% \gls{bc} nodes harvest energy from and modulate information over an external electromagnetic wave by manipulating the magnitude, phase, and/or frequency of the scattered signal.
-	% \gls{sr} incorporates a passive scatter node into existing radio networks to create additional propagation path and ride its own information towards the cooperative receiver.
-	% \gls{ris} is a programmable reflector array that adapts the phase shift response to enhance or suppress signal strength in specific directions.
-	\gls{bc} nodes harvest energy from and modulate information over an external electromagnetic wave.
-	\gls{ris} adapts its phase shift response to enhance or attenuate channel strength in specific directions.
-	In this paper, we show how those two seemingly different technologies (and their derivatives) can be unified into a single architecture called RIScatter.
-	RIScatter consists of multiple dispersed or co-located scatter nodes, whose reflection states are adapted to partially modulate their own information and partially engineer the wireless channel.
-	% This contrasts with \gls{bc} (resp. \gls{ris}) where the reflection pattern is exclusively a function of the information symbol (resp. \gls{csi}).
-	The key principle is to render the probability distribution of reflection states as a joint function of the information source, \gls{csi}, and \gls{qos} of coexisting active primary and passive backscatter links.
-	This enables RIScatter to softly bridge \gls{bc} and \gls{ris}; boil down to either under specific input distribution; or evolve in a mixed form for heterogeneous traffic control and universal hardware design.
-	% To accommodate the characteristics of active-passive coexisting networks, we propose a practical \gls{sic}-free receiver
-	To reap the benefits of RIScatter, we also propose a co-located \gls{sic}-free receiver that semi-coherently decodes the backscatter information, recovers the reflection pattern, and coherently decodes the primary link.
-	For a single-user multi-node RIScatter network, we characterize the achievable primary-(total-)backscatter rate region by designing the input distribution at scatter nodes, the active beamforming at the \gls{ap}, and the energy decision regions at the user.
-	Simulation results demonstrate RIScatter nodes can exploit the scattered paths to smoothly shift between backscatter modulation and passive beamforming.
+	\gls{bc} nodes harvest energy from and modulate information over external electromagnetic waves.
+	\gls{ris} adapts its phase shift response to alter channel strength in specific directions.
+	In this paper, we show how those two different technologies (and their derivatives) can be unified into one architecture called RIScatter.
+	RIScatter consists of dispersed or co-located scatter nodes, whose reflection states are adapted to partially modulate their information and partially engineer the wireless channel.
+	The key is to render the probability distribution of reflection states as a joint function of the information source, \gls{csi}, and relative priority of coexisting links.
+	This enables RIScatter to softly bridge \gls{bc} and \gls{ris}; reduce to either under specific distribution; or evolve in a mixed form for heterogeneous traffic control and universal hardware design.
+	We also propose a low-complexity \gls{sic}-free receiver that effectively exploits the properties of RIScatter.
+	For a single-user multi-node network, we characterize the achievable primary-(total-)backscatter rate region by optimizing the input distribution at scatter nodes, the active beamforming at the \gls{ap}, and the energy decision regions at the user.
+	Simulations demonstrate RIScatter nodes can recycle surrounding radios for backscatter modulation and passive beamforming.
 \end{abstract}
@@
 \begin{IEEEkeywords}
-	Input distribution design, symbol-level precoding, active-passive coexisting network, \gls{sic}-free receiver, energy detection, backscatter communication, reconfigurable intelligent surface, ambient backscatter communication, symbiotic radio.
+	Backscatter communication, reconfigurable intelligent surface, active-passive coexisting network, input distribution design, \gls{sic}-free receiver.
 \end{IEEEkeywords}
@@
 \begin{section}{Introduction}
-	% \begin{subsection}{Fundamentals}
 	\IEEEPARstart{F}{uture} wireless network is envisioned to provide high throughput, uniform coverage, pervasive connectivity, heterogeneous control, and cognitive intelligence for trillions of low-power devices.
-	% As a mature low-power communication technique,
 	\gls{bc} separates a transmitter into a \gls{rf} carrier emitter with power-hungry elements (e.g., synthesizer and amplifier) and an information-bearing node with power-efficient components (e.g., harvester and modulator) \cite{Boyer2014}.
-	% In particular, the node harvests energy from impinging wave and embeds information over scattered signal, and
 	The receiver (reader) can be either co-located or separated with the carrier emitter, known as \gls{mbc} and \gls{bbc} in Fig.~\subref*{fg:mbc} and \subref*{fg:bbc}, respectively.
@@
 	However, conventional backscatter nodes only respond when externally inquired by a nearby reader.
-	% To tackle this, \cite{Liu2013b} proposed \gls{ambc} where battery-free nodes recycle ambient signals (e.g., radio, television and Wi-Fi) to harvest energy and establish connection in between.
 	\gls{ambc} in Fig.~\subref*{fg:ambc} was proposed a decade ago where battery-free nodes recycle ambient signals (e.g., radio, television and Wi-Fi) to harvest energy and establish connections \cite{Liu2013b}.
 	It does not require dedicated power source, carrier emitter, or frequency spectrum, but the backscatter decoding is subject to the strong interference from the primary (legacy) link.
-	% Cooperative \gls{ambc} that employs a co-located receiver to decode both coexisting links was considered in \cite{Yang2018}, and the rate and error performance are evaluated for various detection schemes.
 	To tackle this, cooperative \gls{ambc} \cite{Yang2018} employs a co-located receiver to decode both coexisting links and the concept was further refined as \gls{sr} in Fig.~\subref*{fg:sr} \cite{Liang2020}.
-	% Specifically, the active transmitter generates \gls{rf} wave carrying primary information, the passive node ride extra information over the scattered signal, and the cooperative receiver jointly, individually, or sequentially decodes both links.
 	Specifically, the active transmitter generates \gls{rf} wave carrying primary information, the passive node creates a rich-scattering environment and rides its own information, and the co-located receiver cooperatively decodes both links.
 	In those \gls{bc} applications, the scatter node is considered as an \emph{information source} and the reflection pattern depends exclusively on the information symbol.
-	% Those \gls{bc} applications employ scatter nodes as pure information sources, and the active primary transmission (if it exists) can be influenced by the randomness of backscatter modulation.
 	On the other hand, \gls{ris} in Fig.~\subref*{fg:ris} is a smart signal reflector with numerous passive elements of adjustable phase shifts.
 	It customizes the wireless environment for signal enhancement, interference suppression, scattering enrichment, and/or non-line-of-sight bypassing \cite{Wu2021b}.
-	Each \gls{ris} element is considered as a \emph{channel adaptor} and the reflection pattern depends exclusively on the \gls{csi}.
-	% In summary, \gls{mbc}/\gls{bbc} (resp.
-\gls{ris}) involves a \emph{single} passive backscatter (resp.
-active primary) link where the passive device modulates information (resp.
-enhances propagation) and the active device generates carrier wave (resp.
-modulated signal).
-	% On the other hand, \gls{ambc} (resp. \gls{sr}) involves \emph{coexisting} active primary and passive backscatter links in a competitive (resp. collaborative) relationship.
-	% In \gls{ambc}, the backscatter link only needs to know the basic information (e.g., operating frequency) of the primary link, while the primary link may be completely unaware of the backscatter link.
-	% In \gls{sr}, relevant \gls{csi} is exploited at the co-located receiver for cooperative decoding, and may also be exploited at the primary transmitter for cooperative active beamforming.
-
-	\begin{figure}[!t]
-		\centering
-		\subfloat[\gls{mbc}]{
-			\resizebox{0.48\linewidth}{!}{
-				\input{assets/illustration/mbc.tex}
-			}
-			\label{fg:mbc}
-		}
-		\subfloat[\gls{bbc}]{
-			\resizebox{0.48\linewidth}{!}{
-				\input{assets/illustration/bbc.tex}
-			}
-			\label{fg:bbc}
-		}
-		\\
-		\subfloat[\gls{ambc}]{
-			\resizebox{0.48\linewidth}{!}{
-				\input{assets/illustration/ambc.tex}
-			}
-			\label{fg:ambc}
-		}
-		\subfloat[\gls{sr}]{
-			\resizebox{0.48\linewidth}{!}{
-				\input{assets/illustration/sr.tex}
-			}
-			\label{fg:sr}
-		}
-		\\
-		\subfloat[\gls{ris}]{
-			\resizebox{0.48\linewidth}{!}{
-				\input{assets/illustration/ris.tex}
-			}
-			\label{fg:ris}
-		}
-		\subfloat[RIScatter]{
-			\resizebox{0.48\linewidth}{!}{
-				\input{assets/illustration/riscatter.tex}
-			}
-			\label{fg:riscatter}
-		}
-		\caption{
-			Illustration of scattering applications.
-			The blue flow(s) constitutes the primary link while the magenta/green flow denotes the backscatter link.
-		}
-		\label{fg:scatter_illustration}
-	\end{figure}
-	% \end{subsection}
-
-	\begin{table*}[!t]
-		\caption{Comparison of Scattering Applications}
-		\label{tb:scattering_applications}
-		\rowcolors{2}{gray!25}{white}
-		\renewcommand{\arraystretch}{1.4}
-		\begin{tabularx}{\textwidth}{CCCCCC}
-			\toprule
-			\hiderowcolors
-			                                       & \gls{mbc}/\gls{bbc} & \gls{ambc}                  & \gls{sr} (large spreading factor)               & \gls{ris}           & RIScatter                                                   \\ \midrule
-			\showrowcolors
-			Information link(s)                    & Backscatter         & Coexisting                  & Coexisting                                      & Primary             & Coexisting                                                  \\
-			Primary signal on backscatter decoding & Carrier             & Multiplicative interference & Spreading code                                  & ---                 & Energy uncertainty                                          \\
-			Backscatter signal on primary decoding & ---                 & Multiplicative interference & \gls{csi} uncertainty                           & Passive beamforming & Dynamic passive beamforming                                 \\
-			Cooperative devices                    & ---                 & No                          & Primary transmitter and co-located receiver     & ---                 & Primary transmitter, scatter nodes, and co-located receiver \\
-			Sequential decoding                    & ---                 & No                          & Primary-to-backscatter, \gls{sic} and \gls{mrc} & ---                 & Backscatter-to-primary, no \gls{sic}/\gls{mrc}              \\
-			% Primary decoding                        & ---                 & Semi-coherent               & Semi-coherent                                   & Coherent            & Coherent                                                    \\
-			% Backscatter decoding                    & Coherent            & Semi-coherent               & Coherent                                        & ---                 & Semi-coherent                                               \\
-			Reflection pattern depends on          & Information source  & Information source          & Information source                              & \gls{csi}           & Information source, \gls{csi}, and \gls{qos}                \\
-			Reflection state distribution          & Equiprobable        & Equiprobable                & Equiprobable or Gaussian                        & Degenerate          & Flexible                                                    \\
-			Load-switching speed                   & Fast                & Slow                        & Slow                                            & Quasi-static        & Arbitrary                                                   \\ \bottomrule
-		\end{tabularx}
-	\end{table*}
-
-	% \begin{subsection}{Related Works}
+	Each \gls{ris} element is considered as a \emph{channel shaper} and the reflection pattern depends exclusively on the \gls{csi}.
+
 	As a special case of \gls{cr}, active and passive transmissions coexist and interplay in \gls{ambc} and \gls{sr}.
@@
 	During primary decoding, the backscatter signal can be modelled as channel uncertainty or multiplicative interference when the spreading factor is large or small, respectively.
-	Decoding each backscatter symbol also requires multiple \gls{sic} followed by a \gls{mrc} and is operation-intensive and \gls{csi}-sensitive.
-	% Such a \gls{sic} receiver is operation-intensive and \gls{csi}-sensitive because it involves $N$ re-encoding, precoding, subtraction together with a time-domain \gls{mrc} to decode each backscatter symbol.
+	Decoding each backscatter symbol also requires multiple \gls{sic} followed by a \gls{mrc} over primary blocks, which is operation-intensive and \gls{csi}-sensitive.
 	When the spreading factor is sufficiently large, the primary achievable rate under semi-coherent detection\footnote{In this paper, semi-coherent detection refers to the primary/backscatter decoding with known \gls{csi} and unknown backscatter/primary symbols.} asymptotically approaches its coherent counterpart and both links are decoded interference-free \cite{Long2020a}.
-	% However, it significantly increases \gls{sic} operations per backscatter symbol and severely limits the backscatter \emph{throughput}.
 	However, this severely limits the backscatter throughput and requires numerous \gls{sic} per backscatter symbol.
 
-	% On the other hand, efficient backscatter multiple access design remains an open issue for \gls{bc}.
-	% \cite{Xu2021a} proposed a \gls{noma}-based \gls{sr} where the \gls{sic} order depends on the backscatter channel strength, but the performance deteriorates fast as the number of nodes increases.
-	% \gls{tdma}-based \gls{sr} was also considered in \cite{Yang2021a} where each node transmits information during its dedicated slot and harvests energy otherwise.
-	% It enables adaptive transmission time and reflection ratio design but introduces extra coordination cost.
-	% \cite{Vougioukas2019} modifies the load-switching speed to shift the scattered signal to the desired frequency band.
-	% This enables backscatter \gls{fdma} at the cost of larger bandwidth and higher power consumption at the scatter nodes.
-	% To reduce the coordination cost, \cite{Han2021} proposed a random code-assisted multiple access for \gls{sr} and evaluated the asymptotic \gls{sinr} using random matrix theory.
-	% This code-domain solution suffers from the near-far problem and imperfect synchronization, both being severe in \gls{bc}.
-
-	% A comparison of scattering applications is summarized in Table~\ref{tb:scattering_applications}.
+	\begin{figure}[!t]
+		\centering
+		\subfloat[\gls{mbc}]{
+			\resizebox{0.48\linewidth}{!}{
+				\input{assets/illustration/mbc.tex}
+			}
+			\label{fg:mbc}
+		}
+		\subfloat[\gls{bbc}]{
+			\resizebox{0.48\linewidth}{!}{
+				\input{assets/illustration/bbc.tex}
+			}
+			\label{fg:bbc}
+		}
+		\\
+		\subfloat[\gls{ambc}]{
+			\resizebox{0.48\linewidth}{!}{
+				\input{assets/illustration/ambc.tex}
+			}
+			\label{fg:ambc}
+		}
+		\subfloat[\gls{sr}]{
+			\resizebox{0.48\linewidth}{!}{
+				\input{assets/illustration/sr.tex}
+			}
+			\label{fg:sr}
+		}
+		\\
+		\subfloat[\gls{ris}]{
+			\resizebox{0.48\linewidth}{!}{
+				\input{assets/illustration/ris.tex}
+			}
+			\label{fg:ris}
+		}
+		\subfloat[RIScatter]{
+			\resizebox{0.48\linewidth}{!}{
+				\input{assets/illustration/riscatter.tex}
+			}
+			\label{fg:riscatter}
+		}
+		\caption{
+			Illustration of scattering applications.
+			The blue flow(s) constitutes the primary link while the magenta/green flow denotes the backscatter link.
+		}
+		\label{fg:scatter_illustration}
+	\end{figure}
+
+	\begin{table*}[!t]
+		\caption{Comparison of Scattering Applications}
+		\label{tb:scattering_applications}
+		\rowcolors{2}{gray!25}{white}
+		\renewcommand{\arraystretch}{1.4}
+		\begin{tabularx}{\textwidth}{CCCCCC}
+			\toprule
+			\hiderowcolors
+			                                       & \glsentryshort{mbc}/\glsentryshort{bbc} & \glsentryshort{ambc}        & \glsentryshort{sr} (large spreading factor)                         & \glsentryshort{ris} & RIScatter                                                          \\ \midrule
+			\showrowcolors
+			Information link(s)                    & Backscatter                             & Coexisting                  & Coexisting                                                          & Primary             & Coexisting                                                         \\
+			Primary signal on backscatter decoding & Carrier                                 & Multiplicative interference & Spreading code                                                      & ---                 & Energy uncertainty                                                 \\
+			Backscatter signal on primary decoding & ---                                     & Multiplicative interference & \glsentryshort{csi} uncertainty                                     & Passive beamforming & Dynamic passive beamforming                                        \\
+			Cooperative devices                    & ---                                     & No                          & Primary transmitter and co-located receiver                         & ---                 & Primary transmitter, scatter nodes, and co-located receiver        \\
+			Sequential decoding                    & ---                                     & No                          & Primary-to-backscatter, \glsentryshort{sic} and \glsentryshort{mrc} & ---                 & Backscatter-to-primary, no \glsentryshort{sic}/\glsentryshort{mrc} \\
+			Reflection pattern depends on          & Information source                      & Information source          & Information source                                                  & \glsentryshort{csi} & Information source, \glsentryshort{csi}, and \glsentryshort{qos}   \\
+			Reflection state distribution          & Equiprobable                            & Equiprobable                & Equiprobable or Gaussian                                            & Degenerate          & Flexible                                                           \\
+			Load-switching speed                   & Fast                                    & Slow                        & Slow                                                                & Quasi-static        & Arbitrary                                                          \\ \bottomrule
+		\end{tabularx}
+	\end{table*}
 
@@
 	Relevant literature also considers either Gaussian codebook \cite{Guo2019b,Ding2020,Long2020a,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Hu2021b} that is impractical for low-power nodes or finite equiprobable inputs \cite{Yang2018,Liang2020,Han2021,Zhang2022,Liu2019d,Bereyhi2020,Xu2020b,Zhang2021d,Hua2022,Basar2020,Ma2020a,Yuan2021,Hu2021a} that does not fully exploit the \gls{csi} and properties of active-passive coexisting networks.
-	% \end{subsection}
 	Those problems are addressed in this paper and the contributions are summarized below.
 
-	% \begin{subsection}{Contributions}
 	\emph{First,} we propose RIScatter as a novel protocol that unifies \gls{bc} and \gls{ris} by adaptive reflection state (backscatter input) distribution design.
-	% \emph{First,} we propose RIScatter as a novel scatter protocol that simultaneously modulates the node information and engineers the wireless channel via adaptive reflection state (backscatter input) distribution design.
 	The concept is shown in Fig.~\subref*{fg:riscatter} where one or more RIScatter nodes ride over an active transmission and simultaneously modulate their information and engineer the wireless channel.
 	A co-located receiver cooperatively decodes both coexisting links and each reflection state simultaneously acts as information and passive beamforming codewords.
-	The reflection pattern of each node is semi-randomly chosen with the guidance of input distribution as a joint function of the information source, \gls{csi}, and \gls{qos}.
+	The reflection pattern of each node is semi-randomly chosen with the guidance of input distribution as a joint function of the information source, \gls{csi}, and \gls{qos}\footnote{\gls{qos} refers to the relative priority of the primary link.}.
 	Such an adaptive channel coding boils down to the degenerate distribution of \gls{ris} when the primary link is prioritized, and outperforms the uniform distribution of \gls{bc} (by accounting the \gls{csi}) when the backscatter link is prioritized.
@@
 	\begin{subsection}{Principles}
-		\gls{rf} wave scattering/reflecting are often manipulated by passive antennas or programmable metamaterial \cite{Liang2022}.
-		% can be described by a unified signal model and implemented by passive antennas or programmable metamaterial \cite{Liang2022}.
-		% An antenna-based scatterer usually consists of an integrated antenna, a load-switching modulator, an energy harvester, and on-chip components (e.g., microcontroller and sensors) \cite{Dobkin2012}.
-		% An antenna-based scatterer usually consists of an integrated antenna, a load-switching modulator, an energy harvester, and on-chip components (e.g., microcontroller and sensors) \cite{Dobkin2012}.
-		The former first receives the impinging signals then reradiates some back to the space and dissipates the remaining \cite{Dobkin2012}.
-		% In comparison, a typical metamaterial-based scatterer comprises an outer metamaterial layer of numerous sub-wavelength metallic/dielectric patches (with tunable permittivity/permeability), a middle copper plate layer that avoids leakage, an inner circuit board layer that adjusts patch responses, and an integrated microcontroller/\glsentryshort{fpga} for coordination and control \cite{Wu2020}.
-		% In comparison, a typical metamaterial-based scatterer comprises an outer metamaterial layer of numerous sub-wavelength metallic/dielectric patches (with tunable permittivity/permeability), a middle copper plate layer that avoids leakage, an inner circuit board layer that adjusts patch responses, and an integrated microcontroller/\glsentryshort{fpga} for coordination and control \cite{Wu2020}.
-		In contrast, the latter reflects the wave at the space-metamaterial boundary without receiving them and mainly applies a phase shift.
-		% In practice, both types of scatterers have {finite} reflection states with non-zero reflection loss.
-		% In general, the scattered signal consists of a structural mode component that consistently contributes to environment multipath and can be modelled within \gls{csi}, and an \emph{antenna} mode component that depends on the impedance mismatch and can be used for backscatter modulation and/or passive beamforming \cite{Hansen1989}.
-		The scattered signal consists of a structural mode component that consistently contributes to environment multipath (usually modelled within \gls{csi}) and an antenna mode component that depends on the impedance mismatch (mainly used for backscatter modulation and/or passive beamforming) \cite{Hansen1989}.
-		% The former is usually modelled within \gls{csi} while the latter is mainly used for backscatter modulation and/or passive beamforming.
+		\gls{rf} wave scattering or reflecting are often manipulated by passive antennas or programmable metamaterial \cite{Liang2022}.
+		The former receives the impinging signals and reradiates some back to the space, while the latter reflects at the space-cell boundary and mainly applies a phase shift.
+		In the scattered signal, the structural mode component depends on the scatterer geometry and material.
+		It is usually modelled as a DC offset \cite{Boyer2014} or part of environment multipath \cite{Thomas2012}.
+		On the other hand, the antenna mode component depends on the impedance mismatch and is widely exploited in scattering applications.
 		For an antenna (resp. metamaterial) scatterer with $M$ reflection states, the reflection coefficient at state $m \in \mathcal{M} \triangleq \{1,\ldots,M\}$ is
@@
 		\end{equation}
-		where $Z_m$ is the antenna load (resp. metamaterial unit) impedance at state $m$ and $Z$ is the antenna input (resp. medium characteristic) impedance.
-
-		\gls{bc} treats scatterers as information sources that \emph{randomly} choosing the reflection state based on information symbol.
-		For $M$-ary \gls{qam}, constellation point $c_m$ maps to reflection coefficient $\Gamma_m$ by \cite{Thomas2012a}
-		\begin{equation}
-			\Gamma_m = \alpha \frac{c_m}{\max_{m'} \lvert c_{m'} \rvert},
+		where $Z_m$ is the antenna load (resp. metamaterial cell) impedance at state $m$, and $Z$ is the antenna input (resp. medium characteristic) impedance.
+		Specifically,
+		\begin{itemize}
+			\item \gls{bc}: The scatterer is an information source with random reflection pattern over time.
+			The reflection coefficient at state $m$ is used merely an information codeword \cite{Thomas2012a}
+			\begin{equation}
+				\Gamma_m = \alpha_m \frac{c_m}{\max_{m'} \lvert c_{m'} \rvert},
 				\label{eq:backscatter_modulation}
 			\end{equation}
-		where $\alpha \in \mathbb{I}$ is the common amplitude scattering ratio at the direction of interest.
-		In contrast, \gls{ris} treats scatterers as channel adaptors that \emph{deterministically} choosing the reflection state based on \gls{csi}.
-		For a \gls{ris} element with $M$ available states, phase shift $\theta_m$ maps to reflection coefficient $\Gamma_m$ by \cite{Wu2018}
-		\begin{equation}
-			\Gamma_m = \beta_m \exp(j \theta_m),
+			where $\alpha_m \in \mathbb{I}$ is the amplitude scattering ratio and $c_m$ is the constellation point.
+			\item \gls{ris}: The scatterer is a channel shaper with deterministic reflection pattern over time.
+			The reflection coefficient at state $m$ is used merely a passive beamforming codeword \cite{Wu2018}
+			\begin{equation}
+				\Gamma_m = \alpha_m \exp(j \theta_m),
 				\label{eq:passive_beamforming}
 			\end{equation}
-		where $\beta_m \in \mathbb{I}$ is the overall amplitude scattering ratio at state $m$.\footnote{Most existing \gls{ris} literature assumes lossless reflection $\beta_m=1$, $\forall m$.}
-		% A natural question is, is it possible to use a scatterer
-		For a scatter node with given load impedance set, \gls{bc} employs $\Gamma_m$ only as an information codeword while \gls{ris} employs $\Gamma_m$ only as a passive beamforming codeword.
-		RIScatter generalizes both from a probabilistic perspective where each node \emph{semi-randomly} chooses the reflection state with the guidance of probability $P(\Gamma_m)$.
-		The input distribution is flexibly designed as a joint function of the information source, \gls{csi}, and \gls{qos} of both links.
-		\gls{bc} and (static) \gls{ris} can be regarded as its extreme cases where the input distribution boils down to uniform and degenerate, respectively.
-		Fig.~\ref{fg:scatter_comparison} compares the input distribution and reflection pattern of RIScatter to \gls{bc} and \gls{ris}.
+			where $\theta_m$ is the phase shift.\footnote{It is commonly assumed $\alpha_m \ll 1$ in \gls{bc} and $\alpha_m=1$ in \gls{ris}.}
+		\end{itemize}
+
+		RIScatter generalizes \gls{bc} and \gls{ris} from a probabilistic perspective.
+		Each reflection coefficient is simultaneously an information codeword and a passive beamforming codeword.
+		As shown in Fig.~\ref{fg:scatter_comparison}, RIScatter nodes semi-randomly choose reflection states according to an input distribution that strikes a balance between backscatter modulation and passive beamforming.
 		\begin{figure}[!t]
@@
 				Shadowing means presence of primary link.
-				In this example, the optimal passive beamformer is state \num{2} and its input probability for RIScatter is \num{0.75}.
-				% RIScatter node transmit symbol \num{1}
-				The spreading factor is \num{4} for RIScatter and \num{8} for \gls{ambc}/\gls{sr}.
+				In this example, the optimal passive beamformer corresponds to state \num{2}, and the spreading factor is \num{4} for RIScatter and \num{8} for \gls{ambc}/\gls{sr}.
+				\gls{bc} and \gls{ris} can be viewed as extreme cases of RIScatter, where the input distribution boils down to uniform and degenerate, respectively.
 			}
@@
 		\begin{remark}
-			RIScatter is different from conventional dynamic passive beamforming since the reflection pattern conveys additional information.
-			% There are many ways to order
-			% The latter only involves time sharing between different states but there are many ways to ensure within a channel block.
-			The latter only involves time sharing between different states and the actual order has no impact on the (ergodic) primary performance.
-			For RIScatter, different state combinations correspond to different messages and the impact reduces to dynamic passive beamforming upon successful backscatter decoding.
-			% However, different combinations correspond to different backscatter messages and RIScatter impact is determined dynamic passive beamforming once successfully decoded.
+			Unlike dynamic \gls{ris} that simply performs a time sharing between reflection states, RIScatter conveys additional information by randomizing the reflection pattern over time while still guaranteeing the probability of occurrence of each state.
+			Upon successful backscatter detection, the impact of RIScatter nodes on the primary link can be modelled as dynamic passive beamforming.
 		\end{remark}
@@
 		\end{figure*}
-		To exploit the benefits of RIScatter, we also propose a practical co-located receiver that semi-coherently decodes the backscatter information, recovers the reflection pattern, and coherently decodes the primary link.
+		To exploit the benefits of RIScatter, we also propose a low-complexity receiver that semi-coherently decodes the backscatter link, recovers the reflection pattern, and coherently decodes the primary link.
 		The detail will be covered in Section~\ref{se:system_model}.
-		% We also propose a practical co-located receiver to exploit the benefits of RIScatter and the detail will be covered in Section~\ref{se:system_model}.
 	\end{subsection}
@@
 		All nodes have $M$ available reflection states.
-		In the primary point-to-point system, the \gls{ap} transmits information to the user over a multipath channel enhanced by RIScatter nodes.
-		In the backscatter multiple access system, the \gls{ap} acts as carrier emitter, the RIScatter nodes modulate over scattered signal, and the user jointly decodes all node messages.
-		For simplicity, we consider a quasi-static block fading model and focus on a specific block where the \gls{csi} remains constant.
-		It is assumed the signal reflected by two or more times is negligible, the primary symbol duration is much longer than multipath delay spread (no inter-symbol interference), and the spreading factor $N$ is a positive integer.
+		In the primary point-to-point system, the \gls{ap} transmits information to the user over a multipath channel\footnote{It is assumed the primary symbol duration is much longer than multipath delay spread (no inter-symbol interference).} enhanced by RIScatter nodes.
+		In the backscatter multiple access system, the \gls{ap} acts as carrier emitter, the RIScatter nodes modulate over scattered signal, and the user jointly decodes all node messages.\footnote{It is assumed that the signal going through two or more RIScatter nodes is too weak to be received by the user.}
+		For simplicity, we consider a quasi-static block fading model and focus on a specific channel block where the \gls{csi} remains constant.
 		Denote the \gls{ap}-user direct channel as $\boldsymbol{h}_{\text{D}}^\mathsf{H} \in \mathbb{C}^{1 \times Q}$, the \gls{ap}-node $k \in \mathcal{K} \triangleq \{1,\ldots,K\}$ forward channel as $\boldsymbol{h}_{\text{F},k}^\mathsf{H} \in \mathbb{C}^{1 \times Q}$, the node $k$-user backward channel as $h_{\text{B},k}$, and the cascaded \gls{ap}-node $k$-user channel as $\boldsymbol{h}_{\text{C},k}^\mathsf{H} \triangleq h_{\text{B},k} \boldsymbol{h}_{\text{F},k}^\mathsf{H} \in \mathbb{C}^{1 \times Q}$.
-		We assume perfect direct and cascaded \gls{csi} are available at the \gls{ap} and the user\footnote{The cascaded \gls{csi} can be estimated by sequential \cite{Bharadia2015,Yang2015b,Guo2019g} or parallel \cite{Jin2021a} approaches for dispersed nodes, or group-based \cite{Zheng2019} or hierarchical \cite{You2019} approaches for co-located nodes.}.
+		We assume the direct and cascaded \gls{csi} are available at the \gls{ap} and user\footnote{The cascaded \gls{csi} can be estimated by sequential \cite{Bharadia2015,Yang2015b,Guo2019g} or parallel \cite{Jin2021a} approaches for dispersed nodes, or group-based \cite{Zheng2019} or hierarchical \cite{You2019} approaches for co-located nodes.}.
+		% It is assumed that the signal going through two or more RIScatter nodes is too weak to be received by the user, the primary symbol duration is much longer than multipath delay spread (no inter-symbol interference), and the spreading factor $N$ is a positive integer.
 		% For dispersed RIScatter nodes, relevant \gls{csi} can be estimated by sequential \cite{Bharadia2015,Yang2015b,Guo2019g} or parallel approaches \cite{Jin2021a} originally proposed for \gls{bc}.
 For co-located RIScatter nodes, the estimation can be simplified by group-based \cite{Zheng2019} and hierarchical \cite{You2019} trainings originally proposed for \gls{ris}.}.
+
 		Let $x_k \in \mathcal{X} \triangleq \{c_1,\ldots,c_M\}$ be the coded backscatter symbol of node $k$ and $x_{\mathcal{K}} \triangleq (x_1,\ldots,x_K)$ be the backscatter symbol tuple of all nodes.
@@
 		where $\alpha_k \in \mathbb{I}$ is the common amplitude scattering ratio of node $k$, $\boldsymbol{\alpha} \triangleq [\alpha_1,\ldots,\alpha_K]^\mathsf{T} \in \mathbb{I}^{K}$, $\boldsymbol{x} \triangleq [x_1,\ldots,x_K]^\mathsf{H} \in \mathcal{X}^{K}$, and $\boldsymbol{H}_{\text{C}} \triangleq [\boldsymbol{h}_{\text{C},1},\ldots,\boldsymbol{h}_{\text{C},K}]^\mathsf{H} \in \mathbb{C}^{K \times Q}$.
+
 		Next, we consider the signal model within one backscatter block.

### 2023-07-28 main.tex
:speech_balloon: Update system model

@@
 \newacronym{bpsphz}{\si{bps/Hz}}{bits per second per Hertz}
+\newacronym{clt}{CLT}{Central Limit Theorem}
 \newacronym{cp}{CP}{Canonical Polyadic}
@@
 	Once the backscatter information is successfully decoded, its contribution can be modelled within composite channel as dynamic passive beamforming (rather than re-precoded and cancelled).
-	It requires only one energy comparison and re-encoding per backscatter symbol and is much efficient than conventional decoding based on \gls{sic} and \gls{mrc}.
+	% It requires only one energy comparison and re-encoding per backscatter symbol and is much efficient than conventional decoding based on \gls{sic} and \gls{mrc}.
+	Such a sequential decoding transforms backscatter modulation into dynamic passive beamforming using only one re-encoding and one energy level comparison per backscatter block.
 	It is also suitable for arbitrary input distribution and spreading factor, which significantly improves backscatter throughput.
@@
 			\item \gls{bc}: The scatterer is an information source with random reflection pattern over time.
-			The reflection coefficient at state $m$ is used merely an information codeword \cite{Thomas2012a}
+			The reflection coefficient is used merely an information codeword \cite{Thomas2012a}
 			\begin{equation}
@@
 			\item \gls{ris}: The scatterer is a channel shaper with deterministic reflection pattern over time.
-			The reflection coefficient at state $m$ is used merely a passive beamforming codeword \cite{Wu2018}
+			The reflection coefficient is used merely a passive beamforming codeword \cite{Wu2018}
 			\begin{equation}
@@
 		RIScatter generalizes \gls{bc} and \gls{ris} from a probabilistic perspective.
-		Each reflection coefficient is simultaneously an information codeword and a passive beamforming codeword.
-		As shown in Fig.~\ref{fg:scatter_comparison}, RIScatter nodes semi-randomly choose reflection states according to an input distribution that strikes a balance between backscatter modulation and passive beamforming.
+		Each reflection coefficient simultaneously acts as an information codeword and a passive beamforming codeword.
+		As shown in Fig.~\ref{fg:scatter_comparison}, RIScatter nodes semi-randomly choose reflection states according to an input distribution, which strikes a balance between backscatter modulation and passive beamforming.
 		\begin{figure}[!t]
@@
 				Shadowing means presence of primary link.
-				In this example, the optimal passive beamformer corresponds to state \num{2}, and the spreading factor is \num{4} for RIScatter and \num{8} for \gls{ambc}/\gls{sr}.
+				In this example, the optimal passive beamformer corresponds to state \num{2}.
+				The spreading factor is \num{4} for RIScatter and \num{8} for \gls{ambc}/\gls{sr}.
 				\gls{bc} and \gls{ris} can be viewed as extreme cases of RIScatter, where the input distribution boils down to uniform and degenerate, respectively.
@@
 
-	% As illustrated in Fig.~\ref{fg:energy_distribution}, conditioned on different reflection state hypotheses, the accumulated energy per backscatter block follows Gamma distribution with different scale parameters \cite{Qian2017b}.
-	% \begin{figure}[!t]
-	% 	\centering
-	% 	\resizebox{0.8\columnwidth}{!}{
-	% 		\input{assets/illustration/energy_distribution.tex}
-	% 	}
-	% 	\caption{
-	% 		\gls{pdf} of accumulated energy per backscatter block conditioned on different reflection state hypotheses.
-	% 		$z$, $t$, $\mathcal{H}$ and $\mathcal{R}$ denote the accumulated energy, decision threshold, reflection state hypothesis, and decision regions, respectively.
-	% 	}
-	% 	\label{fg:energy_distribution}
-	% \end{figure}
-
-	% Hence, the receiver can semi-coherently (under primary uncertainty) decode RIScatter nodes from the accumulated energy, re-encode to recover the reflection patterns, and combine those with cascaded \gls{csi} to determine the multipath response and model within the primary channel.
-	% Such a backscatter-primary decoding enables simultaneous backscatter modulation and dynamic passive beamforming by only one energy comparison and re-encoding during each backscatter (instead of primary) block.
-	% It enjoys a three-fold benefit compared to conventional primary-backscatter decoding with \gls{sic}, namely
-	% 1) reduces the re-encoding frequencies to $1/N$;
-	% 2) requires no re-precoding, cancellation, or \gls{mrc};
-	% 3) preserves backscatter modulation and passive beamforming at smaller spreading factors for potentially higher backscatter throughput.
-
-	% % ! add to signal model
-	% % Importantly, RIScatter system design only requires the \emph{direct} transmitter-receiver and \emph{cascaded} transmitter-scatter-receiver \gls{csi}.
-	% % For dispersed RIScatter nodes, relevant \gls{csi} can be estimated by sequential \cite{Bharadia2015,Yang2015b,Guo2019g} or parallel approaches \cite{Jin2021a} originally proposed for \gls{bc}.
-	% % For co-located RIScatter nodes, the estimation can be simplified by group-based \cite{Zheng2019} and hierarchical \cite{You2019} trainings originally proposed for \gls{ris}.
-
 	\begin{subsection}{System Model}
@@
 			}
-			\caption{A single-user multi-node RIScatter system.}
+			\caption{A single-user multi-node RIScatter network.}
 			\label{fg:riscatter_network}
 		\end{figure}
-		As shown in Fig.~\ref{fg:riscatter_network}, we consider a RIScatter system where a $Q$-antenna \gls{ap} serves a single-antenna user and $K$ nearby dispersed or co-located RIScatter nodes.
+		As shown in Fig.~\ref{fg:riscatter_network}, we consider a RIScatter network where a $Q$-antenna \gls{ap} serves a single-antenna user and $K$ nearby dispersed or co-located RIScatter nodes.
 		All nodes have $M$ available reflection states.
 		In the primary point-to-point system, the \gls{ap} transmits information to the user over a multipath channel\footnote{It is assumed the primary symbol duration is much longer than multipath delay spread (no inter-symbol interference).} enhanced by RIScatter nodes.
-		In the backscatter multiple access system, the \gls{ap} acts as carrier emitter, the RIScatter nodes modulate over scattered signal, and the user jointly decodes all node messages.\footnote{It is assumed that the signal going through two or more RIScatter nodes is too weak to be received by the user.}
+		In the backscatter multiple access system, the \gls{ap} acts as carrier emitter, the RIScatter nodes modulate over scattered signal, and the user jointly decodes all node messages.\footnote{It is assumed the signal going through two or more RIScatter nodes is too weak to be received by the user.}
 		For simplicity, we consider a quasi-static block fading model and focus on a specific channel block where the \gls{csi} remains constant.
@@
 		We assume the direct and cascaded \gls{csi} are available at the \gls{ap} and user\footnote{The cascaded \gls{csi} can be estimated by sequential \cite{Bharadia2015,Yang2015b,Guo2019g} or parallel \cite{Jin2021a} approaches for dispersed nodes, or group-based \cite{Zheng2019} or hierarchical \cite{You2019} approaches for co-located nodes.}.
-		% It is assumed that the signal going through two or more RIScatter nodes is too weak to be received by the user, the primary symbol duration is much longer than multipath delay spread (no inter-symbol interference), and the spreading factor $N$ is a positive integer.
-		% For dispersed RIScatter nodes, relevant \gls{csi} can be estimated by sequential \cite{Bharadia2015,Yang2015b,Guo2019g} or parallel approaches \cite{Jin2021a} originally proposed for \gls{bc}.
-For co-located RIScatter nodes, the estimation can be simplified by group-based \cite{Zheng2019} and hierarchical \cite{You2019} trainings originally proposed for \gls{ris}.}.
-
-		Let $x_k \in \mathcal{X} \triangleq \{c_1,\ldots,c_M\}$ be the coded backscatter symbol of node $k$ and $x_{\mathcal{K}} \triangleq (x_1,\ldots,x_K)$ be the backscatter symbol tuple of all nodes.
-		Due to double modulation, the composite channel is a function of backscatter symbol tuple\footnote{\eqref{eq:equivalent_channel_bc} and \eqref{eq:equivalent_channel_ris} are often used in \gls{bc} and \gls{ris} literature, respectively.}
+
+		Let $\alpha_k \in \mathbb{I}$ be the amplitude scattering ratio of node $k$, $x_k \in \mathcal{X} \triangleq \{c_1,\ldots,c_M\}$ be the coded backscatter symbol of node $k$, and $x_{\mathcal{K}} \triangleq (x_1,\ldots,x_K)$ be the backscatter symbol tuple of all nodes.
+		As a sequence of double modulation, the composite channel is a function of backscatter symbol tuple\footnote{\eqref{eq:equivalent_channel_bc} and \eqref{eq:equivalent_channel_ris} are often used in \gls{bc} and \gls{ris} literature, respectively.}
 		\begin{subequations}
@@
 		\end{subequations}
-		where $\alpha_k \in \mathbb{I}$ is the common amplitude scattering ratio of node $k$, $\boldsymbol{\alpha} \triangleq [\alpha_1,\ldots,\alpha_K]^\mathsf{T} \in \mathbb{I}^{K}$, $\boldsymbol{x} \triangleq [x_1,\ldots,x_K]^\mathsf{H} \in \mathcal{X}^{K}$, and $\boldsymbol{H}_{\text{C}} \triangleq [\boldsymbol{h}_{\text{C},1},\ldots,\boldsymbol{h}_{\text{C},K}]^\mathsf{H} \in \mathbb{C}^{K \times Q}$.
-
-		Next, we consider the signal model within one backscatter block.
-		The signal received by the user at primary block $n \in \mathcal{N} \triangleq \{1,\ldots,N\}$ is
+		where $\boldsymbol{\alpha} \triangleq [\alpha_1,\ldots,\alpha_K]^\mathsf{T} \in \mathbb{I}^{K}$, $\boldsymbol{x} \triangleq [x_1,\ldots,x_K]^\mathsf{H} \in \mathcal{X}^{K}$, and $\boldsymbol{H}_{\text{C}} \triangleq [\boldsymbol{h}_{\text{C},1},\ldots,\boldsymbol{h}_{\text{C},K}]^\mathsf{H} \in \mathbb{C}^{K \times Q}$.
+		Within one backscatter block, the signal received by the user at primary block $n \in \mathcal{N} \triangleq \{1,\ldots,N\}$ is
 		\begin{equation}
@@
 		\end{equation}
-		where $\boldsymbol{w} \in \mathbb{C}^{Q}$ is the active beamformer satisfying average transmit power constraint $\lVert \boldsymbol{w} \rVert^2 \le P$, $s \sim \mathcal{CN}(0,1)$ is the primary symbol, and $v \sim \mathcal{CN}(0,\sigma_v^2)$ is the \gls{awgn} with average power $\sigma_v^2$.
-		Let $m_k \in \mathcal{M} \triangleq \{1,\ldots,M\}$ be the reflection state index of node $k$ and $m_{\mathcal{K}} \triangleq (m_1,\ldots,m_K)$ be the state index tuple of all nodes.
-		% The backscatter symbol $x_k$ (resp.
-symbol tuple $x_{\mathcal{K}}$) is a random variable (resp.
-variable tuple) that takes value $x_{m_k}$ (resp.
-value tuple $x_{m_{\mathcal{K}}}$) when state $m_k$ (resp.
-state tuple $m_{\mathcal{K}}$) is employed.
-		The backscatter symbol tuple $x_{\mathcal{K}}$ is a random variable that takes value $x_{m_{\mathcal{K}}}$ when state tuple $m_{\mathcal{K}}$ is used.
-		Conditioned on hypothesis $\mathcal{H}_{m_{\mathcal{K}}}$, the receive signal per primary block follows \gls{cscg} distribution $\mathcal{CN}(0,\sigma_{m_{\mathcal{K}}}^2)$, where
-		\begin{equation}
-			\sigma_{m_{\mathcal{K}}}^2 = \lvert \boldsymbol{h}^\mathsf{H}(x_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2 + \sigma_v^2
+		where $\boldsymbol{w} \in \mathbb{C}^{Q}$ is the active beamformer satisfying $\lVert \boldsymbol{w} \rVert^2 \le P$, $P$ is the average transmit power budget, $s \sim \mathcal{CN}(0,1)$ is the primary symbol, and $v \sim \mathcal{CN}(0,\sigma_v^2)$ is the \gls{awgn} with variance $\sigma_v^2$.
+
+		Let $m_k \in \mathcal{M} \triangleq \{1,\ldots,M\}$ be the reflection state index of node $k$, and $m_{\mathcal{K}} \triangleq (m_1,\ldots,m_K)$ be the state index tuple of all nodes.
+		The backscatter symbol $x_k$ (resp.
+symbol tuple $x_{\mathcal{K}}$) is a random variable that takes value $x_{m_k}$ (resp.
+value tuple $x_{m_{\mathcal{K}}}$) with probability $p(x_{m_k})$ (resp.
+$p(x_{m_{\mathcal{K}}})$).
+		\begin{remark}
+			Dispersed RIScatter nodes encode independently such that
+			\begin{equation}
+				p(x_{m_{\mathcal{K}}}) = \prod_k p(x_{m_k}).
+				\label{eq:equivalent_distribution}
+			\end{equation}
+			When the nodes are co-located, they can jointly encode by designing $p(x_{m_{\mathcal{K}}})$ directly.
+		\end{remark}
+
+		Let $z=\sum_{n} \bigl\lvert y[n] \bigr\rvert^2$ be the receive energy per backscatter block.
+		When backscatter symbol tuple $x_{m_\mathcal{K}}$ occurs, the receive signal $y$ follows \gls{cscg} distribution $\mathcal{CN}(0,\sigma_{m_{\mathcal{K}}}^2)$ with variance
+		\begin{equation}
+			\sigma_{m_{\mathcal{K}}}^2 = \lvert \boldsymbol{h}^\mathsf{H}(x_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2 + \sigma_v^2,
 			\label{eq:receive_variance}
 		\end{equation}
-		is its variance.
-		Let $z=\sum_{n} \bigl\lvert y[n] \bigr\rvert^2$ be the accumulated energy per backscatter block.
-		Since $z$ is the sum of $N$ \gls{iid} exponential variables, the conditional \gls{pdf} follows Gamma distribution
-		\begin{equation}
-			f(z|\mathcal{H}_{m_{\mathcal{K}}}) = \frac{z^{N-1} \exp(-z/\sigma_{m_{\mathcal{K}}}^2)}{\sigma_{m_{\mathcal{K}}}^{2N} (N-1)!}.
+		and $z$ follows Gamma distribution with conditional \gls{pdf}
+		\begin{equation}
+			f(z|x_{m_{\mathcal{K}}}) = \frac{z^{N-1} \exp(-z/\sigma_{m_{\mathcal{K}}}^2)}{\sigma_{m_{\mathcal{K}}}^{2N} (N-1)!}.
 			\label{eq:energy_distribution}
 		\end{equation}
-		% The receiver first jointly decodes all backscatter messages under primary interference by energy detection.
-		% This essentially formulates a \gls{dmmac} over disjoint energy decision regions.
-		The user first jointly decodes all backscatter messages under primary interference by performing energy detection over disjoint decision regions.
-		For the ease of notation, we map the state index tuple $m_{\mathcal{K}}$ to $l \in \mathcal{L} \triangleq \{1,\ldots,L\}$, where $L \triangleq M^K$ and $\sigma_1^2,\ldots,\sigma_L^2$ forms an increasing sequence.
-		Both notations are used interchangeably in the following context.
-		The decision region of backscatter symbol tuple $l$ is
+
+		\begin{remark}
+			We have assumed Gaussian codebook for the primary source and finite support for the backscatter nodes.
+			The proposed framework is extendable to non-Gaussian primary source, and the conditional \gls{pdf} \eqref{eq:energy_distribution} can be approximated using \gls{clt} for large $N$.
+		\end{remark}
+
+		The user first jointly decodes the backscatter message of all nodes using a low-complexity energy detector.
+		The energy detector formulates a \gls{dmtc} of size $M^K \times M^K$.
+
+		\begin{remark}
+			The capacity-achieving decision region design for \gls{dmtc} with non-binary inputs in arbitrary distribution remains an open issue.
+			It was proved deterministic detectors can be rate-optimal, but non-convex regions (comprise non-adjacent partitions) are generally required and the optimal number of thresholds is unknown \cite{Nguyen2018,Nguyen2021}.
+			Next, we restrict the energy detector to convex deterministic decision regions and consider sequential threshold design.
+		\end{remark}
+
+		Let $L = M^K$ be the number of backscatter symbol tuples.
+		Sort $\{\sigma_{m_{\mathcal{K}}}^2\}$ in ascending order and denote the result sequence as $\sigma_1^2,\ldots,\sigma_L^2$.
+		With sequential thresholding, the decision region of backscatter symbol tuple $l \in \mathcal{L} = \{1,\ldots,L\}$ is\footnote{$m_{\mathcal{K}}$ and $l$ are one-to-one and used interchangeably in the following context.}
 		\begin{equation}
@@
 		\end{equation}
-		where $t_l$ is the energy decision threshold between hypotheses $\mathcal{H}_{l}$ and $\mathcal{H}_{l+1}$.
-		For a given decision threshold vector $\boldsymbol{t} \triangleq [t_0,\ldots,t_L]^\mathsf{T} \in \mathbb{R}_+^{(L+1)}$, we can formulate a \gls{dmmac} with transition probability from input $x_{m_{\mathcal{K}}}$ to output $\hat{x}_{m_{\mathcal{K}}'}$ as
-		\begin{equation}
-			P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}}) = \int_{\mathcal{R}_{m_{\mathcal{K}}'}} f(z|\mathcal{H}_{m_{\mathcal{K}}}) \, d z,
-			\label{eq:dmmac}
-		\end{equation}
-		over which input distribution of all RIScatter nodes can be designed.
-		An example of energy detection is illustrated in Fig.~\ref{fg:energy_distribution}.
-		% Conditioned on different reflection state hypotheses, the accumulated energy per backscatter block follows Gamma distribution with different scale parameters.
+		where $t_l$ is the decision threshold between hypotheses of tuple $x_{l}$ and $x_{l+1}$.
+		An example is shown in Fig.~\ref{fg:energy_distribution}.
+
 		\begin{figure}[!t]
@@
 			\caption{
-				\gls{pdf} of accumulated energy per backscatter block conditioned on different reflection state hypotheses.
+				\gls{pdf} of receive energy per backscatter block conditioned on different reflection state.
 			}
@@
 		\end{figure}
-		\begin{remark}
-			The capacity-achieving decision region design for \gls{dmtc} with non-binary inputs in arbitrary distribution remains an open issue.
-			It was proved deterministic detectors can be rate-optimal, but non-convex decision regions (comprise non-adjacent partitions) are generally required and the optimal number of thresholds remains unknown \cite{Nguyen2018,Nguyen2021}.
-			Hence, we limit the energy detector to convex deterministic decision regions and consider sequential threshold design.
-		\end{remark}
-		After successful backscatter decoding, the user can re-encode for exact reflection pattern and obtain the composite channel by \eqref{eq:equivalent_channel}, then coherently decode the primary link.
-		Such an \gls{sic}-free sequential decoding enables backscatter modulation and dynamic passive beamforming by only one energy comparison and re-encoding per backscatter symbol.
-		It also supports arbitrary input distribution and spreading factor for higher backscatter throughput.
+
+		When the threshold vector $\boldsymbol{t} \triangleq [t_0,\ldots,t_L]^\mathsf{T} \in \mathbb{R}_+^{L+1}$ is given, we can formulate a \gls{dmmac} with transition probability from input $x_{m_{\mathcal{K}}}$ to output $\hat{x}_{m_{\mathcal{K}}'}$ as
+		\begin{equation}
+			q(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}}) = \int_{\mathcal{R}_{m_{\mathcal{K}}'}} f(z|x_{m_{\mathcal{K}}}) \, d z.
+			\label{eq:dmmac}
+		\end{equation}
+		The backscatter mutual information is
+		\begin{equation}
+			I_{\text{B}}(x_{\mathcal{K}};\hat{x}_{\mathcal{K}}) = \sum_{m_{\mathcal{K}}} p(x_{m_{\mathcal{K}}}) I_{\text{B}}(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}}),
+			\label{eq:backscatter_mutual_information}
+		\end{equation}
+		where $I_{\text{B}}(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}})$ is the backscatter information function
+		\begin{equation}
+			I_{\text{B}}(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}}) \triangleq \sum_{m_{\mathcal{K}}'} q(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}}) \log \frac{q(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}})}{p(\hat{x}_{m_{\mathcal{K}}'})}.
+			\label{eq:backscatter_information_function}
+		\end{equation}
+
+		Once the backscatter information is successfully decoded, the user recovers the exact reflection pattern, determines the composite channel by \eqref{eq:equivalent_channel}, and coherently decodes the primary link.
+		The primary mutual information is
+		\begin{equation}
+			I_{\text{P}}(s;y|x_{\mathcal{K}}) = \sum_{m_{\mathcal{K}}} p(x_{m_{\mathcal{K}}}) I_{\text{P}}(s;y|x_{m_{\mathcal{K}}}),
+			\label{eq:primary_mutual_information}
+		\end{equation}
+		where $I_{\text{P}}(s;y|x_{\mathcal{K}})$ is the primary information function
+		\begin{equation}
+			I_{\text{P}}(s;y|x_{m_{\mathcal{K}}}) \triangleq \log \Bigl(1 + \frac{\lvert \boldsymbol{h}^\mathsf{H}(x_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_v^2}\Bigr).
+			\label{eq:primary_information_function}
+		\end{equation}
+
+		% With a slight abuse of notation, we also define the weighed sum-functions
+		% \begin{align}
+		% 	I(x_{m_{\mathcal{K}}})
+		% 	 & \triangleq \rho I_{\text{P}}(s;y|x_{m_{\mathcal{K}}}) + (1 - \rho) I_{\text{B}}(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}}),\label{eq:weighted_sum_information_function} \\
+		% 	I_k(x_{m_k})
+		% 	 & \triangleq \rho I_{\text{P},k}(s;y|x_{m_k}) + (1 - \rho) I_{\text{B},k}(x_{m_k};\hat{x}_{\mathcal{K}}),\label{eq:weighted_sum_marginal_information}                     \\
+		% 	I(x_{\mathcal{K}})
+		% 	 & \triangleq \rho I_{\text{P}}(s;y|x_{\mathcal{K}}) + (1 - \rho) I_{\text{B}}(x_{\mathcal{K}};\hat{x}_{\mathcal{K}}),\label{eq:weighted_sum_mutual_information}
+		% \end{align}
+		% where $\rho \in \mathbb{I}$ is the relative \gls{qos} of the primary link.
 		\label{st:system_model}
@@
 	\begin{subsection}{Achievable Rates}
-		Denote the probability of node $k$ choosing reflection state $m_k$ as $P_k(x_{m_k})$ and let $\boldsymbol{p}_k \triangleq [P_k(c_1),\ldots,P_k(c_M)]^\mathsf{T} \in \mathbb{I}^{M}$.
-		For dispersed nodes with independent encoding, the probability of backscatter symbol tuple $x_{m_{\mathcal{K}}}$ is
-		\begin{equation}
-			P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) = \prod_{k \in \mathcal{K}} P_k(x_{m_k}).
-			\label{eq:equivalent_distribution}
-		\end{equation}
+		% Denote the probability of node $k$ choosing reflection state $m_k$ as $P_k(x_{m_k})$ and let $\boldsymbol{p}_k \triangleq [P_k(c_1),\ldots,P_k(c_M)]^\mathsf{T} \in \mathbb{I}^{M}$.
+		% For dispersed nodes with independent encoding, the probability of backscatter symbol tuple $x_{m_{\mathcal{K}}}$ is
+		% \begin{equation}
+		% 	P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) = \prod_{k \in \mathcal{K}} P_k(x_{m_k}).
+		% 	\label{eq:equivalent_distribution}
+		% \end{equation}
 		Following \cite{Rezaeian2004}, we define the backscatter information function between input value tuple $x_{m_{\mathcal{K}}}$ and output variable tuple $\hat{x}_{\mathcal{K}}$ as
-		\begin{equation}
-			I_{\text{B}}(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}}) \triangleq \sum_{m_{\mathcal{K}}'} P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}}) \log \frac{P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}})}{P_{\mathcal{K}}(\hat{x}_{m_{\mathcal{K}}'})},
-			\label{eq:backscatter_information_function}
-		\end{equation}
+		% \begin{equation}
+		% 	I_{\text{B}}(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}}) \triangleq \sum_{m_{\mathcal{K}}'} P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}}) \log \frac{P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}})}{P_{\mathcal{K}}(\hat{x}_{m_{\mathcal{K}}'})},
+		% 	\label{eq:backscatter_information_function}
+		% \end{equation}
 		where $P_{\mathcal{K}}(\hat{x}_{m_{\mathcal{K}}'}) = \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}})$.
@@
 		Hence, the backscatter mutual information can be written as
-		\begin{equation}
-			I_{\text{B}}(x_{\mathcal{K}};\hat{x}_{\mathcal{K}}) = \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) I_{\text{B}}(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}}).
-			\label{eq:backscatter_mutual_information}
-		\end{equation}
+		% \begin{equation}
+		% 	I_{\text{B}}(x_{\mathcal{K}};\hat{x}_{\mathcal{K}}) = \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) I_{\text{B}}(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}}).
+		% 	\label{eq:backscatter_mutual_information}
+		% \end{equation}
 
@@
 		The primary information function conditioned on $x_{m_{\mathcal{K}}}$ is
-		\begin{equation}
-			I_{\text{P}}(s;y|x_{m_{\mathcal{K}}}) \triangleq \log \Bigl(1 + \frac{\lvert \boldsymbol{h}^\mathsf{H}(x_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_v^2}\Bigr),
-			\label{eq:primary_information_function}
-		\end{equation}
+		% \begin{equation}
+		% 	I_{\text{P}}(s;y|x_{m_{\mathcal{K}}}) \triangleq \log \Bigl(1 + \frac{\lvert \boldsymbol{h}^\mathsf{H}(x_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_v^2}\Bigr),
+		% 	\label{eq:primary_information_function}
+		% \end{equation}
 		the primary marginal information of $x_{m_k}$ is
@@
 		and the average primary mutual information is
-		\begin{equation}
-			I_{\text{P}}(s;y|x_{\mathcal{K}}) = \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) I_{\text{P}}(s;y|x_{m_{\mathcal{K}}}).
-			\label{eq:primary_mutual_information}
-		\end{equation}
+		% \begin{equation}
+		% 	I_{\text{P}}(s;y|x_{\mathcal{K}}) = \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) I_{\text{P}}(s;y|x_{m_{\mathcal{K}}}).
+		% 	\label{eq:primary_mutual_information}
+		% \end{equation}
 
@@
 \begin{section}{Rate-Region Characterization}
-	To characterize the achievable primary-(total-)backscatter rate region for the RIScatter system, we aim to maximize the weighted sum rate with respect to input distribution $\{\boldsymbol{p}_k\}_{k \in \mathcal{K}}$, active beamforming $\boldsymbol{w}$, and decision thresholds $\boldsymbol{t}$ by
+	With a slight abuse of notation, we define the weighed sum mutual information
+	\begin{equation}
+		I(x_{\mathcal{K}}) = \rho I_{\text{P}}(s;y|x_{\mathcal{K}}) + (1 - \rho) I_{\text{B}}(x_{\mathcal{K}};\hat{x}_{\mathcal{K}}),\label{eq:weighted_sum_mutual_information}
+	\end{equation}
+	% \begin{align}
+	% 	I(x_{\mathcal{K}})
+	% 	 & \triangleq \rho I_{\text{P}}(s;y|x_{\mathcal{K}}) + (1 - \rho) I_{\text{B}}(x_{\mathcal{K}};\hat{x}_{\mathcal{K}}),\label{eq:weighted_sum_mutual_information}
+	% 	I(x_{m_{\mathcal{K}}})
+	% 	 & \triangleq \rho I_{\text{P}}(s;y|x_{m_{\mathcal{K}}}) + (1 - \rho) I_{\text{B}}(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}}),\label{eq:weighted_sum_information_function} \\
+	% 	% I_k(x_{m_k})
+	% 	%  & \triangleq \rho I_{\text{P},k}(s;y|x_{m_k}) + (1 - \rho) I_{\text{B},k}(x_{m_k};\hat{x}_{\mathcal{K}}),\label{eq:weighted_sum_marginal_information}                     \\
+	% \end{align}
+	where $\rho \in \mathbb{I}$ is the \gls{qos}.
+	To obtain the achievable primary-(total-)backscatter rate region for the RIScatter network in Fig.~\ref{fg:riscatter_network}, we maximize the weighted sum mutual information with independent encoding at all nodes.\footnote{Joint encoding over multiple nodes formulates an augmented source with larger codebook and can be viewed as its special case.}
+	Denote the input distribution of node $k$ as $\boldsymbol{p}_k = [p(x_{1_k}), \ldots, p(x_{M_k})]^\mathsf{T} \in \mathbb{I}^M$.
+	The problem is formulated as
+	% To characterize the achievable primary-(total-)backscatter rate region for the RIScatter network in Fig.~\ref{fg:riscatter_network}, we aim to maximize the weighted sum mutual information with respect to input distribution $\{\boldsymbol{p}_k\}_{k \in \mathcal{K}}$, active beamforming $\boldsymbol{w}$, and decision thresholds $\boldsymbol{t}$ by
 	\begin{maxi!}
@@
 
-	Problem \eqref{op:weighted_sum_rate} generalizes conventional \gls{bc} by allowing \gls{csi}- and \gls{qos}-adaptive input distribution and decision region design.
-	It also generalizes the discrete \gls{ris} phase shift selection problem by stochastic reflection that relaxes the feasible domain from the vertices of $M$-dimensional probability simplex to the simplex itself.
+	It generalizes conventional \gls{bc} by allowing \gls{csi}- and \gls{qos}-adaptive input distribution and decision region design.
+	On the other hand, it also relaxes the feasible domain of discrete \gls{ris} phase shift selection problem from vertices of $M$-dimensional probability simplex to the simplex itself.
 	Problem \eqref{op:weighted_sum_rate} is highly non-convex and we propose a \gls{bcd} algorithm that iteratively updates $\{\boldsymbol{p}_k\}_{k \in \mathcal{K}}$, $\boldsymbol{w}$ and $\boldsymbol{t}$.
@@
 				\State \phantom{Set} $\sigma^2_{m_{\mathcal{K}}}$, $\forall m_{\mathcal{K}}$ by \eqref{eq:receive_variance}
-				\State \phantom{Set} $f(z|\mathcal{H}_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}$ by \eqref{eq:energy_distribution}
+				\State \phantom{Set} $f(z|x_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}$ by \eqref{eq:energy_distribution}
 				\State \phantom{Set} $P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}, m_{\mathcal{K}}'$ by \eqref{eq:dmmac}
@@
 \begin{section}{Simulation Results}
-	In this section, we provide numerical results to evaluate the proposed input distribution, active beamforming, and backscatter decision designs for the considered RIScatter system.
+	In this section, we provide numerical results to evaluate the proposed input distribution, active beamforming, and backscatter decision designs for the considered RIScatter network.
 	We assume the AP-user distance is \SI{10}{\meter} and at least one RIScatter nodes are randomly dropped in a disk centered at the user with radius $r$.
@@
 	We choose $\gamma_{\text{D}}=2.6$, $\gamma_{\text{F}}=2.4$, $\gamma_{\text{B}}=2$, and $\kappa_{\text{D}}=\kappa_{\text{F}}=\kappa_{\text{B}}=5$ for direct, forward and backward links.
-	The finite decision threshold domain $\mathcal{T}$ is obtained by $b$-bit uniform discretization over the critical interval defined by the confidence bounds of edge hypotheses (i.e., lower bound of $\mathcal{H}_1$ and upper bound of $\mathcal{H}_L$) with confidence $1-\varepsilon$.
+	The finite decision threshold domain $\mathcal{T}$ is obtained by $b$-bit uniform discretization over the critical interval defined by the confidence bounds of edge hypotheses (i.e., lower bound of $x_1$ and upper bound of $x_L$) with confidence $1-\varepsilon$.
 	We set $b=9$ and $\varepsilon=\num{e-3}$.
@@
 			The total backscatter rate of coherent decoding approaches $K \log M$ when $N$ is sufficiently large.
-			% which follows non-zero mean complex Gaussian distribution $\mathcal{CN}\bigl((\boldsymbol{h}_{\text{D}}^\mathsf{H} + \sum_{k} \alpha_k \boldsymbol{h}_{\text{C},k}^\mathsf{H} x_{m_k}) \boldsymbol{w},\sigma_v^2\bigr)$ under hypothesis $\mathcal{H}_{m_{\mathcal{K}}}$.
-			% The corresponding \gls{pdf} of accumulated energy over $N$ primary blocks is
+			% which follows non-zero mean complex Gaussian distribution $\mathcal{CN}\bigl((\boldsymbol{h}_{\text{D}}^\mathsf{H} + \sum_{k} \alpha_k \boldsymbol{h}_{\text{C},k}^\mathsf{H} x_{m_k}) \boldsymbol{w},\sigma_v^2\bigr)$ under hypothesis $x_{m_{\mathcal{K}}}$.
+			% The corresponding \gls{pdf} of receive energy over $N$ primary blocks is
 			% \begin{equation}
-			% 	f^{\text{\gls{bbc}}}(z|\mathcal{H}_{m_{\mathcal{K}}}) = \frac{(z-\mu_{m_{\mathcal{K}}}^{\text{\gls{bbc}}})^{N-1} \exp \bigl(-(z-\mu_{m_{\mathcal{K}}}^{\text{\gls{bbc}}})/\sigma_v^2 \bigr)}{\sigma_v^{2N} (N-1)!},
+			% 	f^{\text{\gls{bbc}}}(z|x_{m_{\mathcal{K}}}) = \frac{(z-\mu_{m_{\mathcal{K}}}^{\text{\gls{bbc}}})^{N-1} \exp \bigl(-(z-\mu_{m_{\mathcal{K}}}^{\text{\gls{bbc}}})/\sigma_v^2 \bigr)}{\sigma_v^{2N} (N-1)!},
 			% 	\label{eq:energy_distribution_bbc}
@@
 			The total backscatter rate of coherent decoding approaches $K \log M$ when $N$ is sufficiently large.
-			% which only involves noise uncertainty under hypothesis $\mathcal{H}_{m_{\mathcal{K}}}$.
+			% which only involves noise uncertainty under hypothesis $x_{m_{\mathcal{K}}}$.
 			% During backscatter detection, the primary symbols $s[1],\ldots,s[N]$ function as a spreading code and the receiver performs \gls{mrc} on $\hat{y}^{\text{\gls{sr}}}[n]$ over $N$ primary blocks.
@@
 		% However, the primary rate benefit
-		% For \gls{bbc} with coherent energy detection, the conditional \gls{pdf} of accumulated energy \eqref{eq:energy_distribution_bbc} is more skewed at a large $N$, such that the equivalent \gls{dmmac} \eqref{eq:dmmac} has lower error probabilities.
+		% For \gls{bbc} with coherent energy detection, the conditional \gls{pdf} of receive energy \eqref{eq:energy_distribution_bbc} is more skewed at a large $N$, such that the equivalent \gls{dmmac} \eqref{eq:dmmac} has lower error probabilities.
 		% For \gls{sic}-based \gls{sr}, the effective backscatter \gls{snr} is increased by $N$ times and the penalty term $\iota$ becomes insignificant.
@@
 			In the low-$\rho$ regime, the proposed \gls{pgd} beamformer significantly outperforms both \gls{mrt} schemes in terms of total backscatter rate.
-			This is because the semi-coherent backscatter decoding relies on the \emph{relative difference} of accumulated energy under different symbol tuples.
+			This is because the semi-coherent backscatter decoding relies on the \emph{relative difference} of receive energy under different symbol tuples.
 			Such an energy diversity is enhanced by \gls{pgd} that effectively exploits backscatter constellation and input distribution knowledge rather than simply maximizing the direct/ergodic \gls{snr}.
@@
 			This is because the double fading effect is less severe for near-far setups.
-			In a multi-user RIScatter system with dispersed nodes, each node may be assigned to the nearest user to guarantee uniformly good performance for both links.
+			In a multi-user RIScatter network with dispersed nodes, each node may be assigned to the nearest user to guarantee uniformly good performance for both links.
 		\end{subsubsection}
@@
 	We also propose a practical \gls{sic}-free receiver that exploits the properties of active-passive coexisting networks to maintain primary benefit and improve backscatter throughput.
-	The achievable primary-total-backscatter rate region is then studied for a single-user multi-node RIScatter system, where the input distribution, active beamforming, and decision thresholds are iteratively updated.
+	The achievable primary-total-backscatter rate region is then studied for a single-user multi-node RIScatter network, where the input distribution, active beamforming, and decision thresholds are iteratively updated.
 	Numerical results not only validated the proposed algorithms but also emphasized the importance of adaptive input distribution and cooperative decoding for both primary and backscatter links.

### 2023-07-29 main.tex
:speech_balloon: Update algorithms and proofs

@@
 \usepackage{booktabs}
+\usepackage[makeroom]{cancel}
 \usepackage[american]{circuitikz}
@@
 \newacronym{pdf}{PDF}{Probability Density Function}
-\newacronym{pgd}{PGD}{Projected Gradient Descent}
+\newacronym{pga}{PGA}{Projected Gradient Ascent}
 \newacronym{psk}{PSK}{Phase Shift Keying}
@@
 	We characterize the achievable primary-(total-)backscatter rate region by optimizing the input distribution at RIScatter nodes, the active beamforming at the \gls{ap}, and the energy decision regions at the user under different \gls{qos}.
-	A \gls{bcd} algorithm is proposed where the \gls{kkt} input distribution is numerically evaluated by limit of sequences, the active beamforming is optimized by \gls{pgd}, and the decision regions are refined by existing sequential quantizer for \gls{dmtc}.
+	A \gls{bcd} algorithm is proposed where the \gls{kkt} input distribution is numerically evaluated by limit of sequences, the active beamforming is optimized by \gls{pga}, and the decision regions are refined by existing sequential quantizer for \gls{dmtc}.
 	Uniquely, we consider \gls{csi}, \gls{qos}, and backscatter constellation in the optimization and the input distribution result is applicable to general detection schemes.
@@
 	% 6) it also supports scatter nodes with faster load-switching speed for potentially higher throughput;
-	% 7) \gls{pgd} active beamformer effectively increases the primary (resp.
+	% 7) \gls{pga} active beamformer effectively increases the primary (resp.
 backscatter) rate by boosting the receive \gls{snr} (resp.
@@
 		Let $z=\sum_{n} \bigl\lvert y[n] \bigr\rvert^2$ be the receive energy per backscatter block.
-		When backscatter symbol tuple $x_{m_\mathcal{K}}$ occurs, the receive signal $y$ follows \gls{cscg} distribution $\mathcal{CN}(0,\sigma_{m_{\mathcal{K}}}^2)$ with variance
+		When $x_{m_\mathcal{K}}$ is transmitted, the receive signal $y$ follows \gls{cscg} distribution $\mathcal{CN}(0,\sigma_{m_{\mathcal{K}}}^2)$ with variance
 		\begin{equation}
@@
 
-		Let $L = M^K$ be the number of backscatter symbol tuples.
+		Let $L = M^K$ be the number of decision regions.
 		Sort $\{\sigma_{m_{\mathcal{K}}}^2\}$ in ascending order and denote the result sequence as $\sigma_1^2,\ldots,\sigma_L^2$.
@@
 		\end{equation}
-		where $t_l$ is the decision threshold between hypotheses of tuple $x_{l}$ and $x_{l+1}$.
+		where $t_l$ is the decision threshold between hypotheses $x_{l}$ and $x_{l+1}$.
 		An example is shown in Fig.~\ref{fg:energy_distribution}.
@@
 		\end{equation}
-		where $I_{\text{P}}(s;y|x_{\mathcal{K}})$ is the primary information function
+		where $I_{\text{P}}(s;y|x_{m_{\mathcal{K}}})$ is the primary information function
 		\begin{equation}
@@
 		\end{equation}
-
-		% With a slight abuse of notation, we also define the weighed sum-functions
-		% \begin{align}
-		% 	I(x_{m_{\mathcal{K}}})
-		% 	 & \triangleq \rho I_{\text{P}}(s;y|x_{m_{\mathcal{K}}}) + (1 - \rho) I_{\text{B}}(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}}),\label{eq:weighted_sum_information_function} \\
-		% 	I_k(x_{m_k})
-		% 	 & \triangleq \rho I_{\text{P},k}(s;y|x_{m_k}) + (1 - \rho) I_{\text{B},k}(x_{m_k};\hat{x}_{\mathcal{K}}),\label{eq:weighted_sum_marginal_information}                     \\
-		% 	I(x_{\mathcal{K}})
-		% 	 & \triangleq \rho I_{\text{P}}(s;y|x_{\mathcal{K}}) + (1 - \rho) I_{\text{B}}(x_{\mathcal{K}};\hat{x}_{\mathcal{K}}),\label{eq:weighted_sum_mutual_information}
-		% \end{align}
-		% where $\rho \in \mathbb{I}$ is the relative \gls{qos} of the primary link.
 		\label{st:system_model}
-	\end{subsection}
-
-	\begin{subsection}{Achievable Rates}
-		% Denote the probability of node $k$ choosing reflection state $m_k$ as $P_k(x_{m_k})$ and let $\boldsymbol{p}_k \triangleq [P_k(c_1),\ldots,P_k(c_M)]^\mathsf{T} \in \mathbb{I}^{M}$.
-		% For dispersed nodes with independent encoding, the probability of backscatter symbol tuple $x_{m_{\mathcal{K}}}$ is
-		% \begin{equation}
-		% 	P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) = \prod_{k \in \mathcal{K}} P_k(x_{m_k}).
-		% 	\label{eq:equivalent_distribution}
-		% \end{equation}
-		Following \cite{Rezaeian2004}, we define the backscatter information function between input value tuple $x_{m_{\mathcal{K}}}$ and output variable tuple $\hat{x}_{\mathcal{K}}$ as
-		% \begin{equation}
-		% 	I_{\text{B}}(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}}) \triangleq \sum_{m_{\mathcal{K}}'} P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}}) \log \frac{P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}})}{P_{\mathcal{K}}(\hat{x}_{m_{\mathcal{K}}'})},
-		% 	\label{eq:backscatter_information_function}
-		% \end{equation}
-		where $P_{\mathcal{K}}(\hat{x}_{m_{\mathcal{K}}'}) = \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}})$.
-		We also define the backscatter marginal information of $x_{m_k}$ as
-		\begin{equation}
-			I_{\text{B},k}(x_{m_k};\hat{x}_{\mathcal{K}}) \triangleq \sum_{m_{\mathcal{K} \setminus \{k\}}} P_{\mathcal{K} \setminus \{k\}}(x_{m_{\mathcal{K} \setminus \{k\}}}) I_{\text{B}}(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}}),
-			\label{eq:backscatter_marginal_information}
-		\end{equation}
-		where $P_{\mathcal{K} \setminus \{k\}}(x_{m_{\mathcal{K} \setminus \{k\}}}) = \prod_{q \in \mathcal{K} \setminus \{k\}} P_{q}(x_{m_{q}})$.
-		Hence, the backscatter mutual information can be written as
-		% \begin{equation}
-		% 	I_{\text{B}}(x_{\mathcal{K}};\hat{x}_{\mathcal{K}}) = \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) I_{\text{B}}(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}}).
-		% 	\label{eq:backscatter_mutual_information}
-		% \end{equation}
-
-		Once nodes are successfully decoded, we can re-encode and determine the composite channel by \eqref{eq:equivalent_channel}.
-		The primary information function conditioned on $x_{m_{\mathcal{K}}}$ is
-		% \begin{equation}
-		% 	I_{\text{P}}(s;y|x_{m_{\mathcal{K}}}) \triangleq \log \Bigl(1 + \frac{\lvert \boldsymbol{h}^\mathsf{H}(x_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_v^2}\Bigr),
-		% 	\label{eq:primary_information_function}
-		% \end{equation}
-		the primary marginal information of $x_{m_k}$ is
-		% the primary marginal information conditioned on letter $x_{m_k}$ of node $k$ as
-		\begin{equation}
-			I_{\text{P},k}(s;y|x_{m_k}) \triangleq \sum_{m_{\mathcal{K} \setminus \{k\}}} P_{\mathcal{K} \setminus \{k\}}(x_{m_{\mathcal{K} \setminus \{k\}}}) I_{\text{P}}(s;y|x_{m_{\mathcal{K}}}),
-			\label{eq:primary_marginal_information}
-		\end{equation}
-		and the average primary mutual information is
-		% \begin{equation}
-		% 	I_{\text{P}}(s;y|x_{\mathcal{K}}) = \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) I_{\text{P}}(s;y|x_{m_{\mathcal{K}}}).
-		% 	\label{eq:primary_mutual_information}
-		% \end{equation}
-
-		With a slight abuse of notation, we define the weighted sum information function, marginal information, and mutual information as
-		\begin{align}
-			I(x_{m_{\mathcal{K}}})
-			 & \triangleq \rho I_{\text{P}}(s;y|x_{m_{\mathcal{K}}}) + (1 - \rho) I_{\text{B}}(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}}),\label{eq:weighted_sum_information_function} \\
-			I_k(x_{m_k})
-			 & \triangleq \rho I_{\text{P},k}(s;y|x_{m_k}) + (1 - \rho) I_{\text{B},k}(x_{m_k};\hat{x}_{\mathcal{K}}),\label{eq:weighted_sum_marginal_information}                     \\
-			I(x_{\mathcal{K}})
-			 & \triangleq \rho I_{\text{P}}(s;y|x_{\mathcal{K}}) + (1 - \rho) I_{\text{B}}(x_{\mathcal{K}};\hat{x}_{\mathcal{K}}),\label{eq:weighted_sum_mutual_information}
-		\end{align}
-		where $\rho \in \mathbb{I}$ is the relative \gls{qos} of the primary link.
-		We notice the average primary rate \eqref{eq:primary_mutual_information} depends on the backscatter input distribution and active beamforming, while the total backscatter rate depends on the input distribution and \gls{dmmac} \eqref{eq:dmmac} that relates to the active beamforming and decision thresholds.
-		\label{st:information_theory}
 	\end{subsection}
@@
 \begin{section}{Rate-Region Characterization}
-	With a slight abuse of notation, we define the weighed sum mutual information
-	\begin{equation}
-		I(x_{\mathcal{K}}) = \rho I_{\text{P}}(s;y|x_{\mathcal{K}}) + (1 - \rho) I_{\text{B}}(x_{\mathcal{K}};\hat{x}_{\mathcal{K}}),\label{eq:weighted_sum_mutual_information}
-	\end{equation}
-	% \begin{align}
-	% 	I(x_{\mathcal{K}})
-	% 	 & \triangleq \rho I_{\text{P}}(s;y|x_{\mathcal{K}}) + (1 - \rho) I_{\text{B}}(x_{\mathcal{K}};\hat{x}_{\mathcal{K}}),\label{eq:weighted_sum_mutual_information}
-	% 	I(x_{m_{\mathcal{K}}})
-	% 	 & \triangleq \rho I_{\text{P}}(s;y|x_{m_{\mathcal{K}}}) + (1 - \rho) I_{\text{B}}(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}}),\label{eq:weighted_sum_information_function} \\
-	% 	% I_k(x_{m_k})
-	% 	%  & \triangleq \rho I_{\text{P},k}(s;y|x_{m_k}) + (1 - \rho) I_{\text{B},k}(x_{m_k};\hat{x}_{\mathcal{K}}),\label{eq:weighted_sum_marginal_information}                     \\
-	% \end{align}
+	With a slight abuse of notation, we define the weighed sum mutual information and information function as
+	\begin{align}
+		I(x_{\mathcal{K}})
+		 & \triangleq \rho I_{\text{P}}(s;y|x_{\mathcal{K}}) + (1 - \rho) I_{\text{B}}(x_{\mathcal{K}};\hat{x}_{\mathcal{K}}),\label{eq:weighted_sum_mutual_information}           \\
+		I(x_{m_\mathcal{K}})
+		 & \triangleq \rho I_{\text{P}}(s;y|x_{m_{\mathcal{K}}}) + (1 - \rho) I_{\text{B}}(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}}),\label{eq:weighted_sum_information_function}
+	\end{align}
 	where $\rho \in \mathbb{I}$ is the \gls{qos}.
-	To obtain the achievable primary-(total-)backscatter rate region for the RIScatter network in Fig.~\ref{fg:riscatter_network}, we maximize the weighted sum mutual information with independent encoding at all nodes.\footnote{Joint encoding over multiple nodes formulates an augmented source with larger codebook and can be viewed as its special case.}
-	Denote the input distribution of node $k$ as $\boldsymbol{p}_k = [p(x_{1_k}), \ldots, p(x_{M_k})]^\mathsf{T} \in \mathbb{I}^M$.
-	The problem is formulated as
-	% To characterize the achievable primary-(total-)backscatter rate region for the RIScatter network in Fig.~\ref{fg:riscatter_network}, we aim to maximize the weighted sum mutual information with respect to input distribution $\{\boldsymbol{p}_k\}_{k \in \mathcal{K}}$, active beamforming $\boldsymbol{w}$, and decision thresholds $\boldsymbol{t}$ by
+	To obtain the achievable primary-(total-)backscatter rate region, we consider the weighted sum mutual information maximization problem with independent encoding at all nodes\footnote{Joint encoding over multiple nodes can be viewed as its special case with an augmented source.}
 	\begin{maxi!}
@@
 		\addConstraint{t_{l-1}}{\le t_l,}{\quad \forall l}{\label{co:sequential_threshold}}
-		\addConstraint{\boldsymbol{t}}{\ge \boldsymbol{0}.}{\label{co:nonnegative_threshold}}
+		\addConstraint{\boldsymbol{t}}{\ge \boldsymbol{0},}{\label{co:nonnegative_threshold}}
 	\end{maxi!}
-
-	It generalizes conventional \gls{bc} by allowing \gls{csi}- and \gls{qos}-adaptive input distribution and decision region design.
+	where $\boldsymbol{p}_k = [p(x_{1_k}), \ldots, p(x_{M_k})]^\mathsf{T} \in \mathbb{I}^M$ is the input distribution of node $k$.
+	Problem \eqref{op:weighted_sum_rate} generalizes \gls{bc} by allowing \gls{csi}- and \gls{qos}-adaptive input distribution and decision region design.
 	On the other hand, it also relaxes the feasible domain of discrete \gls{ris} phase shift selection problem from vertices of $M$-dimensional probability simplex to the simplex itself.
-	Problem \eqref{op:weighted_sum_rate} is highly non-convex and we propose a \gls{bcd} algorithm that iteratively updates $\{\boldsymbol{p}_k\}_{k \in \mathcal{K}}$, $\boldsymbol{w}$ and $\boldsymbol{t}$.
+	The original problem is highly non-convex and we propose a \gls{bcd} algorithm that iteratively updates $\{\boldsymbol{p}_k\}_{k \in \mathcal{K}}$, $\boldsymbol{w}$ and $\boldsymbol{t}$.
 
 	\begin{subsection}{Input Distribution}
-		For any given $\boldsymbol{w}$ and $\boldsymbol{t}$, we can construct the equivalent \gls{dmmac} by \eqref{eq:dmmac} and simplify \eqref{op:weighted_sum_rate} to
+		For any given $\boldsymbol{w}$ and $\boldsymbol{t}$, we can formulate a \gls{dmmac} by \eqref{eq:dmmac} and simplify \eqref{op:weighted_sum_rate} to
 		\begin{maxi!}
@@
 		\end{maxi!}
-		which is convex when $K=1$ or joint encoding\footnote{Joint encoding formulates an equivalent source of $M^K$ codewords, such that one can directly design $P_{\mathcal{K}}(x_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}$ instead of $P_k(x_{m_k})$, $\forall k,m_k$.} over $K>1$ co-located nodes.
-		When the nodes are dispersed, problem \eqref{op:input_distribution} involves product term $\prod_{k \in \mathcal{K}} P_k(x_{m_k})$ and is non-convex.
-		Following \cite{Rezaeian2004}, we first recast the \gls{kkt} conditions to their equivalent forms then propose a numerical method that guarantees those conditions on convergence of sequences.
-		% ? Next, we propose a numerical method that evaluate the \gls{kkt} input distribution by limit of sequences.
-		\begin{remark}
-			As demonstrated in \cite{Buhler2011}, \gls{kkt} conditions are generally necessary but insufficient for total rate maximization of \gls{dmmac}.
-			We will later show by simulation that, for a moderate $K$, the average achievable rate regions of \gls{kkt} and global-optimal input distributions completely coincide with each other.
-			\label{re:input_kkt_distribution}
-		\end{remark}
+		which involves the product term \eqref{eq:equivalent_distribution} and is generally non-convex (unless $K=1$).
+		Following \cite{Rezaeian2004}, we first recast the \gls{kkt} conditions to their equivalent forms, then propose a numerical method that guarantees those conditions on convergence of sequences.
 		\begin{proposition}
@@
 				\begin{alignat}{2}
-					I_k^\star(x_{m_k}) & = I^\star(x_{\mathcal{K}}), \quad   &  & P_k^\star(x_{m_k}) > 0,\label{eq:probable_states} \\
-					I_k^\star(x_{m_k}) & \le I^\star(x_{\mathcal{K}}), \quad &  & P_k^\star(x_{m_k}) = 0.\label{eq:dropped_states}
+					I_k^\star(x_{m_k}) & = I^\star(x_{\mathcal{K}}), \quad   &  & \text{if} \ p^\star(x_{m_k}) > 0,\label{eq:probable_states} \\
+					I_k^\star(x_{m_k}) & \le I^\star(x_{\mathcal{K}}), \quad &  & \text{if} \ p^\star(x_{m_k}) = 0,\label{eq:dropped_states}
 				\end{alignat}
 			\end{subequations}
+			where $I_k(x_{m_k})$ is the weighted sum marginal information
+			\begin{align}
+				I_k(x_{m_k})
+				 & = \sum_{m_{\mathcal{K} \setminus \{k\}}} p(x_{m_{\mathcal{K} \setminus \{k\}}}) I(x_{m_\mathcal{K}}).
+				\label{eq:weighted_sum_marginal_information}
+			\end{align}
 			\label{pr:input_kkt_condition}
@@
 
-		For each RIScatter node, \eqref{eq:probable_states} suggests each probable state should produce the same marginal information (averaged over all states of other nodes) while \eqref{eq:dropped_states} suggests any state with potentially less marginal information should not be used.
+		For each RIScatter node, \eqref{eq:probable_states} suggests each probable state should produce the same marginal information (averaged over all states of other nodes), while \eqref{eq:dropped_states} suggests any state with potentially less marginal information should not be used.
 		\begin{proposition}
@@
 			\begin{equation}
-				P_k^{(r+1)}(x_{m_k}) = \frac{P_k^{(r)}(x_{m_k}) \exp \Bigl( \frac{\rho}{1 - \rho} I_k^{(r)}(x_{m_k}) \Bigr)}{\sum_{m_k'} P_k^{(r)}(x_{m_k'}) \exp \Bigl( \frac{\rho}{1 - \rho} I_k^{(r)}(x_{m_k'}) \Bigr)},
+				p^{(r+1)}(x_{m_k}) = \frac{p^{(r)}(x_{m_k}) \exp \Bigl( \frac{\rho}{1 - \rho} I_k^{(r)}(x_{m_k}) \Bigr)}{\sum_{m_k'} p^{(r)}(x_{m_k'}) \exp \Bigl( \frac{\rho}{1 - \rho} I_k^{(r)}(x_{m_k'}) \Bigr)},
 				\label{eq:input_kkt_solution}
@@
 
-		For \eqref{eq:input_kkt_solution} at iteration $r+1$, the input distribution of node $k$ is updated over $\bigl\{\{\boldsymbol{p}_q^{(r+1)}\}_{q=1}^{k-1},\{\boldsymbol{p}_q^{(r)}\}_{q=k}^{K}\bigr\}$.
+		At iteration $r+1$, the input distribution of node $k$ is updated over $\bigl\{\{\boldsymbol{p}_q^{(r+1)}\}_{q=1}^{k-1},\{\boldsymbol{p}_q^{(r)}\}_{q=k}^{K}\bigr\}$.
 		The \gls{kkt} input distribution design is summarized in Algorithm \ref{al:input_distribution}.
@@
 		\begin{algorithm}[!t]
-			\caption{Numerical \gls{kkt} Input Distribution Evaluation by Limits of Sequence}
+			\caption{\gls{kkt} Input Distribution Evaluation by Limits of Sequence}
 			\label{al:input_distribution}
@@
 				\State \phantom{Set} $f(z|x_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}$ by \eqref{eq:energy_distribution}
-				\State \phantom{Set} $P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}, m_{\mathcal{K}}'$ by \eqref{eq:dmmac}
+				\State \phantom{Set} $q(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}, m_{\mathcal{K}}'$ by \eqref{eq:dmmac}
 				\State Initialize $r \gets 0$
 				\State \phantom{Initialize} $\boldsymbol{p}_k^{(0)} > \boldsymbol{0}$, $\forall k$
-				\State Get $P_{\mathcal{K}}^{(r)}(x_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}$ by \eqref{eq:equivalent_distribution} \label{st:input_distribution_begin}
+				\State Get $p^{(r)}(x_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}$ by \eqref{eq:equivalent_distribution} \label{st:input_distribution_begin}
 				\State \phantom{Get} $I^{(r)}(x_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}$ by \eqref{eq:backscatter_information_function}, \eqref{eq:primary_information_function}, \eqref{eq:weighted_sum_information_function}
-				\State \phantom{Get} $I^{(r)}_k(x_{m_k})$, $\forall k,m_k$ by \eqref{eq:backscatter_marginal_information}, \eqref{eq:primary_marginal_information}, \eqref{eq:weighted_sum_marginal_information}
+				\State \phantom{Get} $I^{(r)}_k(x_{m_k})$, $\forall k,m_k$ by \eqref{eq:weighted_sum_marginal_information}
 				\State \phantom{Get} $I^{(r)}(x_{\mathcal{K}})$ by \eqref{eq:backscatter_mutual_information}, \eqref{eq:primary_mutual_information}, \eqref{eq:weighted_sum_mutual_information} \label{st:input_distribution_end}
@@
 		\end{algorithm}
+
+		\begin{remark}
+			The insufficiency of the \gls{kkt} conditions for problem \eqref{op:input_distribution} implies that the proposed method may not converge to the global-optimal solution.
+			However, simulation results show that the average performance gap is indistinguishable at a moderate $K$.
+			\label{re:input_kkt_distribution}
+		\end{remark}
 	\end{subsection}
@@
 		which is still non-convex due to the integration and entropy terms.
-		To tackle this, we rewrite the \gls{dmmac} transition probability \eqref{eq:dmmac} as a regularized incomplete Gamma function in the series representation \cite[Theorem 3]{Jameson2016}
-		\begin{equation}
-			\begin{gathered}
-				Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr) = \frac{\int_{{t_{l-1}}/{\sigma_{m_{\mathcal{K}}}^2}}^{{t_l}/{\sigma_{m_{\mathcal{K}}}^2}} z^{N-1} \exp(-z) \, d z}{(N-1)!}\\
-				= \exp \Bigl(-\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2}\Bigr) \sum_{n=0}^{N-1} \frac{\bigl(\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2}\bigr)^n}{n!} - \exp \Bigl(-\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr) \sum_{n=0}^{N-1} \frac{\bigl(\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\bigr)^n}{n!}.
-			\end{gathered}
+		Plugging \eqref{eq:energy_distribution} into \eqref{eq:dmmac}, we notice the \gls{dmmac} $q(x_l|x_{m_{\mathcal{K}}})$ can be rewritten as
+		\begin{align}
+			q(x_l|x_{m_{\mathcal{K}}})
+			 & = \frac{\int_{{t_{l-1}}/{\sigma_{m_{\mathcal{K}}}^2}}^{{t_l}/{\sigma_{m_{\mathcal{K}}}^2}} z^{N-1} \exp(-z) \, d z}{(N-1)!} \\
+			 & = Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr)
+		\end{align}
+		where $Q(N, b_1, b_2) \triangleq \int_{b_1}^{b_2} z^{N-1} \exp(-z) / (N - 1)! \, d z$ is the regularized incomplete Gamma function.
+		Its series expansion is given by \cite[Theorem 3]{Jameson2016}
+		\begin{align}
+			Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr)
+			 & = \exp \Bigl(-\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2}\Bigr) \sum_{n=0}^{N-1} \frac{\bigl(\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2}\bigr)^n}{n!} \nonumber \\
+			 & \quad - \exp \Bigl(-\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr) \sum_{n=0}^{N-1} \frac{\bigl(\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\bigr)^n}{n!},
 			\label{eq:regularized_incomplete_gamma}
-		\end{equation}
-		Its gradient with respect to $\boldsymbol{w}^*$ can be derived as
-		\begin{equation}
-			\nabla_{\boldsymbol{w}^*} Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr) = \frac{\boldsymbol{h}(x_{m_{\mathcal{K}}})\boldsymbol{h}^\mathsf{H}(x_{m_{\mathcal{K}}})\boldsymbol{w}}{(\sigma_{m_{\mathcal{K}}}^2)^2} g_{m_{\mathcal{K}}}(t_{l-1},t_l),
+		\end{align}
+		whose gradient with respect to $\boldsymbol{w}^*$ is
+		\begin{align}
+			\nabla_{\boldsymbol{w}^*} Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr)
+			 & = \frac{\boldsymbol{h}(x_{m_{\mathcal{K}}})\boldsymbol{h}^\mathsf{H}(x_{m_{\mathcal{K}}})\boldsymbol{w}}{(\sigma_{m_{\mathcal{K}}}^2)^2} \nonumber \\
+			 & \quad \times \Bigl(g_{m_{\mathcal{K}}}(t_l) - g_{m_{\mathcal{K}}}(t_{l-1})\Bigr),
 			\label{eq:regularized_incomplete_gamma_gradient}
-		\end{equation}
-		where $g_{m_{\mathcal{K}}}(t_{l-1},t_l) \triangleq g_{m_{\mathcal{K}}}(t_l)-g_{m_{\mathcal{K}}}(t_{l-1})$ and
+		\end{align}
+		where
 		\begin{equation}
@@
 		\end{equation}
-		On top of \eqref{eq:regularized_incomplete_gamma} and \eqref{eq:regularized_incomplete_gamma_gradient}, we explicitly express the objective function \eqref{ob:active_beamforming} and its gradient as \eqref{eq:weighted_sum_mutual_information_explicit} and \eqref{eq:weighted_sum_mutual_information_gradient} at the end of page \pageref{eq:weighted_sum_mutual_information_explicit}, respectively.
+		On top of \eqref{eq:regularized_incomplete_gamma} and \eqref{eq:regularized_incomplete_gamma_gradient}, we rewrite $I(x_{\mathcal{K}})$ and $\nabla_{\boldsymbol{w}^*} I(x_{\mathcal{K}})$ as \eqref{eq:weighted_sum_mutual_information_explicit} and \eqref{eq:weighted_sum_mutual_information_gradient} at the end of page \pageref{eq:weighted_sum_mutual_information_explicit}, respectively.
 		\begin{figure*}[!b]
@@
 			\begin{equation}
-				I(x_{\mathcal{K}})=\sum_{m_{\mathcal{K}}}P_{\mathcal{K}}(x_{m_{\mathcal{K}}})\Biggl(\rho\log\Bigl(1+\frac{\lvert\boldsymbol{h}^\mathsf{H}(x_{m_{\mathcal{K}}})\boldsymbol{w}\rvert^2}{\sigma_v^2}\Bigr)+(1-\rho)\sum_l Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr) \log \frac{Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr)}{\sum_{m_{\mathcal{K}}'} P_{\mathcal{K}}(x_{m_{\mathcal{K}}'}) Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}'}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}'}^2}\Bigr)}\Biggr)
+				I(x_{\mathcal{K}})=\sum_{m_{\mathcal{K}}}p(x_{m_{\mathcal{K}}})\Biggl(\rho\log\Bigl(1+\frac{\lvert\boldsymbol{h}^\mathsf{H}(x_{m_{\mathcal{K}}})\boldsymbol{w}\rvert^2}{\sigma_v^2}\Bigr)+(1-\rho)\sum_l Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr) \log \frac{Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr)}{\sum_{m_{\mathcal{K}}'} p(x_{m_{\mathcal{K}}'}) Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}'}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}'}^2}\Bigr)}\Biggr)
 				\label{eq:weighted_sum_mutual_information_explicit}
@@
 				\nabla_{\boldsymbol{w}^*} I(x_{\mathcal{K}})
-				 & = \sum_{m_{\mathcal{K}}}P_{\mathcal{K}}(x_{m_{\mathcal{K}}})\Biggl(\rho\frac{\boldsymbol{h}(x_{m_{\mathcal{K}}})\boldsymbol{h}^\mathsf{H}(x_{m_{\mathcal{K}}})\boldsymbol{w}}{\sigma_{m_{\mathcal{K}}}^2}+(1-\rho)\sum_l\biggl(\log\frac{Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr)}{\sum_{m_{\mathcal{K}}'}P_{\mathcal{K}}(x_{m_{\mathcal{K}}'})Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}'}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}'}^2}\Bigr)}+1\biggr)\nonumber                                                                                   \\
-				 & \qquad \times \nabla_{\boldsymbol{w}^*} Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr)-\frac{Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr)\sum_{m_{\mathcal{K}}'}P_{\mathcal{K}}(x_{m_{\mathcal{K}}'})\nabla_{\boldsymbol{w}^*}Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}'}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}'}^2}\Bigr)}{\sum_{m_{\mathcal{K}}'}P_{\mathcal{K}}(x_{m_{\mathcal{K}}'})Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}'}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}'}^2}\Bigr)}\Biggr)
+				 & = \sum_{m_{\mathcal{K}}}p(x_{m_{\mathcal{K}}})\Biggl(\rho\frac{\boldsymbol{h}(x_{m_{\mathcal{K}}})\boldsymbol{h}^\mathsf{H}(x_{m_{\mathcal{K}}})\boldsymbol{w}}{\sigma_{m_{\mathcal{K}}}^2}+(1-\rho)\sum_l\biggl(\log\frac{Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr)}{\sum_{m_{\mathcal{K}}'}p(x_{m_{\mathcal{K}}'})Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}'}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}'}^2}\Bigr)}+1\biggr)\nonumber                                                                                   \\
+				 & \qquad \times \nabla_{\boldsymbol{w}^*} Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr)-\frac{Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr)\sum_{m_{\mathcal{K}}'}p(x_{m_{\mathcal{K}}'})\nabla_{\boldsymbol{w}^*}Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}'}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}'}^2}\Bigr)}{\sum_{m_{\mathcal{K}}'}p(x_{m_{\mathcal{K}}'})Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}'}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}'}^2}\Bigr)}\Biggr)
 				\label{eq:weighted_sum_mutual_information_gradient}
@@
 		\end{figure*}
-		They allows problem \eqref{op:active_beamforming} to be solved by the \gls{pgd} method, where any unregulated beamformer $\bar{\boldsymbol{w}}$ can be projected onto the feasible domain of average transmit power constraint \eqref{co:transmit_power} by
-		\begin{equation}
-			\boldsymbol{w} = \sqrt{P} \frac{\bar{\boldsymbol{w}}}{\max\bigl(\sqrt{P},\lVert\bar{\boldsymbol{w}}\rVert\bigr)}.
+		Problem \eqref{op:active_beamforming} can thus be solved by the \gls{pga} method.
+		At each iteration $r$, the unregulated active beamformer is updated by
+		\begin{equation}
+			\bar{\boldsymbol{w}}^{(r)} = \boldsymbol{w}^{(r-1)}+\gamma\nabla_{\boldsymbol{w}^*} I^{(r-1)}(x_{\mathcal{K}}),
+			\label{eq:beamforming_gradient_ascent}
+		\end{equation}
+		where $\gamma$ is the step size (refinable by backtracking line search \cite[Section 9.2]{Boyd2004}).
+		Then, $\bar{\boldsymbol{w}}$ is projected onto the feasible domain \eqref{co:transmit_power} to retrieve the active beamformer
+		\begin{equation}
+			\boldsymbol{w} = \frac{\sqrt{P} \bar{\boldsymbol{w}}}{\max\bigl(\sqrt{P},\lVert\bar{\boldsymbol{w}}\rVert\bigr)}.
 			\label{eq:beamforming_projection}
 		\end{equation}
-		The \gls{pgd} active beamforming optimization with step size $\gamma$ refined by \gls{bls} \cite[Section 9.2]{Boyd2004} is summarized in Algorithm \ref{al:active_beamforming}.
+
+		The \gls{pga} active beamforming design is summarized in Algorithm \ref{al:active_beamforming}.
 		\begin{algorithm}[!t]
-			\caption{Iterative Active Beamforming Optimization by \gls{pgd} with \gls{bls}}
+			\caption{Active Beamforming Optimization by \gls{pga}}
 			\label{al:active_beamforming}
@@
 				\State Set $\boldsymbol{h}^\mathsf{H}(x_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}$ by \eqref{eq:equivalent_channel}
-				\State \phantom{Set} $P_{\mathcal{K}}(x_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}$ by \eqref{eq:equivalent_distribution}
+				\State \phantom{Set} $p(x_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}$ by \eqref{eq:equivalent_distribution}
 				\State Initialize $r \gets 0$
@@
 					\State \phantom{Update} $\gamma^{(r)}\gets\gamma$
-					\State \phantom{Update} $\bar{\boldsymbol{w}}^{(r)} \gets \boldsymbol{w}^{(r-1)}+\gamma\nabla_{\boldsymbol{w}^*} I^{(r-1)}(x_{\mathcal{K}})$ \label{st:backtracking_line_search_begin}
+					\State \phantom{Update} $\bar{\boldsymbol{w}}^{(r)}$ by \eqref{eq:beamforming_gradient_ascent} \label{st:backtracking_line_search_begin}
 					\State \phantom{Update} $\boldsymbol{w}^{(r)}$ by \eqref{eq:beamforming_projection}
@@
 		\end{maxi!}
-		which is still non-convex because variable $\boldsymbol{t}$ appears on the limits of integration \eqref{eq:dmmac}.
-		Fortunately, we can further simplify problem \eqref{op:decision_threshold} as a point-to-point rate-optimal quantizer design for a \gls{dcmc}, thanks to Remark \ref{re:backscatter_decision} and \ref{re:augmented_source}.
-
-		\begin{remark}
-			Energy detector design has no impact on the primary achievable rate since the composite channel \eqref{eq:equivalent_channel} can always be reconstructed after backscatter decoding and re-encoding.
-			It suggests any thresholding scheme maximizing the total backscatter rate \eqref{eq:backscatter_mutual_information} is also optimal for problem \eqref{op:decision_threshold}.
-			\label{re:backscatter_decision}
-		\end{remark}
-
-		\begin{remark}
-			In terms of total backscatter rate, the potentially dispersed nodes with known input distribution can be viewed as an equivalent source with tuple codewords.
-			As such, the \gls{dmmac} \eqref{eq:dmmac} becomes a \gls{dmtc} and problem \eqref{op:decision_threshold} reduces to the rate-optimal quantization design for a \gls{dcmc}.
-			\label{re:augmented_source}
-		\end{remark}
-
-		Next, we constrain the feasible domain of problem \eqref{op:decision_threshold} from continuous space $\mathbb{R}_+^{L+1}$ to finite candidate set (i.e., fine-grained discrete energy levels) $\mathcal{T}^{L+1}$.
+		which is still non-convex since $\boldsymbol{t}$ appears on the limits of integration \eqref{eq:dmmac}.
+		Instead of solving it directly, we constrain the feasible domain from continuous space $\mathbb{R}_+^{L+1}$ to discrete candidates (i.e., fine-grained energy levels) $\mathcal{T}^{L+1}$.
+		As shown in Fig.~\ref{fg:discrete_outputs}, grouping adjacent energy bins formulates decision regions.
 		\begin{figure}[!t]
@@
 			}
-			\caption{The decision thresholds are selected from fine-grained discrete energy levels instead of continuous space. Each decision region consists of at least one neighbor energy bins.}
+			\caption{The thresholds are chosen from fine-grained candidates instead of the continuous space. Each decision region consists of at least one bin.}
 			\label{fg:discrete_outputs}
 		\end{figure}
-		As shown in Fig.~\ref{fg:discrete_outputs}, by introducing this extra analog-to-digital conversion, we can group adjacent high-resolution energy bins to construct backscatter decision regions.
-		Thus, problem \eqref{op:decision_threshold} can be recast as
+
+		\begin{remark}
+			The design of the energy detector does not affect the primary achievable rate, since the composite channel \eqref{eq:equivalent_channel} can always be determined after backscatter decoding and re-encoding.
+			This implies that any thresholding maximizing the total backscatter rate is optimal for problem \eqref{op:decision_threshold}.
+			\label{re:backscatter_decision}
+		\end{remark}
+
+		\begin{remark}
+			In terms of total backscatter rate, the nodes can be viewed as an augmented source, and problem \eqref{op:decision_threshold} becomes the rate-optimal quantizer design for \gls{dmtc}.
+			\label{re:augmented_source}
+		\end{remark}
+
+		Thanks to Remark \ref{re:backscatter_decision} and \ref{re:augmented_source}, problem \eqref{op:decision_threshold} can be recast as
 		\begin{maxi!}
@@
 		\end{maxi!}
-		which can be solved by existing rate-optimal sequential quantizer designs for \gls{dmtc}.
-		To obtain global optimal solution, \cite{He2021} started from the quadrangle inequality and proposed a \gls{dp} method accelerated by the \gls{smawk} algorithm with computational complexity $\mathcal{O}\bigl(L^2(\mathrm{card}(\mathcal{T})-L)\bigr)$, while \cite{Nguyen2020a} started from the optimality condition for three neighbor thresholds and presented a traverse-then-bisect algorithm with complexity $\mathcal{O}\bigl(\mathrm{card}(\mathcal{T})L\log(\mathrm{card}(\mathcal{T})L)\bigr)$.
+		whose global optimal solution has been obtained in recent works.
+		\cite{He2021} started from the quadrangle inequality and proposed a \gls{dp} method accelerated by the \gls{smawk} algorithm with computational complexity $\mathcal{O}\bigl(L^2(\mathrm{card}(\mathcal{T})-L)\bigr)$.
+		On the other hand, \cite{Nguyen2020a} started from the optimality condition for three neighbor thresholds and presented a traverse-then-bisect algorithm with complexity $\mathcal{O}\bigl(\mathrm{card}(\mathcal{T})L\log(\mathrm{card}(\mathcal{T})L)\bigr)$.
 		In Section \ref{st:simulation_results}, both schemes will be compared with the \gls{ml} scheme \cite{Qian2019}
@@
 		\end{equation}
-		which is generally suboptimal for problem \eqref{op:decision_threshold} unless all RIScatter nodes are with equiprobable inputs.
+		which is suboptimal for problem \eqref{op:decision_threshold} unless all nodes are with equiprobable inputs.
 	\end{subsection}
@@
 
-			In Fig.~\ref{fg:wsr_convergence}, we plot the weighted sum of primary and total backscatter rates at $\rho=0$ for \gls{kkt}, \gls{pgd} and \gls{bcd} algorithms on the first call.
+			In Fig.~\ref{fg:wsr_convergence}, we plot the weighted sum of primary and total backscatter rates at $\rho=0$ for \gls{kkt}, \gls{pga} and \gls{bcd} algorithms on the first call.
 			For $K=8$ and $M=2$, Algorithm \ref{al:input_distribution} typically takes around \num{100} fast iterations to converge to the \gls{kkt} input distribution.
@@
 			\begin{itemize}
-				\item \emph{Cooperation:} Joint nodes encoding using a $K$-dimensional probability array $P_{\mathcal{K}}(x_{m_{\mathcal{K}}})$ by Algorithm \ref{al:input_distribution};
+				\item \emph{Cooperation:} Joint nodes encoding using a $K$-dimensional probability array $p(x_{m_{\mathcal{K}}})$ by Algorithm \ref{al:input_distribution};
 				\item \emph{Exhaustion:} Exhaustive search over the $M$-dimensional probability simplex with resolution $\Delta p = \num{e-2}$;
@@
 			\begin{itemize}
-				\item \emph{\gls{pgd}:} Iterative \gls{pgd} optimization by Algorithm \ref{al:active_beamforming};
-				\item \emph{E-\gls{mrt}:} \gls{mrt} towards the ergodic composite channel $\sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) \boldsymbol{h}^\mathsf{H}(x_{m_{\mathcal{K}}})$;
+				\item \emph{\gls{pga}:} Iterative \gls{pga} optimization by Algorithm \ref{al:active_beamforming};
+				\item \emph{E-\gls{mrt}:} \gls{mrt} towards the ergodic composite channel $\sum_{m_{\mathcal{K}}} p(x_{m_{\mathcal{K}}}) \boldsymbol{h}^\mathsf{H}(x_{m_{\mathcal{K}}})$;
 				\item \emph{D-\gls{mrt}:} \gls{mrt} towards the direct channel $\boldsymbol{h}_{\text{D}}^\mathsf{H}$.
@@
 			Fig.~\subref*{fg:region_beamforming} presents the average achievable rate regions for those schemes.
-			In the low-$\rho$ regime, the proposed \gls{pgd} beamformer significantly outperforms both \gls{mrt} schemes in terms of total backscatter rate.
+			In the low-$\rho$ regime, the proposed \gls{pga} beamformer significantly outperforms both \gls{mrt} schemes in terms of total backscatter rate.
 			This is because the semi-coherent backscatter decoding relies on the \emph{relative difference} of receive energy under different symbol tuples.
-			Such an energy diversity is enhanced by \gls{pgd} that effectively exploits backscatter constellation and input distribution knowledge rather than simply maximizing the direct/ergodic \gls{snr}.
-			As $\rho$ increases, the primary equivalent \gls{snr} outweighs the backscatter energy difference in \eqref{eq:weighted_sum_mutual_information_explicit} and \gls{pgd} beamformer becomes closer to both \gls{mrt} schemes.
-			At $\rho=1$, both \gls{pgd} and E-\gls{mrt} boil down to \gls{mrt} towards the composite channel.
+			Such an energy diversity is enhanced by \gls{pga} that effectively exploits backscatter constellation and input distribution knowledge rather than simply maximizing the direct/ergodic \gls{snr}.
+			As $\rho$ increases, the primary equivalent \gls{snr} outweighs the backscatter energy difference in \eqref{eq:weighted_sum_mutual_information_explicit} and \gls{pga} beamformer becomes closer to both \gls{mrt} schemes.
+			At $\rho=1$, both \gls{pga} and E-\gls{mrt} boil down to \gls{mrt} towards the composite channel.
 			The difference between E-\gls{mrt} and D-\gls{mrt} is insignificant when RIScatter nodes are dispersed.
-			Those observations prove the proposed \gls{pgd} active beamforming design can exploit the \gls{csi}, \gls{qos}, and backscatter constellation to balance the primary equivalent \gls{snr} and backscatter energy difference and enlarge the achievable rate region.
+			Those observations prove the proposed \gls{pga} active beamforming design can exploit the \gls{csi}, \gls{qos}, and backscatter constellation to balance the primary equivalent \gls{snr} and backscatter energy difference and enlarge the achievable rate region.
 		\end{subsubsection}
@@
 			Fig.~\subref*{fg:region_txs} illustrates the impact of transmit antennas $Q$ on the average performance.
-			As $Q$ increases, more scattered paths are available to \gls{pgd} and the channel diversity can be further exploited to enhance the primary equivalent \gls{snr} and backscatter energy difference, which enlarges the achievable rate region.
-			It emphasizes the importance of multi-antenna RIScatter systems and demonstrate the effectiveness of the proposed \gls{pgd} design.
+			As $Q$ increases, more scattered paths are available to \gls{pga} and the channel diversity can be further exploited to enhance the primary equivalent \gls{snr} and backscatter energy difference, which enlarges the achievable rate region.
+			It emphasizes the importance of multi-antenna RIScatter systems and demonstrate the effectiveness of the proposed \gls{pga} design.
 		\end{subsubsection}
@@
 	\begin{subsection}{Proof of Proposition \ref{pr:input_kkt_condition}}
-		Denote the Lagrange multipliers associated with \eqref{co:sum_probability} and \eqref{co:nonnegative_probability} as $\{\nu_k\}_{k \in \mathcal{K}}$ and $\{\lambda_{k,m_k}\}_{k \in \mathcal{K},m_k \in \mathcal{M}}$, respectively.
+		Denote the Lagrange multipliers associated with \eqref{co:sum_probability} and \eqref{co:nonnegative_probability} as $\{\nu_k\}_{k \in \mathcal{K}}$ and $\{\lambda_{m_k}\}_{k \in \mathcal{K},m_k \in \mathcal{M}}$, respectively.
 		The Lagrangian function of problem \eqref{op:input_distribution} is
 		\begin{equation}
-			- I(x_{\mathcal{K}}) + \sum_k \nu_k \biggl( \sum_{m_k} P_k(x_{m_k}) - 1 \biggr) - \sum_k \sum_{m_k} \lambda_{k,m_k} P_k(x_{m_k})
+			I(x_{\mathcal{K}}) + \sum_k \nu_k \biggl( \sum_{m_k} p(x_{m_k}) - 1 \biggr) + \sum_k \sum_{m_k} \lambda_{m_k} p(x_{m_k})
 		\end{equation}
@@
 			\label{eq:input_kkt_condition_original}
-			\begin{equation}
-				- \nabla_{P_k^\star(x_{m_k})} I^\star(x_{\mathcal{K}}) + \nu_k^\star - \lambda_{k,m_k}^\star = 0,
-			\end{equation}
-			\begin{equation}
-				\lambda_{k,m_k}^\star = 0, \quad P_k^\star(x_{m_k}) > 0,
-			\end{equation}
-			\begin{equation}
-				\lambda_{k,m_k}^\star \ge 0, \quad P_k^\star(x_{m_k}) = 0,
-			\end{equation}
+			\begin{gather}
+				I_k^\star(x_{m_k}) - (1 - \rho) + \nu_k^\star + \lambda_{m_k}^\star = 0, \label{eq:input_kkt_condition_1} \\
+				\lambda_{m_k}^\star = 0, \quad    \text{if} \ p^\star(x_{m_k}) > 0, \label{eq:input_kkt_condition_2} \\
+				\lambda_{m_k}^\star \ge 0, \quad  \text{if} \ p^\star(x_{m_k}) = 0 \label{eq:input_kkt_condition_3}.
+			\end{gather}
 		\end{subequations}
-		where directional derivative is explicitly written as
-		\begin{equation}
-			\nabla_{P_k^\star(x_{m_k})} I^\star(x_{\mathcal{K}}) = I_k^\star(x_{m_k}) - (1 - \rho).
-			\label{eq:input_directional_derivative}
-		\end{equation}
-		Combining \eqref{eq:input_kkt_condition_original} and \eqref{eq:input_directional_derivative}, we have
+		Plugging \eqref{eq:input_kkt_condition_2} and \eqref{eq:input_kkt_condition_3} into \eqref{eq:input_kkt_condition_1} yields
 		\begin{subequations}
@@
 			\begin{alignat}{2}
-				I_k^\star(x_{m_k}) & = \nu_k^\star + (1 - \rho), \quad   &  & P_k^\star(x_{m_k}) > 0,\label{eq:probable_states_marginal} \\
-				I_k^\star(x_{m_k}) & \le \nu_k^\star + (1 - \rho), \quad &  & P_k^\star(x_{m_k}) = 0,\label{eq:dropped_states_marginal}
+				I_k^\star(x_{m_k}) & = 1 - \rho - \nu_k^\star, \quad   &  & \text{if} \ p^\star(x_{m_k}) > 0,\label{eq:probable_states_marginal} \\
+				I_k^\star(x_{m_k}) & \le 1 - \rho - \nu_k^\star, \quad &  & \text{if} \ p^\star(x_{m_k}) = 0,\label{eq:dropped_states_marginal}
 			\end{alignat}
@@
 		\begin{equation}
-			\sum_{m_k} P_k^\star(x_{m_k}) I_k^\star(x_{m_k}) = \nu_k^\star + (1 - \rho).
+			\sum_{m_k} p^\star(x_{m_k}) I_k^\star(x_{m_k}) = 1 - \rho - \nu_k^\star.
 			\label{eq:input_kkt_condition_implied}
@@
 		\begin{equation}
-			\sum_{m_k} P_k^\star(x_{m_k}) I_k^\star(x_{m_k}) = I^\star(x_{\mathcal{K}}),
+			\sum_{m_k} p^\star(x_{m_k}) I_k^\star(x_{m_k}) = I^\star(x_{\mathcal{K}}),
 			\label{eq:weighted_sum_marginal_information_implied}
@@
 		We first prove sequence \eqref{eq:input_kkt_solution} is non-decreasing in weighted sum mutual information.
-		Let $P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) = \prod_{q \in \mathcal{K}} P_q(x_{m_q})$ and $P_{\mathcal{K}}'(x_{m_{\mathcal{K}}}) = P_k'(x_{m_k}) \prod_{q \in \mathcal{K} \setminus \{k\}} P_q(x_{m_q})$ be two probability distributions with potentially different marginal for tag $k$ at state $m_k$, and define an intermediate function $J \bigl( P_{\mathcal{K}}(x_{m_{\mathcal{K}}}),P_{\mathcal{K}}'(x_{m_{\mathcal{K}}}) \bigr)$ as \eqref{eq:intermediate_information_function} at the end of page \pageref{eq:intermediate_information_function}.
+		Let $p(x_{m_{\mathcal{K}}}) = \prod_{q \in \mathcal{K}} p(x_{m_q})$ and $p'(x_{m_{\mathcal{K}}}) = p'(x_{m_k}) \prod_{q \in \mathcal{K} \setminus \{k\}} p(x_{m_q})$ be two distributions potentially different at $x_{m_k}$,
+		and $J \bigl(p(x_{m_{\mathcal{K}}}),p'(x_{m_{\mathcal{K}}}) \bigr)$ be a joint function defined in \eqref{eq:intermediate_information_function} at the end of page \pageref{eq:intermediate_information_function}.
 		\begin{figure*}[!b]
@@
 			\begin{equation}
-				J \bigl( P_{\mathcal{K}}(x_{m_{\mathcal{K}}}),P_{\mathcal{K}}'(x_{m_{\mathcal{K}}}) \bigr) \triangleq \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}})
-				\Biggl( \rho \log \Bigl(1 + \frac{\lvert \boldsymbol{h}^\mathsf{H}(x_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_v^2}\Bigr) + (1 - \rho) \sum_{m_{\mathcal{K}}'} P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}}) \log \frac{P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}}) P_{\mathcal{K}}'(x_{m_{\mathcal{K}}})}{P_{\mathcal{K}}'(\hat{x}_{m_{\mathcal{K}}'}) P_{\mathcal{K}}(x_{m_{\mathcal{K}}})} \Biggr).
+				J \bigl( p(x_{m_{\mathcal{K}}}),p'(x_{m_{\mathcal{K}}}) \bigr) \triangleq \sum_{m_{\mathcal{K}}} p(x_{m_{\mathcal{K}}})
+				\Biggl( \rho \log \Bigl(1 + \frac{\lvert \boldsymbol{h}^\mathsf{H}(x_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_v^2}\Bigr) + (1 - \rho) \sum_{m_{\mathcal{K}}'} q(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}}) \log \frac{q(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}}) p'(x_{m_{\mathcal{K}}})}{p'(\hat{x}_{m_{\mathcal{K}}'}) p(x_{m_{\mathcal{K}}})} \Biggr).
 				\label{eq:intermediate_information_function}
@@
 		\end{figure*}
-		It is straightforward to verify $J \bigl( P_{\mathcal{K}}(x_{m_{\mathcal{K}}}),P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) \bigr) = I(x_{\mathcal{K}})$ and $J \bigl( P_{\mathcal{K}}(x_{m_{\mathcal{K}}}),P_{\mathcal{K}}'(x_{m_{\mathcal{K}}}) \bigr)$ is a concave function for a fixed $P_{\mathcal{K}}'(x_{m_{\mathcal{K}}})$.
-		Setting $\nabla_{P_k^\star(x_{m_k})} J \bigl( P_{\mathcal{K}}(x_{m_{\mathcal{K}}}),P_{\mathcal{K}}'(x_{m_{\mathcal{K}}}) \bigr) = 0$, we have
-		\begin{equation}
-			S_k'(x_{m_k}) - S_k'(x_{i_k}) + (1 - \rho) \log \frac{P_k(x_{i_k})}{P_k^\star(x_{m_k})} = 0,
+		It is straightforward to verify $J \bigl( p(x_{m_{\mathcal{K}}}),p(x_{m_{\mathcal{K}}}) \bigr) = I(x_{\mathcal{K}})$ and $J \bigl( p(x_{m_{\mathcal{K}}}),p'(x_{m_{\mathcal{K}}}) \bigr)$ is a concave function for a given $p'(x_{m_{\mathcal{K}}})$.
+		Setting $\nabla_{p(x_{m_k})} J \bigl( p(x_{m_{\mathcal{K}}}),p'(x_{m_{\mathcal{K}}}) \bigr) = 0$ yields
+		\begin{equation}
+			S_k'(x_{m_k}) - S_k'(x_{i_k}) + (1 - \rho) \log \frac{p(x_{i_k})}{p^\star(x_{m_k})} = 0,
 			\label{eq:optimal_intermediate_information_condition}
@@
 			S_k'(x_{m_k})
-			 & \triangleq I_k'(x_{m_k}) + (1 - \rho) \sum_{m_{\mathcal{K} \setminus \{k\}}} P_{\mathcal{K} \setminus \{k\}}(x_{m_{\mathcal{K} \setminus \{k\}}})\nonumber \\
-			 & \quad \times \sum_{m_{\mathcal{K}}'} P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}}) \log P_{\mathcal{K}}'(x_{m_{\mathcal{K}}}).
+			 & \triangleq I_k'(x_{m_k}) + (1 - \rho) \sum_{m_{\mathcal{K} \setminus \{k\}}} p(x_{m_{\mathcal{K} \setminus \{k\}}})\nonumber \\
+			 & \quad \times \sum_{m_{\mathcal{K}}'} q(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}}) \log p'(x_{m_{\mathcal{K}}}).
 		\end{align}
@@
 		\begin{equation}
-			P_k^\star(x_{m_k}) = \frac{P_k'(x_{m_k}) \exp \Bigl( \frac{\rho}{1 - \rho} I_k'(x_{m_k}) \Bigr)}{\sum_{m_k'} P_k'(x_{m_k'}) \exp \Bigl( \frac{\rho}{1 - \rho} I_k'(x_{m_k'}) \Bigr)}.
+			p^\star(x_{m_k}) = \frac{p'(x_{m_k}) \exp \Bigl( \frac{\rho}{1 - \rho} I_k'(x_{m_k}) \Bigr)}{\sum_{m_k'} p'(x_{m_k'}) \exp \Bigl( \frac{\rho}{1 - \rho} I_k'(x_{m_k'}) \Bigr)}.
 			\label{eq:optimal_relative_distribution}
 		\end{equation}
-		Since $P_k(x_{i_k}) = 1 - \sum_{m_k \ne i_k} P_k^\star(x_{m_k})$ has exactly the same form as \eqref{eq:optimal_relative_distribution}, the choice of reference state $i_k$ does not matter and \eqref{eq:optimal_relative_distribution} is indeed optimal $\forall m_k \in \mathcal{M}$.
-		That is, for a fixed $P_{\mathcal{K}}'(x_{m_{\mathcal{K}}})$, choosing $P_k(x_{m_k})$ by \eqref{eq:optimal_relative_distribution} ensures
-		\begin{equation}
-			J \bigl( P_{\mathcal{K}}(x_{m_{\mathcal{K}}}),P_{\mathcal{K}}'(x_{m_{\mathcal{K}}}) \bigr) \ge I'(x_{\mathcal{K}}).
+		Since $p(x_{i_k}) = 1 - \sum_{m_k \ne i_k} p^\star(x_{m_k})$ has exactly the same form as \eqref{eq:optimal_relative_distribution}, the choice of reference does not matter and \eqref{eq:optimal_relative_distribution} is optimal $\forall m_k \in \mathcal{M}$.
+		That is, for a fixed $p'(x_{m_{\mathcal{K}}})$, \eqref{eq:optimal_relative_distribution} ensures
+		\begin{equation}
+			J \bigl( p(x_{m_{\mathcal{K}}}),p'(x_{m_{\mathcal{K}}}) \bigr) \ge I'(x_{\mathcal{K}}).
 			\label{eq:information_difference_lower}
 		\end{equation}
-		On the other hand, we also have
+		On the other hand, we notice
+		% \begin{subequations}
+		% 	\label{eq:information_difference_upper}
+		% 	\begin{align}
+		% 		\Delta
+		% 		 & \triangleq I(x_{\mathcal{K}}) - J \bigl( p(x_{m_{\mathcal{K}}}),p'(x_{m_{\mathcal{K}}}) \bigr)                                                                                                          \\
+		% 		 & = (1 - \rho) \sum_{m_k} \frac{p'(x_{m_k}) f_k'(x_{m_k})}{\sum_{m_k'} p'(x_{m_k'}) f_k'(x_{m_k'})} \sum_{m_{\mathcal{K}}''} q(\hat{x}_{m_{\mathcal{K}}''}|x_{m_k})\nonumber                              \\
+		% 		 & \quad \times \log \frac{\sum_{m_k'} p'(x_{m_k'}) q(\hat{x}_{m_{\mathcal{K}}''}|x_{m_k'}) f_k'(x_{m_k})}{\sum_{m_k'} p'(x_{m_k'}) q(\hat{x}_{m_{\mathcal{K}}''}|x_{m_k'}) f_k'(x_{m_k'})}                \\
+		% 		 & \ge (1 - \rho) \sum_{m_k} \frac{p'(x_{m_k}) f_k'(x_{m_k})}{\sum_{m_k'} p'(x_{m_k'}) f_k'(x_{m_k'})} \sum_{m_{\mathcal{K}}''} q(\hat{x}_{m_{\mathcal{K}}''}|x_{m_k})\nonumber                            \\
+		% 		 & \quad \times \Biggl( 1 - \frac{\sum_{m_k'} p'(x_{m_k'}) q(\hat{x}_{m_{\mathcal{K}}''}|x_{m_k'}) f_k'(x_{m_k'})}{\sum_{m_k'} p'(x_{m_k'}) q(\hat{x}_{m_{\mathcal{K}}''}|x_{m_k'}) f_k'(x_{m_k})} \Biggr) \\
+		% 		 & = 0,
+		% 	\end{align}
+		% \end{subequations}
 		\begin{subequations}
+			\allowdisplaybreaks
 			\label{eq:information_difference_upper}
 			\begin{align}
-				\Delta
-				 & \triangleq I(x_{\mathcal{K}}) - J \bigl( P_{\mathcal{K}}(x_{m_{\mathcal{K}}}),P_{\mathcal{K}}'(x_{m_{\mathcal{K}}}) \bigr)                                                                                  \\
-				 & = (1 - \rho) \sum_{m_k} \frac{P_k'(x_{m_k}) f_k'(x_{m_k})}{\sum_{m_k'} P_k'(x_{m_k'}) f_k'(x_{m_k'})} \sum_{m_{\mathcal{K}}''} P(\hat{x}_{m_{\mathcal{K}}''}|x_{m_k})\nonumber                              \\
-				 & \quad \times \log \frac{\sum_{m_k'} P_k'(x_{m_k'}) P(\hat{x}_{m_{\mathcal{K}}''}|x_{m_k'}) f_k'(x_{m_k})}{\sum_{m_k'} P_k'(x_{m_k'}) P(\hat{x}_{m_{\mathcal{K}}''}|x_{m_k'}) f_k'(x_{m_k'})}                \\
-				 & \ge (1 - \rho) \sum_{m_k} \frac{P_k'(x_{m_k}) f_k'(x_{m_k})}{\sum_{m_k'} P_k'(x_{m_k'}) f_k'(x_{m_k'})} \sum_{m_{\mathcal{K}}''} P(\hat{x}_{m_{\mathcal{K}}''}|x_{m_k})\nonumber                            \\
-				 & \quad \times \Biggl( 1 - \frac{\sum_{m_k'} P_k'(x_{m_k'}) P(\hat{x}_{m_{\mathcal{K}}''}|x_{m_k'}) f_k'(x_{m_k'})}{\sum_{m_k'} P_k'(x_{m_k'}) P(\hat{x}_{m_{\mathcal{K}}''}|x_{m_k'}) f_k'(x_{m_k})} \Biggr) \\
+				 & I(x_{\mathcal{K}}) - J \bigl( p(x_{m_{\mathcal{K}}}),p'(x_{m_{\mathcal{K}}}) \bigr)                                                                                                                    \nonumber           \\
+				 & = (1 - \rho) \sum_{m_k} \frac{p'(x_{m_k}) f_k'(x_{m_k})}{\sum_{m_k'} p'(x_{m_k'}) f_k'(x_{m_k'})} \sum_{m_{\mathcal{K}}''} q(\hat{x}_{m_{\mathcal{K}}''}|x_{m_k})                                      \nonumber           \\
+				 & \quad \times \log \frac{\sum_{m_k'} p'(x_{m_k'}) q(\hat{x}_{m_{\mathcal{K}}''}|x_{m_k'}) f_k'(x_{m_k})}{\sum_{m_k'} p'(x_{m_k'}) q(\hat{x}_{m_{\mathcal{K}}''}|x_{m_k'}) f_k'(x_{m_k'})}                                   \\
+				 & \ge (1 - \rho) \sum_{m_k} \frac{p'(x_{m_k}) f_k'(x_{m_k})}{\sum_{m_k'} p'(x_{m_k'}) f_k'(x_{m_k'})} \sum_{m_{\mathcal{K}}''} q(\hat{x}_{m_{\mathcal{K}}''}|x_{m_k})                                    \nonumber           \\
+				 & \quad \times \Biggl( 1 - \frac{\sum_{m_k'} p'(x_{m_k'}) q(\hat{x}_{m_{\mathcal{K}}''}|x_{m_k'}) f_k'(x_{m_k'})}{\sum_{m_k'} p'(x_{m_k'}) q(\hat{x}_{m_{\mathcal{K}}''}|x_{m_k'}) f_k'(x_{m_k})} \Biggr)                    \\
+				 & = (1 - \rho) \Biggl( 1 - \sum_{m_k} \frac{p'(x_{m_k}) \cancel{f_k'(x_{m_k})}}{\sum_{m_k'} p'(x_{m_k'}) f_k'(x_{m_k'})} \sum_{m_{\mathcal{K}}''} q(\hat{x}_{m_{\mathcal{K}}''}|x_{m_k})                 \nonumber           \\
+				 & \quad \times \frac{\sum_{m_k'} p'(x_{m_k'}) q(\hat{x}_{m_{\mathcal{K}}''}|x_{m_k'}) f_k'(x_{m_k'})}{\sum_{m_k'} p'(x_{m_k'}) q(\hat{x}_{m_{\mathcal{K}}''}|x_{m_k'}) \cancel{f_k'(x_{m_k})}} \Biggr)                       \\
+				 & = (1 - \rho) \Biggl( 1 - \sum_{m_{\mathcal{K}}''} \frac{\cancel{\sum_{m_k} p'(x_{m_k}) q(\hat{x}_{m_{\mathcal{K}}''}|x_{m_k})}}{\sum_{m_k'} p'(x_{m_k'}) f_k'(x_{m_k'})}                                        \nonumber  \\
+				 & \quad \times \frac{\sum_{m_k'} p'(x_{m_k'}) q(\hat{x}_{m_{\mathcal{K}}''}|x_{m_k'}) f_k'(x_{m_k'})}{\cancel{\sum_{m_k'} p'(x_{m_k'}) q(\hat{x}_{m_{\mathcal{K}}''}|x_{m_k'})}} \Biggr)                                     \\
+				 & = (1 - \rho) \Biggl( 1 - \frac{\sum_{m_k'} p'(x_{m_k'}) f_k'(x_{m_k'}) \sum_{m_{\mathcal{K}}''} q(\hat{x}_{m_{\mathcal{K}}''}|x_{m_k'})}{\sum_{m_k'} p'(x_{m_k'}) f_k'(x_{m_k'})} \Biggr)                        \nonumber \\
 				 & = 0,
@@
 		\end{subequations}
-		where $f_k'(x_{m_k}) \triangleq \exp \bigl( \frac{\rho}{1 - \rho} I_k'(x_{m_k}) \bigr)$ and the equality holds if and only if \eqref{eq:optimal_relative_distribution} converges.
+		where $f_k'(x_{m_k}) \triangleq \exp \bigl( \frac{\rho}{1 - \rho} I_k'(x_{m_k}) \bigr)$ and the equality holds if and only if $p(x_{m_{\mathcal{K}}})$ and $p'(x_{m_{\mathcal{K}}})$ equals (i.e., \eqref{eq:optimal_relative_distribution} converges).
 		\eqref{eq:information_difference_lower} and \eqref{eq:information_difference_upper} together imply $I(x_{\mathcal{K}}) \ge I'(x_{\mathcal{K}})$.
-		Since mutual information is bounded above, we conclude the sequence \eqref{eq:input_kkt_solution} is non-decreasing and convergent in mutual information.
-
-		Next, we prove any converging point of sequence \eqref{eq:input_kkt_solution}, denoted as $P_k^\star(x_{m_k})$, fulfills \gls{kkt} conditions \eqref{eq:input_kkt_condition}.
-		To see this, let
-		\begin{equation}
-			D_k^{(r)}(x_{m_k}) \triangleq \frac{P_k^{(r+1)}(x_{m_k})}{P_k^{(r)}(x_{m_k})} = \frac{f_k^{(r)}(x_{m_k})}{\sum_{m_k'} P_k^{(r)}(x_{m_k'}) f_k^{(r)}(x_{m_k'})}.
-		\end{equation}
-		As sequence \eqref{eq:input_kkt_solution} is convergent, any state with $P_k^\star(x_{m_k}) > 0$ need to satisfy $D_k^\star(x_{m_k}) \triangleq \lim_{r \to \infty} D_k^{(r)}(x_{m_k}) = 1$, namely
-		\begin{equation}
-			I_k^\star(x_{m_k}) = \frac{1 - \rho}{\rho} \log \sum_{m_k'} P_k^\star(x_{m_k'}) f_k^\star(x_{m_k'}),
-		\end{equation}
-		which is reminiscent of \eqref{eq:probable_states_marginal} and \eqref{eq:probable_states}.
-		That is, given $P_k^{(0)}(x_{m_k}) > 0$, any converging point with $P_k^\star(x_{m_k}) > 0$ must satisfy \eqref{eq:probable_states}.
-		On the other hand, we assume $P_k^\star(x_{m_k})$ does not satisfy \eqref{eq:dropped_states}, such that for any state with $P_k^\star(x_{m_k}) = 0$,
-		\begin{equation}
-			I_k^\star(x_{m_k}) > I^\star(x_{\mathcal{K}}) = \sum_{m_k'} P_k^\star(x_{m_k'}) I_k^\star(x_{m_k'}),
-		\end{equation}
-		where the equality inherits from \eqref{eq:weighted_sum_mutual_information}.
-		Since the exponential function is monotonically increasing, we have $f_k^\star(x_{m_k}) > \sum_{m_k'} P_k^\star(x_{m_k'}) f_k^\star(x_{m_k'})$ and $D_k^\star(x_{m_k}) > 1$.
-		Considering $P_k^{(0)}(x_{m_k}) > 0$ and $P_k^\star(x_{m_k}) = 0$, it contradicts with
-		\begin{equation}
-			P_k^{(r)}(x_{m_k}) = P_k^{(0)}(x_{m_k}) \prod_{n=1}^r D_k^{(n)}(x_{m_k}).
-		\end{equation}
-		That is, given $P_k^{(0)}(x_{m_k}) > 0$, any converging point with $P_k^\star(x_{m_k}) = 0$ must satisfy \eqref{eq:dropped_states}.
-		The proof is thus completed.
+		Since mutual information is bounded above, we conclude the sequence \eqref{eq:input_kkt_solution} is non-decreasing and convergent.
+
+		Next, we prove any converging point of sequence \eqref{eq:input_kkt_solution}, denoted as $p^\star(x_{m_k})$, fulfills \gls{kkt} conditions \eqref{eq:input_kkt_condition}.
+		Let
+		\begin{equation}
+			D^{(r)}(x_{m_k}) \triangleq \frac{p^{(r+1)}(x_{m_k})}{p^{(r)}(x_{m_k})} = \frac{f_k^{(r)}(x_{m_k})}{\sum_{m_k'} p^{(r)}(x_{m_k'}) f_k^{(r)}(x_{m_k'})}.
+		\end{equation}
+		As sequence \eqref{eq:input_kkt_solution} is convergent, any state with $p^\star(x_{m_k}) > 0$ need to satisfy $D^\star(x_{m_k}) \triangleq \lim_{r \to \infty} D^{(r)}(x_{m_k}) = 1$, namely
+		\begin{equation}
+			I_k^\star(x_{m_k}) = \frac{1 - \rho}{\rho} \log \sum_{m_k'} p^\star(x_{m_k'}) \exp \Bigl( \frac{\rho}{1 - \rho} I_k^\star(x_{m_k'}) \Bigr),
+		\end{equation}
+		The right-hand side is a constant for node $k$ and implies \eqref{eq:probable_states_marginal}.
+		That is, any converging point with nonzero probability must satisfy \eqref{eq:probable_states}.
+		On the other hand, we assume $p^\star(x_{m_k}) = 0$ does not satisfy \eqref{eq:dropped_states}, namely
+		\begin{equation}
+			I_k^\star(x_{m_k}) > I^\star(x_{\mathcal{K}}) = \sum_{m_k'} p^\star(x_{m_k'}) I_k^\star(x_{m_k'}),
+			\label{eq:dropped_states_assumption}
+		\end{equation}
+		Since the exponential function is monotonically increasing, \eqref{eq:dropped_states_assumption} implies $f_k^\star(x_{m_k}) > \sum_{m_k'} p^\star(x_{m_k'}) f_k^\star(x_{m_k'})$ and $D^\star(x_{m_k}) > 1$.
+		It contradicts with
+		\begin{equation}
+			p^{(r)}(x_{m_k}) = p^{(0)}(x_{m_k}) \prod_{n=1}^r D^{(n)}(x_{m_k}),
+		\end{equation}
+		since the left-hand side is zero while all terms on the right-hand side are strictly positive.
+		The proof is completed.
 		\label{ap:input_kkt_solution}

### 2023-07-29 review/response.tex
:speech_balloon: Update response

@@
 	\reply {Thank you for the suggestion and we understand it can be very difficult for readers to keep track of all acronyms and notations throughout the paper.
-We tried to add a list of acronyms and notations, but it would violate the 30-page limit and we cannot squeeze enough space from other places.
-Therefore, we decided not to include the list.
-We have ensured that all acronyms are defined before their first usage.}
+Due to the space limitation, we have made the decision not to include the list, but have taken the necessary steps to ensure that all acronyms and notations are clearly defined before their first usage.
+We appreciate your understanding in this matter.}
 
@@
 (46) is used without prior definition.
+	\reply {The issue has been addressed in the revised manuscript.}
 
@@
 (4b), the dimensions for $\mathbb{I}$ are not defined.
+	\reply {We have revised the manuscript to ensure consistency with the notation introduced in Section I.
+In the provided example, $\alpha_k \in \mathbb{I}$ refers to $\alpha_k \in \mathbb{I}^1$ and the $1$ was omitted for brevity.}
 
@@
 Please use a consistent term to refer to the same entity throughout the entire paper to avoid confusion and improve clarity.
+	\reply {Thank you for bringing this to our attention.
+We were trying to be rigorous and consistent with the notation used in the literature, but didn't realize the confusion it may cause to the readers.
+In BackCom literatures, $\alpha_k$ is a constant that measures the \emph{average} reflection efficiency (irrelevant to the state) for node $k$.
+In RIS literatures, $\beta_m$ measures the scattering ratio of one element at state $m$.
+We have unified the notation and terminology in the revised manuscript.}
 
 	\point The expression in eq. (1) represents the conjugate of the reflection coefficient, not the reflection coefficient itself.
+	\reply {After a careful investigation, we found there are different definitions for the reflection coefficient in the literature:
+		\begin{enumerate}
+			\item $\Gamma_m = \frac{Z_m - Z^*}{Z_m + Z}$ in overview papers \cite{VanHuynh2017,Liang2022};
+			\item $\Gamma_m = \frac{Z_m - Z^*}{Z_m + Z^*}$ in BackCom paper \cite{Boyer2014};
+			\item $\Gamma_m^* = \frac{Z^* - Z_m}{Z + Z_m}$ in RF paper \cite{Hansen1989},
+		\end{enumerate}
+		where $Z_m$ is the load impedance at state $m$ and $Z$ is the antenna impedance.
+It is guessed that they choose different reference (antenna and space).
+However, we are not microwave engineering experts and would be grateful to hear your valuable opinion on this issue.
+The current version sticks to the seeming most popular definition 1.}
 
@@
 Please provide additional details and reasoning.
+	\reply {We apologize for the confusion caused by poor wording.
+QoS refers to the relative priority of the primary link, and it should be either ``QoS'' or ``relative priority''.
+We have added a footnote on this.
+Besides, the information theory part (including the derivation of eqs.
+(17-19)) has been incorporated into Section II.B with proper explanation.
+We also modified Remark 1 and added Remark 2 to clarify the derivation of achievable rates.}
 
@@
 (25) lacks clarity and misses intermediate steps.
-Also, the expression of the function Q provided in eq.
-(25) appears to be independent of the active beamforming `w'.
-It is unclear how the derivation of Q with respect to 'w' is performed in this case.
-Please clarify the relationship between Q and 'w' and provide a clear derivation for better understanding.
+Also, the expression of the function $Q$ provided in eq.
+(25) appears to be independent of the active beamforming $\boldsymbol{w}$.
+It is unclear how the derivation of $Q$ with respect to $\boldsymbol{w}$ is performed in this case.
+Please clarify the relationship between $Q$ and $\boldsymbol{w}$ and provide a clear derivation for better understanding.
 The same remark about clarity applies to eq.
@@
 (33).
+	\reply {$Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr)$ is the regularized incomplete Gamma function that depends on the variance of accumulated receive energy $\sigma_{m_{\mathcal{K}}}^2$, which is a function of $\boldsymbol{w}$.
+We have added a reminder on this, and have added the intermediate steps from (9) to (25) with proper details.
+The corresponding part has been completely rewritten to improve logic and clarity.}
 
 	\point Is the BCD algorithm convergent for the optimization problem (20)?
+	\reply {The BCD algorithm is convergent for the optimization problem (20), since the input distribution and active beamforming subproblems converge and the thresholding subproblem attains global optimality.
+This argument has been added prior to the convergence results in Fig.
+7.}
 
@@
 \end{reviewer}
+
+\bibliographystyle{IEEEtran}
+\bibliography{../library.bib}
 \end{document}

### 2023-07-29 main.tex
:speech_balloon: Update response

@@
 		On the other hand, the antenna mode component depends on the impedance mismatch and is widely exploited in scattering applications.
-		For an antenna (resp. metamaterial) scatterer with $M$ reflection states, the reflection coefficient at state $m \in \mathcal{M} \triangleq \{1,\ldots,M\}$ is
+		For an antenna (resp. metamaterial) scatterer with $M$ reflection states, the reflection coefficient at state $m \in \mathcal{M} \triangleq \{1,\ldots,M\}$ is \cite{VanHuynh2017,Liang2022}
 		\begin{equation}
@@
 		which is still non-convex due to the integration and entropy terms.
-		Plugging \eqref{eq:energy_distribution} into \eqref{eq:dmmac}, we notice the \gls{dmmac} $q(x_l|x_{m_{\mathcal{K}}})$ can be rewritten as
+		Note the \gls{dmmac} $q(x_l|x_{m_{\mathcal{K}}})$ depends on the variance of accumulated receive energy $\sigma_{m_{\mathcal{K}}}^2$, which is a function of $\boldsymbol{w}$.
+		Plugging \eqref{eq:energy_distribution} into \eqref{eq:dmmac}, we have
 		\begin{align}
@@
 			 & = \frac{\int_{{t_{l-1}}/{\sigma_{m_{\mathcal{K}}}^2}}^{{t_l}/{\sigma_{m_{\mathcal{K}}}^2}} z^{N-1} \exp(-z) \, d z}{(N-1)!} \\
-			 & = Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr)
+			 & = Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr),
 		\end{align}
@@
 			\end{figure}
-
+			The \gls{bcd} algorithm is convergent for the optimization problem \eqref{op:weighted_sum_rate}, since the input distribution and active beamforming subproblems converge and the thresholding subproblem attains global optimality.
 			In Fig.~\ref{fg:wsr_convergence}, we plot the weighted sum of primary and total backscatter rates at $\rho=0$ for \gls{kkt}, \gls{pga} and \gls{bcd} algorithms on the first call.

### 2023-07-31 review/response.tex
:speech_balloon: Add new plots

@@
 If the optimization problem is intended to be a minimization problem, it should be explicitly mentioned to avoid any ambiguity or confusion.
+	\reply {In the revised manuscript, we have simplified many notations and rewritten (40) properly. Problem (21) is a maximization problem and the sign of the Lagrangian function has been corrected.}
 
 	\point The expression of the primary achievable rate in eq. (37) seems to be wrong since the primary message is also included in the cascaded channel and cannot be ignored.
+	\reply {We appreciate your careful reading.
+The primary message is indeed included in the scattered component.
+However, since the user decodes both links independently, the backscatter uncertainty cannot be eliminated when decoding the primary link.
+That is to say, the scattered component should be treated as interference with average power $\mathbb{E}\bigl\{\sum_{k} \alpha_k \boldsymbol{h}_{\text{C},k}^\mathsf{H} x_k \boldsymbol{w}s[n]\bigr\} = \sum_{k} \lvert \alpha_k \boldsymbol{h}_{\text{C},k}^\mathsf{H} \boldsymbol{w} \rvert^2$.
+The same reasoning was considered in \cite{Long2020a}.
+We have revised the corresponding footnote to justify this.}
 
@@
 Additionally, please provide the unit for the weighted sum rate axis.
+	\reply {In company with BCD, we also plotted the convergence results of KKT and PGD algorithms to show how much performance gain is provided by solving each subproblem (over the initialization method specified in the previous paragraph).
+The unit of the y axis is bit/s/Hz and we have added this in the revised manuscript.}
 
@@
 In other words, can the user in practice decode the backscatter information especially in the presence of the noise and signal variations due to the fading or the interference, etc.?
+	\reply {The energy detector is a simple and practical method for backscatter information decoding, and its reliability is improved by the adaptive input distribution and thresholding design.
+With high-order modulation or large number of scatter nodes, its performance can be further enhanced by increasing the spreading factor $N$ or using stronger error correction codes with lower code-rate.
+In practice, the user can decode backscatter nodes ranging from few to hundreds of meters in the presence of noise and interference, and the backscatter throughput can reach few Kbps to tens of Mbps.
+We have added a footnote on this, and the reviewer is referred to Table 2 in \cite{Wu2022e} for more details.}
 
@@
 In other words, is the choice of $s \sim \mathcal{CN} (0,1)$ optimal?
+	\reply {This is indeed a very good question.
+The choice of $s \sim \mathcal{CN} (0,1)$ is generally not optimal for weighted sum mutual information.
+To the best of our knowledge, the optimal primary distribution in this case remains an open issue, but some insights were given in those papers:
+		\begin{itemize}
+			\item If there is no direct link and the node is with \emph{average} power constraint, then the optimal distribution for \emph{weighted sum mutual information} requires a time-sharing between those modes \cite{Pillai2011}:
+			\begin{itemize}
+				\item $s$ follows zero-mean Gaussian distribution and $x$ is a constant;
+				\item $x$ follows zero-mean Gaussian distribution and $s$ is a constant;
+				\item $s$ and $x$ equal 0.
+			\end{itemize}
+			\item If there is no direct link and the node is with \emph{peak} power constraint, then the optimal distribution for \emph{sum mutual information} is not unique, for example \cite{Zhang2023} (came out after our submission):
+			\begin{itemize}
+				\item $s$ follows zero-mean Gaussian distribution and $x$ is a constant;
+				\item $s$ follows Rayleigh distribution and $x$ follows uniform distribution on $[0, 2 \pi]$;
+			\end{itemize}
+		\end{itemize}
+		Despite not optimal, the assumption of Gaussian primary source and finite-support backscatter source are relatively practical and widely adopted in relevant literatures.
+We have added Remark 3 on this, but intentionally avoided the discussion of optimal distribution, since it is beyond the scope of this paper and may confuse the readers.
+We appreciate your understanding in this matter.}
 
@@
 The RIS can also add those components destructively which could be used for example to enhance the physical layer security of a system in the presence of an eavesdropper.
+	\reply {We apologize for the oversight. It has been modified to ``Here, RIS ensures constructive superposition of direct and scattered components.''}
 \end{reviewer}

### 2023-07-31 main.tex
:speech_balloon: Add new plots

@@
 		\begin{remark}
-			We have assumed Gaussian codebook for the primary source and finite support for the backscatter nodes.
+			We have assumed Gaussian codebook for the primary source and finite support for the backscatter nodes, since they are relatively practical and widely adopted in relevant literatures.
 			The proposed framework is extendable to non-Gaussian primary source, and the conditional \gls{pdf} \eqref{eq:energy_distribution} can be approximated using \gls{clt} for large $N$.
@@
 
-		The user first jointly decodes the backscatter message of all nodes using a low-complexity energy detector.
+		The user first jointly decodes the backscatter message of all nodes using a low-complexity energy detector.\footnote{The reliability of the energy detector is improved by the adaptive input distribution and thresholding design.
+With high-order modulation or large number of scatter nodes, the reliability can be further enhanced by increasing the spreading factor or using error correction codes with lower code-rate.
+In practice, users can decode backscatter nodes ranging from a few to hundreds of meters in the presence of noise and interference, and the backscatter throughput can reach few Kbps to tens of Mbps \cite{Wu2022e}.}
 		The energy detector formulates a \gls{dmtc} of size $M^K \times M^K$.
@@
 			\caption{
-				\gls{pdf} of receive energy per backscatter block conditioned on different reflection state.
+				\gls{pdf} of the receive energy per backscatter block conditioned on different reflection state.
 			}
@@
 \begin{section}{Simulation Results}
-	In this section, we provide numerical results to evaluate the proposed input distribution, active beamforming, and backscatter decision designs for the considered RIScatter network.
+	In this section, we provide numerical results to evaluate the proposed input distribution, active beamforming, and backscatter decision algorithms.
 	We assume the AP-user distance is \SI{10}{\meter} and at least one RIScatter nodes are randomly dropped in a disk centered at the user with radius $r$.
-	% The \gls{ap} is with an average transmit power budget $P=\SI{36}{\dBm}$, all nodes employs $M$-\gls{qam} with amplitude scattering ratio $\alpha=0.5$, and the user is with average noise power $\sigma_v^2=\SI{-40}{\dBm}$.
 	The \gls{ap} is with an average transmit power budget $P=\SI{36}{\dBm}$ and all nodes employs $M$-\gls{qam} with $\alpha=0.5$.
@@
 	We set $b=9$ and $\varepsilon=\num{e-3}$.
-	All achievable rate points/regions are averaged over \num{e3} channel realizations.
+	All achievable rate regions are averaged over \num{e3} channel realizations.
 
@@
 		\begin{subsubsection}{Initialization}
-			To characterize each achievable rate region, we progressively obtain all boundary points by successively increasing the primary \gls{qos} $\rho$ and solving problem \eqref{op:weighted_sum_rate}.
+			To characterize the achievable rate region, we progressively obtain all boundary points by successively increasing $\rho$ and solving problem \eqref{op:weighted_sum_rate}.
 			For $\rho=0$ where the backscatter link is prioritized, we initialize Algorithm \ref{al:input_distribution} and \ref{al:active_beamforming} by uniform input distribution and \gls{mrt} towards the sum cascaded channel $\sum_{k} \boldsymbol{h}_{\text{C},k}^\mathsf{H}$, respectively.
-			At the following points, both algorithms are initialized by the final solutions at the previous point.
+			At the following points, both algorithms are initialized by the solutions at the previous point.
 		\end{subsubsection}
@@
 			\end{figure}
-			The \gls{bcd} algorithm is convergent for the optimization problem \eqref{op:weighted_sum_rate}, since the input distribution and active beamforming subproblems converge and the thresholding subproblem attains global optimality.
-			In Fig.~\ref{fg:wsr_convergence}, we plot the weighted sum of primary and total backscatter rates at $\rho=0$ for \gls{kkt}, \gls{pga} and \gls{bcd} algorithms on the first call.
-			For $K=8$ and $M=2$, Algorithm \ref{al:input_distribution} typically takes around \num{100} fast iterations to converge to the \gls{kkt} input distribution.
-			For $Q=4$, around \num{10} iterations are required for Algorithm \ref{al:active_beamforming} to converge.
-			Overall, the initial \gls{bcd} algorithm requires at most \num{5} iterations to converge.
-			At the following points (not presented here), the convergence of all three algorithms are much faster thanks to the progressive initialization.
-			We conclude the proposed algorithms have good convergence performances.
+			The \gls{bcd} algorithm is convergent for problem \eqref{op:weighted_sum_rate} since the input distribution and active beamforming subproblems converge and the thresholding subproblem attains global optimality.
+			In company with \gls{bcd}, we also plotted the convergence results of \gls{kkt} and \gls{pga} algorithms in Fig.~\ref{fg:wsr_convergence} to show how much performance is gained by solving each subproblem.
+			It is observed that Algorithm \ref{al:input_distribution} and \ref{al:active_beamforming} take around \num{100} and \num{10} iterations to converge, respectively.
+			Overall, the \gls{bcd} algorithm requires at most \num{5} iterations to converge.
+			As $\rho$ increases (not presented here), the convergence of all three algorithms are much faster thanks to the progressive initialization.
 		\end{subsubsection}
@@
 			The total backscatter rate of coherent decoding approaches $K \log M$ when $N$ is sufficiently large.
-			% which follows non-zero mean complex Gaussian distribution $\mathcal{CN}\bigl((\boldsymbol{h}_{\text{D}}^\mathsf{H} + \sum_{k} \alpha_k \boldsymbol{h}_{\text{C},k}^\mathsf{H} x_{m_k}) \boldsymbol{w},\sigma_v^2\bigr)$ under hypothesis $x_{m_{\mathcal{K}}}$.
-			% The corresponding \gls{pdf} of receive energy over $N$ primary blocks is
-			% \begin{equation}
-			% 	f^{\text{\gls{bbc}}}(z|x_{m_{\mathcal{K}}}) = \frac{(z-\mu_{m_{\mathcal{K}}}^{\text{\gls{bbc}}})^{N-1} \exp \bigl(-(z-\mu_{m_{\mathcal{K}}}^{\text{\gls{bbc}}})/\sigma_v^2 \bigr)}{\sigma_v^{2N} (N-1)!},
-			% 	\label{eq:energy_distribution_bbc}
-			% \end{equation}
-			% where $\mu_{m_{\mathcal{K}}}^{\text{\gls{bbc}}} \triangleq N \bigl\lvert \bigl(\boldsymbol{h}_{\text{D}}^\mathsf{H} + \sum_{k} \alpha_k \boldsymbol{h}_{\text{C},k}^\mathsf{H} x_{m_k}\bigr) \boldsymbol{w} \bigr\rvert^2$.
-			% The \gls{ml} decision threshold is derived as, $\forall l \in \mathcal{L} \setminus \{L\}$,
-			% \begin{equation}
-			% 	t_l^{\text{\gls{bbc}}} = \frac{\mu_{l-1}^{\text{\gls{bbc}}} \exp \bigl((\mu_{l-1}^{\text{\gls{bbc}}}-\mu_{l}^{\text{\gls{bbc}}})/\sigma_v^2 (N-1)\bigr) - \mu_{l}^{\text{\gls{bbc}}}}{\exp \bigl((\mu_{l-1}^{\text{\gls{bbc}}}-\mu_{l}^{\text{\gls{bbc}}})/\sigma_v^2 (N-1)\bigr) - 1}.
-			% 	\label{eq:detection_threshold_ml_bbc}
-			% \end{equation}
 			\item \emph{\gls{ambc}:} The user decodes both links independently and semi-coherently by treating the other as interference.
-			The primary achievable rate is approximately\footnote{To provide a preliminary benchmark, we regard the scattered component $\sum_{k} \alpha_k \boldsymbol{h}_{\text{C},k}^\mathsf{H} x_k \boldsymbol{w}s[n]$ as \gls{awgn} during primary decoding \cite{Long2020a}.}
+			The primary achievable rate is approximately\footnote{The scattered component is treated as interference with average power $\mathbb{E}\bigl\{\sum_{k} \alpha_k \boldsymbol{h}_{\text{C},k}^\mathsf{H} x_k \boldsymbol{w}s[n]\bigr\} = \sum_{k} \lvert \alpha_k \boldsymbol{h}_{\text{C},k}^\mathsf{H} \boldsymbol{w} \rvert^2$ \cite{Long2020a}.}
 			\begin{equation}
@@
 			The total backscatter rate of coherent decoding approaches $K \log M$ when $N$ is sufficiently large.
-			% which only involves noise uncertainty under hypothesis $x_{m_{\mathcal{K}}}$.
-			% During backscatter detection, the primary symbols $s[1],\ldots,s[N]$ function as a spreading code and the receiver performs \gls{mrc} on $\hat{y}^{\text{\gls{sr}}}[n]$ over $N$ primary blocks.
-			% This essentially formulates a \gls{dcmc} and the total backscatter achievable rate is maximized with equiprobable inputs as \cite{Ng2006}
-			% \begin{equation}
-			% 	I_{\text{B}}(x_{\mathcal{K}};\hat{y}^{\text{\gls{sr}}}) = K \log M - \frac{\iota}{M^K},
-			% \end{equation}
-			% where $\iota \triangleq \sum_{m_{\mathcal{K}}} \mathbb{E}_{\hat{v}} \log \sum_{m_{\mathcal{K}}'} \exp ( - {\lvert x_{m_{\mathcal{K}}} - x_{m_{\mathcal{K}}'} + \hat{v} \rvert^2}/{2 \sigma^2} )$ and $\hat{v} \sim \mathcal{CN}(0,\sigma_v^2/N)$.
-			% For a sufficiently large $N$, $\iota$ is negligible and the total backscatter rate approaches $K \log M$.
 			\item \emph{\gls{ris}:} The reflection pattern is deterministic and the total backscatter rate is zero.
@@
 
-		Fig.~\ref{fg:region_comparison} compares the typical achievable rate region/points of RIScatter and the strategies above.
-		% \emph{First,} we observe both \gls{bbc} and \gls{sr} achieves when the spreading factor $N$ is sufficiently large.
+		Fig.~\ref{fg:region_comparison} compares the typical achievable rate region/points of RIScatter and those strategies.
 		\emph{First,} we observe \gls{bbc} and \gls{sr} achieve the best backscatter performance thanks to coherent decoding.
-		% However, \gls{sr} requires $N$ \gls{sic} followed by a \gls
-		% However, \gls{sr} requires $N$ re-encoding, precoding, subtraction together with a time-domain \gls{mrc} to decode each backscatter symbol and the cost can be prohibitive.
 		For \gls{sr}, this comes with the cost of $N$ re-encoding, precoding, subtraction together with a time-domain \gls{mrc} per backscatter symbol.
-		% However, the primary rate benefit
-		% For \gls{bbc} with coherent energy detection, the conditional \gls{pdf} of receive energy \eqref{eq:energy_distribution_bbc} is more skewed at a large $N$, such that the equivalent \gls{dmmac} \eqref{eq:dmmac} has lower error probabilities.
-		% For \gls{sic}-based \gls{sr}, the effective backscatter \gls{snr} is increased by $N$ times and the penalty term $\iota$ becomes insignificant.
-		% However, the primary rate is only maintained at a very large spreading factor, which significantly constrains the backscatter \emph{throughput}.
 		\emph{Second,} the average primary rate slightly decreases/increases in the presence of a \gls{ambc}/\gls{ris} node and the benefit of \gls{sr} is not obvious.
 		This is because the cascaded channel is usually orders of magnitude weaker than the direct channel.
-		\gls{ris} always ensures constructive superposition of direct and scattered components while \gls{sr} only creates a quasi-static rich-scattering environment that marginally enhances the average primary rate.
+		Here, \gls{ris} ensures constructive superposition of direct and scattered components while \gls{sr} only creates a quasi-static rich-scattering environment that marginally enhances the average primary rate.
 		When $N$ is moderate, the randomly scattered signals should be modelled as interference rather than multipath components and the \gls{sr} point should move towards the \gls{ambc} point.
@@
 		On the other hand, for a large $N$, the maximum backscatter achievable rate of RIScatter is lower than \gls{bbc} and \gls{sr} but higher than \gls{ambc}.
-		This is because both RIScatter and \gls{ambc} employ semi-coherent energy detection, and the adaptive channel coding of RIScatter provides better performance than equiprobable inputs of \gls{ambc} especially at the low \gls{snr} of double fading.
-		When multiple antenna is available at the \gls{ap}, active beamforming can be optimized for RIScatter nodes and the backscatter rate gain over \gls{ambc} can be even larger.
+		This is because both RIScatter and \gls{ambc} employ semi-coherent energy detection, and the adaptive channel coding of RIScatter outperforms the equiprobable inputs of \gls{ambc}, especially at the low backscatter \gls{snr} in the double fading scenario.
+		When multiple antenna is available at the \gls{ap}, active beamforming can be optimized for RIScatter nodes and the backscatter rate gain over \gls{ambc} is more prominent.
 	\end{subsection}
@@
 		The objective is to demonstrate RIScatter nodes can leverage \gls{csi}- and \gls{qos}-adaptive input distribution design to balance backscatter modulation and passive beamforming.
-		For one RIScatter node with $M=4$, we evaluate the \gls{kkt} input distribution\footnote{Problem \eqref{op:input_distribution} is convex when $K=1$ and the \gls{kkt} solution is global optimal.} at different \gls{qos} and present the result in Fig.~\ref{fg:distribution_weights}.
+		For one RIScatter node with $M=4$, we evaluate the \gls{kkt} input distribution at different \gls{qos} and present the result in Fig.~\ref{fg:distribution_weights}.
 		At $\rho=0$ where the backscatter performance is prioritized, the optimal input distribution is \num{0} on two states and nearly uniform on the other two.
-		This is inline with Shannon's observation that binary antipodal inputs can be good enough for channel capacity at the low \gls{snr} \cite{Shannon1948}.
+		This is inline with Shannon's observation that binary antipodal inputs is good enough for channel capacity at the low \gls{snr} \cite{Shannon1948}.
 		Due to the weak scattered signal, the conditional energy \gls{pdf} under different hypotheses can be closely spaced as in Fig.~\ref{fg:energy_distribution}.
-		The extreme states producing the lowest/highest energy are always assigned with non-zero probability and the middle ones may not provide enough energy difference and thus end up unused.
+		The extreme states producing the lowest/highest energy are always assigned with non-zero probability, while the middles cannot provide enough energy difference and thus end up unused.
 		At $\rho=1$ where the primary performance is prioritized, the optimal input distribution is \num{1} at the state that maximizes the primary \gls{snr} and \num{0} at the others.
 		That is, the reflection pattern becomes deterministic and the RIScatter node boils down to a discrete \gls{ris} element.
-		Increasing $\rho$ from \num{0} to \num{1} provides a smooth transition from backscatter modulation to passive beamforming and proves RIScatter unifies \gls{bc} and \gls{ris} from a probabilistic perspective.
+		Increasing $\rho$ from \num{0} to \num{1} provides a smooth transition from backscatter modulation to passive beamforming, suggesting RIScatter unifies \gls{bc} and \gls{ris} from a probabilistic perspective.
 	\end{subsection}
@@
 			\begin{itemize}
-				\item \emph{Cooperation:} Joint nodes encoding using a $K$-dimensional probability array $p(x_{m_{\mathcal{K}}})$ by Algorithm \ref{al:input_distribution};
+				\item \emph{Cooperation:} Joint encoding using a joint probability array $p(x_{m_{\mathcal{K}}})$ with $M^K$ entries by Algorithm \ref{al:input_distribution};
 				\item \emph{Exhaustion:} Exhaustive search over the $M$-dimensional probability simplex with resolution $\Delta p = \num{e-2}$;
-				\item \emph{\gls{kkt}:} Numerical \gls{kkt} evaluation by Algorithm \ref{al:input_distribution};
-				\item \emph{Equiprobable:} Uniform input distribution for all nodes.
+				\item \emph{\gls{kkt}:} The \gls{kkt} solution by Algorithm \ref{al:input_distribution};
+				\item \emph{Equiprobable:} Uniform input distribution.
 			\end{itemize}
-			For dispersed nodes, joint encoding is inapplicable and we consider these independent input distribution recovery methods (from the joint probability array):
+			We also consider these independent distribution recovery methods from the joint probability array:
 			\begin{itemize}
 				\item \emph{Marginalization:} Marginal probability distributions;
-				\item \emph{Decomposition:} Normalized rank-\num{1} \gls{cp} decomposition tensors by \texttt{Tensor Toolbox} \cite{Bader2022};
+				\item \emph{Decomposition:} Normalized rank-\num{1} \gls{cp} decomposed tensors by \texttt{Tensor Toolbox} \cite{Bader2022};
 				\item \emph{Randomization:} Gaussian randomization with the guidance of correlation matrix \cite{Calvo2010}.
-				% guided by correlation matrix \cite{Calvo2010}.
 			\end{itemize}
 
-			Fig.~\subref*{fg:region_distribution} shows the average achievable rate regions for those designs.
-			We observe Cooperation provides the outer bound and joint encoding can be beneficial.
-			The average rate performance of Exhaustion and \gls{kkt} completely coincide with each other, demonstrating \gls{kkt} input distribution is favorable for a moderate $K$ as mentioned in Remark \ref{re:input_kkt_distribution}.
+			Fig.~\subref*{fg:region_distribution} shows their average achievable rate regions.
+			It is observed that Cooperation achieves the outer bound of all schemes, but its backscatter rate gain comes at the cost of implementation and computation complexity.
+			Besides, the average rate performance of Exhaustion and \gls{kkt} completely coincide with each other when $K=2$.
+			This confirms Remark \ref{re:input_kkt_distribution} that the \gls{kkt} input distribution can be good enough when $K$ is not very large.
 			Equiprobable experiences minor backscatter and major primary rate losses without exploiting \gls{csi} and \gls{qos}.
-			Both rate gaps should be larger when $M$ and/or $K$ increase.
-			For the recovery methods, the simple Marginalization provides a close performance to \gls{kkt}, but Randomization and Decomposition fail our expectations for most channel realizations.
-			Those observations emphasize the importance of (joint) adaptive RIScatter encoding and demonstrate the advantage of the proposed \gls{kkt} input distribution design.
+			Those gaps should be larger when $M$ and/or $K$ increase.
+			For the recovery methods, Marginalization provides a close performance to \gls{kkt}, but Randomization and Decomposition fail our expectations for most channel realizations.
+			Those observations emphasize the importance of adaptive RIScatter encoding and demonstrate the advantage of the proposed \gls{kkt} input distribution design.
 		\end{subsubsection}
@@
 			In the low-$\rho$ regime, the proposed \gls{pga} beamformer significantly outperforms both \gls{mrt} schemes in terms of total backscatter rate.
-			This is because the semi-coherent backscatter decoding relies on the \emph{relative difference} of receive energy under different symbol tuples.
-			Such an energy diversity is enhanced by \gls{pga} that effectively exploits backscatter constellation and input distribution knowledge rather than simply maximizing the direct/ergodic \gls{snr}.
-			As $\rho$ increases, the primary equivalent \gls{snr} outweighs the backscatter energy difference in \eqref{eq:weighted_sum_mutual_information_explicit} and \gls{pga} beamformer becomes closer to both \gls{mrt} schemes.
+			This is because the semi-coherent backscatter decoding relies on the \emph{relative difference} of receive energy under different backscatter symbol tuples.
+			Such an energy diversity is enhanced by \gls{pga}, which effectively exploits backscatter constellation and input distribution knowledge rather than simply maximizing the direct/ergodic channel strength.
+			As $\rho$ increases, the primary \gls{snr} outweighs the backscatter energy difference in \eqref{eq:weighted_sum_mutual_information_explicit}, and \gls{pga} beamformer approaches both \gls{mrt} schemes.
 			At $\rho=1$, both \gls{pga} and E-\gls{mrt} boil down to \gls{mrt} towards the composite channel.
 			The difference between E-\gls{mrt} and D-\gls{mrt} is insignificant when RIScatter nodes are dispersed.
-			Those observations prove the proposed \gls{pga} active beamforming design can exploit the \gls{csi}, \gls{qos}, and backscatter constellation to balance the primary equivalent \gls{snr} and backscatter energy difference and enlarge the achievable rate region.
+			Those observations prove the proposed \gls{pga} active beamforming design can exploit the \gls{csi}, \gls{qos}, and backscatter constellation to enlarge the achievable rate region.
 		\end{subsubsection}
@@
 			This is because the total backscatter rate \eqref{eq:backscatter_mutual_information} is a function of both input distribution and decision regions, and the rate-optimal threshold design heavily depends on input distribution.
-			For example, the backscatter symbol tuples with zero input probability should be assigned with empty decision regions in order to increase the success detection rates of other hypotheses.
+			For example, the backscatter symbol tuples with zero input probability should be assigned with empty decision regions, in order to increase the success detection rates of other hypotheses.
 			It highlights the importance of joint input distribution and decision threshold design in rate maximization problems.
@@
 			Interestingly, we observe that increasing $K$ has a larger benefit on the total backscatter rate than primary.
-			This is because each RIScatter node not only affects the primary equivalent \gls{snr} but also influences the relative energy difference that other nodes can create.
+			This is because each RIScatter node not only affects the primary \gls{snr} but also influences the relative energy difference that other nodes can make.
 			To maximize the total backscatter rate, some nodes closer to the user may need to sacrifice their own rate and use the state that \emph{minimizes} the composite channel strength, in order to increase the backscatter rate of other nodes.
 			This accounts for the significant primary rate decrease in the low-$\rho$ regime.
-			On the other hand, when the primary link is prioritized, the RIScatter nodes boil down to \gls{ris} elements and enjoy a conventional passive array gain $N^2$.
+			On the other hand, when the primary link is prioritized, the RIScatter nodes boil down to \gls{ris} elements and enjoy a conventional passive array gain $K^2$.
 		\end{subsubsection}
@@
 		\begin{subsubsection}{Number of States}
-			Fig.~\subref*{fg:region_states} shows the relationship between available reflection states (i.e., \gls{qam} order) $M$ and achievable rate regions.
-			We notice increasing the reflection states has a marginal effect on both primary and total backscatter rates.
-			This is because once the scope of reflection coefficient is determined, using denser constellation points only creates marginal phase resolution and energy diversity for primary and backscatter links.
-			Due to the maximum amplitude normalization in \eqref{eq:backscatter_modulation}, the average rate region of \num{8}-\gls{qam} (points on rectangle border) is smaller than that of \num{4}-\gls{qam} (points on square vertices), and the \num{4} points on the rectangle edges are less frequently used.
-			On the other hand, \num{16}-\gls{qam} provides significant higher backscatter rate benefit than primary.
-			It motivates one to use high-resolution metamaterial units as RIScatter nodes.
-			% The results in this and previous paragraphs motivate one to replace the high-resolution metamaterial units by multiple low-order scatter nodes.
+			Fig.~\subref*{fg:region_states} shows the relationship between available reflection states (i.e., \gls{qam} order) $M$ and achievable rate regions when $K=1$.
+			We notice that increasing the reflection states has a marginal effect on the primary rate but significantly improves the backscatter rate.
+			This is because the maximum amplitude normalized-\gls{qam} \eqref{eq:backscatter_modulation} involves more weak reflection points as $M$ increases.
+			It greatly enhances the receive energy difference but cannot provide enough phase shift resolution with strong reflection.
 		\end{subsubsection}
@@
 			Fig.~\subref*{fg:region_txs} illustrates the impact of transmit antennas $Q$ on the average performance.
-			As $Q$ increases, more scattered paths are available to \gls{pga} and the channel diversity can be further exploited to enhance the primary equivalent \gls{snr} and backscatter energy difference, which enlarges the achievable rate region.
+			As $Q$ increases, more scattered paths are available to \gls{pga} and the channel diversity can be further exploited to enhance the primary \gls{snr} and backscatter energy difference.
 			It emphasizes the importance of multi-antenna RIScatter systems and demonstrate the effectiveness of the proposed \gls{pga} design.
@@
 		\begin{subsubsection}{Spreading factor}
-			Fig.~\subref*{fg:region_duration} presents how the spreading factor $N$ affects the achievable rate region.
-			Please notice here the unit of total backscatter rate is bits per primary block to indicate throughput.
-			Apparently, using a very large $N$ can severely constrain the backscatter throughput, since the gain in energy certainty (by law of large numbers) cannot withstand the loss in gross rate.
-			As $N \to \infty$, RIScatter nodes boil down to \gls{ris} elements with fixed reflection pattern during whole channel block and the total backscatter rate approaches \num{0}.
-			On the other hand, when $N$ is too small, the equivalent \gls{dmmac} \eqref{eq:dmmac} has very high error probabilities and the energy detection is thus unreliable.
+			Fig.~\subref*{fg:region_duration} shows how the spreading factor $N$ affects the achievable rate region.\footnote{Please notice in Fig.~\subref*{fg:region_duration} the unit of total backscatter rate is bits per primary block to indicate throughput.}
+			Using a very large $N$ can severely constrain the backscatter throughput, since the gain in energy certainty (by law of large numbers) cannot withstand the loss in gross rate.
+			As $N \to \infty$, RIScatter nodes boil down to static \gls{ris} elements and the total backscatter rate approaches \num{0}.
+			On the other hand, when $N$ is too small, energy detection is error-prone as the \gls{dmmac} \eqref{eq:dmmac} is unreliable.
 			It explains the observation that $N=10$ provides lower backscatter throughput than $N=20$.
-			Therefore, we conclude the design of spreading factor $N$ in RIScatter systems should accommodate multiple factors (e.g., data rate requirements, load switching constraints at the nodes, and signal processing capability at the user).
+			Therefore, we conclude the spreading factor $N$ should be carefully designed over multiple factors (e.g., data rate requirements, load switching speed at the nodes, and signal processing capability at the user).
 		\end{subsubsection}
@@
 \begin{section}{Conclusion}
-	This paper introduced RIScatter as a low-power scatter protocol that simultaneously provides backscatter modulation and passive beamforming by smart input distribution design.
-	Starting from scattering principles, we showed how RIScatter nodes generalize information nodes of \gls{bc} and reflect elements of \gls{ris} as special cases, how they can be built over existing passive scatter devices, and how they simultaneously encode self information and assist legacy transmission.
-	We also propose a practical \gls{sic}-free receiver that exploits the properties of active-passive coexisting networks to maintain primary benefit and improve backscatter throughput.
-	The achievable primary-total-backscatter rate region is then studied for a single-user multi-node RIScatter network, where the input distribution, active beamforming, and decision thresholds are iteratively updated.
-	Numerical results not only validated the proposed algorithms but also emphasized the importance of adaptive input distribution and cooperative decoding for both primary and backscatter links.
+	This paper introduced RIScatter as a novel scatter protocol that bridges backscatter modulation and passive beamforming.
+	Starting from scattering principles, we showed how RIScatter nodes generalize information nodes of \gls{bc} and reflect elements of \gls{ris}, how they can be built over existing passive scatter devices, and how they simultaneously encode self information and assist legacy transmission.
+	We also proposed a practical \gls{sic}-free receiver that exploits the properties of active-passive coexisting networks to benefit both subsystems.
+	The achievable primary-total-backscatter rate region was then studied for a single-user multi-node RIScatter network, where the input distribution, active beamforming, and decision thresholds are iteratively updated.
+	Numerical results validated the proposed algorithms and emphasized the importance of adaptive input distribution and cooperative receiver design.
 
@@
 	Another interesting question is how to design RIScatter node and receiver in a multi-user system to fully exploit the dynamic passive beamforming that naturally origins from backscatter modulation.
-	% If one node can be decoded by multiple users, its input distribution may be further adjusted to mimic the multi-beam gain of dynamic passive beamforming \cite{Qiu2022}.
-	% This will be answered in our future work.
 \end{section}

### 2023-07-31 src/config/config_csi.m

@@ -1,0 +1,49 @@
+%% * System
+% number of transmit antennas
+nTxs = 4;
+% number of scatter antennas
+nSxs = 1;
+% number of receive antennas
+nRxs = 1;
+% number of tags
+nTags = 8;
+% number of available states at tags (i.e., modulation order)
+nStates = 2;
+% constellation diagram at tags
+constellation = normalize(qammod(transpose(0 : nStates - 1), nStates), 'norm', Inf);
+% amplitude scatter ratio at tags
+scatterRatio = 0.5;
+% backscatter/primary symbol duration ratio
+symbolRatio = 20;
+% average transmit power
+transmitPower = db2pow(6);
+% average noise power
+noisePower = db2pow(-70);
+% layout and distance
+directDistance = 10;
+coverage = 2;
+[forwardDistance, backwardDistance] = layout(directDistance, nTags, coverage);
+% path loss exponents
+directExponent = 2.6;
+forwardExponent = 2.4;
+backwardExponent = 2;
+% Ricean factors
+directFactor = 5;
+forwardFactor = 5;
+backwardFactor = 5;
+
+%% * Algorithm
+% relative priority of primary link
+weightSet = [0 : 0.01 : 0.05, 0.075, 0.1 : 0.05 : 0.25, 0.3 : 0.1 : 0.5, 0.75, 1];
+% number of weights on rate region boundary
+nWeights = length(weightSet);
+% number of quantization bins
+nBins = 2 ^ 9;
+
+%% * Variable
+Variable = struct('channelVariance', num2cell([0, 0.05, 0.1, 0.2]));
+nVariables = length(Variable);
+
+%% * PBS
+% number of instances
+nInstances = 1e3;

### 2023-07-31 src/config/config_snr.m

@@ -1,0 +1,49 @@
+%% * System
+% number of transmit antennas
+nTxs = 4;
+% number of scatter antennas
+nSxs = 1;
+% number of receive antennas
+nRxs = 1;
+% number of tags
+nTags = 8;
+% number of available states at tags (i.e., modulation order)
+nStates = 2;
+% constellation diagram at tags
+constellation = normalize(qammod(transpose(0 : nStates - 1), nStates), 'norm', Inf);
+% amplitude scatter ratio at tags
+scatterRatio = 0.5;
+% backscatter/primary symbol duration ratio
+symbolRatio = 20;
+% average transmit power
+transmitPower = db2pow(6);
+% average noise power
+noisePower = db2pow(-70);
+% layout and distance
+directDistance = 10;
+coverage = 2;
+[forwardDistance, backwardDistance] = layout(directDistance, nTags, coverage);
+% path loss exponents
+directExponent = 2.6;
+forwardExponent = 2.4;
+backwardExponent = 2;
+% Ricean factors
+directFactor = 5;
+forwardFactor = 5;
+backwardFactor = 5;
+
+%% * Algorithm
+% relative priority of primary link
+weightSet = [0 : 0.01 : 0.05, 0.075, 0.1 : 0.05 : 0.25, 0.3 : 0.1 : 0.5, 0.75, 1];
+% number of weights on rate region boundary
+nWeights = length(weightSet);
+% number of quantization bins
+nBins = 2 ^ 9;
+
+%% * Variable
+Variable = struct('cascadedPathLoss', num2cell(db2pow(-86 : -10 : -106)));
+nVariables = length(Variable);
+
+%% * PBS
+% number of instances
+nInstances = 1e3;

### 2023-07-31 src/lib/distribution_kkt.m

@@ -27,7 +27,7 @@ function [distribution, equivalentDistribution, convergence] = distribution_kkt(
 		weight;
 		snr;
 		dmac;
-		tolerance = 1e-9;
+		tolerance = 1e-8;
 	end
 
 	% * Get data

### 2023-07-31 src/plot/plot_convergence.m

@@ -14,7 +14,7 @@ hold off; legend('Location', 'se'); grid on; box on;
 nexttile;
 plotHandle(2) = plot(0 : length(convergence.pgd) - 1, convergence.pgd, 'DisplayName', 'PGD');
 hold off; legend('Location', 'se'); grid on; box on;
-ylabel('Weighed Sum-Rate');
+ylabel('Weighed Sum-Rate [bits/s/Hz]');
 
 % * BCD
 nexttile;

### 2023-07-31 src/plot/plot_csi.m

@@ -17,12 +17,12 @@ end
 save(strcat('../data/region_', erase(mfilename, 'plot_')));
 
 %% * Draw primary-(sum-)backscatter rate regions
-figure('Name', 'Average Primary-(Sum-)Backscatter Rate Region vs Primary SNR', 'Position', [0, 0, 500, 400]);
+figure('Name', 'Average Primary-(Sum-)Backscatter Rate Region vs Cascaded Channel Estimation Error', 'Position', [0, 0, 500, 400]);
 plotHandle = gobjects(nVariables, 1);
 hold all;
 for iVariable = 1 : nVariables
-	noisePower = Variable(iVariable).noisePower;
-	plotHandle(iVariable) = plot(region{iVariable}(1, :) / log(2), region{iVariable}(2, :) / log(2), 'DisplayName', strcat('$\gamma_P = ', num2str(-50 - pow2db(noisePower)), '$ dB'));
+	channelVariance = Variable(iVariable).channelVariance;
+	plotHandle(iVariable) = plot(region{iVariable}(1, :) / log(2), region{iVariable}(2, :) / log(2), 'DisplayName', strcat('$\iota = ', num2str(channelVariance), '$'));
 end
 hold off; legend('Location', 'se'); grid on; box on; axis tight;
 xlabel('Primary Rate [bits/s/Hz]');

### 2023-07-31 src/plot/plot_snr.m

@@ -17,12 +17,12 @@ end
 save(strcat('../data/region_', erase(mfilename, 'plot_')));
 
 %% * Draw primary-(sum-)backscatter rate regions
-figure('Name', 'Average Primary-(Sum-)Backscatter Rate Region vs Primary SNR', 'Position', [0, 0, 500, 400]);
+figure('Name', 'Average Primary-(Sum-)Backscatter Rate Region vs Backscatter SNR', 'Position', [0, 0, 500, 400]);
 plotHandle = gobjects(nVariables, 1);
 hold all;
 for iVariable = 1 : nVariables
-	noisePower = Variable(iVariable).noisePower;
-	plotHandle(iVariable) = plot(region{iVariable}(1, :) / log(2), region{iVariable}(2, :) / log(2), 'DisplayName', strcat('$\gamma_P = ', num2str(-50 - pow2db(noisePower)), '$ dB'));
+	cascadedPathLoss = Variable(iVariable).cascadedPathLoss;
+	plotHandle(iVariable) = plot(region{iVariable}(1, :) / log(2), region{iVariable}(2, :) / log(2), 'DisplayName', strcat('$\gamma_B = ', num2str(pow2db(transmitPower) - cascadedPathLoss - pow2db(noisePower)), '$ dB'));
 end
 hold off; legend('Location', 'se'); grid on; box on; axis tight;
 xlabel('Primary Rate [bits/s/Hz]');

### 2023-07-31 src/region_csi.m

@@ -1,0 +1,43 @@
+clear; setup; cvx_begin; cvx_end; clc; run(strcat('config_', erase(mfilename, 'region_')));
+
+% * Initialize struct
+Reference(1, nWeights) = struct('weight', [], 'rate', [], 'distribution', [], 'threshold', [], 'beamforming', []);
+Result(nVariables, nWeights) = struct('weight', [], 'rate', [], 'distribution', [], 'threshold', [], 'beamforming', []);
+
+% * Generate channels
+directChannel = sqrt(path_loss(directDistance, directExponent)) * fading_ricean(nTxs, nRxs, directFactor);
+cascadedChannel = zeros(nTxs, nTags);
+for iTag = 1 : nTags
+	cascadedChannel(:, iTag) = sqrt(path_loss(forwardDistance(iTag), forwardExponent)) * fading_ricean(nTxs, nSxs, forwardFactor) * sqrt(path_loss(backwardDistance(iTag), backwardExponent)) * fading_ricean(nSxs, nRxs, backwardFactor);
+end
+equivalentChannel = directChannel + scatterRatio * cascadedChannel * transpose(constellation(tuple_tag(repmat(transpose(1 : nStates), [1, nTags]))));
+
+% * Evaluate rate region vs cascaded channel estimation error
+for iVariable = 1 : nVariables
+	% * Set cascaded channel estimation error
+	channelVariance = Variable(iVariable).channelVariance;
+	cascadedChannelEstimation = cascadedChannel .* (ones(size(cascadedChannel)) + sqrt(0.5 * channelVariance) * (randn(size(cascadedChannel)) + 1i * randn(size(cascadedChannel))));
+	equivalentChannelEstimation = directChannel + scatterRatio * cascadedChannelEstimation * transpose(constellation(tuple_tag(repmat(transpose(1 : nStates), [1, nTags]))));
+
+	% * Clear persistent variables
+	clear block_coordinate_descent distribution_kkt distribution_cooperation beamforming_pgd threshold_bisection;
+
+	% * Evaluate rate region
+	for iWeight = 1 : nWeights
+		weight = weightSet(iWeight);
+		[~, distribution, threshold, beamforming] = block_coordinate_descent(nTags, symbolRatio, transmitPower, noisePower, nBins, weight, equivalentChannelEstimation, cascadedChannelEstimation, 'Distribution', 'kkt', 'Beamforming', 'pgd', 'Threshold', 'smawk');
+
[…]

### 2023-07-31 src/region_snr.m

@@ -1,0 +1,33 @@
+clear; setup; cvx_begin; cvx_end; clc; run(strcat('config_', erase(mfilename, 'region_')));
+
+% * Initialize struct
+Result(nVariables, nWeights) = struct('weight', [], 'rate', [], 'distribution', [], 'threshold', [], 'beamforming', []);
+
+% * Generate channels
+directChannel = sqrt(path_loss(directDistance, directExponent)) * fading_ricean(nTxs, nRxs, directFactor);
+cascadedFading = zeros(nTxs, nTags);
+for iTag = 1 : nTags
+	cascadedFading(:, iTag) = fading_ricean(nTxs, nSxs, forwardFactor) * fading_ricean(nSxs, nRxs, backwardFactor);
+end
+
+% * Evaluate rate region vs backscatter/primary symbol duration ratio
+for iVariable = 1 : nVariables
+	% * Set cascaded path loss
+	cascadedPathLoss = Variable(iVariable).cascadedPathLoss;
+
+	cascadedChannel = sqrt(cascadedPathLoss) * cascadedFading;
+	equivalentChannel = directChannel + scatterRatio * cascadedChannel * transpose(constellation(tuple_tag(repmat(transpose(1 : nStates), [1, nTags]))));
+
+	% * Clear persistent variables
+	clear block_coordinate_descent distribution_kkt distribution_cooperation beamforming_pgd threshold_bisection;
+
+	% * Evaluate rate region
+	for iWeight = 1 : nWeights
+		weight = weightSet(iWeight);
+		[rate, distribution, threshold, beamforming] = block_coordinate_descent(nTags, symbolRatio, transmitPower, noisePower, nBins, weight, equivalentChannel, cascadedChannel, 'Distribution', 'kkt', 'Beamforming', 'pgd', 'Threshold', 'smawk');
+		Result(iVariable, iWeight) = struct('weight', weight, 'rate', rate, 'distribution', distribution, 'threshold', threshold, 'beamforming', beamforming);
+	end
+end
+
+directory = strcat('data/', mfilename, '/');
+data_save;

### 2023-08-02 review/response.tex
:speech_balloon: Add comments

@@
 The authors should perhaps study in terms of simulations the impact of imperfect CSI and necessary degrees of freedom (for channel estimation) on the achieved rates, carefully taking into account the tag(s) small SNR as well as the primary link much stronger SNR.
+	\reply {We agree with the reviewer that the assumption of perfect CSI is very strong.
+Fast and accurate acquisition of cascaded CSI can be challenging especially when the backscatter SNR is weak and/or the number of nodes is large.
+To investigate the impact of CSI estimation error on the system performance, we have applied the proposed algorithms to an imperfect CSI model, where the cascaded channel of node $k$ is estimated as
+		\begin{equation}
+			\hat{\boldsymbol{h}}_{\text{C},k} = \boldsymbol{h}_{\text{C},k} + \tilde{\boldsymbol{h}}_{\text{C},k},
+		\end{equation}
+		$\tilde{\boldsymbol{h}}_{\text{C},k}$ is the estimation error with entries following i.i.d.
+CSCG distribution $\mathcal{CN}(0, \iota \Lambda_\text{C})$, $\iota$ is the relative estimation error, and $\Lambda_\text{C}$ is the cascaded path loss.
+	}
 
@@
 Some discussion on the above is necessary, while some thoughts on non-Gaussian codebooks and how the methodology could be extended is perhaps important.
+	\reply {Your valuable comments on scatter modeling and codebook design are very much appreciated.
+When the transmitted waveform is a continuous carrier wave (CW) that carries no information, the structure mode component is also a CW.
+After downconversion, its contribution is indeed modelled as a DC offset \cite{Boyer2014}.
+However, when the transmitted waveform is a modulated signal, the structure mode component is proportional to the modulated signal, and its contribution can thus be absorbed in the environment multipath \cite{Thomas2012,Liang2020}.
+When estimating the cascaded CSI, the reflection efficiency $\{\alpha_k\}$ can be set to some pre-determined values, such that the cascaded channels can be separated from the reflection efficiency.
+We agree with the reviewer that adding integrated receivers will increase the complexity and reduce the sensitivity of the nodes.
+The aim is to coordinate the nodes with the active source and to acquire the optimized input distributions, instead of decoding the primary information dedicated for the user.
+Thus, those receivers can be implemented using very simple circuits or even integrated with the rectifier \cite{Kim2021a} to reduce cost and complexity.
+Besides, the assumption of perfect symbol-level synchronization and integer spreading ratio are made to simplify the achievable rate analysis, and they have been widely adopted in relevant literatures \cite{Liang2020,Ding2020,Long2020a,Guo2019b,Han2021,Zhang2022}.
+If they are not satisfied, some penalty can be introduced to the achievable rate and it is left for future work.
+We have incorporated the above discussions in the revised manuscript.}
 
@@
 When the channel changes, one would expect the distribution of the tags' loads to be sensitive on channel statistics.
+	\reply {We apologize for the confusion caused by poor writing.
+The achievable rate analysis and the algorithms are provided for the most general case where all nodes encode independently.
+When multiple nodes are co-located, they can jointly encode by designing the joint probability $p(x_{m_{\mathcal{K}}})$ directly.
+This formulates an augmented backscatter source and becomes a special case of above.
+Regarding the observation in Fig.
+9, please note that one state corresponds to one equivalent load (and one reflection coefficient).
+In this case, there is exactly one reflection coefficient (corresponds to state 3) that maximizes the primary SNR, and it should be used with probability 1 to maximize the primary rate.
+Instead of explicitly designing the value of load impedance, we assume that they have been designed to fulfill the reflection coefficient codebook.
+The node input distribution (not the reflection coefficient codebook) is indeed adaptive to CSI, as mentioned in Section III.A.
+We have clarified the above points in the revised manuscript.}
 
 	\point All simulation results and respective optimization solutions are offered with relatively small number of K and M; some discussion on ways to extend the methodology for larger networks and loads should be helpful.
+	\reply {Thank you for the suggestion.
+The main limitations for massive RIScatter are the energy detection and the dynamic programming algorithm.
+For $K$ nodes each with $M$ states, there are a total of $L = M^K$ energy decision regions to design.
+The candidate threshold set $\mathcal{T}$ should be even finer, which results in a very fast growth of the computational complexity ($\mathcal{O}\bigl(L^2(\mathrm{card}(\mathcal{T})-L)\bigr)$ for SMAWK and $\mathcal{O}\bigl(\mathrm{card}(\mathcal{T})L\log(\mathrm{card}(\mathcal{T})L)\bigr)$ for bisection).
+To support massive RIScatter networks with large number of nodes and states, one possible future direction is to consider backscatter detection over the received signal domain rather than energy domain, where multi-antenna \cite{Liu2022c} and learning-based approaches can be promising.
+We have added this to the conclusion part of the revised manuscript.}
 

### 2023-08-02 main.tex
:speech_balloon: Add comments

@@
 \newacronym{clt}{CLT}{Central Limit Theorem}
+\newacronym{cw}{CW}{Continuous Waveform}
 \newacronym{cp}{CP}{Canonical Polyadic}
@@
 		In the scattered signal, the structural mode component depends on the scatterer geometry and material.
-		It is usually modelled as a DC offset \cite{Boyer2014} or part of environment multipath \cite{Thomas2012}.
+		Its impact is usually modelled as part of environment multipath \cite{Thomas2012,Liang2020}, or simply a DC offset in the baseband signal when the impinging signal is a \gls{cw} \cite{Boyer2014}.
 		On the other hand, the antenna mode component depends on the impedance mismatch and is widely exploited in scattering applications.
@@
 
-		RIScatter nodes can be implemented, for example, by adding an integrated receiver \cite{Kim2021a} and adaptive encoder \cite{He2020e} to off-the-shelf passive \gls{rfid} tags.
+		RIScatter nodes can be implemented, for example, by adding an integrated receiver\footnote{The aim is to coordinate the node with the active source and to acquire the optimized input distribution, instead of decoding the primary information dedicated for the user.
+The node receiver can be implemented using very simple circuits or even integrated with the rectifier \cite{Kim2021a} to reduce cost and complexity.} \cite{Kim2021a} and adaptive encoder \cite{He2020e} to off-the-shelf passive \gls{rfid} tags.
 		The block diagram, equivalent circuit, and scatter model are illustrated in Fig.~\ref{fg:riscatter_node}.
@@
 		All nodes have $M$ available reflection states.
-		In the primary point-to-point system, the \gls{ap} transmits information to the user over a multipath channel\footnote{It is assumed the primary symbol duration is much longer than multipath delay spread (no inter-symbol interference).} enhanced by RIScatter nodes.
+		In the primary point-to-point system, the \gls{ap} transmits information to the user over a multipath channel\footnote{It is assumed the primary symbol duration is much longer than multipath delay spread (i.e., no inter-symbol interference).} enhanced by RIScatter nodes.
 		In the backscatter multiple access system, the \gls{ap} acts as carrier emitter, the RIScatter nodes modulate over scattered signal, and the user jointly decodes all node messages.\footnote{It is assumed the signal going through two or more RIScatter nodes is too weak to be received by the user.}
@@
 		where $\boldsymbol{\alpha} \triangleq [\alpha_1,\ldots,\alpha_K]^\mathsf{T} \in \mathbb{I}^{K}$, $\boldsymbol{x} \triangleq [x_1,\ldots,x_K]^\mathsf{H} \in \mathcal{X}^{K}$, and $\boldsymbol{H}_{\text{C}} \triangleq [\boldsymbol{h}_{\text{C},1},\ldots,\boldsymbol{h}_{\text{C},K}]^\mathsf{H} \in \mathbb{C}^{K \times Q}$.
+		Without loss of generality, we assume the spreading factor $N$ is a positive integer.
 		Within one backscatter block, the signal received by the user at primary block $n \in \mathcal{N} \triangleq \{1,\ldots,N\}$ is
@@
 			\end{equation}
-			When the nodes are co-located, they can jointly encode by designing $p(x_{m_{\mathcal{K}}})$ directly.
+			When multiple nodes are co-located, they can jointly encode by designing the joint probability $p(x_{m_{\mathcal{K}}})$ directly.
 		\end{remark}
@@
 		The extreme states producing the lowest/highest energy are always assigned with non-zero probability, while the middles cannot provide enough energy difference and thus end up unused.
-		At $\rho=1$ where the primary performance is prioritized, the optimal input distribution is \num{1} at the state that maximizes the primary \gls{snr} and \num{0} at the others.
+		At $\rho=1$ where the primary link is prioritized, the optimal input distribution is \num{1} at state \num{3}, since the corresponding reflection coefficient maximizes the primary \gls{snr}.
 		That is, the reflection pattern becomes deterministic and the RIScatter node boils down to a discrete \gls{ris} element.
@@
 
-	One possible future direction is to consider backscatter detection over the received signal domain rather than energy domain, where multi-antenna \cite{Liu2022c} and learning-based approaches can be promising.
+	To support massive RIScatter networks with large number of nodes and states, one possible future direction is to consider backscatter detection over the received signal domain rather than energy domain, where multi-antenna \cite{Liu2022c} and learning-based approaches can be promising.
 	Another interesting question is how to design RIScatter node and receiver in a multi-user system to fully exploit the dynamic passive beamforming that naturally origins from backscatter modulation.
@@
 		On the other hand, we notice
-		% \begin{subequations}
-		% 	\label{eq:information_difference_upper}
-		% 	\begin{align}
-		% 		\Delta
-		% 		 & \triangleq I(x_{\mathcal{K}}) - J \bigl( p(x_{m_{\mathcal{K}}}),p'(x_{m_{\mathcal{K}}}) \bigr)                                                                                                          \\
-		% 		 & = (1 - \rho) \sum_{m_k} \frac{p'(x_{m_k}) f_k'(x_{m_k})}{\sum_{m_k'} p'(x_{m_k'}) f_k'(x_{m_k'})} \sum_{m_{\mathcal{K}}''} q(\hat{x}_{m_{\mathcal{K}}''}|x_{m_k})\nonumber                              \\
-		% 		 & \quad \times \log \frac{\sum_{m_k'} p'(x_{m_k'}) q(\hat{x}_{m_{\mathcal{K}}''}|x_{m_k'}) f_k'(x_{m_k})}{\sum_{m_k'} p'(x_{m_k'}) q(\hat{x}_{m_{\mathcal{K}}''}|x_{m_k'}) f_k'(x_{m_k'})}                \\
-		% 		 & \ge (1 - \rho) \sum_{m_k} \frac{p'(x_{m_k}) f_k'(x_{m_k})}{\sum_{m_k'} p'(x_{m_k'}) f_k'(x_{m_k'})} \sum_{m_{\mathcal{K}}''} q(\hat{x}_{m_{\mathcal{K}}''}|x_{m_k})\nonumber                            \\
-		% 		 & \quad \times \Biggl( 1 - \frac{\sum_{m_k'} p'(x_{m_k'}) q(\hat{x}_{m_{\mathcal{K}}''}|x_{m_k'}) f_k'(x_{m_k'})}{\sum_{m_k'} p'(x_{m_k'}) q(\hat{x}_{m_{\mathcal{K}}''}|x_{m_k'}) f_k'(x_{m_k})} \Biggr) \\
-		% 		 & = 0,
-		% 	\end{align}
-		% \end{subequations}
 		\begin{subequations}

### 2023-08-03 review/response.tex
:speech_balloon: Update response

@@
 2022, conference version available at IEEE Globecom 2021.
+	\reply {We agree with the reviewer that the reference list could be improved.
+The current state of the art in BackCom is indeed very rich and diverse.
+In the previous version of our manuscript, we only introduced papers that use RIS for backscatter modulation.
+In contrast, the recommended reference exploits commodity RFID tags, powered and controlled by a software-defined radio reader, to perform passive beamforming towards a legacy user at a different frequency.
+It validates the feasibility of using batteryless devices to adaptively enhance the SNR of the primary link.
+This reference makes the literature review more comprehensive, and we have added it to the revised manuscript.}
 \end{reviewer}
@@
 	The manuscript presents a novel concept, i.e., RIScatter, and studies an interesting problem. However, there are several problems with the manuscript, namely:
+
+	\point Presentation and use of English: the presentation is sometimes unclear about the differences of RIScatter and existing techniques, it seems that the authors are concerned about listing the contributions in the introduction and forgot to contrast the key differences between existing approaches and the proposed RIScatter.
+Perhaps the authors can polish this part and make it more compact.
+Sometimes, a shorted and compact text can be made easier to understand.
+Moreover, there are too many poorly written sentences, typos and Grammar errors throughout the manuscript.
+It is not acceptable that a JSAC paper would feature with this level of English (especially coming from a British university!).
+Therefore, it is fundamental to improve the use of English and make sentences properly structured.
+	\reply {We agree with the reviewer that the contrast between RIScatter and existing techniques could be clearer.
+The introduction and contribution have been refined in precise and explicit words for improved readability and clarity.
+Also, we have completely rewritten Section II.A on RIScatter principles to highlight the key differences between RIScatter and existing techniques.
+Remark 1 now emphasizes the distinction and relationship between RIScatter and dynamic RIS.
+We also apologize for the poor English usage.
+The manuscript has been carefully proofread and revised to address the typos and grammar errors.
+We believe that the revised manuscript should be much easier to understand.}
 
@@
 	\end{itemize}
+	\reply {We appreciate your expert and insightful comments on the reference list. We have incorporated the above references in the revised manuscript.}
 
@@
 
-	\point Overall, the technical approach of the paper is credible, there is a clear technical contribution although there are aspects related to the use of English and presentation that must be revised.
 \end{reviewer}

### 2023-08-03 main.tex
:speech_balloon: Update response

@@
 	\gls{ris} adapts its phase shift response to alter channel strength in specific directions.
-	In this paper, we show how those two different technologies (and their derivatives) can be unified into one architecture called RIScatter.
+	In this paper, we show how those two seemingly different technologies (and their derivatives) can be unified into one architecture called RIScatter.
 	RIScatter consists of dispersed or co-located scatter nodes, whose reflection states are adapted to partially modulate their information and partially engineer the wireless channel.
@@
 	This enables RIScatter to softly bridge \gls{bc} and \gls{ris}; reduce to either under specific distribution; or evolve in a mixed form for heterogeneous traffic control and universal hardware design.
-	We also propose a low-complexity \gls{sic}-free receiver that effectively exploits the properties of RIScatter.
+	We also propose a low-complexity \gls{sic}-free receiver that exploits the properties of RIScatter.
 	For a single-user multi-node network, we characterize the achievable primary-(total-)backscatter rate region by optimizing the input distribution at scatter nodes, the active beamforming at the \gls{ap}, and the energy decision regions at the user.
@@
 	It does not require dedicated power source, carrier emitter, or frequency spectrum, but the backscatter decoding is subject to the strong interference from the primary (legacy) link.
-	To tackle this, cooperative \gls{ambc} \cite{Yang2018} employs a co-located receiver to decode both coexisting links and the concept was further refined as \gls{sr} in Fig.~\subref*{fg:sr} \cite{Liang2020}.
+	To tackle this, cooperative \gls{ambc} \cite{Yang2018} employs a co-located receiver to decode both coexisting links, and the concept was further refined as \gls{sr} in Fig.~\subref*{fg:sr} \cite{Liang2020}.
 	Specifically, the active transmitter generates \gls{rf} wave carrying primary information, the passive node creates a rich-scattering environment and rides its own information, and the co-located receiver cooperatively decodes both links.
@@
 	Such a coexistence is classified into commensal (overlay), parasitic (underlay), and competitive (interfering) paradigms, and their achievable rate and outage performance were investigated in \cite{Guo2019b,Ding2020}.
-	For the co-located cooperative receiver, the \gls{ber} performance of \gls{ml}, linear, and \gls{sic} detectors are derived over flat fading channels \cite{Yang2018}.
-	However, the work assumed equal symbol duration and perfect synchronization for primary and backscatter links.
+	% The \gls{ber} performance of \gls{ml}, linear, and \gls{sic} receivers are derived over flat fading channels \cite{Yang2018}.
+	The authors of \cite{Hassani2023} analyzed the energy efficiency and achievable rate region for an \gls{ambc}-aided multi-user downlink \gls{noma} system.
+	However, it assumed equal symbol duration and perfect synchronization for the coexisting links.
 	Importantly, active-passive coexisting networks have three special and important properties:
@@
 	\end{enumerate}
-	The second property motivated \cite{Long2020a,Liang2020,Guo2019b,Ding2020,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Yang2018,Han2021,Zhang2022} to view \gls{sr} as a multiplicative \gls{noma} and perform \gls{sic} from primary to backscatter link.
+	The second property motivated \cite{Long2020a,Liang2020,Guo2019b,Ding2020,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Yang2018,Han2021,Zhang2022,Dai2023} to view \gls{sr} as a multiplicative \gls{noma} and perform \gls{sic} from primary to backscatter link.
 	During primary decoding, the backscatter signal can be modelled as channel uncertainty or multiplicative interference when the spreading factor is large or small, respectively.
 	Decoding each backscatter symbol also requires multiple \gls{sic} followed by a \gls{mrc} over primary blocks, which is operation-intensive and \gls{csi}-sensitive.
+	Under those assumptions, the achievable rate region of cell-free \gls{sr} is characterized in \cite{Dai2023}.
 	When the spreading factor is sufficiently large, the primary achievable rate under semi-coherent detection\footnote{In this paper, semi-coherent detection refers to the primary/backscatter decoding with known \gls{csi} and unknown backscatter/primary symbols.} asymptotically approaches its coherent counterpart and both links are decoded interference-free \cite{Long2020a}.
@@
 
-	On the other hand, static \gls{ris} design with fixed reflection pattern per channel block has been extensively studied in wireless communication, sensing, and power literature \cite{Wu2018,Zhang2019a,Lin2022,Liu2022,Feng2022,Zhao2022}.
+	On the other hand, static \gls{ris} that employs fixed reflection pattern per channel block has been extensively studied in wireless communication, sensing, and power literature \cite{Wu2018,Zhang2019a,Lin2022,Liu2022,Feng2022,Zhao2022}.
 	Dynamic \gls{ris} performs time sharing between different phase shifts and introduces artificial channel diversity within each channel block.
-	It was first proposed to fine-tune the \gls{ofdm} resource blocks \cite{Yang2020} then extended to the downlink power and uplink information phases of \gls{wpcn} \cite{Wu2021,Wu2021d,Hua2022a}.
-	However, dynamic \gls{ris} carries \emph{no} additional information since the reflection state at each time slot is known to the receiver.
-	\gls{ris} can also be used as an information source and prototypes have been developed for \gls{psk} \cite{Tang2019a} and \gls{qam} \cite{Dai2020a}.
-	From an information-theoretic perspective, the authors of \cite{Karasik2020} reported that joint transmitter-\gls{ris} encoding achieves the capacity of \gls{ris}-aided finite-input channel and using \gls{ris} as a naive passive beamformer to maximize the receive \gls{snr} is generally suboptimal.
-	This inspired \gls{ris}-empowered \gls{bc} \cite{Liu2019d,Bereyhi2020,Xu2020b,Zhang2021d,Hu2021b,Hua2022,Basar2020,Ma2020a,Yuan2021,Hu2021a} to combine passive beamforming and backscatter modulation in the overall reflection pattern.
+	The idea was first proposed to fine-tune the \gls{ofdm} resource blocks \cite{Yang2020}, then extended to the downlink power and uplink information phases of \gls{wpcn} \cite{Wu2021,Wu2021d,Hua2022a}.
+	However, dynamic \gls{ris} carries no information because the reflection state at a specific time is known to the receiver.
+	\gls{ris} can also be used as an information source, and prototypes have been developed for \gls{psk} \cite{Tang2019a} and \gls{qam} \cite{Dai2020a}.
+	From an information-theoretic perspective, the authors of \cite{Karasik2020} reported that joint transmitter-\gls{ris} encoding achieves the capacity of \gls{ris}-aided finite-input channel, and using \gls{ris} as a naive passive beamformer to maximize the receive \gls{snr} is generally suboptimal.
+	This inspired \cite{Liu2019d,Bereyhi2020,Xu2020b,Zhang2021d,Hu2021b,Hua2022,Basar2020,Ma2020a,Yuan2021,Hu2021a} to combine passive beamforming and backscatter modulation in the overall \gls{ris} design.
 	In particular, \emph{symbol level precoding} maps the information symbols to the optimized \gls{ris} coefficient sets \cite{Liu2019d,Bereyhi2020}, \emph{overlay modulation} superposes the information symbols over a common auxiliary matrix \cite{Xu2020b,Zhang2021d,Hu2021b,Hua2022}, \emph{spatial modulation} switches between the reflection coefficient sets that maximize \gls{snr} at different receive antennas \cite{Basar2020,Ma2020a,Yuan2021}, and \emph{index modulation} employs dedicated reflection elements (resp.
@@
 backscatter modulation) \cite{Hu2021a}.
-	However, those joint designs incur advanced hardware architecture and high optimization complexity.
-	Relevant literature also considers either Gaussian codebook \cite{Guo2019b,Ding2020,Long2020a,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Hu2021b} that is impractical for low-power nodes or finite equiprobable inputs \cite{Yang2018,Liang2020,Han2021,Zhang2022,Liu2019d,Bereyhi2020,Xu2020b,Zhang2021d,Hua2022,Basar2020,Ma2020a,Yuan2021,Hu2021a} that does not fully exploit the \gls{csi} and properties of active-passive coexisting networks.
+	Those \gls{ris}-based backscatter modulation schemes incur advanced hardware architecture and high optimization complexity.
+	In contrast, \cite{Vardakis2023} exploits commodity \gls{rfid} tags, powered and controlled by a software-defined radio reader, to perform passive beamforming (but no backscatter modulation) towards a legacy user at a different frequency.
+	% The authors demonstrated the feasibility of using batteryless devices to adaptively enhance the \gls{snr} of a primary link, but did not consider backscatter modulation at.
+	Most relevant literature considers either Gaussian codebook \cite{Guo2019b,Ding2020,Long2020a,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Hu2021b} that is impractical for low-power nodes, or finite equiprobable inputs \cite{Yang2018,Liang2020,Han2021,Zhang2022,Liu2019d,Bereyhi2020,Xu2020b,Zhang2021d,Hua2022,Basar2020,Ma2020a,Yuan2021,Hu2021a} that does not fully exploit the \gls{csi} and properties of active-passive coexisting networks.
+	For binary-input \gls{ambc}, the achievable rate and optimal input distribution are investigated in \cite{Qian2019b}, but the authors did not consider its impact on the primary link.
 	Those problems are addressed in this paper and the contributions are summarized below.
@@
 	\emph{First,} we propose RIScatter as a novel protocol that unifies \gls{bc} and \gls{ris} by adaptive reflection state (backscatter input) distribution design.
-	The concept is shown in Fig.~\subref*{fg:riscatter} where one or more RIScatter nodes ride over an active transmission and simultaneously modulate their information and engineer the wireless channel.
-	A co-located receiver cooperatively decodes both coexisting links and each reflection state simultaneously acts as information and passive beamforming codewords.
-	The reflection pattern of each node is semi-randomly chosen with the guidance of input distribution as a joint function of the information source, \gls{csi}, and \gls{qos}\footnote{\gls{qos} refers to the relative priority of the primary link.}.
+	The concept is shown in Fig.~\subref*{fg:riscatter} where one or more RIScatter nodes ride over an active transmission, simultaneously modulating their information and engineering the wireless channel.
+	A co-located receiver cooperatively decodes both coexisting links.
+	Each reflection state is simultaneously an information codeword and a passive beamforming codeword.
+	The reflection pattern over time is semi-random and guided by the input probability assigned to each state.
+	This probability distribution is carefully designed to incorporate the backscatter information, \gls{csi}, and \gls{qos}\footnote{\gls{qos} refers to the relative priority of the primary link.}.
 	Such an adaptive channel coding boils down to the degenerate distribution of \gls{ris} when the primary link is prioritized, and outperforms the uniform distribution of \gls{bc} (by accounting the \gls{csi}) when the backscatter link is prioritized.
-	Joint and independent encoding are available when multiple RIScatter nodes are co-located and dispersed, respectively.
 	Table~\ref{tb:scattering_applications} compares RIScatter to \gls{bc} and \gls{ris}.
@@
 
-	\emph{Second,} we address the first challenge and propose a practical receiver that semi-coherently decodes the backscatter information, recovers the reflection pattern, and coherently decodes the primary link.
-	We consider backscatter energy detection and formulate a \gls{dmmac} over disjoint decision regions.
-	Thanks to the double modulation and symbol-level passive precoding, the semi-coherent backscatter decoding is essentially part of channel training.
-	Once the backscatter information is successfully decoded, its contribution can be modelled within composite channel as dynamic passive beamforming (rather than re-precoded and cancelled).
-	% It requires only one energy comparison and re-encoding per backscatter symbol and is much efficient than conventional decoding based on \gls{sic} and \gls{mrc}.
-	Such a sequential decoding transforms backscatter modulation into dynamic passive beamforming using only one re-encoding and one energy level comparison per backscatter block.
-	It is also suitable for arbitrary input distribution and spreading factor, which significantly improves backscatter throughput.
-	This is the first paper to consider practical backscatter-primary decoding scheme to exploit backscatter modulation as dynamic passive beamforming at the co-located receiver.
-
-	\emph{Third,} we address the second challenge and consider a single-user multi-node \gls{miso} scenario.
+	\emph{Second,} we address the first challenge and propose a low-complexity \gls{sic}-free receiver.
+	It semi-coherently decodes the weak backscatter signal using an energy detector, re-encodes for the exact reflection pattern, then coherently decodes the primary link.
+	Thanks to double modulation, the backscatter detection becomes part of channel training, and the impact of backscatter modulation can be modelled as dynamic passive beamforming.
+	The proposed receiver may be built over legacy receivers with minor hardware upgrade, since it only requires one additional energy comparison and re-encoding per backscatter symbol (instead of primary symbol).
+	The energy detector can also be tailored for arbitrary input distribution and spreading factor to increase backscatter throughput.
+	This is the first paper to propose a \gls{sic}-free receiver for active-passive coexisting networks.
+
+	\emph{Third,} we address the second challenge in a single-user multi-node \gls{miso} scenario.
 	We characterize the achievable primary-(total-)backscatter rate region by optimizing the input distribution at RIScatter nodes, the active beamforming at the \gls{ap}, and the energy decision regions at the user under different \gls{qos}.
 	A \gls{bcd} algorithm is proposed where the \gls{kkt} input distribution is numerically evaluated by limit of sequences, the active beamforming is optimized by \gls{pga}, and the decision regions are refined by existing sequential quantizer for \gls{dmtc}.
-	Uniquely, we consider \gls{csi}, \gls{qos}, and backscatter constellation in the optimization and the input distribution result is applicable to general detection schemes.
+	Uniquely, our optimization problem takes into account the \gls{csi}, \gls{qos}, and backscatter constellation, and the resulting input distribution is applicable to any detection scheme.
 	This is also the first paper to reveal the importance of backscatter input distribution and decision region designs in active-passive coexisting networks.
@@
 
+		% TODO
+		While existing work
 		RIScatter generalizes \gls{bc} and \gls{ris} from a probabilistic perspective.
 		Each reflection coefficient simultaneously acts as an information codeword and a passive beamforming codeword.
-		As shown in Fig.~\ref{fg:scatter_comparison}, RIScatter nodes semi-randomly choose reflection states according to an input distribution, which strikes a balance between backscatter modulation and passive beamforming.
+		As shown in Fig.~\ref{fg:scatter_comparison}, the reflection pattern of each RIScatter node over time is semi-random and guided by the input probability assigned to each state.
+		This probability distribution is carefully designed to incorporate the backscatter information, \gls{csi}, and \gls{qos}, in order to strike a balance between backscatter modulation and passive beamforming.
 		\begin{figure}[!t]
@@
 		\end{figure*}
-		To exploit the benefits of RIScatter, we also propose a low-complexity receiver that semi-coherently decodes the backscatter link, recovers the reflection pattern, and coherently decodes the primary link.
-		The detail will be covered in Section~\ref{se:system_model}.
+		% To exploit the benefits of RIScatter, we also propose a low-complexity receiver that semi-coherently decodes the backscatter link, re-encodes to recover the reflection pattern, and coherently decodes the primary link.
+		% The detail will be covered in Section~\ref{se:system_model}.
 	\end{subsection}
@@
 
-		Once the backscatter information is successfully decoded, the user recovers the exact reflection pattern, determines the composite channel by \eqref{eq:equivalent_channel}, and coherently decodes the primary link.
+		Once the backscatter information is successfully decoded, the user re-encodes to recover the exact reflection pattern and thus the composite channel by \eqref{eq:equivalent_channel}, then coherently decodes the primary link.
 		The primary mutual information is

### 2023-08-03 main.tex
:speech_balloon: Update response

@@
 	Such a coexistence is classified into commensal (overlay), parasitic (underlay), and competitive (interfering) paradigms, and their achievable rate and outage performance were investigated in \cite{Guo2019b,Ding2020}.
+	The achievable rate and optimal input distribution for binary-input \gls{ambc} are investigated in \cite{Qian2019b}, but its impact on the primary link is not considered.
+	% For binary-input \gls{ambc},  are investigated in \cite{Qian2019b}, but the authors did not consider its impact on the primary link.
 	% The \gls{ber} performance of \gls{ml}, linear, and \gls{sic} receivers are derived over flat fading channels \cite{Yang2018}.
-	The authors of \cite{Hassani2023} analyzed the energy efficiency and achievable rate region for an \gls{ambc}-aided multi-user downlink \gls{noma} system.
-	However, it assumed equal symbol duration and perfect synchronization for the coexisting links.
+	% The authors of \cite{Hassani2023} analyzed the energy efficiency and achievable rate region for an \gls{ambc}-aided multi-user downlink \gls{noma} system.
+	In \cite{Hassani2023}, the authors analyzed the energy efficiency and achievable rate region for an \gls{ambc}-aided multi-user downlink \gls{noma} system.
+	However, they assumed equal symbol duration and perfect synchronization for the coexisting links.
 	Importantly, active-passive coexisting networks have three special and important properties:
@@
 	Most relevant literature considers either Gaussian codebook \cite{Guo2019b,Ding2020,Long2020a,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Hu2021b} that is impractical for low-power nodes, or finite equiprobable inputs \cite{Yang2018,Liang2020,Han2021,Zhang2022,Liu2019d,Bereyhi2020,Xu2020b,Zhang2021d,Hua2022,Basar2020,Ma2020a,Yuan2021,Hu2021a} that does not fully exploit the \gls{csi} and properties of active-passive coexisting networks.
-	For binary-input \gls{ambc}, the achievable rate and optimal input distribution are investigated in \cite{Qian2019b}, but the authors did not consider its impact on the primary link.
 	Those problems are addressed in this paper and the contributions are summarized below.

### 2023-08-04 review/response.tex
:speech_balloon: Update response

@@
 \usepackage{tikz}
+
+% \usepackage{xr-hyper}
+% \usepackage{hyperref}
+% \makeatletter
+% \long\def\myempty{}
+% \def\XR@addURL#1{\XR@@dURL#1\myempty{}{}{}{}{}\\}
+% \def\XR@@dURL#1#2#3#4#5#6#7\\{%
+%   {#1}{#2}%
+%   \ifx\myempty#6\@empty
+% 	{#3}{#4}{\XR@URL}%
+%   \else
+%   \fi
+% }
+% \makeatother
+
+\usepackage[pagewise]{lineno}
+\usepackage{xr}
+\externaldocument[m-]{../main}
 
@@
 	\point The abstract and the number of keywords exceed the specified authorized limit. Please check IEEE JSAC guidelines.
-	\reply {We apologize for the mistake. The abstract and the number of keywords have been revised to meet the specifications.}
+	\reply {We apologize for the mistake. The abstract and keywords have been revised to meet the specifications.}
 
@@
 	\reply {Thank you for the suggestion and we understand it can be very difficult for readers to keep track of all acronyms and notations throughout the paper.
-Due to the space limitation, we have made the decision not to include the list, but have taken the necessary steps to ensure that all acronyms and notations are clearly defined before their first usage.
+Due to the space limitation, the list is not included but have carefully defined all acronyms and notations before their first usage.
 We appreciate your understanding in this matter.}
@@
 (46) is used without prior definition.
-	\reply {The issue has been addressed in the revised manuscript.}
+	\reply {The issue has been addressed in the revised manuscript. $\mathbf{h}_E^H$ in eq. (46) should be $\mathbf{h}^H$.}
 
@@
 (4b), the dimensions for $\mathbb{I}$ are not defined.
-	\reply {We have revised the manuscript to ensure consistency with the notation introduced in Section I.
+	\reply {We have revised the manuscript to ensure consistency with the notation introduced in Section~\ref{m-sc:introduction}.
 In the provided example, $\alpha_k \in \mathbb{I}$ refers to $\alpha_k \in \mathbb{I}^1$ and the $1$ was omitted for brevity.}
@@
 In RIS literatures, $\beta_m$ measures the scattering ratio of one element at state $m$.
-We have unified the notation and terminology in the revised manuscript.}
+In the revised manuscript, we have unified those notation in page~\pageref{m-eq:backscatter_modulation} and revised the term ``tag'' to ``node'' in the appendix.}
 
 	\point The expression in eq. (1) represents the conjugate of the reflection coefficient, not the reflection coefficient itself.
-	\reply {After a careful investigation, we found there are different definitions for the reflection coefficient in the literature:
+	\reply {After a careful investigation, we found there are three different definitions for the reflection coefficient in the literature:
 		\begin{enumerate}
@@
 		where $Z_m$ is the load impedance at state $m$ and $Z$ is the antenna impedance.
-It is guessed that they choose different reference (antenna and space).
-However, we are not microwave engineering experts and would be grateful to hear your valuable opinion on this issue.
-The current version sticks to the seeming most popular definition 1.}
+		Unfortunately, we are not microwave engineering experts and have to guess that they may choose different parties (antenna and space) as reference.
+In the current version, we have not made any change to eq.
+(1) but would be grateful to hear your opinion on this issue.}
 
@@
 We have added a footnote on this.
-Besides, the information theory part (including the derivation of eqs.
-(17-19)) has been incorporated into Section II.B with proper explanation.
-We also modified Remark 1 and added Remark 2 to clarify the derivation of achievable rates.}
+Besides, the information theory subsection (including the derivation of eqs.
+(17-19)) has been rewritten and incorporated into Section II.B with proper explanation.
+We also modified Remark \ref{m-re:dynamic_passive_beamforming} and added Remark \ref{m-re:independent_encoding} to clarify the derivation of achievable rates.
+Please see page~\pageref{m-re:dynamic_passive_beamforming}--\pageref{m-eq:weighted_sum_mutual_information} for details.}
 
@@
 (33).
-	\reply {$Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr)$ is the regularized incomplete Gamma function that depends on the variance of accumulated receive energy $\sigma_{m_{\mathcal{K}}}^2$, which is a function of $\boldsymbol{w}$.
-We have added a reminder on this, and have added the intermediate steps from (9) to (25) with proper details.
+	\reply {
+		Plugging the conditional energy PDF into the DMMAC expression, we have
+		\begin{equation}
+			q(x_l|x_{m_{\mathcal{K}}}) = \frac{\int_{{t_{l-1}}/{\sigma_{m_{\mathcal{K}}}^2}}^{{t_l}/{\sigma_{m_{\mathcal{K}}}^2}} z^{N-1} \exp(-z) \, d z}{(N-1)!} = Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr),
+			\label{eq:dmmac_gamma}
+		\end{equation}
+		where $Q(N, b_1, b_2) \triangleq \int_{b_1}^{b_2} z^{N-1} \exp(-z) / (N - 1)! \, d z$ is the regularized incomplete Gamma function.
+		$Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr)$ depends on the variance of accumulated receive energy $\sigma_{m_{\mathcal{K}}}^2$, which is a function of $\boldsymbol{w}$.
+		Its series expansion is given by \cite[Theorem 3]{Jameson2016}
+		\begin{equation}
+			Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr) = \exp \Bigl(-\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2}\Bigr) \sum_{n=0}^{N-1} \frac{\bigl(\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2}\bigr)^n}{n!} - \exp \Bigl(-\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr) \sum_{n=0}^{N-1} \frac{\bigl(\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\bigr)^n}{n!}.
+			\label{eq:regularized_incomplete_gamma}
+		\end{equation}
+		In the revised manuscript, we have added the intermediate steps from (9) to (25) in page~\pageref{m-eq:dmmac_gamma} with proper details.
 The corresponding part has been completely rewritten to improve logic and clarity.}
@@
 If the optimization problem is intended to be a minimization problem, it should be explicitly mentioned to avoid any ambiguity or confusion.
-	\reply {In the revised manuscript, we have simplified many notations and rewritten (40) properly. Problem (21) is a maximization problem and the sign of the Lagrangian function has been corrected.}
+	\reply {Problem (21) is a maximization problem and the Lagrangian function (40) has been rewritten as
+		\begin{equation}
+			I(x_{\mathcal{K}}) + \sum_k \nu_k \biggl( \sum_{m_k} p(x_{m_k}) - 1 \biggr) + \sum_k \sum_{m_k} \lambda_{m_k} p(x_{m_k}).
+		\end{equation}
+	}
 
@@
 The same reasoning was considered in \cite{Long2020a}.
-We have revised the corresponding footnote to justify this.}
+We have revised the corresponding footnote \ref{m-fn:ambc} to justify this.}
 
@@
 	\reply {In company with BCD, we also plotted the convergence results of KKT and PGD algorithms to show how much performance gain is provided by solving each subproblem (over the initialization method specified in the previous paragraph).
-The unit of the y axis is bit/s/Hz and we have added this in the revised manuscript.}
+We have justified this in Section~\ref{m-sc:convergence}.
+The unit of the y axis of Fig.~\ref{m-fg:distribution_weights} has been specified as bit/s/Hz.}
 
@@
 In practice, the user can decode backscatter nodes ranging from few to hundreds of meters in the presence of noise and interference, and the backscatter throughput can reach few Kbps to tens of Mbps.
-We have added a footnote on this, and the reviewer is referred to Table 2 in \cite{Wu2022e} for more details.}
+We have added footnote \ref{m-fn:energy_detector} on this issue, and the reviewer is referred to Table II in \cite{Wu2022e} for more details.}
 
@@
 				\item $s$ follows zero-mean Gaussian distribution and $x$ is a constant;
-				\item $s$ follows Rayleigh distribution and $x$ follows uniform distribution on $[0, 2 \pi]$;
+				\item $s$ follows Rayleigh distribution and $x$ follows uniform distribution on $[0, 2 \pi)$;
 			\end{itemize}
@@
 		Despite not optimal, the assumption of Gaussian primary source and finite-support backscatter source are relatively practical and widely adopted in relevant literatures.
-We have added Remark 3 on this, but intentionally avoided the discussion of optimal distribution, since it is beyond the scope of this paper and may confuse the readers.
+We have added Remark~\ref{m-re:non_gaussian} on this, but intentionally avoided the discussion of optimal distribution, since it is beyond the scope of this paper and may confuse the readers.
 We appreciate your understanding in this matter.}
@@
 The RIS can also add those components destructively which could be used for example to enhance the physical layer security of a system in the presence of an eavesdropper.
-	\reply {We apologize for the oversight. It has been modified to ``Here, RIS ensures constructive superposition of direct and scattered components.''}
+	\reply {We apologize for the oversight. The argument has been modified to ``Here, RIS ensures constructive superposition of direct and scattered components.''}
 \end{reviewer}
@@
 	\end{itemize}
-	\reply {We appreciate your expert and insightful comments on the reference list. We have incorporated the above references in the revised manuscript.}
+	\reply {We appreciate your expert and insightful comments on the reference list. Those papers have been incorporated into the revised manuscript.}
 
@@
 Can you explain why this is reasonable?
+	\reply {Please kindly refer to response 2.1 for the discussion on imperfect CSI and response 2.2 for the discussion on perfect synchronization.}
 
@@
 Could explain why not include results such as information rates versus SNR or BER versus SNR?
+	\reply {Thank you for the suggestion.
+In the previous version of the manuscript, we showed the impact of average noise power and disk radius on the achievable rate region.
+The former influences both primary and backscatter SNR, while the latter implicitly influences the backscatter SNR.
+In the revised manuscript, we have added explicit results on the achievable region vs primary SNR and backscatter SNR.
+However, we do not include BER vs SNR because (1) we have reached the page limit and (2) the BER performance is not the focus of this paper.
+We appreciate your understanding in this matter.}
 

### 2023-08-04 main.tex
:speech_balloon: Update response

@@
 
-% siunitx
-\DeclareSIUnit{\belm}{Bm}
-\DeclareSIUnit{\dBm}{\deci\belm}
-\DeclareSIUnit{\beli}{Bi}
-\DeclareSIUnit{\dBi}{\deci\beli}
-
 % PGF/TikZ
@@
 \newacronym{csi}{CSI}{Channel State Information}
+\newacronym{dc}{DC}{Direct Current}
 \newacronym{df}{DF}{Decode-and-Forward}
@@
 \begin{section}{Introduction}
+	\label{sc:introduction}
 	\IEEEPARstart{F}{uture} wireless network is envisioned to provide high throughput, uniform coverage, pervasive connectivity, heterogeneous control, and cognitive intelligence for trillions of low-power devices.
@@
 		\item Backscatter signal strength is much weaker than primary due to the \emph{double fading} effect;
-		\item The spreading factor (i.e., backscatter symbol duration over primary) is usually large\footnote{The load-switching interval of low-power backscatter modulators is usually \num{0.1} to \SI{10}{\us} \cite{Torres2021}, accounting for a typical spreading factor between \num{10} and \num{e3}.}.
+		\item The spreading factor (i.e., backscatter symbol duration over primary) is usually large\footnote{The load-switching interval of low-power backscatter modulators is usually \num{0.1} to \qty{10}{\us} \cite{Torres2021}, accounting for a typical spreading factor between \num{10} and \num{e3}.}.
 	\end{enumerate}
@@
 \begin{section}{RIScatter}
+	\label{sc:riscatter}
 	\begin{subsection}{Principles}
+		\label{sc:principles}
 		\gls{rf} wave scattering or reflecting are often manipulated by passive antennas or programmable metamaterial \cite{Liang2022}.
@@
 		In the scattered signal, the structural mode component depends on the scatterer geometry and material.
-		Its impact is usually modelled as part of environment multipath \cite{Thomas2012,Liang2020}, or simply a DC offset in the baseband signal when the impinging signal is a \gls{cw} \cite{Boyer2014}.
+		Its impact is usually modelled as part of environment multipath \cite{Thomas2012,Liang2020}, or simply a \gls{dc} offset in the baseband signal when the impinging signal is a \gls{cw} \cite{Boyer2014}.
 		On the other hand, the antenna mode component depends on the impedance mismatch and is widely exploited in scattering applications.
@@
 
-		% TODO
-		While existing work
 		RIScatter generalizes \gls{bc} and \gls{ris} from a probabilistic perspective.
@@
 			Upon successful backscatter detection, the impact of RIScatter nodes on the primary link can be modelled as dynamic passive beamforming.
+			\label{re:dynamic_passive_beamforming}
 		\end{remark}
@@
 		% To exploit the benefits of RIScatter, we also propose a low-complexity receiver that semi-coherently decodes the backscatter link, re-encodes to recover the reflection pattern, and coherently decodes the primary link.
-		% The detail will be covered in Section~\ref{se:system_model}.
+		% The detail will be covered in Section~\ref{st:system_model}.
 	\end{subsection}
@@
 			When multiple nodes are co-located, they can jointly encode by designing the joint probability $p(x_{m_{\mathcal{K}}})$ directly.
+			\label{re:independent_encoding}
 		\end{remark}
@@
 			The proposed framework is extendable to non-Gaussian primary source, and the conditional \gls{pdf} \eqref{eq:energy_distribution} can be approximated using \gls{clt} for large $N$.
+			\label{re:non_gaussian}
 		\end{remark}
@@
 With high-order modulation or large number of scatter nodes, the reliability can be further enhanced by increasing the spreading factor or using error correction codes with lower code-rate.
-In practice, users can decode backscatter nodes ranging from a few to hundreds of meters in the presence of noise and interference, and the backscatter throughput can reach few Kbps to tens of Mbps \cite{Wu2022e}.}
+In practice, users can decode backscatter nodes ranging from a few to hundreds of meters in the presence of noise and interference, and the backscatter throughput can reach few Kbps to tens of Mbps \cite{Wu2022e}.\label{fn:energy_detector}}
+		Then, the user decodes the primary message using the \gls{ml} detector.
 		The energy detector formulates a \gls{dmtc} of size $M^K \times M^K$.
@@
 		\end{equation}
-		\label{st:system_model}
 	\end{subsection}
-	\label{st:riscatter}
 \end{section}
@@
 			 & = Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr),
+			\label{eq:dmmac_gamma}
 		\end{align}
@@
 		On the other hand, \cite{Nguyen2020a} started from the optimality condition for three neighbor thresholds and presented a traverse-then-bisect algorithm with complexity $\mathcal{O}\bigl(\mathrm{card}(\mathcal{T})L\log(\mathrm{card}(\mathcal{T})L)\bigr)$.
-		In Section \ref{st:simulation_results}, both schemes will be compared with the \gls{ml} scheme \cite{Qian2019}
+		In Section \ref{sc:simulation_results}, both schemes will be compared with the \gls{ml} scheme \cite{Qian2019}
 		\begin{equation}
@@
 \begin{section}{Simulation Results}
+	\label{sc:simulation_results}
 	In this section, we provide numerical results to evaluate the proposed input distribution, active beamforming, and backscatter decision algorithms.
-	We assume the AP-user distance is \SI{10}{\meter} and at least one RIScatter nodes are randomly dropped in a disk centered at the user with radius $r$.
-	The \gls{ap} is with an average transmit power budget $P=\SI{36}{\dBm}$ and all nodes employs $M$-\gls{qam} with $\alpha=0.5$.
+	We assume the AP-user distance is \qty{10}{m} and at least one RIScatter nodes are randomly dropped in a disk centered at the user with radius $r$.
+	The \gls{ap} is with an average transmit power budget $P=\qty{36}{dBm}$ and all nodes employs $M$-\gls{qam} with $\alpha=0.5$.
 	For all channels involved, we consider a distance-dependent path loss model
@@
 	\end{equation}
-	where $d$ is the transmission distance, $L_0=-\SI{30}{\dB}$ is the reference path loss at $d_0=\SI{1}{\meter}$, $\kappa$ is the Rician K-factor, $\bar{\boldsymbol{H}}$ is the deterministic line-of-sight component with unit-magnitude entries, and $\tilde{\boldsymbol{H}}$ is the Rayleigh fading component with standard \gls{iid} \gls{cscg} entries.
+	where $d$ is the transmission distance, $L_0=-\qty{30}{dB}$ is the reference path loss at $d_0=\qty{1}{m}$, $\kappa$ is the Rician K-factor, $\bar{\boldsymbol{H}}$ is the deterministic line-of-sight component with unit-magnitude entries, and $\tilde{\boldsymbol{H}}$ is the Rayleigh fading component with standard \gls{iid} \gls{cscg} entries.
 	We choose $\gamma_{\text{D}}=2.6$, $\gamma_{\text{F}}=2.4$, $\gamma_{\text{B}}=2$, and $\kappa_{\text{D}}=\kappa_{\text{F}}=\kappa_{\text{B}}=5$ for direct, forward and backward links.
@@
 		\begin{subsubsection}{Convergence}
+			\label{sc:convergence}
 			\begin{figure}[!t]
@@
 				}
-				\caption{Typical convergence curves at $\rho=0$ for $Q=4$, $K=8$, $M=2$, $N=20$, $\sigma_v^2=\SI{-40}{\dBm}$ and $r=\SI{2}{\meter}$.}
+				\caption{Typical convergence curves at $\rho=0$ for $Q=4$, $K=8$, $M=2$, $N=20$, $\sigma_v^2=\qty{-40}{dBm}$ and $r=\qty{2}{m}$.}
 				\label{fg:wsr_convergence}
@@
 			\item \emph{\gls{ambc}:} The user decodes both links independently and semi-coherently by treating the other as interference.
-			The primary achievable rate is approximately\footnote{The scattered component is treated as interference with average power $\mathbb{E}\bigl\{\sum_{k} \alpha_k \boldsymbol{h}_{\text{C},k}^\mathsf{H} x_k \boldsymbol{w}s[n]\bigr\} = \sum_{k} \lvert \alpha_k \boldsymbol{h}_{\text{C},k}^\mathsf{H} \boldsymbol{w} \rvert^2$ \cite{Long2020a}.}
+			The primary achievable rate is approximately\footnote{The scattered component is treated as interference with average power $\mathbb{E}\bigl\{\sum_{k} \alpha_k \boldsymbol{h}_{\text{C},k}^\mathsf{H} x_k \boldsymbol{w}s[n]\bigr\} = \sum_{k} \lvert \alpha_k \boldsymbol{h}_{\text{C},k}^\mathsf{H} \boldsymbol{w} \rvert^2$ \cite{Long2020a}.\label{fn:ambc}}
 			\begin{equation}
@@
 			}
-			\caption{Typical achievable rate region/points of scattering applications for $Q=1$, $K=1$, $M=4$, $N=\num{e3}$, $\sigma_v^2=\SI{-40}{\dBm}$ and $r=\SI{2}{\meter}$.}
+			\caption{Typical achievable rate region/points of scattering applications for $Q=1$, $K=1$, $M=4$, $N=\num{e3}$, $\sigma_v^2=\qty{-40}{dBm}$ and $r=\qty{2}{m}$.}
 			\label{fg:region_comparison}
@@
 			}
-			\caption{Typical RIScatter reflection state distribution at different $\rho$ for $Q=1$, $K=1$, $M=4$, $N=20$, $\sigma_v^2=\SI{-40}{\dBm}$ and $r=\SI{2}{\meter}$.}
+			\caption{Typical RIScatter reflection state distribution at different $\rho$ for $Q=1$, $K=1$, $M=4$, $N=20$, $\sigma_v^2=\qty{-40}{dBm}$ and $r=\qty{2}{m}$.}
 			\label{fg:distribution_weights}
@@
 			\caption{
-				Average primary-total-backscatter rate regions by different input distribution, active beamforming, and decision threshold schemes for $K=2$, $M=4$, $N=20$, $\sigma_v^2=\SI{-40}{\dBm}$ and $r=\SI{2}{\meter}$.
+				Average primary-total-backscatter rate regions by different input distribution, active beamforming, and decision threshold schemes for $K=2$, $M=4$, $N=20$, $\sigma_v^2=\qty{-40}{dBm}$ and $r=\qty{2}{m}$.
 			}
@@
 			}
-			\subfloat[Disk Radius\label{fg:region_coverage}]{
+			\subfloat[Imperfect \gls{csi}\label{fg:region_csi}]{
 				\resizebox{0.48\columnwidth}{!}{
-					\input{assets/simulation/region_coverage.tex}
+					\input{assets/simulation/region_csi.tex}
 				}
@@
 		\end{figure}
-		In this study, we choose $Q=4$, $K=8$, $M=2$, $N=20$, $\sigma_v^2=\SI{-40}{\dBm}$ and $r=\SI{2}{\meter}$ as a reference.
+		In this study, we choose $Q=4$, $K=8$, $M=2$, $N=20$, $\sigma_v^2=\qty{-40}{dBm}$ and $r=\qty{2}{m}$ as a reference.
 		\begin{subsubsection}{Number of Nodes}
@@
 
-		\begin{subsubsection}{Coverage Disk Radius}
-			Fig.~\subref*{fg:region_coverage} shows the relationship between disk radius $r$ and achievable rate region.
-			We observe both primary and backscatter performance are enhanced when nodes are located closer to the user.
-			This is because the double fading effect is less severe for near-far setups.
-			In a multi-user RIScatter network with dispersed nodes, each node may be assigned to the nearest user to guarantee uniformly good performance for both links.
+		% \begin{subsubsection}{Coverage Disk Radius}
+		% 	Fig.~\subref*{fg:region_coverage} shows the relationship between disk radius $r$ and achievable rate region.
+		% 	We observe both primary and backscatter performance are enhanced when nodes are located closer to the user.
+		% 	This is because the double fading effect is less severe for near-far setups.
+		% 	In a multi-user RIScatter network with dispersed nodes, each node may be assigned to the nearest user to guarantee uniformly good performance for both links.
+		% \end{subsubsection}
+
+		\begin{subsubsection}{Imperfect \gls{csi}}
+			Due to the lack of \gls{rf} chains at RIScatter nodes, fast and accurate acquisition of the cascaded \gls{csi} can be challenging, especially when the backscatter \gls{snr} is weak or the number of nodes is large.
+			We consider an imperfect \gls{csi} model, where the cascaded channel of node $k$ is estimated as
+			\begin{equation}
+				\hat{\boldsymbol{h}}_{\text{C},k} = \boldsymbol{h}_{\text{C},k} + \tilde{\boldsymbol{h}}_{\text{C},k},
+			\end{equation}
+			$\tilde{\boldsymbol{h}}_{\text{C},k}$ is the estimation error with entries following i.i.d.
+CSCG distribution $\mathcal{CN}(0, \iota \Lambda_\text{C})$, $\iota$ is the relative estimation error, and $\Lambda_\text{C}$ is the cascaded path loss.
+			In Fig.~\subref*{fg:region_csi}, it is observed that the channel estimation error mainly affects the backscatter rate.
+			When $\iota$ increases from \num{0} to \num{0.2}, the maximum total backscatter rate decreases by \qty{20}{\percent}.
+			This is because the energy detector is sensitive to the \gls{dmmac} \eqref{eq:dmmac} and thus $\hat{\boldsymbol{h}}_{\text{C},k}$.
+			On the other hand, a small estimation error may be insufficient to change the optimal passive beamforming state (especially for a small $M$) and the primary rate is almost unchanged here.
 		\end{subsubsection}
 	\end{subsection}
-	\label{st:simulation_results}
 \end{section}
@@
 		\begin{equation}
-			I(x_{\mathcal{K}}) + \sum_k \nu_k \biggl( \sum_{m_k} p(x_{m_k}) - 1 \biggr) + \sum_k \sum_{m_k} \lambda_{m_k} p(x_{m_k})
+			I(x_{\mathcal{K}}) + \sum_k \nu_k \biggl( \sum_{m_k} p(x_{m_k}) - 1 \biggr) + \sum_k \sum_{m_k} \lambda_{m_k} p(x_{m_k}),
 		\end{equation}

### 2023-08-05 assets/simulation/region_comparison.tex
:bento: Update assets

@@
 \begin{axis}[%
-width=4.079in,
-height=1.587in,
-at={(0.684in,0.361in)},
+width=4.014in,
+height=1.552in,
+at={(0.673in,0.356in)},
 scale only axis,
@@
 ymajorgrids,
-legend style={at={(0.03,0.03)}, anchor=south west, legend cell align=left, align=left, draw=white!15!black},
+legend style={at={(0.03,0.97)}, anchor=north west, legend cell align=left, align=left, draw=white!15!black},
 align=center,

### 2023-08-05 review/response.tex
:speech_balloon: Update response

@@
 \usepackage{tikz}
-
-% \usepackage{xr-hyper}
-% \usepackage{hyperref}
-% \makeatletter
-% \long\def\myempty{}
-% \def\XR@addURL#1{\XR@@dURL#1\myempty{}{}{}{}{}\\}
-% \def\XR@@dURL#1#2#3#4#5#6#7\\{%
-%   {#1}{#2}%
-%   \ifx\myempty#6\@empty
-% 	{#3}{#4}{\XR@URL}%
-%   \else
-%   \fi
-% }
-% \makeatother
 
@@
 	\point The abstract and the number of keywords exceed the specified authorized limit. Please check IEEE JSAC guidelines.
-	\reply {We apologize for the mistake. The abstract and keywords have been revised to meet the specifications.}
+	\reply {We apologize for the mistake. The abstract and keywords have been refined to meet the specifications.}
 
@@
 	\reply {We have revised the manuscript to ensure consistency with the notation introduced in Section~\ref{m-sc:introduction}.
-In the provided example, $\alpha_k \in \mathbb{I}$ refers to $\alpha_k \in \mathbb{I}^1$ and the $1$ was omitted for brevity.}
+In this example, $\alpha_k \in \mathbb{I}$ refers to $\alpha_k \in \mathbb{I}^1$ and the $1$ was omitted for brevity.}
 
@@
 QoS refers to the relative priority of the primary link, and it should be either ``QoS'' or ``relative priority''.
-We have added a footnote on this.
+We have added footnote \ref{m-fn:qos} on this.
 Besides, the information theory subsection (including the derivation of eqs.
-(17-19)) has been rewritten and incorporated into Section II.B with proper explanation.
+(17-19)) has been rewritten and incorporated into Section~\ref{m-sc:system_model} with proper explanation.
 We also modified Remark \ref{m-re:dynamic_passive_beamforming} and added Remark \ref{m-re:independent_encoding} to clarify the derivation of achievable rates.
@@
 	\reply {The BCD algorithm is convergent for the optimization problem (20), since the input distribution and active beamforming subproblems converge and the thresholding subproblem attains global optimality.
-This argument has been added prior to the convergence results in Fig.
-7.}
+This argument has been added prior to the convergence results in Fig.~\subref*{m-fg:wsr_convergence}.}
 
@@
 The choice of $s \sim \mathcal{CN} (0,1)$ is generally not optimal for weighted sum mutual information.
-To the best of our knowledge, the optimal primary distribution in this case remains an open issue, but some insights were given in those papers:
+To the best of our knowledge, the optimal primary distribution in this case remains an open issue, but some insights were given in these papers:
 		\begin{itemize}
-			\item If there is no direct link and the node is with \emph{average} power constraint, then the optimal distribution for \emph{weighted sum mutual information} requires a time-sharing between those modes \cite{Pillai2011}:
+			\item If there is no direct link and the node is with \emph{average} power constraint, then the optimal distribution for \emph{weighted sum mutual information} requires a time-sharing between these modes \cite{Pillai2011}:
 			\begin{itemize}
@@
 \begin{reviewer}
-	The paper studies the achievable rates for both primary transmission and backscatter information, assuming a Gaussian distribution for primary transmission and K tags (with M loads each) and a single source-destination primary link; the authors assume full CSI knowledge and formulate a mutual information maximization problem, with probability distribution of loads per tag as a function to be optimized (in conjunction with beamforming weights for the multi-antenna transmitter and energy thresholds for the energy-based detector for the backscatter information).
+	The paper studies the achievable rates for both primary transmission and backscatter information, assuming a Gaussian distribution for primary transmission and $K$ tags (with $M$ loads each) and a single source-destination primary link; the authors assume full CSI knowledge and formulate a mutual information maximization problem, with probability distribution of loads per tag as a function to be optimized (in conjunction with beamforming weights for the multi-antenna transmitter and energy thresholds for the energy-based detector for the backscatter information).
 The problem is non-convex and challenging, and the authors revert to a series of approximations to relax it and offer a solution.
@@
 CSCG distribution $\mathcal{CN}(0, \iota \Lambda_\text{C})$, $\iota$ is the relative estimation error, and $\Lambda_\text{C}$ is the cascaded path loss.
+		In Fig.~\ref{fg:region_csi}, it is observed that the channel estimation error mainly affects the backscatter rate.
+		When $\iota$ increases from \num{0} to \num{0.2}, the maximum total backscatter rate decreases by \qty{20}{\percent}.
+		This is because the energy detector is sensitive to the DMMAC and thus $\hat{\boldsymbol{h}}_{\text{C},k}$.
+		On the other hand, a small estimation error may be insufficient to change the optimal passive beamforming state (especially for a small $M$) and the primary rate is almost unchanged in this case.
+		We have added the result and discussion on imperfect CSI in page~\pageref{m-fg:region_csi}.
 	}
+	\begin{figure}[!t]
+		\centering
+		\resizebox{0.48\columnwidth}{!}{
+			\input{../assets/simulation/region_csi.tex}
+		}
+		\caption{
+			Average primary-total-backscatter rate regions vs imperfect cascaded CSI.
+		}
+		\label{fg:region_csi}
+	\end{figure}
 
@@
 If they are not satisfied, some penalty can be introduced to the achievable rate and it is left for future work.
-We have incorporated the above discussions in the revised manuscript.}
+We have incorporated the above discussions in footnote \ref{m-fn:integrated_receiver}.}
 
@@
 When multiple nodes are co-located, they can jointly encode by designing the joint probability $p(x_{m_{\mathcal{K}}})$ directly.
-This formulates an augmented backscatter source and becomes a special case of above.
+This formulates an augmented backscatter source and becomes a special case of independent encoding.
+In the revised manuscript, we have clarified the above points in Remark~\ref{m-re:augmented_source} and footnote~\ref{m-fn:joint_encoding}.
 Regarding the observation in Fig.
@@
 Instead of explicitly designing the value of load impedance, we assume that they have been designed to fulfill the reflection coefficient codebook.
-The node input distribution (not the reflection coefficient codebook) is indeed adaptive to CSI, as mentioned in Section III.A.
+The node input distribution (not the reflection coefficient codebook) is indeed adaptive to CSI, as mentioned in Section~\ref{m-sc:input_distribution}.
 We have clarified the above points in the revised manuscript.}
@@
 To support massive RIScatter networks with large number of nodes and states, one possible future direction is to consider backscatter detection over the received signal domain rather than energy domain, where multi-antenna \cite{Liu2022c} and learning-based approaches can be promising.
-We have added this to the conclusion part of the revised manuscript.}
+We have added this to Section~\ref{m-sc:conclusion} of the revised manuscript.}
 
@@
 It validates the feasibility of using batteryless devices to adaptively enhance the SNR of the primary link.
-This reference makes the literature review more comprehensive, and we have added it to the revised manuscript.}
+This reference makes the literature review more comprehensive, and we have added it in page~\pageref{m-cm:2.5} of the revised manuscript.}
 \end{reviewer}
@@
 The introduction and contribution have been refined in precise and explicit words for improved readability and clarity.
-Also, we have completely rewritten Section II.A on RIScatter principles to highlight the key differences between RIScatter and existing techniques.
-Remark 1 now emphasizes the distinction and relationship between RIScatter and dynamic RIS.
+Also, we have completely rewritten Section~\ref{m-sc:principles} on RIScatter principles to highlight the key differences between RIScatter and existing techniques.
+Remark~\ref{m-re:dynamic_passive_beamforming} now emphasizes the distinction and relationship between RIScatter and dynamic RIS.
 We also apologize for the poor English usage.
@@
 	\end{itemize}
-	\reply {We appreciate your expert and insightful comments on the reference list. Those papers have been incorporated into the revised manuscript.}
+	\reply {We appreciate your insightful comments on the reference list. Those papers have been incorporated into the literature review.}
 
@@
 In the revised manuscript, we have added explicit results on the achievable region vs primary SNR and backscatter SNR.
-However, we do not include BER vs SNR because (1) we have reached the page limit and (2) the BER performance is not the focus of this paper.
-We appreciate your understanding in this matter.}
+		Interestingly, Fig.~\subref*{fg:region_snr_primary} shows that increasing the primary SNR can improve the primary rate but degrade the backscatter rate.
+		The reason is that the relative strength of the scattered signal compared to the direct signal is weakened, such that the nodes cannot make enough difference to the energy detector.
+		This emphasizes the importance of accounting the primary-backscatter tradeoff in active-passive coexisting networks.
+		Fig.~\subref*{fg:region_snr_backscatter} shows that the primary and backscatter rates are both improved when the backscatter SNR increases.
+		This motivates one to use high-efficiency or semi-passive RIScatter nodes to improve the overall performance.
+		In a multi-user RIScatter network, each node may be assigned to the nearest user to guarantee uniformly good performance for both links.
+		The above results are added to Section~\ref{m-sc:simulation_results}.
+		However, we do not include BER vs SNR because we have reached the page limit and the BER performance is not the focus of this paper. We appreciate your understanding in this matter.}
 
+	\begin{figure}[!t]
+		\centering
+		\subfloat[Primary SNR\label{fg:region_snr_primary}]{
+			\resizebox{0.48\columnwidth}{!}{
+				\input{../assets/simulation/region_snr_primary.tex}
+			}
+		}
+		\subfloat[Backscatter SNR\label{fg:region_snr_backscatter}]{
+			\resizebox{0.48\columnwidth}{!}{
+				\input{../assets/simulation/region_snr_backscatter.tex}
+			}
+		}
+		\label{fg:region_config}
+	\end{figure}
 \end{reviewer}

### 2023-08-05 main.tex
:speech_balloon: Update response

@@
 	In contrast, \cite{Vardakis2023} exploits commodity \gls{rfid} tags, powered and controlled by a software-defined radio reader, to perform passive beamforming (but no backscatter modulation) towards a legacy user at a different frequency.
+\label{cm:2.5}
 	% The authors demonstrated the feasibility of using batteryless devices to adaptively enhance the \gls{snr} of a primary link, but did not consider backscatter modulation at.
@@
 	The reflection pattern over time is semi-random and guided by the input probability assigned to each state.
-	This probability distribution is carefully designed to incorporate the backscatter information, \gls{csi}, and \gls{qos}\footnote{\gls{qos} refers to the relative priority of the primary link.}.
+	This probability distribution is carefully designed to incorporate the backscatter information, \gls{csi}, and \gls{qos}\footnote{\gls{qos} refers to the relative priority of the primary link.\label{fn:qos}}.
 	Such an adaptive channel coding boils down to the degenerate distribution of \gls{ris} when the primary link is prioritized, and outperforms the uniform distribution of \gls{bc} (by accounting the \gls{csi}) when the backscatter link is prioritized.
@@
 		RIScatter nodes can be implemented, for example, by adding an integrated receiver\footnote{The aim is to coordinate the node with the active source and to acquire the optimized input distribution, instead of decoding the primary information dedicated for the user.
-The node receiver can be implemented using very simple circuits or even integrated with the rectifier \cite{Kim2021a} to reduce cost and complexity.} \cite{Kim2021a} and adaptive encoder \cite{He2020e} to off-the-shelf passive \gls{rfid} tags.
+The node receiver can be implemented using very simple circuits or even integrated with the rectifier \cite{Kim2021a} to reduce cost and complexity.\label{fn:integrated_receiver}} \cite{Kim2021a} and adaptive encoder \cite{He2020e} to off-the-shelf passive \gls{rfid} tags.
 		The block diagram, equivalent circuit, and scatter model are illustrated in Fig.~\ref{fg:riscatter_node}.
@@
 	\begin{subsection}{System Model}
-		\label{se:system_model}
+		\label{sc:system_model}
 		\begin{figure}[!t]
@@
 	where $\rho \in \mathbb{I}$ is the \gls{qos}.
-	To obtain the achievable primary-(total-)backscatter rate region, we consider the weighted sum mutual information maximization problem with independent encoding at all nodes\footnote{Joint encoding over multiple nodes can be viewed as its special case with an augmented source.}
+	To obtain the achievable primary-(total-)backscatter rate region, we consider the weighted sum mutual information maximization problem with independent encoding at all nodes\footnote{Joint encoding over multiple nodes can be viewed as its special case with an augmented source.\label{fn:joint_encoding}}.
 	\begin{maxi!}
@@
 	\begin{subsection}{Input Distribution}
+		\label{sc:input_distribution}
 		For any given $\boldsymbol{w}$ and $\boldsymbol{t}$, we can formulate a \gls{dmmac} by \eqref{eq:dmmac} and simplify \eqref{op:weighted_sum_rate} to
@@
 			}
-			\subfloat[Input States\label{fg:region_states}]{
+			\subfloat[Reflection States\label{fg:region_states}]{
 				\resizebox{0.48\columnwidth}{!}{
@@
 					\input{assets/simulation/region_csi.tex}
+				}
+			}
+			\\
+			\subfloat[Primary \gls{snr}\label{fg:region_snr_primary}]{
+				\resizebox{0.48\columnwidth}{!}{
+					\input{assets/simulation/region_snr_primary.tex}
+				}
+			}
+			\subfloat[Backscatter \gls{snr}\label{fg:region_snr_backscatter}]{
+				\resizebox{0.48\columnwidth}{!}{
+					\input{assets/simulation/region_snr_backscatter.tex}
 				}
@@
 			Fig.~\subref*{fg:region_noise} depicts the impact of average noise power $\sigma_v^2$ on average rate regions.
-			It shows the proposed practical semi-coherent backscatter energy detection is suitable for a wide range of noise levels.
-			When $\sigma_v^2$ relatively high, one can choose a larger $N$ to maintain the backscatter \gls{snr} for better energy detection performance.
+			Note that the noise influences both primary and backscatter \gls{snr}.
+			% It shows the proposed adaptive energy detector is suitable for a wide range of noise levels.
+			When $\sigma_v^2$ relatively high, one can choose a larger $N$ to improve the energy detection \gls{snr}.
 		\end{subsubsection}
@@
 			This is because the energy detector is sensitive to the \gls{dmmac} \eqref{eq:dmmac} and thus $\hat{\boldsymbol{h}}_{\text{C},k}$.
-			On the other hand, a small estimation error may be insufficient to change the optimal passive beamforming state (especially for a small $M$) and the primary rate is almost unchanged here.
+			On the other hand, a small estimation error may be insufficient to change the optimal passive beamforming state (especially for a small $M$) and the primary rate is almost unchanged in this case.
+		\end{subsubsection}
+
+		\begin{subsubsection}{Primary \gls{snr}}
+			\label{sc:primary_snr}
+			The backscatter \gls{snr} is fixed to \qty{0}{dB} in this study.
+			Interestingly, Fig.~\subref*{fg:region_snr_primary} shows that increasing the primary \gls{snr} can improve the primary rate but degrade the backscatter rate.
+			The reason is that the relative strength of the scattered signal compared to the direct signal is weakened, such that the nodes cannot make enough difference to the energy detector.
+			% This, together with Fig.~\subref*{fg:region_beamforming} and \subref*{fg:region_tags}, emphasizes the importance of balancing the primary and backscatter \gls{snr} in active-passive coexisting networks.
+			This, together with Fig.~\subref*{fg:region_beamforming} and \subref*{fg:region_tags}, emphasizes the importance of accounting the primary-backscatter tradeoff in active-passive coexisting networks.
+		\end{subsubsection}
+
+		\begin{subsubsection}{Backscatter \gls{snr}}
+			The primary \gls{snr} is fixed to \qty{20}{dB} in this study.
+			Fig.~\subref*{fg:region_snr_backscatter} shows that the primary and backscatter rates are both improved when the backscatter \gls{snr} increases.
+			This motivates one to use high-efficiency or semi-passive RIScatter nodes to improve the overall performance.
+			In a multi-user RIScatter network, each node may be assigned to the nearest user to guarantee uniformly good performance for both links.
 		\end{subsubsection}
@@
 \begin{section}{Conclusion}
+	\label{sc:conclusion}
 	This paper introduced RIScatter as a novel scatter protocol that bridges backscatter modulation and passive beamforming.

### 2023-08-06 review/response.tex
:pencil: Update manuscript and response

@@
 In RIS literatures, $\beta_m$ measures the scattering ratio of one element at state $m$.
-In the revised manuscript, we have unified those notation in page~\pageref{m-eq:backscatter_modulation} and revised the term ``tag'' to ``node'' in the appendix.}
+In the revised manuscript, we have unified those notation in page~\pageref{m-eq:backscatter_modulation}, modified footnote~\ref{m-fn:scattering_ratio}, and revised the term ``tag'' to ``node'' in the appendix.}
 
 	\point The expression in eq. (1) represents the conjugate of the reflection coefficient, not the reflection coefficient itself.
-	\reply {After a careful investigation, we found there are three different definitions for the reflection coefficient in the literature:
+	\reply {After a careful investigation, we found there are at least three different definitions for the reflection coefficient in the literature:
 		\begin{enumerate}
@@
 	\reply {The BCD algorithm is convergent for the optimization problem (20), since the input distribution and active beamforming subproblems converge and the thresholding subproblem attains global optimality.
-This argument has been added prior to the convergence results in Fig.~\subref*{m-fg:wsr_convergence}.}
+This argument has been added in the discussion of Fig.~\ref{m-fg:wsr_convergence}.}
 

### 2023-08-06 main.tex
:pencil: Update manuscript and response

@@
 	The key is to render the probability distribution of reflection states as a joint function of the information source, \gls{csi}, and relative priority of coexisting links.
-	This enables RIScatter to softly bridge \gls{bc} and \gls{ris}; reduce to either under specific distribution; or evolve in a mixed form for heterogeneous traffic control and universal hardware design.
+	This enables RIScatter to softly bridge \gls{bc} and \gls{ris}; reduce to either under specific setup; or evolve in a mixed form for heterogeneous traffic control and universal hardware design.
 	We also propose a low-complexity \gls{sic}-free receiver that exploits the properties of RIScatter.
@@
 	Such a coexistence is classified into commensal (overlay), parasitic (underlay), and competitive (interfering) paradigms, and their achievable rate and outage performance were investigated in \cite{Guo2019b,Ding2020}.
-	The achievable rate and optimal input distribution for binary-input \gls{ambc} are investigated in \cite{Qian2019b}, but its impact on the primary link is not considered.
+	The achievable rate and optimal input distribution for binary-input \gls{ambc} are investigated in \cite{Qian2019b}, but its impact on the primary link is omitted.
 	% For binary-input \gls{ambc},  are investigated in \cite{Qian2019b}, but the authors did not consider its impact on the primary link.
@@
 		\item Primary and backscatter symbols are superimposed by \emph{double modulation} (i.e., multiplication coding);
-		\item Backscatter signal strength is much weaker than primary due to the \emph{double fading} effect;
+		\item Backscatter signal strength is much weaker than primary due to \emph{double fading};
 		\item The spreading factor (i.e., backscatter symbol duration over primary) is usually large\footnote{The load-switching interval of low-power backscatter modulators is usually \num{0.1} to \qty{10}{\us} \cite{Torres2021}, accounting for a typical spreading factor between \num{10} and \num{e3}.}.
@@
 	The second property motivated \cite{Long2020a,Liang2020,Guo2019b,Ding2020,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Yang2018,Han2021,Zhang2022,Dai2023} to view \gls{sr} as a multiplicative \gls{noma} and perform \gls{sic} from primary to backscatter link.
-	During primary decoding, the backscatter signal can be modelled as channel uncertainty or multiplicative interference when the spreading factor is large or small, respectively.
+	During primary decoding, the backscatter signal can be modelled as channel uncertainty or multiplicative interference, when the spreading factor is large or small.
 	Decoding each backscatter symbol also requires multiple \gls{sic} followed by a \gls{mrc} over primary blocks, which is operation-intensive and \gls{csi}-sensitive.
 	Under those assumptions, the achievable rate region of cell-free \gls{sr} is characterized in \cite{Dai2023}.
-	When the spreading factor is sufficiently large, the primary achievable rate under semi-coherent detection\footnote{In this paper, semi-coherent detection refers to the primary/backscatter decoding with known \gls{csi} and unknown backscatter/primary symbols.} asymptotically approaches its coherent counterpart and both links are decoded interference-free \cite{Long2020a}.
-	However, this severely limits the backscatter throughput and requires numerous \gls{sic} per backscatter symbol.
+	When the spreading factor is sufficiently large, the primary achievable rate under semi-coherent detection\footnote{In this paper, semi-coherent detection refers to the primary/backscatter decoding with known \gls{csi} and unknown backscatter/primary symbols.} asymptotically approaches its coherent counterpart such that both links are approximately interference-free \cite{Long2020a}.
+	However, this assumption severely limits the backscatter throughput.
 
@@
 	Those \gls{ris}-based backscatter modulation schemes incur advanced hardware architecture and high optimization complexity.
-	In contrast, \cite{Vardakis2023} exploits commodity \gls{rfid} tags, powered and controlled by a software-defined radio reader, to perform passive beamforming (but no backscatter modulation) towards a legacy user at a different frequency.
+	In contrast, \cite{Vardakis2023} exploits commodity \gls{rfid} tags, powered and controlled by a software-defined radio reader at a different frequency, to perform passive beamforming (but no backscatter modulation) towards a legacy user.
 \label{cm:2.5}
@@
 	\emph{First,} we propose RIScatter as a novel protocol that unifies \gls{bc} and \gls{ris} by adaptive reflection state (backscatter input) distribution design.
-	The concept is shown in Fig.~\subref*{fg:riscatter} where one or more RIScatter nodes ride over an active transmission, simultaneously modulating their information and engineering the wireless channel.
+	The concept is shown in Fig.~\subref*{fg:riscatter}, where one or more RIScatter nodes ride over an active transmission to simultaneously modulate their information and engineer the wireless channel.
 	A co-located receiver cooperatively decodes both coexisting links.
@@
 	Table~\ref{tb:scattering_applications} compares RIScatter to \gls{bc} and \gls{ris}.
-	However, two major challenges for RIScatter are the practical receiver and input distribution design.
+	However, two major challenges for RIScatter are the receiver design and input distribution design.
 	This is the first paper to unify \gls{bc} and \gls{ris} from the perspective of input distribution.
@@
 	It semi-coherently decodes the weak backscatter signal using an energy detector, re-encodes for the exact reflection pattern, then coherently decodes the primary link.
-	Thanks to double modulation, the backscatter detection becomes part of channel training, and the impact of backscatter modulation can be modelled as dynamic passive beamforming.
-	The proposed receiver may be built over legacy receivers with minor hardware upgrade, since it only requires one additional energy comparison and re-encoding per backscatter symbol (instead of primary symbol).
+	Thanks to double modulation, backscatter detection can be viewed as part of channel training, and the impact of backscatter modulation can be modelled as dynamic passive beamforming afterwards.
+	The proposed receiver may be built over legacy receivers with minor hardware upgrade, as it only requires one additional energy comparison and re-encoding per backscatter symbol (instead of primary symbol).
 	The energy detector can also be tailored for arbitrary input distribution and spreading factor to increase backscatter throughput.
-	This is the first paper to propose a \gls{sic}-free receiver for active-passive coexisting networks.
+	This is the first paper to propose a \gls{sic}-free cooperative receiver for active-passive coexisting networks.
 
@@
 	We characterize the achievable primary-(total-)backscatter rate region by optimizing the input distribution at RIScatter nodes, the active beamforming at the \gls{ap}, and the energy decision regions at the user under different \gls{qos}.
-	A \gls{bcd} algorithm is proposed where the \gls{kkt} input distribution is numerically evaluated by limit of sequences, the active beamforming is optimized by \gls{pga}, and the decision regions are refined by existing sequential quantizer for \gls{dmtc}.
+	A \gls{bcd} algorithm is proposed where the \gls{kkt} input distribution is numerically evaluated by limit of sequences, the active beamforming is optimized by \gls{pga}, and the decision regions are refined by state-of-the-art sequential quantizer designs for \gls{dmtc}.
 	Uniquely, our optimization problem takes into account the \gls{csi}, \gls{qos}, and backscatter constellation, and the resulting input distribution is applicable to any detection scheme.
@@
 		In the scattered signal, the structural mode component depends on the scatterer geometry and material.
-		Its impact is usually modelled as part of environment multipath \cite{Thomas2012,Liang2020}, or simply a \gls{dc} offset in the baseband signal when the impinging signal is a \gls{cw} \cite{Boyer2014}.
+		Its impact is usually modelled as part of environment multipath \cite{Thomas2012,Liang2020}, or simply a baseband \gls{dc} offset when the impinging signal is a \gls{cw} \cite{Boyer2014}.
 		On the other hand, the antenna mode component depends on the impedance mismatch and is widely exploited in scattering applications.
@@
 			\end{equation}
-			where $\alpha_m \in \mathbb{I}$ is the amplitude scattering ratio and $c_m$ is the constellation point.
+			where $\alpha_m \in \mathbb{I}$ is the amplitude scattering ratio at state $m$, and $c_m$ is the corresponding constellation point.
 			\item \gls{ris}: The scatterer is a channel shaper with deterministic reflection pattern over time.
@@
 			\end{equation}
-			where $\theta_m$ is the phase shift.\footnote{It is commonly assumed $\alpha_m \ll 1$ in \gls{bc} and $\alpha_m=1$ in \gls{ris}.}
+			where $\theta_m$ is the phase shift at state $m$.\footnote{Most papers assume $\alpha_m = \alpha$, with $\alpha \ll 1$ for \gls{bc} and $\alpha=1$ for \gls{ris}.\label{fn:scattering_ratio}}
 		\end{itemize}
@@
 		RIScatter nodes can be implemented, for example, by adding an integrated receiver\footnote{The aim is to coordinate the node with the active source and to acquire the optimized input distribution, instead of decoding the primary information dedicated for the user.
-The node receiver can be implemented using very simple circuits or even integrated with the rectifier \cite{Kim2021a} to reduce cost and complexity.\label{fn:integrated_receiver}} \cite{Kim2021a} and adaptive encoder \cite{He2020e} to off-the-shelf passive \gls{rfid} tags.
+The node receiver can be implemented using simple circuits or even integrated with the rectifier \cite{Kim2021a} to reduce cost and complexity.\label{fn:integrated_receiver}} \cite{Kim2021a} and adaptive encoder \cite{He2020e} to off-the-shelf passive \gls{rfid} tags.
 		The block diagram, equivalent circuit, and scatter model are illustrated in Fig.~\ref{fg:riscatter_node}.
@@
 		As shown in Fig.~\ref{fg:riscatter_network}, we consider a RIScatter network where a $Q$-antenna \gls{ap} serves a single-antenna user and $K$ nearby dispersed or co-located RIScatter nodes.
-		All nodes have $M$ available reflection states.
+		Without loss of generality, we assume all nodes have $M$ available reflection states.
 		In the primary point-to-point system, the \gls{ap} transmits information to the user over a multipath channel\footnote{It is assumed the primary symbol duration is much longer than multipath delay spread (i.e., no inter-symbol interference).} enhanced by RIScatter nodes.
-		In the backscatter multiple access system, the \gls{ap} acts as carrier emitter, the RIScatter nodes modulate over scattered signal, and the user jointly decodes all node messages.\footnote{It is assumed the signal going through two or more RIScatter nodes is too weak to be received by the user.}
+		In the backscatter multiple access system, the \gls{ap} acts as a carrier emitter, the RIScatter nodes modulate over the scattered signal, and the user jointly decodes all nodes.\footnote{It is assumed the signal going through two or more RIScatter nodes is too weak to be received by the user.}
 		For simplicity, we consider a quasi-static block fading model and focus on a specific channel block where the \gls{csi} remains constant.
@@
 
-		Let $\alpha_k \in \mathbb{I}$ be the amplitude scattering ratio of node $k$, $x_k \in \mathcal{X} \triangleq \{c_1,\ldots,c_M\}$ be the coded backscatter symbol of node $k$, and $x_{\mathcal{K}} \triangleq (x_1,\ldots,x_K)$ be the backscatter symbol tuple of all nodes.
-		As a sequence of double modulation, the composite channel is a function of backscatter symbol tuple\footnote{\eqref{eq:equivalent_channel_bc} and \eqref{eq:equivalent_channel_ris} are often used in \gls{bc} and \gls{ris} literature, respectively.}
+		Let $\alpha_k = \in \mathbb{I}$ be the amplitude scattering ratio of node $k$, $x_k \in \mathcal{X} \triangleq \{c_1,\ldots,c_M\}$ be the (coded) backscatter symbol of node $k$, and $x_{\mathcal{K}} \triangleq (x_1,\ldots,x_K)$ be the backscatter symbol tuple of all nodes.
+		Due to double modulation, the composite channel is a function of backscatter symbol tuple\footnote{\eqref{eq:equivalent_channel_bc} and \eqref{eq:equivalent_channel_ris} are often used in \gls{bc} and \gls{ris} literature, respectively.}
 		\begin{subequations}
@@
 		\end{equation}
-		where $\boldsymbol{w} \in \mathbb{C}^{Q}$ is the active beamformer satisfying $\lVert \boldsymbol{w} \rVert^2 \le P$, $P$ is the average transmit power budget, $s \sim \mathcal{CN}(0,1)$ is the primary symbol, and $v \sim \mathcal{CN}(0,\sigma_v^2)$ is the \gls{awgn} with variance $\sigma_v^2$.
+		where $\boldsymbol{w} \in \mathbb{C}^{Q}$ is the active beamformer satisfying $\lVert \boldsymbol{w} \rVert^2 \le P$, $P$ is the maximum average transmit power, $s \sim \mathcal{CN}(0,1)$ is the primary symbol, and $v \sim \mathcal{CN}(0,\sigma_v^2)$ is the \gls{awgn} with variance $\sigma_v^2$.
 
@@
 		The user first jointly decodes the backscatter message of all nodes using a low-complexity energy detector.\footnote{The reliability of the energy detector is improved by the adaptive input distribution and thresholding design.
-With high-order modulation or large number of scatter nodes, the reliability can be further enhanced by increasing the spreading factor or using error correction codes with lower code-rate.
+With high-order modulation or large number of scatter nodes, the reliability can be further enhanced by increasing the spreading factor or using error correction codes with low code-rate.
 In practice, users can decode backscatter nodes ranging from a few to hundreds of meters in the presence of noise and interference, and the backscatter throughput can reach few Kbps to tens of Mbps \cite{Wu2022e}.\label{fn:energy_detector}}
-		Then, the user decodes the primary message using the \gls{ml} detector.
 		The energy detector formulates a \gls{dmtc} of size $M^K \times M^K$.
@@
 			The capacity-achieving decision region design for \gls{dmtc} with non-binary inputs in arbitrary distribution remains an open issue.
-			It was proved deterministic detectors can be rate-optimal, but non-convex regions (comprise non-adjacent partitions) are generally required and the optimal number of thresholds is unknown \cite{Nguyen2018,Nguyen2021}.
+			It was proved deterministic detectors can be rate-optimal, but non-convex regions (consist of non-adjacent partitions) are generally required and the optimal number of thresholds is unknown \cite{Nguyen2018,Nguyen2021}.
 			Next, we restrict the energy detector to convex deterministic decision regions and consider sequential threshold design.
@@
 		Sort $\{\sigma_{m_{\mathcal{K}}}^2\}$ in ascending order and denote the result sequence as $\sigma_1^2,\ldots,\sigma_L^2$.
-		With sequential thresholding, the decision region of backscatter symbol tuple $l \in \mathcal{L} = \{1,\ldots,L\}$ is\footnote{$m_{\mathcal{K}}$ and $l$ are one-to-one and used interchangeably in the following context.}
+		With sequential thresholding, the decision region of backscatter symbol tuple $l \in \mathcal{L} = \{1,\ldots,L\}$ is\footnote{$m_{\mathcal{K}}$ and $l$ are one-to-one mapped.
+Both notations are used interchangeably in the following context.}
 		\begin{equation}
@@
 
-		Once the backscatter information is successfully decoded, the user re-encodes to recover the exact reflection pattern and thus the composite channel by \eqref{eq:equivalent_channel}, then coherently decodes the primary link.
+		Once the backscatter information is successfully decoded, the user re-encodes to recover the reflection pattern, constructs the composite channel by \eqref{eq:equivalent_channel}, then coherently decodes the primary link.
 		The primary mutual information is
@@
 	where $\rho \in \mathbb{I}$ is the \gls{qos}.
-	To obtain the achievable primary-(total-)backscatter rate region, we consider the weighted sum mutual information maximization problem with independent encoding at all nodes\footnote{Joint encoding over multiple nodes can be viewed as its special case with an augmented source.\label{fn:joint_encoding}}.
+	To obtain the achievable primary-(total-)backscatter rate region, we consider the weighted sum mutual information maximization problem with independent encoding at all nodes\footnote{Joint encoding over multiple nodes can be viewed as the special case with an augmented source.\label{fn:joint_encoding}}
 	\begin{maxi!}
@@
 		Problem \eqref{op:active_beamforming} can thus be solved by the \gls{pga} method.
-		At each iteration $r$, the unregulated active beamformer is updated by
-		\begin{equation}
-			\bar{\boldsymbol{w}}^{(r)} = \boldsymbol{w}^{(r-1)}+\gamma\nabla_{\boldsymbol{w}^*} I^{(r-1)}(x_{\mathcal{K}}),
+		At iteration $r+1$, the unregulated active beamformer is updated by
+		\begin{equation}
+			\bar{\boldsymbol{w}}^{(r+1)} = \boldsymbol{w}^{(r)}+\gamma\nabla_{\boldsymbol{w}^*} I^{(r)}(x_{\mathcal{K}}),
 			\label{eq:beamforming_gradient_ascent}
@@
 	\label{sc:simulation_results}
-	In this section, we provide numerical results to evaluate the proposed input distribution, active beamforming, and backscatter decision algorithms.
+	In this section, we provide numerical results to evaluate the proposed algorithms.
 	We assume the AP-user distance is \qty{10}{m} and at least one RIScatter nodes are randomly dropped in a disk centered at the user with radius $r$.
-	The \gls{ap} is with an average transmit power budget $P=\qty{36}{dBm}$ and all nodes employs $M$-\gls{qam} with $\alpha=0.5$.
+	The \gls{ap} is with maximum average transmit power $P=\qty{36}{dBm}$ and all nodes employs $M$-\gls{qam} with $\alpha=0.5$.
 	For all channels involved, we consider a distance-dependent path loss model
@@
 		For \gls{sr}, this comes with the cost of $N$ re-encoding, precoding, subtraction together with a time-domain \gls{mrc} per backscatter symbol.
-		\emph{Second,} the average primary rate slightly decreases/increases in the presence of a \gls{ambc}/\gls{ris} node and the benefit of \gls{sr} is not obvious.
-		This is because the cascaded channel is usually orders of magnitude weaker than the direct channel.
+		\emph{Second,} the average primary rate slightly decreases/increases in the presence of a \gls{ambc}/\gls{ris} node, and the benefit of \gls{sr} is not obvious.
+		This is because the cascaded channel is around \qty{25}{dB} weaker than the direct channel.
 		Here, \gls{ris} ensures constructive superposition of direct and scattered components while \gls{sr} only creates a quasi-static rich-scattering environment that marginally enhances the average primary rate.
-		When $N$ is moderate, the randomly scattered signals should be modelled as interference rather than multipath components and the \gls{sr} point should move towards the \gls{ambc} point.
+		When $N$ is moderate, the randomly scattered signals should be modelled as interference rather than multipath components, and the \gls{sr} point should move towards the \gls{ambc} point.
 		\emph{Third,} RIScatter enables a flexible primary-backscatter tradeoff with adaptive input distribution design.
@@
 		On the other hand, for a large $N$, the maximum backscatter achievable rate of RIScatter is lower than \gls{bbc} and \gls{sr} but higher than \gls{ambc}.
-		This is because both RIScatter and \gls{ambc} employ semi-coherent energy detection, and the adaptive channel coding of RIScatter outperforms the equiprobable inputs of \gls{ambc}, especially at the low backscatter \gls{snr} in the double fading scenario.
-		When multiple antenna is available at the \gls{ap}, active beamforming can be optimized for RIScatter nodes and the backscatter rate gain over \gls{ambc} is more prominent.
+		This is because both RIScatter and \gls{ambc} employ semi-coherent energy detection, and the adaptive channel coding of RIScatter outperforms the equiprobable inputs of \gls{ambc}, especially at low backscatter \gls{snr}.
+		When multiple antenna is available at the \gls{ap}, active beamforming can be optimized for RIScatter nodes and the backscatter rate gain over \gls{ambc} should be more prominent.
 	\end{subsection}
@@
 		At $\rho=0$ where the backscatter performance is prioritized, the optimal input distribution is \num{0} on two states and nearly uniform on the other two.
-		This is inline with Shannon's observation that binary antipodal inputs is good enough for channel capacity at the low \gls{snr} \cite{Shannon1948}.
+		This is inline with Shannon's observation that binary antipodal inputs is good enough for channel capacity at low \gls{snr} \cite{Shannon1948}.
 		Due to the weak scattered signal, the conditional energy \gls{pdf} under different hypotheses can be closely spaced as in Fig.~\ref{fg:energy_distribution}.
@@
 			Fig.~\subref*{fg:region_distribution} shows their average achievable rate regions.
-			It is observed that Cooperation achieves the outer bound of all schemes, but its backscatter rate gain comes at the cost of implementation and computation complexity.
+			It is observed that Cooperation achieves the outer bound of all schemes, but the backscatter rate gain comes at the cost of implementation and computation complexity.
 			Besides, the average rate performance of Exhaustion and \gls{kkt} completely coincide with each other when $K=2$.
@@
 			Equiprobable experiences minor backscatter and major primary rate losses without exploiting \gls{csi} and \gls{qos}.
-			Those gaps should be larger when $M$ and/or $K$ increase.
+			Those gaps should be larger when $M$ or $K$ increases.
 			For the recovery methods, Marginalization provides a close performance to \gls{kkt}, but Randomization and Decomposition fail our expectations for most channel realizations.
@@
 			In the low-$\rho$ regime, the proposed \gls{pga} beamformer significantly outperforms both \gls{mrt} schemes in terms of total backscatter rate.
-			This is because the semi-coherent backscatter decoding relies on the \emph{relative difference} of receive energy under different backscatter symbol tuples.
+			This is because the semi-coherent backscatter decoding relies on the relative energy difference under different backscatter symbol tuples.
 			Such an energy diversity is enhanced by \gls{pga}, which effectively exploits backscatter constellation and input distribution knowledge rather than simply maximizing the direct/ergodic channel strength.
-			As $\rho$ increases, the primary \gls{snr} outweighs the backscatter energy difference in \eqref{eq:weighted_sum_mutual_information_explicit}, and \gls{pga} beamformer approaches both \gls{mrt} schemes.
-			At $\rho=1$, both \gls{pga} and E-\gls{mrt} boil down to \gls{mrt} towards the composite channel.
+			As $\rho$ increases, the primary \gls{snr} outweighs the backscatter energy difference in \eqref{eq:weighted_sum_mutual_information_explicit}, and \gls{pga} beamformer approaches E-\gls{mrt}.
+			At $\rho=1$, both \gls{pga} and E-\gls{mrt} boil down to \gls{mrt} towards the strongest composite channel.
 			The difference between E-\gls{mrt} and D-\gls{mrt} is insignificant when RIScatter nodes are dispersed.
@@
 			The distribution-aware schemes \gls{dp}, \gls{smawk} and Bisection ensure higher total backscatter rate than \gls{ml}.
-			This is because the total backscatter rate \eqref{eq:backscatter_mutual_information} is a function of both input distribution and decision regions, and the rate-optimal threshold design heavily depends on input distribution.
+			This is because the total backscatter rate \eqref{eq:backscatter_mutual_information} is a function of both input distribution and decision regions, and the rate-optimal thresholding depends heavily on the input distribution.
 			For example, the backscatter symbol tuples with zero input probability should be assigned with empty decision regions, in order to increase the success detection rates of other hypotheses.
@@
 		\begin{subsubsection}{Number of Nodes}
-			Fig.~\subref*{fg:region_tags} reveals how the number RIScatter nodes $K$ influence the primary-backscatter tradeoff.
+			Fig.~\subref*{fg:region_tags} reveals how the number RIScatter nodes $K$ influences the primary-backscatter tradeoff.
 			Interestingly, we observe that increasing $K$ has a larger benefit on the total backscatter rate than primary.
@@
 			This accounts for the significant primary rate decrease in the low-$\rho$ regime.
-			On the other hand, when the primary link is prioritized, the RIScatter nodes boil down to \gls{ris} elements and enjoy a conventional passive array gain $K^2$.
+			On the other hand, when the primary link is prioritized, the RIScatter nodes boil down to \gls{ris} elements and enjoy a passive array gain $K^2$.
 		\end{subsubsection}
@@
 		\begin{subsubsection}{Spreading factor}
-			Fig.~\subref*{fg:region_duration} shows how the spreading factor $N$ affects the achievable rate region.\footnote{Please notice in Fig.~\subref*{fg:region_duration} the unit of total backscatter rate is bits per primary block to indicate throughput.}
+			Fig.~\subref*{fg:region_duration} shows how the spreading factor $N$ affects the achievable rate region.\footnote{Here, the unit of total backscatter rate is bits per primary block to show backscatter throughput.}
 			Using a very large $N$ can severely constrain the backscatter throughput, since the gain in energy certainty (by law of large numbers) cannot withstand the loss in gross rate.
 			As $N \to \infty$, RIScatter nodes boil down to static \gls{ris} elements and the total backscatter rate approaches \num{0}.
-			On the other hand, when $N$ is too small, energy detection is error-prone as the \gls{dmmac} \eqref{eq:dmmac} is unreliable.
+			On the other hand, when $N$ is too small, energy detection is error-prone as the \gls{dmmac} \eqref{eq:dmmac} becomes unreliable.
 			It explains the observation that $N=10$ provides lower backscatter throughput than $N=20$.
-			Therefore, we conclude the spreading factor $N$ should be carefully designed over multiple factors (e.g., data rate requirements, load switching speed at the nodes, and signal processing capability at the user).
+			Therefore, we conclude the spreading factor $N$ should be carefully designed over multiple factors (e.g., primary and backscatter \gls{snr}, data rate requirements, load switching speed at the nodes, and signal processing capability at the user).
 		\end{subsubsection}
@@
 			% It shows the proposed adaptive energy detector is suitable for a wide range of noise levels.
-			When $\sigma_v^2$ relatively high, one can choose a larger $N$ to improve the energy detection \gls{snr}.
+			When $\sigma_v^2$ relatively high, one can choose a larger $N$ to improve the \gls{snr} of energy detection.
 		\end{subsubsection}
@@
 			The reason is that the relative strength of the scattered signal compared to the direct signal is weakened, such that the nodes cannot make enough difference to the energy detector.
-			% This, together with Fig.~\subref*{fg:region_beamforming} and \subref*{fg:region_tags}, emphasizes the importance of balancing the primary and backscatter \gls{snr} in active-passive coexisting networks.
-			This, together with Fig.~\subref*{fg:region_beamforming} and \subref*{fg:region_tags}, emphasizes the importance of accounting the primary-backscatter tradeoff in active-passive coexisting networks.
+			This, together with Fig.~\subref*{fg:region_beamforming} and \subref*{fg:region_tags}, emphasizes the importance of balancing the primary and backscatter \gls{snr} in the design of active-passive coexisting networks.
+			% This, together with Fig.~\subref*{fg:region_beamforming} and \subref*{fg:region_tags}, emphasizes the importance of primary-backscatter tradeoff in active-passive coexisting networks.
 		\end{subsubsection}
@@
 	To support massive RIScatter networks with large number of nodes and states, one possible future direction is to consider backscatter detection over the received signal domain rather than energy domain, where multi-antenna \cite{Liu2022c} and learning-based approaches can be promising.
-	Another interesting question is how to design RIScatter node and receiver in a multi-user system to fully exploit the dynamic passive beamforming that naturally origins from backscatter modulation.
+	Another interesting question is how to design RIScatter nodes and receivers in a multi-user system to fully exploit the dynamic passive beamforming that naturally origins from backscatter modulation.
 \end{section}

### 2023-08-10 src/plot/plot_convergence.m
:speech_balloon: Update WSR unit as bpcu

@@ -14,7 +14,7 @@ hold off; legend('Location', 'se'); grid on; box on;
 nexttile;
 plotHandle(2) = plot(0 : length(convergence.pgd) - 1, convergence.pgd, 'DisplayName', 'PGD');
 hold off; legend('Location', 'se'); grid on; box on;
-ylabel('Weighed Sum-Rate [bits/s/Hz]');
+ylabel('Weighed Sum-Rate [bits/cu]');
 
 % * BCD
 nexttile;

### 2023-08-12 main.tex
:speech_balloon: Fix label font

@@
 			\label{sc:primary_snr}
-			The backscatter \gls{snr} is fixed to \qty{0}{dB} in this study.
+			The backscatter \gls{snr} is fixed to \qty{0}{dB} with $Q=1$ in this study.
 			Interestingly, Fig.~\subref*{fg:region_snr_primary} shows that increasing the primary \gls{snr} can improve the primary rate but degrade the backscatter rate.
@@
 		\begin{subsubsection}{Backscatter \gls{snr}}
-			The primary \gls{snr} is fixed to \qty{20}{dB} in this study.
+			The primary \gls{snr} is fixed to \qty{20}{dB} with $Q=1$ in this study.
 			Fig.~\subref*{fg:region_snr_backscatter} shows that the primary and backscatter rates are both improved when the backscatter \gls{snr} increases.

### 2023-08-15 review/response.tex
:speech_balloon: Update WSR unit as bpcu
:triangular_flag_on_post: JSAC 230815

@@
 \usepackage{xr}
-\externaldocument[m-]{../main}
+\externaldocument[m-]{../jsac}
 
@@
 	We would like to express our sincere gratitude to you for the valuable comments and suggestions, which helped us improve the quality of the manuscript significantly.
-	Below, we prepare a point-to-point response and describe all the changes made to the manuscript.
+	Below, we prepare a point-to-point response and highlight all the changes made to the manuscript.
 	We hope that the revisions and clarifications make the manuscript meet the standards of JSAC publications.
@@
 		\begin{equation}
-			I(x_{\mathcal{K}}) + \sum_k \nu_k \biggl( \sum_{m_k} p(x_{m_k}) - 1 \biggr) + \sum_k \sum_{m_k} \lambda_{m_k} p(x_{m_k}).
+			L(p, \nu, \lambda) = I(x_{\mathcal{K}}) + \sum_k \nu_k \Bigl( \sum_{m_k} p(x_{m_k}) - 1 \Bigr) + \sum_{k,m_k} \lambda_{m_k} p(x_{m_k}),
 		\end{equation}
@@
 We have justified this in Section~\ref{m-sc:convergence}.
-The unit of the y axis of Fig.~\ref{m-fg:distribution_weights} has been specified as bit/s/Hz.}
+The unit of the y axis of Fig.~\ref{m-fg:distribution_weights} has been specified as bits per channel use.}
 

### 2023-08-15 arxiv.tex
:triangular_flag_on_post: JSAC 230815

--- 2023-02-26 main.tex
@@
 \usepackage{tikz}
-% dark mode
-% \usepackage{xcolor} \pagecolor[rgb]{0,0,0} \color[rgb]{1,1,1}
+
+% page limit hacks
+% \usepackage{setspace}
+% ! \usepackage[top=1cm, bottom=1cm, left=1cm, right=1cm]{geometry}
+% \abovedisplayskip=1mm
+% \belowdisplayskip=1mm
+% \abovedisplayshortskip=1mm
+% \belowdisplayshortskip=1mm
+% \setlength{\jot}{0.1mm}
+% \setlength{\floatsep}{1mm}
+% \setlength{\textfloatsep}{1mm}
+% \setlength{\intextsep}{1mm}
+% \setlength{\skip\footins}{2mm}
 
@@
 \newtheorem{remark}{Remark}
-
-% siunitx
-\DeclareSIUnit{\belm}{Bm}
-\DeclareSIUnit{\dBm}{\deci\belm}
-\DeclareSIUnit{\beli}{Bi}
-\DeclareSIUnit{\dBi}{\deci\beli}
 
@@
 \newacronym{bpsphz}{\si{bps/Hz}}{bits per second per Hertz}
+\newacronym{clt}{CLT}{Central Limit Theorem}
+\newacronym{cw}{CW}{Continuous Waveform}
 \newacronym{cp}{CP}{Canonical Polyadic}
@@
 \maketitle
-% TODO why not use metamaterial? because high computational complexity and expectations of freedom (flexibility, reliability)
-% * cooperative input design can be used for co-located RIScatter nodes.
-% * hardward to modulate using RIS is already available.
-% * RIScatter: enhance backscatter signal characteristics (suppress primary interference) or primary signal strength.
-% ? For Backscatter community: why not adaptive channel coding? For RIS community: why not add randomness for modulation?
-% ? RIS involves nonlinear circuits (e.g., diodes) and impedance design (i.e., perfect mismatching) is tricky for continuous phase shift; discrete candidate set is preferred (2-3 bits optimal)
-% * Redefine RIS using book
-% x Using RIS to encode is not very interesting as controller is anyway usable
-% * Wi-Fi sampling rate 20 MHz (symbol period 50 nS), RFID symbol rate/load-switching speed 100s KHz to 10s MHz [Backscatter Communication], fast load-switching speed is key for high data rate - symbol ratio is not very large
-% * Beamforming can cancel direct interference to avoid the collapse of noncoherent energy detection and enlarge energy gap.
-% ?
-[Reconfigurable Intelligent Surface-Assisted Ambient Backscatter Communication Experimental Assessment]the authors of [5] show that, even in line-of-sight (LOS), the interferences and the desired signal can combine in such a way that the received signals at the reader side in the two states are close in power and only differ by their phases
-% TODO Input probability distribution for discrete-value reflection (backscatter), constellation design for continue-value reflection (RIS)
-% * channel coding: non-adaptive (line-coding) or adaptive (DMC)
-% ? [Turbocharging] Since averaging must be done over a significant period of time to smooth out the variation in the TV transmissions, averaging does not allow rates much higher than 10 kbps [24].
-% ? [mu-code]: use multiple Rxs for noncoherent direct interference cancellation (instead of receive diversity)
-% * backscatter modulation <-> passive beamforming; add adaptive channel coding over (NRZ) line coding.
-% ? semi-coherent: known CSI, unknown primary/backscatter symbols
-% * initialization, convergence, base 2 in simulation
-% * SR analysis can achieve large rate at the cost of large N; RIScatter can achieve slightly lower rate at the same N, but also preserves primary performance for smaller N
-% TODO tradeoff between primary (RIScatter, no SIC) and backscatter (SR, SIC)
-% * SR assume very large N for primary rate analysis.
-However, in such cases SIC is questionable as energy detection over received signal as BBC is already good enough and noncoherent detection can also achieve reasonable performance?
-% x when primary symbols are determined, optimal input distribution at high backscatter SNR is equiprobable for any detection (signal/energy)
-% ? Channel estimation error, coordination issues
-
-% * add table row: adaptive to information source/csi/link weights
-% * explain link weights
-% * add table row: distributions
-% * table to sentences
-% * add primary and backscatter flows to illustrations
-% * discuss table and add challenges in contribution 1
-% * transition challenges (distribution and constellation-adaptive) to contribution 2, 3
-% * think RIScatter applications (use Rui's slides)
 
 \begin{abstract}
-	% \gls{bc} nodes harvest energy from and modulate information over an external electromagnetic wave by manipulating the magnitude, phase, and/or frequency of the scattered signal.
-	% \gls{sr} incorporates a passive scatter node into existing radio networks to create additional propagation path and ride its own information towards the cooperative receiver.
-	% \gls{ris} is a programmable reflector array that adapts the phase shift response to enhance or suppress signal strength in specific directions.
-	\gls{bc} nodes harvest energy from and modulate information over an external electromagnetic wave.
-	\gls{ris} adapts its phase shift response to enhance or attenuate channel strength in specific directions.
-	In this paper, we show how those two seemingly different technologies (and their derivatives) can be unified into a single architecture called RIScatter.
-	RIScatter consists of multiple dispersed or co-located scatter nodes, whose reflection states are adapted to partially modulate their own information and partially engineer the wireless channel.
-	% This contrasts with \gls{bc} (resp. \gls{ris}) where the reflection pattern is exclusively a function of the information symbol (resp. \gls{csi}).
-	The key principle is to render the probability distribution of reflection states as a joint function of the information source, \gls{csi}, and \gls{qos} of coexisting active primary and passive backscatter links.
-	This enables RIScatter to softly bridge \gls{bc} and \gls{ris}; boil down to either under specific input distribution; or evolve in a mixed form for heterogeneous traffic control and universal hardware design.
-	% To accommodate the characteristics of active-passive coexisting networks, we propose a practical \gls{sic}-free receiver
-	To reap the benefits of RIScatter, we also propose a co-located \gls{sic}-free receiver that semi-coherently decodes the backscatter information, recovers the reflection pattern, and coherently decodes the primary link.
-	For a single-user multi-node RIScatter network, we characterize the achievable primary-(total-)backscatter rate region by designing the input distribution at scatter nodes, the active beamforming at the \gls{ap}, and the energy decision regions at the user.
-	Simulation results demonstrate RIScatter nodes can exploit the scattered paths to smoothly shift between backscatter modulation and passive beamforming.
+	\gls{bc} nodes harvest energy from and modulate information over external electromagnetic waves.
+	\gls{ris} adapts its phase shift response to alter channel strength in specific directions.
+	In this paper, we show how those two seemingly different technologies (and their derivatives) can be unified into one architecture called RIScatter.
+	RIScatter consists of dispersed or co-located scatter nodes, whose reflection states are adapted to partially modulate their information and partially engineer the wireless channel.
+	The key is to render the probability distribution of reflection states as a joint function of the information source, \gls{csi}, and relative priority of coexisting links.
+	This enables RIScatter to softly bridge \gls{bc} and \gls{ris}; reduce to either under specific setup; or evolve in a mixed form for heterogeneous traffic control and universal hardware design.
+	We also propose a low-complexity \gls{sic}-free receiver that exploits the properties of RIScatter.
+	For a single-user multi-node network, we characterize the achievable primary-(total-)backscatter rate region by optimizing the input distribution at scatter nodes, the active beamforming at the \gls{ap}, and the energy decision regions at the user.
+	Simulations demonstrate RIScatter nodes can recycle surrounding radios for backscatter modulation and passive beamforming.
 \end{abstract}
@@
 \begin{IEEEkeywords}
-	Input distribution design, energy detection, \gls{sic}-free receiver, symbol-level precoding, active-passive coexisting network, backscatter communication, reconfigurable intelligent surface, ambient backscatter communication, symbiotic radio.
+	Backscatter communication, reconfigurable intelligent surface, active-passive coexisting network, input distribution design, \gls{sic}-free receiver.
 \end{IEEEkeywords}
@@
 \begin{section}{Introduction}
-	% \begin{subsection}{Fundamentals}
+	\label{sc:introduction}
 	\IEEEPARstart{F}{uture} wireless network is envisioned to provide high throughput, uniform coverage, pervasive connectivity, heterogeneous control, and cognitive intelligence for trillions of low-power devices.
-	% As a mature low-power communication technique,
 	\gls{bc} separates a transmitter into a \gls{rf} carrier emitter with power-hungry elements (e.g., synthesizer and amplifier) and an information-bearing node with power-efficient components (e.g., harvester and modulator) \cite{Boyer2014}.
-	% In particular, the node harvests energy from impinging wave and embeds information over scattered signal, and
 	The receiver (reader) can be either co-located or separated with the carrier emitter, known as \gls{mbc} and \gls{bbc} in Fig.~\subref*{fg:mbc} and \subref*{fg:bbc}, respectively.
@@
 	However, conventional backscatter nodes only respond when externally inquired by a nearby reader.
-	% To tackle this, \cite{Liu2013b} proposed \gls{ambc} where battery-free nodes recycle ambient signals (e.g., radio, television and Wi-Fi) to harvest energy and establish connection in between.
 	\gls{ambc} in Fig.~\subref*{fg:ambc} was proposed a decade ago where battery-free nodes recycle ambient signals (e.g., radio, television and Wi-Fi) to harvest energy and establish connections \cite{Liu2013b}.
 	It does not require dedicated power source, carrier emitter, or frequency spectrum, but the backscatter decoding is subject to the strong interference from the primary (legacy) link.
-	% Cooperative \gls{ambc} that employs a co-located receiver to decode both coexisting links was considered in \cite{Yang2018}, and the rate and error performance are evaluated for various detection schemes.
-	To tackle this, cooperative \gls{ambc} \cite{Yang2018} employs a co-located receiver to decode both coexisting links and the concept was further refined as \gls{sr} in Fig.~\subref*{fg:sr} \cite{Liang2020}.
-	% Specifically, the active transmitter generates \gls{rf} wave carrying primary information, the passive node ride extra information over the scattered signal, and the cooperative receiver jointly, individually, or sequentially decodes both links.
-	Specifically, the active transmitter generates \gls{rf} wave carrying primary information, the passive node creates a rich-scattering environment and rides its own information, and the co-located receiver cooperatively decodes both links.
+	To tackle this, cooperative \gls{ambc} \cite{Yang2018} employs a co-located receiver to decode both coexisting links, and the concept was further refined as \gls{sr} in Fig.~\subref*{fg:sr} \cite{Liang2020}.
+	Specifically, the active transmitter generates \gls{rf} wave carrying primary information, the passive node creates a rich-scattering environment and superimposes its own information, and the co-located receiver cooperatively decodes both links.
 	In those \gls{bc} applications, the scatter node is considered as an \emph{information source} and the reflection pattern depends exclusively on the information symbol.
-	% Those \gls{bc} applications employ scatter nodes as pure information sources, and the active primary transmission (if it exists) can be influenced by the randomness of backscatter modulation.
 	On the other hand, \gls{ris} in Fig.~\subref*{fg:ris} is a smart signal reflector with numerous passive elements of adjustable phase shifts.
 	It customizes the wireless environment for signal enhancement, interference suppression, scattering enrichment, and/or non-line-of-sight bypassing \cite{Wu2021b}.
-	Each \gls{ris} element is considered as a \emph{channel adaptor} and the reflection pattern depends exclusively on the \gls{csi}.
-	% In summary, \gls{mbc}/\gls{bbc} (resp.
-\gls{ris}) involves a \emph{single} passive backscatter (resp.
-active primary) link where the passive device modulates information (resp.
-enhances propagation) and the active device generates carrier wave (resp.
-modulated signal).
-	% On the other hand, \gls{ambc} (resp. \gls{sr}) involves \emph{coexisting} active primary and passive backscatter links in a competitive (resp. collaborative) relationship.
-	% In \gls{ambc}, the backscatter link only needs to know the basic information (e.g., operating frequency) of the primary link, while the primary link may be completely unaware of the backscatter link.
-	% In \gls{sr}, relevant \gls{csi} is exploited at the co-located receiver for cooperative decoding, and may also be exploited at the primary transmitter for cooperative active beamforming.
+	Each \gls{ris} element is considered as a \emph{channel shaper} and the reflection pattern depends exclusively on the \gls{csi}.
+
+	As a special case of \gls{cr}, active and passive transmissions coexist and interplay in \gls{ambc} and \gls{sr}.
+	Such a coexistence is classified into commensal (overlay), parasitic (underlay), and competitive (interfering) paradigms, and their achievable rate and outage performance were investigated in \cite{Guo2019b,Ding2020}.
+	The achievable rate and optimal input distribution for binary-input \gls{ambc} are investigated in \cite{Qian2019b}, but its impact on the primary link is omitted.
+	% For binary-input \gls{ambc},  are investigated in \cite{Qian2019b}, but the authors did not consider its impact on the primary link.
+	% The \gls{ber} performance of \gls{ml}, linear, and \gls{sic} receivers are derived over flat fading channels \cite{Yang2018}.
+	% The authors of \cite{Hassani2023} analyzed the energy efficiency and achievable rate region for an \gls{ambc}-aided multi-user downlink \gls{noma} system.
+	In \cite{Hassani2023}, the authors analyzed the energy efficiency and achievable rate region for an \gls{ambc}-aided multi-user downlink \gls{noma} system.
+	However, they assumed equal symbol duration and perfect synchronization for the coexisting links.
+	Importantly, active-passive coexisting networks have three special and important properties:
+	\begin{enumerate}
+		\item Primary and backscatter symbols are superimposed by \emph{double modulation} (i.e., multiplication coding);
+		\item Backscatter signal strength is much weaker than primary due to \emph{double fading};
+		\item The spreading factor (i.e., backscatter symbol duration over primary) is usually large\footnote{The load-switching interval of low-power backscatter modulators is usually \num{0.1} to \qty{10}{\us} \cite{Torres2021}, accounting for a typical spreading factor between \num{10} and \num{e3}.}.
+	\end{enumerate}
+	The second property motivated \cite{Long2020a,Liang2020,Guo2019b,Ding2020,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Yang2018,Han2021,Zhang2022,Dai2023} to view \gls{sr} as a multiplicative \gls{noma} and perform \gls{sic} from primary to backscatter link.
+	During primary decoding, the backscatter signal can be modelled as channel uncertainty or multiplicative interference, when the spreading factor is large or small.
+	Decoding each backscatter symbol also requires multiple \gls{sic} followed by a \gls{mrc} over primary blocks, which is operation-intensive and \gls{csi}-sensitive.
+	Under those assumptions, the achievable rate region of cell-free \gls{sr} is characterized in \cite{Dai2023}.
+	When the spreading factor is sufficiently large, the primary achievable rate under semi-coherent detection\footnote{In this paper, semi-coherent detection refers to the primary/backscatter decoding with known \gls{csi} and unknown backscatter/primary symbols.} asymptotically approaches its coherent counterpart such that both links are approximately interference-free \cite{Long2020a}.
+	However, this assumption severely limits the backscatter throughput.
 
@@
 	\end{figure}
-	% \end{subsection}
 
@@
 			\hiderowcolors
-			                                       & \gls{mbc}/\gls{bbc} & \gls{ambc}                  & \gls{sr} (large spreading factor)               & \gls{ris}           & RIScatter                                                   \\ \midrule
+			                                       & \glsentryshort{mbc}/\glsentryshort{bbc} & \glsentryshort{ambc}        & \glsentryshort{sr} (large spreading factor)                         & \glsentryshort{ris} & RIScatter                                                          \\ \midrule
 			\showrowcolors
@@
 			Primary signal on backscatter decoding & Carrier                                 & Multiplicative interference & Spreading code                                                      & ---                 & Energy uncertainty                                                 \\
-			Backscatter signal on primary decoding & ---                 & Multiplicative interference & \gls{csi} uncertainty                           & Passive beamforming & Dynamic passive beamforming                                 \\
+			Backscatter signal on primary decoding & ---                                     & Multiplicative interference & \glsentryshort{csi} uncertainty                                     & Passive beamforming & Dynamic passive beamforming                                        \\
 			Cooperative devices                    & ---                                     & No                          & Primary transmitter and co-located receiver                         & ---                 & Primary transmitter, scatter nodes, and co-located receiver        \\
-			Sequential decoding                    & ---                 & No                          & Primary-to-backscatter, \gls{sic} and \gls{mrc} & ---                 & Backscatter-to-primary, no \gls{sic}/\gls{mrc}              \\
-			% Primary decoding                        & ---                 & Semi-coherent               & Semi-coherent                                   & Coherent            & Coherent                                                    \\
-			% Backscatter decoding                    & Coherent            & Semi-coherent               & Coherent                                        & ---                 & Semi-coherent                                               \\
-			Reflection pattern depends on          & Information source  & Information source          & Information source                              & \gls{csi}           & Information source, \gls{csi}, and \gls{qos}                \\
+			Sequential decoding                    & ---                                     & No                          & Primary-to-backscatter, \glsentryshort{sic} and \glsentryshort{mrc} & ---                 & Backscatter-to-primary, no \glsentryshort{sic}/\glsentryshort{mrc} \\
+			Reflection pattern depends on          & Information source                      & Information source          & Information source                                                  & \glsentryshort{csi} & Information source, \glsentryshort{csi}, and \glsentryshort{qos}   \\
 			Reflection state distribution          & Equiprobable                            & Equiprobable                & Equiprobable or Gaussian                                            & Degenerate          & Flexible                                                           \\
@@
 
-	% \begin{subsection}{Related Works}
-	As a special case of \gls{cr}, active and passive transmissions coexist and interplay in \gls{ambc} and \gls{sr}.
-	Such a coexistence is classified into commensal (overlay), parasitic (underlay), and competitive paradigms, and their achievable rate and outage performance were investigated in \cite{Guo2019b,Ding2020}.
-	For the co-located cooperative receiver, the \gls{ber} performance of \gls{ml}, linear, and \gls{sic} detectors are derived over flat fading channels \cite{Yang2018}.
-	However, the work assumed equal symbol duration and perfect synchronization for primary and backscatter links.
-	Importantly, active-passive coexisting networks have three special and important properties:
-	\begin{enumerate}
-		\item Primary and backscatter symbols are superimposed by \emph{double modulation} (i.e., multiplication coding);
-		\item Backscatter signal strength is much weaker than primary due to the \emph{double fading} effect;
-		\item The spreading factor (i.e., backscatter symbol duration over primary) is usually large\footnote{The load-switching interval of low-power backscatter modulators is usually \num{0.1} to \qty{10}{\us} \cite{Torres2021}, accounting for a typical spreading factor between \num{10} and \num{e3}.}.
-	\end{enumerate}
-	The second property motivated \cite{Long2020a,Liang2020,Guo2019b,Ding2020,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Yang2018,Han2021,Zhang2022} to view \gls{sr} as a multiplicative \gls{noma} and perform \gls{sic} from primary to backscatter link.
-	During primary decoding, the backscatter signal can be modelled as channel uncertainty or multiplicative interference when the spreading factor is large or small, respectively.
-	Decoding each backscatter symbol also requires multiple \gls{sic} followed by a \gls{mrc} and is operation-intensive and \gls{csi}-sensitive.
-	% Such a \gls{sic} receiver is operation-intensive and \gls{csi}-sensitive because it involves $N$ re-encoding, precoding, subtraction together with a time-domain \gls{mrc} to decode each backscatter symbol.
-	When the spreading factor is sufficiently large, the primary achievable rate under semi-coherent detection\footnote{In this paper, semi-coherent detection refers to the primary/backscatter decoding with known \gls{csi} and unknown backscatter/primary symbols.} asymptotically approaches its coherent counterpart and both links are decoded interference-free \cite{Long2020a}.
-	% However, it significantly increases \gls{sic} operations per backscatter symbol and severely limits the backscatter \emph{throughput}.
-	However, it severely limits the backscatter throughput and requires numerous \gls{sic} per backscatter symbol.
-
-	% On the other hand, efficient backscatter multiple access design remains an open issue for \gls{bc}.
-	% \cite{Xu2021a} proposed a \gls{noma}-based \gls{sr} where the \gls{sic} order depends on the backscatter channel strength, but the performance deteriorates fast as the number of nodes increases.
-	% \gls{tdma}-based \gls{sr} was also considered in \cite{Yang2021a} where each node transmits information during its dedicated slot and harvests energy otherwise.
-	% It enables adaptive transmission time and reflection ratio design but introduces extra coordination cost.
-	% \cite{Vougioukas2019} modifies the load-switching speed to shift the scattered signal to the desired frequency band.
-	% This enables backscatter \gls{fdma} at the cost of larger bandwidth and higher power consumption at the scatter nodes.
-	% To reduce the coordination cost, \cite{Han2021} proposed a random code-assisted multiple access for \gls{sr} and evaluated the asymptotic \gls{sinr} using random matrix theory.
-	% This code-domain solution suffers from the near-far problem and imperfect synchronization, both being severe in \gls{bc}.
-
-	% A comparison of scattering applications is summarized in Table~\ref{tb:scattering_applications}.
-
-	On the other hand, static \gls{ris} design with fixed reflection pattern per channel block has been extensively studied in wireless communication, sensing, and power literature \cite{Wu2018,Zhang2019a,Lin2022,Liu2022,Feng2022,Zhao2022}.
+	On the other hand, static \gls{ris} that employs fixed reflection pattern per channel block has been extensively studied in wireless communication, sensing, and power literature \cite{Wu2018,Zhang2019a,Lin2022,Liu2022,Feng2022,Zhao2022}.
 	Dynamic \gls{ris} performs time sharing between different phase shifts and introduces artificial channel diversity within each channel block.
-	It was first proposed to fine-tune the \gls{ofdm} resource blocks \cite{Yang2020} then extended to the downlink power and uplink information phases of \gls{wpcn} \cite{Wu2021,Wu2021d,Hua2022a}.
-	However, dynamic \gls{ris} carries no information since the reflection state at each time slot is known to the receiver.
-	\gls{ris} can also be used as an index-modulated information source and prototypes have been developed for \gls{psk} \cite{Tang2019a} and \gls{qam} \cite{Dai2020a}.
-	From an information-theoretic perspective, the authors of \cite{Karasik2020} reported that joint transmitter-\gls{ris} encoding achieves the capacity of \gls{ris}-aided finite-input channel and using \gls{ris} as a naive passive beamformer to maximize the receive \gls{snr} is generally suboptimal.
-	This inspired \gls{ris}-empowered \gls{bc} \cite{Liu2019d,Bereyhi2020,Xu2020b,Zhang2021d,Hu2021b,Hua2022,Basar2020,Ma2020a,Yuan2021,Hu2021a} to combine passive beamforming and backscatter modulation in the overall reflection pattern.
+	The idea was first proposed to fine-tune the \gls{ofdm} resource blocks \cite{Yang2020}, then extended to the downlink power and uplink information phases of \gls{wpcn} \cite{Wu2021,Wu2021d,Hua2022a}.
+	However, dynamic \gls{ris} carries no information because the reflection state at a specific time is known to the receiver.
+	\gls{ris} can also be used as an information source, and prototypes have been developed for \gls{psk} \cite{Tang2019a} and \gls{qam} \cite{Dai2020a}.
+	From an information-theoretic perspective, the authors of \cite{Karasik2020} reported that joint transmitter-\gls{ris} encoding achieves the capacity of \gls{ris}-aided finite-input channel, and using \gls{ris} as a naive passive beamformer to maximize the receive \gls{snr} is generally rate-suboptimal.
+	This inspired \cite{Liu2019d,Bereyhi2020,Xu2020b,Zhang2021d,Hu2021b,Hua2022,Basar2020,Ma2020a,Yuan2021,Hu2021a} to combine passive beamforming and backscatter modulation in the overall \gls{ris} design.
 	In particular, \emph{symbol level precoding} maps the information symbols to the optimized \gls{ris} coefficient sets \cite{Liu2019d,Bereyhi2020}, \emph{overlay modulation} superposes the information symbols over a common auxiliary matrix \cite{Xu2020b,Zhang2021d,Hu2021b,Hua2022}, \emph{spatial modulation} switches between the reflection coefficient sets that maximize \gls{snr} at different receive antennas \cite{Basar2020,Ma2020a,Yuan2021}, and \emph{index modulation} employs dedicated reflection elements (resp.
@@
 backscatter modulation) \cite{Hu2021a}.
-	However, those joint designs incur advanced hardware architecture and high optimization complexity.
-	Relevant literature also considers either Gaussian codebook \cite{Guo2019b,Ding2020,Long2020a,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Hu2021b} that is impractical for low-power nodes or finite equiprobable inputs \cite{Yang2018,Liang2020,Han2021,Zhang2022,Liu2019d,Bereyhi2020,Xu2020b,Zhang2021d,Hua2022,Basar2020,Ma2020a,Yuan2021,Hu2021a} that does not fully exploit the \gls{csi} and properties of active-passive coexisting networks.
-	% \end{subsection}
+	Those \gls{ris}-based backscatter modulation schemes incur advanced hardware architecture and high optimization complexity.
+	In contrast, \cite{Vardakis2023} exploits commodity \gls{rfid} tags, powered and controlled by a software-defined radio reader at a different frequency, to perform passive beamforming (but no backscatter modulation) towards a legacy user.
+\label{cm:2.5}
+	% The authors demonstrated the feasibility of using batteryless devices to adaptively enhance the \gls{snr} of a primary link, but did not consider backscatter modulation at.
+	Most relevant literature considers either Gaussian codebook \cite{Guo2019b,Ding2020,Long2020a,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Hu2021b} that is impractical for low-power nodes, or finite equiprobable inputs \cite{Yang2018,Liang2020,Han2021,Zhang2022,Liu2019d,Bereyhi2020,Xu2020b,Zhang2021d,Hua2022,Basar2020,Ma2020a,Yuan2021,Hu2021a} that does not fully exploit the \gls{csi} and properties of active-passive coexisting networks.
 	Those problems are addressed in this paper and the contributions are summarized below.
 
-	% \begin{subsection}{Contributions}
 	\emph{First,} we propose RIScatter as a novel protocol that unifies \gls{bc} and \gls{ris} by adaptive reflection state (backscatter input) distribution design.
-	% \emph{First,} we propose RIScatter as a novel scatter protocol that simultaneously modulates the node information and engineers the wireless channel via adaptive reflection state (backscatter input) distribution design.
-	The concept is shown in Fig.~\subref*{fg:riscatter} where one or more RIScatter nodes ride over an active transmission and simultaneously modulate their information and engineer the wireless channel.
-	A co-located receiver cooperatively decodes both coexisting links and each reflection state simultaneously acts as information and passive beamforming codewords.
-	The reflection pattern of each node is semi-randomly chosen with the guidance of input distribution as a joint function of the information source, \gls{csi}, and \gls{qos}.
+	The concept is shown in Fig.~\subref*{fg:riscatter}, where one or more RIScatter nodes ride over an active transmission to simultaneously modulate their information and engineer the wireless channel.
+	A co-located receiver cooperatively decodes both coexisting links.
+	Each reflection state is simultaneously an information codeword and a passive beamforming codeword.
+	The reflection pattern over time is semi-random and guided by the input probability assigned to each state.
+	This probability distribution is carefully designed to incorporate the backscatter information, \gls{csi}, and \gls{qos}\footnote{\gls{qos} refers to the relative priority of the primary link.\label{fn:qos}}.
 	Such an adaptive channel coding boils down to the degenerate distribution of \gls{ris} when the primary link is prioritized, and outperforms the uniform distribution of \gls{bc} (by accounting the \gls{csi}) when the backscatter link is prioritized.
-	Joint and independent encoding are available when multiple RIScatter nodes are co-located and dispersed, respectively.
 	Table~\ref{tb:scattering_applications} compares RIScatter to \gls{bc} and \gls{ris}.
-	However, two major challenges for RIScatter are the practical receiver and input distribution design.
+	However, two major challenges for RIScatter are the receiver design and input distribution design.
 	This is the first paper to unify \gls{bc} and \gls{ris} from the perspective of input distribution.
 
-	\emph{Second,} we address the first challenge and propose a practical receiver that semi-coherently decodes the backscatter information, recovers the reflection pattern, and coherently decodes the primary link.
-	We consider backscatter energy detection and formulate a \gls{dmmac} over disjoint decision regions.
-	Thanks to the double modulation and symbol-level passive precoding, the semi-coherent backscatter decoding also acts as part of channel training.
-	Once the backscatter information is successfully decoded, its contribution can be modelled within composite channel as dynamic passive beamforming rather than re-precoded and cancelled.
-	It requires only one energy comparison and re-encoding per backscatter symbol and is much efficient than conventional decoding based on \gls{sic} and \gls{mrc}.
-	It is also suitable for arbitrary input distribution and spreading factor, which significantly improves backscatter throughput.
-	This is the first paper to consider practical backscatter-primary decoding scheme to exploit dynamic passive beamforming at the co-located receiver.
-
-	\emph{Third,} we address the second challenge and consider a single-user multi-node \gls{miso} scenario.
+	\emph{Second,} we address the first challenge and propose a low-complexity \gls{sic}-free receiver.
+	It semi-coherently decodes the weak backscatter signal using an energy detector, re-encodes for the exact reflection pattern, then coherently decodes the primary link.
+	Thanks to double modulation, backscatter detection can be viewed as part of channel training, and the impact of backscatter modulation can be modelled as dynamic passive beamforming afterwards.
+	The proposed receiver may be built over legacy receivers with minor hardware upgrade, as it only requires one additional energy comparison and re-encoding per backscatter symbol (instead of primary symbol).
+	The energy detector can also be tailored for arbitrary input distribution and spreading factor to increase backscatter throughput.
+	This is the first paper to propose a \gls{sic}-free cooperative receiver for active-passive coexisting networks.
+
+	\emph{Third,} we address the second challenge in a single-user multi-node \gls{miso} scenario.
 	We characterize the achievable primary-(total-)backscatter rate region by optimizing the input distribution at RIScatter nodes, the active beamforming at the \gls{ap}, and the energy decision regions at the user under different \gls{qos}.
-	A \gls{bcd} algorithm is proposed where the \gls{kkt} input distribution is numerically evaluated by limit of sequences, the active beamforming is optimized by \gls{pgd}, and the decision regions are refined by existing sequential quantizer for \gls{dmtc}.
-	Uniquely, we consider \gls{csi}, \gls{qos}, and backscatter constellation in the optimization and the input distribution result is applicable to general detection schemes.
+	A \gls{bcd} algorithm is proposed where the \gls{kkt} input distribution is numerically evaluated by the converging point of a sequence, the active beamforming is optimized by \gls{pga}, and the decision regions are refined by state-of-the-art sequential quantizer designs for \gls{dmtc}.
+	Uniquely, our optimization problem takes into account the \gls{csi}, \gls{qos}, and backscatter constellation, and the resulting input distribution is applicable to other detection schemes.
 	This is also the first paper to reveal the importance of backscatter input distribution and decision region designs in active-passive coexisting networks.
@@
 \begin{section}{RIScatter}
+	\label{sc:riscatter}
 	\begin{subsection}{Principles}
-		\gls{rf} wave scattering/reflecting are often manipulated by passive antennas or programmable metamaterial \cite{Liang2022}.
-		% can be described by a unified signal model and implemented by passive antennas or programmable metamaterial \cite{Liang2022}.
-		% An antenna-based scatterer usually consists of an integrated antenna, a load-switching modulator, an energy harvester, and on-chip components (e.g., microcontroller and sensors) \cite{Dobkin2012}.
-		% An antenna-based scatterer usually consists of an integrated antenna, a load-switching modulator, an energy harvester, and on-chip components (e.g., microcontroller and sensors) \cite{Dobkin2012}.
-		An antenna scatterer first receives the impinging signals then reradiates some back to the space and dissipates the remaining \cite{Dobkin2012}.
-		% In comparison, a typical metamaterial-based scatterer comprises an outer metamaterial layer of numerous sub-wavelength metallic/dielectric patches (with tunable permittivity/permeability), a middle copper plate layer that avoids leakage, an inner circuit board layer that adjusts patch responses, and an integrated microcontroller/\glsentryshort{fpga} for coordination and control \cite{Wu2020}.
-		% In comparison, a typical metamaterial-based scatterer comprises an outer metamaterial layer of numerous sub-wavelength metallic/dielectric patches (with tunable permittivity/permeability), a middle copper plate layer that avoids leakage, an inner circuit board layer that adjusts patch responses, and an integrated microcontroller/\glsentryshort{fpga} for coordination and control \cite{Wu2020}.
-		An ideal metamaterial scatterer reflects the wave at the space-metamaterial boundary without receiving them and mainly applies a phase shift on top.
-		% In practice, both types of scatterers have {finite} reflection states with non-zero reflection loss.
-		% In general, the scattered signal consists of a structural mode component that consistently contributes to environment multipath and can be modelled within \gls{csi}, and an \emph{antenna} mode component that depends on the impedance mismatch and can be used for backscatter modulation and/or passive beamforming \cite{Hansen1989}.
-		In general, the scattered signal consists of a structural mode component that consistently contributes to environment multipath and an antenna mode component that depends on the impedance mismatch \cite{Hansen1989}.
-		The former is usually modelled within \gls{csi} while the latter is mainly used for backscatter modulation and/or passive beamforming.
-		For an antenna (resp. metamaterial) scatterer with $M$ reflection states, the reflection coefficient at state $m \in \mathcal{M} \triangleq \{1,\ldots,M\}$ is
+		\label{sc:principles}
+		\gls{rf} wave scattering or reflecting are often manipulated by passive antennas or programmable metamaterial \cite{Liang2022}.
+		The former receives the impinging signals and reradiates some back to the space, while the latter reflects at the space-cell boundary and mainly applies a phase shift.
+		In the scattered signal, the structural mode component depends on the scatterer geometry and material.
+		Its impact is usually modelled as part of environment multipath \cite{Thomas2012,Liang2020}, or simply a baseband \gls{dc} offset when the impinging signal is a \gls{cw} \cite{Boyer2014}.
+		On the other hand, the antenna mode component depends on the impedance mismatch and is widely exploited in scattering applications.
+		For an antenna (resp. metamaterial) scatterer with $M$ reflection states, the reflection coefficient at state $m \in \mathcal{M} \triangleq \{1,\ldots,M\}$ is \cite{VanHuynh2017,Liang2022}
 		\begin{equation}
@@
 		\end{equation}
-		where $Z_m$ is the antenna load (resp. metamaterial unit) impedance at state $m$ and $Z$ is the antenna input (resp. medium characteristic) impedance.
-		\gls{bc} treats scatterers as information sources that \emph{randomly} choosing the reflection state based on information symbol.
-		For $M$-ary \gls{qam}, constellation point $c_m$ maps to reflection coefficient $\Gamma_m$ by \cite{Thomas2012a}
-		\begin{equation}
-			\Gamma_m = \alpha \frac{c_m}{\max_{m'} \lvert c_{m'} \rvert},
+		where $Z_m$ is the antenna load (resp. metamaterial cell) impedance at state $m$, and $Z$ is the antenna input (resp. medium characteristic) impedance.
+		Specifically,
+		\begin{itemize}
+			\item \gls{bc}: The scatterer is an information source with random reflection pattern over time.
+			The reflection coefficient is used merely as an information codeword \cite{Thomas2012a}
+			\begin{equation}
+				\Gamma_m = \alpha_m \frac{c_m}{\max_{m'} \lvert c_{m'} \rvert},
 				\label{eq:backscatter_modulation}
 			\end{equation}
-		where $\alpha \in \mathbb{I}$ is the common amplitude scattering ratio at the direction of interest.
-		In contrast, \gls{ris} treats scatterers as channel adaptors that \emph{deterministically} choosing the reflection state based on \gls{csi}.
-		For a \gls{ris} element with $M$ available states, phase shift $\theta_m$ maps to reflection coefficient $\Gamma_m$ by \cite{Wu2018}
-		\begin{equation}
-			\Gamma_m = \beta_m \exp(j \theta_m),
+			where $\alpha_m \in \mathbb{I}$ is the amplitude scattering ratio at state $m$, and $c_m$ is the corresponding constellation point.
+			\item \gls{ris}: The scatterer is a channel shaper with deterministic reflection pattern over time.
+			The reflection coefficient is used merely as a passive beamforming codeword \cite{Wu2018}
+			\begin{equation}
+				\Gamma_m = \alpha_m \exp(j \theta_m),
 				\label{eq:passive_beamforming}
 			\end{equation}
-		where $\beta_m \in \mathbb{I}$ is the overall amplitude scattering ratio at state $m$.\footnote{Most existing \gls{ris} literature assumes lossless reflection $\beta_m=1$, $\forall m$.}
-		% A natural question is, is it possible to use a scatterer
-		For a scatter node with given load impedance set, \gls{bc} employs $\Gamma_m$ only as an information codeword while \gls{ris} employs $\Gamma_m$ only as a passive beamforming codeword.
-		RIScatter generalizes both from a probabilistic perspective where each node \emph{semi-randomly} chooses the reflection state with the guidance of probability $P(\Gamma_m)$.
-		The input distribution is flexibly designed as a joint function of the information source, \gls{csi}, and \gls{qos}.
-		\gls{bc} and (static) \gls{ris} can be regarded as its extreme cases where the input distribution boils down to uniform and degenerate, respectively.
-		Fig.~\ref{fg:scatter_comparison} compares the input distribution and reflection pattern of RIScatter to \gls{bc} and \gls{ris}.
+			where $\theta_m$ is the phase shift at state $m$.\footnote{Most papers assume $\alpha_m = \alpha$, with $\alpha \ll 1$ for \gls{bc} and $\alpha=1$ for \gls{ris}.\label{fn:scattering_ratio}}
+		\end{itemize}
+
+		RIScatter generalizes \gls{bc} and \gls{ris} from a probabilistic perspective.
+		Each reflection coefficient simultaneously acts as an information codeword and a passive beamforming codeword.
+		As shown in Fig.~\ref{fg:scatter_comparison}, the reflection pattern of each RIScatter node over time is semi-random and guided by the input probability assigned to each state.
+		This probability distribution is carefully designed to incorporate the backscatter information, \gls{csi}, and \gls{qos}, in order to strike a balance between backscatter modulation and passive beamforming.
 		\begin{figure}[!t]
@@
 				Shadowing means presence of primary link.
-				In this example, the optimal passive beamformer is state \num{2} and its input probability for RIScatter is \num{0.75}.
-				% RIScatter node transmit symbol \num{1}
+				In this example, the optimal passive beamformer corresponds to state \num{2}.
 				The spreading factor is \num{4} for RIScatter and \num{8} for \gls{ambc}/\gls{sr}.
+				\gls{bc} and \gls{ris} can be viewed as extreme cases of RIScatter, where the input distribution boils down to uniform and degenerate, respectively.
 			}
@@
 		\begin{remark}
-			RIScatter is different from conventional dynamic passive beamforming since the reflection pattern conveys additional information.
-			% There are many ways to order
-			% The latter only involves time sharing between different states but there are many ways to ensure within a channel block.
-			The latter only involves time sharing between different states and the actual order has no impact on the (ergodic) primary performance.
-			For RIScatter, different state combinations correspond to different messages and the impact reduces to dynamic passive beamforming upon successful backscatter decoding.
-			% However, different combinations correspond to different backscatter messages and RIScatter impact is determined dynamic passive beamforming once successfully decoded.
+			Unlike dynamic \gls{ris} that simply performs a time sharing between reflection states, RIScatter conveys additional information by randomizing the reflection pattern over time while still guaranteeing the probability of occurrence of each state.
+			Upon successful backscatter detection, the impact of RIScatter nodes on the primary link can be modelled as dynamic passive beamforming.
+			\label{re:dynamic_passive_beamforming}
 		\end{remark}
 
-		RIScatter nodes can be implemented, for example, by adding an integrated receiver \cite{Kim2021a} and adaptive encoder \cite{He2020e} to off-the-shelf passive \gls{rfid} tags.
+		RIScatter nodes can be implemented, for example, by adding an integrated receiver\footnote{The aim is to coordinate the node with the active source and to acquire the optimized input distribution, instead of decoding the primary information dedicated for the user.
+The node receiver can be implemented using simple circuits or even integrated with the rectifier \cite{Kim2021a} to reduce cost and complexity.\label{fn:integrated_receiver}} \cite{Kim2021a} and adaptive encoder \cite{He2020e} to off-the-shelf passive \gls{rfid} tags.
 		The block diagram, equivalent circuit, and scatter model are illustrated in Fig.~\ref{fg:riscatter_node}.
@@
 		\end{figure*}
-		To exploit the benefits of RIScatter, we also propose a practical co-located receiver that semi-coherently decodes the backscatter information, recovers the reflection pattern, and coherently decodes the primary link.
-		The detail will be covered in Section~\ref{se:system_model}.
-		% We also propose a practical co-located receiver to exploit the benefits of RIScatter and the detail will be covered in Section~\ref{se:system_model}.
+		% To exploit the benefits of RIScatter, we also propose a low-complexity receiver that semi-coherently decodes the backscatter link, re-encodes to recover the reflection pattern, and coherently decodes the primary link.
+		% The detail will be covered in Section~\ref{st:system_model}.
 	\end{subsection}
 
-	% As illustrated in Fig.~\ref{fg:energy_distribution}, conditioned on different reflection state hypotheses, the accumulated energy per backscatter block follows Gamma distribution with different scale parameters \cite{Qian2017b}.
-	% \begin{figure}[!t]
-	% 	\centering
-	% 	\resizebox{0.8\columnwidth}{!}{
-	% 		\input{assets/illustration/energy_distribution.tex}
-	% 	}
-	% 	\caption{
-	% 		\gls{pdf} of accumulated energy per backscatter block conditioned on different reflection state hypotheses.
-	% 		$z$, $t$, $\mathcal{H}$ and $\mathcal{R}$ denote the accumulated energy, decision threshold, reflection state hypothesis, and decision regions, respectively.
-	% 	}
-	% 	\label{fg:energy_distribution}
-	% \end{figure}
-
-	% Hence, the receiver can semi-coherently (under primary uncertainty) decode RIScatter nodes from the accumulated energy, re-encode to recover the reflection patterns, and combine those with cascaded \gls{csi} to determine the multipath response and model within the primary channel.
-	% Such a backscatter-primary decoding enables simultaneous backscatter modulation and dynamic passive beamforming by only one energy comparison and re-encoding during each backscatter (instead of primary) block.
-	% It enjoys a three-fold benefit compared to conventional primary-backscatter decoding with \gls{sic}, namely
-	% 1) reduces the re-encoding frequencies to $1/N$;
-	% 2) requires no re-precoding, cancellation, or \gls{mrc};
-	% 3) preserves backscatter modulation and passive beamforming at smaller spreading factors for potentially higher backscatter throughput.
-
-	% % ! add to signal model
-	% % Importantly, RIScatter system design only requires the \emph{direct} transmitter-receiver and \emph{cascaded} transmitter-scatter-receiver \gls{csi}.
-	% % For dispersed RIScatter nodes, relevant \gls{csi} can be estimated by sequential \cite{Bharadia2015,Yang2015b,Guo2019g} or parallel approaches \cite{Jin2021a} originally proposed for \gls{bc}.
-	% % For co-located RIScatter nodes, the estimation can be simplified by group-based \cite{Zheng2019} and hierarchical \cite{You2019} trainings originally proposed for \gls{ris}.
-
 	\begin{subsection}{System Model}
-		\label{se:system_model}
+		\label{sc:system_model}
 		\begin{figure}[!t]
@@
 			}
-			\caption{A single-user multi-node RIScatter system.}
+			\caption{A single-user multi-node RIScatter network.}
 			\label{fg:riscatter_network}
 		\end{figure}
-		As shown in Fig.~\ref{fg:riscatter_network}, we consider a RIScatter system where a $Q$-antenna \gls{ap} serves a single-antenna user and $K$ nearby dispersed or co-located RIScatter nodes.
-		All nodes have $M$ available reflection states.
-		In the primary point-to-point system, the \gls{ap} transmits information to the user over a multipath channel enhanced by RIScatter nodes.
-		In the backscatter multiple access system, the \gls{ap} acts as carrier emitter, the RIScatter nodes modulate over scattered signal, and the user jointly decodes all node messages.
-		For simplicity, we consider a quasi-static block fading model and focus on a specific block where the \gls{csi} remains constant.
-		It is assumed the signal reflected by two or more times is negligible, the primary symbol duration is much longer than multipath delay spread (no inter-symbol interference), and the spreading factor $N$ is a positive integer.
+		As shown in Fig.~\ref{fg:riscatter_network}, we consider a RIScatter network where a $Q$-antenna \gls{ap} serves a single-antenna user and $K$ nearby dispersed or co-located RIScatter nodes.
+		Without loss of generality, we assume all nodes have $M$ available reflection states.
+		In the primary point-to-point system, the \gls{ap} transmits information to the user over a multipath channel\footnote{It is assumed the primary symbol duration is much longer than multipath delay spread (i.e., no inter-symbol interference).} enhanced by RIScatter nodes.
+		In the backscatter multiple access system, the \gls{ap} acts as a carrier emitter, the RIScatter nodes modulate over the scattered signal, and the user jointly decodes all nodes.\footnote{It is assumed the signal going through two or more RIScatter nodes is too weak to be received by the user.}
+		For simplicity, we consider a quasi-static block fading model and focus on a specific channel block where the \gls{csi} remains constant.
 		Denote the \gls{ap}-user direct channel as $\boldsymbol{h}_{\text{D}}^\mathsf{H} \in \mathbb{C}^{1 \times Q}$, the \gls{ap}-node $k \in \mathcal{K} \triangleq \{1,\ldots,K\}$ forward channel as $\boldsymbol{h}_{\text{F},k}^\mathsf{H} \in \mathbb{C}^{1 \times Q}$, the node $k$-user backward channel as $h_{\text{B},k}$, and the cascaded \gls{ap}-node $k$-user channel as $\boldsymbol{h}_{\text{C},k}^\mathsf{H} \triangleq h_{\text{B},k} \boldsymbol{h}_{\text{F},k}^\mathsf{H} \in \mathbb{C}^{1 \times Q}$.
-		We assume perfect direct and cascaded \gls{csi} are available at the \gls{ap} and the user\footnote{The cascaded \gls{csi} can be estimated by sequential \cite{Bharadia2015,Yang2015b,Guo2019g} or parallel \cite{Jin2021a} approaches for dispersed nodes, or group-based \cite{Zheng2019} or hierarchical \cite{You2019} approaches for co-located nodes.}.
-		% For dispersed RIScatter nodes, relevant \gls{csi} can be estimated by sequential \cite{Bharadia2015,Yang2015b,Guo2019g} or parallel approaches \cite{Jin2021a} originally proposed for \gls{bc}.
-For co-located RIScatter nodes, the estimation can be simplified by group-based \cite{Zheng2019} and hierarchical \cite{You2019} trainings originally proposed for \gls{ris}.}.
-		Let $x_k \in \mathcal{X} \triangleq \{c_1,\ldots,c_M\}$ be the coded backscatter symbol of node $k$ and $x_{\mathcal{K}} \triangleq (x_1,\ldots,x_K)$ be the backscatter symbol tuple of all nodes.
+		We assume the direct and cascaded \gls{csi} are available at the \gls{ap} and user\footnote{The cascaded \gls{csi} can be estimated by sequential \cite{Bharadia2015,Yang2015b,Guo2019g} or parallel \cite{Jin2021a} approaches for dispersed nodes, or group-based \cite{Zheng2019} or hierarchical \cite{You2019} approaches for co-located nodes.
+The impact of channel estimation error will be investigated in Section~\ref{sc:simulation_results}.}.
+
+		Let $\alpha_k \in \mathbb{I}$ be the amplitude scattering ratio of node $k$, $x_k \in \mathcal{X} \triangleq \{c_1,\ldots,c_M\}$ be the (coded) backscatter symbol of node $k$, and $x_{\mathcal{K}} \triangleq (x_1,\ldots,x_K)$ be the backscatter symbol tuple of all nodes.
 		Due to double modulation, the composite channel is a function of backscatter symbol tuple\footnote{\eqref{eq:equivalent_channel_bc} and \eqref{eq:equivalent_channel_ris} are often used in \gls{bc} and \gls{ris} literature, respectively.}
@@
 		\end{subequations}
-		where $\alpha_k \in \mathbb{I}$ is the common amplitude scattering ratio of node $k$, $\boldsymbol{\alpha} \triangleq [\alpha_1,\ldots,\alpha_K]^\mathsf{T} \in \mathbb{I}^{K}$, $\boldsymbol{x} \triangleq [x_1,\ldots,x_K]^\mathsf{H} \in \mathcal{X}^{K}$, and $\boldsymbol{H}_{\text{C}} \triangleq [\boldsymbol{h}_{\text{C},1},\ldots,\boldsymbol{h}_{\text{C},K}]^\mathsf{H} \in \mathbb{C}^{K \times Q}$.
-		Next, we consider the signal model within one backscatter block.
-		The signal received by the user at primary block $n \in \mathcal{N} \triangleq \{1,\ldots,N\}$ is
+		where $\boldsymbol{\alpha} \triangleq [\alpha_1,\ldots,\alpha_K]^\mathsf{T} \in \mathbb{I}^{K}$, $\boldsymbol{x} \triangleq [x_1,\ldots,x_K]^\mathsf{H} \in \mathcal{X}^{K}$, and $\boldsymbol{H}_{\text{C}} \triangleq [\boldsymbol{h}_{\text{C},1},\ldots,\boldsymbol{h}_{\text{C},K}]^\mathsf{H} \in \mathbb{C}^{K \times Q}$.
+		Without loss of generality, we assume the spreading factor $N$ is a positive integer.
+		Within one backscatter block, the signal received by the user at primary block $n \in \mathcal{N} \triangleq \{1,\ldots,N\}$ is
 		\begin{equation}
@@
 		\end{equation}
-		where $\boldsymbol{w} \in \mathbb{C}^{Q}$ is the active beamformer satisfying average transmit power constraint $\lVert \boldsymbol{w} \rVert^2 \le P$, $s \sim \mathcal{CN}(0,1)$ is the primary symbol, and $v \sim \mathcal{CN}(0,\sigma_v^2)$ is the \gls{awgn} with average power $\sigma_v^2$.
-		Let $m_k \in \mathcal{M} \triangleq \{1,\ldots,M\}$ be the reflection state index of node $k$ and $m_{\mathcal{K}} \triangleq (m_1,\ldots,m_K)$ be the state index tuple of all nodes.
-		% The backscatter symbol $x_k$ (resp.
-symbol tuple $x_{\mathcal{K}}$) is a random variable (resp.
-variable tuple) that takes value $x_{m_k}$ (resp.
-value tuple $x_{m_{\mathcal{K}}}$) when state $m_k$ (resp.
-state tuple $m_{\mathcal{K}}$) is employed.
-		The backscatter symbol tuple $x_{\mathcal{K}}$ is a random variable that takes value $x_{m_{\mathcal{K}}}$ when state tuple $m_{\mathcal{K}}$ is used.
-		Conditioned on hypothesis $\mathcal{H}_{m_{\mathcal{K}}}$, the receive signal per primary block follows \gls{cscg} distribution $\mathcal{CN}(0,\sigma_{m_{\mathcal{K}}}^2)$, where
-		\begin{equation}
-			\sigma_{m_{\mathcal{K}}}^2 = \lvert \boldsymbol{h}^\mathsf{H}(x_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2 + \sigma_v^2
+		where $\boldsymbol{w} \in \mathbb{C}^{Q}$ is the active beamformer satisfying $\lVert \boldsymbol{w} \rVert^2 \le P$, $P$ is the maximum average transmit power, $s \sim \mathcal{CN}(0,1)$ is the primary symbol, and $v \sim \mathcal{CN}(0,\sigma_v^2)$ is the \gls{awgn} with variance $\sigma_v^2$.
+
+		Let $m_k \in \mathcal{M} \triangleq \{1,\ldots,M\}$ be the reflection state index of node $k$, and $m_{\mathcal{K}} \triangleq (m_1,\ldots,m_K)$ be the state index tuple of all nodes.
+		The backscatter symbol $x_k$ (resp.
+symbol tuple $x_{\mathcal{K}}$) is a random variable that takes value $x_{m_k}$ (resp.
+value tuple $x_{m_{\mathcal{K}}}$) with probability $p(x_{m_k})$ (resp.
+$p(x_{m_{\mathcal{K}}})$).
+		\begin{remark}
+			Dispersed RIScatter nodes encode independently such that
+			\begin{equation}
+				p(x_{m_{\mathcal{K}}}) = \prod_k p(x_{m_k}).
+				\label{eq:equivalent_distribution}
+			\end{equation}
+			When multiple nodes are co-located, they can jointly encode by designing the joint probability $p(x_{m_{\mathcal{K}}})$ directly.
+			\label{re:independent_encoding}
+		\end{remark}
+
+		Let $z=\sum_{n} \bigl\lvert y[n] \bigr\rvert^2$ be the receive energy per backscatter block.
+		When $x_{m_\mathcal{K}}$ is transmitted, the receive signal $y$ follows \gls{cscg} distribution $\mathcal{CN}(0,\sigma_{m_{\mathcal{K}}}^2)$ with variance
+		\begin{equation}
+			\sigma_{m_{\mathcal{K}}}^2 = \lvert \boldsymbol{h}^\mathsf{H}(x_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2 + \sigma_v^2,
 			\label{eq:receive_variance}
 		\end{equation}
-		is its variance.
-		Let $z=\sum_{n} \bigl\lvert y[n] \bigr\rvert^2$ be the accumulated energy per backscatter block.
-		Since $z$ is the sum of $N$ \gls{iid} exponential variables, the conditional \gls{pdf} follows Gamma distribution
-		\begin{equation}
-			f(z|\mathcal{H}_{m_{\mathcal{K}}}) = \frac{z^{N-1} \exp(-z/\sigma_{m_{\mathcal{K}}}^2)}{\sigma_{m_{\mathcal{K}}}^{2N} (N-1)!}.
+		and $z$ follows Gamma distribution with conditional \gls{pdf}
+		\begin{equation}
+			f(z|x_{m_{\mathcal{K}}}) = \frac{z^{N-1} \exp(-z/\sigma_{m_{\mathcal{K}}}^2)}{\sigma_{m_{\mathcal{K}}}^{2N} (N-1)!}.
 			\label{eq:energy_distribution}
 		\end{equation}
-		% The receiver first jointly decodes all backscatter messages under primary interference by energy detection.
-		% This essentially formulates a \gls{dmmac} over disjoint energy decision regions.
-		The user first jointly decodes all backscatter messages under primary interference by performing energy detection over disjoint decision regions.
-		For the ease of notation, we map the state index tuple $m_{\mathcal{K}}$ to $l \in \mathcal{L} \triangleq \{1,\ldots,L\}$, where $L \triangleq M^K$ and $\sigma_1^2,\ldots,\sigma_L^2$ forms an increasing sequence.
-		Both notations are used interchangeably in the following context.
-		The decision region of backscatter symbol tuple $l$ is
+
+		\begin{remark}
+			We have assumed Gaussian codebook for the primary source and finite support for the backscatter nodes, since they are relatively practical and widely adopted in relevant literatures.
+			The proposed framework is extendable to non-Gaussian primary source, and the conditional \gls{pdf} \eqref{eq:energy_distribution} can be approximated using \gls{clt} for large $N$.
+			\label{re:non_gaussian}
+		\end{remark}
+
+		The user first jointly decodes the backscatter message of all nodes using a low-complexity energy detector.\footnote{The reliability of the energy detector is improved by the adaptive input distribution and thresholding design.
+With high-order modulation or large number of scatter nodes, the reliability can be further enhanced by increasing the spreading factor or using error correction codes with low code-rate.
+In practice, users can decode backscatter nodes ranging from a few to hundreds of meters in the presence of noise and interference, and the backscatter throughput can reach few Kbps to tens of Mbps \cite{Wu2022e}.\label{fn:energy_detector}}
+		The energy detector formulates a \gls{dmtc} of size $M^K \times M^K$.
+
+		\begin{remark}
+			The capacity-achieving decision region design for \gls{dmtc} with non-binary inputs in arbitrary distribution remains an open issue.
+			It was proved deterministic detectors can be rate-optimal, but non-convex regions (consist of non-adjacent partitions) are generally required and the optimal number of thresholds is unknown \cite{Nguyen2018,Nguyen2021}.
+			Next, we restrict the energy detector to convex deterministic decision regions and consider sequential threshold design.
+		\end{remark}
+
+		Let $L = M^K$ be the number of decision regions.
+		Sort $\{\sigma_{m_{\mathcal{K}}}^2\}$ in ascending order and denote the result sequence as $\sigma_1^2,\ldots,\sigma_L^2$.
+		With sequential thresholding, the decision region of backscatter symbol tuple $l \in \mathcal{L} \triangleq \{1,\ldots,L\}$ is\footnote{$m_{\mathcal{K}}$ and $l$ are one-to-one mapped.
+Both notations are used interchangeably in the following context.}
 		\begin{equation}
@@
 		\end{equation}
-		where $t_l$ is the energy decision threshold between hypotheses $\mathcal{H}_{l}$ and $\mathcal{H}_{l+1}$.
-		For a given decision threshold vector $\boldsymbol{t} \triangleq [t_0,\ldots,t_L]^\mathsf{T} \in \mathbb{R}_+^{(L+1)}$, we can formulate a \gls{dmmac} with transition probability from input $x_{m_{\mathcal{K}}}$ to output $\hat{x}_{m_{\mathcal{K}}'}$ as
-		\begin{equation}
-			P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}}) = \int_{\mathcal{R}_{m_{\mathcal{K}}'}} f(z|\mathcal{H}_{m_{\mathcal{K}}}) \, d z,
-			\label{eq:dmmac}
-		\end{equation}
-		over which input distribution of all RIScatter nodes can be designed.
-		An example of energy detection is illustrated in Fig.~\ref{fg:energy_distribution}.
-		% Conditioned on different reflection state hypotheses, the accumulated energy per backscatter block follows Gamma distribution with different scale parameters.
+		where $t_l$ is the decision threshold between hypotheses $x_{l}$ and $x_{l+1}$.
+		An example is shown in Fig.~\ref{fg:energy_distribution}.
+
 		\begin{figure}[!t]
 			\centering
-			\resizebox{0.8\columnwidth}{!}{
-				\input{assets/illustration/energy_distribution.tex}
-			}
+			\includegraphics[width=0.8\columnwidth]{assets/illustration/energy_distribution.jpg}
 			\caption{
-				\gls{pdf} of accumulated energy per backscatter block conditioned on different reflection state hypotheses.
+				\gls{pdf} of the receive energy per backscatter block conditioned on different reflection state.
 			}
@@
 		\end{figure}
-		\begin{remark}
-			The capacity-achieving decision region design for \gls{dmtc} with non-binary inputs in arbitrary distribution remains an open issue.
-			It was proved deterministic detectors can be rate-optimal, but non-convex decision regions (comprise non-adjacent partitions) are generally required and the optimal number of thresholds remains unknown \cite{Nguyen2018,Nguyen2021}.
-			Hence, we limit the energy detector to convex deterministic decision regions and consider sequential threshold design.
-		\end{remark}
-		After successful backscatter decoding, the user can re-encode for exact reflection pattern and obtain the composite channel by \eqref{eq:equivalent_channel}, then coherently decode the primary link.
-		Such an \gls{sic}-free sequential decoding enables backscatter modulation and dynamic passive beamforming by only one energy comparison and re-encoding per backscatter symbol.
-		It also supports arbitrary input distribution and spreading factor for higher backscatter throughput.
-		\label{st:system_model}
+		When the threshold vector $\boldsymbol{t} \triangleq [t_0,\ldots,t_L]^\mathsf{T} \in \mathbb{R}_+^{L+1}$ is given, we can formulate a \gls{dmmac} with transition probability from input $x_{m_{\mathcal{K}}}$ to output $\hat{x}_{m_{\mathcal{K}}'}$ as
+		\begin{equation}
+			q(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}}) = \int_{\mathcal{R}_{m_{\mathcal{K}}'}} f(z|x_{m_{\mathcal{K}}}) \, d z.
+			\label{eq:dmmac}
+		\end{equation}
+		The backscatter mutual information is
+		\begin{equation}
+			I_{\text{B}}(x_{\mathcal{K}};\hat{x}_{\mathcal{K}}) = \sum_{m_{\mathcal{K}}} p(x_{m_{\mathcal{K}}}) I_{\text{B}}(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}}),
+			\label{eq:backscatter_mutual_information}
+		\end{equation}
+		where $I_{\text{B}}(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}})$ is the backscatter information function
+		\begin{equation}
+			I_{\text{B}}(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}}) \triangleq \sum_{m_{\mathcal{K}}'} q(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}}) \log \frac{q(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}})}{p(\hat{x}_{m_{\mathcal{K}}'})}.
+			\label{eq:backscatter_information_function}
+		\end{equation}
+
+		Once the backscatter information is successfully decoded, the user re-encodes to recover the reflection pattern, constructs the composite channel by \eqref{eq:equivalent_channel}, then coherently decodes the primary link.
+		The primary mutual information is
+		\begin{equation}
+			I_{\text{P}}(s;y|x_{\mathcal{K}}) = \sum_{m_{\mathcal{K}}} p(x_{m_{\mathcal{K}}}) I_{\text{P}}(s;y|x_{m_{\mathcal{K}}}),
+			\label{eq:primary_mutual_information}
+		\end{equation}
+		where $I_{\text{P}}(s;y|x_{m_{\mathcal{K}}})$ is the primary information function
+		\begin{equation}
+			I_{\text{P}}(s;y|x_{m_{\mathcal{K}}}) \triangleq \log \Bigl(1 + \frac{\lvert \boldsymbol{h}^\mathsf{H}(x_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_v^2}\Bigr).
+			\label{eq:primary_information_function}
+		\end{equation}
 	\end{subsection}
-
-	\begin{subsection}{Achievable Rates}
-		Denote the probability of node $k$ choosing reflection state $m_k$ as $P_k(x_{m_k})$ and let $\boldsymbol{p}_k \triangleq [P_k(c_1),\ldots,P_k(c_M)]^\mathsf{T} \in \mathbb{I}^{M}$.
-		For dispersed nodes with independent encoding, the probability of backscatter symbol tuple $x_{m_{\mathcal{K}}}$ is
-		\begin{equation}
-			P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) = \prod_{k \in \mathcal{K}} P_k(x_{m_k}).
-			\label{eq:equivalent_distribution}
-		\end{equation}
-		Following \cite{Rezaeian2004}, we define the backscatter information function between input value tuple $x_{m_{\mathcal{K}}}$ and output variable tuple $\hat{x}_{\mathcal{K}}$ as
-		\begin{equation}
-			I_{\text{B}}(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}}) \triangleq \sum_{m_{\mathcal{K}}'} P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}}) \log \frac{P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}})}{P_{\mathcal{K}}(\hat{x}_{m_{\mathcal{K}}'})},
-			\label{eq:backscatter_information_function}
-		\end{equation}
-		where $P_{\mathcal{K}}(\hat{x}_{m_{\mathcal{K}}'}) = \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}})$.
-		We also define the backscatter marginal information of $x_{m_k}$ as
-		\begin{equation}
-			I_{\text{B},k}(x_{m_k};\hat{x}_{\mathcal{K}}) \triangleq \sum_{m_{\mathcal{K} \setminus \{k\}}} P_{\mathcal{K} \setminus \{k\}}(x_{m_{\mathcal{K} \setminus \{k\}}}) I_{\text{B}}(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}}),
-			\label{eq:backscatter_marginal_information}
-		\end{equation}
-		where $P_{\mathcal{K} \setminus \{k\}}(x_{m_{\mathcal{K} \setminus \{k\}}}) = \prod_{q \in \mathcal{K} \setminus \{k\}} P_{q}(x_{m_{q}})$.
-		Hence, the backscatter mutual information can be written as
-		\begin{equation}
-			I_{\text{B}}(x_{\mathcal{K}};\hat{x}_{\mathcal{K}}) = \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) I_{\text{B}}(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}}).
-			\label{eq:backscatter_mutual_information}
-		\end{equation}
-
-		Once nodes are successfully decoded, we can re-encode and determine the composite channel by \eqref{eq:equivalent_channel}.
-		The primary information function conditioned on $x_{m_{\mathcal{K}}}$ is
-		\begin{equation}
-			I_{\text{P}}(s;y|x_{m_{\mathcal{K}}}) \triangleq \log \Bigl(1 + \frac{\lvert \boldsymbol{h}^\mathsf{H}(x_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_v^2}\Bigr),
-			\label{eq:primary_information_function}
-		\end{equation}
-		the primary marginal information of $x_{m_k}$ is
-		% the primary marginal information conditioned on letter $x_{m_k}$ of node $k$ as
-		\begin{equation}
-			I_{\text{P},k}(s;y|x_{m_k}) \triangleq \sum_{m_{\mathcal{K} \setminus \{k\}}} P_{\mathcal{K} \setminus \{k\}}(x_{m_{\mathcal{K} \setminus \{k\}}}) I_{\text{P}}(s;y|x_{m_{\mathcal{K}}}),
-			\label{eq:primary_marginal_information}
-		\end{equation}
-		and the average primary mutual information is
-		\begin{equation}
-			I_{\text{P}}(s;y|x_{\mathcal{K}}) = \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) I_{\text{P}}(s;y|x_{m_{\mathcal{K}}}).
-			\label{eq:primary_mutual_information}
-		\end{equation}
-
-		With a slight abuse of notation, we define the weighted sum information function, marginal information, and mutual information as
+\end{section}
+
+\begin{section}{Rate-Region Characterization}
+	With a slight abuse of notation, we define the weighed sum mutual information and information function as
 	\begin{align}
-			I(x_{m_{\mathcal{K}}})
-			 & \triangleq \rho I_{\text{P}}(s;y|x_{m_{\mathcal{K}}}) + (1 - \rho) I_{\text{B}}(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}}),\label{eq:weighted_sum_information_function} \\
-			I_k(x_{m_k})
-			 & \triangleq \rho I_{\text{P},k}(s;y|x_{m_k}) + (1 - \rho) I_{\text{B},k}(x_{m_k};\hat{x}_{\mathcal{K}}),\label{eq:weighted_sum_marginal_information}                     \\
 		I(x_{\mathcal{K}})
-			 & \triangleq \rho I_{\text{P}}(s;y|x_{\mathcal{K}}) + (1 - \rho) I_{\text{B}}(x_{\mathcal{K}};\hat{x}_{\mathcal{K}}),\label{eq:weighted_sum_mutual_information}
+		 & \triangleq \rho I_{\text{P}}(s;y|x_{\mathcal{K}}) + (1 - \rho) I_{\text{B}}(x_{\mathcal{K}};\hat{x}_{\mathcal{K}}),\label{eq:weighted_sum_mutual_information}           \\
+		I(x_{m_\mathcal{K}})
+		 & \triangleq \rho I_{\text{P}}(s;y|x_{m_{\mathcal{K}}}) + (1 - \rho) I_{\text{B}}(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}}),\label{eq:weighted_sum_information_function}
 	\end{align}
-		where $\rho \in \mathbb{I}$ is the relative \gls{qos} of the primary link.
-		We notice the average primary rate \eqref{eq:primary_mutual_information} depends on the backscatter input distribution and active beamforming, while the total backscatter rate depends on the input distribution and \gls{dmmac} \eqref{eq:dmmac} that relates to the active beamforming and decision thresholds.
-		\label{st:information_theory}
-	\end{subsection}
-	\label{st:riscatter}
-\end{section}
-
-\begin{section}{Rate-Region Characterization}
-	To characterize the achievable primary-(total-)backscatter rate region for the RIScatter system, we aim to maximize the weighted sum rate with respect to input distribution $\{\boldsymbol{p}_k\}_{k \in \mathcal{K}}$, active beamforming $\boldsymbol{w}$, and decision thresholds $\boldsymbol{t}$ by
+	where $\rho \in \mathbb{I}$ is the \gls{qos}.
+	To obtain the achievable primary-(total-)backscatter rate region, we consider the weighted sum mutual information maximization problem with independent encoding at all nodes\footnote{Joint encoding over multiple nodes can be viewed as its special case with an augmented backscatter source.\label{fn:joint_encoding}}
 	\begin{maxi!}
@@
 		\addConstraint{t_{l-1}}{\le t_l,}{\quad \forall l}{\label{co:sequential_threshold}}
-		\addConstraint{\boldsymbol{t}}{\ge \boldsymbol{0}.}{\label{co:nonnegative_threshold}}
+		\addConstraint{\boldsymbol{t}}{\ge \boldsymbol{0},}{\label{co:nonnegative_threshold}}
 	\end{maxi!}
-
-	Problem \eqref{op:weighted_sum_rate} generalizes conventional \gls{bc} by allowing \gls{csi}- and \gls{qos}-adaptive input distribution and decision region design.
-	It also generalizes the discrete \gls{ris} phase shift selection by allowing stochastic reflection, relaxing the feasible domain from the vertices of $M$-dimensional probability simplex to the simplex itself.
-	Problem \eqref{op:weighted_sum_rate} is highly non-convex and we propose a \gls{bcd} algorithm that iteratively updates $\{\boldsymbol{p}_k\}_{k \in \mathcal{K}}$, $\boldsymbol{w}$ and $\boldsymbol{t}$.
+	where $\boldsymbol{p}_k = [p(x_{1_k}), \ldots, p(x_{M_k})]^\mathsf{T} \in \mathbb{I}^M$ is the input distribution of node $k$.
+	Problem \eqref{op:weighted_sum_rate} generalizes \gls{bc} by allowing \gls{csi}- and \gls{qos}-adaptive input distribution and decision region design.
+	On the other hand, it also relaxes the feasible domain of discrete \gls{ris} phase shift selection problems from the vertices of $M$-dimensional probability simplex to the simplex itself.
+	The original problem is highly non-convex and we propose a \gls{bcd} algorithm that iteratively updates $\{\boldsymbol{p}_k\}_{k \in \mathcal{K}}$, $\boldsymbol{w}$ and $\boldsymbol{t}$.
 
 	\begin{subsection}{Input Distribution}
-		For any given $\boldsymbol{w}$ and $\boldsymbol{t}$, we can construct the equivalent \gls{dmmac} by \eqref{eq:dmmac} and simplify \eqref{op:weighted_sum_rate} to
+		\label{sc:input_distribution}
+		For any given $\boldsymbol{w}$ and $\boldsymbol{t}$, we can formulate a \gls{dmmac} by \eqref{eq:dmmac} and simplify \eqref{op:weighted_sum_rate} to
 		\begin{maxi!}
@@
 		\end{maxi!}
-		which is convex when $K=1$ or joint encoding\footnote{Joint encoding formulates an equivalent source of $M^K$ codewords, such that one can directly design $P_{\mathcal{K}}(x_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}$ instead of $P_k(x_{m_k})$, $\forall k,m_k$.} over $K>1$ co-located nodes.
-		When the nodes are dispersed, problem \eqref{op:input_distribution} involves product term $\prod_{k \in \mathcal{K}} P_k(x_{m_k})$ and is non-convex.
-		Following \cite{Rezaeian2004}, we first recast the \gls{kkt} conditions to their equivalent forms then propose a numerical method that guarantees those conditions on convergence of sequences.
-		% ? Next, we propose a numerical method that evaluate the \gls{kkt} input distribution by limit of sequences.
-		\begin{remark}
-			As demonstrated in \cite{Buhler2011}, \gls{kkt} conditions are generally necessary but insufficient for total rate maximization of \gls{dmmac}.
-			We will later show by simulation that, for a moderate $K$, the average achievable rate regions of \gls{kkt} and global-optimal input distributions completely coincide with each other.
-			\label{re:input_kkt_distribution}
-		\end{remark}
+		which involves the product term \eqref{eq:equivalent_distribution} and is generally non-convex (unless $K=1$).
+		Following \cite{Rezaeian2004}, we first recast the \gls{kkt} conditions to their equivalent forms, then propose a numerical solution that guarantees those conditions on the converging point of a sequence.
 		\begin{proposition}
@@
 				\begin{alignat}{2}
-					I_k^\star(x_{m_k}) & = I^\star(x_{\mathcal{K}}), \quad   &  & P_k^\star(x_{m_k}) > 0,\label{eq:probable_states} \\
-					I_k^\star(x_{m_k}) & \le I^\star(x_{\mathcal{K}}), \quad &  & P_k^\star(x_{m_k}) = 0.\label{eq:dropped_states}
+					I_k^\star(x_{m_k}) & = I^\star(x_{\mathcal{K}}), \quad   &  & \text{if} \ p^\star(x_{m_k}) > 0,\label{eq:probable_states} \\
+					I_k^\star(x_{m_k}) & \le I^\star(x_{\mathcal{K}}), \quad &  & \text{if} \ p^\star(x_{m_k}) = 0,\label{eq:dropped_states}
 				\end{alignat}
 			\end{subequations}
+			where $I_k(x_{m_k})$ is the weighted sum marginal information
+			\begin{align}
+				I_k(x_{m_k})
+				 & \triangleq \sum_{m_{\mathcal{K} \setminus \{k\}}} p(x_{m_{\mathcal{K} \setminus \{k\}}}) I(x_{m_\mathcal{K}}).
+				\label{eq:weighted_sum_marginal_information}
+			\end{align}
 			\label{pr:input_kkt_condition}
@@
 
-		For \eqref{eq:input_kkt_solution} at iteration $r+1$, the input distribution of node $k$ is updated over $\bigl\{\{\boldsymbol{p}_q^{(r+1)}\}_{q=1}^{k-1},\{\boldsymbol{p}_q^{(r)}\}_{q=k}^{K}\bigr\}$.
+		At iteration $r+1$, the input distribution of node $k$ is updated over $\bigl\{\{\boldsymbol{p}_q^{(r+1)}\}_{q=1}^{k-1},\{\boldsymbol{p}_q^{(r)}\}_{q=k}^{K}\bigr\}$.
 		The \gls{kkt} input distribution design is summarized in Algorithm \ref{al:input_distribution}.
 
+		\setalgorithmcaptionfont{\small}
 		\begin{algorithm}[!t]
-			\caption{Numerical \gls{kkt} Input Distribution Evaluation by Limits of Sequence}
+			\small
+			\caption{Input Distribution Evaluation by a Sequence}
 			\label{al:input_distribution}
@@
 				\State \phantom{Set} $\sigma^2_{m_{\mathcal{K}}}$, $\forall m_{\mathcal{K}}$ by \eqref{eq:receive_variance}
-				\State \phantom{Set} $f(z|\mathcal{H}_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}$ by \eqref{eq:energy_distribution}
-				\State \phantom{Set} $P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}, m_{\mathcal{K}}'$ by \eqref{eq:dmmac}
+				\State \phantom{Set} $f(z|x_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}$ by \eqref{eq:energy_distribution}
+				\State \phantom{Set} $q(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}, m_{\mathcal{K}}'$ by \eqref{eq:dmmac}
 				\State Initialize $r \gets 0$
 				\State \phantom{Initialize} $\boldsymbol{p}_k^{(0)} > \boldsymbol{0}$, $\forall k$
-				\State Get $P_{\mathcal{K}}^{(r)}(x_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}$ by \eqref{eq:equivalent_distribution} \label{st:input_distribution_begin}
+				\State Get $p^{(r)}(x_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}$ by \eqref{eq:equivalent_distribution} \label{st:input_distribution_begin}
 				\State \phantom{Get} $I^{(r)}(x_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}$ by \eqref{eq:backscatter_information_function}, \eqref{eq:primary_information_function}, \eqref{eq:weighted_sum_information_function}
-				\State \phantom{Get} $I^{(r)}_k(x_{m_k})$, $\forall k,m_k$ by \eqref{eq:backscatter_marginal_information}, \eqref{eq:primary_marginal_information}, \eqref{eq:weighted_sum_marginal_information}
+				\State \phantom{Get} $I^{(r)}_k(x_{m_k})$, $\forall k,m_k$ by \eqref{eq:weighted_sum_marginal_information}
 				\State \phantom{Get} $I^{(r)}(x_{\mathcal{K}})$ by \eqref{eq:backscatter_mutual_information}, \eqref{eq:primary_mutual_information}, \eqref{eq:weighted_sum_mutual_information} \label{st:input_distribution_end}
@@
 		\end{algorithm}
+
+		\begin{remark}
+			The insufficiency of the \gls{kkt} conditions for problem \eqref{op:input_distribution} implies that the proposed method may not converge to the global-optimal solution.
+			However, simulation results in Section~\ref{sc:simulation_results} will show that the average performance gap is indistinguishable at a moderate $K$.
+			\label{re:input_kkt_distribution}
+		\end{remark}
 	\end{subsection}
@@
 		which is still non-convex due to the integration and entropy terms.
-		To tackle this, we rewrite the \gls{dmmac} transition probability \eqref{eq:dmmac} as a regularized incomplete Gamma function in the series representation \cite[Theorem 3]{Jameson2016}
-		\begin{equation}
-			\begin{gathered}
-				Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr) = \frac{\int_{{t_{l-1}}/{\sigma_{m_{\mathcal{K}}}^2}}^{{t_l}/{\sigma_{m_{\mathcal{K}}}^2}} z^{N-1} \exp(-z) \, d z}{(N-1)!}\\
-				= \exp \Bigl(-\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2}\Bigr) \sum_{n=0}^{N-1} \frac{\bigl(\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2}\bigr)^n}{n!} - \exp \Bigl(-\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr) \sum_{n=0}^{N-1} \frac{\bigl(\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\bigr)^n}{n!}.
-			\end{gathered}
+		Note the \gls{dmmac} $q(x_l|x_{m_{\mathcal{K}}})$ depends on the variance of accumulated receive energy $\sigma_{m_{\mathcal{K}}}^2$, which is a function of $\boldsymbol{w}$.
+		Plugging \eqref{eq:energy_distribution} into \eqref{eq:dmmac}, we have
+		\begin{align}
+			q(x_l|x_{m_{\mathcal{K}}})
+			 & = \frac{\int_{{t_{l-1}}/{\sigma_{m_{\mathcal{K}}}^2}}^{{t_l}/{\sigma_{m_{\mathcal{K}}}^2}} z^{N-1} \exp(-z) \, d z}{(N-1)!} \\
+			 & = Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr),
+			\label{eq:dmmac_gamma}
+		\end{align}
+		where $Q(N, b_1, b_2) \triangleq \int_{b_1}^{b_2} z^{N-1} \exp(-z) / (N - 1)! \, d z$ is the regularized incomplete Gamma function.
+		Its series expansion is given by \cite[Theorem 3]{Jameson2016}
+		\begin{align}
+			Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr)
+			 & = \exp \Bigl(-\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2}\Bigr) \sum_{n=0}^{N-1} \frac{\bigl(\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2}\bigr)^n}{n!} \nonumber \\
+			 & \quad - \exp \Bigl(-\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr) \sum_{n=0}^{N-1} \frac{\bigl(\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\bigr)^n}{n!},
 			\label{eq:regularized_incomplete_gamma}
-		\end{equation}
-		Its gradient with respect to $\boldsymbol{w}^*$ can be derived as
-		\begin{equation}
-			\nabla_{\boldsymbol{w}^*} Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr) = \frac{\boldsymbol{h}(x_{m_{\mathcal{K}}})\boldsymbol{h}^\mathsf{H}(x_{m_{\mathcal{K}}})\boldsymbol{w}}{(\sigma_{m_{\mathcal{K}}}^2)^2} g_{m_{\mathcal{K}}}(t_{l-1},t_l),
+		\end{align}
+		whose gradient with respect to $\boldsymbol{w}^*$ is
+		\begin{align}
+			\nabla_{\boldsymbol{w}^*} Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr)
+			 & = \frac{\boldsymbol{h}(x_{m_{\mathcal{K}}})\boldsymbol{h}^\mathsf{H}(x_{m_{\mathcal{K}}})\boldsymbol{w}}{(\sigma_{m_{\mathcal{K}}}^2)^2} \nonumber \\
+			 & \quad \times \Bigl(g_{m_{\mathcal{K}}}(t_l) - g_{m_{\mathcal{K}}}(t_{l-1})\Bigr),
 			\label{eq:regularized_incomplete_gamma_gradient}
-		\end{equation}
-		where $g_{m_{\mathcal{K}}}(t_{l-1},t_l) \triangleq g_{m_{\mathcal{K}}}(t_l)-g_{m_{\mathcal{K}}}(t_{l-1})$ and
+		\end{align}
+		where
 		\begin{equation}
@@
 		\end{figure*}
-		They allows problem \eqref{op:active_beamforming} to be solved by the \gls{pgd} method, where any unregulated beamformer $\bar{\boldsymbol{w}}$ can be projected onto the feasible domain of average transmit power constraint \eqref{co:transmit_power} by
-		\begin{equation}
-			\boldsymbol{w} = \sqrt{P} \frac{\bar{\boldsymbol{w}}}{\max\bigl(\sqrt{P},\lVert\bar{\boldsymbol{w}}\rVert\bigr)}.
+		Problem \eqref{op:active_beamforming} can thus be solved by the \gls{pga} method.
+		At iteration $r+1$, the unregulated active beamformer is updated by
+		\begin{equation}
+			\bar{\boldsymbol{w}}^{(r+1)} = \boldsymbol{w}^{(r)}+\gamma\nabla_{\boldsymbol{w}^*} I^{(r)}(x_{\mathcal{K}}),
+			\label{eq:beamforming_gradient_ascent}
+		\end{equation}
+		where $\gamma$ is the step size (refinable by backtracking line search \cite[Section 9.2]{Boyd2004}).
+		Then, $\bar{\boldsymbol{w}}$ is projected onto the feasible domain \eqref{co:transmit_power} to retrieve the active beamformer
+		\begin{equation}
+			\boldsymbol{w} = \frac{\sqrt{P} \bar{\boldsymbol{w}}}{\max\bigl(\sqrt{P},\lVert\bar{\boldsymbol{w}}\rVert\bigr)}.
 			\label{eq:beamforming_projection}
 		\end{equation}
-		The \gls{pgd} active beamforming optimization with step size $\gamma$ refined by \gls{bls} \cite[Section 9.2]{Boyd2004} is summarized in Algorithm \ref{al:active_beamforming}.
+
+		The \gls{pga} active beamforming design is summarized in Algorithm \ref{al:active_beamforming}.
+		\setalgorithmcaptionfont{\small}
 		\begin{algorithm}[!t]
-			\caption{Iterative Active Beamforming Optimization by \gls{pgd} with \gls{bls}}
+			\small
+			\caption{Active Beamforming Optimization by \gls{pga}}
 			\label{al:active_beamforming}
@@
 		\end{maxi!}
-		which is still non-convex because variable $\boldsymbol{t}$ appears on the limits of integration \eqref{eq:dmmac}.
-		Fortunately, we can further simplify problem \eqref{op:decision_threshold} as a point-to-point rate-optimal quantizer design for a \gls{dcmc}, thanks to Remark \ref{re:backscatter_decision} and \ref{re:augmented_source}.
-
-		\begin{remark}
-			Energy detector design has no impact on the primary achievable rate since the composite channel \eqref{eq:equivalent_channel} can always be reconstructed by re-encoding.
-			It suggests any thresholding scheme that maximize the total backscatter rate \eqref{eq:backscatter_mutual_information} is also optimal for problem \eqref{op:decision_threshold}.
-			\label{re:backscatter_decision}
-		\end{remark}
-
-		\begin{remark}
-			In terms of total backscatter rate, the potentially dispersed nodes with known input distribution can be viewed as an equivalent source with tuple codewords.
-			As such, the \gls{dmmac} \eqref{eq:dmmac} becomes a \gls{dmtc} and problem \eqref{op:decision_threshold} reduces to the rate-optimal quantization design for a \gls{dcmc}.
-			\label{re:augmented_source}
-		\end{remark}
-
-		Next, we constrain the feasible domain of problem \eqref{op:decision_threshold} from continuous space $\mathbb{R}_+^{L+1}$ to finite candidate set (i.e., fine-grained discrete energy levels) $\mathcal{T}^{L+1}$.
+		which is still non-convex since $\boldsymbol{t}$ appears on the limits of integration \eqref{eq:dmmac}.
+		Instead of solving it directly, we constrain the feasible domain from continuous space $\mathbb{R}_+^{L+1}$ to discrete candidates (i.e., fine-grained energy levels) $\mathcal{T}^{L+1}$.
+		As shown in Fig.~\ref{fg:discrete_outputs}, the decision regions are formulated by grouping adjacent energy bins.
 		\begin{figure}[!t]
@@
 		\end{maxi!}
-		which can be solved by existing rate-optimal sequential quantizer designs for \gls{dmtc}.
-		To obtain global optimal solution, \cite{He2021} started from the quadrangle inequality and proposed a \gls{dp} method accelerated by the \gls{smawk} algorithm with computational complexity $\mathcal{O}\bigl(L^2(\mathrm{card}(\mathcal{T})-L)\bigr)$, while \cite{Nguyen2020a} started from the optimality condition for three neighbor thresholds and presented a traverse-then-bisect algorithm with complexity $\mathcal{O}\bigl(\mathrm{card}(\mathcal{T})L\log(\mathrm{card}(\mathcal{T})L)\bigr)$.
-		In Section \ref{st:simulation_results}, both schemes will be compared with the \gls{ml} scheme \cite{Qian2019}
+		whose global optimal solution has been obtained in recent works.
+		\cite{He2021} started from the quadrangle inequality and proposed a \gls{dp} method accelerated by the \gls{smawk} algorithm with computational complexity $\mathcal{O}\bigl(L^2(\mathrm{card}(\mathcal{T})-L)\bigr)$.
+		On the other hand, \cite{Nguyen2020a} started from the optimality condition for three neighbor thresholds and presented a traverse-then-bisect algorithm with complexity $\mathcal{O}\bigl(\mathrm{card}(\mathcal{T})L\log(\mathrm{card}(\mathcal{T})L)\bigr)$.
+		In Section \ref{sc:simulation_results}, both schemes will be compared with the \gls{ml} scheme \cite{Qian2019}
 		\begin{equation}
@@
 \begin{section}{Simulation Results}
-	In this section, we provide numerical results to evaluate the proposed input distribution, active beamforming, and backscatter decision designs for the considered RIScatter system.
-	We assume the AP-user distance is \qty{10}{\meter} and at least one RIScatter nodes are randomly dropped in a disk centered at the user with radius $r$.
-	% The \gls{ap} is with an average transmit power budget $P=\qty{36}{\dBm}$, all nodes employs $M$-\gls{qam} with amplitude scattering ratio $\alpha=0.5$, and the user is with average noise power $\sigma_v^2=\qty{-40}{\dBm}$.
-	The \gls{ap} is with an average transmit power budget $P=\qty{36}{\dBm}$ and all nodes employs $M$-\gls{qam} with $\alpha=0.5$.
+	\label{sc:simulation_results}
+	In this section, we provide numerical results to evaluate the proposed algorithms.
+	We assume the AP-user distance is \qty{10}{m} and at least one RIScatter nodes are randomly dropped in a disk centered at the user with radius $r$.
+	The \gls{ap} is with maximum average transmit power $P=\qty{36}{dBm}$ and all nodes employs $M$-\gls{qam} with $\alpha=0.5$.
 	For all channels involved, we consider a distance-dependent path loss model
@@
 	\end{equation}
-	where $d$ is the transmission distance, $L_0=-\qty{30}{\dB}$ is the reference path loss at $d_0=\qty{1}{\meter}$, $\kappa$ is the Rician K-factor, $\bar{\boldsymbol{H}}$ is the deterministic line-of-sight component with unit-magnitude entries, and $\tilde{\boldsymbol{H}}$ is the Rayleigh fading component with standard \gls{iid} \gls{cscg} entries.
+	where $d$ is the transmission distance, $L_0=-\qty{30}{dB}$ is the reference path loss at $d_0=\qty{1}{m}$, $\kappa$ is the Rician K-factor, $\bar{\boldsymbol{H}}$ is the deterministic line-of-sight component with unit-magnitude entries, and $\tilde{\boldsymbol{H}}$ is the Rayleigh fading component with standard \gls{iid} \gls{cscg} entries.
 	We choose $\gamma_{\text{D}}=2.6$, $\gamma_{\text{F}}=2.4$, $\gamma_{\text{B}}=2$, and $\kappa_{\text{D}}=\kappa_{\text{F}}=\kappa_{\text{B}}=5$ for direct, forward and backward links.
-	The finite decision threshold domain $\mathcal{T}$ is obtained by $b$-bit uniform discretization over the critical interval defined by the confidence bounds of edge hypotheses (i.e., lower bound of $\mathcal{H}_1$ and upper bound of $\mathcal{H}_L$) with confidence $1-\varepsilon$.
-	We choose $b=9$ and $\varepsilon=\num{e-3}$.
-	All achievable rate points/regions are averaged over \num{e3} channel realizations.
+	The finite decision threshold domain $\mathcal{T}$ is obtained by $b$-bit uniform discretization over the critical interval defined by the $1-\varepsilon$ confidence bounds of edge hypotheses (i.e., lower bound of $x_1$ and upper bound of $x_L$).
+	We set $b=9$ and $\varepsilon=\num{e-3}$.
+	All achievable rate regions are averaged over \num{e3} channel realizations.
 
@@
 				}
-				\caption{Typical convergence curves at $\rho=0$ for $Q=4$, $K=8$, $M=2$, $N=20$, $\sigma_v^2=\qty{-40}{\dBm}$ and $r=\qty{2}{\meter}$.}
+				\caption{Typical convergence curves at $\rho=0$ for $Q=4$, $K=8$, $M=2$, $N=20$, $\sigma_v^2=\qty{-40}{dBm}$ and $r=\qty{2}{m}$.}
 				\label{fg:wsr_convergence}
 			\end{figure}
-
-			In Fig.~\ref{fg:wsr_convergence}, we plot the weighted sum of primary and total backscatter rates at $\rho=0$ for \gls{kkt}, \gls{pgd} and \gls{bcd} algorithms on the first call.
-			For $K=8$ and $M=2$, Algorithm \ref{al:input_distribution} typically takes around \num{100} fast iterations to converge to the \gls{kkt} input distribution.
-			For $Q=4$, around \num{10} iterations are required for Algorithm \ref{al:active_beamforming} to converge.
-			Overall, the initial \gls{bcd} algorithm requires at most \num{5} iterations to converge.
-			At the following points (not presented here), the convergence of all three algorithms are much faster thanks to the progressive initialization.
-			We conclude the proposed algorithms have good convergence performances.
+			The \gls{bcd} algorithm is convergent for problem \eqref{op:weighted_sum_rate} since the input distribution and active beamforming subproblems converge and the thresholding subproblem attains global optimality.
+			In company with \gls{bcd}, we also plotted the convergence results of \gls{kkt} and \gls{pga} algorithms in Fig.~\ref{fg:wsr_convergence} to show how much performance is gained by solving each subproblem.
+			It is observed that Algorithm \ref{al:input_distribution} and \ref{al:active_beamforming} take around \num{100} and \num{10} iterations to converge, respectively.
+			Overall, the \gls{bcd} algorithm requires at most \num{5} iterations to converge.
+			As $\rho$ increases (not presented here), the convergence of all three algorithms are much faster thanks to the progressive initialization.
 		\end{subsubsection}
@@
 		\begin{itemize}
-			\item \emph{Legacy:} Active transmission without scatterers.
-			\item \emph{\gls{bbc}:} The primary symbol becomes deterministic $s[n]=1$ and the receive signal becomes
+			\item \emph{Legacy:} Legacy transmission without scatter nodes.
+			\item \emph{\gls{bbc}:} The primary signal is \gls{cw} and the receive signal is
 			\begin{equation}
@@
 			\end{equation}
-			The total backscatter rate of coherent decoding approaches $K \log M$ when $N$ is sufficiently large.
-			% which follows non-zero mean complex Gaussian distribution $\mathcal{CN}\bigl((\boldsymbol{h}_{\text{D}}^\mathsf{H} + \sum_{k} \alpha_k \boldsymbol{h}_{\text{C},k}^\mathsf{H} x_{m_k}) \boldsymbol{w},\sigma_v^2\bigr)$ under hypothesis $\mathcal{H}_{m_{\mathcal{K}}}$.
-			% The corresponding \gls{pdf} of accumulated energy over $N$ primary blocks is
-			% \begin{equation}
-			% 	f^{\text{\gls{bbc}}}(z|\mathcal{H}_{m_{\mathcal{K}}}) = \frac{(z-\mu_{m_{\mathcal{K}}}^{\text{\gls{bbc}}})^{N-1} \exp \bigl(-(z-\mu_{m_{\mathcal{K}}}^{\text{\gls{bbc}}})/\sigma_v^2 \bigr)}{\sigma_v^{2N} (N-1)!},
-			% 	\label{eq:energy_distribution_bbc}
-			% \end{equation}
-			% where $\mu_{m_{\mathcal{K}}}^{\text{\gls{bbc}}} \triangleq N \bigl\lvert \bigl(\boldsymbol{h}_{\text{D}}^\mathsf{H} + \sum_{k} \alpha_k \boldsymbol{h}_{\text{C},k}^\mathsf{H} x_{m_k}\bigr) \boldsymbol{w} \bigr\rvert^2$.
-			% The \gls{ml} decision threshold is derived as, $\forall l \in \mathcal{L} \setminus \{L\}$,
-			% \begin{equation}
-			% 	t_l^{\text{\gls{bbc}}} = \frac{\mu_{l-1}^{\text{\gls{bbc}}} \exp \bigl((\mu_{l-1}^{\text{\gls{bbc}}}-\mu_{l}^{\text{\gls{bbc}}})/\sigma_v^2 (N-1)\bigr) - \mu_{l}^{\text{\gls{bbc}}}}{\exp \bigl((\mu_{l-1}^{\text{\gls{bbc}}}-\mu_{l}^{\text{\gls{bbc}}})/\sigma_v^2 (N-1)\bigr) - 1}.
-			% 	\label{eq:detection_threshold_ml_bbc}
-			% \end{equation}
-			\item \emph{\gls{ambc}:} The user decodes both links independently and semi-coherently by treating the other as interference.
-			The primary achievable rate is approximately\footnote{To provide a preliminary benchmark, we regard the scattered component $\sum_{k} \alpha_k \boldsymbol{h}_{\text{C},k}^\mathsf{H} x_k \boldsymbol{w}s[n]$ as \gls{awgn} during primary decoding \cite{Long2020a}.}
+			The total backscatter rate approaches $K \log M$ when $N$ is sufficiently large.
+			\item \emph{\gls{ambc}:} The user decodes each link independently and semi-coherently while treating the other as interference.
+			The primary achievable rate is approximately\footnote{The scattered component is treated as interference with average power $\mathbb{E}\bigl\{\sum_{k} \alpha_k \boldsymbol{h}_{\text{C},k}^\mathsf{H} x_k \boldsymbol{w}s[n]\bigr\} = \sum_{k} \lvert \alpha_k \boldsymbol{h}_{\text{C},k}^\mathsf{H} \boldsymbol{w} \rvert^2$ \cite{Long2020a}.\label{fn:ambc}}
 			\begin{equation}
@@
 			\end{equation}
-			The total backscatter rate of coherent decoding approaches $K \log M$ when $N$ is sufficiently large.
-			% which only involves noise uncertainty under hypothesis $\mathcal{H}_{m_{\mathcal{K}}}$.
-			% During backscatter detection, the primary symbols $s[1],\ldots,s[N]$ function as a spreading code and the receiver performs \gls{mrc} on $\hat{y}^{\text{\gls{sr}}}[n]$ over $N$ primary blocks.
-			% This essentially formulates a \gls{dcmc} and the total backscatter achievable rate is maximized with equiprobable inputs as \cite{Ng2006}
-			% \begin{equation}
-			% 	I_{\text{B}}(x_{\mathcal{K}};\hat{y}^{\text{\gls{sr}}}) = K \log M - \frac{\iota}{M^K},
-			% \end{equation}
-			% where $\iota \triangleq \sum_{m_{\mathcal{K}}} \mathbb{E}_{\hat{v}} \log \sum_{m_{\mathcal{K}}'} \exp ( - {\lvert x_{m_{\mathcal{K}}} - x_{m_{\mathcal{K}}'} + \hat{v} \rvert^2}/{2 \sigma^2} )$ and $\hat{v} \sim \mathcal{CN}(0,\sigma_v^2/N)$.
-			% For a sufficiently large $N$, $\iota$ is negligible and the total backscatter rate approaches $K \log M$.
+			The total backscatter rate approaches $K \log M$.
 			\item \emph{\gls{ris}:} The reflection pattern is deterministic and the total backscatter rate is zero.
@@
 			}
-			\caption{Typical achievable rate region/points of scattering applications for $Q=1$, $K=1$, $M=4$, $N=e3$, $\sigma_v^2=\qty{-40}{\dBm}$ and $r=\qty{2}{\meter}$.}
+			\caption{Typical achievable rate region/points of scattering applications for $Q=1$, $K=1$, $M=4$, $N=\num{e3}$, $\sigma_v^2=\qty{-40}{dBm}$ and $r=\qty{2}{m}$.}
 			\label{fg:region_comparison}
@@
 
-		Fig.~\ref{fg:region_comparison} compares the typical achievable rate region/points of RIScatter and the strategies above.
-		% \emph{First,} we observe both \gls{bbc} and \gls{sr} achieves when the spreading factor $N$ is sufficiently large.
-		\emph{First,} we observe \gls{bbc} and \gls{sr} achieve the best backscatter performance thanks to coherent decoding.
-		% However, \gls{sr} requires $N$ \gls{sic} followed by a \gls
-		% However, \gls{sr} requires $N$ re-encoding, precoding, subtraction together with a time-domain \gls{mrc} to decode each backscatter symbol and the cost can be prohibitive.
+		Fig.~\ref{fg:region_comparison} compares the typical achievable rate region/points of RIScatter and those strategies.
+		\emph{First,} we observe \gls{bbc} and \gls{sr} achieve the best backscatter performance thanks to the coherent decoding.
 		For \gls{sr}, this comes with the cost of $N$ re-encoding, precoding, subtraction together with a time-domain \gls{mrc} per backscatter symbol.
-		% However, the primary rate benefit
-		% For \gls{bbc} with coherent energy detection, the conditional \gls{pdf} of accumulated energy \eqref{eq:energy_distribution_bbc} is more skewed at a large $N$, such that the equivalent \gls{dmmac} \eqref{eq:dmmac} has lower error probabilities.
-		% For \gls{sic}-based \gls{sr}, the effective backscatter \gls{snr} is increased by $N$ times and the penalty term $\iota$ becomes insignificant.
-		% However, the primary rate is only maintained at a very large spreading factor, which significantly constrains the backscatter \emph{throughput}.
-		\emph{Second,} the average primary rate slightly decreases/increases in the presence of a \gls{ambc}/\gls{ris} node and the benefit of \gls{sr} is not obvious.
-		This is because the cascaded channel is usually orders of magnitude weaker than the direct channel.
-		\gls{ris} always ensures constructive superposition of direct and scattered components while \gls{sr} only creates a quasi-static rich-scattering environment that marginally enhances the average primary rate.
-		When $N$ is moderate, the randomly scattered signals should be modelled as interference rather than multipath components and the \gls{sr} point should move towards the \gls{ambc} point.
+		Since \gls{sr} requires a very large $N$ to guarantee the primary rate, the signal processing cost at the receiver can be prohibitive, and the backscatter \emph{throughput} can be severely constrained.
+		\emph{Second,} the average primary rate slightly decreases/increases in the presence of a \gls{ambc}/\gls{ris} node, and the benefit of \gls{sr} is not obvious.
+		This is because the cascaded channel is around \qty{25}{dB} weaker than the direct channel.
+		Here, \gls{ris} ensures a constructive superposition of the direct and scattered components, while \gls{sr} only creates a quasi-static rich-scattering environment that marginally enhances the average primary rate.
+		When $N$ is moderate, the randomly scattered signals should be modelled as interference rather than stable multipath, and the \gls{sr} point should move vertically towards the \gls{ambc} point.
 		\emph{Third,} RIScatter enables a flexible primary-backscatter tradeoff with adaptive input distribution design.
-		In terms of maximum primary achievable rate, RIScatter coincides with \gls{ris} and outperforms the others using deterministic reflection pattern.
-		On the other hand, for a large $N$, the maximum backscatter achievable rate of RIScatter is lower than \gls{bbc} and \gls{sr} but higher than \gls{ambc}.
-		This is because both RIScatter and \gls{ambc} employ semi-coherent energy detection, and the adaptive channel coding of RIScatter provides better performance than equiprobable inputs of \gls{ambc} especially at the low \gls{snr} of double fading.
+		In terms of maximum primary achievable rate, RIScatter coincides with \gls{ris} and outperforms the others by using the static reflection pattern that maximizes the primary \gls{snr} all the time.
+		On the other hand, its maximum backscatter achievable rate is higher than that of \gls{ambc}.
+		This is because the adaptive channel coding of RIScatter outperforms the equiprobable inputs of \gls{ambc}, especially at the low backscatter \gls{snr} caused by double fading.
+		When multiple antenna is available at the \gls{ap}, active beamforming can be optimized for RIScatter nodes and the advantage over \gls{ambc} should be more prominent.
 	\end{subsection}
@@
 			}
-			\caption{Typical RIScatter reflection state distribution at different $\rho$ for $Q=1$, $K=1$, $M=4$, $N=20$, $\sigma_v^2=\qty{-40}{\dBm}$ and $r=\qty{2}{\meter}$.}
+			\caption{Typical RIScatter reflection state distribution at different $\rho$ for $Q=1$, $K=1$, $M=4$, $N=20$, $\sigma_v^2=\qty{-40}{dBm}$ and $r=\qty{2}{m}$.}
 			\label{fg:distribution_weights}
@@
 		The objective is to demonstrate RIScatter nodes can leverage \gls{csi}- and \gls{qos}-adaptive input distribution design to balance backscatter modulation and passive beamforming.
-		For one RIScatter node with $M=4$, we evaluate the \gls{kkt} input distribution\footnote{Problem \eqref{op:input_distribution} is convex when $K=1$ and the \gls{kkt} solution is global optimal.} at different \gls{qos} and present the result in Fig.~\ref{fg:distribution_weights}.
+		For one RIScatter node with $M=4$, we evaluate the \gls{kkt} input distribution at different \gls{qos} and present the result in Fig.~\ref{fg:distribution_weights}.
 		At $\rho=0$ where the backscatter performance is prioritized, the optimal input distribution is \num{0} on two states and nearly uniform on the other two.
-		This is inline with Shannon's observation that binary antipodal inputs can be good enough for channel capacity at the low \gls{snr} \cite{Shannon1948}.
-		Due to the weak scattered signal, the conditional energy \gls{pdf} under different hypotheses can be closely spaced as in Fig.~\ref{fg:energy_distribution}.
-		The extreme states producing the lowest/highest energy are always assigned with non-zero probability and the middle ones may not provide enough energy difference and thus end up unused.
-		At $\rho=1$ where the primary performance is prioritized, the optimal input distribution is \num{1} at the state that maximizes the primary \gls{snr} and \num{0} at the others.
-		That is, the reflection pattern becomes deterministic and the RIScatter node boils down to a discrete \gls{ris} element.
-		Increasing $\rho$ from \num{0} to \num{1} provides a smooth transition from backscatter modulation to passive beamforming and proves RIScatter unifies \gls{bc} and \gls{ris} from a probabilistic perspective.
+		This is inline with Shannon's observation that binary antipodal inputs is good enough for channel capacity at low \gls{snr} \cite{Shannon1948}.
+		When the scattered signal is relatively weak, the conditional energy \gls{pdf} under different hypotheses can be closely spaced as in Fig.~\ref{fg:energy_distribution}.
+		The extreme states producing the lowest/highest energy are always assigned with non-zero probability, while the middles cannot provide enough energy diversity and end up unused.
+		At $\rho=1$ where the primary link is prioritized, the optimal input distribution is $[0, 0, 1, 0]^\mathsf{T}$ since state 3 provides higher primary \gls{snr} than other states.
+		That is, the reflection pattern becomes deterministic and the RIScatter node boils down to a static discrete \gls{ris} element.
+		Increasing $\rho$ from \num{0} to \num{1} creates a smooth transition from backscatter modulation to passive beamforming, suggesting RIScatter unifies \gls{bc} and \gls{ris} from a probabilistic perspective.
 	\end{subsection}
@@
 			\caption{
-				Average primary-total-backscatter rate regions by different input distribution, active beamforming, and decision threshold schemes for $K=2$, $M=4$, $N=20$, $\sigma_v^2=\qty{-40}{\dBm}$ and $r=\qty{2}{\meter}$.
+				Average primary-total-backscatter rate regions by different input distribution, active beamforming, and decision threshold schemes for $K=2$, $M=4$, $N=20$, $\sigma_v^2=\qty{-40}{dBm}$ and $r=\qty{2}{m}$.
 			}
@@
 			\begin{itemize}
-				\item \emph{Cooperation:} Joint nodes encoding using a $K$-dimensional probability array $P_{\mathcal{K}}(x_{m_{\mathcal{K}}})$ by Algorithm \ref{al:input_distribution};
+				\item \emph{Cooperation:} Joint encoding using a joint probability array $p(x_{m_{\mathcal{K}}})$ with $M^K$ entries by Algorithm \ref{al:input_distribution};
 				\item \emph{Exhaustion:} Exhaustive search over the $M$-dimensional probability simplex with resolution $\Delta p = \num{e-2}$;
-				\item \emph{\gls{kkt}:} Numerical \gls{kkt} evaluation by Algorithm \ref{al:input_distribution};
-				\item \emph{Equiprobable:} Uniform input distribution for all nodes.
+				\item \emph{\gls{kkt}:} Solution by Algorithm \ref{al:input_distribution};
+				\item \emph{Equiprobable:} Uniform input distribution.
 			\end{itemize}
-			For dispersed nodes, joint encoding is inapplicable and we consider these independent input distribution recovery methods (from the joint probability array):
+			We also consider these independent distribution recovery methods from the joint probability array:
 			\begin{itemize}
 				\item \emph{Marginalization:} Marginal probability distributions;
-				\item \emph{Decomposition:} Normalized rank-\num{1} \gls{cp} decomposition tensors by \texttt{Tensor Toolbox} \cite{Bader2022};
+				\item \emph{Decomposition:} Normalized rank-\num{1} \gls{cp} decomposed tensors by \texttt{Tensor Toolbox} \cite{Bader2022};
 				\item \emph{Randomization:} Gaussian randomization with the guidance of correlation matrix \cite{Calvo2010}.
-				% guided by correlation matrix \cite{Calvo2010}.
 			\end{itemize}
 
-			Fig.~\subref*{fg:region_distribution} shows the average achievable rate regions for those designs.
-			We observe Cooperation provides the outer bound since joint encoding is always beneficial.
-			The average rate performance of Exhaustion and \gls{kkt} completely coincide with each other, demonstrating \gls{kkt} input distribution is favorable for a moderate $K$ as stated in Remark \ref{re:input_kkt_distribution}.
-			Equiprobable experiences minor backscatter and major primary rate losses without exploiting \gls{csi} and \gls{qos}.
-			Both rate gaps should be larger when $M$ and/or $K$ increase.
-			For the recovery methods, the simple Marginalization provides a close performance to \gls{kkt}, but Randomization and Decomposition fail our expectations for most channel realizations.
-			Those observations emphasize the importance of (joint) adaptive RIScatter encoding and demonstrate the advantage of the proposed \gls{kkt} input distribution design.
+			Fig.~\subref*{fg:region_distribution} shows their average achievable rate regions.
+			Cooperation achieves the outer bound of all schemes, but joint encoding over passive devices may incur additional hardware cost.
+			Besides, the average rate performance of Exhaustion and \gls{kkt} completely coincide with each other when $K=2$.
+			This confirms Remark \ref{re:input_kkt_distribution} that the \gls{kkt} input distribution can be good enough when $K$ is moderate.
+			Equiprobable experiences minor backscatter and major primary rate losses without exploiting \gls{csi} and \gls{qos}, and those gaps should be larger when $M$ or $K$ increases.
+			Marginalization provides a close performance to \gls{kkt}, but Randomization and Decomposition fail our expectations for most channel realizations.
+			Those observations emphasize the importance of adaptive RIScatter encoding and demonstrate the advantage of the proposed \gls{kkt} input distribution design.
 		\end{subsubsection}
@@
 			\begin{itemize}
-				\item \emph{\gls{pgd}:} Iterative \gls{pgd} optimization by Algorithm \ref{al:active_beamforming};
-				\item \emph{E-\gls{mrt}:} \gls{mrt} towards the ergodic composite channel $\sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) \boldsymbol{h}^\mathsf{H}(x_{m_{\mathcal{K}}})$;
+				\item \emph{\gls{pga}:} Solution by Algorithm \ref{al:active_beamforming};
+				\item \emph{E-\gls{mrt}:} \gls{mrt} towards the ergodic composite channel $\sum_{m_{\mathcal{K}}} p(x_{m_{\mathcal{K}}}) \boldsymbol{h}^\mathsf{H}(x_{m_{\mathcal{K}}})$;
 				\item \emph{D-\gls{mrt}:} \gls{mrt} towards the direct channel $\boldsymbol{h}_{\text{D}}^\mathsf{H}$.
@@
 			Fig.~\subref*{fg:region_beamforming} presents the average achievable rate regions for those schemes.
-			In the low-$\rho$ regime, the proposed \gls{pgd} beamformer significantly outperforms both \gls{mrt} schemes in terms of total backscatter rate.
-			This is because the semi-coherent backscatter decoding relies on the \emph{relative difference} of accumulated energy under different symbol tuples.
-			Such an energy diversity is enhanced by \gls{pgd} that effectively exploits backscatter constellation and input distribution knowledge rather than simply maximizing the direct/ergodic \gls{snr}.
-			As $\rho$ increases, the primary equivalent \gls{snr} outweighs the backscatter energy difference in \eqref{eq:weighted_sum_mutual_information_explicit} and \gls{pgd} beamformer becomes closer to both \gls{mrt} schemes.
-			At $\rho=1$, both \gls{pgd} and E-\gls{mrt} boil down to \gls{mrt} towards the composite channel.
+			In the low-$\rho$ regime, the proposed \gls{pga} beamformer significantly outperforms both \gls{mrt} schemes in terms of total backscatter rate.
+			This is because the semi-coherent backscatter decoding relies on the relative energy difference under different backscatter symbol tuples.
+			Such an energy diversity is enhanced by \gls{pga} that effectively exploits backscatter constellation and input distribution knowledge rather than simply maximizes the channel strength.
+			As $\rho$ increases, the primary \gls{snr} outweighs the backscatter energy difference in \eqref{eq:weighted_sum_mutual_information_explicit}, and \gls{pga} beamformer approaches E-\gls{mrt}.
+			At $\rho=1$, both \gls{pga} and E-\gls{mrt} boil down to \gls{mrt} towards the strongest composite channel.
 			The difference between E-\gls{mrt} and D-\gls{mrt} is insignificant when RIScatter nodes are dispersed.
-			Those observations prove the proposed \gls{pgd} active beamforming design can exploit the \gls{csi}, \gls{qos}, and backscatter constellation to balance the primary equivalent \gls{snr} and backscatter energy difference and enlarge the achievable rate region.
+			Those observations confirm that the proposed \gls{pga} active beamforming design can exploit the \gls{csi}, \gls{qos}, and backscatter constellation to enlarge the achievable rate region.
 		\end{subsubsection}
@@
 			The distribution-aware schemes \gls{dp}, \gls{smawk} and Bisection ensure higher total backscatter rate than \gls{ml}.
-			This is because the total backscatter rate \eqref{eq:backscatter_mutual_information} is a function of both input distribution and decision regions, and the rate-optimal threshold design heavily depends on input distribution.
-			For example, the backscatter symbol tuples with zero input probability should be assigned with empty decision regions in order to increase the success detection rates of other hypotheses.
+			This is because the total backscatter rate \eqref{eq:backscatter_mutual_information} is a function of both input distribution and decision regions, and the rate-optimal thresholding depends heavily on the input distribution.
+			For example, the backscatter symbol tuples with zero input probability should be assigned with empty decision regions, in order to increase the success detection rates of other hypotheses.
 			It highlights the importance of joint input distribution and decision threshold design in rate maximization problems.
@@
 			}
-			\subfloat[Disk Radius\label{fg:region_coverage}]{
+			\subfloat[Imperfect \gls{csi}\label{fg:region_csi}]{
 				\resizebox{0.48\columnwidth}{!}{
-					\input{assets/simulation/region_coverage.tex}
+					\input{assets/simulation/region_csi.tex}
+				}
+			}
+			\\
+			\subfloat[Primary \gls{snr}\label{fg:region_snr_primary}]{
+				\resizebox{0.48\columnwidth}{!}{
+					\input{assets/simulation/region_snr_primary.tex}
+				}
+			}
+			\subfloat[Backscatter \gls{snr}\label{fg:region_snr_backscatter}]{
+				\resizebox{0.48\columnwidth}{!}{
+					\input{assets/simulation/region_snr_backscatter.tex}
 				}
@@
 		\end{figure}
-		In this study, we choose $Q=4$, $K=8$, $M=2$, $N=20$, $\sigma_v^2=\qty{-40}{\dBm}$ and $r=\qty{2}{\meter}$ as a reference.
+		In this study, we choose $Q=4$, $K=8$, $M=2$, $N=20$, $\sigma_v^2=\qty{-40}{dBm}$ and $r=\qty{2}{m}$ as a reference, unless otherwise specified.
 		\begin{subsubsection}{Number of Nodes}
-			Fig.~\subref*{fg:region_tags} reveals how the number RIScatter nodes $K$ influence the primary-backscatter tradeoff.
+			Fig.~\subref*{fg:region_tags} reveals how the number RIScatter nodes $K$ influences the primary-backscatter tradeoff.
 			Interestingly, we observe that increasing $K$ has a larger benefit on the total backscatter rate than primary.
-			This is because each RIScatter node not only affects the primary equivalent \gls{snr} but also influences the relative energy difference that other nodes can create.
+			This is because each RIScatter node not only affects the primary \gls{snr} but also influences the relative energy difference that other nodes can make.
 			To maximize the total backscatter rate, some nodes closer to the user may need to sacrifice their own rate and use the state that \emph{minimizes} the composite channel strength, in order to increase the backscatter rate of other nodes.
 			This accounts for the significant primary rate decrease in the low-$\rho$ regime.
-			On the other hand, when the primary link is prioritized, the RIScatter nodes boil down to \gls{ris} elements and enjoy a conventional passive array gain $N^2$.
+			On the other hand, when the primary link is prioritized, the RIScatter nodes boil down to \gls{ris} elements and enjoy a passive array gain of $K^2$.
 		\end{subsubsection}
@@
 		\begin{subsubsection}{Number of States}
-			Fig.~\subref*{fg:region_states} shows the relationship between available reflection states (i.e., \gls{qam} order) $M$ and achievable rate regions.
-			We notice increasing the reflection states has a marginal effect on both primary and total backscatter rates.
-			This is because once the scope of reflection coefficient is determined, using denser constellation points may not create enough phase resolution and energy diversity for primary and backscatter links.
-			Due to the maximum amplitude normalization in \eqref{eq:backscatter_modulation}, the average rate region of \num{8}-\gls{qam} (points on rectangle border) is smaller than that of \num{4}-\gls{qam} (points on square vertices), and the inner constellation points with smaller amplitudes are less frequently used.
-			On the other hand, \num{16}-\gls{qam} provides significant higher backscatter rate benefit than primary.
-			It motivates one to use high-resolution metamaterial units as RIScatter nodes.
-			% The results in this and previous paragraphs motivate one to replace the high-resolution metamaterial units by multiple low-order scatter nodes.
+			Fig.~\subref*{fg:region_states} shows the relationship between the available reflection states (i.e., \gls{qam} order) $M$ and the achievable rate region when $K=1$.
+			We notice that increasing the reflection states has a marginal effect on the primary rate but significantly improves the backscatter rate.
+			This is because the maximum amplitude normalized-\gls{qam} \eqref{eq:backscatter_modulation} involves more weak reflection points as $M$ increases.
+			It enhances the receive energy diversity but cannot provide enough phase shift resolution with maximum reflection.
 		\end{subsubsection}
@@
 			Fig.~\subref*{fg:region_txs} illustrates the impact of transmit antennas $Q$ on the average performance.
-			As $Q$ increases, more scattered paths are available to \gls{pgd} and the channel diversity can be further exploited to enhance the primary equivalent \gls{snr} and backscatter energy difference, which enlarges the achievable rate region.
-			It emphasizes the importance of multi-antenna RIScatter systems and demonstrate the effectiveness of the proposed \gls{pgd} design.
+			As $Q$ increases, more scattered paths become available and the channel diversity can be better exploited to improve the primary-backscatter tradeoff.
+			It emphasizes the importance of multi-antenna RIScatter systems and demonstrate the effectiveness of the proposed \gls{pga} design.
 		\end{subsubsection}
@@
 		\begin{subsubsection}{Spreading factor}
-			Fig.~\subref*{fg:region_duration} presents how the spreading factor $N$ affects the achievable rate region.
-			Please notice here the unit of total backscatter rate is bits per primary block to indicate throughput.
-			Apparently, using a very large $N$ can severely constrain the backscatter throughput, since the gain in energy certainty (by law of large numbers) cannot withstand the loss in gross rate.
-			As $N \to \infty$, RIScatter nodes boil down to \gls{ris} elements with fixed reflection pattern during whole channel block and the total backscatter rate approaches \num{0}.
-			On the other hand, when $N$ is too small, the equivalent \gls{dmmac} \eqref{eq:dmmac} has very high error probabilities and the energy detection is thus unreliable.
-			It explains the observation that $N=10$ provides lower backscatter achievable rate than $N=20$.
-			Therefore, we conclude the design of spreading factor $N$ in RIScatter systems should accommodate multiple factors (e.g., data rate requirements, load switching constraints at the nodes, and signal processing capability at the user).
+			Fig.~\subref*{fg:region_duration} shows how the spreading factor $N$ affects the achievable rate region.\footnote{Here, the unit of total backscatter rate is bits per primary block to show backscatter throughput.}
+			Using a very large $N$ (as in the case of \gls{sr}) can severely constrain the backscatter throughput, since the gain in energy certainty (by the law of large numbers) cannot withstand the loss in the gross rate.
+			As $N \to \infty$, RIScatter nodes boil down to static \gls{ris} elements and the total backscatter rate approaches \num{0}.
+			On the other hand, when $N$ is too small, the \gls{dmmac} \eqref{eq:dmmac} becomes unreliable and energy detection is error-prone.
+			It explains the observation that $N=10$ provides lower backscatter throughput than $N=20$.
+			Therefore, we conclude the spreading factor $N$ should be carefully designed over multiple factors (e.g., primary and backscatter \gls{snr}, data rate requirements, load switching speed at the nodes, and signal processing capability at the user).
 		\end{subsubsection}
@@
 			Fig.~\subref*{fg:region_noise} depicts the impact of average noise power $\sigma_v^2$ on average rate regions.
-			It shows the proposed practical semi-coherent backscatter energy detection is suitable for a wide range of noise levels.
-			When $\sigma_v^2$ relatively high, one can choose a larger $N$ to maintain the backscatter \gls{snr} for better energy detection performance.
+			Note that the noise influences both primary and backscatter \gls{snr}.
+			% It shows the proposed adaptive energy detector is suitable for a wide range of noise levels.
+			When $\sigma_v^2$ relatively high, one can choose a larger $N$ to improve the \gls{snr} of energy detection.
 		\end{subsubsection}
 
-		\begin{subsubsection}{Coverage Disk Radius}
-			Fig.~\subref*{fg:region_coverage} shows the relationship between disk radius $r$ and achievable rate region.
-			We observe both primary and backscatter performance are enhanced when nodes are located closer to the user.
-			This is because the double fading effect is less severe for near-far setups.
-			In a multi-user RIScatter system with dispersed nodes, each node may be assigned to the nearest user to guarantee uniformly good performance for both links.
+		% \begin{subsubsection}{Coverage Disk Radius}
+		% 	Fig.~\subref*{fg:region_coverage} shows the relationship between disk radius $r$ and achievable rate region.
+		% 	We observe both primary and backscatter performance are enhanced when nodes are located closer to the user.
+		% 	This is because the double fading effect is less severe for near-far setups.
+		% 	In a multi-user RIScatter network with dispersed nodes, each node may be assigned to the nearest user to guarantee uniformly good performance for both links.
+		% \end{subsubsection}
+
+		\begin{subsubsection}{Imperfect \gls{csi}}
+			Due to the lack of \gls{rf} chains at RIScatter nodes, fast and accurate acquisition of the cascaded \gls{csi} can be challenging, especially when the backscatter \gls{snr} is weak or the number of nodes is large.
+			We consider an imperfect \gls{csi} model, where the cascaded channel of node $k$ is estimated as
+			\begin{equation}
+				\hat{\boldsymbol{h}}_{\text{C},k} = \boldsymbol{h}_{\text{C},k} + \tilde{\boldsymbol{h}}_{\text{C},k},
+			\end{equation}
+			$\tilde{\boldsymbol{h}}_{\text{C},k}$ is the estimation error with entries following i.i.d.
+CSCG distribution $\mathcal{CN}(0, \iota \Lambda_\text{C})$, $\iota$ is the relative estimation error, and $\Lambda_\text{C}$ is the cascaded path loss.
+			In Fig.~\subref*{fg:region_csi}, it is observed that the channel estimation error mainly affects the backscatter rate.
+			When $\iota$ increases from \num{0} to \num{0.2}, the maximum total backscatter rate decreases by \qty{20}{\percent}.
+			This is because the energy detector is sensitive to the \gls{dmmac} \eqref{eq:dmmac} and thus the estimation of the cascaded channel.
+			On the other hand, a small estimation error may be insufficient to change the optimal passive beamforming state and the primary rate is almost unchanged.
+		\end{subsubsection}
+
+		\begin{subsubsection}{Primary \gls{snr}}
+			\label{sc:primary_snr}
+			The backscatter \gls{snr} is fixed to \qty{0}{dB} with $Q=1$ in this study.
+			Interestingly, Fig.~\subref*{fg:region_snr_primary} shows that increasing the primary \gls{snr} can improve the primary rate but degrade the backscatter rate.
+			The reason is that the relative strength of the scattered signal compared to the direct signal is weakened, such that the nodes cannot make enough difference to the energy detector.
+			This, together with Fig.~\subref*{fg:region_beamforming} and \subref*{fg:region_tags}, emphasizes the importance of balancing the primary and backscatter \gls{snr} in the design of active-passive coexisting networks.
+			% This, together with Fig.~\subref*{fg:region_beamforming} and \subref*{fg:region_tags}, emphasizes the importance of primary-backscatter tradeoff in active-passive coexisting networks.
+		\end{subsubsection}
+
+		\begin{subsubsection}{Backscatter \gls{snr}}
+			The primary \gls{snr} is fixed to \qty{20}{dB} with $Q=1$ in this study.
+			Fig.~\subref*{fg:region_snr_backscatter} shows that the primary and backscatter rates are both improved when the backscatter \gls{snr} increases.
+			This motivates one to use high-efficiency or semi-passive RIScatter nodes to improve the overall performance.
+			In a multi-user RIScatter network, each node may be assigned to the nearest user to guarantee uniformly good performance for both links.
 		\end{subsubsection}
 	\end{subsection}
-	\label{st:simulation_results}
 \end{section}
@@
 \begin{section}{Conclusion}
-	This paper introduced RIScatter as a low-power scatter protocol that simultaneously enables backscatter modulation and dynamic passive beamforming by smart input distribution design.
-	Starting from scattering principles, we showed how RIScatter nodes generalize information nodes of \gls{bc} and reflect elements of \gls{ris} as special cases, how they can be built over existing passive scatter devices, and how they simultaneously encode self information and assist legacy transmission.
-	We also propose a practical \gls{sic}-free receiver that exploits the properties of active-passive coexisting networks to guarantee primary benefit and improve backscatter throughput.
-	The achievable primary-total-backscatter rate region is then studied for a single-user multi-node RIScatter system, where the input distribution, active beamforming, and decision thresholds are iteratively updated.
-	Numerical results not only validated the proposed algorithms but also emphasized the importance of adaptive input distribution and cooperative decoding for both primary and backscatter links.
-
-	One possible future direction is to consider backscatter detection over the received signal domain rather than energy domain, where multi-antenna \cite{Liu2022c} and learning-based approaches can be promising.
-	Another interesting question is how to design RIScatter node and receiver in a multi-user system to fully exploit the dynamic passive beamforming that naturally origins from backscatter modulation.
-	% If one node can be decoded by multiple users, its input distribution may be further adjusted to mimic the multi-beam gain of dynamic passive beamforming \cite{Qiu2022}.
-	% This will be answered in our future work.
+	\label{sc:conclusion}
+	This paper introduced RIScatter as a novel scatter protocol that bridges backscatter modulation and passive beamforming.
+	Starting from scattering principles, we showed how RIScatter nodes generalize information nodes of \gls{bc} and reflect elements of \gls{ris}, how they can be built over existing passive scatter devices, and how they simultaneously encode self information and assist legacy transmission.
+	We also proposed a practical \gls{sic}-free receiver that exploits the properties of active-passive coexisting networks to benefit both subsystems.
+	The achievable primary-total-backscatter rate region was then studied for a single-user multi-node RIScatter network, where the input distribution, active beamforming, and decision thresholds are iteratively updated.
+	Numerical results validated the proposed algorithms and emphasized the importance of adaptive input distribution and cooperative receiver design.
+
+	To support massive RIScatter networks with large number of nodes and states, one possible future direction is to consider backscatter detection over the received signal domain rather than energy domain, where multi-antenna \cite{Liu2022c} and learning-based approaches can be promising.
+	Another interesting question is how to design RIScatter nodes and receivers in a multi-user system to fully exploit the dynamic passive beamforming that naturally origins from backscatter modulation.
 \end{section}
@@
 	\begin{subsection}{Proof of Proposition \ref{pr:input_kkt_condition}}
-		Denote the Lagrange multipliers associated with \eqref{co:sum_probability} and \eqref{co:nonnegative_probability} as $\{\nu_k\}_{k \in \mathcal{K}}$ and $\{\lambda_{k,m_k}\}_{k \in \mathcal{K},m_k \in \mathcal{M}}$, respectively.
+		Denote the Lagrange multipliers associated with \eqref{co:sum_probability} and \eqref{co:nonnegative_probability} as $\{\nu_k\}_{k \in \mathcal{K}}$ and $\{\lambda_{m_k}\}_{k \in \mathcal{K},m_k \in \mathcal{M}}$, respectively.
 		The Lagrangian function of problem \eqref{op:input_distribution} is
 		\begin{equation}
-			- I(x_{\mathcal{K}}) + \sum_k \nu_k \biggl( \sum_{m_k} P_k(x_{m_k}) - 1 \biggr) - \sum_k \sum_{m_k} \lambda_{k,m_k} P_k(x_{m_k})
+			L(p, \nu, \lambda) = I(x_{\mathcal{K}}) + \sum_k \nu_k \Bigl( \sum_{m_k} p(x_{m_k}) - 1 \Bigr) + \sum_{k,m_k} \lambda_{m_k} p(x_{m_k}),
 		\end{equation}
@@
 		\begin{equation}
-			P_k^\star(x_{m_k}) = \frac{P_k'(x_{m_k}) \exp \Bigl( \frac{\rho}{1 - \rho} I_k'(x_{m_k}) \Bigr)}{\sum_{m_k'} P_k'(x_{m_k'}) \exp \Bigl( \frac{\rho}{1 - \rho} I_k'(x_{m_k'}) \Bigr)}.
+			p^\star(x_{m_k}) = \frac{p'(x_{m_k}) \exp \Bigl( \frac{\rho}{1 - \rho} I_k'(x_{m_k}) \Bigr)}{\sum_{m_k'} p'(x_{m_k'}) \exp \Bigl( \frac{\rho}{1 - \rho} I_k'(x_{m_k'}) \Bigr)}.
 			\label{eq:optimal_relative_distribution}
 		\end{equation}
-		Since $P_k(x_{i_k}) = 1 - \sum_{m_k \ne i_k} P_k^\star(x_{m_k})$ has exactly the same form as \eqref{eq:optimal_relative_distribution}, the choice of reference state $i_k$ does not matter and \eqref{eq:optimal_relative_distribution} is indeed optimal $\forall m_k \in \mathcal{M}$.
-		That is, for a fixed $P_{\mathcal{K}}'(x_{m_{\mathcal{K}}})$, choosing $P_k(x_{m_k})$ by \eqref{eq:optimal_relative_distribution} ensures
-		\begin{equation}
-			J \bigl( P_{\mathcal{K}}(x_{m_{\mathcal{K}}}),P_{\mathcal{K}}'(x_{m_{\mathcal{K}}}) \bigr) \ge I'(x_{\mathcal{K}}).
+		Since $p(x_{i_k}) = 1 - \sum_{m_k \ne i_k} p^\star(x_{m_k})$ has exactly the same form as \eqref{eq:optimal_relative_distribution}, the choice of reference does not matter and \eqref{eq:optimal_relative_distribution} is optimal $\forall m_k \in \mathcal{M}$.
+		That is, for a fixed $p'(x_{m_{\mathcal{K}}})$, \eqref{eq:optimal_relative_distribution} ensures
+		\begin{equation}
+			J \bigl( p(x_{m_{\mathcal{K}}}),p'(x_{m_{\mathcal{K}}}) \bigr) \ge I'(x_{\mathcal{K}}).
 			\label{eq:information_difference_lower}
 		\end{equation}
-		On the other hand, we also have
+		On the other hand, we notice
 		\begin{subequations}
+			\allowdisplaybreaks
 			\label{eq:information_difference_upper}
 			\begin{align}
-				\Delta
-				 & \triangleq I(x_{\mathcal{K}}) - J \bigl( P_{\mathcal{K}}(x_{m_{\mathcal{K}}}),P_{\mathcal{K}}'(x_{m_{\mathcal{K}}}) \bigr)                                                                                  \\
-				 & = (1 - \rho) \sum_{m_k} \frac{P_k'(x_{m_k}) f_k'(x_{m_k})}{\sum_{m_k'} P_k'(x_{m_k'}) f_k'(x_{m_k'})} \sum_{m_{\mathcal{K}}''} P(\hat{x}_{m_{\mathcal{K}}''}|x_{m_k})\nonumber                              \\
-				 & \quad \times \log \frac{\sum_{m_k'} P_k'(x_{m_k'}) P(\hat{x}_{m_{\mathcal{K}}''}|x_{m_k'}) f_k'(x_{m_k})}{\sum_{m_k'} P_k'(x_{m_k'}) P(\hat{x}_{m_{\mathcal{K}}''}|x_{m_k'}) f_k'(x_{m_k'})}                \\
-				 & \ge (1 - \rho) \sum_{m_k} \frac{P_k'(x_{m_k}) f_k'(x_{m_k})}{\sum_{m_k'} P_k'(x_{m_k'}) f_k'(x_{m_k'})} \sum_{m_{\mathcal{K}}''} P(\hat{x}_{m_{\mathcal{K}}''}|x_{m_k})\nonumber                            \\
-				 & \quad \times \Biggl( 1 - \frac{\sum_{m_k'} P_k'(x_{m_k'}) P(\hat{x}_{m_{\mathcal{K}}''}|x_{m_k'}) f_k'(x_{m_k'})}{\sum_{m_k'} P_k'(x_{m_k'}) P(\hat{x}_{m_{\mathcal{K}}''}|x_{m_k'}) f_k'(x_{m_k})} \Biggr) \\
+				 & I(x_{\mathcal{K}}) - J \bigl( p(x_{m_{\mathcal{K}}}),p'(x_{m_{\mathcal{K}}}) \bigr)                                                                                                                    \nonumber           \\
+				 & = (1 - \rho) \sum_{m_k} \frac{p'(x_{m_k}) f_k'(x_{m_k})}{\sum_{m_k'} p'(x_{m_k'}) f_k'(x_{m_k'})} \sum_{m_{\mathcal{K}}''} q(\hat{x}_{m_{\mathcal{K}}''}|x_{m_k})                                      \nonumber           \\
+				 & \quad \times \log \frac{\sum_{m_k'} p'(x_{m_k'}) q(\hat{x}_{m_{\mathcal{K}}''}|x_{m_k'}) f_k'(x_{m_k})}{\sum_{m_k'} p'(x_{m_k'}) q(\hat{x}_{m_{\mathcal{K}}''}|x_{m_k'}) f_k'(x_{m_k'})}                                   \\
+				 & \ge (1 - \rho) \sum_{m_k} \frac{p'(x_{m_k}) f_k'(x_{m_k})}{\sum_{m_k'} p'(x_{m_k'}) f_k'(x_{m_k'})} \sum_{m_{\mathcal{K}}''} q(\hat{x}_{m_{\mathcal{K}}''}|x_{m_k})                                    \nonumber           \\
+				 & \quad \times \Biggl( 1 - \frac{\sum_{m_k'} p'(x_{m_k'}) q(\hat{x}_{m_{\mathcal{K}}''}|x_{m_k'}) f_k'(x_{m_k'})}{\sum_{m_k'} p'(x_{m_k'}) q(\hat{x}_{m_{\mathcal{K}}''}|x_{m_k'}) f_k'(x_{m_k})} \Biggr)                    \\
+				 & = (1 - \rho) \Biggl( 1 - \sum_{m_k} \frac{p'(x_{m_k}) \cancel{f_k'(x_{m_k})}}{\sum_{m_k'} p'(x_{m_k'}) f_k'(x_{m_k'})} \sum_{m_{\mathcal{K}}''} q(\hat{x}_{m_{\mathcal{K}}''}|x_{m_k})                 \nonumber           \\
+				 & \quad \times \frac{\sum_{m_k'} p'(x_{m_k'}) q(\hat{x}_{m_{\mathcal{K}}''}|x_{m_k'}) f_k'(x_{m_k'})}{\sum_{m_k'} p'(x_{m_k'}) q(\hat{x}_{m_{\mathcal{K}}''}|x_{m_k'}) \cancel{f_k'(x_{m_k})}} \Biggr)                       \\
+				 & = (1 - \rho) \Biggl( 1 - \sum_{m_{\mathcal{K}}''} \frac{\cancel{\sum_{m_k} p'(x_{m_k}) q(\hat{x}_{m_{\mathcal{K}}''}|x_{m_k})}}{\sum_{m_k'} p'(x_{m_k'}) f_k'(x_{m_k'})}                                        \nonumber  \\
+				 & \quad \times \frac{\sum_{m_k'} p'(x_{m_k'}) q(\hat{x}_{m_{\mathcal{K}}''}|x_{m_k'}) f_k'(x_{m_k'})}{\cancel{\sum_{m_k'} p'(x_{m_k'}) q(\hat{x}_{m_{\mathcal{K}}''}|x_{m_k'})}} \Biggr)                                     \\
+				 & = (1 - \rho) \Biggl( 1 - \frac{\sum_{m_k'} p'(x_{m_k'}) f_k'(x_{m_k'}) \sum_{m_{\mathcal{K}}''} q(\hat{x}_{m_{\mathcal{K}}''}|x_{m_k'})}{\sum_{m_k'} p'(x_{m_k'}) f_k'(x_{m_k'})} \Biggr)                        \nonumber \\
 				 & = 0,
@@
 		\end{subequations}
-		where $f_k'(x_{m_k}) \triangleq \exp \bigl( \frac{\rho}{1 - \rho} I_k'(x_{m_k}) \bigr)$ and the equality holds if and only if \eqref{eq:optimal_relative_distribution} converges.
+		where $f_k'(x_{m_k}) \triangleq \exp \bigl( \frac{\rho}{1 - \rho} I_k'(x_{m_k}) \bigr)$ and the equality holds if and only if $p(x_{m_{\mathcal{K}}})$ and $p'(x_{m_{\mathcal{K}}})$ equals (i.e., \eqref{eq:optimal_relative_distribution} converges).
 		\eqref{eq:information_difference_lower} and \eqref{eq:information_difference_upper} together imply $I(x_{\mathcal{K}}) \ge I'(x_{\mathcal{K}})$.
-		Since mutual information is bounded above, we conclude the sequence \eqref{eq:input_kkt_solution} is non-decreasing and convergent in mutual information.
-
-		Next, we prove any converging point of sequence \eqref{eq:input_kkt_solution}, denoted as $P_k^\star(x_{m_k})$, fulfills \gls{kkt} conditions \eqref{eq:input_kkt_condition}.
-		To see this, let
-		\begin{equation}
-			D_k^{(r)}(x_{m_k}) \triangleq \frac{P_k^{(r+1)}(x_{m_k})}{P_k^{(r)}(x_{m_k})} = \frac{f_k^{(r)}(x_{m_k})}{\sum_{m_k'} P_k^{(r)}(x_{m_k'}) f_k^{(r)}(x_{m_k'})}.
-		\end{equation}
-		As sequence \eqref{eq:input_kkt_solution} is convergent, any state with $P_k^\star(x_{m_k}) > 0$ need to satisfy $D_k^\star(x_{m_k}) \triangleq \lim_{r \to \infty} D_k^{(r)}(x_{m_k}) = 1$, namely
-		\begin{equation}
-			I_k^\star(x_{m_k}) = \frac{1 - \rho}{\rho} \log \sum_{m_k'} P_k^\star(x_{m_k'}) f_k^\star(x_{m_k'}),
-		\end{equation}
-		which is reminiscent of \eqref{eq:probable_states_marginal} and \eqref{eq:probable_states}.
-		That is, given $P_k^{(0)}(x_{m_k}) > 0$, any converging point with $P_k^\star(x_{m_k}) > 0$ must satisfy \eqref{eq:probable_states}.
-		On the other hand, we assume $P_k^\star(x_{m_k})$ does not satisfy \eqref{eq:dropped_states}, such that for any state with $P_k^\star(x_{m_k}) = 0$,
-		\begin{equation}
-			I_k^\star(x_{m_k}) > I^\star(x_{\mathcal{K}}) = \sum_{m_k'} P_k^\star(x_{m_k'}) I_k^\star(x_{m_k'}),
-		\end{equation}
-		where the equality inherits from \eqref{eq:weighted_sum_mutual_information}.
-		Since the exponential function is monotonically increasing, we have $f_k^\star(x_{m_k}) > \sum_{m_k'} P_k^\star(x_{m_k'}) f_k^\star(x_{m_k'})$ and $D_k^\star(x_{m_k}) > 1$.
-		Considering $P_k^{(0)}(x_{m_k}) > 0$ and $P_k^\star(x_{m_k}) = 0$, it contradicts with
-		\begin{equation}
-			P_k^{(r)}(x_{m_k}) = P_k^{(0)}(x_{m_k}) \prod_{n=1}^r D_k^{(n)}(x_{m_k}).
-		\end{equation}
-		That is, given $P_k^{(0)}(x_{m_k}) > 0$, any converging point with $P_k^\star(x_{m_k}) = 0$ must satisfy \eqref{eq:dropped_states}.
-		The proof is thus completed.
+		Since mutual information is bounded above, we conclude the sequence \eqref{eq:input_kkt_solution} is non-decreasing and convergent.
+
+		Next, we prove any converging point of sequence \eqref{eq:input_kkt_solution}, denoted as $p^\star(x_{m_k})$, fulfills the \gls{kkt} conditions \eqref{eq:input_kkt_condition}.
+		Let
+		\begin{equation}
+			D^{(r)}(x_{m_k}) \triangleq \frac{p^{(r+1)}(x_{m_k})}{p^{(r)}(x_{m_k})} = \frac{f_k^{(r)}(x_{m_k})}{\sum_{m_k'} p^{(r)}(x_{m_k'}) f_k^{(r)}(x_{m_k'})}.
+		\end{equation}
+		As sequence \eqref{eq:input_kkt_solution} is convergent, any state with $p^\star(x_{m_k}) > 0$ need to satisfy $D^\star(x_{m_k}) \triangleq \lim_{r \to \infty} D^{(r)}(x_{m_k}) = 1$, namely
+		\begin{equation}
+			I_k^\star(x_{m_k}) = \frac{1 - \rho}{\rho} \log \sum_{m_k'} p^\star(x_{m_k'}) \exp \Bigl( \frac{\rho}{1 - \rho} I_k^\star(x_{m_k'}) \Bigr).
+		\end{equation}
+		The right-hand side is a constant for node $k$ and implies \eqref{eq:probable_states_marginal}.
+		That is, any converging point with nonzero probability must satisfy \eqref{eq:probable_states}.
+		On the other hand, we assume $p^\star(x_{m_k}) = 0$ does not satisfy \eqref{eq:dropped_states}, namely
+		\begin{equation}
+			I_k^\star(x_{m_k}) > I^\star(x_{\mathcal{K}}) = \sum_{m_k'} p^\star(x_{m_k'}) I_k^\star(x_{m_k'}),
+			\label{eq:dropped_states_assumption}
+		\end{equation}
+		Since the exponential function is monotonically increasing, \eqref{eq:dropped_states_assumption} implies $f_k^\star(x_{m_k}) > \sum_{m_k'} p^\star(x_{m_k'}) f_k^\star(x_{m_k'})$ and $D^\star(x_{m_k}) > 1$.
+		It contradicts with
+		\begin{equation}
+			p^{(r)}(x_{m_k}) = p^{(0)}(x_{m_k}) \prod_{n=1}^r D^{(n)}(x_{m_k}),
+		\end{equation}
+		since the left-hand side is zero while all terms on the right-hand side are strictly positive.
+		The proof is completed.
 		\label{ap:input_kkt_solution}
 	\end{subsection}
-
-	% \begin{subsection}{Proof of Proposition \ref{pr:threshold}}
-	% 	Since $L$ input letters are with non-zero probability and $x \to z \to \hat{x}$ formulates a Markov chain, we need $L$ non-empty decision regions and at least $L+1$ distinct thresholds (including \num{0} and $\infty$) to minimize the distortion between source and decision.
-	% 	On the other hand, the optimal decision regions are apparently empty for those unused letters.
-
-	% 	Suppose the optimal number of thresholds is $S+1$ where $S \ge L$.
-	% 	Let $\boldsymbol{t} \triangleq [t_0,\ldots,t_S]^\mathsf{T} \in \mathbb{R}_{+}^{(S+1)}$ be the optimal threshold vector where $t_{s-1} < t_s$, $\forall s \in \mathcal{S} \triangleq \{1,\ldots,S\}$.
-	% 	Since the optimal decision region for any letter may consist of multiple partitions, without loss of generality, we assume the mapping from threshold vector to decision region $l' \in \mathcal{L} \triangleq \{1,\ldots,L\}$ is given by $\mathcal{R}_{l'} = \bigcup_{s \equiv l' \pmod L} [t_{s-1},t_s)$.
-	% 	\begin{footnote}
-	% 		The proof holds for any valid mapping from threshold vector to decision regions, and we consider this specific case for the ease of presentation.
-	% 	\end{footnote}
-	% 	The threshold optimization problem is
-	% 	\begin{maxi!}
-	% 		{\scriptstyle{\boldsymbol{t}}}{I_{\text{B}}(x;\hat{x})}{\label{op:decision_threshold}}{\label{ob:backscatter_mutual_information}}
-	% 		\addConstraint{t_{s-1}}{< t_s,}{\quad \forall s \in \mathcal{S}.}{\label{co:strict_inequality}}
-	% 	\end{maxi!}
-
-	% 	Problem \eqref{op:decision_threshold} is intricate due to the strict inequality constraint \eqref{co:strict_inequality}.
-	% 	Following \cite{Nguyen2020}, we first relax it to the convex counterpart, then discard the solutions that violate any original constraint.
-	% 	The Lagrangian function for the relaxed problem is
-	% 	\begin{equation}
-	% 		L = - I_{\text{B}}(x;\hat{x}) + \sum_{s \in \mathcal{S}} \mu_s (t_{s-1} - t_s),
-	% 	\end{equation}
-	% 	where $\mu_s$ is the Lagrange multiplier associated with the non-strict version of \eqref{co:strict_inequality}.
-	% 	The \gls{kkt} conditions on the optimal primal and dual solutions are, $\forall s \in \mathcal{S}$,
-	% 	\begin{subequations}
-	% 		\label{eq:kkt_thresholding}
-	% 		\begin{equation}
-	% 			- \nabla_{t_s^\star} I^\star_{\text{B}}(x;\hat{x}) + \mu_{s-1}^\star - \mu_s^\star = 0,
-	% 			\label{eq:stationarity}
-	% 		\end{equation}
-	% 		\begin{equation}
-	% 			\mu_s^\star \ge 0,
-	% 			\label{eq:dual_feasibility}
-	% 		\end{equation}
-	% 		\begin{equation}
-	% 			\mu_s^\star (t_{s-1}^\star - t_s^\star) = 0.
-	% 			\label{eq:complementary_slackness}
-	% 		\end{equation}
-
-	% 	\end{subequations}
-	% 	Due to the strict inequality constraint \eqref{co:strict_inequality}, conditions \eqref{eq:dual_feasibility} and \eqref{eq:complementary_slackness} together imply $\mu_s^\star = 0$, $\forall s \in \mathcal{S}$.
-	% 	Besides, it is trivial to conclude $t_0^\star = 0$ for energy-based detection.
-	% 	As such, the necessary optimality conditions for problem \eqref{op:decision_threshold}, $\forall s \in \mathcal{S}$,
-	% 	\begin{equation}
-	% 		\nabla_{t_{s}^\star} I^\star_{\text{B}}(x;\hat{x}) = 0,
-	% 	\end{equation}
-	% 	which can be explicitly written as, $\forall s \equiv l' \pmod L$,
-	% 	\begin{equation}
-	% 		\sum_l P(x_l) \frac{(t_s^\star)^{N-1} \exp{-t_s^\star/\sigma_l^2}}{\sigma_l^{2N} (N-1)!} \log \frac{P(x_l|\hat{x}_{l'+1})}{P(x_l|\hat{x}_{l'})} = 0,
-	% 		\label{eq:kkt_threshold_explicit}
-	% 	\end{equation}
-
-	% 	According to \cite{He2021}, the optimal backward channel quantizer is convex and separates each pair of posterior distribution by a hyperplane.
-	% 	It implies, for a given output letter $l'$, the sequence $\{\log {P(x_l|\hat{x}_{l'+1})}/{P(x_l|\hat{x}_{l'})}\}_{l \in \mathcal{L}}$ changes sign exactly once.
-	% 	We notice the left-hand side of \eqref{eq:kkt_threshold_explicit} is a generalized Dirichlet polynomial, and by Descartes' rule of signs \cite{Jameson2006}, has at most one positive solution.
-	% 	% TODO
-	% 	In other words, starting from $t_0^\star$, each optimal decision region requires at most one additional distinct threshold, and we have $S \le L$.
-	% 	Therefore, we conclude $S = L$ and the proof is completed.
-	% 	\qedsymbol
-	% 	\label{ap:threshold}
-	% \end{subsection}
 \end{appendix}

### 2023-08-15 jsac.tex
:triangular_flag_on_post: JSAC 230815

@@
 \usepackage[subtle]{savetrees}
-\usepackage{setspace}
 \usepackage{siunitx}
@@
 % page limit hacks
+\usepackage{setspace}
 % ! \usepackage[top=1cm, bottom=1cm, left=1cm, right=1cm]{geometry}
@@
 \setlength{\skip\footins}{2mm}
-% dark mode
-% \usepackage{xcolor} \pagecolor[rgb]{0,0,0} \color[rgb]{1,1,1}
 
@@
 \begin{IEEEkeywords}
-	Input distribution design, symbol-level precoding, index modulation, active-passive coexisting network, \gls{sic}-free receiver, energy detection, backscatter communication, reconfigurable intelligent surface, ambient backscatter communication, symbiotic radio.
+	Backscatter communication, reconfigurable intelligent surface, active-passive coexisting network, input distribution design, \gls{sic}-free receiver.
 \end{IEEEkeywords}
@@
 
-	% \begin{subsection}{Related Works}
-	As a special case of \gls{cr}, active and passive transmissions coexist and interplay in \gls{ambc} and \gls{sr}.
-	Such a coexistence is classified into commensal (overlay), parasitic (underlay), and competitive (interfering) paradigms, and their achievable rate and outage performance were investigated in \cite{Guo2019b,Ding2020}.
-	For the co-located cooperative receiver, the \gls{ber} performance of \gls{ml}, linear, and \gls{sic} detectors are derived over flat fading channels \cite{Yang2018}.
-	However, the work assumed equal symbol duration and perfect synchronization for primary and backscatter links.
-	Importantly, active-passive coexisting networks have three special and important properties:
-	\begin{enumerate}
-		\item Primary and backscatter symbols are superimposed by \emph{double modulation} (i.e., multiplication coding);
-		\item Backscatter signal strength is much weaker than primary due to the \emph{double fading} effect;
-		\item The spreading factor (i.e., backscatter symbol duration over primary) is usually large\footnote{The load-switching interval of low-power backscatter modulators is usually \num{0.1} to \SI{10}{\us} \cite{Torres2021}, accounting for a typical spreading factor between \num{10} and \num{e3}.}.
-	\end{enumerate}
-	The second property motivated \cite{Long2020a,Liang2020,Guo2019b,Ding2020,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Yang2018,Han2021,Zhang2022} to view \gls{sr} as a multiplicative \gls{noma} and perform \gls{sic} from primary to backscatter link.
-	During primary decoding, the backscatter signal can be modelled as channel uncertainty or multiplicative interference when the spreading factor is large or small, respectively.
-	Decoding each backscatter symbol also requires multiple \gls{sic} followed by a \gls{mrc} and is operation-intensive and \gls{csi}-sensitive.
-	% Such a \gls{sic} receiver is operation-intensive and \gls{csi}-sensitive because it involves $N$ re-encoding, precoding, subtraction together with a time-domain \gls{mrc} to decode each backscatter symbol.
-	When the spreading factor is sufficiently large, the primary achievable rate under semi-coherent detection\footnote{In this paper, semi-coherent detection refers to the primary/backscatter decoding with known \gls{csi} and unknown backscatter/primary symbols.} asymptotically approaches its coherent counterpart and both links are decoded interference-free \cite{Long2020a}.
-	% However, it significantly increases \gls{sic} operations per backscatter symbol and severely limits the backscatter \emph{throughput}.
-	However, this severely limits the backscatter throughput and requires numerous \gls{sic} per backscatter symbol.
-
-	% On the other hand, efficient backscatter multiple access design remains an open issue for \gls{bc}.
-	% \cite{Xu2021a} proposed a \gls{noma}-based \gls{sr} where the \gls{sic} order depends on the backscatter channel strength, but the performance deteriorates fast as the number of nodes increases.
-	% \gls{tdma}-based \gls{sr} was also considered in \cite{Yang2021a} where each node transmits information during its dedicated slot and harvests energy otherwise.
-	% It enables adaptive transmission time and reflection ratio design but introduces extra coordination cost.
-	% \cite{Vougioukas2019} modifies the load-switching speed to shift the scattered signal to the desired frequency band.
-	% This enables backscatter \gls{fdma} at the cost of larger bandwidth and higher power consumption at the scatter nodes.
-	% To reduce the coordination cost, \cite{Han2021} proposed a random code-assisted multiple access for \gls{sr} and evaluated the asymptotic \gls{sinr} using random matrix theory.
-	% This code-domain solution suffers from the near-far problem and imperfect synchronization, both being severe in \gls{bc}.
-
-	% A comparison of scattering applications is summarized in Table~\ref{tb:scattering_applications}.
-
-	On the other hand, static \gls{ris} design with fixed reflection pattern per channel block has been extensively studied in wireless communication, sensing, and power literature \cite{Wu2018,Zhang2019a,Lin2022,Liu2022,Feng2022,Zhao2022}.
+	On the other hand, static \gls{ris} that employs fixed reflection pattern per channel block has been extensively studied in wireless communication, sensing, and power literature \cite{Wu2018,Zhang2019a,Lin2022,Liu2022,Feng2022,Zhao2022}.
 	Dynamic \gls{ris} performs time sharing between different phase shifts and introduces artificial channel diversity within each channel block.
-	It was first proposed to fine-tune the \gls{ofdm} resource blocks \cite{Yang2020} then extended to the downlink power and uplink information phases of \gls{wpcn} \cite{Wu2021,Wu2021d,Hua2022a}.
-	However, dynamic \gls{ris} carries \emph{no} additional information since the reflection state at each time slot is known to the receiver.
-	\gls{ris} can also be used as an information source and prototypes have been developed for \gls{psk} \cite{Tang2019a} and \gls{qam} \cite{Dai2020a}.
-	From an information-theoretic perspective, the authors of \cite{Karasik2020} reported that joint transmitter-\gls{ris} encoding achieves the capacity of \gls{ris}-aided finite-input channel and using \gls{ris} as a naive passive beamformer to maximize the receive \gls{snr} is generally suboptimal.
-	This inspired \gls{ris}-empowered \gls{bc} \cite{Liu2019d,Bereyhi2020,Xu2020b,Zhang2021d,Hu2021b,Hua2022,Basar2020,Ma2020a,Yuan2021,Hu2021a} to combine passive beamforming and backscatter modulation in the overall reflection pattern.
+	The idea was first proposed to fine-tune the \gls{ofdm} resource blocks \cite{Yang2020}, then extended to the downlink power and uplink information phases of \gls{wpcn} \cite{Wu2021,Wu2021d,Hua2022a}.
+	However, dynamic \gls{ris} carries no information because the reflection state at a specific time is known to the receiver.
+	\gls{ris} can also be used as an information source, and prototypes have been developed for \gls{psk} \cite{Tang2019a} and \gls{qam} \cite{Dai2020a}.
+	From an information-theoretic perspective, the authors of \cite{Karasik2020} reported that joint transmitter-\gls{ris} encoding achieves the capacity of \gls{ris}-aided finite-input channel, and using \gls{ris} as a naive passive beamformer to maximize the receive \gls{snr} is generally rate-suboptimal.
+	This inspired \cite{Liu2019d,Bereyhi2020,Xu2020b,Zhang2021d,Hu2021b,Hua2022,Basar2020,Ma2020a,Yuan2021,Hu2021a} to combine passive beamforming and backscatter modulation in the overall \gls{ris} design.
 	In particular, \emph{symbol level precoding} maps the information symbols to the optimized \gls{ris} coefficient sets \cite{Liu2019d,Bereyhi2020}, \emph{overlay modulation} superposes the information symbols over a common auxiliary matrix \cite{Xu2020b,Zhang2021d,Hu2021b,Hua2022}, \emph{spatial modulation} switches between the reflection coefficient sets that maximize \gls{snr} at different receive antennas \cite{Basar2020,Ma2020a,Yuan2021}, and \emph{index modulation} employs dedicated reflection elements (resp.
@@
 backscatter modulation) \cite{Hu2021a}.
-	However, those joint designs incur advanced hardware architecture and high optimization complexity.
-	Relevant literature also considers either Gaussian codebook \cite{Guo2019b,Ding2020,Long2020a,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Hu2021b} that is impractical for low-power nodes or finite equiprobable inputs \cite{Yang2018,Liang2020,Han2021,Zhang2022,Liu2019d,Bereyhi2020,Xu2020b,Zhang2021d,Hua2022,Basar2020,Ma2020a,Yuan2021,Hu2021a} that does not fully exploit the \gls{csi} and properties of active-passive coexisting networks.
-	% \end{subsection}
+	Those \gls{ris}-based backscatter modulation schemes incur advanced hardware architecture and high optimization complexity.
+	In contrast, \cite{Vardakis2023} exploits commodity \gls{rfid} tags, powered and controlled by a software-defined radio reader at a different frequency, to perform passive beamforming (but no backscatter modulation) towards a legacy user.
+\label{cm:2.5}
+	% The authors demonstrated the feasibility of using batteryless devices to adaptively enhance the \gls{snr} of a primary link, but did not consider backscatter modulation at.
+	Most relevant literature considers either Gaussian codebook \cite{Guo2019b,Ding2020,Long2020a,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Hu2021b} that is impractical for low-power nodes, or finite equiprobable inputs \cite{Yang2018,Liang2020,Han2021,Zhang2022,Liu2019d,Bereyhi2020,Xu2020b,Zhang2021d,Hua2022,Basar2020,Ma2020a,Yuan2021,Hu2021a} that does not fully exploit the \gls{csi} and properties of active-passive coexisting networks.
 	Those problems are addressed in this paper and the contributions are summarized below.
 
-	% \begin{subsection}{Contributions}
 	\emph{First,} we propose RIScatter as a novel protocol that unifies \gls{bc} and \gls{ris} by adaptive reflection state (backscatter input) distribution design.
-	% \emph{First,} we propose RIScatter as a novel scatter protocol that simultaneously modulates the node information and engineers the wireless channel via adaptive reflection state (backscatter input) distribution design.
-	The concept is shown in Fig.~\subref*{fg:riscatter} where one or more RIScatter nodes ride over an active transmission and simultaneously modulate their information and engineer the wireless channel.
-	A co-located receiver cooperatively decodes both coexisting links and each reflection state simultaneously acts as information and passive beamforming codewords.
-	The reflection pattern of each node is semi-randomly chosen with the guidance of input distribution as a joint function of the information source, \gls{csi}, and \gls{qos}.
+	The concept is shown in Fig.~\subref*{fg:riscatter}, where one or more RIScatter nodes ride over an active transmission to simultaneously modulate their information and engineer the wireless channel.
+	A co-located receiver cooperatively decodes both coexisting links.
+	Each reflection state is simultaneously an information codeword and a passive beamforming codeword.
+	The reflection pattern over time is semi-random and guided by the input probability assigned to each state.
+	This probability distribution is carefully designed to incorporate the backscatter information, \gls{csi}, and \gls{qos}\footnote{\gls{qos} refers to the relative priority of the primary link.\label{fn:qos}}.
 	Such an adaptive channel coding boils down to the degenerate distribution of \gls{ris} when the primary link is prioritized, and outperforms the uniform distribution of \gls{bc} (by accounting the \gls{csi}) when the backscatter link is prioritized.
-	Joint and independent encoding are available when multiple RIScatter nodes are co-located and dispersed, respectively.
 	Table~\ref{tb:scattering_applications} compares RIScatter to \gls{bc} and \gls{ris}.
-	However, two major challenges for RIScatter are the practical receiver and input distribution design.
+	However, two major challenges for RIScatter are the receiver design and input distribution design.
 	This is the first paper to unify \gls{bc} and \gls{ris} from the perspective of input distribution.
 
-	\emph{Second,} we address the first challenge and propose a practical receiver that semi-coherently decodes the backscatter information, recovers the reflection pattern, and coherently decodes the primary link.
-	We consider backscatter energy detection and formulate a \gls{dmmac} over disjoint decision regions.
-	Thanks to the double modulation and symbol-level passive precoding, the semi-coherent backscatter decoding is essentially part of channel training.
-	Once the backscatter information is successfully decoded, its contribution can be modelled within composite channel as dynamic passive beamforming (rather than re-precoded and cancelled).
-	It requires only one energy comparison and re-encoding per backscatter symbol and is much efficient than conventional decoding based on \gls{sic} and \gls{mrc}.
-	It is also suitable for arbitrary input distribution and spreading factor, which significantly improves backscatter throughput.
-	This is the first paper to consider practical backscatter-primary decoding scheme to exploit backscatter modulation as dynamic passive beamforming at the co-located receiver.
-
-	\emph{Third,} we address the second challenge and consider a single-user multi-node \gls{miso} scenario.
+	\emph{Second,} we address the first challenge and propose a low-complexity \gls{sic}-free receiver.
+	It semi-coherently decodes the weak backscatter signal using an energy detector, re-encodes for the exact reflection pattern, then coherently decodes the primary link.
+	Thanks to double modulation, backscatter detection can be viewed as part of channel training, and the impact of backscatter modulation can be modelled as dynamic passive beamforming afterwards.
+	The proposed receiver may be built over legacy receivers with minor hardware upgrade, as it only requires one additional energy comparison and re-encoding per backscatter symbol (instead of primary symbol).
+	The energy detector can also be tailored for arbitrary input distribution and spreading factor to increase backscatter throughput.
+	This is the first paper to propose a \gls{sic}-free cooperative receiver for active-passive coexisting networks.
+
+	\emph{Third,} we address the second challenge in a single-user multi-node \gls{miso} scenario.
 	We characterize the achievable primary-(total-)backscatter rate region by optimizing the input distribution at RIScatter nodes, the active beamforming at the \gls{ap}, and the energy decision regions at the user under different \gls{qos}.
-	A \gls{bcd} algorithm is proposed where the \gls{kkt} input distribution is numerically evaluated by limit of sequences, the active beamforming is optimized by \gls{pgd}, and the decision regions are refined by existing sequential quantizer for \gls{dmtc}.
-	Uniquely, we consider \gls{csi}, \gls{qos}, and backscatter constellation in the optimization and the input distribution result is applicable to general detection schemes.
+	A \gls{bcd} algorithm is proposed where the \gls{kkt} input distribution is numerically evaluated by the converging point of a sequence, the active beamforming is optimized by \gls{pga}, and the decision regions are refined by state-of-the-art sequential quantizer designs for \gls{dmtc}.
+	Uniquely, our optimization problem takes into account the \gls{csi}, \gls{qos}, and backscatter constellation, and the resulting input distribution is applicable to other detection schemes.
 	This is also the first paper to reveal the importance of backscatter input distribution and decision region designs in active-passive coexisting networks.
@@
 \begin{section}{RIScatter}
+	\label{sc:riscatter}
 	\begin{subsection}{Principles}
-		\gls{rf} wave scattering/reflecting are often manipulated by passive antennas or programmable metamaterial \cite{Liang2022}.
-		% can be described by a unified signal model and implemented by passive antennas or programmable metamaterial \cite{Liang2022}.
-		% An antenna-based scatterer usually consists of an integrated antenna, a load-switching modulator, an energy harvester, and on-chip components (e.g., microcontroller and sensors) \cite{Dobkin2012}.
-		% An antenna-based scatterer usually consists of an integrated antenna, a load-switching modulator, an energy harvester, and on-chip components (e.g., microcontroller and sensors) \cite{Dobkin2012}.
-		The former first receives the impinging signals then reradiates some back to the space and dissipates the remaining \cite{Dobkin2012}.
-		% In comparison, a typical metamaterial-based scatterer comprises an outer metamaterial layer of numerous sub-wavelength metallic/dielectric patches (with tunable permittivity/permeability), a middle copper plate layer that avoids leakage, an inner circuit board layer that adjusts patch responses, and an integrated microcontroller/\glsentryshort{fpga} for coordination and control \cite{Wu2020}.
-		% In comparison, a typical metamaterial-based scatterer comprises an outer metamaterial layer of numerous sub-wavelength metallic/dielectric patches (with tunable permittivity/permeability), a middle copper plate layer that avoids leakage, an inner circuit board layer that adjusts patch responses, and an integrated microcontroller/\glsentryshort{fpga} for coordination and control \cite{Wu2020}.
-		In contrast, the latter reflects the wave at the space-metamaterial boundary without receiving them and mainly applies a phase shift.
-		% In practice, both types of scatterers have {finite} reflection states with non-zero reflection loss.
-		% In general, the scattered signal consists of a structural mode component that consistently contributes to environment multipath and can be modelled within \gls{csi}, and an \emph{antenna} mode component that depends on the impedance mismatch and can be used for backscatter modulation and/or passive beamforming \cite{Hansen1989}.
-		The scattered signal consists of a structural mode component that consistently contributes to environment multipath (usually modelled within \gls{csi}) and an antenna mode component that depends on the impedance mismatch (mainly used for backscatter modulation and/or passive beamforming) \cite{Hansen1989}.
-		% The former is usually modelled within \gls{csi} while the latter is mainly used for backscatter modulation and/or passive beamforming.
-		For an antenna (resp. metamaterial) scatterer with $M$ reflection states, the reflection coefficient at state $m \in \mathcal{M} \triangleq \{1,\ldots,M\}$ is
+		\label{sc:principles}
+		\gls{rf} wave scattering or reflecting are often manipulated by passive antennas or programmable metamaterial \cite{Liang2022}.
+		The former receives the impinging signals and reradiates some back to the space, while the latter reflects at the space-cell boundary and mainly applies a phase shift.
+		In the scattered signal, the structural mode component depends on the scatterer geometry and material.
+		Its impact is usually modelled as part of environment multipath \cite{Thomas2012,Liang2020}, or simply a baseband \gls{dc} offset when the impinging signal is a \gls{cw} \cite{Boyer2014}.
+		On the other hand, the antenna mode component depends on the impedance mismatch and is widely exploited in scattering applications.
+		For an antenna (resp. metamaterial) scatterer with $M$ reflection states, the reflection coefficient at state $m \in \mathcal{M} \triangleq \{1,\ldots,M\}$ is \cite{VanHuynh2017,Liang2022}
 		\begin{equation}
@@
 		\end{equation}
-		where $Z_m$ is the antenna load (resp. metamaterial unit) impedance at state $m$ and $Z$ is the antenna input (resp. medium characteristic) impedance.
-
-		\gls{bc} treats scatterers as information sources that \emph{randomly} choosing the reflection state based on information symbol.
-		For $M$-ary \gls{qam}, constellation point $c_m$ maps to reflection coefficient $\Gamma_m$ by \cite{Thomas2012a}
-		\begin{equation}
-			\Gamma_m = \alpha \frac{c_m}{\max_{m'} \lvert c_{m'} \rvert},
+		where $Z_m$ is the antenna load (resp. metamaterial cell) impedance at state $m$, and $Z$ is the antenna input (resp. medium characteristic) impedance.
+		Specifically,
+		\begin{itemize}
+			\item \gls{bc}: The scatterer is an information source with random reflection pattern over time.
+			The reflection coefficient is used merely as an information codeword \cite{Thomas2012a}
+			\begin{equation}
+				\Gamma_m = \alpha_m \frac{c_m}{\max_{m'} \lvert c_{m'} \rvert},
 				\label{eq:backscatter_modulation}
 			\end{equation}
-		where $\alpha \in \mathbb{I}$ is the common amplitude scattering ratio at the direction of interest.
-		In contrast, \gls{ris} treats scatterers as channel adaptors that \emph{deterministically} choosing the reflection state based on \gls{csi}.
-		For a \gls{ris} element with $M$ available states, phase shift $\theta_m$ maps to reflection coefficient $\Gamma_m$ by \cite{Wu2018}
-		\begin{equation}
-			\Gamma_m = \beta_m \exp(j \theta_m),
+			where $\alpha_m \in \mathbb{I}$ is the amplitude scattering ratio at state $m$, and $c_m$ is the corresponding constellation point.
+			\item \gls{ris}: The scatterer is a channel shaper with deterministic reflection pattern over time.
+			The reflection coefficient is used merely as a passive beamforming codeword \cite{Wu2018}
+			\begin{equation}
+				\Gamma_m = \alpha_m \exp(j \theta_m),
 				\label{eq:passive_beamforming}
 			\end{equation}
-		where $\beta_m \in \mathbb{I}$ is the overall amplitude scattering ratio at state $m$.\footnote{Most existing \gls{ris} literature assumes lossless reflection $\beta_m=1$, $\forall m$.}
-		% A natural question is, is it possible to use a scatterer
-		For a scatter node with given load impedance set, \gls{bc} employs $\Gamma_m$ only as an information codeword while \gls{ris} employs $\Gamma_m$ only as a passive beamforming codeword.
-		RIScatter generalizes both from a probabilistic perspective where each node \emph{semi-randomly} chooses the reflection state with the guidance of probability $P(\Gamma_m)$.
-		The input distribution is flexibly designed as a joint function of the information source, \gls{csi}, and \gls{qos} of both links.
-		\gls{bc} and (static) \gls{ris} can be regarded as its extreme cases where the input distribution boils down to uniform and degenerate, respectively.
-		Fig.~\ref{fg:scatter_comparison} compares the input distribution and reflection pattern of RIScatter to \gls{bc} and \gls{ris}.
+			where $\theta_m$ is the phase shift at state $m$.\footnote{Most papers assume $\alpha_m = \alpha$, with $\alpha \ll 1$ for \gls{bc} and $\alpha=1$ for \gls{ris}.\label{fn:scattering_ratio}}
+		\end{itemize}
+
+		RIScatter generalizes \gls{bc} and \gls{ris} from a probabilistic perspective.
+		Each reflection coefficient simultaneously acts as an information codeword and a passive beamforming codeword.
+		As shown in Fig.~\ref{fg:scatter_comparison}, the reflection pattern of each RIScatter node over time is semi-random and guided by the input probability assigned to each state.
+		This probability distribution is carefully designed to incorporate the backscatter information, \gls{csi}, and \gls{qos}, in order to strike a balance between backscatter modulation and passive beamforming.
 		\begin{figure}[!t]
@@
 		\end{equation}
-		where $t_l$ is the energy decision threshold between hypotheses $\mathcal{H}_{l}$ and $\mathcal{H}_{l+1}$.
-		For a given decision threshold vector $\boldsymbol{t} \triangleq [t_0,\ldots,t_L]^\mathsf{T} \in \mathbb{R}_+^{(L+1)}$, we can formulate a \gls{dmmac} with transition probability from input $x_{m_{\mathcal{K}}}$ to output $\hat{x}_{m_{\mathcal{K}}'}$ as
-		\begin{equation}
-			P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}}) = \int_{\mathcal{R}_{m_{\mathcal{K}}'}} f(z|\mathcal{H}_{m_{\mathcal{K}}}) \, d z,
-			\label{eq:dmmac}
-		\end{equation}
-		over which input distribution of all RIScatter nodes can be designed.
-		An example of energy detection is illustrated in Fig.~\ref{fg:energy_distribution}.
-		% Conditioned on different reflection state hypotheses, the accumulated energy per backscatter block follows Gamma distribution with different scale parameters.
+		where $t_l$ is the decision threshold between hypotheses $x_{l}$ and $x_{l+1}$.
+		An example is shown in Fig.~\ref{fg:energy_distribution}.
+
 		\begin{figure}[!t]
@@
 			\caption{
-				\gls{pdf} of accumulated energy per backscatter block conditioned on different reflection state hypotheses.
+				\gls{pdf} of the receive energy per backscatter block conditioned on different reflection state.
 			}
@@
 		\end{figure}
-		\begin{remark}
-			The capacity-achieving decision region design for \gls{dmtc} with non-binary inputs in arbitrary distribution remains an open issue.
-			It was proved deterministic detectors can be rate-optimal, but non-convex decision regions (comprise non-adjacent partitions) are generally required and the optimal number of thresholds remains unknown \cite{Nguyen2018,Nguyen2021}.
-			Hence, we limit the energy detector to convex deterministic decision regions and consider sequential threshold design.
-		\end{remark}
-		After successful backscatter decoding, the user can re-encode for exact reflection pattern and obtain the composite channel by \eqref{eq:equivalent_channel}, then coherently decode the primary link.
-		Such an \gls{sic}-free sequential decoding enables backscatter modulation and dynamic passive beamforming by only one energy comparison and re-encoding per backscatter symbol.
-		It also supports arbitrary input distribution and spreading factor for higher backscatter throughput.
-		\label{st:system_model}
+
+		When the threshold vector $\boldsymbol{t} \triangleq [t_0,\ldots,t_L]^\mathsf{T} \in \mathbb{R}_+^{L+1}$ is given, we can formulate a \gls{dmmac} with transition probability from input $x_{m_{\mathcal{K}}}$ to output $\hat{x}_{m_{\mathcal{K}}'}$ as
+		\begin{equation}
+			q(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}}) = \int_{\mathcal{R}_{m_{\mathcal{K}}'}} f(z|x_{m_{\mathcal{K}}}) \, d z.
+			\label{eq:dmmac}
+		\end{equation}
+		The backscatter mutual information is
+		\begin{equation}
+			I_{\text{B}}(x_{\mathcal{K}};\hat{x}_{\mathcal{K}}) = \sum_{m_{\mathcal{K}}} p(x_{m_{\mathcal{K}}}) I_{\text{B}}(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}}),
+			\label{eq:backscatter_mutual_information}
+		\end{equation}
+		where $I_{\text{B}}(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}})$ is the backscatter information function
+		\begin{equation}
+			I_{\text{B}}(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}}) \triangleq \sum_{m_{\mathcal{K}}'} q(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}}) \log \frac{q(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}})}{p(\hat{x}_{m_{\mathcal{K}}'})}.
+			\label{eq:backscatter_information_function}
+		\end{equation}
+
+		Once the backscatter information is successfully decoded, the user re-encodes to recover the reflection pattern, constructs the composite channel by \eqref{eq:equivalent_channel}, then coherently decodes the primary link.
+		The primary mutual information is
+		\begin{equation}
+			I_{\text{P}}(s;y|x_{\mathcal{K}}) = \sum_{m_{\mathcal{K}}} p(x_{m_{\mathcal{K}}}) I_{\text{P}}(s;y|x_{m_{\mathcal{K}}}),
+			\label{eq:primary_mutual_information}
+		\end{equation}
+		where $I_{\text{P}}(s;y|x_{m_{\mathcal{K}}})$ is the primary information function
+		\begin{equation}
+			I_{\text{P}}(s;y|x_{m_{\mathcal{K}}}) \triangleq \log \Bigl(1 + \frac{\lvert \boldsymbol{h}^\mathsf{H}(x_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_v^2}\Bigr).
+			\label{eq:primary_information_function}
+		\end{equation}
 	\end{subsection}
-
-	\begin{subsection}{Achievable Rates}
-		Denote the probability of node $k$ choosing reflection state $m_k$ as $P_k(x_{m_k})$ and let $\boldsymbol{p}_k \triangleq [P_k(c_1),\ldots,P_k(c_M)]^\mathsf{T} \in \mathbb{I}^{M}$.
-		For dispersed nodes with independent encoding, the probability of backscatter symbol tuple $x_{m_{\mathcal{K}}}$ is
-		\begin{equation}
-			P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) = \prod_{k \in \mathcal{K}} P_k(x_{m_k}).
-			\label{eq:equivalent_distribution}
-		\end{equation}
-		Following \cite{Rezaeian2004}, we define the backscatter information function between input value tuple $x_{m_{\mathcal{K}}}$ and output variable tuple $\hat{x}_{\mathcal{K}}$ as
-		\begin{equation}
-			I_{\text{B}}(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}}) \triangleq \sum_{m_{\mathcal{K}}'} P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}}) \log \frac{P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}})}{P_{\mathcal{K}}(\hat{x}_{m_{\mathcal{K}}'})},
-			\label{eq:backscatter_information_function}
-		\end{equation}
-		where $P_{\mathcal{K}}(\hat{x}_{m_{\mathcal{K}}'}) = \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}})$.
-		We also define the backscatter marginal information of $x_{m_k}$ as
-		\begin{equation}
-			I_{\text{B},k}(x_{m_k};\hat{x}_{\mathcal{K}}) \triangleq \sum_{m_{\mathcal{K} \setminus \{k\}}} P_{\mathcal{K} \setminus \{k\}}(x_{m_{\mathcal{K} \setminus \{k\}}}) I_{\text{B}}(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}}),
-			\label{eq:backscatter_marginal_information}
-		\end{equation}
-		where $P_{\mathcal{K} \setminus \{k\}}(x_{m_{\mathcal{K} \setminus \{k\}}}) = \prod_{q \in \mathcal{K} \setminus \{k\}} P_{q}(x_{m_{q}})$.
-		Hence, the backscatter mutual information can be written as
-		\begin{equation}
-			I_{\text{B}}(x_{\mathcal{K}};\hat{x}_{\mathcal{K}}) = \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) I_{\text{B}}(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}}).
-			\label{eq:backscatter_mutual_information}
-		\end{equation}
-
-		Once nodes are successfully decoded, we can re-encode and determine the composite channel by \eqref{eq:equivalent_channel}.
-		The primary information function conditioned on $x_{m_{\mathcal{K}}}$ is
-		\begin{equation}
-			I_{\text{P}}(s;y|x_{m_{\mathcal{K}}}) \triangleq \log \Bigl(1 + \frac{\lvert \boldsymbol{h}^\mathsf{H}(x_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_v^2}\Bigr),
-			\label{eq:primary_information_function}
-		\end{equation}
-		the primary marginal information of $x_{m_k}$ is
-		% the primary marginal information conditioned on letter $x_{m_k}$ of node $k$ as
-		\begin{equation}
-			I_{\text{P},k}(s;y|x_{m_k}) \triangleq \sum_{m_{\mathcal{K} \setminus \{k\}}} P_{\mathcal{K} \setminus \{k\}}(x_{m_{\mathcal{K} \setminus \{k\}}}) I_{\text{P}}(s;y|x_{m_{\mathcal{K}}}),
-			\label{eq:primary_marginal_information}
-		\end{equation}
-		and the average primary mutual information is
-		\begin{equation}
-			I_{\text{P}}(s;y|x_{\mathcal{K}}) = \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) I_{\text{P}}(s;y|x_{m_{\mathcal{K}}}).
-			\label{eq:primary_mutual_information}
-		\end{equation}
-
-		With a slight abuse of notation, we define the weighted sum information function, marginal information, and mutual information as
+\end{section}
+
+\begin{section}{Rate-Region Characterization}
+	With a slight abuse of notation, we define the weighed sum mutual information and information function as
 	\begin{align}
-			I(x_{m_{\mathcal{K}}})
-			 & \triangleq \rho I_{\text{P}}(s;y|x_{m_{\mathcal{K}}}) + (1 - \rho) I_{\text{B}}(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}}),\label{eq:weighted_sum_information_function} \\
-			I_k(x_{m_k})
-			 & \triangleq \rho I_{\text{P},k}(s;y|x_{m_k}) + (1 - \rho) I_{\text{B},k}(x_{m_k};\hat{x}_{\mathcal{K}}),\label{eq:weighted_sum_marginal_information}                     \\
 		I(x_{\mathcal{K}})
-			 & \triangleq \rho I_{\text{P}}(s;y|x_{\mathcal{K}}) + (1 - \rho) I_{\text{B}}(x_{\mathcal{K}};\hat{x}_{\mathcal{K}}),\label{eq:weighted_sum_mutual_information}
+		 & \triangleq \rho I_{\text{P}}(s;y|x_{\mathcal{K}}) + (1 - \rho) I_{\text{B}}(x_{\mathcal{K}};\hat{x}_{\mathcal{K}}),\label{eq:weighted_sum_mutual_information}           \\
+		I(x_{m_\mathcal{K}})
+		 & \triangleq \rho I_{\text{P}}(s;y|x_{m_{\mathcal{K}}}) + (1 - \rho) I_{\text{B}}(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}}),\label{eq:weighted_sum_information_function}
 	\end{align}
-		where $\rho \in \mathbb{I}$ is the relative \gls{qos} of the primary link.
-		We notice the average primary rate \eqref{eq:primary_mutual_information} depends on the backscatter input distribution and active beamforming, while the total backscatter rate depends on the input distribution and \gls{dmmac} \eqref{eq:dmmac} that relates to the active beamforming and decision thresholds.
-		\label{st:information_theory}
-	\end{subsection}
-	\label{st:riscatter}
-\end{section}
-
-\begin{section}{Rate-Region Characterization}
-	To characterize the achievable primary-(total-)backscatter rate region for the RIScatter system, we aim to maximize the weighted sum rate with respect to input distribution $\{\boldsymbol{p}_k\}_{k \in \mathcal{K}}$, active beamforming $\boldsymbol{w}$, and decision thresholds $\boldsymbol{t}$ by
+	where $\rho \in \mathbb{I}$ is the \gls{qos}.
+	To obtain the achievable primary-(total-)backscatter rate region, we consider the weighted sum mutual information maximization problem with independent encoding at all nodes\footnote{Joint encoding over multiple nodes can be viewed as its special case with an augmented backscatter source.\label{fn:joint_encoding}}
 	\begin{maxi!}
@@
 		\addConstraint{t_{l-1}}{\le t_l,}{\quad \forall l}{\label{co:sequential_threshold}}
-		\addConstraint{\boldsymbol{t}}{\ge \boldsymbol{0}.}{\label{co:nonnegative_threshold}}
+		\addConstraint{\boldsymbol{t}}{\ge \boldsymbol{0},}{\label{co:nonnegative_threshold}}
 	\end{maxi!}
-
-	Problem \eqref{op:weighted_sum_rate} generalizes conventional \gls{bc} by allowing \gls{csi}- and \gls{qos}-adaptive input distribution and decision region design.
-	It also generalizes the discrete \gls{ris} phase shift selection problem by stochastic reflection that relaxes the feasible domain from the vertices of $M$-dimensional probability simplex to the simplex itself.
-	Problem \eqref{op:weighted_sum_rate} is highly non-convex and we propose a \gls{bcd} algorithm that iteratively updates $\{\boldsymbol{p}_k\}_{k \in \mathcal{K}}$, $\boldsymbol{w}$ and $\boldsymbol{t}$.
+	where $\boldsymbol{p}_k = [p(x_{1_k}), \ldots, p(x_{M_k})]^\mathsf{T} \in \mathbb{I}^M$ is the input distribution of node $k$.
+	Problem \eqref{op:weighted_sum_rate} generalizes \gls{bc} by allowing \gls{csi}- and \gls{qos}-adaptive input distribution and decision region design.
+	On the other hand, it also relaxes the feasible domain of discrete \gls{ris} phase shift selection problems from the vertices of $M$-dimensional probability simplex to the simplex itself.
+	The original problem is highly non-convex and we propose a \gls{bcd} algorithm that iteratively updates $\{\boldsymbol{p}_k\}_{k \in \mathcal{K}}$, $\boldsymbol{w}$ and $\boldsymbol{t}$.
 
 	\begin{subsection}{Input Distribution}
-		For any given $\boldsymbol{w}$ and $\boldsymbol{t}$, we can construct the equivalent \gls{dmmac} by \eqref{eq:dmmac} and simplify \eqref{op:weighted_sum_rate} to
+		\label{sc:input_distribution}
+		For any given $\boldsymbol{w}$ and $\boldsymbol{t}$, we can formulate a \gls{dmmac} by \eqref{eq:dmmac} and simplify \eqref{op:weighted_sum_rate} to
 		\begin{maxi!}
@@
 		\end{maxi!}
-		which is convex when $K=1$ or joint encoding\footnote{Joint encoding formulates an equivalent source of $M^K$ codewords, such that one can directly design $P_{\mathcal{K}}(x_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}$ instead of $P_k(x_{m_k})$, $\forall k,m_k$.} over $K>1$ co-located nodes.
-		When the nodes are dispersed, problem \eqref{op:input_distribution} involves product term $\prod_{k \in \mathcal{K}} P_k(x_{m_k})$ and is non-convex.
-		Following \cite{Rezaeian2004}, we first recast the \gls{kkt} conditions to their equivalent forms then propose a numerical method that guarantees those conditions on convergence of sequences.
-		% ? Next, we propose a numerical method that evaluate the \gls{kkt} input distribution by limit of sequences.
-		\begin{remark}
-			As demonstrated in \cite{Buhler2011}, \gls{kkt} conditions are generally necessary but insufficient for total rate maximization of \gls{dmmac}.
-			We will later show by simulation that, for a moderate $K$, the average achievable rate regions of \gls{kkt} and global-optimal input distributions completely coincide with each other.
-			\label{re:input_kkt_distribution}
-		\end{remark}
+		which involves the product term \eqref{eq:equivalent_distribution} and is generally non-convex (unless $K=1$).
+		Following \cite{Rezaeian2004}, we first recast the \gls{kkt} conditions to their equivalent forms, then propose a numerical solution that guarantees those conditions on the converging point a sequence.
 		\begin{proposition}
@@
 		\begin{algorithm}[!t]
-			\caption{Numerical \gls{kkt} Input Distribution Evaluation by Limits of Sequence}
+			\small
+			\caption{Input Distribution Evaluation by a Sequence}
 			\label{al:input_distribution}
@@
 		which is still non-convex due to the integration and entropy terms.
-		To tackle this, we rewrite the \gls{dmmac} transition probability \eqref{eq:dmmac} as a regularized incomplete Gamma function in the series representation \cite[Theorem 3]{Jameson2016}
-		\begin{equation}
-			% \begin{gathered}
-			% 	Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr) = \frac{\int_{{t_{l-1}}/{\sigma_{m_{\mathcal{K}}}^2}}^{{t_l}/{\sigma_{m_{\mathcal{K}}}^2}} z^{N-1} \exp(-z) \, d z}{(N-1)!}\\
-			% 	= \exp \Bigl(-\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2}\Bigr) \sum_{n=0}^{N-1} \frac{\bigl(\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2}\bigr)^n}{n!} - \exp \Bigl(-\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr) \sum_{n=0}^{N-1} \frac{\bigl(\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\bigr)^n}{n!}.
-			% \end{gathered}
-			Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr) = \frac{\int_{{t_{l-1}}/{\sigma_{m_{\mathcal{K}}}^2}}^{{t_l}/{\sigma_{m_{\mathcal{K}}}^2}} z^{N-1} \exp(-z) \, d z}{(N-1)!} = \exp \Bigl(-\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2}\Bigr) \sum_{n=0}^{N-1} \frac{\bigl(\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2}\bigr)^n}{n!} - \exp \Bigl(-\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr) \sum_{n=0}^{N-1} \frac{\bigl(\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\bigr)^n}{n!}.
+		Note the \gls{dmmac} $q(x_l|x_{m_{\mathcal{K}}})$ depends on the variance of accumulated receive energy $\sigma_{m_{\mathcal{K}}}^2$, which is a function of $\boldsymbol{w}$.
+		Plugging \eqref{eq:energy_distribution} into \eqref{eq:dmmac}, we have
+		\begin{equation}
+			q(x_l|x_{m_{\mathcal{K}}}) = \frac{\int_{{t_{l-1}}/{\sigma_{m_{\mathcal{K}}}^2}}^{{t_l}/{\sigma_{m_{\mathcal{K}}}^2}} z^{N-1} \exp(-z) \, d z}{(N-1)!} = Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr),
+			\label{eq:dmmac_gamma}
+		\end{equation}
+		where $Q(N, b_1, b_2) \triangleq \int_{b_1}^{b_2} z^{N-1} \exp(-z) / (N - 1)! \, d z$ is the regularized incomplete Gamma function.
+		Its series expansion is given by \cite[Theorem 3]{Jameson2016}
+		\begin{equation}
+			Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr) = \exp \Bigl(-\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2}\Bigr) \sum_{n=0}^{N-1} \frac{\bigl(\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2}\bigr)^n}{n!} - \exp \Bigl(-\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr) \sum_{n=0}^{N-1} \frac{\bigl(\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\bigr)^n}{n!},
 			\label{eq:regularized_incomplete_gamma}
 		\end{equation}
-		Its gradient with respect to $\boldsymbol{w}^*$ can be derived as
-		\begin{equation}
-			\nabla_{\boldsymbol{w}^*} Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr) = \frac{\boldsymbol{h}(x_{m_{\mathcal{K}}})\boldsymbol{h}^\mathsf{H}(x_{m_{\mathcal{K}}})\boldsymbol{w}}{(\sigma_{m_{\mathcal{K}}}^2)^2} g_{m_{\mathcal{K}}}(t_{l-1},t_l),
+		whose gradient with respect to $\boldsymbol{w}^*$ is
+		\begin{equation}
+			\nabla_{\boldsymbol{w}^*} Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr) = \frac{\boldsymbol{h}(x_{m_{\mathcal{K}}})\boldsymbol{h}^\mathsf{H}(x_{m_{\mathcal{K}}})\boldsymbol{w}}{(\sigma_{m_{\mathcal{K}}}^2)^2} \Bigl(g_{m_{\mathcal{K}}}(t_l) - g_{m_{\mathcal{K}}}(t_{l-1})\Bigr),
 			\label{eq:regularized_incomplete_gamma_gradient}
 		\end{equation}
-		where $g_{m_{\mathcal{K}}}(t_{l-1},t_l) \triangleq g_{m_{\mathcal{K}}}(t_l)-g_{m_{\mathcal{K}}}(t_{l-1})$ and
+		where
 		\begin{equation}
@@
 		\end{equation}
-		On top of \eqref{eq:regularized_incomplete_gamma} and \eqref{eq:regularized_incomplete_gamma_gradient}, we explicitly express the objective function \eqref{ob:active_beamforming} and its gradient as
-		\begin{align}
-			I(x_{\mathcal{K}})
-			 & =\sum_{m_{\mathcal{K}}}P_{\mathcal{K}}(x_{m_{\mathcal{K}}})\Biggl(\rho\log\Bigl(1+\frac{\lvert\boldsymbol{h}^\mathsf{H}(x_{m_{\mathcal{K}}})\boldsymbol{w}\rvert^2}{\sigma_v^2}\Bigr) \nonumber                                                                                                                                                                                                                 \\
-			 & \qquad + (1-\rho)\sum_l Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr) \log \frac{Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr)}{\sum_{m_{\mathcal{K}}'} P_{\mathcal{K}}(x_{m_{\mathcal{K}}'}) Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}'}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}'}^2}\Bigr)}\Biggr),
+		On top of \eqref{eq:regularized_incomplete_gamma} and \eqref{eq:regularized_incomplete_gamma_gradient}, we rewrite $I(x_{\mathcal{K}})$ and $\nabla_{\boldsymbol{w}^*} I(x_{\mathcal{K}})$ as \eqref{eq:weighted_sum_mutual_information_explicit} and \eqref{eq:weighted_sum_mutual_information_gradient} at the end of page \pageref{eq:weighted_sum_mutual_information_explicit}, respectively.
+		\begin{figure*}[!b]
+			\hrule
+			\small
+			\begin{equation}
+				I(x_{\mathcal{K}})=\sum_{m_{\mathcal{K}}}p(x_{m_{\mathcal{K}}})\Biggl(\rho\log\Bigl(1+\frac{\lvert\boldsymbol{h}^\mathsf{H}(x_{m_{\mathcal{K}}})\boldsymbol{w}\rvert^2}{\sigma_v^2}\Bigr)+(1-\rho)\sum_l Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr) \log \frac{Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr)}{\sum_{m_{\mathcal{K}}'} p(x_{m_{\mathcal{K}}'}) Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}'}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}'}^2}\Bigr)}\Biggr)
 				\label{eq:weighted_sum_mutual_information_explicit}
-		\end{align}
+			\end{equation}
 			\begin{align}
 				\nabla_{\boldsymbol{w}^*} I(x_{\mathcal{K}})
-			 & = \sum_{m_{\mathcal{K}}}P_{\mathcal{K}}(x_{m_{\mathcal{K}}})\Biggl(\rho\frac{\boldsymbol{h}(x_{m_{\mathcal{K}}})\boldsymbol{h}^\mathsf{H}(x_{m_{\mathcal{K}}})\boldsymbol{w}}{\sigma_{m_{\mathcal{K}}}^2}+(1-\rho)\sum_l\biggl(\log\frac{Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr)}{\sum_{m_{\mathcal{K}}'}P_{\mathcal{K}}(x_{m_{\mathcal{K}}'})Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}'}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}'}^2}\Bigr)}+1\biggr)\nonumber                                                                                    \\
-			 & \qquad \times \nabla_{\boldsymbol{w}^*} Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr)-\frac{Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr)\sum_{m_{\mathcal{K}}'}P_{\mathcal{K}}(x_{m_{\mathcal{K}}'})\nabla_{\boldsymbol{w}^*}Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}'}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}'}^2}\Bigr)}{\sum_{m_{\mathcal{K}}'}P_{\mathcal{K}}(x_{m_{\mathcal{K}}'})Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}'}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}'}^2}\Bigr)}\Biggr).
+				 & = \sum_{m_{\mathcal{K}}}p(x_{m_{\mathcal{K}}})\Biggl(\rho\frac{\boldsymbol{h}(x_{m_{\mathcal{K}}})\boldsymbol{h}^\mathsf{H}(x_{m_{\mathcal{K}}})\boldsymbol{w}}{\sigma_{m_{\mathcal{K}}}^2}+(1-\rho)\sum_l\biggl(\log\frac{Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr)}{\sum_{m_{\mathcal{K}}'}p(x_{m_{\mathcal{K}}'})Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}'}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}'}^2}\Bigr)}+1\biggr)\nonumber                                                                                   \\
+				 & \qquad \times \nabla_{\boldsymbol{w}^*} Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr)-\frac{Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr)\sum_{m_{\mathcal{K}}'}p(x_{m_{\mathcal{K}}'})\nabla_{\boldsymbol{w}^*}Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}'}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}'}^2}\Bigr)}{\sum_{m_{\mathcal{K}}'}p(x_{m_{\mathcal{K}}'})Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}'}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}'}^2}\Bigr)}\Biggr)
 				\label{eq:weighted_sum_mutual_information_gradient}
 			\end{align}
-		They allows problem \eqref{op:active_beamforming} to be solved by the \gls{pgd} method, where any unregulated beamformer $\bar{\boldsymbol{w}}$ can be projected onto the feasible domain of average transmit power constraint \eqref{co:transmit_power} by
-		\begin{equation}
-			\boldsymbol{w} = \sqrt{P} \frac{\bar{\boldsymbol{w}}}{\max\bigl(\sqrt{P},\lVert\bar{\boldsymbol{w}}\rVert\bigr)}.
+		\end{figure*}
+		Problem \eqref{op:active_beamforming} can thus be solved by the \gls{pga} method.
+		At iteration $r+1$, the unregulated active beamformer is updated by
+		\begin{equation}
+			\bar{\boldsymbol{w}}^{(r+1)} = \boldsymbol{w}^{(r)}+\gamma\nabla_{\boldsymbol{w}^*} I^{(r)}(x_{\mathcal{K}}),
+			\label{eq:beamforming_gradient_ascent}
+		\end{equation}
+		where $\gamma$ is the step size (refinable by backtracking line search \cite[Section 9.2]{Boyd2004}).
+		Then, $\bar{\boldsymbol{w}}$ is projected onto the feasible domain \eqref{co:transmit_power} to retrieve the active beamformer
+		\begin{equation}
+			\boldsymbol{w} = \frac{\sqrt{P} \bar{\boldsymbol{w}}}{\max\bigl(\sqrt{P},\lVert\bar{\boldsymbol{w}}\rVert\bigr)}.
 			\label{eq:beamforming_projection}
 		\end{equation}
-		The \gls{pgd} active beamforming optimization with step size $\gamma$ refined by \gls{bls} \cite[Section 9.2]{Boyd2004} is summarized in Algorithm \ref{al:active_beamforming}.
+
+		The \gls{pga} active beamforming design is summarized in Algorithm \ref{al:active_beamforming}.
 		\setalgorithmcaptionfont{\small}
 		\begin{algorithm}[!t]
-			\caption{Iterative Active Beamforming Optimization by \gls{pgd} with \gls{bls}}
+			\small
+			\caption{Active Beamforming Optimization by \gls{pga}}
 			\label{al:active_beamforming}
@@
 		\end{maxi!}
-		which is still non-convex because variable $\boldsymbol{t}$ appears on the limits of integration \eqref{eq:dmmac}.
-		Fortunately, we can further simplify problem \eqref{op:decision_threshold} as a point-to-point rate-optimal quantizer design for a \gls{dcmc}, thanks to Remark \ref{re:backscatter_decision} and \ref{re:augmented_source}.
-
-		\begin{remark}
-			Energy detector design has no impact on the primary achievable rate since the composite channel \eqref{eq:equivalent_channel} can always be reconstructed after backscatter decoding and re-encoding.
-			It suggests any thresholding scheme maximizing the total backscatter rate \eqref{eq:backscatter_mutual_information} is also optimal for problem \eqref{op:decision_threshold}.
-			\label{re:backscatter_decision}
-		\end{remark}
-
-		\begin{remark}
-			In terms of total backscatter rate, the potentially dispersed nodes with known input distribution can be viewed as an equivalent source with tuple codewords.
-			As such, the \gls{dmmac} \eqref{eq:dmmac} becomes a \gls{dmtc} and problem \eqref{op:decision_threshold} reduces to the rate-optimal quantization design for a \gls{dcmc}.
-			\label{re:augmented_source}
-		\end{remark}
-
-		Next, we constrain the feasible domain of problem \eqref{op:decision_threshold} from continuous space $\mathbb{R}_+^{L+1}$ to finite candidate set (i.e., fine-grained discrete energy levels) $\mathcal{T}^{L+1}$.
+		which is still non-convex since $\boldsymbol{t}$ appears on the limits of integration \eqref{eq:dmmac}.
+		Instead of solving it directly, we constrain the feasible domain from continuous space $\mathbb{R}_+^{L+1}$ to discrete candidates (i.e., fine-grained energy levels) $\mathcal{T}^{L+1}$.
+		As shown in Fig.~\ref{fg:discrete_outputs}, the decision regions are formulated by grouping adjacent energy bins.
 		\begin{figure}[!t]
@@
 \begin{section}{Simulation Results}
-	In this section, we provide numerical results to evaluate the proposed input distribution, active beamforming, and backscatter decision designs for the considered RIScatter system.
-	We assume the AP-user distance is \SI{10}{\meter} and at least one RIScatter nodes are randomly dropped in a disk centered at the user with radius $r$.
-	% The \gls{ap} is with an average transmit power budget $P=\SI{36}{\dBm}$, all nodes employs $M$-\gls{qam} with amplitude scattering ratio $\alpha=0.5$, and the user is with average noise power $\sigma_v^2=\SI{-40}{\dBm}$.
-	The \gls{ap} is with an average transmit power budget $P=\SI{36}{\dBm}$ and all nodes employs $M$-\gls{qam} with $\alpha=0.5$.
+	\label{sc:simulation_results}
+	In this section, we provide numerical results to evaluate the proposed algorithms.
+	We assume the AP-user distance is \qty{10}{m} and at least one RIScatter nodes are randomly dropped in a disk centered at the user with radius $r$.
+	The \gls{ap} is with maximum average transmit power $P=\qty{36}{dBm}$ and all nodes employs $M$-\gls{qam} with $\alpha=0.5$.
 	For all channels involved, we consider a distance-dependent path loss model
@@
 	\end{equation}
-	where $d$ is the transmission distance, $L_0=-\SI{30}{\dB}$ is the reference path loss at $d_0=\SI{1}{\meter}$, $\kappa$ is the Rician K-factor, $\bar{\boldsymbol{H}}$ is the deterministic line-of-sight component with unit-magnitude entries, and $\tilde{\boldsymbol{H}}$ is the Rayleigh fading component with standard \gls{iid} \gls{cscg} entries.
+	where $d$ is the transmission distance, $L_0=-\qty{30}{dB}$ is the reference path loss at $d_0=\qty{1}{m}$, $\kappa$ is the Rician K-factor, $\bar{\boldsymbol{H}}$ is the deterministic line-of-sight component with unit-magnitude entries, and $\tilde{\boldsymbol{H}}$ is the Rayleigh fading component with standard \gls{iid} \gls{cscg} entries.
 	We choose $\gamma_{\text{D}}=2.6$, $\gamma_{\text{F}}=2.4$, $\gamma_{\text{B}}=2$, and $\kappa_{\text{D}}=\kappa_{\text{F}}=\kappa_{\text{B}}=5$ for direct, forward and backward links.
-	The finite decision threshold domain $\mathcal{T}$ is obtained by $b$-bit uniform discretization over the critical interval defined by the confidence bounds of edge hypotheses (i.e., lower bound of $\mathcal{H}_1$ and upper bound of $\mathcal{H}_L$) with confidence $1-\varepsilon$.
+	The finite decision threshold domain $\mathcal{T}$ is obtained by $b$-bit uniform discretization over the critical interval defined by the $1-\varepsilon$ confidence bounds of edge hypotheses (i.e., lower bound of $x_1$ and upper bound of $x_L$).
 	We set $b=9$ and $\varepsilon=\num{e-3}$.
-	All achievable rate points/regions are averaged over \num{e3} channel realizations.
+	All achievable rate regions are averaged over \num{e3} channel realizations.
 
@@
 				}
-				\caption{Typical convergence curves at $\rho=0$ for $Q=4$, $K=8$, $M=2$, $N=20$, $\sigma_v^2=\SI{-40}{\dBm}$ and $r=\SI{2}{\meter}$.}
+				\caption{Typical convergence curves at $\rho=0$ for $Q=4$, $K=8$, $M=2$, $N=20$, $\sigma_v^2=\qty{-40}{dBm}$ and $r=\qty{2}{m}$.}
 				\label{fg:wsr_convergence}
 			\end{figure}
-
-			In Fig.~\ref{fg:wsr_convergence}, we plot the weighted sum of primary and total backscatter rates at $\rho=0$ for \gls{kkt}, \gls{pgd} and \gls{bcd} algorithms on the first call.
-			For $K=8$ and $M=2$, Algorithm \ref{al:input_distribution} typically takes around \num{100} fast iterations to converge to the \gls{kkt} input distribution.
-			For $Q=4$, around \num{10} iterations are required for Algorithm \ref{al:active_beamforming} to converge.
-			Overall, the initial \gls{bcd} algorithm requires at most \num{5} iterations to converge.
-			At the following points (not presented here), the convergence of all three algorithms are much faster thanks to the progressive initialization.
-			We conclude the proposed algorithms have good convergence performances.
+			The \gls{bcd} algorithm is convergent for problem \eqref{op:weighted_sum_rate} since the input distribution and active beamforming subproblems converge and the thresholding subproblem attains global optimality.
+			In company with \gls{bcd}, we also plotted the convergence results of \gls{kkt} and \gls{pga} algorithms in Fig.~\ref{fg:wsr_convergence} to show how much performance is gained by solving each subproblem.
+			It is observed that Algorithm \ref{al:input_distribution} and \ref{al:active_beamforming} take around \num{100} and \num{10} iterations to converge, respectively.
+			Overall, the \gls{bcd} algorithm requires at most \num{5} iterations to converge.
+			As $\rho$ increases (not presented here), the convergence of all three algorithms are much faster thanks to the progressive initialization.
 		\end{subsubsection}
@@
 
-		Fig.~\ref{fg:region_comparison} compares the typical achievable rate region/points of RIScatter and the strategies above.
-		% \emph{First,} we observe both \gls{bbc} and \gls{sr} achieves when the spreading factor $N$ is sufficiently large.
-		\emph{First,} we observe \gls{bbc} and \gls{sr} achieve the best backscatter performance thanks to coherent decoding.
-		% However, \gls{sr} requires $N$ \gls{sic} followed by a \gls
-		% However, \gls{sr} requires $N$ re-encoding, precoding, subtraction together with a time-domain \gls{mrc} to decode each backscatter symbol and the cost can be prohibitive.
+		Fig.~\ref{fg:region_comparison} compares the typical achievable rate region/points of RIScatter and those strategies.
+		\emph{First,} we observe \gls{bbc} and \gls{sr} achieve the best backscatter performance thanks to the coherent decoding.
 		For \gls{sr}, this comes with the cost of $N$ re-encoding, precoding, subtraction together with a time-domain \gls{mrc} per backscatter symbol.
-		% However, the primary rate benefit
-		% For \gls{bbc} with coherent energy detection, the conditional \gls{pdf} of accumulated energy \eqref{eq:energy_distribution_bbc} is more skewed at a large $N$, such that the equivalent \gls{dmmac} \eqref{eq:dmmac} has lower error probabilities.
-		% For \gls{sic}-based \gls{sr}, the effective backscatter \gls{snr} is increased by $N$ times and the penalty term $\iota$ becomes insignificant.
-		% However, the primary rate is only maintained at a very large spreading factor, which significantly constrains the backscatter \emph{throughput}.
-		\emph{Second,} the average primary rate slightly decreases/increases in the presence of a \gls{ambc}/\gls{ris} node and the benefit of \gls{sr} is not obvious.
-		This is because the cascaded channel is usually orders of magnitude weaker than the direct channel.
-		\gls{ris} always ensures constructive superposition of direct and scattered components while \gls{sr} only creates a quasi-static rich-scattering environment that marginally enhances the average primary rate.
-		When $N$ is moderate, the randomly scattered signals should be modelled as interference rather than multipath components and the \gls{sr} point should move towards the \gls{ambc} point.
+		Since \gls{sr} requires a very large $N$ to guarantee the primary rate, the signal processing cost at the receiver can be prohibitive, and the backscatter \emph{throughput} can be severely constrained.
+		\emph{Second,} the average primary rate slightly decreases/increases in the presence of a \gls{ambc}/\gls{ris} node, and the benefit of \gls{sr} is not obvious.
+		This is because the cascaded channel in this case is around \qty{25}{dB} weaker than the direct channel.
+		Here, \gls{ris} ensures a constructive superposition of the direct and scattered components, while \gls{sr} only creates a quasi-static rich-scattering environment that marginally enhances the average primary rate.
+		When $N$ is moderate, the randomly scattered signals should be modelled as interference rather than stable multipath, and the \gls{sr} point should move vertically towards the \gls{ambc} point.
 		\emph{Third,} RIScatter enables a flexible primary-backscatter tradeoff with adaptive input distribution design.
-		In terms of maximum primary achievable rate, RIScatter coincides with \gls{ris} and outperforms the others using deterministic reflection pattern.
-		On the other hand, for a large $N$, the maximum backscatter achievable rate of RIScatter is lower than \gls{bbc} and \gls{sr} but higher than \gls{ambc}.
-		This is because both RIScatter and \gls{ambc} employ semi-coherent energy detection, and the adaptive channel coding of RIScatter provides better performance than equiprobable inputs of \gls{ambc} especially at the low \gls{snr} of double fading.
-		When multiple antenna is available at the \gls{ap}, active beamforming can be optimized for RIScatter nodes and the backscatter rate gain over \gls{ambc} can be even larger.
+		In terms of maximum primary achievable rate, RIScatter coincides with \gls{ris} and outperforms the others by using the static reflection pattern that maximizes the primary \gls{snr} all the time.
+		On the other hand, its maximum backscatter achievable rate is higher than that of \gls{ambc}.
+		This is because the adaptive channel coding of RIScatter outperforms the equiprobable inputs of \gls{ambc}, especially at the low backscatter \gls{snr} caused by double fading.
+		When multiple antenna is available at the \gls{ap}, active beamforming can be optimized for RIScatter nodes and the advantage over \gls{ambc} should be more prominent.
 	\end{subsection}
@@
 			\begin{itemize}
-				\item \emph{Cooperation:} Joint nodes encoding using a $K$-dimensional probability array $P_{\mathcal{K}}(x_{m_{\mathcal{K}}})$ by Algorithm \ref{al:input_distribution};
+				\item \emph{Cooperation:} Joint encoding using a joint probability array $p(x_{m_{\mathcal{K}}})$ with $M^K$ entries by Algorithm \ref{al:input_distribution};
 				\item \emph{Exhaustion:} Exhaustive search over the $M$-dimensional probability simplex with resolution $\Delta p = \num{e-2}$;
-				\item \emph{\gls{kkt}:} Numerical \gls{kkt} evaluation by Algorithm \ref{al:input_distribution};
-				\item \emph{Equiprobable:} Uniform input distribution for all nodes.
+				\item \emph{\gls{kkt}:} Solution by Algorithm \ref{al:input_distribution};
+				\item \emph{Equiprobable:} Uniform input distribution.
 			\end{itemize}
-			For dispersed nodes, joint encoding is inapplicable and we consider these independent input distribution recovery methods (from the joint probability array):
+			We also consider these independent distribution recovery methods from the joint probability array:
 			\begin{itemize}
 				\item \emph{Marginalization:} Marginal probability distributions;
-				\item \emph{Decomposition:} Normalized rank-\num{1} \gls{cp} decomposition tensors by \texttt{Tensor Toolbox} \cite{Bader2022};
+				\item \emph{Decomposition:} Normalized rank-\num{1} \gls{cp} decomposed tensors by \texttt{Tensor Toolbox} \cite{Bader2022};
 				\item \emph{Randomization:} Gaussian randomization with the guidance of correlation matrix \cite{Calvo2010}.
-				% guided by correlation matrix \cite{Calvo2010}.
 			\end{itemize}
 
-			Fig.~\subref*{fg:region_distribution} shows the average achievable rate regions for those designs.
-			We observe Cooperation provides the outer bound and joint encoding can be beneficial.
-			The average rate performance of Exhaustion and \gls{kkt} completely coincide with each other, demonstrating \gls{kkt} input distribution is favorable for a moderate $K$ as mentioned in Remark \ref{re:input_kkt_distribution}.
-			Equiprobable experiences minor backscatter and major primary rate losses without exploiting \gls{csi} and \gls{qos}.
-			Both rate gaps should be larger when $M$ and/or $K$ increase.
-			For the recovery methods, the simple Marginalization provides a close performance to \gls{kkt}, but Randomization and Decomposition fail our expectations for most channel realizations.
-			Those observations emphasize the importance of (joint) adaptive RIScatter encoding and demonstrate the advantage of the proposed \gls{kkt} input distribution design.
+			Fig.~\subref*{fg:region_distribution} shows their average achievable rate regions.
+			Cooperation achieves the outer bound of all schemes, but joint encoding over passive devices may incur additional hardware cost.
+			Besides, the average rate performance of Exhaustion and \gls{kkt} completely coincide with each other when $K=2$.
+			This confirms Remark \ref{re:input_kkt_distribution} that the \gls{kkt} input distribution can be good enough when $K$ is moderate.
+			Equiprobable experiences minor backscatter and major primary rate losses without exploiting \gls{csi} and \gls{qos}, and those gaps should be larger when $M$ or $K$ increases.
+			Marginalization provides a close performance to \gls{kkt}, but Randomization and Decomposition fail our expectations for most channel realizations.
+			Those observations emphasize the importance of adaptive RIScatter encoding and demonstrate the advantage of the proposed \gls{kkt} input distribution design.
 		\end{subsubsection}
@@
 			\subfloat[RIScatter Nodes\label{fg:region_tags}]{
-				\resizebox{0.27\columnwidth}{!}{
+				\resizebox{0.23\columnwidth}{!}{
 					\input{assets/simulation/region_tags.tex}
@@
 			}
-			\subfloat[Input States\label{fg:region_states}]{
-				\resizebox{0.27\columnwidth}{!}{
+			\subfloat[Reflection States\label{fg:region_states}]{
+				\resizebox{0.23\columnwidth}{!}{
 					\input{assets/simulation/region_states.tex}
@@
 			\subfloat[Transmit Antennas\label{fg:region_txs}]{
-				\resizebox{0.27\columnwidth}{!}{
+				\resizebox{0.23\columnwidth}{!}{
 					\input{assets/simulation/region_txs.tex}
@@
 			}
+			\subfloat[Spreading Factor\label{fg:region_duration}]{
+				\resizebox{0.23\columnwidth}{!}{
+					\input{assets/simulation/region_duration.tex}
+				}
+			}
 			\\
-			\subfloat[Spreading Factor\label{fg:region_duration}]{
-				\resizebox{0.27\columnwidth}{!}{
-					\input{assets/simulation/region_duration.tex}
-				}
-			}
 			\subfloat[Average Noise Power\label{fg:region_noise}]{
-				\resizebox{0.27\columnwidth}{!}{
+				\resizebox{0.23\columnwidth}{!}{
 					\input{assets/simulation/region_noise.tex}
@@
 			}
-			\subfloat[Disk Radius\label{fg:region_coverage}]{
-				\resizebox{0.27\columnwidth}{!}{
-					\input{assets/simulation/region_coverage.tex}
+			\subfloat[Imperfect \gls{csi}\label{fg:region_csi}]{
+				\resizebox{0.23\columnwidth}{!}{
+					\input{assets/simulation/region_csi.tex}
+				}
+			}
+			\subfloat[Primary \gls{snr}\label{fg:region_snr_primary}]{
+				\resizebox{0.23\columnwidth}{!}{
+					\input{assets/simulation/region_snr_primary.tex}
+				}
+			}
+			\subfloat[Backscatter \gls{snr}\label{fg:region_snr_backscatter}]{
+				\resizebox{0.23\columnwidth}{!}{
+					\input{assets/simulation/region_snr_backscatter.tex}
 				}
@@
 		\end{figure}
-		In this study, we choose $Q=4$, $K=8$, $M=2$, $N=20$, $\sigma_v^2=\SI{-40}{\dBm}$ and $r=\SI{2}{\meter}$ as a reference.
+		In this study, we choose $Q=4$, $K=8$, $M=2$, $N=20$, $\sigma_v^2=\qty{-40}{dBm}$ and $r=\qty{2}{m}$ as a reference, unless otherwise specified.
 		\begin{subsubsection}{Number of Nodes}
-			Fig.~\subref*{fg:region_tags} reveals how the number RIScatter nodes $K$ influence the primary-backscatter tradeoff.
+			Fig.~\subref*{fg:region_tags} reveals how the number RIScatter nodes $K$ influences the primary-backscatter tradeoff.
 			Interestingly, we observe that increasing $K$ has a larger benefit on the total backscatter rate than primary.
-			This is because each RIScatter node not only affects the primary equivalent \gls{snr} but also influences the relative energy difference that other nodes can create.
+			This is because each RIScatter node not only affects the primary \gls{snr} but also influences the relative energy difference that other nodes can make.
 			To maximize the total backscatter rate, some nodes closer to the user may need to sacrifice their own rate and use the state that \emph{minimizes} the composite channel strength, in order to increase the backscatter rate of other nodes.
 			This accounts for the significant primary rate decrease in the low-$\rho$ regime.
-			On the other hand, when the primary link is prioritized, the RIScatter nodes boil down to \gls{ris} elements and enjoy a conventional passive array gain $N^2$.
+			On the other hand, when the primary link is prioritized, the RIScatter nodes boil down to \gls{ris} elements and enjoy a passive array gain of $K^2$.
 		\end{subsubsection}
@@
 		\begin{subsubsection}{Number of States}
-			Fig.~\subref*{fg:region_states} shows the relationship between available reflection states (i.e., \gls{qam} order) $M$ and achievable rate regions.
-			We notice increasing the reflection states has a marginal effect on both primary and total backscatter rates.
-			This is because once the scope of reflection coefficient is determined, using denser constellation points only creates marginal phase resolution and energy diversity for primary and backscatter links.
-			Due to the maximum amplitude normalization in \eqref{eq:backscatter_modulation}, the average rate region of \num{8}-\gls{qam} (points on rectangle border) is smaller than that of \num{4}-\gls{qam} (points on square vertices), and the \num{4} points on the rectangle edges are less frequently used.
-			On the other hand, \num{16}-\gls{qam} provides significant higher backscatter rate benefit than primary.
-			It motivates one to use high-resolution metamaterial units as RIScatter nodes.
-			% The results in this and previous paragraphs motivate one to replace the high-resolution metamaterial units by multiple low-order scatter nodes.
+			Fig.~\subref*{fg:region_states} shows the relationship between the available reflection states (i.e., \gls{qam} order) $M$ and the achievable rate region when $K=1$.
+			We notice that increasing the reflection states has a marginal effect on the primary rate but significantly improves the backscatter rate.
+			This is because the maximum amplitude normalized-\gls{qam} \eqref{eq:backscatter_modulation} involves more weak reflection points as $M$ increases.
+			It enhances the receive energy diversity but cannot provide enough phase shift resolution with maximum reflection.
 		\end{subsubsection}
@@
 		\begin{subsubsection}{Spreading factor}
-			Fig.~\subref*{fg:region_duration} presents how the spreading factor $N$ affects the achievable rate region.
-			Please notice here the unit of total backscatter rate is bits per primary block to indicate throughput.
-			Apparently, using a very large $N$ can severely constrain the backscatter throughput, since the gain in energy certainty (by law of large numbers) cannot withstand the loss in gross rate.
-			As $N \to \infty$, RIScatter nodes boil down to \gls{ris} elements with fixed reflection pattern during whole channel block and the total backscatter rate approaches \num{0}.
-			On the other hand, when $N$ is too small, the equivalent \gls{dmmac} \eqref{eq:dmmac} has very high error probabilities and the energy detection is thus unreliable.
+			Fig.~\subref*{fg:region_duration} shows how the spreading factor $N$ affects the achievable rate region.\footnote{Here, the unit of total backscatter rate is bits per primary block to show backscatter throughput.}
+			Using a very large $N$ (as in the case of \gls{sr}) can severely constrain the backscatter throughput, since the gain in energy certainty (by the law of large numbers) cannot withstand the loss in the gross rate.
+			As $N \to \infty$, RIScatter nodes boil down to static \gls{ris} elements and the total backscatter rate approaches \num{0}.
+			On the other hand, when $N$ is too small, the \gls{dmmac} \eqref{eq:dmmac} becomes unreliable and energy detection is error-prone.
 			It explains the observation that $N=10$ provides lower backscatter throughput than $N=20$.
-			Therefore, we conclude the design of spreading factor $N$ in RIScatter systems should accommodate multiple factors (e.g., data rate requirements, load switching constraints at the nodes, and signal processing capability at the user).
+			Therefore, we conclude the spreading factor $N$ should be carefully designed over multiple factors (e.g., primary and backscatter \gls{snr}, data rate requirements, load switching speed at the nodes, and signal processing capability at the user).
 		\end{subsubsection}
@@
 \begin{section}{Conclusion}
-	This paper introduced RIScatter as a low-power scatter protocol that simultaneously provides backscatter modulation and passive beamforming by smart input distribution design.
-	Starting from scattering principles, we showed how RIScatter nodes generalize information nodes of \gls{bc} and reflect elements of \gls{ris} as special cases, how they can be built over existing passive scatter devices, and how they simultaneously encode self information and assist legacy transmission.
-	We also propose a practical \gls{sic}-free receiver that exploits the properties of active-passive coexisting networks to maintain primary benefit and improve backscatter throughput.
-	The achievable primary-total-backscatter rate region is then studied for a single-user multi-node RIScatter system, where the input distribution, active beamforming, and decision thresholds are iteratively updated.
-	Numerical results not only validated the proposed algorithms but also emphasized the importance of adaptive input distribution and cooperative decoding for both primary and backscatter links.
-
-	One possible future direction is to consider backscatter detection over the received signal domain rather than energy domain, where multi-antenna \cite{Liu2022c} and learning-based approaches can be promising.
-	Another interesting question is how to design RIScatter node and receiver in a multi-user system to fully exploit the dynamic passive beamforming that naturally origins from backscatter modulation.
-	% If one node can be decoded by multiple users, its input distribution may be further adjusted to mimic the multi-beam gain of dynamic passive beamforming \cite{Qiu2022}.
-	% This will be answered in our future work.
+	\label{sc:conclusion}
+	This paper introduced RIScatter as a novel scatter protocol that bridges backscatter modulation and passive beamforming.
+	Starting from scattering principles, we showed how RIScatter nodes generalize information nodes of \gls{bc} and reflect elements of \gls{ris}, how they can be built over existing passive scatter devices, and how they simultaneously encode self information and assist legacy transmission.
+	We also proposed a practical \gls{sic}-free receiver that exploits the properties of active-passive coexisting networks to benefit both subsystems.
+	The achievable primary-total-backscatter rate region was then studied for a single-user multi-node RIScatter network, where the input distribution, active beamforming, and decision thresholds are iteratively updated.
+	Numerical results validated the proposed algorithms and emphasized the importance of adaptive input distribution and cooperative receiver design.
+
+	To support massive RIScatter networks with large number of nodes and states, one possible future direction is to consider backscatter detection over the received signal domain rather than energy domain, where multi-antenna \cite{Liu2022c} and learning-based approaches can be promising.
+	Another interesting question is how to design RIScatter nodes and receivers in a multi-user system to fully exploit the dynamic passive beamforming that naturally origins from backscatter modulation.
 \end{section}
@@
 		We first prove sequence \eqref{eq:input_kkt_solution} is non-decreasing in weighted sum mutual information.
-		Let $P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) = \prod_{q \in \mathcal{K}} P_q(x_{m_q})$ and $P_{\mathcal{K}}'(x_{m_{\mathcal{K}}}) = P_k'(x_{m_k}) \prod_{q \in \mathcal{K} \setminus \{k\}} P_q(x_{m_q})$ be two probability distributions with potentially different marginal for tag $k$ at state $m_k$, and define an intermediate function
-		\begin{align}
-			J \bigl( P_{\mathcal{K}}(x_{m_{\mathcal{K}}}),P_{\mathcal{K}}'(x_{m_{\mathcal{K}}}) \bigr)
-			 & \triangleq \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}})
-			\Biggl( \rho \log \Bigl(1 + \frac{\lvert \boldsymbol{h}_{\text{E}}^\mathsf{H}(x_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_v^2}\Bigr) \nonumber                                                                                                                                          \\
-			 & \qquad + (1 - \rho) \sum_{m_{\mathcal{K}}'} P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}}) \log \frac{P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}}) P_{\mathcal{K}}'(x_{m_{\mathcal{K}}})}{P_{\mathcal{K}}'(\hat{x}_{m_{\mathcal{K}}'}) P_{\mathcal{K}}(x_{m_{\mathcal{K}}})} \Biggr).
+		Let $p(x_{m_{\mathcal{K}}}) = \prod_{q \in \mathcal{K}} p(x_{m_q})$ and $p'(x_{m_{\mathcal{K}}}) = p'(x_{m_k}) \prod_{q \in \mathcal{K} \setminus \{k\}} p(x_{m_q})$ be two distributions potentially different at $x_{m_k}$, and define a joint function
+
+			{\small
+				\begin{equation}
+					J \bigl( p(x_{m_{\mathcal{K}}}),p'(x_{m_{\mathcal{K}}}) \bigr) \triangleq \sum_{m_{\mathcal{K}}} p(x_{m_{\mathcal{K}}})
+					\Biggl( \rho \log \Bigl(1 + \frac{\lvert \boldsymbol{h}^\mathsf{H}(x_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_v^2}\Bigr) + (1 - \rho) \sum_{m_{\mathcal{K}}'} q(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}}) \log \frac{q(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}}) p'(x_{m_{\mathcal{K}}})}{p'(\hat{x}_{m_{\mathcal{K}}'}) p(x_{m_{\mathcal{K}}})} \Biggr).
 					\label{eq:intermediate_information_function}
-		\end{align}
-		It is straightforward to verify $J \bigl( P_{\mathcal{K}}(x_{m_{\mathcal{K}}}),P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) \bigr) = I(x_{\mathcal{K}})$ and $J \bigl( P_{\mathcal{K}}(x_{m_{\mathcal{K}}}),P_{\mathcal{K}}'(x_{m_{\mathcal{K}}}) \bigr)$ is a concave function for a fixed $P_{\mathcal{K}}'(x_{m_{\mathcal{K}}})$.
-		Setting $\nabla_{P_k^\star(x_{m_k})} J \bigl( P_{\mathcal{K}}(x_{m_{\mathcal{K}}}),P_{\mathcal{K}}'(x_{m_{\mathcal{K}}}) \bigr) = 0$, we have
-		\begin{equation}
-			S_k'(x_{m_k}) - S_k'(x_{i_k}) + (1 - \rho) \log \frac{P_k(x_{i_k})}{P_k^\star(x_{m_k})} = 0,
+				\end{equation}}
+
+		It is straightforward to verify $J \bigl( p(x_{m_{\mathcal{K}}}),p(x_{m_{\mathcal{K}}}) \bigr) = I(x_{\mathcal{K}})$ and $J \bigl( p(x_{m_{\mathcal{K}}}),p'(x_{m_{\mathcal{K}}}) \bigr)$ is a concave function for a given $p'(x_{m_{\mathcal{K}}})$.
+		Setting $\nabla_{p(x_{m_k})} J \bigl( p(x_{m_{\mathcal{K}}}),p'(x_{m_{\mathcal{K}}}) \bigr) = 0$ yields
+		\begin{equation}
+			S_k'(x_{m_k}) - S_k'(x_{i_k}) + (1 - \rho) \log \frac{p(x_{i_k})}{p^\star(x_{m_k})} = 0,
 			\label{eq:optimal_intermediate_information_condition}
@@
 		where $i_k \ne m_k$ is the reference state and
-		\begin{align}
-			S_k'(x_{m_k})
-			 & \triangleq I_k'(x_{m_k}) + (1 - \rho) \sum_{m_{\mathcal{K} \setminus \{k\}}} P_{\mathcal{K} \setminus \{k\}}(x_{m_{\mathcal{K} \setminus \{k\}}})\nonumber \\
-			 & \quad \times \sum_{m_{\mathcal{K}}'} P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}}) \log P_{\mathcal{K}}'(x_{m_{\mathcal{K}}}).
-		\end{align}
+		\begin{equation}
+			S_k'(x_{m_k}) \triangleq I_k'(x_{m_k}) + (1 - \rho) \sum_{m_{\mathcal{K} \setminus \{k\}}} p(x_{m_{\mathcal{K} \setminus \{k\}}}) \sum_{m_{\mathcal{K}}'} q(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}}) \log p'(x_{m_{\mathcal{K}}}).
+		\end{equation}
 		Evidently, $\forall m_k \ne i_k$, \eqref{eq:optimal_intermediate_information_condition} boils down to
 		\begin{equation}
-			P_k^\star(x_{m_k}) = \frac{P_k'(x_{m_k}) \exp \Bigl( \frac{\rho}{1 - \rho} I_k'(x_{m_k}) \Bigr)}{\sum_{m_k'} P_k'(x_{m_k'}) \exp \Bigl( \frac{\rho}{1 - \rho} I_k'(x_{m_k'}) \Bigr)}.
+			p^\star(x_{m_k}) = \frac{p'(x_{m_k}) \exp \Bigl( \frac{\rho}{1 - \rho} I_k'(x_{m_k}) \Bigr)}{\sum_{m_k'} p'(x_{m_k'}) \exp \Bigl( \frac{\rho}{1 - \rho} I_k'(x_{m_k'}) \Bigr)}.
 			\label{eq:optimal_relative_distribution}
 		\end{equation}
-		Since $P_k(x_{i_k}) = 1 - \sum_{m_k \ne i_k} P_k^\star(x_{m_k})$ has exactly the same form as \eqref{eq:optimal_relative_distribution}, the choice of reference state $i_k$ does not matter and \eqref{eq:optimal_relative_distribution} is indeed optimal $\forall m_k \in \mathcal{M}$.
-		That is, for a fixed $P_{\mathcal{K}}'(x_{m_{\mathcal{K}}})$, choosing $P_k(x_{m_k})$ by \eqref{eq:optimal_relative_distribution} ensures
-		\begin{equation}
-			J \bigl( P_{\mathcal{K}}(x_{m_{\mathcal{K}}}),P_{\mathcal{K}}'(x_{m_{\mathcal{K}}}) \bigr) \ge I'(x_{\mathcal{K}}).
+		Since $p(x_{i_k}) = 1 - \sum_{m_k \ne i_k} p^\star(x_{m_k})$ has exactly the same form as \eqref{eq:optimal_relative_distribution}, the choice of reference does not matter and \eqref{eq:optimal_relative_distribution} is optimal $\forall m_k \in \mathcal{M}$.
+		That is, for a fixed $p'(x_{m_{\mathcal{K}}})$, \eqref{eq:optimal_relative_distribution} ensures
+		\begin{equation}
+			J \bigl( p(x_{m_{\mathcal{K}}}),p'(x_{m_{\mathcal{K}}}) \bigr) \ge I'(x_{\mathcal{K}}).
 			\label{eq:information_difference_lower}
 		\end{equation}
-		On the other hand, we also have
+		On the other hand, we notice
 		\begin{subequations}
+			\allowdisplaybreaks
 			\label{eq:information_difference_upper}
 			\begin{align}
-				\Delta
-				 & \triangleq I(x_{\mathcal{K}}) - J \bigl( P_{\mathcal{K}}(x_{m_{\mathcal{K}}}),P_{\mathcal{K}}'(x_{m_{\mathcal{K}}}) \bigr)                                                                                                                                                                                                                                                  \\
-				 & = (1 - \rho) \sum_{m_k} \frac{P_k'(x_{m_k}) f_k'(x_{m_k})}{\sum_{m_k'} P_k'(x_{m_k'}) f_k'(x_{m_k'})} \sum_{m_{\mathcal{K}}''} P(\hat{x}_{m_{\mathcal{K}}''}|x_{m_k}) \log \frac{\sum_{m_k'} P_k'(x_{m_k'}) P(\hat{x}_{m_{\mathcal{K}}''}|x_{m_k'}) f_k'(x_{m_k})}{\sum_{m_k'} P_k'(x_{m_k'}) P(\hat{x}_{m_{\mathcal{K}}''}|x_{m_k'}) f_k'(x_{m_k'})}                       \\
-				 & \ge (1 - \rho) \sum_{m_k} \frac{P_k'(x_{m_k}) f_k'(x_{m_k})}{\sum_{m_k'} P_k'(x_{m_k'}) f_k'(x_{m_k'})} \sum_{m_{\mathcal{K}}''} P(\hat{x}_{m_{\mathcal{K}}''}|x_{m_k}) \Biggl( 1 - \frac{\sum_{m_k'} P_k'(x_{m_k'}) P(\hat{x}_{m_{\mathcal{K}}''}|x_{m_k'}) f_k'(x_{m_k'})}{\sum_{m_k'} P_k'(x_{m_k'}) P(\hat{x}_{m_{\mathcal{K}}''}|x_{m_k'}) f_k'(x_{m_k})} \Biggr) = 0,
+				 & I(x_{\mathcal{K}}) - J \bigl( p(x_{m_{\mathcal{K}}}),p'(x_{m_{\mathcal{K}}}) \bigr)                                                                                                                    \nonumber                                                                                                                                                               \\
+				 & = (1 - \rho) \sum_{m_k} \frac{p'(x_{m_k}) f_k'(x_{m_k})}{\sum_{m_k'} p'(x_{m_k'}) f_k'(x_{m_k'})} \sum_{m_{\mathcal{K}}''} q(\hat{x}_{m_{\mathcal{K}}''}|x_{m_k}) \log \frac{\sum_{m_k'} p'(x_{m_k'}) q(\hat{x}_{m_{\mathcal{K}}''}|x_{m_k'}) f_k'(x_{m_k})}{\sum_{m_k'} p'(x_{m_k'}) q(\hat{x}_{m_{\mathcal{K}}''}|x_{m_k'}) f_k'(x_{m_k'})}                                  \\
+				 & \ge (1 - \rho) \sum_{m_k} \frac{p'(x_{m_k}) f_k'(x_{m_k})}{\sum_{m_k'} p'(x_{m_k'}) f_k'(x_{m_k'})} \sum_{m_{\mathcal{K}}''} q(\hat{x}_{m_{\mathcal{K}}''}|x_{m_k}) \Biggl( 1 - \frac{\sum_{m_k'} p'(x_{m_k'}) q(\hat{x}_{m_{\mathcal{K}}''}|x_{m_k'}) f_k'(x_{m_k'})}{\sum_{m_k'} p'(x_{m_k'}) q(\hat{x}_{m_{\mathcal{K}}''}|x_{m_k'}) f_k'(x_{m_k})} \Biggr)                 \\
+				 & = (1 - \rho) \Biggl( 1 - \sum_{m_k} \frac{p'(x_{m_k}) \cancel{f_k'(x_{m_k})}}{\sum_{m_k'} p'(x_{m_k'}) f_k'(x_{m_k'})} \sum_{m_{\mathcal{K}}''} q(\hat{x}_{m_{\mathcal{K}}''}|x_{m_k}) \frac{\sum_{m_k'} p'(x_{m_k'}) q(\hat{x}_{m_{\mathcal{K}}''}|x_{m_k'}) f_k'(x_{m_k'})}{\sum_{m_k'} p'(x_{m_k'}) q(\hat{x}_{m_{\mathcal{K}}''}|x_{m_k'}) \cancel{f_k'(x_{m_k})}} \Biggr) \\
+				 & = (1 - \rho) \Biggl( 1 - \sum_{m_{\mathcal{K}}''} \frac{\cancel{\sum_{m_k} p'(x_{m_k}) q(\hat{x}_{m_{\mathcal{K}}''}|x_{m_k})}}{\sum_{m_k'} p'(x_{m_k'}) f_k'(x_{m_k'})} \frac{\sum_{m_k'} p'(x_{m_k'}) q(\hat{x}_{m_{\mathcal{K}}''}|x_{m_k'}) f_k'(x_{m_k'})}{\cancel{\sum_{m_k'} p'(x_{m_k'}) q(\hat{x}_{m_{\mathcal{K}}''}|x_{m_k'})}} \Biggr)                             \\
+				 & = (1 - \rho) \Biggl( 1 - \frac{\sum_{m_k'} p'(x_{m_k'}) f_k'(x_{m_k'}) \sum_{m_{\mathcal{K}}''} q(\hat{x}_{m_{\mathcal{K}}''}|x_{m_k'})}{\sum_{m_k'} p'(x_{m_k'}) f_k'(x_{m_k'})} \Biggr)                                                                                                                                                                                      \\
+				 & = 0,
 			\end{align}
 		\end{subequations}
-		where $f_k'(x_{m_k}) \triangleq \exp \bigl( \frac{\rho}{1 - \rho} I_k'(x_{m_k}) \bigr)$ and the equality holds if and only if \eqref{eq:optimal_relative_distribution} converges.
+		where $f_k'(x_{m_k}) \triangleq \exp \bigl( \frac{\rho}{1 - \rho} I_k'(x_{m_k}) \bigr)$ and the equality holds if and only if $p(x_{m_{\mathcal{K}}})$ and $p'(x_{m_{\mathcal{K}}})$ equals (i.e., \eqref{eq:optimal_relative_distribution} converges).
 		\eqref{eq:information_difference_lower} and \eqref{eq:information_difference_upper} together imply $I(x_{\mathcal{K}}) \ge I'(x_{\mathcal{K}})$.
-		Since mutual information is bounded above, we conclude the sequence \eqref{eq:input_kkt_solution} is non-decreasing and convergent in mutual information.
-
-		Next, we prove any converging point of sequence \eqref{eq:input_kkt_solution}, denoted as $P_k^\star(x_{m_k})$, fulfills \gls{kkt} conditions \eqref{eq:input_kkt_condition}.
-		To see this, let
-		\begin{equation}
-			D_k^{(r)}(x_{m_k}) \triangleq \frac{P_k^{(r+1)}(x_{m_k})}{P_k^{(r)}(x_{m_k})} = \frac{f_k^{(r)}(x_{m_k})}{\sum_{m_k'} P_k^{(r)}(x_{m_k'}) f_k^{(r)}(x_{m_k'})}.
-		\end{equation}
-		As sequence \eqref{eq:input_kkt_solution} is convergent, any state with $P_k^\star(x_{m_k}) > 0$ need to satisfy $D_k^\star(x_{m_k}) \triangleq \lim_{r \to \infty} D_k^{(r)}(x_{m_k}) = 1$, namely
-		\begin{equation}
-			I_k^\star(x_{m_k}) = \frac{1 - \rho}{\rho} \log \sum_{m_k'} P_k^\star(x_{m_k'}) f_k^\star(x_{m_k'}),
-		\end{equation}
-		which is reminiscent of \eqref{eq:probable_states_marginal} and \eqref{eq:probable_states}.
-		That is, given $P_k^{(0)}(x_{m_k}) > 0$, any converging point with $P_k^\star(x_{m_k}) > 0$ must satisfy \eqref{eq:probable_states}.
-		On the other hand, we assume $P_k^\star(x_{m_k})$ does not satisfy \eqref{eq:dropped_states}, such that for any state with $P_k^\star(x_{m_k}) = 0$,
-		\begin{equation}
-			I_k^\star(x_{m_k}) > I^\star(x_{\mathcal{K}}) = \sum_{m_k'} P_k^\star(x_{m_k'}) I_k^\star(x_{m_k'}),
-		\end{equation}
-		where the equality inherits from \eqref{eq:weighted_sum_mutual_information}.
-		Since the exponential function is monotonically increasing, we have $f_k^\star(x_{m_k}) > \sum_{m_k'} P_k^\star(x_{m_k'}) f_k^\star(x_{m_k'})$ and $D_k^\star(x_{m_k}) > 1$.
-		Considering $P_k^{(0)}(x_{m_k}) > 0$ and $P_k^\star(x_{m_k}) = 0$, it contradicts with
-		\begin{equation}
-			P_k^{(r)}(x_{m_k}) = P_k^{(0)}(x_{m_k}) \prod_{n=1}^r D_k^{(n)}(x_{m_k}).
-		\end{equation}
-		That is, given $P_k^{(0)}(x_{m_k}) > 0$, any converging point with $P_k^\star(x_{m_k}) = 0$ must satisfy \eqref{eq:dropped_states}.
-		The proof is thus completed.
+		Since mutual information is bounded above, we conclude the sequence \eqref{eq:input_kkt_solution} is non-decreasing and convergent.
+
+		Next, we prove any converging point of sequence \eqref{eq:input_kkt_solution}, denoted as $p^\star(x_{m_k})$, fulfills the \gls{kkt} conditions \eqref{eq:input_kkt_condition}.
+		Let
+		\begin{equation}
+			D^{(r)}(x_{m_k}) \triangleq \frac{p^{(r+1)}(x_{m_k})}{p^{(r)}(x_{m_k})} = \frac{f_k^{(r)}(x_{m_k})}{\sum_{m_k'} p^{(r)}(x_{m_k'}) f_k^{(r)}(x_{m_k'})}.
+		\end{equation}
+		As sequence \eqref{eq:input_kkt_solution} is convergent, any state with $p^\star(x_{m_k}) > 0$ need to satisfy $D^\star(x_{m_k}) \triangleq \lim_{r \to \infty} D^{(r)}(x_{m_k}) = 1$, namely
+		\begin{equation}
+			I_k^\star(x_{m_k}) = \frac{1 - \rho}{\rho} \log \sum_{m_k'} p^\star(x_{m_k'}) \exp \Bigl( \frac{\rho}{1 - \rho} I_k^\star(x_{m_k'}) \Bigr).
+		\end{equation}
+		The right-hand side is a constant for node $k$ and implies \eqref{eq:probable_states_marginal}.
+		That is, any converging point with nonzero probability must satisfy \eqref{eq:probable_states}.
+		On the other hand, we assume $p^\star(x_{m_k}) = 0$ does not satisfy \eqref{eq:dropped_states}, namely
+		\begin{equation}
+			I_k^\star(x_{m_k}) > I^\star(x_{\mathcal{K}}) = \sum_{m_k'} p^\star(x_{m_k'}) I_k^\star(x_{m_k'}),
+			\label{eq:dropped_states_assumption}
+		\end{equation}
+		Since the exponential function is monotonically increasing, \eqref{eq:dropped_states_assumption} implies $f_k^\star(x_{m_k}) > \sum_{m_k'} p^\star(x_{m_k'}) f_k^\star(x_{m_k'})$ and $D^\star(x_{m_k}) > 1$.
+		It contradicts with
+		\begin{equation}
+			p^{(r)}(x_{m_k}) = p^{(0)}(x_{m_k}) \prod_{n=1}^r D^{(n)}(x_{m_k}),
+		\end{equation}
+		since the left-hand side is zero while all terms on the right-hand side are strictly positive.
+		The proof is completed.
 		\label{ap:input_kkt_solution}
 	\end{subsection}
-
-	% \begin{subsection}{Proof of Proposition \ref{pr:threshold}}
-	% 	Since $L$ input letters are with non-zero probability and $x \to z \to \hat{x}$ formulates a Markov chain, we need $L$ non-empty decision regions and at least $L+1$ distinct thresholds (including \num{0} and $\infty$) to minimize the distortion between source and decision.
-	% 	On the other hand, the optimal decision regions are apparently empty for those unused letters.
-
-	% 	Suppose the optimal number of thresholds is $S+1$ where $S \ge L$.
-	% 	Let $\boldsymbol{t} \triangleq [t_0,\ldots,t_S]^\mathsf{T} \in \mathbb{R}_{+}^{(S+1)}$ be the optimal threshold vector where $t_{s-1} < t_s$, $\forall s \in \mathcal{S} \triangleq \{1,\ldots,S\}$.
-	% 	Since the optimal decision region for any letter may consist of multiple partitions, without loss of generality, we assume the mapping from threshold vector to decision region $l' \in \mathcal{L} \triangleq \{1,\ldots,L\}$ is given by $\mathcal{R}_{l'} = \bigcup_{s \equiv l' \pmod L} [t_{s-1},t_s)$.
-	% 	\begin{footnote}
-	% 		The proof holds for any valid mapping from threshold vector to decision regions, and we consider this specific case for the ease of presentation.
-	% 	\end{footnote}
-	% 	The threshold optimization problem is
-	% 	\begin{maxi!}
-	% 		{\scriptstyle{\boldsymbol{t}}}{I_{\text{B}}(x;\hat{x})}{\label{op:decision_threshold}}{\label{ob:backscatter_mutual_information}}
-	% 		\addConstraint{t_{s-1}}{< t_s,}{\quad \forall s \in \mathcal{S}.}{\label{co:strict_inequality}}
-	% 	\end{maxi!}
-
-	% 	Problem \eqref{op:decision_threshold} is intricate due to the strict inequality constraint \eqref{co:strict_inequality}.
-	% 	Following \cite{Nguyen2020}, we first relax it to the convex counterpart, then discard the solutions that violate any original constraint.
-	% 	The Lagrangian function for the relaxed problem is
-	% 	\begin{equation}
-	% 		L = - I_{\text{B}}(x;\hat{x}) + \sum_{s \in \mathcal{S}} \mu_s (t_{s-1} - t_s),
-	% 	\end{equation}
-	% 	where $\mu_s$ is the Lagrange multiplier associated with the non-strict version of \eqref{co:strict_inequality}.
-	% 	The \gls{kkt} conditions on the optimal primal and dual solutions are, $\forall s \in \mathcal{S}$,
-	% 	\begin{subequations}
-	% 		\label{eq:kkt_thresholding}
-	% 		\begin{equation}
-	% 			- \nabla_{t_s^\star} I^\star_{\text{B}}(x;\hat{x}) + \mu_{s-1}^\star - \mu_s^\star = 0,
-	% 			\label{eq:stationarity}
-	% 		\end{equation}
-	% 		\begin{equation}
-	% 			\mu_s^\star \ge 0,
-	% 			\label{eq:dual_feasibility}
-	% 		\end{equation}
-	% 		\begin{equation}
-	% 			\mu_s^\star (t_{s-1}^\star - t_s^\star) = 0.
-	% 			\label{eq:complementary_slackness}
-	% 		\end{equation}
-
-	% 	\end{subequations}
-	% 	Due to the strict inequality constraint \eqref{co:strict_inequality}, conditions \eqref{eq:dual_feasibility} and \eqref{eq:complementary_slackness} together imply $\mu_s^\star = 0$, $\forall s \in \mathcal{S}$.
-	% 	Besides, it is trivial to conclude $t_0^\star = 0$ for energy-based detection.
-	% 	As such, the necessary optimality conditions for problem \eqref{op:decision_threshold}, $\forall s \in \mathcal{S}$,
-	% 	\begin{equation}
-	% 		\nabla_{t_{s}^\star} I^\star_{\text{B}}(x;\hat{x}) = 0,
-	% 	\end{equation}
-	% 	which can be explicitly written as, $\forall s \equiv l' \pmod L$,
-	% 	\begin{equation}
-	% 		\sum_l P(x_l) \frac{(t_s^\star)^{N-1} \exp{-t_s^\star/\sigma_l^2}}{\sigma_l^{2N} (N-1)!} \log \frac{P(x_l|\hat{x}_{l'+1})}{P(x_l|\hat{x}_{l'})} = 0,
-	% 		\label{eq:kkt_threshold_explicit}
-	% 	\end{equation}
-
-	% 	According to \cite{He2021}, the optimal backward channel quantizer is convex and separates each pair of posterior distribution by a hyperplane.
-	% 	It implies, for a given output letter $l'$, the sequence $\{\log {P(x_l|\hat{x}_{l'+1})}/{P(x_l|\hat{x}_{l'})}\}_{l \in \mathcal{L}}$ changes sign exactly once.
-	% 	We notice the left-hand side of \eqref{eq:kkt_threshold_explicit} is a generalized Dirichlet polynomial, and by Descartes' rule of signs \cite{Jameson2006}, has at most one positive solution.
-	% 	% TODO
-	% 	In other words, starting from $t_0^\star$, each optimal decision region requires at most one additional distinct threshold, and we have $S \le L$.
-	% 	Therefore, we conclude $S = L$ and the proof is completed.
-	% 	\qedsymbol
-	% 	\label{ap:threshold}
-	% \end{subsection}
 \end{appendix}

### 2023-08-15 main.tex
:triangular_flag_on_post: JSAC 230815

@@
 
+% page limit hacks
+% \usepackage{setspace}
+% ! \usepackage[top=1cm, bottom=1cm, left=1cm, right=1cm]{geometry}
+% \abovedisplayskip=1mm
+% \belowdisplayskip=1mm
+% \abovedisplayshortskip=1mm
+% \belowdisplayshortskip=1mm
+% \setlength{\jot}{0.1mm}
+% \setlength{\floatsep}{1mm}
+% \setlength{\textfloatsep}{1mm}
+% \setlength{\intextsep}{1mm}
+% \setlength{\skip\footins}{2mm}
+
 % amsthm
@@
 \renewcommand{\fnum@algorithm}{\fname@algorithm{} \thealgorithm:}
+\newcommand\setalgorithmcaptionfont[1]{%
+	\let\my@floatc@ruled\floatc@ruled          % save \floatc@ruled
+	\def\floatc@ruled{%
+		\global\let\floatc@ruled\my@floatc@ruled % restore \floatc@ruled
+		#1\floatc@ruled}}
 \makeatother
@@
 	To tackle this, cooperative \gls{ambc} \cite{Yang2018} employs a co-located receiver to decode both coexisting links, and the concept was further refined as \gls{sr} in Fig.~\subref*{fg:sr} \cite{Liang2020}.
-	Specifically, the active transmitter generates \gls{rf} wave carrying primary information, the passive node creates a rich-scattering environment and rides its own information, and the co-located receiver cooperatively decodes both links.
+	Specifically, the active transmitter generates \gls{rf} wave carrying primary information, the passive node creates a rich-scattering environment and superimposes its own information, and the co-located receiver cooperatively decodes both links.
 	In those \gls{bc} applications, the scatter node is considered as an \emph{information source} and the reflection pattern depends exclusively on the information symbol.
@@
 	\gls{ris} can also be used as an information source, and prototypes have been developed for \gls{psk} \cite{Tang2019a} and \gls{qam} \cite{Dai2020a}.
-	From an information-theoretic perspective, the authors of \cite{Karasik2020} reported that joint transmitter-\gls{ris} encoding achieves the capacity of \gls{ris}-aided finite-input channel, and using \gls{ris} as a naive passive beamformer to maximize the receive \gls{snr} is generally suboptimal.
+	From an information-theoretic perspective, the authors of \cite{Karasik2020} reported that joint transmitter-\gls{ris} encoding achieves the capacity of \gls{ris}-aided finite-input channel, and using \gls{ris} as a naive passive beamformer to maximize the receive \gls{snr} is generally rate-suboptimal.
 	This inspired \cite{Liu2019d,Bereyhi2020,Xu2020b,Zhang2021d,Hu2021b,Hua2022,Basar2020,Ma2020a,Yuan2021,Hu2021a} to combine passive beamforming and backscatter modulation in the overall \gls{ris} design.
@@
 	We characterize the achievable primary-(total-)backscatter rate region by optimizing the input distribution at RIScatter nodes, the active beamforming at the \gls{ap}, and the energy decision regions at the user under different \gls{qos}.
-	A \gls{bcd} algorithm is proposed where the \gls{kkt} input distribution is numerically evaluated by limit of sequences, the active beamforming is optimized by \gls{pga}, and the decision regions are refined by state-of-the-art sequential quantizer designs for \gls{dmtc}.
-	Uniquely, our optimization problem takes into account the \gls{csi}, \gls{qos}, and backscatter constellation, and the resulting input distribution is applicable to any detection scheme.
+	A \gls{bcd} algorithm is proposed where the \gls{kkt} input distribution is numerically evaluated by the converging point of a sequence, the active beamforming is optimized by \gls{pga}, and the decision regions are refined by state-of-the-art sequential quantizer designs for \gls{dmtc}.
+	Uniquely, our optimization problem takes into account the \gls{csi}, \gls{qos}, and backscatter constellation, and the resulting input distribution is applicable to other detection schemes.
 	This is also the first paper to reveal the importance of backscatter input distribution and decision region designs in active-passive coexisting networks.
@@
 			\item \gls{bc}: The scatterer is an information source with random reflection pattern over time.
-			The reflection coefficient is used merely an information codeword \cite{Thomas2012a}
+			The reflection coefficient is used merely as an information codeword \cite{Thomas2012a}
 			\begin{equation}
@@
 			\item \gls{ris}: The scatterer is a channel shaper with deterministic reflection pattern over time.
-			The reflection coefficient is used merely a passive beamforming codeword \cite{Wu2018}
+			The reflection coefficient is used merely as a passive beamforming codeword \cite{Wu2018}
 			\begin{equation}
@@
 		Denote the \gls{ap}-user direct channel as $\boldsymbol{h}_{\text{D}}^\mathsf{H} \in \mathbb{C}^{1 \times Q}$, the \gls{ap}-node $k \in \mathcal{K} \triangleq \{1,\ldots,K\}$ forward channel as $\boldsymbol{h}_{\text{F},k}^\mathsf{H} \in \mathbb{C}^{1 \times Q}$, the node $k$-user backward channel as $h_{\text{B},k}$, and the cascaded \gls{ap}-node $k$-user channel as $\boldsymbol{h}_{\text{C},k}^\mathsf{H} \triangleq h_{\text{B},k} \boldsymbol{h}_{\text{F},k}^\mathsf{H} \in \mathbb{C}^{1 \times Q}$.
-		We assume the direct and cascaded \gls{csi} are available at the \gls{ap} and user\footnote{The cascaded \gls{csi} can be estimated by sequential \cite{Bharadia2015,Yang2015b,Guo2019g} or parallel \cite{Jin2021a} approaches for dispersed nodes, or group-based \cite{Zheng2019} or hierarchical \cite{You2019} approaches for co-located nodes.}.
-
-		Let $\alpha_k = \in \mathbb{I}$ be the amplitude scattering ratio of node $k$, $x_k \in \mathcal{X} \triangleq \{c_1,\ldots,c_M\}$ be the (coded) backscatter symbol of node $k$, and $x_{\mathcal{K}} \triangleq (x_1,\ldots,x_K)$ be the backscatter symbol tuple of all nodes.
+		We assume the direct and cascaded \gls{csi} are available at the \gls{ap} and user\footnote{The cascaded \gls{csi} can be estimated by sequential \cite{Bharadia2015,Yang2015b,Guo2019g} or parallel \cite{Jin2021a} approaches for dispersed nodes, or group-based \cite{Zheng2019} or hierarchical \cite{You2019} approaches for co-located nodes.
+The impact of channel estimation error will be investigated in Section~\ref{sc:simulation_results}.}.
+
+		Let $\alpha_k \in \mathbb{I}$ be the amplitude scattering ratio of node $k$, $x_k \in \mathcal{X} \triangleq \{c_1,\ldots,c_M\}$ be the (coded) backscatter symbol of node $k$, and $x_{\mathcal{K}} \triangleq (x_1,\ldots,x_K)$ be the backscatter symbol tuple of all nodes.
 		Due to double modulation, the composite channel is a function of backscatter symbol tuple\footnote{\eqref{eq:equivalent_channel_bc} and \eqref{eq:equivalent_channel_ris} are often used in \gls{bc} and \gls{ris} literature, respectively.}
@@
 		Sort $\{\sigma_{m_{\mathcal{K}}}^2\}$ in ascending order and denote the result sequence as $\sigma_1^2,\ldots,\sigma_L^2$.
-		With sequential thresholding, the decision region of backscatter symbol tuple $l \in \mathcal{L} = \{1,\ldots,L\}$ is\footnote{$m_{\mathcal{K}}$ and $l$ are one-to-one mapped.
+		With sequential thresholding, the decision region of backscatter symbol tuple $l \in \mathcal{L} \triangleq \{1,\ldots,L\}$ is\footnote{$m_{\mathcal{K}}$ and $l$ are one-to-one mapped.
 Both notations are used interchangeably in the following context.}
@@
 	where $\rho \in \mathbb{I}$ is the \gls{qos}.
-	To obtain the achievable primary-(total-)backscatter rate region, we consider the weighted sum mutual information maximization problem with independent encoding at all nodes\footnote{Joint encoding over multiple nodes can be viewed as the special case with an augmented source.\label{fn:joint_encoding}}
+	To obtain the achievable primary-(total-)backscatter rate region, we consider the weighted sum mutual information maximization problem with independent encoding at all nodes\footnote{Joint encoding over multiple nodes can be viewed as its special case with an augmented backscatter source.\label{fn:joint_encoding}}
 	\begin{maxi!}
@@
 	Problem \eqref{op:weighted_sum_rate} generalizes \gls{bc} by allowing \gls{csi}- and \gls{qos}-adaptive input distribution and decision region design.
-	On the other hand, it also relaxes the feasible domain of discrete \gls{ris} phase shift selection problem from vertices of $M$-dimensional probability simplex to the simplex itself.
+	On the other hand, it also relaxes the feasible domain of discrete \gls{ris} phase shift selection problems from the vertices of $M$-dimensional probability simplex to the simplex itself.
 	The original problem is highly non-convex and we propose a \gls{bcd} algorithm that iteratively updates $\{\boldsymbol{p}_k\}_{k \in \mathcal{K}}$, $\boldsymbol{w}$ and $\boldsymbol{t}$.
@@
 		which involves the product term \eqref{eq:equivalent_distribution} and is generally non-convex (unless $K=1$).
-		Following \cite{Rezaeian2004}, we first recast the \gls{kkt} conditions to their equivalent forms, then propose a numerical method that guarantees those conditions on convergence of sequences.
+		Following \cite{Rezaeian2004}, we first recast the \gls{kkt} conditions to their equivalent forms, then propose a numerical solution that guarantees those conditions on the converging point of a sequence.
 		\begin{proposition}
@@
 				I_k(x_{m_k})
-				 & = \sum_{m_{\mathcal{K} \setminus \{k\}}} p(x_{m_{\mathcal{K} \setminus \{k\}}}) I(x_{m_\mathcal{K}}).
+				 & \triangleq \sum_{m_{\mathcal{K} \setminus \{k\}}} p(x_{m_{\mathcal{K} \setminus \{k\}}}) I(x_{m_\mathcal{K}}).
 				\label{eq:weighted_sum_marginal_information}
@@
 
+		\setalgorithmcaptionfont{\small}
 		\begin{algorithm}[!t]
-			\caption{\gls{kkt} Input Distribution Evaluation by Limits of Sequence}
+			\small
+			\caption{Input Distribution Evaluation by a Sequence}
 			\label{al:input_distribution}
@@
 			The insufficiency of the \gls{kkt} conditions for problem \eqref{op:input_distribution} implies that the proposed method may not converge to the global-optimal solution.
-			However, simulation results show that the average performance gap is indistinguishable at a moderate $K$.
+			However, simulation results in Section~\ref{sc:simulation_results} will show that the average performance gap is indistinguishable at a moderate $K$.
 			\label{re:input_kkt_distribution}
@@
 		The \gls{pga} active beamforming design is summarized in Algorithm \ref{al:active_beamforming}.
+		\setalgorithmcaptionfont{\small}
 		\begin{algorithm}[!t]
+			\small
 			\caption{Active Beamforming Optimization by \gls{pga}}
@@
 		Instead of solving it directly, we constrain the feasible domain from continuous space $\mathbb{R}_+^{L+1}$ to discrete candidates (i.e., fine-grained energy levels) $\mathcal{T}^{L+1}$.
-		As shown in Fig.~\ref{fg:discrete_outputs}, grouping adjacent energy bins formulates decision regions.
+		As shown in Fig.~\ref{fg:discrete_outputs}, the decision regions are formulated by grouping adjacent energy bins.
 		\begin{figure}[!t]
@@
 	We choose $\gamma_{\text{D}}=2.6$, $\gamma_{\text{F}}=2.4$, $\gamma_{\text{B}}=2$, and $\kappa_{\text{D}}=\kappa_{\text{F}}=\kappa_{\text{B}}=5$ for direct, forward and backward links.
-	The finite decision threshold domain $\mathcal{T}$ is obtained by $b$-bit uniform discretization over the critical interval defined by the confidence bounds of edge hypotheses (i.e., lower bound of $x_1$ and upper bound of $x_L$) with confidence $1-\varepsilon$.
+	The finite decision threshold domain $\mathcal{T}$ is obtained by $b$-bit uniform discretization over the critical interval defined by the $1-\varepsilon$ confidence bounds of edge hypotheses (i.e., lower bound of $x_1$ and upper bound of $x_L$).
 	We set $b=9$ and $\varepsilon=\num{e-3}$.
@@
 			\end{equation}
-			The total backscatter rate of coherent decoding approaches $K \log M$ when $N$ is sufficiently large.
-			\item \emph{\gls{ambc}:} The user decodes both links independently and semi-coherently by treating the other as interference.
+			The total backscatter rate approaches $K \log M$ when $N$ is sufficiently large.
+			\item \emph{\gls{ambc}:} The user decodes each link independently and semi-coherently while treating the other as interference.
 			The primary achievable rate is approximately\footnote{The scattered component is treated as interference with average power $\mathbb{E}\bigl\{\sum_{k} \alpha_k \boldsymbol{h}_{\text{C},k}^\mathsf{H} x_k \boldsymbol{w}s[n]\bigr\} = \sum_{k} \lvert \alpha_k \boldsymbol{h}_{\text{C},k}^\mathsf{H} \boldsymbol{w} \rvert^2$ \cite{Long2020a}.\label{fn:ambc}}
@@
 			\end{equation}
-			The total backscatter rate of coherent decoding approaches $K \log M$ when $N$ is sufficiently large.
+			The total backscatter rate approaches $K \log M$.
 			\item \emph{\gls{ris}:} The reflection pattern is deterministic and the total backscatter rate is zero.
@@
 		Fig.~\ref{fg:region_comparison} compares the typical achievable rate region/points of RIScatter and those strategies.
-		\emph{First,} we observe \gls{bbc} and \gls{sr} achieve the best backscatter performance thanks to coherent decoding.
+		\emph{First,} we observe \gls{bbc} and \gls{sr} achieve the best backscatter performance thanks to the coherent decoding.
 		For \gls{sr}, this comes with the cost of $N$ re-encoding, precoding, subtraction together with a time-domain \gls{mrc} per backscatter symbol.
+		Since \gls{sr} requires a very large $N$ to guarantee the primary rate, the signal processing cost at the receiver can be prohibitive, and the backscatter \emph{throughput} can be severely constrained.
 		\emph{Second,} the average primary rate slightly decreases/increases in the presence of a \gls{ambc}/\gls{ris} node, and the benefit of \gls{sr} is not obvious.
 		This is because the cascaded channel is around \qty{25}{dB} weaker than the direct channel.
-		Here, \gls{ris} ensures constructive superposition of direct and scattered components while \gls{sr} only creates a quasi-static rich-scattering environment that marginally enhances the average primary rate.
-		When $N$ is moderate, the randomly scattered signals should be modelled as interference rather than multipath components, and the \gls{sr} point should move towards the \gls{ambc} point.
+		Here, \gls{ris} ensures a constructive superposition of the direct and scattered components, while \gls{sr} only creates a quasi-static rich-scattering environment that marginally enhances the average primary rate.
+		When $N$ is moderate, the randomly scattered signals should be modelled as interference rather than stable multipath, and the \gls{sr} point should move vertically towards the \gls{ambc} point.
 		\emph{Third,} RIScatter enables a flexible primary-backscatter tradeoff with adaptive input distribution design.
-		In terms of maximum primary achievable rate, RIScatter coincides with \gls{ris} and outperforms the others using deterministic reflection pattern.
-		On the other hand, for a large $N$, the maximum backscatter achievable rate of RIScatter is lower than \gls{bbc} and \gls{sr} but higher than \gls{ambc}.
-		This is because both RIScatter and \gls{ambc} employ semi-coherent energy detection, and the adaptive channel coding of RIScatter outperforms the equiprobable inputs of \gls{ambc}, especially at low backscatter \gls{snr}.
-		When multiple antenna is available at the \gls{ap}, active beamforming can be optimized for RIScatter nodes and the backscatter rate gain over \gls{ambc} should be more prominent.
+		In terms of maximum primary achievable rate, RIScatter coincides with \gls{ris} and outperforms the others by using the static reflection pattern that maximizes the primary \gls{snr} all the time.
+		On the other hand, its maximum backscatter achievable rate is higher than that of \gls{ambc}.
+		This is because the adaptive channel coding of RIScatter outperforms the equiprobable inputs of \gls{ambc}, especially at the low backscatter \gls{snr} caused by double fading.
+		When multiple antenna is available at the \gls{ap}, active beamforming can be optimized for RIScatter nodes and the advantage over \gls{ambc} should be more prominent.
 	\end{subsection}
@@
 		This is inline with Shannon's observation that binary antipodal inputs is good enough for channel capacity at low \gls{snr} \cite{Shannon1948}.
-		Due to the weak scattered signal, the conditional energy \gls{pdf} under different hypotheses can be closely spaced as in Fig.~\ref{fg:energy_distribution}.
-		The extreme states producing the lowest/highest energy are always assigned with non-zero probability, while the middles cannot provide enough energy difference and thus end up unused.
-		At $\rho=1$ where the primary link is prioritized, the optimal input distribution is \num{1} at state \num{3}, since the corresponding reflection coefficient maximizes the primary \gls{snr}.
-		That is, the reflection pattern becomes deterministic and the RIScatter node boils down to a discrete \gls{ris} element.
-		Increasing $\rho$ from \num{0} to \num{1} provides a smooth transition from backscatter modulation to passive beamforming, suggesting RIScatter unifies \gls{bc} and \gls{ris} from a probabilistic perspective.
+		When the scattered signal is relatively weak, the conditional energy \gls{pdf} under different hypotheses can be closely spaced as in Fig.~\ref{fg:energy_distribution}.
+		The extreme states producing the lowest/highest energy are always assigned with non-zero probability, while the middles cannot provide enough energy diversity and end up unused.
+		At $\rho=1$ where the primary link is prioritized, the optimal input distribution is $[0, 0, 1, 0]^\mathsf{T}$ since state 3 provides higher primary \gls{snr} than other states.
+		That is, the reflection pattern becomes deterministic and the RIScatter node boils down to a static discrete \gls{ris} element.
+		Increasing $\rho$ from \num{0} to \num{1} creates a smooth transition from backscatter modulation to passive beamforming, suggesting RIScatter unifies \gls{bc} and \gls{ris} from a probabilistic perspective.
 	\end{subsection}
@@
 				\item \emph{Exhaustion:} Exhaustive search over the $M$-dimensional probability simplex with resolution $\Delta p = \num{e-2}$;
-				\item \emph{\gls{kkt}:} The \gls{kkt} solution by Algorithm \ref{al:input_distribution};
+				\item \emph{\gls{kkt}:} Solution by Algorithm \ref{al:input_distribution};
 				\item \emph{Equiprobable:} Uniform input distribution.
@@
 			Fig.~\subref*{fg:region_distribution} shows their average achievable rate regions.
-			It is observed that Cooperation achieves the outer bound of all schemes, but the backscatter rate gain comes at the cost of implementation and computation complexity.
+			Cooperation achieves the outer bound of all schemes, but joint encoding over passive devices may incur additional hardware cost.
 			Besides, the average rate performance of Exhaustion and \gls{kkt} completely coincide with each other when $K=2$.
-			This confirms Remark \ref{re:input_kkt_distribution} that the \gls{kkt} input distribution can be good enough when $K$ is not very large.
-			Equiprobable experiences minor backscatter and major primary rate losses without exploiting \gls{csi} and \gls{qos}.
-			Those gaps should be larger when $M$ or $K$ increases.
-			For the recovery methods, Marginalization provides a close performance to \gls{kkt}, but Randomization and Decomposition fail our expectations for most channel realizations.
+			This confirms Remark \ref{re:input_kkt_distribution} that the \gls{kkt} input distribution can be good enough when $K$ is moderate.
+			Equiprobable experiences minor backscatter and major primary rate losses without exploiting \gls{csi} and \gls{qos}, and those gaps should be larger when $M$ or $K$ increases.
+			Marginalization provides a close performance to \gls{kkt}, but Randomization and Decomposition fail our expectations for most channel realizations.
 			Those observations emphasize the importance of adaptive RIScatter encoding and demonstrate the advantage of the proposed \gls{kkt} input distribution design.
@@
 			\begin{itemize}
-				\item \emph{\gls{pga}:} Iterative \gls{pga} optimization by Algorithm \ref{al:active_beamforming};
+				\item \emph{\gls{pga}:} Solution by Algorithm \ref{al:active_beamforming};
 				\item \emph{E-\gls{mrt}:} \gls{mrt} towards the ergodic composite channel $\sum_{m_{\mathcal{K}}} p(x_{m_{\mathcal{K}}}) \boldsymbol{h}^\mathsf{H}(x_{m_{\mathcal{K}}})$;
@@
 			This is because the semi-coherent backscatter decoding relies on the relative energy difference under different backscatter symbol tuples.
-			Such an energy diversity is enhanced by \gls{pga}, which effectively exploits backscatter constellation and input distribution knowledge rather than simply maximizing the direct/ergodic channel strength.
+			Such an energy diversity is enhanced by \gls{pga} that effectively exploits backscatter constellation and input distribution knowledge rather than simply maximizes the channel strength.
 			As $\rho$ increases, the primary \gls{snr} outweighs the backscatter energy difference in \eqref{eq:weighted_sum_mutual_information_explicit}, and \gls{pga} beamformer approaches E-\gls{mrt}.
@@
 			The difference between E-\gls{mrt} and D-\gls{mrt} is insignificant when RIScatter nodes are dispersed.
-			Those observations prove the proposed \gls{pga} active beamforming design can exploit the \gls{csi}, \gls{qos}, and backscatter constellation to enlarge the achievable rate region.
+			Those observations confirm that the proposed \gls{pga} active beamforming design can exploit the \gls{csi}, \gls{qos}, and backscatter constellation to enlarge the achievable rate region.
 		\end{subsubsection}
@@
 		\end{figure}
-		In this study, we choose $Q=4$, $K=8$, $M=2$, $N=20$, $\sigma_v^2=\qty{-40}{dBm}$ and $r=\qty{2}{m}$ as a reference.
+		In this study, we choose $Q=4$, $K=8$, $M=2$, $N=20$, $\sigma_v^2=\qty{-40}{dBm}$ and $r=\qty{2}{m}$ as a reference, unless otherwise specified.
 		\begin{subsubsection}{Number of Nodes}
@@
 			This accounts for the significant primary rate decrease in the low-$\rho$ regime.
-			On the other hand, when the primary link is prioritized, the RIScatter nodes boil down to \gls{ris} elements and enjoy a passive array gain $K^2$.
+			On the other hand, when the primary link is prioritized, the RIScatter nodes boil down to \gls{ris} elements and enjoy a passive array gain of $K^2$.
 		\end{subsubsection}
@@
 		\begin{subsubsection}{Number of States}
-			Fig.~\subref*{fg:region_states} shows the relationship between available reflection states (i.e., \gls{qam} order) $M$ and achievable rate regions when $K=1$.
+			Fig.~\subref*{fg:region_states} shows the relationship between the available reflection states (i.e., \gls{qam} order) $M$ and the achievable rate region when $K=1$.
 			We notice that increasing the reflection states has a marginal effect on the primary rate but significantly improves the backscatter rate.
 			This is because the maximum amplitude normalized-\gls{qam} \eqref{eq:backscatter_modulation} involves more weak reflection points as $M$ increases.
-			It greatly enhances the receive energy difference but cannot provide enough phase shift resolution with strong reflection.
+			It enhances the receive energy diversity but cannot provide enough phase shift resolution with maximum reflection.
 		\end{subsubsection}
@@
 			Fig.~\subref*{fg:region_txs} illustrates the impact of transmit antennas $Q$ on the average performance.
-			As $Q$ increases, more scattered paths are available to \gls{pga} and the channel diversity can be further exploited to enhance the primary \gls{snr} and backscatter energy difference.
+			As $Q$ increases, more scattered paths become available and the channel diversity can be better exploited to improve the primary-backscatter tradeoff.
 			It emphasizes the importance of multi-antenna RIScatter systems and demonstrate the effectiveness of the proposed \gls{pga} design.
@@
 			Fig.~\subref*{fg:region_duration} shows how the spreading factor $N$ affects the achievable rate region.\footnote{Here, the unit of total backscatter rate is bits per primary block to show backscatter throughput.}
-			Using a very large $N$ can severely constrain the backscatter throughput, since the gain in energy certainty (by law of large numbers) cannot withstand the loss in gross rate.
+			Using a very large $N$ (as in the case of \gls{sr}) can severely constrain the backscatter throughput, since the gain in energy certainty (by the law of large numbers) cannot withstand the loss in the gross rate.
 			As $N \to \infty$, RIScatter nodes boil down to static \gls{ris} elements and the total backscatter rate approaches \num{0}.
-			On the other hand, when $N$ is too small, energy detection is error-prone as the \gls{dmmac} \eqref{eq:dmmac} becomes unreliable.
+			On the other hand, when $N$ is too small, the \gls{dmmac} \eqref{eq:dmmac} becomes unreliable and energy detection is error-prone.
 			It explains the observation that $N=10$ provides lower backscatter throughput than $N=20$.
@@
 			When $\iota$ increases from \num{0} to \num{0.2}, the maximum total backscatter rate decreases by \qty{20}{\percent}.
-			This is because the energy detector is sensitive to the \gls{dmmac} \eqref{eq:dmmac} and thus $\hat{\boldsymbol{h}}_{\text{C},k}$.
-			On the other hand, a small estimation error may be insufficient to change the optimal passive beamforming state (especially for a small $M$) and the primary rate is almost unchanged in this case.
+			This is because the energy detector is sensitive to the \gls{dmmac} \eqref{eq:dmmac} and thus the estimation of the cascaded channel.
+			On the other hand, a small estimation error may be insufficient to change the optimal passive beamforming state and the primary rate is almost unchanged.
 		\end{subsubsection}
@@
 		\begin{equation}
-			I(x_{\mathcal{K}}) + \sum_k \nu_k \biggl( \sum_{m_k} p(x_{m_k}) - 1 \biggr) + \sum_k \sum_{m_k} \lambda_{m_k} p(x_{m_k}),
+			L(p, \nu, \lambda) = I(x_{\mathcal{K}}) + \sum_k \nu_k \Bigl( \sum_{m_k} p(x_{m_k}) - 1 \Bigr) + \sum_{k,m_k} \lambda_{m_k} p(x_{m_k}),
 		\end{equation}
@@
 
-		Next, we prove any converging point of sequence \eqref{eq:input_kkt_solution}, denoted as $p^\star(x_{m_k})$, fulfills \gls{kkt} conditions \eqref{eq:input_kkt_condition}.
+		Next, we prove any converging point of sequence \eqref{eq:input_kkt_solution}, denoted as $p^\star(x_{m_k})$, fulfills the \gls{kkt} conditions \eqref{eq:input_kkt_condition}.
 		Let
@@
 		\begin{equation}
-			I_k^\star(x_{m_k}) = \frac{1 - \rho}{\rho} \log \sum_{m_k'} p^\star(x_{m_k'}) \exp \Bigl( \frac{\rho}{1 - \rho} I_k^\star(x_{m_k'}) \Bigr),
+			I_k^\star(x_{m_k}) = \frac{1 - \rho}{\rho} \log \sum_{m_k'} p^\star(x_{m_k'}) \exp \Bigl( \frac{\rho}{1 - \rho} I_k^\star(x_{m_k'}) \Bigr).
 		\end{equation}

### 2023-08-19 misc/abstract.tex
:speech_balloon: Add extended abstract

--- 2023-08-15 arxiv.tex
@@
 \usepackage{tikz}
+\usepackage{float}
 
@@
 \begin{abstract}
-	\gls{bc} nodes harvest energy from and modulate information over external electromagnetic waves.
-	\gls{ris} adapts its phase shift response to alter channel strength in specific directions.
-	In this paper, we show how those two seemingly different technologies (and their derivatives) can be unified into one architecture called RIScatter.
-	RIScatter consists of dispersed or co-located scatter nodes, whose reflection states are adapted to partially modulate their information and partially engineer the wireless channel.
+	We propose RIScatter as a novel protocol that unifies \gls{bc} and \gls{ris} from a probabilistic perspective.
+	In particular, batteryless scatter nodes powered by ambient transmission partially modulate their information and partially engineer the wireless channel.
 	The key is to render the probability distribution of reflection states as a joint function of the information source, \gls{csi}, and relative priority of coexisting links.
-	This enables RIScatter to softly bridge \gls{bc} and \gls{ris}; reduce to either under specific setup; or evolve in a mixed form for heterogeneous traffic control and universal hardware design.
-	We also propose a low-complexity \gls{sic}-free receiver that exploits the properties of RIScatter.
-	For a single-user multi-node network, we characterize the achievable primary-(total-)backscatter rate region by optimizing the input distribution at scatter nodes, the active beamforming at the \gls{ap}, and the energy decision regions at the user.
-	Simulations demonstrate RIScatter nodes can recycle surrounding radios for backscatter modulation and passive beamforming.
 \end{abstract}
@@
 \begin{IEEEkeywords}
-	Backscatter communication, reconfigurable intelligent surface, active-passive coexisting network, input distribution design, \gls{sic}-free receiver.
+	Active-passive coexisting network, input distribution design, \gls{sic}-free receiver.
 \end{IEEEkeywords}
@@
 	\label{sc:introduction}
-	\IEEEPARstart{F}{uture} wireless network is envisioned to provide high throughput, uniform coverage, pervasive connectivity, heterogeneous control, and cognitive intelligence for trillions of low-power devices.
-	\gls{bc} separates a transmitter into a \gls{rf} carrier emitter with power-hungry elements (e.g., synthesizer and amplifier) and an information-bearing node with power-efficient components (e.g., harvester and modulator) \cite{Boyer2014}.
-	The receiver (reader) can be either co-located or separated with the carrier emitter, known as \gls{mbc} and \gls{bbc} in Fig.~\subref*{fg:mbc} and \subref*{fg:bbc}, respectively.
-	Relevant applications such as \gls{rfid} \cite{Dobkin2012,Landt2005} and passive sensor network \cite{Vannucci2008,Assimonis2016} have been extensively researched, standardized, and commercialized to embrace the \gls{ioe}.
-	However, conventional backscatter nodes only respond when externally inquired by a nearby reader.
-	\gls{ambc} in Fig.~\subref*{fg:ambc} was proposed a decade ago where battery-free nodes recycle ambient signals (e.g., radio, television and Wi-Fi) to harvest energy and establish connections \cite{Liu2013b}.
-	It does not require dedicated power source, carrier emitter, or frequency spectrum, but the backscatter decoding is subject to the strong interference from the primary (legacy) link.
-	To tackle this, cooperative \gls{ambc} \cite{Yang2018} employs a co-located receiver to decode both coexisting links, and the concept was further refined as \gls{sr} in Fig.~\subref*{fg:sr} \cite{Liang2020}.
-	Specifically, the active transmitter generates \gls{rf} wave carrying primary information, the passive node creates a rich-scattering environment and superimposes its own information, and the co-located receiver cooperatively decodes both links.
-	In those \gls{bc} applications, the scatter node is considered as an \emph{information source} and the reflection pattern depends exclusively on the information symbol.
-	On the other hand, \gls{ris} in Fig.~\subref*{fg:ris} is a smart signal reflector with numerous passive elements of adjustable phase shifts.
-	It customizes the wireless environment for signal enhancement, interference suppression, scattering enrichment, and/or non-line-of-sight bypassing \cite{Wu2021b}.
-	Each \gls{ris} element is considered as a \emph{channel shaper} and the reflection pattern depends exclusively on the \gls{csi}.
-
-	As a special case of \gls{cr}, active and passive transmissions coexist and interplay in \gls{ambc} and \gls{sr}.
-	Such a coexistence is classified into commensal (overlay), parasitic (underlay), and competitive (interfering) paradigms, and their achievable rate and outage performance were investigated in \cite{Guo2019b,Ding2020}.
-	The achievable rate and optimal input distribution for binary-input \gls{ambc} are investigated in \cite{Qian2019b}, but its impact on the primary link is omitted.
-	% For binary-input \gls{ambc},  are investigated in \cite{Qian2019b}, but the authors did not consider its impact on the primary link.
-	% The \gls{ber} performance of \gls{ml}, linear, and \gls{sic} receivers are derived over flat fading channels \cite{Yang2018}.
-	% The authors of \cite{Hassani2023} analyzed the energy efficiency and achievable rate region for an \gls{ambc}-aided multi-user downlink \gls{noma} system.
-	In \cite{Hassani2023}, the authors analyzed the energy efficiency and achievable rate region for an \gls{ambc}-aided multi-user downlink \gls{noma} system.
-	However, they assumed equal symbol duration and perfect synchronization for the coexisting links.
-	Importantly, active-passive coexisting networks have three special and important properties:
-	\begin{enumerate}
-		\item Primary and backscatter symbols are superimposed by \emph{double modulation} (i.e., multiplication coding);
-		\item Backscatter signal strength is much weaker than primary due to \emph{double fading};
-		\item The spreading factor (i.e., backscatter symbol duration over primary) is usually large\footnote{The load-switching interval of low-power backscatter modulators is usually \num{0.1} to \qty{10}{\us} \cite{Torres2021}, accounting for a typical spreading factor between \num{10} and \num{e3}.}.
-	\end{enumerate}
-	The second property motivated \cite{Long2020a,Liang2020,Guo2019b,Ding2020,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Yang2018,Han2021,Zhang2022,Dai2023} to view \gls{sr} as a multiplicative \gls{noma} and perform \gls{sic} from primary to backscatter link.
-	During primary decoding, the backscatter signal can be modelled as channel uncertainty or multiplicative interference, when the spreading factor is large or small.
-	Decoding each backscatter symbol also requires multiple \gls{sic} followed by a \gls{mrc} over primary blocks, which is operation-intensive and \gls{csi}-sensitive.
-	Under those assumptions, the achievable rate region of cell-free \gls{sr} is characterized in \cite{Dai2023}.
-	When the spreading factor is sufficiently large, the primary achievable rate under semi-coherent detection\footnote{In this paper, semi-coherent detection refers to the primary/backscatter decoding with known \gls{csi} and unknown backscatter/primary symbols.} asymptotically approaches its coherent counterpart such that both links are approximately interference-free \cite{Long2020a}.
-	However, this assumption severely limits the backscatter throughput.
-
-	\begin{figure}[!t]
-		\centering
-		\subfloat[\gls{mbc}]{
-			\resizebox{0.48\linewidth}{!}{
-				\input{assets/illustration/mbc.tex}
-			}
-			\label{fg:mbc}
-		}
-		\subfloat[\gls{bbc}]{
-			\resizebox{0.48\linewidth}{!}{
-				\input{assets/illustration/bbc.tex}
-			}
-			\label{fg:bbc}
-		}
-		\\
-		\subfloat[\gls{ambc}]{
-			\resizebox{0.48\linewidth}{!}{
-				\input{assets/illustration/ambc.tex}
-			}
-			\label{fg:ambc}
-		}
-		\subfloat[\gls{sr}]{
-			\resizebox{0.48\linewidth}{!}{
-				\input{assets/illustration/sr.tex}
-			}
-			\label{fg:sr}
-		}
-		\\
-		\subfloat[\gls{ris}]{
-			\resizebox{0.48\linewidth}{!}{
-				\input{assets/illustration/ris.tex}
-			}
-			\label{fg:ris}
-		}
-		\subfloat[RIScatter]{
-			\resizebox{0.48\linewidth}{!}{
-				\input{assets/illustration/riscatter.tex}
-			}
-			\label{fg:riscatter}
-		}
-		\caption{
-			Illustration of scattering applications.
-			The blue flow(s) constitutes the primary link while the magenta/green flow denotes the backscatter link.
-		}
-		\label{fg:scatter_illustration}
-	\end{figure}
-
-	\begin{table*}[!t]
-		\caption{Comparison of Scattering Applications}
-		\label{tb:scattering_applications}
-		\rowcolors{2}{gray!25}{white}
-		\renewcommand{\arraystretch}{1.4}
-		\begin{tabularx}{\textwidth}{CCCCCC}
-			\toprule
-			\hiderowcolors
-			                                       & \glsentryshort{mbc}/\glsentryshort{bbc} & \glsentryshort{ambc}        & \glsentryshort{sr} (large spreading factor)                         & \glsentryshort{ris} & RIScatter                                                          \\ \midrule
-			\showrowcolors
-			Information link(s)                    & Backscatter                             & Coexisting                  & Coexisting                                                          & Primary             & Coexisting                                                         \\
-			Primary signal on backscatter decoding & Carrier                                 & Multiplicative interference & Spreading code                                                      & ---                 & Energy uncertainty                                                 \\
-			Backscatter signal on primary decoding & ---                                     & Multiplicative interference & \glsentryshort{csi} uncertainty                                     & Passive beamforming & Dynamic passive beamforming                                        \\
-			Cooperative devices                    & ---                                     & No                          & Primary transmitter and co-located receiver                         & ---                 & Primary transmitter, scatter nodes, and co-located receiver        \\
-			Sequential decoding                    & ---                                     & No                          & Primary-to-backscatter, \glsentryshort{sic} and \glsentryshort{mrc} & ---                 & Backscatter-to-primary, no \glsentryshort{sic}/\glsentryshort{mrc} \\
-			Reflection pattern depends on          & Information source                      & Information source          & Information source                                                  & \glsentryshort{csi} & Information source, \glsentryshort{csi}, and \glsentryshort{qos}   \\
-			Reflection state distribution          & Equiprobable                            & Equiprobable                & Equiprobable or Gaussian                                            & Degenerate          & Flexible                                                           \\
-			Load-switching speed                   & Fast                                    & Slow                        & Slow                                                                & Quasi-static        & Arbitrary                                                          \\ \bottomrule
-		\end{tabularx}
-	\end{table*}
-
-	On the other hand, static \gls{ris} that employs fixed reflection pattern per channel block has been extensively studied in wireless communication, sensing, and power literature \cite{Wu2018,Zhang2019a,Lin2022,Liu2022,Feng2022,Zhao2022}.
-	Dynamic \gls{ris} performs time sharing between different phase shifts and introduces artificial channel diversity within each channel block.
-	The idea was first proposed to fine-tune the \gls{ofdm} resource blocks \cite{Yang2020}, then extended to the downlink power and uplink information phases of \gls{wpcn} \cite{Wu2021,Wu2021d,Hua2022a}.
-	However, dynamic \gls{ris} carries no information because the reflection state at a specific time is known to the receiver.
-	\gls{ris} can also be used as an information source, and prototypes have been developed for \gls{psk} \cite{Tang2019a} and \gls{qam} \cite{Dai2020a}.
-	From an information-theoretic perspective, the authors of \cite{Karasik2020} reported that joint transmitter-\gls{ris} encoding achieves the capacity of \gls{ris}-aided finite-input channel, and using \gls{ris} as a naive passive beamformer to maximize the receive \gls{snr} is generally rate-suboptimal.
-	This inspired \cite{Liu2019d,Bereyhi2020,Xu2020b,Zhang2021d,Hu2021b,Hua2022,Basar2020,Ma2020a,Yuan2021,Hu2021a} to combine passive beamforming and backscatter modulation in the overall \gls{ris} design.
-	In particular, \emph{symbol level precoding} maps the information symbols to the optimized \gls{ris} coefficient sets \cite{Liu2019d,Bereyhi2020}, \emph{overlay modulation} superposes the information symbols over a common auxiliary matrix \cite{Xu2020b,Zhang2021d,Hu2021b,Hua2022}, \emph{spatial modulation} switches between the reflection coefficient sets that maximize \gls{snr} at different receive antennas \cite{Basar2020,Ma2020a,Yuan2021}, and \emph{index modulation} employs dedicated reflection elements (resp.
-information elements) for passive beamforming (resp.
-backscatter modulation) \cite{Hu2021a}.
-	Those \gls{ris}-based backscatter modulation schemes incur advanced hardware architecture and high optimization complexity.
-	In contrast, \cite{Vardakis2023} exploits commodity \gls{rfid} tags, powered and controlled by a software-defined radio reader at a different frequency, to perform passive beamforming (but no backscatter modulation) towards a legacy user.
-\label{cm:2.5}
-	% The authors demonstrated the feasibility of using batteryless devices to adaptively enhance the \gls{snr} of a primary link, but did not consider backscatter modulation at.
-	Most relevant literature considers either Gaussian codebook \cite{Guo2019b,Ding2020,Long2020a,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Hu2021b} that is impractical for low-power nodes, or finite equiprobable inputs \cite{Yang2018,Liang2020,Han2021,Zhang2022,Liu2019d,Bereyhi2020,Xu2020b,Zhang2021d,Hua2022,Basar2020,Ma2020a,Yuan2021,Hu2021a} that does not fully exploit the \gls{csi} and properties of active-passive coexisting networks.
-	Those problems are addressed in this paper and the contributions are summarized below.
-
-	\emph{First,} we propose RIScatter as a novel protocol that unifies \gls{bc} and \gls{ris} by adaptive reflection state (backscatter input) distribution design.
-	The concept is shown in Fig.~\subref*{fg:riscatter}, where one or more RIScatter nodes ride over an active transmission to simultaneously modulate their information and engineer the wireless channel.
-	A co-located receiver cooperatively decodes both coexisting links.
-	Each reflection state is simultaneously an information codeword and a passive beamforming codeword.
-	The reflection pattern over time is semi-random and guided by the input probability assigned to each state.
-	This probability distribution is carefully designed to incorporate the backscatter information, \gls{csi}, and \gls{qos}\footnote{\gls{qos} refers to the relative priority of the primary link.\label{fn:qos}}.
-	Such an adaptive channel coding boils down to the degenerate distribution of \gls{ris} when the primary link is prioritized, and outperforms the uniform distribution of \gls{bc} (by accounting the \gls{csi}) when the backscatter link is prioritized.
-	Table~\ref{tb:scattering_applications} compares RIScatter to \gls{bc} and \gls{ris}.
-	However, two major challenges for RIScatter are the receiver design and input distribution design.
-	This is the first paper to unify \gls{bc} and \gls{ris} from the perspective of input distribution.
-
-	\emph{Second,} we address the first challenge and propose a low-complexity \gls{sic}-free receiver.
-	It semi-coherently decodes the weak backscatter signal using an energy detector, re-encodes for the exact reflection pattern, then coherently decodes the primary link.
-	Thanks to double modulation, backscatter detection can be viewed as part of channel training, and the impact of backscatter modulation can be modelled as dynamic passive beamforming afterwards.
-	The proposed receiver may be built over legacy receivers with minor hardware upgrade, as it only requires one additional energy comparison and re-encoding per backscatter symbol (instead of primary symbol).
-	The energy detector can also be tailored for arbitrary input distribution and spreading factor to increase backscatter throughput.
-	This is the first paper to propose a \gls{sic}-free cooperative receiver for active-passive coexisting networks.
-
-	\emph{Third,} we address the second challenge in a single-user multi-node \gls{miso} scenario.
-	We characterize the achievable primary-(total-)backscatter rate region by optimizing the input distribution at RIScatter nodes, the active beamforming at the \gls{ap}, and the energy decision regions at the user under different \gls{qos}.
-	A \gls{bcd} algorithm is proposed where the \gls{kkt} input distribution is numerically evaluated by the converging point of a sequence, the active beamforming is optimized by \gls{pga}, and the decision regions are refined by state-of-the-art sequential quantizer designs for \gls{dmtc}.
-	Uniquely, our optimization problem takes into account the \gls{csi}, \gls{qos}, and backscatter constellation, and the resulting input distribution is applicable to other detection schemes.
-	This is also the first paper to reveal the importance of backscatter input distribution and decision region designs in active-passive coexisting networks.
-
-	% \emph{Fourth,} we provide numerical results to demonstrate the benefits of RIScatter and proposed algorithms.
-	% The observations include:
-	% 1) adaptive reflection state distribution design can flexibly shift between backscatter modulation and passive beamforming;
-	% 2) when the primary link is prioritized, input distribution becomes degenerate and RIScatter nodes coincide with discrete \gls{ris};
-	% 3) when the backscatter link is prioritized, adaptive RIScatter encoding achieves higher backscatter rate than conventional line-coded \gls{bc} with equiprobable inputs;
-	% 4) co-located RIScatter nodes can further leverage total backscatter rate by joint encoding;
-	% 5) the proposed receiver maintains the passive beamforming benefit and provides comparable backscatter rate to \gls{sic}-based \gls{sr}, with re-encoding costs reduced to $1/N$ and no re-precoding/cancellation;
-	% 6) it also supports scatter nodes with faster load-switching speed for potentially higher throughput;
-	% 7) \gls{pga} active beamformer effectively increases the primary (resp.
-backscatter) rate by boosting the receive \gls{snr} (resp.
-widening the energy gap under different reflection states), and can smoothly transition in between under different \gls{qos};
-	% 8) distribution-aware backscatter detectors provide higher backscatter rate than the conventional \gls{ml} detector.
-	% \end{subsection}
-
-	\emph{Notations:}
-	Italic, bold lower-case, and bold upper-case letters denote scalars, vectors and matrices, respectively.
-	$\boldsymbol{0}$ and $\boldsymbol{1}$ denote zero and one array of appropriate size, respectively.
-$\mathbb{I}^{x \times y}$, $\mathbb{R}_+^{x \times y}$, and $\mathbb{C}^{x \times y}$ denote the unit, real nonnegative, and complex spaces of dimension $x \times y$, respectively.
-	$j$ denotes the imaginary unit.
-	$\mathrm{diag}(\cdot)$ returns a square matrix with the input vector on its main diagonal and zeros elsewhere.
-	$\mathrm{card}(\cdot)$ returns the cardinality of a set.
-	$\log(\cdot)$ denotes logarithm of base $e$.
-	$(\cdot)^*$, $(\cdot)^\mathsf{T}$, $(\cdot)^\mathsf{H}$, $\lvert{\cdot}\rvert$, and $\lVert{\cdot}\rVert$ denote the conjugate, transpose, conjugate transpose (Hermitian), absolute value, and Euclidean norm operators, respectively.
-	$(\cdot)^{(r)}$ and $(\cdot)^{\star}$ denote the $r$-th iterated and optimal results, respectively.
-	The distribution of a \gls{cscg} random variable with zero mean and variance $\sigma^2$ is denoted by $\mathcal{CN}(0,\sigma^2)$, and $\sim$ means ``distributed as''.
+	\gls{ambc} has been recognized as a promising technology that allows low-power devices to charge and communicate wirelessly by recycling ambient radio waves \cite{Liu2013b}.
+	The idea was extended to \gls{sr} where the legacy transmitter and passive node are cooperatively decoded by a co-located receiver \cite{Liang2020}.
+	On the other hand, \gls{ris} is a passive signal reflector that customizes the wireless environment for signal enhancement, interference suppression, etc \cite{Wu2021b}.
+	Those concepts essentially exploit the same physical mechanism of RF wave scattering/reflecting, but for different aims (backscatter modulation and passive beamforming).
 \end{section}
@@
 	\label{sc:riscatter}
-	\begin{subsection}{Principles}
-		\label{sc:principles}
-		\gls{rf} wave scattering or reflecting are often manipulated by passive antennas or programmable metamaterial \cite{Liang2022}.
-		The former receives the impinging signals and reradiates some back to the space, while the latter reflects at the space-cell boundary and mainly applies a phase shift.
-		In the scattered signal, the structural mode component depends on the scatterer geometry and material.
-		Its impact is usually modelled as part of environment multipath \cite{Thomas2012,Liang2020}, or simply a baseband \gls{dc} offset when the impinging signal is a \gls{cw} \cite{Boyer2014}.
-		On the other hand, the antenna mode component depends on the impedance mismatch and is widely exploited in scattering applications.
-		For an antenna (resp. metamaterial) scatterer with $M$ reflection states, the reflection coefficient at state $m \in \mathcal{M} \triangleq \{1,\ldots,M\}$ is \cite{VanHuynh2017,Liang2022}
-		\begin{equation}
-			\Gamma_m = \frac{Z_m - Z^*}{Z_m + Z},
-			\label{eq:reflection_coefficient}
-		\end{equation}
-		where $Z_m$ is the antenna load (resp. metamaterial cell) impedance at state $m$, and $Z$ is the antenna input (resp. medium characteristic) impedance.
-		Specifically,
-		\begin{itemize}
-			\item \gls{bc}: The scatterer is an information source with random reflection pattern over time.
-			The reflection coefficient is used merely as an information codeword \cite{Thomas2012a}
-			\begin{equation}
-				\Gamma_m = \alpha_m \frac{c_m}{\max_{m'} \lvert c_{m'} \rvert},
-				\label{eq:backscatter_modulation}
-			\end{equation}
-			where $\alpha_m \in \mathbb{I}$ is the amplitude scattering ratio at state $m$, and $c_m$ is the corresponding constellation point.
-			\item \gls{ris}: The scatterer is a channel shaper with deterministic reflection pattern over time.
-			The reflection coefficient is used merely as a passive beamforming codeword \cite{Wu2018}
-			\begin{equation}
-				\Gamma_m = \alpha_m \exp(j \theta_m),
-				\label{eq:passive_beamforming}
-			\end{equation}
-			where $\theta_m$ is the phase shift at state $m$.\footnote{Most papers assume $\alpha_m = \alpha$, with $\alpha \ll 1$ for \gls{bc} and $\alpha=1$ for \gls{ris}.\label{fn:scattering_ratio}}
-		\end{itemize}
+	For passive RIScatter nodes, each reflection state is simultaneously an information codeword and a passive beamforming codeword.
+	The nodes randomize the reflection pattern over time while still guaranteeing the probability of occurrence of each state.
+	This probability distribution is carefully designed to incorporate the backscatter information, \gls{csi}, and relative priority of both coexisting links.
 
-		RIScatter generalizes \gls{bc} and \gls{ris} from a probabilistic perspective.
-		Each reflection coefficient simultaneously acts as an information codeword and a passive beamforming codeword.
-		As shown in Fig.~\ref{fg:scatter_comparison}, the reflection pattern of each RIScatter node over time is semi-random and guided by the input probability assigned to each state.
-		This probability distribution is carefully designed to incorporate the backscatter information, \gls{csi}, and \gls{qos}, in order to strike a balance between backscatter modulation and passive beamforming.
-		\begin{figure}[!t]
+	We also propose a low-complexity sequential decoding scheme that is readily applicable to legacy receivers.
+	It semi-coherently decodes the weak backscatter signal using an energy detector, re-encodes for the exact reflection pattern, then coherently decodes the primary link.
+	Therefore, backscatter detection can be viewed as part of channel training, and the impact of backscatter modulation can be modelled as dynamic passive beamforming.
+	It only requires one additional energy comparison and re-encoding per backscatter symbol (instead of primary symbol), and can be tailored for arbitrary input distribution and spreading factor.
+
+	In a single-user multi-node \gls{miso} RIScatter network, we characterize the achievable primary-(total-)backscatter rate region by optimizing the input distribution at RIScatter nodes, the active beamforming at the \gls{ap}, and the energy decision regions at the user under different \gls{qos}.
+	Uniquely, our optimization problem takes into account the \gls{csi}, \gls{qos}, and backscatter constellation.
+	This is the first proposal to reveal the importance of backscatter input distribution and decision region designs in active-passive coexisting networks.
+\end{section}
+
+\begin{section}{Results}
+	\label{sc:simulation_results}
+	\begin{figure}[H]
 		\centering
-			\subfloat[Input Distribution]{
-				\resizebox{0.8\columnwidth}{!}{
-					\input{assets/illustration/input_distribution.tex}
+		\subfloat[Input distribution: illustration]{
+			\resizebox{0.7\columnwidth}{!}{
+				\input{../assets/illustration/input_distribution.tex}
 			}
-				\label{fg:input_distribution}
+			\label{fg:input_distribution_illustration}
 		}
 		\\
-			\subfloat[Reflection Pattern]{
-				\resizebox{0.8\columnwidth}{!}{
-					\input{assets/illustration/time_structure.tex}
+		\subfloat[Input distribution: simulation]{
+			\resizebox{0.7\columnwidth}{!}{
+				\input{../assets/simulation/distribution_weights.tex}
 			}
-				\label{fg:time_structure}
+			\label{fg:input_distribution_simulation}
 		}
-			\caption{
-				Input distribution and reflection pattern of scattering applications.
-				``PB'', ``BB'', and ``CB'' refer to primary symbol block, backscatter symbol block, and channel block, respectively.
-				Shadowing means presence of primary link.
-				In this example, the optimal passive beamformer corresponds to state \num{2}.
-				The spreading factor is \num{4} for RIScatter and \num{8} for \gls{ambc}/\gls{sr}.
-				\gls{bc} and \gls{ris} can be viewed as extreme cases of RIScatter, where the input distribution boils down to uniform and degenerate, respectively.
-			}
-			\label{fg:scatter_comparison}
+		\caption{\gls{bc} and \gls{ris} can be viewed as extreme cases of RIScatter, where the input distribution boils down to uniform and degenerate. $\rho$ is the relative priority of the primary link.}
 	\end{figure}
-		\begin{remark}
-			Unlike dynamic \gls{ris} that simply performs a time sharing between reflection states, RIScatter conveys additional information by randomizing the reflection pattern over time while still guaranteeing the probability of occurrence of each state.
-			Upon successful backscatter detection, the impact of RIScatter nodes on the primary link can be modelled as dynamic passive beamforming.
-			\label{re:dynamic_passive_beamforming}
-		\end{remark}
-
-		RIScatter nodes can be implemented, for example, by adding an integrated receiver\footnote{The aim is to coordinate the node with the active source and to acquire the optimized input distribution, instead of decoding the primary information dedicated for the user.
-The node receiver can be implemented using simple circuits or even integrated with the rectifier \cite{Kim2021a} to reduce cost and complexity.\label{fn:integrated_receiver}} \cite{Kim2021a} and adaptive encoder \cite{He2020e} to off-the-shelf passive \gls{rfid} tags.
-		The block diagram, equivalent circuit, and scatter model are illustrated in Fig.~\ref{fg:riscatter_node}.
-		\begin{figure*}[!t]
-			\centering
-			\subfloat[Block Diagram]{
-				\resizebox{0.32\linewidth}{!}{
-					\input{assets/illustration/block_diagram.tex}
-				}
-				\label{fg:block_diagram}
-			}
-			\subfloat[Equivalent Circuit]{
-				\resizebox{0.37\linewidth}{!}{
-					\input{assets/illustration/equivalent_circuit.tex}
-				}
-				\label{fg:equivalent_circuit}
-			}
-			\subfloat[Scatter Model]{
-				\resizebox{0.28\linewidth}{!}{
-					\input{assets/illustration/scatter_model.tex}
-				}
-				\label{fg:scatter_model}
-			}
-			\caption{
-			Block diagram, equivalent circuit, and scatter model of a RIScatter node.
-			The solid and dashed vectors represent signal and energy flows.
-			The scatter antenna behaves as a constant power source, where the voltage $V_0$ and current $I_0$ are introduced by incident electric field $\vec{E}_{\text{I}}$ and magnetic field $\vec{H}_{\text{I}}$ \cite{Huang2021}.
-			}
-			\label{fg:riscatter_node}
-		\end{figure*}
-		% To exploit the benefits of RIScatter, we also propose a low-complexity receiver that semi-coherently decodes the backscatter link, re-encodes to recover the reflection pattern, and coherently decodes the primary link.
-		% The detail will be covered in Section~\ref{st:system_model}.
-	\end{subsection}
-
-	\begin{subsection}{System Model}
-		\label{sc:system_model}
-		\begin{figure}[!t]
-			\centering
-			\def\svgwidth{0.7\columnwidth}
-			\footnotesize{
-				\import{assets/illustration/}{riscatter_network.pdf_tex}
-			}
-			\caption{A single-user multi-node RIScatter network.}
-			\label{fg:riscatter_network}
-		\end{figure}
-		As shown in Fig.~\ref{fg:riscatter_network}, we consider a RIScatter network where a $Q$-antenna \gls{ap} serves a single-antenna user and $K$ nearby dispersed or co-located RIScatter nodes.
-		Without loss of generality, we assume all nodes have $M$ available reflection states.
-		In the primary point-to-point system, the \gls{ap} transmits information to the user over a multipath channel\footnote{It is assumed the primary symbol duration is much longer than multipath delay spread (i.e., no inter-symbol interference).} enhanced by RIScatter nodes.
-		In the backscatter multiple access system, the \gls{ap} acts as a carrier emitter, the RIScatter nodes modulate over the scattered signal, and the user jointly decodes all nodes.\footnote{It is assumed the signal going through two or more RIScatter nodes is too weak to be received by the user.}
-		For simplicity, we consider a quasi-static block fading model and focus on a specific channel block where the \gls{csi} remains constant.
-		Denote the \gls{ap}-user direct channel as $\boldsymbol{h}_{\text{D}}^\mathsf{H} \in \mathbb{C}^{1 \times Q}$, the \gls{ap}-node $k \in \mathcal{K} \triangleq \{1,\ldots,K\}$ forward channel as $\boldsymbol{h}_{\text{F},k}^\mathsf{H} \in \mathbb{C}^{1 \times Q}$, the node $k$-user backward channel as $h_{\text{B},k}$, and the cascaded \gls{ap}-node $k$-user channel as $\boldsymbol{h}_{\text{C},k}^\mathsf{H} \triangleq h_{\text{B},k} \boldsymbol{h}_{\text{F},k}^\mathsf{H} \in \mathbb{C}^{1 \times Q}$.
-		We assume the direct and cascaded \gls{csi} are available at the \gls{ap} and user\footnote{The cascaded \gls{csi} can be estimated by sequential \cite{Bharadia2015,Yang2015b,Guo2019g} or parallel \cite{Jin2021a} approaches for dispersed nodes, or group-based \cite{Zheng2019} or hierarchical \cite{You2019} approaches for co-located nodes.
-The impact of channel estimation error will be investigated in Section~\ref{sc:simulation_results}.}.
-
-		Let $\alpha_k \in \mathbb{I}$ be the amplitude scattering ratio of node $k$, $x_k \in \mathcal{X} \triangleq \{c_1,\ldots,c_M\}$ be the (coded) backscatter symbol of node $k$, and $x_{\mathcal{K}} \triangleq (x_1,\ldots,x_K)$ be the backscatter symbol tuple of all nodes.
-		Due to double modulation, the composite channel is a function of backscatter symbol tuple\footnote{\eqref{eq:equivalent_channel_bc} and \eqref{eq:equivalent_channel_ris} are often used in \gls{bc} and \gls{ris} literature, respectively.}
-		\begin{subequations}
-			\label{eq:equivalent_channel}
-			\begin{align}
-				\boldsymbol{h}^\mathsf{H}(x_{\mathcal{K}})
-				 & \triangleq \boldsymbol{h}_{\text{D}}^\mathsf{H} + \sum_{k} \alpha_k \boldsymbol{h}_{\text{C},k}^\mathsf{H} x_k \label{eq:equivalent_channel_bc}                    \\
-				 & = \boldsymbol{h}_{\text{D}}^\mathsf{H} + \boldsymbol{x}^\mathsf{H} \mathrm{diag}(\boldsymbol{\alpha}) \boldsymbol{H}_{\text{C}}, \label{eq:equivalent_channel_ris}
-			\end{align}
-		\end{subequations}
-		where $\boldsymbol{\alpha} \triangleq [\alpha_1,\ldots,\alpha_K]^\mathsf{T} \in \mathbb{I}^{K}$, $\boldsymbol{x} \triangleq [x_1,\ldots,x_K]^\mathsf{H} \in \mathcal{X}^{K}$, and $\boldsymbol{H}_{\text{C}} \triangleq [\boldsymbol{h}_{\text{C},1},\ldots,\boldsymbol{h}_{\text{C},K}]^\mathsf{H} \in \mathbb{C}^{K \times Q}$.
-		Without loss of generality, we assume the spreading factor $N$ is a positive integer.
-		Within one backscatter block, the signal received by the user at primary block $n \in \mathcal{N} \triangleq \{1,\ldots,N\}$ is
-		\begin{equation}
-			y[n] = \boldsymbol{h}^\mathsf{H}(x_{\mathcal{K}}) \boldsymbol{w} s[n] + v[n],
-			\label{eq:receive_signal}
-		\end{equation}
-		where $\boldsymbol{w} \in \mathbb{C}^{Q}$ is the active beamformer satisfying $\lVert \boldsymbol{w} \rVert^2 \le P$, $P$ is the maximum average transmit power, $s \sim \mathcal{CN}(0,1)$ is the primary symbol, and $v \sim \mathcal{CN}(0,\sigma_v^2)$ is the \gls{awgn} with variance $\sigma_v^2$.
-
-		Let $m_k \in \mathcal{M} \triangleq \{1,\ldots,M\}$ be the reflection state index of node $k$, and $m_{\mathcal{K}} \triangleq (m_1,\ldots,m_K)$ be the state index tuple of all nodes.
-		The backscatter symbol $x_k$ (resp.
-symbol tuple $x_{\mathcal{K}}$) is a random variable that takes value $x_{m_k}$ (resp.
-value tuple $x_{m_{\mathcal{K}}}$) with probability $p(x_{m_k})$ (resp.
-$p(x_{m_{\mathcal{K}}})$).
-		\begin{remark}
-			Dispersed RIScatter nodes encode independently such that
-			\begin{equation}
-				p(x_{m_{\mathcal{K}}}) = \prod_k p(x_{m_k}).
-				\label{eq:equivalent_distribution}
-			\end{equation}
-			When multiple nodes are co-located, they can jointly encode by designing the joint probability $p(x_{m_{\mathcal{K}}})$ directly.
-			\label{re:independent_encoding}
-		\end{remark}
-
-		Let $z=\sum_{n} \bigl\lvert y[n] \bigr\rvert^2$ be the receive energy per backscatter block.
-		When $x_{m_\mathcal{K}}$ is transmitted, the receive signal $y$ follows \gls{cscg} distribution $\mathcal{CN}(0,\sigma_{m_{\mathcal{K}}}^2)$ with variance
-		\begin{equation}
-			\sigma_{m_{\mathcal{K}}}^2 = \lvert \boldsymbol{h}^\mathsf{H}(x_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2 + \sigma_v^2,
-			\label{eq:receive_variance}
-		\end{equation}
-		and $z$ follows Gamma distribution with conditional \gls{pdf}
-		\begin{equation}
-			f(z|x_{m_{\mathcal{K}}}) = \frac{z^{N-1} \exp(-z/\sigma_{m_{\mathcal{K}}}^2)}{\sigma_{m_{\mathcal{K}}}^{2N} (N-1)!}.
-			\label{eq:energy_distribution}
-		\end{equation}
-
-		\begin{remark}
-			We have assumed Gaussian codebook for the primary source and finite support for the backscatter nodes, since they are relatively practical and widely adopted in relevant literatures.
-			The proposed framework is extendable to non-Gaussian primary source, and the conditional \gls{pdf} \eqref{eq:energy_distribution} can be approximated using \gls{clt} for large $N$.
-			\label{re:non_gaussian}
-		\end{remark}
-
-		The user first jointly decodes the backscatter message of all nodes using a low-complexity energy detector.\footnote{The reliability of the energy detector is improved by the adaptive input distribution and thresholding design.
-With high-order modulation or large number of scatter nodes, the reliability can be further enhanced by increasing the spreading factor or using error correction codes with low code-rate.
-In practice, users can decode backscatter nodes ranging from a few to hundreds of meters in the presence of noise and interference, and the backscatter throughput can reach few Kbps to tens of Mbps \cite{Wu2022e}.\label{fn:energy_detector}}
-		The energy detector formulates a \gls{dmtc} of size $M^K \times M^K$.
-
-		\begin{remark}
-			The capacity-achieving decision region design for \gls{dmtc} with non-binary inputs in arbitrary distribution remains an open issue.
-			It was proved deterministic detectors can be rate-optimal, but non-convex regions (consist of non-adjacent partitions) are generally required and the optimal number of thresholds is unknown \cite{Nguyen2018,Nguyen2021}.
-			Next, we restrict the energy detector to convex deterministic decision regions and consider sequential threshold design.
-		\end{remark}
-
-		Let $L = M^K$ be the number of decision regions.
-		Sort $\{\sigma_{m_{\mathcal{K}}}^2\}$ in ascending order and denote the result sequence as $\sigma_1^2,\ldots,\sigma_L^2$.
-		With sequential thresholding, the decision region of backscatter symbol tuple $l \in \mathcal{L} \triangleq \{1,\ldots,L\}$ is\footnote{$m_{\mathcal{K}}$ and $l$ are one-to-one mapped.
-Both notations are used interchangeably in the following context.}
-		\begin{equation}
-			\mathcal{R}_{l} \triangleq [t_{l-1},t_l), \quad 0 \le t_{l-1} \le t_l,
-		\end{equation}
-		where $t_l$ is the decision threshold between hypotheses $x_{l}$ and $x_{l+1}$.
-		An example is shown in Fig.~\ref{fg:energy_distribution}.
-
-		\begin{figure}[!t]
-			\centering
-			\includegraphics[width=0.8\columnwidth]{assets/illustration/energy_distribution.jpg}
-			\caption{
-				\gls{pdf} of the receive energy per backscatter block conditioned on different reflection state.
-			}
-			\label{fg:energy_distribution}
-		\end{figure}
-		When the threshold vector $\boldsymbol{t} \triangleq [t_0,\ldots,t_L]^\mathsf{T} \in \mathbb{R}_+^{L+1}$ is given, we can formulate a \gls{dmmac} with transition probability from input $x_{m_{\mathcal{K}}}$ to output $\hat{x}_{m_{\mathcal{K}}'}$ as
-		\begin{equation}
-			q(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}}) = \int_{\mathcal{R}_{m_{\mathcal{K}}'}} f(z|x_{m_{\mathcal{K}}}) \, d z.
-			\label{eq:dmmac}
-		\end{equation}
-		The backscatter mutual information is
-		\begin{equation}
-			I_{\text{B}}(x_{\mathcal{K}};\hat{x}_{\mathcal{K}}) = \sum_{m_{\mathcal{K}}} p(x_{m_{\mathcal{K}}}) I_{\text{B}}(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}}),
-			\label{eq:backscatter_mutual_information}
-		\end{equation}
-		where $I_{\text{B}}(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}})$ is the backscatter information function
-		\begin{equation}
-			I_{\text{B}}(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}}) \triangleq \sum_{m_{\mathcal{K}}'} q(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}}) \log \frac{q(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}})}{p(\hat{x}_{m_{\mathcal{K}}'})}.
-			\label{eq:backscatter_information_function}
-		\end{equation}
-
-		Once the backscatter information is successfully decoded, the user re-encodes to recover the reflection pattern, constructs the composite channel by \eqref{eq:equivalent_channel}, then coherently decodes the primary link.
-		The primary mutual information is
-		\begin{equation}
-			I_{\text{P}}(s;y|x_{\mathcal{K}}) = \sum_{m_{\mathcal{K}}} p(x_{m_{\mathcal{K}}}) I_{\text{P}}(s;y|x_{m_{\mathcal{K}}}),
-			\label{eq:primary_mutual_information}
-		\end{equation}
-		where $I_{\text{P}}(s;y|x_{m_{\mathcal{K}}})$ is the primary information function
-		\begin{equation}
-			I_{\text{P}}(s;y|x_{m_{\mathcal{K}}}) \triangleq \log \Bigl(1 + \frac{\lvert \boldsymbol{h}^\mathsf{H}(x_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_v^2}\Bigr).
-			\label{eq:primary_information_function}
-		\end{equation}
-	\end{subsection}
-\end{section}
-
-\begin{section}{Rate-Region Characterization}
-	With a slight abuse of notation, we define the weighed sum mutual information and information function as
-	\begin{align}
-		I(x_{\mathcal{K}})
-		 & \triangleq \rho I_{\text{P}}(s;y|x_{\mathcal{K}}) + (1 - \rho) I_{\text{B}}(x_{\mathcal{K}};\hat{x}_{\mathcal{K}}),\label{eq:weighted_sum_mutual_information}           \\
-		I(x_{m_\mathcal{K}})
-		 & \triangleq \rho I_{\text{P}}(s;y|x_{m_{\mathcal{K}}}) + (1 - \rho) I_{\text{B}}(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}}),\label{eq:weighted_sum_information_function}
-	\end{align}
-	where $\rho \in \mathbb{I}$ is the \gls{qos}.
-	To obtain the achievable primary-(total-)backscatter rate region, we consider the weighted sum mutual information maximization problem with independent encoding at all nodes\footnote{Joint encoding over multiple nodes can be viewed as its special case with an augmented backscatter source.\label{fn:joint_encoding}}
-	\begin{maxi!}
-		{\scriptstyle{\{\boldsymbol{p}_k\}_{k \in \mathcal{K}},\boldsymbol{w},\boldsymbol{t}}}{I(x_{\mathcal{K}})}{\label{op:weighted_sum_rate}}{\label{ob:weighted_sum_rate}}
-		\addConstraint{\boldsymbol{1}^\mathsf{T} \boldsymbol{p}_k}{=1,}{\quad \forall k}{\label{co:sum_probability}}
-		\addConstraint{\boldsymbol{p}_k}{\ge \boldsymbol{0},}{\quad \forall k}{\label{co:nonnegative_probability}}
-		\addConstraint{\lVert \boldsymbol{w} \rVert^2}{\le P}{\label{co:transmit_power}}
-		\addConstraint{t_{l-1}}{\le t_l,}{\quad \forall l}{\label{co:sequential_threshold}}
-		\addConstraint{\boldsymbol{t}}{\ge \boldsymbol{0},}{\label{co:nonnegative_threshold}}
-	\end{maxi!}
-	where $\boldsymbol{p}_k = [p(x_{1_k}), \ldots, p(x_{M_k})]^\mathsf{T} \in \mathbb{I}^M$ is the input distribution of node $k$.
-	Problem \eqref{op:weighted_sum_rate} generalizes \gls{bc} by allowing \gls{csi}- and \gls{qos}-adaptive input distribution and decision region design.
-	On the other hand, it also relaxes the feasible domain of discrete \gls{ris} phase shift selection problems from the vertices of $M$-dimensional probability simplex to the simplex itself.
-	The original problem is highly non-convex and we propose a \gls{bcd} algorithm that iteratively updates $\{\boldsymbol{p}_k\}_{k \in \mathcal{K}}$, $\boldsymbol{w}$ and $\boldsymbol{t}$.
-
-	\begin{subsection}{Input Distribution}
-		\label{sc:input_distribution}
-		For any given $\boldsymbol{w}$ and $\boldsymbol{t}$, we can formulate a \gls{dmmac} by \eqref{eq:dmmac} and simplify \eqref{op:weighted_sum_rate} to
-		\begin{maxi!}
-			{\scriptstyle{\{\boldsymbol{p}_k\}_{k \in \mathcal{K}}}}{I(x_{\mathcal{K}})}{\label{op:input_distribution}}{}
-			\addConstraint{\eqref{co:sum_probability},\eqref{co:nonnegative_probability},}
-		\end{maxi!}
-		which involves the product term \eqref{eq:equivalent_distribution} and is generally non-convex (unless $K=1$).
-		Following \cite{Rezaeian2004}, we first recast the \gls{kkt} conditions to their equivalent forms, then propose a numerical solution that guarantees those conditions on the converging point of a sequence.
-		\begin{proposition}
-			The \gls{kkt} optimality conditions for problem \eqref{op:input_distribution} are equivalent to, $\forall k,m_k$,
-			\begin{subequations}
-				\label{eq:input_kkt_condition}
-				\begin{alignat}{2}
-					I_k^\star(x_{m_k}) & = I^\star(x_{\mathcal{K}}), \quad   &  & \text{if} \ p^\star(x_{m_k}) > 0,\label{eq:probable_states} \\
-					I_k^\star(x_{m_k}) & \le I^\star(x_{\mathcal{K}}), \quad &  & \text{if} \ p^\star(x_{m_k}) = 0,\label{eq:dropped_states}
-				\end{alignat}
-			\end{subequations}
-			where $I_k(x_{m_k})$ is the weighted sum marginal information
-			\begin{align}
-				I_k(x_{m_k})
-				 & \triangleq \sum_{m_{\mathcal{K} \setminus \{k\}}} p(x_{m_{\mathcal{K} \setminus \{k\}}}) I(x_{m_\mathcal{K}}).
-				\label{eq:weighted_sum_marginal_information}
-			\end{align}
-			\label{pr:input_kkt_condition}
-		\end{proposition}
-
-		\begin{proof}
-			Please refer to Appendix \ref{ap:input_kkt_condition}.
-			\label{pf:input_kkt_condition}
-		\end{proof}
-
-		For each RIScatter node, \eqref{eq:probable_states} suggests each probable state should produce the same marginal information (averaged over all states of other nodes), while \eqref{eq:dropped_states} suggests any state with potentially less marginal information should not be used.
-		\begin{proposition}
-			For any strictly positive initializer $\{\boldsymbol{p}_k^{(0)}\}_{k \in \mathcal{K}}$, the \gls{kkt} input probability of node $k$ at state $m_k$ is given by the converging point of the sequence
-			\begin{equation}
-				p^{(r+1)}(x_{m_k}) = \frac{p^{(r)}(x_{m_k}) \exp \Bigl( \frac{\rho}{1 - \rho} I_k^{(r)}(x_{m_k}) \Bigr)}{\sum_{m_k'} p^{(r)}(x_{m_k'}) \exp \Bigl( \frac{\rho}{1 - \rho} I_k^{(r)}(x_{m_k'}) \Bigr)},
-				\label{eq:input_kkt_solution}
-			\end{equation}
-			where $r$ is the iteration index.
-			\label{pr:input_kkt_solution}
-		\end{proposition}
-		\begin{proof}
-			Please refer to Appendix \ref{ap:input_kkt_solution}.
-			\label{pf:input_kkt_solution}
-		\end{proof}
-
-		At iteration $r+1$, the input distribution of node $k$ is updated over $\bigl\{\{\boldsymbol{p}_q^{(r+1)}\}_{q=1}^{k-1},\{\boldsymbol{p}_q^{(r)}\}_{q=k}^{K}\bigr\}$.
-		The \gls{kkt} input distribution design is summarized in Algorithm \ref{al:input_distribution}.
-
-		\setalgorithmcaptionfont{\small}
-		\begin{algorithm}[!t]
-			\small
-			\caption{Input Distribution Evaluation by a Sequence}
-			\label{al:input_distribution}
-			\begin{algorithmic}[1]
-				\Require $K$, $N$, $\boldsymbol{h}_{\text{D}}^\mathsf{H}$, $\boldsymbol{H}_{\text{C}}$, $\boldsymbol{\alpha}$, $\mathcal{X}$, $\sigma_v^2$, $\rho$, $\boldsymbol{w}$, $\boldsymbol{t}$, $\epsilon$
-				\Ensure $\{\boldsymbol{p}_k^\star\}_{k \in \mathcal{K}}$
-				\State Set $\boldsymbol{h}^\mathsf{H}(x_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}$ by \eqref{eq:equivalent_channel}
-				\State \phantom{Set} $\sigma^2_{m_{\mathcal{K}}}$, $\forall m_{\mathcal{K}}$ by \eqref{eq:receive_variance}
-				\State \phantom{Set} $f(z|x_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}$ by \eqref{eq:energy_distribution}
-				\State \phantom{Set} $q(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}, m_{\mathcal{K}}'$ by \eqref{eq:dmmac}
-				\State Initialize $r \gets 0$
-				\State \phantom{Initialize} $\boldsymbol{p}_k^{(0)} > \boldsymbol{0}$, $\forall k$
-				\State Get $p^{(r)}(x_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}$ by \eqref{eq:equivalent_distribution} \label{st:input_distribution_begin}
-				\State \phantom{Get} $I^{(r)}(x_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}$ by \eqref{eq:backscatter_information_function}, \eqref{eq:primary_information_function}, \eqref{eq:weighted_sum_information_function}
-				\State \phantom{Get} $I^{(r)}_k(x_{m_k})$, $\forall k,m_k$ by \eqref{eq:weighted_sum_marginal_information}
-				\State \phantom{Get} $I^{(r)}(x_{\mathcal{K}})$ by \eqref{eq:backscatter_mutual_information}, \eqref{eq:primary_mutual_information}, \eqref{eq:weighted_sum_mutual_information} \label{st:input_distribution_end}
-				\Repeat
-					\State Update $r \gets r+1$
-					\State \phantom{Update} $\boldsymbol{p}_k^{(r)}$, $\forall k$ by \eqref{eq:input_kkt_solution}
-					\State Redo step \ref{st:input_distribution_begin}--\ref{st:input_distribution_end}
-				\Until $I^{(r)}(x_{\mathcal{K}}) - I^{(r-1)}(x_{\mathcal{K}}) \le \epsilon$
-			\end{algorithmic}
-		\end{algorithm}
-
-		\begin{remark}
-			The insufficiency of the \gls{kkt} conditions for problem \eqref{op:input_distribution} implies that the proposed method may not converge to the global-optimal solution.
-			However, simulation results in Section~\ref{sc:simulation_results} will show that the average performance gap is indistinguishable at a moderate $K$.
-			\label{re:input_kkt_distribution}
-		\end{remark}
-	\end{subsection}
-
-	\begin{subsection}{Active Beamforming}
-		For any given $\{\boldsymbol{p}_k\}_{k \in \mathcal{K}}$ and $\boldsymbol{t}$, problem \eqref{op:weighted_sum_rate} reduces to
-		\begin{maxi!}
-			{\scriptstyle{\boldsymbol{w}}}{I(x_{\mathcal{K}})}{\label{op:active_beamforming}}{\label{ob:active_beamforming}}
-			\addConstraint{\eqref{co:transmit_power},}
-		\end{maxi!}
-		which is still non-convex due to the integration and entropy terms.
-		Note the \gls{dmmac} $q(x_l|x_{m_{\mathcal{K}}})$ depends on the variance of accumulated receive energy $\sigma_{m_{\mathcal{K}}}^2$, which is a function of $\boldsymbol{w}$.
-		Plugging \eqref{eq:energy_distribution} into \eqref{eq:dmmac}, we have
-		\begin{align}
-			q(x_l|x_{m_{\mathcal{K}}})
-			 & = \frac{\int_{{t_{l-1}}/{\sigma_{m_{\mathcal{K}}}^2}}^{{t_l}/{\sigma_{m_{\mathcal{K}}}^2}} z^{N-1} \exp(-z) \, d z}{(N-1)!} \\
-			 & = Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr),
-			\label{eq:dmmac_gamma}
-		\end{align}
-		where $Q(N, b_1, b_2) \triangleq \int_{b_1}^{b_2} z^{N-1} \exp(-z) / (N - 1)! \, d z$ is the regularized incomplete Gamma function.
-		Its series expansion is given by \cite[Theorem 3]{Jameson2016}
-		\begin{align}
-			Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr)
-			 & = \exp \Bigl(-\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2}\Bigr) \sum_{n=0}^{N-1} \frac{\bigl(\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2}\bigr)^n}{n!} \nonumber \\
-			 & \quad - \exp \Bigl(-\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr) \sum_{n=0}^{N-1} \frac{\bigl(\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\bigr)^n}{n!},
-			\label{eq:regularized_incomplete_gamma}
-		\end{align}
-		whose gradient with respect to $\boldsymbol{w}^*$ is
-		\begin{align}
-			\nabla_{\boldsymbol{w}^*} Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr)
-			 & = \frac{\boldsymbol{h}(x_{m_{\mathcal{K}}})\boldsymbol{h}^\mathsf{H}(x_{m_{\mathcal{K}}})\boldsymbol{w}}{(\sigma_{m_{\mathcal{K}}}^2)^2} \nonumber \\
-			 & \quad \times \Bigl(g_{m_{\mathcal{K}}}(t_l) - g_{m_{\mathcal{K}}}(t_{l-1})\Bigr),
-			\label{eq:regularized_incomplete_gamma_gradient}
-		\end{align}
-		where
-		\begin{equation}
-			g_{m_{\mathcal{K}}}(t_l) = t_l\exp\Bigl(-\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr)\Bigl(-1+\sum_{n=1}^{N-1} \frac{\bigl(n - \frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\bigr) \bigl(\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\bigr)^{n-1}}{n!}\Bigr).
-			\label{eq:regularized_incomplete_gamma_gradient_component}
-		\end{equation}
-		On top of \eqref{eq:regularized_incomplete_gamma} and \eqref{eq:regularized_incomplete_gamma_gradient}, we rewrite $I(x_{\mathcal{K}})$ and $\nabla_{\boldsymbol{w}^*} I(x_{\mathcal{K}})$ as \eqref{eq:weighted_sum_mutual_information_explicit} and \eqref{eq:weighted_sum_mutual_information_gradient} at the end of page \pageref{eq:weighted_sum_mutual_information_explicit}, respectively.
-		\begin{figure*}[!b]
-			\hrule
-			\begin{equation}
-				I(x_{\mathcal{K}})=\sum_{m_{\mathcal{K}}}p(x_{m_{\mathcal{K}}})\Biggl(\rho\log\Bigl(1+\frac{\lvert\boldsymbol{h}^\mathsf{H}(x_{m_{\mathcal{K}}})\boldsymbol{w}\rvert^2}{\sigma_v^2}\Bigr)+(1-\rho)\sum_l Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr) \log \frac{Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr)}{\sum_{m_{\mathcal{K}}'} p(x_{m_{\mathcal{K}}'}) Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}'}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}'}^2}\Bigr)}\Biggr)
-				\label{eq:weighted_sum_mutual_information_explicit}
-			\end{equation}
-			\begin{align}
-				\nabla_{\boldsymbol{w}^*} I(x_{\mathcal{K}})
-				 & = \sum_{m_{\mathcal{K}}}p(x_{m_{\mathcal{K}}})\Biggl(\rho\frac{\boldsymbol{h}(x_{m_{\mathcal{K}}})\boldsymbol{h}^\mathsf{H}(x_{m_{\mathcal{K}}})\boldsymbol{w}}{\sigma_{m_{\mathcal{K}}}^2}+(1-\rho)\sum_l\biggl(\log\frac{Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr)}{\sum_{m_{\mathcal{K}}'}p(x_{m_{\mathcal{K}}'})Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}'}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}'}^2}\Bigr)}+1\biggr)\nonumber                                                                                   \\
-				 & \qquad \times \nabla_{\boldsymbol{w}^*} Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr)-\frac{Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr)\sum_{m_{\mathcal{K}}'}p(x_{m_{\mathcal{K}}'})\nabla_{\boldsymbol{w}^*}Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}'}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}'}^2}\Bigr)}{\sum_{m_{\mathcal{K}}'}p(x_{m_{\mathcal{K}}'})Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}'}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}'}^2}\Bigr)}\Biggr)
-				\label{eq:weighted_sum_mutual_information_gradient}
-			\end{align}
-		\end{figure*}
-		Problem \eqref{op:active_beamforming} can thus be solved by the \gls{pga} method.
-		At iteration $r+1$, the unregulated active beamformer is updated by
-		\begin{equation}
-			\bar{\boldsymbol{w}}^{(r+1)} = \boldsymbol{w}^{(r)}+\gamma\nabla_{\boldsymbol{w}^*} I^{(r)}(x_{\mathcal{K}}),
-			\label{eq:beamforming_gradient_ascent}
-		\end{equation}
-		where $\gamma$ is the step size (refinable by backtracking line search \cite[Section 9.2]{Boyd2004}).
-		Then, $\bar{\boldsymbol{w}}$ is projected onto the feasible domain \eqref{co:transmit_power} to retrieve the active beamformer
-		\begin{equation}
-			\boldsymbol{w} = \frac{\sqrt{P} \bar{\boldsymbol{w}}}{\max\bigl(\sqrt{P},\lVert\bar{\boldsymbol{w}}\rVert\bigr)}.
-			\label{eq:beamforming_projection}
-		\end{equation}
-
-		The \gls{pga} active beamforming design is summarized in Algorithm \ref{al:active_beamforming}.
-		\setalgorithmcaptionfont{\small}
-		\begin{algorithm}[!t]
-			\small
-			\caption{Active Beamforming Optimization by \gls{pga}}
-			\label{al:active_beamforming}
-			\begin{algorithmic}[1]
-				\Require $Q$, $N$, $\boldsymbol{h}_{\text{D}}^\mathsf{H}$, $\boldsymbol{H}_{\text{C}}$, $\boldsymbol{\alpha}$, $\mathcal{X}$, $P$, $\sigma_v^2$, $\rho$, $\{\boldsymbol{p}_k\}_{k \in \mathcal{K}}$, $\boldsymbol{t}$, $\alpha$, $\beta$, $\gamma$, $\epsilon$
-				\Ensure $\boldsymbol{w}^\star$
-				\State Set $\boldsymbol{h}^\mathsf{H}(x_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}$ by \eqref{eq:equivalent_channel}
-				\State \phantom{Set} $p(x_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}$ by \eqref{eq:equivalent_distribution}
-				\State Initialize $r \gets 0$
-				\State \phantom{Initialize} $\boldsymbol{w}^{(0)}$, $\lVert\boldsymbol{w}^{(0)}\rVert^2 \le P$
-				\State Get $(\sigma_{m_{\mathcal{K}}}^{(r)})^2$, $\forall m_{\mathcal{K}}$ by \eqref{eq:receive_variance} \label{st:gradient_descent_begin}
-				\State \phantom{Get} $Q^{(r)}\bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\bigr)$, $\forall m_{\mathcal{K}},l$ by \eqref{eq:regularized_incomplete_gamma}
-				\State \phantom{Get} $I^{(r)}(x_{\mathcal{K}})$ by \eqref{eq:weighted_sum_mutual_information_explicit} \label{st:gradient_descent_end}
-				\State \phantom{Get} $\nabla_{\boldsymbol{w}^*} Q^{(r)}\bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\bigr)$, $\forall m_{\mathcal{K}},l$ by \eqref{eq:regularized_incomplete_gamma_gradient} \label{st:gradient_update_start}
-				\State \phantom{Get} $\nabla_{\boldsymbol{w}^*} I^{(r)}(x_{\mathcal{K}})$ by \eqref{eq:weighted_sum_mutual_information_gradient} \label{st:gradient_update_end}
-				\Repeat
-					\State Update $r \gets r+1$
-					\State \phantom{Update} $\gamma^{(r)}\gets\gamma$
-					\State \phantom{Update} $\bar{\boldsymbol{w}}^{(r)}$ by \eqref{eq:beamforming_gradient_ascent} \label{st:backtracking_line_search_begin}
-					\State \phantom{Update} $\boldsymbol{w}^{(r)}$ by \eqref{eq:beamforming_projection}
-					\State Redo step \ref{st:gradient_descent_begin}--\ref{st:gradient_descent_end} \label{st:backtracking_line_search_end}
-					\While{$I^{(r)}(x_{\mathcal{K}})<I^{(r-1)}(x_{\mathcal{K}})+\alpha\gamma\lVert\nabla_{\boldsymbol{w}^*}I^{(r-1)}(x_{\mathcal{K}})\rVert^2$}
-						\State Set $\gamma^{(r)}\gets\beta\gamma^{(r)}$
-						\State Redo step \ref{st:backtracking_line_search_begin}--\ref{st:backtracking_line_search_end}
-					\EndWhile
-					\State Redo step \ref{st:gradient_update_start}, \ref{st:gradient_update_end}
-				\Until $\lVert\boldsymbol{w}^{(r)}-\boldsymbol{w}^{(r-1)}\rVert \le \epsilon$
-			\end{algorithmic}
-		\end{algorithm}
-	\end{subsection}
-
-	\begin{subsection}{Decision Threshold}
-		For any given $\{\boldsymbol{p}_k\}_{k \in \mathcal{K}}$ and $\boldsymbol{w}$, problem \eqref{op:weighted_sum_rate} reduces to
-		\begin{maxi!}
-			{\scriptstyle{\boldsymbol{t}}}{I(x_{\mathcal{K}})}{\label{op:decision_threshold}}{\label{ob:decision_threshold}}
-			\addConstraint{\eqref{co:sequential_threshold},\eqref{co:nonnegative_threshold},}
-		\end{maxi!}
-		which is still non-convex since $\boldsymbol{t}$ appears on the limits of integration \eqref{eq:dmmac}.
-		Instead of solving it directly, we constrain the feasible domain from continuous space $\mathbb{R}_+^{L+1}$ to discrete candidates (i.e., fine-grained energy levels) $\mathcal{T}^{L+1}$.
-		As shown in Fig.~\ref{fg:discrete_outputs}, the decision regions are formulated by grouping adjacent energy bins.
-		\begin{figure}[!t]
-			\centering
-			\resizebox{0.9\columnwidth}{!}{
-				\input{assets/illustration/discrete_outputs.tex}
-			}
-			\caption{The thresholds are chosen from fine-grained candidates instead of the continuous space. Each decision region consists of at least one bin.}
-			\label{fg:discrete_outputs}
-		\end{figure}
-
-		\begin{remark}
-			The design of the energy detector does not affect the primary achievable rate, since the composite channel \eqref{eq:equivalent_channel} can always be determined after backscatter decoding and re-encoding.
-			This implies that any thresholding maximizing the total backscatter rate is optimal for problem \eqref{op:decision_threshold}.
-			\label{re:backscatter_decision}
-		\end{remark}
-
-		\begin{remark}
-			In terms of total backscatter rate, the nodes can be viewed as an augmented source, and problem \eqref{op:decision_threshold} becomes the rate-optimal quantizer design for \gls{dmtc}.
-			\label{re:augmented_source}
-		\end{remark}
-
-		Thanks to Remark \ref{re:backscatter_decision} and \ref{re:augmented_source}, problem \eqref{op:decision_threshold} can be recast as
-		\begin{maxi!}
-			{\scriptstyle{\boldsymbol{t} \in \mathcal{T}^{L+1}}}{I_{\text{B}}(x_{\mathcal{K}};\hat{x}_{\mathcal{K}})}{\label{op:decision_threshold_discrete}}{\label{ob:decision_threshold_discrete}}
-			\addConstraint{\eqref{co:sequential_threshold},}
-		\end{maxi!}
-		whose global optimal solution has been obtained in recent works.
-		\cite{He2021} started from the quadrangle inequality and proposed a \gls{dp} method accelerated by the \gls{smawk} algorithm with computational complexity $\mathcal{O}\bigl(L^2(\mathrm{card}(\mathcal{T})-L)\bigr)$.
-		On the other hand, \cite{Nguyen2020a} started from the optimality condition for three neighbor thresholds and presented a traverse-then-bisect algorithm with complexity $\mathcal{O}\bigl(\mathrm{card}(\mathcal{T})L\log(\mathrm{card}(\mathcal{T})L)\bigr)$.
-		In Section \ref{sc:simulation_results}, both schemes will be compared with the \gls{ml} scheme \cite{Qian2019}
-		\begin{equation}
-			t_{l}^{\text{\gls{ml}}} = N \frac{\sigma_{l-1}^2 \sigma_{l}^2}{\sigma_{l-1}^2 - \sigma_{l}^2} \log \frac{\sigma_{l-1}^2}{\sigma_{l}^2}, \quad l \in \mathcal{L} \setminus \{L\},
-			\label{eq:detection_threshold_ml}
-		\end{equation}
-		which is suboptimal for problem \eqref{op:decision_threshold} unless all nodes are with equiprobable inputs.
-	\end{subsection}
-\end{section}
-
-\begin{section}{Simulation Results}
-	\label{sc:simulation_results}
-	In this section, we provide numerical results to evaluate the proposed algorithms.
-	We assume the AP-user distance is \qty{10}{m} and at least one RIScatter nodes are randomly dropped in a disk centered at the user with radius $r$.
-	The \gls{ap} is with maximum average transmit power $P=\qty{36}{dBm}$ and all nodes employs $M$-\gls{qam} with $\alpha=0.5$.
-	For all channels involved, we consider a distance-dependent path loss model
-	\begin{equation}
-		L(d) = L_0 \biggl(\frac{d_0}{d}\biggr)^\gamma,
-	\end{equation}
-	together with a Rician fading model
-	\begin{equation}
-		\boldsymbol{H} = \sqrt{\frac{\kappa}{1+\kappa}} \bar{\boldsymbol{H}} + \sqrt{\frac{1}{1+\kappa}} \tilde{\boldsymbol{H}},
-	\end{equation}
-	where $d$ is the transmission distance, $L_0=-\qty{30}{dB}$ is the reference path loss at $d_0=\qty{1}{m}$, $\kappa$ is the Rician K-factor, $\bar{\boldsymbol{H}}$ is the deterministic line-of-sight component with unit-magnitude entries, and $\tilde{\boldsymbol{H}}$ is the Rayleigh fading component with standard \gls{iid} \gls{cscg} entries.
-	We choose $\gamma_{\text{D}}=2.6$, $\gamma_{\text{F}}=2.4$, $\gamma_{\text{B}}=2$, and $\kappa_{\text{D}}=\kappa_{\text{F}}=\kappa_{\text{B}}=5$ for direct, forward and backward links.
-	The finite decision threshold domain $\mathcal{T}$ is obtained by $b$-bit uniform discretization over the critical interval defined by the $1-\varepsilon$ confidence bounds of edge hypotheses (i.e., lower bound of $x_1$ and upper bound of $x_L$).
-	We set $b=9$ and $\varepsilon=\num{e-3}$.
-	All achievable rate regions are averaged over \num{e3} channel realizations.
-
-	\begin{subsection}{Evaluation of Proposed Algorithms}
-		\begin{subsubsection}{Initialization}
-			To characterize the achievable rate region, we progressively obtain all boundary points by successively increasing $\rho$ and solving problem \eqref{op:weighted_sum_rate}.
-			For $\rho=0$ where the backscatter link is prioritized, we initialize Algorithm \ref{al:input_distribution} and \ref{al:active_beamforming} by uniform input distribution and \gls{mrt} towards the sum cascaded channel $\sum_{k} \boldsymbol{h}_{\text{C},k}^\mathsf{H}$, respectively.
-			At the following points, both algorithms are initialized by the solutions at the previous point.
-		\end{subsubsection}
-
-		\begin{subsubsection}{Convergence}
-			\label{sc:convergence}
-			\begin{figure}[!t]
-				\centering
-				\resizebox{0.75\columnwidth}{!}{
-					\input{assets/simulation/wsr_convergence.tex}
-				}
-				\caption{Typical convergence curves at $\rho=0$ for $Q=4$, $K=8$, $M=2$, $N=20$, $\sigma_v^2=\qty{-40}{dBm}$ and $r=\qty{2}{m}$.}
-				\label{fg:wsr_convergence}
-			\end{figure}
-			The \gls{bcd} algorithm is convergent for problem \eqref{op:weighted_sum_rate} since the input distribution and active beamforming subproblems converge and the thresholding subproblem attains global optimality.
-			In company with \gls{bcd}, we also plotted the convergence results of \gls{kkt} and \gls{pga} algorithms in Fig.~\ref{fg:wsr_convergence} to show how much performance is gained by solving each subproblem.
-			It is observed that Algorithm \ref{al:input_distribution} and \ref{al:active_beamforming} take around \num{100} and \num{10} iterations to converge, respectively.
-			Overall, the \gls{bcd} algorithm requires at most \num{5} iterations to converge.
-			As $\rho$ increases (not presented here), the convergence of all three algorithms are much faster thanks to the progressive initialization.
-		\end{subsubsection}
-	\end{subsection}
-
-	\begin{subsection}{Comparison of Scattering Applications}
-		On top of the setup in Fig.~\ref{fg:riscatter_network}, we consider RIScatter and the following benchmark applications:
-		\begin{itemize}
-			\item \emph{Legacy:} Legacy transmission without scatter nodes.
-			\item \emph{\gls{bbc}:} The primary signal is \gls{cw} and the receive signal is
-			\begin{equation}
-				y^{\text{\gls{bbc}}}[n] = \Bigl(\boldsymbol{h}_{\text{D}}^\mathsf{H} + \sum_{k} \alpha_k \boldsymbol{h}_{\text{C},k}^\mathsf{H} x_k\Bigr) \boldsymbol{w} + v[n].
-			\end{equation}
-			The total backscatter rate approaches $K \log M$ when $N$ is sufficiently large.
-			\item \emph{\gls{ambc}:} The user decodes each link independently and semi-coherently while treating the other as interference.
-			The primary achievable rate is approximately\footnote{The scattered component is treated as interference with average power $\mathbb{E}\bigl\{\sum_{k} \alpha_k \boldsymbol{h}_{\text{C},k}^\mathsf{H} x_k \boldsymbol{w}s[n]\bigr\} = \sum_{k} \lvert \alpha_k \boldsymbol{h}_{\text{C},k}^\mathsf{H} \boldsymbol{w} \rvert^2$ \cite{Long2020a}.\label{fn:ambc}}
-			\begin{equation}
-				I_{\text{P}}^{\text{\gls{ambc}}}(s;y) \approx \log \Bigl(1 + \frac{\lvert\boldsymbol{h}_{\text{D}}^\mathsf{H}\boldsymbol{w}\rvert^2}{\sum_{k}\lvert \alpha_k \boldsymbol{h}_{\text{C},k}^\mathsf{H} \boldsymbol{w}\rvert^2+\sigma_v^2}\Bigr),
-			\end{equation}
-			while the total backscatter rate follows \eqref{eq:backscatter_mutual_information} with uniform input distribution.
-			\item \emph{\gls{sr}:} For a sufficiently large $N$, the average primary rate under semi-coherent detection asymptotically approaches \eqref{eq:primary_mutual_information} with uniform input distribution \cite{Long2020a}.
-			When $s[n]$ is successfully decoded and the direct interference $\boldsymbol{h}_{\text{D}}^\mathsf{H} \boldsymbol{w} s[n]$ is perfectly cancelled, the intermediate signal is
-			\begin{equation}
-				\hat{y}^{\text{\gls{sr}}}[n] = \sum_{k} \alpha_k \boldsymbol{h}_{\text{C},k}^\mathsf{H} x_k \boldsymbol{w} s[n] + v[n].
-				\label{eq:intermediate_signal}
-			\end{equation}
-			The total backscatter rate approaches $K \log M$.
-			\item \emph{\gls{ris}:} The reflection pattern is deterministic and the total backscatter rate is zero.
-			The primary achievable rate is a special case of \eqref{eq:primary_mutual_information}
-			\begin{equation}
-				I_{\text{P}}^{\text{\gls{ris}}}(s;y|x_{\mathcal{K}}) = I_{\text{P}}(s;y|x_{m_{\mathcal{K}}^{\star}}) = \log \Bigl(1 + \frac{\lvert \boldsymbol{h}^\mathsf{H}(x_{m_{\mathcal{K}}^{\star}}) \boldsymbol{w} \rvert^2}{\sigma_v^2}\Bigr),
-			\end{equation}
-			where $m_{\mathcal{K}}^{\star} = \arg \max_{m_{\mathcal{K}}} I_{\text{P}}^{\text{\gls{ris}}}(s;y|x_{m_{\mathcal{K}}})$.
-		\end{itemize}
-		\begin{figure}[!t]
-			\centering
-			\resizebox{0.65\columnwidth}{!}{
-				\input{assets/simulation/region_comparison.tex}
-			}
-			\caption{Typical achievable rate region/points of scattering applications for $Q=1$, $K=1$, $M=4$, $N=\num{e3}$, $\sigma_v^2=\qty{-40}{dBm}$ and $r=\qty{2}{m}$.}
-			\label{fg:region_comparison}
-		\end{figure}
-
-		Fig.~\ref{fg:region_comparison} compares the typical achievable rate region/points of RIScatter and those strategies.
-		\emph{First,} we observe \gls{bbc} and \gls{sr} achieve the best backscatter performance thanks to the coherent decoding.
-		For \gls{sr}, this comes with the cost of $N$ re-encoding, precoding, subtraction together with a time-domain \gls{mrc} per backscatter symbol.
-		Since \gls{sr} requires a very large $N$ to guarantee the primary rate, the signal processing cost at the receiver can be prohibitive, and the backscatter \emph{throughput} can be severely constrained.
-		\emph{Second,} the average primary rate slightly decreases/increases in the presence of a \gls{ambc}/\gls{ris} node, and the benefit of \gls{sr} is not obvious.
-		This is because the cascaded channel is around \qty{25}{dB} weaker than the direct channel.
-		Here, \gls{ris} ensures a constructive superposition of the direct and scattered components, while \gls{sr} only creates a quasi-static rich-scattering environment that marginally enhances the average primary rate.
-		When $N$ is moderate, the randomly scattered signals should be modelled as interference rather than stable multipath, and the \gls{sr} point should move vertically towards the \gls{ambc} point.
-		\emph{Third,} RIScatter enables a flexible primary-backscatter tradeoff with adaptive input distribution design.
-		In terms of maximum primary achievable rate, RIScatter coincides with \gls{ris} and outperforms the others by using the static reflection pattern that maximizes the primary \gls{snr} all the time.
-		On the other hand, its maximum backscatter achievable rate is higher than that of \gls{ambc}.
-		This is because the adaptive channel coding of RIScatter outperforms the equiprobable inputs of \gls{ambc}, especially at the low backscatter \gls{snr} caused by double fading.
-		When multiple antenna is available at the \gls{ap}, active beamforming can be optimized for RIScatter nodes and the advantage over \gls{ambc} should be more prominent.
-	\end{subsection}
-
-	\begin{subsection}{Input Distribution under Different \gls{qos}}
-		\begin{figure}[!t]
-			\centering
-			\resizebox{0.65\columnwidth}{!}{
-				\input{assets/simulation/distribution_weights.tex}
-			}
-			\caption{Typical RIScatter reflection state distribution at different $\rho$ for $Q=1$, $K=1$, $M=4$, $N=20$, $\sigma_v^2=\qty{-40}{dBm}$ and $r=\qty{2}{m}$.}
-			\label{fg:distribution_weights}
-		\end{figure}
-		The objective is to demonstrate RIScatter nodes can leverage \gls{csi}- and \gls{qos}-adaptive input distribution design to balance backscatter modulation and passive beamforming.
-		For one RIScatter node with $M=4$, we evaluate the \gls{kkt} input distribution at different \gls{qos} and present the result in Fig.~\ref{fg:distribution_weights}.
 	At $\rho=0$ where the backscatter performance is prioritized, the optimal input distribution is \num{0} on two states and nearly uniform on the other two.
 	This is inline with Shannon's observation that binary antipodal inputs is good enough for channel capacity at low \gls{snr} \cite{Shannon1948}.
-		When the scattered signal is relatively weak, the conditional energy \gls{pdf} under different hypotheses can be closely spaced as in Fig.~\ref{fg:energy_distribution}.
-		The extreme states producing the lowest/highest energy are always assigned with non-zero probability, while the middles cannot provide enough energy diversity and end up unused.
 	At $\rho=1$ where the primary link is prioritized, the optimal input distribution is $[0, 0, 1, 0]^\mathsf{T}$ since state 3 provides higher primary \gls{snr} than other states.
@@
 	Increasing $\rho$ from \num{0} to \num{1} creates a smooth transition from backscatter modulation to passive beamforming, suggesting RIScatter unifies \gls{bc} and \gls{ris} from a probabilistic perspective.
-	\end{subsection}
 
-	\begin{subsection}{Rate Region by Different Schemes}
-		\begin{figure}[!t]
+	\begin{figure}[H]
 		\centering
-			\subfloat[Input Distribution, $Q=1$\label{fg:region_distribution}]{
-				\resizebox{0.6\columnwidth}{!}{
-					\input{assets/simulation/region_distribution.tex}
+		\resizebox{0.7\columnwidth}{!}{
+			\input{../assets/simulation/region_comparison.tex}
 		}
-			}
-			\\
-			\subfloat[Active Beamforming, $Q=4$\label{fg:region_beamforming}]{
-				\resizebox{0.48\columnwidth}{!}{
-					\input{assets/simulation/region_beamforming.tex}
-				}
-			}
-			\subfloat[Decision Threshold, $Q=4$\label{fg:region_threshold}]{
-				\resizebox{0.48\columnwidth}{!}{
-					\input{assets/simulation/region_threshold.tex}
-				}
-			}
-			\caption{
-				Average primary-total-backscatter rate regions by different input distribution, active beamforming, and decision threshold schemes for $K=2$, $M=4$, $N=20$, $\sigma_v^2=\qty{-40}{dBm}$ and $r=\qty{2}{m}$.
-			}
+		\caption{Achievable rate of different scattering applications. ``Legacy'' means active transmission without scatter nodes. ``BBC'' means bistatic \gls{bc}.}
+		\label{fg:scatter_comparison}
 	\end{figure}
-		\begin{subsubsection}{Input Distribution}
-			We compare these input distribution designs for problem \eqref{op:input_distribution}:
-			\begin{itemize}
-				\item \emph{Cooperation:} Joint encoding using a joint probability array $p(x_{m_{\mathcal{K}}})$ with $M^K$ entries by Algorithm \ref{al:input_distribution};
-				\item \emph{Exhaustion:} Exhaustive search over the $M$-dimensional probability simplex with resolution $\Delta p = \num{e-2}$;
-				\item \emph{\gls{kkt}:} Solution by Algorithm \ref{al:input_distribution};
-				\item \emph{Equiprobable:} Uniform input distribution.
-			\end{itemize}
-			We also consider these independent distribution recovery methods from the joint probability array:
-			\begin{itemize}
-				\item \emph{Marginalization:} Marginal probability distributions;
-				\item \emph{Decomposition:} Normalized rank-\num{1} \gls{cp} decomposed tensors by \texttt{Tensor Toolbox} \cite{Bader2022};
-				\item \emph{Randomization:} Gaussian randomization with the guidance of correlation matrix \cite{Calvo2010}.
-			\end{itemize}
-
-			Fig.~\subref*{fg:region_distribution} shows their average achievable rate regions.
-			Cooperation achieves the outer bound of all schemes, but joint encoding over passive devices may incur additional hardware cost.
-			Besides, the average rate performance of Exhaustion and \gls{kkt} completely coincide with each other when $K=2$.
-			This confirms Remark \ref{re:input_kkt_distribution} that the \gls{kkt} input distribution can be good enough when $K$ is moderate.
-			Equiprobable experiences minor backscatter and major primary rate losses without exploiting \gls{csi} and \gls{qos}, and those gaps should be larger when $M$ or $K$ increases.
-			Marginalization provides a close performance to \gls{kkt}, but Randomization and Decomposition fail our expectations for most channel realizations.
-			Those observations emphasize the importance of adaptive RIScatter encoding and demonstrate the advantage of the proposed \gls{kkt} input distribution design.
-		\end{subsubsection}
-
-		\begin{subsubsection}{Active Beamforming}
-			We consider three typical active beamforming schemes for problem \eqref{op:active_beamforming}:
-			\begin{itemize}
-				\item \emph{\gls{pga}:} Solution by Algorithm \ref{al:active_beamforming};
-				\item \emph{E-\gls{mrt}:} \gls{mrt} towards the ergodic composite channel $\sum_{m_{\mathcal{K}}} p(x_{m_{\mathcal{K}}}) \boldsymbol{h}^\mathsf{H}(x_{m_{\mathcal{K}}})$;
-				\item \emph{D-\gls{mrt}:} \gls{mrt} towards the direct channel $\boldsymbol{h}_{\text{D}}^\mathsf{H}$.
-			\end{itemize}
-
-			Fig.~\subref*{fg:region_beamforming} presents the average achievable rate regions for those schemes.
-			In the low-$\rho$ regime, the proposed \gls{pga} beamformer significantly outperforms both \gls{mrt} schemes in terms of total backscatter rate.
-			This is because the semi-coherent backscatter decoding relies on the relative energy difference under different backscatter symbol tuples.
-			Such an energy diversity is enhanced by \gls{pga} that effectively exploits backscatter constellation and input distribution knowledge rather than simply maximizes the channel strength.
-			As $\rho$ increases, the primary \gls{snr} outweighs the backscatter energy difference in \eqref{eq:weighted_sum_mutual_information_explicit}, and \gls{pga} beamformer approaches E-\gls{mrt}.
-			At $\rho=1$, both \gls{pga} and E-\gls{mrt} boil down to \gls{mrt} towards the strongest composite channel.
-			The difference between E-\gls{mrt} and D-\gls{mrt} is insignificant when RIScatter nodes are dispersed.
-			Those observations confirm that the proposed \gls{pga} active beamforming design can exploit the \gls{csi}, \gls{qos}, and backscatter constellation to enlarge the achievable rate region.
-		\end{subsubsection}
-
-		\begin{subsubsection}{Decision Threshold}
-			We evaluate the following decision threshold strategies for problem \eqref{op:decision_threshold_discrete}:
-			\begin{itemize}
-				\item \emph{\gls{dp}:} Benchmark \gls{dp} method for sequential quantizer \cite{He2021};
-				\item \emph{\gls{smawk}:} \emph{\gls{dp}} accelerated by the \gls{smawk} algorithm \cite{He2021};
-				\item \emph{Bisection:} The traverse-then-bisect algorithm \cite{Nguyen2020a};
-				\item \emph{\gls{ml}:} Maximum likelihood detector \eqref{eq:detection_threshold_ml} \cite{Qian2019}.
-			\end{itemize}
-
-			Fig.~\subref*{fg:region_threshold} reveals the average achievable rate region for those strategies.
-			The distribution-aware schemes \gls{dp}, \gls{smawk} and Bisection ensure higher total backscatter rate than \gls{ml}.
-			This is because the total backscatter rate \eqref{eq:backscatter_mutual_information} is a function of both input distribution and decision regions, and the rate-optimal thresholding depends heavily on the input distribution.
-			For example, the backscatter symbol tuples with zero input probability should be assigned with empty decision regions, in order to increase the success detection rates of other hypotheses.
-			It highlights the importance of joint input distribution and decision threshold design in rate maximization problems.
-		\end{subsubsection}
-
-	\end{subsection}
-
-	\begin{subsection}{Rate Region under Different Configurations}
-		\begin{figure}[!t]
-			\centering
-			\subfloat[RIScatter Nodes\label{fg:region_tags}]{
-				\resizebox{0.48\columnwidth}{!}{
-					\input{assets/simulation/region_tags.tex}
-				}
-			}
-			\subfloat[Reflection States\label{fg:region_states}]{
-				\resizebox{0.48\columnwidth}{!}{
-					\input{assets/simulation/region_states.tex}
-				}
-			}
-			\\
-			\subfloat[Transmit Antennas\label{fg:region_txs}]{
-				\resizebox{0.48\columnwidth}{!}{
-					\input{assets/simulation/region_txs.tex}
-				}
-			}
-			\subfloat[Spreading Factor\label{fg:region_duration}]{
-				\resizebox{0.48\columnwidth}{!}{
-					\input{assets/simulation/region_duration.tex}
-				}
-			}
-			\\
-			\subfloat[Average Noise Power\label{fg:region_noise}]{
-				\resizebox{0.48\columnwidth}{!}{
-					\input{assets/simulation/region_noise.tex}
-				}
-			}
-			\subfloat[Imperfect \gls{csi}\label{fg:region_csi}]{
-				\resizebox{0.48\columnwidth}{!}{
-					\input{assets/simulation/region_csi.tex}
-				}
-			}
-			\\
-			\subfloat[Primary \gls{snr}\label{fg:region_snr_primary}]{
-				\resizebox{0.48\columnwidth}{!}{
-					\input{assets/simulation/region_snr_primary.tex}
-				}
-			}
-			\subfloat[Backscatter \gls{snr}\label{fg:region_snr_backscatter}]{
-				\resizebox{0.48\columnwidth}{!}{
-					\input{assets/simulation/region_snr_backscatter.tex}
-				}
-			}
-			\caption{
-				Average primary-total-backscatter rate regions for different system configurations.
-			}
-			\label{fg:region_config}
-		\end{figure}
-		In this study, we choose $Q=4$, $K=8$, $M=2$, $N=20$, $\sigma_v^2=\qty{-40}{dBm}$ and $r=\qty{2}{m}$ as a reference, unless otherwise specified.
-		\begin{subsubsection}{Number of Nodes}
-			Fig.~\subref*{fg:region_tags} reveals how the number RIScatter nodes $K$ influences the primary-backscatter tradeoff.
-			Interestingly, we observe that increasing $K$ has a larger benefit on the total backscatter rate than primary.
-			This is because each RIScatter node not only affects the primary \gls{snr} but also influences the relative energy difference that other nodes can make.
-			To maximize the total backscatter rate, some nodes closer to the user may need to sacrifice their own rate and use the state that \emph{minimizes} the composite channel strength, in order to increase the backscatter rate of other nodes.
-			This accounts for the significant primary rate decrease in the low-$\rho$ regime.
-			On the other hand, when the primary link is prioritized, the RIScatter nodes boil down to \gls{ris} elements and enjoy a passive array gain of $K^2$.
-		\end{subsubsection}
-
-		\begin{subsubsection}{Number of States}
-			Fig.~\subref*{fg:region_states} shows the relationship between the available reflection states (i.e., \gls{qam} order) $M$ and the achievable rate region when $K=1$.
-			We notice that increasing the reflection states has a marginal effect on the primary rate but significantly improves the backscatter rate.
-			This is because the maximum amplitude normalized-\gls{qam} \eqref{eq:backscatter_modulation} involves more weak reflection points as $M$ increases.
-			It enhances the receive energy diversity but cannot provide enough phase shift resolution with maximum reflection.
-		\end{subsubsection}
-
-		\begin{subsubsection}{Number of Transmit Antennas}
-			Fig.~\subref*{fg:region_txs} illustrates the impact of transmit antennas $Q$ on the average performance.
-			As $Q$ increases, more scattered paths become available and the channel diversity can be better exploited to improve the primary-backscatter tradeoff.
-			It emphasizes the importance of multi-antenna RIScatter systems and demonstrate the effectiveness of the proposed \gls{pga} design.
-		\end{subsubsection}
-
-		\begin{subsubsection}{Spreading factor}
-			Fig.~\subref*{fg:region_duration} shows how the spreading factor $N$ affects the achievable rate region.\footnote{Here, the unit of total backscatter rate is bits per primary block to show backscatter throughput.}
-			Using a very large $N$ (as in the case of \gls{sr}) can severely constrain the backscatter throughput, since the gain in energy certainty (by the law of large numbers) cannot withstand the loss in the gross rate.
-			As $N \to \infty$, RIScatter nodes boil down to static \gls{ris} elements and the total backscatter rate approaches \num{0}.
-			On the other hand, when $N$ is too small, the \gls{dmmac} \eqref{eq:dmmac} becomes unreliable and energy detection is error-prone.
-			It explains the observation that $N=10$ provides lower backscatter throughput than $N=20$.
-			Therefore, we conclude the spreading factor $N$ should be carefully designed over multiple factors (e.g., primary and backscatter \gls{snr}, data rate requirements, load switching speed at the nodes, and signal processing capability at the user).
-		\end{subsubsection}
-
-		\begin{subsubsection}{Average Noise Power}
-			Fig.~\subref*{fg:region_noise} depicts the impact of average noise power $\sigma_v^2$ on average rate regions.
-			Note that the noise influences both primary and backscatter \gls{snr}.
-			% It shows the proposed adaptive energy detector is suitable for a wide range of noise levels.
-			When $\sigma_v^2$ relatively high, one can choose a larger $N$ to improve the \gls{snr} of energy detection.
-		\end{subsubsection}
-
-		% \begin{subsubsection}{Coverage Disk Radius}
-		% 	Fig.~\subref*{fg:region_coverage} shows the relationship between disk radius $r$ and achievable rate region.
-		% 	We observe both primary and backscatter performance are enhanced when nodes are located closer to the user.
-		% 	This is because the double fading effect is less severe for near-far setups.
-		% 	In a multi-user RIScatter network with dispersed nodes, each node may be assigned to the nearest user to guarantee uniformly good performance for both links.
-		% \end{subsubsection}
-
-		\begin{subsubsection}{Imperfect \gls{csi}}
-			Due to the lack of \gls{rf} chains at RIScatter nodes, fast and accurate acquisition of the cascaded \gls{csi} can be challenging, especially when the backscatter \gls{snr} is weak or the number of nodes is large.
-			We consider an imperfect \gls{csi} model, where the cascaded channel of node $k$ is estimated as
-			\begin{equation}
-				\hat{\boldsymbol{h}}_{\text{C},k} = \boldsymbol{h}_{\text{C},k} + \tilde{\boldsymbol{h}}_{\text{C},k},
-			\end{equation}
-			$\tilde{\boldsymbol{h}}_{\text{C},k}$ is the estimation error with entries following i.i.d.
-CSCG distribution $\mathcal{CN}(0, \iota \Lambda_\text{C})$, $\iota$ is the relative estimation error, and $\Lambda_\text{C}$ is the cascaded path loss.
-			In Fig.~\subref*{fg:region_csi}, it is observed that the channel estimation error mainly affects the backscatter rate.
-			When $\iota$ increases from \num{0} to \num{0.2}, the maximum total backscatter rate decreases by \qty{20}{\percent}.
-			This is because the energy detector is sensitive to the \gls{dmmac} \eqref{eq:dmmac} and thus the estimation of the cascaded channel.
-			On the other hand, a small estimation error may be insufficient to change the optimal passive beamforming state and the primary rate is almost unchanged.
-		\end{subsubsection}
-
-		\begin{subsubsection}{Primary \gls{snr}}
-			\label{sc:primary_snr}
-			The backscatter \gls{snr} is fixed to \qty{0}{dB} with $Q=1$ in this study.
-			Interestingly, Fig.~\subref*{fg:region_snr_primary} shows that increasing the primary \gls{snr} can improve the primary rate but degrade the backscatter rate.
-			The reason is that the relative strength of the scattered signal compared to the direct signal is weakened, such that the nodes cannot make enough difference to the energy detector.
-			This, together with Fig.~\subref*{fg:region_beamforming} and \subref*{fg:region_tags}, emphasizes the importance of balancing the primary and backscatter \gls{snr} in the design of active-passive coexisting networks.
-			% This, together with Fig.~\subref*{fg:region_beamforming} and \subref*{fg:region_tags}, emphasizes the importance of primary-backscatter tradeoff in active-passive coexisting networks.
-		\end{subsubsection}
-
-		\begin{subsubsection}{Backscatter \gls{snr}}
-			The primary \gls{snr} is fixed to \qty{20}{dB} with $Q=1$ in this study.
-			Fig.~\subref*{fg:region_snr_backscatter} shows that the primary and backscatter rates are both improved when the backscatter \gls{snr} increases.
-			This motivates one to use high-efficiency or semi-passive RIScatter nodes to improve the overall performance.
-			In a multi-user RIScatter network, each node may be assigned to the nearest user to guarantee uniformly good performance for both links.
-		\end{subsubsection}
-	\end{subsection}
+	Fig.~\ref{fg:scatter_comparison} suggests RIScatter enables a flexible primary-backscatter tradeoff.
+	In terms of maximum primary rate, RIScatter coincides with \gls{ris} and outperforms the others.
+	On the other hand, the maximum backscatter rate is higher than that of \gls{ambc} thanks to adaptive active beamforming and input distribution design.
+	To decode each backscatter symbol, \gls{sr} requires multiple re-encoding, precoding, subtraction and a time-domain \gls{mrc}, while RIScatter only requires one energy comparison and re-encoding.
+	This allows RIScatter to achieve a higher backscatter throughput at a lower cost.
 \end{section}
 
-\begin{section}{Conclusion}
-	\label{sc:conclusion}
-	This paper introduced RIScatter as a novel scatter protocol that bridges backscatter modulation and passive beamforming.
-	Starting from scattering principles, we showed how RIScatter nodes generalize information nodes of \gls{bc} and reflect elements of \gls{ris}, how they can be built over existing passive scatter devices, and how they simultaneously encode self information and assist legacy transmission.
-	We also proposed a practical \gls{sic}-free receiver that exploits the properties of active-passive coexisting networks to benefit both subsystems.
-	The achievable primary-total-backscatter rate region was then studied for a single-user multi-node RIScatter network, where the input distribution, active beamforming, and decision thresholds are iteratively updated.
-	Numerical results validated the proposed algorithms and emphasized the importance of adaptive input distribution and cooperative receiver design.
-
-	To support massive RIScatter networks with large number of nodes and states, one possible future direction is to consider backscatter detection over the received signal domain rather than energy domain, where multi-antenna \cite{Liu2022c} and learning-based approaches can be promising.
-	Another interesting question is how to design RIScatter nodes and receivers in a multi-user system to fully exploit the dynamic passive beamforming that naturally origins from backscatter modulation.
-\end{section}
-
-\begin{appendix}
-	\begin{subsection}{Proof of Proposition \ref{pr:input_kkt_condition}}
-		Denote the Lagrange multipliers associated with \eqref{co:sum_probability} and \eqref{co:nonnegative_probability} as $\{\nu_k\}_{k \in \mathcal{K}}$ and $\{\lambda_{m_k}\}_{k \in \mathcal{K},m_k \in \mathcal{M}}$, respectively.
-		The Lagrangian function of problem \eqref{op:input_distribution} is
-		\begin{equation}
-			L(p, \nu, \lambda) = I(x_{\mathcal{K}}) + \sum_k \nu_k \Bigl( \sum_{m_k} p(x_{m_k}) - 1 \Bigr) + \sum_{k,m_k} \lambda_{m_k} p(x_{m_k}),
-		\end{equation}
-		and the \gls{kkt} conditions are, $\forall k,m_k$,
-		\begin{subequations}
-			\label{eq:input_kkt_condition_original}
-			\begin{gather}
-				I_k^\star(x_{m_k}) - (1 - \rho) + \nu_k^\star + \lambda_{m_k}^\star = 0, \label{eq:input_kkt_condition_1} \\
-				\lambda_{m_k}^\star = 0, \quad    \text{if} \ p^\star(x_{m_k}) > 0, \label{eq:input_kkt_condition_2} \\
-				\lambda_{m_k}^\star \ge 0, \quad  \text{if} \ p^\star(x_{m_k}) = 0 \label{eq:input_kkt_condition_3}.
-			\end{gather}
-		\end{subequations}
-		Plugging \eqref{eq:input_kkt_condition_2} and \eqref{eq:input_kkt_condition_3} into \eqref{eq:input_kkt_condition_1} yields
-		\begin{subequations}
-			\label{eq:input_kkt_condition_transformed}
-			\begin{alignat}{2}
-				I_k^\star(x_{m_k}) & = 1 - \rho - \nu_k^\star, \quad   &  & \text{if} \ p^\star(x_{m_k}) > 0,\label{eq:probable_states_marginal} \\
-				I_k^\star(x_{m_k}) & \le 1 - \rho - \nu_k^\star, \quad &  & \text{if} \ p^\star(x_{m_k}) = 0,\label{eq:dropped_states_marginal}
-			\end{alignat}
-		\end{subequations}
-		such that
-		\begin{equation}
-			\sum_{m_k} p^\star(x_{m_k}) I_k^\star(x_{m_k}) = 1 - \rho - \nu_k^\star.
-			\label{eq:input_kkt_condition_implied}
-		\end{equation}
-		On the other hand, by definition \eqref{eq:weighted_sum_marginal_information} we have
-		\begin{equation}
-			\sum_{m_k} p^\star(x_{m_k}) I_k^\star(x_{m_k}) = I^\star(x_{\mathcal{K}}),
-			\label{eq:weighted_sum_marginal_information_implied}
-		\end{equation}
-		where the right-hand side is irrelevant to $k$.
-		\eqref{eq:input_kkt_condition_transformed}, \eqref{eq:input_kkt_condition_implied}, and \eqref{eq:weighted_sum_marginal_information_implied} together complete the proof.
-		\label{ap:input_kkt_condition}
-	\end{subsection}
-
-	\begin{subsection}{Proof of Proposition \ref{pr:input_kkt_solution}}
-		We first prove sequence \eqref{eq:input_kkt_solution} is non-decreasing in weighted sum mutual information.
-		Let $p(x_{m_{\mathcal{K}}}) = \prod_{q \in \mathcal{K}} p(x_{m_q})$ and $p'(x_{m_{\mathcal{K}}}) = p'(x_{m_k}) \prod_{q \in \mathcal{K} \setminus \{k\}} p(x_{m_q})$ be two distributions potentially different at $x_{m_k}$,
-		and $J \bigl(p(x_{m_{\mathcal{K}}}),p'(x_{m_{\mathcal{K}}}) \bigr)$ be a joint function defined in \eqref{eq:intermediate_information_function} at the end of page \pageref{eq:intermediate_information_function}.
-		\begin{figure*}[!b]
-			\hrule
-			\begin{equation}
-				J \bigl( p(x_{m_{\mathcal{K}}}),p'(x_{m_{\mathcal{K}}}) \bigr) \triangleq \sum_{m_{\mathcal{K}}} p(x_{m_{\mathcal{K}}})
-				\Biggl( \rho \log \Bigl(1 + \frac{\lvert \boldsymbol{h}^\mathsf{H}(x_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_v^2}\Bigr) + (1 - \rho) \sum_{m_{\mathcal{K}}'} q(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}}) \log \frac{q(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}}) p'(x_{m_{\mathcal{K}}})}{p'(\hat{x}_{m_{\mathcal{K}}'}) p(x_{m_{\mathcal{K}}})} \Biggr).
-				\label{eq:intermediate_information_function}
-			\end{equation}
-		\end{figure*}
-		It is straightforward to verify $J \bigl( p(x_{m_{\mathcal{K}}}),p(x_{m_{\mathcal{K}}}) \bigr) = I(x_{\mathcal{K}})$ and $J \bigl( p(x_{m_{\mathcal{K}}}),p'(x_{m_{\mathcal{K}}}) \bigr)$ is a concave function for a given $p'(x_{m_{\mathcal{K}}})$.
-		Setting $\nabla_{p(x_{m_k})} J \bigl( p(x_{m_{\mathcal{K}}}),p'(x_{m_{\mathcal{K}}}) \bigr) = 0$ yields
-		\begin{equation}
-			S_k'(x_{m_k}) - S_k'(x_{i_k}) + (1 - \rho) \log \frac{p(x_{i_k})}{p^\star(x_{m_k})} = 0,
-			\label{eq:optimal_intermediate_information_condition}
-		\end{equation}
-		where $i_k \ne m_k$ is the reference state and
-		\begin{align}
-			S_k'(x_{m_k})
-			 & \triangleq I_k'(x_{m_k}) + (1 - \rho) \sum_{m_{\mathcal{K} \setminus \{k\}}} p(x_{m_{\mathcal{K} \setminus \{k\}}})\nonumber \\
-			 & \quad \times \sum_{m_{\mathcal{K}}'} q(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}}) \log p'(x_{m_{\mathcal{K}}}).
-		\end{align}
-		Evidently, $\forall m_k \ne i_k$, \eqref{eq:optimal_intermediate_information_condition} boils down to
-		\begin{equation}
-			p^\star(x_{m_k}) = \frac{p'(x_{m_k}) \exp \Bigl( \frac{\rho}{1 - \rho} I_k'(x_{m_k}) \Bigr)}{\sum_{m_k'} p'(x_{m_k'}) \exp \Bigl( \frac{\rho}{1 - \rho} I_k'(x_{m_k'}) \Bigr)}.
-			\label{eq:optimal_relative_distribution}
-		\end{equation}
-		Since $p(x_{i_k}) = 1 - \sum_{m_k \ne i_k} p^\star(x_{m_k})$ has exactly the same form as \eqref{eq:optimal_relative_distribution}, the choice of reference does not matter and \eqref{eq:optimal_relative_distribution} is optimal $\forall m_k \in \mathcal{M}$.
-		That is, for a fixed $p'(x_{m_{\mathcal{K}}})$, \eqref{eq:optimal_relative_distribution} ensures
-		\begin{equation}
-			J \bigl( p(x_{m_{\mathcal{K}}}),p'(x_{m_{\mathcal{K}}}) \bigr) \ge I'(x_{\mathcal{K}}).
-			\label{eq:information_difference_lower}
-		\end{equation}
-		On the other hand, we notice
-		\begin{subequations}
-			\allowdisplaybreaks
-			\label{eq:information_difference_upper}
-			\begin{align}
-				 & I(x_{\mathcal{K}}) - J \bigl( p(x_{m_{\mathcal{K}}}),p'(x_{m_{\mathcal{K}}}) \bigr)                                                                                                                    \nonumber           \\
-				 & = (1 - \rho) \sum_{m_k} \frac{p'(x_{m_k}) f_k'(x_{m_k})}{\sum_{m_k'} p'(x_{m_k'}) f_k'(x_{m_k'})} \sum_{m_{\mathcal{K}}''} q(\hat{x}_{m_{\mathcal{K}}''}|x_{m_k})                                      \nonumber           \\
-				 & \quad \times \log \frac{\sum_{m_k'} p'(x_{m_k'}) q(\hat{x}_{m_{\mathcal{K}}''}|x_{m_k'}) f_k'(x_{m_k})}{\sum_{m_k'} p'(x_{m_k'}) q(\hat{x}_{m_{\mathcal{K}}''}|x_{m_k'}) f_k'(x_{m_k'})}                                   \\
-				 & \ge (1 - \rho) \sum_{m_k} \frac{p'(x_{m_k}) f_k'(x_{m_k})}{\sum_{m_k'} p'(x_{m_k'}) f_k'(x_{m_k'})} \sum_{m_{\mathcal{K}}''} q(\hat{x}_{m_{\mathcal{K}}''}|x_{m_k})                                    \nonumber           \\
-				 & \quad \times \Biggl( 1 - \frac{\sum_{m_k'} p'(x_{m_k'}) q(\hat{x}_{m_{\mathcal{K}}''}|x_{m_k'}) f_k'(x_{m_k'})}{\sum_{m_k'} p'(x_{m_k'}) q(\hat{x}_{m_{\mathcal{K}}''}|x_{m_k'}) f_k'(x_{m_k})} \Biggr)                    \\
-				 & = (1 - \rho) \Biggl( 1 - \sum_{m_k} \frac{p'(x_{m_k}) \cancel{f_k'(x_{m_k})}}{\sum_{m_k'} p'(x_{m_k'}) f_k'(x_{m_k'})} \sum_{m_{\mathcal{K}}''} q(\hat{x}_{m_{\mathcal{K}}''}|x_{m_k})                 \nonumber           \\
-				 & \quad \times \frac{\sum_{m_k'} p'(x_{m_k'}) q(\hat{x}_{m_{\mathcal{K}}''}|x_{m_k'}) f_k'(x_{m_k'})}{\sum_{m_k'} p'(x_{m_k'}) q(\hat{x}_{m_{\mathcal{K}}''}|x_{m_k'}) \cancel{f_k'(x_{m_k})}} \Biggr)                       \\
-				 & = (1 - \rho) \Biggl( 1 - \sum_{m_{\mathcal{K}}''} \frac{\cancel{\sum_{m_k} p'(x_{m_k}) q(\hat{x}_{m_{\mathcal{K}}''}|x_{m_k})}}{\sum_{m_k'} p'(x_{m_k'}) f_k'(x_{m_k'})}                                        \nonumber  \\
-				 & \quad \times \frac{\sum_{m_k'} p'(x_{m_k'}) q(\hat{x}_{m_{\mathcal{K}}''}|x_{m_k'}) f_k'(x_{m_k'})}{\cancel{\sum_{m_k'} p'(x_{m_k'}) q(\hat{x}_{m_{\mathcal{K}}''}|x_{m_k'})}} \Biggr)                                     \\
-				 & = (1 - \rho) \Biggl( 1 - \frac{\sum_{m_k'} p'(x_{m_k'}) f_k'(x_{m_k'}) \sum_{m_{\mathcal{K}}''} q(\hat{x}_{m_{\mathcal{K}}''}|x_{m_k'})}{\sum_{m_k'} p'(x_{m_k'}) f_k'(x_{m_k'})} \Biggr)                        \nonumber \\
-				 & = 0,
-			\end{align}
-		\end{subequations}
-		where $f_k'(x_{m_k}) \triangleq \exp \bigl( \frac{\rho}{1 - \rho} I_k'(x_{m_k}) \bigr)$ and the equality holds if and only if $p(x_{m_{\mathcal{K}}})$ and $p'(x_{m_{\mathcal{K}}})$ equals (i.e., \eqref{eq:optimal_relative_distribution} converges).
-		\eqref{eq:information_difference_lower} and \eqref{eq:information_difference_upper} together imply $I(x_{\mathcal{K}}) \ge I'(x_{\mathcal{K}})$.
-		Since mutual information is bounded above, we conclude the sequence \eqref{eq:input_kkt_solution} is non-decreasing and convergent.
-
-		Next, we prove any converging point of sequence \eqref{eq:input_kkt_solution}, denoted as $p^\star(x_{m_k})$, fulfills the \gls{kkt} conditions \eqref{eq:input_kkt_condition}.
-		Let
-		\begin{equation}
-			D^{(r)}(x_{m_k}) \triangleq \frac{p^{(r+1)}(x_{m_k})}{p^{(r)}(x_{m_k})} = \frac{f_k^{(r)}(x_{m_k})}{\sum_{m_k'} p^{(r)}(x_{m_k'}) f_k^{(r)}(x_{m_k'})}.
-		\end{equation}
-		As sequence \eqref{eq:input_kkt_solution} is convergent, any state with $p^\star(x_{m_k}) > 0$ need to satisfy $D^\star(x_{m_k}) \triangleq \lim_{r \to \infty} D^{(r)}(x_{m_k}) = 1$, namely
-		\begin{equation}
-			I_k^\star(x_{m_k}) = \frac{1 - \rho}{\rho} \log \sum_{m_k'} p^\star(x_{m_k'}) \exp \Bigl( \frac{\rho}{1 - \rho} I_k^\star(x_{m_k'}) \Bigr).
-		\end{equation}
-		The right-hand side is a constant for node $k$ and implies \eqref{eq:probable_states_marginal}.
-		That is, any converging point with nonzero probability must satisfy \eqref{eq:probable_states}.
-		On the other hand, we assume $p^\star(x_{m_k}) = 0$ does not satisfy \eqref{eq:dropped_states}, namely
-		\begin{equation}
-			I_k^\star(x_{m_k}) > I^\star(x_{\mathcal{K}}) = \sum_{m_k'} p^\star(x_{m_k'}) I_k^\star(x_{m_k'}),
-			\label{eq:dropped_states_assumption}
-		\end{equation}
-		Since the exponential function is monotonically increasing, \eqref{eq:dropped_states_assumption} implies $f_k^\star(x_{m_k}) > \sum_{m_k'} p^\star(x_{m_k'}) f_k^\star(x_{m_k'})$ and $D^\star(x_{m_k}) > 1$.
-		It contradicts with
-		\begin{equation}
-			p^{(r)}(x_{m_k}) = p^{(0)}(x_{m_k}) \prod_{n=1}^r D^{(n)}(x_{m_k}),
-		\end{equation}
-		since the left-hand side is zero while all terms on the right-hand side are strictly positive.
-		The proof is completed.
-		\label{ap:input_kkt_solution}
-	\end{subsection}
-\end{appendix}
-
-\begin{section}{Acknowledgement}
-	The authors would like to thank Prof. Geoffrey Ye Li for his clinical comments on earlier versions of the manuscript.
+\begin{section}{Appendix}
+	Full text is available at \url{https://arxiv.org/abs/2212.09121}.
+	Source code will be released at \url{https://github.com/snowztail/riscatter}.
 \end{section}
@@
 \bibliographystyle{IEEEtran}
-\bibliography{library.bib}
+\bibliography{../library.bib}
 \end{document}

### 2023-10-22 review/response.tex
:triangular_flag_on_post: JSAC 231022

@@
 In the previous version of our manuscript, we only introduced papers that use RIS for backscatter modulation.
-In contrast, the recommended reference exploits commodity RFID tags, powered and controlled by a software-defined radio reader, to perform passive beamforming towards a legacy user at a different frequency.
+In contrast, the recommended reference exploited commodity RFID tags, powered and controlled by a software-defined radio reader, to perform passive beamforming towards a legacy user at a different frequency.
 It validates the feasibility of using batteryless devices to adaptively enhance the SNR of the primary link.

### 2023-10-22 arxiv.tex
:triangular_flag_on_post: JSAC 231022

@@
 \begin{abstract}
-	\gls{bc} nodes harvest energy from and modulate information over external electromagnetic waves.
-	\gls{ris} adapts its phase shift response to alter channel strength in specific directions.
-	In this paper, we show how those two seemingly different technologies (and their derivatives) can be unified into one architecture called RIScatter.
-	RIScatter consists of dispersed or co-located scatter nodes, whose reflection states are adapted to partially modulate their information and partially engineer the wireless channel.
+	\gls{bc} nodes harvest energy from and modulate information over external carriers.
+	\gls{ris} adapts phase shift response to alter channel strength in specific directions.
+	In this paper, we unify those two seemingly different technologies (and their derivatives) into one architecture called RIScatter.
+	RIScatter is a batteryless cognitive radio that recycles ambient signal in an adaptive and customizable manner, where dispersed or co-located scatter nodes partially modulate their information and partially engineer the wireless channel.
 	The key is to render the probability distribution of reflection states as a joint function of the information source, \gls{csi}, and relative priority of coexisting links.
-	This enables RIScatter to softly bridge \gls{bc} and \gls{ris}; reduce to either under specific setup; or evolve in a mixed form for heterogeneous traffic control and universal hardware design.
+	This enables RIScatter to softly bridge \gls{bc} and \gls{ris}; reduce to either in special cases; or evolve in a mixed form for heterogeneous traffic control and universal hardware design.
 	We also propose a low-complexity \gls{sic}-free receiver that exploits the properties of RIScatter.
 	For a single-user multi-node network, we characterize the achievable primary-(total-)backscatter rate region by optimizing the input distribution at scatter nodes, the active beamforming at the \gls{ap}, and the energy decision regions at the user.
-	Simulations demonstrate RIScatter nodes can recycle surrounding radios for backscatter modulation and passive beamforming.
+	Simulations demonstrate RIScatter nodes can shift between backscatter modulation and passive beamforming.
 \end{abstract}
@@
 	Such a coexistence is classified into commensal (overlay), parasitic (underlay), and competitive (interfering) paradigms, and their achievable rate and outage performance were investigated in \cite{Guo2019b,Ding2020}.
-	The achievable rate and optimal input distribution for binary-input \gls{ambc} are investigated in \cite{Qian2019b}, but its impact on the primary link is omitted.
+	The achievable rate and optimal input distribution for binary-input \gls{ambc} were investigated in \cite{Qian2019b}, but its impact on the primary link was omitted.
 	% For binary-input \gls{ambc},  are investigated in \cite{Qian2019b}, but the authors did not consider its impact on the primary link.
@@
 	\end{enumerate}
-	The second property motivated \cite{Long2020a,Liang2020,Guo2019b,Ding2020,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Yang2018,Han2021,Zhang2022,Dai2023} to view \gls{sr} as a multiplicative \gls{noma} and perform \gls{sic} from primary to backscatter link.
+	The second property motivated \cite{Long2020a,Liang2020,Guo2019b,Ding2020,Hassani2023,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Yang2018,Han2021,Zhang2022,Dai2023} to view \gls{sr} as a multiplicative \gls{noma} and perform \gls{sic} from primary to backscatter link.
 	During primary decoding, the backscatter signal can be modelled as channel uncertainty or multiplicative interference, when the spreading factor is large or small.
 	Decoding each backscatter symbol also requires multiple \gls{sic} followed by a \gls{mrc} over primary blocks, which is operation-intensive and \gls{csi}-sensitive.
-	Under those assumptions, the achievable rate region of cell-free \gls{sr} is characterized in \cite{Dai2023}.
+	Under those assumptions, the achievable rate region of cell-free \gls{sr} was characterized in \cite{Dai2023}.
 	When the spreading factor is sufficiently large, the primary achievable rate under semi-coherent detection\footnote{In this paper, semi-coherent detection refers to the primary/backscatter decoding with known \gls{csi} and unknown backscatter/primary symbols.} asymptotically approaches its coherent counterpart such that both links are approximately interference-free \cite{Long2020a}.
@@
 	Those \gls{ris}-based backscatter modulation schemes incur advanced hardware architecture and high optimization complexity.
-	In contrast, \cite{Vardakis2023} exploits commodity \gls{rfid} tags, powered and controlled by a software-defined radio reader at a different frequency, to perform passive beamforming (but no backscatter modulation) towards a legacy user.
+	In contrast, \cite{Vardakis2023} exploited commodity \gls{rfid} tags, powered and controlled by a software-defined radio reader at a different frequency, to perform passive beamforming (but no backscatter modulation) towards a legacy user.
 \label{cm:2.5}
 	% The authors demonstrated the feasibility of using batteryless devices to adaptively enhance the \gls{snr} of a primary link, but did not consider backscatter modulation at.
-	Most relevant literature considers either Gaussian codebook \cite{Guo2019b,Ding2020,Long2020a,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Hu2021b} that is impractical for low-power nodes, or finite equiprobable inputs \cite{Yang2018,Liang2020,Han2021,Zhang2022,Liu2019d,Bereyhi2020,Xu2020b,Zhang2021d,Hua2022,Basar2020,Ma2020a,Yuan2021,Hu2021a} that does not fully exploit the \gls{csi} and properties of active-passive coexisting networks.
+	Most relevant literature considered either Gaussian codebook \cite{Guo2019b,Ding2020,Long2020a,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Hu2021b} that is impractical for low-power nodes, or finite equiprobable inputs \cite{Yang2018,Liang2020,Han2021,Zhang2022,Liu2019d,Bereyhi2020,Xu2020b,Zhang2021d,Hua2022,Basar2020,Ma2020a,Yuan2021,Hu2021a} that does not fully exploit the \gls{csi} and properties of active-passive coexisting networks.
 	Those problems are addressed in this paper and the contributions are summarized below.
@@
 	A co-located receiver cooperatively decodes both coexisting links.
-	Each reflection state is simultaneously an information codeword and a passive beamforming codeword.
+	Each reflection state is simultaneously a passive beamforming codeword and part of information codeword.
 	The reflection pattern over time is semi-random and guided by the input probability assigned to each state.
@@
 			\item \gls{bc}: The scatterer is an information source with random reflection pattern over time.
-			The reflection coefficient is used merely as an information codeword \cite{Thomas2012a}
+			The reflection coefficient is used merely as part of information codeword \cite{Thomas2012a}
 			\begin{equation}
@@
 		RIScatter generalizes \gls{bc} and \gls{ris} from a probabilistic perspective.
-		Each reflection coefficient simultaneously acts as an information codeword and a passive beamforming codeword.
+		Each reflection coefficient simultaneously acts as a passive beamforming codeword and part of information codeword.
 		As shown in Fig.~\ref{fg:scatter_comparison}, the reflection pattern of each RIScatter node over time is semi-random and guided by the input probability assigned to each state.
@@
 		\begin{remark}
-			We have assumed Gaussian codebook for the primary source and finite support for the backscatter nodes, since they are relatively practical and widely adopted in relevant literatures.
+			We have assumed Gaussian codebook for the primary source and finite support for the backscatter nodes, since they are relatively practical and widely adopted in relevant literatures \cite{Long2020a,Liang2020,Guo2019b,Qian2019b,Ding2020,Hassani2023,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Yang2018,Han2021,Zhang2022,Dai2023}.
 			The proposed framework is extendable to non-Gaussian primary source, and the conditional \gls{pdf} \eqref{eq:energy_distribution} can be approximated using \gls{clt} for large $N$.
@@
 	We set $b=9$ and $\varepsilon=\num{e-3}$.
-	All achievable rate regions are averaged over \num{e3} channel realizations.
+	All achievable rate regions are averaged over \num{e3} channel realizations.\footnote{The code is publicly available at \url{https://github.com/snowztail/riscatter/}.}
 

### 2023-10-22 misc/abstract.tex
:triangular_flag_on_post: JSAC 231022

@@
 	\label{sc:riscatter}
-	For passive RIScatter nodes, each reflection state is simultaneously an information codeword and a passive beamforming codeword.
+	For passive RIScatter nodes, each reflection state is simultaneously a passive beamforming codeword and part of information codeword.
 	The nodes randomize the reflection pattern over time while still guaranteeing the probability of occurrence of each state.

### 2023-10-22 arxiv.tex
:triangular_flag_on_post: JSAC 231022

@@
 		\begin{remark}
-			We have assumed Gaussian codebook for the primary source and finite support for the backscatter nodes, since they are relatively practical and widely adopted in relevant literatures \cite{Long2020a,Liang2020,Guo2019b,Qian2019b,Ding2020,Hassani2023,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Yang2018,Han2021,Zhang2022,Dai2023}.
+			We have assumed Gaussian codebook for the primary source and finite support for the backscatter nodes, since they are relatively practical and widely adopted in relevant literatures \cite{Qian2019b,Xu2020b,Zhang2021d,Hua2022,Hu2021a,Qian2019}.
 			The proposed framework is extendable to non-Gaussian primary source, and the conditional \gls{pdf} \eqref{eq:energy_distribution} can be approximated using \gls{clt} for large $N$.

### 2023-10-22 assets/poster/discrete_outputs.tex
:camera_flash: Add poster

--- 2022-11-25 assets/illustration/discrete_outputs.tex
@@
-\begin{tikzpicture}
+\begin{tikzpicture}[font=\tiny]
 	\begin{axis}[width=10cm,height=5cm,xmin=0,xmax=6.5,ymin=-0.1,ymax=0.1,xlabel=$z$,axis x line=middle,axis y line=none,xtick={0,2,3,4,6},xticklabels={$t_0$,$t_1$,$t_2$,$t_3$,$t_4$},xtick style={draw=none},every axis x label/.style={at=(current axis.right of origin),anchor=west},domain=0:6]
-		\addplot[mark=*,mark size=0.5pt,only marks,color=gray] {0};
-		\addplot[mark=*,mark size=1pt,only marks,color=black] coordinates{(0,0) (2,0) (3,0) (4,0) (6,0)};
+		\addplot[mark=*,mark size=1pt,only marks,color=gray] {0};
+		\addplot[mark=*,mark size=1.5pt,only marks,color=black] coordinates{(0,0) (2,0) (3,0) (4,0) (6,0)};
 		\draw[decorate,decoration={brace,amplitude=10}] (0,0) -- (2,0) node[above,midway,yshift=10]{$\mathcal{R}_1$};

### 2023-10-22 assets/poster/energy_distribution.tex
:camera_flash: Add poster

--- 2022-11-11 assets/illustration/energy_distribution.tex
@@
 			clip mode=individual,
-			height=4cm,
+			height=5cm,
 			width=10cm,
+			inner sep=1pt,
+			outer sep=1pt,
 			xlabel = $z$,
-			ylabel = {Probability Density},
-			font=\normalsize,
+			ylabel = {PDF},
+			font=\tiny,
 			no markers,
@@
 			yticklabels=\empty,
+			% enlargelimits=false,
+			legend style={fill=none},
 			samples = 200
@@
 				plot gmm(x,10,1)};
-		\addlegendentryexpanded{$f(z \mid \mathcal{H}_1)$}
+		\addlegendentryexpanded{$f(z \mid x_1)$}
 
@@
 				plot gmm(x,10,0.6)};
-		\addlegendentryexpanded{$f(z \mid \mathcal{H}_2)$}
+		\addlegendentryexpanded{$f(z \mid x_2)$}
 
@@
 				plot gmm(x,10,0.4)};
-		\addlegendentryexpanded{$f(z \mid \mathcal{H}_3)$}
+		\addlegendentryexpanded{$f(z \mid x_3)$}
 
@@
 				plot gmm(x,10,0.28)};
-		\addlegendentryexpanded{$f(z \mid \mathcal{H}_4)$}
+		\addlegendentryexpanded{$f(z \mid x_4)$}
 		\draw[latex-latex] (0,0) -- (12.78,0) node[above,midway,yshift=-2]{$\mathcal{R}_1$};

### 2023-10-22 assets/poster/input_distribution.tex
:camera_flash: Add poster

--- 2023-02-25 assets/illustration/input_distribution.tex
@@
-\begin{tikzpicture}
+\begin{tikzpicture}[font=\tiny]
 	\begin{groupplot}
@@
 			enlarge y limits={value=0.1,upper},
-			width=10cm,
-			height=2.6cm,
+			width=11.6cm,
+			height=3cm,
+			x tick style={draw=none},
+			x label style={inner sep=5.5pt},
+			% font=\tiny,
+			legend style={fill=none},
 			every axis plot/.append style={bar shift=0}

### 2023-10-22 assets/poster/receiver.tex
:camera_flash: Add poster

\begin{tikzpicture}[
		% every axis plot/.append style={thick},
		every node/.append style={draw,minimum width=16cm},
		align=center
	]
	\draw[-{Latex[length=4mm]}] (0,0) node[anchor=south](0){Semi-coherently decode node message} to ++(0,-1) node[anchor=north](1){Re-encode for reflection pattern};
	\draw[-{Latex[length=4mm]}] (1.south) to ++(0,-1) node[anchor=north](2){Model within equivalent channel};
	\draw[-{Latex[length=4mm]}] (2.south) to ++(0,-1) node[anchor=north](3){Coherently decode primary message};
\end{tikzpicture}

### 2023-10-22 assets/poster/region_comparison.tex
:camera_flash: Add poster

--- 2023-08-05 assets/simulation/region_comparison.tex
@@
 	\begin{axis}[%
-width=4.014in,
-height=1.552in,
+			width=10cm,
+			height=5.55cm,
 			at={(0.673in,0.356in)},
@@
 			ylabel style={font=\color{white!15!black}},
-ylabel={Backscatter\\Rate [bits/BB]},
-axis background/.style={fill=white},
+			ylabel={Backscatter Rate [bits/cu]},
+			% axis background/.style={fill=white},
 			xmajorgrids,
 			ymajorgrids,
-legend style={at={(0.03,0.97)}, anchor=north west, legend cell align=left, align=left, draw=white!15!black},
+			legend style={at={(0.03,0.97)}, anchor=north west, legend cell align=left, align=left, draw=white!15!black, fill=none},
 			align=center,
-title style={font=\LARGE},
-label style={font=\LARGE},
-ticklabel style={font=\Large},
-legend style={font=\Large},
+			font=\tiny,
+			title style={font=\tiny},
+			label style={font=\tiny},
+			ticklabel style={font=\tiny},
+			legend style={font=\tiny},
 			reverse legend,
@@
 			};
-\addlegendentry{BBC}
+		\addlegendentry{Backscatter-only}
 
@@
 			};
-\addlegendentry{Legacy}
+		\addlegendentry{Primary-only}
 

### 2023-10-22 assets/poster/riscatter.tex
:camera_flash: Add poster

--- 2022-11-25 assets/illustration/riscatter.tex
@@
-\begin{tikzpicture}[font=\LARGE,every node/.style={draw,ultra thick},every path/.style={ultra thick},every text node part/.style={align=center}]
+\begin{tikzpicture}[font=\tiny,every node/.style={draw,ultra thick},every path/.style={ultra thick},every text node part/.style={align=center}]
 	\node at (0,0) [circular sector,shape border rotate=90,minimum width=2cm] {};
@@
 	\draw[blue,decorate,decoration={waves,segment length=4mm,radius=2mm}] (6,3.1625) -- (8,1.25);
-	\draw[green,decorate,decoration={crosses,segment length=8mm,shape size=1.5mm}] (6.29,2.885) -- (8,1.25);
+	\draw[red,decorate,decoration={crosses,segment length=8mm,shape size=1.5mm}] (6.29,2.885) -- (8,1.25);
 

### 2023-10-22 assets/poster/scatter_model.tex
:camera_flash: Add poster

--- 2022-11-28 assets/illustration/scatter_model.tex
@@
 \begin{circuitikz}[transform shape]
-	\tikzstyle{every node}=[font=\large]
+	\tikzstyle{every node}=[font=\tiny]
 	\ctikzset{multipoles/rotary/arrow=both}
@@
 	\draw (WR.south east) ++(0.35,0) node{$\vec{H}_m$};
-	\draw (bareantenna) to ++(0,-1.1) to [generic,l=$Z_{\text{A}}$,/tikz/circuitikz/bipoles/length=0.75cm] ++(2.3,0) node[rotary switch=4 in 90 wiper 30,anchor=ext center,rotate=0](SW){};
+	\draw (bareantenna) to ++(0,-1.1) to [generic,l_=$Z_{\text{A}}$,/tikz/circuitikz/bipoles/length=0.75cm] ++(2.3,0) node[rotary switch=4 in 90 wiper 30,anchor=ext center,rotate=0](SW){};
 	\draw (SW.cout 1) to ++(0.625,+0.5) to [generic,/tikz/circuitikz/bipoles/length=0.75cm] ++(2.2,0) coordinate(E1);
-	\draw (SW.cout 2) node[above right]{$m$} to [generic,l=$Z_m$,/tikz/circuitikz/bipoles/length=0.75cm] ++(2.2,0) coordinate(E2);
+	\draw (SW.cout 2) node[above right,yshift=-0.2cm]{$m$} to [generic,/tikz/circuitikz/bipoles/length=0.75cm] ++(2.2,0) coordinate(E2);
 	\draw (SW.cout 3) to [generic,/tikz/circuitikz/bipoles/length=0.75cm] ++(2.2,0) coordinate(E3);

### 2023-10-22 poster/beamer.tex
:camera_flash: Add poster

\documentclass[final,xcolor={table}]{beamer}
%% Possible paper sizes: a0, a0b, a1, a2, a3, a4.
%% Possible orientations: portrait, landscape
%% Font sizes can be changed using the scale option.
\usepackage[size=a0,orientation=landscape]{beamerposter}

\usetheme{gemini}
\usecolortheme{seagull}
\useinnertheme{rectangles}
\usefonttheme[onlymath]{serif}

\setlength\lineskip{20pt}
% \let\OLDitemize\itemize
% \renewcommand\itemize{\OLDitemize\addtolength{\itemsep}{20pt}}
\renewcommand\baselinestretch{1.25}

% ====================
% Packages
% ====================

% \usepackage[utf8]{inputenc}
% \usepackage[table]{xcolor}
\usepackage{adjustbox}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{tikz}
\usepackage{pgfplots}
\usepackage[T1]{fontenc}
\usepackage[sfdefault]{FiraSans}
\usepackage[acronym]{glossaries-extra}
\usepackage{siunitx}
\usepackage[caption=false,font=footnotesize,subrefformat=parens,labelformat=parens]{subfig}
\usepackage{tabularx}
\usepackage[american]{circuitikz}
\usepackage[short]{optidef}

\usetikzlibrary{arrows,calc,matrix,patterns,plotmarks,positioning,shapes}
\usetikzlibrary{decorations.pathmorphing,decorations.pathreplacing,decorations.shapes,shapes.geometric}
\usepgfplotslibrary{groupplots,patchplots}
\pgfplotsset{compat=newest}

\glsdisablehyper
\setabbreviationstyle[acronym]{long-short}
\newacronym{af}{AF}{Amplify-and-Forward}
\newacronym{ambc}{AmBC}{Ambient Backscatter Communication}
\newacronym{ap}{AP}{Access Point}
\newacronym{awgn}{AWGN}{Additive White Gaussian Noise}
\newacronym{bcd}{BCD}{Block Coordinate Descent}
\newacronym{bc}{BackCom}{Backscatter Communication}
\newacronym{bibo}{BIBO}{Binary-Input Binary-Output}
\newacronym{bpcu}{\si{bpcu}}{bits per channel use}
\newacronym{bpsphz}{\si{bps/Hz}}{bits per second per Hertz}
\newacronym{clt}{CLT}{Central Limit Theorem}
\newacronym{cw}{CW}{Continuous Waveform}
\newacronym{cp}{CP}{Canonical Polyadic}
\newacronym{cr}{CR}{Cognitive Radio}
\newacronym{cscg}{CSCG}{Circularly Symmetric Complex Gaussian}
\newacronym{csi}{CSI}{Channel State Information}
\newacronym{dc}{DC}{Direct Current}
\newacronym{df}{DF}{Decode-and-Forward}
\newacronym{dmc}{DMC}{Discrete Memoryless Channel}
\newacronym{dmtc}{DMTC}{Discrete Memoryless Thresholding Channel}
\newacronym{dmmac}{DMMAC}{Discrete Memoryless Multiple Access Channel}
\newacronym{dcmc}{DCMC}{Discrete-input Continuous-output Memoryless Channel}
\newacronym{dp}{DP}{Dynamic Programming}
\newacronym{fdma}{FDMA}{Frequency-Division Multiple Access}
\newacronym{iid}{i.i.d.}{independent and identically distributed}
\newacronym{ioe}{IoE}{Internet of Everything}
\newacronym{iot}{IoT}{Internet of Things}
\newacronym{kkt}{KKT}{Karush-Kuhn-Tucker}
\newacronym{m2m}{M2M}{Machine to Machine}
\newacronym{mac}{MAC}{Multiple Access Channel}
\newacronym{mc}{MC}{Multiplication Coding}
\newacronym{miso}{MISO}{Multiple-Input Single-Output}
\newacronym{mimo}{MIMO}{Multiple-Input Multiple-Output}
\newacronym{ml}{ML}{Maximum-Likelihood}
\newacronym{mrt}{MRT}{Maximum Ratio Transmission}
\newacronym{noma}{NOMA}{Non-Orthogonal Multiple Access}
\newacronym{ofdm}{OFDM}{Orthogonal Frequency-Division Multiplexing}
\newacronym{pdf}{PDF}{Probability Density Function}
\newacronym{pga}{PGA}{Projected Gradient Ascent}
\newacronym{psk}{PSK}{Phase Shift Keying}
\newacronym{qam}{QAM}{Quadrature Amplitude Modulation}
\newacronym{qos}{QoS}{Quality of Service}
\newacronym{rf}{RF}{Radio-Frequency}
\newacronym{rfid}{RFID}{Radio-Frequency Identification}
\newacronym{ris}{RIS}{Reconfigurable Intelligent Surface}
\newacronym{sc}{SC}{Superposition Coding}
\newacronym{sic}{SIC}{Successive Interference Cancellation}
\newacronym{simo}{SIMO}{Single-Input Multiple-Output}
\newacronym{sinr}{SINR}{Signal-to-Interference-plus-Noise Ratio}
\newacronym{smawk}{SMAWK}{Shor-Moran-Aggarwal-Wilber-Klawe}
\newacronym{snr}{SNR}{Signal-to-Noise Ratio}
\newacronym{sr}{SR}{Symbiotic Radio}
\newacronym{swipt}{SWIPT}{Simultaneous Wireless Information and Power Transfer}
\newacronym{tdma}{TDMA}{Time-Division Multiple Access}
\newacronym{ue}{UE}{user}
\newacronym{wit}{WIT}{Wireless Information Transfer}
\newacronym{wpcn}{WPCN}{Wireless Powered Communication Network}
\newacronym{wpt}{WPT}{Wireless Power Transfer}
\newacronym{mbc}{MBC}{Monostatic \glsentryshort{bc}}
\newacronym{bbc}{BBC}{Bistatic \glsentryshort{bc}}
\newacronym{bls}{BLS}{Backtracking Line Search}
\newacronym{mrc}{MRC}{Maximal Ratio Combining}
\newacronym{sdma}{SDMA}{Space-Division Multiple Access}
\newacronym{nlos}{NLoS}{Non-Line-of-Sight}
\newacronym{zf}{ZF}{Zero-Forcing}
\newacronym{mmse}{MMSE}{Minimum Mean-Square-Error}
\newacronym{fpga}{FPGA}{Field-Programmable Gate Array}
\newacronym{ber}{BER}{Bit Error Rate}

% ====================
% Lengths
% ====================

% If you have N columns, choose \sepwidth and \colwidth such that
% (N+1)*\sepwidth + N*\colwidth = \paperwidth
\newlength{\sepwidth}
\newlength{\colwidth}
\setlength{\sepwidth}{0.025\paperwidth}
\setlength{\colwidth}{0.3\paperwidth}
% \setlength{\sepwidth}{0.03\paperwidth}
% \setlength{\colwidth}{0.45\paperwidth}

\newcommand{\separatorcolumn}{\begin{column}{\sepwidth}\end{column}}

% ====================
% Logo (optional)
% ====================

% LaTeX logo taken from https://commons.wikimedia.org/wiki/File:LaTeX_logo.svg
% use this to include logos on the left and/or right side of the header:
\logoleft{\includegraphics[height=4cm]{../assets/poster/icl.eps}}
\logoright{\includegraphics[height=4cm]{../assets/poster/qr.pdf}}

% ====================
% Footer (optional)
% ====================

\footercontent{
	SAL 6G Symposium, Linz, Austria \hfill
	November 22 \& 23, 2023 \hfill
	\href{mailto:yang.zhao18@imperial.ac.uk}{\texttt{yang.zhao18@imperial.ac.uk}}
}
% (can be left out to remove footer)

% ====================
% My own customization
% - BibLaTeX
% - Boxes with tcolorbox
% - User-defined commands
% ====================
\input{custom-defs.tex}

%% Reference Sources
% \addbibresource{library.bib}
\renewcommand{\pgfuseimage}[1]{\includegraphics[scale=2.0]{#1}}

\title{RIScatter: Unifying Backscatter Communication and Reconfigurable Intelligent Surface}

\author{Yang Zhao \and Bruno Clerckx}

\date{January 01, 2025}

\begin{document}

\begin{frame}[t]
	\begin{columns}[t]
		\separatorcolumn

		\begin{column}{\colwidth}
			\begin{block}{Overview}
				\begin{itemize}\setlength\itemsep{20pt}
					\item \textbf{What does this paper propose?}

					RIScatter -- a batteryless cognitive radio that recycles ambient signal in an adaptive and customizable manner.
					\item \textbf{How does it differ from previous work?}

					Backscatter modulation and passive beamforming are seamlessly integrated from the perspective of probability distribution.
					\item \textbf{What are the benefits?}

					It supports cooperative and distributed deployment, avoids complex architecture and signal processing, and can be built over legacy systems.
				\end{itemize}
			\end{block}

			\begin{block}{RIScatter system}
				\begin{figure}[!t]
					\centering
					\resizebox{0.5\linewidth}{!}{
						\input{../assets/poster/riscatter.tex}
					}
					\label{fg:riscatter}
				\end{figure}
				\begin{itemize}\setlength\itemsep{20pt}
					\item {\color{blue}Primary link:} active ambient transmission from an RF source
					\item {\color{red}Backscatter link:} passive free-ride transmission from IoT nodes
				\end{itemize}
			\end{block}

			\begin{block}{Node architecture}
				\begin{figure}[!t]
					\captionsetup[subfloat]{captionskip=20pt}
					\centering
					\subfloat[Block Diagram]{
						\resizebox{0.53\linewidth}{!}{
							\input{../assets/poster/block_diagram.tex}
						}
						\label{fg:block_diagram}
					}
					\subfloat[Scatter Model]{
						\resizebox{0.42\linewidth}{!}{
							\input{../assets/poster/scatter_model.tex}
						}
						\label{fg:scatter_model}
					}
					\label{fg:riscatter_node}
				\end{figure}
				\vspace{0.62cm}
				\begin{itemize}\setlength\itemsep{20pt}
					\item Wave scattering or reflection are manipulated by antenna or metamaterial
					\item Incoming signals are used for powering, modulation, and beamforming
					\item The node changes reflection state by switching load impedance
					% \item A reflection state corresponds to a load impedance
				\end{itemize}
			\end{block}

			\begin{alertblock}{Properties}
				\begin{enumerate}\setlength\itemsep{20pt}
					\item Primary and backscatter symbols are superimposed by \emph{double modulation}
					\item Backscatter signal is much weaker due to \emph{double fading}
					\item The spreading factor (symbol period ratio) is usually large
					\item Each \emph{state} is simultaneously part of information and beamforming \emph{codeword}
					\item Reflection pattern over time is semi-random and guided by input probability assigned to each state
				\end{enumerate}
			\end{alertblock}
		\end{column}

		\separatorcolumn

		\begin{column}{2\colwidth+\sepwidth}
			\begin{block}{Applications comparison}
				\begin{table}[!t]
					\rowcolors{2}{gray!25}{white}
					\renewcommand{\arraystretch}{1.25}
					\begin{tabular}{c c c c c c}
						\toprule
						\hiderowcolors
						                       & Backscatter        & Ambient backscatter         & Symbiotic radio          & Reconfigurable intelligent surface & RIScatter                                          \\ \midrule
						\showrowcolors
						Information link(s)    & Backscatter        & Coexisting                  & Coexisting               & Primary                            & Coexisting                                         \\
						Primary on backscatter & Carrier            & Multiplicative interference & Spreading code           & ---                                & Energy uncertainty                                 \\
						Backscatter on primary & ---                & Multiplicative interference & Channel uncertainty      & Passive beamforming                & Dynamic passive beamforming                        \\
						Cooperative devices    & ---                & No                          & Transmitter and receiver & ---                                & Transmitter, nodes, and receiver                   \\
						Sequential decoding    & ---                & No                          & Primary-to-backscatter   & ---                                & Backscatter-to-primary                             \\
						Reflection pattern by  & Information source & Information source          & Information source       & Channel                            & Information source, channel, and relative priority \\
						Input distribution     & Equiprobable       & Equiprobable                & Equiprobable or Gaussian & Degenerate                         & Flexible                                           \\
						Load-switching speed   & Fast               & Slow                        & Slow                     & Quasi-static                       & Arbitrary                                          \\ \bottomrule
					\end{tabular}
				\end{table}
			\end{block}

			\vspace{-1.3cm}
			\begin{columns}[t,totalwidth=\textwidth]
				\begin{column}{\colwidth}
					\begin{block}{Low-complexity receiver}
						\begin{figure}[!t]
							\centering
							\subfloat{
								\resizebox{0.42\linewidth}{!}{
									\input{../assets/poster/receiver.tex}
								}
							}
							\hspace{-1.5cm}
							\subfloat{
								\resizebox{0.58\linewidth}{!}{
									\input{../assets/poster/energy_distribution.tex}
								}
							}
							\label{fg:receiver}
						\end{figure}
						\vspace{0.5cm}
						\begin{itemize}\setlength\itemsep{20pt}
							\item Accumulated receive energy follows conditional Gamma distribution
							\item Node detection under primary uncertainty becomes part of channel training
							\item Requires one additional energy comparison and re-encoding per backscatter symbol
							% \item Backscatter achievable rate depends on decision region design
						\end{itemize}
					\end{block}

					\begin{block}{Problem formulation}
						\vspace{-0.5cm}
						\begin{columns}[c,totalwidth=\textwidth]
							\begin{column}{0.48\colwidth}
								\begin{maxi*}
									{\scriptstyle{\{\boldsymbol{p}_k\},\boldsymbol{w},\boldsymbol{t}}}{\rho R_\text{P} + (1-\rho) \sum_k R_{\text{B},k}}{}{}
									\addConstraint{\boldsymbol{1}^\mathsf{T} \boldsymbol{p}_k=1,}{\quad \boldsymbol{p}_k \ge \boldsymbol{0},}{\quad \forall k}
									\addConstraint{t_{l-1} \le t_l,}{\quad t_l \ge 0,}{\quad \forall l}
									\addConstraint{\lVert \boldsymbol{w} \rVert^2 \le P}{}{}
								\end{maxi*}
							\end{column}
							\begin{column}{0.48\colwidth}
								\begin{itemize}\setlength\itemsep{20pt}
									% \item $\rho$ is the priority of the primary link
									\item $\boldsymbol{p}_k$ is the input distribution of node $k$
									\item $\boldsymbol{w}$ is the active beamforming vector
									\item $\boldsymbol{t}$ is the decision threshold vector
								\end{itemize}
							\end{column}
						\end{columns}
					\end{block}

					\begin{thm}{Input distribution}{}
						\begin{equation*}
							p^{(r+1)}(x_{m_k}) \gets \frac{p^{(r)}(x_{m_k}) \exp \Bigl( \frac{\rho}{1 - \rho} I_k^{(r)}(x_{m_k}) \Bigr)}{\sum_{m_k'} p^{(r)}(x_{m_k'}) \exp \Bigl( \frac{\rho}{1 - \rho} I_k^{(r)}(x_{m_k'}) \Bigr)}
							\label{eq:input_kkt_solution}
						\end{equation*}
					\end{thm}

					\begin{thm}{Decision threshold}{}
						\begin{figure}[!t]
							\centering
							\resizebox{0.65\linewidth}{!}{
								\input{../assets/poster/discrete_outputs.tex}
							}
						\end{figure}
						\begin{itemize}\setlength\itemsep{15pt}
							% \item Constrain the domain to fine-grained energy levels
							\item Obtain the rate-optimal quantization by dynamic programming or bisection
						\end{itemize}
					\end{thm}

					\begin{thm}{Active beamformer}{}
						\begin{equation*}
							\boldsymbol{w}^{(r+1)} \gets \mathrm{proj}_{\lVert \boldsymbol{w} \rVert^2 \le P}\Bigl(\boldsymbol{w}^{(r)}+\gamma\nabla_{\boldsymbol{w}^*} R^{(r)}\Bigr),
							\label{eq:beamforming_gradient_ascent}
						\end{equation*}
					\end{thm}
				\end{column}

				\separatorcolumn
				\begin{column}{\colwidth}
					\begin{exampleblock}{Input distribution}
						\begin{figure}[!t]
							\centering
							\subfloat{
								\resizebox{0.48\linewidth}{!}{
									\input{../assets/poster/input_distribution.tex}
								}
							}
							\subfloat{
								\resizebox{0.48\linewidth}{!}{
									\input{../assets/poster/distribution_weights.tex}
								}
							}
						\end{figure}
						Backscatter communication and reconfigurable intelligent surface are special cases of RIScatter with uniform and degenerate input distribution.
						Increasing $\rho$ from 0 to 1 creates a smooth transition from backscatter modulation to passive beamforming.
					\end{exampleblock}
					\begin{exampleblock}{Rate region}
						\begin{figure}[!t]
							\centering
							\subfloat{
								\resizebox{0.48\linewidth}{!}{
									\input{../assets/poster/region_comparison.tex}
								}
							}
							\subfloat{
								\resizebox{0.48\linewidth}{!}{
									\input{../assets/poster/region_duration.tex}
								}
							}
						\end{figure}
						RIScatter backscatter rate is lower than symbiotic radio (due to energy detection) but higher than ambient backscatter (due to adaptive encoding).
						% Throughput depends on the spreading factor $N$.
						For backscatter link, a large spreading factor improves the bit error rate but reduces the gross data rate.
					\end{exampleblock}

					\begin{block}{Conclusion}
						\begin{itemize}\setlength\itemsep{20pt}
							\item Cognitive active and passive transmission can benefit each other
							\item RIScatter nodes recycle ambient signal for modulation and beamforming
							\item No interference cancellation is required at the co-located receiver
							\item The key is to render the input distribution as a joint function of the information source, channel state information, and priority of coexisting links
						\end{itemize}
					\end{block}
				\end{column}
			\end{columns}
		\end{column}

		\separatorcolumn
	\end{columns}

	% \begin{columns}[t]

	% 	\begin{column}{2\colwidth+\sepwidth}
	% 		\begin{block}{Overview \& Motivation}
	% 			\begin{itemize}
	% 				\item What is backscatter communication?
	% 				\item What is reconfigurable intelligent surface?
	% 			\end{itemize}
	% 		\end{block}
	% 	\end{column}

	% \end{columns}

	% \begin{columns}[t]
	% 	\separatorcolumn

	% 	\begin{column}{\colwidth}

	% 		\begin{thm}{A \texttt{tcolorbox} theorem block containing a list}{}

	% 			Nam vulputate nunc felis, non condimentum lacus porta ultrices. Nullam sed
	% 			sagittis metus. Etiam consectetur gravida urna quis suscipit.

	% 			\begin{itemize}
	% 				\item \textbf{Mauris tempor} risus nulla, sed ornare
	% 				\item \textbf{Libero tincidunt} a duis congue vitae
	% 				\item \textbf{Dui ac pretium} morbi justo neque, ullamcorper
	% 			\end{itemize}

	% 			Eget augue porta, bibendum venenatis tortor.

	% 		\end{thm}

	% 		\begin{alertblock}{A highlighted block}

	% 			This block catches your eye, so \textbf{important stuff} should probably go
	% 			here.

	% 			Curabitur eu libero vehicula, cursus est fringilla, luctus est. Morbi
	% 			consectetur mauris quam, at finibus elit auctor ac. Aliquam erat volutpat.
	% 			Aenean at nisl ut ex ullamcorper eleifend et eu augue. Aenean quis velit
	% 			tristique odio convallis ultrices a ac odio.

	% 			\begin{itemize}
	% 				\item \textbf{Fusce dapibus tellus} vel tellus semper finibus. In
	% 				consequat, nibh sed mattis luctus, augue diam fermentum lectus.
	% 				\item \textbf{In euismod erat metus} non ex. Vestibulum luctus augue in
	% 				mi condimentum, at sollicitudin lorem viverra.
	% 			\end{itemize}

	% 			\begin{enumerate}
	% 				\item \textbf{Morbi mauris purus}, egestas at vehicula et, convallis
	% 				accumsan orci. Orci varius natoque penatibus et magnis dis parturient
	% 				montes, nascetur ridiculus mus.
	% 				\item \textbf{Cras vehicula blandit urna ut maximus}. Aliquam blandit nec
	% 				massa ac sollicitudin. Curabitur cursus, metus nec imperdiet bibendum,
	% 				velit lectus faucibus dolor, quis gravida metus mauris gravida turpis.
	% 			\end{enumerate}

	% 			Aenean tincidunt risus eros, at gravida lorem sagittis vel. Vestibulum ante
	% 			ipsum primis in faucibus orci luctus et ultrices posuere cubilia Curae.

	% 		\end{alertblock}

	% 		\begin{defbox}{A block containing an enumerated list}{}

	% 			Vivamus congue volutpat elit non semper. Praesent molestie nec erat ac
	% 			interdum. In quis suscipit erat. \textbf{Phasellus mauris felis, molestie
	% 				ac pharetra quis}, tempus nec ante. Donec finibus ante vel purus mollis
	% 			fermentum. Sed felis mi, pharetra eget nibh a, feugiat eleifend dolor. Nam
	% 			mollis condimentum purus quis sodales. Nullam eu felis eu nulla eleifend
	% 			bibendum nec eu lorem. Vivamus felis velit, volutpat ut facilisis ac,
	% 			commodo in metus.

	% 			\begin{enumerate}
	% 				\item \textbf{Morbi mauris purus}, egestas at vehicula et, convallis
	% 				accumsan orci. Orci varius natoque penatibus et magnis dis parturient
	% 				montes, nascetur ridiculus mus.
	% 				\item \textbf{Cras vehicula blandit urna ut maximus}. Aliquam blandit nec
	% 				massa ac sollicitudin. Curabitur cursus, metus nec imperdiet bibendum,
	% 				velit lectus faucibus dolor, quis gravida metus mauris gravida turpis.
	% 				\item \textbf{Vestibulum et massa diam}. Phasellus fermentum augue non
	% 				nulla accumsan, non rhoncus lectus condimentum.
	% 			\end{enumerate}

	% 		\end{defbox}

	% 		\begin{block}{Fusce aliquam magna velit}

	% 			Et rutrum ex euismod vel. Pellentesque ultricies, velit in fermentum
	% 			vestibulum, lectus nisi pretium nibh, sit amet aliquam lectus augue vel
	% 			velit.

	% 			\begin{enumerate}
	% 				\item \textbf{Morbi mauris purus}, egestas at vehicula et, convallis
	% 				accumsan orci. Orci varius natoque penatibus et magnis dis parturient
	% 				montes, nascetur ridiculus mus.
	% 				\item \textbf{Cras vehicula blandit urna ut maximus}. Aliquam blandit nec
	% 				massa ac sollicitudin. Curabitur cursus, metus nec imperdiet bibendum,
	% 				velit lectus faucibus dolor, quis gravida metus mauris gravida turpis.
	% 			\end{enumerate}

	% 			\begin{figure}
	% 				\centering
	% 				\begin{tikzpicture}
	% 					\begin{axis}[
	% 							scale only axis,
	% 							no markers,
	% 							domain=0:2*pi,
	% 							samples=100,
	% 							axis lines=center,
	% 							axis line style={-},
	% 							ticks=none]
	% 						\addplot[red] {sin(deg(x))};
	% 						\addplot[blue] {cos(deg(x))};
	% 					\end{axis}
	% 				\end{tikzpicture}
	% 				\caption{Another figure caption.}
	% 			\end{figure}

	% 		\end{block}

	% 	\end{column}

	% 	\separatorcolumn

	% 	\begin{column}{\colwidth}

	% 		\begin{block}{Nam cursus consequat egestas}

	% 			\begin{itemize}
	% 				\item \textbf{Sed consequat} id ante vel efficitur. Praesent congue massa
	% 				sed est scelerisque, elementum mollis augue iaculis.
	% 				\begin{itemize}
	% 					\item In sed est finibus, vulputate
	% 					nunc gravida, pulvinar lorem. In maximus nunc dolor, sed auctor eros
	% 					porttitor quis.
	% 					\item Fusce ornare dignissim nisi. Nam sit amet risus vel lacus
	% 					tempor tincidunt eu a arcu.
	% 					\item Donec rhoncus vestibulum erat, quis aliquam leo
	% 					gravida egestas.
	% 				\end{itemize}
	% 				\item \textbf{Sed luctus, elit sit amet} dictum maximus, diam dolor
	% 				faucibus purus, sed lobortis justo erat id turpis.
	% 				\item \textbf{Pellentesque facilisis dolor in leo} bibendum congue.
	% 				Maecenas congue finibus justo, vitae eleifend urna facilisis at.
	% 			\end{itemize}

	% 		\end{block}

	% 		\begin{exampleblock}{An example block containing some math}{}

	% 			Nullam non est elit. In eu ornare justo. Maecenas porttitor sodales lacus,
	% 			ut cursus augue sodales ac.

	% 			$$
	% 				\int_{-\infty}^{\infty} e^{-x^2}\,dx = \sqrt{\pi}
	% 			$$

	% 			\begin{enumerate}
	% 				\item \textbf{Morbi mauris purus}, egestas at vehicula et, convallis
	% 				accumsan orci. Orci varius natoque penatibus et magnis dis parturient
	% 				montes, nascetur ridiculus mus.
	% 				\item \textbf{Cras vehicula blandit urna ut maximus}. Aliquam blandit nec
	% 				massa ac sollicitudin. Curabitur cursus, metus nec imperdiet bibendum,
	% 				velit lectus faucibus dolor, quis gravida metus mauris gravida turpis.
	% 			\end{enumerate}

	% 			\heading{A heading inside a block}

	% 			Praesent consectetur mi $x^2 + y^2$ metus, nec vestibulum justo viverra
	% 			nec. Proin eget nulla pretium, egestas magna aliquam, mollis neque. Vivamus
	% 			dictum $\mathbf{u}^\intercal\mathbf{v}$ sagittis odio, vel porta erat
	% 			congue sed. Maecenas ut dolor quis arcu auctor porttitor.

	% 			\heading{Another heading inside a block}

	% 			Sed augue erat, scelerisque a purus ultricies, placerat porttitor neque.
	% 			Donec $P(y \mid x)$ fermentum consectetur $\nabla_x P(y \mid x)$ sapien
	% 			sagittis egestas. Duis eget leo euismod nunc viverra imperdiet nec id
	% 			justo.

	% 		\end{exampleblock}

	% 		\begin{block}{Nullam vel erat at velit convallis laoreet}

	% 			Class aptent taciti sociosqu ad litora torquent per conubia nostra, per
	% 			inceptos himenaeos. Phasellus libero enim, gravida sed erat sit amet,
	% 			scelerisque congue diam. Fusce dapibus dui ut augue pulvinar iaculis.

	% 			\begin{table}
	% 				\centering
	% 				\begin{tabular}{l r r c}
	% 					\toprule
	% 					\textbf{First column} & \textbf{Second column} & \textbf{Third column} & \textbf{Fourth} \\
	% 					\midrule
	% 					Foo                   & 13.37                  & 384,394               & $\alpha$        \\
	% 					Bar                   & 2.17                   & 1,392                 & $\beta$         \\
	% 					Baz                   & 3.14                   & 83,742                & $\delta$        \\
	% 					Qux                   & 7.59                   & 974                   & $\gamma$        \\
	% 					\bottomrule
	% 				\end{tabular}
	% 				\caption{A table caption.}
	% 			\end{table}

	% 			Donec quis posuere ligula. Nunc feugiat elit a mi malesuada consequat. Sed
	% 			imperdiet augue ac nibh aliquet tristique. Aenean eu tortor vulputate,
	% 			eleifend lorem in, dictum urna. Proin auctor ante in augue tincidunt
	% 			tempor. Proin pellentesque vulputate odio, ac gravida nulla posuere
	% 			efficitur. Aenean at velit vel dolor blandit molestie. Mauris laoreet
	% 			commodo quam, non luctus nibh ullamcorper in. Class aptent taciti sociosqu
	% 			ad litora torquent per conubia nostra, per inceptos himenaeos.

	% 			Nulla varius finibus volutpat. Mauris molestie lorem tincidunt, iaculis
	% 			libero at, gravida ante. Phasellus at felis eu neque suscipit suscipit.
	% 			Integer ullamcorper, dui nec pretium ornare, urna dolor consequat libero,
	% 			in feugiat elit lorem euismod lacus. Pellentesque sit amet dolor mollis,
	% 			auctor urna non, tempus sem.

	% 		\end{block}

	% 		\begin{block}{References}
	% 			% \printbibliography[heading=none]
	% 		\end{block}
	% 	\end{column}

	% 	\separatorcolumn
	% \end{columns}
\end{frame}
\end{document}

### 2023-10-22 poster/custom-defs.tex
:camera_flash: Add poster

% ====================
% BibLaTeX
% ====================

% \usepackage[backend=biber,
% 	bibstyle=authoryear,
% 	citestyle=authoryear,
% 	style=authoryear,
% 	maxcitenames=2,
% 	maxbibnames=20, % limit the length of list of names (authors/editors/etc.)
% 	sorting=ydnt, % sort references by year (descending), name, title
% 	dashed=false, % show authors instead of dash in publications having the same authors
% 	giveninits=true % render authors' given name initials and not the full given names
% ]{biblatex}
% %% Biblatex with Beamer bibliography icons
% \setbeamertemplate{bibliography item}{%
% 	\ifboolexpr{ test {\ifentrytype{book}} or test {\ifentrytype{mvbook}}
% 		or test {\ifentrytype{collection}} or test {\ifentrytype{mvcollection}}
% 		or test {\ifentrytype{reference}} or test {\ifentrytype{mvreference}} }
% 	{\setbeamertemplate{bibliography item}[book]}
% 	{\ifentrytype{online}
% 		{\setbeamertemplate{bibliography item}[online]}
% 		{\setbeamertemplate{bibliography item}[article]}}%
% 	\usebeamertemplate{bibliography item}}
% \defbibenvironment{bibliography}
% {\list{}
% 	{\settowidth{\labelwidth}{\usebeamertemplate{bibliography item}}%
% 		\setlength{\leftmargin}{\labelwidth}%
% 		\setlength{\labelsep}{\biblabelsep}%
% 		\addtolength{\leftmargin}{\labelsep}%
% 		\setlength{\itemsep}{\bibitemsep}%
% 		\setlength{\parsep}{\bibparsep}}}
% {\endlist}
% {\item}
% %% Redefine \refname
% \renewcommand{\bibname}{References}
% %% Redefine \parencite to use square brackets instead of braces
% \DeclareCiteCommand{\parencite}
% {\usebibmacro{prenote}}
% {\usebibmacro{citeindex}%
% 	\printtext[bibhyperref]{[\usebibmacro{cite}]}}
% {\multicitedelim}
% {\usebibmacro{postnote}}
% %% Highlight author names using Beamer data annotation
% %% Usage: add a new line `author+an = {<author-order>=highlight}` to an entry
% %% For example: author+an = {3=highlight} => highlight the 3rd author name
% \AtBeginBibliography{
% 	\renewcommand*{\mkbibnamegiven}[1]{%
% 		\ifitemannotation{highlight}
% 		{\textbf{#1}}
% 		{#1}%
% 	}

% 	\renewcommand*{\mkbibnamefamily}[1]{%
% 		\ifitemannotation{highlight}
% 		{\textbf{#1}}
% 		{#1}%
% 	}
% }

% ====================
% Boxes with tcolorbox
% ====================
\usepackage[most]{tcolorbox}

%%% Beamer colors in boxes

\newcommand{\beamercolorsinboxes}[1]{
	\setbeamercolor{itemize item}{fg=#1!75!black}
	\setbeamercolor{itemize/enumerate body}{fg=#1!65!white}
	\setbeamercolor{itemize/enumerate subbody}{fg=#1!65!white}
	\setbeamercolor{item projected}{fg=white, bg=#1!75!black}
}

%%% Highlight Oval Box
\newtcbox{\xmybox}[1][red]{on line,
	arc=7pt,colback=#1!10!white,colframe=#1!50!black,
	before upper={\rule[-3pt]{0pt}{10pt}},boxrule=1pt,
	boxsep=0pt,left=6pt,right=6pt,top=2pt,bottom=2pt}
%%% Box for stating problems
%%%%%%%%
%Usage: (similar for infobox)
%	\begin{defbox}{title}
%		contents
%	\end{defbox}
%%%%%%%%
\newtcolorbox{defbox}[1]{%
	enhanced,
	attach boxed title to top 	left={xshift=5mm,yshift=-5mm,yshifttext=-5mm},
	colback=cyan!5!white,
	colframe=cyan!75!black,
	coltitle=cyan!80!black,
	%	left=0mm,right=0mm,top=2mm,bottom=0mm,
	title={#1},
	fonttitle=\bfseries\large, fontupper=\color{cyan!65!white},
	boxed title style={colback=cyan!5!white,colframe=cyan!75!black},
	before upper={
			\beamercolorsinboxes{cyan}
		}
}%
%%% Box for announcement
\newtcolorbox{infobox}[1]{%
	enhanced,
	attach boxed title to top 	left={xshift=5mm,yshift=-5mm,yshifttext=-5mm},
	colback=yellow,
	colframe=red!75!black,
	coltitle=red!75!black,
	%	left=0mm,right=0mm,top=2mm,bottom=0mm,
	title={#1},
	fonttitle=\bfseries\large, fontupper=\color{red!65!white},
	boxed title style={colback=yellow,colframe=red!75!black},
	before upper={
			\beamercolorsinboxes{red}
		}
}%
%%% Box for example
\newtcolorbox{exabox}[1]{%
	enhanced,
	attach boxed title to top 	left={xshift=5mm,yshift=-5mm,yshifttext=-5mm},
	colframe=brown!75!black,colback=brown!5!white,coltitle=brown!50!brown!75!black,
	%	left=0mm,right=0mm,top=2mm,bottom=0mm,
	title={#1},
	fonttitle=\bfseries\large, fontupper=\color{brown!65!white},
	boxed title style={colback=brown!5!white,coltitle=brown!50!brown!75!black},
	before upper={
			\beamercolorsinboxes{brown}
		}
}%
%%% Theorem Box
%%%%%%%%
%Usage: (similar for conjecture, lemma, etc.)
%	\begin{thm}{title}{nameref}
%		contents
%	\end{thm}
% Use \ref{thm:nameref} to refer to the theorem
%%%%%%%%
%%%% Use \newtcbtheorem[number within=section]{thm} to number within each section
\newtcbtheorem[]{thm}%
% {Theorem}{attach boxed title to top 	left={xshift=5mm,yshift=-5mm,yshifttext=-5mm},
{Block}{attach boxed title to top 	left={xshift=5mm,yshift=-5mm,yshifttext=-5mm},
	enhanced jigsaw,
	top=2mm,bottom=6mm,left=0mm,right=0mm,
	% fonttitle=\bfseries\large,fontupper=\itshape\color{blue!65!white},
	fonttitle=\bfseries\large,fontupper=\color{blue!65!white},
	colframe=blue!75!black,colback=blue!5!white,coltitle=blue!50!blue!75!black,
	boxed title style={colback=blue!5!white,coltitle=blue!50!blue!75!black},
	before upper={
			\beamercolorsinboxes{blue}
		}
}{thm}%
%%% Proposition Box
\newtcbtheorem[use counter from=thm]{prop}%
{Proposition}{attach boxed title to top 	left={xshift=5mm,yshift=-5mm,yshifttext=-5mm},
	enhanced jigsaw,
	%	top=2mm,bottom=0mm,left=0mm,right=0mm,
	fonttitle=\bfseries\large,fontupper=\itshape,
	colframe=gray!75!black,colback=gray!5!white,coltitle=gray!50!gray!75!black,
	boxed title style={colback=gray!5!white,coltitle=gray!50!gray!75!black},
	before upper={
			\beamercolorsinboxes{gray}
		}
}{prop}%
%%% Conjecture Box
\newtcbtheorem[use counter from=thm]{conj}%
{Conjecture}{attach boxed title to top 	left={xshift=5mm,yshift=-5mm,yshifttext=-5mm},
	enhanced jigsaw,
	%	top=2mm,bottom=0mm,left=0mm,right=0mm,
	fonttitle=\bfseries\large,fontupper=\slshape,
	colframe=orange!75!black,colback=orange!5!white,coltitle=orange!50!orange!75!black,
	boxed title style={colback=orange!5!white,coltitle=orange!50!orange!75!black},
	before upper={
			\beamercolorsinboxes{orange}
		}
}{conj}%
%%% Lemma Box
\newtcbtheorem[use counter from=thm]{lem}%
{Lemma}{attach boxed title to top 	left={xshift=5mm,yshift=-5mm,yshifttext=-5mm},
	enhanced jigsaw,
	%	top=2mm,bottom=0mm,left=0mm,right=0mm,
	fonttitle=\bfseries\large,fontupper=\itshape,
	colframe=green!75!black,colback=green!5!white,coltitle=green!50!green!75!black,
	boxed title style={colback=green!5!white,coltitle=green!50!green!75!black},
	before upper={
			\beamercolorsinboxes{green}
		}
}{lem}%
%%% Claim Box
\newtcbtheorem[use counter from=thm]{clm}%
{Claim}{attach boxed title to top 	left={xshift=5mm,yshift=-5mm,yshifttext=-5mm},
	enhanced jigsaw,
	%	top=2mm,bottom=0mm,left=0mm,right=0mm,
	fonttitle=\bfseries\large,fontupper=\itshape,
	colframe=pink!75!black,colback=pink!5!white,coltitle=pink!50!pink!75!black,
	boxed title style={colback=pink!5!white,coltitle=pink!50!pink!75!black},
	before upper={
			\beamercolorsinboxes{pink}
		}
}{clm}%

### 2024-06-20 review/response.tex
:speech_balloon: Update response

@@
 
+\begin{reviewer}
+	\point RIS has been hailed as one of "the" 6G technologies by the academia, but much less so by the industry.
+How to do you see the potential of your scheme to change this, since it also speaks along the line of Ambient IoT?
+	\reply{
+		Many researchers and companies expect RIS to be a massive surface mounted to walls and windows, functioning as an all-purpose programmable RF lens to focus ambient waves on the target.
+		This, on paper, could mitigate two major challenges in 5G: reduce energy consumption of massive MIMO and improve channel condition for mmWave radios.
+		However, outdoor deployment of such large surfaces shall comply with local regulations and requires a cooperation between building constructors, network operators, and equipment vendors, which could be a long-term project.
+		Our RIScatter scheme, on the other hand, aims to unify RIS (wireless channel shaper) and backscatter device (information source) into one batteryless cognitive radio featuring heterogeneous traffic control and universal hardware design.
+		This is especially suitable for indoor environments where the scattering nodes can be geometrically distributed in the proximity of transceivers.
+		Imagine a wireless future where the boundary between the network and environment is blurred --- everything can be “smartened” by coating with a metamaterial layer and attaching a microcontroller.
+Only a few radiating sources (like the sun) are active, while most objects (like the universe) can exploit ambient waves to energize themselves, sense the environment, communicate with devices, and assist legacy transmissions when idle.
+		% Indoor deployment of RIS seems more feasible,
+		% For the indoor scenario, the cost-effectiveness of RIS over conventional relays remains an open question.
+		% This vision calls for a rethinking of waveform design, receiver architecture, and multiple access schemes to accommodate the new paradigm of ambient IoT.
+	}
+
+	\point We can think of a future in which a number of ambient IoT devices do not have a transmitter and instead they communicate based on backscattering.
+Where do you see the main challenges towards wide adoption of those devices?
+	\reply{
+		We would like to highlight three main challenges for batteryless ambient IoT devices: energy harvesting, spectrum sharing, and security issue.
+		Far-field wireless power transfer has been recognized as a promising solution to energize ultra-low power devices, but the operation range is quite short (within few meters) and the end-to-end power efficiency is usually low (less than few percents).
+		In such case, idle RIScatter nodes can operate in full RIS mode and redirect local RF waves to those in transmitting mode for higher energy efficiency and backscatter SNR.
+		Spectrum sharing with legacy wireless systems is another challenge, as backscatter devices manipulate existing radio signals to transmit data.
+		This raises concerns about potential interference with other wireless applications operating in the same spectrum, and calls for a rethinking of waveform design, receiver architecture, modulation and coding scheme, and multiple access strategy to ensure a symbiotic coexistence.
+		Finally, security issue is a major concern for batteryless devices since they are vulnerable to eavesdropping, jamming, and spoofing attacks.
+	}
+
+	\point What was the main criticism you have received during the review process and how did you address it?
+	\reply{
+		The main technical criticism we received during the review process was the uncompleteness of simulation results.
+		Reviewers were interested in the impact of imperfect CSI and primary/backscatter SNR on the achievable rate region.
+		Those results evaluate the practicality of RIScatter systems and have been added to the revised manuscript.
+		One reviewer also suggested including analytical and numerical results on BER vs SNR.
+		While we fully acknowledge its importance, the BER analysis is non-trivial due to the coexistence of both links, and we would like to reserve this for a future work.
+		Another interesting question was the optimal primary input distribution that maximizes the weighted sum mutual information.
+		It deserves further research but we decided to stay with CSCG primary source for a tractable rate expression.
+		Two reviewers also pointed out that perfect symbol-level synchronization of both links is a strong assumption, especially for large-scale RIScatter system with small spreading ratio.
+		If necessary, some penalty factor can be introduced to the rate expression to compensate for the synchronization error.
+	}
+
+\end{reviewer}
+
 \bibliographystyle{IEEEtran}
